### 2018-09-27 EquivCompFrameworks_20180911kc.tex
initial commit of tex file

% An equivalence of compositional frameworks
% John Baez, Kenny Courser and Christina Vasilakopoulou
% 2019/09/11 - KC

\documentclass{amsart}
\usepackage{amssymb,amsmath,stmaryrd,txfonts,mathrsfs,amsthm}

\usepackage[all,2cell]{xy}
\usepackage[neveradjust]{paralist}
\usepackage{hyperref}
\usepackage{mathtools}
\usepackage{multirow}
\usepackage[outline]{contour}
\contourlength{1.2pt}
\usepackage{tikz}
\usepackage{tikz-cd}
\usepackage{xcolor}
\usepackage{framed,color}
\usepackage[draft]{fixme}
\usetikzlibrary{matrix,arrows,decorations.pathmorphing,positioning}
\usetikzlibrary{intersections,decorations.markings}
\usetikzlibrary{arrows,positioning,fit,matrix,shapes.geometric,external}
\usetikzlibrary{backgrounds,circuits,circuits.ee.IEC,shapes,fit,matrix}
\usepackage{tikz}
\usepackage[all,2cell]{xy}
\usetikzlibrary{matrix,arrows}
\definecolor{rewritecolor}{rgb}{0,.9,1}
\tikzset{rewritenode/.style={shape=circle,fill=rewritecolor,scale=0.25,font=\Huge}}
\tikzset{RWopen/.style={shape=circle,draw=black,fill=white,scale=0.5,font=\Huge}}
\tikzset{RWclosed/.style={shape=circle,fill=black,scale=0.5,font=\Huge}}
\tikzset{CDnode/.style={shape=circle,fill=white,scale=.5}}
\makeatletter
\let\ea\expandafter

\pgfdeclarelayer{edgelayer}
\pgfdeclarelayer{nodelayer}
\pgfsetlayers{edgelayer,nodelayer,main}

% Petri nets
\definecolor{lblue}{rgb}{0,250,255}
\tikzstyle{species}=[circle,fill=yellow,draw=black,scale=1.15]
\tikzstyle{transition}=[rectangle,fill=lblue,draw=black,scale=1.15]
\tikzstyle{inarrow}=[->, >=stealth, shorten >=.03cm,line width=1.5]
\tikzstyle{empty}=[circle,fill=none, draw=none]
\tikzstyle{inputdot}=[circle,fill=purple,draw=purple, scale=.25]
\tikzstyle{inputarrow}=[->,draw=purple, shorten >=.05cm]
\tikzstyle{simple}=[-,draw=purple,line width=1.000]
\tikzstyle{none}=[inner sep=0pt]

\definecolor{shadecolor}{rgb}{1,0.8,0.3}
\definecolor{myurlcolor}{rgb}{0.6,0,0}
\definecolor{mycitecolor}{rgb}{0,0,0.8}
\definecolor{myrefcolor}{rgb}{0,0,0.8}
\hypersetup{colorlinks, linkcolor=myrefcolor, citecolor=mycitecolor, urlcolor=myurlcolor}

\tikzset{->-/.style={decoration={
  markings,
  mark=at position .5 with {\arrow{>}}},postaction={decorate}}}

%% Defining commands that are always in math mode.
\def\mdef#1#2{\ea\ea\ea\gdef\ea\ea\noexpand#1\ea{\ea\ensuremath\ea{#2}}}
\def\alwaysmath#1{\ea\ea\ea\global\ea\ea\ea\let\ea\ea\csname your@#1\endcsname\csname #1\endcsname
  \ea\def\csname #1\endcsname{\ensuremath{\csname your@#1\endcsname}}}

\newcommand{\define}[1]{{\bf \boldmath{#1}}}

% Script letters
\newcommand{\sA}{\ensuremath{\mathscr{A}}}
\newcommand{\sB}{\ensuremath{\mathscr{B}}}
\newcommand{\sC}{\ensuremath{\mathscr{C}}}
\newcommand{\sD}{\ensuremath{\mathscr{D}}}
\newcommand{\sE}{\ensuremath{\mathscr{E}}}
\newcommand{\sF}{\ensuremath{\mathscr{F}}}
\newcommand{\sG}{\ensuremath{\mathscr{G}}}
\newcommand{\sH}{\ensuremath{\mathscr{H}}}
\newcommand{\sI}{\ensuremath{\mathscr{I}}}
\newcommand{\sJ}{\ensuremath{\mathscr{J}}}
\newcommand{\sK}{\ensuremath{\mathscr{K}}}
\newcommand{\sL}{\ensuremath{\mathscr{L}}}
\newcommand{\sM}{\ensuremath{\mathscr{M}}}
\newcommand{\sN}{\ensuremath{\mathscr{N}}}
\newcommand{\sO}{\ensuremath{\mathscr{O}}}
\newcommand{\sP}{\ensuremath{\mathscr{P}}}
\newcommand{\sQ}{\ensuremath{\mathscr{Q}}}
\newcommand{\sR}{\ensuremath{\mathscr{R}}}
\newcommand{\sS}{\ensuremath{\mathscr{S}}}
\newcommand{\sT}{\ensuremath{\mathscr{T}}}
\newcommand{\sU}{\ensuremath{\mathscr{U}}}
\newcommand{\sV}{\ensuremath{\mathscr{V}}}
\newcommand{\sW}{\ensuremath{\mathscr{W}}}
\newcommand{\sX}{\ensuremath{\mathscr{X}}}
\newcommand{\sY}{\ensuremath{\mathscr{Y}}}
\newcommand{\sZ}{\ensuremath{\mathscr{Z}}}

% Calligraphic letters
\newcommand{\cA}{\ensuremath{\mathcal{A}}}
\newcommand{\cB}{\ensuremath{\mathcal{B}}}
\newcommand{\cC}{\ensuremath{\mathcal{C}}}
\newcommand{\cD}{\ensuremath{\mathcal{D}}}
\newcommand{\cE}{\ensuremath{\mathcal{E}}}
\newcommand{\cF}{\ensuremath{\mathcal{F}}}
\newcommand{\cG}{\ensuremath{\mathcal{G}}}
\newcommand{\cH}{\ensuremath{\mathcal{H}}}
\newcommand{\cI}{\ensuremath{\mathcal{I}}}
\newcommand{\cJ}{\ensuremath{\mathcal{J}}}
\newcommand{\cK}{\ensuremath{\mathcal{K}}}
\newcommand{\cL}{\ensuremath{\mathcal{L}}}
\newcommand{\cM}{\ensuremath{\mathcal{M}}}
\newcommand{\cN}{\ensuremath{\mathcal{N}}}
\newcommand{\cO}{\ensuremath{\mathcal{O}}}
\newcommand{\cP}{\ensuremath{\mathcal{P}}}
\newcommand{\cQ}{\ensuremath{\mathcal{Q}}}
\newcommand{\cR}{\ensuremath{\mathcal{R}}}
\newcommand{\cS}{\ensuremath{\mathcal{S}}}
\newcommand{\cT}{\ensuremath{\mathcal{T}}}
\newcommand{\cU}{\ensuremath{\mathcal{U}}}
\newcommand{\cV}{\ensuremath{\mathcal{V}}}
\newcommand{\cW}{\ensuremath{\mathcal{W}}}
\newcommand{\cX}{\ensuremath{\mathcal{X}}}
\newcommand{\cY}{\ensuremath{\mathcal{Y}}}
\newcommand{\cZ}{\ensuremath{\mathcal{Z}}}

% blackboard bold letters
\newcommand{\lA}{\ensuremath{\mathbb{A}}}
\newcommand{\lB}{\ensuremath{\mathbb{B}}}
\newcommand{\lC}{\ensuremath{\mathbb{C}}}
\newcommand{\lD}{\ensuremath{\mathbb{D}}}
\newcommand{\lE}{\ensuremath{\mathbb{E}}}
\newcommand{\lF}{\ensuremath{\mathbb{F}}}
\newcommand{\lG}{\ensuremath{\mathbb{G}}}
\newcommand{\lH}{\ensuremath{\mathbb{H}}}
\newcommand{\lI}{\ensuremath{\mathbb{I}}}
\newcommand{\lJ}{\ensuremath{\mathbb{J}}}
\newcommand{\lK}{\ensuremath{\mathbb{K}}}
\newcommand{\lL}{\ensuremath{\mathbb{L}}}
\newcommand{\lM}{\ensuremath{\mathbb{M}}}
\newcommand{\lN}{\ensuremath{\mathbb{N}}}
\newcommand{\lO}{\ensuremath{\mathbb{O}}}
\newcommand{\lP}{\ensuremath{\mathbb{P}}}
\newcommand{\lQ}{\ensuremath{\mathbb{Q}}}
\newcommand{\lR}{\ensuremath{\mathbb{R}}}
\newcommand{\lS}{\ensuremath{\mathbb{S}}}
\newcommand{\lT}{\ensuremath{\mathbb{T}}}
\newcommand{\lU}{\ensuremath{\mathbb{U}}}
\newcommand{\lV}{\ensuremath{\mathbb{V}}}
\newcommand{\lW}{\ensuremath{\mathbb{W}}}
\newcommand{\lX}{\ensuremath{\mathbb{X}}}
\newcommand{\lY}{\ensuremath{\mathbb{Y}}}
\newcommand{\lZ}{\ensuremath{\mathbb{Z}}}

% bold letters
\newcommand{\bA}{\ensuremath{\mathbf{A}}}
\newcommand{\bB}{\ensuremath{\mathbf{B}}}
\newcommand{\bC}{\ensuremath{\mathbf{C}}}
\newcommand{\bD}{\ensuremath{\mathbf{D}}}
\newcommand{\bE}{\ensuremath{\mathbf{E}}}
\newcommand{\bF}{\ensuremath{\mathbf{F}}}
\newcommand{\bG}{\ensuremath{\mathbf{G}}}
\newcommand{\bH}{\ensuremath{\mathbf{H}}}
\newcommand{\bI}{\ensuremath{\mathbf{I}}}
\newcommand{\bJ}{\ensuremath{\mathbf{J}}}
\newcommand{\bK}{\ensuremath{\mathbf{K}}}
\newcommand{\bL}{\ensuremath{\mathbf{L}}}
\newcommand{\bM}{\ensuremath{\mathbf{M}}}
\newcommand{\bN}{\ensuremath{\mathbf{N}}}
\newcommand{\bO}{\ensuremath{\mathbf{O}}}
\newcommand{\bP}{\ensuremath{\mathbf{P}}}
\newcommand{\bQ}{\ensuremath{\mathbf{Q}}}
\newcommand{\bR}{\ensuremath{\mathbf{R}}}
\newcommand{\bS}{\ensuremath{\mathbf{S}}}
\newcommand{\bT}{\ensuremath{\mathbf{T}}}
\newcommand{\bU}{\ensuremath{\mathbf{U}}}
\newcommand{\bV}{\ensuremath{\mathbf{V}}}
\newcommand{\bW}{\ensuremath{\mathbf{W}}}
\newcommand{\bX}{\ensuremath{\mathbf{X}}}
\newcommand{\bY}{\ensuremath{\mathbf{Y}}}
\newcommand{\bZ}{\ensuremath{\mathbf{Z}}}

% fraktur letters
\newcommand{\fa}{\ensuremath{\mathfrak{a}}}
\newcommand{\fb}{\ensuremath{\mathfrak{b}}}
\newcommand{\fc}{\ensuremath{\mathfrak{c}}}
\newcommand{\fd}{\ensuremath{\mathfrak{d}}}
\newcommand{\fe}{\ensuremath{\mathfrak{e}}}
\newcommand{\ff}{\ensuremath{\mathfrak{f}}}
\newcommand{\fg}{\ensuremath{\mathfrak{g}}}
\newcommand{\fh}{\ensuremath{\mathfrak{h}}}
\newcommand{\fj}{\ensuremath{\mathfrak{j}}}
\newcommand{\fk}{\ensuremath{\mathfrak{k}}}
\newcommand{\fl}{\ensuremath{\mathfrak{l}}}
\newcommand{\fm}{\ensuremath{\mathfrak{m}}}
\newcommand{\fn}{\ensuremath{\mathfrak{n}}}
\newcommand{\fo}{\ensuremath{\mathfrak{o}}}
\newcommand{\fp}{\ensuremath{\mathfrak{p}}}
\newcommand{\fq}{\ensuremath{\mathfrak{q}}}
\newcommand{\fr}{\ensuremath{\mathfrak{r}}}
\newcommand{\fs}{\ensuremath{\mathfrak{s}}}
\newcommand{\ft}{\ensuremath{\mathfrak{t}}}
\newcommand{\fu}{\ensuremath{\mathfrak{u}}}
\newcommand{\fv}{\ensuremath{\mathfrak{v}}}
\newcommand{\fw}{\ensuremath{\mathfrak{w}}}
\newcommand{\fx}{\ensuremath{\mathfrak{x}}}
\newcommand{\fy}{\ensuremath{\mathfrak{y}}}
\newcommand{\fz}{\ensuremath{\mathfrak{z}}}

\mdef\fahat{\hat{\fa}}

% Underline letters
\newcommand{\uA}{\ensuremath{\underline{A}}}
\newcommand{\uB}{\ensuremath{\underline{B}}}
\newcommand{\uC}{\ensuremath{\underline{C}}}
\newcommand{\uD}{\ensuremath{\underline{D}}}
\newcommand{\uE}{\ensuremath{\underline{E}}}
\newcommand{\uF}{\ensuremath{\underline{F}}}
\newcommand{\uG}{\ensuremath{\underline{G}}}
\newcommand{\uH}{\ensuremath{\underline{H}}}
\newcommand{\uI}{\ensuremath{\underline{I}}}
\newcommand{\uJ}{\ensuremath{\underline{J}}}
\newcommand{\uK}{\ensuremath{\underline{K}}}
\newcommand{\uL}{\ensuremath{\underline{L}}}
\newcommand{\uM}{\ensuremath{\underline{M}}}
\newcommand{\uN}{\ensuremath{\underline{N}}}
\newcommand{\uO}{\ensuremath{\underline{O}}}
\newcommand{\uP}{\ensuremath{\underline{P}}}
\newcommand{\uQ}{\ensuremath{\underline{Q}}}
\newcommand{\uR}{\ensuremath{\underline{R}}}
\newcommand{\uS}{\ensuremath{\underline{S}}}
\newcommand{\uT}{\ensuremath{\underline{T}}}
\newcommand{\uU}{\ensuremath{\underline{U}}}
\newcommand{\uV}{\ensuremath{\underline{V}}}
\newcommand{\uW}{\ensuremath{\underline{W}}}
\newcommand{\uX}{\ensuremath{\underline{X}}}
\newcommand{\uY}{\ensuremath{\underline{Y}}}
\newcommand{\uZ}{\ensuremath{\underline{Z}}}

% bars
\newcommand{\Abar}{\ensuremath{\overline{A}}}
\newcommand{\Bbar}{\ensuremath{\overline{B}}}
\newcommand{\Cbar}{\ensuremath{\overline{C}}}
\newcommand{\Dbar}{\ensuremath{\overline{D}}}
\newcommand{\Ebar}{\ensuremath{\overline{E}}}
\newcommand{\Fbar}{\ensuremath{\overline{F}}}
\newcommand{\Gbar}{\ensuremath{\overline{G}}}
\newcommand{\Hbar}{\ensuremath{\overline{H}}}
\newcommand{\Ibar}{\ensuremath{\overline{I}}}
\newcommand{\Jbar}{\ensuremath{\overline{J}}}
\newcommand{\Kbar}{\ensuremath{\overline{K}}}
\newcommand{\Lbar}{\ensuremath{\overline{L}}}
\newcommand{\Mbar}{\ensuremath{\overline{M}}}
\newcommand{\Nbar}{\ensuremath{\overline{N}}}
\newcommand{\Obar}{\ensuremath{\overline{O}}}
\newcommand{\Pbar}{\ensuremath{\overline{P}}}
\newcommand{\Qbar}{\ensuremath{\overline{Q}}}
\newcommand{\Rbar}{\ensuremath{\overline{R}}}
\newcommand{\Sbar}{\ensuremath{\overline{S}}}
\newcommand{\Tbar}{\ensuremath{\overline{T}}}
\newcommand{\Ubar}{\ensuremath{\overline{U}}}
\newcommand{\Vbar}{\ensuremath{\overline{V}}}
\newcommand{\Wbar}{\ensuremath{\overline{W}}}
\newcommand{\Xbar}{\ensuremath{\overline{X}}}
\newcommand{\Ybar}{\ensuremath{\overline{Y}}}
\newcommand{\Zbar}{\ensuremath{\overline{Z}}}
\newcommand{\abar}{\ensuremath{\overline{a}}}
\newcommand{\bbar}{\ensuremath{\overline{b}}}
\newcommand{\cbar}{\ensuremath{\overline{c}}}
\newcommand{\dbar}{\ensuremath{\overline{d}}}
\newcommand{\ebar}{\ensuremath{\overline{e}}}
\newcommand{\fbar}{\ensuremath{\overline{f}}}
\newcommand{\gbar}{\ensuremath{\overline{g}}}
%\newcommand{\hbar}{\ensuremath{\overline{h}}} % whoops, \hbar means something else!
\newcommand{\ibar}{\ensuremath{\overline{\imath}}}
\newcommand{\jbar}{\ensuremath{\overline{\jmath}}}
\newcommand{\kbar}{\ensuremath{\overline{k}}}
\newcommand{\lbar}{\ensuremath{\overline{l}}}
\newcommand{\mbar}{\ensuremath{\overline{m}}}
\newcommand{\nbar}{\ensuremath{\overline{n}}}
%\newcommand{\obar}{\ensuremath{\overline{o}}}
\newcommand{\pbar}{\ensuremath{\overline{p}}}
\newcommand{\qbar}{\ensuremath{\overline{q}}}
\newcommand{\rbar}{\ensuremath{\overline{r}}}
\newcommand{\sbar}{\ensuremath{\overline{s}}}
\newcommand{\tbar}{\ensuremath{\overline{t}}}
\newcommand{\ubar}{\ensuremath{\overline{u}}}
\newcommand{\vbar}{\ensuremath{\overline{v}}}
\newcommand{\wbar}{\ensuremath{\overline{w}}}
\newcommand{\xbar}{\ensuremath{\overline{x}}}
\newcommand{\ybar}{\ensuremath{\overline{y}}}
\newcommand{\zbar}{\ensuremath{\overline{z}}}

% tildes
\newcommand{\Atil}{\ensuremath{\widetilde{A}}}
\newcommand{\Btil}{\ensuremath{\widetilde{B}}}
\newcommand{\Ctil}{\ensuremath{\widetilde{C}}}
\newcommand{\Dtil}{\ensuremath{\widetilde{D}}}
\newcommand{\Etil}{\ensuremath{\widetilde{E}}}
\newcommand{\Ftil}{\ensuremath{\widetilde{F}}}
\newcommand{\Gtil}{\ensuremath{\widetilde{G}}}
\newcommand{\Htil}{\ensuremath{\widetilde{H}}}
\newcommand{\Itil}{\ensuremath{\widetilde{I}}}
\newcommand{\Jtil}{\ensuremath{\widetilde{J}}}
\newcommand{\Ktil}{\ensuremath{\widetilde{K}}}
\newcommand{\Ltil}{\ensuremath{\widetilde{L}}}
\newcommand{\Mtil}{\ensuremath{\widetilde{M}}}
\newcommand{\Ntil}{\ensuremath{\widetilde{N}}}
\newcommand{\Otil}{\ensuremath{\widetilde{O}}}
\newcommand{\Ptil}{\ensuremath{\widetilde{P}}}
\newcommand{\Qtil}{\ensuremath{\widetilde{Q}}}
\newcommand{\Rtil}{\ensuremath{\widetilde{R}}}
\newcommand{\Stil}{\ensuremath{\widetilde{S}}}
\newcommand{\Ttil}{\ensuremath{\widetilde{T}}}
\newcommand{\Util}{\ensuremath{\widetilde{U}}}
\newcommand{\Vtil}{\ensuremath{\widetilde{V}}}
\newcommand{\Wtil}{\ensuremath{\widetilde{W}}}
\newcommand{\Xtil}{\ensuremath{\widetilde{X}}}
\newcommand{\Ytil}{\ensuremath{\widetilde{Y}}}
\newcommand{\Ztil}{\ensuremath{\widetilde{Z}}}
\newcommand{\atil}{\ensuremath{\widetilde{a}}}
\newcommand{\btil}{\ensuremath{\widetilde{b}}}
\newcommand{\ctil}{\ensuremath{\widetilde{c}}}
\newcommand{\dtil}{\ensuremath{\widetilde{d}}}
\newcommand{\etil}{\ensuremath{\widetilde{e}}}
\newcommand{\ftil}{\ensuremath{\widetilde{f}}}
\newcommand{\gtil}{\ensuremath{\widetilde{g}}}
\newcommand{\htil}{\ensuremath{\widetilde{h}}}
\newcommand{\itil}{\ensuremath{\widetilde{\imath}}}
\newcommand{\jtil}{\ensuremath{\widetilde{\jmath}}}
\newcommand{\ktil}{\ensuremath{\widetilde{k}}}
\newcommand{\ltil}{\ensuremath{\widetilde{l}}}
\newcommand{\mtil}{\ensuremath{\widetilde{m}}}
\newcommand{\ntil}{\ensuremath{\widetilde{n}}}
\newcommand{\otil}{\ensuremath{\widetilde{o}}}
\newcommand{\ptil}{\ensuremath{\widetilde{p}}}
\newcommand{\qtil}{\ensuremath{\widetilde{q}}}
\newcommand{\rtil}{\ensuremath{\widetilde{r}}}
\newcommand{\stil}{\ensuremath{\widetilde{s}}}
\newcommand{\ttil}{\ensuremath{\widetilde{t}}}
\newcommand{\util}{\ensuremath{\widetilde{u}}}
\newcommand{\vtil}{\ensuremath{\widetilde{v}}}
\newcommand{\wtil}{\ensuremath{\widetilde{w}}}
\newcommand{\xtil}{\ensuremath{\widetilde{x}}}
\newcommand{\ytil}{\ensuremath{\widetilde{y}}}
\newcommand{\ztil}{\ensuremath{\widetilde{z}}}

% Hats
\newcommand{\Ahat}{\ensuremath{\widehat{A}}}
\newcommand{\Bhat}{\ensuremath{\widehat{B}}}
\newcommand{\Chat}{\ensuremath{\widehat{C}}}
\newcommand{\Dhat}{\ensuremath{\widehat{D}}}
\newcommand{\Ehat}{\ensuremath{\widehat{E}}}
\newcommand{\Fhat}{\ensuremath{\widehat{F}}}
\newcommand{\Ghat}{\ensuremath{\widehat{G}}}
\newcommand{\Hhat}{\ensuremath{\widehat{H}}}
\newcommand{\Ihat}{\ensuremath{\widehat{I}}}
\newcommand{\Jhat}{\ensuremath{\widehat{J}}}
\newcommand{\Khat}{\ensuremath{\widehat{K}}}
\newcommand{\Lhat}{\ensuremath{\widehat{L}}}
\newcommand{\Mhat}{\ensuremath{\widehat{M}}}
\newcommand{\Nhat}{\ensuremath{\widehat{N}}}
\newcommand{\Ohat}{\ensuremath{\widehat{O}}}
\newcommand{\Phat}{\ensuremath{\widehat{P}}}
\newcommand{\Qhat}{\ensuremath{\widehat{Q}}}
\newcommand{\Rhat}{\ensuremath{\widehat{R}}}
\newcommand{\Shat}{\ensuremath{\widehat{S}}}
\newcommand{\That}{\ensuremath{\widehat{T}}}
\newcommand{\Uhat}{\ensuremath{\widehat{U}}}
\newcommand{\Vhat}{\ensuremath{\widehat{V}}}
\newcommand{\What}{\ensuremath{\widehat{W}}}
\newcommand{\Xhat}{\ensuremath{\widehat{X}}}
\newcommand{\Yhat}{\ensuremath{\widehat{Y}}}
\newcommand{\Zhat}{\ensuremath{\widehat{Z}}}
\newcommand{\ahat}{\ensuremath{\hat{a}}}
\newcommand{\bhat}{\ensuremath{\hat{b}}}
\newcommand{\chat}{\ensuremath{\hat{c}}}
\newcommand{\dhat}{\ensuremath{\hat{d}}}
\newcommand{\ehat}{\ensuremath{\hat{e}}}
\newcommand{\fhat}{\ensuremath{\hat{f}}}
\newcommand{\ghat}{\ensuremath{\hat{g}}}
\newcommand{\hhat}{\ensuremath{\hat{h}}}
\newcommand{\ihat}{\ensuremath{\hat{\imath}}}
\newcommand{\jhat}{\ensuremath{\hat{\jmath}}}
\newcommand{\khat}{\ensuremath{\hat{k}}}
\newcommand{\lhat}{\ensuremath{\hat{l}}}
\newcommand{\mhat}{\ensuremath{\hat{m}}}
\newcommand{\nhat}{\ensuremath{\hat{n}}}
\newcommand{\ohat}{\ensuremath{\hat{o}}}
\newcommand{\phat}{\ensuremath{\hat{p}}}
\newcommand{\qhat}{\ensuremath{\hat{q}}}
\newcommand{\rhat}{\ensuremath{\hat{r}}}
\newcommand{\shat}{\ensuremath{\hat{s}}}
\newcommand{\that}{\ensuremath{\hat{t}}}
\newcommand{\uhat}{\ensuremath{\hat{u}}}
\newcommand{\vhat}{\ensuremath{\hat{v}}}
\newcommand{\what}{\ensuremath{\hat{w}}}
\newcommand{\xhat}{\ensuremath{\hat{x}}}
\newcommand{\yhat}{\ensuremath{\hat{y}}}
\newcommand{\zhat}{\ensuremath{\hat{z}}}

%% FONTS AND DECORATION FOR GREEK LETTERS

%% the package `mathbbol' gives us blackboard bold greek and numbers,
%% but it does it by redefining \mathbb to use a different font, so that
%% all the other \mathbb letters look different too.  Here we import the
%% font with bb greek and numbers, but assign it a different name,
%% \mathbbb, so as not to replace the usual one.
\DeclareSymbolFont{bbold}{U}{bbold}{m}{n}
\DeclareSymbolFontAlphabet{\mathbbb}{bbold}
\newcommand{\bbDelta}{\ensuremath{\mathbbb{\Delta}}}
\newcommand{\bbone}{\ensuremath{\mathbbb{1}}}
\newcommand{\bbtwo}{\ensuremath{\mathbbb{2}}}
\newcommand{\bbthree}{\ensuremath{\mathbbb{3}}}

% greek with bars
\newcommand{\albar}{\ensuremath{\overline{\alpha}}}
\newcommand{\bebar}{\ensuremath{\overline{\beta}}}
\newcommand{\gmbar}{\ensuremath{\overline{\gamma}}}
\newcommand{\debar}{\ensuremath{\overline{\delta}}}
\newcommand{\phibar}{\ensuremath{\overline{\varphi}}}
\newcommand{\psibar}{\ensuremath{\overline{\psi}}}
\newcommand{\xibar}{\ensuremath{\overline{\xi}}}
\newcommand{\ombar}{\ensuremath{\overline{\omega}}}

% greek with hats
\newcommand{\alhat}{\ensuremath{\hat{\alpha}}}
\newcommand{\behat}{\ensuremath{\hat{\beta}}}
\newcommand{\gmhat}{\ensuremath{\hat{\gamma}}}
\newcommand{\dehat}{\ensuremath{\hat{\delta}}}

% greek with checks
\newcommand{\alchk}{\ensuremath{\check{\alpha}}}
\newcommand{\bechk}{\ensuremath{\check{\beta}}}
\newcommand{\gmchk}{\ensuremath{\check{\gamma}}}
\newcommand{\dechk}{\ensuremath{\check{\delta}}}

% greek with tildes
\newcommand{\altil}{\ensuremath{\widetilde{\alpha}}}
\newcommand{\betil}{\ensuremath{\widetilde{\beta}}}
\newcommand{\gmtil}{\ensuremath{\widetilde{\gamma}}}
\newcommand{\phitil}{\ensuremath{\widetilde{\varphi}}}
\newcommand{\psitil}{\ensuremath{\widetilde{\psi}}}
\newcommand{\xitil}{\ensuremath{\widetilde{\xi}}}
\newcommand{\omtil}{\ensuremath{\widetilde{\omega}}}

% MISCELLANEOUS SYMBOLS
\mdef\del{\partial}
\mdef\delbar{\overline{\partial}}
\let\sm\wedge
\newcommand{\dd}[1]{\ensuremath{\frac{\partial}{\partial {#1}}}}
\newcommand{\inv}{^{-1}}
\newcommand{\dual}{^{\vee}}
\mdef\hf{\textstyle\frac{1}{2}}
\mdef\thrd{\textstyle\frac{1}{3}}
\mdef\qtr{\textstyle\frac{1}{4}}
\let\meet\wedge
\let\join\vee
\let\dn\downarrow
\newcommand{\op}{^{\mathit{op}}}
\newcommand{\co}{^{\mathit{co}}}
\newcommand{\coop}{^{\mathit{coop}}}
\newcommand{\id}{\mathm{id}}
\let\adj\dashv
\SelectTips{cm}{}
\newdir{ >}{{}*!/-10pt/@{>}}    % extra spacing for tail arrows in XYpic
\newcommand{\pushoutcorner}[1][dr]{\save*!/#1+1.2pc/#1:(1,-1)@^{|-}\restore}
\newcommand{\pullbackcorner}[1][dr]{\save*!/#1-1.2pc/#1:(-1,1)@^{|-}\restore}
\let\iso\cong
\let\eqv\simeq
\let\cng\equiv
\mdef\Id{\mathrm{Id}}
\mdef\id{\mathrm{id}}
\alwaysmath{ell}
\alwaysmath{infty}
\alwaysmath{odot}
\def\frc#1/#2.{\frac{#1}{#2}}   % \frc x^2+1 / x^2-1 .
\mdef\ten{\mathrel{\otimes}}
\mdef\bigten{\bigotimes}
\mdef\sqten{\mathrel{\boxtimes}}
\def\pow(#1,#2){\mathop{\pitchfork}(#1,#2)} % powers and
\def\cpw{\mathop{\odot}}                    % copowers

%% OPERATORS
\DeclareMathOperator\lan{Lan}
\DeclareMathOperator\ran{Ran}
\DeclareMathOperator\colim{colim}
\DeclareMathOperator\coeq{coeq}
\DeclareMathOperator\eq{eq}
\DeclareMathOperator\Tot{Tot}
\DeclareMathOperator\cosk{cosk}
\DeclareMathOperator\sk{sk}
\DeclareMathOperator\im{im}
\DeclareMathOperator\Spec{Spec}
\DeclareMathOperator\Ho{Ho}
\DeclareMathOperator\Aut{Aut}
\DeclareMathOperator\End{End}
\DeclareMathOperator\Hom{Hom}
\DeclareMathOperator\Map{Map}

%% ARROWS
% \to already exists
\newcommand{\too}[1][]{\ensuremath{\overset{#1}{\longrightarrow}}}
\newcommand{\ot}{\ensuremath{\leftarrow}}
\newcommand{\oot}[1][]{\ensuremath{\overset{#1}{\longleftarrow}}}
\let\toot\rightleftarrows
\let\otto\leftrightarrows
\let\Impl\Rightarrow
\let\imp\Rightarrow
\let\toto\rightrightarrows
\let\into\hookrightarrow
\let\xinto\xhookrightarrow
\mdef\we{\overset{\sim}{\longrightarrow}}
\mdef\leftwe{\overset{\sim}{\longleftarrow}}
\let\mono\rightarrowtail
\let\leftmono\leftarrowtail
\let\cof\rightarrowtail
\let\leftcof\leftarrowtail
\let\epi\twoheadrightarrow
\let\leftepi\twoheadleftarrow
\let\fib\twoheadrightarrow
\let\leftfib\twoheadleftarrow
\let\cohto\rightsquigarrow
\let\maps\colon
\newcommand{\spam}{\,:\!}       % \maps for left arrows

%% EXTENSIBLE ARROWS
\let\xto\xrightarrow
\let\xot\xleftarrow
% See Voss' Mathmode.tex for instructions on how to create new
% extensible arrows.
\def\rightarrowtailfill@{\arrowfill@{\Yright\joinrel\relbar}\relbar\rightarrow}
\newcommand\xrightarrowtail[2][]{\ext@arrow 0055{\rightarrowtailfill@}{#1}{#2}}
\let\xmono\xrightarrowtail
\let\xcof\xrightarrowtail
\def\twoheadrightarrowfill@{\arrowfill@{\relbar\joinrel\relbar}\relbar\twoheadrightarrow}
\newcommand\xtwoheadrightarrow[2][]{\ext@arrow 0055{\twoheadrightarrowfill@}{#1}{#2}}
\let\xepi\xtwoheadrightarrow
\let\xfib\xtwoheadrightarrow
% Let's leave the left-going ones until I need them.

%% EXTENSIBLE SLASHED ARROWS
% Making extensible slashed arrows, by modifying the underlying AMS code.
% Arguments are:
% 1 = arrowhead on the left (\relbar or \Relbar if none)
% 2 = fill character (usually \relbar or \Relbar)
% 3 = slash character (such as \mapstochar or \Mapstochar)
% 4 = arrowhead on the left (\relbar or \Relbar if none)
% 5 = display mode (\displaystyle etc)
\def\slashedarrowfill@#1#2#3#4#5{%
  $\m@th\thickmuskip0mu\medmuskip\thickmuskip\thinmuskip\thickmuskip
   \relax#5#1\mkern-7mu%
   \cleaders\hbox{$#5\mkern-2mu#2\mkern-2mu$}\hfill
   \mathclap{#3}\mathclap{#2}%
   \cleaders\hbox{$#5\mkern-2mu#2\mkern-2mu$}\hfill
   \mkern-7mu#4$%
}
% Here's the idea: \<slashed>arrowfill@ should be a box containing
% some stretchable space that is the "middle of the arrow".  This
% space is created as a "leader" using \cleader<thing>\hfill, which
% fills an \hfill of space with copies of <thing>.  Here instead of
% just one \cleader, we use two, with the slash in between (and an
% extra copy of the filler, to avoid extra space around the slash).
\def\rightslashedarrowfill@{%
  \slashedarrowfill@\relbar\relbar\mapstochar\rightarrow}
\newcommand\xslashedrightarrow[2][]{%
  \ext@arrow 0055{\rightslashedarrowfill@}{#1}{#2}}
\mdef\hto{\xslashedrightarrow{}}
\mdef\htoo{\xslashedrightarrow{\quad}}
\let\xhto\xslashedrightarrow

%% To get a slashed arrow in XYpic, do
% \[\xymatrix{A \ar[r]|-@{|} & B}\]

% ISOMORPHISMS
\def\xiso#1{\mathrel{\mathrlap{\smash{\xto[\smash{\raisebox{1.3mm}{$\scriptstyle\sim$}}]{#1}}}\hphantom{\xto{#1}}}}
\def\toiso{\xto{\smash{\raisebox{-.5mm}{$\scriptstyle\sim$}}}}

% SHADOWS
\def\shvar#1#2{{\ensuremath{%
  \hspace{1mm}\makebox[-1mm]{$#1\langle$}\makebox[0mm]{$#1\langle$}\hspace{1mm}%
  {#2}%
  \makebox[1mm]{$#1\rangle$}\makebox[0mm]{$#1\rangle$}%
}}}
\def\sh{\shvar{}}
\def\scriptsh{\shvar{\scriptstyle}}
\def\bigsh{\shvar{\big}}
\def\Bigsh{\shvar{\Big}}
\def\biggsh{\shvar{\bigg}}
\def\Biggsh{\shvar{\Bigg}}

% THEOREM-TYPE ENVIRONMENTS, hacked to
%% (a) number all with the same numbers, and
%% (b) have the right names for autoref
\def\defthm#1#2{%
  \newtheorem{#1}{#2}[section]%
  \expandafter\def\csname #1autorefname\endcsname{#2}%
  \expandafter\let\csname c@#1\endcsname\c@thm}
\newtheorem{thm}{Theorem}[section]
\newcommand{\thmautorefname}{Theorem}
\defthm{cor}{Corollary}
\defthm{prop}{Proposition}
\defthm{lem}{Lemma}
\defthm{sch}{Scholium}
\defthm{assume}{Assumption}
\defthm{claim}{Claim}
\defthm{conj}{Conjecture}
\defthm{hyp}{Hypothesis}
\defthm{fact}{Fact}
\theoremstyle{definition}
\defthm{defn}{Definition}
\defthm{notn}{Notation}
\theoremstyle{remark}
\defthm{rmk}{Remark}
\defthm{eg}{Example}
\defthm{egs}{Examples}
\defthm{ex}{Exercise}
\defthm{ceg}{Counterexample}

% How to get QED symbols inside equations at the end of the statements
% of theorems.  AMS LaTeX knows how to do this inside equations at the
% end of *proofs* with \qedhere, and at the end of the statement of a
% theorem with \qed (meaning no proof will be given), but it can't
% seem to combine the two.  Use this instead.
\def\thmqedhere{\expandafter\csname\csname @currenvir\endcsname @qed\endcsname}

% Number numbered lists as (i), (ii), ...
\renewcommand{\theenumi}{(\roman{enumi})}
\renewcommand{\labelenumi}{\theenumi}

%% Labeling that keeps track of theorem-type names.  Superseded by
%% autoref from hyperref, as above, but we keep this in case we are
%% using a journal style file that is incompatible with hyperref.
% 
% \ifx\SK@label\undefined\let\SK@label\label\fi
% \let\your@thm\@thm
% \def\@thm#1#2#3{\gdef\currthmtype{#3}\your@thm{#1}{#2}{#3}}
% \def\xlabel#1{{\let\your@currentlabel\@currentlabel\def\@currentlabel
% {\currthmtype~\your@currentlabel}
% \SK@label{#1@}}\label{#1}}
% \def\xref#1{\ref{#1@}}

% Also number formulas with the theorem counter
\let\c@equation\c@thm
\numberwithin{equation}{section}

% Only show numbers for equations that are actually referenced (or
% whose tags are specified manually) - uses mathtools.
\mathtoolsset{showonlyrefs,showmanualtags}

%% Fix enumerate spacing with paralist.  This has two parts:
%%   1. enable mixing of "old spacing" lists with those adjusted by paralist
%%   2. allow us to specify a number based on which to adjust the spacing
%% For the first, use \killspacingtrue when you want the spacing
%% adjusted, then \killspacingfalse to turn adjustment off.  For the
%% second, use \maxenum=14 to set the widest number you want the
%% spacing to be calculated with.
\newlength\oldleftmargini       % save old spacing
\newlength\oldleftmarginii
\newlength\oldleftmarginiii
\newlength\oldleftmarginiv
\newlength\oldleftmarginv
\newlength\oldleftmarginvi
\newcount\maxenum
\maxenum=7
\newif\ifkillspacing
\def\@adjust@enum@labelwidth{%
  \advance\@listdepth by 1\relax
  \ifkillspacing                % do the paralist thing
    \csname c@\@enumctr\endcsname\maxenum
    \settowidth{\@tempdima}{%
      \csname label\@enumctr\endcsname\hspace{\labelsep}}%
    \csname leftmargin\romannumeral\@listdepth\endcsname
      \@tempdima
  \else                         % otherwise, reset it
    \csname fixspacing\romannumeral\@listdepth\endcsname
  \fi
  \advance\@listdepth by -1\relax}
% these commands, one for each enum level (I couldn't get a generic
% one to work), test whether oldleftmargin has been set yet, and if
% not, set it from leftmargin; otherwise, they reset leftmargin to
% it.  Just setting oldleftmargin to leftmargin in the preamble
% doesn't seem to work.
\def\fixspacingi{\ifnum\oldleftmargini=0\setlength\oldleftmargini\leftmargini\else\setlength\leftmargini\oldleftmargini\fi}
\def\fixspacingii{\ifnum\oldleftmarginii=0\setlength\oldleftmarginii\leftmarginii\else\setlength\leftmarginii\oldleftmarginii\fi}
\def\fixspacingiii{\ifnum\oldleftmarginiii=0\setlength\oldleftmarginiii\leftmarginiii\else\setlength\leftmarginiii\oldleftmarginiii\fi}
\def\fixspacingiv{\ifnum\oldleftmarginiv=0\setlength\oldleftmarginiv\leftmarginiv\else\setlength\leftmarginiv\oldleftmarginiv\fi}
\def\fixspacingv{\ifnum\oldleftmarginv=0\setlength\oldleftmarginv\leftmarginv\else\setlength\leftmarginv\oldleftmarginv\fi}
\def\fixspacingvi{\ifnum\oldleftmarginvi=0\setlength\oldleftmarginvi\leftmarginvi\else\setlength\leftmarginvi\oldleftmarginvi\fi}

%% Fix paralist references, so that we can refer to (1) instead of
%% just 1.
\def\pl@label#1#2{%
  \edef\pl@the{\noexpand#1{\@enumctr}}%
  \pl@lab\expandafter{\the\pl@lab\csname yourthe\@enumctr\endcsname}%
  \advance\@tempcnta1
  \pl@loop}
\def\@enumlabel@#1[#2]{%
  \@plmylabeltrue
  \@tempcnta0
  \pl@lab{}%
  \let\pl@the\pl@qmark
  \expandafter\pl@loop\@gobble#2\@@@
  \ifnum\@tempcnta=1\else
    \PackageWarning{paralist}{Incorrect label; no or multiple
      counters.\MessageBreak The label is: \@gobble#2}%
  \fi
  \expandafter\edef\csname label\@enumctr\endcsname{\the\pl@lab}%
  \expandafter\edef\csname the\@enumctr\endcsname{\the\pl@lab}%
  \expandafter\let\csname yourthe\@enumctr\endcsname\pl@the
  #1}

\def\tobar{\mathrel{\mkern3mu  \vcenter{\hbox{$\scriptscriptstyle+$}}%
                    \mkern-12mu{\to}}}

%\input{decls}
\UseAllTwocells

\newcommand{\dblcat}[1]{\mathbb{#1}}
\mdef\fchk{\check{f}}

\title{An equivalence of compositional frameworks}

\begin{document}
\maketitle

\begin{center}   
 % {\bf Structured cospans \\}   
  \vspace{0.3cm}
  {\em John\ C.\ Baez \\}
  \vspace{0.3cm}
  {\small
 Department of Mathematics \\
    University of California \\
  Riverside CA, USA 92521 \\ and \\
 Centre for Quantum Technologies  \\
  National University of Singapore \\
    Singapore 117543  \\    } 
 \vspace{0.4cm}
{\em Kenny Courser \\}
\vspace{0.3cm}
   {\small
  Department of Mathematics \\
  University of California \\
  Riverside CA, USA 92521 \\}
  \vspace{0.4cm}   
{\em Christina Vasilakopoulou \\}
\vspace{0.3cm}
   {\small
  Department of Mathematics \\
  University of California \\
  Riverside CA, USA 92521 \\}
  \vspace{0.3cm}   
  {\small email: baez@math.ucr.edu, courser@math.ucr.edu, vasilak@ucr.edu\\} 
  \vspace{0.3cm}   
  {\small \today}
  \vspace{0.3cm}   
\end{center}

\begin{abstract}
\noindent
The first two authors have developed a compositional framework well-suited for studying networks that are built out of finite sets equipped with extra stuff. This framework, which goes by the name of `structured cospans', utilizes double categories where the objects are seen as inputs and outputs, morphisms are `open networks', and 2-morphisms are maps between open networks. In this setup a functor $L \colon \bold{C} \to \bold{D}$, which is typically a left adjoint, is used to replace the objects and vertical 1-morphisms of a given double category $\mathbb{D}$ with the objects and morphisms, respectively, of the category $\bold{C}$. Horizontal 1-cells are then cospans in $\bold{D}$ of a particular form with 2-morphisms given by maps of these cospans. Fong has also developed a similar framework which also uses cospans and goes by the name of `decorated cospans'. In this setup, a lax monoidal functor $F \colon \bold{C} \to \bold{E}$ is used to `decorate' the apices of cospans in $\bold{C}$ with elements of $\bold{E}$ giving the cospans extra structure. Using a slight variation of Fong's framework, we prove that these two frameworks are equivalent in the situation where a left adjoint can be obtained from a lax monoidal pseudofunctor using a well known construction of Grothendieck.
\end{abstract}

\section{Introduction}
Networks are playing an increasingly prominent role in our understanding of the world and as a result, methods of characterizing and studying networks have become evermore necessary. Applied category theory provides such an avenue and much work has been done towards this effort  \cite{BC,BCR,BF,BFP,BP,Cour,Fong,JM,LS,Yass}. One of the more recent frameworks developed suitable for studying networks is Fong's `decorated cospans' \cite{Fong}. A $\textbf{cospan}$ in any category is a diagram of the form:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,1) {$c$};
\node (C) at (2,0) {$b$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B);
\end{tikzpicture}
\]
We call $c$ the $\textbf{apex}$ of the cospan and $a$ and $b$ the $\textbf{feet}$ of the cospan. The morphisms $i$ and $o$ are called the $\textbf{legs}$. Cospans are ideal for realizing networks and more generally `open' systems where here open means each system or network comes with prescribed inputs and outputs which are represented by the feet of the cospan $a$ and $b$, respectively. Two open systems viewed as cospans such that the outputs of the first and the inputs of the second coincide can then naturally be composed via pushout. For example, we can compose the above cospan with the following:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$b$};
\node (B) at (1,1) {$f$};
\node (C) at (2,0) {$e$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i^\prime$} (B)
(C) edge node[above]{$o^\prime$} (B);
\end{tikzpicture}
\]
to obtain a new cospan whose left foot is the left foot of the first, whose right foot is the right foot of the second, and whose apex and legs are given by the pushout.
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,1) {$c$};
\node (C) at (2,0) {$b$};
\node (D) at (3,1) {$f$};
\node (E) at (4,0) {$e$};
\node (F) at (2,2) {$c+_b f$};
\node (G) at (2,1.25) {$c+f$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B)
(C) edge node[above]{$i^\prime$} (D)
(E) edge node[above]{$o^\prime$} (D)
(B) edge node[left]{$\psi j_c$} (F)
(D) edge node[right]{$\psi j_f$} (F)
(B) edge node[above]{$j_c$} (G)
(D) edge node[above]{$j_f$} (G)
(G) edge node [left] {$\psi$} (F);
\end{tikzpicture}
\]

In Fong's theory of decorated cospans, given a category $\bold{C}$ with finite colmits, a symmetric lax monoidal functor $F \colon (\bold{C},+,0) \to (\bold{D},\otimes,I)$ is used to `decorate' the apex of a cospan in $\bold{C}$ with an element of the image of its apex under the functor $F$, in the case of the first cospan above, a morphism $d \colon I \to F(c)$. Here $F(c)$ is the collection of all $F$-decorations on the object $c$ and the morphism $d$ is selecting a particular one. Thus a decorated cospan is then a pair:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,1) {$c$};
\node (C) at (2,0) {$b$};
\node (D) at (3,0.5) {$I$};
\node (E) at (4,0.5) {$F(c)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B)
(D) edge node [above] {$d$} (E);
\end{tikzpicture}
\]
To obtain a decoration on the composition of two composable $F$-decorated cospans:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,1) {$c$};
\node (C) at (2,0) {$b$};
\node (F) at (3,0) {$b$};
\node (G) at (4,1) {$f$};
\node (H) at (5,0) {$e$};
\node (D) at (0.5,-0.5) {$I$};
\node (E) at (1.5,-0.5) {$F(c)$};
\node (D') at (3.5,-0.5) {$I$};
\node (E') at (4.5,-0.5) {$F(f)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B)
(F) edge node[above]{$i^\prime$} (G)
(H) edge node[above]{$o^\prime$} (G)
(D) edge node [above] {$d_1$} (E)
(D') edge node [above] {$d_2$} (E');
\end{tikzpicture}
\]
we use the natural map from a coproduct to a pushout as well as the natural map that comes as part of the structure of a lax monoidal functor:
 $$1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{d_1 \times d_2} F(c) \times F(f) \xrightarrow{\phi_{c,f}} F(c+ f) \xrightarrow{F(j_{c,f})} F(c+_b f).$$

From this symmetric lax monoidal functor $F \colon \bold{C} \to \bold{D}$, Fong then constructs a symmetric monoidal category $F\textnormal{Cospan}(\bold{C})$ which has:
\begin{enumerate}
\item{objects as those of $\bold{C}$ and}
\item{morphisms as isomorphism classes of $F$-decorated cospans, where an $F$-decorated cospan is given as above, and two $F$-decorated cospans are in the same isomorphism class if there exists an isomorphism between the apices such that the following diagrams commute:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,1) {$c$};
\node (B') at (1,-1) {$c^\prime$};
\node (C) at (2,0) {$b$};
\node (D) at (3,0) {$I$};
\node (E) at (4,0.5) {$F(c)$};
\node (E') at (4,-0.5) {$F(c^\prime)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B)
(A) edge node[below]{$i^\prime$} (B')
(C) edge node[below]{$o^\prime$} (B')
(B) edge node [left] {$f$} (B')
(D) edge node [above] {$d$} (E)
(D) edge node [below] {$d^\prime$} (E')
(E) edge node [right] {$F(f)$} (E');
\end{tikzpicture}
\]
}
\end{enumerate}
There are some subtleties to this approach. To illustrate, consider the example where $F \colon \bold{FinSet} \to \bold{Set}$ is the symmetric lax monoidal functor that assigns to a finite set $N$ the (large) set of all possible graph structures on the finite set $N$, where a graph structure on $N$ is given by a diagram in $\bold{Set}$ of the form:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$E$};
\node (B) at (1,0) {$N.$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge[bend left] node[above]{$s$} (B)
(A) edge[bend right] node[below]{$t$} (B);
\end{tikzpicture}
\]
Let $N=\{ v_1,v_2 \}$ be a two element set. Then one element of the set $F(N)$, in other words, one possible decoration, which is a graph structure, on the set $N$ is given by a single edge $e$ whose source and target are $v_1$ and $v_2$, respectively.
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$v_1$};
\node (B) at (1,0) {$v_2$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$e$} (B);
\end{tikzpicture}
\]
Denote this element of $F(N)$ as $d$. We could label the edge $e$ something else, for instance, $e^\prime$, and this single edge would another element of $F(N)$.
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$v_1$};
\node (B) at (1,0) {$v_2$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$e^\prime$} (B);
\end{tikzpicture}
\]
Denote this second element of $F(N)$ as $d^\prime$. These two graphs constitute distinct isomorphism classes in the symmetric monoidal category $F$Cospan$(\bold{FinSet})$, as $f=\id_N$ and thus $F(f)=\id_{F(N)}$, but clearly $d \neq d^\prime$. The issue here is that the functor $F$ is decorating each finite set $N$ not only with extra structure, but with extra \emph{stuff}. Moreover, the finite set $N$ is being decorated with \emph{different} stuff in each instance and this difference in stuff is not entirely detected by the function $F(f)$. This phenomenon doesn't occur when the decorations only involve extra structure, and this has been utilized in other works \cite{BFP,BP,Yass}.

One approach to remedying this nuisance is to instead view $F$ as a functor $F \colon\bold{C} \to \bold{Cat}$ and then consider $F(c)$ not as a \emph{set} of decorations on the element $c$ but as a \emph{category} of decorations on the element $c$. Then one can construct a similar symmetric monoidal category similar to Fong's, which by similarity and an abuse of notation we also call $F\textnormal{Cospan}(\bold{C})$. This symmetric monoidal category will have:
\begin{enumerate}
\item{objects as those of $\bold{C}$ and}
\item{morphisms as isomorphism classes of cospans of $\bold{C}$ together with an element of image of the apex under the functor $F$.
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,1) {$c$};
\node (C) at (2,0) {$b$};
\node (D) at (3,0.5) {$d \in F(c)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B);
\end{tikzpicture}
\]
Except now, given another morphism:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,-1) {$c^\prime$};
\node (C) at (2,0) {$b$};
\node (D) at (3,-0.5) {$d^\prime \in F(c^\prime)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[below]{$i^\prime$} (B)
(C) edge node[below]{$o^\prime$} (B);
\end{tikzpicture}
\]
these two morphisms are in the same isomorphism class if the following diagrams commute
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,1) {$c$};
\node (B') at (1,-1) {$c^\prime$};
\node (C) at (2,0) {$b$};
\node (D) at (3,0) {$\bold{1}$};
\node (E) at (4,0.5) {$F(c)$};
\node (E') at (4,-0.5) {$F(c^\prime)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B)
(A) edge node[below]{$i^\prime$} (B')
(C) edge node[below]{$o^\prime$} (B')
(B) edge node [left] {$f$} (B')
(D) edge node [above] {$d$} (E)
(D) edge node [below] {$d^\prime$} (E')
(E) edge node [right] {$F(f)$} (E');
\end{tikzpicture}
\]
and there exists an isomorphism $\iota \colon F(f)(d) \to d^\prime$ in the category $F(c^\prime)$.
}
\end{enumerate}
Note that the existence of an isomorphism $\iota \colon F(f)(d) \to d^\prime$ is equivalent to the triangle above on the right commuting up to a 2-isomorphism.
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (4,0) {$\iota \Swarrow$};
\node (D) at (3,0) {$\bold{1}$};
\node (E) at (4.5,1) {$F(c)$};
\node (E') at (4.5,-1) {$F(c^\prime)$};
\path[->,font=\scriptsize,>=angle 90]
(D) edge node [above] {$d$} (E)
(D) edge node [below] {$d^\prime$} (E')
(E) edge node [right] {$F(f)$} (E');
\end{tikzpicture}
\]
In other words, the isomorphism $\iota$ is a \emph{natural} isomorphism. We will typically just write this as $\iota \colon F(f)(d) \to d^\prime$ to conserve space.

In this new category, the added structure of an isomorphism in the category of decorations shapes the isomorphism classes to look as one would expect. Fong's symmetric monoidal category has been extended to a bicategory by the first author \cite{Cour} and this was one of the original illuminations of the above obstacle. In this bicategory, objects and morphisms are given as in Fong's category modulo taking cospans up to isomorphism class and 2-morphisms are given by a pair of commuting diagrams:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,1) {$c$};
\node (B') at (1,-1) {$c^\prime$};
\node (C) at (2,0) {$b$};
\node (D) at (3,0) {$\bold{1}$};
\node (E) at (4,0.5) {$F(c)$};
\node (E') at (4,-0.5) {$F(c^\prime)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B)
(A) edge node[below]{$i^\prime$} (B')
(C) edge node[below]{$o^\prime$} (B')
(B) edge node [left] {$f$} (B')
(D) edge node [above] {$d$} (E)
(D) edge node [below] {$d^\prime$} (E')
(E) edge node [right] {$F(f)$} (E');
\end{tikzpicture}
\]
In this case, there would be no 2-morphism from:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$v_1$};
\node (B) at (1,0) {$v_2$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$e$} (B);
\end{tikzpicture}
\]
to:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$v_1$};
\node (B) at (1,0) {$v_2.$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$e^\prime$} (B);
\end{tikzpicture}
\]
Morally speaking, these two simple single-edged graphs should belong to the same isomorphism class, as there is a natural isomorphism of graphs between them.

In the present work, we construct a symmetric monoidal `double category' $\mathbb{F}\textnormal{Cospan}(\bold{C})$. Double categories were first introduced by Ehresmann \cite{Ehresmann63, Ehresmann65} and symmetric monoidal double categories by Shulman \cite{Shul}. They have long been used in topology and other branches of pure mathematics \cite{Brown1,Brown2}.  More recently they have been used to study open dynamical systems \cite{LS} and open Markov processes \cite{BC}. While a mere category has only objects and morphisms, a double category has a few more types of entities:
\[
\begin{tikzpicture}[scale=1]
\node (D) at (-4,0.5) {$A$};
\node (E) at (-2,0.5) {$B$};
\node (F) at (-4,-1) {$C$};
\node (A) at (-2,-1) {$D$};
\node (B) at (-3,-0.25) {$\Downarrow a$};
\path[->,font=\scriptsize,>=angle 90]
(D) edge node [above]{$M$}(E)
(E) edge node [right]{$g$}(A)
(D) edge node [left]{$f$}(F)
(F) edge node [above]{$N$} (A);
\end{tikzpicture}
\]
We call $A, B, C$ and $D$ `objects', $f$ and $g$ `vertical 1-morphisms', $M$ and $N$ `horizontal 1-cells', and $a$ a `2-morphism'.   We can compose vertical 1-morphisms to get new vertical 1-morphisms and compose horizontal 1-cells to get new horizontal 1-cells.  We can compose the 2-morphisms in two ways: horizontally by setting squares side by side, and vertically by setting one on top of the other.   In a `strict' double category all these forms of composition are associative.  In a `pseudo' double category, horizontal 1-cells compose in a weakly associative manner: that is, the associative law holds only up to an invertible 2-morphism, called the `associator', which obeys a coherence law. The double category $\mathbb{F}\textnormal{Cospan}(\bold{C})$ that we construct in this paper has:
\begin{enumerate}
\item{objects as those of $\bold{C}$,}
\item{vertical 1-morphisms as morphisms of $\bold{C}$,}
\item{horizontal 1-cells as $F$-decorated cospans of $\bold{C}$, which are pairs:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,1) {$c$};
\node (C) at (2,0) {$b$};
\node (D) at (3,0.5) {$d \in F(c)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B);
\end{tikzpicture}
\]
and}
\item{2-morphisms as pairs of commuting diagrams:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,0) {$c$};
\node (C) at (2,0) {$b$};
\node (A') at (0,-1) {$a^\prime$};
\node (B') at (1,-1) {$c^\prime$};
\node (C') at (2,-1) {$b^\prime$};
\node (D) at (3,-0.5) {$1$};
\node (E) at (4,0) {$F(c)$};
\node (E') at (4,-1) {$F(c^\prime)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$i$} (B)
(A') edge node[above]{$i^\prime$} (B')
(C') edge node[above]{$o^\prime$} (B')
(A) edge node [left]{$f$} (A')
(B) edge node [left]{$h$} (B')
(C) edge node [left]{$g$} (C')
(D) edge node [above] {$d$} (E)
(D) edge node [below] {$d^\prime$} (E')
(E) edge node [left] {$F(h)$} (E');
\end{tikzpicture}
\]
together with a morphism $\iota \colon F(h)(d) \to d^\prime$ in $F(c^\prime)$.}
\end{enumerate}
We can then obtain a symmetric monoidal bicategory $H(\mathbb{F}\textnormal{Cospan}(\bold{C}))$ as the `horizontal bicategory' of the symmetric monoidal double category $\mathbb{F}\textnormal{Cospan}(\bold{C})$ using a result of Shulman \cite{Shul}. This bicategory will have:
\begin{enumerate}
\item{objects as those of $\bold{C}$,}
\item{morphisms as pairs:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,1) {$c$};
\node (C) at (2,0) {$b$};
\node (D) at (3,0.5) {$d \in F(c)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B);
\end{tikzpicture}
\]
and}
\item{2-morphisms as pairs of commuting diagrams:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,1) {$c$};
\node (B') at (1,-1) {$c^\prime$};
\node (C) at (2,0) {$b$};
\node (D) at (3,0) {$\bold{1}$};
\node (E) at (4,0.5) {$F(c)$};
\node (E') at (4,-0.5) {$F(c^\prime)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B)
(A) edge node[below]{$i^\prime$} (B')
(C) edge node[below]{$o^\prime$} (B')
(B) edge node [left] {$f$} (B')
(D) edge node [above] {$d$} (E)
(D) edge node [below] {$d^\prime$} (E')
(E) edge node [right] {$F(f)$} (E');
\end{tikzpicture}
\]
together with a morphism $\iota \colon F(f)(d) \to d^\prime$ of $F(c^\prime)$.}

\end{enumerate}
Then we can obtain the above improved symmetric monoidal category as a decategorification of the symmetric monoidal bicategory $H(\mathbb{F}\textnormal{Cospan}(\bold{C}))$.

The outline for the paper is as follows: In the second section we present the definition of double category and symmetric monoidal double category, both of which can be found in earlier works \cite{Shul}. In the third section, we construct the symmetric monoidal double category $F\textnormal{Cospan}(\bold{C})$ mentioned above as well as a result of Shulman that allows us to obtain a symmetric monoidal bicategory whose decategorification is an improved version of Fong's symmetric monoidal category. In the fourth section we investigate when a symmetric lax monoidal pseudofunctor gives rise to a left adjoint via the Grothendieck construction. In the fifth section we review another compositional framework which uses cospans equipped with extra structure due to Baez and the first author, namely `structured cospans' and prove that the double categorical versions of decorated cospans and structured cospans are equivalent, and in the final section, we present a few examples that can be realized with either framework and exhibit the equivalences.

\section{A review of double categories and symmetric monoidal double categories}
This section is meant to serve as a review of double categories and to present the definitions of double category, symmetric monoidal double category and a few more ideas that will be used later in the paper. Nothing in this section is new and can be found in the work of Shulman \cite{Shul}.

Before formally defining `pseudo double category', it is helpful to have the following picture in mind. A pseudo double category has 2-morphisms shaped like:

\[
\begin{tikzpicture}[scale=1]
\node (D) at (-4,0.5) {$A$};
\node (E) at (-2,0.5) {$B$};
\node (F) at (-4,-1) {$C$};
\node (A) at (-2,-1) {$D$};
\node (B) at (-3,-0.25) {$\Downarrow a$};
\path[->,font=\scriptsize,>=angle 90]
(D) edge node [above]{$M$}(E)
(E) edge node [right]{$g$}(A)
(D) edge node [left]{$f$}(F)
(F) edge node [above]{$N$} (A);
\end{tikzpicture}
\]

We call $A, B, C$ and $D$ \textbf{objects} or \textbf{0-cells}, $f$ and $g$ \textbf{vertical 1-morphisms}, $M$ and $N$ \textbf{horizontal 1-cells} and $a$ a \textbf{2-morphism}. Note that a vertical 1-morphism is a morphism between 0-cells and a 2-morphism is a morphism between horizontal 1-cells. We will denote both kinds of morphisms and horizontal 1-cells as a single arrow, namely `$\to$'. We follow the notation of Shulman \cite{Shul} with the following definitions.

\begin{defn}
A \textbf{pseudo double category} $\lD$, or $\textbf{double category}$ for short, consists of a category of objects $\bold{D_{0}}$ and a category of arrows $\bold{D_{1}}$ with the following functors
\begin{center}
$U\colon \bold{D_{0}} \to \bold{D_{1}}$\\
$S,T \colon \bold{D_{1}} \rightrightarrows \bold{D_{0}}$\\
$\odot \colon \bold{D_{1}} \times_{\bold{D_{0}}} \bold{D_{1}} \to \bold{D_{1}}$ (where the pullback is taken over $\bold{D_{1}} \xrightarrow[]{T} \bold{D_{0}} \xleftarrow[]{S} \bold{D_{1}}$) \\
\end{center}
 such that \\
\begin{center}
$S(U_{A})=A=T(U_{A})$\\
$S(M \odot N)=SN$\\
$T(M \odot N)=TM$\\
\end{center}
equipped with natural isomorphisms
\begin{center}

$\alpha \colon (M \odot N) \odot P \xrightarrow{\sim} M \odot (N \odot P)$\\
$\lambda \colon U_{B} \odot M \xrightarrow{\sim} M$\\
$\rho \colon M \odot U_{A} \xrightarrow{\sim} M$

\end{center}
such that $S(\alpha), S(\lambda), S(\rho), T(\alpha), T(\lambda)$ and $T(\rho)$ are all identities and that the coherence axioms of a monoidal category are satisfied. Following the notation of Shulman, objects of $\bold{D_{0}}$ are called $\textbf{0-cells}$ and morphisms of $\bold{D_{0}}$ are called $\textbf{vertical 1-morphisms}$. Objects of $\bold{D_{1}}$ are called $\textbf{horizontal 1-cells}$ and morphisms of $\bold{D_{1}}$ are called $\textbf{2-morphisms}$. The morphisms of $\bold{D_{0}}$, which are vertical 1-morphisms, will be denoted $f \colon A \to C$ and we denote a 1-cell $M$ with $S(M)=A,T(M)=B$ by $M \colon A \to B$. Then a 2-morphism $a \colon M \to N$ of $\bold{D_{1}}$ with $S(a)=f,T(a)=g$ would look like:
\[
\begin{tikzpicture}[scale=1]
\node (D) at (-4,0.5) {$A$};
\node (E) at (-2,0.5) {$B$};
\node (F) at (-4,-1) {$C$};
\node (A) at (-2,-1) {$D$};
\node (B) at (-3,-0.25) {$\Downarrow a$};
\path[->,font=\scriptsize,>=angle 90]
(D) edge node [above]{$M$}(E)
(E) edge node [right]{$g$}(A)
(D) edge node [left]{$f$}(F)
(F) edge node [above]{$N$} (A);
\end{tikzpicture}
\]
\end{defn}

The key difference between a `strict' double category and a pseudo double category is that in a pseudo double category, horizontal composition is associative and unital only up to natural isomorphism. Equivalently, as a double category can be viewed as a category internal to $\bold{Cat}$, we can view a pseudo double category as a category `weakly' internal to $\bold{Cat}$. We will sometimes omit the word pseudo and simply say double category.

\begin{defn}
A 2-morphism where $f$ and $g$ are identities is called a \textbf{globular 2-morphism}.
\end{defn}

\begin{defn}
Let $\lD$ be a pseudo double category. Then the $\textbf{horizontal bicategory}$ of $\lD$, which we denote as $H(\lD)$, is the bicategory consisting of objects of $\lD$, morphisms that are horizontal 1-cells of $\lD$ and 2-morphisms that are globular 2-morphisms of $\lD$.
\end{defn}

\begin{defn}
  A \textbf{monoidal double category} is a double category equipped the following
structure.
\begin{enumerate}
\item $\bold{D_{0}}$ and $\bold{D_{1}}$ are both monoidal categories.
\item If $I$ is the monoidal unit of $\bold{D_{0}}$, then $U_I$ is the
  monoidal unit of $\bold{D_{1}}$.
\item The functors $S$ and $T$ are strict monoidal, i.e.\ $S(M\ten N)
  = SM\ten SN$ and $T(M\ten N)=TM\ten TN$ and $S$ and $T$ also
  preserve the associativity and unit constraints.
\item We have globular isomorphisms
  \[\chi \maps (M_1\ten N_1)\odot (M_2\ten N_2)\too[\sim] (M_1\odot M_2)\ten (N_1\odot N_2)\]
  and
  \[\mu\maps U_{A\ten B} \too[\sim] (U_A \ten U_B)\]
  such that the following diagrams commute:
		\item \label{diag:MonDblCat}
			The following diagrams commute expressing the constraint data for the double functor $\otimes$.
			\[
			\begin{tikzpicture}
				\node (A) at (0,3) {\footnotesize{
							$((M_1\otimes N_1)\odot (M_2\otimes N_2)) \odot (M_3\otimes N_3)$}
				};
				\node (B) at (7,3) {\footnotesize{
						$((M_1\odot M_2)\otimes (N_1\odot N_2)) \odot (M_3\otimes N_3) $}
				};
				\node (A') at (0,1.5) {\footnotesize{
						$(M_1\otimes N_1)\odot ((M_2\otimes N_2) \odot (M_3\otimes N_3)) $}
				};
				\node (B') at (7,1.5) {\footnotesize{
						$((M_1\odot M_2)\odot M_3) \otimes ((N_1\odot N_2)\odot N_3)$}
				};
				\node (A'') at (0,0) {\footnotesize{
						$(M_1\otimes N_1) \odot ((M_2\odot M_3) \otimes (N_2\odot N_3))$}
				};
				\node (B'') at (7,0) {\footnotesize{
						$(M_1\odot (M_2\odot M_3)) \otimes (N_1\odot (N_2\odot N_3))$}
				};
			%
			\path[->,font=\scriptsize]
				(A) edge node[left]{$\alpha$} (A')
				(A') edge node[left]{$1 \odot \chi$} (A'')
				(B) edge node[right]{$\chi$} (B')
				(B') edge node[right]{$\alpha \otimes \alpha$} (B'')
				(A) edge node[above]{$\chi \odot 1$} (B)
				(A'') edge node[above]{$\chi$} (B'');
		\end{tikzpicture}
		\]
		\[
		\begin{tikzpicture}
			\node (UL) at (0,1.5) {\footnotesize{
					$(M\otimes N) \odot U_{C\otimes D}$}
			};
			\node (LL) at (0,0) {\footnotesize{
					$M\otimes N$}
			};
			\node (UR) at (3.5,1.5) {\footnotesize{
					$(M\otimes N)\odot (U_C\otimes U_D)$}
			};
			\node (LR) at (3.5,0) {\footnotesize{
					$(M\odot U_C) \otimes (N\odot U_D)$}
			};
			%
			\path[->,font=\scriptsize]
				(UL) edge node[above]{$1 \odot \mu$} (UR) 
				(UL) edge node[left]{$\rho$} (LL)
				(LR) edge node[above]{$\rho \otimes \rho$} (LL)
				(UR) edge node[right]{$\chi$} (LR);
		\end{tikzpicture}
		%
		\quad
		%
		\begin{tikzpicture}
			\node (UL) at (0,1.5) {\scriptsize{$U_{A\otimes B}\odot (M\otimes N)$}};
			\node (LL) at (0,0) {\scriptsize{$M\otimes N$}};
			\node (UR) at (3.5,1.5) {\scriptsize{$(U_A\otimes U_B)\odot (M\otimes N)$}};
			\node (LR) at (3.5,0) {\scriptsize{$(U_A \odot M) \otimes (U_B\odot N)$}};
			%
			\path[->,font=\scriptsize]
				(UL) edge node[above]{$\chi \odot 1$} (UR) 
				(UL) edge node[left]{$\lambda$} (LL)
				(LR) edge node[above]{$\lambda \otimes \lambda$} (LL)
				(UR) edge node[right]{$\chi$} (LR);
		\end{tikzpicture}
		\]
		%
		\item The following diagrams commute expressing 
		the associativity isomorphism for $\otimes$ is a transformation of double categories.
		\[
		\begin{tikzpicture}
			\node (A) at (0,3) {\footnotesize{
					$((M_1\otimes N_1)\otimes P_1) \odot ((M_2\otimes N_2)\otimes P_2)$}
			};
			\node (B) at (7,3) {\footnotesize{
					$(M_1\otimes (N_1\otimes P_1)) \odot (M_2\otimes (N_2\otimes P_2))$}
			};
			\node (A') at (0,1.5) {\footnotesize{
					$((M_1\otimes N_1) \odot (M_2\otimes N_2)) \otimes (P_1\odot P_2)$}
			};
			\node (B') at (7,1.5) {\footnotesize{
					$(M_1\odot M_2) \otimes ((N_1\otimes P_1)\odot (N_2\otimes P_2))$}
			};
			\node (A'') at (0,0) {\footnotesize{
					$((M_1\odot M_2) \otimes(N_1\odot N_2)) \otimes (P_1\odot P_2)$}
			};
			\node (B'') at (7,0) {\footnotesize{
					$(M_1\odot M_2) \otimes ((N_1\odot N_2)\otimes (P_1\odot P_2))$}
			};
			%
			\path[->,font=\scriptsize]
				(A) edge node[left]{$\chi$} (A')
				(A') edge node[left]{$\chi \otimes 1$} (A'')
				(B) edge node[right]{$\chi$} (B')
				(B') edge node[right]{$1 \otimes \chi$} (B'')
				(A) edge node[above]{$\alpha \odot \alpha$} (B)
				(A'') edge node[above]{$\alpha$} (B'');
		\end{tikzpicture}
		\]
		\[
		\begin{tikzpicture}
			\node (A) at (0,3) {\footnotesize{$U_{(A\otimes B)\otimes C}$}};
			\node (B) at (4,3) {\footnotesize{$U_{A\otimes (B\otimes C)} $}};
			\node (A') at (0,1.5) {\footnotesize{$U_{A\otimes B} \otimes U_C $}};
			\node (B') at (4,1.5) {\footnotesize{$U_A\otimes U_{B\otimes C}$}};
			\node (A'') at (0,0) {\footnotesize{$(U_A\otimes U_B)\otimes U_C$}};
			\node (B'') at (4,0) {\footnotesize{$U_A\otimes (U_B\otimes U_C) $}};
			%
			\path[->,font=\scriptsize]
				(A) edge node[left]{$\mu$} (A')
				(A') edge node[left]{$\mu \otimes 1$} (A'')
				(B) edge node[right]{$\mu$} (B')
				(B') edge node[right]{$1 \otimes \mu$} (B'')
				(A) edge node[above]{$U_{\alpha}$} (B)
				(A'') edge node[above]{$\alpha$} (B'');
		\end{tikzpicture}
		\]
		\item The following diagrams commute expressing that 
		the unit isomorphisms for $\otimes$ are transformations of double categories. 
		\[
		\begin{tikzpicture}
			\node (A) at (0,1.5) {\footnotesize{$(M\otimes U_I)\odot (N\otimes U_I)$}};
			\node (A') at (0,0) {\footnotesize{$M\odot N $}};
			\node (B) at (4,1.5) {\footnotesize{$(M\odot N)\otimes (U_I \odot U_I) $}};
			\node (B') at (4,0) {\footnotesize{$(M\odot N)\otimes U_I $}};
			%
			\path[->,font=\scriptsize]
				(A) edge node[left]{$r \odot r$} (A')
				(A) edge node[above]{$\chi$} (B)
				(B) edge node[right]{$1 \otimes \rho$} (B')
				(B') edge node[above]{$r$} (A');
		\end{tikzpicture}
		%
		\quad
		%
		\begin{tikzpicture}
			\node (A) at (0,0.75) {\footnotesize{$U_{A\otimes I} $}};
			\node (B) at (1.5,1.5) {\footnotesize{$U_A\otimes U_I $}};
			\node (B') at (1.5,0) {\footnotesize{$U_A$}};
			%
			\path[->,font=\scriptsize]
				(A) edge node[above]{$\mu$} (B)
				(A) edge node[below]{$U_{r}$} (B')
				(B) edge node[right]{$r$} (B');
		\end{tikzpicture}
		\]
		%
		%
		%
		%
		\[
		\begin{tikzpicture}
			\node (A) at (0,1.5) {\footnotesize{$(U_I\otimes M)\odot (U_I\otimes N)$}};
			\node (A') at (0,0) {\footnotesize{$M\odot N$}};
			\node (B) at (4,1.5) {\footnotesize{$(U_I \odot U_I) \otimes (M\odot N)$}};
			\node (B') at (4,0) {\footnotesize{$U_I\otimes (M\odot N) $}};
			%
			\path[->,font=\scriptsize]
				(A) edge node[left]{$\ell \odot \ell$} (A')
				(A) edge node[above]{$\chi$} (B)
				(B) edge node[right]{$\lambda \otimes 1$} (B')
				(B') edge node[above]{$\ell$} (A');
		\end{tikzpicture}
		%
		\quad
		\begin{tikzpicture}
			\node (A) at (0,0.75) {\footnotesize{$U_{I\otimes A}$}};
			\node (B) at (1.5,1.5) {\footnotesize{$U_I\otimes U_A$}};
			\node (B') at (1.5,0) {\footnotesize{$U_A$}};
			%
			\path[->,font=\scriptsize]
				(A) edge node[above]{$\mu$} (B)
				(A) edge node[below]{$U_{\ell}$} (B')
				(B) edge node[right]{$\ell$} (B');
		\end{tikzpicture}
		\]
		\newcounter{mondbl}
		\setcounter{mondbl}{\value{enumi}}
	\end{enumerate}
	A \textbf{braided monoidal double category} 
	is a monoidal double category 
	such that:
	\begin{enumerate}
		\setcounter{enumi}{\value{mondbl}}
		\item $\dblcat{D}_{0}$ and $\dblcat{D}_{1}$ are braided monoidal categories.
		\item The functors $S$ and $T$ are strict braided monoidal functors.
		\item The following diagrams commute expressing that the braiding is a transformation of double categories.
		\[
		\begin{tikzpicture}
			\node (A) at (0,1.5) {\footnotesize{$(M_1 \odot M_2) \otimes (N_1 \odot N_2)$}};
			\node (A') at (0,0) {\footnotesize{$(M_1\otimes N_1) \odot (M_2\otimes N_2)$}};
			\node (B) at (5,1.5) {\footnotesize{$(N_1\odot N_2) \otimes (M_1 \odot M_2)$}};
			\node (B') at (5,0) {\footnotesize{$(N_1 \otimes M_1) \odot (N_2 \otimes M_2)$}};
			%
			\path[->,font=\scriptsize]
				(A) edge node[left]{$\chi$} (A')
				(A) edge node[above]{$\beta$} (B)
				(B) edge node[right]{$\chi$} (B')
				(A') edge node[above]{$\beta \odot \beta$} (B');
		\end{tikzpicture}
		%
		\quad
		%
		\begin{tikzpicture}
			\node (A) at (0,1.5) {\footnotesize{$U_A \otimes U_B$}};
			\node (A') at (0,0) {\footnotesize{$U_B\otimes U_A$}};
			\node (B) at (2,1.5) {\footnotesize{$U_{A\otimes B} $}};
			\node (B') at (2,0) {\footnotesize{$U_{B\otimes A}$}};
			%
			\path[->,font=\scriptsize]
				(A) edge node[left]{$\beta$} (A')
				(B) edge node[above]{$\mu$} (A)
				(B) edge node[right]{$U_\beta$} (B')
				(B') edge node[above]{$\mu$} (A');
		\end{tikzpicture}
		\]
		\setcounter{mondbl}{\value{enumi}}
	\end{enumerate}
	Finally, a \textbf{symmetric monoidal double category} 
	is a braided monoidal double category $\mathbb{D}$ such that:
	\begin{enumerate}
		\setcounter{enumi}{\value{mondbl}}
		\item $\dblcat{D}_{0}$ and $\dblcat{D}_{1}$ are symmetric monoidal.
	\end{enumerate}
\end{defn}

\begin{defn}\label{def:companion}
  Let \lD\ be a double category and $f\maps A\to B$ a vertical
  1-morphism.  A \textbf{companion} of $f$ is a horizontal 1-cell
  $\fhat\maps A\to B$ together with 2-morphisms
	\[
	\raisebox{-0.5\height}{
	\begin{tikzpicture}
		\node (A) at (0,1) {$A$};
		\node (B) at (1,1) {$B$};
		\node (A') at (0,0) {$B$};
		\node (B') at (1,0) {$B$};
		%
		\path[->,font=\scriptsize,>=angle 90]
			(A) edge node[above]{$\widehat{f}$} (B)
			(A) edge node[left]{$f$} (A')
			(B) edge node[right]{$1$} (B')
			(A') edge node[below]{$U_B$} (B');
		%
	%	\draw (0.5,.925) -- (0.5,1.075);
	%	\draw (0.5,-.075) -- (0.5,.075);
		\node () at (0.5,0.5) {\scriptsize{$\Downarrow$}};
	\end{tikzpicture}
	}
	%
	\quad \text{ and } \quad
	%
	\raisebox{-0.5\height}{
	\begin{tikzpicture}
		\node (A) at (0,1) {$A$};
		\node (B) at (1,1) {$A$};
		\node (A') at (0,0) {$A$};
		\node (B') at (1,0) {$B$};
		%
		\path[->,font=\scriptsize,>=angle 90]
			(A) edge node[above]{$U_A$} (B)
			(A) edge node[left]{$1$} (A')
			(B) edge node[right]{$f$} (B')
			(A') edge node[below]{ $\widehat{f}$} (B');
		%
	%	\draw (0.5,.925) -- (0.5,1.075);
	%	\draw (0.5,-.075) -- (0.5,.075);
		\node () at (0.5,0.5) {\scriptsize{$\Downarrow$}};
	\end{tikzpicture}
	}
	\]
  such that the following equations hold.
	\begin{equation}
	\label{eq:CompanionEq}
	\raisebox{-0.5\height}{
	\begin{tikzpicture}
		\node (A) at (0,2) {$A$};
		\node (B) at (1.1,2) {$A$};
		\node (A') at (0,1) {$A$};
		\node (B') at (1.1,1) {$B$};
		\node (A'') at (0,0) {$B$};
		\node (B'') at (1.1,0) {$B$};
		%
		\path[->,font=\scriptsize,>=angle 90]
			(A) edge node[left]{$1$} (A')
			(A') edge node[left]{$f$} (A'')
			(B) edge node[right]{$f$} (B')
			(B') edge node[right]{$1$} (B'')
			(A) edge node[above]{$U_A$} (B)
			(A') edge  (B')
			(A'') edge node[below]{$U_B$} (B'');
		%
	%	\draw (0.5,1.925) -- (0.5,2.075);
		\draw[line width=2mm,white] (0.5,.925) -- (0.5,1.075);
	%	\draw (0.5,-.075) -- (0.5,.075);
		\node () at (0.5,0.5) {\scriptsize{$\Downarrow$}};
		\node () at (0.5,1.5) {\scriptsize{$\Downarrow$}};
		\node () at (0.5,1) {\scriptsize $\widehat{f}$};
	\end{tikzpicture}
	}
	%
	\raisebox{-0.5\height}{=}
	%
	\raisebox{-0.5\height}{
	\begin{tikzpicture}
		\node (A) at (0,1) {$A$};
		\node (B) at (1,1) {$A$};
		\node (A') at (0,0) {$B$};
		\node (B') at (1,0) {$B$};
		%
		\path[->,font=\scriptsize,>=angle 90]
		(A) edge node[left]{$f$} (A')
		(B) edge node[right]{$f$} (B')
		(A) edge node[above]{$U_A$} (B)
		(A') edge node[below]{$U_B$} (B');
		%
		%\draw (0.5,.925) -- (0.5,1.075);
		%\draw (0.5,-.075) -- (0.5,.075);
		\node () at (0.5,0.5) {\scriptsize{$\Downarrow U_f$}};
	\end{tikzpicture}
	}
	%
	\raisebox{-0.5\height}{\text{   and   }}
	%
	\raisebox{-0.5\height}{
	\begin{tikzpicture}
		\node (A) at (0,1) {$A$};
		\node (A') at (0,0) {$A$};
		\node (B) at (1,1) {$A$};
		\node (B') at (1,0) {$B$};
		\node (C) at (2,1) {$B$};
		\node (C') at (2,0) {$B$};
		%
		\path[->,font=\scriptsize,>=angle 90]
			(A) edge node[left]{$1$} (A')
			(B) edge node[left]{$f$} (B')
			(C) edge node[right]{$1$} (C')
			(A) edge node[above]{$U_A$} (B)
			(B) edge node[above]{$\widehat{f}$} (C)
			(A') edge node[below]{$\widehat{f}$} (B')
			(B') edge node[below]{$U_B$} (C');
		%
	%	\draw (1.5,0.925) -- (1.5,1.075);
	%	\draw (1.5,0.925) -- (1.5,1.075);
	%	\draw (0.5,.925) -- (0.5,1.075);
	%	\draw (0.5,-.075) -- (0.5,.075);
		\node () at (0.5,0.5) {\scriptsize{$\Downarrow$}};
		\node () at (1.5,0.5) {\scriptsize{$\Downarrow$}};
	\end{tikzpicture}
	}
	%
	\raisebox{-0.5\height}{=}
	%
	\raisebox{-0.5\height}{
	\begin{tikzpicture}
		\node (A) at (0,1) {$A$};
		\node (B) at (1,1) {$B$};
		\node (A') at (0,0) {$A$};
		\node (B') at (1,0) {$B$};
		%
		\path[->,font=\scriptsize,>=angle 90]
			(A) edge node[left]{$1$} (A')
			(B) edge node[right]{$1$} (B')
			(A) edge node[above]{$\widehat{f}$} (B)
			(A') edge node[below]{$\widehat{f}$} (B');
		%
	%	\draw (0.5,.925) -- (0.5,1.075);
	%	\draw (0.5,-.075) -- (0.5,.075);
		\node () at (0.5,0.5) {\scriptsize{$\Downarrow \id_{\widehat{f}}$}};
	\end{tikzpicture}
	}
	\end{equation}
  A \textbf{conjoint} of $f$, denoted $\fchk \maps B\to A$, is a
  companion of $f$ in the double category $\lD^{h\cdot\mathrm{op}}$
  obtained by reversing the horizontal 1-cells, but not the vertical
  1-morphisms, of \lD.
\end{defn}
\noindent
In a pseudo double category, the second equation above requires an insertion of unit isomorphisms to make sense due to horizontal composition only holding up to isomorphism.
\begin{defn}
  We say that a double category is \textbf{fibrant} if every vertical
  1-morphism has both a companion and a conjoint and \define{isofibrant} if every vertical 1-isomorphism has both a companion and a conjoint.
\end{defn}

%\section{Outline for paper}
%\begin{enumerate}
%\item{Need to build a symmetric monoidal decorated cospan category $F$Cospan$(\bold{C})$ from a lax symmetric monoidal pseudofunctor $F \colon \bold{C} \to \bold{Cat}$.}
%\item{Need to view $F$Cospan$(\bold{C})$ as a one object bicategory and then a one object pseudo double category.}
%\item{Deloop the symmetric monoidal $(\bold{Cat,\times})$ into a one object bicategory and then view this as a one object pseudo double category in which there is only an identity for vertical 1-morphisms and the objects of $\bold{Cat}$ appear as horizontal 1-cells, and morphisms of $\bold{Cat}$ as 2-morphisms. Denote this pseudo double category as $\mathbb{C}\bold{at}$.}
%\item{Define a symmetric monoidal lax double functor $\mathbb{F} \colon$ $F$Cospan$(\bold{C}) \to \mathbb{C} \bold{at}$.}
%\item{Define a symmetric monoidal oplax double functor $\mathbb{I} \colon \bold{1} \to \mathbb{C} \bold{at}$ where $\bold{1}$ is the one object double category.}
%\item{Obtain a symmetric monoidal double category of decorated cospans $\mathbb{F}$Cospan$(\bold{C})$ as a comma object from the cospan $\bold{1} \xrightarrow{ \mathbb{I} } \mathbb{C}\bold{at} \xleftarrow{ \mathbb{F} } F\textrm{Cospan}(\bold{C})$ in the 2-category $\mathbb{DBL}$ of monoidal double categories and lax functors. (Note that the functor $\mathbb{I} \colon \bold{1} \to \mathbb{C}\bold{at}$ is actually pseudo, and hence both lax and oplax.)} 
%\item{Figure out what a (double?) equivalence of symmetric monoidal double categories is.}
%\item{Show that $_F \textrm{Csp}(\bold{C})$ is equivalent to $\mathbb{F}\textrm{Cospan}(\bold{C})$ as symmetric monoidal double categories, where $_F \textrm{Csp}(\bold{C})$ is the structured cospan double category that comes from the double category Csp$(\bold{C})$ and the functor $F \colon \bold{C} \to \bold{Cat}$.}
%\end{enumerate}

\section{A symmetric monoidal double category of decorated cospans}\label{DecCospansDoublecat}
In this section we build the symmetric monoidal double category mentioned in the introduction. A double category $\mathbb{D}=(\mathbb{D}_0,\mathbb{D}_1)$ consists of a category of objects $\mathbb{D}_0$ and a category of arrows $\mathbb{D}_1$. We obtain $\mathbb{D}$ as a comma object in the 2-category $\bold{Dbl}$ of monoidal double categories, monoidal double functors and monoidal double transformations by obtaining each of $\mathbb{D}_0$ and $\mathbb{D}_1$ as comma categories in $\bold{Cat}$.

If $\bold{C}$ is a category with finite colimits, there is a well-known symmetric monoidal pseudo double category $\mathbb{C} \textnormal{ospan}(\bold{C})$ which has:
\begin{enumerate}
\item{objects as those of $\bold{C}$,}
\item{vertical 1-morphisms as morphisms of $\bold{C}$,}
\item{horizontal 1-cells as cospans in $\bold{C}$, and}
\item{2-morphisms as maps of cospans in $\bold{C}.$
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$c_1$};
\node (B) at (1,0) {$d$};
\node (C) at (2,0) {$c_2$};
\node (A') at (0,-1) {$c_1^\prime$};
\node (B') at (1,-1) {$d^\prime$};
\node (C') at (2,-1) {$c_2^\prime$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$$} (B)
(C) edge node[above]{$$} (B)
(A') edge node[above]{$$} (B')
(C') edge node[above]{$$} (B')
(A) edge node [above]{$$} (A')
(B) edge node [above]{$$} (B')
(C) edge node [above]{$$} (C');
\end{tikzpicture}
\]}
\end{enumerate}

The symmetric monoidal category $(\bold{Cat},\times,\bold{1})$ consisting of categories and functors can naturally be viewed as a one object bicategory using a standard level shift. This one object bicategory, which we denote as $\textnormal{BD}(\bold{Cat})$, will have:
\begin{enumerate}
\item{one object $\{ \star \}$,}
\item{objects of $\bold{Cat}$ as morphisms, and}
\item{morphisms of $\bold{Cat}$ as 2-morphisms.}
\end{enumerate}
We can then view this one object bicategory as a one object pseudo double category $\mathbb{B}\textnormal{D}(\bold{Cat})$, which will have:
\begin{enumerate}
\item{one object $\{ \star \}$,}
\item{only an identity for vertical 1-morphisms,}
\item{morphisms of $\textnormal{BD}(\bold{Cat})$, which are objects of $\bold{Cat}$, as horizontal 1-cells, and}
\item{2-morphisms of $\textnormal{BD}(\bold{Cat})$, which are morphisms of $\bold{Cat}$, as 2-morphisms.}
\end{enumerate}
This one object pseudo double category $\mathbb{B}\textnormal{D}(\bold{Cat})$ will serve as the apex of a cospan:

\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$\bold{1}$};
\node (B) at (1,1) {$\mathbb{B}\textnormal{D}(\bold{Cat})$};
\node (C) at (2,0) {$\mathbb{C}\textnormal{ospan}(\bold{C})$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$\mathbb{G}$} (B)
(C) edge node[above]{$\mathbb{F}$} (B);
\end{tikzpicture}
\]
which we will use to construct a comma object in $\bold{Dbl}$, the 2-category of double categories, double functors and double transformations. In order for the double comma object to exist in $\bold{Dbl}$, namely a pseudo comma double category, it is necessary that $\mathbb{F}$ and $\mathbb{G}$ be lax and oplax double functors, respectively. This was made known to the first author by Shulman. This result is true in general, but we will only prove it for this particular case that we are interested in.

The oplax double functor $\mathbb{G} \colon 1 \to \mathbb{B}\textnormal{D}(\bold{Cat})$ is trivially defined modulo $\mathbb{G}$ mapping the identity horizontal 1-cell to the monoidal unit of $\mathbb{B}\textnormal{D}(\bold{Cat})$ which is given by the terminal category $\bold{1}$. The category $\bold{C}$ has finite colimits and can be viewed as a 2-category with only trivial 2-morphisms. Then from a symmetric lax monoidal pseudofunctor $F \colon \bold{C} \to \bold{Cat}$, we can obtain symmetric lax monoidal lax double functor $\mathbb{F} \colon \mathbb{C}\textnormal{ospan}(\bold{C}) \to \mathbb{B}\textnormal{D}(\bold{Cat})$ which is defined as the pseudofunctor $F$ on horizontal 1-cells and 2-morphisms; note that $\mathbb{B}\textnormal{D}(\bold{Cat})$ has a single object and an identity vertical 1-morphism. Thus $\mathbb{F}$ will map a cospan in $\bold{C}$: $$a \rightarrow c \leftarrow b$$ to $F(c) \in \bold{Cat}$ and 
\begin{thm}
Let $F \colon \bold{C} \to \bold{Cat}$ be a symmetric lax monoidal pseudofunctor. Then there exists a symmetric (lax) monoidal lax double functor $\mathbb{F} \colon \mathbb{C}\textnormal{ospan}(\bold{C}) \to \mathbb{B}\textnormal{D}(\bold{Cat})$ which is defined:
\begin{enumerate}
\item{trivially on objects as $\mathbb{B}\textnormal{D}(\bold{Cat})$ only has a single object,}
\item{trivially on vertical 1-morphisms as $\mathbb{B}\textnormal{D}(\bold{Cat})$ only has a single identity vertical 1-morphism,}
\item{as the pseudofunctor $F \colon \bold{C} \to \bold{Cat}$ on horizontal 1-cells, meaning that $$(c_1 \xrightarrow{i} c \xleftarrow{o} c_2) \mapsto F(c)$$ and}
\item{as the pseudofunctor $F \colon \bold{C} \to \bold{Cat}$ on 2-morphisms, meaning that 
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$c_1$};
\node (B) at (1,0) {$c$};
\node (C) at (2,0) {$c_2$};
\node (A') at (0,-1) {$c_1^\prime$};
\node (B') at (1,-1) {$c^\prime$};
\node (C') at (2,-1) {$c_2^\prime$};
\node (D) at (3,-0.5) {$\mapsto$};
\node (E) at (4,0) {$F(c)$};
\node (E') at (4,-1) {$F(c^\prime)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$$} (B)
(C) edge node[above]{$$} (B)
(A') edge node[above]{$$} (B')
(C') edge node[above]{$$} (B')
(A) edge node [above]{$$} (A')
(B) edge node [left]{$f$} (B')
(C) edge node [above]{$$} (C')
(E) edge node [right] {$F(f)$} (E');
\end{tikzpicture}
\]
}
\end{enumerate}
\end{thm}
\begin{proof}
The functor $\mathbb{F} \colon \mathbb{C}\textnormal{ospan}(\bold{C}) \to \mathbb{B} \textnormal{D}(\bold{Cat})$ is defined trivially on objects and vertical 1-morphisms as the object category of $\mathbb{B}\textnormal{D}(\bold{Cat})$ is trivial. Given two composable horizontal 1-cells $M$ and $N$ in $\mathbb{C}\textnormal{ospan}(\bold{C})$ given respectively by:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$c_1$};
\node (B) at (1,1) {$c$};
\node (C) at (2,0) {$c_2$};
\node (D) at (3,0) {$c_2$};
\node (E) at (4,1) {$c^\prime$};
\node (F) at (5,0) {$c_3$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B)
(D) edge node[above]{$i^\prime$} (E)
(F) edge node[above]{$o^\prime$} (E);
\end{tikzpicture}
\]
we have that $\mathbb{F}(M)=F(c)$ and $\mathbb{F}(N)=F(c^\prime)$. The composite $M \odot N$ is given by the pushout:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$c_1$};
\node (B) at (1,1) {$c+_{c_2} c^\prime$};
\node (C) at (2,0) {$c_3$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$j \psi_c i$} (B)
(C) edge node[right]{$j \psi_{c^\prime} o$} (B);
\end{tikzpicture}
\]
and so $\mathbb{F}(M \odot N)=F(c+_{c_2} c^\prime)$. The comparison constraint globular 2-morphism $\mathbb{F}_{M,N} \colon \mathbb{F}(M) \odot \mathbb{F}(N) \to \mathbb{F}(M \odot N)$ is then given by:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$\star$};
\node (B) at (1.5,0) {$\star$};
\node (A') at (0,-1.5) {$\star$};
\node (B') at (1.5,-1.5) {$\star$};
\node (C) at (.75,-.75) {$\Downarrow F(j) \phi_{c,c^\prime}$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$F(c) \times F(c^\prime)$} (B)
(A') edge node[above]{$F(c+_{c_2} c^\prime)$} (B')
(A) edge node [left]{$\id$} (A')
(B) edge node [right]{$\id$} (B');
\end{tikzpicture}
\]
where $\phi_{c,c^\prime} \colon F(c) \times F(c^\prime) \to F(c+c^\prime)$ is one of the natural transformations of the symmetric lax monoidal pseudo functor $F$ and $j \colon c+c^\prime \to c+_{c_2}c^\prime$ is the natural map from the coproduct to the pushout.

Given an object $c$ in $\mathbb{C}\textnormal{ospan}(\bold{C})$, $\mathbb{F}(c)$ is the single object $\star$ of $\mathbb{B}\textnormal{D}(\bold{Cat})$, and so $1_{\mathbb{F}(c)}$ is the identity horizontal 1-cell on $\star$. Similarly, $1_c$ is the identity cospan on $c$ and then $\mathbb{F}(1_c)=F(c)$. The identity comparison is then the globular 2-morphism $\mathbb{F}_c \colon 1_{\mathbb{F}(c)} \to \mathbb{F}(1_c)$ given by:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$\star$};
\node (B) at (1.5,0) {$\star$};
\node (A') at (0,-1.5) {$\star$};
\node (B') at (1.5,-1.5) {$\star$};
\node (C) at (.75,-.75) {$\Downarrow$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$$} (B)
(A') edge node[above]{$F(c)$} (B')
(A) edge node [left]{$\id$} (A')
(B) edge node [right]{$\id$} (B');
\end{tikzpicture}
\]
\textbf{Finish this...}
\end{proof}
\begin{prop}
Let $\bold{1}$ denote the trivial double category with a single object and only identities. Then there exists a symmetric lax monoidal oplax double functor $\mathbb{G} \colon \mathbf{1} \to \mathbb{B}\textnormal{D}(\bold{Cat})$ which is defined:
\begin{enumerate}
\item{trivially on objects, as both $\bold{1}$ and $\mathbb{B} \textnormal{D}(\bold{Cat})$ have a single object,}
\item{trivially on vertical 1-morphisms, as both $\bold{1}$ and $\mathbb{B} \textnormal{D}(\bold{Cat})$ only have a single identity vertical 1-morphism,}
\item{the identity horizontal 1-cell of $\bold{1}$ maps to the monoidal unit of $(\mathbb{B}\textnormal{D}(\bold{Cat}),\times, \bold{1})$, which is the terminal category $\bold{1}$ with a single object and identity morphism, and}
\item{the identity 2-morphism maps to the identity functor $! \colon \bold{1} \to \bold{1}$ on the terminal category.}
\end{enumerate}
\end{prop}
We recall the definition of \emph{comma category} which will be crucial for the next step.
\begin{defn}
Let $f \colon \textbf{C} \to \textbf{E}$ and $g \colon \textbf{D} \to \textbf{E}$ be functors with a common codomain. Then the $\textbf{comma category}$ determined by $f$ and $g$ is the category $(f/g)$ whose:
\begin{enumerate}
\item{objects are triples $(c,d,\alpha)$ where $c \in \textbf{C}, d \in \textbf{D}$ and $\alpha \colon f(c) \to g(d)$ is a morphism in $\textbf{E}$, and whose}
\item{morphisms from $(c_{1},d_{1},\alpha_{1})$ to $(c_{2},d_{2},\alpha_{2})$ are pairs $(\beta, \gamma)$ where $\beta \colon c_{1} \to c_{2}$ and $\gamma \colon d_{1} \to d_{2}$ are morphisms in $\textbf{C}$ and $\textbf{D}$, respectively, such that the following diagram commutes}
\end{enumerate}
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (1,1) {$f(c_{1})$};
\node (B) at (2,1) {$f(c_{2})$};
\node (A') at (1,0) {$g(d_{1})$};
\node (B') at (2,0) {$g(d_{2})$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$f(\beta)$} (B)
(A') edge node[above]{$g(\gamma)$} (B')
(A) edge node[left]{$\alpha_{1}$} (A')
(B) edge node[right]{$\alpha_{2}$} (B');
\end{tikzpicture}
\]
\end{defn}
\begin{defn}
Let $f \colon \textbf{C} \to \textbf{E}$ and $g \colon \textbf{D} \to \textbf{E}$ be pseudofunctors between bicategories with a common codomain. Then the $\textbf{(weak) comma category}$ determined by $f$ and $g$ is the category $(f/g)$ whose:
\begin{enumerate}
\item{objects are triples $(c,d,\alpha)$ where $c \in \textbf{C}, d \in \textbf{D}$ and $\alpha \colon f(c) \to g(d)$ is a morphism in $\textbf{E}$, and whose}
\item{morphisms from $(c_{1},d_{1},\alpha_{1})$ to $(c_{2},d_{2},\alpha_{2})$ are triples $(\beta, \gamma, \iota)$ where $\beta \colon c_{1} \to c_{2}$ and $\gamma \colon d_{1} \to d_{2}$ are morphisms in $\textbf{C}$ and $\textbf{D}$, respectively and $\iota$ is a 2-morphism in $\bold{E}$, such that the following diagram commutes up to the 2-morphism $\iota$:}
\end{enumerate}
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (1,1) {$f(c_{1})$};
\node (B) at (2,1) {$f(c_{2})$};
\node (A') at (1,0) {$g(d_{1})$};
\node (B') at (2,0) {$g(d_{2})$};
\node (C) at (1.5,0.5) {$\iota \Swarrow$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$f(\beta)$} (B)
(A') edge node[above]{$g(\gamma)$} (B')
(A) edge node[left]{$\alpha_{1}$} (A')
(B) edge node[right]{$\alpha_{2}$} (B');
\end{tikzpicture}
\]
\end{defn}
Using this definition we want to construct a `pseudo comma double category' from the lax double functor $\mathbb{F} \colon \mathbb{C}\textnormal{ospan}(\bold{C}) \to \mathbb{B} \textnormal{D}(\bold{Cat})$ and the oplax double functor $\mathbb{G} \colon \bold{1} \to \mathbb{B}\textnormal{D}(\bold{Cat})$. First, we define how this pseudo comma double category $(\mathbb{G} / \mathbb{F}) \coloneqq \mathbb{F}\textnormal{Cospan}(\bold{C})$ is obtained.
\textbf{Should this be a proposition or a definition? Ask Dr. Baez and Christina for their opinions.}
\begin{defn}
Let $\mathbb{G} \colon \lC \to \lE$ be an oplax double functor and $\mathbb{F} \colon \lD \to \lE$ be a lax double functor where $\lC = (\bold{C}_{0},\bold{C}_{1}), \lD = (\bold{D}_{0}, \bold{D}_{1})$ and $\lE = (\bold{E}_{0}, \bold{E}_{1})$ are pseudo  double categories with $\bold{C}_{0}, \bold{C}_{1}$ the category of objects and category of arrows of the double category $\lC$, respectively, and likewise for $\bold{D}_{0}, \bold{D}_{1}, \bold{E}_{0}$ and $\bold{E}_{1}$. Then the \define{pseudo comma double category} determined by the double functors $\mathbb{G}$ and $\mathbb{F}$ is the pseudo double category $(\mathbb{G} / \mathbb{F})$ consisting of a category of objects $(\mathbb{G} / \mathbb{F})_{0}$ and category of arrows $(\mathbb{G} / \mathbb{F})_{1}$ where the category of objects $(\mathbb{G} / \mathbb{F})_0$ is the comma category obtained from the functors $\mathbb{G}_0 \colon \bold{C}_{0} \to \bold{E}_{0}$ and $\mathbb{F}_0 \colon \bold{D}_{0} \to \bold{E}_{0}$ and $(\mathbb{G} / \mathbb{F})_1$ is the comma category obtained from the functors $\mathbb{G}_{1} \colon \bold{C}_{1} \to \bold{E}_{1}$ and $\mathbb{F}_1 \colon \bold{D}_{1} \to \bold{E}_{1}$.
\end{defn}
\begin{thm}
Let $\mathbb{G} \colon \bold{1} \to \mathbb{B}\textnormal{D}(\bold{Cat})$ be the oplax double functor previously defined and let $\mathbb{F} \colon \mathbb{F}\textnormal{Cospan}(\bold{C}) \to \mathbb{B}(\bold{Cat})$ be the lax double functor previously defined. 
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$\bold{1}$};
\node (B) at (1,1) {$\mathbb{B}\textnormal{D}(\bold{Cat})$};
\node (C) at (2,0) {$\mathbb{C}\textnormal{ospan}(\bold{C})$};
\node (D) at (1,-1) {$(\mathbb{G} / \mathbb{F})$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$\mathbb{G}$} (B)
(C) edge node[above]{$\mathbb{F}$} (B)
(D) edge node [below] {$p$} (A)
(D) edge node [below] {$q$} (C);
\end{tikzpicture}
\]
Then there exists a category $(\mathbb{G} / \mathbb{F})_0 \coloneqq (\mathbb{G}_0 / \mathbb{F}_0)$ obtained as a comma category from the functors $\mathbb{F}_0 \colon \mathbb{C}\textnormal{ospan}(\bold{C})_0 \to \mathbb{B}\textnormal{D}(\bold{Cat})_0$ and $\mathbb{G}_0 \colon \bold{1} \to \mathbb{B}\textnormal{D}(\bold{Cat})_0$ which has:
\begin{enumerate}
\item{objects as those of $\bold{C}$ and}
\item{morphisms as those of $\bold{C}$,}
\end{enumerate}
and there exists a category $(\mathbb{G} / \mathbb{F})_1 \coloneqq (\mathbb{G}_1 / \mathbb{F}_1)$ obtained as a comma category from the functors $\mathbb{F}_1 \colon \mathbb{C}\textnormal{ospan}(\bold{C})_1 \to \mathbb{B}\textnormal{D}(\bold{Cat})_1$ and $\mathbb{G}_1 \colon \bold{1} \to \mathbb{B}\textnormal{D}(\bold{Cat})_1$ which has:
\begin{enumerate}
\item{objects as $F$-decorated cospans of $\bold{C}$, which are pairs:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,1) {$c$};
\node (C) at (2,0) {$b$};
\node (D) at (3,0.5) {$d \in F(c)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B);
\end{tikzpicture}
\]
and}
\item{morphisms as maps of cospans of $\bold{C}$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0.5) {$a$};
\node (A') at (0,-0.5) {$a^\prime$};
\node (B) at (1,0.5) {$c$};
\node (C) at (2,0.5) {$b$};
\node (C') at (2,-0.5) {$b^\prime$};
\node (D) at (1,-0.5) {$c^\prime$};
\node (E) at (3,0.5) {$d \in F(c)$};
\node (F) at (3,-0.5) {$d^\prime \in F(c^\prime)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$$} (B)
(C) edge node[above]{$$} (B)
(A) edge node[left]{$f$} (A')
(C) edge node[left]{$g$} (C')
(A') edge node {$$} (D)
(C') edge node {$$} (D)
(B) edge node [left] {$h$} (D);
\end{tikzpicture}
\]
together with a morphism $\iota \colon F(h)(d) \to d^\prime$ in $F(c^\prime)$.
 }
\end{enumerate}
\end{thm}
\begin{proof}
The category $(\mathbb{G} / \mathbb{F})_0$ will be the comma category obtained from the following cospan:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$\bold{1}$};
\node (B) at (1,1) {$\mathbb{B}\textnormal{D}(\bold{Cat})_0$};
\node (C) at (2,0) {$\mathbb{C}\textnormal{ospan}(\bold{C})_0=\bold{C}$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$\mathbb{G}_0$} (B)
(C) edge node[above]{$\mathbb{F}_0$} (B);
\end{tikzpicture}
\]
Thus $(\mathbb{G} / \mathbb{F})_0$ will be the comma category which has objects given by triples $(\star,c,\alpha \colon \mathbb{G}(\star) \to \mathbb{F}(c))$ where $\star$ is the single object of $\bold{1}$, $c$ is a object of $\bold{C}$ and $\alpha \colon \mathbb{G}(\star) \to \mathbb{F}(c)$ is a morphism in $\mathbb{B}\textnormal{D}(\bold{Cat})_0$. The pseudo double category $\mathbb{B}\textnormal{D}(\bold{Cat})$ only has a single object $\star$ and identity vertical 1-morphism, so the triple $(\star,c,\alpha \colon \mathbb{G}(\star) \to \mathbb{F}(c))$ amounts to an object of $\bold{C}$ together with trivial structure. Given another object $(\star, c^\prime, \alpha^\prime \colon \mathbb{G}(\star) \to \mathbb{F}(c^\prime))$, a morphism from the first triple to the second triple is a pair $(\beta, \gamma)$ where $\beta = \id_{\star}$ is a morphism in $\bold{1}$ and $\gamma \colon c \to c^\prime$ is a morphism in $\bold{C}$ such that the following diagram commutes:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (1,1) {$\mathbb{G}(\star)$};
\node (B) at (2,1) {$\mathbb{G}(\star)$};
\node (A') at (1,0) {$\mathbb{F}(c)$};
\node (B') at (2,0) {$\mathbb{F}(c^\prime)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$\mathbb{G}(\id_{\star})$} (B)
(A') edge node[above]{$\mathbb{F}(\gamma)$} (B')
(A) edge node[left]{$\alpha$} (A')
(B) edge node[right]{$\alpha^\prime$} (B');
\end{tikzpicture}
\]
The double category $\mathbb{B}\textnormal{D}(\bold{Cat})$ only has a single object and identity vertical 1-morphism, so this diagram is trivial,  as all four objects are the same and all four morphisms are identities. Thus, morphisms are given by morphisms of $\bold{C}$ with added trivial structure, and so the category $(\mathbb{G}/ \mathbb{F})_0$ has objects and morphisms of $\bold{C}$, and we have an isomorphism of categories $(\mathbb{G} / \mathbb{F})_0 \cong \bold{C}$.

Next we build the category $(\mathbb{G} / \mathbb{F})_1$ which will be the comma category obtained from the following cospan:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$\bold{1}$};
\node (B) at (1,1) {$\mathbb{B}\textnormal{D}(\bold{Cat})_1$};
\node (C) at (2,0) {$\mathbb{C}\textnormal{ospan}(\bold{C})_1$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$\mathbb{G}_1$} (B)
(C) edge node[above]{$\mathbb{F}_1$} (B);
\end{tikzpicture}
\]
Objects are given by triples $$(1_{\star}, a \rightarrow c \leftarrow b, d \colon \mathbb{G}(1_{\star}) \to \mathbb{F}(a \rightarrow c \leftarrow b))$$ where $1_{\star}$ is the identity horizontal 1-cell on $\star$ and $a \rightarrow c \leftarrow b$ is a cospan in $\bold{C}$. The double functor $\mathbb{G}$ maps the identity horizontal 1-cell to the monoidal unit of $\bold{Cat}$ under $\times$, namely the terminal category $\bold{1}$, and the double functor $\mathbb{F}$ acts as the functor $F$ on horizontal 1-cells, meaning that $\mathbb{F}(a \rightarrow c \leftarrow b)=F(c)$. Thus the above triple is a cospan in $\bold{C}$ together with an element $d \colon \bold{1} \to F(c)$, and this is precisely an $F$-decorated cospan, namely a pair $$((a \rightarrow c \leftarrow b),d \in F(c)).$$

Given two objects $((a \rightarrow c \leftarrow b),d \in F(c))$ and $(a^\prime \rightarrow c^\prime \leftarrow b^\prime),d^\prime \in F(c^\prime))$, a morphism from the first to the second is a triple $(\delta,h,\iota)$ that makes the following diagram commute:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$\mathbb{G}(1_\star)$};
\node (B) at (0,-1) {$\mathbb{G}(1_\star)$};
\node (C) at (2,0) {$\mathbb{F}(a \rightarrow c \leftarrow b)$};
\node (D) at (2,-1) {$\mathbb{F}(a^\prime \rightarrow c^\prime \leftarrow b^\prime)$};
\node (E) at (1,-0.5) {$\iota \Swarrow$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$\mathbb{G}(\delta)$} (B)
(A) edge node[above]{$d$} (C)
(C) edge node[right]{$\mathbb{F}(h)$} (D)
(B) edge node [above] {$d^\prime$} (D);
\end{tikzpicture}
\]
Simplifying things a bit, $\mathbb{G}(\delta)$ must be the identity 2-morphism of $\bold{1}$ and $h$ is a morphism of $\mathbb{C}\textnormal{ospan}(\bold{C})$, namely a triple of morphisms $(h_1,h,h_2)$ in $\bold{C}$ that makes the following diagram commute:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0.5) {$a$};
\node (A') at (0,-0.5) {$a^\prime$};
\node (B) at (1,0.5) {$c$};
\node (C) at (2,0.5) {$b$};
\node (C') at (2,-0.5) {$b^\prime$};
\node (D) at (1,-0.5) {$c^\prime$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$$} (B)
(C) edge node[above]{$$} (B)
(A) edge node[left]{$h_1$} (A')
(C) edge node[left]{$h_2$} (C')
(A') edge node {$$} (D)
(C') edge node {$$} (D)
(B) edge node [left] {$h$} (D);
\end{tikzpicture}
\]
Thus the above diagram containing the 2-morphism $\iota$ becomes:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (4,0) {$\iota \Swarrow$};
\node (D) at (3,0) {$\bold{1}$};
\node (E) at (4.5,0.5) {$F(c)$};
\node (E') at (4.5,-0.5) {$F(c^\prime)$};
\path[->,font=\scriptsize,>=angle 90]
(D) edge node [above] {$d$} (E)
(D) edge node [below] {$d^\prime$} (E')
(E) edge node [right] {$F(h)$} (E');
\end{tikzpicture}
\]
which is just a morphism $\iota \colon F(h)(d) \to d^\prime$ in $F(c^\prime)$. Thus a morphism of $(\mathbb{G} / \mathbb{F})_1$ is a map of cospans in $\bold{C}$ together with a natural transformation that that makes the above triangle commute.
\begin{thm}
Let $\bold{C}$ be a category with finite colimits and $F \colon \bold{C} \to \bold{Cat}$ a lax monoidal pseudofunctor. Then there exists a double category $\mathbb{F} \textnormal{Cospan}(\bold{C}) \coloneqq (\mathbb{G}/ \mathbb{F})$ which has:
\begin{enumerate}
\item{objects as those of $\bold{C}$,}
\item{vertical 1-morphisms as morphisms of $\bold{C}$,}
\item{horizontal 1-cells as pairs:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,1) {$c$};
\node (C) at (2,0) {$b$};
\node (D) at (3,0.5) {$d \in F(c)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B);
\end{tikzpicture}
\]
and}
\item{2-morphisms as maps of cospans in $\bold{C}$
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0.5) {$a$};
\node (A') at (0,-0.5) {$a^\prime$};
\node (B) at (1,0.5) {$c$};
\node (C) at (2,0.5) {$b$};
\node (C') at (2,-0.5) {$b^\prime$};
\node (D) at (1,-0.5) {$c^\prime$};
\node (E) at (3,0.5) {$d \in F(c)$};
\node (F) at (3,-0.5) {$d^\prime \in F(c^\prime)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$$} (B)
(C) edge node[above]{$$} (B)
(A) edge node[left]{$f$} (A')
(C) edge node[left]{$g$} (C')
(A') edge node {$$} (D)
(C') edge node {$$} (D)
(B) edge node [left] {$h$} (D);
\end{tikzpicture}
\]
together with a morphism $\iota \colon F(h)(d) \to d^\prime$ in $F(c^\prime)$.}
\end{enumerate}
\end{thm}
The unit structure functor $U \colon (\mathbb{G},\mathbb{F})_0 \to (\mathbb{G},\mathbb{F})_1$ is defined on objects as: 
\[
\begin{tikzpicture}[scale=1.5]
\node (E) at (-1,0.5) {$c \mapsto$};
\node (A) at (0,0) {$c$};
\node (B) at (1,1) {$c$};
\node (C) at (2,0) {$c$};
\node (D) at (3,0.5) {$I \in F(c)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$1$} (B)
(C) edge node[right]{$1$} (B);
\end{tikzpicture}
\]
where $I \in F(c)$ is the trivial decoration on $c$ given by the composition of the unique map $F(!) \colon F(0) \to F(c)$ and the morphism $\phi \colon \bold{1} \to F(0)$  which comes from the symmetric lax monoidal pseudofunctor $F \colon \bold{C} \to \bold{Cat}$. For morphisms, the structure functor $U$ is defined as:
\[
\begin{tikzpicture}[scale=1.5]
\node (G) at (-1,0.5) {$c$};
\node (G') at (-1,-0.5) {$c^\prime$};
\node (A) at (0,0.5) {$c$};
\node (A') at (0,-0.5) {$c^\prime$};
\node (B) at (1,0.5) {$c$};
\node (C) at (2,0.5) {$c$};
\node (C') at (2,-0.5) {$c^\prime$};
\node (D) at (1,-0.5) {$c^\prime$};
\node (E) at (3,0.5) {$I \in F(c)$};
\node (F) at (3,-0.5) {$I^\prime \in F(c^\prime)$};
\node (H) at (-0.5,0) {$\mapsto$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$$} (B)
(C) edge node[above]{$$} (B)
(A) edge node[left]{$f$} (A')
(C) edge node[left]{$f$} (C')
(A') edge node {$$} (D)
(C') edge node {$$} (D)
(B) edge node [left] {$f$} (D)
(G) edge node [left] {$f$} (G');
\end{tikzpicture}
\]
together with the morphism $\iota_{!_f} = F(f) F(!) \phi \colon \bold{1} \to F(c^\prime)$. We also have source and target structure functors $s,t \colon (\mathbb{G} / \mathbb{F})_1 \to (\mathbb{G} / \mathbb{F})_0$ where the source of a horizontal 1-cell
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,1) {$c$};
\node (C) at (2,0) {$b$};
\node (D) at (3,0.5) {$d \in F(c)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B);
\end{tikzpicture}
\]
is the object $a$ in $\bold{C}$ and the source of a 2-morphism
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0.5) {$a$};
\node (A') at (0,-0.5) {$a^\prime$};
\node (B) at (1,0.5) {$c$};
\node (C) at (2,0.5) {$b$};
\node (C') at (2,-0.5) {$b^\prime$};
\node (D) at (1,-0.5) {$c^\prime$};
\node (E) at (3,0.5) {$d \in F(c)$};
\node (F) at (3,-0.5) {$d^\prime \in F(c^\prime)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$$} (B)
(C) edge node[above]{$$} (B)
(A) edge node[left]{$f$} (A')
(C) edge node[left]{$g$} (C')
(A') edge node {$$} (D)
(C') edge node {$$} (D)
(B) edge node [left] {$h$} (D);
\end{tikzpicture}
\]
$$\iota \colon F(h)(d) \to d^\prime$$
is the source of the underlying map of cospans in $\bold{C}$, namely the morphism $f$ in $\bold{C}$; the target structure functor is defined similarly. The functors satisfy the equations $$SU(c)=1(c)=TU(c)$$for all objects $c$ of $\bold{C}$.

Given two composable horizontal 1-cells:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,1) {$c$};
\node (C) at (2,0) {$b$};
\node (D) at (1,-0.5) {$d \in F(c)$};
\node (E) at (3,0) {$b$};
\node (F) at (4,1) {$c^\prime$};
\node (G) at (5,0) {$e$};
\node (H) at (4,-0.5) {$d^\prime \in F(c^\prime)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B)
(E) edge node[above]{$i^\prime$} (F)
(G) edge node[above]{$o^\prime$} (F);
\end{tikzpicture}
\]
the composite is given by:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,1) {$c$};
\node (C) at (2,0) {$b$};
\node (D) at (3,1) {$c^\prime$};
\node (E) at (4,0) {$e$};
\node (F) at (2,2) {$c+c^\prime$};
\node (G) at (2,3) {$c+_{b} c^\prime$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B)
(C) edge node [above] {$i^\prime$} (D)
(E) edge node [above] {$o^\prime$} (D)
(B) edge node [above] {$j$} (F)
(D) edge node [above] {$j^\prime$} (F)
(F) edge node [left] {$\psi$} (G)
(A) edge node [left] {$\psi j i$} (G)
(E) edge node [right] {$\psi j^\prime o^\prime$} (G);
\end{tikzpicture}
\]
with the corresponding decoration of the apex $\hat{d} \in F(c+_b c^\prime)$ given by:
$$1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{d \times d^\prime} F(c) \times F(c^\prime) \xrightarrow{\phi_{c,c^\prime}} F(c+c^\prime) \xrightarrow{F(\psi)} F(c+_{b}c^\prime)$$
where $\psi \colon c + c^\prime \to c+_b c^\prime$ is the natural map from the coproduct to the pushout and $\phi_{c,c^\prime} \colon F(c) \times F(c^\prime) \to F(c+c^\prime)$ is the natural transformation of the symmetric lax monoidal pseudofunctor $F \colon \bold{C} \to \bold{Cat}$. Denoting the first and second of these horizontal 1-cells as $M$ and $N$, respectively, the source and target structure functors satisfy the equations $S(N \odot M)=S(M)$ and $T(N \odot M)=T(N)$.

Given three composable horizontal 1-cells $M_1, M_2$ and $M_3$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,1) {$c$};
\node (C) at (2,0) {$b$};
\node (D) at (1,-0.5) {$d_1 \in F(c)$};
\node (E) at (3,0) {$b$};
\node (F) at (4,1) {$c^\prime$};
\node (G) at (5,0) {$e$};
\node (H) at (4,-0.5) {$d_2 \in F(c^\prime)$};
\node (I) at (6,0) {$e$};
\node (J) at (7,1) {$c''$};
\node (K) at (8,0) {$f$};
\node (L) at (7,-0.5) {$d_3 \in F(c'')$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B)
(E) edge node[above]{$i^\prime$} (F)
(G) edge node[above]{$o^\prime$} (F)
(I) edge node[above]{$i''$} (J)
(K) edge node[above]{$o''$} (J);
\end{tikzpicture}
\]
we get a natural isomorphism $a \colon (M_1 \odot M_2) \odot M_3 \to M_1 \odot (M_2 \odot M_3)$ which is a globular 2-morphism given by a map of cospans $(\id_a,\sigma,\id_f)$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0.5) {$a$};
\node (A') at (0,-0.5) {$a$};
\node (B) at (1.5,0.5) {$(c+_b c^\prime)+_e c''$};
\node (C) at (3,0.5) {$f$};
\node (C') at (3,-0.5) {$f$};
\node (D) at (1.5,-0.5) {$c+_b(c^\prime +_e c'')$};
\node (E) at (4.5,0.5) {$d \in F((c+_b c^\prime)+_e c'')$};
\node (F) at (4.5,-0.5) {$d^\prime \in F(c+_b (c^\prime +_e c''))$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$$} (B)
(C) edge node[above]{$$} (B)
(A) edge node[left]{$\id_a$} (A')
(C) edge node[left]{$\id_f$} (C')
(A') edge node {$$} (D)
(C') edge node {$$} (D)
(B) edge node [left] {$\sigma$} (D);
\end{tikzpicture}
\]
with elements of the image of the cospan's apices under the pseudofunctor $F$ given by:
$$ d \coloneqq 1 \xrightarrow{\zeta_1} F(c+_b c^\prime) \times F(c'') \xrightarrow{F(\phi_{c+_b c^\prime, c''})} F((c+_{b}c^\prime) +c'') \xrightarrow{F(j_{c+_b c^\prime,c''})} F((c+_b c^\prime)+_e c'')$$ $$\zeta_1 = d_3 \lambda^{-1} F(j_{c,c^\prime}) \phi_{c,c^\prime} (d_1 \times d_2) \lambda^{-1}$$
and
$$ d^\prime \coloneqq 1 \xrightarrow{\zeta_2} F(c) \times F(c^\prime +_e c'') \xrightarrow{F(\phi_{c, c^\prime +_e c''})} F(c+(c^\prime +_e c'')) \xrightarrow{F(j_{c,c^\prime +_e c''})} F(c+_b (c^\prime+_e c''))$$ $$\zeta_2 = d_1 \lambda^{-1} F(j_{c^\prime,c''}) \phi_{c^\prime,c''} (d_2 \times d_3) \lambda^{-1}$$
together with an isomorphism $\iota_a \colon F(\sigma)(d) \to d^\prime$. We also have left and right unitors where given a horizontal 1-cell $M$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,1) {$c$};
\node (C) at (2,0) {$b$};
\node (D) at (3,0.5) {$d \in F(c)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B);
\end{tikzpicture}
\]
if we, say, compose with the identity horizontal 1-cell of $b$ on the right:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,1) {$c$};
\node (C) at (2,0) {$b$};
\node (D) at (1,-0.5) {$d \in F(c)$};
\node (E) at (3,0) {$b$};
\node (F) at (4,1) {$b$};
\node (G) at (5,0) {$b$};
\node (H) at (4,-0.5) {$!_b \in F(b)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B)
(E) edge node[above]{$1$} (F)
(G) edge node[above]{$1$} (F);
\end{tikzpicture}
\]
where $!_b = F(!)  \phi \colon \bold{1} \to F(b)$ is the trivial decoration on $b$. Composing these then gives:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,1) {$c+_b b$};
\node (C) at (2,0) {$b$};
\node (D) at (3,0.5) {$\hat{d} \in F(c +_b b)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$j \psi_c i$} (B)
(C) edge node[right]{$j \psi_b$} (B);
\end{tikzpicture}
\]
where $\psi_b \colon b \to c+b$ is the natural map into the coproduct and likewise for $\psi_c$ and $j \colon c+b \to c+_b b$ is the natural map from the coproduct to the pushout. The decoration $\hat{d} \colon \bold{1} \to F(c+_b b)$ is given by: $$1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{d \times !_b} F(c) \times F(b) \xrightarrow{\phi_{c,b}} F(c+b) \xrightarrow{F(j_{c,b})} F(c+_b b).$$ We then have that the right unitor of the original horizontal 1-cell $M$ is given by the globular 2-morphism $(\id_a,\gamma,\id_b)$ from the above composite to $M$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0.5) {$a$};
\node (A') at (0,-0.5) {$a$};
\node (B) at (1.5,0.5) {$c+_b b$};
\node (C) at (3,0.5) {$b$};
\node (C') at (3,-0.5) {$b$};
\node (D) at (1.5,-0.5) {$c$};
\node (E) at (4.5,0.5) {$\hat{d} \in F((c+_b b)$};
\node (F) at (4.5,-0.5) {$d \in F(c)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$j \psi_c i$} (B)
(C) edge node[above]{$j \psi_b$} (B)
(A) edge node[left]{$\id_a$} (A')
(C) edge node[left]{$\id_b$} (C')
(A') edge node [above]{$i$} (D)
(C') edge node [above]{$o$} (D)
(B) edge node [left] {$\gamma$} (D);
\end{tikzpicture}
\]
where $\gamma \colon c+_b b \xrightarrow{\sim} c$ together with an isomorphism $\iota_\rho \colon F(\gamma)(\hat{d}) \to d$. The left unitor is similar. The source and target functor applied to the left and right unitors and associators yield identities. The left and right unitors together with the associator satisfy the standard pentagon and triangle identities of a monoidal category or bicategory. Finally, for the interchange law, given four 2-morphisms:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0.5) {$a$};
\node (A') at (0,-0.5) {$a^\prime$};
\node (B) at (1,0.5) {$c$};
\node (C) at (2,0.5) {$b$};
\node (C') at (2,-0.5) {$b^\prime$};
\node (D) at (1,-0.5) {$c^\prime$};
\node (E) at (3,0.5) {$d_1 \in F(c)$};
\node (F) at (3,-0.5) {$d_1^\prime \in F(c^\prime)$};
\node (G) at (4,0.5) {$b$};
\node (H) at (5,0.5) {$e$};
\node (I) at (6,0.5) {$x$};
\node (G') at (4,-0.5) {$b^\prime$};
\node (H') at (5,-0.5) {$e^\prime$};
\node (I') at (6,-0.5) {$x^\prime$};
\node (J) at (7,0.5) {$d_2 \in F(e)$};
\node (K) at (7,-0.5) {$d_2^\prime \in F(e^\prime)$};
\node (L) at (1,-1) {$\iota_1 \colon F(h_1)(d_1) \to d_1^\prime$};
\node (M) at (5,-1) {$\iota_2 \colon F(h_2)(d_2) \to d_2^\prime$};
\node (A'') at (0,-1.5) {$a^\prime$};
\node (A''') at (0,-2.5) {$a''$};
\node (B'') at (1,-1.5) {$c^\prime$};
\node (C'') at (2,-1.5) {$b^\prime$};
\node (C''') at (2,-2.5) {$b''$};
\node (D'') at (1,-2.5) {$c''$};
\node (E'') at (3,-1.5) {$d_1^\prime \in F(c^\prime)$};
\node (F'') at (3,-2.5) {$d_1'' \in F(c'')$};
\node (G'') at (4,-1.5) {$b^\prime$};
\node (H'') at (5,-1.5) {$e^\prime$};
\node (I'') at (6,-1.5) {$x^\prime$};
\node (G''') at (4,-2.5) {$b''$};
\node (H''') at (5,-2.5) {$e''$};
\node (I''') at (6,-2.5) {$x''$};
\node (J'') at (7,-1.5) {$d_2^\prime \in F(e^\prime)$};
\node (K'') at (7,-2.5) {$d_2'' \in F(e'')$};
\node (L'') at (1,-3) {$\iota_1^\prime \colon F(h_1^\prime)(d_1^\prime) \to d_1''$};
\node (M'') at (5,-3) {$\iota_2^\prime \colon F(h_2^\prime)(d_2^\prime) \to d_2''$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i_1$} (B)
(C) edge node[above]{$o_1$} (B)
(A) edge node[left]{$f$} (A')
(C) edge node[left]{$g$} (C')
(A') edge node[above] {$i_1^\prime$} (D)
(C') edge node[above] {$o_1^\prime$} (D)
(B) edge node [left] {$h_1$} (D)
(G) edge node [above] {$i_2$} (H)
(G) edge node [left] {$g$} (G')
(H) edge node [left] {$h_2$} (H')
(G') edge node [above] {$i_2^\prime$} (H')
(I) edge node [above] {$o_2$} (H)
(I) edge node [left] {$k$} (I')
(I') edge node [above] {$o_2^\prime$} (H')
(A'') edge node[above]{$i_1^\prime$} (B'')
(C'') edge node[above]{$o_1^\prime$} (B'')
(A'') edge node[left]{$f^\prime$} (A''')
(C'') edge node[left]{$g^\prime$} (C''')
(A''') edge node[above] {$i_1''$} (D'')
(C''') edge node[above] {$o_1''$} (D'')
(B'') edge node [left] {$h_1^\prime$} (D'')
(G'') edge node [above] {$i_2^\prime$} (H'')
(G'') edge node [left] {$g^\prime$} (G''')
(H'') edge node [left] {$h_2^\prime$} (H''')
(G''') edge node [above] {$i_2''$} (H''')
(I'') edge node [above] {$o_2^\prime$} (H'')
(I'') edge node [left] {$k^\prime$} (I''')
(I''') edge node [above] {$o_2''$} (H''');
\end{tikzpicture}
\]
if we first compose horizontally we obtain:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0.5) {$a$};
\node (A') at (0,-0.5) {$a^\prime$};
\node (B) at (1.5,0.5) {$c+_b e$};
\node (C) at (3,0.5) {$x$};
\node (C') at (3,-0.5) {$x^\prime$};
\node (D) at (1.5,-0.5) {$c^\prime +_{b^\prime} e^\prime$};
\node (E) at (4.5,0.5) {$d_{1,2} \in F(c+_b e)$};
\node (F) at (4.5,-0.5) {$d_{1,2}^\prime \in F(c^\prime +_{b^\prime} e^\prime)$};
\node (G) at (1.5,-1) {$\iota_{1,2} \colon F(h_1 +_g h_2)(d_{1,2}) \to d_{1,2}^\prime$};
\node (A'') at (0,-1.5) {$a^\prime$};
\node (A''') at (0,-2.5) {$a''$};
\node (B'') at (1.5,-1.5) {$c^\prime +_{b^\prime} e^\prime$};
\node (C'') at (3,-1.5) {$x^\prime$};
\node (C''') at (3,-2.5) {$x''$};
\node (D'') at (1.5,-2.5) {$c'' +_{b''} e''$};
\node (E'') at (4.5,-1.5) {$d_{1,2}^\prime \in F(c^\prime+_{b^\prime} e^\prime)$};
\node (F'') at (4.5,-2.5) {$d_{1,2}'' \in F(c'' +_{b''} e'')$};
\node (G'') at (1.5,-3) {$\iota_{1,2}^\prime \colon F(h_1^\prime +_{g^\prime} h_2^\prime)(d_{1,2}^\prime) \to d_{1,2}''.$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$j \psi_a i_1$} (B)
(C) edge node[above]{$j \psi_x o_2$} (B)
(A) edge node[left]{$f$} (A')
(C) edge node[left]{$k$} (C')
(A') edge node [above]{$j \psi_{a^\prime} i_1^\prime$} (D)
(C') edge node [above]{$j \psi_{x^\prime} o_2^\prime$} (D)
(B) edge node [left] {$h_1 +_g h_2$} (D)
(A'') edge node[above]{$j \psi_{a^\prime} i_1^\prime$} (B'')
(C'') edge node[above]{$j \psi_{x^\prime} o_2^\prime$} (B'')
(A'') edge node[left]{$f^\prime$} (A''')
(C'') edge node[left]{$k^\prime$} (C''')
(A''') edge node [above]{$j \psi_{a''} i_1''$} (D'')
(C''') edge node [above]{$j \psi_{x''} o_2''$} (D'')
(B'') edge node [left] {$h_1^\prime +_{g^\prime} h_2^\prime$} (D'');
\end{tikzpicture}
\]
To obtain the morphism of decorations for a horizontal composite, we have as initial data:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (4,0) {$\iota_1 \Swarrow$};
\node (D) at (3,0) {$\bold{1}$};
\node (E) at (4.5,0.5) {$F(c)$};
\node (E') at (4.5,-0.5) {$F(c^\prime)$};
\node (A') at (6.5,0) {$\iota_2 \Swarrow$};
\node (D') at (5.5,0) {$\bold{1}$};
\node (E'') at (7,0.5) {$F(e)$};
\node (E''') at (7,-0.5) {$F(e^\prime)$};
\path[->,font=\scriptsize,>=angle 90]
(D) edge node [above] {$d_1$} (E)
(D) edge node [below] {$d_1^\prime$} (E')
(E) edge node [right] {$F(h_1)$} (E')
(D') edge node [above] {$d_2$} (E'')
(D') edge node [below] {$d_2^\prime$} (E''')
(E'') edge node [right] {$F(h_2)$} (E''');
\end{tikzpicture}
\]
and then multiply these viewed as two 2-morphisms in $\bold{Cat}$ which results in:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (4.75,0) {$\iota_1 \times \iota_2 \Swarrow$};
\node (D) at (3,0) {$\bold{1} \xrightarrow{\lambda^{-1}} \bold{1} \times \bold{1}$};
\node (E) at (5.5,0.5) {$F(c) \times F(e)$};
\node (E') at (5.5,-0.5) {$F(c^\prime) \times F(e^\prime)$};
\node (B) at (7.5,0.5) {$F(c+e)$};
\node (B') at (7.5,-0.5) {$F(c^\prime + e^\prime)$};
\node (C) at (9,0.5) {$F(c+_b e)$};
\node (C') at (9,-0.5) {$F(c^\prime +_{b^\prime} e^\prime)$};
\path[->,font=\scriptsize,>=angle 90]
(E) edge node [above] {$\phi_{c,e}$} (B)
(E') edge node [above] {$\phi_{c^\prime,e^\prime}$} (B')
(B) edge node [above] {$F(j_{c,e})$} (C)
(B') edge node [above] {$F(j_{c^\prime,e^\prime})$} (C')
(C) edge node [right] {$F(h_1 +_g h_2)$} (C')
(B) edge node [right] {$F(h_1 + h_2)$} (B')
(D) edge node [above] {$d_1 \times d_2$} (E)
(D) edge node [below] {$d_1^\prime \times d_2^\prime$} (E')
(E) edge node [right] {$F(h_1) \times F(h_2)$} (E');
\end{tikzpicture}
\]
where the middle square commutes since $F$ is a lax monoidal pseudofunctor and the right square commutes as the underlying diagram commutes. The objects $d_{1,2}$ and $d^\prime_{1,2}$ are given by top and bottom composite of arrows and the morphism of decorations $\iota_{1,2}$ is given by composing $\iota_1 \times \iota_2$ with the two commuting squares. Returning the interchange law, composing the two horizontal compositions above vertically then results in:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0.5) {$a$};
\node (A') at (0,-0.5) {$a''$};
\node (B) at (2,0.5) {$c+_b e$};
\node (C) at (4,0.5) {$x$};
\node (C') at (4,-0.5) {$x''$};
\node (D) at (2,-0.5) {$c'' +_{b''} e''$};
\node (E) at (5.5,0.5) {$d_{1,2} \in F(c+_b e)$};
\node (F) at (5.5,-0.5) {$d_{1,2}'' \in F(c'' +_{b''} e'')$};
\node (G) at (2,-1) {$(\iota_{1,2}^\prime \iota_{1,2}) \colon F((h_1^\prime +_{g^\prime} h_2^\prime)(h_1 +_g h_2))(d_{1,2}) \to d_{1,2}''.$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$j \psi_a i_1$} (B)
(C) edge node[above]{$j \psi_x o_2$} (B)
(A) edge node[left]{$f^\prime f$} (A')
(C) edge node[left]{$k^\prime k$} (C')
(A') edge node [above]{$j \psi_{a''} i_1''$} (D)
(C') edge node [above]{$j \psi_{x''} o_2''$} (D)
(B) edge node [left] {$(h_1^\prime +_{g^\prime} h_2^\prime)(h_1 +_g h_2)$} (D);
\end{tikzpicture}
\]
\textbf{F being pseudo might do something here...}
The vertical composite of two morphisms of decorations is straightforward. On the other hand, if we first compose vertically we obtain:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0.5) {$a$};
\node (A') at (0,-0.5) {$a''$};
\node (B) at (1,0.5) {$c$};
\node (C) at (2,0.5) {$b$};
\node (C') at (2,-0.5) {$b''$};
\node (D) at (1,-0.5) {$c''$};
\node (E) at (3,0.5) {$d_1 \in F(c)$};
\node (F) at (3,-0.5) {$d_1'' \in F(c'')$};
\node (G) at (4,0.5) {$b$};
\node (H) at (5,0.5) {$e$};
\node (I) at (6,0.5) {$x$};
\node (G') at (4,-0.5) {$b''$};
\node (H') at (5,-0.5) {$e''$};
\node (I') at (6,-0.5) {$x''$};
\node (J) at (7,0.5) {$d_2 \in F(e)$};
\node (K) at (7,-0.5) {$d_2'' \in F(e'')$};
\node (L) at (1,-1) {$\iota_1^\prime \iota_1 \colon F(h_1^\prime h_1)(d_1) \to d_1''$};
\node (M) at (5,-1) {$\iota_2^\prime \iota_2 \colon F(h_2^\prime h_2)(d_2) \to d_2''$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i_1$} (B)
(C) edge node[above]{$o_1$} (B)
(A) edge node[left]{$f^\prime f$} (A')
(C) edge node[left]{$g^\prime g$} (C')
(A') edge node[above] {$i_1''$} (D)
(C') edge node[above] {$o_1''$} (D)
(B) edge node [left] {$h_1^\prime h_1$} (D)
(G) edge node [above] {$i_2$} (H)
(G) edge node [left] {$g^\prime g$} (G')
(H) edge node [left] {$h_2^\prime h_2$} (H')
(G') edge node [above] {$i_2''$} (H')
(I) edge node [above] {$o_2$} (H)
(I) edge node [left] {$k^\prime k$} (I')
(I') edge node [above] {$o_2''$} (H');
\end{tikzpicture}
\]
and then composing horizontally results in:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0.5) {$a$};
\node (A') at (0,-0.5) {$a''$};
\node (B) at (2,0.5) {$c+_b e$};
\node (C) at (4,0.5) {$x$};
\node (C') at (4,-0.5) {$x''$};
\node (D) at (2,-0.5) {$c'' +_{b''} e''$};
\node (E) at (5.5,0.5) {$d_{1,2} \in F(c+_b e)$};
\node (F) at (5.5,-0.5) {$d_{1,2}'' \in F(c'' +_{b''} e'')$};
\node (G) at (2,-1) {$(\iota_1^\prime \iota_1,\iota_2^\prime \iota_2) \colon F((h_1^\prime h_1)+_{g^\prime g} (h_2^\prime h_2))(d_{1,2}) \to d_{1,2}''.$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$j \psi_a i_1$} (B)
(C) edge node[above]{$j \psi_x o_2$} (B)
(A) edge node[left]{$f^\prime f$} (A')
(C) edge node[left]{$k^\prime k$} (C')
(A') edge node [above]{$j \psi_{a''} i_1''$} (D)
(C') edge node [above]{$j \psi_{x''} o_2''$} (D)
(B) edge node [left] {$(h_1^\prime h_1) +_{g^\prime g} (h_2^\prime h_2)$} (D);
\end{tikzpicture}
\]
%The decorations of 
%\[
%\begin{tikzpicture}[scale=1.5]
%\node (A) at (0,0) {$1$};
%\node (B) at (2,0) {$F(c) \times F(e)$};
%\node (C) at (4,0) {$F(c+e)$};
%\node (D) at (4,-1) {$F(c+_b e)$};
%\node (E) at (4,-2) {$F(c'' +_{b''} e'')$};
%\node (F) at (0,-1) {$F(c) \times F(e)$};
%\node (G) at (0,-2) {$F(c'') \times F(e'')$};
%\node (H) at (2,-2) {$F(c'' + e'')$};
%\path[->,font=\scriptsize,>=angle 90]
%(A) edge node [above]{$d_1 \times d_2$} (B)
%(B) edge node [above] {$\phi_{c,e}$} (C)
%(C) edge node [right]{$F(j_{c,e})$} (D)
%(D) edge node [right] {$F((h_1^\prime +_{g^\prime} h_2^\prime)(h_1 +_g h_2))$} (E)
%(A) edge node [left] {$d_1 \times d_2$} (F)
%(F) edge node [left] {$F((h_1^\prime h_1) \times (h_2^\prime h_2))$} (G)
%(G) edge node [above] {$\phi_{c'',e''}$} (H)
%(H) edge node [above] {$F(j_{c'',e''})$} (E);
%\end{tikzpicture}
%\]
As is usual concerning the interchange law of double categories of this nature, only the `interior' of the two compositions appears different, but the two morphisms $(h_1^\prime +_{g^\prime} h_2^\prime)(h_1 +_g h_2) \colon c+_b e \to c'' +_{b''} e''$ and $(h_1^\prime h_1) +_{g^\prime g} (h_2^\prime h_2) \colon c+_b e \to c'' +_{b''}e''$ are the same universal map realized in two different ways. The two morphisms of decorations are two compositions of 2-morphisms in $\bold{Cat}$ for which the interchange law already holds, and as a result, the morphisms $$(\iota_{1,2}^\prime \iota_{1,2}) \colon F((h_1^\prime +_{g^\prime} h_2^\prime)(h_1 +_g h_2))(d_{1,2}) \to d_{1,2}''$$ and $$(\iota_1^\prime \iota_1,\iota_2^\prime \iota_2) \colon F((h_1^\prime h_1)+_{g^\prime g} (h_2^\prime h_2))(d_{1,2}) \to d_{1,2}''$$ are also the same.
\end{proof}

\begin{thm}\label{main1}
Let $\bold{C}$ be a category with finite colimits and $F \colon \bold{C} \to \bold{Cat}$ a symmetric lax monoidal pseudofunctor. Then the double category $\mathbb{F}\textnormal{Cospan}(\bold{C})$ is symmetric monoidal.
\end{thm}
\begin{proof}
First we note that the category of objects $\mathbb{F}\textnormal{Cospan}(\bold{C})_0=\bold{C}$ is symmetric monoidal under binary coproducts and the left and right unitors, associators and braidings are given as natural maps. The category of arrows $\mathbb{F}\textnormal{Cospan}(\bold{C})_1$ has:
\begin{enumerate}
\item{objects as pairs:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,1) {$c$};
\node (C) at (2,0) {$b$};
\node (D) at (3,0.5) {$d \in F(c)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B);
\end{tikzpicture}
\]
and}
\item{morphisms as maps of cospans in $\bold{C}$
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0.5) {$a$};
\node (A') at (0,-0.5) {$a^\prime$};
\node (B) at (1,0.5) {$c$};
\node (C) at (2,0.5) {$b$};
\node (C') at (2,-0.5) {$b^\prime$};
\node (D) at (1,-0.5) {$c^\prime$};
\node (E) at (3,0.5) {$d \in F(c)$};
\node (F) at (3,-0.5) {$d^\prime \in F(c^\prime)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B)
(A) edge node[left]{$f$} (A')
(C) edge node[left]{$g$} (C')
(A') edge node [above]{$i^\prime$} (D)
(C') edge node [above]{$o^\prime$} (D)
(B) edge node [left] {$h$} (D);
\end{tikzpicture}
\]
together with elements of the images of the apices under the pseudofunctor $F$ and a morphism $\iota \colon F(h)(d) \to d^\prime$.
}
\end{enumerate}
Given two objects $M_1$ and $M_2$ of $\mathbb{F}\textnormal{Cospan}(\bold{C})_1$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a_1$};
\node (B) at (1,1) {$c_1$};
\node (C) at (2,0) {$b_1$};
\node (D) at (1,-0.5) {$d_1 \in F(c_1)$};
\node (E) at (3,0) {$a_2$};
\node (F) at (4,1) {$c_2$};
\node (G) at (5,0) {$b_2$};
\node (H) at (4,-0.5) {$d_2 \in F(c_2)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i_1$} (B)
(C) edge node[above]{$o_1$} (B)
(E) edge node[above]{$i_2$} (F)
(G) edge node[above]{$o_2$} (F);
\end{tikzpicture}
\]
their tensor product $M_1 \otimes M_2$ is given by taking the coproducts of the cospans of $\bold{C}$
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a_1+a_2$};
\node (B) at (1,1) {$c_1+c_2$};
\node (C) at (2,0) {$b_1+b_2$};
\node (D) at (3.5,0.5) {$d_{M_1 \otimes M_2} \in F(c_1+c_2)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$i_1+i_2$} (B)
(C) edge node[right]{$o_1+o_2$} (B);
\end{tikzpicture}
\]
and where the element of the image of the apex under $F$  is obtained using the natural transformation of the symmetric lax monoidal pseudofunctor $F:$ $$1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{d_1 \times d_2} F(c_1) \times F(c_2) \xrightarrow{\phi_{c_1,c_2}} F(c_1 + c_2).$$The monoidal unit is given by:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$0$};
\node (B) at (1,1) {$0$};
\node (C) at (2,0) {$0$};
\node (D) at (3,0.5) {$! \in F(0)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$!$} (B)
(C) edge node[above]{$!$} (B);
\end{tikzpicture}
\]
where $0$ is the monoidal unit of $\bold{C}$ and $! \colon \bold{1} \to F(0)$ is the morphism which is part of the structure of the symmetric lax monoidal pseudofunctor $F \colon \bold{C} \to \bold{Cat}$. Tensoring an object with the monoidal unit, say, on the left:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$0$};
\node (B) at (1,1) {$0$};
\node (C) at (2,0) {$0$};
\node (D) at (1,-0.5) {$! \in F(0)$};
\node (E) at (3,0) {$a$};
\node (F) at (4,1) {$c$};
\node (G) at (5,0) {$b$};
\node (H) at (4,-0.5) {$d \in F(c)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$!$} (B)
(C) edge node[above]{$!$} (B)
(E) edge node[above]{$i$} (F)
(G) edge node[above]{$o$} (F);
\end{tikzpicture}
\]
results in:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$0+a$};
\node (B) at (1,1) {$0+c$};
\node (C) at (2,0) {$0+b$};
\node (D) at (3,0.5) {$d^\prime \in F(0+c)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$!+i$} (B)
(C) edge node[right]{$!+o$} (B);
\end{tikzpicture}
\]
where $d^\prime \in F(0+c)$ is given by $$1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{\phi \times d} F(0) \times F(c) \xrightarrow{\phi_{0,d}} F(0+c).$$The left unitor is then a morphism in $\mathbb{F} \textnormal{Cospan}(\bold{C})_1$ given by:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0.5) {$0+a$};
\node (A') at (0,-0.5) {$a$};
\node (B) at (1,0.5) {$0+c$};
\node (C) at (2,0.5) {$0+b$};
\node (C') at (2,-0.5) {$b$};
\node (D) at (1,-0.5) {$c$};
\node (E) at (3.5,0.5) {$d^\prime \in F(0+c)$};
\node (F) at (3.5,-0.5) {$d \in F(c)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$!+i$} (B)
(C) edge node[above]{$!+o$} (B)
(A) edge node[left]{$\ell$} (A')
(C) edge node[left]{$\ell$} (C')
(A') edge node [above]{$i$} (D)
(C') edge node [above]{$o$} (D)
(B) edge node [left] {$\ell$} (D);
\end{tikzpicture}
\]
where $\ell$ is the left unitor of $(\bold{C},+,0)$, together with the morphism $\iota_{\lambda} \colon F(\ell)(d^\prime) \to d$. The right unitor is similar.

Given three objects $M_1, M_2$ and $M_3$ in $\mathbb{F}\textnormal{Cospan}(\bold{C})_1$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a_1$};
\node (B) at (1,1) {$c_1$};
\node (C) at (2,0) {$b_1$};
\node (D) at (1,-0.5) {$d_1 \in F(c_1)$};
\node (E) at (3,0) {$a_2$};
\node (F) at (4,1) {$c_2$};
\node (G) at (5,0) {$b_2$};
\node (H) at (4,-0.5) {$d_2 \in F(c_2)$};
\node (I) at (6,0) {$a_3$};
\node (J) at (7,1) {$c_3$};
\node (K) at (8,0) {$b_3$};
\node (L) at (7,-0.5) {$d_3 \in F(c_3)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i_1$} (B)
(C) edge node[above]{$o_1$} (B)
(E) edge node[above]{$i_2$} (F)
(G) edge node[above]{$o_2$} (F)
(I) edge node[above]{$i_3$} (J)
(K) edge node[above]{$o_3$} (J);
\end{tikzpicture}
\]
tensoring the first two and then the third results in $(M_1 \otimes M_2) \otimes M_3$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$(a_1+a_2)+a_3$};
\node (B) at (1,1) {$(c_1+c_2)+c_3$};
\node (C) at (2,0) {$(b_1+b_2)+b_3$};
\node (D) at (4.5,0.5) {$d_{(M_1 \otimes M_2) \otimes M_3} \in F((c_1+c_2)+c_3)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$(i_1+i_2)+i_3$} (B)
(C) edge node[right]{$(o_1+o_2)+o_3$} (B);
\end{tikzpicture}
\]
where $d_{(M_1 \otimes M_2) \otimes M_3} \colon \bold{1} \to F((c_1+c_2)+c_3)$ is given by: $$1 \xrightarrow{((d_1 \times d_2) \times d_3)} (F(c_1) \times F(c_2)) \times F(c_3) \xrightarrow{\phi_{c_1,c_2} \times 1} F(c_1+c_2) \times F(c_3) \xrightarrow{\phi_{c_1+c_2,c_3}} F((c_1+c_2)+c_3)$$whereas tensoring the last two and then the first results in $M_1 \otimes (M_2 \otimes M_3)$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a_1+(a_2+a_3)$};
\node (B) at (1,1) {$c_1+(c_2+c_3)$};
\node (C) at (2,0) {$b_1+(b_2+b_3)$};
\node (D) at (4.5,0.5) {$d_{M_1 \otimes (M_2 \otimes M_3)} \in F(c_1+(c_2+c_3))$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$i_1+(i_2+i_3)$} (B)
(C) edge node[right]{$o_1+(o_2+o_3)$} (B);
\end{tikzpicture}
\]
where $d_{M_1 \otimes (M_2 \otimes M_3)} \colon \bold{1} \to F(c_1+(c_2+c_3))$ is given by: $$1 \xrightarrow{d_1 \times (d_2 \times d_3)} F(c_1) \times (F(c_2) \times F(c_3)) \xrightarrow{1 \times \phi_{c_2,c_3}} F(c_1) \times F(c_2+c_3) \xrightarrow{\phi_{c_1,c_2+c_3}} F(c_1+(c_2+c_3)).$$If we let $a$ denote the associator of $(\bold{C},+,0)$, the associator of $\mathbb{F} \textnormal{Cospan}(\bold{C})_1$ is then a map of cospans in $\bold{C}$ from $(M_1 \otimes M_2) \otimes M_3)$ to $M_1 \otimes (M_2 \otimes M_3)$ given by:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0.5) {$(a_1+a_2)+a_3$};
\node (A') at (0,-0.5) {$a_1+(a_2+a_3)$};
\node (B) at (2.25,0.5) {$(c_1+c_2)+c_3$};
\node (C) at (4.5,0.5) {$(b_1+b_2)+b_3$};
\node (C') at (4.5,-0.5) {$b_1+(b_2+b_3)$};
\node (D) at (2.25,-0.5) {$c_1+(c_2+c_3)$};
\node (E) at (7,0.5) {$d_{(M_1 \otimes M_2) \otimes M_3} \in F((c_1+c_2)+c_3)$};
\node (F) at (7,-0.5) {$d_{M_1 \otimes (M_2 \otimes M_3)} \in F(c_1+(c_2+c_3))$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$(i_1+i_2)+i_3$} (B)
(C) edge node[above]{$(o_1+o_2)+o_3$} (B)
(A) edge node[left]{$a$} (A')
(C) edge node[left]{$a$} (C')
(A') edge node [above]{$i_1+(i_2+i_3)$} (D)
(C') edge node [above]{$o_1+(o_2+o_3)$} (D)
(B) edge node [left] {$a$} (D);
\end{tikzpicture}
\]
together with the morphism $\iota_a \colon F(a)(d_{(M_1 \otimes M_2) \otimes M_3}) \to d_{M_1 \otimes (M_2 \otimes M_3)}$. If we denote the above associator simply as $a$ and the left and right unitors as $\lambda$ and $\rho$, respectively, then given four objects in $F\textnormal{Cospan}(\bold{C})_1$, say $M_1, M_2, M_3$ and $M_4$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a_1$};
\node (B) at (1,1) {$c_1$};
\node (C) at (2,0) {$b_1$};
\node (D) at (1,-0.5) {$d_1 \in F(c_1)$};
\node (E) at (3,0) {$a_2$};
\node (F) at (4,1) {$c_2$};
\node (G) at (5,0) {$b_2$};
\node (H) at (4,-0.5) {$d_2 \in F(c_2)$};
\node (I) at (0,-2) {$a_3$};
\node (J) at (1,-1) {$c_3$};
\node (K) at (2,-2) {$b_3$};
\node (L) at (1,-2.5) {$d_3 \in F(c_3)$};
\node (M) at (3,-2) {$a_4$};
\node (N) at (4,-1) {$c_4$};
\node (O) at (5,-2) {$b_4$};
\node (P) at (4,-2.5) {$d_4 \in F(c_4)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i_1$} (B)
(C) edge node[above]{$o_1$} (B)
(E) edge node[above]{$i_2$} (F)
(G) edge node[above]{$o_2$} (F)
(I) edge node[above]{$i_3$} (J)
(K) edge node[above]{$o_3$} (J)
(M) edge node[above]{$i_4$} (N)
(O) edge node[above]{$o_4$} (N);
\end{tikzpicture}
\]
then the following pentagon of underlying cospans commutes:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$((M_1 \otimes M_2) \otimes M_3) \otimes M_4$};
\node (B) at (2.25,1.5) {$(M_1 \otimes M_2) \otimes (M_3 \otimes M_4)$};
\node (C) at (4.5,0) {$M_1 \otimes (M_2 \otimes (M_3 \otimes M_4))$};
\node (D) at (.75,-2) {$(M_1 \otimes (M_2 \otimes M_3)) \otimes M_4$};
\node (E) at (3.75,-2) {$M_1 \otimes ((M_2 \otimes M_3) \otimes M_4)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$a$} (B)
(B) edge node[above]{$a$} (C)
(A) edge node[left]{$a \otimes 1$} (D)
(D) edge node[above]{$a$} (E)
(E) edge node[right]{$1 \otimes a$} (C);
\end{tikzpicture}
\]
as well as the following pentagon of corresponding decorations in the category $F(c_1 +(c_2 +(c_3+c_4)))$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (-.5,0) {$F(aa)(d_{((M_1 \otimes M_2) \otimes M_3) \otimes M_4}) $};
\node (B) at (2.25,1.5) {$F(a)(d_{(M_1 \otimes M_2) \otimes (M_3 \otimes M_4)})$};
\node (C) at (5,0) {$d_{M_1 \otimes (M_2 \otimes (M_3 \otimes M_4))}$};
\node (D) at (-.5,-2) {$F((1 \otimes a)a)(d_{(M_1 \otimes (M_2 \otimes M_3)) \otimes M_4}) $};
\node (E) at (5,-2) {$F(1 \otimes a)(d_{M_1 \otimes ((M_2 \otimes M_3) \otimes M_4)}) $};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$F(a)(\iota_a)$} (B)
(B) edge node[above]{$\iota_a$} (C)
(A) edge node[left]{$F((1 \otimes a)a)(\iota_{a \otimes 1})$} (D)
(D) edge node[above]{$F(1 \otimes a)(\iota_a)$} (E)
(E) edge node[right]{$\iota_{1 \otimes a}$} (C);
\end{tikzpicture}
\]
since $$F(aa)(d_{((M_1 \otimes M_2) \otimes M_3) \otimes M_4})=F((1 \otimes a)a(a \otimes 1))(d_{((M_1 \otimes M_2) \otimes M_3) \otimes M_4})$$ as the above underlying diagram of maps of cospans commutes.

Similarly, if we denote the left and right unitors as $\lambda$ and $\rho$, respectively, then the following triangle of underlying maps of cospans commutes:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$(M_1 \otimes U_{0}) \otimes M_2$};
\node (B) at (2.25,1.5) {$M_1 \otimes M_2$};
\node (C) at (4.5,0) {$M_1 \otimes (U_0 \otimes M_2)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$\rho \otimes 1$} (B)
(C) edge node[right]{$1 \otimes \lambda$} (B)
(A) edge node[above]{$a$} (C);
\end{tikzpicture}
\]
as well as the following triangle of corresponding decorations in the category $F(c_1+c_2)$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$F(\rho \otimes 1)(d_{(M_1 \otimes U_0) \otimes M_2})$};
\node (B) at (2.25,1.5) {$d_{M_1 \otimes M_2}$};
\node (C) at (4.5,0) {$F(1 \otimes \lambda)(d_{M_1 \otimes (U_0 \otimes M_2)}) $};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$\iota_{\rho \otimes 1}$} (B)
(C) edge node[right]{$\iota_{1 \otimes \lambda}$} (B)
(A) edge node[above]{$F(\iota_a)$} (C);
\end{tikzpicture}
\]
since $$F(\rho \otimes 1)(d_{(M_1 \otimes U_0) \otimes M_2})=F(a \otimes (1 \otimes \lambda))(d_{(M_1 \otimes U_0) \otimes M_2})$$ as the above underlying diagram of maps of cospans commutes.

For a monoidal product of objects $M_1 \otimes M_2$ in $\mathbb{F} \textnormal{Cospan}(\bold{C})_1$, the source and target structure functors $S,T \colon \mathbb{F} \textnormal{Cospan}(\bold{C})_1 \to \mathbb{F} \textnormal{Cospan}(\bold{C})_0$ satisfy the following equations: $$S(M_1 \otimes M_2)=S(M_1) \otimes S(M_2)$$ $$T(M_1 \otimes M_2)=T(M_1) \otimes T(M_2).$$
For two objects $M_1$ and $M_2$ in $\mathbb{F} \textnormal{Cospan}(\bold{C})_1$, we have a braiding $\beta_{M_1,M_2} \colon M_1 \otimes M_2 \to M_2 \otimes M_1$ given by:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0.5) {$a_1+a_2$};
\node (A') at (0,-0.5) {$a_2+a_1$};
\node (B) at (2,0.5) {$c_1+c_2$};
\node (C) at (4,0.5) {$b_1+b_2$};
\node (C') at (4,-0.5) {$b_2+b_1$};
\node (D) at (2,-0.5) {$c_2+c_1$};
\node (E) at (5.5,0.5) {$d_{M_1 \otimes M_2} \in F(c_1+c_2)$};
\node (F) at (5.5,-0.5) {$d_{M_2 \otimes M_1} \in F(c_2+c_1)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i_1+i_2$} (B)
(C) edge node[above]{$o_1+o_2$} (B)
(A) edge node[left]{$\beta_{a_1,a_2}$} (A')
(C) edge node[left]{$\beta_{b_1,b_2}$} (C')
(A') edge node [above]{$i_2+i_1$} (D)
(C') edge node [above]{$o_2+o_1$} (D)
(B) edge node [left] {$\beta_{c_1,c_2}$} (D);
\end{tikzpicture}
\]
$$\iota_{\beta_{M_1,M_2}} \colon F(\beta_{c_1,c_2})(d_{M_1 \otimes M_2}) \xrightarrow{\sim} d_{M_2 \otimes M_1}.$$
This braiding makes the following triangle of underlying cospans commute:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$M_1 \otimes M_2$};
\node (B) at (2.25,1.5) {$M_1 \otimes M_2$};
\node (C) at (4.5,0) {$M_2 \otimes M_1$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$1$} (B)
(C) edge node[right]{$\beta_{M_2,M_1}$} (B)
(A) edge node[above]{$\beta_{M_1,M_2}$} (C);
\end{tikzpicture}
\]
as well as the following diagram of corresponding decorations in the category $F(c_2+c_1)$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$F(\beta_{c_1,c_2})(d_{M_1 \otimes M_2})$};
\node (B) at (2.25,1.5) {$F(\beta_{c_1,c_2})(d_{M_1 \otimes M_2}) $};
\node (C) at (4.5,0) {$d_{M_2 \otimes M_1} $};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$1$} (B)
(C) edge node[right]{$F(\beta_{c_1,c_2})(\iota_{\beta_{M_2,M_1}})$} (B)
(A) edge node[above]{$\iota_{\beta_{M_1,M_2}}$} (C);
\end{tikzpicture}
\]
since $F(\beta_{c_1,c_2} \beta_{c_2,c_1}) (d_{M_2 \otimes M_1}) = d_{M_2 \otimes M_1}$. Thus $\mathbb{F} \textnormal{Cospan}(\bold{C})_1$ is also symmetric monoidal.

Now, given four horizontal 1-cells $M_1, M_2, N_1$ and $N_2$ respectively by:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a_1$};
\node (B) at (1,1) {$c_1$};
\node (C) at (2,0) {$b_1$};
\node (D) at (1,-0.5) {$d_{M_1} \in F(c_1)$};
\node (E) at (3,0) {$b_1$};
\node (F) at (4,1) {$e_1$};
\node (G) at (5,0) {$x_1$};
\node (H) at (4,-0.5) {$d_{M_2} \in F(e_1)$};
\node (I) at (0,-2) {$a_2$};
\node (J) at (1,-1) {$c_2$};
\node (K) at (2,-2) {$b_2$};
\node (L) at (1,-2.5) {$d_{N_1} \in F(c_2)$};
\node (M) at (3,-2) {$b_2$};
\node (N) at (4,-1) {$e_2$};
\node (O) at (5,-2) {$x_2$};
\node (P) at (4,-2.5) {$d_{N_2} \in F(e_2)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i_1$} (B)
(C) edge node[above]{$o_1$} (B)
(E) edge node[above]{$i_1^\prime$} (F)
(G) edge node[above]{$o_1^\prime$} (F)
(I) edge node[above]{$i_2$} (J)
(K) edge node[above]{$o_2$} (J)
(M) edge node[above]{$i_2^\prime$} (N)
(O) edge node[above]{$o_2^\prime$} (N);
\end{tikzpicture}
\]
we have that $(M_1 \otimes N_1) \odot (M_2 \otimes N_2)$ is given by:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a_1+a_2$};
\node (B) at (1,1) {$(c_1+c_2)+_{b_1+b_2}(e_1+e_2)$};
\node (C) at (2,0) {$x_1+x_2$};
\node (D) at (1,-0.5) {$d_{(M_1 \otimes N_1) \odot (M_2 \otimes N_2)} \in F((c_1+c_2)+_{b_1+b_2}(e_1+e_2))$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$j \psi(i_1+i_2)$} (B)
(C) edge node[right]{$j \psi(o_1^\prime + o_2^\prime)$} (B);
\end{tikzpicture}
\]
and $(M_1 \odot M_2) \otimes (N_1 \odot N_2)$ is given by:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a_1+a_2$};
\node (B) at (1,1) {$(c_1+_{b_1} e_1) + (c_2 +_{b_2} e_2)$};
\node (C) at (2,0) {$x_1+x_2$};
\node (D) at (1,-0.5) {$d_{(M_1 \odot M_2) \otimes (N_1 \odot N_2)} \in F((c_1+_{b_1}e_1)+(c_2+_{b_2}e_2))$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$(j \psi i_2)+(j \psi i_1)$} (B)
(C) edge node[right]{$(j \psi o_2^\prime)+(j \psi o_1^\prime)$} (B);
\end{tikzpicture}
\]
where $\psi$ and $j$ are the natural maps into a coproduct and from a coproduct into a pushout, respectively. We then get a globular 2-morphism $$\chi \colon (M_1 \otimes N_1) \odot (M_2 \otimes N_2) \to (M_1 \odot M_2) \otimes (N_1 \odot N_2)$$ given by:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0.5) {$a_1+a_2$};
\node (A') at (0,-0.5) {$a_1+a_2$};
\node (B) at (2.5,0.5) {$(c_1+c_2)+_{b_1+b_2}(e_1+e_2)$};
\node (C) at (5,0.5) {$b_1+b_2$};
\node (C') at (5,-0.5) {$b_1+b_2$};
\node (D) at (2.5,-0.5) {$(c_1+_{b_1}e_1)+(c_2+_{b_2}e_2)$};
\node (E) at (2.5,1) {$\hat{d}_1 \in F((c_1+c_2)+_{b_1+b_2}(e_1+e_2))$};
\node (F) at (2.5,-1) {$\hat{d}_2 \in F((c_1+_{b_1}e_1)+(c_2+_{b_2}e_2))$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$j \psi (i_1+i_2)$} (B)
(C) edge node[above]{$j \psi (o_1^\prime + o_2^\prime)$} (B)
(A) edge node[left]{$1$} (A')
(C) edge node[left]{$1$} (C')
(A') edge node [above]{$(j \psi i_2)+(j \psi i_1)$} (D)
(C') edge node [above]{$(j \psi o_2^\prime)+(j \psi o_1^\prime)$} (D)
(B) edge node [left] {$\hat{\chi}$} (D);
\end{tikzpicture}
\]
$$\iota_{\hat{\chi}} \colon F(\hat{\chi})(d_{(M_1 \otimes N_1) \odot (M_2 \otimes N_2)}) \to d_{(M_1 \odot M_2) \otimes (N_1 \odot N_2)}.$$
For two objects $a,b \in \bold{C}$, $U_{a+b}$ is given by:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a+b$};
\node (B) at (1,1) {$a+b$};
\node (C) at (2,0) {$a+b$};
\node (D) at (3,0.5) {$!_{a+b} \in F(a+b)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$1_{a+b}$} (B)
(C) edge node[right]{$1_{a+b}$} (B);
\end{tikzpicture}
\]
where $$!_{a+b} \colon 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{\phi \times \phi} F(0) \times F(0) \xrightarrow{F(!_a) \times F(!_b)} F(a) \times F(b) \xrightarrow{\phi_{a,b}} F(a+b).$$
Similarly, we have $U_a$ and $U_b$ given respectively by:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,1) {$a$};
\node (C) at (2,0) {$a$};
\node (D) at (1,-0.5) {$!_a \in F(a)$};
\node (E) at (3,0) {$b$};
\node (F) at (4,1) {$b$};
\node (G) at (5,0) {$b$};
\node (H) at (4,-0.5) {$!_b \in F(b)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$1_a$} (B)
(C) edge node[above]{$1_a$} (B)
(E) edge node[above]{$1_b$} (F)
(G) edge node[above]{$1_b$} (F);
\end{tikzpicture}
\]
and then $U_a + U_b$ is given by:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a+b$};
\node (B) at (1,1) {$a+b$};
\node (C) at (2,0) {$a+b$};
\node (D) at (3.25,0.5) {$!_a + !_b \in F(a+b)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$1_a + 1_b$} (B)
(C) edge node[right]{$1_a + 1_b$} (B);
\end{tikzpicture}
\]
where
$$!_a + !_b \colon 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{!_a \times !_b} F(a) \times F(b) \xrightarrow{\phi_{a,b}} F(a+b).$$
We then have another globular isomorphism $$\mu_{a,b} \colon U_{a+b} \to U_a + U_b$$ given by the identity 2-morphism:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0.5) {$a+b$};
\node (A') at (0,-0.5) {$a+b$};
\node (B) at (2,0.5) {$a+b$};
\node (C) at (4,0.5) {$a+b$};
\node (C') at (4,-0.5) {$a+b$};
\node (D) at (2,-0.5) {$a+b$};
\node (E) at (5.5,0.5) {$!_{a+b} \in F(a+b)$};
\node (F) at (5.5,-0.5) {$!_a + !_b \in F(a+b)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$1_{a+b}$} (B)
(C) edge node[above]{$1_{a+b}$} (B)
(A) edge node[left]{$1$} (A')
(C) edge node[left]{$1$} (C')
(A') edge node [above]{$1_a + 1_b$} (D)
(C') edge node [above]{$1_a + 1_b$} (D)
(B) edge node [left] {$1$} (D);
\end{tikzpicture}
\]
$$\iota_{a,b} \colon !_{a+b} \xrightarrow{\sim} !_a + !_b.$$

There are a fair amount of coherence diagrams to verify, many of which are similar in flavor and make use of the two above globular ismorphisms. We check a few to give a sense of what these are like. For example,  given horizontal 1-cells $M_i,N_i,P_i$, the following commutative diagram expresses the associativity isomorphism as a transformation of double categories.
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0.5) {$((M_1 \otimes N_1) \otimes P_1) \odot ((M_2 \otimes N_2) \otimes P_2)$};
\node (A') at (4.5,0.5) {$(M_1 \otimes (N_1 \otimes P_1)) \odot (M_2 \otimes (N_2 \otimes P_2))$};
\node (B) at (0,-0.5) {$((M_1 \otimes N_1) \odot (M_2 \otimes N_2)) \otimes (P_1 \odot P_2)$};
\node (C) at (4.5,-0.5) {$(M_1 \odot M_2) \otimes ((N_1 \otimes P_1) \odot (N_2 \otimes P_2))$};
\node (C') at (0,-1.5) {$((M_1 \odot M_2) \otimes (N_1 \odot N_2)) \otimes (P_1 \odot P_2)$};
\node (D) at (4.5,-1.5) {$(M_1 \odot M_2) \otimes ((N_1 \odot N_2) \otimes (P_1 \odot P_2))$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$a \odot a$} (A')
(A) edge node[left]{$\mu$} (B)
(A') edge node[right]{$\mu$} (C)
(B) edge node[left]{$\mu \otimes 1$} (C')
(C) edge node [right] {$1 \otimes \mu$} (D)
(C') edge node [above] {$a$} (D);
\end{tikzpicture}
\]
Here, $a$ is the associator of $\mathbb{F}\textnormal{Cospan}(\bold{C})_1$ and $\mu$ is the first globular isomorphism above. To see that this diagram does indeed commute, we first consider this diagram with respect to only the underlying cospans of each horizontal 1-cell. For notation:
	\[
		\begin{tikzpicture}
			\node (k) at (0,0) {$k$};
			\node (l) at (1,.5) {$l$};
			\node (m) at (2,0) {$m$};
			\node (M1) at (-1,.25) {$M_1 =$};
			\node (N1) at (3,.25) {$N_1 =$};
			\node (q) at (4,0) {$q$};
			\node (r) at (5,.5) {$r$};
			\node (s) at (6,0) {$s$};
			\node (P1) at (7,.25) {$P_1 =$};
			\node (v) at (8,0) {$v$};
			\node (w) at (9,.5) {$w$};
			\node (x) at (10,0) {$x$};
			\node (m2) at (0,-2) {$m$};
			\node (n) at (1,-1.5) {$n$};
			\node (p) at (2,-2) {$p$};
			\node (M2) at (-1,-1.75) {$M_2 =$};
			\node (N2) at (3,-1.75) {$N_2 =$};
			\node (s2) at (4,-2) {$s$};
			\node (t) at (5,-1.5) {$t$};
			\node (u) at (6,-2) {$u$};
			\node (P2) at (7,-1.75) {$P_2 =$};
			\node (x2) at (8,-2) {$x$};
			\node (y) at (9,-1.5) {$y$};
			\node (z) at (10,-2) {$z$};
\node (dM1) at (1,-0.5) {$d_{M_1} \in F(l)$};
\node (dM2) at (1,-2.5) {$d_{M_2} \in F(n)$};
\node (dN1) at (5,-0.5) {$d_{N_1} \in F(r)$};
\node (dN2) at (5,-2.5) {$d_{N_2} \in F(t)$};
\node (dP1) at (9,-0.5) {$d_{P_1} \in F(w)$};
\node (dP2) at (9,-2.5) {$d_{P_2} \in F(y)$};
			\path[->,font=\scriptsize,>=angle 90]
			(k) edge node[above]{$$} (l)
			(m) edge node[above]{$$} (l)
			(q) edge node[above]{$$} (r)
			(s) edge node[above]{$$} (r)
			(v) edge node[above]{$$} (w)
			(x) edge node[above]{$$} (w)
			(m2) edge node[above]{$$} (n)
			(p) edge node[above]{$$} (n)
			(s2) edge node[above]{$$} (t)
			(u) edge node[above]{$$} (t)
			(x2) edge node[above]{$$} (y)
			(z) edge node[above]{$$} (y);
		\end{tikzpicture}
	\]
The above diagram then becomes:
\[
		\begin{tikzpicture}
			\node (a) at (-4,0) {$k+m$};
			\node (b) at (1,0) {$((l+r)+w) +_{((m+s)+x)}((n+t)+y)$};
			\node (c) at (6,0) {$v+x$};
			\node (a2) at (-4,1.5) {$k+m$};
			\node (b2) at (1,1.5) {$(l+(r+w)) +_{(m+(s+x))}(n+(t+y))$};
			\node (c2) at (6,1.5) {$v+x$};
                                \node (a3) at (-4,3) {$k+m$};
			\node (b3) at (1,3) {$(l+_m n)+((r+w)+_{(s+x)}(t+y))$};
			\node (c3) at (6,3) {$v+x$};
                                \node (a4) at (-4,4.5) {$k+m$};
			\node (b4) at (1,4.5) {$(l+_m n)+((r+_s t)+(w+_x y))$};
			\node (c4) at (6,4.5) {$v+x$};
                                \node (a5) at (-4,-1.5) {$k+m$};
			\node (b5) at (1,-1.5) {$((l+r)+_{(m+s)}(n+t))+(w+_x y)$};
			\node (c5) at (6,-1.5) {$v+x$};
                                \node (a6) at (-4,-3) {$k+m$};
			\node (b6) at (1,-3) {$((l+_m n)+(r+_s t))+(w+_x y)$};
			\node (c6) at (6,-3) {$v+x$};
                                \node (a7) at (-4,-4.5) {$k+m$};
			\node (b7) at (1,-4.5) {$(l+_m n)+((r+_s t)+(w+_x y))$};
			\node (c7) at (6,-4.5) {$v+x$};
			\path[->,font=\scriptsize,>=angle 90]
			(a) edge node[above]{$$} (b)
			(c) edge node[above]{$$} (b)
                                (a2) edge node[above]{$$} (b2)
			(c2) edge node[above]{$$} (b2)
                                (a) edge node[above]{$$} (a2)
                                (b) edge node[left]{$a \odot a$} (b2)
(b) edge node[right]{$\iota_1$} (b2)
			(c) edge node[above]{$$} (c2)
                                (a3) edge node[above]{$$} (b3)
			(c3) edge node[above]{$$} (b3)
                                (a2) edge node[above]{$$} (a3)
                                (b2) edge node[left]{$\mu$} (b3)
(b2) edge node[right]{$\iota_2$} (b3)
			(c2) edge node[above]{$$} (c3)
                                (a4) edge node[above]{$$} (b4)
			(c4) edge node[above]{$$} (b4)
                                (a3) edge node[above]{$$} (a4)
                                (b3) edge node[left]{$1 \otimes \mu$} (b4)
(b3) edge node[right]{$\iota_3$} (b4)
			(c3) edge node[above]{$$} (c4)
                                (a5) edge node[above]{$$} (b5)
			(c5) edge node[above]{$$} (b5)
                                (a) edge node[above]{$$} (a5)
                                (b) edge node[left]{$\mu$} (b5)
(b) edge node[right]{$\iota_4$} (b5)
			(c) edge node[above]{$$} (c5)
                                (a6) edge node[above]{$$} (b6)
			(c6) edge node[above]{$$} (b6)
                                (a5) edge node[above]{$$} (a6)
                                (b5) edge node[left]{$\mu \otimes 1$} (b6)
 (b5) edge node[right]{$\iota_5$} (b6)
			(c5) edge node[above]{$$} (c6)
                                (a7) edge node[above]{$$} (b7)
			(c7) edge node[above]{$$} (b7)
                                (a6) edge node[above]{$$} (a7)
                                (b6) edge node[left]{$a$} (b7)
(b6) edge node[right]{$\iota_6$} (b7)
			(c6) edge node[above]{$$} (c7);
		\end{tikzpicture}
	\]
Here all of the vertical 1-morphisms on the left and right are identities, the middle vertical 1-morphisms are the 2-morphisms from the previous commutative diagram, and the horizontal vertical 1-morphisms pointing towards the middle are natural maps into each colimit, all of which are naturally isomorphic to each other as all the middle objects are colimits of the same diagram, namely the previous collection of cospans, taken in various ways. The above diagram of maps of cospans can then be visualized as a hexagonal prism in which all the faces commute by identifying the top and the bottom as the same. As for the decorations, each isomorphism $\iota_n$ goes from the domain under the image of the functor $F$ applied to natural isomorphism adjacent to it to the codomain as written, meaning that, for example: $$\iota_1 \colon F(a \odot a)(d_{((M_1 \otimes N_1) \otimes P_1) \odot ((M_2 \otimes N_2) \otimes P_2)}) \to d_{(M_1 \otimes (N_1 \otimes P_1)) \odot (M_2 \otimes (N_2 \otimes P_2))}.$$  The following diagram commutes in the category $F((l+_m n) + ((r+_s t) + (w+_x y)))$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0.5) {$F( a (\mu \otimes 1)\mu)(d_{((M_1 \otimes N_1) \otimes P_1) \odot ((M_2 \otimes N_2) \otimes P_2)})$};
\node (A') at (4.5,0.5) {$F((1 \otimes \mu) \mu)(d_{(M_1 \otimes (N_1 \otimes P_1)) \odot (M_2 \otimes (N_2 \otimes P_2))})$};
\node (B) at (0,-0.5) {$F(a(\mu  \otimes 1))(d_{((M_1 \otimes N_1) \odot (M_2 \otimes N_2)) \otimes (P_1 \odot P_2)})$};
\node (C) at (4.5,-0.5) {$F(1 \otimes \mu)(d_{(M_1 \odot M_2) \otimes ((N_1 \otimes P_1) \odot (N_2 \otimes P_2))})$};
\node (C') at (0,-1.5) {$F(a)(d_{((M_1 \odot M_2) \otimes (N_1 \odot N_2)) \otimes (P_1 \odot P_2)})$};
\node (D) at (4.5,-1.5) {$d_{(M_1 \odot M_2) \otimes ((N_1 \odot N_2) \otimes (P_1 \odot P_2))}$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$F((1 \otimes \mu) \mu)(\iota_1)$} (A')
(A) edge node[left]{$F(a(\mu \otimes 1))(\iota_4)$} (B)
(A') edge node[right]{$F(1 \otimes \mu)(\iota_2)$} (C)
(B) edge node[left]{$F(a)(\iota_5)$} (C')
(C) edge node [right] {$\iota_3$} (D)
(C') edge node [above] {$\iota_6$} (D);
\end{tikzpicture}
\]
since $$F(a(\mu \otimes 1)\mu)(d_{((M_1 \otimes N_1) \otimes P_1) \odot ((M_2 \otimes N_2) \otimes P_2)}) = F((1 \otimes \mu) \mu (a \odot a))(d_{((M_1 \otimes N_1) \otimes P_1) \odot ((M_2 \otimes N_2) \otimes P_2)})$$
as the above underlying diagram of maps of cospans commutes.

Another requirement for a double category to be symmetric monoidal is that the braiding $$\beta_{ ( \_, \_ ) } \colon \mathbb{F}\textnormal{Cospan}(\bold{C})_1 \times \mathbb{F}\textnormal{Cospan}(\bold{C})_1 \to \mathbb{F}\textnormal{Cospan}(\bold{C})_1 \times \mathbb{F}\textnormal{Cospan}(\bold{C})_1$$ be a transformation of double categories, and one of the diagrams that is required to commute is the following:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$(M_1 \odot M_2) \otimes (N_1 \odot N_2)$};
\node (B) at (3,0) {$(N_1 \odot N_2) \otimes (M_1 \odot M_2)$};
\node (C) at (0,-1) {$(M_1 \otimes N_1) \odot (M_2 \otimes N_2)$};
\node (D) at (3,-1) {$(N_1 \otimes M_1) \odot (N_2 \otimes M_2)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$\beta$} (B)
(B) edge node[right]{$\mu$} (D)
(A) edge node[left]{$\mu$} (C)
(C) edge node[above]{$\beta \odot \beta$} (D);
\end{tikzpicture}
\]
Using the same notation as the previous coherence diagram, the diagram for the underlying maps of cospans becomes:
\[
		\begin{tikzpicture}
			\node (a) at (-4,0) {$k+m$};
			\node (b) at (1,0) {$(l+_m n) + (r+_s t)$};
			\node (c) at (6,0) {$s+u$};
			\node (a2) at (-4,1.5) {$k+m$};
			\node (b2) at (1,1.5) {$(r +_s t) + (l +_m n)$};
			\node (c2) at (6,1.5) {$s+u$};
                                \node (a3) at (-4,3) {$k+m$};
			\node (b3) at (1,3) {$(r+l) +_{(s+m)} (t+n)$};
			\node (c3) at (6,3) {$s+u$};
                                \node (a5) at (-4,-1.5) {$k+m$};
			\node (b5) at (1,-1.5) {$(l+r) +_{(m+s)} (n+t)$};
			\node (c5) at (6,-1.5) {$s+u$};
                                \node (a6) at (-4,-3) {$k+m$};
			\node (b6) at (1,-3) {$(r+l) +_{(s+m)} (t+n)$};
			\node (c6) at (6,-3) {$s+u$};
			\path[->,font=\scriptsize,>=angle 90]
			(a) edge node[above]{$$} (b)
			(c) edge node[above]{$$} (b)
                                (a2) edge node[above]{$$} (b2)
			(c2) edge node[above]{$$} (b2)
                                (a) edge node[above]{$$} (a2)
                                (b) edge node[left]{$\beta$} (b2)
(b) edge node[right]{$\iota_1$} (b2)
			(c) edge node[above]{$$} (c2)
                                (a3) edge node[above]{$$} (b3)
			(c3) edge node[above]{$$} (b3)
                                (a2) edge node[above]{$$} (a3)
                                (b2) edge node[left]{$\mu$} (b3)
(b2) edge node[right]{$\iota_2$} (b3)
			(c2) edge node[above]{$$} (c3)
                                (a5) edge node[above]{$$} (b5)
			(c5) edge node[above]{$$} (b5)
                                (a) edge node[above]{$$} (a5)
                                (b) edge node[left]{$\mu$} (b5)
(b) edge node[right]{$\iota_4$} (b5)
			(c) edge node[above]{$$} (c5)
                                (a6) edge node[above]{$$} (b6)
			(c6) edge node[above]{$$} (b6)
                                (a5) edge node[above]{$$} (a6)
                                (b5) edge node[left]{$\beta \odot \beta$} (b6)
 (b5) edge node[right]{$\iota_5$} (b6)
			(c5) edge node[above]{$$} (c6);
		\end{tikzpicture}
	\]
All the comments about the previous underlying coherence diagram of maps of cospans apply to this one. As for the decorations, the following diagram commutes in the category $F((r+l)+_{(s+m)}(t+n))$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$F(\mu \beta)(d_{(M_1 \odot M_2) \otimes (N_1 \odot N_2)})$};
\node (B) at (3,0) {$F(\mu)(d_{(N_1 \odot N_2) \otimes (M_1 \odot M_2)})$};
\node (C) at (0,-1) {$F(\beta \odot \beta)(d_{(M_1 \otimes N_1) \odot (M_2 \otimes N_2)})$};
\node (D) at (3,-1) {$d_{(N_1 \otimes M_1) \odot (N_2 \otimes M_2)}$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$F(\mu)(\iota_1)$} (B)
(B) edge node[right]{$\iota_2$} (D)
(A) edge node[left]{$F(\beta \odot \beta)(\iota_3)$} (C)
(C) edge node[above]{$\iota_4$} (D);
\end{tikzpicture}
\]
since $$F(\mu \beta)(d_{(M_1 \odot M_2) \otimes (N_1 \odot N_2)}) = F((\beta \odot \beta)\mu)(d_{(M_1 \odot M_2) \otimes (N_1 \odot N_2)})$$
as the above underlying diagram of maps of cospans commutes. The other diagrams are shown to commute similarly.
\end{proof}

\begin{lem}
The double category $\mathbb{F}\textnormal{Cospan}(\bold{C})$ is fibrant.
\end{lem}

\begin{proof}
Let $f \colon c \to c^\prime$ be a vertical 1-morphism in $\mathbb{F} \textnormal{Cospan}(\bold{C})$. We can lift $f$ to the companion horizontal 1-cell $\hat{f}$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$c$};
\node (B) at (1,1) {$c^\prime$};
\node (C) at (2,0) {$c^\prime$};
\node (D) at (3,0.5) {$!_{c^\prime} \in F(c^\prime)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$f$} (B)
(C) edge node[above]{$1$} (B);
\end{tikzpicture}
\]
and then obtain the following two 2-morphisms:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0.5) {$c$};
\node (A') at (0,-0.5) {$c^\prime$};
\node (B) at (1,0.5) {$c^\prime$};
\node (C) at (2,0.5) {$c^\prime$};
\node (C') at (2,-0.5) {$c^\prime$};
\node (D) at (1,-0.5) {$c^\prime$};
\node (E) at (3,0.5) {$!_{c^\prime} \in F(c^\prime)$};
\node (F) at (3,-0.5) {$!_{c^\prime} \in F(c^\prime)$};
\node (G) at (4,0.5) {$c$};
\node (H) at (5,0.5) {$c$};
\node (I) at (6,0.5) {$c$};
\node (G') at (4,-0.5) {$c$};
\node (H') at (5,-0.5) {$c^\prime$};
\node (I') at (6,-0.5) {$c^\prime$};
\node (J) at (7,0.5) {$!_{c} \in F(c)$};
\node (K) at (7,-0.5) {$!_{c^\prime} \in F(c^\prime)$};
\node (L) at (1,-1) {$\iota_{c^\prime} = 1_{!_{c^\prime}}$};
\node (M) at (5,-1) {$\iota_f \colon F(f)(!_c) \to !_{c^\prime}$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$f$} (B)
(C) edge node[above]{$1$} (B)
(A) edge node[left]{$f$} (A')
(C) edge node[left]{$1$} (C')
(A') edge node[above] {$1$} (D)
(C') edge node[above] {$1$} (D)
(B) edge node [left] {$1$} (D)
(G) edge node [above] {$1$} (H)
(G) edge node [left] {$1$} (G')
(H) edge node [left] {$f$} (H')
(G') edge node [above] {$f$} (H')
(I) edge node [above] {$1$} (H)
(I) edge node [left] {$f$} (I')
(I') edge node [above] {$1$} (H');
\end{tikzpicture}
\]
which satisfy the equations:
\[
\begin{tikzpicture}[scale=1.5]
\node (N) at (0,1.5) {$c$};
\node (O) at (1,1.5) {$c$};
\node (P) at (2,1.5) {$c$};
\node (Q) at (-1,1.5) {$!_c \in F(c)$};
\node (A) at (0,0.5) {$c$};
\node (A') at (0,-0.5) {$c^\prime$};
\node (B) at (1,0.5) {$c^\prime$};
\node (C) at (2,0.5) {$c^\prime$};
\node (C') at (2,-0.5) {$c^\prime$};
\node (D) at (1,-0.5) {$c^\prime$};
\node (E) at (-1,0.5) {$!_{c^\prime} \in F(c^\prime)$};
\node (F) at (-1,-0.5) {$!_{c^\prime} \in F(c^\prime)$};
\node (G) at (4,1) {$c$};
\node (H) at (5,1) {$c$};
\node (I) at (6,1) {$c$};
\node (G') at (4,0) {$c^\prime$};
\node (H') at (5,0) {$c^\prime$};
\node (I') at (6,0) {$c^\prime$};
\node (J) at (7,1) {$!_{c} \in F(c)$};
\node (K) at (7,0) {$!_{c^\prime} \in F(c^\prime)$};
\node (Q) at (1,-1) {$\iota_f \colon F(f)(!_c) \to !_{c^\prime}$};
\node (L) at (1,-1.5) {$\iota_{c^\prime} = 1_{!_{c^\prime}}$};
\node (M) at (5,-0.5) {$\iota_f \colon F(f)(!_c) \to !_{c^\prime}$};
\node (R) at (3,0.5) {$=$};
\path[->,font=\scriptsize,>=angle 90]
(N) edge node[above]{$1$} (O)
(P) edge node[above]{$1$} (O)
(N) edge node[left]{$1$} (A)
(O) edge node[left]{$f$} (B)
(P) edge node[left]{$f$} (C)
(A) edge node[above]{$f$} (B)
(C) edge node[above]{$1$} (B)
(A) edge node[left]{$f$} (A')
(C) edge node[left]{$1$} (C')
(A') edge node[above] {$1$} (D)
(C') edge node[above] {$1$} (D)
(B) edge node [left] {$1$} (D)
(G) edge node [above] {$1$} (H)
(G) edge node [left] {$f$} (G')
(H) edge node [left] {$f$} (H')
(G') edge node [above] {$1$} (H')
(I) edge node [above] {$1$} (H)
(I) edge node [left] {$f$} (I')
(I') edge node [above] {$1$} (H');
\end{tikzpicture}
\]
\[
\begin{tikzpicture}[scale=1.5]
\node (G) at (-1,0.5) {$c$};
\node (H) at (-1,-0.5)  {$c^\prime$};
\node (I) at (-2,0.5) {$c$};
\node (J) at (-2,-0.5) {$c$};
\node (A) at (0,0.5) {$c$};
\node (A') at (0,-0.5) {$c^\prime$};
\node (B) at (1,0.5) {$c^\prime$};
\node (C) at (2,0.5) {$c^\prime$};
\node (C') at (2,-0.5) {$c^\prime$};
\node (D) at (1,-0.5) {$c^\prime$};
\node (E) at (1,1) {$!_{c^\prime} \in F(c^\prime)$};
\node (F) at (1,-1) {$!_{c^\prime} \in F(c^\prime)$};

\node (L) at (1,-1.5) {$\iota_{c^\prime} = 1_{!_{c^\prime}}$};
\node (E') at (-1,1) {$!_{c} \in F(c)$};
\node (F') at (-1,-1) {$!_{c^\prime} \in F(c^\prime)$};

\node (L') at (-1,-1.5) {$\iota_{f} \colon F(f)(!_c) \to !_{c^\prime}$};

\node (M) at (2.5,0) {$=$};
\node (N) at (3,0.5) {$c$};
\node (O) at (3,-0.5) {$c$};
\node (P) at (4,0.5) {$c^\prime$};
\node (Q) at (4,-0.5) {$c^\prime$};
\node (R) at (5,0.5) {$c^\prime$};
\node (S) at (5,-0.5) {$c^\prime$};
\node (T) at (4,1) {$!_{c^\prime} \in F(c^\prime)$};
\node (U) at (4,-1) {$!_{c^\prime} \in F(c^\prime)$};
\node (V) at (4,-1.5) {$\iota_{c^\prime} = 1_{!_{c^\prime}}$};

\path[->,font=\scriptsize,>=angle 90]
(N) edge node[left]{$1$} (O)
(P) edge node[left]{$1$} (Q)
(R) edge node[left]{$1$} (S)
(N) edge node[above]{$f$} (P)
(O) edge node[above]{$f$} (Q)
(R) edge node[above]{$1$} (P)
(S) edge node[above]{$1$} (Q)

(A) edge node[above]{$f$} (B)
(C) edge node[above]{$1$} (B)
(A) edge node[left]{$f$} (A')
(C) edge node[left]{$1$} (C')
(A') edge node[above] {$1$} (D)
(C') edge node[above] {$1$} (D)
(B) edge node [left] {$1$} (D)
(A) edge node[above]{$1$} (G)
(G) edge node[left]{$f$} (H)
(A') edge node[above]{$1$} (H)
(J) edge node[above] {$f$} (H)
(I) edge node[left] {$1$} (J)
(I) edge node [above] {$1$} (G);
\end{tikzpicture}
\]
The right hand sides of the above two equations are given respectively by the 2-morphisms $U_f$ and $1_{\hat{f}}$. The conjoint of $f$ is given by the $F$-decorated cospan $\check{f}$ which is just the opposite of the companion above:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$c^\prime$};
\node (B) at (1,1) {$c^\prime$};
\node (C) at (2,0) {$c$};
\node (D) at (3,0.5) {$!_{c^\prime} \in F(c^\prime)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$1$} (B)
(C) edge node[above]{$f$} (B);
\end{tikzpicture}
\]
\end{proof}

The property of being fibrant is what allows us to lift the monoidal structure from the object category of a double category to its arrow category and obtain a symmetric monoidal bicategory. The following result, which only requires fibrancy on vertical 1-isomorphisms (isofibrancy) is due to Shulman \cite{Shul}:

\begin{thm}[Shulman]\label{Shul}
Let $\mathbb{D}$ be an isofibrant symmetric monoidal pseudo double category. Then the horizontal bicategory $H(\mathbb{D})$ of $\mathbb{D}$ is a symmetric monoidal bicategory which has:
\begin{enumerate}
\item{objects as those of $\mathbb{D}$,}
\item{morphisms as horizontal 1-cells of $\mathbb{D}$, and}
\item{2-morphisms as globular 2-morphisms of $\mathbb{D}$.}
\end{enumerate}
\end{thm}

\begin{thm}
There exists a symmetric monoidal bicategory $H(\mathbb{F}\textnormal{Cospan}(\bold{C}))$ which has:
\begin{enumerate}
\item{objects as those of $\bold{C}$,}
\item{morphisms as pairs:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,1) {$c$};
\node (C) at (2,0) {$b$};
\node (D) at (3,0.5) {$d \in F(c)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B);
\end{tikzpicture}
\]
and}
\item{2-morphisms as maps of cospans in $\bold{C}$ of the form:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,1) {$c$};
\node (C) at (2,0) {$b$};
\node (E) at (1,-1) {$c^\prime$};
\node (D) at (3,0.5) {$d \in F(c)$};
\node (F) at (3,-0.5) {$d^\prime \in F(c^\prime)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B)
(A) edge node[below]{$i^\prime$} (E)
(B) edge node[left]{$h$} (E)
(C) edge node[below]{$o^\prime$} (E);
\end{tikzpicture}
\]
together with a morphism $\iota \colon F(h)(d) \to d^\prime$ in $F(c^\prime)$.}
\end{enumerate}
\end{thm}

\begin{proof}
This follows immediately by Shulman's Theorem \ref{Shul} above.
\end{proof}

This symmetric monoidal bicategory is a superior version of the symmetric monoidal bicategory constructed earlier by the second author \cite{Cour}. The previous bicategory constructed by the second author suffered even more so from the issue discussed in the introduction. Given a symmetric lax monoidal functor $F \colon \bold{C} \to \bold{Set}$, a result of Fong \cite{Fong} yields a symmetric monoidal category $F \textnormal{Cospan}(\bold{C})$ which has:
\begin{enumerate}
\item{objects as those of $\bold{C}$ and}
\item{morphisms as isomorphism classes of decorated cospans in $\bold{C}$.}
\end{enumerate}
The second author then using a result of Shulman \cite{Shul} extended this to a bicategory also called $F \textnormal{Cospan}(\bold{C})$ which has:
\begin{enumerate}
\item{objects as those of $\bold{C}$,}
\item{morphisms as now just decorated cospans in $\bold{C}$, and}
\item{2-morphisms as pairs of commuting diagrams:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,1) {$c$};
\node (B') at (1,-1) {$c^\prime$};
\node (C) at (2,0) {$b$};
\node (D) at (3,0) {$\bold{1}$};
\node (E) at (4,0.5) {$F(c)$};
\node (E') at (4,-0.5) {$F(c^\prime)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B)
(A) edge node[below]{$i^\prime$} (B')
(C) edge node[below]{$o^\prime$} (B')
(B) edge node [left] {$f$} (B')
(D) edge node [above] {$d$} (E)
(D) edge node [below] {$d^\prime$} (E')
(E) edge node [right] {$F(f)$} (E');
\end{tikzpicture}
\]
}
\end{enumerate}
This was discussed in the introduction and it was mentioned how in the symmetric monoidal category version of $F \textnormal{Cospan}(\bold{C})$, that the two single-edged graphs:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$v_1$};
\node (B) at (1,0) {$v_2$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$e$} (B);
\end{tikzpicture}
\]
and
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$v_1$};
\node (B) at (1,0) {$v_2.$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$e^\prime$} (B);
\end{tikzpicture}
\]
resided in distinct isomorphism classes. In the bicategorical version of $F \textnormal{Cospan}(\bold{C})$ where we are no longer considering decorated cospans up to isomorphism class, there is no 2-morphism between these two graphs due to the strict commutativity of the triangle to the right above. This problem does not occur in the symmetric monoidal bicategory $H(\mathbb{F}\textnormal{Cospan}(\bold{C}))$ and there is in fact a 2-(iso)morphism between these two graphs given by the map $\iota \colon F(f)(d) \to d^\prime$ which maps the edge $e$ to the edge $e^\prime$, where $f$ is the underlying map of vertices.

%Again, let $F \colon \bold{FinSet} \to \bold{Set}$ be the symmetric lax monoidal functor that maps a finite set $N$ to the large set of all possible graph structures whose underlying set of vertices is $N$. Then a result of Fong \cite{Fong} yields a symmetric monoidal category $F\textnormal{Cospan}(\bold{FinSet})$ which has:
%\begin{enumerate}
%\item{finite sets as objects and}
%\item{isomorphism classes of `open' graphs as morphisms, where an open graph is a cospan of finite sets whose apex is equipped with the structure of a graph.}
%\end{enumerate}

%An example of an open graph is:
%\begin{center}
%\begin{tikzpicture}[scale=2.15]
%\node (N) at (0.5,-1.25) {$N=\{v_1,v_2,v_3\}$};
%    \node[circle,draw,inner sep=1pt,fill=gray,color=gray]         (x) at (-1.4,-.43) {};
%    \node at (-1.4,-.9) {$X$};
%    \node       (A) at (0,0) {$v_1$};
%    \node     (B) at (1,0) {$v_2$};
%    \node        (C) at (0.5,-.86) {$v_3$};
%    \node[circle,draw,inner sep=1pt,fill=gray,color=gray]         (y1) at (2.4,-.25) {};
%    \node[circle,draw,inner sep=1pt,fill=gray,color=gray]         (y2) at (2.4,-.61) {};
%    \node at (2.4,-.9) {$Y$};
%    \path (B) edge  [bend right,->-] node[above] {$e_1$} (A);
%    \path (A) edge  [bend right,->-] node[below] {$e_2$} (B);
%    \path (A) edge  [->-] node[left] {$e_3$} (C);
%    \path (C) edge  [->-] node[right] {$e_4$} (B);
%    \path[color=gray, very thick, shorten >=10pt, shorten <=5pt, ->, >=stealth] (x) edge (A);
%    \path[color=gray, very thick, shorten >=10pt, shorten <=5pt, ->, >=stealth] (y1) edge (B);
%    \path[color=gray, very thick, shorten >=10pt, shorten <=5pt, ->, >=stealth] (y2) edge (B);
%\end{tikzpicture}
%\end{center}
%Here, the sets $X$ and $Y$ serve as inputs and outputs. The second author then extended Fong's category using a result of Shulman \cite{Shul} to obtain a symmetric monoidal bicategory which has:

%the following two single-edged graphs constituted distinct isomorphism classes:
%\[
%\begin{tikzpicture}[scale=1.5]
%\node (A) at (0,0) {$v_1$};
%\node (B) at (2,0) {$v_2$};
%\node (C) at (0,-2) {$v_1$};
%\node (D) at (2,-2) {$v_2$};
%\path[->,font=\scriptsize,>=angle 90]
%(A) edge node[above]{$e$} (B)
%(C) edge node[above]{$e^\prime$} (D);
%\end{tikzpicture}
%\]

We can the decategorify this symmetric monoidal bicategory to obtain a symmetric monoidal category similar to the one obtained using Fong's result:

\begin{cor}
Given a symmetric lax monoidal pseudofunctor $F \colon \bold{C} \to \bold{Cat}$ where $\bold{C}$ is a category with finite colimits and whose monoidal structure is given by binary coproducts, there exists a symmetric monoidal category $D(H(F\textnormal{Cospan}(\bold{C})))$ which has:
\begin{enumerate}
\item{objects as those of $\bold{C}$ and}
\item{morphisms as isomorphism classes of $F$-decorated cospans of $\bold{C}$, where an $F$-decorated cospan is given by a pair:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,1) {$c$};
\node (C) at (2,0) {$b$};
\node (D) at (3,0.5) {$d \in F(c)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B);
\end{tikzpicture}
\]
Given another $F$-decorated cospan:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,-1) {$c^\prime$};
\node (C) at (2,0) {$b$};
\node (D) at (3,-0.5) {$d^\prime \in F(c^\prime)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[below]{$i^\prime$} (B)
(C) edge node[below]{$o^\prime$} (B);
\end{tikzpicture}
\]
these two $F$-decorated cospans are in the same isomorphism class if there exists an isomorphism $f \colon c \to c^\prime$ such that following diagram commutes:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B') at (1,1) {$c$};
\node (B) at (1,-1) {$c^\prime$};
\node (C) at (2,0) {$b$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[below]{$i^\prime$} (B)
(C) edge node[below]{$o^\prime$} (B)
(A) edge node[above]{$i$} (B')
(C) edge node[above]{$o$} (B')
(B') edge node[left]{$f$} (B);
\end{tikzpicture}
\]
and there exists an isomorphism $\iota \colon F(f)(d) \to d^\prime$ in $F(c^\prime)$.}
\end{enumerate}
\end{cor}
In this symmetric monoidal category, isomorphism classes are as they should morally be, and the instance of two graphs having different edge sets does not prevent them from being in the same isomorphism class due to the isomorphism $\iota$.

\section{Maps of decorated cospan double categories}
Let $F \colon \bold{C} \to \bold{Cat}$ be a symmetric lax monoidal pseudofunctor. Then by Theorem \ref{main1} of the previous section, we get a symmetric monoidal double category $\mathbb{F}\textnormal{Cospan}(\bold{C})$. This symmetric monoidal double category has:
\begin{enumerate}
\item{objects as those of $\bold{C}$,}
\item{vertical 1-morphisms as morphisms of $\bold{C}$,}
\item{horizontal 1-cells as pairs:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,1) {$c$};
\node (C) at (2,0) {$b$};
\node (D) at (3,0.5) {$d \in F(c)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B);
\end{tikzpicture}
\]
and}
\item{2-morphisms as maps of cospans in $\bold{C}$
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0.5) {$a$};
\node (A') at (0,-0.5) {$a^\prime$};
\node (B) at (1,0.5) {$c$};
\node (C) at (2,0.5) {$b$};
\node (C') at (2,-0.5) {$b^\prime$};
\node (D) at (1,-0.5) {$c^\prime$};
\node (E) at (3,0.5) {$d \in F(c)$};
\node (F) at (3,-0.5) {$d^\prime \in F(c^\prime)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$$} (B)
(C) edge node[above]{$$} (B)
(A) edge node[left]{$f$} (A')
(C) edge node[left]{$g$} (C')
(A') edge node {$$} (D)
(C') edge node {$$} (D)
(B) edge node [left] {$h$} (D);
\end{tikzpicture}
\]
together with a morphism $\iota \colon F(h)(d) \to d^\prime$ in $F(c^\prime)$.}
\end{enumerate}
Given another symmetric lax monoidal pseudofunctor $F^\prime \colon \bold{C^\prime} \to \bold{Cat}$, we can obtain another symmetric monoidal double category $\mathbb{F^\prime}\textnormal{Cospan}(\bold{C^\prime})$. Then a map from $\mathbb{F}\textnormal{Cospan}(\bold{C})$ to $\mathbb{F^\prime}\textnormal{Cospan}(\bold{C^\prime})$ will be a double functor $\mathbb{H} \colon \mathbb{F}\textnormal{Cospan}(\bold{C}) \to \mathbb{F^\prime}\textnormal{Cospan}(\bold{C^\prime})$ whose object component is given by a finite colimit preserving functor $\mathbb{H}_0 = H \colon \bold{C} \to \bold{C^\prime}$ and whose arrow component is given by a functor $\mathbb{H}_1$ defined on horizontal 1-cells by:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,1) {$c$};
\node (C) at (2,0) {$b$};
\node (D) at (1,-0.5) {$d \in F(c)$};
\node (E) at (2.75,0.25) {$\mapsto$};
\node (A') at (3.5,0) {$H(a)$};
\node (B') at (4.5,1) {$H(c)$};
\node (C') at (5.5,0) {$H(b)$};
\node (D') at (4.5,-0.5) {$E(d) \in F^\prime(H(c))$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$i$} (B)
(C) edge node[right]{$o$} (B)
(A') edge node[left]{$H(i)$} (B')
(C') edge node[right]{$H(o)$} (B');
\end{tikzpicture}
\]
and on 2-morphisms by:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0.5) {$a$};
\node (A') at (0,-0.5) {$a^\prime$};
\node (B) at (1,0.5) {$c$};
\node (C) at (2,0.5) {$b$};
\node (C') at (2,-0.5) {$b^\prime$};
\node (D) at (1,-0.5) {$c^\prime$};
\node (E) at (3,0.5) {$d \in F(c)$};
\node (F) at (3,-0.5) {$d^\prime \in F(c^\prime)$};
\node (G) at (1,-1) {$\iota \colon F(h)(d) \to d^\prime$};
\node (A'') at (4.25,0.5) {$H(a)$};
\node (A''') at (4.25,-0.5) {$H(a^\prime)$};
\node (B'') at (5.25,0.5) {$H(c)$};
\node (C'') at (6.25,0.5) {$H(b)$};
\node (C''') at (6.25,-0.5) {$H(b^\prime)$};
\node (D'') at (5.25,-0.5) {$H(c^\prime)$};
\node (E'') at (7.5,0.5) {$E(d) \in F^\prime(H(c))$};
\node (F'') at (7.5,-0.5) {$E(d^\prime) \in F^\prime(H(c^\prime))$};
\node (G'') at (5.25,-1) {$E(\iota) \colon F^\prime(H(h))(E(d)) \to E(d^\prime)$};
\node (H) at (3.5,0) {$\mapsto$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$$} (B)
(C) edge node[above]{$$} (B)
(A) edge node[left]{$f$} (A')
(C) edge node[left]{$g$} (C')
(A') edge node {$$} (D)
(C') edge node {$$} (D)
(B) edge node [left] {$h$} (D)
(A'') edge node[above]{$$} (B'')
(C'') edge node[above]{$$} (B'')
(A'') edge node[left]{$H(f)$} (A''')
(C'') edge node[left]{$H(g)$} (C''')
(A''') edge node {$$} (D'')
(C''') edge node {$$} (D'')
(B'') edge node [left] {$H(h)$} (D'');
\end{tikzpicture}
\]
where $E \colon \bold{Cat} \to \bold{Cat}$ is a terminal category preserving 2-functor such that the following diagram commutes:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$\bold{C}$};
\node (B) at (1,0) {$\bold{Cat}$};
\node (C) at (0,-1) {$\bold{C^\prime}$};
\node (D) at (1,-1) {$\bold{Cat}$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$F$} (B)
(A) edge node[left]{$H$} (C)
(B) edge node[right]{$E$} (D)
(C) edge node[above]{$F^\prime$} (D);
\end{tikzpicture}
\]
Recall that we can think of the element $d \in F(c)$ as a morphism $d \colon \bold{1} \to F(c)$ and the morphism $\iota \colon F(h)(d) \to d^\prime$ of $F(c^\prime)$ as a 2-morphism  in $\bold{Cat}$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,-0.5) {$\bold{1}$};
\node (B) at (1,0) {$F(c)$};
\node (D) at (1,-1) {$F(c^\prime)$};
\node (C) at (0.75,-0.5) {$\Swarrow$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$d$} (B)
(A) edge node[below]{$d^\prime$} (D)
(B) edge node[right]{$F(h)$} (D);
\end{tikzpicture}
\]
Applying the terminal category preserving 2-functor $E \colon \bold{Cat} \to \bold{Cat}$ to this diagram yields:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,-0.5) {$E(\bold{1}) \cong \bold{1}$};
\node (B) at (1.5,0.25) {$E(F(c))$};
\node (D) at (1.5,-1.25) {$E(F(c^\prime))$};
\node (C) at (1,-0.5) {$\Swarrow$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$E(d)$} (B)
(A) edge node[below]{$E(d^\prime)$} (D)
(B) edge node[right]{$E(F(h))$} (D);
\end{tikzpicture}
\]
Then because the above square commutes, this is the same as 
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,-0.5) {$E(\bold{1}) \cong \bold{1}$};
\node (B) at (1.5,0.25) {$F^\prime(H(c))$};
\node (D) at (1.5,-1.25) {$F^\prime(H(c^\prime))$};
\node (C) at (1,-0.5) {$\Swarrow$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$E(d)$} (B)
(A) edge node[below]{$E(d^\prime)$} (D)
(B) edge node[right]{$F^\prime(H((h))$} (D);
\end{tikzpicture}
\]
which is the same as a morphism $E(\iota) \colon F^\prime(H(h))(E(d)) \to E(d^\prime)$ in $F^\prime(H(c^\prime))$. To check that the above recipe is functorial, given two vertically composable 2-morphisms in $\mathbb{F}\textnormal{Cospan}(\bold{C})$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0.5) {$a$};
\node (A') at (0,-0.5) {$a^\prime$};
\node (B) at (1.5,0.5) {$c$};
\node (C) at (3,0.5) {$b$};
\node (C') at (3,-0.5) {$b^\prime$};
\node (D) at (1.5,-0.5) {$c^\prime$};
\node (E) at (4.5,0.5) {$d \in F(c)$};
\node (F) at (4.5,-0.5) {$d^\prime \in F(c^\prime)$};
\node (G) at (1.5,-1) {$\iota \colon F(h)(d) \to d^\prime$};
\node (A'') at (0,-1.5) {$a^\prime$};
\node (A''') at (0,-2.5) {$a''$};
\node (B'') at (1.5,-1.5) {$c^\prime$};
\node (C'') at (3,-1.5) {$b^\prime$};
\node (C''') at (3,-2.5) {$b''$};
\node (D'') at (1.5,-2.5) {$c''$};
\node (E'') at (4.5,-1.5) {$d^\prime \in F(c^\prime)$};
\node (F'') at (4.5,-2.5) {$d'' \in F(c'')$};
\node (G'') at (1.5,-3) {$\iota^\prime \colon F(h^\prime)(d^\prime) \to d''$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$$} (B)
(C) edge node[above]{$$} (B)
(A) edge node[left]{$f$} (A')
(C) edge node[left]{$g$} (C')
(A') edge node [above]{$$} (D)
(C') edge node [above]{$$} (D)
(B) edge node [left] {$h$} (D)
(A'') edge node[above]{$$} (B'')
(C'') edge node[above]{$$} (B'')
(A'') edge node[left]{$f^\prime$} (A''')
(C'') edge node[left]{$g^\prime$} (C''')
(A''') edge node [above]{$$} (D'')
(C''') edge node [above]{$$} (D'')
(B'') edge node [left] {$h^\prime$} (D'');
\end{tikzpicture}
\]
if we first compose these, the result is:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0.5) {$a$};
\node (A') at (0,-0.5) {$a''$};
\node (B) at (1.5,0.5) {$c$};
\node (C) at (3,0.5) {$b$};
\node (C') at (3,-0.5) {$b''$};
\node (D) at (1.5,-0.5) {$c''$};
\node (E) at (4.5,0.5) {$d \in F(c)$};
\node (F) at (4.5,-0.5) {$d'' \in F(c'')$};
\node (G) at (1.5,-1) {$\iota ^\prime \iota \colon F(h^\prime h)(d) \to d''$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$$} (B)
(C) edge node[above]{$$} (B)
(A) edge node[left]{$f^\prime f$} (A')
(C) edge node[left]{$g^\prime g$} (C')
(A') edge node [above]{$$} (D)
(C') edge node [above]{$$} (D)
(B) edge node [left] {$h^\prime h$} (D);
\end{tikzpicture}
\]
and then the image of this 2-morphism under the double functor $\mathbb{H}$ is given by:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0.5) {$H(a)$};
\node (A') at (0,-0.5) {$H(a'')$};
\node (B) at (1.5,0.5) {$H(c)$};
\node (C) at (3,0.5) {$H(b)$};
\node (C') at (3,-0.5) {$H(b'')$};
\node (D) at (1.5,-0.5) {$H(c'')$};
\node (E) at (4.5,0.5) {$E(d) \in F^\prime(H(c))$};
\node (F) at (4.5,-0.5) {$E(d'') \in F^\prime(H(c''))$};
\node (G) at (1.5,-1) {$E(\iota ^\prime \iota) \colon F^\prime(H(h^\prime h))(E(d)) \to E(d'').$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$$} (B)
(C) edge node[above]{$$} (B)
(A) edge node[left]{$H(f^\prime f)$} (A')
(C) edge node[left]{$H(g^\prime g)$} (C')
(A') edge node [above]{$$} (D)
(C') edge node [above]{$$} (D)
(B) edge node [left] {$H(h^\prime h)$} (D);
\end{tikzpicture}
\]
On the other hand, applying the double functor $\mathbb{H}$ first gives:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0.5) {$H(a)$};
\node (A') at (0,-0.5) {$H(a^\prime)$};
\node (B) at (1.5,0.5) {$H(c)$};
\node (C) at (3,0.5) {$H(b)$};
\node (C') at (3,-0.5) {$H(b^\prime)$};
\node (D) at (1.5,-0.5) {$H(c^\prime)$};
\node (E) at (4.5,0.5) {$E(d) \in F^\prime(H(c))$};
\node (F) at (4.5,-0.5) {$E(d^\prime) \in F^\prime(H(c^\prime))$};
\node (G) at (1.5,-1) {$E(\iota) \colon F^\prime(H(h))(E(d)) \to E(d^\prime)$};
\node (A'') at (0,-1.5) {$H(a^\prime)$};
\node (A''') at (0,-2.5) {$H(a'')$};
\node (B'') at (1.5,-1.5) {$H(c^\prime)$};
\node (C'') at (3,-1.5) {$H(b^\prime)$};
\node (C''') at (3,-2.5) {$H(b'')$};
\node (D'') at (1.5,-2.5) {$H(c'')$};
\node (E'') at (4.5,-1.5) {$E(d^\prime) \in F^\prime(H(c^\prime))$};
\node (F'') at (4.5,-2.5) {$E(d'') \in F^\prime(H(c''))$};
\node (G'') at (1.5,-3) {$E(\iota^\prime) \colon F^\prime(H(h^\prime))(E(d^\prime)) \to E(d'')$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$$} (B)
(C) edge node[above]{$$} (B)
(A) edge node[left]{$H(f)$} (A')
(C) edge node[left]{$H(g)$} (C')
(A') edge node [above]{$$} (D)
(C') edge node [above]{$$} (D)
(B) edge node [left] {$H(h)$} (D)
(A'') edge node[above]{$$} (B'')
(C'') edge node[above]{$$} (B'')
(A'') edge node[left]{$H(f^\prime)$} (A''')
(C'') edge node[left]{$H(g^\prime)$} (C''')
(A''') edge node [above]{$$} (D'')
(C''') edge node [above]{$$} (D'')
(B'') edge node [left] {$H(h^\prime)$} (D'');
\end{tikzpicture}
\]
and then composing these gives:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0.5) {$H(a)$};
\node (A') at (0,-0.5) {$H(a'')$};
\node (B) at (1.5,0.5) {$H(c)$};
\node (C) at (3,0.5) {$H(b)$};
\node (C') at (3,-0.5) {$H(b'')$};
\node (D) at (1.5,-0.5) {$H(c'')$};
\node (E) at (4.5,0.5) {$E(d) \in F^\prime(H(c))$};
\node (F) at (4.5,-0.5) {$E(d'') \in F^\prime(H(c''))$};
\node (G) at (1.5,-1) {$E(\iota ^\prime \iota) \colon F^\prime(H(h^\prime h))(E(d)) \to E(d'').$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$$} (B)
(C) edge node[above]{$$} (B)
(A) edge node[left]{$H(f^\prime f)$} (A')
(C) edge node[left]{$H(g^\prime g)$} (C')
(A') edge node [above]{$$} (D)
(C') edge node [above]{$$} (D)
(B) edge node [left] {$H(h^\prime h)$} (D);
\end{tikzpicture}
\]
This double functor $\mathbb{H}$ satisfies the equations $S \mathbb{H}_1 = HS$ and $T \mathbb{H}_1=HT$.

Given two composable horizontal 1-cells $M$ and $N$ in $\mathbb{F}\textnormal{Cospan}(\bold{C})$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a_1$};
\node (B) at (1,1) {$c_1$};
\node (C) at (2,0) {$b$};
\node (D) at (1,-0.5) {$d_1 \in F(c_1)$};
\node (E) at (3,0) {$b$};
\node (F) at (4,1) {$c_2$};
\node (G) at (5,0) {$a_2$};
\node (H) at (4,-0.5) {$d_2 \in F(c_2)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i_1$} (B)
(C) edge node[above]{$o_1$} (B)
(E) edge node[above]{$i_2$} (F)
(G) edge node[above]{$o_2$} (F);
\end{tikzpicture}
\]
composing first gives $M \odot N$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a_1$};
\node (B) at (1,1) {$c_1+_b c_2$};
\node (C) at (2,0) {$a_2$};
\node (D) at (1,-0.5) {$d \in F(c_1 +_b c_2)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$\psi j_{c_1} i_1$} (B)
(C) edge node[right]{$\psi j_{c_2} o_2$} (B);
\end{tikzpicture}
\]
where $$d \colon 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{d_1 \times d_2} F(c_1) \times F(c_2) \xrightarrow{\phi_{c_1,c_2}} F(c_1+c_2) \xrightarrow{F(\psi)}F(c_1 +_b c_2).$$ The image of this horizontal 1-cell is then given by $\mathbb{H}(M \odot N)$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$H(a_1)$};
\node (B) at (1,1) {$H(c_1+_b c_2)$};
\node (C) at (2,0) {$H(a_2)$};
\node (D) at (1,-0.5) {$E(d) \in F^\prime(H(c_1 +_b c_2))$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$H(\psi j_{c_1} i_1)$} (B)
(C) edge node[right]{$H(\psi j_{c_2} o_2)$} (B);
\end{tikzpicture}
\]
where $$E(d) \colon 1 \xrightarrow{E(d)} E(F(c_1 +_b c_2)) = F^\prime(H(c_1 +_b c_2)).$$ On the other hand, the image of each horizontal 1-cell under the double functor $\mathbb{H}$ is given respectively by $\mathbb{H}(M)$ and $\mathbb{H}(N)$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$H(a_1)$};
\node (B) at (1,1) {$H(c_1)$};
\node (C) at (2,0) {$H(b)$};
\node (D) at (1,-0.5) {$E(d_1) \in F^\prime(H(c_1))$};
\node (E) at (3,0) {$H(b)$};
\node (F) at (4,1) {$H(c_2)$};
\node (G) at (5,0) {$H(a_2)$};
\node (H) at (4,-0.5) {$E(d_2) \in F^\prime(H(c_2))$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$H(i_1)$} (B)
(C) edge node[right]{$H(o_1)$} (B)
(E) edge node[left]{$H(i_2)$} (F)
(G) edge node[right]{$H(o_2)$} (F);
\end{tikzpicture}
\]
Composing these then gives $\mathbb{H}(M) \odot \mathbb{H}(N)$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$H(a_1)$};
\node (B) at (1,1) {$H(c_1)+_{H(b)} H(c_2)$};
\node (C) at (2,0) {$H(a_2)$};
\node (D) at (1,-0.5) {$d^\prime \in F^\prime(H(c_1) +_{H(b)} H(c_2))$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$\Psi j_{H(c_1)} H(i_1)$} (B)
(C) edge node[right]{$\Psi j_{H(c_2)} H(o_2)$} (B);
\end{tikzpicture}
\]
where $$d^\prime \colon 1 \xrightarrow{E(d_1) \times E(d_2)} F^\prime(H(c_1)) \times F^\prime(H(c_2)) \xrightarrow{\Phi_{H(c_1),H(c_2)}} F^\prime(H(c_1)+ H(c_2)) \xrightarrow{F^\prime (H(\Psi))} F^\prime(H(c_1) +_{H(b)} H(c_2)).$$
We then have a comparison constraint: $$\mathbb{H}_{M,N} \colon \mathbb{H}(M) \odot \mathbb{H}(N) \xrightarrow{\sim} \mathbb{H}(M \odot N)$$given by the globular 2-isomorphism:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0.5) {$H(a_1)$};
\node (A') at (0,-0.5) {$H(a_1)$};
\node (B) at (2.5,0.5) {$H(c_1)+_{H(b)} H(c_2)$};
\node (C) at (5,0.5) {$H(a_2)$};
\node (C') at (5,-0.5) {$H(a_2)$};
\node (D) at (2.5,-0.5) {$H(c_1 +_b c_2)$};
\node (E) at (7,0.5) {$d^\prime \in F^\prime(H(c_1)+_{H(b_1)}H(c_2))$};
\node (F) at (7,-0.5) {$d \in F^\prime(H(c_1 +_b c_2))$};
\node (G) at (2.5,-1) {$\iota_{\kappa^{-1}} \colon F^\prime(\kappa^{-1})(d^\prime) \to d.$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$\Psi j_{H(c_1)} H(i_1)$} (B)
(C) edge node[above]{$\Psi j_{H(c_2)} H(o_2)$} (B)
(A) edge node[left]{$1$} (A')
(C) edge node[left]{$1$} (C')
(A') edge node [above]{$H(\psi j_{c_1} i_1)$} (D)
(C') edge node [above]{$H(\psi j_{c_2} o_2)$} (D)
(B) edge node [left] {$\kappa^{-1}$} (D);
\end{tikzpicture}
\]
where $\kappa$ is the isomorphism $$\kappa \colon H(c_1 +_b c_2) \xrightarrow{\sim} H(c_1) +_{H(b)} H(c_2)$$ which comes from the functor $H \colon \bold{C} \to \bold{C^\prime}$ preserving finite colimits. The above diagram commutes by a similar argument as to the one used in Theorem \ref{main2}. Similarly we have a unit comparison constraint $$\mathbb{H}_U \colon U_{\mathbb{H}(c)} \to \mathbb{H}(U_c)$$ given by the globular 2-isomorphism:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0.5) {$H(c)$};
\node (A') at (0,-0.5) {$H(c)$};
\node (B) at (1.5,0.5) {$H(c)$};
\node (C) at (3,0.5) {$H(c)$};
\node (C') at (3,-0.5) {$H(c)$};
\node (D) at (1.5,-0.5) {$H(c)$};
\node (E) at (4.5,0.5) {$!_{H(c)} \in F^\prime(H(c))$};
\node (F) at (4.5,-0.5) {$E(!_c) \in F^\prime(H(c))$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$1$} (B)
(C) edge node[above]{$1$} (B)
(A) edge node[left]{$1$} (A')
(C) edge node[left]{$1$} (C')
(A') edge node [above]{$1$} (D)
(C') edge node [above]{$1$} (D)
(B) edge node [left] {$1$} (D);
\end{tikzpicture}
\]
where the morphism of decorations is the identity $!_{H(c)} = E(!_c)$ as $EF=F^\prime H$. These comparison constrains satisfy the coherence axioms of a monoidal category, namely:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0.5) {$(\mathbb{H}(M) \odot \mathbb{H}(N)) \odot \mathbb{H}(P)$};
\node (B) at (0,-0.5) {$\mathbb{H}(M \odot N) \odot \mathbb{H}(P)$};
\node (C) at (0,-1.5) {$\mathbb{H}((M \odot N) \odot P)$};
\node (A') at (3,0.5) {$\mathbb{H}(M) \odot (\mathbb{H}(N) \odot \mathbb{H}(P))$};
\node (B') at (3,-0.5) {$\mathbb{H}(M) \odot \mathbb{H}(N \odot P)$};
\node (C') at (3,-1.5) {$\mathbb{H}(M \odot (N \odot P))$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$\mathbb{H}_{M,N} \odot 1$} (B)
(B) edge node[left]{$\mathbb{H}_{M \odot N,P}$} (C)
(A) edge node[above]{$a$} (A')
(C) edge node [above] {$\mathbb{H}(a^\prime)$} (C')
(B') edge node [right] {$\mathbb{H}_{M,N \odot P}$} (C')
(A') edge node [right]{$1 \odot \mathbb{H}_{N \odot P}$} (B');
\end{tikzpicture}
\]
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$U_{\mathbb{H}(a)} \odot \mathbb{H}(M)$};
\node (B) at (2.5,0) {$\mathbb{H}(U_a) \odot \mathbb{H}(M)$};
\node (C) at (0,-1) {$\mathbb{H}(M)$};
\node (D) at (2.5,-1) {$\mathbb{H}(U_a \odot M)$};
\node (A') at (5,0) {$\mathbb{H}(M) \odot U_{\mathbb{H}(b)}$};
\node (B') at (7.5,0) {$\mathbb{H}(M) \odot \mathbb{H}(U_b)$};
\node (C') at (5,-1) {$\mathbb{H}(M)$};
\node (D') at (7.5,-1) {$\mathbb{H}(M \odot U_b)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$\mathbb{H}_U \odot 1$} (B)
(A) edge node[left]{$\lambda$} (C)
(B) edge node[right]{$\mathbb{H}_{U_a,M}$} (D)
(D) edge node[above]{$\mathbb{H}(\lambda^\prime)$} (C)
(A') edge node[above]{$1 \odot \mathbb{H}_U$} (B')
(A') edge node[left]{$\rho$} (C')
(B') edge node[right]{$\mathbb{H}_{M,U_b}$} (D')
(D') edge node[above]{$\mathbb{H}(\rho^\prime)$} (C');
\end{tikzpicture}
\]
This shows that $\mathbb{H}=(H,E)$ is a double functor. Next we show that this double functor is in fact symmetric monoidal. First, that the object component $\mathbb{H}_0=H$ is symmetric monoidal is clear as $H$ preserves finite colimits. As for the arrow component $\mathbb{H}_1$, given two horizontal 1-cells $M_1$ and $M_2$ in $\mathbb{F}\textnormal{Cospan}(\bold{C})$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a_1$};
\node (B) at (1,1) {$c_1$};
\node (C) at (2,0) {$b_1$};
\node (D) at (1,-0.5) {$d_1 \in F(c_1)$};
\node (E) at (3,0) {$a_2$};
\node (F) at (4,1) {$c_2$};
\node (G) at (5,0) {$b_2$};
\node (H) at (4,-0.5) {$d_2 \in F(c_2)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i_1$} (B)
(C) edge node[above]{$o_1$} (B)
(E) edge node[above]{$i_2$} (F)
(G) edge node[above]{$o_2$} (F);
\end{tikzpicture}
\]
their tensor product $M_1 \otimes M_2$ in $\mathbb{F}\textnormal{Cospan}(\bold{C})$ is given by:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a_1+a_2$};
\node (B) at (1,1) {$c_1+c_2$};
\node (C) at (2,0) {$b_1+b_2$};
\node (D) at (1,-0.5) {$d_1+d_2 \in F(c_1)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$i_1+i_2$} (B)
(C) edge node[right]{$o_1+o_2$} (B);
\end{tikzpicture}
\]
$$d_1+d_2 \colon 1 \xrightarrow{d_1 \times d_2} F(c_1) \times F(c_2) \xrightarrow{\phi_{c_1,c_2}} F(c_1+c_2)$$
and the image of this horizontal 1-cell under the double functor $\mathbb{H}$ is $\mathbb{H}(M_1 \otimes M_2)$ given by:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$H(a_1+a_2)$};
\node (B) at (1,1) {$H(c_1+c_2)$};
\node (C) at (2,0) {$H(b_1+b_2)$};
\node (D) at (1,-0.5) {$E(d_1+d_2) \in E(F(c_1+c_2)) = F^\prime(H(c_1+c_2))$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$H(i_1+i_2)$} (B)
(C) edge node[right]{$H(o_1+o_2)$} (B);
\end{tikzpicture}
\]
On the other hand, the image of $M_1$ and $M_2$ is given by $\mathbb{H}(M_1)$ and $\mathbb{H}(M_2)$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$H(a_1)$};
\node (B) at (1,1) {$H(c_1)$};
\node (C) at (2,0) {$H(b_1)$};
\node (D) at (1,-0.5) {$E(d_1) \in F^\prime(H(c_1))$};
\node (E) at (3,0) {$H(a_2)$};
\node (F) at (4,1) {$H(c_2)$};
\node (G) at (5,0) {$H(b_2)$};
\node (H) at (4,-0.5) {$E(d_2) \in F^\prime(H(c_2))$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$H(i_1)$} (B)
(C) edge node[right]{$H(o_1)$} (B)
(E) edge node[left]{$H(i_2)$} (F)
(G) edge node[right]{$H(o_2)$} (F);
\end{tikzpicture}
\]
and their tensor product $\mathbb{H}(M_1) \otimes \mathbb{H}(M_2)$ is given by:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$H(a_1)+H(a_2)$};
\node (B) at (1,1) {$H(c_1)+H(c_2)$};
\node (C) at (2,0) {$H(b_1)+H(b_2)$};
\node (D) at (1,-0.5) {$E(d_1)+E(d_2) \in F^\prime(H(c_1)+H(c_2))$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$H(i_1)+H(i_2)$} (B)
(C) edge node[right]{$H(o_1)+H(o_2)$} (B);
\end{tikzpicture}
\]
$$E(d_1)+E(d_2) \colon 1 \xrightarrow{E(d_1) \times E(d_2)} F^\prime(H(c_1)) \times F^\prime(H(c_2)) \xrightarrow{\Phi_{H(c_1),H(c_2)}} F^\prime (H(c_1)+H(c_2)).$$  We then have a natural 2-isomorphism $\mu_{M_1,M_2} \colon \mathbb{H}(M_1) \otimes \mathbb{H}(M_2) \to \mathbb{H}(M_1 \otimes M_2)$ in $\mathbb{F^\prime}\textnormal{Cospan}(\bold{C^\prime})$ given by:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0.5) {$H(a_1)+H(a_2)$};
\node (A') at (0,-0.5) {$H(a_1+a_2)$};
\node (B) at (2.5,0.5) {$H(c_1)+H(c_2)$};
\node (C) at (5,0.5) {$H(b_1)+H(b_2)$};
\node (C') at (5,-0.5) {$H(b_1+b_2)$};
\node (D) at (2.5,-0.5) {$H(c_1+c_2)$};
\node (E) at (2.5,1) {$E(d_1)+E(d_2) \in F^\prime(H(c_1)+H(c_2))$};
\node (F) at (2.5,-1) {$E(d_1+d_2) \in F^\prime(H(c_1+c_2))$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$H(i_1)+H(i_2)$} (B)
(C) edge node[above]{$H(o_1)+H(o_2)$} (B)
(A) edge node[left]{$\kappa$} (A')
(C) edge node[left]{$\kappa$} (C')
(A') edge node [above]{$H(i_1+i_2)$} (D)
(C') edge node [above]{$H(o_1+o_2)$} (D)
(B) edge node [left] {$\kappa$} (D);
\end{tikzpicture}
\]
$$\iota_\kappa \colon F^\prime(\kappa)(E(d_1)+E(d_2)) \to E(d_1+d_2)$$
where $\kappa$ denotes the isomorphism arising from $H$ preserving finite colimits. This natural 2-isomorphism together with the associators of $\mathbb{F}\textnormal{Cospan}(\bold{C})$ and $\mathbb{F^\prime} \textnormal{Cospan}(\bold{C^\prime})$, respectively $\alpha$ and $\alpha^\prime$, make the following diagram commute:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0.5) {$(\mathbb{H}(M_1) \otimes \mathbb{H}(M_2)) \otimes \mathbb{H}(M_3)$};
\node (B) at (0,-0.5) {$\mathbb{H}(M_1 \otimes M_2) \otimes \mathbb{H}(M_3)$};
\node (C) at (0,-1.5) {$\mathbb{H}((M_1 \otimes M_2) \otimes M_3)$};
\node (A') at (3,0.5) {$\mathbb{H}(M_1) \otimes (\mathbb{H}(M_2) \otimes \mathbb{H}(M_3))$};
\node (B') at (3,-0.5) {$\mathbb{H}(M_1) \otimes \mathbb{H}(M_2 \otimes M_3)$};
\node (C') at (3,-1.5) {$\mathbb{H}(M_1 \otimes (M_2 \otimes M_3))$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$\mu_{M_1,M_2} \otimes 1$} (B)
(B) edge node[left]{$\mu_{M_1 \otimes M_2,M_3}$} (C)
(A) edge node[above]{$\alpha^\prime$} (A')
(C) edge node [above] {$\mathbb{H}(\alpha)$} (C')
(B') edge node [right] {$\mathbb{H}_{M_1,M_2 \otimes M_3}$} (C')
(A') edge node [right]{$1 \otimes \mu_{M_2 \otimes M_3}$} (B');
\end{tikzpicture}
\]
with the corresponding diagram of decorations:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0.5) {$F^\prime(\alpha \kappa \kappa)((E(d_1)+E(d_2))+E(d_3))$};
\node (B) at (0,-0.5) {$F^\prime(\alpha \kappa)(E(d_1+d_2)+E(d_3))$};
\node (C) at (0,-1.5) {$F^\prime(\alpha)(E((d_1+d_2)+d_3))$};
\node (A') at (5,0.5) {$F^\prime(\kappa \kappa)(E(d_1)+(E(d_2)+E(d_3)))$};
\node (B') at (5,-0.5) {$F^\prime(\kappa)(E(d_1)+E(d_2+d_3))$};
\node (C') at (5,-1.5) {$E(d_1+(d_2+d_3))$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$F^\prime(\alpha \kappa)(\iota_\kappa + 1)$} (B)
(B) edge node[left]{$F^\prime(\alpha)(\iota_\kappa)$} (C)
(A) edge node[above]{$F^\prime(\kappa \kappa)(\iota_{\alpha^\prime})$} (A')
(C) edge node [above] {$\iota_\alpha$} (C')
(B') edge node [right] {$\iota_\kappa$} (C')
(A') edge node [right]{$F^\prime(\kappa)(1+\iota_\kappa)$} (B');
\end{tikzpicture}
\]
where $$F^\prime(\alpha \kappa \kappa)((E(d_1)+E(d_2))+E(d_3)) = F^\prime(\kappa \kappa \alpha^\prime)((E(d_1)+E(d_2))+E(d_3)).$$
We also have that the monoidal unit of $\mathbb{F}\textnormal{Cospan}(\bold{C})_1$ is given by:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$1_\bold{C}$};
\node (B) at (1,1) {$1_\bold{C}$};
\node (C) at (2,0) {$1_\bold{C}$};
\node (D) at (1,-0.5) {$!_{1_\bold{C}} \in F(1_\bold{C})$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$1$} (B)
(C) edge node[right]{$1$} (B);
\end{tikzpicture}
\]
where $1_\bold{C}$ is the monoidal unit of the finitely cocartesian category $\bold{C}$. The image of this horizontal 1-cell under $\mathbb{H}$ is given by:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$H(1_\bold{C})$};
\node (B) at (1,1) {$H(1_\bold{C})$};
\node (C) at (2,0) {$H(1_\bold{C})$};
\node (E) at (3,0.5) {$=$};
\node (F) at (4,0) {$1_\bold{C^\prime}$};
\node (G) at (5,1) {$1_\bold{C^\prime}$};
\node (H) at (6,0) {$1_\bold{C^\prime}$};
\node (I) at (5,-0.5) {$!_{1_{\bold{C^\prime}}} \in F^\prime(1_{\bold{C^\prime}})$};
\node (D) at (1,-0.5) {$E(!_{1_\bold{C}}) \in F^\prime(H(1_\bold{C}))$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$1$} (B)
(C) edge node[right]{$1$} (B)
(F) edge node[left]{$1$} (G)
(H) edge node[right]{$1$} (G);
\end{tikzpicture}
\]
since $H$ preserves finite colimits. We then have a 2-isomorphism in $\mathbb{F^\prime}\textnormal{Cospan}(\bold{C^\prime})$ given by: $$\mu \colon 1_{\mathbb{F^\prime}\textnormal{Cospan}(\bold{C^\prime})_1} \to \mathbb{H}(1_{\mathbb{F}\textnormal{Cospan}(\bold{C})_1})$$ 
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0.5) {$1_{\bold{C^\prime}}$};
\node (A') at (0,-0.5) {$H(1_\bold{C})$};
\node (B) at (1.5,0.5) {$1_{\bold{C^\prime}}$};
\node (C) at (3,0.5) {$1_{\bold{C^\prime}}$};
\node (C') at (3,-0.5) {$H(1_\bold{C})$};
\node (D) at (1.5,-0.5) {$H(1_\bold{C})$};
\node (E) at (4.5,0.5) {$!_{1_\bold{C^\prime}} \in F^\prime(1_\bold{C^\prime})$};
\node (F) at (4.5,-0.5) {$E(!_{1_\bold{C}}) \in F^\prime(H(1_\bold{C}))$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$1$} (B)
(C) edge node[above]{$1$} (B)
(A) edge node[left]{$\kappa$} (A')
(C) edge node[left]{$\kappa$} (C')
(A') edge node [above]{$1$} (D)
(C') edge node [above]{$1$} (D)
(B) edge node [left] {$\kappa$} (D);
\end{tikzpicture}
\]
together with the morphism $\iota_\mu \colon F^\prime(\kappa)(!_{1_\bold{C^\prime}}) \to E(!_{1_\bold{C}})$ in $F^\prime(H(1_\bold{C}))$. The following square then commutes: 
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$1_\bold{C^\prime} \otimes \mathbb{H}(M)$};
\node (B) at (2.5,0) {$\mathbb{H}(1_\bold{C}) \otimes \mathbb{H}(M)$};
\node (C) at (0,-1) {$\mathbb{H}(M)$};
\node (D) at (2.5,-1) {$\mathbb{H}(1_\bold{C} + M)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$\mu \otimes 1$} (B)
(A) edge node[left]{$\ell$} (C)
(B) edge node[right]{$\mu_{1_\bold{C},M}$} (D)
(D) edge node[above]{$\mathbb{H}(\ell^\prime)$} (C);
\end{tikzpicture}
\]
where we have abbreviated the monoidal units of $\mathbb{F}\textnormal{Cospan}(\bold{C})_1$ and $\mathbb{F^\prime}\textnormal{Cospan}(\bold{C^\prime})_1$ as $1_\bold{C}$ and $1_\bold{C^\prime}$, respectively. The diagram of corresponding decorations is given by:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0.5) {$F^\prime(\ell)(!_{1_\bold{C^\prime}} + E(d))$};
\node (B) at (0,-0.5) {$E(d)$};
\node (A') at (4,0.5) {$F^\prime(H(\ell^\prime) \kappa)(E(!_{1_\bold{C}})+E(d))$};
\node (B') at (4,-0.5) {$F^\prime(H(\ell^\prime))(E(!_{1_\bold{C}} + d))$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$\iota_\ell$} (B)
(A) edge node[above]{$F^\prime(H(\ell^\prime)\kappa)(\iota_{\mu+1})$} (A')
(A') edge node [right]{$F^\prime(H(\ell^\prime))(\iota_\kappa)$} (B')
(B') edge node [above] {$\iota_{H(\ell^\prime)}$} (B);
\end{tikzpicture}
\]
where $$F^\prime(\ell)(!_{1_\bold{C^\prime}} + E(d))=F^\prime(H(\ell^\prime)\kappa(\mu+1))(!_{1_\bold{C^\prime}} + E(d)).$$ The other square involving the right unitors $r$ and $r^\prime$ is similar. Note that because $\mu$ and $\mu_{(\_ , \_)}$ are both isomorphisms, the symmetric monoidal double functor $\mathbb{H}$ is strong.

%\newpage
%Scratch work for Petri net problem
%\newline
%Let $P = (s_1,t_1 \colon T_1 \to \mathbb{N}(S_1))$ and $Q = (s_2,t_2 \colon T_2 \to \mathbb{N}(S_2))$. We want to show that the functor $F \colon \textrm{Petri} \to \textrm{CMC}$ preserves pushouts of cospans of the form $$P \xleftarrow{} L(Y) \xrightarrow{} Q$$ meaning that $F(P+_{L(Y)} Q) \cong F(P) +_{F(L(Y))} F(Q)$. Here, $L \colon \textrm{Set} \to \textrm{Petri}$ is the left adjoint which sends a set $Y$ to the discrete Petri net with $Y$ as its set of species and no transitions. Thus no transitions are identified in the pushout $P+_{L(Y)} Q$, and so the set of transitions of $P+_{L(Y)} Q$ is given by $$\textrm{Trans}(P)+\textrm{Trans}(Q).$$ Thus the morphisms \emph{contributed from transitions} in both $F(P+_{L(Y)}Q)$ and $F(P)+_{F(L(Y)} F(Q)$ are the same. If we can show that $$\textrm{Ob}(F(P+_{L(Y)}Q) \cong \textrm{Ob}(F(P)+_{F(L(Y))} F(Q)$$ then the remaining morphisms in each commutative monoidal category will be canonically isomorphic as sets.

%Now, what can we say about $\textrm{Ob}(F(P+_{L(Y)}Q))$ vs. $\textrm{Ob}(F(P)+_{F(L(Y))} F(Q))$? Well, $\textrm{Ob}(F(P+_{L(Y)}Q)) = \mathbb{N}(S_1+_Y S_2)$ and $\textrm{Ob}(F(P)+_{F(L(Y))} F(Q))= \mathbb{N}(S_1) +_{\mathbb{N}(Y)} \mathbb{N}(S_2)$.

%\newpage

\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0.5) {$\bold{1}$};
\node (A') at (0,-0.5) {$F^\prime(1_\bold{C^\prime})$};
\node (B) at (1.5,0.5) {$F(1_\bold{C})$};
\node (C) at (3.5,0.5) {$F(c)$};
\node (C') at (3.5,-0.5) {$F^\prime(H(c))=E(F(c))$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$\phi$} (B)
(B) edge node[above]{$F(!_c)$} (C)
(A) edge node[left]{$\Phi$} (A')
(C) edge node [left] {$$} (C')
(A') edge node [above]{$F^\prime(!_{H(c)})$} (C');
\end{tikzpicture}
\]
\newline
\textbf{show symmetric monoidal, make sure using all assumptions on the functors H and E}

%is given by $$\bold{1} \to F(c_1) \times F(c_2) \xrightarrow{} F(c_1 + c_2) \xrightarrow{} F(c_1 + _b c_2)$$ and then applying the functor $E$ results in $\bold{1} \to E(F(c_1+_b c_2))$, which by the comutative square is the same as $\bold{1} \to F^\prime(H(c_1+_b c_2))$. On the other hand, applying the functor $E$ to each decoration results in $$\bold{1} \to E(F(c_1)) \times E(F(c_2)) \xrightarrow{} E(F(c_1) \times F(c_2)) \xrightarrow{} E(F(c_1+c_2)) \xrightarrow E(F(c_1+_b c_2)) \xrightarrow{} F^\prime(H(c_1 +_b c_2))$$

\section{From pseudofunctors to left adjoints}
In this section we investigate the necessary conditions to obtain a category $\bold{D}$ and a left adjoint $L \colon \bold{C} \to \bold{D}$ from a category $\bold{C}$ with finite colimits and a symmetric lax monoidal pseudofunctor $F \colon \bold{C} \to \bold{Cat}$. The main tool that allows us to do this will be the Grothendieck construction which we recall:

\begin{defn}
Let $\bold{Cat}_{\textnormal{lax},\star}$ denote the \define{2-category of lax-pointed categories} which has:
\begin{enumerate}
\item{objects as pairs $(\bold{C},c)$ where $\bold{C}$ is a category and $c$ is an object of $\bold{C}$, and}
\item{a morphism from $(\bold{C},c)$ to $(\bold{D},d)$ is a pair $(F,f)$ where $F \colon \bold{C} \to \bold{D}$ is a functor and $f \colon F(c) \to d$ is a morphism in $\bold{D}$.}
\end{enumerate}
\end{defn}

\begin{defn}
Given a pseudofunctor $F \colon \bold{C} \to \bold{Cat}$, the \define{Grothendieck construction of} $F$ is given by the `strict 2-pullback' of the following cospan:
 \[
\begin{tikzpicture}[scale=1.5]
\node (D) at (1,1) {$\int F$};
\node (A) at (0,0) {$\bold{C}$};
\node (B) at (1,-1) {$\bold{Cat}$};
\node (C) at (2,0) {$\bold{Cat}_{\textnormal{lax},\star}$};
\path[->,font=\scriptsize,>=angle 90]
(D) edge[dashed] node[above]{$p$} (A)
(D) edge[dashed] node[above]{$q$} (C)
(A) edge node[below]{$F$} (B)
(C) edge node[below]{$P$} (B);
\end{tikzpicture}
\]
where $P \colon \bold{Cat}_{\textnormal{lax},\star} \to \bold{Cat}$ is the forgetful functor. This means that $\int F$ is a category which has:
\begin{enumerate}
\item{objects as pairs $(c, d \in F(c))$ and}
\item{a morphism from $(c, d \in F(c))$ to $(c^\prime, d^\prime \in F(c^\prime))$ is a pair $(f \colon c \to c^\prime,\alpha \colon F(f)(d) \to d^\prime)$.

This can also be thought of as a morphism and a 2-morphism:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$\star$};
\node (B) at (1,0.5) {$F(c)$};
\node (C) at (1,-0.5) {$F(c^\prime)$};
\node (D) at (2,0.5) {$c$};
\node (E) at (2,-0.5) {$c^\prime$};
\node (F) at (0.65,0) {$\Swarrow \alpha$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$d$} (B)
(B) edge node[right]{$F(f)$} (C)
(A) edge node[below]{$d^\prime$} (C)
(D) edge node[left] {$f$} (E);
\end{tikzpicture}
\]
}
\end{enumerate}
\end{defn}

\begin{defn}
Given bicategories $\bold{C}$ and $\bold{D}$ and 2-functors (possibly lax or oplax) $(F,\phi),(G,\psi) \colon \bold{C} \to \bold{D}$, a \define{pseudonatural transformation} $\sigma \colon (F,\phi) \to (G,\psi)$ consists of:
\begin{enumerate}
\item{for each object $a \in \bold{C}$, a morphism $\sigma_a \colon F(a) \to G(a)$ in $\bold{D}$ and}
\item{for every pair of objects $a$ and $b$ of $\bold{C}$, we have natural isomorphisms:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$\bold{C}(a,b)$};
\node (B) at (2,0) {$\bold{D}(F(a),F(b))$};
\node (C) at (0,-1) {$\bold{D}(G(a),G(b))$};
\node (D) at (2,-1) {$\bold{D}(F(a),G(b))$};
\node (E) at (1,-0.5) {$\sigma_{a,b} \Nearrow$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$F$} (B)
(B) edge node[right]{$(\sigma_{b})_*$} (D)
(A) edge node[left]{$G$} (C)
(C) edge node[above]{$(\sigma_a)^*$} (D);
\end{tikzpicture}
\]
where $(\sigma_a)^*$ and $(\sigma_b)_*$ are the functors induced by precomposition and postcompositon, respectively. Thus for each morphism $f \colon a \to b$ in $\bold{C}$, we have an invertible 2-morphism $\sigma_f \colon G(f) \sigma_a \xrightarrow{\sim} \sigma_{b} F(f)$ in $\bold{D}$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$F(a)$};
\node (B) at (1,0) {$F(b)$};
\node (C) at (0,-1) {$G(a)$};
\node (D) at (1,-1) {$G(b)$};
\node (E) at (0.5,-0.5) {$\sigma_f \Nearrow$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$F(f)$} (B)
(B) edge node[right]{$\sigma_{b}$} (D)
(A) edge node[left]{$\sigma_a$} (C)
(C) edge node[above]{$G(f)$} (D);
\end{tikzpicture}
\]}
\end{enumerate}
such that for each composable pair of morphisms $f \colon a \to b$ and $g \colon b \to c$ of $\bold{C}$, the following diagrams commute:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0.5) {$(G(g)G(f))\sigma_a$};
\node (A') at (2,0.5) {$G(g)(G(f) \sigma_a)$};
\node (B) at (0,-0.5) {$G(gf) \sigma_a$};
\node (C) at (4,0.5) {$G(g) (\sigma_b F(f))$};
\node (C') at (4,-0.5) {$\sigma_c F(gf)$};
\node (D) at (6,0.5) {$(G(g) \sigma_b) F(f)$};
\node (D') at (8,-0.5) {$\sigma_c (F(g)F(f))$};
\node (F) at (8,0.5) {$(\sigma_c F(g)) F(f)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$a^\prime$} (A')
(A) edge node[left]{$\psi 1_{\sigma_a}$} (B)
(A') edge node[above]{$1_{G(g)} \sigma_f$} (C)
(B) edge node[above]{$\sigma_{gf}$} (C')
(C) edge node [above] {${a^\prime}^{-1}$} (D)
(D') edge node [above] {$1_{\sigma_c} \phi$} (C')
(D) edge node [above] {$\sigma_g 1_{F(f)}$} (F)
(F) edge node [right] {$a^\prime$} (D');
\end{tikzpicture}
\]
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$1_{G(a)} \sigma_a$};
\node (B) at (1,1) {$G(1_a) \sigma_a$};
\node (C) at (2,0) {$\sigma_a F(1_a)$};
\node (D) at (0.5,-1) {$\sigma_a$};
\node (E) at (1.5,-1) {$\sigma_a 1_{F(a)}$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$\psi 1_{\sigma_a}$} (B)
(B) edge node[right]{$\sigma_{1_a}$} (C)
(A) edge node [left] {$\ell^\prime$} (D)
(D) edge node [above] {${\rho^\prime}^{-1}$} (E)
(E) edge node [right] {$1_{\sigma_a} \phi$} (C);
\end{tikzpicture}
\]
\end{defn}

Let $[\bold{C},\bold{Cat}]_{\textnormal{pseudo}}$ denote the 2-category which has:
\begin{enumerate}
\item{objects as pseudofunctors $(F,\phi) \colon \bold{C} \to \bold{Cat}$,}
\item{a morphism from a pseudofunctor $(F,\phi) \colon \bold{C} \to \bold{Cat}$ to another $(G,\psi) \colon \bold{C} \to \bold{Cat}$ is a pseudonatural transformation $\sigma \colon (F,\phi) \to (G,\psi)$, and}
\item{2-morphisms are modifications.}
\end{enumerate}

%\begin{defn}
%Let $P \colon \bold{D} \to \bold{C}$ be a functor. A morphism $f \colon d_{1} \to d_{2}$ in the category $\bold{D}$ is \textbf{cartesian (with respect to the functor P)} if for any object $d^\prime$ in $\bold{D}$ and morphism $g \colon d^\prime \to d_{2}$ and every $p \colon P(d^\prime) \to P(d_{1})$ such that $P(g)=P(f)p$, there exists a unique $h \colon d^\prime \to d_{1}$ such that $g=fh$ and $p=P(h)$.
%\[
%\begin{tikzpicture}[scale=1.5]
%\node (A) at (0,0) {$d^\prime$};
%\node (B) at (0,-1.5) {$d_{1}$};
%\node (C) at (1.5,-1.5) {$d_{2}$};
%\node (H) at (2,-0.5) {$P$};
%\node (D) at (2,-.75) {$\mapsto$};
%\node (E) at (3,0) {$P(d^\prime)$};
%\node (F) at (3,-1.5) {$P(d_{1})$};
%\node (G) at (4.5,-1.5) {$P(d_{2})$};
%\path[->,font=\scriptsize,>=angle 90]
%(A) edge[dashed] node[above,left]{$\exists ! h$} (B)
%(A) edge node[above]{$g$} (C)
%(E) edge node[above,left]{$p=P(h)$} (F)
%(F) edge node[above]{$P(f)$} (G)
%(E) edge node[above,right]{$P(g)$} (G)
%(B)edge node[above]{$f$}(C);
%\end{tikzpicture}
%\]
%\end{defn}
\begin{defn}
Let $P \colon \bold{D} \to \bold{C}$ be a functor. A morphism $f \colon d_{1} \to d_{2}$ in the category $\bold{D}$ is \textbf{cocartesian (with respect to the functor P)} if for any object $d^\prime$ in $\bold{D}$ and morphism $g \colon d_{1} \to d^\prime$ and every $p \colon P(d_{2}) \to P(d^\prime)$ such that $P(g)=p P(f)$, there exists a unique $h \colon d_{2} \to d^\prime$ such that $g=hf$ and $p=P(h)$.
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$d^\prime$};
\node (B) at (0,-1.5) {$d_{2}$};
\node (C) at (1.5,-1.5) {$d_{1}$};
\node (H) at (2,-0.5) {$P$};
\node (D) at (2,-.75) {$\mapsto$};
\node (E) at (3,0) {$P(d^\prime)$};
\node (F) at (3,-1.5) {$P(d_{2})$};
\node (G) at (4.5,-1.5) {$P(d_{1})$};
\path[->,font=\scriptsize,>=angle 90]
(B) edge[dashed] node[above,left]{$\exists ! h$} (A)
(C) edge node[above,right]{$g$} (A)
(F) edge node[above,left]{$p=P(h)$} (E)
(G) edge node[above]{$P(f)$} (F)
(G) edge node[above,right]{$P(g)$} (E)
(C)edge node[above]{$f$}(B);
\end{tikzpicture}
\]
\end{defn}
\begin{defn}
A functor $P \colon \bold{D} \to \bold{C}$ is a \textbf{(Grothendieck) opfibration} if for any object $d$ in $\bold{D}$ and morphism $f \colon c \to P(d)$ there exists a cocartesian morphism $\phi \colon d^\prime \to d$ such that $P(\phi)=f$.
\end{defn}

\begin{defn}
Let $P \colon \bold{D} \to \bold{C}$ and $P^\prime \colon \bold{D^\prime} \to \bold{C}$ be opfibrations over a category $\bold{C}$. A \define{morphism of opfibrations} is a functor $F \colon \bold{D} \to \bold{D}^\prime$ such that $F(p)$ is cocartesian with respect to $P^\prime$ if $p$ is cocartesian with respect to $P$ and $P=P^\prime F$.
\end{defn}

Let Opfib$(\bold{C})$ denote the 2-category of opfibrations over $\bold{C}$ which has:
\begin{enumerate}
\item{objects as opfibrations $P \colon \bold{D} \to \bold{C}$,}
\item{morphisms as morphisms of opfibrations, and}
\item{a 2-morphism from one morphism of opfibrations $F \colon P \to P^\prime$ to another $F^\prime \colon P \to P^\prime$ is a natural transformation $\alpha \colon F \to F^\prime$ such that the left whiskering $P^\prime \alpha$ is trivial.}
\end{enumerate}

The 2-category Opfib$(\bold{C})$ is a 2-subcategory of $\bold{Cat}/ \bold{C}$ where $\bold{Cat} / \bold{C}$ is the 2-category of functors over $\bold{C}$. The Grothendieck construction is a 2-functor $\int F \colon [ \bold{C},\bold{Cat}] \to \bold{Cat}/ \bold{C}$ which factors through the image of the embedding $\textnormal{Opfib}(\bold{C}) \hookrightarrow \bold{Cat} / \bold{C}$: $$\int F \colon [ \bold{C}, \bold{Cat} ] \to \textnormal{Opfib}(\bold{C}) \hookrightarrow \bold{Cat} / \bold{C}.$$

Under certain conditions, the functor resulting from the Grothendieck construction $p \colon \int{F} \to \bold{C}$ will be right adjoint to the desired left adjoint $L \colon \bold{C} \to \bold{D}$.

\section{An equivalence of symmetric monoidal double categories}
In this section we prove that two different frameworks which utilize symmetric monoidal double categories, namely decorated cospans and `structured cospans', are equivalent under the conditions required from the previous section that allow for a left adjoint $L \colon \bold{C} \to \bold{D}$ to be obtained from a symmetric lax monoidal pseudofunctor $F \colon \bold{C} \to \bold{Cat}$. The double category version of decorataed cospans is given in Section \ref{DecCospansDoublecat}. The other framework which also utilizes symmetric monoidal double categories, due to Baez and the first author and goes by the name of `structured cospans', is explained below. Once again following the notation of Shulman \cite{Shul2}, given a double category $\mathbb{C}$, we write $_f \mathbb{C}_g(M,N)$ for the set of 2-morphisms in $\mathbb{C}$ of the form:
\[
  \xymatrix@-.5pc{
    A \ar[r]|{|}^{M}  \ar[d]_f \ar@{}[dr]|{\Downarrow a}&
    B\ar[d]^g\\
    C \ar[r]|{|}_N & D
  }
\]
We call $M$ and $N$ the \define{horizontal source and target} of the 2-morphism $a$, respectively, and likewise we call $f$ and $g$ the \define{vertical source and target} of the 2-morphism $a$, respectively. Thus $_f \mathbb{C}_g(M,N)$ denotes the set of 2-morphisms in $\mathbb{C}$ with horizontal source and target $M$ and $N$ and vertical source and target $f$ and $g$.
\begin{defn}
A (possibly lax or oplax) double functor $\mathbb{F} \colon \mathbb{C} \to \mathbb{D}$ is \define{full} (respectively, \define{faithful}) if $\mathbb{F}_0 \colon \mathbb{C}_0 \to \mathbb{D}_0$ is full (respectively, faithful) and each map $$\mathbb{F}_1 \colon _f \mathbb{C}_g(M,N) \to _{\mathbb{F}(f)} \mathbb{D}_{\mathbb{F}(g)}(\mathbb{F}(M),\mathbb{F}(N))$$ is surjective (respectively, injective).
\end{defn}
\begin{defn}
A (possibly lax or oplax) double functor $\mathbb{F} \colon \mathbb{C} \to \mathbb{D}$ is \define{essentially surjective} if we can simultaneously make the following choices:
\begin{enumerate}
\item{For each object $d \in \mathbb{D}$, we can find an object $\hat{d} \in \mathbb{C}$ together with a vertical 1-isomorphism $\alpha_d \colon \mathbb{F}(\hat{d}) \to d$, and}
\item{For each horizontal 1-cell $N \colon d_1 \tobar d_2$  of $\mathbb{D}$, we can find a horizontal 1-cell $\hat{N} \colon \hat{d_1} \tobar \hat{d_2}$ of $\mathbb{C}$ and a 2-isomorphism $a_{N}$ of $\mathbb{D}$ as in the following diagram:
\[
  \xymatrix@-.5pc{
    \mathbb{F}(\hat{d_1}) \ar[r]|{|}^{\mathbb{F}(\hat{N})}  \ar[d]_{\alpha_{d_1}} \ar@{}[dr]|{\Downarrow a_N}&
    \mathbb{F}(\hat{d_2}) \ar[d]^{\alpha_{d_2}}\\
    d_1 \ar[r]|{|}_N & d_2
  }
\]
}
\end{enumerate}
\end{defn}
\begin{defn}
A double functor $\mathbb{F} \colon \mathbb{C} \to \mathbb{D}$ is \define{strong} if the comparison and unit constraints are globular isomorphisms, meaning that for each composable pair of horizontal 1-cells $M$ and $N$ we have a natural isomorphism $$\mathbb{F}_{M,N} \colon \mathbb{F}(M) \odot \mathbb{F}(N) \xrightarrow{\sim} \mathbb{F}(M \odot N)$$and for each object $c \in \mathbb{C}$ a natural isomorphism $$\mathbb{F}_c \colon \hat{U}_{\mathbb{F}(c)} \xrightarrow{\sim} \mathbb{F}(U_c).$$
\end{defn}
\begin{thm}[Shulman,7.8]\label{ShulDubEquiv}
Given a strong double functor $\mathbb{F} \colon \mathbb{C} \to \mathbb{D}$, $\mathbb{F}$ is part of a double equivalence if and only if $\mathbb{F}$ is full, faithful and essentially surjective.
\end{thm}
\begin{thm}
Let $\mathbb{C}$ and $\mathbb{D}$ be symmetric monoidal double categories and let $\mathbb{F} \colon \mathbb{C} \to \mathbb{D}$ be a symmetric monoidal strong double functor. If $\mathbb{F}$ is part of a double equivalence, then $\mathbb{F}$ is in fact part of a symmetric monoidal double equivalence, and $\mathbb{C}$ and $\mathbb{D}$ are equivalent as symmetric monoidal double categories.
\end{thm}
\begin{proof}
\textbf{Prove this...is there anything to even prove?}
\end{proof}
Our next goal is to show that the symmetric monoidal double category $\mathbb{F}\textnormal{Cospan}(\bold{C})$ of Section \ref{DecCospansDoublecat} is equivalent as a symmetric monoidal double category to the symmetric monoidal double category $_L \mathbb{C}\textnormal{sp}(\bold{D})$ obtained using structured cospans.

\begin{thm}
Given a category $\bold{D}$ with finite colimits and a category $\bold{C}$ with finite coproducts and a left adjoint $L \colon \bold{C} \to \bold{D}$ with $\bold{C}$ and $\bold{D}$ regarded as symmetric monoidal categories under binary coproducts, we can obtain a symmetric monoidal double category $_L \mathbb{C}\textnormal{sp}(\bold{D})$ which has:
\begin{enumerate}
\item{objects given by objects of $\bold{C}$,}
\item{vertical 1-morphisms given by morphisms of $\bold{C}$,}
\item{horizontal 1-cells given by cospans of $\bold{D}$ of the form:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$L(c)$};
\node (B) at (1,1) {$d$};
\node (C) at (2,0) {$L(c^\prime)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$$} (B)
(C) edge node[above]{$$} (B);
\end{tikzpicture}
\]
and}
\item{2-morphisms given by maps of cospans of $\bold{D}$ of the form:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$L(c_1)$};
\node (B) at (1,0) {$d$};
\node (C) at (2,0) {$L(c_2)$};
\node (A') at (0,-1) {$L(c_1^\prime)$};
\node (B') at (1,-1) {$d^\prime$};
\node (C') at (2,-1) {$L(c_2^\prime)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$$} (B)
(C) edge node[above]{$$} (B)
(A') edge node[above]{$$} (B')
(C') edge node[above]{$$} (B')
(A) edge node [left]{$L(f)$} (A')
(B) edge node [left]{$h$} (B')
(C) edge node [left]{$L(g)$} (C');
\end{tikzpicture}
\]
Composition of horizontal 1-cells and 2-morphisms is given by pushouts in $\bold{D}$ and tensoring of objects is under binary coproducts in $\bold{C}$.
}
\end{enumerate}
\end{thm}
\begin{proof}
See \cite{BC2}.
\end{proof}
In the previous section, we started with a symmetric lax monoidal pseudofunctor $F \colon \bold{C} \to \bold{Cat}$ and created a symmetric monoidal double category $\mathbb{F}\textnormal{Cospan}(\bold{C})$ which has:
\begin{enumerate}
\item{objects of $\bold{C}$ as objects,}
\item{morphisms of $\bold{C}$ as vertical 1-morphisms,}
\item{horizontal 1-cells are given by $F$-decorated cospans, which are pairs:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$c_1$};
\node (B) at (1,1) {$c$};
\node (C) at (2,0) {$c_2$};
\node (D) at (3,0.5) {$d \in F(c)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B);
\end{tikzpicture}
\]
and}
\item{2-morphisms are given by maps of cospans in $\bold{C}$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$c_1$};
\node (B) at (1,0) {$c$};
\node (C) at (2,0) {$c_2$};
\node (A') at (0,-1) {$c_1^\prime$};
\node (B') at (1,-1) {$c^\prime$};
\node (C') at (2,-1) {$c_2^\prime$};
\node (D) at (3,0) {$d \in F(c)$};
\node (D') at (3,-1) {$d^\prime \in F(c^\prime)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B)
(A') edge node[above]{$i^\prime$} (B')
(C') edge node[above]{$o^\prime$} (B')
(A) edge node [left]{$f$} (A')
(B) edge node [left]{$h$} (B')
(C) edge node [left]{$g$} (C');
\end{tikzpicture}
\]
together with a morphism $\iota \colon F(h)(d) \to d^\prime$ in $F(c^\prime)$.}
\end{enumerate}
We now show that these two symmetric monoidal double categories are equivalent. 
\begin{thm}\label{main2}
Let $\bold{C}$ and $\bold{D}$ be categories with finite colimits and $F \colon \bold{C} \to \bold{Cat}$ a symmetric lax monoidal pseudofunctor. Let $L \colon \bold{C} \to \int{F} \cong \bold{D}$ be the left adjoint of the Grothendieck construction $R \colon \int{F} \to \bold{C}$ of $F$. Then the symmetric monoidal double category $_L \mathbb{C}\textnormal{sp}(\bold{D})$ utilizing structured cospans and the symmetric monoidal double category $\mathbb{F}\textnormal{Cospan}(\bold{C})$ utilizing decorated cospans are equivalent as symmetric monoidal double categories.
\end{thm}
\begin{proof}
To prove this, we define a double functor $\mathbb{E} \colon _L \mathbb{C}\textnormal{sp}(\bold{D}) \to \mathbb{F}\textnormal{Cospan}(\bold{C})$ as follows: the object component of the double functor $\mathbb{E}$ is given by $\mathbb{E}_0 = \id_{\bold{C}}$ as both double categories $_L \mathbb{C}\textnormal{sp}(\bold{D})$ and $\mathbb{F}\textnormal{Cospan}(\bold{C})$ have objects and morphisms of $\bold{C}$ as objects and vertical 1-morphisms, respectively. The functor $\mathbb{E}_0$ is trivially an equivalence of categories.

Given a horizontal 1-cell of $_L \mathbb{C}\textnormal{sp}(\bold{D})$, which is a cospan in $\bold{D}$ of the form:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$L(c)$};
\node (B) at (1,1) {$d$};
\node (C) at (2,0) {$L(c^\prime)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$i$} (B)
(C) edge node[right]{$o$} (B);
\end{tikzpicture}
\]
the image of this horizontal 1-cell under the arrow component $\mathbb{E}_1$ is the pair:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$c$};
\node (B) at (1,1) {$R(d)$};
\node (C) at (2,0) {$c^\prime$};
\node (D) at (3,0.5) {$d \in F(R(d))$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$R(i) {\eta_c}$} (B)
(C) edge node[right]{$R(o) {\eta_{c^\prime}}$} (B);
\end{tikzpicture}
\]
where $R\colon \bold{D} \to \bold{C}$ is the right adjoint to the functor $L \colon \bold{C} \to \bold{D}$ and $\eta \colon 1_{\bold{C}} \to RL$ is the unit of the adjunction $L \dashv R$ which is an isomorphism since $L$ is fully faithful. \textbf{Hopefully...} Similarly, the image of a 2-morphism in $_L \mathbb{C}\textnormal{sp}(\bold{D})$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$L(c_1)$};
\node (B) at (1,0) {$d$};
\node (C) at (2,0) {$L(c_2)$};
\node (A') at (0,-1) {$L(c_1^\prime)$};
\node (B') at (1,-1) {$d^\prime$};
\node (C') at (2,-1) {$L(c_2^\prime)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B)
(A') edge node[above]{$i^\prime$} (B')
(C') edge node[above]{$o^\prime$} (B')
(A) edge node [left]{$L(f)$} (A')
(B) edge node [left]{$h$} (B')
(C) edge node [left]{$L(g)$} (C');
\end{tikzpicture}
\]
is the 2-morphism in $\mathbb{F}\textnormal{Cospan}(\bold{C})$ given by:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$c_1$};
\node (B) at (1,0) {$R(d)$};
\node (C) at (2,0) {$c_2$};
\node (A') at (0,-1) {$c_1^\prime$};
\node (B') at (1,-1) {$R(d^\prime)$};
\node (C') at (2,-1) {$c_2^\prime$};
\node (D) at (3,0) {$d \in F(R(d))$};
\node (D') at (3,-1) {$d^\prime \in F(R(d^\prime))$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$R(i) \eta_{c_1}$} (B)
(C) edge node[above]{$R(o) \eta_{c_2}$} (B)
(A') edge node[above]{$R(i^\prime) \eta_{c_1^\prime}$} (B')
(C') edge node[above]{$R(o^\prime) \eta_{c_2^\prime}$} (B')
(A) edge node [left]{$f$} (A')
(B) edge node [left]{$R(h)$} (B')
(C) edge node [left]{$g$} (C');
\end{tikzpicture}
\]
together with a morphism $\iota \colon F(R(h))(d) \to d^\prime$ in $F(R(d^\prime)) \subseteq \bold{D}$ which comes from the Grothendieck construction of the pseudofunctor $F \colon \bold{C} \to \bold{Cat}$. First, to see that this functor is essentially surjective, given a horizontal 1-cell in $\mathbb{F}\textnormal{Cospan}(\bold{C})$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$c_1$};
\node (B) at (1,1) {$c$};
\node (C) at (2,0) {$c_2$};
\node (D) at (3,0.5) {$d \in F(c)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$i$} (B)
(C) edge node[right]{$o$} (B);
\end{tikzpicture}
\]
we can find a 2-isomorphism in $\mathbb{F}\textnormal{Cospan}(\bold{C})$ whose codomain is the above horizontal 1-cell and whose domain is the image of the following horizontal 1-cell in $_L \mathbb{C}\textnormal{sp}(\bold{D})$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$L(c_1)$};
\node (B) at (1,1) {$d$};
\node (C) at (2,0) {$L(c_2)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$i^\prime$} (B)
(C) edge node[right]{$o^\prime$} (B);
\end{tikzpicture}
\]
with the 2-isomorphism in $\mathbb{F}\textnormal{Cospan}(\bold{C})$ given by:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$c_1$};
\node (B) at (1,0) {$R(d)$};
\node (C) at (2,0) {$c_2$};
\node (A') at (0,-1) {$c_1$};
\node (B') at (1,-1) {$c$};
\node (C') at (2,-1) {$c_2$};
\node (D) at (3,0) {$d \in F(R(d))$};
\node (D') at (3,-1) {$d \in F(c)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$R(i^\prime) \eta_{c_1}$} (B)
(C) edge node[above]{$R(o^\prime) \eta_{c_2}$} (B)
(A') edge node[above]{$i$} (B')
(C') edge node[above]{$o$} (B')
(A) edge node [left]{$1$} (A')
(B) edge node [left]{${(R(e) \eta_c)}^{-1}$} (B')
(C) edge node [left]{$1$} (C');
\end{tikzpicture}
\]
$$\iota \colon F({(R(e)\eta_c)}^{-1})(d) \to d$$
where $e \colon L(c) \to d$ is given by the map from the trivial decoration on $c$ to $d \in F(c)$. The object and arrow components $\mathbb{E}_0$ and $\mathbb{E}_1$ satisfy the equations $S \mathbb{E}_1 = \mathbb{E}_0 S$ and $T \mathbb{E}_1 = \mathbb{E}_0 T$.

To show that the double functor $\mathbb{E}$ is fully faithful, we need to show that the map  $$\mathbb{E}_1 \colon _f { _L \mathbb{C}\textnormal{sp}(\bold{D})}_g(M,N) \to _{\mathbb{E}(f)} {\mathbb{F}\textnormal{Cospan}(\bold{C})}_{\mathbb{E}(g)}(\mathbb{E}(M),\mathbb{E}(N))$$ is bijective for arbitrary vertical 1-morphisms $f$ and $g$ and horizontal 1-cells $M$ and $N$ of $_L \mathbb{C}\textnormal{sp}(\bold{D})$. Consider a 2-morphism in $_L \mathbb{C}\textnormal{sp}(\bold{D})$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$L(c_1)$};
\node (B) at (1,0) {$d$};
\node (C) at (2,0) {$L(c_2)$};
\node (A') at (0,-1) {$L(c_1^\prime)$};
\node (B') at (1,-1) {$d^\prime$};
\node (C') at (2,-1) {$L(c_2^\prime)$};
\node (D) at (1,0.5) {$M$};
\node (E) at (-1,-0.5) {$f$};
\node (F) at (1,-1.5) {$N$};
\node (G) at (3,-0.5) {$g$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B)
(A') edge node[above]{$i^\prime$} (B')
(C') edge node[above]{$o^\prime$} (B')
(A) edge node [left]{$L(f)$} (A')
(B) edge node [left]{$\alpha$} (B')
(C) edge node [left]{$L(g)$} (C');
\end{tikzpicture}
\]
The set $$_f { _L \mathbb{C}\textnormal{sp}(\bold{D})}_g(M,N)$$ consists of triples $$(f,\alpha,g)$$ where $f$ and $g$ are morphisms of $\bold{C}$ and $\alpha$ is a morphism of $\bold{D}$. The image of the above 2-morphism under the double functor $\mathbb{E}$ is given by:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$c_1$};
\node (B) at (1,0) {$R(d)$};
\node (C) at (2,0) {$c_2$};
\node (A') at (0,-1) {$c_1^\prime$};
\node (B') at (1,-1) {$R(d^\prime)$};
\node (C') at (2,-1) {$c_2^\prime$};
\node (D) at (1,0.5) {$d \in F(R(d))$};
\node (D') at (1,-1.5) {$d^\prime \in F(R(d^\prime))$};
\node (E) at (1,1) {$\mathbb{E}(M)$};
\node (F) at (-1,-0.5) {$\mathbb{E}(f)$};
\node (G) at (1,-2) {$\mathbb{E}(N)$};
\node (H) at (3,-0.5) {$\mathbb{E}(g)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$R(i)\eta_{c_1}$} (B)
(C) edge node[above]{$R(o)\eta_{c_2}$} (B)
(A') edge node[above]{$R(i^\prime)\eta_{c_1^\prime}$} (B')
(C') edge node[above]{$R(o^\prime)\eta_{c_2^\prime}$} (B')
(A) edge node [left]{$f$} (A')
(B) edge node [left]{$R(\alpha)$} (B')
(C) edge node [left]{$g$} (C');
\end{tikzpicture}
\]
together with a morphism $\iota \colon F(R(\alpha))(d) \to d^\prime$ of $F(R(d^\prime))$.
Thus the set $$_{\mathbb{E}(f)} {\mathbb{F}\textnormal{Cospan}(\bold{C})}_{\mathbb{E}(g)}(\mathbb{E}(M),\mathbb{E}(N))$$ consists of 4-tuples $$(f,R(\alpha),g,\iota).$$ The morphisms $R(\alpha) \colon R(d) \to R(d^\prime)$ and $\iota \colon F(R(\alpha))(d) \to d^\prime$ together carry all of the information of the morphism $\alpha \colon d \to d^\prime$ in $\bold{D}$ and conversely; given two objects $d=(c,d \in F(c))$ and $d^\prime=(c^\prime,d^\prime \in F(c^\prime))$ of $\bold{D}=\int{F}$, a morphism from $\alpha \colon d \to d^\prime$ is a pair $$(h \colon c \to c^\prime, \iota \colon F(h)(d) \to d^\prime)$$ where $h \colon c \to c^\prime$ is given by $R(\alpha) \colon R(d) \to R(d^\prime)$. This shows that $\mathbb{E}$ is fully faithful. \textbf{At least in my favorite example...}

Next we show that the double functor $\mathbb{E}$ is strong by exhibiting natural isomorphisms $$\mathbb{E}_{M,N} \colon \mathbb{E}(M) \odot \mathbb{E}(N) \xrightarrow{\sim} \mathbb{E}(M \odot N)$$ for every pair of composable horizontal 1-cells $M$ and $N$ of $_L \mathbb{C}\textnormal{sp}(\bold{D})$ and for each object $c \in { _L \mathbb{C}\textnormal{sp}(\bold{D})}$ a natural isomorphism $$\mathbb{E}_c \colon \hat{U}_{\mathbb{E}(c)} \xrightarrow{\sim} \mathbb{E}(U_c)$$ where $U$ and $\hat{U}$ are the unit structure functors of $_L \mathbb{C} \textnormal{sp}(\bold{D})$ and $\mathbb{F}\textnormal{Cospan}(\bold{C})$, respectively. For any object $c$, the horizontal 1-cell $\hat{U}_{\mathbb{E}(c)}$ is given by $\hat{U}_c$ which is given by the pair:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$c$};
\node (B) at (1,1) {$c$};
\node (C) at (2,0) {$c$};
\node (D) at (3,0.5) {$!_c \in F(c)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$1$} (B)
(C) edge node[right]{$1$} (B);
\end{tikzpicture}
\]
The horizontal 1-cell $U_c$ is given by
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$L(c)$};
\node (B) at (1,1) {$L(c)$};
\node (C) at (2,0) {$L(c)$};
%\node (D) at (3,0.5) {$!_c \in F(c)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$1$} (B)
(C) edge node[right]{$1$} (B);
\end{tikzpicture}
\]
and so $\mathbb{E}(U_c)$ is given by the pair:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$c$};
\node (B) at (1,1) {$R(L(c))$};
\node (C) at (2,0) {$c$};
\node (D) at (3.25,0.5) {$!_c \in F(R(L(c)))$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$\eta_c$} (B)
(C) edge node[right]{$\eta_c$} (B);
\end{tikzpicture}
\]
Then we can obtain the natural isomorphism $\mathbb{E}_c$ as the 2-morphism
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$c$};
\node (B) at (1,0) {$c$};
\node (C) at (2,0) {$c$};
\node (A') at (0,-1) {$c$};
\node (B') at (1,-1) {$R(L(c))$};
\node (C') at (2,-1) {$c$};
\node (D) at (3,0) {$!_c \in F(c)$};
\node (D') at (3.25,-1) {$!_c \in F(R(L(c)))$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$1$} (B)
(C) edge node[above]{$1$} (B)
(A') edge node[above]{$\eta_c$} (B')
(C') edge node[above]{$\eta_c$} (B')
(A) edge node [left]{$1$} (A')
(B) edge node [left]{$\eta_c$} (B')
(C) edge node [left]{$1$} (C');
\end{tikzpicture}
\]
$$\iota \colon F(\eta_c)(!_c) \xrightarrow{!} L(c)$$
of $\mathbb{F}\textnormal{Cospan}(\bold{C})$. Seems reasonable...

Next, given composable horizontal 1-cells $M$ and $N$ in $_L \mathbb{C}\textnormal{sp}(\bold{D})$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$L(c_1)$};
\node (B) at (1,1) {$d$};
\node (C) at (2,0) {$L(c_2)$};
\node (D) at (3,0) {$L(c_2)$};
\node (E) at (4,1) {$d^\prime$};
\node (F) at (5,0) {$L(c_3)$};
%\node (D) at (3,0.5) {$!_c \in F(c)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$i$} (B)
(C) edge node[right]{$o$} (B)
(D) edge node[left]{$i^\prime$} (E)
(F) edge node[right]{$o^\prime$} (E);
\end{tikzpicture}
\]
their images $\mathbb{E}(M)$ and $\mathbb{E}(N)$ are given by:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$c_1$};
\node (B) at (1,1) {$R(d)$};
\node (C) at (2,0) {$c_2$};
\node (D) at (3,0) {$c_2$};
\node (E) at (4,1) {$R(d^\prime)$};
\node (F) at (5,0) {$c_3$};
\node (G) at (1,-0.5) {$d \in F(R(d))$};
\node (H) at (4,-0.5) {$d^\prime \in F(R(d^\prime))$};
%\node (D) at (3,0.5) {$!_c \in F(c)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$R(i) \eta_{c_1}$} (B)
(C) edge node[right]{$R(o) \eta_{c_2}$} (B)
(D) edge node[left]{$R(i^\prime) \eta_{c_2}$} (E)
(F) edge node[right]{$R(o^\prime) \eta_{c_3}$} (E);
\end{tikzpicture}
\]
and so $\mathbb{E}(M) \odot \mathbb{E}(N)$ is given by:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$c_1$};
\node (B) at (1,1) {$R(d)+_{c_2}R(d^\prime)$};
\node (C) at (2,0) {$c_3$};
\node (G) at (1,-0.5) {$\hat{d} \in F(R(d)+_{c_2}R(d^\prime))$};
%\node (D) at (3,0.5) {$!_c \in F(c)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$j \psi R(i) \eta_{c_1}$} (B)
(C) edge node[right]{$j \psi R(o^\prime) \eta_{c_3}$} (B);
\end{tikzpicture}
\]
$$\hat{d} \colon 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{d \times d^\prime} F(R(d)) \times F(R(d^\prime)) \xrightarrow{\phi_{R(d),R(d^\prime)}} F(R(d)+R(d^\prime)) \xrightarrow{F(j_{R(d),R(d^\prime)})} F(R(d)+_{c_2}R(d^\prime))$$where $\psi$ denotes each natural map into the coproduct and $j$ denotes the natural map from the coproduct to the pushout. On the other hand, $M \odot N$ is given by
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$L(c_1)$};
\node (B) at (1,1) {$d+_{L(c_2)}d^\prime$};
\node (C) at (2,0) {$L(c_3)$};
%\node (G) at (1,-0.5) {$\hat{d} \in F(R(d)+_{c_2}R(d^\prime))$};
%\node (D) at (3,0.5) {$!_c \in F(c)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$J \zeta i$} (B)
(C) edge node[right]{$J \zeta o^\prime$} (B);
\end{tikzpicture}
\]
where $\zeta$ is each inclusion into the coproduct and $J$ is the natural map from the coproduct to the pushout. Then $E(M \odot N)$ is given by
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$c_1$};
\node (B) at (1,1) {$R(d+_{L(c_2)}d^\prime)$};
\node (C) at (2,0) {$c_3$};
\node (G) at (1,-0.5) {$d+_{L(c_2)} d^\prime \in F(R(d+_{L(c_2)}d^\prime))$};
%\node (D) at (3,0.5) {$!_c \in F(c)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$R(J \zeta i) \eta_{c_1}$} (B)
(C) edge node[right]{$R(J \zeta o^\prime) \eta_{c_3}$} (B);
\end{tikzpicture}
\]
and so $\mathbb{E}_{M,N} \colon \mathbb{E}(M) \odot \mathbb{E}(N) \xrightarrow{\sim} \mathbb{E}(M \odot N)$ is given by the 2-morphism:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$c_1$};
\node (B) at (1.5,0) {$R(d)+_{c_2}R(d^\prime)$};
\node (C) at (3,0) {$c_3$};
\node (A') at (0,-1) {$c_1$};
\node (B') at (1.5,-1) {$R(d+_{L(c_2)}d^\prime)$};
\node (C') at (3,-1) {$c_3$};
\node (D) at (5.5 ,0) {$\hat{d} \in F(R(d)+_{c_2}R(d^\prime))$};
\node (D') at (5.5,-1) {$d+_{L(c_2)}d^\prime \in F(R(d+_{L(c_2)}d^\prime))$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$j \psi R(i) \eta_{c_1}$} (B)
(C) edge node[above]{$j \psi R(o^\prime) \eta_{c_3}$} (B)
(A') edge node[above]{$R(J \zeta i) \eta_{c_1}$} (B')
(C') edge node[above]{$R(J \zeta o^\prime) \eta_{c_3}$} (B')
(A) edge node [left]{$1$} (A')
(B) edge node [left]{$\sigma$} (B')
(C) edge node [left]{$1$} (C');
\end{tikzpicture}
\]
First, if the right adjoint $R \colon \bold{D} \to \bold{C}$ is also a left adjoint, then $R$ also preserves all colimits and we have an isomorphism $$\kappa \colon R(d) +_{R(L(c_2))} R(d^\prime) \to R(d+_{L(c_2)}d^\prime).$$ Also, since the left adjoint $L \colon \bold{C} \to \bold{D}$ is fully faithful, the unit of the adjunction $L \dashv R$ at the object $c_2$ gives an isomorphism $\eta_{c_2} \colon c_2 \to R(L(c_2))$ which results in an isomorphism $$j_{\eta_{c_2}} \colon R(d) +_{c_2} R(d^\prime) \to R(d) +_{R(L(c_2))} R(d^\prime).$$ Composing these two results in an isomorphism $$\sigma \coloneqq \kappa j_{\eta_{c_2}} \colon R(d) +_{c_2} R(d^\prime) \to R(d+_{L(c_2)}d^\prime).$$
Next, to see that the above diagram commutes, it suffices to show that for the object $c_1 \in \bold{C}$, $$R(J \zeta i)\eta_{c_1}(c_1) = R(J)R(\zeta)R(i)\eta_{c_1}(c_1) \stackrel{!}{=} \sigma j \psi R(i)\eta_{c_1}(c_1).$$ This follows as $R(i) \eta_{c_1} \colon c_1 \to R(d)$ and the following diagram commutes:
\[
\begin{tikzpicture}[scale=1.5]
\node (B) at (0,0) {$R(d)$};
\node (C) at (2,0) {$R(d)+R(d^\prime)$};
\node (A') at (4,0) {$R(d)+_{c_2}R(d^\prime)$};
\node (B') at (4,-2) {$R(d+_{L(c_2)}d^\prime)$};
\node (D) at (0,-2) {$R(d+d^\prime)$};
\node (D') at (4,-1) {$R(d)+_{R(L(c_2))} R(d^\prime)$};
\path[->,font=\scriptsize,>=angle 90]
(C) edge node[above]{$j$} (A')
(B) edge node[above]{$\psi$} (C)
(D) edge node[above]{$R(J)$} (B')
(B) edge node [left]{$R(\zeta)$} (D)
(A') edge node [right]{$j_{\eta_{c_2}}$} (D')
(A') edge [out=345,in=15] node [right]{$\sigma$} (B')
(D') edge node [right]{$\kappa$} (B');
\end{tikzpicture}
\]
Lastly, this map of cospans comes with an isomorphism $\iota \colon F(\sigma)(\hat{d}) \to (d+_{L(c_2)}d^\prime)$ in $F(R(d+_{L(c_2)}d^\prime))$. This shows that $\mathbb{E}$ is strong, and so $\mathbb{E} \colon _L \mathbb{C}\textnormal{sp}(\bold{D}) \xrightarrow{\sim} \mathbb{F}\textnormal{Cospan}(\bold{C})$ is part of a double equivalence by Theorem \ref{ShulDubEquiv}.

Next, if both double categories $_L \mathbb{C}\textnormal{sp}(\bold{D})$ and $\mathbb{F}\textnormal{Cospan}(\bold{C})$ are symmetric monoidal, as they are if both $\bold{C}$ and $\bold{D}$ have finite colimits, then this equivalence of double categories $\mathbb{E} \colon _L \mathbb{C}\textnormal{sp}(\bold{D}) \to \mathbb{F} \textnormal{Cospan}(\bold{C})$ will be symmetric monoidal. First note that we have an isomorphism $\epsilon \colon 1_{\mathbb{F}\textnormal{Cospan}(\bold{C})} \to \mathbb{E}(1_{_L \mathbb{C}\textnormal{sp}(\bold{D})})$ and natural isomorphisms $\mu_{c_1,c_2} \colon \mathbb{E}(c_1) \otimes \mathbb{E}(c_2) \to \mathbb{E}(c_1 \otimes c_2)$ for every pair of objects $c_1,c_2 \in {_L \mathbb{C} \textnormal{sp}(\bold{D})}$ both of which are given by identities since both double categories $_L \mathbb{C}\textnormal{sp}(\bold{D})$ and $\mathbb{F}\textnormal{Cospan}(\bold{C})$ have $\bold{C}$ as their category of objects and $\mathbb{E}_0=\id_{\bold{C}}$. The diagrams containing these morphisms that are required to commute do so trivially.

For the arrow component $\mathbb{E}_1$, we have an isomorphism $\delta \colon U_{1_{\mathbb{F}\textnormal{Cospan}(\bold{C})}} \to \mathbb{E}(U_{1_{_L \mathbb{C}\textnormal{sp}(\bold{D})}})$ where the horizontal 1-cell $U_{1_{\mathbb{F}\textnormal{Cospan}(\bold{C})}}$ is given by:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$1_\bold{C}$};
\node (B) at (1,1) {$1_\bold{C}$};
\node (C) at (2,0) {$1_\bold{C}$};
\node (D) at (3,0.5) {$!_{1_{\bold{C}}} \in F(1_\bold{C})$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$1$} (B)
(C) edge node[right]{$1$} (B);
\end{tikzpicture}
\]
where $!_{1_{\bold{C}}} = \phi \colon \bold{1} \to F(1_\bold{C})$ is the trivial decoration which comes from the structure of the symmetric lax monoidal pseudofunctor $F \colon \bold{C} \to \bold{Cat}$. The horizontal 1-cell $U_{1_{_L \mathbb{C}\textnormal{sp}(\bold{D})}}$ is given by:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$L(1_\bold{C})$};
\node (B) at (1,1) {$L(1_\bold{C})$};
\node (C) at (2,0) {$L(1_\bold{C})$};
%\node (D) at (3,0.5) {$I \in F(1_\bold{C})$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$1$} (B)
(C) edge node[right]{$1$} (B);
\end{tikzpicture}
\]
where here we make use of the fact that the left adjoint $L \colon (\bold{C},+,1_\bold{C}) \to (\bold{D},+,1_\bold{D})$ preserves all colimits and thus $L(1_\bold{C}) \cong 1_\bold{D}$. The horizontal 1-cell $\mathbb{E}(U_{1_{_L \mathbb{C} \textnormal{sp}(\bold{D})}})$ is given by the pair:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$1_\bold{C}$};
\node (B) at (1,1) {$R(L(1_\bold{C}))$};
\node (C) at (2,0) {$1_\bold{C}$};
\node (D) at (3.5,0.5) {$!_{1_\bold{C}} \in F(R(L(1_\bold{C}))) \cong F(1_\bold{C})$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{${\eta_{1_\bold{C}}}$} (B)
(C) edge node[right]{${\eta_{1_\bold{C}}}$} (B);
\end{tikzpicture}
\]
The isomorphism $\delta$ is then given by the 2-morphism:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$1_\bold{C}$};
\node (B) at (1,0) {$1_{\bold{C}}$};
\node (C) at (2,0) {$1_\bold{C}$};
\node (A') at (0,-1) {$1_\bold{C}$};
\node (B') at (1,-1) {$R(L(1_\bold{C}))$};
\node (C') at (2,-1) {$1_\bold{C}$};
\node (D) at (3,0) {$!_{1_\bold{C}} \in F(1_\bold{C})$};
\node (D') at (3.75,-1) {$!_{1_\bold{C}} \in F(R(L(1_\bold{C}))) \cong F(1_\bold{C})$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$1$} (B)
(C) edge node[above]{$1$} (B)
(A') edge node[above]{${\eta_{1_\bold{C}}}$} (B')
(C') edge node[above]{${\eta_{1_\bold{C}}}$} (B')
(A) edge node [left]{$1$} (A')
(B) edge node [left]{${\eta_{1_\bold{C}}}$} (B')
(C) edge node [left]{$1$} (C');
\end{tikzpicture}
\]
$$\iota_{{\eta_{1_\bold{C}}}} \colon F({\eta_{1_\bold{C}}}(!_{1_\bold{C}})) \to !_{1_\bold{C}}$$
of $\mathbb{F}\textnormal{Cospan}(\bold{C})$.

Given two horizontal 1-cells $M$ and $N$ of $_L \mathbb{C}\textnormal{sp}(\bold{D})$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$L(c_1)$};
\node (B) at (1,1) {$d$};
\node (C) at (2,0) {$L(c_2)$};
\node (D) at (3,0) {$L(c_1^\prime)$};
\node (E) at (4,1) {$d^\prime$};
\node (F) at (5,0) {$L(c_2^\prime)$};
%\node (D) at (3,0.5) {$!_c \in F(c)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$i$} (B)
(C) edge node[right]{$o$} (B)
(D) edge node[left]{$i^\prime$} (E)
(F) edge node[right]{$o^\prime$} (E);
\end{tikzpicture}
\]
their images $\mathbb{E}(M)$ and $\mathbb{E}(N)$ are given by:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$c_1$};
\node (B) at (1,1) {$R(d)$};
\node (C) at (2,0) {$c_2$};
\node (D) at (3,0) {$c_1^\prime$};
\node (E) at (4,1) {$R(d^\prime)$};
\node (F) at (5,0) {$c_2^\prime$};
\node (G) at (1,-0.5) {$d \in F(R(d))$};
\node (H) at (4,-0.5) {$d^\prime \in F(R(d^\prime))$};
%\node (D) at (3,0.5) {$!_c \in F(c)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$R(i) \eta_{c_1}$} (B)
(C) edge node[right]{$R(o) \eta_{c_2}$} (B)
(D) edge node[left]{$R(i^\prime) \eta_{c_1^\prime}$} (E)
(F) edge node[right]{$R(o^\prime) \eta_{c_2^\prime}$} (E);
\end{tikzpicture}
\]
and so $\mathbb{E}(M) \otimes \mathbb{E}(N)$ is given by:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$c_1+c_1^\prime$};
\node (B) at (1,1) {$R(d)+R(d^\prime)$};
\node (C) at (2,0) {$c_2+c_2^\prime$};
\node (D) at (1,-0.5) {$\hat{d} \in F(R(d)+R(d^\prime)$}; 
%\node (D) at (3,0.5) {$!_c \in F(c)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$R(i) \eta_{c_1} +R(i^\prime) \eta_{c_1^\prime}$} (B)
(C) edge node[right]{$R(o) \eta_{c_2} + R(o) \eta_{c_2^\prime}$} (B);
\end{tikzpicture}
\]
where $$\hat{d} \colon 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{d \times d^\prime} F(R(d)) \times F(R(d^\prime)) \xrightarrow{\phi_{R(d),R(d^\prime)}} F(R(d)+R(d^\prime)).$$ On the other hand, $M \otimes N$ is given by
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$L(c_1+c_1^\prime)$};
\node (B) at (1,1) {$d+d^\prime$};
\node (C) at (2,0) {$L(c_2+c_2^\prime)$};
%\node (D) at (3,0.5) {$!_c \in F(c)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$i+i^\prime$} (B)
(C) edge node[right]{$o+o^\prime$} (B);
\end{tikzpicture}
\]
and $\mathbb{E}(M \otimes N)$ is given by:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$c_1+c_1^\prime$};
\node (B) at (1,1) {$R(d+d^\prime)$};
\node (C) at (2,0) {$c_2+c_2^\prime$};
\node (D) at (1,-0.5) {$d+d^\prime \in F(R(d+d^\prime))$};
%\node (D) at (3,0.5) {$!_c \in F(c)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$R(i+i^\prime) \eta_{c_1+c_1^\prime}$} (B)
(C) edge node[right]{$R(o+o^\prime) \eta_{c_2+c_2^\prime}$} (B);
\end{tikzpicture}
\]
We then have a 2-isomorphism $\mu_{M,N} \colon E(M) \otimes E(N) \xrightarrow{\sim} E(M \otimes N)$ in $\mathbb{F}\textnormal{Cospan}(\bold{C})$ given by:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$c_1+c_1^\prime$};
\node (B) at (2,0) {$R(d)+R(d^\prime)$};
\node (C) at (4,0) {$c_2+c_2^\prime$};
\node (A') at (0,-1) {$c_1+c_1^\prime$};
\node (B') at (2,-1) {$R(d+d^\prime)$};
\node (C') at (4,-1) {$c_2+c_2^\prime$};
\node (D) at (5.75,0) {$\hat{d} \in F(R(d)+R(d^\prime))$};
\node (D') at (5.75,-1) {$d+d^\prime \in F(R(d+d^\prime))$};
\node (E) at (2,-1.5) {$\iota_\mu \colon F(\kappa)(\hat{d}) \to d+d^\prime$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$R(i)\eta_{c_1} + R(i^\prime)\eta_{c_1^\prime}$} (B)
(C) edge node[above]{$R(o)\eta_{c_2} + R(o^\prime)\eta_{c_2^\prime}$} (B)
(A') edge node[above]{$R(i+i^\prime)\eta_{c_1+c_1^\prime}$} (B')
(C') edge node[above]{$R(o+o^\prime)\eta_{c_2+c_2^\prime}$} (B')
(A) edge node [left]{$1$} (A')
(B) edge node [left]{$\kappa$} (B')
(C) edge node [left]{$1$} (C');
\end{tikzpicture}
\]
The isomorphisms $\delta$ and $\mu$ satisfy the left and right unitality squares, associativity hexagon and braiding square. Let $M_1,M_2$ and $M_3$ be horizontal 1-cells in $_L \mathbb{C}\textnormal{sp}(\bold{D})$ given by:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$L(c_1)$};
\node (B) at (1,1) {$d_1$};
\node (C) at (2,0) {$L(c_1^\prime)$};
\node (D) at (3,0) {$L(c_2)$};
\node (E) at (4,1) {$d_2$};
\node (F) at (5,0) {$L(c_2^\prime)$};
\node (G) at (6,0) {$L(c_3)$};
\node (H) at (7,1) {$d_3$};
\node (I) at (8,0) {$L(c_3^\prime)$};
%\node (D) at (3,0.5) {$!_c \in F(c)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$i_1$} (B)
(C) edge node[right]{$o_1$} (B)
(D) edge node[left]{$i_2$} (E)
(F) edge node[right]{$o_2$} (E)
(G) edge node[left]{$i_3$} (H)
(I) edge node[right]{$o_3$} (H);
\end{tikzpicture}
\]
The left unitality square:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$1_{\mathbb{F}\textnormal{Cospan}(\bold{C})} \otimes \mathbb{E}(M_1)$};
\node (B) at (3,0) {$\mathbb{E}(1_{ _L \mathbb{C}\textnormal{sp}(\bold{D})}) \otimes \mathbb{E}(M_1)$};
\node (C) at (0,-1) {$\mathbb{E}(M_1)$};
\node (D) at (3,-1) {$\mathbb{E}(1_{ _L \mathbb{C}\textnormal{sp}(\bold{D})} \otimes M_1)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$\delta \otimes 1$} (B)
(B) edge node[right]{$\mu_{1,M_1}$} (D)
(A) edge node[left]{$\lambda$} (C)
(D) edge node[above]{$\mathbb{E}(\lambda)$} (C);
\end{tikzpicture}
\]
has underlying maps of cospans given by:
\[
		\begin{tikzpicture}
			\node (d) at (7.5,0) {$\mathbb{E}(1_{ _L \mathbb{C}\textnormal{sp}(\bold{D})}) \otimes \mathbb{E}(M_1)$};
			\node (a) at (-4,0) {$1_\bold{C}+c_1$};
			\node (b) at (0.5,0) {$R(L(1_\bold{C})) + R(d_1)$};
			\node (c) at (5,0) {$1_\bold{C}+c_1^\prime$};
			\node (d2) at (7.5,1.5) {$1_{\mathbb{F}\textnormal{Cospan}(\bold{C})} \otimes \mathbb{E}(M_1)$};
			\node (a2) at (-4,1.5) {$1_\bold{C}+c_1$};
			\node (b2) at (0.5,1.5) {$1_\bold{C}+R(d_1)$};
			\node (c2) at (5,1.5) {$1_\bold{C}+c_1^\prime$};
			\node (d3) at (7.5,3) {$\mathbb{E}(M_1)$};
                                \node (a3) at (-4,3) {$c_1$};
			\node (b3) at (0.5,3) {$R(d_1)$};
			\node (c3) at (5,3) {$c_1^\prime$};
			\node (d4) at (7.5,-1.5) {$\mathbb{E}(1_{ _L \mathbb{C}\textnormal{sp}(\bold{D})} \otimes M_1)$};
                                \node (a5) at (-4,-1.5) {$1_\bold{C}+c_1^\prime$};
			\node (b5) at (0.5,-1.5) {$R(L(1_\bold{C})+d_1)$};
			\node (c5) at (5,-1.5) {$1_\bold{C}+c_1^\prime$};
			\node (d5) at (7.5,-3) {$\mathbb{E}(M_1)$};
                                \node (a6) at (-4,-3) {$c_1$};
			\node (b6) at (0.5,-3) {$R(d_1)$};
			\node (c6) at (5,-3) {$c_1^\prime$};
			\path[->,font=\scriptsize,>=angle 90]
			(d2) edge node [left]{$\lambda$} (d3)
			(d2) edge node [left] {$\delta \otimes 1$} (d)
			(d) edge node [left] {$\mu_{1,M_1}$} (d4)
			(d4) edge node [left] {$\mathbb{E}(\lambda)$} (d5)
			(a) edge node[above]{$\eta_{1_\bold{C}}+R(i_1)\eta_{c_1}$} (b)
			(c) edge node[above]{$\eta_{1_\bold{C}}+R(o_1)\eta_{c_1^\prime}$} (b)
                                (a2) edge node[above]{$1+R(i_1)\eta_{c_1}$} (b2)
			(c2) edge node[above]{$1+R(o_1)\eta_{c_1^\prime}$} (b2)
                                (a2) edge node[left]{$1$} (a)
                                (b2) edge node[left]{$\eta_{1_\bold{C}}+1$} (b)
(b2) edge node[right]{$\iota_2$} (b)
			(c2) edge node[left]{$1$} (c)
                                (a3) edge node[above]{$R(i_1)\eta_{c_1}$} (b3)
			(c3) edge node[above]{$R(o_1)\eta_{c_1^\prime}$} (b3)
                                (a2) edge node[left]{$\lambda_{\bold{C}}$} (a3)
                                (b2) edge node[left]{$\lambda_{\bold{C}}$} (b3)
(b2) edge node[right]{$\iota_1$} (b3)
			(c2) edge node[left]{$\lambda_{\bold{C}}$} (c3)
                                (a5) edge node[above]{$(\mu_{L(1_\bold{C}),d_1})(\eta_{1_\bold{C}}+R(i_1)\eta_{c_1})$} (b5)
			(c5) edge node[above]{$(\mu_{L(1_\bold{C}),d_1})(\eta_{1_\bold{C}}+R(o_1)\eta_{c_1^\prime})$} (b5)
                                (a) edge node[left]{$1$} (a5)
                                (b) edge node[left]{$\mu_{L(1_\bold{C}),d_1}$} (b5)
(b) edge node[right]{$\iota_3$} (b5)
			(c) edge node[left]{$1$} (c5)
                                (a6) edge node[above]{$R(i_1)\eta_{c_1}$} (b6)
			(c6) edge node[above]{$R(o_1)\eta_{c_1^\prime}$} (b6)
                                (a5) edge node[left]{$\lambda_{\bold{C}}$} (a6)
                                (b5) edge node[left]{$R(\lambda_{\bold{D}})$} (b6)
 (b5) edge node[right]{$\iota_4$} (b6)
			(c5) edge node[left]{$\lambda_{\bold{C}}$} (c6);
		\end{tikzpicture}
	\]
with the corresponding maps of decorations amounting to the following commutative diagram in $F(R(d_1))$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (-.5,0) {$F(\lambda_{\bold{C}})(!_{1_\bold{C}}+d_1)$};
\node (C) at (4,0) {$F(R(\lambda_{\bold{D}})(\mu_{L(1_\bold{C}),d_1}))(!_{R(L(1_\bold{C}))} +d_1$)};
\node (D) at (-.5,-1) {$d_1$};
\node (E) at (4,-1) {$F(R(\lambda_\bold{D}))(d_{!+1})$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$F(R(\lambda_{\bold{D}})(\mu_{L(1_\bold{C}),d_1}))(\iota_2)$} (C)
(A) edge node[left]{$\iota_1$} (D)
(E) edge node[above]{$\iota_4$} (D)
(C) edge node[right]{$F(R(\lambda_\bold{D}))(\iota_3)$} (E);
\end{tikzpicture}
\]
where $d_{!+1}$ is the decoration $d_1$ on the element $R(L(1_\bold{C})+d_1) \in \bold{C}$. The above square commutes because $$F(\lambda_\bold{C})(!_{1_\bold{C}}+d_1) = F(R(\lambda_\bold{D})(\mu_{L(1_\bold{C}),d_1})(\eta_{1_\bold{C}}+1))(!_{1_\bold{C}}+d_1)$$ as the above diagram of maps of cospans commutes. The right unitality square is similar. The associator hexagon:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$(\mathbb{E}(M_1) \otimes \mathbb{E}(M_2)) \otimes \mathbb{E}(M_3)$};
\node (B) at (3.5,0) {$\mathbb{E}(M_1 \otimes M_2) \otimes \mathbb{E}(M_3)$};
\node (C) at (7,0) {$\mathbb{E}((M_1 \otimes M_2) \otimes M_3)$};
\node (A') at (0,-1) {$\mathbb{E}(M_1) \otimes (\mathbb{E}(M_2) \otimes \mathbb{E}(M_3))$};
\node (B') at (3.5,-1) {$\mathbb{E}(M_1) \otimes \mathbb{E}(M_2 \otimes M_3)$};
\node (C') at (7,-1) {$\mathbb{E}(M_1 \otimes (M_2 \otimes M_3))$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$\mu_{M_1,M_2} \otimes 1$} (B)
(B) edge node[above]{$\mu_{M_1 \otimes M_2,M_3}$} (C)
(A') edge node[above]{$1 \otimes \mu_{M_2,M_3}$} (B')
(B') edge node[above]{$\mu_{M_1,M_2 \otimes M_3}$} (C')
(A) edge node [left]{$a^\prime$} (A')
(C) edge node [left]{$\mathbb{E}(a)$} (C');
\end{tikzpicture}
\]
has underlying maps of cospans given by:
\[
		\begin{tikzpicture}
\node(d) at (1.5,10.5) {$(\mathbb{E}(M_1) \otimes \mathbb{E}(M_2)) \otimes \mathbb{E}(M_3)$};
\node (d2) at (1.5,12) {$\mathbb{E}(M_1 \otimes M_2) \otimes \mathbb{E}(M_3)$};
\node (d3) at (1.5,13.5) {$\mathbb{E}((M_1 \otimes M_2) \otimes M_3)$};
\node (d4) at (1.5,15) {$\mathbb{E}(M_1 \otimes (M_2 \otimes M_3))$};
\node (d5) at (1.5,9) {$\mathbb{E}(M_1) \otimes (\mathbb{E}(M_2) \otimes \mathbb{E}(M_3))$};
\node (d6) at (1.5,7.5) {$\mathbb{E}(M_1) \otimes \mathbb{E}(M_2 \otimes M_3)$};
\node (d7) at (1.5,6) {$\mathbb{E}(M_1 \otimes (M_2 \otimes M_3))$};
			\node (a) at (-4.25,0) {$(c_1+c_2)+c_3$};
			\node (b) at (1.5,0) {$(R(d_1)+R(d_2))+R(d_3)$};
			\node (c) at (7.25,0) {$(c_1^\prime+c_2^\prime)+c_3^\prime$};
			\node (a2) at (-4.25,1.5) {$(c_1+c_2)+c_3$};
			\node (b2) at (1.5,1.5) {$R(d_1+d_2)+R(d_3)$};
			\node (c2) at (7.25,1.5) {$(c_1^\prime+c_2^\prime)+c_3^\prime$};
                                \node (a3) at (-4.25,3) {$(c_1+c_2)+c_3$};
			\node (b3) at (1.5,3) {$R((d_1+d_2)+d_3)$};
			\node (c3) at (7.25,3) {$(c_1^\prime+c_2^\prime)+c_3^\prime$};
                                \node (a4) at (-4.25,4.5) {$c_1+(c_2+c_3)$};
			\node (b4) at (1.5,4.5) {$R(d_1+(d_2+d_3))$};
			\node (c4) at (7.25,4.5) {$c_1^\prime + (c_2^\prime + c_3^\prime)$};
                                \node (a5) at (-4.25,-1.5) {$c_1+(c_2+c_3)$};
			\node (b5) at (1.5,-1.5) {$R(d_1)+(R(d_2)+R(d_3))$};
			\node (c5) at (7.25,-1.5) {$c_1^\prime + (c_2^\prime + c_3^\prime)$};
                                \node (a6) at (-4.25,-3) {$c_1+(c_2+c_3)$};
			\node (b6) at (1.5,-3) {$R(d_1)+R(d_2+d_3)$};
			\node (c6) at (7.25,-3) {$c_1^\prime + (c_2^\prime + c_3^\prime)$};
                                \node (a7) at (-4.25,-4.5) {$c_1+(c_2+c_3)$};
			\node (b7) at (1.5,-4.5) {$R(d_1+(d_2+d_3))$};
			\node (c7) at (7.25,-4.5) {$c_1^\prime + (c_2^\prime + c_3^\prime)$};
			\path[->,font=\scriptsize,>=angle 90]
(d) edge node[left] {$\mu_{M_1,M_2} \otimes 1$} (d2)
(d2) edge node[left] {$\mu_{M_1 \otimes M_2,M_3}$} (d3)
(d3) edge node[left] {$\mathbb{E}(a)$} (d4)
(d) edge node[left] {$a^\prime$} (d5)
(d5) edge node[left] {$1 \otimes \mu_{M_2,M_3}$} (d6)
(d6) edge node[left] {$\mu_{M_1,M_2 \otimes M_3}$} (d7)
			(a) edge node[above]{$(R(i_1)\eta_{c_1}+R(i_2)\eta_{c_2})+R(i_3)\eta_{c_3}$} (b)
			(c) edge node[above]{$(R(o_1)\eta_{c_1^\prime}+R(o_2)\eta_{c_2^\prime})+R(o_3)\eta_{c_3^\prime}$} (b)
                                (a2) edge node[above]{$R(i_1+i_2)\eta_{c_1+c_2}+R(i_3)\eta_{c_3}$} (b2)
			(c2) edge node[above]{$R(o_1+o_2)\eta_{c_1^\prime+c_2^\prime}+R(o_3)\eta_{c_3^\prime}$} (b2)
                                (a) edge node[left]{$1$} (a2)
                                (b) edge node[left]{$\kappa + 1$} (b2)
(b) edge node[right]{$\iota_1$} (b2)
			(c) edge node[left]{$1$} (c2)
                                (a3) edge node[above]{$R((i_1+i_2)+i_3)\eta_{(c_1+c_2)+c_3}$} (b3)
			(c3) edge node[above]{$R((o_1+o_2)+o_3)\eta_{(c_1^\prime+c_2^\prime)+c_3^\prime}$} (b3)
                                (a2) edge node[left]{$1$} (a3)
                                (b2) edge node[left]{$\kappa$} (b3)
(b2) edge node[right]{$\iota_2$} (b3)
			(c2) edge node[left]{$1$} (c3)
                                (a4) edge node[above]{$R(i_1+(i_2+i_3))\eta_{c_1+(c_2+c_3)}$} (b4)
			(c4) edge node[above]{$R(o_1+(o_2+o_3))\eta_{c_1^\prime+(c_2^\prime+c_3^\prime)}$} (b4)
                                (a3) edge node[left]{$a_\bold{C}$} (a4)
                                (b3) edge node[left]{$R(a_\bold{D})$} (b4)
(b3) edge node[right]{$\iota_3$} (b4)
			(c3) edge node[left]{$a_\bold{C}$} (c4)
                                (a5) edge node[above]{$R(i_1)\eta_{c_1}+(R(i_2)\eta_{c_2}+R(i_3)\eta_{c_3})$} (b5)
			(c5) edge node[above]{$R(o_1)\eta_{c_1^\prime}+(R(o_2)\eta_{c_2^\prime}+R(o_3)\eta_{c_3^\prime})$} (b5)
                                (a) edge node[left]{$a_\bold{C}$} (a5)
                                (b) edge node[left]{$a_\bold{C}$} (b5)
(b) edge node[right]{$\iota_4$} (b5)
			(c) edge node[left]{$a_\bold{C}$} (c5)
                                (a6) edge node[above]{$R(i_1)\eta_{c_1}+R(i_2+i_3)\eta_{c_2+c_3}$} (b6)
			(c6) edge node[above]{$R(o_1)\eta_{c_1^\prime}+R(o_2+o_3)\eta_{c_2^\prime+c_3^\prime}$} (b6)
                                (a5) edge node[left]{$1$} (a6)
                                (b5) edge node[left]{$1+\kappa$} (b6)
 (b5) edge node[right]{$\iota_5$} (b6)
			(c5) edge node[left]{$1$} (c6)
                                (a7) edge node[above]{$R(i_1+(i_2+i_3))\eta_{c_1+(c_2+c_3)}$} (b7)
			(c7) edge node[above]{$R(o_1+(o_2+o_3))\eta_{c_1^\prime+(c_2^\prime+c_3^\prime)}$} (b7)
                                (a6) edge node[left]{$1$} (a7)
                                (b6) edge node[left]{$\kappa$} (b7)
(b6) edge node[right]{$\iota_6$} (b7)
			(c6) edge node[left]{$1$} (c7);
		\end{tikzpicture}
	\]
with the corresponding maps of decorations amounting to the following commutative diagram in $F(R(d_1+(d_2+d_3)))$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$F((\kappa)(1+\kappa)(a_\bold{C}))((d_1+d_2)+d_3)$};
\node (B) at (5,0) {$F((R(a_\bold{D}))(\kappa))((d_1+d_2)+d_3)$};
\node (C) at (5,-1) {$F(R(a_\bold{D}))((d_1+d_2)+d_3)$};
\node (D) at (5,-2) {$d_1+(d_2+d_3)$};
\node (E) at (0,-1) {$F((\kappa)(1+\kappa))((d_1+d_2)+d_3)$};
\node (F) at (0,-2) {$F(\kappa)(d_1+(d_2+d_3))$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$F((R(a_\bold{D}))(\kappa))(\iota_1)$} (B)
(B) edge node[right]{$F(R(a_\bold{D}))(\iota_2)$} (C)
(C) edge node[right]{$\iota_3$} (D)
(A) edge node[left]{$F((\kappa)(1+\kappa))(\iota_4)$} (E)
(E) edge node[left]{$F(\kappa)(\iota_5)$} (F)
(F) edge node[above]{$\iota_6$} (D);
\end{tikzpicture}
\]
The above square commutes because $$F((\kappa)(1+\kappa)(a_\bold{C}))((d_1+d_2)+d_3) = F((R(a_\bold{D}))(\kappa)(\kappa+1))((d_1+d_2)+d_3)$$ as the above diagram of maps of cospans commutes. Lastly, the braiding square:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$\mathbb{E}(M_1) \otimes \mathbb{E}(M_2)$};
\node (B) at (3,0) {$\mathbb{E}(M_2) \otimes \mathbb{E}(M_1)$};
\node (C) at (0,-1) {$\mathbb{E}(M_1 \otimes M_2)$};
\node (D) at (3,-1) {$\mathbb{E}(M_2 \otimes M_1)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$\beta$} (B)
(B) edge node[right]{$\mu_{M_2,M_1}$} (D)
(A) edge node[left]{$\mu_{M_1,M_2}$} (C)
(C) edge node[above]{$\mathbb{E}(\beta)$} (D);
\end{tikzpicture}
\]
has underlying map of cospans given by:
\[
		\begin{tikzpicture}
\node (d) at (7,0) {$\mathbb{E}(M_1) \otimes \mathbb{E}(M_2)$};
\node (d2) at (7,1.5) {$\mathbb{E}(M_2) \otimes \mathbb{E}(M_1)$};
\node (d3) at (7,3) {$\mathbb{E}(M_2 \otimes M_1)$};
\node (d4) at (7,-1.5) {$\mathbb{E}(M_1 \otimes M_2)$};
\node (d5) at (7,-3) {$\mathbb{E}(M_2 \otimes M_1)$};
			\node (a) at (-4,0) {$c_1+c_2$};
			\node (b) at (0.5,0) {$R(d_1)+R(d_2)$};
			\node (c) at (5,0) {$c_1^\prime+c_2^\prime$};
			\node (a2) at (-4,1.5) {$c_2+c_1$};
			\node (b2) at (0.5,1.5) {$R(d_2)+R(d_1)$};
			\node (c2) at (5,1.5) {$c_2^\prime+c_1^\prime$};
                                \node (a3) at (-4,3) {$c_2+c_1$};
			\node (b3) at (0.5,3) {$R(d_2+d_1)$};
			\node (c3) at (5,3) {$c_2^\prime + c_1^\prime$};
                                \node (a5) at (-4,-1.5) {$c_1+c_2$};
			\node (b5) at (0.5,-1.5) {$R(d_1+d_2)$};
			\node (c5) at (5,-1.5) {$c_1^\prime+c_2^\prime$};
                                \node (a6) at (-4,-3) {$c_2+c_1$};
			\node (b6) at (0.5,-3) {$R(d_2+d_1)$};
			\node (c6) at (5,-3) {$c_2^\prime + c_1^\prime$};
			\path[->,font=\scriptsize,>=angle 90]
(d) edge node[left]{$\beta$} (d2)
(d2) edge node[left]{$\mu_{M_2,M_1}$}(d3)
(d) edge node[left] {$\mu_{M_1,M_2}$}(d4)
(d4)edge node[left]{$\mathbb{E}(\beta)$}(d5)
			(a) edge node[above]{$R(i_1) \eta_{c_1} + R(i_2)\eta_{c_2}$} (b)
			(c) edge node[above]{$R(o_1) \eta_{c_1^\prime} + R(o_2) \eta_{c_2^\prime}$} (b)
                                (a2) edge node[above]{$R(i_2) \eta_{c_2} + R(i_1) \eta_{c_1}$} (b2)
			(c2) edge node[above]{$R(o_2) \eta_{c_2^\prime} + R(o_1) \eta_{c_1^\prime}$} (b2)
                                (a) edge node[left]{$\beta_\bold{C}$} (a2)
                                (b) edge node[left]{$\beta_\bold{C}$} (b2)
(b) edge node[right]{$\iota_1$} (b2)
			(c) edge node[left]{$\beta_\bold{C}$} (c2)
                                (a3) edge node[above]{$R(i_2+i_1)\eta_{c_2+c_1}$} (b3)
			(c3) edge node[above]{$R(o_2+o_1)\eta_{c_2^\prime+c_1^\prime}$} (b3)
                                (a2) edge node[left]{$1$} (a3)
                                (b2) edge node[left]{$\kappa$} (b3)
(b2) edge node[right]{$\iota_2$} (b3)
			(c2) edge node[left]{$1$} (c3)
                                (a5) edge node[above]{$R(i_1+i_2)\eta_{c_1+c_2}$} (b5)
			(c5) edge node[above]{$R(o_1+o_2)\eta_{c_1^\prime+c_2^\prime}$} (b5)
                                (a) edge node[left]{$1$} (a5)
                                (b) edge node[left]{$\kappa$} (b5)
(b) edge node[right]{$\iota_3$} (b5)
			(c) edge node[left]{$1$} (c5)
                                (a6) edge node[above]{$R(i_2+i_1)\eta_{c_2+c_1}$} (b6)
			(c6) edge node[above]{$R(o_2+o_1)\eta_{c_2^\prime+c_1^\prime}$} (b6)
                                (a5) edge node[left]{$\beta_\bold{C}$} (a6)
                                (b5) edge node[left]{$R(\beta_\bold{D})$} (b6)
 (b5) edge node[right]{$\iota_4$} (b6)
			(c5) edge node[left]{$\beta_\bold{C}$} (c6);
		\end{tikzpicture}
	\]
with the corresponding maps of decorations amounting to the following commutative diagram in $F(R(d_2+d_1))$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (-.5,0) {$F((\kappa)(\beta_\bold{C}))(d_1+d_2)$};
\node (C) at (4,0) {$F(\kappa)(d_2+d_1)$};
\node (D) at (-.5,-1) {$F(R(\beta_\bold{D}))(d_1+d_2)$};
\node (E) at (4,-1) {$d_2+d_1$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$F(\kappa)(\iota_1)$} (C)
(A) edge node[left]{$F(R(\beta_\bold{D}))(\iota_3)$} (D)
(D) edge node[above]{$\iota_4$} (E)
(C) edge node[right]{$\iota_2$} (E);
\end{tikzpicture}
\]
The above square commutes because $$F((\kappa)(\beta_\bold{C}))(d_1+d_2) = F((R(\beta_\bold{D}))(\kappa))(d_1+d_2)$$ as the above diagram of maps of cospans commutes. Thus the double functor $\mathbb{E} \colon _L\mathbb{C}\textnormal{sp}(\bold{D}) \to \mathbb{F}\textnormal{Cospan}(\bold{C})$ is symmetric monoidal.
\end{proof}
Using a result of Shulman \cite{Shul}, each of the isofibrant symmetric monoidal double categories $\mathbb{F}\textnormal{Cospan}(\bold{C})$ and $_L \textnormal{Csp}(\bold{D})$ give rise to underlying symmetric monoidal bicategories, namely $\mathbb{F}\textnormal{Cospan}(\bold{C})$ induces a symmetric monoidal bicategory $H(\mathbb{F}\textnormal{Cospan}(\bold{C}))$ which has:
\begin{enumerate}
\item{objects as those of $\bold{C}$,}
\item{morphisms as horizontal 1-cells of $\mathbb{F}\textnormal{Cospan}(\bold{C})$, and}
\item{2-morphisms as globular 2-morphisms of $\mathbb{F}\textnormal{Cospan}(\bold{C})$.}
\end{enumerate} 
Likewise, $_L \textnormal{Csp}(\bold{D})$ induces a symmetric monoidal bicategory $H( {_L \textnormal{Csp}(\bold{D})})$ which has:
\begin{enumerate}
\item{objects as those of $\bold{C}$,}
\item{morphisms as horizontal 1-cells of $_L \textnormal{Csp}(\bold{D})$, and}
\item{2-morphisms as globular 2-morphisms of $_L \textnormal{Csp}(\bold{D})$.}
\end{enumerate}
Another result of Shulman \cite{Shul2} is the following:
\begin{prop}[Shulman, Prop. B.3]
An equivalence of fibrant double categories induces a biequivalence of horizontal bicategories.
\end{prop}
\begin{cor}
The bicategories $H(\mathbb{F}\textnormal{Cospan}(\bold{C}))$ and $H( {_L \textnormal{Csp}(\bold{D})})$ are biequivalent.
\end{cor}
\textbf{Is this biequivalnce symmetric monoidal? Probably}

We can also define the part of the double equivalence $\mathbb{G} \colon \mathbb{F}\textnormal{Cospan}(\bold{C}) \to _L \mathbb{C} \textnormal{sp}(\bold{D})$ which goes in the other direction: again, the object component of this double functor will be $\mathbb{G}_0 = \id_{\bold{C}}$.

Given a horizontal 1-cell $M$ of $\mathbb{F} \textnormal{Cospan}(\bold{C})$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$c_1$};
\node (B) at (1,1) {$c$};
\node (C) at (2,0) {$c_2$};
\node (D) at (1,-0.5) {$d \in F(c)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$I$} (B)
(C) edge node[above]{$O$} (B);
\end{tikzpicture}
\]
the image $\mathbb{G}(M)$ is the horizontal 1-cell in $_L \mathbb{C}\textnormal{sp}(\bold{D})$ given by:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$L(c_1)$};
\node (B) at (1,1) {$d$};
\node (C) at (2,0) {$L(c_2)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$L(I)$} (B)
(C) edge node[right]{$L(O)$} (B);
\end{tikzpicture}
\]
and similarly, given a 2-morphism $(f,h,g,\iota) \colon M \to M^\prime$ of $\mathbb{F} \textnormal{Cospan}(\bold{C})$:
\[
\begin{tikzpicture}[scale=1.5]
\node (D) at (1,0.5) {$d \in F(c)$};
\node (D') at (1,-1.5) {$d^\prime \in F(c^\prime)$};
\node (A) at (0,0) {$c_1$};
\node (B) at (1,0) {$c$};
\node (C) at (2,0) {$c_2$};
\node (A') at (0,-1) {$c_1^\prime$};
\node (B') at (1,-1) {$c^\prime$};
\node (C') at (2,-1) {$c_2^\prime$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$I$} (B)
(C) edge node[above]{$O$} (B)
(A') edge node[above]{$I^\prime$} (B')
(C') edge node[above]{$O^\prime$} (B')
(A) edge node [left]{$f$} (A')
(B) edge node [left]{$h$} (B')
(C) edge node [left]{$g$} (C');
\end{tikzpicture}
\]
$$\iota \colon F(h)(d) \to d^\prime$$
the image in $_L \mathbb{C}\textnormal{sp}(\bold{D})$ is given by the 2-morphism:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$L(c_1)$};
\node (B) at (1,0) {$d$};
\node (C) at (2,0) {$L(c_2)$};
\node (A') at (0,-1) {$L(c_1^\prime)$};
\node (B') at (1,-1) {$d^\prime$};
\node (C') at (2,-1) {$L(c_2^\prime)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$L(I)$} (B)
(C) edge node[above]{$L(O)$} (B)
(A') edge node[above]{$L(I^\prime)$} (B')
(C') edge node[above]{$L(O^\prime)$} (B')
(A) edge node [left]{$L(f)$} (A')
(B) edge node [left]{$\alpha$} (B')
(C) edge node [left]{$L(g)$} (C');
\end{tikzpicture}
\]
where $\alpha \colon d \to d^\prime$ is a morphism in the Grothendieck construction of $F$ given by $\alpha = (h \colon c \to c^\prime, \iota \colon F(h)(d) \to d^\prime)$.

Next, we exhibit natural isomorphisms $\eta \colon \id_{ _L \mathbb{C}\textnormal{sp}(\bold{D})} \cong \mathbb{G} \mathbb{E}$ and $\epsilon \colon \mathbb{E} \mathbb{G} \cong \id_{\mathbb{F}\textnormal{Cospan}(\bold{C})}$. First we compute the composites $\mathbb{G} \mathbb{E}$ and $\mathbb{E} \mathbb{G}$. On the object categories, both composites are $\id_\bold{C}$ and we have natural isomorphism $\eta \colon \id_{\bold{C}} \cong \mathbb{G}_0 \mathbb{E}_0$ and $\epsilon \colon \mathbb{E}_0 \mathbb{G}_0 \cong \id_{\bold{C}}$.

Given a horizontal 1-cell $M$ in $_L \mathbb{C} \textnormal{sp}(\bold{D})$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$L(c_1)$};
\node (B) at (1,1) {$d$};
\node (C) at (2,0) {$L(c_2)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B);
\end{tikzpicture}
\]
the horizontal 1-cell $\mathbb{E}(M)$ is given by:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$c_1$};
\node (B) at (1,1) {$R(d)$};
\node (C) at (2,0) {$c_2$};
\node (D) at (1,-0.5) {$d \in F(R(d))$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$R(i)$} (B)
(C) edge node[right]{$R(o)$} (B);
\end{tikzpicture}
\]
and then the horizontal 1-cell $\mathbb{G} \mathbb{E}(M)$ is given by:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$L(c_1)$};
\node (B) at (1,1) {$d$};
\node (C) at (2,0) {$L(c_2)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$L(R(i))$} (B)
(C) edge node[right]{$L(R(o))$} (B);
\end{tikzpicture}
\]
\textbf{What can we say about LR? Find a 2-iso between these in $_L Csp(D)$.}
Then we can find a 2-isomorphism $\eta \colon M \xrightarrow{\sim} \mathbb{G}\mathbb{E}(M) $ in $_L \mathbb{C} \textnormal{sp}(\bold{C})$ given by:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$L(c_1)$};
\node (B) at (1,0) {$d$};
\node (C) at (2,0) {$L(c_2)$};
\node (A') at (0,-1) {$L(c_1)$};
\node (B') at (1,-1) {$d$};
\node (C') at (2,-1) {$L(c_2)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B)
(A') edge node[above]{$L(R(i))$} (B')
(C') edge node[above]{$L(R(o))$} (B')
(A) edge node [left]{$1$} (A')
(B) edge node [left]{$1$} (B')
(C) edge node [left]{$1$} (C');
\end{tikzpicture}
\]

On the other hand, given a horizontal 1-cell $N$ in $\mathbb{F}\textnormal{Cospan}(\bold{C})$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$c_1$};
\node (B) at (1,1) {$c$};
\node (C) at (2,0) {$c_2$};
\node (D) at (1,-0.5) {$d \in F(c)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$I$} (B)
(C) edge node[right]{$O$} (B);
\end{tikzpicture}
\]
the horizontal 1-cell $\mathbb{G}(N)$ is given by:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$L(c_1)$};
\node (B) at (1,1) {$d$};
\node (C) at (2,0) {$L(c_2)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$L(I)$} (B)
(C) edge node[right]{$L(O)$} (B);
\end{tikzpicture}
\]
and then the horizontal 1-cell $\mathbb{E} \mathbb{G}(N)$ is given by:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$c_1$};
\node (B) at (1,1) {$R(d)$};
\node (C) at (2,0) {$c_2$};
\node (D) at (1,-0.5) {$d \in F(R(d))$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$R(L(I))$} (B)
(C) edge node[right]{$R(L(O))$} (B);
\end{tikzpicture}
\]
Then we can find a 2-isomorphism $\epsilon \colon \mathbb{E} \mathbb{G} (N) \xrightarrow{\sim} N$ in $\mathbb{F}\textnormal{Cospan}(\bold{C})$ given by:
\[
\begin{tikzpicture}[scale=1.5]
\node (D) at (1,0.5) {$d \in F(R(d))$};
\node (D') at (1,-1.5) {$d \in F(c)$};
\node (A) at (0,0) {$c_1$};
\node (B) at (1,0) {$R(d)$};
\node (C) at (2,0) {$c_2$};
\node (A') at (0,-1) {$c_1$};
\node (B') at (1,-1) {$c$};
\node (C') at (2,-1) {$c_2$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$R(L(I))$} (B)
(C) edge node[above]{$R(L(O))$} (B)
(A') edge node[above]{$I$} (B')
(C') edge node[above]{$O$} (B')
(A) edge node [left]{$1$} (A')
(B) edge node [left]{$e$} (B')
(C) edge node [left]{$1$} (C');
\end{tikzpicture}
\]
$$\iota \colon F(e)(d) \to d$$
where $R(L(I))=I$ and $R(L(O))=O$ since $L \colon \bold{C} \to \bold{D} \cong \int{F}$ is a left adjoint with right adjoint $R \colon \int{F} \to \bold{C}$ as its inverse.
\section{An example}
As an example, let $L \colon \bold{FinSet} \to \bold{Graph}$ be the functor which is left adjoint to the forgetful functor $R \colon \bold{Graph} \to \bold{FinSet}$; the functor $L$ maps a finite set $N$ to the discrete graph with $N$ as its set of vertices and no edges. Since $\bold{Graph}$ is a topos and thus has finite colimits, we can then obtain a symmetric monoidal double category $_L \mathbb{C}\textnormal{sp}(\bold{Graph})$ which has:
\begin{enumerate}
\item{finite sets as objects,}
\item{functions as vertical 1-morphisms,}
\item{cospans of graphs of the form
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$L(N)$};
\node (B) at (1,1) {$M$};
\node (C) at (2,0) {$L(N^\prime)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B);
\end{tikzpicture}
\]
as horizontal 1-cells, where $L(N)$ and $L(N^\prime)$ are discrete graphs on the sets $N$ and $N^\prime$, respectively, $M$ is a graph and $i$ and $o$ are graph morphisms, and}
\item{maps of cospans of graphs of the form
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$L(N_1)$};
\node (B) at (1,0) {$M$};
\node (C) at (2,0) {$L(N_2)$};
\node (A') at (0,-1) {$L(N_1^\prime)$};
\node (B') at (1,-1) {$M^\prime$};
\node (C') at (2,-1) {$L(N_2^\prime)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B)
(A') edge node[above]{$i^\prime$} (B')
(C') edge node[above]{$o^\prime$} (B')
(A) edge node [left]{$L(f)$} (A')
(B) edge node [left]{$h$} (B')
(C) edge node [left]{$L(g)$} (C');
\end{tikzpicture}
\]
as 2-morphisms, where $L(f)$ and $L(g)$ are maps of discrete graphs given by the underlying functions $f$ and $g$, respectively, and $h \colon M \to M^\prime$ is a graph morphism.
}
\end{enumerate}

On the other hand, let $F \colon \bold{FinSet} \to \bold{Cat}$ be the symmetric lax monoidal pseudofunctor that assigns to a finite set $N$ the \emph{category} of all graph structures whose underlying set of vertices is $N$. Using Theorem \ref{main1}, we can then obtain a symmetric monoidal double category $\mathbb{F}\textnormal{Cospan}(\bold{FinSet})$ which has:
\begin{enumerate}
\item{finite sets as objects,}
\item{functions as vertical 1-morphisms,}
\item{horizontal 1-cells are given by pairs:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$N_1$};
\node (B) at (1,1) {$N$};
\node (C) at (2,0) {$N_2$};
\node (D) at (3,0.5) {$M \in F(N)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B);
\end{tikzpicture}
\]
and}
\item{2-morphisms as maps of cospans 
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$N_1$};
\node (A') at (0,-1) {$N_1^\prime$};
\node (C') at (2,-1) {$N_2^\prime$};
\node (B) at (1,0) {$N$};
\node (C) at (2,0) {$N_2$};
\node (D) at (1,-1) {$N^\prime$};
\node (E) at (3,0) {$M \in F(N)$};
\node (F) at (3,-1) {$M^\prime \in F(N^\prime)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B)
(A) edge node[left]{$f$} (A')
(C) edge node[right]{$g$} (C')
(C') edge node [above] {$o^\prime$} (D)
(A') edge node [above] {$i^\prime$} (D)
(B) edge node [left] {$h$} (D);
\end{tikzpicture}
\]
together with a graph morphism $\iota \colon F(h)(M) \to M^\prime$ in $F(N^\prime)$.}
\end{enumerate}
We thus have two symmetric monoidal double categories: $_L \mathbb{C}\textnormal{sp}(\bold{Graph})$ obtained from structured cospans and $\mathbb{F}\textnormal{Cospan}(\bold{FinSet})$ using Theorem \ref{main1}. These two double categories are in fact equivalent as symmetric monoidal double categories which we now show.

Define a double functor $\mathbb{E} \colon _L \mathbb{C}\textnormal{sp}(\bold{Graph}) \to \mathbb{F}\textnormal{Cospan}(\bold{FinSet})$ as follows: $\mathbb{E}_0=\id_{\bold{FinSet}}$ as both double categories $_L \mathbb{C}\textnormal{sp}(\bold{Graph})$ and $\mathbb{F}\textnormal{Cospan}(\bold{FinSet})$ have $\bold{FinSet}$ as their category of objects. The identity functor on $\bold{FinSet}$ is trivially an equivalence. For the arrow component $\mathbb{E}_1$, given a horizontal 1-cell of $_L \mathbb{C}\textnormal{sp}(\bold{Graph})$, which is a cospan in $\bold{Graph}$ of the form:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$L(N)$};
\node (B) at (1,1) {$M$};
\node (C) at (2,0) {$L(N^\prime)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B);
\end{tikzpicture}
\]
the functor $\mathbb{E}_1$ maps this horizontal 1-cell to the horizontal 1-cell of $\mathbb{F}\textnormal{Cospan}(\bold{FinSet})$ given by:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$N$};
\node (B) at (1,1) {$R(M)$};
\node (C) at (2,0) {$N^\prime$};
\node (D) at (3,0.5) {$M \in F(R(M))$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$R(i)$} (B)
(C) edge node[right]{$R(o)$} (B);
\end{tikzpicture}
\]
where $R \colon \bold{Graph} \to \bold{FinSet}$ is the forgetful functor, right adjoint to $L \colon \bold{FinSet} \to \bold{Graph}$. The image of a 2-morphism in $_L \mathbb{C}\textnormal{sp}(\bold{Graph})$ given by:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$L(N_1)$};
\node (B) at (1,0) {$M$};
\node (C) at (2,0) {$L(N_2)$};
\node (A') at (0,-1) {$L(N_1^\prime)$};
\node (B') at (1,-1) {$M^\prime$};
\node (C') at (2,-1) {$L(N_2^\prime)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B)
(A') edge node[above]{$i^\prime$} (B')
(C') edge node[above]{$o^\prime$} (B')
(A) edge node [left]{$L(f)$} (A')
(B) edge node [left]{$h$} (B')
(C) edge node [left]{$L(g)$} (C');
\end{tikzpicture}
\]
is the 2-morphism in $\mathbb{F}\textnormal{Cospan}(\bold{FinSet})$ given by:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$N_1$};
\node (B) at (1,0) {$R(M)$};
\node (C) at (2,0) {$N_2$};
\node (A') at (0,-1) {$N_1^\prime$};
\node (B') at (1,-1) {$R(M^\prime)$};
\node (C') at (2,-1) {$N_2^\prime$};
\node (D) at (4,0) {$F(R(M))$};
\node (D') at (4,-1) {$F(R(M^\prime))$};
\node (E) at (3,-0.5) {$1$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$R(i)$} (B)
(C) edge node[above]{$R(o)$} (B)
(A') edge node[above]{$R(i^\prime)$} (B')
(C') edge node[above]{$R(o^\prime)$} (B')
(A) edge node [left]{$f$} (A')
(B) edge node [left]{$R(h)$} (B')
(C) edge node [left]{$g$} (C')
(E) edge node [above] {$M$} (D)
(E) edge node [below] {$M^\prime$} (D')
(D) edge node [right] {$F(R(h))$} (D');
\end{tikzpicture}
\]
together with a graph morphism $\iota_h \colon F(R(h))(M) \to M^\prime$. Denoting a cospan by its apex, the map $$\mathbb{E}_1 \colon { _f { _L \mathbb{C}\textnormal{sp}(\bold{Graph})}_g} (M,M^\prime) \to { _{\mathbb{E}(f)} \mathbb{F}\textnormal{Cospan}(\bold{FinSet})_{\mathbb{E}(g)}}(\mathbb{E}(M),\mathbb{E}(M^\prime))$$ is bijective and thus the double functor $\mathbb{E}$ is full and faithful. To see that it is also essentially surjective, given a horizontal 1-cell in $\mathbb{F}\textnormal{Cospan}(\bold{FinSet})$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$N_1$};
\node (B) at (1,1) {$N$};
\node (C) at (2,0) {$N_2$};
\node (D) at (3,0.5) {$M \in F(N)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B);
\end{tikzpicture}
\]
there exists a horizontal 1-cell in $_L \mathbb{C}\textnormal{sp}(\bold{Graph})$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$L(N_1)$};
\node (B) at (1,1) {$M$};
\node (C) at (2,0) {$L(N_2)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i^\prime$} (B)
(C) edge node[above]{$o^\prime$} (B);
\end{tikzpicture}
\]
and a 2-isomorphism in $\mathbb{F}\textnormal{Cospan}(\bold{FinSet})$ from the image of the latter horizontal 1-cell to the former given by:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$N_1$};
\node (B) at (1,0) {$R(M)$};
\node (C) at (2,0) {$N_2$};
\node (A') at (0,-1) {$N_1$};
\node (B') at (1,-1) {$N$};
\node (C') at (2,-1) {$N_2$};
\node (D) at (3.5,0) {$M \in F(R(M))$};
\node (D') at (3.5,-1) {$M \in F(N)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$R(i^\prime)$} (B)
(C) edge node[above]{$R(o^\prime)$} (B)
(A') edge node[above]{$i$} (B')
(C') edge node[above]{$o$} (B')
(A) edge node [left]{$1$} (A')
(B) edge node [left]{$1$} (B')
(C) edge node [left]{$1$} (C');
\end{tikzpicture}
\]
$$\iota = \id_{M} \colon F(R(M)) \to M$$ 
which trivially commutes as $R(M)=N$ and $R(i^\prime)$ and $R(o^\prime)$ are the underlying maps of vertices of the graph morphisms $i^\prime$ and $o^\prime$ which act as the functions $i$ and $o$, respectively. Given two composable horizontal 1-cells $\alpha$ and $\beta$ of $_L \mathbb{C}\textnormal{sp}(\bold{Graph})$: 
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$L(N_1)$};
\node (B) at (1,1) {$M$};
\node (C) at (2,0) {$L(N_2)$};
\node (D) at (3,0) {$L(N_2)$};
\node (E) at (4,1) {$M^\prime$};
\node (F) at (5,0) {$L(N_3)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$i_1$} (B)
(C) edge node[right]{$o_1$} (B)
(D) edge node[left]{$i_2$} (E)
(F) edge node[right]{$o_2$} (E);
\end{tikzpicture}
\]
we have a natural isomorphism $\mathbb{E}_{\alpha,\beta} \colon \mathbb{E}(\alpha) \odot \mathbb{E}(\beta) \to \mathbb{E}(\alpha \odot \beta)$ given by: 
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$N_1$};
\node (B) at (2,0) {$R(M)+_{N_2} R(M^\prime)$};
\node (C) at (4,0) {$N_3$};
\node (A') at (0,-1) {$N_1$};
\node (B') at (2,-1) {$R(M +_{L(N_2)} M^\prime)$};
\node (C') at (4,-1) {$N_3$};
\node (D) at (6.5,0) {$M+_{L(N_2)}M^\prime \in F(R(M) +_{N_2} R(M^\prime))$};
\node (D') at (6.5,-1) {$M +_{L(N_2)} M^\prime \in F(R(M+_{L(N_2)} M^\prime))$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$j \psi R(i_1)$} (B)
(C) edge node[above]{$j \psi R(o_2)$} (B)
(A') edge node[above]{$U(i^\prime)$} (B')
(C') edge node[above]{$U(o^\prime)$} (B')
(A) edge node [left]{$1$} (A')
(B) edge node [left]{$$} (B')
(C) edge node [left]{$1$} (C');
\end{tikzpicture}
\]
The right adjoint $R \colon \textrm{Graph} \to \textrm{Set}$ is also a left adjoint $R \dashv K$ to the codiscrete graph functor $K \colon \textrm{Set} \to \textrm{Graph}$ which sends a finite set $N$ to the complete graph with $N$ as its underlying set of vertices. The functor $R \colon \textrm{Graph} \to \textrm{Set}$ thus also preserves colimits which yields an isomorphism $$ R(M +_{L(N_2)} M^\prime) \cong R(M) +_{R(L(N_2))} R(M^\prime)$$ and again we make use of the fact that the left adjoint $L \colon \textrm{Set} \to \textrm{Graph}$ is fully faithful and thus the unit $$\eta_{N_2} \colon N_2 \to R(L(N_2))$$ is an isomorphism which gives $$R(M +_{L(N_2)} M^\prime) \cong R(M) +_{R(L(N_2))} R(M^\prime) \cong R(M) +_{N_2} R(M^\prime).$$ Thus the double functor $\mathbb{E} \colon _L \mathbb{C}\textnormal{sp}(\bold{Graph}) \to \mathbb{F}\textnormal{Cospan}(\bold{Set})$ is strong and we  have an equivalence of double categories $_L \mathbb{C}\textnormal{sp}(\textrm{Graph}) \sim \mathbb{F}\textrm{Cospan}(\textrm{Set})$. Moreover, each of these categories is symmetric monoidal and the double functor $\mathbb{E}$ is symmetric monoidal; first, we have that the following diagrams commute.
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$_L \mathbb{C} \textnormal{sp}(\textrm{Graph})_1$};
\node (B) at (4,0) {$\mathbb{F}\textnormal{Cospan}(\textrm{FinSet})_1$};
\node (C) at (0,-1) {$_L \mathbb{C}\textnormal{sp}(\textrm{FinGraph)}_0 = \textrm{FinSet}$};
\node (D) at (4,-1) {$\mathbb{F} \textnormal{Cospan}(\textrm{FinSet})_0 = \textrm{FinSet}$};
\node (A') at (0,-2) {$_L \mathbb{C} \textnormal{sp}(\textrm{Graph})_1$};
\node (B') at (4,-2) {$\mathbb{F}\textnormal{Cospan}(\textrm{FinSet})_1$};
\node (C') at (0,-3) {$_L \mathbb{C}\textnormal{sp}(\textrm{Graph)}_0 = \textrm{FinSet}$};
\node (D') at (4,-3) {$\mathbb{F} \textnormal{Cospan}(\textrm{FinSet})_0 = \textrm{FinSet}$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$\mathbb{E}_1$} (B)
(A) edge node[left]{$S$} (C)
(C) edge node[above]{$\mathbb{E}_0=\id_{\textrm{FinSet}}$} (D)
(B) edge node[right]{$S$} (D)
(A') edge node [above]{$\mathbb{E}_1$} (B')
(A') edge node [left]{$T$} (C')
(C') edge node [above]{$\mathbb{E}_0=\id_{\textrm{FinSet}}$} (D')
(B') edge node [right] {$T$} (D');
\end{tikzpicture}
\]
Both diagrams are similar: focusing on the top one and starting with an object of $_L \mathbb{C}\textnormal{sp}(\textrm{Graph})_1$ which is a cospan in $\textrm{Graph}$ of the form:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$L(N)$};
\node (B) at (1,1) {$M$};
\node (C) at (2,0) {$L(N_2)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B);
\end{tikzpicture}
\]
the functor $\mathbb{E}_1$ then maps this horizontal 1-cell to the horizontal 1-cell in $\mathbb{F}\textnormal{Cospan}(\textrm{FinSet})$ which is given by the pair:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$N_1$};
\node (B) at (1,1) {$R(M)$};
\node (C) at (2,0) {$N_2$};
\node (D) at (3,0.5) {$M \in F(R(M))$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$R(i)$} (B)
(C) edge node[right]{$R(o)$} (B);
\end{tikzpicture}
\]
and the source of this horizontal 1-cell is the object $N_1 \in \textrm{FinSet}$. Going the other way around the diagram also yields $N_1$. A morphism in $_L \mathbb{C} \textnormal{sp}(\textrm{Graph})_1$ given by a map of cospans in $\textrm{Graph}$ of the form:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$L(N_1)$};
\node (B) at (1,0) {$M$};
\node (C) at (2,0) {$L(N_2)$};
\node (A') at (0,-1) {$L(N_1^\prime)$};
\node (B') at (1,-1) {$M^\prime$};
\node (C') at (2,-1) {$L(N_2^\prime)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i_1$} (B)
(C) edge node[above]{$o_1$} (B)
(A') edge node[above]{$i_2$} (B')
(C') edge node[above]{$o_2$} (B')
(A) edge node [left]{$L(f)$} (A')
(B) edge node [left]{$h$} (B')
(C) edge node [left]{$L(g)$} (C');
\end{tikzpicture}
\]
maps under the functor $\mathbb{E}_1$ to:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$N_1$};
\node (B) at (1,0) {$R(M)$};
\node (C) at (2,0) {$N_2$};
\node (A') at (0,-1) {$N_1^\prime$};
\node (B') at (1,-1) {$R(M^\prime)$};
\node (C') at (2,-1) {$N_2^\prime$};
\node (D) at (3,0) {$M \in F(R(M))$};
\node (D') at (3,-1) {$M^\prime \in F(R(M^\prime)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$R(i_1)$} (B)
(C) edge node[above]{$R(o_1)$} (B)
(A') edge node[above]{$R(i_2)$} (B')
(C') edge node[above]{$R(o_2)$} (B')
(A) edge node [left]{$f$} (A')
(B) edge node [left]{$R(h)$} (B')
(C) edge node [left]{$g$} (C');
\end{tikzpicture}
\]
together with a morphism $\iota \colon F(R(h))(M) \to M^\prime$ in $\textrm{Graph}$ which is really just the morphism $h \in \textrm{Graph}$. The source of this morphism is then the morphism $f \in \textrm{FinSet}$, compared with going the other way around the diagram which also results in $f$ and thus both of these squares commute.

\section{Acknowledgements}
Dr. Baez, Daniel Cicala...
\begin{thebibliography}{100}

\bibitem{BC} J.\ C.\ Baez and K.\ Courser, Coarse-graining open Markov processes. Available as \href{https://arxiv.org/abs/1710.11343}{arXiv:1710.11343}.

\bibitem{BC2} J.\ C.\ Baez and K.\ Courser, Structured cospans. In preparation.

\bibitem{BCR} J.\ C.\ Baez, B.\ Coya and F.\ Rebro, Props in circuit theory. In preparation. THIS IS FINISHED!!!

\bibitem{BF} J.\ C.\ Baez and B.\ Fong, A compositional framework for passive linear networks. Available as \href{http://arxiv.org/abs/1504.05625}{arXiv:1504.05625}.

\bibitem{BFP} J.\ C.\ Baez, B.\ Fong and B.\ Pollard, A compositional framework for Markov processes, \textsl{Jour. Math. Phys.} \textbf{57} (2016), 033301. Available as \href{http://arxiv.org/abs/1508.06448}{arXiv:1508.06448}.

\bibitem{BP} J.\ C.\ Baez and B.\ Pollard, A compositional framework for chemical reaction networks, in preparation.

\bibitem{Brown1} R.\ Brown and C.\ B.\ Spencer, Double groupoids and crossed modules, 
\textsl{Cah.\ Top.\ G\'eom.\ Diff.} \textbf{17} (1976), 343--362.

\bibitem{Brown2} R.\ Brown, K.\ Hardie, H.\ Kamps and T.\ Porter, The homotopy double groupoid of a Hausdorff space, \textsl{Th.\ Appl.\ Categ.} \textbf{10} (2002), 71--93.

%\bibitem{Be} J.\ B\'enabou, Introduction to bicategories, in {\sl Reports
%of the Midwest Category Seminar}, Lecture Notes in Mathematics, vol.\ \textbf{47}, Springer, Berlin, 1967, pp.\ 1--77.

%\bibitem{Brown1} R.\ Brown and C.\ B.\ Spencer, Double groupoids and crossed modules, 
%\textsl{Cah.\ Top.\ G\'eom.\ Diff.} \textbf{17} (1976), 343--362.

%\bibitem{Brown2} R.\ Brown, K.\ Hardie, H.\ Kamps and T.\ Porter, The homotopy double groupoid of a Hausdorff space, \textsl{Th.\ Appl.\ Categ.} \textbf{10} (2002), 71--93.

%\bibitem{CC} D.\ Cicala and K.\ Courser, Spans of cospans in a topos. Available as \href{https://arxiv.org/abs/1707.02098}{arXiv:1707.02098}.

\bibitem{Cour} K.\ Courser, A bicategory of decorated cospans, \emph{Theor.\ Appl.\ Cat.} \textbf{32} (2017), 995--1027. Also available as \href{https://arxiv.org/abs/1605.08100}{arXiv:1605.08100}.

%\bibitem{Ehresmann63} C.\ Ehresmann, Cat\'egories structur\'ees III: Quintettes et applications covariantes,  \textsl{Cah.\ Top.\ G\'eom.\ Diff.} \textbf{5} (1963), 1--22.

%\bibitem{Ehresmann65} C.\ Ehresmann, {\sl Cat\'egories et Structures,} Dunod, Paris, 1965.

\bibitem{Ehresmann63} C.\ Ehresmann, Cat\'egories structur\'ees III: Quintettes et applications covariantes,  \textsl{Cah.\ Top.\ G\'eom.\ Diff.} \textbf{5} (1963), 1--22.

\bibitem{Ehresmann65} C.\ Ehresmann, {\sl Cat\'egories et Structures,} Dunod, Paris, 1965.

\bibitem{Fong} B.\ Fong, Decorated cospans, \emph{Theor.\ Appl.\ Cat.} \textbf{30} (2015), 1096--1120. Also available as \href{http://arxiv.org/abs/1502.00872}{arXiv:1502.00872}.

%\bibitem{GP1} M.\ Grandis and R.\ Par\'e, Limits in double categories, \textsl{Cah.\ Top.\ G\'eom.\ Diff.} \textbf{40} (1999), 162--220.

%\bibitem{GP2} M.\ Grandis and R.\ Par\'e, Adjoints for double categories, 
% \textsl{Cah.\ Top.\ G\'eom.\ Diff.} \textbf{45} (2004), 193--240.

%\bibitem{Haug} R.\ Haugseng, Iterated spans and ``classical" topological field theories. Available as \href{https://arxiv.org/abs/1409.0837}{arXiv:1409.0837}.

%\bibitem{Hoff} A.\ Hoffnung, Spans in 2-categories: a monoidal tricategory. Available as \href{http://arxiv.org/abs/1112.0560}{arXiv:1112.0560}.

\bibitem{JM} J.\ C.\ Baez and J.\ Master, A compositional framework for Petri nets. In preparation.

\bibitem{LS} E.\ Lerman and D.\ Spivak, An algebra of open continuous time dynamical systems and networks. Available as \href{http://arxiv.org/abs/1602.01017}{arXiv:1602.01017}.

%\bibitem{Lack} S.\ Lack, Limits for lax morphisms, \emph{Applied Categorical Structures} $\bold{30}$ (2005), 189--203. Available %at \href{http://maths.mq.edu.au/~slack/papers/talgl.pdf}{http://maths.mq.edu.au/$\sim$slack/papers/talgl.pdf}.

   %\bibitem{Lerm} E.\ Lerman and D.\ Spivak, An algebra of open continuous time dynamical systems and networks. Available as %%\href{http://arxiv.org/abs/1602.01017}{arXiv:1602.01017}.

%   \bibitem{ML} S.\ Mac Lane, {\sl Categories for the Working Mathematician},
%     Springer, Berlin, 1998.

%\bibitem{Pol} B.\ Pollard, Open Markov processes: A compositional perspective on non-equilibrium steady states in biology, %%%\emph{Entropy} $\bold{18}$ (2016), 140. Available as \href{http://arxiv.org/abs/1601.00711}{arXiv:1601.00711}.

%\bibitem{Nie}
%S.~Niefield,
%Span, cospan, and other double categories.
%\textsl{Theory Appl.\ Categ.}
%\textbf{26} (2012), 729--742.
%Available as \href{https://arxiv.org/abs/1201.3789}{arXiv:1201.3789}.

%\bibitem{Panan} F.\ Clerc, H.\ Humphrey and P.\ Panangaden, Bicategories of Markov processes,  to appear.

%\bibitem{RSW} R.\ Rosebrugh, N.\ Sabadini and R.\ F.\ C.\ Walters, Generic commutative separable algebras and cospans of graphs, \textsl{Theory Appl. Categ.} \textbf{15} (2005), 164--177. Available at \href{http:/.www.tac.mta.ca/tac/volumes/15/6/15-06.pdf}{http:/.www.tac.mta.ca/tac/volumes/15/6/15-06.pdf}.

%\bibitem{Reb} F.\ Rebro, Constructing the bicategory Span$_{2}(\bold{C})$. Available as \href{https://arxiv.org/abs/1501.00792}{arXiv:1501.00792}.

\bibitem{Shul} M.\ Shulman, Constructing symmetric monoidal bicategories. Available as \href{http://arxiv.org/abs/1004.0993}{arXiv:1004.0993}.

\bibitem{Shul2} M.\ Shulman, Framed bicategories and monoidal fibrations. Available as \href{https://arxiv.org/abs/0706.1286}{arXiv:0706.1286}.

%\bibitem{Stay} M.\ Stay, Compact closed bicategories.  Available as \href{http://arxiv.org/abs/1301.1053}{arXiv:1301.1053}.

\bibitem{Yass} A.\ Yassine, Open Systems in Classical Mechanics. Available as \href{https://arxiv.org/abs/1710.11392}{arXiv:1710.11392}.

\end{thebibliography}
\end{document}

### 2018-09-27 EquivCompFrameworks_20180911kc.tex
initial2

@@
 \section{Introduction}
+
+HELLO ALL!
+
 Networks are playing an increasingly prominent role in our understanding of the world and as a result, methods of characterizing and studying networks have become evermore necessary.

### 2018-09-27 EquivCompFrameworks_20180911kc.tex
tiny
initial3
made it! and preamble

@@
 % 2019/09/11 - KC
-
 \documentclass{amsart}
-\usepackage{amssymb,amsmath,stmaryrd,txfonts,mathrsfs,amsthm}
-
-\usepackage[all,2cell]{xy}
-\usepackage[neveradjust]{paralist}
-\usepackage{hyperref}
-\usepackage{mathtools}
-\usepackage{multirow}
-\usepackage[outline]{contour}
-\contourlength{1.2pt}
-\usepackage{tikz}
-\usepackage{tikz-cd}
-\usepackage{xcolor}
-\usepackage{framed,color}
-\usepackage[draft]{fixme}
-\usetikzlibrary{matrix,arrows,decorations.pathmorphing,positioning}
-\usetikzlibrary{intersections,decorations.markings}
-\usetikzlibrary{arrows,positioning,fit,matrix,shapes.geometric,external}
-\usetikzlibrary{backgrounds,circuits,circuits.ee.IEC,shapes,fit,matrix}
-\usepackage{tikz}
-\usepackage[all,2cell]{xy}
-\usetikzlibrary{matrix,arrows}
-\definecolor{rewritecolor}{rgb}{0,.9,1}
-\tikzset{rewritenode/.style={shape=circle,fill=rewritecolor,scale=0.25,font=\Huge}}
-\tikzset{RWopen/.style={shape=circle,draw=black,fill=white,scale=0.5,font=\Huge}}
-\tikzset{RWclosed/.style={shape=circle,fill=black,scale=0.5,font=\Huge}}
-\tikzset{CDnode/.style={shape=circle,fill=white,scale=.5}}
-\makeatletter
-\let\ea\expandafter
-
-\pgfdeclarelayer{edgelayer}
-\pgfdeclarelayer{nodelayer}
-\pgfsetlayers{edgelayer,nodelayer,main}
-
-% Petri nets
-\definecolor{lblue}{rgb}{0,250,255}
-\tikzstyle{species}=[circle,fill=yellow,draw=black,scale=1.15]
-\tikzstyle{transition}=[rectangle,fill=lblue,draw=black,scale=1.15]
-\tikzstyle{inarrow}=[->, >=stealth, shorten >=.03cm,line width=1.5]
-\tikzstyle{empty}=[circle,fill=none, draw=none]
-\tikzstyle{inputdot}=[circle,fill=purple,draw=purple, scale=.25]
-\tikzstyle{inputarrow}=[->,draw=purple, shorten >=.05cm]
-\tikzstyle{simple}=[-,draw=purple,line width=1.000]
-\tikzstyle{none}=[inner sep=0pt]
-
-\definecolor{shadecolor}{rgb}{1,0.8,0.3}
-\definecolor{myurlcolor}{rgb}{0.6,0,0}
-\definecolor{mycitecolor}{rgb}{0,0,0.8}
-\definecolor{myrefcolor}{rgb}{0,0,0.8}
-\hypersetup{colorlinks, linkcolor=myrefcolor, citecolor=mycitecolor, urlcolor=myurlcolor}
-
-\tikzset{->-/.style={decoration={
-  markings,
-  mark=at position .5 with {\arrow{>}}},postaction={decorate}}}
-
-%% Defining commands that are always in math mode.
-\def\mdef#1#2{\ea\ea\ea\gdef\ea\ea\noexpand#1\ea{\ea\ensuremath\ea{#2}}}
-\def\alwaysmath#1{\ea\ea\ea\global\ea\ea\ea\let\ea\ea\csname your@#1\endcsname\csname #1\endcsname
-  \ea\def\csname #1\endcsname{\ensuremath{\csname your@#1\endcsname}}}
-
-\newcommand{\define}[1]{{\bf \boldmath{#1}}}
-
-% Script letters
-\newcommand{\sA}{\ensuremath{\mathscr{A}}}
-\newcommand{\sB}{\ensuremath{\mathscr{B}}}
-\newcommand{\sC}{\ensuremath{\mathscr{C}}}
-\newcommand{\sD}{\ensuremath{\mathscr{D}}}
-\newcommand{\sE}{\ensuremath{\mathscr{E}}}
-\newcommand{\sF}{\ensuremath{\mathscr{F}}}
-\newcommand{\sG}{\ensuremath{\mathscr{G}}}
-\newcommand{\sH}{\ensuremath{\mathscr{H}}}
-\newcommand{\sI}{\ensuremath{\mathscr{I}}}
-\newcommand{\sJ}{\ensuremath{\mathscr{J}}}
-\newcommand{\sK}{\ensuremath{\mathscr{K}}}
-\newcommand{\sL}{\ensuremath{\mathscr{L}}}
-\newcommand{\sM}{\ensuremath{\mathscr{M}}}
-\newcommand{\sN}{\ensuremath{\mathscr{N}}}
-\newcommand{\sO}{\ensuremath{\mathscr{O}}}
-\newcommand{\sP}{\ensuremath{\mathscr{P}}}
-\newcommand{\sQ}{\ensuremath{\mathscr{Q}}}
-\newcommand{\sR}{\ensuremath{\mathscr{R}}}
-\newcommand{\sS}{\ensuremath{\mathscr{S}}}
-\newcommand{\sT}{\ensuremath{\mathscr{T}}}
-\newcommand{\sU}{\ensuremath{\mathscr{U}}}
-\newcommand{\sV}{\ensuremath{\mathscr{V}}}
-\newcommand{\sW}{\ensuremath{\mathscr{W}}}
-\newcommand{\sX}{\ensuremath{\mathscr{X}}}
-\newcommand{\sY}{\ensuremath{\mathscr{Y}}}
-\newcommand{\sZ}{\ensuremath{\mathscr{Z}}}
-
-% Calligraphic letters
-\newcommand{\cA}{\ensuremath{\mathcal{A}}}
-\newcommand{\cB}{\ensuremath{\mathcal{B}}}
-\newcommand{\cC}{\ensuremath{\mathcal{C}}}
-\newcommand{\cD}{\ensuremath{\mathcal{D}}}
-\newcommand{\cE}{\ensuremath{\mathcal{E}}}
-\newcommand{\cF}{\ensuremath{\mathcal{F}}}
-\newcommand{\cG}{\ensuremath{\mathcal{G}}}
-\newcommand{\cH}{\ensuremath{\mathcal{H}}}
-\newcommand{\cI}{\ensuremath{\mathcal{I}}}
-\newcommand{\cJ}{\ensuremath{\mathcal{J}}}
-\newcommand{\cK}{\ensuremath{\mathcal{K}}}
-\newcommand{\cL}{\ensuremath{\mathcal{L}}}
-\newcommand{\cM}{\ensuremath{\mathcal{M}}}
-\newcommand{\cN}{\ensuremath{\mathcal{N}}}
-\newcommand{\cO}{\ensuremath{\mathcal{O}}}
-\newcommand{\cP}{\ensuremath{\mathcal{P}}}
-\newcommand{\cQ}{\ensuremath{\mathcal{Q}}}
-\newcommand{\cR}{\ensuremath{\mathcal{R}}}
-\newcommand{\cS}{\ensuremath{\mathcal{S}}}
-\newcommand{\cT}{\ensuremath{\mathcal{T}}}
-\newcommand{\cU}{\ensuremath{\mathcal{U}}}
-\newcommand{\cV}{\ensuremath{\mathcal{V}}}
-\newcommand{\cW}{\ensuremath{\mathcal{W}}}
-\newcommand{\cX}{\ensuremath{\mathcal{X}}}
-\newcommand{\cY}{\ensuremath{\mathcal{Y}}}
-\newcommand{\cZ}{\ensuremath{\mathcal{Z}}}
-
-% blackboard bold letters
-\newcommand{\lA}{\ensuremath{\mathbb{A}}}
-\newcommand{\lB}{\ensuremath{\mathbb{B}}}
-\newcommand{\lC}{\ensuremath{\mathbb{C}}}
-\newcommand{\lD}{\ensuremath{\mathbb{D}}}
-\newcommand{\lE}{\ensuremath{\mathbb{E}}}
-\newcommand{\lF}{\ensuremath{\mathbb{F}}}
-\newcommand{\lG}{\ensuremath{\mathbb{G}}}
-\newcommand{\lH}{\ensuremath{\mathbb{H}}}
-\newcommand{\lI}{\ensuremath{\mathbb{I}}}
-\newcommand{\lJ}{\ensuremath{\mathbb{J}}}
-\newcommand{\lK}{\ensuremath{\mathbb{K}}}
-\newcommand{\lL}{\ensuremath{\mathbb{L}}}
-\newcommand{\lM}{\ensuremath{\mathbb{M}}}
-\newcommand{\lN}{\ensuremath{\mathbb{N}}}
-\newcommand{\lO}{\ensuremath{\mathbb{O}}}
-\newcommand{\lP}{\ensuremath{\mathbb{P}}}
-\newcommand{\lQ}{\ensuremath{\mathbb{Q}}}
-\newcommand{\lR}{\ensuremath{\mathbb{R}}}
-\newcommand{\lS}{\ensuremath{\mathbb{S}}}
-\newcommand{\lT}{\ensuremath{\mathbb{T}}}
-\newcommand{\lU}{\ensuremath{\mathbb{U}}}
-\newcommand{\lV}{\ensuremath{\mathbb{V}}}
-\newcommand{\lW}{\ensuremath{\mathbb{W}}}
-\newcommand{\lX}{\ensuremath{\mathbb{X}}}
-\newcommand{\lY}{\ensuremath{\mathbb{Y}}}
-\newcommand{\lZ}{\ensuremath{\mathbb{Z}}}
-
-% bold letters
-\newcommand{\bA}{\ensuremath{\mathbf{A}}}
-\newcommand{\bB}{\ensuremath{\mathbf{B}}}
-\newcommand{\bC}{\ensuremath{\mathbf{C}}}
-\newcommand{\bD}{\ensuremath{\mathbf{D}}}
-\newcommand{\bE}{\ensuremath{\mathbf{E}}}
-\newcommand{\bF}{\ensuremath{\mathbf{F}}}
-\newcommand{\bG}{\ensuremath{\mathbf{G}}}
-\newcommand{\bH}{\ensuremath{\mathbf{H}}}
-\newcommand{\bI}{\ensuremath{\mathbf{I}}}
-\newcommand{\bJ}{\ensuremath{\mathbf{J}}}
-\newcommand{\bK}{\ensuremath{\mathbf{K}}}
-\newcommand{\bL}{\ensuremath{\mathbf{L}}}
-\newcommand{\bM}{\ensuremath{\mathbf{M}}}
-\newcommand{\bN}{\ensuremath{\mathbf{N}}}
-\newcommand{\bO}{\ensuremath{\mathbf{O}}}
-\newcommand{\bP}{\ensuremath{\mathbf{P}}}
-\newcommand{\bQ}{\ensuremath{\mathbf{Q}}}
-\newcommand{\bR}{\ensuremath{\mathbf{R}}}
-\newcommand{\bS}{\ensuremath{\mathbf{S}}}
-\newcommand{\bT}{\ensuremath{\mathbf{T}}}
-\newcommand{\bU}{\ensuremath{\mathbf{U}}}
-\newcommand{\bV}{\ensuremath{\mathbf{V}}}
-\newcommand{\bW}{\ensuremath{\mathbf{W}}}
-\newcommand{\bX}{\ensuremath{\mathbf{X}}}
-\newcommand{\bY}{\ensuremath{\mathbf{Y}}}
-\newcommand{\bZ}{\ensuremath{\mathbf{Z}}}
-
-% fraktur letters
-\newcommand{\fa}{\ensuremath{\mathfrak{a}}}
-\newcommand{\fb}{\ensuremath{\mathfrak{b}}}
-\newcommand{\fc}{\ensuremath{\mathfrak{c}}}
-\newcommand{\fd}{\ensuremath{\mathfrak{d}}}
-\newcommand{\fe}{\ensuremath{\mathfrak{e}}}
-\newcommand{\ff}{\ensuremath{\mathfrak{f}}}
-\newcommand{\fg}{\ensuremath{\mathfrak{g}}}
-\newcommand{\fh}{\ensuremath{\mathfrak{h}}}
-\newcommand{\fj}{\ensuremath{\mathfrak{j}}}
-\newcommand{\fk}{\ensuremath{\mathfrak{k}}}
-\newcommand{\fl}{\ensuremath{\mathfrak{l}}}
-\newcommand{\fm}{\ensuremath{\mathfrak{m}}}
-\newcommand{\fn}{\ensuremath{\mathfrak{n}}}
-\newcommand{\fo}{\ensuremath{\mathfrak{o}}}
-\newcommand{\fp}{\ensuremath{\mathfrak{p}}}
-\newcommand{\fq}{\ensuremath{\mathfrak{q}}}
-\newcommand{\fr}{\ensuremath{\mathfrak{r}}}
-\newcommand{\fs}{\ensuremath{\mathfrak{s}}}
-\newcommand{\ft}{\ensuremath{\mathfrak{t}}}
-\newcommand{\fu}{\ensuremath{\mathfrak{u}}}
-\newcommand{\fv}{\ensuremath{\mathfrak{v}}}
-\newcommand{\fw}{\ensuremath{\mathfrak{w}}}
-\newcommand{\fx}{\ensuremath{\mathfrak{x}}}
-\newcommand{\fy}{\ensuremath{\mathfrak{y}}}
-\newcommand{\fz}{\ensuremath{\mathfrak{z}}}
-
-\mdef\fahat{\hat{\fa}}
-
-% Underline letters
-\newcommand{\uA}{\ensuremath{\underline{A}}}
-\newcommand{\uB}{\ensuremath{\underline{B}}}
-\newcommand{\uC}{\ensuremath{\underline{C}}}
-\newcommand{\uD}{\ensuremath{\underline{D}}}
-\newcommand{\uE}{\ensuremath{\underline{E}}}
-\newcommand{\uF}{\ensuremath{\underline{F}}}
-\newcommand{\uG}{\ensuremath{\underline{G}}}
-\newcommand{\uH}{\ensuremath{\underline{H}}}
-\newcommand{\uI}{\ensuremath{\underline{I}}}
-\newcommand{\uJ}{\ensuremath{\underline{J}}}
-\newcommand{\uK}{\ensuremath{\underline{K}}}
-\newcommand{\uL}{\ensuremath{\underline{L}}}
-\newcommand{\uM}{\ensuremath{\underline{M}}}
-\newcommand{\uN}{\ensuremath{\underline{N}}}
-\newcommand{\uO}{\ensuremath{\underline{O}}}
-\newcommand{\uP}{\ensuremath{\underline{P}}}
-\newcommand{\uQ}{\ensuremath{\underline{Q}}}
-\newcommand{\uR}{\ensuremath{\underline{R}}}
-\newcommand{\uS}{\ensuremath{\underline{S}}}
-\newcommand{\uT}{\ensuremath{\underline{T}}}
-\newcommand{\uU}{\ensuremath{\underline{U}}}
-\newcommand{\uV}{\ensuremath{\underline{V}}}
-\newcommand{\uW}{\ensuremath{\underline{W}}}
-\newcommand{\uX}{\ensuremath{\underline{X}}}
-\newcommand{\uY}{\ensuremath{\underline{Y}}}
-\newcommand{\uZ}{\ensuremath{\underline{Z}}}
-
-% bars
-\newcommand{\Abar}{\ensuremath{\overline{A}}}
-\newcommand{\Bbar}{\ensuremath{\overline{B}}}
-\newcommand{\Cbar}{\ensuremath{\overline{C}}}
-\newcommand{\Dbar}{\ensuremath{\overline{D}}}
-\newcommand{\Ebar}{\ensuremath{\overline{E}}}
-\newcommand{\Fbar}{\ensuremath{\overline{F}}}
-\newcommand{\Gbar}{\ensuremath{\overline{G}}}
-\newcommand{\Hbar}{\ensuremath{\overline{H}}}
-\newcommand{\Ibar}{\ensuremath{\overline{I}}}
-\newcommand{\Jbar}{\ensuremath{\overline{J}}}
-\newcommand{\Kbar}{\ensuremath{\overline{K}}}
-\newcommand{\Lbar}{\ensuremath{\overline{L}}}
-\newcommand{\Mbar}{\ensuremath{\overline{M}}}
-\newcommand{\Nbar}{\ensuremath{\overline{N}}}
-\newcommand{\Obar}{\ensuremath{\overline{O}}}
-\newcommand{\Pbar}{\ensuremath{\overline{P}}}
-\newcommand{\Qbar}{\ensuremath{\overline{Q}}}
-\newcommand{\Rbar}{\ensuremath{\overline{R}}}
-\newcommand{\Sbar}{\ensuremath{\overline{S}}}
-\newcommand{\Tbar}{\ensuremath{\overline{T}}}
-\newcommand{\Ubar}{\ensuremath{\overline{U}}}
-\newcommand{\Vbar}{\ensuremath{\overline{V}}}
-\newcommand{\Wbar}{\ensuremath{\overline{W}}}
-\newcommand{\Xbar}{\ensuremath{\overline{X}}}
-\newcommand{\Ybar}{\ensuremath{\overline{Y}}}
-\newcommand{\Zbar}{\ensuremath{\overline{Z}}}
-\newcommand{\abar}{\ensuremath{\overline{a}}}
-\newcommand{\bbar}{\ensuremath{\overline{b}}}
-\newcommand{\cbar}{\ensuremath{\overline{c}}}
-\newcommand{\dbar}{\ensuremath{\overline{d}}}
-\newcommand{\ebar}{\ensuremath{\overline{e}}}
-\newcommand{\fbar}{\ensuremath{\overline{f}}}
-\newcommand{\gbar}{\ensuremath{\overline{g}}}
-%\newcommand{\hbar}{\ensuremath{\overline{h}}} % whoops, \hbar means something else!
-\newcommand{\ibar}{\ensuremath{\overline{\imath}}}
-\newcommand{\jbar}{\ensuremath{\overline{\jmath}}}
-\newcommand{\kbar}{\ensuremath{\overline{k}}}
-\newcommand{\lbar}{\ensuremath{\overline{l}}}
-\newcommand{\mbar}{\ensuremath{\overline{m}}}
-\newcommand{\nbar}{\ensuremath{\overline{n}}}
-%\newcommand{\obar}{\ensuremath{\overline{o}}}
-\newcommand{\pbar}{\ensuremath{\overline{p}}}
-\newcommand{\qbar}{\ensuremath{\overline{q}}}
-\newcommand{\rbar}{\ensuremath{\overline{r}}}
-\newcommand{\sbar}{\ensuremath{\overline{s}}}
-\newcommand{\tbar}{\ensuremath{\overline{t}}}
-\newcommand{\ubar}{\ensuremath{\overline{u}}}
-\newcommand{\vbar}{\ensuremath{\overline{v}}}
-\newcommand{\wbar}{\ensuremath{\overline{w}}}
-\newcommand{\xbar}{\ensuremath{\overline{x}}}
-\newcommand{\ybar}{\ensuremath{\overline{y}}}
-\newcommand{\zbar}{\ensuremath{\overline{z}}}
-
-% tildes
-\newcommand{\Atil}{\ensuremath{\widetilde{A}}}
-\newcommand{\Btil}{\ensuremath{\widetilde{B}}}
-\newcommand{\Ctil}{\ensuremath{\widetilde{C}}}
-\newcommand{\Dtil}{\ensuremath{\widetilde{D}}}
-\newcommand{\Etil}{\ensuremath{\widetilde{E}}}
-\newcommand{\Ftil}{\ensuremath{\widetilde{F}}}
-\newcommand{\Gtil}{\ensuremath{\widetilde{G}}}
-\newcommand{\Htil}{\ensuremath{\widetilde{H}}}
-\newcommand{\Itil}{\ensuremath{\widetilde{I}}}
-\newcommand{\Jtil}{\ensuremath{\widetilde{J}}}
-\newcommand{\Ktil}{\ensuremath{\widetilde{K}}}
-\newcommand{\Ltil}{\ensuremath{\widetilde{L}}}
-\newcommand{\Mtil}{\ensuremath{\widetilde{M}}}
-\newcommand{\Ntil}{\ensuremath{\widetilde{N}}}
-\newcommand{\Otil}{\ensuremath{\widetilde{O}}}
-\newcommand{\Ptil}{\ensuremath{\widetilde{P}}}
-\newcommand{\Qtil}{\ensuremath{\widetilde{Q}}}
-\newcommand{\Rtil}{\ensuremath{\widetilde{R}}}
-\newcommand{\Stil}{\ensuremath{\widetilde{S}}}
-\newcommand{\Ttil}{\ensuremath{\widetilde{T}}}
-\newcommand{\Util}{\ensuremath{\widetilde{U}}}
-\newcommand{\Vtil}{\ensuremath{\widetilde{V}}}
-\newcommand{\Wtil}{\ensuremath{\widetilde{W}}}
-\newcommand{\Xtil}{\ensuremath{\widetilde{X}}}
-\newcommand{\Ytil}{\ensuremath{\widetilde{Y}}}
-\newcommand{\Ztil}{\ensuremath{\widetilde{Z}}}
-\newcommand{\atil}{\ensuremath{\widetilde{a}}}
-\newcommand{\btil}{\ensuremath{\widetilde{b}}}
-\newcommand{\ctil}{\ensuremath{\widetilde{c}}}
-\newcommand{\dtil}{\ensuremath{\widetilde{d}}}
-\newcommand{\etil}{\ensuremath{\widetilde{e}}}
-\newcommand{\ftil}{\ensuremath{\widetilde{f}}}
-\newcommand{\gtil}{\ensuremath{\widetilde{g}}}
-\newcommand{\htil}{\ensuremath{\widetilde{h}}}
-\newcommand{\itil}{\ensuremath{\widetilde{\imath}}}
-\newcommand{\jtil}{\ensuremath{\widetilde{\jmath}}}
-\newcommand{\ktil}{\ensuremath{\widetilde{k}}}
-\newcommand{\ltil}{\ensuremath{\widetilde{l}}}
-\newcommand{\mtil}{\ensuremath{\widetilde{m}}}
-\newcommand{\ntil}{\ensuremath{\widetilde{n}}}
-\newcommand{\otil}{\ensuremath{\widetilde{o}}}
-\newcommand{\ptil}{\ensuremath{\widetilde{p}}}
-\newcommand{\qtil}{\ensuremath{\widetilde{q}}}
-\newcommand{\rtil}{\ensuremath{\widetilde{r}}}
-\newcommand{\stil}{\ensuremath{\widetilde{s}}}
-\newcommand{\ttil}{\ensuremath{\widetilde{t}}}
-\newcommand{\util}{\ensuremath{\widetilde{u}}}
-\newcommand{\vtil}{\ensuremath{\widetilde{v}}}
-\newcommand{\wtil}{\ensuremath{\widetilde{w}}}
-\newcommand{\xtil}{\ensuremath{\widetilde{x}}}
-\newcommand{\ytil}{\ensuremath{\widetilde{y}}}
-\newcommand{\ztil}{\ensuremath{\widetilde{z}}}
-
-% Hats
-\newcommand{\Ahat}{\ensuremath{\widehat{A}}}
-\newcommand{\Bhat}{\ensuremath{\widehat{B}}}
-\newcommand{\Chat}{\ensuremath{\widehat{C}}}
-\newcommand{\Dhat}{\ensuremath{\widehat{D}}}
-\newcommand{\Ehat}{\ensuremath{\widehat{E}}}
-\newcommand{\Fhat}{\ensuremath{\widehat{F}}}
-\newcommand{\Ghat}{\ensuremath{\widehat{G}}}
-\newcommand{\Hhat}{\ensuremath{\widehat{H}}}
-\newcommand{\Ihat}{\ensuremath{\widehat{I}}}
-\newcommand{\Jhat}{\ensuremath{\widehat{J}}}
-\newcommand{\Khat}{\ensuremath{\widehat{K}}}
-\newcommand{\Lhat}{\ensuremath{\widehat{L}}}
-\newcommand{\Mhat}{\ensuremath{\widehat{M}}}
-\newcommand{\Nhat}{\ensuremath{\widehat{N}}}
-\newcommand{\Ohat}{\ensuremath{\widehat{O}}}
-\newcommand{\Phat}{\ensuremath{\widehat{P}}}
-\newcommand{\Qhat}{\ensuremath{\widehat{Q}}}
-\newcommand{\Rhat}{\ensuremath{\widehat{R}}}
-\newcommand{\Shat}{\ensuremath{\widehat{S}}}
-\newcommand{\That}{\ensuremath{\widehat{T}}}
-\newcommand{\Uhat}{\ensuremath{\widehat{U}}}
-\newcommand{\Vhat}{\ensuremath{\widehat{V}}}
-\newcommand{\What}{\ensuremath{\widehat{W}}}
-\newcommand{\Xhat}{\ensuremath{\widehat{X}}}
-\newcommand{\Yhat}{\ensuremath{\widehat{Y}}}
-\newcommand{\Zhat}{\ensuremath{\widehat{Z}}}
-\newcommand{\ahat}{\ensuremath{\hat{a}}}
-\newcommand{\bhat}{\ensuremath{\hat{b}}}
-\newcommand{\chat}{\ensuremath{\hat{c}}}
-\newcommand{\dhat}{\ensuremath{\hat{d}}}
-\newcommand{\ehat}{\ensuremath{\hat{e}}}
-\newcommand{\fhat}{\ensuremath{\hat{f}}}
-\newcommand{\ghat}{\ensuremath{\hat{g}}}
-\newcommand{\hhat}{\ensuremath{\hat{h}}}
-\newcommand{\ihat}{\ensuremath{\hat{\imath}}}
-\newcommand{\jhat}{\ensuremath{\hat{\jmath}}}
-\newcommand{\khat}{\ensuremath{\hat{k}}}
-\newcommand{\lhat}{\ensuremath{\hat{l}}}
-\newcommand{\mhat}{\ensuremath{\hat{m}}}
-\newcommand{\nhat}{\ensuremath{\hat{n}}}
-\newcommand{\ohat}{\ensuremath{\hat{o}}}
-\newcommand{\phat}{\ensuremath{\hat{p}}}
-\newcommand{\qhat}{\ensuremath{\hat{q}}}
-\newcommand{\rhat}{\ensuremath{\hat{r}}}
-\newcommand{\shat}{\ensuremath{\hat{s}}}
-\newcommand{\that}{\ensuremath{\hat{t}}}
-\newcommand{\uhat}{\ensuremath{\hat{u}}}
-\newcommand{\vhat}{\ensuremath{\hat{v}}}
-\newcommand{\what}{\ensuremath{\hat{w}}}
-\newcommand{\xhat}{\ensuremath{\hat{x}}}
-\newcommand{\yhat}{\ensuremath{\hat{y}}}
-\newcommand{\zhat}{\ensuremath{\hat{z}}}
-
-%% FONTS AND DECORATION FOR GREEK LETTERS
-
-%% the package `mathbbol' gives us blackboard bold greek and numbers,
-%% but it does it by redefining \mathbb to use a different font, so that
-%% all the other \mathbb letters look different too.  Here we import the
-%% font with bb greek and numbers, but assign it a different name,
-%% \mathbbb, so as not to replace the usual one.
-\DeclareSymbolFont{bbold}{U}{bbold}{m}{n}
-\DeclareSymbolFontAlphabet{\mathbbb}{bbold}
-\newcommand{\bbDelta}{\ensuremath{\mathbbb{\Delta}}}
-\newcommand{\bbone}{\ensuremath{\mathbbb{1}}}
-\newcommand{\bbtwo}{\ensuremath{\mathbbb{2}}}
-\newcommand{\bbthree}{\ensuremath{\mathbbb{3}}}
-
-% greek with bars
-\newcommand{\albar}{\ensuremath{\overline{\alpha}}}
-\newcommand{\bebar}{\ensuremath{\overline{\beta}}}
-\newcommand{\gmbar}{\ensuremath{\overline{\gamma}}}
-\newcommand{\debar}{\ensuremath{\overline{\delta}}}
-\newcommand{\phibar}{\ensuremath{\overline{\varphi}}}
-\newcommand{\psibar}{\ensuremath{\overline{\psi}}}
-\newcommand{\xibar}{\ensuremath{\overline{\xi}}}
-\newcommand{\ombar}{\ensuremath{\overline{\omega}}}
-
-% greek with hats
-\newcommand{\alhat}{\ensuremath{\hat{\alpha}}}
-\newcommand{\behat}{\ensuremath{\hat{\beta}}}
-\newcommand{\gmhat}{\ensuremath{\hat{\gamma}}}
-\newcommand{\dehat}{\ensuremath{\hat{\delta}}}
-
-% greek with checks
-\newcommand{\alchk}{\ensuremath{\check{\alpha}}}
-\newcommand{\bechk}{\ensuremath{\check{\beta}}}
-\newcommand{\gmchk}{\ensuremath{\check{\gamma}}}
-\newcommand{\dechk}{\ensuremath{\check{\delta}}}
-
-% greek with tildes
-\newcommand{\altil}{\ensuremath{\widetilde{\alpha}}}
-\newcommand{\betil}{\ensuremath{\widetilde{\beta}}}
-\newcommand{\gmtil}{\ensuremath{\widetilde{\gamma}}}
-\newcommand{\phitil}{\ensuremath{\widetilde{\varphi}}}
-\newcommand{\psitil}{\ensuremath{\widetilde{\psi}}}
-\newcommand{\xitil}{\ensuremath{\widetilde{\xi}}}
-\newcommand{\omtil}{\ensuremath{\widetilde{\omega}}}
-
-% MISCELLANEOUS SYMBOLS
-\mdef\del{\partial}
-\mdef\delbar{\overline{\partial}}
-\let\sm\wedge
-\newcommand{\dd}[1]{\ensuremath{\frac{\partial}{\partial {#1}}}}
-\newcommand{\inv}{^{-1}}
-\newcommand{\dual}{^{\vee}}
-\mdef\hf{\textstyle\frac{1}{2}}
-\mdef\thrd{\textstyle\frac{1}{3}}
-\mdef\qtr{\textstyle\frac{1}{4}}
-\let\meet\wedge
-\let\join\vee
-\let\dn\downarrow
-\newcommand{\op}{^{\mathit{op}}}
-\newcommand{\co}{^{\mathit{co}}}
-\newcommand{\coop}{^{\mathit{coop}}}
-\newcommand{\id}{\mathm{id}}
-\let\adj\dashv
-\SelectTips{cm}{}
-\newdir{ >}{{}*!/-10pt/@{>}}    % extra spacing for tail arrows in XYpic
-\newcommand{\pushoutcorner}[1][dr]{\save*!/#1+1.2pc/#1:(1,-1)@^{|-}\restore}
-\newcommand{\pullbackcorner}[1][dr]{\save*!/#1-1.2pc/#1:(-1,1)@^{|-}\restore}
-\let\iso\cong
-\let\eqv\simeq
-\let\cng\equiv
-\mdef\Id{\mathrm{Id}}
-\mdef\id{\mathrm{id}}
-\alwaysmath{ell}
-\alwaysmath{infty}
-\alwaysmath{odot}
-\def\frc#1/#2.{\frac{#1}{#2}}   % \frc x^2+1 / x^2-1 .
-\mdef\ten{\mathrel{\otimes}}
-\mdef\bigten{\bigotimes}
-\mdef\sqten{\mathrel{\boxtimes}}
-\def\pow(#1,#2){\mathop{\pitchfork}(#1,#2)} % powers and
-\def\cpw{\mathop{\odot}}                    % copowers
-
-%% OPERATORS
-\DeclareMathOperator\lan{Lan}
-\DeclareMathOperator\ran{Ran}
-\DeclareMathOperator\colim{colim}
-\DeclareMathOperator\coeq{coeq}
-\DeclareMathOperator\eq{eq}
-\DeclareMathOperator\Tot{Tot}
-\DeclareMathOperator\cosk{cosk}
-\DeclareMathOperator\sk{sk}
-\DeclareMathOperator\im{im}
-\DeclareMathOperator\Spec{Spec}
-\DeclareMathOperator\Ho{Ho}
-\DeclareMathOperator\Aut{Aut}
-\DeclareMathOperator\End{End}
-\DeclareMathOperator\Hom{Hom}
-\DeclareMathOperator\Map{Map}
-
-%% ARROWS
-% \to already exists
-\newcommand{\too}[1][]{\ensuremath{\overset{#1}{\longrightarrow}}}
-\newcommand{\ot}{\ensuremath{\leftarrow}}
-\newcommand{\oot}[1][]{\ensuremath{\overset{#1}{\longleftarrow}}}
-\let\toot\rightleftarrows
-\let\otto\leftrightarrows
-\let\Impl\Rightarrow
-\let\imp\Rightarrow
-\let\toto\rightrightarrows
-\let\into\hookrightarrow
-\let\xinto\xhookrightarrow
-\mdef\we{\overset{\sim}{\longrightarrow}}
-\mdef\leftwe{\overset{\sim}{\longleftarrow}}
-\let\mono\rightarrowtail
-\let\leftmono\leftarrowtail
-\let\cof\rightarrowtail
-\let\leftcof\leftarrowtail
-\let\epi\twoheadrightarrow
-\let\leftepi\twoheadleftarrow
-\let\fib\twoheadrightarrow
-\let\leftfib\twoheadleftarrow
-\let\cohto\rightsquigarrow
-\let\maps\colon
-\newcommand{\spam}{\,:\!}       % \maps for left arrows
-
-%% EXTENSIBLE ARROWS
-\let\xto\xrightarrow
-\let\xot\xleftarrow
-% See Voss' Mathmode.tex for instructions on how to create new
-% extensible arrows.
-\def\rightarrowtailfill@{\arrowfill@{\Yright\joinrel\relbar}\relbar\rightarrow}
-\newcommand\xrightarrowtail[2][]{\ext@arrow 0055{\rightarrowtailfill@}{#1}{#2}}
-\let\xmono\xrightarrowtail
-\let\xcof\xrightarrowtail
-\def\twoheadrightarrowfill@{\arrowfill@{\relbar\joinrel\relbar}\relbar\twoheadrightarrow}
-\newcommand\xtwoheadrightarrow[2][]{\ext@arrow 0055{\twoheadrightarrowfill@}{#1}{#2}}
-\let\xepi\xtwoheadrightarrow
-\let\xfib\xtwoheadrightarrow
-% Let's leave the left-going ones until I need them.
-
-%% EXTENSIBLE SLASHED ARROWS
-% Making extensible slashed arrows, by modifying the underlying AMS code.
-% Arguments are:
-% 1 = arrowhead on the left (\relbar or \Relbar if none)
-% 2 = fill character (usually \relbar or \Relbar)
-% 3 = slash character (such as \mapstochar or \Mapstochar)
-% 4 = arrowhead on the left (\relbar or \Relbar if none)
-% 5 = display mode (\displaystyle etc)
-\def\slashedarrowfill@#1#2#3#4#5{%
-  $\m@th\thickmuskip0mu\medmuskip\thickmuskip\thinmuskip\thickmuskip
-   \relax#5#1\mkern-7mu%
-   \cleaders\hbox{$#5\mkern-2mu#2\mkern-2mu$}\hfill
-   \mathclap{#3}\mathclap{#2}%
-   \cleaders\hbox{$#5\mkern-2mu#2\mkern-2mu$}\hfill
-   \mkern-7mu#4$%
-}
-% Here's the idea: \<slashed>arrowfill@ should be a box containing
-% some stretchable space that is the "middle of the arrow".  This
-% space is created as a "leader" using \cleader<thing>\hfill, which
-% fills an \hfill of space with copies of <thing>.  Here instead of
-% just one \cleader, we use two, with the slash in between (and an
-% extra copy of the filler, to avoid extra space around the slash).
-\def\rightslashedarrowfill@{%
-  \slashedarrowfill@\relbar\relbar\mapstochar\rightarrow}
-\newcommand\xslashedrightarrow[2][]{%
-  \ext@arrow 0055{\rightslashedarrowfill@}{#1}{#2}}
-\mdef\hto{\xslashedrightarrow{}}
-\mdef\htoo{\xslashedrightarrow{\quad}}
-\let\xhto\xslashedrightarrow
-
-%% To get a slashed arrow in XYpic, do
-% \[\xymatrix{A \ar[r]|-@{|} & B}\]
-
-% ISOMORPHISMS
-\def\xiso#1{\mathrel{\mathrlap{\smash{\xto[\smash{\raisebox{1.3mm}{$\scriptstyle\sim$}}]{#1}}}\hphantom{\xto{#1}}}}
-\def\toiso{\xto{\smash{\raisebox{-.5mm}{$\scriptstyle\sim$}}}}
-
-% SHADOWS
-\def\shvar#1#2{{\ensuremath{%
-  \hspace{1mm}\makebox[-1mm]{$#1\langle$}\makebox[0mm]{$#1\langle$}\hspace{1mm}%
-  {#2}%
-  \makebox[1mm]{$#1\rangle$}\makebox[0mm]{$#1\rangle$}%
-}}}
-\def\sh{\shvar{}}
-\def\scriptsh{\shvar{\scriptstyle}}
-\def\bigsh{\shvar{\big}}
-\def\Bigsh{\shvar{\Big}}
-\def\biggsh{\shvar{\bigg}}
-\def\Biggsh{\shvar{\Bigg}}
-
-% THEOREM-TYPE ENVIRONMENTS, hacked to
-%% (a) number all with the same numbers, and
-%% (b) have the right names for autoref
-\def\defthm#1#2{%
-  \newtheorem{#1}{#2}[section]%
-  \expandafter\def\csname #1autorefname\endcsname{#2}%
-  \expandafter\let\csname c@#1\endcsname\c@thm}
-\newtheorem{thm}{Theorem}[section]
-\newcommand{\thmautorefname}{Theorem}
-\defthm{cor}{Corollary}
-\defthm{prop}{Proposition}
-\defthm{lem}{Lemma}
-\defthm{sch}{Scholium}
-\defthm{assume}{Assumption}
-\defthm{claim}{Claim}
-\defthm{conj}{Conjecture}
-\defthm{hyp}{Hypothesis}
-\defthm{fact}{Fact}
-\theoremstyle{definition}
-\defthm{defn}{Definition}
-\defthm{notn}{Notation}
-\theoremstyle{remark}
-\defthm{rmk}{Remark}
-\defthm{eg}{Example}
-\defthm{egs}{Examples}
-\defthm{ex}{Exercise}
-\defthm{ceg}{Counterexample}
-
-% How to get QED symbols inside equations at the end of the statements
-% of theorems.  AMS LaTeX knows how to do this inside equations at the
-% end of *proofs* with \qedhere, and at the end of the statement of a
-% theorem with \qed (meaning no proof will be given), but it can't
-% seem to combine the two.  Use this instead.
-\def\thmqedhere{\expandafter\csname\csname @currenvir\endcsname @qed\endcsname}
-
-% Number numbered lists as (i), (ii), ...
-\renewcommand{\theenumi}{(\roman{enumi})}
-\renewcommand{\labelenumi}{\theenumi}
-
-%% Labeling that keeps track of theorem-type names.  Superseded by
-%% autoref from hyperref, as above, but we keep this in case we are
-%% using a journal style file that is incompatible with hyperref.
-% 
-% \ifx\SK@label\undefined\let\SK@label\label\fi
-% \let\your@thm\@thm
-% \def\@thm#1#2#3{\gdef\currthmtype{#3}\your@thm{#1}{#2}{#3}}
-% \def\xlabel#1{{\let\your@currentlabel\@currentlabel\def\@currentlabel
-% {\currthmtype~\your@currentlabel}
-% \SK@label{#1@}}\label{#1}}
-% \def\xref#1{\ref{#1@}}
-
-% Also number formulas with the theorem counter
-\let\c@equation\c@thm
-\numberwithin{equation}{section}
-
-% Only show numbers for equations that are actually referenced (or
-% whose tags are specified manually) - uses mathtools.
-\mathtoolsset{showonlyrefs,showmanualtags}
-
-%% Fix enumerate spacing with paralist.  This has two parts:
-%%   1. enable mixing of "old spacing" lists with those adjusted by paralist
-%%   2. allow us to specify a number based on which to adjust the spacing
-%% For the first, use \killspacingtrue when you want the spacing
-%% adjusted, then \killspacingfalse to turn adjustment off.  For the
-%% second, use \maxenum=14 to set the widest number you want the
-%% spacing to be calculated with.
-\newlength\oldleftmargini       % save old spacing
-\newlength\oldleftmarginii
-\newlength\oldleftmarginiii
-\newlength\oldleftmarginiv
-\newlength\oldleftmarginv
-\newlength\oldleftmarginvi
-\newcount\maxenum
-\maxenum=7
-\newif\ifkillspacing
-\def\@adjust@enum@labelwidth{%
-  \advance\@listdepth by 1\relax
-  \ifkillspacing                % do the paralist thing
-    \csname c@\@enumctr\endcsname\maxenum
-    \settowidth{\@tempdima}{%
-      \csname label\@enumctr\endcsname\hspace{\labelsep}}%
-    \csname leftmargin\romannumeral\@listdepth\endcsname
-      \@tempdima
-  \else                         % otherwise, reset it
-    \csname fixspacing\romannumeral\@listdepth\endcsname
-  \fi
-  \advance\@listdepth by -1\relax}
-% these commands, one for each enum level (I couldn't get a generic
-% one to work), test whether oldleftmargin has been set yet, and if
-% not, set it from leftmargin; otherwise, they reset leftmargin to
-% it.  Just setting oldleftmargin to leftmargin in the preamble
-% doesn't seem to work.
-\def\fixspacingi{\ifnum\oldleftmargini=0\setlength\oldleftmargini\leftmargini\else\setlength\leftmargini\oldleftmargini\fi}
-\def\fixspacingii{\ifnum\oldleftmarginii=0\setlength\oldleftmarginii\leftmarginii\else\setlength\leftmarginii\oldleftmarginii\fi}
-\def\fixspacingiii{\ifnum\oldleftmarginiii=0\setlength\oldleftmarginiii\leftmarginiii\else\setlength\leftmarginiii\oldleftmarginiii\fi}
-\def\fixspacingiv{\ifnum\oldleftmarginiv=0\setlength\oldleftmarginiv\leftmarginiv\else\setlength\leftmarginiv\oldleftmarginiv\fi}
-\def\fixspacingv{\ifnum\oldleftmarginv=0\setlength\oldleftmarginv\leftmarginv\else\setlength\leftmarginv\oldleftmarginv\fi}
-\def\fixspacingvi{\ifnum\oldleftmarginvi=0\setlength\oldleftmarginvi\leftmarginvi\else\setlength\leftmarginvi\oldleftmarginvi\fi}
-
-%% Fix paralist references, so that we can refer to (1) instead of
-%% just 1.
-\def\pl@label#1#2{%
-  \edef\pl@the{\noexpand#1{\@enumctr}}%
-  \pl@lab\expandafter{\the\pl@lab\csname yourthe\@enumctr\endcsname}%
-  \advance\@tempcnta1
-  \pl@loop}
-\def\@enumlabel@#1[#2]{%
-  \@plmylabeltrue
-  \@tempcnta0
-  \pl@lab{}%
-  \let\pl@the\pl@qmark
-  \expandafter\pl@loop\@gobble#2\@@@
-  \ifnum\@tempcnta=1\else
-    \PackageWarning{paralist}{Incorrect label; no or multiple
-      counters.\MessageBreak The label is: \@gobble#2}%
-  \fi
-  \expandafter\edef\csname label\@enumctr\endcsname{\the\pl@lab}%
-  \expandafter\edef\csname the\@enumctr\endcsname{\the\pl@lab}%
-  \expandafter\let\csname yourthe\@enumctr\endcsname\pl@the
-  #1}
-
-\def\tobar{\mathrel{\mkern3mu  \vcenter{\hbox{$\scriptscriptstyle+$}}%
-                    \mkern-12mu{\to}}}
-
-%\input{decls}
-\UseAllTwocells
-
-\newcommand{\dblcat}[1]{\mathbb{#1}}
-\mdef\fchk{\check{f}}
+\input{Equiv_preamble.tex}
 
@@
 \section{Introduction}
-
-HELLO ALL!
 

### 2018-09-28 EquivCompFrameworks_20180911kc.tex
initial3
mainly condensing diagrams

@@
 
+git pro coming through!
+
 Networks are playing an increasingly prominent role in our understanding of the world and as a result, methods of characterizing and studying networks have become evermore necessary.
@@
 Here $F(c)$ is the collection of all $F$-decorations on the object $c$ and the morphism $d$ is selecting a particular one.
-Thus a decorated cospan is then a pair:
+Thus a decorated cospan is given by a pair:
 \[
@@
 \node (A) at (0,0) {$a$};
-\node (B) at (1,1) {$c$};
+\node (B) at (1,0) {$c$};
 \node (C) at (2,0) {$b$};
-\node (D) at (3,0.5) {$I$};
-\node (E) at (4,0.5) {$F(c)$};
+\node (D) at (3,0) {$I$};
+\node (E) at (4,0) {$F(c)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \node (A) at (0,0) {$a$};
-\node (B) at (1,1) {$c$};
+\node (B) at (1,0) {$c$};
 \node (C) at (2,0) {$b$};
 \node (F) at (3,0) {$b$};
-\node (G) at (4,1) {$f$};
+\node (G) at (4,0) {$f$};
 \node (H) at (5,0) {$e$};
@@
 \node (A) at (0,0) {$a$};
-\node (B) at (1,1) {$c$};
+\node (B) at (1,0) {$c$};
 \node (C) at (2,0) {$b$};
-\node (D) at (3,0.5) {$d \in F(c)$};
+\node (D) at (3,0) {$d \in F(c)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \node (A) at (0,0) {$a$};
-\node (B) at (1,-1) {$c^\prime$};
+\node (B) at (1,0) {$c^\prime$};
 \node (C) at (2,0) {$b$};
-\node (D) at (3,-0.5) {$d^\prime \in F(c^\prime)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[below]{$i^\prime$} (B)
-(C) edge node[below]{$o^\prime$} (B);
+\node (D) at (3,0) {$d^\prime \in F(c^\prime)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i^\prime$} (B)
+(C) edge node[above]{$o^\prime$} (B);
 \end{tikzpicture}
@@
 \section{A review of double categories and symmetric monoidal double categories}
+\textbf{Likely move this to an appendix or remove entirely and just cite another paper.}
 This section is meant to serve as a review of double categories and to present the definitions of double category, symmetric monoidal double category and a few more ideas that will be used later in the paper.
@@
 Thus a morphism of $(\mathbb{G} / \mathbb{F})_1$ is a map of cospans in $\bold{C}$ together with a natural transformation that that makes the above triangle commute.
+\textbf{Likely delete everything in this section before this line.}
 \begin{thm}
@@
 \begin{tikzpicture}[scale=1.5]
-\node (E) at (-1,0.5) {$c \mapsto$};
+\node (E) at (-1,0) {$c \mapsto$};
 \node (A) at (0,0) {$c$};
-\node (B) at (1,1) {$c$};
+\node (B) at (1,0) {$c$};
 \node (C) at (2,0) {$c$};
-\node (D) at (3,0.5) {$I \in F(c)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[left]{$1$} (B)
-(C) edge node[right]{$1$} (B);
+\node (D) at (3,0) {$I \in F(c)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$1$} (B)
+(C) edge node[above]{$1$} (B);
 \end{tikzpicture}
@@
 \node (A) at (0,0) {$a$};
-\node (B) at (1,1) {$c$};
+\node (B) at (1,0) {$c$};
 \node (C) at (2,0) {$b$};
@@
 \node (E) at (3,0) {$b$};
-\node (F) at (4,1) {$c^\prime$};
+\node (F) at (4,0) {$c^\prime$};
 \node (G) at (5,0) {$e$};
@@
 \node (I) at (6,0) {$e$};
-\node (J) at (7,1) {$c''$};
+\node (J) at (7,0) {$c''$};
 \node (K) at (8,0) {$f$};
@@
 (C) edge node[above]{$$} (B)
-(A) edge node[left]{$\id_a$} (A')
-(C) edge node[left]{$\id_f$} (C')
+(A) edge node[left]{$1$} (A')
+(C) edge node[left]{$1$} (C')
 (A') edge node {$$} (D)
@@
 \node (E) at (3,0) {$b$};
-\node (F) at (4,1) {$b$};
+\node (F) at (4,0) {$b$};
 \node (G) at (5,0) {$b$};
@@
 \]
-where $!_b = F(!)  \phi \colon \bold{1} \to F(b)$ is the trivial decoration on $b$. Composing these then gives:
+where $!_b = F(!)  \phi \colon 1 \to F(b)$ is the trivial decoration on $b$. Composing these then gives:
 \[
@@
 \node (A) at (0,0) {$a$};
-\node (B) at (1,1) {$c+_b b$};
+\node (B) at (1,0) {$c+_b b$};
 \node (C) at (2,0) {$b$};
-\node (D) at (3,0.5) {$\hat{d} \in F(c +_b b)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[left]{$j \psi_c i$} (B)
-(C) edge node[right]{$j \psi_b$} (B);
+\node (D) at (3,0) {$\hat{d} \in F(c +_b b)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$j \psi_c i$} (B)
+(C) edge node[above]{$j \psi_b$} (B);
 \end{tikzpicture}
@@
 The objects $d_{1,2}$ and $d^\prime_{1,2}$ are given by top and bottom composite of arrows and the morphism of decorations $\iota_{1,2}$ is given by composing $\iota_1 \times \iota_2$ with the two commuting squares.
-Returning the interchange law, composing the two horizontal compositions above vertically then results in:
+Returning to the interchange law, composing the two horizontal compositions above vertically then results in:
 \[
@@
 \node (A) at (0,0) {$a_1$};
-\node (B) at (1,1) {$c_1$};
+\node (B) at (1,0) {$c_1$};
 \node (C) at (2,0) {$b_1$};
@@
 \node (E) at (3,0) {$a_2$};
-\node (F) at (4,1) {$c_2$};
+\node (F) at (4,0) {$c_2$};
 \node (G) at (5,0) {$b_2$};
@@
 \node (A) at (0,0) {$a_1+a_2$};
-\node (B) at (1,1) {$c_1+c_2$};
-\node (C) at (2,0) {$b_1+b_2$};
-\node (D) at (3.5,0.5) {$d_{M_1 \otimes M_2} \in F(c_1+c_2)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[left]{$i_1+i_2$} (B)
-(C) edge node[right]{$o_1+o_2$} (B);
+\node (B) at (1.25,0) {$c_1+c_2$};
+\node (C) at (2.5,0) {$b_1+b_2$};
+\node (D) at (4.25,0) {$d_{M_1 \otimes M_2} \in F(c_1+c_2)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i_1+i_2$} (B)
+(C) edge node[above]{$o_1+o_2$} (B);
 \end{tikzpicture}
@@
 \node (A) at (0,0) {$0$};
-\node (B) at (1,1) {$0$};
+\node (B) at (1,0) {$0$};
 \node (C) at (2,0) {$0$};
-\node (D) at (3,0.5) {$! \in F(0)$};
+\node (D) at (3,0) {$! \in F(0)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \node (A) at (0,0) {$0$};
-\node (B) at (1,1) {$0$};
+\node (B) at (1,0) {$0$};
 \node (C) at (2,0) {$0$};
@@
 \node (E) at (3,0) {$a$};
-\node (F) at (4,1) {$c$};
+\node (F) at (4,0) {$c$};
 \node (G) at (5,0) {$b$};
@@
 \node (A) at (0,0) {$0+a$};
-\node (B) at (1,1) {$0+c$};
+\node (B) at (1,0) {$0+c$};
 \node (C) at (2,0) {$0+b$};
-\node (D) at (3,0.5) {$d^\prime \in F(0+c)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[left]{$!+i$} (B)
-(C) edge node[right]{$!+o$} (B);
+\node (D) at (3.5,0) {$d^\prime \in F(0+c)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$!+i$} (B)
+(C) edge node[above]{$!+o$} (B);
 \end{tikzpicture}
@@
 \path[->,font=\scriptsize,>=angle 90]
-(A) edge node[left]{$L(I)$} (B)
-(C) edge node[right]{$L(O)$} (B);
-\end{tikzpicture}
-\]
-and similarly, given a 2-morphism $(f,h,g,\iota) \colon M \to M^\prime$ of $\mathbb{F} \textnormal{Cospan}(\bold{C})$:
+(A) edge node[left]{$\tau_c L(I)$} (B)
+(C) edge node[right]{$\tau_ c L(O)$} (B);
+\end{tikzpicture}
+\]
+where $\tau_c \colon L(c) \to d$ is the unique morphism from the trival decoration on $c$ given by $$!_c \coloneqq 1 \xrightarrow{\phi} F(0) \xrightarrow{F(!)} F(c)$$ to $d \in F(c)$.
+In other words, the trivial decoraction $!_c$ is initial in $F(c)$ and $\tau_c \colon !_c \to d$ is the unique morphism to $d$.
+Similarly, given a 2-morphism $(f,h,g,\iota) \colon M \to M^\prime$ of $\mathbb{F} \textnormal{Cospan}(\bold{C})$:
 \[
@@
 \path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$L(I)$} (B)
-(C) edge node[above]{$L(O)$} (B)
-(A') edge node[above]{$L(I^\prime)$} (B')
-(C') edge node[above]{$L(O^\prime)$} (B')
+(A) edge node[above]{$\tau_c L(I)$} (B)
+(C) edge node[above]{$\tau_c L(O)$} (B)
+(A') edge node[above]{$\tau_{c^\prime} L(I^\prime)$} (B')
+(C') edge node[above]{$\tau_{c^\prime} L(O^\prime)$} (B')
 (A) edge node [left]{$L(f)$} (A')
@@
 Next, we exhibit natural isomorphisms $\eta \colon \id_{ _L \mathbb{C}\textnormal{sp}(\bold{D})} \cong \mathbb{G} \mathbb{E}$ and $\epsilon \colon \mathbb{E} \mathbb{G} \cong \id_{\mathbb{F}\textnormal{Cospan}(\bold{C})}$.
+Specifically, these are double natural isomorphisms given by double transformations $\eta$ and $\epsilon$ whose components are isomorphisms.
+
 First we compute the composites $\mathbb{G} \mathbb{E}$ and $\mathbb{E} \mathbb{G}$.
-On the object categories, both composites are $\id_\bold{C}$ and we have natural isomorphism $\eta \colon \id_{\bold{C}} \cong \mathbb{G}_0 \mathbb{E}_0$ and $\epsilon \colon \mathbb{E}_0 \mathbb{G}_0 \cong \id_{\bold{C}}$.
+On the object categories, both composites are $\id_\bold{C}$ and we have natural isomorphisms $\eta \colon \id_{\bold{C}} \cong \mathbb{G}_0 \mathbb{E}_0$ and $\epsilon \colon \mathbb{E}_0 \mathbb{G}_0 \cong \id_{\bold{C}}$.
 
@@
 \path[->,font=\scriptsize,>=angle 90]
-(A) edge node[left]{$L(R(i))$} (B)
-(C) edge node[right]{$L(R(o))$} (B);
+(A) edge node[left]{$\tau_{R(d)}L(R(i))$} (B)
+(C) edge node[right]{$\tau_{R(d)}L(R(o))$} (B);
 \end{tikzpicture}
@@
 \textbf{What can we say about LR? Find a 2-iso between these in $_L Csp(D)$.}
-Then we can find a 2-isomorphism $\eta \colon M \xrightarrow{\sim} \mathbb{G}\mathbb{E}(M) $ in $_L \mathbb{C} \textnormal{sp}(\bold{C})$ given by:
+Then we can find a 2-isomorphism $\eta_M \colon M \xrightarrow{\sim} \mathbb{G}\mathbb{E}(M) $ in $_L \mathbb{C} \textnormal{sp}(\bold{C})$ given by:
 \[
@@
 \node (A) at (0,0) {$L(c_1)$};
-\node (B) at (1,0) {$d$};
-\node (C) at (2,0) {$L(c_2)$};
+\node (B) at (1.25,0) {$d$};
+\node (C) at (2.5,0) {$L(c_2)$};
 \node (A') at (0,-1) {$L(c_1)$};
-\node (B') at (1,-1) {$d$};
-\node (C') at (2,-1) {$L(c_2)$};
+\node (B') at (1.25,-1) {$d$};
+\node (C') at (2.5,-1) {$L(c_2)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (C) edge node[above]{$o$} (B)
-(A') edge node[above]{$L(R(i))$} (B')
-(C') edge node[above]{$L(R(o))$} (B')
+(A') edge node[above]{$\tau_{R(d)}L(R(i))$} (B')
+(C') edge node[above]{$\tau_{R(d)}L(R(o))$} (B')
 (A) edge node [left]{$1$} (A')
@@
 \]
-
 On the other hand, given a horizontal 1-cell $N$ in $\mathbb{F}\textnormal{Cospan}(\bold{C})$:
@@
 \path[->,font=\scriptsize,>=angle 90]
-(A) edge node[left]{$L(I)$} (B)
-(C) edge node[right]{$L(O)$} (B);
+(A) edge node[left]{$\tau_c L(I)$} (B)
+(C) edge node[right]{$\tau_c L(O)$} (B);
 \end{tikzpicture}
@@
 \path[->,font=\scriptsize,>=angle 90]
-(A) edge node[left]{$R(L(I))$} (B)
-(C) edge node[right]{$R(L(O))$} (B);
-\end{tikzpicture}
-\]
-Then we can find a 2-isomorphism $\epsilon \colon \mathbb{E} \mathbb{G} (N) \xrightarrow{\sim} N$ in $\mathbb{F}\textnormal{Cospan}(\bold{C})$ given by:
+(A) edge node[left]{$R(\tau_c)I$} (B)
+(C) edge node[right]{$R(\tau_c)O$} (B);
+\end{tikzpicture}
+\]
+Then we can find a 2-isomorphism $\epsilon_N \colon \mathbb{E} \mathbb{G} (N) \xrightarrow{\sim} N$ in $\mathbb{F}\textnormal{Cospan}(\bold{C})$ given by:
 \[
@@
 \path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$R(L(I))$} (B)
-(C) edge node[above]{$R(L(O))$} (B)
+(A) edge node[above]{$R(\tau_c)I$} (B)
+(C) edge node[above]{$R(\tau_c)O$} (B)
 (A') edge node[above]{$I$} (B')
@@
 $$\iota \colon F(e)(d) \to d$$
-where $R(L(I))=I$ and $R(L(O))=O$ since $L \colon \bold{C} \to \bold{D} \cong \int{F}$ is a left adjoint with right adjoint $R \colon \int{F} \to \bold{C}$ as its inverse.
 \section{An example}

### 2018-09-29 EquivCompFrameworks_20180911kc.tex
more diagram condensing

@@
 \node (I) at (6,0) {$a_3$};
-\node (J) at (7,1) {$c_3$};
+\node (J) at (7,0) {$c_3$};
 \node (K) at (8,0) {$b_3$};
@@
 \node (A) at (0,0) {$(a_1+a_2)+a_3$};
-\node (B) at (1,1) {$(c_1+c_2)+c_3$};
-\node (C) at (2,0) {$(b_1+b_2)+b_3$};
-\node (D) at (4.5,0.5) {$d_{(M_1 \otimes M_2) \otimes M_3} \in F((c_1+c_2)+c_3)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[left]{$(i_1+i_2)+i_3$} (B)
-(C) edge node[right]{$(o_1+o_2)+o_3$} (B);
+\node (B) at (2.25,0){$(c_1+c_2)+c_3$};
+\node (C) at (4.5,0) {$(b_1+b_2)+b_3$};
+\node (D) at (2.25,-0.5) {$d_{(M_1 \otimes M_2) \otimes M_3} \in F((c_1+c_2)+c_3)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$(i_1+i_2)+i_3$} (B)
+(C) edge node[above]{$(o_1+o_2)+o_3$} (B);
 \end{tikzpicture}
@@
 \node (A) at (0,0) {$a_1+(a_2+a_3)$};
-\node (B) at (1,1) {$c_1+(c_2+c_3)$};
-\node (C) at (2,0) {$b_1+(b_2+b_3)$};
-\node (D) at (4.5,0.5) {$d_{M_1 \otimes (M_2 \otimes M_3)} \in F(c_1+(c_2+c_3))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[left]{$i_1+(i_2+i_3)$} (B)
-(C) edge node[right]{$o_1+(o_2+o_3)$} (B);
+\node (B) at (2.25,0) {$c_1+(c_2+c_3)$};
+\node (C) at (4.5,0) {$b_1+(b_2+b_3)$};
+\node (D) at (2.25,-0.5) {$d_{M_1 \otimes (M_2 \otimes M_3)} \in F(c_1+(c_2+c_3))$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i_1+(i_2+i_3)$} (B)
+(C) edge node[above]{$o_1+(o_2+o_3)$} (B);
 \end{tikzpicture}
@@
 \]
-together with the morphism $\iota_a \colon F(a)(d_{(M_1 \otimes M_2) \otimes M_3}) \to d_{M_1 \otimes (M_2 \otimes M_3)}$.
-If we denote the above associator simply as $a$ and the left and right unitors as $\lambda$ and $\rho$, respectively, then given four objects in $F\textnormal{Cospan}(\bold{C})_1$, say $M_1, M_2, M_3$ and $M_4$:
+together with the isomorphism $\iota_a \colon F(a)(d_{(M_1 \otimes M_2) \otimes M_3}) \to d_{M_1 \otimes (M_2 \otimes M_3)}$.
+If we denote the above associator simply as $a$ and the left and right unitors as $\lambda$ and $\rho$, respectively, then given four objects in $\mathbb{F}\textnormal{Cospan}(\bold{C})_1$, say $M_1, M_2, M_3$ and $M_4$:
 \[
@@
 \node (E) at (3,0) {$a_2$};
-\node (F) at (4,1) {$c_2$};
+\node (F) at (4,0) {$c_2$};
 \node (G) at (5,0) {$b_2$};
 \node (H) at (4,-0.5) {$d_2 \in F(c_2)$};
-\node (I) at (0,-2) {$a_3$};
-\node (J) at (1,-1) {$c_3$};
-\node (K) at (2,-2) {$b_3$};
-\node (L) at (1,-2.5) {$d_3 \in F(c_3)$};
-\node (M) at (3,-2) {$a_4$};
-\node (N) at (4,-1) {$c_4$};
-\node (O) at (5,-2) {$b_4$};
-\node (P) at (4,-2.5) {$d_4 \in F(c_4)$};
+\node (I) at (0,-1.5) {$a_3$};
+\node (J) at (1,-1.5) {$c_3$};
+\node (K) at (2,-1.5) {$b_3$};
+\node (L) at (1,-2) {$d_3 \in F(c_3)$};
+\node (M) at (3,-1.5) {$a_4$};
+\node (N) at (4,-1.5) {$c_4$};
+\node (O) at (5,-1.5) {$b_4$};
+\node (P) at (4,-2) {$d_4 \in F(c_4)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \node (A) at (0,0) {$((M_1 \otimes M_2) \otimes M_3) \otimes M_4$};
-\node (B) at (2.25,1.5) {$(M_1 \otimes M_2) \otimes (M_3 \otimes M_4)$};
+\node (B) at (2.25,1) {$(M_1 \otimes M_2) \otimes (M_3 \otimes M_4)$};
 \node (C) at (4.5,0) {$M_1 \otimes (M_2 \otimes (M_3 \otimes M_4))$};
-\node (D) at (.75,-2) {$(M_1 \otimes (M_2 \otimes M_3)) \otimes M_4$};
-\node (E) at (3.75,-2) {$M_1 \otimes ((M_2 \otimes M_3) \otimes M_4)$};
+\node (D) at (.75,-1.5) {$(M_1 \otimes (M_2 \otimes M_3)) \otimes M_4$};
+\node (E) at (3.75,-1.5) {$M_1 \otimes ((M_2 \otimes M_3) \otimes M_4)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \node (A) at (-.5,0) {$F(aa)(d_{((M_1 \otimes M_2) \otimes M_3) \otimes M_4}) $};
-\node (B) at (2.25,1.5) {$F(a)(d_{(M_1 \otimes M_2) \otimes (M_3 \otimes M_4)})$};
+\node (B) at (2.25,1) {$F(a)(d_{(M_1 \otimes M_2) \otimes (M_3 \otimes M_4)})$};
 \node (C) at (5,0) {$d_{M_1 \otimes (M_2 \otimes (M_3 \otimes M_4))}$};
-\node (D) at (-.5,-2) {$F((1 \otimes a)a)(d_{(M_1 \otimes (M_2 \otimes M_3)) \otimes M_4}) $};
-\node (E) at (5,-2) {$F(1 \otimes a)(d_{M_1 \otimes ((M_2 \otimes M_3) \otimes M_4)}) $};
+\node (D) at (-.5,-1) {$F((1 \otimes a)a)(d_{(M_1 \otimes (M_2 \otimes M_3)) \otimes M_4}) $};
+\node (E) at (5,-1) {$F(1 \otimes a)(d_{M_1 \otimes ((M_2 \otimes M_3) \otimes M_4)}) $};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \node (A) at (0,0) {$(M_1 \otimes U_{0}) \otimes M_2$};
-\node (B) at (2.25,1.5) {$M_1 \otimes M_2$};
+\node (B) at (2.25,1) {$M_1 \otimes M_2$};
 \node (C) at (4.5,0) {$M_1 \otimes (U_0 \otimes M_2)$};
@@
 \node (A) at (0,0) {$F(\rho \otimes 1)(d_{(M_1 \otimes U_0) \otimes M_2})$};
-\node (B) at (2.25,1.5) {$d_{M_1 \otimes M_2}$};
+\node (B) at (2.25,1) {$d_{M_1 \otimes M_2}$};
 \node (C) at (4.5,0) {$F(1 \otimes \lambda)(d_{M_1 \otimes (U_0 \otimes M_2)}) $};
@@
 \node (A) at (0,0) {$M_1 \otimes M_2$};
-\node (B) at (2.25,1.5) {$M_1 \otimes M_2$};
+\node (B) at (2.25,1) {$M_1 \otimes M_2$};
 \node (C) at (4.5,0) {$M_2 \otimes M_1$};
 \path[->,font=\scriptsize,>=angle 90]
-(A) edge node[left]{$1$} (B)
-(C) edge node[right]{$\beta_{M_2,M_1}$} (B)
+(A) edge node[above]{$1$} (B)
+(C) edge node[above]{$\beta_{M_2,M_1}$} (B)
 (A) edge node[above]{$\beta_{M_1,M_2}$} (C);
@@
 \node (A) at (0,0) {$F(\beta_{c_1,c_2})(d_{M_1 \otimes M_2})$};
-\node (B) at (2.25,1.5) {$F(\beta_{c_1,c_2})(d_{M_1 \otimes M_2}) $};
+\node (B) at (2.25,1) {$F(\beta_{c_1,c_2})(d_{M_1 \otimes M_2}) $};
 \node (C) at (4.5,0) {$d_{M_2 \otimes M_1} $};
 \path[->,font=\scriptsize,>=angle 90]
-(A) edge node[left]{$1$} (B)
+(A) edge node[above]{$1$} (B)
 (C) edge node[right]{$F(\beta_{c_1,c_2})(\iota_{\beta_{M_2,M_1}})$} (B)
@@
 \node (E) at (3,0) {$b_1$};
-\node (F) at (4,1) {$e_1$};
+\node (F) at (4,0) {$e_1$};
 \node (G) at (5,0) {$x_1$};
 \node (H) at (4,-0.5) {$d_{M_2} \in F(e_1)$};
-\node (I) at (0,-2) {$a_2$};
-\node (J) at (1,-1) {$c_2$};
-\node (K) at (2,-2) {$b_2$};
-\node (L) at (1,-2.5) {$d_{N_1} \in F(c_2)$};
-\node (M) at (3,-2) {$b_2$};
-\node (N) at (4,-1) {$e_2$};
-\node (O) at (5,-2) {$x_2$};
-\node (P) at (4,-2.5) {$d_{N_2} \in F(e_2)$};
+\node (I) at (0,-1.5) {$a_2$};
+\node (J) at (1,-1.5) {$c_2$};
+\node (K) at (2,-1.5) {$b_2$};
+\node (L) at (1,-2) {$d_{N_1} \in F(c_2)$};
+\node (M) at (3,-1.5) {$b_2$};
+\node (N) at (4,-1.5) {$e_2$};
+\node (O) at (5,-1.5) {$x_2$};
+\node (P) at (4,-2) {$d_{N_2} \in F(e_2)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \node (A) at (0,0) {$a_1+a_2$};
-\node (B) at (1,1) {$(c_1+c_2)+_{b_1+b_2}(e_1+e_2)$};
-\node (C) at (2,0) {$x_1+x_2$};
-\node (D) at (1,-0.5) {$d_{(M_1 \otimes N_1) \odot (M_2 \otimes N_2)} \in F((c_1+c_2)+_{b_1+b_2}(e_1+e_2))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[left]{$j \psi(i_1+i_2)$} (B)
-(C) edge node[right]{$j \psi(o_1^\prime + o_2^\prime)$} (B);
+\node (B) at (2.5,0) {$(c_1+c_2)+_{b_1+b_2}(e_1+e_2)$};
+\node (C) at (5,0) {$x_1+x_2$};
+\node (D) at (2.5,-0.5) {$d_{(M_1 \otimes N_1) \odot (M_2 \otimes N_2)} \in F((c_1+c_2)+_{b_1+b_2}(e_1+e_2))$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$j \psi(i_1+i_2)$} (B)
+(C) edge node[above]{$j \psi(o_1^\prime + o_2^\prime)$} (B);
 \end{tikzpicture}
@@
 \node (A) at (0,0) {$a_1+a_2$};
-\node (B) at (1,1) {$(c_1+_{b_1} e_1) + (c_2 +_{b_2} e_2)$};
-\node (C) at (2,0) {$x_1+x_2$};
-\node (D) at (1,-0.5) {$d_{(M_1 \odot M_2) \otimes (N_1 \odot N_2)} \in F((c_1+_{b_1}e_1)+(c_2+_{b_2}e_2))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[left]{$(j \psi i_2)+(j \psi i_1)$} (B)
-(C) edge node[right]{$(j \psi o_2^\prime)+(j \psi o_1^\prime)$} (B);
+\node (B) at (2.5,0) {$(c_1+_{b_1} e_1) + (c_2 +_{b_2} e_2)$};
+\node (C) at (5,0) {$x_1+x_2$};
+\node (D) at (2.5,-0.5) {$d_{(M_1 \odot M_2) \otimes (N_1 \odot N_2)} \in F((c_1+_{b_1}e_1)+(c_2+_{b_2}e_2))$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$(j \psi i_2)+(j \psi i_1)$} (B)
+(C) edge node[above]{$(j \psi o_2^\prime)+(j \psi o_1^\prime)$} (B);
 \end{tikzpicture}
@@
 \node (A) at (0,0) {$a+b$};
-\node (B) at (1,1) {$a+b$};
+\node (B) at (1,0) {$a+b$};
 \node (C) at (2,0) {$a+b$};
-\node (D) at (3,0.5) {$!_{a+b} \in F(a+b)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[left]{$1_{a+b}$} (B)
-(C) edge node[right]{$1_{a+b}$} (B);
+\node (D) at (1,-0.5) {$!_{a+b} \in F(a+b)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$1_{a+b}$} (B)
+(C) edge node[above]{$1_{a+b}$} (B);
 \end{tikzpicture}
@@
 \node (A) at (0,0) {$a$};
-\node (B) at (1,1) {$a$};
+\node (B) at (1,0) {$a$};
 \node (C) at (2,0) {$a$};
@@
 \node (A) at (0,0) {$a+b$};
-\node (B) at (1,1) {$a+b$};
-\node (C) at (2,0) {$a+b$};
-\node (D) at (3.25,0.5) {$!_a + !_b \in F(a+b)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[left]{$1_a + 1_b$} (B)
-(C) edge node[right]{$1_a + 1_b$} (B);
+\node (B) at (1.25,0) {$a+b$};
+\node (C) at (2.5,0) {$a+b$};
+\node (D) at (1.25,-0.5) {$!_a + !_b \in F(a+b)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$1_a + 1_b$} (B)
+(C) edge node[above]{$1_a + 1_b$} (B);
 \end{tikzpicture}
@@
 \node (A') at (4.5,0.5) {$(M_1 \otimes (N_1 \otimes P_1)) \odot (M_2 \otimes (N_2 \otimes P_2))$};
-\node (B) at (0,-0.5) {$((M_1 \otimes N_1) \odot (M_2 \otimes N_2)) \otimes (P_1 \odot P_2)$};
-\node (C) at (4.5,-0.5) {$(M_1 \odot M_2) \otimes ((N_1 \otimes P_1) \odot (N_2 \otimes P_2))$};
-\node (C') at (0,-1.5) {$((M_1 \odot M_2) \otimes (N_1 \odot N_2)) \otimes (P_1 \odot P_2)$};
-\node (D) at (4.5,-1.5) {$(M_1 \odot M_2) \otimes ((N_1 \odot N_2) \otimes (P_1 \odot P_2))$};
+\node (B) at (0,-0.25) {$((M_1 \otimes N_1) \odot (M_2 \otimes N_2)) \otimes (P_1 \odot P_2)$};
+\node (C) at (4.5,-0.25) {$(M_1 \odot M_2) \otimes ((N_1 \otimes P_1) \odot (N_2 \otimes P_2))$};
+\node (C') at (0,-1) {$((M_1 \odot M_2) \otimes (N_1 \odot N_2)) \otimes (P_1 \odot P_2)$};
+\node (D) at (4.5,-1) {$(M_1 \odot M_2) \otimes ((N_1 \odot N_2) \otimes (P_1 \odot P_2))$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 			\node (k) at (0,0) {$k$};
-			\node (l) at (1,.5) {$l$};
+			\node (l) at (1,0) {$l$};
 			\node (m) at (2,0) {$m$};
-			\node (M1) at (-1,.25) {$M_1 =$};
-			\node (N1) at (3,.25) {$N_1 =$};
+			\node (M1) at (-1,0) {$M_1 =$};
+			\node (N1) at (3,0) {$N_1 =$};
 			\node (q) at (4,0) {$q$};
-			\node (r) at (5,.5) {$r$};
+			\node (r) at (5,0) {$r$};
 			\node (s) at (6,0) {$s$};
-			\node (P1) at (7,.25) {$P_1 =$};
+			\node (P1) at (7,0) {$P_1 =$};
 			\node (v) at (8,0) {$v$};
-			\node (w) at (9,.5) {$w$};
+			\node (w) at (9,0) {$w$};
 			\node (x) at (10,0) {$x$};
-			\node (m2) at (0,-2) {$m$};
+			\node (m2) at (0,-1.5) {$m$};
 			\node (n) at (1,-1.5) {$n$};
-			\node (p) at (2,-2) {$p$};
-			\node (M2) at (-1,-1.75) {$M_2 =$};
-			\node (N2) at (3,-1.75) {$N_2 =$};
-			\node (s2) at (4,-2) {$s$};
+			\node (p) at (2,-1.5) {$p$};
+			\node (M2) at (-1,-1.5) {$M_2 =$};
+			\node (N2) at (3,-1.5) {$N_2 =$};
+			\node (s2) at (4,-1.5) {$s$};
 			\node (t) at (5,-1.5) {$t$};
-			\node (u) at (6,-2) {$u$};
-			\node (P2) at (7,-1.75) {$P_2 =$};
-			\node (x2) at (8,-2) {$x$};
+			\node (u) at (6,-1.5) {$u$};
+			\node (P2) at (7,-1.5) {$P_2 =$};
+			\node (x2) at (8,-1.5) {$x$};
 			\node (y) at (9,-1.5) {$y$};
-			\node (z) at (10,-2) {$z$};
+			\node (z) at (10,-1.5) {$z$};
 \node (dM1) at (1,-0.5) {$d_{M_1} \in F(l)$};
-\node (dM2) at (1,-2.5) {$d_{M_2} \in F(n)$};
+\node (dM2) at (1,-2) {$d_{M_2} \in F(n)$};
 \node (dN1) at (5,-0.5) {$d_{N_1} \in F(r)$};
-\node (dN2) at (5,-2.5) {$d_{N_2} \in F(t)$};
+\node (dN2) at (5,-2) {$d_{N_2} \in F(t)$};
 \node (dP1) at (9,-0.5) {$d_{P_1} \in F(w)$};
-\node (dP2) at (9,-2.5) {$d_{P_2} \in F(y)$};
+\node (dP2) at (9,-2) {$d_{P_2} \in F(y)$};
 			\path[->,font=\scriptsize,>=angle 90]
@@
 			\node (c) at (6,0) {$v+x$};
-			\node (a2) at (-4,1.5) {$k+m$};
-			\node (b2) at (1,1.5) {$(l+(r+w)) +_{(m+(s+x))}(n+(t+y))$};
-			\node (c2) at (6,1.5) {$v+x$};
-                                \node (a3) at (-4,3) {$k+m$};
-			\node (b3) at (1,3) {$(l+_m n)+((r+w)+_{(s+x)}(t+y))$};
-			\node (c3) at (6,3) {$v+x$};
-                                \node (a4) at (-4,4.5) {$k+m$};
-			\node (b4) at (1,4.5) {$(l+_m n)+((r+_s t)+(w+_x y))$};
-			\node (c4) at (6,4.5) {$v+x$};
-                                \node (a5) at (-4,-1.5) {$k+m$};
-			\node (b5) at (1,-1.5) {$((l+r)+_{(m+s)}(n+t))+(w+_x y)$};
-			\node (c5) at (6,-1.5) {$v+x$};
-                                \node (a6) at (-4,-3) {$k+m$};
-			\node (b6) at (1,-3) {$((l+_m n)+(r+_s t))+(w+_x y)$};
-			\node (c6) at (6,-3) {$v+x$};
-                                \node (a7) at (-4,-4.5) {$k+m$};
-			\node (b7) at (1,-4.5) {$(l+_m n)+((r+_s t)+(w+_x y))$};
-			\node (c7) at (6,-4.5) {$v+x$};
+			\node (a2) at (-4,1) {$k+m$};
+			\node (b2) at (1,1) {$(l+(r+w)) +_{(m+(s+x))}(n+(t+y))$};
+			\node (c2) at (6,1) {$v+x$};
+                                \node (a3) at (-4,2) {$k+m$};
+			\node (b3) at (1,2) {$(l+_m n)+((r+w)+_{(s+x)}(t+y))$};
+			\node (c3) at (6,2) {$v+x$};
+                                \node (a4) at (-4,3) {$k+m$};
+			\node (b4) at (1,3) {$(l+_m n)+((r+_s t)+(w+_x y))$};
+			\node (c4) at (6,3) {$v+x$};
+                                \node (a5) at (-4,-1) {$k+m$};
+			\node (b5) at (1,-1) {$((l+r)+_{(m+s)}(n+t))+(w+_x y)$};
+			\node (c5) at (6,-1) {$v+x$};
+                                \node (a6) at (-4,-2) {$k+m$};
+			\node (b6) at (1,-2) {$((l+_m n)+(r+_s t))+(w+_x y)$};
+			\node (c6) at (6,-2) {$v+x$};
+                                \node (a7) at (-4,-3) {$k+m$};
+			\node (b7) at (1,-3) {$(l+_m n)+((r+_s t)+(w+_x y))$};
+			\node (c7) at (6,-3) {$v+x$};
 			\path[->,font=\scriptsize,>=angle 90]
@@
 \node (B) at (3,0) {$(N_1 \odot N_2) \otimes (M_1 \odot M_2)$};
-\node (C) at (0,-1) {$(M_1 \otimes N_1) \odot (M_2 \otimes N_2)$};
-\node (D) at (3,-1) {$(N_1 \otimes M_1) \odot (N_2 \otimes M_2)$};
+\node (C) at (0,-.75) {$(M_1 \otimes N_1) \odot (M_2 \otimes N_2)$};
+\node (D) at (3,-.75) {$(N_1 \otimes M_1) \odot (N_2 \otimes M_2)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 			\node (c) at (6,0) {$s+u$};
-			\node (a2) at (-4,1.5) {$k+m$};
-			\node (b2) at (1,1.5) {$(r +_s t) + (l +_m n)$};
-			\node (c2) at (6,1.5) {$s+u$};
-                                \node (a3) at (-4,3) {$k+m$};
-			\node (b3) at (1,3) {$(r+l) +_{(s+m)} (t+n)$};
-			\node (c3) at (6,3) {$s+u$};
-                                \node (a5) at (-4,-1.5) {$k+m$};
-			\node (b5) at (1,-1.5) {$(l+r) +_{(m+s)} (n+t)$};
-			\node (c5) at (6,-1.5) {$s+u$};
-                                \node (a6) at (-4,-3) {$k+m$};
-			\node (b6) at (1,-3) {$(r+l) +_{(s+m)} (t+n)$};
-			\node (c6) at (6,-3) {$s+u$};
+			\node (a2) at (-4,1) {$k+m$};
+			\node (b2) at (1,1) {$(r +_s t) + (l +_m n)$};
+			\node (c2) at (6,1) {$s+u$};
+                                \node (a3) at (-4,2) {$k+m$};
+			\node (b3) at (1,2) {$(r+l) +_{(s+m)} (t+n)$};
+			\node (c3) at (6,2) {$s+u$};
+                                \node (a5) at (-4,-1) {$k+m$};
+			\node (b5) at (1,-1) {$(l+r) +_{(m+s)} (n+t)$};
+			\node (c5) at (6,-1) {$s+u$};
+                                \node (a6) at (-4,-2) {$k+m$};
+			\node (b6) at (1,-2) {$(r+l) +_{(s+m)} (t+n)$};
+			\node (c6) at (6,-2) {$s+u$};
 			\path[->,font=\scriptsize,>=angle 90]
@@
 \node (A) at (0,0) {$c$};
-\node (B) at (1,1) {$c^\prime$};
+\node (B) at (1,0) {$c^\prime$};
 \node (C) at (2,0) {$c^\prime$};
-\node (D) at (3,0.5) {$!_{c^\prime} \in F(c^\prime)$};
+\node (D) at (1,-0.5) {$!_{c^\prime} \in F(c^\prime)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \node (A) at (0,0) {$c^\prime$};
-\node (B) at (1,1) {$c^\prime$};
+\node (B) at (1,0) {$c^\prime$};
 \node (C) at (2,0) {$c$};
-\node (D) at (3,0.5) {$!_{c^\prime} \in F(c^\prime)$};
+\node (D) at (4,0) {$!_{c^\prime} \in F(c^\prime)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \node (A) at (0,0) {$a$};
-\node (B) at (1,1) {$c$};
+\node (B) at (1,0) {$c$};
 \node (C) at (2,0) {$b$};
-\node (D) at (3,0.5) {$d \in F(c)$};
+\node (D) at (4,0) {$d \in F(c)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \node (A) at (0,0) {$a$};
-\node (B) at (1,1) {$c$};
+\node (B) at (1,0.5) {$c$};
 \node (C) at (2,0) {$b$};
-\node (E) at (1,-1) {$c^\prime$};
+\node (E) at (1,-0.5) {$c^\prime$};
 \node (D) at (3,0.5) {$d \in F(c)$};
@@
 \node (A) at (0,0) {$a$};
-\node (B) at (1,1) {$c$};
-\node (B') at (1,-1) {$c^\prime$};
+\node (B) at (1,0.5) {$c$};
+\node (B') at (1,-0.5) {$c^\prime$};
 \node (C) at (2,0) {$b$};
@@
 \node (A) at (0,0) {$a$};
-\node (B) at (1,-1) {$c^\prime$};
+\node (B) at (1,0) {$c^\prime$};
 \node (C) at (2,0) {$b$};
-\node (D) at (3,-0.5) {$d^\prime \in F(c^\prime)$};
+\node (D) at (4,0) {$d^\prime \in F(c^\prime)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \node (A) at (0,0) {$a$};
-\node (B') at (1,1) {$c$};
-\node (B) at (1,-1) {$c^\prime$};
+\node (B') at (1,0.5) {$c$};
+\node (B) at (1,-0.5) {$c^\prime$};
 \node (C) at (2,0) {$b$};
@@
 \node (A) at (0,0) {$a$};
-\node (B) at (1,1) {$c$};
+\node (B) at (1,0) {$c$};
 \node (C) at (2,0) {$b$};
 \node (D) at (1,-0.5) {$d \in F(c)$};
-\node (E) at (2.75,0.25) {$\mapsto$};
+\node (E) at (2.75,0) {$\mapsto$};
 \node (A') at (3.5,0) {$H(a)$};
-\node (B') at (4.5,1) {$H(c)$};
+\node (B') at (4.5,0) {$H(c)$};
 \node (C') at (5.5,0) {$H(b)$};
@@
 \path[->,font=\scriptsize,>=angle 90]
-(A) edge node[left]{$i$} (B)
-(C) edge node[right]{$o$} (B)
-(A') edge node[left]{$H(i)$} (B')
-(C') edge node[right]{$H(o)$} (B');
+(A) edge node[above]{$i$} (B)
+(C) edge node[above]{$o$} (B)
+(A') edge node[above]{$H(i)$} (B')
+(C') edge node[above]{$H(o)$} (B');
 \end{tikzpicture}
@@
 \node (A) at (0,-0.5) {$E(\bold{1}) \cong \bold{1}$};
-\node (B) at (1.5,0.25) {$E(F(c))$};
-\node (D) at (1.5,-1.25) {$E(F(c^\prime))$};
+\node (B) at (1.5,0) {$E(F(c))$};
+\node (D) at (1.5,-1) {$E(F(c^\prime))$};
 \node (C) at (1,-0.5) {$\Swarrow$};
@@
 \node (A) at (0,-0.5) {$E(\bold{1}) \cong \bold{1}$};
-\node (B) at (1.5,0.25) {$F^\prime(H(c))$};
-\node (D) at (1.5,-1.25) {$F^\prime(H(c^\prime))$};
+\node (B) at (1.5,0) {$F^\prime(H(c))$};
+\node (D) at (1.5,-1) {$F^\prime(H(c^\prime))$};
 \node (C) at (1,-0.5) {$\Swarrow$};
@@
 \node (A) at (0,0) {$a_1$};
-\node (B) at (1,1) {$c_1$};
+\node (B) at (1,0) {$c_1$};
 \node (C) at (2,0) {$b$};
@@
 \node (E) at (3,0) {$b$};
-\node (F) at (4,1) {$c_2$};
+\node (F) at (4,0) {$c_2$};
 \node (G) at (5,0) {$a_2$};
@@
 \node (A) at (0,0) {$a_1$};
-\node (B) at (1,1) {$c_1+_b c_2$};
-\node (C) at (2,0) {$a_2$};
-\node (D) at (1,-0.5) {$d \in F(c_1 +_b c_2)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[left]{$\psi j_{c_1} i_1$} (B)
-(C) edge node[right]{$\psi j_{c_2} o_2$} (B);
+\node (B) at (1.5,0) {$c_1+_b c_2$};
+\node (C) at (3,0) {$a_2$};
+\node (D) at (1.5,-0.5) {$d \in F(c_1 +_b c_2)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$\psi j_{c_1} i_1$} (B)
+(C) edge node[above]{$\psi j_{c_2} o_2$} (B);
 \end{tikzpicture}
@@
 \node (A) at (0,0) {$H(a_1)$};
-\node (B) at (1,1) {$H(c_1+_b c_2)$};
-\node (C) at (2,0) {$H(a_2)$};
-\node (D) at (1,-0.5) {$E(d) \in F^\prime(H(c_1 +_b c_2))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[left]{$H(\psi j_{c_1} i_1)$} (B)
-(C) edge node[right]{$H(\psi j_{c_2} o_2)$} (B);
+\node (B) at (1.5,0) {$H(c_1+_b c_2)$};
+\node (C) at (3,0) {$H(a_2)$};
+\node (D) at (1.5,-0.5) {$E(d) \in F^\prime(H(c_1 +_b c_2))$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$H(\psi j_{c_1} i_1)$} (B)
+(C) edge node[above]{$H(\psi j_{c_2} o_2)$} (B);
 \end{tikzpicture}
@@
 \node (A) at (0,0) {$H(a_1)$};
-\node (B) at (1,1) {$H(c_1)$};
+\node (B) at (1,0) {$H(c_1)$};
 \node (C) at (2,0) {$H(b)$};
@@
 \node (E) at (3,0) {$H(b)$};
-\node (F) at (4,1) {$H(c_2)$};
+\node (F) at (4,0) {$H(c_2)$};
 \node (G) at (5,0) {$H(a_2)$};
@@
 \path[->,font=\scriptsize,>=angle 90]
-(A) edge node[left]{$H(i_1)$} (B)
-(C) edge node[right]{$H(o_1)$} (B)
-(E) edge node[left]{$H(i_2)$} (F)
-(G) edge node[right]{$H(o_2)$} (F);
+(A) edge node[above]{$H(i_1)$} (B)
+(C) edge node[above]{$H(o_1)$} (B)
+(E) edge node[above]{$H(i_2)$} (F)
+(G) edge node[above]{$H(o_2)$} (F);
 \end{tikzpicture}
@@
 \node (A) at (0,0) {$H(a_1)$};
-\node (B) at (1,1) {$H(c_1)+_{H(b)} H(c_2)$};
-\node (C) at (2,0) {$H(a_2)$};
-\node (D) at (1,-0.5) {$d^\prime \in F^\prime(H(c_1) +_{H(b)} H(c_2))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[left]{$\Psi j_{H(c_1)} H(i_1)$} (B)
-(C) edge node[right]{$\Psi j_{H(c_2)} H(o_2)$} (B);
+\node (B) at (2,0) {$H(c_1)+_{H(b)} H(c_2)$};
+\node (C) at (4,0) {$H(a_2)$};
+\node (D) at (2,-0.5) {$d^\prime \in F^\prime(H(c_1) +_{H(b)} H(c_2))$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$\Psi j_{H(c_1)} H(i_1)$} (B)
+(C) edge node[above]{$\Psi j_{H(c_2)} H(o_2)$} (B);
 \end{tikzpicture}
@@
 \node (A) at (0,0) {$a_1+a_2$};
-\node (B) at (1,1) {$c_1+c_2$};
-\node (C) at (2,0) {$b_1+b_2$};
-\node (D) at (1,-0.5) {$d_1+d_2 \in F(c_1)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[left]{$i_1+i_2$} (B)
-(C) edge node[right]{$o_1+o_2$} (B);
+\node (B) at (1.5,0) {$c_1+c_2$};
+\node (C) at (3,0) {$b_1+b_2$};
+\node (D) at (1.5,-0.5) {$d_1+d_2 \in F(c_1)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i_1+i_2$} (B)
+(C) edge node[above]{$o_1+o_2$} (B);
 \end{tikzpicture}
@@
 \node (A) at (0,0) {$H(a_1+a_2)$};
-\node (B) at (1,1) {$H(c_1+c_2)$};
-\node (C) at (2,0) {$H(b_1+b_2)$};
-\node (D) at (1,-0.5) {$E(d_1+d_2) \in E(F(c_1+c_2)) = F^\prime(H(c_1+c_2))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[left]{$H(i_1+i_2)$} (B)
-(C) edge node[right]{$H(o_1+o_2)$} (B);
+\node (B) at (2,0) {$H(c_1+c_2)$};
+\node (C) at (4,0) {$H(b_1+b_2)$};
+\node (D) at (2,-0.5) {$E(d_1+d_2) \in E(F(c_1+c_2)) = F^\prime(H(c_1+c_2))$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$H(i_1+i_2)$} (B)
+(C) edge node[above]{$H(o_1+o_2)$} (B);
 \end{tikzpicture}
@@
 \node (A) at (0,0) {$H(a_1)$};
-\node (B) at (1,1) {$H(c_1)$};
+\node (B) at (1,0) {$H(c_1)$};
 \node (C) at (2,0) {$H(b_1)$};
@@
 \node (E) at (3,0) {$H(a_2)$};
-\node (F) at (4,1) {$H(c_2)$};
+\node (F) at (4,0) {$H(c_2)$};
 \node (G) at (5,0) {$H(b_2)$};
@@
 \node (A) at (0,0) {$H(a_1)+H(a_2)$};
-\node (B) at (1,1) {$H(c_1)+H(c_2)$};
-\node (C) at (2,0) {$H(b_1)+H(b_2)$};
-\node (D) at (1,-0.5) {$E(d_1)+E(d_2) \in F^\prime(H(c_1)+H(c_2))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[left]{$H(i_1)+H(i_2)$} (B)
-(C) edge node[right]{$H(o_1)+H(o_2)$} (B);
+\node (B) at (2,0) {$H(c_1)+H(c_2)$};
+\node (C) at (4,0) {$H(b_1)+H(b_2)$};
+\node (D) at (2,-0.5) {$E(d_1)+E(d_2) \in F^\prime(H(c_1)+H(c_2))$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$H(i_1)+H(i_2)$} (B)
+(C) edge node[above]{$H(o_1)+H(o_2)$} (B);
 \end{tikzpicture}
@@
 \node (A) at (0,0) {$1_\bold{C}$};
-\node (B) at (1,1) {$1_\bold{C}$};
+\node (B) at (1,0) {$1_\bold{C}$};
 \node (C) at (2,0) {$1_\bold{C}$};
@@
 \path[->,font=\scriptsize,>=angle 90]
-(A) edge node[left]{$1$} (B)
-(C) edge node[right]{$1$} (B);
+(A) edge node[above]{$1$} (B)
+(C) edge node[above]{$1$} (B);
 \end{tikzpicture}
@@
 \node (A) at (0,0) {$H(1_\bold{C})$};
-\node (B) at (1,1) {$H(1_\bold{C})$};
+\node (B) at (1,0) {$H(1_\bold{C})$};
 \node (C) at (2,0) {$H(1_\bold{C})$};
-\node (E) at (3,0.5) {$=$};
+\node (E) at (3,0) {$=$};
 \node (F) at (4,0) {$1_\bold{C^\prime}$};
-\node (G) at (5,1) {$1_\bold{C^\prime}$};
+\node (G) at (5,0) {$1_\bold{C^\prime}$};
 \node (H) at (6,0) {$1_\bold{C^\prime}$};
@@
 \path[->,font=\scriptsize,>=angle 90]
-(A) edge node[left]{$1$} (B)
-(C) edge node[right]{$1$} (B)
-(F) edge node[left]{$1$} (G)
-(H) edge node[right]{$1$} (G);
+(A) edge node[above]{$1$} (B)
+(C) edge node[above]{$1$} (B)
+(F) edge node[above]{$1$} (G)
+(H) edge node[above]{$1$} (G);
 \end{tikzpicture}
@@
 \node (A) at (0,0) {$d^\prime$};
-\node (B) at (0,-1.5) {$d_{2}$};
-\node (C) at (1.5,-1.5) {$d_{1}$};
-\node (H) at (2,-0.5) {$P$};
-\node (D) at (2,-.75) {$\mapsto$};
+\node (B) at (0,-1) {$d_{2}$};
+\node (C) at (1.5,-1) {$d_{1}$};
+\node (H) at (2,-0.25) {$P$};
+\node (D) at (2,-.5) {$\mapsto$};
 \node (E) at (3,0) {$P(d^\prime)$};
-\node (F) at (3,-1.5) {$P(d_{2})$};
-\node (G) at (4.5,-1.5) {$P(d_{1})$};
+\node (F) at (3,-1) {$P(d_{2})$};
+\node (G) at (4.5,-1) {$P(d_{1})$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \end{thm}
-\begin{thm}
+\begin{prop}
 Let $\mathbb{C}$ and $\mathbb{D}$ be symmetric monoidal double categories and let $\mathbb{F} \colon \mathbb{C} \to \mathbb{D}$ be a symmetric monoidal strong double functor.
 If $\mathbb{F}$ is part of a double equivalence, then $\mathbb{F}$ is in fact part of a symmetric monoidal double equivalence, and $\mathbb{C}$ and $\mathbb{D}$ are equivalent as symmetric monoidal double categories.
-\end{thm}
-\begin{proof}
-\textbf{Prove this...is there anything to even prove?}
-\end{proof}
+\end{prop}
 Our next goal is to show that the symmetric monoidal double category $\mathbb{F}\textnormal{Cospan}(\bold{C})$ of Section \ref{DecCospansDoublecat} is equivalent as a symmetric monoidal double category to the symmetric monoidal double category $_L \mathbb{C}\textnormal{sp}(\bold{D})$ obtained using structured cospans.
@@
 \node (A) at (0,0) {$L(c)$};
-\node (B) at (1,1) {$d$};
+\node (B) at (1,0) {$d$};
 \node (C) at (2,0) {$L(c^\prime)$};

### 2018-09-30 EquivCompFrameworks_20180911kc.tex
even more diagram condensing

@@
 \node (A) at (0,0) {$c_1$};
-\node (B) at (1,1) {$c$};
+\node (B) at (1,0) {$c$};
 \node (C) at (2,0) {$c_2$};
-\node (D) at (3,0.5) {$d \in F(c)$};
+\node (D) at (3,0) {$d \in F(c)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \node (A) at (0,0) {$L(c)$};
-\node (B) at (1,1) {$d$};
+\node (B) at (1,0) {$d$};
 \node (C) at (2,0) {$L(c^\prime)$};
 \path[->,font=\scriptsize,>=angle 90]
-(A) edge node[left]{$i$} (B)
-(C) edge node[right]{$o$} (B);
+(A) edge node[above]{$i$} (B)
+(C) edge node[above]{$o$} (B);
 \end{tikzpicture}
@@
 \node (A) at (0,0) {$c$};
-\node (B) at (1,1) {$R(d)$};
+\node (B) at (1,0) {$R(d)$};
 \node (C) at (2,0) {$c^\prime$};
-\node (D) at (3,0.5) {$d \in F(R(d))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[left]{$R(i) {\eta_c}$} (B)
-(C) edge node[right]{$R(o) {\eta_{c^\prime}}$} (B);
+\node (D) at (3,0) {$d \in F(R(d))$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$R(i) {\eta_c}$} (B)
+(C) edge node[above]{$R(o) {\eta_{c^\prime}}$} (B);
 \end{tikzpicture}
@@
 \node (A) at (0,0) {$c_1$};
-\node (B) at (1,1) {$c$};
+\node (B) at (1,0) {$c$};
 \node (C) at (2,0) {$c_2$};
-\node (D) at (3,0.5) {$d \in F(c)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[left]{$i$} (B)
-(C) edge node[right]{$o$} (B);
+\node (D) at (3,0) {$d \in F(c)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i$} (B)
+(C) edge node[above]{$o$} (B);
 \end{tikzpicture}
@@
 \node (A) at (0,0) {$L(c_1)$};
-\node (B) at (1,1) {$d$};
+\node (B) at (1,0) {$d$};
 \node (C) at (2,0) {$L(c_2)$};
 \path[->,font=\scriptsize,>=angle 90]
-(A) edge node[left]{$i^\prime$} (B)
-(C) edge node[right]{$o^\prime$} (B);
+(A) edge node[above]{$i^\prime$} (B)
+(C) edge node[above]{$o^\prime$} (B);
 \end{tikzpicture}
@@
 \node (A) at (0,0) {$c$};
-\node (B) at (1,1) {$c$};
+\node (B) at (1,0) {$c$};
 \node (C) at (2,0) {$c$};
-\node (D) at (3,0.5) {$!_c \in F(c)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[left]{$1$} (B)
-(C) edge node[right]{$1$} (B);
+\node (D) at (3,0) {$!_c \in F(c)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$1$} (B)
+(C) edge node[above]{$1$} (B);
 \end{tikzpicture}
@@
 \node (A) at (0,0) {$L(c)$};
-\node (B) at (1,1) {$L(c)$};
+\node (B) at (1,0) {$L(c)$};
 \node (C) at (2,0) {$L(c)$};
@@
 \node (A) at (0,0) {$c$};
-\node (B) at (1,1) {$R(L(c))$};
+\node (B) at (1,0) {$R(L(c))$};
 \node (C) at (2,0) {$c$};
-\node (D) at (3.25,0.5) {$!_c \in F(R(L(c)))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[left]{$\eta_c$} (B)
-(C) edge node[right]{$\eta_c$} (B);
+\node (D) at (3.25,0) {$!_c \in F(R(L(c)))$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$\eta_c$} (B)
+(C) edge node[above]{$\eta_c$} (B);
 \end{tikzpicture}
@@
 \node (A) at (0,0) {$L(c_1)$};
-\node (B) at (1,1) {$d$};
+\node (B) at (1,0) {$d$};
 \node (C) at (2,0) {$L(c_2)$};
 \node (D) at (3,0) {$L(c_2)$};
-\node (E) at (4,1) {$d^\prime$};
+\node (E) at (4,0) {$d^\prime$};
 \node (F) at (5,0) {$L(c_3)$};
@@
 \path[->,font=\scriptsize,>=angle 90]
-(A) edge node[left]{$i$} (B)
-(C) edge node[right]{$o$} (B)
-(D) edge node[left]{$i^\prime$} (E)
-(F) edge node[right]{$o^\prime$} (E);
+(A) edge node[above]{$i$} (B)
+(C) edge node[above]{$o$} (B)
+(D) edge node[above]{$i^\prime$} (E)
+(F) edge node[above]{$o^\prime$} (E);
 \end{tikzpicture}
@@
 \node (A) at (0,0) {$c_1$};
-\node (B) at (1,1) {$R(d)$};
+\node (B) at (1,0) {$R(d)$};
 \node (C) at (2,0) {$c_2$};
 \node (D) at (3,0) {$c_2$};
-\node (E) at (4,1) {$R(d^\prime)$};
+\node (E) at (4,0) {$R(d^\prime)$};
 \node (F) at (5,0) {$c_3$};
@@
 \path[->,font=\scriptsize,>=angle 90]
-(A) edge node[left]{$R(i) \eta_{c_1}$} (B)
-(C) edge node[right]{$R(o) \eta_{c_2}$} (B)
-(D) edge node[left]{$R(i^\prime) \eta_{c_2}$} (E)
-(F) edge node[right]{$R(o^\prime) \eta_{c_3}$} (E);
+(A) edge node[above]{$R(i) \eta_{c_1}$} (B)
+(C) edge node[above]{$R(o) \eta_{c_2}$} (B)
+(D) edge node[above]{$R(i^\prime) \eta_{c_2}$} (E)
+(F) edge node[above]{$R(o^\prime) \eta_{c_3}$} (E);
 \end{tikzpicture}
@@
 \node (A) at (0,0) {$c_1$};
-\node (B) at (1,1) {$R(d)+_{c_2}R(d^\prime)$};
-\node (C) at (2,0) {$c_3$};
-\node (G) at (1,-0.5) {$\hat{d} \in F(R(d)+_{c_2}R(d^\prime))$};
+\node (B) at (1.5,0) {$R(d)+_{c_2}R(d^\prime)$};
+\node (C) at (3,0) {$c_3$};
+\node (G) at (1.5,-0.5) {$\hat{d} \in F(R(d)+_{c_2}R(d^\prime))$};
 %\node (D) at (3,0.5) {$!_c \in F(c)$};
 \path[->,font=\scriptsize,>=angle 90]
-(A) edge node[left]{$j \psi R(i) \eta_{c_1}$} (B)
-(C) edge node[right]{$j \psi R(o^\prime) \eta_{c_3}$} (B);
+(A) edge node[above]{$j \psi R(i) \eta_{c_1}$} (B)
+(C) edge node[above]{$j \psi R(o^\prime) \eta_{c_3}$} (B);
 \end{tikzpicture}
@@
 \node (A) at (0,0) {$L(c_1)$};
-\node (B) at (1,1) {$d+_{L(c_2)}d^\prime$};
-\node (C) at (2,0) {$L(c_3)$};
+\node (B) at (1.25,0) {$d+_{L(c_2)}d^\prime$};
+\node (C) at (2.5,0) {$L(c_3)$};
 %\node (G) at (1,-0.5) {$\hat{d} \in F(R(d)+_{c_2}R(d^\prime))$};
@@
 \path[->,font=\scriptsize,>=angle 90]
-(A) edge node[left]{$J \zeta i$} (B)
-(C) edge node[right]{$J \zeta o^\prime$} (B);
+(A) edge node[above]{$J \zeta i$} (B)
+(C) edge node[above]{$J \zeta o^\prime$} (B);
 \end{tikzpicture}
@@
 \node (A) at (0,0) {$c_1$};
-\node (B) at (1,1) {$R(d+_{L(c_2)}d^\prime)$};
-\node (C) at (2,0) {$c_3$};
-\node (G) at (1,-0.5) {$d+_{L(c_2)} d^\prime \in F(R(d+_{L(c_2)}d^\prime))$};
+\node (B) at (1.5,0) {$R(d+_{L(c_2)}d^\prime)$};
+\node (C) at (3,0) {$c_3$};
+\node (G) at (1.5,-0.5) {$d+_{L(c_2)} d^\prime \in F(R(d+_{L(c_2)}d^\prime))$};
 %\node (D) at (3,0.5) {$!_c \in F(c)$};
 \path[->,font=\scriptsize,>=angle 90]
-(A) edge node[left]{$R(J \zeta i) \eta_{c_1}$} (B)
-(C) edge node[right]{$R(J \zeta o^\prime) \eta_{c_3}$} (B);
+(A) edge node[above]{$R(J \zeta i) \eta_{c_1}$} (B)
+(C) edge node[above]{$R(J \zeta o^\prime) \eta_{c_3}$} (B);
 \end{tikzpicture}
@@
 \node (A) at (0,0) {$1_\bold{C}$};
-\node (B) at (1,1) {$1_\bold{C}$};
+\node (B) at (1,0) {$1_\bold{C}$};
 \node (C) at (2,0) {$1_\bold{C}$};
-\node (D) at (3,0.5) {$!_{1_{\bold{C}}} \in F(1_\bold{C})$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[left]{$1$} (B)
-(C) edge node[right]{$1$} (B);
+\node (D) at (3,0) {$!_{1_{\bold{C}}} \in F(1_\bold{C})$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$1$} (B)
+(C) edge node[above]{$1$} (B);
 \end{tikzpicture}
@@
 \node (A) at (0,0) {$L(1_\bold{C})$};
-\node (B) at (1,1) {$L(1_\bold{C})$};
+\node (B) at (1,0) {$L(1_\bold{C})$};
 \node (C) at (2,0) {$L(1_\bold{C})$};
@@
 \node (A) at (0,0) {$1_\bold{C}$};
-\node (B) at (1,1) {$R(L(1_\bold{C}))$};
-\node (C) at (2,0) {$1_\bold{C}$};
-\node (D) at (3.5,0.5) {$!_{1_\bold{C}} \in F(R(L(1_\bold{C}))) \cong F(1_\bold{C})$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[left]{${\eta_{1_\bold{C}}}$} (B)
-(C) edge node[right]{${\eta_{1_\bold{C}}}$} (B);
+\node (B) at (1.25,0) {$R(L(1_\bold{C}))$};
+\node (C) at (2.5,0) {$1_\bold{C}$};
+\node (D) at (4,0) {$!_{1_\bold{C}} \in F(R(L(1_\bold{C}))) \cong F(1_\bold{C})$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{${\eta_{1_\bold{C}}}$} (B)
+(C) edge node[above]{${\eta_{1_\bold{C}}}$} (B);
 \end{tikzpicture}
@@
 \node (A) at (0,0) {$L(c_1)$};
-\node (B) at (1,1) {$d$};
+\node (B) at (1,0) {$d$};
 \node (C) at (2,0) {$L(c_2)$};
 \node (D) at (3,0) {$L(c_1^\prime)$};
-\node (E) at (4,1) {$d^\prime$};
+\node (E) at (4,0) {$d^\prime$};
 \node (F) at (5,0) {$L(c_2^\prime)$};
@@
 \node (A) at (0,0) {$c_1$};
-\node (B) at (1,1) {$R(d)$};
+\node (B) at (1,0) {$R(d)$};
 \node (C) at (2,0) {$c_2$};
 \node (D) at (3,0) {$c_1^\prime$};
-\node (E) at (4,1) {$R(d^\prime)$};
+\node (E) at (4,0) {$R(d^\prime)$};
 \node (F) at (5,0) {$c_2^\prime$};
@@
 \path[->,font=\scriptsize,>=angle 90]
-(A) edge node[left]{$R(i) \eta_{c_1}$} (B)
-(C) edge node[right]{$R(o) \eta_{c_2}$} (B)
-(D) edge node[left]{$R(i^\prime) \eta_{c_1^\prime}$} (E)
-(F) edge node[right]{$R(o^\prime) \eta_{c_2^\prime}$} (E);
+(A) edge node[above]{$R(i) \eta_{c_1}$} (B)
+(C) edge node[above]{$R(o) \eta_{c_2}$} (B)
+(D) edge node[above]{$R(i^\prime) \eta_{c_1^\prime}$} (E)
+(F) edge node[above]{$R(o^\prime) \eta_{c_2^\prime}$} (E);
 \end{tikzpicture}
@@
 \node (A) at (0,0) {$c_1+c_1^\prime$};
-\node (B) at (1,1) {$R(d)+R(d^\prime)$};
-\node (C) at (2,0) {$c_2+c_2^\prime$};
-\node (D) at (1,-0.5) {$\hat{d} \in F(R(d)+R(d^\prime)$}; 
+\node (B) at (2.25,0) {$R(d)+R(d^\prime)$};
+\node (C) at (4.5,0) {$c_2+c_2^\prime$};
+\node (D) at (2.25,-0.5) {$\hat{d} \in F(R(d)+R(d^\prime)$}; 
 %\node (D) at (3,0.5) {$!_c \in F(c)$};
 \path[->,font=\scriptsize,>=angle 90]
-(A) edge node[left]{$R(i) \eta_{c_1} +R(i^\prime) \eta_{c_1^\prime}$} (B)
-(C) edge node[right]{$R(o) \eta_{c_2} + R(o) \eta_{c_2^\prime}$} (B);
+(A) edge node[above]{$R(i) \eta_{c_1} +R(i^\prime) \eta_{c_1^\prime}$} (B)
+(C) edge node[above]{$R(o) \eta_{c_2} + R(o) \eta_{c_2^\prime}$} (B);
 \end{tikzpicture}
@@
 \node (A) at (0,0) {$L(c_1+c_1^\prime)$};
-\node (B) at (1,1) {$d+d^\prime$};
-\node (C) at (2,0) {$L(c_2+c_2^\prime)$};
+\node (B) at (1.5,0) {$d+d^\prime$};
+\node (C) at (3,0) {$L(c_2+c_2^\prime)$};
 %\node (D) at (3,0.5) {$!_c \in F(c)$};
 \path[->,font=\scriptsize,>=angle 90]
-(A) edge node[left]{$i+i^\prime$} (B)
-(C) edge node[right]{$o+o^\prime$} (B);
+(A) edge node[above]{$i+i^\prime$} (B)
+(C) edge node[above]{$o+o^\prime$} (B);
 \end{tikzpicture}
@@
 \node (A) at (0,0) {$c_1+c_1^\prime$};
-\node (B) at (1,1) {$R(d+d^\prime)$};
-\node (C) at (2,0) {$c_2+c_2^\prime$};
-\node (D) at (1,-0.5) {$d+d^\prime \in F(R(d+d^\prime))$};
+\node (B) at (2,0) {$R(d+d^\prime)$};
+\node (C) at (4,0) {$c_2+c_2^\prime$};
+\node (D) at (2,-0.5) {$d+d^\prime \in F(R(d+d^\prime))$};
 %\node (D) at (3,0.5) {$!_c \in F(c)$};
 \path[->,font=\scriptsize,>=angle 90]
-(A) edge node[left]{$R(i+i^\prime) \eta_{c_1+c_1^\prime}$} (B)
-(C) edge node[right]{$R(o+o^\prime) \eta_{c_2+c_2^\prime}$} (B);
+(A) edge node[above]{$R(i+i^\prime) \eta_{c_1+c_1^\prime}$} (B)
+(C) edge node[above]{$R(o+o^\prime) \eta_{c_2+c_2^\prime}$} (B);
 \end{tikzpicture}
@@
 \node (A) at (0,0) {$L(c_1)$};
-\node (B) at (1,1) {$d_1$};
+\node (B) at (1,0) {$d_1$};
 \node (C) at (2,0) {$L(c_1^\prime)$};
 \node (D) at (3,0) {$L(c_2)$};
-\node (E) at (4,1) {$d_2$};
+\node (E) at (4,0) {$d_2$};
 \node (F) at (5,0) {$L(c_2^\prime)$};
 \node (G) at (6,0) {$L(c_3)$};
-\node (H) at (7,1) {$d_3$};
+\node (H) at (7,0) {$d_3$};
 \node (I) at (8,0) {$L(c_3^\prime)$};
@@
 \path[->,font=\scriptsize,>=angle 90]
-(A) edge node[left]{$i_1$} (B)
-(C) edge node[right]{$o_1$} (B)
-(D) edge node[left]{$i_2$} (E)
-(F) edge node[right]{$o_2$} (E)
-(G) edge node[left]{$i_3$} (H)
-(I) edge node[right]{$o_3$} (H);
+(A) edge node[above]{$i_1$} (B)
+(C) edge node[above]{$o_1$} (B)
+(D) edge node[above]{$i_2$} (E)
+(F) edge node[above]{$o_2$} (E)
+(G) edge node[above]{$i_3$} (H)
+(I) edge node[above]{$o_3$} (H);
 \end{tikzpicture}
@@
 			\node (c) at (5,0) {$1_\bold{C}+c_1^\prime$};
-			\node (d2) at (7.5,1.5) {$1_{\mathbb{F}\textnormal{Cospan}(\bold{C})} \otimes \mathbb{E}(M_1)$};
-			\node (a2) at (-4,1.5) {$1_\bold{C}+c_1$};
-			\node (b2) at (0.5,1.5) {$1_\bold{C}+R(d_1)$};
-			\node (c2) at (5,1.5) {$1_\bold{C}+c_1^\prime$};
-			\node (d3) at (7.5,3) {$\mathbb{E}(M_1)$};
-                                \node (a3) at (-4,3) {$c_1$};
-			\node (b3) at (0.5,3) {$R(d_1)$};
-			\node (c3) at (5,3) {$c_1^\prime$};
-			\node (d4) at (7.5,-1.5) {$\mathbb{E}(1_{ _L \mathbb{C}\textnormal{sp}(\bold{D})} \otimes M_1)$};
-                                \node (a5) at (-4,-1.5) {$1_\bold{C}+c_1^\prime$};
-			\node (b5) at (0.5,-1.5) {$R(L(1_\bold{C})+d_1)$};
-			\node (c5) at (5,-1.5) {$1_\bold{C}+c_1^\prime$};
-			\node (d5) at (7.5,-3) {$\mathbb{E}(M_1)$};
-                                \node (a6) at (-4,-3) {$c_1$};
-			\node (b6) at (0.5,-3) {$R(d_1)$};
-			\node (c6) at (5,-3) {$c_1^\prime$};
+			\node (d2) at (7.5,1) {$1_{\mathbb{F}\textnormal{Cospan}(\bold{C})} \otimes \mathbb{E}(M_1)$};
+			\node (a2) at (-4,1) {$1_\bold{C}+c_1$};
+			\node (b2) at (0.5,1) {$1_\bold{C}+R(d_1)$};
+			\node (c2) at (5,1) {$1_\bold{C}+c_1^\prime$};
+			\node (d3) at (7.5,2) {$\mathbb{E}(M_1)$};
+                                \node (a3) at (-4,2) {$c_1$};
+			\node (b3) at (0.5,2) {$R(d_1)$};
+			\node (c3) at (5,2) {$c_1^\prime$};
+			\node (d4) at (7.5,-1) {$\mathbb{E}(1_{ _L \mathbb{C}\textnormal{sp}(\bold{D})} \otimes M_1)$};
+                                \node (a5) at (-4,-1) {$1_\bold{C}+c_1^\prime$};
+			\node (b5) at (0.5,-1) {$R(L(1_\bold{C})+d_1)$};
+			\node (c5) at (5,-1) {$1_\bold{C}+c_1^\prime$};
+			\node (d5) at (7.5,-2) {$\mathbb{E}(M_1)$};
+                                \node (a6) at (-4,-2) {$c_1$};
+			\node (b6) at (0.5,-2) {$R(d_1)$};
+			\node (c6) at (5,-2) {$c_1^\prime$};
 			\path[->,font=\scriptsize,>=angle 90]
@@
 		\begin{tikzpicture}
-\node(d) at (1.5,10.5) {$(\mathbb{E}(M_1) \otimes \mathbb{E}(M_2)) \otimes \mathbb{E}(M_3)$};
-\node (d2) at (1.5,12) {$\mathbb{E}(M_1 \otimes M_2) \otimes \mathbb{E}(M_3)$};
-\node (d3) at (1.5,13.5) {$\mathbb{E}((M_1 \otimes M_2) \otimes M_3)$};
-\node (d4) at (1.5,15) {$\mathbb{E}(M_1 \otimes (M_2 \otimes M_3))$};
-\node (d5) at (1.5,9) {$\mathbb{E}(M_1) \otimes (\mathbb{E}(M_2) \otimes \mathbb{E}(M_3))$};
-\node (d6) at (1.5,7.5) {$\mathbb{E}(M_1) \otimes \mathbb{E}(M_2 \otimes M_3)$};
-\node (d7) at (1.5,6) {$\mathbb{E}(M_1 \otimes (M_2 \otimes M_3))$};
+\node(d) at (1.5,7) {$(\mathbb{E}(M_1) \otimes \mathbb{E}(M_2)) \otimes \mathbb{E}(M_3)$};
+\node (d2) at (1.5,8) {$\mathbb{E}(M_1 \otimes M_2) \otimes \mathbb{E}(M_3)$};
+\node (d3) at (1.5,9) {$\mathbb{E}((M_1 \otimes M_2) \otimes M_3)$};
+\node (d4) at (1.5,10) {$\mathbb{E}(M_1 \otimes (M_2 \otimes M_3))$};
+\node (d5) at (1.5,6) {$\mathbb{E}(M_1) \otimes (\mathbb{E}(M_2) \otimes \mathbb{E}(M_3))$};
+\node (d6) at (1.5,5) {$\mathbb{E}(M_1) \otimes \mathbb{E}(M_2 \otimes M_3)$};
+\node (d7) at (1.5,4) {$\mathbb{E}(M_1 \otimes (M_2 \otimes M_3))$};
 			\node (a) at (-4.25,0) {$(c_1+c_2)+c_3$};
@@
 			\node (c) at (7.25,0) {$(c_1^\prime+c_2^\prime)+c_3^\prime$};
-			\node (a2) at (-4.25,1.5) {$(c_1+c_2)+c_3$};
-			\node (b2) at (1.5,1.5) {$R(d_1+d_2)+R(d_3)$};
-			\node (c2) at (7.25,1.5) {$(c_1^\prime+c_2^\prime)+c_3^\prime$};
-                                \node (a3) at (-4.25,3) {$(c_1+c_2)+c_3$};
-			\node (b3) at (1.5,3) {$R((d_1+d_2)+d_3)$};
-			\node (c3) at (7.25,3) {$(c_1^\prime+c_2^\prime)+c_3^\prime$};
-                                \node (a4) at (-4.25,4.5) {$c_1+(c_2+c_3)$};
-			\node (b4) at (1.5,4.5) {$R(d_1+(d_2+d_3))$};
-			\node (c4) at (7.25,4.5) {$c_1^\prime + (c_2^\prime + c_3^\prime)$};
-                                \node (a5) at (-4.25,-1.5) {$c_1+(c_2+c_3)$};
-			\node (b5) at (1.5,-1.5) {$R(d_1)+(R(d_2)+R(d_3))$};
-			\node (c5) at (7.25,-1.5) {$c_1^\prime + (c_2^\prime + c_3^\prime)$};
-                                \node (a6) at (-4.25,-3) {$c_1+(c_2+c_3)$};
-			\node (b6) at (1.5,-3) {$R(d_1)+R(d_2+d_3)$};
-			\node (c6) at (7.25,-3) {$c_1^\prime + (c_2^\prime + c_3^\prime)$};
-                                \node (a7) at (-4.25,-4.5) {$c_1+(c_2+c_3)$};
-			\node (b7) at (1.5,-4.5) {$R(d_1+(d_2+d_3))$};
-			\node (c7) at (7.25,-4.5) {$c_1^\prime + (c_2^\prime + c_3^\prime)$};
+			\node (a2) at (-4.25,1) {$(c_1+c_2)+c_3$};
+			\node (b2) at (1.5,1) {$R(d_1+d_2)+R(d_3)$};
+			\node (c2) at (7.25,1) {$(c_1^\prime+c_2^\prime)+c_3^\prime$};
+                                \node (a3) at (-4.25,2) {$(c_1+c_2)+c_3$};
+			\node (b3) at (1.5,2) {$R((d_1+d_2)+d_3)$};
+			\node (c3) at (7.25,2) {$(c_1^\prime+c_2^\prime)+c_3^\prime$};
+                                \node (a4) at (-4.25,3) {$c_1+(c_2+c_3)$};
+			\node (b4) at (1.5,3) {$R(d_1+(d_2+d_3))$};
+			\node (c4) at (7.25,3) {$c_1^\prime + (c_2^\prime + c_3^\prime)$};
+                                \node (a5) at (-4.25,-1) {$c_1+(c_2+c_3)$};
+			\node (b5) at (1.5,-1) {$R(d_1)+(R(d_2)+R(d_3))$};
+			\node (c5) at (7.25,-1) {$c_1^\prime + (c_2^\prime + c_3^\prime)$};
+                                \node (a6) at (-4.25,-2) {$c_1+(c_2+c_3)$};
+			\node (b6) at (1.5,-2) {$R(d_1)+R(d_2+d_3)$};
+			\node (c6) at (7.25,-2) {$c_1^\prime + (c_2^\prime + c_3^\prime)$};
+                                \node (a7) at (-4.25,-3) {$c_1+(c_2+c_3)$};
+			\node (b7) at (1.5,-3) {$R(d_1+(d_2+d_3))$};
+			\node (c7) at (7.25,-3) {$c_1^\prime + (c_2^\prime + c_3^\prime)$};
 			\path[->,font=\scriptsize,>=angle 90]
@@
 \node (d) at (7,0) {$\mathbb{E}(M_1) \otimes \mathbb{E}(M_2)$};
-\node (d2) at (7,1.5) {$\mathbb{E}(M_2) \otimes \mathbb{E}(M_1)$};
-\node (d3) at (7,3) {$\mathbb{E}(M_2 \otimes M_1)$};
-\node (d4) at (7,-1.5) {$\mathbb{E}(M_1 \otimes M_2)$};
-\node (d5) at (7,-3) {$\mathbb{E}(M_2 \otimes M_1)$};
+\node (d2) at (7,1) {$\mathbb{E}(M_2) \otimes \mathbb{E}(M_1)$};
+\node (d3) at (7,2) {$\mathbb{E}(M_2 \otimes M_1)$};
+\node (d4) at (7,-1) {$\mathbb{E}(M_1 \otimes M_2)$};
+\node (d5) at (7,-2) {$\mathbb{E}(M_2 \otimes M_1)$};
 			\node (a) at (-4,0) {$c_1+c_2$};
@@
 			\node (c) at (5,0) {$c_1^\prime+c_2^\prime$};
-			\node (a2) at (-4,1.5) {$c_2+c_1$};
-			\node (b2) at (0.5,1.5) {$R(d_2)+R(d_1)$};
-			\node (c2) at (5,1.5) {$c_2^\prime+c_1^\prime$};
-                                \node (a3) at (-4,3) {$c_2+c_1$};
-			\node (b3) at (0.5,3) {$R(d_2+d_1)$};
-			\node (c3) at (5,3) {$c_2^\prime + c_1^\prime$};
-                                \node (a5) at (-4,-1.5) {$c_1+c_2$};
-			\node (b5) at (0.5,-1.5) {$R(d_1+d_2)$};
-			\node (c5) at (5,-1.5) {$c_1^\prime+c_2^\prime$};
-                                \node (a6) at (-4,-3) {$c_2+c_1$};
-			\node (b6) at (0.5,-3) {$R(d_2+d_1)$};
-			\node (c6) at (5,-3) {$c_2^\prime + c_1^\prime$};
+			\node (a2) at (-4,1) {$c_2+c_1$};
+			\node (b2) at (0.5,1) {$R(d_2)+R(d_1)$};
+			\node (c2) at (5,1) {$c_2^\prime+c_1^\prime$};
+                                \node (a3) at (-4,2) {$c_2+c_1$};
+			\node (b3) at (0.5,2) {$R(d_2+d_1)$};
+			\node (c3) at (5,2) {$c_2^\prime + c_1^\prime$};
+                                \node (a5) at (-4,-1) {$c_1+c_2$};
+			\node (b5) at (0.5,-1) {$R(d_1+d_2)$};
+			\node (c5) at (5,-1) {$c_1^\prime+c_2^\prime$};
+                                \node (a6) at (-4,-2) {$c_2+c_1$};
+			\node (b6) at (0.5,-2) {$R(d_2+d_1)$};
+			\node (c6) at (5,-2) {$c_2^\prime + c_1^\prime$};
 			\path[->,font=\scriptsize,>=angle 90]
@@
 \node (A) at (0,0) {$c_1$};
-\node (B) at (1,1) {$c$};
+\node (B) at (1,0) {$c$};
 \node (C) at (2,0) {$c_2$};
@@
 \node (A) at (0,0) {$L(c_1)$};
-\node (B) at (1,1) {$d$};
+\node (B) at (1,0) {$d$};
 \node (C) at (2,0) {$L(c_2)$};
 \path[->,font=\scriptsize,>=angle 90]
-(A) edge node[left]{$\tau_c L(I)$} (B)
-(C) edge node[right]{$\tau_ c L(O)$} (B);
+(A) edge node[above]{$\tau_c L(I)$} (B)
+(C) edge node[above]{$\tau_ c L(O)$} (B);
 \end{tikzpicture}
@@
 \node (A) at (0,0) {$L(c_1)$};
-\node (B) at (1,1) {$d$};
+\node (B) at (1,0) {$d$};
 \node (C) at (2,0) {$L(c_2)$};
@@
 \node (A) at (0,0) {$c_1$};
-\node (B) at (1,1) {$R(d)$};
+\node (B) at (1,0) {$R(d)$};
 \node (C) at (2,0) {$c_2$};
@@
 \path[->,font=\scriptsize,>=angle 90]
-(A) edge node[left]{$R(i)$} (B)
-(C) edge node[right]{$R(o)$} (B);
+(A) edge node[above]{$R(i)$} (B)
+(C) edge node[above]{$R(o)$} (B);
 \end{tikzpicture}
@@
 \node (A) at (0,0) {$L(c_1)$};
-\node (B) at (1,1) {$d$};
-\node (C) at (2,0) {$L(c_2)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[left]{$\tau_{R(d)}L(R(i))$} (B)
-(C) edge node[right]{$\tau_{R(d)}L(R(o))$} (B);
+\node (B) at (1.5,0) {$d$};
+\node (C) at (3,0) {$L(c_2)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$\tau_{R(d)}L(R(i))$} (B)
+(C) edge node[above]{$\tau_{R(d)}L(R(o))$} (B);
 \end{tikzpicture}
@@
 \path[->,font=\scriptsize,>=angle 90]
-(A) edge node[left]{$I$} (B)
-(C) edge node[right]{$O$} (B);
+(A) edge node[above]{$I$} (B)
+(C) edge node[above]{$O$} (B);
 \end{tikzpicture}
@@
 \node (A) at (0,0) {$L(c_1)$};
-\node (B) at (1,1) {$d$};
+\node (B) at (1,0) {$d$};
 \node (C) at (2,0) {$L(c_2)$};
 \path[->,font=\scriptsize,>=angle 90]
-(A) edge node[left]{$\tau_c L(I)$} (B)
-(C) edge node[right]{$\tau_c L(O)$} (B);
+(A) edge node[above]{$\tau_c L(I)$} (B)
+(C) edge node[above]{$\tau_c L(O)$} (B);
 \end{tikzpicture}
@@
 \path[->,font=\scriptsize,>=angle 90]
-(A) edge node[left]{$R(\tau_c)I$} (B)
-(C) edge node[right]{$R(\tau_c)O$} (B);
+(A) edge node[above]{$R(\tau_c)I$} (B)
+(C) edge node[above]{$R(\tau_c)O$} (B);
 \end{tikzpicture}
@@
 \node (A) at (0,0) {$L(N)$};
-\node (B) at (1,1) {$M$};
+\node (B) at (1,0) {$M$};
 \node (C) at (2,0) {$L(N^\prime)$};
@@
 \node (A) at (0,0) {$N_1$};
-\node (B) at (1,1) {$N$};
+\node (B) at (1,0) {$N$};
 \node (C) at (2,0) {$N_2$};
-\node (D) at (3,0.5) {$M \in F(N)$};
+\node (D) at (3.25,0) {$M \in F(N)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \node (A) at (0,0) {$N$};
-\node (B) at (1,1) {$R(M)$};
+\node (B) at (1,0) {$R(M)$};
 \node (C) at (2,0) {$N^\prime$};
-\node (D) at (3,0.5) {$M \in F(R(M))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[left]{$R(i)$} (B)
-(C) edge node[right]{$R(o)$} (B);
+\node (D) at (3.5,0) {$M \in F(R(M))$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$R(i)$} (B)
+(C) edge node[above]{$R(o)$} (B);
 \end{tikzpicture}
@@
 \node (A) at (0,0) {$N_1$};
-\node (B) at (1,1) {$N$};
+\node (B) at (1,0) {$N$};
 \node (C) at (2,0) {$N_2$};
-\node (D) at (3,0.5) {$M \in F(N)$};
+\node (D) at (3,0) {$M \in F(N)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \node (A) at (0,0) {$L(N_1)$};
-\node (B) at (1,1) {$M$};
+\node (B) at (1,0) {$M$};
 \node (C) at (2,0) {$L(N_2)$};
@@
 \node (A) at (0,0) {$L(N_1)$};
-\node (B) at (1,1) {$M$};
+\node (B) at (1,0) {$M$};
 \node (C) at (2,0) {$L(N_2)$};
 \node (D) at (3,0) {$L(N_2)$};
-\node (E) at (4,1) {$M^\prime$};
+\node (E) at (4,0) {$M^\prime$};
 \node (F) at (5,0) {$L(N_3)$};
 \path[->,font=\scriptsize,>=angle 90]
-(A) edge node[left]{$i_1$} (B)
-(C) edge node[right]{$o_1$} (B)
-(D) edge node[left]{$i_2$} (E)
-(F) edge node[right]{$o_2$} (E);
+(A) edge node[above]{$i_1$} (B)
+(C) edge node[above]{$o_1$} (B)
+(D) edge node[above]{$i_2$} (E)
+(F) edge node[above]{$o_2$} (E);
 \end{tikzpicture}
@@
 \node (A) at (0,0) {$L(N)$};
-\node (B) at (1,1) {$M$};
+\node (B) at (1,0) {$M$};
 \node (C) at (2,0) {$L(N_2)$};
@@
 \node (A) at (0,0) {$N_1$};
-\node (B) at (1,1) {$R(M)$};
+\node (B) at (1,0) {$R(M)$};
 \node (C) at (2,0) {$N_2$};
-\node (D) at (3,0.5) {$M \in F(R(M))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[left]{$R(i)$} (B)
-(C) edge node[right]{$R(o)$} (B);
+\node (D) at (3.5,0) {$M \in F(R(M))$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$R(i)$} (B)
+(C) edge node[above]{$R(o)$} (B);
 \end{tikzpicture}
@@
 \section{Acknowledgements}
-Dr. Baez, Daniel Cicala...
+Daniel Cicala, person that Christina emailed about lax slice category?
 \begin{thebibliography}{100}
@@
 
-\bibitem{Brown1} R.\ Brown and C.\ B.\ Spencer, Double groupoids and crossed modules, 
+%\bibitem{Brown1} R.\ Brown and C.\ B.\ Spencer, Double groupoids and crossed modules, 
 \textsl{Cah.\ Top.\ G\'eom.\ Diff.} \textbf{17} (1976), 343--362.
 
-\bibitem{Brown2} R.\ Brown, K.\ Hardie, H.\ Kamps and T.\ Porter, The homotopy double groupoid of a Hausdorff space, \textsl{Th.\ Appl.\ Categ.} \textbf{10} (2002), 71--93.
+%\bibitem{Brown2} R.\ Brown, K.\ Hardie, H.\ Kamps and T.\ Porter, The homotopy double groupoid of a Hausdorff space, \textsl{Th.\ Appl.\ Categ.} \textbf{10} (2002), 71--93.
 

### 2018-10-03 EquivCompFrameworks_20180911kc.tex
Changed notation to match notation used in structured cospans paper

@@
 This framework, which goes by the name of `structured cospans', utilizes double categories where the objects are seen as inputs and outputs, morphisms are `open networks', and 2-morphisms are maps between open networks.
-In this setup a functor $L \colon \bold{C} \to \bold{D}$, which is typically a left adjoint, is used to replace the objects and vertical 1-morphisms of a given double category $\mathbb{D}$ with the objects and morphisms, respectively, of the category $\bold{C}$.
-Horizontal 1-cells are then cospans in $\bold{D}$ of a particular form with 2-morphisms given by maps of these cospans.
+In this setup a functor $L \colon \textrm{A} \to \textrm{X}$, which is typically a left adjoint, is used to replace the objects and vertical 1-morphisms of a given double category $\mathbb{X}$ with the objects and morphisms, respectively, of the category $\textrm{A}$.
+Horizontal 1-cells are then cospans in $\textrm{X}$ of a particular form with 2-morphisms given by maps of these cospans.
 Fong has also developed a similar framework which also uses cospans and goes by the name of `decorated cospans'.
-In this setup, a lax monoidal functor $F \colon \bold{C} \to \bold{E}$ is used to `decorate' the apices of cospans in $\bold{C}$ with elements of $\bold{E}$ giving the cospans extra structure.
+In this setup, a lax monoidal functor $F \colon \textrm{A} \to \textrm{Set}$ is used to `decorate' the apices of cospans in $\textrm{A}$ with elements of $\textrm{Set}$ giving the cospans extra structure.
 Using a slight variation of Fong's framework, we prove that these two frameworks are equivalent in the situation where a left adjoint can be obtained from a lax monoidal pseudofunctor using a well known construction of Grothendieck.
@@
 \section{Introduction}
-
-git pro coming through!
-
 Networks are playing an increasingly prominent role in our understanding of the world and as a result, methods of characterizing and studying networks have become evermore necessary.
@@
 
-In Fong's theory of decorated cospans, given a category $\bold{C}$ with finite colmits, a symmetric lax monoidal functor $F \colon (\bold{C},+,0) \to (\bold{D},\otimes,I)$ is used to `decorate' the apex of a cospan in $\bold{C}$ with an element of the image of its apex under the functor $F$, in the case of the first cospan above, a morphism $d \colon I \to F(c)$.
+In Fong's theory of decorated cospans, given a category $\textrm{A}$ with finite colmits, a symmetric lax monoidal functor $F \colon (\textrm{A},+,0) \to (\textrm{Set},\times,1)$ is used to `decorate' the apex of a cospan in $\textrm{A}$ with an element of the image of its apex under the functor $F$, in the case of the first cospan above, a morphism $d \colon 1 \to F(c)$.
 Here $F(c)$ is the collection of all $F$-decorations on the object $c$ and the morphism $d$ is selecting a particular one.
@@
 
-From this symmetric lax monoidal functor $F \colon \bold{C} \to \bold{D}$, Fong then constructs a symmetric monoidal category $F\textnormal{Cospan}(\bold{C})$ which has:
+From this symmetric lax monoidal functor $F \colon \textrm{A} \to \mathrm{Set}$, Fong then constructs a symmetric monoidal category $F\textnormal{Cospan}(\mathrm{A})$ which has:
 \begin{enumerate}
-\item{objects as those of $\bold{C}$ and}
+\item{objects as those of $\mathrm{A}$ and}
 \item{morphisms as isomorphism classes of $F$-decorated cospans, where an $F$-decorated cospan is given as above, and two $F$-decorated cospans are in the same isomorphism class if there exists an isomorphism between the apices such that the following diagrams commute:
@@
 \node (C) at (2,0) {$b$};
-\node (D) at (3,0) {$I$};
+\node (D) at (3,0) {$1$};
 \node (E) at (4,0.5) {$F(c)$};
@@
 There are some subtleties to this approach.
-To illustrate, consider the example where $F \colon \bold{FinSet} \to \bold{Set}$ is the symmetric lax monoidal functor that assigns to a finite set $N$ the (large) set of all possible graph structures on the finite set $N$, where a graph structure on $N$ is given by a diagram in $\bold{Set}$ of the form:
+To illustrate, consider the example where $F \colon \textrm{FinSet} \to \textrm{Set}$ is the symmetric lax monoidal functor that assigns to a finite set $N$ the (large) set of all possible graph structures on the finite set $N$, where a graph structure on $N$ is given by a diagram in $\textrm{Set}$ of the form:
 \[
@@
 Denote this second element of $F(N)$ as $d^\prime$.
-These two graphs constitute distinct isomorphism classes in the symmetric monoidal category $F$Cospan$(\bold{FinSet})$, as $f=\id_N$ and thus $F(f)=\id_{F(N)}$, but clearly $d \neq d^\prime$.
+These two graphs constitute distinct isomorphism classes in the symmetric monoidal category $F$Cospan$(\textrm{FinSet})$, as $f=\id_N$ and thus $F(f)=\id_{F(N)}$, but clearly $d \neq d^\prime$.
 The issue here is that the functor $F$ is decorating each finite set $N$ not only with extra structure, but with extra \emph{stuff}.
@@
 
-One approach to remedying this nuisance is to instead view $F$ as a functor $F \colon\bold{C} \to \bold{Cat}$ and then consider $F(c)$ not as a \emph{set} of decorations on the element $c$ but as a \emph{category} of decorations on the element $c$.
-Then one can construct a similar symmetric monoidal category similar to Fong's, which by similarity and an abuse of notation we also call $F\textnormal{Cospan}(\bold{C})$.
+One approach to remedying this nuisance is to instead view $F$ as a functor $F \colon \textrm{A} \to \bold{Cat}$ and then consider $F(c)$ not as a \emph{set} of decorations on the element $c$ but as a \emph{category} of decorations on the element $c$.
+Then one can construct a similar symmetric monoidal category similar to Fong's, which will be called $D(H(\mathbb{F}\textnormal{Cospan}(\mathrm{A})))$ for reasons that will be explained later.
 This symmetric monoidal category will have:
 \begin{enumerate}
-\item{objects as those of $\bold{C}$ and}
-\item{morphisms as isomorphism classes of cospans of $\bold{C}$ together with an element of image of the apex under the functor $F$.
+\item{objects as those of $\mathrm{A}$ and}
+\item{morphisms as isomorphism classes of cospans of $\mathrm{A}$ together with an element of image of the apex under the functor $F$.
 \[
@@
 \node (C) at (2,0) {$b$};
-\node (D) at (3,0) {$\bold{1}$};
+\node (D) at (3,0) {$1$};
 \node (E) at (4,0.5) {$F(c)$};
@@
 \node (A) at (4,0) {$\iota \Swarrow$};
-\node (D) at (3,0) {$\bold{1}$};
+\node (D) at (3,0) {$1$};
 \node (E) at (4.5,1) {$F(c)$};
@@
 
-In the present work, we construct a symmetric monoidal `double category' $\mathbb{F}\textnormal{Cospan}(\bold{C})$.
+In the present work, we construct a symmetric monoidal `double category' $\mathbb{F}\textnormal{Cospan}(\textrm{A})$.
 Double categories were first introduced by Ehresmann \cite{Ehresmann63, Ehresmann65} and symmetric monoidal double categories by Shulman \cite{Shul}.
@@
 In a `pseudo' double category, horizontal 1-cells compose in a weakly associative manner: that is, the associative law holds only up to an invertible 2-morphism, called the `associator', which obeys a coherence law.
-The double category $\mathbb{F}\textnormal{Cospan}(\bold{C})$ that we construct in this paper has:
+The double category $\mathbb{F}\textnormal{Cospan}(\textrm{A})$ that we construct in this paper has:
 \begin{enumerate}
-\item{objects as those of $\bold{C}$,}
-\item{vertical 1-morphisms as morphisms of $\bold{C}$,}
-\item{horizontal 1-cells as $F$-decorated cospans of $\bold{C}$, which are pairs:
+\item{objects as those of $\textrm{A}$,}
+\item{vertical 1-morphisms as morphisms of $\textrm{A}$,}
+\item{horizontal 1-cells as $F$-decorated cospans of $\textrm{A}$, which are pairs:
 \[
@@
 \end{enumerate}
-We can then obtain a symmetric monoidal bicategory $H(\mathbb{F}\textnormal{Cospan}(\bold{C}))$ as the `horizontal bicategory' of the symmetric monoidal double category $\mathbb{F}\textnormal{Cospan}(\bold{C})$ using a result of Shulman \cite{Shul}.
+We can then obtain a symmetric monoidal bicategory $H(\mathbb{F}\textnormal{Cospan}(\textrm{A}))$ as the `horizontal bicategory' of the symmetric monoidal double category $\mathbb{F}\textnormal{Cospan}(\textrm{A})$ using a result of Shulman \cite{Shul}.
 This bicategory will have:
 \begin{enumerate}
-\item{objects as those of $\bold{C}$,}
+\item{objects as those of $\textrm{A}$,}
 \item{morphisms as pairs:
@@
 \end{enumerate}
-Then we can obtain the above improved symmetric monoidal category as a decategorification of the symmetric monoidal bicategory $H(\mathbb{F}\textnormal{Cospan}(\bold{C}))$.
+Then we can obtain the above improved symmetric monoidal category as a decategorification of the symmetric monoidal bicategory $H(\mathbb{F}\textnormal{Cospan}(\textrm{A}))$.
 
 The outline for the paper is as follows: In the second section we present the definition of double category and symmetric monoidal double category, both of which can be found in earlier works \cite{Shul}.
-In the third section, we construct the symmetric monoidal double category $F\textnormal{Cospan}(\bold{C})$ mentioned above as well as a result of Shulman that allows us to obtain a symmetric monoidal bicategory whose decategorification is an improved version of Fong's symmetric monoidal category.
+In the third section, we construct the symmetric monoidal double category $F\textnormal{Cospan}(\textrm{A})$ mentioned above as well as a result of Shulman that allows us to obtain a symmetric monoidal bicategory whose decategorification is an improved version of Fong's symmetric monoidal category.
 In the fourth section we investigate when a symmetric lax monoidal pseudofunctor gives rise to a left adjoint via the Grothendieck construction.
-In the fifth section we review another compositional framework which uses cospans equipped with extra structure due to Baez and the first author, namely `structured cospans' and prove that the double categorical versions of decorated cospans and structured cospans are equivalent, and in the final section, we present a few examples that can be realized with either framework and exhibit the equivalences.
+In the fifth section we review another compositional framework which uses cospans equipped with extra structure due to the first two authors, namely `structured cospans' and prove that the double categorical versions of decorated cospans and structured cospans are equivalent, and in the final section, we present a few examples that can be realized with either framework and exhibit the equivalences.
 
@@
 %\begin{enumerate}
-%\item{Need to build a symmetric monoidal decorated cospan category $F$Cospan$(\bold{C})$ from a lax symmetric monoidal pseudofunctor $F \colon \bold{C} \to \bold{Cat}$.}
-%\item{Need to view $F$Cospan$(\bold{C})$ as a one object bicategory and then a one object pseudo double category.}
+%\item{Need to build a symmetric monoidal decorated cospan category $F$Cospan$(\mathrm{A})$ from a lax symmetric monoidal pseudofunctor $F \colon \mathrm{A} \to \bold{Cat}$.}
+%\item{Need to view $F$Cospan$(\mathrm{A})$ as a one object bicategory and then a one object pseudo double category.}
 %\item{Deloop the symmetric monoidal $(\bold{Cat,\times})$ into a one object bicategory and then view this as a one object pseudo double category in which there is only an identity for vertical 1-morphisms and the objects of $\bold{Cat}$ appear as horizontal 1-cells, and morphisms of $\bold{Cat}$ as 2-morphisms.
 Denote this pseudo double category as $\mathbb{C}\bold{at}$.}
-%\item{Define a symmetric monoidal lax double functor $\mathbb{F} \colon$ $F$Cospan$(\bold{C}) \to \mathbb{C} \bold{at}$.}
-%\item{Define a symmetric monoidal oplax double functor $\mathbb{I} \colon \bold{1} \to \mathbb{C} \bold{at}$ where $\bold{1}$ is the one object double category.}
-%\item{Obtain a symmetric monoidal double category of decorated cospans $\mathbb{F}$Cospan$(\bold{C})$ as a comma object from the cospan $\bold{1} \xrightarrow{ \mathbb{I} } \mathbb{C}\bold{at} \xleftarrow{ \mathbb{F} } F\textrm{Cospan}(\bold{C})$ in the 2-category $\mathbb{DBL}$ of monoidal double categories and lax functors.
-(Note that the functor $\mathbb{I} \colon \bold{1} \to \mathbb{C}\bold{at}$ is actually pseudo, and hence both lax and oplax.)}
+%\item{Define a symmetric monoidal lax double functor $\mathbb{F} \colon$ $F$Cospan$(\mathrm{A}) \to \mathbb{C} \bold{at}$.}
+%\item{Define a symmetric monoidal oplax double functor $\mathbb{I} \colon 1 \to \mathbb{C} \bold{at}$ where $1$ is the one object double category.}
+%\item{Obtain a symmetric monoidal double category of decorated cospans $\mathbb{F}$Cospan$(\mathrm{A})$ as a comma object from the cospan $1 \xrightarrow{ \mathbb{I} } \mathbb{C}\bold{at} \xleftarrow{ \mathbb{F} } F\textrm{Cospan}(\mathrm{A})$ in the 2-category $\mathbb{DBL}$ of monoidal double categories and lax functors.
+(Note that the functor $\mathbb{I} \colon 1 \to \mathbb{C}\bold{at}$ is actually pseudo, and hence both lax and oplax.)}
 %\item{Figure out what a (double?) equivalence of symmetric monoidal double categories is.}
-%\item{Show that $_F \textrm{Csp}(\bold{C})$ is equivalent to $\mathbb{F}\textrm{Cospan}(\bold{C})$ as symmetric monoidal double categories, where $_F \textrm{Csp}(\bold{C})$ is the structured cospan double category that comes from the double category Csp$(\bold{C})$ and the functor $F \colon \bold{C} \to \bold{Cat}$.}
+%\item{Show that $_F \textrm{Csp}(\mathrm{A})$ is equivalent to $\mathbb{F}\textrm{Cospan}(\mathrm{A})$ as symmetric monoidal double categories, where $_F \textrm{Csp}(\mathrm{A})$ is the structured cospan double category that comes from the double category Csp$(\mathrm{A})$ and the functor $F \colon \mathrm{A} \to \bold{Cat}$.}
 %\end{enumerate}
@@
 
-If $\bold{C}$ is a category with finite colimits, there is a well-known symmetric monoidal pseudo double category $\mathbb{C} \textnormal{ospan}(\bold{C})$ which has:
+If $\mathrm{A}$ is a category with finite colimits, there is a well-known symmetric monoidal pseudo double category $\mathbb{C} \textnormal{ospan}(\mathrm{A})$ which has:
 \begin{enumerate}
-\item{objects as those of $\bold{C}$,}
-\item{vertical 1-morphisms as morphisms of $\bold{C}$,}
-\item{horizontal 1-cells as cospans in $\bold{C}$, and}
-\item{2-morphisms as maps of cospans in $\bold{C}.$
+\item{objects as those of $\mathrm{A}$,}
+\item{vertical 1-morphisms as morphisms of $\mathrm{A}$,}
+\item{horizontal 1-cells as cospans in $\mathrm{A}$, and}
+\item{2-morphisms as maps of cospans in $\mathrm{A}.$
 \[
@@
 
-The symmetric monoidal category $(\bold{Cat},\times,\bold{1})$ consisting of categories and functors can naturally be viewed as a one object bicategory using a standard level shift.
+The symmetric monoidal category $(\bold{Cat},\times,1)$ consisting of categories and functors can naturally be viewed as a one object bicategory using a standard level shift.
 This one object bicategory, which we denote as $\textnormal{BD}(\bold{Cat})$, will have:
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$\bold{1}$};
+\node (A) at (0,0) {$1$};
 \node (B) at (1,1) {$\mathbb{B}\textnormal{D}(\bold{Cat})$};
-\node (C) at (2,0) {$\mathbb{C}\textnormal{ospan}(\bold{C})$};
+\node (C) at (2,0) {$\mathbb{C}\textnormal{ospan}(\mathrm{A})$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 
-The oplax double functor $\mathbb{G} \colon 1 \to \mathbb{B}\textnormal{D}(\bold{Cat})$ is trivially defined modulo $\mathbb{G}$ mapping the identity horizontal 1-cell to the monoidal unit of $\mathbb{B}\textnormal{D}(\bold{Cat})$ which is given by the terminal category $\bold{1}$.
-The category $\bold{C}$ has finite colimits and can be viewed as a 2-category with only trivial 2-morphisms.
-Then from a symmetric lax monoidal pseudofunctor $F \colon \bold{C} \to \bold{Cat}$, we can obtain symmetric lax monoidal lax double functor $\mathbb{F} \colon \mathbb{C}\textnormal{ospan}(\bold{C}) \to \mathbb{B}\textnormal{D}(\bold{Cat})$ which is defined as the pseudofunctor $F$ on horizontal 1-cells and 2-morphisms; note that $\mathbb{B}\textnormal{D}(\bold{Cat})$ has a single object and an identity vertical 1-morphism.
-Thus $\mathbb{F}$ will map a cospan in $\bold{C}$: $$a \rightarrow c \leftarrow b$$ to $F(c) \in \bold{Cat}$ and
+The oplax double functor $\mathbb{G} \colon 1 \to \mathbb{B}\textnormal{D}(\bold{Cat})$ is trivially defined modulo $\mathbb{G}$ mapping the identity horizontal 1-cell to the monoidal unit of $\mathbb{B}\textnormal{D}(\bold{Cat})$ which is given by the terminal category $1$.
+The category $\mathrm{A}$ has finite colimits and can be viewed as a 2-category with only trivial 2-morphisms.
+Then from a symmetric lax monoidal pseudofunctor $F \colon \mathrm{A} \to \bold{Cat}$, we can obtain symmetric lax monoidal lax double functor $\mathbb{F} \colon \mathbb{C}\textnormal{ospan}(\mathrm{A}) \to \mathbb{B}\textnormal{D}(\bold{Cat})$ which is defined as the pseudofunctor $F$ on horizontal 1-cells and 2-morphisms; note that $\mathbb{B}\textnormal{D}(\bold{Cat})$ has a single object and an identity vertical 1-morphism.
+Thus $\mathbb{F}$ will map a cospan in $\mathrm{A}$: $$a \rightarrow c \leftarrow b$$ to $F(c) \in \bold{Cat}$ and
 \begin{thm}
-Let $F \colon \bold{C} \to \bold{Cat}$ be a symmetric lax monoidal pseudofunctor.
-Then there exists a symmetric (lax) monoidal lax double functor $\mathbb{F} \colon \mathbb{C}\textnormal{ospan}(\bold{C}) \to \mathbb{B}\textnormal{D}(\bold{Cat})$ which is defined:
+Let $F \colon \mathrm{A} \to \bold{Cat}$ be a symmetric lax monoidal pseudofunctor.
+Then there exists a symmetric (lax) monoidal lax double functor $\mathbb{F} \colon \mathbb{C}\textnormal{ospan}(\mathrm{A}) \to \mathbb{B}\textnormal{D}(\bold{Cat})$ which is defined:
 \begin{enumerate}
@@
 \item{trivially on vertical 1-morphisms as $\mathbb{B}\textnormal{D}(\bold{Cat})$ only has a single identity vertical 1-morphism,}
-\item{as the pseudofunctor $F \colon \bold{C} \to \bold{Cat}$ on horizontal 1-cells, meaning that $$(c_1 \xrightarrow{i} c \xleftarrow{o} c_2) \mapsto F(c)$$ and}
-\item{as the pseudofunctor $F \colon \bold{C} \to \bold{Cat}$ on 2-morphisms, meaning that 
+\item{as the pseudofunctor $F \colon \mathrm{A} \to \bold{Cat}$ on horizontal 1-cells, meaning that $$(c_1 \xrightarrow{i} c \xleftarrow{o} c_2) \mapsto F(c)$$ and}
+\item{as the pseudofunctor $F \colon \mathrm{A} \to \bold{Cat}$ on 2-morphisms, meaning that 
 \[
@@
 \begin{proof}
-The functor $\mathbb{F} \colon \mathbb{C}\textnormal{ospan}(\bold{C}) \to \mathbb{B} \textnormal{D}(\bold{Cat})$ is defined trivially on objects and vertical 1-morphisms as the object category of $\mathbb{B}\textnormal{D}(\bold{Cat})$ is trivial.
-Given two composable horizontal 1-cells $M$ and $N$ in $\mathbb{C}\textnormal{ospan}(\bold{C})$ given respectively by:
+The functor $\mathbb{F} \colon \mathbb{C}\textnormal{ospan}(\mathrm{A}) \to \mathbb{B} \textnormal{D}(\bold{Cat})$ is defined trivially on objects and vertical 1-morphisms as the object category of $\mathbb{B}\textnormal{D}(\bold{Cat})$ is trivial.
+Given two composable horizontal 1-cells $M$ and $N$ in $\mathbb{C}\textnormal{ospan}(\mathrm{A})$ given respectively by:
 \[
@@
 
-Given an object $c$ in $\mathbb{C}\textnormal{ospan}(\bold{C})$, $\mathbb{F}(c)$ is the single object $\star$ of $\mathbb{B}\textnormal{D}(\bold{Cat})$, and so $1_{\mathbb{F}(c)}$ is the identity horizontal 1-cell on $\star$.
+Given an object $c$ in $\mathbb{C}\textnormal{ospan}(\mathrm{A})$, $\mathbb{F}(c)$ is the single object $\star$ of $\mathbb{B}\textnormal{D}(\bold{Cat})$, and so $1_{\mathbb{F}(c)}$ is the identity horizontal 1-cell on $\star$.
 Similarly, $1_c$ is the identity cospan on $c$ and then $\mathbb{F}(1_c)=F(c)$.
@@
 \begin{prop}
-Let $\bold{1}$ denote the trivial double category with a single object and only identities.
+Let $1$ denote the trivial double category with a single object and only identities.
 Then there exists a symmetric lax monoidal oplax double functor $\mathbb{G} \colon \mathbf{1} \to \mathbb{B}\textnormal{D}(\bold{Cat})$ which is defined:
 \begin{enumerate}
-\item{trivially on objects, as both $\bold{1}$ and $\mathbb{B} \textnormal{D}(\bold{Cat})$ have a single object,}
-\item{trivially on vertical 1-morphisms, as both $\bold{1}$ and $\mathbb{B} \textnormal{D}(\bold{Cat})$ only have a single identity vertical 1-morphism,}
-\item{the identity horizontal 1-cell of $\bold{1}$ maps to the monoidal unit of $(\mathbb{B}\textnormal{D}(\bold{Cat}),\times, \bold{1})$, which is the terminal category $\bold{1}$ with a single object and identity morphism, and}
-\item{the identity 2-morphism maps to the identity functor $! \colon \bold{1} \to \bold{1}$ on the terminal category.}
+\item{trivially on objects, as both $1$ and $\mathbb{B} \textnormal{D}(\bold{Cat})$ have a single object,}
+\item{trivially on vertical 1-morphisms, as both $1$ and $\mathbb{B} \textnormal{D}(\bold{Cat})$ only have a single identity vertical 1-morphism,}
+\item{the identity horizontal 1-cell of $1$ maps to the monoidal unit of $(\mathbb{B}\textnormal{D}(\bold{Cat}),\times, 1)$, which is the terminal category $1$ with a single object and identity morphism, and}
+\item{the identity 2-morphism maps to the identity functor $! \colon 1 \to 1$ on the terminal category.}
 \end{enumerate}
@@
 \end{defn}
-Using this definition we want to construct a `pseudo comma double category' from the lax double functor $\mathbb{F} \colon \mathbb{C}\textnormal{ospan}(\bold{C}) \to \mathbb{B} \textnormal{D}(\bold{Cat})$ and the oplax double functor $\mathbb{G} \colon \bold{1} \to \mathbb{B}\textnormal{D}(\bold{Cat})$.
-First, we define how this pseudo comma double category $(\mathbb{G} / \mathbb{F}) \coloneqq \mathbb{F}\textnormal{Cospan}(\bold{C})$ is obtained.
+Using this definition we want to construct a `pseudo comma double category' from the lax double functor $\mathbb{F} \colon \mathbb{C}\textnormal{ospan}(\mathrm{A}) \to \mathbb{B} \textnormal{D}(\bold{Cat})$ and the oplax double functor $\mathbb{G} \colon 1 \to \mathbb{B}\textnormal{D}(\bold{Cat})$.
+First, we define how this pseudo comma double category $(\mathbb{G} / \mathbb{F}) \coloneqq \mathbb{F}\textnormal{Cospan}(\mathrm{A})$ is obtained.
 \textbf{Should this be a proposition or a definition? Ask Dr. Baez and Christina for their opinions.}
 \begin{defn}
-Let $\mathbb{G} \colon \lC \to \lE$ be an oplax double functor and $\mathbb{F} \colon \lD \to \lE$ be a lax double functor where $\lC = (\bold{C}_{0},\bold{C}_{1}), \lD = (\bold{D}_{0}, \bold{D}_{1})$ and $\lE = (\bold{E}_{0}, \bold{E}_{1})$ are pseudo  double categories with $\bold{C}_{0}, \bold{C}_{1}$ the category of objects and category of arrows of the double category $\lC$, respectively, and likewise for $\bold{D}_{0}, \bold{D}_{1}, \bold{E}_{0}$ and $\bold{E}_{1}$.
-Then the \define{pseudo comma double category} determined by the double functors $\mathbb{G}$ and $\mathbb{F}$ is the pseudo double category $(\mathbb{G} / \mathbb{F})$ consisting of a category of objects $(\mathbb{G} / \mathbb{F})_{0}$ and category of arrows $(\mathbb{G} / \mathbb{F})_{1}$ where the category of objects $(\mathbb{G} / \mathbb{F})_0$ is the comma category obtained from the functors $\mathbb{G}_0 \colon \bold{C}_{0} \to \bold{E}_{0}$ and $\mathbb{F}_0 \colon \bold{D}_{0} \to \bold{E}_{0}$ and $(\mathbb{G} / \mathbb{F})_1$ is the comma category obtained from the functors $\mathbb{G}_{1} \colon \bold{C}_{1} \to \bold{E}_{1}$ and $\mathbb{F}_1 \colon \bold{D}_{1} \to \bold{E}_{1}$.
+Let $\mathbb{G} \colon \lC \to \lE$ be an oplax double functor and $\mathbb{F} \colon \lD \to \lE$ be a lax double functor where $\lC = (\mathrm{A}_{0},\mathrm{A}_{1}), \lD = (\bold{D}_{0}, \bold{D}_{1})$ and $\lE = (\bold{E}_{0}, \bold{E}_{1})$ are pseudo  double categories with $\mathrm{A}_{0}, \mathrm{A}_{1}$ the category of objects and category of arrows of the double category $\lC$, respectively, and likewise for $\bold{D}_{0}, \bold{D}_{1}, \bold{E}_{0}$ and $\bold{E}_{1}$.
+Then the \define{pseudo comma double category} determined by the double functors $\mathbb{G}$ and $\mathbb{F}$ is the pseudo double category $(\mathbb{G} / \mathbb{F})$ consisting of a category of objects $(\mathbb{G} / \mathbb{F})_{0}$ and category of arrows $(\mathbb{G} / \mathbb{F})_{1}$ where the category of objects $(\mathbb{G} / \mathbb{F})_0$ is the comma category obtained from the functors $\mathbb{G}_0 \colon \mathrm{A}_{0} \to \bold{E}_{0}$ and $\mathbb{F}_0 \colon \bold{D}_{0} \to \bold{E}_{0}$ and $(\mathbb{G} / \mathbb{F})_1$ is the comma category obtained from the functors $\mathbb{G}_{1} \colon \mathrm{A}_{1} \to \bold{E}_{1}$ and $\mathbb{F}_1 \colon \bold{D}_{1} \to \bold{E}_{1}$.
 \end{defn}
 \begin{thm}
-Let $\mathbb{G} \colon \bold{1} \to \mathbb{B}\textnormal{D}(\bold{Cat})$ be the oplax double functor previously defined and let $\mathbb{F} \colon \mathbb{F}\textnormal{Cospan}(\bold{C}) \to \mathbb{B}(\bold{Cat})$ be the lax double functor previously defined.
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$\bold{1}$};
+Let $\mathbb{G} \colon 1 \to \mathbb{B}\textnormal{D}(\bold{Cat})$ be the oplax double functor previously defined and let $\mathbb{F} \colon \mathbb{F}\textnormal{Cospan}(\mathrm{A}) \to \mathbb{B}(\bold{Cat})$ be the lax double functor previously defined.
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$1$};
 \node (B) at (1,1) {$\mathbb{B}\textnormal{D}(\bold{Cat})$};
-\node (C) at (2,0) {$\mathbb{C}\textnormal{ospan}(\bold{C})$};
+\node (C) at (2,0) {$\mathbb{C}\textnormal{ospan}(\mathrm{A})$};
 \node (D) at (1,-1) {$(\mathbb{G} / \mathbb{F})$};
@@
 \]
-Then there exists a category $(\mathbb{G} / \mathbb{F})_0 \coloneqq (\mathbb{G}_0 / \mathbb{F}_0)$ obtained as a comma category from the functors $\mathbb{F}_0 \colon \mathbb{C}\textnormal{ospan}(\bold{C})_0 \to \mathbb{B}\textnormal{D}(\bold{Cat})_0$ and $\mathbb{G}_0 \colon \bold{1} \to \mathbb{B}\textnormal{D}(\bold{Cat})_0$ which has:
+Then there exists a category $(\mathbb{G} / \mathbb{F})_0 \coloneqq (\mathbb{G}_0 / \mathbb{F}_0)$ obtained as a comma category from the functors $\mathbb{F}_0 \colon \mathbb{C}\textnormal{ospan}(\mathrm{A})_0 \to \mathbb{B}\textnormal{D}(\bold{Cat})_0$ and $\mathbb{G}_0 \colon 1 \to \mathbb{B}\textnormal{D}(\bold{Cat})_0$ which has:
 \begin{enumerate}
-\item{objects as those of $\bold{C}$ and}
-\item{morphisms as those of $\bold{C}$,}
+\item{objects as those of $\mathrm{A}$ and}
+\item{morphisms as those of $\mathrm{A}$,}
 \end{enumerate}
-and there exists a category $(\mathbb{G} / \mathbb{F})_1 \coloneqq (\mathbb{G}_1 / \mathbb{F}_1)$ obtained as a comma category from the functors $\mathbb{F}_1 \colon \mathbb{C}\textnormal{ospan}(\bold{C})_1 \to \mathbb{B}\textnormal{D}(\bold{Cat})_1$ and $\mathbb{G}_1 \colon \bold{1} \to \mathbb{B}\textnormal{D}(\bold{Cat})_1$ which has:
+and there exists a category $(\mathbb{G} / \mathbb{F})_1 \coloneqq (\mathbb{G}_1 / \mathbb{F}_1)$ obtained as a comma category from the functors $\mathbb{F}_1 \colon \mathbb{C}\textnormal{ospan}(\mathrm{A})_1 \to \mathbb{B}\textnormal{D}(\bold{Cat})_1$ and $\mathbb{G}_1 \colon 1 \to \mathbb{B}\textnormal{D}(\bold{Cat})_1$ which has:
 \begin{enumerate}
-\item{objects as $F$-decorated cospans of $\bold{C}$, which are pairs:
+\item{objects as $F$-decorated cospans of $\mathrm{A}$, which are pairs:
 \[
@@
 and}
-\item{morphisms as maps of cospans of $\bold{C}$:
+\item{morphisms as maps of cospans of $\mathrm{A}$:
 \[
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$\bold{1}$};
+\node (A) at (0,0) {$1$};
 \node (B) at (1,1) {$\mathbb{B}\textnormal{D}(\bold{Cat})_0$};
-\node (C) at (2,0) {$\mathbb{C}\textnormal{ospan}(\bold{C})_0=\bold{C}$};
+\node (C) at (2,0) {$\mathbb{C}\textnormal{ospan}(\mathrm{A})_0=\mathrm{A}$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-Thus $(\mathbb{G} / \mathbb{F})_0$ will be the comma category which has objects given by triples $(\star,c,\alpha \colon \mathbb{G}(\star) \to \mathbb{F}(c))$ where $\star$ is the single object of $\bold{1}$, $c$ is a object of $\bold{C}$ and $\alpha \colon \mathbb{G}(\star) \to \mathbb{F}(c)$ is a morphism in $\mathbb{B}\textnormal{D}(\bold{Cat})_0$.
-The pseudo double category $\mathbb{B}\textnormal{D}(\bold{Cat})$ only has a single object $\star$ and identity vertical 1-morphism, so the triple $(\star,c,\alpha \colon \mathbb{G}(\star) \to \mathbb{F}(c))$ amounts to an object of $\bold{C}$ together with trivial structure.
-Given another object $(\star, c^\prime, \alpha^\prime \colon \mathbb{G}(\star) \to \mathbb{F}(c^\prime))$, a morphism from the first triple to the second triple is a pair $(\beta, \gamma)$ where $\beta = \id_{\star}$ is a morphism in $\bold{1}$ and $\gamma \colon c \to c^\prime$ is a morphism in $\bold{C}$ such that the following diagram commutes:
+Thus $(\mathbb{G} / \mathbb{F})_0$ will be the comma category which has objects given by triples $(\star,c,\alpha \colon \mathbb{G}(\star) \to \mathbb{F}(c))$ where $\star$ is the single object of $1$, $c$ is a object of $\mathrm{A}$ and $\alpha \colon \mathbb{G}(\star) \to \mathbb{F}(c)$ is a morphism in $\mathbb{B}\textnormal{D}(\bold{Cat})_0$.
+The pseudo double category $\mathbb{B}\textnormal{D}(\bold{Cat})$ only has a single object $\star$ and identity vertical 1-morphism, so the triple $(\star,c,\alpha \colon \mathbb{G}(\star) \to \mathbb{F}(c))$ amounts to an object of $\mathrm{A}$ together with trivial structure.
+Given another object $(\star, c^\prime, \alpha^\prime \colon \mathbb{G}(\star) \to \mathbb{F}(c^\prime))$, a morphism from the first triple to the second triple is a pair $(\beta, \gamma)$ where $\beta = \id_{\star}$ is a morphism in $1$ and $\gamma \colon c \to c^\prime$ is a morphism in $\mathrm{A}$ such that the following diagram commutes:
 \[
@@
 The double category $\mathbb{B}\textnormal{D}(\bold{Cat})$ only has a single object and identity vertical 1-morphism, so this diagram is trivial,  as all four objects are the same and all four morphisms are identities.
-Thus, morphisms are given by morphisms of $\bold{C}$ with added trivial structure, and so the category $(\mathbb{G}/ \mathbb{F})_0$ has objects and morphisms of $\bold{C}$, and we have an isomorphism of categories $(\mathbb{G} / \mathbb{F})_0 \cong \bold{C}$.
+Thus, morphisms are given by morphisms of $\mathrm{A}$ with added trivial structure, and so the category $(\mathbb{G}/ \mathbb{F})_0$ has objects and morphisms of $\mathrm{A}$, and we have an isomorphism of categories $(\mathbb{G} / \mathbb{F})_0 \cong \mathrm{A}$.
 
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$\bold{1}$};
+\node (A) at (0,0) {$1$};
 \node (B) at (1,1) {$\mathbb{B}\textnormal{D}(\bold{Cat})_1$};
-\node (C) at (2,0) {$\mathbb{C}\textnormal{ospan}(\bold{C})_1$};
+\node (C) at (2,0) {$\mathbb{C}\textnormal{ospan}(\mathrm{A})_1$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-Objects are given by triples $$(1_{\star}, a \rightarrow c \leftarrow b, d \colon \mathbb{G}(1_{\star}) \to \mathbb{F}(a \rightarrow c \leftarrow b))$$ where $1_{\star}$ is the identity horizontal 1-cell on $\star$ and $a \rightarrow c \leftarrow b$ is a cospan in $\bold{C}$.
-The double functor $\mathbb{G}$ maps the identity horizontal 1-cell to the monoidal unit of $\bold{Cat}$ under $\times$, namely the terminal category $\bold{1}$, and the double functor $\mathbb{F}$ acts as the functor $F$ on horizontal 1-cells, meaning that $\mathbb{F}(a \rightarrow c \leftarrow b)=F(c)$.
-Thus the above triple is a cospan in $\bold{C}$ together with an element $d \colon \bold{1} \to F(c)$, and this is precisely an $F$-decorated cospan, namely a pair $$((a \rightarrow c \leftarrow b),d \in F(c)).$$
+Objects are given by triples $$(1_{\star}, a \rightarrow c \leftarrow b, d \colon \mathbb{G}(1_{\star}) \to \mathbb{F}(a \rightarrow c \leftarrow b))$$ where $1_{\star}$ is the identity horizontal 1-cell on $\star$ and $a \rightarrow c \leftarrow b$ is a cospan in $\mathrm{A}$.
+The double functor $\mathbb{G}$ maps the identity horizontal 1-cell to the monoidal unit of $\bold{Cat}$ under $\times$, namely the terminal category $1$, and the double functor $\mathbb{F}$ acts as the functor $F$ on horizontal 1-cells, meaning that $\mathbb{F}(a \rightarrow c \leftarrow b)=F(c)$.
+Thus the above triple is a cospan in $\mathrm{A}$ together with an element $d \colon 1 \to F(c)$, and this is precisely an $F$-decorated cospan, namely a pair $$((a \rightarrow c \leftarrow b),d \in F(c)).$$
 
@@
 \]
-Simplifying things a bit, $\mathbb{G}(\delta)$ must be the identity 2-morphism of $\bold{1}$ and $h$ is a morphism of $\mathbb{C}\textnormal{ospan}(\bold{C})$, namely a triple of morphisms $(h_1,h,h_2)$ in $\bold{C}$ that makes the following diagram commute:
+Simplifying things a bit, $\mathbb{G}(\delta)$ must be the identity 2-morphism of $1$ and $h$ is a morphism of $\mathbb{C}\textnormal{ospan}(\mathrm{A})$, namely a triple of morphisms $(h_1,h,h_2)$ in $\mathrm{A}$ that makes the following diagram commute:
 \[
@@
 \node (A) at (4,0) {$\iota \Swarrow$};
-\node (D) at (3,0) {$\bold{1}$};
+\node (D) at (3,0) {$1$};
 \node (E) at (4.5,0.5) {$F(c)$};
@@
 which is just a morphism $\iota \colon F(h)(d) \to d^\prime$ in $F(c^\prime)$.
-Thus a morphism of $(\mathbb{G} / \mathbb{F})_1$ is a map of cospans in $\bold{C}$ together with a natural transformation that that makes the above triangle commute.
+Thus a morphism of $(\mathbb{G} / \mathbb{F})_1$ is a map of cospans in $\mathrm{A}$ together with a natural transformation that that makes the above triangle commute.
+\newline
 \textbf{Likely delete everything in this section before this line.}
 \begin{thm}
-Let $\bold{C}$ be a category with finite colimits and $F \colon \bold{C} \to \bold{Cat}$ a lax monoidal pseudofunctor.
-Then there exists a double category $\mathbb{F} \textnormal{Cospan}(\bold{C}) \coloneqq (\mathbb{G}/ \mathbb{F})$ which has:
+Let $\mathrm{A}$ be a category with finite colimits and $F \colon \mathrm{A} \to \bold{Cat}$ a lax monoidal pseudofunctor.
+Then there exists a double category $\mathbb{F} \textnormal{Cospan}(\mathrm{A}) \coloneqq (\mathbb{G}/ \mathbb{F})$ which has:
 \begin{enumerate}
-\item{objects as those of $\bold{C}$,}
-\item{vertical 1-morphisms as morphisms of $\bold{C}$,}
+\item{objects as those of $\mathrm{A}$,}
+\item{vertical 1-morphisms as morphisms of $\mathrm{A}$,}
 \item{horizontal 1-cells as pairs:
@@
 and}
-\item{2-morphisms as maps of cospans in $\bold{C}$
+\item{2-morphisms as maps of cospans in $\mathrm{A}$
 \[
@@
 \node (C) at (2,0) {$c$};
-\node (D) at (3,0) {$I \in F(c)$};
+\node (D) at (3,0) {$!_c \in F(c)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-where $I \in F(c)$ is the trivial decoration on $c$ given by the composition of the unique map $F(!) \colon F(0) \to F(c)$ and the morphism $\phi \colon \bold{1} \to F(0)$  which comes from the symmetric lax monoidal pseudofunctor $F \colon \bold{C} \to \bold{Cat}$.
+where $!_c \in F(c)$ is the trivial decoration on $c$ given by the composition of the unique map $F(!) \colon F(0) \to F(c)$ and the morphism $\phi \colon 1 \to F(0)$  which comes from the symmetric lax monoidal pseudofunctor $F \colon \mathrm{A} \to \bold{Cat}$.
 For morphisms, the structure functor $U$ is defined as:
@@
 \node (D) at (1,-0.5) {$c^\prime$};
-\node (E) at (3,0.5) {$I \in F(c)$};
-\node (F) at (3,-0.5) {$I^\prime \in F(c^\prime)$};
+\node (E) at (3,0.5) {$!_c \in F(c)$};
+\node (F) at (3,-0.5) {$!_{c^\prime} \in F(c^\prime)$};
 \node (H) at (-0.5,0) {$\mapsto$};
@@
 \]
-together with the morphism $\iota_{!_f} = F(f) F(!) \phi \colon \bold{1} \to F(c^\prime)$.
+together with the morphism $\iota_{!_f} = F(f) F(!) \phi \colon 1 \to F(c^\prime)$.
 We also have source and target structure functors $s,t \colon (\mathbb{G} / \mathbb{F})_1 \to (\mathbb{G} / \mathbb{F})_0$ where the source of a horizontal 1-cell
@@
 \]
-is the object $a$ in $\bold{C}$ and the source of a 2-morphism
+is the object $a$ in $\mathrm{A}$ and the source of a 2-morphism
 \[
@@
 $$\iota \colon F(h)(d) \to d^\prime$$
-is the source of the underlying map of cospans in $\bold{C}$, namely the morphism $f$ in $\bold{C}$; the target structure functor is defined similarly.
-The functors satisfy the equations $$SU(c)=1(c)=TU(c)$$for all objects $c$ of $\bold{C}$.
+is the source of the underlying map of cospans in $\mathrm{A}$, namely the morphism $f$ in $\mathrm{A}$; the target structure functor is defined similarly.
+The functors satisfy the equations $$SU(c)=1(c)=TU(c)$$for all objects $c$ of $\mathrm{A}$.
 
@@
 $$1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{d \times d^\prime} F(c) \times F(c^\prime) \xrightarrow{\phi_{c,c^\prime}} F(c+c^\prime) \xrightarrow{F(\psi)} F(c+_{b}c^\prime)$$
-where $\psi \colon c + c^\prime \to c+_b c^\prime$ is the natural map from the coproduct to the pushout and $\phi_{c,c^\prime} \colon F(c) \times F(c^\prime) \to F(c+c^\prime)$ is the natural transformation of the symmetric lax monoidal pseudofunctor $F \colon \bold{C} \to \bold{Cat}$.
+where $\psi \colon c + c^\prime \to c+_b c^\prime$ is the natural map from the coproduct to the pushout and $\phi_{c,c^\prime} \colon F(c) \times F(c^\prime) \to F(c+c^\prime)$ is the natural transformation of the symmetric lax monoidal pseudofunctor $F \colon \mathrm{A} \to \bold{Cat}$.
 Denoting the first and second of these horizontal 1-cells as $M$ and $N$, respectively, the source and target structure functors satisfy the equations $S(N \odot M)=S(M)$ and $T(N \odot M)=T(N)$.
@@
 where $\psi_b \colon b \to c+b$ is the natural map into the coproduct and likewise for $\psi_c$ and $j \colon c+b \to c+_b b$ is the natural map from the coproduct to the pushout.
-The decoration $\hat{d} \colon \bold{1} \to F(c+_b b)$ is given by: $$1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{d \times !_b} F(c) \times F(b) \xrightarrow{\phi_{c,b}} F(c+b) \xrightarrow{F(j_{c,b})} F(c+_b b).$$ We then have that the right unitor of the original horizontal 1-cell $M$ is given by the globular 2-morphism $(\id_a,\gamma,\id_b)$ from the above composite to $M$:
+The decoration $\hat{d} \colon 1 \to F(c+_b b)$ is given by: $$1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{d \times !_b} F(c) \times F(b) \xrightarrow{\phi_{c,b}} F(c+b) \xrightarrow{F(j_{c,b})} F(c+_b b).$$ We then have that the right unitor of the original horizontal 1-cell $M$ is given by the globular 2-morphism $(\id_a,\gamma,\id_b)$ from the above composite to $M$:
 \[
@@
 \node (A) at (4,0) {$\iota_1 \Swarrow$};
-\node (D) at (3,0) {$\bold{1}$};
+\node (D) at (3,0) {$1$};
 \node (E) at (4.5,0.5) {$F(c)$};
@@
 \node (A') at (6.5,0) {$\iota_2 \Swarrow$};
-\node (D') at (5.5,0) {$\bold{1}$};
+\node (D') at (5.5,0) {$1$};
 \node (E'') at (7,0.5) {$F(e)$};
@@
 \node (A) at (4.75,0) {$\iota_1 \times \iota_2 \Swarrow$};
-\node (D) at (3,0) {$\bold{1} \xrightarrow{\lambda^{-1}} \bold{1} \times \bold{1}$};
+\node (D) at (3,0) {$1 \xrightarrow{\lambda^{-1}} 1 \times 1$};
 \node (E) at (5.5,0.5) {$F(c) \times F(e)$};
@@
 \begin{thm}\label{main1}
-Let $\bold{C}$ be a category with finite colimits and $F \colon \bold{C} \to \bold{Cat}$ a symmetric lax monoidal pseudofunctor.
-Then the double category $\mathbb{F}\textnormal{Cospan}(\bold{C})$ is symmetric monoidal.
+Let $\mathrm{A}$ be a category with finite colimits and $F \colon \mathrm{A} \to \bold{Cat}$ a symmetric lax monoidal pseudofunctor.
+Then the double category $\mathbb{F}\textnormal{Cospan}(\mathrm{A})$ is symmetric monoidal.
 \end{thm}
 \begin{proof}
-First we note that the category of objects $\mathbb{F}\textnormal{Cospan}(\bold{C})_0=\bold{C}$ is symmetric monoidal under binary coproducts and the left and right unitors, associators and braidings are given as natural maps.
-The category of arrows $\mathbb{F}\textnormal{Cospan}(\bold{C})_1$ has:
+First we note that the category of objects $\mathbb{F}\textnormal{Cospan}(\mathrm{A})_0=\mathrm{A}$ is symmetric monoidal under binary coproducts and the left and right unitors, associators and braidings are given as natural maps.
+The category of arrows $\mathbb{F}\textnormal{Cospan}(\mathrm{A})_1$ has:
 \begin{enumerate}
@@
 and}
-\item{morphisms as maps of cospans in $\bold{C}$
+\item{morphisms as maps of cospans in $\mathrm{A}$
 \[
@@
 \end{enumerate}
-Given two objects $M_1$ and $M_2$ of $\mathbb{F}\textnormal{Cospan}(\bold{C})_1$:
+Given two objects $M_1$ and $M_2$ of $\mathbb{F}\textnormal{Cospan}(\mathrm{A})_1$:
 \[
@@
 \]
-their tensor product $M_1 \otimes M_2$ is given by taking the coproducts of the cospans of $\bold{C}$
+their tensor product $M_1 \otimes M_2$ is given by taking the coproducts of the cospans of $\mathrm{A}$
 \[
@@
 \]
-where $0$ is the monoidal unit of $\bold{C}$ and $!
-\colon \bold{1} \to F(0)$ is the morphism which is part of the structure of the symmetric lax monoidal pseudofunctor $F \colon \bold{C} \to \bold{Cat}$.
+where $0$ is the monoidal unit of $\mathrm{A}$ and $!
+\colon 1 \to F(0)$ is the morphism which is part of the structure of the symmetric lax monoidal pseudofunctor $F \colon \mathrm{A} \to \bold{Cat}$.
 Tensoring an object with the monoidal unit, say, on the left:
@@
 \]
-where $d^\prime \in F(0+c)$ is given by $$1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{\phi \times d} F(0) \times F(c) \xrightarrow{\phi_{0,d}} F(0+c).$$The left unitor is then a morphism in $\mathbb{F} \textnormal{Cospan}(\bold{C})_1$ given by:
+where $d^\prime \in F(0+c)$ is given by $$1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{\phi \times d} F(0) \times F(c) \xrightarrow{\phi_{0,d}} F(0+c).$$The left unitor is then a morphism in $\mathbb{F} \textnormal{Cospan}(\mathrm{A})_1$ given by:
 \[
@@
 \]
-where $\ell$ is the left unitor of $(\bold{C},+,0)$, together with the morphism $\iota_{\lambda} \colon F(\ell)(d^\prime) \to d$. The right unitor is similar.
-
-Given three objects $M_1, M_2$ and $M_3$ in $\mathbb{F}\textnormal{Cospan}(\bold{C})_1$:
+where $\ell$ is the left unitor of $(\mathrm{A},+,0)$, together with the morphism $\iota_{\lambda} \colon F(\ell)(d^\prime) \to d$. The right unitor is similar.
+
+Given three objects $M_1, M_2$ and $M_3$ in $\mathbb{F}\textnormal{Cospan}(\mathrm{A})_1$:
 \[
@@
 \]
-where $d_{(M_1 \otimes M_2) \otimes M_3} \colon \bold{1} \to F((c_1+c_2)+c_3)$ is given by: $$1 \xrightarrow{((d_1 \times d_2) \times d_3)} (F(c_1) \times F(c_2)) \times F(c_3) \xrightarrow{\phi_{c_1,c_2} \times 1} F(c_1+c_2) \times F(c_3) \xrightarrow{\phi_{c_1+c_2,c_3}} F((c_1+c_2)+c_3)$$whereas tensoring the last two and then the first results in $M_1 \otimes (M_2 \otimes M_3)$:
+where $d_{(M_1 \otimes M_2) \otimes M_3} \colon 1 \to F((c_1+c_2)+c_3)$ is given by: $$1 \xrightarrow{((d_1 \times d_2) \times d_3)} (F(c_1) \times F(c_2)) \times F(c_3) \xrightarrow{\phi_{c_1,c_2} \times 1} F(c_1+c_2) \times F(c_3) \xrightarrow{\phi_{c_1+c_2,c_3}} F((c_1+c_2)+c_3)$$whereas tensoring the last two and then the first results in $M_1 \otimes (M_2 \otimes M_3)$:
 \[
@@
 \]
-where $d_{M_1 \otimes (M_2 \otimes M_3)} \colon \bold{1} \to F(c_1+(c_2+c_3))$ is given by: $$1 \xrightarrow{d_1 \times (d_2 \times d_3)} F(c_1) \times (F(c_2) \times F(c_3)) \xrightarrow{1 \times \phi_{c_2,c_3}} F(c_1) \times F(c_2+c_3) \xrightarrow{\phi_{c_1,c_2+c_3}} F(c_1+(c_2+c_3)).$$If we let $a$ denote the associator of $(\bold{C},+,0)$, the associator of $\mathbb{F} \textnormal{Cospan}(\bold{C})_1$ is then a map of cospans in $\bold{C}$ from $(M_1 \otimes M_2) \otimes M_3)$ to $M_1 \otimes (M_2 \otimes M_3)$ given by:
+where $d_{M_1 \otimes (M_2 \otimes M_3)} \colon 1 \to F(c_1+(c_2+c_3))$ is given by: $$1 \xrightarrow{d_1 \times (d_2 \times d_3)} F(c_1) \times (F(c_2) \times F(c_3)) \xrightarrow{1 \times \phi_{c_2,c_3}} F(c_1) \times F(c_2+c_3) \xrightarrow{\phi_{c_1,c_2+c_3}} F(c_1+(c_2+c_3)).$$If we let $a$ denote the associator of $(\mathrm{A},+,0)$, the associator of $\mathbb{F} \textnormal{Cospan}(\mathrm{A})_1$ is then a map of cospans in $\mathrm{A}$ from $(M_1 \otimes M_2) \otimes M_3)$ to $M_1 \otimes (M_2 \otimes M_3)$ given by:
 \[
@@
 together with the isomorphism $\iota_a \colon F(a)(d_{(M_1 \otimes M_2) \otimes M_3}) \to d_{M_1 \otimes (M_2 \otimes M_3)}$.
-If we denote the above associator simply as $a$ and the left and right unitors as $\lambda$ and $\rho$, respectively, then given four objects in $\mathbb{F}\textnormal{Cospan}(\bold{C})_1$, say $M_1, M_2, M_3$ and $M_4$:
+If we denote the above associator simply as $a$ and the left and right unitors as $\lambda$ and $\rho$, respectively, then given four objects in $\mathbb{F}\textnormal{Cospan}(\mathrm{A})_1$, say $M_1, M_2, M_3$ and $M_4$:
 \[
@@
 
-For a monoidal product of objects $M_1 \otimes M_2$ in $\mathbb{F} \textnormal{Cospan}(\bold{C})_1$, the source and target structure functors $S,T \colon \mathbb{F} \textnormal{Cospan}(\bold{C})_1 \to \mathbb{F} \textnormal{Cospan}(\bold{C})_0$ satisfy the following equations: $$S(M_1 \otimes M_2)=S(M_1) \otimes S(M_2)$$ $$T(M_1 \otimes M_2)=T(M_1) \otimes T(M_2).$$
-For two objects $M_1$ and $M_2$ in $\mathbb{F} \textnormal{Cospan}(\bold{C})_1$, we have a braiding $\beta_{M_1,M_2} \colon M_1 \otimes M_2 \to M_2 \otimes M_1$ given by:
+For a monoidal product of objects $M_1 \otimes M_2$ in $\mathbb{F} \textnormal{Cospan}(\mathrm{A})_1$, the source and target structure functors $S,T \colon \mathbb{F} \textnormal{Cospan}(\mathrm{A})_1 \to \mathbb{F} \textnormal{Cospan}(\mathrm{A})_0$ satisfy the following equations: $$S(M_1 \otimes M_2)=S(M_1) \otimes S(M_2)$$ $$T(M_1 \otimes M_2)=T(M_1) \otimes T(M_2).$$
+For two objects $M_1$ and $M_2$ in $\mathbb{F} \textnormal{Cospan}(\mathrm{A})_1$, we have a braiding $\beta_{M_1,M_2} \colon M_1 \otimes M_2 \to M_2 \otimes M_1$ given by:
 \[
@@
 \]
-since $F(\beta_{c_1,c_2} \beta_{c_2,c_1}) (d_{M_2 \otimes M_1}) = d_{M_2 \otimes M_1}$. Thus $\mathbb{F} \textnormal{Cospan}(\bold{C})_1$ is also symmetric monoidal.
+since $F(\beta_{c_1,c_2} \beta_{c_2,c_1}) (d_{M_2 \otimes M_1}) = d_{M_2 \otimes M_1}$. Thus $\mathbb{F} \textnormal{Cospan}(\mathrm{A})_1$ is also symmetric monoidal.
 
@@
 $$\iota_{\hat{\chi}} \colon F(\hat{\chi})(d_{(M_1 \otimes N_1) \odot (M_2 \otimes N_2)}) \to d_{(M_1 \odot M_2) \otimes (N_1 \odot N_2)}.$$
-For two objects $a,b \in \bold{C}$, $U_{a+b}$ is given by:
+For two objects $a,b \in \mathrm{A}$, $U_{a+b}$ is given by:
 \[
@@
 \]
-Here, $a$ is the associator of $\mathbb{F}\textnormal{Cospan}(\bold{C})_1$ and $\mu$ is the first globular isomorphism above.
+Here, $a$ is the associator of $\mathbb{F}\textnormal{Cospan}(\mathrm{A})_1$ and $\mu$ is the first globular isomorphism above.
 To see that this diagram does indeed commute, we first consider this diagram with respect to only the underlying cospans of each horizontal 1-cell.
@@
 
-Another requirement for a double category to be symmetric monoidal is that the braiding $$\beta_{ ( \_, \_ ) } \colon \mathbb{F}\textnormal{Cospan}(\bold{C})_1 \times \mathbb{F}\textnormal{Cospan}(\bold{C})_1 \to \mathbb{F}\textnormal{Cospan}(\bold{C})_1 \times \mathbb{F}\textnormal{Cospan}(\bold{C})_1$$ be a transformation of double categories, and one of the diagrams that is required to commute is the following:
+Another requirement for a double category to be symmetric monoidal is that the braiding $$\beta_{ ( \_, \_ ) } \colon \mathbb{F}\textnormal{Cospan}(\mathrm{A})_1 \times \mathbb{F}\textnormal{Cospan}(\mathrm{A})_1 \to \mathbb{F}\textnormal{Cospan}(\mathrm{A})_1 \times \mathbb{F}\textnormal{Cospan}(\mathrm{A})_1$$ be a transformation of double categories, and one of the diagrams that is required to commute is the following:
 \[
@@
 \begin{lem}
-The double category $\mathbb{F}\textnormal{Cospan}(\bold{C})$ is fibrant.
+The double category $\mathbb{F}\textnormal{Cospan}(\mathrm{A})$ is fibrant.
 \end{lem}
@@
 \begin{proof}
-Let $f \colon c \to c^\prime$ be a vertical 1-morphism in $\mathbb{F} \textnormal{Cospan}(\bold{C})$. We can lift $f$ to the companion horizontal 1-cell $\hat{f}$:
+Let $f \colon c \to c^\prime$ be a vertical 1-morphism in $\mathbb{F} \textnormal{Cospan}(\mathrm{A})$. We can lift $f$ to the companion horizontal 1-cell $\hat{f}$:
 \[
@@
 \begin{thm}[Shulman]\label{Shul}
-Let $\mathbb{D}$ be an isofibrant symmetric monoidal pseudo double category. Then the horizontal bicategory $H(\mathbb{D})$ of $\mathbb{D}$ is a symmetric monoidal bicategory which has:
+Let $\mathbb{X}$ be an isofibrant symmetric monoidal pseudo double category. Then the horizontal bicategory $H(\mathbb{X})$ of $\mathbb{X}$ is a symmetric monoidal bicategory which has:
 \begin{enumerate}
-\item{objects as those of $\mathbb{D}$,}
-\item{morphisms as horizontal 1-cells of $\mathbb{D}$, and}
-\item{2-morphisms as globular 2-morphisms of $\mathbb{D}$.}
+\item{objects as those of $\mathbb{X}$,}
+\item{morphisms as horizontal 1-cells of $\mathbb{X}$, and}
+\item{2-morphisms as globular 2-morphisms of $\mathbb{X}$.}
 \end{enumerate}
@@
 \begin{thm}
-There exists a symmetric monoidal bicategory $H(\mathbb{F}\textnormal{Cospan}(\bold{C}))$ which has:
+There exists a symmetric monoidal bicategory $H(\mathbb{F}\textnormal{Cospan}(\mathrm{A}))$ which has:
 \begin{enumerate}
-\item{objects as those of $\bold{C}$,}
+\item{objects as those of $\mathrm{A}$,}
 \item{morphisms as pairs:
@@
 and}
-\item{2-morphisms as maps of cospans in $\bold{C}$ of the form:
+\item{2-morphisms as maps of cospans in $\mathrm{A}$ of the form:
 \[
@@
 The previous bicategory constructed by the second author suffered even more so from the issue discussed in the introduction.
-Given a symmetric lax monoidal functor $F \colon \bold{C} \to \bold{Set}$, a result of Fong \cite{Fong} yields a symmetric monoidal category $F \textnormal{Cospan}(\bold{C})$ which has:
+Given a symmetric lax monoidal functor $F \colon \mathrm{A} \to \mathrm{Set}$, a result of Fong \cite{Fong} yields a symmetric monoidal category $F \textnormal{Cospan}(\mathrm{A})$ which has:
 \begin{enumerate}
-\item{objects as those of $\bold{C}$ and}
-\item{morphisms as isomorphism classes of decorated cospans in $\bold{C}$.}
+\item{objects as those of $\mathrm{A}$ and}
+\item{morphisms as isomorphism classes of decorated cospans in $\mathrm{A}$.}
 \end{enumerate}
-The second author then using a result of Shulman \cite{Shul} extended this to a bicategory also called $F \textnormal{Cospan}(\bold{C})$ which has:
+The second author then using a result of Shulman \cite{Shul} extended this to a bicategory also called $F \textnormal{Cospan}(\mathrm{A})$ which has:
 \begin{enumerate}
-\item{objects as those of $\bold{C}$,}
-\item{morphisms as now just decorated cospans in $\bold{C}$, and}
+\item{objects as those of $\mathrm{A}$,}
+\item{morphisms as now just decorated cospans in $\mathrm{A}$, and}
 \item{2-morphisms as pairs of commuting diagrams:
@@
 \end{enumerate}
-This was discussed in the introduction and it was mentioned how in the symmetric monoidal category version of $F \textnormal{Cospan}(\bold{C})$, that the two single-edged graphs:
+This was discussed in the introduction and it was mentioned how in the symmetric monoidal category version of $F \textnormal{Cospan}(\mathrm{A})$, that the two single-edged graphs:
 \[
@@
 resided in distinct isomorphism classes.
-In the bicategorical version of $F \textnormal{Cospan}(\bold{C})$ where we are no longer considering decorated cospans up to isomorphism class, there is no 2-morphism between these two graphs due to the strict commutativity of the triangle to the right above.
-This problem does not occur in the symmetric monoidal bicategory $H(\mathbb{F}\textnormal{Cospan}(\bold{C}))$ and there is in fact a 2-(iso)morphism between these two graphs given by the map $\iota \colon F(f)(d) \to d^\prime$ which maps the edge $e$ to the edge $e^\prime$, where $f$ is the underlying map of vertices.
+In the bicategorical version of $F \textnormal{Cospan}(\mathrm{A})$ where we are no longer considering decorated cospans up to isomorphism class, there is no 2-morphism between these two graphs due to the strict commutativity of the triangle to the right above.
+This problem does not occur in the symmetric monoidal bicategory $H(\mathbb{F}\textnormal{Cospan}(\mathrm{A}))$ and there is in fact a 2-(iso)morphism between these two graphs given by the map $\iota \colon F(f)(d) \to d^\prime$ which maps the edge $e$ to the edge $e^\prime$, where $f$ is the underlying map of vertices.
 
@@
 \begin{cor}
-Given a symmetric lax monoidal pseudofunctor $F \colon \bold{C} \to \bold{Cat}$ where $\bold{C}$ is a category with finite colimits and whose monoidal structure is given by binary coproducts, there exists a symmetric monoidal category $D(H(F\textnormal{Cospan}(\bold{C})))$ which has:
+Given a symmetric lax monoidal pseudofunctor $F \colon \mathrm{A} \to \bold{Cat}$ where $\mathrm{A}$ is a category with finite colimits and whose monoidal structure is given by binary coproducts, there exists a symmetric monoidal category $D(H(\mathbb{F}\textnormal{Cospan}(\mathrm{A})))$ which has:
 \begin{enumerate}
-\item{objects as those of $\bold{C}$ and}
-\item{morphisms as isomorphism classes of $F$-decorated cospans of $\bold{C}$, where an $F$-decorated cospan is given by a pair:
+\item{objects as those of $\mathrm{A}$ and}
+\item{morphisms as isomorphism classes of $F$-decorated cospans of $\mathrm{A}$, where an $F$-decorated cospan is given by a pair:
 \[
@@
 \section{Maps of decorated cospan double categories}
-Let $F \colon \bold{C} \to \bold{Cat}$ be a symmetric lax monoidal pseudofunctor.
-Then by Theorem \ref{main1} of the previous section, we get a symmetric monoidal double category $\mathbb{F}\textnormal{Cospan}(\bold{C})$.
+Let $F \colon \mathrm{A} \to \bold{Cat}$ be a symmetric lax monoidal pseudofunctor.
+Then by Theorem \ref{main1} of the previous section, we get a symmetric monoidal double category $\mathbb{F}\textnormal{Cospan}(\mathrm{A})$.
 This symmetric monoidal double category has:
 \begin{enumerate}
-\item{objects as those of $\bold{C}$,}
-\item{vertical 1-morphisms as morphisms of $\bold{C}$,}
+\item{objects as those of $\mathrm{A}$,}
+\item{vertical 1-morphisms as morphisms of $\mathrm{A}$,}
 \item{horizontal 1-cells as pairs:
@@
 \end{enumerate}
-Given another symmetric lax monoidal pseudofunctor $F^\prime \colon \bold{C^\prime} \to \bold{Cat}$, we can obtain another symmetric monoidal double category $\mathbb{F^\prime}\textnormal{Cospan}(\bold{C^\prime})$.
-Then a map from $\mathbb{F}\textnormal{Cospan}(\bold{C})$ to $\mathbb{F^\prime}\textnormal{Cospan}(\bold{C^\prime})$ will be a double functor $\mathbb{H} \colon \mathbb{F}\textnormal{Cospan}(\bold{C}) \to \mathbb{F^\prime}\textnormal{Cospan}(\bold{C^\prime})$ whose object component is given by a finite colimit preserving functor $\mathbb{H}_0 = H \colon \bold{C} \to \bold{C^\prime}$ and whose arrow component is given by a functor $\mathbb{H}_1$ defined on horizontal 1-cells by:
+Given another symmetric lax monoidal pseudofunctor $F^\prime \colon \mathrm{A^\prime} \to \bold{Cat}$, we can obtain another symmetric monoidal double category $\mathbb{F^\prime}\textnormal{Cospan}(\mathrm{A^\prime})$.
+Then a map from $\mathbb{F}\textnormal{Cospan}(\mathrm{A})$ to $\mathbb{F^\prime}\textnormal{Cospan}(\mathrm{A^\prime})$ will be a double functor $\mathbb{H} \colon \mathbb{F}\textnormal{Cospan}(\mathrm{A}) \to \mathbb{F^\prime}\textnormal{Cospan}(\mathrm{A^\prime})$ whose object component is given by a finite colimit preserving functor $\mathbb{H}_0 = H \colon \mathrm{A} \to \mathrm{A^\prime}$ and whose arrow component is given by a functor $\mathbb{H}_1$ defined on horizontal 1-cells by:
 \[
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$\bold{C}$};
+\node (A) at (0,0) {$\mathrm{A}$};
 \node (B) at (1,0) {$\bold{Cat}$};
-\node (C) at (0,-1) {$\bold{C^\prime}$};
+\node (C) at (0,-1) {$\mathrm{A^\prime}$};
 \node (D) at (1,-1) {$\bold{Cat}$};
@@
 \]
-Recall that we can think of the element $d \in F(c)$ as a morphism $d \colon \bold{1} \to F(c)$ and the morphism $\iota \colon F(h)(d) \to d^\prime$ of $F(c^\prime)$ as a 2-morphism  in $\bold{Cat}$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,-0.5) {$\bold{1}$};
+Recall that we can think of the element $d \in F(c)$ as a morphism $d \colon 1 \to F(c)$ and the morphism $\iota \colon F(h)(d) \to d^\prime$ of $F(c^\prime)$ as a 2-morphism  in $\bold{Cat}$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,-0.5) {$1$};
 \node (B) at (1,0) {$F(c)$};
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,-0.5) {$E(\bold{1}) \cong \bold{1}$};
+\node (A) at (0,-0.5) {$E(1) \cong 1$};
 \node (B) at (1.5,0) {$E(F(c))$};
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,-0.5) {$E(\bold{1}) \cong \bold{1}$};
+\node (A) at (0,-0.5) {$E(1) \cong 1$};
 \node (B) at (1.5,0) {$F^\prime(H(c))$};
@@
 which is the same as a morphism $E(\iota) \colon F^\prime(H(h))(E(d)) \to E(d^\prime)$ in $F^\prime(H(c^\prime))$.
-To check that the above recipe is functorial, given two vertically composable 2-morphisms in $\mathbb{F}\textnormal{Cospan}(\bold{C})$:
+To check that the above recipe is functorial, given two vertically composable 2-morphisms in $\mathbb{F}\textnormal{Cospan}(\mathrm{A})$:
 \[
@@
 
-Given two composable horizontal 1-cells $M$ and $N$ in $\mathbb{F}\textnormal{Cospan}(\bold{C})$:
+Given two composable horizontal 1-cells $M$ and $N$ in $\mathbb{F}\textnormal{Cospan}(\mathrm{A})$:
 \[
@@
 \]
-where $\kappa$ is the isomorphism $$\kappa \colon H(c_1 +_b c_2) \xrightarrow{\sim} H(c_1) +_{H(b)} H(c_2)$$ which comes from the functor $H \colon \bold{C} \to \bold{C^\prime}$ preserving finite colimits.
+where $\kappa$ is the isomorphism $$\kappa \colon H(c_1 +_b c_2) \xrightarrow{\sim} H(c_1) +_{H(b)} H(c_2)$$ which comes from the functor $H \colon \mathrm{A} \to \mathrm{A^\prime}$ preserving finite colimits.
 The above diagram commutes by a similar argument as to the one used in Theorem \ref{main2}.
@@
 First, that the object component $\mathbb{H}_0=H$ is symmetric monoidal is clear as $H$ preserves finite colimits.
-As for the arrow component $\mathbb{H}_1$, given two horizontal 1-cells $M_1$ and $M_2$ in $\mathbb{F}\textnormal{Cospan}(\bold{C})$:
+As for the arrow component $\mathbb{H}_1$, given two horizontal 1-cells $M_1$ and $M_2$ in $\mathbb{F}\textnormal{Cospan}(\mathrm{A})$:
 \[
@@
 \]
-their tensor product $M_1 \otimes M_2$ in $\mathbb{F}\textnormal{Cospan}(\bold{C})$ is given by:
+their tensor product $M_1 \otimes M_2$ in $\mathbb{F}\textnormal{Cospan}(\mathrm{A})$ is given by:
 \[
@@
 \node (A) at (0,0) {$H(a_1)+H(a_2)$};
-\node (B) at (2,0) {$H(c_1)+H(c_2)$};
-\node (C) at (4,0) {$H(b_1)+H(b_2)$};
-\node (D) at (2,-0.5) {$E(d_1)+E(d_2) \in F^\prime(H(c_1)+H(c_2))$};
+\node (B) at (2.5,0) {$H(c_1)+H(c_2)$};
+\node (C) at (5,0) {$H(b_1)+H(b_2)$};
+\node (D) at (2.5,-0.5) {$E(d_1)+E(d_2) \in F^\prime(H(c_1)+H(c_2))$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-$$E(d_1)+E(d_2) \colon 1 \xrightarrow{E(d_1) \times E(d_2)} F^\prime(H(c_1)) \times F^\prime(H(c_2)) \xrightarrow{\Phi_{H(c_1),H(c_2)}} F^\prime (H(c_1)+H(c_2)).$$  We then have a natural 2-isomorphism $\mu_{M_1,M_2} \colon \mathbb{H}(M_1) \otimes \mathbb{H}(M_2) \to \mathbb{H}(M_1 \otimes M_2)$ in $\mathbb{F^\prime}\textnormal{Cospan}(\bold{C^\prime})$ given by:
+$$E(d_1)+E(d_2) \colon 1 \xrightarrow{E(d_1) \times E(d_2)} F^\prime(H(c_1)) \times F^\prime(H(c_2)) \xrightarrow{\Phi_{H(c_1),H(c_2)}} F^\prime (H(c_1)+H(c_2)).$$  We then have a natural 2-isomorphism $\mu_{M_1,M_2} \colon \mathbb{H}(M_1) \otimes \mathbb{H}(M_2) \to \mathbb{H}(M_1 \otimes M_2)$ in $\mathbb{F^\prime}\textnormal{Cospan}(\mathrm{A^\prime})$ given by:
 \[
@@
 where $\kappa$ denotes the isomorphism arising from $H$ preserving finite colimits.
-This natural 2-isomorphism together with the associators of $\mathbb{F}\textnormal{Cospan}(\bold{C})$ and $\mathbb{F^\prime} \textnormal{Cospan}(\bold{C^\prime})$, respectively $\alpha$ and $\alpha^\prime$, make the following diagram commute:
+This natural 2-isomorphism together with the associators of $\mathbb{F}\textnormal{Cospan}(\mathrm{A})$ and $\mathbb{F^\prime} \textnormal{Cospan}(\mathrm{A^\prime})$, respectively $\alpha$ and $\alpha^\prime$, make the following diagram commute:
 \[
@@
 where $$F^\prime(\alpha \kappa \kappa)((E(d_1)+E(d_2))+E(d_3)) = F^\prime(\kappa \kappa \alpha^\prime)((E(d_1)+E(d_2))+E(d_3)).$$
-We also have that the monoidal unit of $\mathbb{F}\textnormal{Cospan}(\bold{C})_1$ is given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$1_\bold{C}$};
-\node (B) at (1,0) {$1_\bold{C}$};
-\node (C) at (2,0) {$1_\bold{C}$};
-\node (D) at (1,-0.5) {$!_{1_\bold{C}} \in F(1_\bold{C})$};
+We also have that the monoidal unit of $\mathbb{F}\textnormal{Cospan}(\mathrm{A})_1$ is given by:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$1_\mathrm{A}$};
+\node (B) at (1,0) {$1_\mathrm{A}$};
+\node (C) at (2,0) {$1_\mathrm{A}$};
+\node (D) at (1,-0.5) {$!_{1_\mathrm{A}} \in F(1_\mathrm{A})$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-where $1_\bold{C}$ is the monoidal unit of the finitely cocartesian category $\bold{C}$. The image of this horizontal 1-cell under $\mathbb{H}$ is given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$H(1_\bold{C})$};
-\node (B) at (1,0) {$H(1_\bold{C})$};
-\node (C) at (2,0) {$H(1_\bold{C})$};
+where $1_\mathrm{A}$ is the monoidal unit of the finitely cocartesian category $\mathrm{A}$. The image of this horizontal 1-cell under $\mathbb{H}$ is given by:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$H(1_\mathrm{A})$};
+\node (B) at (1,0) {$H(1_\mathrm{A})$};
+\node (C) at (2,0) {$H(1_\mathrm{A})$};
 \node (E) at (3,0) {$=$};
-\node (F) at (4,0) {$1_\bold{C^\prime}$};
-\node (G) at (5,0) {$1_\bold{C^\prime}$};
-\node (H) at (6,0) {$1_\bold{C^\prime}$};
-\node (I) at (5,-0.5) {$!_{1_{\bold{C^\prime}}} \in F^\prime(1_{\bold{C^\prime}})$};
-\node (D) at (1,-0.5) {$E(!_{1_\bold{C}}) \in F^\prime(H(1_\bold{C}))$};
+\node (F) at (4,0) {$1_\mathrm{A^\prime}$};
+\node (G) at (5,0) {$1_\mathrm{A^\prime}$};
+\node (H) at (6,0) {$1_\mathrm{A^\prime}$};
+\node (I) at (5,-0.5) {$!_{1_{\mathrm{A^\prime}}} \in F^\prime(1_{\mathrm{A^\prime}})$};
+\node (D) at (1,-0.5) {$E(!_{1_\mathrm{A}}) \in F^\prime(H(1_\mathrm{A}))$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 since $H$ preserves finite colimits.
-We then have a 2-isomorphism in $\mathbb{F^\prime}\textnormal{Cospan}(\bold{C^\prime})$ given by: $$\mu \colon 1_{\mathbb{F^\prime}\textnormal{Cospan}(\bold{C^\prime})_1} \to \mathbb{H}(1_{\mathbb{F}\textnormal{Cospan}(\bold{C})_1})$$
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$1_{\bold{C^\prime}}$};
-\node (A') at (0,-0.5) {$H(1_\bold{C})$};
-\node (B) at (1.5,0.5) {$1_{\bold{C^\prime}}$};
-\node (C) at (3,0.5) {$1_{\bold{C^\prime}}$};
-\node (C') at (3,-0.5) {$H(1_\bold{C})$};
-\node (D) at (1.5,-0.5) {$H(1_\bold{C})$};
-\node (E) at (4.5,0.5) {$!_{1_\bold{C^\prime}} \in F^\prime(1_\bold{C^\prime})$};
-\node (F) at (4.5,-0.5) {$E(!_{1_\bold{C}}) \in F^\prime(H(1_\bold{C}))$};
+We then have a 2-isomorphism in $\mathbb{F^\prime}\textnormal{Cospan}(\mathrm{A^\prime})$ given by: $$\mu \colon 1_{\mathbb{F^\prime}\textnormal{Cospan}(\mathrm{A^\prime})_1} \to \mathbb{H}(1_{\mathbb{F}\textnormal{Cospan}(\mathrm{A})_1})$$
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0.5) {$1_{\mathrm{A^\prime}}$};
+\node (A') at (0,-0.5) {$H(1_\mathrm{A})$};
+\node (B) at (1.5,0.5) {$1_{\mathrm{A^\prime}}$};
+\node (C) at (3,0.5) {$1_{\mathrm{A^\prime}}$};
+\node (C') at (3,-0.5) {$H(1_\mathrm{A})$};
+\node (D) at (1.5,-0.5) {$H(1_\mathrm{A})$};
+\node (E) at (4.5,0.5) {$!_{1_\mathrm{A^\prime}} \in F^\prime(1_\mathrm{A^\prime})$};
+\node (F) at (4.5,-0.5) {$E(!_{1_\mathrm{A}}) \in F^\prime(H(1_\mathrm{A}))$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-together with the morphism $\iota_\mu \colon F^\prime(\kappa)(!_{1_\bold{C^\prime}}) \to E(!_{1_\bold{C}})$ in $F^\prime(H(1_\bold{C}))$. The following square then commutes: 
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$1_\bold{C^\prime} \otimes \mathbb{H}(M)$};
-\node (B) at (2.5,0) {$\mathbb{H}(1_\bold{C}) \otimes \mathbb{H}(M)$};
+together with the morphism $\iota_\mu \colon F^\prime(\kappa)(!_{1_\mathrm{A^\prime}}) \to E(!_{1_\mathrm{A}})$ in $F^\prime(H(1_\mathrm{A}))$. The following square then commutes: 
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$1_\mathrm{A^\prime} \otimes \mathbb{H}(M)$};
+\node (B) at (2.5,0) {$\mathbb{H}(1_\mathrm{A}) \otimes \mathbb{H}(M)$};
 \node (C) at (0,-1) {$\mathbb{H}(M)$};
-\node (D) at (2.5,-1) {$\mathbb{H}(1_\bold{C} + M)$};
+\node (D) at (2.5,-1) {$\mathbb{H}(1_\mathrm{A} + M)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (A) edge node[left]{$\ell$} (C)
-(B) edge node[right]{$\mu_{1_\bold{C},M}$} (D)
+(B) edge node[right]{$\mu_{1_\mathrm{A},M}$} (D)
 (D) edge node[above]{$\mathbb{H}(\ell^\prime)$} (C);
@@
 \]
-where we have abbreviated the monoidal units of $\mathbb{F}\textnormal{Cospan}(\bold{C})_1$ and $\mathbb{F^\prime}\textnormal{Cospan}(\bold{C^\prime})_1$ as $1_\bold{C}$ and $1_\bold{C^\prime}$, respectively.
+where we have abbreviated the monoidal units of $\mathbb{F}\textnormal{Cospan}(\mathrm{A})_1$ and $\mathbb{F^\prime}\textnormal{Cospan}(\mathrm{A^\prime})_1$ as $1_\mathrm{A}$ and $1_\mathrm{A^\prime}$, respectively.
 The diagram of corresponding decorations is given by:
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$F^\prime(\ell)(!_{1_\bold{C^\prime}} + E(d))$};
+\node (A) at (0,0.5) {$F^\prime(\ell)(!_{1_\mathrm{A^\prime}} + E(d))$};
 \node (B) at (0,-0.5) {$E(d)$};
-\node (A') at (4,0.5) {$F^\prime(H(\ell^\prime) \kappa)(E(!_{1_\bold{C}})+E(d))$};
-\node (B') at (4,-0.5) {$F^\prime(H(\ell^\prime))(E(!_{1_\bold{C}} + d))$};
+\node (A') at (4,0.5) {$F^\prime(H(\ell^\prime) \kappa)(E(!_{1_\mathrm{A}})+E(d))$};
+\node (B') at (4,-0.5) {$F^\prime(H(\ell^\prime))(E(!_{1_\mathrm{A}} + d))$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-where $$F^\prime(\ell)(!_{1_\bold{C^\prime}} + E(d))=F^\prime(H(\ell^\prime)\kappa(\mu+1))(!_{1_\bold{C^\prime}} + E(d)).$$ The other square involving the right unitors $r$ and $r^\prime$ is similar.
+where $$F^\prime(\ell)(!_{1_\mathrm{A^\prime}} + E(d))=F^\prime(H(\ell^\prime)\kappa(\mu+1))(!_{1_\mathrm{A^\prime}} + E(d)).$$ The other square involving the right unitors $r$ and $r^\prime$ is similar.
 Note that because $\mu$ and $\mu_{(\_ , \_)}$ are both isomorphisms, the symmetric monoidal double functor $\mathbb{H}$ is strong.
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$\bold{1}$};
-\node (A') at (0,-0.5) {$F^\prime(1_\bold{C^\prime})$};
-\node (B) at (1.5,0.5) {$F(1_\bold{C})$};
+\node (A) at (0,0.5) {$1$};
+\node (A') at (0,-0.5) {$F^\prime(1_\mathrm{A^\prime})$};
+\node (B) at (1.5,0.5) {$F(1_\mathrm{A})$};
 \node (C) at (3.5,0.5) {$F(c)$};
@@
 
-%is given by $$\bold{1} \to F(c_1) \times F(c_2) \xrightarrow{} F(c_1 + c_2) \xrightarrow{} F(c_1 + _b c_2)$$ and then applying the functor $E$ results in $\bold{1} \to E(F(c_1+_b c_2))$, which by the comutative square is the same as $\bold{1} \to F^\prime(H(c_1+_b c_2))$.
-On the other hand, applying the functor $E$ to each decoration results in $$\bold{1} \to E(F(c_1)) \times E(F(c_2)) \xrightarrow{} E(F(c_1) \times F(c_2)) \xrightarrow{} E(F(c_1+c_2)) \xrightarrow E(F(c_1+_b c_2)) \xrightarrow{} F^\prime(H(c_1 +_b c_2))$$
+%is given by $$1 \to F(c_1) \times F(c_2) \xrightarrow{} F(c_1 + c_2) \xrightarrow{} F(c_1 + _b c_2)$$ and then applying the functor $E$ results in $1 \to E(F(c_1+_b c_2))$, which by the comutative square is the same as $1 \to F^\prime(H(c_1+_b c_2))$.
+On the other hand, applying the functor $E$ to each decoration results in $$1 \to E(F(c_1)) \times E(F(c_2)) \xrightarrow{} E(F(c_1) \times F(c_2)) \xrightarrow{} E(F(c_1+c_2)) \xrightarrow E(F(c_1+_b c_2)) \xrightarrow{} F^\prime(H(c_1 +_b c_2))$$
 
 \section{From pseudofunctors to left adjoints}
-In this section we investigate the necessary conditions to obtain a category $\bold{D}$ and a left adjoint $L \colon \bold{C} \to \bold{D}$ from a category $\bold{C}$ with finite colimits and a symmetric lax monoidal pseudofunctor $F \colon \bold{C} \to \bold{Cat}$.
+In this section we investigate the necessary conditions to obtain a category $\mathrm{X}$ and a left adjoint $L \colon \mathrm{A} \to \mathrm{X}$ from a category $\mathrm{A}$ with finite colimits and a symmetric lax monoidal pseudofunctor $F \colon \mathrm{A} \to \bold{Cat}$.
 The main tool that allows us to do this will be the Grothendieck construction which we recall:
@@
 \begin{enumerate}
-\item{objects as pairs $(\bold{C},c)$ where $\bold{C}$ is a category and $c$ is an object of $\bold{C}$, and}
-\item{a morphism from $(\bold{C},c)$ to $(\bold{D},d)$ is a pair $(F,f)$ where $F \colon \bold{C} \to \bold{D}$ is a functor and $f \colon F(c) \to d$ is a morphism in $\bold{D}$.}
+\item{objects as pairs $(\mathrm{A},c)$ where $\mathrm{A}$ is a category and $c$ is an object of $\mathrm{A}$, and}
+\item{a morphism from $(\mathrm{A},c)$ to $(\mathrm{X},y)$ is a pair $(F,f)$ where $F \colon \mathrm{A} \to \mathrm{X}$ is a functor and $f \colon F(c) \to y$ is a morphism in $\mathrm{X}$.}
 \end{enumerate}
@@
 \begin{defn}
-Given a pseudofunctor $F \colon \bold{C} \to \bold{Cat}$, the \define{Grothendieck construction of} $F$ is given by the `strict 2-pullback' of the following cospan:
+Given a pseudofunctor $F \colon \mathrm{A} \to \bold{Cat}$, the \define{Grothendieck construction of} $F$ is given by the `strict 2-pullback' of the following cospan:
  \[
@@
 \node (D) at (1,1) {$\int F$};
-\node (A) at (0,0) {$\bold{C}$};
+\node (A) at (0,0) {$\mathrm{A}$};
 \node (B) at (1,-1) {$\bold{Cat}$};
@@
 \begin{defn}
-Given bicategories $\bold{C}$ and $\bold{D}$ and 2-functors (possibly lax or oplax) $(F,\phi),(G,\psi) \colon \bold{C} \to \bold{D}$, a \define{pseudonatural transformation} $\sigma \colon (F,\phi) \to (G,\psi)$ consists of:
+Given bicategories $\bold{A}$ and $\bold{X}$ and 2-functors (possibly lax or oplax) $(F,\phi),(G,\psi) \colon \bold{A} \to \bold{X}$, a \define{pseudonatural transformation} $\sigma \colon (F,\phi) \to (G,\psi)$ consists of:
 \begin{enumerate}
-\item{for each object $a \in \bold{C}$, a morphism $\sigma_a \colon F(a) \to G(a)$ in $\bold{D}$ and}
-\item{for every pair of objects $a$ and $b$ of $\bold{C}$, we have natural isomorphisms:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$\bold{C}(a,b)$};
-\node (B) at (2,0) {$\bold{D}(F(a),F(b))$};
-\node (C) at (0,-1) {$\bold{D}(G(a),G(b))$};
-\node (D) at (2,-1) {$\bold{D}(F(a),G(b))$};
+\item{for each object $a \in \bold{A}$, a morphism $\sigma_a \colon F(a) \to G(a)$ in $\bold{X}$ and}
+\item{for every pair of objects $a$ and $b$ of $\bold{A}$, we have natural isomorphisms:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$\bold{A}(a,b)$};
+\node (B) at (2,0) {$\bold{X}(F(a),F(b))$};
+\node (C) at (0,-1) {$\bold{X}(G(a),G(b))$};
+\node (D) at (2,-1) {$\bold{X}(F(a),G(b))$};
 \node (E) at (1,-0.5) {$\sigma_{a,b} \Nearrow$};
@@
 where $(\sigma_a)^*$ and $(\sigma_b)_*$ are the functors induced by precomposition and postcompositon, respectively.
-Thus for each morphism $f \colon a \to b$ in $\bold{C}$, we have an invertible 2-morphism $\sigma_f \colon G(f) \sigma_a \xrightarrow{\sim} \sigma_{b} F(f)$ in $\bold{D}$:
+Thus for each morphism $f \colon a \to b$ in $\bold{A}$, we have an invertible 2-morphism $\sigma_f \colon G(f) \sigma_a \xrightarrow{\sim} \sigma_{b} F(f)$ in $\bold{X}$:
 \[
@@
 \end{enumerate}
-such that for each composable pair of morphisms $f \colon a \to b$ and $g \colon b \to c$ of $\bold{C}$, the following diagrams commute:
+such that for each composable pair of morphisms $f \colon a \to b$ and $g \colon b \to c$ of $\bold{A}$, the following diagrams commute:
 \[
@@
 
-Let $[\bold{C},\bold{Cat}]_{\textnormal{pseudo}}$ denote the 2-category which has:
+Let $[\bold{A},\bold{Cat}]_{\textnormal{pseudo}}$ denote the 2-category which has:
 \begin{enumerate}
-\item{objects as pseudofunctors $(F,\phi) \colon \bold{C} \to \bold{Cat}$,}
-\item{a morphism from a pseudofunctor $(F,\phi) \colon \bold{C} \to \bold{Cat}$ to another $(G,\psi) \colon \bold{C} \to \bold{Cat}$ is a pseudonatural transformation $\sigma \colon (F,\phi) \to (G,\psi)$, and}
-\item{2-morphisms are modifications.}
+\item{objects as pseudofunctors $(F,\phi) \colon \bold{A} \to \bold{Cat}$,}
+\item{a morphism from a pseudofunctor $(F,\phi) \colon \bold{A} \to \bold{Cat}$ to another $(G,\psi) \colon \bold{A} \to \bold{Cat}$ is a pseudonatural transformation $\sigma \colon (F,\phi) \to (G,\psi)$, and}
+\item{2-morphisms as modifications.}
 \end{enumerate}
@@
 %\begin{defn}
-%Let $P \colon \bold{D} \to \bold{C}$ be a functor.
+%Let $P \colon \bold{D} \to \mathrm{A}$ be a functor.
 A morphism $f \colon d_{1} \to d_{2}$ in the category $\bold{D}$ is \textbf{cartesian (with respect to the functor P)} if for any object $d^\prime$ in $\bold{D}$ and morphism $g \colon d^\prime \to d_{2}$ and every $p \colon P(d^\prime) \to P(d_{1})$ such that $P(g)=P(f)p$, there exists a unique $h \colon d^\prime \to d_{1}$ such that $g=fh$ and $p=P(h)$.
@@
 \begin{defn}
-Let $P \colon \bold{D} \to \bold{C}$ be a functor.
-A morphism $f \colon d_{1} \to d_{2}$ in the category $\bold{D}$ is \textbf{cocartesian (with respect to the functor P)} if for any object $d^\prime$ in $\bold{D}$ and morphism $g \colon d_{1} \to d^\prime$ and every $p \colon P(d_{2}) \to P(d^\prime)$ such that $P(g)=p P(f)$, there exists a unique $h \colon d_{2} \to d^\prime$ such that $g=hf$ and $p=P(h)$.
+Let $P \colon \mathrm{D} \to \mathrm{A}$ be a functor.
+A morphism $f \colon d_{1} \to d_{2}$ in the category $\mathrm{D}$ is \textbf{cocartesian (with respect to the functor P)} if for any object $d^\prime$ in $\mathrm{D}$ and morphism $g \colon d_{1} \to d^\prime$ and every $p \colon P(d_{2}) \to P(d^\prime)$ such that $P(g)=p P(f)$, there exists a unique $h \colon d_{2} \to d^\prime$ such that $g=hf$ and $p=P(h)$.
 \[
@@
 \begin{defn}
-A functor $P \colon \bold{D} \to \bold{C}$ is a \textbf{(Grothendieck) opfibration} if for any object $d$ in $\bold{D}$ and morphism $f \colon c \to P(d)$ there exists a cocartesian morphism $\phi \colon d^\prime \to d$ such that $P(\phi)=f$.
+A functor $P \colon \mathrm{D} \to \mathrm{A}$ is a \textbf{(Grothendieck) opfibration} if for any object $d$ in $\bold{D}$ and morphism $f \colon c \to P(d)$ there exists a cocartesian morphism $\phi \colon d^\prime \to d$ such that $P(\phi)=f$.
 \end{defn}
@@
 \begin{defn}
-Let $P \colon \bold{D} \to \bold{C}$ and $P^\prime \colon \bold{D^\prime} \to \bold{C}$ be opfibrations over a category $\bold{C}$.
-A \define{morphism of opfibrations} is a functor $F \colon \bold{D} \to \bold{D}^\prime$ such that $F(p)$ is cocartesian with respect to $P^\prime$ if $p$ is cocartesian with respect to $P$ and $P=P^\prime F$.
+Let $P \colon \mathrm{D} \to \mathrm{A}$ and $P^\prime \colon \mathrm{D^\prime} \to \mathrm{A}$ be opfibrations over a category $\mathrm{A}$.
+A \define{morphism of opfibrations} is a functor $F \colon \mathrm{D} \to \mathrm{D}^\prime$ such that $F(p)$ is cocartesian with respect to $P^\prime$ if $p$ is cocartesian with respect to $P$ and $P=P^\prime F$.
 \end{defn}
 
-Let Opfib$(\bold{C})$ denote the 2-category of opfibrations over $\bold{C}$ which has:
+Let Opfib$(\mathrm{A})$ denote the 2-category of opfibrations over $\mathrm{A}$ which has:
 \begin{enumerate}
-\item{objects as opfibrations $P \colon \bold{D} \to \bold{C}$,}
+\item{objects as opfibrations $P \colon \mathrm{D} \to \mathrm{A}$,}
 \item{morphisms as morphisms of opfibrations, and}
@@
 
-The 2-category Opfib$(\bold{C})$ is a 2-subcategory of $\bold{Cat}/ \bold{C}$ where $\bold{Cat} / \bold{C}$ is the 2-category of functors over $\bold{C}$.
-The Grothendieck construction is a 2-functor $\int F \colon [ \bold{C},\bold{Cat}] \to \bold{Cat}/ \bold{C}$ which factors through the image of the embedding $\textnormal{Opfib}(\bold{C}) \hookrightarrow \bold{Cat} / \bold{C}$: $$\int F \colon [ \bold{C}, \bold{Cat} ] \to \textnormal{Opfib}(\bold{C}) \hookrightarrow \bold{Cat} / \bold{C}.$$
-
-Under certain conditions, the functor resulting from the Grothendieck construction $p \colon \int{F} \to \bold{C}$ will be right adjoint to the desired left adjoint $L \colon \bold{C} \to \bold{D}$.
+The 2-category Opfib$(\mathrm{A})$ is a 2-subcategory of $\bold{Cat}/ \mathrm{A}$ where $\bold{Cat} / \mathrm{A}$ is the 2-category of functors over $\mathrm{A}$.
+The Grothendieck construction is a 2-functor $\int F \colon [ \mathrm{A},\bold{Cat}] \to \bold{Cat}/ \mathrm{A}$ which factors through the image of the embedding $\textnormal{Opfib}(\mathrm{A}) \hookrightarrow \bold{Cat} / \mathrm{A}$: $$\int F \colon [ \mathrm{A}, \bold{Cat} ] \to \textnormal{Opfib}(\mathrm{A}) \hookrightarrow \bold{Cat} / \mathrm{A}.$$
+
+Under certain conditions, the functor resulting from the Grothendieck construction $p \colon \int{F} \to \mathrm{A}$ will be right adjoint to the desired left adjoint $L \colon \mathrm{A} \to \mathrm{X}$.
 
 \section{An equivalence of symmetric monoidal double categories}
-In this section we prove that two different frameworks which utilize symmetric monoidal double categories, namely decorated cospans and `structured cospans', are equivalent under the conditions required from the previous section that allow for a left adjoint $L \colon \bold{C} \to \bold{D}$ to be obtained from a symmetric lax monoidal pseudofunctor $F \colon \bold{C} \to \bold{Cat}$.
+In this section we prove that two different frameworks which utilize symmetric monoidal double categories, namely decorated cospans and `structured cospans', are equivalent under the conditions required from the previous section that allow for a left adjoint $L \colon \mathrm{A} \to \mathrm{X}$ to be obtained from a symmetric lax monoidal pseudofunctor $F \colon \mathrm{A} \to \bold{Cat}$.
 The double category version of decorataed cospans is given in Section \ref{DecCospansDoublecat}.
 The other framework which also utilizes symmetric monoidal double categories, due to Baez and the first author and goes by the name of `structured cospans', is explained below.
-Once again following the notation of Shulman \cite{Shul2}, given a double category $\mathbb{C}$, we write $_f \mathbb{C}_g(M,N)$ for the set of 2-morphisms in $\mathbb{C}$ of the form:
+Once again following the notation of Shulman \cite{Shul2}, given a double category $\mathbb{A}$, we write $_f \mathbb{A}_g(M,N)$ for the set of 2-morphisms in $\mathbb{A}$ of the form:
 \[
@@
 We call $M$ and $N$ the \define{horizontal source and target} of the 2-morphism $a$, respectively, and likewise we call $f$ and $g$ the \define{vertical source and target} of the 2-morphism $a$, respectively.
-Thus $_f \mathbb{C}_g(M,N)$ denotes the set of 2-morphisms in $\mathbb{C}$ with horizontal source and target $M$ and $N$ and vertical source and target $f$ and $g$.
+Thus $_f \mathbb{A}_g(M,N)$ denotes the set of 2-morphisms in $\mathbb{A}$ with horizontal source and target $M$ and $N$ and vertical source and target $f$ and $g$.
 \begin{defn}
-A (possibly lax or oplax) double functor $\mathbb{F} \colon \mathbb{C} \to \mathbb{D}$ is \define{full} (respectively, \define{faithful}) if $\mathbb{F}_0 \colon \mathbb{C}_0 \to \mathbb{D}_0$ is full (respectively, faithful) and each map $$\mathbb{F}_1 \colon _f \mathbb{C}_g(M,N) \to _{\mathbb{F}(f)} \mathbb{D}_{\mathbb{F}(g)}(\mathbb{F}(M),\mathbb{F}(N))$$ is surjective (respectively, injective).
+A (possibly lax or oplax) double functor $\mathbb{F} \colon \mathbb{A} \to \mathbb{X}$ is \define{full} (respectively, \define{faithful}) if $\mathbb{F}_0 \colon \mathbb{A}_0 \to \mathbb{X}_0$ is full (respectively, faithful) and each map $$\mathbb{F}_1 \colon _f \mathbb{A}_g(M,N) \to _{\mathbb{F}(f)} \mathbb{X}_{\mathbb{F}(g)}(\mathbb{F}(M),\mathbb{F}(N))$$ is surjective (respectively, injective).
 \end{defn}
 \begin{defn}
-A (possibly lax or oplax) double functor $\mathbb{F} \colon \mathbb{C} \to \mathbb{D}$ is \define{essentially surjective} if we can simultaneously make the following choices:
+A (possibly lax or oplax) double functor $\mathbb{F} \colon \mathbb{A} \to \mathbb{X}$ is \define{essentially surjective} if we can simultaneously make the following choices:
 \begin{enumerate}
-\item{For each object $d \in \mathbb{D}$, we can find an object $\hat{d} \in \mathbb{C}$ together with a vertical 1-isomorphism $\alpha_d \colon \mathbb{F}(\hat{d}) \to d$, and}
-\item{For each horizontal 1-cell $N \colon d_1 \tobar d_2$  of $\mathbb{D}$, we can find a horizontal 1-cell $\hat{N} \colon \hat{d_1} \tobar \hat{d_2}$ of $\mathbb{C}$ and a 2-isomorphism $a_{N}$ of $\mathbb{D}$ as in the following diagram:
+\item{For each object $x \in \mathbb{X}$, we can find an object $a \in \mathbb{A}$ together with a vertical 1-isomorphism $\alpha_x \colon \mathbb{F}(a) \to x$, and}
+\item{For each horizontal 1-cell $N \colon x_1 \tobar x_2$  of $\mathbb{X}$, we can find a horizontal 1-cell $M \colon a_1 \tobar a_2$ of $\mathbb{A}$ and a 2-isomorphism $a_{N}$ of $\mathbb{X}$ as in the following diagram:
 \[
   \xymatrix@-.5pc{
-    \mathbb{F}(\hat{d_1}) \ar[r]|{|}^{\mathbb{F}(\hat{N})}  \ar[d]_{\alpha_{d_1}} \ar@{}[dr]|{\Downarrow a_N}&
-    \mathbb{F}(\hat{d_2}) \ar[d]^{\alpha_{d_2}}\\
-    d_1 \ar[r]|{|}_N & d_2
+    \mathbb{F}(a_1) \ar[r]|{|}^{\mathbb{F}(M)}  \ar[d]_{\alpha_{x_1}} \ar@{}[dr]|{\Downarrow a_N}&
+    \mathbb{F}(a_1) \ar[d]^{\alpha_{x_2}}\\
+    x_1 \ar[r]|{|}_N & x_2
   }
@@
 \begin{defn}
-A double functor $\mathbb{F} \colon \mathbb{C} \to \mathbb{D}$ is \define{strong} if the comparison and unit constraints are globular isomorphisms, meaning that for each composable pair of horizontal 1-cells $M$ and $N$ we have a natural isomorphism $$\mathbb{F}_{M,N} \colon \mathbb{F}(M) \odot \mathbb{F}(N) \xrightarrow{\sim} \mathbb{F}(M \odot N)$$and for each object $c \in \mathbb{C}$ a natural isomorphism $$\mathbb{F}_c \colon \hat{U}_{\mathbb{F}(c)} \xrightarrow{\sim} \mathbb{F}(U_c).$$
+A double functor $\mathbb{F} \colon \mathbb{A} \to \mathbb{X}$ is \define{strong} if the comparison and unit constraints are globular isomorphisms, meaning that for each composable pair of horizontal 1-cells $M$ and $N$ we have a natural isomorphism $$\mathbb{F}_{M,N} \colon \mathbb{F}(M) \odot \mathbb{F}(N) \xrightarrow{\sim} \mathbb{F}(M \odot N)$$and for each object $a \in \mathbb{A}$ a natural isomorphism $$\mathbb{F}_a \colon \hat{U}_{\mathbb{F}(a)} \xrightarrow{\sim} \mathbb{F}(U_a).$$
 \end{defn}
 \begin{thm}[Shulman,7.8]\label{ShulDubEquiv}
-Given a strong double functor $\mathbb{F} \colon \mathbb{C} \to \mathbb{D}$, $\mathbb{F}$ is part of a double equivalence if and only if $\mathbb{F}$ is full, faithful and essentially surjective.
+Given a strong double functor $\mathbb{F} \colon \mathbb{A} \to \mathbb{X}$, $\mathbb{F}$ is part of a double equivalence if and only if $\mathbb{F}$ is full, faithful and essentially surjective.
 \end{thm}
 \begin{prop}
-Let $\mathbb{C}$ and $\mathbb{D}$ be symmetric monoidal double categories and let $\mathbb{F} \colon \mathbb{C} \to \mathbb{D}$ be a symmetric monoidal strong double functor.
-If $\mathbb{F}$ is part of a double equivalence, then $\mathbb{F}$ is in fact part of a symmetric monoidal double equivalence, and $\mathbb{C}$ and $\mathbb{D}$ are equivalent as symmetric monoidal double categories.
+Let $\mathbb{A}$ and $\mathbb{X}$ be symmetric monoidal double categories and let $\mathbb{F} \colon \mathbb{A} \to \mathbb{X}$ be a symmetric monoidal strong double functor.
+If $\mathbb{F}$ is part of a double equivalence, then $\mathbb{F}$ is in fact part of a symmetric monoidal double equivalence, and $\mathbb{A}$ and $\mathbb{X}$ are equivalent as symmetric monoidal double categories.
 \end{prop}
-Our next goal is to show that the symmetric monoidal double category $\mathbb{F}\textnormal{Cospan}(\bold{C})$ of Section \ref{DecCospansDoublecat} is equivalent as a symmetric monoidal double category to the symmetric monoidal double category $_L \mathbb{C}\textnormal{sp}(\bold{D})$ obtained using structured cospans.
+Our next goal is to show that the symmetric monoidal double category $\mathbb{F}\textnormal{Cospan}(\mathrm{A})$ of Section \ref{DecCospansDoublecat} is equivalent as a symmetric monoidal double category to the symmetric monoidal double category $_L \mathbb{C}\textnormal{sp}(\mathrm{X})$ obtained using structured cospans.
 
 \begin{thm}
-Given a category $\bold{D}$ with finite colimits and a category $\bold{C}$ with finite coproducts and a left adjoint $L \colon \bold{C} \to \bold{D}$ with $\bold{C}$ and $\bold{D}$ regarded as symmetric monoidal categories under binary coproducts, we can obtain a symmetric monoidal double category $_L \mathbb{C}\textnormal{sp}(\bold{D})$ which has:
+Given a category $\mathrm{X}$ with finite colimits and a category $\mathrm{A}$ with finite coproducts and a left adjoint $L \colon \mathrm{A} \to \mathrm{X}$ with $\mathrm{A}$ and $\mathrm{X}$ regarded as symmetric monoidal categories under binary coproducts, we can obtain a symmetric monoidal double category $_L \mathbb{C}\textnormal{sp}(\mathrm{X})$ which has:
 \begin{enumerate}
-\item{objects given by objects of $\bold{C}$,}
-\item{vertical 1-morphisms given by morphisms of $\bold{C}$,}
-\item{horizontal 1-cells given by cospans of $\bold{D}$ of the form:
+\item{objects given by objects of $\mathrm{A}$,}
+\item{vertical 1-morphisms given by morphisms of $\mathrm{A}$,}
+\item{horizontal 1-cells given by cospans of $\mathrm{X}$ of the form:
 \[
@@
 \node (A) at (0,0) {$L(c)$};
-\node (B) at (1,0) {$d$};
+\node (B) at (1,0) {$x$};
 \node (C) at (2,0) {$L(c^\prime)$};
@@
 and}
-\item{2-morphisms given by maps of cospans of $\bold{D}$ of the form:
+\item{2-morphisms given by maps of cospans of $\mathrm{X}$ of the form:
 \[
@@
 \node (A) at (0,0) {$L(c_1)$};
-\node (B) at (1,0) {$d$};
+\node (B) at (1,0) {$x$};
 \node (C) at (2,0) {$L(c_2)$};
 \node (A') at (0,-1) {$L(c_1^\prime)$};
-\node (B') at (1,-1) {$d^\prime$};
+\node (B') at (1,-1) {$x^\prime$};
 \node (C') at (2,-1) {$L(c_2^\prime)$};
@@
 (A) edge node [left]{$L(f)$} (A')
-(B) edge node [left]{$h$} (B')
+(B) edge node [left]{$\alpha$} (B')
 (C) edge node [left]{$L(g)$} (C');
@@
 \]
-Composition of horizontal 1-cells and 2-morphisms is given by pushouts in $\bold{D}$ and tensoring of objects is under binary coproducts in $\bold{C}$.
+Composition of horizontal 1-cells and 2-morphisms is given by pushouts in $\mathrm{X}$ and tensoring of objects is under binary coproducts in $\mathrm{A}$.
 }
@@
 \begin{proof}
-See \cite{BC2}.
+See the first two authors' work on structured cospans \cite{BC2}.
 \end{proof}
-In the previous section, we started with a symmetric lax monoidal pseudofunctor $F \colon \bold{C} \to \bold{Cat}$ and created a symmetric monoidal double category $\mathbb{F}\textnormal{Cospan}(\bold{C})$ which has:
+In the previous section, we started with a symmetric lax monoidal pseudofunctor $F \colon \mathrm{A} \to \bold{Cat}$ and created a symmetric monoidal double category $\mathbb{F}\textnormal{Cospan}(\mathrm{A})$ which has:
 \begin{enumerate}
-\item{objects of $\bold{C}$ as objects,}
-\item{morphisms of $\bold{C}$ as vertical 1-morphisms,}
+\item{objects of $\mathrm{A}$ as objects,}
+\item{morphisms of $\mathrm{A}$ as vertical 1-morphisms,}
 \item{horizontal 1-cells are given by $F$-decorated cospans, which are pairs:
@@
 \node (C) at (2,0) {$c_2$};
-\node (D) at (3,0) {$d \in F(c)$};
+\node (D) at (3,0) {$x \in F(c)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 and}
-\item{2-morphisms are given by maps of cospans in $\bold{C}$:
+\item{2-morphisms are given by maps of cospans in $\mathrm{A}$:
 \[
@@
 \node (C') at (2,-1) {$c_2^\prime$};
-\node (D) at (3,0) {$d \in F(c)$};
-\node (D') at (3,-1) {$d^\prime \in F(c^\prime)$};
+\node (D) at (3,0) {$x \in F(c)$};
+\node (D') at (3,-1) {$x^\prime \in F(c^\prime)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \begin{thm}\label{main2}
-Let $\bold{C}$ and $\bold{D}$ be categories with finite colimits and $F \colon \bold{C} \to \bold{Cat}$ a symmetric lax monoidal pseudofunctor.
-Let $L \colon \bold{C} \to \int{F} \cong \bold{D}$ be the left adjoint of the Grothendieck construction $R \colon \int{F} \to \bold{C}$ of $F$.
-Then the symmetric monoidal double category $_L \mathbb{C}\textnormal{sp}(\bold{D})$ utilizing structured cospans and the symmetric monoidal double category $\mathbb{F}\textnormal{Cospan}(\bold{C})$ utilizing decorated cospans are equivalent as symmetric monoidal double categories.
+Let $\mathrm{A}$ and $\mathrm{X}$ be categories with finite colimits and $F \colon \mathrm{A} \to \bold{Cat}$ a symmetric lax monoidal pseudofunctor.
+Let $L \colon \mathrm{A} \to \int{F} \cong \mathrm{X}$ be the left adjoint of the Grothendieck construction $R \colon \int{F} \to \mathrm{A}$ of $F$.
+Then the symmetric monoidal double category $_L \mathbb{C}\textnormal{sp}(\mathrm{X})$ utilizing structured cospans and the symmetric monoidal double category $\mathbb{F}\textnormal{Cospan}(\mathrm{A})$ utilizing decorated cospans are equivalent as symmetric monoidal double categories.
 \end{thm}
 \begin{proof}
-To prove this, we define a double functor $\mathbb{E} \colon _L \mathbb{C}\textnormal{sp}(\bold{D}) \to \mathbb{F}\textnormal{Cospan}(\bold{C})$ as follows: the object component of the double functor $\mathbb{E}$ is given by $\mathbb{E}_0 = \id_{\bold{C}}$ as both double categories $_L \mathbb{C}\textnormal{sp}(\bold{D})$ and $\mathbb{F}\textnormal{Cospan}(\bold{C})$ have objects and morphisms of $\bold{C}$ as objects and vertical 1-morphisms, respectively.
+To prove this, we define a double functor $\mathbb{E} \colon _L \mathbb{C}\textnormal{sp}(\mathrm{X}) \to \mathbb{F}\textnormal{Cospan}(\mathrm{A})$ as follows: the object component of the double functor $\mathbb{E}$ is given by $\mathbb{E}_0 = \id_{\mathrm{A}}$ as both double categories $_L \mathbb{C}\textnormal{sp}(\mathrm{X})$ and $\mathbb{F}\textnormal{Cospan}(\mathrm{A})$ have objects and morphisms of $\mathrm{A}$ as objects and vertical 1-morphisms, respectively.
 The functor $\mathbb{E}_0$ is trivially an equivalence of categories.
 
-Given a horizontal 1-cell of $_L \mathbb{C}\textnormal{sp}(\bold{D})$, which is a cospan in $\bold{D}$ of the form:
+Given a horizontal 1-cell of $_L \mathbb{C}\textnormal{sp}(\mathrm{X})$, which is a cospan in $\mathrm{X}$ of the form:
 \[
@@
 \node (A) at (0,0) {$c$};
-\node (B) at (1,0) {$R(d)$};
+\node (B) at (1,0) {$R(x)$};
 \node (C) at (2,0) {$c^\prime$};
-\node (D) at (3,0) {$d \in F(R(d))$};
+\node (D) at (3,0) {$x \in F(R(x))$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-where $R\colon \bold{D} \to \bold{C}$ is the right adjoint to the functor $L \colon \bold{C} \to \bold{D}$ and $\eta \colon 1_{\bold{C}} \to RL$ is the unit of the adjunction $L \dashv R$ which is an isomorphism since $L$ is fully faithful.
-\textbf{Hopefully...} Similarly, the image of a 2-morphism in $_L \mathbb{C}\textnormal{sp}(\bold{D})$:
+where $R\colon \mathrm{X} \to \mathrm{A}$ is the right adjoint to the functor $L \colon \mathrm{A} \to \mathrm{X}$ and $\eta \colon 1_{\mathrm{A}} \to RL$ is the unit of the adjunction $L \dashv R$ which is an isomorphism since $L$ is fully faithful.
+\textbf{Hopefully...actually, it's a `lari'!} Similarly, the image of a 2-morphism in $_L \mathbb{C}\textnormal{sp}(\mathrm{X})$:
 \[
@@
 \]
-is the 2-morphism in $\mathbb{F}\textnormal{Cospan}(\bold{C})$ given by:
+is the 2-morphism in $\mathbb{F}\textnormal{Cospan}(\mathrm{A})$ given by:
 \[
@@
 \node (A) at (0,0) {$c_1$};
-\node (B) at (1,0) {$R(d)$};
+\node (B) at (1,0) {$R(x)$};
 \node (C) at (2,0) {$c_2$};
 \node (A') at (0,-1) {$c_1^\prime$};
-\node (B') at (1,-1) {$R(d^\prime)$};
+\node (B') at (1,-1) {$R(x^\prime)$};
 \node (C') at (2,-1) {$c_2^\prime$};
-\node (D) at (3,0) {$d \in F(R(d))$};
-\node (D') at (3,-1) {$d^\prime \in F(R(d^\prime))$};
+\node (D) at (3,0) {$x \in F(R(x))$};
+\node (D') at (3,-1) {$x^\prime \in F(R(x^\prime))$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (A) edge node [left]{$f$} (A')
-(B) edge node [left]{$R(h)$} (B')
+(B) edge node [left]{$R(\alpha)$} (B')
 (C) edge node [left]{$g$} (C');
@@
 \]
-together with a morphism $\iota \colon F(R(h))(d) \to d^\prime$ in $F(R(d^\prime)) \subseteq \bold{D}$ which comes from the Grothendieck construction of the pseudofunctor $F \colon \bold{C} \to \bold{Cat}$.
-First, to see that this functor is essentially surjective, given a horizontal 1-cell in $\mathbb{F}\textnormal{Cospan}(\bold{C})$:
+together with a morphism $\iota \colon F(R(h))(x) \to x^\prime$ in $F(R(x^\prime)) \subseteq \mathrm{X}$ which comes from the Grothendieck construction of the pseudofunctor $F \colon \mathrm{A} \to \bold{Cat}$.
+First, to see that this functor is essentially surjective, given a horizontal 1-cell in $\mathbb{F}\textnormal{Cospan}(\mathrm{A})$:
 \[
@@
 \]
-we can find a 2-isomorphism in $\mathbb{F}\textnormal{Cospan}(\bold{C})$ whose codomain is the above horizontal 1-cell and whose domain is the image of the following horizontal 1-cell in $_L \mathbb{C}\textnormal{sp}(\bold{D})$:
+we can find a 2-isomorphism in $\mathbb{F}\textnormal{Cospan}(\mathrm{A})$ whose codomain is the above horizontal 1-cell and whose domain is the image of the following horizontal 1-cell in $_L \mathbb{C}\textnormal{sp}(\bold{D})$:
 \[
@@
 \node (A) at (0,0) {$L(c_1)$};
-\node (B) at (1,0) {$d$};
+\node (B) at (1,0) {$x$};
 \node (C) at (2,0) {$L(c_2)$};
@@
 \]
-with the 2-isomorphism in $\mathbb{F}\textnormal{Cospan}(\bold{C})$ given by:
+with the 2-isomorphism in $\mathbb{F}\textnormal{Cospan}(\mathrm{A})$ given by:
 \[
@@
 \node (A) at (0,0) {$c_1$};
-\node (B) at (1,0) {$R(d)$};
+\node (B) at (1,0) {$R(x)$};
 \node (C) at (2,0) {$c_2$};
@@
 \node (C') at (2,-1) {$c_2$};
-\node (D) at (3,0) {$d \in F(R(d))$};
-\node (D') at (3,-1) {$d \in F(c)$};
+\node (D) at (3,0) {$x \in F(R(x))$};
+\node (D') at (3,-1) {$x \in F(c)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-$$\iota \colon F({(R(e)\eta_c)}^{-1})(d) \to d$$
-where $e \colon L(c) \to d$ is given by the map from the trivial decoration on $c$ to $d \in F(c)$.
+$$\iota \colon F({(R(e)\eta_c)}^{-1})(x) \to x$$
+where $e \colon L(c) \to x$ is given by the map from the trivial decoration on $c$ to $x \in F(c)$.
 The object and arrow components $\mathbb{E}_0$ and $\mathbb{E}_1$ satisfy the equations $S \mathbb{E}_1 = \mathbb{E}_0 S$ and $T \mathbb{E}_1 = \mathbb{E}_0 T$.
 
-To show that the double functor $\mathbb{E}$ is fully faithful, we need to show that the map  $$\mathbb{E}_1 \colon _f { _L \mathbb{C}\textnormal{sp}(\bold{D})}_g(M,N) \to _{\mathbb{E}(f)} {\mathbb{F}\textnormal{Cospan}(\bold{C})}_{\mathbb{E}(g)}(\mathbb{E}(M),\mathbb{E}(N))$$ is bijective for arbitrary vertical 1-morphisms $f$ and $g$ and horizontal 1-cells $M$ and $N$ of $_L \mathbb{C}\textnormal{sp}(\bold{D})$.
-Consider a 2-morphism in $_L \mathbb{C}\textnormal{sp}(\bold{D})$:
+To show that the double functor $\mathbb{E}$ is fully faithful, we need to show that the map  $$\mathbb{E}_1 \colon _f { _L \mathbb{C}\textnormal{sp}(\mathrm{X})}_g(M,N) \to _{\mathbb{E}(f)} {\mathbb{F}\textnormal{Cospan}(\mathrm{A})}_{\mathbb{E}(g)}(\mathbb{E}(M),\mathbb{E}(N))$$ is bijective for arbitrary vertical 1-morphisms $f$ and $g$ and horizontal 1-cells $M$ and $N$ of $_L \mathbb{C}\textnormal{sp}(\bold{D})$.
+Consider a 2-morphism in $_L \mathbb{C}\textnormal{sp}(\mathrm{X})$:
 \[
@@
 \]
-The set $$_f { _L \mathbb{C}\textnormal{sp}(\bold{D})}_g(M,N)$$ consists of triples $$(f,\alpha,g)$$ where $f$ and $g$ are morphisms of $\bold{C}$ and $\alpha$ is a morphism of $\bold{D}$.
+The set $$_f { _L \mathbb{C}\textnormal{sp}(\mathrm{X})}_g(M,N)$$ consists of triples $$(f,\alpha,g)$$ where $f$ and $g$ are morphisms of $\mathrm{A}$ and $\alpha$ is a morphism of $\mathrm{X}$.
 The image of the above 2-morphism under the double functor $\mathbb{E}$ is given by:
@@
 \node (A) at (0,0) {$c_1$};
-\node (B) at (1,0) {$R(d)$};
+\node (B) at (1,0) {$R(x)$};
 \node (C) at (2,0) {$c_2$};
 \node (A') at (0,-1) {$c_1^\prime$};
-\node (B') at (1,-1) {$R(d^\prime)$};
+\node (B') at (1,-1) {$R(x^\prime)$};
 \node (C') at (2,-1) {$c_2^\prime$};
-\node (D) at (1,0.5) {$d \in F(R(d))$};
-\node (D') at (1,-1.5) {$d^\prime \in F(R(d^\prime))$};
+\node (D) at (1,0.5) {$x \in F(R(x))$};
+\node (D') at (1,-1.5) {$x^\prime \in F(R(x^\prime))$};
 \node (E) at (1,1) {$\mathbb{E}(M)$};
@@
 \]
-together with a morphism $\iota \colon F(R(\alpha))(d) \to d^\prime$ of $F(R(d^\prime))$.
-Thus the set $$_{\mathbb{E}(f)} {\mathbb{F}\textnormal{Cospan}(\bold{C})}_{\mathbb{E}(g)}(\mathbb{E}(M),\mathbb{E}(N))$$ consists of 4-tuples $$(f,R(\alpha),g,\iota).$$ The morphisms $R(\alpha) \colon R(d) \to R(d^\prime)$ and $\iota \colon F(R(\alpha))(d) \to d^\prime$ together carry all of the information of the morphism $\alpha \colon d \to d^\prime$ in $\bold{D}$ and conversely; given two objects $d=(c,d \in F(c))$ and $d^\prime=(c^\prime,d^\prime \in F(c^\prime))$ of $\bold{D}=\int{F}$, a morphism from $\alpha \colon d \to d^\prime$ is a pair $$(h \colon c \to c^\prime, \iota \colon F(h)(d) \to d^\prime)$$ where $h \colon c \to c^\prime$ is given by $R(\alpha) \colon R(d) \to R(d^\prime)$.
+together with a morphism $\iota \colon F(R(\alpha))(x) \to x^\prime$ of $F(R(x^\prime))$.
+Thus the set $$_{\mathbb{E}(f)} {\mathbb{F}\textnormal{Cospan}(\mathrm{A})}_{\mathbb{E}(g)}(\mathbb{E}(M),\mathbb{E}(N))$$ consists of 4-tuples $$(f,R(\alpha),g,\iota).$$ The morphisms $R(\alpha) \colon R(x) \to R(x^\prime)$ and $\iota \colon F(R(\alpha))(x) \to x^\prime$ together carry all of the information of the morphism $\alpha \colon x \to x^\prime$ in $\mathrm{X}$ and conversely; given two objects $x=(c,x \in F(c))$ and $x^\prime=(c^\prime,x^\prime \in F(c^\prime))$ of $\mathrm{X}=\int{F}$, a morphism from $\alpha \colon x \to x^\prime$ is a pair $$(h \colon c \to c^\prime, \iota \colon F(h)(x) \to x^\prime)$$ where $h \colon c \to c^\prime$ is given by $R(\alpha) \colon R(x) \to R(x^\prime)$.
 This shows that $\mathbb{E}$ is fully faithful.
@@
 
-Next we show that the double functor $\mathbb{E}$ is strong by exhibiting natural isomorphisms $$\mathbb{E}_{M,N} \colon \mathbb{E}(M) \odot \mathbb{E}(N) \xrightarrow{\sim} \mathbb{E}(M \odot N)$$ for every pair of composable horizontal 1-cells $M$ and $N$ of $_L \mathbb{C}\textnormal{sp}(\bold{D})$ and for each object $c \in { _L \mathbb{C}\textnormal{sp}(\bold{D})}$ a natural isomorphism $$\mathbb{E}_c \colon \hat{U}_{\mathbb{E}(c)} \xrightarrow{\sim} \mathbb{E}(U_c)$$ where $U$ and $\hat{U}$ are the unit structure functors of $_L \mathbb{C} \textnormal{sp}(\bold{D})$ and $\mathbb{F}\textnormal{Cospan}(\bold{C})$, respectively.
+Next we show that the double functor $\mathbb{E}$ is strong by exhibiting natural isomorphisms $$\mathbb{E}_{M,N} \colon \mathbb{E}(M) \odot \mathbb{E}(N) \xrightarrow{\sim} \mathbb{E}(M \odot N)$$ for every pair of composable horizontal 1-cells $M$ and $N$ of $_L \mathbb{C}\textnormal{sp}(\mathrm{X})$ and for each object $c \in { _L \mathbb{C}\textnormal{sp}(\mathrm{X})}$ a natural isomorphism $$\mathbb{E}_c \colon \hat{U}_{\mathbb{E}(c)} \xrightarrow{\sim} \mathbb{E}(U_c)$$ where $U$ and $\hat{U}$ are the unit structure functors of $_L \mathbb{C} \textnormal{sp}(\mathrm{X})$ and $\mathbb{F}\textnormal{Cospan}(\mathrm{A})$, respectively.
 For any object $c$, the horizontal 1-cell $\hat{U}_{\mathbb{E}(c)}$ is given by $\hat{U}_c$ which is given by the pair:
@@
 $$\iota \colon F(\eta_c)(!_c) \xrightarrow{!} L(c)$$
-of $\mathbb{F}\textnormal{Cospan}(\bold{C})$. Seems reasonable...
-
-Next, given composable horizontal 1-cells $M$ and $N$ in $_L \mathbb{C}\textnormal{sp}(\bold{D})$:
+of $\mathbb{F}\textnormal{Cospan}(\mathrm{A})$. Seems reasonable...
+
+Next, given composable horizontal 1-cells $M$ and $N$ in $_L \mathbb{C}\textnormal{sp}(\mathrm{X})$:
 \[
@@
 \node (A) at (0,0) {$L(c_1)$};
-\node (B) at (1,0) {$d$};
+\node (B) at (1,0) {$x$};
 \node (C) at (2,0) {$L(c_2)$};
 \node (D) at (3,0) {$L(c_2)$};
-\node (E) at (4,0) {$d^\prime$};
+\node (E) at (4,0) {$x^\prime$};
 \node (F) at (5,0) {$L(c_3)$};
@@
 \node (A) at (0,0) {$c_1$};
-\node (B) at (1,0) {$R(d)$};
+\node (B) at (1,0) {$R(x)$};
 \node (C) at (2,0) {$c_2$};
 \node (D) at (3,0) {$c_2$};
-\node (E) at (4,0) {$R(d^\prime)$};
+\node (E) at (4,0) {$R(x^\prime)$};
 \node (F) at (5,0) {$c_3$};
-\node (G) at (1,-0.5) {$d \in F(R(d))$};
-\node (H) at (4,-0.5) {$d^\prime \in F(R(d^\prime))$};
+\node (G) at (1,-0.5) {$x \in F(R(x))$};
+\node (H) at (4,-0.5) {$x^\prime \in F(R(x^\prime))$};
 %\node (D) at (3,0.5) {$!_c \in F(c)$};
@@
 \node (A) at (0,0) {$c_1$};
-\node (B) at (1.5,0) {$R(d)+_{c_2}R(d^\prime)$};
+\node (B) at (1.5,0) {$R(x)+_{c_2}R(x^\prime)$};
 \node (C) at (3,0) {$c_3$};
-\node (G) at (1.5,-0.5) {$\hat{d} \in F(R(d)+_{c_2}R(d^\prime))$};
+\node (G) at (1.5,-0.5) {$\hat{x} \in F(R(x)+_{c_2}R(x^\prime))$};
 %\node (D) at (3,0.5) {$!_c \in F(c)$};
@@
 \]
-$$\hat{d} \colon 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{d \times d^\prime} F(R(d)) \times F(R(d^\prime)) \xrightarrow{\phi_{R(d),R(d^\prime)}} F(R(d)+R(d^\prime)) \xrightarrow{F(j_{R(d),R(d^\prime)})} F(R(d)+_{c_2}R(d^\prime))$$where $\psi$ denotes each natural map into the coproduct and $j$ denotes the natural map from the coproduct to the pushout.
+$$\hat{x} \colon 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{x \times x^\prime} F(R(x)) \times F(R(x^\prime)) \xrightarrow{\phi_{R(x),R(x^\prime)}} F(R(x)+R(x^\prime)) \xrightarrow{F(j_{R(x),R(x^\prime)})} F(R(x)+_{c_2}R(x^\prime))$$where $\psi$ denotes each natural map into the coproduct and $j$ denotes the natural map from the coproduct to the pushout.
 On the other hand, $M \odot N$ is given by
@@
 \node (A) at (0,0) {$L(c_1)$};
-\node (B) at (1.25,0) {$d+_{L(c_2)}d^\prime$};
+\node (B) at (1.25,0) {$x+_{L(c_2)}x^\prime$};
 \node (C) at (2.5,0) {$L(c_3)$};
@@
 \node (A) at (0,0) {$c_1$};
-\node (B) at (1.5,0) {$R(d+_{L(c_2)}d^\prime)$};
+\node (B) at (1.5,0) {$R(x+_{L(c_2)}x^\prime)$};
 \node (C) at (3,0) {$c_3$};
-\node (G) at (1.5,-0.5) {$d+_{L(c_2)} d^\prime \in F(R(d+_{L(c_2)}d^\prime))$};
+\node (G) at (1.5,-0.5) {$x+_{L(c_2)} x^\prime \in F(R(x+_{L(c_2)}x^\prime))$};
 %\node (D) at (3,0.5) {$!_c \in F(c)$};
@@
 \node (A) at (0,0) {$c_1$};
-\node (B) at (1.5,0) {$R(d)+_{c_2}R(d^\prime)$};
+\node (B) at (1.5,0) {$R(x)+_{c_2}R(x^\prime)$};
 \node (C) at (3,0) {$c_3$};
 \node (A') at (0,-1) {$c_1$};
-\node (B') at (1.5,-1) {$R(d+_{L(c_2)}d^\prime)$};
+\node (B') at (1.5,-1) {$R(x+_{L(c_2)}x^\prime)$};
 \node (C') at (3,-1) {$c_3$};
-\node (D) at (5.5 ,0) {$\hat{d} \in F(R(d)+_{c_2}R(d^\prime))$};
-\node (D') at (5.5,-1) {$d+_{L(c_2)}d^\prime \in F(R(d+_{L(c_2)}d^\prime))$};
+\node (D) at (5.5 ,0) {$\hat{x} \in F(R(x)+_{c_2}R(x^\prime))$};
+\node (D') at (5.5,-1) {$x+_{L(c_2)}x^\prime \in F(R(x+_{L(c_2)}x^\prime))$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-First, if the right adjoint $R \colon \bold{D} \to \bold{C}$ is also a left adjoint, then $R$ also preserves all colimits and we have an isomorphism $$\kappa \colon R(d) +_{R(L(c_2))} R(d^\prime) \to R(d+_{L(c_2)}d^\prime).$$ Also, since the left adjoint $L \colon \bold{C} \to \bold{D}$ is fully faithful, the unit of the adjunction $L \dashv R$ at the object $c_2$ gives an isomorphism $\eta_{c_2} \colon c_2 \to R(L(c_2))$ which results in an isomorphism $$j_{\eta_{c_2}} \colon R(d) +_{c_2} R(d^\prime) \to R(d) +_{R(L(c_2))} R(d^\prime).$$ Composing these two results in an isomorphism $$\sigma \coloneqq \kappa j_{\eta_{c_2}} \colon R(d) +_{c_2} R(d^\prime) \to R(d+_{L(c_2)}d^\prime).$$
-Next, to see that the above diagram commutes, it suffices to show that for the object $c_1 \in \bold{C}$, $$R(J \zeta i)\eta_{c_1}(c_1) = R(J)R(\zeta)R(i)\eta_{c_1}(c_1) \stackrel{!}{=} \sigma j \psi R(i)\eta_{c_1}(c_1).$$ This follows as $R(i) \eta_{c_1} \colon c_1 \to R(d)$ and the following diagram commutes:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (B) at (0,0) {$R(d)$};
-\node (C) at (2,0) {$R(d)+R(d^\prime)$};
-\node (A') at (4,0) {$R(d)+_{c_2}R(d^\prime)$};
-\node (B') at (4,-2) {$R(d+_{L(c_2)}d^\prime)$};
-\node (D) at (0,-2) {$R(d+d^\prime)$};
-\node (D') at (4,-1) {$R(d)+_{R(L(c_2))} R(d^\prime)$};
+First, if the right adjoint $R \colon \mathrm{X} \to \mathrm{A}$ is also a left adjoint, then $R$ also preserves all colimits and we have an isomorphism $$\kappa \colon R(x) +_{R(L(c_2))} R(x^\prime) \to R(x+_{L(c_2)}x^\prime).$$ Also, since the left adjoint $L \colon \mathrm{A} \to \mathrm{X}$ is fully faithful, the unit of the adjunction $L \dashv R$ at the object $c_2$ gives an isomorphism $\eta_{c_2} \colon c_2 \to R(L(c_2))$ which results in an isomorphism $$j_{\eta_{c_2}} \colon R(x) +_{c_2} R(x^\prime) \to R(x) +_{R(L(c_2))} R(x^\prime).$$ Composing these two results in an isomorphism $$\sigma \coloneqq \kappa j_{\eta_{c_2}} \colon R(x) +_{c_2} R(x^\prime) \to R(x+_{L(c_2)}x^\prime).$$
+Next, to see that the above diagram commutes, it suffices to show that for the object $c_1 \in \mathrm{A}$, $$R(J \zeta i)\eta_{c_1}(c_1) = R(J)R(\zeta)R(i)\eta_{c_1}(c_1) \stackrel{!}{=} \sigma j \psi R(i)\eta_{c_1}(c_1).$$ This follows as $R(i) \eta_{c_1} \colon c_1 \to R(x)$ and the following diagram commutes:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (B) at (0,0) {$R(x)$};
+\node (C) at (2,0) {$R(x)+R(x^\prime)$};
+\node (A') at (4,0) {$R(x)+_{c_2}R(x^\prime)$};
+\node (B') at (4,-2) {$R(x+_{L(c_2)}x^\prime)$};
+\node (D) at (0,-2) {$R(x+x^\prime)$};
+\node (D') at (4,-1) {$R(x)+_{R(L(c_2))} R(x^\prime)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-Lastly, this map of cospans comes with an isomorphism $\iota \colon F(\sigma)(\hat{d}) \to (d+_{L(c_2)}d^\prime)$ in $F(R(d+_{L(c_2)}d^\prime))$.
-This shows that $\mathbb{E}$ is strong, and so $\mathbb{E} \colon _L \mathbb{C}\textnormal{sp}(\bold{D}) \xrightarrow{\sim} \mathbb{F}\textnormal{Cospan}(\bold{C})$ is part of a double equivalence by Theorem \ref{ShulDubEquiv}.
-
-Next, if both double categories $_L \mathbb{C}\textnormal{sp}(\bold{D})$ and $\mathbb{F}\textnormal{Cospan}(\bold{C})$ are symmetric monoidal, as they are if both $\bold{C}$ and $\bold{D}$ have finite colimits, then this equivalence of double categories $\mathbb{E} \colon _L \mathbb{C}\textnormal{sp}(\bold{D}) \to \mathbb{F} \textnormal{Cospan}(\bold{C})$ will be symmetric monoidal.
-First note that we have an isomorphism $\epsilon \colon 1_{\mathbb{F}\textnormal{Cospan}(\bold{C})} \to \mathbb{E}(1_{_L \mathbb{C}\textnormal{sp}(\bold{D})})$ and natural isomorphisms $\mu_{c_1,c_2} \colon \mathbb{E}(c_1) \otimes \mathbb{E}(c_2) \to \mathbb{E}(c_1 \otimes c_2)$ for every pair of objects $c_1,c_2 \in {_L \mathbb{C} \textnormal{sp}(\bold{D})}$ both of which are given by identities since both double categories $_L \mathbb{C}\textnormal{sp}(\bold{D})$ and $\mathbb{F}\textnormal{Cospan}(\bold{C})$ have $\bold{C}$ as their category of objects and $\mathbb{E}_0=\id_{\bold{C}}$.
+Lastly, this map of cospans comes with an isomorphism $\iota \colon F(\sigma)(\hat{x}) \to (x+_{L(c_2)}x^\prime)$ in $F(R(x+_{L(c_2)}x^\prime))$.
+This shows that $\mathbb{E}$ is strong, and so $\mathbb{E} \colon _L \mathbb{C}\textnormal{sp}(\mathrm{X}) \xrightarrow{\sim} \mathbb{F}\textnormal{Cospan}(\mathrm{A})$ is part of a double equivalence by Theorem \ref{ShulDubEquiv}.
+
+Next, if both double categories $_L \mathbb{C}\textnormal{sp}(\mathrm{X})$ and $\mathbb{F}\textnormal{Cospan}(\mathrm{A})$ are symmetric monoidal, as they are if both $\mathrm{A}$ and $\mathrm{X}$ have finite colimits, then this equivalence of double categories $\mathbb{E} \colon _L \mathbb{C}\textnormal{sp}(\mathrm{X}) \to \mathbb{F} \textnormal{Cospan}(\mathrm{A})$ will be symmetric monoidal.
+First note that we have an isomorphism $\epsilon \colon 1_{\mathbb{F}\textnormal{Cospan}(\mathrm{A})} \to \mathbb{E}(1_{_L \mathbb{C}\textnormal{sp}(\mathrm{X})})$ and natural isomorphisms $\mu_{c_1,c_2} \colon \mathbb{E}(c_1) \otimes \mathbb{E}(c_2) \to \mathbb{E}(c_1 \otimes c_2)$ for every pair of objects $c_1,c_2 \in {_L \mathbb{C} \textnormal{sp}(\mathrm{X})}$ both of which are given by identities since both double categories $_L \mathbb{C}\textnormal{sp}(\mathrm{X})$ and $\mathbb{F}\textnormal{Cospan}(\mathrm{A})$ have $\mathrm{A}$ as their category of objects and $\mathbb{E}_0=\id_{\mathrm{A}}$.
 The diagrams containing these morphisms that are required to commute do so trivially.
 
-For the arrow component $\mathbb{E}_1$, we have an isomorphism $\delta \colon U_{1_{\mathbb{F}\textnormal{Cospan}(\bold{C})}} \to \mathbb{E}(U_{1_{_L \mathbb{C}\textnormal{sp}(\bold{D})}})$ where the horizontal 1-cell $U_{1_{\mathbb{F}\textnormal{Cospan}(\bold{C})}}$ is given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$1_\bold{C}$};
-\node (B) at (1,0) {$1_\bold{C}$};
-\node (C) at (2,0) {$1_\bold{C}$};
-\node (D) at (3,0) {$!_{1_{\bold{C}}} \in F(1_\bold{C})$};
+For the arrow component $\mathbb{E}_1$, we have an isomorphism $\delta \colon U_{1_{\mathbb{F}\textnormal{Cospan}(\mathrm{A})}} \to \mathbb{E}(U_{1_{_L \mathbb{C}\textnormal{sp}(\mathrm{X})}})$ where the horizontal 1-cell $U_{1_{\mathbb{F}\textnormal{Cospan}(\mathrm{A})}}$ is given by:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$1_\mathrm{A}$};
+\node (B) at (1,0) {$1_\mathrm{A}$};
+\node (C) at (2,0) {$1_\mathrm{A}$};
+\node (D) at (3,0) {$!_{1_{\mathrm{A}}} \in F(1_\mathrm{A})$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-where $!_{1_{\bold{C}}} = \phi \colon \bold{1} \to F(1_\bold{C})$ is the trivial decoration which comes from the structure of the symmetric lax monoidal pseudofunctor $F \colon \bold{C} \to \bold{Cat}$.
-The horizontal 1-cell $U_{1_{_L \mathbb{C}\textnormal{sp}(\bold{D})}}$ is given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$L(1_\bold{C})$};
-\node (B) at (1,0) {$L(1_\bold{C})$};
-\node (C) at (2,0) {$L(1_\bold{C})$};
-%\node (D) at (3,0.5) {$I \in F(1_\bold{C})$};
+where $!_{1_{\mathrm{A}}} = \phi \colon 1 \to F(1_\mathrm{A})$ is the trivial decoration which comes from the structure of the symmetric lax monoidal pseudofunctor $F \colon \mathrm{A} \to \bold{Cat}$.
+The horizontal 1-cell $U_{1_{_L \mathbb{C}\textnormal{sp}(\mathrm{X})}}$ is given by:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$L(1_\mathrm{A})$};
+\node (B) at (1,0) {$L(1_\mathrm{A})$};
+\node (C) at (2,0) {$L(1_\mathrm{A})$};
+%\node (D) at (3,0.5) {$I \in F(1_\mathrm{A})$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-where here we make use of the fact that the left adjoint $L \colon (\bold{C},+,1_\bold{C}) \to (\bold{D},+,1_\bold{D})$ preserves all colimits and thus $L(1_\bold{C}) \cong 1_\bold{D}$.
-The horizontal 1-cell $\mathbb{E}(U_{1_{_L \mathbb{C} \textnormal{sp}(\bold{D})}})$ is given by the pair:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$1_\bold{C}$};
-\node (B) at (1.25,0) {$R(L(1_\bold{C}))$};
-\node (C) at (2.5,0) {$1_\bold{C}$};
-\node (D) at (4,0) {$!_{1_\bold{C}} \in F(R(L(1_\bold{C}))) \cong F(1_\bold{C})$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{${\eta_{1_\bold{C}}}$} (B)
-(C) edge node[above]{${\eta_{1_\bold{C}}}$} (B);
+where here we make use of the fact that the left adjoint $L \colon (\mathrm{A},+,1_\mathrm{A}) \to (\mathrm{X},+,1_\mathrm{X})$ preserves all colimits and thus $L(1_\mathrm{A}) \cong 1_\mathrm{X}$.
+The horizontal 1-cell $\mathbb{E}(U_{1_{_L \mathbb{C} \textnormal{sp}(\mathrm{X})}})$ is given by the pair:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$1_\mathrm{A}$};
+\node (B) at (1.25,0) {$R(L(1_\mathrm{A}))$};
+\node (C) at (2.5,0) {$1_\mathrm{A}$};
+\node (D) at (4,0) {$!_{1_\mathrm{A}} \in F(R(L(1_\mathrm{A}))) \cong F(1_\mathrm{A})$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{${\eta_{1_\mathrm{A}}}$} (B)
+(C) edge node[above]{${\eta_{1_\mathrm{A}}}$} (B);
 \end{tikzpicture}
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$1_\bold{C}$};
-\node (B) at (1,0) {$1_{\bold{C}}$};
-\node (C) at (2,0) {$1_\bold{C}$};
-\node (A') at (0,-1) {$1_\bold{C}$};
-\node (B') at (1,-1) {$R(L(1_\bold{C}))$};
-\node (C') at (2,-1) {$1_\bold{C}$};
-\node (D) at (3,0) {$!_{1_\bold{C}} \in F(1_\bold{C})$};
-\node (D') at (3.75,-1) {$!_{1_\bold{C}} \in F(R(L(1_\bold{C}))) \cong F(1_\bold{C})$};
+\node (A) at (0,0) {$1_\mathrm{A}$};
+\node (B) at (1,0) {$1_{\mathrm{A}}$};
+\node (C) at (2,0) {$1_\mathrm{A}$};
+\node (A') at (0,-1) {$1_\mathrm{A}$};
+\node (B') at (1,-1) {$R(L(1_\mathrm{A}))$};
+\node (C') at (2,-1) {$1_\mathrm{A}$};
+\node (D) at (3,0) {$!_{1_\mathrm{A}} \in F(1_\mathrm{A})$};
+\node (D') at (3.75,-1) {$!_{1_\mathrm{A}} \in F(R(L(1_\mathrm{A}))) \cong F(1_\mathrm{A})$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (C) edge node[above]{$1$} (B)
-(A') edge node[above]{${\eta_{1_\bold{C}}}$} (B')
-(C') edge node[above]{${\eta_{1_\bold{C}}}$} (B')
+(A') edge node[above]{${\eta_{1_\mathrm{A}}}$} (B')
+(C') edge node[above]{${\eta_{1_\mathrm{A}}}$} (B')
 (A) edge node [left]{$1$} (A')
-(B) edge node [left]{${\eta_{1_\bold{C}}}$} (B')
+(B) edge node [left]{${\eta_{1_\mathrm{A}}}$} (B')
 (C) edge node [left]{$1$} (C');
@@
 \]
-$$\iota_{{\eta_{1_\bold{C}}}} \colon F({\eta_{1_\bold{C}}}(!_{1_\bold{C}})) \to !_{1_\bold{C}}$$
-of $\mathbb{F}\textnormal{Cospan}(\bold{C})$.
-
-Given two horizontal 1-cells $M$ and $N$ of $_L \mathbb{C}\textnormal{sp}(\bold{D})$:
+$$\iota_{{\eta_{1_\mathrm{A}}}} \colon F({\eta_{1_\mathrm{A}}}(!_{1_\mathrm{A}})) \to !_{1_\mathrm{A}}$$
+of $\mathbb{F}\textnormal{Cospan}(\mathrm{A})$.
+
+Given two horizontal 1-cells $M$ and $N$ of $_L \mathbb{C}\textnormal{sp}(\mathrm{X})$:
 \[
@@
 \node (A) at (0,0) {$L(c_1)$};
-\node (B) at (1,0) {$d$};
+\node (B) at (1,0) {$x$};
 \node (C) at (2,0) {$L(c_2)$};
 \node (D) at (3,0) {$L(c_1^\prime)$};
-\node (E) at (4,0) {$d^\prime$};
+\node (E) at (4,0) {$x^\prime$};
 \node (F) at (5,0) {$L(c_2^\prime)$};
@@
 \node (A) at (0,0) {$c_1$};
-\node (B) at (1,0) {$R(d)$};
+\node (B) at (1,0) {$R(x)$};
 \node (C) at (2,0) {$c_2$};
 \node (D) at (3,0) {$c_1^\prime$};
-\node (E) at (4,0) {$R(d^\prime)$};
+\node (E) at (4,0) {$R(x^\prime)$};
 \node (F) at (5,0) {$c_2^\prime$};
-\node (G) at (1,-0.5) {$d \in F(R(d))$};
-\node (H) at (4,-0.5) {$d^\prime \in F(R(d^\prime))$};
+\node (G) at (1,-0.5) {$x \in F(R(x))$};
+\node (H) at (4,-0.5) {$x^\prime \in F(R(x^\prime))$};
 %\node (D) at (3,0.5) {$!_c \in F(c)$};
@@
 \node (A) at (0,0) {$c_1+c_1^\prime$};
-\node (B) at (2.25,0) {$R(d)+R(d^\prime)$};
+\node (B) at (2.25,0) {$R(x)+R(x^\prime)$};
 \node (C) at (4.5,0) {$c_2+c_2^\prime$};
-\node (D) at (2.25,-0.5) {$\hat{d} \in F(R(d)+R(d^\prime)$}; 
+\node (D) at (2.25,-0.5) {$\hat{x} \in F(R(x)+R(x^\prime))$}; 
 %\node (D) at (3,0.5) {$!_c \in F(c)$};
@@
 \]
-where $$\hat{d} \colon 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{d \times d^\prime} F(R(d)) \times F(R(d^\prime)) \xrightarrow{\phi_{R(d),R(d^\prime)}} F(R(d)+R(d^\prime)).$$ On the other hand, $M \otimes N$ is given by
+where $$\hat{x} \colon 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{x \times x^\prime} F(R(x)) \times F(R(x^\prime)) \xrightarrow{\phi_{R(x),R(x^\prime)}} F(R(x)+R(x^\prime)).$$ On the other hand, $M \otimes N$ is given by
 \[
@@
 \node (A) at (0,0) {$L(c_1+c_1^\prime)$};
-\node (B) at (1.5,0) {$d+d^\prime$};
+\node (B) at (1.5,0) {$x+x^\prime$};
 \node (C) at (3,0) {$L(c_2+c_2^\prime)$};
@@
 \node (A) at (0,0) {$c_1+c_1^\prime$};
-\node (B) at (2,0) {$R(d+d^\prime)$};
+\node (B) at (2,0) {$R(x+x^\prime)$};
 \node (C) at (4,0) {$c_2+c_2^\prime$};
-\node (D) at (2,-0.5) {$d+d^\prime \in F(R(d+d^\prime))$};
+\node (D) at (2,-0.5) {$x+x^\prime \in F(R(x+x^\prime))$};
 %\node (D) at (3,0.5) {$!_c \in F(c)$};
@@
 \]
-We then have a 2-isomorphism $\mu_{M,N} \colon E(M) \otimes E(N) \xrightarrow{\sim} E(M \otimes N)$ in $\mathbb{F}\textnormal{Cospan}(\bold{C})$ given by:
+We then have a 2-isomorphism $\mu_{M,N} \colon E(M) \otimes E(N) \xrightarrow{\sim} E(M \otimes N)$ in $\mathbb{F}\textnormal{Cospan}(\mathrm{A})$ given by:
 \[
@@
 \node (A) at (0,0) {$c_1+c_1^\prime$};
-\node (B) at (2,0) {$R(d)+R(d^\prime)$};
+\node (B) at (2,0) {$R(x)+R(x^\prime)$};
 \node (C) at (4,0) {$c_2+c_2^\prime$};
 \node (A') at (0,-1) {$c_1+c_1^\prime$};
-\node (B') at (2,-1) {$R(d+d^\prime)$};
+\node (B') at (2,-1) {$R(x+x^\prime)$};
 \node (C') at (4,-1) {$c_2+c_2^\prime$};
-\node (D) at (5.75,0) {$\hat{d} \in F(R(d)+R(d^\prime))$};
-\node (D') at (5.75,-1) {$d+d^\prime \in F(R(d+d^\prime))$};
-\node (E) at (2,-1.5) {$\iota_\mu \colon F(\kappa)(\hat{d}) \to d+d^\prime$};
+\node (D) at (5.75,0) {$\hat{x} \in F(R(x)+R(x^\prime))$};
+\node (D') at (5.75,-1) {$x+x^\prime \in F(R(x+x^\prime))$};
+\node (E) at (2,-1.5) {$\iota_\mu \colon F(\kappa)(\hat{x}) \to x+x^\prime$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 The isomorphisms $\delta$ and $\mu$ satisfy the left and right unitality squares, associativity hexagon and braiding square.
-Let $M_1,M_2$ and $M_3$ be horizontal 1-cells in $_L \mathbb{C}\textnormal{sp}(\bold{D})$ given by:
+Let $M_1,M_2$ and $M_3$ be horizontal 1-cells in $_L \mathbb{C}\textnormal{sp}(\mathrm{X})$ given by:
 \[
@@
 \node (A) at (0,0) {$L(c_1)$};
-\node (B) at (1,0) {$d_1$};
+\node (B) at (1,0) {$x_1$};
 \node (C) at (2,0) {$L(c_1^\prime)$};
 \node (D) at (3,0) {$L(c_2)$};
-\node (E) at (4,0) {$d_2$};
+\node (E) at (4,0) {$x_2$};
 \node (F) at (5,0) {$L(c_2^\prime)$};
 \node (G) at (6,0) {$L(c_3)$};
-\node (H) at (7,0) {$d_3$};
+\node (H) at (7,0) {$x_3$};
 \node (I) at (8,0) {$L(c_3^\prime)$};
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$1_{\mathbb{F}\textnormal{Cospan}(\bold{C})} \otimes \mathbb{E}(M_1)$};
-\node (B) at (3,0) {$\mathbb{E}(1_{ _L \mathbb{C}\textnormal{sp}(\bold{D})}) \otimes \mathbb{E}(M_1)$};
+\node (A) at (0,0) {$1_{\mathbb{F}\textnormal{Cospan}(\mathrm{A})} \otimes \mathbb{E}(M_1)$};
+\node (B) at (3,0) {$\mathbb{E}(1_{ _L \mathbb{C}\textnormal{sp}(\mathrm{X})}) \otimes \mathbb{E}(M_1)$};
 \node (C) at (0,-1) {$\mathbb{E}(M_1)$};
-\node (D) at (3,-1) {$\mathbb{E}(1_{ _L \mathbb{C}\textnormal{sp}(\bold{D})} \otimes M_1)$};
+\node (D) at (3,-1) {$\mathbb{E}(1_{ _L \mathbb{C}\textnormal{sp}(\mathrm{X})} \otimes M_1)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 		\begin{tikzpicture}
-			\node (d) at (7.5,0) {$\mathbb{E}(1_{ _L \mathbb{C}\textnormal{sp}(\bold{D})}) \otimes \mathbb{E}(M_1)$};
-			\node (a) at (-4,0) {$1_\bold{C}+c_1$};
-			\node (b) at (0.5,0) {$R(L(1_\bold{C})) + R(d_1)$};
-			\node (c) at (5,0) {$1_\bold{C}+c_1^\prime$};
-			\node (d2) at (7.5,1) {$1_{\mathbb{F}\textnormal{Cospan}(\bold{C})} \otimes \mathbb{E}(M_1)$};
-			\node (a2) at (-4,1) {$1_\bold{C}+c_1$};
-			\node (b2) at (0.5,1) {$1_\bold{C}+R(d_1)$};
-			\node (c2) at (5,1) {$1_\bold{C}+c_1^\prime$};
+			\node (d) at (7.5,0) {$\mathbb{E}(1_{ _L \mathbb{C}\textnormal{sp}(\mathrm{X})}) \otimes \mathbb{E}(M_1)$};
+			\node (a) at (-4,0) {$1_\mathrm{A}+c_1$};
+			\node (b) at (0.5,0) {$R(L(1_\mathrm{A})) + R(x_1)$};
+			\node (c) at (5,0) {$1_\mathrm{A}+c_1^\prime$};
+			\node (d2) at (7.5,1) {$1_{\mathbb{F}\textnormal{Cospan}(\mathrm{A})} \otimes \mathbb{E}(M_1)$};
+			\node (a2) at (-4,1) {$1_\mathrm{A}+c_1$};
+			\node (b2) at (0.5,1) {$1_\mathrm{A}+R(x_1)$};
+			\node (c2) at (5,1) {$1_\mathrm{A}+c_1^\prime$};
 			\node (d3) at (7.5,2) {$\mathbb{E}(M_1)$};
                                 \node (a3) at (-4,2) {$c_1$};
-			\node (b3) at (0.5,2) {$R(d_1)$};
+			\node (b3) at (0.5,2) {$R(x_1)$};
 			\node (c3) at (5,2) {$c_1^\prime$};
-			\node (d4) at (7.5,-1) {$\mathbb{E}(1_{ _L \mathbb{C}\textnormal{sp}(\bold{D})} \otimes M_1)$};
-                                \node (a5) at (-4,-1) {$1_\bold{C}+c_1^\prime$};
-			\node (b5) at (0.5,-1) {$R(L(1_\bold{C})+d_1)$};
-			\node (c5) at (5,-1) {$1_\bold{C}+c_1^\prime$};
+			\node (d4) at (7.5,-1) {$\mathbb{E}(1_{ _L \mathbb{C}\textnormal{sp}(\mathrm{X})} \otimes M_1)$};
+                                \node (a5) at (-4,-1) {$1_\mathrm{A}+c_1^\prime$};
+			\node (b5) at (0.5,-1) {$R(L(1_\mathrm{A})+x_1)$};
+			\node (c5) at (5,-1) {$1_\mathrm{A}+c_1^\prime$};
 			\node (d5) at (7.5,-2) {$\mathbb{E}(M_1)$};
                                 \node (a6) at (-4,-2) {$c_1$};
-			\node (b6) at (0.5,-2) {$R(d_1)$};
+			\node (b6) at (0.5,-2) {$R(x_1)$};
 			\node (c6) at (5,-2) {$c_1^\prime$};
@@
 			(d4) edge node [left] {$\mathbb{E}(\lambda)$} (d5)
-			(a) edge node[above]{$\eta_{1_\bold{C}}+R(i_1)\eta_{c_1}$} (b)
-			(c) edge node[above]{$\eta_{1_\bold{C}}+R(o_1)\eta_{c_1^\prime}$} (b)
+			(a) edge node[above]{$\eta_{1_\mathrm{A}}+R(i_1)\eta_{c_1}$} (b)
+			(c) edge node[above]{$\eta_{1_\mathrm{A}}+R(o_1)\eta_{c_1^\prime}$} (b)
                                 (a2) edge node[above]{$1+R(i_1)\eta_{c_1}$} (b2)
@@
                                 (a2) edge node[left]{$1$} (a)
-                                (b2) edge node[left]{$\eta_{1_\bold{C}}+1$} (b)
+                                (b2) edge node[left]{$\eta_{1_\mathrm{A}}+1$} (b)
 (b2) edge node[right]{$\iota_2$} (b)
@@
 			(c3) edge node[above]{$R(o_1)\eta_{c_1^\prime}$} (b3)
-                                (a2) edge node[left]{$\lambda_{\bold{C}}$} (a3)
-                                (b2) edge node[left]{$\lambda_{\bold{C}}$} (b3)
+                                (a2) edge node[left]{$\lambda_{\mathrm{A}}$} (a3)
+                                (b2) edge node[left]{$\lambda_{\mathrm{A}}$} (b3)
 (b2) edge node[right]{$\iota_1$} (b3)
-			(c2) edge node[left]{$\lambda_{\bold{C}}$} (c3)
-                                (a5) edge node[above]{$(\mu_{L(1_\bold{C}),d_1})(\eta_{1_\bold{C}}+R(i_1)\eta_{c_1})$} (b5)
-			(c5) edge node[above]{$(\mu_{L(1_\bold{C}),d_1})(\eta_{1_\bold{C}}+R(o_1)\eta_{c_1^\prime})$} (b5)
+			(c2) edge node[left]{$\lambda_{\mathrm{A}}$} (c3)
+                                (a5) edge node[above]{$(\mu_{L(1_\mathrm{A}),d_1})(\eta_{1_\mathrm{A}}+R(i_1)\eta_{c_1})$} (b5)
+			(c5) edge node[above]{$(\mu_{L(1_\mathrm{A}),d_1})(\eta_{1_\mathrm{A}}+R(o_1)\eta_{c_1^\prime})$} (b5)
                                 (a) edge node[left]{$1$} (a5)
-                                (b) edge node[left]{$\mu_{L(1_\bold{C}),d_1}$} (b5)
+                                (b) edge node[left]{$\mu_{L(1_\mathrm{A}),d_1}$} (b5)
 (b) edge node[right]{$\iota_3$} (b5)
@@
 			(c6) edge node[above]{$R(o_1)\eta_{c_1^\prime}$} (b6)
-                                (a5) edge node[left]{$\lambda_{\bold{C}}$} (a6)
-                                (b5) edge node[left]{$R(\lambda_{\bold{D}})$} (b6)
+                                (a5) edge node[left]{$\lambda_{\mathrm{A}}$} (a6)
+                                (b5) edge node[left]{$R(\lambda_{\mathrm{X}})$} (b6)
  (b5) edge node[right]{$\iota_4$} (b6)
-			(c5) edge node[left]{$\lambda_{\bold{C}}$} (c6);
-		\end{tikzpicture}
-	\]
-with the corresponding maps of decorations amounting to the following commutative diagram in $F(R(d_1))$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (-.5,0) {$F(\lambda_{\bold{C}})(!_{1_\bold{C}}+d_1)$};
-\node (C) at (4,0) {$F(R(\lambda_{\bold{D}})(\mu_{L(1_\bold{C}),d_1}))(!_{R(L(1_\bold{C}))} +d_1$)};
-\node (D) at (-.5,-1) {$d_1$};
-\node (E) at (4,-1) {$F(R(\lambda_\bold{D}))(d_{!+1})$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$F(R(\lambda_{\bold{D}})(\mu_{L(1_\bold{C}),d_1}))(\iota_2)$} (C)
+			(c5) edge node[left]{$\lambda_{\mathrm{A}}$} (c6);
+		\end{tikzpicture}
+	\]
+with the corresponding maps of decorations amounting to the following commutative diagram in $F(R(x_1))$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (-.5,0) {$F(\lambda_{\mathrm{A}})(!_{1_\mathrm{A}}+x_1)$};
+\node (C) at (4,0) {$F(R(\lambda_{\mathrm{X}})(\mu_{L(1_\mathrm{A}),x_1}))(!_{R(L(1_\mathrm{A}))} +x_1$)};
+\node (D) at (-.5,-1) {$x_1$};
+\node (E) at (4,-1) {$F(R(\lambda_\mathrm{X}))(x_{!+1})$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$F(R(\lambda_{\mathrm{X}})(\mu_{L(1_\mathrm{A}),x_1}))(\iota_2)$} (C)
 (A) edge node[left]{$\iota_1$} (D)
 (E) edge node[above]{$\iota_4$} (D)
-(C) edge node[right]{$F(R(\lambda_\bold{D}))(\iota_3)$} (E);
-\end{tikzpicture}
-\]
-where $d_{!+1}$ is the decoration $d_1$ on the element $R(L(1_\bold{C})+d_1) \in \bold{C}$.
-The above square commutes because $$F(\lambda_\bold{C})(!_{1_\bold{C}}+d_1) = F(R(\lambda_\bold{D})(\mu_{L(1_\bold{C}),d_1})(\eta_{1_\bold{C}}+1))(!_{1_\bold{C}}+d_1)$$ as the above diagram of maps of cospans commutes.
+(C) edge node[right]{$F(R(\lambda_\mathrm{X}))(\iota_3)$} (E);
+\end{tikzpicture}
+\]
+where $x_{!+1}$ is the decoration $x_1$ on the element $R(L(1_\mathrm{A})+x_1) \in \mathrm{A}$.
+The above square commutes because $$F(\lambda_\mathrm{A})(!_{1_\mathrm{A}}+x_1) = F(R(\lambda_\mathrm{X})(\mu_{L(1_\mathrm{A}),x_1})(\eta_{1_\mathrm{A}}+1))(!_{1_\mathrm{A}}+x_1)$$ as the above diagram of maps of cospans commutes.
 The right unitality square is similar.
@@
 			\node (a) at (-4.25,0) {$(c_1+c_2)+c_3$};
-			\node (b) at (1.5,0) {$(R(d_1)+R(d_2))+R(d_3)$};
+			\node (b) at (1.5,0) {$(R(x_1)+R(x_2))+R(x_3)$};
 			\node (c) at (7.25,0) {$(c_1^\prime+c_2^\prime)+c_3^\prime$};
 			\node (a2) at (-4.25,1) {$(c_1+c_2)+c_3$};
-			\node (b2) at (1.5,1) {$R(d_1+d_2)+R(d_3)$};
+			\node (b2) at (1.5,1) {$R(x_1+x_2)+R(x_3)$};
 			\node (c2) at (7.25,1) {$(c_1^\prime+c_2^\prime)+c_3^\prime$};
                                 \node (a3) at (-4.25,2) {$(c_1+c_2)+c_3$};
-			\node (b3) at (1.5,2) {$R((d_1+d_2)+d_3)$};
+			\node (b3) at (1.5,2) {$R((x_1+x_2)+x_3)$};
 			\node (c3) at (7.25,2) {$(c_1^\prime+c_2^\prime)+c_3^\prime$};
                                 \node (a4) at (-4.25,3) {$c_1+(c_2+c_3)$};
-			\node (b4) at (1.5,3) {$R(d_1+(d_2+d_3))$};
+			\node (b4) at (1.5,3) {$R(x_1+(x_2+x_3))$};
 			\node (c4) at (7.25,3) {$c_1^\prime + (c_2^\prime + c_3^\prime)$};
                                 \node (a5) at (-4.25,-1) {$c_1+(c_2+c_3)$};
-			\node (b5) at (1.5,-1) {$R(d_1)+(R(d_2)+R(d_3))$};
+			\node (b5) at (1.5,-1) {$R(x_1)+(R(x_2)+R(x_3))$};
 			\node (c5) at (7.25,-1) {$c_1^\prime + (c_2^\prime + c_3^\prime)$};
                                 \node (a6) at (-4.25,-2) {$c_1+(c_2+c_3)$};
-			\node (b6) at (1.5,-2) {$R(d_1)+R(d_2+d_3)$};
+			\node (b6) at (1.5,-2) {$R(x_1)+R(x_2+x_3)$};
 			\node (c6) at (7.25,-2) {$c_1^\prime + (c_2^\prime + c_3^\prime)$};
                                 \node (a7) at (-4.25,-3) {$c_1+(c_2+c_3)$};
-			\node (b7) at (1.5,-3) {$R(d_1+(d_2+d_3))$};
+			\node (b7) at (1.5,-3) {$R(x_1+(x_2+x_3))$};
 			\node (c7) at (7.25,-3) {$c_1^\prime + (c_2^\prime + c_3^\prime)$};
@@
 			(c4) edge node[above]{$R(o_1+(o_2+o_3))\eta_{c_1^\prime+(c_2^\prime+c_3^\prime)}$} (b4)
-                                (a3) edge node[left]{$a_\bold{C}$} (a4)
-                                (b3) edge node[left]{$R(a_\bold{D})$} (b4)
+                                (a3) edge node[left]{$a_\mathrm{A}$} (a4)
+                                (b3) edge node[left]{$R(a_\mathrm{X})$} (b4)
 (b3) edge node[right]{$\iota_3$} (b4)
-			(c3) edge node[left]{$a_\bold{C}$} (c4)
+			(c3) edge node[left]{$a_\mathrm{A}$} (c4)
                                 (a5) edge node[above]{$R(i_1)\eta_{c_1}+(R(i_2)\eta_{c_2}+R(i_3)\eta_{c_3})$} (b5)
 			(c5) edge node[above]{$R(o_1)\eta_{c_1^\prime}+(R(o_2)\eta_{c_2^\prime}+R(o_3)\eta_{c_3^\prime})$} (b5)
-                                (a) edge node[left]{$a_\bold{C}$} (a5)
-                                (b) edge node[left]{$a_\bold{C}$} (b5)
+                                (a) edge node[left]{$a_\mathrm{A}$} (a5)
+                                (b) edge node[left]{$a_\mathrm{A}$} (b5)
 (b) edge node[right]{$\iota_4$} (b5)
-			(c) edge node[left]{$a_\bold{C}$} (c5)
+			(c) edge node[left]{$a_\mathrm{A}$} (c5)
                                 (a6) edge node[above]{$R(i_1)\eta_{c_1}+R(i_2+i_3)\eta_{c_2+c_3}$} (b6)
@@
 	\]
-with the corresponding maps of decorations amounting to the following commutative diagram in $F(R(d_1+(d_2+d_3)))$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$F((\kappa)(1+\kappa)(a_\bold{C}))((d_1+d_2)+d_3)$};
-\node (B) at (5,0) {$F((R(a_\bold{D}))(\kappa))((d_1+d_2)+d_3)$};
-\node (C) at (5,-1) {$F(R(a_\bold{D}))((d_1+d_2)+d_3)$};
-\node (D) at (5,-2) {$d_1+(d_2+d_3)$};
-\node (E) at (0,-1) {$F((\kappa)(1+\kappa))((d_1+d_2)+d_3)$};
-\node (F) at (0,-2) {$F(\kappa)(d_1+(d_2+d_3))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$F((R(a_\bold{D}))(\kappa))(\iota_1)$} (B)
-(B) edge node[right]{$F(R(a_\bold{D}))(\iota_2)$} (C)
+with the corresponding maps of decorations amounting to the following commutative diagram in $F(R(x_1+(x_2+x_3)))$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$F((\kappa)(1+\kappa)(a_\mathrm{A}))((x_1+x_2)+x_3)$};
+\node (B) at (5,0) {$F((R(a_\mathrm{X}))(\kappa))((x_1+x_2)+x_3)$};
+\node (C) at (5,-1) {$F(R(a_\mathrm{X}))((x_1+x_2)+x_3)$};
+\node (D) at (5,-2) {$x_1+(x_2+x_3)$};
+\node (E) at (0,-1) {$F((\kappa)(1+\kappa))((x_1+x_2)+x_3)$};
+\node (F) at (0,-2) {$F(\kappa)(x_1+(x_2+x_3))$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$F((R(a_\mathrm{X}))(\kappa))(\iota_1)$} (B)
+(B) edge node[right]{$F(R(a_\mathrm{X}))(\iota_2)$} (C)
 (C) edge node[right]{$\iota_3$} (D)
@@
 \]
-The above square commutes because $$F((\kappa)(1+\kappa)(a_\bold{C}))((d_1+d_2)+d_3) = F((R(a_\bold{D}))(\kappa)(\kappa+1))((d_1+d_2)+d_3)$$ as the above diagram of maps of cospans commutes.
+The above square commutes because $$F((\kappa)(1+\kappa)(a_\mathrm{A}))((x_1+x_2)+x_3) = F((R(a_\mathrm{X}))(\kappa)(\kappa+1))((x_1+x_2)+x_3)$$ as the above diagram of maps of cospans commutes.
 Lastly, the braiding square:
@@
 			\node (a) at (-4,0) {$c_1+c_2$};
-			\node (b) at (0.5,0) {$R(d_1)+R(d_2)$};
+			\node (b) at (0.5,0) {$R(x_1)+R(x_2)$};
 			\node (c) at (5,0) {$c_1^\prime+c_2^\prime$};
 			\node (a2) at (-4,1) {$c_2+c_1$};
-			\node (b2) at (0.5,1) {$R(d_2)+R(d_1)$};
+			\node (b2) at (0.5,1) {$R(x_2)+R(x_1)$};
 			\node (c2) at (5,1) {$c_2^\prime+c_1^\prime$};
                                 \node (a3) at (-4,2) {$c_2+c_1$};
-			\node (b3) at (0.5,2) {$R(d_2+d_1)$};
+			\node (b3) at (0.5,2) {$R(x_2+x_1)$};
 			\node (c3) at (5,2) {$c_2^\prime + c_1^\prime$};
                                 \node (a5) at (-4,-1) {$c_1+c_2$};
-			\node (b5) at (0.5,-1) {$R(d_1+d_2)$};
+			\node (b5) at (0.5,-1) {$R(x_1+x_2)$};
 			\node (c5) at (5,-1) {$c_1^\prime+c_2^\prime$};
                                 \node (a6) at (-4,-2) {$c_2+c_1$};
-			\node (b6) at (0.5,-2) {$R(d_2+d_1)$};
+			\node (b6) at (0.5,-2) {$R(x_2+x_1)$};
 			\node (c6) at (5,-2) {$c_2^\prime + c_1^\prime$};
@@
 			(c2) edge node[above]{$R(o_2) \eta_{c_2^\prime} + R(o_1) \eta_{c_1^\prime}$} (b2)
-                                (a) edge node[left]{$\beta_\bold{C}$} (a2)
-                                (b) edge node[left]{$\beta_\bold{C}$} (b2)
+                                (a) edge node[left]{$\beta_\mathrm{A}$} (a2)
+                                (b) edge node[left]{$\beta_\mathrm{A}$} (b2)
 (b) edge node[right]{$\iota_1$} (b2)
-			(c) edge node[left]{$\beta_\bold{C}$} (c2)
+			(c) edge node[left]{$\beta_\mathrm{A}$} (c2)
                                 (a3) edge node[above]{$R(i_2+i_1)\eta_{c_2+c_1}$} (b3)
@@
 			(c6) edge node[above]{$R(o_2+o_1)\eta_{c_2^\prime+c_1^\prime}$} (b6)
-                                (a5) edge node[left]{$\beta_\bold{C}$} (a6)
-                                (b5) edge node[left]{$R(\beta_\bold{D})$} (b6)
+                                (a5) edge node[left]{$\beta_\mathrm{A}$} (a6)
+                                (b5) edge node[left]{$R(\beta_\mathrm{X})$} (b6)
  (b5) edge node[right]{$\iota_4$} (b6)
-			(c5) edge node[left]{$\beta_\bold{C}$} (c6);
-		\end{tikzpicture}
-	\]
-with the corresponding maps of decorations amounting to the following commutative diagram in $F(R(d_2+d_1))$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (-.5,0) {$F((\kappa)(\beta_\bold{C}))(d_1+d_2)$};
-\node (C) at (4,0) {$F(\kappa)(d_2+d_1)$};
-\node (D) at (-.5,-1) {$F(R(\beta_\bold{D}))(d_1+d_2)$};
-\node (E) at (4,-1) {$d_2+d_1$};
+			(c5) edge node[left]{$\beta_\mathrm{A}$} (c6);
+		\end{tikzpicture}
+	\]
+with the corresponding maps of decorations amounting to the following commutative diagram in $F(R(x_2+x_1))$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (-.5,0) {$F((\kappa)(\beta_\mathrm{A}))(x_1+x_2)$};
+\node (C) at (4,0) {$F(\kappa)(x_2+x_1)$};
+\node (D) at (-.5,-1) {$F(R(\beta_\mathrm{X}))(x_1+x_2)$};
+\node (E) at (4,-1) {$x_2+x_1$};
 \path[->,font=\scriptsize,>=angle 90]
 (A) edge node[above]{$F(\kappa)(\iota_1)$} (C)
-(A) edge node[left]{$F(R(\beta_\bold{D}))(\iota_3)$} (D)
+(A) edge node[left]{$F(R(\beta_\mathrm{X}))(\iota_3)$} (D)
 (D) edge node[above]{$\iota_4$} (E)
@@
 \]
-The above square commutes because $$F((\kappa)(\beta_\bold{C}))(d_1+d_2) = F((R(\beta_\bold{D}))(\kappa))(d_1+d_2)$$ as the above diagram of maps of cospans commutes.
-Thus the double functor $\mathbb{E} \colon _L\mathbb{C}\textnormal{sp}(\bold{D}) \to \mathbb{F}\textnormal{Cospan}(\bold{C})$ is symmetric monoidal.
+The above square commutes because $$F((\kappa)(\beta_\mathrm{A}))(x_1+x_2) = F((R(\beta_\mathrm{X}))(\kappa))(x_1+x_2)$$ as the above diagram of maps of cospans commutes.
+Thus the double functor $\mathbb{E} \colon _L\mathbb{C}\textnormal{sp}(\mathrm{X}) \to \mathbb{F}\textnormal{Cospan}(\mathrm{A})$ is symmetric monoidal.
 \end{proof}
-Using a result of Shulman \cite{Shul}, each of the isofibrant symmetric monoidal double categories $\mathbb{F}\textnormal{Cospan}(\bold{C})$ and $_L \textnormal{Csp}(\bold{D})$ give rise to underlying symmetric monoidal bicategories, namely $\mathbb{F}\textnormal{Cospan}(\bold{C})$ induces a symmetric monoidal bicategory $H(\mathbb{F}\textnormal{Cospan}(\bold{C}))$ which has:
+Using a result of Shulman \cite{Shul}, each of the isofibrant symmetric monoidal double categories $\mathbb{F}\textnormal{Cospan}(\mathrm{A})$ and $_L \mathbb{C}\textnormal{sp}(\mathrm{X})$ give rise to underlying symmetric monoidal bicategories, namely $\mathbb{F}\textnormal{Cospan}(\mathrm{A})$ induces a symmetric monoidal bicategory $H(\mathbb{F}\textnormal{Cospan}(\mathrm{A}))$ which has:
 \begin{enumerate}
-\item{objects as those of $\bold{C}$,}
-\item{morphisms as horizontal 1-cells of $\mathbb{F}\textnormal{Cospan}(\bold{C})$, and}
-\item{2-morphisms as globular 2-morphisms of $\mathbb{F}\textnormal{Cospan}(\bold{C})$.}
+\item{objects as those of $\mathrm{A}$,}
+\item{morphisms as horizontal 1-cells of $\mathbb{F}\textnormal{Cospan}(\mathrm{A})$, and}
+\item{2-morphisms as globular 2-morphisms of $\mathbb{F}\textnormal{Cospan}(\mathrm{A})$.}
 \end{enumerate} 
-Likewise, $_L \textnormal{Csp}(\bold{D})$ induces a symmetric monoidal bicategory $H( {_L \textnormal{Csp}(\bold{D})})$ which has:
+Likewise, $_L \mathbb{C}\textnormal{sp}(\mathrm{X})$ induces a symmetric monoidal bicategory $H( {_L \mathbb{C}\textnormal{sp}(\mathrm{X})})$ which has:
 \begin{enumerate}
-\item{objects as those of $\bold{C}$,}
-\item{morphisms as horizontal 1-cells of $_L \textnormal{Csp}(\bold{D})$, and}
-\item{2-morphisms as globular 2-morphisms of $_L \textnormal{Csp}(\bold{D})$.}
+\item{objects as those of $\mathrm{A}$,}
+\item{morphisms as horizontal 1-cells of $_L \mathbb{C}\textnormal{sp}(\mathrm{X})$, and}
+\item{2-morphisms as globular 2-morphisms of $_L \mathbb{C}\textnormal{sp}(\mathrm{X})$.}
 \end{enumerate}
@@
 \begin{cor}
-The bicategories $H(\mathbb{F}\textnormal{Cospan}(\bold{C}))$ and $H( {_L \textnormal{Csp}(\bold{D})})$ are biequivalent.
+The bicategories $H(\mathbb{F}\textnormal{Cospan}(\mathrm{A}))$ and $H( {_L \mathbb{C}\textnormal{sp}(\mathrm{X})})$ are biequivalent.
 \end{cor}
@@
 
-We can also define the part of the double equivalence $\mathbb{G} \colon \mathbb{F}\textnormal{Cospan}(\bold{C}) \to _L \mathbb{C} \textnormal{sp}(\bold{D})$ which goes in the other direction: again, the object component of this double functor will be $\mathbb{G}_0 = \id_{\bold{C}}$.
-
-Given a horizontal 1-cell $M$ of $\mathbb{F} \textnormal{Cospan}(\bold{C})$:
+We can also define the part of the double equivalence $\mathbb{G} \colon \mathbb{F}\textnormal{Cospan}(\mathrm{A}) \to _L \mathbb{C} \textnormal{sp}(\mathrm{X})$ which goes in the other direction: again, the object component of this double functor will be $\mathbb{G}_0 = \id_{\mathrm{A}}$.
+
+Given a horizontal 1-cell $M$ of $\mathbb{F} \textnormal{Cospan}(\mathrm{A})$:
 \[
@@
 \node (C) at (2,0) {$c_2$};
-\node (D) at (1,-0.5) {$d \in F(c)$};
+\node (D) at (1,-0.5) {$x \in F(c)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-the image $\mathbb{G}(M)$ is the horizontal 1-cell in $_L \mathbb{C}\textnormal{sp}(\bold{D})$ given by:
+the image $\mathbb{G}(M)$ is the horizontal 1-cell in $_L \mathbb{C}\textnormal{sp}(\mathrm{X})$ given by:
 \[
@@
 \]
-where $\tau_c \colon L(c) \to d$ is the unique morphism from the trival decoration on $c$ given by $$!_c \coloneqq 1 \xrightarrow{\phi} F(0) \xrightarrow{F(!)} F(c)$$ to $d \in F(c)$.
-In other words, the trivial decoraction $!_c$ is initial in $F(c)$ and $\tau_c \colon !_c \to d$ is the unique morphism to $d$.
-Similarly, given a 2-morphism $(f,h,g,\iota) \colon M \to M^\prime$ of $\mathbb{F} \textnormal{Cospan}(\bold{C})$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (D) at (1,0.5) {$d \in F(c)$};
-\node (D') at (1,-1.5) {$d^\prime \in F(c^\prime)$};
+where $\tau_c \colon L(c) \to x$ is the unique morphism from the trival decoration on $c$ given by $$!_c \coloneqq 1 \xrightarrow{\phi} F(0) \xrightarrow{F(!)} F(c)$$ to $x \in F(c)$.
+In other words, the trivial decoraction $!_c$ is initial in $F(c)$ and $\tau_c \colon !_c \to x$ is the unique morphism to $x$.
+Similarly, given a 2-morphism $(f,h,g,\iota) \colon M \to M^\prime$ of $\mathbb{F} \textnormal{Cospan}(\mathrm{A})$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (D) at (1,0.5) {$x \in F(c)$};
+\node (D') at (1,-1.5) {$x^\prime \in F(c^\prime)$};
 \node (A) at (0,0) {$c_1$};
@@
 \]
-$$\iota \colon F(h)(d) \to d^\prime$$
-the image in $_L \mathbb{C}\textnormal{sp}(\bold{D})$ is given by the 2-morphism:
+$$\iota \colon F(h)(x) \to x^\prime$$
+the image in $_L \mathbb{C}\textnormal{sp}(\mathrm{X})$ is given by the 2-morphism:
 \[
@@
 \]
-where $\alpha \colon d \to d^\prime$ is a morphism in the Grothendieck construction of $F$ given by $\alpha = (h \colon c \to c^\prime, \iota \colon F(h)(d) \to d^\prime)$.
-
-Next, we exhibit natural isomorphisms $\eta \colon \id_{ _L \mathbb{C}\textnormal{sp}(\bold{D})} \cong \mathbb{G} \mathbb{E}$ and $\epsilon \colon \mathbb{E} \mathbb{G} \cong \id_{\mathbb{F}\textnormal{Cospan}(\bold{C})}$.
+where $\alpha \colon x \to x^\prime$ is a morphism in the Grothendieck construction of $F$ given by $\alpha = (h \colon c \to c^\prime, \iota \colon F(h)(x) \to x^\prime)$.
+
+Next, we exhibit natural isomorphisms $\eta \colon \id_{ _L \mathbb{C}\textnormal{sp}(\mathrm{X})} \cong \mathbb{G} \mathbb{E}$ and $\epsilon \colon \mathbb{E} \mathbb{G} \cong \id_{\mathbb{F}\textnormal{Cospan}(\mathrm{A})}$.
 Specifically, these are double natural isomorphisms given by double transformations $\eta$ and $\epsilon$ whose components are isomorphisms.
@@
 First we compute the composites $\mathbb{G} \mathbb{E}$ and $\mathbb{E} \mathbb{G}$.
-On the object categories, both composites are $\id_\bold{C}$ and we have natural isomorphisms $\eta \colon \id_{\bold{C}} \cong \mathbb{G}_0 \mathbb{E}_0$ and $\epsilon \colon \mathbb{E}_0 \mathbb{G}_0 \cong \id_{\bold{C}}$.
-
-Given a horizontal 1-cell $M$ in $_L \mathbb{C} \textnormal{sp}(\bold{D})$:
+On the object categories, both composites are $\id_\mathrm{A}$ and we have natural isomorphisms $\eta \colon \id_{\mathrm{A}} \cong \mathbb{G}_0 \mathbb{E}_0$ and $\epsilon \colon \mathbb{E}_0 \mathbb{G}_0 \cong \id_{\mathrm{A}}$.
+
+Given a horizontal 1-cell $M$ in $_L \mathbb{C} \textnormal{sp}(\mathrm{X})$:
 \[
@@
 \node (A) at (0,0) {$c_1$};
-\node (B) at (1,0) {$R(d)$};
+\node (B) at (1,0) {$R(x)$};
 \node (C) at (2,0) {$c_2$};
-\node (D) at (1,-0.5) {$d \in F(R(d))$};
+\node (D) at (1,-0.5) {$x \in F(R(x))$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \node (A) at (0,0) {$L(c_1)$};
-\node (B) at (1.5,0) {$d$};
+\node (B) at (1.5,0) {$x$};
 \node (C) at (3,0) {$L(c_2)$};
 \path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$\tau_{R(d)}L(R(i))$} (B)
-(C) edge node[above]{$\tau_{R(d)}L(R(o))$} (B);
-\end{tikzpicture}
-\]
-\textbf{What can we say about LR? Find a 2-iso between these in $_L Csp(D)$.}
-Then we can find a 2-isomorphism $\eta_M \colon M \xrightarrow{\sim} \mathbb{G}\mathbb{E}(M) $ in $_L \mathbb{C} \textnormal{sp}(\bold{C})$ given by:
+(A) edge node[above]{$\tau_{R(x)}L(R(i))$} (B)
+(C) edge node[above]{$\tau_{R(x)}L(R(o))$} (B);
+\end{tikzpicture}
+\]
+\textbf{What can we say about LR? Find a 2-iso between these in $_L \mathbb{C}\textnormal{sp}(\mathrm{X})$.}
+Then we can find a 2-isomorphism $\eta_M \colon M \xrightarrow{\sim} \mathbb{G}\mathbb{E}(M) $ in $_L \mathbb{C} \textnormal{sp}(\mathrm{X})$ given by:
 \[
@@
 \node (A) at (0,0) {$L(c_1)$};
-\node (B) at (1.25,0) {$d$};
+\node (B) at (1.25,0) {$x$};
 \node (C) at (2.5,0) {$L(c_2)$};
 \node (A') at (0,-1) {$L(c_1)$};
-\node (B') at (1.25,-1) {$d$};
+\node (B') at (1.25,-1) {$x$};
 \node (C') at (2.5,-1) {$L(c_2)$};
@@
 (C) edge node[above]{$o$} (B)
-(A') edge node[above]{$\tau_{R(d)}L(R(i))$} (B')
-(C') edge node[above]{$\tau_{R(d)}L(R(o))$} (B')
+(A') edge node[above]{$\tau_{R(x)}L(R(i))$} (B')
+(C') edge node[above]{$\tau_{R(x)}L(R(o))$} (B')
 (A) edge node [left]{$1$} (A')
@@
 \]
-On the other hand, given a horizontal 1-cell $N$ in $\mathbb{F}\textnormal{Cospan}(\bold{C})$:
+On the other hand, given a horizontal 1-cell $N$ in $\mathbb{F}\textnormal{Cospan}(\mathrm{A})$:
 \[
@@
 \]
-Then we can find a 2-isomorphism $\epsilon_N \colon \mathbb{E} \mathbb{G} (N) \xrightarrow{\sim} N$ in $\mathbb{F}\textnormal{Cospan}(\bold{C})$ given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (D) at (1,0.5) {$d \in F(R(d))$};
-\node (D') at (1,-1.5) {$d \in F(c)$};
+Then we can find a 2-isomorphism $\epsilon_N \colon \mathbb{E} \mathbb{G} (N) \xrightarrow{\sim} N$ in $\mathbb{F}\textnormal{Cospan}(\mathrm{A})$ given by:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (D) at (1,0.5) {$x \in F(R(x))$};
+\node (D') at (1,-1.5) {$x \in F(c)$};
 \node (A) at (0,0) {$c_1$};
-\node (B) at (1,0) {$R(d)$};
+\node (B) at (1,0) {$R(x)$};
 \node (C) at (2,0) {$c_2$};
@@
 \]
-$$\iota \colon F(e)(d) \to d$$
+$$\iota \colon F(e)(x) \to x$$
 \section{An example}
-As an example, let $L \colon \bold{FinSet} \to \bold{Graph}$ be the functor which is left adjoint to the forgetful functor $R \colon \bold{Graph} \to \bold{FinSet}$; the functor $L$ maps a finite set $N$ to the discrete graph with $N$ as its set of vertices and no edges.
-Since $\bold{Graph}$ is a topos and thus has finite colimits, we can then obtain a symmetric monoidal double category $_L \mathbb{C}\textnormal{sp}(\bold{Graph})$ which has:
+As an example, let $L \colon \mathrm{FinSet} \to \mathrm{Graph}$ be the functor which is left adjoint to the forgetful functor $R \colon \mathrm{Graph} \to \mathrm{FinSet}$; the functor $L$ maps a finite set $N$ to the discrete graph with $N$ as its set of vertices and no edges.
+Since $\mathrm{Graph}$ is a topos and thus has finite colimits, we can then obtain a symmetric monoidal double category $_L \mathbb{C}\textnormal{sp}(\mathrm{Graph})$ which has:
 \begin{enumerate}
@@
 
-On the other hand, let $F \colon \bold{FinSet} \to \bold{Cat}$ be the symmetric lax monoidal pseudofunctor that assigns to a finite set $N$ the \emph{category} of all graph structures whose underlying set of vertices is $N$.
-Using Theorem \ref{main1}, we can then obtain a symmetric monoidal double category $\mathbb{F}\textnormal{Cospan}(\bold{FinSet})$ which has:
+On the other hand, let $F \colon \mathrm{FinSet} \to \mathrm{Cat}$ be the symmetric lax monoidal pseudofunctor that assigns to a finite set $N$ the \emph{category} of all graph structures whose underlying set of vertices is $N$.
+Using Theorem \ref{main1}, we can then obtain a symmetric monoidal double category $\mathbb{F}\textnormal{Cospan}(\mathrm{FinSet})$ which has:
 \begin{enumerate}
@@
 \end{enumerate}
-We thus have two symmetric monoidal double categories: $_L \mathbb{C}\textnormal{sp}(\bold{Graph})$ obtained from structured cospans and $\mathbb{F}\textnormal{Cospan}(\bold{FinSet})$ using Theorem \ref{main1}.
+We thus have two symmetric monoidal double categories: $_L \mathbb{C}\textnormal{sp}(\mathrm{Graph})$ obtained from structured cospans and $\mathbb{F}\textnormal{Cospan}(\mathrm{FinSet})$ using Theorem \ref{main1}.
 These two double categories are in fact equivalent as symmetric monoidal double categories which we now show.
 
-Define a double functor $\mathbb{E} \colon _L \mathbb{C}\textnormal{sp}(\bold{Graph}) \to \mathbb{F}\textnormal{Cospan}(\bold{FinSet})$ as follows: $\mathbb{E}_0=\id_{\bold{FinSet}}$ as both double categories $_L \mathbb{C}\textnormal{sp}(\bold{Graph})$ and $\mathbb{F}\textnormal{Cospan}(\bold{FinSet})$ have $\bold{FinSet}$ as their category of objects.
-The identity functor on $\bold{FinSet}$ is trivially an equivalence.
-For the arrow component $\mathbb{E}_1$, given a horizontal 1-cell of $_L \mathbb{C}\textnormal{sp}(\bold{Graph})$, which is a cospan in $\bold{Graph}$ of the form:
+\textbf{Probably delete stuff after this line.}
+
+Define a double functor $\mathbb{E} \colon _L \mathbb{C}\textnormal{sp}(\mathrm{Graph}) \to \mathbb{F}\textnormal{Cospan}(\mathrm{FinSet})$ as follows: $\mathbb{E}_0=\id_{\mathrm{FinSet}}$ as both double categories $_L \mathbb{C}\textnormal{sp}(\mathrm{Graph})$ and $\mathbb{F}\textnormal{Cospan}(\mathrm{FinSet})$ have $\mathrm{FinSet}$ as their category of objects.
+The identity functor on $\mathrm{FinSet}$ is trivially an equivalence.
+For the arrow component $\mathbb{E}_1$, given a horizontal 1-cell of $_L \mathbb{C}\textnormal{sp}(\mathrm{Graph})$, which is a cospan in $\mathrm{Graph}$ of the form:
 \[
@@
 \]
-the functor $\mathbb{E}_1$ maps this horizontal 1-cell to the horizontal 1-cell of $\mathbb{F}\textnormal{Cospan}(\bold{FinSet})$ given by:
+the functor $\mathbb{E}_1$ maps this horizontal 1-cell to the horizontal 1-cell of $\mathbb{F}\textnormal{Cospan}(\mathrm{FinSet})$ given by:
 \[
@@
 \]
-where $R \colon \bold{Graph} \to \bold{FinSet}$ is the forgetful functor, right adjoint to $L \colon \bold{FinSet} \to \bold{Graph}$.
-The image of a 2-morphism in $_L \mathbb{C}\textnormal{sp}(\bold{Graph})$ given by:
+where $R \colon \mathrm{Graph} \to \mathrm{FinSet}$ is the forgetful functor, right adjoint to $L \colon \mathrm{FinSet} \to \mathrm{Graph}$.
+The image of a 2-morphism in $_L \mathbb{C}\textnormal{sp}(\mathrm{Graph})$ given by:
 \[
@@
 \]
-is the 2-morphism in $\mathbb{F}\textnormal{Cospan}(\bold{FinSet})$ given by:
+is the 2-morphism in $\mathbb{F}\textnormal{Cospan}(\mathrm{FinSet})$ given by:
 \[
@@
 together with a graph morphism $\iota_h \colon F(R(h))(M) \to M^\prime$.
-Denoting a cospan by its apex, the map $$\mathbb{E}_1 \colon { _f { _L \mathbb{C}\textnormal{sp}(\bold{Graph})}_g} (M,M^\prime) \to { _{\mathbb{E}(f)} \mathbb{F}\textnormal{Cospan}(\bold{FinSet})_{\mathbb{E}(g)}}(\mathbb{E}(M),\mathbb{E}(M^\prime))$$ is bijective and thus the double functor $\mathbb{E}$ is full and faithful.
-To see that it is also essentially surjective, given a horizontal 1-cell in $\mathbb{F}\textnormal{Cospan}(\bold{FinSet})$:
+Denoting a cospan by its apex, the map $$\mathbb{E}_1 \colon { _f { _L \mathbb{C}\textnormal{sp}(\mathrm{Graph})}_g} (M,M^\prime) \to { _{\mathbb{E}(f)} \mathbb{F}\textnormal{Cospan}(\mathrm{FinSet})_{\mathbb{E}(g)}}(\mathbb{E}(M),\mathbb{E}(M^\prime))$$ is bijective and thus the double functor $\mathbb{E}$ is full and faithful.
+To see that it is also essentially surjective, given a horizontal 1-cell in $\mathbb{F}\textnormal{Cospan}(\mathrm{FinSet})$:
 \[
@@
 \]
-there exists a horizontal 1-cell in $_L \mathbb{C}\textnormal{sp}(\bold{Graph})$:
+there exists a horizontal 1-cell in $_L \mathbb{C}\textnormal{sp}(\mathrm{Graph})$:
 \[
@@
 \]
-and a 2-isomorphism in $\mathbb{F}\textnormal{Cospan}(\bold{FinSet})$ from the image of the latter horizontal 1-cell to the former given by:
+and a 2-isomorphism in $\mathbb{F}\textnormal{Cospan}(\mathrm{FinSet})$ from the image of the latter horizontal 1-cell to the former given by:
 \[
@@
 which trivially commutes as $R(M)=N$ and $R(i^\prime)$ and $R(o^\prime)$ are the underlying maps of vertices of the graph morphisms $i^\prime$ and $o^\prime$ which act as the functions $i$ and $o$, respectively.
-Given two composable horizontal 1-cells $\alpha$ and $\beta$ of $_L \mathbb{C}\textnormal{sp}(\bold{Graph})$:
+Given two composable horizontal 1-cells $\alpha$ and $\beta$ of $_L \mathbb{C}\textnormal{sp}(\mathrm{Graph})$:
 \[
@@
 The right adjoint $R \colon \textrm{Graph} \to \textrm{Set}$ is also a left adjoint $R \dashv K$ to the codiscrete graph functor $K \colon \textrm{Set} \to \textrm{Graph}$ which sends a finite set $N$ to the complete graph with $N$ as its underlying set of vertices.
-The functor $R \colon \textrm{Graph} \to \textrm{Set}$ thus also preserves colimits which yields an isomorphism $$ R(M +_{L(N_2)} M^\prime) \cong R(M) +_{R(L(N_2))} R(M^\prime)$$ and again we make use of the fact that the left adjoint $L \colon \textrm{Set} \to \textrm{Graph}$ is fully faithful and thus the unit $$\eta_{N_2} \colon N_2 \to R(L(N_2))$$ is an isomorphism which gives $$R(M +_{L(N_2)} M^\prime) \cong R(M) +_{R(L(N_2))} R(M^\prime) \cong R(M) +_{N_2} R(M^\prime).$$ Thus the double functor $\mathbb{E} \colon _L \mathbb{C}\textnormal{sp}(\bold{Graph}) \to \mathbb{F}\textnormal{Cospan}(\bold{Set})$ is strong and we  have an equivalence of double categories $_L \mathbb{C}\textnormal{sp}(\textrm{Graph}) \sim \mathbb{F}\textrm{Cospan}(\textrm{Set})$.
+The functor $R \colon \textrm{Graph} \to \textrm{Set}$ thus also preserves colimits which yields an isomorphism $$ R(M +_{L(N_2)} M^\prime) \cong R(M) +_{R(L(N_2))} R(M^\prime)$$ and again we make use of the fact that the left adjoint $L \colon \textrm{Set} \to \textrm{Graph}$ is fully faithful and thus the unit $$\eta_{N_2} \colon N_2 \to R(L(N_2))$$ is an isomorphism which gives $$R(M +_{L(N_2)} M^\prime) \cong R(M) +_{R(L(N_2))} R(M^\prime) \cong R(M) +_{N_2} R(M^\prime).$$ Thus the double functor $\mathbb{E} \colon _L \mathbb{C}\textnormal{sp}(\mathrm{Graph}) \to \mathbb{F}\textnormal{Cospan}(\mathrm{FinSet})$ is strong and we  have an equivalence of double categories $_L \mathbb{C}\textnormal{sp}(\textrm{Graph}) \sim \mathbb{F}\textrm{Cospan}(\textrm{FinSet})$.
 Moreover, each of these categories is symmetric monoidal and the double functor $\mathbb{E}$ is symmetric monoidal; first, we have that the following diagrams commute.
@@
 
-%\bibitem{Brown1} R.\ Brown and C.\ B.\ Spencer, Double groupoids and crossed modules, 
+\bibitem{Brown1} R.\ Brown and C.\ B.\ Spencer, Double groupoids and crossed modules, 
 \textsl{Cah.\ Top.\ G\'eom.\ Diff.} \textbf{17} (1976), 343--362.
 
-%\bibitem{Brown2} R.\ Brown, K.\ Hardie, H.\ Kamps and T.\ Porter, The homotopy double groupoid of a Hausdorff space, \textsl{Th.\ Appl.\ Categ.} \textbf{10} (2002), 71--93.
+\bibitem{Brown2} R.\ Brown, K.\ Hardie, H.\ Kamps and T.\ Porter, The homotopy double groupoid of a Hausdorff space, \textsl{Th.\ Appl.\ Categ.} \textbf{10} (2002), 71--93.
 
@@
 
-%\bibitem{Reb} F.\ Rebro, Constructing the bicategory Span$_{2}(\bold{C})$. Available as \href{https://arxiv.org/abs/1501.00792}{arXiv:1501.00792}.
+%\bibitem{Reb} F.\ Rebro, Constructing the bicategory Span$_{2}(\mathrm{A})$. Available as \href{https://arxiv.org/abs/1501.00792}{arXiv:1501.00792}.
 

### 2018-10-05 EquivCompFrameworks_20180911kc.tex
removed stuff that probably won't be used, under 50 pages now

@@
 
-The outline for the paper is as follows: In the second section we present the definition of double category and symmetric monoidal double category, both of which can be found in earlier works \cite{Shul}.
-In the third section, we construct the symmetric monoidal double category $F\textnormal{Cospan}(\textrm{A})$ mentioned above as well as a result of Shulman that allows us to obtain a symmetric monoidal bicategory whose decategorification is an improved version of Fong's symmetric monoidal category.
+The outline for the paper is as follows: In the second section, we construct the symmetric monoidal double category $F\textnormal{Cospan}(\textrm{A})$ mentioned above as well as a result of Shulman that allows us to obtain a symmetric monoidal bicategory whose decategorification is an improved version of Fong's symmetric monoidal category.
+In the third section we define maps between decorated cospan double categories which are double functors of an appropriate type.
 In the fourth section we investigate when a symmetric lax monoidal pseudofunctor gives rise to a left adjoint via the Grothendieck construction.
-In the fifth section we review another compositional framework which uses cospans equipped with extra structure due to the first two authors, namely `structured cospans' and prove that the double categorical versions of decorated cospans and structured cospans are equivalent, and in the final section, we present a few examples that can be realized with either framework and exhibit the equivalences.
-
-\section{A review of double categories and symmetric monoidal double categories}
-\textbf{Likely move this to an appendix or remove entirely and just cite another paper.}
-This section is meant to serve as a review of double categories and to present the definitions of double category, symmetric monoidal double category and a few more ideas that will be used later in the paper.
-Nothing in this section is new and can be found in the work of Shulman \cite{Shul}.
-
-Before formally defining `pseudo double category', it is helpful to have the following picture in mind. A pseudo double category has 2-morphisms shaped like:
-
-\[
-\begin{tikzpicture}[scale=1]
-\node (D) at (-4,0.5) {$A$};
-\node (E) at (-2,0.5) {$B$};
-\node (F) at (-4,-1) {$C$};
-\node (A) at (-2,-1) {$D$};
-\node (B) at (-3,-0.25) {$\Downarrow a$};
-\path[->,font=\scriptsize,>=angle 90]
-(D) edge node [above]{$M$}(E)
-(E) edge node [right]{$g$}(A)
-(D) edge node [left]{$f$}(F)
-(F) edge node [above]{$N$} (A);
-\end{tikzpicture}
-\]
-
-We call $A, B, C$ and $D$ \textbf{objects} or \textbf{0-cells}, $f$ and $g$ \textbf{vertical 1-morphisms}, $M$ and $N$ \textbf{horizontal 1-cells} and $a$ a \textbf{2-morphism}.
-Note that a vertical 1-morphism is a morphism between 0-cells and a 2-morphism is a morphism between horizontal 1-cells.
-We will denote both kinds of morphisms and horizontal 1-cells as a single arrow, namely `$\to$'.
-We follow the notation of Shulman \cite{Shul} with the following definitions.
-
-\begin{defn}
-A \textbf{pseudo double category} $\lD$, or $\textbf{double category}$ for short, consists of a category of objects $\bold{D_{0}}$ and a category of arrows $\bold{D_{1}}$ with the following functors
-\begin{center}
-$U\colon \bold{D_{0}} \to \bold{D_{1}}$\\
-$S,T \colon \bold{D_{1}} \rightrightarrows \bold{D_{0}}$\\
-$\odot \colon \bold{D_{1}} \times_{\bold{D_{0}}} \bold{D_{1}} \to \bold{D_{1}}$ (where the pullback is taken over $\bold{D_{1}} \xrightarrow[]{T} \bold{D_{0}} \xleftarrow[]{S} \bold{D_{1}}$) \\
-\end{center}
- such that \\
-\begin{center}
-$S(U_{A})=A=T(U_{A})$\\
-$S(M \odot N)=SN$\\
-$T(M \odot N)=TM$\\
-\end{center}
-equipped with natural isomorphisms
-\begin{center}
-
-$\alpha \colon (M \odot N) \odot P \xrightarrow{\sim} M \odot (N \odot P)$\\
-$\lambda \colon U_{B} \odot M \xrightarrow{\sim} M$\\
-$\rho \colon M \odot U_{A} \xrightarrow{\sim} M$
-
-\end{center}
-such that $S(\alpha), S(\lambda), S(\rho), T(\alpha), T(\lambda)$ and $T(\rho)$ are all identities and that the coherence axioms of a monoidal category are satisfied.
-Following the notation of Shulman, objects of $\bold{D_{0}}$ are called $\textbf{0-cells}$ and morphisms of $\bold{D_{0}}$ are called $\textbf{vertical 1-morphisms}$.
-Objects of $\bold{D_{1}}$ are called $\textbf{horizontal 1-cells}$ and morphisms of $\bold{D_{1}}$ are called $\textbf{2-morphisms}$.
-The morphisms of $\bold{D_{0}}$, which are vertical 1-morphisms, will be denoted $f \colon A \to C$ and we denote a 1-cell $M$ with $S(M)=A,T(M)=B$ by $M \colon A \to B$.
-Then a 2-morphism $a \colon M \to N$ of $\bold{D_{1}}$ with $S(a)=f,T(a)=g$ would look like:
-\[
-\begin{tikzpicture}[scale=1]
-\node (D) at (-4,0.5) {$A$};
-\node (E) at (-2,0.5) {$B$};
-\node (F) at (-4,-1) {$C$};
-\node (A) at (-2,-1) {$D$};
-\node (B) at (-3,-0.25) {$\Downarrow a$};
-\path[->,font=\scriptsize,>=angle 90]
-(D) edge node [above]{$M$}(E)
-(E) edge node [right]{$g$}(A)
-(D) edge node [left]{$f$}(F)
-(F) edge node [above]{$N$} (A);
-\end{tikzpicture}
-\]
-\end{defn}
-
-The key difference between a `strict' double category and a pseudo double category is that in a pseudo double category, horizontal composition is associative and unital only up to natural isomorphism.
-Equivalently, as a double category can be viewed as a category internal to $\bold{Cat}$, we can view a pseudo double category as a category `weakly' internal to $\bold{Cat}$.
-We will sometimes omit the word pseudo and simply say double category.
-
-\begin{defn}
-A 2-morphism where $f$ and $g$ are identities is called a \textbf{globular 2-morphism}.
-\end{defn}
-
-\begin{defn}
-Let $\lD$ be a pseudo double category.
-Then the $\textbf{horizontal bicategory}$ of $\lD$, which we denote as $H(\lD)$, is the bicategory consisting of objects of $\lD$, morphisms that are horizontal 1-cells of $\lD$ and 2-morphisms that are globular 2-morphisms of $\lD$.
-\end{defn}
-
-\begin{defn}
-  A \textbf{monoidal double category} is a double category equipped the following
-structure.
-\begin{enumerate}
-\item $\bold{D_{0}}$ and $\bold{D_{1}}$ are both monoidal categories.
-\item If $I$ is the monoidal unit of $\bold{D_{0}}$, then $U_I$ is the
-  monoidal unit of $\bold{D_{1}}$.
-\item The functors $S$ and $T$ are strict monoidal, i.e.\ $S(M\ten N)
-  = SM\ten SN$ and $T(M\ten N)=TM\ten TN$ and $S$ and $T$ also
-  preserve the associativity and unit constraints.
-\item We have globular isomorphisms
-  \[\chi \maps (M_1\ten N_1)\odot (M_2\ten N_2)\too[\sim] (M_1\odot M_2)\ten (N_1\odot N_2)\]
-  and
-  \[\mu\maps U_{A\ten B} \too[\sim] (U_A \ten U_B)\]
-  such that the following diagrams commute:
-		\item \label{diag:MonDblCat}
-			The following diagrams commute expressing the constraint data for the double functor $\otimes$.
-			\[
-			\begin{tikzpicture}
-				\node (A) at (0,3) {\footnotesize{
-							$((M_1\otimes N_1)\odot (M_2\otimes N_2)) \odot (M_3\otimes N_3)$}
-				};
-				\node (B) at (7,3) {\footnotesize{
-						$((M_1\odot M_2)\otimes (N_1\odot N_2)) \odot (M_3\otimes N_3) $}
-				};
-				\node (A') at (0,1.5) {\footnotesize{
-						$(M_1\otimes N_1)\odot ((M_2\otimes N_2) \odot (M_3\otimes N_3)) $}
-				};
-				\node (B') at (7,1.5) {\footnotesize{
-						$((M_1\odot M_2)\odot M_3) \otimes ((N_1\odot N_2)\odot N_3)$}
-				};
-				\node (A'') at (0,0) {\footnotesize{
-						$(M_1\otimes N_1) \odot ((M_2\odot M_3) \otimes (N_2\odot N_3))$}
-				};
-				\node (B'') at (7,0) {\footnotesize{
-						$(M_1\odot (M_2\odot M_3)) \otimes (N_1\odot (N_2\odot N_3))$}
-				};
-			%
-			\path[->,font=\scriptsize]
-				(A) edge node[left]{$\alpha$} (A')
-				(A') edge node[left]{$1 \odot \chi$} (A'')
-				(B) edge node[right]{$\chi$} (B')
-				(B') edge node[right]{$\alpha \otimes \alpha$} (B'')
-				(A) edge node[above]{$\chi \odot 1$} (B)
-				(A'') edge node[above]{$\chi$} (B'');
-		\end{tikzpicture}
-		\]
-		\[
-		\begin{tikzpicture}
-			\node (UL) at (0,1.5) {\footnotesize{
-					$(M\otimes N) \odot U_{C\otimes D}$}
-			};
-			\node (LL) at (0,0) {\footnotesize{
-					$M\otimes N$}
-			};
-			\node (UR) at (3.5,1.5) {\footnotesize{
-					$(M\otimes N)\odot (U_C\otimes U_D)$}
-			};
-			\node (LR) at (3.5,0) {\footnotesize{
-					$(M\odot U_C) \otimes (N\odot U_D)$}
-			};
-			%
-			\path[->,font=\scriptsize]
-				(UL) edge node[above]{$1 \odot \mu$} (UR) 
-				(UL) edge node[left]{$\rho$} (LL)
-				(LR) edge node[above]{$\rho \otimes \rho$} (LL)
-				(UR) edge node[right]{$\chi$} (LR);
-		\end{tikzpicture}
-		%
-		\quad
-		%
-		\begin{tikzpicture}
-			\node (UL) at (0,1.5) {\scriptsize{$U_{A\otimes B}\odot (M\otimes N)$}};
-			\node (LL) at (0,0) {\scriptsize{$M\otimes N$}};
-			\node (UR) at (3.5,1.5) {\scriptsize{$(U_A\otimes U_B)\odot (M\otimes N)$}};
-			\node (LR) at (3.5,0) {\scriptsize{$(U_A \odot M) \otimes (U_B\odot N)$}};
-			%
-			\path[->,font=\scriptsize]
-				(UL) edge node[above]{$\chi \odot 1$} (UR) 
-				(UL) edge node[left]{$\lambda$} (LL)
-				(LR) edge node[above]{$\lambda \otimes \lambda$} (LL)
-				(UR) edge node[right]{$\chi$} (LR);
-		\end{tikzpicture}
-		\]
-		%
-		\item The following diagrams commute expressing 
-		the associativity isomorphism for $\otimes$ is a transformation of double categories.
-		\[
-		\begin{tikzpicture}
-			\node (A) at (0,3) {\footnotesize{
-					$((M_1\otimes N_1)\otimes P_1) \odot ((M_2\otimes N_2)\otimes P_2)$}
-			};
-			\node (B) at (7,3) {\footnotesize{
-					$(M_1\otimes (N_1\otimes P_1)) \odot (M_2\otimes (N_2\otimes P_2))$}
-			};
-			\node (A') at (0,1.5) {\footnotesize{
-					$((M_1\otimes N_1) \odot (M_2\otimes N_2)) \otimes (P_1\odot P_2)$}
-			};
-			\node (B') at (7,1.5) {\footnotesize{
-					$(M_1\odot M_2) \otimes ((N_1\otimes P_1)\odot (N_2\otimes P_2))$}
-			};
-			\node (A'') at (0,0) {\footnotesize{
-					$((M_1\odot M_2) \otimes(N_1\odot N_2)) \otimes (P_1\odot P_2)$}
-			};
-			\node (B'') at (7,0) {\footnotesize{
-					$(M_1\odot M_2) \otimes ((N_1\odot N_2)\otimes (P_1\odot P_2))$}
-			};
-			%
-			\path[->,font=\scriptsize]
-				(A) edge node[left]{$\chi$} (A')
-				(A') edge node[left]{$\chi \otimes 1$} (A'')
-				(B) edge node[right]{$\chi$} (B')
-				(B') edge node[right]{$1 \otimes \chi$} (B'')
-				(A) edge node[above]{$\alpha \odot \alpha$} (B)
-				(A'') edge node[above]{$\alpha$} (B'');
-		\end{tikzpicture}
-		\]
-		\[
-		\begin{tikzpicture}
-			\node (A) at (0,3) {\footnotesize{$U_{(A\otimes B)\otimes C}$}};
-			\node (B) at (4,3) {\footnotesize{$U_{A\otimes (B\otimes C)} $}};
-			\node (A') at (0,1.5) {\footnotesize{$U_{A\otimes B} \otimes U_C $}};
-			\node (B') at (4,1.5) {\footnotesize{$U_A\otimes U_{B\otimes C}$}};
-			\node (A'') at (0,0) {\footnotesize{$(U_A\otimes U_B)\otimes U_C$}};
-			\node (B'') at (4,0) {\footnotesize{$U_A\otimes (U_B\otimes U_C) $}};
-			%
-			\path[->,font=\scriptsize]
-				(A) edge node[left]{$\mu$} (A')
-				(A') edge node[left]{$\mu \otimes 1$} (A'')
-				(B) edge node[right]{$\mu$} (B')
-				(B') edge node[right]{$1 \otimes \mu$} (B'')
-				(A) edge node[above]{$U_{\alpha}$} (B)
-				(A'') edge node[above]{$\alpha$} (B'');
-		\end{tikzpicture}
-		\]
-		\item The following diagrams commute expressing that 
-		the unit isomorphisms for $\otimes$ are transformations of double categories. 
-		\[
-		\begin{tikzpicture}
-			\node (A) at (0,1.5) {\footnotesize{$(M\otimes U_I)\odot (N\otimes U_I)$}};
-			\node (A') at (0,0) {\footnotesize{$M\odot N $}};
-			\node (B) at (4,1.5) {\footnotesize{$(M\odot N)\otimes (U_I \odot U_I) $}};
-			\node (B') at (4,0) {\footnotesize{$(M\odot N)\otimes U_I $}};
-			%
-			\path[->,font=\scriptsize]
-				(A) edge node[left]{$r \odot r$} (A')
-				(A) edge node[above]{$\chi$} (B)
-				(B) edge node[right]{$1 \otimes \rho$} (B')
-				(B') edge node[above]{$r$} (A');
-		\end{tikzpicture}
-		%
-		\quad
-		%
-		\begin{tikzpicture}
-			\node (A) at (0,0.75) {\footnotesize{$U_{A\otimes I} $}};
-			\node (B) at (1.5,1.5) {\footnotesize{$U_A\otimes U_I $}};
-			\node (B') at (1.5,0) {\footnotesize{$U_A$}};
-			%
-			\path[->,font=\scriptsize]
-				(A) edge node[above]{$\mu$} (B)
-				(A) edge node[below]{$U_{r}$} (B')
-				(B) edge node[right]{$r$} (B');
-		\end{tikzpicture}
-		\]
-		%
-		%
-		%
-		%
-		\[
-		\begin{tikzpicture}
-			\node (A) at (0,1.5) {\footnotesize{$(U_I\otimes M)\odot (U_I\otimes N)$}};
-			\node (A') at (0,0) {\footnotesize{$M\odot N$}};
-			\node (B) at (4,1.5) {\footnotesize{$(U_I \odot U_I) \otimes (M\odot N)$}};
-			\node (B') at (4,0) {\footnotesize{$U_I\otimes (M\odot N) $}};
-			%
-			\path[->,font=\scriptsize]
-				(A) edge node[left]{$\ell \odot \ell$} (A')
-				(A) edge node[above]{$\chi$} (B)
-				(B) edge node[right]{$\lambda \otimes 1$} (B')
-				(B') edge node[above]{$\ell$} (A');
-		\end{tikzpicture}
-		%
-		\quad
-		\begin{tikzpicture}
-			\node (A) at (0,0.75) {\footnotesize{$U_{I\otimes A}$}};
-			\node (B) at (1.5,1.5) {\footnotesize{$U_I\otimes U_A$}};
-			\node (B') at (1.5,0) {\footnotesize{$U_A$}};
-			%
-			\path[->,font=\scriptsize]
-				(A) edge node[above]{$\mu$} (B)
-				(A) edge node[below]{$U_{\ell}$} (B')
-				(B) edge node[right]{$\ell$} (B');
-		\end{tikzpicture}
-		\]
-		\newcounter{mondbl}
-		\setcounter{mondbl}{\value{enumi}}
-	\end{enumerate}
-	A \textbf{braided monoidal double category} 
-	is a monoidal double category 
-	such that:
-	\begin{enumerate}
-		\setcounter{enumi}{\value{mondbl}}
-		\item $\dblcat{D}_{0}$ and $\dblcat{D}_{1}$ are braided monoidal categories.
-		\item The functors $S$ and $T$ are strict braided monoidal functors.
-		\item The following diagrams commute expressing that the braiding is a transformation of double categories.
-		\[
-		\begin{tikzpicture}
-			\node (A) at (0,1.5) {\footnotesize{$(M_1 \odot M_2) \otimes (N_1 \odot N_2)$}};
-			\node (A') at (0,0) {\footnotesize{$(M_1\otimes N_1) \odot (M_2\otimes N_2)$}};
-			\node (B) at (5,1.5) {\footnotesize{$(N_1\odot N_2) \otimes (M_1 \odot M_2)$}};
-			\node (B') at (5,0) {\footnotesize{$(N_1 \otimes M_1) \odot (N_2 \otimes M_2)$}};
-			%
-			\path[->,font=\scriptsize]
-				(A) edge node[left]{$\chi$} (A')
-				(A) edge node[above]{$\beta$} (B)
-				(B) edge node[right]{$\chi$} (B')
-				(A') edge node[above]{$\beta \odot \beta$} (B');
-		\end{tikzpicture}
-		%
-		\quad
-		%
-		\begin{tikzpicture}
-			\node (A) at (0,1.5) {\footnotesize{$U_A \otimes U_B$}};
-			\node (A') at (0,0) {\footnotesize{$U_B\otimes U_A$}};
-			\node (B) at (2,1.5) {\footnotesize{$U_{A\otimes B} $}};
-			\node (B') at (2,0) {\footnotesize{$U_{B\otimes A}$}};
-			%
-			\path[->,font=\scriptsize]
-				(A) edge node[left]{$\beta$} (A')
-				(B) edge node[above]{$\mu$} (A)
-				(B) edge node[right]{$U_\beta$} (B')
-				(B') edge node[above]{$\mu$} (A');
-		\end{tikzpicture}
-		\]
-		\setcounter{mondbl}{\value{enumi}}
-	\end{enumerate}
-	Finally, a \textbf{symmetric monoidal double category} 
-	is a braided monoidal double category $\mathbb{D}$ such that:
-	\begin{enumerate}
-		\setcounter{enumi}{\value{mondbl}}
-		\item $\dblcat{D}_{0}$ and $\dblcat{D}_{1}$ are symmetric monoidal.
-	\end{enumerate}
-\end{defn}
-
-\begin{defn}\label{def:companion}
-  Let \lD\ be a double category and $f\maps A\to B$ a vertical
-  1-morphism.  A \textbf{companion} of $f$ is a horizontal 1-cell
-  $\fhat\maps A\to B$ together with 2-morphisms
-	\[
-	\raisebox{-0.5\height}{
-	\begin{tikzpicture}
-		\node (A) at (0,1) {$A$};
-		\node (B) at (1,1) {$B$};
-		\node (A') at (0,0) {$B$};
-		\node (B') at (1,0) {$B$};
-		%
-		\path[->,font=\scriptsize,>=angle 90]
-			(A) edge node[above]{$\widehat{f}$} (B)
-			(A) edge node[left]{$f$} (A')
-			(B) edge node[right]{$1$} (B')
-			(A') edge node[below]{$U_B$} (B');
-		%
-	%	\draw (0.5,.925) -- (0.5,1.075);
-	%	\draw (0.5,-.075) -- (0.5,.075);
-		\node () at (0.5,0.5) {\scriptsize{$\Downarrow$}};
-	\end{tikzpicture}
-	}
-	%
-	\quad \text{ and } \quad
-	%
-	\raisebox{-0.5\height}{
-	\begin{tikzpicture}
-		\node (A) at (0,1) {$A$};
-		\node (B) at (1,1) {$A$};
-		\node (A') at (0,0) {$A$};
-		\node (B') at (1,0) {$B$};
-		%
-		\path[->,font=\scriptsize,>=angle 90]
-			(A) edge node[above]{$U_A$} (B)
-			(A) edge node[left]{$1$} (A')
-			(B) edge node[right]{$f$} (B')
-			(A') edge node[below]{ $\widehat{f}$} (B');
-		%
-	%	\draw (0.5,.925) -- (0.5,1.075);
-	%	\draw (0.5,-.075) -- (0.5,.075);
-		\node () at (0.5,0.5) {\scriptsize{$\Downarrow$}};
-	\end{tikzpicture}
-	}
-	\]
-  such that the following equations hold.
-	\begin{equation}
-	\label{eq:CompanionEq}
-	\raisebox{-0.5\height}{
-	\begin{tikzpicture}
-		\node (A) at (0,2) {$A$};
-		\node (B) at (1.1,2) {$A$};
-		\node (A') at (0,1) {$A$};
-		\node (B') at (1.1,1) {$B$};
-		\node (A'') at (0,0) {$B$};
-		\node (B'') at (1.1,0) {$B$};
-		%
-		\path[->,font=\scriptsize,>=angle 90]
-			(A) edge node[left]{$1$} (A')
-			(A') edge node[left]{$f$} (A'')
-			(B) edge node[right]{$f$} (B')
-			(B') edge node[right]{$1$} (B'')
-			(A) edge node[above]{$U_A$} (B)
-			(A') edge  (B')
-			(A'') edge node[below]{$U_B$} (B'');
-		%
-	%	\draw (0.5,1.925) -- (0.5,2.075);
-		\draw[line width=2mm,white] (0.5,.925) -- (0.5,1.075);
-	%	\draw (0.5,-.075) -- (0.5,.075);
-		\node () at (0.5,0.5) {\scriptsize{$\Downarrow$}};
-		\node () at (0.5,1.5) {\scriptsize{$\Downarrow$}};
-		\node () at (0.5,1) {\scriptsize $\widehat{f}$};
-	\end{tikzpicture}
-	}
-	%
-	\raisebox{-0.5\height}{=}
-	%
-	\raisebox{-0.5\height}{
-	\begin{tikzpicture}
-		\node (A) at (0,1) {$A$};
-		\node (B) at (1,1) {$A$};
-		\node (A') at (0,0) {$B$};
-		\node (B') at (1,0) {$B$};
-		%
-		\path[->,font=\scriptsize,>=angle 90]
-		(A) edge node[left]{$f$} (A')
-		(B) edge node[right]{$f$} (B')
-		(A) edge node[above]{$U_A$} (B)
-		(A') edge node[below]{$U_B$} (B');
-		%
-		%\draw (0.5,.925) -- (0.5,1.075);
-		%\draw (0.5,-.075) -- (0.5,.075);
-		\node () at (0.5,0.5) {\scriptsize{$\Downarrow U_f$}};
-	\end{tikzpicture}
-	}
-	%
-	\raisebox{-0.5\height}{\text{   and   }}
-	%
-	\raisebox{-0.5\height}{
-	\begin{tikzpicture}
-		\node (A) at (0,1) {$A$};
-		\node (A') at (0,0) {$A$};
-		\node (B) at (1,1) {$A$};
-		\node (B') at (1,0) {$B$};
-		\node (C) at (2,1) {$B$};
-		\node (C') at (2,0) {$B$};
-		%
-		\path[->,font=\scriptsize,>=angle 90]
-			(A) edge node[left]{$1$} (A')
-			(B) edge node[left]{$f$} (B')
-			(C) edge node[right]{$1$} (C')
-			(A) edge node[above]{$U_A$} (B)
-			(B) edge node[above]{$\widehat{f}$} (C)
-			(A') edge node[below]{$\widehat{f}$} (B')
-			(B') edge node[below]{$U_B$} (C');
-		%
-	%	\draw (1.5,0.925) -- (1.5,1.075);
-	%	\draw (1.5,0.925) -- (1.5,1.075);
-	%	\draw (0.5,.925) -- (0.5,1.075);
-	%	\draw (0.5,-.075) -- (0.5,.075);
-		\node () at (0.5,0.5) {\scriptsize{$\Downarrow$}};
-		\node () at (1.5,0.5) {\scriptsize{$\Downarrow$}};
-	\end{tikzpicture}
-	}
-	%
-	\raisebox{-0.5\height}{=}
-	%
-	\raisebox{-0.5\height}{
-	\begin{tikzpicture}
-		\node (A) at (0,1) {$A$};
-		\node (B) at (1,1) {$B$};
-		\node (A') at (0,0) {$A$};
-		\node (B') at (1,0) {$B$};
-		%
-		\path[->,font=\scriptsize,>=angle 90]
-			(A) edge node[left]{$1$} (A')
-			(B) edge node[right]{$1$} (B')
-			(A) edge node[above]{$\widehat{f}$} (B)
-			(A') edge node[below]{$\widehat{f}$} (B');
-		%
-	%	\draw (0.5,.925) -- (0.5,1.075);
-	%	\draw (0.5,-.075) -- (0.5,.075);
-		\node () at (0.5,0.5) {\scriptsize{$\Downarrow \id_{\widehat{f}}$}};
-	\end{tikzpicture}
-	}
-	\end{equation}
-  A \textbf{conjoint} of $f$, denoted $\fchk \maps B\to A$, is a
-  companion of $f$ in the double category $\lD^{h\cdot\mathrm{op}}$
-  obtained by reversing the horizontal 1-cells, but not the vertical
-  1-morphisms, of \lD.
-\end{defn}
-\noindent
-In a pseudo double category, the second equation above requires an insertion of unit isomorphisms to make sense due to horizontal composition only holding up to isomorphism.
-\begin{defn}
-  We say that a double category is \textbf{fibrant} if every vertical
-  1-morphism has both a companion and a conjoint and \define{isofibrant} if every vertical 1-isomorphism has both a companion and a conjoint.
-\end{defn}
-
-%\section{Outline for paper}
-%\begin{enumerate}
-%\item{Need to build a symmetric monoidal decorated cospan category $F$Cospan$(\mathrm{A})$ from a lax symmetric monoidal pseudofunctor $F \colon \mathrm{A} \to \bold{Cat}$.}
-%\item{Need to view $F$Cospan$(\mathrm{A})$ as a one object bicategory and then a one object pseudo double category.}
-%\item{Deloop the symmetric monoidal $(\bold{Cat,\times})$ into a one object bicategory and then view this as a one object pseudo double category in which there is only an identity for vertical 1-morphisms and the objects of $\bold{Cat}$ appear as horizontal 1-cells, and morphisms of $\bold{Cat}$ as 2-morphisms.
-Denote this pseudo double category as $\mathbb{C}\bold{at}$.}
-%\item{Define a symmetric monoidal lax double functor $\mathbb{F} \colon$ $F$Cospan$(\mathrm{A}) \to \mathbb{C} \bold{at}$.}
-%\item{Define a symmetric monoidal oplax double functor $\mathbb{I} \colon 1 \to \mathbb{C} \bold{at}$ where $1$ is the one object double category.}
-%\item{Obtain a symmetric monoidal double category of decorated cospans $\mathbb{F}$Cospan$(\mathrm{A})$ as a comma object from the cospan $1 \xrightarrow{ \mathbb{I} } \mathbb{C}\bold{at} \xleftarrow{ \mathbb{F} } F\textrm{Cospan}(\mathrm{A})$ in the 2-category $\mathbb{DBL}$ of monoidal double categories and lax functors.
-(Note that the functor $\mathbb{I} \colon 1 \to \mathbb{C}\bold{at}$ is actually pseudo, and hence both lax and oplax.)}
-%\item{Figure out what a (double?) equivalence of symmetric monoidal double categories is.}
-%\item{Show that $_F \textrm{Csp}(\mathrm{A})$ is equivalent to $\mathbb{F}\textrm{Cospan}(\mathrm{A})$ as symmetric monoidal double categories, where $_F \textrm{Csp}(\mathrm{A})$ is the structured cospan double category that comes from the double category Csp$(\mathrm{A})$ and the functor $F \colon \mathrm{A} \to \bold{Cat}$.}
-%\end{enumerate}
+In the fifth section we briefly review another compositional framework which uses cospans equipped with extra structure due to the first two authors, namely `structured cospans' and prove that the double categorical versions of decorated cospans and structured cospans are equivalent, and in the final section, we present a few examples that can be realized with either framework and discuss the realized equivalences.
 
@@
 In this section we build the symmetric monoidal double category mentioned in the introduction. 
-A double category $\mathbb{D}=(\mathbb{D}_0,\mathbb{D}_1)$ consists of a category of objects $\mathbb{D}_0$ and a category of arrows $\mathbb{D}_1$.
-We obtain $\mathbb{D}$ as a comma object in the 2-category $\bold{Dbl}$ of monoidal double categories, monoidal double functors and monoidal double transformations by obtaining each of $\mathbb{D}_0$ and $\mathbb{D}_1$ as comma categories in $\bold{Cat}$.
-
-If $\mathrm{A}$ is a category with finite colimits, there is a well-known symmetric monoidal pseudo double category $\mathbb{C} \textnormal{ospan}(\mathrm{A})$ which has:
+\textbf{Add more here.}
+\begin{thm}
+Let $\mathrm{A}$ be a category with finite colimits and $F \colon \mathrm{A} \to \bold{Cat}$ a lax monoidal pseudofunctor.
+Then there exists a double category $\mathbb{F} \textnormal{Cospan}(\mathrm{A}) \coloneqq (\mathbb{G}/ \mathbb{F})$ which has:
 \begin{enumerate}
@@
 \item{vertical 1-morphisms as morphisms of $\mathrm{A}$,}
-\item{horizontal 1-cells as cospans in $\mathrm{A}$, and}
-\item{2-morphisms as maps of cospans in $\mathrm{A}.$
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$c_1$};
-\node (B) at (1,0) {$d$};
-\node (C) at (2,0) {$c_2$};
-\node (A') at (0,-1) {$c_1^\prime$};
-\node (B') at (1,-1) {$d^\prime$};
-\node (C') at (2,-1) {$c_2^\prime$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$$} (B)
-(C) edge node[above]{$$} (B)
-(A') edge node[above]{$$} (B')
-(C') edge node[above]{$$} (B')
-(A) edge node [above]{$$} (A')
-(B) edge node [above]{$$} (B')
-(C) edge node [above]{$$} (C');
-\end{tikzpicture}
-\]}
-\end{enumerate}
-
-The symmetric monoidal category $(\bold{Cat},\times,1)$ consisting of categories and functors can naturally be viewed as a one object bicategory using a standard level shift.
-This one object bicategory, which we denote as $\textnormal{BD}(\bold{Cat})$, will have:
-\begin{enumerate}
-\item{one object $\{ \star \}$,}
-\item{objects of $\bold{Cat}$ as morphisms, and}
-\item{morphisms of $\bold{Cat}$ as 2-morphisms.}
-\end{enumerate}
-We can then view this one object bicategory as a one object pseudo double category $\mathbb{B}\textnormal{D}(\bold{Cat})$, which will have:
-\begin{enumerate}
-\item{one object $\{ \star \}$,}
-\item{only an identity for vertical 1-morphisms,}
-\item{morphisms of $\textnormal{BD}(\bold{Cat})$, which are objects of $\bold{Cat}$, as horizontal 1-cells, and}
-\item{2-morphisms of $\textnormal{BD}(\bold{Cat})$, which are morphisms of $\bold{Cat}$, as 2-morphisms.}
-\end{enumerate}
-This one object pseudo double category $\mathbb{B}\textnormal{D}(\bold{Cat})$ will serve as the apex of a cospan:
-
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$1$};
-\node (B) at (1,1) {$\mathbb{B}\textnormal{D}(\bold{Cat})$};
-\node (C) at (2,0) {$\mathbb{C}\textnormal{ospan}(\mathrm{A})$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$\mathbb{G}$} (B)
-(C) edge node[above]{$\mathbb{F}$} (B);
-\end{tikzpicture}
-\]
-which we will use to construct a comma object in $\bold{Dbl}$, the 2-category of double categories, double functors and double transformations.
-In order for the double comma object to exist in $\bold{Dbl}$, namely a pseudo comma double category, it is necessary that $\mathbb{F}$ and $\mathbb{G}$ be lax and oplax double functors, respectively.
-This was made known to the first author by Shulman.
-This result is true in general, but we will only prove it for this particular case that we are interested in.
-
-The oplax double functor $\mathbb{G} \colon 1 \to \mathbb{B}\textnormal{D}(\bold{Cat})$ is trivially defined modulo $\mathbb{G}$ mapping the identity horizontal 1-cell to the monoidal unit of $\mathbb{B}\textnormal{D}(\bold{Cat})$ which is given by the terminal category $1$.
-The category $\mathrm{A}$ has finite colimits and can be viewed as a 2-category with only trivial 2-morphisms.
-Then from a symmetric lax monoidal pseudofunctor $F \colon \mathrm{A} \to \bold{Cat}$, we can obtain symmetric lax monoidal lax double functor $\mathbb{F} \colon \mathbb{C}\textnormal{ospan}(\mathrm{A}) \to \mathbb{B}\textnormal{D}(\bold{Cat})$ which is defined as the pseudofunctor $F$ on horizontal 1-cells and 2-morphisms; note that $\mathbb{B}\textnormal{D}(\bold{Cat})$ has a single object and an identity vertical 1-morphism.
-Thus $\mathbb{F}$ will map a cospan in $\mathrm{A}$: $$a \rightarrow c \leftarrow b$$ to $F(c) \in \bold{Cat}$ and
-\begin{thm}
-Let $F \colon \mathrm{A} \to \bold{Cat}$ be a symmetric lax monoidal pseudofunctor.
-Then there exists a symmetric (lax) monoidal lax double functor $\mathbb{F} \colon \mathbb{C}\textnormal{ospan}(\mathrm{A}) \to \mathbb{B}\textnormal{D}(\bold{Cat})$ which is defined:
-\begin{enumerate}
-\item{trivially on objects as $\mathbb{B}\textnormal{D}(\bold{Cat})$ only has a single object,}
-\item{trivially on vertical 1-morphisms as $\mathbb{B}\textnormal{D}(\bold{Cat})$ only has a single identity vertical 1-morphism,}
-\item{as the pseudofunctor $F \colon \mathrm{A} \to \bold{Cat}$ on horizontal 1-cells, meaning that $$(c_1 \xrightarrow{i} c \xleftarrow{o} c_2) \mapsto F(c)$$ and}
-\item{as the pseudofunctor $F \colon \mathrm{A} \to \bold{Cat}$ on 2-morphisms, meaning that 
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$c_1$};
+\item{horizontal 1-cells as pairs:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$a$};
 \node (B) at (1,0) {$c$};
-\node (C) at (2,0) {$c_2$};
-\node (A') at (0,-1) {$c_1^\prime$};
-\node (B') at (1,-1) {$c^\prime$};
-\node (C') at (2,-1) {$c_2^\prime$};
-\node (D) at (3,-0.5) {$\mapsto$};
-\node (E) at (4,0) {$F(c)$};
-\node (E') at (4,-1) {$F(c^\prime)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$$} (B)
-(C) edge node[above]{$$} (B)
-(A') edge node[above]{$$} (B')
-(C') edge node[above]{$$} (B')
-(A) edge node [above]{$$} (A')
-(B) edge node [left]{$f$} (B')
-(C) edge node [above]{$$} (C')
-(E) edge node [right] {$F(f)$} (E');
-\end{tikzpicture}
-\]
-}
-\end{enumerate}
-\end{thm}
-\begin{proof}
-The functor $\mathbb{F} \colon \mathbb{C}\textnormal{ospan}(\mathrm{A}) \to \mathbb{B} \textnormal{D}(\bold{Cat})$ is defined trivially on objects and vertical 1-morphisms as the object category of $\mathbb{B}\textnormal{D}(\bold{Cat})$ is trivial.
-Given two composable horizontal 1-cells $M$ and $N$ in $\mathbb{C}\textnormal{ospan}(\mathrm{A})$ given respectively by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$c_1$};
-\node (B) at (1,1) {$c$};
-\node (C) at (2,0) {$c_2$};
-\node (D) at (3,0) {$c_2$};
-\node (E) at (4,1) {$c^\prime$};
-\node (F) at (5,0) {$c_3$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i$} (B)
-(C) edge node[above]{$o$} (B)
-(D) edge node[above]{$i^\prime$} (E)
-(F) edge node[above]{$o^\prime$} (E);
-\end{tikzpicture}
-\]
-we have that $\mathbb{F}(M)=F(c)$ and $\mathbb{F}(N)=F(c^\prime)$. The composite $M \odot N$ is given by the pushout:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$c_1$};
-\node (B) at (1,1) {$c+_{c_2} c^\prime$};
-\node (C) at (2,0) {$c_3$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[left]{$j \psi_c i$} (B)
-(C) edge node[right]{$j \psi_{c^\prime} o$} (B);
-\end{tikzpicture}
-\]
-and so $\mathbb{F}(M \odot N)=F(c+_{c_2} c^\prime)$.
-The comparison constraint globular 2-morphism $\mathbb{F}_{M,N} \colon \mathbb{F}(M) \odot \mathbb{F}(N) \to \mathbb{F}(M \odot N)$ is then given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$\star$};
-\node (B) at (1.5,0) {$\star$};
-\node (A') at (0,-1.5) {$\star$};
-\node (B') at (1.5,-1.5) {$\star$};
-\node (C) at (.75,-.75) {$\Downarrow F(j) \phi_{c,c^\prime}$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$F(c) \times F(c^\prime)$} (B)
-(A') edge node[above]{$F(c+_{c_2} c^\prime)$} (B')
-(A) edge node [left]{$\id$} (A')
-(B) edge node [right]{$\id$} (B');
-\end{tikzpicture}
-\]
-where $\phi_{c,c^\prime} \colon F(c) \times F(c^\prime) \to F(c+c^\prime)$ is one of the natural transformations of the symmetric lax monoidal pseudo functor $F$ and $j \colon c+c^\prime \to c+_{c_2}c^\prime$ is the natural map from the coproduct to the pushout.
-
-Given an object $c$ in $\mathbb{C}\textnormal{ospan}(\mathrm{A})$, $\mathbb{F}(c)$ is the single object $\star$ of $\mathbb{B}\textnormal{D}(\bold{Cat})$, and so $1_{\mathbb{F}(c)}$ is the identity horizontal 1-cell on $\star$.
-Similarly, $1_c$ is the identity cospan on $c$ and then $\mathbb{F}(1_c)=F(c)$.
-The identity comparison is then the globular 2-morphism $\mathbb{F}_c \colon 1_{\mathbb{F}(c)} \to \mathbb{F}(1_c)$ given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$\star$};
-\node (B) at (1.5,0) {$\star$};
-\node (A') at (0,-1.5) {$\star$};
-\node (B') at (1.5,-1.5) {$\star$};
-\node (C) at (.75,-.75) {$\Downarrow$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$$} (B)
-(A') edge node[above]{$F(c)$} (B')
-(A) edge node [left]{$\id$} (A')
-(B) edge node [right]{$\id$} (B');
-\end{tikzpicture}
-\]
-\textbf{Finish this...}
-\end{proof}
-\begin{prop}
-Let $1$ denote the trivial double category with a single object and only identities.
-Then there exists a symmetric lax monoidal oplax double functor $\mathbb{G} \colon \mathbf{1} \to \mathbb{B}\textnormal{D}(\bold{Cat})$ which is defined:
-\begin{enumerate}
-\item{trivially on objects, as both $1$ and $\mathbb{B} \textnormal{D}(\bold{Cat})$ have a single object,}
-\item{trivially on vertical 1-morphisms, as both $1$ and $\mathbb{B} \textnormal{D}(\bold{Cat})$ only have a single identity vertical 1-morphism,}
-\item{the identity horizontal 1-cell of $1$ maps to the monoidal unit of $(\mathbb{B}\textnormal{D}(\bold{Cat}),\times, 1)$, which is the terminal category $1$ with a single object and identity morphism, and}
-\item{the identity 2-morphism maps to the identity functor $! \colon 1 \to 1$ on the terminal category.}
-\end{enumerate}
-\end{prop}
-We recall the definition of \emph{comma category} which will be crucial for the next step.
-\begin{defn}
-Let $f \colon \textbf{C} \to \textbf{E}$ and $g \colon \textbf{D} \to \textbf{E}$ be functors with a common codomain.
-Then the $\textbf{comma category}$ determined by $f$ and $g$ is the category $(f/g)$ whose:
-\begin{enumerate}
-\item{objects are triples $(c,d,\alpha)$ where $c \in \textbf{C}, d \in \textbf{D}$ and $\alpha \colon f(c) \to g(d)$ is a morphism in $\textbf{E}$, and whose}
-\item{morphisms from $(c_{1},d_{1},\alpha_{1})$ to $(c_{2},d_{2},\alpha_{2})$ are pairs $(\beta, \gamma)$ where $\beta \colon c_{1} \to c_{2}$ and $\gamma \colon d_{1} \to d_{2}$ are morphisms in $\textbf{C}$ and $\textbf{D}$, respectively, such that the following diagram commutes}
-\end{enumerate}
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (1,1) {$f(c_{1})$};
-\node (B) at (2,1) {$f(c_{2})$};
-\node (A') at (1,0) {$g(d_{1})$};
-\node (B') at (2,0) {$g(d_{2})$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$f(\beta)$} (B)
-(A') edge node[above]{$g(\gamma)$} (B')
-(A) edge node[left]{$\alpha_{1}$} (A')
-(B) edge node[right]{$\alpha_{2}$} (B');
-\end{tikzpicture}
-\]
-\end{defn}
-\begin{defn}
-Let $f \colon \textbf{C} \to \textbf{E}$ and $g \colon \textbf{D} \to \textbf{E}$ be pseudofunctors between bicategories with a common codomain.
-Then the $\textbf{(weak) comma category}$ determined by $f$ and $g$ is the category $(f/g)$ whose:
-\begin{enumerate}
-\item{objects are triples $(c,d,\alpha)$ where $c \in \textbf{C}, d \in \textbf{D}$ and $\alpha \colon f(c) \to g(d)$ is a morphism in $\textbf{E}$, and whose}
-\item{morphisms from $(c_{1},d_{1},\alpha_{1})$ to $(c_{2},d_{2},\alpha_{2})$ are triples $(\beta, \gamma, \iota)$ where $\beta \colon c_{1} \to c_{2}$ and $\gamma \colon d_{1} \to d_{2}$ are morphisms in $\textbf{C}$ and $\textbf{D}$, respectively and $\iota$ is a 2-morphism in $\bold{E}$, such that the following diagram commutes up to the 2-morphism $\iota$:}
-\end{enumerate}
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (1,1) {$f(c_{1})$};
-\node (B) at (2,1) {$f(c_{2})$};
-\node (A') at (1,0) {$g(d_{1})$};
-\node (B') at (2,0) {$g(d_{2})$};
-\node (C) at (1.5,0.5) {$\iota \Swarrow$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$f(\beta)$} (B)
-(A') edge node[above]{$g(\gamma)$} (B')
-(A) edge node[left]{$\alpha_{1}$} (A')
-(B) edge node[right]{$\alpha_{2}$} (B');
-\end{tikzpicture}
-\]
-\end{defn}
-Using this definition we want to construct a `pseudo comma double category' from the lax double functor $\mathbb{F} \colon \mathbb{C}\textnormal{ospan}(\mathrm{A}) \to \mathbb{B} \textnormal{D}(\bold{Cat})$ and the oplax double functor $\mathbb{G} \colon 1 \to \mathbb{B}\textnormal{D}(\bold{Cat})$.
-First, we define how this pseudo comma double category $(\mathbb{G} / \mathbb{F}) \coloneqq \mathbb{F}\textnormal{Cospan}(\mathrm{A})$ is obtained.
-\textbf{Should this be a proposition or a definition? Ask Dr. Baez and Christina for their opinions.}
-\begin{defn}
-Let $\mathbb{G} \colon \lC \to \lE$ be an oplax double functor and $\mathbb{F} \colon \lD \to \lE$ be a lax double functor where $\lC = (\mathrm{A}_{0},\mathrm{A}_{1}), \lD = (\bold{D}_{0}, \bold{D}_{1})$ and $\lE = (\bold{E}_{0}, \bold{E}_{1})$ are pseudo  double categories with $\mathrm{A}_{0}, \mathrm{A}_{1}$ the category of objects and category of arrows of the double category $\lC$, respectively, and likewise for $\bold{D}_{0}, \bold{D}_{1}, \bold{E}_{0}$ and $\bold{E}_{1}$.
-Then the \define{pseudo comma double category} determined by the double functors $\mathbb{G}$ and $\mathbb{F}$ is the pseudo double category $(\mathbb{G} / \mathbb{F})$ consisting of a category of objects $(\mathbb{G} / \mathbb{F})_{0}$ and category of arrows $(\mathbb{G} / \mathbb{F})_{1}$ where the category of objects $(\mathbb{G} / \mathbb{F})_0$ is the comma category obtained from the functors $\mathbb{G}_0 \colon \mathrm{A}_{0} \to \bold{E}_{0}$ and $\mathbb{F}_0 \colon \bold{D}_{0} \to \bold{E}_{0}$ and $(\mathbb{G} / \mathbb{F})_1$ is the comma category obtained from the functors $\mathbb{G}_{1} \colon \mathrm{A}_{1} \to \bold{E}_{1}$ and $\mathbb{F}_1 \colon \bold{D}_{1} \to \bold{E}_{1}$.
-\end{defn}
-\begin{thm}
-Let $\mathbb{G} \colon 1 \to \mathbb{B}\textnormal{D}(\bold{Cat})$ be the oplax double functor previously defined and let $\mathbb{F} \colon \mathbb{F}\textnormal{Cospan}(\mathrm{A}) \to \mathbb{B}(\bold{Cat})$ be the lax double functor previously defined.
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$1$};
-\node (B) at (1,1) {$\mathbb{B}\textnormal{D}(\bold{Cat})$};
-\node (C) at (2,0) {$\mathbb{C}\textnormal{ospan}(\mathrm{A})$};
-\node (D) at (1,-1) {$(\mathbb{G} / \mathbb{F})$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$\mathbb{G}$} (B)
-(C) edge node[above]{$\mathbb{F}$} (B)
-(D) edge node [below] {$p$} (A)
-(D) edge node [below] {$q$} (C);
-\end{tikzpicture}
-\]
-Then there exists a category $(\mathbb{G} / \mathbb{F})_0 \coloneqq (\mathbb{G}_0 / \mathbb{F}_0)$ obtained as a comma category from the functors $\mathbb{F}_0 \colon \mathbb{C}\textnormal{ospan}(\mathrm{A})_0 \to \mathbb{B}\textnormal{D}(\bold{Cat})_0$ and $\mathbb{G}_0 \colon 1 \to \mathbb{B}\textnormal{D}(\bold{Cat})_0$ which has:
-\begin{enumerate}
-\item{objects as those of $\mathrm{A}$ and}
-\item{morphisms as those of $\mathrm{A}$,}
-\end{enumerate}
-and there exists a category $(\mathbb{G} / \mathbb{F})_1 \coloneqq (\mathbb{G}_1 / \mathbb{F}_1)$ obtained as a comma category from the functors $\mathbb{F}_1 \colon \mathbb{C}\textnormal{ospan}(\mathrm{A})_1 \to \mathbb{B}\textnormal{D}(\bold{Cat})_1$ and $\mathbb{G}_1 \colon 1 \to \mathbb{B}\textnormal{D}(\bold{Cat})_1$ which has:
-\begin{enumerate}
-\item{objects as $F$-decorated cospans of $\mathrm{A}$, which are pairs:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a$};
-\node (B) at (1,1) {$c$};
 \node (C) at (2,0) {$b$};
-\node (D) at (3,0.5) {$d \in F(c)$};
+\node (D) at (3,0) {$d \in F(c)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 and}
-\item{morphisms as maps of cospans of $\mathrm{A}$:
+\item{2-morphisms as maps of cospans in $\mathrm{A}$
 \[
@@
 \]
-together with a morphism $\iota \colon F(h)(d) \to d^\prime$ in $F(c^\prime)$.
- }
+together with a morphism $\iota \colon F(h)(d) \to d^\prime$ in $F(c^\prime)$.}
 \end{enumerate}
@@
 \begin{proof}
-The category $(\mathbb{G} / \mathbb{F})_0$ will be the comma category obtained from the following cospan:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$1$};
-\node (B) at (1,1) {$\mathbb{B}\textnormal{D}(\bold{Cat})_0$};
-\node (C) at (2,0) {$\mathbb{C}\textnormal{ospan}(\mathrm{A})_0=\mathrm{A}$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$\mathbb{G}_0$} (B)
-(C) edge node[above]{$\mathbb{F}_0$} (B);
-\end{tikzpicture}
-\]
-Thus $(\mathbb{G} / \mathbb{F})_0$ will be the comma category which has objects given by triples $(\star,c,\alpha \colon \mathbb{G}(\star) \to \mathbb{F}(c))$ where $\star$ is the single object of $1$, $c$ is a object of $\mathrm{A}$ and $\alpha \colon \mathbb{G}(\star) \to \mathbb{F}(c)$ is a morphism in $\mathbb{B}\textnormal{D}(\bold{Cat})_0$.
-The pseudo double category $\mathbb{B}\textnormal{D}(\bold{Cat})$ only has a single object $\star$ and identity vertical 1-morphism, so the triple $(\star,c,\alpha \colon \mathbb{G}(\star) \to \mathbb{F}(c))$ amounts to an object of $\mathrm{A}$ together with trivial structure.
-Given another object $(\star, c^\prime, \alpha^\prime \colon \mathbb{G}(\star) \to \mathbb{F}(c^\prime))$, a morphism from the first triple to the second triple is a pair $(\beta, \gamma)$ where $\beta = \id_{\star}$ is a morphism in $1$ and $\gamma \colon c \to c^\prime$ is a morphism in $\mathrm{A}$ such that the following diagram commutes:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (1,1) {$\mathbb{G}(\star)$};
-\node (B) at (2,1) {$\mathbb{G}(\star)$};
-\node (A') at (1,0) {$\mathbb{F}(c)$};
-\node (B') at (2,0) {$\mathbb{F}(c^\prime)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$\mathbb{G}(\id_{\star})$} (B)
-(A') edge node[above]{$\mathbb{F}(\gamma)$} (B')
-(A) edge node[left]{$\alpha$} (A')
-(B) edge node[right]{$\alpha^\prime$} (B');
-\end{tikzpicture}
-\]
-The double category $\mathbb{B}\textnormal{D}(\bold{Cat})$ only has a single object and identity vertical 1-morphism, so this diagram is trivial,  as all four objects are the same and all four morphisms are identities.
-Thus, morphisms are given by morphisms of $\mathrm{A}$ with added trivial structure, and so the category $(\mathbb{G}/ \mathbb{F})_0$ has objects and morphisms of $\mathrm{A}$, and we have an isomorphism of categories $(\mathbb{G} / \mathbb{F})_0 \cong \mathrm{A}$.
-
-Next we build the category $(\mathbb{G} / \mathbb{F})_1$ which will be the comma category obtained from the following cospan:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$1$};
-\node (B) at (1,1) {$\mathbb{B}\textnormal{D}(\bold{Cat})_1$};
-\node (C) at (2,0) {$\mathbb{C}\textnormal{ospan}(\mathrm{A})_1$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$\mathbb{G}_1$} (B)
-(C) edge node[above]{$\mathbb{F}_1$} (B);
-\end{tikzpicture}
-\]
-Objects are given by triples $$(1_{\star}, a \rightarrow c \leftarrow b, d \colon \mathbb{G}(1_{\star}) \to \mathbb{F}(a \rightarrow c \leftarrow b))$$ where $1_{\star}$ is the identity horizontal 1-cell on $\star$ and $a \rightarrow c \leftarrow b$ is a cospan in $\mathrm{A}$.
-The double functor $\mathbb{G}$ maps the identity horizontal 1-cell to the monoidal unit of $\bold{Cat}$ under $\times$, namely the terminal category $1$, and the double functor $\mathbb{F}$ acts as the functor $F$ on horizontal 1-cells, meaning that $\mathbb{F}(a \rightarrow c \leftarrow b)=F(c)$.
-Thus the above triple is a cospan in $\mathrm{A}$ together with an element $d \colon 1 \to F(c)$, and this is precisely an $F$-decorated cospan, namely a pair $$((a \rightarrow c \leftarrow b),d \in F(c)).$$
-
-Given two objects $((a \rightarrow c \leftarrow b),d \in F(c))$ and $(a^\prime \rightarrow c^\prime \leftarrow b^\prime),d^\prime \in F(c^\prime))$, a morphism from the first to the second is a triple $(\delta,h,\iota)$ that makes the following diagram commute:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$\mathbb{G}(1_\star)$};
-\node (B) at (0,-1) {$\mathbb{G}(1_\star)$};
-\node (C) at (2,0) {$\mathbb{F}(a \rightarrow c \leftarrow b)$};
-\node (D) at (2,-1) {$\mathbb{F}(a^\prime \rightarrow c^\prime \leftarrow b^\prime)$};
-\node (E) at (1,-0.5) {$\iota \Swarrow$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[left]{$\mathbb{G}(\delta)$} (B)
-(A) edge node[above]{$d$} (C)
-(C) edge node[right]{$\mathbb{F}(h)$} (D)
-(B) edge node [above] {$d^\prime$} (D);
-\end{tikzpicture}
-\]
-Simplifying things a bit, $\mathbb{G}(\delta)$ must be the identity 2-morphism of $1$ and $h$ is a morphism of $\mathbb{C}\textnormal{ospan}(\mathrm{A})$, namely a triple of morphisms $(h_1,h,h_2)$ in $\mathrm{A}$ that makes the following diagram commute:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$a$};
-\node (A') at (0,-0.5) {$a^\prime$};
-\node (B) at (1,0.5) {$c$};
-\node (C) at (2,0.5) {$b$};
-\node (C') at (2,-0.5) {$b^\prime$};
-\node (D) at (1,-0.5) {$c^\prime$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$$} (B)
-(C) edge node[above]{$$} (B)
-(A) edge node[left]{$h_1$} (A')
-(C) edge node[left]{$h_2$} (C')
-(A') edge node {$$} (D)
-(C') edge node {$$} (D)
-(B) edge node [left] {$h$} (D);
-\end{tikzpicture}
-\]
-Thus the above diagram containing the 2-morphism $\iota$ becomes:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (4,0) {$\iota \Swarrow$};
-\node (D) at (3,0) {$1$};
-\node (E) at (4.5,0.5) {$F(c)$};
-\node (E') at (4.5,-0.5) {$F(c^\prime)$};
-\path[->,font=\scriptsize,>=angle 90]
-(D) edge node [above] {$d$} (E)
-(D) edge node [below] {$d^\prime$} (E')
-(E) edge node [right] {$F(h)$} (E');
-\end{tikzpicture}
-\]
-which is just a morphism $\iota \colon F(h)(d) \to d^\prime$ in $F(c^\prime)$.
-Thus a morphism of $(\mathbb{G} / \mathbb{F})_1$ is a map of cospans in $\mathrm{A}$ together with a natural transformation that that makes the above triangle commute.
-\newline
-\textbf{Likely delete everything in this section before this line.}
-\begin{thm}
-Let $\mathrm{A}$ be a category with finite colimits and $F \colon \mathrm{A} \to \bold{Cat}$ a lax monoidal pseudofunctor.
-Then there exists a double category $\mathbb{F} \textnormal{Cospan}(\mathrm{A}) \coloneqq (\mathbb{G}/ \mathbb{F})$ which has:
-\begin{enumerate}
-\item{objects as those of $\mathrm{A}$,}
-\item{vertical 1-morphisms as morphisms of $\mathrm{A}$,}
-\item{horizontal 1-cells as pairs:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a$};
-\node (B) at (1,0) {$c$};
-\node (C) at (2,0) {$b$};
-\node (D) at (3,0) {$d \in F(c)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i$} (B)
-(C) edge node[above]{$o$} (B);
-\end{tikzpicture}
-\]
-and}
-\item{2-morphisms as maps of cospans in $\mathrm{A}$
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$a$};
-\node (A') at (0,-0.5) {$a^\prime$};
-\node (B) at (1,0.5) {$c$};
-\node (C) at (2,0.5) {$b$};
-\node (C') at (2,-0.5) {$b^\prime$};
-\node (D) at (1,-0.5) {$c^\prime$};
-\node (E) at (3,0.5) {$d \in F(c)$};
-\node (F) at (3,-0.5) {$d^\prime \in F(c^\prime)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$$} (B)
-(C) edge node[above]{$$} (B)
-(A) edge node[left]{$f$} (A')
-(C) edge node[left]{$g$} (C')
-(A') edge node {$$} (D)
-(C') edge node {$$} (D)
-(B) edge node [left] {$h$} (D);
-\end{tikzpicture}
-\]
-together with a morphism $\iota \colon F(h)(d) \to d^\prime$ in $F(c^\prime)$.}
-\end{enumerate}
-\end{thm}
 The unit structure functor $U \colon (\mathbb{G},\mathbb{F})_0 \to (\mathbb{G},\mathbb{F})_1$ is defined on objects as: 
@@
 $$\iota \colon F(e)(x) \to x$$
-\section{An example}
+\section{Applications}
 As an example, let $L \colon \mathrm{FinSet} \to \mathrm{Graph}$ be the functor which is left adjoint to the forgetful functor $R \colon \mathrm{Graph} \to \mathrm{FinSet}$; the functor $L$ maps a finite set $N$ to the discrete graph with $N$ as its set of vertices and no edges.
@@
 We thus have two symmetric monoidal double categories: $_L \mathbb{C}\textnormal{sp}(\mathrm{Graph})$ obtained from structured cospans and $\mathbb{F}\textnormal{Cospan}(\mathrm{FinSet})$ using Theorem \ref{main1}.
-These two double categories are in fact equivalent as symmetric monoidal double categories which we now show.
-
-\textbf{Probably delete stuff after this line.}
-
-Define a double functor $\mathbb{E} \colon _L \mathbb{C}\textnormal{sp}(\mathrm{Graph}) \to \mathbb{F}\textnormal{Cospan}(\mathrm{FinSet})$ as follows: $\mathbb{E}_0=\id_{\mathrm{FinSet}}$ as both double categories $_L \mathbb{C}\textnormal{sp}(\mathrm{Graph})$ and $\mathbb{F}\textnormal{Cospan}(\mathrm{FinSet})$ have $\mathrm{FinSet}$ as their category of objects.
-The identity functor on $\mathrm{FinSet}$ is trivially an equivalence.
-For the arrow component $\mathbb{E}_1$, given a horizontal 1-cell of $_L \mathbb{C}\textnormal{sp}(\mathrm{Graph})$, which is a cospan in $\mathrm{Graph}$ of the form:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$L(N)$};
-\node (B) at (1,0) {$M$};
-\node (C) at (2,0) {$L(N^\prime)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i$} (B)
-(C) edge node[above]{$o$} (B);
-\end{tikzpicture}
-\]
-the functor $\mathbb{E}_1$ maps this horizontal 1-cell to the horizontal 1-cell of $\mathbb{F}\textnormal{Cospan}(\mathrm{FinSet})$ given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$N$};
-\node (B) at (1,0) {$R(M)$};
-\node (C) at (2,0) {$N^\prime$};
-\node (D) at (3.5,0) {$M \in F(R(M))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$R(i)$} (B)
-(C) edge node[above]{$R(o)$} (B);
-\end{tikzpicture}
-\]
-where $R \colon \mathrm{Graph} \to \mathrm{FinSet}$ is the forgetful functor, right adjoint to $L \colon \mathrm{FinSet} \to \mathrm{Graph}$.
-The image of a 2-morphism in $_L \mathbb{C}\textnormal{sp}(\mathrm{Graph})$ given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$L(N_1)$};
-\node (B) at (1,0) {$M$};
-\node (C) at (2,0) {$L(N_2)$};
-\node (A') at (0,-1) {$L(N_1^\prime)$};
-\node (B') at (1,-1) {$M^\prime$};
-\node (C') at (2,-1) {$L(N_2^\prime)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i$} (B)
-(C) edge node[above]{$o$} (B)
-(A') edge node[above]{$i^\prime$} (B')
-(C') edge node[above]{$o^\prime$} (B')
-(A) edge node [left]{$L(f)$} (A')
-(B) edge node [left]{$h$} (B')
-(C) edge node [left]{$L(g)$} (C');
-\end{tikzpicture}
-\]
-is the 2-morphism in $\mathbb{F}\textnormal{Cospan}(\mathrm{FinSet})$ given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$N_1$};
-\node (B) at (1,0) {$R(M)$};
-\node (C) at (2,0) {$N_2$};
-\node (A') at (0,-1) {$N_1^\prime$};
-\node (B') at (1,-1) {$R(M^\prime)$};
-\node (C') at (2,-1) {$N_2^\prime$};
-\node (D) at (4,0) {$F(R(M))$};
-\node (D') at (4,-1) {$F(R(M^\prime))$};
-\node (E) at (3,-0.5) {$1$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$R(i)$} (B)
-(C) edge node[above]{$R(o)$} (B)
-(A') edge node[above]{$R(i^\prime)$} (B')
-(C') edge node[above]{$R(o^\prime)$} (B')
-(A) edge node [left]{$f$} (A')
-(B) edge node [left]{$R(h)$} (B')
-(C) edge node [left]{$g$} (C')
-(E) edge node [above] {$M$} (D)
-(E) edge node [below] {$M^\prime$} (D')
-(D) edge node [right] {$F(R(h))$} (D');
-\end{tikzpicture}
-\]
-together with a graph morphism $\iota_h \colon F(R(h))(M) \to M^\prime$.
-Denoting a cospan by its apex, the map $$\mathbb{E}_1 \colon { _f { _L \mathbb{C}\textnormal{sp}(\mathrm{Graph})}_g} (M,M^\prime) \to { _{\mathbb{E}(f)} \mathbb{F}\textnormal{Cospan}(\mathrm{FinSet})_{\mathbb{E}(g)}}(\mathbb{E}(M),\mathbb{E}(M^\prime))$$ is bijective and thus the double functor $\mathbb{E}$ is full and faithful.
-To see that it is also essentially surjective, given a horizontal 1-cell in $\mathbb{F}\textnormal{Cospan}(\mathrm{FinSet})$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$N_1$};
-\node (B) at (1,0) {$N$};
-\node (C) at (2,0) {$N_2$};
-\node (D) at (3,0) {$M \in F(N)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i$} (B)
-(C) edge node[above]{$o$} (B);
-\end{tikzpicture}
-\]
-there exists a horizontal 1-cell in $_L \mathbb{C}\textnormal{sp}(\mathrm{Graph})$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$L(N_1)$};
-\node (B) at (1,0) {$M$};
-\node (C) at (2,0) {$L(N_2)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i^\prime$} (B)
-(C) edge node[above]{$o^\prime$} (B);
-\end{tikzpicture}
-\]
-and a 2-isomorphism in $\mathbb{F}\textnormal{Cospan}(\mathrm{FinSet})$ from the image of the latter horizontal 1-cell to the former given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$N_1$};
-\node (B) at (1,0) {$R(M)$};
-\node (C) at (2,0) {$N_2$};
-\node (A') at (0,-1) {$N_1$};
-\node (B') at (1,-1) {$N$};
-\node (C') at (2,-1) {$N_2$};
-\node (D) at (3.5,0) {$M \in F(R(M))$};
-\node (D') at (3.5,-1) {$M \in F(N)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$R(i^\prime)$} (B)
-(C) edge node[above]{$R(o^\prime)$} (B)
-(A') edge node[above]{$i$} (B')
-(C') edge node[above]{$o$} (B')
-(A) edge node [left]{$1$} (A')
-(B) edge node [left]{$1$} (B')
-(C) edge node [left]{$1$} (C');
-\end{tikzpicture}
-\]
-$$\iota = \id_{M} \colon F(R(M)) \to M$$ 
-which trivially commutes as $R(M)=N$ and $R(i^\prime)$ and $R(o^\prime)$ are the underlying maps of vertices of the graph morphisms $i^\prime$ and $o^\prime$ which act as the functions $i$ and $o$, respectively.
-Given two composable horizontal 1-cells $\alpha$ and $\beta$ of $_L \mathbb{C}\textnormal{sp}(\mathrm{Graph})$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$L(N_1)$};
-\node (B) at (1,0) {$M$};
-\node (C) at (2,0) {$L(N_2)$};
-\node (D) at (3,0) {$L(N_2)$};
-\node (E) at (4,0) {$M^\prime$};
-\node (F) at (5,0) {$L(N_3)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i_1$} (B)
-(C) edge node[above]{$o_1$} (B)
-(D) edge node[above]{$i_2$} (E)
-(F) edge node[above]{$o_2$} (E);
-\end{tikzpicture}
-\]
-we have a natural isomorphism $\mathbb{E}_{\alpha,\beta} \colon \mathbb{E}(\alpha) \odot \mathbb{E}(\beta) \to \mathbb{E}(\alpha \odot \beta)$ given by: 
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$N_1$};
-\node (B) at (2,0) {$R(M)+_{N_2} R(M^\prime)$};
-\node (C) at (4,0) {$N_3$};
-\node (A') at (0,-1) {$N_1$};
-\node (B') at (2,-1) {$R(M +_{L(N_2)} M^\prime)$};
-\node (C') at (4,-1) {$N_3$};
-\node (D) at (6.5,0) {$M+_{L(N_2)}M^\prime \in F(R(M) +_{N_2} R(M^\prime))$};
-\node (D') at (6.5,-1) {$M +_{L(N_2)} M^\prime \in F(R(M+_{L(N_2)} M^\prime))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$j \psi R(i_1)$} (B)
-(C) edge node[above]{$j \psi R(o_2)$} (B)
-(A') edge node[above]{$U(i^\prime)$} (B')
-(C') edge node[above]{$U(o^\prime)$} (B')
-(A) edge node [left]{$1$} (A')
-(B) edge node [left]{$$} (B')
-(C) edge node [left]{$1$} (C');
-\end{tikzpicture}
-\]
-The right adjoint $R \colon \textrm{Graph} \to \textrm{Set}$ is also a left adjoint $R \dashv K$ to the codiscrete graph functor $K \colon \textrm{Set} \to \textrm{Graph}$ which sends a finite set $N$ to the complete graph with $N$ as its underlying set of vertices.
-The functor $R \colon \textrm{Graph} \to \textrm{Set}$ thus also preserves colimits which yields an isomorphism $$ R(M +_{L(N_2)} M^\prime) \cong R(M) +_{R(L(N_2))} R(M^\prime)$$ and again we make use of the fact that the left adjoint $L \colon \textrm{Set} \to \textrm{Graph}$ is fully faithful and thus the unit $$\eta_{N_2} \colon N_2 \to R(L(N_2))$$ is an isomorphism which gives $$R(M +_{L(N_2)} M^\prime) \cong R(M) +_{R(L(N_2))} R(M^\prime) \cong R(M) +_{N_2} R(M^\prime).$$ Thus the double functor $\mathbb{E} \colon _L \mathbb{C}\textnormal{sp}(\mathrm{Graph}) \to \mathbb{F}\textnormal{Cospan}(\mathrm{FinSet})$ is strong and we  have an equivalence of double categories $_L \mathbb{C}\textnormal{sp}(\textrm{Graph}) \sim \mathbb{F}\textrm{Cospan}(\textrm{FinSet})$.
-Moreover, each of these categories is symmetric monoidal and the double functor $\mathbb{E}$ is symmetric monoidal; first, we have that the following diagrams commute.
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$_L \mathbb{C} \textnormal{sp}(\textrm{Graph})_1$};
-\node (B) at (4,0) {$\mathbb{F}\textnormal{Cospan}(\textrm{FinSet})_1$};
-\node (C) at (0,-1) {$_L \mathbb{C}\textnormal{sp}(\textrm{FinGraph)}_0 = \textrm{FinSet}$};
-\node (D) at (4,-1) {$\mathbb{F} \textnormal{Cospan}(\textrm{FinSet})_0 = \textrm{FinSet}$};
-\node (A') at (0,-2) {$_L \mathbb{C} \textnormal{sp}(\textrm{Graph})_1$};
-\node (B') at (4,-2) {$\mathbb{F}\textnormal{Cospan}(\textrm{FinSet})_1$};
-\node (C') at (0,-3) {$_L \mathbb{C}\textnormal{sp}(\textrm{Graph)}_0 = \textrm{FinSet}$};
-\node (D') at (4,-3) {$\mathbb{F} \textnormal{Cospan}(\textrm{FinSet})_0 = \textrm{FinSet}$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$\mathbb{E}_1$} (B)
-(A) edge node[left]{$S$} (C)
-(C) edge node[above]{$\mathbb{E}_0=\id_{\textrm{FinSet}}$} (D)
-(B) edge node[right]{$S$} (D)
-(A') edge node [above]{$\mathbb{E}_1$} (B')
-(A') edge node [left]{$T$} (C')
-(C') edge node [above]{$\mathbb{E}_0=\id_{\textrm{FinSet}}$} (D')
-(B') edge node [right] {$T$} (D');
-\end{tikzpicture}
-\]
-Both diagrams are similar: focusing on the top one and starting with an object of $_L \mathbb{C}\textnormal{sp}(\textrm{Graph})_1$ which is a cospan in $\textrm{Graph}$ of the form:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$L(N)$};
-\node (B) at (1,0) {$M$};
-\node (C) at (2,0) {$L(N_2)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i$} (B)
-(C) edge node[above]{$o$} (B);
-\end{tikzpicture}
-\]
-the functor $\mathbb{E}_1$ then maps this horizontal 1-cell to the horizontal 1-cell in $\mathbb{F}\textnormal{Cospan}(\textrm{FinSet})$ which is given by the pair:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$N_1$};
-\node (B) at (1,0) {$R(M)$};
-\node (C) at (2,0) {$N_2$};
-\node (D) at (3.5,0) {$M \in F(R(M))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$R(i)$} (B)
-(C) edge node[above]{$R(o)$} (B);
-\end{tikzpicture}
-\]
-and the source of this horizontal 1-cell is the object $N_1 \in \textrm{FinSet}$.
-Going the other way around the diagram also yields $N_1$.
-A morphism in $_L \mathbb{C} \textnormal{sp}(\textrm{Graph})_1$ given by a map of cospans in $\textrm{Graph}$ of the form:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$L(N_1)$};
-\node (B) at (1,0) {$M$};
-\node (C) at (2,0) {$L(N_2)$};
-\node (A') at (0,-1) {$L(N_1^\prime)$};
-\node (B') at (1,-1) {$M^\prime$};
-\node (C') at (2,-1) {$L(N_2^\prime)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i_1$} (B)
-(C) edge node[above]{$o_1$} (B)
-(A') edge node[above]{$i_2$} (B')
-(C') edge node[above]{$o_2$} (B')
-(A) edge node [left]{$L(f)$} (A')
-(B) edge node [left]{$h$} (B')
-(C) edge node [left]{$L(g)$} (C');
-\end{tikzpicture}
-\]
-maps under the functor $\mathbb{E}_1$ to:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$N_1$};
-\node (B) at (1,0) {$R(M)$};
-\node (C) at (2,0) {$N_2$};
-\node (A') at (0,-1) {$N_1^\prime$};
-\node (B') at (1,-1) {$R(M^\prime)$};
-\node (C') at (2,-1) {$N_2^\prime$};
-\node (D) at (3,0) {$M \in F(R(M))$};
-\node (D') at (3,-1) {$M^\prime \in F(R(M^\prime)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$R(i_1)$} (B)
-(C) edge node[above]{$R(o_1)$} (B)
-(A') edge node[above]{$R(i_2)$} (B')
-(C') edge node[above]{$R(o_2)$} (B')
-(A) edge node [left]{$f$} (A')
-(B) edge node [left]{$R(h)$} (B')
-(C) edge node [left]{$g$} (C');
-\end{tikzpicture}
-\]
-together with a morphism $\iota \colon F(R(h))(M) \to M^\prime$ in $\textrm{Graph}$ which is really just the morphism $h \in \textrm{Graph}$.
-The source of this morphism is then the morphism $f \in \textrm{FinSet}$, compared with going the other way around the diagram which also results in $f$ and thus both of these squares commute.
-
+
+\textbf{Also talk about electrical circuit, Markov process and Petri net examples.}
+
+\section{Appendix}
+Before formally defining `pseudo double category', it is helpful to have the following picture in mind. A pseudo double category has 2-morphisms shaped like:
+
+\[
+\begin{tikzpicture}[scale=1]
+\node (D) at (-4,0.5) {$A$};
+\node (E) at (-2,0.5) {$B$};
+\node (F) at (-4,-1) {$C$};
+\node (A) at (-2,-1) {$D$};
+\node (B) at (-3,-0.25) {$\Downarrow a$};
+\path[->,font=\scriptsize,>=angle 90]
+(D) edge node [above]{$M$}(E)
+(E) edge node [right]{$g$}(A)
+(D) edge node [left]{$f$}(F)
+(F) edge node [above]{$N$} (A);
+\end{tikzpicture}
+\]
+
+We call $A, B, C$ and $D$ \textbf{objects} or \textbf{0-cells}, $f$ and $g$ \textbf{vertical 1-morphisms}, $M$ and $N$ \textbf{horizontal 1-cells} and $a$ a \textbf{2-morphism}.
+Note that a vertical 1-morphism is a morphism between 0-cells and a 2-morphism is a morphism between horizontal 1-cells.
+We will denote both kinds of morphisms and horizontal 1-cells as a single arrow, namely `$\to$'.
+We follow the notation of Shulman \cite{Shul} with the following definitions.
+
+\begin{defn}
+A \textbf{pseudo double category} $\lD$, or $\textbf{double category}$ for short, consists of a category of objects $\bold{D_{0}}$ and a category of arrows $\bold{D_{1}}$ with the following functors
+\begin{center}
+$U\colon \bold{D_{0}} \to \bold{D_{1}}$\\
+$S,T \colon \bold{D_{1}} \rightrightarrows \bold{D_{0}}$\\
+$\odot \colon \bold{D_{1}} \times_{\bold{D_{0}}} \bold{D_{1}} \to \bold{D_{1}}$ (where the pullback is taken over $\bold{D_{1}} \xrightarrow[]{T} \bold{D_{0}} \xleftarrow[]{S} \bold{D_{1}}$) \\
+\end{center}
+ such that \\
+\begin{center}
+$S(U_{A})=A=T(U_{A})$\\
+$S(M \odot N)=SN$\\
+$T(M \odot N)=TM$\\
+\end{center}
+equipped with natural isomorphisms
+\begin{center}
+
+$\alpha \colon (M \odot N) \odot P \xrightarrow{\sim} M \odot (N \odot P)$\\
+$\lambda \colon U_{B} \odot M \xrightarrow{\sim} M$\\
+$\rho \colon M \odot U_{A} \xrightarrow{\sim} M$
+
+\end{center}
+such that $S(\alpha), S(\lambda), S(\rho), T(\alpha), T(\lambda)$ and $T(\rho)$ are all identities and that the coherence axioms of a monoidal category are satisfied.
+Following the notation of Shulman, objects of $\bold{D_{0}}$ are called $\textbf{0-cells}$ and morphisms of $\bold{D_{0}}$ are called $\textbf{vertical 1-morphisms}$.
+Objects of $\bold{D_{1}}$ are called $\textbf{horizontal 1-cells}$ and morphisms of $\bold{D_{1}}$ are called $\textbf{2-morphisms}$.
+The morphisms of $\bold{D_{0}}$, which are vertical 1-morphisms, will be denoted $f \colon A \to C$ and we denote a 1-cell $M$ with $S(M)=A,T(M)=B$ by $M \colon A \to B$.
+Then a 2-morphism $a \colon M \to N$ of $\bold{D_{1}}$ with $S(a)=f,T(a)=g$ would look like:
+\[
+\begin{tikzpicture}[scale=1]
+\node (D) at (-4,0.5) {$A$};
+\node (E) at (-2,0.5) {$B$};
+\node (F) at (-4,-1) {$C$};
+\node (A) at (-2,-1) {$D$};
+\node (B) at (-3,-0.25) {$\Downarrow a$};
+\path[->,font=\scriptsize,>=angle 90]
+(D) edge node [above]{$M$}(E)
+(E) edge node [right]{$g$}(A)
+(D) edge node [left]{$f$}(F)
+(F) edge node [above]{$N$} (A);
+\end{tikzpicture}
+\]
+\end{defn}
+
+The key difference between a `strict' double category and a pseudo double category is that in a pseudo double category, horizontal composition is associative and unital only up to natural isomorphism.
+Equivalently, as a double category can be viewed as a category internal to $\bold{Cat}$, we can view a pseudo double category as a category `weakly' internal to $\bold{Cat}$.
+We will sometimes omit the word pseudo and simply say double category.
+
+\begin{defn}
+A 2-morphism where $f$ and $g$ are identities is called a \textbf{globular 2-morphism}.
+\end{defn}
+
+\begin{defn}
+Let $\lD$ be a pseudo double category.
+Then the $\textbf{horizontal bicategory}$ of $\lD$, which we denote as $H(\lD)$, is the bicategory consisting of objects of $\lD$, morphisms that are horizontal 1-cells of $\lD$ and 2-morphisms that are globular 2-morphisms of $\lD$.
+\end{defn}
+
+\begin{defn}
+  A \textbf{monoidal double category} is a double category equipped the following
+structure.
+\begin{enumerate}
+\item $\bold{D_{0}}$ and $\bold{D_{1}}$ are both monoidal categories.
+\item If $I$ is the monoidal unit of $\bold{D_{0}}$, then $U_I$ is the
+  monoidal unit of $\bold{D_{1}}$.
+\item The functors $S$ and $T$ are strict monoidal, i.e.\ $S(M\ten N)
+  = SM\ten SN$ and $T(M\ten N)=TM\ten TN$ and $S$ and $T$ also
+  preserve the associativity and unit constraints.
+\item We have globular isomorphisms
+  \[\chi \maps (M_1\ten N_1)\odot (M_2\ten N_2)\too[\sim] (M_1\odot M_2)\ten (N_1\odot N_2)\]
+  and
+  \[\mu\maps U_{A\ten B} \too[\sim] (U_A \ten U_B)\]
+  such that the following diagrams commute:
+		\item \label{diag:MonDblCat}
+			The following diagrams commute expressing the constraint data for the double functor $\otimes$.
+			\[
+			\begin{tikzpicture}
+				\node (A) at (0,3) {\footnotesize{
+							$((M_1\otimes N_1)\odot (M_2\otimes N_2)) \odot (M_3\otimes N_3)$}
+				};
+				\node (B) at (7,3) {\footnotesize{
+						$((M_1\odot M_2)\otimes (N_1\odot N_2)) \odot (M_3\otimes N_3) $}
+				};
+				\node (A') at (0,1.5) {\footnotesize{
+						$(M_1\otimes N_1)\odot ((M_2\otimes N_2) \odot (M_3\otimes N_3)) $}
+				};
+				\node (B') at (7,1.5) {\footnotesize{
+						$((M_1\odot M_2)\odot M_3) \otimes ((N_1\odot N_2)\odot N_3)$}
+				};
+				\node (A'') at (0,0) {\footnotesize{
+						$(M_1\otimes N_1) \odot ((M_2\odot M_3) \otimes (N_2\odot N_3))$}
+				};
+				\node (B'') at (7,0) {\footnotesize{
+						$(M_1\odot (M_2\odot M_3)) \otimes (N_1\odot (N_2\odot N_3))$}
+				};
+			%
+			\path[->,font=\scriptsize]
+				(A) edge node[left]{$\alpha$} (A')
+				(A') edge node[left]{$1 \odot \chi$} (A'')
+				(B) edge node[right]{$\chi$} (B')
+				(B') edge node[right]{$\alpha \otimes \alpha$} (B'')
+				(A) edge node[above]{$\chi \odot 1$} (B)
+				(A'') edge node[above]{$\chi$} (B'');
+		\end{tikzpicture}
+		\]
+		\[
+		\begin{tikzpicture}
+			\node (UL) at (0,1.5) {\footnotesize{
+					$(M\otimes N) \odot U_{C\otimes D}$}
+			};
+			\node (LL) at (0,0) {\footnotesize{
+					$M\otimes N$}
+			};
+			\node (UR) at (3.5,1.5) {\footnotesize{
+					$(M\otimes N)\odot (U_C\otimes U_D)$}
+			};
+			\node (LR) at (3.5,0) {\footnotesize{
+					$(M\odot U_C) \otimes (N\odot U_D)$}
+			};
+			%
+			\path[->,font=\scriptsize]
+				(UL) edge node[above]{$1 \odot \mu$} (UR) 
+				(UL) edge node[left]{$\rho$} (LL)
+				(LR) edge node[above]{$\rho \otimes \rho$} (LL)
+				(UR) edge node[right]{$\chi$} (LR);
+		\end{tikzpicture}
+		%
+		\quad
+		%
+		\begin{tikzpicture}
+			\node (UL) at (0,1.5) {\scriptsize{$U_{A\otimes B}\odot (M\otimes N)$}};
+			\node (LL) at (0,0) {\scriptsize{$M\otimes N$}};
+			\node (UR) at (3.5,1.5) {\scriptsize{$(U_A\otimes U_B)\odot (M\otimes N)$}};
+			\node (LR) at (3.5,0) {\scriptsize{$(U_A \odot M) \otimes (U_B\odot N)$}};
+			%
+			\path[->,font=\scriptsize]
+				(UL) edge node[above]{$\chi \odot 1$} (UR) 
+				(UL) edge node[left]{$\lambda$} (LL)
+				(LR) edge node[above]{$\lambda \otimes \lambda$} (LL)
+				(UR) edge node[right]{$\chi$} (LR);
+		\end{tikzpicture}
+		\]
+		%
+		\item The following diagrams commute expressing 
+		the associativity isomorphism for $\otimes$ is a transformation of double categories.
+		\[
+		\begin{tikzpicture}
+			\node (A) at (0,3) {\footnotesize{
+					$((M_1\otimes N_1)\otimes P_1) \odot ((M_2\otimes N_2)\otimes P_2)$}
+			};
+			\node (B) at (7,3) {\footnotesize{
+					$(M_1\otimes (N_1\otimes P_1)) \odot (M_2\otimes (N_2\otimes P_2))$}
+			};
+			\node (A') at (0,1.5) {\footnotesize{
+					$((M_1\otimes N_1) \odot (M_2\otimes N_2)) \otimes (P_1\odot P_2)$}
+			};
+			\node (B') at (7,1.5) {\footnotesize{
+					$(M_1\odot M_2) \otimes ((N_1\otimes P_1)\odot (N_2\otimes P_2))$}
+			};
+			\node (A'') at (0,0) {\footnotesize{
+					$((M_1\odot M_2) \otimes(N_1\odot N_2)) \otimes (P_1\odot P_2)$}
+			};
+			\node (B'') at (7,0) {\footnotesize{
+					$(M_1\odot M_2) \otimes ((N_1\odot N_2)\otimes (P_1\odot P_2))$}
+			};
+			%
+			\path[->,font=\scriptsize]
+				(A) edge node[left]{$\chi$} (A')
+				(A') edge node[left]{$\chi \otimes 1$} (A'')
+				(B) edge node[right]{$\chi$} (B')
+				(B') edge node[right]{$1 \otimes \chi$} (B'')
+				(A) edge node[above]{$\alpha \odot \alpha$} (B)
+				(A'') edge node[above]{$\alpha$} (B'');
+		\end{tikzpicture}
+		\]
+		\[
+		\begin{tikzpicture}
+			\node (A) at (0,3) {\footnotesize{$U_{(A\otimes B)\otimes C}$}};
+			\node (B) at (4,3) {\footnotesize{$U_{A\otimes (B\otimes C)} $}};
+			\node (A') at (0,1.5) {\footnotesize{$U_{A\otimes B} \otimes U_C $}};
+			\node (B') at (4,1.5) {\footnotesize{$U_A\otimes U_{B\otimes C}$}};
+			\node (A'') at (0,0) {\footnotesize{$(U_A\otimes U_B)\otimes U_C$}};
+			\node (B'') at (4,0) {\footnotesize{$U_A\otimes (U_B\otimes U_C) $}};
+			%
+			\path[->,font=\scriptsize]
+				(A) edge node[left]{$\mu$} (A')
+				(A') edge node[left]{$\mu \otimes 1$} (A'')
+				(B) edge node[right]{$\mu$} (B')
+				(B') edge node[right]{$1 \otimes \mu$} (B'')
+				(A) edge node[above]{$U_{\alpha}$} (B)
+				(A'') edge node[above]{$\alpha$} (B'');
+		\end{tikzpicture}
+		\]
+		\item The following diagrams commute expressing that 
+		the unit isomorphisms for $\otimes$ are transformations of double categories. 
+		\[
+		\begin{tikzpicture}
+			\node (A) at (0,1.5) {\footnotesize{$(M\otimes U_I)\odot (N\otimes U_I)$}};
+			\node (A') at (0,0) {\footnotesize{$M\odot N $}};
+			\node (B) at (4,1.5) {\footnotesize{$(M\odot N)\otimes (U_I \odot U_I) $}};
+			\node (B') at (4,0) {\footnotesize{$(M\odot N)\otimes U_I $}};
+			%
+			\path[->,font=\scriptsize]
+				(A) edge node[left]{$r \odot r$} (A')
+				(A) edge node[above]{$\chi$} (B)
+				(B) edge node[right]{$1 \otimes \rho$} (B')
+				(B') edge node[above]{$r$} (A');
+		\end{tikzpicture}
+		%
+		\quad
+		%
+		\begin{tikzpicture}
+			\node (A) at (0,0.75) {\footnotesize{$U_{A\otimes I} $}};
+			\node (B) at (1.5,1.5) {\footnotesize{$U_A\otimes U_I $}};
+			\node (B') at (1.5,0) {\footnotesize{$U_A$}};
+			%
+			\path[->,font=\scriptsize]
+				(A) edge node[above]{$\mu$} (B)
+				(A) edge node[below]{$U_{r}$} (B')
+				(B) edge node[right]{$r$} (B');
+		\end{tikzpicture}
+		\]
+		%
+		%
+		%
+		%
+		\[
+		\begin{tikzpicture}
+			\node (A) at (0,1.5) {\footnotesize{$(U_I\otimes M)\odot (U_I\otimes N)$}};
+			\node (A') at (0,0) {\footnotesize{$M\odot N$}};
+			\node (B) at (4,1.5) {\footnotesize{$(U_I \odot U_I) \otimes (M\odot N)$}};
+			\node (B') at (4,0) {\footnotesize{$U_I\otimes (M\odot N) $}};
+			%
+			\path[->,font=\scriptsize]
+				(A) edge node[left]{$\ell \odot \ell$} (A')
+				(A) edge node[above]{$\chi$} (B)
+				(B) edge node[right]{$\lambda \otimes 1$} (B')
+				(B') edge node[above]{$\ell$} (A');
+		\end{tikzpicture}
+		%
+		\quad
+		\begin{tikzpicture}
+			\node (A) at (0,0.75) {\footnotesize{$U_{I\otimes A}$}};
+			\node (B) at (1.5,1.5) {\footnotesize{$U_I\otimes U_A$}};
+			\node (B') at (1.5,0) {\footnotesize{$U_A$}};
+			%
+			\path[->,font=\scriptsize]
+				(A) edge node[above]{$\mu$} (B)
+				(A) edge node[below]{$U_{\ell}$} (B')
+				(B) edge node[right]{$\ell$} (B');
+		\end{tikzpicture}
+		\]
+		\newcounter{mondbl}
+		\setcounter{mondbl}{\value{enumi}}
+	\end{enumerate}
+	A \textbf{braided monoidal double category} 
+	is a monoidal double category 
+	such that:
+	\begin{enumerate}
+		\setcounter{enumi}{\value{mondbl}}
+		\item $\dblcat{D}_{0}$ and $\dblcat{D}_{1}$ are braided monoidal categories.
+		\item The functors $S$ and $T$ are strict braided monoidal functors.
+		\item The following diagrams commute expressing that the braiding is a transformation of double categories.
+		\[
+		\begin{tikzpicture}
+			\node (A) at (0,1.5) {\footnotesize{$(M_1 \odot M_2) \otimes (N_1 \odot N_2)$}};
+			\node (A') at (0,0) {\footnotesize{$(M_1\otimes N_1) \odot (M_2\otimes N_2)$}};
+			\node (B) at (5,1.5) {\footnotesize{$(N_1\odot N_2) \otimes (M_1 \odot M_2)$}};
+			\node (B') at (5,0) {\footnotesize{$(N_1 \otimes M_1) \odot (N_2 \otimes M_2)$}};
+			%
+			\path[->,font=\scriptsize]
+				(A) edge node[left]{$\chi$} (A')
+				(A) edge node[above]{$\beta$} (B)
+				(B) edge node[right]{$\chi$} (B')
+				(A') edge node[above]{$\beta \odot \beta$} (B');
+		\end{tikzpicture}
+		%
+		\quad
+		%
+		\begin{tikzpicture}
+			\node (A) at (0,1.5) {\footnotesize{$U_A \otimes U_B$}};
+			\node (A') at (0,0) {\footnotesize{$U_B\otimes U_A$}};
+			\node (B) at (2,1.5) {\footnotesize{$U_{A\otimes B} $}};
+			\node (B') at (2,0) {\footnotesize{$U_{B\otimes A}$}};
+			%
+			\path[->,font=\scriptsize]
+				(A) edge node[left]{$\beta$} (A')
+				(B) edge node[above]{$\mu$} (A)
+				(B) edge node[right]{$U_\beta$} (B')
+				(B') edge node[above]{$\mu$} (A');
+		\end{tikzpicture}
+		\]
+		\setcounter{mondbl}{\value{enumi}}
+	\end{enumerate}
+	Finally, a \textbf{symmetric monoidal double category} 
+	is a braided monoidal double category $\mathbb{D}$ such that:
+	\begin{enumerate}
+		\setcounter{enumi}{\value{mondbl}}
+		\item $\dblcat{D}_{0}$ and $\dblcat{D}_{1}$ are symmetric monoidal.
+	\end{enumerate}
+\end{defn}
+
+\begin{defn}\label{def:companion}
+  Let \lD\ be a double category and $f\maps A\to B$ a vertical
+  1-morphism.  A \textbf{companion} of $f$ is a horizontal 1-cell
+  $\fhat\maps A\to B$ together with 2-morphisms
+	\[
+	\raisebox{-0.5\height}{
+	\begin{tikzpicture}
+		\node (A) at (0,1) {$A$};
+		\node (B) at (1,1) {$B$};
+		\node (A') at (0,0) {$B$};
+		\node (B') at (1,0) {$B$};
+		%
+		\path[->,font=\scriptsize,>=angle 90]
+			(A) edge node[above]{$\widehat{f}$} (B)
+			(A) edge node[left]{$f$} (A')
+			(B) edge node[right]{$1$} (B')
+			(A') edge node[below]{$U_B$} (B');
+		%
+	%	\draw (0.5,.925) -- (0.5,1.075);
+	%	\draw (0.5,-.075) -- (0.5,.075);
+		\node () at (0.5,0.5) {\scriptsize{$\Downarrow$}};
+	\end{tikzpicture}
+	}
+	%
+	\quad \text{ and } \quad
+	%
+	\raisebox{-0.5\height}{
+	\begin{tikzpicture}
+		\node (A) at (0,1) {$A$};
+		\node (B) at (1,1) {$A$};
+		\node (A') at (0,0) {$A$};
+		\node (B') at (1,0) {$B$};
+		%
+		\path[->,font=\scriptsize,>=angle 90]
+			(A) edge node[above]{$U_A$} (B)
+			(A) edge node[left]{$1$} (A')
+			(B) edge node[right]{$f$} (B')
+			(A') edge node[below]{ $\widehat{f}$} (B');
+		%
+	%	\draw (0.5,.925) -- (0.5,1.075);
+	%	\draw (0.5,-.075) -- (0.5,.075);
+		\node () at (0.5,0.5) {\scriptsize{$\Downarrow$}};
+	\end{tikzpicture}
+	}
+	\]
+  such that the following equations hold.
+	\begin{equation}
+	\label{eq:CompanionEq}
+	\raisebox{-0.5\height}{
+	\begin{tikzpicture}
+		\node (A) at (0,2) {$A$};
+		\node (B) at (1.1,2) {$A$};
+		\node (A') at (0,1) {$A$};
+		\node (B') at (1.1,1) {$B$};
+		\node (A'') at (0,0) {$B$};
+		\node (B'') at (1.1,0) {$B$};
+		%
+		\path[->,font=\scriptsize,>=angle 90]
+			(A) edge node[left]{$1$} (A')
+			(A') edge node[left]{$f$} (A'')
+			(B) edge node[right]{$f$} (B')
+			(B') edge node[right]{$1$} (B'')
+			(A) edge node[above]{$U_A$} (B)
+			(A') edge  (B')
+			(A'') edge node[below]{$U_B$} (B'');
+		%
+	%	\draw (0.5,1.925) -- (0.5,2.075);
+		\draw[line width=2mm,white] (0.5,.925) -- (0.5,1.075);
+	%	\draw (0.5,-.075) -- (0.5,.075);
+		\node () at (0.5,0.5) {\scriptsize{$\Downarrow$}};
+		\node () at (0.5,1.5) {\scriptsize{$\Downarrow$}};
+		\node () at (0.5,1) {\scriptsize $\widehat{f}$};
+	\end{tikzpicture}
+	}
+	%
+	\raisebox{-0.5\height}{=}
+	%
+	\raisebox{-0.5\height}{
+	\begin{tikzpicture}
+		\node (A) at (0,1) {$A$};
+		\node (B) at (1,1) {$A$};
+		\node (A') at (0,0) {$B$};
+		\node (B') at (1,0) {$B$};
+		%
+		\path[->,font=\scriptsize,>=angle 90]
+		(A) edge node[left]{$f$} (A')
+		(B) edge node[right]{$f$} (B')
+		(A) edge node[above]{$U_A$} (B)
+		(A') edge node[below]{$U_B$} (B');
+		%
+		%\draw (0.5,.925) -- (0.5,1.075);
+		%\draw (0.5,-.075) -- (0.5,.075);
+		\node () at (0.5,0.5) {\scriptsize{$\Downarrow U_f$}};
+	\end{tikzpicture}
+	}
+	%
+	\raisebox{-0.5\height}{\text{   and   }}
+	%
+	\raisebox{-0.5\height}{
+	\begin{tikzpicture}
+		\node (A) at (0,1) {$A$};
+		\node (A') at (0,0) {$A$};
+		\node (B) at (1,1) {$A$};
+		\node (B') at (1,0) {$B$};
+		\node (C) at (2,1) {$B$};
+		\node (C') at (2,0) {$B$};
+		%
+		\path[->,font=\scriptsize,>=angle 90]
+			(A) edge node[left]{$1$} (A')
+			(B) edge node[left]{$f$} (B')
+			(C) edge node[right]{$1$} (C')
+			(A) edge node[above]{$U_A$} (B)
+			(B) edge node[above]{$\widehat{f}$} (C)
+			(A') edge node[below]{$\widehat{f}$} (B')
+			(B') edge node[below]{$U_B$} (C');
+		%
+	%	\draw (1.5,0.925) -- (1.5,1.075);
+	%	\draw (1.5,0.925) -- (1.5,1.075);
+	%	\draw (0.5,.925) -- (0.5,1.075);
+	%	\draw (0.5,-.075) -- (0.5,.075);
+		\node () at (0.5,0.5) {\scriptsize{$\Downarrow$}};
+		\node () at (1.5,0.5) {\scriptsize{$\Downarrow$}};
+	\end{tikzpicture}
+	}
+	%
+	\raisebox{-0.5\height}{=}
+	%
+	\raisebox{-0.5\height}{
+	\begin{tikzpicture}
+		\node (A) at (0,1) {$A$};
+		\node (B) at (1,1) {$B$};
+		\node (A') at (0,0) {$A$};
+		\node (B') at (1,0) {$B$};
+		%
+		\path[->,font=\scriptsize,>=angle 90]
+			(A) edge node[left]{$1$} (A')
+			(B) edge node[right]{$1$} (B')
+			(A) edge node[above]{$\widehat{f}$} (B)
+			(A') edge node[below]{$\widehat{f}$} (B');
+		%
+	%	\draw (0.5,.925) -- (0.5,1.075);
+	%	\draw (0.5,-.075) -- (0.5,.075);
+		\node () at (0.5,0.5) {\scriptsize{$\Downarrow \id_{\widehat{f}}$}};
+	\end{tikzpicture}
+	}
+	\end{equation}
+  A \textbf{conjoint} of $f$, denoted $\fchk \maps B\to A$, is a
+  companion of $f$ in the double category $\lD^{h\cdot\mathrm{op}}$
+  obtained by reversing the horizontal 1-cells, but not the vertical
+  1-morphisms, of \lD.
+\end{defn}
+\noindent
+In a pseudo double category, the second equation above requires an insertion of unit isomorphisms to make sense due to horizontal composition only holding up to isomorphism.
+\begin{defn}
+  We say that a double category is \textbf{fibrant} if every vertical
+  1-morphism has both a companion and a conjoint and \define{isofibrant} if every vertical 1-isomorphism has both a companion and a conjoint.
+\end{defn}
 \section{Acknowledgements}

### 2018-10-06 EquivCompFrameworks_20180911kc.tex
minor changes, cleaning up and adding to applications section

@@
 Let $\mathrm{A}$ be a category with finite colimits and $F \colon \mathrm{A} \to \bold{Cat}$ a lax monoidal pseudofunctor.
-Then there exists a double category $\mathbb{F} \textnormal{Cospan}(\mathrm{A}) \coloneqq (\mathbb{G}/ \mathbb{F})$ which has:
+Then there exists a double category $\mathbb{F} \textnormal{Cospan}(\mathrm{A})$ which has:
 \begin{enumerate}
@@
 \begin{proof}
-The unit structure functor $U \colon (\mathbb{G},\mathbb{F})_0 \to (\mathbb{G},\mathbb{F})_1$ is defined on objects as: 
+The unit structure functor $U \colon \mathbb{F}\textnormal{Cospan}(\mathrm{A})_0 \to \mathbb{F}\textnormal{Cospan}(\mathrm{A})_1$ is defined on objects as: 
 \[
@@
 together with the morphism $\iota_{!_f} = F(f) F(!) \phi \colon 1 \to F(c^\prime)$.
-We also have source and target structure functors $s,t \colon (\mathbb{G} / \mathbb{F})_1 \to (\mathbb{G} / \mathbb{F})_0$ where the source of a horizontal 1-cell
+We also have source and target structure functors $S, T \colon \mathbb{F}\textnormal{Cospan}(\mathrm{A})_1 \to \mathbb{F}\textnormal{Cospan}(\mathrm{A})_0$ where the source of a horizontal 1-cell
 \[
@@
 The double category version of decorataed cospans is given in Section \ref{DecCospansDoublecat}.
-The other framework which also utilizes symmetric monoidal double categories, due to Baez and the first author and goes by the name of `structured cospans', is explained below.
+The other framework also utilizing symmetric monoidal double categories due to the first two authors and which goes by the name of `structured cospans', is explained below.
 Once again following the notation of Shulman \cite{Shul2}, given a double category $\mathbb{A}$, we write $_f \mathbb{A}_g(M,N)$ for the set of 2-morphisms in $\mathbb{A}$ of the form:
@@
 \section{Applications}
+In this section we present several examples each of which may be realized in the context of decorated cospans or in the context of structured cospans.
+The first example regarding graphs was mentioned in the introduction and used as a reoccurring theme throughout the paper.
+The next three examples which take on more of an applied flavor, consists of electrical circuits, Markov processes and Petri nets.
+Each of these has been studied extensively by the first author and others by way of `black-boxing'.
+Black-boxing is a way of interpreting the behavior of an open system, that is, a system with prescribed inputs and outputs such as the terminals of an electrical circuit, by observing the activity at the inputs and the outputs.
+The semantics of the activity at an open system's inputs and outputs is typically described in a category such as $\mathrm{LinRel}$ of finite dimensonal vector spaces and linear relations.
+Thus, in each case, black-boxing results in functors such as: $$\blacksquare_1 \colon \mathrm{Circ} \to \mathrm{LinRel}$$ $$\blacksquare_2 \colon \mathrm{Mark} \to \mathrm{LinRel}$$ $$\blacksquare_3 \colon \mathrm{Petri} \to \mathrm{LinRel}.$$ Each of these black-boxing functors also possess other convenient properties such as being symmetric monoidal.
+The first two of these were first done using Fong's theory of decorated cospans and then extended by the first two authors using structured cospans.
+The last two of these were also extended by being realized as double functors between double categories.
+\textbf{Make this better...}
+\subsection{Graphs}
 As an example, let $L \colon \mathrm{FinSet} \to \mathrm{Graph}$ be the functor which is left adjoint to the forgetful functor $R \colon \mathrm{Graph} \to \mathrm{FinSet}$; the functor $L$ maps a finite set $N$ to the discrete graph with $N$ as its set of vertices and no edges.
@@
 
-\textbf{Also talk about electrical circuit, Markov process and Petri net examples.}
+\subsection{Electrial circuits}
+
+\subsection{Markov processes}
+
+\subsection{Petri nets}
 

### 2018-10-07 EquivCompFrameworks_20180911kc.tex
Working on applications section

@@
 
-\begin{thm}\label{main1}
+\begin{thm}\label{DC}
 Let $\mathrm{A}$ be a category with finite colimits and $F \colon \mathrm{A} \to \bold{Cat}$ a symmetric lax monoidal pseudofunctor.
@@
 
-\begin{thm}
-Given a category $\mathrm{X}$ with finite colimits and a category $\mathrm{A}$ with finite coproducts and a left adjoint $L \colon \mathrm{A} \to \mathrm{X}$ with $\mathrm{A}$ and $\mathrm{X}$ regarded as symmetric monoidal categories under binary coproducts, we can obtain a symmetric monoidal double category $_L \mathbb{C}\textnormal{sp}(\mathrm{X})$ which has:
+\begin{thm}\label{SC}
+Given a category $\mathrm{X}$ with finite colimits and a category $\mathrm{A}$ with finite coproducts and a finite coproduct preserving functor $L \colon \mathrm{A} \to \mathrm{X}$ with $\mathrm{A}$ and $\mathrm{X}$ regarded as cocartesian monoidal categories, there exists a symmetric monoidal double category $_L \mathbb{C}\textnormal{sp}(\mathrm{X})$ which has:
 \begin{enumerate}
@@
 We now show that these two symmetric monoidal double categories are equivalent. 
-\begin{thm}\label{main2}
+\begin{thm}\label{Equiv}
 Let $\mathrm{A}$ and $\mathrm{X}$ be categories with finite colimits and $F \colon \mathrm{A} \to \bold{Cat}$ a symmetric lax monoidal pseudofunctor.
@@
 \subsection{Graphs}
-As an example, let $L \colon \mathrm{FinSet} \to \mathrm{Graph}$ be the functor which is left adjoint to the forgetful functor $R \colon \mathrm{Graph} \to \mathrm{FinSet}$; the functor $L$ maps a finite set $N$ to the discrete graph with $N$ as its set of vertices and no edges.
-Since $\mathrm{Graph}$ is a topos and thus has finite colimits, we can then obtain a symmetric monoidal double category $_L \mathbb{C}\textnormal{sp}(\mathrm{Graph})$ which has:
+As a first example that was also mentioned in the introduction, let $L \colon \mathrm{Set} \to \mathrm{Graph}$ be the functor that assigns to a set $N$ the \emph{discrete graph} on $N$ which is the edgeless graph $L(N)$ with no edges and $N$ as its set of vertices.
+Both $\mathrm{Set}$ and $\mathrm{Graph}$ are cocartesian monoidal and the functor $L \colon \mathrm{Set} \to \mathrm{Graph}$ is left adjoint to the forgetful functor $R \colon \mathrm{Graph} \to \mathrm{Set}$ which assigns to a graph $G$ its underlying set of vertices $U(G)$.
+Using structured cospans and appealing to Theorem \ref{SC}, we get a symmetric monoidal double category $_L \mathbb{C}\textnormal{sp}(\mathrm{Graph})$ which has:
 \begin{enumerate}
-\item{finite sets as objects,}
+\item{sets as objects,}
 \item{functions as vertical 1-morphisms,}
-\item{cospans of graphs of the form
+\item{cospans of graphs, or, \emph{open} graphs of the form
 \[
@@
 \node (A) at (0,0) {$L(N)$};
-\node (B) at (1,0) {$M$};
-\node (C) at (2,0) {$L(N^\prime)$};
+\node (B) at (1,0) {$G$};
+\node (C) at (2,0) {$L(M)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$I$} (B)
+(C) edge node[above]{$O$} (B);
+\end{tikzpicture}
+\]
+as horizontal 1-cells, where $L(N)$ and $L(M)$ are discrete graphs on the sets $N$ and $M$, respectively, $G$ is a graph and $I$ and $O$ are graph morphisms, and}
+\item{maps of cospans of graphs of the form
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$L(N_1)$};
+\node (B) at (1,0) {$G_1$};
+\node (C) at (2,0) {$L(M_1)$};
+\node (A') at (0,-1) {$L(N_2)$};
+\node (B') at (1,-1) {$G_2$};
+\node (C') at (2,-1) {$L(M_2)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$I_1$} (B)
+(C) edge node[above]{$O_1$} (B)
+(A') edge node[above]{$I_2$} (B')
+(C') edge node[above]{$O_2$} (B')
+(A) edge node [left]{$L(f)$} (A')
+(B) edge node [left]{$\alpha$} (B')
+(C) edge node [left]{$L(g)$} (C');
+\end{tikzpicture}
+\]
+as 2-morphisms, where $L(f)$ and $L(g)$ are maps of discrete graphs induced by the underlying functions $f$ and $g$, respectively, and $\alpha \colon G_1 \to G_2$ is a graph morphism.
+}
+\end{enumerate}
+
+We can obtain a similar symmetric monoidal double category using decorated cospans.
+Let $F \colon \mathrm{Set} \to \mathrm{Cat}$ be the symmetric lax monoidal pseudofunctor that assigns to a set $N$ the \emph{category} of all graph structures whose underlying set of vertices is $N$.
+Using Theorem \ref{DC}, we then obtain a symmetric monoidal double category $\mathbb{F}\textnormal{Cospan}(\mathrm{Set})$ which has:
+\begin{enumerate}
+\item{sets as objects,}
+\item{functions as vertical 1-morphisms,}
+\item{horizontal 1-cells as pairs:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$N$};
+\node (B) at (1,0) {$P$};
+\node (C) at (2,0) {$M$};
+\node (D) at (3.25,0) {$G \in F(P)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-as horizontal 1-cells, where $L(N)$ and $L(N^\prime)$ are discrete graphs on the sets $N$ and $N^\prime$, respectively, $M$ is a graph and $i$ and $o$ are graph morphisms, and}
-\item{maps of cospans of graphs of the form
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$L(N_1)$};
-\node (B) at (1,0) {$M$};
-\node (C) at (2,0) {$L(N_2)$};
-\node (A') at (0,-1) {$L(N_1^\prime)$};
-\node (B') at (1,-1) {$M^\prime$};
-\node (C') at (2,-1) {$L(N_2^\prime)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i$} (B)
-(C) edge node[above]{$o$} (B)
-(A') edge node[above]{$i^\prime$} (B')
-(C') edge node[above]{$o^\prime$} (B')
-(A) edge node [left]{$L(f)$} (A')
-(B) edge node [left]{$h$} (B')
-(C) edge node [left]{$L(g)$} (C');
-\end{tikzpicture}
-\]
-as 2-morphisms, where $L(f)$ and $L(g)$ are maps of discrete graphs given by the underlying functions $f$ and $g$, respectively, and $h \colon M \to M^\prime$ is a graph morphism.
-}
-\end{enumerate}
-
-On the other hand, let $F \colon \mathrm{FinSet} \to \mathrm{Cat}$ be the symmetric lax monoidal pseudofunctor that assigns to a finite set $N$ the \emph{category} of all graph structures whose underlying set of vertices is $N$.
-Using Theorem \ref{main1}, we can then obtain a symmetric monoidal double category $\mathbb{F}\textnormal{Cospan}(\mathrm{FinSet})$ which has:
-\begin{enumerate}
-\item{finite sets as objects,}
-\item{functions as vertical 1-morphisms,}
-\item{horizontal 1-cells are given by pairs:
+which can also be thought of as open graphs, and}
+\item{2-morphisms as maps of cospans of sets
 \[
@@
 \node (A) at (0,0) {$N_1$};
-\node (B) at (1,0) {$N$};
-\node (C) at (2,0) {$N_2$};
-\node (D) at (3.25,0) {$M \in F(N)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i$} (B)
-(C) edge node[above]{$o$} (B);
-\end{tikzpicture}
-\]
-and}
-\item{2-morphisms as maps of cospans 
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$N_1$};
-\node (A') at (0,-1) {$N_1^\prime$};
-\node (C') at (2,-1) {$N_2^\prime$};
-\node (B) at (1,0) {$N$};
-\node (C) at (2,0) {$N_2$};
-\node (D) at (1,-1) {$N^\prime$};
-\node (E) at (3,0) {$M \in F(N)$};
-\node (F) at (3,-1) {$M^\prime \in F(N^\prime)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i$} (B)
-(C) edge node[above]{$o$} (B)
+\node (A') at (0,-1) {$N_2$};
+\node (C') at (2,-1) {$M_2$};
+\node (B) at (1,0) {$P_1$};
+\node (C) at (2,0) {$M_1$};
+\node (D) at (1,-1) {$P_2$};
+\node (E) at (3,0) {$G_1 \in F(P_1)$};
+\node (F) at (3,-1) {$G_2 \in F(P_2)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i_1$} (B)
+(C) edge node[above]{$o_1$} (B)
 (A) edge node[left]{$f$} (A')
 (C) edge node[right]{$g$} (C')
-(C') edge node [above] {$o^\prime$} (D)
-(A') edge node [above] {$i^\prime$} (D)
+(C') edge node [above] {$o_2$} (D)
+(A') edge node [above] {$i_2$} (D)
 (B) edge node [left] {$h$} (D);
@@
 \]
-together with a graph morphism $\iota \colon F(h)(M) \to M^\prime$ in $F(N^\prime)$.}
+together with a graph morphism $\iota \colon F(h)(G_1) \to G_2$ in $F(P_2)$.}
 \end{enumerate}
-We thus have two symmetric monoidal double categories: $_L \mathbb{C}\textnormal{sp}(\mathrm{Graph})$ obtained from structured cospans and $\mathbb{F}\textnormal{Cospan}(\mathrm{FinSet})$ using Theorem \ref{main1}.
+We thus have two symmetric monoidal double categories: $_L \mathbb{C}\textnormal{sp}(\mathrm{Graph})$ obtained from structured cospans and $\mathbb{F}\textnormal{Cospan}(\mathrm{Set})$ obtained from decorated cospans.
+Both of these double categories have $\mathrm{Set}$ as their categories of objects, open graphs as horizontal 1-cells and maps of open graphs as 2-morphisms, and by Theorem \ref{Equiv}, we have an equivalence of symmetric monoidal double categories $$_L \mathbb{C}\textnormal{sp}(\mathrm{Graph}) \sim \mathbb{F}\textnormal{Cospan}(\mathrm{Set}).$$
 

### 2018-10-08 EquivCompFrameworks_20180911kc.tex
added some stuff about Petri nets in applications section

@@
 \subsection{Petri nets}
+In a previous work, Master and the first author used structured cospans to obtain a symmetric monoidal double category of `open Petri nets'.
+A Petri net is given by a diagram in $\mathrm{Set}$ of the form:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (B) at (1,0) {$T$};
+\node (C) at (2,0) {$\mathbb{N}[S].$};
+\path[->,font=\scriptsize,>=angle 90]
+(B)edge[bend left] node[above]{$s$}(C)
+(B)edge[bend right] node[below]{$t$}(C);
+\end{tikzpicture}
+\]
+Here, $T$ is the set of \emph{transitions} and $S$ is the set of \emph{species}, and then $\mathbb{N}[S]$ is the free commutative monoid on the set $S$.
+Each transition then has a formal linear combination of species given by an element of $\mathbb{N}[S]$ as its source and target as prescribed by the functions $s$ and $t$, respectively.
+An example of a Petri net is given by:
+\[
+\begin{tikzpicture}
+	\begin{pgfonlayer}{nodelayer}
+		\node [style=species] (I) at (0,1) {H};
+		\node [style=species] (T) at (0,-1) {O};
+		\node [style=transition] (W) at (2,0) {$\alpha$};
+		\node [style=species] (Water) at (4,0) {$\textnormal{H}_2$O};
+%		\node [style=transition] (Something) at (6,0) {\tiny{Something}};
+%		\node [style=species] (A) at (8,1) {O$\textnormal{H}^{-}$};
+%		\node [style=species] (B) at (8,-1) {$\textnormal{H}_3 \textnormal{O}^{+}$};
+	\end{pgfonlayer}
+	\begin{pgfonlayer}{edgelayer}
+		\draw [style=inarrow, bend right=40, looseness=1.00] (I) to (W);
+		\draw [style=inarrow, bend left=40, looseness=1.00] (I) to (W);
+		\draw [style=inarrow, bend right=40, looseness=1.00] (T) to (W);
+		\draw [style=inarrow] (W) to (Water);
+%		\draw [style=inarrow, bend left=40, looseness=1.00] (Water) to (Something);
+%		\draw [style=inarrow, bend right=40, looseness=1.00] (Water) to (Something);
+%		\draw [style=inarrow, bend left=40, looseness=1.00] (Something) to (A);
+%		\draw [style=inarrow, bend right=40, looseness=1.00] (Something) to (B);
+	\end{pgfonlayer}
+\end{tikzpicture}
+\]
+This Petri net has a single transition $\alpha$ with $2\textnormal{H}+\textnormal{O}$ as its source and $\textnormal{H}_2 \textnormal{O}$ as its target.
+See the original paper for more details on Petri nets \cite{BM}.
+
+Each set of species $S$ gives rise to a discrete Petri net $L(S)$ with $S$ as its set of species and no transitions.
+Master and the first author show the existence of a left adjoint $L \colon \mathrm{Set} \to \mathrm{Petri}$ where $\mathrm{Petri}$ is the category whose objects are Petri nets and whose `morphisms are morphisms of Petri nets'.
+They also show that $\mathrm{Petri}$ has finite colimits and thus using Theorem \ref{SC} obtain a symmetric monoidal double category $\mathbb{O}\bold{pen}(\mathrm{Petri})$ of open Petri nets which has:
+\begin{enumerate}
+\item{objects given by sets,}
+\item{vertical 1-morphisms given by functions,}
+\item{horizontal 1-cells as open Petri nets which are given by cospans in $\mathrm{Petri}$ of the form:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (D) at (-3,0) {$L(X)$};
+\node (E) at (-2,0) {$P$};
+\node (F) at (-1,0) {$L(Y)$};
+\path[->,font=\scriptsize,>=angle 90]
+(D) edge node [above] {$I$} (E)
+(F) edge node [above] {$O$} (E);
+\end{tikzpicture}
+\]
+and}
+\item{2-morphisms as maps of cospans in $\mathrm{Petri}$ of the form:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (E) at (3,0) {$L(X)$};
+\node (F) at (5,0) {$L(Y)$};
+\node (G) at (4,0) {$P$};
+\node (E') at (3,-1) {$L(X^\prime)$};
+\node (F') at (5,-1) {$L(Y^\prime)$};
+\node (G') at (4,-1) {$P^\prime$};
+\path[->,font=\scriptsize,>=angle 90]
+(F) edge node[above]{$O$} (G)
+(E) edge node[left]{$L(f)$} (E')
+(F) edge node[right]{$L(g)$} (F')
+(G) edge node[left]{$\alpha$} (G')
+(E) edge node[above]{$I$} (G)
+(E') edge node[above]{$I^\prime$} (G')
+(F') edge node[above]{$O^\prime$} (G');
+\end{tikzpicture}
+\]
+}
+\end{enumerate}
+We can also obtain a similar double category using decorated cospans: define a pseudofunctor $F \colon \mathrm{Set} \to \mathrm{Cat}$ where given a set $s$, $F(s)$ is the (large) category of all Petri net structures with $s$ as its set of species.
+This functor $F$ is symmetric lax monoidal as both $(\mathrm{Set},+,\emptyset)$ and $(\mathrm{Cat},\times,1)$ are symmetric monoidal and given Petri nets $P \in F(s)$ and $P^\prime \in F(s^\prime)$, we can place them side by side and consider them together as a single Petri net $P+P^\prime \in F(s+s^\prime)$ with set of species $s+s^\prime$, and thus we have natural transformations $\phi_{s,s^\prime} \colon F(s) \times F(s^\prime) \to F(s+s^\prime)$ for any two sets $s$ and $s^\prime$.
+The other structure morphism between monoidal units $\phi \colon 1_{\mathrm{Petri}} \to F(\emptyset)$ is defined by the unique morphism from the empty Petri net with the empty set for species to the only possible Petri net on the empty set, which is also the empty Petri net.
+All of the diagrams that are required to commute are straightforward.
+Using Theorem \ref{DC}, we obtain a symmetric monoidal double category $\mathbb{F}\textnormal{Cospan}(\mathrm{Set})$ which has:
+\begin{enumerate}
+\item{objects given by sets,}
+\item{vertical 1-morphisms given by functions,}
+\item{horizontal 1-cells given by pairs:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (D) at (-3,0) {$X$};
+\node (E) at (-2,0) {$Z$};
+\node (F) at (-1,0) {$Y$};
+\node (A) at (0,0) {$P \in F(Z)$};
+\path[->,font=\scriptsize,>=angle 90]
+(D) edge node [above] {$i$} (E)
+(F) edge node [above] {$o$} (E);
+\end{tikzpicture}
+\]
+and}
+\item{2-morphisms as maps of cospans in $\mathrm{Set}$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (E) at (3,0) {$X$};
+\node (F) at (5,0) {$Y$};
+\node (G) at (4,0) {$Z$};
+\node (E') at (3,-1) {$X^\prime$};
+\node (F') at (5,-1) {$Y^\prime$};
+\node (G') at (4,-1) {$Z^\prime$};
+\node (A) at (6,0) {$P \in F(Z)$};
+\node (B) at (6,-1) {$P^\prime \in F(Z^\prime)$};
+\path[->,font=\scriptsize,>=angle 90]
+(F) edge node[above]{$o$} (G)
+(E) edge node[left]{$f$} (E')
+(F) edge node[right]{$g$} (F')
+(G) edge node[left]{$h$} (G')
+(E) edge node[above]{$i$} (G)
+(E') edge node[above]{$i^\prime$} (G')
+(F') edge node[above]{$o^\prime$} (G');
+\end{tikzpicture}
+\]
+together with a morphism of Petri nets $\iota \colon F(h)(P) \to P^\prime$ in $F(Z^\prime)$.}
+\end{enumerate}
+Thus we have a symmetric monoidal double category $\mathbb{O}\bold{pen}(\mathrm{Petri})$ of open Petri nets obtained from structured cospans and a symmetric monoidal double category $\mathbb{F}\textnormal{Cospan}(\mathrm{Set})$ of open Petri nets obtain from decorated cospans, and of course, we have an equivalence $\mathbb{O}\bold{pen}(\mathrm{Petri}) \sim \mathbb{F}\textnormal{Cospan}(\mathrm{Set})$ of symmetric monoidal double categories by Theorem \ref{Equiv}.
 
@@
 
+\bibitem{BM} J.\ C. \ Baez and J.\ Master, Open Petri nets. Available as \href{https://arxiv.org/abs/1808.05415}{arXiv:1808.05415}.
+
 \bibitem{BP} J.\ C.\ Baez and B.\ Pollard, A compositional framework for chemical reaction networks, in preparation.

### 2018-10-10 EquivCompFrameworks_20180911kc.tex
added some stuff about passive linear circuits

@@
 \subsection{Electrial circuits}
-
+In a previous work \cite{BP}, Fong and the first author used decorated cospans to construct a symmetric monoidal category of `open passive linear circuits'.
+Roughly speaking, given a field $k$, a passive linear circuit is given by a `$k$-graph' which is a diagram in $\mathrm{FinSet}$ of the form:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (B) at (1,0) {$E$};
+\node (C) at (2,0) {$V$};
+\node (A) at (0,0) {$k^+$};
+\path[->,font=\scriptsize,>=angle 90]
+(B)edge node[above] {$r$}(A)
+(B)edge[bend left] node[above]{$s$}(C)
+(B)edge[bend right] node[below]{$t$}(C);
+\end{tikzpicture}
+\]
+Here the finite sets $E$ and $V$ are the sets of edges and vertices, respectively, and if we take the field $k = \mathbb{R}$, the function $r \colon E \to \mathbb{R}^+$ assigns to each edge $e \in E$ a positive real number $r(e) \in \mathbb{R}^+$ which can be interpreted as the resistance at the edge $e$.
+An open passive linear circuit is then given by a cospan of finite sets
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (B) at (1,0) {$V$};
+\node (C) at (2,0) {$Y$};
+\node (A) at (0,0) {$X$};
+\path[->,font=\scriptsize,>=angle 90]
+(A)edge node[above] {$i$}(B)
+(C)edge node[above]{$o$}(B);
+\end{tikzpicture}
+\]
+where the apex $V$ is equipped with the structure of a passive linear circuit. See the original paper for more details \cite{BP}.
+
+Let $\mathrm{Graph}_k$ be the category whose objects are given by $k$-graphs and morphisms by morphisms of $k$-graphs, where a morphism of $k$-graphs is given by a pair of functions $f \colon E \to E^\prime$ and $g \colon V \to V^\prime$ between the edge sets and vertex sets, respectively, of two $k$-graphs that respect the source and target functions of each.
+In a previous work introducing structured cospans, the first two authors showed that the category $\mathrm{Graph}_k$ has finite colimits.
+We can then obtain a double category of open passive linear circuits by defining a left adjoint $L \colon \mathrm{Set} \to \mathrm{Graph}_k$ that assigns to a set $V$ the discrete electrical circuit $L(V)$ given by passive linear circuit with $V$ as its set of vertices and no edges.
+The resulting symmetric monoidal double category $_L \mathbb{C}\textnormal{sp}(\mathrm{Graph}_k)$ has:
+\begin{enumerate}
+\item{finite sets as objects,}
+\item{functions as vertical 1-morphisms,}
+\item{open pass linear circuits as horizontal 1-cells
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (B) at (1,0) {$V$};
+\node (C) at (2,0) {$Y$};
+\node (A) at (0,0) {$X$};
+\node (D) at (3,0) {$k^+$};
+\node (E) at (4,0) {$\mathbb{E}$};
+\node (F) at (5,0) {$\mathbb{V}$};
+\path[->,font=\scriptsize,>=angle 90]
+(E) edge node [above] {$r$} (D)
+(E) edge [bend left] node [above] {$s$} (F)
+(E) edge [bend right] node [below] {$t$} (F)
+(A)edge node[above] {$i$}(B)
+(C)edge node[above]{$o$}(B);
+\end{tikzpicture}
+\]
+and}
+\item{maps of cospans as 2-morphisms together with a map of passive linear circuits between the apices.
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$X_1$};
+\node (A') at (0,-1) {$X_2$};
+\node (C') at (2,-1) {$Y_2$};
+\node (B) at (1,0) {$V_1$};
+\node (C) at (2,0) {$Y_1$};
+\node (D) at (1,-1) {$V_2$};
+\node (E) at (3,0) {$k^+$};
+\node (E') at (3,-1) {$k^+$};
+\node (F) at (4,0) {$E_1$};
+\node (F') at (4,-1) {$E_2$};
+\node (G) at (5,0) {$V_1$};
+\node (G') at (5,-1) {$V_2$};
+\path[->,font=\scriptsize,>=angle 90]
+(F) edge node[above] {$r_1$} (E)
+(F) edge [bend left] node [above] {$s_1$} (G)
+(F) edge [bend right] node [below] {$t_1$} (G)
+(F') edge node[above] {$r_2$} (E')
+(F') edge [bend left] node [above] {$s_2$} (G')
+(F') edge [bend right] node [below] {$t_2$} (G')
+(A) edge node[above]{$i_1$} (B)
+(C) edge node[above]{$o_1$} (B)
+(A) edge node[left]{$h$} (A')
+(C) edge node[left]{$h^\prime$} (C')
+(C') edge node [above] {$o_2$} (D)
+(A') edge node [above] {$i_2$} (D)
+(B) edge node [left] {$g$} (D)
+(F) edge node [left] {$f$} (F')
+(G) edge node [right] {$g$} (G');
+\end{tikzpicture}
+\]
+}
+\end{enumerate}
+We can also obtain a similar double category using decorated cospans...
 \subsection{Markov processes}

### 2018-10-12 EquivCompFrameworks_20180911kc.tex
added more to passive linear circuit example

@@
 
-\subsection{Electrial circuits}
+\subsection{Passive linear circuits}
 In a previous work \cite{BP}, Fong and the first author used decorated cospans to construct a symmetric monoidal category of `open passive linear circuits'.
@@
 In a previous work introducing structured cospans, the first two authors showed that the category $\mathrm{Graph}_k$ has finite colimits.
-We can then obtain a double category of open passive linear circuits by defining a left adjoint $L \colon \mathrm{Set} \to \mathrm{Graph}_k$ that assigns to a set $V$ the discrete electrical circuit $L(V)$ given by passive linear circuit with $V$ as its set of vertices and no edges.
+We can then obtain a double category of open passive linear circuits by defining a left adjoint $L \colon \mathrm{Set} \to \mathrm{Graph}_k$ that assigns to a set $V$ the discrete passive linear circuit $L(V)$ given by passive linear circuit with $V$ as its set of vertices and no edges.
 The resulting symmetric monoidal double category $_L \mathbb{C}\textnormal{sp}(\mathrm{Graph}_k)$ has:
@@
 \end{enumerate}
-We can also obtain a similar double category using decorated cospans...
+We can also obtain a similar double category using decorated cospans: define a pseudofunctor $F \colon \mathrm{FinSet} \to \mathrm{Cat}$ that assigns to a finite set $V$ the category of all $k$-graph structures on the finite set $V$ and to a function $f \colon V \to V^\prime$ the corresponding functor $F(f) \colon F(V) \to F(V^\prime)$ between decoration categories.
+Both categories $\mathrm{FinSet}$ and $\mathrm{Cat}$ are symmetric monoidal and the pseudofunctor $F \colon \mathrm{FinSet} \to \mathrm{Cat}$ is symmetric lax monoidal, as given a $k$-graph structure on a finite set $V_1$ denoted by an element $K_1 \in F(V_1)$ and a $k$-graph structure on a finite set $V_2$ denoted by an element $K_2 \in F(V_2)$, we can consider the $k$-graph structures simultaneously as a single graph structure $\phi_{V_1,V_2}(K_1,K_2)$ on the finite set $V_1+V_2$.
+Thus we get a family of natural transformations $$\phi_{V_1,V_2} \colon F(V_1) \times F(V_2) \to F(V_1+V_2)$$ as well as a morphism $\phi \colon 1_{\mathrm{Graph}_k} \to F(\emptyset)$ which together satisfy coherence conditions of a monoidal functor.
+The braiding is also clear as the following diagram commutes:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (E) at (3,0) {$F(V_1) \times F(V_2)$};
+\node (G) at (5,0) {$F(V_2) \times F(V_1)$};
+\node (E') at (3,-1) {$F(V_1+V_2)$};
+\node (G') at (5,-1) {$F(V_2+V_1)$};
+\path[->,font=\scriptsize,>=angle 90]
+(E) edge node[left]{$\phi_{V_1,V_2}$} (E')
+(G) edge node[right]{$\phi_{V_2,V_1}$} (G')
+(E) edge node[above]{$\beta_{V_1,V_2}$} (G)
+(E') edge node[above]{$F(\beta_{V_1,V_2})$} (G');
+\end{tikzpicture}
+\]
+Thus the pseudofunctor $F$ is symmetric lax monoidal and so by Theorem \ref{DC} we get a symmetric monoidal double category $\mathbb{F}\textnormal{Cospan}(\mathrm{FinSet})$ which has:
+\begin{enumerate}
+\item{objects as finite sets,}
+\item{vertical 1-morphisms as functions,}
+\item{horizontal 1-cells as cospans of finite sets together with the structure of a $k$-graph given by an element of the image of the apex under the pseudofunctor $F$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (D) at (-3,0) {$U$};
+\node (E) at (-2,0) {$V$};
+\node (F) at (-1,0) {$W$};
+\node (A) at (0,0) {$K \in F(V)$};
+\path[->,font=\scriptsize,>=angle 90]
+(D) edge node [above] {$i$} (E)
+(F) edge node [above] {$o$} (E);
+\end{tikzpicture}
+\]
+and}
+\item{2-morphisms as maps of cospans of finite sets 
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (E) at (3,0) {$U$};
+\node (F) at (5,0) {$W$};
+\node (G) at (4,0) {$V$};
+\node (E') at (3,-1) {$U^\prime$};
+\node (F') at (5,-1) {$W^\prime$};
+\node (G') at (4,-1) {$V^\prime$};
+\node (A) at (6,0) {$K \in F(V)$};
+\node (B) at (6,-1) {$K^\prime \in F(V^\prime)$};
+\path[->,font=\scriptsize,>=angle 90]
+(F) edge node[above]{$o$} (G)
+(E) edge node[left]{$f$} (E')
+(F) edge node[right]{$g$} (F')
+(G) edge node[left]{$h$} (G')
+(E) edge node[above]{$i$} (G)
+(E') edge node[above]{$i^\prime$} (G')
+(F') edge node[above]{$o^\prime$} (G');
+\end{tikzpicture}
+\]
+together with a morphism of $k$-graphs $\iota \colon F(h)(K) \to K^\prime$ in $F(V^\prime)$.}
+\end{enumerate}
+These two double categories $_L \mathbb{C}\textnormal{sp}(\mathrm{Graph}_k)$ and $\mathbb{F}\textnormal{Cospan}(\mathrm{FinSet})$ are equivalent by Theorem \ref{Equiv}.
 \subsection{Markov processes}

### 2018-10-13 EquivCompFrameworks_20180911kc.tex
added a bit about the old decorated cospans version of open Markov processes

@@
 Let $\mathrm{Graph}_k$ be the category whose objects are given by $k$-graphs and morphisms by morphisms of $k$-graphs, where a morphism of $k$-graphs is given by a pair of functions $f \colon E \to E^\prime$ and $g \colon V \to V^\prime$ between the edge sets and vertex sets, respectively, of two $k$-graphs that respect the source and target functions of each.
-In a previous work introducing structured cospans, the first two authors showed that the category $\mathrm{Graph}_k$ has finite colimits.
+In a previous work introducing structured cospans, the first two authors showed that the category $\mathrm{Graph}_k$ has finite colimits \cite{BC2}.
 We can then obtain a double category of open passive linear circuits by defining a left adjoint $L \colon \mathrm{Set} \to \mathrm{Graph}_k$ that assigns to a set $V$ the discrete passive linear circuit $L(V)$ given by passive linear circuit with $V$ as its set of vertices and no edges.
@@
 \node (D) at (3,0) {$k^+$};
-\node (E) at (4,0) {$\mathbb{E}$};
-\node (F) at (5,0) {$\mathbb{V}$};
+\node (E) at (4,0) {$E$};
+\node (F) at (5,0) {$V$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \begin{tikzpicture}[scale=1.5]
-\node (E) at (3,0) {$U$};
-\node (F) at (5,0) {$W$};
-\node (G) at (4,0) {$V$};
-\node (E') at (3,-1) {$U^\prime$};
-\node (F') at (5,-1) {$W^\prime$};
-\node (G') at (4,-1) {$V^\prime$};
-\node (A) at (6,0) {$K \in F(V)$};
-\node (B) at (6,-1) {$K^\prime \in F(V^\prime)$};
-\path[->,font=\scriptsize,>=angle 90]
-(F) edge node[above]{$o$} (G)
+\node (E) at (3,0) {$U_1$};
+\node (F) at (5,0) {$W_1$};
+\node (G) at (4,0) {$V_1$};
+\node (E') at (3,-1) {$U_2$};
+\node (F') at (5,-1) {$W_2$};
+\node (G') at (4,-1) {$V_2$};
+\node (A) at (6,0) {$K_1 \in F(V_1)$};
+\node (B) at (6,-1) {$K_2 \in F(V_2)$};
+\path[->,font=\scriptsize,>=angle 90]
+(F) edge node[above]{$o_1$} (G)
 (E) edge node[left]{$f$} (E')
@@
 (G) edge node[left]{$h$} (G')
-(E) edge node[above]{$i$} (G)
-(E') edge node[above]{$i^\prime$} (G')
-(F') edge node[above]{$o^\prime$} (G');
-\end{tikzpicture}
-\]
-together with a morphism of $k$-graphs $\iota \colon F(h)(K) \to K^\prime$ in $F(V^\prime)$.}
+(E) edge node[above]{$i_1$} (G)
+(E') edge node[above]{$i_2$} (G')
+(F') edge node[above]{$o_2$} (G');
+\end{tikzpicture}
+\]
+together with a morphism of $k$-graphs $\iota \colon F(h)(K_1) \to K_2$ in $F(V_2)$.}
 \end{enumerate}
 These two double categories $_L \mathbb{C}\textnormal{sp}(\mathrm{Graph}_k)$ and $\mathbb{F}\textnormal{Cospan}(\mathrm{FinSet})$ are equivalent by Theorem \ref{Equiv}.
+
 \subsection{Markov processes}
+In another previous work \cite{BFP}, Fong, Pollard and the first author used decorated cospans to construct a symmetric monoidal category of `open Markov processes'.
+In this framework, a Markov process on a finite set $N$ is given by a diagram in $\mathrm{Set}$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (D) at (3,0) {$(0,\infty)$};
+\node (E) at (4,0) {$E$};
+\node (F) at (5,0) {$N$};
+\path[->,font=\scriptsize,>=angle 90]
+(E) edge node [above] {$r$} (D)
+(E) edge [bend left] node [above] {$s$} (F)
+(E) edge [bend right] node [below] {$t$} (F);
+\end{tikzpicture}
+\]
+where $E$ and $N$ are finite sets of edges and nodes, respectively.
+This is really just a special case of the previous example of passive linear circuits with $k = \mathbb{R}$.
+An open Markov process is then of course a cospan of finite sets where the apex is equipped with a Markov process:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (B) at (1,0) {$N$};
+\node (C) at (2,0) {$Y$};
+\node (A) at (0,0) {$X$};
+\node (D) at (3,0) {$k^+$};
+\node (E) at (4,0) {$E$};
+\node (F) at (5,0) {$N$};
+\path[->,font=\scriptsize,>=angle 90]
+(E) edge node [above] {$r$} (D)
+(E) edge [bend left] node [above] {$s$} (F)
+(E) edge [bend right] node [below] {$t$} (F)
+(A)edge node[above] {$i$}(B)
+(C)edge node[above]{$o$}(B);
+\end{tikzpicture}
+\]
+Fong, Pollard and the first author then add extra structure to open Markov processes such as populations at each node to obtain a symmetric monoidal category $\mathrm{DetlBalMark}$ of open Markov processes in `detailed balance' and then construct a black box functor $\blacksquare \colon \mathrm{DetBalMark} \to \mathrm{LinRel}$ that describes the steady state behavior of an open Markov process in detailed balance.
+On the way to doing this, one of the categories they construct using Fong's decorated cospan machinery is a symmetric monoidal category $\mathrm{Mark}$ which has:
+\begin{enumerate}
+\item{objects as finite sets and}
+\item{morphisms as isomorphism classes of open Markov processes, where composition is by pushout.}
+\end{enumerate}
+This is done using a symmetric lax monoidal functor $F \colon \mathrm{FinSet} \to \mathrm{Set}$ which assigns to each finite set $N$ the (large) set of all Markov processes on $N$ as defined above.
+Viewing this functor $F$ as now a symmetric lax monoidal pseudofunctor $F \colon \mathrm{FinSet} \to \mathrm{Cat}$ that assigns to a finite set $N$ the \emph{category} $F(N)$ of all Markov processes on $N$, we then get by Theorem \ref{DC} a symmetric monoidal double category $\mathbb{F}\textnormal{Cospan}(\mathrm{FinSet})$ which has:
+\begin{enumerate}
+\item{finite sets as objects,}
+\item{functions as vertical 1-morphisms,}
+\item{open Markov processes as horizontal 1-cells, and}
+\item{maps of open Markov processes as 2-morphisms which are given by maps of cospans of finite sets:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$X_1$};
+\node (A') at (0,-1) {$X_2$};
+\node (C') at (2,-1) {$Y_2$};
+\node (B) at (1,0) {$N_1$};
+\node (C) at (2,0) {$Y_1$};
+\node (D) at (1,-1) {$N_2$};
+\node (E) at (3,0) {$M_1 \in F(N_1)$};
+\node (E') at (3,-1) {$M_2 \in F(N_2)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i_1$} (B)
+(C) edge node[above]{$o_1$} (B)
+(A) edge node[left]{$f$} (A')
+(C) edge node[left]{$f^\prime$} (C')
+(C') edge node [above] {$o_2$} (D)
+(A') edge node [above] {$i_2$} (D)
+(B) edge node [left] {$h$} (D);
+\end{tikzpicture}
+\]
+together with a map of Markov processes $\iota \colon F(h)(M_1) \to M_2$ in $F(N_2)$, where a map between two Markov processes to be given by a pair of functions $(g,h)$ that make the following diagram commute:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (E) at (3,0) {$(0,\infty)$};
+\node (E') at (3,-1) {$(0,\infty)$};
+\node (F) at (4,0) {$E_1$};
+\node (F') at (4,-1) {$E_2$};
+\node (G) at (5,0) {$N_1$};
+\node (G') at (5,-1) {$N_2$};
+\path[->,font=\scriptsize,>=angle 90]
+(F) edge node[above] {$r_1$} (E)
+(F) edge [bend left] node [above] {$s_1$} (G)
+(F) edge [bend right] node [below] {$t_1$} (G)
+(F') edge node[above] {$r_2$} (E')
+(F') edge [bend left] node [above] {$s_2$} (G')
+(F') edge [bend right] node [below] {$t_2$} (G')
+(F) edge node [left] {$g$} (F')
+(G) edge node [right] {$h$} (G');
+\end{tikzpicture}
+\]
+}
+\end{enumerate}
+
+In a more recent work \cite{BC}, the first two authors have constructed a symmetric monoidal double category of `open Markov processes' and `coarse-grainings', where roughly speaking, a coarse-graining is a way of approximating a larger open Markov process by a smaller one by partitioning the set of states into `lumps'.
+This construction uses neither decorated cospans nor structured cospans.
 
@@
 \begin{tikzpicture}[scale=1.5]
-\node (E) at (3,0) {$L(X)$};
-\node (F) at (5,0) {$L(Y)$};
-\node (G) at (4,0) {$P$};
-\node (E') at (3,-1) {$L(X^\prime)$};
-\node (F') at (5,-1) {$L(Y^\prime)$};
-\node (G') at (4,-1) {$P^\prime$};
-\path[->,font=\scriptsize,>=angle 90]
-(F) edge node[above]{$O$} (G)
+\node (E) at (3,0) {$L(X_1)$};
+\node (F) at (5,0) {$L(Y_1)$};
+\node (G) at (4,0) {$P_1$};
+\node (E') at (3,-1) {$L(X_2)$};
+\node (F') at (5,-1) {$L(Y_2)$};
+\node (G') at (4,-1) {$P_2$};
+\path[->,font=\scriptsize,>=angle 90]
+(F) edge node[above]{$O_1$} (G)
 (E) edge node[left]{$L(f)$} (E')
@@
 (G) edge node[left]{$\alpha$} (G')
-(E) edge node[above]{$I$} (G)
-(E') edge node[above]{$I^\prime$} (G')
-(F') edge node[above]{$O^\prime$} (G');
+(E) edge node[above]{$I_1$} (G)
+(E') edge node[above]{$I_2$} (G')
+(F') edge node[above]{$O_2$} (G');
 \end{tikzpicture}
@@
 \begin{tikzpicture}[scale=1.5]
-\node (E) at (3,0) {$X$};
-\node (F) at (5,0) {$Y$};
-\node (G) at (4,0) {$Z$};
-\node (E') at (3,-1) {$X^\prime$};
-\node (F') at (5,-1) {$Y^\prime$};
-\node (G') at (4,-1) {$Z^\prime$};
-\node (A) at (6,0) {$P \in F(Z)$};
-\node (B) at (6,-1) {$P^\prime \in F(Z^\prime)$};
-\path[->,font=\scriptsize,>=angle 90]
-(F) edge node[above]{$o$} (G)
+\node (E) at (3,0) {$X_1$};
+\node (F) at (5,0) {$Y_1$};
+\node (G) at (4,0) {$Z_1$};
+\node (E') at (3,-1) {$X_2$};
+\node (F') at (5,-1) {$Y_2$};
+\node (G') at (4,-1) {$Z_2$};
+\node (A) at (6,0) {$P_1 \in F(Z_1)$};
+\node (B) at (6,-1) {$P_2 \in F(Z_2)$};
+\path[->,font=\scriptsize,>=angle 90]
+(F) edge node[above]{$o_1$} (G)
 (E) edge node[left]{$f$} (E')
@@
 (G) edge node[left]{$h$} (G')
-(E) edge node[above]{$i$} (G)
-(E') edge node[above]{$i^\prime$} (G')
-(F') edge node[above]{$o^\prime$} (G');
+(E) edge node[above]{$i_1$} (G)
+(E') edge node[above]{$i_2$} (G')
+(F') edge node[above]{$o_2$} (G');
 \end{tikzpicture}

### 2018-10-14 EquivCompFrameworks_20180911kc.tex
added a bit more to Markov process subsection

@@
 \node (A) at (0,0) {$X$};
-\node (D) at (3,0) {$k^+$};
+\node (D) at (3,0) {$(0,\infty)$};
 \node (E) at (4,0) {$E$};
@@
 \]
+For example:
+\[
+\begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=3.7cm,
+thick,main node/.style={circle,fill=white!20,draw,font=\sffamily\Large\bfseries},terminal/.style={circle,fill=blue!20,draw,font=\sffamily\Large\bfseries}]]
+\node[main node](1) {$b_1$};
+\node[main node](2) [left=0.8cm of 1] {$a_1$};.5
+\node[main node](3) [below right=0.7cm and 2.4cm of 1] {$c_2$};
+\node[main node](5) [above right=0.7cm and 2.4cm of 1] {$c_1$};
+\node[main node](4) [above right=0.7cm and 2.4cm of 3] {$d_1$};
+\node(A) [left=1cm of 2,circle,draw,inner sep=1pt,fill=gray,color=purple] {};
+\node(C) [right=1cm of 4,circle,draw,inner sep=1pt,fill=gray,color=purple] {};
+\node[left=1.25 cm of 2,color=purple] {$S$};
+\node[right=1.25 cm of 4,color=purple] {$T$};
+\path[every node/.style={font=\sffamily\small}, shorten >=1pt]
+(3) edge [bend right =15] node[below] {$e_6$} (4)
+(5) edge [bend left =15] node[below] {$e_5$} (4)
+(2) edge [bend left=15] node[below] {$e_1$} (1)
+(1) edge [bend left =15] node[below] {$e_2$} (5)
+(5) edge [bend right =15] node[right] {$e_4$} (3)
+(1) edge [bend right =15] node[below] {$e_3$} (3)
+(3) edge [bend right =15] node[above] {$6$} (4)
+(5) edge [bend left =15] node[above] {$6$} (4)
+(2) edge [bend left=15] node[above] {$5$} (1)
+(1) edge [bend left =15] node[above] {$8$} (5)
+(5) edge [bend right =15] node[left] {$4$} (3)
+(1) edge [bend right =15] node[above] {$8$} (3);
+\path[color=purple, very thick, shorten >=10pt, ->, >=stealth] (C) edge (4);
+\path[color=purple, very thick, shorten >=10pt, ->, >=stealth] (A) edge (2);
+\end{tikzpicture}
+\]
+Here we have an open Markov process on the finite set $N = \{a_1,b_1,c_1,c_2,d_1 \}$ with input and output sets given by the singletons $S$ and $T$, respectively.
+
 Fong, Pollard and the first author then add extra structure to open Markov processes such as populations at each node to obtain a symmetric monoidal category $\mathrm{DetlBalMark}$ of open Markov processes in `detailed balance' and then construct a black box functor $\blacksquare \colon \mathrm{DetBalMark} \to \mathrm{LinRel}$ that describes the steady state behavior of an open Markov process in detailed balance.
@@
 \end{enumerate}
+A symmetric monoidal double category of open Markov processes can also be obtained using structured cospans by defining a functor $L \colon \mathrm{FinSet} \to \mathrm{Mark}$ which assigns to a finite set $N$ the discrete Markov process $L(N)$ with no edges and to a function $f \colon N \to N^\prime$ the induced map of discrete Markov processes.
+Both categories $\mathrm{FinSet}$ and $\mathrm{Mark}$ have finite colimits and the functor $L$ is left adjoint to the forgetful functor $R \colon \mathrm{Mark} \to \mathrm{FinSet}$ which maps a Markov process to its underlying finite set of states.
+By Theorem \ref{SC}, we get a symmetric monoidal double category $_L \mathbb{C}\textnormal{sp}(\mathrm{Mark})$ which has:
+\begin{enumerate}
+\item{objects as finite sets,}
+\item{vertical 1-morphisms as functions,}
+\item{horizontal 1-cells as cospans in $\mathrm{Mark}$ of the form:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (D) at (-3,0) {$L(N_1)$};
+\node (E) at (-2,0) {$M$};
+\node (F) at (-1,0) {$L(N_2)$};
+\path[->,font=\scriptsize,>=angle 90]
+(D) edge node [above] {$I$} (E)
+(F) edge node [above] {$O$} (E);
+\end{tikzpicture}
+\]
+and}
+\item{2-morphisms as maps of cospans in $\mathrm{Mark}$.
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (E) at (3,0) {$L(N_1)$};
+\node (F) at (5,0) {$L(N_2)$};
+\node (G) at (4,0) {$M$};
+\node (E') at (3,-1) {$L(N_1^\prime)$};
+\node (F') at (5,-1) {$L(N_2^\prime)$};
+\node (G') at (4,-1) {$M^\prime$};
+\path[->,font=\scriptsize,>=angle 90]
+(F) edge node[above]{$O$} (G)
+(E) edge node[left]{$L(f_1)$} (E')
+(F) edge node[right]{$L(f_2)$} (F')
+(G) edge node[left]{$(g,h)$} (G')
+(E) edge node[above]{$I$} (G)
+(E') edge node[above]{$I^\prime$} (G')
+(F') edge node[above]{$O^\prime$} (G');
+\end{tikzpicture}
+\]
+}
+\end{enumerate}
+The two double categories $\mathbb{F}\textnormal{Cospan}(\mathrm{FinSet})$ and $_L \mathbb{C} \textnormal{sp}(\mathrm{Mark})$ are equivalent by Theorem \ref{Equiv}.
 

### 2018-10-20 EquivCompFrameworks_20180911kc.tex
messing with intro

@@
 The first two authors have developed a compositional framework well-suited for studying networks that are built out of finite sets equipped with extra stuff.
-This framework, which goes by the name of `structured cospans', utilizes double categories where the objects are seen as inputs and outputs, morphisms are `open networks', and 2-morphisms are maps between open networks.
+This framework, which goes by the name of `structured cospans', utilizes double categories where the objects are seen as inputs and outputs, horizontal 1-cells are `open networks', and 2-morphisms are maps between open networks.
 In this setup a functor $L \colon \textrm{A} \to \textrm{X}$, which is typically a left adjoint, is used to replace the objects and vertical 1-morphisms of a given double category $\mathbb{X}$ with the objects and morphisms, respectively, of the category $\textrm{A}$.
 Horizontal 1-cells are then cospans in $\textrm{X}$ of a particular form with 2-morphisms given by maps of these cospans.
-Fong has also developed a similar framework which also uses cospans and goes by the name of `decorated cospans'.
+Fong has also developed a similar framework utilizing cospans to study open networks which goes by the name of `decorated cospans'.
 In this setup, a lax monoidal functor $F \colon \textrm{A} \to \textrm{Set}$ is used to `decorate' the apices of cospans in $\textrm{A}$ with elements of $\textrm{Set}$ giving the cospans extra structure.
@@
 Applied category theory provides such an avenue and much work has been done towards this effort  \cite{BC,BCR,BF,BFP,BP,Cour,Fong,JM,LS,Yass}.
-One of the more recent frameworks developed suitable for studying networks is Fong's `decorated cospans' \cite{Fong}.
+One of the more recent frameworks developed that is suitable for studying networks is Fong's `decorated cospans' \cite{Fong}.
 A $\textbf{cospan}$ in any category is a diagram of the form:
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a$};
-\node (B) at (1,1) {$c$};
-\node (C) at (2,0) {$b$};
+\node (A) at (0,0) {$a_1$};
+\node (B) at (1,1) {$b$};
+\node (C) at (2,0) {$a_2$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-We call $c$ the $\textbf{apex}$ of the cospan and $a$ and $b$ the $\textbf{feet}$ of the cospan.
+We call $b$ the $\textbf{apex}$ of the cospan and $a_1$ and $a_2$ the $\textbf{feet}$ of the cospan.
 The morphisms $i$ and $o$ are called the $\textbf{legs}$.
-Cospans are ideal for realizing networks and more generally `open' systems where here open means each system or network comes with prescribed inputs and outputs which are represented by the feet of the cospan $a$ and $b$, respectively.
-Two open systems viewed as cospans such that the outputs of the first and the inputs of the second coincide can then naturally be composed via pushout.
+Cospans are ideal for realizing networks and more generally `open' systems where here open means that each system or network comes with prescribed inputs and outputs which are represented by the feet of the cospan $a$ and $b$, respectively.
+Two open systems viewed as cospans such that the outputs of the first and the inputs of the second coincide can then naturally be composed via pushout to obtain an open system whose inputs are that of the first and outputs are that of the second.
 For example, we can compose the above cospan with the following:
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$b$};
-\node (B) at (1,1) {$f$};
-\node (C) at (2,0) {$e$};
+\node (A) at (0,0) {$a_2$};
+\node (B) at (1,1) {$b^\prime$};
+\node (C) at (2,0) {$a_3$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a$};
-\node (B) at (1,1) {$c$};
-\node (C) at (2,0) {$b$};
-\node (D) at (3,1) {$f$};
-\node (E) at (4,0) {$e$};
-\node (F) at (2,2) {$c+_b f$};
-\node (G) at (2,1.25) {$c+f$};
+\node (A) at (0,0) {$a_1$};
+\node (B) at (1,1) {$b$};
+\node (C) at (2,0) {$a_2$};
+\node (D) at (3,1) {$b^\prime$};
+\node (E) at (4,0) {$a_3$};
+\node (F) at (2,2) {$b+_{a_2} b^\prime$};
+\node (G) at (2,1) {$b+b^\prime$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (E) edge node[above]{$o^\prime$} (D)
-(B) edge node[left]{$\psi j_c$} (F)
-(D) edge node[right]{$\psi j_f$} (F)
-(B) edge node[above]{$j_c$} (G)
-(D) edge node[above]{$j_f$} (G)
+(B) edge node[left]{$\psi j_b$} (F)
+(D) edge node[right]{$\psi j_{b^\prime}$} (F)
+(B) edge node[above]{$j_b$} (G)
+(D) edge node[above]{$j_{b^\prime}$} (G)
 (G) edge node [left] {$\psi$} (F);
@@
 
-In Fong's theory of decorated cospans, given a category $\textrm{A}$ with finite colmits, a symmetric lax monoidal functor $F \colon (\textrm{A},+,0) \to (\textrm{Set},\times,1)$ is used to `decorate' the apex of a cospan in $\textrm{A}$ with an element of the image of its apex under the functor $F$, in the case of the first cospan above, a morphism $d \colon 1 \to F(c)$.
-Here $F(c)$ is the collection of all $F$-decorations on the object $c$ and the morphism $d$ is selecting a particular one.
+In Fong's theory of decorated cospans, given a category $\textrm{A}$ with finite colmits, a symmetric lax monoidal functor $F \colon (\textrm{A},+,0) \to (\textrm{Set},\times,1)$ is used to `decorate' the apex of a cospan in $\textrm{A}$ with an element of the image of its apex under the functor $F$.
+In the case of the first cospan above, an element of the image of the apex under the functor $F$ is given by a morphism $d \colon 1 \to F(b)$.
+Here, $1$ is any terminal object in $\mathrm{Set}$, $F(b)$ is the collection of all $F$-decorations on the object $b$ and the morphism $d$ is selecting a particular one.
 Thus a decorated cospan is given by a pair:
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a$};
-\node (B) at (1,0) {$c$};
-\node (C) at (2,0) {$b$};
-\node (D) at (3,0) {$I$};
-\node (E) at (4,0) {$F(c)$};
+\node (A) at (0,0) {$a_1$};
+\node (B) at (1,0) {$b$};
+\node (C) at (2,0) {$a_2$};
+\node (D) at (3,0) {$1$};
+\node (E) at (4,0) {$F(b)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a$};
-\node (B) at (1,0) {$c$};
-\node (C) at (2,0) {$b$};
-\node (F) at (3,0) {$b$};
-\node (G) at (4,0) {$f$};
-\node (H) at (5,0) {$e$};
-\node (D) at (0.5,-0.5) {$I$};
-\node (E) at (1.5,-0.5) {$F(c)$};
-\node (D') at (3.5,-0.5) {$I$};
-\node (E') at (4.5,-0.5) {$F(f)$};
+\node (A) at (0,0) {$a_1$};
+\node (B) at (1,0) {$b$};
+\node (C) at (2,0) {$a_2$};
+\node (F) at (3,0) {$a_2$};
+\node (G) at (4,0) {$b^\prime$};
+\node (H) at (5,0) {$a_3$};
+\node (D) at (0.5,-0.5) {$1$};
+\node (E) at (1.5,-0.5) {$F(b)$};
+\node (D') at (3.5,-0.5) {$1$};
+\node (E') at (4.5,-0.5) {$F(b^\prime)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-we use the natural map from a coproduct to a pushout as well as the natural map that comes as part of the structure of a lax monoidal functor:
- $$1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{d_1 \times d_2} F(c) \times F(f) \xrightarrow{\phi_{c,f}} F(c+ f) \xrightarrow{F(j_{c,f})} F(c+_b f).$$
-
+we use the natural map from a coproduct to a pushout as well as the structure maps, or `laxators', that come as part of the structure of a lax monoidal functor:
+ $$1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{d_1 \times d_2} F(b) \times F(b^\prime) \xrightarrow{\phi_{b,b^\prime}} F(b+ b^\prime) \xrightarrow{F(j_{b,b^\prime})} F(b+_{a_2} b^\prime).$$
 From this symmetric lax monoidal functor $F \colon \textrm{A} \to \mathrm{Set}$, Fong then constructs a symmetric monoidal category $F\textnormal{Cospan}(\mathrm{A})$ which has:
@@
 \item{objects as those of $\mathrm{A}$ and}
-\item{morphisms as isomorphism classes of $F$-decorated cospans, where an $F$-decorated cospan is given as above, and two $F$-decorated cospans are in the same isomorphism class if there exists an isomorphism between the apices such that the following diagrams commute:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a$};
-\node (B) at (1,1) {$c$};
-\node (B') at (1,-1) {$c^\prime$};
-\node (C) at (2,0) {$b$};
+\item{morphisms as isomorphism classes of $F$-decorated cospans, where an $F$-decorated cospan is given as above, and two $F$-decorated cospans are in the same isomorphism class if there exists an isomorphism $f \colon b \to b^\prime$ between the apices such that the following diagrams commute:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$a_1$};
+\node (B) at (1,1) {$b$};
+\node (B') at (1,-1) {$b^\prime$};
+\node (C) at (2,0) {$a_2$};
 \node (D) at (3,0) {$1$};
-\node (E) at (4,0.5) {$F(c)$};
-\node (E') at (4,-0.5) {$F(c^\prime)$};
+\node (E) at (4,0.5) {$F(b)$};
+\node (E') at (4,-0.5) {$F(b^\prime)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (B) edge node [left] {$f$} (B')
+(B) edge node [right] {$\sim$} (B')
 (D) edge node [above] {$d$} (E)
@@
 \end{enumerate}
-There are some subtleties to this approach.
-To illustrate, consider the example where $F \colon \textrm{FinSet} \to \textrm{Set}$ is the symmetric lax monoidal functor that assigns to a finite set $N$ the (large) set of all possible graph structures on the finite set $N$, where a graph structure on $N$ is given by a diagram in $\textrm{Set}$ of the form:
+
+As an example, let $F \colon \textrm{FinSet} \to \textrm{Set}$ be the symmetric lax monoidal functor that assigns to a finite set $b$ the (large) set of all possible graph structures on the finite set $b$, where a graph structure on $b$ is given by a diagram in $\textrm{Set}$ of the form:
 \[
@@
 \node (A) at (0,0) {$E$};
-\node (B) at (1,0) {$N.$};
+\node (B) at (1,0) {$b.$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-Let $N=\{ v_1,v_2 \}$ be a two element set.
-Then one element of the set $F(N)$, in other words, one possible decoration, which is a graph structure, on the set $N$ is given by a single edge $e$ whose source and target are $v_1$ and $v_2$, respectively.
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$v_1$};
-\node (B) at (1,0) {$v_2$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$e$} (B);
-\end{tikzpicture}
-\]
-Denote this element of $F(N)$ as $d$. We could label the edge $e$ something else, for instance, $e^\prime$, and this single edge would another element of $F(N)$.
+Let $b=\{ v_1,v_2 \}$ be a two element set.
+Then one element of the (large) set $F(b)$, which is the collection of all graph structures on the finite set $b$, is given by a single edge $e$ whose source and target are $v_1$ and $v_2$, respectively.
+\[
+\begin{tikzpicture}
+  [scale=.8,auto=left]
+  \node [style={circle,fill=teal}] (n1) at (1,10) {$v_1$};
+  \node[style={circle,fill=teal}] (n2) at (4,10)  {$v_2$};
+\path[->,font=\scriptsize,>=angle 90]
+(n1) edge node[above]{$e$} (n2);
+\end{tikzpicture}
+\]
+%\[
+%\begin{tikzpicture}[scale=1.5]
+%\node (A) at (0,0) {$v_1$};
+%\node (B) at (1,0) {$v_2$};
+%\path[->,font=\scriptsize,>=angle 90]
+%(A) edge node[above]{$e$} (B);
+%\end{tikzpicture}
+%\]
+Denote this element of $F(b)$ as $d \colon 1 \to F(b)$.
+Let $a_1=\{ 1 \}$ and $a_2=\{2,3\}$ and define functions $i \colon a_1 \to b$ and $o \colon a_2 \to b$ by $i(1)=v_1$ and $o(2)=o(3)=v_2$.
+Then we have an $F$-decorated cospan:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$a_1$};
+\node (B) at (1,0) {$b$};
+\node (C) at (2,0) {$a_2$};
+\node (D) at (3,0) {$1$};
+\node (E) at (4,0) {$F(b)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i$} (B)
+(C) edge node[above]{$o$} (B)
+(D) edge node [above] {$d$} (E);
+\end{tikzpicture}
+\]
+which is given by the open graph:
+\[
+\begin{tikzpicture}
+  [scale=.8,auto=left]
+\node (a) at (-2,10) {$1$};
+\node (b) at (7,10.5) {$2$};
+\node (c) at (7,9.5) {$3$};
+\node (i) at (-0.5,11) {$i$};
+\node (o) at (5.5,11) {$o$};
+  \node [style={circle,fill=teal}] (n1) at (1,10) {$v_1$};
+  \node[style={circle,fill=teal}] (n2) at (4,10)  {$v_2$};
+\path[->,font=\scriptsize,>=angle 90]
+(a) edge[dashed] node[above] {$$} (n1)
+(b) edge[dashed,bend right] node[below] {$$} (n2)
+(c) edge[dashed,bend left] node[above] {$$} (n2)
+(n1) edge node[above]{$e$} (n2);
+\end{tikzpicture}
+\]
+We could label the edge $e$ something else, for instance, $e^\prime$, and this single edge would another element of $F(N)$.
 \[

### 2018-10-21 EquivCompFrameworks_20180911kc.tex
more messing with the intro

@@
 (a) edge[dashed] node[above] {$$} (n1)
-(b) edge[dashed,bend right] node[below] {$$} (n2)
-(c) edge[dashed,bend left] node[above] {$$} (n2)
+(b) edge[dashed] node[below] {$$} (n2)
+(c) edge[dashed] node[above] {$$} (n2)
 (n1) edge node[above]{$e$} (n2);
@@
 \]
+We can compose this open graph with another whose set inputs coincide with the set of outputs of the above open graph, namely the set $a_2=\{2,3\}$. For example:
+\[
+\begin{tikzpicture}
+  [scale=.8,auto=left]
+%\node (a) at (-2,10) {$1$};
+\node (b) at (7,10.5) {$2$};
+\node (c) at (7,9.5) {$3$};
+%\node (i) at (-0.5,11) {$i$};
+\node (o) at (8.5,11.5) {$i^\prime$};
+\node (d) at (16,10) {$4$};
+\node (e) at (14.5,11.5) {$o^\prime$};
+  \node [style={circle,fill=teal}] (n1) at (10,11.5) {$v_4$};
+  \node[style={circle,fill=teal}] (n2) at (10,8.5)  {$v_3$};
+  \node[style={circle,fill=teal}] (n3) at (13,10)  {$v_5$};
+\path[->,font=\scriptsize,>=angle 90]
+%(a) edge[dashed] node[above] {$$} (n1)
+(b) edge[dashed] node[below] {$$} (n1)
+(c) edge[dashed] node[above] {$$} (n2)
+(n1) edge[bend left] node[above]{$e_2$} (n3)
+(n3) edge[bend left] node[below]{$e_3$} (n2)
+(n2) edge[bend left] node[left]{$e_1$} (n1)
+(d) edge[dashed] node[above]{$$}(n3);
+\end{tikzpicture}
+\]
+This second open graph can be represented by the $F$-decorated cospan:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$a_2$};
+\node (B) at (1,0) {$b^\prime$};
+\node (C) at (2,0) {$a_3$};
+\node (D) at (3,0) {$1$};
+\node (E) at (4,0) {$F(b^\prime)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i^\prime$} (B)
+(C) edge node[above]{$o^\prime$} (B)
+(D) edge node [above] {$d^\prime$} (E);
+\end{tikzpicture}
+\]
+The composite of these two open graphs is then given by:
+\[
+\begin{tikzpicture}
+  [scale=.8,auto=left]
+\node (a) at (-2,10) {$1$};
+%\node (b) at (7,10.5) {$2$};
+\node (c) at (10,10) {$4$};
+\node (i) at (-0.5,11) {$i$};
+\node (o) at (8.5,11) {$o^\prime$};
+  \node [style={circle,fill=teal}] (n1) at (1,10) {$v_1$};
+  \node[style={circle,fill=teal}] (n2) at (4,10)  {$v_2$};
+  \node[style={circle,fill=teal}] (n3) at (7,10)  {$v_5$};
+\path[->,font=\scriptsize,>=angle 90]
+(a) edge[dashed] node[above] {$$} (n1)
+%(b) edge[dashed] node[below] {$$} (n2)
+(c) edge[dashed] node[above] {$$} (n3)
+(n1) edge node[above]{$e$} (n2)
+(n2) edge[bend left] node[above]{$e_2$} (n3)
+(n2) edge[loop below]node{$e_1$} (n2)
+(n3) edge[bend left] node[below]{$e_3$} (n2);
+\end{tikzpicture}
+\]
+where we identify $v_2=v_3=v_4$ in taking the pushout of the two cospans of finite sets. The composite open graph is represented by the $F$-decorated cospan:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$a_1$};
+\node (B) at (1.25,0) {$b+_{a_2}b^\prime$};
+\node (C) at (2.5,0) {$a_3$};
+\node (D) at (3,0) {$1$};
+\node (E) at (4,0) {$F(b+_{a_2}b^\prime)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$\psi j_b i$} (B)
+(C) edge node[above]{$\psi j_{b^\prime} o^\prime$} (B)
+(D) edge node [above] {$d''$} (E);
+\end{tikzpicture}
+\]
+where $j$ is the natural map into a coproduct and $\psi$ the natural map from a coproduct into a pushout.
+
+We can also consider the above two open graphs in parallel:
+\[
+\begin{tikzpicture}
+  [scale=.8,auto=left]
+\node (a') at (7,12.5) {$1$};
+\node (b') at (16,12.5) {$2$};
+\node (c') at (16,11.5) {$3$};
+\node (i') at (8.5,13.5) {$i+i^\prime$};
+\node (o') at (14.5,13.5) {$o+o^\prime$};
+  \node [style={circle,fill=teal}] (n1') at (10,13) {$v_1$};
+  \node[style={circle,fill=teal}] (n2') at (13,13)  {$v_2$};
+\node (b) at (7,11.5) {$2$};
+\node (c) at (7,10.5) {$3$};
+\node (d) at (16,10.5) {$4$};
+  \node [style={circle,fill=teal}] (n1) at (10,11.5) {$v_4$};
+  \node[style={circle,fill=teal}] (n2) at (10,8.5)  {$v_3$};
+  \node[style={circle,fill=teal}] (n3) at (13,10)  {$v_5$};
+\path[->,font=\scriptsize,>=angle 90]
+(a') edge[dashed] node[above] {$$} (n1')
+(b') edge[dashed] node[below] {$$} (n2')
+(c') edge[dashed] node[above] {$$} (n2')
+(n1') edge node[above]{$e$} (n2')
+(b) edge[dashed] node[below] {$$} (n1)
+(c) edge[dashed] node[above] {$$} (n2)
+(n1) edge[bend left] node[above]{$e_2$} (n3)
+(n3) edge[bend left] node[below]{$e_3$} (n2)
+(n2) edge[bend left] node[left]{$e_1$} (n1)
+(d) edge[dashed] node[above]{$$}(n3);
+\end{tikzpicture}
+\]
+which is represented by the tensor product of the above two $F$-decorated cospans:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$a_1+a_2$};
+\node (B) at (1.25,0) {$b+b^\prime$};
+\node (C) at (2.5,0) {$a_2+a_3$};
+\node (D) at (3.5,0) {$1$};
+\node (E) at (4.5,0) {$F(b+b^\prime)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i+i^\prime$} (B)
+(C) edge node[above]{$o+ o^\prime$} (B)
+(D) edge node [above] {$d+d^\prime$} (E);
+\end{tikzpicture}
+\]
+
+There are some subtleties to this framework...
 We could label the edge $e$ something else, for instance, $e^\prime$, and this single edge would another element of $F(N)$.

### 2018-10-23 EquivCompFrameworks_20180911kc.tex
changing bold's to mathbf's

@@
 \input{Equiv_preamble.tex}
+\usepackage[foot]{amsaddr}
+\usepackage{comment}
 
@@
 
+\author{John\ C.\ Baez$^{*,\bullet}$, Kenny Courser$^*$, and Christina Vasilakopoulou$^*$}
+\address{$^*$Department of Mathematics, University of California, Riverside CA, USA 92521}
+\address{$^\bullet$Centre for Quantum Technologies, National University of Singapore, Singapore 117543}
+\email{baez@ucr.edu, kcour001@ucr.edu, vasilak@ucr.edu}
+
 \begin{document}
+\begin{abstract}
+\noindent
+The first two authors have developed a compositional framework well-suited for studying networks that are built out of finite sets equipped with extra stuff.
+This framework, which goes by the name of `structured cospans', utilizes double categories where the objects are seen as inputs and outputs, horizontal 1-cells are `open networks', and 2-morphisms are maps between open networks.
+In this setup a functor $L \colon \textrm{A} \to \textrm{X}$, which is typically a left adjoint, is used to replace the objects and vertical 1-morphisms of a given double category $\mathbb{X}$ with the objects and morphisms, respectively, of the category $\textrm{A}$.
+Horizontal 1-cells are then cospans in $\textrm{X}$ of a particular form with 2-morphisms given by maps of these cospans.
+Fong has also developed a similar framework utilizing cospans to study open networks which goes by the name of `decorated cospans'.
+In this setup, a lax monoidal functor $F \colon \textrm{A} \to \textrm{Set}$ is used to `decorate' the apices of cospans in $\textrm{A}$ with elements of $\textrm{Set}$ giving the cospans extra structure.
+Using a slight variation of Fong's framework, we prove that these two frameworks are equivalent in the situation where a left adjoint can be obtained from a lax monoidal pseudofunctor using a well known construction of Grothendieck.
+\end{abstract}
+
 \maketitle
 
+\begin{comment}
 \begin{center}   
@@
 \end{center}   
-
-\begin{abstract}
-\noindent
-The first two authors have developed a compositional framework well-suited for studying networks that are built out of finite sets equipped with extra stuff.
-This framework, which goes by the name of `structured cospans', utilizes double categories where the objects are seen as inputs and outputs, horizontal 1-cells are `open networks', and 2-morphisms are maps between open networks.
-In this setup a functor $L \colon \textrm{A} \to \textrm{X}$, which is typically a left adjoint, is used to replace the objects and vertical 1-morphisms of a given double category $\mathbb{X}$ with the objects and morphisms, respectively, of the category $\textrm{A}$.
-Horizontal 1-cells are then cospans in $\textrm{X}$ of a particular form with 2-morphisms given by maps of these cospans.
-Fong has also developed a similar framework utilizing cospans to study open networks which goes by the name of `decorated cospans'.
-In this setup, a lax monoidal functor $F \colon \textrm{A} \to \textrm{Set}$ is used to `decorate' the apices of cospans in $\textrm{A}$ with elements of $\textrm{Set}$ giving the cospans extra structure.
-Using a slight variation of Fong's framework, we prove that these two frameworks are equivalent in the situation where a left adjoint can be obtained from a lax monoidal pseudofunctor using a well known construction of Grothendieck.
-\end{abstract}
+\end{comment}
+
+\tableofcontents
 
@@
 
-One approach to remedying this nuisance is to instead view $F$ as a functor $F \colon \textrm{A} \to \bold{Cat}$ and then consider $F(c)$ not as a \emph{set} of decorations on the element $c$ but as a \emph{category} of decorations on the element $c$.
+One approach to remedying this nuisance is to instead view $F$ as a functor $F \colon \textrm{A} \to \mathbf{Cat}$ and then consider $F(c)$ not as a \emph{set} of decorations on the element $c$ but as a \emph{category} of decorations on the element $c$.
 Then one can construct a similar symmetric monoidal category similar to Fong's, which will be called $D(H(\mathbb{F}\textnormal{Cospan}(\mathrm{A})))$ for reasons that will be explained later.
@@
 \begin{thm}
-Let $\mathrm{A}$ be a category with finite colimits and $F \colon \mathrm{A} \to \bold{Cat}$ a lax monoidal pseudofunctor.
+Let $\mathrm{A}$ be a category with finite colimits and $F \colon \mathrm{A} \to \mathbf{Cat}$ a lax monoidal pseudofunctor.
 Then there exists a double category $\mathbb{F} \textnormal{Cospan}(\mathrm{A})$ which has:
@@
 \]
-where $!_c \in F(c)$ is the trivial decoration on $c$ given by the composition of the unique map $F(!) \colon F(0) \to F(c)$ and the morphism $\phi \colon 1 \to F(0)$  which comes from the symmetric lax monoidal pseudofunctor $F \colon \mathrm{A} \to \bold{Cat}$.
+where $!_c \in F(c)$ is the trivial decoration on $c$ given by the composition of the unique map $F(!) \colon F(0) \to F(c)$ and the morphism $\phi \colon 1 \to F(0)$  which comes from the symmetric lax monoidal pseudofunctor $F \colon \mathrm{A} \to \mathbf{Cat}$.
 For morphisms, the structure functor $U$ is defined as:
@@
 $$1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{d \times d^\prime} F(c) \times F(c^\prime) \xrightarrow{\phi_{c,c^\prime}} F(c+c^\prime) \xrightarrow{F(\psi)} F(c+_{b}c^\prime)$$
-where $\psi \colon c + c^\prime \to c+_b c^\prime$ is the natural map from the coproduct to the pushout and $\phi_{c,c^\prime} \colon F(c) \times F(c^\prime) \to F(c+c^\prime)$ is the natural transformation of the symmetric lax monoidal pseudofunctor $F \colon \mathrm{A} \to \bold{Cat}$.
+where $\psi \colon c + c^\prime \to c+_b c^\prime$ is the natural map from the coproduct to the pushout and $\phi_{c,c^\prime} \colon F(c) \times F(c^\prime) \to F(c+c^\prime)$ is the natural transformation of the symmetric lax monoidal pseudofunctor $F \colon \mathrm{A} \to \mathbf{Cat}$.
 Denoting the first and second of these horizontal 1-cells as $M$ and $N$, respectively, the source and target structure functors satisfy the equations $S(N \odot M)=S(M)$ and $T(N \odot M)=T(N)$.
@@
 \]
-and then multiply these viewed as two 2-morphisms in $\bold{Cat}$ which results in:
+and then multiply these viewed as two 2-morphisms in $\mathbf{Cat}$ which results in:
 \[
@@
 As is usual concerning the interchange law of double categories of this nature, only the `interior' of the two compositions appears different, but the two morphisms $(h_1^\prime +_{g^\prime} h_2^\prime)(h_1 +_g h_2) \colon c+_b e \to c'' +_{b''} e''$ and $(h_1^\prime h_1) +_{g^\prime g} (h_2^\prime h_2) \colon c+_b e \to c'' +_{b''}e''$ are the same universal map realized in two different ways.
-The two morphisms of decorations are two compositions of 2-morphisms in $\bold{Cat}$ for which the interchange law already holds, and as a result, the morphisms $$(\iota_{1,2}^\prime \iota_{1,2}) \colon F((h_1^\prime +_{g^\prime} h_2^\prime)(h_1 +_g h_2))(d_{1,2}) \to d_{1,2}''$$ and $$(\iota_1^\prime \iota_1,\iota_2^\prime \iota_2) \colon F((h_1^\prime h_1)+_{g^\prime g} (h_2^\prime h_2))(d_{1,2}) \to d_{1,2}''$$ are also the same.
+The two morphisms of decorations are two compositions of 2-morphisms in $\mathbf{Cat}$ for which the interchange law already holds, and as a result, the morphisms $$(\iota_{1,2}^\prime \iota_{1,2}) \colon F((h_1^\prime +_{g^\prime} h_2^\prime)(h_1 +_g h_2))(d_{1,2}) \to d_{1,2}''$$ and $$(\iota_1^\prime \iota_1,\iota_2^\prime \iota_2) \colon F((h_1^\prime h_1)+_{g^\prime g} (h_2^\prime h_2))(d_{1,2}) \to d_{1,2}''$$ are also the same.
 \end{proof}
@@
 \begin{thm}\label{DC}
-Let $\mathrm{A}$ be a category with finite colimits and $F \colon \mathrm{A} \to \bold{Cat}$ a symmetric lax monoidal pseudofunctor.
+Let $\mathrm{A}$ be a category with finite colimits and $F \colon \mathrm{A} \to \mathbf{Cat}$ a symmetric lax monoidal pseudofunctor.
 Then the double category $\mathbb{F}\textnormal{Cospan}(\mathrm{A})$ is symmetric monoidal.
@@
 where $0$ is the monoidal unit of $\mathrm{A}$ and $!
-\colon 1 \to F(0)$ is the morphism which is part of the structure of the symmetric lax monoidal pseudofunctor $F \colon \mathrm{A} \to \bold{Cat}$.
+\colon 1 \to F(0)$ is the morphism which is part of the structure of the symmetric lax monoidal pseudofunctor $F \colon \mathrm{A} \to \mathbf{Cat}$.
 Tensoring an object with the monoidal unit, say, on the left:
@@
 
-%Again, let $F \colon \bold{FinSet} \to \bold{Set}$ be the symmetric lax monoidal functor that maps a finite set $N$ to the large set of all possible graph structures whose underlying set of vertices is $N$.
-Then a result of Fong \cite{Fong} yields a symmetric monoidal category $F\textnormal{Cospan}(\bold{FinSet})$ which has:
+%Again, let $F \colon \mathbf{FinSet} \to \mathbf{Set}$ be the symmetric lax monoidal functor that maps a finite set $N$ to the large set of all possible graph structures whose underlying set of vertices is $N$.
+Then a result of Fong \cite{Fong} yields a symmetric monoidal category $F\textnormal{Cospan}(\mathbf{FinSet})$ which has:
 %\begin{enumerate}
@@
 \begin{cor}
-Given a symmetric lax monoidal pseudofunctor $F \colon \mathrm{A} \to \bold{Cat}$ where $\mathrm{A}$ is a category with finite colimits and whose monoidal structure is given by binary coproducts, there exists a symmetric monoidal category $D(H(\mathbb{F}\textnormal{Cospan}(\mathrm{A})))$ which has:
+Given a symmetric lax monoidal pseudofunctor $F \colon \mathrm{A} \to \mathbf{Cat}$ where $\mathrm{A}$ is a category with finite colimits and whose monoidal structure is given by binary coproducts, there exists a symmetric monoidal category $D(H(\mathbb{F}\textnormal{Cospan}(\mathrm{A})))$ which has:
 \begin{enumerate}
@@
 \section{Maps of decorated cospan double categories}
-Let $F \colon \mathrm{A} \to \bold{Cat}$ be a symmetric lax monoidal pseudofunctor.
+Let $F \colon \mathrm{A} \to \mathbf{Cat}$ be a symmetric lax monoidal pseudofunctor.
 Then by Theorem \ref{main1} of the previous section, we get a symmetric monoidal double category $\mathbb{F}\textnormal{Cospan}(\mathrm{A})$.
@@
 \end{enumerate}
-Given another symmetric lax monoidal pseudofunctor $F^\prime \colon \mathrm{A^\prime} \to \bold{Cat}$, we can obtain another symmetric monoidal double category $\mathbb{F^\prime}\textnormal{Cospan}(\mathrm{A^\prime})$.
+Given another symmetric lax monoidal pseudofunctor $F^\prime \colon \mathrm{A^\prime} \to \mathbf{Cat}$, we can obtain another symmetric monoidal double category $\mathbb{F^\prime}\textnormal{Cospan}(\mathrm{A^\prime})$.
 Then a map from $\mathbb{F}\textnormal{Cospan}(\mathrm{A})$ to $\mathbb{F^\prime}\textnormal{Cospan}(\mathrm{A^\prime})$ will be a double functor $\mathbb{H} \colon \mathbb{F}\textnormal{Cospan}(\mathrm{A}) \to \mathbb{F^\prime}\textnormal{Cospan}(\mathrm{A^\prime})$ whose object component is given by a finite colimit preserving functor $\mathbb{H}_0 = H \colon \mathrm{A} \to \mathrm{A^\prime}$ and whose arrow component is given by a functor $\mathbb{H}_1$ defined on horizontal 1-cells by:
@@
 \]
-where $E \colon \bold{Cat} \to \bold{Cat}$ is a terminal category preserving 2-functor such that the following diagram commutes:
+where $E \colon \mathbf{Cat} \to \mathbf{Cat}$ is a terminal category preserving 2-functor such that the following diagram commutes:
 \[
@@
 \node (A) at (0,0) {$\mathrm{A}$};
-\node (B) at (1,0) {$\bold{Cat}$};
+\node (B) at (1,0) {$\mathbf{Cat}$};
 \node (C) at (0,-1) {$\mathrm{A^\prime}$};
-\node (D) at (1,-1) {$\bold{Cat}$};
+\node (D) at (1,-1) {$\mathbf{Cat}$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-Recall that we can think of the element $d \in F(c)$ as a morphism $d \colon 1 \to F(c)$ and the morphism $\iota \colon F(h)(d) \to d^\prime$ of $F(c^\prime)$ as a 2-morphism  in $\bold{Cat}$:
+Recall that we can think of the element $d \in F(c)$ as a morphism $d \colon 1 \to F(c)$ and the morphism $\iota \colon F(h)(d) \to d^\prime$ of $F(c^\prime)$ as a 2-morphism  in $\mathbf{Cat}$:
 \[
@@
 \]
-Applying the terminal category preserving 2-functor $E \colon \bold{Cat} \to \bold{Cat}$ to this diagram yields:
+Applying the terminal category preserving 2-functor $E \colon \mathbf{Cat} \to \mathbf{Cat}$ to this diagram yields:
 \[
@@
 \section{From pseudofunctors to left adjoints}
-In this section we investigate the necessary conditions to obtain a category $\mathrm{X}$ and a left adjoint $L \colon \mathrm{A} \to \mathrm{X}$ from a category $\mathrm{A}$ with finite colimits and a symmetric lax monoidal pseudofunctor $F \colon \mathrm{A} \to \bold{Cat}$.
+In this section we investigate the necessary conditions to obtain a category $\mathrm{X}$ and a left adjoint $L \colon \mathrm{A} \to \mathrm{X}$ from a category $\mathrm{A}$ with finite colimits and a symmetric lax monoidal pseudofunctor $F \colon \mathrm{A} \to \mathbf{Cat}$.
 The main tool that allows us to do this will be the Grothendieck construction which we recall:
@@
 \begin{defn}
-Let $\bold{Cat}_{\textnormal{lax},\star}$ denote the \define{2-category of lax-pointed categories} which has:
+Let $\mathbf{Cat}_{\textnormal{lax},\star}$ denote the \define{2-category of lax-pointed categories} which has:
 \begin{enumerate}
@@
 \begin{defn}
-Given a pseudofunctor $F \colon \mathrm{A} \to \bold{Cat}$, the \define{Grothendieck construction of} $F$ is given by the `strict 2-pullback' of the following cospan:
+Given a pseudofunctor $F \colon \mathrm{A} \to \mathbf{Cat}$, the \define{Grothendieck construction of} $F$ is given by the `strict 2-pullback' of the following cospan:
  \[
@@
 \node (A) at (0,0) {$\mathrm{A}$};
-\node (B) at (1,-1) {$\bold{Cat}$};
-\node (C) at (2,0) {$\bold{Cat}_{\textnormal{lax},\star}$};
+\node (B) at (1,-1) {$\mathbf{Cat}$};
+\node (C) at (2,0) {$\mathbf{Cat}_{\textnormal{lax},\star}$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-where $P \colon \bold{Cat}_{\textnormal{lax},\star} \to \bold{Cat}$ is the forgetful functor. This means that $\int F$ is a category which has:
+where $P \colon \mathbf{Cat}_{\textnormal{lax},\star} \to \mathbf{Cat}$ is the forgetful functor. This means that $\int F$ is a category which has:
 \begin{enumerate}
@@
 \begin{defn}
-Given bicategories $\bold{A}$ and $\bold{X}$ and 2-functors (possibly lax or oplax) $(F,\phi),(G,\psi) \colon \bold{A} \to \bold{X}$, a \define{pseudonatural transformation} $\sigma \colon (F,\phi) \to (G,\psi)$ consists of:
+Given bicategories $\mathbf{A}$ and $\mathbf{X}$ and 2-functors (possibly lax or oplax) $(F,\phi),(G,\psi) \colon \mathbf{A} \to \mathbf{X}$, a \define{pseudonatural transformation} $\sigma \colon (F,\phi) \to (G,\psi)$ consists of:
 \begin{enumerate}
-\item{for each object $a \in \bold{A}$, a morphism $\sigma_a \colon F(a) \to G(a)$ in $\bold{X}$ and}
-\item{for every pair of objects $a$ and $b$ of $\bold{A}$, we have natural isomorphisms:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$\bold{A}(a,b)$};
-\node (B) at (2,0) {$\bold{X}(F(a),F(b))$};
-\node (C) at (0,-1) {$\bold{X}(G(a),G(b))$};
-\node (D) at (2,-1) {$\bold{X}(F(a),G(b))$};
+\item{for each object $a \in \mathbf{A}$, a morphism $\sigma_a \colon F(a) \to G(a)$ in $\mathbf{X}$ and}
+\item{for every pair of objects $a$ and $b$ of $\mathbf{A}$, we have natural isomorphisms:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$\mathbf{A}(a,b)$};
+\node (B) at (2,0) {$\mathbf{X}(F(a),F(b))$};
+\node (C) at (0,-1) {$\mathbf{X}(G(a),G(b))$};
+\node (D) at (2,-1) {$\mathbf{X}(F(a),G(b))$};
 \node (E) at (1,-0.5) {$\sigma_{a,b} \Nearrow$};
@@
 where $(\sigma_a)^*$ and $(\sigma_b)_*$ are the functors induced by precomposition and postcompositon, respectively.
-Thus for each morphism $f \colon a \to b$ in $\bold{A}$, we have an invertible 2-morphism $\sigma_f \colon G(f) \sigma_a \xrightarrow{\sim} \sigma_{b} F(f)$ in $\bold{X}$:
+Thus for each morphism $f \colon a \to b$ in $\mathbf{A}$, we have an invertible 2-morphism $\sigma_f \colon G(f) \sigma_a \xrightarrow{\sim} \sigma_{b} F(f)$ in $\mathbf{X}$:
 \[
@@
 \end{enumerate}
-such that for each composable pair of morphisms $f \colon a \to b$ and $g \colon b \to c$ of $\bold{A}$, the following diagrams commute:
+such that for each composable pair of morphisms $f \colon a \to b$ and $g \colon b \to c$ of $\mathbf{A}$, the following diagrams commute:
 \[
@@
 
-Let $[\bold{A},\bold{Cat}]_{\textnormal{pseudo}}$ denote the 2-category which has:
+Let $[\mathbf{A},\mathbf{Cat}]_{\textnormal{pseudo}}$ denote the 2-category which has:
 \begin{enumerate}
-\item{objects as pseudofunctors $(F,\phi) \colon \bold{A} \to \bold{Cat}$,}
-\item{a morphism from a pseudofunctor $(F,\phi) \colon \bold{A} \to \bold{Cat}$ to another $(G,\psi) \colon \bold{A} \to \bold{Cat}$ is a pseudonatural transformation $\sigma \colon (F,\phi) \to (G,\psi)$, and}
+\item{objects as pseudofunctors $(F,\phi) \colon \mathbf{A} \to \mathbf{Cat}$,}
+\item{a morphism from a pseudofunctor $(F,\phi) \colon \mathbf{A} \to \mathbf{Cat}$ to another $(G,\psi) \colon \mathbf{A} \to \mathbf{Cat}$ is a pseudonatural transformation $\sigma \colon (F,\phi) \to (G,\psi)$, and}
 \item{2-morphisms as modifications.}
@@
 %\begin{defn}
-%Let $P \colon \bold{D} \to \mathrm{A}$ be a functor.
-A morphism $f \colon d_{1} \to d_{2}$ in the category $\bold{D}$ is \textbf{cartesian (with respect to the functor P)} if for any object $d^\prime$ in $\bold{D}$ and morphism $g \colon d^\prime \to d_{2}$ and every $p \colon P(d^\prime) \to P(d_{1})$ such that $P(g)=P(f)p$, there exists a unique $h \colon d^\prime \to d_{1}$ such that $g=fh$ and $p=P(h)$.
+%Let $P \colon \mathbf{D} \to \mathrm{A}$ be a functor.
+A morphism $f \colon d_{1} \to d_{2}$ in the category $\mathbf{D}$ is \textbf{cartesian (with respect to the functor P)} if for any object $d^\prime$ in $\mathbf{D}$ and morphism $g \colon d^\prime \to d_{2}$ and every $p \colon P(d^\prime) \to P(d_{1})$ such that $P(g)=P(f)p$, there exists a unique $h \colon d^\prime \to d_{1}$ such that $g=fh$ and $p=P(h)$.
 %\[
@@
 \begin{defn}
-A functor $P \colon \mathrm{D} \to \mathrm{A}$ is a \textbf{(Grothendieck) opfibration} if for any object $d$ in $\bold{D}$ and morphism $f \colon c \to P(d)$ there exists a cocartesian morphism $\phi \colon d^\prime \to d$ such that $P(\phi)=f$.
+A functor $P \colon \mathrm{D} \to \mathrm{A}$ is a \textbf{(Grothendieck) opfibration} if for any object $d$ in $\mathbf{D}$ and morphism $f \colon c \to P(d)$ there exists a cocartesian morphism $\phi \colon d^\prime \to d$ such that $P(\phi)=f$.
 \end{defn}
@@
 
-The 2-category Opfib$(\mathrm{A})$ is a 2-subcategory of $\bold{Cat}/ \mathrm{A}$ where $\bold{Cat} / \mathrm{A}$ is the 2-category of functors over $\mathrm{A}$.
-The Grothendieck construction is a 2-functor $\int F \colon [ \mathrm{A},\bold{Cat}] \to \bold{Cat}/ \mathrm{A}$ which factors through the image of the embedding $\textnormal{Opfib}(\mathrm{A}) \hookrightarrow \bold{Cat} / \mathrm{A}$: $$\int F \colon [ \mathrm{A}, \bold{Cat} ] \to \textnormal{Opfib}(\mathrm{A}) \hookrightarrow \bold{Cat} / \mathrm{A}.$$
+The 2-category Opfib$(\mathrm{A})$ is a 2-subcategory of $\mathbf{Cat}/ \mathrm{A}$ where $\mathbf{Cat} / \mathrm{A}$ is the 2-category of functors over $\mathrm{A}$.
+The Grothendieck construction is a 2-functor $\int F \colon [ \mathrm{A},\mathbf{Cat}] \to \mathbf{Cat}/ \mathrm{A}$ which factors through the image of the embedding $\textnormal{Opfib}(\mathrm{A}) \hookrightarrow \mathbf{Cat} / \mathrm{A}$: $$\int F \colon [ \mathrm{A}, \mathbf{Cat} ] \to \textnormal{Opfib}(\mathrm{A}) \hookrightarrow \mathbf{Cat} / \mathrm{A}.$$
 
@@
 \section{An equivalence of symmetric monoidal double categories}
-In this section we prove that two different frameworks which utilize symmetric monoidal double categories, namely decorated cospans and `structured cospans', are equivalent under the conditions required from the previous section that allow for a left adjoint $L \colon \mathrm{A} \to \mathrm{X}$ to be obtained from a symmetric lax monoidal pseudofunctor $F \colon \mathrm{A} \to \bold{Cat}$.
+In this section we prove that two different frameworks which utilize symmetric monoidal double categories, namely decorated cospans and `structured cospans', are equivalent under the conditions required from the previous section that allow for a left adjoint $L \colon \mathrm{A} \to \mathrm{X}$ to be obtained from a symmetric lax monoidal pseudofunctor $F \colon \mathrm{A} \to \mathbf{Cat}$.
 The double category version of decorataed cospans is given in Section \ref{DecCospansDoublecat}.
@@
 \end{proof}
-In the previous section, we started with a symmetric lax monoidal pseudofunctor $F \colon \mathrm{A} \to \bold{Cat}$ and created a symmetric monoidal double category $\mathbb{F}\textnormal{Cospan}(\mathrm{A})$ which has:
+In the previous section, we started with a symmetric lax monoidal pseudofunctor $F \colon \mathrm{A} \to \mathbf{Cat}$ and created a symmetric monoidal double category $\mathbb{F}\textnormal{Cospan}(\mathrm{A})$ which has:
 \begin{enumerate}
@@
 \begin{thm}\label{Equiv}
-Let $\mathrm{A}$ and $\mathrm{X}$ be categories with finite colimits and $F \colon \mathrm{A} \to \bold{Cat}$ a symmetric lax monoidal pseudofunctor.
+Let $\mathrm{A}$ and $\mathrm{X}$ be categories with finite colimits and $F \colon \mathrm{A} \to \mathbf{Cat}$ a symmetric lax monoidal pseudofunctor.
 Let $L \colon \mathrm{A} \to \int{F} \cong \mathrm{X}$ be the left adjoint of the Grothendieck construction $R \colon \int{F} \to \mathrm{A}$ of $F$.
@@
 \]
-together with a morphism $\iota \colon F(R(h))(x) \to x^\prime$ in $F(R(x^\prime)) \subseteq \mathrm{X}$ which comes from the Grothendieck construction of the pseudofunctor $F \colon \mathrm{A} \to \bold{Cat}$.
+together with a morphism $\iota \colon F(R(h))(x) \to x^\prime$ in $F(R(x^\prime)) \subseteq \mathrm{X}$ which comes from the Grothendieck construction of the pseudofunctor $F \colon \mathrm{A} \to \mathbf{Cat}$.
 First, to see that this functor is essentially surjective, given a horizontal 1-cell in $\mathbb{F}\textnormal{Cospan}(\mathrm{A})$:
@@
 \]
-we can find a 2-isomorphism in $\mathbb{F}\textnormal{Cospan}(\mathrm{A})$ whose codomain is the above horizontal 1-cell and whose domain is the image of the following horizontal 1-cell in $_L \mathbb{C}\textnormal{sp}(\bold{D})$:
+we can find a 2-isomorphism in $\mathbb{F}\textnormal{Cospan}(\mathrm{A})$ whose codomain is the above horizontal 1-cell and whose domain is the image of the following horizontal 1-cell in $_L \mathbb{C}\textnormal{sp}(\mathbf{D})$:
 \[
@@
 
-To show that the double functor $\mathbb{E}$ is fully faithful, we need to show that the map  $$\mathbb{E}_1 \colon _f { _L \mathbb{C}\textnormal{sp}(\mathrm{X})}_g(M,N) \to _{\mathbb{E}(f)} {\mathbb{F}\textnormal{Cospan}(\mathrm{A})}_{\mathbb{E}(g)}(\mathbb{E}(M),\mathbb{E}(N))$$ is bijective for arbitrary vertical 1-morphisms $f$ and $g$ and horizontal 1-cells $M$ and $N$ of $_L \mathbb{C}\textnormal{sp}(\bold{D})$.
+To show that the double functor $\mathbb{E}$ is fully faithful, we need to show that the map  $$\mathbb{E}_1 \colon _f { _L \mathbb{C}\textnormal{sp}(\mathrm{X})}_g(M,N) \to _{\mathbb{E}(f)} {\mathbb{F}\textnormal{Cospan}(\mathrm{A})}_{\mathbb{E}(g)}(\mathbb{E}(M),\mathbb{E}(N))$$ is bijective for arbitrary vertical 1-morphisms $f$ and $g$ and horizontal 1-cells $M$ and $N$ of $_L \mathbb{C}\textnormal{sp}(\mathbf{D})$.
 Consider a 2-morphism in $_L \mathbb{C}\textnormal{sp}(\mathrm{X})$:
@@
 \]
-where $!_{1_{\mathrm{A}}} = \phi \colon 1 \to F(1_\mathrm{A})$ is the trivial decoration which comes from the structure of the symmetric lax monoidal pseudofunctor $F \colon \mathrm{A} \to \bold{Cat}$.
+where $!_{1_{\mathrm{A}}} = \phi \colon 1 \to F(1_\mathrm{A})$ is the trivial decoration which comes from the structure of the symmetric lax monoidal pseudofunctor $F \colon \mathrm{A} \to \mathbf{Cat}$.
 The horizontal 1-cell $U_{1_{_L \mathbb{C}\textnormal{sp}(\mathrm{X})}}$ is given by:
@@
 Master and the first author show the existence of a left adjoint $L \colon \mathrm{Set} \to \mathrm{Petri}$ where $\mathrm{Petri}$ is the category whose objects are Petri nets and whose `morphisms are morphisms of Petri nets'.
-They also show that $\mathrm{Petri}$ has finite colimits and thus using Theorem \ref{SC} obtain a symmetric monoidal double category $\mathbb{O}\bold{pen}(\mathrm{Petri})$ of open Petri nets which has:
+They also show that $\mathrm{Petri}$ has finite colimits and thus using Theorem \ref{SC} obtain a symmetric monoidal double category $\mathbb{O}\mathbf{pen}(\mathrm{Petri})$ of open Petri nets which has:
 \begin{enumerate}
@@
 \end{enumerate}
-Thus we have a symmetric monoidal double category $\mathbb{O}\bold{pen}(\mathrm{Petri})$ of open Petri nets obtained from structured cospans and a symmetric monoidal double category $\mathbb{F}\textnormal{Cospan}(\mathrm{Set})$ of open Petri nets obtain from decorated cospans, and of course, we have an equivalence $\mathbb{O}\bold{pen}(\mathrm{Petri}) \sim \mathbb{F}\textnormal{Cospan}(\mathrm{Set})$ of symmetric monoidal double categories by Theorem \ref{Equiv}.
+Thus we have a symmetric monoidal double category $\mathbb{O}\mathbf{pen}(\mathrm{Petri})$ of open Petri nets obtained from structured cospans and a symmetric monoidal double category $\mathbb{F}\textnormal{Cospan}(\mathrm{Set})$ of open Petri nets obtain from decorated cospans, and of course, we have an equivalence $\mathbb{O}\mathbf{pen}(\mathrm{Petri}) \sim \mathbb{F}\textnormal{Cospan}(\mathrm{Set})$ of symmetric monoidal double categories by Theorem \ref{Equiv}.
 
@@
 \begin{defn}
-A \textbf{pseudo double category} $\lD$, or $\textbf{double category}$ for short, consists of a category of objects $\bold{D_{0}}$ and a category of arrows $\bold{D_{1}}$ with the following functors
+A \textbf{pseudo double category} $\lD$, or $\textbf{double category}$ for short, consists of a category of objects $\mathbf{D_{0}}$ and a category of arrows $\mathbf{D_{1}}$ with the following functors
 \begin{center}
-$U\colon \bold{D_{0}} \to \bold{D_{1}}$\\
-$S,T \colon \bold{D_{1}} \rightrightarrows \bold{D_{0}}$\\
-$\odot \colon \bold{D_{1}} \times_{\bold{D_{0}}} \bold{D_{1}} \to \bold{D_{1}}$ (where the pullback is taken over $\bold{D_{1}} \xrightarrow[]{T} \bold{D_{0}} \xleftarrow[]{S} \bold{D_{1}}$) \\
+$U\colon \mathbf{D_{0}} \to \mathbf{D_{1}}$\\
+$S,T \colon \mathbf{D_{1}} \rightrightarrows \mathbf{D_{0}}$\\
+$\odot \colon \mathbf{D_{1}} \times_{\mathbf{D_{0}}} \mathbf{D_{1}} \to \mathbf{D_{1}}$ (where the pullback is taken over $\mathbf{D_{1}} \xrightarrow[]{T} \mathbf{D_{0}} \xleftarrow[]{S} \mathbf{D_{1}}$) \\
 \end{center}
@@
 such that $S(\alpha), S(\lambda), S(\rho), T(\alpha), T(\lambda)$ and $T(\rho)$ are all identities and that the coherence axioms of a monoidal category are satisfied.
-Following the notation of Shulman, objects of $\bold{D_{0}}$ are called $\textbf{0-cells}$ and morphisms of $\bold{D_{0}}$ are called $\textbf{vertical 1-morphisms}$.
-Objects of $\bold{D_{1}}$ are called $\textbf{horizontal 1-cells}$ and morphisms of $\bold{D_{1}}$ are called $\textbf{2-morphisms}$.
-The morphisms of $\bold{D_{0}}$, which are vertical 1-morphisms, will be denoted $f \colon A \to C$ and we denote a 1-cell $M$ with $S(M)=A,T(M)=B$ by $M \colon A \to B$.
-Then a 2-morphism $a \colon M \to N$ of $\bold{D_{1}}$ with $S(a)=f,T(a)=g$ would look like:
+Following the notation of Shulman, objects of $\mathbf{D_{0}}$ are called $\textbf{0-cells}$ and morphisms of $\mathbf{D_{0}}$ are called $\textbf{vertical 1-morphisms}$.
+Objects of $\mathbf{D_{1}}$ are called $\textbf{horizontal 1-cells}$ and morphisms of $\mathbf{D_{1}}$ are called $\textbf{2-morphisms}$.
+The morphisms of $\mathbf{D_{0}}$, which are vertical 1-morphisms, will be denoted $f \colon A \to C$ and we denote a 1-cell $M$ with $S(M)=A,T(M)=B$ by $M \colon A \to B$.
+Then a 2-morphism $a \colon M \to N$ of $\mathbf{D_{1}}$ with $S(a)=f,T(a)=g$ would look like:
 \[
@@
 The key difference between a `strict' double category and a pseudo double category is that in a pseudo double category, horizontal composition is associative and unital only up to natural isomorphism.
-Equivalently, as a double category can be viewed as a category internal to $\bold{Cat}$, we can view a pseudo double category as a category `weakly' internal to $\bold{Cat}$.
+Equivalently, as a double category can be viewed as a category internal to $\mathbf{Cat}$, we can view a pseudo double category as a category `weakly' internal to $\mathbf{Cat}$.
 We will sometimes omit the word pseudo and simply say double category.
@@
 \begin{enumerate}
-\item $\bold{D_{0}}$ and $\bold{D_{1}}$ are both monoidal categories.
-\item If $I$ is the monoidal unit of $\bold{D_{0}}$, then $U_I$ is the
-  monoidal unit of $\bold{D_{1}}$.
+\item $\mathbf{D_{0}}$ and $\mathbf{D_{1}}$ are both monoidal categories.
+\item If $I$ is the monoidal unit of $\mathbf{D_{0}}$, then $U_I$ is the
+  monoidal unit of $\mathbf{D_{1}}$.
 \item The functors $S$ and $T$ are strict monoidal, i.e.\ $S(M\ten N)
@@
 
-%\bibitem{Lack} S.\ Lack, Limits for lax morphisms, \emph{Applied Categorical Structures} $\bold{30}$ (2005), 189--203.
+%\bibitem{Lack} S.\ Lack, Limits for lax morphisms, \emph{Applied Categorical Structures} $\mathbf{30}$ (2005), 189--203.
 Available %at \href{http://maths.mq.edu.au/~slack/papers/talgl.pdf}{http://maths.mq.edu.au/$\sim$slack/papers/talgl.pdf}.
@@
 
-%\bibitem{Pol} B.\ Pollard, Open Markov processes: A compositional perspective on non-equilibrium steady states in biology, %%%\emph{Entropy} $\bold{18}$ (2016), 140.
+%\bibitem{Pol} B.\ Pollard, Open Markov processes: A compositional perspective on non-equilibrium steady states in biology, %%%\emph{Entropy} $\mathbf{18}$ (2016), 140.
 Available as \href{http://arxiv.org/abs/1601.00711}{arXiv:1601.00711}.

### 2018-10-23 EquivCompFrameworks_20180911kc.tex
small things here and there

@@
 \usepackage[foot]{amsaddr}
-\usepackage{comment}
 
@@
 \tableofcontents
+
+\section*{Various issues-in-progress}
+{\chris If Kenny likes, we can use this as a section for all the current issues that need to be resolved, or what we are currently working on or something!}
 
@@
 We now show that these two symmetric monoidal double categories are equivalent.
+
+{\chris Statement of Theorem, and proof, will be heavily edited soon!}
 \begin{thm}\label{Equiv}
@@
 \section{Acknowledgements}
-Daniel Cicala, person that Christina emailed about lax slice category?
+Daniel Cicala, person that Christina emailed about lax slice category? {\chris did you use it after all?}
 \begin{thebibliography}{100}

### 2018-10-27 EquivCompFrameworks_20180911kc.tex
reminder
another reminder
more polishing of intro

@@
 {\chris If Kenny likes, we can use this as a section for all the current issues that need to be resolved, or what we are currently working on or something!}
+\begin{itemize}
+\item Fix notation for structured and decorated cospans.
+\end{itemize}
 
@@
 In Fong's theory of decorated cospans, given a category $\textrm{A}$ with finite colmits, a symmetric lax monoidal functor $F \colon (\textrm{A},+,0) \to (\textrm{Set},\times,1)$ is used to `decorate' the apex of a cospan in $\textrm{A}$ with an element of the image of its apex under the functor $F$.
-In the case of the first cospan above, an element of the image of the apex under the functor $F$ is given by a morphism $d \colon 1 \to F(b)$.
+In the case of the first cospan above, an element of the image of the apex under the functor $F$ is given by a morphism $d \colon 1 \to F(b)$, and we call $d$ a \textbf{decoration} on $b$.
 Here, $1$ is any terminal object in $\mathrm{Set}$, $F(b)$ is the collection of all $F$-decorations on the object $b$ and the morphism $d$ is selecting a particular one.
@@
 
-There are some subtleties to this framework...
+There are some subtleties to this framework; consider two decorated cospans with the same inputs and outputs.
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$a_1$};
+\node (B) at (1,0) {$b$};
+\node (C) at (2,0) {$a_2$};
+\node (F) at (3,0) {$a_1$};
+\node (G) at (4,0) {$b^\prime$};
+\node (H) at (5,0) {$a_2$};
+\node (D) at (0.5,-0.5) {$1$};
+\node (E) at (1.5,-0.5) {$F(b)$};
+\node (D') at (3.5,-0.5) {$1$};
+\node (E') at (4.5,-0.5) {$F(b^\prime)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i$} (B)
+(C) edge node[above]{$o$} (B)
+(F) edge node[above]{$i^\prime$} (G)
+(H) edge node[above]{$o^\prime$} (G)
+(D) edge node [above] {$d$} (E)
+(D') edge node [above] {$d^\prime$} (E');
+\end{tikzpicture}
+\]
+For these two $F$-decorated cospans to be in the same isomorphism class, the following triangle is to commute:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (D) at (3,0) {$1$};
+\node (E) at (4,0.5) {$F(b)$};
+\node (E') at (4,-0.5) {$F(b^\prime)$};
+\path[->,font=\scriptsize,>=angle 90]
+(D) edge node [above] {$d$} (E)
+(D) edge node [below] {$d^\prime$} (E')
+(E) edge node [right] {$F(f)$} (E');
+\end{tikzpicture}
+\]
+This commutative triangle in $\mathsf{Set}$ in the context of the symmetric lax monoidal functor $F \colon \mathsf{FinSet} \to \mathsf{Set}$ says the following: given a decoration $d \in F(b)$, which is a graph structure with underlying set of vertices $b$, the function $F(f)$ pushes forward the graph structure $d$ to the graph structure $d^\prime \in F(b^\prime)$ with underlying set of vertices $b^\prime$, and \emph{precisely} this graph structure.
+The graph structure is given by set of edges of $d$.
+For example, if we take $b = \{v_1 ,v_2\}$ as before and let $d \in F(b)$ be given by:
+\[
+\begin{tikzpicture}
+  [scale=.8,auto=left]
+\node (a) at (-2,10) {$1$};
+\node (b) at (7,10) {$2$};
+\node (i) at (-0.5,11) {$i$};
+\node (o) at (5.5,11) {$o$};
+  \node [style={circle,fill=teal}] (n1) at (1,10) {$v_1$};
+  \node[style={circle,fill=teal}] (n2) at (4,10)  {$v_2$};
+\path[->,font=\scriptsize,>=angle 90]
+(a) edge[dashed] node[above] {$$} (n1)
+(b) edge[dashed] node[below] {$$} (n2)
+(n1) edge node[above]{$e$} (n2);
+\end{tikzpicture}
+\]
+Let $b^\prime = \{w_1,w_2\}$ and a define bijection $f \colon b \to b^\prime$ by $f(v_i)=w_i$ for $i=1,2$.
+Then the requirement $F(f)(d)=d^\prime$ says that $d^\prime \in F(b^\prime)$ must be given by:
+\[
+\begin{tikzpicture}
+  [scale=.8,auto=left]
+\node (a) at (-2,10) {$1$};
+\node (b) at (7,10) {$2$};
+\node (i) at (-0.5,11) {$i^\prime$};
+\node (o) at (5.5,11) {$o^\prime$};
+  \node [style={circle,fill=teal}] (n1) at (1,10) {$w_1$};
+  \node[style={circle,fill=teal}] (n2) at (4,10)  {$w_2$};
+\path[->,font=\scriptsize,>=angle 90]
+(a) edge[dashed] node[above] {$$} (n1)
+(b) edge[dashed] node[below] {$$} (n2)
+(n1) edge node[above]{$e$} (n2);
+\end{tikzpicture}
+\]
+The point to be made here is that the single edge of $d^\prime$ must also be $e$.
+If we were to label it say, $e^\prime$, there is no bijection $f \colon b \to b^\prime$ such that the triangle on the right commutes, and hence no isomorphism between these two $F$-decorated cospans.
+\[
+\begin{tikzpicture}
+  [scale=.8,auto=left]
+\node (D) at (9,11.5) {$1$};
+\node (E) at (11,12.5) {$F(b)$};
+\node (E') at (11,10.5) {$F(b^\prime)$};
+\node (a) at (-2,11.5) {$1$};
+\node (b) at (7,11.5) {$2$};
+\node (i) at (-0.5,12.5) {$i$};
+\node (o) at (5.5,12.5) {$o$};
+\node (i') at (-0.5,10.5) {$i^\prime$};
+\node (o') at (5.5,10.5) {$o^\prime$};
+\node (A) at (2.5,11.5) {$\nexists F(f) \Downarrow$};
+  \node [style={circle,fill=teal}] (n1) at (1,13) {$v_1$};
+  \node[style={circle,fill=teal}] (n2) at (4,13)  {$v_2$};
+  \node [style={circle,fill=red}] (n1') at (1,10) {$w_1$};
+  \node[style={circle,fill=red}] (n2') at (4,10)  {$w_2$};
+\path[->,font=\scriptsize,>=angle 90]
+(D) edge node [above] {$d$} (E)
+(D) edge node [below] {$d^\prime$} (E')
+(E) edge[dashed] node [right] {$\nexists F(f)$} (E')
+(a) edge[dashed] node[above] {$$} (n1)
+(b) edge[dashed] node[above] {$$} (n2)
+(a) edge[dashed] node[below] {$$} (n1')
+(b) edge[dashed] node[below] {$$} (n2')
+(n1) edge node[above]{$e$} (n2)
+(n1') edge node[above]{$e^\prime$} (n2');
+\end{tikzpicture}
+\]
+Thus these two $F$-decorated cospans constitute distinct isomorphism classes. This nuisance is amplified when viewed from a higher categorical perspective.
+
+The second author in a previous work extended...
+
 We could label the edge $e$ something else, for instance, $e^\prime$, and this single edge would another element of $F(N)$.

### 2018-11-13 EquivCompFrameworks_20180911kc.tex
small

@@
 
-\begin{comment}
-\begin{center}   
- % {\bf Structured cospans \\}   
-  \vspace{0.3cm}
-  {\em John\ C.\ Baez \\}
-  \vspace{0.3cm}
-  {\small
- Department of Mathematics \\
-    University of California \\
-  Riverside CA, USA 92521 \\ and \\
- Centre for Quantum Technologies  \\
-  National University of Singapore \\
-    Singapore 117543  \\    } 
- \vspace{0.4cm}
-{\em Kenny Courser \\}
-\vspace{0.3cm}
-   {\small
-  Department of Mathematics \\
-  University of California \\
-  Riverside CA, USA 92521 \\}
-  \vspace{0.4cm}   
-{\em Christina Vasilakopoulou \\}
-\vspace{0.3cm}
-   {\small
-  Department of Mathematics \\
-  University of California \\
-  Riverside CA, USA 92521 \\}
-  \vspace{0.3cm}   
-  {\small email: baez@math.ucr.edu, courser@math.ucr.edu, vasilak@ucr.edu\\} 
-  \vspace{0.3cm}   
-  {\small \today}
-  \vspace{0.3cm}   
-\end{center}   
-\end{comment}
-
 \tableofcontents
@@
 \item Fix notation for structured and decorated cospans.
+\item {\chris I think structured cospans should be introduced/recalled way earlier! This is a paper that compares the two,
+and both should be presented early.}
 \end{itemize}

### 2018-12-30 EquivCompFrameworks_20180911kc.tex
Continuing work on intro

@@
 
-The second author in a previous work extended...
-
-We could label the edge $e$ something else, for instance, $e^\prime$, and this single edge would another element of $F(N)$.
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$v_1$};
-\node (B) at (1,0) {$v_2$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$e^\prime$} (B);
-\end{tikzpicture}
-\]
-Denote this second element of $F(N)$ as $d^\prime$.
-These two graphs constitute distinct isomorphism classes in the symmetric monoidal category $F$Cospan$(\textrm{FinSet})$, as $f=\id_N$ and thus $F(f)=\id_{F(N)}$, but clearly $d \neq d^\prime$.
-The issue here is that the functor $F$ is decorating each finite set $N$ not only with extra structure, but with extra \emph{stuff}.
-Moreover, the finite set $N$ is being decorated with \emph{different} stuff in each instance and this difference in stuff is not entirely detected by the function $F(f)$.
-This phenomenon doesn't occur when the decorations only involve extra structure, and this has been utilized in other works \cite{BFP,BP,Yass}.
-
-One approach to remedying this nuisance is to instead view $F$ as a functor $F \colon \textrm{A} \to \mathbf{Cat}$ and then consider $F(c)$ not as a \emph{set} of decorations on the element $c$ but as a \emph{category} of decorations on the element $c$.
-Then one can construct a similar symmetric monoidal category similar to Fong's, which will be called $D(H(\mathbb{F}\textnormal{Cospan}(\mathrm{A})))$ for reasons that will be explained later.
-This symmetric monoidal category will have:
+In a previous work, the second author extended Fong's theory of decorated cospans to a symmetric monoidal bicategory of decorated cospans \cite{Cour}.
+Namely, under the same hypotheses used by Fong amounting to a category $\mathsf{A}$ with finite colimits and a symmetric lax monoidal functor $F \colon (\mathsf{A},+,0) \to (\mathsf{Set}, \times, 1)$, there exists a symmetric monoidal bicategory $F\mathbf{Cospan}(\mathsf{A})$ which has:
+\begin{enumerate}
+\item objects as those of $\mathsf{A}$,
+\item morphisms as $F$-decorated cospans in $\mathsf{A}$, which again are pairs
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$a_1$};
+\node (B) at (1,0) {$b$};
+\node (C) at (2,0) {$a_2$};
+\node (D) at (3,0) {$1$};
+\node (E) at (4,0) {$F(b)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i$} (B)
+(C) edge node[above]{$o$} (B)
+(D) edge node [above] {$d$} (E);
+\end{tikzpicture}
+\]
+and
+\item 2-morphisms as pairs of commuting diagrams where the left diagram is a map of cospans in $\mathsf{A}$ and the right diagram is a commutative triangle in $\mathsf{Set}$.
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$a_1$};
+\node (B) at (1,1) {$b$};
+\node (B') at (1,-1) {$b^\prime$};
+\node (C) at (2,0) {$a_2$};
+\node (D) at (3,0) {$1$};
+\node (E) at (4,0.5) {$F(b)$};
+\node (E') at (4,-0.5) {$F(b^\prime)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i$} (B)
+(C) edge node[above]{$o$} (B)
+(A) edge node[below]{$i^\prime$} (B')
+(C) edge node[below]{$o^\prime$} (B')
+(B) edge node [left] {$f$} (B')
+%(B) edge node [right] {$\sim$} (B')
+(D) edge node [above] {$d$} (E)
+(D) edge node [below] {$d^\prime$} (E')
+(E) edge node [right] {$F(f)$} (E');
+\end{tikzpicture}
+\]
+\end{enumerate}
+Returning to the previous example where we take the functor $F$ to be the functor $F \colon \mathsf{FinSet} \to \mathsf{Set}$, the situation becomes more dire.
+Previously, in the ordinary symmetric monoidal category $F$Cospan$(\mathsf{FinSet})$ the following two $F$-decorated cospans resided in distinct isomorphism classes:
+\[
+\begin{tikzpicture}
+  [scale=.8,auto=left]
+%\node (D) at (9,11.5) {$1$};
+\node (E) at (9,13) {$d \in F(b)$};
+\node (E') at (9,10) {$d^\prime \in F(b^\prime)$};
+\node (a) at (-2,13) {$1$};
+\node (a') at (-2,10) {$1$};
+\node (b) at (7,13) {$2$};
+\node (b') at (7,10) {$2$};
+\node (i) at (-0.5,13.5) {$i$};
+\node (o) at (5.5,13.5) {$o$};
+\node (i') at (-0.5,10.5) {$i^\prime$};
+\node (o') at (5.5,10.5) {$o^\prime$};
+%\node (A) at (2.5,11.5) {$\nexists F(f) \Downarrow$};
+  \node [style={circle,fill=teal}] (n1) at (1,13) {$v_1$};
+  \node[style={circle,fill=teal}] (n2) at (4,13)  {$v_2$};
+  \node [style={circle,fill=red}] (n1') at (1,10) {$w_1$};
+  \node[style={circle,fill=red}] (n2') at (4,10)  {$w_2$};
+\path[->,font=\scriptsize,>=angle 90]
+%(D) edge node [above] {$d$} (E)
+%(D) edge node [below] {$d^\prime$} (E')
+%(E) edge[dashed] node [right] {$\nexists F(f)$} (E')
+(a) edge[dashed] node[above] {$$} (n1)
+(b) edge[dashed] node[above] {$$} (n2)
+(a') edge[dashed] node[below] {$$} (n1')
+(b') edge[dashed] node[below] {$$} (n2')
+(n1) edge node[above]{$e$} (n2)
+(n1') edge node[above]{$e^\prime$} (n2');
+\end{tikzpicture}
+\]
+In the symmetric monoidal bicategory $F\mathbf{Cospan}(\mathsf{FinSet})$, the above two $F$-decorated cospans are two morphisms - with \emph{no 2-morphism between them!} The culprit for this is the same as before - the requirement that the triangle of decorations in $\mathsf{Set}$ commute `on the nose'.
+In this paper we construct a similar symmetric monoidal bicategory $F$Csp which will remedy this situation, and whose decategorification will remedy the analogous problem for decorated cospan categories above.
+
+It is worth noting that in both examples involving sets and graphs above, we are decorating each finite set with extra \emph{stuff}.
+This phenomenon does not occur when the decorations only involve extra structure, and this has been utilized in other works \cite{BFP,BP,Yass}.
+
+Our approach is to instead view the functor $F$ as a pseudofunctor $F \colon \textrm{A} \to \mathbf{Cat}$ and then consider $F(a)$ not as a \emph{set} of decorations on the object $a$ but as a \emph{category} of decorations on the element $a$.
+Then we first construct a symmetric monoidal double category $F \mathbb{C}$sp.
+This symmetric monoidal double category will have:
 \begin{enumerate}

### 2018-12-31 EquivCompFrameworks_20180911kc.tex
almost done with intro

@@
 Previously, in the ordinary symmetric monoidal category $F$Cospan$(\mathsf{FinSet})$ the following two $F$-decorated cospans resided in distinct isomorphism classes:
-\[
+\begin{equation}\label{eqn:no2morphism}
 \begin{tikzpicture}
@@
 \end{tikzpicture}
-\]
+\end{equation}
 In the symmetric monoidal bicategory $F\mathbf{Cospan}(\mathsf{FinSet})$, the above two $F$-decorated cospans are two morphisms - with \emph{no 2-morphism between them!} The culprit for this is the same as before - the requirement that the triangle of decorations in $\mathsf{Set}$ commute `on the nose'.
@@
 
-Our approach is to instead view the functor $F$ as a pseudofunctor $F \colon \textrm{A} \to \mathbf{Cat}$ and then consider $F(a)$ not as a \emph{set} of decorations on the object $a$ but as a \emph{category} of decorations on the element $a$.
-Then we first construct a symmetric monoidal double category $F \mathbb{C}$sp.
-This symmetric monoidal double category will have:
+Our approach is to instead view the functor $F$ as a pseudofunctor $F \colon \textrm{A} \to \mathbf{Cat}$ and take advantage of the 2-categorical structure of $\mathbf{Cat}$.
+Given an object $a \in \mathsf{A}$, this then allows us to view $F(a)$ not as a \emph{set} of decorations on the object $a$ but as a \emph{category} of decorations on the object $a$.
+From this pseudofunctor, we construct a symmetric monoidal double category $F \mathbb{C}$sp.
+Double categories were first introduced by Ehresmann \cite{Ehresmann63, Ehresmann65} and symmetric monoidal double categories by Shulman \cite{Shul}.
+They have long been used in topology and other branches of pure mathematics \cite{Brown1,Brown2}.
+More recently they have been used to study open dynamical systems \cite{LS} and open Markov processes \cite{BC}.
+While a mere category has only objects and morphisms, a double category has a few more types of entities:
+\[
+\begin{tikzpicture}[scale=1]
+\node (D) at (-4,0.5) {$A$};
+\node (E) at (-2,0.5) {$B$};
+\node (F) at (-4,-1) {$C$};
+\node (A) at (-2,-1) {$D$};
+\node (B) at (-3,-0.25) {$\Downarrow a$};
+\path[->,font=\scriptsize,>=angle 90]
+(D) edge node [above]{$M$}(E)
+(E) edge node [right]{$g$}(A)
+(D) edge node [left]{$f$}(F)
+(F) edge node [above]{$N$} (A);
+\end{tikzpicture}
+\]
+We call $A, B, C$ and $D$ `objects', $f$ and $g$ `vertical 1-morphisms', $M$ and $N$ `horizontal 1-cells', and $a$ a `2-morphism'.
+We can compose vertical 1-morphisms to get new vertical 1-morphisms and compose horizontal 1-cells to get new horizontal 1-cells.
+We can compose the 2-morphisms in two ways: horizontally by setting squares side by side, and vertically by setting one on top of the other.
+In a `strict' double category all these forms of composition are associative.
+In a `pseudo' double category, horizontal 1-cells compose in a weakly associative manner: that is, the associative law holds only up to an invertible 2-morphism, called the `associator', which obeys a coherence law.
+
+The symmetric monoidal double category $F \mathbb{C}$sp we construct has:
 \begin{enumerate}
-\item{objects as those of $\mathrm{A}$ and}
-\item{morphisms as isomorphism classes of cospans of $\mathrm{A}$ together with an element of image of the apex under the functor $F$.
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a$};
-\node (B) at (1,0) {$c$};
-\node (C) at (2,0) {$b$};
-\node (D) at (3,0) {$d \in F(c)$};
+\item{objects as those of $\mathrm{A}$,}
+\item{vertical 1-morphisms as morphisms of $\mathrm{A}$,}
+\item{horizontal 1-cells as $F$-decorated cospans in $\mathrm{A}$
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$a_1$};
+\node (B) at (1,0) {$b$};
+\node (C) at (2,0) {$a_2$};
+\node (D) at (3,0) {$d \in F(b)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-Except now, given another morphism:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a$};
-\node (B) at (1,0) {$c^\prime$};
-\node (C) at (2,0) {$b$};
-\node (D) at (3,0) {$d^\prime \in F(c^\prime)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i^\prime$} (B)
-(C) edge node[above]{$o^\prime$} (B);
-\end{tikzpicture}
-\]
-these two morphisms are in the same isomorphism class if the following diagrams commute
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a$};
-\node (B) at (1,1) {$c$};
-\node (B') at (1,-1) {$c^\prime$};
-\node (C) at (2,0) {$b$};
+and}
+\item{2-morphisms as maps of cospans together with a natural transformation.
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0.5) {$a_1$};
+\node (A') at (0,-0.5) {$a_1'$};
+\node (B) at (1,0.5) {$b$};
+\node (B') at (1,-0.5) {$b^\prime$};
+\node (C) at (2,0.5) {$a_2$};
+\node (C') at (2,-0.5) {$a_2;$};
 \node (D) at (3,0) {$1$};
-\node (E) at (4,0.5) {$F(c)$};
-\node (E') at (4,-0.5) {$F(c^\prime)$};
+\node (E) at (4,0.5) {$F(b)$};
+\node (E') at (4,-0.5) {$F(b^\prime)$};
+\node (F) at (3.65,0) {$\Swarrow \iota$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i$} (B)
+(C) edge node[above]{$o$} (B)
+(A) edge node {$$} (A')
+(C) edge node {$$} (C')
+(A') edge node[above]{$i^\prime$} (B')
+(C') edge node[above]{$o^\prime$} (B')
+(B) edge node [left] {$f$} (B')
+(D) edge node [above] {$d$} (E)
+(D) edge node [below] {$d^\prime$} (E')
+(E) edge node [right] {$F(f)$} (E');
+\end{tikzpicture}
+\]
+}
+\end{enumerate}
+Note that the natural transformation is a family of morphisms in the category $F(b^\prime)$ indexed by $1$, and so is the same as just a morphism $\iota \colon F(f)(d) \to d^\prime$ in $F(b^\prime)$.
+We will typically write the transformation $\iota$ in later sections as a morphism in $F(b^\prime)$ to conserve space.
+In the context of the example above involving graphs, this morphism $\iota$ will be a map between two possibly distinct sets of edges and thus already solves the problem.
+
+This double category is in fact fibrant and so a result of Shulman \cite{Shul} allows us to extract from this symmetric monoidal double category $F \mathbb{C}$sp a symmetric monoidal bicategory $H(F \mathbb{C}\textnormal{sp})$ as the `horizontal edge bicategory' of the double category $F \mathbb{C}$sp.
+This bicategory $H(F \mathbb{C}\textnormal{sp})$ has:
+\begin{enumerate}
+\item{objects as those of $\mathrm{A}$,}
+\item{morphisms as the horizontal 1-cells of $F\mathbb{C}$sp, which are $F$-decorated cospans of $\mathsf{A}$
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$a_1$};
+\node (B) at (1,0) {$b$};
+\node (C) at (2,0) {$a_2$};
+\node (D) at (3,0) {$d \in F(b)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i$} (B)
+(C) edge node[above]{$o$} (B);
+\end{tikzpicture}
+\]
+and}
+\item{2-morphisms as maps of cospans with the same feet together with a natrual transformation.
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$a_1$};
+\node (B) at (1,1) {$b$};
+\node (B') at (1,-1) {$b^\prime$};
+\node (C) at (2,0) {$a_2$};
+\node (D) at (3,0) {$1$};
+\node (E) at (4,0.5) {$F(b)$};
+\node (E') at (4,-0.5) {$F(b^\prime)$};
+\node (F) at (3.65,0) {$\Swarrow \iota$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-and there exists an isomorphism $\iota \colon F(f)(d) \to d^\prime$ in the category $F(c^\prime)$.
 }
 \end{enumerate}
+This bicategory $H(F\mathbb{C}\textnormal{sp})$ is superior to the original bicategory $F$Cospan$(A)$ constructed by the second author \cite{Cour} in that it has the 2-morphisms that one would expect such a bicategory to have, such as \ref{eqn:no2morphism}.
+\textbf{marker}
+
+Except now, given another morphism:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$a$};
+\node (B) at (1,0) {$c^\prime$};
+\node (C) at (2,0) {$b$};
+\node (D) at (3,0) {$d^\prime \in F(c^\prime)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i^\prime$} (B)
+(C) edge node[above]{$o^\prime$} (B);
+\end{tikzpicture}
+\]
+these two morphisms are in the same isomorphism class if the following diagrams commute
+
+and there exists an isomorphism $\iota \colon F(f)(d) \to d^\prime$ in the category $F(c^\prime)$.
+
 Note that the existence of an isomorphism $\iota \colon F(f)(d) \to d^\prime$ is equivalent to the triangle above on the right commuting up to a 2-isomorphism.
@@
 In the present work, we construct a symmetric monoidal `double category' $\mathbb{F}\textnormal{Cospan}(\textrm{A})$.
-Double categories were first introduced by Ehresmann \cite{Ehresmann63, Ehresmann65} and symmetric monoidal double categories by Shulman \cite{Shul}.
-They have long been used in topology and other branches of pure mathematics \cite{Brown1,Brown2}.
-More recently they have been used to study open dynamical systems \cite{LS} and open Markov processes \cite{BC}.
-While a mere category has only objects and morphisms, a double category has a few more types of entities:
-\[
-\begin{tikzpicture}[scale=1]
-\node (D) at (-4,0.5) {$A$};
-\node (E) at (-2,0.5) {$B$};
-\node (F) at (-4,-1) {$C$};
-\node (A) at (-2,-1) {$D$};
-\node (B) at (-3,-0.25) {$\Downarrow a$};
-\path[->,font=\scriptsize,>=angle 90]
-(D) edge node [above]{$M$}(E)
-(E) edge node [right]{$g$}(A)
-(D) edge node [left]{$f$}(F)
-(F) edge node [above]{$N$} (A);
-\end{tikzpicture}
-\]
-We call $A, B, C$ and $D$ `objects', $f$ and $g$ `vertical 1-morphisms', $M$ and $N$ `horizontal 1-cells', and $a$ a `2-morphism'.
-We can compose vertical 1-morphisms to get new vertical 1-morphisms and compose horizontal 1-cells to get new horizontal 1-cells.
-We can compose the 2-morphisms in two ways: horizontally by setting squares side by side, and vertically by setting one on top of the other.
-In a `strict' double category all these forms of composition are associative.
-In a `pseudo' double category, horizontal 1-cells compose in a weakly associative manner: that is, the associative law holds only up to an invertible 2-morphism, called the `associator', which obeys a coherence law.
 The double category $\mathbb{F}\textnormal{Cospan}(\textrm{A})$ that we construct in this paper has:

### 2019-01-01 EquivCompFrameworks_20180911kc.tex
Done with intro modulo some annoying diagram labeling. Going to fix up Sections 2, 3 and 5 next.

@@
 and both should be presented early.}
+\item Sure, I'm fine with that. What section do you think we should bring it up in, or maybe create a new section entirely to mention it?
 \end{itemize}
@@
 \[
-\begin{tikzpicture}
+\begin{tikzpicture}\label{distinctisoclasses}
   [scale=.8,auto=left]
@@
 Previously, in the ordinary symmetric monoidal category $F$Cospan$(\mathsf{FinSet})$ the following two $F$-decorated cospans resided in distinct isomorphism classes:
-\begin{equation}\label{eqn:no2morphism}
-\begin{tikzpicture}
+\[
+\begin{tikzpicture}\label{no2morphism}
   [scale=.8,auto=left]
@@
 \end{tikzpicture}
-\end{equation}
+\]
 In the symmetric monoidal bicategory $F\mathbf{Cospan}(\mathsf{FinSet})$, the above two $F$-decorated cospans are two morphisms - with \emph{no 2-morphism between them!} The culprit for this is the same as before - the requirement that the triangle of decorations in $\mathsf{Set}$ commute `on the nose'.
@@
 
-This double category is in fact fibrant and so a result of Shulman \cite{Shul} allows us to extract from this symmetric monoidal double category $F \mathbb{C}$sp a symmetric monoidal bicategory $H(F \mathbb{C}\textnormal{sp})$ as the `horizontal edge bicategory' of the double category $F \mathbb{C}$sp.
-This bicategory $H(F \mathbb{C}\textnormal{sp})$ has:
+This double category is in fact fibrant and so a result of Shulman \cite{Shul} allows us to extract from this symmetric monoidal double category $F \mathbb{C}$sp a symmetric monoidal bicategory $F \mathbf{Csp} \coloneqq H(F \mathbb{C}\textnormal{sp})$ as the `horizontal edge bicategory' of the double category $F \mathbb{C}$sp.
+This bicategory $F \mathbf{Csp}$ has:
 \begin{enumerate}
@@
 and}
-\item{2-morphisms as maps of cospans with the same feet together with a natrual transformation.
+\item{2-morphisms as maps of $F$-decorated cospans in $\mathsf{A}$ with the same feet together with a natrual transformation.
 \[
@@
 \end{enumerate}
-This bicategory $H(F\mathbb{C}\textnormal{sp})$ is superior to the original bicategory $F$Cospan$(A)$ constructed by the second author \cite{Cour} in that it has the 2-morphisms that one would expect such a bicategory to have, such as \ref{eqn:no2morphism}.
-\textbf{marker}
-
-Except now, given another morphism:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a$};
-\node (B) at (1,0) {$c^\prime$};
-\node (C) at (2,0) {$b$};
-\node (D) at (3,0) {$d^\prime \in F(c^\prime)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i^\prime$} (B)
-(C) edge node[above]{$o^\prime$} (B);
-\end{tikzpicture}
-\]
-these two morphisms are in the same isomorphism class if the following diagrams commute
-
-and there exists an isomorphism $\iota \colon F(f)(d) \to d^\prime$ in the category $F(c^\prime)$.
-
-Note that the existence of an isomorphism $\iota \colon F(f)(d) \to d^\prime$ is equivalent to the triangle above on the right commuting up to a 2-isomorphism.
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (4,0) {$\iota \Swarrow$};
+This bicategory $F\mathbf{Csp}$ is superior to the original bicategory $F$Cospan$(A)$ constructed by the second author \cite{Cour} in that it has the 2-morphisms that one would expect such a bicategory to have, such as (\ref{no2morphism}).
+
+Finally, we can decategorify the symmetric monoidal bicategory $F \mathbf{Csp}$ to obtain a symmetric monoidal category $F \textnormal{Csp} \coloneqq D(F\mathbf{Csp})$.
+This symmetric monoidal category $F$Csp has:
+
+\begin{enumerate}
+\item{objects as those of $\mathsf{A}$ and}
+\item{morphisms as isomorphism classes of $F$-decorated cospans in $\mathsf{A}$ with the same feet together with a natural isomorphism, where two $F$-decorated cospans are in the same isomorphism class if $f$ and $\iota$ are isomorphisms.
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$a_1$};
+\node (B) at (1,1) {$b$};
+\node (B') at (1,-1) {$b^\prime$};
+\node (C) at (2,0) {$a_2$};
 \node (D) at (3,0) {$1$};
-\node (E) at (4.5,1) {$F(c)$};
-\node (E') at (4.5,-1) {$F(c^\prime)$};
-\path[->,font=\scriptsize,>=angle 90]
-(D) edge node [above] {$d$} (E)
-(D) edge node [below] {$d^\prime$} (E')
-(E) edge node [right] {$F(f)$} (E');
-\end{tikzpicture}
-\]
-In other words, the isomorphism $\iota$ is a \emph{natural} isomorphism. We will typically just write this as $\iota \colon F(f)(d) \to d^\prime$ to conserve space.
-
-In this new category, the added structure of an isomorphism in the category of decorations shapes the isomorphism classes to look as one would expect.
-Fong's symmetric monoidal category has been extended to a bicategory by the first author \cite{Cour} and this was one of the original illuminations of the above obstacle.
-In this bicategory, objects and morphisms are given as in Fong's category modulo taking cospans up to isomorphism class and 2-morphisms are given by a pair of commuting diagrams:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a$};
-\node (B) at (1,1) {$c$};
-\node (B') at (1,-1) {$c^\prime$};
-\node (C) at (2,0) {$b$};
-\node (D) at (3,0) {$1$};
-\node (E) at (4,0.5) {$F(c)$};
-\node (E') at (4,-0.5) {$F(c^\prime)$};
+\node (E) at (4,0.5) {$F(b)$};
+\node (E') at (4,-0.5) {$F(b^\prime)$};
+\node (F) at (3.5,0) {$\Swarrow \iota$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (B) edge node [left] {$f$} (B')
+(B) edge node [right] {$\sim$} (B')
 (D) edge node [above] {$d$} (E)
 (D) edge node [below] {$d^\prime$} (E')
-(E) edge node [right] {$F(f)$} (E');
-\end{tikzpicture}
-\]
-In this case, there would be no 2-morphism from:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$v_1$};
-\node (B) at (1,0) {$v_2$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$e$} (B);
-\end{tikzpicture}
-\]
-to:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$v_1$};
-\node (B) at (1,0) {$v_2.$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$e^\prime$} (B);
-\end{tikzpicture}
-\]
-Morally speaking, these two simple single-edged graphs should belong to the same isomorphism class, as there is a natural isomorphism of graphs between them.
-
-In the present work, we construct a symmetric monoidal `double category' $\mathbb{F}\textnormal{Cospan}(\textrm{A})$.
-The double category $\mathbb{F}\textnormal{Cospan}(\textrm{A})$ that we construct in this paper has:
-\begin{enumerate}
-\item{objects as those of $\textrm{A}$,}
-\item{vertical 1-morphisms as morphisms of $\textrm{A}$,}
-\item{horizontal 1-cells as $F$-decorated cospans of $\textrm{A}$, which are pairs:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a$};
-\node (B) at (1,0) {$c$};
-\node (C) at (2,0) {$b$};
-\node (D) at (3,0) {$d \in F(c)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i$} (B)
-(C) edge node[above]{$o$} (B);
-\end{tikzpicture}
-\]
-and}
-\item{2-morphisms as pairs of commuting diagrams:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a$};
-\node (B) at (1,0) {$c$};
-\node (C) at (2,0) {$b$};
-\node (A') at (0,-1) {$a^\prime$};
-\node (B') at (1,-1) {$c^\prime$};
-\node (C') at (2,-1) {$b^\prime$};
-\node (D) at (3,-0.5) {$1$};
-\node (E) at (4,0) {$F(c)$};
-\node (E') at (4,-1) {$F(c^\prime)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i$} (B)
-(C) edge node[above]{$i$} (B)
-(A') edge node[above]{$i^\prime$} (B')
-(C') edge node[above]{$o^\prime$} (B')
-(A) edge node [left]{$f$} (A')
-(B) edge node [left]{$h$} (B')
-(C) edge node [left]{$g$} (C')
-(D) edge node [above] {$d$} (E)
-(D) edge node [below] {$d^\prime$} (E')
-(E) edge node [left] {$F(h)$} (E');
-\end{tikzpicture}
-\]
-together with a morphism $\iota \colon F(h)(d) \to d^\prime$ in $F(c^\prime)$.}
+(E) edge node [right] {$F(f)$} (E')
+(E) edge node [left] {$\sim$} (E');
+\end{tikzpicture}
+\]
+}
 \end{enumerate}
-We can then obtain a symmetric monoidal bicategory $H(\mathbb{F}\textnormal{Cospan}(\textrm{A}))$ as the `horizontal bicategory' of the symmetric monoidal double category $\mathbb{F}\textnormal{Cospan}(\textrm{A})$ using a result of Shulman \cite{Shul}.
-This bicategory will have:
-\begin{enumerate}
-\item{objects as those of $\textrm{A}$,}
-\item{morphisms as pairs:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a$};
-\node (B) at (1,0) {$c$};
-\node (C) at (2,0) {$b$};
-\node (D) at (3,0) {$d \in F(c)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i$} (B)
-(C) edge node[above]{$o$} (B);
-\end{tikzpicture}
-\]
-and}
-\item{2-morphisms as pairs of commuting diagrams:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a$};
-\node (B) at (1,1) {$c$};
-\node (B') at (1,-1) {$c^\prime$};
-\node (C) at (2,0) {$b$};
-\node (D) at (3,0) {$1$};
-\node (E) at (4,0.5) {$F(c)$};
-\node (E') at (4,-0.5) {$F(c^\prime)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i$} (B)
-(C) edge node[above]{$o$} (B)
-(A) edge node[below]{$i^\prime$} (B')
-(C) edge node[below]{$o^\prime$} (B')
-(B) edge node [left] {$f$} (B')
-(D) edge node [above] {$d$} (E)
-(D) edge node [below] {$d^\prime$} (E')
-(E) edge node [right] {$F(f)$} (E');
-\end{tikzpicture}
-\]
-together with a morphism $\iota \colon F(f)(d) \to d^\prime$ of $F(c^\prime)$.}
-
-\end{enumerate}
-Then we can obtain the above improved symmetric monoidal category as a decategorification of the symmetric monoidal bicategory $H(\mathbb{F}\textnormal{Cospan}(\textrm{A}))$.
-
-The outline for the paper is as follows: In the second section, we construct the symmetric monoidal double category $F\textnormal{Cospan}(\textrm{A})$ mentioned above as well as a result of Shulman that allows us to obtain a symmetric monoidal bicategory whose decategorification is an improved version of Fong's symmetric monoidal category.
-In the third section we define maps between decorated cospan double categories which are double functors of an appropriate type.
-In the fourth section we investigate when a symmetric lax monoidal pseudofunctor gives rise to a left adjoint via the Grothendieck construction.
-In the fifth section we briefly review another compositional framework which uses cospans equipped with extra structure due to the first two authors, namely `structured cospans' and prove that the double categorical versions of decorated cospans and structured cospans are equivalent, and in the final section, we present a few examples that can be realized with either framework and discuss the realized equivalences.
-
-\section{A symmetric monoidal double category of decorated cospans}\label{DecCospansDoublecat}
+This symmetric monoidal category $F$Csp has isomorphism classes as one would expect, and in the context of the example with finite sets and graphs above solves the problem in (\ref{distinctisoclasses}).
+In this particular example, $\iota \colon F(f)(d) \xrightarrow{\sim} d^\prime$ is a bijection between possibly different sets of edges which respects the source and target of each edge.
+
+The outline for the paper is as follows: In Section \ref{DecCospansDoubleCat}, we construct the symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$, obtain the underlying symmetric monoidal bicategory $F \mathbf{Csp}$ via a result of Shulman, and decategorify this symmetric monoidal bicategory to obtain the symmetric monoidal category $F$Csp.
+In Section \ref{MapsDecCospansDoubleCat} we define maps between decorated cospan double categories which are double functors of an appropriate type.
+In Section \ref{some other section} we investigate when a symmetric lax monoidal pseudofunctor gives rise to a left adjoint via the Grothendieck construction, which naturally leads to another compositional framework known as `Structured cospans'.
+In Section \ref{EquivDoubleCats} we briefly review the framework Structured cospans and prove that the double categorical versions of decorated cospans and structured cospans are equivalent when both are appropriate.
+Finally, in Section \ref{Applications}, we present a few examples that can be realized with either framework and discuss the realized equivalences.
+
+\section{A symmetric monoidal double category of decorated cospans}\label{DecCospansDoubleCat}
 In this section we build the symmetric monoidal double category mentioned in the introduction. 
@@
 
-\section{Maps of decorated cospan double categories}
+\section{Maps of decorated cospan double categories}\label{MapsDecCospansDoubleCat}
 Let $F \colon \mathrm{A} \to \mathbf{Cat}$ be a symmetric lax monoidal pseudofunctor.
@@
 
-\section{From pseudofunctors to left adjoints}
+\section{From pseudofunctors to left adjoints}\label{some other section}
 In this section we investigate the necessary conditions to obtain a category $\mathrm{X}$ and a left adjoint $L \colon \mathrm{A} \to \mathrm{X}$ from a category $\mathrm{A}$ with finite colimits and a symmetric lax monoidal pseudofunctor $F \colon \mathrm{A} \to \mathbf{Cat}$.
@@
 
-\section{An equivalence of symmetric monoidal double categories}
+\section{An equivalence of symmetric monoidal double categories} \label{EquivDoubleCats}
 In this section we prove that two different frameworks which utilize symmetric monoidal double categories, namely decorated cospans and `structured cospans', are equivalent under the conditions required from the previous section that allow for a left adjoint $L \colon \mathrm{A} \to \mathrm{X}$ to be obtained from a symmetric lax monoidal pseudofunctor $F \colon \mathrm{A} \to \mathbf{Cat}$.
@@
 $$\iota \colon F(e)(x) \to x$$
-\section{Applications}
+\section{Applications}\label{Applications}
 In this section we present several examples each of which may be realized in the context of decorated cospans or in the context of structured cospans.

### 2019-01-02 EquivCompFrameworks_20180911kc.tex
Going through Section 2 (specifically Theorem 2.1)

@@
 \section{A symmetric monoidal double category of decorated cospans}\label{DecCospansDoubleCat}
-In this section we build the symmetric monoidal double category mentioned in the introduction. 
-\textbf{Add more here.}
+In this section we build the symmetric monoidal double category $F \mathbb{C}$sp mentioned in the introduction.
+Then we obtain an underlying symmetric monoidal bicategory $F \mathbf{Csp}$ using a result of Shulman \cite{Shul} and then finally decategorify the obtained symmetric monoidal bicategory to obtain a symmetric monoidal category $F$Csp which is a generalization of Fong's original decorated cospan category \cite{Fong}.
 \begin{thm}
-Let $\mathrm{A}$ be a category with finite colimits and $F \colon \mathrm{A} \to \mathbf{Cat}$ a lax monoidal pseudofunctor.
-Then there exists a double category $\mathbb{F} \textnormal{Cospan}(\mathrm{A})$ which has:
+Let $\mathsf{A}$ be a category with finite colimits and $F \colon \mathsf{A} \to \mathbf{Cat}$ a lax monoidal pseudofunctor. Then there exists a double category $F\mathbb{C}$sp which has:
 \begin{enumerate}
-\item{objects as those of $\mathrm{A}$,}
-\item{vertical 1-morphisms as morphisms of $\mathrm{A}$,}
-\item{horizontal 1-cells as pairs:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a$};
-\node (B) at (1,0) {$c$};
-\node (C) at (2,0) {$b$};
-\node (D) at (3,0) {$d \in F(c)$};
+\item{objects as those of $\mathsf{A}$,}
+\item{vertical 1-morphisms as morphisms of $\mathsf{A}$,}
+\item{horizontal 1-cells as $F$-decorated cospans in $\mathsf{A}$ which are pairs:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$a_1$};
+\node (B) at (1,0) {$b$};
+\node (C) at (2,0) {$a_2$};
+\node (D) at (3,0) {$d \in F(b)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 and}
-\item{2-morphisms as maps of cospans in $\mathrm{A}$
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$a$};
-\node (A') at (0,-0.5) {$a^\prime$};
-\node (B) at (1,0.5) {$c$};
-\node (C) at (2,0.5) {$b$};
-\node (C') at (2,-0.5) {$b^\prime$};
-\node (D) at (1,-0.5) {$c^\prime$};
-\node (E) at (3,0.5) {$d \in F(c)$};
-\node (F) at (3,-0.5) {$d^\prime \in F(c^\prime)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$$} (B)
-(C) edge node[above]{$$} (B)
+\item{2-morphisms as maps of $F$-decorated cospans in $\mathsf{A}$
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0.5) {$a_1$};
+\node (A') at (0,-0.5) {$a_1^\prime$};
+\node (B) at (1,0.5) {$b$};
+\node (C) at (2,0.5) {$a_2$};
+\node (C') at (2,-0.5) {$a_2^\prime$};
+\node (D) at (1,-0.5) {$b^\prime$};
+\node (E) at (3,0.5) {$d \in F(b)$};
+\node (F) at (3,-0.5) {$d^\prime \in F(b^\prime)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i$} (B)
+(C) edge node[above]{$o$} (B)
 (A) edge node[left]{$f$} (A')
 (C) edge node[left]{$g$} (C')
-(A') edge node {$$} (D)
-(C') edge node {$$} (D)
+(A') edge node[above] {$i'$} (D)
+(C') edge node[above] {$o'$} (D)
 (B) edge node [left] {$h$} (D);
@@
 \]
-together with a morphism $\iota \colon F(h)(d) \to d^\prime$ in $F(c^\prime)$.}
+together with a morphism $\iota \colon F(h)(d) \to d^\prime$ in $F(b^\prime)$.}
 \end{enumerate}
@@
 \begin{proof}
-The unit structure functor $U \colon \mathbb{F}\textnormal{Cospan}(\mathrm{A})_0 \to \mathbb{F}\textnormal{Cospan}(\mathrm{A})_1$ is defined on objects as: 
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (E) at (-1,0) {$c \mapsto$};
-\node (A) at (0,0) {$c$};
-\node (B) at (1,0) {$c$};
-\node (C) at (2,0) {$c$};
-\node (D) at (3,0) {$!_c \in F(c)$};
+The unit structure functor $U \colon F\mathbb{C}\textnormal{sp}_0 \to F\mathbb{C}\textnormal{sp}_1$ is defined on objects as: 
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (E) at (-1,0) {$a$};
+\node (F) at (-.5,0) {$\mapsto$};
+\node (A) at (0,0) {$a$};
+\node (B) at (1,0) {$a$};
+\node (C) at (2,0) {$a$};
+\node (D) at (3,0) {$!_a \in F(a)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-where $!_c \in F(c)$ is the trivial decoration on $c$ given by the composition of the unique map $F(!) \colon F(0) \to F(c)$ and the morphism $\phi \colon 1 \to F(0)$  which comes from the symmetric lax monoidal pseudofunctor $F \colon \mathrm{A} \to \mathbf{Cat}$.
+where $!_a \in F(a)$ is the trivial decoration on $a$ given by the composition of the unique map $F(!) \colon F(0) \to F(a)$ and the morphism $\phi \colon 1 \to F(0)$  which comes from the structure of the lax monoidal pseudofunctor $F \colon \mathsf{A} \to \mathbf{Cat}$.
 For morphisms, the structure functor $U$ is defined as:
@@
 \begin{tikzpicture}[scale=1.5]
-\node (G) at (-1,0.5) {$c$};
-\node (G') at (-1,-0.5) {$c^\prime$};
-\node (A) at (0,0.5) {$c$};
-\node (A') at (0,-0.5) {$c^\prime$};
-\node (B) at (1,0.5) {$c$};
-\node (C) at (2,0.5) {$c$};
-\node (C') at (2,-0.5) {$c^\prime$};
-\node (D) at (1,-0.5) {$c^\prime$};
-\node (E) at (3,0.5) {$!_c \in F(c)$};
-\node (F) at (3,-0.5) {$!_{c^\prime} \in F(c^\prime)$};
+\node (G) at (-1,0.5) {$a$};
+\node (G') at (-1,-0.5) {$a^\prime$};
+\node (A) at (0,0.5) {$a$};
+\node (A') at (0,-0.5) {$a^\prime$};
+\node (B) at (1,0.5) {$a$};
+\node (C) at (2,0.5) {$a$};
+\node (C') at (2,-0.5) {$a^\prime$};
+\node (D) at (1,-0.5) {$a^\prime$};
+\node (E) at (3,0.5) {$!_a \in F(a)$};
+\node (F) at (3,-0.5) {$!_{a^\prime} \in F(a^\prime)$};
 \node (H) at (-0.5,0) {$\mapsto$};
 \path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$$} (B)
-(C) edge node[above]{$$} (B)
+(A) edge node[above]{$1$} (B)
+(C) edge node[above]{$1$} (B)
 (A) edge node[left]{$f$} (A')
 (C) edge node[left]{$f$} (C')
-(A') edge node {$$} (D)
-(C') edge node {$$} (D)
+(A') edge node[above] {$1$} (D)
+(C') edge node[above] {$1$} (D)
 (B) edge node [left] {$f$} (D)
@@
 \]
-together with the morphism $\iota_{!_f} = F(f) F(!) \phi \colon 1 \to F(c^\prime)$.
-We also have source and target structure functors $S, T \colon \mathbb{F}\textnormal{Cospan}(\mathrm{A})_1 \to \mathbb{F}\textnormal{Cospan}(\mathrm{A})_0$ where the source of a horizontal 1-cell
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a$};
-\node (B) at (1,0) {$c$};
-\node (C) at (2,0) {$b$};
-\node (D) at (3,0) {$d \in F(c)$};
+together with the morphism $\iota_{!_f} = F(f) F(!) \phi \colon 1 \to F(a^\prime)$.
+We also have source and target structure functors $S, T \colon F\mathbb{C}\textnormal{sp}_1 \to F\mathbb{C}\textnormal{sp}_0$ where the source of the horizontal 1-cell
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$a_1$};
+\node (B) at (1,0) {$b$};
+\node (C) at (2,0) {$a_2$};
+\node (D) at (3,0) {$d \in F(b)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-is the object $a$ in $\mathrm{A}$ and the source of a 2-morphism
+is the object $a_1$ in $\mathsf{A}$ and the source of the 2-morphism
 \[
@@
 \node (A') at (0,-0.5) {$a^\prime$};
-\node (B) at (1,0.5) {$c$};
-\node (C) at (2,0.5) {$b$};
-\node (C') at (2,-0.5) {$b^\prime$};
-\node (D) at (1,-0.5) {$c^\prime$};
-\node (E) at (3,0.5) {$d \in F(c)$};
-\node (F) at (3,-0.5) {$d^\prime \in F(c^\prime)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$$} (B)
-(C) edge node[above]{$$} (B)
+\node (B) at (1,0.5) {$b$};
+\node (C) at (2,0.5) {$a_2$};
+\node (C') at (2,-0.5) {$a_2^\prime$};
+\node (D) at (1,-0.5) {$b^\prime$};
+\node (E) at (3,0.5) {$d \in F(b)$};
+\node (F) at (3,-0.5) {$d^\prime \in F(b^\prime)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i$} (B)
+(C) edge node[above]{$o$} (B)
 (A) edge node[left]{$f$} (A')
 (C) edge node[left]{$g$} (C')
-(A') edge node {$$} (D)
-(C') edge node {$$} (D)
+(A') edge node[above] {$i'$} (D)
+(C') edge node[above] {$o'$} (D)
 (B) edge node [left] {$h$} (D);
@@
 $$\iota \colon F(h)(d) \to d^\prime$$
-is the source of the underlying map of cospans in $\mathrm{A}$, namely the morphism $f$ in $\mathrm{A}$; the target structure functor is defined similarly.
-The functors satisfy the equations $$SU(c)=1(c)=TU(c)$$for all objects $c$ of $\mathrm{A}$.
-
-Given two composable horizontal 1-cells:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a$};
-\node (B) at (1,0) {$c$};
-\node (C) at (2,0) {$b$};
-\node (D) at (1,-0.5) {$d \in F(c)$};
-\node (E) at (3,0) {$b$};
-\node (F) at (4,0) {$c^\prime$};
-\node (G) at (5,0) {$e$};
-\node (H) at (4,-0.5) {$d^\prime \in F(c^\prime)$};
+is the source of the underlying map of cospans in $\mathsf{A}$, namely the morphism $f$ in $\mathsf{A}$; the target structure functor is defined similarly.
+These structure functors satisfy the equations $$SU(a)=1(a)=TU(a)$$for all objects $a$ of $\mathsf{A}$.
+
+Given two composable horizontal 1-cells $M$ and $N$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$a_1$};
+\node (B) at (1,0) {$b$};
+\node (C) at (2,0) {$a_2$};
+\node (D) at (1,-0.5) {$d \in F(b)$};
+\node (E) at (3,0) {$a_2$};
+\node (F) at (4,0) {$b^\prime$};
+\node (G) at (5,0) {$a_3$};
+\node (H) at (4,-0.5) {$d^\prime \in F(b^\prime)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-the composite is given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a$};
-\node (B) at (1,1) {$c$};
-\node (C) at (2,0) {$b$};
-\node (D) at (3,1) {$c^\prime$};
-\node (E) at (4,0) {$e$};
-\node (F) at (2,2) {$c+c^\prime$};
-\node (G) at (2,3) {$c+_{b} c^\prime$};
+the composite $N \odot M$ is given by:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$a_1$};
+\node (B) at (1,1) {$b$};
+\node (C) at (2,0) {$a_2$};
+\node (D) at (3,1) {$b^\prime$};
+\node (E) at (4,0) {$a_3$};
+\node (F) at (2,2) {$b+b^\prime$};
+\node (G) at (2,3) {$b+_{a_2} b^\prime$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (F) edge node [left] {$\psi$} (G)
-(A) edge node [left] {$\psi j i$} (G)
-(E) edge node [right] {$\psi j^\prime o^\prime$} (G);
-\end{tikzpicture}
-\]
-with the corresponding decoration of the apex $\hat{d} \in F(c+_b c^\prime)$ given by:
-$$1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{d \times d^\prime} F(c) \times F(c^\prime) \xrightarrow{\phi_{c,c^\prime}} F(c+c^\prime) \xrightarrow{F(\psi)} F(c+_{b}c^\prime)$$
-where $\psi \colon c + c^\prime \to c+_b c^\prime$ is the natural map from the coproduct to the pushout and $\phi_{c,c^\prime} \colon F(c) \times F(c^\prime) \to F(c+c^\prime)$ is the natural transformation of the symmetric lax monoidal pseudofunctor $F \colon \mathrm{A} \to \mathbf{Cat}$.
+(A) edge[bend left] node [left] {$\psi j i$} (G)
+(E) edge[bend right] node [right] {$\psi j^\prime o^\prime$} (G);
+\end{tikzpicture}
+\]
+with the corresponding decoration of the apex $\hat{d} \in F(b+_{a_2} b^\prime)$ given by:
+$$1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{d \times d^\prime} F(b) \times F(b^\prime) \xrightarrow{\phi_{b,b^\prime}} F(b+b^\prime) \xrightarrow{F(\psi)} F(b+_{a_2}b^\prime)$$
+where $\psi \colon b + b^\prime \to b+_{a_2} b^\prime$ is the natural map from the coproduct to the pushout and $\phi_{b,b^\prime} \colon F(b) \times F(b^\prime) \to F(b+b^\prime)$ is the natural transformation coming from the structure of the lax monoidal pseudofunctor $F \colon \mathsf{A} \to \mathbf{Cat}$.
 Denoting the first and second of these horizontal 1-cells as $M$ and $N$, respectively, the source and target structure functors satisfy the equations $S(N \odot M)=S(M)$ and $T(N \odot M)=T(N)$.
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a$};
-\node (B) at (1,0) {$c$};
-\node (C) at (2,0) {$b$};
-\node (D) at (1,-0.5) {$d_1 \in F(c)$};
-\node (E) at (3,0) {$b$};
-\node (F) at (4,0) {$c^\prime$};
-\node (G) at (5,0) {$e$};
-\node (H) at (4,-0.5) {$d_2 \in F(c^\prime)$};
-\node (I) at (6,0) {$e$};
-\node (J) at (7,0) {$c''$};
-\node (K) at (8,0) {$f$};
-\node (L) at (7,-0.5) {$d_3 \in F(c'')$};
+\node (A) at (0,0) {$a_1$};
+\node (B) at (1,0) {$b$};
+\node (C) at (2,0) {$a_2$};
+\node (D) at (1,-0.5) {$d_{M_1} \in F(b)$};
+\node (E) at (3,0) {$a_2$};
+\node (F) at (4,0) {$b^\prime$};
+\node (G) at (5,0) {$a_3$};
+\node (H) at (4,-0.5) {$d_{M_2} \in F(b^\prime)$};
+\node (I) at (6,0) {$a_3$};
+\node (J) at (7,0) {$b''$};
+\node (K) at (8,0) {$a_4$};
+\node (L) at (7,-0.5) {$d_{M_3} \in F(b'')$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-we get a natural isomorphism $a \colon (M_1 \odot M_2) \odot M_3 \to M_1 \odot (M_2 \odot M_3)$ which is a globular 2-morphism given by a map of cospans $(\id_a,\sigma,\id_f)$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$a$};
-\node (A') at (0,-0.5) {$a$};
-\node (B) at (1.5,0.5) {$(c+_b c^\prime)+_e c''$};
-\node (C) at (3,0.5) {$f$};
-\node (C') at (3,-0.5) {$f$};
-\node (D) at (1.5,-0.5) {$c+_b(c^\prime +_e c'')$};
-\node (E) at (4.5,0.5) {$d \in F((c+_b c^\prime)+_e c'')$};
-\node (F) at (4.5,-0.5) {$d^\prime \in F(c+_b (c^\prime +_e c''))$};
+we get a natural isomorphism $a_{M_1,M_2,M_3} \colon (M_1 \odot M_2) \odot M_3 \to M_1 \odot (M_2 \odot M_3)$ which is a globular 2-morphism given by a map of cospans $(\id_{a_1},\sigma,\id_{a_4})$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0.5) {$a_1$};
+\node (A') at (0,-0.5) {$a_1$};
+\node (B) at (1.5,0.5) {$(b+_{a_2} b^\prime)+_{a_3} b''$};
+\node (C) at (3,0.5) {$a_4$};
+\node (C') at (3,-0.5) {$a_4$};
+\node (D) at (1.5,-0.5) {$b+_{a_2}(b^\prime +_{a_3} b'')$};
+\node (E) at (5.5,0.5) {$d_{(M_1 \odot M_2) \odot M_3} \in F((b+_{a_2} b^\prime)+_{a_3} b'')$};
+\node (F) at (5.5,-0.5) {$d_{M_1 \odot (M_2 \odot M_3)} \in F(b+_{a_2} (b^\prime +_{a_3} b''))$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (C') edge node {$$} (D)
-(B) edge node [left] {$\sigma$} (D);
-\end{tikzpicture}
-\]
-with elements of the image of the cospan's apices under the pseudofunctor $F$ given by:
-$$ d \coloneqq 1 \xrightarrow{\zeta_1} F(c+_b c^\prime) \times F(c'') \xrightarrow{F(\phi_{c+_b c^\prime, c''})} F((c+_{b}c^\prime) +c'') \xrightarrow{F(j_{c+_b c^\prime,c''})} F((c+_b c^\prime)+_e c'')$$ $$\zeta_1 = d_3 \lambda^{-1} F(j_{c,c^\prime}) \phi_{c,c^\prime} (d_1 \times d_2) \lambda^{-1}$$
+(B) edge node [left] {$a$} (D);
+\end{tikzpicture}
+\]
+with the decorations on the cospan's apices given by:
+$$ d_{(M_1 \odot M_2) \odot M_3} \coloneqq 1 \xrightarrow{\zeta_1} F(b+_{a_2} b^\prime) \times F(b'') \xrightarrow{\phi_{b+_{a_2} b^\prime, b''}} F((b+_{a_2}b^\prime) +b'') \xrightarrow{F(j_{b+_{a_2} b^\prime,b''})} F((b+_{a_2} b^\prime)+_{a_3} b'')$$ $$\zeta_1 = d_{M_3} \lambda^{-1} F(j_{b,b^\prime}) \phi_{b,b^\prime} (d_{M_1} \times d_{M_2}) \lambda^{-1}$$
 and
-$$ d^\prime \coloneqq 1 \xrightarrow{\zeta_2} F(c) \times F(c^\prime +_e c'') \xrightarrow{F(\phi_{c, c^\prime +_e c''})} F(c+(c^\prime +_e c'')) \xrightarrow{F(j_{c,c^\prime +_e c''})} F(c+_b (c^\prime+_e c''))$$ $$\zeta_2 = d_1 \lambda^{-1} F(j_{c^\prime,c''}) \phi_{c^\prime,c''} (d_2 \times d_3) \lambda^{-1}$$
-together with an isomorphism $\iota_a \colon F(\sigma)(d) \to d^\prime$. We also have left and right unitors where given a horizontal 1-cell $M$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a$};
-\node (B) at (1,0) {$c$};
-\node (C) at (2,0) {$b$};
-\node (D) at (3,0) {$d \in F(c)$};
+$$ d_{M_1 \odot (M_2 \odot M_3)} \coloneqq 1 \xrightarrow{\zeta_2} F(b) \times F(b^\prime +_{a_3} b'') \xrightarrow{\phi_{b, b^\prime +_{a_3} b''}} F(b+(b^\prime +_{a_3} b'')) \xrightarrow{F(j_{b,b^\prime +_{a_3} b''})} F(b+_{a_2} (b^\prime+_{a_3} b''))$$ $$\zeta_2 = d_{M_1} \lambda^{-1} F(j_{b^\prime,b''}) \phi_{b^\prime,b''} (d_{M_2} \times d_{M_3}) \lambda^{-1}$$
+together with the isomorphism $\iota_a \colon F(a)(d_{(M_1 \odot M_2) \odot M_3}) \to d_{M_1 \odot (M_2 \odot M_3)}$.
+Note that the map $a \colon (b+_{a_2} b')+_{a_3}b'' \to b+_{a_2}(b'+_{a_3}b'')$ is the universal map between two colimits of the same diagram.
+We also have left and right unitors where given a horizontal 1-cell $M$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$a_1$};
+\node (B) at (1,0) {$b$};
+\node (C) at (2,0) {$a_2$};
+\node (D) at (3,0) {$d \in F(b)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-if we, say, compose with the identity horizontal 1-cell of $b$ on the right:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a$};
-\node (B) at (1,0) {$c$};
-\node (C) at (2,0) {$b$};
-\node (D) at (1,-0.5) {$d \in F(c)$};
-\node (E) at (3,0) {$b$};
-\node (F) at (4,0) {$b$};
-\node (G) at (5,0) {$b$};
-\node (H) at (4,-0.5) {$!_b \in F(b)$};
+if we, say, compose with the identity horizontal 1-cell of $a_2$ on the right:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$a_1$};
+\node (B) at (1,0) {$b$};
+\node (C) at (2,0) {$a_2$};
+\node (D) at (1,-0.5) {$d \in F(b)$};
+\node (E) at (3,0) {$a_2$};
+\node (F) at (4,0) {$a_2$};
+\node (G) at (5,0) {$a_2$};
+\node (H) at (4,-0.5) {$!_{a_2} \in F(a_2)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-where $!_b = F(!)  \phi \colon 1 \to F(b)$ is the trivial decoration on $b$. Composing these then gives:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a$};
-\node (B) at (1,0) {$c+_b b$};
-\node (C) at (2,0) {$b$};
-\node (D) at (3,0) {$\hat{d} \in F(c +_b b)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$j \psi_c i$} (B)
-(C) edge node[above]{$j \psi_b$} (B);
-\end{tikzpicture}
-\]
-where $\psi_b \colon b \to c+b$ is the natural map into the coproduct and likewise for $\psi_c$ and $j \colon c+b \to c+_b b$ is the natural map from the coproduct to the pushout.
-The decoration $\hat{d} \colon 1 \to F(c+_b b)$ is given by: $$1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{d \times !_b} F(c) \times F(b) \xrightarrow{\phi_{c,b}} F(c+b) \xrightarrow{F(j_{c,b})} F(c+_b b).$$ We then have that the right unitor of the original horizontal 1-cell $M$ is given by the globular 2-morphism $(\id_a,\gamma,\id_b)$ from the above composite to $M$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$a$};
-\node (A') at (0,-0.5) {$a$};
-\node (B) at (1.5,0.5) {$c+_b b$};
-\node (C) at (3,0.5) {$b$};
-\node (C') at (3,-0.5) {$b$};
-\node (D) at (1.5,-0.5) {$c$};
-\node (E) at (4.5,0.5) {$\hat{d} \in F((c+_b b)$};
-\node (F) at (4.5,-0.5) {$d \in F(c)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$j \psi_c i$} (B)
-(C) edge node[above]{$j \psi_b$} (B)
-(A) edge node[left]{$\id_a$} (A')
-(C) edge node[left]{$\id_b$} (C')
+where $!_{a_2} = F(!)  \phi \colon 1 \to F(a_2)$ is the trivial decoration on $a_2$, composing these then gives:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$a_1$};
+\node (B) at (1,0) {$b+_{a_2} a_2$};
+\node (C) at (2,0) {$a_2$};
+\node (D) at (3.5,0) {$d_{M+!_{a_2}} \in F(b +_{a_2} a_2)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$j \psi_b i$} (B)
+(C) edge node[above]{$j \psi_{a_2}$} (B);
+\end{tikzpicture}
+\]
+where $\psi_b \colon b \to b+a_2$ is the natural map into the coproduct and likewise for $\psi_{a_2}$ and $j \colon b+a_2 \to b+_{a_2} a_2$ is the natural map from the coproduct to the pushout.
+The decoration $d_{M+!_{a_2}} \colon 1 \to F(b+_{a_2} a_2)$ is given by: $$1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{d_{M} \times !_{a_2}} F(b) \times F(a_2) \xrightarrow{\phi_{b,a_2}} F(b+a_2) \xrightarrow{F(j_{b,a_2})} F(b+_{a_2} a_2).$$ We then have that the right unitor $R \colon M \odot 1_{a_2} \xrightarrow{\sim} M$ is given by the globular 2-morphism $(\id_{a_1},r,\id_{a_2})$ from the above composite to $M$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0.5) {$a_1$};
+\node (A') at (0,-0.5) {$a_1$};
+\node (B) at (1.5,0.5) {$b+_{a_2} a_2$};
+\node (C) at (3,0.5) {$a_2$};
+\node (C') at (3,-0.5) {$a_2$};
+\node (D) at (1.5,-0.5) {$b$};
+\node (E) at (4.5,0.5) {$d_{M+!_{a_2}} \in F(b+_{a_2} a_2)$};
+\node (F) at (4.5,-0.5) {$d_{M} \in F(b)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$j \psi_b i$} (B)
+(C) edge node[above]{$j \psi_{a_2}$} (B)
+(A) edge node[left]{$\id_{a_1}$} (A')
+(C) edge node[left]{$\id_{a_2}$} (C')
 (A') edge node [above]{$i$} (D)
 (C') edge node [above]{$o$} (D)
-(B) edge node [left] {$\gamma$} (D);
-\end{tikzpicture}
-\]
-where $\gamma \colon c+_b b \xrightarrow{\sim} c$ together with an isomorphism $\iota_\rho \colon F(\gamma)(\hat{d}) \to d$.
+(B) edge node [left] {$r$} (D);
+\end{tikzpicture}
+\]
+where $r \colon b+_{a_2} a_2 \xrightarrow{\sim} b$ is a universal map together with the isomorphism $\iota_r \colon F(r)(d_{M+!_{a_2}}) \to d_M$.
 The left unitor is similar.

### 2019-01-03 EquivCompFrameworks_20180911kc.tex
Theorem 2.1 looks good. Going through Theorem 2.2 next.

@@
 \begin{thm}
-Let $\mathsf{A}$ be a category with finite colimits and $F \colon \mathsf{A} \to \mathbf{Cat}$ a lax monoidal pseudofunctor. Then there exists a double category $F\mathbb{C}$sp which has:
+Let $\mathsf{A}$ be a category with finite colimits and $F \colon \mathsf{A} \to \mathbf{Cat}$ a lax monoidal pseudofunctor. Then there exists a (pseudo) double category $F\mathbb{C}$sp which has:
 \begin{enumerate}
@@
 The left and right unitors together with the associator satisfy the standard pentagon and triangle identities of a monoidal category or bicategory.
-Finally, for the interchange law, given four 2-morphisms:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$a$};
-\node (A') at (0,-0.5) {$a^\prime$};
-\node (B) at (1,0.5) {$c$};
-\node (C) at (2,0.5) {$b$};
-\node (C') at (2,-0.5) {$b^\prime$};
-\node (D) at (1,-0.5) {$c^\prime$};
-\node (E) at (3,0.5) {$d_1 \in F(c)$};
-\node (F) at (3,-0.5) {$d_1^\prime \in F(c^\prime)$};
-\node (G) at (4,0.5) {$b$};
-\node (H) at (5,0.5) {$e$};
-\node (I) at (6,0.5) {$x$};
-\node (G') at (4,-0.5) {$b^\prime$};
-\node (H') at (5,-0.5) {$e^\prime$};
-\node (I') at (6,-0.5) {$x^\prime$};
-\node (J) at (7,0.5) {$d_2 \in F(e)$};
-\node (K) at (7,-0.5) {$d_2^\prime \in F(e^\prime)$};
-\node (L) at (1,-1) {$\iota_1 \colon F(h_1)(d_1) \to d_1^\prime$};
-\node (M) at (5,-1) {$\iota_2 \colon F(h_2)(d_2) \to d_2^\prime$};
-\node (A'') at (0,-1.5) {$a^\prime$};
-\node (A''') at (0,-2.5) {$a''$};
-\node (B'') at (1,-1.5) {$c^\prime$};
-\node (C'') at (2,-1.5) {$b^\prime$};
-\node (C''') at (2,-2.5) {$b''$};
-\node (D'') at (1,-2.5) {$c''$};
-\node (E'') at (3,-1.5) {$d_1^\prime \in F(c^\prime)$};
-\node (F'') at (3,-2.5) {$d_1'' \in F(c'')$};
-\node (G'') at (4,-1.5) {$b^\prime$};
-\node (H'') at (5,-1.5) {$e^\prime$};
-\node (I'') at (6,-1.5) {$x^\prime$};
-\node (G''') at (4,-2.5) {$b''$};
-\node (H''') at (5,-2.5) {$e''$};
-\node (I''') at (6,-2.5) {$x''$};
-\node (J'') at (7,-1.5) {$d_2^\prime \in F(e^\prime)$};
-\node (K'') at (7,-2.5) {$d_2'' \in F(e'')$};
-\node (L'') at (1,-3) {$\iota_1^\prime \colon F(h_1^\prime)(d_1^\prime) \to d_1''$};
-\node (M'') at (5,-3) {$\iota_2^\prime \colon F(h_2^\prime)(d_2^\prime) \to d_2''$};
+Finally, for the interchange law, given four 2-morphisms $\alpha, \beta, \alpha^\prime$ and $\beta^\prime$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0.5) {$a_1$};
+\node (A') at (0,-0.5) {$a_1^\prime$};
+\node (B) at (1,0.5) {$b$};
+\node (C) at (2,0.5) {$a_2$};
+\node (C') at (2,-0.5) {$a_2^\prime$};
+\node (D) at (1,-0.5) {$b^\prime$};
+\node (E) at (3,0.5) {$d_{M_1} \in F(b)$};
+\node (F) at (3,-0.5) {$d_{M_2} \in F(b^\prime)$};
+\node (G) at (4,0.5) {$a_2$};
+\node (H) at (5,0.5) {$c$};
+\node (I) at (6,0.5) {$a_3$};
+\node (G') at (4,-0.5) {$a_2^\prime$};
+\node (H') at (5,-0.5) {$c^\prime$};
+\node (I') at (6,-0.5) {$a_3^\prime$};
+\node (J) at (7,0.5) {$d_{N_1} \in F(c)$};
+\node (K) at (7,-0.5) {$d_{N_2} \in F(c^\prime)$};
+\node (L) at (1,-1) {$\iota_\alpha \colon F(h_1)(d_{M_1}) \to d_{M_2}$};
+\node (M) at (5,-1) {$\iota_\beta \colon F(h_2)(d_{N_1}) \to d_{N_2}$};
+\node (A'') at (0,-1.5) {$a_1^\prime$};
+\node (A''') at (0,-2.5) {$a_1''$};
+\node (B'') at (1,-1.5) {$b^\prime$};
+\node (C'') at (2,-1.5) {$a_2^\prime$};
+\node (C''') at (2,-2.5) {$a_2''$};
+\node (D'') at (1,-2.5) {$b''$};
+\node (E'') at (3,-1.5) {$d_{M_2} \in F(b^\prime)$};
+\node (F'') at (3,-2.5) {$d_{M_3} \in F(b'')$};
+\node (G'') at (4,-1.5) {$a_2^\prime$};
+\node (H'') at (5,-1.5) {$c^\prime$};
+\node (I'') at (6,-1.5) {$a_3^\prime$};
+\node (G''') at (4,-2.5) {$a_2''$};
+\node (H''') at (5,-2.5) {$c''$};
+\node (I''') at (6,-2.5) {$a_3''$};
+\node (J'') at (7,-1.5) {$d_{N_2} \in F(b^\prime)$};
+\node (K'') at (7,-2.5) {$d_{N_3} \in F(b'')$};
+\node (L'') at (1,-3) {$\iota_{\alpha^\prime} \colon F(h_1^\prime)(d_{M_2}) \to d_{M_3}$};
+\node (M'') at (5,-3) {$\iota_{\beta^\prime} \colon F(h_2^\prime)(d_{N_2}) \to d_{N_3}$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$a$};
-\node (A') at (0,-0.5) {$a^\prime$};
-\node (B) at (1.5,0.5) {$c+_b e$};
-\node (C) at (3,0.5) {$x$};
-\node (C') at (3,-0.5) {$x^\prime$};
-\node (D) at (1.5,-0.5) {$c^\prime +_{b^\prime} e^\prime$};
-\node (E) at (4.5,0.5) {$d_{1,2} \in F(c+_b e)$};
-\node (F) at (4.5,-0.5) {$d_{1,2}^\prime \in F(c^\prime +_{b^\prime} e^\prime)$};
-\node (G) at (1.5,-1) {$\iota_{1,2} \colon F(h_1 +_g h_2)(d_{1,2}) \to d_{1,2}^\prime$};
-\node (A'') at (0,-1.5) {$a^\prime$};
-\node (A''') at (0,-2.5) {$a''$};
-\node (B'') at (1.5,-1.5) {$c^\prime +_{b^\prime} e^\prime$};
-\node (C'') at (3,-1.5) {$x^\prime$};
-\node (C''') at (3,-2.5) {$x''$};
-\node (D'') at (1.5,-2.5) {$c'' +_{b''} e''$};
-\node (E'') at (4.5,-1.5) {$d_{1,2}^\prime \in F(c^\prime+_{b^\prime} e^\prime)$};
-\node (F'') at (4.5,-2.5) {$d_{1,2}'' \in F(c'' +_{b''} e'')$};
-\node (G'') at (1.5,-3) {$\iota_{1,2}^\prime \colon F(h_1^\prime +_{g^\prime} h_2^\prime)(d_{1,2}^\prime) \to d_{1,2}''.$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$j \psi_a i_1$} (B)
-(C) edge node[above]{$j \psi_x o_2$} (B)
+\node (A) at (0,0.5) {$a_1$};
+\node (A') at (0,-0.5) {$a_1^\prime$};
+\node (B) at (1.5,0.5) {$b+_{a_2} c$};
+\node (C) at (3,0.5) {$a_3$};
+\node (C') at (3,-0.5) {$a_3^\prime$};
+\node (D) at (1.5,-0.5) {$b^\prime +_{a_2^\prime} c^\prime$};
+\node (E) at (4.5,0.5) {$d_{M_1 \odot N_1} \in F(b+_{a_2} c)$};
+\node (F) at (4.5,-0.5) {$d_{M_2 \odot N_2} \in F(b^\prime +_{a_2^\prime} c^\prime)$};
+\node (G) at (1.5,-1) {$\iota_{\alpha \odot \beta} \colon F(h_1 +_g h_2)(d_{M_1 \odot N_1}) \to d_{M_1^\prime \odot N_1^\prime}$};
+\node (A'') at (0,-1.5) {$a_1^\prime$};
+\node (A''') at (0,-2.5) {$a_1''$};
+\node (B'') at (1.5,-1.5) {$b^\prime +_{a_2^\prime} c^\prime$};
+\node (C'') at (3,-1.5) {$a_3^\prime$};
+\node (C''') at (3,-2.5) {$a_3''$};
+\node (D'') at (1.5,-2.5) {$b'' +_{a_2''} c''$};
+\node (E'') at (4.5,-1.5) {$d_{M_2 \odot N_2} \in F(b^\prime+_{a_2^\prime} c^\prime)$};
+\node (F'') at (4.5,-2.5) {$d_{M_3 \odot N_3} \in F(b'' +_{a_2''} c'')$};
+\node (G'') at (1.5,-3) {$\iota_{\alpha^\prime \odot \beta^\prime} \colon F(h_1^\prime +_{g^\prime} h_2^\prime)(d_{M_2 \odot N_2}) \to d_{M_3 \odot N_3}.$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$j \psi_{a_1} i_1$} (B)
+(C) edge node[above]{$j \psi_{a_3} o_2$} (B)
 (A) edge node[left]{$f$} (A')
 (C) edge node[left]{$k$} (C')
-(A') edge node [above]{$j \psi_{a^\prime} i_1^\prime$} (D)
-(C') edge node [above]{$j \psi_{x^\prime} o_2^\prime$} (D)
+(A') edge node [above]{$j \psi_{a_1^\prime} i_1^\prime$} (D)
+(C') edge node [above]{$j \psi_{a_3^\prime} o_2^\prime$} (D)
 (B) edge node [left] {$h_1 +_g h_2$} (D)
-(A'') edge node[above]{$j \psi_{a^\prime} i_1^\prime$} (B'')
-(C'') edge node[above]{$j \psi_{x^\prime} o_2^\prime$} (B'')
+(A'') edge node[above]{$j \psi_{a_1^\prime} i_1^\prime$} (B'')
+(C'') edge node[above]{$j \psi_{a_3^\prime} o_2^\prime$} (B'')
 (A'') edge node[left]{$f^\prime$} (A''')
 (C'') edge node[left]{$k^\prime$} (C''')
-(A''') edge node [above]{$j \psi_{a''} i_1''$} (D'')
-(C''') edge node [above]{$j \psi_{x''} o_2''$} (D'')
+(A''') edge node [above]{$j \psi_{a_1''} i_1''$} (D'')
+(C''') edge node [above]{$j \psi_{a_3''} o_2''$} (D'')
 (B'') edge node [left] {$h_1^\prime +_{g^\prime} h_2^\prime$} (D'');
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (4,0) {$\iota_1 \Swarrow$};
+\node (A) at (4,0) {$\iota_\alpha \Swarrow$};
 \node (D) at (3,0) {$1$};
-\node (E) at (4.5,0.5) {$F(c)$};
-\node (E') at (4.5,-0.5) {$F(c^\prime)$};
-\node (A') at (6.5,0) {$\iota_2 \Swarrow$};
+\node (E) at (4.5,0.5) {$F(b)$};
+\node (E') at (4.5,-0.5) {$F(b^\prime)$};
+\node (A') at (6.5,0) {$\iota_\beta \Swarrow$};
 \node (D') at (5.5,0) {$1$};
-\node (E'') at (7,0.5) {$F(e)$};
-\node (E''') at (7,-0.5) {$F(e^\prime)$};
-\path[->,font=\scriptsize,>=angle 90]
-(D) edge node [above] {$d_1$} (E)
-(D) edge node [below] {$d_1^\prime$} (E')
+\node (E'') at (7,0.5) {$F(c)$};
+\node (E''') at (7,-0.5) {$F(c^\prime)$};
+\path[->,font=\scriptsize,>=angle 90]
+(D) edge node [above] {$d_{M_1}$} (E)
+(D) edge node [below] {$d_{M_2}$} (E')
 (E) edge node [right] {$F(h_1)$} (E')
-(D') edge node [above] {$d_2$} (E'')
-(D') edge node [below] {$d_2^\prime$} (E''')
+(D') edge node [above] {$d_{N_1}$} (E'')
+(D') edge node [below] {$d_{N_2}$} (E''')
 (E'') edge node [right] {$F(h_2)$} (E''');
@@
 \]
-and then multiply these viewed as two 2-morphisms in $\mathbf{Cat}$ which results in:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (4.75,0) {$\iota_1 \times \iota_2 \Swarrow$};
+These two 2-morphisms $\iota_\alpha$ and $\iota_\beta$ are two 2-morphisms in the monoidal 2-category $(\mathbf{Cat},\times,1)$ and so we can tensor them which results in:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (4.75,0) {$\iota_\alpha \times \iota_\beta \Swarrow$};
 \node (D) at (3,0) {$1 \xrightarrow{\lambda^{-1}} 1 \times 1$};
-\node (E) at (5.5,0.5) {$F(c) \times F(e)$};
-\node (E') at (5.5,-0.5) {$F(c^\prime) \times F(e^\prime)$};
-\node (B) at (7.5,0.5) {$F(c+e)$};
-\node (B') at (7.5,-0.5) {$F(c^\prime + e^\prime)$};
-\node (C) at (9,0.5) {$F(c+_b e)$};
-\node (C') at (9,-0.5) {$F(c^\prime +_{b^\prime} e^\prime)$};
-\path[->,font=\scriptsize,>=angle 90]
-(E) edge node [above] {$\phi_{c,e}$} (B)
-(E') edge node [above] {$\phi_{c^\prime,e^\prime}$} (B')
-(B) edge node [above] {$F(j_{c,e})$} (C)
-(B') edge node [above] {$F(j_{c^\prime,e^\prime})$} (C')
+\node (E) at (5.5,0.5) {$F(b) \times F(c)$};
+\node (E') at (5.5,-0.5) {$F(b^\prime) \times F(c^\prime)$};
+\node (B) at (7.5,0.5) {$F(b+c)$};
+\node (B') at (7.5,-0.5) {$F(b^\prime + c^\prime)$};
+\node (C) at (9.25,0.5) {$F(b+_{a_2} c)$};
+\node (C') at (9.25,-0.5) {$F(b^\prime +_{a_2^\prime} c^\prime)$};
+\path[->,font=\scriptsize,>=angle 90]
+(E) edge node [above] {$\phi_{b,c}$} (B)
+(E') edge node [above] {$\phi_{b^\prime,c^\prime}$} (B')
+(B) edge node [above] {$F(j_{b,c})$} (C)
+(B') edge node [above] {$F(j_{b^\prime,c^\prime})$} (C')
 (C) edge node [right] {$F(h_1 +_g h_2)$} (C')
 (B) edge node [right] {$F(h_1 + h_2)$} (B')
-(D) edge node [above] {$d_1 \times d_2$} (E)
-(D) edge node [below] {$d_1^\prime \times d_2^\prime$} (E')
+(D) edge node [above] {$d_{M_1} \times d_{N_1}$} (E)
+(D) edge node [below] {$d_{M_2} \times d_{N_2}$} (E')
 (E) edge node [right] {$F(h_1) \times F(h_2)$} (E');
@@
 where the middle square commutes since $F$ is a lax monoidal pseudofunctor and the right square commutes as the underlying diagram commutes.
-The objects $d_{1,2}$ and $d^\prime_{1,2}$ are given by top and bottom composite of arrows and the morphism of decorations $\iota_{1,2}$ is given by composing $\iota_1 \times \iota_2$ with the two commuting squares.
+The decorations $d_{M_1 \odot N_1}$ and $d_{M_2 \odot N_2}$ are given respectively by top and bottom composite of arrows and the morphism of decorations $\iota_{\alpha \odot \beta}$ is given by composing $\iota_\alpha \times \iota_\beta$ with the two commuting squares, which can equivalently be viewed as a morphism in $F(b' +_{a_2'} c')$.
+
 Returning to the interchange law, composing the two horizontal compositions above vertically then results in:
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$a$};
-\node (A') at (0,-0.5) {$a''$};
-\node (B) at (2,0.5) {$c+_b e$};
-\node (C) at (4,0.5) {$x$};
-\node (C') at (4,-0.5) {$x''$};
-\node (D) at (2,-0.5) {$c'' +_{b''} e''$};
-\node (E) at (5.5,0.5) {$d_{1,2} \in F(c+_b e)$};
-\node (F) at (5.5,-0.5) {$d_{1,2}'' \in F(c'' +_{b''} e'')$};
-\node (G) at (2,-1) {$(\iota_{1,2}^\prime \iota_{1,2}) \colon F((h_1^\prime +_{g^\prime} h_2^\prime)(h_1 +_g h_2))(d_{1,2}) \to d_{1,2}''.$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$j \psi_a i_1$} (B)
-(C) edge node[above]{$j \psi_x o_2$} (B)
+\node (A) at (0,0.5) {$a_1$};
+\node (A') at (0,-0.5) {$a_1''$};
+\node (B) at (2,0.5) {$b+_{a_2} c$};
+\node (C) at (4,0.5) {$a_3$};
+\node (C') at (4,-0.5) {$a_3''$};
+\node (D) at (2,-0.5) {$b'' +_{a_2''} c''$};
+\node (E) at (5.5,0.5) {$d_{M_1 \odot N_1} \in F(b+_{a_2} c)$};
+\node (F) at (5.5,-0.5) {$d_{M_3 \odot N_3} \in F(b'' +_{a_2''} c'')$};
+\node (G) at (2,-1) {$\iota_{(a^\prime \odot \beta^\prime)(\alpha \odot \beta)} \colon F((h_1^\prime +_{g^\prime} h_2^\prime)(h_1 +_g h_2))(d_{M_1 \odot N_1}) \to d_{M_3 \odot N_3}.$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$j \psi_{a_1} i_1$} (B)
+(C) edge node[above]{$j \psi_{a_3} o_2$} (B)
 (A) edge node[left]{$f^\prime f$} (A')
 (C) edge node[left]{$k^\prime k$} (C')
-(A') edge node [above]{$j \psi_{a''} i_1''$} (D)
-(C') edge node [above]{$j \psi_{x''} o_2''$} (D)
+(A') edge node [above]{$j \psi_{a_1''} i_1''$} (D)
+(C') edge node [above]{$j \psi_{a_3''} o_2''$} (D)
 (B) edge node [left] {$(h_1^\prime +_{g^\prime} h_2^\prime)(h_1 +_g h_2)$} (D);
@@
 \]
-\textbf{F being pseudo might do something here...}
 The vertical composite of two morphisms of decorations is straightforward. On the other hand, if we first compose vertically we obtain:
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$a$};
-\node (A') at (0,-0.5) {$a''$};
-\node (B) at (1,0.5) {$c$};
-\node (C) at (2,0.5) {$b$};
-\node (C') at (2,-0.5) {$b''$};
-\node (D) at (1,-0.5) {$c''$};
-\node (E) at (3,0.5) {$d_1 \in F(c)$};
-\node (F) at (3,-0.5) {$d_1'' \in F(c'')$};
-\node (G) at (4,0.5) {$b$};
-\node (H) at (5,0.5) {$e$};
-\node (I) at (6,0.5) {$x$};
-\node (G') at (4,-0.5) {$b''$};
-\node (H') at (5,-0.5) {$e''$};
-\node (I') at (6,-0.5) {$x''$};
-\node (J) at (7,0.5) {$d_2 \in F(e)$};
-\node (K) at (7,-0.5) {$d_2'' \in F(e'')$};
-\node (L) at (1,-1) {$\iota_1^\prime \iota_1 \colon F(h_1^\prime h_1)(d_1) \to d_1''$};
-\node (M) at (5,-1) {$\iota_2^\prime \iota_2 \colon F(h_2^\prime h_2)(d_2) \to d_2''$};
+\node (A) at (0,0.5) {$a_1$};
+\node (A') at (0,-0.5) {$a_1''$};
+\node (B) at (1,0.5) {$b$};
+\node (C) at (2,0.5) {$a_2$};
+\node (C') at (2,-0.5) {$a_2''$};
+\node (D) at (1,-0.5) {$b''$};
+\node (E) at (3,0.5) {$d_{M_1} \in F(b)$};
+\node (F) at (3,-0.5) {$d_{M_3} \in F(b'')$};
+\node (G) at (4,0.5) {$a_2$};
+\node (H) at (5,0.5) {$c$};
+\node (I) at (6,0.5) {$a_3$};
+\node (G') at (4,-0.5) {$a_2''$};
+\node (H') at (5,-0.5) {$c''$};
+\node (I') at (6,-0.5) {$a_3''$};
+\node (J) at (7,0.5) {$d_{N_1} \in F(c)$};
+\node (K) at (7,-0.5) {$d_{N_3} \in F(c'')$};
+\node (L) at (1,-1) {$\iota_{\alpha^\prime \alpha} \colon F(h_1^\prime h_1)(d_{M_1}) \to d_{M_3}$};
+\node (M) at (5,-1) {$\iota_{\beta^\prime \beta} \colon F(h_2^\prime h_2)(d_{N_1}) \to d_{N_3}$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$a$};
-\node (A') at (0,-0.5) {$a''$};
-\node (B) at (2,0.5) {$c+_b e$};
-\node (C) at (4,0.5) {$x$};
-\node (C') at (4,-0.5) {$x''$};
-\node (D) at (2,-0.5) {$c'' +_{b''} e''$};
-\node (E) at (5.5,0.5) {$d_{1,2} \in F(c+_b e)$};
-\node (F) at (5.5,-0.5) {$d_{1,2}'' \in F(c'' +_{b''} e'')$};
-\node (G) at (2,-1) {$(\iota_1^\prime \iota_1,\iota_2^\prime \iota_2) \colon F((h_1^\prime h_1)+_{g^\prime g} (h_2^\prime h_2))(d_{1,2}) \to d_{1,2}''.$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$j \psi_a i_1$} (B)
-(C) edge node[above]{$j \psi_x o_2$} (B)
+\node (A) at (0,0.5) {$a_1$};
+\node (A') at (0,-0.5) {$a_1''$};
+\node (B) at (2,0.5) {$b+_{a_2} c$};
+\node (C) at (4,0.5) {$a_3$};
+\node (C') at (4,-0.5) {$a_3''$};
+\node (D) at (2,-0.5) {$b'' +_{a_2''} c''$};
+\node (E) at (5.5,0.5) {$d_{M_1 \odot N_1} \in F(b+_{a_2} c)$};
+\node (F) at (5.5,-0.5) {$d_{M_3 \odot N_3} \in F(b'' +_{a_3''} c'')$};
+\node (G) at (2,-1) {$\iota_{(\alpha^\prime \alpha) \odot (\beta^\prime \beta)} \colon F((h_1^\prime h_1)+_{g^\prime g} (h_2^\prime h_2))(d_{M_1 \odot N_1}) \to d_{M_3 \odot N_3}.$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$j \psi_{a_1} i_1$} (B)
+(C) edge node[above]{$j \psi_{a_3} o_2$} (B)
 (A) edge node[left]{$f^\prime f$} (A')
 (C) edge node[left]{$k^\prime k$} (C')
-(A') edge node [above]{$j \psi_{a''} i_1''$} (D)
-(C') edge node [above]{$j \psi_{x''} o_2''$} (D)
+(A') edge node [above]{$j \psi_{a_1''} i_1''$} (D)
+(C') edge node [above]{$j \psi_{a_3''} o_2''$} (D)
 (B) edge node [left] {$(h_1^\prime h_1) +_{g^\prime g} (h_2^\prime h_2)$} (D);
@@
 %\]
-As is usual concerning the interchange law of double categories of this nature, only the `interior' of the two compositions appears different, but the two morphisms $(h_1^\prime +_{g^\prime} h_2^\prime)(h_1 +_g h_2) \colon c+_b e \to c'' +_{b''} e''$ and $(h_1^\prime h_1) +_{g^\prime g} (h_2^\prime h_2) \colon c+_b e \to c'' +_{b''}e''$ are the same universal map realized in two different ways.
-The two morphisms of decorations are two compositions of 2-morphisms in $\mathbf{Cat}$ for which the interchange law already holds, and as a result, the morphisms $$(\iota_{1,2}^\prime \iota_{1,2}) \colon F((h_1^\prime +_{g^\prime} h_2^\prime)(h_1 +_g h_2))(d_{1,2}) \to d_{1,2}''$$ and $$(\iota_1^\prime \iota_1,\iota_2^\prime \iota_2) \colon F((h_1^\prime h_1)+_{g^\prime g} (h_2^\prime h_2))(d_{1,2}) \to d_{1,2}''$$ are also the same.
+As is usual concerning the interchange law of double categories of this nature, only the `interior' of the two compositions appears different, but the two morphisms $(h_1^\prime +_{g^\prime} h_2^\prime)(h_1 +_g h_2) \colon b+_{a_2} c \to b'' +_{a_2''} c''$ and $(h_1^\prime h_1) +_{g^\prime g} (h_2^\prime h_2) \colon b+_{a_2} c \to b'' +_{a_2''}c''$ are the same universal map realized in two different ways.
+The two morphisms of decorations $\iota_{(\alpha^\prime \odot \beta^\prime)(\alpha \odot \beta)}$ and $\iota_{(\alpha^\prime \alpha) \odot (\beta^\prime \beta)}$ are obtained as two different compositions of four 2-morphisms in $\mathbf{Cat}$, namely horizontally then vertically and vertically then horizontally.
+As $\mathbf{Cat}$ is a 2-category, the interchange law for these 2-morphisms already holds, and as a result, the morphisms $$\iota_{(\alpha' \odot \beta')(\alpha \odot \beta)} \colon F((h_1^\prime +_{g^\prime} h_2^\prime)(h_1 +_g h_2))(d_{M_1 \odot N_1}) \to d_{M_3 \odot N_3}$$ and $$\iota_{(\alpha^\prime \alpha)\odot(\beta^\prime \beta)} \colon F((h_1^\prime h_1)+_{g^\prime g} (h_2^\prime h_2))(d_{M_1 \odot N_1}) \to d_{M_3 \odot N_3}$$ are also the same.
+Thus the interchange law for 2-morphisms holds and $F\mathbb{C}$sp is a double category.
 \end{proof}

### 2019-01-04 EquivCompFrameworks_20180911kc.tex
Polishing Theorem 2.2

@@
 \begin{thm}\label{DC}
-Let $\mathrm{A}$ be a category with finite colimits and $F \colon \mathrm{A} \to \mathbf{Cat}$ a symmetric lax monoidal pseudofunctor.
-Then the double category $\mathbb{F}\textnormal{Cospan}(\mathrm{A})$ is symmetric monoidal.
+Let $\mathsf{A}$ be a category with finite colimits and $F \colon \mathsf{A} \to \mathbf{Cat}$ a symmetric lax monoidal pseudofunctor. Then the double category $F\mathbb{C}$sp is symmetric monoidal.
 \end{thm}
 \begin{proof}
-First we note that the category of objects $\mathbb{F}\textnormal{Cospan}(\mathrm{A})_0=\mathrm{A}$ is symmetric monoidal under binary coproducts and the left and right unitors, associators and braidings are given as natural maps.
-The category of arrows $\mathbb{F}\textnormal{Cospan}(\mathrm{A})_1$ has:
+First we note that the category of objects $F\mathbb{C}\textnormal{sp}_0=\mathsf{A}$ is symmetric monoidal under binary coproducts and the left and right unitors, associators and braidings are given as natural maps.
+The category of arrows $F\mathbb{C}\textnormal{sp}_1$ has:
 \begin{enumerate}
-\item{objects as pairs:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a$};
-\node (B) at (1,0) {$c$};
-\node (C) at (2,0) {$b$};
-\node (D) at (3,0) {$d \in F(c)$};
+\item{objects as $F$-decorated cospans which are pairs:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$a_1$};
+\node (B) at (1,0) {$b$};
+\node (C) at (2,0) {$a_2$};
+\node (D) at (3,0) {$d \in F(b)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 and}
-\item{morphisms as maps of cospans in $\mathrm{A}$
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$a$};
-\node (A') at (0,-0.5) {$a^\prime$};
-\node (B) at (1,0.5) {$c$};
-\node (C) at (2,0.5) {$b$};
-\node (C') at (2,-0.5) {$b^\prime$};
-\node (D) at (1,-0.5) {$c^\prime$};
-\node (E) at (3,0.5) {$d \in F(c)$};
-\node (F) at (3,-0.5) {$d^\prime \in F(c^\prime)$};
+\item{morphisms as maps of cospans in $\mathsf{A}$
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0.5) {$a_1$};
+\node (A') at (0,-0.5) {$a_1^\prime$};
+\node (B) at (1,0.5) {$b$};
+\node (C) at (2,0.5) {$a_2$};
+\node (C') at (2,-0.5) {$a_2^\prime$};
+\node (D) at (1,-0.5) {$b^\prime$};
+\node (E) at (3,0.5) {$d \in F(b)$};
+\node (F) at (3,-0.5) {$d^\prime \in F(b^\prime)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-together with elements of the images of the apices under the pseudofunctor $F$ and a morphism $\iota \colon F(h)(d) \to d^\prime$.
+together with a morphism $\iota \colon F(h)(d) \to d^\prime$.
 }
 \end{enumerate}
-Given two objects $M_1$ and $M_2$ of $\mathbb{F}\textnormal{Cospan}(\mathrm{A})_1$:
+Given two objects $M_1$ and $M_2$ of $F\mathbb{C}\textnormal{sp}_1$:
 \[
@@
 \node (A) at (0,0) {$a_1$};
-\node (B) at (1,0) {$c_1$};
-\node (C) at (2,0) {$b_1$};
-\node (D) at (1,-0.5) {$d_1 \in F(c_1)$};
-\node (E) at (3,0) {$a_2$};
-\node (F) at (4,0) {$c_2$};
-\node (G) at (5,0) {$b_2$};
-\node (H) at (4,-0.5) {$d_2 \in F(c_2)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i_1$} (B)
-(C) edge node[above]{$o_1$} (B)
-(E) edge node[above]{$i_2$} (F)
-(G) edge node[above]{$o_2$} (F);
-\end{tikzpicture}
-\]
-their tensor product $M_1 \otimes M_2$ is given by taking the coproducts of the cospans of $\mathrm{A}$
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a_1+a_2$};
-\node (B) at (1.25,0) {$c_1+c_2$};
-\node (C) at (2.5,0) {$b_1+b_2$};
-\node (D) at (4.25,0) {$d_{M_1 \otimes M_2} \in F(c_1+c_2)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i_1+i_2$} (B)
-(C) edge node[above]{$o_1+o_2$} (B);
-\end{tikzpicture}
-\]
-and where the element of the image of the apex under $F$  is obtained using the natural transformation of the symmetric lax monoidal pseudofunctor $F:$ $$1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{d_1 \times d_2} F(c_1) \times F(c_2) \xrightarrow{\phi_{c_1,c_2}} F(c_1 + c_2).$$The monoidal unit is given by:
+\node (B) at (1,0) {$b$};
+\node (C) at (2,0) {$a_2$};
+\node (D) at (1,-0.5) {$d_{M_1} \in F(b)$};
+\node (E) at (3,0) {$a_1^\prime$};
+\node (F) at (4,0) {$b^\prime$};
+\node (G) at (5,0) {$a_2^\prime$};
+\node (H) at (4,-0.5) {$d_{M_2} \in F(b^\prime)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i$} (B)
+(C) edge node[above]{$o$} (B)
+(E) edge node[above]{$i^\prime$} (F)
+(G) edge node[above]{$o^\prime$} (F);
+\end{tikzpicture}
+\]
+their tensor product $M_1 \otimes M_2$ is given by taking the coproducts of the cospans of $\mathsf{A}$
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$a_1+a_1^\prime$};
+\node (B) at (1.25,0) {$b+b^\prime$};
+\node (C) at (2.5,0) {$a_2+a_2^\prime$};
+\node (D) at (4.25,0) {$d_{M_1 \otimes M_2} \in F(b+b')$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i+i'$} (B)
+(C) edge node[above]{$o+o'$} (B);
+\end{tikzpicture}
+\]
+and where the decoration on the apex is obtained using the natural transformation of the symmetric lax monoidal pseudofunctor $F:$ $$d_{M_1 \otimes M_2} \coloneqq 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{d_{M_1} \times d_{M_2}} F(b) \times F(b') \xrightarrow{\phi_{b,b'}} F(b+b').$$The monoidal unit 0 is given by:
 \[
@@
 \node (C) at (2,0) {$0$};
-\node (D) at (3,0) {$! \in F(0)$};
+\node (D) at (3,0) {$!_0 \in F(0)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-where $0$ is the monoidal unit of $\mathrm{A}$ and $!
-\colon 1 \to F(0)$ is the morphism which is part of the structure of the symmetric lax monoidal pseudofunctor $F \colon \mathrm{A} \to \mathbf{Cat}$.
+where $0$ is the monoidal unit of $\mathsf{A}$ and $!_0 \colon 1 \to F(0)$ is the morphism which is part of the structure of the symmetric lax monoidal pseudofunctor $F \colon \mathsf{A} \to \mathbf{Cat}$.
 Tensoring an object with the monoidal unit, say, on the left:
@@
 \node (C) at (2,0) {$0$};
-\node (D) at (1,-0.5) {$! \in F(0)$};
-\node (E) at (3,0) {$a$};
-\node (F) at (4,0) {$c$};
-\node (G) at (5,0) {$b$};
-\node (H) at (4,-0.5) {$d \in F(c)$};
+\node (D) at (1,-0.5) {$!_0 \in F(0)$};
+\node (E) at (3,0) {$a_1$};
+\node (F) at (4,0) {$b$};
+\node (G) at (5,0) {$a_2$};
+\node (H) at (4,-0.5) {$d_M \in F(b)$};
+\node (I) at (2.5,0) {$\otimes$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$0+a$};
-\node (B) at (1,0) {$0+c$};
-\node (C) at (2,0) {$0+b$};
-\node (D) at (3.5,0) {$d^\prime \in F(0+c)$};
+\node (A) at (0,0) {$0+a_1$};
+\node (B) at (1,0) {$0+b$};
+\node (C) at (2,0) {$0+a_2$};
+\node (D) at (3.5,0) {$d_{0 \otimes M} \in F(0+b)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-where $d^\prime \in F(0+c)$ is given by $$1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{\phi \times d} F(0) \times F(c) \xrightarrow{\phi_{0,d}} F(0+c).$$The left unitor is then a morphism in $\mathbb{F} \textnormal{Cospan}(\mathrm{A})_1$ given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$0+a$};
-\node (A') at (0,-0.5) {$a$};
-\node (B) at (1,0.5) {$0+c$};
-\node (C) at (2,0.5) {$0+b$};
-\node (C') at (2,-0.5) {$b$};
-\node (D) at (1,-0.5) {$c$};
-\node (E) at (3.5,0.5) {$d^\prime \in F(0+c)$};
-\node (F) at (3.5,-0.5) {$d \in F(c)$};
+where $d_{0\otimes M} \in F(0+b)$ is given by $$1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{!_0 \times d_M} F(0) \times F(b) \xrightarrow{\phi_{0,b}} F(0+b).$$The left unitor is then an isomorphism in $F\mathbb{C}\textnormal{sp}_1$ given by:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0.5) {$0+a_1$};
+\node (A') at (0,-0.5) {$a_1$};
+\node (B) at (1,0.5) {$0+b$};
+\node (C) at (2,0.5) {$0+a_2$};
+\node (C') at (2,-0.5) {$a_2$};
+\node (D) at (1,-0.5) {$b$};
+\node (E) at (3.5,0.5) {$d_{0+M} \in F(0+b)$};
+\node (F) at (3.5,-0.5) {$d_M \in F(b)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-where $\ell$ is the left unitor of $(\mathrm{A},+,0)$, together with the morphism $\iota_{\lambda} \colon F(\ell)(d^\prime) \to d$. The right unitor is similar.
-
-Given three objects $M_1, M_2$ and $M_3$ in $\mathbb{F}\textnormal{Cospan}(\mathrm{A})_1$:
+where $\ell$ is the left unitor of $(\mathsf{A},+,0)$, together with the isomorphism $\iota_{\lambda} \colon F(\ell)(d_{0 \otimes M}) \to d_M$ which is specified by the isomorphism of categories $F(0+b) \cong F(b)$.
+The right unitor is similar.
+
+Given three objects $M_1, M_2$ and $M_3$ in $F\mathbb{C}\textnormal{sp}_1$:
 \[
@@
 \node (C) at (2,0) {$b_1$};
-\node (D) at (1,-0.5) {$d_1 \in F(c_1)$};
+\node (D) at (1,-0.5) {$d_{M_1} \in F(c_1)$};
 \node (E) at (3,0) {$a_2$};
@@
 \node (G) at (5,0) {$b_2$};
-\node (H) at (4,-0.5) {$d_2 \in F(c_2)$};
+\node (H) at (4,-0.5) {$d_{M_2} \in F(c_2)$};
 \node (I) at (6,0) {$a_3$};
@@
 \node (K) at (8,0) {$b_3$};
-\node (L) at (7,-0.5) {$d_3 \in F(c_3)$};
+\node (L) at (7,-0.5) {$d_{M_3} \in F(c_3)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-where $d_{(M_1 \otimes M_2) \otimes M_3} \colon 1 \to F((c_1+c_2)+c_3)$ is given by: $$1 \xrightarrow{((d_1 \times d_2) \times d_3)} (F(c_1) \times F(c_2)) \times F(c_3) \xrightarrow{\phi_{c_1,c_2} \times 1} F(c_1+c_2) \times F(c_3) \xrightarrow{\phi_{c_1+c_2,c_3}} F((c_1+c_2)+c_3)$$whereas tensoring the last two and then the first results in $M_1 \otimes (M_2 \otimes M_3)$:
+where $d_{(M_1 \otimes M_2) \otimes M_3} \colon 1 \to F((c_1+c_2)+c_3)$ is given by: $$1 \xrightarrow{(d_{M_1} \times d_{M_2}) \times d_{M_3})} (F(c_1) \times F(c_2)) \times F(c_3) \xrightarrow{\phi_{c_1,c_2} \times 1} F(c_1+c_2) \times F(c_3) \xrightarrow{\phi_{c_1+c_2,c_3}} F((c_1+c_2)+c_3)$$whereas tensoring the last two and then the first results in $M_1 \otimes (M_2 \otimes M_3)$:
 \[
@@
 \]
-where $d_{M_1 \otimes (M_2 \otimes M_3)} \colon 1 \to F(c_1+(c_2+c_3))$ is given by: $$1 \xrightarrow{d_1 \times (d_2 \times d_3)} F(c_1) \times (F(c_2) \times F(c_3)) \xrightarrow{1 \times \phi_{c_2,c_3}} F(c_1) \times F(c_2+c_3) \xrightarrow{\phi_{c_1,c_2+c_3}} F(c_1+(c_2+c_3)).$$If we let $a$ denote the associator of $(\mathrm{A},+,0)$, the associator of $\mathbb{F} \textnormal{Cospan}(\mathrm{A})_1$ is then a map of cospans in $\mathrm{A}$ from $(M_1 \otimes M_2) \otimes M_3)$ to $M_1 \otimes (M_2 \otimes M_3)$ given by:
+where $d_{M_1 \otimes (M_2 \otimes M_3)} \colon 1 \to F(c_1+(c_2+c_3))$ is given by: $$1 \xrightarrow{d_{M_1} \times (d_{M_2} \times d_{M_3})} F(c_1) \times (F(c_2) \times F(c_3)) \xrightarrow{1 \times \phi_{c_2,c_3}} F(c_1) \times F(c_2+c_3) \xrightarrow{\phi_{c_1,c_2+c_3}} F(c_1+(c_2+c_3)).$$If we let $a$ denote the associator of $(\mathsf{A},+,0)$, the associator of $F\mathbb{C}\textnormal{sp}_1$ is then a map of cospans in $\mathsf{A}$ from $(M_1 \otimes M_2) \otimes M_3$ to $M_1 \otimes (M_2 \otimes M_3)$ given by:
 \[
@@
 together with the isomorphism $\iota_a \colon F(a)(d_{(M_1 \otimes M_2) \otimes M_3}) \to d_{M_1 \otimes (M_2 \otimes M_3)}$.
-If we denote the above associator simply as $a$ and the left and right unitors as $\lambda$ and $\rho$, respectively, then given four objects in $\mathbb{F}\textnormal{Cospan}(\mathrm{A})_1$, say $M_1, M_2, M_3$ and $M_4$:
+If we denote the above associator simply as $a$ and the left and right unitors as $\lambda$ and $\rho$, respectively, then given four objects in $F\mathbb{C}\textnormal{sp}_1$, say $M_1, M_2, M_3$ and $M_4$:
 \[
@@
 \node (G) at (5,0) {$b_2$};
-\node (H) at (4,-0.5) {$d_2 \in F(c_2)$};
+\node (H) at (4,-0.5) {$d_{M_2} \in F(c_2)$};
 \node (I) at (0,-1.5) {$a_3$};
@@
 \node (K) at (2,-1.5) {$b_3$};
-\node (L) at (1,-2) {$d_3 \in F(c_3)$};
+\node (L) at (1,-2) {$d_{M_3} \in F(c_3)$};
 \node (M) at (3,-1.5) {$a_4$};
@@
 \node (O) at (5,-1.5) {$b_4$};
-\node (P) at (4,-2) {$d_4 \in F(c_4)$};
+\node (P) at (4,-2) {$d_{M_4} \in F(c_4)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-then the following pentagon of underlying cospans commutes:
+then as $\mathbb{C}\textnormal{sp}(\mathsf{A})$ is a symmetric monoidal double category, the following pentagon of underlying cospans commutes:
 \[
@@
 \]
-since $$F(aa)(d_{((M_1 \otimes M_2) \otimes M_3) \otimes M_4})=F((1 \otimes a)a(a \otimes 1))(d_{((M_1 \otimes M_2) \otimes M_3) \otimes M_4})$$ as the above underlying diagram of maps of cospans commutes.
+since $$F(aa)(d_{((M_1 \otimes M_2) \otimes M_3) \otimes M_4})=F((1 \otimes a)a(a \otimes 1))(d_{((M_1 \otimes M_2) \otimes M_3) \otimes M_4})$$ as the corresponding pentagon in the symmetric monoidal category $(\mathsf{A},+,0)$ commutes.
 
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$(M_1 \otimes U_{0}) \otimes M_2$};
+\node (A) at (0,0) {$(M_1 \otimes 0) \otimes M_2$};
 \node (B) at (2.25,1) {$M_1 \otimes M_2$};
-\node (C) at (4.5,0) {$M_1 \otimes (U_0 \otimes M_2)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[left]{$\rho \otimes 1$} (B)
-(C) edge node[right]{$1 \otimes \lambda$} (B)
+\node (C) at (4.5,0) {$M_1 \otimes (0 \otimes M_2)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$\rho \otimes 1$} (B)
+(C) edge node[above]{$1 \otimes \lambda$} (B)
 (A) edge node[above]{$a$} (C);
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$F(\rho \otimes 1)(d_{(M_1 \otimes U_0) \otimes M_2})$};
+\node (A) at (0,0) {$F(\rho \otimes 1)(d_{(M_1 \otimes 0) \otimes M_2})$};
 \node (B) at (2.25,1) {$d_{M_1 \otimes M_2}$};
-\node (C) at (4.5,0) {$F(1 \otimes \lambda)(d_{M_1 \otimes (U_0 \otimes M_2)}) $};
+\node (C) at (4.5,0) {$F(1 \otimes \lambda)(d_{M_1 \otimes (0 \otimes M_2)}) $};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (C) edge node[right]{$\iota_{1 \otimes \lambda}$} (B)
-(A) edge node[above]{$F(\iota_a)$} (C);
-\end{tikzpicture}
-\]
-since $$F(\rho \otimes 1)(d_{(M_1 \otimes U_0) \otimes M_2})=F(a \otimes (1 \otimes \lambda))(d_{(M_1 \otimes U_0) \otimes M_2})$$ as the above underlying diagram of maps of cospans commutes.
-
-For a monoidal product of objects $M_1 \otimes M_2$ in $\mathbb{F} \textnormal{Cospan}(\mathrm{A})_1$, the source and target structure functors $S,T \colon \mathbb{F} \textnormal{Cospan}(\mathrm{A})_1 \to \mathbb{F} \textnormal{Cospan}(\mathrm{A})_0$ satisfy the following equations: $$S(M_1 \otimes M_2)=S(M_1) \otimes S(M_2)$$ $$T(M_1 \otimes M_2)=T(M_1) \otimes T(M_2).$$
-For two objects $M_1$ and $M_2$ in $\mathbb{F} \textnormal{Cospan}(\mathrm{A})_1$, we have a braiding $\beta_{M_1,M_2} \colon M_1 \otimes M_2 \to M_2 \otimes M_1$ given by:
+(A) edge node[above]{$F(1 \otimes \lambda)(\iota_a)$} (C);
+\end{tikzpicture}
+\]
+since $$F(\rho \otimes 1)(d_{(M_1 \otimes 0) \otimes M_2})=F((1 \otimes \lambda)a)(d_{(M_1 \otimes 0) \otimes M_2})$$ as the corresponding triangle in the symmetric monoidal category $(\mathsf{A},+,0)$ commutes.
+
+For a tensor product of objects $M_1 \otimes M_2$ in $F\mathbb{C}\textnormal{sp}_1$, the source and target structure functors $S,T \colon F\mathbb{C}\textnormal{sp}_1 \to F\mathbb{C}\textnormal{sp}_0$ satisfy the following equations: $$S(M_1 \otimes M_2)=S(M_1) \otimes S(M_2)$$ $$T(M_1 \otimes M_2)=T(M_1) \otimes T(M_2).$$
+For two objects $M_1$ and $M_2$ in $F\mathbb{C}\textnormal{sp}_1$, we have a braiding $\beta_{M_1,M_2} \colon M_1 \otimes M_2 \to M_2 \otimes M_1$ given by:
 \[
@@
 \]
-$$\iota_{\beta_{M_1,M_2}} \colon F(\beta_{c_1,c_2})(d_{M_1 \otimes M_2}) \xrightarrow{\sim} d_{M_2 \otimes M_1}.$$
+$$\iota_{\beta_{M_1,M_2}} \colon F(\beta_{c_1,c_2})(d_{M_1 \otimes M_2}) \xrightarrow{\sim} d_{M_2 \otimes M_1}$$ where the vertical 1-morphisms are given by braidings in $(\mathsf{A},+,0)$.
 This braiding makes the following triangle of underlying cospans commute:
@@
 \]
-as well as the following diagram of corresponding decorations in the category $F(c_2+c_1)$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$F(\beta_{c_1,c_2})(d_{M_1 \otimes M_2})$};
-\node (B) at (2.25,1) {$F(\beta_{c_1,c_2})(d_{M_1 \otimes M_2}) $};
-\node (C) at (4.5,0) {$d_{M_2 \otimes M_1} $};
+as well as the following diagram of corresponding decorations in the category $F(c_1+c_2)$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$d_{M_1 \otimes M_2}$};
+\node (B) at (2.25,1) {$d_{M_1 \otimes M_2} $};
+\node (C) at (4.5,0) {$F(\beta_{c_2,c_1})(d_{M_2 \otimes M_1}) $};
 \path[->,font=\scriptsize,>=angle 90]
 (A) edge node[above]{$1$} (B)
-(C) edge node[right]{$F(\beta_{c_1,c_2})(\iota_{\beta_{M_2,M_1}})$} (B)
-(A) edge node[above]{$\iota_{\beta_{M_1,M_2}}$} (C);
-\end{tikzpicture}
-\]
-since $F(\beta_{c_1,c_2} \beta_{c_2,c_1}) (d_{M_2 \otimes M_1}) = d_{M_2 \otimes M_1}$. Thus $\mathbb{F} \textnormal{Cospan}(\mathrm{A})_1$ is also symmetric monoidal.
+(C) edge node[right]{$\iota_{\beta_{M_2,M_1}}$} (B)
+(A) edge node[above]{$F(\beta_{c_2,c_1})(\iota_{\beta_{M_1,M_2}})$} (C);
+\end{tikzpicture}
+\]
+since $F(\beta_{c_2,c_1} \beta_{c_1,c_2}) (d_{M_1 \otimes M_2}) = d_{M_1 \otimes M_2}$. Thus $F\mathbb{C}\textnormal{sp}_1$ is also symmetric monoidal.
 

### 2019-01-05 EquivCompFrameworks_20180911kc.tex
More polishing

@@
 \]
-where $\ell$ is the left unitor of $(\mathsf{A},+,0)$, together with the isomorphism $\iota_{\lambda} \colon F(\ell)(d_{0 \otimes M}) \to d_M$ which is specified by the isomorphism of categories $F(0+b) \cong F(b)$.
-The right unitor is similar.
+where $\ell$ is the left unitor of $(\mathsf{A},+,0)$, together with the isomorphism $\iota_{\lambda} \colon F(\ell)(d_{0 \otimes M}) \to d_M$. The right unitor is similar.
 
@@
 \node (A) at (0,0) {$a_1$};
-\node (B) at (1,0) {$c_1$};
-\node (C) at (2,0) {$b_1$};
-\node (D) at (1,-0.5) {$d_{M_1} \in F(c_1)$};
-\node (E) at (3,0) {$b_1$};
-\node (F) at (4,0) {$e_1$};
-\node (G) at (5,0) {$x_1$};
-\node (H) at (4,-0.5) {$d_{M_2} \in F(e_1)$};
-\node (I) at (0,-1.5) {$a_2$};
-\node (J) at (1,-1.5) {$c_2$};
-\node (K) at (2,-1.5) {$b_2$};
-\node (L) at (1,-2) {$d_{N_1} \in F(c_2)$};
-\node (M) at (3,-1.5) {$b_2$};
-\node (N) at (4,-1.5) {$e_2$};
-\node (O) at (5,-1.5) {$x_2$};
-\node (P) at (4,-2) {$d_{N_2} \in F(e_2)$};
+\node (B) at (1,0) {$b$};
+\node (C) at (2,0) {$a_2$};
+\node (D) at (1,-0.5) {$d_{M_1} \in F(b)$};
+\node (E) at (3,0) {$a_2$};
+\node (F) at (4,0) {$b'$};
+\node (G) at (5,0) {$a_3$};
+\node (H) at (4,-0.5) {$d_{M_2} \in F(b')$};
+\node (I) at (0,-1.5) {$a_1'$};
+\node (J) at (1,-1.5) {$c$};
+\node (K) at (2,-1.5) {$a_2'$};
+\node (L) at (1,-2) {$d_{N_1} \in F(c)$};
+\node (M) at (3,-1.5) {$a_2'$};
+\node (N) at (4,-1.5) {$c'$};
+\node (O) at (5,-1.5) {$a_3'$};
+\node (P) at (4,-2) {$d_{N_2} \in F(c')$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (C) edge node[above]{$o_1$} (B)
-(E) edge node[above]{$i_1^\prime$} (F)
-(G) edge node[above]{$o_1^\prime$} (F)
-(I) edge node[above]{$i_2$} (J)
-(K) edge node[above]{$o_2$} (J)
+(E) edge node[above]{$i_2$} (F)
+(G) edge node[above]{$o_2$} (F)
+(I) edge node[above]{$i_1^\prime$} (J)
+(K) edge node[above]{$o_1^\prime$} (J)
 (M) edge node[above]{$i_2^\prime$} (N)
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a_1+a_2$};
-\node (B) at (2.5,0) {$(c_1+c_2)+_{b_1+b_2}(e_1+e_2)$};
-\node (C) at (5,0) {$x_1+x_2$};
-\node (D) at (2.5,-0.5) {$d_{(M_1 \otimes N_1) \odot (M_2 \otimes N_2)} \in F((c_1+c_2)+_{b_1+b_2}(e_1+e_2))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$j \psi(i_1+i_2)$} (B)
-(C) edge node[above]{$j \psi(o_1^\prime + o_2^\prime)$} (B);
+\node (A) at (0,0) {$a_1+a_1'$};
+\node (B) at (2.5,0) {$(b+c)+_{a_2+a_2'}(b'+c')$};
+\node (C) at (5,0) {$a_3+a_3'$};
+\node (D) at (2.5,-0.5) {$d_{(M_1 \otimes N_1) \odot (M_2 \otimes N_2)} \in F((b+c)+_{a_2+a_2'}(b'+c'))$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$j \psi(i_1+i_1')$} (B)
+(C) edge node[above]{$j \psi(o_2 + o_2^\prime)$} (B);
+\end{tikzpicture}
+\]
+where the decoration $d_{(M_1 \otimes N_1) \odot (M_2 \otimes N_2)} \in F((b+c)+_{a_2+a_2'}(b'+c'))$ is given by:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$1$};
+\node (B) at (0,-1) {$1 \times 1$};
+\node (C) at (0,-2) {$(1 \times 1) \times (1 \times 1)$};
+\node (D) at (0,-3) {$(F(b) \times F(c)) \times (F(b') \times F(c'))$};
+\node (E) at (0,-4) {$F(b+c) \times F(b'+c')$};
+\node (F) at (0,-5) {$F((b+c)+(b'+c'))$};
+\node (G) at (0,-6) {$F((b+c)+_{a_2+a_2'}(b'+c'))$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[left]{$\lambda^{-1}$} (B)
+(B) edge node[left]{$\lambda^{-1} \times \lambda^{-1}$} (C)
+(C) edge node[left]{$(d_{M_1} \times d_{N_1}) \times (d_{M_2} \times d_{N_2})$} (D)
+(D) edge node[left]{$\phi_{b,c} \times \phi_{b',c'}$} (E)
+(E) edge node[left]{$\phi_{b+c,b'+c'}$} (F)
+(F) edge node[left]{$F(j_{b+c,b'+c'})$} (G);
 \end{tikzpicture}
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a_1+a_2$};
-\node (B) at (2.5,0) {$(c_1+_{b_1} e_1) + (c_2 +_{b_2} e_2)$};
-\node (C) at (5,0) {$x_1+x_2$};
-\node (D) at (2.5,-0.5) {$d_{(M_1 \odot M_2) \otimes (N_1 \odot N_2)} \in F((c_1+_{b_1}e_1)+(c_2+_{b_2}e_2))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$(j \psi i_2)+(j \psi i_1)$} (B)
-(C) edge node[above]{$(j \psi o_2^\prime)+(j \psi o_1^\prime)$} (B);
-\end{tikzpicture}
-\]
-where $\psi$ and $j$ are the natural maps into a coproduct and from a coproduct into a pushout, respectively.
+\node (A) at (0,0) {$a_1+a_1'$};
+\node (B) at (2.5,0) {$(b+_{a_2} c) + (b' +_{a_2'} c')$};
+\node (C) at (5,0) {$a_3+a_3'$};
+\node (D) at (2.5,-0.5) {$d_{(M_1 \odot M_2) \otimes (N_1 \odot N_2)} \in F((b+_{a_2}c)+(b'+_{a_2'}c'))$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$(j \psi i_1)+(j \psi i_1')$} (B)
+(C) edge node[above]{$(j \psi o_2)+(j \psi o_2^\prime)$} (B);
+\end{tikzpicture}
+\]
+where the decoration $d_{((M_1 \odot M_2) \otimes (N_1 \odot N_2))} \in F((b+_{a_2}c)+(b'+_{a_2'}c'))$ is given by:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$1$};
+\node (B) at (0,-1) {$1 \times 1$};
+\node (C) at (0,-2) {$(1 \times 1) \times (1 \times 1)$};
+\node (D) at (0,-3) {$(F(b) \times F(c)) \times (F(b') \times F(c'))$};
+\node (E) at (0,-4) {$F(b+c) \times F(b'+c')$};
+\node (F) at (0,-5) {$F(b+_{a_2}c) \times F(b'+_{a_2'}c')$};
+\node (G) at (0,-6) {$F((b+_{a_2}c)+(b'+_{a_2'}c'))$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[left]{$\lambda^{-1}$} (B)
+(B) edge node[left]{$\lambda^{-1} \times \lambda^{-1}$} (C)
+(C) edge node[left]{$(d_{M_1} \times d_{N_1}) \times (d_{M_2} \times d_{N_2})$} (D)
+(D) edge node[left]{$\phi_{b,c} \times \phi_{b',c'}$} (E)
+(E) edge node[left]{$F(j_{b,c}) \times F(j_{b',c'})$} (F)
+(F) edge node[left]{$\phi_{b+_{a_2}c,b'+_{a_2'}c'}$} (G);
+\end{tikzpicture}
+\]
+and where $\psi$ and $j$ are the natural maps into a coproduct and from a coproduct into a pushout, respectively.
 We then get a globular 2-morphism $$\chi \colon (M_1 \otimes N_1) \odot (M_2 \otimes N_2) \to (M_1 \odot M_2) \otimes (N_1 \odot N_2)$$ given by:
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$a_1+a_2$};
-\node (A') at (0,-0.5) {$a_1+a_2$};
-\node (B) at (2.5,0.5) {$(c_1+c_2)+_{b_1+b_2}(e_1+e_2)$};
-\node (C) at (5,0.5) {$b_1+b_2$};
-\node (C') at (5,-0.5) {$b_1+b_2$};
-\node (D) at (2.5,-0.5) {$(c_1+_{b_1}e_1)+(c_2+_{b_2}e_2)$};
-\node (E) at (2.5,1) {$\hat{d}_1 \in F((c_1+c_2)+_{b_1+b_2}(e_1+e_2))$};
-\node (F) at (2.5,-1) {$\hat{d}_2 \in F((c_1+_{b_1}e_1)+(c_2+_{b_2}e_2))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$j \psi (i_1+i_2)$} (B)
-(C) edge node[above]{$j \psi (o_1^\prime + o_2^\prime)$} (B)
+\node (A) at (0,0.5) {$a_1+a_1'$};
+\node (A') at (0,-0.5) {$a_1+a_1'$};
+\node (B) at (2.5,0.5) {$(b+c)+_{a_2+a_2'}(b'+c')$};
+\node (C) at (5,0.5) {$a_3+a_3'$};
+\node (C') at (5,-0.5) {$a_3+a_3'$};
+\node (D) at (2.5,-0.5) {$(b+_{a_2}c)+(b'+_{a_2'}c')$};
+\node (E) at (2.5,1) {$d_{(M_1 \otimes N_1) \odot (M_2 \otimes N_2)} \in F((b+c)+_{a_2+a_2'}(b'+c'))$};
+\node (F) at (2.5,-1) {$d_{(M_1 \odot M_2) \otimes (N_1 \odot N_2)} \in F((b+_{a_2}c)+(b'+_{a_2'}c'))$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$j \psi (i_1+i_1')$} (B)
+(C) edge node[above]{$j \psi (o_2 + o_2^\prime)$} (B)
 (A) edge node[left]{$1$} (A')
 (C) edge node[left]{$1$} (C')
-(A') edge node [above]{$(j \psi i_2)+(j \psi i_1)$} (D)
-(C') edge node [above]{$(j \psi o_2^\prime)+(j \psi o_1^\prime)$} (D)
+(A') edge node [above]{$(j \psi i_1')+(j \psi i_1)$} (D)
+(C') edge node [above]{$(j \psi o_2)+(j \psi o_2^\prime)$} (D)
 (B) edge node [left] {$\hat{\chi}$} (D);
@@
 \]
-$$\iota_{\hat{\chi}} \colon F(\hat{\chi})(d_{(M_1 \otimes N_1) \odot (M_2 \otimes N_2)}) \to d_{(M_1 \odot M_2) \otimes (N_1 \odot N_2)}.$$
+$$\iota_{\hat{\chi}} \colon F(\hat{\chi})(d_{(M_1 \otimes N_1) \odot (M_2 \otimes N_2)}) \to d_{(M_1 \odot M_2) \otimes (N_1 \odot N_2)}$$
+where $\hat{\chi}$ is the universal map between two colimits of the same diagram.
 For two objects $a,b \in \mathrm{A}$, $U_{a+b}$ is given by:
@@
 \]
-where $$!_{a+b} \colon 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{\phi \times \phi} F(0) \times F(0) \xrightarrow{F(!_a) \times F(!_b)} F(a) \times F(b) \xrightarrow{\phi_{a,b}} F(a+b).$$
+where $$!_{a+b} \colon 1 \xrightarrow{\phi} F(0) \xrightarrow{F(!_{a+b})}  F(a+b).$$
 Similarly, we have $U_a$ and $U_b$ given respectively by:
@@
 where
-$$!_a + !_b \colon 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{!_a \times !_b} F(a) \times F(b) \xrightarrow{\phi_{a,b}} F(a+b).$$
+$$!_a + !_b \colon 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{\phi \times \phi} F(0) \times F(0) \xrightarrow{F(!_a) \times F(!_b)} F(a) \times F(b) \xrightarrow{\phi_{a,b}} F(a+b).$$
 We then have another globular isomorphism $$\mu_{a,b} \colon U_{a+b} \to U_a + U_b$$ given by the identity 2-morphism:
@@
 \]
-$$\iota_{a,b} \colon !_{a+b} \xrightarrow{\sim} !_a + !_b.$$
+$$\iota_{a,b} \colon !_{a+b} \xrightarrow{\sim} !_a + !_b$$
+where $!_{a+b}$ and $!_a + !_b$ are both initial objects in $F(a+b)$, hence isomorphic.
 
@@
 (A) edge node[above]{$a \odot a$} (A')
-(A) edge node[left]{$\mu$} (B)
-(A') edge node[right]{$\mu$} (C)
-(B) edge node[left]{$\mu \otimes 1$} (C')
-(C) edge node [right] {$1 \otimes \mu$} (D)
+(A) edge node[left]{$\chi$} (B)
+(A') edge node[right]{$\chi$} (C)
+(B) edge node[left]{$\chi \otimes 1$} (C')
+(C) edge node [right] {$1 \otimes \chi$} (D)
 (C') edge node [above] {$a$} (D);
@@
 \]
-Here, $a$ is the associator of $\mathbb{F}\textnormal{Cospan}(\mathrm{A})_1$ and $\mu$ is the first globular isomorphism above.
+Here, $a$ is the associator of $F\mathbb{C}\textnormal{sp}_1$ and $\chi$ is the first globular isomorphism above.
 To see that this diagram does indeed commute, we first consider this diagram with respect to only the underlying cospans of each horizontal 1-cell.
@@
                                 (a2) edge node[above]{$$} (a3)
-                                (b2) edge node[left]{$\mu$} (b3)
+                                (b2) edge node[left]{$\chi$} (b3)
 (b2) edge node[right]{$\iota_2$} (b3)
@@
                                 (a3) edge node[above]{$$} (a4)
-                                (b3) edge node[left]{$1 \otimes \mu$} (b4)
+                                (b3) edge node[left]{$1 \otimes \chi$} (b4)
 (b3) edge node[right]{$\iota_3$} (b4)
@@
                                 (a) edge node[above]{$$} (a5)
-                                (b) edge node[left]{$\mu$} (b5)
+                                (b) edge node[left]{$\chi$} (b5)
 (b) edge node[right]{$\iota_4$} (b5)
@@
                                 (a5) edge node[above]{$$} (a6)
-                                (b5) edge node[left]{$\mu \otimes 1$} (b6)
+                                (b5) edge node[left]{$\chi \otimes 1$} (b6)
  (b5) edge node[right]{$\iota_5$} (b6)
@@
 The above diagram of maps of cospans can then be visualized as a hexagonal prism in which all the faces commute by identifying the top and the bottom as the same.
-As for the decorations, each isomorphism $\iota_n$ goes from the domain under the image of the functor $F$ applied to natural isomorphism adjacent to it to the codomain as written, meaning that, for example: $$\iota_1 \colon F(a \odot a)(d_{((M_1 \otimes N_1) \otimes P_1) \odot ((M_2 \otimes N_2) \otimes P_2)}) \to d_{(M_1 \otimes (N_1 \otimes P_1)) \odot (M_2 \otimes (N_2 \otimes P_2))}.$$  The following diagram commutes in the category $F((l+_m n) + ((r+_s t) + (w+_x y)))$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$F( a (\mu \otimes 1)\mu)(d_{((M_1 \otimes N_1) \otimes P_1) \odot ((M_2 \otimes N_2) \otimes P_2)})$};
-\node (A') at (4.5,0.5) {$F((1 \otimes \mu) \mu)(d_{(M_1 \otimes (N_1 \otimes P_1)) \odot (M_2 \otimes (N_2 \otimes P_2))})$};
-\node (B) at (0,-0.5) {$F(a(\mu  \otimes 1))(d_{((M_1 \otimes N_1) \odot (M_2 \otimes N_2)) \otimes (P_1 \odot P_2)})$};
-\node (C) at (4.5,-0.5) {$F(1 \otimes \mu)(d_{(M_1 \odot M_2) \otimes ((N_1 \otimes P_1) \odot (N_2 \otimes P_2))})$};
+As for the morphisms of decorations, each isomorphism $\iota_n$ goes from the domain under the image of the functor $F$ applied to natural isomorphism adjacent to it to the codomain as written, meaning that, for example: $$\iota_1 \colon F(a \odot a)(d_{((M_1 \otimes N_1) \otimes P_1) \odot ((M_2 \otimes N_2) \otimes P_2)}) \to d_{(M_1 \otimes (N_1 \otimes P_1)) \odot (M_2 \otimes (N_2 \otimes P_2))}.$$  The following diagram commutes in the category $F((l+_m n) + ((r+_s t) + (w+_x y)))$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0.5) {$F( a (\chi \otimes 1)\chi)(d_{((M_1 \otimes N_1) \otimes P_1) \odot ((M_2 \otimes N_2) \otimes P_2)})$};
+\node (A') at (4.5,0.5) {$F((1 \otimes \chi) \chi)(d_{(M_1 \otimes (N_1 \otimes P_1)) \odot (M_2 \otimes (N_2 \otimes P_2))})$};
+\node (B) at (0,-0.5) {$F(a(\chi  \otimes 1))(d_{((M_1 \otimes N_1) \odot (M_2 \otimes N_2)) \otimes (P_1 \odot P_2)})$};
+\node (C) at (4.5,-0.5) {$F(1 \otimes \chi)(d_{(M_1 \odot M_2) \otimes ((N_1 \otimes P_1) \odot (N_2 \otimes P_2))})$};
 \node (C') at (0,-1.5) {$F(a)(d_{((M_1 \odot M_2) \otimes (N_1 \odot N_2)) \otimes (P_1 \odot P_2)})$};
@@
 \path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$F((1 \otimes \mu) \mu)(\iota_1)$} (A')
-(A) edge node[left]{$F(a(\mu \otimes 1))(\iota_4)$} (B)
-(A') edge node[right]{$F(1 \otimes \mu)(\iota_2)$} (C)
+(A) edge node[above]{$F((1 \otimes \chi) \chi)(\iota_1)$} (A')
+(A) edge node[left]{$F(a(\chi \otimes 1))(\iota_4)$} (B)
+(A') edge node[right]{$F(1 \otimes \chi)(\iota_2)$} (C)
 (B) edge node[left]{$F(a)(\iota_5)$} (C')
@@
 \]
-since $$F(a(\mu \otimes 1)\mu)(d_{((M_1 \otimes N_1) \otimes P_1) \odot ((M_2 \otimes N_2) \otimes P_2)}) = F((1 \otimes \mu) \mu (a \odot a))(d_{((M_1 \otimes N_1) \otimes P_1) \odot ((M_2 \otimes N_2) \otimes P_2)})$$
+since $$F(a(\chi \otimes 1)\chi)(d_{((M_1 \otimes N_1) \otimes P_1) \odot ((M_2 \otimes N_2) \otimes P_2)}) = F((1 \otimes \chi) \chi (a \odot a))(d_{((M_1 \otimes N_1) \otimes P_1) \odot ((M_2 \otimes N_2) \otimes P_2)})$$
 as the above underlying diagram of maps of cospans commutes.
 
-Another requirement for a double category to be symmetric monoidal is that the braiding $$\beta_{ ( \_, \_ ) } \colon \mathbb{F}\textnormal{Cospan}(\mathrm{A})_1 \times \mathbb{F}\textnormal{Cospan}(\mathrm{A})_1 \to \mathbb{F}\textnormal{Cospan}(\mathrm{A})_1 \times \mathbb{F}\textnormal{Cospan}(\mathrm{A})_1$$ be a transformation of double categories, and one of the diagrams that is required to commute is the following:
+Another requirement for a double category to be symmetric monoidal is that the braiding $$\beta_{ ( \_, \_ ) } \colon F\mathbb{C}\textnormal{sp}_1 \times F\mathbb{C}\textnormal{sp}_1 \to F\mathbb{C}\textnormal{sp}_1 \times F\mathbb{C}\textnormal{sp}_1$$ be a transformation of double categories, and one of the diagrams that is required to commute is the following:
 \[
@@
 (A) edge node[above]{$\beta$} (B)
-(B) edge node[right]{$\mu$} (D)
-(A) edge node[left]{$\mu$} (C)
+(B) edge node[right]{$\chi$} (D)
+(A) edge node[left]{$\chi$} (C)
 (C) edge node[above]{$\beta \odot \beta$} (D);
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$F(\mu \beta)(d_{(M_1 \odot M_2) \otimes (N_1 \odot N_2)})$};
-\node (B) at (3,0) {$F(\mu)(d_{(N_1 \odot N_2) \otimes (M_1 \odot M_2)})$};
+\node (A) at (0,0) {$F(\chi \beta)(d_{(M_1 \odot M_2) \otimes (N_1 \odot N_2)})$};
+\node (B) at (3,0) {$F(\chi)(d_{(N_1 \odot N_2) \otimes (M_1 \odot M_2)})$};
 \node (C) at (0,-1) {$F(\beta \odot \beta)(d_{(M_1 \otimes N_1) \odot (M_2 \otimes N_2)})$};
@@
 \path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$F(\mu)(\iota_1)$} (B)
+(A) edge node[above]{$F(\chi)(\iota_1)$} (B)
 (B) edge node[right]{$\iota_2$} (D)
@@
 \]
-since $$F(\mu \beta)(d_{(M_1 \odot M_2) \otimes (N_1 \odot N_2)}) = F((\beta \odot \beta)\mu)(d_{(M_1 \odot M_2) \otimes (N_1 \odot N_2)})$$
+since $$F(\chi \beta)(d_{(M_1 \odot M_2) \otimes (N_1 \odot N_2)}) = F((\beta \odot \beta)\chi)(d_{(M_1 \odot M_2) \otimes (N_1 \odot N_2)})$$
 as the above underlying diagram of maps of cospans commutes. The other diagrams are shown to commute similarly.

### 2019-01-06 EquivCompFrameworks_20180911kc.tex
Changing some notation/cleaning stuff up

@@
 \begin{thm}\label{Equiv}
-Let $\mathrm{A}$ and $\mathrm{X}$ be categories with finite colimits and $F \colon \mathrm{A} \to \mathbf{Cat}$ a symmetric lax monoidal pseudofunctor.
-Let $L \colon \mathrm{A} \to \int{F} \cong \mathrm{X}$ be the left adjoint of the Grothendieck construction $R \colon \int{F} \to \mathrm{A}$ of $F$.
-Then the symmetric monoidal double category $_L \mathbb{C}\textnormal{sp}(\mathrm{X})$ utilizing structured cospans and the symmetric monoidal double category $\mathbb{F}\textnormal{Cospan}(\mathrm{A})$ utilizing decorated cospans are equivalent as symmetric monoidal double categories.
+Let $\mathsf{A}$ and $\mathsf{X}$ be categories with finite colimits and $F \colon \mathsf{A} \to \mathbf{Cat}$ a symmetric lax monoidal pseudofunctor.
+Let $L \colon \mathsf{A} \to \int{F} \cong \mathsf{X}$ be the left adjoint of the Grothendieck construction $R \colon \int{F} \to \mathsf{A}$ of $F$.
+Then the symmetric monoidal double category $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$ utilizing structured cospans and the symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$ utilizing decorated cospans are equivalent as symmetric monoidal double categories.
 \end{thm}
 \begin{proof}
-To prove this, we define a double functor $\mathbb{E} \colon _L \mathbb{C}\textnormal{sp}(\mathrm{X}) \to \mathbb{F}\textnormal{Cospan}(\mathrm{A})$ as follows: the object component of the double functor $\mathbb{E}$ is given by $\mathbb{E}_0 = \id_{\mathrm{A}}$ as both double categories $_L \mathbb{C}\textnormal{sp}(\mathrm{X})$ and $\mathbb{F}\textnormal{Cospan}(\mathrm{A})$ have objects and morphisms of $\mathrm{A}$ as objects and vertical 1-morphisms, respectively.
+To prove this, we define a double functor $\mathbb{E} \colon _L \mathbb{C}\textnormal{sp}(\mathsf{X}) \to F\mathbb{C}\textnormal{sp}$ as follows: the object component of the double functor $\mathbb{E}$ is given by $\mathbb{E}_0 = \id_{\mathsf{A}}$ as both double categories $_L \mathbb{C}\textnormal{sp}(\mathrm{X})$ and $F\mathbb{C}\textnormal{sp}$ have objects and morphisms of $\mathsf{A}$ as objects and vertical 1-morphisms, respectively.
 The functor $\mathbb{E}_0$ is trivially an equivalence of categories.
 
-Given a horizontal 1-cell of $_L \mathbb{C}\textnormal{sp}(\mathrm{X})$, which is a cospan in $\mathrm{X}$ of the form:
+Given a horizontal 1-cell $M$ of $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$, which is a cospan in $\mathsf{X}$ of the form:
 \[
@@
 \]
-the image of this horizontal 1-cell under the arrow component $\mathbb{E}_1$ is the pair:
+the image $\mathbb{E}_1(M)$ is given by the pair:
 \[
@@
 \]
-where $R\colon \mathrm{X} \to \mathrm{A}$ is the right adjoint to the functor $L \colon \mathrm{A} \to \mathrm{X}$ and $\eta \colon 1_{\mathrm{A}} \to RL$ is the unit of the adjunction $L \dashv R$ which is an isomorphism since $L$ is fully faithful.
-\textbf{Hopefully...actually, it's a `lari'!} Similarly, the image of a 2-morphism in $_L \mathbb{C}\textnormal{sp}(\mathrm{X})$:
+where $R\colon \mathsf{X} \to \mathsf{A}$ is the right adjoint to the functor $L \colon \mathsf{A} \to \mathsf{X}$ and $\eta \colon 1_{\mathsf{A}} \to RL$ is the unit of the adjunction $L \dashv R$ which is an isomorphism since $L$ is fully faithful.
+\textbf{Hopefully...actually, it's a `lari'!} Similarly, the image of a 2-morphism $\alpha \colon M \to N$ in $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$:
 \[
@@
 \]
-is the 2-morphism in $\mathbb{F}\textnormal{Cospan}(\mathrm{A})$ given by:
+is given by the 2-morphism $\mathbb{E}_1(\alpha) \colon \mathbb{E}_1(M) \to \mathbb{E}_1(N)$ in $\mathbb{F}\textnormal{Cospan}(\mathsf{A})$ given by:
 \[
@@
 \]
-together with a morphism $\iota \colon F(R(h))(x) \to x^\prime$ in $F(R(x^\prime)) \subseteq \mathrm{X}$ which comes from the Grothendieck construction of the pseudofunctor $F \colon \mathrm{A} \to \mathbf{Cat}$.
-First, to see that this functor is essentially surjective, given a horizontal 1-cell in $\mathbb{F}\textnormal{Cospan}(\mathrm{A})$:
+together with a morphism $\iota \colon F(R(\alpha))(x) \to x^\prime$ in $F(R(x^\prime)) \subseteq \mathrm{X}$ which comes from the Grothendieck construction of the pseudofunctor $F \colon \mathsf{A} \to \mathbf{Cat}$.
+First, to see that this functor is essentially surjective, given a horizontal 1-cell in $F\mathbb{C}\textnormal{sp}$:
 \[
@@
 \]
-we can find a 2-isomorphism in $\mathbb{F}\textnormal{Cospan}(\mathrm{A})$ whose codomain is the above horizontal 1-cell and whose domain is the image of the following horizontal 1-cell in $_L \mathbb{C}\textnormal{sp}(\mathbf{D})$:
+we can find a 2-isomorphism in $F\mathbb{C}\textnormal{sp}$ whose codomain is the above horizontal 1-cell and whose domain is the image of the following horizontal 1-cell in $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$:
 \[
@@
 \]
-with the 2-isomorphism in $\mathbb{F}\textnormal{Cospan}(\mathrm{A})$ given by:
+with the 2-isomorphism in $F\mathbb{C}\textnormal{sp}$ given by:
 \[
@@
 
-To show that the double functor $\mathbb{E}$ is fully faithful, we need to show that the map  $$\mathbb{E}_1 \colon _f { _L \mathbb{C}\textnormal{sp}(\mathrm{X})}_g(M,N) \to _{\mathbb{E}(f)} {\mathbb{F}\textnormal{Cospan}(\mathrm{A})}_{\mathbb{E}(g)}(\mathbb{E}(M),\mathbb{E}(N))$$ is bijective for arbitrary vertical 1-morphisms $f$ and $g$ and horizontal 1-cells $M$ and $N$ of $_L \mathbb{C}\textnormal{sp}(\mathbf{D})$.
-Consider a 2-morphism in $_L \mathbb{C}\textnormal{sp}(\mathrm{X})$:
+To show that the double functor $\mathbb{E}$ is fully faithful, we need to show that the map  $$\mathbb{E}_1 \colon _f { _L \mathbb{C}\textnormal{sp}(\mathsf{X})}_g(M,N) \to _{\mathbb{E}(f)} {F\mathbb{C}\textnormal{sp}}_{\mathbb{E}(g)}(\mathbb{E}(M),\mathbb{E}(N))$$ is bijective for arbitrary vertical 1-morphisms $f$ and $g$ and horizontal 1-cells $M$ and $N$ of $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$.
+Consider a 2-morphism in $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$:
 \[
@@
 \]
-The set $$_f { _L \mathbb{C}\textnormal{sp}(\mathrm{X})}_g(M,N)$$ consists of triples $$(f,\alpha,g)$$ where $f$ and $g$ are morphisms of $\mathrm{A}$ and $\alpha$ is a morphism of $\mathrm{X}$.
+Thus the set $$_f { _L \mathbb{C}\textnormal{sp}(\mathsf{X})}_g(M,N)$$ consists of triples $$(f,\alpha,g)$$ rendering the above diagram commutative where $f$ and $g$ are morphisms of $\mathsf{A}$ and $\alpha$ is a morphism of $\mathsf{X}$.
 The image of the above 2-morphism under the double functor $\mathbb{E}$ is given by:
@@
 together with a morphism $\iota \colon F(R(\alpha))(x) \to x^\prime$ of $F(R(x^\prime))$.
-Thus the set $$_{\mathbb{E}(f)} {\mathbb{F}\textnormal{Cospan}(\mathrm{A})}_{\mathbb{E}(g)}(\mathbb{E}(M),\mathbb{E}(N))$$ consists of 4-tuples $$(f,R(\alpha),g,\iota).$$ The morphisms $R(\alpha) \colon R(x) \to R(x^\prime)$ and $\iota \colon F(R(\alpha))(x) \to x^\prime$ together carry all of the information of the morphism $\alpha \colon x \to x^\prime$ in $\mathrm{X}$ and conversely; given two objects $x=(c,x \in F(c))$ and $x^\prime=(c^\prime,x^\prime \in F(c^\prime))$ of $\mathrm{X}=\int{F}$, a morphism from $\alpha \colon x \to x^\prime$ is a pair $$(h \colon c \to c^\prime, \iota \colon F(h)(x) \to x^\prime)$$ where $h \colon c \to c^\prime$ is given by $R(\alpha) \colon R(x) \to R(x^\prime)$.
+Thus the set $$_{\mathbb{E}(f)} {F\mathbb{C}\textnormal{sp}}_{\mathbb{E}(g)}(\mathbb{E}(M),\mathbb{E}(N))$$ consists of 4-tuples $$(f,R(\alpha),g,\iota)$$ rendering the above diagram commutative and where $f,g$ and $R(\alpha)$ are morphisms of $\mathsf{A}$ and $\iota$ is a morphism in $F(R(x'))$.
+The morphisms $R(\alpha) \colon R(x) \to R(x^\prime)$ and $\iota \colon F(R(\alpha))(x) \to x^\prime$ together determine the morphism $\alpha \colon x \to x^\prime$ in $\mathrm{X}$ and conversely; given two objects $x=(c,x \in F(c))$ and $x^\prime=(c^\prime,x^\prime \in F(c^\prime))$ of $\mathsf{X}=\int{F}$, a morphism from $\alpha \colon x \to x^\prime$ is a pair $$(h \colon c \to c^\prime, \iota \colon F(h)(x) \to x^\prime)$$ where $h \colon c \to c^\prime$ is given by $R(\alpha) \colon R(x) \to R(x^\prime)$.
 This shows that $\mathbb{E}$ is fully faithful.
@@
 
-Next we show that the double functor $\mathbb{E}$ is strong by exhibiting natural isomorphisms $$\mathbb{E}_{M,N} \colon \mathbb{E}(M) \odot \mathbb{E}(N) \xrightarrow{\sim} \mathbb{E}(M \odot N)$$ for every pair of composable horizontal 1-cells $M$ and $N$ of $_L \mathbb{C}\textnormal{sp}(\mathrm{X})$ and for each object $c \in { _L \mathbb{C}\textnormal{sp}(\mathrm{X})}$ a natural isomorphism $$\mathbb{E}_c \colon \hat{U}_{\mathbb{E}(c)} \xrightarrow{\sim} \mathbb{E}(U_c)$$ where $U$ and $\hat{U}$ are the unit structure functors of $_L \mathbb{C} \textnormal{sp}(\mathrm{X})$ and $\mathbb{F}\textnormal{Cospan}(\mathrm{A})$, respectively.
+Next we show that the double functor $\mathbb{E}$ is strong by exhibiting a natural isomorphism $$\mathbb{E}_{M,N} \colon \mathbb{E}(M) \odot \mathbb{E}(N) \xrightarrow{\sim} \mathbb{E}(M \odot N)$$ for every pair of composable horizontal 1-cells $M$ and $N$ of $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$ and for each object $c \in { _L \mathbb{C}\textnormal{sp}(\mathsf{X})}$ a natural isomorphism $$\mathbb{E}_c \colon \hat{U}_{\mathbb{E}(c)} \xrightarrow{\sim} \mathbb{E}(U_c)$$ where $U$ and $\hat{U}$ are the unit structure functors of $_L \mathbb{C} \textnormal{sp}(\mathsf{X})$ and $F\mathbb{C}\textnormal{sp}$, respectively.
 For any object $c$, the horizontal 1-cell $\hat{U}_{\mathbb{E}(c)}$ is given by $\hat{U}_c$ which is given by the pair:
@@
 \]
-Then we can obtain the natural isomorphism $\mathbb{E}_c$ as the 2-morphism
+Then we can obtain the natural isomorphism $\mathbb{E}_c \colon \hat{U}_{\mathbb{E}(c)} \xrightarrow{\sim} \mathbb{E}(U_c)$ as the 2-morphism
 \[
@@
 \node (D) at (3,0) {$!_c \in F(c)$};
-\node (D') at (3.25,-1) {$!_c \in F(R(L(c)))$};
+\node (D') at (3.25,-1) {$!_{R(L(c))} \in F(R(L(c)))$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-$$\iota \colon F(\eta_c)(!_c) \xrightarrow{!} L(c)$$
-of $\mathbb{F}\textnormal{Cospan}(\mathrm{A})$. Seems reasonable...
-
-Next, given composable horizontal 1-cells $M$ and $N$ in $_L \mathbb{C}\textnormal{sp}(\mathrm{X})$:
+$$\iota \colon F(\eta_c)(!_c) \xrightarrow{!} !_{R(L(c))}$$
+of $F\mathbb{C}\textnormal{sp}$.
+
+Next, given composable horizontal 1-cells $M$ and $N$ in $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$:
 \[
@@
 \]
-where $\zeta$ is each inclusion into the coproduct and $J$ is the natural map from the coproduct to the pushout. Then $E(M \odot N)$ is given by
+where $\zeta$ is a natural map into a coproduct and $J$ is the natural map from the coproduct to the pushout. Then $E(M \odot N)$ is given by
 \[
@@
 \]
-First, if the right adjoint $R \colon \mathrm{X} \to \mathrm{A}$ is also a left adjoint, then $R$ also preserves all colimits and we have an isomorphism $$\kappa \colon R(x) +_{R(L(c_2))} R(x^\prime) \to R(x+_{L(c_2)}x^\prime).$$ Also, since the left adjoint $L \colon \mathrm{A} \to \mathrm{X}$ is fully faithful, the unit of the adjunction $L \dashv R$ at the object $c_2$ gives an isomorphism $\eta_{c_2} \colon c_2 \to R(L(c_2))$ which results in an isomorphism $$j_{\eta_{c_2}} \colon R(x) +_{c_2} R(x^\prime) \to R(x) +_{R(L(c_2))} R(x^\prime).$$ Composing these two results in an isomorphism $$\sigma \coloneqq \kappa j_{\eta_{c_2}} \colon R(x) +_{c_2} R(x^\prime) \to R(x+_{L(c_2)}x^\prime).$$
-Next, to see that the above diagram commutes, it suffices to show that for the object $c_1 \in \mathrm{A}$, $$R(J \zeta i)\eta_{c_1}(c_1) = R(J)R(\zeta)R(i)\eta_{c_1}(c_1) \stackrel{!}{=} \sigma j \psi R(i)\eta_{c_1}(c_1).$$ This follows as $R(i) \eta_{c_1} \colon c_1 \to R(x)$ and the following diagram commutes:
+First, if the right adjoint $R \colon \mathsf{X} \to \mathsf{A}$ is also a left adjoint, then $R$ also preserves all colimits and we have an isomorphism $$\kappa \colon R(x) +_{R(L(c_2))} R(x^\prime) \to R(x+_{L(c_2)}x^\prime).$$ Also, since the left adjoint $L \colon \mathsf{A} \to \mathsf{X}$ is fully faithful, the unit of the adjunction $L \dashv R$ at the object $c_2$ gives an isomorphism $\eta_{c_2} \colon c_2 \to R(L(c_2))$ which results in an isomorphism $$j_{\eta_{c_2}} \colon R(x) +_{c_2} R(x^\prime) \to R(x) +_{R(L(c_2))} R(x^\prime).$$ Composing these two results in an isomorphism $$\sigma \coloneqq \kappa j_{\eta_{c_2}} \colon R(x) +_{c_2} R(x^\prime) \to R(x+_{L(c_2)}x^\prime).$$
+Next, to see that the above diagram commutes, it suffices to show that for the object $c_1 \in \mathrm{A}$, $$R(J)R(\zeta)R(i)\eta_{c_1}(c_1) = R(J \zeta i)\eta_{c_1}(c_1)  \stackrel{!}{=} \sigma j \psi R(i)\eta_{c_1}(c_1) = \kappa j_{\eta_{c_2}} \psi R(i) \eta_{c_1}(c_1).$$ This follows as $R(i) \eta_{c_1} \colon c_1 \to R(x)$ and the following diagram commutes:
 \[
@@
 Lastly, this map of cospans comes with an isomorphism $\iota \colon F(\sigma)(\hat{x}) \to (x+_{L(c_2)}x^\prime)$ in $F(R(x+_{L(c_2)}x^\prime))$.
-This shows that $\mathbb{E}$ is strong, and so $\mathbb{E} \colon _L \mathbb{C}\textnormal{sp}(\mathrm{X}) \xrightarrow{\sim} \mathbb{F}\textnormal{Cospan}(\mathrm{A})$ is part of a double equivalence by Theorem \ref{ShulDubEquiv}.
-
-Next, if both double categories $_L \mathbb{C}\textnormal{sp}(\mathrm{X})$ and $\mathbb{F}\textnormal{Cospan}(\mathrm{A})$ are symmetric monoidal, as they are if both $\mathrm{A}$ and $\mathrm{X}$ have finite colimits, then this equivalence of double categories $\mathbb{E} \colon _L \mathbb{C}\textnormal{sp}(\mathrm{X}) \to \mathbb{F} \textnormal{Cospan}(\mathrm{A})$ will be symmetric monoidal.
-First note that we have an isomorphism $\epsilon \colon 1_{\mathbb{F}\textnormal{Cospan}(\mathrm{A})} \to \mathbb{E}(1_{_L \mathbb{C}\textnormal{sp}(\mathrm{X})})$ and natural isomorphisms $\mu_{c_1,c_2} \colon \mathbb{E}(c_1) \otimes \mathbb{E}(c_2) \to \mathbb{E}(c_1 \otimes c_2)$ for every pair of objects $c_1,c_2 \in {_L \mathbb{C} \textnormal{sp}(\mathrm{X})}$ both of which are given by identities since both double categories $_L \mathbb{C}\textnormal{sp}(\mathrm{X})$ and $\mathbb{F}\textnormal{Cospan}(\mathrm{A})$ have $\mathrm{A}$ as their category of objects and $\mathbb{E}_0=\id_{\mathrm{A}}$.
-The diagrams containing these morphisms that are required to commute do so trivially.
-
-For the arrow component $\mathbb{E}_1$, we have an isomorphism $\delta \colon U_{1_{\mathbb{F}\textnormal{Cospan}(\mathrm{A})}} \to \mathbb{E}(U_{1_{_L \mathbb{C}\textnormal{sp}(\mathrm{X})}})$ where the horizontal 1-cell $U_{1_{\mathbb{F}\textnormal{Cospan}(\mathrm{A})}}$ is given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$1_\mathrm{A}$};
-\node (B) at (1,0) {$1_\mathrm{A}$};
-\node (C) at (2,0) {$1_\mathrm{A}$};
-\node (D) at (3,0) {$!_{1_{\mathrm{A}}} \in F(1_\mathrm{A})$};
+This shows that $\mathbb{E}$ is strong, and so $\mathbb{E} \colon _L \mathbb{C}\textnormal{sp}(\mathsf{X}) \xrightarrow{\sim} F\mathbb{C}\textnormal{sp}$ is part of a double equivalence by Theorem \ref{ShulDubEquiv}.
+
+Next, if both double categories $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$ and $F\mathbb{C}\textnormal{sp}$ are symmetric monoidal, as they are if both $\mathsf{A}$ and $\mathsf{X}$ have finite colimits, then this equivalence of double categories $\mathbb{E} \colon _L \mathbb{C}\textnormal{sp}(\mathsf{X}) \to F\mathbb{C}\textnormal{sp}$ will be symmetric monoidal.
+First, note that we have an isomorphism $\epsilon \colon 1_{F\mathbb{C}\textnormal{sp}} \to \mathbb{E}(1_{_L \mathbb{C}\textnormal{sp}(\mathsf{X})})$ and natural isomorphisms $\mu_{c_1,c_2} \colon \mathbb{E}(c_1) \otimes \mathbb{E}(c_2) \to \mathbb{E}(c_1 \otimes c_2)$ for every pair of objects $c_1,c_2 \in {_L \mathbb{C} \textnormal{sp}(\mathsf{X})}$ both of which are given by identities since both double categories $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$ and $F\mathbb{C}\textnormal{sp}$ have $\mathsf{A}$ as their category of objects and $\mathbb{E}_0=\id_{\mathsf{A}}$.
+The diagrams utilizing these maps that are required to commute do so trivially.
+
+For the arrow component $\mathbb{E}_1$, we have an isomorphism $\delta \colon U_{1_{F\mathbb{C}\textnormal{sp}}} \to \mathbb{E}(U_{1_{_L \mathbb{C}\textnormal{sp}(\mathsf{X})}})$ where the horizontal 1-cell $U_{1_{F\mathbb{C}\textnormal{sp}}}$ is given by:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$1_\mathsf{A}$};
+\node (B) at (1,0) {$1_\mathsf{A}$};
+\node (C) at (2,0) {$1_\mathsf{A}$};
+\node (D) at (3,0) {$!_{1_{\mathsf{A}}} \in F(1_\mathsf{A})$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-where $!_{1_{\mathrm{A}}} = \phi \colon 1 \to F(1_\mathrm{A})$ is the trivial decoration which comes from the structure of the symmetric lax monoidal pseudofunctor $F \colon \mathrm{A} \to \mathbf{Cat}$.
-The horizontal 1-cell $U_{1_{_L \mathbb{C}\textnormal{sp}(\mathrm{X})}}$ is given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$L(1_\mathrm{A})$};
-\node (B) at (1,0) {$L(1_\mathrm{A})$};
-\node (C) at (2,0) {$L(1_\mathrm{A})$};
+where $!_{1_{\mathsf{A}}} = \phi \colon 1 \to F(1_\mathsf{A})$ is the trivial decoration which comes from the structure of the symmetric lax monoidal pseudofunctor $F \colon \mathsf{A} \to \mathbf{Cat}$.
+The horizontal 1-cell $U_{1_{_L \mathbb{C}\textnormal{sp}(\mathsf{X})}}$ is given by:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$L(1_\mathsf{A})$};
+\node (B) at (1,0) {$L(1_\mathsf{A})$};
+\node (C) at (2,0) {$L(1_\mathsf{A})$};
 %\node (D) at (3,0.5) {$I \in F(1_\mathrm{A})$};
@@
 \]
-where here we make use of the fact that the left adjoint $L \colon (\mathrm{A},+,1_\mathrm{A}) \to (\mathrm{X},+,1_\mathrm{X})$ preserves all colimits and thus $L(1_\mathrm{A}) \cong 1_\mathrm{X}$.
-The horizontal 1-cell $\mathbb{E}(U_{1_{_L \mathbb{C} \textnormal{sp}(\mathrm{X})}})$ is given by the pair:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$1_\mathrm{A}$};
-\node (B) at (1.25,0) {$R(L(1_\mathrm{A}))$};
-\node (C) at (2.5,0) {$1_\mathrm{A}$};
-\node (D) at (4,0) {$!_{1_\mathrm{A}} \in F(R(L(1_\mathrm{A}))) \cong F(1_\mathrm{A})$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{${\eta_{1_\mathrm{A}}}$} (B)
-(C) edge node[above]{${\eta_{1_\mathrm{A}}}$} (B);
+where here we make use of the fact that the left adjoint $L \colon (\mathsf{A},+,1_\mathsf{A}) \to (\mathsf{X},+,1_\mathsf{X})$ preserves all colimits and thus $L(1_\mathsf{A}) \cong 1_\mathsf{X}$.
+The horizontal 1-cell $\mathbb{E}(U_{1_{_L \mathbb{C} \textnormal{sp}(\mathsf{X})}})$ is then given by the pair:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$1_\mathsf{A}$};
+\node (B) at (1.25,0) {$R(L(1_\mathsf{A}))$};
+\node (C) at (2.5,0) {$1_\mathsf{A}$};
+\node (D) at (4.5,0) {$!_{R(L(1_\mathsf{A}))} \in F(R(L(1_\mathsf{A})))$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{${\eta_{1_\mathsf{A}}}$} (B)
+(C) edge node[above]{${\eta_{1_\mathsf{A}}}$} (B);
 \end{tikzpicture}
@@
 $$\iota_{{\eta_{1_\mathrm{A}}}} \colon F({\eta_{1_\mathrm{A}}}(!_{1_\mathrm{A}})) \to !_{1_\mathrm{A}}$$
-of $\mathbb{F}\textnormal{Cospan}(\mathrm{A})$.
+of $\mathbb{F}\textnormal{Cospan}(\mathrm{A})$. This is just the natural isomorphism $\mathbb{E}_{1_\mathsf{A}}$ from earlier.
 

### 2019-01-07 EquivCompFrameworks_20180911kc.tex
More cleaning up

@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$1_\mathrm{A}$};
-\node (B) at (1,0) {$1_{\mathrm{A}}$};
-\node (C) at (2,0) {$1_\mathrm{A}$};
-\node (A') at (0,-1) {$1_\mathrm{A}$};
-\node (B') at (1,-1) {$R(L(1_\mathrm{A}))$};
-\node (C') at (2,-1) {$1_\mathrm{A}$};
-\node (D) at (3,0) {$!_{1_\mathrm{A}} \in F(1_\mathrm{A})$};
-\node (D') at (3.75,-1) {$!_{1_\mathrm{A}} \in F(R(L(1_\mathrm{A}))) \cong F(1_\mathrm{A})$};
+\node (A) at (0,0) {$1_\mathsf{A}$};
+\node (B) at (1,0) {$1_{\mathsf{A}}$};
+\node (C) at (2,0) {$1_\mathsf{A}$};
+\node (A') at (0,-1) {$1_\mathsf{A}$};
+\node (B') at (1,-1) {$R(L(1_\mathsf{A}))$};
+\node (C') at (2,-1) {$1_\mathsf{A}$};
+\node (D) at (3,0) {$!_{1_\mathsf{A}} \in F(1_\mathsf{A})$};
+\node (D') at (3.75,-1) {$!_{R(L(1_\mathsf{A}))} \in F(R(L(1_\mathsf{A})))$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (C) edge node[above]{$1$} (B)
-(A') edge node[above]{${\eta_{1_\mathrm{A}}}$} (B')
-(C') edge node[above]{${\eta_{1_\mathrm{A}}}$} (B')
+(A') edge node[above]{${\eta_{1_\mathsf{A}}}$} (B')
+(C') edge node[above]{${\eta_{1_\mathsf{A}}}$} (B')
 (A) edge node [left]{$1$} (A')
-(B) edge node [left]{${\eta_{1_\mathrm{A}}}$} (B')
+(B) edge node [left]{${\eta_{1_\mathsf{A}}}$} (B')
 (C) edge node [left]{$1$} (C');
@@
 \]
-$$\iota_{{\eta_{1_\mathrm{A}}}} \colon F({\eta_{1_\mathrm{A}}}(!_{1_\mathrm{A}})) \to !_{1_\mathrm{A}}$$
-of $\mathbb{F}\textnormal{Cospan}(\mathrm{A})$. This is just the natural isomorphism $\mathbb{E}_{1_\mathsf{A}}$ from earlier.
-
-Given two horizontal 1-cells $M$ and $N$ of $_L \mathbb{C}\textnormal{sp}(\mathrm{X})$:
+$$\iota_{{\eta_{1_\mathsf{A}}}} \colon F({\eta_{1_\mathsf{A}}})(!_{1_\mathsf{A}})) \to !_{R(L(1_\mathsf{A}))}$$
+of $F\mathbb{C}\textnormal{sp}$. This is just the natural isomorphism $\mathbb{E}_{1_\mathsf{A}}$ from earlier.
+
+Given two horizontal 1-cells $M$ and $N$ of $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$:
 \[
@@
 \node (C) at (4,0) {$c_2+c_2^\prime$};
-\node (D) at (2,-0.5) {$x+x^\prime \in F(R(x+x^\prime))$};
+\node (D) at (2,-0.5) {$x+x^\prime \in F(R(x+x^\prime)).$};
 %\node (D) at (3,0.5) {$!_c \in F(c)$};
@@
 \]
-We then have a 2-isomorphism $\mu_{M,N} \colon E(M) \otimes E(N) \xrightarrow{\sim} E(M \otimes N)$ in $\mathbb{F}\textnormal{Cospan}(\mathrm{A})$ given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$c_1+c_1^\prime$};
+We then have a 2-isomorphism $\mu_{M,N} \colon E(M) \otimes E(N) \xrightarrow{\sim} E(M \otimes N)$ in $F\mathbb{C}\textnormal{sp}$ given by:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (-0.5,0) {$c_1+c_1^\prime$};
 \node (B) at (2,0) {$R(x)+R(x^\prime)$};
-\node (C) at (4,0) {$c_2+c_2^\prime$};
-\node (A') at (0,-1) {$c_1+c_1^\prime$};
+\node (C) at (4.5,0) {$c_2+c_2^\prime$};
+\node (A') at (-0.5,-1) {$c_1+c_1^\prime$};
 \node (B') at (2,-1) {$R(x+x^\prime)$};
-\node (C') at (4,-1) {$c_2+c_2^\prime$};
-\node (D) at (5.75,0) {$\hat{x} \in F(R(x)+R(x^\prime))$};
-\node (D') at (5.75,-1) {$x+x^\prime \in F(R(x+x^\prime))$};
+\node (C') at (4.5,-1) {$c_2+c_2^\prime$};
+\node (D) at (6.25,0) {$\hat{x} \in F(R(x)+R(x^\prime))$};
+\node (D') at (6.25,-1) {$x+x^\prime \in F(R(x+x^\prime))$};
 \node (E) at (2,-1.5) {$\iota_\mu \colon F(\kappa)(\hat{x}) \to x+x^\prime$};
@@
 \]
+where $\kappa$ is an isomorphism as $R \colon \mathsf{X} \to \mathsf{A}$ preserves finite colimits.
+
 The isomorphisms $\delta$ and $\mu$ satisfy the left and right unitality squares, associativity hexagon and braiding square.
-Let $M_1,M_2$ and $M_3$ be horizontal 1-cells in $_L \mathbb{C}\textnormal{sp}(\mathrm{X})$ given by:
+Let $M_1,M_2$ and $M_3$ be horizontal 1-cells in $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$ given by:
 \[
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$1_{\mathbb{F}\textnormal{Cospan}(\mathrm{A})} \otimes \mathbb{E}(M_1)$};
-\node (B) at (3,0) {$\mathbb{E}(1_{ _L \mathbb{C}\textnormal{sp}(\mathrm{X})}) \otimes \mathbb{E}(M_1)$};
+\node (A) at (0,0) {$1_{F\mathbb{C}\textnormal{sp}} \otimes \mathbb{E}(M_1)$};
+\node (B) at (3,0) {$\mathbb{E}(1_{ _L \mathbb{C}\textnormal{sp}(\mathsf{X})}) \otimes \mathbb{E}(M_1)$};
 \node (C) at (0,-1) {$\mathbb{E}(M_1)$};
-\node (D) at (3,-1) {$\mathbb{E}(1_{ _L \mathbb{C}\textnormal{sp}(\mathrm{X})} \otimes M_1)$};
+\node (D) at (3,-1) {$\mathbb{E}(1_{ _L \mathbb{C}\textnormal{sp}(\mathsf{X})} \otimes M_1)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 		\begin{tikzpicture}
-			\node (d) at (7.5,0) {$\mathbb{E}(1_{ _L \mathbb{C}\textnormal{sp}(\mathrm{X})}) \otimes \mathbb{E}(M_1)$};
-			\node (a) at (-4,0) {$1_\mathrm{A}+c_1$};
-			\node (b) at (0.5,0) {$R(L(1_\mathrm{A})) + R(x_1)$};
-			\node (c) at (5,0) {$1_\mathrm{A}+c_1^\prime$};
-			\node (d2) at (7.5,1) {$1_{\mathbb{F}\textnormal{Cospan}(\mathrm{A})} \otimes \mathbb{E}(M_1)$};
-			\node (a2) at (-4,1) {$1_\mathrm{A}+c_1$};
-			\node (b2) at (0.5,1) {$1_\mathrm{A}+R(x_1)$};
-			\node (c2) at (5,1) {$1_\mathrm{A}+c_1^\prime$};
+			\node (d) at (7.5,0) {$\mathbb{E}(1_{ _L \mathbb{C}\textnormal{sp}(\mathsf{X})}) \otimes \mathbb{E}(M_1)$};
+			\node (a) at (-4,0) {$1_\mathsf{A}+c_1$};
+			\node (b) at (0.5,0) {$R(L(1_\mathsf{A})) + R(x_1)$};
+			\node (c) at (5,0) {$1_\mathsf{A}+c_1^\prime$};
+			\node (d2) at (7.5,1) {$1_{F\mathbb{C}\textnormal{sp}} \otimes \mathbb{E}(M_1)$};
+			\node (a2) at (-4,1) {$1_\mathsf{A}+c_1$};
+			\node (b2) at (0.5,1) {$1_\mathsf{A}+R(x_1)$};
+			\node (c2) at (5,1) {$1_\mathsf{A}+c_1^\prime$};
 			\node (d3) at (7.5,2) {$\mathbb{E}(M_1)$};
@@
 			\node (c3) at (5,2) {$c_1^\prime$};
-			\node (d4) at (7.5,-1) {$\mathbb{E}(1_{ _L \mathbb{C}\textnormal{sp}(\mathrm{X})} \otimes M_1)$};
-                                \node (a5) at (-4,-1) {$1_\mathrm{A}+c_1^\prime$};
-			\node (b5) at (0.5,-1) {$R(L(1_\mathrm{A})+x_1)$};
-			\node (c5) at (5,-1) {$1_\mathrm{A}+c_1^\prime$};
+			\node (d4) at (7.5,-1) {$\mathbb{E}(1_{ _L \mathbb{C}\textnormal{sp}(\mathsf{X})} \otimes M_1)$};
+                                \node (a5) at (-4,-1) {$1_\mathsf{A}+c_1^\prime$};
+			\node (b5) at (0.5,-1) {$R(L(1_\mathsf{A})+x_1)$};
+			\node (c5) at (5,-1) {$1_\mathsf{A}+c_1^\prime$};
 			\node (d5) at (7.5,-2) {$\mathbb{E}(M_1)$};
@@
 			(d4) edge node [left] {$\mathbb{E}(\lambda)$} (d5)
-			(a) edge node[above]{$\eta_{1_\mathrm{A}}+R(i_1)\eta_{c_1}$} (b)
-			(c) edge node[above]{$\eta_{1_\mathrm{A}}+R(o_1)\eta_{c_1^\prime}$} (b)
+			(a) edge node[above]{$\eta_{1_\mathsf{A}}+R(i_1)\eta_{c_1}$} (b)
+			(c) edge node[above]{$\eta_{1_\mathsf{A}}+R(o_1)\eta_{c_1^\prime}$} (b)
                                 (a2) edge node[above]{$1+R(i_1)\eta_{c_1}$} (b2)
@@
                                 (a2) edge node[left]{$1$} (a)
-                                (b2) edge node[left]{$\eta_{1_\mathrm{A}}+1$} (b)
+                                (b2) edge node[left]{$\eta_{1_\mathsf{A}}+1$} (b)
 (b2) edge node[right]{$\iota_2$} (b)
@@
 			(c3) edge node[above]{$R(o_1)\eta_{c_1^\prime}$} (b3)
-                                (a2) edge node[left]{$\lambda_{\mathrm{A}}$} (a3)
-                                (b2) edge node[left]{$\lambda_{\mathrm{A}}$} (b3)
+                                (a2) edge node[left]{$\lambda_{\mathsf{A}}$} (a3)
+                                (b2) edge node[left]{$\lambda_{\mathsf{A}}$} (b3)
 (b2) edge node[right]{$\iota_1$} (b3)
-			(c2) edge node[left]{$\lambda_{\mathrm{A}}$} (c3)
-                                (a5) edge node[above]{$(\mu_{L(1_\mathrm{A}),d_1})(\eta_{1_\mathrm{A}}+R(i_1)\eta_{c_1})$} (b5)
-			(c5) edge node[above]{$(\mu_{L(1_\mathrm{A}),d_1})(\eta_{1_\mathrm{A}}+R(o_1)\eta_{c_1^\prime})$} (b5)
+			(c2) edge node[left]{$\lambda_{\mathsf{A}}$} (c3)
+                                (a5) edge node[above]{$(\mu_{L(1_\mathsf{A}),d_1})(\eta_{1_\mathsf{A}}+R(i_1)\eta_{c_1})$} (b5)
+			(c5) edge node[above]{$(\mu_{L(1_\mathsf{A}),d_1})(\eta_{1_\mathsf{A}}+R(o_1)\eta_{c_1^\prime})$} (b5)
                                 (a) edge node[left]{$1$} (a5)
-                                (b) edge node[left]{$\mu_{L(1_\mathrm{A}),d_1}$} (b5)
+                                (b) edge node[left]{$\mu_{L(1_\mathsf{A}),x_1}$} (b5)
 (b) edge node[right]{$\iota_3$} (b5)
@@
 			(c6) edge node[above]{$R(o_1)\eta_{c_1^\prime}$} (b6)
-                                (a5) edge node[left]{$\lambda_{\mathrm{A}}$} (a6)
-                                (b5) edge node[left]{$R(\lambda_{\mathrm{X}})$} (b6)
+                                (a5) edge node[left]{$\lambda_{\mathsf{A}}$} (a6)
+                                (b5) edge node[left]{$R(\lambda_{\mathsf{X}})$} (b6)
  (b5) edge node[right]{$\iota_4$} (b6)
-			(c5) edge node[left]{$\lambda_{\mathrm{A}}$} (c6);
+			(c5) edge node[left]{$\lambda_{\mathsf{A}}$} (c6);
 		\end{tikzpicture}
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (-.5,0) {$F(\lambda_{\mathrm{A}})(!_{1_\mathrm{A}}+x_1)$};
-\node (C) at (4,0) {$F(R(\lambda_{\mathrm{X}})(\mu_{L(1_\mathrm{A}),x_1}))(!_{R(L(1_\mathrm{A}))} +x_1$)};
+\node (A) at (-.5,0) {$F(\lambda_{\mathsf{A}})(!_{1_\mathsf{A}}+x_1)$};
+\node (C) at (4,0) {$F(R(\lambda_{\mathsf{X}})(\mu_{L(1_\mathsf{A}),x_1}))(!_{R(L(1_\mathsf{A}))} +x_1$)};
 \node (D) at (-.5,-1) {$x_1$};
-\node (E) at (4,-1) {$F(R(\lambda_\mathrm{X}))(x_{!+1})$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$F(R(\lambda_{\mathrm{X}})(\mu_{L(1_\mathrm{A}),x_1}))(\iota_2)$} (C)
+\node (E) at (4,-1) {$F(R(\lambda_\mathsf{X}))(x_{!+1})$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$F(R(\lambda_{\mathsf{X}})(\mu_{L(1_\mathsf{A}),x_1}))(\iota_2)$} (C)
 (A) edge node[left]{$\iota_1$} (D)
 (E) edge node[above]{$\iota_4$} (D)
-(C) edge node[right]{$F(R(\lambda_\mathrm{X}))(\iota_3)$} (E);
-\end{tikzpicture}
-\]
-where $x_{!+1}$ is the decoration $x_1$ on the element $R(L(1_\mathrm{A})+x_1) \in \mathrm{A}$.
-The above square commutes because $$F(\lambda_\mathrm{A})(!_{1_\mathrm{A}}+x_1) = F(R(\lambda_\mathrm{X})(\mu_{L(1_\mathrm{A}),x_1})(\eta_{1_\mathrm{A}}+1))(!_{1_\mathrm{A}}+x_1)$$ as the above diagram of maps of cospans commutes.
+(C) edge node[right]{$F(R(\lambda_\mathsf{X}))(\iota_3)$} (E);
+\end{tikzpicture}
+\]
+where $x_{!+1}$ is the decoration $x_1$ on the object $R(L(1_\mathsf{A})+x_1) \in \mathsf{A}$.
+The above square commutes because $$F(\lambda_\mathsf{A})(!_{1_\mathsf{A}}+x_1) = F(R(\lambda_\mathsf{X})(\mu_{L(1_\mathsf{A}),x_1})(\eta_{1_\mathsf{A}}+1))(!_{1_\mathsf{A}}+x_1)$$ as the corresponding left unitality square for the symmetric monoidal functor $R \colon (\mathsf{X},1_\mathsf{X},+) \to (\mathsf{A},1_\mathsf{A},+)$ commutes.
 The right unitality square is similar.
@@
 			(c4) edge node[above]{$R(o_1+(o_2+o_3))\eta_{c_1^\prime+(c_2^\prime+c_3^\prime)}$} (b4)
-                                (a3) edge node[left]{$a_\mathrm{A}$} (a4)
-                                (b3) edge node[left]{$R(a_\mathrm{X})$} (b4)
+                                (a3) edge node[left]{$a_\mathsf{A}$} (a4)
+                                (b3) edge node[left]{$R(a_\mathsf{X})$} (b4)
 (b3) edge node[right]{$\iota_3$} (b4)
-			(c3) edge node[left]{$a_\mathrm{A}$} (c4)
+			(c3) edge node[left]{$a_\mathsf{A}$} (c4)
                                 (a5) edge node[above]{$R(i_1)\eta_{c_1}+(R(i_2)\eta_{c_2}+R(i_3)\eta_{c_3})$} (b5)
 			(c5) edge node[above]{$R(o_1)\eta_{c_1^\prime}+(R(o_2)\eta_{c_2^\prime}+R(o_3)\eta_{c_3^\prime})$} (b5)
-                                (a) edge node[left]{$a_\mathrm{A}$} (a5)
-                                (b) edge node[left]{$a_\mathrm{A}$} (b5)
+                                (a) edge node[left]{$a_\mathsf{A}$} (a5)
+                                (b) edge node[left]{$a_\mathsf{A}$} (b5)
 (b) edge node[right]{$\iota_4$} (b5)
-			(c) edge node[left]{$a_\mathrm{A}$} (c5)
+			(c) edge node[left]{$a_\mathsf{A}$} (c5)
                                 (a6) edge node[above]{$R(i_1)\eta_{c_1}+R(i_2+i_3)\eta_{c_2+c_3}$} (b6)
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$F((\kappa)(1+\kappa)(a_\mathrm{A}))((x_1+x_2)+x_3)$};
+\node (A) at (0,0) {$F((\kappa)(1+\kappa)(a_\mathsf{A}))((x_1+x_2)+x_3)$};
 \node (B) at (5,0) {$F((R(a_\mathrm{X}))(\kappa))((x_1+x_2)+x_3)$};
@@
 \path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$F((R(a_\mathrm{X}))(\kappa))(\iota_1)$} (B)
-(B) edge node[right]{$F(R(a_\mathrm{X}))(\iota_2)$} (C)
+(A) edge node[above]{$F((R(a_\mathsf{X}))(\kappa))(\iota_1)$} (B)
+(B) edge node[right]{$F(R(a_\mathsf{X}))(\iota_2)$} (C)
 (C) edge node[right]{$\iota_3$} (D)
@@
 \]
-The above square commutes because $$F((\kappa)(1+\kappa)(a_\mathrm{A}))((x_1+x_2)+x_3) = F((R(a_\mathrm{X}))(\kappa)(\kappa+1))((x_1+x_2)+x_3)$$ as the above diagram of maps of cospans commutes.
+The above square commutes because $$F((\kappa)(1+\kappa)(a_\mathsf{A}))((x_1+x_2)+x_3) = F((R(a_\mathsf{X}))(\kappa)(\kappa+1))((x_1+x_2)+x_3)$$ as the corresponding associator hexagon for the symmetric monoidal functor $R \colon (\mathsf{X},1_\mathsf{X},+) \to (\mathsf{A},1_\mathsf{A},+)$ commutes.
 Lastly, the braiding square:
@@
 \path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$\beta$} (B)
+(A) edge node[above]{$\beta^\prime$} (B)
 (B) edge node[right]{$\mu_{M_2,M_1}$} (D)
@@
 			\path[->,font=\scriptsize,>=angle 90]
-(d) edge node[left]{$\beta$} (d2)
+(d) edge node[left]{$\beta^\prime$} (d2)
 (d2) edge node[left]{$\mu_{M_2,M_1}$}(d3)
@@
 			(c2) edge node[above]{$R(o_2) \eta_{c_2^\prime} + R(o_1) \eta_{c_1^\prime}$} (b2)
-                                (a) edge node[left]{$\beta_\mathrm{A}$} (a2)
-                                (b) edge node[left]{$\beta_\mathrm{A}$} (b2)
+                                (a) edge node[left]{$\beta_\mathsf{A}$} (a2)
+                                (b) edge node[left]{$\beta_\mathsf{A}$} (b2)
 (b) edge node[right]{$\iota_1$} (b2)
-			(c) edge node[left]{$\beta_\mathrm{A}$} (c2)
+			(c) edge node[left]{$\beta_\mathsf{A}$} (c2)
                                 (a3) edge node[above]{$R(i_2+i_1)\eta_{c_2+c_1}$} (b3)
@@
 			(c6) edge node[above]{$R(o_2+o_1)\eta_{c_2^\prime+c_1^\prime}$} (b6)
-                                (a5) edge node[left]{$\beta_\mathrm{A}$} (a6)
-                                (b5) edge node[left]{$R(\beta_\mathrm{X})$} (b6)
+                                (a5) edge node[left]{$\beta_\mathsf{A}$} (a6)
+                                (b5) edge node[left]{$R(\beta_\mathsf{X})$} (b6)
  (b5) edge node[right]{$\iota_4$} (b6)
-			(c5) edge node[left]{$\beta_\mathrm{A}$} (c6);
+			(c5) edge node[left]{$\beta_\mathsf{A}$} (c6);
 		\end{tikzpicture}
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (-.5,0) {$F((\kappa)(\beta_\mathrm{A}))(x_1+x_2)$};
+\node (A) at (-.5,0) {$F((\kappa)(\beta_\mathsf{A}))(x_1+x_2)$};
 \node (C) at (4,0) {$F(\kappa)(x_2+x_1)$};
-\node (D) at (-.5,-1) {$F(R(\beta_\mathrm{X}))(x_1+x_2)$};
+\node (D) at (-.5,-1) {$F(R(\beta_\mathsf{X}))(x_1+x_2)$};
 \node (E) at (4,-1) {$x_2+x_1$};
@@
 (A) edge node[above]{$F(\kappa)(\iota_1)$} (C)
-(A) edge node[left]{$F(R(\beta_\mathrm{X}))(\iota_3)$} (D)
+(A) edge node[left]{$F(R(\beta_\mathsf{X}))(\iota_3)$} (D)
 (D) edge node[above]{$\iota_4$} (E)
@@
 \]
-The above square commutes because $$F((\kappa)(\beta_\mathrm{A}))(x_1+x_2) = F((R(\beta_\mathrm{X}))(\kappa))(x_1+x_2)$$ as the above diagram of maps of cospans commutes.
-Thus the double functor $\mathbb{E} \colon _L\mathbb{C}\textnormal{sp}(\mathrm{X}) \to \mathbb{F}\textnormal{Cospan}(\mathrm{A})$ is symmetric monoidal.
+The above square commutes because $$F((\kappa)(\beta_\mathsf{A}))(x_1+x_2) = F((R(\beta_\mathsf{X}))(\kappa))(x_1+x_2)$$ as the corresponding braiding square for the symmetric monoidal functor $R \colon (\mathsf{X},1_\mathsf{X},+) \to (\mathsf{A},1_\mathsf{A},+)$ commutes.
+Thus the double functor $\mathbb{E} \colon _L\mathbb{C}\textnormal{sp}(\mathsf{X}) \to F\mathbb{C}\textnormal{sp}$ is symmetric monoidal.
 \end{proof}

### 2019-01-08 EquivCompFrameworks_20180911kc.tex
More notational changes

@@
 \begin{lem}
-The double category $\mathbb{F}\textnormal{Cospan}(\mathrm{A})$ is fibrant.
+The double category $F\mathbb{C}\textnormal{sp}$ is fibrant.
 \end{lem}
@@
 \begin{proof}
-Let $f \colon c \to c^\prime$ be a vertical 1-morphism in $\mathbb{F} \textnormal{Cospan}(\mathrm{A})$. We can lift $f$ to the companion horizontal 1-cell $\hat{f}$:
+Let $f \colon c \to c^\prime$ be a vertical 1-morphism in $F\mathbb{C}\textnormal{sp}$. We can lift $f$ to the companion horizontal 1-cell $\hat{f}$:
 \[
@@
 \node (K) at (7,-0.5) {$!_{c^\prime} \in F(c^\prime)$};
-\node (L) at (1,-1) {$\iota_{c^\prime} = 1_{!_{c^\prime}}$};
+\node (L) at (1,-1) {$\iota_{1_{c^\prime}} = 1_{!_{c^\prime}}$};
 \node (M) at (5,-1) {$\iota_f \colon F(f)(!_c) \to !_{c^\prime}$};
@@
 
-\begin{thm}
-There exists a symmetric monoidal bicategory $H(\mathbb{F}\textnormal{Cospan}(\mathrm{A}))$ which has:
+\begin{cor}
+Let $(\mathsf{C},+,0)$ be a category with finite colimts and $F \colon \mathsf{C} \to \mathbf{Cat}$ a symmetric lax monoidal pseudofunctor.
+Then there exists a symmetric monoidal bicategory $F \mathbf{Csp} \coloneqq H(F\mathbb{C}\textnormal{sp})$ which has:
 \begin{enumerate}
-\item{objects as those of $\mathrm{A}$,}
-\item{morphisms as pairs:
+\item{objects as those of $\mathsf{A}$,}
+\item{morphisms as $F$-decorated cospans:
 \[
@@
 and}
-\item{2-morphisms as maps of cospans in $\mathrm{A}$ of the form:
+\item{2-morphisms as maps of cospans in $\mathsf{A}$ of the form:
 \[
@@
 \end{enumerate}
-\end{thm}
+\end{cor}
 
 \begin{proof}
-This follows immediately by Shulman's Theorem \ref{Shul} above.
+This follows immediately by Shulman's Theorem \ref{Shul} above applied to the fibrant symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$.
 \end{proof}
 
-This symmetric monoidal bicategory is a superior version of the symmetric monoidal bicategory constructed earlier by the second author \cite{Cour}.
-The previous bicategory constructed by the second author suffered even more so from the issue discussed in the introduction.
+This symmetric monoidal bicategory $F\mathbf{Csp}$ is a superior version of the symmetric monoidal bicategory $F$Cospan$(\mathsf{A})$ constructed earlier by the second author \cite{Cour} in that there is greater flexibility in what 2-morphisms are allowed.
+
+%The previous bicategory constructed by the second author suffered even more so from the issue discussed in the introduction.
 Given a symmetric lax monoidal functor $F \colon \mathrm{A} \to \mathrm{Set}$, a result of Fong \cite{Fong} yields a symmetric monoidal category $F \textnormal{Cospan}(\mathrm{A})$ which has:
-\begin{enumerate}
-\item{objects as those of $\mathrm{A}$ and}
-\item{morphisms as isomorphism classes of decorated cospans in $\mathrm{A}$.}
-\end{enumerate}
-The second author then using a result of Shulman \cite{Shul} extended this to a bicategory also called $F \textnormal{Cospan}(\mathrm{A})$ which has:
-\begin{enumerate}
-\item{objects as those of $\mathrm{A}$,}
-\item{morphisms as now just decorated cospans in $\mathrm{A}$, and}
-\item{2-morphisms as pairs of commuting diagrams:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a$};
-\node (B) at (1,0.5) {$c$};
-\node (B') at (1,-0.5) {$c^\prime$};
-\node (C) at (2,0) {$b$};
-\node (D) at (3,0) {$1$};
-\node (E) at (4,0.5) {$F(c)$};
-\node (E') at (4,-0.5) {$F(c^\prime)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i$} (B)
-(C) edge node[above]{$o$} (B)
-(A) edge node[below]{$i^\prime$} (B')
-(C) edge node[below]{$o^\prime$} (B')
-(B) edge node [left] {$f$} (B')
-(D) edge node [above] {$d$} (E)
-(D) edge node [below] {$d^\prime$} (E')
-(E) edge node [right] {$F(f)$} (E');
-\end{tikzpicture}
-\]
-}
-\end{enumerate}
-This was discussed in the introduction and it was mentioned how in the symmetric monoidal category version of $F \textnormal{Cospan}(\mathrm{A})$, that the two single-edged graphs:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$v_1$};
-\node (B) at (1,0) {$v_2$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$e$} (B);
-\end{tikzpicture}
-\]
-and
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$v_1$};
-\node (B) at (1,0) {$v_2.$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$e^\prime$} (B);
-\end{tikzpicture}
-\]
-resided in distinct isomorphism classes.
+%\begin{enumerate}
+%\item{objects as those of $\mathrm{A}$ and}
+%\item{morphisms as isomorphism classes of decorated cospans in $\mathrm{A}$.}
+%\end{enumerate}
+%The second author then using a result of Shulman \cite{Shul} extended this to a bicategory also called $F \textnormal{Cospan}(\mathrm{A})$ which has:
+%\begin{enumerate}
+%\item{objects as those of $\mathrm{A}$,}
+%\item{morphisms as now just decorated cospans in $\mathrm{A}$, and}
+%\item{2-morphisms as pairs of commuting diagrams:
+%\[
+%\begin{tikzpicture}[scale=1.5]
+%\node (A) at (0,0) {$a$};
+%\node (B) at (1,0.5) {$c$};
+%\node (B') at (1,-0.5) {$c^\prime$};
+%\node (C) at (2,0) {$b$};
+%\node (D) at (3,0) {$1$};
+%\node (E) at (4,0.5) {$F(c)$};
+%\node (E') at (4,-0.5) {$F(c^\prime)$};
+%\path[->,font=\scriptsize,>=angle 90]
+%(A) edge node[above]{$i$} (B)
+%(C) edge node[above]{$o$} (B)
+%(A) edge node[below]{$i^\prime$} (B')
+%(C) edge node[below]{$o^\prime$} (B')
+%(B) edge node [left] {$f$} (B')
+%(D) edge node [above] {$d$} (E)
+%(D) edge node [below] {$d^\prime$} (E')
+%(E) edge node [right] {$F(f)$} (E');
+%\end{tikzpicture}
+%\]
+%}
+%\end{enumerate}
+%This was discussed in the introduction and it was mentioned how in the symmetric monoidal category version of $F \textnormal{Cospan}(\mathrm{A})$, that the two single-edged graphs:
+%\[
+%\begin{tikzpicture}[scale=1.5]
+%\node (A) at (0,0) {$v_1$};
+%\node (B) at (1,0) {$v_2$};
+%\path[->,font=\scriptsize,>=angle 90]
+%(A) edge node[above]{$e$} (B);
+%\end{tikzpicture}
+%\]
+%and
+%\[
+%\begin{tikzpicture}[scale=1.5]
+%\node (A) at (0,0) {$v_1$};
+%\node (B) at (1,0) {$v_2.$};
+%\path[->,font=\scriptsize,>=angle 90]
+%(A) edge node[above]{$e^\prime$} (B);
+%\end{tikzpicture}
+%\]
+%resided in distinct isomorphism classes.
 In the bicategorical version of $F \textnormal{Cospan}(\mathrm{A})$ where we are no longer considering decorated cospans up to isomorphism class, there is no 2-morphism between these two graphs due to the strict commutativity of the triangle to the right above.
@@
 
-We can the decategorify this symmetric monoidal bicategory to obtain a symmetric monoidal category similar to the one obtained using Fong's result:
+We can then decategorify this symmetric monoidal bicategory to obtain a symmetric monoidal category similar to the one obtained using Fong's result, but with larger isomorphism classes:
 
 \begin{cor}
-Given a symmetric lax monoidal pseudofunctor $F \colon \mathrm{A} \to \mathbf{Cat}$ where $\mathrm{A}$ is a category with finite colimits and whose monoidal structure is given by binary coproducts, there exists a symmetric monoidal category $D(H(\mathbb{F}\textnormal{Cospan}(\mathrm{A})))$ which has:
+Given a symmetric lax monoidal pseudofunctor $F \colon \mathsf{A} \to \mathbf{Cat}$ where $\mathsf{A}$ is a category with finite colimits and whose monoidal structure is given by binary coproducts, there exists a symmetric monoidal category $F\textnormal{Csp} \coloneqq D(F\mathbf{Csp})$ which has:
 \begin{enumerate}
-\item{objects as those of $\mathrm{A}$ and}
-\item{morphisms as isomorphism classes of $F$-decorated cospans of $\mathrm{A}$, where an $F$-decorated cospan is given by a pair:
+\item{objects as those of $\mathsf{A}$ and}
+\item{morphisms as isomorphism classes of $F$-decorated cospans of $\mathsf{A}$, where an $F$-decorated cospan is given by a pair:
 \[
@@
 \section{Maps of decorated cospan double categories}\label{MapsDecCospansDoubleCat}
-Let $F \colon \mathrm{A} \to \mathbf{Cat}$ be a symmetric lax monoidal pseudofunctor.
-Then by Theorem \ref{main1} of the previous section, we get a symmetric monoidal double category $\mathbb{F}\textnormal{Cospan}(\mathrm{A})$.
+Let $F \colon \mathsf{A} \to \mathbf{Cat}$ be a symmetric lax monoidal pseudofunctor.
+Then by Theorem \ref{DC} of the previous section, we get a symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$.
 This symmetric monoidal double category has:
 \begin{enumerate}
-\item{objects as those of $\mathrm{A}$,}
-\item{vertical 1-morphisms as morphisms of $\mathrm{A}$,}
+\item{objects as those of $\mathsf{A}$,}
+\item{vertical 1-morphisms as morphisms of $\mathsf{A}$,}
 \item{horizontal 1-cells as pairs:
@@
 and}
-\item{2-morphisms as maps of cospans in $\mathrm{A}$
+\item{2-morphisms as maps of cospans in $\mathsf{A}$
 \[
@@
 \end{enumerate}
-Given another symmetric lax monoidal pseudofunctor $F^\prime \colon \mathrm{A^\prime} \to \mathbf{Cat}$, we can obtain another symmetric monoidal double category $\mathbb{F^\prime}\textnormal{Cospan}(\mathrm{A^\prime})$.
-Then a map from $\mathbb{F}\textnormal{Cospan}(\mathrm{A})$ to $\mathbb{F^\prime}\textnormal{Cospan}(\mathrm{A^\prime})$ will be a double functor $\mathbb{H} \colon \mathbb{F}\textnormal{Cospan}(\mathrm{A}) \to \mathbb{F^\prime}\textnormal{Cospan}(\mathrm{A^\prime})$ whose object component is given by a finite colimit preserving functor $\mathbb{H}_0 = H \colon \mathrm{A} \to \mathrm{A^\prime}$ and whose arrow component is given by a functor $\mathbb{H}_1$ defined on horizontal 1-cells by:
+Given another symmetric lax monoidal pseudofunctor $F^\prime \colon \mathsf{A^\prime} \to \mathbf{Cat}$, we can obtain another symmetric monoidal double category $F^\prime \mathbb{C}\textnormal{sp}$.
+Then a map from $F\mathbb{C}\textnormal{sp}$ to $F^\prime \mathbb{C}\textnormal{sp}$ will be a double functor $\mathbb{H} \colon F\mathbb{C}\textnormal{sp} \to F' \mathbb{C}\textnormal{sp}$ whose object component is given by a finite colimit preserving functor $\mathbb{H}_0 = H \colon \mathsf{A} \to \mathsf{A^\prime}$ and whose arrow component is given by a functor $\mathbb{H}_1$ defined on horizontal 1-cells by:
 \[
@@
 \]
-where $E \colon \mathbf{Cat} \to \mathbf{Cat}$ is a terminal category preserving 2-functor such that the following diagram commutes:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$\mathrm{A}$};
+where $E \colon \mathbf{Cat} \to \mathbf{Cat}$ is a symmetric lax monoidal pseudofuctor such that the following diagram commutes:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$\mathsf{A}$};
 \node (B) at (1,0) {$\mathbf{Cat}$};
-\node (C) at (0,-1) {$\mathrm{A^\prime}$};
+\node (C) at (0,-1) {$\mathsf{A^\prime}$};
 \node (D) at (1,-1) {$\mathbf{Cat}$};
@@
 \]
-Applying the terminal category preserving 2-functor $E \colon \mathbf{Cat} \to \mathbf{Cat}$ to this diagram yields:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,-0.5) {$E(1) \cong 1$};
+Applying the pseudofunctor $E \colon \mathbf{Cat} \to \mathbf{Cat}$ to this diagram yields:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,-0.5) {$1 \xrightarrow{\sim} E(1)$};
 \node (B) at (1.5,0) {$E(F(c))$};
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,-0.5) {$E(1) \cong 1$};
+\node (A) at (0,-0.5) {$1 \xrightarrow{\sim} E(1)$};
 \node (B) at (1.5,0) {$F^\prime(H(c))$};
@@
 which is the same as a morphism $E(\iota) \colon F^\prime(H(h))(E(d)) \to E(d^\prime)$ in $F^\prime(H(c^\prime))$.
-To check that the above recipe is functorial, given two vertically composable 2-morphisms in $\mathbb{F}\textnormal{Cospan}(\mathrm{A})$:
+To check that the above recipe is functorial, given two vertically composable 2-morphisms in $F\mathbb{C}\textnormal{sp}$:
 \[
@@
 
-Given two composable horizontal 1-cells $M$ and $N$ in $\mathbb{F}\textnormal{Cospan}(\mathrm{A})$:
+Given two composable horizontal 1-cells $M$ and $N$ in $F\mathbb{C}\textnormal{sp}$:
 \[
@@
 \node (A) at (0,0) {$H(a_1)$};
-\node (B) at (1.5,0) {$H(c_1+_b c_2)$};
-\node (C) at (3,0) {$H(a_2)$};
-\node (D) at (1.5,-0.5) {$E(d) \in F^\prime(H(c_1 +_b c_2))$};
+\node (B) at (2,0) {$H(c_1+_b c_2)$};
+\node (C) at (4,0) {$H(a_2)$};
+\node (D) at (2,-0.5) {$E(d) \in F^\prime(H(c_1 +_b c_2))$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \node (A) at (0,0) {$H(a_1)$};
-\node (B) at (2,0) {$H(c_1)+_{H(b)} H(c_2)$};
-\node (C) at (4,0) {$H(a_2)$};
-\node (D) at (2,-0.5) {$d^\prime \in F^\prime(H(c_1) +_{H(b)} H(c_2))$};
+\node (B) at (2.25,0) {$H(c_1)+_{H(b)} H(c_2)$};
+\node (C) at (4.5,0) {$H(a_2)$};
+\node (D) at (2.25,-0.5) {$d^\prime \in F^\prime(H(c_1) +_{H(b)} H(c_2))$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \node (E) at (7,0.5) {$d^\prime \in F^\prime(H(c_1)+_{H(b_1)}H(c_2))$};
-\node (F) at (7,-0.5) {$d \in F^\prime(H(c_1 +_b c_2))$};
-\node (G) at (2.5,-1) {$\iota_{\kappa^{-1}} \colon F^\prime(\kappa^{-1})(d^\prime) \to d.$};
+\node (F) at (7,-0.5) {$E(d) \in F^\prime(H(c_1 +_b c_2))$};
+\node (G) at (2.5,-1) {$\iota_{\kappa^{-1}} \colon F^\prime(\kappa^{-1})(d^\prime) \to E(d).$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-where $\kappa$ is the isomorphism $$\kappa \colon H(c_1 +_b c_2) \xrightarrow{\sim} H(c_1) +_{H(b)} H(c_2)$$ which comes from the functor $H \colon \mathrm{A} \to \mathrm{A^\prime}$ preserving finite colimits.
-The above diagram commutes by a similar argument as to the one used in Theorem \ref{main2}.
+where $\kappa$ is the isomorphism $$\kappa \colon H(c_1 +_b c_2) \xrightarrow{\sim} H(c_1) +_{H(b)} H(c_2)$$ comes from the finite colimit preserving functor $H \colon \mathsf{A} \to \mathsf{A^\prime}$.
+The above diagram commutes by a similar argument to the one used in Theorem \ref{Equiv}.
 Similarly we have a unit comparison constraint $$\mathbb{H}_U \colon U_{\mathbb{H}(c)} \to \mathbb{H}(U_c)$$ given by the globular 2-isomorphism:
@@
 \]
-where the morphism of decorations is the identity $!_{H(c)} = E(!_c)$ as $EF=F^\prime H$. These comparison constrains satisfy the coherence axioms of a monoidal category, namely:
+where the morphism of decorations is the morphism $\iota \colon !_{H(c)} \to E(!_c)$ in $F'(H(c))$. These comparison constrains satisfy the coherence axioms of a monoidal category, namely:
 \[
@@
 (B') edge node [right] {$\mathbb{H}_{M,N \odot P}$} (C')
-(A') edge node [right]{$1 \odot \mathbb{H}_{N \odot P}$} (B');
+(A') edge node [right]{$1 \odot \mathbb{H}_{N,P}$} (B');
 \end{tikzpicture}
@@
 \]
+The diagrams involving the morphisms of decorations are similar to those in Theorem \ref{DC}.
 This shows that $\mathbb{H}=(H,E)$ is a double functor.
-Next we show that this double functor is in fact symmetric monoidal.
-First, that the object component $\mathbb{H}_0=H$ is symmetric monoidal is clear as $H$ preserves finite colimits.
-As for the arrow component $\mathbb{H}_1$, given two horizontal 1-cells $M_1$ and $M_2$ in $\mathbb{F}\textnormal{Cospan}(\mathrm{A})$:
+Next we show that this double functor is symmetric monoidal.
+First, that the object component $\mathbb{H}_0=H$ is symmetric monoidal is clear as $H \colon \mathsf{A} \to \mathsf{A}^\prime$ preserves finite colimits.
+As for the arrow component $\mathbb{H}_1$, given two horizontal 1-cells $M_1$ and $M_2$ in $F\mathbb{C}\textnormal{sp}$:
 \[
@@
 \]
-their tensor product $M_1 \otimes M_2$ in $\mathbb{F}\textnormal{Cospan}(\mathrm{A})$ is given by:
+their tensor product $M_1 \otimes M_2$ in $F\mathbb{C}\textnormal{sp}$ is given by:
 \[
@@
 \node (C) at (3,0) {$b_1+b_2$};
-\node (D) at (1.5,-0.5) {$d_1+d_2 \in F(c_1)$};
+\node (D) at (1.5,-0.5) {$d_1+d_2 \in F(c_1+c_2)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-$$E(d_1)+E(d_2) \colon 1 \xrightarrow{E(d_1) \times E(d_2)} F^\prime(H(c_1)) \times F^\prime(H(c_2)) \xrightarrow{\Phi_{H(c_1),H(c_2)}} F^\prime (H(c_1)+H(c_2)).$$  We then have a natural 2-isomorphism $\mu_{M_1,M_2} \colon \mathbb{H}(M_1) \otimes \mathbb{H}(M_2) \to \mathbb{H}(M_1 \otimes M_2)$ in $\mathbb{F^\prime}\textnormal{Cospan}(\mathrm{A^\prime})$ given by:
+$$E(d_1)+E(d_2) \colon 1 \xrightarrow{E(d_1) \times E(d_2)} F^\prime(H(c_1)) \times F^\prime(H(c_2)) \xrightarrow{\Phi_{H(c_1),H(c_2)}} F^\prime (H(c_1)+H(c_2)).$$  We then have a natural 2-isomorphism $\mu_{M_1,M_2} \colon \mathbb{H}(M_1) \otimes \mathbb{H}(M_2) \to \mathbb{H}(M_1 \otimes M_2)$ in $F'\mathbb{C}\textnormal{sp}$ given by:
 \[
@@
 where $\kappa$ denotes the isomorphism arising from $H$ preserving finite colimits.
-This natural 2-isomorphism together with the associators of $\mathbb{F}\textnormal{Cospan}(\mathrm{A})$ and $\mathbb{F^\prime} \textnormal{Cospan}(\mathrm{A^\prime})$, respectively $\alpha$ and $\alpha^\prime$, make the following diagram commute:
+This natural 2-isomorphism together with the associators of $F\mathbb{C}\textnormal{sp}$ and $F'\mathbb{C}\textnormal{sp}$, respectively $\alpha$ and $\alpha^\prime$, make the following diagram commute:
 \[
@@
 (C) edge node [above] {$\mathbb{H}(\alpha)$} (C')
-(B') edge node [right] {$\mathbb{H}_{M_1,M_2 \otimes M_3}$} (C')
+(B') edge node [right] {$\mu_{M_1,M_2 \otimes M_3}$} (C')
 (A') edge node [right]{$1 \otimes \mu_{M_2 \otimes M_3}$} (B');
@@
 \]
-where $$F^\prime(\alpha \kappa \kappa)((E(d_1)+E(d_2))+E(d_3)) = F^\prime(\kappa \kappa \alpha^\prime)((E(d_1)+E(d_2))+E(d_3)).$$
-We also have that the monoidal unit of $\mathbb{F}\textnormal{Cospan}(\mathrm{A})_1$ is given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$1_\mathrm{A}$};
-\node (B) at (1,0) {$1_\mathrm{A}$};
-\node (C) at (2,0) {$1_\mathrm{A}$};
-\node (D) at (1,-0.5) {$!_{1_\mathrm{A}} \in F(1_\mathrm{A})$};
+where $$F^\prime(\alpha \kappa \kappa)((E(d_1)+E(d_2))+E(d_3)) = F^\prime(\kappa \kappa \alpha^\prime)((E(d_1)+E(d_2))+E(d_3))$$
+as the corresponding hexagon for the symmetric lax monoidal pseudofunctor $E \colon \mathbf{Cat} \to \mathbf{Cat}$ commutes.
+
+We also have that the monoidal unit of $F\mathbb{C}\textnormal{sp}_1$ is given by:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$1_\mathsf{A}$};
+\node (B) at (1,0) {$1_\mathsf{A}$};
+\node (C) at (2,0) {$1_\mathsf{A}$};
+\node (D) at (1,-0.5) {$!_{1_\mathsf{A}} \in F(1_\mathsf{A})$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-where $1_\mathrm{A}$ is the monoidal unit of the finitely cocartesian category $\mathrm{A}$. The image of this horizontal 1-cell under $\mathbb{H}$ is given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$H(1_\mathrm{A})$};
-\node (B) at (1,0) {$H(1_\mathrm{A})$};
-\node (C) at (2,0) {$H(1_\mathrm{A})$};
-\node (E) at (3,0) {$=$};
-\node (F) at (4,0) {$1_\mathrm{A^\prime}$};
-\node (G) at (5,0) {$1_\mathrm{A^\prime}$};
-\node (H) at (6,0) {$1_\mathrm{A^\prime}$};
-\node (I) at (5,-0.5) {$!_{1_{\mathrm{A^\prime}}} \in F^\prime(1_{\mathrm{A^\prime}})$};
-\node (D) at (1,-0.5) {$E(!_{1_\mathrm{A}}) \in F^\prime(H(1_\mathrm{A}))$};
+where $1_\mathsf{A}$ is the monoidal unit of the finitely cocartesian category $\mathsf{A}$. The image of this horizontal 1-cell under $\mathbb{H}$ is given by:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$H(1_\mathsf{A})$};
+\node (B) at (1,0) {$H(1_\mathsf{A})$};
+\node (C) at (2,0) {$H(1_\mathsf{A})$};
+%\node (E) at (3,0) {$=$};
+%\node (F) at (4,0) {$1_\mathsf{A^\prime}$};
+%\node (G) at (5,0) {$1_\mathsf{A^\prime}$};
+%\node (H) at (6,0) {$1_\mathsf{A^\prime}$};
+%\node (I) at (5,-0.5) {$!_{1_{\mathsf{A^\prime}}} \in F^\prime(1_{\mathsf{A^\prime}})$};
+\node (D) at (1,-0.5) {$E(!_{1_\mathsf{A}}) \in F^\prime(H(1_\mathsf{A}))$};
 \path[->,font=\scriptsize,>=angle 90]
 (A) edge node[above]{$1$} (B)
-(C) edge node[above]{$1$} (B)
-(F) edge node[above]{$1$} (G)
-(H) edge node[above]{$1$} (G);
-\end{tikzpicture}
-\]
-since $H$ preserves finite colimits.
-We then have a 2-isomorphism in $\mathbb{F^\prime}\textnormal{Cospan}(\mathrm{A^\prime})$ given by: $$\mu \colon 1_{\mathbb{F^\prime}\textnormal{Cospan}(\mathrm{A^\prime})_1} \to \mathbb{H}(1_{\mathbb{F}\textnormal{Cospan}(\mathrm{A})_1})$$
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$1_{\mathrm{A^\prime}}$};
-\node (A') at (0,-0.5) {$H(1_\mathrm{A})$};
-\node (B) at (1.5,0.5) {$1_{\mathrm{A^\prime}}$};
-\node (C) at (3,0.5) {$1_{\mathrm{A^\prime}}$};
-\node (C') at (3,-0.5) {$H(1_\mathrm{A})$};
-\node (D) at (1.5,-0.5) {$H(1_\mathrm{A})$};
-\node (E) at (4.5,0.5) {$!_{1_\mathrm{A^\prime}} \in F^\prime(1_\mathrm{A^\prime})$};
-\node (F) at (4.5,-0.5) {$E(!_{1_\mathrm{A}}) \in F^\prime(H(1_\mathrm{A}))$};
+(C) edge node[above]{$1$} (B);
+%(F) edge node[above]{$1$} (G)
+%(H) edge node[above]{$1$} (G);
+\end{tikzpicture}
+\]
+as $H$ preserves finite colimits.
+We then have a 2-isomorphism in $F'\mathbb{C}\textnormal{sp}$ given by: $$\mu \colon 1_{F'\mathbb{C}\textnormal{sp}_1} \to \mathbb{H}(1_{F\mathbb{C}\textnormal{sp}_1})$$
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0.5) {$1_{\mathsf{A^\prime}}$};
+\node (A') at (0,-0.5) {$H(1_\mathsf{A})$};
+\node (B) at (1.5,0.5) {$1_{\mathsf{A^\prime}}$};
+\node (C) at (3,0.5) {$1_{\mathsf{A^\prime}}$};
+\node (C') at (3,-0.5) {$H(1_\mathsf{A})$};
+\node (D) at (1.5,-0.5) {$H(1_\mathsf{A})$};
+\node (E) at (4.5,0.5) {$!_{1_\mathsf{A^\prime}} \in F^\prime(1_\mathsf{A^\prime})$};
+\node (F) at (4.5,-0.5) {$E(!_{1_\mathsf{A}}) \in F^\prime(H(1_\mathsf{A}))$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-together with the morphism $\iota_\mu \colon F^\prime(\kappa)(!_{1_\mathrm{A^\prime}}) \to E(!_{1_\mathrm{A}})$ in $F^\prime(H(1_\mathrm{A}))$. The following square then commutes: 
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$1_\mathrm{A^\prime} \otimes \mathbb{H}(M)$};
-\node (B) at (2.5,0) {$\mathbb{H}(1_\mathrm{A}) \otimes \mathbb{H}(M)$};
+together with the morphism $\iota_\mu \colon F^\prime(\kappa)(!_{1_\mathsf{A^\prime}}) \to E(!_{1_\mathsf{A}})$ in $F^\prime(H(1_\mathsf{A}))$. The following square then commutes: 
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$1_\mathsf{A^\prime} \otimes \mathbb{H}(M)$};
+\node (B) at (2.5,0) {$\mathbb{H}(1_\mathsf{A}) \otimes \mathbb{H}(M)$};
 \node (C) at (0,-1) {$\mathbb{H}(M)$};
-\node (D) at (2.5,-1) {$\mathbb{H}(1_\mathrm{A} + M)$};
+\node (D) at (2.5,-1) {$\mathbb{H}(1_\mathsf{A} + M)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-where we have abbreviated the monoidal units of $\mathbb{F}\textnormal{Cospan}(\mathrm{A})_1$ and $\mathbb{F^\prime}\textnormal{Cospan}(\mathrm{A^\prime})_1$ as $1_\mathrm{A}$ and $1_\mathrm{A^\prime}$, respectively.
+where we have abbreviated the monoidal units of $F\mathbb{C}\textnormal{sp}_1$ and $F'\mathbb{C}\textnormal{sp}_1$ as $1_\mathsf{A}$ and $1_\mathsf{A^\prime}$, respectively.
 The diagram of corresponding decorations is given by:
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$F^\prime(\ell)(!_{1_\mathrm{A^\prime}} + E(d))$};
+\node (A) at (0,0.5) {$F^\prime(\ell)(!_{1_\mathsf{A^\prime}} + E(d))$};
 \node (B) at (0,-0.5) {$E(d)$};
-\node (A') at (4,0.5) {$F^\prime(H(\ell^\prime) \kappa)(E(!_{1_\mathrm{A}})+E(d))$};
-\node (B') at (4,-0.5) {$F^\prime(H(\ell^\prime))(E(!_{1_\mathrm{A}} + d))$};
+\node (A') at (4,0.5) {$F^\prime(H(\ell^\prime) \kappa)(E(!_{1_\mathsf{A}})+E(d))$};
+\node (B') at (4,-0.5) {$F^\prime(H(\ell^\prime))(E(!_{1_\mathsf{A}} + d))$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-where $$F^\prime(\ell)(!_{1_\mathrm{A^\prime}} + E(d))=F^\prime(H(\ell^\prime)\kappa(\mu+1))(!_{1_\mathrm{A^\prime}} + E(d)).$$ The other square involving the right unitors $r$ and $r^\prime$ is similar.
+where $$F^\prime(\ell)(!_{1_\mathrm{A^\prime}} + E(d))=F^\prime(H(\ell^\prime)\kappa(\mu+1))(!_{1_\mathrm{A^\prime}} + E(d))$$ since the corresponding square involving left unitors for the symmetric lax monoidal pseudofunctor $E \colon \mathbf{Cat} \to \mathbf{Cat}$ commutes.
+The other square involving the right unitors $r$ and $r^\prime$ is similar.
 Note that because $\mu$ and $\mu_{(\_ , \_)}$ are both isomorphisms, the symmetric monoidal double functor $\mathbb{H}$ is strong.
+
+\begin{thm}
+Given two finitely cocomplete categories $\mathsf{A}$ and $\mathsf{A}'$ and two symmetric lax monoidal pseudofunctors $F \colon \mathsf{A} \to \mathbf{Cat}$ and $F' \colon \mathsf{A}' \to \mathbf{Cat}$, a map $\mathbb{H} \colon F\mathbb{C}\textnormal{sp} \to F'\mathbb{C}\textnormal{sp}$ is given by a pair $(H,E)$ where $H \colon \mathsf{A} \to \mathsf{A}'$ is a finite colimit preserving functor and a symmetric lax monoidal pseudofunctor $E \colon \mathbf{Cat} \to \mathbf{Cat}$ that make the following square commute.
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$\mathsf{A}$};
+\node (B) at (1,0) {$\mathbf{Cat}$};
+\node (C) at (0,-1) {$\mathsf{A^\prime}$};
+\node (D) at (1,-1) {$\mathbf{Cat}$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$F$} (B)
+(A) edge node[left]{$H$} (C)
+(B) edge node[right]{$E$} (D)
+(C) edge node[above]{$F^\prime$} (D);
+\end{tikzpicture}
+\]
+\end{thm}
 
@@
 %\newpage
-
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$1$};
-\node (A') at (0,-0.5) {$F^\prime(1_\mathrm{A^\prime})$};
-\node (B) at (1.5,0.5) {$F(1_\mathrm{A})$};
-\node (C) at (3.5,0.5) {$F(c)$};
-\node (C') at (3.5,-0.5) {$F^\prime(H(c))=E(F(c))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$\phi$} (B)
-(B) edge node[above]{$F(!_c)$} (C)
-(A) edge node[left]{$\Phi$} (A')
-(C) edge node [left] {$$} (C')
-(A') edge node [above]{$F^\prime(!_{H(c)})$} (C');
-\end{tikzpicture}
-\]
-\newline
-\textbf{show symmetric monoidal, make sure using all assumptions on the functors H and E}
 
@@
 \section{An equivalence of symmetric monoidal double categories} \label{EquivDoubleCats}
-In this section we prove that two different frameworks which utilize symmetric monoidal double categories, namely decorated cospans and `structured cospans', are equivalent under the conditions required from the previous section that allow for a left adjoint $L \colon \mathrm{A} \to \mathrm{X}$ to be obtained from a symmetric lax monoidal pseudofunctor $F \colon \mathrm{A} \to \mathbf{Cat}$.
-The double category version of decorataed cospans is given in Section \ref{DecCospansDoublecat}.
-The other framework also utilizing symmetric monoidal double categories due to the first two authors and which goes by the name of `structured cospans', is explained below.
+In this section we prove that two different frameworks which utilize symmetric monoidal double categories, namely decorated cospans and `structured cospans', are equivalent under the conditions required from the previous section that allow for a left adjoint $L \colon \mathsf{A} \to \mathsf{X}$ to be obtained from a symmetric lax monoidal pseudofunctor $F \colon \mathsf{A} \to \mathbf{Cat}$.
+The double category version of decorataed cospans is given in Section \ref{DecCospansDoubleCat}.
+The other framework also utilizing symmetric monoidal double categories due to the first two authors and which goes by the name of `structured cospans', is introduced below.
 Once again following the notation of Shulman \cite{Shul2}, given a double category $\mathbb{A}$, we write $_f \mathbb{A}_g(M,N)$ for the set of 2-morphisms in $\mathbb{A}$ of the form:
@@
 \end{thm}
+
 \begin{prop}
@@
 \end{prop}
-Our next goal is to show that the symmetric monoidal double category $\mathbb{F}\textnormal{Cospan}(\mathrm{A})$ of Section \ref{DecCospansDoublecat} is equivalent as a symmetric monoidal double category to the symmetric monoidal double category $_L \mathbb{C}\textnormal{sp}(\mathrm{X})$ obtained using structured cospans.
+
+Our next goal is to show that the symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$ of Section \ref{DecCospansDoubleCat} is equivalent as a symmetric monoidal double category to the symmetric monoidal double category $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$ obtained using structured cospans.
 
 \begin{thm}\label{SC}
-Given a category $\mathrm{X}$ with finite colimits and a category $\mathrm{A}$ with finite coproducts and a finite coproduct preserving functor $L \colon \mathrm{A} \to \mathrm{X}$ with $\mathrm{A}$ and $\mathrm{X}$ regarded as cocartesian monoidal categories, there exists a symmetric monoidal double category $_L \mathbb{C}\textnormal{sp}(\mathrm{X})$ which has:
+Given a category $\mathsf{X}$ with finite colimits and a category $\mathsf{A}$ with finite coproducts and a finite coproduct preserving functor $L \colon \mathsf{A} \to \mathsf{X}$ with $\mathsf{A}$ and $\mathsf{X}$ regarded as cocartesian monoidal categories, there exists a symmetric monoidal double category $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$ which has:
 \begin{enumerate}
-\item{objects given by objects of $\mathrm{A}$,}
-\item{vertical 1-morphisms given by morphisms of $\mathrm{A}$,}
-\item{horizontal 1-cells given by cospans of $\mathrm{X}$ of the form:
+\item{objects given by objects of $\mathsf{A}$,}
+\item{vertical 1-morphisms given by morphisms of $\mathsf{A}$,}
+\item{horizontal 1-cells given by cospans of $\mathsf{X}$ of the form:
 \[
@@
 and}
-\item{2-morphisms given by maps of cospans of $\mathrm{X}$ of the form:
+\item{2-morphisms given by maps of cospans of $\mathsf{X}$ of the form:
 \[
@@
 \]
-Composition of horizontal 1-cells and 2-morphisms is given by pushouts in $\mathrm{X}$ and tensoring of objects is under binary coproducts in $\mathrm{A}$.
+Composition of horizontal 1-cells and 2-morphisms is given by pushouts in $\mathsf{X}$ and tensoring of objects is under binary coproducts in $\mathsf{A}$.
 }
@@
 \end{proof}
-In the previous section, we started with a symmetric lax monoidal pseudofunctor $F \colon \mathrm{A} \to \mathbf{Cat}$ and created a symmetric monoidal double category $\mathbb{F}\textnormal{Cospan}(\mathrm{A})$ which has:
+In the previous section, we started with a symmetric lax monoidal pseudofunctor $F \colon \mathsf{A} \to \mathbf{Cat}$ and created a symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$ which has:
 \begin{enumerate}
-\item{objects of $\mathrm{A}$ as objects,}
-\item{morphisms of $\mathrm{A}$ as vertical 1-morphisms,}
+\item{objects of $\mathsf{A}$ as objects,}
+\item{morphisms of $\mathsf{A}$ as vertical 1-morphisms,}
 \item{horizontal 1-cells are given by $F$-decorated cospans, which are pairs:
@@
 and}
-\item{2-morphisms are given by maps of cospans in $\mathrm{A}$:
+\item{2-morphisms are given by maps of cospans in $\mathsf{A}$:
 \[
@@
 \end{proof}
-Using a result of Shulman \cite{Shul}, each of the isofibrant symmetric monoidal double categories $\mathbb{F}\textnormal{Cospan}(\mathrm{A})$ and $_L \mathbb{C}\textnormal{sp}(\mathrm{X})$ give rise to underlying symmetric monoidal bicategories, namely $\mathbb{F}\textnormal{Cospan}(\mathrm{A})$ induces a symmetric monoidal bicategory $H(\mathbb{F}\textnormal{Cospan}(\mathrm{A}))$ which has:
+Using a result of Shulman \cite{Shul}, each of the isofibrant symmetric monoidal double categories $F\mathbb{C}\textnormal{sp}$ and $_L \mathbb{C}\textnormal{sp}(\mathrm{X})$ give rise to underlying symmetric monoidal bicategories, namely $F\mathbb{C}\textnormal{sp}$ induces a symmetric monoidal bicategory $F\mathbf{Csp} \coloneqq H(F\mathbb{C}\textnormal{sp})$ which has:
 \begin{enumerate}
-\item{objects as those of $\mathrm{A}$,}
-\item{morphisms as horizontal 1-cells of $\mathbb{F}\textnormal{Cospan}(\mathrm{A})$, and}
-\item{2-morphisms as globular 2-morphisms of $\mathbb{F}\textnormal{Cospan}(\mathrm{A})$.}
+\item{objects as those of $\mathsf{A}$,}
+\item{morphisms as horizontal 1-cells of $F\mathbb{C}\textnormal{sp}$, and}
+\item{2-morphisms as globular 2-morphisms of $F\mathbb{C}\textnormal{sp}$.}
 \end{enumerate} 
-Likewise, $_L \mathbb{C}\textnormal{sp}(\mathrm{X})$ induces a symmetric monoidal bicategory $H( {_L \mathbb{C}\textnormal{sp}(\mathrm{X})})$ which has:
+Likewise, $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$ induces a symmetric monoidal bicategory $H( {_L \mathbb{C}\textnormal{sp}(\mathsf{X})})$ which has:
 \begin{enumerate}
-\item{objects as those of $\mathrm{A}$,}
-\item{morphisms as horizontal 1-cells of $_L \mathbb{C}\textnormal{sp}(\mathrm{X})$, and}
-\item{2-morphisms as globular 2-morphisms of $_L \mathbb{C}\textnormal{sp}(\mathrm{X})$.}
+\item{objects as those of $\mathsf{A}$,}
+\item{morphisms as horizontal 1-cells of $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$, and}
+\item{2-morphisms as globular 2-morphisms of $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$.}
 \end{enumerate}
@@
 \begin{cor}
-The bicategories $H(\mathbb{F}\textnormal{Cospan}(\mathrm{A}))$ and $H( {_L \mathbb{C}\textnormal{sp}(\mathrm{X})})$ are biequivalent.
+The bicategories $F\mathbf{Csp}$ and $H( {_L \mathbb{C}\textnormal{sp}(\mathsf{X})})$ are biequivalent.
 \end{cor}
@@
 The next three examples which take on more of an applied flavor, consists of electrical circuits, Markov processes and Petri nets.
-Each of these has been studied extensively by the first author and others by way of `black-boxing'.
+Each of these has been studied extensively by the first author and others by way of `black-boxing' \cite{BCR,BF,BFP,BM,BP}.
 Black-boxing is a way of interpreting the behavior of an open system, that is, a system with prescribed inputs and outputs such as the terminals of an electrical circuit, by observing the activity at the inputs and the outputs.
-The semantics of the activity at an open system's inputs and outputs is typically described in a category such as $\mathrm{LinRel}$ of finite dimensonal vector spaces and linear relations.
-Thus, in each case, black-boxing results in functors such as: $$\blacksquare_1 \colon \mathrm{Circ} \to \mathrm{LinRel}$$ $$\blacksquare_2 \colon \mathrm{Mark} \to \mathrm{LinRel}$$ $$\blacksquare_3 \colon \mathrm{Petri} \to \mathrm{LinRel}.$$ Each of these black-boxing functors also possess other convenient properties such as being symmetric monoidal.
+The semantics of the activity at an open system's inputs and outputs is typically described in a category such as $\mathsf{LinRel}$ of finite dimensonal vector spaces and linear relations.
+Thus, in each case, black-boxing results in functors such as: $$\blacksquare_1 \colon \mathsf{Circ} \to \mathsf{LinRel}$$ $$\blacksquare_2 \colon \mathsf{Mark} \to \mathsf{LinRel}$$ $$\blacksquare_3 \colon \mathsf{Petri} \to \mathsf{LinRel}.$$ Each of these black-boxing functors also possess other convenient properties such as being symmetric monoidal.
 The first two of these were first done using Fong's theory of decorated cospans and then extended by the first two authors using structured cospans.
-The last two of these were also extended by being realized as double functors between double categories.
-\textbf{Make this better...}
+The last two of these were also extended by being realized as double functors between double categories \cite{BC,BM}.
 \subsection{Graphs}
-As a first example that was also mentioned in the introduction, let $L \colon \mathrm{Set} \to \mathrm{Graph}$ be the functor that assigns to a set $N$ the \emph{discrete graph} on $N$ which is the edgeless graph $L(N)$ with no edges and $N$ as its set of vertices.
-Both $\mathrm{Set}$ and $\mathrm{Graph}$ are cocartesian monoidal and the functor $L \colon \mathrm{Set} \to \mathrm{Graph}$ is left adjoint to the forgetful functor $R \colon \mathrm{Graph} \to \mathrm{Set}$ which assigns to a graph $G$ its underlying set of vertices $U(G)$.
-Using structured cospans and appealing to Theorem \ref{SC}, we get a symmetric monoidal double category $_L \mathbb{C}\textnormal{sp}(\mathrm{Graph})$ which has:
+As a first example that was also mentioned in the introduction, let $L \colon \mathsf{Set} \to \mathsf{Graph}$ be the functor that assigns to a set $N$ the \emph{discrete graph} on $N$ which is the edgeless graph $L(N)$ with no edges and $N$ as its set of vertices.
+Both $\mathsf{Set}$ and $\mathsf{Graph}$ are cocartesian monoidal and the functor $L \colon \mathsf{Set} \to \mathsf{Graph}$ is left adjoint to the forgetful functor $R \colon \mathsf{Graph} \to \mathsf{Set}$ which assigns to a graph $G$ its underlying set of vertices $U(G)$.
+Using structured cospans and appealing to Theorem \ref{SC}, we get a symmetric monoidal double category $_L \mathbb{C}\textnormal{sp}(\mathsf{Graph})$ which has:
 \begin{enumerate}
@@
 We can obtain a similar symmetric monoidal double category using decorated cospans.
-Let $F \colon \mathrm{Set} \to \mathrm{Cat}$ be the symmetric lax monoidal pseudofunctor that assigns to a set $N$ the \emph{category} of all graph structures whose underlying set of vertices is $N$.
-Using Theorem \ref{DC}, we then obtain a symmetric monoidal double category $\mathbb{F}\textnormal{Cospan}(\mathrm{Set})$ which has:
+Let $F \colon \mathsf{Set} \to \mathsf{Cat}$ be the symmetric lax monoidal pseudofunctor that assigns to a set $N$ the \emph{category} of all graph structures whose underlying set of vertices is $N$.
+Using Theorem \ref{DC}, we then obtain a symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$ which has:
 \begin{enumerate}
@@
 \end{enumerate}
-We thus have two symmetric monoidal double categories: $_L \mathbb{C}\textnormal{sp}(\mathrm{Graph})$ obtained from structured cospans and $\mathbb{F}\textnormal{Cospan}(\mathrm{Set})$ obtained from decorated cospans.
-Both of these double categories have $\mathrm{Set}$ as their categories of objects, open graphs as horizontal 1-cells and maps of open graphs as 2-morphisms, and by Theorem \ref{Equiv}, we have an equivalence of symmetric monoidal double categories $$_L \mathbb{C}\textnormal{sp}(\mathrm{Graph}) \sim \mathbb{F}\textnormal{Cospan}(\mathrm{Set}).$$
+We thus have two symmetric monoidal double categories: $_L \mathbb{C}\textnormal{sp}(\mathsf{Graph})$ obtained from structured cospans and $F\mathbb{C}\textnormal{sp}$ obtained from decorated cospans.
+Both of these double categories have $\mathsf{Set}$ as their categories of objects, open graphs as horizontal 1-cells and maps of open graphs as 2-morphisms, and by Theorem \ref{Equiv}, we have an equivalence of symmetric monoidal double categories $$_L \mathbb{C}\textnormal{sp}(\mathsf{Graph}) \sim F\mathbb{C}\textnormal{sp}.$$
 
@@
 In a previous work \cite{BP}, Fong and the first author used decorated cospans to construct a symmetric monoidal category of `open passive linear circuits'.
-Roughly speaking, given a field $k$, a passive linear circuit is given by a `$k$-graph' which is a diagram in $\mathrm{FinSet}$ of the form:
+Roughly speaking, given a field $k$, a passive linear circuit is given by a `$k$-graph' which is a diagram in $\mathsf{FinSet}$ of the form:
 \[
@@
 
-Let $\mathrm{Graph}_k$ be the category whose objects are given by $k$-graphs and morphisms by morphisms of $k$-graphs, where a morphism of $k$-graphs is given by a pair of functions $f \colon E \to E^\prime$ and $g \colon V \to V^\prime$ between the edge sets and vertex sets, respectively, of two $k$-graphs that respect the source and target functions of each.
-In a previous work introducing structured cospans, the first two authors showed that the category $\mathrm{Graph}_k$ has finite colimits \cite{BC2}.
-We can then obtain a double category of open passive linear circuits by defining a left adjoint $L \colon \mathrm{Set} \to \mathrm{Graph}_k$ that assigns to a set $V$ the discrete passive linear circuit $L(V)$ given by passive linear circuit with $V$ as its set of vertices and no edges.
-The resulting symmetric monoidal double category $_L \mathbb{C}\textnormal{sp}(\mathrm{Graph}_k)$ has:
+Let $\mathsf{Graph}_k$ be the category whose objects are given by $k$-graphs and morphisms by morphisms of $k$-graphs, where a morphism of $k$-graphs is given by a pair of functions $f \colon E \to E^\prime$ and $g \colon V \to V^\prime$ between the edge sets and vertex sets, respectively, of two $k$-graphs that respect the source and target functions of each.
+In a previous work introducing structured cospans, the first two authors showed that the category $\mathsf{Graph}_k$ has finite colimits \cite{BC2}.
+We can then obtain a double category of open passive linear circuits by defining a left adjoint $L \colon \mathsf{Set} \to \mathsf{Graph}_k$ that assigns to a set $V$ the discrete passive linear circuit $L(V)$ given by passive linear circuit with $V$ as its set of vertices and no edges.
+The resulting symmetric monoidal double category $_L \mathbb{C}\textnormal{sp}(\mathsf{Graph}_k)$ has:
 \begin{enumerate}
@@
 \item{functions as vertical 1-morphisms,}
-\item{open pass linear circuits as horizontal 1-cells
+\item{open passive linear circuits as horizontal 1-cells
 \[
@@
 \end{enumerate}
-We can also obtain a similar double category using decorated cospans: define a pseudofunctor $F \colon \mathrm{FinSet} \to \mathrm{Cat}$ that assigns to a finite set $V$ the category of all $k$-graph structures on the finite set $V$ and to a function $f \colon V \to V^\prime$ the corresponding functor $F(f) \colon F(V) \to F(V^\prime)$ between decoration categories.
-Both categories $\mathrm{FinSet}$ and $\mathrm{Cat}$ are symmetric monoidal and the pseudofunctor $F \colon \mathrm{FinSet} \to \mathrm{Cat}$ is symmetric lax monoidal, as given a $k$-graph structure on a finite set $V_1$ denoted by an element $K_1 \in F(V_1)$ and a $k$-graph structure on a finite set $V_2$ denoted by an element $K_2 \in F(V_2)$, we can consider the $k$-graph structures simultaneously as a single graph structure $\phi_{V_1,V_2}(K_1,K_2)$ on the finite set $V_1+V_2$.
-Thus we get a family of natural transformations $$\phi_{V_1,V_2} \colon F(V_1) \times F(V_2) \to F(V_1+V_2)$$ as well as a morphism $\phi \colon 1_{\mathrm{Graph}_k} \to F(\emptyset)$ which together satisfy coherence conditions of a monoidal functor.
+We can also obtain a similar double category using decorated cospans: define a pseudofunctor $F \colon \mathsf{FinSet} \to \mathbf{Cat}$ that assigns to a finite set $V$ the category of all $k$-graph structures on the finite set $V$ and to a function $f \colon V \to V^\prime$ the corresponding functor $F(f) \colon F(V) \to F(V^\prime)$ between decoration categories.
+Both categories $\mathsf{FinSet}$ and $\mathbf{Cat}$ are symmetric monoidal and the pseudofunctor $F \colon \mathsf{FinSet} \to \mathbf{Cat}$ is symmetric lax monoidal, as given a $k$-graph structure on a finite set $V_1$ denoted by an element $K_1 \in F(V_1)$ and a $k$-graph structure on a finite set $V_2$ denoted by an element $K_2 \in F(V_2)$, we can consider the $k$-graph structures simultaneously as a single graph structure $\phi_{V_1,V_2}(K_1,K_2)$ on the finite set $V_1+V_2$.
+Thus we get a family of natural transformations $$\phi_{V_1,V_2} \colon F(V_1) \times F(V_2) \to F(V_1+V_2)$$ as well as a morphism $\phi \colon 1_{\mathsf{Graph}_k} \to F(\emptyset)$ which together satisfy the coherence conditions of a monoidal functor.
 The braiding is also clear as the following diagram commutes:
@@
 \]
-Thus the pseudofunctor $F$ is symmetric lax monoidal and so by Theorem \ref{DC} we get a symmetric monoidal double category $\mathbb{F}\textnormal{Cospan}(\mathrm{FinSet})$ which has:
+Thus the pseudofunctor $F$ is symmetric lax monoidal and so by Theorem \ref{DC} we get a symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$ which has:
 \begin{enumerate}
@@
 \end{enumerate}
-These two double categories $_L \mathbb{C}\textnormal{sp}(\mathrm{Graph}_k)$ and $\mathbb{F}\textnormal{Cospan}(\mathrm{FinSet})$ are equivalent by Theorem \ref{Equiv}.
+These two double categories $_L \mathbb{C}\textnormal{sp}(\mathsf{Graph}_k)$ and $F\mathbb{C}\textnormal{sp}$ are equivalent by Theorem \ref{Equiv}.
 
@@
 In another previous work \cite{BFP}, Fong, Pollard and the first author used decorated cospans to construct a symmetric monoidal category of `open Markov processes'.
-In this framework, a Markov process on a finite set $N$ is given by a diagram in $\mathrm{Set}$:
+In this framework, a Markov process on a finite set $N$ is given by a diagram in $\mathsf{Set}$:
 \[
@@
 
-Fong, Pollard and the first author then add extra structure to open Markov processes such as populations at each node to obtain a symmetric monoidal category $\mathrm{DetlBalMark}$ of open Markov processes in `detailed balance' and then construct a black box functor $\blacksquare \colon \mathrm{DetBalMark} \to \mathrm{LinRel}$ that describes the steady state behavior of an open Markov process in detailed balance.
-On the way to doing this, one of the categories they construct using Fong's decorated cospan machinery is a symmetric monoidal category $\mathrm{Mark}$ which has:
+Fong, Pollard and the first author then add extra structure to open Markov processes such as populations at each node to obtain a symmetric monoidal category $\mathsf{DetlBalMark}$ of open Markov processes in `detailed balance' and then construct a black box functor $\blacksquare \colon \mathsf{DetBalMark} \to \mathsf{LinRel}$ that describes the steady state behavior of an open Markov process in detailed balance.
+On the way to doing this, one of the categories they construct using Fong's decorated cospan machinery is a symmetric monoidal category $\mathsf{Mark}$ which has:
 \begin{enumerate}
@@
 \end{enumerate}
-This is done using a symmetric lax monoidal functor $F \colon \mathrm{FinSet} \to \mathrm{Set}$ which assigns to each finite set $N$ the (large) set of all Markov processes on $N$ as defined above.
-Viewing this functor $F$ as now a symmetric lax monoidal pseudofunctor $F \colon \mathrm{FinSet} \to \mathrm{Cat}$ that assigns to a finite set $N$ the \emph{category} $F(N)$ of all Markov processes on $N$, we then get by Theorem \ref{DC} a symmetric monoidal double category $\mathbb{F}\textnormal{Cospan}(\mathrm{FinSet})$ which has:
+This is done using a symmetric lax monoidal functor $F \colon \mathsf{FinSet} \to \mathsf{Set}$ which assigns to each finite set $N$ the (large) set of all Markov processes on $N$ as defined above.
+Viewing this functor $F$ as now a symmetric lax monoidal pseudofunctor $F \colon \mathsf{FinSet} \to \mathbf{Cat}$ that assigns to a finite set $N$ the \emph{category} $F(N)$ of all Markov processes on $N$, we then get by Theorem \ref{DC} a symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$ which has:
 \begin{enumerate}
@@
 \end{enumerate}
-A symmetric monoidal double category of open Markov processes can also be obtained using structured cospans by defining a functor $L \colon \mathrm{FinSet} \to \mathrm{Mark}$ which assigns to a finite set $N$ the discrete Markov process $L(N)$ with no edges and to a function $f \colon N \to N^\prime$ the induced map of discrete Markov processes.
-Both categories $\mathrm{FinSet}$ and $\mathrm{Mark}$ have finite colimits and the functor $L$ is left adjoint to the forgetful functor $R \colon \mathrm{Mark} \to \mathrm{FinSet}$ which maps a Markov process to its underlying finite set of states.
-By Theorem \ref{SC}, we get a symmetric monoidal double category $_L \mathbb{C}\textnormal{sp}(\mathrm{Mark})$ which has:
+A symmetric monoidal double category of open Markov processes can also be obtained using structured cospans by defining a functor $L \colon \mathsf{FinSet} \to \mathsf{Mark}$ which assigns to a finite set $N$ the discrete Markov process $L(N)$ with no edges and to a function $f \colon N \to N^\prime$ the induced map of discrete Markov processes.
+Both categories $\mathsf{FinSet}$ and $\mathsf{Mark}$ have finite colimits and the functor $L$ is left adjoint to the forgetful functor $R \colon \mathsf{Mark} \to \mathsf{FinSet}$ which maps a Markov process to its underlying finite set of states.
+By Theorem \ref{SC}, we get a symmetric monoidal double category $_L \mathbb{C}\textnormal{sp}(\mathsf{Mark})$ which has:
 \begin{enumerate}
@@
 \end{enumerate}
-The two double categories $\mathbb{F}\textnormal{Cospan}(\mathrm{FinSet})$ and $_L \mathbb{C} \textnormal{sp}(\mathrm{Mark})$ are equivalent by Theorem \ref{Equiv}.
+The two double categories $F\mathbb{C}\textnormal{sp}$ and $_L \mathbb{C} \textnormal{sp}(\mathsf{Mark})$ are equivalent by Theorem \ref{Equiv}.
 
@@
 In a previous work, Master and the first author used structured cospans to obtain a symmetric monoidal double category of `open Petri nets'.
-A Petri net is given by a diagram in $\mathrm{Set}$ of the form:
+A Petri net is given by a diagram in $\mathsf{Set}$ of the form:
 \[
@@
 Each set of species $S$ gives rise to a discrete Petri net $L(S)$ with $S$ as its set of species and no transitions.
-Master and the first author show the existence of a left adjoint $L \colon \mathrm{Set} \to \mathrm{Petri}$ where $\mathrm{Petri}$ is the category whose objects are Petri nets and whose `morphisms are morphisms of Petri nets'.
-They also show that $\mathrm{Petri}$ has finite colimits and thus using Theorem \ref{SC} obtain a symmetric monoidal double category $\mathbb{O}\mathbf{pen}(\mathrm{Petri})$ of open Petri nets which has:
+Master and the first author show the existence of a left adjoint $L \colon \mathsf{Set} \to \mathsf{Petri}$ where $\mathsf{Petri}$ is the category whose objects are Petri nets and whose `morphisms are morphisms of Petri nets'.
+They also show that $\mathsf{Petri}$ has finite colimits and thus using Theorem \ref{SC} obtain a symmetric monoidal double category $\mathbb{O}\mathbf{pen}(\mathrm{Petri})$ of open Petri nets which has:
 \begin{enumerate}
@@
 \item{vertical 1-morphisms given by functions,}
-\item{horizontal 1-cells as open Petri nets which are given by cospans in $\mathrm{Petri}$ of the form:
+\item{horizontal 1-cells as open Petri nets which are given by cospans in $\mathsf{Petri}$ of the form:
 \[
@@
 and}
-\item{2-morphisms as maps of cospans in $\mathrm{Petri}$ of the form:
+\item{2-morphisms as maps of cospans in $\mathsf{Petri}$ of the form:
 \[
@@
 \end{enumerate}
-We can also obtain a similar double category using decorated cospans: define a pseudofunctor $F \colon \mathrm{Set} \to \mathrm{Cat}$ where given a set $s$, $F(s)$ is the (large) category of all Petri net structures with $s$ as its set of species.
-This functor $F$ is symmetric lax monoidal as both $(\mathrm{Set},+,\emptyset)$ and $(\mathrm{Cat},\times,1)$ are symmetric monoidal and given Petri nets $P \in F(s)$ and $P^\prime \in F(s^\prime)$, we can place them side by side and consider them together as a single Petri net $P+P^\prime \in F(s+s^\prime)$ with set of species $s+s^\prime$, and thus we have natural transformations $\phi_{s,s^\prime} \colon F(s) \times F(s^\prime) \to F(s+s^\prime)$ for any two sets $s$ and $s^\prime$.
-The other structure morphism between monoidal units $\phi \colon 1_{\mathrm{Petri}} \to F(\emptyset)$ is defined by the unique morphism from the empty Petri net with the empty set for species to the only possible Petri net on the empty set, which is also the empty Petri net.
+We can also obtain a similar double category using decorated cospans: define a pseudofunctor $F \colon \mathsf{Set} \to \mathbf{Cat}$ where given a set $s$, $F(s)$ is the category of all Petri net structures with $s$ as its set of species.
+This pseudofunctor $F$ is symmetric lax monoidal as both $(\mathsf{Set},+,\emptyset)$ and $(\mathbf{Cat},\times,1)$ are symmetric monoidal and given Petri nets $P \in F(s)$ and $P^\prime \in F(s^\prime)$, we can place them side by side and consider them together as a single Petri net $P+P^\prime \in F(s+s^\prime)$ with set of species $s+s^\prime$, and thus we have natural transformations $\phi_{s,s^\prime} \colon F(s) \times F(s^\prime) \to F(s+s^\prime)$ for any two sets $s$ and $s^\prime$.
+The other structure morphism between monoidal units $\phi \colon 1_{\mathsf{Petri}} \to F(\emptyset)$ is defined by the unique morphism from the empty Petri net with the empty set forits set of species to the only possible Petri net on the empty set, which is also the empty Petri net.
 All of the diagrams that are required to commute are straightforward.
-Using Theorem \ref{DC}, we obtain a symmetric monoidal double category $\mathbb{F}\textnormal{Cospan}(\mathrm{Set})$ which has:
+Using Theorem \ref{DC}, we obtain a symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$ which has:
 \begin{enumerate}
@@
 and}
-\item{2-morphisms as maps of cospans in $\mathrm{Set}$:
+\item{2-morphisms as maps of cospans in $\mathsf{Set}$:
 \[
@@
 \]
-together with a morphism of Petri nets $\iota \colon F(h)(P) \to P^\prime$ in $F(Z^\prime)$.}
+together with a morphism of Petri nets $\iota \colon F(h)(P_1) \to P_2$ in $F(Z_2)$.}
 \end{enumerate}
-Thus we have a symmetric monoidal double category $\mathbb{O}\mathbf{pen}(\mathrm{Petri})$ of open Petri nets obtained from structured cospans and a symmetric monoidal double category $\mathbb{F}\textnormal{Cospan}(\mathrm{Set})$ of open Petri nets obtain from decorated cospans, and of course, we have an equivalence $\mathbb{O}\mathbf{pen}(\mathrm{Petri}) \sim \mathbb{F}\textnormal{Cospan}(\mathrm{Set})$ of symmetric monoidal double categories by Theorem \ref{Equiv}.
+Thus we have a symmetric monoidal double category $\mathbb{O}\mathbf{pen}(\mathrm{Petri})$ of open Petri nets obtained from structured cospans and a symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$ of open Petri nets obtain from decorated cospans, and of course, we have an equivalence $\mathbb{O}\mathbf{pen}(\mathrm{Petri}) \sim F\mathbb{C}\textnormal{sp}$ of symmetric monoidal double categories by Theorem \ref{Equiv}.
 

### 2019-01-09 EquivCompFrameworks_20180911kc.tex
one more small change - the notation should be consistent now
Alternative way of obtaining double equivalence via pair of double natural isomorphisms?

@@
 \begin{itemize}
-\item Fix notation for structured and decorated cospans.
 \item {\chris I think structured cospans should be introduced/recalled way earlier! This is a paper that compares the two,
@@
 \end{cor}
+
 \textbf{Is this biequivalnce symmetric monoidal? Probably}
-
-We can also define the part of the double equivalence $\mathbb{G} \colon \mathbb{F}\textnormal{Cospan}(\mathrm{A}) \to _L \mathbb{C} \textnormal{sp}(\mathrm{X})$ which goes in the other direction: again, the object component of this double functor will be $\mathbb{G}_0 = \id_{\mathrm{A}}$.
-
-Given a horizontal 1-cell $M$ of $\mathbb{F} \textnormal{Cospan}(\mathrm{A})$:
+\newline
+
+We can also define the part of the double equivalence $\mathbb{G} \colon F\mathbb{C}\textnormal{sp} \to {_L \mathbb{C} \textnormal{sp}(\mathsf{X})}$ which goes in the other direction: again, the object component of this double functor will be $\mathbb{G}_0 = \id_{\mathsf{A}}$.
+
+Given a horizontal 1-cell $M$ of $F\mathbb{C}\textnormal{sp}$:
 \[
@@
 \]
-the image $\mathbb{G}(M)$ is the horizontal 1-cell in $_L \mathbb{C}\textnormal{sp}(\mathrm{X})$ given by:
+the image $\mathbb{G}(M)$ is the horizontal 1-cell in $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$ given by:
 \[
@@
 \path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$\tau_c L(I)$} (B)
-(C) edge node[above]{$\tau_ c L(O)$} (B);
-\end{tikzpicture}
-\]
-where $\tau_c \colon L(c) \to x$ is the unique morphism from the trival decoration on $c$ given by $$!_c \coloneqq 1 \xrightarrow{\phi} F(0) \xrightarrow{F(!)} F(c)$$ to $x \in F(c)$.
-In other words, the trivial decoraction $!_c$ is initial in $F(c)$ and $\tau_c \colon !_c \to x$ is the unique morphism to $x$.
-Similarly, given a 2-morphism $(f,h,g,\iota) \colon M \to M^\prime$ of $\mathbb{F} \textnormal{Cospan}(\mathrm{A})$:
+(A) edge node[above]{$!_{c} L(I)$} (B)
+(C) edge node[above]{$!_{c} L(O)$} (B);
+\end{tikzpicture}
+\]
+where $!_{c} \colon L(c) \to x$ is the unique morphism from the trival decoration on $c$ given by $$!_{c} \coloneqq 1 \xrightarrow{\phi} F(0) \xrightarrow{F(!)} F(c)$$ to $x \in F(c)$.
+In other words, the trivial decoraction $!_{c}$ is initial in $F(c)$.
+Similarly, given a 2-morphism $(f,h,g,\iota) \colon M \to M^\prime$ of $F\mathbb{C}\textnormal{sp}$:
 \[
@@
 $$\iota \colon F(h)(x) \to x^\prime$$
-the image in $_L \mathbb{C}\textnormal{sp}(\mathrm{X})$ is given by the 2-morphism:
+the image in $\mathbb{G}(f,h,g,\iota)$ in $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$ is given by the 2-morphism:
 \[
@@
 \node (A) at (0,0) {$L(c_1)$};
-\node (B) at (1,0) {$x$};
-\node (C) at (2,0) {$L(c_2)$};
+\node (B) at (1.5,0) {$x$};
+\node (C) at (3,0) {$L(c_2)$};
 \node (A') at (0,-1) {$L(c_1^\prime)$};
-\node (B') at (1,-1) {$x^\prime$};
-\node (C') at (2,-1) {$L(c_2^\prime)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$\tau_c L(I)$} (B)
-(C) edge node[above]{$\tau_c L(O)$} (B)
-(A') edge node[above]{$\tau_{c^\prime} L(I^\prime)$} (B')
-(C') edge node[above]{$\tau_{c^\prime} L(O^\prime)$} (B')
+\node (B') at (1.5,-1) {$x^\prime$};
+\node (C') at (3,-1) {$L(c_2^\prime)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$!_{c} L(I)$} (B)
+(C) edge node[above]{$!_{c} L(O)$} (B)
+(A') edge node[above]{$!_{c^\prime} L(I^\prime)$} (B')
+(C') edge node[above]{$!_{c^\prime} L(O^\prime)$} (B')
 (A) edge node [left]{$L(f)$} (A')
@@
 \]
-where $\alpha \colon x \to x^\prime$ is a morphism in the Grothendieck construction of $F$ given by $\alpha = (h \colon c \to c^\prime, \iota \colon F(h)(x) \to x^\prime)$.
-
-Next, we exhibit natural isomorphisms $\eta \colon \id_{ _L \mathbb{C}\textnormal{sp}(\mathrm{X})} \cong \mathbb{G} \mathbb{E}$ and $\epsilon \colon \mathbb{E} \mathbb{G} \cong \id_{\mathbb{F}\textnormal{Cospan}(\mathrm{A})}$.
-Specifically, these are double natural isomorphisms given by double transformations $\eta$ and $\epsilon$ whose components are isomorphisms.
+where $\alpha \colon x \to x^\prime$ is the morphism in the Grothendieck construction of $F$ given by $\alpha = (h \colon c \to c^\prime, \iota \colon F(h)(x) \to x^\prime)$.
+
+Next, we exhibit natural isomorphisms $\eta \colon \id_{ _L \mathbb{C}\textnormal{sp}(\mathsf{X})} \cong \mathbb{G} \mathbb{E}$ and $\epsilon \colon \mathbb{E} \mathbb{G} \cong \id_{F\mathbb{C}\textnormal{sp}}$.
+Specifically, these are double natural isomorphisms given by double transformations \cite{Shul2} $\eta$ and $\epsilon$ whose object and arrow components are isomorphisms.
 
 First we compute the composites $\mathbb{G} \mathbb{E}$ and $\mathbb{E} \mathbb{G}$.
-On the object categories, both composites are $\id_\mathrm{A}$ and we have natural isomorphisms $\eta \colon \id_{\mathrm{A}} \cong \mathbb{G}_0 \mathbb{E}_0$ and $\epsilon \colon \mathbb{E}_0 \mathbb{G}_0 \cong \id_{\mathrm{A}}$.
-
-Given a horizontal 1-cell $M$ in $_L \mathbb{C} \textnormal{sp}(\mathrm{X})$:
+On the object categories, both composites are $\id_\mathsf{A}$ and we have natural isomorphisms $\eta \colon \id_{\mathsf{A}} \cong \mathbb{G}_0 \mathbb{E}_0$ and $\epsilon \colon \mathbb{E}_0 \mathbb{G}_0 \cong \id_{\mathsf{A}}$.
+
+Given a horizontal 1-cell $M$ in $_L \mathbb{C} \textnormal{sp}(\mathsf{X})$:
 \[
@@
 \path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$R(i)$} (B)
-(C) edge node[above]{$R(o)$} (B);
+(A) edge node[above]{$R(i) \eta_{c_1}$} (B)
+(C) edge node[above]{$R(o) \eta_{c_2}$} (B);
 \end{tikzpicture}
@@
 \path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$\tau_{R(x)}L(R(i))$} (B)
-(C) edge node[above]{$\tau_{R(x)}L(R(o))$} (B);
-\end{tikzpicture}
-\]
-\textbf{What can we say about LR? Find a 2-iso between these in $_L \mathbb{C}\textnormal{sp}(\mathrm{X})$.}
-Then we can find a 2-isomorphism $\eta_M \colon M \xrightarrow{\sim} \mathbb{G}\mathbb{E}(M) $ in $_L \mathbb{C} \textnormal{sp}(\mathrm{X})$ given by:
+(A) edge node[above]{$!_{R(x)}L(R(i)\eta_{c_1})$} (B)
+(C) edge node[above]{$!_{R(x)}L(R(o)\eta_{c_2})$} (B);
+\end{tikzpicture}
+\]
+Then we can find a 2-isomorphism $\eta_M \colon M \xrightarrow{\sim} \mathbb{G}\mathbb{E}(M) $ in $_L \mathbb{C} \textnormal{sp}(\mathsf{X})$ given by:
 \[
@@
 \node (A) at (0,0) {$L(c_1)$};
-\node (B) at (1.25,0) {$x$};
-\node (C) at (2.5,0) {$L(c_2)$};
+\node (B) at (1.5,0) {$x$};
+\node (C) at (3,0) {$L(c_2)$};
 \node (A') at (0,-1) {$L(c_1)$};
-\node (B') at (1.25,-1) {$x$};
-\node (C') at (2.5,-1) {$L(c_2)$};
+\node (B') at (1.5,-1) {$x$};
+\node (C') at (3,-1) {$L(c_2)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (C) edge node[above]{$o$} (B)
-(A') edge node[above]{$\tau_{R(x)}L(R(i))$} (B')
-(C') edge node[above]{$\tau_{R(x)}L(R(o))$} (B')
+(A') edge node[above]{$!_{R(x)}L(R(i)\eta_{c_1})$} (B')
+(C') edge node[above]{$!_{R(x)}L(R(o)\eta_{c_2})$} (B')
 (A) edge node [left]{$1$} (A')
@@
 \]
-On the other hand, given a horizontal 1-cell $N$ in $\mathbb{F}\textnormal{Cospan}(\mathrm{A})$:
+where
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (-0.5,0) {$L(c_1)$};
+\node (B) at (1,0) {$L(R(L(c_1)))$};
+\node (C) at (2.5,0) {$L(R(x))$};
+\node (D) at (3.5,0) {$x$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$L(\eta_{c_1})$} (B)
+(B) edge node[above]{$L(R(i))$} (C)
+(C) edge node[above]{$!_{R(x)}$} (D)
+(A) edge[bend right] node [above]{$i$} (D);
+\end{tikzpicture}
+\]
+commutes.
+
+On the other hand, given a horizontal 1-cell $N$ in $F\mathbb{C}\textnormal{sp}$:
 \[
@@
 \path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$\tau_c L(I)$} (B)
-(C) edge node[above]{$\tau_c L(O)$} (B);
+(A) edge node[above]{$!_c L(I)$} (B)
+(C) edge node[above]{$!_c L(O)$} (B);
 \end{tikzpicture}
@@
 \node (A) at (0,0) {$c_1$};
-\node (B) at (1,0) {$R(x)$};
-\node (C) at (2,0) {$c_2$};
-\node (D) at (1,-0.5) {$x \in F(R(x))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$R(\tau_c)I$} (B)
-(C) edge node[above]{$R(\tau_c)O$} (B);
-\end{tikzpicture}
-\]
-Then we can find a 2-isomorphism $\epsilon_N \colon \mathbb{E} \mathbb{G} (N) \xrightarrow{\sim} N$ in $\mathbb{F}\textnormal{Cospan}(\mathrm{A})$ given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (D) at (1,0.5) {$x \in F(R(x))$};
-\node (D') at (1,-1.5) {$x \in F(c)$};
+\node (B) at (1.5,0) {$R(x)$};
+\node (C) at (3,0) {$c_2$};
+\node (D) at (1.5,-0.5) {$x \in F(R(x))$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$R(!_c L(I))\eta_{c_1}$} (B)
+(C) edge node[above]{$R(!_c L(O))\eta_{c_2}$} (B);
+\end{tikzpicture}
+\]
+Then we have a 2-isomorphism $\epsilon_N \colon \mathbb{E} \mathbb{G} (N) \xrightarrow{\sim} N$ in $F\mathbb{C}\textnormal{sp}$ given by:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (D) at (1.5,0.5) {$x \in F(R(x))$};
+\node (D') at (1.5,-1.5) {$x \in F(c)$};
 \node (A) at (0,0) {$c_1$};
-\node (B) at (1,0) {$R(x)$};
-\node (C) at (2,0) {$c_2$};
+\node (B) at (1.5,0) {$R(x)$};
+\node (C) at (3,0) {$c_2$};
 \node (A') at (0,-1) {$c_1$};
-\node (B') at (1,-1) {$c$};
-\node (C') at (2,-1) {$c_2$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$R(\tau_c)I$} (B)
-(C) edge node[above]{$R(\tau_c)O$} (B)
+\node (B') at (1.5,-1) {$c$};
+\node (C') at (3,-1) {$c_2$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$R(!_c L(I))\eta_{c_1}$} (B)
+(C) edge node[above]{$R(!_c L(O))\eta_{c_2}$} (B)
 (A') edge node[above]{$I$} (B')
@@
 $$\iota \colon F(e)(x) \to x$$
+where 
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$c_1$};
+\node (B) at (1,0) {$R(L(c_1))$};
+\node (C) at (2.5,0) {$R(L(c))$};
+\node (D) at (3.5,0) {$R(x)$};
+\node (E) at (4.5,0) {$c$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$\eta_{c_1}$} (B)
+(B) edge node[above]{$R(L(I))$} (C)
+(C) edge node[above]{$R(!_c)$} (D)
+(D) edge node[above]{$e$} (E)
+(A) edge[bend right] node [above]{$I$} (E);
+\end{tikzpicture}
+\]
+commutes.
 \section{Applications}\label{Applications}
@@
 \section{Acknowledgements}
-Daniel Cicala, person that Christina emailed about lax slice category? {\chris did you use it after all?}
+Daniel Cicala, person that Christina emailed about lax slice category? {\chris did you use it after all?} No, I did not.
 \begin{thebibliography}{100}

### 2019-01-09 EquivCompFrameworks_20180911kc.tex
few minor fixes

@@
 This framework, which goes by the name of `structured cospans', utilizes double categories where the objects are seen as inputs and outputs, horizontal 1-cells are `open networks', and 2-morphisms are maps between open networks.
-In this setup a functor $L \colon \textrm{A} \to \textrm{X}$, which is typically a left adjoint, is used to replace the objects and vertical 1-morphisms of a given double category $\mathbb{X}$ with the objects and morphisms, respectively, of the category $\textrm{A}$.
-Horizontal 1-cells are then cospans in $\textrm{X}$ of a particular form with 2-morphisms given by maps of these cospans.
+In this setup a functor $L \colon \textsf{A} \to \textsf{X}$, which is typically a left adjoint, is used to replace the objects and vertical 1-morphisms of a given double category $\mathbb{X}$ with the objects and morphisms, respectively, of the category $\textsf{A}$.
+Horizontal 1-cells are then cospans in $\textsf{X}$ of a particular form with 2-morphisms given by maps of these cospans.
 Fong has also developed a similar framework utilizing cospans to study open networks which goes by the name of `decorated cospans'.
-In this setup, a lax monoidal functor $F \colon \textrm{A} \to \textrm{Set}$ is used to `decorate' the apices of cospans in $\textrm{A}$ with elements of $\textrm{Set}$ giving the cospans extra structure.
+In this setup, a lax monoidal functor $F \colon \textsf{A} \to \textsf{Set}$ is used to `decorate' the apices of cospans in $\textsf{A}$ with elements of $\textsf{Set}$ giving the cospans extra structure.
 Using a slight variation of Fong's framework, we prove that these two frameworks are equivalent in the situation where a left adjoint can be obtained from a lax monoidal pseudofunctor using a well known construction of Grothendieck.
@@
 
-In Fong's theory of decorated cospans, given a category $\textrm{A}$ with finite colmits, a symmetric lax monoidal functor $F \colon (\textrm{A},+,0) \to (\textrm{Set},\times,1)$ is used to `decorate' the apex of a cospan in $\textrm{A}$ with an element of the image of its apex under the functor $F$.
+In Fong's theory of decorated cospans, given a category $\textsf{A}$ with finite colmits, a symmetric lax monoidal functor $F \colon (\textsf{A},+,0) \to (\textsf{Set},\times,1)$ is used to `decorate' the apex of a cospan in $\textsf{A}$ with an element of the image of its apex under the functor $F$.
 In the case of the first cospan above, an element of the image of the apex under the functor $F$ is given by a morphism $d \colon 1 \to F(b)$, and we call $d$ a \textbf{decoration} on $b$.
-Here, $1$ is any terminal object in $\mathrm{Set}$, $F(b)$ is the collection of all $F$-decorations on the object $b$ and the morphism $d$ is selecting a particular one.
+Here, $1$ is any terminal object in $\mathsf{Set}$, $F(b)$ is the collection of all $F$-decorations on the object $b$ and the morphism $d$ is selecting a particular one.
 Thus a decorated cospan is given by a pair:
@@
  $$1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{d_1 \times d_2} F(b) \times F(b^\prime) \xrightarrow{\phi_{b,b^\prime}} F(b+ b^\prime) \xrightarrow{F(j_{b,b^\prime})} F(b+_{a_2} b^\prime).$$
-From this symmetric lax monoidal functor $F \colon \textrm{A} \to \mathrm{Set}$, Fong then constructs a symmetric monoidal category $F\textnormal{Cospan}(\mathrm{A})$ which has:
+From this symmetric lax monoidal functor $F \colon \textsf{A} \to \mathsf{Set}$, Fong then constructs a symmetric monoidal category $F\textnormal{Cospan}(\mathsf{A})$ which has:
 \begin{enumerate}
-\item{objects as those of $\mathrm{A}$ and}
+\item{objects as those of $\mathsf{A}$ and}
 \item{morphisms as isomorphism classes of $F$-decorated cospans, where an $F$-decorated cospan is given as above, and two $F$-decorated cospans are in the same isomorphism class if there exists an isomorphism $f \colon b \to b^\prime$ between the apices such that the following diagrams commute:
@@
 
-As an example, let $F \colon \textrm{FinSet} \to \textrm{Set}$ be the symmetric lax monoidal functor that assigns to a finite set $b$ the (large) set of all possible graph structures on the finite set $b$, where a graph structure on $b$ is given by a diagram in $\textrm{Set}$ of the form:
+As an example, let $F \colon \textsf{FinSet} \to \textsf{Set}$ be the symmetric lax monoidal functor that assigns to a finite set $b$ the (large) set of all possible graph structures on the finite set $b$, where a graph structure on $b$ is given by a diagram in $\textsf{Set}$ of the form:
 \[

### 2019-04-23 EquivCompFrameworks_20180911kc.tex
added and edited various needed parts. Next step, the proof of the theorem!

@@
 \item {\chris I think structured cospans should be introduced/recalled way earlier! This is a paper that compares the two,
-and both should be presented early.}
-\item Sure, I'm fine with that. What section do you think we should bring it up in, or maybe create a new section entirely to mention it?
+and both should be presented early.} Sure, I'm fine with that.
+What section do you think we should bring it up in, or maybe create a new section entirely to mention it?
+{\chris I think a new section right before that equivalence section would be great!}
 \end{itemize}
@@
 
+{\chris edit appropriately, notation etc.}
+\begin{thm}\label{thm:Grothendieck}
+    \begin{enumerate}
+        \item Every opfibration $\U \maps \D \to \C$ gives rise to a pseudofunctor $F_U \maps \C {\to}Cat$.
+        \item Every opindexed category $F \maps \C \to Cat$ gives rise to  an opfibration $\U_F \colon \int F\to\C$.
+        \item The above correspondences yield an equivalence of 2-categories 
+        \begin{displaymath}
+            ICat(\C) \simeq opFib(\C)
+        \end{displaymath}
+        so that $F_{\U_F} \cong F$ and $\U_{F_\U} \cong \U$.
+%        \item The above 2-equivalence extends to one between 2-categories of arbitrary-base fibrations and arbitrary-domain indexed categories
+%        \begin{equation}\label{eq:Gr_equiv}
+%        \ICat\simeq\Fib    
+%        \end{equation}
+    \end{enumerate}
+\end{thm}
+
 Under certain conditions, the functor resulting from the Grothendieck construction $p \colon \int{F} \to \mathrm{A}$ will be right adjoint to the desired left adjoint $L \colon \mathrm{A} \to \mathrm{X}$.
 
+{\chris  moved and motivated appropriately}
+\begin{thm}\label{thm:mainthmDX}\cite{CV}
+Suppose that $\D$ and $\C$ have chosen pushouts and initial objects, and a functor $\U\colon\D\to\C$ strictly preserves them.
+Then $\U$ is a right adjoint left inverse if and only if $\U$ is an opfibration.
+\end{thm}
+
 \section{An equivalence of symmetric monoidal double categories} \label{EquivDoubleCats}
-In this section we prove that two different frameworks which utilize symmetric monoidal double categories, namely decorated cospans and `structured cospans', are equivalent under the conditions required from the previous section that allow for a left adjoint $L \colon \mathsf{A} \to \mathsf{X}$ to be obtained from a symmetric lax monoidal pseudofunctor $F \colon \mathsf{A} \to \mathbf{Cat}$.
-The double category version of decorataed cospans is given in Section \ref{DecCospansDoubleCat}.
-The other framework also utilizing symmetric monoidal double categories due to the first two authors and which goes by the name of `structured cospans', is introduced below.
+In this section we prove that two different frameworks which utilize symmetric monoidal double categories, namely decorated cospans and structured cospans described in {\chris refer to somewhere}, are equivalent under the conditions required from the previous section that allow for a left adjoint $L \colon \mathsf{A} \to \mathsf{X}$ to be obtained from a symmetric lax {\chris have to specify lax VS weak which is the standard terminology, happy to use lax though} monoidal pseudofunctor $F \colon \mathsf{A} \to \mathbf{Cat}$.
+The double category version of decorated cospans is given in Section \ref{DecCospansDoubleCat}.
+The other framework also utilizing symmetric monoidal double categories due to the first two authors and which goes by the name of `structured cospans', is introduced below {\chris I see, prefer earlier!}.
 Once again following the notation of Shulman \cite{Shul2}, given a double category $\mathbb{A}$, we write $_f \mathbb{A}_g(M,N)$ for the set of 2-morphisms in $\mathbb{A}$ of the form:
@@
 
-{\chris Statement of Theorem, and proof, will be heavily edited soon!}
+{\chris in progress}
 \begin{thm}\label{Equiv}
-Let $\mathsf{A}$ and $\mathsf{X}$ be categories with finite colimits and $F \colon \mathsf{A} \to \mathbf{Cat}$ a symmetric lax monoidal pseudofunctor.
-Let $L \colon \mathsf{A} \to \int{F} \cong \mathsf{X}$ be the left adjoint of the Grothendieck construction $R \colon \int{F} \to \mathsf{A}$ of $F$.
-Then the symmetric monoidal double category $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$ utilizing structured cospans and the symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$ utilizing decorated cospans are equivalent as symmetric monoidal double categories.
+Let $\mathsf{A}$ and $\mathsf{X}$ be categories with (chosen) finite colimits, and $F \colon(\mathsf{A},+,0) \to (\mathbf{Cat},\times,\mathbf{1})$ a symmetric lax monoidal pseudofunctor.
+The symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$ of decorated cospans is equivalent to the symmetric monoidal double category $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$ of structured cospans, where $L \colon \mathsf{A} \to \int{F} \cong \mathsf{X}$ is the left adjoint of the induced Grothendieck opfibration $\U_F\colon \int{F} \to \mathsf{A}$ by \cref{thm:Grothendieck} under the assumptions of \cref{thm:mainthmDX}.
 \end{thm}
@@
 
+\bibitem{CV} D.\ Cicala and C.\ Vasilakopoulou, On Adjoints and Fibrations. In preparation.
+
 \bibitem{Cour} K.\ Courser, A bicategory of decorated cospans, \emph{Theor.\ Appl.\ Cat.} \textbf{32} (2017), 995--1027. Also available as \href{https://arxiv.org/abs/1605.08100}{arXiv:1605.08100}.

### 2019-04-23 EquivCompFrameworks_20180911kc.tex
tiny

@@
 {\chris I think a new section right before that equivalence section would be great!}
+\item {\chris Discuss the name of Decorated and Structured cospan double categories one last time? :)}
 \end{itemize}
@@
 \begin{thm}\label{Equiv}
-Let $\mathsf{A}$ and $\mathsf{X}$ be categories with (chosen) finite colimits, and $F \colon(\mathsf{A},+,0) \to (\mathbf{Cat},\times,\mathbf{1})$ a symmetric lax monoidal pseudofunctor.
+Let $\mathsf{A}$ and $\mathsf{X}$ be categories with finite colimits, and $F \colon(\mathsf{A},+,0) \to (\mathbf{Cat},\times,\mathbf{1})$ a symmetric lax monoidal pseudofunctor.
 The symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$ of decorated cospans is equivalent to the symmetric monoidal double category $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$ of structured cospans, where $L \colon \mathsf{A} \to \int{F} \cong \mathsf{X}$ is the left adjoint of the induced Grothendieck opfibration $\U_F\colon \int{F} \to \mathsf{A}$ by \cref{thm:Grothendieck} under the assumptions of \cref{thm:mainthmDX}.

### 2019-04-24 EquivCompFrameworks_20180911kc.tex
tiny

@@
 The next three examples which take on more of an applied flavor, consists of electrical circuits, Markov processes and Petri nets.
-Each of these has been studied extensively by the first author and others by way of `black-boxing' \cite{BCR,BF,BFP,BM,BP}.
+Each of these has been studied extensively by Baez, Fong, Master and Pollard by way of `black-boxing' \cite{BCR,BF,BFP,BM,BP}.
 Black-boxing is a way of interpreting the behavior of an open system, that is, a system with prescribed inputs and outputs such as the terminals of an electrical circuit, by observing the activity at the inputs and the outputs.
@@
 The first two of these were first done using Fong's theory of decorated cospans and then extended by the first two authors using structured cospans.
-The last two of these were also extended by being realized as double functors between double categories \cite{BC,BM}.
+The last two of these were also extended by being realized as double functors between double categories \cite{BC,BM} and is discussed in Chapter \ref{Chapter6}.
 \subsection{Graphs}

### 2019-04-25 EquivCompFrameworks_20180911kc.tex
initial work on proof

@@
 \item {\chris Discuss the name of Decorated and Structured cospan double categories one last time? :)}
+\item {\chris I'm starting a few macros to help us write faster and adjust accordingly if we need to later.
+On that note, could Kenny `clean' the preamble at some point?
+I.e.
+erase the commands not used here, to make it easier to navigate?
+I would do it but I wouldn't want to erase something you use!}
 \end{itemize}
@@
 
-{\chris in progress}
 \begin{thm}\label{Equiv}
 Let $\mathsf{A}$ and $\mathsf{X}$ be categories with finite colimits, and $F \colon(\mathsf{A},+,0) \to (\mathbf{Cat},\times,\mathbf{1})$ a symmetric lax monoidal pseudofunctor.
-The symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$ of decorated cospans is equivalent to the symmetric monoidal double category $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$ of structured cospans, where $L \colon \mathsf{A} \to \int{F} \cong \mathsf{X}$ is the left adjoint of the induced Grothendieck opfibration $\U_F\colon \int{F} \to \mathsf{A}$ by \cref{thm:Grothendieck} under the assumptions of \cref{thm:mainthmDX}.
+The symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$ of decorated cospans is equivalent to the symmetric monoidal double category $_{L_F} \mathbb{C}\textnormal{sp}(\mathsf{X})$ of structured cospans, where $L_F \colon \mathsf{A} \to \int{F}$ is the left adjoint of the induced Grothendieck opfibration $\U_F\colon \int{F} \to \mathsf{A}$ by \cref{thm:Grothendieck} under the assumptions of \cref{thm:mainthmDX}.
 \end{thm}
 \begin{proof}
+As explained in (ref), the double category of decorated cospans $\dcsp{F}$ has $\A$ as its category of objects and vertical 1-morphisms, whereas horizontal 1-cells $a\tickar b$ are cospans $\cspn{a}{c}{b}{}{}$ in $\A$ along with $d\in F(c)$ and 2-morphisms are cospan maps $k\colon c\to c'$ such that $(Fk)(d)=d'$.
+
+The symmetric lax monoidal pseudofunctor $F$ corresponds, under the (monoidal) Gro\-the
+-ndieck construction, to an opfibration $U_F\colon\int{F}\to\A$ with such and such properties.
+
+{\chris in progress}
 To prove this, we define a double functor $\mathbb{E} \colon _L \mathbb{C}\textnormal{sp}(\mathsf{X}) \to F\mathbb{C}\textnormal{sp}$ as follows: the object component of the double functor $\mathbb{E}$ is given by $\mathbb{E}_0 = \id_{\mathsf{A}}$ as both double categories $_L \mathbb{C}\textnormal{sp}(\mathrm{X})$ and $F\mathbb{C}\textnormal{sp}$ have objects and morphisms of $\mathsf{A}$ as objects and vertical 1-morphisms, respectively.

### 2019-04-30 EquivCompFrameworks_20180911kc.tex
getting ready for the equivalence section

@@
 
+\setcounter{tocdepth}{1} % comment this out if you want to see the subsections in the table of contents
 \tableofcontents
@@
 \begin{itemize}
-\item {\chris I think structured cospans should be introduced/recalled way earlier! This is a paper that compares the two,
-and both should be presented early.} Sure, I'm fine with that.
-What section do you think we should bring it up in, or maybe create a new section entirely to mention it?
-{\chris I think a new section right before that equivalence section would be great!}
 \item {\chris Discuss the name of Decorated and Structured cospan double categories one last time? :)}
@@
 
+\begin{comment}
 \section{Introduction}
@@
 
+\subsection*{Outline}
+
+{\chris Amend at the end}
 The outline for the paper is as follows: In Section \ref{DecCospansDoubleCat}, we construct the symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$, obtain the underlying symmetric monoidal bicategory $F \mathbf{Csp}$ via a result of Shulman, and decategorify this symmetric monoidal bicategory to obtain the symmetric monoidal category $F$Csp.
@@
 Finally, in Section \ref{Applications}, we present a few examples that can be realized with either framework and discuss the realized equivalences.
+
+\subsection*{Acknowledgements}
+Daniel Cicala, person that Christina emailed about lax slice category? {\chris did you use it after all?} No, I did not.
+\end{comment}
+
+\section{A symmetric monoidal double category of structured cospans}\label{sec:structuredcospans}
+
+In this section, we recall the double category of \emph{structured cospans}, a formalism introduced to the first two authors.
+One of the main goals of this paper is to provide a double equivalence between this double category and one of \emph{decorated cospans}, described in detail in the subsequent section.
+
+Once again following the notation of Shulman \cite{Shul2}, given a double category $\mathbb{A}$, we write $_f \mathbb{A}_g(M,N)$ for the set of 2-morphisms in $\mathbb{A}$ of the form:
+\[
+  \xymatrix@-.5pc{
+    A \ar[r]|{|}^{M}  \ar[d]_f \ar@{}[dr]|{\Downarrow a}&
+    B\ar[d]^g\\
+    C \ar[r]|{|}_N & D
+  }
+\]
+We call $M$ and $N$ the \define{horizontal source and target} of the 2-morphism $a$, respectively, and likewise we call $f$ and $g$ the \define{vertical source and target} of the 2-morphism $a$, respectively.
+Thus $_f \mathbb{A}_g(M,N)$ denotes the set of 2-morphisms in $\mathbb{A}$ with horizontal source and target $M$ and $N$ and vertical source and target $f$ and $g$.
+\begin{defn}
+A (possibly lax or oplax) double functor $\mathbb{F} \colon \mathbb{A} \to \mathbb{X}$ is \define{full} (respectively, \define{faithful}) if $\mathbb{F}_0 \colon \mathbb{A}_0 \to \mathbb{X}_0$ is full (respectively, faithful) and each map $$\mathbb{F}_1 \colon _f \mathbb{A}_g(M,N) \to _{\mathbb{F}(f)} \mathbb{X}_{\mathbb{F}(g)}(\mathbb{F}(M),\mathbb{F}(N))$$ is surjective (respectively, injective).
+\end{defn}
+\begin{defn}
+A (possibly lax or oplax) double functor $\mathbb{F} \colon \mathbb{A} \to \mathbb{X}$ is \define{essentially surjective} if we can simultaneously make the following choices:
+\begin{enumerate}
+\item{For each object $x \in \mathbb{X}$, we can find an object $a \in \mathbb{A}$ together with a vertical 1-isomorphism $\alpha_x \colon \mathbb{F}(a) \to x$, and}
+\item{For each horizontal 1-cell $N \colon x_1 \tobar x_2$  of $\mathbb{X}$, we can find a horizontal 1-cell $M \colon a_1 \tobar a_2$ of $\mathbb{A}$ and a 2-isomorphism $a_{N}$ of $\mathbb{X}$ as in the following diagram:
+\[
+  \xymatrix@-.5pc{
+    \mathbb{F}(a_1) \ar[r]|{|}^{\mathbb{F}(M)}  \ar[d]_{\alpha_{x_1}} \ar@{}[dr]|{\Downarrow a_N}&
+    \mathbb{F}(a_1) \ar[d]^{\alpha_{x_2}}\\
+    x_1 \ar[r]|{|}_N & x_2
+  }
+\]
+}
+\end{enumerate}
+\end{defn}
+\begin{defn}
+A double functor $\mathbb{F} \colon \mathbb{A} \to \mathbb{X}$ is \define{strong} if the comparison and unit constraints are globular isomorphisms, meaning that for each composable pair of horizontal 1-cells $M$ and $N$ we have a natural isomorphism $$\mathbb{F}_{M,N} \colon \mathbb{F}(M) \odot \mathbb{F}(N) \xrightarrow{\sim} \mathbb{F}(M \odot N)$$and for each object $a \in \mathbb{A}$ a natural isomorphism $$\mathbb{F}_a \colon \hat{U}_{\mathbb{F}(a)} \xrightarrow{\sim} \mathbb{F}(U_a).$$
+\end{defn}
+\begin{thm}[Shulman,7.8]\label{ShulDubEquiv}
+Given a strong double functor $\mathbb{F} \colon \mathbb{A} \to \mathbb{X}$, $\mathbb{F}$ is part of a double equivalence if and only if $\mathbb{F}$ is full, faithful and essentially surjective.
+\end{thm}
+
+\begin{prop}
+Let $\mathbb{A}$ and $\mathbb{X}$ be symmetric monoidal double categories and let $\mathbb{F} \colon \mathbb{A} \to \mathbb{X}$ be a symmetric monoidal strong double functor.
+If $\mathbb{F}$ is part of a double equivalence, then $\mathbb{F}$ is in fact part of a symmetric monoidal double equivalence, and $\mathbb{A}$ and $\mathbb{X}$ are equivalent as symmetric monoidal double categories.
+\end{prop}
+
+Our next goal is to show that the symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$ of Section \ref{DecCospansDoubleCat} is equivalent as a symmetric monoidal double category to the symmetric monoidal double category $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$ obtained using structured cospans.
+
+\begin{thm}\label{SC}
+Given a category $\mathsf{X}$ with finite colimits and a category $\mathsf{A}$ with finite coproducts and a finite coproduct preserving functor $L \colon \mathsf{A} \to \mathsf{X}$ with $\mathsf{A}$ and $\mathsf{X}$ regarded as cocartesian monoidal categories, there exists a symmetric monoidal double category $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$ which has:
+\begin{enumerate}
+\item{objects given by objects of $\mathsf{A}$,}
+\item{vertical 1-morphisms given by morphisms of $\mathsf{A}$,}
+\item{horizontal 1-cells given by cospans of $\mathsf{X}$ of the form:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$L(c)$};
+\node (B) at (1,0) {$x$};
+\node (C) at (2,0) {$L(c^\prime)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$$} (B)
+(C) edge node[above]{$$} (B);
+\end{tikzpicture}
+\]
+and}
+\item{2-morphisms given by maps of cospans of $\mathsf{X}$ of the form:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$L(c_1)$};
+\node (B) at (1,0) {$x$};
+\node (C) at (2,0) {$L(c_2)$};
+\node (A') at (0,-1) {$L(c_1^\prime)$};
+\node (B') at (1,-1) {$x^\prime$};
+\node (C') at (2,-1) {$L(c_2^\prime)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$$} (B)
+(C) edge node[above]{$$} (B)
+(A') edge node[above]{$$} (B')
+(C') edge node[above]{$$} (B')
+(A) edge node [left]{$L(f)$} (A')
+(B) edge node [left]{$\alpha$} (B')
+(C) edge node [left]{$L(g)$} (C');
+\end{tikzpicture}
+\]
+Composition of horizontal 1-cells and 2-morphisms is given by pushouts in $\mathsf{X}$ and tensoring of objects is under binary coproducts in $\mathsf{A}$.
+}
+\end{enumerate}
+\end{thm}
+\begin{proof}
+See the first two authors' work on structured cospans \cite{BC2}.
+\end{proof}
+In the previous section, we started with a symmetric lax monoidal pseudofunctor $F \colon \mathsf{A} \to \mathbf{Cat}$ and created a symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$ which has:
+\begin{enumerate}
+\item{objects of $\mathsf{A}$ as objects,}
+\item{morphisms of $\mathsf{A}$ as vertical 1-morphisms,}
+\item{horizontal 1-cells are given by $F$-decorated cospans, which are pairs:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$c_1$};
+\node (B) at (1,0) {$c$};
+\node (C) at (2,0) {$c_2$};
+\node (D) at (3,0) {$x \in F(c)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i$} (B)
+(C) edge node[above]{$o$} (B);
+\end{tikzpicture}
+\]
+and}
+\item{2-morphisms are given by maps of cospans in $\mathsf{A}$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$c_1$};
+\node (B) at (1,0) {$c$};
+\node (C) at (2,0) {$c_2$};
+\node (A') at (0,-1) {$c_1^\prime$};
+\node (B') at (1,-1) {$c^\prime$};
+\node (C') at (2,-1) {$c_2^\prime$};
+\node (D) at (3,0) {$x \in F(c)$};
+\node (D') at (3,-1) {$x^\prime \in F(c^\prime)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i$} (B)
+(C) edge node[above]{$o$} (B)
+(A') edge node[above]{$i^\prime$} (B')
+(C') edge node[above]{$o^\prime$} (B')
+(A) edge node [left]{$f$} (A')
+(B) edge node [left]{$h$} (B')
+(C) edge node [left]{$g$} (C');
+\end{tikzpicture}
+\]
+together with a morphism $\iota \colon F(h)(d) \to d^\prime$ in $F(c^\prime)$.}
+\end{enumerate}
 
@@
 
+\begin{comment}
 \section{Maps of decorated cospan double categories}\label{MapsDecCospansDoubleCat}
@@
 On the other hand, applying the functor $E$ to each decoration results in $$1 \to E(F(c_1)) \times E(F(c_2)) \xrightarrow{} E(F(c_1) \times F(c_2)) \xrightarrow{} E(F(c_1+c_2)) \xrightarrow E(F(c_1+_b c_2)) \xrightarrow{} F^\prime(H(c_1 +_b c_2))$$
-
-\section{From pseudofunctors to left adjoints}\label{some other section}
+\end{comment}
+
+%\section{From pseudofunctors to left adjoints}\label{some other section}
+
+\section{An equivalence of symmetric monoidal double categories} \label{EquivDoubleCats}
+In this section we prove that two different frameworks which utilize symmetric monoidal double categories, namely decorated cospans and structured cospans described in \cref{sec:structuredcospans,DecCospansDoubleCat}, are equivalent.
+This is established by \cref{Equiv}, under some assumptions relevant to the existence of a left adjoints for opfibrations.
+We begin by elaborating this underlying framework, using results mainly from \cite{CV} and \cite{MV}.
+
+{\chris in so much progress}
 In this section we investigate the necessary conditions to obtain a category $\mathrm{X}$ and a left adjoint $L \colon \mathrm{A} \to \mathrm{X}$ from a category $\mathrm{A}$ with finite colimits and a symmetric lax monoidal pseudofunctor $F \colon \mathrm{A} \to \mathbf{Cat}$.
@@
 
-\section{An equivalence of symmetric monoidal double categories} \label{EquivDoubleCats}
-In this section we prove that two different frameworks which utilize symmetric monoidal double categories, namely decorated cospans and structured cospans described in {\chris refer to somewhere}, are equivalent under the conditions required from the previous section that allow for a left adjoint $L \colon \mathsf{A} \to \mathsf{X}$ to be obtained from a symmetric lax {\chris have to specify lax VS weak which is the standard terminology, happy to use lax though} monoidal pseudofunctor $F \colon \mathsf{A} \to \mathbf{Cat}$.
-The double category version of decorated cospans is given in Section \ref{DecCospansDoubleCat}.
-The other framework also utilizing symmetric monoidal double categories due to the first two authors and which goes by the name of `structured cospans', is introduced below {\chris I see, prefer earlier!}.
-Once again following the notation of Shulman \cite{Shul2}, given a double category $\mathbb{A}$, we write $_f \mathbb{A}_g(M,N)$ for the set of 2-morphisms in $\mathbb{A}$ of the form:
-\[
-  \xymatrix@-.5pc{
-    A \ar[r]|{|}^{M}  \ar[d]_f \ar@{}[dr]|{\Downarrow a}&
-    B\ar[d]^g\\
-    C \ar[r]|{|}_N & D
-  }
-\]
-We call $M$ and $N$ the \define{horizontal source and target} of the 2-morphism $a$, respectively, and likewise we call $f$ and $g$ the \define{vertical source and target} of the 2-morphism $a$, respectively.
-Thus $_f \mathbb{A}_g(M,N)$ denotes the set of 2-morphisms in $\mathbb{A}$ with horizontal source and target $M$ and $N$ and vertical source and target $f$ and $g$.
-\begin{defn}
-A (possibly lax or oplax) double functor $\mathbb{F} \colon \mathbb{A} \to \mathbb{X}$ is \define{full} (respectively, \define{faithful}) if $\mathbb{F}_0 \colon \mathbb{A}_0 \to \mathbb{X}_0$ is full (respectively, faithful) and each map $$\mathbb{F}_1 \colon _f \mathbb{A}_g(M,N) \to _{\mathbb{F}(f)} \mathbb{X}_{\mathbb{F}(g)}(\mathbb{F}(M),\mathbb{F}(N))$$ is surjective (respectively, injective).
-\end{defn}
-\begin{defn}
-A (possibly lax or oplax) double functor $\mathbb{F} \colon \mathbb{A} \to \mathbb{X}$ is \define{essentially surjective} if we can simultaneously make the following choices:
-\begin{enumerate}
-\item{For each object $x \in \mathbb{X}$, we can find an object $a \in \mathbb{A}$ together with a vertical 1-isomorphism $\alpha_x \colon \mathbb{F}(a) \to x$, and}
-\item{For each horizontal 1-cell $N \colon x_1 \tobar x_2$  of $\mathbb{X}$, we can find a horizontal 1-cell $M \colon a_1 \tobar a_2$ of $\mathbb{A}$ and a 2-isomorphism $a_{N}$ of $\mathbb{X}$ as in the following diagram:
-\[
-  \xymatrix@-.5pc{
-    \mathbb{F}(a_1) \ar[r]|{|}^{\mathbb{F}(M)}  \ar[d]_{\alpha_{x_1}} \ar@{}[dr]|{\Downarrow a_N}&
-    \mathbb{F}(a_1) \ar[d]^{\alpha_{x_2}}\\
-    x_1 \ar[r]|{|}_N & x_2
-  }
-\]
-}
-\end{enumerate}
-\end{defn}
-\begin{defn}
-A double functor $\mathbb{F} \colon \mathbb{A} \to \mathbb{X}$ is \define{strong} if the comparison and unit constraints are globular isomorphisms, meaning that for each composable pair of horizontal 1-cells $M$ and $N$ we have a natural isomorphism $$\mathbb{F}_{M,N} \colon \mathbb{F}(M) \odot \mathbb{F}(N) \xrightarrow{\sim} \mathbb{F}(M \odot N)$$and for each object $a \in \mathbb{A}$ a natural isomorphism $$\mathbb{F}_a \colon \hat{U}_{\mathbb{F}(a)} \xrightarrow{\sim} \mathbb{F}(U_a).$$
-\end{defn}
-\begin{thm}[Shulman,7.8]\label{ShulDubEquiv}
-Given a strong double functor $\mathbb{F} \colon \mathbb{A} \to \mathbb{X}$, $\mathbb{F}$ is part of a double equivalence if and only if $\mathbb{F}$ is full, faithful and essentially surjective.
-\end{thm}
-
-\begin{prop}
-Let $\mathbb{A}$ and $\mathbb{X}$ be symmetric monoidal double categories and let $\mathbb{F} \colon \mathbb{A} \to \mathbb{X}$ be a symmetric monoidal strong double functor.
-If $\mathbb{F}$ is part of a double equivalence, then $\mathbb{F}$ is in fact part of a symmetric monoidal double equivalence, and $\mathbb{A}$ and $\mathbb{X}$ are equivalent as symmetric monoidal double categories.
-\end{prop}
-
-Our next goal is to show that the symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$ of Section \ref{DecCospansDoubleCat} is equivalent as a symmetric monoidal double category to the symmetric monoidal double category $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$ obtained using structured cospans.
-
-\begin{thm}\label{SC}
-Given a category $\mathsf{X}$ with finite colimits and a category $\mathsf{A}$ with finite coproducts and a finite coproduct preserving functor $L \colon \mathsf{A} \to \mathsf{X}$ with $\mathsf{A}$ and $\mathsf{X}$ regarded as cocartesian monoidal categories, there exists a symmetric monoidal double category $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$ which has:
-\begin{enumerate}
-\item{objects given by objects of $\mathsf{A}$,}
-\item{vertical 1-morphisms given by morphisms of $\mathsf{A}$,}
-\item{horizontal 1-cells given by cospans of $\mathsf{X}$ of the form:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$L(c)$};
-\node (B) at (1,0) {$x$};
-\node (C) at (2,0) {$L(c^\prime)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$$} (B)
-(C) edge node[above]{$$} (B);
-\end{tikzpicture}
-\]
-and}
-\item{2-morphisms given by maps of cospans of $\mathsf{X}$ of the form:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$L(c_1)$};
-\node (B) at (1,0) {$x$};
-\node (C) at (2,0) {$L(c_2)$};
-\node (A') at (0,-1) {$L(c_1^\prime)$};
-\node (B') at (1,-1) {$x^\prime$};
-\node (C') at (2,-1) {$L(c_2^\prime)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$$} (B)
-(C) edge node[above]{$$} (B)
-(A') edge node[above]{$$} (B')
-(C') edge node[above]{$$} (B')
-(A) edge node [left]{$L(f)$} (A')
-(B) edge node [left]{$\alpha$} (B')
-(C) edge node [left]{$L(g)$} (C');
-\end{tikzpicture}
-\]
-Composition of horizontal 1-cells and 2-morphisms is given by pushouts in $\mathsf{X}$ and tensoring of objects is under binary coproducts in $\mathsf{A}$.
-}
-\end{enumerate}
-\end{thm}
-\begin{proof}
-See the first two authors' work on structured cospans \cite{BC2}.
-\end{proof}
-In the previous section, we started with a symmetric lax monoidal pseudofunctor $F \colon \mathsf{A} \to \mathbf{Cat}$ and created a symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$ which has:
-\begin{enumerate}
-\item{objects of $\mathsf{A}$ as objects,}
-\item{morphisms of $\mathsf{A}$ as vertical 1-morphisms,}
-\item{horizontal 1-cells are given by $F$-decorated cospans, which are pairs:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$c_1$};
-\node (B) at (1,0) {$c$};
-\node (C) at (2,0) {$c_2$};
-\node (D) at (3,0) {$x \in F(c)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i$} (B)
-(C) edge node[above]{$o$} (B);
-\end{tikzpicture}
-\]
-and}
-\item{2-morphisms are given by maps of cospans in $\mathsf{A}$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$c_1$};
-\node (B) at (1,0) {$c$};
-\node (C) at (2,0) {$c_2$};
-\node (A') at (0,-1) {$c_1^\prime$};
-\node (B') at (1,-1) {$c^\prime$};
-\node (C') at (2,-1) {$c_2^\prime$};
-\node (D) at (3,0) {$x \in F(c)$};
-\node (D') at (3,-1) {$x^\prime \in F(c^\prime)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i$} (B)
-(C) edge node[above]{$o$} (B)
-(A') edge node[above]{$i^\prime$} (B')
-(C') edge node[above]{$o^\prime$} (B')
-(A) edge node [left]{$f$} (A')
-(B) edge node [left]{$h$} (B')
-(C) edge node [left]{$g$} (C');
-\end{tikzpicture}
-\]
-together with a morphism $\iota \colon F(h)(d) \to d^\prime$ in $F(c^\prime)$.}
-\end{enumerate}
+under the conditions required from the previous section that allow for a left adjoint $L \colon \mathsf{A} \to \mathsf{X}$ to be obtained from a symmetric lax {\chris have to specify lax VS weak which is the standard terminology, happy to use lax though} monoidal pseudofunctor $F \colon \mathsf{A} \to \mathbf{Cat}$.
+%The double category version of decorated cospans is given in Section \ref{DecCospansDoubleCat}.
+
 We now show that these two symmetric monoidal double categories are equivalent.
@@
 commutes.
+
+\begin{comment}
 \section{Applications}\label{Applications}
@@
 Thus we have a symmetric monoidal double category $\mathbb{O}\mathbf{pen}(\mathrm{Petri})$ of open Petri nets obtained from structured cospans and a symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$ of open Petri nets obtain from decorated cospans, and of course, we have an equivalence $\mathbb{O}\mathbf{pen}(\mathrm{Petri}) \sim F\mathbb{C}\textnormal{sp}$ of symmetric monoidal double categories by Theorem \ref{Equiv}.
-
+\end{comment}
+
+\begin{comment}
 \section{Appendix}
@@
 \end{defn}
-\section{Acknowledgements}
-Daniel Cicala, person that Christina emailed about lax slice category? {\chris did you use it after all?} No, I did not.
+\end{comment}
+
 \begin{thebibliography}{100}
@@
 %     Springer, Berlin, 1998.
+
+\bibitem{MV} J.\ Moeller and C.\ Vasilakopoulou, Monoidal Grothendieck construction. Available as \href{https://arxiv.org/abs/1809.00727}{arXiv:1809.00727}.
 

### 2019-04-30 EquivCompFrameworks_20180911kc.tex
various rearrangements before theorem in progress

@@
 \section*{Various issues-in-progress}
-{\chris If Kenny likes, we can use this as a section for all the current issues that need to be resolved, or what we are currently working on or something!}
+
 \begin{itemize}
@@
 I would do it but I wouldn't want to erase something you use!}
+\item {\chris Where should we put some standard things we use? For exampe, lax monoidal pseudofunctor should be recalled early. Together with pseudonatural transformations I believe.}
 \end{itemize}
+
+\section*{Various notions to be recalled, earlier rather than later}
+
+Recall that a pseudofunctor $F\colon\bicat{A}\to\bicat{B}$ between bicategories $\bicat{A}$ and $\bicat{B}$ is functorial up to coherent natural isomorphism, namely for composable arrows we have $F(g\circ f)\cong Fg\circ Ff$ and $F(1_a)\cong1_{Fa}$ satisfying standard axioms.
+Given pseudofunctors $F,G\colon \bicat{A} \to \bicat{B}$, a \define{pseudonatural transformation} $\sigma$ consists of {\chris notation below needs fixing}
+\begin{itemize}
+\item for each object $a \in \bicat{A}$, a morphism $\sigma_a \colon F(a) \to G(a)$ in $\bicat{B}$ 
+\item for every pair of objects $a$ and $b$ of $\mathbf{A}$, we have natural isomorphisms
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$\mathbf{A}(a,b)$};
+\node (B) at (2,0) {$\mathbf{X}(F(a),F(b))$};
+\node (C) at (0,-1) {$\mathbf{X}(G(a),G(b))$};
+\node (D) at (2,-1) {$\mathbf{X}(F(a),G(b))$};
+\node (E) at (1,-0.5) {$\sigma_{a,b} \Nearrow$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$F$} (B)
+(B) edge node[right]{$(\sigma_{b})_*$} (D)
+(A) edge node[left]{$G$} (C)
+(C) edge node[above]{$(\sigma_a)^*$} (D);
+\end{tikzpicture}
+\]
+where $(\sigma_a)^*$ and $(\sigma_b)_*$ are the functors induced by precomposition and postcompositon, respectively.
+Thus for each morphism $f \colon a \to b$ in $\mathbf{A}$, we have an invertible 2-morphism $\sigma_f \colon G(f) \sigma_a \xrightarrow{\sim} \sigma_{b} F(f)$ in $\mathbf{X}$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$F(a)$};
+\node (B) at (1,0) {$F(b)$};
+\node (C) at (0,-1) {$G(a)$};
+\node (D) at (1,-1) {$G(b)$};
+\node (E) at (0.5,-0.5) {$\sigma_f \Nearrow$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$F(f)$} (B)
+(B) edge node[right]{$\sigma_{b}$} (D)
+(A) edge node[left]{$\sigma_a$} (C)
+(C) edge node[above]{$G(f)$} (D);
+\end{tikzpicture}
+\]
+which is compatible with composition and identities.
+\end{itemize}
+%such that for each composable pair of morphisms $f \colon a \to b$ and $g \colon b \to c$ of $\mathbf{A}$, the following diagrams commute:
+%\[
+%\begin{tikzpicture}[scale=1.5]
+%\node (A) at (0,0.5) {$(G(g)G(f))\sigma_a$};
+%\node (A') at (2,0.5) {$G(g)(G(f) \sigma_a)$};
+%\node (B) at (0,-0.5) {$G(gf) \sigma_a$};
+%\node (C) at (4,0.5) {$G(g) (\sigma_b F(f))$};
+%\node (C') at (4,-0.5) {$\sigma_c F(gf)$};
+%\node (D) at (6,0.5) {$(G(g) \sigma_b) F(f)$};
+%\node (D') at (8,-0.5) {$\sigma_c (F(g)F(f))$};
+%\node (F) at (8,0.5) {$(\sigma_c F(g)) F(f)$};
+%\path[->,font=\scriptsize,>=angle 90]
+%(A) edge node[above]{$a^\prime$} (A')
+%(A) edge node[left]{$\psi 1_{\sigma_a}$} (B)
+%(A') edge node[above]{$1_{G(g)} \sigma_f$} (C)
+%(B) edge node[above]{$\sigma_{gf}$} (C')
+%(C) edge node [above] {${a^\prime}^{-1}$} (D)
+%(D') edge node [above] {$1_{\sigma_c} \phi$} (C')
+%(D) edge node [above] {$\sigma_g 1_{F(f)}$} (F)
+%(F) edge node [right] {$a^\prime$} (D');
+%\end{tikzpicture}
+%\]
+%\[
+%\begin{tikzpicture}[scale=1.5]
+%\node (A) at (0,0) {$1_{G(a)} \sigma_a$};
+%\node (B) at (1,1) {$G(1_a) \sigma_a$};
+%\node (C) at (2,0) {$\sigma_a F(1_a)$};
+%\node (D) at (0.5,-1) {$\sigma_a$};
+%\node (E) at (1.5,-1) {$\sigma_a 1_{F(a)}$};
+%\path[->,font=\scriptsize,>=angle 90]
+%(A) edge node[left]{$\psi 1_{\sigma_a}$} (B)
+%(B) edge node[right]{$\sigma_{1_a}$} (C)
+%(A) edge node [left] {$\ell^\prime$} (D)
+%(D) edge node [above] {${\rho^\prime}^{-1}$} (E)
+%(E) edge node [right] {$1_{\sigma_a} \phi$} (C);
+%\end{tikzpicture}
+%\]
+%Christina: I removed the above, they are not needed I believe
+We denote by $\opICat(\A)$ the 2-category 
+%$[\mathbf{A},\mathbf{Cat}]_{\textnormal{pseudo}}$
+of pseudofunctors, pseudonatural transformations and modifications from an ordinary category $\A$ viewed as a 2-category with trivial 2-cells, into $\bicat{Cat}$.
+Classicaly this has been referred to as the 2-category of \emph{opindexed categories}, since an indexed category is a contravariant pseudofunctor into $\bicat{Cat}$.
+
+A \define{lax monoidal} pseudofunctor is....
+A \define{symmetric lax monoidal} pseudofunctor...
+{\chris Not sure if we need monoidal transformations?}
 
@@
 
+{\chris Moved it into a new section here, amend to make nice with surroundings}
 In this section, we recall the double category of \emph{structured cospans}, a formalism introduced to the first two authors.
@@
 In this section we prove that two different frameworks which utilize symmetric monoidal double categories, namely decorated cospans and structured cospans described in \cref{sec:structuredcospans,DecCospansDoubleCat}, are equivalent.
-This is established by \cref{Equiv}, under some assumptions relevant to the existence of a left adjoints for opfibrations.
+This is established by \cref{Equiv}, under some assumptions relevant to the existence of left adjoints for opfibrations.
 We begin by elaborating this underlying framework, using results mainly from \cite{CV} and \cite{MV}.
 
-{\chris in so much progress}
-In this section we investigate the necessary conditions to obtain a category $\mathrm{X}$ and a left adjoint $L \colon \mathrm{A} \to \mathrm{X}$ from a category $\mathrm{A}$ with finite colimits and a symmetric lax monoidal pseudofunctor $F \colon \mathrm{A} \to \mathbf{Cat}$.
+%In this section we investigate the necessary conditions to obtain a category $\mathrm{X}$ and a left adjoint $L \colon \mathrm{A} \to \mathrm{X}$ from a category $\mathrm{A}$ with finite colimits and a symmetric lax monoidal pseudofunctor $F \colon \mathrm{A} \to \mathbf{Cat}$.
 The main tool that allows us to do this will be the Grothendieck construction which we recall:
-
+First of all we recall some basics regarding opfibrations and their relation to pseudofunctors into $\bicat{Cat}$ via the Grothendieck construction.
+{\chris Below I would suggest to change D to X because that's what we agreed on, and moreover the cocartesian universal property is a bit more general than that!
+However, do we really want to go into such detail?
+Also, more notation changes needed.}
+\begin{defn}
+Let $P \colon \ca{X} \to \ca{A}$ be a functor.
+A morphism $f \colon d_{1} \to d_{2}$ in the category $\mathrm{D}$ is \textbf{cocartesian (with respect to the functor P)} if for any object $d^\prime$ in $\mathrm{D}$ and morphism $g \colon d_{1} \to d^\prime$ and every $p \colon P(d_{2}) \to P(d^\prime)$ such that $P(g)=p P(f)$, there exists a unique $h \colon d_{2} \to d^\prime$ such that $g=hf$ and $p=P(h)$.
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$d^\prime$};
+\node (B) at (0,-1) {$d_{2}$};
+\node (C) at (1.5,-1) {$d_{1}$};
+\node (H) at (2,-0.25) {$P$};
+\node (D) at (2,-.5) {$\mapsto$};
+\node (E) at (3,0) {$P(d^\prime)$};
+\node (F) at (3,-1) {$P(d_{2})$};
+\node (G) at (4.5,-1) {$P(d_{1})$};
+\path[->,font=\scriptsize,>=angle 90]
+(B) edge[dashed] node[above,left]{$\exists ! h$} (A)
+(C) edge node[above,right]{$g$} (A)
+(F) edge node[above,left]{$p=P(h)$} (E)
+(G) edge node[above]{$P(f)$} (F)
+(G) edge node[above,right]{$P(g)$} (E)
+(C)edge node[above]{$f$}(B);
+\end{tikzpicture}
+\]
+\end{defn}
+\begin{defn}
+A functor $P \colon \mathrm{D} \to \mathrm{A}$ is a \textbf{(Grothendieck) opfibration} if for any object $d$ in $\mathbf{D}$ and morphism $f \colon c \to P(d)$ there exists a cocartesian morphism $\phi \colon d^\prime \to d$ such that $P(\phi)=f$.
+\end{defn}
+
+\begin{defn}
+Let $P \colon \mathrm{D} \to \mathrm{A}$ and $P^\prime \colon \mathrm{D^\prime} \to \mathrm{A}$ be opfibrations over a category $\mathrm{A}$.
+A \define{morphism of opfibrations} is a functor $F \colon \mathrm{D} \to \mathrm{D}^\prime$ such that $F(p)$ is cocartesian with respect to $P^\prime$ if $p$ is cocartesian with respect to $P$ and $P=P^\prime F$.
+\end{defn}
+
+Let $\OpFib(\A)$ denote the 2-subcategory of the slice $\mathbf{Cat}/ \A$ of opfibrations over $\A$, opfibrations morphisms and natural transformations with vertical components.
+
+{\chris in progress}
+The Grothendieck construction is a 2-functor $\int F \colon [ \mathrm{A},\mathbf{Cat}] \to \mathbf{Cat}/ \mathrm{A}$ which factors through the image of the embedding $\textnormal{Opfib}(\mathrm{A}) \hookrightarrow \mathbf{Cat} / \mathrm{A}$: $$\int F \colon [ \mathrm{A}, \mathbf{Cat} ] \to \textnormal{Opfib}(\mathrm{A}) \hookrightarrow \mathbf{Cat} / \mathrm{A}.$$
+
+{\chris edit appropriately, notation etc.}
+\begin{thm}\label{thm:Grothendieck}
+    \begin{enumerate}
+        \item Every opfibration $\U \maps \D \to \C$ gives rise to a pseudofunctor $F_U \maps \C {\to}Cat$.
+        \item Every opindexed category $F \maps \C \to Cat$ gives rise to  an opfibration $\U_F \colon \int F\to\C$.
+        \item The above correspondences yield an equivalence of 2-categories 
+        \begin{displaymath}
+            ICat(\C) \simeq opFib(\C)
+        \end{displaymath}
+        so that $F_{\U_F} \cong F$ and $\U_{F_\U} \cong \U$.
+%        \item The above 2-equivalence extends to one between 2-categories of arbitrary-base fibrations and arbitrary-domain indexed categories
+%        \begin{equation}\label{eq:Gr_equiv}
+%        \ICat\simeq\Fib    
+%        \end{equation}
+    \end{enumerate}
+\end{thm}
+
+{\chris I don't mind this presentation of the Grothendieck construction which I admit not having seeing before.
+If we are to keep, we should put a reference.
+Otherwise we could stay more low level about this and just briefly describe what's going on.}
 \begin{defn}
@@
 \end{defn}
-
-\begin{defn}
-Given bicategories $\mathbf{A}$ and $\mathbf{X}$ and 2-functors (possibly lax or oplax) $(F,\phi),(G,\psi) \colon \mathbf{A} \to \mathbf{X}$, a \define{pseudonatural transformation} $\sigma \colon (F,\phi) \to (G,\psi)$ consists of:
-\begin{enumerate}
-\item{for each object $a \in \mathbf{A}$, a morphism $\sigma_a \colon F(a) \to G(a)$ in $\mathbf{X}$ and}
-\item{for every pair of objects $a$ and $b$ of $\mathbf{A}$, we have natural isomorphisms:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$\mathbf{A}(a,b)$};
-\node (B) at (2,0) {$\mathbf{X}(F(a),F(b))$};
-\node (C) at (0,-1) {$\mathbf{X}(G(a),G(b))$};
-\node (D) at (2,-1) {$\mathbf{X}(F(a),G(b))$};
-\node (E) at (1,-0.5) {$\sigma_{a,b} \Nearrow$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$F$} (B)
-(B) edge node[right]{$(\sigma_{b})_*$} (D)
-(A) edge node[left]{$G$} (C)
-(C) edge node[above]{$(\sigma_a)^*$} (D);
-\end{tikzpicture}
-\]
-where $(\sigma_a)^*$ and $(\sigma_b)_*$ are the functors induced by precomposition and postcompositon, respectively.
-Thus for each morphism $f \colon a \to b$ in $\mathbf{A}$, we have an invertible 2-morphism $\sigma_f \colon G(f) \sigma_a \xrightarrow{\sim} \sigma_{b} F(f)$ in $\mathbf{X}$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$F(a)$};
-\node (B) at (1,0) {$F(b)$};
-\node (C) at (0,-1) {$G(a)$};
-\node (D) at (1,-1) {$G(b)$};
-\node (E) at (0.5,-0.5) {$\sigma_f \Nearrow$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$F(f)$} (B)
-(B) edge node[right]{$\sigma_{b}$} (D)
-(A) edge node[left]{$\sigma_a$} (C)
-(C) edge node[above]{$G(f)$} (D);
-\end{tikzpicture}
-\]}
-\end{enumerate}
-such that for each composable pair of morphisms $f \colon a \to b$ and $g \colon b \to c$ of $\mathbf{A}$, the following diagrams commute:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$(G(g)G(f))\sigma_a$};
-\node (A') at (2,0.5) {$G(g)(G(f) \sigma_a)$};
-\node (B) at (0,-0.5) {$G(gf) \sigma_a$};
-\node (C) at (4,0.5) {$G(g) (\sigma_b F(f))$};
-\node (C') at (4,-0.5) {$\sigma_c F(gf)$};
-\node (D) at (6,0.5) {$(G(g) \sigma_b) F(f)$};
-\node (D') at (8,-0.5) {$\sigma_c (F(g)F(f))$};
-\node (F) at (8,0.5) {$(\sigma_c F(g)) F(f)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$a^\prime$} (A')
-(A) edge node[left]{$\psi 1_{\sigma_a}$} (B)
-(A') edge node[above]{$1_{G(g)} \sigma_f$} (C)
-(B) edge node[above]{$\sigma_{gf}$} (C')
-(C) edge node [above] {${a^\prime}^{-1}$} (D)
-(D') edge node [above] {$1_{\sigma_c} \phi$} (C')
-(D) edge node [above] {$\sigma_g 1_{F(f)}$} (F)
-(F) edge node [right] {$a^\prime$} (D');
-\end{tikzpicture}
-\]
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$1_{G(a)} \sigma_a$};
-\node (B) at (1,1) {$G(1_a) \sigma_a$};
-\node (C) at (2,0) {$\sigma_a F(1_a)$};
-\node (D) at (0.5,-1) {$\sigma_a$};
-\node (E) at (1.5,-1) {$\sigma_a 1_{F(a)}$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[left]{$\psi 1_{\sigma_a}$} (B)
-(B) edge node[right]{$\sigma_{1_a}$} (C)
-(A) edge node [left] {$\ell^\prime$} (D)
-(D) edge node [above] {${\rho^\prime}^{-1}$} (E)
-(E) edge node [right] {$1_{\sigma_a} \phi$} (C);
-\end{tikzpicture}
-\]
-\end{defn}
-
-Let $[\mathbf{A},\mathbf{Cat}]_{\textnormal{pseudo}}$ denote the 2-category which has:
-\begin{enumerate}
-\item{objects as pseudofunctors $(F,\phi) \colon \mathbf{A} \to \mathbf{Cat}$,}
-\item{a morphism from a pseudofunctor $(F,\phi) \colon \mathbf{A} \to \mathbf{Cat}$ to another $(G,\psi) \colon \mathbf{A} \to \mathbf{Cat}$ is a pseudonatural transformation $\sigma \colon (F,\phi) \to (G,\psi)$, and}
-\item{2-morphisms as modifications.}
-\end{enumerate}
 
@@
 %\end{defn}
-\begin{defn}
-Let $P \colon \mathrm{D} \to \mathrm{A}$ be a functor.
-A morphism $f \colon d_{1} \to d_{2}$ in the category $\mathrm{D}$ is \textbf{cocartesian (with respect to the functor P)} if for any object $d^\prime$ in $\mathrm{D}$ and morphism $g \colon d_{1} \to d^\prime$ and every $p \colon P(d_{2}) \to P(d^\prime)$ such that $P(g)=p P(f)$, there exists a unique $h \colon d_{2} \to d^\prime$ such that $g=hf$ and $p=P(h)$.
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$d^\prime$};
-\node (B) at (0,-1) {$d_{2}$};
-\node (C) at (1.5,-1) {$d_{1}$};
-\node (H) at (2,-0.25) {$P$};
-\node (D) at (2,-.5) {$\mapsto$};
-\node (E) at (3,0) {$P(d^\prime)$};
-\node (F) at (3,-1) {$P(d_{2})$};
-\node (G) at (4.5,-1) {$P(d_{1})$};
-\path[->,font=\scriptsize,>=angle 90]
-(B) edge[dashed] node[above,left]{$\exists ! h$} (A)
-(C) edge node[above,right]{$g$} (A)
-(F) edge node[above,left]{$p=P(h)$} (E)
-(G) edge node[above]{$P(f)$} (F)
-(G) edge node[above,right]{$P(g)$} (E)
-(C)edge node[above]{$f$}(B);
-\end{tikzpicture}
-\]
-\end{defn}
-\begin{defn}
-A functor $P \colon \mathrm{D} \to \mathrm{A}$ is a \textbf{(Grothendieck) opfibration} if for any object $d$ in $\mathbf{D}$ and morphism $f \colon c \to P(d)$ there exists a cocartesian morphism $\phi \colon d^\prime \to d$ such that $P(\phi)=f$.
-\end{defn}
-
-\begin{defn}
-Let $P \colon \mathrm{D} \to \mathrm{A}$ and $P^\prime \colon \mathrm{D^\prime} \to \mathrm{A}$ be opfibrations over a category $\mathrm{A}$.
-A \define{morphism of opfibrations} is a functor $F \colon \mathrm{D} \to \mathrm{D}^\prime$ such that $F(p)$ is cocartesian with respect to $P^\prime$ if $p$ is cocartesian with respect to $P$ and $P=P^\prime F$.
-\end{defn}
-
-Let Opfib$(\mathrm{A})$ denote the 2-category of opfibrations over $\mathrm{A}$ which has:
-\begin{enumerate}
-\item{objects as opfibrations $P \colon \mathrm{D} \to \mathrm{A}$,}
-\item{morphisms as morphisms of opfibrations, and}
-\item{a 2-morphism from one morphism of opfibrations $F \colon P \to P^\prime$ to another $F^\prime \colon P \to P^\prime$ is a natural transformation $\alpha \colon F \to F^\prime$ such that the left whiskering $P^\prime \alpha$ is trivial.}
-\end{enumerate}
-
-The 2-category Opfib$(\mathrm{A})$ is a 2-subcategory of $\mathbf{Cat}/ \mathrm{A}$ where $\mathbf{Cat} / \mathrm{A}$ is the 2-category of functors over $\mathrm{A}$.
-The Grothendieck construction is a 2-functor $\int F \colon [ \mathrm{A},\mathbf{Cat}] \to \mathbf{Cat}/ \mathrm{A}$ which factors through the image of the embedding $\textnormal{Opfib}(\mathrm{A}) \hookrightarrow \mathbf{Cat} / \mathrm{A}$: $$\int F \colon [ \mathrm{A}, \mathbf{Cat} ] \to \textnormal{Opfib}(\mathrm{A}) \hookrightarrow \mathbf{Cat} / \mathrm{A}.$$
-
-{\chris edit appropriately, notation etc.}
-\begin{thm}\label{thm:Grothendieck}
-    \begin{enumerate}
-        \item Every opfibration $\U \maps \D \to \C$ gives rise to a pseudofunctor $F_U \maps \C {\to}Cat$.
-        \item Every opindexed category $F \maps \C \to Cat$ gives rise to  an opfibration $\U_F \colon \int F\to\C$.
-        \item The above correspondences yield an equivalence of 2-categories 
-        \begin{displaymath}
-            ICat(\C) \simeq opFib(\C)
-        \end{displaymath}
-        so that $F_{\U_F} \cong F$ and $\U_{F_\U} \cong \U$.
-%        \item The above 2-equivalence extends to one between 2-categories of arbitrary-base fibrations and arbitrary-domain indexed categories
-%        \begin{equation}\label{eq:Gr_equiv}
-%        \ICat\simeq\Fib    
-%        \end{equation}
-    \end{enumerate}
-\end{thm}
 
@@
 
-under the conditions required from the previous section that allow for a left adjoint $L \colon \mathsf{A} \to \mathsf{X}$ to be obtained from a symmetric lax {\chris have to specify lax VS weak which is the standard terminology, happy to use lax though} monoidal pseudofunctor $F \colon \mathsf{A} \to \mathbf{Cat}$.
-%The double category version of decorated cospans is given in Section \ref{DecCospansDoubleCat}.
-
-We now show that these two symmetric monoidal double categories are equivalent.
+In the above described setting, a symmetric lax monoidal functor gives rise to a double category of decorated cospans as well as a double category of structured cospans.
+The result below establishes their equivalence.
 

### 2019-05-01 EquivCompFrameworks_20180911kc.tex
more tidying

@@
 Let $\OpFib(\A)$ denote the 2-subcategory of the slice $\mathbf{Cat}/ \A$ of opfibrations over $\A$, opfibrations morphisms and natural transformations with vertical components.
-
-{\chris in progress}
-The Grothendieck construction is a 2-functor $\int F \colon [ \mathrm{A},\mathbf{Cat}] \to \mathbf{Cat}/ \mathrm{A}$ which factors through the image of the embedding $\textnormal{Opfib}(\mathrm{A}) \hookrightarrow \mathbf{Cat} / \mathrm{A}$: $$\int F \colon [ \mathrm{A}, \mathbf{Cat} ] \to \textnormal{Opfib}(\mathrm{A}) \hookrightarrow \mathbf{Cat} / \mathrm{A}.$$
-
-{\chris edit appropriately, notation etc.}
-\begin{thm}\label{thm:Grothendieck}
+In fact, there is a 2-equivalence between opfibrations over $\A$ and pseudofunctors $\A\to\ca{Cat}$ induced by the so-called Grothendieck construction.
+
+{\chris I don't mind this presentation of the Grothendieck construction which I admit not having seeing before.
+If we are to keep, we should put a reference.
+Otherwise we could stay more low level about this and just briefly describe what's going on.}
+\begin{defn}
+Let $\mathbf{Cat}_{\textnormal{lax},\star}$ denote the \define{2-category of lax-pointed categories} which has:
+\begin{enumerate}
+\item{objects as pairs $(\mathrm{A},c)$ where $\mathrm{A}$ is a category and $c$ is an object of $\mathrm{A}$, and}
+\item{a morphism from $(\mathrm{A},c)$ to $(\mathrm{X},y)$ is a pair $(F,f)$ where $F \colon \mathrm{A} \to \mathrm{X}$ is a functor and $f \colon F(c) \to y$ is a morphism in $\mathrm{X}$.}
+\end{enumerate}
+\end{defn}
+
+\begin{defn}
+Given a pseudofunctor $F \colon \mathrm{A} \to \mathbf{Cat}$, the \define{Grothendieck construction of} $F$ is given by the `strict 2-pullback' of the following cospan:
+ \[
+\begin{tikzpicture}[scale=1.5]
+\node (D) at (1,1) {$\int F$};
+\node (A) at (0,0) {$\mathrm{A}$};
+\node (B) at (1,-1) {$\mathbf{Cat}$};
+\node (C) at (2,0) {$\mathbf{Cat}_{\textnormal{lax},\star}$};
+\path[->,font=\scriptsize,>=angle 90]
+(D) edge[dashed] node[above]{$p$} (A)
+(D) edge[dashed] node[above]{$q$} (C)
+(A) edge node[below]{$F$} (B)
+(C) edge node[below]{$P$} (B);
+\end{tikzpicture}
+\]
+where $P \colon \mathbf{Cat}_{\textnormal{lax},\star} \to \mathbf{Cat}$ is the forgetful functor. This means that $\int F$ is a category which has:
+\begin{enumerate}
+\item{objects as pairs $(c, d \in F(c))$ and}
+\item{a morphism from $(c, d \in F(c))$ to $(c^\prime, d^\prime \in F(c^\prime))$ is a pair $(f \colon c \to c^\prime,\alpha \colon F(f)(d) \to d^\prime)$.
+
+This can also be thought of as a morphism and a 2-morphism:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$\star$};
+\node (B) at (1,0.5) {$F(c)$};
+\node (C) at (1,-0.5) {$F(c^\prime)$};
+\node (D) at (2,0.5) {$c$};
+\node (E) at (2,-0.5) {$c^\prime$};
+\node (F) at (0.65,0) {$\Swarrow \alpha$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$d$} (B)
+(B) edge node[right]{$F(f)$} (C)
+(A) edge node[below]{$d^\prime$} (C)
+(D) edge node[left] {$f$} (E);
+\end{tikzpicture}
+\]
+}
+\end{enumerate}
+\end{defn}
+
+The Grothendieck construction gives rise to a 2-functor $[\A,\mathbf{Cat}] \to \mathbf{Cat}/ \mathrm{A}$ which factors through the image of the embedding $\textnormal{Opfib}(\mathrm{A}) \hookrightarrow \mathbf{Cat} / \mathrm{A}$ as per the following theorem.
+%: $$\int F \colon [ \mathrm{A}, \mathbf{Cat} ] \to \textnormal{Opfib}(\mathrm{A}) \hookrightarrow \mathbf{Cat} / \mathrm{A}.$$
+
+\begin{thm}\label{thm:Grothendieck}\hfill
     \begin{enumerate}
@@
 \end{thm}
-
-{\chris I don't mind this presentation of the Grothendieck construction which I admit not having seeing before.
-If we are to keep, we should put a reference.
-Otherwise we could stay more low level about this and just briefly describe what's going on.}
-\begin{defn}
-Let $\mathbf{Cat}_{\textnormal{lax},\star}$ denote the \define{2-category of lax-pointed categories} which has:
-\begin{enumerate}
-\item{objects as pairs $(\mathrm{A},c)$ where $\mathrm{A}$ is a category and $c$ is an object of $\mathrm{A}$, and}
-\item{a morphism from $(\mathrm{A},c)$ to $(\mathrm{X},y)$ is a pair $(F,f)$ where $F \colon \mathrm{A} \to \mathrm{X}$ is a functor and $f \colon F(c) \to y$ is a morphism in $\mathrm{X}$.}
-\end{enumerate}
-\end{defn}
-
-\begin{defn}
-Given a pseudofunctor $F \colon \mathrm{A} \to \mathbf{Cat}$, the \define{Grothendieck construction of} $F$ is given by the `strict 2-pullback' of the following cospan:
- \[
-\begin{tikzpicture}[scale=1.5]
-\node (D) at (1,1) {$\int F$};
-\node (A) at (0,0) {$\mathrm{A}$};
-\node (B) at (1,-1) {$\mathbf{Cat}$};
-\node (C) at (2,0) {$\mathbf{Cat}_{\textnormal{lax},\star}$};
-\path[->,font=\scriptsize,>=angle 90]
-(D) edge[dashed] node[above]{$p$} (A)
-(D) edge[dashed] node[above]{$q$} (C)
-(A) edge node[below]{$F$} (B)
-(C) edge node[below]{$P$} (B);
-\end{tikzpicture}
-\]
-where $P \colon \mathbf{Cat}_{\textnormal{lax},\star} \to \mathbf{Cat}$ is the forgetful functor. This means that $\int F$ is a category which has:
-\begin{enumerate}
-\item{objects as pairs $(c, d \in F(c))$ and}
-\item{a morphism from $(c, d \in F(c))$ to $(c^\prime, d^\prime \in F(c^\prime))$ is a pair $(f \colon c \to c^\prime,\alpha \colon F(f)(d) \to d^\prime)$.
-
-This can also be thought of as a morphism and a 2-morphism:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$\star$};
-\node (B) at (1,0.5) {$F(c)$};
-\node (C) at (1,-0.5) {$F(c^\prime)$};
-\node (D) at (2,0.5) {$c$};
-\node (E) at (2,-0.5) {$c^\prime$};
-\node (F) at (0.65,0) {$\Swarrow \alpha$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$d$} (B)
-(B) edge node[right]{$F(f)$} (C)
-(A) edge node[below]{$d^\prime$} (C)
-(D) edge node[left] {$f$} (E);
-\end{tikzpicture}
-\]
-}
-\end{enumerate}
-\end{defn}
 
@@
 
-Under certain conditions, the functor resulting from the Grothendieck construction $p \colon \int{F} \to \mathrm{A}$ will be right adjoint to the desired left adjoint $L \colon \mathrm{A} \to \mathrm{X}$.
-
-{\chris  moved and motivated appropriately}
+{\chris A little bit for monoidal Grothendieck here}
+
+For our purposes, we are interested in the fact that under certain conditions, the induced monoidal opfibration by the Grothendieck construction $ \int{F} \to \A$ will be a right adjoint to some adjoint $L_F \colon \A \to \X$, and moreover the unit of the adjunction is the identity; this is called \emph{lari} in [Gray].
+
+{\chris in progress, probably split up in two}
 \begin{thm}\label{thm:mainthmDX}\cite{CV}
-Suppose that $\D$ and $\C$ have chosen pushouts and initial objects, and a functor $\U\colon\D\to\C$ strictly preserves them.
+Suppose that $\X$ and $\A$ have chosen pushouts and initial objects, and a functor $\U\colon\X\to\A$ strictly preserves them.
 Then $\U$ is a right adjoint left inverse if and only if $\U$ is an opfibration.

### 2019-05-02 EquivCompFrameworks_20180911kc.tex
wrote down all pieces of BRIDGE!

@@
 Then we obtain an underlying symmetric monoidal bicategory $F \mathbf{Csp}$ using a result of Shulman \cite{Shul} and then finally decategorify the obtained symmetric monoidal bicategory to obtain a symmetric monoidal category $F$Csp which is a generalization of Fong's original decorated cospan category \cite{Fong}.
-\begin{thm}
+\begin{thm}\label{thm:decoratedcospans}
 Let $\mathsf{A}$ be a category with finite colimits and $F \colon \mathsf{A} \to \mathbf{Cat}$ a lax monoidal pseudofunctor. Then there exists a (pseudo) double category $F\mathbb{C}$sp which has:
@@
 \section{An equivalence of symmetric monoidal double categories} \label{EquivDoubleCats}
-In this section we prove that two different frameworks which utilize symmetric monoidal double categories, namely decorated cospans and structured cospans described in \cref{sec:structuredcospans,DecCospansDoubleCat}, are equivalent.
-This is established by \cref{Equiv}, under some assumptions relevant to the existence of left adjoints for opfibrations.
-We begin by elaborating this underlying framework, using results mainly from \cite{CV} and \cite{MV}.
+In this section we prove that two different frameworks which utilize symmetric monoidal double categories, namely decorated cospans and structured cospans described in \cref{sec:structuredcospans,DecCospansDoubleCat}, are equivalent under certain assumptions.
+This is established by \cref{Equiv} which is based on a framework relevant to the existence of left adjoints for opfibrations.
+We begin by sketching this underlying framework, which is worked out in detail in \cite{CV} and \cite{MV}.
+Standard material on fibrations and the Grothendieck construction can be found for example in \cite{Herm}, \cite{Borc}.
 
@@
     \begin{enumerate}
-        \item Every opfibration $\U \maps \D \to \C$ gives rise to a pseudofunctor $F_U \maps \C {\to}Cat$.
+        \item Every opfibration $\U \maps \D \to \C$ gives rise to a pseudofunctor $F_U \maps \C \to \bicat{Cat}$.
         \item Every opindexed category $F \maps \C \to Cat$ gives rise to  an opfibration $\U_F \colon \int F\to\C$.
@@
 
-{\chris A little bit for monoidal Grothendieck here}
-
-For our purposes, we are interested in the fact that under certain conditions, the induced monoidal opfibration by the Grothendieck construction $ \int{F} \to \A$ will be a right adjoint to some adjoint $L_F \colon \A \to \X$, and moreover the unit of the adjunction is the identity; this is called \emph{lari} in [Gray].
-
-{\chris in progress, probably split up in two}
-\begin{thm}\label{thm:mainthmDX}\cite{CV}
-Suppose that $\X$ and $\A$ have chosen pushouts and initial objects, and a functor $\U\colon\X\to\A$ strictly preserves them.
-Then $\U$ is a right adjoint left inverse if and only if $\U$ is an opfibration.
-\end{thm}
-
-In the above described setting, a symmetric lax monoidal functor gives rise to a double category of decorated cospans as well as a double category of structured cospans.
-The result below establishes their equivalence.
+In \cite{MV}, the Grothendieck construction is generalized to the monoidal setting, namely lax monoidal structures on a pseudofunctor $F\colon\A\to\bicat{Cat}$ bijectively correspond to monoidal structures on the total category $\int F$ such that the induced opfibration is a strict monoidal functor and $\otimes_{\int F}$ is cartesian, see \cite[Thm.
+3.10]{MV}.
+If the monoidal category $\A$ is in fact cocartesian monoidal, there is a further correspondence of the two structures with a sheer pseudofunctor $F\colon\A\to\ca{MonCat}$:
+\begin{gather}
+\textrm{lax monoidal pseudofunctors }F\colon(\A,+,0)\to(\bicat{Cat},\times,1) \\
+\Updownarrow \\
+\textrm{monoidal opfibrations }U\colon(\X,\otimes,I)\to(\A,+,0) \label{monGroth}\\
+\Updownarrow \\
+\textrm{pseudofunctors }F\colon\A\to\bicat{MonCat}
+\end{gather}
+where the second equivalence was already observed by Shulman in \cite{Shul2}.
+Moreover, the above further restricts to the case when the Grothendieck category is specifically cocartesian monoidal itself, see \cite[Cor.
+4.8]{MV} for more details.
+Then, the monoidal opfibration clauses for $U\colon(\X,+,0)\to(\A,+,0)$ in fact translate to the functor (strictly) preserving coproducts and the initial object, and bijectively correspond to pseudofunctors $F\colon\A\to\bicat{cocartCat}$ into the 2-category of cocartesian categories, functors that preserve coproducts and initial objects and natural transformations.
+
+Finally, using the following result we can further restrict to our current case of interest, namely opfibrations that also preserve pushouts, i.e.
+all finite colimits.
+Of course this is more general since it relates the existence of any class of colimits in the total category of an opfibration to their existence in the fibres; for more details, see \cite{Herm}.
+
+\begin{lem}\label{lem:fibrewiselimits}
+Suppose $\ca{J}$ is a small category and $\U\colon\X\to\A$ is an opfibration. If $\A$ has $\ca{J}$-colimits,
+the following are equivalent:
+\begin{enumerate}
+ \item all fibres have $\ca{J}$-colimits, and the reindexing functors preserve them;
+ \item $\X$ has $\ca{J}$-colimits, and $\U$ strictly preserves them.
+\end{enumerate}
+\end{lem}
+
+The first part formulates the existence of colimits \emph{locally} in each fiber, which can equivalently be expressed by the corresponding pseudofunctor $F\colon\A\to\bicat{Cat}$ landing on the sub-2-category $\bicat{fcocCat}$ of finitely cocomplete categories and functors that preserve colimits; the second part formulates the existence of colimits \emph{globally} in the total category $\int F$.
+Combining these, we can deduce the following.
+
+\begin{cor}\label{cor:fcocMonGroth}
+ Suppose $\A$ is a finitely cocomplete category and $F\colon(\A,+,0)\to(\bicat{Cat},\times,1)$ is a lax monoidal pseudofunctor.
+If its corresponding pseudofunctor $\A\to\bicat{MonCat}$ via \cref{monGroth}
+ factors through $\bicat{fcocCat}$, then the Grothendieck category $\int F$ has all finite colimits and the induced opfibration $\U_F\colon\int F\to\A$ preserves them. 
+\end{cor}
+
+On a different but related subject, for our purposes we are interested in the existence of a left adjoint $L_F \colon \A \to \X$ for the induced monoidal opfibration $ \int{F} \to \A$ by the Grothendieck construction as discussed above.
+The following result provides sufficient conditions for that, which go hand-in-hand with \cref{cor:fcocMonGroth}.
+
+\begin{prop}\cite[Prop.\ 4.4]{Gray} \label{prop:opfibtolari}
+  Let $\U \colon\D \to \C$ be an opfibration. Then
+  $\U$ is a right adjoint `left inverse', a.k.a the unit is the identity, if (and only if) its fibers have
+  initial objects which are preserved by the
+  reindexing functors.
+\end{prop}
+%will be a right adjoint to some adjoint , and moreover the unit of the adjunction is the identity; this is called \emph{lari} in [Gray].
+
+In the opposite direction, we also have the following result. For a discussion on the unusual strict cocontinuity condition, we refer the reader to \cite{CV}.
+
+\begin{prop}\label{prop:CV}\cite[Prop. \ 3.3]{CV}
+Suppose $\U\colon\X\to\A$ is a right adjoint `left inverse'. If $\X$ and $\A$ have chosen pushouts and initial objects and $\U$ strictly preserves them, then $\U$ is an opfibration.
+\end{prop}
+%Christina: do we need this direction after all? Discuss.
+
+%\begin{thm}\label{thm:mainthmDX}\cite{CV}
+%Suppose that $\X$ and $\A$ have chosen pushouts and initial objects, and a functor $\U\colon\X\to\A$ strictly preserves them.
+Then $\U$ is a right %adjoint left inverse if and only if $\U$ is an opfibration.
+%\end{thm}
+
+We have now laid all the necessary theoretical background to formally establish an equivalence between the double category of decorated cospans and the double category of structured cospans constructed from a symmetric lax monoidal pseudofunctor into $\bicat{Cat}$.
 
 \begin{thm}\label{Equiv}
-Let $\mathsf{A}$ and $\mathsf{X}$ be categories with finite colimits, and $F \colon(\mathsf{A},+,0) \to (\mathbf{Cat},\times,\mathbf{1})$ a symmetric lax monoidal pseudofunctor.
-The symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$ of decorated cospans is equivalent to the symmetric monoidal double category $_{L_F} \mathbb{C}\textnormal{sp}(\mathsf{X})$ of structured cospans, where $L_F \colon \mathsf{A} \to \int{F}$ is the left adjoint of the induced Grothendieck opfibration $\U_F\colon \int{F} \to \mathsf{A}$ by \cref{thm:Grothendieck} under the assumptions of \cref{thm:mainthmDX}.
+Suppose $\mathsf{A}$ and $\mathsf{X}$ are finitely cocomplete categories and $F \colon(\mathsf{A},+,0) \to (\mathbf{Cat},\times,\mathbf{1})$ is a symmetric lax monoidal pseudofunctor.
+%such that as an ordinary pseudofunctor, it factors through $\bicat{fcocCat}$.
+The symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$ of decorated cospans (\cref{thm:decoratedcospans}) is equivalent to the symmetric monoidal double category $_{L_F} \mathbb{C}\textnormal{sp}(\mathsf{X})$ of structured cospans (\cref{SC}), where $L_F \colon \mathsf{A} \to \int{F}$ is the left adjoint of the induced Grothendieck opfibration $\U_F\colon \int{F} \to \mathsf{A}$ by \cref{thm:Grothendieck}, under the assumptions of \cref{cor:fcocMonGroth}.
 \end{thm}
 \begin{proof}
+{\chris in progress}
 As explained in (ref), the double category of decorated cospans $\dcsp{F}$ has $\A$ as its category of objects and vertical 1-morphisms, whereas horizontal 1-cells $a\tickar b$ are cospans $\cspn{a}{c}{b}{}{}$ in $\A$ along with $d\in F(c)$ and 2-morphisms are cospan maps $k\colon c\to c'$ such that $(Fk)(d)=d'$.
@@
 
-{\chris in progress}
 To prove this, we define a double functor $\mathbb{E} \colon _L \mathbb{C}\textnormal{sp}(\mathsf{X}) \to F\mathbb{C}\textnormal{sp}$ as follows: the object component of the double functor $\mathbb{E}$ is given by $\mathbb{E}_0 = \id_{\mathsf{A}}$ as both double categories $_L \mathbb{C}\textnormal{sp}(\mathrm{X})$ and $F\mathbb{C}\textnormal{sp}$ have objects and morphisms of $\mathsf{A}$ as objects and vertical 1-morphisms, respectively.
@@
 
+\bibitem{Borc} F. \ Borceux, Handbook of categorical algebra. 2, volume 51 of Encyclopedia of Mathematics and its Applications,
+Cambridge University Press, 1994
+
 \bibitem{Brown1} R.\ Brown and C.\ B.\ Spencer, Double groupoids and crossed modules, 
@@
 
+\bibitem{Gray} J. \ Gray, Fibred and Cofibred categories, Proc. Conf. Categorical Algebra (La Jolla, California, 1965), 21---83, New York, 1966
+
 %\bibitem{Haug} R.\ Haugseng, Iterated spans and ``classical" topological field theories. Available as \href{https://arxiv.org/abs/1409.0837}{arXiv:1409.0837}.
+
+\bibitem{Herm} C. \ Hermida, Fibrations, logical predicates and indeterminates, PhD Thesis, University of Edinburgh, 1993.
 

### 2019-05-03 EquivCompFrameworks_20180911kc.tex
cleaned up preamble a bit and commented some stuff out after the equivalence theorem

@@
 
+\begin{comment}
 We can also define the part of the double equivalence $\mathbb{G} \colon F\mathbb{C}\textnormal{sp} \to {_L \mathbb{C} \textnormal{sp}(\mathsf{X})}$ which goes in the other direction: again, the object component of this double functor will be $\mathbb{G}_0 = \id_{\mathsf{A}}$.
@@
 commutes.
+\end{comment}
 
@@
 The first two of these were first done using Fong's theory of decorated cospans and then extended by the first two authors using structured cospans.
-The last two of these were also extended by being realized as double functors between double categories \cite{BC,BM} and is discussed in Chapter \ref{Chapter6}.
+The last two of these were also extended by being realized as double functors between double categories in recent works \cite{BC,BM}.
 \subsection{Graphs}

### 2019-05-07 EquivCompFrameworks_20180911kc.tex
bridge is now polished and ready for review

@@
 \item {\chris Discuss the name of Decorated and Structured cospan double categories one last time? :)}
-\item {\chris I'm starting a few macros to help us write faster and adjust accordingly if we need to later.
-On that note, could Kenny `clean' the preamble at some point?
-I.e.
-erase the commands not used here, to make it easier to navigate?
-I would do it but I wouldn't want to erase something you use!}
 \item {\chris Where should we put some standard things we use? For exampe, lax monoidal pseudofunctor should be recalled early. Together with pseudonatural transformations I believe.}
@@
 %Christina: I removed the above, they are not needed I believe
-We denote by $\opICat(\A)$ the 2-category 
-%$[\mathbf{A},\mathbf{Cat}]_{\textnormal{pseudo}}$
+We denote by $[\A,\bicat{Cat}]_\pse$ the 2-category 
 of pseudofunctors, pseudonatural transformations and modifications from an ordinary category $\A$ viewed as a 2-category with trivial 2-cells, into $\bicat{Cat}$.
@@
 
-%\section{From pseudofunctors to left adjoints}\label{some other section}
-
 \section{An equivalence of symmetric monoidal double categories} \label{EquivDoubleCats}
-In this section we prove that two different frameworks which utilize symmetric monoidal double categories, namely decorated cospans and structured cospans described in \cref{sec:structuredcospans,DecCospansDoubleCat}, are equivalent under certain assumptions.
-This is established by \cref{Equiv} which is based on a framework relevant to the existence of left adjoints for opfibrations.
-We begin by sketching this underlying framework, which is worked out in detail in \cite{CV} and \cite{MV}.
-Standard material on fibrations and the Grothendieck construction can be found for example in \cite{Herm}, \cite{Borc}.
-
+In this section we prove that two different frameworks which utilize symmetric monoidal double categories, namely structured cospans and decorated cospans described respectively in \cref{DecCospansDoubleCat,sec:structuredcospans}, are equivalent under certain assumptions.
+This is established by \cref{Equiv}, which relies on conditions relevant to the existence of left adjoints for opfibrations.
+We begin by sketching this underlying framework, which is worked out in detail in \cite{MV} and \cite{CV}.
 %In this section we investigate the necessary conditions to obtain a category $\mathrm{X}$ and a left adjoint $L \colon \mathrm{A} \to \mathrm{X}$ from a category $\mathrm{A}$ with finite colimits and a symmetric lax monoidal pseudofunctor $F \colon \mathrm{A} \to \mathbf{Cat}$.
 The main tool that allows us to do this will be the Grothendieck construction which we recall:
-First of all we recall some basics regarding opfibrations and their relation to pseudofunctors into $\bicat{Cat}$ via the Grothendieck construction.
-{\chris Below I would suggest to change D to X because that's what we agreed on, and moreover the cocartesian universal property is a bit more general than that!
-However, do we really want to go into such detail?
-Also, more notation changes needed.}
-\begin{defn}
-Let $P \colon \ca{X} \to \ca{A}$ be a functor.
+First of all, we recall some basics regarding opfibrations and their relation to pseudofunctors into $\bicat{Cat}$ via the Grothendieck construction.
+Standard material on fibration theory and the Grothendieck construction can be found for example in \cite{Herm}, \cite{Borc}.
+
+A functor $U \maps \X \to \A$ is a \textbf{Grothendieck opfibration} if for every $x\in\X$ with $U(x)=a$ and $f \colon a \to b$ in $\A$, there exists a \textbf{cocartesian lifting} of $x$ along $f$, namely a morphism $\beta$ in $\X$ with domain $x$ above $f$ with the following universal property: for any $g\colon b\to b'$ in $\A$ and $\gamma\colon x\to y'$ in $\X$ above the composite $g\circ f$, there exists a unique $\delta\colon y\to y'$ such that $U(\delta)=g$ and $\gamma=\delta\circ\beta$ as shown below
+\begin{displaymath}
+\xymatrix @R=.1in @C=.6in
+{&& y'\ar @{.>}@/_/[dd] &&\\
+x\ar[r]_-{\beta} \ar @{.>}@/_/[dd]
+\ar[urr]^-{\gamma} & 
+y \ar @{.>}@/_/[dd] \ar @{-->}[ur]_-{\exists! \delta}
+&& \textrm{in }\X\\
+&& b' &&\\
+a\ar[r]_-{f=U\beta} \ar[urr]^-{g\circ f=U\gamma}
+ & b \ar[ur]_-g && \textrm{in }\A}
+\end{displaymath}
+
+%\begin{defn}
+%Let $P \colon \ca{X} \to \ca{A}$ be a functor.
 A morphism $f \colon d_{1} \to d_{2}$ in the category $\mathrm{D}$ is \textbf{cocartesian (with respect to the functor P)} if for any object $d^\prime$ in $\mathrm{D}$ and morphism $g \colon d_{1} \to d^\prime$ and every $p \colon P(d_{2}) \to P(d^\prime)$ such that $P(g)=p P(f)$, there exists a unique $h \colon d_{2} \to d^\prime$ such that $g=hf$ and $p=P(h)$.
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$d^\prime$};
-\node (B) at (0,-1) {$d_{2}$};
-\node (C) at (1.5,-1) {$d_{1}$};
-\node (H) at (2,-0.25) {$P$};
-\node (D) at (2,-.5) {$\mapsto$};
-\node (E) at (3,0) {$P(d^\prime)$};
-\node (F) at (3,-1) {$P(d_{2})$};
-\node (G) at (4.5,-1) {$P(d_{1})$};
-\path[->,font=\scriptsize,>=angle 90]
-(B) edge[dashed] node[above,left]{$\exists ! h$} (A)
-(C) edge node[above,right]{$g$} (A)
-(F) edge node[above,left]{$p=P(h)$} (E)
-(G) edge node[above]{$P(f)$} (F)
-(G) edge node[above,right]{$P(g)$} (E)
-(C)edge node[above]{$f$}(B);
-\end{tikzpicture}
-\]
-\end{defn}
-\begin{defn}
-A functor $P \colon \mathrm{D} \to \mathrm{A}$ is a \textbf{(Grothendieck) opfibration} if for any object $d$ in $\mathbf{D}$ and morphism $f \colon c \to P(d)$ there exists a cocartesian morphism $\phi \colon d^\prime \to d$ such that $P(\phi)=f$.
-\end{defn}
-
-\begin{defn}
-Let $P \colon \mathrm{D} \to \mathrm{A}$ and $P^\prime \colon \mathrm{D^\prime} \to \mathrm{A}$ be opfibrations over a category $\mathrm{A}$.
+%\[
+%\begin{tikzpicture}[scale=1.5]
+%\node (A) at (0,0) {$d^\prime$};
+%\node (B) at (0,-1) {$d_{2}$};
+%\node (C) at (1.5,-1) {$d_{1}$};
+%\node (H) at (2,-0.25) {$P$};
+%\node (D) at (2,-.5) {$\mapsto$};
+%\node (E) at (3,0) {$P(d^\prime)$};
+%\node (F) at (3,-1) {$P(d_{2})$};
+%\node (G) at (4.5,-1) {$P(d_{1})$};
+%\path[->,font=\scriptsize,>=angle 90]
+%(B) edge[dashed] node[above,left]{$\exists ! h$} (A)
+%(C) edge node[above,right]{$g$} (A)
+%(F) edge node[above,left]{$p=P(h)$} (E)
+%(G) edge node[above]{$P(f)$} (F)
+%(G) edge node[above,right]{$P(g)$} (E)
+%(C)edge node[above]{$f$}(B);
+%\end{tikzpicture}
+%\]
+%\end{defn}
+%\begin{defn}
+%A functor $P \colon \mathrm{D} \to \mathrm{A}$ is a \textbf{(Grothendieck) opfibration} if for any object $d$ in $\mathbf{D}$ and morphism $f \colon c %\to P(d)$ there exists a cocartesian morphism $\phi \colon d^\prime \to d$ such that $P(\phi)=f$.
+%\end{defn}
+%\begin{defn}
+%Let $P \colon \mathrm{D} \to \mathrm{A}$ and $P^\prime \colon \mathrm{D^\prime} \to \mathrm{A}$ be opfibrations over a category $\mathrm{A}$.
 A \define{morphism of opfibrations} is a functor $F \colon \mathrm{D} \to \mathrm{D}^\prime$ such that $F(p)$ is cocartesian with respect to $P^\prime$ if $p$ is cocartesian with respect to $P$ and $P=P^\prime F$.
-\end{defn}
-
-Let $\OpFib(\A)$ denote the 2-subcategory of the slice $\mathbf{Cat}/ \A$ of opfibrations over $\A$, opfibrations morphisms and natural transformations with vertical components.
-In fact, there is a 2-equivalence between opfibrations over $\A$ and pseudofunctors $\A\to\ca{Cat}$ induced by the so-called Grothendieck construction.
-
-{\chris I don't mind this presentation of the Grothendieck construction which I admit not having seeing before.
+%\end{defn}
+The category $\X$ is called the \textbf{total} category, whereas $\A$ is the \textbf{base} category of the opfibration. 
+%Christina: decide later if needed
+%Notice that as a result,
+%any arrow in the total category of an opfibration factorizes uniquely into a vertical morphism (above the identity) followed by a (co)cartesian one:
+%\[
+%\xymatrix @C=.4in @R=.2in
+%{x \ar @{.>}[dd]\ar[rr]^\gamma \ar[drr]_-{\Cocart(g,C)} && D &\\
+%&& f_!C \ar @{-->}[u]_-{\delta} \ar @{.>}[d] & \textrm{in }\C  \\
+%X\ar[rr]_-{g} && Y & \textrm{in }\X.}
+%\]
+Let $\OpFib(\A)$ denote the 2-subcategory of the slice 2-category $\mathbf{Cat}/ \A$ of opfibrations over $\A$, functors that preserve cocartesian liftings and natural transformations with vertical components, namely morphisms in the total category that map to identities in the base category.
+In fact, there is a 2-equivalence between opfibrations and pseudofunctors induced by the so-called Grothendieck construction:
+%{\chris I don't mind this presentation of the Grothendieck construction which I admit not having seeing before.
 If we are to keep, we should put a reference.
 Otherwise we could stay more low level about this and just briefly describe what's going on.}
-\begin{defn}
-Let $\mathbf{Cat}_{\textnormal{lax},\star}$ denote the \define{2-category of lax-pointed categories} which has:
-\begin{enumerate}
-\item{objects as pairs $(\mathrm{A},c)$ where $\mathrm{A}$ is a category and $c$ is an object of $\mathrm{A}$, and}
-\item{a morphism from $(\mathrm{A},c)$ to $(\mathrm{X},y)$ is a pair $(F,f)$ where $F \colon \mathrm{A} \to \mathrm{X}$ is a functor and $f \colon F(c) \to y$ is a morphism in $\mathrm{X}$.}
-\end{enumerate}
-\end{defn}
-
-\begin{defn}
-Given a pseudofunctor $F \colon \mathrm{A} \to \mathbf{Cat}$, the \define{Grothendieck construction of} $F$ is given by the `strict 2-pullback' of the following cospan:
- \[
-\begin{tikzpicture}[scale=1.5]
-\node (D) at (1,1) {$\int F$};
-\node (A) at (0,0) {$\mathrm{A}$};
-\node (B) at (1,-1) {$\mathbf{Cat}$};
-\node (C) at (2,0) {$\mathbf{Cat}_{\textnormal{lax},\star}$};
-\path[->,font=\scriptsize,>=angle 90]
-(D) edge[dashed] node[above]{$p$} (A)
-(D) edge[dashed] node[above]{$q$} (C)
-(A) edge node[below]{$F$} (B)
-(C) edge node[below]{$P$} (B);
-\end{tikzpicture}
-\]
-where $P \colon \mathbf{Cat}_{\textnormal{lax},\star} \to \mathbf{Cat}$ is the forgetful functor. This means that $\int F$ is a category which has:
-\begin{enumerate}
-\item{objects as pairs $(c, d \in F(c))$ and}
-\item{a morphism from $(c, d \in F(c))$ to $(c^\prime, d^\prime \in F(c^\prime))$ is a pair $(f \colon c \to c^\prime,\alpha \colon F(f)(d) \to d^\prime)$.
-
-This can also be thought of as a morphism and a 2-morphism:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$\star$};
-\node (B) at (1,0.5) {$F(c)$};
-\node (C) at (1,-0.5) {$F(c^\prime)$};
-\node (D) at (2,0.5) {$c$};
-\node (E) at (2,-0.5) {$c^\prime$};
-\node (F) at (0.65,0) {$\Swarrow \alpha$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$d$} (B)
-(B) edge node[right]{$F(f)$} (C)
-(A) edge node[below]{$d^\prime$} (C)
-(D) edge node[left] {$f$} (E);
-\end{tikzpicture}
-\]
+%\begin{defn}
+%Let $\mathbf{Cat}_{\textnormal{lax},\star}$ denote the \define{2-category of lax-pointed categories} which has:
+%\begin{enumerate}
+%\item{objects as pairs $(\mathrm{A},c)$ where $\mathrm{A}$ is a category and $c$ is an object of $\mathrm{A}$, and}
+%\item{a morphism from $(\mathrm{A},c)$ to $(\mathrm{X},y)$ is a pair $(F,f)$ where $F \colon \mathrm{A} \to \mathrm{X}$ is a functor and $f \colon F(c) \to y$ is a morphism in $\mathrm{X}$.}
+%\end{enumerate}
+%\end{defn}
+%\begin{defn}
+%Given a pseudofunctor $F \colon \mathrm{A} \to \mathbf{Cat}$, the \define{Grothendieck construction of} $F$ is given by the `strict 2-pullback' of the following cospan:
+% \[
+%\begin{tikzpicture}[scale=1.5]
+%\node (D) at (1,1) {$\int F$};
+%\node (A) at (0,0) {$\mathrm{A}$};
+%\node (B) at (1,-1) {$\mathbf{Cat}$};
+%\node (C) at (2,0) {$\mathbf{Cat}_{\textnormal{lax},\star}$};
+%\path[->,font=\scriptsize,>=angle 90]
+%(D) edge[dashed] node[above]{$p$} (A)
+%(D) edge[dashed] node[above]{$q$} (C)
+%(A) edge node[below]{$F$} (B)
+%(C) edge node[below]{$P$} (B);
+%\end{tikzpicture}
+%\]
+%where $P \colon \mathbf{Cat}_{\textnormal{lax},\star} \to \mathbf{Cat}$ is the forgetful functor. 
+for any pseudofunctor $F\colon\A\to\bicat{Cat}$ where $\A$ is a category viewed as a 2-category with trivial 2-cells, the \textbf{Grothendieck category}
+$\int F$ has:
+\begin{itemize}
+\item{objects as pairs $(a, x \in F(a))$ and}
+\item{a morphism from $(a, x \in F(a))$ to $(b, y\in F(b))$ is a pair $(f \colon a \to b,\delta \colon F(f)(x) \to y)\in\A\times F(b)$. 
+%This can also be thought of as a morphism and a 2-morphism:
+%\[
+%\begin{tikzpicture}[scale=1.5]
+%\node (A) at (0,0) {$\star$};
+%\node (B) at (1,0.5) {$F(c)$};
+%\node (C) at (1,-0.5) {$F(c^\prime)$};
+%\node (D) at (2,0.5) {$c$};
+%\node (E) at (2,-0.5) {$c^\prime$};
+%\node (F) at (0.65,0) {$\Swarrow \alpha$};
+%\path[->,font=\scriptsize,>=angle 90]
+%(A) edge node[above]{$d$} (B)
+%(B) edge node[right]{$F(f)$} (C)
+%(A) edge node[below]{$d^\prime$} (C)
+%(D) edge node[left] {$f$} (E);
+%\end{tikzpicture}
+%\]
 }
-\end{enumerate}
-\end{defn}
-
-The Grothendieck construction gives rise to a 2-functor $[\A,\mathbf{Cat}] \to \mathbf{Cat}/ \mathrm{A}$ which factors through the image of the embedding $\textnormal{Opfib}(\mathrm{A}) \hookrightarrow \mathbf{Cat} / \mathrm{A}$ as per the following theorem.
+\end{itemize}
+%\end{defn}
+
+The Grothendieck construction gives rise to a 2-functor $[\A,\bicat{Cat}]_\pse\to \mathbf{Cat}/ \A$ which factors through the embedding $\OpFib(\A) \hookrightarrow \bicat{Cat} / \A$ as per the following theorem.
 %: $$\int F \colon [ \mathrm{A}, \mathbf{Cat} ] \to \textnormal{Opfib}(\mathrm{A}) \hookrightarrow \mathbf{Cat} / \mathrm{A}.$$
@@
     \begin{enumerate}
-        \item Every opfibration $\U \maps \D \to \C$ gives rise to a pseudofunctor $F_U \maps \C \to \bicat{Cat}$.
-        \item Every opindexed category $F \maps \C \to Cat$ gives rise to  an opfibration $\U_F \colon \int F\to\C$.
+        \item Every opfibration $\U \maps \X \to \A$ gives rise to a pseudofunctor $F_U \maps \A \to \bicat{Cat}$.
+        \item Every opindexed category $F \maps \A \to Cat$ gives rise to  an opfibration $\U_F \colon \int F\to\A$.
         \item The above correspondences yield an equivalence of 2-categories 
         \begin{displaymath}
-            ICat(\C) \simeq opFib(\C)
+            [\A,\bicat{Cat}]_\pse \simeq \OpFib(\A)
         \end{displaymath}
@@
 3.10]{MV}.
-If the monoidal category $\A$ is in fact cocartesian monoidal, there is a further correspondence of the two structures with a sheer pseudofunctor $F\colon\A\to\ca{MonCat}$:
+If the monoidal category $\A$ is in fact cocartesian monoidal, there is a further correspondence of the two structures with an ordinary pseudofunctor $F\colon\A\to\ca{MonCat}$:
 \begin{gather}
-\textrm{lax monoidal pseudofunctors }F\colon(\A,+,0)\to(\bicat{Cat},\times,1) \\
-\Updownarrow \\
+\textrm{lax monoidal pseudofunctors }F\colon(\A,+,0)\to(\bicat{Cat},\times,1) \notag\\
+\Updownarrow \notag\\
 \textrm{monoidal opfibrations }U\colon(\X,\otimes,I)\to(\A,+,0) \label{monGroth}\\
-\Updownarrow \\
-\textrm{pseudofunctors }F\colon\A\to\bicat{MonCat}
+\Updownarrow \notag\\
+\textrm{pseudofunctors }F\colon\A\to\bicat{MonCat} \notag
 \end{gather}
 where the second equivalence was already observed by Shulman in \cite{Shul2}.
-Moreover, the above further restricts to the case when the Grothendieck category is specifically cocartesian monoidal itself, see \cite[Cor.
-4.8]{MV} for more details.
-Then, the monoidal opfibration clauses for $U\colon(\X,+,0)\to(\A,+,0)$ in fact translate to the functor (strictly) preserving coproducts and the initial object, and bijectively correspond to pseudofunctors $F\colon\A\to\bicat{cocartCat}$ into the 2-category of cocartesian categories, functors that preserve coproducts and initial objects and natural transformations.
+Moreover, these correspondences further restrict to the case when the Grothendieck category is specifically cocartesian monoidal itself; for more details, see \cite[Cor.
+4.8]{MV}.
+In that case, the monoidal opfibration clauses for $U\colon(\X,+,0)\to(\A,+,0)$ in fact translate to the functor (strictly) preserving coproducts and the initial object, and bijectively correspond to pseudofunctors $F\colon\A\to\bicat{cocartCat}$ into the 2-category of cocartesian categories, functors that preserve coproducts and initial objects and natural transformations.
 
@@
 all finite colimits.
-Of course this is more general since it relates the existence of any class of colimits in the total category of an opfibration to their existence in the fibres; for more details, see \cite{Herm}.
+Of course, the following is more general since it relates the existence of any class of colimits in the total category of an opfibration to their existence in the fibres; for a more detailed exposition and proof, see \cite{Herm}.
 
 \begin{lem}\label{lem:fibrewiselimits}
-Suppose $\ca{J}$ is a small category and $\U\colon\X\to\A$ is an opfibration. If $\A$ has $\ca{J}$-colimits,
+Suppose $\ca{J}$ is a small category and $\U\colon\X\to\A$ is an opfibration. If the base $\A$ has $\ca{J}$-colimits,
 the following are equivalent:
@@
  \item all fibres have $\ca{J}$-colimits, and the reindexing functors preserve them;
- \item $\X$ has $\ca{J}$-colimits, and $\U$ strictly preserves them.
+ \item the total $\X$ has $\ca{J}$-colimits, and $\U$ preserves them. %removed strict for now!
 \end{enumerate}

### 2019-05-07 EquivCompFrameworks_20180911kc.tex
finally ready to complete theorem I think

@@
 \item {\chris Where should we put some standard things we use? For exampe, lax monoidal pseudofunctor should be recalled early. Together with pseudonatural transformations I believe.}
+\item {\chris Notation between \cref{Equiv} and \cref{thm:decoratedcospans} right now does not match! Need to fix.}
+\item {\chris There might be a way to completely hide the details of version 'fibres have, reindexing preserve' if that's what we want to do.}
 \end{itemize}
@@
 \item{2-morphisms as maps of $F$-decorated cospans in $\mathsf{A}$
-\[
+\begin{equation}\label{eq:FCsp2morph}
 \begin{tikzpicture}[scale=1.5]
@@
 \end{tikzpicture}
-\]
+\end{equation}
 together with a morphism $\iota \colon F(h)(d) \to d^\prime$ in $F(b^\prime)$.}
@@
 The category $\X$ is called the \textbf{total} category, whereas $\A$ is the \textbf{base} category of the opfibration.
+For any $a\in\A$, the \textbf{fibre} $\X_a$ consists of all objects that map to $a$ and vertical morphisms between them, i.e.
+mapping to $1_a$.
+Assuming the axiom of choice, we may select a cocartesian arrow over each $f\maps a\to b$ in $\A$ and $x\in\X _a$, denoted by $\mathrm{Cocart}(f,x)\maps x\to f_!(x)$; $U$ is then called a \textbf{cloven opfibration}.
+This choice induces the so-called \textbf{reindexing functors} $f_!\colon\X _a\to\X _b$ between the fibre categories, which by the liftings universal property adhere to $(1_a)_!\cong1_{\X _a}$ and $(f\circ g)_!\cong f_!\circ g_!$.
+If these isomorphisms are equalities, we have the notion of a \textbf{split} opfibration.
 %Christina: decide later if needed
@@
 %\]
-Let $\OpFib(\A)$ denote the 2-subcategory of the slice 2-category $\mathbf{Cat}/ \A$ of opfibrations over $\A$, functors that preserve cocartesian liftings and natural transformations with vertical components, namely morphisms in the total category that map to identities in the base category.
+
+Let $\OpFib(\A)$ denote the 2-subcategory of the slice 2-category $\mathbf{Cat}/ \A$ of opfibrations over $\A$, functors that preserve cocartesian liftings and natural transformations with vertical components.
 In fact, there is a 2-equivalence between opfibrations and pseudofunctors induced by the so-called Grothendieck construction:
@@
 %\end{defn}
-
-The Grothendieck construction gives rise to a 2-functor $[\A,\bicat{Cat}]_\pse\to \mathbf{Cat}/ \A$ which factors through the embedding $\OpFib(\A) \hookrightarrow \bicat{Cat} / \A$ as per the following theorem.
+This is an opfibration over $\A$, with fibre categories $(\int F)_a=F(a)$ and reindexing functors $f_!=F(f)$. In this way, the Grothendieck construction induces the following equivalence.
+
+%gives rise to a 2-functor $[\A,\bicat{Cat}]_\pse\to \mathbf{Cat}/ \A$ which factors through the embedding $\OpFib(\A) \hookrightarrow \bicat{Cat} / \A$ as per the following theorem.
 %: $$\int F \colon [ \mathrm{A}, \mathbf{Cat} ] \to \textnormal{Opfib}(\mathrm{A}) \hookrightarrow \mathbf{Cat} / \mathrm{A}.$$
@@
 where the second equivalence was already observed by Shulman in \cite{Shul2}.
+In more detail, if $(\phi,\phi_0)$ is the lax monoidal structure of $F$, each fibre category $\X_a=F(a)$ obtains a monoidal structure via
+\begin{gather}\label{eq:explicitstructure1}
+\otimes_a\colon F(a)\times F(a)\xrightarrow{\phi_{a,a}}F(a+a)\xrightarrow{F(\nabla)}F(a)\\
+I_x\colon\mathbf{1}\xrightarrow{\phi_0}F(0)\xrightarrow{F(!)}F(a)\nonumber
+\end{gather}
 Moreover, these correspondences further restrict to the case when the Grothendieck category is specifically cocartesian monoidal itself; for more details, see \cite[Cor.
@@
 On a different but related subject, for our purposes we are interested in the existence of a left adjoint $L_F \colon \A \to \X$ for the induced monoidal opfibration $ \int{F} \to \A$ by the Grothendieck construction as discussed above.
-The following result provides sufficient conditions for that, which go hand-in-hand with \cref{cor:fcocMonGroth}.
+The following result provides sufficient conditions for that, which go hand-in-hand with \cref{cor:fcocMonGroth} and \cref{lem:fibrewiselimits}.
 
 \begin{prop}\cite[Prop.\ 4.4]{Gray} \label{prop:opfibtolari}
-  Let $\U \colon\D \to \C$ be an opfibration. Then
+  Let $\U \colon\X \to \A$ be an opfibration. Then
   $\U$ is a right adjoint `left inverse', a.k.a the unit is the identity, if (and only if) its fibers have
@@
 \end{prop}
+
+\begin{proof}\emph{(Sketch)}
+ The left adjoint $L\colon\A\to\X$ maps an object $a$ to the initial object in its fibre $\X_a$, denoted by $\bot_a$. By construction, $U(L(a))=U(\bot_a)=a$.
+\end{proof}
+
+\begin{rmk}\label{rmk:important}
+Notice that under \cref{lem:fibrewiselimits}, if $\A$ has an initial object $0_\A$, the above conditions are equivalent to $\X$ having an initial object $0_\X$ above $0_\A$.
+%Christina: hiding strict preservence under the rug
+In this case, $\bot_a$ is precisely the cocartesian lifting of $0_\X$ under the unique map $f\colon0_\A$ in the base category:
+\begin{displaymath}
+\xymatrix @C=.4in @R=.2in
+{0_\X \ar @{.>}[d]\ar[rr]^-{\mathrm{Cocart}(0_\X,f)} && f_!(0_X)=:\bot_a\ar @{.>}[d] & \textrm{in }\X  \\
+0_\A\ar[rr]_-{f}\ar[rr]^-{\exists!} && a & \textrm{in }\A}
+\end{displaymath}
+Moreover, if $U=U_F$ for a pseudofunctor $F\colon\A\to\bicat{Cat}$ under \cref{thm:Grothendieck}, the initial object in each fibre is precisely $F(f)(0_\X)$, for $f$ the unique map from $0_\A$ as above.
+Finally, if that pseudofunctor is lax monoidal $(F,\phi,\phi_0)\colon(\A,+,0)\to(\bicat{Cat},\times,\mathbf{1})$ to begin with, the monoidal Grothendieck construction in the cocartesian case discussed earlier (\cref{eq:explicitstructure1}) express $\bot_a$ as the image of the composite
+\begin{equation}\label{eq:initialinfibre}
+\mathbf{1}\xrightarrow{\phi_0}F(0_\A)\xrightarrow{F(f)}F(a) 
+\end{equation}
+\end{rmk}
+
 %will be a right adjoint to some adjoint , and moreover the unit of the adjunction is the identity; this is called \emph{lari} in [Gray].
 
+{\chris not sure if the below is needed after all}
 In the opposite direction, we also have the following result. For a discussion on the unusual strict cocontinuity condition, we refer the reader to \cite{CV}.
@@
 %Christina: do we need this direction after all? Discuss.
-
 %\begin{thm}\label{thm:mainthmDX}\cite{CV}
@@
 \begin{thm}\label{Equiv}
-Suppose $\mathsf{A}$ and $\mathsf{X}$ are finitely cocomplete categories and $F \colon(\mathsf{A},+,0) \to (\mathbf{Cat},\times,\mathbf{1})$ is a symmetric lax monoidal pseudofunctor.
+Suppose $\ca{A}$ is a finitely cocomplete category and $(F,\phi,\phi_0)\colon(\ca{A},+,0) \to (\bicat{Cat},\times,\mathbf{1})$ is a symmetric lax monoidal pseudofunctor.
 %such that as an ordinary pseudofunctor, it factors through $\bicat{fcocCat}$.
-The symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$ of decorated cospans (\cref{thm:decoratedcospans}) is equivalent to the symmetric monoidal double category $_{L_F} \mathbb{C}\textnormal{sp}(\mathsf{X})$ of structured cospans (\cref{SC}), where $L_F \colon \mathsf{A} \to \int{F}$ is the left adjoint of the induced Grothendieck opfibration $\U_F\colon \int{F} \to \mathsf{A}$ by \cref{thm:Grothendieck}, under the assumptions of \cref{cor:fcocMonGroth}.
+Then the symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$ of decorated cospans (\cref{thm:decoratedcospans}) is equivalent to the symmetric monoidal double category $_{L_F} \mathbb{C}\textnormal{sp}(\mathsf{X})$ of structured cospans (\cref{SC}), where $L_F \colon \mathsf{A} \to \int{F}$ is the left adjoint of the induced Grothendieck opfibration $\U_F\colon \int{F} \to \mathsf{A}$ %by \cref{thm:Grothendieck},
+under the assumptions of \cref{cor:fcocMonGroth}.
 \end{thm}
+
 \begin{proof}
+Recall that the double category of decorated cospans $\dcsp{F}$ has objects and vertical 1-morphisms those of $\A$, horizontal 1-cells $a\tickar b$ are cospans $\cspn{a}{c}{b}{}{}$ in $\A$ along with $d\in F(c)$, and 2-morphisms are cospan maps $k\colon c\to c'$ such that $(Fk)(d)=d'$, see \cref{eq:FCsp2morph}.
+
+By \cref{cor:fcocMonGroth}, when $F$ as an ordinary pseudofunctor factors through $\bicat{fcocCat}$, the (monoidal) Gro\-the\-ndieck construction gives rise to a finitely cocomplete $\int F$ such that the corresponding opfibration $U_F\colon(\int{F},+,0)\to(\A,+,0)$ preserves all finite colimits.
+%Christina: maybe the cocartesian structures are redundant to write here, since U_F really preserves all finite colimits anyways.
+Since in particular it preserves the initial object, \cref{prop:opfibtolari} through \cref{lem:fibrewiselimits} applies 
+%which equivalently means that all fibres have initial objects and the reindexing functors preserve them by , %Christina: there is a little bit of circularity here.
+We knew fibres have and reindexing functors preserve from the factorization already!
+Change Gray accordingly perhaps?
+to construct a left adjoint $L_F\colon\A\to\int F$ which is also a right inverse, namely $U_FL_F=\mathrm{id}_\A$.
+In fact, by \cref{rmk:important}, this left adjoint is given by $L(a)=F(f)\circ\phi_0(*)$, the initial object in the fibre above $a$.
+
 {\chris in progress}
-As explained in (ref), the double category of decorated cospans $\dcsp{F}$ has $\A$ as its category of objects and vertical 1-morphisms, whereas horizontal 1-cells $a\tickar b$ are cospans $\cspn{a}{c}{b}{}{}$ in $\A$ along with $d\in F(c)$ and 2-morphisms are cospan maps $k\colon c\to c'$ such that $(Fk)(d)=d'$.
-
-The symmetric lax monoidal pseudofunctor $F$ corresponds, under the (monoidal) Gro\-the
--ndieck construction, to an opfibration $U_F\colon\int{F}\to\A$ with such and such properties.
-
 To prove this, we define a double functor $\mathbb{E} \colon _L \mathbb{C}\textnormal{sp}(\mathsf{X}) \to F\mathbb{C}\textnormal{sp}$ as follows: the object component of the double functor $\mathbb{E}$ is given by $\mathbb{E}_0 = \id_{\mathsf{A}}$ as both double categories $_L \mathbb{C}\textnormal{sp}(\mathrm{X})$ and $F\mathbb{C}\textnormal{sp}$ have objects and morphisms of $\mathsf{A}$ as objects and vertical 1-morphisms, respectively.

### 2019-05-07 EquivCompFrameworks_20180911kc.tex
commented out double functor G going in other direction...might add later

@@
 
-\begin{comment}
 We can also define the part of the double equivalence $\mathbb{G} \colon F\mathbb{C}\textnormal{sp} \to {_L \mathbb{C} \textnormal{sp}(\mathsf{X})}$ which goes in the other direction: again, the object component of this double functor will be $\mathbb{G}_0 = \id_{\mathsf{A}}$.
@@
 commutes.
-\end{comment}
 

### 2019-05-09 EquivCompFrameworks_20180911kc.tex
made integral and structured cospan macros

--- 2019-05-07 EquivCompFrameworks_20180911kc.tex
@@
 %\begin{tikzpicture}[scale=1.5]
-%\node (D) at (1,1) {$\int F$};
+%\node (D) at (1,1) {$\inta F$};
 %\node (A) at (0,0) {$\mathrm{A}$};
@@
 for any pseudofunctor $F\colon\A\to\bicat{Cat}$ where $\A$ is a category viewed as a 2-category with trivial 2-cells, the \textbf{Grothendieck category}
-$\int F$ has:
+$\inta F$ has:
 \begin{itemize}
@@
 %\end{defn}
-This is an opfibration over $\A$, with fibre categories $(\int F)_a=F(a)$ and reindexing functors $f_!=F(f)$. In this way, the Grothendieck construction induces the following equivalence.
+This is an opfibration over $\A$, with fibre categories $(\inta F)_a=F(a)$ and reindexing functors $f_!=F(f)$. In this way, the Grothendieck construction induces the following equivalence.
 
 %gives rise to a 2-functor $[\A,\bicat{Cat}]_\pse\to \mathbf{Cat}/ \A$ which factors through the embedding $\OpFib(\A) \hookrightarrow \bicat{Cat} / \A$ as per the following theorem.
-%: $$\int F \colon [ \mathrm{A}, \mathbf{Cat} ] \to \textnormal{Opfib}(\mathrm{A}) \hookrightarrow \mathbf{Cat} / \mathrm{A}.$$
+%: $$\inta F \colon [ \mathrm{A}, \mathbf{Cat} ] \to \textnormal{Opfib}(\mathrm{A}) \hookrightarrow \mathbf{Cat} / \mathrm{A}.$$
 
@@
         \item Every opfibration $\U \maps \X \to \A$ gives rise to a pseudofunctor $F_U \maps \A \to \bicat{Cat}$.
-        \item Every opindexed category $F \maps \A \to Cat$ gives rise to  an opfibration $\U_F \colon \int F\to\A$.
+        \item Every opindexed category $F \maps \A \to Cat$ gives rise to  an opfibration $\U_F \colon \inta F\to\A$.
         \item The above correspondences yield an equivalence of 2-categories 
@@
 
-In \cite{MV}, the Grothendieck construction is generalized to the monoidal setting, namely lax monoidal structures on a pseudofunctor $F\colon\A\to\bicat{Cat}$ bijectively correspond to monoidal structures on the total category $\int F$ such that the induced opfibration is a strict monoidal functor and $\otimes_{\int F}$ is cartesian, see \cite[Thm.
+In \cite{MV}, the Grothendieck construction is generalized to the monoidal setting, namely lax monoidal structures on a pseudofunctor $F\colon\A\to\bicat{Cat}$ bijectively correspond to monoidal structures on the total category $\inta F$ such that the induced opfibration is a strict monoidal functor and $\otimes_{\inta F}$ is cartesian, see \cite[Thm.
 3.10]{MV}.
@@
 
-The first part formulates the existence of colimits \emph{locally} in each fiber, which can equivalently be expressed by the corresponding pseudofunctor $F\colon\A\to\bicat{Cat}$ landing on the sub-2-category $\bicat{fcocCat}$ of finitely cocomplete categories and functors that preserve colimits; the second part formulates the existence of colimits \emph{globally} in the total category $\int F$.
+The first part formulates the existence of colimits \emph{locally} in each fiber, which can equivalently be expressed by the corresponding pseudofunctor $F\colon\A\to\bicat{Cat}$ landing on the sub-2-category $\bicat{fcocCat}$ of finitely cocomplete categories and functors that preserve colimits; the second part formulates the existence of colimits \emph{globally} in the total category $\inta F$.
 Combining these, we can deduce the following.
@@
 If its corresponding pseudofunctor $\A\to\bicat{MonCat}$ via \cref{monGroth}
- factors through $\bicat{fcocCat}$, then the Grothendieck category $\int F$ has all finite colimits and the induced opfibration $\U_F\colon\int F\to\A$ preserves them. 
+ factors through $\bicat{fcocCat}$, then the Grothendieck category $\inta F$ has all finite colimits and the induced opfibration $\U_F\colon\inta F\to\A$ preserves them. 
 \end{cor}
 
-On a different but related subject, for our purposes we are interested in the existence of a left adjoint $L_F \colon \A \to \X$ for the induced monoidal opfibration $ \int{F} \to \A$ by the Grothendieck construction as discussed above.
+On a different but related subject, for our purposes we are interested in the existence of a left adjoint $L_F \colon \A \to \X$ for the induced monoidal opfibration $ \inta{F} \to \A$ by the Grothendieck construction as discussed above.
 The following result provides sufficient conditions for that, which go hand-in-hand with \cref{cor:fcocMonGroth} and \cref{lem:fibrewiselimits}.
@@
 \end{displaymath}
-Moreover, if $U=U_F$ for a pseudofunctor $F\colon\A\to\bicat{Cat}$ under \cref{thm:Grothendieck}, the initial object in each fibre is precisely $F(f)(0_\X)$, for $f$ the unique map from $0_\A$ as above.
+Moreover, if $U=U_F$ for a pseudofunctor $F\colon\A\to\bicat{Cat}$ under \cref{thm:Grothendieck}, the reindexing functors $f_!$ of the fibration are precisely $F(f)$, therefore $\bot_a=F(f)(0_\X)$ for $f$ the unique map from $0_\A$ as above.
 Finally, if that pseudofunctor is lax monoidal $(F,\phi,\phi_0)\colon(\A,+,0)\to(\bicat{Cat},\times,\mathbf{1})$ to begin with, the monoidal Grothendieck construction in the cocartesian case discussed earlier (\cref{eq:explicitstructure1}) express $\bot_a$ as the image of the composite
@@
 %such that as an ordinary pseudofunctor, it factors through $\bicat{fcocCat}$.
-Then the symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$ of decorated cospans (\cref{thm:decoratedcospans}) is equivalent to the symmetric monoidal double category $_{L_F} \mathbb{C}\textnormal{sp}(\mathsf{X})$ of structured cospans (\cref{SC}), where $L_F \colon \mathsf{A} \to \int{F}$ is the left adjoint of the induced Grothendieck opfibration $\U_F\colon \int{F} \to \mathsf{A}$ %by \cref{thm:Grothendieck},
+Then the symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$ of decorated cospans (\cref{thm:decoratedcospans}) is equivalent to the symmetric monoidal double category $\scsp{L_F}{\inta F}$ of structured cospans (\cref{SC}), where $L_F \colon \mathsf{A} \to \inta{F}$ is the left adjoint of the induced Grothendieck opfibration $\U_F\colon \inta{F} \to \mathsf{A}$ %by \cref{thm:Grothendieck},
 under the assumptions of \cref{cor:fcocMonGroth}.
@@
 
-By \cref{cor:fcocMonGroth}, when $F$ as an ordinary pseudofunctor factors through $\bicat{fcocCat}$, the (monoidal) Gro\-the\-ndieck construction gives rise to a finitely cocomplete $\int F$ such that the corresponding opfibration $U_F\colon(\int{F},+,0)\to(\A,+,0)$ preserves all finite colimits.
+By \cref{cor:fcocMonGroth}, when $F$ as an ordinary pseudofunctor factors through $\bicat{fcocCat}$, the (monoidal) Gro\-the\-ndieck construction gives rise to a finitely cocomplete $\inta F$ such that the corresponding opfibration $U_F\colon(\inta{F},+,0)\to(\A,+,0)$ preserves all finite colimits.
 %Christina: maybe the cocartesian structures are redundant to write here, since U_F really preserves all finite colimits anyways.
@@
 Change Gray accordingly perhaps?
-to construct a left adjoint $L_F\colon\A\to\int F$ which is also a right inverse, namely $U_FL_F=\mathrm{id}_\A$.
-In fact, by \cref{rmk:important}, this left adjoint is given by $L(a)=F(f)\circ\phi_0(*)$, the initial object in the fibre above $a$.
-
-{\chris in progress}
+to construct a left adjoint $L_F\colon\A\to\inta F$ which is also a right inverse, namely $U_FL_F=\mathrm{id}_\A$.
+Explicitly, this left adjoint is given by $L(a)=F(f)\circ\phi_0(*)$ as in \cref{eq:initialinfibre}.
+
+We can now construct the double category of structured cospans $\scsp{L_F}{\inta F}$
 To prove this, we define a double functor $\mathbb{E} \colon _L \mathbb{C}\textnormal{sp}(\mathsf{X}) \to F\mathbb{C}\textnormal{sp}$ as follows: the object component of the double functor $\mathbb{E}$ is given by $\mathbb{E}_0 = \id_{\mathsf{A}}$ as both double categories $_L \mathbb{C}\textnormal{sp}(\mathrm{X})$ and $F\mathbb{C}\textnormal{sp}$ have objects and morphisms of $\mathsf{A}$ as objects and vertical 1-morphisms, respectively.
@@
 Thus the set $$_{\mathbb{E}(f)} {F\mathbb{C}\textnormal{sp}}_{\mathbb{E}(g)}(\mathbb{E}(M),\mathbb{E}(N))$$ consists of 4-tuples $$(f,R(\alpha),g,\iota)$$ rendering the above diagram commutative and where $f,g$ and $R(\alpha)$ are morphisms of $\mathsf{A}$ and $\iota$ is a morphism in $F(R(x'))$.
-The morphisms $R(\alpha) \colon R(x) \to R(x^\prime)$ and $\iota \colon F(R(\alpha))(x) \to x^\prime$ together determine the morphism $\alpha \colon x \to x^\prime$ in $\mathrm{X}$ and conversely; given two objects $x=(c,x \in F(c))$ and $x^\prime=(c^\prime,x^\prime \in F(c^\prime))$ of $\mathsf{X}=\int{F}$, a morphism from $\alpha \colon x \to x^\prime$ is a pair $$(h \colon c \to c^\prime, \iota \colon F(h)(x) \to x^\prime)$$ where $h \colon c \to c^\prime$ is given by $R(\alpha) \colon R(x) \to R(x^\prime)$.
+The morphisms $R(\alpha) \colon R(x) \to R(x^\prime)$ and $\iota \colon F(R(\alpha))(x) \to x^\prime$ together determine the morphism $\alpha \colon x \to x^\prime$ in $\mathrm{X}$ and conversely; given two objects $x=(c,x \in F(c))$ and $x^\prime=(c^\prime,x^\prime \in F(c^\prime))$ of $\mathsf{X}=\inta{F}$, a morphism from $\alpha \colon x \to x^\prime$ is a pair $$(h \colon c \to c^\prime, \iota \colon F(h)(x) \to x^\prime)$$ where $h \colon c \to c^\prime$ is given by $R(\alpha) \colon R(x) \to R(x^\prime)$.
 This shows that $\mathbb{E}$ is fully faithful.

### 2019-05-09 EquivCompFrameworks_20180911kc.tex
worked on theorem up until 2-cells

@@
 Our next goal is to show that the symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$ of Section \ref{DecCospansDoubleCat} is equivalent as a symmetric monoidal double category to the symmetric monoidal double category $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$ obtained using structured cospans.
+{\chris Wait, why do you need to consider them as monoidal in the assumptions of the theorem?}
 
@@
 \item{2-morphisms given by maps of cospans of $\mathsf{X}$ of the form:
-\[
+\begin{equation}\label{eq:2cellsStrCsp}
 \begin{tikzpicture}[scale=1.5]
@@
 \end{tikzpicture}
-\]
+\end{equation}
 Composition of horizontal 1-cells and 2-morphisms is given by pushouts in $\mathsf{X}$ and tensoring of objects is under binary coproducts in $\mathsf{A}$.
@@
 \end{proof}
-In the previous section, we started with a symmetric lax monoidal pseudofunctor $F \colon \mathsf{A} \to \mathbf{Cat}$ and created a symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$ which has:
-\begin{enumerate}
-\item{objects of $\mathsf{A}$ as objects,}
-\item{morphisms of $\mathsf{A}$ as vertical 1-morphisms,}
-\item{horizontal 1-cells are given by $F$-decorated cospans, which are pairs:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$c_1$};
-\node (B) at (1,0) {$c$};
-\node (C) at (2,0) {$c_2$};
-\node (D) at (3,0) {$x \in F(c)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i$} (B)
-(C) edge node[above]{$o$} (B);
-\end{tikzpicture}
-\]
-and}
-\item{2-morphisms are given by maps of cospans in $\mathsf{A}$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$c_1$};
-\node (B) at (1,0) {$c$};
-\node (C) at (2,0) {$c_2$};
-\node (A') at (0,-1) {$c_1^\prime$};
-\node (B') at (1,-1) {$c^\prime$};
-\node (C') at (2,-1) {$c_2^\prime$};
-\node (D) at (3,0) {$x \in F(c)$};
-\node (D') at (3,-1) {$x^\prime \in F(c^\prime)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i$} (B)
-(C) edge node[above]{$o$} (B)
-(A') edge node[above]{$i^\prime$} (B')
-(C') edge node[above]{$o^\prime$} (B')
-(A) edge node [left]{$f$} (A')
-(B) edge node [left]{$h$} (B')
-(C) edge node [left]{$g$} (C');
-\end{tikzpicture}
-\]
-together with a morphism $\iota \colon F(h)(d) \to d^\prime$ in $F(c^\prime)$.}
-\end{enumerate}
+{\chris Below, I commented out a nice short recalled version of decorated cospans, since now their definition is later. Use if we want to recall at some point later}
+%In the previous section, we started with a symmetric lax monoidal pseudofunctor $F \colon \mathsf{A} \to \mathbf{Cat}$ and created a symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$ which has:
+%\begin{enumerate}
+%\item{objects of $\mathsf{A}$ as objects,}
+%\item{morphisms of $\mathsf{A}$ as vertical 1-morphisms,}
+%\item{horizontal 1-cells are given by $F$-decorated cospans, which are pairs:
+%\[
+%\begin{tikzpicture}[scale=1.5]
+%\node (A) at (0,0) {$c_1$};
+%\node (B) at (1,0) {$c$};
+%\node (C) at (2,0) {$c_2$};
+%\node (D) at (3,0) {$x \in F(c)$};
+%\path[->,font=\scriptsize,>=angle 90]
+%(A) edge node[above]{$i$} (B)
+%(C) edge node[above]{$o$} (B);
+%\end{tikzpicture}
+%\]
+%and}
+%\item{2-morphisms are given by maps of cospans in $\mathsf{A}$:
+%\[
+%\begin{tikzpicture}[scale=1.5]
+%\node (A) at (0,0) {$c_1$};
+%\node (B) at (1,0) {$c$};
+%\node (C) at (2,0) {$c_2$};
+%\node (A') at (0,-1) {$c_1^\prime$};
+%\node (B') at (1,-1) {$c^\prime$};
+%\node (C') at (2,-1) {$c_2^\prime$};
+%\node (D) at (3,0) {$x \in F(c)$};
+%\node (D') at (3,-1) {$x^\prime \in F(c^\prime)$};
+%\path[->,font=\scriptsize,>=angle 90]
+%(A) edge node[above]{$i$} (B)
+%(C) edge node[above]{$o$} (B)
+%(A') edge node[above]{$i^\prime$} (B')
+%(C') edge node[above]{$o^\prime$} (B')
+%(A) edge node [left]{$f$} (A')
+%(B) edge node [left]{$h$} (B')
+%(C) edge node [left]{$g$} (C');
+%\end{tikzpicture}
+%\]
+%together with a morphism $\iota \colon F(h)(d) \to d^\prime$ in $F(c^\prime)$.}
+%\end{enumerate}
 
@@
 Let $\OpFib(\A)$ denote the 2-subcategory of the slice 2-category $\mathbf{Cat}/ \A$ of opfibrations over $\A$, functors that preserve cocartesian liftings and natural transformations with vertical components.
-In fact, there is a 2-equivalence between opfibrations and pseudofunctors induced by the so-called Grothendieck construction:
+In fact, there is a 2-equivalence between opfibrations and pseudofunctors induced by the so-called \emph{Grothendieck construction}.
 %{\chris I don't mind this presentation of the Grothendieck construction which I admit not having seeing before.
@@
 %where $P \colon \mathbf{Cat}_{\textnormal{lax},\star} \to \mathbf{Cat}$ is the forgetful functor. 
-for any pseudofunctor $F\colon\A\to\bicat{Cat}$ where $\A$ is a category viewed as a 2-category with trivial 2-cells, the \textbf{Grothendieck category}
-$\inta F$ has:
+\begin{defn}\label{def:GrothCat}
+For any pseudofunctor $F\colon\A\to\bicat{Cat}$ where $\A$ is a category viewed as a 2-category with trivial 2-cells, the \textbf{Grothendieck category}
+$\inta F$ has
 \begin{itemize}
-\item{objects as pairs $(a, x \in F(a))$ and}
-\item{a morphism from $(a, x \in F(a))$ to $(b, y\in F(b))$ is a pair $(f \colon a \to b,\delta \colon F(f)(x) \to y)\in\A\times F(b)$. 
+\item objects pairs $(a, x \in F(a))$ and
+\item a morphism from $(a, x \in F(a))$ to $(b, y\in F(b))$ is a pair $(f \colon a \to b,\delta \colon F(f)(x) \to y)\in\A\times F(b)$.
+\end{itemize}
+This is an opfibred category over $\A$ via the obvious forgetful functor, with fibre categories $(\inta F)_a=F(a)$ and reindexing functors $f_!=F(f)$.
+\end{defn}
 %This can also be thought of as a morphism and a 2-morphism:
@@
 %\]
-}
-\end{itemize}
-%\end{defn}
-This is an opfibration over $\A$, with fibre categories $(\inta F)_a=F(a)$ and reindexing functors $f_!=F(f)$. In this way, the Grothendieck construction induces the following equivalence.
-
+The above in fact provides the one direction of the following well-known equivalence.
 %gives rise to a 2-functor $[\A,\bicat{Cat}]_\pse\to \mathbf{Cat}/ \A$ which factors through the embedding $\OpFib(\A) \hookrightarrow \bicat{Cat} / \A$ as per the following theorem.
@@
 %Christina: hiding strict preservence under the rug
-In this case, $\bot_a$ is precisely the cocartesian lifting of $0_\X$ under the unique map $f\colon0_\A$ in the base category:
+In this case, $\bot_a$ is precisely the cocartesian lifting of $0_\X$ along the unique map $u_a\colon0_\A\to a$ in the base category:
 \begin{displaymath}
 \xymatrix @C=.4in @R=.2in
-{0_\X \ar @{.>}[d]\ar[rr]^-{\mathrm{Cocart}(0_\X,f)} && f_!(0_X)=:\bot_a\ar @{.>}[d] & \textrm{in }\X  \\
-0_\A\ar[rr]_-{f}\ar[rr]^-{\exists!} && a & \textrm{in }\A}
+{0_\X \ar @{.>}[d]\ar[rr]^-{\mathrm{Cocart}(0_\X,u_a)} && (u_a)_!(0_X)=:\bot_a\ar @{.>}[d] & \textrm{in }\X  \\
+0_\A\ar[rr]^-{\exists!u_a} && a & \textrm{in }\A}
 \end{displaymath}
-Moreover, if $U=U_F$ for a pseudofunctor $F\colon\A\to\bicat{Cat}$ under \cref{thm:Grothendieck}, the reindexing functors $f_!$ of the fibration are precisely $F(f)$, therefore $\bot_a=F(f)(0_\X)$ for $f$ the unique map from $0_\A$ as above.
+Moreover, if $U=U_F$ for a pseudofunctor $F\colon\A\to\bicat{Cat}$ under \cref{thm:Grothendieck}, the reindexing functors $(u_a)_!$ of the opfibration are precisely $F(u_a)$, therefore $\bot_a=(a,F(u_a)(0_\X))$ in the Grothendieck category, for $u_a$ the unique map from $0_\A$ as above.
+
 Finally, if that pseudofunctor is lax monoidal $(F,\phi,\phi_0)\colon(\A,+,0)\to(\bicat{Cat},\times,\mathbf{1})$ to begin with, the monoidal Grothendieck construction in the cocartesian case discussed earlier (\cref{eq:explicitstructure1}) express $\bot_a$ as the image of the composite
 \begin{equation}\label{eq:initialinfibre}
-\mathbf{1}\xrightarrow{\phi_0}F(0_\A)\xrightarrow{F(f)}F(a) 
+\mathbf{1}\xrightarrow{\phi_0}F(0_\A)\xrightarrow{F(u_a)}F(a) 
 \end{equation}
@@
 to construct a left adjoint $L_F\colon\A\to\inta F$ which is also a right inverse, namely $U_FL_F=\mathrm{id}_\A$.
-Explicitly, this left adjoint is given by $L(a)=F(f)\circ\phi_0(*)$ as in \cref{eq:initialinfibre}.
-
-We can now construct the double category of structured cospans $\scsp{L_F}{\inta F}$
-To prove this, we define a double functor $\mathbb{E} \colon _L \mathbb{C}\textnormal{sp}(\mathsf{X}) \to F\mathbb{C}\textnormal{sp}$ as follows: the object component of the double functor $\mathbb{E}$ is given by $\mathbb{E}_0 = \id_{\mathsf{A}}$ as both double categories $_L \mathbb{C}\textnormal{sp}(\mathrm{X})$ and $F\mathbb{C}\textnormal{sp}$ have objects and morphisms of $\mathsf{A}$ as objects and vertical 1-morphisms, respectively.
-The functor $\mathbb{E}_0$ is trivially an equivalence of categories.
-
-Given a horizontal 1-cell $M$ of $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$, which is a cospan in $\mathsf{X}$ of the form:
+Explicitly, this left adjoint is given by $L(a)=(a,\bot_a)$, picking the initial object in the finitely cocomplete fibre also expressed as $F(u_a)\circ\phi_0(*)$ as in \cref{eq:initialinfibre}.
+Diagrammatically,
+\begin{displaymath}
+ F\colon\X\to\bicat{Cat}\quad\mapsto\quad\begin{tikzcd}[baseline=.3]\inta F\ar[d,"U_F"'] \\ \X \end{tikzcd}\quad\mapsto\quad\begin{tikzcd}\X\ar[r,bend left,pos=.55,"L_F"]\ar[r,phantom,"\bot"description] & \inta F\ar[l,bend left,pos=.45,"U_F"]\end{tikzcd}
+\end{displaymath}
+roughly describes the bridge between the original $F$ and the resulting $L_F$.
+
+Using this functor $L_F$ between finitely cocomplete categories that preserves all colimits that exist (as a left adjoint), we can construct the double category of structured cospans $\scsp{L_F}{\inta F}$.
+Its objects and vertical morphisms are again those of the category $\A$, whereas horizontal 1-cells $a\tickar b$ are now cospans of the form $\cspn{L_F(a)}{v}{L_F(b)}{}{}$ in the Grothendieck category $\inta F$, which consist of two pairs of morphisms
+\begin{equation}\label{eq:scsphor1cell}
+ (a,\bot_a)\xrightarrow{\scalebox{0.7}{$\begin{cases}i\colon a\to c &\textrm{in }\A \\!\colon F(i)(\bot_a)\to x &\textrm{in }F(c)\end{cases}$}}(c,x)\xleftarrow{\scalebox{0.7}{$\begin{cases}o\colon b\to c &\textrm{in }\A \\!\colon F(o)(\bot_b)\to x &\textrm{in }F(c)\end{cases}$}}(b,\bot_b)
+\end{equation}
+according to \cref{def:GrothCat}. The 2-morphisms in this double category are as in \cref{eq:2cellsStrCsp}.
+
+In order to prove that there is a double equivalence between $\dcsp{F}$ and $\scsp{L_F}{\inta F}$, we define a %n identity-on-objects and vertical morphism
+double functor
+\begin{displaymath}
+\mathbb{E}\colon\scsp{L_F}{\inta F} \longrightarrow\dcsp{F}
+\end{displaymath}
+as follows.
+The object component of $\mathbb{E}=(\mathbb{E}_0,\mathbb{E}_1)$ is $\mathbb{E}_0 = \id_{\mathsf{A}}$ since both double categories have $\mathsf{A}$ as their vertical category; trivially, $\mathbb{E}_0$ is an equivalence of categories.
+Given a horizontal 1-cell in $\scsp{L_F}{\inta F}$ like \cref{eq:scsphor1cell}, the arrow component $\mathbb{E}_1$ of the double functor maps it simply to the decorated cospan
+\begin{displaymath}
+ a\xrightarrow{\; i \;}c\xleftarrow{\; o \;}b\;\textrm{ with decoration }x\in F(c)
+\end{displaymath}
+which is really a bijective correspondence since the unique maps from the initial objects in the fibres are always there. {\chris maybe too informal explanation!}
+
+{\chris in progress}
+which is a cospan in $\mathsf{X}$ of the form:
 \[

### 2019-05-09 EquivCompFrameworks_20180911kc.tex
small edits here and there

@@
 \item {\chris Discuss the name of Decorated and Structured cospan double categories one last time? :)}
-\item {\chris Where should we put some standard things we use? For exampe, lax monoidal pseudofunctor should be recalled early. Together with pseudonatural transformations I believe.}
+\item {\chris Where should we put some standard things we use?
+For exampe, lax monoidal pseudofunctor should be recalled early.
+Together with pseudonatural transformations I believe.
+For now, I put them in an unnamed section}
 \item {\chris Notation between \cref{Equiv} and \cref{thm:decoratedcospans} right now does not match! Need to fix.}
-\item {\chris There might be a way to completely hide the details of version 'fibres have, reindexing preserve' if that's what we want to do.}
+%\item {\chris There might be a way to completely hide the details of version 'fibres have, reindexing preserve' if that's what we want to do.}
 \end{itemize}
@@
 \end{defn}
-\begin{thm}[Shulman,7.8]\label{ShulDubEquiv}
-Given a strong double functor $\mathbb{F} \colon \mathbb{A} \to \mathbb{X}$, $\mathbb{F}$ is part of a double equivalence if and only if $\mathbb{F}$ is full, faithful and essentially surjective.
+
+Formally, two strong double functors between two double categories form a \emph{double equivalence} if {\chris their two-way composite is isomorphic to the identity, better expressed, possibly in a definition environment}.
+Similarly to ordinary equivalence of categories, {\chris cite shulman's theorem here [Shulman,7.8]} allows us to use the following equivalent characterization.
+
+\begin{thm}\label{ShulDubEquiv}
+A strong double functor $\mathbb{F} \colon \mathbb{A} \to \mathbb{X}$ is part of a double equivalence if and only if it is full, faithful and essentially surjective. {\chris on objects?}
 \end{thm}
@@
 \section{An equivalence of symmetric monoidal double categories} \label{EquivDoubleCats}
-In this section we prove that two different frameworks which utilize symmetric monoidal double categories, namely structured cospans and decorated cospans described respectively in \cref{DecCospansDoubleCat,sec:structuredcospans}, are equivalent under certain assumptions.
+In this section we prove that the two different double categorical network frameworks, namely structured cospans and decorated cospans described respectively in \cref{DecCospansDoubleCat,sec:structuredcospans}, are equivalent under certain assumptions.
 This is established by \cref{Equiv}, which relies on conditions relevant to the existence of left adjoints for opfibrations.
@@
 First of all, we recall some basics regarding opfibrations and their relation to pseudofunctors into $\bicat{Cat}$ via the Grothendieck construction.
-Standard material on fibration theory and the Grothendieck construction can be found for example in \cite{Herm}, \cite{Borc}.
+Standard material on the theory of fibrations can be found for example in \cite{Herm}, \cite{Borc}.
 
@@
 %\end{defn}
-The category $\X$ is called the \textbf{total} category, whereas $\A$ is the \textbf{base} category of the opfibration.
-For any $a\in\A$, the \textbf{fibre} $\X_a$ consists of all objects that map to $a$ and vertical morphisms between them, i.e.
+The category $\X$ is called the \textbf{total} category and $\A$ is called the \textbf{base} category of the opfibration.
+For any $a\in\A$, the \textbf{fibre category} $\X_a$ consists of all objects that map to $a$ and vertical morphisms between them, i.e.
 mapping to $1_a$.
-Assuming the axiom of choice, we may select a cocartesian arrow over each $f\maps a\to b$ in $\A$ and $x\in\X _a$, denoted by $\mathrm{Cocart}(f,x)\maps x\to f_!(x)$; $U$ is then called a \textbf{cloven opfibration}.
-This choice induces the so-called \textbf{reindexing functors} $f_!\colon\X _a\to\X _b$ between the fibre categories, which by the liftings universal property adhere to $(1_a)_!\cong1_{\X _a}$ and $(f\circ g)_!\cong f_!\circ g_!$.
+Assuming the axiom of choice, we may select a cocartesian arrow over each $f\maps a\to b$ in $\A$ and $x\in\X _a$, denoted by $\mathrm{Cocart}(f,x)\maps x\to f_!(x)$, rendering $U$ a so-called \textbf{cloven} opfibration.
+This choice induces \textbf{reindexing functors} $f_!\colon\X _a\to\X _b$ between the fibre categories, which by the liftings universal property adhere to natural $(1_a)_!\cong1_{\X _a}$ and $(f\circ g)_!\cong f_!\circ g_!$.
 If these isomorphisms are equalities, we have the notion of a \textbf{split} opfibration.
@@
 Let $\OpFib(\A)$ denote the 2-subcategory of the slice 2-category $\mathbf{Cat}/ \A$ of opfibrations over $\A$, functors that preserve cocartesian liftings and natural transformations with vertical components.
-In fact, there is a 2-equivalence between opfibrations and pseudofunctors induced by the so-called \emph{Grothendieck construction}.
+In fact, there is a 2-equivalence between opfibrations and pseudofunctors, see Section ?, induced by the so-called \emph{Grothendieck construction}.
 %{\chris I don't mind this presentation of the Grothendieck construction which I admit not having seeing before.
@@
         \item Every opfibration $\U \maps \X \to \A$ gives rise to a pseudofunctor $F_U \maps \A \to \bicat{Cat}$.
-        \item Every opindexed category $F \maps \A \to Cat$ gives rise to  an opfibration $\U_F \colon \inta F\to\A$.
+        \item Every pseudofunctor $F \maps \A \to \bicat{Cat}$ gives rise to  an opfibration $\U_F \colon \inta F\to\A$.
         \item The above correspondences yield an equivalence of 2-categories 
@@
 
-In \cite{MV}, the Grothendieck construction is generalized to the monoidal setting, namely lax monoidal structures on a pseudofunctor $F\colon\A\to\bicat{Cat}$ bijectively correspond to monoidal structures on the total category $\inta F$ such that the induced opfibration is a strict monoidal functor and $\otimes_{\inta F}$ is cartesian, see \cite[Thm.
+In \cite{MV}, the Grothendieck construction is generalized to the monoidal setting, namely lax monoidal structures on a pseudofunctor $F\colon\A\to\bicat{Cat}$ bijectively correspond to monoidal structures on the total category $\inta F$ such that the induced opfibration is a strict monoidal functor and $\otimes_{\inta F}$ preserves liftings, see \cite[Thm.
 3.10]{MV}.
-If the monoidal category $\A$ is in fact cocartesian monoidal, there is a further correspondence of the two structures with an ordinary pseudofunctor $F\colon\A\to\ca{MonCat}$:
+If the monoidal category $\A$ is in fact cocartesian, there is a further correspondence of the two structures with an ordinary pseudofunctor $F\colon\A\to\bicat{MonCat}$ into the 2-category of monoidal categories, strong monoidal functors and monoidal natural transformations:
 \begin{gather}
@@
 \end{gather}
-where the second equivalence was already observed by Shulman in \cite{Shul2}.
+The second equivalence was in fact earlier observed by Shulman in \cite{Shul2}.
 In more detail, if $(\phi,\phi_0)$ is the lax monoidal structure of $F$, each fibre category $\X_a=F(a)$ obtains a monoidal structure via
@@
 4.8]{MV}.
-In that case, the monoidal opfibration clauses for $U\colon(\X,+,0)\to(\A,+,0)$ in fact translate to the functor (strictly) preserving coproducts and the initial object, and bijectively correspond to pseudofunctors $F\colon\A\to\bicat{cocartCat}$ into the 2-category of cocartesian categories, functors that preserve coproducts and initial objects and natural transformations.
+In that case, the monoidal opfibration clauses for $U\colon(\X,+,0)\to(\A,+,0)$ translate to the functor (strictly) preserving coproducts and the initial object, and bijectively correspond to pseudofunctors $F\colon\A\to\bicat{cocartCat}$ into the 2-category of cocartesian categories, functors that preserve coproducts and initial objects and natural transformations.
 
@@
 all finite colimits.
-Of course, the following is more general since it relates the existence of any class of colimits in the total category of an opfibration to their existence in the fibres; for a more detailed exposition and proof, see \cite{Herm}.
+Of course, the following statement is more general since it relates the existence of any class of colimits in the total category of an opfibration to their existence in the fibres; for a more detailed exposition and proof, see \cite{Herm}.
 
@@
 
-The first part formulates the existence of colimits \emph{locally} in each fiber, which can equivalently be expressed by the corresponding pseudofunctor $F\colon\A\to\bicat{Cat}$ landing on the sub-2-category $\bicat{fcocCat}$ of finitely cocomplete categories and functors that preserve colimits; the second part formulates the existence of colimits \emph{globally} in the total category $\inta F$.
+The first part formulates the existence of colimits \emph{locally} in each fibre, which can equivalently be expressed by the corresponding pseudofunctor $F\colon\A\to\bicat{Cat}$ landing on the sub-2-category $\bicat{fcocCat}$ of finitely cocomplete categories and functors that preserve colimits.
+The second part formulates the existence of colimits \emph{globally} in the total category $\inta F$.
 Combining these, we can deduce the following.
@@
 
-On a different but related subject, for our purposes we are interested in the existence of a left adjoint $L_F \colon \A \to \X$ for the induced monoidal opfibration $ \inta{F} \to \A$ by the Grothendieck construction as discussed above.
+On a different but related subject, for our purposes we are interested in the existence of a left adjoint $L_F$ to the induced monoidal opfibration $ \inta{F} \to \A$ by the Grothendieck construction as discussed above.
 The following result provides sufficient conditions for that, which go hand-in-hand with \cref{cor:fcocMonGroth} and \cref{lem:fibrewiselimits}.
@@
 
-Finally, if that pseudofunctor is lax monoidal $(F,\phi,\phi_0)\colon(\A,+,0)\to(\bicat{Cat},\times,\mathbf{1})$ to begin with, the monoidal Grothendieck construction in the cocartesian case discussed earlier (\cref{eq:explicitstructure1}) express $\bot_a$ as the image of the composite
+Finally, if that pseudofunctor is lax monoidal $(F,\phi,\phi_0)\colon(\A,+,0)\to(\bicat{Cat},\times,\mathbf{1})$ to begin with, the monoidal Grothendieck construction in the cocartesian case discussed earlier (\cref{eq:explicitstructure1}) expresses $\bot_a$ as the image of the composite
 \begin{equation}\label{eq:initialinfibre}
@@
 
-We have now laid all the necessary theoretical background to formally establish an equivalence between the double category of decorated cospans and the double category of structured cospans constructed from a symmetric lax monoidal pseudofunctor into $\bicat{Cat}$.
+We have now laid all the necessary background to formally establish an equivalence between the double category of decorated cospans and the double category of structured cospans, constructed from a symmetric lax monoidal pseudofunctor into $\bicat{Cat}$.
 
@@
 \begin{proof}
-Recall that the double category of decorated cospans $\dcsp{F}$ has objects and vertical 1-morphisms those of $\A$, horizontal 1-cells $a\tickar b$ are cospans $\cspn{a}{c}{b}{}{}$ in $\A$ along with $d\in F(c)$, and 2-morphisms are cospan maps $k\colon c\to c'$ such that $(Fk)(d)=d'$, see \cref{eq:FCsp2morph}.
+Recall that the double category of decorated cospans $\dcsp{F}$ has objects and vertical 1-morphisms those of $\A$, horizontal 1-cells $a\tickar b$ are cospans $\cspn{a}{c}{b}{}{}$ in $\A$ along with $d\in F(c)$, and 2-morphisms are cospan maps $k\colon c\to c'$ together with a morphism $\iota\colon(Fk)(d)\to d'$, see \cref{eq:FCsp2morph}.
 
@@
 to construct a left adjoint $L_F\colon\A\to\inta F$ which is also a right inverse, namely $U_FL_F=\mathrm{id}_\A$.
-Explicitly, this left adjoint is given by $L(a)=(a,\bot_a)$, picking the initial object in the finitely cocomplete fibre also expressed as $F(u_a)\circ\phi_0(*)$ as in \cref{eq:initialinfibre}.
+Explicitly, this left adjoint is given by $L(a)=(a,\bot_a)$, picking the initial object in the finitely cocomplete fibre also expressed as $F(u_a)\circ\phi_0(*)$ in \cref{eq:initialinfibre}.
 Diagrammatically,
@@
 \end{displaymath}
-roughly describes the bridge between the original $F$ and the resulting $L_F$.
+roughly describes the processes between the original $F$ and the resulting $L_F$.
 
@@
 \end{equation}
-according to \cref{def:GrothCat}. The 2-morphisms in this double category are as in \cref{eq:2cellsStrCsp}.
-
-In order to prove that there is a double equivalence between $\dcsp{F}$ and $\scsp{L_F}{\inta F}$, we define a %n identity-on-objects and vertical morphism
+according to \cref{def:GrothCat}. The 2-morphisms in this double category are as in \cref{eq:2cellsStrCsp}. {\chris will expand.}
+
+In order to prove that there is a double equivalence (\cref{ShulDubEquiv}) between $\dcsp{F}$ and $\scsp{L_F}{\inta F}$, we define a %n identity-on-objects and vertical morphism
 double functor
@@
 The object component of $\mathbb{E}=(\mathbb{E}_0,\mathbb{E}_1)$ is $\mathbb{E}_0 = \id_{\mathsf{A}}$ since both double categories have $\mathsf{A}$ as their vertical category; trivially, $\mathbb{E}_0$ is an equivalence of categories.
-Given a horizontal 1-cell in $\scsp{L_F}{\inta F}$ like \cref{eq:scsphor1cell}, the arrow component $\mathbb{E}_1$ of the double functor maps it simply to the decorated cospan
+Given a horizontal 1-cell in $\scsp{L_F}{\inta F}$ like \cref{eq:scsphor1cell}, the arrow component $\mathbb{E}_1$ of the double functor simply maps it to the decorated cospan
 \begin{displaymath}
@@
 \end{displaymath}
-which is really a bijective correspondence since the unique maps from the initial objects in the fibres are always there. {\chris maybe too informal explanation!}
+Notice that this really is a bijective correspondence since the unique maps from the initial objects in the fibres provide no extra information.
 

### 2019-05-14 EquivCompFrameworks_20180911kc.tex
actually completed the double mapping

@@
 \begin{itemize}
-\item {\chris Discuss the name of Decorated and Structured cospan double categories one last time? :)}
+\item {\chris Discuss notation for Decorated and Structured cospan double categories one last time? :)}
 \item {\chris Where should we put some standard things we use?
@@
 \item{horizontal 1-cells given by cospans of $\mathsf{X}$ of the form:
-\[
+\begin{equation}\label{eq:structuredcospan}
 \begin{tikzpicture}[scale=1.5]
@@
 \end{tikzpicture}
-\]
+\end{equation}
 and}
@@
 \end{itemize}
+{\chris Might need to write the composition rule? Depending on the final proof of Big Theorem.}
 This is an opfibred category over $\A$ via the obvious forgetful functor, with fibre categories $(\inta F)_a=F(a)$ and reindexing functors $f_!=F(f)$.
@@
 \begin{proof}\emph{(Sketch)}
- The left adjoint $L\colon\A\to\X$ maps an object $a$ to the initial object in its fibre $\X_a$, denoted by $\bot_a$. By construction, $U(L(a))=U(\bot_a)=a$.
+ The left adjoint $L\colon\A\to\X$ maps an object $a$ to the initial object in its fibre $\X_a$, denoted by $\bot_a$.
+By construction, $U(L(a))=U(\bot_a)=a$.
+On morphisms $f\colon a\to a'$, $L(f)$ is defined by
+ \begin{equation}\label{eq:Lonarrows}
+  \bot_a\xrightarrow{\Cocart(f,\bot_a)}f_!(\bot_a)\xrightarrow{\;\stackrel{\chi_a}{\cong}\;}\bot_{a'}
+ \end{equation}
+where $\chi_a$ is the unique isomorphism between the initial objects in the fibre above $a'$ since $f_!$ preserves them.
 \end{proof}
@@
 Using this functor $L_F$ between finitely cocomplete categories that preserves all colimits that exist (as a left adjoint), we can construct the double category of structured cospans $\scsp{L_F}{\inta F}$.
-Its objects and vertical morphisms are again those of the category $\A$, whereas horizontal 1-cells $a\tickar b$ are now cospans of the form $\cspn{L_F(a)}{v}{L_F(b)}{}{}$ in the Grothendieck category $\inta F$, which consist of two pairs of morphisms
+Its objects and vertical morphisms are again those of the category $\A$, whereas horizontal 1-cells $a\tickar b$ as in \cref{eq:structuredcospan} are now cospans of the form $\cspn{L_F(a)}{v}{L_F(b)}{}{}$ in the Grothendieck category $\inta F$.
+Explicitly, they consist of two pairs of morphisms
 \begin{equation}\label{eq:scsphor1cell}
@@
 \end{equation}
-according to \cref{def:GrothCat}. The 2-morphisms in this double category are as in \cref{eq:2cellsStrCsp}. {\chris will expand.}
+where $x\in F(c)$, according to \cref{def:GrothCat}. Finally, the 2-morphisms in this double category are as described in \cref{eq:2cellsStrCsp}, in this context fully unravelled below:
+\begin{displaymath}
+ \begin{tikzcd}[sep=1.5in,ampersand replacement=\&]
+ (a,\bot_a)\ar[r,"{\begin{cases}i\colon a\to c &\textrm{in }\A \\!\colon F(i)(\bot_a)\to x &\textrm{in }F(c)\end{cases}}"]\ar[d,"{\begin{cases}f\colon a\to a' &\textrm{in }\A \\\chi_a\colon F(f)(\bot_a)\cong \bot_{a'} &\textrm{in }F(a')\end{cases}}"description] \& (c,x) \ar[d,"{\begin{cases}k\colon c\to c' &\textrm{in }\A \\h\colon F(k)(x)\to x' &\textrm{in }F(c')\end{cases}}"description] \& (b,\bot_b)\ar[l,"{\begin{cases}o\colon b\to c &\textrm{in }\A \\!\colon F(o)(\bot_b)\to x &\textrm{in }F(c)\end{cases}}"']\ar[d,"{\begin{cases}g\colon b\to b' &\textrm{in }\A \\\chi_b\colon F(g)(\bot_b)\cong \bot_{b'} &\textrm{in }F(b')\end{cases}}"description] \\
+ (a',\bot_{a'})\ar[r,"{\begin{cases}i'\colon a'\to c' &\textrm{in }\A \\!\colon F(i')(\bot_{a'})\to x' &\textrm{in }F(c')\end{cases}}"'] \& (c',x') \& (b',\bot_{b'})\ar[l,"{\begin{cases}o'\colon b'\to c' &\textrm{in }\A \\!\colon F(o')(\bot_{b'})\to x' &\textrm{in }F(c')\end{cases}}"]
+ \end{tikzcd}
+\end{displaymath}
+where the outside vertical legs come from the definition of $L_F$ on arrows, \cref{eq:Lonarrows}. 
+{\chris The above diagram might be a bit overwhelming, but all info is there. Choose which parts are required for a smooth proof!}
+The square commutativities translate to $k\circ i=i'\circ f$ and $k\circ o=o'\circ g$ in $\A$, and also by composition in the Grothendieck category, to
+\begin{gather*}
+ F(k\circ i)(\bot_a)\cong Fk(Fi(\bot_a))\xrightarrow{Fk(!)}Fk(x)\xrightarrow{h}x'= \\
+ F(i'\circ f)(\bot_a)\cong Fi'(Ff(\bot_a))\xrightarrow{Fi'(\chi_a)}Fi'(\bot_{a'})\xrightarrow{!}x'
+\end{gather*}
+in the category $F(c')$.
+However, since all maps are unique in the above equality {\chris discuss with John and Kenny}, this gives no extra conditions for the morphisms involved, and similarly for the equality including $o, o'$.
 
@@
 Notice that this really is a bijective correspondence since the unique maps from the initial objects in the fibres provide no extra information.
-
-{\chris in progress}
+Finally, given a 2-morphism of $L_F$-structured cospans as described above, $\mathbb{E}_1$ maps it to the underlying cospan 2-morphism
+\begin{displaymath}
+ \begin{tikzcd}
+a\ar[r,"i"]\ar[d,"f"'] & c\ar[d,"k"] & b\ar[l,"o"']\ar[d,"g"] \\
+a'\ar[r,"i'"']& c' & b'\ar[l,"o'"]
+ \end{tikzcd}
+\end{displaymath}
+ in $\A$ along with the map $h\colon Fk(x)\to x'$ in $F(c')$, namely a decorated cospan 2-morphism as per \cref{eq:FCsp2morph}.
+
+{\chris Now the checking of the equivalence should follow! perhaps in less detail than currently?}
 which is a cospan in $\mathsf{X}$ of the form:

### 2019-05-28 EquivCompFrameworks_20180911kc.tex
Some changes based on Kenny's thesis

@@
 Given another symmetric lax monoidal pseudofunctor $F^\prime \colon \mathsf{A^\prime} \to \mathbf{Cat}$, we can obtain another symmetric monoidal double category $F^\prime \mathbb{C}\textnormal{sp}$.
-Then a map from $F\mathbb{C}\textnormal{sp}$ to $F^\prime \mathbb{C}\textnormal{sp}$ will be a double functor $\mathbb{H} \colon F\mathbb{C}\textnormal{sp} \to F' \mathbb{C}\textnormal{sp}$ whose object component is given by a finite colimit preserving functor $\mathbb{H}_0 = H \colon \mathsf{A} \to \mathsf{A^\prime}$ and whose arrow component is given by a functor $\mathbb{H}_1$ defined on horizontal 1-cells by:
+A map from $F\mathbb{C}\textnormal{sp}$ to $F^\prime \mathbb{C}\textnormal{sp}$ will then be a double functor $\mathbb{H} \colon F\mathbb{C}\textnormal{sp} \to F' \mathbb{C}\textnormal{sp}$ whose object component is given by a finite colimit preserving functor $\mathbb{H}_0 = H \colon \mathsf{A} \to \mathsf{A^\prime}$ and whose arrow component is given by a functor $\mathbb{H}_1$ defined on horizontal 1-cells by:
 \[
@@
 \node (C') at (5.5,0) {$H(b)$};
-\node (D') at (4.5,-0.5) {$E(d) \in F^\prime(H(c))$};
+\node (D') at (4.5,-0.5) {$\theta_c E(d) \phi \in F^\prime(H(c))$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \node (D'') at (5.25,-0.5) {$H(c^\prime)$};
-\node (E'') at (7.5,0.5) {$E(d) \in F^\prime(H(c))$};
-\node (F'') at (7.5,-0.5) {$E(d^\prime) \in F^\prime(H(c^\prime))$};
-\node (G'') at (5.25,-1) {$E(\iota) \colon F^\prime(H(h))(E(d)) \to E(d^\prime)$};
+\node (E'') at (8,0.5) {$\theta_c E(d) \phi \in F^\prime(H(c))$};
+\node (F'') at (8,-0.5) {$\theta_{c'} E(d^\prime) \phi \in F^\prime(H(c^\prime))$};
+\node (G'') at (5.25,-1) {$E(\iota) \colon F^\prime(H(h))(\theta_c E(d)\phi) \to (\theta_{c'}E(d^\prime)\phi)$};
 \node (H) at (3.5,0) {$\mapsto$};
@@
 (A) edge node[left]{$f$} (A')
-(C) edge node[left]{$g$} (C')
+(C) edge node[right]{$g$} (C')
 (A') edge node {$$} (D)
@@
 (A'') edge node[left]{$H(f)$} (A''')
-(C'') edge node[left]{$H(g)$} (C''')
+(C'') edge node[right]{$H(g)$} (C''')
 (A''') edge node {$$} (D'')
@@
 \]
-where $E \colon \mathbf{Cat} \to \mathbf{Cat}$ is a symmetric lax monoidal pseudofuctor such that the following diagram commutes:
+where $E \colon \mathbf{Cat} \to \mathbf{Cat}$ is a symmetric lax monoidal pseudofuctor such that the following diagram commutes up to isomorphism $\theta \colon EF \Rightarrow F'H$:
 \[
@@
 \node (D) at (1,-1) {$\mathbf{Cat}$};
+\node (E) at (0.5,-0.5) {$\Swarrow \theta$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-Recall that we can think of the element $d \in F(c)$ as a morphism $d \colon 1 \to F(c)$ and the morphism $\iota \colon F(h)(d) \to d^\prime$ of $F(c^\prime)$ as a 2-morphism  in $\mathbf{Cat}$:
+Recall that we can think of the object $d \in F(c)$ as a morphism $d \colon 1 \to F(c)$ and the functor $\iota \colon F(h)(d) \to d^\prime$ of $F(c^\prime)$ as a natural transformation  in $\mathbf{Cat}$:
 \[
@@
 \node (D) at (1,-1) {$F(c^\prime)$};
-\node (C) at (0.75,-0.5) {$\Swarrow$};
+\node (C) at (0.75,-0.5) {$\Swarrow \iota$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-Applying the pseudofunctor $E \colon \mathbf{Cat} \to \mathbf{Cat}$ to this diagram yields:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,-0.5) {$1 \xrightarrow{\sim} E(1)$};
-\node (B) at (1.5,0) {$E(F(c))$};
-\node (D) at (1.5,-1) {$E(F(c^\prime))$};
-\node (C) at (1,-0.5) {$\Swarrow$};
+Applying the symmetric lax monoidal pseudofunctor $E \colon \mathbf{Cat} \to \mathbf{Cat}$ to this diagram yields:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,-0.5) {$1 \xrightarrow{\phi} E(1)$};
+\node (B) at (2,0) {$E(F(c))$};
+\node (D) at (2,-1) {$E(F(c^\prime))$};
+\node (C) at (1.5,-0.5) {$\Swarrow E(\iota)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-Then because the above square commutes, this is the same as 
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,-0.5) {$1 \xrightarrow{\sim} E(1)$};
-\node (B) at (1.5,0) {$F^\prime(H(c))$};
-\node (D) at (1.5,-1) {$F^\prime(H(c^\prime))$};
-\node (C) at (1,-0.5) {$\Swarrow$};
-\path[->,font=\scriptsize,>=angle 90]
+Then because the above square commutes up to the isomorphism $\theta \colon EF \Rightarrow F'H$, we get:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,-0.5) {$1 \xrightarrow{\phi} E(1)$};
+\node (B) at (2,0) {$E(F(c))$};
+\node (D) at (2,-1) {$E(F(c'))$};
+\node (C) at (1.5,-0.5) {$\Swarrow E(\iota)$};
+\node (E) at (4,0) {$F^\prime(H(c))$};
+\node (F) at (4,-1) {$F^\prime(H(c'))$};
+\path[->,font=\scriptsize,>=angle 90]
+(B) edge node [above] {$\theta_c$} (E)
+(D) edge node [above] {$\theta_{c'}$} (F)
+(E) edge node [right] {$F'(H(h))$} (F)
 (A) edge node[above]{$E(d)$} (B)
 (A) edge node[below]{$E(d^\prime)$} (D)
-(B) edge node[right]{$F^\prime(H((h))$} (D);
-\end{tikzpicture}
-\]
-which is the same as a morphism $E(\iota) \colon F^\prime(H(h))(E(d)) \to E(d^\prime)$ in $F^\prime(H(c^\prime))$.
+(B) edge node[right]{$E(F((h))$} (D);
+\end{tikzpicture}
+\]
+which results in a 2-morphism $E(\iota) \colon F^\prime(H(h))(\theta_c E(d)\phi) \to (\theta_{c'} E(d^\prime)\phi)$ in $F^\prime(H(c^\prime))$.
 To check that the above recipe is functorial, given two vertically composable 2-morphisms in $F\mathbb{C}\textnormal{sp}$:
@@
 (A) edge node[left]{$f$} (A')
-(C) edge node[left]{$g$} (C')
+(C) edge node[right]{$g$} (C')
 (A') edge node [above]{$$} (D)
@@
 (A'') edge node[left]{$f^\prime$} (A''')
-(C'') edge node[left]{$g^\prime$} (C''')
+(C'') edge node[right]{$g^\prime$} (C''')
 (A''') edge node [above]{$$} (D'')
@@
 (A) edge node[left]{$f^\prime f$} (A')
-(C) edge node[left]{$g^\prime g$} (C')
+(C) edge node[right]{$g^\prime g$} (C')
 (A') edge node [above]{$$} (D)
@@
 \node (D) at (1.5,-0.5) {$H(c'')$};
-\node (E) at (4.5,0.5) {$E(d) \in F^\prime(H(c))$};
-\node (F) at (4.5,-0.5) {$E(d'') \in F^\prime(H(c''))$};
-\node (G) at (1.5,-1) {$E(\iota ^\prime \iota) \colon F^\prime(H(h^\prime h))(E(d)) \to E(d'').$};
+\node (E) at (5,0.5) {$\theta_c E(d) \phi \in F^\prime(H(c))$};
+\node (F) at (5,-0.5) {$\theta_{c''} E(d'') \phi \in F^\prime(H(c''))$};
+\node (G) at (1.5,-1) {$E(\iota ^\prime \iota) \colon F^\prime(H(h^\prime h))(\theta_c E(d)\phi) \to (\theta_{c''}E(d'')\phi).$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (A) edge node[left]{$H(f^\prime f)$} (A')
-(C) edge node[left]{$H(g^\prime g)$} (C')
+(C) edge node[right]{$H(g^\prime g)$} (C')
 (A') edge node [above]{$$} (D)
@@
 \node (D) at (1.5,-0.5) {$H(c^\prime)$};
-\node (E) at (4.5,0.5) {$E(d) \in F^\prime(H(c))$};
-\node (F) at (4.5,-0.5) {$E(d^\prime) \in F^\prime(H(c^\prime))$};
-\node (G) at (1.5,-1) {$E(\iota) \colon F^\prime(H(h))(E(d)) \to E(d^\prime)$};
+\node (E) at (5,0.5) {$\theta_c E(d) \phi \in F^\prime(H(c))$};
+\node (F) at (5,-0.5) {$\theta_{c'} E(d^\prime) \phi \in F^\prime(H(c^\prime))$};
+\node (G) at (1.5,-1) {$E(\iota) \colon F^\prime(H(h))(\theta_c E(d)\phi) \to (\theta_{c'} E(d^\prime)\phi)$};
 \node (A'') at (0,-1.5) {$H(a^\prime)$};
@@
 \node (D'') at (1.5,-2.5) {$H(c'')$};
-\node (E'') at (4.5,-1.5) {$E(d^\prime) \in F^\prime(H(c^\prime))$};
-\node (F'') at (4.5,-2.5) {$E(d'') \in F^\prime(H(c''))$};
-\node (G'') at (1.5,-3) {$E(\iota^\prime) \colon F^\prime(H(h^\prime))(E(d^\prime)) \to E(d'')$};
+\node (E'') at (5,-1.5) {$\theta_{c'} E(d^\prime) \phi \in F^\prime(H(c^\prime))$};
+\node (F'') at (5,-2.5) {$\theta_{c''} E(d'') \phi \in F^\prime(H(c''))$};
+\node (G'') at (1.5,-3) {$E(\iota^\prime) \colon F^\prime(H(h^\prime))(\theta_{c'} E(d^\prime)\phi) \to (\theta_{c''}E(d'')\phi)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (A) edge node[left]{$H(f)$} (A')
-(C) edge node[left]{$H(g)$} (C')
+(C) edge node[right]{$H(g)$} (C')
 (A') edge node [above]{$$} (D)
@@
 (A'') edge node[left]{$H(f^\prime)$} (A''')
-(C'') edge node[left]{$H(g^\prime)$} (C''')
+(C'') edge node[right]{$H(g^\prime)$} (C''')
 (A''') edge node [above]{$$} (D'')
@@
 \node (C) at (2,0) {$b$};
-\node (D) at (1,-0.5) {$d_1 \in F(c_1)$};
+\node (D) at (1,-0.5) {$d_M \in F(c_1)$};
 \node (E) at (3,0) {$b$};
@@
 \node (G) at (5,0) {$a_2$};
-\node (H) at (4,-0.5) {$d_2 \in F(c_2)$};
+\node (H) at (4,-0.5) {$d_N \in F(c_2)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \node (C) at (3,0) {$a_2$};
-\node (D) at (1.5,-0.5) {$d \in F(c_1 +_b c_2)$};
+\node (D) at (1.5,-0.5) {$d_{M \odot N} \in F(c_1 +_b c_2)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-where $$d \colon 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{d_1 \times d_2} F(c_1) \times F(c_2) \xrightarrow{\phi_{c_1,c_2}} F(c_1+c_2) \xrightarrow{F(\psi)}F(c_1 +_b c_2).$$ The image of this horizontal 1-cell is then given by $\mathbb{H}(M \odot N)$:
+where $$d \colon 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{d_1 \times d_2} F(c_1) \times F(c_2) \xrightarrow{\phi_{c_1,c_2}} F(c_1+c_2) \xrightarrow{F(j)}F(c_1 +_b c_2).$$ The image of this horizontal 1-cell is then given by $\mathbb{H}(M \odot N)$:
 \[
@@
 \node (C) at (4,0) {$H(a_2)$};
-\node (D) at (2,-0.5) {$E(d) \in F^\prime(H(c_1 +_b c_2))$};
+\node (D) at (2,-0.5) {$\mathbb{H}(M \odot N) = \theta_{c_1 +_b c_2}E(d_{M \odot N}) \phi \in F^\prime(H(c_1 +_b c_2))$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-where $$E(d) \colon 1 \xrightarrow{E(d)} E(F(c_1 +_b c_2)) = F^\prime(H(c_1 +_b c_2)).$$ On the other hand, the image of each horizontal 1-cell under the double functor $\mathbb{H}$ is given respectively by $\mathbb{H}(M)$ and $\mathbb{H}(N)$:
+where $$\mathbb{H}(M \odot N) = \theta_{c_1 +_b c_2} E(d_{M \odot N}) \phi \colon 1 \xrightarrow{\phi} E(1) \xrightarrow{E(d)} E(F(c_1 +_b c_2)) \xrightarrow{\theta_{c_1 +_b c_2}} F^\prime(H(c_1 +_b c_2)).$$ On the other hand, the image of each horizontal 1-cell under the double functor $\mathbb{H}$ is given respectively by $\mathbb{H}(M)$ and $\mathbb{H}(N)$:
 \[
@@
 \node (C) at (2,0) {$H(b)$};
-\node (D) at (1,-0.5) {$E(d_1) \in F^\prime(H(c_1))$};
+\node (D) at (1,-0.5) {$\theta_{c_1} E(d_M)\phi \in F^\prime(H(c_1))$};
 \node (E) at (3,0) {$H(b)$};
@@
 \node (G) at (5,0) {$H(a_2)$};
-\node (H) at (4,-0.5) {$E(d_2) \in F^\prime(H(c_2))$};
+\node (H) at (4,-0.5) {$\theta_{c_2} E(d_N) \phi \in F^\prime(H(c_2))$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \node (C) at (4.5,0) {$H(a_2)$};
-\node (D) at (2.25,-0.5) {$d^\prime \in F^\prime(H(c_1) +_{H(b)} H(c_2))$};
+\node (D) at (2.25,-0.5) {$d_{\mathbb{H}(M) \odot \mathbb{H}(N)} \in F^\prime(H(c_1) +_{H(b)} H(c_2))$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-where $$d^\prime \colon 1 \xrightarrow{E(d_1) \times E(d_2)} F^\prime(H(c_1)) \times F^\prime(H(c_2)) \xrightarrow{\Phi_{H(c_1),H(c_2)}} F^\prime(H(c_1)+ H(c_2)) \xrightarrow{F^\prime (H(\Psi))} F^\prime(H(c_1) +_{H(b)} H(c_2)).$$
+where $$\hspace{-.4in}\scriptstyle{d_{\mathbb{H}(M) \odot \mathbb{H}(N)} \colon 1 \xrightarrow{(\theta_{c_1} \times \theta_{c_2})(E(d_M) \times E(d_N)) \phi} F^\prime(H(c_1)) \times F^\prime(H(c_2)) \xrightarrow{\Phi_{H(c_1),H(c_2)}} F^\prime(H(c_1)+ H(c_2)) \xrightarrow{F^\prime (J)} F^\prime(H(c_1) +_{H(b)} H(c_2)).}$$
 We then have a comparison constraint: $$\mathbb{H}_{M,N} \colon \mathbb{H}(M) \odot \mathbb{H}(N) \xrightarrow{\sim} \mathbb{H}(M \odot N)$$given by the globular 2-isomorphism:
@@
 \node (D) at (2.5,-0.5) {$H(c_1 +_b c_2)$};
-\node (E) at (7,0.5) {$d^\prime \in F^\prime(H(c_1)+_{H(b_1)}H(c_2))$};
-\node (F) at (7,-0.5) {$E(d) \in F^\prime(H(c_1 +_b c_2))$};
-\node (G) at (2.5,-1) {$\iota_{\kappa^{-1}} \colon F^\prime(\kappa^{-1})(d^\prime) \to E(d).$};
+\node (E) at (7.5,0.5) {$d_{\mathbb{H}(M) \odot \mathbb{H}(N)} \in F^\prime(H(c_1)+_{H(b_1)}H(c_2))$};
+\node (F) at (7.5,-0.5) {$d_{\mathbb{H}(M \odot N)} \in F^\prime(H(c_1 +_b c_2))$};
+\node (G) at (2.5,-1) {$\iota_{\kappa^{-1}} \colon F^\prime(\kappa^{-1})(d_{\mathbb{H}(M) \odot \mathbb{H}(N)}) \to d_{\mathbb{H}(M \odot N)}.$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (A) edge node[left]{$1$} (A')
-(C) edge node[left]{$1$} (C')
+(C) edge node[right]{$1$} (C')
 (A') edge node [above]{$H(\psi j_{c_1} i_1)$} (D)
@@
 \]
-where $\kappa$ is the isomorphism $$\kappa \colon H(c_1 +_b c_2) \xrightarrow{\sim} H(c_1) +_{H(b)} H(c_2)$$ comes from the finite colimit preserving functor $H \colon \mathsf{A} \to \mathsf{A^\prime}$.
+where $\kappa$ is the isomorphism $$\kappa \colon H(c_1 +_b c_2) \xrightarrow{\sim} H(c_1) +_{H(b)} H(c_2)$$ which comes from the finite colimit preserving functor $H \colon \mathsf{A} \to \mathsf{A^\prime}$.
 The above diagram commutes by a similar argument to the one used in Theorem \ref{Equiv}.
-Similarly we have a unit comparison constraint $$\mathbb{H}_U \colon U_{\mathbb{H}(c)} \to \mathbb{H}(U_c)$$ given by the globular 2-isomorphism:
+Similarly, for every object $c \in \mathsf{A}$, we have a unit comparison constraint $$\mathbb{H}_U \colon U_{\mathbb{H}(c)} \to \mathbb{H}(U_c)$$ given by the globular 2-isomorphism:
 \[
@@
 \node (E) at (4.5,0.5) {$!_{H(c)} \in F^\prime(H(c))$};
-\node (F) at (4.5,-0.5) {$E(!_c) \in F^\prime(H(c))$};
+\node (F) at (4.5,-0.5) {$\theta_c E(!_c) \phi \in F^\prime(H(c))$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (A) edge node[left]{$1$} (A')
-(C) edge node[left]{$1$} (C')
+(C) edge node[right]{$1$} (C')
 (A') edge node [above]{$1$} (D)
@@
 \]
-where the morphism of decorations is the morphism $\iota \colon !_{H(c)} \to E(!_c)$ in $F'(H(c))$. These comparison constrains satisfy the coherence axioms of a monoidal category, namely:
+where the morphism of decorations is the morphism $\iota \colon !_{H(c)} \to (\theta_c E(!_c) \phi)$ in $F'(H(c))$.
+These comparison constrains satisfy the coherence axioms of a monoidal category, namely:
 \[
@@
 The diagrams involving the morphisms of decorations are similar to those in Theorem \ref{DC}.
-This shows that $\mathbb{H}=(H,E)$ is a double functor.
+This shows that $\mathbb{H}=(H,E,\theta)$ is a double functor.
 Next we show that this double functor is symmetric monoidal.
@@
 \node (C) at (2,0) {$b_1$};
-\node (D) at (1,-0.5) {$d_1 \in F(c_1)$};
+\node (D) at (1,-0.5) {$d_{M_1}\in F(c_1)$};
 \node (E) at (3,0) {$a_2$};
@@
 \node (G) at (5,0) {$b_2$};
-\node (H) at (4,-0.5) {$d_2 \in F(c_2)$};
+\node (H) at (4,-0.5) {$d_{M_2} \in F(c_2)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \node (C) at (3,0) {$b_1+b_2$};
-\node (D) at (1.5,-0.5) {$d_1+d_2 \in F(c_1+c_2)$};
+\node (D) at (1.5,-0.5) {$d_{M_1 \otimes M_2} \in F(c_1+c_2)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-$$d_1+d_2 \colon 1 \xrightarrow{d_1 \times d_2} F(c_1) \times F(c_2) \xrightarrow{\phi_{c_1,c_2}} F(c_1+c_2)$$
+$$d_{M_1 \otimes M_2} \colon 1 \xrightarrow{d_1 \times d_2} F(c_1) \times F(c_2) \xrightarrow{\phi_{c_1,c_2}} F(c_1+c_2)$$
 and the image of this horizontal 1-cell under the double functor $\mathbb{H}$ is $\mathbb{H}(M_1 \otimes M_2)$ given by:
@@
 \node (C) at (4,0) {$H(b_1+b_2)$};
-\node (D) at (2,-0.5) {$E(d_1+d_2) \in E(F(c_1+c_2)) = F^\prime(H(c_1+c_2))$};
+\node (D) at (2,-0.5) {$d_{\mathbb{H}(M_1 \otimes M_2)} = \theta_{c_1+c_2} E(d_{M_1 \otimes M_2})\phi \in F^\prime(H(c_1+c_2))$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \node (A) at (0,0) {$H(a_1)$};
-\node (B) at (1,0) {$H(c_1)$};
-\node (C) at (2,0) {$H(b_1)$};
-\node (D) at (1,-0.5) {$E(d_1) \in F^\prime(H(c_1))$};
-\node (E) at (3,0) {$H(a_2)$};
-\node (F) at (4,0) {$H(c_2)$};
-\node (G) at (5,0) {$H(b_2)$};
-\node (H) at (4,-0.5) {$E(d_2) \in F^\prime(H(c_2))$};
+\node (B) at (1.5,0) {$H(c_1)$};
+\node (C) at (3,0) {$H(b_1)$};
+\node (D) at (1.5,-0.5) {$d_{\mathbb{H}(M_1)} = \theta_{c_1}E(d_{M_1})\phi \in F^\prime(H(c_1))$};
+\node (E) at (4.5,0) {$H(a_2)$};
+\node (F) at (6,0) {$H(c_2)$};
+\node (G) at (7.5,0) {$H(b_2)$};
+\node (H) at (6,-0.5) {$d_{\mathbb{H}(M_2)} = \theta_{c_2}E(d_{M_2})\phi \in F^\prime(H(c_2))$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \node (C) at (5,0) {$H(b_1)+H(b_2)$};
-\node (D) at (2.5,-0.5) {$E(d_1)+E(d_2) \in F^\prime(H(c_1)+H(c_2))$};
+\node (D) at (2.5,-0.5) {$d_{\mathbb{H}(M_1) \otimes \mathbb{H}(M_2)} \in F^\prime(H(c_1)+H(c_2))$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-$$E(d_1)+E(d_2) \colon 1 \xrightarrow{E(d_1) \times E(d_2)} F^\prime(H(c_1)) \times F^\prime(H(c_2)) \xrightarrow{\Phi_{H(c_1),H(c_2)}} F^\prime (H(c_1)+H(c_2)).$$  We then have a natural 2-isomorphism $\mu_{M_1,M_2} \colon \mathbb{H}(M_1) \otimes \mathbb{H}(M_2) \to \mathbb{H}(M_1 \otimes M_2)$ in $F'\mathbb{C}\textnormal{sp}$ given by:
+$$\hspace{-.4in} \scriptstyle{d_{\mathbb{H}(M_1) \otimes \mathbb{H}(M_2)} \colon 1 \xrightarrow{(\phi \times \phi)(\lambda^{-1} \times \lambda^{-1})} E(1) \times E(1) \xrightarrow{(\theta_{c_1} \times \theta_{c_2})(E(d_{M_1}) \times E(d_{M_2}))} F^\prime(H(c_1)) \times F^\prime(H(c_2)) \xrightarrow{\Phi_{H(c_1),H(c_2)}} F^\prime (H(c_1)+H(c_2)).}$$  We then have a natural 2-isomorphism $\mu_{M_1,M_2} \colon \mathbb{H}(M_1) \otimes \mathbb{H}(M_2) \to \mathbb{H}(M_1 \otimes M_2)$ in $F'\mathbb{C}\textnormal{sp}$ given by:
 \[
@@
 \node (D) at (2.5,-0.5) {$H(c_1+c_2)$};
-\node (E) at (2.5,1) {$E(d_1)+E(d_2) \in F^\prime(H(c_1)+H(c_2))$};
-\node (F) at (2.5,-1) {$E(d_1+d_2) \in F^\prime(H(c_1+c_2))$};
+\node (E) at (2.5,1) {$d_{\mathbb{H}(M_1) \otimes \mathbb{H}(M_2)} \in F^\prime(H(c_1)+H(c_2))$};
+\node (F) at (2.5,-1) {$d_{\mathbb{H}(M_1 \otimes M_2)} \in F^\prime(H(c_1+c_2))$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-$$\iota_\kappa \colon F^\prime(\kappa)(E(d_1)+E(d_2)) \to E(d_1+d_2)$$
+$$\iota_\kappa \colon F^\prime(\kappa)(d_{\mathbb{H}(M_1) \otimes \mathbb{H}(M_2)}) \to d_{\mathbb{H}(M_1 \otimes M_2)}$$
 where $\kappa$ denotes the isomorphism arising from $H$ preserving finite colimits.
@@
 \node (C) at (0,-1.5) {$\mathbb{H}((M_1 \otimes M_2) \otimes M_3)$};
-\node (A') at (3,0.5) {$\mathbb{H}(M_1) \otimes (\mathbb{H}(M_2) \otimes \mathbb{H}(M_3))$};
-\node (B') at (3,-0.5) {$\mathbb{H}(M_1) \otimes \mathbb{H}(M_2 \otimes M_3)$};
-\node (C') at (3,-1.5) {$\mathbb{H}(M_1 \otimes (M_2 \otimes M_3))$};
+\node (A') at (4,0.5) {$\mathbb{H}(M_1) \otimes (\mathbb{H}(M_2) \otimes \mathbb{H}(M_3))$};
+\node (B') at (4,-0.5) {$\mathbb{H}(M_1) \otimes \mathbb{H}(M_2 \otimes M_3)$};
+\node (C') at (4,-1.5) {$\mathbb{H}(M_1 \otimes (M_2 \otimes M_3))$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-with the corresponding diagram of decorations:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$F^\prime(\alpha \kappa \kappa)((E(d_1)+E(d_2))+E(d_3))$};
-\node (B) at (0,-0.5) {$F^\prime(\alpha \kappa)(E(d_1+d_2)+E(d_3))$};
-\node (C) at (0,-1.5) {$F^\prime(\alpha)(E((d_1+d_2)+d_3))$};
-\node (A') at (5,0.5) {$F^\prime(\kappa \kappa)(E(d_1)+(E(d_2)+E(d_3)))$};
-\node (B') at (5,-0.5) {$F^\prime(\kappa)(E(d_1)+E(d_2+d_3))$};
-\node (C') at (5,-1.5) {$E(d_1+(d_2+d_3))$};
+with the corresponding diagram of decorations in $F'(H(c_1+(c_2+c_3)))$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0.5) {$F^\prime(\alpha \kappa \kappa)(d_{(\mathbb{H}(M_1) \otimes \mathbb{H}(M_2)) \otimes \mathbb{H}(M_3)})$};
+\node (B) at (0,-0.5) {$F^\prime(\alpha \kappa)(d_{\mathbb{H}(M_1 \otimes M_2) \otimes \mathbb{H}(M_3)})$};
+\node (C) at (0,-1.5) {$F^\prime(\alpha)(d_{\mathbb{H}((M_1 \otimes M_2) \otimes M_3)})$};
+\node (A') at (5,0.5) {$F^\prime(\kappa \kappa)(d_{\mathbb{H}(M_1) \otimes (\mathbb{H}(M_2) \otimes \mathbb{H}(M_3))})$};
+\node (B') at (5,-0.5) {$F^\prime(\kappa)(d_{\mathbb{H}(M_1) \otimes \mathbb{H}(M_2 \otimes M_3)})$};
+\node (C') at (5,-1.5) {$d_{\mathbb{H}(M_1 \otimes (M_2 \otimes M_3))}$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-where $$F^\prime(\alpha \kappa \kappa)((E(d_1)+E(d_2))+E(d_3)) = F^\prime(\kappa \kappa \alpha^\prime)((E(d_1)+E(d_2))+E(d_3))$$
-as the corresponding hexagon for the symmetric lax monoidal pseudofunctor $E \colon \mathbf{Cat} \to \mathbf{Cat}$ commutes.
+where $$F^\prime(\alpha \kappa \kappa)(d_{(\mathbb{H}(M_1) \otimes \mathbb{H}(M_2)) \otimes \mathbb{H}(M_3)}) = F^\prime(\kappa \kappa \alpha^\prime)(d_{(\mathbb{H}(M_1) \otimes \mathbb{H}(M_2)) \otimes \mathbb{H}(M_3)})$$
+as the corresponding hexagon for the finite colimit preserving functor $H \colon \mathsf{A} \to \mathsf{A'}$ commutes.
+The map $\mu_{M_1,M_2}$ is also compatible with the braidings $\beta$ and $\beta^\prime$ of $F \mathbb{C}\textnormal{sp}_1$ and $F' \mathbb{C}\textnormal{sp}_1$, respectively, and make the necessary square commute as a consequence of the corresponding commutative square involving braidings from the finite colimit preserving functor $H \colon \mathsf{A} \to \mathsf{A'}$.
 
@@
 %\node (I) at (5,-0.5) {$!_{1_{\mathsf{A^\prime}}} \in F^\prime(1_{\mathsf{A^\prime}})$};
-\node (D) at (1,-0.5) {$E(!_{1_\mathsf{A}}) \in F^\prime(H(1_\mathsf{A}))$};
+\node (D) at (1,-0.5) {$\theta_{1_\mathsf{A}}E(!_{1_\mathsf{A}}) \phi \in F^\prime(H(1_\mathsf{A}))$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \node (D) at (1.5,-0.5) {$H(1_\mathsf{A})$};
-\node (E) at (4.5,0.5) {$!_{1_\mathsf{A^\prime}} \in F^\prime(1_\mathsf{A^\prime})$};
-\node (F) at (4.5,-0.5) {$E(!_{1_\mathsf{A}}) \in F^\prime(H(1_\mathsf{A}))$};
+\node (E) at (5,0.5) {$!_{1_\mathsf{A^\prime}} \in F^\prime(1_\mathsf{A^\prime})$};
+\node (F) at (5,-0.5) {$\theta_{1_\mathsf{A}} E(!_{1_\mathsf{A}}) \phi \in F^\prime(H(1_\mathsf{A}))$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (A) edge node[left]{$\kappa$} (A')
-(C) edge node[left]{$\kappa$} (C')
+(C) edge node[right]{$\kappa$} (C')
 (A') edge node [above]{$1$} (D)
@@
 \]
-together with the morphism $\iota_\mu \colon F^\prime(\kappa)(!_{1_\mathsf{A^\prime}}) \to E(!_{1_\mathsf{A}})$ in $F^\prime(H(1_\mathsf{A}))$. The following square then commutes: 
+together with the morphism $\iota_\mu \colon F^\prime(\kappa)(!_{1_\mathsf{A^\prime}}) \to (\theta_{1_\mathsf{A}} E(!_{1_\mathsf{A}})\phi)$ in $F^\prime(H(1_\mathsf{A}))$.
+The following square then commutes for any horizontal 1-cell $M$ of $F \mathbb{C}\textnormal{sp}$:
 \[
@@
 \node (C) at (0,-1) {$\mathbb{H}(M)$};
-\node (D) at (2.5,-1) {$\mathbb{H}(1_\mathsf{A} + M)$};
+\node (D) at (2.5,-1) {$\mathbb{H}(1_\mathsf{A} \otimes M)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$F^\prime(\ell)(!_{1_\mathsf{A^\prime}} + E(d))$};
-\node (B) at (0,-0.5) {$E(d)$};
-\node (A') at (4,0.5) {$F^\prime(H(\ell^\prime) \kappa)(E(!_{1_\mathsf{A}})+E(d))$};
-\node (B') at (4,-0.5) {$F^\prime(H(\ell^\prime))(E(!_{1_\mathsf{A}} + d))$};
+\node (A) at (0,0.5) {$F^\prime(\ell)(d_{!_{1_\mathsf{A^\prime}}} \otimes d_{\mathbb{H}(M)})$};
+\node (B) at (0,-0.5) {$d_{\mathbb{H}(M)}$};
+\node (A') at (4,0.5) {$F^\prime(H(\ell^\prime) \kappa)(d_{!_{\mathbb{H}(1_\mathsf{A})}}\otimes d_{\mathbb{H}(M)})$};
+\node (B') at (4,-0.5) {$F^\prime(H(\ell^\prime))(d_{\mathbb{H}(1_\mathsf{A} \otimes M)})$};
 \path[->,font=\scriptsize,>=angle 90]
 (A) edge node[left]{$\iota_\ell$} (B)
-(A) edge node[above]{$F^\prime(H(\ell^\prime)\kappa)(\iota_{\mu+1})$} (A')
+(A) edge node[above]{$F^\prime(H(\ell^\prime)\kappa)(\iota_{\mu \otimes 1})$} (A')
 (A') edge node [right]{$F^\prime(H(\ell^\prime))(\iota_\kappa)$} (B')
@@
 \]
-where $$F^\prime(\ell)(!_{1_\mathrm{A^\prime}} + E(d))=F^\prime(H(\ell^\prime)\kappa(\mu+1))(!_{1_\mathrm{A^\prime}} + E(d))$$ since the corresponding square involving left unitors for the symmetric lax monoidal pseudofunctor $E \colon \mathbf{Cat} \to \mathbf{Cat}$ commutes.
+where $$F^\prime(\ell)(d_{!_{1_\mathsf{A^\prime}}} \otimes d_{\mathbb{H}(M)})=F^\prime(H(\ell^\prime)\kappa(\mu \otimes 1))(d_{!_{1_\mathsf{A^\prime}}} \otimes d_{\mathbb{H}(M)})$$ since the corresponding square involving left unitors for the finite colimit preserving functor $H \colon \mathsf{A} \to \mathsf{A'}$ commutes.
 The other square involving the right unitors $r$ and $r^\prime$ is similar.
-Note that because $\mu$ and $\mu_{(\_ , \_)}$ are both isomorphisms, the symmetric monoidal double functor $\mathbb{H}$ is strong.
+Note that because the comparison constraints $\mu$ and $\mu_{(\_ , \_)}$ are both isomorphisms, the symmetric monoidal double functor $\mathbb{H}$ is strong.
 
 \begin{thm}
-Given two finitely cocomplete categories $\mathsf{A}$ and $\mathsf{A}'$ and two symmetric lax monoidal pseudofunctors $F \colon \mathsf{A} \to \mathbf{Cat}$ and $F' \colon \mathsf{A}' \to \mathbf{Cat}$, a map $\mathbb{H} \colon F\mathbb{C}\textnormal{sp} \to F'\mathbb{C}\textnormal{sp}$ is given by a pair $(H,E)$ where $H \colon \mathsf{A} \to \mathsf{A}'$ is a finite colimit preserving functor and a symmetric lax monoidal pseudofunctor $E \colon \mathbf{Cat} \to \mathbf{Cat}$ that make the following square commute.
+Given two finitely cocomplete categories $\mathsf{A}$ and $\mathsf{A}'$, two symmetric lax monoidal pseudofunctors $F \colon \mathsf{A} \to \mathbf{Cat}$ and $F' \colon \mathsf{A}' \to \mathbf{Cat}$, a finite colimit preserving functor $H \colon \mathsf{A} \to \mathsf{A}'$, a symmetric lax monoidal pseudofunctor $E \colon \mathbf{Cat} \to \mathbf{Cat}$ and a 2-isomorphism $\theta \colon EF \Rightarrow F^\prime H$ as in the following diagram, the triple $(H,E,\theta)$ induces a double functor $\mathbb{H} \colon F\mathbb{C}\textnormal{sp} \to F'\mathbb{C}\textnormal{sp}$ as defined above.
 \[
@@
 (B) edge node [left]{$\alpha$} (B')
-(C) edge node [left]{$L(g)$} (C');
+(C) edge node [right]{$L(g)$} (C');
 \end{tikzpicture}
@@
 (B) edge node [left]{$R(\alpha)$} (B')
-(C) edge node [left]{$g$} (C');
+(C) edge node [right]{$g$} (C');
 \end{tikzpicture}
@@
 together with a morphism $\iota \colon F(R(\alpha))(x) \to x^\prime$ in $F(R(x^\prime)) \subseteq \mathrm{X}$ which comes from the Grothendieck construction of the pseudofunctor $F \colon \mathsf{A} \to \mathbf{Cat}$.
-First, to see that this functor is essentially surjective, given a horizontal 1-cell in $F\mathbb{C}\textnormal{sp}$:
+That $\mathbb{E}_0$ is a functor is clear.
+For $\mathbb{E}_1$, given two vertically composable 2-morphisms $M$ and $M'$ in $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$,
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$L(c_1)$};
+\node (B) at (1,0) {$x$};
+\node (C) at (2,0) {$L(c_2)$};
+\node (A') at (0,-1) {$L(c_1^\prime)$};
+\node (B') at (1,-1) {$x^\prime$};
+\node (C') at (2,-1) {$L(c_2^\prime)$};
+\node (A'') at (0,-2) {$L(c_1^\prime)$};
+\node (B'') at (1,-2) {$x'$};
+\node (C'') at (2,-2) {$L(c_2')$};
+\node (A''') at (0,-3) {$L(c_1'')$};
+\node (B''') at (1,-3) {$x''$};
+\node (C''') at (2,-3) {$L(c_2'')$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i$} (B)
+(C) edge node[above]{$o$} (B)
+(A') edge node[above]{$i^\prime$} (B')
+(C') edge node[above]{$o^\prime$} (B')
+(A) edge node [left]{$L(f)$} (A')
+(B) edge node [left]{$\alpha$} (B')
+(C) edge node [right]{$L(g)$} (C')
+(A'') edge node[above]{$i'$} (B'')
+(C'') edge node[above]{$o'$} (B'')
+(A''') edge node[above]{$i''$} (B''')
+(C''') edge node[above]{$o''$} (B''')
+(A'') edge node [left]{$L(f')$} (A''')
+(B'') edge node [left]{$\alpha'$} (B''')
+(C'') edge node [right]{$L(g')$} (C''');
+\end{tikzpicture}
+\]
+their vertical composite $M'M$ is given by:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$L(c_1)$};
+\node (B) at (1,0) {$x$};
+\node (C) at (2,0) {$L(c_2)$};
+\node (A') at (0,-1) {$L(c_1'')$};
+\node (B') at (1,-1) {$x''$};
+\node (C') at (2,-1) {$L(c_2'')$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i$} (B)
+(C) edge node[above]{$o$} (B)
+(A') edge node[above]{$i''$} (B')
+(C') edge node[above]{$o''$} (B')
+(A) edge node [left]{$L(f'f)$} (A')
+(B) edge node [left]{$\alpha' \alpha$} (B')
+(C) edge node [right]{$L(g' g)$} (C');
+\end{tikzpicture}
+\]
+and the image of this 2-morphism $\mathbb{E}_1(M'M)$ is given by:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$c_1$};
+\node (B) at (1.5,0) {$R(x)$};
+\node (C) at (3,0) {$c_2$};
+\node (A') at (0,-1) {$c_1''$};
+\node (B') at (1.5,-1) {$R(x'')$};
+\node (C') at (3,-1) {$c_2''$};
+\node (D) at (4,0) {$x \in F(R(x))$};
+\node (D') at (4,-1) {$x'' \in F(R(x''))$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$R(i) \eta_{c_1}$} (B)
+(C) edge node[above]{$R(o) \eta_{c_2}$} (B)
+(A') edge node[above]{$R(i'') \eta_{c_1''}$} (B')
+(C') edge node[above]{$R(o'') \eta_{c_2''}$} (B')
+(A) edge node [left]{$f'f$} (A')
+(B) edge node [left]{$R(\alpha' \alpha)$} (B')
+(C) edge node [right]{$g'g$} (C');
+\end{tikzpicture}
+\]
+together with a morphism $\iota_{M' M} \colon F(R(\alpha' \alpha))(x) \to x''$ in $F(R(x''))$. On the other hand, the individual images $\mathbb{E}_1(M)$ and $\mathbb{E}_1(M')$ are given by:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$c_1$};
+\node (B) at (1.5,0) {$R(x)$};
+\node (C) at (3,0) {$c_2$};
+\node (A') at (0,-1) {$c_1'$};
+\node (B') at (1.5,-1) {$R(x')$};
+\node (C') at (3,-1) {$c_2'$};
+\node (D) at (4,0) {$x \in F(R(x))$};
+\node (D') at (4,-1) {$x' \in F(R(x'))$};
+\node (A'') at (0,-2) {$c_1'$};
+\node (B'') at (1.5,-2) {$R(x')$};
+\node (C'') at (3,-2) {$c_2'$};
+\node (A''') at (0,-3) {$c_1''$};
+\node (B''') at (1.5,-3) {$R(x'')$};
+\node (C''') at (3,-3) {$c_2''$};
+\node (D'') at (4,-2) {$x' \in F(R(x'))$};
+\node (D''') at (4,-3) {$x'' \in F(R(x''))$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$R(i) \eta_{c_1}$} (B)
+(C) edge node[above]{$R(o) \eta_{c_2}$} (B)
+(A') edge node[above]{$R(i') \eta_{c_1'}$} (B')
+(C') edge node[above]{$R(o') \eta_{c_2'}$} (B')
+(A) edge node [left]{$f$} (A')
+(B) edge node [left]{$R(\alpha)$} (B')
+(C) edge node [right]{$g$} (C')
+(A'') edge node[above]{$R(i') \eta_{c_1'}$} (B'')
+(C'') edge node[above]{$R(o') \eta_{c_2'}$} (B'')
+(A''') edge node[above]{$R(i'') \eta_{c_1''}$} (B''')
+(C''') edge node[above]{$R(o'') \eta_{c_2''}$} (B''')
+(A'') edge node [left]{$f'$} (A''')
+(B'') edge node [left]{$R(\alpha')$} (B''')
+(C'') edge node [right]{$g'$} (C''');
+\end{tikzpicture}
+\]
+together with morphisms $\iota_M \colon F(R(\alpha))(x) \to x'$ in $F(R(x'))$ and $\iota_{M'} \colon F(R(\alpha')(x') \to x''$ in $F(R(x''))$, respectively.
+The vertical composite $\mathbb{E}_1(M')\mathbb{E}_1(M)$ of the above two 2-morphisms is given by $\mathbb{E}_1(M'M)$ as $R$ is a functor and $\iota_{M'M}=\iota_{M'} \iota_M$.
+The functors $\mathbb{E}_0$ and $\mathbb{E}_1$ satisfy the equations $\mathbb{E}_0 S = S \mathbb{E}_1$ and $\mathbb{E}_0 T = T \mathbb{E}_1$.
+
+To see that this functor is essentially surjective, given a horizontal 1-cell in $F\mathbb{C}\textnormal{sp}$:
 \[
@@
 (B) edge node [left]{${(R(e) \eta_c)}^{-1}$} (B')
-(C) edge node [left]{$1$} (C');
+(C) edge node [right]{$1$} (C');
 \end{tikzpicture}
@@
 where $e \colon L(c) \to x$ is given by the map from the trivial decoration on $c$ to $x \in F(c)$.
-The object and arrow components $\mathbb{E}_0$ and $\mathbb{E}_1$ satisfy the equations $S \mathbb{E}_1 = \mathbb{E}_0 S$ and $T \mathbb{E}_1 = \mathbb{E}_0 T$.
-
-To show that the double functor $\mathbb{E}$ is fully faithful, we need to show that the map  $$\mathbb{E}_1 \colon _f { _L \mathbb{C}\textnormal{sp}(\mathsf{X})}_g(M,N) \to _{\mathbb{E}(f)} {F\mathbb{C}\textnormal{sp}}_{\mathbb{E}(g)}(\mathbb{E}(M),\mathbb{E}(N))$$ is bijective for arbitrary vertical 1-morphisms $f$ and $g$ and horizontal 1-cells $M$ and $N$ of $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$.
-Consider a 2-morphism in $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$:
+%The object and arrow components $\mathbb{E}_0$ and $\mathbb{E}_1$ satisfy the equations $S \mathbb{E}_1 = \mathbb{E}_0 S$ and $T \mathbb{E}_1 = \mathbb{E}_0 T$.
+
+To show that the double functor $\mathbb{E}$ is fully faithful, we need to show that the map  $$\mathbb{E}_1 \colon _f { _L \mathbb{C}\textnormal{sp}(\mathsf{X})}_g(M,N) \to {_{\mathbb{E}(f)} {F\mathbb{C}\textnormal{sp}}_{\mathbb{E}(g)}}(\mathbb{E}(M),\mathbb{E}(N))$$ is bijective for arbitrary vertical 1-morphisms $f$ and $g$ and horizontal 1-cells $M$ and $N$ of $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$.
+Consider a 2-morphism in $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$ with horizontal source and target $M$ and $N$, respectively and vertical source and target $f$ and $g$, respectively:
 \[
@@
 \node (C) at (3,0) {$c_3$};
-\node (G) at (1.5,-0.5) {$\hat{x} \in F(R(x)+_{c_2}R(x^\prime))$};
+\node (G) at (1.5,-0.5) {$d_{\mathbb{E}(M) \odot \mathbb{E}(N)} = \hat{x} \in F(R(x)+_{c_2}R(x^\prime))$};
 %\node (D) at (3,0.5) {$!_c \in F(c)$};
@@
 \node (C) at (3,0) {$c_3$};
-\node (G) at (1.5,-0.5) {$x+_{L(c_2)} x^\prime \in F(R(x+_{L(c_2)}x^\prime))$};
+\node (G) at (1.5,-0.5) {$d_{\mathbb{E}(M \odot N)} = x+_{L(c_2)} x^\prime \in F(R(x+_{L(c_2)}x^\prime))$};
 %\node (D) at (3,0.5) {$!_c \in F(c)$};
@@
 \node (C') at (3,-1) {$c_3$};
-\node (D) at (5.5 ,0) {$\hat{x} \in F(R(x)+_{c_2}R(x^\prime))$};
-\node (D') at (5.5,-1) {$x+_{L(c_2)}x^\prime \in F(R(x+_{L(c_2)}x^\prime))$};
+\node (D) at (5.5 ,0) {$d_{\mathbb{E}(M) \odot \mathbb{E}(N)} \in F(R(x)+_{c_2}R(x^\prime))$};
+\node (D') at (5.5,-1) {$d_{\mathbb{E}(M \odot N)} \in F(R(x+_{L(c_2)}x^\prime))$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-First, if the right adjoint $R \colon \mathsf{X} \to \mathsf{A}$ is also a left adjoint, then $R$ also preserves all colimits and we have an isomorphism $$\kappa \colon R(x) +_{R(L(c_2))} R(x^\prime) \to R(x+_{L(c_2)}x^\prime).$$ Also, since the left adjoint $L \colon \mathsf{A} \to \mathsf{X}$ is fully faithful, the unit of the adjunction $L \dashv R$ at the object $c_2$ gives an isomorphism $\eta_{c_2} \colon c_2 \to R(L(c_2))$ which results in an isomorphism $$j_{\eta_{c_2}} \colon R(x) +_{c_2} R(x^\prime) \to R(x) +_{R(L(c_2))} R(x^\prime).$$ Composing these two results in an isomorphism $$\sigma \coloneqq \kappa j_{\eta_{c_2}} \colon R(x) +_{c_2} R(x^\prime) \to R(x+_{L(c_2)}x^\prime).$$
+together with a morphism of decorations which is obtained as follows.
+First, as $R \colon \mathsf{X} \to \mathsf{A}$ preserves finite colimits, we have an isomorphism $$\kappa \colon R(x) +_{R(L(c_2))} R(x^\prime) \to R(x+_{L(c_2)}x^\prime).$$ Also, since the left adjoint $L \colon \mathsf{A} \to \mathsf{X}$ is fully faithful, the unit of the adjunction $L \dashv R$ at the object $c_2$ gives an isomorphism $\eta_{c_2} \colon c_2 \to R(L(c_2))$ which results in an isomorphism $$j_{\eta_{c_2}} \colon R(x) +_{c_2} R(x^\prime) \to R(x) +_{R(L(c_2))} R(x^\prime).$$ Composing these two results in an isomorphism $$\sigma \coloneqq \kappa j_{\eta_{c_2}} \colon R(x) +_{c_2} R(x^\prime) \to R(x+_{L(c_2)}x^\prime).$$
 Next, to see that the above diagram commutes, it suffices to show that for the object $c_1 \in \mathrm{A}$, $$R(J)R(\zeta)R(i)\eta_{c_1}(c_1) = R(J \zeta i)\eta_{c_1}(c_1)  \stackrel{!}{=} \sigma j \psi R(i)\eta_{c_1}(c_1) = \kappa j_{\eta_{c_2}} \psi R(i) \eta_{c_1}(c_1).$$ This follows as $R(i) \eta_{c_1} \colon c_1 \to R(x)$ and the following diagram commutes:
@@
 \]
-Lastly, this map of cospans comes with an isomorphism $\iota \colon F(\sigma)(\hat{x}) \to (x+_{L(c_2)}x^\prime)$ in $F(R(x+_{L(c_2)}x^\prime))$.
+Lastly, this map of cospans comes with an isomorphism $$\iota \colon F(\sigma)(d_{\mathbb{E}(M) \odot \mathbb{E}(N)}) \to d_{\mathbb{E}(M \odot N)}$$ in $F(R(x+_{L(c_2)}x^\prime))$.
 This shows that $\mathbb{E}$ is strong, and so $\mathbb{E} \colon _L \mathbb{C}\textnormal{sp}(\mathsf{X}) \xrightarrow{\sim} F\mathbb{C}\textnormal{sp}$ is part of a double equivalence by Theorem \ref{ShulDubEquiv}.
 
-Next, if both double categories $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$ and $F\mathbb{C}\textnormal{sp}$ are symmetric monoidal, as they are if both $\mathsf{A}$ and $\mathsf{X}$ have finite colimits, then this equivalence of double categories $\mathbb{E} \colon _L \mathbb{C}\textnormal{sp}(\mathsf{X}) \to F\mathbb{C}\textnormal{sp}$ will be symmetric monoidal.
+Next, we show that if both double categories $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$ and $F\mathbb{C}\textnormal{sp}$ are symmetric monoidal, as they are if both $\mathsf{A}$ and $\mathsf{X}$ have finite colimits, then this equivalence of double categories $\mathbb{E} \colon _L \mathbb{C}\textnormal{sp}(\mathsf{X}) \to F\mathbb{C}\textnormal{sp}$ will be symmetric monoidal.
 First, note that we have an isomorphism $\epsilon \colon 1_{F\mathbb{C}\textnormal{sp}} \to \mathbb{E}(1_{_L \mathbb{C}\textnormal{sp}(\mathsf{X})})$ and natural isomorphisms $\mu_{c_1,c_2} \colon \mathbb{E}(c_1) \otimes \mathbb{E}(c_2) \to \mathbb{E}(c_1 \otimes c_2)$ for every pair of objects $c_1,c_2 \in {_L \mathbb{C} \textnormal{sp}(\mathsf{X})}$ both of which are given by identities since both double categories $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$ and $F\mathbb{C}\textnormal{sp}$ have $\mathsf{A}$ as their category of objects and $\mathbb{E}_0=\id_{\mathsf{A}}$.
@@
 \node (A) at (0,0) {$c_1+c_1^\prime$};
-\node (B) at (2.25,0) {$R(x)+R(x^\prime)$};
-\node (C) at (4.5,0) {$c_2+c_2^\prime$};
-\node (D) at (2.25,-0.5) {$\hat{x} \in F(R(x)+R(x^\prime))$}; 
+\node (B) at (3.25,0) {$R(x)+R(x^\prime)$};
+\node (C) at (6.5,0) {$c_2+c_2^\prime$};
+\node (D) at (3.25,-0.5) {$d_{\mathbb{E}(M) \otimes \mathbb{E}(N)} \in F(R(x)+R(x^\prime))$}; 
 %\node (D) at (3,0.5) {$!_c \in F(c)$};
@@
 \]
-where $$\hat{x} \colon 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{x \times x^\prime} F(R(x)) \times F(R(x^\prime)) \xrightarrow{\phi_{R(x),R(x^\prime)}} F(R(x)+R(x^\prime)).$$ On the other hand, $M \otimes N$ is given by
+where $$d_{\mathbb{E}(M) \otimes \mathbb{E}(N)} \colon 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{x \times x^\prime} F(R(x)) \times F(R(x^\prime)) \xrightarrow{\phi_{R(x),R(x^\prime)}} F(R(x)+R(x^\prime)).$$ On the other hand, $M \otimes N$ is given by
 \[
@@
 \node (A) at (0,0) {$L(c_1+c_1^\prime)$};
-\node (B) at (1.5,0) {$x+x^\prime$};
-\node (C) at (3,0) {$L(c_2+c_2^\prime)$};
+\node (B) at (2,0) {$x+x^\prime$};
+\node (C) at (4,0) {$L(c_2+c_2^\prime)$};
 %\node (D) at (3,0.5) {$!_c \in F(c)$};
 \path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i+i^\prime$} (B)
-(C) edge node[above]{$o+o^\prime$} (B);
+(A) edge node[above]{$(i+i^\prime)\phi_{c_1,c_1'}^{-1}$} (B)
+(C) edge node[above]{$(o+o^\prime)\phi_{c_2,c_2'}^{-1}$} (B);
 \end{tikzpicture}
@@
 \node (A) at (0,0) {$c_1+c_1^\prime$};
-\node (B) at (2,0) {$R(x+x^\prime)$};
-\node (C) at (4,0) {$c_2+c_2^\prime$};
-\node (D) at (2,-0.5) {$x+x^\prime \in F(R(x+x^\prime)).$};
+\node (B) at (4,0) {$R(x+x^\prime)$};
+\node (C) at (8,0) {$c_2+c_2^\prime$};
+\node (D) at (4,-0.5) {$d_{\mathbb{E}(M \odot N)} \in F(R(x+x^\prime)).$};
 %\node (D) at (3,0.5) {$!_c \in F(c)$};
 \path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$R(i+i^\prime) \eta_{c_1+c_1^\prime}$} (B)
-(C) edge node[above]{$R(o+o^\prime) \eta_{c_2+c_2^\prime}$} (B);
+(A) edge node[above]{$R((i+i^\prime)\phi_{c_1,c_1'}^{-1}) \eta_{c_1+c_1^\prime}$} (B)
+(C) edge node[above]{$R((o+o^\prime)\phi_{c_2,c_2'}^{-1}) \eta_{c_2+c_2^\prime}$} (B);
 \end{tikzpicture}
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (-0.5,0) {$c_1+c_1^\prime$};
-\node (B) at (2,0) {$R(x)+R(x^\prime)$};
+\node (A) at (-2.5,0) {$c_1+c_1^\prime$};
+\node (B) at (1,0) {$R(x)+R(x^\prime)$};
 \node (C) at (4.5,0) {$c_2+c_2^\prime$};
-\node (A') at (-0.5,-1) {$c_1+c_1^\prime$};
-\node (B') at (2,-1) {$R(x+x^\prime)$};
+\node (A') at (-2.5,-1) {$c_1+c_1^\prime$};
+\node (B') at (1,-1) {$R(x+x^\prime)$};
 \node (C') at (4.5,-1) {$c_2+c_2^\prime$};
-\node (D) at (6.25,0) {$\hat{x} \in F(R(x)+R(x^\prime))$};
-\node (D') at (6.25,-1) {$x+x^\prime \in F(R(x+x^\prime))$};
-\node (E) at (2,-1.5) {$\iota_\mu \colon F(\kappa)(\hat{x}) \to x+x^\prime$};
+\node (D) at (6.55,0) {$d_{\mathbb{E}(M) \otimes \mathbb{E}(N)} \in F(R(x)+R(x^\prime))$};
+\node (D') at (6.55,-1) {$d_{\mathbb{E}(M \otimes N)} \in F(R(x+x^\prime))$};
+\node (E) at (2,-1.5) {$\iota_\mu \colon F(\kappa)(d_{\mathbb{E}(M) \odot \mathbb{E}(N)}) \to d_{\mathbb{E}(M \odot N)}$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (C) edge node[above]{$R(o)\eta_{c_2} + R(o^\prime)\eta_{c_2^\prime}$} (B)
-(A') edge node[above]{$R(i+i^\prime)\eta_{c_1+c_1^\prime}$} (B')
-(C') edge node[above]{$R(o+o^\prime)\eta_{c_2+c_2^\prime}$} (B')
+(A') edge node[above]{$R((i+i^\prime)\phi_{c_1,c_1'}^{-1}) \eta_{c_1+c_1^\prime}$} (B')
+(C') edge node[above]{$R((o+o^\prime)\phi_{c_2,c_2'}^{-1}) \eta_{c_2+c_2^\prime}$} (B')
 (A) edge node [left]{$1$} (A')
 (B) edge node [left]{$\kappa$} (B')
-(C) edge node [left]{$1$} (C');
-\end{tikzpicture}
-\]
-where $\kappa$ is an isomorphism as $R \colon \mathsf{X} \to \mathsf{A}$ preserves finite colimits.
+(C) edge node [right]{$1$} (C');
+\end{tikzpicture}
+\]
+where $\kappa$ is the isomorphism which comes from $R \colon \mathsf{X} \to \mathsf{A}$ preserving finite colimits.
 
 The isomorphisms $\delta$ and $\mu$ satisfy the left and right unitality squares, associativity hexagon and braiding square.
-Let $M_1,M_2$ and $M_3$ be horizontal 1-cells in $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$ given by:
+To see this, let $M_1,M_2$ and $M_3$ be horizontal 1-cells in $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$ given by:
 \[
@@
 (B) edge node[right]{$\mu_{1,M_1}$} (D)
-(A) edge node[left]{$\lambda$} (C)
+(A) edge node[left]{$\lambda'$} (C)
 (D) edge node[above]{$\mathbb{E}(\lambda)$} (C);
@@
 \]
-has underlying maps of cospans given by:
+has an underlying diagram of maps of cospans given by:
 \[
@@
 			\node (d) at (7.5,0) {$\mathbb{E}(1_{ _L \mathbb{C}\textnormal{sp}(\mathsf{X})}) \otimes \mathbb{E}(M_1)$};
-			\node (a) at (-4,0) {$1_\mathsf{A}+c_1$};
-			\node (b) at (0.5,0) {$R(L(1_\mathsf{A})) + R(x_1)$};
+			\node (a) at (-6,0) {$1_\mathsf{A}+c_1$};
+			\node (b) at (-0.5,0) {$R(L(1_\mathsf{A})) + R(x_1)$};
 			\node (c) at (5,0) {$1_\mathsf{A}+c_1^\prime$};
 			\node (d2) at (7.5,1) {$1_{F\mathbb{C}\textnormal{sp}} \otimes \mathbb{E}(M_1)$};
-			\node (a2) at (-4,1) {$1_\mathsf{A}+c_1$};
-			\node (b2) at (0.5,1) {$1_\mathsf{A}+R(x_1)$};
+			\node (a2) at (-6,1) {$1_\mathsf{A}+c_1$};
+			\node (b2) at (-0.5,1) {$1_\mathsf{A}+R(x_1)$};
 			\node (c2) at (5,1) {$1_\mathsf{A}+c_1^\prime$};
 			\node (d3) at (7.5,2) {$\mathbb{E}(M_1)$};
-                                \node (a3) at (-4,2) {$c_1$};
-			\node (b3) at (0.5,2) {$R(x_1)$};
+                                \node (a3) at (-6,2) {$c_1$};
+			\node (b3) at (-0.5,2) {$R(x_1)$};
 			\node (c3) at (5,2) {$c_1^\prime$};
 			\node (d4) at (7.5,-1) {$\mathbb{E}(1_{ _L \mathbb{C}\textnormal{sp}(\mathsf{X})} \otimes M_1)$};
-                                \node (a5) at (-4,-1) {$1_\mathsf{A}+c_1^\prime$};
-			\node (b5) at (0.5,-1) {$R(L(1_\mathsf{A})+x_1)$};
+                                \node (a5) at (-6,-1) {$1_\mathsf{A}+c_1^\prime$};
+			\node (b5) at (-0.5,-1) {$R(L(1_\mathsf{A})+x_1)$};
 			\node (c5) at (5,-1) {$1_\mathsf{A}+c_1^\prime$};
 			\node (d5) at (7.5,-2) {$\mathbb{E}(M_1)$};
-                                \node (a6) at (-4,-2) {$c_1$};
-			\node (b6) at (0.5,-2) {$R(x_1)$};
+                                \node (a6) at (-6,-2) {$c_1$};
+			\node (b6) at (-0.5,-2) {$R(x_1)$};
 			\node (c6) at (5,-2) {$c_1^\prime$};
@@
 (b2) edge node[right]{$\iota_2$} (b)
-			(c2) edge node[left]{$1$} (c)
+			(c2) edge node[right]{$1$} (c)
                                 (a3) edge node[above]{$R(i_1)\eta_{c_1}$} (b3)
@@
 (b2) edge node[right]{$\iota_1$} (b3)
-			(c2) edge node[left]{$\lambda_{\mathsf{A}}$} (c3)
+			(c2) edge node[right]{$\lambda_{\mathsf{A}}$} (c3)
                                 (a5) edge node[above]{$(\mu_{L(1_\mathsf{A}),d_1})(\eta_{1_\mathsf{A}}+R(i_1)\eta_{c_1})$} (b5)
@@
 (b) edge node[right]{$\iota_3$} (b5)
-			(c) edge node[left]{$1$} (c5)
+			(c) edge node[right]{$1$} (c5)
                                 (a6) edge node[above]{$R(i_1)\eta_{c_1}$} (b6)
@@
  (b5) edge node[right]{$\iota_4$} (b6)
-			(c5) edge node[left]{$\lambda_{\mathsf{A}}$} (c6);
+			(c5) edge node[right]{$\lambda_{\mathsf{A}}$} (c6);
 		\end{tikzpicture}
@@
 where $x_{!+1}$ is the decoration $x_1$ on the object $R(L(1_\mathsf{A})+x_1) \in \mathsf{A}$.
-The above square commutes because $$F(\lambda_\mathsf{A})(!_{1_\mathsf{A}}+x_1) = F(R(\lambda_\mathsf{X})(\mu_{L(1_\mathsf{A}),x_1})(\eta_{1_\mathsf{A}}+1))(!_{1_\mathsf{A}}+x_1)$$ as the corresponding left unitality square for the symmetric monoidal functor $R \colon (\mathsf{X},1_\mathsf{X},+) \to (\mathsf{A},1_\mathsf{A},+)$ commutes.
+The above square commutes because $$F(\lambda_\mathsf{A})(!_{1_\mathsf{A}}+x_1) = F(R(\lambda_\mathsf{X})(\mu_{L(1_\mathsf{A}),x_1})(\eta_{1_\mathsf{A}}+1))(!_{1_\mathsf{A}}+x_1)$$ as the corresponding left unitality square for the finite colimit preserving functor $R \colon (\mathsf{X},1_\mathsf{X},+) \to (\mathsf{A},1_\mathsf{A},+)$ commutes.
 The right unitality square is similar.
@@
 (A) edge node [left]{$a^\prime$} (A')
-(C) edge node [left]{$\mathbb{E}(a)$} (C');
+(C) edge node [right]{$\mathbb{E}(a)$} (C');
 \end{tikzpicture}
@@
 			\node (a) at (-4.25,0) {$(c_1+c_2)+c_3$};
-			\node (b) at (1.5,0) {$(R(x_1)+R(x_2))+R(x_3)$};
-			\node (c) at (7.25,0) {$(c_1^\prime+c_2^\prime)+c_3^\prime$};
+			\node (b) at (2.5,0) {$(R(x_1)+R(x_2))+R(x_3)$};
+			\node (c) at (9.25,0) {$(c_1^\prime+c_2^\prime)+c_3^\prime$};
 			\node (a2) at (-4.25,1) {$(c_1+c_2)+c_3$};
-			\node (b2) at (1.5,1) {$R(x_1+x_2)+R(x_3)$};
-			\node (c2) at (7.25,1) {$(c_1^\prime+c_2^\prime)+c_3^\prime$};
+			\node (b2) at (2.5,1) {$R(x_1+x_2)+R(x_3)$};
+			\node (c2) at (9.25,1) {$(c_1^\prime+c_2^\prime)+c_3^\prime$};
                                 \node (a3) at (-4.25,2) {$(c_1+c_2)+c_3$};
-			\node (b3) at (1.5,2) {$R((x_1+x_2)+x_3)$};
-			\node (c3) at (7.25,2) {$(c_1^\prime+c_2^\prime)+c_3^\prime$};
+			\node (b3) at (2.5,2) {$R((x_1+x_2)+x_3)$};
+			\node (c3) at (9.25,2) {$(c_1^\prime+c_2^\prime)+c_3^\prime$};
                                 \node (a4) at (-4.25,3) {$c_1+(c_2+c_3)$};
-			\node (b4) at (1.5,3) {$R(x_1+(x_2+x_3))$};
-			\node (c4) at (7.25,3) {$c_1^\prime + (c_2^\prime + c_3^\prime)$};
+			\node (b4) at (2.5,3) {$R(x_1+(x_2+x_3))$};
+			\node (c4) at (9.25,3) {$c_1^\prime + (c_2^\prime + c_3^\prime)$};
                                 \node (a5) at (-4.25,-1) {$c_1+(c_2+c_3)$};
-			\node (b5) at (1.5,-1) {$R(x_1)+(R(x_2)+R(x_3))$};
-			\node (c5) at (7.25,-1) {$c_1^\prime + (c_2^\prime + c_3^\prime)$};
+			\node (b5) at (2.5,-1) {$R(x_1)+(R(x_2)+R(x_3))$};
+			\node (c5) at (9.25,-1) {$c_1^\prime + (c_2^\prime + c_3^\prime)$};
                                 \node (a6) at (-4.25,-2) {$c_1+(c_2+c_3)$};
-			\node (b6) at (1.5,-2) {$R(x_1)+R(x_2+x_3)$};
-			\node (c6) at (7.25,-2) {$c_1^\prime + (c_2^\prime + c_3^\prime)$};
+			\node (b6) at (2.5,-2) {$R(x_1)+R(x_2+x_3)$};
+			\node (c6) at (9.25,-2) {$c_1^\prime + (c_2^\prime + c_3^\prime)$};
                                 \node (a7) at (-4.25,-3) {$c_1+(c_2+c_3)$};
-			\node (b7) at (1.5,-3) {$R(x_1+(x_2+x_3))$};
-			\node (c7) at (7.25,-3) {$c_1^\prime + (c_2^\prime + c_3^\prime)$};
+			\node (b7) at (2.5,-3) {$R(x_1+(x_2+x_3))$};
+			\node (c7) at (9.25,-3) {$c_1^\prime + (c_2^\prime + c_3^\prime)$};
 			\path[->,font=\scriptsize,>=angle 90]
@@
 (b) edge node[right]{$\iota_1$} (b2)
-			(c) edge node[left]{$1$} (c2)
+			(c) edge node[right]{$1$} (c2)
                                 (a3) edge node[above]{$R((i_1+i_2)+i_3)\eta_{(c_1+c_2)+c_3}$} (b3)
@@
 (b2) edge node[right]{$\iota_2$} (b3)
-			(c2) edge node[left]{$1$} (c3)
+			(c2) edge node[right]{$1$} (c3)
                                 (a4) edge node[above]{$R(i_1+(i_2+i_3))\eta_{c_1+(c_2+c_3)}$} (b4)
@@
 (b3) edge node[right]{$\iota_3$} (b4)
-			(c3) edge node[left]{$a_\mathsf{A}$} (c4)
+			(c3) edge node[right]{$a_\mathsf{A}$} (c4)
                                 (a5) edge node[above]{$R(i_1)\eta_{c_1}+(R(i_2)\eta_{c_2}+R(i_3)\eta_{c_3})$} (b5)
@@
 (b) edge node[right]{$\iota_4$} (b5)
-			(c) edge node[left]{$a_\mathsf{A}$} (c5)
+			(c) edge node[right]{$a_\mathsf{A}$} (c5)
                                 (a6) edge node[above]{$R(i_1)\eta_{c_1}+R(i_2+i_3)\eta_{c_2+c_3}$} (b6)
@@
  (b5) edge node[right]{$\iota_5$} (b6)
-			(c5) edge node[left]{$1$} (c6)
+			(c5) edge node[right]{$1$} (c6)
                                 (a7) edge node[above]{$R(i_1+(i_2+i_3))\eta_{c_1+(c_2+c_3)}$} (b7)
@@
 (b6) edge node[right]{$\iota_6$} (b7)
-			(c6) edge node[left]{$1$} (c7);
-		\end{tikzpicture}
-	\]
-with the corresponding maps of decorations amounting to the following commutative diagram in $F(R(x_1+(x_2+x_3)))$:
+			(c6) edge node[right]{$1$} (c7);
+		\end{tikzpicture}
+	\]
+Here we have omitted the natural isomorphisms $\phi_{c_i,c_j} \colon L(c_i) + L(c_j) \to L(c_i + c_j)$ on the inward pointing morphisms which make up the legs of each cospan due to limited space.
+The corresponding maps of decorations amount to the following commutative diagram in $F(R(x_1+(x_2+x_3)))$:
 \[
@@
 \]
-The above square commutes because $$F((\kappa)(1+\kappa)(a_\mathsf{A}))((x_1+x_2)+x_3) = F((R(a_\mathsf{X}))(\kappa)(\kappa+1))((x_1+x_2)+x_3)$$ as the corresponding associator hexagon for the symmetric monoidal functor $R \colon (\mathsf{X},1_\mathsf{X},+) \to (\mathsf{A},1_\mathsf{A},+)$ commutes.
+The above square commutes because $$F((\kappa)(1+\kappa)(a_\mathsf{A}))((x_1+x_2)+x_3) = F((R(a_\mathsf{X}))(\kappa)(\kappa+1))((x_1+x_2)+x_3)$$ as the corresponding associator hexagon for the finite colimit preserving functor $R \colon (\mathsf{X},1_\mathsf{X},+) \to (\mathsf{A},1_\mathsf{A},+)$ commutes.
 Lastly, the braiding square:
@@
 (b) edge node[right]{$\iota_1$} (b2)
-			(c) edge node[left]{$\beta_\mathsf{A}$} (c2)
+			(c) edge node[right]{$\beta_\mathsf{A}$} (c2)
                                 (a3) edge node[above]{$R(i_2+i_1)\eta_{c_2+c_1}$} (b3)
@@
 (b2) edge node[right]{$\iota_2$} (b3)
-			(c2) edge node[left]{$1$} (c3)
+			(c2) edge node[right]{$1$} (c3)
                                 (a5) edge node[above]{$R(i_1+i_2)\eta_{c_1+c_2}$} (b5)
@@
 (b) edge node[right]{$\iota_3$} (b5)
-			(c) edge node[left]{$1$} (c5)
+			(c) edge node[right]{$1$} (c5)
                                 (a6) edge node[above]{$R(i_2+i_1)\eta_{c_2+c_1}$} (b6)
@@
  (b5) edge node[right]{$\iota_4$} (b6)
-			(c5) edge node[left]{$\beta_\mathsf{A}$} (c6);
-		\end{tikzpicture}
-	\]
-with the corresponding maps of decorations amounting to the following commutative diagram in $F(R(x_2+x_1))$:
+			(c5) edge node[right]{$\beta_\mathsf{A}$} (c6);
+		\end{tikzpicture}
+	\]
+Again, we have omitted the natural isomorphisms $\phi_{c_i,c_j}$ on the inward pointing morphisms on each cospan leg due to space restrictions.
+The corresponding maps of decorations amounting to the following commutative diagram in $F(R(x_2+x_1))$:
 \[
@@
 \]
-The above square commutes because $$F((\kappa)(\beta_\mathsf{A}))(x_1+x_2) = F((R(\beta_\mathsf{X}))(\kappa))(x_1+x_2)$$ as the corresponding braiding square for the symmetric monoidal functor $R \colon (\mathsf{X},1_\mathsf{X},+) \to (\mathsf{A},1_\mathsf{A},+)$ commutes.
+The above square commutes because $$F((\kappa)(\beta_\mathsf{A}))(x_1+x_2) = F((R(\beta_\mathsf{X}))(\kappa))(x_1+x_2)$$ as the corresponding braiding square for the finite colimit preserving functor $R \colon (\mathsf{X},1_\mathsf{X},+) \to (\mathsf{A},1_\mathsf{A},+)$ commutes.
 Thus the double functor $\mathbb{E} \colon _L\mathbb{C}\textnormal{sp}(\mathsf{X}) \to F\mathbb{C}\textnormal{sp}$ is symmetric monoidal.
@@
 
-\textbf{Is this biequivalnce symmetric monoidal? Probably}
+\textbf{Is this biequivalnce symmetric monoidal? Mike says yes, but it follows from a result that he has yet to officially publish. It's a result of a paper he's currently working on with someone.}
 \newline
@@
 (B) edge node [left]{$h$} (B')
-(C) edge node [left]{$g$} (C');
+(C) edge node [right]{$g$} (C');
 \end{tikzpicture}
@@
 $$\iota \colon F(h)(x) \to x^\prime$$
-the image in $\mathbb{G}(f,h,g,\iota)$ in $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$ is given by the 2-morphism:
+the image $\mathbb{G}(f,h,g,\iota)$ in $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$ is given by the 2-morphism:
 \[
@@
 Next, we exhibit natural isomorphisms $\eta \colon \id_{ _L \mathbb{C}\textnormal{sp}(\mathsf{X})} \cong \mathbb{G} \mathbb{E}$ and $\epsilon \colon \mathbb{E} \mathbb{G} \cong \id_{F\mathbb{C}\textnormal{sp}}$.
-Specifically, these are double natural isomorphisms given by double transformations \cite{Shul2} $\eta$ and $\epsilon$ whose object and arrow components are isomorphisms.
+Specifically, these are double natural isomorphisms given by double transformations \cite{Shul2} $\eta$ and $\epsilon$ whose object and arrow components are natural isomorphisms.
 
@@
 (B) edge node [left]{$1$} (B')
-(C) edge node [left]{$1$} (C');
+(C) edge node [right]{$1$} (C');
 \end{tikzpicture}
@@
 (A) edge node [left]{$1$} (A')
-(B) edge node [left]{$e$} (B')
-(C) edge node [left]{$1$} (C');
-\end{tikzpicture}
-\]
-$$\iota \colon F(e)(x) \to x$$
+(B) edge node [left]{$\hat{e}$} (B')
+(C) edge node [right]{$1$} (C');
+\end{tikzpicture}
+\]
+$$\iota \colon F(\hat{e})(x) \to x$$
 where 
@@
 (C) edge node[above]{$R(!_c)$} (D)
-(D) edge node[above]{$e$} (E)
+(D) edge node[above]{$\hat{e}$} (E)
 (A) edge[bend right] node [above]{$I$} (E);

### 2019-05-28 EquivCompFrameworks_20180911kc.tex
tiny notation

@@
 \begin{proof}
-Recall that the double category of decorated cospans $\dcsp{F}$ has objects and vertical 1-morphisms those of $\A$, horizontal 1-cells $a\tickar b$ are cospans $\cspn{a}{c}{b}{}{}$ in $\A$ along with $d\in F(c)$, and 2-morphisms are cospan maps $k\colon c\to c'$ together with a morphism $\iota\colon(Fk)(d)\to d'$, see \cref{eq:FCsp2morph}.
+Recall that the double category of decorated cospans $\dcsp{F}$ has objects and vertical 1-morphisms those of $\A$, horizontal 1-cells $a\tickar b$ are cospans $\cspn{a}{c}{b}{}{}$ in $\A$ along with $x\in F(c)$, and 2-morphisms are cospan maps $k\colon c\to c'$ together with a morphism $(Fk)(x)\to x'$, see \cref{eq:FCsp2morph}.
 

### 2019-05-28 EquivCompFrameworks_20180911kc.tex
another tiny

@@
  \begin{tikzcd}[sep=1.5in,ampersand replacement=\&]
- (a,\bot_a)\ar[r,"{\begin{cases}i\colon a\to c &\textrm{in }\A \\!\colon F(i)(\bot_a)\to x &\textrm{in }F(c)\end{cases}}"]\ar[d,"{\begin{cases}f\colon a\to a' &\textrm{in }\A \\\chi_a\colon F(f)(\bot_a)\cong \bot_{a'} &\textrm{in }F(a')\end{cases}}"description] \& (c,x) \ar[d,"{\begin{cases}k\colon c\to c' &\textrm{in }\A \\h\colon F(k)(x)\to x' &\textrm{in }F(c')\end{cases}}"description] \& (b,\bot_b)\ar[l,"{\begin{cases}o\colon b\to c &\textrm{in }\A \\!\colon F(o)(\bot_b)\to x &\textrm{in }F(c)\end{cases}}"']\ar[d,"{\begin{cases}g\colon b\to b' &\textrm{in }\A \\\chi_b\colon F(g)(\bot_b)\cong \bot_{b'} &\textrm{in }F(b')\end{cases}}"description] \\
+ (a,\bot_a)\ar[r,"{\begin{cases}i\colon a\to c &\textrm{in }\A \\!\colon F(i)(\bot_a)\to x &\textrm{in }F(c)\end{cases}}"]\ar[d,"{\begin{cases}f\colon a\to a' &\textrm{in }\A \\\chi_a\colon F(f)(\bot_a)\cong \bot_{a'} &\textrm{in }F(a')\end{cases}}"description] \& (c,x) \ar[d,"{\begin{cases}k\colon c\to c' &\textrm{in }\A \\ \iota\colon F(k)(x)\to x' &\textrm{in }F(c')\end{cases}}"description] \& (b,\bot_b)\ar[l,"{\begin{cases}o\colon b\to c &\textrm{in }\A \\!\colon F(o)(\bot_b)\to x &\textrm{in }F(c)\end{cases}}"']\ar[d,"{\begin{cases}g\colon b\to b' &\textrm{in }\A \\\chi_b\colon F(g)(\bot_b)\cong \bot_{b'} &\textrm{in }F(b')\end{cases}}"description] \\
  (a',\bot_{a'})\ar[r,"{\begin{cases}i'\colon a'\to c' &\textrm{in }\A \\!\colon F(i')(\bot_{a'})\to x' &\textrm{in }F(c')\end{cases}}"'] \& (c',x') \& (b',\bot_{b'})\ar[l,"{\begin{cases}o'\colon b'\to c' &\textrm{in }\A \\!\colon F(o')(\bot_{b'})\to x' &\textrm{in }F(c')\end{cases}}"]
@@
 where the outside vertical legs come from the definition of $L_F$ on arrows, \cref{eq:Lonarrows}. 
-{\chris The above diagram might be a bit overwhelming, but all info is there. Choose which parts are required for a smooth proof!}
+{\chris The above diagram might be a bit overwhelming, but all info is there.
+Choose which parts are required for a smooth proof!} {\chris Also, iota and letter i look alarmingly similar.
+Should we change iota to some other distinctive greek letter?}
 The square commutativities translate to $k\circ i=i'\circ f$ and $k\circ o=o'\circ g$ in $\A$, and also by composition in the Grothendieck category, to
 \begin{gather*}
- F(k\circ i)(\bot_a)\cong Fk(Fi(\bot_a))\xrightarrow{Fk(!)}Fk(x)\xrightarrow{h}x'= \\
+ F(k\circ i)(\bot_a)\cong Fk(Fi(\bot_a))\xrightarrow{Fk(!)}Fk(x)\xrightarrow{\iota}x'= \\
  F(i'\circ f)(\bot_a)\cong Fi'(Ff(\bot_a))\xrightarrow{Fi'(\chi_a)}Fi'(\bot_{a'})\xrightarrow{!}x'

### 2019-05-30 EquivCompFrameworks_20180911kc.tex
added some definitions to the appendix and commented some stuff out

@@
 
-\begin{comment}
+%\begin{comment}
 \section{Introduction}
@@
 Daniel Cicala, person that Christina emailed about lax slice category? {\chris did you use it after all?} No, I did not.
-\end{comment}
+%\end{comment}
 
@@
 \end{thm}
+\textbf{Kenny: We should try to make this theorem shorter.}
 \begin{proof}
@@
 
-\begin{comment}
+%\begin{comment}
 \section{Maps of decorated cospan double categories}\label{MapsDecCospansDoubleCat}
@@
 \]
+
+\begin{comment}
 Recall that we can think of the object $d \in F(c)$ as a morphism $d \colon 1 \to F(c)$ and the functor $\iota \colon F(h)(d) \to d^\prime$ of $F(c^\prime)$ as a natural transformation  in $\mathbf{Cat}$:
@@
 
+\end{comment}
+
 \begin{thm}
-Given two finitely cocomplete categories $\mathsf{A}$ and $\mathsf{A}'$, two symmetric lax monoidal pseudofunctors $F \colon \mathsf{A} \to \mathbf{Cat}$ and $F' \colon \mathsf{A}' \to \mathbf{Cat}$, a finite colimit preserving functor $H \colon \mathsf{A} \to \mathsf{A}'$, a symmetric lax monoidal pseudofunctor $E \colon \mathbf{Cat} \to \mathbf{Cat}$ and a 2-isomorphism $\theta \colon EF \Rightarrow F^\prime H$ as in the following diagram, the triple $(H,E,\theta)$ induces a double functor $\mathbb{H} \colon F\mathbb{C}\textnormal{sp} \to F'\mathbb{C}\textnormal{sp}$ as defined above.
+Given two finitely cocomplete categories $\mathsf{A}$ and $\mathsf{A}'$, two symmetric lax monoidal pseudofunctors $F \colon \mathsf{A} \to \mathbf{Cat}$ and $F' \colon \mathsf{A}' \to \mathbf{Cat}$, a finite colimit preserving functor $H \colon \mathsf{A} \to \mathsf{A}'$, a symmetric lax monoidal pseudofunctor $E \colon \mathbf{Cat} \to \mathbf{Cat}$ and a 2-isomorphism $\theta \colon EF \Rightarrow F^\prime H$ as in the following diagram, the triple $(H,E,\theta)$ induces a symmetric monoidal (strong) double functor $\mathbb{H} \colon F\mathbb{C}\textnormal{sp} \to F'\mathbb{C}\textnormal{sp}$ as defined above.
 \[
@@
 On the other hand, applying the functor $E$ to each decoration results in $$1 \to E(F(c_1)) \times E(F(c_2)) \xrightarrow{} E(F(c_1) \times F(c_2)) \xrightarrow{} E(F(c_1+c_2)) \xrightarrow E(F(c_1+_b c_2)) \xrightarrow{} F^\prime(H(c_1 +_b c_2))$$
-\end{comment}
+%end{comment}
 
@@
 The isomorphisms $\delta$ and $\mu$ satisfy the left and right unitality squares, associativity hexagon and braiding square.
-To see this, let $M_1,M_2$ and $M_3$ be horizontal 1-cells in $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$ given by:
+\textbf{Kenny: I think this might be a good place to cut the monoidal stuff.} To see this, let $M_1,M_2$ and $M_3$ be horizontal 1-cells in $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$ given by:
 \[
@@
 
+\begin{comment}
+
 We can also define the part of the double equivalence $\mathbb{G} \colon F\mathbb{C}\textnormal{sp} \to {_L \mathbb{C} \textnormal{sp}(\mathsf{X})}$ which goes in the other direction: again, the object component of this double functor will be $\mathbb{G}_0 = \id_{\mathsf{A}}$.
@@
 
-\begin{comment}
+\end{comment}
+
+%\begin{comment}
 \section{Applications}\label{Applications}
@@
 Thus we have a symmetric monoidal double category $\mathbb{O}\mathbf{pen}(\mathrm{Petri})$ of open Petri nets obtained from structured cospans and a symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$ of open Petri nets obtain from decorated cospans, and of course, we have an equivalence $\mathbb{O}\mathbf{pen}(\mathrm{Petri}) \sim F\mathbb{C}\textnormal{sp}$ of symmetric monoidal double categories by Theorem \ref{Equiv}.
-\end{comment}
-
-\begin{comment}
+%\end{comment}
+
+%\begin{comment}
 \section{Appendix}
@@
 \end{defn}
-\end{comment}
+
+\begin{defn}
+Let $\mathbb{A}$ and $\mathbb{B}$ be pseudo double categories.
+A \define{lax double functor} is a functor $\mathbb{F} \colon\mathbb{A}\to \mathbb{B}$ that takes items of $\mathbb{A}$ to items of $\mathbb{B}$ of the corresponding type, respecting vertical composition in the strict sense and the horizontal composition up to an assigned comparison $\phi$.
+This means that we have functors $\mathbb{F}_0 \colon \mathbb{A}_0 \to \mathbb{B}_0$ and $\mathbb{F}_1 \colon \mathbb{A}_1 \to \mathbb{B}_1$ such that the following equations are satisfied: $$S \circ \mathbb{F}_1 = \mathbb{F}_0 \circ S$$ $$T \circ \mathbb{F}_1 = \mathbb{F}_0 \circ T$$ Sometimes for brevity, we will omit the subscripts and simply say $\mathbb{F}$.
+As to whether we mean $\mathbb{F}_0$ or $\mathbb{F}_1$ will be clear from context.
+
+Also, every object $a$ is equipped with a special globular 2-morphism $\phi_{a} \colon 1_{\mathbb{F}(a)} \to \mathbb{F}(1_{a})$ (the identity comparison), and every horizontal composition $N_{1} \odot N_{2}$ is equipped with a special globular 2-morphism $\phi(N_{1},N_{2}) \colon \mathbb{F}(N_{1}) \odot \mathbb{F}(N_{2}) \to \mathbb{F}(N_{1} \odot N_{2})$ (the composition comparison), in a coherent way.
+This means that the following diagrams commute.
+
+\begin{enumerate}
+
+\item For a horizontal composite, $\beta \odot \alpha$,
+
+\begin{equation}\label{eq:square}
+  \xymatrix@-.5pc{
+    \mathbb{F}(A) \ar[r]|{|}^{\mathbb{F}(N_{2})}  \ar[d] \ar@{}[dr]|{\mathbb{F}(\alpha)}&
+    \mathbb{F}(B) \ar[d] \ar[r]|{|}^{\mathbb{F}(N_{1})} \ar@{}[dr]|{\mathbb{F}(\beta)}&
+    \mathbb{F}(C) \ar[d] &
+     &
+    \mathbb{F}(A) \ar[r]|{|}^{\mathbb{F}(N_{2})} \ar@{}[drr]|{\phi(N_{1},N_{2})} \ar[d]_{1} &
+    \mathbb{F}(B) \ar[r]|{|}^{\mathbb{F}(N_{1})} &
+    \mathbb{F}(C) \ar[d]^{1} \\
+    \mathbb{F}(A') \ar[r]|{|}_{\mathbb{F}(N_{4})} \ar@{}[drr]|{\phi(N_{3},N_{4})} \ar[d]_{1}&
+    \mathbb{F}(B') \ar[r]|{|}_{\mathbb{F}(N_{3})} &
+    \mathbb{F}(C') \ar[d]^{1}&
+    = &
+    \mathbb{F}(A) \ar[rr]|{|}^{\mathbb{F}(N_{1} \odot N_{2})} \ar[d] \ar@{}[drr]|{\mathbb{F}(\beta \odot \alpha)}&
+     &
+    \mathbb{F}(C) \ar[d] \\
+    \mathbb{F}(A') \ar[rr]|{|}_{\mathbb{F}(N_{3} \odot N_{4})} & 
+     & 
+    \mathbb{F}(C') &
+     &
+    \mathbb{F}(A') \ar[rr]|{|}_{\mathbb{F}(N_{3} \odot N_{4})} &
+     &
+    \mathbb{F}(C') \\
+  }.
+\end{equation}
+
+\item For a horizontal 1-cell $N \colon A \to B$, the following diagrams are commutative (under horizontal composition).
+
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (1,1) {$\mathbb{F}(N) \odot 1_{\mathbb{F}(A)}$};
+\node (C) at (3,1) {$\mathbb{F}(N)$};
+\node (A') at (1,-1) {$\mathbb{F}(N) \odot \mathbb{F}(1_{A})$};
+\node (C') at (3,-1) {$\mathbb{F}(N \odot 1_{A})$};
+\node (B) at (5,1) {$1_{\mathbb{F}(B)} \odot \mathbb{F}(N)$};
+\node (B') at (5,-1) {$\mathbb{F}(1_{B}) \odot \mathbb{F}(N)$};
+\node (D) at (7,1) {$\mathbb{F}(N)$};
+\node (D') at (7,-1) {$\mathbb{F}(1_{B} \odot N)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[left]{$1 \odot \phi_{A}$} (A')
+(C') edge node[right]{$\mathbb{F} \rho$} (C)
+(A) edge node[above]{$\rho_{\mathbb{F}(N)}$} (C)
+(A') edge node[above]{$\phi(N,1_{A})$} (C')
+(B) edge node[left]{$\phi_{B} \odot 1$} (B')
+(B') edge node[above]{$\phi(1_{B},N)$} (D')
+(B) edge node[above]{$\lambda_{\mathbb{F}(N)}$} (D)
+(D') edge node[right]{$F \lambda$} (D);
+\end{tikzpicture}
+\]
+
+\item For consecutive horizontal 1-cells $N_{1},N_{2}$ and $N_{3}$, the following diagram is commutative.
+
+ \[\xymatrix{
+    (\mathbb{F}(N_{1}) \odot \mathbb{F}(N_{2})) \odot \mathbb{F}(N_{3}) \ar[r]^{a'}\ar[d]_{\phi(N_{1},N_{2}) \odot 1}
+    & \mathbb{F}(N_{1}) \odot (\mathbb{F}(N_{2}) \odot \mathbb{F}(N_{3})) \ar[d]^{1 \odot \phi(N_{2},N_{3})}\\
+    \mathbb{F}(N_{1} \odot N_{2}) \odot \mathbb{F}(N_{3}) \ar[d]_{\phi(N_{1} \odot N_{2},N_{3})} &
+    \mathbb{F}(N_{1}) \odot \mathbb{F}(N_{2} \odot N_{3}) \ar[d]^{\phi(N_{1},N_{2} \odot N_{3})}\\
+    \mathbb{F}((N_{1} \odot N_{2}) \odot N_{3})\ar[r]^{\mathbb{F}a} &
+    \mathbb{F}(N_{1} \odot (N_{2} \odot N_{3}))}\]
+\end{enumerate}
+We say the double functor $\mathbb{F}$ is \define{strict} if the comparison constraints $\phi_a$ and $\phi_{N_1,N_2}$ are identities, \define{pseudo} if the comparison constraints are isomorphisms, and \define{oplax} if the comparison constraints go in the opposite direction.
+\end{defn}
+
+\begin{defn}
+\label{defn:monoidal_double_functor}
+A \define{(strong) monoidal lax double functor} $\mathbb{F} \colon \mathbb{C} \to \mathbb{D}$ between monoidal double categories $\mathbb{C}$ and $\mathbb{D}$ is a lax double functor $\mathbb{F} \maps \mathbb{C} \to \mathbb{D}$ such that
+	\begin{itemize}
+		\item $\mathbb{F}_0$ and $\mathbb{F}_1$ are monoidal functors, meaning that there exists
+
+\begin{enumerate}
+\item{an isomorphism $\epsilon \colon 1_{\lD} \to \mathbb{F}(1_{\lC})$}
+\item{a natural isomorphism $\mu_{A,B} \colon \mathbb{F}(A) \otimes \mathbb{F}(B) \to \mathbb{F}(A \otimes B)$ for all objects $A$ and $B$ of $\lC$}
+\item{an isomorphism $\delta \colon U_{1_{\lD}} \to \mathbb{F}(U_{1_{\lC}})$}
+\item{a natural isomorphism $\nu_{M,N} \colon \mathbb{F}(M) \otimes \mathbb{F}(N) \to \mathbb{F}(M \otimes N)$ for all horizontal 1-cells $N$ and $M$ of $\lC$}
+\end{enumerate}
+such that the following diagrams commute: for objects $A,B$ and $C$ of $\lC$,
+ \[\xymatrix{
+    (\mathbb{F}(A) \otimes \mathbb{F}(B)) \otimes \mathbb{F}(C) \ar[r]^{\alpha^\prime}\ar[d]_{\mu_{A,B} \otimes 1}
+    & \mathbb{F}(A) \otimes (\mathbb{F}(B) \otimes \mathbb{F}(C)) \ar[d]^{1 \otimes \mu_{B,C}}\\
+    \mathbb{F}(A \otimes B) \otimes \mathbb{F}(C) \ar[d]_{\mu_{A \otimes B,C}} &
+    \mathbb{F}(A) \otimes \mathbb{F}(B \otimes C) \ar[d]^{\mu_{A,B \otimes C}}\\
+    \mathbb{F}((A \otimes B) \otimes C)\ar[r]^{\mathbb{F}\alpha} &
+    \mathbb{F}(A \otimes (B \otimes C))}\]
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (1,1) {$\mathbb{F}(A) \otimes 1_{\lD}$};
+\node (C) at (3,1) {$\mathbb{F}(A)$};
+\node (A') at (1,-1) {$\mathbb{F}(A) \otimes \mathbb{F}(1_{\lC})$};
+\node (C') at (3,-1) {$\mathbb{F}(A \otimes 1_{\lC})$};
+\node (B) at (5,1) {$1_{\lD} \otimes \mathbb{F}(A)$};
+\node (B') at (5,-1) {$\mathbb{F}(1_{\lC}) \otimes \mathbb{F}(A)$};
+\node (D) at (7,1) {$\mathbb{F}(A)$};
+\node (D') at (7,-1) {$\mathbb{F}(1_{\lC} \otimes A)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[left]{$1 \otimes \epsilon$} (A')
+(C') edge node[right]{$\mathbb{F}(r_{A})$} (C)
+(A) edge node[above]{$r_{\mathbb{F}(A)}$} (C)
+(A') edge node[above]{$\mu_{A,1_{\lC}}$} (C')
+(B) edge node[left]{$\epsilon \otimes 1$} (B')
+(B') edge node[above]{$\mu_{1_{\lC},A}$} (D')
+(B) edge node[above]{$\ell_{\mathbb{F}(A)}$} (D)
+(D') edge node[right]{$\mathbb{F}(\ell_{A})$} (D);
+\end{tikzpicture}
+\]
+and for horizontal 1-cells $N_{1},N_{2}$ and $N_{3}$ of $\lC$,
+ \[\xymatrix{
+    (\mathbb{F}(N_{1}) \otimes \mathbb{F}(N_{2})) \otimes \mathbb{F}(N_{3}) \ar[r]^{\alpha^\prime}\ar[d]_{\nu_{N_{1},N_{2}} \otimes 1}
+    & \mathbb{F}(N_{1}) \otimes (\mathbb{F}(N_{2}) \otimes \mathbb{F}(N_{3})) \ar[d]^{1 \otimes \nu_{N_{2},N_{3}}}\\
+    \mathbb{F}(N_{1} \otimes N_{2}) \otimes \mathbb{F}(N_{3}) \ar[d]_{\nu_{N_{1} \otimes N_{2},N_{3}}} &
+    \mathbb{F}(N_{1}) \otimes \mathbb{F}(N_{2} \otimes N_{3}) \ar[d]^{\nu_{N_{1},N_{2} \otimes N_{3}}}\\
+    \mathbb{F}((N_{1} \otimes N_{2}) \otimes N_{3})\ar[r]^{\mathbb{F}\alpha} &
+    \mathbb{F}(N_{1} \otimes (N_{2} \otimes N_{3}))}\]
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,1) {$\mathbb{F}(N_{1}) \otimes U_{1_{\lD}}$};
+\node (C) at (3,1) {$\mathbb{F}(N_{1})$};
+\node (A') at (0,-1) {$\mathbb{F}(N_{1}) \otimes \mathbb{F}(U_{1_{\lC}})$};
+\node (C') at (3,-1) {$\mathbb{F}(N_{1} \otimes U_{1_{\lC}})$};
+\node (B) at (5,1) {$U_{1_{\lD}} \otimes \mathbb{F}(N_{1})$};
+\node (B') at (5,-1) {$\mathbb{F}(U_{1_{\lC}}) \otimes \mathbb{F}(N_{1})$};
+\node (D) at (8,1) {$\mathbb{F}(N_{1})$};
+\node (D') at (8,-1) {$\mathbb{F}(U_{1_{\lC}} \otimes N_{1})$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[left]{$1 \otimes \delta$} (A')
+(C') edge node[right]{$\mathbb{F}(r_{N_{1}})$} (C)
+(A) edge node[above]{$r_{\mathbb{F}(N_{1})}$} (C)
+(A') edge node[above]{$\nu_{N_{1},U_{1_{\lC}}}$} (C')
+(B) edge node[left]{$\delta \otimes 1$} (B')
+(B') edge node[above]{$\nu_{U_{1_{\lC}},N_{1}}$} (D')
+(B) edge node[above]{$\ell_{\mathbb{F}(N_{1})}$} (D)
+(D') edge node[right]{$\mathbb{F}(\ell_{N_{1}})$} (D);
+\end{tikzpicture}
+\]
+
+		\item $S\mathbb{F}_1= \mathbb{F}_0S$ and $T\mathbb{F}_1 = \mathbb{F}_0T$ are equations between monoidal functors, and
+		\item the composition and unit comparisons $\phi(N_1,N_2) \maps \mathbb{F}_1(N_1) \odot \mathbb{F}_1(N_2) \to \mathbb{F}_1(N_1\odot N_2)$ and $\phi_A \maps U_{\mathbb{F}_0 (A)} \to \mathbb{F}_1(U_A)$ are monoidal natural transformations.
+	\end{itemize}
+The monoidal lax double functor is \define{braided} if $\mathbb{F}_0$ and $\mathbb{F}_1$ are braided monoidal functors and \define{symmetric} if they are symmetric monoidal functors, and lax monoidal or oplax monoidal if the isomorphisms and families of natural isomorphisms of items (1)-(4) above are merely morphisms and natural transformations going in the appropriate directions.
+\end{defn}
+%\end{comment}
 

### 2019-05-30 EquivCompFrameworks_20180911kc.tex
leftover tiny
some general rearrangement based on what we discussed

@@
 \item {\chris Discuss notation for Decorated and Structured cospan double categories one last time? :)}
-\item {\chris Where should we put some standard things we use?
-For exampe, lax monoidal pseudofunctor should be recalled early.
-Together with pseudonatural transformations I believe.
-For now, I put them in an unnamed section}
 \item {\chris Notation between \cref{Equiv} and \cref{thm:decoratedcospans} right now does not match! Need to fix.}
@@
 \end{itemize}
-
-\section*{Various notions to be recalled, earlier rather than later}
-
-Recall that a pseudofunctor $F\colon\bicat{A}\to\bicat{B}$ between bicategories $\bicat{A}$ and $\bicat{B}$ is functorial up to coherent natural isomorphism, namely for composable arrows we have $F(g\circ f)\cong Fg\circ Ff$ and $F(1_a)\cong1_{Fa}$ satisfying standard axioms.
-Given pseudofunctors $F,G\colon \bicat{A} \to \bicat{B}$, a \define{pseudonatural transformation} $\sigma$ consists of {\chris notation below needs fixing}
-\begin{itemize}
-\item for each object $a \in \bicat{A}$, a morphism $\sigma_a \colon F(a) \to G(a)$ in $\bicat{B}$ 
-\item for every pair of objects $a$ and $b$ of $\mathbf{A}$, we have natural isomorphisms
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$\mathbf{A}(a,b)$};
-\node (B) at (2,0) {$\mathbf{X}(F(a),F(b))$};
-\node (C) at (0,-1) {$\mathbf{X}(G(a),G(b))$};
-\node (D) at (2,-1) {$\mathbf{X}(F(a),G(b))$};
-\node (E) at (1,-0.5) {$\sigma_{a,b} \Nearrow$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$F$} (B)
-(B) edge node[right]{$(\sigma_{b})_*$} (D)
-(A) edge node[left]{$G$} (C)
-(C) edge node[above]{$(\sigma_a)^*$} (D);
-\end{tikzpicture}
-\]
-where $(\sigma_a)^*$ and $(\sigma_b)_*$ are the functors induced by precomposition and postcompositon, respectively.
-Thus for each morphism $f \colon a \to b$ in $\mathbf{A}$, we have an invertible 2-morphism $\sigma_f \colon G(f) \sigma_a \xrightarrow{\sim} \sigma_{b} F(f)$ in $\mathbf{X}$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$F(a)$};
-\node (B) at (1,0) {$F(b)$};
-\node (C) at (0,-1) {$G(a)$};
-\node (D) at (1,-1) {$G(b)$};
-\node (E) at (0.5,-0.5) {$\sigma_f \Nearrow$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$F(f)$} (B)
-(B) edge node[right]{$\sigma_{b}$} (D)
-(A) edge node[left]{$\sigma_a$} (C)
-(C) edge node[above]{$G(f)$} (D);
-\end{tikzpicture}
-\]
-which is compatible with composition and identities.
-\end{itemize}
-%such that for each composable pair of morphisms $f \colon a \to b$ and $g \colon b \to c$ of $\mathbf{A}$, the following diagrams commute:
-%\[
-%\begin{tikzpicture}[scale=1.5]
-%\node (A) at (0,0.5) {$(G(g)G(f))\sigma_a$};
-%\node (A') at (2,0.5) {$G(g)(G(f) \sigma_a)$};
-%\node (B) at (0,-0.5) {$G(gf) \sigma_a$};
-%\node (C) at (4,0.5) {$G(g) (\sigma_b F(f))$};
-%\node (C') at (4,-0.5) {$\sigma_c F(gf)$};
-%\node (D) at (6,0.5) {$(G(g) \sigma_b) F(f)$};
-%\node (D') at (8,-0.5) {$\sigma_c (F(g)F(f))$};
-%\node (F) at (8,0.5) {$(\sigma_c F(g)) F(f)$};
-%\path[->,font=\scriptsize,>=angle 90]
-%(A) edge node[above]{$a^\prime$} (A')
-%(A) edge node[left]{$\psi 1_{\sigma_a}$} (B)
-%(A') edge node[above]{$1_{G(g)} \sigma_f$} (C)
-%(B) edge node[above]{$\sigma_{gf}$} (C')
-%(C) edge node [above] {${a^\prime}^{-1}$} (D)
-%(D') edge node [above] {$1_{\sigma_c} \phi$} (C')
-%(D) edge node [above] {$\sigma_g 1_{F(f)}$} (F)
-%(F) edge node [right] {$a^\prime$} (D');
-%\end{tikzpicture}
-%\]
-%\[
-%\begin{tikzpicture}[scale=1.5]
-%\node (A) at (0,0) {$1_{G(a)} \sigma_a$};
-%\node (B) at (1,1) {$G(1_a) \sigma_a$};
-%\node (C) at (2,0) {$\sigma_a F(1_a)$};
-%\node (D) at (0.5,-1) {$\sigma_a$};
-%\node (E) at (1.5,-1) {$\sigma_a 1_{F(a)}$};
-%\path[->,font=\scriptsize,>=angle 90]
-%(A) edge node[left]{$\psi 1_{\sigma_a}$} (B)
-%(B) edge node[right]{$\sigma_{1_a}$} (C)
-%(A) edge node [left] {$\ell^\prime$} (D)
-%(D) edge node [above] {${\rho^\prime}^{-1}$} (E)
-%(E) edge node [right] {$1_{\sigma_a} \phi$} (C);
-%\end{tikzpicture}
-%\]
-%Christina: I removed the above, they are not needed I believe
-We denote by $[\A,\bicat{Cat}]_\pse$ the 2-category 
-of pseudofunctors, pseudonatural transformations and modifications from an ordinary category $\A$ viewed as a 2-category with trivial 2-cells, into $\bicat{Cat}$.
-Classicaly this has been referred to as the 2-category of \emph{opindexed categories}, since an indexed category is a contravariant pseudofunctor into $\bicat{Cat}$.
-
-A \define{lax monoidal} pseudofunctor is....
-A \define{symmetric lax monoidal} pseudofunctor...
-{\chris Not sure if we need monoidal transformations?}
 
@@
 %\end{comment}
-
-\section{A symmetric monoidal double category of structured cospans}\label{sec:structuredcospans}
-
-{\chris Moved it into a new section here, amend to make nice with surroundings}
-In this section, we recall the double category of \emph{structured cospans}, a formalism introduced to the first two authors.
-One of the main goals of this paper is to provide a double equivalence between this double category and one of \emph{decorated cospans}, described in detail in the subsequent section.
-
-Once again following the notation of Shulman \cite{Shul2}, given a double category $\mathbb{A}$, we write $_f \mathbb{A}_g(M,N)$ for the set of 2-morphisms in $\mathbb{A}$ of the form:
-\[
-  \xymatrix@-.5pc{
-    A \ar[r]|{|}^{M}  \ar[d]_f \ar@{}[dr]|{\Downarrow a}&
-    B\ar[d]^g\\
-    C \ar[r]|{|}_N & D
-  }
-\]
-We call $M$ and $N$ the \define{horizontal source and target} of the 2-morphism $a$, respectively, and likewise we call $f$ and $g$ the \define{vertical source and target} of the 2-morphism $a$, respectively.
-Thus $_f \mathbb{A}_g(M,N)$ denotes the set of 2-morphisms in $\mathbb{A}$ with horizontal source and target $M$ and $N$ and vertical source and target $f$ and $g$.
-\begin{defn}
-A (possibly lax or oplax) double functor $\mathbb{F} \colon \mathbb{A} \to \mathbb{X}$ is \define{full} (respectively, \define{faithful}) if $\mathbb{F}_0 \colon \mathbb{A}_0 \to \mathbb{X}_0$ is full (respectively, faithful) and each map $$\mathbb{F}_1 \colon _f \mathbb{A}_g(M,N) \to _{\mathbb{F}(f)} \mathbb{X}_{\mathbb{F}(g)}(\mathbb{F}(M),\mathbb{F}(N))$$ is surjective (respectively, injective).
-\end{defn}
-\begin{defn}
-A (possibly lax or oplax) double functor $\mathbb{F} \colon \mathbb{A} \to \mathbb{X}$ is \define{essentially surjective} if we can simultaneously make the following choices:
-\begin{enumerate}
-\item{For each object $x \in \mathbb{X}$, we can find an object $a \in \mathbb{A}$ together with a vertical 1-isomorphism $\alpha_x \colon \mathbb{F}(a) \to x$, and}
-\item{For each horizontal 1-cell $N \colon x_1 \tobar x_2$  of $\mathbb{X}$, we can find a horizontal 1-cell $M \colon a_1 \tobar a_2$ of $\mathbb{A}$ and a 2-isomorphism $a_{N}$ of $\mathbb{X}$ as in the following diagram:
-\[
-  \xymatrix@-.5pc{
-    \mathbb{F}(a_1) \ar[r]|{|}^{\mathbb{F}(M)}  \ar[d]_{\alpha_{x_1}} \ar@{}[dr]|{\Downarrow a_N}&
-    \mathbb{F}(a_1) \ar[d]^{\alpha_{x_2}}\\
-    x_1 \ar[r]|{|}_N & x_2
-  }
-\]
-}
-\end{enumerate}
-\end{defn}
-\begin{defn}
-A double functor $\mathbb{F} \colon \mathbb{A} \to \mathbb{X}$ is \define{strong} if the comparison and unit constraints are globular isomorphisms, meaning that for each composable pair of horizontal 1-cells $M$ and $N$ we have a natural isomorphism $$\mathbb{F}_{M,N} \colon \mathbb{F}(M) \odot \mathbb{F}(N) \xrightarrow{\sim} \mathbb{F}(M \odot N)$$and for each object $a \in \mathbb{A}$ a natural isomorphism $$\mathbb{F}_a \colon \hat{U}_{\mathbb{F}(a)} \xrightarrow{\sim} \mathbb{F}(U_a).$$
-\end{defn}
-
-Formally, two strong double functors between two double categories form a \emph{double equivalence} if {\chris their two-way composite is isomorphic to the identity, better expressed, possibly in a definition environment}.
-Similarly to ordinary equivalence of categories, {\chris cite shulman's theorem here [Shulman,7.8]} allows us to use the following equivalent characterization.
-
-\begin{thm}\label{ShulDubEquiv}
-A strong double functor $\mathbb{F} \colon \mathbb{A} \to \mathbb{X}$ is part of a double equivalence if and only if it is full, faithful and essentially surjective. {\chris on objects?}
-\end{thm}
-
-\begin{prop}
-Let $\mathbb{A}$ and $\mathbb{X}$ be symmetric monoidal double categories and let $\mathbb{F} \colon \mathbb{A} \to \mathbb{X}$ be a symmetric monoidal strong double functor.
-If $\mathbb{F}$ is part of a double equivalence, then $\mathbb{F}$ is in fact part of a symmetric monoidal double equivalence, and $\mathbb{A}$ and $\mathbb{X}$ are equivalent as symmetric monoidal double categories.
-\end{prop}
-
-Our next goal is to show that the symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$ of Section \ref{DecCospansDoubleCat} is equivalent as a symmetric monoidal double category to the symmetric monoidal double category $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$ obtained using structured cospans.
-{\chris Wait, why do you need to consider them as monoidal in the assumptions of the theorem?}
-
-\begin{thm}\label{SC}
-Given a category $\mathsf{X}$ with finite colimits and a category $\mathsf{A}$ with finite coproducts and a finite coproduct preserving functor $L \colon \mathsf{A} \to \mathsf{X}$ with $\mathsf{A}$ and $\mathsf{X}$ regarded as cocartesian monoidal categories, there exists a symmetric monoidal double category $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$ which has:
-\begin{enumerate}
-\item{objects given by objects of $\mathsf{A}$,}
-\item{vertical 1-morphisms given by morphisms of $\mathsf{A}$,}
-\item{horizontal 1-cells given by cospans of $\mathsf{X}$ of the form:
-\begin{equation}\label{eq:structuredcospan}
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$L(c)$};
-\node (B) at (1,0) {$x$};
-\node (C) at (2,0) {$L(c^\prime)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$$} (B)
-(C) edge node[above]{$$} (B);
-\end{tikzpicture}
-\end{equation}
-and}
-\item{2-morphisms given by maps of cospans of $\mathsf{X}$ of the form:
-\begin{equation}\label{eq:2cellsStrCsp}
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$L(c_1)$};
-\node (B) at (1,0) {$x$};
-\node (C) at (2,0) {$L(c_2)$};
-\node (A') at (0,-1) {$L(c_1^\prime)$};
-\node (B') at (1,-1) {$x^\prime$};
-\node (C') at (2,-1) {$L(c_2^\prime)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$$} (B)
-(C) edge node[above]{$$} (B)
-(A') edge node[above]{$$} (B')
-(C') edge node[above]{$$} (B')
-(A) edge node [left]{$L(f)$} (A')
-(B) edge node [left]{$\alpha$} (B')
-(C) edge node [left]{$L(g)$} (C');
-\end{tikzpicture}
-\end{equation}
-Composition of horizontal 1-cells and 2-morphisms is given by pushouts in $\mathsf{X}$ and tensoring of objects is under binary coproducts in $\mathsf{A}$.
-}
-\end{enumerate}
-\end{thm}
-\begin{proof}
-See the first two authors' work on structured cospans \cite{BC2}.
-\end{proof}
-{\chris Below, I commented out a nice short recalled version of decorated cospans, since now their definition is later. Use if we want to recall at some point later}
-%In the previous section, we started with a symmetric lax monoidal pseudofunctor $F \colon \mathsf{A} \to \mathbf{Cat}$ and created a symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$ which has:
-%\begin{enumerate}
-%\item{objects of $\mathsf{A}$ as objects,}
-%\item{morphisms of $\mathsf{A}$ as vertical 1-morphisms,}
-%\item{horizontal 1-cells are given by $F$-decorated cospans, which are pairs:
-%\[
-%\begin{tikzpicture}[scale=1.5]
-%\node (A) at (0,0) {$c_1$};
-%\node (B) at (1,0) {$c$};
-%\node (C) at (2,0) {$c_2$};
-%\node (D) at (3,0) {$x \in F(c)$};
-%\path[->,font=\scriptsize,>=angle 90]
-%(A) edge node[above]{$i$} (B)
-%(C) edge node[above]{$o$} (B);
-%\end{tikzpicture}
-%\]
-%and}
-%\item{2-morphisms are given by maps of cospans in $\mathsf{A}$:
-%\[
-%\begin{tikzpicture}[scale=1.5]
-%\node (A) at (0,0) {$c_1$};
-%\node (B) at (1,0) {$c$};
-%\node (C) at (2,0) {$c_2$};
-%\node (A') at (0,-1) {$c_1^\prime$};
-%\node (B') at (1,-1) {$c^\prime$};
-%\node (C') at (2,-1) {$c_2^\prime$};
-%\node (D) at (3,0) {$x \in F(c)$};
-%\node (D') at (3,-1) {$x^\prime \in F(c^\prime)$};
-%\path[->,font=\scriptsize,>=angle 90]
-%(A) edge node[above]{$i$} (B)
-%(C) edge node[above]{$o$} (B)
-%(A') edge node[above]{$i^\prime$} (B')
-%(C') edge node[above]{$o^\prime$} (B')
-%(A) edge node [left]{$f$} (A')
-%(B) edge node [left]{$h$} (B')
-%(C) edge node [left]{$g$} (C');
-%\end{tikzpicture}
-%\]
-%together with a morphism $\iota \colon F(h)(d) \to d^\prime$ in $F(c^\prime)$.}
-%\end{enumerate}
 
@@
 
-%\begin{comment}
-\section{Maps of decorated cospan double categories}\label{MapsDecCospansDoubleCat}
-Let $F \colon \mathsf{A} \to \mathbf{Cat}$ be a symmetric lax monoidal pseudofunctor.
+%Let $F \colon \mathsf{A} \to \mathbf{Cat}$ be a symmetric lax monoidal pseudofunctor.
 Then by Theorem \ref{DC} of the previous section, we get a symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$.
 This symmetric monoidal double category has:
-\begin{enumerate}
-\item{objects as those of $\mathsf{A}$,}
-\item{vertical 1-morphisms as morphisms of $\mathsf{A}$,}
-\item{horizontal 1-cells as pairs:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a$};
-\node (B) at (1,0) {$c$};
-\node (C) at (2,0) {$b$};
-\node (D) at (4,0) {$d \in F(c)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i$} (B)
-(C) edge node[above]{$o$} (B);
-\end{tikzpicture}
-\]
-and}
-\item{2-morphisms as maps of cospans in $\mathsf{A}$
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$a$};
-\node (A') at (0,-0.5) {$a^\prime$};
-\node (B) at (1,0.5) {$c$};
-\node (C) at (2,0.5) {$b$};
-\node (C') at (2,-0.5) {$b^\prime$};
-\node (D) at (1,-0.5) {$c^\prime$};
-\node (E) at (3,0.5) {$d \in F(c)$};
-\node (F) at (3,-0.5) {$d^\prime \in F(c^\prime)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$$} (B)
-(C) edge node[above]{$$} (B)
-(A) edge node[left]{$f$} (A')
-(C) edge node[left]{$g$} (C')
-(A') edge node {$$} (D)
-(C') edge node {$$} (D)
-(B) edge node [left] {$h$} (D);
-\end{tikzpicture}
-\]
-together with a morphism $\iota \colon F(h)(d) \to d^\prime$ in $F(c^\prime)$.}
-\end{enumerate}
-Given another symmetric lax monoidal pseudofunctor $F^\prime \colon \mathsf{A^\prime} \to \mathbf{Cat}$, we can obtain another symmetric monoidal double category $F^\prime \mathbb{C}\textnormal{sp}$.
-A map from $F\mathbb{C}\textnormal{sp}$ to $F^\prime \mathbb{C}\textnormal{sp}$ will then be a double functor $\mathbb{H} \colon F\mathbb{C}\textnormal{sp} \to F' \mathbb{C}\textnormal{sp}$ whose object component is given by a finite colimit preserving functor $\mathbb{H}_0 = H \colon \mathsf{A} \to \mathsf{A^\prime}$ and whose arrow component is given by a functor $\mathbb{H}_1$ defined on horizontal 1-cells by:
+%\begin{enumerate}
+%\item{objects as those of $\mathsf{A}$,}
+%\item{vertical 1-morphisms as morphisms of $\mathsf{A}$,}
+%\item{horizontal 1-cells as pairs:
+%\[
+%\begin{tikzpicture}[scale=1.5]
+%\node (A) at (0,0) {$a$};
+%\node (B) at (1,0) {$c$};
+%\node (C) at (2,0) {$b$};
+%\node (D) at (4,0) {$d \in F(c)$};
+%\path[->,font=\scriptsize,>=angle 90]
+%(A) edge node[above]{$i$} (B)
+%(C) edge node[above]{$o$} (B);
+%\end{tikzpicture}
+%\]
+%and}
+%\item{2-morphisms as maps of cospans in $\mathsf{A}$
+%\[
+%\begin{tikzpicture}[scale=1.5]
+%\node (A) at (0,0.5) {$a$};
+%\node (A') at (0,-0.5) {$a^\prime$};
+%\node (B) at (1,0.5) {$c$};
+%\node (C) at (2,0.5) {$b$};
+%\node (C') at (2,-0.5) {$b^\prime$};
+%\node (D) at (1,-0.5) {$c^\prime$};
+%\node (E) at (3,0.5) {$d \in F(c)$};
+%\node (F) at (3,-0.5) {$d^\prime \in F(c^\prime)$};
+%\path[->,font=\scriptsize,>=angle 90]
+%(A) edge node[above]{$$} (B)
+%(C) edge node[above]{$$} (B)
+%(A) edge node[left]{$f$} (A')
+%(C) edge node[left]{$g$} (C')
+%(A') edge node {$$} (D)
+%(C') edge node {$$} (D)
+%(B) edge node [left] {$h$} (D);
+%\end{tikzpicture}
+%\]
+%together with a morphism $\iota \colon F(h)(d) \to d^\prime$ in $F(c^\prime)$.}
+%\end{enumerate}
+
+Regarding maps between symmetric monoidal double categories, consider another symmetric lax monoidal pseudofunctor $F^\prime \colon \mathsf{A^\prime} \to \mathbf{Cat}$%, we can obtain another symmetric monoidal double category $F^\prime \mathbb{C}\textnormal{sp}$.
+a morphism from $F\mathbb{C}\textnormal{sp}$ to $F^\prime \mathbb{C}\textnormal{sp}$ will then be a double functor $\mathbb{H} \colon F\mathbb{C}\textnormal{sp} \to F' \mathbb{C}\textnormal{sp}$ whose object component is given by a finite colimit preserving functor $\mathbb{H}_0 = H \colon \mathsf{A} \to \mathsf{A^\prime}$ and whose arrow component is given by a functor $\mathbb{H}_1$ defined on horizontal 1-cells by:
 \[
@@
 \section{An equivalence of symmetric monoidal double categories} \label{EquivDoubleCats}
+
+{\chris moved here preliminary}
+In this section, we recall the double category of \emph{structured cospans}, a formalism introduced to the first two authors.
+One of the main goals of this paper is to provide a double equivalence between this double category and one of \emph{decorated cospans}, described in detail in the subsequent section.
+
+{\chris Wait, why do you need to consider them as monoidal in the assumptions of the theorem?}
+
+\begin{thm}\label{SC}
+Given a category $\mathsf{X}$ with finite colimits and a category $\mathsf{A}$ with finite coproducts and a finite coproduct preserving functor $L \colon \mathsf{A} \to \mathsf{X}$ with $\mathsf{A}$ and $\mathsf{X}$ regarded as cocartesian monoidal categories, there exists a symmetric monoidal double category $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$ which has:
+\begin{enumerate}
+\item{objects given by objects of $\mathsf{A}$,}
+\item{vertical 1-morphisms given by morphisms of $\mathsf{A}$,}
+\item{horizontal 1-cells given by cospans of $\mathsf{X}$ of the form:
+\begin{equation}\label{eq:structuredcospan}
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$L(c)$};
+\node (B) at (1,0) {$x$};
+\node (C) at (2,0) {$L(c^\prime)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$$} (B)
+(C) edge node[above]{$$} (B);
+\end{tikzpicture}
+\end{equation}
+and}
+\item{2-morphisms given by maps of cospans of $\mathsf{X}$ of the form:
+\begin{equation}\label{eq:2cellsStrCsp}
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$L(c_1)$};
+\node (B) at (1,0) {$x$};
+\node (C) at (2,0) {$L(c_2)$};
+\node (A') at (0,-1) {$L(c_1^\prime)$};
+\node (B') at (1,-1) {$x^\prime$};
+\node (C') at (2,-1) {$L(c_2^\prime)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$$} (B)
+(C) edge node[above]{$$} (B)
+(A') edge node[above]{$$} (B')
+(C') edge node[above]{$$} (B')
+(A) edge node [left]{$L(f)$} (A')
+(B) edge node [left]{$\alpha$} (B')
+(C) edge node [left]{$L(g)$} (C');
+\end{tikzpicture}
+\end{equation}
+Composition of horizontal 1-cells and 2-morphisms is given by pushouts in $\mathsf{X}$ and tensoring of objects is under binary coproducts in $\mathsf{A}$.
+}
+\end{enumerate}
+\end{thm}
+\begin{proof}
+See the first two authors' work on structured cospans \cite{BC2}.
+\end{proof}
+{\chris Below, I commented out a nice short recalled version of decorated cospans, since now their definition is later. Use if we want to recall at some point later}
+%In the previous section, we started with a symmetric lax monoidal pseudofunctor $F \colon \mathsf{A} \to \mathbf{Cat}$ and created a symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$ which has:
+%\begin{enumerate}
+%\item{objects of $\mathsf{A}$ as objects,}
+%\item{morphisms of $\mathsf{A}$ as vertical 1-morphisms,}
+%\item{horizontal 1-cells are given by $F$-decorated cospans, which are pairs:
+%\[
+%\begin{tikzpicture}[scale=1.5]
+%\node (A) at (0,0) {$c_1$};
+%\node (B) at (1,0) {$c$};
+%\node (C) at (2,0) {$c_2$};
+%\node (D) at (3,0) {$x \in F(c)$};
+%\path[->,font=\scriptsize,>=angle 90]
+%(A) edge node[above]{$i$} (B)
+%(C) edge node[above]{$o$} (B);
+%\end{tikzpicture}
+%\]
+%and}
+%\item{2-morphisms are given by maps of cospans in $\mathsf{A}$:
+%\[
+%\begin{tikzpicture}[scale=1.5]
+%\node (A) at (0,0) {$c_1$};
+%\node (B) at (1,0) {$c$};
+%\node (C) at (2,0) {$c_2$};
+%\node (A') at (0,-1) {$c_1^\prime$};
+%\node (B') at (1,-1) {$c^\prime$};
+%\node (C') at (2,-1) {$c_2^\prime$};
+%\node (D) at (3,0) {$x \in F(c)$};
+%\node (D') at (3,-1) {$x^\prime \in F(c^\prime)$};
+%\path[->,font=\scriptsize,>=angle 90]
+%(A) edge node[above]{$i$} (B)
+%(C) edge node[above]{$o$} (B)
+%(A') edge node[above]{$i^\prime$} (B')
+%(C') edge node[above]{$o^\prime$} (B')
+%(A) edge node [left]{$f$} (A')
+%(B) edge node [left]{$h$} (B')
+%(C) edge node [left]{$g$} (C');
+%\end{tikzpicture}
+%\]
+%together with a morphism $\iota \colon F(h)(d) \to d^\prime$ in $F(c^\prime)$.}
+%\end{enumerate}
+
+{\chris here ends old}
+
 In this section we prove that the two different double categorical network frameworks, namely structured cospans and decorated cospans described respectively in \cref{DecCospansDoubleCat,sec:structuredcospans}, are equivalent under certain assumptions.
@@
 {\chris The above diagram might be a bit overwhelming, but all info is there.
-Choose which parts are required for a smooth proof!} {\chris Also, iota and letter i look alarmingly similar.
+Choose which parts are required for a smooth proof!} {\chris Also, iota and the letter i look alarmingly similar.
 Should we change iota to some other distinctive greek letter?}
@@
 \section{Appendix}
+
+{\chris Put various stuff here, fix in the very end}
+Recall that a pseudofunctor $F\colon\bicat{A}\to\bicat{B}$ between bicategories $\bicat{A}$ and $\bicat{B}$ is functorial up to coherent natural isomorphism, namely for composable arrows we have $F(g\circ f)\cong Fg\circ Ff$ and $F(1_a)\cong1_{Fa}$ satisfying standard axioms.
+Given pseudofunctors $F,G\colon \bicat{A} \to \bicat{B}$, a \define{pseudonatural transformation} $\sigma$ consists of {\chris notation below needs fixing}
+\begin{itemize}
+\item for each object $a \in \bicat{A}$, a morphism $\sigma_a \colon F(a) \to G(a)$ in $\bicat{B}$ 
+\item for every pair of objects $a$ and $b$ of $\mathbf{A}$, we have natural isomorphisms
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$\mathbf{A}(a,b)$};
+\node (B) at (2,0) {$\mathbf{X}(F(a),F(b))$};
+\node (C) at (0,-1) {$\mathbf{X}(G(a),G(b))$};
+\node (D) at (2,-1) {$\mathbf{X}(F(a),G(b))$};
+\node (E) at (1,-0.5) {$\sigma_{a,b} \Nearrow$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$F$} (B)
+(B) edge node[right]{$(\sigma_{b})_*$} (D)
+(A) edge node[left]{$G$} (C)
+(C) edge node[above]{$(\sigma_a)^*$} (D);
+\end{tikzpicture}
+\]
+where $(\sigma_a)^*$ and $(\sigma_b)_*$ are the functors induced by precomposition and postcompositon, respectively.
+Thus for each morphism $f \colon a \to b$ in $\mathbf{A}$, we have an invertible 2-morphism $\sigma_f \colon G(f) \sigma_a \xrightarrow{\sim} \sigma_{b} F(f)$ in $\mathbf{X}$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$F(a)$};
+\node (B) at (1,0) {$F(b)$};
+\node (C) at (0,-1) {$G(a)$};
+\node (D) at (1,-1) {$G(b)$};
+\node (E) at (0.5,-0.5) {$\sigma_f \Nearrow$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$F(f)$} (B)
+(B) edge node[right]{$\sigma_{b}$} (D)
+(A) edge node[left]{$\sigma_a$} (C)
+(C) edge node[above]{$G(f)$} (D);
+\end{tikzpicture}
+\]
+which is compatible with composition and identities.
+\end{itemize}
+%such that for each composable pair of morphisms $f \colon a \to b$ and $g \colon b \to c$ of $\mathbf{A}$, the following diagrams commute:
+%\[
+%\begin{tikzpicture}[scale=1.5]
+%\node (A) at (0,0.5) {$(G(g)G(f))\sigma_a$};
+%\node (A') at (2,0.5) {$G(g)(G(f) \sigma_a)$};
+%\node (B) at (0,-0.5) {$G(gf) \sigma_a$};
+%\node (C) at (4,0.5) {$G(g) (\sigma_b F(f))$};
+%\node (C') at (4,-0.5) {$\sigma_c F(gf)$};
+%\node (D) at (6,0.5) {$(G(g) \sigma_b) F(f)$};
+%\node (D') at (8,-0.5) {$\sigma_c (F(g)F(f))$};
+%\node (F) at (8,0.5) {$(\sigma_c F(g)) F(f)$};
+%\path[->,font=\scriptsize,>=angle 90]
+%(A) edge node[above]{$a^\prime$} (A')
+%(A) edge node[left]{$\psi 1_{\sigma_a}$} (B)
+%(A') edge node[above]{$1_{G(g)} \sigma_f$} (C)
+%(B) edge node[above]{$\sigma_{gf}$} (C')
+%(C) edge node [above] {${a^\prime}^{-1}$} (D)
+%(D') edge node [above] {$1_{\sigma_c} \phi$} (C')
+%(D) edge node [above] {$\sigma_g 1_{F(f)}$} (F)
+%(F) edge node [right] {$a^\prime$} (D');
+%\end{tikzpicture}
+%\]
+%\[
+%\begin{tikzpicture}[scale=1.5]
+%\node (A) at (0,0) {$1_{G(a)} \sigma_a$};
+%\node (B) at (1,1) {$G(1_a) \sigma_a$};
+%\node (C) at (2,0) {$\sigma_a F(1_a)$};
+%\node (D) at (0.5,-1) {$\sigma_a$};
+%\node (E) at (1.5,-1) {$\sigma_a 1_{F(a)}$};
+%\path[->,font=\scriptsize,>=angle 90]
+%(A) edge node[left]{$\psi 1_{\sigma_a}$} (B)
+%(B) edge node[right]{$\sigma_{1_a}$} (C)
+%(A) edge node [left] {$\ell^\prime$} (D)
+%(D) edge node [above] {${\rho^\prime}^{-1}$} (E)
+%(E) edge node [right] {$1_{\sigma_a} \phi$} (C);
+%\end{tikzpicture}
+%\]
+%Christina: I removed the above, they are not needed I believe
+We denote by $[\A,\bicat{Cat}]_\pse$ the 2-category 
+of pseudofunctors, pseudonatural transformations and modifications from an ordinary category $\A$ viewed as a 2-category with trivial 2-cells, into $\bicat{Cat}$.
+Classicaly this has been referred to as the 2-category of \emph{opindexed categories}, since an indexed category is a contravariant pseudofunctor into $\bicat{Cat}$.
+
+A \define{lax monoidal} pseudofunctor is....
+A \define{symmetric lax monoidal} pseudofunctor...
+{\chris Not sure if we need monoidal transformations?}
+
+{\chris Moved from earlier, probably merge with what follows}
+Once again following the notation of Shulman \cite{Shul2}, given a double category $\mathbb{A}$, we write $_f \mathbb{A}_g(M,N)$ for the set of 2-morphisms in $\mathbb{A}$ of the form:
+\[
+  \xymatrix@-.5pc{
+    A \ar[r]|{|}^{M}  \ar[d]_f \ar@{}[dr]|{\Downarrow a}&
+    B\ar[d]^g\\
+    C \ar[r]|{|}_N & D
+  }
+\]
+We call $M$ and $N$ the \define{horizontal source and target} of the 2-morphism $a$, respectively, and likewise we call $f$ and $g$ the \define{vertical source and target} of the 2-morphism $a$, respectively.
+Thus $_f \mathbb{A}_g(M,N)$ denotes the set of 2-morphisms in $\mathbb{A}$ with horizontal source and target $M$ and $N$ and vertical source and target $f$ and $g$.
+\begin{defn}
+A (possibly lax or oplax) double functor $\mathbb{F} \colon \mathbb{A} \to \mathbb{X}$ is \define{full} (respectively, \define{faithful}) if $\mathbb{F}_0 \colon \mathbb{A}_0 \to \mathbb{X}_0$ is full (respectively, faithful) and each map $$\mathbb{F}_1 \colon _f \mathbb{A}_g(M,N) \to _{\mathbb{F}(f)} \mathbb{X}_{\mathbb{F}(g)}(\mathbb{F}(M),\mathbb{F}(N))$$ is surjective (respectively, injective).
+\end{defn}
+\begin{defn}
+A (possibly lax or oplax) double functor $\mathbb{F} \colon \mathbb{A} \to \mathbb{X}$ is \define{essentially surjective} if we can simultaneously make the following choices:
+\begin{enumerate}
+\item{For each object $x \in \mathbb{X}$, we can find an object $a \in \mathbb{A}$ together with a vertical 1-isomorphism $\alpha_x \colon \mathbb{F}(a) \to x$, and}
+\item{For each horizontal 1-cell $N \colon x_1 \tobar x_2$  of $\mathbb{X}$, we can find a horizontal 1-cell $M \colon a_1 \tobar a_2$ of $\mathbb{A}$ and a 2-isomorphism $a_{N}$ of $\mathbb{X}$ as in the following diagram:
+\[
+  \xymatrix@-.5pc{
+    \mathbb{F}(a_1) \ar[r]|{|}^{\mathbb{F}(M)}  \ar[d]_{\alpha_{x_1}} \ar@{}[dr]|{\Downarrow a_N}&
+    \mathbb{F}(a_1) \ar[d]^{\alpha_{x_2}}\\
+    x_1 \ar[r]|{|}_N & x_2
+  }
+\]
+}
+\end{enumerate}
+\end{defn}
+\begin{defn}
+A double functor $\mathbb{F} \colon \mathbb{A} \to \mathbb{X}$ is \define{strong} if the comparison and unit constraints are globular isomorphisms, meaning that for each composable pair of horizontal 1-cells $M$ and $N$ we have a natural isomorphism $$\mathbb{F}_{M,N} \colon \mathbb{F}(M) \odot \mathbb{F}(N) \xrightarrow{\sim} \mathbb{F}(M \odot N)$$and for each object $a \in \mathbb{A}$ a natural isomorphism $$\mathbb{F}_a \colon \hat{U}_{\mathbb{F}(a)} \xrightarrow{\sim} \mathbb{F}(U_a).$$
+\end{defn}
+
+Formally, two strong double functors between two double categories form a \emph{double equivalence} if {\chris their two-way composite is isomorphic to the identity, better expressed, possibly in a definition environment}.
+Similarly to ordinary equivalence of categories, {\chris cite shulman's theorem here [Shulman,7.8]} allows us to use the following equivalent characterization.
+
+\begin{thm}\label{ShulDubEquiv}
+A strong double functor $\mathbb{F} \colon \mathbb{A} \to \mathbb{X}$ is part of a double equivalence if and only if it is full, faithful and essentially surjective. {\chris on objects?}
+\end{thm}
+
+\begin{prop}
+Let $\mathbb{A}$ and $\mathbb{X}$ be symmetric monoidal double categories and let $\mathbb{F} \colon \mathbb{A} \to \mathbb{X}$ be a symmetric monoidal strong double functor.
+If $\mathbb{F}$ is part of a double equivalence, then $\mathbb{F}$ is in fact part of a symmetric monoidal double equivalence, and $\mathbb{A}$ and $\mathbb{X}$ are equivalent as symmetric monoidal double categories.
+\end{prop}
+
+{\chris Here ends what I moved}
+
 Before formally defining `pseudo double category', it is helpful to have the following picture in mind. A pseudo double category has 2-morphisms shaped like:

### 2019-05-30 EquivCompFrameworks_20180911kc.tex
getting ready to work

@@
 
-%\begin{comment}
 \section{Introduction}
+\begin{comment}
 Networks are playing an increasingly prominent role in our understanding of the world and as a result, methods of characterizing and studying networks have become evermore necessary.
@@
 \subsection*{Acknowledgements}
-Daniel Cicala, person that Christina emailed about lax slice category? {\chris did you use it after all?} No, I did not.
-%\end{comment}
+Daniel Cicala, various others.
+\end{comment}
 
@@
 \end{thm}
+
+Details of the constructions and the proof of the above theorem can be found at \cite{CourPhD}.
 
@@
 
-%\begin{comment}
 \section{Appendix}
 
+\begin{comment}
 {\chris Put various stuff here, fix in the very end}
@@
 \end{defn}
-%\end{comment}
+\end{comment}
 
@@
 \bibitem{Cour} K.\ Courser, A bicategory of decorated cospans, \emph{Theor.\ Appl.\ Cat.} \textbf{32} (2017), 995--1027. Also available as \href{https://arxiv.org/abs/1605.08100}{arXiv:1605.08100}.
+
+\bibitem{CourPhD} K.\ Courser, Cospans for Networks, PhD Thesis, University of California at Riverside (2019)
 

### 2019-05-30 EquivCompFrameworks_20180911kc.tex
small

@@
 Then we obtain an underlying symmetric monoidal bicategory $F \mathbf{Csp}$ using a result of Shulman \cite{Shul} and then finally decategorify the obtained symmetric monoidal bicategory to obtain a symmetric monoidal category $F$Csp which is a generalization of Fong's original decorated cospan category \cite{Fong}.
+The definition of a lax monoidal pseudofunctor is recalled in \cref{sec:2cats}.
+
 \begin{thm}\label{thm:decoratedcospans}
@@
 \end{thm}
-\textbf{Kenny: We should try to make this theorem shorter.}
+\textbf{Kenny: We should try to make this theorem shorter.} {\chris I agree!}
 \begin{proof}
@@
 \end{thm}
-\textbf{Kenny: We should try to make this theorem shorter.}
+\textbf{Kenny: We should try to make this theorem shorter.} {\chris Yes!}
 \begin{proof}
@@
 On the other hand, applying the functor $E$ to each decoration results in $$1 \to E(F(c_1)) \times E(F(c_2)) \xrightarrow{} E(F(c_1) \times F(c_2)) \xrightarrow{} E(F(c_1+c_2)) \xrightarrow E(F(c_1+_b c_2)) \xrightarrow{} F^\prime(H(c_1 +_b c_2))$$
-%end{comment}
 
 \section{An equivalence of symmetric monoidal double categories} \label{EquivDoubleCats}
+\begin{comment}
 
@@
 
-\begin{comment}
-
 We can also define the part of the double equivalence $\mathbb{G} \colon F\mathbb{C}\textnormal{sp} \to {_L \mathbb{C} \textnormal{sp}(\mathsf{X})}$ which goes in the other direction: again, the object component of this double functor will be $\mathbb{G}_0 = \id_{\mathsf{A}}$.
@@
 
-%\begin{comment}
 \section{Applications}\label{Applications}
+\begin{comment}
 In this section we present several examples each of which may be realized in the context of decorated cospans or in the context of structured cospans.
@@
 Thus we have a symmetric monoidal double category $\mathbb{O}\mathbf{pen}(\mathrm{Petri})$ of open Petri nets obtained from structured cospans and a symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$ of open Petri nets obtain from decorated cospans, and of course, we have an equivalence $\mathbb{O}\mathbf{pen}(\mathrm{Petri}) \sim F\mathbb{C}\textnormal{sp}$ of symmetric monoidal double categories by Theorem \ref{Equiv}.
-%\end{comment}
+\end{comment}
 
@@
 
-\begin{comment}
-{\chris Put various stuff here, fix in the very end}
+%\begin{comment}
+\subsection{2-categories}\label{sec:2cats}
+For standard 2-categorical material, we refer the reader to there and there.
+
 Recall that a pseudofunctor $F\colon\bicat{A}\to\bicat{B}$ between bicategories $\bicat{A}$ and $\bicat{B}$ is functorial up to coherent natural isomorphism, namely for composable arrows we have $F(g\circ f)\cong Fg\circ Ff$ and $F(1_a)\cong1_{Fa}$ satisfying standard axioms.
@@
 
+\subsection{Double categories}\label{sec:doublecats}
 {\chris Moved from earlier, probably merge with what follows}
@@
 \end{defn}
-\end{comment}
+%\end{comment}
 

### 2019-05-30 EquivCompFrameworks_20180911kc.tex
rearranged and slightly polished appendix

@@
 Then we obtain an underlying symmetric monoidal bicategory $F \mathbf{Csp}$ using a result of Shulman \cite{Shul} and then finally decategorify the obtained symmetric monoidal bicategory to obtain a symmetric monoidal category $F$Csp which is a generalization of Fong's original decorated cospan category \cite{Fong}.
-The definition of a lax monoidal pseudofunctor is recalled in \cref{sec:2cats}.
+The definition of a lax monoidal pseudofunctor is recalled in \cref{sec:2cats}, and the basics of (pseudo) double categories are recalled in \cref{sec:doublecats}.
 
@@
 %\begin{comment}
+
+{\chris Here, I basically rearranged things to make them come in a certain order, and also added a few things for monoidal bicats, maybe more is needed or not.
+Didn't change Kenny's notation or writings almost at all}
+
+In this chapter, we gather some well-known concepts required to make the material self-contained, as well as references to more detailed expositions.
+
 \subsection{2-categories}\label{sec:2cats}
-For standard 2-categorical material, we refer the reader to there and there.
+For standard 2-categorical material, we refer the reader to e.g. \cite{KS} or \cite{DS} for monoidal structures.
 
 Recall that a pseudofunctor $F\colon\bicat{A}\to\bicat{B}$ between bicategories $\bicat{A}$ and $\bicat{B}$ is functorial up to coherent natural isomorphism, namely for composable arrows we have $F(g\circ f)\cong Fg\circ Ff$ and $F(1_a)\cong1_{Fa}$ satisfying standard axioms.
-Given pseudofunctors $F,G\colon \bicat{A} \to \bicat{B}$, a \define{pseudonatural transformation} $\sigma$ consists of {\chris notation below needs fixing}
+Given pseudofunctors $F,G\colon \bicat{A} \to \bicat{B}$, a \define{pseudonatural transformation} $\sigma$ consists of
 \begin{itemize}
 \item for each object $a \in \bicat{A}$, a morphism $\sigma_a \colon F(a) \to G(a)$ in $\bicat{B}$ 
-\item for every pair of objects $a$ and $b$ of $\mathbf{A}$, we have natural isomorphisms
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$\mathbf{A}(a,b)$};
-\node (B) at (2,0) {$\mathbf{X}(F(a),F(b))$};
-\node (C) at (0,-1) {$\mathbf{X}(G(a),G(b))$};
-\node (D) at (2,-1) {$\mathbf{X}(F(a),G(b))$};
-\node (E) at (1,-0.5) {$\sigma_{a,b} \Nearrow$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$F$} (B)
-(B) edge node[right]{$(\sigma_{b})_*$} (D)
-(A) edge node[left]{$G$} (C)
-(C) edge node[above]{$(\sigma_a)^*$} (D);
-\end{tikzpicture}
-\]
-where $(\sigma_a)^*$ and $(\sigma_b)_*$ are the functors induced by precomposition and postcompositon, respectively.
-Thus for each morphism $f \colon a \to b$ in $\mathbf{A}$, we have an invertible 2-morphism $\sigma_f \colon G(f) \sigma_a \xrightarrow{\sim} \sigma_{b} F(f)$ in $\mathbf{X}$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$F(a)$};
-\node (B) at (1,0) {$F(b)$};
-\node (C) at (0,-1) {$G(a)$};
-\node (D) at (1,-1) {$G(b)$};
-\node (E) at (0.5,-0.5) {$\sigma_f \Nearrow$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$F(f)$} (B)
-(B) edge node[right]{$\sigma_{b}$} (D)
-(A) edge node[left]{$\sigma_a$} (C)
-(C) edge node[above]{$G(f)$} (D);
-\end{tikzpicture}
-\]
-which is compatible with composition and identities.
+\item 
+%for every pair of objects $a$ and $b$ of $\mathbf{A}$, we have natural isomorphisms
+%\[
+%\begin{tikzpicture}[scale=1.5]
+%\node (A) at (0,0) {$\mathbf{A}(a,b)$};
+%\node (B) at (2,0) {$\mathbf{X}(F(a),F(b))$};
+%\node (C) at (0,-1) {$\mathbf{X}(G(a),G(b))$};
+%\node (D) at (2,-1) {$\mathbf{X}(F(a),G(b))$};
+%\node (E) at (1,-0.5) {$\sigma_{a,b} \Nearrow$};
+%\path[->,font=\scriptsize,>=angle 90]
+%(A) edge node[above]{$F$} (B)
+%(B) edge node[right]{$(\sigma_{b})_*$} (D)
+%(A) edge node[left]{$G$} (C)
+%(C) edge node[above]{$(\sigma_a)^*$} (D);
+%\end{tikzpicture}
+%\]
+%where $(\sigma_a)^*$ and $(\sigma_b)_*$ are the functors induced by precomposition and postcompositon, respectively. Thus 
+for each morphism $f \colon a \to b$ in $\mathbf{A}$, an invertible natural 2-morphism $\sigma_f \colon G(f) \sigma_a \xrightarrow{\sim} \sigma_{b} F(f)$ in $\mathbf{B}$
+%:
+%\[
+%\begin{tikzpicture}[scale=1.5]
+%\node (A) at (0,0) {$F(a)$};
+%\node (B) at (1,0) {$F(b)$};
+%\node (C) at (0,-1) {$G(a)$};
+%\node (D) at (1,-1) {$G(b)$};
+%\node (E) at (0.5,-0.5) {$\sigma_f \Nearrow$};
+%\path[->,font=\scriptsize,>=angle 90]
+%(A) edge node[above]{$F(f)$} (B)
+%(B) edge node[right]{$\sigma_{b}$} (D)
+%(A) edge node[left]{$\sigma_a$} (C)
+%(C) edge node[above]{$G(f)$} (D);
+%\end{tikzpicture}
+%\]
+compatible with composition and identities.
 \end{itemize}
@@
 of pseudofunctors, pseudonatural transformations and modifications from an ordinary category $\A$ viewed as a 2-category with trivial 2-cells, into $\bicat{Cat}$.
-Classicaly this has been referred to as the 2-category of \emph{opindexed categories}, since an indexed category is a contravariant pseudofunctor into $\bicat{Cat}$.
-
-A \define{lax monoidal} pseudofunctor is....
-A \define{symmetric lax monoidal} pseudofunctor...
-{\chris Not sure if we need monoidal transformations?}
+This is also referred to as the 2-category of \emph{opindexed categories}, since an indexed category is a contravariant pseudofunctor into $\bicat{Cat}$.
+
+A \define{lax monoidal} pseudofunctor between monoidal bicategories $F\colon\bicat{A}\to\bicat{B}$ is a pseudofunctor equipped with pseudonatural transformations with components $\mu_{a,b}\colon Fa\otimes Fb\to F(a\otimes b)$ and $\mu_0\colon I\to FI$ along with coherent invertible modifications for associativity and unitality.
+This is commonly also called `weak monoida' pseudofunctor.
+A \define{symmetric lax monoidal} pseudofunctor between symmetric monoidal bicategories comes with invertible $F(b)\circ \mu_{a,b}\cong \mu_{b,a}\circ b$, where $b$ is the braiding.
+{\chris Hiding various details under the rug - e.g. what a symmetric monoidal bicategory is. Should be fine? Also, not sure if we need monoidal transformations?}
 
 \subsection{Double categories}\label{sec:doublecats}
-{\chris Moved from earlier, probably merge with what follows}
-Once again following the notation of Shulman \cite{Shul2}, given a double category $\mathbb{A}$, we write $_f \mathbb{A}_g(M,N)$ for the set of 2-morphisms in $\mathbb{A}$ of the form:
-\[
-  \xymatrix@-.5pc{
-    A \ar[r]|{|}^{M}  \ar[d]_f \ar@{}[dr]|{\Downarrow a}&
-    B\ar[d]^g\\
-    C \ar[r]|{|}_N & D
-  }
-\]
-We call $M$ and $N$ the \define{horizontal source and target} of the 2-morphism $a$, respectively, and likewise we call $f$ and $g$ the \define{vertical source and target} of the 2-morphism $a$, respectively.
-Thus $_f \mathbb{A}_g(M,N)$ denotes the set of 2-morphisms in $\mathbb{A}$ with horizontal source and target $M$ and $N$ and vertical source and target $f$ and $g$.
-\begin{defn}
-A (possibly lax or oplax) double functor $\mathbb{F} \colon \mathbb{A} \to \mathbb{X}$ is \define{full} (respectively, \define{faithful}) if $\mathbb{F}_0 \colon \mathbb{A}_0 \to \mathbb{X}_0$ is full (respectively, faithful) and each map $$\mathbb{F}_1 \colon _f \mathbb{A}_g(M,N) \to _{\mathbb{F}(f)} \mathbb{X}_{\mathbb{F}(g)}(\mathbb{F}(M),\mathbb{F}(N))$$ is surjective (respectively, injective).
-\end{defn}
-\begin{defn}
-A (possibly lax or oplax) double functor $\mathbb{F} \colon \mathbb{A} \to \mathbb{X}$ is \define{essentially surjective} if we can simultaneously make the following choices:
-\begin{enumerate}
-\item{For each object $x \in \mathbb{X}$, we can find an object $a \in \mathbb{A}$ together with a vertical 1-isomorphism $\alpha_x \colon \mathbb{F}(a) \to x$, and}
-\item{For each horizontal 1-cell $N \colon x_1 \tobar x_2$  of $\mathbb{X}$, we can find a horizontal 1-cell $M \colon a_1 \tobar a_2$ of $\mathbb{A}$ and a 2-isomorphism $a_{N}$ of $\mathbb{X}$ as in the following diagram:
-\[
-  \xymatrix@-.5pc{
-    \mathbb{F}(a_1) \ar[r]|{|}^{\mathbb{F}(M)}  \ar[d]_{\alpha_{x_1}} \ar@{}[dr]|{\Downarrow a_N}&
-    \mathbb{F}(a_1) \ar[d]^{\alpha_{x_2}}\\
-    x_1 \ar[r]|{|}_N & x_2
-  }
-\]
-}
-\end{enumerate}
-\end{defn}
-\begin{defn}
-A double functor $\mathbb{F} \colon \mathbb{A} \to \mathbb{X}$ is \define{strong} if the comparison and unit constraints are globular isomorphisms, meaning that for each composable pair of horizontal 1-cells $M$ and $N$ we have a natural isomorphism $$\mathbb{F}_{M,N} \colon \mathbb{F}(M) \odot \mathbb{F}(N) \xrightarrow{\sim} \mathbb{F}(M \odot N)$$and for each object $a \in \mathbb{A}$ a natural isomorphism $$\mathbb{F}_a \colon \hat{U}_{\mathbb{F}(a)} \xrightarrow{\sim} \mathbb{F}(U_a).$$
-\end{defn}
-
-Formally, two strong double functors between two double categories form a \emph{double equivalence} if {\chris their two-way composite is isomorphic to the identity, better expressed, possibly in a definition environment}.
-Similarly to ordinary equivalence of categories, {\chris cite shulman's theorem here [Shulman,7.8]} allows us to use the following equivalent characterization.
-
-\begin{thm}\label{ShulDubEquiv}
-A strong double functor $\mathbb{F} \colon \mathbb{A} \to \mathbb{X}$ is part of a double equivalence if and only if it is full, faithful and essentially surjective. {\chris on objects?}
-\end{thm}
-
-\begin{prop}
-Let $\mathbb{A}$ and $\mathbb{X}$ be symmetric monoidal double categories and let $\mathbb{F} \colon \mathbb{A} \to \mathbb{X}$ be a symmetric monoidal strong double functor.
-If $\mathbb{F}$ is part of a double equivalence, then $\mathbb{F}$ is in fact part of a symmetric monoidal double equivalence, and $\mathbb{A}$ and $\mathbb{X}$ are equivalent as symmetric monoidal double categories.
-\end{prop}
-
-{\chris Here ends what I moved}
 
@@
 \end{defn}
+
+\begin{defn}
+Let $\mathbb{A}$ and $\mathbb{B}$ be pseudo double categories.
+A \define{lax double functor} is a functor $\mathbb{F} \colon\mathbb{A}\to \mathbb{B}$ that takes items of $\mathbb{A}$ to items of $\mathbb{B}$ of the corresponding type, respecting vertical composition in the strict sense and the horizontal composition up to an assigned comparison $\phi$.
+This means that we have functors $\mathbb{F}_0 \colon \mathbb{A}_0 \to \mathbb{B}_0$ and $\mathbb{F}_1 \colon \mathbb{A}_1 \to \mathbb{B}_1$ such that the following equations are satisfied: $$S \circ \mathbb{F}_1 = \mathbb{F}_0 \circ S$$ $$T \circ \mathbb{F}_1 = \mathbb{F}_0 \circ T$$ Sometimes for brevity, we will omit the subscripts and simply say $\mathbb{F}$.
+As to whether we mean $\mathbb{F}_0$ or $\mathbb{F}_1$ will be clear from context.
+
+Also, every object $a$ is equipped with a special globular 2-morphism $\phi_{a} \colon 1_{\mathbb{F}(a)} \to \mathbb{F}(1_{a})$ (the identity comparison), and every horizontal composition $N_{1} \odot N_{2}$ is equipped with a special globular 2-morphism $\phi(N_{1},N_{2}) \colon \mathbb{F}(N_{1}) \odot \mathbb{F}(N_{2}) \to \mathbb{F}(N_{1} \odot N_{2})$ (the composition comparison), in a coherent way.
+This means that the following diagrams commute.
+
+\begin{enumerate}
+
+\item For a horizontal composite, $\beta \odot \alpha$,
+
+\begin{equation}\label{eq:square}
+  \xymatrix@-.5pc{
+    \mathbb{F}(A) \ar[r]|{|}^{\mathbb{F}(N_{2})}  \ar[d] \ar@{}[dr]|{\mathbb{F}(\alpha)}&
+    \mathbb{F}(B) \ar[d] \ar[r]|{|}^{\mathbb{F}(N_{1})} \ar@{}[dr]|{\mathbb{F}(\beta)}&
+    \mathbb{F}(C) \ar[d] &
+     &
+    \mathbb{F}(A) \ar[r]|{|}^{\mathbb{F}(N_{2})} \ar@{}[drr]|{\phi(N_{1},N_{2})} \ar[d]_{1} &
+    \mathbb{F}(B) \ar[r]|{|}^{\mathbb{F}(N_{1})} &
+    \mathbb{F}(C) \ar[d]^{1} \\
+    \mathbb{F}(A') \ar[r]|{|}_{\mathbb{F}(N_{4})} \ar@{}[drr]|{\phi(N_{3},N_{4})} \ar[d]_{1}&
+    \mathbb{F}(B') \ar[r]|{|}_{\mathbb{F}(N_{3})} &
+    \mathbb{F}(C') \ar[d]^{1}&
+    = &
+    \mathbb{F}(A) \ar[rr]|{|}^{\mathbb{F}(N_{1} \odot N_{2})} \ar[d] \ar@{}[drr]|{\mathbb{F}(\beta \odot \alpha)}&
+     &
+    \mathbb{F}(C) \ar[d] \\
+    \mathbb{F}(A') \ar[rr]|{|}_{\mathbb{F}(N_{3} \odot N_{4})} & 
+     & 
+    \mathbb{F}(C') &
+     &
+    \mathbb{F}(A') \ar[rr]|{|}_{\mathbb{F}(N_{3} \odot N_{4})} &
+     &
+    \mathbb{F}(C') \\
+  }.
+\end{equation}
+
+\item For a horizontal 1-cell $N \colon A \to B$, the following diagrams are commutative (under horizontal composition).
+
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (1,1) {$\mathbb{F}(N) \odot 1_{\mathbb{F}(A)}$};
+\node (C) at (3,1) {$\mathbb{F}(N)$};
+\node (A') at (1,-1) {$\mathbb{F}(N) \odot \mathbb{F}(1_{A})$};
+\node (C') at (3,-1) {$\mathbb{F}(N \odot 1_{A})$};
+\node (B) at (5,1) {$1_{\mathbb{F}(B)} \odot \mathbb{F}(N)$};
+\node (B') at (5,-1) {$\mathbb{F}(1_{B}) \odot \mathbb{F}(N)$};
+\node (D) at (7,1) {$\mathbb{F}(N)$};
+\node (D') at (7,-1) {$\mathbb{F}(1_{B} \odot N)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[left]{$1 \odot \phi_{A}$} (A')
+(C') edge node[right]{$\mathbb{F} \rho$} (C)
+(A) edge node[above]{$\rho_{\mathbb{F}(N)}$} (C)
+(A') edge node[above]{$\phi(N,1_{A})$} (C')
+(B) edge node[left]{$\phi_{B} \odot 1$} (B')
+(B') edge node[above]{$\phi(1_{B},N)$} (D')
+(B) edge node[above]{$\lambda_{\mathbb{F}(N)}$} (D)
+(D') edge node[right]{$F \lambda$} (D);
+\end{tikzpicture}
+\]
+
+\item For consecutive horizontal 1-cells $N_{1},N_{2}$ and $N_{3}$, the following diagram is commutative.
+
+ \[\xymatrix{
+    (\mathbb{F}(N_{1}) \odot \mathbb{F}(N_{2})) \odot \mathbb{F}(N_{3}) \ar[r]^{a'}\ar[d]_{\phi(N_{1},N_{2}) \odot 1}
+    & \mathbb{F}(N_{1}) \odot (\mathbb{F}(N_{2}) \odot \mathbb{F}(N_{3})) \ar[d]^{1 \odot \phi(N_{2},N_{3})}\\
+    \mathbb{F}(N_{1} \odot N_{2}) \odot \mathbb{F}(N_{3}) \ar[d]_{\phi(N_{1} \odot N_{2},N_{3})} &
+    \mathbb{F}(N_{1}) \odot \mathbb{F}(N_{2} \odot N_{3}) \ar[d]^{\phi(N_{1},N_{2} \odot N_{3})}\\
+    \mathbb{F}((N_{1} \odot N_{2}) \odot N_{3})\ar[r]^{\mathbb{F}a} &
+    \mathbb{F}(N_{1} \odot (N_{2} \odot N_{3}))}\]
+\end{enumerate}
+We say the double functor $\mathbb{F}$ is \define{strict} if the comparison constraints $\phi_a$ and $\phi_{N_1,N_2}$ are identities, \define{pseudo} if the comparison constraints are isomorphisms, and \define{oplax} if the comparison constraints go in the opposite direction.
+\end{defn}
+
+{\chris Pretty sure the def below can be incorporated above, however got a bit lost in different notation. Kenny Fix?}
+\begin{defn}
+A double functor $\mathbb{F} \colon \mathbb{A} \to \mathbb{X}$ is \define{strong} if the comparison and unit constraints are globular isomorphisms, meaning that for each composable pair of horizontal 1-cells $M$ and $N$ we have a natural isomorphism $$\mathbb{F}_{M,N} \colon \mathbb{F}(M) \odot \mathbb{F}(N) \xrightarrow{\sim} \mathbb{F}(M \odot N)$$and for each object $a \in \mathbb{A}$ a natural isomorphism $$\mathbb{F}_a \colon \hat{U}_{\mathbb{F}(a)} \xrightarrow{\sim} \mathbb{F}(U_a).$$
+\end{defn}
+
+Following the notation of Shulman \cite{Shul2}, given a double category $\mathbb{A}$, we write $_f \mathbb{A}_g(M,N)$ for the set of 2-morphisms in $\mathbb{A}$ of the form:
+\[
+  \xymatrix@-.5pc{
+    A \ar[r]|{|}^{M}  \ar[d]_f \ar@{}[dr]|{\Downarrow a}&
+    B\ar[d]^g\\
+    C \ar[r]|{|}_N & D
+  }
+\]
+We call $M$ and $N$ the \define{horizontal source and target} of the 2-morphism $a$, respectively, and likewise we call $f$ and $g$ the \define{vertical source and target} of the 2-morphism $a$, respectively.
+Thus $_f \mathbb{A}_g(M,N)$ denotes the set of 2-morphisms in $\mathbb{A}$ with horizontal source and target $M$ and $N$ and vertical source and target $f$ and $g$.
+\begin{defn}
+A (possibly lax or oplax) double functor $\mathbb{F} \colon \mathbb{A} \to \mathbb{X}$ is \define{full} (respectively, \define{faithful}) if $\mathbb{F}_0 \colon \mathbb{A}_0 \to \mathbb{X}_0$ is full (respectively, faithful) and each map $$\mathbb{F}_1 \colon _f \mathbb{A}_g(M,N) \to _{\mathbb{F}(f)} \mathbb{X}_{\mathbb{F}(g)}(\mathbb{F}(M),\mathbb{F}(N))$$ is surjective (respectively, injective).
+\end{defn}
+\begin{defn}
+A (possibly lax or oplax) double functor $\mathbb{F} \colon \mathbb{A} \to \mathbb{X}$ is \define{essentially surjective} if we can simultaneously make the following choices:
+\begin{enumerate}
+\item{For each object $x \in \mathbb{X}$, we can find an object $a \in \mathbb{A}$ together with a vertical 1-isomorphism $\alpha_x \colon \mathbb{F}(a) \to x$, and}
+\item{For each horizontal 1-cell $N \colon x_1 \tobar x_2$  of $\mathbb{X}$, we can find a horizontal 1-cell $M \colon a_1 \tobar a_2$ of $\mathbb{A}$ and a 2-isomorphism $a_{N}$ of $\mathbb{X}$ as in the following diagram:
+\[
+  \xymatrix@-.5pc{
+    \mathbb{F}(a_1) \ar[r]|{|}^{\mathbb{F}(M)}  \ar[d]_{\alpha_{x_1}} \ar@{}[dr]|{\Downarrow a_N}&
+    \mathbb{F}(a_1) \ar[d]^{\alpha_{x_2}}\\
+    x_1 \ar[r]|{|}_N & x_2
+  }
+\]
+}
+\end{enumerate}
+\end{defn}
+
+Formally, two strong double functors between two double categories form a \emph{double equivalence} if {\chris their two-way composite is isomorphic to the identity, better expressed, possibly in a definition environment}.
+Similarly to ordinary equivalence of categories, {\chris cite shulman's theorem here [Shulman,7.8]} allows us to use the following equivalent characterization.
+
+\begin{thm}\label{ShulDubEquiv}
+A strong double functor $\mathbb{F} \colon \mathbb{A} \to \mathbb{X}$ is part of a double equivalence if and only if it is full, faithful and essentially surjective. {\chris on objects?}
+\end{thm}
+
+\begin{prop}
+Let $\mathbb{A}$ and $\mathbb{X}$ be symmetric monoidal double categories and let $\mathbb{F} \colon \mathbb{A} \to \mathbb{X}$ be a symmetric monoidal strong double functor.
+If $\mathbb{F}$ is part of a double equivalence, then $\mathbb{F}$ is in fact part of a symmetric monoidal double equivalence, and $\mathbb{A}$ and $\mathbb{X}$ are equivalent as symmetric monoidal double categories.
+\end{prop}
 
@@
 \begin{defn}
-Let $\mathbb{A}$ and $\mathbb{B}$ be pseudo double categories.
-A \define{lax double functor} is a functor $\mathbb{F} \colon\mathbb{A}\to \mathbb{B}$ that takes items of $\mathbb{A}$ to items of $\mathbb{B}$ of the corresponding type, respecting vertical composition in the strict sense and the horizontal composition up to an assigned comparison $\phi$.
-This means that we have functors $\mathbb{F}_0 \colon \mathbb{A}_0 \to \mathbb{B}_0$ and $\mathbb{F}_1 \colon \mathbb{A}_1 \to \mathbb{B}_1$ such that the following equations are satisfied: $$S \circ \mathbb{F}_1 = \mathbb{F}_0 \circ S$$ $$T \circ \mathbb{F}_1 = \mathbb{F}_0 \circ T$$ Sometimes for brevity, we will omit the subscripts and simply say $\mathbb{F}$.
-As to whether we mean $\mathbb{F}_0$ or $\mathbb{F}_1$ will be clear from context.
-
-Also, every object $a$ is equipped with a special globular 2-morphism $\phi_{a} \colon 1_{\mathbb{F}(a)} \to \mathbb{F}(1_{a})$ (the identity comparison), and every horizontal composition $N_{1} \odot N_{2}$ is equipped with a special globular 2-morphism $\phi(N_{1},N_{2}) \colon \mathbb{F}(N_{1}) \odot \mathbb{F}(N_{2}) \to \mathbb{F}(N_{1} \odot N_{2})$ (the composition comparison), in a coherent way.
-This means that the following diagrams commute.
-
-\begin{enumerate}
-
-\item For a horizontal composite, $\beta \odot \alpha$,
-
-\begin{equation}\label{eq:square}
-  \xymatrix@-.5pc{
-    \mathbb{F}(A) \ar[r]|{|}^{\mathbb{F}(N_{2})}  \ar[d] \ar@{}[dr]|{\mathbb{F}(\alpha)}&
-    \mathbb{F}(B) \ar[d] \ar[r]|{|}^{\mathbb{F}(N_{1})} \ar@{}[dr]|{\mathbb{F}(\beta)}&
-    \mathbb{F}(C) \ar[d] &
-     &
-    \mathbb{F}(A) \ar[r]|{|}^{\mathbb{F}(N_{2})} \ar@{}[drr]|{\phi(N_{1},N_{2})} \ar[d]_{1} &
-    \mathbb{F}(B) \ar[r]|{|}^{\mathbb{F}(N_{1})} &
-    \mathbb{F}(C) \ar[d]^{1} \\
-    \mathbb{F}(A') \ar[r]|{|}_{\mathbb{F}(N_{4})} \ar@{}[drr]|{\phi(N_{3},N_{4})} \ar[d]_{1}&
-    \mathbb{F}(B') \ar[r]|{|}_{\mathbb{F}(N_{3})} &
-    \mathbb{F}(C') \ar[d]^{1}&
-    = &
-    \mathbb{F}(A) \ar[rr]|{|}^{\mathbb{F}(N_{1} \odot N_{2})} \ar[d] \ar@{}[drr]|{\mathbb{F}(\beta \odot \alpha)}&
-     &
-    \mathbb{F}(C) \ar[d] \\
-    \mathbb{F}(A') \ar[rr]|{|}_{\mathbb{F}(N_{3} \odot N_{4})} & 
-     & 
-    \mathbb{F}(C') &
-     &
-    \mathbb{F}(A') \ar[rr]|{|}_{\mathbb{F}(N_{3} \odot N_{4})} &
-     &
-    \mathbb{F}(C') \\
-  }.
-\end{equation}
-
-\item For a horizontal 1-cell $N \colon A \to B$, the following diagrams are commutative (under horizontal composition).
-
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (1,1) {$\mathbb{F}(N) \odot 1_{\mathbb{F}(A)}$};
-\node (C) at (3,1) {$\mathbb{F}(N)$};
-\node (A') at (1,-1) {$\mathbb{F}(N) \odot \mathbb{F}(1_{A})$};
-\node (C') at (3,-1) {$\mathbb{F}(N \odot 1_{A})$};
-\node (B) at (5,1) {$1_{\mathbb{F}(B)} \odot \mathbb{F}(N)$};
-\node (B') at (5,-1) {$\mathbb{F}(1_{B}) \odot \mathbb{F}(N)$};
-\node (D) at (7,1) {$\mathbb{F}(N)$};
-\node (D') at (7,-1) {$\mathbb{F}(1_{B} \odot N)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[left]{$1 \odot \phi_{A}$} (A')
-(C') edge node[right]{$\mathbb{F} \rho$} (C)
-(A) edge node[above]{$\rho_{\mathbb{F}(N)}$} (C)
-(A') edge node[above]{$\phi(N,1_{A})$} (C')
-(B) edge node[left]{$\phi_{B} \odot 1$} (B')
-(B') edge node[above]{$\phi(1_{B},N)$} (D')
-(B) edge node[above]{$\lambda_{\mathbb{F}(N)}$} (D)
-(D') edge node[right]{$F \lambda$} (D);
-\end{tikzpicture}
-\]
-
-\item For consecutive horizontal 1-cells $N_{1},N_{2}$ and $N_{3}$, the following diagram is commutative.
-
- \[\xymatrix{
-    (\mathbb{F}(N_{1}) \odot \mathbb{F}(N_{2})) \odot \mathbb{F}(N_{3}) \ar[r]^{a'}\ar[d]_{\phi(N_{1},N_{2}) \odot 1}
-    & \mathbb{F}(N_{1}) \odot (\mathbb{F}(N_{2}) \odot \mathbb{F}(N_{3})) \ar[d]^{1 \odot \phi(N_{2},N_{3})}\\
-    \mathbb{F}(N_{1} \odot N_{2}) \odot \mathbb{F}(N_{3}) \ar[d]_{\phi(N_{1} \odot N_{2},N_{3})} &
-    \mathbb{F}(N_{1}) \odot \mathbb{F}(N_{2} \odot N_{3}) \ar[d]^{\phi(N_{1},N_{2} \odot N_{3})}\\
-    \mathbb{F}((N_{1} \odot N_{2}) \odot N_{3})\ar[r]^{\mathbb{F}a} &
-    \mathbb{F}(N_{1} \odot (N_{2} \odot N_{3}))}\]
-\end{enumerate}
-We say the double functor $\mathbb{F}$ is \define{strict} if the comparison constraints $\phi_a$ and $\phi_{N_1,N_2}$ are identities, \define{pseudo} if the comparison constraints are isomorphisms, and \define{oplax} if the comparison constraints go in the opposite direction.
-\end{defn}
-
-\begin{defn}
 \label{defn:monoidal_double_functor}
@@
 
-\bibitem{CourPhD} K.\ Courser, Cospans for Networks, PhD Thesis, University of California at Riverside (2019)
-
+\bibitem{CourPhD} K.\ Courser, Open Systems: a Double Categorical Perspective, PhD Thesis, University of California at Riverside (2019)
+
+\bibitem{DS} B.\ Day and R.\ Street, Monoidal Bicategories and Hopf Algebroids, \emph{Adv. Math.}, 129(1):99--157, 1997.
 %\bibitem{Ehresmann63} C.\ Ehresmann, Cat\'egories structur\'ees III: Quintettes et applications covariantes,  \textsl{Cah.\ Top.\ G\'eom.\ Diff.} \textbf{5} (1963), 1--22.
@@
 \bibitem{JM} J.\ C.\ Baez and J.\ Master, A compositional framework for Petri nets. In preparation.
+
+\bibitem{KS} G.\ Kelly and R.\ Street, Review of the elements of 2-categories, \emph{Lecture Notes in Mathematics} vol. 40, pages 75---103, Springer Berlin/Heidelberg, 1974.
 

### 2019-05-30 EquivCompFrameworks_20180911kc.tex
getting ready for equivalence chapter

@@
 \item {\chris Discuss notation for Decorated and Structured cospan double categories one last time? :)}
-\item {\chris Notation between \cref{Equiv} and \cref{thm:decoratedcospans} right now does not match! Need to fix.}
+\item {\chris Notation between \cref{Equiv} and \cref{thm:decoratedcospans} right now does not match!
+Need to fix.
+Slightly prefer a,b,c for objects of A, then $a'$ and $b'$ for other objects, and x an object of the category F(c) namely the decoration.
+The previously used `d' is slightly confusing around all these a's, b's and c's that are in a different category.
+Also I prefer $a$ and $b$ rather than $a_1$ and $a_2$.}
 %\item {\chris There might be a way to completely hide the details of version 'fibres have, reindexing preserve' if that's what we want to do.}
@@
 Then we obtain an underlying symmetric monoidal bicategory $F \mathbf{Csp}$ using a result of Shulman \cite{Shul} and then finally decategorify the obtained symmetric monoidal bicategory to obtain a symmetric monoidal category $F$Csp which is a generalization of Fong's original decorated cospan category \cite{Fong}.
-The definition of a lax monoidal pseudofunctor is recalled in \cref{sec:2cats}, and the basics of (pseudo) double categories are recalled in \cref{sec:doublecats}.
+The definition of a lax monoidal pseudofunctor is recalled in \cref{sec:2cats}, and the basics of double categories are recalled in \cref{sec:doublecats}.
 
@@
 \section{An equivalence of symmetric monoidal double categories} \label{EquivDoubleCats}
-\begin{comment}
+%\begin{comment}
 
@@
 
-\end{comment}
+%\end{comment}
 

### 2019-05-30 EquivCompFrameworks_20180911kc.tex
why not fibrations in appendix as well?

@@
 \begin{itemize}
+\item {\chris Would a title like `An equivalence of compositional frameworks for networks' or `An equivalence of compositional network frameworks' be more informative?
+Otherwise, compositional framework on its own doesn't say much!}
 \item {\chris Discuss notation for Decorated and Structured cospan double categories one last time? :)}
@@
 
-{\chris moved here preliminary}
-In this section, we recall the double category of \emph{structured cospans}, a formalism introduced to the first two authors.
-One of the main goals of this paper is to provide a double equivalence between this double category and one of \emph{decorated cospans}, described in detail in the subsequent section.
+In \cite{BC2}, the first two authors introduces the symmetric monoidal double category of \emph{structured cospans} as a formalism to capture open networks.
+One of the main goals of this paper is to provide a monoidal double equivalence between this double category and that of \emph{decorated cospans}, described in detail in \cref{DecCospansDoubleCat}.
+Below we recall the double category structured cospans form.
 
 {\chris Wait, why do you need to consider them as monoidal in the assumptions of the theorem?}
-
 \begin{thm}\label{SC}
 Given a category $\mathsf{X}$ with finite colimits and a category $\mathsf{A}$ with finite coproducts and a finite coproduct preserving functor $L \colon \mathsf{A} \to \mathsf{X}$ with $\mathsf{A}$ and $\mathsf{X}$ regarded as cocartesian monoidal categories, there exists a symmetric monoidal double category $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$ which has:
-\begin{enumerate}
+\begin{itemize}
 \item{objects given by objects of $\mathsf{A}$,}
 \item{vertical 1-morphisms given by morphisms of $\mathsf{A}$,}
-\item{horizontal 1-cells given by cospans of $\mathsf{X}$ of the form:
+\item{horizontal 1-cells $a\tickar b$ given by cospans of $\mathsf{X}$ of the form:
 \begin{equation}\label{eq:structuredcospan}
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$L(c)$};
+\node (A) at (0,0) {$L(a)$};
 \node (B) at (1,0) {$x$};
-\node (C) at (2,0) {$L(c^\prime)$};
+\node (C) at (2,0) {$L(b)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \end{tikzpicture}
-\end{equation}
-and}
-\item{2-morphisms given by maps of cospans of $\mathsf{X}$ of the form:
+\end{equation}}
+\item 2-morphisms given by maps of cospans of $\mathsf{X}$ of the form:
 \begin{equation}\label{eq:2cellsStrCsp}
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$L(c_1)$};
+\node (A) at (0,0) {$L(a)$};
 \node (B) at (1,0) {$x$};
-\node (C) at (2,0) {$L(c_2)$};
-\node (A') at (0,-1) {$L(c_1^\prime)$};
-\node (B') at (1,-1) {$x^\prime$};
-\node (C') at (2,-1) {$L(c_2^\prime)$};
+\node (C) at (2,0) {$L(b)$};
+\node (A') at (0,-1) {$L(a')$};
+\node (B') at (1,-1) {$x'$};
+\node (C') at (2,-1) {$L(b')$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (B) edge node [left]{$\alpha$} (B')
-(C) edge node [left]{$L(g)$} (C');
+(C) edge node [right]{$L(g)$} (C');
 \end{tikzpicture}
 \end{equation}
+\end{itemize}
 Composition of horizontal 1-cells and 2-morphisms is given by pushouts in $\mathsf{X}$ and tensoring of objects is under binary coproducts in $\mathsf{A}$.
-}
-\end{enumerate}
 \end{thm}
@@
 \end{proof}
-{\chris Below, I commented out a nice short recalled version of decorated cospans, since now their definition is later. Use if we want to recall at some point later}
-%In the previous section, we started with a symmetric lax monoidal pseudofunctor $F \colon \mathsf{A} \to \mathbf{Cat}$ and created a symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$ which has:
-%\begin{enumerate}
-%\item{objects of $\mathsf{A}$ as objects,}
-%\item{morphisms of $\mathsf{A}$ as vertical 1-morphisms,}
-%\item{horizontal 1-cells are given by $F$-decorated cospans, which are pairs:
-%\[
-%\begin{tikzpicture}[scale=1.5]
-%\node (A) at (0,0) {$c_1$};
-%\node (B) at (1,0) {$c$};
-%\node (C) at (2,0) {$c_2$};
-%\node (D) at (3,0) {$x \in F(c)$};
-%\path[->,font=\scriptsize,>=angle 90]
-%(A) edge node[above]{$i$} (B)
-%(C) edge node[above]{$o$} (B);
-%\end{tikzpicture}
-%\]
-%and}
-%\item{2-morphisms are given by maps of cospans in $\mathsf{A}$:
-%\[
-%\begin{tikzpicture}[scale=1.5]
-%\node (A) at (0,0) {$c_1$};
-%\node (B) at (1,0) {$c$};
-%\node (C) at (2,0) {$c_2$};
-%\node (A') at (0,-1) {$c_1^\prime$};
-%\node (B') at (1,-1) {$c^\prime$};
-%\node (C') at (2,-1) {$c_2^\prime$};
-%\node (D) at (3,0) {$x \in F(c)$};
-%\node (D') at (3,-1) {$x^\prime \in F(c^\prime)$};
-%\path[->,font=\scriptsize,>=angle 90]
-%(A) edge node[above]{$i$} (B)
-%(C) edge node[above]{$o$} (B)
-%(A') edge node[above]{$i^\prime$} (B')
-%(C') edge node[above]{$o^\prime$} (B')
-%(A) edge node [left]{$f$} (A')
-%(B) edge node [left]{$h$} (B')
-%(C) edge node [left]{$g$} (C');
-%\end{tikzpicture}
-%\]
-%together with a morphism $\iota \colon F(h)(d) \to d^\prime$ in $F(c^\prime)$.}
-%\end{enumerate}
-
-{\chris here ends old}
-
-In this section we prove that the two different double categorical network frameworks, namely structured cospans and decorated cospans described respectively in \cref{DecCospansDoubleCat,sec:structuredcospans}, are equivalent under certain assumptions.
-This is established by \cref{Equiv}, which relies on conditions relevant to the existence of left adjoints for opfibrations.
-We begin by sketching this underlying framework, which is worked out in detail in \cite{MV} and \cite{CV}.
-%In this section we investigate the necessary conditions to obtain a category $\mathrm{X}$ and a left adjoint $L \colon \mathrm{A} \to \mathrm{X}$ from a category $\mathrm{A}$ with finite colimits and a symmetric lax monoidal pseudofunctor $F \colon \mathrm{A} \to \mathbf{Cat}$.
-The main tool that allows us to do this will be the Grothendieck construction which we recall:
-First of all, we recall some basics regarding opfibrations and their relation to pseudofunctors into $\bicat{Cat}$ via the Grothendieck construction.
-Standard material on the theory of fibrations can be found for example in \cite{Herm}, \cite{Borc}.
-
-A functor $U \maps \X \to \A$ is a \textbf{Grothendieck opfibration} if for every $x\in\X$ with $U(x)=a$ and $f \colon a \to b$ in $\A$, there exists a \textbf{cocartesian lifting} of $x$ along $f$, namely a morphism $\beta$ in $\X$ with domain $x$ above $f$ with the following universal property: for any $g\colon b\to b'$ in $\A$ and $\gamma\colon x\to y'$ in $\X$ above the composite $g\circ f$, there exists a unique $\delta\colon y\to y'$ such that $U(\delta)=g$ and $\gamma=\delta\circ\beta$ as shown below
-\begin{displaymath}
-\xymatrix @R=.1in @C=.6in
-{&& y'\ar @{.>}@/_/[dd] &&\\
-x\ar[r]_-{\beta} \ar @{.>}@/_/[dd]
-\ar[urr]^-{\gamma} & 
-y \ar @{.>}@/_/[dd] \ar @{-->}[ur]_-{\exists! \delta}
-&& \textrm{in }\X\\
-&& b' &&\\
-a\ar[r]_-{f=U\beta} \ar[urr]^-{g\circ f=U\gamma}
- & b \ar[ur]_-g && \textrm{in }\A}
-\end{displaymath}
-
-%\begin{defn}
-%Let $P \colon \ca{X} \to \ca{A}$ be a functor.
-A morphism $f \colon d_{1} \to d_{2}$ in the category $\mathrm{D}$ is \textbf{cocartesian (with respect to the functor P)} if for any object $d^\prime$ in $\mathrm{D}$ and morphism $g \colon d_{1} \to d^\prime$ and every $p \colon P(d_{2}) \to P(d^\prime)$ such that $P(g)=p P(f)$, there exists a unique $h \colon d_{2} \to d^\prime$ such that $g=hf$ and $p=P(h)$.
-%\[
-%\begin{tikzpicture}[scale=1.5]
-%\node (A) at (0,0) {$d^\prime$};
-%\node (B) at (0,-1) {$d_{2}$};
-%\node (C) at (1.5,-1) {$d_{1}$};
-%\node (H) at (2,-0.25) {$P$};
-%\node (D) at (2,-.5) {$\mapsto$};
-%\node (E) at (3,0) {$P(d^\prime)$};
-%\node (F) at (3,-1) {$P(d_{2})$};
-%\node (G) at (4.5,-1) {$P(d_{1})$};
-%\path[->,font=\scriptsize,>=angle 90]
-%(B) edge[dashed] node[above,left]{$\exists ! h$} (A)
-%(C) edge node[above,right]{$g$} (A)
-%(F) edge node[above,left]{$p=P(h)$} (E)
-%(G) edge node[above]{$P(f)$} (F)
-%(G) edge node[above,right]{$P(g)$} (E)
-%(C)edge node[above]{$f$}(B);
-%\end{tikzpicture}
-%\]
-%\end{defn}
-%\begin{defn}
-%A functor $P \colon \mathrm{D} \to \mathrm{A}$ is a \textbf{(Grothendieck) opfibration} if for any object $d$ in $\mathbf{D}$ and morphism $f \colon c %\to P(d)$ there exists a cocartesian morphism $\phi \colon d^\prime \to d$ such that $P(\phi)=f$.
-%\end{defn}
-%\begin{defn}
-%Let $P \colon \mathrm{D} \to \mathrm{A}$ and $P^\prime \colon \mathrm{D^\prime} \to \mathrm{A}$ be opfibrations over a category $\mathrm{A}$.
-A \define{morphism of opfibrations} is a functor $F \colon \mathrm{D} \to \mathrm{D}^\prime$ such that $F(p)$ is cocartesian with respect to $P^\prime$ if $p$ is cocartesian with respect to $P$ and $P=P^\prime F$.
-%\end{defn}
-The category $\X$ is called the \textbf{total} category and $\A$ is called the \textbf{base} category of the opfibration.
-For any $a\in\A$, the \textbf{fibre category} $\X_a$ consists of all objects that map to $a$ and vertical morphisms between them, i.e.
-mapping to $1_a$.
-Assuming the axiom of choice, we may select a cocartesian arrow over each $f\maps a\to b$ in $\A$ and $x\in\X _a$, denoted by $\mathrm{Cocart}(f,x)\maps x\to f_!(x)$, rendering $U$ a so-called \textbf{cloven} opfibration.
-This choice induces \textbf{reindexing functors} $f_!\colon\X _a\to\X _b$ between the fibre categories, which by the liftings universal property adhere to natural $(1_a)_!\cong1_{\X _a}$ and $(f\circ g)_!\cong f_!\circ g_!$.
-If these isomorphisms are equalities, we have the notion of a \textbf{split} opfibration.
-%Christina: decide later if needed
-%Notice that as a result,
-%any arrow in the total category of an opfibration factorizes uniquely into a vertical morphism (above the identity) followed by a (co)cartesian one:
-%\[
-%\xymatrix @C=.4in @R=.2in
-%{x \ar @{.>}[dd]\ar[rr]^\gamma \ar[drr]_-{\Cocart(g,C)} && D &\\
-%&& f_!C \ar @{-->}[u]_-{\delta} \ar @{.>}[d] & \textrm{in }\C  \\
-%X\ar[rr]_-{g} && Y & \textrm{in }\X.}
-%\]
-
-Let $\OpFib(\A)$ denote the 2-subcategory of the slice 2-category $\mathbf{Cat}/ \A$ of opfibrations over $\A$, functors that preserve cocartesian liftings and natural transformations with vertical components.
-In fact, there is a 2-equivalence between opfibrations and pseudofunctors, see Section ?, induced by the so-called \emph{Grothendieck construction}.
-%{\chris I don't mind this presentation of the Grothendieck construction which I admit not having seeing before.
-If we are to keep, we should put a reference.
-Otherwise we could stay more low level about this and just briefly describe what's going on.}
-%\begin{defn}
-%Let $\mathbf{Cat}_{\textnormal{lax},\star}$ denote the \define{2-category of lax-pointed categories} which has:
-%\begin{enumerate}
-%\item{objects as pairs $(\mathrm{A},c)$ where $\mathrm{A}$ is a category and $c$ is an object of $\mathrm{A}$, and}
-%\item{a morphism from $(\mathrm{A},c)$ to $(\mathrm{X},y)$ is a pair $(F,f)$ where $F \colon \mathrm{A} \to \mathrm{X}$ is a functor and $f \colon F(c) \to y$ is a morphism in $\mathrm{X}$.}
-%\end{enumerate}
-%\end{defn}
-%\begin{defn}
-%Given a pseudofunctor $F \colon \mathrm{A} \to \mathbf{Cat}$, the \define{Grothendieck construction of} $F$ is given by the `strict 2-pullback' of the following cospan:
-% \[
-%\begin{tikzpicture}[scale=1.5]
-%\node (D) at (1,1) {$\inta F$};
-%\node (A) at (0,0) {$\mathrm{A}$};
-%\node (B) at (1,-1) {$\mathbf{Cat}$};
-%\node (C) at (2,0) {$\mathbf{Cat}_{\textnormal{lax},\star}$};
-%\path[->,font=\scriptsize,>=angle 90]
-%(D) edge[dashed] node[above]{$p$} (A)
-%(D) edge[dashed] node[above]{$q$} (C)
-%(A) edge node[below]{$F$} (B)
-%(C) edge node[below]{$P$} (B);
-%\end{tikzpicture}
-%\]
-%where $P \colon \mathbf{Cat}_{\textnormal{lax},\star} \to \mathbf{Cat}$ is the forgetful functor. 
-\begin{defn}\label{def:GrothCat}
-For any pseudofunctor $F\colon\A\to\bicat{Cat}$ where $\A$ is a category viewed as a 2-category with trivial 2-cells, the \textbf{Grothendieck category}
-$\inta F$ has
-\begin{itemize}
-\item objects pairs $(a, x \in F(a))$ and
-\item a morphism from $(a, x \in F(a))$ to $(b, y\in F(b))$ is a pair $(f \colon a \to b,\delta \colon F(f)(x) \to y)\in\A\times F(b)$.
-\end{itemize}
-{\chris Might need to write the composition rule? Depending on the final proof of Big Theorem.}
-This is an opfibred category over $\A$ via the obvious forgetful functor, with fibre categories $(\inta F)_a=F(a)$ and reindexing functors $f_!=F(f)$.
-\end{defn}
-%This can also be thought of as a morphism and a 2-morphism:
-%\[
-%\begin{tikzpicture}[scale=1.5]
-%\node (A) at (0,0) {$\star$};
-%\node (B) at (1,0.5) {$F(c)$};
-%\node (C) at (1,-0.5) {$F(c^\prime)$};
-%\node (D) at (2,0.5) {$c$};
-%\node (E) at (2,-0.5) {$c^\prime$};
-%\node (F) at (0.65,0) {$\Swarrow \alpha$};
-%\path[->,font=\scriptsize,>=angle 90]
-%(A) edge node[above]{$d$} (B)
-%(B) edge node[right]{$F(f)$} (C)
-%(A) edge node[below]{$d^\prime$} (C)
-%(D) edge node[left] {$f$} (E);
-%\end{tikzpicture}
-%\]
-The above in fact provides the one direction of the following well-known equivalence.
-%gives rise to a 2-functor $[\A,\bicat{Cat}]_\pse\to \mathbf{Cat}/ \A$ which factors through the embedding $\OpFib(\A) \hookrightarrow \bicat{Cat} / \A$ as per the following theorem.
-%: $$\inta F \colon [ \mathrm{A}, \mathbf{Cat} ] \to \textnormal{Opfib}(\mathrm{A}) \hookrightarrow \mathbf{Cat} / \mathrm{A}.$$
-
-\begin{thm}\label{thm:Grothendieck}\hfill
-    \begin{enumerate}
-        \item Every opfibration $\U \maps \X \to \A$ gives rise to a pseudofunctor $F_U \maps \A \to \bicat{Cat}$.
-        \item Every pseudofunctor $F \maps \A \to \bicat{Cat}$ gives rise to  an opfibration $\U_F \colon \inta F\to\A$.
-        \item The above correspondences yield an equivalence of 2-categories 
-        \begin{displaymath}
-            [\A,\bicat{Cat}]_\pse \simeq \OpFib(\A)
-        \end{displaymath}
-        so that $F_{\U_F} \cong F$ and $\U_{F_\U} \cong \U$.
-%        \item The above 2-equivalence extends to one between 2-categories of arbitrary-base fibrations and arbitrary-domain indexed categories
-%        \begin{equation}\label{eq:Gr_equiv}
-%        \ICat\simeq\Fib    
-%        \end{equation}
-    \end{enumerate}
+
+The desired equivalence between these two different double categorical network frameworks, namely structured cospans and decorated cospans,
+is established by the following theorem. We denote by $\bicat{fcocCat}$ the 2-category of finitely cocomplete categories and finitely cocontinuous functors.
+
+\begin{thm}\label{Equiv}
+Suppose $\ca{A}$ is a finitely cocomplete category and $(F,\phi,\phi_0)\colon(\ca{A},+,0) \to (\bicat{Cat},\times,\mathbf{1})$ is a symmetric lax monoidal pseudofunctor, which factors through $\bicat{fcocCat}$ as an ordinary pseudofunctor.
+Then the symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$ of decorated cospans (\cref{thm:decoratedcospans}) is equivalent to the symmetric monoidal double category $\scsp{L_F}{\inta F}$ of structured cospans (\cref{SC}), where $L_F \colon \mathsf{A} \to \inta{F}$ is the left adjoint of the induced Grothendieck opfibration $\U_F\colon \inta{F} \to \mathsf{A}$.
+%by \cref{thm:Grothendieck},
+%under the assumptions of \cref{cor:fcocMonGroth}.
 \end{thm}
 
-%\begin{defn}
-%Let $P \colon \mathbf{D} \to \mathrm{A}$ be a functor.
-A morphism $f \colon d_{1} \to d_{2}$ in the category $\mathbf{D}$ is \textbf{cartesian (with respect to the functor P)} if for any object $d^\prime$ in $\mathbf{D}$ and morphism $g \colon d^\prime \to d_{2}$ and every $p \colon P(d^\prime) \to P(d_{1})$ such that $P(g)=P(f)p$, there exists a unique $h \colon d^\prime \to d_{1}$ such that $g=fh$ and $p=P(h)$.
-%\[
-%\begin{tikzpicture}[scale=1.5]
-%\node (A) at (0,0) {$d^\prime$};
-%\node (B) at (0,-1.5) {$d_{1}$};
-%\node (C) at (1.5,-1.5) {$d_{2}$};
-%\node (H) at (2,-0.5) {$P$};
-%\node (D) at (2,-.75) {$\mapsto$};
-%\node (E) at (3,0) {$P(d^\prime)$};
-%\node (F) at (3,-1.5) {$P(d_{1})$};
-%\node (G) at (4.5,-1.5) {$P(d_{2})$};
-%\path[->,font=\scriptsize,>=angle 90]
-%(A) edge[dashed] node[above,left]{$\exists ! h$} (B)
-%(A) edge node[above]{$g$} (C)
-%(E) edge node[above,left]{$p=P(h)$} (F)
-%(F) edge node[above]{$P(f)$} (G)
-%(E) edge node[above,right]{$P(g)$} (G)
-%(B)edge node[above]{$f$}(C);
-%\end{tikzpicture}
-%\]
-%\end{defn}
+The conditions of the above theorem relate to the existence of left adjoints for opfibrations; we first sketch this underlying framework, and then we proceed to the proof of the theorem.
 
@@
 
-\begin{thm}\label{Equiv}
-Suppose $\ca{A}$ is a finitely cocomplete category and $(F,\phi,\phi_0)\colon(\ca{A},+,0) \to (\bicat{Cat},\times,\mathbf{1})$ is a symmetric lax monoidal pseudofunctor.
-%such that as an ordinary pseudofunctor, it factors through $\bicat{fcocCat}$.
-Then the symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$ of decorated cospans (\cref{thm:decoratedcospans}) is equivalent to the symmetric monoidal double category $\scsp{L_F}{\inta F}$ of structured cospans (\cref{SC}), where $L_F \colon \mathsf{A} \to \inta{F}$ is the left adjoint of the induced Grothendieck opfibration $\U_F\colon \inta{F} \to \mathsf{A}$ %by \cref{thm:Grothendieck},
-under the assumptions of \cref{cor:fcocMonGroth}.
-\end{thm}
-
-\begin{proof}
+\begin{proof}[Proof of \cref{Equiv}]
 Recall that the double category of decorated cospans $\dcsp{F}$ has objects and vertical 1-morphisms those of $\A$, horizontal 1-cells $a\tickar b$ are cospans $\cspn{a}{c}{b}{}{}$ in $\A$ along with $x\in F(c)$, and 2-morphisms are cospan maps $k\colon c\to c'$ together with a morphism $(Fk)(x)\to x'$, see \cref{eq:FCsp2morph}.
@@
 
+\subsection{Fibrations}\label{sec:fibrations}
+We now recall some basics regarding opfibrations and their relation to pseudofunctors into $\bicat{Cat}$ via the Grothendieck construction.
+Standard material on the theory of fibrations can be found for example in \cite{Herm}, \cite{Borc}.
+
+A functor $U \maps \X \to \A$ is a \textbf{Grothendieck opfibration} if for every $x\in\X$ with $U(x)=a$ and $f \colon a \to b$ in $\A$, there exists a \textbf{cocartesian lifting} of $x$ along $f$, namely a morphism $\beta$ in $\X$ with domain $x$ above $f$ with the following universal property: for any $g\colon b\to b'$ in $\A$ and $\gamma\colon x\to y'$ in $\X$ above the composite $g\circ f$, there exists a unique $\delta\colon y\to y'$ such that $U(\delta)=g$ and $\gamma=\delta\circ\beta$ as shown below
+\begin{displaymath}
+\xymatrix @R=.1in @C=.6in
+{&& y'\ar @{.>}@/_/[dd] &&\\
+x\ar[r]_-{\beta} \ar @{.>}@/_/[dd]
+\ar[urr]^-{\gamma} & 
+y \ar @{.>}@/_/[dd] \ar @{-->}[ur]_-{\exists! \delta}
+&& \textrm{in }\X\\
+&& b' &&\\
+a\ar[r]_-{f=U\beta} \ar[urr]^-{g\circ f=U\gamma}
+ & b \ar[ur]_-g && \textrm{in }\A}
+\end{displaymath}
+
+%\begin{defn}
+%Let $P \colon \ca{X} \to \ca{A}$ be a functor.
+A morphism $f \colon d_{1} \to d_{2}$ in the category $\mathrm{D}$ is \textbf{cocartesian (with respect to the functor P)} if for any object $d^\prime$ in $\mathrm{D}$ and morphism $g \colon d_{1} \to d^\prime$ and every $p \colon P(d_{2}) \to P(d^\prime)$ such that $P(g)=p P(f)$, there exists a unique $h \colon d_{2} \to d^\prime$ such that $g=hf$ and $p=P(h)$.
+%\[
+%\begin{tikzpicture}[scale=1.5]
+%\node (A) at (0,0) {$d^\prime$};
+%\node (B) at (0,-1) {$d_{2}$};
+%\node (C) at (1.5,-1) {$d_{1}$};
+%\node (H) at (2,-0.25) {$P$};
+%\node (D) at (2,-.5) {$\mapsto$};
+%\node (E) at (3,0) {$P(d^\prime)$};
+%\node (F) at (3,-1) {$P(d_{2})$};
+%\node (G) at (4.5,-1) {$P(d_{1})$};
+%\path[->,font=\scriptsize,>=angle 90]
+%(B) edge[dashed] node[above,left]{$\exists ! h$} (A)
+%(C) edge node[above,right]{$g$} (A)
+%(F) edge node[above,left]{$p=P(h)$} (E)
+%(G) edge node[above]{$P(f)$} (F)
+%(G) edge node[above,right]{$P(g)$} (E)
+%(C)edge node[above]{$f$}(B);
+%\end{tikzpicture}
+%\]
+%\end{defn}
+%\begin{defn}
+%A functor $P \colon \mathrm{D} \to \mathrm{A}$ is a \textbf{(Grothendieck) opfibration} if for any object $d$ in $\mathbf{D}$ and morphism $f \colon c %\to P(d)$ there exists a cocartesian morphism $\phi \colon d^\prime \to d$ such that $P(\phi)=f$.
+%\end{defn}
+%\begin{defn}
+%Let $P \colon \mathrm{D} \to \mathrm{A}$ and $P^\prime \colon \mathrm{D^\prime} \to \mathrm{A}$ be opfibrations over a category $\mathrm{A}$.
+A \define{morphism of opfibrations} is a functor $F \colon \mathrm{D} \to \mathrm{D}^\prime$ such that $F(p)$ is cocartesian with respect to $P^\prime$ if $p$ is cocartesian with respect to $P$ and $P=P^\prime F$.
+%\end{defn}
+The category $\X$ is called the \textbf{total} category and $\A$ is called the \textbf{base} category of the opfibration.
+For any $a\in\A$, the \textbf{fibre category} $\X_a$ consists of all objects that map to $a$ and vertical morphisms between them, i.e.
+mapping to $1_a$.
+Assuming the axiom of choice, we may select a cocartesian arrow over each $f\maps a\to b$ in $\A$ and $x\in\X _a$, denoted by $\mathrm{Cocart}(f,x)\maps x\to f_!(x)$, rendering $U$ a so-called \textbf{cloven} opfibration.
+This choice induces \textbf{reindexing functors} $f_!\colon\X _a\to\X _b$ between the fibre categories, which by the liftings universal property adhere to natural $(1_a)_!\cong1_{\X _a}$ and $(f\circ g)_!\cong f_!\circ g_!$.
+If these isomorphisms are equalities, we have the notion of a \textbf{split} opfibration.
+%Christina: decide later if needed
+%Notice that as a result,
+%any arrow in the total category of an opfibration factorizes uniquely into a vertical morphism (above the identity) followed by a (co)cartesian one:
+%\[
+%\xymatrix @C=.4in @R=.2in
+%{x \ar @{.>}[dd]\ar[rr]^\gamma \ar[drr]_-{\Cocart(g,C)} && D &\\
+%&& f_!C \ar @{-->}[u]_-{\delta} \ar @{.>}[d] & \textrm{in }\C  \\
+%X\ar[rr]_-{g} && Y & \textrm{in }\X.}
+%\]
+
+Let $\OpFib(\A)$ denote the 2-subcategory of the slice 2-category $\mathbf{Cat}/ \A$ of opfibrations over $\A$, functors that preserve cocartesian liftings and natural transformations with vertical components.
+In fact, there is a 2-equivalence between opfibrations and pseudofunctors induced by the so-called \emph{Grothendieck construction}.
+%{\chris I don't mind this presentation of the Grothendieck construction which I admit not having seeing before.
+If we are to keep, we should put a reference.
+Otherwise we could stay more low level about this and just briefly describe what's going on.}
+%\begin{defn}
+%Let $\mathbf{Cat}_{\textnormal{lax},\star}$ denote the \define{2-category of lax-pointed categories} which has:
+%\begin{enumerate}
+%\item{objects as pairs $(\mathrm{A},c)$ where $\mathrm{A}$ is a category and $c$ is an object of $\mathrm{A}$, and}
+%\item{a morphism from $(\mathrm{A},c)$ to $(\mathrm{X},y)$ is a pair $(F,f)$ where $F \colon \mathrm{A} \to \mathrm{X}$ is a functor and $f \colon F(c) \to y$ is a morphism in $\mathrm{X}$.}
+%\end{enumerate}
+%\end{defn}
+%\begin{defn}
+%Given a pseudofunctor $F \colon \mathrm{A} \to \mathbf{Cat}$, the \define{Grothendieck construction of} $F$ is given by the `strict 2-pullback' of the following cospan:
+% \[
+%\begin{tikzpicture}[scale=1.5]
+%\node (D) at (1,1) {$\inta F$};
+%\node (A) at (0,0) {$\mathrm{A}$};
+%\node (B) at (1,-1) {$\mathbf{Cat}$};
+%\node (C) at (2,0) {$\mathbf{Cat}_{\textnormal{lax},\star}$};
+%\path[->,font=\scriptsize,>=angle 90]
+%(D) edge[dashed] node[above]{$p$} (A)
+%(D) edge[dashed] node[above]{$q$} (C)
+%(A) edge node[below]{$F$} (B)
+%(C) edge node[below]{$P$} (B);
+%\end{tikzpicture}
+%\]
+%where $P \colon \mathbf{Cat}_{\textnormal{lax},\star} \to \mathbf{Cat}$ is the forgetful functor. 
+\begin{defn}\label{def:GrothCat}
+For any pseudofunctor $F\colon\A\to\bicat{Cat}$ where $\A$ is a category viewed as a 2-category with trivial 2-cells, the \textbf{Grothendieck category}
+$\inta F$ has
+\begin{itemize}
+\item objects pairs $(a, x \in F(a))$ and
+\item a morphism from $(a, x \in F(a))$ to $(b, y\in F(b))$ is a pair $(f \colon a \to b,\delta \colon F(f)(x) \to y)\in\A\times F(b)$.
+\end{itemize}
+{\chris Might need to write the composition rule? Depending on the final proof of Big Theorem.}
+This is an opfibred category over $\A$ via the obvious forgetful functor, with fibre categories $(\inta F)_a=F(a)$ and reindexing functors $f_!=F(f)$.
+\end{defn}
+%This can also be thought of as a morphism and a 2-morphism:
+%\[
+%\begin{tikzpicture}[scale=1.5]
+%\node (A) at (0,0) {$\star$};
+%\node (B) at (1,0.5) {$F(c)$};
+%\node (C) at (1,-0.5) {$F(c^\prime)$};
+%\node (D) at (2,0.5) {$c$};
+%\node (E) at (2,-0.5) {$c^\prime$};
+%\node (F) at (0.65,0) {$\Swarrow \alpha$};
+%\path[->,font=\scriptsize,>=angle 90]
+%(A) edge node[above]{$d$} (B)
+%(B) edge node[right]{$F(f)$} (C)
+%(A) edge node[below]{$d^\prime$} (C)
+%(D) edge node[left] {$f$} (E);
+%\end{tikzpicture}
+%\]
+The above in fact provides the one direction of the following well-known equivalence.
+%gives rise to a 2-functor $[\A,\bicat{Cat}]_\pse\to \mathbf{Cat}/ \A$ which factors through the embedding $\OpFib(\A) \hookrightarrow \bicat{Cat} / \A$ as per the following theorem.
+%: $$\inta F \colon [ \mathrm{A}, \mathbf{Cat} ] \to \textnormal{Opfib}(\mathrm{A}) \hookrightarrow \mathbf{Cat} / \mathrm{A}.$$
+
+\begin{thm}\label{thm:Grothendieck}\hfill
+    \begin{enumerate}
+        \item Every opfibration $\U \maps \X \to \A$ gives rise to a pseudofunctor $F_U \maps \A \to \bicat{Cat}$.
+        \item Every pseudofunctor $F \maps \A \to \bicat{Cat}$ gives rise to  an opfibration $\U_F \colon \inta F\to\A$.
+        \item The above correspondences yield an equivalence of 2-categories 
+        \begin{displaymath}
+            [\A,\bicat{Cat}]_\pse \simeq \OpFib(\A)
+        \end{displaymath}
+        so that $F_{\U_F} \cong F$ and $\U_{F_\U} \cong \U$.
+%        \item The above 2-equivalence extends to one between 2-categories of arbitrary-base fibrations and arbitrary-domain indexed categories
+%        \begin{equation}\label{eq:Gr_equiv}
+%        \ICat\simeq\Fib    
+%        \end{equation}
+    \end{enumerate}
+\end{thm}
+
+%\begin{defn}
+%Let $P \colon \mathbf{D} \to \mathrm{A}$ be a functor.
+A morphism $f \colon d_{1} \to d_{2}$ in the category $\mathbf{D}$ is \textbf{cartesian (with respect to the functor P)} if for any object $d^\prime$ in $\mathbf{D}$ and morphism $g \colon d^\prime \to d_{2}$ and every $p \colon P(d^\prime) \to P(d_{1})$ such that $P(g)=P(f)p$, there exists a unique $h \colon d^\prime \to d_{1}$ such that $g=fh$ and $p=P(h)$.
+%\[
+%\begin{tikzpicture}[scale=1.5]
+%\node (A) at (0,0) {$d^\prime$};
+%\node (B) at (0,-1.5) {$d_{1}$};
+%\node (C) at (1.5,-1.5) {$d_{2}$};
+%\node (H) at (2,-0.5) {$P$};
+%\node (D) at (2,-.75) {$\mapsto$};
+%\node (E) at (3,0) {$P(d^\prime)$};
+%\node (F) at (3,-1.5) {$P(d_{1})$};
+%\node (G) at (4.5,-1.5) {$P(d_{2})$};
+%\path[->,font=\scriptsize,>=angle 90]
+%(A) edge[dashed] node[above,left]{$\exists ! h$} (B)
+%(A) edge node[above]{$g$} (C)
+%(E) edge node[above,left]{$p=P(h)$} (F)
+%(F) edge node[above]{$P(f)$} (G)
+%(E) edge node[above,right]{$P(g)$} (G)
+%(B)edge node[above]{$f$}(C);
+%\end{tikzpicture}
+%\]
+%\end{defn}
+
 \subsection{Double categories}\label{sec:doublecats}

### 2019-05-30 EquivCompFrameworks_20180911kc.tex
polished until proof

@@
 
-In \cite{MV}, the Grothendieck construction is generalized to the monoidal setting, namely lax monoidal structures on a pseudofunctor $F\colon\A\to\bicat{Cat}$ bijectively correspond to monoidal structures on the total category $\inta F$ such that the induced opfibration is a strict monoidal functor and $\otimes_{\inta F}$ preserves liftings, see \cite[Thm.
+The basics of fibration theory needed for our purposes are recalled in \cref{sec:fibrations}. 
+In \cite{MV}, the classic Grothendieck construction is generalized to the monoidal setting: lax monoidal structures on a pseudofunctor $F\colon\A\to\bicat{Cat}$ bijectively correspond to monoidal structures on the total category $\inta F$ such that the induced opfibration is a strict monoidal functor and $\otimes_{\inta F}$ preserves liftings, see \cite[Thm.
 3.10]{MV}.
-If the monoidal category $\A$ is in fact cocartesian, there is a further correspondence of the two structures with an ordinary pseudofunctor $F\colon\A\to\bicat{MonCat}$ into the 2-category of monoidal categories, strong monoidal functors and monoidal natural transformations:
+If the monoidal category $\A$ is in fact cocartesian, there is a further correspondence of the two structures with an ordinary pseudofunctor $F\colon\A\to\bicat{MonCat}$ into the 2-category of monoidal categories, strong monoidal functors and monoidal natural transformations, summarized as
 \begin{gather}
@@
 
-Finally, if that pseudofunctor is lax monoidal $(F,\phi,\phi_0)\colon(\A,+,0)\to(\bicat{Cat},\times,\mathbf{1})$ to begin with, the monoidal Grothendieck construction in the cocartesian case discussed earlier (\cref{eq:explicitstructure1}) expresses $\bot_a$ as the image of the composite
+Finally, if that pseudofunctor is lax monoidal $(F,\phi,\phi_0)\colon(\A,+,0)\to(\bicat{Cat},\times,\mathbf{1})$ to begin with, the monoidal Grothendieck construction in the cocartesian case discussed earlier \cref{eq:explicitstructure1} expresses $\bot_a$ as the image of the composite
 \begin{equation}\label{eq:initialinfibre}
@@
 
-We have now laid all the necessary background to formally establish an equivalence between the double category of decorated cospans and the double category of structured cospans, constructed from a symmetric lax monoidal pseudofunctor into $\bicat{Cat}$.
+We have now laid all the necessary background to formally construct an equivalence between the double category of decorated cospans and the double category of structured cospans, constructed from a symmetric lax monoidal pseudofunctor into $\bicat{Cat}$.
 
@@
 \subsection{Fibrations}\label{sec:fibrations}
-We now recall some basics regarding opfibrations and their relation to pseudofunctors into $\bicat{Cat}$ via the Grothendieck construction.
+We recall some basics regarding opfibrations and their relation to pseudofunctors into $\bicat{Cat}$ via the Grothendieck construction.
 Standard material on the theory of fibrations can be found for example in \cite{Herm}, \cite{Borc}.

### 2019-06-04 EquivCompFrameworks.tex
new improved version

--- 2019-05-30 EquivCompFrameworks_20180911kc.tex
@@
 The square commutativities translate to $k\circ i=i'\circ f$ and $k\circ o=o'\circ g$ in $\A$, and also by composition in the Grothendieck category, to
-\begin{gather*}
+\begin{gather}\label{eq:Grothcommutativity}
  F(k\circ i)(\bot_a)\cong Fk(Fi(\bot_a))\xrightarrow{Fk(!)}Fk(x)\xrightarrow{\iota}x'= \\
- F(i'\circ f)(\bot_a)\cong Fi'(Ff(\bot_a))\xrightarrow{Fi'(\chi_a)}Fi'(\bot_{a'})\xrightarrow{!}x'
-\end{gather*}
+ F(i'\circ f)(\bot_a)\cong Fi'(Ff(\bot_a))\xrightarrow{Fi'(\chi_a)}Fi'(\bot_{a'})\xrightarrow{!}x'\nonumber
+\end{gather}
 in the category $F(c')$.
-However, since all maps are unique in the above equality {\chris discuss with John and Kenny}, this gives no extra conditions for the morphisms involved, and similarly for the equality including $o, o'$.
+However, since all maps are unique in the above equality, emanating from initial objects (since reindexing functors preserve those), this gives no extra conditions for the morphisms involved; similarly for the equality including $o, o'$.
 
@@
 \end{displaymath}
- in $\A$ along with the map $h\colon Fk(x)\to x'$ in $F(c')$, namely a decorated cospan 2-morphism as per \cref{eq:FCsp2morph}.
-
-{\chris Now the checking of the equivalence should follow! perhaps in less detail than currently?}
+ in $\A$ along with the map $\iota\colon Fk(x)\to x'$ in $F(c')$, namely a decorated cospan 2-morphism as per \cref{eq:FCsp2morph}.
+Once again, this is a bijective correspondence since, as discussed above, the commutativity \cref{eq:Grothcommutativity} holds automatically by initiality of the domain.
+ {\chris Christina commented out big chunks of proof. They are right below if we want to revive parts of them, if we think the reader needs deeper level of detail.}
+
+\begin{comment}
 which is a cospan in $\mathsf{X}$ of the form:
@@
 \textbf{At least in my favorite example...}
-
-Next we show that the double functor $\mathbb{E}$ is strong by exhibiting a natural isomorphism $$\mathbb{E}_{M,N} \colon \mathbb{E}(M) \odot \mathbb{E}(N) \xrightarrow{\sim} \mathbb{E}(M \odot N)$$ for every pair of composable horizontal 1-cells $M$ and $N$ of $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$ and for each object $c \in { _L \mathbb{C}\textnormal{sp}(\mathsf{X})}$ a natural isomorphism $$\mathbb{E}_c \colon \hat{U}_{\mathbb{E}(c)} \xrightarrow{\sim} \mathbb{E}(U_c)$$ where $U$ and $\hat{U}$ are the unit structure functors of $_L \mathbb{C} \textnormal{sp}(\mathsf{X})$ and $F\mathbb{C}\textnormal{sp}$, respectively.
+\end{comment}
+Functoriality of $\mathbb{E}_1$ can be verified, and moreover $(\mathbb{E}_0,\mathbb{E}_1)$ indeed define a strong double functor: there exist natural isomorphisms
+\begin{gather*}
+ \mathbb{E}(M) \odot \mathbb{E}(N) \xrightarrow{\sim} \mathbb{E}(M \odot N) \\
+U_{\mathbb{E}(c,x)} \xrightarrow{\sim} \mathbb{E}(U_{(c,x)})
+\end{gather*}
+for any pair of composable horizontal 1-cells $M$ and $N$ and any object $(c,x)$ of $\scsp{L_F}{\inta F}$
+{\chris in progress}
+
 For any object $c$, the horizontal 1-cell $\hat{U}_{\mathbb{E}(c)}$ is given by $\hat{U}_c$ which is given by the pair:
@@
 Lastly, this map of cospans comes with an isomorphism $$\iota \colon F(\sigma)(d_{\mathbb{E}(M) \odot \mathbb{E}(N)}) \to d_{\mathbb{E}(M \odot N)}$$ in $F(R(x+_{L(c_2)}x^\prime))$.
-This shows that $\mathbb{E}$ is strong, and so $\mathbb{E} \colon _L \mathbb{C}\textnormal{sp}(\mathsf{X}) \xrightarrow{\sim} F\mathbb{C}\textnormal{sp}$ is part of a double equivalence by Theorem \ref{ShulDubEquiv}.
+This shows that $\mathbb{E}$ is strong, and so
+
+{\chris Up to here}
+
+Based on the above description of its mapping, it follows that the strong double functor $\mathbb{E}=(\mathbb{E}_0,\mathbb{E}_1)$ is full, faithful and essentially surjective on objects as per \cref{def:fullfaithful,def:essentiallysurj}.
+Therefore $\mathbb{E} \colon \scsp{L_F}{\inta F} \to \dcsp{F}$ is a double equivalence, by \cref{ShulDubEquiv}.
+{\chris In fact, Christina and Kenny believe it is an isomorphism of double categories! Bijective on all levels of objects and morphisms...should we say?}
 
@@
 The isomorphisms $\delta$ and $\mu$ satisfy the left and right unitality squares, associativity hexagon and braiding square.
-\textbf{Kenny: I think this might be a good place to cut the monoidal stuff.} To see this, let $M_1,M_2$ and $M_3$ be horizontal 1-cells in $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$ given by:
+\textbf{Kenny: I think this might be a good place to cut the monoidal stuff.}{\chris Deal!
+They are right below.}
+
+\begin{comment}
+To see this, let $M_1,M_2$ and $M_3$ be horizontal 1-cells in $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$ given by:
 \[
@@
 Thus the double functor $\mathbb{E} \colon _L\mathbb{C}\textnormal{sp}(\mathsf{X}) \to F\mathbb{C}\textnormal{sp}$ is symmetric monoidal.
+\end{comment}
+
 \end{proof}
+
 Using a result of Shulman \cite{Shul}, each of the isofibrant symmetric monoidal double categories $F\mathbb{C}\textnormal{sp}$ and $_L \mathbb{C}\textnormal{sp}(\mathrm{X})$ give rise to underlying symmetric monoidal bicategories, namely $F\mathbb{C}\textnormal{sp}$ induces a symmetric monoidal bicategory $F\mathbf{Csp} \coloneqq H(F\mathbb{C}\textnormal{sp})$ which has:
@@
 Thus $_f \mathbb{A}_g(M,N)$ denotes the set of 2-morphisms in $\mathbb{A}$ with horizontal source and target $M$ and $N$ and vertical source and target $f$ and $g$.
-\begin{defn}
+\begin{defn}\label{def:fullfaithful}
 A (possibly lax or oplax) double functor $\mathbb{F} \colon \mathbb{A} \to \mathbb{X}$ is \define{full} (respectively, \define{faithful}) if $\mathbb{F}_0 \colon \mathbb{A}_0 \to \mathbb{X}_0$ is full (respectively, faithful) and each map $$\mathbb{F}_1 \colon _f \mathbb{A}_g(M,N) \to _{\mathbb{F}(f)} \mathbb{X}_{\mathbb{F}(g)}(\mathbb{F}(M),\mathbb{F}(N))$$ is surjective (respectively, injective).
 \end{defn}
-\begin{defn}
+\begin{defn}\label{def:essentiallysurj}
 A (possibly lax or oplax) double functor $\mathbb{F} \colon \mathbb{A} \to \mathbb{X}$ is \define{essentially surjective} if we can simultaneously make the following choices:

### 2019-06-14 cospans.tex
new title
tiny small edits notation

--- 2019-06-04 EquivCompFrameworks.tex
@@
-% An equivalence of compositional frameworks
+% Structured and decorated cospans
 % John Baez, Kenny Courser and Christina Vasilakopoulou
@@
 
-\title{An equivalence of compositional frameworks}
+\title{Structured and decorated cospans}
 
@@
 \begin{itemize}
-\item {\chris Would a title like `An equivalence of compositional frameworks for networks' or `An equivalence of compositional network frameworks' be more informative?
-Otherwise, compositional framework on its own doesn't say much!}
-\item {\chris Discuss notation for Decorated and Structured cospan double categories one last time? :)}
 \item {\chris Notation between \cref{Equiv} and \cref{thm:decoratedcospans} right now does not match!
@@
 Also I prefer $a$ and $b$ rather than $a_1$ and $a_2$.}
+
+{\chris After a brief discussion in John's office, for \cref{Equiv} I used $a,b,c$ for the feet and $m,n$ for the apices so we can serially compose. Of course can change as we like.}
 %\item {\chris There might be a way to completely hide the details of version 'fibres have, reindexing preserve' if that's what we want to do.}
+
 \end{itemize}
@@
 \begin{proof}[Proof of \cref{Equiv}]
-Recall that the double category of decorated cospans $\dcsp{F}$ has objects and vertical 1-morphisms those of $\A$, horizontal 1-cells $a\tickar b$ are cospans $\cspn{a}{c}{b}{}{}$ in $\A$ along with $x\in F(c)$, and 2-morphisms are cospan maps $k\colon c\to c'$ together with a morphism $(Fk)(x)\to x'$, see \cref{eq:FCsp2morph}.
+Recall that the double category of decorated cospans $\dcsp{F}$ has objects and vertical 1-morphisms those of $\A$, horizontal 1-cells $a\tickar b$ are cospans $\cspn{a}{m}{b}{}{}$ in $\A$ along with $x\in F(m)$, and 2-morphisms are cospan maps $k\colon m\to m'$ together with a morphism $(Fk)(x)\to x'$, see \cref{eq:FCsp2morph}.
 
@@
 \begin{equation}\label{eq:scsphor1cell}
- (a,\bot_a)\xrightarrow{\scalebox{0.7}{$\begin{cases}i\colon a\to c &\textrm{in }\A \\!\colon F(i)(\bot_a)\to x &\textrm{in }F(c)\end{cases}$}}(c,x)\xleftarrow{\scalebox{0.7}{$\begin{cases}o\colon b\to c &\textrm{in }\A \\!\colon F(o)(\bot_b)\to x &\textrm{in }F(c)\end{cases}$}}(b,\bot_b)
+ (a,\bot_a)\xrightarrow{\scalebox{0.7}{$\begin{cases}i\colon a\to m &\textrm{in }\A \\!\colon F(i)(\bot_a)\to x &\textrm{in }F(m)\end{cases}$}}(m,x)\xleftarrow{\scalebox{0.7}{$\begin{cases}o\colon b\to m &\textrm{in }\A \\!\colon F(o)(\bot_b)\to x &\textrm{in }F(m)\end{cases}$}}(b,\bot_b)
 \end{equation}
-where $x\in F(c)$, according to \cref{def:GrothCat}. Finally, the 2-morphisms in this double category are as described in \cref{eq:2cellsStrCsp}, in this context fully unravelled below:
+where $x\in F(m)$, according to \cref{def:GrothCat}. Finally, the 2-morphisms in this double category are as described in \cref{eq:2cellsStrCsp}, in this context fully unravelled below:
 \begin{displaymath}
  \begin{tikzcd}[sep=1.5in,ampersand replacement=\&]
- (a,\bot_a)\ar[r,"{\begin{cases}i\colon a\to c &\textrm{in }\A \\!\colon F(i)(\bot_a)\to x &\textrm{in }F(c)\end{cases}}"]\ar[d,"{\begin{cases}f\colon a\to a' &\textrm{in }\A \\\chi_a\colon F(f)(\bot_a)\cong \bot_{a'} &\textrm{in }F(a')\end{cases}}"description] \& (c,x) \ar[d,"{\begin{cases}k\colon c\to c' &\textrm{in }\A \\ \iota\colon F(k)(x)\to x' &\textrm{in }F(c')\end{cases}}"description] \& (b,\bot_b)\ar[l,"{\begin{cases}o\colon b\to c &\textrm{in }\A \\!\colon F(o)(\bot_b)\to x &\textrm{in }F(c)\end{cases}}"']\ar[d,"{\begin{cases}g\colon b\to b' &\textrm{in }\A \\\chi_b\colon F(g)(\bot_b)\cong \bot_{b'} &\textrm{in }F(b')\end{cases}}"description] \\
- (a',\bot_{a'})\ar[r,"{\begin{cases}i'\colon a'\to c' &\textrm{in }\A \\!\colon F(i')(\bot_{a'})\to x' &\textrm{in }F(c')\end{cases}}"'] \& (c',x') \& (b',\bot_{b'})\ar[l,"{\begin{cases}o'\colon b'\to c' &\textrm{in }\A \\!\colon F(o')(\bot_{b'})\to x' &\textrm{in }F(c')\end{cases}}"]
+ (a,\bot_a)\ar[r,"{\begin{cases}i\colon a\to m &\textrm{in }\A \\!\colon F(i)(\bot_a)\to x &\textrm{in }F(m)\end{cases}}"]\ar[d,"{\begin{cases}f\colon a\to a' &\textrm{in }\A \\\chi_a\colon F(f)(\bot_a)\cong \bot_{a'} &\textrm{in }F(a')\end{cases}}"description] \& (m,x) \ar[d,"{\begin{cases}k\colon m\to m' &\textrm{in }\A \\ \iota\colon F(k)(x)\to x' &\textrm{in }F(m')\end{cases}}"description] \& (b,\bot_b)\ar[l,"{\begin{cases}o\colon b\to m &\textrm{in }\A \\!\colon F(o)(\bot_b)\to x &\textrm{in }F(m)\end{cases}}"']\ar[d,"{\begin{cases}g\colon b\to b' &\textrm{in }\A \\\chi_b\colon F(g)(\bot_b)\cong \bot_{b'} &\textrm{in }F(b')\end{cases}}"description] \\
+ (a',\bot_{a'})\ar[r,"{\begin{cases}i'\colon a'\to m' &\textrm{in }\A \\!\colon F(i')(\bot_{a'})\to x' &\textrm{in }F(m')\end{cases}}"'] \& (m',x') \& (b',\bot_{b'})\ar[l,"{\begin{cases}o'\colon b'\to m' &\textrm{in }\A \\!\colon F(o')(\bot_{b'})\to x' &\textrm{in }F(m')\end{cases}}"]
  \end{tikzcd}
@@
 \end{gather}
-in the category $F(c')$.
+in the category $F(m')$.
 However, since all maps are unique in the above equality, emanating from initial objects (since reindexing functors preserve those), this gives no extra conditions for the morphisms involved; similarly for the equality including $o, o'$.
@@
 \begin{displaymath}
- a\xrightarrow{\; i \;}c\xleftarrow{\; o \;}b\;\textrm{ with decoration }x\in F(c)
+ a\xrightarrow{\; i \;}m\xleftarrow{\; o \;}b\;\textrm{ with decoration }x\in F(m)
 \end{displaymath}
@@
  \begin{tikzcd}
-a\ar[r,"i"]\ar[d,"f"'] & c\ar[d,"k"] & b\ar[l,"o"']\ar[d,"g"] \\
-a'\ar[r,"i'"']& c' & b'\ar[l,"o'"]
+a\ar[r,"i"]\ar[d,"f"'] & m\ar[d,"k"] & b\ar[l,"o"']\ar[d,"g"] \\
+a'\ar[r,"i'"']& m' & b'\ar[l,"o'"]
  \end{tikzcd}
 \end{displaymath}
- in $\A$ along with the map $\iota\colon Fk(x)\to x'$ in $F(c')$, namely a decorated cospan 2-morphism as per \cref{eq:FCsp2morph}.
+ in $\A$ along with the map $\iota\colon Fk(x)\to x'$ in $F(m')$, namely a decorated cospan 2-morphism as per \cref{eq:FCsp2morph}.
 Once again, this is a bijective correspondence since, as discussed above, the commutativity \cref{eq:Grothcommutativity} holds automatically by initiality of the domain.
@@
  \mathbb{E}(M) \odot \mathbb{E}(N) \xrightarrow{\sim} \mathbb{E}(M \odot N) \\
-U_{\mathbb{E}(c,x)} \xrightarrow{\sim} \mathbb{E}(U_{(c,x)})
+U_{\mathbb{E}(m,x)} \xrightarrow{\sim} \mathbb{E}(U_{(m,x)})
 \end{gather*}
-for any pair of composable horizontal 1-cells $M$ and $N$ and any object $(c,x)$ of $\scsp{L_F}{\inta F}$
+for any pair of composable horizontal 1-cells $M$ and $N$ and any object $(m,x)$ of $\scsp{L_F}{\inta F}$
 {\chris in progress}

### 2019-06-14 cospans.tex
adequately completed required parts of proof in the new approach. Leaving soon!

@@
 the composite $N \odot M$ is given by:
-\[
+\begin{equation}\label{eq:dcospanscomposition}
 \begin{tikzpicture}[scale=1.5]
@@
 \end{tikzpicture}
-\]
+\end{equation}
 with the corresponding decoration of the apex $\hat{d} \in F(b+_{a_2} b^\prime)$ given by:
@@
 Once again, this is a bijective correspondence since, as discussed above, the commutativity \cref{eq:Grothcommutativity} holds automatically by initiality of the domain.
- {\chris Christina commented out big chunks of proof. They are right below if we want to revive parts of them, if we think the reader needs deeper level of detail.}
+ {\chris Christina commented out big chunks of proof.
+They are right below if we want to revive parts of them, if we think the reader needs deeper level of detail.
+The idea is that the above description suffices as fully faithful and essentially surjective evidence, but perhaps we would like to spell that out more.
+On to strongness next.}
 
@@
  \mathbb{E}(M) \odot \mathbb{E}(N) \xrightarrow{\sim} \mathbb{E}(M \odot N) \\
-U_{\mathbb{E}(m,x)} \xrightarrow{\sim} \mathbb{E}(U_{(m,x)})
+U_{\mathbb{E}m} \xrightarrow{\sim} \mathbb{E}(U_m)
 \end{gather*}
-for any pair of composable horizontal 1-cells $M$ and $N$ and any object $(m,x)$ of $\scsp{L_F}{\inta F}$
-{\chris in progress}
+for any pair of composable horizontal 1-cells $M=\cspn{(a,\bot_a)}{(m,x)}{(b,\bot_b)}{}{}$ and $N=\cspn{(b,\bot_b)}{(n,y)}{(c,\bot_c)}{}{}$ and any object $m$ of $\scsp{L_F}{\inta F}$.
+In more detail, $\mathbb{E}(M)\odot \mathbb{E}(N)$ is given as in \cref{eq:dcospanscomposition} via the pushout cospan and decoration
+\begin{displaymath}
+ \begin{tikzcd}
+  & m+_bn & \\
+  a\ar[ur,"j_m\circ i"] && b,\ar[ul,"j_n\circ o"']
+ \end{tikzcd}
+ \begin{tikzcd}
+  1\ar[r,"x\times y"]\ar[drr,dashed] & F(m)\times F(n)\ar[r,"\phi_{m,n}"] & F(m+ n)\ar[d,"F(j)"] \\ 
+  && F(m+_b n)
+ \end{tikzcd}
+\end{displaymath}
+where $j_m, j_n$ denote the maps into a pushout.
+On the other hand, first composing $M$ and $N$ in the Grothendieck category $\scsp{L_F}{\inta F}$ using fibrewise pushouts constructed using \cref{lem:fibrewiselimits} ({\chris I could make this specific construction into a lemma earlier if you want, I have it in my notes}) produces
+\begin{displaymath}
+ \begin{tikzcd}
+ && (m+_b n,F(j_m)x+_{\bot_{m+_bn}}F(j_n)y) && \\
+ & (m,x) \ar[ur] && (n,y)\ar[ul] \\
+ (a,\bot_a)\ar[ur] && (b,\bot_b)\ar[ur]\ar[ul] && (c,\bot_c)\ar[ul]
+ \end{tikzcd}
+\end{displaymath}
+which is mapped, under $\mathbb{E}$, to precisely the cospan $\cspn{a}{m+_bn}{b}{}{}$ as above, and the decorations are the same {\chris isomorphic would be enough but they look equal to me!} due to the following commutative diagram
+\begin{displaymath}
+ \begin{tikzcd}
+F(m)\times F(n)\ar[rr,"\phi"]\ar[d,"F(j_m)\times F(j_n)"'] && F(m+n)\ar[d,"F(j)"] \\
+F(m+_bn)\times F(m+_bn)\ar[r,"\phi"] & F((m+_bn)+(m+_bn))\ar[r,"F\nabla"] & F(m+_bn)
+ \end{tikzcd}
+\end{displaymath}
+since taking a pushout over an initial object is really a coproduct, and the fibrewise coproduct in $F(m+_bn)$ is given as in \cref{eq:explicitstructure1}.
+
+Regarding the identity morphisms, $U_m$ is $\cspn{(m,\bot_m)}{(m,\bot_m)}{(m,\bot_m)}{}{}$ with $1_m$ as the $A$-component of the morphisms and isomorphisms between initial objects in the fibres.
+Thus $\mathbb{E}(U_m)$ is the identity cospan in $A$ together with the `initial decoration' $\bot_m\in F(m)$, whereas $U_{\mathbb{E}(m)}$ is exactly the same thing.
+
+{\chris Below, up to my next comment, is Kenny's earlier proof on the same thing.}
 
@@
 
-{\chris Up to here}
+{\chris Up to here was Kenny's strong functoriality.}
 
@@
 {\chris In fact, Christina and Kenny believe it is an isomorphism of double categories! Bijective on all levels of objects and morphisms...should we say?}
+
+{\chris Have not edited below, but everything should be fine up to notation changes. Happy to do if needed in the future.}
 

### 2019-06-15 cospans.tex
changed some notation in Theorem 2.1

@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a_1$};
-\node (B) at (1,0) {$b$};
-\node (C) at (2,0) {$a_2$};
-\node (D) at (3,0) {$d \in F(b)$};
+\node (A) at (0,0) {$a$};
+\node (B) at (1,0) {$m$};
+\node (C) at (2,0) {$b$};
+\node (D) at (3,0) {$x \in F(m)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$a_1$};
-\node (A') at (0,-0.5) {$a_1^\prime$};
-\node (B) at (1,0.5) {$b$};
-\node (C) at (2,0.5) {$a_2$};
-\node (C') at (2,-0.5) {$a_2^\prime$};
-\node (D) at (1,-0.5) {$b^\prime$};
-\node (E) at (3,0.5) {$d \in F(b)$};
-\node (F) at (3,-0.5) {$d^\prime \in F(b^\prime)$};
+\node (A) at (0,0.5) {$a$};
+\node (A') at (0,-0.5) {$a'$};
+\node (B) at (1,0.5) {$m$};
+\node (C) at (2,0.5) {$b$};
+\node (C') at (2,-0.5) {$b'$};
+\node (D) at (1,-0.5) {$m'$};
+\node (E) at (3,0.5) {$x \in F(m)$};
+\node (F) at (3,-0.5) {$x' \in F(m')$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (A) edge node[left]{$f$} (A')
-(C) edge node[left]{$g$} (C')
+(C) edge node[right]{$g$} (C')
 (A') edge node[above] {$i'$} (D)
@@
 \end{equation}
-together with a morphism $\iota \colon F(h)(d) \to d^\prime$ in $F(b^\prime)$.}
+together with a morphism $\iota \colon F(h)(m) \to m^\prime$ in $F(m^\prime)$.}
 \end{enumerate}
@@
 \textbf{Kenny: We should try to make this theorem shorter.} {\chris I agree!}
+\textbf{Kenny: On second thought, I'm not sure what we can cut out of this theorem. We're already saying "the standard monoidal category diagrams are satisfied" rather than displaying them.}
 \begin{proof}
@@
 \]
-where $!_a \in F(a)$ is the trivial decoration on $a$ given by the composition of the unique map $F(!) \colon F(0) \to F(a)$ and the morphism $\phi \colon 1 \to F(0)$  which comes from the structure of the lax monoidal pseudofunctor $F \colon \mathsf{A} \to \mathbf{Cat}$.
+where $!_a \in F(a)$ is the trivial decoration on $a$ given by the composite of the unique map $F(!) \colon F(0) \to F(a)$ and the morphism $\phi \colon 1 \to F(0)$  which comes from the structure of the lax monoidal pseudofunctor $F \colon \mathsf{A} \to \mathbf{Cat}$.
 For morphisms, the structure functor $U$ is defined as:
@@
 (A) edge node[left]{$f$} (A')
-(C) edge node[left]{$f$} (C')
+(C) edge node[right]{$f$} (C')
 (A') edge node[above] {$1$} (D)
@@
 \]
-is the object $a_1$ in $\mathsf{A}$ and the source of the 2-morphism
+is the object $a$ in $\mathsf{A}$ and the source of the 2-morphism
 \[
@@
 \node (A') at (0,-0.5) {$a^\prime$};
-\node (B) at (1,0.5) {$b$};
-\node (C) at (2,0.5) {$a_2$};
-\node (C') at (2,-0.5) {$a_2^\prime$};
-\node (D) at (1,-0.5) {$b^\prime$};
-\node (E) at (3,0.5) {$d \in F(b)$};
-\node (F) at (3,-0.5) {$d^\prime \in F(b^\prime)$};
+\node (B) at (1,0.5) {$m$};
+\node (C) at (2,0.5) {$b$};
+\node (C') at (2,-0.5) {$b^\prime$};
+\node (D) at (1,-0.5) {$m^\prime$};
+\node (E) at (3,0.5) {$x \in F(m)$};
+\node (F) at (3,-0.5) {$x^\prime \in F(m^\prime)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-$$\iota \colon F(h)(d) \to d^\prime$$
+$$\iota \colon F(h)(m) \to m^\prime$$
 is the source of the underlying map of cospans in $\mathsf{A}$, namely the morphism $f$ in $\mathsf{A}$; the target structure functor is defined similarly.
-These structure functors satisfy the equations $$SU(a)=1(a)=TU(a)$$for all objects $a$ of $\mathsf{A}$.
+These structure functors satisfy the equations $$SU(a)=\id_a=TU(a)$$for all objects $a$ of $\mathsf{A}$.
 
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a_1$};
-\node (B) at (1,0) {$b$};
-\node (C) at (2,0) {$a_2$};
-\node (D) at (1,-0.5) {$d \in F(b)$};
-\node (E) at (3,0) {$a_2$};
-\node (F) at (4,0) {$b^\prime$};
-\node (G) at (5,0) {$a_3$};
-\node (H) at (4,-0.5) {$d^\prime \in F(b^\prime)$};
+\node (A) at (0,0) {$a$};
+\node (B) at (1,0) {$m$};
+\node (C) at (2,0) {$b$};
+\node (D) at (1,-0.5) {$x \in F(m)$};
+\node (E) at (3,0) {$b$};
+\node (F) at (4,0) {$n$};
+\node (G) at (5,0) {$c$};
+\node (H) at (4,-0.5) {$y \in F(n)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a_1$};
-\node (B) at (1,1) {$b$};
-\node (C) at (2,0) {$a_2$};
-\node (D) at (3,1) {$b^\prime$};
-\node (E) at (4,0) {$a_3$};
-\node (F) at (2,2) {$b+b^\prime$};
-\node (G) at (2,3) {$b+_{a_2} b^\prime$};
+\node (A) at (0,0) {$a$};
+\node (B) at (1,1) {$m$};
+\node (C) at (2,0) {$b$};
+\node (D) at (3,1) {$n$};
+\node (E) at (4,0) {$c$};
+\node (F) at (2,2) {$m+n$};
+\node (G) at (2,3) {$m+_{b} n$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \end{equation}
-with the corresponding decoration of the apex $\hat{d} \in F(b+_{a_2} b^\prime)$ given by:
-$$1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{d \times d^\prime} F(b) \times F(b^\prime) \xrightarrow{\phi_{b,b^\prime}} F(b+b^\prime) \xrightarrow{F(\psi)} F(b+_{a_2}b^\prime)$$
-where $\psi \colon b + b^\prime \to b+_{a_2} b^\prime$ is the natural map from the coproduct to the pushout and $\phi_{b,b^\prime} \colon F(b) \times F(b^\prime) \to F(b+b^\prime)$ is the natural transformation coming from the structure of the lax monoidal pseudofunctor $F \colon \mathsf{A} \to \mathbf{Cat}$.
+with the corresponding decoration of the apex $x \odot y \in F(m+_{b} n)$ given by:
+$$1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{x \times y} F(m) \times F(n) \xrightarrow{\phi_{m,n}} F(m+n) \xrightarrow{F(\psi)} F(m+_{b}n)$$
+where $\psi \colon m + n \to m+_{b} n$ is the natural map from the coproduct to the pushout and $\phi_{m,n} \colon F(m) \times F(n) \to F(m+n)$ is the natural transformation coming from the structure of the lax monoidal pseudofunctor $F \colon \mathsf{A} \to \mathbf{Cat}$.
 Denoting the first and second of these horizontal 1-cells as $M$ and $N$, respectively, the source and target structure functors satisfy the equations $S(N \odot M)=S(M)$ and $T(N \odot M)=T(N)$.
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a_1$};
-\node (B) at (1,0) {$b$};
-\node (C) at (2,0) {$a_2$};
-\node (D) at (1,-0.5) {$d_{M_1} \in F(b)$};
-\node (E) at (3,0) {$a_2$};
-\node (F) at (4,0) {$b^\prime$};
-\node (G) at (5,0) {$a_3$};
-\node (H) at (4,-0.5) {$d_{M_2} \in F(b^\prime)$};
-\node (I) at (6,0) {$a_3$};
-\node (J) at (7,0) {$b''$};
-\node (K) at (8,0) {$a_4$};
-\node (L) at (7,-0.5) {$d_{M_3} \in F(b'')$};
+\node (A) at (0,0) {$a$};
+\node (B) at (1,0) {$m_1$};
+\node (C) at (2,0) {$b$};
+\node (D) at (1,-0.5) {$x \in F(m_1)$};
+\node (E) at (3,0) {$b$};
+\node (F) at (4,0) {$m_2$};
+\node (G) at (5,0) {$c$};
+\node (H) at (4,-0.5) {$x_2 \in F(m_2)$};
+\node (I) at (6,0) {$c$};
+\node (J) at (7,0) {$m_3$};
+\node (K) at (8,0) {$d$};
+\node (L) at (7,-0.5) {$x_3 \in F(m_3)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$a_1$};
-\node (A') at (0,-0.5) {$a_1$};
-\node (B) at (1.5,0.5) {$(b+_{a_2} b^\prime)+_{a_3} b''$};
-\node (C) at (3,0.5) {$a_4$};
-\node (C') at (3,-0.5) {$a_4$};
-\node (D) at (1.5,-0.5) {$b+_{a_2}(b^\prime +_{a_3} b'')$};
-\node (E) at (5.5,0.5) {$d_{(M_1 \odot M_2) \odot M_3} \in F((b+_{a_2} b^\prime)+_{a_3} b'')$};
-\node (F) at (5.5,-0.5) {$d_{M_1 \odot (M_2 \odot M_3)} \in F(b+_{a_2} (b^\prime +_{a_3} b''))$};
+\node (A) at (0,0.5) {$a$};
+\node (A') at (0,-0.5) {$a$};
+\node (B) at (1.5,0.5) {$(m_1+_{b} m_2)+_{c} m_3$};
+\node (C) at (3,0.5) {$d$};
+\node (C') at (3,-0.5) {$d$};
+\node (D) at (1.5,-0.5) {$m_1+_{b}(m_2 +_{c} m_3)$};
+\node (E) at (5.5,0.5) {$(x \odot y) \odot z \in F((m_1+_{b} m_2)+_{c} m_3)$};
+\node (F) at (5.5,-0.5) {$x \odot (y \odot z) \in F(m_1+_{b} (m_2 +_{c} m_3))$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (C) edge node[above]{$$} (B)
-(A) edge node[left]{$1$} (A')
-(C) edge node[left]{$1$} (C')
+(A) edge node[left]{$\id_a$} (A')
+(C) edge node[right]{$\id_d$} (C')
 (A') edge node {$$} (D)
 (C') edge node {$$} (D)
-(B) edge node [left] {$a$} (D);
+(B) edge node [left] {$\sigma$} (D);
 \end{tikzpicture}
@@
 with the decorations on the cospan's apices given by:
-$$ d_{(M_1 \odot M_2) \odot M_3} \coloneqq 1 \xrightarrow{\zeta_1} F(b+_{a_2} b^\prime) \times F(b'') \xrightarrow{\phi_{b+_{a_2} b^\prime, b''}} F((b+_{a_2}b^\prime) +b'') \xrightarrow{F(j_{b+_{a_2} b^\prime,b''})} F((b+_{a_2} b^\prime)+_{a_3} b'')$$ $$\zeta_1 = d_{M_3} \lambda^{-1} F(j_{b,b^\prime}) \phi_{b,b^\prime} (d_{M_1} \times d_{M_2}) \lambda^{-1}$$
+$$ (x \odot y) \odot z \coloneqq 1 \xrightarrow{\zeta_1} F(m_1+_{b} m_2) \times F(m_3) \xrightarrow{\phi_{m_1+_{b} m_2, m_3}} F((m_1+_{b}m_2) +m_3) \xrightarrow{F(j_{m_1+_{b} m_2,m_3})} F((m_1+_{b} m_2)+_{c} m_3)$$ $$\zeta_1 = (1 \times z) \rho^{-1} F(j_{m_1,m_2}) \phi_{m_1,m_2} (x \times y) \lambda^{-1}$$
 and
-$$ d_{M_1 \odot (M_2 \odot M_3)} \coloneqq 1 \xrightarrow{\zeta_2} F(b) \times F(b^\prime +_{a_3} b'') \xrightarrow{\phi_{b, b^\prime +_{a_3} b''}} F(b+(b^\prime +_{a_3} b'')) \xrightarrow{F(j_{b,b^\prime +_{a_3} b''})} F(b+_{a_2} (b^\prime+_{a_3} b''))$$ $$\zeta_2 = d_{M_1} \lambda^{-1} F(j_{b^\prime,b''}) \phi_{b^\prime,b''} (d_{M_2} \times d_{M_3}) \lambda^{-1}$$
-together with the isomorphism $\iota_a \colon F(a)(d_{(M_1 \odot M_2) \odot M_3}) \to d_{M_1 \odot (M_2 \odot M_3)}$.
-Note that the map $a \colon (b+_{a_2} b')+_{a_3}b'' \to b+_{a_2}(b'+_{a_3}b'')$ is the universal map between two colimits of the same diagram.
+$$ x \odot (y \odot z) \coloneqq 1 \xrightarrow{\zeta_2} F(m_1) \times F(m_2 +_{c} m_3) \xrightarrow{\phi_{m_1, m_2 +_{c} m_3}} F(m_1+(m_2 +_{c} m_3)) \xrightarrow{F(j_{m_1,m_2 +_{c} m_3})} F(m_1+_{b} (m_2+_{c} m_3))$$ $$\zeta_2 = (x \times 1) \lambda^{-1} F(j_{m_2,m_3}) \phi_{m_2,m_3} (y \odot z) \lambda^{-1}$$
+together with the isomorphism $\iota_\sigma \colon F(\sigma)((x \odot y) \odot z) \to x \odot (y \odot z)$.
+Note that the map $\sigma \colon (m_1+_{b} m_2)+_{c}m_3 \to m_1+_{b}(m_2+_{c}m_3)$ is the universal map between two colimits of the same diagram.
 We also have left and right unitors where given a horizontal 1-cell $M$:
@@
 \]
-if we, say, compose with the identity horizontal 1-cell of $a_2$ on the right:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a_1$};
-\node (B) at (1,0) {$b$};
-\node (C) at (2,0) {$a_2$};
-\node (D) at (1,-0.5) {$d \in F(b)$};
-\node (E) at (3,0) {$a_2$};
-\node (F) at (4,0) {$a_2$};
-\node (G) at (5,0) {$a_2$};
-\node (H) at (4,-0.5) {$!_{a_2} \in F(a_2)$};
+if we, say, compose with the identity horizontal 1-cell of $b$ on the right:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$a$};
+\node (B) at (1,0) {$m$};
+\node (C) at (2,0) {$b$};
+\node (D) at (1,-0.5) {$x \in F(m)$};
+\node (E) at (3,0) {$b$};
+\node (F) at (4,0) {$b$};
+\node (G) at (5,0) {$b$};
+\node (H) at (4,-0.5) {$!_{b} \in F(b)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-where $!_{a_2} = F(!)  \phi \colon 1 \to F(a_2)$ is the trivial decoration on $a_2$, composing these then gives:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a_1$};
-\node (B) at (1,0) {$b+_{a_2} a_2$};
-\node (C) at (2,0) {$a_2$};
-\node (D) at (3.5,0) {$d_{M+!_{a_2}} \in F(b +_{a_2} a_2)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$j \psi_b i$} (B)
-(C) edge node[above]{$j \psi_{a_2}$} (B);
-\end{tikzpicture}
-\]
-where $\psi_b \colon b \to b+a_2$ is the natural map into the coproduct and likewise for $\psi_{a_2}$ and $j \colon b+a_2 \to b+_{a_2} a_2$ is the natural map from the coproduct to the pushout.
-The decoration $d_{M+!_{a_2}} \colon 1 \to F(b+_{a_2} a_2)$ is given by: $$1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{d_{M} \times !_{a_2}} F(b) \times F(a_2) \xrightarrow{\phi_{b,a_2}} F(b+a_2) \xrightarrow{F(j_{b,a_2})} F(b+_{a_2} a_2).$$ We then have that the right unitor $R \colon M \odot 1_{a_2} \xrightarrow{\sim} M$ is given by the globular 2-morphism $(\id_{a_1},r,\id_{a_2})$ from the above composite to $M$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$a_1$};
-\node (A') at (0,-0.5) {$a_1$};
-\node (B) at (1.5,0.5) {$b+_{a_2} a_2$};
-\node (C) at (3,0.5) {$a_2$};
-\node (C') at (3,-0.5) {$a_2$};
-\node (D) at (1.5,-0.5) {$b$};
-\node (E) at (4.5,0.5) {$d_{M+!_{a_2}} \in F(b+_{a_2} a_2)$};
-\node (F) at (4.5,-0.5) {$d_{M} \in F(b)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$j \psi_b i$} (B)
-(C) edge node[above]{$j \psi_{a_2}$} (B)
-(A) edge node[left]{$\id_{a_1}$} (A')
-(C) edge node[left]{$\id_{a_2}$} (C')
+where $!_{b} = F(!)  \phi \colon 1 \to F(b)$ is the trivial decoration on $b$, composing these then gives:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$a$};
+\node (B) at (1,0) {$m+_{b} b$};
+\node (C) at (2,0) {$b$};
+\node (D) at (3.5,0) {$x \odot !_b \in F(m +_{b} b)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$j \psi_m i$} (B)
+(C) edge node[above]{$j \psi_{b}$} (B);
+\end{tikzpicture}
+\]
+where $\psi_m \colon m \to m+b$ is the natural map into the coproduct and likewise for $\psi_{b}$ and $j \colon m+b \to m+_{b} b$ is the natural map from the coproduct to the pushout.
+The decoration $x \odot !_b \colon 1 \to F(m+_{b} b)$ is given by: $$1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{x \times !_{b}} F(m) \times F(b) \xrightarrow{\phi_{m,b}} F(m+b) \xrightarrow{F(j_{m,b})} F(m+_{b} b).$$ We then have that the right unitor $R \colon M \odot 1_{b} \xrightarrow{\sim} M$ is given by the globular 2-morphism $(\id_{a},r,\id_{b})$ from the above composite to $M$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0.5) {$a$};
+\node (A') at (0,-0.5) {$a$};
+\node (B) at (1.5,0.5) {$m+_{b} b$};
+\node (C) at (3,0.5) {$b$};
+\node (C') at (3,-0.5) {$b$};
+\node (D) at (1.5,-0.5) {$m$};
+\node (E) at (4.5,0.5) {$x \odot !_b \in F(m+_{b} b)$};
+\node (F) at (4.5,-0.5) {$x \in F(m)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$j \psi_m i$} (B)
+(C) edge node[above]{$j \psi_{b}$} (B)
+(A) edge node[left]{$\id_{a}$} (A')
+(C) edge node[right]{$\id_{b}$} (C')
 (A') edge node [above]{$i$} (D)
@@
 \]
-where $r \colon b+_{a_2} a_2 \xrightarrow{\sim} b$ is a universal map together with the isomorphism $\iota_r \colon F(r)(d_{M+!_{a_2}}) \to d_M$.
+where $r \colon m+_{b} b \xrightarrow{\sim} m$ is a universal map together with the isomorphism $\iota_r \colon F(r)(x \odot !_b) \to x$.
 The left unitor is similar.
-The source and target functor applied to the left and right unitors and associators yield identities.
-The left and right unitors together with the associator satisfy the standard pentagon and triangle identities of a monoidal category or bicategory.
+The source and target functor applied to the left and right unitors and associators yield identities, and the left and right unitors together with the associator satisfy the standard pentagon and triangle identities of a monoidal category or bicategory.
 Finally, for the interchange law, given four 2-morphisms $\alpha, \beta, \alpha^\prime$ and $\beta^\prime$:
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$a_1$};
-\node (A') at (0,-0.5) {$a_1^\prime$};
-\node (B) at (1,0.5) {$b$};
-\node (C) at (2,0.5) {$a_2$};
-\node (C') at (2,-0.5) {$a_2^\prime$};
-\node (D) at (1,-0.5) {$b^\prime$};
-\node (E) at (3,0.5) {$d_{M_1} \in F(b)$};
-\node (F) at (3,-0.5) {$d_{M_2} \in F(b^\prime)$};
-\node (G) at (4,0.5) {$a_2$};
-\node (H) at (5,0.5) {$c$};
-\node (I) at (6,0.5) {$a_3$};
-\node (G') at (4,-0.5) {$a_2^\prime$};
-\node (H') at (5,-0.5) {$c^\prime$};
-\node (I') at (6,-0.5) {$a_3^\prime$};
-\node (J) at (7,0.5) {$d_{N_1} \in F(c)$};
-\node (K) at (7,-0.5) {$d_{N_2} \in F(c^\prime)$};
-\node (L) at (1,-1) {$\iota_\alpha \colon F(h_1)(d_{M_1}) \to d_{M_2}$};
-\node (M) at (5,-1) {$\iota_\beta \colon F(h_2)(d_{N_1}) \to d_{N_2}$};
-\node (A'') at (0,-1.5) {$a_1^\prime$};
-\node (A''') at (0,-2.5) {$a_1''$};
-\node (B'') at (1,-1.5) {$b^\prime$};
-\node (C'') at (2,-1.5) {$a_2^\prime$};
-\node (C''') at (2,-2.5) {$a_2''$};
-\node (D'') at (1,-2.5) {$b''$};
-\node (E'') at (3,-1.5) {$d_{M_2} \in F(b^\prime)$};
-\node (F'') at (3,-2.5) {$d_{M_3} \in F(b'')$};
-\node (G'') at (4,-1.5) {$a_2^\prime$};
-\node (H'') at (5,-1.5) {$c^\prime$};
-\node (I'') at (6,-1.5) {$a_3^\prime$};
-\node (G''') at (4,-2.5) {$a_2''$};
-\node (H''') at (5,-2.5) {$c''$};
-\node (I''') at (6,-2.5) {$a_3''$};
-\node (J'') at (7,-1.5) {$d_{N_2} \in F(b^\prime)$};
-\node (K'') at (7,-2.5) {$d_{N_3} \in F(b'')$};
-\node (L'') at (1,-3) {$\iota_{\alpha^\prime} \colon F(h_1^\prime)(d_{M_2}) \to d_{M_3}$};
-\node (M'') at (5,-3) {$\iota_{\beta^\prime} \colon F(h_2^\prime)(d_{N_2}) \to d_{N_3}$};
+\node (A) at (0,0.5) {$a$};
+\node (A') at (0,-0.5) {$a'$};
+\node (B) at (1,0.5) {$m$};
+\node (C) at (2,0.5) {$b$};
+\node (C') at (2,-0.5) {$b^\prime$};
+\node (D) at (1,-0.5) {$m^\prime$};
+\node (E) at (3,0.5) {$x \in F(m)$};
+\node (F) at (3,-0.5) {$x' \in F(m^\prime)$};
+\node (G) at (4,0.5) {$b$};
+\node (H) at (5,0.5) {$n$};
+\node (I) at (6,0.5) {$c$};
+\node (G') at (4,-0.5) {$b^\prime$};
+\node (H') at (5,-0.5) {$n^\prime$};
+\node (I') at (6,-0.5) {$c^\prime$};
+\node (J) at (7,0.5) {$y \in F(n)$};
+\node (K) at (7,-0.5) {$y' \in F(n^\prime)$};
+\node (L) at (1,-1) {$\iota_\alpha \colon F(h_1)(x) \to x'$};
+\node (M) at (5,-1) {$\iota_\beta \colon F(h_2)(y) \to y'$};
+\node (A'') at (0,-1.5) {$a^\prime$};
+\node (A''') at (0,-2.5) {$a''$};
+\node (B'') at (1,-1.5) {$m^\prime$};
+\node (C'') at (2,-1.5) {$b^\prime$};
+\node (C''') at (2,-2.5) {$b''$};
+\node (D'') at (1,-2.5) {$m''$};
+\node (E'') at (3,-1.5) {$x' \in F(m^\prime)$};
+\node (F'') at (3,-2.5) {$x'' \in F(m'')$};
+\node (G'') at (4,-1.5) {$b^\prime$};
+\node (H'') at (5,-1.5) {$n^\prime$};
+\node (I'') at (6,-1.5) {$c^\prime$};
+\node (G''') at (4,-2.5) {$b''$};
+\node (H''') at (5,-2.5) {$n''$};
+\node (I''') at (6,-2.5) {$c''$};
+\node (J'') at (7,-1.5) {$y' \in F(n^\prime)$};
+\node (K'') at (7,-2.5) {$y'' \in F(n'')$};
+\node (L'') at (1,-3) {$\iota_{\alpha^\prime} \colon F(h_1^\prime)(x') \to x''$};
+\node (M'') at (5,-3) {$\iota_{\beta^\prime} \colon F(h_2^\prime)(y') \to y''$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (A) edge node[left]{$f$} (A')
-(C) edge node[left]{$g$} (C')
+(C) edge node[right]{$g$} (C')
 (A') edge node[above] {$i_1^\prime$} (D)
@@
 (I) edge node [above] {$o_2$} (H)
-(I) edge node [left] {$k$} (I')
+(I) edge node [right] {$k$} (I')
 (I') edge node [above] {$o_2^\prime$} (H')
@@
 (A'') edge node[left]{$f^\prime$} (A''')
-(C'') edge node[left]{$g^\prime$} (C''')
+(C'') edge node[right]{$g^\prime$} (C''')
 (A''') edge node[above] {$i_1''$} (D'')
@@
 (I'') edge node [above] {$o_2^\prime$} (H'')
-(I'') edge node [left] {$k^\prime$} (I''')
+(I'') edge node [right] {$k^\prime$} (I''')
 (I''') edge node [above] {$o_2''$} (H''');
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$a_1$};
-\node (A') at (0,-0.5) {$a_1^\prime$};
-\node (B) at (1.5,0.5) {$b+_{a_2} c$};
-\node (C) at (3,0.5) {$a_3$};
-\node (C') at (3,-0.5) {$a_3^\prime$};
-\node (D) at (1.5,-0.5) {$b^\prime +_{a_2^\prime} c^\prime$};
-\node (E) at (4.5,0.5) {$d_{M_1 \odot N_1} \in F(b+_{a_2} c)$};
-\node (F) at (4.5,-0.5) {$d_{M_2 \odot N_2} \in F(b^\prime +_{a_2^\prime} c^\prime)$};
-\node (G) at (1.5,-1) {$\iota_{\alpha \odot \beta} \colon F(h_1 +_g h_2)(d_{M_1 \odot N_1}) \to d_{M_1^\prime \odot N_1^\prime}$};
-\node (A'') at (0,-1.5) {$a_1^\prime$};
-\node (A''') at (0,-2.5) {$a_1''$};
-\node (B'') at (1.5,-1.5) {$b^\prime +_{a_2^\prime} c^\prime$};
-\node (C'') at (3,-1.5) {$a_3^\prime$};
-\node (C''') at (3,-2.5) {$a_3''$};
-\node (D'') at (1.5,-2.5) {$b'' +_{a_2''} c''$};
-\node (E'') at (4.5,-1.5) {$d_{M_2 \odot N_2} \in F(b^\prime+_{a_2^\prime} c^\prime)$};
-\node (F'') at (4.5,-2.5) {$d_{M_3 \odot N_3} \in F(b'' +_{a_2''} c'')$};
-\node (G'') at (1.5,-3) {$\iota_{\alpha^\prime \odot \beta^\prime} \colon F(h_1^\prime +_{g^\prime} h_2^\prime)(d_{M_2 \odot N_2}) \to d_{M_3 \odot N_3}.$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$j \psi_{a_1} i_1$} (B)
-(C) edge node[above]{$j \psi_{a_3} o_2$} (B)
+\node (A) at (0,0.5) {$a$};
+\node (A') at (0,-0.5) {$a^\prime$};
+\node (B) at (1.5,0.5) {$m+_{b} n$};
+\node (C) at (3,0.5) {$c$};
+\node (C') at (3,-0.5) {$c^\prime$};
+\node (D) at (1.5,-0.5) {$m' +_{b'} n^\prime$};
+\node (E) at (4.5,0.5) {$x \odot y \in F(m+_{b} n)$};
+\node (F) at (4.5,-0.5) {$x' \odot y' \in F(m^\prime +_{b'} n^\prime)$};
+\node (G) at (1.5,-1) {$\iota_{\alpha \odot \beta} \colon F(h_1 +_g h_2)(x \odot y) \to x' \odot y'$};
+\node (A'') at (0,-1.5) {$a^\prime$};
+\node (A''') at (0,-2.5) {$a''$};
+\node (B'') at (1.5,-1.5) {$m^\prime +_{b\prime} n^\prime$};
+\node (C'') at (3,-1.5) {$c^\prime$};
+\node (C''') at (3,-2.5) {$c''$};
+\node (D'') at (1.5,-2.5) {$m'' +_{b''} n''$};
+\node (E'') at (4.5,-1.5) {$x' \odot y' \in F(m^\prime+_{b^\prime} n^\prime)$};
+\node (F'') at (4.5,-2.5) {$x'' \odot y'' \in F(m'' +_{b''} n'')$};
+\node (G'') at (1.5,-3) {$\iota_{\alpha^\prime \odot \beta^\prime} \colon F(h_1^\prime +_{g^\prime} h_2^\prime)(x' \odot y') \to x'' \odot y''.$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$j \psi_{m} i_1$} (B)
+(C) edge node[above]{$j \psi_{n} o_2$} (B)
 (A) edge node[left]{$f$} (A')
-(C) edge node[left]{$k$} (C')
-(A') edge node [above]{$j \psi_{a_1^\prime} i_1^\prime$} (D)
-(C') edge node [above]{$j \psi_{a_3^\prime} o_2^\prime$} (D)
+(C) edge node[right]{$k$} (C')
+(A') edge node [above]{$j \psi_{m^\prime} i_1^\prime$} (D)
+(C') edge node [above]{$j \psi_{n^\prime} o_2^\prime$} (D)
 (B) edge node [left] {$h_1 +_g h_2$} (D)
-(A'') edge node[above]{$j \psi_{a_1^\prime} i_1^\prime$} (B'')
-(C'') edge node[above]{$j \psi_{a_3^\prime} o_2^\prime$} (B'')
+(A'') edge node[above]{$j \psi_{m^\prime} i_1^\prime$} (B'')
+(C'') edge node[above]{$j \psi_{n^\prime} o_2^\prime$} (B'')
 (A'') edge node[left]{$f^\prime$} (A''')
-(C'') edge node[left]{$k^\prime$} (C''')
-(A''') edge node [above]{$j \psi_{a_1''} i_1''$} (D'')
-(C''') edge node [above]{$j \psi_{a_3''} o_2''$} (D'')
+(C'') edge node[right]{$k^\prime$} (C''')
+(A''') edge node [above]{$j \psi_{m''} i_1''$} (D'')
+(C''') edge node [above]{$j \psi_{n''} o_2''$} (D'')
 (B'') edge node [left] {$h_1^\prime +_{g^\prime} h_2^\prime$} (D'');
@@
 \node (D) at (3,0) {$1$};
-\node (E) at (4.5,0.5) {$F(b)$};
-\node (E') at (4.5,-0.5) {$F(b^\prime)$};
+\node (E) at (4.5,0.5) {$F(m)$};
+\node (E') at (4.5,-0.5) {$F(m^\prime)$};
 \node (A') at (6.5,0) {$\iota_\beta \Swarrow$};
 \node (D') at (5.5,0) {$1$};
-\node (E'') at (7,0.5) {$F(c)$};
-\node (E''') at (7,-0.5) {$F(c^\prime)$};
-\path[->,font=\scriptsize,>=angle 90]
-(D) edge node [above] {$d_{M_1}$} (E)
-(D) edge node [below] {$d_{M_2}$} (E')
+\node (E'') at (7,0.5) {$F(n)$};
+\node (E''') at (7,-0.5) {$F(n^\prime)$};
+\path[->,font=\scriptsize,>=angle 90]
+(D) edge node [above] {$x$} (E)
+(D) edge node [below] {$x'$} (E')
 (E) edge node [right] {$F(h_1)$} (E')
-(D') edge node [above] {$d_{N_1}$} (E'')
-(D') edge node [below] {$d_{N_2}$} (E''')
+(D') edge node [above] {$y$} (E'')
+(D') edge node [below] {$y'$} (E''')
 (E'') edge node [right] {$F(h_2)$} (E''');
@@
 \node (D) at (3,0) {$1 \xrightarrow{\lambda^{-1}} 1 \times 1$};
-\node (E) at (5.5,0.5) {$F(b) \times F(c)$};
-\node (E') at (5.5,-0.5) {$F(b^\prime) \times F(c^\prime)$};
-\node (B) at (7.5,0.5) {$F(b+c)$};
-\node (B') at (7.5,-0.5) {$F(b^\prime + c^\prime)$};
-\node (C) at (9.25,0.5) {$F(b+_{a_2} c)$};
-\node (C') at (9.25,-0.5) {$F(b^\prime +_{a_2^\prime} c^\prime)$};
-\path[->,font=\scriptsize,>=angle 90]
-(E) edge node [above] {$\phi_{b,c}$} (B)
-(E') edge node [above] {$\phi_{b^\prime,c^\prime}$} (B')
-(B) edge node [above] {$F(j_{b,c})$} (C)
-(B') edge node [above] {$F(j_{b^\prime,c^\prime})$} (C')
+\node (E) at (5.5,0.5) {$F(m) \times F(n)$};
+\node (E') at (5.5,-0.5) {$F(m^\prime) \times F(n^\prime)$};
+\node (B) at (7.5,0.5) {$F(m+n)$};
+\node (B') at (7.5,-0.5) {$F(m^\prime + n^\prime)$};
+\node (C) at (9.25,0.5) {$F(m+_{b} n)$};
+\node (C') at (9.25,-0.5) {$F(m^\prime +_{b^\prime} n^\prime)$};
+\path[->,font=\scriptsize,>=angle 90]
+(E) edge node [above] {$\phi_{m,n}$} (B)
+(E') edge node [above] {$\phi_{m^\prime,n^\prime}$} (B')
+(B) edge node [above] {$F(j_{m,n})$} (C)
+(B') edge node [above] {$F(j_{m^\prime,n^\prime})$} (C')
 (C) edge node [right] {$F(h_1 +_g h_2)$} (C')
 (B) edge node [right] {$F(h_1 + h_2)$} (B')
-(D) edge node [above] {$d_{M_1} \times d_{N_1}$} (E)
-(D) edge node [below] {$d_{M_2} \times d_{N_2}$} (E')
+(D) edge node [above] {$x \times y$} (E)
+(D) edge node [below] {$x' \times y'$} (E')
 (E) edge node [right] {$F(h_1) \times F(h_2)$} (E');
@@
 where the middle square commutes since $F$ is a lax monoidal pseudofunctor and the right square commutes as the underlying diagram commutes.
-The decorations $d_{M_1 \odot N_1}$ and $d_{M_2 \odot N_2}$ are given respectively by top and bottom composite of arrows and the morphism of decorations $\iota_{\alpha \odot \beta}$ is given by composing $\iota_\alpha \times \iota_\beta$ with the two commuting squares, which can equivalently be viewed as a morphism in $F(b' +_{a_2'} c')$.
+The decorations $x \odot y$ and $x' \odot y'$ are given respectively by top and bottom composite of arrows and the morphism of decorations $\iota_{\alpha \odot \beta}$ is given by composing $\iota_\alpha \times \iota_\beta$ with the two commuting squares, which can equivalently be viewed as a morphism in $F(m' +_{b'} n')$.
 
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$a_1$};
-\node (A') at (0,-0.5) {$a_1''$};
-\node (B) at (2,0.5) {$b+_{a_2} c$};
-\node (C) at (4,0.5) {$a_3$};
-\node (C') at (4,-0.5) {$a_3''$};
-\node (D) at (2,-0.5) {$b'' +_{a_2''} c''$};
-\node (E) at (5.5,0.5) {$d_{M_1 \odot N_1} \in F(b+_{a_2} c)$};
-\node (F) at (5.5,-0.5) {$d_{M_3 \odot N_3} \in F(b'' +_{a_2''} c'')$};
-\node (G) at (2,-1) {$\iota_{(a^\prime \odot \beta^\prime)(\alpha \odot \beta)} \colon F((h_1^\prime +_{g^\prime} h_2^\prime)(h_1 +_g h_2))(d_{M_1 \odot N_1}) \to d_{M_3 \odot N_3}.$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$j \psi_{a_1} i_1$} (B)
-(C) edge node[above]{$j \psi_{a_3} o_2$} (B)
+\node (A) at (0,0.5) {$a$};
+\node (A') at (0,-0.5) {$a''$};
+\node (B) at (2,0.5) {$m+_{b} n$};
+\node (C) at (4,0.5) {$c$};
+\node (C') at (4,-0.5) {$c''$};
+\node (D) at (2,-0.5) {$m'' +_{b''} n''$};
+\node (E) at (5.5,0.5) {$x \odot y \in F(m+_{b} n)$};
+\node (F) at (5.5,-0.5) {$x'' \odot y'' \in F(m'' +_{b''} n'')$};
+\node (G) at (2,-1) {$\iota_{(a^\prime \odot \beta^\prime)(\alpha \odot \beta)} \colon F((h_1^\prime +_{g^\prime} h_2^\prime)(h_1 +_g h_2))(x \odot y) \to x'' \odot y''.$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$j \psi_{m} i_1$} (B)
+(C) edge node[above]{$j \psi_{n} o_2$} (B)
 (A) edge node[left]{$f^\prime f$} (A')
-(C) edge node[left]{$k^\prime k$} (C')
-(A') edge node [above]{$j \psi_{a_1''} i_1''$} (D)
-(C') edge node [above]{$j \psi_{a_3''} o_2''$} (D)
+(C) edge node[right]{$k^\prime k$} (C')
+(A') edge node [above]{$j \psi_{m''} i_1''$} (D)
+(C') edge node [above]{$j \psi_{n''} o_2''$} (D)
 (B) edge node [left] {$(h_1^\prime +_{g^\prime} h_2^\prime)(h_1 +_g h_2)$} (D);
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$a_1$};
-\node (A') at (0,-0.5) {$a_1''$};
-\node (B) at (1,0.5) {$b$};
-\node (C) at (2,0.5) {$a_2$};
-\node (C') at (2,-0.5) {$a_2''$};
-\node (D) at (1,-0.5) {$b''$};
-\node (E) at (3,0.5) {$d_{M_1} \in F(b)$};
-\node (F) at (3,-0.5) {$d_{M_3} \in F(b'')$};
-\node (G) at (4,0.5) {$a_2$};
-\node (H) at (5,0.5) {$c$};
-\node (I) at (6,0.5) {$a_3$};
-\node (G') at (4,-0.5) {$a_2''$};
-\node (H') at (5,-0.5) {$c''$};
-\node (I') at (6,-0.5) {$a_3''$};
-\node (J) at (7,0.5) {$d_{N_1} \in F(c)$};
-\node (K) at (7,-0.5) {$d_{N_3} \in F(c'')$};
-\node (L) at (1,-1) {$\iota_{\alpha^\prime \alpha} \colon F(h_1^\prime h_1)(d_{M_1}) \to d_{M_3}$};
-\node (M) at (5,-1) {$\iota_{\beta^\prime \beta} \colon F(h_2^\prime h_2)(d_{N_1}) \to d_{N_3}$};
+\node (A) at (0,0.5) {$a$};
+\node (A') at (0,-0.5) {$a''$};
+\node (B) at (1,0.5) {$m$};
+\node (C) at (2,0.5) {$b$};
+\node (C') at (2,-0.5) {$b''$};
+\node (D) at (1,-0.5) {$m''$};
+\node (E) at (3,0.5) {$x \in F(m)$};
+\node (F) at (3,-0.5) {$x'' \in F(m'')$};
+\node (G) at (4,0.5) {$b$};
+\node (H) at (5,0.5) {$n$};
+\node (I) at (6,0.5) {$c$};
+\node (G') at (4,-0.5) {$b''$};
+\node (H') at (5,-0.5) {$n''$};
+\node (I') at (6,-0.5) {$c''$};
+\node (J) at (7,0.5) {$y \in F(n)$};
+\node (K) at (7,-0.5) {$y'' \in F(n'')$};
+\node (L) at (1,-1) {$\iota_{\alpha^\prime \alpha} \colon F(h_1^\prime h_1)(x) \to x''$};
+\node (M) at (5,-1) {$\iota_{\beta^\prime \beta} \colon F(h_2^\prime h_2)(y) \to y''$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (A) edge node[left]{$f^\prime f$} (A')
-(C) edge node[left]{$g^\prime g$} (C')
+(C) edge node[right]{$g^\prime g$} (C')
 (A') edge node[above] {$i_1''$} (D)
@@
 (I) edge node [above] {$o_2$} (H)
-(I) edge node [left] {$k^\prime k$} (I')
+(I) edge node [right] {$k^\prime k$} (I')
 (I') edge node [above] {$o_2''$} (H');
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$a_1$};
-\node (A') at (0,-0.5) {$a_1''$};
-\node (B) at (2,0.5) {$b+_{a_2} c$};
-\node (C) at (4,0.5) {$a_3$};
-\node (C') at (4,-0.5) {$a_3''$};
-\node (D) at (2,-0.5) {$b'' +_{a_2''} c''$};
-\node (E) at (5.5,0.5) {$d_{M_1 \odot N_1} \in F(b+_{a_2} c)$};
-\node (F) at (5.5,-0.5) {$d_{M_3 \odot N_3} \in F(b'' +_{a_3''} c'')$};
-\node (G) at (2,-1) {$\iota_{(\alpha^\prime \alpha) \odot (\beta^\prime \beta)} \colon F((h_1^\prime h_1)+_{g^\prime g} (h_2^\prime h_2))(d_{M_1 \odot N_1}) \to d_{M_3 \odot N_3}.$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$j \psi_{a_1} i_1$} (B)
-(C) edge node[above]{$j \psi_{a_3} o_2$} (B)
+\node (A) at (0,0.5) {$a$};
+\node (A') at (0,-0.5) {$a''$};
+\node (B) at (2,0.5) {$m+_{b} n$};
+\node (C) at (4,0.5) {$c$};
+\node (C') at (4,-0.5) {$c''$};
+\node (D) at (2,-0.5) {$m'' +_{b''} n''$};
+\node (E) at (5.5,0.5) {$x \odot y \in F(m+_{b} n)$};
+\node (F) at (5.5,-0.5) {$x'' \odot y'' \in F(m'' +_{b''} n'')$};
+\node (G) at (2,-1) {$\iota_{(\alpha^\prime \alpha) \odot (\beta^\prime \beta)} \colon F((h_1^\prime h_1)+_{g^\prime g} (h_2^\prime h_2))(x \odot y) \to x'' \odot y''.$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$j \psi_{m} i_1$} (B)
+(C) edge node[above]{$j \psi_{n} o_2$} (B)
 (A) edge node[left]{$f^\prime f$} (A')
-(C) edge node[left]{$k^\prime k$} (C')
-(A') edge node [above]{$j \psi_{a_1''} i_1''$} (D)
-(C') edge node [above]{$j \psi_{a_3''} o_2''$} (D)
+(C) edge node[right]{$k^\prime k$} (C')
+(A') edge node [above]{$j \psi_{m''} i_1''$} (D)
+(C') edge node [above]{$j \psi_{n''} o_2''$} (D)
 (B) edge node [left] {$(h_1^\prime h_1) +_{g^\prime g} (h_2^\prime h_2)$} (D);
@@
 %\]
-As is usual concerning the interchange law of double categories of this nature, only the `interior' of the two compositions appears different, but the two morphisms $(h_1^\prime +_{g^\prime} h_2^\prime)(h_1 +_g h_2) \colon b+_{a_2} c \to b'' +_{a_2''} c''$ and $(h_1^\prime h_1) +_{g^\prime g} (h_2^\prime h_2) \colon b+_{a_2} c \to b'' +_{a_2''}c''$ are the same universal map realized in two different ways.
+As is usual concerning the interchange law of double categories of this nature, only the `interior' of the two composites appears different, but the two morphisms $(h_1^\prime +_{g^\prime} h_2^\prime)(h_1 +_g h_2) \colon m+_{b} n \to m'' +_{b''} n''$ and $(h_1^\prime h_1) +_{g^\prime g} (h_2^\prime h_2) \colon m+_{b} n \to m'' +_{b''}n''$ are the same universal map realized in two different ways.
 The two morphisms of decorations $\iota_{(\alpha^\prime \odot \beta^\prime)(\alpha \odot \beta)}$ and $\iota_{(\alpha^\prime \alpha) \odot (\beta^\prime \beta)}$ are obtained as two different compositions of four 2-morphisms in $\mathbf{Cat}$, namely horizontally then vertically and vertically then horizontally.
-As $\mathbf{Cat}$ is a 2-category, the interchange law for these 2-morphisms already holds, and as a result, the morphisms $$\iota_{(\alpha' \odot \beta')(\alpha \odot \beta)} \colon F((h_1^\prime +_{g^\prime} h_2^\prime)(h_1 +_g h_2))(d_{M_1 \odot N_1}) \to d_{M_3 \odot N_3}$$ and $$\iota_{(\alpha^\prime \alpha)\odot(\beta^\prime \beta)} \colon F((h_1^\prime h_1)+_{g^\prime g} (h_2^\prime h_2))(d_{M_1 \odot N_1}) \to d_{M_3 \odot N_3}$$ are also the same.
+As $\mathbf{Cat}$ is a 2-category, the interchange law for these 2-morphisms already holds, and as a result, the morphisms $$\iota_{(\alpha' \odot \beta')(\alpha \odot \beta)} \colon F((h_1^\prime +_{g^\prime} h_2^\prime)(h_1 +_g h_2))(x \odot y) \to x'' \odot y''$$ and $$\iota_{(\alpha^\prime \alpha)\odot(\beta^\prime \beta)} \colon F((h_1^\prime h_1)+_{g^\prime g} (h_2^\prime h_2))(x \odot y) \to x'' \odot y''$$ are also the same.
 Thus the interchange law for 2-morphisms holds and $F\mathbb{C}$sp is a double category.

### 2019-06-16 cospans.tex
Changing some notation in Theorem 2.2 and suggesting things that we can cut out.

@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a_1$};
-\node (B) at (1,0) {$b$};
-\node (C) at (2,0) {$a_2$};
-\node (D) at (3,0) {$d \in F(b)$};
+\node (A) at (0,0) {$a$};
+\node (B) at (1,0) {$m$};
+\node (C) at (2,0) {$b$};
+\node (D) at (3,0) {$x \in F(b)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$a_1$};
-\node (A') at (0,-0.5) {$a_1^\prime$};
-\node (B) at (1,0.5) {$b$};
-\node (C) at (2,0.5) {$a_2$};
-\node (C') at (2,-0.5) {$a_2^\prime$};
-\node (D) at (1,-0.5) {$b^\prime$};
-\node (E) at (3,0.5) {$d \in F(b)$};
-\node (F) at (3,-0.5) {$d^\prime \in F(b^\prime)$};
+\node (A) at (0,0.5) {$a$};
+\node (A') at (0,-0.5) {$a^\prime$};
+\node (B) at (1,0.5) {$m$};
+\node (C) at (2,0.5) {$b$};
+\node (C') at (2,-0.5) {$b^\prime$};
+\node (D) at (1,-0.5) {$m^\prime$};
+\node (E) at (3,0.5) {$x \in F(m)$};
+\node (F) at (3,-0.5) {$x^\prime \in F(m^\prime)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (A) edge node[left]{$f$} (A')
-(C) edge node[left]{$g$} (C')
+(C) edge node[right]{$g$} (C')
 (A') edge node [above]{$i^\prime$} (D)
@@
 \]
-together with a morphism $\iota \colon F(h)(d) \to d^\prime$.
+together with a morphism $\iota \colon F(h)(x) \to x^\prime$.
 }
@@
 \node (A) at (0,0) {$a_1$};
-\node (B) at (1,0) {$b$};
-\node (C) at (2,0) {$a_2$};
-\node (D) at (1,-0.5) {$d_{M_1} \in F(b)$};
-\node (E) at (3,0) {$a_1^\prime$};
-\node (F) at (4,0) {$b^\prime$};
-\node (G) at (5,0) {$a_2^\prime$};
-\node (H) at (4,-0.5) {$d_{M_2} \in F(b^\prime)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i$} (B)
-(C) edge node[above]{$o$} (B)
-(E) edge node[above]{$i^\prime$} (F)
-(G) edge node[above]{$o^\prime$} (F);
+\node (B) at (1,0) {$m_1$};
+\node (C) at (2,0) {$b_1$};
+\node (D) at (1,-0.5) {$x_1 \in F(m_1)$};
+\node (E) at (3,0) {$a_2$};
+\node (F) at (4,0) {$m_2$};
+\node (G) at (5,0) {$b_2$};
+\node (H) at (4,-0.5) {$x_2 \in F(m_2)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i_1$} (B)
+(C) edge node[above]{$o_1$} (B)
+(E) edge node[above]{$i_2$} (F)
+(G) edge node[above]{$o_2$} (F);
 \end{tikzpicture}
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a_1+a_1^\prime$};
-\node (B) at (1.25,0) {$b+b^\prime$};
-\node (C) at (2.5,0) {$a_2+a_2^\prime$};
-\node (D) at (4.25,0) {$d_{M_1 \otimes M_2} \in F(b+b')$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i+i'$} (B)
-(C) edge node[above]{$o+o'$} (B);
-\end{tikzpicture}
-\]
-and where the decoration on the apex is obtained using the natural transformation of the symmetric lax monoidal pseudofunctor $F:$ $$d_{M_1 \otimes M_2} \coloneqq 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{d_{M_1} \times d_{M_2}} F(b) \times F(b') \xrightarrow{\phi_{b,b'}} F(b+b').$$The monoidal unit 0 is given by:
+\node (A) at (0,0) {$a_1+a_2$};
+\node (B) at (1.25,0) {$m_1+m_2$};
+\node (C) at (2.5,0) {$b_1+b_2$};
+\node (D) at (4.25,0) {$x_1+x_2 \in F(m_1+m_2)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i_1+i_2$} (B)
+(C) edge node[above]{$o_1+o_2$} (B);
+\end{tikzpicture}
+\]
+and where the decoration on the apex is obtained using the natural transformation of the symmetric lax monoidal pseudofunctor $F:$ $$x_1+x_2 \coloneqq 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{x_1 \times x_2} F(m_1) \times F(m_2) \xrightarrow{\phi_{m_1,m_2}} F(m_1+m_2).$$The monoidal unit 0 is given by:
 \[
@@
 \node (D) at (1,-0.5) {$!_0 \in F(0)$};
-\node (E) at (3,0) {$a_1$};
-\node (F) at (4,0) {$b$};
-\node (G) at (5,0) {$a_2$};
-\node (H) at (4,-0.5) {$d_M \in F(b)$};
+\node (E) at (3,0) {$a$};
+\node (F) at (4,0) {$m$};
+\node (G) at (5,0) {$b$};
+\node (H) at (4,-0.5) {$x \in F(m)$};
 \node (I) at (2.5,0) {$\otimes$};
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$0+a_1$};
-\node (B) at (1,0) {$0+b$};
-\node (C) at (2,0) {$0+a_2$};
-\node (D) at (3.5,0) {$d_{0 \otimes M} \in F(0+b)$};
+\node (A) at (0,0) {$0+a$};
+\node (B) at (1,0) {$0+m$};
+\node (C) at (2,0) {$0+b$};
+\node (D) at (3.5,0) {$!_0 + x \in F(0+m)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-where $d_{0\otimes M} \in F(0+b)$ is given by $$1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{!_0 \times d_M} F(0) \times F(b) \xrightarrow{\phi_{0,b}} F(0+b).$$The left unitor is then an isomorphism in $F\mathbb{C}\textnormal{sp}_1$ given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$0+a_1$};
-\node (A') at (0,-0.5) {$a_1$};
-\node (B) at (1,0.5) {$0+b$};
-\node (C) at (2,0.5) {$0+a_2$};
-\node (C') at (2,-0.5) {$a_2$};
-\node (D) at (1,-0.5) {$b$};
-\node (E) at (3.5,0.5) {$d_{0+M} \in F(0+b)$};
-\node (F) at (3.5,-0.5) {$d_M \in F(b)$};
+where $!_0 + x \in F(0+m)$ is given by $$1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{!_0 \times x} F(0) \times F(m) \xrightarrow{\phi_{0,m}} F(0+m).$$The left unitor is then an isomorphism in $F\mathbb{C}\textnormal{sp}_1$ given by:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0.5) {$0+a$};
+\node (A') at (0,-0.5) {$a$};
+\node (B) at (1,0.5) {$0+m$};
+\node (C) at (2,0.5) {$0+b$};
+\node (C') at (2,-0.5) {$b$};
+\node (D) at (1,-0.5) {$m$};
+\node (E) at (3.5,0.5) {$!_0 + x \in F(0+m)$};
+\node (F) at (3.5,-0.5) {$x \in F(m)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (A) edge node[left]{$\ell$} (A')
-(C) edge node[left]{$\ell$} (C')
+(C) edge node[right]{$\ell$} (C')
 (A') edge node [above]{$i$} (D)
@@
 \]
-where $\ell$ is the left unitor of $(\mathsf{A},+,0)$, together with the isomorphism $\iota_{\lambda} \colon F(\ell)(d_{0 \otimes M}) \to d_M$. The right unitor is similar.
+where $\ell$ is the left unitor of $(\mathsf{A},+,0)$, together with the isomorphism $\iota_{\lambda} \colon F(\ell)(!_0 + x) \to x$. The right unitor is similar.
 
@@
 \node (A) at (0,0) {$a_1$};
-\node (B) at (1,0) {$c_1$};
+\node (B) at (1,0) {$m_1$};
 \node (C) at (2,0) {$b_1$};
-\node (D) at (1,-0.5) {$d_{M_1} \in F(c_1)$};
+\node (D) at (1,-0.5) {$x_1 \in F(m_1)$};
 \node (E) at (3,0) {$a_2$};
-\node (F) at (4,0) {$c_2$};
+\node (F) at (4,0) {$m_2$};
 \node (G) at (5,0) {$b_2$};
-\node (H) at (4,-0.5) {$d_{M_2} \in F(c_2)$};
+\node (H) at (4,-0.5) {$x_2 \in F(m_2)$};
 \node (I) at (6,0) {$a_3$};
-\node (J) at (7,0) {$c_3$};
+\node (J) at (7,0) {$m_3$};
 \node (K) at (8,0) {$b_3$};
-\node (L) at (7,-0.5) {$d_{M_3} \in F(c_3)$};
+\node (L) at (7,-0.5) {$x_3 \in F(m_3)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \node (A) at (0,0) {$(a_1+a_2)+a_3$};
-\node (B) at (2.25,0){$(c_1+c_2)+c_3$};
+\node (B) at (2.25,0){$(m_1+m_2)+m_3$};
 \node (C) at (4.5,0) {$(b_1+b_2)+b_3$};
-\node (D) at (2.25,-0.5) {$d_{(M_1 \otimes M_2) \otimes M_3} \in F((c_1+c_2)+c_3)$};
+\node (D) at (2.25,-0.5) {$(x_1+x_2)+x_3 \in F((m_1+m_2)+m_3)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-where $d_{(M_1 \otimes M_2) \otimes M_3} \colon 1 \to F((c_1+c_2)+c_3)$ is given by: $$1 \xrightarrow{(d_{M_1} \times d_{M_2}) \times d_{M_3})} (F(c_1) \times F(c_2)) \times F(c_3) \xrightarrow{\phi_{c_1,c_2} \times 1} F(c_1+c_2) \times F(c_3) \xrightarrow{\phi_{c_1+c_2,c_3}} F((c_1+c_2)+c_3)$$whereas tensoring the last two and then the first results in $M_1 \otimes (M_2 \otimes M_3)$:
+where $(x_1+x_2)+x_3 \colon 1 \to F((m_1+m_2)+m_3)$ is given by: $$1 \xrightarrow{(x_1 \times x_2) \times x_3} (F(m_1) \times F(m_2)) \times F(m_3) \xrightarrow{\phi_{m_1,m_2} \times 1} F(m_1+m_2) \times F(m_3) \xrightarrow{\phi_{m_1+m_2,m_3}} F((m_1+m_2)+m_3)$$whereas tensoring the last two and then the first results in $M_1 \otimes (M_2 \otimes M_3)$:
 \[
@@
 \node (A) at (0,0) {$a_1+(a_2+a_3)$};
-\node (B) at (2.25,0) {$c_1+(c_2+c_3)$};
+\node (B) at (2.25,0) {$m_1+(m_2+m_3)$};
 \node (C) at (4.5,0) {$b_1+(b_2+b_3)$};
-\node (D) at (2.25,-0.5) {$d_{M_1 \otimes (M_2 \otimes M_3)} \in F(c_1+(c_2+c_3))$};
+\node (D) at (2.25,-0.5) {$x_1+(x_2+x_3) \in F(m_1+(m_2+m_3))$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-where $d_{M_1 \otimes (M_2 \otimes M_3)} \colon 1 \to F(c_1+(c_2+c_3))$ is given by: $$1 \xrightarrow{d_{M_1} \times (d_{M_2} \times d_{M_3})} F(c_1) \times (F(c_2) \times F(c_3)) \xrightarrow{1 \times \phi_{c_2,c_3}} F(c_1) \times F(c_2+c_3) \xrightarrow{\phi_{c_1,c_2+c_3}} F(c_1+(c_2+c_3)).$$If we let $a$ denote the associator of $(\mathsf{A},+,0)$, the associator of $F\mathbb{C}\textnormal{sp}_1$ is then a map of cospans in $\mathsf{A}$ from $(M_1 \otimes M_2) \otimes M_3$ to $M_1 \otimes (M_2 \otimes M_3)$ given by:
+where $x_1+(x_2+x_3) \colon 1 \to F(m_1+(m_2+m_3))$ is given by: $$1 \xrightarrow{x_1 \times (x_2 \times x_3)} F(m_1) \times (F(m_2) \times F(m_3)) \xrightarrow{1 \times \phi_{m_2,m_3}} F(m_1) \times F(m_2+m_3) \xrightarrow{\phi_{m_1,m_2+m_3}} F(m_1+(m_2+m_3)).$$If we let $a$ denote the associator of $(\mathsf{A},+,0)$, the associator of $F\mathbb{C}\textnormal{sp}_1$ is then a map of cospans in $\mathsf{A}$ from $(M_1 \otimes M_2) \otimes M_3$ to $M_1 \otimes (M_2 \otimes M_3)$ given by:
 \[
@@
 \node (A') at (0,-0.5) {$a_1+(a_2+a_3)$};
-\node (B) at (2.25,0.5) {$(c_1+c_2)+c_3$};
+\node (B) at (2.25,0.5) {$(m_1+m_2)+m_3$};
 \node (C) at (4.5,0.5) {$(b_1+b_2)+b_3$};
 \node (C') at (4.5,-0.5) {$b_1+(b_2+b_3)$};
-\node (D) at (2.25,-0.5) {$c_1+(c_2+c_3)$};
-\node (E) at (7,0.5) {$d_{(M_1 \otimes M_2) \otimes M_3} \in F((c_1+c_2)+c_3)$};
-\node (F) at (7,-0.5) {$d_{M_1 \otimes (M_2 \otimes M_3)} \in F(c_1+(c_2+c_3))$};
+\node (D) at (2.25,-0.5) {$m_1+(m_2+m_3)$};
+\node (E) at (7,0.5) {$(x_1+x_2)+x_3 \in F((m_1+m_2)+m_3)$};
+\node (F) at (7,-0.5) {$x_1+(x_2+x_3) \in F(m_1+(m_2+m_3))$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (A) edge node[left]{$a$} (A')
-(C) edge node[left]{$a$} (C')
+(C) edge node[right]{$a$} (C')
 (A') edge node [above]{$i_1+(i_2+i_3)$} (D)
@@
 \]
-together with the isomorphism $\iota_a \colon F(a)(d_{(M_1 \otimes M_2) \otimes M_3}) \to d_{M_1 \otimes (M_2 \otimes M_3)}$.
-If we denote the above associator simply as $a$ and the left and right unitors as $\lambda$ and $\rho$, respectively, then given four objects in $F\mathbb{C}\textnormal{sp}_1$, say $M_1, M_2, M_3$ and $M_4$:
+together with the isomorphism $\iota_a \colon F(a)((x_1+x_2)+x_3) \to x_1+(x_2+x_3)$.
+These associators and left and right unitors together satisfy the pentagon and triangle identities of a monoidal category.
+\textbf{Kenny: Probably cut stuff out below this.} If we denote the above associator simply as $a$ and the left and right unitors as $\lambda$ and $\rho$, respectively, then given four objects in $F\mathbb{C}\textnormal{sp}_1$, say $M_1, M_2, M_3$ and $M_4$:
 \[
@@
 \node (A) at (0,0) {$a_1$};
-\node (B) at (1,0) {$c_1$};
+\node (B) at (1,0) {$m_1$};
 \node (C) at (2,0) {$b_1$};
-\node (D) at (1,-0.5) {$d_{M_1} \in F(c_1)$};
+\node (D) at (1,-0.5) {$x_1 \in F(m_1)$};
 \node (E) at (3,0) {$a_2$};
-\node (F) at (4,0) {$c_2$};
+\node (F) at (4,0) {$m_2$};
 \node (G) at (5,0) {$b_2$};
-\node (H) at (4,-0.5) {$d_{M_2} \in F(c_2)$};
+\node (H) at (4,-0.5) {$x_2 \in F(m_2)$};
 \node (I) at (0,-1.5) {$a_3$};
-\node (J) at (1,-1.5) {$c_3$};
+\node (J) at (1,-1.5) {$m_3$};
 \node (K) at (2,-1.5) {$b_3$};
-\node (L) at (1,-2) {$d_{M_3} \in F(c_3)$};
+\node (L) at (1,-2) {$x_3 \in F(m_3)$};
 \node (M) at (3,-1.5) {$a_4$};
-\node (N) at (4,-1.5) {$c_4$};
+\node (N) at (4,-1.5) {$m_4$};
 \node (O) at (5,-1.5) {$b_4$};
-\node (P) at (4,-2) {$d_{M_4} \in F(c_4)$};
+\node (P) at (4,-2) {$x_4 \in F(m_4)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-then as $\mathbb{C}\textnormal{sp}(\mathsf{A})$ is a symmetric monoidal double category, the following pentagon of underlying cospans commutes:
+then as $\mathbb{C}\textnormal{sp}(\mathsf{A})$ is a symmetric monoidal double category, the following pentagon of underlying cospans and maps of cospans commutes:
 \[
@@
 \]
-as well as the following pentagon of corresponding decorations in the category $F(c_1 +(c_2 +(c_3+c_4)))$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (-.5,0) {$F(aa)(d_{((M_1 \otimes M_2) \otimes M_3) \otimes M_4}) $};
-\node (B) at (2.25,1) {$F(a)(d_{(M_1 \otimes M_2) \otimes (M_3 \otimes M_4)})$};
-\node (C) at (5,0) {$d_{M_1 \otimes (M_2 \otimes (M_3 \otimes M_4))}$};
-\node (D) at (-.5,-1) {$F((1 \otimes a)a)(d_{(M_1 \otimes (M_2 \otimes M_3)) \otimes M_4}) $};
-\node (E) at (5,-1) {$F(1 \otimes a)(d_{M_1 \otimes ((M_2 \otimes M_3) \otimes M_4)}) $};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[left]{$F(a)(\iota_a)$} (B)
+as well as the following pentagon of corresponding decorations in the category $F(m_1 +(m_2 +(m_3+m_4)))$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (-.5,0) {$F(aa)(((x_1+x_2)+x_3)+x_4) $};
+\node (B) at (2.25,1) {$F(a)((x_1+x_2)+(x_3+x_4))$};
+\node (C) at (5,0) {$x_1+(x_2+(x_3+x_4))$};
+\node (D) at (-.5,-1) {$F((1 \otimes a)a)((x_1+(x_2+x_3))+x_4) $};
+\node (E) at (5,-1) {$F(1 \otimes a)(x_1+((x_2+x_3)+x_4)) $};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$F(a)(\iota_a)$} (B)
 (B) edge node[above]{$\iota_a$} (C)
@@
 \]
-since $$F(aa)(d_{((M_1 \otimes M_2) \otimes M_3) \otimes M_4})=F((1 \otimes a)a(a \otimes 1))(d_{((M_1 \otimes M_2) \otimes M_3) \otimes M_4})$$ as the corresponding pentagon in the symmetric monoidal category $(\mathsf{A},+,0)$ commutes.
+since $$F(aa)(((x_1+x_2)+x_3)+x_4)=F((1 \otimes a)a(a \otimes 1))(((x_1+x_2)+x_3)+x_4)$$ as the corresponding pentagon in the symmetric monoidal category $(\mathsf{A},+,0)$ commutes, and then appliying the pseudofunctor $F$ to said pentagon yields a commutative pentagon in $\mathbf{Cat}$.
 

### 2019-06-17 cospans.tex
more notation changes in Theorem 2.2

@@
 
-Similarly, if we denote the left and right unitors as $\lambda$ and $\rho$, respectively, then the following triangle of underlying maps of cospans commutes:
+Similarly, if we denote the left and right unitors as $\lambda$ and $\rho$, respectively, then the following triangle of cospans and underlying maps of cospans commutes:
 \[
@@
 \]
-as well as the following triangle of corresponding decorations in the category $F(c_1+c_2)$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$F(\rho \otimes 1)(d_{(M_1 \otimes 0) \otimes M_2})$};
-\node (B) at (2.25,1) {$d_{M_1 \otimes M_2}$};
-\node (C) at (4.5,0) {$F(1 \otimes \lambda)(d_{M_1 \otimes (0 \otimes M_2)}) $};
+as well as the following triangle of corresponding decorations in the category $F(m_1+m_2)$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$F(\rho \otimes 1)((x_1+0)+x_2)$};
+\node (B) at (2.25,1) {$x_1+x_2$};
+\node (C) at (4.5,0) {$F(1 \otimes \lambda)(x_1+(0+x_2)) $};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-since $$F(\rho \otimes 1)(d_{(M_1 \otimes 0) \otimes M_2})=F((1 \otimes \lambda)a)(d_{(M_1 \otimes 0) \otimes M_2})$$ as the corresponding triangle in the symmetric monoidal category $(\mathsf{A},+,0)$ commutes.
+since $$F(\rho \otimes 1)((x_1+0)+x_2)=F((1 \otimes \lambda)a)((x_1+0)+x_2)$$ as the corresponding triangle in the symmetric monoidal category $(\mathsf{A},+,0)$ commutes and applying the pseudofunctor $F$ to this commutative triangle results in a commutative triangle in $\mathbf{Cat}$.
 
@@
 \node (A') at (0,-0.5) {$a_2+a_1$};
-\node (B) at (2,0.5) {$c_1+c_2$};
+\node (B) at (2,0.5) {$m_1+m_2$};
 \node (C) at (4,0.5) {$b_1+b_2$};
 \node (C') at (4,-0.5) {$b_2+b_1$};
-\node (D) at (2,-0.5) {$c_2+c_1$};
-\node (E) at (5.5,0.5) {$d_{M_1 \otimes M_2} \in F(c_1+c_2)$};
-\node (F) at (5.5,-0.5) {$d_{M_2 \otimes M_1} \in F(c_2+c_1)$};
+\node (D) at (2,-0.5) {$m_2+m_1$};
+\node (E) at (5.5,0.5) {$x_1+x_2 \in F(m_1+m_2)$};
+\node (F) at (5.5,-0.5) {$x_2+x_1 \in F(m_2+m_1)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (C') edge node [above]{$o_2+o_1$} (D)
-(B) edge node [left] {$\beta_{c_1,c_2}$} (D);
-\end{tikzpicture}
-\]
-$$\iota_{\beta_{M_1,M_2}} \colon F(\beta_{c_1,c_2})(d_{M_1 \otimes M_2}) \xrightarrow{\sim} d_{M_2 \otimes M_1}$$ where the vertical 1-morphisms are given by braidings in $(\mathsf{A},+,0)$.
+(B) edge node [left] {$\beta_{m_1,m_2}$} (D);
+\end{tikzpicture}
+\]
+$$\iota_{\beta_{M_1,M_2}} \colon F(\beta_{m_1,m_2})(x_1+x_2) \xrightarrow{\sim} x_2+x_1$$ where the vertical 1-morphisms are given by braidings in $(\mathsf{A},+,0)$.
 This braiding makes the following triangle of underlying cospans commute:
@@
 \]
-as well as the following diagram of corresponding decorations in the category $F(c_1+c_2)$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$d_{M_1 \otimes M_2}$};
-\node (B) at (2.25,1) {$d_{M_1 \otimes M_2} $};
-\node (C) at (4.5,0) {$F(\beta_{c_2,c_1})(d_{M_2 \otimes M_1}) $};
+as well as the following diagram of corresponding decorations in the category $F(m_1+m_2)$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$x_1+x_2$};
+\node (B) at (2.25,1) {$x_1+x_2$};
+\node (C) at (4.5,0) {$F(\beta_{m_2,m_1})(x_2+x_1)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (C) edge node[right]{$\iota_{\beta_{M_2,M_1}}$} (B)
-(A) edge node[above]{$F(\beta_{c_2,c_1})(\iota_{\beta_{M_1,M_2}})$} (C);
-\end{tikzpicture}
-\]
-since $F(\beta_{c_2,c_1} \beta_{c_1,c_2}) (d_{M_1 \otimes M_2}) = d_{M_1 \otimes M_2}$. Thus $F\mathbb{C}\textnormal{sp}_1$ is also symmetric monoidal.
-
-Now, given four horizontal 1-cells $M_1, M_2, N_1$ and $N_2$ respectively by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a_1$};
-\node (B) at (1,0) {$b$};
-\node (C) at (2,0) {$a_2$};
-\node (D) at (1,-0.5) {$d_{M_1} \in F(b)$};
-\node (E) at (3,0) {$a_2$};
-\node (F) at (4,0) {$b'$};
-\node (G) at (5,0) {$a_3$};
-\node (H) at (4,-0.5) {$d_{M_2} \in F(b')$};
-\node (I) at (0,-1.5) {$a_1'$};
-\node (J) at (1,-1.5) {$c$};
-\node (K) at (2,-1.5) {$a_2'$};
-\node (L) at (1,-2) {$d_{N_1} \in F(c)$};
-\node (M) at (3,-1.5) {$a_2'$};
-\node (N) at (4,-1.5) {$c'$};
-\node (O) at (5,-1.5) {$a_3'$};
-\node (P) at (4,-2) {$d_{N_2} \in F(c')$};
+(A) edge node[above]{$F(\beta_{m_2,m_1})(\iota_{\beta_{M_1,M_2}})$} (C);
+\end{tikzpicture}
+\]
+since $F(\beta_{m_2,m_1} \beta_{m_1,m_2}) (x_1+x_2) = x_1+x_2$. Thus $F\mathbb{C}\textnormal{sp}_1$ is also symmetric monoidal.
+
+Next we derive the globular isomorphisms required in the definition of a symmetric monoidal double category relating horizontal composition and the tensor product.
+Given four horizontal 1-cells $M_1, M_2, N_1$ and $N_2$ respectively by:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$a$};
+\node (B) at (1,0) {$m_1$};
+\node (C) at (2,0) {$b$};
+\node (D) at (1,-0.5) {$x_1 \in F(m_1)$};
+\node (E) at (3,0) {$b$};
+\node (F) at (4,0) {$m_2$};
+\node (G) at (5,0) {$c$};
+\node (H) at (4,-0.5) {$x_2 \in F(m_2)$};
+\node (I) at (0,-1.5) {$a'$};
+\node (J) at (1,-1.5) {$n_1$};
+\node (K) at (2,-1.5) {$b'$};
+\node (L) at (1,-2) {$y_1 \in F(n_1)$};
+\node (M) at (3,-1.5) {$b'$};
+\node (N) at (4,-1.5) {$n_2$};
+\node (O) at (5,-1.5) {$c'$};
+\node (P) at (4,-2) {$y_2 \in F(n_2)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a_1+a_1'$};
-\node (B) at (2.5,0) {$(b+c)+_{a_2+a_2'}(b'+c')$};
-\node (C) at (5,0) {$a_3+a_3'$};
-\node (D) at (2.5,-0.5) {$d_{(M_1 \otimes N_1) \odot (M_2 \otimes N_2)} \in F((b+c)+_{a_2+a_2'}(b'+c'))$};
+\node (A) at (0,0) {$a+a'$};
+\node (B) at (2.5,0) {$(m_1+n_1)+_{b+b'}(m_2+n_2)$};
+\node (C) at (5,0) {$c+c'$};
+\node (D) at (2.5,-0.5) {$(x_1+y_1)\odot(x_2+y_2) \in F((m_1+n_1)+_{b+b'}(m_2+n_2))$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-where the decoration $d_{(M_1 \otimes N_1) \odot (M_2 \otimes N_2)} \in F((b+c)+_{a_2+a_2'}(b'+c'))$ is given by:
+where the decoration $(x_1+y_1) \odot (x_2+y_2) \in F((m_1+n_1)+_{b+b'}(m_2+n_2))$ is given by:
 \[
@@
 \node (C) at (0,-2) {$(1 \times 1) \times (1 \times 1)$};
-\node (D) at (0,-3) {$(F(b) \times F(c)) \times (F(b') \times F(c'))$};
-\node (E) at (0,-4) {$F(b+c) \times F(b'+c')$};
-\node (F) at (0,-5) {$F((b+c)+(b'+c'))$};
-\node (G) at (0,-6) {$F((b+c)+_{a_2+a_2'}(b'+c'))$};
+\node (D) at (0,-3) {$(F(m_1) \times F(n_1)) \times (F(m_2) \times F(n_2))$};
+\node (E) at (0,-4) {$F(m_1+n_1) \times F(m_2+n_2)$};
+\node (F) at (0,-5) {$F((m_1+n_1)+(m_2+n_2))$};
+\node (G) at (0,-6) {$F((m_1+n_1)+_{b+b'}(m_2+n_2))$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (B) edge node[left]{$\lambda^{-1} \times \lambda^{-1}$} (C)
-(C) edge node[left]{$(d_{M_1} \times d_{N_1}) \times (d_{M_2} \times d_{N_2})$} (D)
-(D) edge node[left]{$\phi_{b,c} \times \phi_{b',c'}$} (E)
-(E) edge node[left]{$\phi_{b+c,b'+c'}$} (F)
-(F) edge node[left]{$F(j_{b+c,b'+c'})$} (G);
+(C) edge node[left]{$(x_1 \times y_1) \times (x_2 \times y_2)$} (D)
+(D) edge node[left]{$\phi_{m_1,n_1} \times \phi_{m_2,n_2}$} (E)
+(E) edge node[left]{$\phi_{m_1+n_1,m_2+n_2}$} (F)
+(F) edge node[left]{$F(j_{m_1+n_1,m_2+n_2})$} (G);
 \end{tikzpicture}
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a_1+a_1'$};
-\node (B) at (2.5,0) {$(b+_{a_2} c) + (b' +_{a_2'} c')$};
-\node (C) at (5,0) {$a_3+a_3'$};
-\node (D) at (2.5,-0.5) {$d_{(M_1 \odot M_2) \otimes (N_1 \odot N_2)} \in F((b+_{a_2}c)+(b'+_{a_2'}c'))$};
+\node (A) at (0,0) {$a+a'$};
+\node (B) at (2.5,0) {$(m_1+_{b} m_2) + (n_1 +_{b'} n_2)$};
+\node (C) at (5,0) {$c+c'$};
+\node (D) at (2.5,-0.5) {$(x_1 \odot x_2) + (y_1 \odot y_2) \in F((m_1+_{b}m_2)+(n_1+_{b'}n_2))$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-where the decoration $d_{((M_1 \odot M_2) \otimes (N_1 \odot N_2))} \in F((b+_{a_2}c)+(b'+_{a_2'}c'))$ is given by:
+where the decoration $(x_1 \odot x_2) + (y_1 \odot y_2) \in F((m_1+_{b}m_2)+(n_1+_{b'}n_2))$ is given by:
 \[
@@
 \node (C) at (0,-2) {$(1 \times 1) \times (1 \times 1)$};
-\node (D) at (0,-3) {$(F(b) \times F(c)) \times (F(b') \times F(c'))$};
-\node (E) at (0,-4) {$F(b+c) \times F(b'+c')$};
-\node (F) at (0,-5) {$F(b+_{a_2}c) \times F(b'+_{a_2'}c')$};
-\node (G) at (0,-6) {$F((b+_{a_2}c)+(b'+_{a_2'}c'))$};
+\node (D) at (0,-3) {$(F(m_1) \times F(m_2)) \times (F(n_1) \times F(n_2))$};
+\node (E) at (0,-4) {$F(m_1+m_2) \times F(n_1+n_2)$};
+\node (F) at (0,-5) {$F(m_1+_{b}m_2) \times F(n_1+_{b'}n_2)$};
+\node (G) at (0,-6) {$F((m_1+_{b}m_2)+(n_1+_{b'}n_2))$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (B) edge node[left]{$\lambda^{-1} \times \lambda^{-1}$} (C)
-(C) edge node[left]{$(d_{M_1} \times d_{N_1}) \times (d_{M_2} \times d_{N_2})$} (D)
-(D) edge node[left]{$\phi_{b,c} \times \phi_{b',c'}$} (E)
-(E) edge node[left]{$F(j_{b,c}) \times F(j_{b',c'})$} (F)
-(F) edge node[left]{$\phi_{b+_{a_2}c,b'+_{a_2'}c'}$} (G);
+(C) edge node[left]{$(x_1 \times x_2) \times (y_1 \times y_2)$} (D)
+(D) edge node[left]{$\phi_{m_1,m_2} \times \phi_{n_1,n_2}$} (E)
+(E) edge node[left]{$F(j_{m_1,m_2}) \times F(j_{n_1,n_2})$} (F)
+(F) edge node[left]{$\phi_{m_1+_{b}m_2,n_1+_{b'}n_2}$} (G);
 \end{tikzpicture}
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$a_1+a_1'$};
-\node (A') at (0,-0.5) {$a_1+a_1'$};
-\node (B) at (2.5,0.5) {$(b+c)+_{a_2+a_2'}(b'+c')$};
-\node (C) at (5,0.5) {$a_3+a_3'$};
-\node (C') at (5,-0.5) {$a_3+a_3'$};
-\node (D) at (2.5,-0.5) {$(b+_{a_2}c)+(b'+_{a_2'}c')$};
-\node (E) at (2.5,1) {$d_{(M_1 \otimes N_1) \odot (M_2 \otimes N_2)} \in F((b+c)+_{a_2+a_2'}(b'+c'))$};
-\node (F) at (2.5,-1) {$d_{(M_1 \odot M_2) \otimes (N_1 \odot N_2)} \in F((b+_{a_2}c)+(b'+_{a_2'}c'))$};
+\node (A) at (0,0.5) {$a+a'$};
+\node (A') at (0,-0.5) {$a+a'$};
+\node (B) at (2.5,0.5) {$(m_1+n_1)+_{b+b'}(m_2+n_2)$};
+\node (C) at (5,0.5) {$c+c'$};
+\node (C') at (5,-0.5) {$c+c'$};
+\node (D) at (2.5,-0.5) {$(m_1+_{b}m_2)+(n_1+_{b'}n_2)$};
+\node (E) at (2.5,1) {$(x_1+y_1) \odot (x_2+y_2) \in F((m_1+n_1)+_{b+b'}(m_2+n_2))$};
+\node (F) at (2.5,-1) {$(x_1 \odot x_2)+(y_1 \odot y_2) \in F((m_1+_{b}m_2)+(n_1+_{b'}n_2))$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-$$\iota_{\hat{\chi}} \colon F(\hat{\chi})(d_{(M_1 \otimes N_1) \odot (M_2 \otimes N_2)}) \to d_{(M_1 \odot M_2) \otimes (N_1 \odot N_2)}$$
+$$\iota_{\hat{\chi}} \colon F(\hat{\chi})((x_1+y_1)\odot(x_2+y_2)) \to (x_1 \odot x_2)+(y_1 \odot y_2)$$
 where $\hat{\chi}$ is the universal map between two colimits of the same diagram.

### 2019-06-17 cospans.tex
more notational changes for Theorem 2.2

@@
 (A) edge node[left]{$1$} (A')
-(C) edge node[left]{$1$} (C')
+(C) edge node[right]{$1$} (C')
 (A') edge node [above]{$(j \psi i_1')+(j \psi i_1)$} (D)
@@
 (A) edge node[left]{$1$} (A')
-(C) edge node[left]{$1$} (C')
+(C) edge node[right]{$1$} (C')
 (A') edge node [above]{$1_a + 1_b$} (D)
@@
 We check a few to give a sense of what these are like.
-For example,  given horizontal 1-cells $M_i,N_i,P_i$, the following commutative diagram expresses the associativity isomorphism as a transformation of double categories.
+For example,  given horizontal 1-cells $M_i,N_i,P_i$ for $i=1,2$, the following commutative diagram expresses the associativity isomorphism as a transformation of double categories.
 \[
@@
 		\begin{tikzpicture}
-			\node (k) at (0,0) {$k$};
-			\node (l) at (1,0) {$l$};
-			\node (m) at (2,0) {$m$};
+			\node (k) at (0,0) {$a$};
+			\node (l) at (1,0) {$m_1$};
+			\node (m) at (2,0) {$b$};
 			\node (M1) at (-1,0) {$M_1 =$};
 			\node (N1) at (3,0) {$N_1 =$};
-			\node (q) at (4,0) {$q$};
-			\node (r) at (5,0) {$r$};
-			\node (s) at (6,0) {$s$};
+			\node (q) at (4,0) {$a'$};
+			\node (r) at (5,0) {$n_1$};
+			\node (s) at (6,0) {$b'$};
 			\node (P1) at (7,0) {$P_1 =$};
-			\node (v) at (8,0) {$v$};
-			\node (w) at (9,0) {$w$};
-			\node (x) at (10,0) {$x$};
-			\node (m2) at (0,-1.5) {$m$};
-			\node (n) at (1,-1.5) {$n$};
-			\node (p) at (2,-1.5) {$p$};
+			\node (v) at (8,0) {$a''$};
+			\node (w) at (9,0) {$p_1$};
+			\node (x) at (10,0) {$b''$};
+			\node (m2) at (0,-1.5) {$b$};
+			\node (n) at (1,-1.5) {$m_2$};
+			\node (p) at (2,-1.5) {$c$};
 			\node (M2) at (-1,-1.5) {$M_2 =$};
 			\node (N2) at (3,-1.5) {$N_2 =$};
-			\node (s2) at (4,-1.5) {$s$};
-			\node (t) at (5,-1.5) {$t$};
-			\node (u) at (6,-1.5) {$u$};
+			\node (s2) at (4,-1.5) {$b'$};
+			\node (t) at (5,-1.5) {$n_2$};
+			\node (u) at (6,-1.5) {$c'$};
 			\node (P2) at (7,-1.5) {$P_2 =$};
-			\node (x2) at (8,-1.5) {$x$};
-			\node (y) at (9,-1.5) {$y$};
-			\node (z) at (10,-1.5) {$z$};
-\node (dM1) at (1,-0.5) {$d_{M_1} \in F(l)$};
-\node (dM2) at (1,-2) {$d_{M_2} \in F(n)$};
-\node (dN1) at (5,-0.5) {$d_{N_1} \in F(r)$};
-\node (dN2) at (5,-2) {$d_{N_2} \in F(t)$};
-\node (dP1) at (9,-0.5) {$d_{P_1} \in F(w)$};
-\node (dP2) at (9,-2) {$d_{P_2} \in F(y)$};
+			\node (x2) at (8,-1.5) {$b''$};
+			\node (y) at (9,-1.5) {$p_2$};
+			\node (z) at (10,-1.5) {$c''$};
+\node (dM1) at (1,-0.5) {$x_1 \in F(m_1)$};
+\node (dM2) at (1,-2) {$x_2 \in F(m_2)$};
+\node (dN1) at (5,-0.5) {$y_1 \in F(n_1)$};
+\node (dN2) at (5,-2) {$y_2 \in F(n_2)$};
+\node (dP1) at (9,-0.5) {$z_1 \in F(p_1)$};
+\node (dP2) at (9,-2) {$z_2 \in F(p_2)$};
 			\path[->,font=\scriptsize,>=angle 90]
@@
 		\begin{tikzpicture}
-			\node (a) at (-4,0) {$k+m$};
-			\node (b) at (1,0) {$((l+r)+w) +_{((m+s)+x)}((n+t)+y)$};
-			\node (c) at (6,0) {$v+x$};
-			\node (a2) at (-4,1) {$k+m$};
-			\node (b2) at (1,1) {$(l+(r+w)) +_{(m+(s+x))}(n+(t+y))$};
-			\node (c2) at (6,1) {$v+x$};
-                                \node (a3) at (-4,2) {$k+m$};
-			\node (b3) at (1,2) {$(l+_m n)+((r+w)+_{(s+x)}(t+y))$};
-			\node (c3) at (6,2) {$v+x$};
-                                \node (a4) at (-4,3) {$k+m$};
-			\node (b4) at (1,3) {$(l+_m n)+((r+_s t)+(w+_x y))$};
-			\node (c4) at (6,3) {$v+x$};
-                                \node (a5) at (-4,-1) {$k+m$};
-			\node (b5) at (1,-1) {$((l+r)+_{(m+s)}(n+t))+(w+_x y)$};
-			\node (c5) at (6,-1) {$v+x$};
-                                \node (a6) at (-4,-2) {$k+m$};
-			\node (b6) at (1,-2) {$((l+_m n)+(r+_s t))+(w+_x y)$};
-			\node (c6) at (6,-2) {$v+x$};
-                                \node (a7) at (-4,-3) {$k+m$};
-			\node (b7) at (1,-3) {$(l+_m n)+((r+_s t)+(w+_x y))$};
-			\node (c7) at (6,-3) {$v+x$};
+			\node (a) at (-4,0) {$(a+a')+a''$};
+			\node (b) at (1,0) {$((m_1+n_1)+p_1) +_{((b+b')+b'')}((m_2+n_2)+p_2)$};
+			\node (c) at (6,0) {$(c+c')+c''$};
+			\node (a2) at (-4,1) {$a+(a'+a'')$};
+			\node (b2) at (1,1) {$(m_1+(n_1+p_1)) +_{(b+(b'+b''))}(m_2+(n_2+p_2))$};
+			\node (c2) at (6,1) {$c+(c'+c'')$};
+                                \node (a3) at (-4,2) {$a+(a'+a'')$};
+			\node (b3) at (1,2) {$(m_1+_b m_2)+((n_1+p_1)+_{(b'+b'')}(n_2+p_2))$};
+			\node (c3) at (6,2) {$c+(c'+c'')$};
+                                \node (a4) at (-4,3) {$a+(a'+a'')$};
+			\node (b4) at (1,3) {$(m_1+_b m_2)+((n_1+_{b'} n_2)+(p_1+_{b''} p_2))$};
+			\node (c4) at (6,3) {$c+(c'+c'')$};
+                                \node (a5) at (-4,-1) {$(a+a')+a''$};
+			\node (b5) at (1,-1) {$((m_1+n_1)+_{(b+b')}(m_2+n_2))+(p_1+_{b''} p_2)$};
+			\node (c5) at (6,-1) {$(c+c')+c''$};
+                                \node (a6) at (-4,-2) {$(a+a')+a''$};
+			\node (b6) at (1,-2) {$((m_1+_b m_2)+(n_1+_{b'} n_2))+(p_1+_{b''} p_2)$};
+			\node (c6) at (6,-2) {$(c+c')+c''$};
+                                \node (a7) at (-4,-3) {$a+(a'+a'')$};
+			\node (b7) at (1,-3) {$(m_1+_b m_2)+((n_1+_{b'} n_2)+(p_1+_{b''} p_2))$};
+			\node (c7) at (6,-3) {$c+(c'+c'')$};
 			\path[->,font=\scriptsize,>=angle 90]
@@
 			(c2) edge node[above]{$$} (b2)
-                                (a) edge node[above]{$$} (a2)
+                                (a) edge node[left]{$$} (a2)
                                 (b) edge node[left]{$a \odot a$} (b2)
@@
 	\]
-Here all of the vertical 1-morphisms on the left and right are identities, the middle vertical 1-morphisms are the 2-morphisms from the previous commutative diagram, and the horizontal vertical 1-morphisms pointing towards the middle are natural maps into each colimit, all of which are naturally isomorphic to each other as all the middle objects are colimits of the same diagram, namely the previous collection of cospans, taken in various ways.
+Here all of the vertical 1-morphisms on the left and right are associators or identities, the middle vertical 1-morphisms labeled on the left are the 2-morphisms from the previous commutative diagram, and the horizontal vertical 1-morphisms pointing towards the middle are natural maps into each colimit, all of which are naturally isomorphic to each other as all the middle objects are colimits of the same diagram, namely the previous collection of cospans, taken in various ways.
 The above diagram of maps of cospans can then be visualized as a hexagonal prism in which all the faces commute by identifying the top and the bottom as the same.
-As for the morphisms of decorations, each isomorphism $\iota_n$ goes from the domain under the image of the functor $F$ applied to natural isomorphism adjacent to it to the codomain as written, meaning that, for example: $$\iota_1 \colon F(a \odot a)(d_{((M_1 \otimes N_1) \otimes P_1) \odot ((M_2 \otimes N_2) \otimes P_2)}) \to d_{(M_1 \otimes (N_1 \otimes P_1)) \odot (M_2 \otimes (N_2 \otimes P_2))}.$$  The following diagram commutes in the category $F((l+_m n) + ((r+_s t) + (w+_x y)))$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$F( a (\chi \otimes 1)\chi)(d_{((M_1 \otimes N_1) \otimes P_1) \odot ((M_2 \otimes N_2) \otimes P_2)})$};
-\node (A') at (4.5,0.5) {$F((1 \otimes \chi) \chi)(d_{(M_1 \otimes (N_1 \otimes P_1)) \odot (M_2 \otimes (N_2 \otimes P_2))})$};
-\node (B) at (0,-0.5) {$F(a(\chi  \otimes 1))(d_{((M_1 \otimes N_1) \odot (M_2 \otimes N_2)) \otimes (P_1 \odot P_2)})$};
-\node (C) at (4.5,-0.5) {$F(1 \otimes \chi)(d_{(M_1 \odot M_2) \otimes ((N_1 \otimes P_1) \odot (N_2 \otimes P_2))})$};
-\node (C') at (0,-1.5) {$F(a)(d_{((M_1 \odot M_2) \otimes (N_1 \odot N_2)) \otimes (P_1 \odot P_2)})$};
-\node (D) at (4.5,-1.5) {$d_{(M_1 \odot M_2) \otimes ((N_1 \odot N_2) \otimes (P_1 \odot P_2))}$};
+As for the morphisms of decorations, which are labeled on the right of the interior vertical 1-morphisms, each isomorphism $\iota_n$ goes from the domain under the image of the functor $F$ applied to natural isomorphism adjacent to it to the codomain as written, meaning that, for example: $$\iota_1 \colon F(a \odot a)(((x_1+y_1)+z_1) \odot ((x_2+y_2)+z_2)) \to (x_1+(y_1+z_1)) \odot (x_2+(y_2+z_2)).$$  The following diagram commutes in the category $F((m_1+_b m_2) + ((n_1+_{b'} n_2) + (p_1+_{b''} p_2)))$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0.5) {$F( a (\chi \otimes 1)\chi)(((x_1+y_1)+z_1) \odot ((x_2+y_2)+z_2))$};
+\node (A') at (6,0.5) {$F((1 \otimes \chi) \chi)((x_1+(y_1+z_1)) \odot (x_2+(y_2+z_2)))$};
+\node (B) at (0,-0.5) {$F(a(\chi  \otimes 1))(((x_1+y_1) \odot (x_2+y_2)) + (z_1 \odot z_2))$};
+\node (C) at (6,-0.5) {$F(1 \otimes \chi)((x_1 \odot x_2) + ((y_1+z_1) \odot (y_2+z_2)))$};
+\node (C') at (0,-1.5) {$F(a)(((x_1 \odot x_2)+(y_1 \odot y_2)) + (z_1 \odot z_2))$};
+\node (D) at (6,-1.5) {$(x_1 \odot x_2) + ((y_1 \odot y_2) + (z_1 \odot z_2))$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-since $$F(a(\chi \otimes 1)\chi)(d_{((M_1 \otimes N_1) \otimes P_1) \odot ((M_2 \otimes N_2) \otimes P_2)}) = F((1 \otimes \chi) \chi (a \odot a))(d_{((M_1 \otimes N_1) \otimes P_1) \odot ((M_2 \otimes N_2) \otimes P_2)})$$
-as the above underlying diagram of maps of cospans commutes.
+since $$F(a(\chi \otimes 1)\chi)(((x_1+y_1)+z_1) \odot ((x_2+y_2)+z_2)) = F((1 \otimes \chi) \chi (a \odot a))(((x_1+y_1)+z_1) \odot ((x_2+y_2)+z_2))$$
+as the above underlying diagram of maps of cospans commutes and then applying the pseudofunctor $F$ yields a commutative diagram in $\mathbf{Cat}$.
 
@@
 		\begin{tikzpicture}
-			\node (a) at (-4,0) {$k+m$};
-			\node (b) at (1,0) {$(l+_m n) + (r+_s t)$};
-			\node (c) at (6,0) {$s+u$};
-			\node (a2) at (-4,1) {$k+m$};
-			\node (b2) at (1,1) {$(r +_s t) + (l +_m n)$};
-			\node (c2) at (6,1) {$s+u$};
-                                \node (a3) at (-4,2) {$k+m$};
-			\node (b3) at (1,2) {$(r+l) +_{(s+m)} (t+n)$};
-			\node (c3) at (6,2) {$s+u$};
-                                \node (a5) at (-4,-1) {$k+m$};
-			\node (b5) at (1,-1) {$(l+r) +_{(m+s)} (n+t)$};
-			\node (c5) at (6,-1) {$s+u$};
-                                \node (a6) at (-4,-2) {$k+m$};
-			\node (b6) at (1,-2) {$(r+l) +_{(s+m)} (t+n)$};
-			\node (c6) at (6,-2) {$s+u$};
+			\node (a) at (-4,0) {$a+a'$};
+			\node (b) at (1,0) {$(m_1+_b m_2) + (n_1+_{b'} n_2)$};
+			\node (c) at (6,0) {$c+c'$};
+			\node (a2) at (-4,1) {$a'+a$};
+			\node (b2) at (1,1) {$(n_1 +_{b'} n_2) + (m_1 +_b m_2)$};
+			\node (c2) at (6,1) {$c'+c$};
+                                \node (a3) at (-4,2) {$a'+a$};
+			\node (b3) at (1,2) {$(n_1+m_1) +_{(b'+b)} (n_2+m_2)$};
+			\node (c3) at (6,2) {$c'+c$};
+                                \node (a5) at (-4,-1) {$a+a'$};
+			\node (b5) at (1,-1) {$(m_1+n_1) +_{(b+b')} (m_2+n_2)$};
+			\node (c5) at (6,-1) {$c+c'$};
+                                \node (a6) at (-4,-2) {$a'+a$};
+			\node (b6) at (1,-2) {$(n_1+m_1) +_{(b'+b)} (n_2+m_2)$};
+			\node (c6) at (6,-2) {$c'+c$};
 			\path[->,font=\scriptsize,>=angle 90]
@@
 	\]
-All the comments about the previous underlying coherence diagram of maps of cospans apply to this one. As for the decorations, the following diagram commutes in the category $F((r+l)+_{(s+m)}(t+n))$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$F(\chi \beta)(d_{(M_1 \odot M_2) \otimes (N_1 \odot N_2)})$};
-\node (B) at (3,0) {$F(\chi)(d_{(N_1 \odot N_2) \otimes (M_1 \odot M_2)})$};
-\node (C) at (0,-1) {$F(\beta \odot \beta)(d_{(M_1 \otimes N_1) \odot (M_2 \otimes N_2)})$};
-\node (D) at (3,-1) {$d_{(N_1 \otimes M_1) \odot (N_2 \otimes M_2)}$};
+All the comments about the previous underlying coherence diagram of maps of cospans apply to this one.
+As for the decorations, the following diagram commutes in the category $F((y_1+x_1)+_{(b'+b)}(y_2+x_2))$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$F(\chi \beta)((x_1 \odot x_2)+(y_1 \odot y_2))$};
+\node (B) at (4,0) {$F(\chi)((y_1 \odot y_2)+(x_1 \odot x_2))$};
+\node (C) at (0,-1) {$F(\beta \odot \beta)((x_1+y_1) \odot (x_2 + y_2))$};
+\node (D) at (4,-1) {$(y_1+x_1) \odot (y_2+x_2)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-since $$F(\chi \beta)(d_{(M_1 \odot M_2) \otimes (N_1 \odot N_2)}) = F((\beta \odot \beta)\chi)(d_{(M_1 \odot M_2) \otimes (N_1 \odot N_2)})$$
-as the above underlying diagram of maps of cospans commutes. The other diagrams are shown to commute similarly.
+since $$F(\chi \beta)((x_1 \odot x_2)+(y_1 \odot y_2)) = F((\beta \odot \beta)\chi)((x_1 \odot x_2)+(y_1 \odot y_2))$$
+as the above underlying diagram of maps of cospans commutes and then applying the pseudofunctor $F$ to this diagram yields a commutative diagram in $\mathbf{Cat}$.
+The other diagrams are shown to commute similarly.
 \end{proof}

### 2019-06-18 cospans.tex
just commented out some unused stuff

@@
 
-%\end{comment}
+\end{comment}
 

### 2019-06-29 cospans.tex
2-cat of finitely cocomplete cats now called "Rex"

--- 2019-06-17 cospans.tex
@@
 \begin{itemize}
+\item {\chris Would a title like `An equivalence of compositional frameworks for networks' or `An equivalence of compositional network frameworks' be more informative?
+Otherwise, compositional framework on its own doesn't say much!}
+\item {\chris Discuss notation for Decorated and Structured cospan double categories one last time? :)}
 \item {\chris Notation between \cref{Equiv} and \cref{thm:decoratedcospans} right now does not match!
@@
 Also I prefer $a$ and $b$ rather than $a_1$ and $a_2$.}
-
-{\chris After a brief discussion in John's office, for \cref{Equiv} I used $a,b,c$ for the feet and $m,n$ for the apices so we can serially compose. Of course can change as we like.}
 %\item {\chris There might be a way to completely hide the details of version 'fibres have, reindexing preserve' if that's what we want to do.}
-
 \end{itemize}
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a$};
-\node (B) at (1,0) {$m$};
-\node (C) at (2,0) {$b$};
-\node (D) at (3,0) {$x \in F(m)$};
+\node (A) at (0,0) {$a_1$};
+\node (B) at (1,0) {$b$};
+\node (C) at (2,0) {$a_2$};
+\node (D) at (3,0) {$d \in F(b)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$a$};
-\node (A') at (0,-0.5) {$a'$};
-\node (B) at (1,0.5) {$m$};
-\node (C) at (2,0.5) {$b$};
-\node (C') at (2,-0.5) {$b'$};
-\node (D) at (1,-0.5) {$m'$};
-\node (E) at (3,0.5) {$x \in F(m)$};
-\node (F) at (3,-0.5) {$x' \in F(m')$};
+\node (A) at (0,0.5) {$a_1$};
+\node (A') at (0,-0.5) {$a_1^\prime$};
+\node (B) at (1,0.5) {$b$};
+\node (C) at (2,0.5) {$a_2$};
+\node (C') at (2,-0.5) {$a_2^\prime$};
+\node (D) at (1,-0.5) {$b^\prime$};
+\node (E) at (3,0.5) {$d \in F(b)$};
+\node (F) at (3,-0.5) {$d^\prime \in F(b^\prime)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (A) edge node[left]{$f$} (A')
-(C) edge node[right]{$g$} (C')
+(C) edge node[left]{$g$} (C')
 (A') edge node[above] {$i'$} (D)
@@
 \end{equation}
-together with a morphism $\iota \colon F(h)(m) \to m^\prime$ in $F(m^\prime)$.}
+together with a morphism $\iota \colon F(h)(d) \to d^\prime$ in $F(b^\prime)$.}
 \end{enumerate}
@@
 \textbf{Kenny: We should try to make this theorem shorter.} {\chris I agree!}
-\textbf{Kenny: On second thought, I'm not sure what we can cut out of this theorem. We're already saying "the standard monoidal category diagrams are satisfied" rather than displaying them.}
 \begin{proof}
@@
 \]
-where $!_a \in F(a)$ is the trivial decoration on $a$ given by the composite of the unique map $F(!) \colon F(0) \to F(a)$ and the morphism $\phi \colon 1 \to F(0)$  which comes from the structure of the lax monoidal pseudofunctor $F \colon \mathsf{A} \to \mathbf{Cat}$.
+where $!_a \in F(a)$ is the trivial decoration on $a$ given by the composition of the unique map $F(!) \colon F(0) \to F(a)$ and the morphism $\phi \colon 1 \to F(0)$  which comes from the structure of the lax monoidal pseudofunctor $F \colon \mathsf{A} \to \mathbf{Cat}$.
 For morphisms, the structure functor $U$ is defined as:
@@
 (A) edge node[left]{$f$} (A')
-(C) edge node[right]{$f$} (C')
+(C) edge node[left]{$f$} (C')
 (A') edge node[above] {$1$} (D)
@@
 \]
-is the object $a$ in $\mathsf{A}$ and the source of the 2-morphism
+is the object $a_1$ in $\mathsf{A}$ and the source of the 2-morphism
 \[
@@
 \node (A') at (0,-0.5) {$a^\prime$};
-\node (B) at (1,0.5) {$m$};
-\node (C) at (2,0.5) {$b$};
-\node (C') at (2,-0.5) {$b^\prime$};
-\node (D) at (1,-0.5) {$m^\prime$};
-\node (E) at (3,0.5) {$x \in F(m)$};
-\node (F) at (3,-0.5) {$x^\prime \in F(m^\prime)$};
+\node (B) at (1,0.5) {$b$};
+\node (C) at (2,0.5) {$a_2$};
+\node (C') at (2,-0.5) {$a_2^\prime$};
+\node (D) at (1,-0.5) {$b^\prime$};
+\node (E) at (3,0.5) {$d \in F(b)$};
+\node (F) at (3,-0.5) {$d^\prime \in F(b^\prime)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-$$\iota \colon F(h)(m) \to m^\prime$$
+$$\iota \colon F(h)(d) \to d^\prime$$
 is the source of the underlying map of cospans in $\mathsf{A}$, namely the morphism $f$ in $\mathsf{A}$; the target structure functor is defined similarly.
-These structure functors satisfy the equations $$SU(a)=\id_a=TU(a)$$for all objects $a$ of $\mathsf{A}$.
+These structure functors satisfy the equations $$SU(a)=1(a)=TU(a)$$for all objects $a$ of $\mathsf{A}$.
 
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a$};
-\node (B) at (1,0) {$m$};
-\node (C) at (2,0) {$b$};
-\node (D) at (1,-0.5) {$x \in F(m)$};
-\node (E) at (3,0) {$b$};
-\node (F) at (4,0) {$n$};
-\node (G) at (5,0) {$c$};
-\node (H) at (4,-0.5) {$y \in F(n)$};
+\node (A) at (0,0) {$a_1$};
+\node (B) at (1,0) {$b$};
+\node (C) at (2,0) {$a_2$};
+\node (D) at (1,-0.5) {$d \in F(b)$};
+\node (E) at (3,0) {$a_2$};
+\node (F) at (4,0) {$b^\prime$};
+\node (G) at (5,0) {$a_3$};
+\node (H) at (4,-0.5) {$d^\prime \in F(b^\prime)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 the composite $N \odot M$ is given by:
-\begin{equation}\label{eq:dcospanscomposition}
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a$};
-\node (B) at (1,1) {$m$};
-\node (C) at (2,0) {$b$};
-\node (D) at (3,1) {$n$};
-\node (E) at (4,0) {$c$};
-\node (F) at (2,2) {$m+n$};
-\node (G) at (2,3) {$m+_{b} n$};
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$a_1$};
+\node (B) at (1,1) {$b$};
+\node (C) at (2,0) {$a_2$};
+\node (D) at (3,1) {$b^\prime$};
+\node (E) at (4,0) {$a_3$};
+\node (F) at (2,2) {$b+b^\prime$};
+\node (G) at (2,3) {$b+_{a_2} b^\prime$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \end{tikzpicture}
-\end{equation}
-with the corresponding decoration of the apex $x \odot y \in F(m+_{b} n)$ given by:
-$$1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{x \times y} F(m) \times F(n) \xrightarrow{\phi_{m,n}} F(m+n) \xrightarrow{F(\psi)} F(m+_{b}n)$$
-where $\psi \colon m + n \to m+_{b} n$ is the natural map from the coproduct to the pushout and $\phi_{m,n} \colon F(m) \times F(n) \to F(m+n)$ is the natural transformation coming from the structure of the lax monoidal pseudofunctor $F \colon \mathsf{A} \to \mathbf{Cat}$.
+\]
+with the corresponding decoration of the apex $\hat{d} \in F(b+_{a_2} b^\prime)$ given by:
+$$1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{d \times d^\prime} F(b) \times F(b^\prime) \xrightarrow{\phi_{b,b^\prime}} F(b+b^\prime) \xrightarrow{F(\psi)} F(b+_{a_2}b^\prime)$$
+where $\psi \colon b + b^\prime \to b+_{a_2} b^\prime$ is the natural map from the coproduct to the pushout and $\phi_{b,b^\prime} \colon F(b) \times F(b^\prime) \to F(b+b^\prime)$ is the natural transformation coming from the structure of the lax monoidal pseudofunctor $F \colon \mathsf{A} \to \mathbf{Cat}$.
 Denoting the first and second of these horizontal 1-cells as $M$ and $N$, respectively, the source and target structure functors satisfy the equations $S(N \odot M)=S(M)$ and $T(N \odot M)=T(N)$.
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a$};
-\node (B) at (1,0) {$m_1$};
-\node (C) at (2,0) {$b$};
-\node (D) at (1,-0.5) {$x \in F(m_1)$};
-\node (E) at (3,0) {$b$};
-\node (F) at (4,0) {$m_2$};
-\node (G) at (5,0) {$c$};
-\node (H) at (4,-0.5) {$x_2 \in F(m_2)$};
-\node (I) at (6,0) {$c$};
-\node (J) at (7,0) {$m_3$};
-\node (K) at (8,0) {$d$};
-\node (L) at (7,-0.5) {$x_3 \in F(m_3)$};
+\node (A) at (0,0) {$a_1$};
+\node (B) at (1,0) {$b$};
+\node (C) at (2,0) {$a_2$};
+\node (D) at (1,-0.5) {$d_{M_1} \in F(b)$};
+\node (E) at (3,0) {$a_2$};
+\node (F) at (4,0) {$b^\prime$};
+\node (G) at (5,0) {$a_3$};
+\node (H) at (4,-0.5) {$d_{M_2} \in F(b^\prime)$};
+\node (I) at (6,0) {$a_3$};
+\node (J) at (7,0) {$b''$};
+\node (K) at (8,0) {$a_4$};
+\node (L) at (7,-0.5) {$d_{M_3} \in F(b'')$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$a$};
-\node (A') at (0,-0.5) {$a$};
-\node (B) at (1.5,0.5) {$(m_1+_{b} m_2)+_{c} m_3$};
-\node (C) at (3,0.5) {$d$};
-\node (C') at (3,-0.5) {$d$};
-\node (D) at (1.5,-0.5) {$m_1+_{b}(m_2 +_{c} m_3)$};
-\node (E) at (5.5,0.5) {$(x \odot y) \odot z \in F((m_1+_{b} m_2)+_{c} m_3)$};
-\node (F) at (5.5,-0.5) {$x \odot (y \odot z) \in F(m_1+_{b} (m_2 +_{c} m_3))$};
+\node (A) at (0,0.5) {$a_1$};
+\node (A') at (0,-0.5) {$a_1$};
+\node (B) at (1.5,0.5) {$(b+_{a_2} b^\prime)+_{a_3} b''$};
+\node (C) at (3,0.5) {$a_4$};
+\node (C') at (3,-0.5) {$a_4$};
+\node (D) at (1.5,-0.5) {$b+_{a_2}(b^\prime +_{a_3} b'')$};
+\node (E) at (5.5,0.5) {$d_{(M_1 \odot M_2) \odot M_3} \in F((b+_{a_2} b^\prime)+_{a_3} b'')$};
+\node (F) at (5.5,-0.5) {$d_{M_1 \odot (M_2 \odot M_3)} \in F(b+_{a_2} (b^\prime +_{a_3} b''))$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (C) edge node[above]{$$} (B)
-(A) edge node[left]{$\id_a$} (A')
-(C) edge node[right]{$\id_d$} (C')
+(A) edge node[left]{$1$} (A')
+(C) edge node[left]{$1$} (C')
 (A') edge node {$$} (D)
 (C') edge node {$$} (D)
-(B) edge node [left] {$\sigma$} (D);
+(B) edge node [left] {$a$} (D);
 \end{tikzpicture}
@@
 with the decorations on the cospan's apices given by:
-$$ (x \odot y) \odot z \coloneqq 1 \xrightarrow{\zeta_1} F(m_1+_{b} m_2) \times F(m_3) \xrightarrow{\phi_{m_1+_{b} m_2, m_3}} F((m_1+_{b}m_2) +m_3) \xrightarrow{F(j_{m_1+_{b} m_2,m_3})} F((m_1+_{b} m_2)+_{c} m_3)$$ $$\zeta_1 = (1 \times z) \rho^{-1} F(j_{m_1,m_2}) \phi_{m_1,m_2} (x \times y) \lambda^{-1}$$
+$$ d_{(M_1 \odot M_2) \odot M_3} \coloneqq 1 \xrightarrow{\zeta_1} F(b+_{a_2} b^\prime) \times F(b'') \xrightarrow{\phi_{b+_{a_2} b^\prime, b''}} F((b+_{a_2}b^\prime) +b'') \xrightarrow{F(j_{b+_{a_2} b^\prime,b''})} F((b+_{a_2} b^\prime)+_{a_3} b'')$$ $$\zeta_1 = d_{M_3} \lambda^{-1} F(j_{b,b^\prime}) \phi_{b,b^\prime} (d_{M_1} \times d_{M_2}) \lambda^{-1}$$
 and
-$$ x \odot (y \odot z) \coloneqq 1 \xrightarrow{\zeta_2} F(m_1) \times F(m_2 +_{c} m_3) \xrightarrow{\phi_{m_1, m_2 +_{c} m_3}} F(m_1+(m_2 +_{c} m_3)) \xrightarrow{F(j_{m_1,m_2 +_{c} m_3})} F(m_1+_{b} (m_2+_{c} m_3))$$ $$\zeta_2 = (x \times 1) \lambda^{-1} F(j_{m_2,m_3}) \phi_{m_2,m_3} (y \odot z) \lambda^{-1}$$
-together with the isomorphism $\iota_\sigma \colon F(\sigma)((x \odot y) \odot z) \to x \odot (y \odot z)$.
-Note that the map $\sigma \colon (m_1+_{b} m_2)+_{c}m_3 \to m_1+_{b}(m_2+_{c}m_3)$ is the universal map between two colimits of the same diagram.
+$$ d_{M_1 \odot (M_2 \odot M_3)} \coloneqq 1 \xrightarrow{\zeta_2} F(b) \times F(b^\prime +_{a_3} b'') \xrightarrow{\phi_{b, b^\prime +_{a_3} b''}} F(b+(b^\prime +_{a_3} b'')) \xrightarrow{F(j_{b,b^\prime +_{a_3} b''})} F(b+_{a_2} (b^\prime+_{a_3} b''))$$ $$\zeta_2 = d_{M_1} \lambda^{-1} F(j_{b^\prime,b''}) \phi_{b^\prime,b''} (d_{M_2} \times d_{M_3}) \lambda^{-1}$$
+together with the isomorphism $\iota_a \colon F(a)(d_{(M_1 \odot M_2) \odot M_3}) \to d_{M_1 \odot (M_2 \odot M_3)}$.
+Note that the map $a \colon (b+_{a_2} b')+_{a_3}b'' \to b+_{a_2}(b'+_{a_3}b'')$ is the universal map between two colimits of the same diagram.
 We also have left and right unitors where given a horizontal 1-cell $M$:
@@
 \]
-if we, say, compose with the identity horizontal 1-cell of $b$ on the right:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a$};
-\node (B) at (1,0) {$m$};
-\node (C) at (2,0) {$b$};
-\node (D) at (1,-0.5) {$x \in F(m)$};
-\node (E) at (3,0) {$b$};
-\node (F) at (4,0) {$b$};
-\node (G) at (5,0) {$b$};
-\node (H) at (4,-0.5) {$!_{b} \in F(b)$};
+if we, say, compose with the identity horizontal 1-cell of $a_2$ on the right:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$a_1$};
+\node (B) at (1,0) {$b$};
+\node (C) at (2,0) {$a_2$};
+\node (D) at (1,-0.5) {$d \in F(b)$};
+\node (E) at (3,0) {$a_2$};
+\node (F) at (4,0) {$a_2$};
+\node (G) at (5,0) {$a_2$};
+\node (H) at (4,-0.5) {$!_{a_2} \in F(a_2)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-where $!_{b} = F(!)  \phi \colon 1 \to F(b)$ is the trivial decoration on $b$, composing these then gives:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a$};
-\node (B) at (1,0) {$m+_{b} b$};
-\node (C) at (2,0) {$b$};
-\node (D) at (3.5,0) {$x \odot !_b \in F(m +_{b} b)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$j \psi_m i$} (B)
-(C) edge node[above]{$j \psi_{b}$} (B);
-\end{tikzpicture}
-\]
-where $\psi_m \colon m \to m+b$ is the natural map into the coproduct and likewise for $\psi_{b}$ and $j \colon m+b \to m+_{b} b$ is the natural map from the coproduct to the pushout.
-The decoration $x \odot !_b \colon 1 \to F(m+_{b} b)$ is given by: $$1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{x \times !_{b}} F(m) \times F(b) \xrightarrow{\phi_{m,b}} F(m+b) \xrightarrow{F(j_{m,b})} F(m+_{b} b).$$ We then have that the right unitor $R \colon M \odot 1_{b} \xrightarrow{\sim} M$ is given by the globular 2-morphism $(\id_{a},r,\id_{b})$ from the above composite to $M$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$a$};
-\node (A') at (0,-0.5) {$a$};
-\node (B) at (1.5,0.5) {$m+_{b} b$};
-\node (C) at (3,0.5) {$b$};
-\node (C') at (3,-0.5) {$b$};
-\node (D) at (1.5,-0.5) {$m$};
-\node (E) at (4.5,0.5) {$x \odot !_b \in F(m+_{b} b)$};
-\node (F) at (4.5,-0.5) {$x \in F(m)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$j \psi_m i$} (B)
-(C) edge node[above]{$j \psi_{b}$} (B)
-(A) edge node[left]{$\id_{a}$} (A')
-(C) edge node[right]{$\id_{b}$} (C')
+where $!_{a_2} = F(!)  \phi \colon 1 \to F(a_2)$ is the trivial decoration on $a_2$, composing these then gives:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$a_1$};
+\node (B) at (1,0) {$b+_{a_2} a_2$};
+\node (C) at (2,0) {$a_2$};
+\node (D) at (3.5,0) {$d_{M+!_{a_2}} \in F(b +_{a_2} a_2)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$j \psi_b i$} (B)
+(C) edge node[above]{$j \psi_{a_2}$} (B);
+\end{tikzpicture}
+\]
+where $\psi_b \colon b \to b+a_2$ is the natural map into the coproduct and likewise for $\psi_{a_2}$ and $j \colon b+a_2 \to b+_{a_2} a_2$ is the natural map from the coproduct to the pushout.
+The decoration $d_{M+!_{a_2}} \colon 1 \to F(b+_{a_2} a_2)$ is given by: $$1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{d_{M} \times !_{a_2}} F(b) \times F(a_2) \xrightarrow{\phi_{b,a_2}} F(b+a_2) \xrightarrow{F(j_{b,a_2})} F(b+_{a_2} a_2).$$ We then have that the right unitor $R \colon M \odot 1_{a_2} \xrightarrow{\sim} M$ is given by the globular 2-morphism $(\id_{a_1},r,\id_{a_2})$ from the above composite to $M$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0.5) {$a_1$};
+\node (A') at (0,-0.5) {$a_1$};
+\node (B) at (1.5,0.5) {$b+_{a_2} a_2$};
+\node (C) at (3,0.5) {$a_2$};
+\node (C') at (3,-0.5) {$a_2$};
+\node (D) at (1.5,-0.5) {$b$};
+\node (E) at (4.5,0.5) {$d_{M+!_{a_2}} \in F(b+_{a_2} a_2)$};
+\node (F) at (4.5,-0.5) {$d_{M} \in F(b)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$j \psi_b i$} (B)
+(C) edge node[above]{$j \psi_{a_2}$} (B)
+(A) edge node[left]{$\id_{a_1}$} (A')
+(C) edge node[left]{$\id_{a_2}$} (C')
 (A') edge node [above]{$i$} (D)
@@
 \]
-where $r \colon m+_{b} b \xrightarrow{\sim} m$ is a universal map together with the isomorphism $\iota_r \colon F(r)(x \odot !_b) \to x$.
+where $r \colon b+_{a_2} a_2 \xrightarrow{\sim} b$ is a universal map together with the isomorphism $\iota_r \colon F(r)(d_{M+!_{a_2}}) \to d_M$.
 The left unitor is similar.
-The source and target functor applied to the left and right unitors and associators yield identities, and the left and right unitors together with the associator satisfy the standard pentagon and triangle identities of a monoidal category or bicategory.
+The source and target functor applied to the left and right unitors and associators yield identities.
+The left and right unitors together with the associator satisfy the standard pentagon and triangle identities of a monoidal category or bicategory.
 Finally, for the interchange law, given four 2-morphisms $\alpha, \beta, \alpha^\prime$ and $\beta^\prime$:
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$a$};
-\node (A') at (0,-0.5) {$a'$};
-\node (B) at (1,0.5) {$m$};
-\node (C) at (2,0.5) {$b$};
-\node (C') at (2,-0.5) {$b^\prime$};
-\node (D) at (1,-0.5) {$m^\prime$};
-\node (E) at (3,0.5) {$x \in F(m)$};
-\node (F) at (3,-0.5) {$x' \in F(m^\prime)$};
-\node (G) at (4,0.5) {$b$};
-\node (H) at (5,0.5) {$n$};
-\node (I) at (6,0.5) {$c$};
-\node (G') at (4,-0.5) {$b^\prime$};
-\node (H') at (5,-0.5) {$n^\prime$};
-\node (I') at (6,-0.5) {$c^\prime$};
-\node (J) at (7,0.5) {$y \in F(n)$};
-\node (K) at (7,-0.5) {$y' \in F(n^\prime)$};
-\node (L) at (1,-1) {$\iota_\alpha \colon F(h_1)(x) \to x'$};
-\node (M) at (5,-1) {$\iota_\beta \colon F(h_2)(y) \to y'$};
-\node (A'') at (0,-1.5) {$a^\prime$};
-\node (A''') at (0,-2.5) {$a''$};
-\node (B'') at (1,-1.5) {$m^\prime$};
-\node (C'') at (2,-1.5) {$b^\prime$};
-\node (C''') at (2,-2.5) {$b''$};
-\node (D'') at (1,-2.5) {$m''$};
-\node (E'') at (3,-1.5) {$x' \in F(m^\prime)$};
-\node (F'') at (3,-2.5) {$x'' \in F(m'')$};
-\node (G'') at (4,-1.5) {$b^\prime$};
-\node (H'') at (5,-1.5) {$n^\prime$};
-\node (I'') at (6,-1.5) {$c^\prime$};
-\node (G''') at (4,-2.5) {$b''$};
-\node (H''') at (5,-2.5) {$n''$};
-\node (I''') at (6,-2.5) {$c''$};
-\node (J'') at (7,-1.5) {$y' \in F(n^\prime)$};
-\node (K'') at (7,-2.5) {$y'' \in F(n'')$};
-\node (L'') at (1,-3) {$\iota_{\alpha^\prime} \colon F(h_1^\prime)(x') \to x''$};
-\node (M'') at (5,-3) {$\iota_{\beta^\prime} \colon F(h_2^\prime)(y') \to y''$};
+\node (A) at (0,0.5) {$a_1$};
+\node (A') at (0,-0.5) {$a_1^\prime$};
+\node (B) at (1,0.5) {$b$};
+\node (C) at (2,0.5) {$a_2$};
+\node (C') at (2,-0.5) {$a_2^\prime$};
+\node (D) at (1,-0.5) {$b^\prime$};
+\node (E) at (3,0.5) {$d_{M_1} \in F(b)$};
+\node (F) at (3,-0.5) {$d_{M_2} \in F(b^\prime)$};
+\node (G) at (4,0.5) {$a_2$};
+\node (H) at (5,0.5) {$c$};
+\node (I) at (6,0.5) {$a_3$};
+\node (G') at (4,-0.5) {$a_2^\prime$};
+\node (H') at (5,-0.5) {$c^\prime$};
+\node (I') at (6,-0.5) {$a_3^\prime$};
+\node (J) at (7,0.5) {$d_{N_1} \in F(c)$};
+\node (K) at (7,-0.5) {$d_{N_2} \in F(c^\prime)$};
+\node (L) at (1,-1) {$\iota_\alpha \colon F(h_1)(d_{M_1}) \to d_{M_2}$};
+\node (M) at (5,-1) {$\iota_\beta \colon F(h_2)(d_{N_1}) \to d_{N_2}$};
+\node (A'') at (0,-1.5) {$a_1^\prime$};
+\node (A''') at (0,-2.5) {$a_1''$};
+\node (B'') at (1,-1.5) {$b^\prime$};
+\node (C'') at (2,-1.5) {$a_2^\prime$};
+\node (C''') at (2,-2.5) {$a_2''$};
+\node (D'') at (1,-2.5) {$b''$};
+\node (E'') at (3,-1.5) {$d_{M_2} \in F(b^\prime)$};
+\node (F'') at (3,-2.5) {$d_{M_3} \in F(b'')$};
+\node (G'') at (4,-1.5) {$a_2^\prime$};
+\node (H'') at (5,-1.5) {$c^\prime$};
+\node (I'') at (6,-1.5) {$a_3^\prime$};
+\node (G''') at (4,-2.5) {$a_2''$};
+\node (H''') at (5,-2.5) {$c''$};
+\node (I''') at (6,-2.5) {$a_3''$};
+\node (J'') at (7,-1.5) {$d_{N_2} \in F(b^\prime)$};
+\node (K'') at (7,-2.5) {$d_{N_3} \in F(b'')$};
+\node (L'') at (1,-3) {$\iota_{\alpha^\prime} \colon F(h_1^\prime)(d_{M_2}) \to d_{M_3}$};
+\node (M'') at (5,-3) {$\iota_{\beta^\prime} \colon F(h_2^\prime)(d_{N_2}) \to d_{N_3}$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (A) edge node[left]{$f$} (A')
-(C) edge node[right]{$g$} (C')
+(C) edge node[left]{$g$} (C')
 (A') edge node[above] {$i_1^\prime$} (D)
@@
 (I) edge node [above] {$o_2$} (H)
-(I) edge node [right] {$k$} (I')
+(I) edge node [left] {$k$} (I')
 (I') edge node [above] {$o_2^\prime$} (H')
@@
 (A'') edge node[left]{$f^\prime$} (A''')
-(C'') edge node[right]{$g^\prime$} (C''')
+(C'') edge node[left]{$g^\prime$} (C''')
 (A''') edge node[above] {$i_1''$} (D'')
@@
 (I'') edge node [above] {$o_2^\prime$} (H'')
-(I'') edge node [right] {$k^\prime$} (I''')
+(I'') edge node [left] {$k^\prime$} (I''')
 (I''') edge node [above] {$o_2''$} (H''');
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$a$};
-\node (A') at (0,-0.5) {$a^\prime$};
-\node (B) at (1.5,0.5) {$m+_{b} n$};
-\node (C) at (3,0.5) {$c$};
-\node (C') at (3,-0.5) {$c^\prime$};
-\node (D) at (1.5,-0.5) {$m' +_{b'} n^\prime$};
-\node (E) at (4.5,0.5) {$x \odot y \in F(m+_{b} n)$};
-\node (F) at (4.5,-0.5) {$x' \odot y' \in F(m^\prime +_{b'} n^\prime)$};
-\node (G) at (1.5,-1) {$\iota_{\alpha \odot \beta} \colon F(h_1 +_g h_2)(x \odot y) \to x' \odot y'$};
-\node (A'') at (0,-1.5) {$a^\prime$};
-\node (A''') at (0,-2.5) {$a''$};
-\node (B'') at (1.5,-1.5) {$m^\prime +_{b\prime} n^\prime$};
-\node (C'') at (3,-1.5) {$c^\prime$};
-\node (C''') at (3,-2.5) {$c''$};
-\node (D'') at (1.5,-2.5) {$m'' +_{b''} n''$};
-\node (E'') at (4.5,-1.5) {$x' \odot y' \in F(m^\prime+_{b^\prime} n^\prime)$};
-\node (F'') at (4.5,-2.5) {$x'' \odot y'' \in F(m'' +_{b''} n'')$};
-\node (G'') at (1.5,-3) {$\iota_{\alpha^\prime \odot \beta^\prime} \colon F(h_1^\prime +_{g^\prime} h_2^\prime)(x' \odot y') \to x'' \odot y''.$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$j \psi_{m} i_1$} (B)
-(C) edge node[above]{$j \psi_{n} o_2$} (B)
+\node (A) at (0,0.5) {$a_1$};
+\node (A') at (0,-0.5) {$a_1^\prime$};
+\node (B) at (1.5,0.5) {$b+_{a_2} c$};
+\node (C) at (3,0.5) {$a_3$};
+\node (C') at (3,-0.5) {$a_3^\prime$};
+\node (D) at (1.5,-0.5) {$b^\prime +_{a_2^\prime} c^\prime$};
+\node (E) at (4.5,0.5) {$d_{M_1 \odot N_1} \in F(b+_{a_2} c)$};
+\node (F) at (4.5,-0.5) {$d_{M_2 \odot N_2} \in F(b^\prime +_{a_2^\prime} c^\prime)$};
+\node (G) at (1.5,-1) {$\iota_{\alpha \odot \beta} \colon F(h_1 +_g h_2)(d_{M_1 \odot N_1}) \to d_{M_1^\prime \odot N_1^\prime}$};
+\node (A'') at (0,-1.5) {$a_1^\prime$};
+\node (A''') at (0,-2.5) {$a_1''$};
+\node (B'') at (1.5,-1.5) {$b^\prime +_{a_2^\prime} c^\prime$};
+\node (C'') at (3,-1.5) {$a_3^\prime$};
+\node (C''') at (3,-2.5) {$a_3''$};
+\node (D'') at (1.5,-2.5) {$b'' +_{a_2''} c''$};
+\node (E'') at (4.5,-1.5) {$d_{M_2 \odot N_2} \in F(b^\prime+_{a_2^\prime} c^\prime)$};
+\node (F'') at (4.5,-2.5) {$d_{M_3 \odot N_3} \in F(b'' +_{a_2''} c'')$};
+\node (G'') at (1.5,-3) {$\iota_{\alpha^\prime \odot \beta^\prime} \colon F(h_1^\prime +_{g^\prime} h_2^\prime)(d_{M_2 \odot N_2}) \to d_{M_3 \odot N_3}.$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$j \psi_{a_1} i_1$} (B)
+(C) edge node[above]{$j \psi_{a_3} o_2$} (B)
 (A) edge node[left]{$f$} (A')
-(C) edge node[right]{$k$} (C')
-(A') edge node [above]{$j \psi_{m^\prime} i_1^\prime$} (D)
-(C') edge node [above]{$j \psi_{n^\prime} o_2^\prime$} (D)
+(C) edge node[left]{$k$} (C')
+(A') edge node [above]{$j \psi_{a_1^\prime} i_1^\prime$} (D)
+(C') edge node [above]{$j \psi_{a_3^\prime} o_2^\prime$} (D)
 (B) edge node [left] {$h_1 +_g h_2$} (D)
-(A'') edge node[above]{$j \psi_{m^\prime} i_1^\prime$} (B'')
-(C'') edge node[above]{$j \psi_{n^\prime} o_2^\prime$} (B'')
+(A'') edge node[above]{$j \psi_{a_1^\prime} i_1^\prime$} (B'')
+(C'') edge node[above]{$j \psi_{a_3^\prime} o_2^\prime$} (B'')
 (A'') edge node[left]{$f^\prime$} (A''')
-(C'') edge node[right]{$k^\prime$} (C''')
-(A''') edge node [above]{$j \psi_{m''} i_1''$} (D'')
-(C''') edge node [above]{$j \psi_{n''} o_2''$} (D'')
+(C'') edge node[left]{$k^\prime$} (C''')
+(A''') edge node [above]{$j \psi_{a_1''} i_1''$} (D'')
+(C''') edge node [above]{$j \psi_{a_3''} o_2''$} (D'')
 (B'') edge node [left] {$h_1^\prime +_{g^\prime} h_2^\prime$} (D'');
@@
 \node (D) at (3,0) {$1$};
-\node (E) at (4.5,0.5) {$F(m)$};
-\node (E') at (4.5,-0.5) {$F(m^\prime)$};
+\node (E) at (4.5,0.5) {$F(b)$};
+\node (E') at (4.5,-0.5) {$F(b^\prime)$};
 \node (A') at (6.5,0) {$\iota_\beta \Swarrow$};
 \node (D') at (5.5,0) {$1$};
-\node (E'') at (7,0.5) {$F(n)$};
-\node (E''') at (7,-0.5) {$F(n^\prime)$};
-\path[->,font=\scriptsize,>=angle 90]
-(D) edge node [above] {$x$} (E)
-(D) edge node [below] {$x'$} (E')
+\node (E'') at (7,0.5) {$F(c)$};
+\node (E''') at (7,-0.5) {$F(c^\prime)$};
+\path[->,font=\scriptsize,>=angle 90]
+(D) edge node [above] {$d_{M_1}$} (E)
+(D) edge node [below] {$d_{M_2}$} (E')
 (E) edge node [right] {$F(h_1)$} (E')
-(D') edge node [above] {$y$} (E'')
-(D') edge node [below] {$y'$} (E''')
+(D') edge node [above] {$d_{N_1}$} (E'')
+(D') edge node [below] {$d_{N_2}$} (E''')
 (E'') edge node [right] {$F(h_2)$} (E''');
@@
 \node (D) at (3,0) {$1 \xrightarrow{\lambda^{-1}} 1 \times 1$};
-\node (E) at (5.5,0.5) {$F(m) \times F(n)$};
-\node (E') at (5.5,-0.5) {$F(m^\prime) \times F(n^\prime)$};
-\node (B) at (7.5,0.5) {$F(m+n)$};
-\node (B') at (7.5,-0.5) {$F(m^\prime + n^\prime)$};
-\node (C) at (9.25,0.5) {$F(m+_{b} n)$};
-\node (C') at (9.25,-0.5) {$F(m^\prime +_{b^\prime} n^\prime)$};
-\path[->,font=\scriptsize,>=angle 90]
-(E) edge node [above] {$\phi_{m,n}$} (B)
-(E') edge node [above] {$\phi_{m^\prime,n^\prime}$} (B')
-(B) edge node [above] {$F(j_{m,n})$} (C)
-(B') edge node [above] {$F(j_{m^\prime,n^\prime})$} (C')
+\node (E) at (5.5,0.5) {$F(b) \times F(c)$};
+\node (E') at (5.5,-0.5) {$F(b^\prime) \times F(c^\prime)$};
+\node (B) at (7.5,0.5) {$F(b+c)$};
+\node (B') at (7.5,-0.5) {$F(b^\prime + c^\prime)$};
+\node (C) at (9.25,0.5) {$F(b+_{a_2} c)$};
+\node (C') at (9.25,-0.5) {$F(b^\prime +_{a_2^\prime} c^\prime)$};
+\path[->,font=\scriptsize,>=angle 90]
+(E) edge node [above] {$\phi_{b,c}$} (B)
+(E') edge node [above] {$\phi_{b^\prime,c^\prime}$} (B')
+(B) edge node [above] {$F(j_{b,c})$} (C)
+(B') edge node [above] {$F(j_{b^\prime,c^\prime})$} (C')
 (C) edge node [right] {$F(h_1 +_g h_2)$} (C')
 (B) edge node [right] {$F(h_1 + h_2)$} (B')
-(D) edge node [above] {$x \times y$} (E)
-(D) edge node [below] {$x' \times y'$} (E')
+(D) edge node [above] {$d_{M_1} \times d_{N_1}$} (E)
+(D) edge node [below] {$d_{M_2} \times d_{N_2}$} (E')
 (E) edge node [right] {$F(h_1) \times F(h_2)$} (E');
@@
 where the middle square commutes since $F$ is a lax monoidal pseudofunctor and the right square commutes as the underlying diagram commutes.
-The decorations $x \odot y$ and $x' \odot y'$ are given respectively by top and bottom composite of arrows and the morphism of decorations $\iota_{\alpha \odot \beta}$ is given by composing $\iota_\alpha \times \iota_\beta$ with the two commuting squares, which can equivalently be viewed as a morphism in $F(m' +_{b'} n')$.
+The decorations $d_{M_1 \odot N_1}$ and $d_{M_2 \odot N_2}$ are given respectively by top and bottom composite of arrows and the morphism of decorations $\iota_{\alpha \odot \beta}$ is given by composing $\iota_\alpha \times \iota_\beta$ with the two commuting squares, which can equivalently be viewed as a morphism in $F(b' +_{a_2'} c')$.
 
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$a$};
-\node (A') at (0,-0.5) {$a''$};
-\node (B) at (2,0.5) {$m+_{b} n$};
-\node (C) at (4,0.5) {$c$};
-\node (C') at (4,-0.5) {$c''$};
-\node (D) at (2,-0.5) {$m'' +_{b''} n''$};
-\node (E) at (5.5,0.5) {$x \odot y \in F(m+_{b} n)$};
-\node (F) at (5.5,-0.5) {$x'' \odot y'' \in F(m'' +_{b''} n'')$};
-\node (G) at (2,-1) {$\iota_{(a^\prime \odot \beta^\prime)(\alpha \odot \beta)} \colon F((h_1^\prime +_{g^\prime} h_2^\prime)(h_1 +_g h_2))(x \odot y) \to x'' \odot y''.$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$j \psi_{m} i_1$} (B)
-(C) edge node[above]{$j \psi_{n} o_2$} (B)
+\node (A) at (0,0.5) {$a_1$};
+\node (A') at (0,-0.5) {$a_1''$};
+\node (B) at (2,0.5) {$b+_{a_2} c$};
+\node (C) at (4,0.5) {$a_3$};
+\node (C') at (4,-0.5) {$a_3''$};
+\node (D) at (2,-0.5) {$b'' +_{a_2''} c''$};
+\node (E) at (5.5,0.5) {$d_{M_1 \odot N_1} \in F(b+_{a_2} c)$};
+\node (F) at (5.5,-0.5) {$d_{M_3 \odot N_3} \in F(b'' +_{a_2''} c'')$};
+\node (G) at (2,-1) {$\iota_{(a^\prime \odot \beta^\prime)(\alpha \odot \beta)} \colon F((h_1^\prime +_{g^\prime} h_2^\prime)(h_1 +_g h_2))(d_{M_1 \odot N_1}) \to d_{M_3 \odot N_3}.$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$j \psi_{a_1} i_1$} (B)
+(C) edge node[above]{$j \psi_{a_3} o_2$} (B)
 (A) edge node[left]{$f^\prime f$} (A')
-(C) edge node[right]{$k^\prime k$} (C')
-(A') edge node [above]{$j \psi_{m''} i_1''$} (D)
-(C') edge node [above]{$j \psi_{n''} o_2''$} (D)
+(C) edge node[left]{$k^\prime k$} (C')
+(A') edge node [above]{$j \psi_{a_1''} i_1''$} (D)
+(C') edge node [above]{$j \psi_{a_3''} o_2''$} (D)
 (B) edge node [left] {$(h_1^\prime +_{g^\prime} h_2^\prime)(h_1 +_g h_2)$} (D);
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$a$};
-\node (A') at (0,-0.5) {$a''$};
-\node (B) at (1,0.5) {$m$};
-\node (C) at (2,0.5) {$b$};
-\node (C') at (2,-0.5) {$b''$};
-\node (D) at (1,-0.5) {$m''$};
-\node (E) at (3,0.5) {$x \in F(m)$};
-\node (F) at (3,-0.5) {$x'' \in F(m'')$};
-\node (G) at (4,0.5) {$b$};
-\node (H) at (5,0.5) {$n$};
-\node (I) at (6,0.5) {$c$};
-\node (G') at (4,-0.5) {$b''$};
-\node (H') at (5,-0.5) {$n''$};
-\node (I') at (6,-0.5) {$c''$};
-\node (J) at (7,0.5) {$y \in F(n)$};
-\node (K) at (7,-0.5) {$y'' \in F(n'')$};
-\node (L) at (1,-1) {$\iota_{\alpha^\prime \alpha} \colon F(h_1^\prime h_1)(x) \to x''$};
-\node (M) at (5,-1) {$\iota_{\beta^\prime \beta} \colon F(h_2^\prime h_2)(y) \to y''$};
+\node (A) at (0,0.5) {$a_1$};
+\node (A') at (0,-0.5) {$a_1''$};
+\node (B) at (1,0.5) {$b$};
+\node (C) at (2,0.5) {$a_2$};
+\node (C') at (2,-0.5) {$a_2''$};
+\node (D) at (1,-0.5) {$b''$};
+\node (E) at (3,0.5) {$d_{M_1} \in F(b)$};
+\node (F) at (3,-0.5) {$d_{M_3} \in F(b'')$};
+\node (G) at (4,0.5) {$a_2$};
+\node (H) at (5,0.5) {$c$};
+\node (I) at (6,0.5) {$a_3$};
+\node (G') at (4,-0.5) {$a_2''$};
+\node (H') at (5,-0.5) {$c''$};
+\node (I') at (6,-0.5) {$a_3''$};
+\node (J) at (7,0.5) {$d_{N_1} \in F(c)$};
+\node (K) at (7,-0.5) {$d_{N_3} \in F(c'')$};
+\node (L) at (1,-1) {$\iota_{\alpha^\prime \alpha} \colon F(h_1^\prime h_1)(d_{M_1}) \to d_{M_3}$};
+\node (M) at (5,-1) {$\iota_{\beta^\prime \beta} \colon F(h_2^\prime h_2)(d_{N_1}) \to d_{N_3}$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (A) edge node[left]{$f^\prime f$} (A')
-(C) edge node[right]{$g^\prime g$} (C')
+(C) edge node[left]{$g^\prime g$} (C')
 (A') edge node[above] {$i_1''$} (D)
@@
 (I) edge node [above] {$o_2$} (H)
-(I) edge node [right] {$k^\prime k$} (I')
+(I) edge node [left] {$k^\prime k$} (I')
 (I') edge node [above] {$o_2''$} (H');
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$a$};
-\node (A') at (0,-0.5) {$a''$};
-\node (B) at (2,0.5) {$m+_{b} n$};
-\node (C) at (4,0.5) {$c$};
-\node (C') at (4,-0.5) {$c''$};
-\node (D) at (2,-0.5) {$m'' +_{b''} n''$};
-\node (E) at (5.5,0.5) {$x \odot y \in F(m+_{b} n)$};
-\node (F) at (5.5,-0.5) {$x'' \odot y'' \in F(m'' +_{b''} n'')$};
-\node (G) at (2,-1) {$\iota_{(\alpha^\prime \alpha) \odot (\beta^\prime \beta)} \colon F((h_1^\prime h_1)+_{g^\prime g} (h_2^\prime h_2))(x \odot y) \to x'' \odot y''.$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$j \psi_{m} i_1$} (B)
-(C) edge node[above]{$j \psi_{n} o_2$} (B)
+\node (A) at (0,0.5) {$a_1$};
+\node (A') at (0,-0.5) {$a_1''$};
+\node (B) at (2,0.5) {$b+_{a_2} c$};
+\node (C) at (4,0.5) {$a_3$};
+\node (C') at (4,-0.5) {$a_3''$};
+\node (D) at (2,-0.5) {$b'' +_{a_2''} c''$};
+\node (E) at (5.5,0.5) {$d_{M_1 \odot N_1} \in F(b+_{a_2} c)$};
+\node (F) at (5.5,-0.5) {$d_{M_3 \odot N_3} \in F(b'' +_{a_3''} c'')$};
+\node (G) at (2,-1) {$\iota_{(\alpha^\prime \alpha) \odot (\beta^\prime \beta)} \colon F((h_1^\prime h_1)+_{g^\prime g} (h_2^\prime h_2))(d_{M_1 \odot N_1}) \to d_{M_3 \odot N_3}.$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$j \psi_{a_1} i_1$} (B)
+(C) edge node[above]{$j \psi_{a_3} o_2$} (B)
 (A) edge node[left]{$f^\prime f$} (A')
-(C) edge node[right]{$k^\prime k$} (C')
-(A') edge node [above]{$j \psi_{m''} i_1''$} (D)
-(C') edge node [above]{$j \psi_{n''} o_2''$} (D)
+(C) edge node[left]{$k^\prime k$} (C')
+(A') edge node [above]{$j \psi_{a_1''} i_1''$} (D)
+(C') edge node [above]{$j \psi_{a_3''} o_2''$} (D)
 (B) edge node [left] {$(h_1^\prime h_1) +_{g^\prime g} (h_2^\prime h_2)$} (D);
@@
 %\]
-As is usual concerning the interchange law of double categories of this nature, only the `interior' of the two composites appears different, but the two morphisms $(h_1^\prime +_{g^\prime} h_2^\prime)(h_1 +_g h_2) \colon m+_{b} n \to m'' +_{b''} n''$ and $(h_1^\prime h_1) +_{g^\prime g} (h_2^\prime h_2) \colon m+_{b} n \to m'' +_{b''}n''$ are the same universal map realized in two different ways.
+As is usual concerning the interchange law of double categories of this nature, only the `interior' of the two compositions appears different, but the two morphisms $(h_1^\prime +_{g^\prime} h_2^\prime)(h_1 +_g h_2) \colon b+_{a_2} c \to b'' +_{a_2''} c''$ and $(h_1^\prime h_1) +_{g^\prime g} (h_2^\prime h_2) \colon b+_{a_2} c \to b'' +_{a_2''}c''$ are the same universal map realized in two different ways.
 The two morphisms of decorations $\iota_{(\alpha^\prime \odot \beta^\prime)(\alpha \odot \beta)}$ and $\iota_{(\alpha^\prime \alpha) \odot (\beta^\prime \beta)}$ are obtained as two different compositions of four 2-morphisms in $\mathbf{Cat}$, namely horizontally then vertically and vertically then horizontally.
-As $\mathbf{Cat}$ is a 2-category, the interchange law for these 2-morphisms already holds, and as a result, the morphisms $$\iota_{(\alpha' \odot \beta')(\alpha \odot \beta)} \colon F((h_1^\prime +_{g^\prime} h_2^\prime)(h_1 +_g h_2))(x \odot y) \to x'' \odot y''$$ and $$\iota_{(\alpha^\prime \alpha)\odot(\beta^\prime \beta)} \colon F((h_1^\prime h_1)+_{g^\prime g} (h_2^\prime h_2))(x \odot y) \to x'' \odot y''$$ are also the same.
+As $\mathbf{Cat}$ is a 2-category, the interchange law for these 2-morphisms already holds, and as a result, the morphisms $$\iota_{(\alpha' \odot \beta')(\alpha \odot \beta)} \colon F((h_1^\prime +_{g^\prime} h_2^\prime)(h_1 +_g h_2))(d_{M_1 \odot N_1}) \to d_{M_3 \odot N_3}$$ and $$\iota_{(\alpha^\prime \alpha)\odot(\beta^\prime \beta)} \colon F((h_1^\prime h_1)+_{g^\prime g} (h_2^\prime h_2))(d_{M_1 \odot N_1}) \to d_{M_3 \odot N_3}$$ are also the same.
 Thus the interchange law for 2-morphisms holds and $F\mathbb{C}$sp is a double category.
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a$};
-\node (B) at (1,0) {$m$};
-\node (C) at (2,0) {$b$};
-\node (D) at (3,0) {$x \in F(b)$};
+\node (A) at (0,0) {$a_1$};
+\node (B) at (1,0) {$b$};
+\node (C) at (2,0) {$a_2$};
+\node (D) at (3,0) {$d \in F(b)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$a$};
-\node (A') at (0,-0.5) {$a^\prime$};
-\node (B) at (1,0.5) {$m$};
-\node (C) at (2,0.5) {$b$};
-\node (C') at (2,-0.5) {$b^\prime$};
-\node (D) at (1,-0.5) {$m^\prime$};
-\node (E) at (3,0.5) {$x \in F(m)$};
-\node (F) at (3,-0.5) {$x^\prime \in F(m^\prime)$};
+\node (A) at (0,0.5) {$a_1$};
+\node (A') at (0,-0.5) {$a_1^\prime$};
+\node (B) at (1,0.5) {$b$};
+\node (C) at (2,0.5) {$a_2$};
+\node (C') at (2,-0.5) {$a_2^\prime$};
+\node (D) at (1,-0.5) {$b^\prime$};
+\node (E) at (3,0.5) {$d \in F(b)$};
+\node (F) at (3,-0.5) {$d^\prime \in F(b^\prime)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (A) edge node[left]{$f$} (A')
-(C) edge node[right]{$g$} (C')
+(C) edge node[left]{$g$} (C')
 (A') edge node [above]{$i^\prime$} (D)
@@
 \]
-together with a morphism $\iota \colon F(h)(x) \to x^\prime$.
+together with a morphism $\iota \colon F(h)(d) \to d^\prime$.
 }
@@
 \node (A) at (0,0) {$a_1$};
-\node (B) at (1,0) {$m_1$};
-\node (C) at (2,0) {$b_1$};
-\node (D) at (1,-0.5) {$x_1 \in F(m_1)$};
-\node (E) at (3,0) {$a_2$};
-\node (F) at (4,0) {$m_2$};
-\node (G) at (5,0) {$b_2$};
-\node (H) at (4,-0.5) {$x_2 \in F(m_2)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i_1$} (B)
-(C) edge node[above]{$o_1$} (B)
-(E) edge node[above]{$i_2$} (F)
-(G) edge node[above]{$o_2$} (F);
+\node (B) at (1,0) {$b$};
+\node (C) at (2,0) {$a_2$};
+\node (D) at (1,-0.5) {$d_{M_1} \in F(b)$};
+\node (E) at (3,0) {$a_1^\prime$};
+\node (F) at (4,0) {$b^\prime$};
+\node (G) at (5,0) {$a_2^\prime$};
+\node (H) at (4,-0.5) {$d_{M_2} \in F(b^\prime)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i$} (B)
+(C) edge node[above]{$o$} (B)
+(E) edge node[above]{$i^\prime$} (F)
+(G) edge node[above]{$o^\prime$} (F);
 \end{tikzpicture}
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a_1+a_2$};
-\node (B) at (1.25,0) {$m_1+m_2$};
-\node (C) at (2.5,0) {$b_1+b_2$};
-\node (D) at (4.25,0) {$x_1+x_2 \in F(m_1+m_2)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i_1+i_2$} (B)
-(C) edge node[above]{$o_1+o_2$} (B);
-\end{tikzpicture}
-\]
-and where the decoration on the apex is obtained using the natural transformation of the symmetric lax monoidal pseudofunctor $F:$ $$x_1+x_2 \coloneqq 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{x_1 \times x_2} F(m_1) \times F(m_2) \xrightarrow{\phi_{m_1,m_2}} F(m_1+m_2).$$The monoidal unit 0 is given by:
+\node (A) at (0,0) {$a_1+a_1^\prime$};
+\node (B) at (1.25,0) {$b+b^\prime$};
+\node (C) at (2.5,0) {$a_2+a_2^\prime$};
+\node (D) at (4.25,0) {$d_{M_1 \otimes M_2} \in F(b+b')$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i+i'$} (B)
+(C) edge node[above]{$o+o'$} (B);
+\end{tikzpicture}
+\]
+and where the decoration on the apex is obtained using the natural transformation of the symmetric lax monoidal pseudofunctor $F:$ $$d_{M_1 \otimes M_2} \coloneqq 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{d_{M_1} \times d_{M_2}} F(b) \times F(b') \xrightarrow{\phi_{b,b'}} F(b+b').$$The monoidal unit 0 is given by:
 \[
@@
 \node (D) at (1,-0.5) {$!_0 \in F(0)$};
-\node (E) at (3,0) {$a$};
-\node (F) at (4,0) {$m$};
-\node (G) at (5,0) {$b$};
-\node (H) at (4,-0.5) {$x \in F(m)$};
+\node (E) at (3,0) {$a_1$};
+\node (F) at (4,0) {$b$};
+\node (G) at (5,0) {$a_2$};
+\node (H) at (4,-0.5) {$d_M \in F(b)$};
 \node (I) at (2.5,0) {$\otimes$};
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$0+a$};
-\node (B) at (1,0) {$0+m$};
-\node (C) at (2,0) {$0+b$};
-\node (D) at (3.5,0) {$!_0 + x \in F(0+m)$};
+\node (A) at (0,0) {$0+a_1$};
+\node (B) at (1,0) {$0+b$};
+\node (C) at (2,0) {$0+a_2$};
+\node (D) at (3.5,0) {$d_{0 \otimes M} \in F(0+b)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-where $!_0 + x \in F(0+m)$ is given by $$1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{!_0 \times x} F(0) \times F(m) \xrightarrow{\phi_{0,m}} F(0+m).$$The left unitor is then an isomorphism in $F\mathbb{C}\textnormal{sp}_1$ given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$0+a$};
-\node (A') at (0,-0.5) {$a$};
-\node (B) at (1,0.5) {$0+m$};
-\node (C) at (2,0.5) {$0+b$};
-\node (C') at (2,-0.5) {$b$};
-\node (D) at (1,-0.5) {$m$};
-\node (E) at (3.5,0.5) {$!_0 + x \in F(0+m)$};
-\node (F) at (3.5,-0.5) {$x \in F(m)$};
+where $d_{0\otimes M} \in F(0+b)$ is given by $$1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{!_0 \times d_M} F(0) \times F(b) \xrightarrow{\phi_{0,b}} F(0+b).$$The left unitor is then an isomorphism in $F\mathbb{C}\textnormal{sp}_1$ given by:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0.5) {$0+a_1$};
+\node (A') at (0,-0.5) {$a_1$};
+\node (B) at (1,0.5) {$0+b$};
+\node (C) at (2,0.5) {$0+a_2$};
+\node (C') at (2,-0.5) {$a_2$};
+\node (D) at (1,-0.5) {$b$};
+\node (E) at (3.5,0.5) {$d_{0+M} \in F(0+b)$};
+\node (F) at (3.5,-0.5) {$d_M \in F(b)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (A) edge node[left]{$\ell$} (A')
-(C) edge node[right]{$\ell$} (C')
+(C) edge node[left]{$\ell$} (C')
 (A') edge node [above]{$i$} (D)
@@
 \]
-where $\ell$ is the left unitor of $(\mathsf{A},+,0)$, together with the isomorphism $\iota_{\lambda} \colon F(\ell)(!_0 + x) \to x$. The right unitor is similar.
+where $\ell$ is the left unitor of $(\mathsf{A},+,0)$, together with the isomorphism $\iota_{\lambda} \colon F(\ell)(d_{0 \otimes M}) \to d_M$. The right unitor is similar.
 
@@
 \node (A) at (0,0) {$a_1$};
-\node (B) at (1,0) {$m_1$};
+\node (B) at (1,0) {$c_1$};
 \node (C) at (2,0) {$b_1$};
-\node (D) at (1,-0.5) {$x_1 \in F(m_1)$};
+\node (D) at (1,-0.5) {$d_{M_1} \in F(c_1)$};
 \node (E) at (3,0) {$a_2$};
-\node (F) at (4,0) {$m_2$};
+\node (F) at (4,0) {$c_2$};
 \node (G) at (5,0) {$b_2$};
-\node (H) at (4,-0.5) {$x_2 \in F(m_2)$};
+\node (H) at (4,-0.5) {$d_{M_2} \in F(c_2)$};
 \node (I) at (6,0) {$a_3$};
-\node (J) at (7,0) {$m_3$};
+\node (J) at (7,0) {$c_3$};
 \node (K) at (8,0) {$b_3$};
-\node (L) at (7,-0.5) {$x_3 \in F(m_3)$};
+\node (L) at (7,-0.5) {$d_{M_3} \in F(c_3)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \node (A) at (0,0) {$(a_1+a_2)+a_3$};
-\node (B) at (2.25,0){$(m_1+m_2)+m_3$};
+\node (B) at (2.25,0){$(c_1+c_2)+c_3$};
 \node (C) at (4.5,0) {$(b_1+b_2)+b_3$};
-\node (D) at (2.25,-0.5) {$(x_1+x_2)+x_3 \in F((m_1+m_2)+m_3)$};
+\node (D) at (2.25,-0.5) {$d_{(M_1 \otimes M_2) \otimes M_3} \in F((c_1+c_2)+c_3)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-where $(x_1+x_2)+x_3 \colon 1 \to F((m_1+m_2)+m_3)$ is given by: $$1 \xrightarrow{(x_1 \times x_2) \times x_3} (F(m_1) \times F(m_2)) \times F(m_3) \xrightarrow{\phi_{m_1,m_2} \times 1} F(m_1+m_2) \times F(m_3) \xrightarrow{\phi_{m_1+m_2,m_3}} F((m_1+m_2)+m_3)$$whereas tensoring the last two and then the first results in $M_1 \otimes (M_2 \otimes M_3)$:
+where $d_{(M_1 \otimes M_2) \otimes M_3} \colon 1 \to F((c_1+c_2)+c_3)$ is given by: $$1 \xrightarrow{(d_{M_1} \times d_{M_2}) \times d_{M_3})} (F(c_1) \times F(c_2)) \times F(c_3) \xrightarrow{\phi_{c_1,c_2} \times 1} F(c_1+c_2) \times F(c_3) \xrightarrow{\phi_{c_1+c_2,c_3}} F((c_1+c_2)+c_3)$$whereas tensoring the last two and then the first results in $M_1 \otimes (M_2 \otimes M_3)$:
 \[
@@
 \node (A) at (0,0) {$a_1+(a_2+a_3)$};
-\node (B) at (2.25,0) {$m_1+(m_2+m_3)$};
+\node (B) at (2.25,0) {$c_1+(c_2+c_3)$};
 \node (C) at (4.5,0) {$b_1+(b_2+b_3)$};
-\node (D) at (2.25,-0.5) {$x_1+(x_2+x_3) \in F(m_1+(m_2+m_3))$};
+\node (D) at (2.25,-0.5) {$d_{M_1 \otimes (M_2 \otimes M_3)} \in F(c_1+(c_2+c_3))$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-where $x_1+(x_2+x_3) \colon 1 \to F(m_1+(m_2+m_3))$ is given by: $$1 \xrightarrow{x_1 \times (x_2 \times x_3)} F(m_1) \times (F(m_2) \times F(m_3)) \xrightarrow{1 \times \phi_{m_2,m_3}} F(m_1) \times F(m_2+m_3) \xrightarrow{\phi_{m_1,m_2+m_3}} F(m_1+(m_2+m_3)).$$If we let $a$ denote the associator of $(\mathsf{A},+,0)$, the associator of $F\mathbb{C}\textnormal{sp}_1$ is then a map of cospans in $\mathsf{A}$ from $(M_1 \otimes M_2) \otimes M_3$ to $M_1 \otimes (M_2 \otimes M_3)$ given by:
+where $d_{M_1 \otimes (M_2 \otimes M_3)} \colon 1 \to F(c_1+(c_2+c_3))$ is given by: $$1 \xrightarrow{d_{M_1} \times (d_{M_2} \times d_{M_3})} F(c_1) \times (F(c_2) \times F(c_3)) \xrightarrow{1 \times \phi_{c_2,c_3}} F(c_1) \times F(c_2+c_3) \xrightarrow{\phi_{c_1,c_2+c_3}} F(c_1+(c_2+c_3)).$$If we let $a$ denote the associator of $(\mathsf{A},+,0)$, the associator of $F\mathbb{C}\textnormal{sp}_1$ is then a map of cospans in $\mathsf{A}$ from $(M_1 \otimes M_2) \otimes M_3$ to $M_1 \otimes (M_2 \otimes M_3)$ given by:
 \[
@@
 \node (A') at (0,-0.5) {$a_1+(a_2+a_3)$};
-\node (B) at (2.25,0.5) {$(m_1+m_2)+m_3$};
+\node (B) at (2.25,0.5) {$(c_1+c_2)+c_3$};
 \node (C) at (4.5,0.5) {$(b_1+b_2)+b_3$};
 \node (C') at (4.5,-0.5) {$b_1+(b_2+b_3)$};
-\node (D) at (2.25,-0.5) {$m_1+(m_2+m_3)$};
-\node (E) at (7,0.5) {$(x_1+x_2)+x_3 \in F((m_1+m_2)+m_3)$};
-\node (F) at (7,-0.5) {$x_1+(x_2+x_3) \in F(m_1+(m_2+m_3))$};
+\node (D) at (2.25,-0.5) {$c_1+(c_2+c_3)$};
+\node (E) at (7,0.5) {$d_{(M_1 \otimes M_2) \otimes M_3} \in F((c_1+c_2)+c_3)$};
+\node (F) at (7,-0.5) {$d_{M_1 \otimes (M_2 \otimes M_3)} \in F(c_1+(c_2+c_3))$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (A) edge node[left]{$a$} (A')
-(C) edge node[right]{$a$} (C')
+(C) edge node[left]{$a$} (C')
 (A') edge node [above]{$i_1+(i_2+i_3)$} (D)
@@
 \]
-together with the isomorphism $\iota_a \colon F(a)((x_1+x_2)+x_3) \to x_1+(x_2+x_3)$.
-These associators and left and right unitors together satisfy the pentagon and triangle identities of a monoidal category.
-\textbf{Kenny: Probably cut stuff out below this.} If we denote the above associator simply as $a$ and the left and right unitors as $\lambda$ and $\rho$, respectively, then given four objects in $F\mathbb{C}\textnormal{sp}_1$, say $M_1, M_2, M_3$ and $M_4$:
+together with the isomorphism $\iota_a \colon F(a)(d_{(M_1 \otimes M_2) \otimes M_3}) \to d_{M_1 \otimes (M_2 \otimes M_3)}$.
+If we denote the above associator simply as $a$ and the left and right unitors as $\lambda$ and $\rho$, respectively, then given four objects in $F\mathbb{C}\textnormal{sp}_1$, say $M_1, M_2, M_3$ and $M_4$:
 \[
@@
 \node (A) at (0,0) {$a_1$};
-\node (B) at (1,0) {$m_1$};
+\node (B) at (1,0) {$c_1$};
 \node (C) at (2,0) {$b_1$};
-\node (D) at (1,-0.5) {$x_1 \in F(m_1)$};
+\node (D) at (1,-0.5) {$d_{M_1} \in F(c_1)$};
 \node (E) at (3,0) {$a_2$};
-\node (F) at (4,0) {$m_2$};
+\node (F) at (4,0) {$c_2$};
 \node (G) at (5,0) {$b_2$};
-\node (H) at (4,-0.5) {$x_2 \in F(m_2)$};
+\node (H) at (4,-0.5) {$d_{M_2} \in F(c_2)$};
 \node (I) at (0,-1.5) {$a_3$};
-\node (J) at (1,-1.5) {$m_3$};
+\node (J) at (1,-1.5) {$c_3$};
 \node (K) at (2,-1.5) {$b_3$};
-\node (L) at (1,-2) {$x_3 \in F(m_3)$};
+\node (L) at (1,-2) {$d_{M_3} \in F(c_3)$};
 \node (M) at (3,-1.5) {$a_4$};
-\node (N) at (4,-1.5) {$m_4$};
+\node (N) at (4,-1.5) {$c_4$};
 \node (O) at (5,-1.5) {$b_4$};
-\node (P) at (4,-2) {$x_4 \in F(m_4)$};
+\node (P) at (4,-2) {$d_{M_4} \in F(c_4)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-then as $\mathbb{C}\textnormal{sp}(\mathsf{A})$ is a symmetric monoidal double category, the following pentagon of underlying cospans and maps of cospans commutes:
+then as $\mathbb{C}\textnormal{sp}(\mathsf{A})$ is a symmetric monoidal double category, the following pentagon of underlying cospans commutes:
 \[
@@
 \]
-as well as the following pentagon of corresponding decorations in the category $F(m_1 +(m_2 +(m_3+m_4)))$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (-.5,0) {$F(aa)(((x_1+x_2)+x_3)+x_4) $};
-\node (B) at (2.25,1) {$F(a)((x_1+x_2)+(x_3+x_4))$};
-\node (C) at (5,0) {$x_1+(x_2+(x_3+x_4))$};
-\node (D) at (-.5,-1) {$F((1 \otimes a)a)((x_1+(x_2+x_3))+x_4) $};
-\node (E) at (5,-1) {$F(1 \otimes a)(x_1+((x_2+x_3)+x_4)) $};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$F(a)(\iota_a)$} (B)
+as well as the following pentagon of corresponding decorations in the category $F(c_1 +(c_2 +(c_3+c_4)))$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (-.5,0) {$F(aa)(d_{((M_1 \otimes M_2) \otimes M_3) \otimes M_4}) $};
+\node (B) at (2.25,1) {$F(a)(d_{(M_1 \otimes M_2) \otimes (M_3 \otimes M_4)})$};
+\node (C) at (5,0) {$d_{M_1 \otimes (M_2 \otimes (M_3 \otimes M_4))}$};
+\node (D) at (-.5,-1) {$F((1 \otimes a)a)(d_{(M_1 \otimes (M_2 \otimes M_3)) \otimes M_4}) $};
+\node (E) at (5,-1) {$F(1 \otimes a)(d_{M_1 \otimes ((M_2 \otimes M_3) \otimes M_4)}) $};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[left]{$F(a)(\iota_a)$} (B)
 (B) edge node[above]{$\iota_a$} (C)
@@
 \]
-since $$F(aa)(((x_1+x_2)+x_3)+x_4)=F((1 \otimes a)a(a \otimes 1))(((x_1+x_2)+x_3)+x_4)$$ as the corresponding pentagon in the symmetric monoidal category $(\mathsf{A},+,0)$ commutes, and then appliying the pseudofunctor $F$ to said pentagon yields a commutative pentagon in $\mathbf{Cat}$.
-
-Similarly, if we denote the left and right unitors as $\lambda$ and $\rho$, respectively, then the following triangle of cospans and underlying maps of cospans commutes:
+since $$F(aa)(d_{((M_1 \otimes M_2) \otimes M_3) \otimes M_4})=F((1 \otimes a)a(a \otimes 1))(d_{((M_1 \otimes M_2) \otimes M_3) \otimes M_4})$$ as the corresponding pentagon in the symmetric monoidal category $(\mathsf{A},+,0)$ commutes.
+
+Similarly, if we denote the left and right unitors as $\lambda$ and $\rho$, respectively, then the following triangle of underlying maps of cospans commutes:
 \[
@@
 \]
-as well as the following triangle of corresponding decorations in the category $F(m_1+m_2)$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$F(\rho \otimes 1)((x_1+0)+x_2)$};
-\node (B) at (2.25,1) {$x_1+x_2$};
-\node (C) at (4.5,0) {$F(1 \otimes \lambda)(x_1+(0+x_2)) $};
+as well as the following triangle of corresponding decorations in the category $F(c_1+c_2)$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$F(\rho \otimes 1)(d_{(M_1 \otimes 0) \otimes M_2})$};
+\node (B) at (2.25,1) {$d_{M_1 \otimes M_2}$};
+\node (C) at (4.5,0) {$F(1 \otimes \lambda)(d_{M_1 \otimes (0 \otimes M_2)}) $};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-since $$F(\rho \otimes 1)((x_1+0)+x_2)=F((1 \otimes \lambda)a)((x_1+0)+x_2)$$ as the corresponding triangle in the symmetric monoidal category $(\mathsf{A},+,0)$ commutes and applying the pseudofunctor $F$ to this commutative triangle results in a commutative triangle in $\mathbf{Cat}$.
+since $$F(\rho \otimes 1)(d_{(M_1 \otimes 0) \otimes M_2})=F((1 \otimes \lambda)a)(d_{(M_1 \otimes 0) \otimes M_2})$$ as the corresponding triangle in the symmetric monoidal category $(\mathsf{A},+,0)$ commutes.
 
@@
 \node (A') at (0,-0.5) {$a_2+a_1$};
-\node (B) at (2,0.5) {$m_1+m_2$};
+\node (B) at (2,0.5) {$c_1+c_2$};
 \node (C) at (4,0.5) {$b_1+b_2$};
 \node (C') at (4,-0.5) {$b_2+b_1$};
-\node (D) at (2,-0.5) {$m_2+m_1$};
-\node (E) at (5.5,0.5) {$x_1+x_2 \in F(m_1+m_2)$};
-\node (F) at (5.5,-0.5) {$x_2+x_1 \in F(m_2+m_1)$};
+\node (D) at (2,-0.5) {$c_2+c_1$};
+\node (E) at (5.5,0.5) {$d_{M_1 \otimes M_2} \in F(c_1+c_2)$};
+\node (F) at (5.5,-0.5) {$d_{M_2 \otimes M_1} \in F(c_2+c_1)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (C') edge node [above]{$o_2+o_1$} (D)
-(B) edge node [left] {$\beta_{m_1,m_2}$} (D);
-\end{tikzpicture}
-\]
-$$\iota_{\beta_{M_1,M_2}} \colon F(\beta_{m_1,m_2})(x_1+x_2) \xrightarrow{\sim} x_2+x_1$$ where the vertical 1-morphisms are given by braidings in $(\mathsf{A},+,0)$.
+(B) edge node [left] {$\beta_{c_1,c_2}$} (D);
+\end{tikzpicture}
+\]
+$$\iota_{\beta_{M_1,M_2}} \colon F(\beta_{c_1,c_2})(d_{M_1 \otimes M_2}) \xrightarrow{\sim} d_{M_2 \otimes M_1}$$ where the vertical 1-morphisms are given by braidings in $(\mathsf{A},+,0)$.
 This braiding makes the following triangle of underlying cospans commute:
@@
 \]
-as well as the following diagram of corresponding decorations in the category $F(m_1+m_2)$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$x_1+x_2$};
-\node (B) at (2.25,1) {$x_1+x_2$};
-\node (C) at (4.5,0) {$F(\beta_{m_2,m_1})(x_2+x_1)$};
+as well as the following diagram of corresponding decorations in the category $F(c_1+c_2)$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$d_{M_1 \otimes M_2}$};
+\node (B) at (2.25,1) {$d_{M_1 \otimes M_2} $};
+\node (C) at (4.5,0) {$F(\beta_{c_2,c_1})(d_{M_2 \otimes M_1}) $};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (C) edge node[right]{$\iota_{\beta_{M_2,M_1}}$} (B)
-(A) edge node[above]{$F(\beta_{m_2,m_1})(\iota_{\beta_{M_1,M_2}})$} (C);
-\end{tikzpicture}
-\]
-since $F(\beta_{m_2,m_1} \beta_{m_1,m_2}) (x_1+x_2) = x_1+x_2$. Thus $F\mathbb{C}\textnormal{sp}_1$ is also symmetric monoidal.
-
-Next we derive the globular isomorphisms required in the definition of a symmetric monoidal double category relating horizontal composition and the tensor product.
-Given four horizontal 1-cells $M_1, M_2, N_1$ and $N_2$ respectively by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a$};
-\node (B) at (1,0) {$m_1$};
-\node (C) at (2,0) {$b$};
-\node (D) at (1,-0.5) {$x_1 \in F(m_1)$};
-\node (E) at (3,0) {$b$};
-\node (F) at (4,0) {$m_2$};
-\node (G) at (5,0) {$c$};
-\node (H) at (4,-0.5) {$x_2 \in F(m_2)$};
-\node (I) at (0,-1.5) {$a'$};
-\node (J) at (1,-1.5) {$n_1$};
-\node (K) at (2,-1.5) {$b'$};
-\node (L) at (1,-2) {$y_1 \in F(n_1)$};
-\node (M) at (3,-1.5) {$b'$};
-\node (N) at (4,-1.5) {$n_2$};
-\node (O) at (5,-1.5) {$c'$};
-\node (P) at (4,-2) {$y_2 \in F(n_2)$};
+(A) edge node[above]{$F(\beta_{c_2,c_1})(\iota_{\beta_{M_1,M_2}})$} (C);
+\end{tikzpicture}
+\]
+since $F(\beta_{c_2,c_1} \beta_{c_1,c_2}) (d_{M_1 \otimes M_2}) = d_{M_1 \otimes M_2}$. Thus $F\mathbb{C}\textnormal{sp}_1$ is also symmetric monoidal.
+
+Now, given four horizontal 1-cells $M_1, M_2, N_1$ and $N_2$ respectively by:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$a_1$};
+\node (B) at (1,0) {$b$};
+\node (C) at (2,0) {$a_2$};
+\node (D) at (1,-0.5) {$d_{M_1} \in F(b)$};
+\node (E) at (3,0) {$a_2$};
+\node (F) at (4,0) {$b'$};
+\node (G) at (5,0) {$a_3$};
+\node (H) at (4,-0.5) {$d_{M_2} \in F(b')$};
+\node (I) at (0,-1.5) {$a_1'$};
+\node (J) at (1,-1.5) {$c$};
+\node (K) at (2,-1.5) {$a_2'$};
+\node (L) at (1,-2) {$d_{N_1} \in F(c)$};
+\node (M) at (3,-1.5) {$a_2'$};
+\node (N) at (4,-1.5) {$c'$};
+\node (O) at (5,-1.5) {$a_3'$};
+\node (P) at (4,-2) {$d_{N_2} \in F(c')$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a+a'$};
-\node (B) at (2.5,0) {$(m_1+n_1)+_{b+b'}(m_2+n_2)$};
-\node (C) at (5,0) {$c+c'$};
-\node (D) at (2.5,-0.5) {$(x_1+y_1)\odot(x_2+y_2) \in F((m_1+n_1)+_{b+b'}(m_2+n_2))$};
+\node (A) at (0,0) {$a_1+a_1'$};
+\node (B) at (2.5,0) {$(b+c)+_{a_2+a_2'}(b'+c')$};
+\node (C) at (5,0) {$a_3+a_3'$};
+\node (D) at (2.5,-0.5) {$d_{(M_1 \otimes N_1) \odot (M_2 \otimes N_2)} \in F((b+c)+_{a_2+a_2'}(b'+c'))$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-where the decoration $(x_1+y_1) \odot (x_2+y_2) \in F((m_1+n_1)+_{b+b'}(m_2+n_2))$ is given by:
+where the decoration $d_{(M_1 \otimes N_1) \odot (M_2 \otimes N_2)} \in F((b+c)+_{a_2+a_2'}(b'+c'))$ is given by:
 \[
@@
 \node (C) at (0,-2) {$(1 \times 1) \times (1 \times 1)$};
-\node (D) at (0,-3) {$(F(m_1) \times F(n_1)) \times (F(m_2) \times F(n_2))$};
-\node (E) at (0,-4) {$F(m_1+n_1) \times F(m_2+n_2)$};
-\node (F) at (0,-5) {$F((m_1+n_1)+(m_2+n_2))$};
-\node (G) at (0,-6) {$F((m_1+n_1)+_{b+b'}(m_2+n_2))$};
+\node (D) at (0,-3) {$(F(b) \times F(c)) \times (F(b') \times F(c'))$};
+\node (E) at (0,-4) {$F(b+c) \times F(b'+c')$};
+\node (F) at (0,-5) {$F((b+c)+(b'+c'))$};
+\node (G) at (0,-6) {$F((b+c)+_{a_2+a_2'}(b'+c'))$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (B) edge node[left]{$\lambda^{-1} \times \lambda^{-1}$} (C)
-(C) edge node[left]{$(x_1 \times y_1) \times (x_2 \times y_2)$} (D)
-(D) edge node[left]{$\phi_{m_1,n_1} \times \phi_{m_2,n_2}$} (E)
-(E) edge node[left]{$\phi_{m_1+n_1,m_2+n_2}$} (F)
-(F) edge node[left]{$F(j_{m_1+n_1,m_2+n_2})$} (G);
+(C) edge node[left]{$(d_{M_1} \times d_{N_1}) \times (d_{M_2} \times d_{N_2})$} (D)
+(D) edge node[left]{$\phi_{b,c} \times \phi_{b',c'}$} (E)
+(E) edge node[left]{$\phi_{b+c,b'+c'}$} (F)
+(F) edge node[left]{$F(j_{b+c,b'+c'})$} (G);
 \end{tikzpicture}
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a+a'$};
-\node (B) at (2.5,0) {$(m_1+_{b} m_2) + (n_1 +_{b'} n_2)$};
-\node (C) at (5,0) {$c+c'$};
-\node (D) at (2.5,-0.5) {$(x_1 \odot x_2) + (y_1 \odot y_2) \in F((m_1+_{b}m_2)+(n_1+_{b'}n_2))$};
+\node (A) at (0,0) {$a_1+a_1'$};
+\node (B) at (2.5,0) {$(b+_{a_2} c) + (b' +_{a_2'} c')$};
+\node (C) at (5,0) {$a_3+a_3'$};
+\node (D) at (2.5,-0.5) {$d_{(M_1 \odot M_2) \otimes (N_1 \odot N_2)} \in F((b+_{a_2}c)+(b'+_{a_2'}c'))$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-where the decoration $(x_1 \odot x_2) + (y_1 \odot y_2) \in F((m_1+_{b}m_2)+(n_1+_{b'}n_2))$ is given by:
+where the decoration $d_{((M_1 \odot M_2) \otimes (N_1 \odot N_2))} \in F((b+_{a_2}c)+(b'+_{a_2'}c'))$ is given by:
 \[
@@
 \node (C) at (0,-2) {$(1 \times 1) \times (1 \times 1)$};
-\node (D) at (0,-3) {$(F(m_1) \times F(m_2)) \times (F(n_1) \times F(n_2))$};
-\node (E) at (0,-4) {$F(m_1+m_2) \times F(n_1+n_2)$};
-\node (F) at (0,-5) {$F(m_1+_{b}m_2) \times F(n_1+_{b'}n_2)$};
-\node (G) at (0,-6) {$F((m_1+_{b}m_2)+(n_1+_{b'}n_2))$};
+\node (D) at (0,-3) {$(F(b) \times F(c)) \times (F(b') \times F(c'))$};
+\node (E) at (0,-4) {$F(b+c) \times F(b'+c')$};
+\node (F) at (0,-5) {$F(b+_{a_2}c) \times F(b'+_{a_2'}c')$};
+\node (G) at (0,-6) {$F((b+_{a_2}c)+(b'+_{a_2'}c'))$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (B) edge node[left]{$\lambda^{-1} \times \lambda^{-1}$} (C)
-(C) edge node[left]{$(x_1 \times x_2) \times (y_1 \times y_2)$} (D)
-(D) edge node[left]{$\phi_{m_1,m_2} \times \phi_{n_1,n_2}$} (E)
-(E) edge node[left]{$F(j_{m_1,m_2}) \times F(j_{n_1,n_2})$} (F)
-(F) edge node[left]{$\phi_{m_1+_{b}m_2,n_1+_{b'}n_2}$} (G);
+(C) edge node[left]{$(d_{M_1} \times d_{N_1}) \times (d_{M_2} \times d_{N_2})$} (D)
+(D) edge node[left]{$\phi_{b,c} \times \phi_{b',c'}$} (E)
+(E) edge node[left]{$F(j_{b,c}) \times F(j_{b',c'})$} (F)
+(F) edge node[left]{$\phi_{b+_{a_2}c,b'+_{a_2'}c'}$} (G);
 \end{tikzpicture}
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$a+a'$};
-\node (A') at (0,-0.5) {$a+a'$};
-\node (B) at (2.5,0.5) {$(m_1+n_1)+_{b+b'}(m_2+n_2)$};
-\node (C) at (5,0.5) {$c+c'$};
-\node (C') at (5,-0.5) {$c+c'$};
-\node (D) at (2.5,-0.5) {$(m_1+_{b}m_2)+(n_1+_{b'}n_2)$};
-\node (E) at (2.5,1) {$(x_1+y_1) \odot (x_2+y_2) \in F((m_1+n_1)+_{b+b'}(m_2+n_2))$};
-\node (F) at (2.5,-1) {$(x_1 \odot x_2)+(y_1 \odot y_2) \in F((m_1+_{b}m_2)+(n_1+_{b'}n_2))$};
+\node (A) at (0,0.5) {$a_1+a_1'$};
+\node (A') at (0,-0.5) {$a_1+a_1'$};
+\node (B) at (2.5,0.5) {$(b+c)+_{a_2+a_2'}(b'+c')$};
+\node (C) at (5,0.5) {$a_3+a_3'$};
+\node (C') at (5,-0.5) {$a_3+a_3'$};
+\node (D) at (2.5,-0.5) {$(b+_{a_2}c)+(b'+_{a_2'}c')$};
+\node (E) at (2.5,1) {$d_{(M_1 \otimes N_1) \odot (M_2 \otimes N_2)} \in F((b+c)+_{a_2+a_2'}(b'+c'))$};
+\node (F) at (2.5,-1) {$d_{(M_1 \odot M_2) \otimes (N_1 \odot N_2)} \in F((b+_{a_2}c)+(b'+_{a_2'}c'))$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-$$\iota_{\hat{\chi}} \colon F(\hat{\chi})((x_1+y_1)\odot(x_2+y_2)) \to (x_1 \odot x_2)+(y_1 \odot y_2)$$
+$$\iota_{\hat{\chi}} \colon F(\hat{\chi})(d_{(M_1 \otimes N_1) \odot (M_2 \otimes N_2)}) \to d_{(M_1 \odot M_2) \otimes (N_1 \odot N_2)}$$
 where $\hat{\chi}$ is the universal map between two colimits of the same diagram.
@@
 The desired equivalence between these two different double categorical network frameworks, namely structured cospans and decorated cospans,
-is established by the following theorem. We denote by $\bicat{fcocCat}$ the 2-category of finitely cocomplete categories and finitely cocontinuous functors.
+is established by the following theorem. We denote by $\bicat{Rex}$ the 2-category of finitely cocomplete categories and finitely cocontinuous functors.
 
 \begin{thm}\label{Equiv}
-Suppose $\ca{A}$ is a finitely cocomplete category and $(F,\phi,\phi_0)\colon(\ca{A},+,0) \to (\bicat{Cat},\times,\mathbf{1})$ is a symmetric lax monoidal pseudofunctor, which factors through $\bicat{fcocCat}$ as an ordinary pseudofunctor.
+Suppose $\ca{A}$ is a finitely cocomplete category and $(F,\phi,\phi_0)\colon(\ca{A},+,0) \to (\bicat{Cat},\times,\mathbf{1})$ is a symmetric lax monoidal pseudofunctor, which factors through $\bicat{Rex}$ as an ordinary pseudofunctor.
 Then the symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$ of decorated cospans (\cref{thm:decoratedcospans}) is equivalent to the symmetric monoidal double category $\scsp{L_F}{\inta F}$ of structured cospans (\cref{SC}), where $L_F \colon \mathsf{A} \to \inta{F}$ is the left adjoint of the induced Grothendieck opfibration $\U_F\colon \inta{F} \to \mathsf{A}$.
@@
 
-The first part formulates the existence of colimits \emph{locally} in each fibre, which can equivalently be expressed by the corresponding pseudofunctor $F\colon\A\to\bicat{Cat}$ landing on the sub-2-category $\bicat{fcocCat}$ of finitely cocomplete categories and functors that preserve colimits.
+The first part formulates the existence of colimits \emph{locally} in each fibre, which can equivalently be expressed by the corresponding pseudofunctor $F\colon\A\to\bicat{Cat}$ landing on the sub-2-category $\bicat{Rex}$ of finitely cocomplete categories and functors that preserve colimits.
 The second part formulates the existence of colimits \emph{globally} in the total category $\inta F$.
@@
 If its corresponding pseudofunctor $\A\to\bicat{MonCat}$ via \cref{monGroth}
- factors through $\bicat{fcocCat}$, then the Grothendieck category $\inta F$ has all finite colimits and the induced opfibration $\U_F\colon\inta F\to\A$ preserves them. 
+ factors through $\bicat{Rex}$, then the Grothendieck category $\inta F$ has all finite colimits and the induced opfibration $\U_F\colon\inta F\to\A$ preserves them. 
 \end{cor}
@@
 \begin{proof}[Proof of \cref{Equiv}]
-Recall that the double category of decorated cospans $\dcsp{F}$ has objects and vertical 1-morphisms those of $\A$, horizontal 1-cells $a\tickar b$ are cospans $\cspn{a}{m}{b}{}{}$ in $\A$ along with $x\in F(m)$, and 2-morphisms are cospan maps $k\colon m\to m'$ together with a morphism $(Fk)(x)\to x'$, see \cref{eq:FCsp2morph}.
-
-By \cref{cor:fcocMonGroth}, when $F$ as an ordinary pseudofunctor factors through $\bicat{fcocCat}$, the (monoidal) Gro\-the\-ndieck construction gives rise to a finitely cocomplete $\inta F$ such that the corresponding opfibration $U_F\colon(\inta{F},+,0)\to(\A,+,0)$ preserves all finite colimits.
+Recall that the double category of decorated cospans $\dcsp{F}$ has objects and vertical 1-morphisms those of $\A$, horizontal 1-cells $a\tickar b$ are cospans $\cspn{a}{c}{b}{}{}$ in $\A$ along with $x\in F(c)$, and 2-morphisms are cospan maps $k\colon c\to c'$ together with a morphism $(Fk)(x)\to x'$, see \cref{eq:FCsp2morph}.
+
+By \cref{cor:fcocMonGroth}, when $F$ as an ordinary pseudofunctor factors through $\bicat{Rex}$, the (monoidal) Gro\-the\-ndieck construction gives rise to a finitely cocomplete $\inta F$ such that the corresponding opfibration $U_F\colon(\inta{F},+,0)\to(\A,+,0)$ preserves all finite colimits.
 %Christina: maybe the cocartesian structures are redundant to write here, since U_F really preserves all finite colimits anyways.
@@
 \begin{equation}\label{eq:scsphor1cell}
- (a,\bot_a)\xrightarrow{\scalebox{0.7}{$\begin{cases}i\colon a\to m &\textrm{in }\A \\!\colon F(i)(\bot_a)\to x &\textrm{in }F(m)\end{cases}$}}(m,x)\xleftarrow{\scalebox{0.7}{$\begin{cases}o\colon b\to m &\textrm{in }\A \\!\colon F(o)(\bot_b)\to x &\textrm{in }F(m)\end{cases}$}}(b,\bot_b)
+ (a,\bot_a)\xrightarrow{\scalebox{0.7}{$\begin{cases}i\colon a\to c &\textrm{in }\A \\!\colon F(i)(\bot_a)\to x &\textrm{in }F(c)\end{cases}$}}(c,x)\xleftarrow{\scalebox{0.7}{$\begin{cases}o\colon b\to c &\textrm{in }\A \\!\colon F(o)(\bot_b)\to x &\textrm{in }F(c)\end{cases}$}}(b,\bot_b)
 \end{equation}
-where $x\in F(m)$, according to \cref{def:GrothCat}. Finally, the 2-morphisms in this double category are as described in \cref{eq:2cellsStrCsp}, in this context fully unravelled below:
+where $x\in F(c)$, according to \cref{def:GrothCat}. Finally, the 2-morphisms in this double category are as described in \cref{eq:2cellsStrCsp}, in this context fully unravelled below:
 \begin{displaymath}
  \begin{tikzcd}[sep=1.5in,ampersand replacement=\&]
- (a,\bot_a)\ar[r,"{\begin{cases}i\colon a\to m &\textrm{in }\A \\!\colon F(i)(\bot_a)\to x &\textrm{in }F(m)\end{cases}}"]\ar[d,"{\begin{cases}f\colon a\to a' &\textrm{in }\A \\\chi_a\colon F(f)(\bot_a)\cong \bot_{a'} &\textrm{in }F(a')\end{cases}}"description] \& (m,x) \ar[d,"{\begin{cases}k\colon m\to m' &\textrm{in }\A \\ \iota\colon F(k)(x)\to x' &\textrm{in }F(m')\end{cases}}"description] \& (b,\bot_b)\ar[l,"{\begin{cases}o\colon b\to m &\textrm{in }\A \\!\colon F(o)(\bot_b)\to x &\textrm{in }F(m)\end{cases}}"']\ar[d,"{\begin{cases}g\colon b\to b' &\textrm{in }\A \\\chi_b\colon F(g)(\bot_b)\cong \bot_{b'} &\textrm{in }F(b')\end{cases}}"description] \\
- (a',\bot_{a'})\ar[r,"{\begin{cases}i'\colon a'\to m' &\textrm{in }\A \\!\colon F(i')(\bot_{a'})\to x' &\textrm{in }F(m')\end{cases}}"'] \& (m',x') \& (b',\bot_{b'})\ar[l,"{\begin{cases}o'\colon b'\to m' &\textrm{in }\A \\!\colon F(o')(\bot_{b'})\to x' &\textrm{in }F(m')\end{cases}}"]
+ (a,\bot_a)\ar[r,"{\begin{cases}i\colon a\to c &\textrm{in }\A \\!\colon F(i)(\bot_a)\to x &\textrm{in }F(c)\end{cases}}"]\ar[d,"{\begin{cases}f\colon a\to a' &\textrm{in }\A \\\chi_a\colon F(f)(\bot_a)\cong \bot_{a'} &\textrm{in }F(a')\end{cases}}"description] \& (c,x) \ar[d,"{\begin{cases}k\colon c\to c' &\textrm{in }\A \\ \iota\colon F(k)(x)\to x' &\textrm{in }F(c')\end{cases}}"description] \& (b,\bot_b)\ar[l,"{\begin{cases}o\colon b\to c &\textrm{in }\A \\!\colon F(o)(\bot_b)\to x &\textrm{in }F(c)\end{cases}}"']\ar[d,"{\begin{cases}g\colon b\to b' &\textrm{in }\A \\\chi_b\colon F(g)(\bot_b)\cong \bot_{b'} &\textrm{in }F(b')\end{cases}}"description] \\
+ (a',\bot_{a'})\ar[r,"{\begin{cases}i'\colon a'\to c' &\textrm{in }\A \\!\colon F(i')(\bot_{a'})\to x' &\textrm{in }F(c')\end{cases}}"'] \& (c',x') \& (b',\bot_{b'})\ar[l,"{\begin{cases}o'\colon b'\to c' &\textrm{in }\A \\!\colon F(o')(\bot_{b'})\to x' &\textrm{in }F(c')\end{cases}}"]
  \end{tikzcd}
@@
 \end{gather}
-in the category $F(m')$.
+in the category $F(c')$.
 However, since all maps are unique in the above equality, emanating from initial objects (since reindexing functors preserve those), this gives no extra conditions for the morphisms involved; similarly for the equality including $o, o'$.
@@
 \begin{displaymath}
- a\xrightarrow{\; i \;}m\xleftarrow{\; o \;}b\;\textrm{ with decoration }x\in F(m)
+ a\xrightarrow{\; i \;}c\xleftarrow{\; o \;}b\;\textrm{ with decoration }x\in F(c)
 \end{displaymath}
@@
  \begin{tikzcd}
-a\ar[r,"i"]\ar[d,"f"'] & m\ar[d,"k"] & b\ar[l,"o"']\ar[d,"g"] \\
-a'\ar[r,"i'"']& m' & b'\ar[l,"o'"]
+a\ar[r,"i"]\ar[d,"f"'] & c\ar[d,"k"] & b\ar[l,"o"']\ar[d,"g"] \\
+a'\ar[r,"i'"']& c' & b'\ar[l,"o'"]
  \end{tikzcd}
 \end{displaymath}
- in $\A$ along with the map $\iota\colon Fk(x)\to x'$ in $F(m')$, namely a decorated cospan 2-morphism as per \cref{eq:FCsp2morph}.
+ in $\A$ along with the map $\iota\colon Fk(x)\to x'$ in $F(c')$, namely a decorated cospan 2-morphism as per \cref{eq:FCsp2morph}.
 Once again, this is a bijective correspondence since, as discussed above, the commutativity \cref{eq:Grothcommutativity} holds automatically by initiality of the domain.
- {\chris Christina commented out big chunks of proof.
-They are right below if we want to revive parts of them, if we think the reader needs deeper level of detail.
-The idea is that the above description suffices as fully faithful and essentially surjective evidence, but perhaps we would like to spell that out more.
-On to strongness next.}
+ {\chris Christina commented out big chunks of proof. They are right below if we want to revive parts of them, if we think the reader needs deeper level of detail.}
 
@@
  \mathbb{E}(M) \odot \mathbb{E}(N) \xrightarrow{\sim} \mathbb{E}(M \odot N) \\
-U_{\mathbb{E}m} \xrightarrow{\sim} \mathbb{E}(U_m)
+U_{\mathbb{E}(c,x)} \xrightarrow{\sim} \mathbb{E}(U_{(c,x)})
 \end{gather*}
-for any pair of composable horizontal 1-cells $M=\cspn{(a,\bot_a)}{(m,x)}{(b,\bot_b)}{}{}$ and $N=\cspn{(b,\bot_b)}{(n,y)}{(c,\bot_c)}{}{}$ and any object $m$ of $\scsp{L_F}{\inta F}$.
-In more detail, $\mathbb{E}(M)\odot \mathbb{E}(N)$ is given as in \cref{eq:dcospanscomposition} via the pushout cospan and decoration
-\begin{displaymath}
- \begin{tikzcd}
-  & m+_bn & \\
-  a\ar[ur,"j_m\circ i"] && b,\ar[ul,"j_n\circ o"']
- \end{tikzcd}
- \begin{tikzcd}
-  1\ar[r,"x\times y"]\ar[drr,dashed] & F(m)\times F(n)\ar[r,"\phi_{m,n}"] & F(m+ n)\ar[d,"F(j)"] \\ 
-  && F(m+_b n)
- \end{tikzcd}
-\end{displaymath}
-where $j_m, j_n$ denote the maps into a pushout.
-On the other hand, first composing $M$ and $N$ in the Grothendieck category $\scsp{L_F}{\inta F}$ using fibrewise pushouts constructed using \cref{lem:fibrewiselimits} ({\chris I could make this specific construction into a lemma earlier if you want, I have it in my notes}) produces
-\begin{displaymath}
- \begin{tikzcd}
- && (m+_b n,F(j_m)x+_{\bot_{m+_bn}}F(j_n)y) && \\
- & (m,x) \ar[ur] && (n,y)\ar[ul] \\
- (a,\bot_a)\ar[ur] && (b,\bot_b)\ar[ur]\ar[ul] && (c,\bot_c)\ar[ul]
- \end{tikzcd}
-\end{displaymath}
-which is mapped, under $\mathbb{E}$, to precisely the cospan $\cspn{a}{m+_bn}{b}{}{}$ as above, and the decorations are the same {\chris isomorphic would be enough but they look equal to me!} due to the following commutative diagram
-\begin{displaymath}
- \begin{tikzcd}
-F(m)\times F(n)\ar[rr,"\phi"]\ar[d,"F(j_m)\times F(j_n)"'] && F(m+n)\ar[d,"F(j)"] \\
-F(m+_bn)\times F(m+_bn)\ar[r,"\phi"] & F((m+_bn)+(m+_bn))\ar[r,"F\nabla"] & F(m+_bn)
- \end{tikzcd}
-\end{displaymath}
-since taking a pushout over an initial object is really a coproduct, and the fibrewise coproduct in $F(m+_bn)$ is given as in \cref{eq:explicitstructure1}.
-
-Regarding the identity morphisms, $U_m$ is $\cspn{(m,\bot_m)}{(m,\bot_m)}{(m,\bot_m)}{}{}$ with $1_m$ as the $A$-component of the morphisms and isomorphisms between initial objects in the fibres.
-Thus $\mathbb{E}(U_m)$ is the identity cospan in $A$ together with the `initial decoration' $\bot_m\in F(m)$, whereas $U_{\mathbb{E}(m)}$ is exactly the same thing.
-
-{\chris Below, up to my next comment, is Kenny's earlier proof on the same thing.}
+for any pair of composable horizontal 1-cells $M$ and $N$ and any object $(c,x)$ of $\scsp{L_F}{\inta F}$
+{\chris in progress}
 
@@
 
-{\chris Up to here was Kenny's strong functoriality.}
+{\chris Up to here}
 
@@
 {\chris In fact, Christina and Kenny believe it is an isomorphism of double categories! Bijective on all levels of objects and morphisms...should we say?}
-
-{\chris Have not edited below, but everything should be fine up to notation changes. Happy to do if needed in the future.}
 

### 2019-06-29 cospans.tex

--- 2019-06-18 cospans.tex
@@
 
-By \cref{cor:fcocMonGroth}, when $F$ as an ordinary pseudofunctor factors through $\bicat{fcocCat}$, the (monoidal) Gro\-the\-ndieck construction gives rise to a finitely cocomplete $\inta F$ such that the corresponding opfibration $U_F\colon(\inta{F},+,0)\to(\A,+,0)$ preserves all finite colimits.
+By \cref{cor:fcocMonGroth}, when $F$ as an ordinary pseudofunctor factors through $\bicat{Rex}$, the (monoidal) Gro\-the\-ndieck construction gives rise to a finitely cocomplete $\inta F$ such that the corresponding opfibration $U_F\colon(\inta{F},+,0)\to(\A,+,0)$ preserves all finite colimits.
 %Christina: maybe the cocartesian structures are redundant to write here, since U_F really preserves all finite colimits anyways.

### 2020-08-25 cospans.tex
changed title
changed Christinas affiliation

@@
 % John Baez, Kenny Courser and Christina Vasilakopoulou
-% 2019/09/11 - KC
+% 2019/10/27 - JB
+
 \documentclass{amsart}
@@
 
-\title{Structured and decorated cospans}
-
-\author{John\ C.\ Baez$^{*,\bullet}$, Kenny Courser$^*$, and Christina Vasilakopoulou$^*$}
+\title{Structured Versus Decorated Cospans}
+
+\author{John\ C.\ Baez$^{*,\bullet}$, Kenny Courser$^*$, and Christina Vasilakopoulou$^\square$}
 \address{$^*$Department of Mathematics, University of California, Riverside CA, USA 92521}
 \address{$^\bullet$Centre for Quantum Technologies, National University of Singapore, Singapore 117543}
-\email{baez@ucr.edu, kcour001@ucr.edu, vasilak@ucr.edu}
+\address{$^\square$Department of Mathematics, University of Patras, Greece 265 04}
+\email{baez@ucr.edu, kcour001@ucr.edu, cvasilak@math.upatrs.gr}
 

### 2020-11-09 cospans.tex
Changed preamble and also made small changes in paper.

@@
 % John Baez, Kenny Courser and Christina Vasilakopoulou
-% 2019/10/27 - JB
+% 2020/11/09 - JB
 
@@
 This framework, which goes by the name of `structured cospans', utilizes double categories where the objects are seen as inputs and outputs, horizontal 1-cells are `open networks', and 2-morphisms are maps between open networks.
-In this setup a functor $L \colon \textsf{A} \to \textsf{X}$, which is typically a left adjoint, is used to replace the objects and vertical 1-morphisms of a given double category $\mathbb{X}$ with the objects and morphisms, respectively, of the category $\textsf{A}$.
+In this setup a functor $L \maps \textsf{A} \to \textsf{X}$, which is typically a left adjoint, is used to replace the objects and vertical 1-morphisms of a given double category $\mathbb{X}$ with the objects and morphisms, respectively, of the category $\textsf{A}$.
 Horizontal 1-cells are then cospans in $\textsf{X}$ of a particular form with 2-morphisms given by maps of these cospans.
 Fong has also developed a similar framework utilizing cospans to study open networks which goes by the name of `decorated cospans'.
-In this setup, a lax monoidal functor $F \colon \textsf{A} \to \textsf{Set}$ is used to `decorate' the apices of cospans in $\textsf{A}$ with elements of $\textsf{Set}$ giving the cospans extra structure.
+In this setup, a lax monoidal functor $F \maps \textsf{A} \to \textsf{Set}$ is used to `decorate' the apices of cospans in $\textsf{A}$ with elements of $\textsf{Set}$ giving the cospans extra structure.
 Using a slight variation of Fong's framework, we prove that these two frameworks are equivalent in the situation where a left adjoint can be obtained from a lax monoidal pseudofunctor using a well known construction of Grothendieck.
@@
 
-In Fong's theory of decorated cospans, given a category $\textsf{A}$ with finite colmits, a symmetric lax monoidal functor $F \colon (\textsf{A},+,0) \to (\textsf{Set},\times,1)$ is used to `decorate' the apex of a cospan in $\textsf{A}$ with an element of the image of its apex under the functor $F$.
-In the case of the first cospan above, an element of the image of the apex under the functor $F$ is given by a morphism $d \colon 1 \to F(b)$, and we call $d$ a \textbf{decoration} on $b$.
+In Fong's theory of decorated cospans, given a category $\textsf{A}$ with finite colmits, a symmetric lax monoidal functor $F \maps (\textsf{A},+,0) \to (\textsf{Set},\times,1)$ is used to `decorate' the apex of a cospan in $\textsf{A}$ with an element of the image of its apex under the functor $F$.
+In the case of the first cospan above, an element of the image of the apex under the functor $F$ is given by a morphism $d \maps 1 \to F(b)$, and we call $d$ a \textbf{decoration} on $b$.
 Here, $1$ is any terminal object in $\mathsf{Set}$, $F(b)$ is the collection of all $F$-decorations on the object $b$ and the morphism $d$ is selecting a particular one.
@@
  $$1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{d_1 \times d_2} F(b) \times F(b^\prime) \xrightarrow{\phi_{b,b^\prime}} F(b+ b^\prime) \xrightarrow{F(j_{b,b^\prime})} F(b+_{a_2} b^\prime).$$
-From this symmetric lax monoidal functor $F \colon \textsf{A} \to \mathsf{Set}$, Fong then constructs a symmetric monoidal category $F\textnormal{Cospan}(\mathsf{A})$ which has:
+From this symmetric lax monoidal functor $F \maps \textsf{A} \to \mathsf{Set}$, Fong then constructs a symmetric monoidal category $F\textnormal{Cospan}(\mathsf{A})$ which has:
 \begin{enumerate}
 \item{objects as those of $\mathsf{A}$ and}
-\item{morphisms as isomorphism classes of $F$-decorated cospans, where an $F$-decorated cospan is given as above, and two $F$-decorated cospans are in the same isomorphism class if there exists an isomorphism $f \colon b \to b^\prime$ between the apices such that the following diagrams commute:
+\item{morphisms as isomorphism classes of $F$-decorated cospans, where an $F$-decorated cospan is given as above, and two $F$-decorated cospans are in the same isomorphism class if there exists an isomorphism $f \maps b \to b^\prime$ between the apices such that the following diagrams commute:
 \[
@@
 
-As an example, let $F \colon \textsf{FinSet} \to \textsf{Set}$ be the symmetric lax monoidal functor that assigns to a finite set $b$ the (large) set of all possible graph structures on the finite set $b$, where a graph structure on $b$ is given by a diagram in $\textsf{Set}$ of the form:
+As an example, let $F \maps \textsf{FinSet} \to \textsf{Set}$ be the symmetric lax monoidal functor that assigns to a finite set $b$ the (large) set of all possible graph structures on the finite set $b$, where a graph structure on $b$ is given by a diagram in $\textsf{Set}$ of the form:
 \[
@@
 %\]
-Denote this element of $F(b)$ as $d \colon 1 \to F(b)$.
-Let $a_1=\{ 1 \}$ and $a_2=\{2,3\}$ and define functions $i \colon a_1 \to b$ and $o \colon a_2 \to b$ by $i(1)=v_1$ and $o(2)=o(3)=v_2$.
+Denote this element of $F(b)$ as $d \maps 1 \to F(b)$.
+Let $a_1=\{ 1 \}$ and $a_2=\{2,3\}$ and define functions $i \maps a_1 \to b$ and $o \maps a_2 \to b$ by $i(1)=v_1$ and $o(2)=o(3)=v_2$.
 Then we have an $F$-decorated cospan:
@@
 \]
-This commutative triangle in $\mathsf{Set}$ in the context of the symmetric lax monoidal functor $F \colon \mathsf{FinSet} \to \mathsf{Set}$ says the following: given a decoration $d \in F(b)$, which is a graph structure with underlying set of vertices $b$, the function $F(f)$ pushes forward the graph structure $d$ to the graph structure $d^\prime \in F(b^\prime)$ with underlying set of vertices $b^\prime$, and \emph{precisely} this graph structure.
+This commutative triangle in $\mathsf{Set}$ in the context of the symmetric lax monoidal functor $F \maps \mathsf{FinSet} \to \mathsf{Set}$ says the following: given a decoration $d \in F(b)$, which is a graph structure with underlying set of vertices $b$, the function $F(f)$ pushes forward the graph structure $d$ to the graph structure $d^\prime \in F(b^\prime)$ with underlying set of vertices $b^\prime$, and \emph{precisely} this graph structure.
 The graph structure is given by set of edges of $d$.
@@
 \]
-Let $b^\prime = \{w_1,w_2\}$ and a define bijection $f \colon b \to b^\prime$ by $f(v_i)=w_i$ for $i=1,2$.
-Then the requirement $F(f)(d)=d^\prime$ says that $d^\prime \in F(b^\prime)$ must be given by:
+Let $b^\prime = \{w_1,w_2\}$ and a define bijection $f \maps b \to b^\prime$ by $f(v_i)=w_i$ for $i=1,2$. Then the requirement $F(f)(d)=d^\prime$ says that $d^\prime \in F(b^\prime)$ must be given by:
 \[
@@
 The point to be made here is that the single edge of $d^\prime$ must also be $e$.
-If we were to label it say, $e^\prime$, there is no bijection $f \colon b \to b^\prime$ such that the triangle on the right commutes, and hence no isomorphism between these two $F$-decorated cospans.
+If we were to label it say, $e^\prime$, there is no bijection $f \maps b \to b^\prime$ such that the triangle on the right commutes, and hence no isomorphism between these two $F$-decorated cospans.
 \[
@@
 In a previous work, the second author extended Fong's theory of decorated cospans to a symmetric monoidal bicategory of decorated cospans \cite{Cour}.
-Namely, under the same hypotheses used by Fong amounting to a category $\mathsf{A}$ with finite colimits and a symmetric lax monoidal functor $F \colon (\mathsf{A},+,0) \to (\mathsf{Set}, \times, 1)$, there exists a symmetric monoidal bicategory $F\mathbf{Cospan}(\mathsf{A})$ which has:
+Namely, under the same hypotheses used by Fong amounting to a category $\mathsf{A}$ with finite colimits and a symmetric lax monoidal functor $F \maps (\mathsf{A},+,0) \to (\mathsf{Set}, \times, 1)$, there exists a symmetric monoidal bicategory $F\mathbf{Cospan}(\mathsf{A})$ which has:
 \begin{enumerate}
@@
 \end{enumerate}
-Returning to the previous example where we take the functor $F$ to be the functor $F \colon \mathsf{FinSet} \to \mathsf{Set}$, the situation becomes more dire.
+Returning to the previous example where we take the functor $F$ to be the functor $F \maps \mathsf{FinSet} \to \mathsf{Set}$, the situation becomes more dire.
 Previously, in the ordinary symmetric monoidal category $F$Cospan$(\mathsf{FinSet})$ the following two $F$-decorated cospans resided in distinct isomorphism classes:
@@
 
-Our approach is to instead view the functor $F$ as a pseudofunctor $F \colon \textrm{A} \to \mathbf{Cat}$ and take advantage of the 2-categorical structure of $\mathbf{Cat}$.
+Our approach is to instead view the functor $F$ as a pseudofunctor $F \maps \textrm{A} \to \mathbf{Cat}$ and take advantage of the 2-categorical structure of $\mathbf{Cat}$.
 Given an object $a \in \mathsf{A}$, this then allows us to view $F(a)$ not as a \emph{set} of decorations on the object $a$ but as a \emph{category} of decorations on the object $a$.
@@
 \end{enumerate}
-Note that the natural transformation is a family of morphisms in the category $F(b^\prime)$ indexed by $1$, and so is the same as just a morphism $\iota \colon F(f)(d) \to d^\prime$ in $F(b^\prime)$.
+Note that the natural transformation is a family of morphisms in the category $F(b^\prime)$ indexed by $1$, and so is the same as just a morphism $\iota \maps F(f)(d) \to d^\prime$ in $F(b^\prime)$.
 We will typically write the transformation $\iota$ in later sections as a morphism in $F(b^\prime)$ to conserve space.
@@
 
-This double category is in fact fibrant and so a result of Shulman \cite{Shul} allows us to extract from this symmetric monoidal double category $F \mathbb{C}$sp a symmetric monoidal bicategory $F \mathbf{Csp} \coloneqq H(F \mathbb{C}\textnormal{sp})$ as the `horizontal edge bicategory' of the double category $F \mathbb{C}$sp.
+This double category is in fact fibrant and so a result of Shulman \cite{Shul} allows us to extract from this symmetric monoidal double category $F \mathbb{C}$sp a symmetric monoidal bicategory $F \mathbf{Csp} \mapseqq H(F \mathbb{C}\textnormal{sp})$ as the `horizontal edge bicategory' of the double category $F \mathbb{C}$sp.
 This bicategory $F \mathbf{Csp}$ has:
@@
 
-Finally, we can decategorify the symmetric monoidal bicategory $F \mathbf{Csp}$ to obtain a symmetric monoidal category $F \textnormal{Csp} \coloneqq D(F\mathbf{Csp})$.
+Finally, we can decategorify the symmetric monoidal bicategory $F \mathbf{Csp}$ to obtain a symmetric monoidal category $F \textnormal{Csp} \mapseqq D(F\mathbf{Csp})$.
 This symmetric monoidal category $F$Csp has:
@@
 This symmetric monoidal category $F$Csp has isomorphism classes as one would expect, and in the context of the example with finite sets and graphs above solves the problem in (\ref{distinctisoclasses}).
-In this particular example, $\iota \colon F(f)(d) \xrightarrow{\sim} d^\prime$ is a bijection between possibly different sets of edges which respects the source and target of each edge.
+In this particular example, $\iota \maps F(f)(d) \xrightarrow{\sim} d^\prime$ is a bijection between possibly different sets of edges which respects the source and target of each edge.
 
@@
 \begin{thm}\label{thm:decoratedcospans}
-Let $\mathsf{A}$ be a category with finite colimits and $F \colon \mathsf{A} \to \mathbf{Cat}$ a lax monoidal pseudofunctor. Then there exists a (pseudo) double category $F\mathbb{C}$sp which has:
+Let $\mathsf{A}$ be a category with finite colimits and $F \maps \mathsf{A} \to \mathbf{Cat}$ a lax monoidal pseudofunctor. Then there exists a (pseudo) double category $F\mathbb{C}$sp which has:
 \begin{enumerate}
@@
 \end{equation}
-together with a morphism $\iota \colon F(h)(m) \to m^\prime$ in $F(m^\prime)$.}
+together with a morphism $\iota \maps F(h)(m) \to m^\prime$ in $F(m^\prime)$.}
 \end{enumerate}
@@
 \begin{proof}
-The unit structure functor $U \colon F\mathbb{C}\textnormal{sp}_0 \to F\mathbb{C}\textnormal{sp}_1$ is defined on objects as: 
+The unit structure functor $U \maps F\mathbb{C}\textnormal{sp}_0 \to F\mathbb{C}\textnormal{sp}_1$ is defined on objects as: 
 \[
@@
 \]
-where $!_a \in F(a)$ is the trivial decoration on $a$ given by the composite of the unique map $F(!) \colon F(0) \to F(a)$ and the morphism $\phi \colon 1 \to F(0)$  which comes from the structure of the lax monoidal pseudofunctor $F \colon \mathsf{A} \to \mathbf{Cat}$.
+where $!_a \in F(a)$ is the trivial decoration on $a$ given by the composite of the unique map $F(!) \maps F(0) \to F(a)$ and the morphism $\phi \maps 1 \to F(0)$  which comes from the structure of the lax monoidal pseudofunctor $F \maps \mathsf{A} \to \mathbf{Cat}$.
 For morphisms, the structure functor $U$ is defined as:
@@
 \]
-together with the morphism $\iota_{!_f} = F(f) F(!) \phi \colon 1 \to F(a^\prime)$.
-We also have source and target structure functors $S, T \colon F\mathbb{C}\textnormal{sp}_1 \to F\mathbb{C}\textnormal{sp}_0$ where the source of the horizontal 1-cell
+together with the morphism $\iota_{!_f} = F(f) F(!) \phi \maps 1 \to F(a^\prime)$.
+We also have source and target structure functors $S, T \maps F\mathbb{C}\textnormal{sp}_1 \to F\mathbb{C}\textnormal{sp}_0$ where the source of the horizontal 1-cell
 \[
@@
 \]
-$$\iota \colon F(h)(m) \to m^\prime$$
+$$\iota \maps F(h)(m) \to m^\prime$$
 is the source of the underlying map of cospans in $\mathsf{A}$, namely the morphism $f$ in $\mathsf{A}$; the target structure functor is defined similarly.
@@
 $$1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{x \times y} F(m) \times F(n) \xrightarrow{\phi_{m,n}} F(m+n) \xrightarrow{F(\psi)} F(m+_{b}n)$$
-where $\psi \colon m + n \to m+_{b} n$ is the natural map from the coproduct to the pushout and $\phi_{m,n} \colon F(m) \times F(n) \to F(m+n)$ is the natural transformation coming from the structure of the lax monoidal pseudofunctor $F \colon \mathsf{A} \to \mathbf{Cat}$.
+where $\psi \maps m + n \to m+_{b} n$ is the natural map from the coproduct to the pushout and $\phi_{m,n} \maps F(m) \times F(n) \to F(m+n)$ is the natural transformation coming from the structure of the lax monoidal pseudofunctor $F \maps \mathsf{A} \to \mathbf{Cat}$.
 Denoting the first and second of these horizontal 1-cells as $M$ and $N$, respectively, the source and target structure functors satisfy the equations $S(N \odot M)=S(M)$ and $T(N \odot M)=T(N)$.
@@
 \]
-we get a natural isomorphism $a_{M_1,M_2,M_3} \colon (M_1 \odot M_2) \odot M_3 \to M_1 \odot (M_2 \odot M_3)$ which is a globular 2-morphism given by a map of cospans $(\id_{a_1},\sigma,\id_{a_4})$:
+we get a natural isomorphism $a_{M_1,M_2,M_3} \maps (M_1 \odot M_2) \odot M_3 \to M_1 \odot (M_2 \odot M_3)$ which is a globular 2-morphism given by a map of cospans $(\id_{a_1},\sigma,\id_{a_4})$:
 \[
@@
 with the decorations on the cospan's apices given by:
-$$ (x \odot y) \odot z \coloneqq 1 \xrightarrow{\zeta_1} F(m_1+_{b} m_2) \times F(m_3) \xrightarrow{\phi_{m_1+_{b} m_2, m_3}} F((m_1+_{b}m_2) +m_3) \xrightarrow{F(j_{m_1+_{b} m_2,m_3})} F((m_1+_{b} m_2)+_{c} m_3)$$ $$\zeta_1 = (1 \times z) \rho^{-1} F(j_{m_1,m_2}) \phi_{m_1,m_2} (x \times y) \lambda^{-1}$$
+$$ (x \odot y) \odot z \mapseqq 1 \xrightarrow{\zeta_1} F(m_1+_{b} m_2) \times F(m_3) \xrightarrow{\phi_{m_1+_{b} m_2, m_3}} F((m_1+_{b}m_2) +m_3) \xrightarrow{F(j_{m_1+_{b} m_2,m_3})} F((m_1+_{b} m_2)+_{c} m_3)$$ $$\zeta_1 = (1 \times z) \rho^{-1} F(j_{m_1,m_2}) \phi_{m_1,m_2} (x \times y) \lambda^{-1}$$
 and
-$$ x \odot (y \odot z) \coloneqq 1 \xrightarrow{\zeta_2} F(m_1) \times F(m_2 +_{c} m_3) \xrightarrow{\phi_{m_1, m_2 +_{c} m_3}} F(m_1+(m_2 +_{c} m_3)) \xrightarrow{F(j_{m_1,m_2 +_{c} m_3})} F(m_1+_{b} (m_2+_{c} m_3))$$ $$\zeta_2 = (x \times 1) \lambda^{-1} F(j_{m_2,m_3}) \phi_{m_2,m_3} (y \odot z) \lambda^{-1}$$
-together with the isomorphism $\iota_\sigma \colon F(\sigma)((x \odot y) \odot z) \to x \odot (y \odot z)$.
-Note that the map $\sigma \colon (m_1+_{b} m_2)+_{c}m_3 \to m_1+_{b}(m_2+_{c}m_3)$ is the universal map between two colimits of the same diagram.
+$$ x \odot (y \odot z) \mapseqq 1 \xrightarrow{\zeta_2} F(m_1) \times F(m_2 +_{c} m_3) \xrightarrow{\phi_{m_1, m_2 +_{c} m_3}} F(m_1+(m_2 +_{c} m_3)) \xrightarrow{F(j_{m_1,m_2 +_{c} m_3})} F(m_1+_{b} (m_2+_{c} m_3))$$ $$\zeta_2 = (x \times 1) \lambda^{-1} F(j_{m_2,m_3}) \phi_{m_2,m_3} (y \odot z) \lambda^{-1}$$
+together with the isomorphism $\iota_\sigma \maps F(\sigma)((x \odot y) \odot z) \to x \odot (y \odot z)$.
+Note that the map $\sigma \maps (m_1+_{b} m_2)+_{c}m_3 \to m_1+_{b}(m_2+_{c}m_3)$ is the universal map between two colimits of the same diagram.
 We also have left and right unitors where given a horizontal 1-cell $M$:
@@
 \]
-where $!_{b} = F(!)  \phi \colon 1 \to F(b)$ is the trivial decoration on $b$, composing these then gives:
+where $!_{b} = F(!)  \phi \maps 1 \to F(b)$ is the trivial decoration on $b$, composing these then gives:
 \[
@@
 \]
-where $\psi_m \colon m \to m+b$ is the natural map into the coproduct and likewise for $\psi_{b}$ and $j \colon m+b \to m+_{b} b$ is the natural map from the coproduct to the pushout.
-The decoration $x \odot !_b \colon 1 \to F(m+_{b} b)$ is given by: $$1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{x \times !_{b}} F(m) \times F(b) \xrightarrow{\phi_{m,b}} F(m+b) \xrightarrow{F(j_{m,b})} F(m+_{b} b).$$ We then have that the right unitor $R \colon M \odot 1_{b} \xrightarrow{\sim} M$ is given by the globular 2-morphism $(\id_{a},r,\id_{b})$ from the above composite to $M$:
+where $\psi_m \maps m \to m+b$ is the natural map into the coproduct and likewise for $\psi_{b}$ and $j \maps m+b \to m+_{b} b$ is the natural map from the coproduct to the pushout.
+The decoration $x \odot !_b \maps 1 \to F(m+_{b} b)$ is given by: $$1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{x \times !_{b}} F(m) \times F(b) \xrightarrow{\phi_{m,b}} F(m+b) \xrightarrow{F(j_{m,b})} F(m+_{b} b).$$ We then have that the right unitor $R \maps M \odot 1_{b} \xrightarrow{\sim} M$ is given by the globular 2-morphism $(\id_{a},r,\id_{b})$ from the above composite to $M$:
 \[
@@
 \]
-where $r \colon m+_{b} b \xrightarrow{\sim} m$ is a universal map together with the isomorphism $\iota_r \colon F(r)(x \odot !_b) \to x$.
+where $r \maps m+_{b} b \xrightarrow{\sim} m$ is a universal map together with the isomorphism $\iota_r \maps F(r)(x \odot !_b) \to x$.
 The left unitor is similar.
@@
 \node (K) at (7,-0.5) {$y' \in F(n^\prime)$};
-\node (L) at (1,-1) {$\iota_\alpha \colon F(h_1)(x) \to x'$};
-\node (M) at (5,-1) {$\iota_\beta \colon F(h_2)(y) \to y'$};
+\node (L) at (1,-1) {$\iota_\alpha \maps F(h_1)(x) \to x'$};
+\node (M) at (5,-1) {$\iota_\beta \maps F(h_2)(y) \to y'$};
 \node (A'') at (0,-1.5) {$a^\prime$};
@@
 \node (K'') at (7,-2.5) {$y'' \in F(n'')$};
-\node (L'') at (1,-3) {$\iota_{\alpha^\prime} \colon F(h_1^\prime)(x') \to x''$};
-\node (M'') at (5,-3) {$\iota_{\beta^\prime} \colon F(h_2^\prime)(y') \to y''$};
+\node (L'') at (1,-3) {$\iota_{\alpha^\prime} \maps F(h_1^\prime)(x') \to x''$};
+\node (M'') at (5,-3) {$\iota_{\beta^\prime} \maps F(h_2^\prime)(y') \to y''$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \node (F) at (4.5,-0.5) {$x' \odot y' \in F(m^\prime +_{b'} n^\prime)$};
-\node (G) at (1.5,-1) {$\iota_{\alpha \odot \beta} \colon F(h_1 +_g h_2)(x \odot y) \to x' \odot y'$};
+\node (G) at (1.5,-1) {$\iota_{\alpha \odot \beta} \maps F(h_1 +_g h_2)(x \odot y) \to x' \odot y'$};
 \node (A'') at (0,-1.5) {$a^\prime$};
@@
 \node (F'') at (4.5,-2.5) {$x'' \odot y'' \in F(m'' +_{b''} n'')$};
-\node (G'') at (1.5,-3) {$\iota_{\alpha^\prime \odot \beta^\prime} \colon F(h_1^\prime +_{g^\prime} h_2^\prime)(x' \odot y') \to x'' \odot y''.$};
+\node (G'') at (1.5,-3) {$\iota_{\alpha^\prime \odot \beta^\prime} \maps F(h_1^\prime +_{g^\prime} h_2^\prime)(x' \odot y') \to x'' \odot y''.$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \node (F) at (5.5,-0.5) {$x'' \odot y'' \in F(m'' +_{b''} n'')$};
-\node (G) at (2,-1) {$\iota_{(a^\prime \odot \beta^\prime)(\alpha \odot \beta)} \colon F((h_1^\prime +_{g^\prime} h_2^\prime)(h_1 +_g h_2))(x \odot y) \to x'' \odot y''.$};
+\node (G) at (2,-1) {$\iota_{(a^\prime \odot \beta^\prime)(\alpha \odot \beta)} \maps F((h_1^\prime +_{g^\prime} h_2^\prime)(h_1 +_g h_2))(x \odot y) \to x'' \odot y''.$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \node (K) at (7,-0.5) {$y'' \in F(n'')$};
-\node (L) at (1,-1) {$\iota_{\alpha^\prime \alpha} \colon F(h_1^\prime h_1)(x) \to x''$};
-\node (M) at (5,-1) {$\iota_{\beta^\prime \beta} \colon F(h_2^\prime h_2)(y) \to y''$};
+\node (L) at (1,-1) {$\iota_{\alpha^\prime \alpha} \maps F(h_1^\prime h_1)(x) \to x''$};
+\node (M) at (5,-1) {$\iota_{\beta^\prime \beta} \maps F(h_2^\prime h_2)(y) \to y''$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \node (F) at (5.5,-0.5) {$x'' \odot y'' \in F(m'' +_{b''} n'')$};
-\node (G) at (2,-1) {$\iota_{(\alpha^\prime \alpha) \odot (\beta^\prime \beta)} \colon F((h_1^\prime h_1)+_{g^\prime g} (h_2^\prime h_2))(x \odot y) \to x'' \odot y''.$};
+\node (G) at (2,-1) {$\iota_{(\alpha^\prime \alpha) \odot (\beta^\prime \beta)} \maps F((h_1^\prime h_1)+_{g^\prime g} (h_2^\prime h_2))(x \odot y) \to x'' \odot y''.$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 %\]
-As is usual concerning the interchange law of double categories of this nature, only the `interior' of the two composites appears different, but the two morphisms $(h_1^\prime +_{g^\prime} h_2^\prime)(h_1 +_g h_2) \colon m+_{b} n \to m'' +_{b''} n''$ and $(h_1^\prime h_1) +_{g^\prime g} (h_2^\prime h_2) \colon m+_{b} n \to m'' +_{b''}n''$ are the same universal map realized in two different ways.
+As is usual concerning the interchange law of double categories of this nature, only the `interior' of the two composites appears different, but the two morphisms $(h_1^\prime +_{g^\prime} h_2^\prime)(h_1 +_g h_2) \maps m+_{b} n \to m'' +_{b''} n''$ and $(h_1^\prime h_1) +_{g^\prime g} (h_2^\prime h_2) \maps m+_{b} n \to m'' +_{b''}n''$ are the same universal map realized in two different ways.
 The two morphisms of decorations $\iota_{(\alpha^\prime \odot \beta^\prime)(\alpha \odot \beta)}$ and $\iota_{(\alpha^\prime \alpha) \odot (\beta^\prime \beta)}$ are obtained as two different compositions of four 2-morphisms in $\mathbf{Cat}$, namely horizontally then vertically and vertically then horizontally.
-As $\mathbf{Cat}$ is a 2-category, the interchange law for these 2-morphisms already holds, and as a result, the morphisms $$\iota_{(\alpha' \odot \beta')(\alpha \odot \beta)} \colon F((h_1^\prime +_{g^\prime} h_2^\prime)(h_1 +_g h_2))(x \odot y) \to x'' \odot y''$$ and $$\iota_{(\alpha^\prime \alpha)\odot(\beta^\prime \beta)} \colon F((h_1^\prime h_1)+_{g^\prime g} (h_2^\prime h_2))(x \odot y) \to x'' \odot y''$$ are also the same.
+As $\mathbf{Cat}$ is a 2-category, the interchange law for these 2-morphisms already holds, and as a result, the morphisms $$\iota_{(\alpha' \odot \beta')(\alpha \odot \beta)} \maps F((h_1^\prime +_{g^\prime} h_2^\prime)(h_1 +_g h_2))(x \odot y) \to x'' \odot y''$$ and $$\iota_{(\alpha^\prime \alpha)\odot(\beta^\prime \beta)} \maps F((h_1^\prime h_1)+_{g^\prime g} (h_2^\prime h_2))(x \odot y) \to x'' \odot y''$$ are also the same.
 Thus the interchange law for 2-morphisms holds and $F\mathbb{C}$sp is a double category.
@@
 \begin{thm}\label{DC}
-Let $\mathsf{A}$ be a category with finite colimits and $F \colon \mathsf{A} \to \mathbf{Cat}$ a symmetric lax monoidal pseudofunctor. Then the double category $F\mathbb{C}$sp is symmetric monoidal.
+Let $\mathsf{A}$ be a category with finite colimits and $F \maps \mathsf{A} \to \mathbf{Cat}$ a symmetric lax monoidal pseudofunctor. Then the double category $F\mathbb{C}$sp is symmetric monoidal.
 \end{thm}
@@
 \]
-together with a morphism $\iota \colon F(h)(x) \to x^\prime$.
+together with a morphism $\iota \maps F(h)(x) \to x^\prime$.
 }
@@
 \]
-and where the decoration on the apex is obtained using the natural transformation of the symmetric lax monoidal pseudofunctor $F:$ $$x_1+x_2 \coloneqq 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{x_1 \times x_2} F(m_1) \times F(m_2) \xrightarrow{\phi_{m_1,m_2}} F(m_1+m_2).$$The monoidal unit 0 is given by:
+and where the decoration on the apex is obtained using the natural transformation of the symmetric lax monoidal pseudofunctor $F:$ $$x_1+x_2 \mapseqq 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{x_1 \times x_2} F(m_1) \times F(m_2) \xrightarrow{\phi_{m_1,m_2}} F(m_1+m_2).$$The monoidal unit 0 is given by:
 \[
@@
 \]
-where $0$ is the monoidal unit of $\mathsf{A}$ and $!_0 \colon 1 \to F(0)$ is the morphism which is part of the structure of the symmetric lax monoidal pseudofunctor $F \colon \mathsf{A} \to \mathbf{Cat}$.
+where $0$ is the monoidal unit of $\mathsf{A}$ and $!_0 \maps 1 \to F(0)$ is the morphism which is part of the structure of the symmetric lax monoidal pseudofunctor $F \maps \mathsf{A} \to \mathbf{Cat}$.
 Tensoring an object with the monoidal unit, say, on the left:
@@
 \]
-where $\ell$ is the left unitor of $(\mathsf{A},+,0)$, together with the isomorphism $\iota_{\lambda} \colon F(\ell)(!_0 + x) \to x$. The right unitor is similar.
+where $\ell$ is the left unitor of $(\mathsf{A},+,0)$, together with the isomorphism $\iota_{\lambda} \maps F(\ell)(!_0 + x) \to x$. The right unitor is similar.
 
@@
 \]
-where $(x_1+x_2)+x_3 \colon 1 \to F((m_1+m_2)+m_3)$ is given by: $$1 \xrightarrow{(x_1 \times x_2) \times x_3} (F(m_1) \times F(m_2)) \times F(m_3) \xrightarrow{\phi_{m_1,m_2} \times 1} F(m_1+m_2) \times F(m_3) \xrightarrow{\phi_{m_1+m_2,m_3}} F((m_1+m_2)+m_3)$$whereas tensoring the last two and then the first results in $M_1 \otimes (M_2 \otimes M_3)$:
+where $(x_1+x_2)+x_3 \maps 1 \to F((m_1+m_2)+m_3)$ is given by: $$1 \xrightarrow{(x_1 \times x_2) \times x_3} (F(m_1) \times F(m_2)) \times F(m_3) \xrightarrow{\phi_{m_1,m_2} \times 1} F(m_1+m_2) \times F(m_3) \xrightarrow{\phi_{m_1+m_2,m_3}} F((m_1+m_2)+m_3)$$whereas tensoring the last two and then the first results in $M_1 \otimes (M_2 \otimes M_3)$:
 \[
@@
 \]
-where $x_1+(x_2+x_3) \colon 1 \to F(m_1+(m_2+m_3))$ is given by: $$1 \xrightarrow{x_1 \times (x_2 \times x_3)} F(m_1) \times (F(m_2) \times F(m_3)) \xrightarrow{1 \times \phi_{m_2,m_3}} F(m_1) \times F(m_2+m_3) \xrightarrow{\phi_{m_1,m_2+m_3}} F(m_1+(m_2+m_3)).$$If we let $a$ denote the associator of $(\mathsf{A},+,0)$, the associator of $F\mathbb{C}\textnormal{sp}_1$ is then a map of cospans in $\mathsf{A}$ from $(M_1 \otimes M_2) \otimes M_3$ to $M_1 \otimes (M_2 \otimes M_3)$ given by:
+where $x_1+(x_2+x_3) \maps 1 \to F(m_1+(m_2+m_3))$ is given by: $$1 \xrightarrow{x_1 \times (x_2 \times x_3)} F(m_1) \times (F(m_2) \times F(m_3)) \xrightarrow{1 \times \phi_{m_2,m_3}} F(m_1) \times F(m_2+m_3) \xrightarrow{\phi_{m_1,m_2+m_3}} F(m_1+(m_2+m_3)).$$If we let $a$ denote the associator of $(\mathsf{A},+,0)$, the associator of $F\mathbb{C}\textnormal{sp}_1$ is then a map of cospans in $\mathsf{A}$ from $(M_1 \otimes M_2) \otimes M_3$ to $M_1 \otimes (M_2 \otimes M_3)$ given by:
 \[
@@
 \]
-together with the isomorphism $\iota_a \colon F(a)((x_1+x_2)+x_3) \to x_1+(x_2+x_3)$.
+together with the isomorphism $\iota_a \maps F(a)((x_1+x_2)+x_3) \to x_1+(x_2+x_3)$.
 These associators and left and right unitors together satisfy the pentagon and triangle identities of a monoidal category.
@@
 
-For a tensor product of objects $M_1 \otimes M_2$ in $F\mathbb{C}\textnormal{sp}_1$, the source and target structure functors $S,T \colon F\mathbb{C}\textnormal{sp}_1 \to F\mathbb{C}\textnormal{sp}_0$ satisfy the following equations: $$S(M_1 \otimes M_2)=S(M_1) \otimes S(M_2)$$ $$T(M_1 \otimes M_2)=T(M_1) \otimes T(M_2).$$
-For two objects $M_1$ and $M_2$ in $F\mathbb{C}\textnormal{sp}_1$, we have a braiding $\beta_{M_1,M_2} \colon M_1 \otimes M_2 \to M_2 \otimes M_1$ given by:
+For a tensor product of objects $M_1 \otimes M_2$ in $F\mathbb{C}\textnormal{sp}_1$, the source and target structure functors $S,T \maps F\mathbb{C}\textnormal{sp}_1 \to F\mathbb{C}\textnormal{sp}_0$ satisfy the following equations: $$S(M_1 \otimes M_2)=S(M_1) \otimes S(M_2)$$ $$T(M_1 \otimes M_2)=T(M_1) \otimes T(M_2).$$
+For two objects $M_1$ and $M_2$ in $F\mathbb{C}\textnormal{sp}_1$, we have a braiding $\beta_{M_1,M_2} \maps M_1 \otimes M_2 \to M_2 \otimes M_1$ given by:
 \[
@@
 \]
-$$\iota_{\beta_{M_1,M_2}} \colon F(\beta_{m_1,m_2})(x_1+x_2) \xrightarrow{\sim} x_2+x_1$$ where the vertical 1-morphisms are given by braidings in $(\mathsf{A},+,0)$.
+$$\iota_{\beta_{M_1,M_2}} \maps F(\beta_{m_1,m_2})(x_1+x_2) \xrightarrow{\sim} x_2+x_1$$ where the vertical 1-morphisms are given by braidings in $(\mathsf{A},+,0)$.
 This braiding makes the following triangle of underlying cospans commute:
@@
 and where $\psi$ and $j$ are the natural maps into a coproduct and from a coproduct into a pushout, respectively.
-We then get a globular 2-morphism $$\chi \colon (M_1 \otimes N_1) \odot (M_2 \otimes N_2) \to (M_1 \odot M_2) \otimes (N_1 \odot N_2)$$ given by:
+We then get a globular 2-morphism $$\chi \maps (M_1 \otimes N_1) \odot (M_2 \otimes N_2) \to (M_1 \odot M_2) \otimes (N_1 \odot N_2)$$ given by:
 \[
@@
 \]
-$$\iota_{\hat{\chi}} \colon F(\hat{\chi})((x_1+y_1)\odot(x_2+y_2)) \to (x_1 \odot x_2)+(y_1 \odot y_2)$$
+$$\iota_{\hat{\chi}} \maps F(\hat{\chi})((x_1+y_1)\odot(x_2+y_2)) \to (x_1 \odot x_2)+(y_1 \odot y_2)$$
 where $\hat{\chi}$ is the universal map between two colimits of the same diagram.
@@
 \]
-where $$!_{a+b} \colon 1 \xrightarrow{\phi} F(0) \xrightarrow{F(!_{a+b})}  F(a+b).$$
+where $$!_{a+b} \maps 1 \xrightarrow{\phi} F(0) \xrightarrow{F(!_{a+b})}  F(a+b).$$
 Similarly, we have $U_a$ and $U_b$ given respectively by:
@@
 where
-$$!_a + !_b \colon 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{\phi \times \phi} F(0) \times F(0) \xrightarrow{F(!_a) \times F(!_b)} F(a) \times F(b) \xrightarrow{\phi_{a,b}} F(a+b).$$
-We then have another globular isomorphism $$\mu_{a,b} \colon U_{a+b} \to U_a + U_b$$ given by the identity 2-morphism:
+$$!_a + !_b \maps 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{\phi \times \phi} F(0) \times F(0) \xrightarrow{F(!_a) \times F(!_b)} F(a) \times F(b) \xrightarrow{\phi_{a,b}} F(a+b).$$
+We then have another globular isomorphism $$\mu_{a,b} \maps U_{a+b} \to U_a + U_b$$ given by the identity 2-morphism:
 \[
@@
 \]
-$$\iota_{a,b} \colon !_{a+b} \xrightarrow{\sim} !_a + !_b$$
+$$\iota_{a,b} \maps !_{a+b} \xrightarrow{\sim} !_a + !_b$$
 where $!_{a+b}$ and $!_a + !_b$ are both initial objects in $F(a+b)$, hence isomorphic.
@@
 The above diagram of maps of cospans can then be visualized as a hexagonal prism in which all the faces commute by identifying the top and the bottom as the same.
-As for the morphisms of decorations, which are labeled on the right of the interior vertical 1-morphisms, each isomorphism $\iota_n$ goes from the domain under the image of the functor $F$ applied to natural isomorphism adjacent to it to the codomain as written, meaning that, for example: $$\iota_1 \colon F(a \odot a)(((x_1+y_1)+z_1) \odot ((x_2+y_2)+z_2)) \to (x_1+(y_1+z_1)) \odot (x_2+(y_2+z_2)).$$  The following diagram commutes in the category $F((m_1+_b m_2) + ((n_1+_{b'} n_2) + (p_1+_{b''} p_2)))$:
+As for the morphisms of decorations, which are labeled on the right of the interior vertical 1-morphisms, each isomorphism $\iota_n$ goes from the domain under the image of the functor $F$ applied to natural isomorphism adjacent to it to the codomain as written, meaning that, for example: $$\iota_1 \maps F(a \odot a)(((x_1+y_1)+z_1) \odot ((x_2+y_2)+z_2)) \to (x_1+(y_1+z_1)) \odot (x_2+(y_2+z_2)).$$  The following diagram commutes in the category $F((m_1+_b m_2) + ((n_1+_{b'} n_2) + (p_1+_{b''} p_2)))$:
 \[
@@
 
-Another requirement for a double category to be symmetric monoidal is that the braiding $$\beta_{ ( \_, \_ ) } \colon F\mathbb{C}\textnormal{sp}_1 \times F\mathbb{C}\textnormal{sp}_1 \to F\mathbb{C}\textnormal{sp}_1 \times F\mathbb{C}\textnormal{sp}_1$$ be a transformation of double categories, and one of the diagrams that is required to commute is the following:
+Another requirement for a double category to be symmetric monoidal is that the braiding $$\beta_{ ( \_, \_ ) } \maps F\mathbb{C}\textnormal{sp}_1 \times F\mathbb{C}\textnormal{sp}_1 \to F\mathbb{C}\textnormal{sp}_1 \times F\mathbb{C}\textnormal{sp}_1$$ be a transformation of double categories, and one of the diagrams that is required to commute is the following:
 \[
@@
 \begin{proof}
-Let $f \colon c \to c^\prime$ be a vertical 1-morphism in $F\mathbb{C}\textnormal{sp}$. We can lift $f$ to the companion horizontal 1-cell $\hat{f}$:
+Let $f \maps c \to c^\prime$ be a vertical 1-morphism in $F\mathbb{C}\textnormal{sp}$. We can lift $f$ to the companion horizontal 1-cell $\hat{f}$:
 \[
@@
 \node (L) at (1,-1) {$\iota_{1_{c^\prime}} = 1_{!_{c^\prime}}$};
-\node (M) at (5,-1) {$\iota_f \colon F(f)(!_c) \to !_{c^\prime}$};
+\node (M) at (5,-1) {$\iota_f \maps F(f)(!_c) \to !_{c^\prime}$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \node (K) at (7,0) {$!_{c^\prime} \in F(c^\prime)$};
-\node (Q) at (1,-1) {$\iota_f \colon F(f)(!_c) \to !_{c^\prime}$};
+\node (Q) at (1,-1) {$\iota_f \maps F(f)(!_c) \to !_{c^\prime}$};
 \node (L) at (1,-1.5) {$\iota_{c^\prime} = 1_{!_{c^\prime}}$};
-\node (M) at (5,-0.5) {$\iota_f \colon F(f)(!_c) \to !_{c^\prime}$};
+\node (M) at (5,-0.5) {$\iota_f \maps F(f)(!_c) \to !_{c^\prime}$};
 \node (R) at (3,0.5) {$=$};
@@
 
-\node (L') at (-1,-1.5) {$\iota_{f} \colon F(f)(!_c) \to !_{c^\prime}$};
+\node (L') at (-1,-1.5) {$\iota_{f} \maps F(f)(!_c) \to !_{c^\prime}$};
 
@@
 \begin{cor}
-Let $(\mathsf{C},+,0)$ be a category with finite colimts and $F \colon \mathsf{C} \to \mathbf{Cat}$ a symmetric lax monoidal pseudofunctor.
-Then there exists a symmetric monoidal bicategory $F \mathbf{Csp} \coloneqq H(F\mathbb{C}\textnormal{sp})$ which has:
+Let $(\mathsf{C},+,0)$ be a category with finite colimts and $F \maps \mathsf{C} \to \mathbf{Cat}$ a symmetric lax monoidal pseudofunctor.
+Then there exists a symmetric monoidal bicategory $F \mathbf{Csp} \mapseqq H(F\mathbb{C}\textnormal{sp})$ which has:
 \begin{enumerate}
@@
 \]
-together with a morphism $\iota \colon F(h)(d) \to d^\prime$ in $F(c^\prime)$.}
+together with a morphism $\iota \maps F(h)(d) \to d^\prime$ in $F(c^\prime)$.}
 \end{enumerate}
@@
 %The previous bicategory constructed by the second author suffered even more so from the issue discussed in the introduction.
-Given a symmetric lax monoidal functor $F \colon \mathrm{A} \to \mathrm{Set}$, a result of Fong \cite{Fong} yields a symmetric monoidal category $F \textnormal{Cospan}(\mathrm{A})$ which has:
+Given a symmetric lax monoidal functor $F \maps \mathrm{A} \to \mathrm{Set}$, a result of Fong \cite{Fong} yields a symmetric monoidal category $F \textnormal{Cospan}(\mathrm{A})$ which has:
 %\begin{enumerate}
@@
 In the bicategorical version of $F \textnormal{Cospan}(\mathrm{A})$ where we are no longer considering decorated cospans up to isomorphism class, there is no 2-morphism between these two graphs due to the strict commutativity of the triangle to the right above.
-This problem does not occur in the symmetric monoidal bicategory $H(\mathbb{F}\textnormal{Cospan}(\mathrm{A}))$ and there is in fact a 2-(iso)morphism between these two graphs given by the map $\iota \colon F(f)(d) \to d^\prime$ which maps the edge $e$ to the edge $e^\prime$, where $f$ is the underlying map of vertices.
-
-%Again, let $F \colon \mathbf{FinSet} \to \mathbf{Set}$ be the symmetric lax monoidal functor that maps a finite set $N$ to the large set of all possible graph structures whose underlying set of vertices is $N$.
+This problem does not occur in the symmetric monoidal bicategory $H(\mathbb{F}\textnormal{Cospan}(\mathrm{A}))$ and there is in fact a 2-(iso)morphism between these two graphs given by the map $\iota \maps F(f)(d) \to d^\prime$ which maps the edge $e$ to the edge $e^\prime$, where $f$ is the underlying map of vertices.
+
+%Again, let $F \maps \mathbf{FinSet} \to \mathbf{Set}$ be the symmetric lax monoidal functor that maps a finite set $N$ to the large set of all possible graph structures whose underlying set of vertices is $N$.
 Then a result of Fong \cite{Fong} yields a symmetric monoidal category $F\textnormal{Cospan}(\mathbf{FinSet})$ which has:
@@
 \begin{cor}
-Given a symmetric lax monoidal pseudofunctor $F \colon \mathsf{A} \to \mathbf{Cat}$ where $\mathsf{A}$ is a category with finite colimits and whose monoidal structure is given by binary coproducts, there exists a symmetric monoidal category $F\textnormal{Csp} \coloneqq D(F\mathbf{Csp})$ which has:
+Given a symmetric lax monoidal pseudofunctor $F \maps \mathsf{A} \to \mathbf{Cat}$ where $\mathsf{A}$ is a category with finite colimits and whose monoidal structure is given by binary coproducts, there exists a symmetric monoidal category $F\textnormal{Csp} \mapseqq D(F\mathbf{Csp})$ which has:
 \begin{enumerate}
@@
 \]
-these two $F$-decorated cospans are in the same isomorphism class if there exists an isomorphism $f \colon c \to c^\prime$ such that following diagram commutes:
+these two $F$-decorated cospans are in the same isomorphism class if there exists an isomorphism $f \maps c \to c^\prime$ such that following diagram commutes:
 \[
@@
 \]
-and there exists an isomorphism $\iota \colon F(f)(d) \to d^\prime$ in $F(c^\prime)$.}
+and there exists an isomorphism $\iota \maps F(f)(d) \to d^\prime$ in $F(c^\prime)$.}
 \end{enumerate}
@@
 
-%Let $F \colon \mathsf{A} \to \mathbf{Cat}$ be a symmetric lax monoidal pseudofunctor.
+%Let $F \maps \mathsf{A} \to \mathbf{Cat}$ be a symmetric lax monoidal pseudofunctor.
 Then by Theorem \ref{DC} of the previous section, we get a symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$.
@@
 %\]
-%together with a morphism $\iota \colon F(h)(d) \to d^\prime$ in $F(c^\prime)$.}
+%together with a morphism $\iota \maps F(h)(d) \to d^\prime$ in $F(c^\prime)$.}
 %\end{enumerate}
 
-Regarding maps between symmetric monoidal double categories, consider another symmetric lax monoidal pseudofunctor $F^\prime \colon \mathsf{A^\prime} \to \mathbf{Cat}$%, we can obtain another symmetric monoidal double category $F^\prime \mathbb{C}\textnormal{sp}$.
-a morphism from $F\mathbb{C}\textnormal{sp}$ to $F^\prime \mathbb{C}\textnormal{sp}$ will then be a double functor $\mathbb{H} \colon F\mathbb{C}\textnormal{sp} \to F' \mathbb{C}\textnormal{sp}$ whose object component is given by a finite colimit preserving functor $\mathbb{H}_0 = H \colon \mathsf{A} \to \mathsf{A^\prime}$ and whose arrow component is given by a functor $\mathbb{H}_1$ defined on horizontal 1-cells by:
+Regarding maps between symmetric monoidal double categories, consider another symmetric lax monoidal pseudofunctor $F^\prime \maps \mathsf{A^\prime} \to \mathbf{Cat}$%, we can obtain another symmetric monoidal double category $F^\prime \mathbb{C}\textnormal{sp}$.
+a morphism from $F\mathbb{C}\textnormal{sp}$ to $F^\prime \mathbb{C}\textnormal{sp}$ will then be a double functor $\mathbb{H} \maps F\mathbb{C}\textnormal{sp} \to F' \mathbb{C}\textnormal{sp}$ whose object component is given by a finite colimit preserving functor $\mathbb{H}_0 = H \maps \mathsf{A} \to \mathsf{A^\prime}$ and whose arrow component is given by a functor $\mathbb{H}_1$ defined on horizontal 1-cells by:
 \[
@@
 \node (F) at (3,-0.5) {$d^\prime \in F(c^\prime)$};
-\node (G) at (1,-1) {$\iota \colon F(h)(d) \to d^\prime$};
+\node (G) at (1,-1) {$\iota \maps F(h)(d) \to d^\prime$};
 \node (A'') at (4.25,0.5) {$H(a)$};
@@
 \node (F'') at (8,-0.5) {$\theta_{c'} E(d^\prime) \phi \in F^\prime(H(c^\prime))$};
-\node (G'') at (5.25,-1) {$E(\iota) \colon F^\prime(H(h))(\theta_c E(d)\phi) \to (\theta_{c'}E(d^\prime)\phi)$};
+\node (G'') at (5.25,-1) {$E(\iota) \maps F^\prime(H(h))(\theta_c E(d)\phi) \to (\theta_{c'}E(d^\prime)\phi)$};
 \node (H) at (3.5,0) {$\mapsto$};
@@
 \]
-where $E \colon \mathbf{Cat} \to \mathbf{Cat}$ is a symmetric lax monoidal pseudofuctor such that the following diagram commutes up to isomorphism $\theta \colon EF \Rightarrow F'H$:
+where $E \maps \mathbf{Cat} \to \mathbf{Cat}$ is a symmetric lax monoidal pseudofuctor such that the following diagram commutes up to isomorphism $\theta \maps EF \Rightarrow F'H$:
 \[
@@
 \begin{comment}
-Recall that we can think of the object $d \in F(c)$ as a morphism $d \colon 1 \to F(c)$ and the functor $\iota \colon F(h)(d) \to d^\prime$ of $F(c^\prime)$ as a natural transformation  in $\mathbf{Cat}$:
+Recall that we can think of the object $d \in F(c)$ as a morphism $d \maps 1 \to F(c)$ and the functor $\iota \maps F(h)(d) \to d^\prime$ of $F(c^\prime)$ as a natural transformation  in $\mathbf{Cat}$:
 \[
@@
 \]
-Applying the symmetric lax monoidal pseudofunctor $E \colon \mathbf{Cat} \to \mathbf{Cat}$ to this diagram yields:
+Applying the symmetric lax monoidal pseudofunctor $E \maps \mathbf{Cat} \to \mathbf{Cat}$ to this diagram yields:
 \[
@@
 \]
-Then because the above square commutes up to the isomorphism $\theta \colon EF \Rightarrow F'H$, we get:
+Then because the above square commutes up to the isomorphism $\theta \maps EF \Rightarrow F'H$, we get:
 \[
@@
 \]
-which results in a 2-morphism $E(\iota) \colon F^\prime(H(h))(\theta_c E(d)\phi) \to (\theta_{c'} E(d^\prime)\phi)$ in $F^\prime(H(c^\prime))$.
+which results in a 2-morphism $E(\iota) \maps F^\prime(H(h))(\theta_c E(d)\phi) \to (\theta_{c'} E(d^\prime)\phi)$ in $F^\prime(H(c^\prime))$.
 To check that the above recipe is functorial, given two vertically composable 2-morphisms in $F\mathbb{C}\textnormal{sp}$:
@@
 \node (F) at (4.5,-0.5) {$d^\prime \in F(c^\prime)$};
-\node (G) at (1.5,-1) {$\iota \colon F(h)(d) \to d^\prime$};
+\node (G) at (1.5,-1) {$\iota \maps F(h)(d) \to d^\prime$};
 \node (A'') at (0,-1.5) {$a^\prime$};
@@
 \node (F'') at (4.5,-2.5) {$d'' \in F(c'')$};
-\node (G'') at (1.5,-3) {$\iota^\prime \colon F(h^\prime)(d^\prime) \to d''$};
+\node (G'') at (1.5,-3) {$\iota^\prime \maps F(h^\prime)(d^\prime) \to d''$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \node (F) at (4.5,-0.5) {$d'' \in F(c'')$};
-\node (G) at (1.5,-1) {$\iota ^\prime \iota \colon F(h^\prime h)(d) \to d''$};
+\node (G) at (1.5,-1) {$\iota ^\prime \iota \maps F(h^\prime h)(d) \to d''$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \node (F) at (5,-0.5) {$\theta_{c''} E(d'') \phi \in F^\prime(H(c''))$};
-\node (G) at (1.5,-1) {$E(\iota ^\prime \iota) \colon F^\prime(H(h^\prime h))(\theta_c E(d)\phi) \to (\theta_{c''}E(d'')\phi).$};
+\node (G) at (1.5,-1) {$E(\iota ^\prime \iota) \maps F^\prime(H(h^\prime h))(\theta_c E(d)\phi) \to (\theta_{c''}E(d'')\phi).$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \node (F) at (5,-0.5) {$\theta_{c'} E(d^\prime) \phi \in F^\prime(H(c^\prime))$};
-\node (G) at (1.5,-1) {$E(\iota) \colon F^\prime(H(h))(\theta_c E(d)\phi) \to (\theta_{c'} E(d^\prime)\phi)$};
+\node (G) at (1.5,-1) {$E(\iota) \maps F^\prime(H(h))(\theta_c E(d)\phi) \to (\theta_{c'} E(d^\prime)\phi)$};
 \node (A'') at (0,-1.5) {$H(a^\prime)$};
@@
 \node (F'') at (5,-2.5) {$\theta_{c''} E(d'') \phi \in F^\prime(H(c''))$};
-\node (G'') at (1.5,-3) {$E(\iota^\prime) \colon F^\prime(H(h^\prime))(\theta_{c'} E(d^\prime)\phi) \to (\theta_{c''}E(d'')\phi)$};
+\node (G'') at (1.5,-3) {$E(\iota^\prime) \maps F^\prime(H(h^\prime))(\theta_{c'} E(d^\prime)\phi) \to (\theta_{c''}E(d'')\phi)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-where $$d \colon 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{d_1 \times d_2} F(c_1) \times F(c_2) \xrightarrow{\phi_{c_1,c_2}} F(c_1+c_2) \xrightarrow{F(j)}F(c_1 +_b c_2).$$ The image of this horizontal 1-cell is then given by $\mathbb{H}(M \odot N)$:
+where $$d \maps 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{d_1 \times d_2} F(c_1) \times F(c_2) \xrightarrow{\phi_{c_1,c_2}} F(c_1+c_2) \xrightarrow{F(j)}F(c_1 +_b c_2).$$ The image of this horizontal 1-cell is then given by $\mathbb{H}(M \odot N)$:
 \[
@@
 \]
-where $$\mathbb{H}(M \odot N) = \theta_{c_1 +_b c_2} E(d_{M \odot N}) \phi \colon 1 \xrightarrow{\phi} E(1) \xrightarrow{E(d)} E(F(c_1 +_b c_2)) \xrightarrow{\theta_{c_1 +_b c_2}} F^\prime(H(c_1 +_b c_2)).$$ On the other hand, the image of each horizontal 1-cell under the double functor $\mathbb{H}$ is given respectively by $\mathbb{H}(M)$ and $\mathbb{H}(N)$:
+where $$\mathbb{H}(M \odot N) = \theta_{c_1 +_b c_2} E(d_{M \odot N}) \phi \maps 1 \xrightarrow{\phi} E(1) \xrightarrow{E(d)} E(F(c_1 +_b c_2)) \xrightarrow{\theta_{c_1 +_b c_2}} F^\prime(H(c_1 +_b c_2)).$$ On the other hand, the image of each horizontal 1-cell under the double functor $\mathbb{H}$ is given respectively by $\mathbb{H}(M)$ and $\mathbb{H}(N)$:
 \[
@@
 \]
-where $$\hspace{-.4in}\scriptstyle{d_{\mathbb{H}(M) \odot \mathbb{H}(N)} \colon 1 \xrightarrow{(\theta_{c_1} \times \theta_{c_2})(E(d_M) \times E(d_N)) \phi} F^\prime(H(c_1)) \times F^\prime(H(c_2)) \xrightarrow{\Phi_{H(c_1),H(c_2)}} F^\prime(H(c_1)+ H(c_2)) \xrightarrow{F^\prime (J)} F^\prime(H(c_1) +_{H(b)} H(c_2)).}$$
-We then have a comparison constraint: $$\mathbb{H}_{M,N} \colon \mathbb{H}(M) \odot \mathbb{H}(N) \xrightarrow{\sim} \mathbb{H}(M \odot N)$$given by the globular 2-isomorphism:
+where $$\hspace{-.4in}\scriptstyle{d_{\mathbb{H}(M) \odot \mathbb{H}(N)} \maps 1 \xrightarrow{(\theta_{c_1} \times \theta_{c_2})(E(d_M) \times E(d_N)) \phi} F^\prime(H(c_1)) \times F^\prime(H(c_2)) \xrightarrow{\Phi_{H(c_1),H(c_2)}} F^\prime(H(c_1)+ H(c_2)) \xrightarrow{F^\prime (J)} F^\prime(H(c_1) +_{H(b)} H(c_2)).}$$
+We then have a comparison constraint: $$\mathbb{H}_{M,N} \maps \mathbb{H}(M) \odot \mathbb{H}(N) \xrightarrow{\sim} \mathbb{H}(M \odot N)$$given by the globular 2-isomorphism:
 \[
@@
 \node (F) at (7.5,-0.5) {$d_{\mathbb{H}(M \odot N)} \in F^\prime(H(c_1 +_b c_2))$};
-\node (G) at (2.5,-1) {$\iota_{\kappa^{-1}} \colon F^\prime(\kappa^{-1})(d_{\mathbb{H}(M) \odot \mathbb{H}(N)}) \to d_{\mathbb{H}(M \odot N)}.$};
+\node (G) at (2.5,-1) {$\iota_{\kappa^{-1}} \maps F^\prime(\kappa^{-1})(d_{\mathbb{H}(M) \odot \mathbb{H}(N)}) \to d_{\mathbb{H}(M \odot N)}.$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-where $\kappa$ is the isomorphism $$\kappa \colon H(c_1 +_b c_2) \xrightarrow{\sim} H(c_1) +_{H(b)} H(c_2)$$ which comes from the finite colimit preserving functor $H \colon \mathsf{A} \to \mathsf{A^\prime}$.
+where $\kappa$ is the isomorphism $$\kappa \maps H(c_1 +_b c_2) \xrightarrow{\sim} H(c_1) +_{H(b)} H(c_2)$$ which comes from the finite colimit preserving functor $H \maps \mathsf{A} \to \mathsf{A^\prime}$.
 The above diagram commutes by a similar argument to the one used in Theorem \ref{Equiv}.
-Similarly, for every object $c \in \mathsf{A}$, we have a unit comparison constraint $$\mathbb{H}_U \colon U_{\mathbb{H}(c)} \to \mathbb{H}(U_c)$$ given by the globular 2-isomorphism:
+Similarly, for every object $c \in \mathsf{A}$, we have a unit comparison constraint $$\mathbb{H}_U \maps U_{\mathbb{H}(c)} \to \mathbb{H}(U_c)$$ given by the globular 2-isomorphism:
 \[
@@
 \]
-where the morphism of decorations is the morphism $\iota \colon !_{H(c)} \to (\theta_c E(!_c) \phi)$ in $F'(H(c))$.
+where the morphism of decorations is the morphism $\iota \maps !_{H(c)} \to (\theta_c E(!_c) \phi)$ in $F'(H(c))$.
 These comparison constrains satisfy the coherence axioms of a monoidal category, namely:
@@
 Next we show that this double functor is symmetric monoidal.
-First, that the object component $\mathbb{H}_0=H$ is symmetric monoidal is clear as $H \colon \mathsf{A} \to \mathsf{A}^\prime$ preserves finite colimits.
+First, that the object component $\mathbb{H}_0=H$ is symmetric monoidal is clear as $H \maps \mathsf{A} \to \mathsf{A}^\prime$ preserves finite colimits.
 As for the arrow component $\mathbb{H}_1$, given two horizontal 1-cells $M_1$ and $M_2$ in $F\mathbb{C}\textnormal{sp}$:
@@
 \]
-$$d_{M_1 \otimes M_2} \colon 1 \xrightarrow{d_1 \times d_2} F(c_1) \times F(c_2) \xrightarrow{\phi_{c_1,c_2}} F(c_1+c_2)$$
+$$d_{M_1 \otimes M_2} \maps 1 \xrightarrow{d_1 \times d_2} F(c_1) \times F(c_2) \xrightarrow{\phi_{c_1,c_2}} F(c_1+c_2)$$
 and the image of this horizontal 1-cell under the double functor $\mathbb{H}$ is $\mathbb{H}(M_1 \otimes M_2)$ given by:
@@
 \]
-$$\hspace{-.4in} \scriptstyle{d_{\mathbb{H}(M_1) \otimes \mathbb{H}(M_2)} \colon 1 \xrightarrow{(\phi \times \phi)(\lambda^{-1} \times \lambda^{-1})} E(1) \times E(1) \xrightarrow{(\theta_{c_1} \times \theta_{c_2})(E(d_{M_1}) \times E(d_{M_2}))} F^\prime(H(c_1)) \times F^\prime(H(c_2)) \xrightarrow{\Phi_{H(c_1),H(c_2)}} F^\prime (H(c_1)+H(c_2)).}$$  We then have a natural 2-isomorphism $\mu_{M_1,M_2} \colon \mathbb{H}(M_1) \otimes \mathbb{H}(M_2) \to \mathbb{H}(M_1 \otimes M_2)$ in $F'\mathbb{C}\textnormal{sp}$ given by:
+$$\hspace{-.4in} \scriptstyle{d_{\mathbb{H}(M_1) \otimes \mathbb{H}(M_2)} \maps 1 \xrightarrow{(\phi \times \phi)(\lambda^{-1} \times \lambda^{-1})} E(1) \times E(1) \xrightarrow{(\theta_{c_1} \times \theta_{c_2})(E(d_{M_1}) \times E(d_{M_2}))} F^\prime(H(c_1)) \times F^\prime(H(c_2)) \xrightarrow{\Phi_{H(c_1),H(c_2)}} F^\prime (H(c_1)+H(c_2)).}$$  We then have a natural 2-isomorphism $\mu_{M_1,M_2} \maps \mathbb{H}(M_1) \otimes \mathbb{H}(M_2) \to \mathbb{H}(M_1 \otimes M_2)$ in $F'\mathbb{C}\textnormal{sp}$ given by:
 \[
@@
 \]
-$$\iota_\kappa \colon F^\prime(\kappa)(d_{\mathbb{H}(M_1) \otimes \mathbb{H}(M_2)}) \to d_{\mathbb{H}(M_1 \otimes M_2)}$$
+$$\iota_\kappa \maps F^\prime(\kappa)(d_{\mathbb{H}(M_1) \otimes \mathbb{H}(M_2)}) \to d_{\mathbb{H}(M_1 \otimes M_2)}$$
 where $\kappa$ denotes the isomorphism arising from $H$ preserving finite colimits.
@@
 where $$F^\prime(\alpha \kappa \kappa)(d_{(\mathbb{H}(M_1) \otimes \mathbb{H}(M_2)) \otimes \mathbb{H}(M_3)}) = F^\prime(\kappa \kappa \alpha^\prime)(d_{(\mathbb{H}(M_1) \otimes \mathbb{H}(M_2)) \otimes \mathbb{H}(M_3)})$$
-as the corresponding hexagon for the finite colimit preserving functor $H \colon \mathsf{A} \to \mathsf{A'}$ commutes.
-The map $\mu_{M_1,M_2}$ is also compatible with the braidings $\beta$ and $\beta^\prime$ of $F \mathbb{C}\textnormal{sp}_1$ and $F' \mathbb{C}\textnormal{sp}_1$, respectively, and make the necessary square commute as a consequence of the corresponding commutative square involving braidings from the finite colimit preserving functor $H \colon \mathsf{A} \to \mathsf{A'}$.
+as the corresponding hexagon for the finite colimit preserving functor $H \maps \mathsf{A} \to \mathsf{A'}$ commutes.
+The map $\mu_{M_1,M_2}$ is also compatible with the braidings $\beta$ and $\beta^\prime$ of $F \mathbb{C}\textnormal{sp}_1$ and $F' \mathbb{C}\textnormal{sp}_1$, respectively, and make the necessary square commute as a consequence of the corresponding commutative square involving braidings from the finite colimit preserving functor $H \maps \mathsf{A} \to \mathsf{A'}$.
 
@@
 \]
-where $1_\mathsf{A}$ is the monoidal unit of the finitely cocartesian category $\mathsf{A}$. The image of this horizontal 1-cell under $\mathbb{H}$ is given by:
+where $1_\mathsf{A}$ is the monoidal unit of the cocartesian category $\mathsf{A}$. The image of this horizontal 1-cell under $\mathbb{H}$ is given by:
 \[
@@
 as $H$ preserves finite colimits.
-We then have a 2-isomorphism in $F'\mathbb{C}\textnormal{sp}$ given by: $$\mu \colon 1_{F'\mathbb{C}\textnormal{sp}_1} \to \mathbb{H}(1_{F\mathbb{C}\textnormal{sp}_1})$$
+We then have a 2-isomorphism in $F'\mathbb{C}\textnormal{sp}$ given by: $$\mu \maps 1_{F'\mathbb{C}\textnormal{sp}_1} \to \mathbb{H}(1_{F\mathbb{C}\textnormal{sp}_1})$$
 \[
@@
 \]
-together with the morphism $\iota_\mu \colon F^\prime(\kappa)(!_{1_\mathsf{A^\prime}}) \to (\theta_{1_\mathsf{A}} E(!_{1_\mathsf{A}})\phi)$ in $F^\prime(H(1_\mathsf{A}))$.
+together with the morphism $\iota_\mu \maps F^\prime(\kappa)(!_{1_\mathsf{A^\prime}}) \to (\theta_{1_\mathsf{A}} E(!_{1_\mathsf{A}})\phi)$ in $F^\prime(H(1_\mathsf{A}))$.
 The following square then commutes for any horizontal 1-cell $M$ of $F \mathbb{C}\textnormal{sp}$:
@@
 \]
-where $$F^\prime(\ell)(d_{!_{1_\mathsf{A^\prime}}} \otimes d_{\mathbb{H}(M)})=F^\prime(H(\ell^\prime)\kappa(\mu \otimes 1))(d_{!_{1_\mathsf{A^\prime}}} \otimes d_{\mathbb{H}(M)})$$ since the corresponding square involving left unitors for the finite colimit preserving functor $H \colon \mathsf{A} \to \mathsf{A'}$ commutes.
+where $$F^\prime(\ell)(d_{!_{1_\mathsf{A^\prime}}} \otimes d_{\mathbb{H}(M)})=F^\prime(H(\ell^\prime)\kappa(\mu \otimes 1))(d_{!_{1_\mathsf{A^\prime}}} \otimes d_{\mathbb{H}(M)})$$ since the corresponding square involving left unitors for the finite colimit preserving functor $H \maps \mathsf{A} \to \mathsf{A'}$ commutes.
 The other square involving the right unitors $r$ and $r^\prime$ is similar.
@@
 \begin{thm}
-Given two finitely cocomplete categories $\mathsf{A}$ and $\mathsf{A}'$, two symmetric lax monoidal pseudofunctors $F \colon \mathsf{A} \to \mathbf{Cat}$ and $F' \colon \mathsf{A}' \to \mathbf{Cat}$, a finite colimit preserving functor $H \colon \mathsf{A} \to \mathsf{A}'$, a symmetric lax monoidal pseudofunctor $E \colon \mathbf{Cat} \to \mathbf{Cat}$ and a 2-isomorphism $\theta \colon EF \Rightarrow F^\prime H$ as in the following diagram, the triple $(H,E,\theta)$ induces a symmetric monoidal (strong) double functor $\mathbb{H} \colon F\mathbb{C}\textnormal{sp} \to F'\mathbb{C}\textnormal{sp}$ as defined above.
+Given two finitely cocomplete categories $\mathsf{A}$ and $\mathsf{A}'$, two symmetric lax monoidal pseudofunctors $F \maps \mathsf{A} \to \mathbf{Cat}$ and $F' \maps \mathsf{A}' \to \mathbf{Cat}$, a finite colimit preserving functor $H \maps \mathsf{A} \to \mathsf{A}'$, a symmetric lax monoidal pseudofunctor $E \maps \mathbf{Cat} \to \mathbf{Cat}$ and a 2-isomorphism $\theta \maps EF \Rightarrow F^\prime H$ as in the following diagram, the triple $(H,E,\theta)$ induces a symmetric monoidal (strong) double functor $\mathbb{H} \maps F\mathbb{C}\textnormal{sp} \to F'\mathbb{C}\textnormal{sp}$ as defined above.
 \[
@@
 %\newline
-%Let $P = (s_1,t_1 \colon T_1 \to \mathbb{N}(S_1))$ and $Q = (s_2,t_2 \colon T_2 \to \mathbb{N}(S_2))$.
-We want to show that the functor $F \colon \textrm{Petri} \to \textrm{CMC}$ preserves pushouts of cospans of the form $$P \xleftarrow{} L(Y) \xrightarrow{} Q$$ meaning that $F(P+_{L(Y)} Q) \cong F(P) +_{F(L(Y))} F(Q)$.
-Here, $L \colon \textrm{Set} \to \textrm{Petri}$ is the left adjoint which sends a set $Y$ to the discrete Petri net with $Y$ as its set of species and no transitions.
+%Let $P = (s_1,t_1 \maps T_1 \to \mathbb{N}(S_1))$ and $Q = (s_2,t_2 \maps T_2 \to \mathbb{N}(S_2))$.
+We want to show that the functor $F \maps \textrm{Petri} \to \textrm{CMC}$ preserves pushouts of cospans of the form $$P \xleftarrow{} L(Y) \xrightarrow{} Q$$ meaning that $F(P+_{L(Y)} Q) \cong F(P) +_{F(L(Y))} F(Q)$.
+Here, $L \maps \textrm{Set} \to \textrm{Petri}$ is the left adjoint which sends a set $Y$ to the discrete Petri net with $Y$ as its set of species and no transitions.
 Thus no transitions are identified in the pushout $P+_{L(Y)} Q$, and so the set of transitions of $P+_{L(Y)} Q$ is given by $$\textrm{Trans}(P)+\textrm{Trans}(Q).$$ Thus the morphisms \emph{contributed from transitions} in both $F(P+_{L(Y)}Q)$ and $F(P)+_{F(L(Y)} F(Q)$ are the same.
@@
 
-{\chris Wait, why do you need to consider them as monoidal in the assumptions of the theorem?}
 \begin{thm}\label{SC}
-Given a category $\mathsf{X}$ with finite colimits and a category $\mathsf{A}$ with finite coproducts and a finite coproduct preserving functor $L \colon \mathsf{A} \to \mathsf{X}$ with $\mathsf{A}$ and $\mathsf{X}$ regarded as cocartesian monoidal categories, there exists a symmetric monoidal double category $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$ which has:
+Given a category $\mathsf{X}$ with finite colimits and a category $\mathsf{A}$ with finite coproducts and a finite coproduct preserving functor $L \maps \mathsf{A} \to \mathsf{X}$ with $\mathsf{A}$ and $\mathsf{X}$, there exists a symmetric monoidal double category $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$ which has:
 \begin{itemize}
@@
 \begin{thm}\label{Equiv}
-Suppose $\ca{A}$ is a finitely cocomplete category and $(F,\phi,\phi_0)\colon(\ca{A},+,0) \to (\bicat{Cat},\times,\mathbf{1})$ is a symmetric lax monoidal pseudofunctor, which factors through $\bicat{Rex}$ as an ordinary pseudofunctor.
-Then the symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$ of decorated cospans (\cref{thm:decoratedcospans}) is equivalent to the symmetric monoidal double category $\scsp{L_F}{\inta F}$ of structured cospans (\cref{SC}), where $L_F \colon \mathsf{A} \to \inta{F}$ is the left adjoint of the induced Grothendieck opfibration $\U_F\colon \inta{F} \to \mathsf{A}$.
+Suppose $\ca{A}$ is a finitely cocomplete category and $(F,\phi,\phi_0)\maps(\ca{A},+,0) \to (\bicat{Cat},\times,\mathbf{1})$ is a symmetric lax monoidal pseudofunctor that factors through $\bicat{Rex}$ as an ordinary pseudofunctor.
+Then the symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$ of decorated cospans given in \cref{thm:decoratedcospans} is equivalent to the symmetric monoidal double category $\scsp{L_F}{\inta F}$ of structured cospans given in \cref{SC}, where $L_F \maps \mathsf{A} \to \inta{F}$ is the left adjoint of the induced Grothendieck opfibration $\U_F\maps \inta{F} \to \mathsf{A}$.
 %by \cref{thm:Grothendieck},
@@
 The basics of fibration theory needed for our purposes are recalled in \cref{sec:fibrations}. 
-In \cite{MV}, the classic Grothendieck construction is generalized to the monoidal setting: lax monoidal structures on a pseudofunctor $F\colon\A\to\bicat{Cat}$ bijectively correspond to monoidal structures on the total category $\inta F$ such that the induced opfibration is a strict monoidal functor and $\otimes_{\inta F}$ preserves liftings, see \cite[Thm.
+In \cite{MV}, the classic Grothendieck construction is generalized to the monoidal setting: lax monoidal structures on a pseudofunctor $F\maps\A\to\bicat{Cat}$ bijectively correspond to monoidal structures on the total category $\inta F$ such that the induced opfibration is a strict monoidal functor and $\otimes_{\inta F}$ preserves liftings, see \cite[Thm.
 3.10]{MV}.
-If the monoidal category $\A$ is in fact cocartesian, there is a further correspondence of the two structures with an ordinary pseudofunctor $F\colon\A\to\bicat{MonCat}$ into the 2-category of monoidal categories, strong monoidal functors and monoidal natural transformations, summarized as
+If the monoidal category $\A$ is in fact cocartesian, there is a further correspondence of the two structures with an ordinary pseudofunctor $F\maps\A\to\bicat{MonCat}$ into the 2-category of monoidal categories, strong monoidal functors and monoidal natural transformations, summarized as
 \begin{gather}
-\textrm{lax monoidal pseudofunctors }F\colon(\A,+,0)\to(\bicat{Cat},\times,1) \notag\\
+\textrm{lax monoidal pseudofunctors }F\maps(\A,+,0)\to(\bicat{Cat},\times,1) \notag\\
 \Updownarrow \notag\\
-\textrm{monoidal opfibrations }U\colon(\X,\otimes,I)\to(\A,+,0) \label{monGroth}\\
+\textrm{monoidal opfibrations }U\maps(\X,\otimes,I)\to(\A,+,0) \label{monGroth}\\
 \Updownarrow \notag\\
-\textrm{pseudofunctors }F\colon\A\to\bicat{MonCat} \notag
+\textrm{pseudofunctors }F\maps\A\to\bicat{MonCat} \notag
 \end{gather}
@@
 \begin{gather}\label{eq:explicitstructure1}
-\otimes_a\colon F(a)\times F(a)\xrightarrow{\phi_{a,a}}F(a+a)\xrightarrow{F(\nabla)}F(a)\\
-I_x\colon\mathbf{1}\xrightarrow{\phi_0}F(0)\xrightarrow{F(!)}F(a)\nonumber
+\otimes_a\maps F(a)\times F(a)\xrightarrow{\phi_{a,a}}F(a+a)\xrightarrow{F(\nabla)}F(a)\\
+I_x\maps\mathbf{1}\xrightarrow{\phi_0}F(0)\xrightarrow{F(!)}F(a)\nonumber
 \end{gather}
@@
 4.8]{MV}.
-In that case, the monoidal opfibration clauses for $U\colon(\X,+,0)\to(\A,+,0)$ translate to the functor (strictly) preserving coproducts and the initial object, and bijectively correspond to pseudofunctors $F\colon\A\to\bicat{cocartCat}$ into the 2-category of cocartesian categories, functors that preserve coproducts and initial objects and natural transformations.
+In that case, the monoidal opfibration clauses for $U\maps(\X,+,0)\to(\A,+,0)$ translate to the functor (strictly) preserving coproducts and the initial object, and bijectively correspond to pseudofunctors $F\maps\A\to\Rex $ into the 2-category of esian categories, functors that preserve coproducts and initial objects and natural transformations.
 
@@
 \begin{lem}\label{lem:fibrewiselimits}
-Suppose $\ca{J}$ is a small category and $\U\colon\X\to\A$ is an opfibration. If the base $\A$ has $\ca{J}$-colimits,
+Suppose $\ca{J}$ is a small category and $\U\maps\X\to\A$ is an opfibration. If the base $\A$ has $\ca{J}$-colimits,
 the following are equivalent:
@@
 
-The first part formulates the existence of colimits \emph{locally} in each fibre, which can equivalently be expressed by the corresponding pseudofunctor $F\colon\A\to\bicat{Cat}$ landing on the sub-2-category $\bicat{Rex}$ of finitely cocomplete categories and functors that preserve colimits.
+The first part formulates the existence of colimits \emph{locally} in each fibre, which can equivalently be expressed by the corresponding pseudofunctor $F\maps\A\to\bicat{Cat}$ landing on the sub-2-category $\bicat{Rex}$ of finitely cocomplete categories and functors that preserve colimits.
 The second part formulates the existence of colimits \emph{globally} in the total category $\inta F$.
@@
 \begin{cor}\label{cor:fcocMonGroth}
- Suppose $\A$ is a finitely cocomplete category and $F\colon(\A,+,0)\to(\bicat{Cat},\times,1)$ is a lax monoidal pseudofunctor.
+ Suppose $\A$ is a finitely cocomplete category and $F\maps(\A,+,0)\to(\bicat{Cat},\times,1)$ is a lax monoidal pseudofunctor.
 If its corresponding pseudofunctor $\A\to\bicat{MonCat}$ via \cref{monGroth}
- factors through $\bicat{Rex}$, then the Grothendieck category $\inta F$ has all finite colimits and the induced opfibration $\U_F\colon\inta F\to\A$ preserves them. 
+ factors through $\bicat{Rex}$, then the Grothendieck category $\inta F$ has all finite colimits and the induced opfibration $\U_F\maps\inta F\to\A$ preserves them. 
 \end{cor}
@@
 \begin{prop}\cite[Prop.\ 4.4]{Gray} \label{prop:opfibtolari}
-  Let $\U \colon\X \to \A$ be an opfibration. Then
+  Let $\U \maps\X \to \A$ be an opfibration. Then
   $\U$ is a right adjoint `left inverse', a.k.a the unit is the identity, if (and only if) its fibers have
@@
 \begin{proof}\emph{(Sketch)}
- The left adjoint $L\colon\A\to\X$ maps an object $a$ to the initial object in its fibre $\X_a$, denoted by $\bot_a$.
+ The left adjoint $L\maps\A\to\X$ maps an object $a$ to the initial object in its fibre $\X_a$, denoted by $\bot_a$.
 By construction, $U(L(a))=U(\bot_a)=a$.
-On morphisms $f\colon a\to a'$, $L(f)$ is defined by
+On morphisms $f\maps a\to a'$, $L(f)$ is defined by
  \begin{equation}\label{eq:Lonarrows}
-  \bot_a\xrightarrow{\Cocart(f,\bot_a)}f_!(\bot_a)\xrightarrow{\;\stackrel{\chi_a}{\cong}\;}\bot_{a'}
+  \bot_a\xrightarrow{\Rex(f,\bot_a)}f_!(\bot_a)\xrightarrow{\;\stackrel{\chi_a}{\cong}\;}\bot_{a'}
  \end{equation}
@@
 %Christina: hiding strict preservence under the rug
-In this case, $\bot_a$ is precisely the cocartesian lifting of $0_\X$ along the unique map $u_a\colon0_\A\to a$ in the base category:
+In this case, $\bot_a$ is precisely the cocartesian lifting of $0_\X$ along the unique map $u_a\maps0_\A\to a$ in the base category:
 \begin{displaymath}
@@
 \end{displaymath}
-Moreover, if $U=U_F$ for a pseudofunctor $F\colon\A\to\bicat{Cat}$ under \cref{thm:Grothendieck}, the reindexing functors $(u_a)_!$ of the opfibration are precisely $F(u_a)$, therefore $\bot_a=(a,F(u_a)(0_\X))$ in the Grothendieck category, for $u_a$ the unique map from $0_\A$ as above.
-
-Finally, if that pseudofunctor is lax monoidal $(F,\phi,\phi_0)\colon(\A,+,0)\to(\bicat{Cat},\times,\mathbf{1})$ to begin with, the monoidal Grothendieck construction in the cocartesian case discussed earlier \cref{eq:explicitstructure1} expresses $\bot_a$ as the image of the composite
+Moreover, if $U=U_F$ for a pseudofunctor $F\maps\A\to\bicat{Cat}$ under \cref{thm:Grothendieck}, the reindexing functors $(u_a)_!$ of the opfibration are precisely $F(u_a)$, therefore $\bot_a=(a,F(u_a)(0_\X))$ in the Grothendieck category, for $u_a$ the unique map from $0_\A$ as above.
+
+Finally, if that pseudofunctor is lax monoidal $(F,\phi,\phi_0)\maps(\A,+,0)\to(\bicat{Cat},\times,\mathbf{1})$ to begin with, the monoidal Grothendieck construction in the cocartesian case discussed earlier \cref{eq:explicitstructure1} expresses $\bot_a$ as the image of the composite
 \begin{equation}\label{eq:initialinfibre}
@@
 
-\begin{prop}\label{prop:CV}\cite[Prop. \ 3.3]{CV}
-Suppose $\U\colon\X\to\A$ is a right adjoint `left inverse'. If $\X$ and $\A$ have chosen pushouts and initial objects and $\U$ strictly preserves them, then $\U$ is an opfibration.
-\end{prop}
+\begin{lem}\label{prop:CV}\cite[Prop. \ 3.3]{CV}
+Suppose $\U\maps\X\to\A$ is a right adjoint `left inverse'. If $\X$ and $\A$ have chosen pushouts and initial objects and $\U$ strictly preserves them, then $\U$ is an opfibration.
+\end{lem}
 %Christina: do we need this direction after all? Discuss.
 %\begin{thm}\label{thm:mainthmDX}\cite{CV}
-%Suppose that $\X$ and $\A$ have chosen pushouts and initial objects, and a functor $\U\colon\X\to\A$ strictly preserves them.
+%Suppose that $\X$ and $\A$ have chosen pushouts and initial objects, and a functor $\U\maps\X\to\A$ strictly preserves them.
 Then $\U$ is a right %adjoint left inverse if and only if $\U$ is an opfibration.
@@
 \begin{proof}[Proof of \cref{Equiv}]
-Recall that the double category of decorated cospans $\dcsp{F}$ has objects and vertical 1-morphisms those of $\A$, horizontal 1-cells $a\tickar b$ are cospans $\cspn{a}{m}{b}{}{}$ in $\A$ along with $x\in F(m)$, and 2-morphisms are cospan maps $k\colon m\to m'$ together with a morphism $(Fk)(x)\to x'$, see \cref{eq:FCsp2morph}.
-
-By \cref{cor:fcocMonGroth}, when $F$ as an ordinary pseudofunctor factors through $\bicat{Rex}$, the (monoidal) Gro\-the\-ndieck construction gives rise to a finitely cocomplete $\inta F$ such that the corresponding opfibration $U_F\colon(\inta{F},+,0)\to(\A,+,0)$ preserves all finite colimits.
+Recall that the double category of decorated cospans $\dcsp{F}$ has objects and vertical 1-morphisms those of $\A$, horizontal 1-cells $a\tickar b$ are cospans $\cspn{a}{m}{b}{}{}$ in $\A$ along with $x\in F(m)$, and 2-morphisms are cospan maps $k\maps m\to m'$ together with a morphism $(Fk)(x)\to x'$, see \cref{eq:FCsp2morph}.
+
+By \cref{cor:fcocMonGroth}, when $F$ as an ordinary pseudofunctor factors through $\bicat{Rex}$, the (monoidal) Gro\-the\-ndieck construction gives rise to a finitely cocomplete $\inta F$ such that the corresponding opfibration $U_F\maps(\inta{F},+,0)\to(\A,+,0)$ preserves all finite colimits.
 %Christina: maybe the cocartesian structures are redundant to write here, since U_F really preserves all finite colimits anyways.
@@
 Change Gray accordingly perhaps?
-to construct a left adjoint $L_F\colon\A\to\inta F$ which is also a right inverse, namely $U_FL_F=\mathrm{id}_\A$.
+to construct a left adjoint $L_F\maps\A\to\inta F$ which is also a right inverse, namely $U_FL_F=\mathrm{id}_\A$.
 Explicitly, this left adjoint is given by $L(a)=(a,\bot_a)$, picking the initial object in the finitely cocomplete fibre also expressed as $F(u_a)\circ\phi_0(*)$ in \cref{eq:initialinfibre}.
@@
 \begin{displaymath}
- F\colon\X\to\bicat{Cat}\quad\mapsto\quad\begin{tikzcd}[baseline=.3]\inta F\ar[d,"U_F"'] \\ \X \end{tikzcd}\quad\mapsto\quad\begin{tikzcd}\X\ar[r,bend left,pos=.55,"L_F"]\ar[r,phantom,"\bot"description] & \inta F\ar[l,bend left,pos=.45,"U_F"]\end{tikzcd}
+ F\maps\X\to\bicat{Cat}\quad\mapsto\quad\begin{tikzcd}[baseline=.3]\inta F\ar[d,"U_F"'] \\ \X \end{tikzcd}\quad\mapsto\quad\begin{tikzcd}\X\ar[r,bend left,pos=.55,"L_F"]\ar[r,phantom,"\bot"description] & \inta F\ar[l,bend left,pos=.45,"U_F"]\end{tikzcd}
 \end{displaymath}
@@
 \begin{equation}\label{eq:scsphor1cell}
- (a,\bot_a)\xrightarrow{\scalebox{0.7}{$\begin{cases}i\colon a\to m &\textrm{in }\A \\!\colon F(i)(\bot_a)\to x &\textrm{in }F(m)\end{cases}$}}(m,x)\xleftarrow{\scalebox{0.7}{$\begin{cases}o\colon b\to m &\textrm{in }\A \\!\colon F(o)(\bot_b)\to x &\textrm{in }F(m)\end{cases}$}}(b,\bot_b)
+ (a,\bot_a)\xrightarrow{\scalebox{0.7}{$\begin{cases}i\maps a\to m &\textrm{in }\A \\!\maps F(i)(\bot_a)\to x &\textrm{in }F(m)\end{cases}$}}(m,x)\xleftarrow{\scalebox{0.7}{$\begin{cases}o\maps b\to m &\textrm{in }\A \\!\maps F(o)(\bot_b)\to x &\textrm{in }F(m)\end{cases}$}}(b,\bot_b)
 \end{equation}
@@
  \begin{tikzcd}[sep=1.5in,ampersand replacement=\&]
- (a,\bot_a)\ar[r,"{\begin{cases}i\colon a\to m &\textrm{in }\A \\!\colon F(i)(\bot_a)\to x &\textrm{in }F(m)\end{cases}}"]\ar[d,"{\begin{cases}f\colon a\to a' &\textrm{in }\A \\\chi_a\colon F(f)(\bot_a)\cong \bot_{a'} &\textrm{in }F(a')\end{cases}}"description] \& (m,x) \ar[d,"{\begin{cases}k\colon m\to m' &\textrm{in }\A \\ \iota\colon F(k)(x)\to x' &\textrm{in }F(m')\end{cases}}"description] \& (b,\bot_b)\ar[l,"{\begin{cases}o\colon b\to m &\textrm{in }\A \\!\colon F(o)(\bot_b)\to x &\textrm{in }F(m)\end{cases}}"']\ar[d,"{\begin{cases}g\colon b\to b' &\textrm{in }\A \\\chi_b\colon F(g)(\bot_b)\cong \bot_{b'} &\textrm{in }F(b')\end{cases}}"description] \\
- (a',\bot_{a'})\ar[r,"{\begin{cases}i'\colon a'\to m' &\textrm{in }\A \\!\colon F(i')(\bot_{a'})\to x' &\textrm{in }F(m')\end{cases}}"'] \& (m',x') \& (b',\bot_{b'})\ar[l,"{\begin{cases}o'\colon b'\to m' &\textrm{in }\A \\!\colon F(o')(\bot_{b'})\to x' &\textrm{in }F(m')\end{cases}}"]
+ (a,\bot_a)\ar[r,"{\begin{cases}i\maps a\to m &\textrm{in }\A \\!\maps F(i)(\bot_a)\to x &\textrm{in }F(m)\end{cases}}"]\ar[d,"{\begin{cases}f\maps a\to a' &\textrm{in }\A \\\chi_a\maps F(f)(\bot_a)\cong \bot_{a'} &\textrm{in }F(a')\end{cases}}"description] \& (m,x) \ar[d,"{\begin{cases}k\maps m\to m' &\textrm{in }\A \\ \iota\maps F(k)(x)\to x' &\textrm{in }F(m')\end{cases}}"description] \& (b,\bot_b)\ar[l,"{\begin{cases}o\maps b\to m &\textrm{in }\A \\!\maps F(o)(\bot_b)\to x &\textrm{in }F(m)\end{cases}}"']\ar[d,"{\begin{cases}g\maps b\to b' &\textrm{in }\A \\\chi_b\maps F(g)(\bot_b)\cong \bot_{b'} &\textrm{in }F(b')\end{cases}}"description] \\
+ (a',\bot_{a'})\ar[r,"{\begin{cases}i'\maps a'\to m' &\textrm{in }\A \\!\maps F(i')(\bot_{a'})\to x' &\textrm{in }F(m')\end{cases}}"'] \& (m',x') \& (b',\bot_{b'})\ar[l,"{\begin{cases}o'\maps b'\to m' &\textrm{in }\A \\!\maps F(o')(\bot_{b'})\to x' &\textrm{in }F(m')\end{cases}}"]
  \end{tikzcd}
@@
 \begin{displaymath}
-\mathbb{E}\colon\scsp{L_F}{\inta F} \longrightarrow\dcsp{F}
+\mathbb{E}\maps\scsp{L_F}{\inta F} \longrightarrow\dcsp{F}
 \end{displaymath}
@@
 \end{displaymath}
- in $\A$ along with the map $\iota\colon Fk(x)\to x'$ in $F(m')$, namely a decorated cospan 2-morphism as per \cref{eq:FCsp2morph}.
+ in $\A$ along with the map $\iota\maps Fk(x)\to x'$ in $F(m')$, namely a decorated cospan 2-morphism as per \cref{eq:FCsp2morph}.
 Once again, this is a bijective correspondence since, as discussed above, the commutativity \cref{eq:Grothcommutativity} holds automatically by initiality of the domain.
@@
 \]
-where $R\colon \mathsf{X} \to \mathsf{A}$ is the right adjoint to the functor $L \colon \mathsf{A} \to \mathsf{X}$ and $\eta \colon 1_{\mathsf{A}} \to RL$ is the unit of the adjunction $L \dashv R$ which is an isomorphism since $L$ is fully faithful.
-\textbf{Hopefully...actually, it's a `lari'!} Similarly, the image of a 2-morphism $\alpha \colon M \to N$ in $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$:
+where $R\maps \mathsf{X} \to \mathsf{A}$ is the right adjoint to the functor $L \maps \mathsf{A} \to \mathsf{X}$ and $\eta \maps 1_{\mathsf{A}} \to RL$ is the unit of the adjunction $L \dashv R$ which is an isomorphism since $L$ is fully faithful.
+\textbf{Hopefully...actually, it's a `lari'!} Similarly, the image of a 2-morphism $\alpha \maps M \to N$ in $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$:
 \[
@@
 \]
-is given by the 2-morphism $\mathbb{E}_1(\alpha) \colon \mathbb{E}_1(M) \to \mathbb{E}_1(N)$ in $\mathbb{F}\textnormal{Cospan}(\mathsf{A})$ given by:
+is given by the 2-morphism $\mathbb{E}_1(\alpha) \maps \mathbb{E}_1(M) \to \mathbb{E}_1(N)$ in $\mathbb{F}\textnormal{Cospan}(\mathsf{A})$ given by:
 \[
@@
 \]
-together with a morphism $\iota \colon F(R(\alpha))(x) \to x^\prime$ in $F(R(x^\prime)) \subseteq \mathrm{X}$ which comes from the Grothendieck construction of the pseudofunctor $F \colon \mathsf{A} \to \mathbf{Cat}$.
+together with a morphism $\iota \maps F(R(\alpha))(x) \to x^\prime$ in $F(R(x^\prime)) \subseteq \mathrm{X}$ which comes from the Grothendieck construction of the pseudofunctor $F \maps \mathsf{A} \to \mathbf{Cat}$.
 That $\mathbb{E}_0$ is a functor is clear.
@@
 \]
-together with a morphism $\iota_{M' M} \colon F(R(\alpha' \alpha))(x) \to x''$ in $F(R(x''))$. On the other hand, the individual images $\mathbb{E}_1(M)$ and $\mathbb{E}_1(M')$ are given by:
+together with a morphism $\iota_{M' M} \maps F(R(\alpha' \alpha))(x) \to x''$ in $F(R(x''))$. On the other hand, the individual images $\mathbb{E}_1(M)$ and $\mathbb{E}_1(M')$ are given by:
 \[
@@
 \]
-together with morphisms $\iota_M \colon F(R(\alpha))(x) \to x'$ in $F(R(x'))$ and $\iota_{M'} \colon F(R(\alpha')(x') \to x''$ in $F(R(x''))$, respectively.
+together with morphisms $\iota_M \maps F(R(\alpha))(x) \to x'$ in $F(R(x'))$ and $\iota_{M'} \maps F(R(\alpha')(x') \to x''$ in $F(R(x''))$, respectively.
 The vertical composite $\mathbb{E}_1(M')\mathbb{E}_1(M)$ of the above two 2-morphisms is given by $\mathbb{E}_1(M'M)$ as $R$ is a functor and $\iota_{M'M}=\iota_{M'} \iota_M$.
@@
 \]
-$$\iota \colon F({(R(e)\eta_c)}^{-1})(x) \to x$$
-where $e \colon L(c) \to x$ is given by the map from the trivial decoration on $c$ to $x \in F(c)$.
+$$\iota \maps F({(R(e)\eta_c)}^{-1})(x) \to x$$
+where $e \maps L(c) \to x$ is given by the map from the trivial decoration on $c$ to $x \in F(c)$.
 %The object and arrow components $\mathbb{E}_0$ and $\mathbb{E}_1$ satisfy the equations $S \mathbb{E}_1 = \mathbb{E}_0 S$ and $T \mathbb{E}_1 = \mathbb{E}_0 T$.
 
-To show that the double functor $\mathbb{E}$ is fully faithful, we need to show that the map  $$\mathbb{E}_1 \colon _f { _L \mathbb{C}\textnormal{sp}(\mathsf{X})}_g(M,N) \to {_{\mathbb{E}(f)} {F\mathbb{C}\textnormal{sp}}_{\mathbb{E}(g)}}(\mathbb{E}(M),\mathbb{E}(N))$$ is bijective for arbitrary vertical 1-morphisms $f$ and $g$ and horizontal 1-cells $M$ and $N$ of $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$.
+To show that the double functor $\mathbb{E}$ is fully faithful, we need to show that the map  $$\mathbb{E}_1 \maps _f { _L \mathbb{C}\textnormal{sp}(\mathsf{X})}_g(M,N) \to {_{\mathbb{E}(f)} {F\mathbb{C}\textnormal{sp}}_{\mathbb{E}(g)}}(\mathbb{E}(M),\mathbb{E}(N))$$ is bijective for arbitrary vertical 1-morphisms $f$ and $g$ and horizontal 1-cells $M$ and $N$ of $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$.
 Consider a 2-morphism in $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$ with horizontal source and target $M$ and $N$, respectively and vertical source and target $f$ and $g$, respectively:
@@
 \]
-together with a morphism $\iota \colon F(R(\alpha))(x) \to x^\prime$ of $F(R(x^\prime))$.
+together with a morphism $\iota \maps F(R(\alpha))(x) \to x^\prime$ of $F(R(x^\prime))$.
 Thus the set $$_{\mathbb{E}(f)} {F\mathbb{C}\textnormal{sp}}_{\mathbb{E}(g)}(\mathbb{E}(M),\mathbb{E}(N))$$ consists of 4-tuples $$(f,R(\alpha),g,\iota)$$ rendering the above diagram commutative and where $f,g$ and $R(\alpha)$ are morphisms of $\mathsf{A}$ and $\iota$ is a morphism in $F(R(x'))$.
-The morphisms $R(\alpha) \colon R(x) \to R(x^\prime)$ and $\iota \colon F(R(\alpha))(x) \to x^\prime$ together determine the morphism $\alpha \colon x \to x^\prime$ in $\mathrm{X}$ and conversely; given two objects $x=(c,x \in F(c))$ and $x^\prime=(c^\prime,x^\prime \in F(c^\prime))$ of $\mathsf{X}=\inta{F}$, a morphism from $\alpha \colon x \to x^\prime$ is a pair $$(h \colon c \to c^\prime, \iota \colon F(h)(x) \to x^\prime)$$ where $h \colon c \to c^\prime$ is given by $R(\alpha) \colon R(x) \to R(x^\prime)$.
+The morphisms $R(\alpha) \maps R(x) \to R(x^\prime)$ and $\iota \maps F(R(\alpha))(x) \to x^\prime$ together determine the morphism $\alpha \maps x \to x^\prime$ in $\mathrm{X}$ and conversely; given two objects $x=(c,x \in F(c))$ and $x^\prime=(c^\prime,x^\prime \in F(c^\prime))$ of $\mathsf{X}=\inta{F}$, a morphism from $\alpha \maps x \to x^\prime$ is a pair $$(h \maps c \to c^\prime, \iota \maps F(h)(x) \to x^\prime)$$ where $h \maps c \to c^\prime$ is given by $R(\alpha) \maps R(x) \to R(x^\prime)$.
 This shows that $\mathbb{E}$ is fully faithful.
@@
 \]
-Then we can obtain the natural isomorphism $\mathbb{E}_c \colon \hat{U}_{\mathbb{E}(c)} \xrightarrow{\sim} \mathbb{E}(U_c)$ as the 2-morphism
+Then we can obtain the natural isomorphism $\mathbb{E}_c \maps \hat{U}_{\mathbb{E}(c)} \xrightarrow{\sim} \mathbb{E}(U_c)$ as the 2-morphism
 \[
@@
 \]
-$$\iota \colon F(\eta_c)(!_c) \xrightarrow{!} !_{R(L(c))}$$
+$$\iota \maps F(\eta_c)(!_c) \xrightarrow{!} !_{R(L(c))}$$
 of $F\mathbb{C}\textnormal{sp}$.
@@
 \]
-$$\hat{x} \colon 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{x \times x^\prime} F(R(x)) \times F(R(x^\prime)) \xrightarrow{\phi_{R(x),R(x^\prime)}} F(R(x)+R(x^\prime)) \xrightarrow{F(j_{R(x),R(x^\prime)})} F(R(x)+_{c_2}R(x^\prime))$$where $\psi$ denotes each natural map into the coproduct and $j$ denotes the natural map from the coproduct to the pushout.
+$$\hat{x} \maps 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{x \times x^\prime} F(R(x)) \times F(R(x^\prime)) \xrightarrow{\phi_{R(x),R(x^\prime)}} F(R(x)+R(x^\prime)) \xrightarrow{F(j_{R(x),R(x^\prime)})} F(R(x)+_{c_2}R(x^\prime))$$where $\psi$ denotes each natural map into the coproduct and $j$ denotes the natural map from the coproduct to the pushout.
 On the other hand, $M \odot N$ is given by
@@
 \]
-and so $\mathbb{E}_{M,N} \colon \mathbb{E}(M) \odot \mathbb{E}(N) \xrightarrow{\sim} \mathbb{E}(M \odot N)$ is given by the 2-morphism:
+and so $\mathbb{E}_{M,N} \maps \mathbb{E}(M) \odot \mathbb{E}(N) \xrightarrow{\sim} \mathbb{E}(M \odot N)$ is given by the 2-morphism:
 \[
@@
 together with a morphism of decorations which is obtained as follows.
-First, as $R \colon \mathsf{X} \to \mathsf{A}$ preserves finite colimits, we have an isomorphism $$\kappa \colon R(x) +_{R(L(c_2))} R(x^\prime) \to R(x+_{L(c_2)}x^\prime).$$ Also, since the left adjoint $L \colon \mathsf{A} \to \mathsf{X}$ is fully faithful, the unit of the adjunction $L \dashv R$ at the object $c_2$ gives an isomorphism $\eta_{c_2} \colon c_2 \to R(L(c_2))$ which results in an isomorphism $$j_{\eta_{c_2}} \colon R(x) +_{c_2} R(x^\prime) \to R(x) +_{R(L(c_2))} R(x^\prime).$$ Composing these two results in an isomorphism $$\sigma \coloneqq \kappa j_{\eta_{c_2}} \colon R(x) +_{c_2} R(x^\prime) \to R(x+_{L(c_2)}x^\prime).$$
-Next, to see that the above diagram commutes, it suffices to show that for the object $c_1 \in \mathrm{A}$, $$R(J)R(\zeta)R(i)\eta_{c_1}(c_1) = R(J \zeta i)\eta_{c_1}(c_1)  \stackrel{!}{=} \sigma j \psi R(i)\eta_{c_1}(c_1) = \kappa j_{\eta_{c_2}} \psi R(i) \eta_{c_1}(c_1).$$ This follows as $R(i) \eta_{c_1} \colon c_1 \to R(x)$ and the following diagram commutes:
+First, as $R \maps \mathsf{X} \to \mathsf{A}$ preserves finite colimits, we have an isomorphism $$\kappa \maps R(x) +_{R(L(c_2))} R(x^\prime) \to R(x+_{L(c_2)}x^\prime).$$ Also, since the left adjoint $L \maps \mathsf{A} \to \mathsf{X}$ is fully faithful, the unit of the adjunction $L \dashv R$ at the object $c_2$ gives an isomorphism $\eta_{c_2} \maps c_2 \to R(L(c_2))$ which results in an isomorphism $$j_{\eta_{c_2}} \maps R(x) +_{c_2} R(x^\prime) \to R(x) +_{R(L(c_2))} R(x^\prime).$$ Composing these two results in an isomorphism $$\sigma \mapseqq \kappa j_{\eta_{c_2}} \maps R(x) +_{c_2} R(x^\prime) \to R(x+_{L(c_2)}x^\prime).$$
+Next, to see that the above diagram commutes, it suffices to show that for the object $c_1 \in \mathrm{A}$, $$R(J)R(\zeta)R(i)\eta_{c_1}(c_1) = R(J \zeta i)\eta_{c_1}(c_1)  \stackrel{!}{=} \sigma j \psi R(i)\eta_{c_1}(c_1) = \kappa j_{\eta_{c_2}} \psi R(i) \eta_{c_1}(c_1).$$ This follows as $R(i) \eta_{c_1} \maps c_1 \to R(x)$ and the following diagram commutes:
 \[
@@
 \]
-Lastly, this map of cospans comes with an isomorphism $$\iota \colon F(\sigma)(d_{\mathbb{E}(M) \odot \mathbb{E}(N)}) \to d_{\mathbb{E}(M \odot N)}$$ in $F(R(x+_{L(c_2)}x^\prime))$.
+Lastly, this map of cospans comes with an isomorphism $$\iota \maps F(\sigma)(d_{\mathbb{E}(M) \odot \mathbb{E}(N)}) \to d_{\mathbb{E}(M \odot N)}$$ in $F(R(x+_{L(c_2)}x^\prime))$.
 This shows that $\mathbb{E}$ is strong, and so
@@
 Based on the above description of its mapping, it follows that the strong double functor $\mathbb{E}=(\mathbb{E}_0,\mathbb{E}_1)$ is full, faithful and essentially surjective on objects as per \cref{def:fullfaithful,def:essentiallysurj}.
-Therefore $\mathbb{E} \colon \scsp{L_F}{\inta F} \to \dcsp{F}$ is a double equivalence, by \cref{ShulDubEquiv}.
+Therefore $\mathbb{E} \maps \scsp{L_F}{\inta F} \to \dcsp{F}$ is a double equivalence, by \cref{ShulDubEquiv}.
 {\chris In fact, Christina and Kenny believe it is an isomorphism of double categories! Bijective on all levels of objects and morphisms...should we say?}
@@
 
-Next, we show that if both double categories $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$ and $F\mathbb{C}\textnormal{sp}$ are symmetric monoidal, as they are if both $\mathsf{A}$ and $\mathsf{X}$ have finite colimits, then this equivalence of double categories $\mathbb{E} \colon _L \mathbb{C}\textnormal{sp}(\mathsf{X}) \to F\mathbb{C}\textnormal{sp}$ will be symmetric monoidal.
-First, note that we have an isomorphism $\epsilon \colon 1_{F\mathbb{C}\textnormal{sp}} \to \mathbb{E}(1_{_L \mathbb{C}\textnormal{sp}(\mathsf{X})})$ and natural isomorphisms $\mu_{c_1,c_2} \colon \mathbb{E}(c_1) \otimes \mathbb{E}(c_2) \to \mathbb{E}(c_1 \otimes c_2)$ for every pair of objects $c_1,c_2 \in {_L \mathbb{C} \textnormal{sp}(\mathsf{X})}$ both of which are given by identities since both double categories $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$ and $F\mathbb{C}\textnormal{sp}$ have $\mathsf{A}$ as their category of objects and $\mathbb{E}_0=\id_{\mathsf{A}}$.
+Next, we show that if both double categories $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$ and $F\mathbb{C}\textnormal{sp}$ are symmetric monoidal, as they are if both $\mathsf{A}$ and $\mathsf{X}$ have finite colimits, then this equivalence of double categories $\mathbb{E} \maps _L \mathbb{C}\textnormal{sp}(\mathsf{X}) \to F\mathbb{C}\textnormal{sp}$ will be symmetric monoidal.
+First, note that we have an isomorphism $\epsilon \maps 1_{F\mathbb{C}\textnormal{sp}} \to \mathbb{E}(1_{_L \mathbb{C}\textnormal{sp}(\mathsf{X})})$ and natural isomorphisms $\mu_{c_1,c_2} \maps \mathbb{E}(c_1) \otimes \mathbb{E}(c_2) \to \mathbb{E}(c_1 \otimes c_2)$ for every pair of objects $c_1,c_2 \in {_L \mathbb{C} \textnormal{sp}(\mathsf{X})}$ both of which are given by identities since both double categories $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$ and $F\mathbb{C}\textnormal{sp}$ have $\mathsf{A}$ as their category of objects and $\mathbb{E}_0=\id_{\mathsf{A}}$.
 The diagrams utilizing these maps that are required to commute do so trivially.
 
-For the arrow component $\mathbb{E}_1$, we have an isomorphism $\delta \colon U_{1_{F\mathbb{C}\textnormal{sp}}} \to \mathbb{E}(U_{1_{_L \mathbb{C}\textnormal{sp}(\mathsf{X})}})$ where the horizontal 1-cell $U_{1_{F\mathbb{C}\textnormal{sp}}}$ is given by:
+For the arrow component $\mathbb{E}_1$, we have an isomorphism $\delta \maps U_{1_{F\mathbb{C}\textnormal{sp}}} \to \mathbb{E}(U_{1_{_L \mathbb{C}\textnormal{sp}(\mathsf{X})}})$ where the horizontal 1-cell $U_{1_{F\mathbb{C}\textnormal{sp}}}$ is given by:
 \[
@@
 \]
-where $!_{1_{\mathsf{A}}} = \phi \colon 1 \to F(1_\mathsf{A})$ is the trivial decoration which comes from the structure of the symmetric lax monoidal pseudofunctor $F \colon \mathsf{A} \to \mathbf{Cat}$.
+where $!_{1_{\mathsf{A}}} = \phi \maps 1 \to F(1_\mathsf{A})$ is the trivial decoration which comes from the structure of the symmetric lax monoidal pseudofunctor $F \maps \mathsf{A} \to \mathbf{Cat}$.
 The horizontal 1-cell $U_{1_{_L \mathbb{C}\textnormal{sp}(\mathsf{X})}}$ is given by:
@@
 \]
-where here we make use of the fact that the left adjoint $L \colon (\mathsf{A},+,1_\mathsf{A}) \to (\mathsf{X},+,1_\mathsf{X})$ preserves all colimits and thus $L(1_\mathsf{A}) \cong 1_\mathsf{X}$.
+where here we make use of the fact that the left adjoint $L \maps (\mathsf{A},+,1_\mathsf{A}) \to (\mathsf{X},+,1_\mathsf{X})$ preserves all colimits and thus $L(1_\mathsf{A}) \cong 1_\mathsf{X}$.
 The horizontal 1-cell $\mathbb{E}(U_{1_{_L \mathbb{C} \textnormal{sp}(\mathsf{X})}})$ is then given by the pair:
@@
 \]
-$$\iota_{{\eta_{1_\mathsf{A}}}} \colon F({\eta_{1_\mathsf{A}}})(!_{1_\mathsf{A}})) \to !_{R(L(1_\mathsf{A}))}$$
+$$\iota_{{\eta_{1_\mathsf{A}}}} \maps F({\eta_{1_\mathsf{A}}})(!_{1_\mathsf{A}})) \to !_{R(L(1_\mathsf{A}))}$$
 of $F\mathbb{C}\textnormal{sp}$. This is just the natural isomorphism $\mathbb{E}_{1_\mathsf{A}}$ from earlier.
@@
 \]
-where $$d_{\mathbb{E}(M) \otimes \mathbb{E}(N)} \colon 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{x \times x^\prime} F(R(x)) \times F(R(x^\prime)) \xrightarrow{\phi_{R(x),R(x^\prime)}} F(R(x)+R(x^\prime)).$$ On the other hand, $M \otimes N$ is given by
+where $$d_{\mathbb{E}(M) \otimes \mathbb{E}(N)} \maps 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{x \times x^\prime} F(R(x)) \times F(R(x^\prime)) \xrightarrow{\phi_{R(x),R(x^\prime)}} F(R(x)+R(x^\prime)).$$ On the other hand, $M \otimes N$ is given by
 \[
@@
 \]
-We then have a 2-isomorphism $\mu_{M,N} \colon E(M) \otimes E(N) \xrightarrow{\sim} E(M \otimes N)$ in $F\mathbb{C}\textnormal{sp}$ given by:
+We then have a 2-isomorphism $\mu_{M,N} \maps E(M) \otimes E(N) \xrightarrow{\sim} E(M \otimes N)$ in $F\mathbb{C}\textnormal{sp}$ given by:
 \[
@@
 \node (D') at (6.55,-1) {$d_{\mathbb{E}(M \otimes N)} \in F(R(x+x^\prime))$};
-\node (E) at (2,-1.5) {$\iota_\mu \colon F(\kappa)(d_{\mathbb{E}(M) \odot \mathbb{E}(N)}) \to d_{\mathbb{E}(M \odot N)}$};
+\node (E) at (2,-1.5) {$\iota_\mu \maps F(\kappa)(d_{\mathbb{E}(M) \odot \mathbb{E}(N)}) \to d_{\mathbb{E}(M \odot N)}$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-where $\kappa$ is the isomorphism which comes from $R \colon \mathsf{X} \to \mathsf{A}$ preserving finite colimits.
+where $\kappa$ is the isomorphism which comes from $R \maps \mathsf{X} \to \mathsf{A}$ preserving finite colimits.
 
@@
 where $x_{!+1}$ is the decoration $x_1$ on the object $R(L(1_\mathsf{A})+x_1) \in \mathsf{A}$.
-The above square commutes because $$F(\lambda_\mathsf{A})(!_{1_\mathsf{A}}+x_1) = F(R(\lambda_\mathsf{X})(\mu_{L(1_\mathsf{A}),x_1})(\eta_{1_\mathsf{A}}+1))(!_{1_\mathsf{A}}+x_1)$$ as the corresponding left unitality square for the finite colimit preserving functor $R \colon (\mathsf{X},1_\mathsf{X},+) \to (\mathsf{A},1_\mathsf{A},+)$ commutes.
+The above square commutes because $$F(\lambda_\mathsf{A})(!_{1_\mathsf{A}}+x_1) = F(R(\lambda_\mathsf{X})(\mu_{L(1_\mathsf{A}),x_1})(\eta_{1_\mathsf{A}}+1))(!_{1_\mathsf{A}}+x_1)$$ as the corresponding left unitality square for the finite colimit preserving functor $R \maps (\mathsf{X},1_\mathsf{X},+) \to (\mathsf{A},1_\mathsf{A},+)$ commutes.
 The right unitality square is similar.
@@
 	\]
-Here we have omitted the natural isomorphisms $\phi_{c_i,c_j} \colon L(c_i) + L(c_j) \to L(c_i + c_j)$ on the inward pointing morphisms which make up the legs of each cospan due to limited space.
+Here we have omitted the natural isomorphisms $\phi_{c_i,c_j} \maps L(c_i) + L(c_j) \to L(c_i + c_j)$ on the inward pointing morphisms which make up the legs of each cospan due to limited space.
 The corresponding maps of decorations amount to the following commutative diagram in $F(R(x_1+(x_2+x_3)))$:
@@
 \]
-The above square commutes because $$F((\kappa)(1+\kappa)(a_\mathsf{A}))((x_1+x_2)+x_3) = F((R(a_\mathsf{X}))(\kappa)(\kappa+1))((x_1+x_2)+x_3)$$ as the corresponding associator hexagon for the finite colimit preserving functor $R \colon (\mathsf{X},1_\mathsf{X},+) \to (\mathsf{A},1_\mathsf{A},+)$ commutes.
+The above square commutes because $$F((\kappa)(1+\kappa)(a_\mathsf{A}))((x_1+x_2)+x_3) = F((R(a_\mathsf{X}))(\kappa)(\kappa+1))((x_1+x_2)+x_3)$$ as the corresponding associator hexagon for the finite colimit preserving functor $R \maps (\mathsf{X},1_\mathsf{X},+) \to (\mathsf{A},1_\mathsf{A},+)$ commutes.
 Lastly, the braiding square:
@@
 \]
-The above square commutes because $$F((\kappa)(\beta_\mathsf{A}))(x_1+x_2) = F((R(\beta_\mathsf{X}))(\kappa))(x_1+x_2)$$ as the corresponding braiding square for the finite colimit preserving functor $R \colon (\mathsf{X},1_\mathsf{X},+) \to (\mathsf{A},1_\mathsf{A},+)$ commutes.
-Thus the double functor $\mathbb{E} \colon _L\mathbb{C}\textnormal{sp}(\mathsf{X}) \to F\mathbb{C}\textnormal{sp}$ is symmetric monoidal.
+The above square commutes because $$F((\kappa)(\beta_\mathsf{A}))(x_1+x_2) = F((R(\beta_\mathsf{X}))(\kappa))(x_1+x_2)$$ as the corresponding braiding square for the finite colimit preserving functor $R \maps (\mathsf{X},1_\mathsf{X},+) \to (\mathsf{A},1_\mathsf{A},+)$ commutes.
+Thus the double functor $\mathbb{E} \maps _L\mathbb{C}\textnormal{sp}(\mathsf{X}) \to F\mathbb{C}\textnormal{sp}$ is symmetric monoidal.
 \end{comment}
@@
 
-Using a result of Shulman \cite{Shul}, each of the isofibrant symmetric monoidal double categories $F\mathbb{C}\textnormal{sp}$ and $_L \mathbb{C}\textnormal{sp}(\mathrm{X})$ give rise to underlying symmetric monoidal bicategories, namely $F\mathbb{C}\textnormal{sp}$ induces a symmetric monoidal bicategory $F\mathbf{Csp} \coloneqq H(F\mathbb{C}\textnormal{sp})$ which has:
+Using a result of Shulman \cite{Shul}, each of the isofibrant symmetric monoidal double categories $F\mathbb{C}\textnormal{sp}$ and $_L \mathbb{C}\textnormal{sp}(\mathrm{X})$ give rise to underlying symmetric monoidal bicategories, namely $F\mathbb{C}\textnormal{sp}$ induces a symmetric monoidal bicategory $F\mathbf{Csp} \mapseqq H(F\mathbb{C}\textnormal{sp})$ which has:
 \begin{enumerate}
@@
 \begin{comment}
-We can also define the part of the double equivalence $\mathbb{G} \colon F\mathbb{C}\textnormal{sp} \to {_L \mathbb{C} \textnormal{sp}(\mathsf{X})}$ which goes in the other direction: again, the object component of this double functor will be $\mathbb{G}_0 = \id_{\mathsf{A}}$.
+We can also define the part of the double equivalence $\mathbb{G} \maps F\mathbb{C}\textnormal{sp} \to {_L \mathbb{C} \textnormal{sp}(\mathsf{X})}$ which goes in the other direction: again, the object component of this double functor will be $\mathbb{G}_0 = \id_{\mathsf{A}}$.
 
@@
 \]
-where $!_{c} \colon L(c) \to x$ is the unique morphism from the trival decoration on $c$ given by $$!_{c} \coloneqq 1 \xrightarrow{\phi} F(0) \xrightarrow{F(!)} F(c)$$ to $x \in F(c)$.
+where $!_{c} \maps L(c) \to x$ is the unique morphism from the trival decoration on $c$ given by $$!_{c} \mapseqq 1 \xrightarrow{\phi} F(0) \xrightarrow{F(!)} F(c)$$ to $x \in F(c)$.
 In other words, the trivial decoraction $!_{c}$ is initial in $F(c)$.
-Similarly, given a 2-morphism $(f,h,g,\iota) \colon M \to M^\prime$ of $F\mathbb{C}\textnormal{sp}$:
+Similarly, given a 2-morphism $(f,h,g,\iota) \maps M \to M^\prime$ of $F\mathbb{C}\textnormal{sp}$:
 \[
@@
 \]
-$$\iota \colon F(h)(x) \to x^\prime$$
+$$\iota \maps F(h)(x) \to x^\prime$$
 the image $\mathbb{G}(f,h,g,\iota)$ in $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$ is given by the 2-morphism:
@@
 \]
-where $\alpha \colon x \to x^\prime$ is the morphism in the Grothendieck construction of $F$ given by $\alpha = (h \colon c \to c^\prime, \iota \colon F(h)(x) \to x^\prime)$.
-
-Next, we exhibit natural isomorphisms $\eta \colon \id_{ _L \mathbb{C}\textnormal{sp}(\mathsf{X})} \cong \mathbb{G} \mathbb{E}$ and $\epsilon \colon \mathbb{E} \mathbb{G} \cong \id_{F\mathbb{C}\textnormal{sp}}$.
+where $\alpha \maps x \to x^\prime$ is the morphism in the Grothendieck construction of $F$ given by $\alpha = (h \maps c \to c^\prime, \iota \maps F(h)(x) \to x^\prime)$.
+
+Next, we exhibit natural isomorphisms $\eta \maps \id_{ _L \mathbb{C}\textnormal{sp}(\mathsf{X})} \cong \mathbb{G} \mathbb{E}$ and $\epsilon \maps \mathbb{E} \mathbb{G} \cong \id_{F\mathbb{C}\textnormal{sp}}$.
 Specifically, these are double natural isomorphisms given by double transformations \cite{Shul2} $\eta$ and $\epsilon$ whose object and arrow components are natural isomorphisms.
@@
 First we compute the composites $\mathbb{G} \mathbb{E}$ and $\mathbb{E} \mathbb{G}$.
-On the object categories, both composites are $\id_\mathsf{A}$ and we have natural isomorphisms $\eta \colon \id_{\mathsf{A}} \cong \mathbb{G}_0 \mathbb{E}_0$ and $\epsilon \colon \mathbb{E}_0 \mathbb{G}_0 \cong \id_{\mathsf{A}}$.
+On the object categories, both composites are $\id_\mathsf{A}$ and we have natural isomorphisms $\eta \maps \id_{\mathsf{A}} \cong \mathbb{G}_0 \mathbb{E}_0$ and $\epsilon \maps \mathbb{E}_0 \mathbb{G}_0 \cong \id_{\mathsf{A}}$.
 
@@
 \]
-Then we can find a 2-isomorphism $\eta_M \colon M \xrightarrow{\sim} \mathbb{G}\mathbb{E}(M) $ in $_L \mathbb{C} \textnormal{sp}(\mathsf{X})$ given by:
+Then we can find a 2-isomorphism $\eta_M \maps M \xrightarrow{\sim} \mathbb{G}\mathbb{E}(M) $ in $_L \mathbb{C} \textnormal{sp}(\mathsf{X})$ given by:
 \[
@@
 \]
-Then we have a 2-isomorphism $\epsilon_N \colon \mathbb{E} \mathbb{G} (N) \xrightarrow{\sim} N$ in $F\mathbb{C}\textnormal{sp}$ given by:
+Then we have a 2-isomorphism $\epsilon_N \maps \mathbb{E} \mathbb{G} (N) \xrightarrow{\sim} N$ in $F\mathbb{C}\textnormal{sp}$ given by:
 \[
@@
 \]
-$$\iota \colon F(\hat{e})(x) \to x$$
+$$\iota \maps F(\hat{e})(x) \to x$$
 where 
@@
 The semantics of the activity at an open system's inputs and outputs is typically described in a category such as $\mathsf{LinRel}$ of finite dimensonal vector spaces and linear relations.
-Thus, in each case, black-boxing results in functors such as: $$\blacksquare_1 \colon \mathsf{Circ} \to \mathsf{LinRel}$$ $$\blacksquare_2 \colon \mathsf{Mark} \to \mathsf{LinRel}$$ $$\blacksquare_3 \colon \mathsf{Petri} \to \mathsf{LinRel}.$$ Each of these black-boxing functors also possess other convenient properties such as being symmetric monoidal.
+Thus, in each case, black-boxing results in functors such as: $$\blacksquare_1 \maps \mathsf{Circ} \to \mathsf{LinRel}$$ $$\blacksquare_2 \maps \mathsf{Mark} \to \mathsf{LinRel}$$ $$\blacksquare_3 \maps \mathsf{Petri} \to \mathsf{LinRel}.$$ Each of these black-boxing functors also possess other convenient properties such as being symmetric monoidal.
 The first two of these were first done using Fong's theory of decorated cospans and then extended by the first two authors using structured cospans.
@@
 \subsection{Graphs}
-As a first example that was also mentioned in the introduction, let $L \colon \mathsf{Set} \to \mathsf{Graph}$ be the functor that assigns to a set $N$ the \emph{discrete graph} on $N$ which is the edgeless graph $L(N)$ with no edges and $N$ as its set of vertices.
-Both $\mathsf{Set}$ and $\mathsf{Graph}$ are cocartesian monoidal and the functor $L \colon \mathsf{Set} \to \mathsf{Graph}$ is left adjoint to the forgetful functor $R \colon \mathsf{Graph} \to \mathsf{Set}$ which assigns to a graph $G$ its underlying set of vertices $U(G)$.
+As a first example that was also mentioned in the introduction, let $L \maps \mathsf{Set} \to \mathsf{Graph}$ be the functor that assigns to a set $N$ the \emph{discrete graph} on $N$ which is the edgeless graph $L(N)$ with no edges and $N$ as its set of vertices.
+Both $\mathsf{Set}$ and $\mathsf{Graph}$ are cocartesian monoidal and the functor $L \maps \mathsf{Set} \to \mathsf{Graph}$ is left adjoint to the forgetful functor $R \maps \mathsf{Graph} \to \mathsf{Set}$ which assigns to a graph $G$ its underlying set of vertices $U(G)$.
 Using structured cospans and appealing to Theorem \ref{SC}, we get a symmetric monoidal double category $_L \mathbb{C}\textnormal{sp}(\mathsf{Graph})$ which has:
@@
 \]
-as 2-morphisms, where $L(f)$ and $L(g)$ are maps of discrete graphs induced by the underlying functions $f$ and $g$, respectively, and $\alpha \colon G_1 \to G_2$ is a graph morphism.
+as 2-morphisms, where $L(f)$ and $L(g)$ are maps of discrete graphs induced by the underlying functions $f$ and $g$, respectively, and $\alpha \maps G_1 \to G_2$ is a graph morphism.
 }
@@
 We can obtain a similar symmetric monoidal double category using decorated cospans.
-Let $F \colon \mathsf{Set} \to \mathsf{Cat}$ be the symmetric lax monoidal pseudofunctor that assigns to a set $N$ the \emph{category} of all graph structures whose underlying set of vertices is $N$.
+Let $F \maps \mathsf{Set} \to \mathsf{Cat}$ be the symmetric lax monoidal pseudofunctor that assigns to a set $N$ the \emph{category} of all graph structures whose underlying set of vertices is $N$.
 Using Theorem \ref{DC}, we then obtain a symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$ which has:
@@
 \]
-together with a graph morphism $\iota \colon F(h)(G_1) \to G_2$ in $F(P_2)$.}
+together with a graph morphism $\iota \maps F(h)(G_1) \to G_2$ in $F(P_2)$.}
 \end{enumerate}
@@
 \]
-Here the finite sets $E$ and $V$ are the sets of edges and vertices, respectively, and if we take the field $k = \mathbb{R}$, the function $r \colon E \to \mathbb{R}^+$ assigns to each edge $e \in E$ a positive real number $r(e) \in \mathbb{R}^+$ which can be interpreted as the resistance at the edge $e$.
+Here the finite sets $E$ and $V$ are the sets of edges and vertices, respectively, and if we take the field $k = \mathbb{R}$, the function $r \maps E \to \mathbb{R}^+$ assigns to each edge $e \in E$ a positive real number $r(e) \in \mathbb{R}^+$ which can be interpreted as the resistance at the edge $e$.
 An open passive linear circuit is then given by a cospan of finite sets
@@
 
-Let $\mathsf{Graph}_k$ be the category whose objects are given by $k$-graphs and morphisms by morphisms of $k$-graphs, where a morphism of $k$-graphs is given by a pair of functions $f \colon E \to E^\prime$ and $g \colon V \to V^\prime$ between the edge sets and vertex sets, respectively, of two $k$-graphs that respect the source and target functions of each.
+Let $\mathsf{Graph}_k$ be the category whose objects are given by $k$-graphs and morphisms by morphisms of $k$-graphs, where a morphism of $k$-graphs is given by a pair of functions $f \maps E \to E^\prime$ and $g \maps V \to V^\prime$ between the edge sets and vertex sets, respectively, of two $k$-graphs that respect the source and target functions of each.
 In a previous work introducing structured cospans, the first two authors showed that the category $\mathsf{Graph}_k$ has finite colimits \cite{BC2}.
-We can then obtain a double category of open passive linear circuits by defining a left adjoint $L \colon \mathsf{Set} \to \mathsf{Graph}_k$ that assigns to a set $V$ the discrete passive linear circuit $L(V)$ given by passive linear circuit with $V$ as its set of vertices and no edges.
+We can then obtain a double category of open passive linear circuits by defining a left adjoint $L \maps \mathsf{Set} \to \mathsf{Graph}_k$ that assigns to a set $V$ the discrete passive linear circuit $L(V)$ given by passive linear circuit with $V$ as its set of vertices and no edges.
 The resulting symmetric monoidal double category $_L \mathbb{C}\textnormal{sp}(\mathsf{Graph}_k)$ has:
@@
 \end{enumerate}
-We can also obtain a similar double category using decorated cospans: define a pseudofunctor $F \colon \mathsf{FinSet} \to \mathbf{Cat}$ that assigns to a finite set $V$ the category of all $k$-graph structures on the finite set $V$ and to a function $f \colon V \to V^\prime$ the corresponding functor $F(f) \colon F(V) \to F(V^\prime)$ between decoration categories.
-Both categories $\mathsf{FinSet}$ and $\mathbf{Cat}$ are symmetric monoidal and the pseudofunctor $F \colon \mathsf{FinSet} \to \mathbf{Cat}$ is symmetric lax monoidal, as given a $k$-graph structure on a finite set $V_1$ denoted by an element $K_1 \in F(V_1)$ and a $k$-graph structure on a finite set $V_2$ denoted by an element $K_2 \in F(V_2)$, we can consider the $k$-graph structures simultaneously as a single graph structure $\phi_{V_1,V_2}(K_1,K_2)$ on the finite set $V_1+V_2$.
-Thus we get a family of natural transformations $$\phi_{V_1,V_2} \colon F(V_1) \times F(V_2) \to F(V_1+V_2)$$ as well as a morphism $\phi \colon 1_{\mathsf{Graph}_k} \to F(\emptyset)$ which together satisfy the coherence conditions of a monoidal functor.
+We can also obtain a similar double category using decorated cospans: define a pseudofunctor $F \maps \mathsf{FinSet} \to \mathbf{Cat}$ that assigns to a finite set $V$ the category of all $k$-graph structures on the finite set $V$ and to a function $f \maps V \to V^\prime$ the corresponding functor $F(f) \maps F(V) \to F(V^\prime)$ between decoration categories.
+Both categories $\mathsf{FinSet}$ and $\mathbf{Cat}$ are symmetric monoidal and the pseudofunctor $F \maps \mathsf{FinSet} \to \mathbf{Cat}$ is symmetric lax monoidal, as given a $k$-graph structure on a finite set $V_1$ denoted by an element $K_1 \in F(V_1)$ and a $k$-graph structure on a finite set $V_2$ denoted by an element $K_2 \in F(V_2)$, we can consider the $k$-graph structures simultaneously as a single graph structure $\phi_{V_1,V_2}(K_1,K_2)$ on the finite set $V_1+V_2$.
+Thus we get a family of natural transformations $$\phi_{V_1,V_2} \maps F(V_1) \times F(V_2) \to F(V_1+V_2)$$ as well as a morphism $\phi \maps 1_{\mathsf{Graph}_k} \to F(\emptyset)$ which together satisfy the coherence conditions of a monoidal functor.
 The braiding is also clear as the following diagram commutes:
@@
 \]
-together with a morphism of $k$-graphs $\iota \colon F(h)(K_1) \to K_2$ in $F(V_2)$.}
+together with a morphism of $k$-graphs $\iota \maps F(h)(K_1) \to K_2$ in $F(V_2)$.}
 \end{enumerate}
@@
 
-Fong, Pollard and the first author then add extra structure to open Markov processes such as populations at each node to obtain a symmetric monoidal category $\mathsf{DetlBalMark}$ of open Markov processes in `detailed balance' and then construct a black box functor $\blacksquare \colon \mathsf{DetBalMark} \to \mathsf{LinRel}$ that describes the steady state behavior of an open Markov process in detailed balance.
+Fong, Pollard and the first author then add extra structure to open Markov processes such as populations at each node to obtain a symmetric monoidal category $\mathsf{DetlBalMark}$ of open Markov processes in `detailed balance' and then construct a black box functor $\blacksquare \maps \mathsf{DetBalMark} \to \mathsf{LinRel}$ that describes the steady state behavior of an open Markov process in detailed balance.
 On the way to doing this, one of the categories they construct using Fong's decorated cospan machinery is a symmetric monoidal category $\mathsf{Mark}$ which has:
@@
 \end{enumerate}
-This is done using a symmetric lax monoidal functor $F \colon \mathsf{FinSet} \to \mathsf{Set}$ which assigns to each finite set $N$ the (large) set of all Markov processes on $N$ as defined above.
-Viewing this functor $F$ as now a symmetric lax monoidal pseudofunctor $F \colon \mathsf{FinSet} \to \mathbf{Cat}$ that assigns to a finite set $N$ the \emph{category} $F(N)$ of all Markov processes on $N$, we then get by Theorem \ref{DC} a symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$ which has:
+This is done using a symmetric lax monoidal functor $F \maps \mathsf{FinSet} \to \mathsf{Set}$ which assigns to each finite set $N$ the (large) set of all Markov processes on $N$ as defined above.
+Viewing this functor $F$ as now a symmetric lax monoidal pseudofunctor $F \maps \mathsf{FinSet} \to \mathbf{Cat}$ that assigns to a finite set $N$ the \emph{category} $F(N)$ of all Markov processes on $N$, we then get by Theorem \ref{DC} a symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$ which has:
 \begin{enumerate}
@@
 \]
-together with a map of Markov processes $\iota \colon F(h)(M_1) \to M_2$ in $F(N_2)$, where a map between two Markov processes to be given by a pair of functions $(g,h)$ that make the following diagram commute:
+together with a map of Markov processes $\iota \maps F(h)(M_1) \to M_2$ in $F(N_2)$, where a map between two Markov processes to be given by a pair of functions $(g,h)$ that make the following diagram commute:
 \[
@@
 \end{enumerate}
-A symmetric monoidal double category of open Markov processes can also be obtained using structured cospans by defining a functor $L \colon \mathsf{FinSet} \to \mathsf{Mark}$ which assigns to a finite set $N$ the discrete Markov process $L(N)$ with no edges and to a function $f \colon N \to N^\prime$ the induced map of discrete Markov processes.
-Both categories $\mathsf{FinSet}$ and $\mathsf{Mark}$ have finite colimits and the functor $L$ is left adjoint to the forgetful functor $R \colon \mathsf{Mark} \to \mathsf{FinSet}$ which maps a Markov process to its underlying finite set of states.
+A symmetric monoidal double category of open Markov processes can also be obtained using structured cospans by defining a functor $L \maps \mathsf{FinSet} \to \mathsf{Mark}$ which assigns to a finite set $N$ the discrete Markov process $L(N)$ with no edges and to a function $f \maps N \to N^\prime$ the induced map of discrete Markov processes.
+Both categories $\mathsf{FinSet}$ and $\mathsf{Mark}$ have finite colimits and the functor $L$ is left adjoint to the forgetful functor $R \maps \mathsf{Mark} \to \mathsf{FinSet}$ which maps a Markov process to its underlying finite set of states.
 By Theorem \ref{SC}, we get a symmetric monoidal double category $_L \mathbb{C}\textnormal{sp}(\mathsf{Mark})$ which has:
@@
 Each set of species $S$ gives rise to a discrete Petri net $L(S)$ with $S$ as its set of species and no transitions.
-Master and the first author show the existence of a left adjoint $L \colon \mathsf{Set} \to \mathsf{Petri}$ where $\mathsf{Petri}$ is the category whose objects are Petri nets and whose `morphisms are morphisms of Petri nets'.
+Master and the first author show the existence of a left adjoint $L \maps \mathsf{Set} \to \mathsf{Petri}$ where $\mathsf{Petri}$ is the category whose objects are Petri nets and whose `morphisms are morphisms of Petri nets'.
 They also show that $\mathsf{Petri}$ has finite colimits and thus using Theorem \ref{SC} obtain a symmetric monoidal double category $\mathbb{O}\mathbf{pen}(\mathrm{Petri})$ of open Petri nets which has:
@@
 \end{enumerate}
-We can also obtain a similar double category using decorated cospans: define a pseudofunctor $F \colon \mathsf{Set} \to \mathbf{Cat}$ where given a set $s$, $F(s)$ is the category of all Petri net structures with $s$ as its set of species.
-This pseudofunctor $F$ is symmetric lax monoidal as both $(\mathsf{Set},+,\emptyset)$ and $(\mathbf{Cat},\times,1)$ are symmetric monoidal and given Petri nets $P \in F(s)$ and $P^\prime \in F(s^\prime)$, we can place them side by side and consider them together as a single Petri net $P+P^\prime \in F(s+s^\prime)$ with set of species $s+s^\prime$, and thus we have natural transformations $\phi_{s,s^\prime} \colon F(s) \times F(s^\prime) \to F(s+s^\prime)$ for any two sets $s$ and $s^\prime$.
-The other structure morphism between monoidal units $\phi \colon 1_{\mathsf{Petri}} \to F(\emptyset)$ is defined by the unique morphism from the empty Petri net with the empty set forits set of species to the only possible Petri net on the empty set, which is also the empty Petri net.
+We can also obtain a similar double category using decorated cospans: define a pseudofunctor $F \maps \mathsf{Set} \to \mathbf{Cat}$ where given a set $s$, $F(s)$ is the category of all Petri net structures with $s$ as its set of species.
+This pseudofunctor $F$ is symmetric lax monoidal as both $(\mathsf{Set},+,\emptyset)$ and $(\mathbf{Cat},\times,1)$ are symmetric monoidal and given Petri nets $P \in F(s)$ and $P^\prime \in F(s^\prime)$, we can place them side by side and consider them together as a single Petri net $P+P^\prime \in F(s+s^\prime)$ with set of species $s+s^\prime$, and thus we have natural transformations $\phi_{s,s^\prime} \maps F(s) \times F(s^\prime) \to F(s+s^\prime)$ for any two sets $s$ and $s^\prime$.
+The other structure morphism between monoidal units $\phi \maps 1_{\mathsf{Petri}} \to F(\emptyset)$ is defined by the unique morphism from the empty Petri net with the empty set forits set of species to the only possible Petri net on the empty set, which is also the empty Petri net.
 All of the diagrams that are required to commute are straightforward.
@@
 \]
-together with a morphism of Petri nets $\iota \colon F(h)(P_1) \to P_2$ in $F(Z_2)$.}
+together with a morphism of Petri nets $\iota \maps F(h)(P_1) \to P_2$ in $F(Z_2)$.}
 \end{enumerate}
@@
 
-Recall that a pseudofunctor $F\colon\bicat{A}\to\bicat{B}$ between bicategories $\bicat{A}$ and $\bicat{B}$ is functorial up to coherent natural isomorphism, namely for composable arrows we have $F(g\circ f)\cong Fg\circ Ff$ and $F(1_a)\cong1_{Fa}$ satisfying standard axioms.
-Given pseudofunctors $F,G\colon \bicat{A} \to \bicat{B}$, a \define{pseudonatural transformation} $\sigma$ consists of
+Recall that a pseudofunctor $F\maps\bicat{A}\to\bicat{B}$ between bicategories $\bicat{A}$ and $\bicat{B}$ is functorial up to coherent natural isomorphism, namely for composable arrows we have $F(g\circ f)\cong Fg\circ Ff$ and $F(1_a)\cong1_{Fa}$ satisfying standard axioms.
+Given pseudofunctors $F,G\maps \bicat{A} \to \bicat{B}$, a \define{pseudonatural transformation} $\sigma$ consists of
 \begin{itemize}
-\item for each object $a \in \bicat{A}$, a morphism $\sigma_a \colon F(a) \to G(a)$ in $\bicat{B}$ 
+\item for each object $a \in \bicat{A}$, a morphism $\sigma_a \maps F(a) \to G(a)$ in $\bicat{B}$ 
 \item 
@@
 %where $(\sigma_a)^*$ and $(\sigma_b)_*$ are the functors induced by precomposition and postcompositon, respectively. Thus 
-for each morphism $f \colon a \to b$ in $\mathbf{A}$, an invertible natural 2-morphism $\sigma_f \colon G(f) \sigma_a \xrightarrow{\sim} \sigma_{b} F(f)$ in $\mathbf{B}$
+for each morphism $f \maps a \to b$ in $\mathbf{A}$, an invertible natural 2-morphism $\sigma_f \maps G(f) \sigma_a \xrightarrow{\sim} \sigma_{b} F(f)$ in $\mathbf{B}$
 %:
@@
 \end{itemize}
-%such that for each composable pair of morphisms $f \colon a \to b$ and $g \colon b \to c$ of $\mathbf{A}$, the following diagrams commute:
+%such that for each composable pair of morphisms $f \maps a \to b$ and $g \maps b \to c$ of $\mathbf{A}$, the following diagrams commute:
 %\[
@@
 
-A \define{lax monoidal} pseudofunctor between monoidal bicategories $F\colon\bicat{A}\to\bicat{B}$ is a pseudofunctor equipped with pseudonatural transformations with components $\mu_{a,b}\colon Fa\otimes Fb\to F(a\otimes b)$ and $\mu_0\colon I\to FI$ along with coherent invertible modifications for associativity and unitality.
+A \define{lax monoidal} pseudofunctor between monoidal bicategories $F\maps\bicat{A}\to\bicat{B}$ is a pseudofunctor equipped with pseudonatural transformations with components $\mu_{a,b}\maps Fa\otimes Fb\to F(a\otimes b)$ and $\mu_0\maps I\to FI$ along with coherent invertible modifications for associativity and unitality.
 This is commonly also called `weak monoida' pseudofunctor.
@@
 
-A functor $U \maps \X \to \A$ is a \textbf{Grothendieck opfibration} if for every $x\in\X$ with $U(x)=a$ and $f \colon a \to b$ in $\A$, there exists a \textbf{cocartesian lifting} of $x$ along $f$, namely a morphism $\beta$ in $\X$ with domain $x$ above $f$ with the following universal property: for any $g\colon b\to b'$ in $\A$ and $\gamma\colon x\to y'$ in $\X$ above the composite $g\circ f$, there exists a unique $\delta\colon y\to y'$ such that $U(\delta)=g$ and $\gamma=\delta\circ\beta$ as shown below
+A functor $U \maps \X \to \A$ is a \textbf{Grothendieck opfibration} if for every $x\in\X$ with $U(x)=a$ and $f \maps a \to b$ in $\A$, there exists a \textbf{cocartesian lifting} of $x$ along $f$, namely a morphism $\beta$ in $\X$ with domain $x$ above $f$ with the following universal property: for any $g\maps b\to b'$ in $\A$ and $\gamma\maps x\to y'$ in $\X$ above the composite $g\circ f$, there exists a unique $\delta\maps y\to y'$ such that $U(\delta)=g$ and $\gamma=\delta\circ\beta$ as shown below
 \begin{displaymath}
@@
 %\begin{defn}
-%Let $P \colon \ca{X} \to \ca{A}$ be a functor.
-A morphism $f \colon d_{1} \to d_{2}$ in the category $\mathrm{D}$ is \textbf{cocartesian (with respect to the functor P)} if for any object $d^\prime$ in $\mathrm{D}$ and morphism $g \colon d_{1} \to d^\prime$ and every $p \colon P(d_{2}) \to P(d^\prime)$ such that $P(g)=p P(f)$, there exists a unique $h \colon d_{2} \to d^\prime$ such that $g=hf$ and $p=P(h)$.
+%Let $P \maps \ca{X} \to \ca{A}$ be a functor.
+A morphism $f \maps d_{1} \to d_{2}$ in the category $\mathrm{D}$ is \textbf{cocartesian (with respect to the functor P)} if for any object $d^\prime$ in $\mathrm{D}$ and morphism $g \maps d_{1} \to d^\prime$ and every $p \maps P(d_{2}) \to P(d^\prime)$ such that $P(g)=p P(f)$, there exists a unique $h \maps d_{2} \to d^\prime$ such that $g=hf$ and $p=P(h)$.
 %\[
@@
 %\begin{defn}
-%A functor $P \colon \mathrm{D} \to \mathrm{A}$ is a \textbf{(Grothendieck) opfibration} if for any object $d$ in $\mathbf{D}$ and morphism $f \colon c %\to P(d)$ there exists a cocartesian morphism $\phi \colon d^\prime \to d$ such that $P(\phi)=f$.
+%A functor $P \maps \mathrm{D} \to \mathrm{A}$ is a \textbf{(Grothendieck) opfibration} if for any object $d$ in $\mathbf{D}$ and morphism $f \maps c %\to P(d)$ there exists a cocartesian morphism $\phi \maps d^\prime \to d$ such that $P(\phi)=f$.
 %\end{defn}
 %\begin{defn}
-%Let $P \colon \mathrm{D} \to \mathrm{A}$ and $P^\prime \colon \mathrm{D^\prime} \to \mathrm{A}$ be opfibrations over a category $\mathrm{A}$.
-A \define{morphism of opfibrations} is a functor $F \colon \mathrm{D} \to \mathrm{D}^\prime$ such that $F(p)$ is cocartesian with respect to $P^\prime$ if $p$ is cocartesian with respect to $P$ and $P=P^\prime F$.
+%Let $P \maps \mathrm{D} \to \mathrm{A}$ and $P^\prime \maps \mathrm{D^\prime} \to \mathrm{A}$ be opfibrations over a category $\mathrm{A}$.
+A \define{morphism of opfibrations} is a functor $F \maps \mathrm{D} \to \mathrm{D}^\prime$ such that $F(p)$ is cocartesian with respect to $P^\prime$ if $p$ is cocartesian with respect to $P$ and $P=P^\prime F$.
 %\end{defn}
@@
 Assuming the axiom of choice, we may select a cocartesian arrow over each $f\maps a\to b$ in $\A$ and $x\in\X _a$, denoted by $\mathrm{Cocart}(f,x)\maps x\to f_!(x)$, rendering $U$ a so-called \textbf{cloven} opfibration.
-This choice induces \textbf{reindexing functors} $f_!\colon\X _a\to\X _b$ between the fibre categories, which by the liftings universal property adhere to natural $(1_a)_!\cong1_{\X _a}$ and $(f\circ g)_!\cong f_!\circ g_!$.
+This choice induces \textbf{reindexing functors} $f_!\maps\X _a\to\X _b$ between the fibre categories, which by the liftings universal property adhere to natural $(1_a)_!\cong1_{\X _a}$ and $(f\circ g)_!\cong f_!\circ g_!$.
 If these isomorphisms are equalities, we have the notion of a \textbf{split} opfibration.
@@
 %\xymatrix @C=.4in @R=.2in
-%{x \ar @{.>}[dd]\ar[rr]^\gamma \ar[drr]_-{\Cocart(g,C)} && D &\\
+%{x \ar @{.>}[dd]\ar[rr]^\gamma \ar[drr]_-{\Rex(g,C)} && D &\\
 %&& f_!C \ar @{-->}[u]_-{\delta} \ar @{.>}[d] & \textrm{in }\C  \\
@@
 %\item{objects as pairs $(\mathrm{A},c)$ where $\mathrm{A}$ is a category and $c$ is an object of $\mathrm{A}$, and}
-%\item{a morphism from $(\mathrm{A},c)$ to $(\mathrm{X},y)$ is a pair $(F,f)$ where $F \colon \mathrm{A} \to \mathrm{X}$ is a functor and $f \colon F(c) \to y$ is a morphism in $\mathrm{X}$.}
+%\item{a morphism from $(\mathrm{A},c)$ to $(\mathrm{X},y)$ is a pair $(F,f)$ where $F \maps \mathrm{A} \to \mathrm{X}$ is a functor and $f \maps F(c) \to y$ is a morphism in $\mathrm{X}$.}
 %\end{enumerate}
@@
 %\begin{defn}
-%Given a pseudofunctor $F \colon \mathrm{A} \to \mathbf{Cat}$, the \define{Grothendieck construction of} $F$ is given by the `strict 2-pullback' of the following cospan:
+%Given a pseudofunctor $F \maps \mathrm{A} \to \mathbf{Cat}$, the \define{Grothendieck construction of} $F$ is given by the `strict 2-pullback' of the following cospan:
 % \[
@@
 %\]
-%where $P \colon \mathbf{Cat}_{\textnormal{lax},\star} \to \mathbf{Cat}$ is the forgetful functor. 
+%where $P \maps \mathbf{Cat}_{\textnormal{lax},\star} \to \mathbf{Cat}$ is the forgetful functor. 
 \begin{defn}\label{def:GrothCat}
-For any pseudofunctor $F\colon\A\to\bicat{Cat}$ where $\A$ is a category viewed as a 2-category with trivial 2-cells, the \textbf{Grothendieck category}
+For any pseudofunctor $F\maps\A\to\bicat{Cat}$ where $\A$ is a category viewed as a 2-category with trivial 2-cells, the \textbf{Grothendieck category}
 $\inta F$ has
@@
 \item objects pairs $(a, x \in F(a))$ and
-\item a morphism from $(a, x \in F(a))$ to $(b, y\in F(b))$ is a pair $(f \colon a \to b,\delta \colon F(f)(x) \to y)\in\A\times F(b)$.
+\item a morphism from $(a, x \in F(a))$ to $(b, y\in F(b))$ is a pair $(f \maps a \to b,\delta \maps F(f)(x) \to y)\in\A\times F(b)$.
 \end{itemize}
@@
 %gives rise to a 2-functor $[\A,\bicat{Cat}]_\pse\to \mathbf{Cat}/ \A$ which factors through the embedding $\OpFib(\A) \hookrightarrow \bicat{Cat} / \A$ as per the following theorem.
-%: $$\inta F \colon [ \mathrm{A}, \mathbf{Cat} ] \to \textnormal{Opfib}(\mathrm{A}) \hookrightarrow \mathbf{Cat} / \mathrm{A}.$$
+%: $$\inta F \maps [ \mathrm{A}, \mathbf{Cat} ] \to \textnormal{Opfib}(\mathrm{A}) \hookrightarrow \mathbf{Cat} / \mathrm{A}.$$
 
@@
         \item Every opfibration $\U \maps \X \to \A$ gives rise to a pseudofunctor $F_U \maps \A \to \bicat{Cat}$.
-        \item Every pseudofunctor $F \maps \A \to \bicat{Cat}$ gives rise to  an opfibration $\U_F \colon \inta F\to\A$.
+        \item Every pseudofunctor $F \maps \A \to \bicat{Cat}$ gives rise to  an opfibration $\U_F \maps \inta F\to\A$.
         \item The above correspondences yield an equivalence of 2-categories 
@@
 %\begin{defn}
-%Let $P \colon \mathbf{D} \to \mathrm{A}$ be a functor.
-A morphism $f \colon d_{1} \to d_{2}$ in the category $\mathbf{D}$ is \textbf{cartesian (with respect to the functor P)} if for any object $d^\prime$ in $\mathbf{D}$ and morphism $g \colon d^\prime \to d_{2}$ and every $p \colon P(d^\prime) \to P(d_{1})$ such that $P(g)=P(f)p$, there exists a unique $h \colon d^\prime \to d_{1}$ such that $g=fh$ and $p=P(h)$.
+%Let $P \maps \mathbf{D} \to \mathrm{A}$ be a functor.
+A morphism $f \maps d_{1} \to d_{2}$ in the category $\mathbf{D}$ is \textbf{cartesian (with respect to the functor P)} if for any object $d^\prime$ in $\mathbf{D}$ and morphism $g \maps d^\prime \to d_{2}$ and every $p \maps P(d^\prime) \to P(d_{1})$ such that $P(g)=P(f)p$, there exists a unique $h \maps d^\prime \to d_{1}$ such that $g=fh$ and $p=P(h)$.
 %\[
@@
 \begin{center}
-$U\colon \mathbf{D_{0}} \to \mathbf{D_{1}}$\\
-$S,T \colon \mathbf{D_{1}} \rightrightarrows \mathbf{D_{0}}$\\
-$\odot \colon \mathbf{D_{1}} \times_{\mathbf{D_{0}}} \mathbf{D_{1}} \to \mathbf{D_{1}}$ (where the pullback is taken over $\mathbf{D_{1}} \xrightarrow[]{T} \mathbf{D_{0}} \xleftarrow[]{S} \mathbf{D_{1}}$) \\
+$U\maps \mathbf{D_{0}} \to \mathbf{D_{1}}$\\
+$S,T \maps \mathbf{D_{1}} \rightrightarrows \mathbf{D_{0}}$\\
+$\odot \maps \mathbf{D_{1}} \times_{\mathbf{D_{0}}} \mathbf{D_{1}} \to \mathbf{D_{1}}$ (where the pullback is taken over $\mathbf{D_{1}} \xrightarrow[]{T} \mathbf{D_{0}} \xleftarrow[]{S} \mathbf{D_{1}}$) \\
 \end{center}
@@
 
-$\alpha \colon (M \odot N) \odot P \xrightarrow{\sim} M \odot (N \odot P)$\\
-$\lambda \colon U_{B} \odot M \xrightarrow{\sim} M$\\
-$\rho \colon M \odot U_{A} \xrightarrow{\sim} M$
+$\alpha \maps (M \odot N) \odot P \xrightarrow{\sim} M \odot (N \odot P)$\\
+$\lambda \maps U_{B} \odot M \xrightarrow{\sim} M$\\
+$\rho \maps M \odot U_{A} \xrightarrow{\sim} M$
 
@@
 Objects of $\mathbf{D_{1}}$ are called $\textbf{horizontal 1-cells}$ and morphisms of $\mathbf{D_{1}}$ are called $\textbf{2-morphisms}$.
-The morphisms of $\mathbf{D_{0}}$, which are vertical 1-morphisms, will be denoted $f \colon A \to C$ and we denote a 1-cell $M$ with $S(M)=A,T(M)=B$ by $M \colon A \to B$.
-Then a 2-morphism $a \colon M \to N$ of $\mathbf{D_{1}}$ with $S(a)=f,T(a)=g$ would look like:
+The morphisms of $\mathbf{D_{0}}$, which are vertical 1-morphisms, will be denoted $f \maps A \to C$ and we denote a 1-cell $M$ with $S(M)=A,T(M)=B$ by $M \maps A \to B$.
+Then a 2-morphism $a \maps M \to N$ of $\mathbf{D_{1}}$ with $S(a)=f,T(a)=g$ would look like:
 \[
@@
 Let $\mathbb{A}$ and $\mathbb{B}$ be pseudo double categories.
-A \define{lax double functor} is a functor $\mathbb{F} \colon\mathbb{A}\to \mathbb{B}$ that takes items of $\mathbb{A}$ to items of $\mathbb{B}$ of the corresponding type, respecting vertical composition in the strict sense and the horizontal composition up to an assigned comparison $\phi$.
-This means that we have functors $\mathbb{F}_0 \colon \mathbb{A}_0 \to \mathbb{B}_0$ and $\mathbb{F}_1 \colon \mathbb{A}_1 \to \mathbb{B}_1$ such that the following equations are satisfied: $$S \circ \mathbb{F}_1 = \mathbb{F}_0 \circ S$$ $$T \circ \mathbb{F}_1 = \mathbb{F}_0 \circ T$$ Sometimes for brevity, we will omit the subscripts and simply say $\mathbb{F}$.
+A \define{lax double functor} is a functor $\mathbb{F} \maps\mathbb{A}\to \mathbb{B}$ that takes items of $\mathbb{A}$ to items of $\mathbb{B}$ of the corresponding type, respecting vertical composition in the strict sense and the horizontal composition up to an assigned comparison $\phi$.
+This means that we have functors $\mathbb{F}_0 \maps \mathbb{A}_0 \to \mathbb{B}_0$ and $\mathbb{F}_1 \maps \mathbb{A}_1 \to \mathbb{B}_1$ such that the following equations are satisfied: $$S \circ \mathbb{F}_1 = \mathbb{F}_0 \circ S$$ $$T \circ \mathbb{F}_1 = \mathbb{F}_0 \circ T$$ Sometimes for brevity, we will omit the subscripts and simply say $\mathbb{F}$.
 As to whether we mean $\mathbb{F}_0$ or $\mathbb{F}_1$ will be clear from context.
 
-Also, every object $a$ is equipped with a special globular 2-morphism $\phi_{a} \colon 1_{\mathbb{F}(a)} \to \mathbb{F}(1_{a})$ (the identity comparison), and every horizontal composition $N_{1} \odot N_{2}$ is equipped with a special globular 2-morphism $\phi(N_{1},N_{2}) \colon \mathbb{F}(N_{1}) \odot \mathbb{F}(N_{2}) \to \mathbb{F}(N_{1} \odot N_{2})$ (the composition comparison), in a coherent way.
+Also, every object $a$ is equipped with a special globular 2-morphism $\phi_{a} \maps 1_{\mathbb{F}(a)} \to \mathbb{F}(1_{a})$ (the identity comparison), and every horizontal composition $N_{1} \odot N_{2}$ is equipped with a special globular 2-morphism $\phi(N_{1},N_{2}) \maps \mathbb{F}(N_{1}) \odot \mathbb{F}(N_{2}) \to \mathbb{F}(N_{1} \odot N_{2})$ (the composition comparison), in a coherent way.
 This means that the following diagrams commute.
@@
 
-\item For a horizontal 1-cell $N \colon A \to B$, the following diagrams are commutative (under horizontal composition).
+\item For a horizontal 1-cell $N \maps A \to B$, the following diagrams are commutative (under horizontal composition).
 
@@
 \begin{defn}
-A double functor $\mathbb{F} \colon \mathbb{A} \to \mathbb{X}$ is \define{strong} if the comparison and unit constraints are globular isomorphisms, meaning that for each composable pair of horizontal 1-cells $M$ and $N$ we have a natural isomorphism $$\mathbb{F}_{M,N} \colon \mathbb{F}(M) \odot \mathbb{F}(N) \xrightarrow{\sim} \mathbb{F}(M \odot N)$$and for each object $a \in \mathbb{A}$ a natural isomorphism $$\mathbb{F}_a \colon \hat{U}_{\mathbb{F}(a)} \xrightarrow{\sim} \mathbb{F}(U_a).$$
+A double functor $\mathbb{F} \maps \mathbb{A} \to \mathbb{X}$ is \define{strong} if the comparison and unit constraints are globular isomorphisms, meaning that for each composable pair of horizontal 1-cells $M$ and $N$ we have a natural isomorphism $$\mathbb{F}_{M,N} \maps \mathbb{F}(M) \odot \mathbb{F}(N) \xrightarrow{\sim} \mathbb{F}(M \odot N)$$and for each object $a \in \mathbb{A}$ a natural isomorphism $$\mathbb{F}_a \maps \hat{U}_{\mathbb{F}(a)} \xrightarrow{\sim} \mathbb{F}(U_a).$$
 \end{defn}
@@
 \begin{defn}\label{def:fullfaithful}
-A (possibly lax or oplax) double functor $\mathbb{F} \colon \mathbb{A} \to \mathbb{X}$ is \define{full} (respectively, \define{faithful}) if $\mathbb{F}_0 \colon \mathbb{A}_0 \to \mathbb{X}_0$ is full (respectively, faithful) and each map $$\mathbb{F}_1 \colon _f \mathbb{A}_g(M,N) \to _{\mathbb{F}(f)} \mathbb{X}_{\mathbb{F}(g)}(\mathbb{F}(M),\mathbb{F}(N))$$ is surjective (respectively, injective).
+A (possibly lax or oplax) double functor $\mathbb{F} \maps \mathbb{A} \to \mathbb{X}$ is \define{full} (respectively, \define{faithful}) if $\mathbb{F}_0 \maps \mathbb{A}_0 \to \mathbb{X}_0$ is full (respectively, faithful) and each map $$\mathbb{F}_1 \maps _f \mathbb{A}_g(M,N) \to _{\mathbb{F}(f)} \mathbb{X}_{\mathbb{F}(g)}(\mathbb{F}(M),\mathbb{F}(N))$$ is surjective (respectively, injective).
 \end{defn}
 \begin{defn}\label{def:essentiallysurj}
-A (possibly lax or oplax) double functor $\mathbb{F} \colon \mathbb{A} \to \mathbb{X}$ is \define{essentially surjective} if we can simultaneously make the following choices:
+A (possibly lax or oplax) double functor $\mathbb{F} \maps \mathbb{A} \to \mathbb{X}$ is \define{essentially surjective} if we can simultaneously make the following choices:
 \begin{enumerate}
-\item{For each object $x \in \mathbb{X}$, we can find an object $a \in \mathbb{A}$ together with a vertical 1-isomorphism $\alpha_x \colon \mathbb{F}(a) \to x$, and}
-\item{For each horizontal 1-cell $N \colon x_1 \tobar x_2$  of $\mathbb{X}$, we can find a horizontal 1-cell $M \colon a_1 \tobar a_2$ of $\mathbb{A}$ and a 2-isomorphism $a_{N}$ of $\mathbb{X}$ as in the following diagram:
+\item{For each object $x \in \mathbb{X}$, we can find an object $a \in \mathbb{A}$ together with a vertical 1-isomorphism $\alpha_x \maps \mathbb{F}(a) \to x$, and}
+\item{For each horizontal 1-cell $N \maps x_1 \tobar x_2$  of $\mathbb{X}$, we can find a horizontal 1-cell $M \maps a_1 \tobar a_2$ of $\mathbb{A}$ and a 2-isomorphism $a_{N}$ of $\mathbb{X}$ as in the following diagram:
 \[
@@
 \begin{thm}\label{ShulDubEquiv}
-A strong double functor $\mathbb{F} \colon \mathbb{A} \to \mathbb{X}$ is part of a double equivalence if and only if it is full, faithful and essentially surjective. {\chris on objects?}
+A strong double functor $\mathbb{F} \maps \mathbb{A} \to \mathbb{X}$ is part of a double equivalence if and only if it is full, faithful and essentially surjective. {\chris on objects?}
 \end{thm}
@@
 \begin{prop}
-Let $\mathbb{A}$ and $\mathbb{X}$ be symmetric monoidal double categories and let $\mathbb{F} \colon \mathbb{A} \to \mathbb{X}$ be a symmetric monoidal strong double functor.
+Let $\mathbb{A}$ and $\mathbb{X}$ be symmetric monoidal double categories and let $\mathbb{F} \maps \mathbb{A} \to \mathbb{X}$ be a symmetric monoidal strong double functor.
 If $\mathbb{F}$ is part of a double equivalence, then $\mathbb{F}$ is in fact part of a symmetric monoidal double equivalence, and $\mathbb{A}$ and $\mathbb{X}$ are equivalent as symmetric monoidal double categories.
@@
 \label{defn:monoidal_double_functor}
-A \define{(strong) monoidal lax double functor} $\mathbb{F} \colon \mathbb{C} \to \mathbb{D}$ between monoidal double categories $\mathbb{C}$ and $\mathbb{D}$ is a lax double functor $\mathbb{F} \maps \mathbb{C} \to \mathbb{D}$ such that
+A \define{(strong) monoidal lax double functor} $\mathbb{F} \maps \mathbb{C} \to \mathbb{D}$ between monoidal double categories $\mathbb{C}$ and $\mathbb{D}$ is a lax double functor $\mathbb{F} \maps \mathbb{C} \to \mathbb{D}$ such that
 	\begin{itemize}
@@
 \begin{enumerate}
-\item{an isomorphism $\epsilon \colon 1_{\lD} \to \mathbb{F}(1_{\lC})$}
-\item{a natural isomorphism $\mu_{A,B} \colon \mathbb{F}(A) \otimes \mathbb{F}(B) \to \mathbb{F}(A \otimes B)$ for all objects $A$ and $B$ of $\lC$}
-\item{an isomorphism $\delta \colon U_{1_{\lD}} \to \mathbb{F}(U_{1_{\lC}})$}
-\item{a natural isomorphism $\nu_{M,N} \colon \mathbb{F}(M) \otimes \mathbb{F}(N) \to \mathbb{F}(M \otimes N)$ for all horizontal 1-cells $N$ and $M$ of $\lC$}
+\item{an isomorphism $\epsilon \maps 1_{\lD} \to \mathbb{F}(1_{\lC})$}
+\item{a natural isomorphism $\mu_{A,B} \maps \mathbb{F}(A) \otimes \mathbb{F}(B) \to \mathbb{F}(A \otimes B)$ for all objects $A$ and $B$ of $\lC$}
+\item{an isomorphism $\delta \maps U_{1_{\lD}} \to \mathbb{F}(U_{1_{\lC}})$}
+\item{a natural isomorphism $\nu_{M,N} \maps \mathbb{F}(M) \otimes \mathbb{F}(N) \to \mathbb{F}(M \otimes N)$ for all horizontal 1-cells $N$ and $M$ of $\lC$}
 \end{enumerate}

### 2020-11-09 cospans.tex
lots of small improvements

@@
 
-\author{John\ C.\ Baez$^{*,\bullet}$, Kenny Courser$^*$, and Christina Vasilakopoulou$^\square$}
-\address{$^*$Department of Mathematics, University of California, Riverside CA, USA 92521}
-\address{$^\bullet$Centre for Quantum Technologies, National University of Singapore, Singapore 117543}
-\address{$^\square$Department of Mathematics, University of Patras, Greece 265 04}
-\email{baez@ucr.edu, kcour001@ucr.edu, cvasilak@math.upatrs.gr}
+\author{John\ C.\ Baez$^{1,2}$, Kenny Courser$^1$, and Christina Vasilakopoulou$^3$}
+\address{$^1$Department of Mathematics, University of California, Riverside CA, USA 92521}
+\address{$^2$Centre for Quantum Technologies, National University of Singapore, Singapore 117543}
+\address{$^3$Department of Mathematics, University of Patras, Greece 265 04}
+\email{baez@math.ucr.edu, kcour001@ucr.edu, cvasilak@math.upatrs.gr}
 
@@
 
-Our approach is to instead view the functor $F$ as a pseudofunctor $F \maps \textrm{A} \to \mathbf{Cat}$ and take advantage of the 2-categorical structure of $\mathbf{Cat}$.
+Our approach is to instead view the functor $F$ as a pseudofunctor $F \maps \textrm{A} \to \Cat$ and take advantage of the 2-categorical structure of $\Cat$.
 Given an object $a \in \mathsf{A}$, this then allows us to view $F(a)$ not as a \emph{set} of decorations on the object $a$ but as a \emph{category} of decorations on the object $a$.
@@
 In this section we build the symmetric monoidal double category $F \mathbb{C}$sp mentioned in the introduction.
-Then we obtain an underlying symmetric monoidal bicategory $F \mathbf{Csp}$ using a result of Shulman \cite{Shul} and then finally decategorify the obtained symmetric monoidal bicategory to obtain a symmetric monoidal category $F$Csp which is a generalization of Fong's original decorated cospan category \cite{Fong}.
+Then we obtain an underlying symmetric monoidal bicategory $F \mathbf{Csp}$ using a result of Shulman \cite{Shul} and finally decategorify this to obtain a symmetric monoidal category $F\mathsf{Csp}$ which is a generalization of Fong's original decorated cospan category \cite{Fong}.
 The definition of a lax monoidal pseudofunctor is recalled in \cref{sec:2cats}, and the basics of double categories are recalled in \cref{sec:doublecats}.
@@
 \begin{thm}\label{thm:decoratedcospans}
-Let $\mathsf{A}$ be a category with finite colimits and $F \maps \mathsf{A} \to \mathbf{Cat}$ a lax monoidal pseudofunctor. Then there exists a (pseudo) double category $F\mathbb{C}$sp which has:
+Let $\mathsf{A}$ be a category with finite colimits and $F \maps \mathsf{A} \to \Cat$ a lax monoidal pseudofunctor. Then there exists a (pseudo) double category $F\mathbb{C}$sp which has:
 \begin{enumerate}
@@
 \]
-where $!_a \in F(a)$ is the trivial decoration on $a$ given by the composite of the unique map $F(!) \maps F(0) \to F(a)$ and the morphism $\phi \maps 1 \to F(0)$  which comes from the structure of the lax monoidal pseudofunctor $F \maps \mathsf{A} \to \mathbf{Cat}$.
+where $!_a \in F(a)$ is the trivial decoration on $a$ given by the composite of the unique map $F(!) \maps F(0) \to F(a)$ and the morphism $\phi \maps 1 \to F(0)$  which comes from the structure of the lax monoidal pseudofunctor $F \maps \mathsf{A} \to \Cat$.
 For morphisms, the structure functor $U$ is defined as:
@@
 $$1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{x \times y} F(m) \times F(n) \xrightarrow{\phi_{m,n}} F(m+n) \xrightarrow{F(\psi)} F(m+_{b}n)$$
-where $\psi \maps m + n \to m+_{b} n$ is the natural map from the coproduct to the pushout and $\phi_{m,n} \maps F(m) \times F(n) \to F(m+n)$ is the natural transformation coming from the structure of the lax monoidal pseudofunctor $F \maps \mathsf{A} \to \mathbf{Cat}$.
+where $\psi \maps m + n \to m+_{b} n$ is the natural map from the coproduct to the pushout and $\phi_{m,n} \maps F(m) \times F(n) \to F(m+n)$ is the natural transformation coming from the structure of the lax monoidal pseudofunctor $F \maps \mathsf{A} \to \Cat$.
 Denoting the first and second of these horizontal 1-cells as $M$ and $N$, respectively, the source and target structure functors satisfy the equations $S(N \odot M)=S(M)$ and $T(N \odot M)=T(N)$.
@@
 \]
-These two 2-morphisms $\iota_\alpha$ and $\iota_\beta$ are two 2-morphisms in the monoidal 2-category $(\mathbf{Cat},\times,1)$ and so we can tensor them which results in:
+These two 2-morphisms $\iota_\alpha$ and $\iota_\beta$ are two 2-morphisms in the monoidal 2-category $(\Cat,\times,1)$ and so we can tensor them which results in:
 \[
@@
 As is usual concerning the interchange law of double categories of this nature, only the `interior' of the two composites appears different, but the two morphisms $(h_1^\prime +_{g^\prime} h_2^\prime)(h_1 +_g h_2) \maps m+_{b} n \to m'' +_{b''} n''$ and $(h_1^\prime h_1) +_{g^\prime g} (h_2^\prime h_2) \maps m+_{b} n \to m'' +_{b''}n''$ are the same universal map realized in two different ways.
-The two morphisms of decorations $\iota_{(\alpha^\prime \odot \beta^\prime)(\alpha \odot \beta)}$ and $\iota_{(\alpha^\prime \alpha) \odot (\beta^\prime \beta)}$ are obtained as two different compositions of four 2-morphisms in $\mathbf{Cat}$, namely horizontally then vertically and vertically then horizontally.
-As $\mathbf{Cat}$ is a 2-category, the interchange law for these 2-morphisms already holds, and as a result, the morphisms $$\iota_{(\alpha' \odot \beta')(\alpha \odot \beta)} \maps F((h_1^\prime +_{g^\prime} h_2^\prime)(h_1 +_g h_2))(x \odot y) \to x'' \odot y''$$ and $$\iota_{(\alpha^\prime \alpha)\odot(\beta^\prime \beta)} \maps F((h_1^\prime h_1)+_{g^\prime g} (h_2^\prime h_2))(x \odot y) \to x'' \odot y''$$ are also the same.
+The two morphisms of decorations $\iota_{(\alpha^\prime \odot \beta^\prime)(\alpha \odot \beta)}$ and $\iota_{(\alpha^\prime \alpha) \odot (\beta^\prime \beta)}$ are obtained as two different compositions of four 2-morphisms in $\Cat$, namely horizontally then vertically and vertically then horizontally.
+As $\Cat$ is a 2-category, the interchange law for these 2-morphisms already holds, and as a result, the morphisms $$\iota_{(\alpha' \odot \beta')(\alpha \odot \beta)} \maps F((h_1^\prime +_{g^\prime} h_2^\prime)(h_1 +_g h_2))(x \odot y) \to x'' \odot y''$$ and $$\iota_{(\alpha^\prime \alpha)\odot(\beta^\prime \beta)} \maps F((h_1^\prime h_1)+_{g^\prime g} (h_2^\prime h_2))(x \odot y) \to x'' \odot y''$$ are also the same.
 Thus the interchange law for 2-morphisms holds and $F\mathbb{C}$sp is a double category.
@@
 \begin{thm}\label{DC}
-Let $\mathsf{A}$ be a category with finite colimits and $F \maps \mathsf{A} \to \mathbf{Cat}$ a symmetric lax monoidal pseudofunctor. Then the double category $F\mathbb{C}$sp is symmetric monoidal.
+Let $\mathsf{A}$ be a category with finite colimits and $F \maps \mathsf{A} \to \Cat$ a symmetric lax monoidal pseudofunctor. Then the double category $F\mathbb{C}$sp is symmetric monoidal.
 \end{thm}
@@
 \]
-where $0$ is the monoidal unit of $\mathsf{A}$ and $!_0 \maps 1 \to F(0)$ is the morphism which is part of the structure of the symmetric lax monoidal pseudofunctor $F \maps \mathsf{A} \to \mathbf{Cat}$.
+where $0$ is the monoidal unit of $\mathsf{A}$ and $!_0 \maps 1 \to F(0)$ is the morphism which is part of the structure of the symmetric lax monoidal pseudofunctor $F \maps \mathsf{A} \to \Cat$.
 Tensoring an object with the monoidal unit, say, on the left:
@@
 \]
-since $$F(aa)(((x_1+x_2)+x_3)+x_4)=F((1 \otimes a)a(a \otimes 1))(((x_1+x_2)+x_3)+x_4)$$ as the corresponding pentagon in the symmetric monoidal category $(\mathsf{A},+,0)$ commutes, and then appliying the pseudofunctor $F$ to said pentagon yields a commutative pentagon in $\mathbf{Cat}$.
+since $$F(aa)(((x_1+x_2)+x_3)+x_4)=F((1 \otimes a)a(a \otimes 1))(((x_1+x_2)+x_3)+x_4)$$ as the corresponding pentagon in the symmetric monoidal category $(\mathsf{A},+,0)$ commutes, and then appliying the pseudofunctor $F$ to said pentagon yields a commutative pentagon in $\Cat$.
 
@@
 \]
-since $$F(\rho \otimes 1)((x_1+0)+x_2)=F((1 \otimes \lambda)a)((x_1+0)+x_2)$$ as the corresponding triangle in the symmetric monoidal category $(\mathsf{A},+,0)$ commutes and applying the pseudofunctor $F$ to this commutative triangle results in a commutative triangle in $\mathbf{Cat}$.
+since $$F(\rho \otimes 1)((x_1+0)+x_2)=F((1 \otimes \lambda)a)((x_1+0)+x_2)$$ as the corresponding triangle in the symmetric monoidal category $(\mathsf{A},+,0)$ commutes and applying the pseudofunctor $F$ to this commutative triangle results in a commutative triangle in $\Cat$.
 
@@
 since $$F(a(\chi \otimes 1)\chi)(((x_1+y_1)+z_1) \odot ((x_2+y_2)+z_2)) = F((1 \otimes \chi) \chi (a \odot a))(((x_1+y_1)+z_1) \odot ((x_2+y_2)+z_2))$$
-as the above underlying diagram of maps of cospans commutes and then applying the pseudofunctor $F$ yields a commutative diagram in $\mathbf{Cat}$.
+as the above underlying diagram of maps of cospans commutes and then applying the pseudofunctor $F$ yields a commutative diagram in $\Cat$.
 
@@
 since $$F(\chi \beta)((x_1 \odot x_2)+(y_1 \odot y_2)) = F((\beta \odot \beta)\chi)((x_1 \odot x_2)+(y_1 \odot y_2))$$
-as the above underlying diagram of maps of cospans commutes and then applying the pseudofunctor $F$ to this diagram yields a commutative diagram in $\mathbf{Cat}$.
+as the above underlying diagram of maps of cospans commutes and then applying the pseudofunctor $F$ to this diagram yields a commutative diagram in $\Cat$.
 The other diagrams are shown to commute similarly.
@@
 
-\begin{thm}[Shulman]\label{Shul}
+\begin{lem}[Shulman]\label{Shul}
 Let $\mathbb{X}$ be an isofibrant symmetric monoidal pseudo double category. Then the horizontal bicategory $H(\mathbb{X})$ of $\mathbb{X}$ is a symmetric monoidal bicategory which has:
@@
 \end{enumerate}
-\end{thm}
-
-\begin{cor}
-Let $(\mathsf{C},+,0)$ be a category with finite colimts and $F \maps \mathsf{C} \to \mathbf{Cat}$ a symmetric lax monoidal pseudofunctor.
+\end{lem}
+
+\begin{thm}
+Let $\A$ be a category with finite colimits and $F \maps (\A, +) \to \Cat$ a symmetric lax monoidal pseudofunctor.
 Then there exists a symmetric monoidal bicategory $F \mathbf{Csp} \mapseqq H(F\mathbb{C}\textnormal{sp})$ which has:
@@
 \end{enumerate}
-\end{cor}
+\end{thm}
 
 \begin{proof}
-This follows immediately by Shulman's Theorem \ref{Shul} above applied to the fibrant symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$.
+This follows immediately by applying \cref{Shul} to the fibrant symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$.
 \end{proof}
@@
 \begin{cor}
-Given a symmetric lax monoidal pseudofunctor $F \maps \mathsf{A} \to \mathbf{Cat}$ where $\mathsf{A}$ is a category with finite colimits and whose monoidal structure is given by binary coproducts, there exists a symmetric monoidal category $F\textnormal{Csp} \mapseqq D(F\mathbf{Csp})$ which has:
+Let $\A$ be a category with finite colimits and $F \maps (\A, +) \to \Cat$ a symmetric lax monoidal pseudofunctor.  Thenthere exists a symmetric monoidal category $F\textnormal{Csp}$ which has:
 \begin{enumerate}
@@
 
-%Let $F \maps \mathsf{A} \to \mathbf{Cat}$ be a symmetric lax monoidal pseudofunctor.
+%Let $F \maps \mathsf{A} \to \Cat$ be a symmetric lax monoidal pseudofunctor.
 Then by Theorem \ref{DC} of the previous section, we get a symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$.
@@
 
-Regarding maps between symmetric monoidal double categories, consider another symmetric lax monoidal pseudofunctor $F^\prime \maps \mathsf{A^\prime} \to \mathbf{Cat}$%, we can obtain another symmetric monoidal double category $F^\prime \mathbb{C}\textnormal{sp}$.
+Regarding maps between symmetric monoidal double categories, consider another symmetric lax monoidal pseudofunctor $F^\prime \maps \mathsf{A^\prime} \to \Cat$%, we can obtain another symmetric monoidal double category $F^\prime \mathbb{C}\textnormal{sp}$.
 a morphism from $F\mathbb{C}\textnormal{sp}$ to $F^\prime \mathbb{C}\textnormal{sp}$ will then be a double functor $\mathbb{H} \maps F\mathbb{C}\textnormal{sp} \to F' \mathbb{C}\textnormal{sp}$ whose object component is given by a finite colimit preserving functor $\mathbb{H}_0 = H \maps \mathsf{A} \to \mathsf{A^\prime}$ and whose arrow component is given by a functor $\mathbb{H}_1$ defined on horizontal 1-cells by:
@@
 \]
-where $E \maps \mathbf{Cat} \to \mathbf{Cat}$ is a symmetric lax monoidal pseudofuctor such that the following diagram commutes up to isomorphism $\theta \maps EF \Rightarrow F'H$:
+where $E \maps \Cat \to \Cat$ is a symmetric lax monoidal pseudofuctor such that the following diagram commutes up to isomorphism $\theta \maps EF \Rightarrow F'H$:
 \[
@@
 \node (A) at (0,0) {$\mathsf{A}$};
-\node (B) at (1,0) {$\mathbf{Cat}$};
+\node (B) at (1,0) {$\Cat$};
 \node (C) at (0,-1) {$\mathsf{A^\prime}$};
-\node (D) at (1,-1) {$\mathbf{Cat}$};
+\node (D) at (1,-1) {$\Cat$};
 \node (E) at (0.5,-0.5) {$\Swarrow \theta$};
@@
 \begin{comment}
-Recall that we can think of the object $d \in F(c)$ as a morphism $d \maps 1 \to F(c)$ and the functor $\iota \maps F(h)(d) \to d^\prime$ of $F(c^\prime)$ as a natural transformation  in $\mathbf{Cat}$:
+Recall that we can think of the object $d \in F(c)$ as a morphism $d \maps 1 \to F(c)$ and the functor $\iota \maps F(h)(d) \to d^\prime$ of $F(c^\prime)$ as a natural transformation  in $\Cat$:
 \[
@@
 \]
-Applying the symmetric lax monoidal pseudofunctor $E \maps \mathbf{Cat} \to \mathbf{Cat}$ to this diagram yields:
+Applying the symmetric lax monoidal pseudofunctor $E \maps \Cat \to \Cat$ to this diagram yields:
 \[
@@
 \begin{thm}
-Given two finitely cocomplete categories $\mathsf{A}$ and $\mathsf{A}'$, two symmetric lax monoidal pseudofunctors $F \maps \mathsf{A} \to \mathbf{Cat}$ and $F' \maps \mathsf{A}' \to \mathbf{Cat}$, a finite colimit preserving functor $H \maps \mathsf{A} \to \mathsf{A}'$, a symmetric lax monoidal pseudofunctor $E \maps \mathbf{Cat} \to \mathbf{Cat}$ and a 2-isomorphism $\theta \maps EF \Rightarrow F^\prime H$ as in the following diagram, the triple $(H,E,\theta)$ induces a symmetric monoidal (strong) double functor $\mathbb{H} \maps F\mathbb{C}\textnormal{sp} \to F'\mathbb{C}\textnormal{sp}$ as defined above.
+Given two finitely cocomplete categories $\mathsf{A}$ and $\mathsf{A}'$, two symmetric lax monoidal pseudofunctors $F \maps \mathsf{A} \to \Cat$ and $F' \maps \mathsf{A}' \to \Cat$, a finite colimit preserving functor $H \maps \mathsf{A} \to \mathsf{A}'$, a symmetric lax monoidal pseudofunctor $E \maps \Cat \to \Cat$ and a 2-isomorphism $\theta \maps EF \Rightarrow F^\prime H$ as in the following diagram, the triple $(H,E,\theta)$ induces a symmetric monoidal (strong) double functor $\mathbb{H} \maps F\mathbb{C}\textnormal{sp} \to F'\mathbb{C}\textnormal{sp}$ as defined above.
 \[
@@
 \]
-together with a morphism $\iota \maps F(R(\alpha))(x) \to x^\prime$ in $F(R(x^\prime)) \subseteq \mathrm{X}$ which comes from the Grothendieck construction of the pseudofunctor $F \maps \mathsf{A} \to \mathbf{Cat}$.
+together with a morphism $\iota \maps F(R(\alpha))(x) \to x^\prime$ in $F(R(x^\prime)) \subseteq \mathrm{X}$ which comes from the Grothendieck construction of the pseudofunctor $F \maps \mathsf{A} \to \Cat$.
 That $\mathbb{E}_0$ is a functor is clear.
@@
 \]
-where $!_{1_{\mathsf{A}}} = \phi \maps 1 \to F(1_\mathsf{A})$ is the trivial decoration which comes from the structure of the symmetric lax monoidal pseudofunctor $F \maps \mathsf{A} \to \mathbf{Cat}$.
+where $!_{1_{\mathsf{A}}} = \phi \maps 1 \to F(1_\mathsf{A})$ is the trivial decoration which comes from the structure of the symmetric lax monoidal pseudofunctor $F \maps \mathsf{A} \to \Cat$.
 The horizontal 1-cell $U_{1_{_L \mathbb{C}\textnormal{sp}(\mathsf{X})}}$ is given by:
@@
 Another result of Shulman \cite{Shul2} is the following:
-\begin{prop}[Shulman, Prop. B.3]
+\begin{lem}[Shulman, Prop.\ B.3]
 An equivalence of fibrant double categories induces a biequivalence of horizontal bicategories.
-\end{prop}
+\end{lem}
+
 \begin{cor}
@@
 \end{enumerate}
-We can also obtain a similar double category using decorated cospans: define a pseudofunctor $F \maps \mathsf{FinSet} \to \mathbf{Cat}$ that assigns to a finite set $V$ the category of all $k$-graph structures on the finite set $V$ and to a function $f \maps V \to V^\prime$ the corresponding functor $F(f) \maps F(V) \to F(V^\prime)$ between decoration categories.
-Both categories $\mathsf{FinSet}$ and $\mathbf{Cat}$ are symmetric monoidal and the pseudofunctor $F \maps \mathsf{FinSet} \to \mathbf{Cat}$ is symmetric lax monoidal, as given a $k$-graph structure on a finite set $V_1$ denoted by an element $K_1 \in F(V_1)$ and a $k$-graph structure on a finite set $V_2$ denoted by an element $K_2 \in F(V_2)$, we can consider the $k$-graph structures simultaneously as a single graph structure $\phi_{V_1,V_2}(K_1,K_2)$ on the finite set $V_1+V_2$.
+We can also obtain a similar double category using decorated cospans: define a pseudofunctor $F \maps \mathsf{FinSet} \to \Cat$ that assigns to a finite set $V$ the category of all $k$-graph structures on the finite set $V$ and to a function $f \maps V \to V^\prime$ the corresponding functor $F(f) \maps F(V) \to F(V^\prime)$ between decoration categories.
+Both categories $\mathsf{FinSet}$ and $\Cat$ are symmetric monoidal and the pseudofunctor $F \maps \mathsf{FinSet} \to \Cat$ is symmetric lax monoidal, as given a $k$-graph structure on a finite set $V_1$ denoted by an element $K_1 \in F(V_1)$ and a $k$-graph structure on a finite set $V_2$ denoted by an element $K_2 \in F(V_2)$, we can consider the $k$-graph structures simultaneously as a single graph structure $\phi_{V_1,V_2}(K_1,K_2)$ on the finite set $V_1+V_2$.
 Thus we get a family of natural transformations $$\phi_{V_1,V_2} \maps F(V_1) \times F(V_2) \to F(V_1+V_2)$$ as well as a morphism $\phi \maps 1_{\mathsf{Graph}_k} \to F(\emptyset)$ which together satisfy the coherence conditions of a monoidal functor.
@@
 This is done using a symmetric lax monoidal functor $F \maps \mathsf{FinSet} \to \mathsf{Set}$ which assigns to each finite set $N$ the (large) set of all Markov processes on $N$ as defined above.
-Viewing this functor $F$ as now a symmetric lax monoidal pseudofunctor $F \maps \mathsf{FinSet} \to \mathbf{Cat}$ that assigns to a finite set $N$ the \emph{category} $F(N)$ of all Markov processes on $N$, we then get by Theorem \ref{DC} a symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$ which has:
+Viewing this functor $F$ as now a symmetric lax monoidal pseudofunctor $F \maps \mathsf{FinSet} \to \Cat$ that assigns to a finite set $N$ the \emph{category} $F(N)$ of all Markov processes on $N$, we then get by Theorem \ref{DC} a symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$ which has:
 \begin{enumerate}
@@
 \end{enumerate}
-We can also obtain a similar double category using decorated cospans: define a pseudofunctor $F \maps \mathsf{Set} \to \mathbf{Cat}$ where given a set $s$, $F(s)$ is the category of all Petri net structures with $s$ as its set of species.
-This pseudofunctor $F$ is symmetric lax monoidal as both $(\mathsf{Set},+,\emptyset)$ and $(\mathbf{Cat},\times,1)$ are symmetric monoidal and given Petri nets $P \in F(s)$ and $P^\prime \in F(s^\prime)$, we can place them side by side and consider them together as a single Petri net $P+P^\prime \in F(s+s^\prime)$ with set of species $s+s^\prime$, and thus we have natural transformations $\phi_{s,s^\prime} \maps F(s) \times F(s^\prime) \to F(s+s^\prime)$ for any two sets $s$ and $s^\prime$.
+We can also obtain a similar double category using decorated cospans: define a pseudofunctor $F \maps \mathsf{Set} \to \Cat$ where given a set $s$, $F(s)$ is the category of all Petri net structures with $s$ as its set of species.
+This pseudofunctor $F$ is symmetric lax monoidal as both $(\mathsf{Set},+,\emptyset)$ and $(\Cat,\times,1)$ are symmetric monoidal and given Petri nets $P \in F(s)$ and $P^\prime \in F(s^\prime)$, we can place them side by side and consider them together as a single Petri net $P+P^\prime \in F(s+s^\prime)$ with set of species $s+s^\prime$, and thus we have natural transformations $\phi_{s,s^\prime} \maps F(s) \times F(s^\prime) \to F(s+s^\prime)$ for any two sets $s$ and $s^\prime$.
 The other structure morphism between monoidal units $\phi \maps 1_{\mathsf{Petri}} \to F(\emptyset)$ is defined by the unique morphism from the empty Petri net with the empty set forits set of species to the only possible Petri net on the empty set, which is also the empty Petri net.
@@
 
-Let $\OpFib(\A)$ denote the 2-subcategory of the slice 2-category $\mathbf{Cat}/ \A$ of opfibrations over $\A$, functors that preserve cocartesian liftings and natural transformations with vertical components.
+Let $\OpFib(\A)$ denote the 2-subcategory of the slice 2-category $\Cat/ \A$ of opfibrations over $\A$, functors that preserve cocartesian liftings and natural transformations with vertical components.
 In fact, there is a 2-equivalence between opfibrations and pseudofunctors induced by the so-called \emph{Grothendieck construction}.
@@
 %\begin{defn}
-%Let $\mathbf{Cat}_{\textnormal{lax},\star}$ denote the \define{2-category of lax-pointed categories} which has:
+%Let $\Cat_{\textnormal{lax},\star}$ denote the \define{2-category of lax-pointed categories} which has:
 %\begin{enumerate}
@@
 %\begin{defn}
-%Given a pseudofunctor $F \maps \mathrm{A} \to \mathbf{Cat}$, the \define{Grothendieck construction of} $F$ is given by the `strict 2-pullback' of the following cospan:
+%Given a pseudofunctor $F \maps \mathrm{A} \to \Cat$, the \define{Grothendieck construction of} $F$ is given by the `strict 2-pullback' of the following cospan:
 % \[
@@
 %\node (A) at (0,0) {$\mathrm{A}$};
-%\node (B) at (1,-1) {$\mathbf{Cat}$};
-%\node (C) at (2,0) {$\mathbf{Cat}_{\textnormal{lax},\star}$};
+%\node (B) at (1,-1) {$\Cat$};
+%\node (C) at (2,0) {$\Cat_{\textnormal{lax},\star}$};
 %\path[->,font=\scriptsize,>=angle 90]
@@
 %\]
-%where $P \maps \mathbf{Cat}_{\textnormal{lax},\star} \to \mathbf{Cat}$ is the forgetful functor. 
+%where $P \maps \Cat_{\textnormal{lax},\star} \to \Cat$ is the forgetful functor. 
 \begin{defn}\label{def:GrothCat}
@@
 The above in fact provides the one direction of the following well-known equivalence.
-%gives rise to a 2-functor $[\A,\bicat{Cat}]_\pse\to \mathbf{Cat}/ \A$ which factors through the embedding $\OpFib(\A) \hookrightarrow \bicat{Cat} / \A$ as per the following theorem.
-%: $$\inta F \maps [ \mathrm{A}, \mathbf{Cat} ] \to \textnormal{Opfib}(\mathrm{A}) \hookrightarrow \mathbf{Cat} / \mathrm{A}.$$
+%gives rise to a 2-functor $[\A,\bicat{Cat}]_\pse\to \Cat/ \A$ which factors through the embedding $\OpFib(\A) \hookrightarrow \bicat{Cat} / \A$ as per the following theorem.
+%: $$\inta F \maps [ \mathrm{A}, \Cat ] \to \textnormal{Opfib}(\mathrm{A}) \hookrightarrow \Cat / \mathrm{A}.$$
 
@@
 The key difference between a `strict' double category and a pseudo double category is that in a pseudo double category, horizontal composition is associative and unital only up to natural isomorphism.
-Equivalently, as a double category can be viewed as a category internal to $\mathbf{Cat}$, we can view a pseudo double category as a category `weakly' internal to $\mathbf{Cat}$.
+Equivalently, as a double category can be viewed as a category internal to $\Cat$, we can view a pseudo double category as a category `weakly' internal to $\Cat$.
 We will sometimes omit the word pseudo and simply say double category.

### 2020-11-10 cospans.tex
typo fixed
decommented introduction

@@
 \section{Introduction}
-\begin{comment}
 Networks are playing an increasingly prominent role in our understanding of the world and as a result, methods of characterizing and studying networks have become evermore necessary.
@@
 Daniel Cicala, various others.
-\end{comment}
 
@@
 \begin{cor}
-Let $\A$ be a category with finite colimits and $F \maps (\A, +) \to \Cat$ a symmetric lax monoidal pseudofunctor.  Thenthere exists a symmetric monoidal category $F\textnormal{Csp}$ which has:
+Let $\A$ be a category with finite colimits and $F \maps (\A, +) \to \Cat$ a symmetric lax monoidal pseudofunctor.  Then there exists a symmetric monoidal category $F\textnormal{Csp}$ which has:
 \begin{enumerate}

### 2020-11-10 cospans.tex
started work on introduction, changed all \mathsf{A} to \A

@@
 This framework, which goes by the name of `structured cospans', utilizes double categories where the objects are seen as inputs and outputs, horizontal 1-cells are `open networks', and 2-morphisms are maps between open networks.
-In this setup a functor $L \maps \textsf{A} \to \textsf{X}$, which is typically a left adjoint, is used to replace the objects and vertical 1-morphisms of a given double category $\mathbb{X}$ with the objects and morphisms, respectively, of the category $\textsf{A}$.
+In this setup a functor $L \maps \A \to \textsf{X}$, which is typically a left adjoint, is used to replace the objects and vertical 1-morphisms of a given double category $\mathbb{X}$ with the objects and morphisms, respectively, of the category $\A$.
 Horizontal 1-cells are then cospans in $\textsf{X}$ of a particular form with 2-morphisms given by maps of these cospans.
 Fong has also developed a similar framework utilizing cospans to study open networks which goes by the name of `decorated cospans'.
-In this setup, a lax monoidal functor $F \maps \textsf{A} \to \textsf{Set}$ is used to `decorate' the apices of cospans in $\textsf{A}$ with elements of $\textsf{Set}$ giving the cospans extra structure.
+In this setup, a lax monoidal functor $F \maps \A \to \textsf{Set}$ is used to `decorate' the apices of cospans in $\A$ with elements of $\textsf{Set}$ giving the cospans extra structure.
 Using a slight variation of Fong's framework, we prove that these two frameworks are equivalent in the situation where a left adjoint can be obtained from a lax monoidal pseudofunctor using a well known construction of Grothendieck.
@@
 \section{Introduction}
-Networks are playing an increasingly prominent role in our understanding of the world and as a result, methods of characterizing and studying networks have become evermore necessary.
-Applied category theory provides such an avenue and much work has been done towards this effort  \cite{BC,BCR,BF,BFP,BP,Cour,Fong,JM,LS,Yass}.
-One of the more recent frameworks developed that is suitable for studying networks is Fong's `decorated cospans' \cite{Fong}.
-A $\textbf{cospan}$ in any category is a diagram of the form:
+
+An `open system' is any sort of system that can interact with the outside world.  Open systems
+are nicely modeled using cospans, which are diagrams of this form:
 \[
@@
 \]
-We call $b$ the $\textbf{apex}$ of the cospan and $a_1$ and $a_2$ the $\textbf{feet}$ of the cospan.
-The morphisms $i$ and $o$ are called the $\textbf{legs}$.
-Cospans are ideal for realizing networks and more generally `open' systems where here open means that each system or network comes with prescribed inputs and outputs which are represented by the feet of the cospan $a$ and $b$, respectively.
-Two open systems viewed as cospans such that the outputs of the first and the inputs of the second coincide can then naturally be composed via pushout to obtain an open system whose inputs are that of the first and outputs are that of the second.
-For example, we can compose the above cospan with the following:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a_2$};
-\node (B) at (1,1) {$b^\prime$};
-\node (C) at (2,0) {$a_3$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i^\prime$} (B)
-(C) edge node[above]{$o^\prime$} (B);
-\end{tikzpicture}
-\]
-to obtain a new cospan whose left foot is the left foot of the first, whose right foot is the right foot of the second, and whose apex and legs are given by the pushout.
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a_1$};
-\node (B) at (1,1) {$b$};
-\node (C) at (2,0) {$a_2$};
-\node (D) at (3,1) {$b^\prime$};
-\node (E) at (4,0) {$a_3$};
-\node (F) at (2,2) {$b+_{a_2} b^\prime$};
-\node (G) at (2,1) {$b+b^\prime$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i$} (B)
-(C) edge node[above]{$o$} (B)
-(C) edge node[above]{$i^\prime$} (D)
-(E) edge node[above]{$o^\prime$} (D)
-(B) edge node[left]{$\psi j_b$} (F)
-(D) edge node[right]{$\psi j_{b^\prime}$} (F)
-(B) edge node[above]{$j_b$} (G)
-(D) edge node[above]{$j_{b^\prime}$} (G)
-(G) edge node [left] {$\psi$} (F);
-\end{tikzpicture}
-\]
-
-In Fong's theory of decorated cospans, given a category $\textsf{A}$ with finite colmits, a symmetric lax monoidal functor $F \maps (\textsf{A},+,0) \to (\textsf{Set},\times,1)$ is used to `decorate' the apex of a cospan in $\textsf{A}$ with an element of the image of its apex under the functor $F$.
-In the case of the first cospan above, an element of the image of the apex under the functor $F$ is given by a morphism $d \maps 1 \to F(b)$, and we call $d$ a \textbf{decoration} on $b$.
-Here, $1$ is any terminal object in $\mathsf{Set}$, $F(b)$ is the collection of all $F$-decorations on the object $b$ and the morphism $d$ is selecting a particular one.
+We call $b$ the \define{apex} of the cospan, $a_1$ and $a_2$ its \define{feet}, and $i$ and $o$ its \define{legs}.   The feet of a cospan describe `interfaces' of the corresponding open system, and
+open systems modeled as cospans can composed via pushout.
+However, we often want the system itself---the apex---to have more structure than its interfaces.
+This led Fong to develop a theory of `decorated' cospans \cite{Fong}.
+
+Given a category $\A$ with finite colimits, a symmetric lax monoidal functor $F \maps (\A,+,0) \to (\textsf{Set},\times,1)$ can be used to `decorate' the apex of a cospan in $\A$ with some extra data: an element of the image of its apex under the functor $F$.
+In the case of the cospan above, this is an element $d \in F(b)$, which we call a \textbf{decoration} on $b$.
 Thus a decorated cospan is given by a pair:
@@
  $$1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{d_1 \times d_2} F(b) \times F(b^\prime) \xrightarrow{\phi_{b,b^\prime}} F(b+ b^\prime) \xrightarrow{F(j_{b,b^\prime})} F(b+_{a_2} b^\prime).$$
-From this symmetric lax monoidal functor $F \maps \textsf{A} \to \mathsf{Set}$, Fong then constructs a symmetric monoidal category $F\textnormal{Cospan}(\mathsf{A})$ which has:
+From this symmetric lax monoidal functor $F \maps \A \to \mathsf{Set}$, Fong then constructs a symmetric monoidal category $F\textnormal{Cospan}(\mathsf{A})$ which has:
 \begin{enumerate}
@@
 
+\subsection*{Conventions}
+
+%Changed Defn. to Definition
+In this paper, `double category' means `pseudo double category', as in Definition \ref{defn:double_category}.   Following Shulman \cite{Shul2010}, vertical composition 
+in our double categories is strictly associative, while horizontal composition need not be.
+We use sans-serif font like $\C$ for categories, boldface like $\B$ for bicategories or
+2-categories, and blackboard bold like $\lD$ for double categories.   We also use blackboard
+bold for weak category objects in any 2-category.
+For double categories with names having more than one letter, like $\lCsp(\X)$, only the first letter is in blackboard bold.
+A double category $\lD$ has a category of objects and a category of arrows, and we call these $\lD_0$ and $\lD_1$ despite the fact that they are categories.
+
 \subsection*{Acknowledgements}
-Daniel Cicala, various others.
+Daniel Cicala, Brendan Fong...
 

### 2020-11-10 cospans.tex
worked on intro, changed all \mathsf{X} to \X

@@
 \]
-We call $b$ the \define{apex} of the cospan, $a_1$ and $a_2$ its \define{feet}, and $i$ and $o$ its \define{legs}.   The feet of a cospan describe `interfaces' of the corresponding open system, and
-open systems modeled as cospans can composed via pushout.
+We call $b$ the \define{apex}, $a_1$ and $a_2$ the \define{feet}, and $i$ and $o$ the \define{legs}.
+The feet describe `interfaces' of the corresponding open system.
 However, we often want the system itself---the apex---to have more structure than its interfaces.
@@
 \begin{thm}\label{SC}
-Given a category $\mathsf{X}$ with finite colimits and a category $\mathsf{A}$ with finite coproducts and a finite coproduct preserving functor $L \maps \mathsf{A} \to \mathsf{X}$ with $\mathsf{A}$ and $\mathsf{X}$, there exists a symmetric monoidal double category $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$ which has:
+Given a category $\X$ with finite colimits and a category $\mathsf{A}$ with finite coproducts and a finite coproduct preserving functor $L \maps \mathsf{A} \to \X$ with $\mathsf{A}$ and $\X$, there exists a symmetric monoidal double category $_L \mathbb{C}\textnormal{sp}(\X)$ which has:
 \begin{itemize}
@@
 \item{vertical 1-morphisms given by morphisms of $\mathsf{A}$,}
-\item{horizontal 1-cells $a\tickar b$ given by cospans of $\mathsf{X}$ of the form:
+\item{horizontal 1-cells $a\tickar b$ given by cospans of $\X$ of the form:
 \begin{equation}\label{eq:structuredcospan}
@@
 \end{equation}}
-\item 2-morphisms given by maps of cospans of $\mathsf{X}$ of the form:
+\item 2-morphisms given by maps of cospans of $\X$ of the form:
 \begin{equation}\label{eq:2cellsStrCsp}
@@
 \end{itemize}
-Composition of horizontal 1-cells and 2-morphisms is given by pushouts in $\mathsf{X}$ and tensoring of objects is under binary coproducts in $\mathsf{A}$.
+Composition of horizontal 1-cells and 2-morphisms is given by pushouts in $\X$ and tensoring of objects is under binary coproducts in $\mathsf{A}$.
 \end{thm}
@@
 \begin{comment}
-which is a cospan in $\mathsf{X}$ of the form:
+which is a cospan in $\X$ of the form:
 \[
@@
 \]
-where $R\maps \mathsf{X} \to \mathsf{A}$ is the right adjoint to the functor $L \maps \mathsf{A} \to \mathsf{X}$ and $\eta \maps 1_{\mathsf{A}} \to RL$ is the unit of the adjunction $L \dashv R$ which is an isomorphism since $L$ is fully faithful.
-\textbf{Hopefully...actually, it's a `lari'!} Similarly, the image of a 2-morphism $\alpha \maps M \to N$ in $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$:
+where $R\maps \X \to \mathsf{A}$ is the right adjoint to the functor $L \maps \mathsf{A} \to \X$ and $\eta \maps 1_{\mathsf{A}} \to RL$ is the unit of the adjunction $L \dashv R$ which is an isomorphism since $L$ is fully faithful.
+\textbf{Hopefully...actually, it's a `lari'!} Similarly, the image of a 2-morphism $\alpha \maps M \to N$ in $_L \mathbb{C}\textnormal{sp}(\X)$:
 \[
@@
 That $\mathbb{E}_0$ is a functor is clear.
-For $\mathbb{E}_1$, given two vertically composable 2-morphisms $M$ and $M'$ in $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$,
+For $\mathbb{E}_1$, given two vertically composable 2-morphisms $M$ and $M'$ in $_L \mathbb{C}\textnormal{sp}(\X)$,
 \[
@@
 \]
-we can find a 2-isomorphism in $F\mathbb{C}\textnormal{sp}$ whose codomain is the above horizontal 1-cell and whose domain is the image of the following horizontal 1-cell in $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$:
+we can find a 2-isomorphism in $F\mathbb{C}\textnormal{sp}$ whose codomain is the above horizontal 1-cell and whose domain is the image of the following horizontal 1-cell in $_L \mathbb{C}\textnormal{sp}(\X)$:
 \[
@@
 
-To show that the double functor $\mathbb{E}$ is fully faithful, we need to show that the map  $$\mathbb{E}_1 \maps _f { _L \mathbb{C}\textnormal{sp}(\mathsf{X})}_g(M,N) \to {_{\mathbb{E}(f)} {F\mathbb{C}\textnormal{sp}}_{\mathbb{E}(g)}}(\mathbb{E}(M),\mathbb{E}(N))$$ is bijective for arbitrary vertical 1-morphisms $f$ and $g$ and horizontal 1-cells $M$ and $N$ of $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$.
-Consider a 2-morphism in $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$ with horizontal source and target $M$ and $N$, respectively and vertical source and target $f$ and $g$, respectively:
+To show that the double functor $\mathbb{E}$ is fully faithful, we need to show that the map  $$\mathbb{E}_1 \maps _f { _L \mathbb{C}\textnormal{sp}(\X)}_g(M,N) \to {_{\mathbb{E}(f)} {F\mathbb{C}\textnormal{sp}}_{\mathbb{E}(g)}}(\mathbb{E}(M),\mathbb{E}(N))$$ is bijective for arbitrary vertical 1-morphisms $f$ and $g$ and horizontal 1-cells $M$ and $N$ of $_L \mathbb{C}\textnormal{sp}(\X)$.
+Consider a 2-morphism in $_L \mathbb{C}\textnormal{sp}(\X)$ with horizontal source and target $M$ and $N$, respectively and vertical source and target $f$ and $g$, respectively:
 \[
@@
 \]
-Thus the set $$_f { _L \mathbb{C}\textnormal{sp}(\mathsf{X})}_g(M,N)$$ consists of triples $$(f,\alpha,g)$$ rendering the above diagram commutative where $f$ and $g$ are morphisms of $\mathsf{A}$ and $\alpha$ is a morphism of $\mathsf{X}$.
+Thus the set $$_f { _L \mathbb{C}\textnormal{sp}(\X)}_g(M,N)$$ consists of triples $$(f,\alpha,g)$$ rendering the above diagram commutative where $f$ and $g$ are morphisms of $\mathsf{A}$ and $\alpha$ is a morphism of $\X$.
 The image of the above 2-morphism under the double functor $\mathbb{E}$ is given by:
@@
 Thus the set $$_{\mathbb{E}(f)} {F\mathbb{C}\textnormal{sp}}_{\mathbb{E}(g)}(\mathbb{E}(M),\mathbb{E}(N))$$ consists of 4-tuples $$(f,R(\alpha),g,\iota)$$ rendering the above diagram commutative and where $f,g$ and $R(\alpha)$ are morphisms of $\mathsf{A}$ and $\iota$ is a morphism in $F(R(x'))$.
-The morphisms $R(\alpha) \maps R(x) \to R(x^\prime)$ and $\iota \maps F(R(\alpha))(x) \to x^\prime$ together determine the morphism $\alpha \maps x \to x^\prime$ in $\mathrm{X}$ and conversely; given two objects $x=(c,x \in F(c))$ and $x^\prime=(c^\prime,x^\prime \in F(c^\prime))$ of $\mathsf{X}=\inta{F}$, a morphism from $\alpha \maps x \to x^\prime$ is a pair $$(h \maps c \to c^\prime, \iota \maps F(h)(x) \to x^\prime)$$ where $h \maps c \to c^\prime$ is given by $R(\alpha) \maps R(x) \to R(x^\prime)$.
+The morphisms $R(\alpha) \maps R(x) \to R(x^\prime)$ and $\iota \maps F(R(\alpha))(x) \to x^\prime$ together determine the morphism $\alpha \maps x \to x^\prime$ in $\mathrm{X}$ and conversely; given two objects $x=(c,x \in F(c))$ and $x^\prime=(c^\prime,x^\prime \in F(c^\prime))$ of $\X=\inta{F}$, a morphism from $\alpha \maps x \to x^\prime$ is a pair $$(h \maps c \to c^\prime, \iota \maps F(h)(x) \to x^\prime)$$ where $h \maps c \to c^\prime$ is given by $R(\alpha) \maps R(x) \to R(x^\prime)$.
 This shows that $\mathbb{E}$ is fully faithful.
@@
 
-Next, given composable horizontal 1-cells $M$ and $N$ in $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$:
+Next, given composable horizontal 1-cells $M$ and $N$ in $_L \mathbb{C}\textnormal{sp}(\X)$:
 \[
@@
 together with a morphism of decorations which is obtained as follows.
-First, as $R \maps \mathsf{X} \to \mathsf{A}$ preserves finite colimits, we have an isomorphism $$\kappa \maps R(x) +_{R(L(c_2))} R(x^\prime) \to R(x+_{L(c_2)}x^\prime).$$ Also, since the left adjoint $L \maps \mathsf{A} \to \mathsf{X}$ is fully faithful, the unit of the adjunction $L \dashv R$ at the object $c_2$ gives an isomorphism $\eta_{c_2} \maps c_2 \to R(L(c_2))$ which results in an isomorphism $$j_{\eta_{c_2}} \maps R(x) +_{c_2} R(x^\prime) \to R(x) +_{R(L(c_2))} R(x^\prime).$$ Composing these two results in an isomorphism $$\sigma \mapseqq \kappa j_{\eta_{c_2}} \maps R(x) +_{c_2} R(x^\prime) \to R(x+_{L(c_2)}x^\prime).$$
+First, as $R \maps \X \to \mathsf{A}$ preserves finite colimits, we have an isomorphism $$\kappa \maps R(x) +_{R(L(c_2))} R(x^\prime) \to R(x+_{L(c_2)}x^\prime).$$ Also, since the left adjoint $L \maps \mathsf{A} \to \X$ is fully faithful, the unit of the adjunction $L \dashv R$ at the object $c_2$ gives an isomorphism $\eta_{c_2} \maps c_2 \to R(L(c_2))$ which results in an isomorphism $$j_{\eta_{c_2}} \maps R(x) +_{c_2} R(x^\prime) \to R(x) +_{R(L(c_2))} R(x^\prime).$$ Composing these two results in an isomorphism $$\sigma \mapseqq \kappa j_{\eta_{c_2}} \maps R(x) +_{c_2} R(x^\prime) \to R(x+_{L(c_2)}x^\prime).$$
 Next, to see that the above diagram commutes, it suffices to show that for the object $c_1 \in \mathrm{A}$, $$R(J)R(\zeta)R(i)\eta_{c_1}(c_1) = R(J \zeta i)\eta_{c_1}(c_1)  \stackrel{!}{=} \sigma j \psi R(i)\eta_{c_1}(c_1) = \kappa j_{\eta_{c_2}} \psi R(i) \eta_{c_1}(c_1).$$ This follows as $R(i) \eta_{c_1} \maps c_1 \to R(x)$ and the following diagram commutes:
@@
 
-Next, we show that if both double categories $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$ and $F\mathbb{C}\textnormal{sp}$ are symmetric monoidal, as they are if both $\mathsf{A}$ and $\mathsf{X}$ have finite colimits, then this equivalence of double categories $\mathbb{E} \maps _L \mathbb{C}\textnormal{sp}(\mathsf{X}) \to F\mathbb{C}\textnormal{sp}$ will be symmetric monoidal.
-First, note that we have an isomorphism $\epsilon \maps 1_{F\mathbb{C}\textnormal{sp}} \to \mathbb{E}(1_{_L \mathbb{C}\textnormal{sp}(\mathsf{X})})$ and natural isomorphisms $\mu_{c_1,c_2} \maps \mathbb{E}(c_1) \otimes \mathbb{E}(c_2) \to \mathbb{E}(c_1 \otimes c_2)$ for every pair of objects $c_1,c_2 \in {_L \mathbb{C} \textnormal{sp}(\mathsf{X})}$ both of which are given by identities since both double categories $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$ and $F\mathbb{C}\textnormal{sp}$ have $\mathsf{A}$ as their category of objects and $\mathbb{E}_0=\id_{\mathsf{A}}$.
+Next, we show that if both double categories $_L \mathbb{C}\textnormal{sp}(\X)$ and $F\mathbb{C}\textnormal{sp}$ are symmetric monoidal, as they are if both $\mathsf{A}$ and $\X$ have finite colimits, then this equivalence of double categories $\mathbb{E} \maps _L \mathbb{C}\textnormal{sp}(\X) \to F\mathbb{C}\textnormal{sp}$ will be symmetric monoidal.
+First, note that we have an isomorphism $\epsilon \maps 1_{F\mathbb{C}\textnormal{sp}} \to \mathbb{E}(1_{_L \mathbb{C}\textnormal{sp}(\X)})$ and natural isomorphisms $\mu_{c_1,c_2} \maps \mathbb{E}(c_1) \otimes \mathbb{E}(c_2) \to \mathbb{E}(c_1 \otimes c_2)$ for every pair of objects $c_1,c_2 \in {_L \mathbb{C} \textnormal{sp}(\X)}$ both of which are given by identities since both double categories $_L \mathbb{C}\textnormal{sp}(\X)$ and $F\mathbb{C}\textnormal{sp}$ have $\mathsf{A}$ as their category of objects and $\mathbb{E}_0=\id_{\mathsf{A}}$.
 The diagrams utilizing these maps that are required to commute do so trivially.
 
-For the arrow component $\mathbb{E}_1$, we have an isomorphism $\delta \maps U_{1_{F\mathbb{C}\textnormal{sp}}} \to \mathbb{E}(U_{1_{_L \mathbb{C}\textnormal{sp}(\mathsf{X})}})$ where the horizontal 1-cell $U_{1_{F\mathbb{C}\textnormal{sp}}}$ is given by:
+For the arrow component $\mathbb{E}_1$, we have an isomorphism $\delta \maps U_{1_{F\mathbb{C}\textnormal{sp}}} \to \mathbb{E}(U_{1_{_L \mathbb{C}\textnormal{sp}(\X)}})$ where the horizontal 1-cell $U_{1_{F\mathbb{C}\textnormal{sp}}}$ is given by:
 \[
@@
 where $!_{1_{\mathsf{A}}} = \phi \maps 1 \to F(1_\mathsf{A})$ is the trivial decoration which comes from the structure of the symmetric lax monoidal pseudofunctor $F \maps \mathsf{A} \to \Cat$.
-The horizontal 1-cell $U_{1_{_L \mathbb{C}\textnormal{sp}(\mathsf{X})}}$ is given by:
+The horizontal 1-cell $U_{1_{_L \mathbb{C}\textnormal{sp}(\X)}}$ is given by:
 \[
@@
 \]
-where here we make use of the fact that the left adjoint $L \maps (\mathsf{A},+,1_\mathsf{A}) \to (\mathsf{X},+,1_\mathsf{X})$ preserves all colimits and thus $L(1_\mathsf{A}) \cong 1_\mathsf{X}$.
-The horizontal 1-cell $\mathbb{E}(U_{1_{_L \mathbb{C} \textnormal{sp}(\mathsf{X})}})$ is then given by the pair:
+where here we make use of the fact that the left adjoint $L \maps (\mathsf{A},+,1_\mathsf{A}) \to (\X,+,1_\X)$ preserves all colimits and thus $L(1_\mathsf{A}) \cong 1_\X$.
+The horizontal 1-cell $\mathbb{E}(U_{1_{_L \mathbb{C} \textnormal{sp}(\X)}})$ is then given by the pair:
 \[
@@
 
-Given two horizontal 1-cells $M$ and $N$ of $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$:
+Given two horizontal 1-cells $M$ and $N$ of $_L \mathbb{C}\textnormal{sp}(\X)$:
 \[
@@
 \]
-where $\kappa$ is the isomorphism which comes from $R \maps \mathsf{X} \to \mathsf{A}$ preserving finite colimits.
+where $\kappa$ is the isomorphism which comes from $R \maps \X \to \mathsf{A}$ preserving finite colimits.
 
@@
 \begin{comment}
-To see this, let $M_1,M_2$ and $M_3$ be horizontal 1-cells in $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$ given by:
+To see this, let $M_1,M_2$ and $M_3$ be horizontal 1-cells in $_L \mathbb{C}\textnormal{sp}(\X)$ given by:
 \[
@@
 \node (A) at (0,0) {$1_{F\mathbb{C}\textnormal{sp}} \otimes \mathbb{E}(M_1)$};
-\node (B) at (3,0) {$\mathbb{E}(1_{ _L \mathbb{C}\textnormal{sp}(\mathsf{X})}) \otimes \mathbb{E}(M_1)$};
+\node (B) at (3,0) {$\mathbb{E}(1_{ _L \mathbb{C}\textnormal{sp}(\X)}) \otimes \mathbb{E}(M_1)$};
 \node (C) at (0,-1) {$\mathbb{E}(M_1)$};
-\node (D) at (3,-1) {$\mathbb{E}(1_{ _L \mathbb{C}\textnormal{sp}(\mathsf{X})} \otimes M_1)$};
+\node (D) at (3,-1) {$\mathbb{E}(1_{ _L \mathbb{C}\textnormal{sp}(\X)} \otimes M_1)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 		\begin{tikzpicture}
-			\node (d) at (7.5,0) {$\mathbb{E}(1_{ _L \mathbb{C}\textnormal{sp}(\mathsf{X})}) \otimes \mathbb{E}(M_1)$};
+			\node (d) at (7.5,0) {$\mathbb{E}(1_{ _L \mathbb{C}\textnormal{sp}(\X)}) \otimes \mathbb{E}(M_1)$};
 			\node (a) at (-6,0) {$1_\mathsf{A}+c_1$};
@@
 			\node (c3) at (5,2) {$c_1^\prime$};
-			\node (d4) at (7.5,-1) {$\mathbb{E}(1_{ _L \mathbb{C}\textnormal{sp}(\mathsf{X})} \otimes M_1)$};
+			\node (d4) at (7.5,-1) {$\mathbb{E}(1_{ _L \mathbb{C}\textnormal{sp}(\X)} \otimes M_1)$};
                                 \node (a5) at (-6,-1) {$1_\mathsf{A}+c_1^\prime$};
@@
                                 (a5) edge node[left]{$\lambda_{\mathsf{A}}$} (a6)
-                                (b5) edge node[left]{$R(\lambda_{\mathsf{X}})$} (b6)
+                                (b5) edge node[left]{$R(\lambda_{\X})$} (b6)
  (b5) edge node[right]{$\iota_4$} (b6)
@@
 \node (A) at (-.5,0) {$F(\lambda_{\mathsf{A}})(!_{1_\mathsf{A}}+x_1)$};
-\node (C) at (4,0) {$F(R(\lambda_{\mathsf{X}})(\mu_{L(1_\mathsf{A}),x_1}))(!_{R(L(1_\mathsf{A}))} +x_1$)};
+\node (C) at (4,0) {$F(R(\lambda_{\X})(\mu_{L(1_\mathsf{A}),x_1}))(!_{R(L(1_\mathsf{A}))} +x_1$)};
 \node (D) at (-.5,-1) {$x_1$};
-\node (E) at (4,-1) {$F(R(\lambda_\mathsf{X}))(x_{!+1})$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$F(R(\lambda_{\mathsf{X}})(\mu_{L(1_\mathsf{A}),x_1}))(\iota_2)$} (C)
+\node (E) at (4,-1) {$F(R(\lambda_\X))(x_{!+1})$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$F(R(\lambda_{\X})(\mu_{L(1_\mathsf{A}),x_1}))(\iota_2)$} (C)
 (A) edge node[left]{$\iota_1$} (D)
 (E) edge node[above]{$\iota_4$} (D)
-(C) edge node[right]{$F(R(\lambda_\mathsf{X}))(\iota_3)$} (E);
+(C) edge node[right]{$F(R(\lambda_\X))(\iota_3)$} (E);
 \end{tikzpicture}
@@
 where $x_{!+1}$ is the decoration $x_1$ on the object $R(L(1_\mathsf{A})+x_1) \in \mathsf{A}$.
-The above square commutes because $$F(\lambda_\mathsf{A})(!_{1_\mathsf{A}}+x_1) = F(R(\lambda_\mathsf{X})(\mu_{L(1_\mathsf{A}),x_1})(\eta_{1_\mathsf{A}}+1))(!_{1_\mathsf{A}}+x_1)$$ as the corresponding left unitality square for the finite colimit preserving functor $R \maps (\mathsf{X},1_\mathsf{X},+) \to (\mathsf{A},1_\mathsf{A},+)$ commutes.
+The above square commutes because $$F(\lambda_\mathsf{A})(!_{1_\mathsf{A}}+x_1) = F(R(\lambda_\X)(\mu_{L(1_\mathsf{A}),x_1})(\eta_{1_\mathsf{A}}+1))(!_{1_\mathsf{A}}+x_1)$$ as the corresponding left unitality square for the finite colimit preserving functor $R \maps (\X,1_\X,+) \to (\mathsf{A},1_\mathsf{A},+)$ commutes.
 The right unitality square is similar.
@@
                                 (a3) edge node[left]{$a_\mathsf{A}$} (a4)
-                                (b3) edge node[left]{$R(a_\mathsf{X})$} (b4)
+                                (b3) edge node[left]{$R(a_\X)$} (b4)
 (b3) edge node[right]{$\iota_3$} (b4)
@@
 \path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$F((R(a_\mathsf{X}))(\kappa))(\iota_1)$} (B)
-(B) edge node[right]{$F(R(a_\mathsf{X}))(\iota_2)$} (C)
+(A) edge node[above]{$F((R(a_\X))(\kappa))(\iota_1)$} (B)
+(B) edge node[right]{$F(R(a_\X))(\iota_2)$} (C)
 (C) edge node[right]{$\iota_3$} (D)
@@
 \]
-The above square commutes because $$F((\kappa)(1+\kappa)(a_\mathsf{A}))((x_1+x_2)+x_3) = F((R(a_\mathsf{X}))(\kappa)(\kappa+1))((x_1+x_2)+x_3)$$ as the corresponding associator hexagon for the finite colimit preserving functor $R \maps (\mathsf{X},1_\mathsf{X},+) \to (\mathsf{A},1_\mathsf{A},+)$ commutes.
+The above square commutes because $$F((\kappa)(1+\kappa)(a_\mathsf{A}))((x_1+x_2)+x_3) = F((R(a_\X))(\kappa)(\kappa+1))((x_1+x_2)+x_3)$$ as the corresponding associator hexagon for the finite colimit preserving functor $R \maps (\X,1_\X,+) \to (\mathsf{A},1_\mathsf{A},+)$ commutes.
 Lastly, the braiding square:
@@
                                 (a5) edge node[left]{$\beta_\mathsf{A}$} (a6)
-                                (b5) edge node[left]{$R(\beta_\mathsf{X})$} (b6)
+                                (b5) edge node[left]{$R(\beta_\X)$} (b6)
  (b5) edge node[right]{$\iota_4$} (b6)
@@
 \node (C) at (4,0) {$F(\kappa)(x_2+x_1)$};
-\node (D) at (-.5,-1) {$F(R(\beta_\mathsf{X}))(x_1+x_2)$};
+\node (D) at (-.5,-1) {$F(R(\beta_\X))(x_1+x_2)$};
 \node (E) at (4,-1) {$x_2+x_1$};
@@
 (A) edge node[above]{$F(\kappa)(\iota_1)$} (C)
-(A) edge node[left]{$F(R(\beta_\mathsf{X}))(\iota_3)$} (D)
+(A) edge node[left]{$F(R(\beta_\X))(\iota_3)$} (D)
 (D) edge node[above]{$\iota_4$} (E)
@@
 \]
-The above square commutes because $$F((\kappa)(\beta_\mathsf{A}))(x_1+x_2) = F((R(\beta_\mathsf{X}))(\kappa))(x_1+x_2)$$ as the corresponding braiding square for the finite colimit preserving functor $R \maps (\mathsf{X},1_\mathsf{X},+) \to (\mathsf{A},1_\mathsf{A},+)$ commutes.
-Thus the double functor $\mathbb{E} \maps _L\mathbb{C}\textnormal{sp}(\mathsf{X}) \to F\mathbb{C}\textnormal{sp}$ is symmetric monoidal.
+The above square commutes because $$F((\kappa)(\beta_\mathsf{A}))(x_1+x_2) = F((R(\beta_\X))(\kappa))(x_1+x_2)$$ as the corresponding braiding square for the finite colimit preserving functor $R \maps (\X,1_\X,+) \to (\mathsf{A},1_\mathsf{A},+)$ commutes.
+Thus the double functor $\mathbb{E} \maps _L\mathbb{C}\textnormal{sp}(\X) \to F\mathbb{C}\textnormal{sp}$ is symmetric monoidal.
 \end{comment}
@@
 \end{enumerate} 
-Likewise, $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$ induces a symmetric monoidal bicategory $H( {_L \mathbb{C}\textnormal{sp}(\mathsf{X})})$ which has:
+Likewise, $_L \mathbb{C}\textnormal{sp}(\X)$ induces a symmetric monoidal bicategory $H( {_L \mathbb{C}\textnormal{sp}(\X)})$ which has:
 \begin{enumerate}
 \item{objects as those of $\mathsf{A}$,}
-\item{morphisms as horizontal 1-cells of $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$, and}
-\item{2-morphisms as globular 2-morphisms of $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$.}
+\item{morphisms as horizontal 1-cells of $_L \mathbb{C}\textnormal{sp}(\X)$, and}
+\item{2-morphisms as globular 2-morphisms of $_L \mathbb{C}\textnormal{sp}(\X)$.}
 \end{enumerate}
@@
 \begin{cor}
-The bicategories $F\mathbf{Csp}$ and $H( {_L \mathbb{C}\textnormal{sp}(\mathsf{X})})$ are biequivalent.
+The bicategories $F\mathbf{Csp}$ and $H( {_L \mathbb{C}\textnormal{sp}(\X)})$ are biequivalent.
 \end{cor}
@@
 \begin{comment}
-We can also define the part of the double equivalence $\mathbb{G} \maps F\mathbb{C}\textnormal{sp} \to {_L \mathbb{C} \textnormal{sp}(\mathsf{X})}$ which goes in the other direction: again, the object component of this double functor will be $\mathbb{G}_0 = \id_{\mathsf{A}}$.
+We can also define the part of the double equivalence $\mathbb{G} \maps F\mathbb{C}\textnormal{sp} \to {_L \mathbb{C} \textnormal{sp}(\X)}$ which goes in the other direction: again, the object component of this double functor will be $\mathbb{G}_0 = \id_{\mathsf{A}}$.
 
@@
 \]
-the image $\mathbb{G}(M)$ is the horizontal 1-cell in $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$ given by:
+the image $\mathbb{G}(M)$ is the horizontal 1-cell in $_L \mathbb{C}\textnormal{sp}(\X)$ given by:
 \[
@@
 $$\iota \maps F(h)(x) \to x^\prime$$
-the image $\mathbb{G}(f,h,g,\iota)$ in $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$ is given by the 2-morphism:
+the image $\mathbb{G}(f,h,g,\iota)$ in $_L \mathbb{C}\textnormal{sp}(\X)$ is given by the 2-morphism:
 \[
@@
 
-Next, we exhibit natural isomorphisms $\eta \maps \id_{ _L \mathbb{C}\textnormal{sp}(\mathsf{X})} \cong \mathbb{G} \mathbb{E}$ and $\epsilon \maps \mathbb{E} \mathbb{G} \cong \id_{F\mathbb{C}\textnormal{sp}}$.
+Next, we exhibit natural isomorphisms $\eta \maps \id_{ _L \mathbb{C}\textnormal{sp}(\X)} \cong \mathbb{G} \mathbb{E}$ and $\epsilon \maps \mathbb{E} \mathbb{G} \cong \id_{F\mathbb{C}\textnormal{sp}}$.
 Specifically, these are double natural isomorphisms given by double transformations \cite{Shul2} $\eta$ and $\epsilon$ whose object and arrow components are natural isomorphisms.
@@
 
-Given a horizontal 1-cell $M$ in $_L \mathbb{C} \textnormal{sp}(\mathsf{X})$:
+Given a horizontal 1-cell $M$ in $_L \mathbb{C} \textnormal{sp}(\X)$:
 \[
@@
 \]
-Then we can find a 2-isomorphism $\eta_M \maps M \xrightarrow{\sim} \mathbb{G}\mathbb{E}(M) $ in $_L \mathbb{C} \textnormal{sp}(\mathsf{X})$ given by:
+Then we can find a 2-isomorphism $\eta_M \maps M \xrightarrow{\sim} \mathbb{G}\mathbb{E}(M) $ in $_L \mathbb{C} \textnormal{sp}(\X)$ given by:
 \[
@@
 
-A functor $U \maps \X \to \A$ is a \textbf{Grothendieck opfibration} if for every $x\in\X$ with $U(x)=a$ and $f \maps a \to b$ in $\A$, there exists a \textbf{cocartesian lifting} of $x$ along $f$, namely a morphism $\beta$ in $\X$ with domain $x$ above $f$ with the following universal property: for any $g\maps b\to b'$ in $\A$ and $\gamma\maps x\to y'$ in $\X$ above the composite $g\circ f$, there exists a unique $\delta\maps y\to y'$ such that $U(\delta)=g$ and $\gamma=\delta\circ\beta$ as shown below
+A functor $U \maps \X \to \A$ is an \textbf{opfibration} if for every $x\in\X$ with $U(x)=a$ and $f \maps a \to b$ in $\A$, there exists a \textbf{cocartesian lifting} of $x$ along $f$, namely a morphism $\beta$ in $\X$ with domain $x$ above $f$ with the following universal property: for any $g\maps b\to b'$ in $\A$ and $\gamma\maps x\to y'$ in $\X$ above the composite $g\circ f$, there exists a unique $\delta\maps y\to y'$ such that $U(\delta)=g$ and $\gamma=\delta\circ\beta$ as shown below
 \begin{displaymath}

### 2020-11-10 cospans.tex
small fixes

@@
 We call $b$ the \define{apex}, $a_1$ and $a_2$ the \define{feet}, and $i$ and $o$ the \define{legs}.
-The feet describe `interfaces' of the corresponding open system.
-However, we often want the system itself---the apex---to have more structure than its interfaces.
+The feet describe `interfaces' of the corresponding open system, while the apex describes the system itself.
+However, we often want the system itself to have more structure than its interfaces.
 This led Fong to develop a theory of `decorated' cospans \cite{Fong}.
 
-Given a category $\A$ with finite colimits, a symmetric lax monoidal functor $F \maps (\A,+,0) \to (\textsf{Set},\times,1)$ can be used to `decorate' the apex of a cospan in $\A$ with some extra data: an element of the image of its apex under the functor $F$.
-In the case of the cospan above, this is an element $d \in F(b)$, which we call a \textbf{decoration} on $b$.
+Given a category $\A$ with finite colimits, a symmetric lax monoidal functor $F \maps (\A,+,0) \to (\textsf{Set},\times,1)$ can be used to `decorate' the apex of a cospan in $\A$ with some extra data: an element of the image of its apex under $F$.
+In the case of the cospan above, this would be an element $d \in F(b)$, which we call a \textbf{decoration} on $b$.
 Thus a decorated cospan is given by a pair:

### 2020-11-11 cospans.tex
small preamble edits, also changed geometry, fill free to amend
the issue was in fact already resolved

@@
 \input{Equiv_preamble.tex}
-\usepackage[foot]{amsaddr}
 
@@
 \noindent
-The first two authors have developed a compositional framework well-suited for studying networks that are built out of finite sets equipped with extra stuff.
-This framework, which goes by the name of `structured cospans', utilizes double categories where the objects are seen as inputs and outputs, horizontal 1-cells are `open networks', and 2-morphisms are maps between open networks.
-In this setup a functor $L \maps \A \to \textsf{X}$, which is typically a left adjoint, is used to replace the objects and vertical 1-morphisms of a given double category $\mathbb{X}$ with the objects and morphisms, respectively, of the category $\A$.
-Horizontal 1-cells are then cospans in $\textsf{X}$ of a particular form with 2-morphisms given by maps of these cospans.
-Fong has also developed a similar framework utilizing cospans to study open networks which goes by the name of `decorated cospans'.
-In this setup, a lax monoidal functor $F \maps \A \to \textsf{Set}$ is used to `decorate' the apices of cospans in $\A$ with elements of $\textsf{Set}$ giving the cospans extra structure.
-Using a slight variation of Fong's framework, we prove that these two frameworks are equivalent in the situation where a left adjoint can be obtained from a lax monoidal pseudofunctor using a well known construction of Grothendieck.
+The first two authors have developed a compositional framework well-suited for studying networks that are built out of finite sets equipped 
+with extra stuff. This framework, which goes by the name of `structured cospans', utilizes double categories where the objects are seen as 
+inputs and outputs, horizontal 1-cells are `open networks', and 2-morphisms are maps between open networks. In this setup a functor $L \maps 
+\A \to \textsf{X}$, which is typically a left adjoint, is used to replace the objects and vertical 1-morphisms of a given double category 
+$\mathbb{X}$ with the objects and morphisms, respectively, of the category $\A$. Horizontal 1-cells are then cospans in $\textsf{X}$ of a 
+particular form with 2-morphisms given by maps of these cospans. Fong has also developed a similar framework utilizing cospans to study open 
+networks which goes by the name of `decorated cospans'. In this setup, a lax monoidal functor $F \maps \A \to \textsf{Set}$ is used to 
+`decorate' the apices of cospans in $\A$ with elements of $\textsf{Set}$ giving the cospans extra structure. Using a slight variation of 
+Fong's framework, we prove that these two frameworks are equivalent in the situation where a left adjoint can be obtained from a lax 
+monoidal pseudofunctor using a well known construction of Grothendieck.
 \end{abstract}
@@
 
-\setcounter{tocdepth}{1} % comment this out if you want to see the subsections in the table of contents
+\setcounter{tocdepth}{1}
 \tableofcontents
-
-\section*{Various issues-in-progress}
-
-\begin{itemize}
-\item {\chris Notation between \cref{Equiv} and \cref{thm:decoratedcospans} right now does not match!
-Need to fix.
-Slightly prefer a,b,c for objects of A, then $a'$ and $b'$ for other objects, and x an object of the category F(c) namely the decoration.
-The previously used `d' is slightly confusing around all these a's, b's and c's that are in a different category.
-Also I prefer $a$ and $b$ rather than $a_1$ and $a_2$.}
-
-{\chris After a brief discussion in John's office, for \cref{Equiv} I used $a,b,c$ for the feet and $m,n$ for the apices so we can serially compose. Of course can change as we like.}
-%\item {\chris There might be a way to completely hide the details of version 'fibres have, reindexing preserve' if that's what we want to do.}
-
-\end{itemize}
 

### 2020-11-11 cospans.tex
made all active inline comments into %git add .!

@@
 
-\documentclass{amsart}
+\documentclass[reqno]{amsart}
 \input{Equiv_preamble.tex}
@@
 \node (E') at (4,-0.5) {$F(b^\prime)$};
-\node (F) at (3.65,0) {$\Swarrow \iota$};
+\node (F) at (3.65,0) {$\Swarrow \tau$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \end{enumerate}
-Note that the natural transformation is a family of morphisms in the category $F(b^\prime)$ indexed by $1$, and so is the same as just a morphism $\iota \maps F(f)(d) \to d^\prime$ in $F(b^\prime)$.
-We will typically write the transformation $\iota$ in later sections as a morphism in $F(b^\prime)$ to conserve space.
-In the context of the example above involving graphs, this morphism $\iota$ will be a map between two possibly distinct sets of edges and thus already solves the problem.
+Note that the natural transformation is a family of morphisms in the category $F(b^\prime)$ indexed by $1$, and so is the same as just a morphism $\tau \maps F(f)(d) \to d^\prime$ in $F(b^\prime)$.
+We will typically write the transformation $\tau$ in later sections as a morphism in $F(b^\prime)$ to conserve space.
+In the context of the example above involving graphs, this morphism $\tau$ will be a map between two possibly distinct sets of edges and thus already solves the problem.
 
@@
 \item{objects as those of $\mathsf{A}$ and}
-\item{morphisms as isomorphism classes of $F$-decorated cospans in $\mathsf{A}$ with the same feet together with a natural isomorphism, where two $F$-decorated cospans are in the same isomorphism class if $f$ and $\iota$ are isomorphisms.
+\item{morphisms as isomorphism classes of $F$-decorated cospans in $\mathsf{A}$ with the same feet together with a natural isomorphism, where two $F$-decorated cospans are in the same isomorphism class if $f$ and $\tau$ are isomorphisms.
 \[
@@
 \node (E') at (4,-0.5) {$F(b^\prime)$};
-\node (F) at (3.5,0) {$\Swarrow \iota$};
+\node (F) at (3.5,0) {$\Swarrow \tau$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 This symmetric monoidal category $F$Csp has isomorphism classes as one would expect, and in the context of the example with finite sets and graphs above solves the problem in (\ref{distinctisoclasses}).
-In this particular example, $\iota \maps F(f)(d) \xrightarrow{\sim} d^\prime$ is a bijection between possibly different sets of edges which respects the source and target of each edge.
+In this particular example, $\tau \maps F(f)(d) \xrightarrow{\sim} d^\prime$ is a bijection between possibly different sets of edges which respects the source and target of each edge.
 
@@
 
-{\chris Amend at the end}
-The outline for the paper is as follows: In Section \ref{DecCospansDoubleCat}, we construct the symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$, obtain the underlying symmetric monoidal bicategory $F \mathbf{Csp}$ via a result of Shulman, and decategorify this symmetric monoidal bicategory to obtain the symmetric monoidal category $F$Csp.
+%{\chris Amend at the end}
+%The outline for the paper is as follows: In Section \ref{DecCospansDoubleCat}, we construct the symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$, obtain the underlying symmetric monoidal bicategory $F \mathbf{Csp}$ via a result of Shulman, and decategorify this symmetric monoidal bicategory to obtain the symmetric monoidal category $F$Csp.
 In Section \ref{MapsDecCospansDoubleCat} we define maps between decorated cospan double categories which are double functors of an appropriate type.
@@
 
-%Changed Defn. to Definition
-In this paper, `double category' means `pseudo double category', as in Definition \ref{defn:double_category}.   Following Shulman \cite{Shul2010}, vertical composition 
+In this paper, `double category' means `pseudo double category', as in \cref{defn:double_category}.   Following Shulman \cite{Shul}, vertical composition 
 in our double categories is strictly associative, while horizontal composition need not be.
@@
 
+%!!!John: So one thing we should do is give a little explanation of (the new) decorated cospans, introducing vocabulary.
+And another thing we should do is give a little explanation of double categories, mainly to introduce vocabulary and symbols.
+I bet there's a lot of this in the appendix but still we should try to be nice to our readers.
+
 \begin{thm}\label{thm:decoratedcospans}
-Let $\mathsf{A}$ be a category with finite colimits and $F \maps \mathsf{A} \to \Cat$ a lax monoidal pseudofunctor. Then there exists a (pseudo) double category $F\mathbb{C}$sp which has:
-\begin{enumerate}
+Let $\mathsf{A}$ be a category with finite colimits and $F \maps \mathsf{A} \to \Cat$ a lax monoidal pseudofunctor. Then there exists a double category $F\mathbb{C}$sp which has:
+\begin{itemize}
 \item{objects as those of $\mathsf{A}$,}
 \item{vertical 1-morphisms as morphisms of $\mathsf{A}$,}
-\item{horizontal 1-cells as $F$-decorated cospans in $\mathsf{A}$ which are pairs:
+\item{horizontal 1-cells as $F$-decorated cospans in $\mathsf{A}$ which are pairs
 \[
@@
 \node (B) at (1,0) {$m$};
-\node (C) at (2,0) {$b$};
+\node (C) at (2,0) {$b,$};
 \node (D) at (3,0) {$x \in F(m)$};
@@
 \end{tikzpicture}
-\]
-and}
+\]}
 \item{2-morphisms as maps of $F$-decorated cospans in $\mathsf{A}$
@@
 \end{equation}
-together with a morphism $\iota \maps F(h)(m) \to m^\prime$ in $F(m^\prime)$.}
-\end{enumerate}
+together with a morphism $\tau \maps F(h)(m) \to m^\prime$ in $F(m^\prime)$.}
+\end{itemize}
 \end{thm}
-\textbf{Kenny: We should try to make this theorem shorter.} {\chris I agree!}
-\textbf{Kenny: On second thought, I'm not sure what we can cut out of this theorem. We're already saying "the standard monoidal category diagrams are satisfied" rather than displaying them.}
+%!!!Kenny: We should try to make this theorem shorter. 
+%!!!Christina: I agree!
+%!!!Kenny: On second thought, I'm not sure what we can cut out of this theorem. We're already saying "the standard monoidal category diagrams are satisfied" rather than displaying them.
+%!!!Christina: I think the proof can be simplified and made shorter in general, combined with John's comment that the reader should be eased in the terminology we use here like `unit structure functor', which could also be simplified to not using such notation, just describing for example the horizontal unit 1-cell and unit 2-cell.
+Kenny, would you like to give it a try?
+Or should I or John?
 \begin{proof}
@@
 \]
-together with the morphism $\iota_{!_f} = F(f) F(!) \phi \maps 1 \to F(a^\prime)$.
+together with the morphism $\tau_{!_f} = F(f) F(!) \phi \maps 1 \to F(a^\prime)$.
 We also have source and target structure functors $S, T \maps F\mathbb{C}\textnormal{sp}_1 \to F\mathbb{C}\textnormal{sp}_0$ where the source of the horizontal 1-cell
@@
 \]
-$$\iota \maps F(h)(m) \to m^\prime$$
+$$\tau \maps F(h)(m) \to m^\prime$$
 is the source of the underlying map of cospans in $\mathsf{A}$, namely the morphism $f$ in $\mathsf{A}$; the target structure functor is defined similarly.
@@
 $$ x \odot (y \odot z) \mapseqq 1 \xrightarrow{\zeta_2} F(m_1) \times F(m_2 +_{c} m_3) \xrightarrow{\phi_{m_1, m_2 +_{c} m_3}} F(m_1+(m_2 +_{c} m_3)) \xrightarrow{F(j_{m_1,m_2 +_{c} m_3})} F(m_1+_{b} (m_2+_{c} m_3))$$ $$\zeta_2 = (x \times 1) \lambda^{-1} F(j_{m_2,m_3}) \phi_{m_2,m_3} (y \odot z) \lambda^{-1}$$
-together with the isomorphism $\iota_\sigma \maps F(\sigma)((x \odot y) \odot z) \to x \odot (y \odot z)$.
+together with the isomorphism $\tau_\sigma \maps F(\sigma)((x \odot y) \odot z) \to x \odot (y \odot z)$.
 Note that the map $\sigma \maps (m_1+_{b} m_2)+_{c}m_3 \to m_1+_{b}(m_2+_{c}m_3)$ is the universal map between two colimits of the same diagram.
@@
 \]
-where $r \maps m+_{b} b \xrightarrow{\sim} m$ is a universal map together with the isomorphism $\iota_r \maps F(r)(x \odot !_b) \to x$.
+where $r \maps m+_{b} b \xrightarrow{\sim} m$ is a universal map together with the isomorphism $\tau_r \maps F(r)(x \odot !_b) \to x$.
 The left unitor is similar.
@@
 \node (K) at (7,-0.5) {$y' \in F(n^\prime)$};
-\node (L) at (1,-1) {$\iota_\alpha \maps F(h_1)(x) \to x'$};
-\node (M) at (5,-1) {$\iota_\beta \maps F(h_2)(y) \to y'$};
+\node (L) at (1,-1) {$\tau_\alpha \maps F(h_1)(x) \to x'$};
+\node (M) at (5,-1) {$\tau_\beta \maps F(h_2)(y) \to y'$};
 \node (A'') at (0,-1.5) {$a^\prime$};
@@
 \node (K'') at (7,-2.5) {$y'' \in F(n'')$};
-\node (L'') at (1,-3) {$\iota_{\alpha^\prime} \maps F(h_1^\prime)(x') \to x''$};
-\node (M'') at (5,-3) {$\iota_{\beta^\prime} \maps F(h_2^\prime)(y') \to y''$};
+\node (L'') at (1,-3) {$\tau_{\alpha^\prime} \maps F(h_1^\prime)(x') \to x''$};
+\node (M'') at (5,-3) {$\tau_{\beta^\prime} \maps F(h_2^\prime)(y') \to y''$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \node (F) at (4.5,-0.5) {$x' \odot y' \in F(m^\prime +_{b'} n^\prime)$};
-\node (G) at (1.5,-1) {$\iota_{\alpha \odot \beta} \maps F(h_1 +_g h_2)(x \odot y) \to x' \odot y'$};
+\node (G) at (1.5,-1) {$\tau_{\alpha \odot \beta} \maps F(h_1 +_g h_2)(x \odot y) \to x' \odot y'$};
 \node (A'') at (0,-1.5) {$a^\prime$};
@@
 \node (F'') at (4.5,-2.5) {$x'' \odot y'' \in F(m'' +_{b''} n'')$};
-\node (G'') at (1.5,-3) {$\iota_{\alpha^\prime \odot \beta^\prime} \maps F(h_1^\prime +_{g^\prime} h_2^\prime)(x' \odot y') \to x'' \odot y''.$};
+\node (G'') at (1.5,-3) {$\tau_{\alpha^\prime \odot \beta^\prime} \maps F(h_1^\prime +_{g^\prime} h_2^\prime)(x' \odot y') \to x'' \odot y''.$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (4,0) {$\iota_\alpha \Swarrow$};
+\node (A) at (4,0) {$\tau_\alpha \Swarrow$};
 \node (D) at (3,0) {$1$};
@@
 \node (E') at (4.5,-0.5) {$F(m^\prime)$};
-\node (A') at (6.5,0) {$\iota_\beta \Swarrow$};
+\node (A') at (6.5,0) {$\tau_\beta \Swarrow$};
 \node (D') at (5.5,0) {$1$};
@@
 \]
-These two 2-morphisms $\iota_\alpha$ and $\iota_\beta$ are two 2-morphisms in the monoidal 2-category $(\Cat,\times,1)$ and so we can tensor them which results in:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (4.75,0) {$\iota_\alpha \times \iota_\beta \Swarrow$};
+These two 2-morphisms $\tau_\alpha$ and $\tau_\beta$ are two 2-morphisms in the monoidal 2-category $(\Cat,\times,1)$ and so we can tensor them which results in:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (4.75,0) {$\tau_\alpha \times \tau_\beta \Swarrow$};
 \node (D) at (3,0) {$1 \xrightarrow{\lambda^{-1}} 1 \times 1$};
@@
 where the middle square commutes since $F$ is a lax monoidal pseudofunctor and the right square commutes as the underlying diagram commutes.
-The decorations $x \odot y$ and $x' \odot y'$ are given respectively by top and bottom composite of arrows and the morphism of decorations $\iota_{\alpha \odot \beta}$ is given by composing $\iota_\alpha \times \iota_\beta$ with the two commuting squares, which can equivalently be viewed as a morphism in $F(m' +_{b'} n')$.
+The decorations $x \odot y$ and $x' \odot y'$ are given respectively by top and bottom composite of arrows and the morphism of decorations $\tau_{\alpha \odot \beta}$ is given by composing $\tau_\alpha \times \tau_\beta$ with the two commuting squares, which can equivalently be viewed as a morphism in $F(m' +_{b'} n')$.
 
@@
 \node (F) at (5.5,-0.5) {$x'' \odot y'' \in F(m'' +_{b''} n'')$};
-\node (G) at (2,-1) {$\iota_{(a^\prime \odot \beta^\prime)(\alpha \odot \beta)} \maps F((h_1^\prime +_{g^\prime} h_2^\prime)(h_1 +_g h_2))(x \odot y) \to x'' \odot y''.$};
+\node (G) at (2,-1) {$\tau_{(a^\prime \odot \beta^\prime)(\alpha \odot \beta)} \maps F((h_1^\prime +_{g^\prime} h_2^\prime)(h_1 +_g h_2))(x \odot y) \to x'' \odot y''.$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \node (K) at (7,-0.5) {$y'' \in F(n'')$};
-\node (L) at (1,-1) {$\iota_{\alpha^\prime \alpha} \maps F(h_1^\prime h_1)(x) \to x''$};
-\node (M) at (5,-1) {$\iota_{\beta^\prime \beta} \maps F(h_2^\prime h_2)(y) \to y''$};
+\node (L) at (1,-1) {$\tau_{\alpha^\prime \alpha} \maps F(h_1^\prime h_1)(x) \to x''$};
+\node (M) at (5,-1) {$\tau_{\beta^\prime \beta} \maps F(h_2^\prime h_2)(y) \to y''$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \node (F) at (5.5,-0.5) {$x'' \odot y'' \in F(m'' +_{b''} n'')$};
-\node (G) at (2,-1) {$\iota_{(\alpha^\prime \alpha) \odot (\beta^\prime \beta)} \maps F((h_1^\prime h_1)+_{g^\prime g} (h_2^\prime h_2))(x \odot y) \to x'' \odot y''.$};
+\node (G) at (2,-1) {$\tau_{(\alpha^\prime \alpha) \odot (\beta^\prime \beta)} \maps F((h_1^\prime h_1)+_{g^\prime g} (h_2^\prime h_2))(x \odot y) \to x'' \odot y''.$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 As is usual concerning the interchange law of double categories of this nature, only the `interior' of the two composites appears different, but the two morphisms $(h_1^\prime +_{g^\prime} h_2^\prime)(h_1 +_g h_2) \maps m+_{b} n \to m'' +_{b''} n''$ and $(h_1^\prime h_1) +_{g^\prime g} (h_2^\prime h_2) \maps m+_{b} n \to m'' +_{b''}n''$ are the same universal map realized in two different ways.
-The two morphisms of decorations $\iota_{(\alpha^\prime \odot \beta^\prime)(\alpha \odot \beta)}$ and $\iota_{(\alpha^\prime \alpha) \odot (\beta^\prime \beta)}$ are obtained as two different compositions of four 2-morphisms in $\Cat$, namely horizontally then vertically and vertically then horizontally.
-As $\Cat$ is a 2-category, the interchange law for these 2-morphisms already holds, and as a result, the morphisms $$\iota_{(\alpha' \odot \beta')(\alpha \odot \beta)} \maps F((h_1^\prime +_{g^\prime} h_2^\prime)(h_1 +_g h_2))(x \odot y) \to x'' \odot y''$$ and $$\iota_{(\alpha^\prime \alpha)\odot(\beta^\prime \beta)} \maps F((h_1^\prime h_1)+_{g^\prime g} (h_2^\prime h_2))(x \odot y) \to x'' \odot y''$$ are also the same.
+The two morphisms of decorations $\tau_{(\alpha^\prime \odot \beta^\prime)(\alpha \odot \beta)}$ and $\tau_{(\alpha^\prime \alpha) \odot (\beta^\prime \beta)}$ are obtained as two different compositions of four 2-morphisms in $\Cat$, namely horizontally then vertically and vertically then horizontally.
+As $\Cat$ is a 2-category, the interchange law for these 2-morphisms already holds, and as a result, the morphisms $$\tau_{(\alpha' \odot \beta')(\alpha \odot \beta)} \maps F((h_1^\prime +_{g^\prime} h_2^\prime)(h_1 +_g h_2))(x \odot y) \to x'' \odot y''$$ and $$\tau_{(\alpha^\prime \alpha)\odot(\beta^\prime \beta)} \maps F((h_1^\prime h_1)+_{g^\prime g} (h_2^\prime h_2))(x \odot y) \to x'' \odot y''$$ are also the same.
 Thus the interchange law for 2-morphisms holds and $F\mathbb{C}$sp is a double category.
@@
 \end{thm}
-\textbf{Kenny: We should try to make this theorem shorter.} {\chris Yes!}
+%!!!Kenny: We should try to make this theorem shorter.
+%Christina: Yes!
+Again, I think that it can be simplified and easier for the reader to follow.
+Should tackle after we do the previous theorem.
+Also notice that a big part of the following proof is commented out below.
 \begin{proof}
@@
 \]
-together with a morphism $\iota \maps F(h)(x) \to x^\prime$.
+together with a morphism $\tau \maps F(h)(x) \to x^\prime$.
 }
@@
 \]
-where $\ell$ is the left unitor of $(\mathsf{A},+,0)$, together with the isomorphism $\iota_{\lambda} \maps F(\ell)(!_0 + x) \to x$. The right unitor is similar.
+where $\ell$ is the left unitor of $(\mathsf{A},+,0)$, together with the isomorphism $\tau_{\lambda} \maps F(\ell)(!_0 + x) \to x$. The right unitor is similar.
 
@@
 \]
-together with the isomorphism $\iota_a \maps F(a)((x_1+x_2)+x_3) \to x_1+(x_2+x_3)$.
+together with the isomorphism $\tau_a \maps F(a)((x_1+x_2)+x_3) \to x_1+(x_2+x_3)$.
 These associators and left and right unitors together satisfy the pentagon and triangle identities of a monoidal category.
-\textbf{Kenny: Probably cut stuff out below this.} If we denote the above associator simply as $a$ and the left and right unitors as $\lambda$ and $\rho$, respectively, then given four objects in $F\mathbb{C}\textnormal{sp}_1$, say $M_1, M_2, M_3$ and $M_4$:
+%!!! Kenny: Probably cut stuff out below this.
+% Christina: Commented them out for now, but should definitely have a close look to see if anything is needed when we go over and remake this proof.
+\begin{comment}
+If we denote the above associator simply as $a$ and the left and right unitors as $\lambda$ and $\rho$, respectively, then given four objects in $F\mathbb{C}\textnormal{sp}_1$, say $M_1, M_2, M_3$ and $M_4$:
 \[
@@
 \path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$F(a)(\iota_a)$} (B)
-(B) edge node[above]{$\iota_a$} (C)
-(A) edge node[left]{$F((1 \otimes a)a)(\iota_{a \otimes 1})$} (D)
-(D) edge node[above]{$F(1 \otimes a)(\iota_a)$} (E)
-(E) edge node[right]{$\iota_{1 \otimes a}$} (C);
+(A) edge node[above]{$F(a)(\tau_a)$} (B)
+(B) edge node[above]{$\tau_a$} (C)
+(A) edge node[left]{$F((1 \otimes a)a)(\tau_{a \otimes 1})$} (D)
+(D) edge node[above]{$F(1 \otimes a)(\tau_a)$} (E)
+(E) edge node[right]{$\tau_{1 \otimes a}$} (C);
 \end{tikzpicture}
@@
 \path[->,font=\scriptsize,>=angle 90]
-(A) edge node[left]{$\iota_{\rho \otimes 1}$} (B)
-(C) edge node[right]{$\iota_{1 \otimes \lambda}$} (B)
-(A) edge node[above]{$F(1 \otimes \lambda)(\iota_a)$} (C);
+(A) edge node[left]{$\tau_{\rho \otimes 1}$} (B)
+(C) edge node[right]{$\tau_{1 \otimes \lambda}$} (B)
+(A) edge node[above]{$F(1 \otimes \lambda)(\tau_a)$} (C);
 \end{tikzpicture}
@@
 \]
-$$\iota_{\beta_{M_1,M_2}} \maps F(\beta_{m_1,m_2})(x_1+x_2) \xrightarrow{\sim} x_2+x_1$$ where the vertical 1-morphisms are given by braidings in $(\mathsf{A},+,0)$.
+$$\tau_{\beta_{M_1,M_2}} \maps F(\beta_{m_1,m_2})(x_1+x_2) \xrightarrow{\sim} x_2+x_1$$ where the vertical 1-morphisms are given by braidings in $(\mathsf{A},+,0)$.
 This braiding makes the following triangle of underlying cospans commute:
@@
 (A) edge node[above]{$1$} (B)
-(C) edge node[right]{$\iota_{\beta_{M_2,M_1}}$} (B)
-(A) edge node[above]{$F(\beta_{m_2,m_1})(\iota_{\beta_{M_1,M_2}})$} (C);
+(C) edge node[right]{$\tau_{\beta_{M_2,M_1}}$} (B)
+(A) edge node[above]{$F(\beta_{m_2,m_1})(\tau_{\beta_{M_1,M_2}})$} (C);
 \end{tikzpicture}
@@
 \]
-$$\iota_{\hat{\chi}} \maps F(\hat{\chi})((x_1+y_1)\odot(x_2+y_2)) \to (x_1 \odot x_2)+(y_1 \odot y_2)$$
+$$\tau_{\hat{\chi}} \maps F(\hat{\chi})((x_1+y_1)\odot(x_2+y_2)) \to (x_1 \odot x_2)+(y_1 \odot y_2)$$
 where $\hat{\chi}$ is the universal map between two colimits of the same diagram.
@@
 \]
-$$\iota_{a,b} \maps !_{a+b} \xrightarrow{\sim} !_a + !_b$$
+$$\tau_{a,b} \maps !_{a+b} \xrightarrow{\sim} !_a + !_b$$
 where $!_{a+b}$ and $!_a + !_b$ are both initial objects in $F(a+b)$, hence isomorphic.
@@
                                 (b) edge node[left]{$a \odot a$} (b2)
-(b) edge node[right]{$\iota_1$} (b2)
+(b) edge node[right]{$\tau_1$} (b2)
 			(c) edge node[above]{$$} (c2)
@@
                                 (b2) edge node[left]{$\chi$} (b3)
-(b2) edge node[right]{$\iota_2$} (b3)
+(b2) edge node[right]{$\tau_2$} (b3)
 			(c2) edge node[above]{$$} (c3)
@@
                                 (b3) edge node[left]{$1 \otimes \chi$} (b4)
-(b3) edge node[right]{$\iota_3$} (b4)
+(b3) edge node[right]{$\tau_3$} (b4)
 			(c3) edge node[above]{$$} (c4)
@@
                                 (b) edge node[left]{$\chi$} (b5)
-(b) edge node[right]{$\iota_4$} (b5)
+(b) edge node[right]{$\tau_4$} (b5)
 			(c) edge node[above]{$$} (c5)
@@
                                 (b5) edge node[left]{$\chi \otimes 1$} (b6)
- (b5) edge node[right]{$\iota_5$} (b6)
+ (b5) edge node[right]{$\tau_5$} (b6)
 			(c5) edge node[above]{$$} (c6)
@@
                                 (b6) edge node[left]{$a$} (b7)
-(b6) edge node[right]{$\iota_6$} (b7)
+(b6) edge node[right]{$\tau_6$} (b7)
 			(c6) edge node[above]{$$} (c7);
@@
 The above diagram of maps of cospans can then be visualized as a hexagonal prism in which all the faces commute by identifying the top and the bottom as the same.
-As for the morphisms of decorations, which are labeled on the right of the interior vertical 1-morphisms, each isomorphism $\iota_n$ goes from the domain under the image of the functor $F$ applied to natural isomorphism adjacent to it to the codomain as written, meaning that, for example: $$\iota_1 \maps F(a \odot a)(((x_1+y_1)+z_1) \odot ((x_2+y_2)+z_2)) \to (x_1+(y_1+z_1)) \odot (x_2+(y_2+z_2)).$$  The following diagram commutes in the category $F((m_1+_b m_2) + ((n_1+_{b'} n_2) + (p_1+_{b''} p_2)))$:
+As for the morphisms of decorations, which are labeled on the right of the interior vertical 1-morphisms, each isomorphism $\tau_n$ goes from the domain under the image of the functor $F$ applied to natural isomorphism adjacent to it to the codomain as written, meaning that, for example: $$\tau_1 \maps F(a \odot a)(((x_1+y_1)+z_1) \odot ((x_2+y_2)+z_2)) \to (x_1+(y_1+z_1)) \odot (x_2+(y_2+z_2)).$$  The following diagram commutes in the category $F((m_1+_b m_2) + ((n_1+_{b'} n_2) + (p_1+_{b''} p_2)))$:
 \[
@@
 \path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$F((1 \otimes \chi) \chi)(\iota_1)$} (A')
-(A) edge node[left]{$F(a(\chi \otimes 1))(\iota_4)$} (B)
-(A') edge node[right]{$F(1 \otimes \chi)(\iota_2)$} (C)
-(B) edge node[left]{$F(a)(\iota_5)$} (C')
-(C) edge node [right] {$\iota_3$} (D)
-(C') edge node [above] {$\iota_6$} (D);
+(A) edge node[above]{$F((1 \otimes \chi) \chi)(\tau_1)$} (A')
+(A) edge node[left]{$F(a(\chi \otimes 1))(\tau_4)$} (B)
+(A') edge node[right]{$F(1 \otimes \chi)(\tau_2)$} (C)
+(B) edge node[left]{$F(a)(\tau_5)$} (C')
+(C) edge node [right] {$\tau_3$} (D)
+(C') edge node [above] {$\tau_6$} (D);
 \end{tikzpicture}
@@
                                 (b) edge node[left]{$\beta$} (b2)
-(b) edge node[right]{$\iota_1$} (b2)
+(b) edge node[right]{$\tau_1$} (b2)
 			(c) edge node[above]{$$} (c2)
@@
                                 (b5) edge node[left]{$\beta \odot \beta$} (b6)
- (b5) edge node[right]{$\iota_5$} (b6)
+ (b5) edge node[right]{$\tau_5$} (b6)
 			(c5) edge node[above]{$$} (c6);
@@
 \path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$F(\chi)(\iota_1)$} (B)
-(B) edge node[right]{$\iota_2$} (D)
-(A) edge node[left]{$F(\beta \odot \beta)(\iota_3)$} (C)
-(C) edge node[above]{$\iota_4$} (D);
+(A) edge node[above]{$F(\chi)(\tau_1)$} (B)
+(B) edge node[right]{$\tau_2$} (D)
+(A) edge node[left]{$F(\beta \odot \beta)(\tau_3)$} (C)
+(C) edge node[above]{$\tau_4$} (D);
 \end{tikzpicture}
@@
 The other diagrams are shown to commute similarly.
+\end{comment}
 \end{proof}
@@
 \node (K) at (7,-0.5) {$!_{c^\prime} \in F(c^\prime)$};
-\node (L) at (1,-1) {$\iota_{1_{c^\prime}} = 1_{!_{c^\prime}}$};
-\node (M) at (5,-1) {$\iota_f \maps F(f)(!_c) \to !_{c^\prime}$};
+\node (L) at (1,-1) {$\tau_{1_{c^\prime}} = 1_{!_{c^\prime}}$};
+\node (M) at (5,-1) {$\tau_f \maps F(f)(!_c) \to !_{c^\prime}$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \node (K) at (7,0) {$!_{c^\prime} \in F(c^\prime)$};
-\node (Q) at (1,-1) {$\iota_f \maps F(f)(!_c) \to !_{c^\prime}$};
-\node (L) at (1,-1.5) {$\iota_{c^\prime} = 1_{!_{c^\prime}}$};
-\node (M) at (5,-0.5) {$\iota_f \maps F(f)(!_c) \to !_{c^\prime}$};
+\node (Q) at (1,-1) {$\tau_f \maps F(f)(!_c) \to !_{c^\prime}$};
+\node (L) at (1,-1.5) {$\tau_{c^\prime} = 1_{!_{c^\prime}}$};
+\node (M) at (5,-0.5) {$\tau_f \maps F(f)(!_c) \to !_{c^\prime}$};
 \node (R) at (3,0.5) {$=$};
@@
 
-\node (L) at (1,-1.5) {$\iota_{c^\prime} = 1_{!_{c^\prime}}$};
+\node (L) at (1,-1.5) {$\tau_{c^\prime} = 1_{!_{c^\prime}}$};
 \node (E') at (-1,1) {$!_{c} \in F(c)$};
@@
 
-\node (L') at (-1,-1.5) {$\iota_{f} \maps F(f)(!_c) \to !_{c^\prime}$};
+\node (L') at (-1,-1.5) {$\tau_{f} \maps F(f)(!_c) \to !_{c^\prime}$};
 
@@
 \node (U) at (4,-1) {$!_{c^\prime} \in F(c^\prime)$};
-\node (V) at (4,-1.5) {$\iota_{c^\prime} = 1_{!_{c^\prime}}$};
+\node (V) at (4,-1.5) {$\tau_{c^\prime} = 1_{!_{c^\prime}}$};
 
@@
 \]
-together with a morphism $\iota \maps F(h)(d) \to d^\prime$ in $F(c^\prime)$.}
+together with a morphism $\tau \maps F(h)(d) \to d^\prime$ in $F(c^\prime)$.}
 \end{enumerate}
@@
 In the bicategorical version of $F \textnormal{Cospan}(\mathrm{A})$ where we are no longer considering decorated cospans up to isomorphism class, there is no 2-morphism between these two graphs due to the strict commutativity of the triangle to the right above.
-This problem does not occur in the symmetric monoidal bicategory $H(\mathbb{F}\textnormal{Cospan}(\mathrm{A}))$ and there is in fact a 2-(iso)morphism between these two graphs given by the map $\iota \maps F(f)(d) \to d^\prime$ which maps the edge $e$ to the edge $e^\prime$, where $f$ is the underlying map of vertices.
+This problem does not occur in the symmetric monoidal bicategory $H(\mathbb{F}\textnormal{Cospan}(\mathrm{A}))$ and there is in fact a 2-(iso)morphism between these two graphs given by the map $\tau \maps F(f)(d) \to d^\prime$ which maps the edge $e$ to the edge $e^\prime$, where $f$ is the underlying map of vertices.
 
@@
 \]
-and there exists an isomorphism $\iota \maps F(f)(d) \to d^\prime$ in $F(c^\prime)$.}
+and there exists an isomorphism $\tau \maps F(f)(d) \to d^\prime$ in $F(c^\prime)$.}
 \end{enumerate}
 \end{cor}
-In this symmetric monoidal category, isomorphism classes are as they should morally be, and the instance of two graphs having different edge sets does not prevent them from being in the same isomorphism class due to the isomorphism $\iota$.
+In this symmetric monoidal category, isomorphism classes are as they should morally be, and the instance of two graphs having different edge sets does not prevent them from being in the same isomorphism class due to the isomorphism $\tau$.
 
@@
 %\]
-%together with a morphism $\iota \maps F(h)(d) \to d^\prime$ in $F(c^\prime)$.}
+%together with a morphism $\tau \maps F(h)(d) \to d^\prime$ in $F(c^\prime)$.}
 %\end{enumerate}
@@
 \node (F) at (3,-0.5) {$d^\prime \in F(c^\prime)$};
-\node (G) at (1,-1) {$\iota \maps F(h)(d) \to d^\prime$};
+\node (G) at (1,-1) {$\tau \maps F(h)(d) \to d^\prime$};
 \node (A'') at (4.25,0.5) {$H(a)$};
@@
 \node (F'') at (8,-0.5) {$\theta_{c'} E(d^\prime) \phi \in F^\prime(H(c^\prime))$};
-\node (G'') at (5.25,-1) {$E(\iota) \maps F^\prime(H(h))(\theta_c E(d)\phi) \to (\theta_{c'}E(d^\prime)\phi)$};
+\node (G'') at (5.25,-1) {$E(\tau) \maps F^\prime(H(h))(\theta_c E(d)\phi) \to (\theta_{c'}E(d^\prime)\phi)$};
 \node (H) at (3.5,0) {$\mapsto$};
@@
 \begin{comment}
-Recall that we can think of the object $d \in F(c)$ as a morphism $d \maps 1 \to F(c)$ and the functor $\iota \maps F(h)(d) \to d^\prime$ of $F(c^\prime)$ as a natural transformation  in $\Cat$:
+Recall that we can think of the object $d \in F(c)$ as a morphism $d \maps 1 \to F(c)$ and the functor $\tau \maps F(h)(d) \to d^\prime$ of $F(c^\prime)$ as a natural transformation  in $\Cat$:
 \[
@@
 \node (D) at (1,-1) {$F(c^\prime)$};
-\node (C) at (0.75,-0.5) {$\Swarrow \iota$};
+\node (C) at (0.75,-0.5) {$\Swarrow \tau$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \node (D) at (2,-1) {$E(F(c^\prime))$};
-\node (C) at (1.5,-0.5) {$\Swarrow E(\iota)$};
+\node (C) at (1.5,-0.5) {$\Swarrow E(\tau)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \node (D) at (2,-1) {$E(F(c'))$};
-\node (C) at (1.5,-0.5) {$\Swarrow E(\iota)$};
+\node (C) at (1.5,-0.5) {$\Swarrow E(\tau)$};
 \node (E) at (4,0) {$F^\prime(H(c))$};
@@
 \]
-which results in a 2-morphism $E(\iota) \maps F^\prime(H(h))(\theta_c E(d)\phi) \to (\theta_{c'} E(d^\prime)\phi)$ in $F^\prime(H(c^\prime))$.
+which results in a 2-morphism $E(\tau) \maps F^\prime(H(h))(\theta_c E(d)\phi) \to (\theta_{c'} E(d^\prime)\phi)$ in $F^\prime(H(c^\prime))$.
 To check that the above recipe is functorial, given two vertically composable 2-morphisms in $F\mathbb{C}\textnormal{sp}$:
@@
 \node (F) at (4.5,-0.5) {$d^\prime \in F(c^\prime)$};
-\node (G) at (1.5,-1) {$\iota \maps F(h)(d) \to d^\prime$};
+\node (G) at (1.5,-1) {$\tau \maps F(h)(d) \to d^\prime$};
 \node (A'') at (0,-1.5) {$a^\prime$};
@@
 \node (F'') at (4.5,-2.5) {$d'' \in F(c'')$};
-\node (G'') at (1.5,-3) {$\iota^\prime \maps F(h^\prime)(d^\prime) \to d''$};
+\node (G'') at (1.5,-3) {$\tau^\prime \maps F(h^\prime)(d^\prime) \to d''$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \node (F) at (4.5,-0.5) {$d'' \in F(c'')$};
-\node (G) at (1.5,-1) {$\iota ^\prime \iota \maps F(h^\prime h)(d) \to d''$};
+\node (G) at (1.5,-1) {$\tau ^\prime \tau \maps F(h^\prime h)(d) \to d''$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \node (F) at (5,-0.5) {$\theta_{c''} E(d'') \phi \in F^\prime(H(c''))$};
-\node (G) at (1.5,-1) {$E(\iota ^\prime \iota) \maps F^\prime(H(h^\prime h))(\theta_c E(d)\phi) \to (\theta_{c''}E(d'')\phi).$};
+\node (G) at (1.5,-1) {$E(\tau ^\prime \tau) \maps F^\prime(H(h^\prime h))(\theta_c E(d)\phi) \to (\theta_{c''}E(d'')\phi).$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \node (F) at (5,-0.5) {$\theta_{c'} E(d^\prime) \phi \in F^\prime(H(c^\prime))$};
-\node (G) at (1.5,-1) {$E(\iota) \maps F^\prime(H(h))(\theta_c E(d)\phi) \to (\theta_{c'} E(d^\prime)\phi)$};
+\node (G) at (1.5,-1) {$E(\tau) \maps F^\prime(H(h))(\theta_c E(d)\phi) \to (\theta_{c'} E(d^\prime)\phi)$};
 \node (A'') at (0,-1.5) {$H(a^\prime)$};
@@
 \node (F'') at (5,-2.5) {$\theta_{c''} E(d'') \phi \in F^\prime(H(c''))$};
-\node (G'') at (1.5,-3) {$E(\iota^\prime) \maps F^\prime(H(h^\prime))(\theta_{c'} E(d^\prime)\phi) \to (\theta_{c''}E(d'')\phi)$};
+\node (G'') at (1.5,-3) {$E(\tau^\prime) \maps F^\prime(H(h^\prime))(\theta_{c'} E(d^\prime)\phi) \to (\theta_{c''}E(d'')\phi)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \node (F) at (7.5,-0.5) {$d_{\mathbb{H}(M \odot N)} \in F^\prime(H(c_1 +_b c_2))$};
-\node (G) at (2.5,-1) {$\iota_{\kappa^{-1}} \maps F^\prime(\kappa^{-1})(d_{\mathbb{H}(M) \odot \mathbb{H}(N)}) \to d_{\mathbb{H}(M \odot N)}.$};
+\node (G) at (2.5,-1) {$\tau_{\kappa^{-1}} \maps F^\prime(\kappa^{-1})(d_{\mathbb{H}(M) \odot \mathbb{H}(N)}) \to d_{\mathbb{H}(M \odot N)}.$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-where the morphism of decorations is the morphism $\iota \maps !_{H(c)} \to (\theta_c E(!_c) \phi)$ in $F'(H(c))$.
+where the morphism of decorations is the morphism $\tau \maps !_{H(c)} \to (\theta_c E(!_c) \phi)$ in $F'(H(c))$.
 These comparison constrains satisfy the coherence axioms of a monoidal category, namely:
@@
 \]
-$$\iota_\kappa \maps F^\prime(\kappa)(d_{\mathbb{H}(M_1) \otimes \mathbb{H}(M_2)}) \to d_{\mathbb{H}(M_1 \otimes M_2)}$$
+$$\tau_\kappa \maps F^\prime(\kappa)(d_{\mathbb{H}(M_1) \otimes \mathbb{H}(M_2)}) \to d_{\mathbb{H}(M_1 \otimes M_2)}$$
 where $\kappa$ denotes the isomorphism arising from $H$ preserving finite colimits.
@@
 \path[->,font=\scriptsize,>=angle 90]
-(A) edge node[left]{$F^\prime(\alpha \kappa)(\iota_\kappa + 1)$} (B)
-(B) edge node[left]{$F^\prime(\alpha)(\iota_\kappa)$} (C)
-(A) edge node[above]{$F^\prime(\kappa \kappa)(\iota_{\alpha^\prime})$} (A')
-(C) edge node [above] {$\iota_\alpha$} (C')
-(B') edge node [right] {$\iota_\kappa$} (C')
-(A') edge node [right]{$F^\prime(\kappa)(1+\iota_\kappa)$} (B');
+(A) edge node[left]{$F^\prime(\alpha \kappa)(\tau_\kappa + 1)$} (B)
+(B) edge node[left]{$F^\prime(\alpha)(\tau_\kappa)$} (C)
+(A) edge node[above]{$F^\prime(\kappa \kappa)(\tau_{\alpha^\prime})$} (A')
+(C) edge node [above] {$\tau_\alpha$} (C')
+(B') edge node [right] {$\tau_\kappa$} (C')
+(A') edge node [right]{$F^\prime(\kappa)(1+\tau_\kappa)$} (B');
 \end{tikzpicture}
@@
 \]
-together with the morphism $\iota_\mu \maps F^\prime(\kappa)(!_{1_\mathsf{A^\prime}}) \to (\theta_{1_\mathsf{A}} E(!_{1_\mathsf{A}})\phi)$ in $F^\prime(H(1_\mathsf{A}))$.
+together with the morphism $\tau_\mu \maps F^\prime(\kappa)(!_{1_\mathsf{A^\prime}}) \to (\theta_{1_\mathsf{A}} E(!_{1_\mathsf{A}})\phi)$ in $F^\prime(H(1_\mathsf{A}))$.
 The following square then commutes for any horizontal 1-cell $M$ of $F \mathbb{C}\textnormal{sp}$:
@@
 \path[->,font=\scriptsize,>=angle 90]
-(A) edge node[left]{$\iota_\ell$} (B)
-(A) edge node[above]{$F^\prime(H(\ell^\prime)\kappa)(\iota_{\mu \otimes 1})$} (A')
-(A') edge node [right]{$F^\prime(H(\ell^\prime))(\iota_\kappa)$} (B')
-(B') edge node [above] {$\iota_{H(\ell^\prime)}$} (B);
+(A) edge node[left]{$\tau_\ell$} (B)
+(A) edge node[above]{$F^\prime(H(\ell^\prime)\kappa)(\tau_{\mu \otimes 1})$} (A')
+(A') edge node [right]{$F^\prime(H(\ell^\prime))(\tau_\kappa)$} (B')
+(B') edge node [above] {$\tau_{H(\ell^\prime)}$} (B);
 \end{tikzpicture}
@@
 
-{\chris not sure if the below is needed after all}
+%!!!Christina: not sure if the below is needed after all
 In the opposite direction, we also have the following result. For a discussion on the unusual strict cocontinuity condition, we refer the reader to \cite{CV}.
@@
  \begin{tikzcd}[sep=1.5in,ampersand replacement=\&]
- (a,\bot_a)\ar[r,"{\begin{cases}i\maps a\to m &\textrm{in }\A \\!\maps F(i)(\bot_a)\to x &\textrm{in }F(m)\end{cases}}"]\ar[d,"{\begin{cases}f\maps a\to a' &\textrm{in }\A \\\chi_a\maps F(f)(\bot_a)\cong \bot_{a'} &\textrm{in }F(a')\end{cases}}"description] \& (m,x) \ar[d,"{\begin{cases}k\maps m\to m' &\textrm{in }\A \\ \iota\maps F(k)(x)\to x' &\textrm{in }F(m')\end{cases}}"description] \& (b,\bot_b)\ar[l,"{\begin{cases}o\maps b\to m &\textrm{in }\A \\!\maps F(o)(\bot_b)\to x &\textrm{in }F(m)\end{cases}}"']\ar[d,"{\begin{cases}g\maps b\to b' &\textrm{in }\A \\\chi_b\maps F(g)(\bot_b)\cong \bot_{b'} &\textrm{in }F(b')\end{cases}}"description] \\
+ (a,\bot_a)\ar[r,"{\begin{cases}i\maps a\to m &\textrm{in }\A \\!\maps F(i)(\bot_a)\to x &\textrm{in }F(m)\end{cases}}"]\ar[d,"{\begin{cases}f\maps a\to a' &\textrm{in }\A \\\chi_a\maps F(f)(\bot_a)\cong \bot_{a'} &\textrm{in }F(a')\end{cases}}"description] \& (m,x) \ar[d,"{\begin{cases}k\maps m\to m' &\textrm{in }\A \\ \tau\maps F(k)(x)\to x' &\textrm{in }F(m')\end{cases}}"description] \& (b,\bot_b)\ar[l,"{\begin{cases}o\maps b\to m &\textrm{in }\A \\!\maps F(o)(\bot_b)\to x &\textrm{in }F(m)\end{cases}}"']\ar[d,"{\begin{cases}g\maps b\to b' &\textrm{in }\A \\\chi_b\maps F(g)(\bot_b)\cong \bot_{b'} &\textrm{in }F(b')\end{cases}}"description] \\
  (a',\bot_{a'})\ar[r,"{\begin{cases}i'\maps a'\to m' &\textrm{in }\A \\!\maps F(i')(\bot_{a'})\to x' &\textrm{in }F(m')\end{cases}}"'] \& (m',x') \& (b',\bot_{b'})\ar[l,"{\begin{cases}o'\maps b'\to m' &\textrm{in }\A \\!\maps F(o')(\bot_{b'})\to x' &\textrm{in }F(m')\end{cases}}"]
@@
 where the outside vertical legs come from the definition of $L_F$ on arrows, \cref{eq:Lonarrows}. 
-{\chris The above diagram might be a bit overwhelming, but all info is there.
-Choose which parts are required for a smooth proof!} {\chris Also, iota and the letter i look alarmingly similar.
-Should we change iota to some other distinctive greek letter?}
+%!!! The above diagram might be a bit overwhelming, but all info is there. Choose which parts are required for a smooth proof!
 The square commutativities translate to $k\circ i=i'\circ f$ and $k\circ o=o'\circ g$ in $\A$, and also by composition in the Grothendieck category, to
 \begin{gather}\label{eq:Grothcommutativity}
- F(k\circ i)(\bot_a)\cong Fk(Fi(\bot_a))\xrightarrow{Fk(!)}Fk(x)\xrightarrow{\iota}x'= \\
+ F(k\circ i)(\bot_a)\cong Fk(Fi(\bot_a))\xrightarrow{Fk(!)}Fk(x)\xrightarrow{\tau}x'= \\
  F(i'\circ f)(\bot_a)\cong Fi'(Ff(\bot_a))\xrightarrow{Fi'(\chi_a)}Fi'(\bot_{a'})\xrightarrow{!}x'\nonumber
@@
 \end{displaymath}
- in $\A$ along with the map $\iota\maps Fk(x)\to x'$ in $F(m')$, namely a decorated cospan 2-morphism as per \cref{eq:FCsp2morph}.
+ in $\A$ along with the map $\tau\maps Fk(x)\to x'$ in $F(m')$, namely a decorated cospan 2-morphism as per \cref{eq:FCsp2morph}.
 Once again, this is a bijective correspondence since, as discussed above, the commutativity \cref{eq:Grothcommutativity} holds automatically by initiality of the domain.
- {\chris Christina commented out big chunks of proof.
+%!!!Christina: commented out big chunks of proof.
 They are right below if we want to revive parts of them, if we think the reader needs deeper level of detail.
 The idea is that the above description suffices as fully faithful and essentially surjective evidence, but perhaps we would like to spell that out more.
-On to strongness next.}
-
+On to strongness next.
 \begin{comment}
@@
 \]
-together with a morphism $\iota \maps F(R(\alpha))(x) \to x^\prime$ in $F(R(x^\prime)) \subseteq \mathrm{X}$ which comes from the Grothendieck construction of the pseudofunctor $F \maps \mathsf{A} \to \Cat$.
+together with a morphism $\tau \maps F(R(\alpha))(x) \to x^\prime$ in $F(R(x^\prime)) \subseteq \mathrm{X}$ which comes from the Grothendieck construction of the pseudofunctor $F \maps \mathsf{A} \to \Cat$.
 That $\mathbb{E}_0$ is a functor is clear.
@@
 \]
-together with a morphism $\iota_{M' M} \maps F(R(\alpha' \alpha))(x) \to x''$ in $F(R(x''))$. On the other hand, the individual images $\mathbb{E}_1(M)$ and $\mathbb{E}_1(M')$ are given by:
+together with a morphism $\tau_{M' M} \maps F(R(\alpha' \alpha))(x) \to x''$ in $F(R(x''))$. On the other hand, the individual images $\mathbb{E}_1(M)$ and $\mathbb{E}_1(M')$ are given by:
 \[
@@
 \]
-together with morphisms $\iota_M \maps F(R(\alpha))(x) \to x'$ in $F(R(x'))$ and $\iota_{M'} \maps F(R(\alpha')(x') \to x''$ in $F(R(x''))$, respectively.
-The vertical composite $\mathbb{E}_1(M')\mathbb{E}_1(M)$ of the above two 2-morphisms is given by $\mathbb{E}_1(M'M)$ as $R$ is a functor and $\iota_{M'M}=\iota_{M'} \iota_M$.
+together with morphisms $\tau_M \maps F(R(\alpha))(x) \to x'$ in $F(R(x'))$ and $\tau_{M'} \maps F(R(\alpha')(x') \to x''$ in $F(R(x''))$, respectively.
+The vertical composite $\mathbb{E}_1(M')\mathbb{E}_1(M)$ of the above two 2-morphisms is given by $\mathbb{E}_1(M'M)$ as $R$ is a functor and $\tau_{M'M}=\tau_{M'} \tau_M$.
 The functors $\mathbb{E}_0$ and $\mathbb{E}_1$ satisfy the equations $\mathbb{E}_0 S = S \mathbb{E}_1$ and $\mathbb{E}_0 T = T \mathbb{E}_1$.
@@
 \]
-$$\iota \maps F({(R(e)\eta_c)}^{-1})(x) \to x$$
+$$\tau \maps F({(R(e)\eta_c)}^{-1})(x) \to x$$
 where $e \maps L(c) \to x$ is given by the map from the trivial decoration on $c$ to $x \in F(c)$.
@@
 \]
-together with a morphism $\iota \maps F(R(\alpha))(x) \to x^\prime$ of $F(R(x^\prime))$.
-Thus the set $$_{\mathbb{E}(f)} {F\mathbb{C}\textnormal{sp}}_{\mathbb{E}(g)}(\mathbb{E}(M),\mathbb{E}(N))$$ consists of 4-tuples $$(f,R(\alpha),g,\iota)$$ rendering the above diagram commutative and where $f,g$ and $R(\alpha)$ are morphisms of $\mathsf{A}$ and $\iota$ is a morphism in $F(R(x'))$.
-The morphisms $R(\alpha) \maps R(x) \to R(x^\prime)$ and $\iota \maps F(R(\alpha))(x) \to x^\prime$ together determine the morphism $\alpha \maps x \to x^\prime$ in $\mathrm{X}$ and conversely; given two objects $x=(c,x \in F(c))$ and $x^\prime=(c^\prime,x^\prime \in F(c^\prime))$ of $\X=\inta{F}$, a morphism from $\alpha \maps x \to x^\prime$ is a pair $$(h \maps c \to c^\prime, \iota \maps F(h)(x) \to x^\prime)$$ where $h \maps c \to c^\prime$ is given by $R(\alpha) \maps R(x) \to R(x^\prime)$.
+together with a morphism $\tau \maps F(R(\alpha))(x) \to x^\prime$ of $F(R(x^\prime))$.
+Thus the set $$_{\mathbb{E}(f)} {F\mathbb{C}\textnormal{sp}}_{\mathbb{E}(g)}(\mathbb{E}(M),\mathbb{E}(N))$$ consists of 4-tuples $$(f,R(\alpha),g,\tau)$$ rendering the above diagram commutative and where $f,g$ and $R(\alpha)$ are morphisms of $\mathsf{A}$ and $\tau$ is a morphism in $F(R(x'))$.
+The morphisms $R(\alpha) \maps R(x) \to R(x^\prime)$ and $\tau \maps F(R(\alpha))(x) \to x^\prime$ together determine the morphism $\alpha \maps x \to x^\prime$ in $\mathrm{X}$ and conversely; given two objects $x=(c,x \in F(c))$ and $x^\prime=(c^\prime,x^\prime \in F(c^\prime))$ of $\X=\inta{F}$, a morphism from $\alpha \maps x \to x^\prime$ is a pair $$(h \maps c \to c^\prime, \tau \maps F(h)(x) \to x^\prime)$$ where $h \maps c \to c^\prime$ is given by $R(\alpha) \maps R(x) \to R(x^\prime)$.
 This shows that $\mathbb{E}$ is fully faithful.
@@
 where $j_m, j_n$ denote the maps into a pushout.
-On the other hand, first composing $M$ and $N$ in the Grothendieck category $\scsp{L_F}{\inta F}$ using fibrewise pushouts constructed using \cref{lem:fibrewiselimits} ({\chris I could make this specific construction into a lemma earlier if you want, I have it in my notes}) produces
+On the other hand, first composing $M$ and $N$ in the Grothendieck category $\scsp{L_F}{\inta F}$ using fibrewise pushouts constructed using \cref{lem:fibrewiselimits} 
+%!!!Chris: I could make this specific construction into a lemma earlier if you want, I have it in my notes
+produces 
 \begin{displaymath}
@@
 \end{displaymath}
-which is mapped, under $\mathbb{E}$, to precisely the cospan $\cspn{a}{m+_bn}{b}{}{}$ as above, and the decorations are the same {\chris isomorphic would be enough but they look equal to me!} due to the following commutative diagram
+which is mapped, under $\mathbb{E}$, to precisely the cospan $\cspn{a}{m+_bn}{b}{}{}$ as above, and the decorations are the same 
+%!!!Christina: isomorphic would be enough but they look equal to me!
+due to the following commutative diagram
 \begin{displaymath}
@@
 
-{\chris Below, up to my next comment, is Kenny's earlier proof on the same thing.}
-
+%!!!Christina: Below, up to my next comment, is Kenny's earlier proof on the same thing.
+\begin{comment}
 For any object $c$, the horizontal 1-cell $\hat{U}_{\mathbb{E}(c)}$ is given by $\hat{U}_c$ which is given by the pair:
@@
 \]
-$$\iota \maps F(\eta_c)(!_c) \xrightarrow{!} !_{R(L(c))}$$
+$$\tau \maps F(\eta_c)(!_c) \xrightarrow{!} !_{R(L(c))}$$
 of $F\mathbb{C}\textnormal{sp}$.
@@
 \]
-Lastly, this map of cospans comes with an isomorphism $$\iota \maps F(\sigma)(d_{\mathbb{E}(M) \odot \mathbb{E}(N)}) \to d_{\mathbb{E}(M \odot N)}$$ in $F(R(x+_{L(c_2)}x^\prime))$.
+Lastly, this map of cospans comes with an isomorphism $$\tau \maps F(\sigma)(d_{\mathbb{E}(M) \odot \mathbb{E}(N)}) \to d_{\mathbb{E}(M \odot N)}$$ in $F(R(x+_{L(c_2)}x^\prime))$.
 This shows that $\mathbb{E}$ is strong, and so
-
-{\chris Up to here was Kenny's strong functoriality.}
+\end{comment}
+%!!!Christina: Up to here was Kenny's strong functoriality.
 
@@
 Therefore $\mathbb{E} \maps \scsp{L_F}{\inta F} \to \dcsp{F}$ is a double equivalence, by \cref{ShulDubEquiv}.
-{\chris In fact, Christina and Kenny believe it is an isomorphism of double categories! Bijective on all levels of objects and morphisms...should we say?}
-
-{\chris Have not edited below, but everything should be fine up to notation changes. Happy to do if needed in the future.}
+%!!!Christina: In fact, Christina and Kenny believe it is an isomorphism of double categories! Bijective on all levels of objects and morphisms...should we say?
+
+%!!!Christina Have not edited below, but everything should be fine up to notation changes. Happy to do if needed in the future.
 
@@
 \]
-$$\iota_{{\eta_{1_\mathsf{A}}}} \maps F({\eta_{1_\mathsf{A}}})(!_{1_\mathsf{A}})) \to !_{R(L(1_\mathsf{A}))}$$
+$$\tau_{{\eta_{1_\mathsf{A}}}} \maps F({\eta_{1_\mathsf{A}}})(!_{1_\mathsf{A}})) \to !_{R(L(1_\mathsf{A}))}$$
 of $F\mathbb{C}\textnormal{sp}$. This is just the natural isomorphism $\mathbb{E}_{1_\mathsf{A}}$ from earlier.
@@
 \node (D') at (6.55,-1) {$d_{\mathbb{E}(M \otimes N)} \in F(R(x+x^\prime))$};
-\node (E) at (2,-1.5) {$\iota_\mu \maps F(\kappa)(d_{\mathbb{E}(M) \odot \mathbb{E}(N)}) \to d_{\mathbb{E}(M \odot N)}$};
+\node (E) at (2,-1.5) {$\tau_\mu \maps F(\kappa)(d_{\mathbb{E}(M) \odot \mathbb{E}(N)}) \to d_{\mathbb{E}(M \odot N)}$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 The isomorphisms $\delta$ and $\mu$ satisfy the left and right unitality squares, associativity hexagon and braiding square. 
-\textbf{Kenny: I think this might be a good place to cut the monoidal stuff.}{\chris Deal!
-They are right below.}
+%Kenny: I think this might be a good place to cut the monoidal stuff.
+%Christina: Deal! They are right below.
 
@@
                                 (b2) edge node[left]{$\eta_{1_\mathsf{A}}+1$} (b)
-(b2) edge node[right]{$\iota_2$} (b)
+(b2) edge node[right]{$\tau_2$} (b)
 			(c2) edge node[right]{$1$} (c)
@@
                                 (b2) edge node[left]{$\lambda_{\mathsf{A}}$} (b3)
-(b2) edge node[right]{$\iota_1$} (b3)
+(b2) edge node[right]{$\tau_1$} (b3)
 			(c2) edge node[right]{$\lambda_{\mathsf{A}}$} (c3)
@@
                                 (b) edge node[left]{$\mu_{L(1_\mathsf{A}),x_1}$} (b5)
-(b) edge node[right]{$\iota_3$} (b5)
+(b) edge node[right]{$\tau_3$} (b5)
 			(c) edge node[right]{$1$} (c5)
@@
                                 (b5) edge node[left]{$R(\lambda_{\X})$} (b6)
- (b5) edge node[right]{$\iota_4$} (b6)
+ (b5) edge node[right]{$\tau_4$} (b6)
 			(c5) edge node[right]{$\lambda_{\mathsf{A}}$} (c6);
@@
 \path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$F(R(\lambda_{\X})(\mu_{L(1_\mathsf{A}),x_1}))(\iota_2)$} (C)
-(A) edge node[left]{$\iota_1$} (D)
-(E) edge node[above]{$\iota_4$} (D)
-(C) edge node[right]{$F(R(\lambda_\X))(\iota_3)$} (E);
+(A) edge node[above]{$F(R(\lambda_{\X})(\mu_{L(1_\mathsf{A}),x_1}))(\tau_2)$} (C)
+(A) edge node[left]{$\tau_1$} (D)
+(E) edge node[above]{$\tau_4$} (D)
+(C) edge node[right]{$F(R(\lambda_\X))(\tau_3)$} (E);
 \end{tikzpicture}
@@
                                 (b) edge node[left]{$\kappa + 1$} (b2)
-(b) edge node[right]{$\iota_1$} (b2)
+(b) edge node[right]{$\tau_1$} (b2)
 			(c) edge node[right]{$1$} (c2)
@@
                                 (b2) edge node[left]{$\kappa$} (b3)
-(b2) edge node[right]{$\iota_2$} (b3)
+(b2) edge node[right]{$\tau_2$} (b3)
 			(c2) edge node[right]{$1$} (c3)
@@
                                 (b3) edge node[left]{$R(a_\X)$} (b4)
-(b3) edge node[right]{$\iota_3$} (b4)
+(b3) edge node[right]{$\tau_3$} (b4)
 			(c3) edge node[right]{$a_\mathsf{A}$} (c4)
@@
                                 (b) edge node[left]{$a_\mathsf{A}$} (b5)
-(b) edge node[right]{$\iota_4$} (b5)
+(b) edge node[right]{$\tau_4$} (b5)
 			(c) edge node[right]{$a_\mathsf{A}$} (c5)
@@
                                 (b5) edge node[left]{$1+\kappa$} (b6)
- (b5) edge node[right]{$\iota_5$} (b6)
+ (b5) edge node[right]{$\tau_5$} (b6)
 			(c5) edge node[right]{$1$} (c6)
@@
                                 (b6) edge node[left]{$\kappa$} (b7)
-(b6) edge node[right]{$\iota_6$} (b7)
+(b6) edge node[right]{$\tau_6$} (b7)
 			(c6) edge node[right]{$1$} (c7);
@@
 \path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$F((R(a_\X))(\kappa))(\iota_1)$} (B)
-(B) edge node[right]{$F(R(a_\X))(\iota_2)$} (C)
-(C) edge node[right]{$\iota_3$} (D)
-(A) edge node[left]{$F((\kappa)(1+\kappa))(\iota_4)$} (E)
-(E) edge node[left]{$F(\kappa)(\iota_5)$} (F)
-(F) edge node[above]{$\iota_6$} (D);
+(A) edge node[above]{$F((R(a_\X))(\kappa))(\tau_1)$} (B)
+(B) edge node[right]{$F(R(a_\X))(\tau_2)$} (C)
+(C) edge node[right]{$\tau_3$} (D)
+(A) edge node[left]{$F((\kappa)(1+\kappa))(\tau_4)$} (E)
+(E) edge node[left]{$F(\kappa)(\tau_5)$} (F)
+(F) edge node[above]{$\tau_6$} (D);
 \end{tikzpicture}
@@
                                 (b) edge node[left]{$\beta_\mathsf{A}$} (b2)
-(b) edge node[right]{$\iota_1$} (b2)
+(b) edge node[right]{$\tau_1$} (b2)
 			(c) edge node[right]{$\beta_\mathsf{A}$} (c2)
@@
                                 (b) edge node[left]{$\kappa$} (b5)
-(b) edge node[right]{$\iota_3$} (b5)
+(b) edge node[right]{$\tau_3$} (b5)
 			(c) edge node[right]{$1$} (c5)
@@
                                 (b5) edge node[left]{$R(\beta_\X)$} (b6)
- (b5) edge node[right]{$\iota_4$} (b6)
+ (b5) edge node[right]{$\tau_4$} (b6)
 			(c5) edge node[right]{$\beta_\mathsf{A}$} (c6);
@@
 \path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$F(\kappa)(\iota_1)$} (C)
-(A) edge node[left]{$F(R(\beta_\X))(\iota_3)$} (D)
-(D) edge node[above]{$\iota_4$} (E)
-(C) edge node[right]{$\iota_2$} (E);
+(A) edge node[above]{$F(\kappa)(\tau_1)$} (C)
+(A) edge node[left]{$F(R(\beta_\X))(\tau_3)$} (D)
+(D) edge node[above]{$\tau_4$} (E)
+(C) edge node[right]{$\tau_2$} (E);
 \end{tikzpicture}
@@
 
-\textbf{Is this biequivalnce symmetric monoidal? Mike says yes, but it follows from a result that he has yet to officially publish. It's a result of a paper he's currently working on with someone.}
-\newline
+%!!!Kenny: Is this biequivalnce symmetric monoidal? Mike says yes, but it follows from a result that he has yet to officially publish. It's a result of a paper he's currently working on with someone.
 
@@
 In other words, the trivial decoraction $!_{c}$ is initial in $F(c)$.
-Similarly, given a 2-morphism $(f,h,g,\iota) \maps M \to M^\prime$ of $F\mathbb{C}\textnormal{sp}$:
+Similarly, given a 2-morphism $(f,h,g,\tau) \maps M \to M^\prime$ of $F\mathbb{C}\textnormal{sp}$:
 \[
@@
 \]
-$$\iota \maps F(h)(x) \to x^\prime$$
-the image $\mathbb{G}(f,h,g,\iota)$ in $_L \mathbb{C}\textnormal{sp}(\X)$ is given by the 2-morphism:
+$$\tau \maps F(h)(x) \to x^\prime$$
+the image $\mathbb{G}(f,h,g,\tau)$ in $_L \mathbb{C}\textnormal{sp}(\X)$ is given by the 2-morphism:
 \[
@@
 \]
-where $\alpha \maps x \to x^\prime$ is the morphism in the Grothendieck construction of $F$ given by $\alpha = (h \maps c \to c^\prime, \iota \maps F(h)(x) \to x^\prime)$.
+where $\alpha \maps x \to x^\prime$ is the morphism in the Grothendieck construction of $F$ given by $\alpha = (h \maps c \to c^\prime, \tau \maps F(h)(x) \to x^\prime)$.
 
@@
 \]
-$$\iota \maps F(\hat{e})(x) \to x$$
+$$\tau \maps F(\hat{e})(x) \to x$$
 where 
@@
 \]
-together with a graph morphism $\iota \maps F(h)(G_1) \to G_2$ in $F(P_2)$.}
+together with a graph morphism $\tau \maps F(h)(G_1) \to G_2$ in $F(P_2)$.}
 \end{enumerate}
@@
 \]
-together with a morphism of $k$-graphs $\iota \maps F(h)(K_1) \to K_2$ in $F(V_2)$.}
+together with a morphism of $k$-graphs $\tau \maps F(h)(K_1) \to K_2$ in $F(V_2)$.}
 \end{enumerate}
@@
 \]
-together with a map of Markov processes $\iota \maps F(h)(M_1) \to M_2$ in $F(N_2)$, where a map between two Markov processes to be given by a pair of functions $(g,h)$ that make the following diagram commute:
+together with a map of Markov processes $\tau \maps F(h)(M_1) \to M_2$ in $F(N_2)$, where a map between two Markov processes to be given by a pair of functions $(g,h)$ that make the following diagram commute:
 \[
@@
 \]
-together with a morphism of Petri nets $\iota \maps F(h)(P_1) \to P_2$ in $F(Z_2)$.}
+together with a morphism of Petri nets $\tau \maps F(h)(P_1) \to P_2$ in $F(Z_2)$.}
 \end{enumerate}
@@
 
-%\begin{comment}
-
-{\chris Here, I basically rearranged things to make them come in a certain order, and also added a few things for monoidal bicats, maybe more is needed or not.
-Didn't change Kenny's notation or writings almost at all}
+%!!!Christina: Here, I basically rearranged things to make them come in a certain order, and also added a few things for monoidal bicats, maybe more is needed or not.
+Didn't change Kenny's notation or writings almost at all
 
@@
 A \define{symmetric lax monoidal} pseudofunctor between symmetric monoidal bicategories comes with invertible $F(b)\circ \mu_{a,b}\cong \mu_{b,a}\circ b$, where $b$ is the braiding.
-{\chris Hiding various details under the rug - e.g. what a symmetric monoidal bicategory is. Should be fine? Also, not sure if we need monoidal transformations?}
+%!!!Christina: Hiding various details under the rug - e.g. what a symmetric monoidal bicategory is. Should be fine? Also, not sure if we need monoidal transformations?
 
@@
 \end{itemize}
-{\chris Might need to write the composition rule? Depending on the final proof of Big Theorem.}
+%!!!Christina: Might need to write the composition rule? Depending on the final proof of Big Theorem.
 This is an opfibred category over $\A$ via the obvious forgetful functor, with fibre categories $(\inta F)_a=F(a)$ and reindexing functors $f_!=F(f)$.
@@
 
-\begin{defn}
+\begin{defn}\label{defn:double_category}
 A \textbf{pseudo double category} $\lD$, or $\textbf{double category}$ for short, consists of a category of objects $\mathbf{D_{0}}$ and a category of arrows $\mathbf{D_{1}}$ with the following functors
@@
 
-{\chris Pretty sure the def below can be incorporated above, however got a bit lost in different notation. Kenny Fix?}
+%ChristinaL Pretty sure the def below can be incorporated above, however got a bit lost in different notation. Kenny Fix?
 \begin{defn}
@@
 
-Formally, two strong double functors between two double categories form a \emph{double equivalence} if {\chris their two-way composite is isomorphic to the identity, better expressed, possibly in a definition environment}.
-Similarly to ordinary equivalence of categories, {\chris cite shulman's theorem here [Shulman,7.8]} allows us to use the following equivalent characterization.
+Formally, two strong double functors between two double categories form a \emph{double equivalence} if ...
+%{\chris their two-way composite is isomorphic to the identity, better expressed, possibly in a definition environment}. 
+Similarly to ordinary equivalence of categories, [Shulman,7.8] allows us to use the following equivalent characterization.
 
@@
 \end{defn}
-%\end{comment}
 
@@
 
-\bibitem{BC2} J.\ C.\ Baez and K.\ Courser, Structured cospans. In preparation.
+\bibitem{BC2} J.\ C.\ Baez and K.\ Courser, Structured cospans. In preparation. THIS IS FINISHED!
 

### 2020-11-11 cospans.tex
tiny

@@
 \begin{equation}\label{eq:scsphor1cell}
- (a,\bot_a)\xrightarrow{\scalebox{0.7}{$\begin{cases}i\maps a\to m &\textrm{in }\A \\!\maps F(i)(\bot_a)\to x &\textrm{in }F(m)\end{cases}$}}(m,x)\xleftarrow{\scalebox{0.7}{$\begin{cases}o\maps b\to m &\textrm{in }\A \\!\maps F(o)(\bot_b)\to x &\textrm{in }F(m)\end{cases}$}}(b,\bot_b)
+ (a,\bot_a)\xrightarrow{\scalebox{0.7}{\(\begin{cases}i\maps a\to m &\textrm{in }\A \\!\maps F(i)(\bot_a)\to x &\textrm{in }F(m)\end{cases}\)}}(m,x)\xleftarrow{\scalebox{0.7}{\(\begin{cases}o\maps b\to m &\textrm{in }\A \\!\maps F(o)(\bot_b)\to x &\textrm{in }F(m)\end{cases}\)}}(b,\bot_b)
 \end{equation}

### 2020-11-11 cospans.tex
changed \ref to \cref everywhere

@@
 %{\chris Amend at the end}
-%The outline for the paper is as follows: In Section \ref{DecCospansDoubleCat}, we construct the symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$, obtain the underlying symmetric monoidal bicategory $F \mathbf{Csp}$ via a result of Shulman, and decategorify this symmetric monoidal bicategory to obtain the symmetric monoidal category $F$Csp.
-In Section \ref{MapsDecCospansDoubleCat} we define maps between decorated cospan double categories which are double functors of an appropriate type.
-In Section \ref{some other section} we investigate when a symmetric lax monoidal pseudofunctor gives rise to a left adjoint via the Grothendieck construction, which naturally leads to another compositional framework known as `Structured cospans'.
-In Section \ref{EquivDoubleCats} we briefly review the framework Structured cospans and prove that the double categorical versions of decorated cospans and structured cospans are equivalent when both are appropriate.
-Finally, in Section \ref{Applications}, we present a few examples that can be realized with either framework and discuss the realized equivalences.
+%The outline for the paper is as follows: In Section \cref{DecCospansDoubleCat}, we construct the symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$, obtain the underlying symmetric monoidal bicategory $F \mathbf{Csp}$ via a result of Shulman, and decategorify this symmetric monoidal bicategory to obtain the symmetric monoidal category $F$Csp.
+In Section \cref{MapsDecCospansDoubleCat} we define maps between decorated cospan double categories which are double functors of an appropriate type.
+In Section \cref{some other section} we investigate when a symmetric lax monoidal pseudofunctor gives rise to a left adjoint via the Grothendieck construction, which naturally leads to another compositional framework known as `Structured cospans'.
+In Section \cref{EquivDoubleCats} we briefly review the framework Structured cospans and prove that the double categorical versions of decorated cospans and structured cospans are equivalent when both are appropriate.
+Finally, in Section \cref{Applications}, we present a few examples that can be realized with either framework and discuss the realized equivalences.
 
@@
 %Let $F \maps \mathsf{A} \to \Cat$ be a symmetric lax monoidal pseudofunctor.
-Then by Theorem \ref{DC} of the previous section, we get a symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$.
+Then by Theorem \cref{DC} of the previous section, we get a symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$.
 This symmetric monoidal double category has:
@@
 where $\kappa$ is the isomorphism $$\kappa \maps H(c_1 +_b c_2) \xrightarrow{\sim} H(c_1) +_{H(b)} H(c_2)$$ which comes from the finite colimit preserving functor $H \maps \mathsf{A} \to \mathsf{A^\prime}$.
-The above diagram commutes by a similar argument to the one used in Theorem \ref{Equiv}.
+The above diagram commutes by a similar argument to the one used in Theorem \cref{Equiv}.
 Similarly, for every object $c \in \mathsf{A}$, we have a unit comparison constraint $$\mathbb{H}_U \maps U_{\mathbb{H}(c)} \to \mathbb{H}(U_c)$$ given by the globular 2-isomorphism:
@@
 \]
-The diagrams involving the morphisms of decorations are similar to those in Theorem \ref{DC}.
+The diagrams involving the morphisms of decorations are similar to those in Theorem \cref{DC}.
 This shows that $\mathbb{H}=(H,E,\theta)$ is a double functor.
@@
 Both $\mathsf{Set}$ and $\mathsf{Graph}$ are cocartesian monoidal and the functor $L \maps \mathsf{Set} \to \mathsf{Graph}$ is left adjoint to the forgetful functor $R \maps \mathsf{Graph} \to \mathsf{Set}$ which assigns to a graph $G$ its underlying set of vertices $U(G)$.
-Using structured cospans and appealing to Theorem \ref{SC}, we get a symmetric monoidal double category $_L \mathbb{C}\textnormal{sp}(\mathsf{Graph})$ which has:
+Using structured cospans and appealing to Theorem \cref{SC}, we get a symmetric monoidal double category $_L \mathbb{C}\textnormal{sp}(\mathsf{Graph})$ which has:
 \begin{enumerate}
@@
 Let $F \maps \mathsf{Set} \to \mathsf{Cat}$ be the symmetric lax monoidal pseudofunctor that assigns to a set $N$ the \emph{category} of all graph structures whose underlying set of vertices is $N$.
-Using Theorem \ref{DC}, we then obtain a symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$ which has:
+Using Theorem \cref{DC}, we then obtain a symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$ which has:
 \begin{enumerate}
@@
 We thus have two symmetric monoidal double categories: $_L \mathbb{C}\textnormal{sp}(\mathsf{Graph})$ obtained from structured cospans and $F\mathbb{C}\textnormal{sp}$ obtained from decorated cospans.
-Both of these double categories have $\mathsf{Set}$ as their categories of objects, open graphs as horizontal 1-cells and maps of open graphs as 2-morphisms, and by Theorem \ref{Equiv}, we have an equivalence of symmetric monoidal double categories $$_L \mathbb{C}\textnormal{sp}(\mathsf{Graph}) \sim F\mathbb{C}\textnormal{sp}.$$
+Both of these double categories have $\mathsf{Set}$ as their categories of objects, open graphs as horizontal 1-cells and maps of open graphs as 2-morphisms, and by Theorem \cref{Equiv}, we have an equivalence of symmetric monoidal double categories $$_L \mathbb{C}\textnormal{sp}(\mathsf{Graph}) \sim F\mathbb{C}\textnormal{sp}.$$
 
@@
 \]
-Thus the pseudofunctor $F$ is symmetric lax monoidal and so by Theorem \ref{DC} we get a symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$ which has:
+Thus the pseudofunctor $F$ is symmetric lax monoidal and so by Theorem \cref{DC} we get a symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$ which has:
 \begin{enumerate}
@@
 \end{enumerate}
-These two double categories $_L \mathbb{C}\textnormal{sp}(\mathsf{Graph}_k)$ and $F\mathbb{C}\textnormal{sp}$ are equivalent by Theorem \ref{Equiv}.
+These two double categories $_L \mathbb{C}\textnormal{sp}(\mathsf{Graph}_k)$ and $F\mathbb{C}\textnormal{sp}$ are equivalent by Theorem \cref{Equiv}.
 
@@
 This is done using a symmetric lax monoidal functor $F \maps \mathsf{FinSet} \to \mathsf{Set}$ which assigns to each finite set $N$ the (large) set of all Markov processes on $N$ as defined above.
-Viewing this functor $F$ as now a symmetric lax monoidal pseudofunctor $F \maps \mathsf{FinSet} \to \Cat$ that assigns to a finite set $N$ the \emph{category} $F(N)$ of all Markov processes on $N$, we then get by Theorem \ref{DC} a symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$ which has:
+Viewing this functor $F$ as now a symmetric lax monoidal pseudofunctor $F \maps \mathsf{FinSet} \to \Cat$ that assigns to a finite set $N$ the \emph{category} $F(N)$ of all Markov processes on $N$, we then get by Theorem \cref{DC} a symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$ which has:
 \begin{enumerate}
@@
 Both categories $\mathsf{FinSet}$ and $\mathsf{Mark}$ have finite colimits and the functor $L$ is left adjoint to the forgetful functor $R \maps \mathsf{Mark} \to \mathsf{FinSet}$ which maps a Markov process to its underlying finite set of states.
-By Theorem \ref{SC}, we get a symmetric monoidal double category $_L \mathbb{C}\textnormal{sp}(\mathsf{Mark})$ which has:
+By Theorem \cref{SC}, we get a symmetric monoidal double category $_L \mathbb{C}\textnormal{sp}(\mathsf{Mark})$ which has:
 \begin{enumerate}
@@
 \end{enumerate}
-The two double categories $F\mathbb{C}\textnormal{sp}$ and $_L \mathbb{C} \textnormal{sp}(\mathsf{Mark})$ are equivalent by Theorem \ref{Equiv}.
+The two double categories $F\mathbb{C}\textnormal{sp}$ and $_L \mathbb{C} \textnormal{sp}(\mathsf{Mark})$ are equivalent by Theorem \cref{Equiv}.
 
@@
 Master and the first author show the existence of a left adjoint $L \maps \mathsf{Set} \to \mathsf{Petri}$ where $\mathsf{Petri}$ is the category whose objects are Petri nets and whose `morphisms are morphisms of Petri nets'.
-They also show that $\mathsf{Petri}$ has finite colimits and thus using Theorem \ref{SC} obtain a symmetric monoidal double category $\mathbb{O}\mathbf{pen}(\mathrm{Petri})$ of open Petri nets which has:
+They also show that $\mathsf{Petri}$ has finite colimits and thus using Theorem \cref{SC} obtain a symmetric monoidal double category $\mathbb{O}\mathbf{pen}(\mathrm{Petri})$ of open Petri nets which has:
 \begin{enumerate}
@@
 All of the diagrams that are required to commute are straightforward.
-Using Theorem \ref{DC}, we obtain a symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$ which has:
+Using Theorem \cref{DC}, we obtain a symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$ which has:
 \begin{enumerate}
@@
 \end{enumerate}
-Thus we have a symmetric monoidal double category $\mathbb{O}\mathbf{pen}(\mathrm{Petri})$ of open Petri nets obtained from structured cospans and a symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$ of open Petri nets obtain from decorated cospans, and of course, we have an equivalence $\mathbb{O}\mathbf{pen}(\mathrm{Petri}) \sim F\mathbb{C}\textnormal{sp}$ of symmetric monoidal double categories by Theorem \ref{Equiv}.
+Thus we have a symmetric monoidal double category $\mathbb{O}\mathbf{pen}(\mathrm{Petri})$ of open Petri nets obtained from structured cospans and a symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$ of open Petri nets obtain from decorated cospans, and of course, we have an equivalence $\mathbb{O}\mathbf{pen}(\mathrm{Petri}) \sim F\mathbb{C}\textnormal{sp}$ of symmetric monoidal double categories by Theorem \cref{Equiv}.
 \end{comment}

### 2020-11-11 cospans.tex
changed \mathsf{A} to \A

@@
  $$1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{d_1 \times d_2} F(b) \times F(b^\prime) \xrightarrow{\phi_{b,b^\prime}} F(b+ b^\prime) \xrightarrow{F(j_{b,b^\prime})} F(b+_{a_2} b^\prime).$$
-From this symmetric lax monoidal functor $F \maps \A \to \mathsf{Set}$, Fong then constructs a symmetric monoidal category $F\textnormal{Cospan}(\mathsf{A})$ which has:
+From this symmetric lax monoidal functor $F \maps \A \to \mathsf{Set}$, Fong then constructs a symmetric monoidal category $F\textnormal{Cospan}(\A)$ which has:
 \begin{enumerate}
-\item{objects as those of $\mathsf{A}$ and}
+\item{objects as those of $\A$ and}
 \item{morphisms as isomorphism classes of $F$-decorated cospans, where an $F$-decorated cospan is given as above, and two $F$-decorated cospans are in the same isomorphism class if there exists an isomorphism $f \maps b \to b^\prime$ between the apices such that the following diagrams commute:
@@
 In a previous work, the second author extended Fong's theory of decorated cospans to a symmetric monoidal bicategory of decorated cospans \cite{Cour}.
-Namely, under the same hypotheses used by Fong amounting to a category $\mathsf{A}$ with finite colimits and a symmetric lax monoidal functor $F \maps (\mathsf{A},+,0) \to (\mathsf{Set}, \times, 1)$, there exists a symmetric monoidal bicategory $F\mathbf{Cospan}(\mathsf{A})$ which has:
+Namely, under the same hypotheses used by Fong amounting to a category $\A$ with finite colimits and a symmetric lax monoidal functor $F \maps (\A,+,0) \to (\mathsf{Set}, \times, 1)$, there exists a symmetric monoidal bicategory $F\mathbf{Cospan}(\A)$ which has:
 \begin{enumerate}
-\item objects as those of $\mathsf{A}$,
-\item morphisms as $F$-decorated cospans in $\mathsf{A}$, which again are pairs
+\item objects as those of $\A$,
+\item morphisms as $F$-decorated cospans in $\A$, which again are pairs
 \[
@@
 and
-\item 2-morphisms as pairs of commuting diagrams where the left diagram is a map of cospans in $\mathsf{A}$ and the right diagram is a commutative triangle in $\mathsf{Set}$.
+\item 2-morphisms as pairs of commuting diagrams where the left diagram is a map of cospans in $\A$ and the right diagram is a commutative triangle in $\mathsf{Set}$.
 \[
@@
 Our approach is to instead view the functor $F$ as a pseudofunctor $F \maps \textrm{A} \to \Cat$ and take advantage of the 2-categorical structure of $\Cat$.
-Given an object $a \in \mathsf{A}$, this then allows us to view $F(a)$ not as a \emph{set} of decorations on the object $a$ but as a \emph{category} of decorations on the object $a$.
+Given an object $a \in \A$, this then allows us to view $F(a)$ not as a \emph{set} of decorations on the object $a$ but as a \emph{category} of decorations on the object $a$.
 From this pseudofunctor, we construct a symmetric monoidal double category $F \mathbb{C}$sp.
@@
 \item{objects as those of $\mathrm{A}$,}
-\item{morphisms as the horizontal 1-cells of $F\mathbb{C}$sp, which are $F$-decorated cospans of $\mathsf{A}$
+\item{morphisms as the horizontal 1-cells of $F\mathbb{C}$sp, which are $F$-decorated cospans of $\A$
 \[
@@
 and}
-\item{2-morphisms as maps of $F$-decorated cospans in $\mathsf{A}$ with the same feet together with a natrual transformation.
+\item{2-morphisms as maps of $F$-decorated cospans in $\A$ with the same feet together with a natrual transformation.
 \[
@@
 \begin{enumerate}
-\item{objects as those of $\mathsf{A}$ and}
-\item{morphisms as isomorphism classes of $F$-decorated cospans in $\mathsf{A}$ with the same feet together with a natural isomorphism, where two $F$-decorated cospans are in the same isomorphism class if $f$ and $\tau$ are isomorphisms.
+\item{objects as those of $\A$ and}
+\item{morphisms as isomorphism classes of $F$-decorated cospans in $\A$ with the same feet together with a natural isomorphism, where two $F$-decorated cospans are in the same isomorphism class if $f$ and $\tau$ are isomorphisms.
 \[
@@
 \begin{thm}\label{thm:decoratedcospans}
-Let $\mathsf{A}$ be a category with finite colimits and $F \maps \mathsf{A} \to \Cat$ a lax monoidal pseudofunctor. Then there exists a double category $F\mathbb{C}$sp which has:
+Let $\A$ be a category with finite colimits and $F \maps \A \to \Cat$ a lax monoidal pseudofunctor. Then there exists a double category $F\mathbb{C}$sp which has:
 \begin{itemize}
-\item{objects as those of $\mathsf{A}$,}
-\item{vertical 1-morphisms as morphisms of $\mathsf{A}$,}
-\item{horizontal 1-cells as $F$-decorated cospans in $\mathsf{A}$ which are pairs
+\item{objects as those of $\A$,}
+\item{vertical 1-morphisms as morphisms of $\A$,}
+\item{horizontal 1-cells as $F$-decorated cospans in $\A$ which are pairs
 \[
@@
 \]}
-\item{2-morphisms as maps of $F$-decorated cospans in $\mathsf{A}$
+\item{2-morphisms as maps of $F$-decorated cospans in $\A$
 \begin{equation}\label{eq:FCsp2morph}
@@
 \]
-where $!_a \in F(a)$ is the trivial decoration on $a$ given by the composite of the unique map $F(!) \maps F(0) \to F(a)$ and the morphism $\phi \maps 1 \to F(0)$  which comes from the structure of the lax monoidal pseudofunctor $F \maps \mathsf{A} \to \Cat$.
+where $!_a \in F(a)$ is the trivial decoration on $a$ given by the composite of the unique map $F(!) \maps F(0) \to F(a)$ and the morphism $\phi \maps 1 \to F(0)$  which comes from the structure of the lax monoidal pseudofunctor $F \maps \A \to \Cat$.
 For morphisms, the structure functor $U$ is defined as:
@@
 \]
-is the object $a$ in $\mathsf{A}$ and the source of the 2-morphism
+is the object $a$ in $\A$ and the source of the 2-morphism
 \[
@@
 $$\tau \maps F(h)(m) \to m^\prime$$
-is the source of the underlying map of cospans in $\mathsf{A}$, namely the morphism $f$ in $\mathsf{A}$; the target structure functor is defined similarly.
-These structure functors satisfy the equations $$SU(a)=\id_a=TU(a)$$for all objects $a$ of $\mathsf{A}$.
+is the source of the underlying map of cospans in $\A$, namely the morphism $f$ in $\A$; the target structure functor is defined similarly.
+These structure functors satisfy the equations $$SU(a)=\id_a=TU(a)$$for all objects $a$ of $\A$.
 
@@
 $$1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{x \times y} F(m) \times F(n) \xrightarrow{\phi_{m,n}} F(m+n) \xrightarrow{F(\psi)} F(m+_{b}n)$$
-where $\psi \maps m + n \to m+_{b} n$ is the natural map from the coproduct to the pushout and $\phi_{m,n} \maps F(m) \times F(n) \to F(m+n)$ is the natural transformation coming from the structure of the lax monoidal pseudofunctor $F \maps \mathsf{A} \to \Cat$.
+where $\psi \maps m + n \to m+_{b} n$ is the natural map from the coproduct to the pushout and $\phi_{m,n} \maps F(m) \times F(n) \to F(m+n)$ is the natural transformation coming from the structure of the lax monoidal pseudofunctor $F \maps \A \to \Cat$.
 Denoting the first and second of these horizontal 1-cells as $M$ and $N$, respectively, the source and target structure functors satisfy the equations $S(N \odot M)=S(M)$ and $T(N \odot M)=T(N)$.
@@
 \begin{thm}\label{DC}
-Let $\mathsf{A}$ be a category with finite colimits and $F \maps \mathsf{A} \to \Cat$ a symmetric lax monoidal pseudofunctor. Then the double category $F\mathbb{C}$sp is symmetric monoidal.
+Let $\A$ be a category with finite colimits and $F \maps \A \to \Cat$ a symmetric lax monoidal pseudofunctor. Then the double category $F\mathbb{C}$sp is symmetric monoidal.
 \end{thm}
@@
 \begin{proof}
-First we note that the category of objects $F\mathbb{C}\textnormal{sp}_0=\mathsf{A}$ is symmetric monoidal under binary coproducts and the left and right unitors, associators and braidings are given as natural maps.
+First we note that the category of objects $F\mathbb{C}\textnormal{sp}_0=\A$ is symmetric monoidal under binary coproducts and the left and right unitors, associators and braidings are given as natural maps.
 The category of arrows $F\mathbb{C}\textnormal{sp}_1$ has:
@@
 and}
-\item{morphisms as maps of cospans in $\mathsf{A}$
+\item{morphisms as maps of cospans in $\A$
 \[
@@
 \]
-their tensor product $M_1 \otimes M_2$ is given by taking the coproducts of the cospans of $\mathsf{A}$
+their tensor product $M_1 \otimes M_2$ is given by taking the coproducts of the cospans of $\A$
 \[
@@
 \]
-where $0$ is the monoidal unit of $\mathsf{A}$ and $!_0 \maps 1 \to F(0)$ is the morphism which is part of the structure of the symmetric lax monoidal pseudofunctor $F \maps \mathsf{A} \to \Cat$.
+where $0$ is the monoidal unit of $\A$ and $!_0 \maps 1 \to F(0)$ is the morphism which is part of the structure of the symmetric lax monoidal pseudofunctor $F \maps \A \to \Cat$.
 Tensoring an object with the monoidal unit, say, on the left:
@@
 \]
-where $\ell$ is the left unitor of $(\mathsf{A},+,0)$, together with the isomorphism $\tau_{\lambda} \maps F(\ell)(!_0 + x) \to x$. The right unitor is similar.
+where $\ell$ is the left unitor of $(\A,+,0)$, together with the isomorphism $\tau_{\lambda} \maps F(\ell)(!_0 + x) \to x$. The right unitor is similar.
 
@@
 \]
-where $x_1+(x_2+x_3) \maps 1 \to F(m_1+(m_2+m_3))$ is given by: $$1 \xrightarrow{x_1 \times (x_2 \times x_3)} F(m_1) \times (F(m_2) \times F(m_3)) \xrightarrow{1 \times \phi_{m_2,m_3}} F(m_1) \times F(m_2+m_3) \xrightarrow{\phi_{m_1,m_2+m_3}} F(m_1+(m_2+m_3)).$$If we let $a$ denote the associator of $(\mathsf{A},+,0)$, the associator of $F\mathbb{C}\textnormal{sp}_1$ is then a map of cospans in $\mathsf{A}$ from $(M_1 \otimes M_2) \otimes M_3$ to $M_1 \otimes (M_2 \otimes M_3)$ given by:
+where $x_1+(x_2+x_3) \maps 1 \to F(m_1+(m_2+m_3))$ is given by: $$1 \xrightarrow{x_1 \times (x_2 \times x_3)} F(m_1) \times (F(m_2) \times F(m_3)) \xrightarrow{1 \times \phi_{m_2,m_3}} F(m_1) \times F(m_2+m_3) \xrightarrow{\phi_{m_1,m_2+m_3}} F(m_1+(m_2+m_3)).$$If we let $a$ denote the associator of $(\A,+,0)$, the associator of $F\mathbb{C}\textnormal{sp}_1$ is then a map of cospans in $\A$ from $(M_1 \otimes M_2) \otimes M_3$ to $M_1 \otimes (M_2 \otimes M_3)$ given by:
 \[
@@
 \]
-then as $\mathbb{C}\textnormal{sp}(\mathsf{A})$ is a symmetric monoidal double category, the following pentagon of underlying cospans and maps of cospans commutes:
+then as $\mathbb{C}\textnormal{sp}(\A)$ is a symmetric monoidal double category, the following pentagon of underlying cospans and maps of cospans commutes:
 \[
@@
 \]
-since $$F(aa)(((x_1+x_2)+x_3)+x_4)=F((1 \otimes a)a(a \otimes 1))(((x_1+x_2)+x_3)+x_4)$$ as the corresponding pentagon in the symmetric monoidal category $(\mathsf{A},+,0)$ commutes, and then appliying the pseudofunctor $F$ to said pentagon yields a commutative pentagon in $\Cat$.
+since $$F(aa)(((x_1+x_2)+x_3)+x_4)=F((1 \otimes a)a(a \otimes 1))(((x_1+x_2)+x_3)+x_4)$$ as the corresponding pentagon in the symmetric monoidal category $(\A,+,0)$ commutes, and then appliying the pseudofunctor $F$ to said pentagon yields a commutative pentagon in $\Cat$.
 
@@
 \]
-since $$F(\rho \otimes 1)((x_1+0)+x_2)=F((1 \otimes \lambda)a)((x_1+0)+x_2)$$ as the corresponding triangle in the symmetric monoidal category $(\mathsf{A},+,0)$ commutes and applying the pseudofunctor $F$ to this commutative triangle results in a commutative triangle in $\Cat$.
+since $$F(\rho \otimes 1)((x_1+0)+x_2)=F((1 \otimes \lambda)a)((x_1+0)+x_2)$$ as the corresponding triangle in the symmetric monoidal category $(\A,+,0)$ commutes and applying the pseudofunctor $F$ to this commutative triangle results in a commutative triangle in $\Cat$.
 
@@
 \]
-$$\tau_{\beta_{M_1,M_2}} \maps F(\beta_{m_1,m_2})(x_1+x_2) \xrightarrow{\sim} x_2+x_1$$ where the vertical 1-morphisms are given by braidings in $(\mathsf{A},+,0)$.
+$$\tau_{\beta_{M_1,M_2}} \maps F(\beta_{m_1,m_2})(x_1+x_2) \xrightarrow{\sim} x_2+x_1$$ where the vertical 1-morphisms are given by braidings in $(\A,+,0)$.
 This braiding makes the following triangle of underlying cospans commute:
@@
 \begin{enumerate}
-\item{objects as those of $\mathsf{A}$,}
+\item{objects as those of $\A$,}
 \item{morphisms as $F$-decorated cospans:
@@
 and}
-\item{2-morphisms as maps of cospans in $\mathsf{A}$ of the form:
+\item{2-morphisms as maps of cospans in $\A$ of the form:
 \[
@@
 
-This symmetric monoidal bicategory $F\mathbf{Csp}$ is a superior version of the symmetric monoidal bicategory $F$Cospan$(\mathsf{A})$ constructed earlier by the second author \cite{Cour} in that there is greater flexibility in what 2-morphisms are allowed.
+This symmetric monoidal bicategory $F\mathbf{Csp}$ is a superior version of the symmetric monoidal bicategory $F$Cospan$(\A)$ constructed earlier by the second author \cite{Cour} in that there is greater flexibility in what 2-morphisms are allowed.
 
@@
 \begin{enumerate}
-\item{objects as those of $\mathsf{A}$ and}
-\item{morphisms as isomorphism classes of $F$-decorated cospans of $\mathsf{A}$, where an $F$-decorated cospan is given by a pair:
+\item{objects as those of $\A$ and}
+\item{morphisms as isomorphism classes of $F$-decorated cospans of $\A$, where an $F$-decorated cospan is given by a pair:
 \[
@@
 
-%Let $F \maps \mathsf{A} \to \Cat$ be a symmetric lax monoidal pseudofunctor.
+%Let $F \maps \A \to \Cat$ be a symmetric lax monoidal pseudofunctor.
 Then by Theorem \cref{DC} of the previous section, we get a symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$.
@@
 %\begin{enumerate}
-%\item{objects as those of $\mathsf{A}$,}
-%\item{vertical 1-morphisms as morphisms of $\mathsf{A}$,}
+%\item{objects as those of $\A$,}
+%\item{vertical 1-morphisms as morphisms of $\A$,}
 %\item{horizontal 1-cells as pairs:
@@
 %and}
-%\item{2-morphisms as maps of cospans in $\mathsf{A}$
+%\item{2-morphisms as maps of cospans in $\A$
 %\[
@@
 Regarding maps between symmetric monoidal double categories, consider another symmetric lax monoidal pseudofunctor $F^\prime \maps \mathsf{A^\prime} \to \Cat$%, we can obtain another symmetric monoidal double category $F^\prime \mathbb{C}\textnormal{sp}$.
-a morphism from $F\mathbb{C}\textnormal{sp}$ to $F^\prime \mathbb{C}\textnormal{sp}$ will then be a double functor $\mathbb{H} \maps F\mathbb{C}\textnormal{sp} \to F' \mathbb{C}\textnormal{sp}$ whose object component is given by a finite colimit preserving functor $\mathbb{H}_0 = H \maps \mathsf{A} \to \mathsf{A^\prime}$ and whose arrow component is given by a functor $\mathbb{H}_1$ defined on horizontal 1-cells by:
+a morphism from $F\mathbb{C}\textnormal{sp}$ to $F^\prime \mathbb{C}\textnormal{sp}$ will then be a double functor $\mathbb{H} \maps F\mathbb{C}\textnormal{sp} \to F' \mathbb{C}\textnormal{sp}$ whose object component is given by a finite colimit preserving functor $\mathbb{H}_0 = H \maps \A \to \mathsf{A^\prime}$ and whose arrow component is given by a functor $\mathbb{H}_1$ defined on horizontal 1-cells by:
 \[
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$\mathsf{A}$};
+\node (A) at (0,0) {$\A$};
 \node (B) at (1,0) {$\Cat$};
@@
 \]
-where $\kappa$ is the isomorphism $$\kappa \maps H(c_1 +_b c_2) \xrightarrow{\sim} H(c_1) +_{H(b)} H(c_2)$$ which comes from the finite colimit preserving functor $H \maps \mathsf{A} \to \mathsf{A^\prime}$.
+where $\kappa$ is the isomorphism $$\kappa \maps H(c_1 +_b c_2) \xrightarrow{\sim} H(c_1) +_{H(b)} H(c_2)$$ which comes from the finite colimit preserving functor $H \maps \A \to \mathsf{A^\prime}$.
 The above diagram commutes by a similar argument to the one used in Theorem \cref{Equiv}.
-Similarly, for every object $c \in \mathsf{A}$, we have a unit comparison constraint $$\mathbb{H}_U \maps U_{\mathbb{H}(c)} \to \mathbb{H}(U_c)$$ given by the globular 2-isomorphism:
+Similarly, for every object $c \in \A$, we have a unit comparison constraint $$\mathbb{H}_U \maps U_{\mathbb{H}(c)} \to \mathbb{H}(U_c)$$ given by the globular 2-isomorphism:
 \[
@@
 Next we show that this double functor is symmetric monoidal.
-First, that the object component $\mathbb{H}_0=H$ is symmetric monoidal is clear as $H \maps \mathsf{A} \to \mathsf{A}^\prime$ preserves finite colimits.
+First, that the object component $\mathbb{H}_0=H$ is symmetric monoidal is clear as $H \maps \A \to \A^\prime$ preserves finite colimits.
 As for the arrow component $\mathbb{H}_1$, given two horizontal 1-cells $M_1$ and $M_2$ in $F\mathbb{C}\textnormal{sp}$:
@@
 where $$F^\prime(\alpha \kappa \kappa)(d_{(\mathbb{H}(M_1) \otimes \mathbb{H}(M_2)) \otimes \mathbb{H}(M_3)}) = F^\prime(\kappa \kappa \alpha^\prime)(d_{(\mathbb{H}(M_1) \otimes \mathbb{H}(M_2)) \otimes \mathbb{H}(M_3)})$$
-as the corresponding hexagon for the finite colimit preserving functor $H \maps \mathsf{A} \to \mathsf{A'}$ commutes.
-The map $\mu_{M_1,M_2}$ is also compatible with the braidings $\beta$ and $\beta^\prime$ of $F \mathbb{C}\textnormal{sp}_1$ and $F' \mathbb{C}\textnormal{sp}_1$, respectively, and make the necessary square commute as a consequence of the corresponding commutative square involving braidings from the finite colimit preserving functor $H \maps \mathsf{A} \to \mathsf{A'}$.
+as the corresponding hexagon for the finite colimit preserving functor $H \maps \A \to \mathsf{A'}$ commutes.
+The map $\mu_{M_1,M_2}$ is also compatible with the braidings $\beta$ and $\beta^\prime$ of $F \mathbb{C}\textnormal{sp}_1$ and $F' \mathbb{C}\textnormal{sp}_1$, respectively, and make the necessary square commute as a consequence of the corresponding commutative square involving braidings from the finite colimit preserving functor $H \maps \A \to \mathsf{A'}$.
 
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$1_\mathsf{A}$};
-\node (B) at (1,0) {$1_\mathsf{A}$};
-\node (C) at (2,0) {$1_\mathsf{A}$};
-\node (D) at (1,-0.5) {$!_{1_\mathsf{A}} \in F(1_\mathsf{A})$};
+\node (A) at (0,0) {$1_\A$};
+\node (B) at (1,0) {$1_\A$};
+\node (C) at (2,0) {$1_\A$};
+\node (D) at (1,-0.5) {$!_{1_\A} \in F(1_\A)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-where $1_\mathsf{A}$ is the monoidal unit of the cocartesian category $\mathsf{A}$. The image of this horizontal 1-cell under $\mathbb{H}$ is given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$H(1_\mathsf{A})$};
-\node (B) at (1,0) {$H(1_\mathsf{A})$};
-\node (C) at (2,0) {$H(1_\mathsf{A})$};
+where $1_\A$ is the monoidal unit of the cocartesian category $\A$. The image of this horizontal 1-cell under $\mathbb{H}$ is given by:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$H(1_\A)$};
+\node (B) at (1,0) {$H(1_\A)$};
+\node (C) at (2,0) {$H(1_\A)$};
 %\node (E) at (3,0) {$=$};
@@
 %\node (I) at (5,-0.5) {$!_{1_{\mathsf{A^\prime}}} \in F^\prime(1_{\mathsf{A^\prime}})$};
-\node (D) at (1,-0.5) {$\theta_{1_\mathsf{A}}E(!_{1_\mathsf{A}}) \phi \in F^\prime(H(1_\mathsf{A}))$};
+\node (D) at (1,-0.5) {$\theta_{1_\A}E(!_{1_\A}) \phi \in F^\prime(H(1_\A))$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \node (A) at (0,0.5) {$1_{\mathsf{A^\prime}}$};
-\node (A') at (0,-0.5) {$H(1_\mathsf{A})$};
+\node (A') at (0,-0.5) {$H(1_\A)$};
 \node (B) at (1.5,0.5) {$1_{\mathsf{A^\prime}}$};
 \node (C) at (3,0.5) {$1_{\mathsf{A^\prime}}$};
-\node (C') at (3,-0.5) {$H(1_\mathsf{A})$};
-\node (D) at (1.5,-0.5) {$H(1_\mathsf{A})$};
+\node (C') at (3,-0.5) {$H(1_\A)$};
+\node (D) at (1.5,-0.5) {$H(1_\A)$};
 \node (E) at (5,0.5) {$!_{1_\mathsf{A^\prime}} \in F^\prime(1_\mathsf{A^\prime})$};
-\node (F) at (5,-0.5) {$\theta_{1_\mathsf{A}} E(!_{1_\mathsf{A}}) \phi \in F^\prime(H(1_\mathsf{A}))$};
+\node (F) at (5,-0.5) {$\theta_{1_\A} E(!_{1_\A}) \phi \in F^\prime(H(1_\A))$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-together with the morphism $\tau_\mu \maps F^\prime(\kappa)(!_{1_\mathsf{A^\prime}}) \to (\theta_{1_\mathsf{A}} E(!_{1_\mathsf{A}})\phi)$ in $F^\prime(H(1_\mathsf{A}))$.
+together with the morphism $\tau_\mu \maps F^\prime(\kappa)(!_{1_\mathsf{A^\prime}}) \to (\theta_{1_\A} E(!_{1_\A})\phi)$ in $F^\prime(H(1_\A))$.
 The following square then commutes for any horizontal 1-cell $M$ of $F \mathbb{C}\textnormal{sp}$:
@@
 \node (A) at (0,0) {$1_\mathsf{A^\prime} \otimes \mathbb{H}(M)$};
-\node (B) at (2.5,0) {$\mathbb{H}(1_\mathsf{A}) \otimes \mathbb{H}(M)$};
+\node (B) at (2.5,0) {$\mathbb{H}(1_\A) \otimes \mathbb{H}(M)$};
 \node (C) at (0,-1) {$\mathbb{H}(M)$};
-\node (D) at (2.5,-1) {$\mathbb{H}(1_\mathsf{A} \otimes M)$};
+\node (D) at (2.5,-1) {$\mathbb{H}(1_\A \otimes M)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-where we have abbreviated the monoidal units of $F\mathbb{C}\textnormal{sp}_1$ and $F'\mathbb{C}\textnormal{sp}_1$ as $1_\mathsf{A}$ and $1_\mathsf{A^\prime}$, respectively.
+where we have abbreviated the monoidal units of $F\mathbb{C}\textnormal{sp}_1$ and $F'\mathbb{C}\textnormal{sp}_1$ as $1_\A$ and $1_\mathsf{A^\prime}$, respectively.
 The diagram of corresponding decorations is given by:
@@
 \node (B) at (0,-0.5) {$d_{\mathbb{H}(M)}$};
-\node (A') at (4,0.5) {$F^\prime(H(\ell^\prime) \kappa)(d_{!_{\mathbb{H}(1_\mathsf{A})}}\otimes d_{\mathbb{H}(M)})$};
-\node (B') at (4,-0.5) {$F^\prime(H(\ell^\prime))(d_{\mathbb{H}(1_\mathsf{A} \otimes M)})$};
+\node (A') at (4,0.5) {$F^\prime(H(\ell^\prime) \kappa)(d_{!_{\mathbb{H}(1_\A)}}\otimes d_{\mathbb{H}(M)})$};
+\node (B') at (4,-0.5) {$F^\prime(H(\ell^\prime))(d_{\mathbb{H}(1_\A \otimes M)})$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-where $$F^\prime(\ell)(d_{!_{1_\mathsf{A^\prime}}} \otimes d_{\mathbb{H}(M)})=F^\prime(H(\ell^\prime)\kappa(\mu \otimes 1))(d_{!_{1_\mathsf{A^\prime}}} \otimes d_{\mathbb{H}(M)})$$ since the corresponding square involving left unitors for the finite colimit preserving functor $H \maps \mathsf{A} \to \mathsf{A'}$ commutes.
+where $$F^\prime(\ell)(d_{!_{1_\mathsf{A^\prime}}} \otimes d_{\mathbb{H}(M)})=F^\prime(H(\ell^\prime)\kappa(\mu \otimes 1))(d_{!_{1_\mathsf{A^\prime}}} \otimes d_{\mathbb{H}(M)})$$ since the corresponding square involving left unitors for the finite colimit preserving functor $H \maps \A \to \mathsf{A'}$ commutes.
 The other square involving the right unitors $r$ and $r^\prime$ is similar.
@@
 \begin{thm}
-Given two finitely cocomplete categories $\mathsf{A}$ and $\mathsf{A}'$, two symmetric lax monoidal pseudofunctors $F \maps \mathsf{A} \to \Cat$ and $F' \maps \mathsf{A}' \to \Cat$, a finite colimit preserving functor $H \maps \mathsf{A} \to \mathsf{A}'$, a symmetric lax monoidal pseudofunctor $E \maps \Cat \to \Cat$ and a 2-isomorphism $\theta \maps EF \Rightarrow F^\prime H$ as in the following diagram, the triple $(H,E,\theta)$ induces a symmetric monoidal (strong) double functor $\mathbb{H} \maps F\mathbb{C}\textnormal{sp} \to F'\mathbb{C}\textnormal{sp}$ as defined above.
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$\mathsf{A}$};
+Given two finitely cocomplete categories $\A$ and $\A'$, two symmetric lax monoidal pseudofunctors $F \maps \A \to \Cat$ and $F' \maps \A' \to \Cat$, a finite colimit preserving functor $H \maps \A \to \A'$, a symmetric lax monoidal pseudofunctor $E \maps \Cat \to \Cat$ and a 2-isomorphism $\theta \maps EF \Rightarrow F^\prime H$ as in the following diagram, the triple $(H,E,\theta)$ induces a symmetric monoidal (strong) double functor $\mathbb{H} \maps F\mathbb{C}\textnormal{sp} \to F'\mathbb{C}\textnormal{sp}$ as defined above.
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$\A$};
 \node (B) at (1,0) {$\Cat$};
@@
 \begin{thm}\label{SC}
-Given a category $\X$ with finite colimits and a category $\mathsf{A}$ with finite coproducts and a finite coproduct preserving functor $L \maps \mathsf{A} \to \X$ with $\mathsf{A}$ and $\X$, there exists a symmetric monoidal double category $_L \mathbb{C}\textnormal{sp}(\X)$ which has:
+Given a category $\X$ with finite colimits and a category $\A$ with finite coproducts and a finite coproduct preserving functor $L \maps \A \to \X$ with $\A$ and $\X$, there exists a symmetric monoidal double category $_L \mathbb{C}\textnormal{sp}(\X)$ which has:
 \begin{itemize}
-\item{objects given by objects of $\mathsf{A}$,}
-\item{vertical 1-morphisms given by morphisms of $\mathsf{A}$,}
+\item{objects given by objects of $\A$,}
+\item{vertical 1-morphisms given by morphisms of $\A$,}
 \item{horizontal 1-cells $a\tickar b$ given by cospans of $\X$ of the form:
@@
 \end{itemize}
-Composition of horizontal 1-cells and 2-morphisms is given by pushouts in $\X$ and tensoring of objects is under binary coproducts in $\mathsf{A}$.
+Composition of horizontal 1-cells and 2-morphisms is given by pushouts in $\X$ and tensoring of objects is under binary coproducts in $\A$.
 \end{thm}
@@
 Suppose $\ca{A}$ is a finitely cocomplete category and $(F,\phi,\phi_0)\maps(\ca{A},+,0) \to (\bicat{Cat},\times,\mathbf{1})$ is a symmetric lax monoidal pseudofunctor that factors through $\bicat{Rex}$ as an ordinary pseudofunctor.
-Then the symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$ of decorated cospans given in \cref{thm:decoratedcospans} is equivalent to the symmetric monoidal double category $\scsp{L_F}{\inta F}$ of structured cospans given in \cref{SC}, where $L_F \maps \mathsf{A} \to \inta{F}$ is the left adjoint of the induced Grothendieck opfibration $\U_F\maps \inta{F} \to \mathsf{A}$.
+Then the symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$ of decorated cospans given in \cref{thm:decoratedcospans} is equivalent to the symmetric monoidal double category $\scsp{L_F}{\inta F}$ of structured cospans given in \cref{SC}, where $L_F \maps \A \to \inta{F}$ is the left adjoint of the induced Grothendieck opfibration $\U_F\maps \inta{F} \to \A$.
 %by \cref{thm:Grothendieck},
@@
 as follows.
-The object component of $\mathbb{E}=(\mathbb{E}_0,\mathbb{E}_1)$ is $\mathbb{E}_0 = \id_{\mathsf{A}}$ since both double categories have $\mathsf{A}$ as their vertical category; trivially, $\mathbb{E}_0$ is an equivalence of categories.
+The object component of $\mathbb{E}=(\mathbb{E}_0,\mathbb{E}_1)$ is $\mathbb{E}_0 = \id_{\A}$ since both double categories have $\A$ as their vertical category; trivially, $\mathbb{E}_0$ is an equivalence of categories.
 Given a horizontal 1-cell in $\scsp{L_F}{\inta F}$ like \cref{eq:scsphor1cell}, the arrow component $\mathbb{E}_1$ of the double functor simply maps it to the decorated cospan
@@
 \]
-where $R\maps \X \to \mathsf{A}$ is the right adjoint to the functor $L \maps \mathsf{A} \to \X$ and $\eta \maps 1_{\mathsf{A}} \to RL$ is the unit of the adjunction $L \dashv R$ which is an isomorphism since $L$ is fully faithful.
+where $R\maps \X \to \A$ is the right adjoint to the functor $L \maps \A \to \X$ and $\eta \maps 1_{\A} \to RL$ is the unit of the adjunction $L \dashv R$ which is an isomorphism since $L$ is fully faithful.
 \textbf{Hopefully...actually, it's a `lari'!} Similarly, the image of a 2-morphism $\alpha \maps M \to N$ in $_L \mathbb{C}\textnormal{sp}(\X)$:
@@
 \]
-is given by the 2-morphism $\mathbb{E}_1(\alpha) \maps \mathbb{E}_1(M) \to \mathbb{E}_1(N)$ in $\mathbb{F}\textnormal{Cospan}(\mathsf{A})$ given by:
+is given by the 2-morphism $\mathbb{E}_1(\alpha) \maps \mathbb{E}_1(M) \to \mathbb{E}_1(N)$ in $\mathbb{F}\textnormal{Cospan}(\A)$ given by:
 \[
@@
 \]
-together with a morphism $\tau \maps F(R(\alpha))(x) \to x^\prime$ in $F(R(x^\prime)) \subseteq \mathrm{X}$ which comes from the Grothendieck construction of the pseudofunctor $F \maps \mathsf{A} \to \Cat$.
+together with a morphism $\tau \maps F(R(\alpha))(x) \to x^\prime$ in $F(R(x^\prime)) \subseteq \mathrm{X}$ which comes from the Grothendieck construction of the pseudofunctor $F \maps \A \to \Cat$.
 That $\mathbb{E}_0$ is a functor is clear.
@@
 \]
-Thus the set $$_f { _L \mathbb{C}\textnormal{sp}(\X)}_g(M,N)$$ consists of triples $$(f,\alpha,g)$$ rendering the above diagram commutative where $f$ and $g$ are morphisms of $\mathsf{A}$ and $\alpha$ is a morphism of $\X$.
+Thus the set $$_f { _L \mathbb{C}\textnormal{sp}(\X)}_g(M,N)$$ consists of triples $$(f,\alpha,g)$$ rendering the above diagram commutative where $f$ and $g$ are morphisms of $\A$ and $\alpha$ is a morphism of $\X$.
 The image of the above 2-morphism under the double functor $\mathbb{E}$ is given by:
@@
 together with a morphism $\tau \maps F(R(\alpha))(x) \to x^\prime$ of $F(R(x^\prime))$.
-Thus the set $$_{\mathbb{E}(f)} {F\mathbb{C}\textnormal{sp}}_{\mathbb{E}(g)}(\mathbb{E}(M),\mathbb{E}(N))$$ consists of 4-tuples $$(f,R(\alpha),g,\tau)$$ rendering the above diagram commutative and where $f,g$ and $R(\alpha)$ are morphisms of $\mathsf{A}$ and $\tau$ is a morphism in $F(R(x'))$.
+Thus the set $$_{\mathbb{E}(f)} {F\mathbb{C}\textnormal{sp}}_{\mathbb{E}(g)}(\mathbb{E}(M),\mathbb{E}(N))$$ consists of 4-tuples $$(f,R(\alpha),g,\tau)$$ rendering the above diagram commutative and where $f,g$ and $R(\alpha)$ are morphisms of $\A$ and $\tau$ is a morphism in $F(R(x'))$.
 The morphisms $R(\alpha) \maps R(x) \to R(x^\prime)$ and $\tau \maps F(R(\alpha))(x) \to x^\prime$ together determine the morphism $\alpha \maps x \to x^\prime$ in $\mathrm{X}$ and conversely; given two objects $x=(c,x \in F(c))$ and $x^\prime=(c^\prime,x^\prime \in F(c^\prime))$ of $\X=\inta{F}$, a morphism from $\alpha \maps x \to x^\prime$ is a pair $$(h \maps c \to c^\prime, \tau \maps F(h)(x) \to x^\prime)$$ where $h \maps c \to c^\prime$ is given by $R(\alpha) \maps R(x) \to R(x^\prime)$.
@@
 together with a morphism of decorations which is obtained as follows.
-First, as $R \maps \X \to \mathsf{A}$ preserves finite colimits, we have an isomorphism $$\kappa \maps R(x) +_{R(L(c_2))} R(x^\prime) \to R(x+_{L(c_2)}x^\prime).$$ Also, since the left adjoint $L \maps \mathsf{A} \to \X$ is fully faithful, the unit of the adjunction $L \dashv R$ at the object $c_2$ gives an isomorphism $\eta_{c_2} \maps c_2 \to R(L(c_2))$ which results in an isomorphism $$j_{\eta_{c_2}} \maps R(x) +_{c_2} R(x^\prime) \to R(x) +_{R(L(c_2))} R(x^\prime).$$ Composing these two results in an isomorphism $$\sigma \mapseqq \kappa j_{\eta_{c_2}} \maps R(x) +_{c_2} R(x^\prime) \to R(x+_{L(c_2)}x^\prime).$$
+First, as $R \maps \X \to \A$ preserves finite colimits, we have an isomorphism $$\kappa \maps R(x) +_{R(L(c_2))} R(x^\prime) \to R(x+_{L(c_2)}x^\prime).$$ Also, since the left adjoint $L \maps \A \to \X$ is fully faithful, the unit of the adjunction $L \dashv R$ at the object $c_2$ gives an isomorphism $\eta_{c_2} \maps c_2 \to R(L(c_2))$ which results in an isomorphism $$j_{\eta_{c_2}} \maps R(x) +_{c_2} R(x^\prime) \to R(x) +_{R(L(c_2))} R(x^\prime).$$ Composing these two results in an isomorphism $$\sigma \mapseqq \kappa j_{\eta_{c_2}} \maps R(x) +_{c_2} R(x^\prime) \to R(x+_{L(c_2)}x^\prime).$$
 Next, to see that the above diagram commutes, it suffices to show that for the object $c_1 \in \mathrm{A}$, $$R(J)R(\zeta)R(i)\eta_{c_1}(c_1) = R(J \zeta i)\eta_{c_1}(c_1)  \stackrel{!}{=} \sigma j \psi R(i)\eta_{c_1}(c_1) = \kappa j_{\eta_{c_2}} \psi R(i) \eta_{c_1}(c_1).$$ This follows as $R(i) \eta_{c_1} \maps c_1 \to R(x)$ and the following diagram commutes:
@@
 
-Next, we show that if both double categories $_L \mathbb{C}\textnormal{sp}(\X)$ and $F\mathbb{C}\textnormal{sp}$ are symmetric monoidal, as they are if both $\mathsf{A}$ and $\X$ have finite colimits, then this equivalence of double categories $\mathbb{E} \maps _L \mathbb{C}\textnormal{sp}(\X) \to F\mathbb{C}\textnormal{sp}$ will be symmetric monoidal.
-First, note that we have an isomorphism $\epsilon \maps 1_{F\mathbb{C}\textnormal{sp}} \to \mathbb{E}(1_{_L \mathbb{C}\textnormal{sp}(\X)})$ and natural isomorphisms $\mu_{c_1,c_2} \maps \mathbb{E}(c_1) \otimes \mathbb{E}(c_2) \to \mathbb{E}(c_1 \otimes c_2)$ for every pair of objects $c_1,c_2 \in {_L \mathbb{C} \textnormal{sp}(\X)}$ both of which are given by identities since both double categories $_L \mathbb{C}\textnormal{sp}(\X)$ and $F\mathbb{C}\textnormal{sp}$ have $\mathsf{A}$ as their category of objects and $\mathbb{E}_0=\id_{\mathsf{A}}$.
+Next, we show that if both double categories $_L \mathbb{C}\textnormal{sp}(\X)$ and $F\mathbb{C}\textnormal{sp}$ are symmetric monoidal, as they are if both $\A$ and $\X$ have finite colimits, then this equivalence of double categories $\mathbb{E} \maps _L \mathbb{C}\textnormal{sp}(\X) \to F\mathbb{C}\textnormal{sp}$ will be symmetric monoidal.
+First, note that we have an isomorphism $\epsilon \maps 1_{F\mathbb{C}\textnormal{sp}} \to \mathbb{E}(1_{_L \mathbb{C}\textnormal{sp}(\X)})$ and natural isomorphisms $\mu_{c_1,c_2} \maps \mathbb{E}(c_1) \otimes \mathbb{E}(c_2) \to \mathbb{E}(c_1 \otimes c_2)$ for every pair of objects $c_1,c_2 \in {_L \mathbb{C} \textnormal{sp}(\X)}$ both of which are given by identities since both double categories $_L \mathbb{C}\textnormal{sp}(\X)$ and $F\mathbb{C}\textnormal{sp}$ have $\A$ as their category of objects and $\mathbb{E}_0=\id_{\A}$.
 The diagrams utilizing these maps that are required to commute do so trivially.
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$1_\mathsf{A}$};
-\node (B) at (1,0) {$1_\mathsf{A}$};
-\node (C) at (2,0) {$1_\mathsf{A}$};
-\node (D) at (3,0) {$!_{1_{\mathsf{A}}} \in F(1_\mathsf{A})$};
+\node (A) at (0,0) {$1_\A$};
+\node (B) at (1,0) {$1_\A$};
+\node (C) at (2,0) {$1_\A$};
+\node (D) at (3,0) {$!_{1_{\A}} \in F(1_\A)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-where $!_{1_{\mathsf{A}}} = \phi \maps 1 \to F(1_\mathsf{A})$ is the trivial decoration which comes from the structure of the symmetric lax monoidal pseudofunctor $F \maps \mathsf{A} \to \Cat$.
+where $!_{1_{\A}} = \phi \maps 1 \to F(1_\A)$ is the trivial decoration which comes from the structure of the symmetric lax monoidal pseudofunctor $F \maps \A \to \Cat$.
 The horizontal 1-cell $U_{1_{_L \mathbb{C}\textnormal{sp}(\X)}}$ is given by:
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$L(1_\mathsf{A})$};
-\node (B) at (1,0) {$L(1_\mathsf{A})$};
-\node (C) at (2,0) {$L(1_\mathsf{A})$};
+\node (A) at (0,0) {$L(1_\A)$};
+\node (B) at (1,0) {$L(1_\A)$};
+\node (C) at (2,0) {$L(1_\A)$};
 %\node (D) at (3,0.5) {$I \in F(1_\mathrm{A})$};
@@
 \]
-where here we make use of the fact that the left adjoint $L \maps (\mathsf{A},+,1_\mathsf{A}) \to (\X,+,1_\X)$ preserves all colimits and thus $L(1_\mathsf{A}) \cong 1_\X$.
+where here we make use of the fact that the left adjoint $L \maps (\A,+,1_\A) \to (\X,+,1_\X)$ preserves all colimits and thus $L(1_\A) \cong 1_\X$.
 The horizontal 1-cell $\mathbb{E}(U_{1_{_L \mathbb{C} \textnormal{sp}(\X)}})$ is then given by the pair:
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$1_\mathsf{A}$};
-\node (B) at (1.25,0) {$R(L(1_\mathsf{A}))$};
-\node (C) at (2.5,0) {$1_\mathsf{A}$};
-\node (D) at (4.5,0) {$!_{R(L(1_\mathsf{A}))} \in F(R(L(1_\mathsf{A})))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{${\eta_{1_\mathsf{A}}}$} (B)
-(C) edge node[above]{${\eta_{1_\mathsf{A}}}$} (B);
+\node (A) at (0,0) {$1_\A$};
+\node (B) at (1.25,0) {$R(L(1_\A))$};
+\node (C) at (2.5,0) {$1_\A$};
+\node (D) at (4.5,0) {$!_{R(L(1_\A))} \in F(R(L(1_\A)))$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{${\eta_{1_\A}}$} (B)
+(C) edge node[above]{${\eta_{1_\A}}$} (B);
 \end{tikzpicture}
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$1_\mathsf{A}$};
-\node (B) at (1,0) {$1_{\mathsf{A}}$};
-\node (C) at (2,0) {$1_\mathsf{A}$};
-\node (A') at (0,-1) {$1_\mathsf{A}$};
-\node (B') at (1,-1) {$R(L(1_\mathsf{A}))$};
-\node (C') at (2,-1) {$1_\mathsf{A}$};
-\node (D) at (3,0) {$!_{1_\mathsf{A}} \in F(1_\mathsf{A})$};
-\node (D') at (3.75,-1) {$!_{R(L(1_\mathsf{A}))} \in F(R(L(1_\mathsf{A})))$};
+\node (A) at (0,0) {$1_\A$};
+\node (B) at (1,0) {$1_{\A}$};
+\node (C) at (2,0) {$1_\A$};
+\node (A') at (0,-1) {$1_\A$};
+\node (B') at (1,-1) {$R(L(1_\A))$};
+\node (C') at (2,-1) {$1_\A$};
+\node (D) at (3,0) {$!_{1_\A} \in F(1_\A)$};
+\node (D') at (3.75,-1) {$!_{R(L(1_\A))} \in F(R(L(1_\A)))$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (C) edge node[above]{$1$} (B)
-(A') edge node[above]{${\eta_{1_\mathsf{A}}}$} (B')
-(C') edge node[above]{${\eta_{1_\mathsf{A}}}$} (B')
+(A') edge node[above]{${\eta_{1_\A}}$} (B')
+(C') edge node[above]{${\eta_{1_\A}}$} (B')
 (A) edge node [left]{$1$} (A')
-(B) edge node [left]{${\eta_{1_\mathsf{A}}}$} (B')
+(B) edge node [left]{${\eta_{1_\A}}$} (B')
 (C) edge node [left]{$1$} (C');
@@
 \]
-$$\tau_{{\eta_{1_\mathsf{A}}}} \maps F({\eta_{1_\mathsf{A}}})(!_{1_\mathsf{A}})) \to !_{R(L(1_\mathsf{A}))}$$
-of $F\mathbb{C}\textnormal{sp}$. This is just the natural isomorphism $\mathbb{E}_{1_\mathsf{A}}$ from earlier.
+$$\tau_{{\eta_{1_\A}}} \maps F({\eta_{1_\A}})(!_{1_\A})) \to !_{R(L(1_\A))}$$
+of $F\mathbb{C}\textnormal{sp}$. This is just the natural isomorphism $\mathbb{E}_{1_\A}$ from earlier.
 
@@
 \]
-where $\kappa$ is the isomorphism which comes from $R \maps \X \to \mathsf{A}$ preserving finite colimits.
+where $\kappa$ is the isomorphism which comes from $R \maps \X \to \A$ preserving finite colimits.
 
@@
 			\node (d) at (7.5,0) {$\mathbb{E}(1_{ _L \mathbb{C}\textnormal{sp}(\X)}) \otimes \mathbb{E}(M_1)$};
-			\node (a) at (-6,0) {$1_\mathsf{A}+c_1$};
-			\node (b) at (-0.5,0) {$R(L(1_\mathsf{A})) + R(x_1)$};
-			\node (c) at (5,0) {$1_\mathsf{A}+c_1^\prime$};
+			\node (a) at (-6,0) {$1_\A+c_1$};
+			\node (b) at (-0.5,0) {$R(L(1_\A)) + R(x_1)$};
+			\node (c) at (5,0) {$1_\A+c_1^\prime$};
 			\node (d2) at (7.5,1) {$1_{F\mathbb{C}\textnormal{sp}} \otimes \mathbb{E}(M_1)$};
-			\node (a2) at (-6,1) {$1_\mathsf{A}+c_1$};
-			\node (b2) at (-0.5,1) {$1_\mathsf{A}+R(x_1)$};
-			\node (c2) at (5,1) {$1_\mathsf{A}+c_1^\prime$};
+			\node (a2) at (-6,1) {$1_\A+c_1$};
+			\node (b2) at (-0.5,1) {$1_\A+R(x_1)$};
+			\node (c2) at (5,1) {$1_\A+c_1^\prime$};
 			\node (d3) at (7.5,2) {$\mathbb{E}(M_1)$};
@@
 			\node (d4) at (7.5,-1) {$\mathbb{E}(1_{ _L \mathbb{C}\textnormal{sp}(\X)} \otimes M_1)$};
-                                \node (a5) at (-6,-1) {$1_\mathsf{A}+c_1^\prime$};
-			\node (b5) at (-0.5,-1) {$R(L(1_\mathsf{A})+x_1)$};
-			\node (c5) at (5,-1) {$1_\mathsf{A}+c_1^\prime$};
+                                \node (a5) at (-6,-1) {$1_\A+c_1^\prime$};
+			\node (b5) at (-0.5,-1) {$R(L(1_\A)+x_1)$};
+			\node (c5) at (5,-1) {$1_\A+c_1^\prime$};
 			\node (d5) at (7.5,-2) {$\mathbb{E}(M_1)$};
@@
 			(d4) edge node [left] {$\mathbb{E}(\lambda)$} (d5)
-			(a) edge node[above]{$\eta_{1_\mathsf{A}}+R(i_1)\eta_{c_1}$} (b)
-			(c) edge node[above]{$\eta_{1_\mathsf{A}}+R(o_1)\eta_{c_1^\prime}$} (b)
+			(a) edge node[above]{$\eta_{1_\A}+R(i_1)\eta_{c_1}$} (b)
+			(c) edge node[above]{$\eta_{1_\A}+R(o_1)\eta_{c_1^\prime}$} (b)
                                 (a2) edge node[above]{$1+R(i_1)\eta_{c_1}$} (b2)
@@
                                 (a2) edge node[left]{$1$} (a)
-                                (b2) edge node[left]{$\eta_{1_\mathsf{A}}+1$} (b)
+                                (b2) edge node[left]{$\eta_{1_\A}+1$} (b)
 (b2) edge node[right]{$\tau_2$} (b)
@@
 			(c3) edge node[above]{$R(o_1)\eta_{c_1^\prime}$} (b3)
-                                (a2) edge node[left]{$\lambda_{\mathsf{A}}$} (a3)
-                                (b2) edge node[left]{$\lambda_{\mathsf{A}}$} (b3)
+                                (a2) edge node[left]{$\lambda_{\A}$} (a3)
+                                (b2) edge node[left]{$\lambda_{\A}$} (b3)
 (b2) edge node[right]{$\tau_1$} (b3)
-			(c2) edge node[right]{$\lambda_{\mathsf{A}}$} (c3)
-                                (a5) edge node[above]{$(\mu_{L(1_\mathsf{A}),d_1})(\eta_{1_\mathsf{A}}+R(i_1)\eta_{c_1})$} (b5)
-			(c5) edge node[above]{$(\mu_{L(1_\mathsf{A}),d_1})(\eta_{1_\mathsf{A}}+R(o_1)\eta_{c_1^\prime})$} (b5)
+			(c2) edge node[right]{$\lambda_{\A}$} (c3)
+                                (a5) edge node[above]{$(\mu_{L(1_\A),d_1})(\eta_{1_\A}+R(i_1)\eta_{c_1})$} (b5)
+			(c5) edge node[above]{$(\mu_{L(1_\A),d_1})(\eta_{1_\A}+R(o_1)\eta_{c_1^\prime})$} (b5)
                                 (a) edge node[left]{$1$} (a5)
-                                (b) edge node[left]{$\mu_{L(1_\mathsf{A}),x_1}$} (b5)
+                                (b) edge node[left]{$\mu_{L(1_\A),x_1}$} (b5)
 (b) edge node[right]{$\tau_3$} (b5)
@@
 			(c6) edge node[above]{$R(o_1)\eta_{c_1^\prime}$} (b6)
-                                (a5) edge node[left]{$\lambda_{\mathsf{A}}$} (a6)
+                                (a5) edge node[left]{$\lambda_{\A}$} (a6)
                                 (b5) edge node[left]{$R(\lambda_{\X})$} (b6)
  (b5) edge node[right]{$\tau_4$} (b6)
-			(c5) edge node[right]{$\lambda_{\mathsf{A}}$} (c6);
+			(c5) edge node[right]{$\lambda_{\A}$} (c6);
 		\end{tikzpicture}
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (-.5,0) {$F(\lambda_{\mathsf{A}})(!_{1_\mathsf{A}}+x_1)$};
-\node (C) at (4,0) {$F(R(\lambda_{\X})(\mu_{L(1_\mathsf{A}),x_1}))(!_{R(L(1_\mathsf{A}))} +x_1$)};
+\node (A) at (-.5,0) {$F(\lambda_{\A})(!_{1_\A}+x_1)$};
+\node (C) at (4,0) {$F(R(\lambda_{\X})(\mu_{L(1_\A),x_1}))(!_{R(L(1_\A))} +x_1$)};
 \node (D) at (-.5,-1) {$x_1$};
@@
 \path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$F(R(\lambda_{\X})(\mu_{L(1_\mathsf{A}),x_1}))(\tau_2)$} (C)
+(A) edge node[above]{$F(R(\lambda_{\X})(\mu_{L(1_\A),x_1}))(\tau_2)$} (C)
 (A) edge node[left]{$\tau_1$} (D)
@@
 \]
-where $x_{!+1}$ is the decoration $x_1$ on the object $R(L(1_\mathsf{A})+x_1) \in \mathsf{A}$.
-The above square commutes because $$F(\lambda_\mathsf{A})(!_{1_\mathsf{A}}+x_1) = F(R(\lambda_\X)(\mu_{L(1_\mathsf{A}),x_1})(\eta_{1_\mathsf{A}}+1))(!_{1_\mathsf{A}}+x_1)$$ as the corresponding left unitality square for the finite colimit preserving functor $R \maps (\X,1_\X,+) \to (\mathsf{A},1_\mathsf{A},+)$ commutes.
+where $x_{!+1}$ is the decoration $x_1$ on the object $R(L(1_\A)+x_1) \in \A$.
+The above square commutes because $$F(\lambda_\A)(!_{1_\A}+x_1) = F(R(\lambda_\X)(\mu_{L(1_\A),x_1})(\eta_{1_\A}+1))(!_{1_\A}+x_1)$$ as the corresponding left unitality square for the finite colimit preserving functor $R \maps (\X,1_\X,+) \to (\A,1_\A,+)$ commutes.
 The right unitality square is similar.
@@
 			(c4) edge node[above]{$R(o_1+(o_2+o_3))\eta_{c_1^\prime+(c_2^\prime+c_3^\prime)}$} (b4)
-                                (a3) edge node[left]{$a_\mathsf{A}$} (a4)
+                                (a3) edge node[left]{$a_\A$} (a4)
                                 (b3) edge node[left]{$R(a_\X)$} (b4)
 (b3) edge node[right]{$\tau_3$} (b4)
-			(c3) edge node[right]{$a_\mathsf{A}$} (c4)
+			(c3) edge node[right]{$a_\A$} (c4)
                                 (a5) edge node[above]{$R(i_1)\eta_{c_1}+(R(i_2)\eta_{c_2}+R(i_3)\eta_{c_3})$} (b5)
 			(c5) edge node[above]{$R(o_1)\eta_{c_1^\prime}+(R(o_2)\eta_{c_2^\prime}+R(o_3)\eta_{c_3^\prime})$} (b5)
-                                (a) edge node[left]{$a_\mathsf{A}$} (a5)
-                                (b) edge node[left]{$a_\mathsf{A}$} (b5)
+                                (a) edge node[left]{$a_\A$} (a5)
+                                (b) edge node[left]{$a_\A$} (b5)
 (b) edge node[right]{$\tau_4$} (b5)
-			(c) edge node[right]{$a_\mathsf{A}$} (c5)
+			(c) edge node[right]{$a_\A$} (c5)
                                 (a6) edge node[above]{$R(i_1)\eta_{c_1}+R(i_2+i_3)\eta_{c_2+c_3}$} (b6)
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$F((\kappa)(1+\kappa)(a_\mathsf{A}))((x_1+x_2)+x_3)$};
+\node (A) at (0,0) {$F((\kappa)(1+\kappa)(a_\A))((x_1+x_2)+x_3)$};
 \node (B) at (5,0) {$F((R(a_\mathrm{X}))(\kappa))((x_1+x_2)+x_3)$};
@@
 \]
-The above square commutes because $$F((\kappa)(1+\kappa)(a_\mathsf{A}))((x_1+x_2)+x_3) = F((R(a_\X))(\kappa)(\kappa+1))((x_1+x_2)+x_3)$$ as the corresponding associator hexagon for the finite colimit preserving functor $R \maps (\X,1_\X,+) \to (\mathsf{A},1_\mathsf{A},+)$ commutes.
+The above square commutes because $$F((\kappa)(1+\kappa)(a_\A))((x_1+x_2)+x_3) = F((R(a_\X))(\kappa)(\kappa+1))((x_1+x_2)+x_3)$$ as the corresponding associator hexagon for the finite colimit preserving functor $R \maps (\X,1_\X,+) \to (\A,1_\A,+)$ commutes.
 Lastly, the braiding square:
@@
 			(c2) edge node[above]{$R(o_2) \eta_{c_2^\prime} + R(o_1) \eta_{c_1^\prime}$} (b2)
-                                (a) edge node[left]{$\beta_\mathsf{A}$} (a2)
-                                (b) edge node[left]{$\beta_\mathsf{A}$} (b2)
+                                (a) edge node[left]{$\beta_\A$} (a2)
+                                (b) edge node[left]{$\beta_\A$} (b2)
 (b) edge node[right]{$\tau_1$} (b2)
-			(c) edge node[right]{$\beta_\mathsf{A}$} (c2)
+			(c) edge node[right]{$\beta_\A$} (c2)
                                 (a3) edge node[above]{$R(i_2+i_1)\eta_{c_2+c_1}$} (b3)
@@
 			(c6) edge node[above]{$R(o_2+o_1)\eta_{c_2^\prime+c_1^\prime}$} (b6)
-                                (a5) edge node[left]{$\beta_\mathsf{A}$} (a6)
+                                (a5) edge node[left]{$\beta_\A$} (a6)
                                 (b5) edge node[left]{$R(\beta_\X)$} (b6)
  (b5) edge node[right]{$\tau_4$} (b6)
-			(c5) edge node[right]{$\beta_\mathsf{A}$} (c6);
+			(c5) edge node[right]{$\beta_\A$} (c6);
 		\end{tikzpicture}
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (-.5,0) {$F((\kappa)(\beta_\mathsf{A}))(x_1+x_2)$};
+\node (A) at (-.5,0) {$F((\kappa)(\beta_\A))(x_1+x_2)$};
 \node (C) at (4,0) {$F(\kappa)(x_2+x_1)$};
@@
 \]
-The above square commutes because $$F((\kappa)(\beta_\mathsf{A}))(x_1+x_2) = F((R(\beta_\X))(\kappa))(x_1+x_2)$$ as the corresponding braiding square for the finite colimit preserving functor $R \maps (\X,1_\X,+) \to (\mathsf{A},1_\mathsf{A},+)$ commutes.
+The above square commutes because $$F((\kappa)(\beta_\A))(x_1+x_2) = F((R(\beta_\X))(\kappa))(x_1+x_2)$$ as the corresponding braiding square for the finite colimit preserving functor $R \maps (\X,1_\X,+) \to (\A,1_\A,+)$ commutes.
 Thus the double functor $\mathbb{E} \maps _L\mathbb{C}\textnormal{sp}(\X) \to F\mathbb{C}\textnormal{sp}$ is symmetric monoidal.
@@
 \begin{enumerate}
-\item{objects as those of $\mathsf{A}$,}
+\item{objects as those of $\A$,}
 \item{morphisms as horizontal 1-cells of $F\mathbb{C}\textnormal{sp}$, and}
@@
 \begin{enumerate}
-\item{objects as those of $\mathsf{A}$,}
+\item{objects as those of $\A$,}
 \item{morphisms as horizontal 1-cells of $_L \mathbb{C}\textnormal{sp}(\X)$, and}
@@
 \begin{comment}
-We can also define the part of the double equivalence $\mathbb{G} \maps F\mathbb{C}\textnormal{sp} \to {_L \mathbb{C} \textnormal{sp}(\X)}$ which goes in the other direction: again, the object component of this double functor will be $\mathbb{G}_0 = \id_{\mathsf{A}}$.
+We can also define the part of the double equivalence $\mathbb{G} \maps F\mathbb{C}\textnormal{sp} \to {_L \mathbb{C} \textnormal{sp}(\X)}$ which goes in the other direction: again, the object component of this double functor will be $\mathbb{G}_0 = \id_{\A}$.
 
@@
 First we compute the composites $\mathbb{G} \mathbb{E}$ and $\mathbb{E} \mathbb{G}$.
-On the object categories, both composites are $\id_\mathsf{A}$ and we have natural isomorphisms $\eta \maps \id_{\mathsf{A}} \cong \mathbb{G}_0 \mathbb{E}_0$ and $\epsilon \maps \mathbb{E}_0 \mathbb{G}_0 \cong \id_{\mathsf{A}}$.
+On the object categories, both composites are $\id_\A$ and we have natural isomorphisms $\eta \maps \id_{\A} \cong \mathbb{G}_0 \mathbb{E}_0$ and $\epsilon \maps \mathbb{E}_0 \mathbb{G}_0 \cong \id_{\A}$.
 

### 2020-11-11 cospans.tex
polished bibliography

@@
 
-An `open system' is any sort of system that can interact with the outside world.  Open systems
-are nicely modeled using cospans, which are diagrams of this form:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a_1$};
-\node (B) at (1,1) {$b$};
-\node (C) at (2,0) {$a_2$};
+An `open system' is any sort of system that can interact with the outside world.
+Experience has shown that open systems are nicely modeled using cospans \cite{CourserThesis, FongThesis, PollardThesis}.
+A cospan in some category $\A$ is a diagram of this form:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$a$};
+\node (B) at (1,1) {$m$};
+\node (C) at (2,0) {$b$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-We call $b$ the \define{apex}, $a_1$ and $a_2$ the \define{feet}, and $i$ and $o$ the \define{legs}.
-The feet describe `interfaces' of the corresponding open system, while the apex describes the system itself.
+We call $m$ the \define{apex}, $a$ and $b$ the \define{feet}, and $i$ and $o$ the \define{legs} of the cospan.
+The apex describes the system itself.
+The feet describe `interfaces'  through which the system can interact with the outside world.
+The legs describe how the interfaces are included in the system.
+If the category $\A$ has finite colimits we can compose cospans using pushouts: this describes the operation of attaching tw open systems together `in series' by identifying one interface of the first with one of the second.
+We can also `tensor' cospans using coproducts: this describes setting open systems side by side, `in parallel'.
+Via these operations we obtain a symmetric monoidal double category with cospans in $\A$ as its horizontal 1-cells \cite{Courser,Niefield}.
+
 However, we often want the system itself to have more structure than its interfaces.
 This led Fong to develop a theory of `decorated' cospans \cite{Fong}.
-
-Given a category $\A$ with finite colimits, a symmetric lax monoidal functor $F \maps (\A,+,0) \to (\textsf{Set},\times,1)$ can be used to `decorate' the apex of a cospan in $\A$ with some extra data: an element of the image of its apex under $F$.
-In the case of the cospan above, this would be an element $d \in F(b)$, which we call a \textbf{decoration} on $b$.
+Given a category $\A$ with finite colimits, a symmetric lax monoidal functor $F \maps (\A,+,0) \to (\textsf{Set},\times,1)$ can be used to `decorate' the apex $m$ of a cospan in $\A$ with some extra data: an element $d \in F(m)$, which we call a \textbf{decoration}.
 Thus a decorated cospan is given by a pair:
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a_1$};
-\node (B) at (1,0) {$b$};
-\node (C) at (2,0) {$a_2$};
+\node (A) at (0,0) {$a$};
+\node (B) at (1,0) {$m$};
+\node (C) at (2,0) {$b$};
 \node (D) at (3,0) {$1$};
-\node (E) at (4,0) {$F(b)$};
+\node (E) at (4,0) {$F(m)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-To obtain a decoration on the composition of two composable $F$-decorated cospans:
+To obtain a decoration on the composition of two composable decorated cospans:
 \[
@@
 we use the natural map from a coproduct to a pushout as well as the structure maps, or `laxators', that come as part of the structure of a lax monoidal functor:
- $$1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{d_1 \times d_2} F(b) \times F(b^\prime) \xrightarrow{\phi_{b,b^\prime}} F(b+ b^\prime) \xrightarrow{F(j_{b,b^\prime})} F(b+_{a_2} b^\prime).$$
-From this symmetric lax monoidal functor $F \maps \A \to \mathsf{Set}$, Fong then constructs a symmetric monoidal category $F\textnormal{Cospan}(\A)$ which has:
+\[
+1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{d_1 \times d_2} F(b) \times F(b^\prime) \xrightarrow{\phi_{b,b^\prime}} F(b+ b^\prime) \xrightarrow{F(j_{b,b^\prime})} F(b+_{a_2} b^\prime).
+\]
+Using this idea, Fong constructed a symmetric monoidal category $F\textnormal{Cospan}(\A)$ which has:
 \begin{enumerate}
@@
 
-Details of the constructions and the proof of the above theorem can be found at \cite{CourPhD}.
+Details of the constructions and the proof of the above theorem can be found at \cite{CourserThesis}.
 
@@
 
-\bibitem{BC} J.\ C.\ Baez and K.\ Courser, Coarse-graining open Markov processes. Available as \href{https://arxiv.org/abs/1710.11343}{arXiv:1710.11343}.
-
-\bibitem{BC2} J.\ C.\ Baez and K.\ Courser, Structured cospans. In preparation. THIS IS FINISHED!
-
-\bibitem{BCR} J.\ C.\ Baez, B.\ Coya and F.\ Rebro, Props in circuit theory. In preparation. THIS IS FINISHED!!!
-
-\bibitem{BF} J.\ C.\ Baez and B.\ Fong, A compositional framework for passive linear networks. Available as \href{http://arxiv.org/abs/1504.05625}{arXiv:1504.05625}.
-
-\bibitem{BFP} J.\ C.\ Baez, B.\ Fong and B.\ Pollard, A compositional framework for Markov processes, \textsl{Jour.
+\bibitem{BC} J.\ C.\ Baez and K.\ Courser, Coarse-graining open Markov processes, \textsl{Theory Appl.\ Categ.\ }\textbf{33} (2018), 1223--1268.
+Available as \href{https://arxiv.org/abs/1710.11343}{arXiv:1710.11343}.
+
+\bibitem{BC2} J.\ C.\ Baez and K.\ Courser, Structured cospans,  \textsl{Theory Appl.\ Categ.\ }\textbf{35} (2020), 1771–1822.   Available as \href{http://arxiv.org/abs/1911.04630}{arXiv:1911.04630}.
+
+\bibitem{BCR} J.\ C.\ Baez, B.\ Coya and F.\ Rebro, Props in circuit theory, \textsl{Theory Appl.\ Categ.\ }\textbf{33} (2018), 727--783.
+Available as \href{https://arxiv.org/abs/1707.08321}{arXiv:1707.08321}.
+
+\bibitem{BF}  J.\ C.\ Baez and B.\ Fong, A compositional framework for passive linear networks, \textsl{Theory Appl.\ Categ.\ }\textbf{33} (2018), 1158--1222.
+Available as \href{http://arxiv.org/abs/1504.05625}{arXiv:1504.05625}.
+
+\bibitem{BFP} J.\ C.\ Baez, B.\ Fong and B.\ S.\ Pollard, A compositional framework for Markov processes, \textsl{Jour.
 Math.
@@
 
-\bibitem{BM} J.\ C. \ Baez and J.\ Master, Open Petri nets. Available as \href{https://arxiv.org/abs/1808.05415}{arXiv:1808.05415}.
-
-\bibitem{BP} J.\ C.\ Baez and B.\ Pollard, A compositional framework for chemical reaction networks, in preparation.
-
-\bibitem{Borc} F. \ Borceux, Handbook of categorical algebra. 2, volume 51 of Encyclopedia of Mathematics and its Applications,
-Cambridge University Press, 1994
+\bibitem{BM}  J.\ C.\ Baez and J.\ Master, Open Petri nets, \textsl{Math.\ Struct.\ Comput.\ Sci.\ }\textbf{30} (2020), 314--341. Available as 
+\href{https://arxiv.org/abs/1808.05415}{arXiv:1808.05415}.
+
+\bibitem{BP} J.\ C.\ Baez and B.\ S.\ Pollard, A compositional framework for chemical reaction networks, \textsl{Rev.\ Math.\ Phys.\ }\textbf{29} (2017), 1750028.
+Available as \href{http://arxiv.org/abs/1704.02051}{arXiv:1704.02051}.
+
+\bibitem{Borc} F. \ Borceux, \textsl{Handbook of Categorical Algebra}, vol.\ 2, 
+Cambridge University Press, Cambridge, 1994
 
@@
 
-\bibitem{CV} D.\ Cicala and C.\ Vasilakopoulou, On Adjoints and Fibrations. In preparation.
-
-\bibitem{Cour} K.\ Courser, A bicategory of decorated cospans, \emph{Theor.\ Appl.\ Cat.} \textbf{32} (2017), 995--1027. Also available as \href{https://arxiv.org/abs/1605.08100}{arXiv:1605.08100}.
-
-\bibitem{CourPhD} K.\ Courser, Open Systems: a Double Categorical Perspective, PhD Thesis, University of California at Riverside (2019)
-
-\bibitem{DS} B.\ Day and R.\ Street, Monoidal Bicategories and Hopf Algebroids, \emph{Adv. Math.}, 129(1):99--157, 1997.
+\bibitem{CV} D.\ Cicala and C.\ Vasilakopoulou, On Adjoints and fibrations. In preparation.
+
+\bibitem{Courser} K.\ Courser, A bicategory of decorated cospans, \emph{Theory Appl.\ Categ.} \textbf{32} (2017), 995--1027. Available as \href{https://arxiv.org/abs/1605.08100}{arXiv:1605.08100}.
+
+\bibitem{CourserThesis} K.\ Courser, \textsl{Open Systems: a Double Categorical Perspective}, Ph.D.\ thesis, Department of Mathematics, U.\ C.\ Riverside, 2020.
+Available as \href{https://arxiv.org/abs/2008.02394}{arxiv:2008.02394}.
+
+\bibitem{DS} B.\ Day and R.\ Street, Monoidal Bicategories and Hopf algebroids, \textsl{Adv.\ Math.} \textbf{129} (1997), 99--157.
+
 %\bibitem{Ehresmann63} C.\ Ehresmann, Cat\'egories structur\'ees III: Quintettes et applications covariantes,  \textsl{Cah.\ Top.\ G\'eom.\ Diff.} \textbf{5} (1963), 1--22.
@@
 
-\bibitem{Fong} B.\ Fong, Decorated cospans, \emph{Theor.\ Appl.\ Cat.} \textbf{30} (2015), 1096--1120. Also available as \href{http://arxiv.org/abs/1502.00872}{arXiv:1502.00872}.
+\bibitem{Fong} B.\ Fong, Decorated cospans, \emph{Theory Appl.\ Categ.} \textbf{30} (2015), 1096--1120.  Available as \href{http://arxiv.org/abs/1502.00872}{arXiv:1502.00872}.
+
+\bibitem{FongThesis} B.\ Fong, \textsl{The Algebra of Open and Interconnected Systems},
+Ph.D.\ thesis, Computer Science Department, University of Oxford, 2016.
+Available as \href{https://arxiv.org/abs/1609.05382}{arXiv:1609.05382}.
 
@@
 
-%\bibitem{Pol} B.\ Pollard, Open Markov processes: A compositional perspective on non-equilibrium steady states in biology, %%%\emph{Entropy} $\mathbf{18}$ (2016), 140.
-Available as \href{http://arxiv.org/abs/1601.00711}{arXiv:1601.00711}.
-
-%\bibitem{Nie}
-%S.~Niefield,
-%Span, cospan, and other double categories.
-%\textsl{Theory Appl.\ Categ.}
-%\textbf{26} (2012), 729--742.
-%Available as \href{https://arxiv.org/abs/1201.3789}{arXiv:1201.3789}.
+\bibitem{Niefield} S.~Niefield, Span, cospan, and other double categories, \textsl{Theory Appl.\ Categ.} \textbf{26} (2012), 729--742.
+Available as \href{https://arxiv.org/abs/1201.3789}{arXiv:1201.3789}.
 
 %\bibitem{Panan} F.\ Clerc, H.\ Humphrey and P.\ Panangaden, Bicategories of Markov processes,  to appear.
+
+\bibitem{PollardThesis} B.\ S.\ Pollard, \textsl{Open Markov Processes and Reaction Networks}, Ph.D.
+thesis, U.
+C.
+Riverside, 2017.
+Available as \href{https://arxiv.org/abs/1709.09743}{arXiv:1709.09743}.
 

### 2020-11-11 cospans.tex
wrote a new introduction

@@
 The legs describe how the interfaces are included in the system.
-If the category $\A$ has finite colimits we can compose cospans using pushouts: this describes the operation of attaching tw open systems together `in series' by identifying one interface of the first with one of the second.
-We can also `tensor' cospans using coproducts: this describes setting open systems side by side, `in parallel'.
+If the category $\A$ has finite colimits, we can compose cospans using pushouts: this describes the operation of attaching two open systems together in series by identifying one interface of the first with one of the second.
+We can also `tensor' cospans using coproducts: this describes setting open systems side by side, in parallel.
 Via these operations we obtain a symmetric monoidal double category with cospans in $\A$ as its horizontal 1-cells \cite{Courser,Niefield}.
@@
 This led Fong to develop a theory of `decorated' cospans \cite{Fong}.
-Given a category $\A$ with finite colimits, a symmetric lax monoidal functor $F \maps (\A,+,0) \to (\textsf{Set},\times,1)$ can be used to `decorate' the apex $m$ of a cospan in $\A$ with some extra data: an element $d \in F(m)$, which we call a \textbf{decoration}.
-Thus a decorated cospan is given by a pair:
+Given a category $\A$ with finite colimits, a symmetric lax monoidal functor $F \maps (\A,+) \to (\textsf{Set},\times)$ can be used to equip the apex $m$ of a cospan in $\A$ with some extra data: an element $d \in F(m)$, which we call a \textbf{decoration}.
+Thus a \define{decorated cospan} is a pair:
 \[
@@
 \node (B) at (1,0) {$m$};
-\node (C) at (2,0) {$b$};
-\node (D) at (3,0) {$1$};
-\node (E) at (4,0) {$F(m)$};
+\node (C) at (2,0) {$b$,};
+\node (E) at (4,0) {$d \in F(m)$.};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i$} (B)
+(C) edge node[above]{$o$} (B);
+\end{tikzpicture}
+\]
+Fong proved that there is a symmetric monoidal category with objects
+of $\A$ as its objects and equivalence classes of decorated cospans as its morphisms.
+Such categories were used to describe a variety of open systems: electrical circuits, Markov processes, chemical reaction networks and dynamical systems \cite{BF,BFP,BP}.
+Later the second author improved Fong's categories to symmetric monoidal double categories, eliminating the need to work with equivalence classes \cite{Courser}.
+
+Unfortunately, many applications of decorated cospans were flawed.
+The problem is that while Fong's decorated cospans are good for decorating the apex $m$ with an element of a set $F(m)$, they are unable to decorate it with an object of a category.
+An example would be equipping a finite set $m$ with edges making its elements into the nodes of a graph.
+We would like the following `open graph' to be a decorated cospan with $m = \{n_1, n_2, n_3, n_4\}$:
+\[
+\scalebox{0.8}{
+\begin{tikzpicture}
+	\begin{pgfonlayer}{nodelayer}
+		\node [contact] (n1) at (-2,0) {$\bullet$};
+		\node [style = none] at (-2.1,0.3) {$n_1$};
+		\node [contact] (n2) at (0,1) {$\bullet$};
+		\node [style = none] at (0,1.3) {$n_2$};
+		\node [contact] (n3) at (0,-1) {$\bullet$};
+		\node [style = none] at (0,-1.3) {$n_3$};
+		\node [contact] (n4) at (2,0) {$\bullet$};
+		\node [style = none] at (2.1,0.3) {$n_4$};
+
+		\node [style = none] at (-1,1) {$e_1$};
+		\node [style = none] at (-1,-1) {$e_2$};
+		\node [style = none] at (1,1) {$e_3$};
+		\node [style = none] at (1,-1) {$e_4$};
+	    \node [style = none] at (0.3,0) {$e_5$};
+
+		\node [style=none] (1) at (-3,0) {1};
+		\node [style=none] (4) at (3,0) {2};
+
+		\node [style=none] (ATL) at (-3.4,1.4) {};
+		\node [style=none] (ATR) at (-2.6,1.4) {};
+		\node [style=none] (ABR) at (-2.6,-1.4) {};
+		\node [style=none] (ABL) at (-3.4,-1.4) {};
+
+		\node [style=none] (X) at (-3,1.8) {$a$};
+		\node [style=inputdot] (inI) at (-2.8,0) {};
+
+		\node [style=none] (Z) at (3,1.8) {$b$};
+	 \node [style=inputdot] (outI') at (2.8,0) {};
+
+		\node [style=none] (MTL) at (2.6,1.4) {};
+		\node [style=none] (MTR) at (3.4,1.4) {};
+		\node [style=none] (MBR) at (3.4,-1.4) {};
+		\node [style=none] (MBL) at (2.6,-1.4) {};
+
+	\end{pgfonlayer}
+	\begin{pgfonlayer}{edgelayer}
+		\draw [style=inarrow, bend left=20, looseness=1.00] (n1) to (n2);
+		\draw [style=inarrow, bend right=20, looseness=1.00] (n1) to (n3);
+		\draw [style=inarrow, bend left=20, looseness=1.00] (n2) to (n4);
+		\draw [style=inarrow, bend right=20, looseness=1.00] (n3) to (n4);
+		\draw [style=inarrow] (n2) to (n3);
+%		\draw [style=inarrow] (W) to (Water);
+%		\draw [style=inarrow, bend left=40, looseness=1.00] (Water2) to (Something);
+%		\draw [style=inarrow, bend right=40, looseness=1.00] (Water2) to (Something);
+%		\draw [style=inarrow, bend left=40, looseness=1.00] (Something) to (A);
+%		\draw [style=inarrow, bend right=40, looseness=1.00] (Something) to (B);
+		\draw [style=simple] (ATL.center) to (ATR.center);
+		\draw [style=simple] (ATR.center) to (ABR.center);
+		\draw [style=simple] (ABR.center) to (ABL.center);
+		\draw [style=simple] (ABL.center) to (ATL.center);
+%		\draw [style=simple] (BTL.center) to (BTR.center);
+%		\draw [style=simple] (BTR.center) to (BBR.center);
+%		\draw [style=simple] (BBR.center) to (BBL.center);
+%		\draw [style=simple] (BBL.center) to (BTL.center);
+		\draw [style=simple] (MTL.center) to (MTR.center);
+		\draw [style=simple] (MTR.center) to (MBR.center);
+		\draw [style=simple] (MBR.center) to (MBL.center);
+		\draw [style=simple] (MBL.center) to (MTL.center);
+%		\draw [style=inputarrow] (outI) to (A);
+%		\draw [style=inputarrow] (outS) to (B);
+		\draw [style=inputarrow] (inI) to (n1);
+		\draw [style=inputarrow] (outI') to (n4);
+%		\draw [style=inputarrow] (inI') to (Water2);
+%		\draw [style=inputarrow] (inS') to (Water2);
+	\end{pgfonlayer}
+\end{tikzpicture}
+}
+\]
+We might hope to do this using symmetric lax monoidal functor $F \maps (\Fin\Set, +) \to (\Set, \times)$ assiging to each finite set $m$ the set of all graphs with $m$ as their set of nodes    But this hope is doomed, for reasons painstakingly explained in \cite[Sec.\ 5]{BC}.
+There is really a \emph{category} of graphs with $m$ as their set of nodes, and trying to treat it as a mere set does not work.
+
+Here we present a solution to this problem.
+Instead of basing the theory of decorated cospans on a symmetric lax monoidal functor $F \maps (\A, +) \to (\Set, \times)$, we use a symmetric lax monoidal pseudofunctor $F \maps (\A, +) \to (\Cat, \times)$.
+In \cref{DC} we use this
+data to construct a symmetric monoidal double category $F\lCsp$ in which:
+\begin{itemize}
+\item an object is an object of $\A$,
+\item a vertical 1-morphism is a morphism of $\A$,
+\item a horizontal 1-cell from $a$ to $b$ is a decorated cospan:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$a$};
+\node (B) at (1,0) {$m$};
+\node (C) at (2,0) {$b,$};
+\node (D) at (3,0) {$x \in F(m)$,};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i$} (B)
+(C) edge node[above]{$o$} (B);
+\end{tikzpicture}
+\]
+\item a 2-morphism is a \define{map of decorated cospans}: that is, a commutative
+diagram
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0.5) {$a$};
+\node (A') at (0,-0.5) {$a'$};
+\node (B) at (1,0.5) {$m$};
+\node (C) at (2,0.5) {$b$};
+\node (C') at (2,-0.5) {$b'$};
+\node (D) at (1,-0.5) {$m'$};
+\node (E) at (3,0.5) {$x \in F(m)$};
+\node (F) at (3,-0.5) {$x' \in F(m')$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (C) edge node[above]{$o$} (B)
-(D) edge node [above] {$d$} (E);
-\end{tikzpicture}
-\]
+(A) edge node[left]{$f$} (A')
+(C) edge node[right]{$g$} (C')
+(A') edge node[above] {$i'$} (D)
+(C') edge node[above] {$o'$} (D)
+(B) edge node [left] {$h$} (D);
+\end{tikzpicture}
+\]
+together with a morphism $\tau \maps F(h)(m) \to m'$ in $F(m')$.
+\end{itemize}
+
+In fact another solution to the problem is already known: the theory of structured cospans \cite{BC,CourserThesis}.
+Given a functor $L \maps \A \to \X$, a \define{structured cospan} is a cospan in $\X$ whose feet come from a pair of objects in $\A$:
+\[
+\begin{tikzpicture}[scale=1.2]
+\node (A) at (0,0) {$L(a)$};
+\node (B) at (1,1) {$x$};
+\node (C) at (2,0) {$L(b).$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$$} (B)
+(C)edge node[above]{$$}(B);
+\end{tikzpicture}
+\]
+This is another way of letting the apex have more structure than the feet.
+When $\A$ and $\X$ have finite colimits and $L$ preserves them, there is a symmetric monoidal double category ${}_L \lCsp(\X)$ where:
+\begin{itemize}
+\item an object is an object of $\A$,
+\item a vertical 1-morphism is a morphism of $\A$,
+\item a horizontal 1-cell from $a$ to $b$ is a diagram in $\X$ of this form:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$L(a)$};
+\node (B) at (1,0) {$x$};
+\node (C) at (2,0) {$L(b)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i$} (B)
+(C)edge node[above]{$o$}(B);
+\end{tikzpicture}
+\]
+\item a 2-morphism is a commutative diagram in $\X$ of this form:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (E) at (3,0) {$L(a)$};
+\node (F) at (5,0) {$L(b)$};
+\node (G) at (4,0) {$x$};
+\node (E') at (3,-1) {$L(a')$};
+\node (F') at (5,-1) {$L(b')$};
+\node (G') at (4,-1) {$x'$};
+\path[->,font=\scriptsize,>=angle 90]
+(F) edge node[above]{$o$} (G)
+(E) edge node[left]{$L(\alpha)$} (E')
+(F) edge node[right]{$L(\beta)$} (F')
+(G) edge node[left]{$f$} (G')
+(E) edge node[above]{$i$} (G)
+(E') edge node[below]{$i'$} (G')
+(F') edge node[below]{$o'$} (G');
+\end{tikzpicture}
+\]
+\end{itemize}
+Many of the flawed applications of decorated cospans have been fixed using structured cospans
+\cite[Sec.\ 6]{BC}.
+
+We show that our new solution subsumes the old one: structured cospan double categories are always equivalent to decorated cospan double categories.  (REALLY????)
+
+We also give sufficient conditions for a decorated cospan double category to be equivalent to a structured cospan double category. 
+Suppose $\A$ has finite colimits and $F \maps (\A , +) \to (\Cat, \times)$ is 
+symmetric lax monoidal pseudofunctor.   Any such pseudofunctor gives an opfibration 
+$R \maps \X \to \A$ where $\X = \int F$ is defined by the Grothendieck construction.
+Let $\Rex$ be the 2-category of finitely cocomplete categories, finite-colimit-preserving
+functors and natural transformations.  We show that if $F$ factors through $\mathbf{Rex}$ as
+a pseudofunctor, the opfibration $R \maps \X \to \A$ is also a right adjoint.
+From the accompanying left adjoint $L \maps \A \to \X$, we  construct a symmetric monoidal double category ${}_L \lCsp(\X)$ of structured cospans.
+Finally, in \cref{Equiv} we prove that this structured cospan double category ${}_L \lCsp(\X)$ is equivalent to the decorated cospan double category $F \lCospan$.
+
+\iffalse
 To obtain a decoration on the composition of two composable decorated cospans:
@@
 \node (F) at (3,0) {$a_2$};
-\node (G) at (4,0) {$b^\prime$};
+\node (G) at (4,0) {$b'$};
 \node (H) at (5,0) {$a_3$};
@@
 \node (D') at (3.5,-0.5) {$1$};
-\node (E') at (4.5,-0.5) {$F(b^\prime)$};
+\node (E') at (4.5,-0.5) {$F(b')$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (C) edge node[above]{$o$} (B)
-(F) edge node[above]{$i^\prime$} (G)
-(H) edge node[above]{$o^\prime$} (G)
+(F) edge node[above]{$i'$} (G)
+(H) edge node[above]{$o'$} (G)
 (D) edge node [above] {$d_1$} (E)
@@
 \[
-1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{d_1 \times d_2} F(b) \times F(b^\prime) \xrightarrow{\phi_{b,b^\prime}} F(b+ b^\prime) \xrightarrow{F(j_{b,b^\prime})} F(b+_{a_2} b^\prime).
+1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{d_1 \times d_2} F(b) \times F(b') \xrightarrow{\phi_{b,b'}} F(b+ b') \xrightarrow{F(j_{b,b'})} F(b+_{a_2} b').
 \]
@@
 \item{objects as those of $\A$ and}
-\item{morphisms as isomorphism classes of $F$-decorated cospans, where an $F$-decorated cospan is given as above, and two $F$-decorated cospans are in the same isomorphism class if there exists an isomorphism $f \maps b \to b^\prime$ between the apices such that the following diagrams commute:
+\item{morphisms as isomorphism classes of $F$-decorated cospans, where an $F$-decorated cospan is given as above, and two $F$-decorated cospans are in the same isomorphism class if there exists an isomorphism $f \maps b \to b'$ between the apices such that the following diagrams commute:
 \[
@@
 \node (B) at (1,1) {$b$};
-\node (B') at (1,-1) {$b^\prime$};
+\node (B') at (1,-1) {$b'$};
 \node (C) at (2,0) {$a_2$};
@@
 \node (E) at (4,0.5) {$F(b)$};
-\node (E') at (4,-0.5) {$F(b^\prime)$};
+\node (E') at (4,-0.5) {$F(b')$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (C) edge node[above]{$o$} (B)
-(A) edge node[below]{$i^\prime$} (B')
-(C) edge node[below]{$o^\prime$} (B')
+(A) edge node[below]{$i'$} (B')
+(C) edge node[below]{$o'$} (B')
 (B) edge node [left] {$f$} (B')
@@
 (D) edge node [above] {$d$} (E)
-(D) edge node [below] {$d^\prime$} (E')
+(D) edge node [below] {$d'$} (E')
 (E) edge node [right] {$F(f)$} (E');
@@
 %\node (i) at (-0.5,11) {$i$};
-\node (o) at (8.5,11.5) {$i^\prime$};
+\node (o) at (8.5,11.5) {$i'$};
 \node (d) at (16,10) {$4$};
-\node (e) at (14.5,11.5) {$o^\prime$};
+\node (e) at (14.5,11.5) {$o'$};
   \node [style={circle,fill=teal}] (n1) at (10,11.5) {$v_4$};
@@
 \node (A) at (0,0) {$a_2$};
-\node (B) at (1,0) {$b^\prime$};
+\node (B) at (1,0) {$b'$};
 \node (C) at (2,0) {$a_3$};
 \node (D) at (3,0) {$1$};
-\node (E) at (4,0) {$F(b^\prime)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i^\prime$} (B)
-(C) edge node[above]{$o^\prime$} (B)
-(D) edge node [above] {$d^\prime$} (E);
+\node (E) at (4,0) {$F(b')$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i'$} (B)
+(C) edge node[above]{$o'$} (B)
+(D) edge node [above] {$d'$} (E);
 \end{tikzpicture}
@@
 \node (i) at (-0.5,11) {$i$};
-\node (o) at (8.5,11) {$o^\prime$};
+\node (o) at (8.5,11) {$o'$};
   \node [style={circle,fill=teal}] (n1) at (1,10) {$v_1$};
@@
 \node (A) at (0,0) {$a_1$};
-\node (B) at (1.25,0) {$b+_{a_2}b^\prime$};
+\node (B) at (1.25,0) {$b+_{a_2}b'$};
 \node (C) at (2.5,0) {$a_3$};
 \node (D) at (3,0) {$1$};
-\node (E) at (4,0) {$F(b+_{a_2}b^\prime)$};
+\node (E) at (4,0) {$F(b+_{a_2}b')$};
 \path[->,font=\scriptsize,>=angle 90]
 (A) edge node[above]{$\psi j_b i$} (B)
-(C) edge node[above]{$\psi j_{b^\prime} o^\prime$} (B)
+(C) edge node[above]{$\psi j_{b'} o'$} (B)
 (D) edge node [above] {$d''$} (E);
@@
 \node (c') at (16,11.5) {$3$};
-\node (i') at (8.5,13.5) {$i+i^\prime$};
-\node (o') at (14.5,13.5) {$o+o^\prime$};
+\node (i') at (8.5,13.5) {$i+i'$};
+\node (o') at (14.5,13.5) {$o+o'$};
   \node [style={circle,fill=teal}] (n1') at (10,13) {$v_1$};
@@
 \node (A) at (0,0) {$a_1+a_2$};
-\node (B) at (1.25,0) {$b+b^\prime$};
+\node (B) at (1.25,0) {$b+b'$};
 \node (C) at (2.5,0) {$a_2+a_3$};
 \node (D) at (3.5,0) {$1$};
-\node (E) at (4.5,0) {$F(b+b^\prime)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i+i^\prime$} (B)
-(C) edge node[above]{$o+ o^\prime$} (B)
-(D) edge node [above] {$d+d^\prime$} (E);
+\node (E) at (4.5,0) {$F(b+b')$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i+i'$} (B)
+(C) edge node[above]{$o+ o'$} (B)
+(D) edge node [above] {$d+d'$} (E);
 \end{tikzpicture}
@@
 \node (F) at (3,0) {$a_1$};
-\node (G) at (4,0) {$b^\prime$};
+\node (G) at (4,0) {$b'$};
 \node (H) at (5,0) {$a_2$};
@@
 (C) edge node[above]{$o$} (B)
-(F) edge node[above]{$i^\prime$} (G)
-(H) edge node[above]{$o^\prime$} (G)
+(F) edge node[above]{$i'$} (G)
+(H) edge node[above]{$o'$} (G)
 (D) edge node [above] {$d$} (E)
-(D') edge node [above] {$d^\prime$} (E');
+(D') edge node [above] {$d'$} (E');
 \end{tikzpicture}
@@
 \node (E) at (4,0.5) {$F(b)$};
-\node (E') at (4,-0.5) {$F(b^\prime)$};
+\node (E') at (4,-0.5) {$F(b')$};
 \path[->,font=\scriptsize,>=angle 90]
 (D) edge node [above] {$d$} (E)
-(D) edge node [below] {$d^\prime$} (E')
+(D) edge node [below] {$d'$} (E')
 (E) edge node [right] {$F(f)$} (E');
@@
 \]
-This commutative triangle in $\mathsf{Set}$ in the context of the symmetric lax monoidal functor $F \maps \mathsf{FinSet} \to \mathsf{Set}$ says the following: given a decoration $d \in F(b)$, which is a graph structure with underlying set of vertices $b$, the function $F(f)$ pushes forward the graph structure $d$ to the graph structure $d^\prime \in F(b^\prime)$ with underlying set of vertices $b^\prime$, and \emph{precisely} this graph structure.
+This commutative triangle in $\mathsf{Set}$ in the context of the symmetric lax monoidal functor $F \maps \mathsf{FinSet} \to \mathsf{Set}$ says the following: given a decoration $d \in F(b)$, which is a graph structure with underlying set of vertices $b$, the function $F(f)$ pushes forward the graph structure $d$ to the graph structure $d' \in F(b')$ with underlying set of vertices $b'$, and \emph{precisely} this graph structure.
 The graph structure is given by set of edges of $d$.
@@
 \]
-Let $b^\prime = \{w_1,w_2\}$ and a define bijection $f \maps b \to b^\prime$ by $f(v_i)=w_i$ for $i=1,2$. Then the requirement $F(f)(d)=d^\prime$ says that $d^\prime \in F(b^\prime)$ must be given by:
+Let $b' = \{w_1,w_2\}$ and a define bijection $f \maps b \to b'$ by $f(v_i)=w_i$ for $i=1,2$. Then the requirement $F(f)(d)=d'$ says that $d' \in F(b')$ must be given by:
 \[
@@
 \node (b) at (7,10) {$2$};
-\node (i) at (-0.5,11) {$i^\prime$};
-\node (o) at (5.5,11) {$o^\prime$};
+\node (i) at (-0.5,11) {$i'$};
+\node (o) at (5.5,11) {$o'$};
   \node [style={circle,fill=teal}] (n1) at (1,10) {$w_1$};
@@
 \]
-The point to be made here is that the single edge of $d^\prime$ must also be $e$.
-If we were to label it say, $e^\prime$, there is no bijection $f \maps b \to b^\prime$ such that the triangle on the right commutes, and hence no isomorphism between these two $F$-decorated cospans.
+The point to be made here is that the single edge of $d'$ must also be $e$.
+If we were to label it say, $e'$, there is no bijection $f \maps b \to b'$ such that the triangle on the right commutes, and hence no isomorphism between these two $F$-decorated cospans.
 \[
@@
 \node (E) at (11,12.5) {$F(b)$};
-\node (E') at (11,10.5) {$F(b^\prime)$};
+\node (E') at (11,10.5) {$F(b')$};
 \node (a) at (-2,11.5) {$1$};
@@
 \node (o) at (5.5,12.5) {$o$};
-\node (i') at (-0.5,10.5) {$i^\prime$};
-\node (o') at (5.5,10.5) {$o^\prime$};
+\node (i') at (-0.5,10.5) {$i'$};
+\node (o') at (5.5,10.5) {$o'$};
 \node (A) at (2.5,11.5) {$\nexists F(f) \Downarrow$};
@@
 (D) edge node [above] {$d$} (E)
-(D) edge node [below] {$d^\prime$} (E')
+(D) edge node [below] {$d'$} (E')
 (E) edge[dashed] node [right] {$\nexists F(f)$} (E')
@@
 (n1) edge node[above]{$e$} (n2)
-(n1') edge node[above]{$e^\prime$} (n2');
+(n1') edge node[above]{$e'$} (n2');
 \end{tikzpicture}
@@
 
-In a previous work, the second author extended Fong's theory of decorated cospans to a symmetric monoidal bicategory of decorated cospans \cite{Cour}.
+In a previous work, the second author extended Fong's theory of decorated cospans to a symmetric monoidal bicategory of decorated cospans \cite{Courser}.
 Namely, under the same hypotheses used by Fong amounting to a category $\A$ with finite colimits and a symmetric lax monoidal functor $F \maps (\A,+,0) \to (\mathsf{Set}, \times, 1)$, there exists a symmetric monoidal bicategory $F\mathbf{Cospan}(\A)$ which has:
@@
 \node (E) at (9,13) {$d \in F(b)$};
-\node (E') at (9,10) {$d^\prime \in F(b^\prime)$};
+\node (E') at (9,10) {$d' \in F(b')$};
 \node (a) at (-2,13) {$1$};
@@
 \node (o) at (5.5,13.5) {$o$};
-\node (i') at (-0.5,10.5) {$i^\prime$};
-\node (o') at (5.5,10.5) {$o^\prime$};
+\node (i') at (-0.5,10.5) {$i'$};
+\node (o') at (5.5,10.5) {$o'$};
 %\node (A) at (2.5,11.5) {$\nexists F(f) \Downarrow$};
@@
 %(D) edge node [above] {$d$} (E)
-%(D) edge node [below] {$d^\prime$} (E')
+%(D) edge node [below] {$d'$} (E')
 %(E) edge[dashed] node [right] {$\nexists F(f)$} (E')
@@
 \node (B) at (1,0.5) {$b$};
-\node (B') at (1,-0.5) {$b^\prime$};
+\node (B') at (1,-0.5) {$b'$};
 \node (C) at (2,0.5) {$a_2$};
@@
 \node (E) at (4,0.5) {$F(b)$};
-\node (E') at (4,-0.5) {$F(b^\prime)$};
+\node (E') at (4,-0.5) {$F(b')$};
 \node (F) at (3.65,0) {$\Swarrow \tau$};
@@
 (C) edge node {$$} (C')
-(A') edge node[above]{$i^\prime$} (B')
-(C') edge node[above]{$o^\prime$} (B')
+(A') edge node[above]{$i'$} (B')
+(C') edge node[above]{$o'$} (B')
 (B) edge node [left] {$f$} (B')
 (D) edge node [above] {$d$} (E)
-(D) edge node [below] {$d^\prime$} (E')
+(D) edge node [below] {$d'$} (E')
 (E) edge node [right] {$F(f)$} (E');
@@
 \end{enumerate}
-Note that the natural transformation is a family of morphisms in the category $F(b^\prime)$ indexed by $1$, and so is the same as just a morphism $\tau \maps F(f)(d) \to d^\prime$ in $F(b^\prime)$.
-We will typically write the transformation $\tau$ in later sections as a morphism in $F(b^\prime)$ to conserve space.
+Note that the natural transformation is a family of morphisms in the category $F(b')$ indexed by $1$, and so is the same as just a morphism $\tau \maps F(f)(d) \to d'$ in $F(b')$.
+We will typically write the transformation $\tau$ in later sections as a morphism in $F(b')$ to conserve space.
 In the context of the example above involving graphs, this morphism $\tau$ will be a map between two possibly distinct sets of edges and thus already solves the problem.
 
-This double category is in fact fibrant and so a result of Shulman \cite{Shul} allows us to extract from this symmetric monoidal double category $F \mathbb{C}$sp a symmetric monoidal bicategory $F \mathbf{Csp} \mapseqq H(F \mathbb{C}\textnormal{sp})$ as the `horizontal edge bicategory' of the double category $F \mathbb{C}$sp.
+This double category is in fact fibrant and so a result of Shulman \cite{Shul} allows us to extract from this symmetric monoidal double category $F \mathbb{C}$sp a symmetric monoidal bicategory $F \mathbf{Csp} \mapseqq H(F \lCsp)$ as the `horizontal edge bicategory' of the double category $F \mathbb{C}$sp.
 This bicategory $F \mathbf{Csp}$ has:
@@
 (C) edge node[above]{$o$} (B)
-(A) edge node[below]{$i^\prime$} (B')
-(C) edge node[below]{$o^\prime$} (B')
+(A) edge node[below]{$i'$} (B')
+(C) edge node[below]{$o'$} (B')
 (B) edge node [left] {$f$} (B')
 (D) edge node [above] {$d$} (E)
-(D) edge node [below] {$d^\prime$} (E')
+(D) edge node [below] {$d'$} (E')
 (E) edge node [right] {$F(f)$} (E');
@@
 \end{enumerate}
-This bicategory $F\mathbf{Csp}$ is superior to the original bicategory $F$Cospan$(A)$ constructed by the second author \cite{Cour} in that it has the 2-morphisms that one would expect such a bicategory to have, such as (\ref{no2morphism}).
+This bicategory $F\mathbf{Csp}$ is superior to the original bicategory $F$Cospan$(A)$ constructed by the second author \cite{Courser} in that it has the 2-morphisms that one would expect such a bicategory to have, such as (\ref{no2morphism}).
 
@@
 \node (E) at (4,0.5) {$F(b)$};
-\node (E') at (4,-0.5) {$F(b^\prime)$};
+\node (E') at (4,-0.5) {$F(b')$};
 \node (F) at (3.5,0) {$\Swarrow \tau$};
@@
 (D) edge node [above] {$d$} (E)
-(D) edge node [below] {$d^\prime$} (E')
+(D) edge node [below] {$d'$} (E')
 (E) edge node [right] {$F(f)$} (E')
@@
 This symmetric monoidal category $F$Csp has isomorphism classes as one would expect, and in the context of the example with finite sets and graphs above solves the problem in (\ref{distinctisoclasses}).
-In this particular example, $\tau \maps F(f)(d) \xrightarrow{\sim} d^\prime$ is a bijection between possibly different sets of edges which respects the source and target of each edge.
+In this particular example, $\tau \maps F(f)(d) \xrightarrow{\sim} d'$ is a bijection between possibly different sets of edges which respects the source and target of each edge.
+\fi
 
@@
 %{\chris Amend at the end}
-%The outline for the paper is as follows: In Section \cref{DecCospansDoubleCat}, we construct the symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$, obtain the underlying symmetric monoidal bicategory $F \mathbf{Csp}$ via a result of Shulman, and decategorify this symmetric monoidal bicategory to obtain the symmetric monoidal category $F$Csp.
+%The outline for the paper is as follows: In Section \cref{DecCospansDoubleCat}, we construct the symmetric monoidal double category $F\lCsp$, obtain the underlying symmetric monoidal bicategory $F \mathbf{Csp}$ via a result of Shulman, and decategorify this symmetric monoidal bicategory to obtain the symmetric monoidal category $F$Csp.
 In Section \cref{MapsDecCospansDoubleCat} we define maps between decorated cospan double categories which are double functors of an appropriate type.
@@
 \end{equation}
-together with a morphism $\tau \maps F(h)(m) \to m^\prime$ in $F(m^\prime)$.}
+together with a morphism $\tau \maps F(h)(m) \to m'$ in $F(m')$.}
 \end{itemize}
@@
 \begin{proof}
-The unit structure functor $U \maps F\mathbb{C}\textnormal{sp}_0 \to F\mathbb{C}\textnormal{sp}_1$ is defined on objects as: 
+The unit structure functor $U \maps F\lCsp_0 \to F\lCsp_1$ is defined on objects as: 
 \[
@@
 \node (G) at (-1,0.5) {$a$};
-\node (G') at (-1,-0.5) {$a^\prime$};
+\node (G') at (-1,-0.5) {$a'$};
 \node (A) at (0,0.5) {$a$};
-\node (A') at (0,-0.5) {$a^\prime$};
+\node (A') at (0,-0.5) {$a'$};
 \node (B) at (1,0.5) {$a$};
 \node (C) at (2,0.5) {$a$};
-\node (C') at (2,-0.5) {$a^\prime$};
-\node (D) at (1,-0.5) {$a^\prime$};
+\node (C') at (2,-0.5) {$a'$};
+\node (D) at (1,-0.5) {$a'$};
 \node (E) at (3,0.5) {$!_a \in F(a)$};
-\node (F) at (3,-0.5) {$!_{a^\prime} \in F(a^\prime)$};
+\node (F) at (3,-0.5) {$!_{a'} \in F(a')$};
 \node (H) at (-0.5,0) {$\mapsto$};
@@
 \]
-together with the morphism $\tau_{!_f} = F(f) F(!) \phi \maps 1 \to F(a^\prime)$.
-We also have source and target structure functors $S, T \maps F\mathbb{C}\textnormal{sp}_1 \to F\mathbb{C}\textnormal{sp}_0$ where the source of the horizontal 1-cell
+together with the morphism $\tau_{!_f} = F(f) F(!) \phi \maps 1 \to F(a')$.
+We also have source and target structure functors $S, T \maps F\lCsp_1 \to F\lCsp_0$ where the source of the horizontal 1-cell
 \[
@@
 \node (A) at (0,0.5) {$a$};
-\node (A') at (0,-0.5) {$a^\prime$};
+\node (A') at (0,-0.5) {$a'$};
 \node (B) at (1,0.5) {$m$};
 \node (C) at (2,0.5) {$b$};
-\node (C') at (2,-0.5) {$b^\prime$};
-\node (D) at (1,-0.5) {$m^\prime$};
+\node (C') at (2,-0.5) {$b'$};
+\node (D) at (1,-0.5) {$m'$};
 \node (E) at (3,0.5) {$x \in F(m)$};
-\node (F) at (3,-0.5) {$x^\prime \in F(m^\prime)$};
+\node (F) at (3,-0.5) {$x' \in F(m')$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-$$\tau \maps F(h)(m) \to m^\prime$$
+$$\tau \maps F(h)(m) \to m'$$
 is the source of the underlying map of cospans in $\A$, namely the morphism $f$ in $\A$; the target structure functor is defined similarly.
@@
 (C) edge node[above]{$o$} (B)
-(E) edge node[above]{$i^\prime$} (F)
-(G) edge node[above]{$o^\prime$} (F);
+(E) edge node[above]{$i'$} (F)
+(G) edge node[above]{$o'$} (F);
 \end{tikzpicture}
@@
 (C) edge node[above]{$o$} (B)
-(C) edge node [above] {$i^\prime$} (D)
-(E) edge node [above] {$o^\prime$} (D)
+(C) edge node [above] {$i'$} (D)
+(E) edge node [above] {$o'$} (D)
 (B) edge node [above] {$j$} (F)
-(D) edge node [above] {$j^\prime$} (F)
+(D) edge node [above] {$j'$} (F)
 (F) edge node [left] {$\psi$} (G)
 (A) edge[bend left] node [left] {$\psi j i$} (G)
-(E) edge[bend right] node [right] {$\psi j^\prime o^\prime$} (G);
+(E) edge[bend right] node [right] {$\psi j' o'$} (G);
 \end{tikzpicture}
@@
 (C) edge node[above]{$o$} (B)
-(E) edge node[above]{$i^\prime$} (F)
-(G) edge node[above]{$o^\prime$} (F)
+(E) edge node[above]{$i'$} (F)
+(G) edge node[above]{$o'$} (F)
 (I) edge node[above]{$i''$} (J)
@@
 The source and target functor applied to the left and right unitors and associators yield identities, and the left and right unitors together with the associator satisfy the standard pentagon and triangle identities of a monoidal category or bicategory.
-Finally, for the interchange law, given four 2-morphisms $\alpha, \beta, \alpha^\prime$ and $\beta^\prime$:
+Finally, for the interchange law, given four 2-morphisms $\alpha, \beta, \alpha'$ and $\beta'$:
 \[
@@
 \node (C) at (2,0.5) {$b$};
-\node (C') at (2,-0.5) {$b^\prime$};
-\node (D) at (1,-0.5) {$m^\prime$};
+\node (C') at (2,-0.5) {$b'$};
+\node (D) at (1,-0.5) {$m'$};
 \node (E) at (3,0.5) {$x \in F(m)$};
-\node (F) at (3,-0.5) {$x' \in F(m^\prime)$};
+\node (F) at (3,-0.5) {$x' \in F(m')$};
 \node (G) at (4,0.5) {$b$};
@@
 \node (I) at (6,0.5) {$c$};
-\node (G') at (4,-0.5) {$b^\prime$};
-\node (H') at (5,-0.5) {$n^\prime$};
-\node (I') at (6,-0.5) {$c^\prime$};
+\node (G') at (4,-0.5) {$b'$};
+\node (H') at (5,-0.5) {$n'$};
+\node (I') at (6,-0.5) {$c'$};
 \node (J) at (7,0.5) {$y \in F(n)$};
-\node (K) at (7,-0.5) {$y' \in F(n^\prime)$};
+\node (K) at (7,-0.5) {$y' \in F(n')$};
 \node (L) at (1,-1) {$\tau_\alpha \maps F(h_1)(x) \to x'$};
 \node (M) at (5,-1) {$\tau_\beta \maps F(h_2)(y) \to y'$};
-\node (A'') at (0,-1.5) {$a^\prime$};
+\node (A'') at (0,-1.5) {$a'$};
 \node (A''') at (0,-2.5) {$a''$};
-\node (B'') at (1,-1.5) {$m^\prime$};
-\node (C'') at (2,-1.5) {$b^\prime$};
+\node (B'') at (1,-1.5) {$m'$};
+\node (C'') at (2,-1.5) {$b'$};
 \node (C''') at (2,-2.5) {$b''$};
 \node (D'') at (1,-2.5) {$m''$};
-\node (E'') at (3,-1.5) {$x' \in F(m^\prime)$};
+\node (E'') at (3,-1.5) {$x' \in F(m')$};
 \node (F'') at (3,-2.5) {$x'' \in F(m'')$};
-\node (G'') at (4,-1.5) {$b^\prime$};
-\node (H'') at (5,-1.5) {$n^\prime$};
-\node (I'') at (6,-1.5) {$c^\prime$};
+\node (G'') at (4,-1.5) {$b'$};
+\node (H'') at (5,-1.5) {$n'$};
+\node (I'') at (6,-1.5) {$c'$};
 \node (G''') at (4,-2.5) {$b''$};
@@
 \node (I''') at (6,-2.5) {$c''$};
-\node (J'') at (7,-1.5) {$y' \in F(n^\prime)$};
+\node (J'') at (7,-1.5) {$y' \in F(n')$};
 \node (K'') at (7,-2.5) {$y'' \in F(n'')$};
-\node (L'') at (1,-3) {$\tau_{\alpha^\prime} \maps F(h_1^\prime)(x') \to x''$};
-\node (M'') at (5,-3) {$\tau_{\beta^\prime} \maps F(h_2^\prime)(y') \to y''$};
+\node (L'') at (1,-3) {$\tau_{\alpha'} \maps F(h_1')(x') \to x''$};
+\node (M'') at (5,-3) {$\tau_{\beta'} \maps F(h_2')(y') \to y''$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (C) edge node[right]{$g$} (C')
-(A') edge node[above] {$i_1^\prime$} (D)
-(C') edge node[above] {$o_1^\prime$} (D)
+(A') edge node[above] {$i_1'$} (D)
+(C') edge node[above] {$o_1'$} (D)
 (B) edge node [left] {$h_1$} (D)
@@
 (H) edge node [left] {$h_2$} (H')
-(G') edge node [above] {$i_2^\prime$} (H')
+(G') edge node [above] {$i_2'$} (H')
 (I) edge node [above] {$o_2$} (H)
 (I) edge node [right] {$k$} (I')
-(I') edge node [above] {$o_2^\prime$} (H')
-(A'') edge node[above]{$i_1^\prime$} (B'')
-(C'') edge node[above]{$o_1^\prime$} (B'')
-(A'') edge node[left]{$f^\prime$} (A''')
-(C'') edge node[right]{$g^\prime$} (C''')
+(I') edge node [above] {$o_2'$} (H')
+(A'') edge node[above]{$i_1'$} (B'')
+(C'') edge node[above]{$o_1'$} (B'')
+(A'') edge node[left]{$f'$} (A''')
+(C'') edge node[right]{$g'$} (C''')
 (A''') edge node[above] {$i_1''$} (D'')
 (C''') edge node[above] {$o_1''$} (D'')
-(B'') edge node [left] {$h_1^\prime$} (D'')
-(G'') edge node [above] {$i_2^\prime$} (H'')
-(G'') edge node [left] {$g^\prime$} (G''')
-(H'') edge node [left] {$h_2^\prime$} (H''')
+(B'') edge node [left] {$h_1'$} (D'')
+(G'') edge node [above] {$i_2'$} (H'')
+(G'') edge node [left] {$g'$} (G''')
+(H'') edge node [left] {$h_2'$} (H''')
 (G''') edge node [above] {$i_2''$} (H''')
-(I'') edge node [above] {$o_2^\prime$} (H'')
-(I'') edge node [right] {$k^\prime$} (I''')
+(I'') edge node [above] {$o_2'$} (H'')
+(I'') edge node [right] {$k'$} (I''')
 (I''') edge node [above] {$o_2''$} (H''');
@@
 \node (A) at (0,0.5) {$a$};
-\node (A') at (0,-0.5) {$a^\prime$};
+\node (A') at (0,-0.5) {$a'$};
 \node (B) at (1.5,0.5) {$m+_{b} n$};
 \node (C) at (3,0.5) {$c$};
-\node (C') at (3,-0.5) {$c^\prime$};
-\node (D) at (1.5,-0.5) {$m' +_{b'} n^\prime$};
+\node (C') at (3,-0.5) {$c'$};
+\node (D) at (1.5,-0.5) {$m' +_{b'} n'$};
 \node (E) at (4.5,0.5) {$x \odot y \in F(m+_{b} n)$};
-\node (F) at (4.5,-0.5) {$x' \odot y' \in F(m^\prime +_{b'} n^\prime)$};
+\node (F) at (4.5,-0.5) {$x' \odot y' \in F(m' +_{b'} n')$};
 \node (G) at (1.5,-1) {$\tau_{\alpha \odot \beta} \maps F(h_1 +_g h_2)(x \odot y) \to x' \odot y'$};
-\node (A'') at (0,-1.5) {$a^\prime$};
+\node (A'') at (0,-1.5) {$a'$};
 \node (A''') at (0,-2.5) {$a''$};
-\node (B'') at (1.5,-1.5) {$m^\prime +_{b\prime} n^\prime$};
-\node (C'') at (3,-1.5) {$c^\prime$};
+\node (B'') at (1.5,-1.5) {$m' +_{b\prime} n'$};
+\node (C'') at (3,-1.5) {$c'$};
 \node (C''') at (3,-2.5) {$c''$};
 \node (D'') at (1.5,-2.5) {$m'' +_{b''} n''$};
-\node (E'') at (4.5,-1.5) {$x' \odot y' \in F(m^\prime+_{b^\prime} n^\prime)$};
+\node (E'') at (4.5,-1.5) {$x' \odot y' \in F(m'+_{b'} n')$};
 \node (F'') at (4.5,-2.5) {$x'' \odot y'' \in F(m'' +_{b''} n'')$};
-\node (G'') at (1.5,-3) {$\tau_{\alpha^\prime \odot \beta^\prime} \maps F(h_1^\prime +_{g^\prime} h_2^\prime)(x' \odot y') \to x'' \odot y''.$};
+\node (G'') at (1.5,-3) {$\tau_{\alpha' \odot \beta'} \maps F(h_1' +_{g'} h_2')(x' \odot y') \to x'' \odot y''.$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (C) edge node[right]{$k$} (C')
-(A') edge node [above]{$j \psi_{m^\prime} i_1^\prime$} (D)
-(C') edge node [above]{$j \psi_{n^\prime} o_2^\prime$} (D)
+(A') edge node [above]{$j \psi_{m'} i_1'$} (D)
+(C') edge node [above]{$j \psi_{n'} o_2'$} (D)
 (B) edge node [left] {$h_1 +_g h_2$} (D)
-(A'') edge node[above]{$j \psi_{m^\prime} i_1^\prime$} (B'')
-(C'') edge node[above]{$j \psi_{n^\prime} o_2^\prime$} (B'')
-(A'') edge node[left]{$f^\prime$} (A''')
-(C'') edge node[right]{$k^\prime$} (C''')
+(A'') edge node[above]{$j \psi_{m'} i_1'$} (B'')
+(C'') edge node[above]{$j \psi_{n'} o_2'$} (B'')
+(A'') edge node[left]{$f'$} (A''')
+(C'') edge node[right]{$k'$} (C''')
 (A''') edge node [above]{$j \psi_{m''} i_1''$} (D'')
 (C''') edge node [above]{$j \psi_{n''} o_2''$} (D'')
-(B'') edge node [left] {$h_1^\prime +_{g^\prime} h_2^\prime$} (D'');
+(B'') edge node [left] {$h_1' +_{g'} h_2'$} (D'');
 \end{tikzpicture}
@@
 \node (E) at (4.5,0.5) {$F(m)$};
-\node (E') at (4.5,-0.5) {$F(m^\prime)$};
+\node (E') at (4.5,-0.5) {$F(m')$};
 \node (A') at (6.5,0) {$\tau_\beta \Swarrow$};
@@
 \node (E'') at (7,0.5) {$F(n)$};
-\node (E''') at (7,-0.5) {$F(n^\prime)$};
+\node (E''') at (7,-0.5) {$F(n')$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \node (E) at (5.5,0.5) {$F(m) \times F(n)$};
-\node (E') at (5.5,-0.5) {$F(m^\prime) \times F(n^\prime)$};
+\node (E') at (5.5,-0.5) {$F(m') \times F(n')$};
 \node (B) at (7.5,0.5) {$F(m+n)$};
-\node (B') at (7.5,-0.5) {$F(m^\prime + n^\prime)$};
+\node (B') at (7.5,-0.5) {$F(m' + n')$};
 \node (C) at (9.25,0.5) {$F(m+_{b} n)$};
-\node (C') at (9.25,-0.5) {$F(m^\prime +_{b^\prime} n^\prime)$};
+\node (C') at (9.25,-0.5) {$F(m' +_{b'} n')$};
 \path[->,font=\scriptsize,>=angle 90]
 (E) edge node [above] {$\phi_{m,n}$} (B)
-(E') edge node [above] {$\phi_{m^\prime,n^\prime}$} (B')
+(E') edge node [above] {$\phi_{m',n'}$} (B')
 (B) edge node [above] {$F(j_{m,n})$} (C)
-(B') edge node [above] {$F(j_{m^\prime,n^\prime})$} (C')
+(B') edge node [above] {$F(j_{m',n'})$} (C')
 (C) edge node [right] {$F(h_1 +_g h_2)$} (C')
@@
 \node (F) at (5.5,-0.5) {$x'' \odot y'' \in F(m'' +_{b''} n'')$};
-\node (G) at (2,-1) {$\tau_{(a^\prime \odot \beta^\prime)(\alpha \odot \beta)} \maps F((h_1^\prime +_{g^\prime} h_2^\prime)(h_1 +_g h_2))(x \odot y) \to x'' \odot y''.$};
+\node (G) at (2,-1) {$\tau_{(a' \odot \beta')(\alpha \odot \beta)} \maps F((h_1' +_{g'} h_2')(h_1 +_g h_2))(x \odot y) \to x'' \odot y''.$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (C) edge node[above]{$j \psi_{n} o_2$} (B)
-(A) edge node[left]{$f^\prime f$} (A')
-(C) edge node[right]{$k^\prime k$} (C')
+(A) edge node[left]{$f' f$} (A')
+(C) edge node[right]{$k' k$} (C')
 (A') edge node [above]{$j \psi_{m''} i_1''$} (D)
 (C') edge node [above]{$j \psi_{n''} o_2''$} (D)
-(B) edge node [left] {$(h_1^\prime +_{g^\prime} h_2^\prime)(h_1 +_g h_2)$} (D);
+(B) edge node [left] {$(h_1' +_{g'} h_2')(h_1 +_g h_2)$} (D);
 \end{tikzpicture}
@@
 \node (K) at (7,-0.5) {$y'' \in F(n'')$};
-\node (L) at (1,-1) {$\tau_{\alpha^\prime \alpha} \maps F(h_1^\prime h_1)(x) \to x''$};
-\node (M) at (5,-1) {$\tau_{\beta^\prime \beta} \maps F(h_2^\prime h_2)(y) \to y''$};
+\node (L) at (1,-1) {$\tau_{\alpha' \alpha} \maps F(h_1' h_1)(x) \to x''$};
+\node (M) at (5,-1) {$\tau_{\beta' \beta} \maps F(h_2' h_2)(y) \to y''$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (C) edge node[above]{$o_1$} (B)
-(A) edge node[left]{$f^\prime f$} (A')
-(C) edge node[right]{$g^\prime g$} (C')
+(A) edge node[left]{$f' f$} (A')
+(C) edge node[right]{$g' g$} (C')
 (A') edge node[above] {$i_1''$} (D)
 (C') edge node[above] {$o_1''$} (D)
-(B) edge node [left] {$h_1^\prime h_1$} (D)
+(B) edge node [left] {$h_1' h_1$} (D)
 (G) edge node [above] {$i_2$} (H)
-(G) edge node [left] {$g^\prime g$} (G')
-(H) edge node [left] {$h_2^\prime h_2$} (H')
+(G) edge node [left] {$g' g$} (G')
+(H) edge node [left] {$h_2' h_2$} (H')
 (G') edge node [above] {$i_2''$} (H')
 (I) edge node [above] {$o_2$} (H)
-(I) edge node [right] {$k^\prime k$} (I')
+(I) edge node [right] {$k' k$} (I')
 (I') edge node [above] {$o_2''$} (H');
@@
 \node (F) at (5.5,-0.5) {$x'' \odot y'' \in F(m'' +_{b''} n'')$};
-\node (G) at (2,-1) {$\tau_{(\alpha^\prime \alpha) \odot (\beta^\prime \beta)} \maps F((h_1^\prime h_1)+_{g^\prime g} (h_2^\prime h_2))(x \odot y) \to x'' \odot y''.$};
+\node (G) at (2,-1) {$\tau_{(\alpha' \alpha) \odot (\beta' \beta)} \maps F((h_1' h_1)+_{g' g} (h_2' h_2))(x \odot y) \to x'' \odot y''.$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (C) edge node[above]{$j \psi_{n} o_2$} (B)
-(A) edge node[left]{$f^\prime f$} (A')
-(C) edge node[right]{$k^\prime k$} (C')
+(A) edge node[left]{$f' f$} (A')
+(C) edge node[right]{$k' k$} (C')
 (A') edge node [above]{$j \psi_{m''} i_1''$} (D)
 (C') edge node [above]{$j \psi_{n''} o_2''$} (D)
-(B) edge node [left] {$(h_1^\prime h_1) +_{g^\prime g} (h_2^\prime h_2)$} (D);
+(B) edge node [left] {$(h_1' h_1) +_{g' g} (h_2' h_2)$} (D);
 \end{tikzpicture}
@@
 %(C) edge node [right]{$F(j_{c,e})$} (D)
-%(D) edge node [right] {$F((h_1^\prime +_{g^\prime} h_2^\prime)(h_1 +_g h_2))$} (E)
+%(D) edge node [right] {$F((h_1' +_{g'} h_2')(h_1 +_g h_2))$} (E)
 %(A) edge node [left] {$d_1 \times d_2$} (F)
-%(F) edge node [left] {$F((h_1^\prime h_1) \times (h_2^\prime h_2))$} (G)
+%(F) edge node [left] {$F((h_1' h_1) \times (h_2' h_2))$} (G)
 %(G) edge node [above] {$\phi_{c'',e''}$} (H)
@@
 %\]
-As is usual concerning the interchange law of double categories of this nature, only the `interior' of the two composites appears different, but the two morphisms $(h_1^\prime +_{g^\prime} h_2^\prime)(h_1 +_g h_2) \maps m+_{b} n \to m'' +_{b''} n''$ and $(h_1^\prime h_1) +_{g^\prime g} (h_2^\prime h_2) \maps m+_{b} n \to m'' +_{b''}n''$ are the same universal map realized in two different ways.
-The two morphisms of decorations $\tau_{(\alpha^\prime \odot \beta^\prime)(\alpha \odot \beta)}$ and $\tau_{(\alpha^\prime \alpha) \odot (\beta^\prime \beta)}$ are obtained as two different compositions of four 2-morphisms in $\Cat$, namely horizontally then vertically and vertically then horizontally.
-As $\Cat$ is a 2-category, the interchange law for these 2-morphisms already holds, and as a result, the morphisms $$\tau_{(\alpha' \odot \beta')(\alpha \odot \beta)} \maps F((h_1^\prime +_{g^\prime} h_2^\prime)(h_1 +_g h_2))(x \odot y) \to x'' \odot y''$$ and $$\tau_{(\alpha^\prime \alpha)\odot(\beta^\prime \beta)} \maps F((h_1^\prime h_1)+_{g^\prime g} (h_2^\prime h_2))(x \odot y) \to x'' \odot y''$$ are also the same.
+As is usual concerning the interchange law of double categories of this nature, only the `interior' of the two composites appears different, but the two morphisms $(h_1' +_{g'} h_2')(h_1 +_g h_2) \maps m+_{b} n \to m'' +_{b''} n''$ and $(h_1' h_1) +_{g' g} (h_2' h_2) \maps m+_{b} n \to m'' +_{b''}n''$ are the same universal map realized in two different ways.
+The two morphisms of decorations $\tau_{(\alpha' \odot \beta')(\alpha \odot \beta)}$ and $\tau_{(\alpha' \alpha) \odot (\beta' \beta)}$ are obtained as two different compositions of four 2-morphisms in $\Cat$, namely horizontally then vertically and vertically then horizontally.
+As $\Cat$ is a 2-category, the interchange law for these 2-morphisms already holds, and as a result, the morphisms $$\tau_{(\alpha' \odot \beta')(\alpha \odot \beta)} \maps F((h_1' +_{g'} h_2')(h_1 +_g h_2))(x \odot y) \to x'' \odot y''$$ and $$\tau_{(\alpha' \alpha)\odot(\beta' \beta)} \maps F((h_1' h_1)+_{g' g} (h_2' h_2))(x \odot y) \to x'' \odot y''$$ are also the same.
 Thus the interchange law for 2-morphisms holds and $F\mathbb{C}$sp is a double category.
@@
 \end{thm}
-%!!!Kenny: We should try to make this theorem shorter.
+%!!!Kenny: We should try to make this proof shorter.
 %Christina: Yes!
@@
 \begin{proof}
-First we note that the category of objects $F\mathbb{C}\textnormal{sp}_0=\A$ is symmetric monoidal under binary coproducts and the left and right unitors, associators and braidings are given as natural maps.
-The category of arrows $F\mathbb{C}\textnormal{sp}_1$ has:
+First we note that the category of objects $F\lCsp_0=\A$ is symmetric monoidal under binary coproducts and the left and right unitors, associators and braidings are given as natural maps.
+The category of arrows $F\lCsp_1$ has:
 \begin{enumerate}
@@
 (C) edge node[right]{$g$} (C')
-(A') edge node [above]{$i^\prime$} (D)
-(C') edge node [above]{$o^\prime$} (D)
+(A') edge node [above]{$i'$} (D)
+(C') edge node [above]{$o'$} (D)
 (B) edge node [left] {$h$} (D);
@@
 \]
-together with a morphism $\tau \maps F(h)(x) \to x^\prime$.
+together with a morphism $\tau \maps F(h)(x) \to x'$.
 }
 \end{enumerate}
-Given two objects $M_1$ and $M_2$ of $F\mathbb{C}\textnormal{sp}_1$:
+Given two objects $M_1$ and $M_2$ of $F\lCsp_1$:
 \[
@@
 \]
-where $!_0 + x \in F(0+m)$ is given by $$1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{!_0 \times x} F(0) \times F(m) \xrightarrow{\phi_{0,m}} F(0+m).$$The left unitor is then an isomorphism in $F\mathbb{C}\textnormal{sp}_1$ given by:
+where $!_0 + x \in F(0+m)$ is given by $$1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{!_0 \times x} F(0) \times F(m) \xrightarrow{\phi_{0,m}} F(0+m).$$The left unitor is then an isomorphism in $F\lCsp_1$ given by:
 \[
@@
 
-Given three objects $M_1, M_2$ and $M_3$ in $F\mathbb{C}\textnormal{sp}_1$:
+Given three objects $M_1, M_2$ and $M_3$ in $F\lCsp_1$:
 \[
@@
 \]
-where $x_1+(x_2+x_3) \maps 1 \to F(m_1+(m_2+m_3))$ is given by: $$1 \xrightarrow{x_1 \times (x_2 \times x_3)} F(m_1) \times (F(m_2) \times F(m_3)) \xrightarrow{1 \times \phi_{m_2,m_3}} F(m_1) \times F(m_2+m_3) \xrightarrow{\phi_{m_1,m_2+m_3}} F(m_1+(m_2+m_3)).$$If we let $a$ denote the associator of $(\A,+,0)$, the associator of $F\mathbb{C}\textnormal{sp}_1$ is then a map of cospans in $\A$ from $(M_1 \otimes M_2) \otimes M_3$ to $M_1 \otimes (M_2 \otimes M_3)$ given by:
+where $x_1+(x_2+x_3) \maps 1 \to F(m_1+(m_2+m_3))$ is given by: $$1 \xrightarrow{x_1 \times (x_2 \times x_3)} F(m_1) \times (F(m_2) \times F(m_3)) \xrightarrow{1 \times \phi_{m_2,m_3}} F(m_1) \times F(m_2+m_3) \xrightarrow{\phi_{m_1,m_2+m_3}} F(m_1+(m_2+m_3)).$$If we let $a$ denote the associator of $(\A,+,0)$, the associator of $F\lCsp_1$ is then a map of cospans in $\A$ from $(M_1 \otimes M_2) \otimes M_3$ to $M_1 \otimes (M_2 \otimes M_3)$ given by:
 \[
@@
 \begin{comment}
-If we denote the above associator simply as $a$ and the left and right unitors as $\lambda$ and $\rho$, respectively, then given four objects in $F\mathbb{C}\textnormal{sp}_1$, say $M_1, M_2, M_3$ and $M_4$:
+If we denote the above associator simply as $a$ and the left and right unitors as $\lambda$ and $\rho$, respectively, then given four objects in $F\lCsp_1$, say $M_1, M_2, M_3$ and $M_4$:
 \[
@@
 \]
-then as $\mathbb{C}\textnormal{sp}(\A)$ is a symmetric monoidal double category, the following pentagon of underlying cospans and maps of cospans commutes:
+then as $\lCsp(\A)$ is a symmetric monoidal double category, the following pentagon of underlying cospans and maps of cospans commutes:
 \[
@@
 
-For a tensor product of objects $M_1 \otimes M_2$ in $F\mathbb{C}\textnormal{sp}_1$, the source and target structure functors $S,T \maps F\mathbb{C}\textnormal{sp}_1 \to F\mathbb{C}\textnormal{sp}_0$ satisfy the following equations: $$S(M_1 \otimes M_2)=S(M_1) \otimes S(M_2)$$ $$T(M_1 \otimes M_2)=T(M_1) \otimes T(M_2).$$
-For two objects $M_1$ and $M_2$ in $F\mathbb{C}\textnormal{sp}_1$, we have a braiding $\beta_{M_1,M_2} \maps M_1 \otimes M_2 \to M_2 \otimes M_1$ given by:
+For a tensor product of objects $M_1 \otimes M_2$ in $F\lCsp_1$, the source and target structure functors $S,T \maps F\lCsp_1 \to F\lCsp_0$ satisfy the following equations: $$S(M_1 \otimes M_2)=S(M_1) \otimes S(M_2)$$ $$T(M_1 \otimes M_2)=T(M_1) \otimes T(M_2).$$
+For two objects $M_1$ and $M_2$ in $F\lCsp_1$, we have a braiding $\beta_{M_1,M_2} \maps M_1 \otimes M_2 \to M_2 \otimes M_1$ given by:
 \[
@@
 \]
-since $F(\beta_{m_2,m_1} \beta_{m_1,m_2}) (x_1+x_2) = x_1+x_2$. Thus $F\mathbb{C}\textnormal{sp}_1$ is also symmetric monoidal.
+since $F(\beta_{m_2,m_1} \beta_{m_1,m_2}) (x_1+x_2) = x_1+x_2$. Thus $F\lCsp_1$ is also symmetric monoidal.
 
@@
 (G) edge node[above]{$o_2$} (F)
-(I) edge node[above]{$i_1^\prime$} (J)
-(K) edge node[above]{$o_1^\prime$} (J)
-(M) edge node[above]{$i_2^\prime$} (N)
-(O) edge node[above]{$o_2^\prime$} (N);
+(I) edge node[above]{$i_1'$} (J)
+(K) edge node[above]{$o_1'$} (J)
+(M) edge node[above]{$i_2'$} (N)
+(O) edge node[above]{$o_2'$} (N);
 \end{tikzpicture}
@@
 (A) edge node[above]{$j \psi(i_1+i_1')$} (B)
-(C) edge node[above]{$j \psi(o_2 + o_2^\prime)$} (B);
+(C) edge node[above]{$j \psi(o_2 + o_2')$} (B);
 \end{tikzpicture}
@@
 (A) edge node[above]{$(j \psi i_1)+(j \psi i_1')$} (B)
-(C) edge node[above]{$(j \psi o_2)+(j \psi o_2^\prime)$} (B);
+(C) edge node[above]{$(j \psi o_2)+(j \psi o_2')$} (B);
 \end{tikzpicture}
@@
 (A) edge node[above]{$j \psi (i_1+i_1')$} (B)
-(C) edge node[above]{$j \psi (o_2 + o_2^\prime)$} (B)
+(C) edge node[above]{$j \psi (o_2 + o_2')$} (B)
 (A) edge node[left]{$1$} (A')
@@
 (A') edge node [above]{$(j \psi i_1')+(j \psi i_1)$} (D)
-(C') edge node [above]{$(j \psi o_2)+(j \psi o_2^\prime)$} (D)
+(C') edge node [above]{$(j \psi o_2)+(j \psi o_2')$} (D)
 (B) edge node [left] {$\hat{\chi}$} (D);
@@
 \]
-Here, $a$ is the associator of $F\mathbb{C}\textnormal{sp}_1$ and $\chi$ is the first globular isomorphism above.
+Here, $a$ is the associator of $F\lCsp_1$ and $\chi$ is the first globular isomorphism above.
 To see that this diagram does indeed commute, we first consider this diagram with respect to only the underlying cospans of each horizontal 1-cell.
@@
 
-Another requirement for a double category to be symmetric monoidal is that the braiding $$\beta_{ ( \_, \_ ) } \maps F\mathbb{C}\textnormal{sp}_1 \times F\mathbb{C}\textnormal{sp}_1 \to F\mathbb{C}\textnormal{sp}_1 \times F\mathbb{C}\textnormal{sp}_1$$ be a transformation of double categories, and one of the diagrams that is required to commute is the following:
+Another requirement for a double category to be symmetric monoidal is that the braiding $$\beta_{ ( \_, \_ ) } \maps F\lCsp_1 \times F\lCsp_1 \to F\lCsp_1 \times F\lCsp_1$$ be a transformation of double categories, and one of the diagrams that is required to commute is the following:
 \[
@@
 \begin{lem}
-The double category $F\mathbb{C}\textnormal{sp}$ is fibrant.
+The double category $F\lCsp$ is fibrant.
 \end{lem}
@@
 \begin{proof}
-Let $f \maps c \to c^\prime$ be a vertical 1-morphism in $F\mathbb{C}\textnormal{sp}$. We can lift $f$ to the companion horizontal 1-cell $\hat{f}$:
+Let $f \maps c \to c'$ be a vertical 1-morphism in $F\lCsp$. We can lift $f$ to the companion horizontal 1-cell $\hat{f}$:
 \[
@@
 \node (A) at (0,0) {$c$};
-\node (B) at (1,0) {$c^\prime$};
-\node (C) at (2,0) {$c^\prime$};
-\node (D) at (1,-0.5) {$!_{c^\prime} \in F(c^\prime)$};
+\node (B) at (1,0) {$c'$};
+\node (C) at (2,0) {$c'$};
+\node (D) at (1,-0.5) {$!_{c'} \in F(c')$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \node (A) at (0,0.5) {$c$};
-\node (A') at (0,-0.5) {$c^\prime$};
-\node (B) at (1,0.5) {$c^\prime$};
-\node (C) at (2,0.5) {$c^\prime$};
-\node (C') at (2,-0.5) {$c^\prime$};
-\node (D) at (1,-0.5) {$c^\prime$};
-\node (E) at (3,0.5) {$!_{c^\prime} \in F(c^\prime)$};
-\node (F) at (3,-0.5) {$!_{c^\prime} \in F(c^\prime)$};
+\node (A') at (0,-0.5) {$c'$};
+\node (B) at (1,0.5) {$c'$};
+\node (C) at (2,0.5) {$c'$};
+\node (C') at (2,-0.5) {$c'$};
+\node (D) at (1,-0.5) {$c'$};
+\node (E) at (3,0.5) {$!_{c'} \in F(c')$};
+\node (F) at (3,-0.5) {$!_{c'} \in F(c')$};
 \node (G) at (4,0.5) {$c$};
@@
 \node (G') at (4,-0.5) {$c$};
-\node (H') at (5,-0.5) {$c^\prime$};
-\node (I') at (6,-0.5) {$c^\prime$};
+\node (H') at (5,-0.5) {$c'$};
+\node (I') at (6,-0.5) {$c'$};
 \node (J) at (7,0.5) {$!_{c} \in F(c)$};
-\node (K) at (7,-0.5) {$!_{c^\prime} \in F(c^\prime)$};
-\node (L) at (1,-1) {$\tau_{1_{c^\prime}} = 1_{!_{c^\prime}}$};
-\node (M) at (5,-1) {$\tau_f \maps F(f)(!_c) \to !_{c^\prime}$};
+\node (K) at (7,-0.5) {$!_{c'} \in F(c')$};
+\node (L) at (1,-1) {$\tau_{1_{c'}} = 1_{!_{c'}}$};
+\node (M) at (5,-1) {$\tau_f \maps F(f)(!_c) \to !_{c'}$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \node (A) at (0,0.5) {$c$};
-\node (A') at (0,-0.5) {$c^\prime$};
-\node (B) at (1,0.5) {$c^\prime$};
-\node (C) at (2,0.5) {$c^\prime$};
-\node (C') at (2,-0.5) {$c^\prime$};
-\node (D) at (1,-0.5) {$c^\prime$};
-\node (E) at (-1,0.5) {$!_{c^\prime} \in F(c^\prime)$};
-\node (F) at (-1,-0.5) {$!_{c^\prime} \in F(c^\prime)$};
+\node (A') at (0,-0.5) {$c'$};
+\node (B) at (1,0.5) {$c'$};
+\node (C) at (2,0.5) {$c'$};
+\node (C') at (2,-0.5) {$c'$};
+\node (D) at (1,-0.5) {$c'$};
+\node (E) at (-1,0.5) {$!_{c'} \in F(c')$};
+\node (F) at (-1,-0.5) {$!_{c'} \in F(c')$};
 \node (G) at (4,1) {$c$};
@@
 \node (I) at (6,1) {$c$};
-\node (G') at (4,0) {$c^\prime$};
-\node (H') at (5,0) {$c^\prime$};
-\node (I') at (6,0) {$c^\prime$};
+\node (G') at (4,0) {$c'$};
+\node (H') at (5,0) {$c'$};
+\node (I') at (6,0) {$c'$};
 \node (J) at (7,1) {$!_{c} \in F(c)$};
-\node (K) at (7,0) {$!_{c^\prime} \in F(c^\prime)$};
-\node (Q) at (1,-1) {$\tau_f \maps F(f)(!_c) \to !_{c^\prime}$};
-\node (L) at (1,-1.5) {$\tau_{c^\prime} = 1_{!_{c^\prime}}$};
-\node (M) at (5,-0.5) {$\tau_f \maps F(f)(!_c) \to !_{c^\prime}$};
+\node (K) at (7,0) {$!_{c'} \in F(c')$};
+\node (Q) at (1,-1) {$\tau_f \maps F(f)(!_c) \to !_{c'}$};
+\node (L) at (1,-1.5) {$\tau_{c'} = 1_{!_{c'}}$};
+\node (M) at (5,-0.5) {$\tau_f \maps F(f)(!_c) \to !_{c'}$};
 \node (R) at (3,0.5) {$=$};
@@
 \node (G) at (-1,0.5) {$c$};
-\node (H) at (-1,-0.5)  {$c^\prime$};
+\node (H) at (-1,-0.5)  {$c'$};
 \node (I) at (-2,0.5) {$c$};
@@
 \node (A) at (0,0.5) {$c$};
-\node (A') at (0,-0.5) {$c^\prime$};
-\node (B) at (1,0.5) {$c^\prime$};
-\node (C) at (2,0.5) {$c^\prime$};
-\node (C') at (2,-0.5) {$c^\prime$};
-\node (D) at (1,-0.5) {$c^\prime$};
-\node (E) at (1,1) {$!_{c^\prime} \in F(c^\prime)$};
-\node (F) at (1,-1) {$!_{c^\prime} \in F(c^\prime)$};
-
-\node (L) at (1,-1.5) {$\tau_{c^\prime} = 1_{!_{c^\prime}}$};
+\node (A') at (0,-0.5) {$c'$};
+\node (B) at (1,0.5) {$c'$};
+\node (C) at (2,0.5) {$c'$};
+\node (C') at (2,-0.5) {$c'$};
+\node (D) at (1,-0.5) {$c'$};
+\node (E) at (1,1) {$!_{c'} \in F(c')$};
+\node (F) at (1,-1) {$!_{c'} \in F(c')$};
+
+\node (L) at (1,-1.5) {$\tau_{c'} = 1_{!_{c'}}$};
 \node (E') at (-1,1) {$!_{c} \in F(c)$};
-\node (F') at (-1,-1) {$!_{c^\prime} \in F(c^\prime)$};
-
-\node (L') at (-1,-1.5) {$\tau_{f} \maps F(f)(!_c) \to !_{c^\prime}$};
+\node (F') at (-1,-1) {$!_{c'} \in F(c')$};
+
+\node (L') at (-1,-1.5) {$\tau_{f} \maps F(f)(!_c) \to !_{c'}$};
 
@@
 \node (O) at (3,-0.5) {$c$};
-\node (P) at (4,0.5) {$c^\prime$};
-\node (Q) at (4,-0.5) {$c^\prime$};
-\node (R) at (5,0.5) {$c^\prime$};
-\node (S) at (5,-0.5) {$c^\prime$};
-\node (T) at (4,1) {$!_{c^\prime} \in F(c^\prime)$};
-\node (U) at (4,-1) {$!_{c^\prime} \in F(c^\prime)$};
-\node (V) at (4,-1.5) {$\tau_{c^\prime} = 1_{!_{c^\prime}}$};
+\node (P) at (4,0.5) {$c'$};
+\node (Q) at (4,-0.5) {$c'$};
+\node (R) at (5,0.5) {$c'$};
+\node (S) at (5,-0.5) {$c'$};
+\node (T) at (4,1) {$!_{c'} \in F(c')$};
+\node (U) at (4,-1) {$!_{c'} \in F(c')$};
+\node (V) at (4,-1.5) {$\tau_{c'} = 1_{!_{c'}}$};
 
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$c^\prime$};
-\node (B) at (1,0) {$c^\prime$};
+\node (A) at (0,0) {$c'$};
+\node (B) at (1,0) {$c'$};
 \node (C) at (2,0) {$c$};
-\node (D) at (4,0) {$!_{c^\prime} \in F(c^\prime)$};
+\node (D) at (4,0) {$!_{c'} \in F(c')$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 Let $\A$ be a category with finite colimits and $F \maps (\A, +) \to \Cat$ a symmetric lax monoidal pseudofunctor.
-Then there exists a symmetric monoidal bicategory $F \mathbf{Csp} \mapseqq H(F\mathbb{C}\textnormal{sp})$ which has:
+Then there exists a symmetric monoidal bicategory $F \mathbf{Csp} \mapseqq H(F\lCsp)$ which has:
 \begin{enumerate}
@@
 \node (C) at (2,0) {$b$};
-\node (E) at (1,-0.5) {$c^\prime$};
+\node (E) at (1,-0.5) {$c'$};
 \node (D) at (3,0.5) {$d \in F(c)$};
-\node (F) at (3,-0.5) {$d^\prime \in F(c^\prime)$};
+\node (F) at (3,-0.5) {$d' \in F(c')$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (C) edge node[above]{$o$} (B)
-(A) edge node[below]{$i^\prime$} (E)
+(A) edge node[below]{$i'$} (E)
 (B) edge node[left]{$h$} (E)
-(C) edge node[below]{$o^\prime$} (E);
-\end{tikzpicture}
-\]
-together with a morphism $\tau \maps F(h)(d) \to d^\prime$ in $F(c^\prime)$.}
+(C) edge node[below]{$o'$} (E);
+\end{tikzpicture}
+\]
+together with a morphism $\tau \maps F(h)(d) \to d'$ in $F(c')$.}
 \end{enumerate}
@@
 \begin{proof}
-This follows immediately by applying \cref{Shul} to the fibrant symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$.
+This follows immediately by applying \cref{Shul} to the fibrant symmetric monoidal double category $F\lCsp$.
 \end{proof}
 
-This symmetric monoidal bicategory $F\mathbf{Csp}$ is a superior version of the symmetric monoidal bicategory $F$Cospan$(\A)$ constructed earlier by the second author \cite{Cour} in that there is greater flexibility in what 2-morphisms are allowed.
+This symmetric monoidal bicategory $F\mathbf{Csp}$ is a superior version of the symmetric monoidal bicategory $F$Cospan$(\A)$ constructed earlier by the second author \cite{Courser} in that there is greater flexibility in what 2-morphisms are allowed.
 
@@
 %\node (B) at (1,0.5) {$c$};
-%\node (B') at (1,-0.5) {$c^\prime$};
+%\node (B') at (1,-0.5) {$c'$};
 %\node (C) at (2,0) {$b$};
@@
 %\node (E) at (4,0.5) {$F(c)$};
-%\node (E') at (4,-0.5) {$F(c^\prime)$};
+%\node (E') at (4,-0.5) {$F(c')$};
 %\path[->,font=\scriptsize,>=angle 90]
@@
 %(C) edge node[above]{$o$} (B)
-%(A) edge node[below]{$i^\prime$} (B')
-%(C) edge node[below]{$o^\prime$} (B')
+%(A) edge node[below]{$i'$} (B')
+%(C) edge node[below]{$o'$} (B')
 %(B) edge node [left] {$f$} (B')
 %(D) edge node [above] {$d$} (E)
-%(D) edge node [below] {$d^\prime$} (E')
+%(D) edge node [below] {$d'$} (E')
 %(E) edge node [right] {$F(f)$} (E');
@@
 %\path[->,font=\scriptsize,>=angle 90]
-%(A) edge node[above]{$e^\prime$} (B);
+%(A) edge node[above]{$e'$} (B);
 %\end{tikzpicture}
@@
 In the bicategorical version of $F \textnormal{Cospan}(\mathrm{A})$ where we are no longer considering decorated cospans up to isomorphism class, there is no 2-morphism between these two graphs due to the strict commutativity of the triangle to the right above.
-This problem does not occur in the symmetric monoidal bicategory $H(\mathbb{F}\textnormal{Cospan}(\mathrm{A}))$ and there is in fact a 2-(iso)morphism between these two graphs given by the map $\tau \maps F(f)(d) \to d^\prime$ which maps the edge $e$ to the edge $e^\prime$, where $f$ is the underlying map of vertices.
+This problem does not occur in the symmetric monoidal bicategory $H(\mathbb{F}\textnormal{Cospan}(\mathrm{A}))$ and there is in fact a 2-(iso)morphism between these two graphs given by the map $\tau \maps F(f)(d) \to d'$ which maps the edge $e$ to the edge $e'$, where $f$ is the underlying map of vertices.
 
@@
 %(A) edge node[above]{$e$} (B)
-%(C) edge node[above]{$e^\prime$} (D);
+%(C) edge node[above]{$e'$} (D);
 %\end{tikzpicture}
@@
 \node (A) at (0,0) {$a$};
-\node (B) at (1,0) {$c^\prime$};
+\node (B) at (1,0) {$c'$};
 \node (C) at (2,0) {$b$};
-\node (D) at (4,0) {$d^\prime \in F(c^\prime)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[below]{$i^\prime$} (B)
-(C) edge node[below]{$o^\prime$} (B);
-\end{tikzpicture}
-\]
-these two $F$-decorated cospans are in the same isomorphism class if there exists an isomorphism $f \maps c \to c^\prime$ such that following diagram commutes:
+\node (D) at (4,0) {$d' \in F(c')$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[below]{$i'$} (B)
+(C) edge node[below]{$o'$} (B);
+\end{tikzpicture}
+\]
+these two $F$-decorated cospans are in the same isomorphism class if there exists an isomorphism $f \maps c \to c'$ such that following diagram commutes:
 \[
@@
 \node (B') at (1,0.5) {$c$};
-\node (B) at (1,-0.5) {$c^\prime$};
+\node (B) at (1,-0.5) {$c'$};
 \node (C) at (2,0) {$b$};
 \path[->,font=\scriptsize,>=angle 90]
-(A) edge node[below]{$i^\prime$} (B)
-(C) edge node[below]{$o^\prime$} (B)
+(A) edge node[below]{$i'$} (B)
+(C) edge node[below]{$o'$} (B)
 (A) edge node[above]{$i$} (B')
@@
 \]
-and there exists an isomorphism $\tau \maps F(f)(d) \to d^\prime$ in $F(c^\prime)$.}
+and there exists an isomorphism $\tau \maps F(f)(d) \to d'$ in $F(c')$.}
 \end{enumerate}
@@
 %Let $F \maps \A \to \Cat$ be a symmetric lax monoidal pseudofunctor.
-Then by Theorem \cref{DC} of the previous section, we get a symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$.
+Then by Theorem \cref{DC} of the previous section, we get a symmetric monoidal double category $F\lCsp$.
 This symmetric monoidal double category has:
@@
 %\node (A) at (0,0.5) {$a$};
-%\node (A') at (0,-0.5) {$a^\prime$};
+%\node (A') at (0,-0.5) {$a'$};
 %\node (B) at (1,0.5) {$c$};
 %\node (C) at (2,0.5) {$b$};
-%\node (C') at (2,-0.5) {$b^\prime$};
-%\node (D) at (1,-0.5) {$c^\prime$};
+%\node (C') at (2,-0.5) {$b'$};
+%\node (D) at (1,-0.5) {$c'$};
 %\node (E) at (3,0.5) {$d \in F(c)$};
-%\node (F) at (3,-0.5) {$d^\prime \in F(c^\prime)$};
+%\node (F) at (3,-0.5) {$d' \in F(c')$};
 %\path[->,font=\scriptsize,>=angle 90]
@@
 %\]
-%together with a morphism $\tau \maps F(h)(d) \to d^\prime$ in $F(c^\prime)$.}
+%together with a morphism $\tau \maps F(h)(d) \to d'$ in $F(c')$.}
 %\end{enumerate}
 
-Regarding maps between symmetric monoidal double categories, consider another symmetric lax monoidal pseudofunctor $F^\prime \maps \mathsf{A^\prime} \to \Cat$%, we can obtain another symmetric monoidal double category $F^\prime \mathbb{C}\textnormal{sp}$.
-a morphism from $F\mathbb{C}\textnormal{sp}$ to $F^\prime \mathbb{C}\textnormal{sp}$ will then be a double functor $\mathbb{H} \maps F\mathbb{C}\textnormal{sp} \to F' \mathbb{C}\textnormal{sp}$ whose object component is given by a finite colimit preserving functor $\mathbb{H}_0 = H \maps \A \to \mathsf{A^\prime}$ and whose arrow component is given by a functor $\mathbb{H}_1$ defined on horizontal 1-cells by:
+Regarding maps between symmetric monoidal double categories, consider another symmetric lax monoidal pseudofunctor $F' \maps \mathsf{A'} \to \Cat$%, we can obtain another symmetric monoidal double category $F' \lCsp$.
+a morphism from $F\lCsp$ to $F' \lCsp$ will then be a double functor $\mathbb{H} \maps F\lCsp \to F' \lCsp$ whose object component is given by a finite colimit preserving functor $\mathbb{H}_0 = H \maps \A \to \mathsf{A'}$ and whose arrow component is given by a functor $\mathbb{H}_1$ defined on horizontal 1-cells by:
 \[
@@
 \node (C') at (5.5,0) {$H(b)$};
-\node (D') at (4.5,-0.5) {$\theta_c E(d) \phi \in F^\prime(H(c))$};
+\node (D') at (4.5,-0.5) {$\theta_c E(d) \phi \in F'(H(c))$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \node (A) at (0,0.5) {$a$};
-\node (A') at (0,-0.5) {$a^\prime$};
+\node (A') at (0,-0.5) {$a'$};
 \node (B) at (1,0.5) {$c$};
 \node (C) at (2,0.5) {$b$};
-\node (C') at (2,-0.5) {$b^\prime$};
-\node (D) at (1,-0.5) {$c^\prime$};
+\node (C') at (2,-0.5) {$b'$};
+\node (D) at (1,-0.5) {$c'$};
 \node (E) at (3,0.5) {$d \in F(c)$};
-\node (F) at (3,-0.5) {$d^\prime \in F(c^\prime)$};
-\node (G) at (1,-1) {$\tau \maps F(h)(d) \to d^\prime$};
+\node (F) at (3,-0.5) {$d' \in F(c')$};
+\node (G) at (1,-1) {$\tau \maps F(h)(d) \to d'$};
 \node (A'') at (4.25,0.5) {$H(a)$};
-\node (A''') at (4.25,-0.5) {$H(a^\prime)$};
+\node (A''') at (4.25,-0.5) {$H(a')$};
 \node (B'') at (5.25,0.5) {$H(c)$};
 \node (C'') at (6.25,0.5) {$H(b)$};
-\node (C''') at (6.25,-0.5) {$H(b^\prime)$};
-\node (D'') at (5.25,-0.5) {$H(c^\prime)$};
-\node (E'') at (8,0.5) {$\theta_c E(d) \phi \in F^\prime(H(c))$};
-\node (F'') at (8,-0.5) {$\theta_{c'} E(d^\prime) \phi \in F^\prime(H(c^\prime))$};
-\node (G'') at (5.25,-1) {$E(\tau) \maps F^\prime(H(h))(\theta_c E(d)\phi) \to (\theta_{c'}E(d^\prime)\phi)$};
+\node (C''') at (6.25,-0.5) {$H(b')$};
+\node (D'') at (5.25,-0.5) {$H(c')$};
+\node (E'') at (8,0.5) {$\theta_c E(d) \phi \in F'(H(c))$};
+\node (F'') at (8,-0.5) {$\theta_{c'} E(d') \phi \in F'(H(c'))$};
+\node (G'') at (5.25,-1) {$E(\tau) \maps F'(H(h))(\theta_c E(d)\phi) \to (\theta_{c'}E(d')\phi)$};
 \node (H) at (3.5,0) {$\mapsto$};
@@
 \node (B) at (1,0) {$\Cat$};
-\node (C) at (0,-1) {$\mathsf{A^\prime}$};
+\node (C) at (0,-1) {$\mathsf{A'}$};
 \node (D) at (1,-1) {$\Cat$};
@@
 (B) edge node[right]{$E$} (D)
-(C) edge node[above]{$F^\prime$} (D);
+(C) edge node[above]{$F'$} (D);
 \end{tikzpicture}
@@
 \begin{comment}
-Recall that we can think of the object $d \in F(c)$ as a morphism $d \maps 1 \to F(c)$ and the functor $\tau \maps F(h)(d) \to d^\prime$ of $F(c^\prime)$ as a natural transformation  in $\Cat$:
+Recall that we can think of the object $d \in F(c)$ as a morphism $d \maps 1 \to F(c)$ and the functor $\tau \maps F(h)(d) \to d'$ of $F(c')$ as a natural transformation  in $\Cat$:
 \[
@@
 \node (B) at (1,0) {$F(c)$};
-\node (D) at (1,-1) {$F(c^\prime)$};
+\node (D) at (1,-1) {$F(c')$};
 \node (C) at (0.75,-0.5) {$\Swarrow \tau$};
@@
 (A) edge node[above]{$d$} (B)
-(A) edge node[below]{$d^\prime$} (D)
+(A) edge node[below]{$d'$} (D)
 (B) edge node[right]{$F(h)$} (D);
@@
 Applying the symmetric lax monoidal pseudofunctor $E \maps \Cat \to \Cat$ to this diagram yields:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,-0.5) {$1 \xrightarrow{\phi} E(1)$};
-\node (B) at (2,0) {$E(F(c))$};
-\node (D) at (2,-1) {$E(F(c^\prime))$};
-\node (C) at (1.5,-0.5) {$\Swarrow E(\tau)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$E(d)$} (B)
-(A) edge node[below]{$E(d^\prime)$} (D)
-(B) edge node[right]{$E(F(h))$} (D);
-\end{tikzpicture}
-\]
-Then because the above square commutes up to the isomorphism $\theta \maps EF \Rightarrow F'H$, we get:
 \[
@@
 \node (C) at (1.5,-0.5) {$\Swarrow E(\tau)$};
-\node (E) at (4,0) {$F^\prime(H(c))$};
-\node (F) at (4,-1) {$F^\prime(H(c'))$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$E(d)$} (B)
+(A) edge node[below]{$E(d')$} (D)
+(B) edge node[right]{$E(F(h))$} (D);
+\end{tikzpicture}
+\]
+Then because the above square commutes up to the isomorphism $\theta \maps EF \Rightarrow F'H$, we get:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,-0.5) {$1 \xrightarrow{\phi} E(1)$};
+\node (B) at (2,0) {$E(F(c))$};
+\node (D) at (2,-1) {$E(F(c'))$};
+\node (C) at (1.5,-0.5) {$\Swarrow E(\tau)$};
+\node (E) at (4,0) {$F'(H(c))$};
+\node (F) at (4,-1) {$F'(H(c'))$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (A) edge node[above]{$E(d)$} (B)
-(A) edge node[below]{$E(d^\prime)$} (D)
+(A) edge node[below]{$E(d')$} (D)
 (B) edge node[right]{$E(F((h))$} (D);
@@
 \]
-which results in a 2-morphism $E(\tau) \maps F^\prime(H(h))(\theta_c E(d)\phi) \to (\theta_{c'} E(d^\prime)\phi)$ in $F^\prime(H(c^\prime))$.
-To check that the above recipe is functorial, given two vertically composable 2-morphisms in $F\mathbb{C}\textnormal{sp}$:
+which results in a 2-morphism $E(\tau) \maps F'(H(h))(\theta_c E(d)\phi) \to (\theta_{c'} E(d')\phi)$ in $F'(H(c'))$.
+To check that the above recipe is functorial, given two vertically composable 2-morphisms in $F\lCsp$:
 \[
@@
 \node (A) at (0,0.5) {$a$};
-\node (A') at (0,-0.5) {$a^\prime$};
+\node (A') at (0,-0.5) {$a'$};
 \node (B) at (1.5,0.5) {$c$};
 \node (C) at (3,0.5) {$b$};
-\node (C') at (3,-0.5) {$b^\prime$};
-\node (D) at (1.5,-0.5) {$c^\prime$};
+\node (C') at (3,-0.5) {$b'$};
+\node (D) at (1.5,-0.5) {$c'$};
 \node (E) at (4.5,0.5) {$d \in F(c)$};
-\node (F) at (4.5,-0.5) {$d^\prime \in F(c^\prime)$};
-\node (G) at (1.5,-1) {$\tau \maps F(h)(d) \to d^\prime$};
-\node (A'') at (0,-1.5) {$a^\prime$};
+\node (F) at (4.5,-0.5) {$d' \in F(c')$};
+\node (G) at (1.5,-1) {$\tau \maps F(h)(d) \to d'$};
+\node (A'') at (0,-1.5) {$a'$};
 \node (A''') at (0,-2.5) {$a''$};
-\node (B'') at (1.5,-1.5) {$c^\prime$};
-\node (C'') at (3,-1.5) {$b^\prime$};
+\node (B'') at (1.5,-1.5) {$c'$};
+\node (C'') at (3,-1.5) {$b'$};
 \node (C''') at (3,-2.5) {$b''$};
 \node (D'') at (1.5,-2.5) {$c''$};
-\node (E'') at (4.5,-1.5) {$d^\prime \in F(c^\prime)$};
+\node (E'') at (4.5,-1.5) {$d' \in F(c')$};
 \node (F'') at (4.5,-2.5) {$d'' \in F(c'')$};
-\node (G'') at (1.5,-3) {$\tau^\prime \maps F(h^\prime)(d^\prime) \to d''$};
+\node (G'') at (1.5,-3) {$\tau' \maps F(h')(d') \to d''$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (C'') edge node[above]{$$} (B'')
-(A'') edge node[left]{$f^\prime$} (A''')
-(C'') edge node[right]{$g^\prime$} (C''')
+(A'') edge node[left]{$f'$} (A''')
+(C'') edge node[right]{$g'$} (C''')
 (A''') edge node [above]{$$} (D'')
 (C''') edge node [above]{$$} (D'')
-(B'') edge node [left] {$h^\prime$} (D'');
+(B'') edge node [left] {$h'$} (D'');
 \end{tikzpicture}
@@
 \node (F) at (4.5,-0.5) {$d'' \in F(c'')$};
-\node (G) at (1.5,-1) {$\tau ^\prime \tau \maps F(h^\prime h)(d) \to d''$};
+\node (G) at (1.5,-1) {$\tau ' \tau \maps F(h' h)(d) \to d''$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (C) edge node[above]{$$} (B)
-(A) edge node[left]{$f^\prime f$} (A')
-(C) edge node[right]{$g^\prime g$} (C')
+(A) edge node[left]{$f' f$} (A')
+(C) edge node[right]{$g' g$} (C')
 (A') edge node [above]{$$} (D)
 (C') edge node [above]{$$} (D)
-(B) edge node [left] {$h^\prime h$} (D);
+(B) edge node [left] {$h' h$} (D);
 \end{tikzpicture}
@@
 \node (D) at (1.5,-0.5) {$H(c'')$};
-\node (E) at (5,0.5) {$\theta_c E(d) \phi \in F^\prime(H(c))$};
-\node (F) at (5,-0.5) {$\theta_{c''} E(d'') \phi \in F^\prime(H(c''))$};
-\node (G) at (1.5,-1) {$E(\tau ^\prime \tau) \maps F^\prime(H(h^\prime h))(\theta_c E(d)\phi) \to (\theta_{c''}E(d'')\phi).$};
+\node (E) at (5,0.5) {$\theta_c E(d) \phi \in F'(H(c))$};
+\node (F) at (5,-0.5) {$\theta_{c''} E(d'') \phi \in F'(H(c''))$};
+\node (G) at (1.5,-1) {$E(\tau ' \tau) \maps F'(H(h' h))(\theta_c E(d)\phi) \to (\theta_{c''}E(d'')\phi).$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (C) edge node[above]{$$} (B)
-(A) edge node[left]{$H(f^\prime f)$} (A')
-(C) edge node[right]{$H(g^\prime g)$} (C')
+(A) edge node[left]{$H(f' f)$} (A')
+(C) edge node[right]{$H(g' g)$} (C')
 (A') edge node [above]{$$} (D)
 (C') edge node [above]{$$} (D)
-(B) edge node [left] {$H(h^\prime h)$} (D);
+(B) edge node [left] {$H(h' h)$} (D);
 \end{tikzpicture}
@@
 \node (A) at (0,0.5) {$H(a)$};
-\node (A') at (0,-0.5) {$H(a^\prime)$};
+\node (A') at (0,-0.5) {$H(a')$};
 \node (B) at (1.5,0.5) {$H(c)$};
 \node (C) at (3,0.5) {$H(b)$};
-\node (C') at (3,-0.5) {$H(b^\prime)$};
-\node (D) at (1.5,-0.5) {$H(c^\prime)$};
-\node (E) at (5,0.5) {$\theta_c E(d) \phi \in F^\prime(H(c))$};
-\node (F) at (5,-0.5) {$\theta_{c'} E(d^\prime) \phi \in F^\prime(H(c^\prime))$};
-\node (G) at (1.5,-1) {$E(\tau) \maps F^\prime(H(h))(\theta_c E(d)\phi) \to (\theta_{c'} E(d^\prime)\phi)$};
-\node (A'') at (0,-1.5) {$H(a^\prime)$};
+\node (C') at (3,-0.5) {$H(b')$};
+\node (D) at (1.5,-0.5) {$H(c')$};
+\node (E) at (5,0.5) {$\theta_c E(d) \phi \in F'(H(c))$};
+\node (F) at (5,-0.5) {$\theta_{c'} E(d') \phi \in F'(H(c'))$};
+\node (G) at (1.5,-1) {$E(\tau) \maps F'(H(h))(\theta_c E(d)\phi) \to (\theta_{c'} E(d')\phi)$};
+\node (A'') at (0,-1.5) {$H(a')$};
 \node (A''') at (0,-2.5) {$H(a'')$};
-\node (B'') at (1.5,-1.5) {$H(c^\prime)$};
-\node (C'') at (3,-1.5) {$H(b^\prime)$};
+\node (B'') at (1.5,-1.5) {$H(c')$};
+\node (C'') at (3,-1.5) {$H(b')$};
 \node (C''') at (3,-2.5) {$H(b'')$};
 \node (D'') at (1.5,-2.5) {$H(c'')$};
-\node (E'') at (5,-1.5) {$\theta_{c'} E(d^\prime) \phi \in F^\prime(H(c^\prime))$};
-\node (F'') at (5,-2.5) {$\theta_{c''} E(d'') \phi \in F^\prime(H(c''))$};
-\node (G'') at (1.5,-3) {$E(\tau^\prime) \maps F^\prime(H(h^\prime))(\theta_{c'} E(d^\prime)\phi) \to (\theta_{c''}E(d'')\phi)$};
+\node (E'') at (5,-1.5) {$\theta_{c'} E(d') \phi \in F'(H(c'))$};
+\node (F'') at (5,-2.5) {$\theta_{c''} E(d'') \phi \in F'(H(c''))$};
+\node (G'') at (1.5,-3) {$E(\tau') \maps F'(H(h'))(\theta_{c'} E(d')\phi) \to (\theta_{c''}E(d'')\phi)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (C'') edge node[above]{$$} (B'')
-(A'') edge node[left]{$H(f^\prime)$} (A''')
-(C'') edge node[right]{$H(g^\prime)$} (C''')
+(A'') edge node[left]{$H(f')$} (A''')
+(C'') edge node[right]{$H(g')$} (C''')
 (A''') edge node [above]{$$} (D'')
 (C''') edge node [above]{$$} (D'')
-(B'') edge node [left] {$H(h^\prime)$} (D'');
+(B'') edge node [left] {$H(h')$} (D'');
 \end{tikzpicture}
@@
 
-Given two composable horizontal 1-cells $M$ and $N$ in $F\mathbb{C}\textnormal{sp}$:
+Given two composable horizontal 1-cells $M$ and $N$ in $F\lCsp$:
 \[
@@
 \node (C) at (4,0) {$H(a_2)$};
-\node (D) at (2,-0.5) {$\mathbb{H}(M \odot N) = \theta_{c_1 +_b c_2}E(d_{M \odot N}) \phi \in F^\prime(H(c_1 +_b c_2))$};
+\node (D) at (2,-0.5) {$\mathbb{H}(M \odot N) = \theta_{c_1 +_b c_2}E(d_{M \odot N}) \phi \in F'(H(c_1 +_b c_2))$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-where $$\mathbb{H}(M \odot N) = \theta_{c_1 +_b c_2} E(d_{M \odot N}) \phi \maps 1 \xrightarrow{\phi} E(1) \xrightarrow{E(d)} E(F(c_1 +_b c_2)) \xrightarrow{\theta_{c_1 +_b c_2}} F^\prime(H(c_1 +_b c_2)).$$ On the other hand, the image of each horizontal 1-cell under the double functor $\mathbb{H}$ is given respectively by $\mathbb{H}(M)$ and $\mathbb{H}(N)$:
+where $$\mathbb{H}(M \odot N) = \theta_{c_1 +_b c_2} E(d_{M \odot N}) \phi \maps 1 \xrightarrow{\phi} E(1) \xrightarrow{E(d)} E(F(c_1 +_b c_2)) \xrightarrow{\theta_{c_1 +_b c_2}} F'(H(c_1 +_b c_2)).$$ On the other hand, the image of each horizontal 1-cell under the double functor $\mathbb{H}$ is given respectively by $\mathbb{H}(M)$ and $\mathbb{H}(N)$:
 \[
@@
 \node (C) at (2,0) {$H(b)$};
-\node (D) at (1,-0.5) {$\theta_{c_1} E(d_M)\phi \in F^\prime(H(c_1))$};
+\node (D) at (1,-0.5) {$\theta_{c_1} E(d_M)\phi \in F'(H(c_1))$};
 \node (E) at (3,0) {$H(b)$};
@@
 \node (G) at (5,0) {$H(a_2)$};
-\node (H) at (4,-0.5) {$\theta_{c_2} E(d_N) \phi \in F^\prime(H(c_2))$};
+\node (H) at (4,-0.5) {$\theta_{c_2} E(d_N) \phi \in F'(H(c_2))$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \node (C) at (4.5,0) {$H(a_2)$};
-\node (D) at (2.25,-0.5) {$d_{\mathbb{H}(M) \odot \mathbb{H}(N)} \in F^\prime(H(c_1) +_{H(b)} H(c_2))$};
+\node (D) at (2.25,-0.5) {$d_{\mathbb{H}(M) \odot \mathbb{H}(N)} \in F'(H(c_1) +_{H(b)} H(c_2))$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-where $$\hspace{-.4in}\scriptstyle{d_{\mathbb{H}(M) \odot \mathbb{H}(N)} \maps 1 \xrightarrow{(\theta_{c_1} \times \theta_{c_2})(E(d_M) \times E(d_N)) \phi} F^\prime(H(c_1)) \times F^\prime(H(c_2)) \xrightarrow{\Phi_{H(c_1),H(c_2)}} F^\prime(H(c_1)+ H(c_2)) \xrightarrow{F^\prime (J)} F^\prime(H(c_1) +_{H(b)} H(c_2)).}$$
+where $$\hspace{-.4in}\scriptstyle{d_{\mathbb{H}(M) \odot \mathbb{H}(N)} \maps 1 \xrightarrow{(\theta_{c_1} \times \theta_{c_2})(E(d_M) \times E(d_N)) \phi} F'(H(c_1)) \times F'(H(c_2)) \xrightarrow{\Phi_{H(c_1),H(c_2)}} F'(H(c_1)+ H(c_2)) \xrightarrow{F' (J)} F'(H(c_1) +_{H(b)} H(c_2)).}$$
 We then have a comparison constraint: $$\mathbb{H}_{M,N} \maps \mathbb{H}(M) \odot \mathbb{H}(N) \xrightarrow{\sim} \mathbb{H}(M \odot N)$$given by the globular 2-isomorphism:
@@
 \node (D) at (2.5,-0.5) {$H(c_1 +_b c_2)$};
-\node (E) at (7.5,0.5) {$d_{\mathbb{H}(M) \odot \mathbb{H}(N)} \in F^\prime(H(c_1)+_{H(b_1)}H(c_2))$};
-\node (F) at (7.5,-0.5) {$d_{\mathbb{H}(M \odot N)} \in F^\prime(H(c_1 +_b c_2))$};
-\node (G) at (2.5,-1) {$\tau_{\kappa^{-1}} \maps F^\prime(\kappa^{-1})(d_{\mathbb{H}(M) \odot \mathbb{H}(N)}) \to d_{\mathbb{H}(M \odot N)}.$};
+\node (E) at (7.5,0.5) {$d_{\mathbb{H}(M) \odot \mathbb{H}(N)} \in F'(H(c_1)+_{H(b_1)}H(c_2))$};
+\node (F) at (7.5,-0.5) {$d_{\mathbb{H}(M \odot N)} \in F'(H(c_1 +_b c_2))$};
+\node (G) at (2.5,-1) {$\tau_{\kappa^{-1}} \maps F'(\kappa^{-1})(d_{\mathbb{H}(M) \odot \mathbb{H}(N)}) \to d_{\mathbb{H}(M \odot N)}.$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-where $\kappa$ is the isomorphism $$\kappa \maps H(c_1 +_b c_2) \xrightarrow{\sim} H(c_1) +_{H(b)} H(c_2)$$ which comes from the finite colimit preserving functor $H \maps \A \to \mathsf{A^\prime}$.
+where $\kappa$ is the isomorphism $$\kappa \maps H(c_1 +_b c_2) \xrightarrow{\sim} H(c_1) +_{H(b)} H(c_2)$$ which comes from the finite colimit preserving functor $H \maps \A \to \mathsf{A'}$.
 The above diagram commutes by a similar argument to the one used in Theorem \cref{Equiv}.
@@
 \node (D) at (1.5,-0.5) {$H(c)$};
-\node (E) at (4.5,0.5) {$!_{H(c)} \in F^\prime(H(c))$};
-\node (F) at (4.5,-0.5) {$\theta_c E(!_c) \phi \in F^\prime(H(c))$};
+\node (E) at (4.5,0.5) {$!_{H(c)} \in F'(H(c))$};
+\node (F) at (4.5,-0.5) {$\theta_c E(!_c) \phi \in F'(H(c))$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (A) edge node[above]{$a$} (A')
-(C) edge node [above] {$\mathbb{H}(a^\prime)$} (C')
+(C) edge node [above] {$\mathbb{H}(a')$} (C')
 (B') edge node [right] {$\mathbb{H}_{M,N \odot P}$} (C')
@@
 (B) edge node[right]{$\mathbb{H}_{U_a,M}$} (D)
-(D) edge node[above]{$\mathbb{H}(\lambda^\prime)$} (C)
+(D) edge node[above]{$\mathbb{H}(\lambda')$} (C)
 (A') edge node[above]{$1 \odot \mathbb{H}_U$} (B')
@@
 (B') edge node[right]{$\mathbb{H}_{M,U_b}$} (D')
-(D') edge node[above]{$\mathbb{H}(\rho^\prime)$} (C');
+(D') edge node[above]{$\mathbb{H}(\rho')$} (C');
 \end{tikzpicture}
@@
 Next we show that this double functor is symmetric monoidal.
-First, that the object component $\mathbb{H}_0=H$ is symmetric monoidal is clear as $H \maps \A \to \A^\prime$ preserves finite colimits.
-As for the arrow component $\mathbb{H}_1$, given two horizontal 1-cells $M_1$ and $M_2$ in $F\mathbb{C}\textnormal{sp}$:
+First, that the object component $\mathbb{H}_0=H$ is symmetric monoidal is clear as $H \maps \A \to \A'$ preserves finite colimits.
+As for the arrow component $\mathbb{H}_1$, given two horizontal 1-cells $M_1$ and $M_2$ in $F\lCsp$:
 \[
@@
 \]
-their tensor product $M_1 \otimes M_2$ in $F\mathbb{C}\textnormal{sp}$ is given by:
+their tensor product $M_1 \otimes M_2$ in $F\lCsp$ is given by:
 \[
@@
 \node (C) at (4,0) {$H(b_1+b_2)$};
-\node (D) at (2,-0.5) {$d_{\mathbb{H}(M_1 \otimes M_2)} = \theta_{c_1+c_2} E(d_{M_1 \otimes M_2})\phi \in F^\prime(H(c_1+c_2))$};
+\node (D) at (2,-0.5) {$d_{\mathbb{H}(M_1 \otimes M_2)} = \theta_{c_1+c_2} E(d_{M_1 \otimes M_2})\phi \in F'(H(c_1+c_2))$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \node (C) at (3,0) {$H(b_1)$};
-\node (D) at (1.5,-0.5) {$d_{\mathbb{H}(M_1)} = \theta_{c_1}E(d_{M_1})\phi \in F^\prime(H(c_1))$};
+\node (D) at (1.5,-0.5) {$d_{\mathbb{H}(M_1)} = \theta_{c_1}E(d_{M_1})\phi \in F'(H(c_1))$};
 \node (E) at (4.5,0) {$H(a_2)$};
@@
 \node (G) at (7.5,0) {$H(b_2)$};
-\node (H) at (6,-0.5) {$d_{\mathbb{H}(M_2)} = \theta_{c_2}E(d_{M_2})\phi \in F^\prime(H(c_2))$};
+\node (H) at (6,-0.5) {$d_{\mathbb{H}(M_2)} = \theta_{c_2}E(d_{M_2})\phi \in F'(H(c_2))$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \node (C) at (5,0) {$H(b_1)+H(b_2)$};
-\node (D) at (2.5,-0.5) {$d_{\mathbb{H}(M_1) \otimes \mathbb{H}(M_2)} \in F^\prime(H(c_1)+H(c_2))$};
+\node (D) at (2.5,-0.5) {$d_{\mathbb{H}(M_1) \otimes \mathbb{H}(M_2)} \in F'(H(c_1)+H(c_2))$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-$$\hspace{-.4in} \scriptstyle{d_{\mathbb{H}(M_1) \otimes \mathbb{H}(M_2)} \maps 1 \xrightarrow{(\phi \times \phi)(\lambda^{-1} \times \lambda^{-1})} E(1) \times E(1) \xrightarrow{(\theta_{c_1} \times \theta_{c_2})(E(d_{M_1}) \times E(d_{M_2}))} F^\prime(H(c_1)) \times F^\prime(H(c_2)) \xrightarrow{\Phi_{H(c_1),H(c_2)}} F^\prime (H(c_1)+H(c_2)).}$$  We then have a natural 2-isomorphism $\mu_{M_1,M_2} \maps \mathbb{H}(M_1) \otimes \mathbb{H}(M_2) \to \mathbb{H}(M_1 \otimes M_2)$ in $F'\mathbb{C}\textnormal{sp}$ given by:
+$$\hspace{-.4in} \scriptstyle{d_{\mathbb{H}(M_1) \otimes \mathbb{H}(M_2)} \maps 1 \xrightarrow{(\phi \times \phi)(\lambda^{-1} \times \lambda^{-1})} E(1) \times E(1) \xrightarrow{(\theta_{c_1} \times \theta_{c_2})(E(d_{M_1}) \times E(d_{M_2}))} F'(H(c_1)) \times F'(H(c_2)) \xrightarrow{\Phi_{H(c_1),H(c_2)}} F' (H(c_1)+H(c_2)).}$$  We then have a natural 2-isomorphism $\mu_{M_1,M_2} \maps \mathbb{H}(M_1) \otimes \mathbb{H}(M_2) \to \mathbb{H}(M_1 \otimes M_2)$ in $F'\lCsp$ given by:
 \[
@@
 \node (D) at (2.5,-0.5) {$H(c_1+c_2)$};
-\node (E) at (2.5,1) {$d_{\mathbb{H}(M_1) \otimes \mathbb{H}(M_2)} \in F^\prime(H(c_1)+H(c_2))$};
-\node (F) at (2.5,-1) {$d_{\mathbb{H}(M_1 \otimes M_2)} \in F^\prime(H(c_1+c_2))$};
+\node (E) at (2.5,1) {$d_{\mathbb{H}(M_1) \otimes \mathbb{H}(M_2)} \in F'(H(c_1)+H(c_2))$};
+\node (F) at (2.5,-1) {$d_{\mathbb{H}(M_1 \otimes M_2)} \in F'(H(c_1+c_2))$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-$$\tau_\kappa \maps F^\prime(\kappa)(d_{\mathbb{H}(M_1) \otimes \mathbb{H}(M_2)}) \to d_{\mathbb{H}(M_1 \otimes M_2)}$$
+$$\tau_\kappa \maps F'(\kappa)(d_{\mathbb{H}(M_1) \otimes \mathbb{H}(M_2)}) \to d_{\mathbb{H}(M_1 \otimes M_2)}$$
 where $\kappa$ denotes the isomorphism arising from $H$ preserving finite colimits.
-This natural 2-isomorphism together with the associators of $F\mathbb{C}\textnormal{sp}$ and $F'\mathbb{C}\textnormal{sp}$, respectively $\alpha$ and $\alpha^\prime$, make the following diagram commute:
+This natural 2-isomorphism together with the associators of $F\lCsp$ and $F'\lCsp$, respectively $\alpha$ and $\alpha'$, make the following diagram commute:
 \[
@@
 (B) edge node[left]{$\mu_{M_1 \otimes M_2,M_3}$} (C)
-(A) edge node[above]{$\alpha^\prime$} (A')
+(A) edge node[above]{$\alpha'$} (A')
 (C) edge node [above] {$\mathbb{H}(\alpha)$} (C')
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$F^\prime(\alpha \kappa \kappa)(d_{(\mathbb{H}(M_1) \otimes \mathbb{H}(M_2)) \otimes \mathbb{H}(M_3)})$};
-\node (B) at (0,-0.5) {$F^\prime(\alpha \kappa)(d_{\mathbb{H}(M_1 \otimes M_2) \otimes \mathbb{H}(M_3)})$};
-\node (C) at (0,-1.5) {$F^\prime(\alpha)(d_{\mathbb{H}((M_1 \otimes M_2) \otimes M_3)})$};
-\node (A') at (5,0.5) {$F^\prime(\kappa \kappa)(d_{\mathbb{H}(M_1) \otimes (\mathbb{H}(M_2) \otimes \mathbb{H}(M_3))})$};
-\node (B') at (5,-0.5) {$F^\prime(\kappa)(d_{\mathbb{H}(M_1) \otimes \mathbb{H}(M_2 \otimes M_3)})$};
+\node (A) at (0,0.5) {$F'(\alpha \kappa \kappa)(d_{(\mathbb{H}(M_1) \otimes \mathbb{H}(M_2)) \otimes \mathbb{H}(M_3)})$};
+\node (B) at (0,-0.5) {$F'(\alpha \kappa)(d_{\mathbb{H}(M_1 \otimes M_2) \otimes \mathbb{H}(M_3)})$};
+\node (C) at (0,-1.5) {$F'(\alpha)(d_{\mathbb{H}((M_1 \otimes M_2) \otimes M_3)})$};
+\node (A') at (5,0.5) {$F'(\kappa \kappa)(d_{\mathbb{H}(M_1) \otimes (\mathbb{H}(M_2) \otimes \mathbb{H}(M_3))})$};
+\node (B') at (5,-0.5) {$F'(\kappa)(d_{\mathbb{H}(M_1) \otimes \mathbb{H}(M_2 \otimes M_3)})$};
 \node (C') at (5,-1.5) {$d_{\mathbb{H}(M_1 \otimes (M_2 \otimes M_3))}$};
 \path[->,font=\scriptsize,>=angle 90]
-(A) edge node[left]{$F^\prime(\alpha \kappa)(\tau_\kappa + 1)$} (B)
-(B) edge node[left]{$F^\prime(\alpha)(\tau_\kappa)$} (C)
-(A) edge node[above]{$F^\prime(\kappa \kappa)(\tau_{\alpha^\prime})$} (A')
+(A) edge node[left]{$F'(\alpha \kappa)(\tau_\kappa + 1)$} (B)
+(B) edge node[left]{$F'(\alpha)(\tau_\kappa)$} (C)
+(A) edge node[above]{$F'(\kappa \kappa)(\tau_{\alpha'})$} (A')
 (C) edge node [above] {$\tau_\alpha$} (C')
 (B') edge node [right] {$\tau_\kappa$} (C')
-(A') edge node [right]{$F^\prime(\kappa)(1+\tau_\kappa)$} (B');
-\end{tikzpicture}
-\]
-where $$F^\prime(\alpha \kappa \kappa)(d_{(\mathbb{H}(M_1) \otimes \mathbb{H}(M_2)) \otimes \mathbb{H}(M_3)}) = F^\prime(\kappa \kappa \alpha^\prime)(d_{(\mathbb{H}(M_1) \otimes \mathbb{H}(M_2)) \otimes \mathbb{H}(M_3)})$$
+(A') edge node [right]{$F'(\kappa)(1+\tau_\kappa)$} (B');
+\end{tikzpicture}
+\]
+where $$F'(\alpha \kappa \kappa)(d_{(\mathbb{H}(M_1) \otimes \mathbb{H}(M_2)) \otimes \mathbb{H}(M_3)}) = F'(\kappa \kappa \alpha')(d_{(\mathbb{H}(M_1) \otimes \mathbb{H}(M_2)) \otimes \mathbb{H}(M_3)})$$
 as the corresponding hexagon for the finite colimit preserving functor $H \maps \A \to \mathsf{A'}$ commutes.
-The map $\mu_{M_1,M_2}$ is also compatible with the braidings $\beta$ and $\beta^\prime$ of $F \mathbb{C}\textnormal{sp}_1$ and $F' \mathbb{C}\textnormal{sp}_1$, respectively, and make the necessary square commute as a consequence of the corresponding commutative square involving braidings from the finite colimit preserving functor $H \maps \A \to \mathsf{A'}$.
-
-We also have that the monoidal unit of $F\mathbb{C}\textnormal{sp}_1$ is given by:
+The map $\mu_{M_1,M_2}$ is also compatible with the braidings $\beta$ and $\beta'$ of $F \lCsp_1$ and $F' \lCsp_1$, respectively, and make the necessary square commute as a consequence of the corresponding commutative square involving braidings from the finite colimit preserving functor $H \maps \A \to \mathsf{A'}$.
+
+We also have that the monoidal unit of $F\lCsp_1$ is given by:
 \[
@@
 %\node (E) at (3,0) {$=$};
-%\node (F) at (4,0) {$1_\mathsf{A^\prime}$};
-%\node (G) at (5,0) {$1_\mathsf{A^\prime}$};
-%\node (H) at (6,0) {$1_\mathsf{A^\prime}$};
-%\node (I) at (5,-0.5) {$!_{1_{\mathsf{A^\prime}}} \in F^\prime(1_{\mathsf{A^\prime}})$};
-\node (D) at (1,-0.5) {$\theta_{1_\A}E(!_{1_\A}) \phi \in F^\prime(H(1_\A))$};
+%\node (F) at (4,0) {$1_\mathsf{A'}$};
+%\node (G) at (5,0) {$1_\mathsf{A'}$};
+%\node (H) at (6,0) {$1_\mathsf{A'}$};
+%\node (I) at (5,-0.5) {$!_{1_{\mathsf{A'}}} \in F'(1_{\mathsf{A'}})$};
+\node (D) at (1,-0.5) {$\theta_{1_\A}E(!_{1_\A}) \phi \in F'(H(1_\A))$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-as $H$ preserves finite colimits.
-We then have a 2-isomorphism in $F'\mathbb{C}\textnormal{sp}$ given by: $$\mu \maps 1_{F'\mathbb{C}\textnormal{sp}_1} \to \mathbb{H}(1_{F\mathbb{C}\textnormal{sp}_1})$$
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$1_{\mathsf{A^\prime}}$};
+as $H$ preserves finite colimits. We then have a 2-isomorphism in $F'\lCsp$ given by: $$\mu \maps 1_{F'\lCsp_1} \to \mathbb{H}(1_{F\lCsp_1})$$ 
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0.5) {$1_{\mathsf{A'}}$};
 \node (A') at (0,-0.5) {$H(1_\A)$};
-\node (B) at (1.5,0.5) {$1_{\mathsf{A^\prime}}$};
-\node (C) at (3,0.5) {$1_{\mathsf{A^\prime}}$};
+\node (B) at (1.5,0.5) {$1_{\mathsf{A'}}$};
+\node (C) at (3,0.5) {$1_{\mathsf{A'}}$};
 \node (C') at (3,-0.5) {$H(1_\A)$};
 \node (D) at (1.5,-0.5) {$H(1_\A)$};
-\node (E) at (5,0.5) {$!_{1_\mathsf{A^\prime}} \in F^\prime(1_\mathsf{A^\prime})$};
-\node (F) at (5,-0.5) {$\theta_{1_\A} E(!_{1_\A}) \phi \in F^\prime(H(1_\A))$};
+\node (E) at (5,0.5) {$!_{1_\mathsf{A'}} \in F'(1_\mathsf{A'})$};
+\node (F) at (5,-0.5) {$\theta_{1_\A} E(!_{1_\A}) \phi \in F'(H(1_\A))$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-together with the morphism $\tau_\mu \maps F^\prime(\kappa)(!_{1_\mathsf{A^\prime}}) \to (\theta_{1_\A} E(!_{1_\A})\phi)$ in $F^\prime(H(1_\A))$.
-The following square then commutes for any horizontal 1-cell $M$ of $F \mathbb{C}\textnormal{sp}$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$1_\mathsf{A^\prime} \otimes \mathbb{H}(M)$};
+together with the morphism $\tau_\mu \maps F'(\kappa)(!_{1_\mathsf{A'}}) \to (\theta_{1_\A} E(!_{1_\A})\phi)$ in $F'(H(1_\A))$.
+The following square then commutes for any horizontal 1-cell $M$ of $F \lCsp$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$1_\mathsf{A'} \otimes \mathbb{H}(M)$};
 \node (B) at (2.5,0) {$\mathbb{H}(1_\A) \otimes \mathbb{H}(M)$};
@@
 (B) edge node[right]{$\mu_{1_\mathrm{A},M}$} (D)
-(D) edge node[above]{$\mathbb{H}(\ell^\prime)$} (C);
-\end{tikzpicture}
-\]
-where we have abbreviated the monoidal units of $F\mathbb{C}\textnormal{sp}_1$ and $F'\mathbb{C}\textnormal{sp}_1$ as $1_\A$ and $1_\mathsf{A^\prime}$, respectively.
-The diagram of corresponding decorations is given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$F^\prime(\ell)(d_{!_{1_\mathsf{A^\prime}}} \otimes d_{\mathbb{H}(M)})$};
+(D) edge node[above]{$\mathbb{H}(\ell')$} (C);
+\end{tikzpicture}
+\]
+where we have abbreviated the monoidal units of $F\lCsp_1$ and $F'\lCsp_1$ as $1_\A$ and $1_\mathsf{A'}$, respectively. The diagram of corresponding decorations is given by:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0.5) {$F'(\ell)(d_{!_{1_\mathsf{A'}}} \otimes d_{\mathbb{H}(M)})$};
 \node (B) at (0,-0.5) {$d_{\mathbb{H}(M)}$};
-\node (A') at (4,0.5) {$F^\prime(H(\ell^\prime) \kappa)(d_{!_{\mathbb{H}(1_\A)}}\otimes d_{\mathbb{H}(M)})$};
-\node (B') at (4,-0.5) {$F^\prime(H(\ell^\prime))(d_{\mathbb{H}(1_\A \otimes M)})$};
+\node (A') at (4,0.5) {$F'(H(\ell') \kappa)(d_{!_{\mathbb{H}(1_\A)}}\otimes d_{\mathbb{H}(M)})$};
+\node (B') at (4,-0.5) {$F'(H(\ell'))(d_{\mathbb{H}(1_\A \otimes M)})$};
 \path[->,font=\scriptsize,>=angle 90]
 (A) edge node[left]{$\tau_\ell$} (B)
-(A) edge node[above]{$F^\prime(H(\ell^\prime)\kappa)(\tau_{\mu \otimes 1})$} (A')
-(A') edge node [right]{$F^\prime(H(\ell^\prime))(\tau_\kappa)$} (B')
-(B') edge node [above] {$\tau_{H(\ell^\prime)}$} (B);
-\end{tikzpicture}
-\]
-where $$F^\prime(\ell)(d_{!_{1_\mathsf{A^\prime}}} \otimes d_{\mathbb{H}(M)})=F^\prime(H(\ell^\prime)\kappa(\mu \otimes 1))(d_{!_{1_\mathsf{A^\prime}}} \otimes d_{\mathbb{H}(M)})$$ since the corresponding square involving left unitors for the finite colimit preserving functor $H \maps \A \to \mathsf{A'}$ commutes.
-The other square involving the right unitors $r$ and $r^\prime$ is similar.
+(A) edge node[above]{$F'(H(\ell')\kappa)(\tau_{\mu \otimes 1})$} (A')
+(A') edge node [right]{$F'(H(\ell'))(\tau_\kappa)$} (B')
+(B') edge node [above] {$\tau_{H(\ell')}$} (B);
+\end{tikzpicture}
+\]
+where $$F'(\ell)(d_{!_{1_\mathsf{A'}}} \otimes d_{\mathbb{H}(M)})=F'(H(\ell')\kappa(\mu \otimes 1))(d_{!_{1_\mathsf{A'}}} \otimes d_{\mathbb{H}(M)})$$ since the corresponding square involving left unitors for the finite colimit preserving functor $H \maps \A \to \mathsf{A'}$ commutes.
+The other square involving the right unitors $r$ and $r'$ is similar.
 Note that because the comparison constraints $\mu$ and $\mu_{(\_ , \_)}$ are both isomorphisms, the symmetric monoidal double functor $\mathbb{H}$ is strong.
@@
 \begin{thm}
-Given two finitely cocomplete categories $\A$ and $\A'$, two symmetric lax monoidal pseudofunctors $F \maps \A \to \Cat$ and $F' \maps \A' \to \Cat$, a finite colimit preserving functor $H \maps \A \to \A'$, a symmetric lax monoidal pseudofunctor $E \maps \Cat \to \Cat$ and a 2-isomorphism $\theta \maps EF \Rightarrow F^\prime H$ as in the following diagram, the triple $(H,E,\theta)$ induces a symmetric monoidal (strong) double functor $\mathbb{H} \maps F\mathbb{C}\textnormal{sp} \to F'\mathbb{C}\textnormal{sp}$ as defined above.
+Given two finitely cocomplete categories $\A$ and $\A'$, two symmetric lax monoidal pseudofunctors $F \maps \A \to \Cat$ and $F' \maps \A' \to \Cat$, a finite colimit preserving functor $H \maps \A \to \A'$, a symmetric lax monoidal pseudofunctor $E \maps \Cat \to \Cat$ and a 2-isomorphism $\theta \maps EF \Rightarrow F' H$ as in the following diagram, the triple $(H,E,\theta)$ induces a symmetric monoidal (strong) double functor $\mathbb{H} \maps F\lCsp \to F'\lCsp$ as defined above.
 \[
@@
 
-%is given by $$1 \to F(c_1) \times F(c_2) \xrightarrow{} F(c_1 + c_2) \xrightarrow{} F(c_1 + _b c_2)$$ and then applying the functor $E$ results in $1 \to E(F(c_1+_b c_2))$, which by the comutative square is the same as $1 \to F^\prime(H(c_1+_b c_2))$.
-On the other hand, applying the functor $E$ to each decoration results in $$1 \to E(F(c_1)) \times E(F(c_2)) \xrightarrow{} E(F(c_1) \times F(c_2)) \xrightarrow{} E(F(c_1+c_2)) \xrightarrow E(F(c_1+_b c_2)) \xrightarrow{} F^\prime(H(c_1 +_b c_2))$$
+%is given by $$1 \to F(c_1) \times F(c_2) \xrightarrow{} F(c_1 + c_2) \xrightarrow{} F(c_1 + _b c_2)$$ and then applying the functor $E$ results in $1 \to E(F(c_1+_b c_2))$, which by the comutative square is the same as $1 \to F'(H(c_1+_b c_2))$.
+On the other hand, applying the functor $E$ to each decoration results in $$1 \to E(F(c_1)) \times E(F(c_2)) \xrightarrow{} E(F(c_1) \times F(c_2)) \xrightarrow{} E(F(c_1+c_2)) \xrightarrow E(F(c_1+_b c_2)) \xrightarrow{} F'(H(c_1 +_b c_2))$$
 
@@
 \begin{thm}\label{SC}
-Given a category $\X$ with finite colimits and a category $\A$ with finite coproducts and a finite coproduct preserving functor $L \maps \A \to \X$ with $\A$ and $\X$, there exists a symmetric monoidal double category $_L \mathbb{C}\textnormal{sp}(\X)$ which has:
+Given a category $\X$ with finite colimits and a category $\A$ with finite coproducts and a finite coproduct preserving functor $L \maps \A \to \X$ with $\A$ and $\X$, there exists a symmetric monoidal double category $_L \lCsp(\X)$ which has:
 \begin{itemize}
@@
 Suppose $\ca{A}$ is a finitely cocomplete category and $(F,\phi,\phi_0)\maps(\ca{A},+,0) \to (\bicat{Cat},\times,\mathbf{1})$ is a symmetric lax monoidal pseudofunctor that factors through $\bicat{Rex}$ as an ordinary pseudofunctor.
-Then the symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$ of decorated cospans given in \cref{thm:decoratedcospans} is equivalent to the symmetric monoidal double category $\scsp{L_F}{\inta F}$ of structured cospans given in \cref{SC}, where $L_F \maps \A \to \inta{F}$ is the left adjoint of the induced Grothendieck opfibration $\U_F\maps \inta{F} \to \A$.
+Then the symmetric monoidal double category $F\lCsp$ of decorated cospans given in \cref{thm:decoratedcospans} is equivalent to the symmetric monoidal double category $\scsp{L_F}{\inta F}$ of structured cospans given in \cref{SC}, where $L_F \maps \A \to \inta{F}$ is the left adjoint of the induced Grothendieck opfibration $\U_F\maps \inta{F} \to \A$.
 %by \cref{thm:Grothendieck},
@@
 \node (B) at (1,0) {$x$};
-\node (C) at (2,0) {$L(c^\prime)$};
+\node (C) at (2,0) {$L(c')$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \node (B) at (1,0) {$R(x)$};
-\node (C) at (2,0) {$c^\prime$};
+\node (C) at (2,0) {$c'$};
 \node (D) at (3,0) {$x \in F(R(x))$};
@@
 (A) edge node[above]{$R(i) {\eta_c}$} (B)
-(C) edge node[above]{$R(o) {\eta_{c^\prime}}$} (B);
+(C) edge node[above]{$R(o) {\eta_{c'}}$} (B);
 \end{tikzpicture}
@@
 where $R\maps \X \to \A$ is the right adjoint to the functor $L \maps \A \to \X$ and $\eta \maps 1_{\A} \to RL$ is the unit of the adjunction $L \dashv R$ which is an isomorphism since $L$ is fully faithful.
-\textbf{Hopefully...actually, it's a `lari'!} Similarly, the image of a 2-morphism $\alpha \maps M \to N$ in $_L \mathbb{C}\textnormal{sp}(\X)$:
+\textbf{Hopefully...actually, it's a `lari'!} Similarly, the image of a 2-morphism $\alpha \maps M \to N$ in $_L \lCsp(\X)$:
 \[
@@
 \node (C) at (2,0) {$L(c_2)$};
-\node (A') at (0,-1) {$L(c_1^\prime)$};
-\node (B') at (1,-1) {$x^\prime$};
-\node (C') at (2,-1) {$L(c_2^\prime)$};
+\node (A') at (0,-1) {$L(c_1')$};
+\node (B') at (1,-1) {$x'$};
+\node (C') at (2,-1) {$L(c_2')$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (C) edge node[above]{$o$} (B)
-(A') edge node[above]{$i^\prime$} (B')
-(C') edge node[above]{$o^\prime$} (B')
+(A') edge node[above]{$i'$} (B')
+(C') edge node[above]{$o'$} (B')
 (A) edge node [left]{$L(f)$} (A')
@@
 \node (C) at (2,0) {$c_2$};
-\node (A') at (0,-1) {$c_1^\prime$};
-\node (B') at (1,-1) {$R(x^\prime)$};
-\node (C') at (2,-1) {$c_2^\prime$};
+\node (A') at (0,-1) {$c_1'$};
+\node (B') at (1,-1) {$R(x')$};
+\node (C') at (2,-1) {$c_2'$};
 \node (D) at (3,0) {$x \in F(R(x))$};
-\node (D') at (3,-1) {$x^\prime \in F(R(x^\prime))$};
+\node (D') at (3,-1) {$x' \in F(R(x'))$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (C) edge node[above]{$R(o) \eta_{c_2}$} (B)
-(A') edge node[above]{$R(i^\prime) \eta_{c_1^\prime}$} (B')
-(C') edge node[above]{$R(o^\prime) \eta_{c_2^\prime}$} (B')
+(A') edge node[above]{$R(i') \eta_{c_1'}$} (B')
+(C') edge node[above]{$R(o') \eta_{c_2'}$} (B')
 (A) edge node [left]{$f$} (A')
@@
 \]
-together with a morphism $\tau \maps F(R(\alpha))(x) \to x^\prime$ in $F(R(x^\prime)) \subseteq \mathrm{X}$ which comes from the Grothendieck construction of the pseudofunctor $F \maps \A \to \Cat$.
+together with a morphism $\tau \maps F(R(\alpha))(x) \to x'$ in $F(R(x')) \subseteq \mathrm{X}$ which comes from the Grothendieck construction of the pseudofunctor $F \maps \A \to \Cat$.
 That $\mathbb{E}_0$ is a functor is clear.
-For $\mathbb{E}_1$, given two vertically composable 2-morphisms $M$ and $M'$ in $_L \mathbb{C}\textnormal{sp}(\X)$,
+For $\mathbb{E}_1$, given two vertically composable 2-morphisms $M$ and $M'$ in $_L \lCsp(\X)$,
 \[
@@
 \node (C) at (2,0) {$L(c_2)$};
-\node (A') at (0,-1) {$L(c_1^\prime)$};
-\node (B') at (1,-1) {$x^\prime$};
-\node (C') at (2,-1) {$L(c_2^\prime)$};
-\node (A'') at (0,-2) {$L(c_1^\prime)$};
+\node (A') at (0,-1) {$L(c_1')$};
+\node (B') at (1,-1) {$x'$};
+\node (C') at (2,-1) {$L(c_2')$};
+\node (A'') at (0,-2) {$L(c_1')$};
 \node (B'') at (1,-2) {$x'$};
@@
 
-To see that this functor is essentially surjective, given a horizontal 1-cell in $F\mathbb{C}\textnormal{sp}$:
+To see that this functor is essentially surjective, given a horizontal 1-cell in $F\lCsp$:
 \[
@@
 \]
-we can find a 2-isomorphism in $F\mathbb{C}\textnormal{sp}$ whose codomain is the above horizontal 1-cell and whose domain is the image of the following horizontal 1-cell in $_L \mathbb{C}\textnormal{sp}(\X)$:
+we can find a 2-isomorphism in $F\lCsp$ whose codomain is the above horizontal 1-cell and whose domain is the image of the following horizontal 1-cell in $_L \lCsp(\X)$:
 \[
@@
 \path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i^\prime$} (B)
-(C) edge node[above]{$o^\prime$} (B);
-\end{tikzpicture}
-\]
-with the 2-isomorphism in $F\mathbb{C}\textnormal{sp}$ given by:
+(A) edge node[above]{$i'$} (B)
+(C) edge node[above]{$o'$} (B);
+\end{tikzpicture}
+\]
+with the 2-isomorphism in $F\lCsp$ given by:
 \[
@@
 \path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$R(i^\prime) \eta_{c_1}$} (B)
-(C) edge node[above]{$R(o^\prime) \eta_{c_2}$} (B)
+(A) edge node[above]{$R(i') \eta_{c_1}$} (B)
+(C) edge node[above]{$R(o') \eta_{c_2}$} (B)
 (A') edge node[above]{$i$} (B')
@@
 
-To show that the double functor $\mathbb{E}$ is fully faithful, we need to show that the map  $$\mathbb{E}_1 \maps _f { _L \mathbb{C}\textnormal{sp}(\X)}_g(M,N) \to {_{\mathbb{E}(f)} {F\mathbb{C}\textnormal{sp}}_{\mathbb{E}(g)}}(\mathbb{E}(M),\mathbb{E}(N))$$ is bijective for arbitrary vertical 1-morphisms $f$ and $g$ and horizontal 1-cells $M$ and $N$ of $_L \mathbb{C}\textnormal{sp}(\X)$.
-Consider a 2-morphism in $_L \mathbb{C}\textnormal{sp}(\X)$ with horizontal source and target $M$ and $N$, respectively and vertical source and target $f$ and $g$, respectively:
+To show that the double functor $\mathbb{E}$ is fully faithful, we need to show that the map  $$\mathbb{E}_1 \maps _f { _L \lCsp(\X)}_g(M,N) \to {_{\mathbb{E}(f)} {F\lCsp}_{\mathbb{E}(g)}}(\mathbb{E}(M),\mathbb{E}(N))$$ is bijective for arbitrary vertical 1-morphisms $f$ and $g$ and horizontal 1-cells $M$ and $N$ of $_L \lCsp(\X)$.
+Consider a 2-morphism in $_L \lCsp(\X)$ with horizontal source and target $M$ and $N$, respectively and vertical source and target $f$ and $g$, respectively:
 \[
@@
 \node (C) at (2,0) {$L(c_2)$};
-\node (A') at (0,-1) {$L(c_1^\prime)$};
-\node (B') at (1,-1) {$x^\prime$};
-\node (C') at (2,-1) {$L(c_2^\prime)$};
+\node (A') at (0,-1) {$L(c_1')$};
+\node (B') at (1,-1) {$x'$};
+\node (C') at (2,-1) {$L(c_2')$};
 \node (D) at (1,0.5) {$M$};
@@
 \]
-Thus the set $$_f { _L \mathbb{C}\textnormal{sp}(\X)}_g(M,N)$$ consists of triples $$(f,\alpha,g)$$ rendering the above diagram commutative where $f$ and $g$ are morphisms of $\A$ and $\alpha$ is a morphism of $\X$.
+Thus the set $$_f { _L \lCsp(\X)}_g(M,N)$$ consists of triples $$(f,\alpha,g)$$ rendering the above diagram commutative where $f$ and $g$ are morphisms of $\A$ and $\alpha$ is a morphism of $\X$.
 The image of the above 2-morphism under the double functor $\mathbb{E}$ is given by:
@@
 \node (C) at (2,0) {$c_2$};
-\node (A') at (0,-1) {$c_1^\prime$};
-\node (B') at (1,-1) {$R(x^\prime)$};
-\node (C') at (2,-1) {$c_2^\prime$};
+\node (A') at (0,-1) {$c_1'$};
+\node (B') at (1,-1) {$R(x')$};
+\node (C') at (2,-1) {$c_2'$};
 \node (D) at (1,0.5) {$x \in F(R(x))$};
-\node (D') at (1,-1.5) {$x^\prime \in F(R(x^\prime))$};
+\node (D') at (1,-1.5) {$x' \in F(R(x'))$};
 \node (E) at (1,1) {$\mathbb{E}(M)$};
@@
 (C) edge node[above]{$R(o)\eta_{c_2}$} (B)
-(A') edge node[above]{$R(i^\prime)\eta_{c_1^\prime}$} (B')
-(C') edge node[above]{$R(o^\prime)\eta_{c_2^\prime}$} (B')
+(A') edge node[above]{$R(i')\eta_{c_1'}$} (B')
+(C') edge node[above]{$R(o')\eta_{c_2'}$} (B')
 (A) edge node [left]{$f$} (A')
@@
 \]
-together with a morphism $\tau \maps F(R(\alpha))(x) \to x^\prime$ of $F(R(x^\prime))$.
-Thus the set $$_{\mathbb{E}(f)} {F\mathbb{C}\textnormal{sp}}_{\mathbb{E}(g)}(\mathbb{E}(M),\mathbb{E}(N))$$ consists of 4-tuples $$(f,R(\alpha),g,\tau)$$ rendering the above diagram commutative and where $f,g$ and $R(\alpha)$ are morphisms of $\A$ and $\tau$ is a morphism in $F(R(x'))$.
-The morphisms $R(\alpha) \maps R(x) \to R(x^\prime)$ and $\tau \maps F(R(\alpha))(x) \to x^\prime$ together determine the morphism $\alpha \maps x \to x^\prime$ in $\mathrm{X}$ and conversely; given two objects $x=(c,x \in F(c))$ and $x^\prime=(c^\prime,x^\prime \in F(c^\prime))$ of $\X=\inta{F}$, a morphism from $\alpha \maps x \to x^\prime$ is a pair $$(h \maps c \to c^\prime, \tau \maps F(h)(x) \to x^\prime)$$ where $h \maps c \to c^\prime$ is given by $R(\alpha) \maps R(x) \to R(x^\prime)$.
+together with a morphism $\tau \maps F(R(\alpha))(x) \to x'$ of $F(R(x'))$.
+Thus the set $$_{\mathbb{E}(f)} {F\lCsp}_{\mathbb{E}(g)}(\mathbb{E}(M),\mathbb{E}(N))$$ consists of 4-tuples $$(f,R(\alpha),g,\tau)$$ rendering the above diagram commutative and where $f,g$ and $R(\alpha)$ are morphisms of $\A$ and $\tau$ is a morphism in $F(R(x'))$.
+The morphisms $R(\alpha) \maps R(x) \to R(x')$ and $\tau \maps F(R(\alpha))(x) \to x'$ together determine the morphism $\alpha \maps x \to x'$ in $\mathrm{X}$ and conversely; given two objects $x=(c,x \in F(c))$ and $x'=(c',x' \in F(c'))$ of $\X=\inta{F}$, a morphism from $\alpha \maps x \to x'$ is a pair $$(h \maps c \to c', \tau \maps F(h)(x) \to x')$$ where $h \maps c \to c'$ is given by $R(\alpha) \maps R(x) \to R(x')$.
 This shows that $\mathbb{E}$ is fully faithful.
@@
 $$\tau \maps F(\eta_c)(!_c) \xrightarrow{!} !_{R(L(c))}$$
-of $F\mathbb{C}\textnormal{sp}$.
-
-Next, given composable horizontal 1-cells $M$ and $N$ in $_L \mathbb{C}\textnormal{sp}(\X)$:
+of $F\lCsp$.
+
+Next, given composable horizontal 1-cells $M$ and $N$ in $_L \lCsp(\X)$:
 \[
@@
 \node (D) at (3,0) {$L(c_2)$};
-\node (E) at (4,0) {$x^\prime$};
+\node (E) at (4,0) {$x'$};
 \node (F) at (5,0) {$L(c_3)$};
@@
 (C) edge node[above]{$o$} (B)
-(D) edge node[above]{$i^\prime$} (E)
-(F) edge node[above]{$o^\prime$} (E);
+(D) edge node[above]{$i'$} (E)
+(F) edge node[above]{$o'$} (E);
 \end{tikzpicture}
@@
 \node (D) at (3,0) {$c_2$};
-\node (E) at (4,0) {$R(x^\prime)$};
+\node (E) at (4,0) {$R(x')$};
 \node (F) at (5,0) {$c_3$};
 \node (G) at (1,-0.5) {$x \in F(R(x))$};
-\node (H) at (4,-0.5) {$x^\prime \in F(R(x^\prime))$};
+\node (H) at (4,-0.5) {$x' \in F(R(x'))$};
 %\node (D) at (3,0.5) {$!_c \in F(c)$};
@@
 (C) edge node[above]{$R(o) \eta_{c_2}$} (B)
-(D) edge node[above]{$R(i^\prime) \eta_{c_2}$} (E)
-(F) edge node[above]{$R(o^\prime) \eta_{c_3}$} (E);
+(D) edge node[above]{$R(i') \eta_{c_2}$} (E)
+(F) edge node[above]{$R(o') \eta_{c_3}$} (E);
 \end{tikzpicture}
@@
 \node (A) at (0,0) {$c_1$};
-\node (B) at (1.5,0) {$R(x)+_{c_2}R(x^\prime)$};
+\node (B) at (1.5,0) {$R(x)+_{c_2}R(x')$};
 \node (C) at (3,0) {$c_3$};
-\node (G) at (1.5,-0.5) {$d_{\mathbb{E}(M) \odot \mathbb{E}(N)} = \hat{x} \in F(R(x)+_{c_2}R(x^\prime))$};
+\node (G) at (1.5,-0.5) {$d_{\mathbb{E}(M) \odot \mathbb{E}(N)} = \hat{x} \in F(R(x)+_{c_2}R(x'))$};
 %\node (D) at (3,0.5) {$!_c \in F(c)$};
@@
 (A) edge node[above]{$j \psi R(i) \eta_{c_1}$} (B)
-(C) edge node[above]{$j \psi R(o^\prime) \eta_{c_3}$} (B);
-\end{tikzpicture}
-\]
-$$\hat{x} \maps 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{x \times x^\prime} F(R(x)) \times F(R(x^\prime)) \xrightarrow{\phi_{R(x),R(x^\prime)}} F(R(x)+R(x^\prime)) \xrightarrow{F(j_{R(x),R(x^\prime)})} F(R(x)+_{c_2}R(x^\prime))$$where $\psi$ denotes each natural map into the coproduct and $j$ denotes the natural map from the coproduct to the pushout.
+(C) edge node[above]{$j \psi R(o') \eta_{c_3}$} (B);
+\end{tikzpicture}
+\]
+$$\hat{x} \maps 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{x \times x'} F(R(x)) \times F(R(x')) \xrightarrow{\phi_{R(x),R(x')}} F(R(x)+R(x')) \xrightarrow{F(j_{R(x),R(x')})} F(R(x)+_{c_2}R(x'))$$where $\psi$ denotes each natural map into the coproduct and $j$ denotes the natural map from the coproduct to the pushout.
 On the other hand, $M \odot N$ is given by
@@
 \node (A) at (0,0) {$L(c_1)$};
-\node (B) at (1.25,0) {$x+_{L(c_2)}x^\prime$};
+\node (B) at (1.25,0) {$x+_{L(c_2)}x'$};
 \node (C) at (2.5,0) {$L(c_3)$};
-%\node (G) at (1,-0.5) {$\hat{d} \in F(R(d)+_{c_2}R(d^\prime))$};
+%\node (G) at (1,-0.5) {$\hat{d} \in F(R(d)+_{c_2}R(d'))$};
 %\node (D) at (3,0.5) {$!_c \in F(c)$};
@@
 (A) edge node[above]{$J \zeta i$} (B)
-(C) edge node[above]{$J \zeta o^\prime$} (B);
+(C) edge node[above]{$J \zeta o'$} (B);
 \end{tikzpicture}
@@
 \node (A) at (0,0) {$c_1$};
-\node (B) at (1.5,0) {$R(x+_{L(c_2)}x^\prime)$};
+\node (B) at (1.5,0) {$R(x+_{L(c_2)}x')$};
 \node (C) at (3,0) {$c_3$};
-\node (G) at (1.5,-0.5) {$d_{\mathbb{E}(M \odot N)} = x+_{L(c_2)} x^\prime \in F(R(x+_{L(c_2)}x^\prime))$};
+\node (G) at (1.5,-0.5) {$d_{\mathbb{E}(M \odot N)} = x+_{L(c_2)} x' \in F(R(x+_{L(c_2)}x'))$};
 %\node (D) at (3,0.5) {$!_c \in F(c)$};
@@
 (A) edge node[above]{$R(J \zeta i) \eta_{c_1}$} (B)
-(C) edge node[above]{$R(J \zeta o^\prime) \eta_{c_3}$} (B);
+(C) edge node[above]{$R(J \zeta o') \eta_{c_3}$} (B);
 \end{tikzpicture}
@@
 \node (A) at (0,0) {$c_1$};
-\node (B) at (1.5,0) {$R(x)+_{c_2}R(x^\prime)$};
+\node (B) at (1.5,0) {$R(x)+_{c_2}R(x')$};
 \node (C) at (3,0) {$c_3$};
 \node (A') at (0,-1) {$c_1$};
-\node (B') at (1.5,-1) {$R(x+_{L(c_2)}x^\prime)$};
+\node (B') at (1.5,-1) {$R(x+_{L(c_2)}x')$};
 \node (C') at (3,-1) {$c_3$};
-\node (D) at (5.5 ,0) {$d_{\mathbb{E}(M) \odot \mathbb{E}(N)} \in F(R(x)+_{c_2}R(x^\prime))$};
-\node (D') at (5.5,-1) {$d_{\mathbb{E}(M \odot N)} \in F(R(x+_{L(c_2)}x^\prime))$};
+\node (D) at (5.5 ,0) {$d_{\mathbb{E}(M) \odot \mathbb{E}(N)} \in F(R(x)+_{c_2}R(x'))$};
+\node (D') at (5.5,-1) {$d_{\mathbb{E}(M \odot N)} \in F(R(x+_{L(c_2)}x'))$};
 \path[->,font=\scriptsize,>=angle 90]
 (A) edge node[above]{$j \psi R(i) \eta_{c_1}$} (B)
-(C) edge node[above]{$j \psi R(o^\prime) \eta_{c_3}$} (B)
+(C) edge node[above]{$j \psi R(o') \eta_{c_3}$} (B)
 (A') edge node[above]{$R(J \zeta i) \eta_{c_1}$} (B')
-(C') edge node[above]{$R(J \zeta o^\prime) \eta_{c_3}$} (B')
+(C') edge node[above]{$R(J \zeta o') \eta_{c_3}$} (B')
 (A) edge node [left]{$1$} (A')
@@
 together with a morphism of decorations which is obtained as follows.
-First, as $R \maps \X \to \A$ preserves finite colimits, we have an isomorphism $$\kappa \maps R(x) +_{R(L(c_2))} R(x^\prime) \to R(x+_{L(c_2)}x^\prime).$$ Also, since the left adjoint $L \maps \A \to \X$ is fully faithful, the unit of the adjunction $L \dashv R$ at the object $c_2$ gives an isomorphism $\eta_{c_2} \maps c_2 \to R(L(c_2))$ which results in an isomorphism $$j_{\eta_{c_2}} \maps R(x) +_{c_2} R(x^\prime) \to R(x) +_{R(L(c_2))} R(x^\prime).$$ Composing these two results in an isomorphism $$\sigma \mapseqq \kappa j_{\eta_{c_2}} \maps R(x) +_{c_2} R(x^\prime) \to R(x+_{L(c_2)}x^\prime).$$
+First, as $R \maps \X \to \A$ preserves finite colimits, we have an isomorphism $$\kappa \maps R(x) +_{R(L(c_2))} R(x') \to R(x+_{L(c_2)}x').$$ Also, since the left adjoint $L \maps \A \to \X$ is fully faithful, the unit of the adjunction $L \dashv R$ at the object $c_2$ gives an isomorphism $\eta_{c_2} \maps c_2 \to R(L(c_2))$ which results in an isomorphism $$j_{\eta_{c_2}} \maps R(x) +_{c_2} R(x') \to R(x) +_{R(L(c_2))} R(x').$$ Composing these two results in an isomorphism $$\sigma \mapseqq \kappa j_{\eta_{c_2}} \maps R(x) +_{c_2} R(x') \to R(x+_{L(c_2)}x').$$
 Next, to see that the above diagram commutes, it suffices to show that for the object $c_1 \in \mathrm{A}$, $$R(J)R(\zeta)R(i)\eta_{c_1}(c_1) = R(J \zeta i)\eta_{c_1}(c_1)  \stackrel{!}{=} \sigma j \psi R(i)\eta_{c_1}(c_1) = \kappa j_{\eta_{c_2}} \psi R(i) \eta_{c_1}(c_1).$$ This follows as $R(i) \eta_{c_1} \maps c_1 \to R(x)$ and the following diagram commutes:
@@
 \node (B) at (0,0) {$R(x)$};
-\node (C) at (2,0) {$R(x)+R(x^\prime)$};
-\node (A') at (4,0) {$R(x)+_{c_2}R(x^\prime)$};
-\node (B') at (4,-2) {$R(x+_{L(c_2)}x^\prime)$};
-\node (D) at (0,-2) {$R(x+x^\prime)$};
-\node (D') at (4,-1) {$R(x)+_{R(L(c_2))} R(x^\prime)$};
+\node (C) at (2,0) {$R(x)+R(x')$};
+\node (A') at (4,0) {$R(x)+_{c_2}R(x')$};
+\node (B') at (4,-2) {$R(x+_{L(c_2)}x')$};
+\node (D) at (0,-2) {$R(x+x')$};
+\node (D') at (4,-1) {$R(x)+_{R(L(c_2))} R(x')$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-Lastly, this map of cospans comes with an isomorphism $$\tau \maps F(\sigma)(d_{\mathbb{E}(M) \odot \mathbb{E}(N)}) \to d_{\mathbb{E}(M \odot N)}$$ in $F(R(x+_{L(c_2)}x^\prime))$.
+Lastly, this map of cospans comes with an isomorphism $$\tau \maps F(\sigma)(d_{\mathbb{E}(M) \odot \mathbb{E}(N)}) \to d_{\mathbb{E}(M \odot N)}$$ in $F(R(x+_{L(c_2)}x'))$.
 This shows that $\mathbb{E}$ is strong, and so
@@
 
-Next, we show that if both double categories $_L \mathbb{C}\textnormal{sp}(\X)$ and $F\mathbb{C}\textnormal{sp}$ are symmetric monoidal, as they are if both $\A$ and $\X$ have finite colimits, then this equivalence of double categories $\mathbb{E} \maps _L \mathbb{C}\textnormal{sp}(\X) \to F\mathbb{C}\textnormal{sp}$ will be symmetric monoidal.
-First, note that we have an isomorphism $\epsilon \maps 1_{F\mathbb{C}\textnormal{sp}} \to \mathbb{E}(1_{_L \mathbb{C}\textnormal{sp}(\X)})$ and natural isomorphisms $\mu_{c_1,c_2} \maps \mathbb{E}(c_1) \otimes \mathbb{E}(c_2) \to \mathbb{E}(c_1 \otimes c_2)$ for every pair of objects $c_1,c_2 \in {_L \mathbb{C} \textnormal{sp}(\X)}$ both of which are given by identities since both double categories $_L \mathbb{C}\textnormal{sp}(\X)$ and $F\mathbb{C}\textnormal{sp}$ have $\A$ as their category of objects and $\mathbb{E}_0=\id_{\A}$.
+Next, we show that if both double categories $_L \lCsp(\X)$ and $F\lCsp$ are symmetric monoidal, as they are if both $\A$ and $\X$ have finite colimits, then this equivalence of double categories $\mathbb{E} \maps _L \lCsp(\X) \to F\lCsp$ will be symmetric monoidal.
+First, note that we have an isomorphism $\epsilon \maps 1_{F\lCsp} \to \mathbb{E}(1_{_L \lCsp(\X)})$ and natural isomorphisms $\mu_{c_1,c_2} \maps \mathbb{E}(c_1) \otimes \mathbb{E}(c_2) \to \mathbb{E}(c_1 \otimes c_2)$ for every pair of objects $c_1,c_2 \in {_L \mathbb{C} \textnormal{sp}(\X)}$ both of which are given by identities since both double categories $_L \lCsp(\X)$ and $F\lCsp$ have $\A$ as their category of objects and $\mathbb{E}_0=\id_{\A}$.
 The diagrams utilizing these maps that are required to commute do so trivially.
 
-For the arrow component $\mathbb{E}_1$, we have an isomorphism $\delta \maps U_{1_{F\mathbb{C}\textnormal{sp}}} \to \mathbb{E}(U_{1_{_L \mathbb{C}\textnormal{sp}(\X)}})$ where the horizontal 1-cell $U_{1_{F\mathbb{C}\textnormal{sp}}}$ is given by:
+For the arrow component $\mathbb{E}_1$, we have an isomorphism $\delta \maps U_{1_{F\lCsp}} \to \mathbb{E}(U_{1_{_L \lCsp(\X)}})$ where the horizontal 1-cell $U_{1_{F\lCsp}}$ is given by:
 \[
@@
 where $!_{1_{\A}} = \phi \maps 1 \to F(1_\A)$ is the trivial decoration which comes from the structure of the symmetric lax monoidal pseudofunctor $F \maps \A \to \Cat$.
-The horizontal 1-cell $U_{1_{_L \mathbb{C}\textnormal{sp}(\X)}}$ is given by:
+The horizontal 1-cell $U_{1_{_L \lCsp(\X)}}$ is given by:
 \[
@@
 $$\tau_{{\eta_{1_\A}}} \maps F({\eta_{1_\A}})(!_{1_\A})) \to !_{R(L(1_\A))}$$
-of $F\mathbb{C}\textnormal{sp}$. This is just the natural isomorphism $\mathbb{E}_{1_\A}$ from earlier.
-
-Given two horizontal 1-cells $M$ and $N$ of $_L \mathbb{C}\textnormal{sp}(\X)$:
+of $F\lCsp$. This is just the natural isomorphism $\mathbb{E}_{1_\A}$ from earlier.
+
+Given two horizontal 1-cells $M$ and $N$ of $_L \lCsp(\X)$:
 \[
@@
 \node (C) at (2,0) {$L(c_2)$};
-\node (D) at (3,0) {$L(c_1^\prime)$};
-\node (E) at (4,0) {$x^\prime$};
-\node (F) at (5,0) {$L(c_2^\prime)$};
+\node (D) at (3,0) {$L(c_1')$};
+\node (E) at (4,0) {$x'$};
+\node (F) at (5,0) {$L(c_2')$};
 %\node (D) at (3,0.5) {$!_c \in F(c)$};
@@
 \node (C) at (2,0) {$c_2$};
-\node (D) at (3,0) {$c_1^\prime$};
-\node (E) at (4,0) {$R(x^\prime)$};
-\node (F) at (5,0) {$c_2^\prime$};
+\node (D) at (3,0) {$c_1'$};
+\node (E) at (4,0) {$R(x')$};
+\node (F) at (5,0) {$c_2'$};
 \node (G) at (1,-0.5) {$x \in F(R(x))$};
-\node (H) at (4,-0.5) {$x^\prime \in F(R(x^\prime))$};
+\node (H) at (4,-0.5) {$x' \in F(R(x'))$};
 %\node (D) at (3,0.5) {$!_c \in F(c)$};
@@
 (C) edge node[above]{$R(o) \eta_{c_2}$} (B)
-(D) edge node[above]{$R(i^\prime) \eta_{c_1^\prime}$} (E)
-(F) edge node[above]{$R(o^\prime) \eta_{c_2^\prime}$} (E);
+(D) edge node[above]{$R(i') \eta_{c_1'}$} (E)
+(F) edge node[above]{$R(o') \eta_{c_2'}$} (E);
 \end{tikzpicture}
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$c_1+c_1^\prime$};
-\node (B) at (3.25,0) {$R(x)+R(x^\prime)$};
-\node (C) at (6.5,0) {$c_2+c_2^\prime$};
-\node (D) at (3.25,-0.5) {$d_{\mathbb{E}(M) \otimes \mathbb{E}(N)} \in F(R(x)+R(x^\prime))$}; 
+\node (A) at (0,0) {$c_1+c_1'$};
+\node (B) at (3.25,0) {$R(x)+R(x')$};
+\node (C) at (6.5,0) {$c_2+c_2'$};
+\node (D) at (3.25,-0.5) {$d_{\mathbb{E}(M) \otimes \mathbb{E}(N)} \in F(R(x)+R(x'))$}; 
 %\node (D) at (3,0.5) {$!_c \in F(c)$};
 \path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$R(i) \eta_{c_1} +R(i^\prime) \eta_{c_1^\prime}$} (B)
-(C) edge node[above]{$R(o) \eta_{c_2} + R(o) \eta_{c_2^\prime}$} (B);
-\end{tikzpicture}
-\]
-where $$d_{\mathbb{E}(M) \otimes \mathbb{E}(N)} \maps 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{x \times x^\prime} F(R(x)) \times F(R(x^\prime)) \xrightarrow{\phi_{R(x),R(x^\prime)}} F(R(x)+R(x^\prime)).$$ On the other hand, $M \otimes N$ is given by
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$L(c_1+c_1^\prime)$};
-\node (B) at (2,0) {$x+x^\prime$};
-\node (C) at (4,0) {$L(c_2+c_2^\prime)$};
+(A) edge node[above]{$R(i) \eta_{c_1} +R(i') \eta_{c_1'}$} (B)
+(C) edge node[above]{$R(o) \eta_{c_2} + R(o) \eta_{c_2'}$} (B);
+\end{tikzpicture}
+\]
+where $$d_{\mathbb{E}(M) \otimes \mathbb{E}(N)} \maps 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{x \times x'} F(R(x)) \times F(R(x')) \xrightarrow{\phi_{R(x),R(x')}} F(R(x)+R(x')).$$ On the other hand, $M \otimes N$ is given by
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$L(c_1+c_1')$};
+\node (B) at (2,0) {$x+x'$};
+\node (C) at (4,0) {$L(c_2+c_2')$};
 %\node (D) at (3,0.5) {$!_c \in F(c)$};
 \path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$(i+i^\prime)\phi_{c_1,c_1'}^{-1}$} (B)
-(C) edge node[above]{$(o+o^\prime)\phi_{c_2,c_2'}^{-1}$} (B);
+(A) edge node[above]{$(i+i')\phi_{c_1,c_1'}^{-1}$} (B)
+(C) edge node[above]{$(o+o')\phi_{c_2,c_2'}^{-1}$} (B);
 \end{tikzpicture}
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$c_1+c_1^\prime$};
-\node (B) at (4,0) {$R(x+x^\prime)$};
-\node (C) at (8,0) {$c_2+c_2^\prime$};
-\node (D) at (4,-0.5) {$d_{\mathbb{E}(M \odot N)} \in F(R(x+x^\prime)).$};
+\node (A) at (0,0) {$c_1+c_1'$};
+\node (B) at (4,0) {$R(x+x')$};
+\node (C) at (8,0) {$c_2+c_2'$};
+\node (D) at (4,-0.5) {$d_{\mathbb{E}(M \odot N)} \in F(R(x+x')).$};
 %\node (D) at (3,0.5) {$!_c \in F(c)$};
 \path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$R((i+i^\prime)\phi_{c_1,c_1'}^{-1}) \eta_{c_1+c_1^\prime}$} (B)
-(C) edge node[above]{$R((o+o^\prime)\phi_{c_2,c_2'}^{-1}) \eta_{c_2+c_2^\prime}$} (B);
-\end{tikzpicture}
-\]
-We then have a 2-isomorphism $\mu_{M,N} \maps E(M) \otimes E(N) \xrightarrow{\sim} E(M \otimes N)$ in $F\mathbb{C}\textnormal{sp}$ given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (-2.5,0) {$c_1+c_1^\prime$};
-\node (B) at (1,0) {$R(x)+R(x^\prime)$};
-\node (C) at (4.5,0) {$c_2+c_2^\prime$};
-\node (A') at (-2.5,-1) {$c_1+c_1^\prime$};
-\node (B') at (1,-1) {$R(x+x^\prime)$};
-\node (C') at (4.5,-1) {$c_2+c_2^\prime$};
-\node (D) at (6.55,0) {$d_{\mathbb{E}(M) \otimes \mathbb{E}(N)} \in F(R(x)+R(x^\prime))$};
-\node (D') at (6.55,-1) {$d_{\mathbb{E}(M \otimes N)} \in F(R(x+x^\prime))$};
+(A) edge node[above]{$R((i+i')\phi_{c_1,c_1'}^{-1}) \eta_{c_1+c_1'}$} (B)
+(C) edge node[above]{$R((o+o')\phi_{c_2,c_2'}^{-1}) \eta_{c_2+c_2'}$} (B);
+\end{tikzpicture}
+\]
+We then have a 2-isomorphism $\mu_{M,N} \maps E(M) \otimes E(N) \xrightarrow{\sim} E(M \otimes N)$ in $F\lCsp$ given by:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (-2.5,0) {$c_1+c_1'$};
+\node (B) at (1,0) {$R(x)+R(x')$};
+\node (C) at (4.5,0) {$c_2+c_2'$};
+\node (A') at (-2.5,-1) {$c_1+c_1'$};
+\node (B') at (1,-1) {$R(x+x')$};
+\node (C') at (4.5,-1) {$c_2+c_2'$};
+\node (D) at (6.55,0) {$d_{\mathbb{E}(M) \otimes \mathbb{E}(N)} \in F(R(x)+R(x'))$};
+\node (D') at (6.55,-1) {$d_{\mathbb{E}(M \otimes N)} \in F(R(x+x'))$};
 \node (E) at (2,-1.5) {$\tau_\mu \maps F(\kappa)(d_{\mathbb{E}(M) \odot \mathbb{E}(N)}) \to d_{\mathbb{E}(M \odot N)}$};
 \path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$R(i)\eta_{c_1} + R(i^\prime)\eta_{c_1^\prime}$} (B)
-(C) edge node[above]{$R(o)\eta_{c_2} + R(o^\prime)\eta_{c_2^\prime}$} (B)
-(A') edge node[above]{$R((i+i^\prime)\phi_{c_1,c_1'}^{-1}) \eta_{c_1+c_1^\prime}$} (B')
-(C') edge node[above]{$R((o+o^\prime)\phi_{c_2,c_2'}^{-1}) \eta_{c_2+c_2^\prime}$} (B')
+(A) edge node[above]{$R(i)\eta_{c_1} + R(i')\eta_{c_1'}$} (B)
+(C) edge node[above]{$R(o)\eta_{c_2} + R(o')\eta_{c_2'}$} (B)
+(A') edge node[above]{$R((i+i')\phi_{c_1,c_1'}^{-1}) \eta_{c_1+c_1'}$} (B')
+(C') edge node[above]{$R((o+o')\phi_{c_2,c_2'}^{-1}) \eta_{c_2+c_2'}$} (B')
 (A) edge node [left]{$1$} (A')
@@
 \begin{comment}
-To see this, let $M_1,M_2$ and $M_3$ be horizontal 1-cells in $_L \mathbb{C}\textnormal{sp}(\X)$ given by:
+To see this, let $M_1,M_2$ and $M_3$ be horizontal 1-cells in $_L \lCsp(\X)$ given by:
 \[
@@
 \node (B) at (1,0) {$x_1$};
-\node (C) at (2,0) {$L(c_1^\prime)$};
+\node (C) at (2,0) {$L(c_1')$};
 \node (D) at (3,0) {$L(c_2)$};
 \node (E) at (4,0) {$x_2$};
-\node (F) at (5,0) {$L(c_2^\prime)$};
+\node (F) at (5,0) {$L(c_2')$};
 \node (G) at (6,0) {$L(c_3)$};
 \node (H) at (7,0) {$x_3$};
-\node (I) at (8,0) {$L(c_3^\prime)$};
+\node (I) at (8,0) {$L(c_3')$};
 %\node (D) at (3,0.5) {$!_c \in F(c)$};
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$1_{F\mathbb{C}\textnormal{sp}} \otimes \mathbb{E}(M_1)$};
-\node (B) at (3,0) {$\mathbb{E}(1_{ _L \mathbb{C}\textnormal{sp}(\X)}) \otimes \mathbb{E}(M_1)$};
+\node (A) at (0,0) {$1_{F\lCsp} \otimes \mathbb{E}(M_1)$};
+\node (B) at (3,0) {$\mathbb{E}(1_{ _L \lCsp(\X)}) \otimes \mathbb{E}(M_1)$};
 \node (C) at (0,-1) {$\mathbb{E}(M_1)$};
-\node (D) at (3,-1) {$\mathbb{E}(1_{ _L \mathbb{C}\textnormal{sp}(\X)} \otimes M_1)$};
+\node (D) at (3,-1) {$\mathbb{E}(1_{ _L \lCsp(\X)} \otimes M_1)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 		\begin{tikzpicture}
-			\node (d) at (7.5,0) {$\mathbb{E}(1_{ _L \mathbb{C}\textnormal{sp}(\X)}) \otimes \mathbb{E}(M_1)$};
+			\node (d) at (7.5,0) {$\mathbb{E}(1_{ _L \lCsp(\X)}) \otimes \mathbb{E}(M_1)$};
 			\node (a) at (-6,0) {$1_\A+c_1$};
 			\node (b) at (-0.5,0) {$R(L(1_\A)) + R(x_1)$};
-			\node (c) at (5,0) {$1_\A+c_1^\prime$};
-			\node (d2) at (7.5,1) {$1_{F\mathbb{C}\textnormal{sp}} \otimes \mathbb{E}(M_1)$};
+			\node (c) at (5,0) {$1_\A+c_1'$};
+			\node (d2) at (7.5,1) {$1_{F\lCsp} \otimes \mathbb{E}(M_1)$};
 			\node (a2) at (-6,1) {$1_\A+c_1$};
 			\node (b2) at (-0.5,1) {$1_\A+R(x_1)$};
-			\node (c2) at (5,1) {$1_\A+c_1^\prime$};
+			\node (c2) at (5,1) {$1_\A+c_1'$};
 			\node (d3) at (7.5,2) {$\mathbb{E}(M_1)$};
@@
 			\node (b3) at (-0.5,2) {$R(x_1)$};
-			\node (c3) at (5,2) {$c_1^\prime$};
-			\node (d4) at (7.5,-1) {$\mathbb{E}(1_{ _L \mathbb{C}\textnormal{sp}(\X)} \otimes M_1)$};
-                                \node (a5) at (-6,-1) {$1_\A+c_1^\prime$};
+			\node (c3) at (5,2) {$c_1'$};
+			\node (d4) at (7.5,-1) {$\mathbb{E}(1_{ _L \lCsp(\X)} \otimes M_1)$};
+                                \node (a5) at (-6,-1) {$1_\A+c_1'$};
 			\node (b5) at (-0.5,-1) {$R(L(1_\A)+x_1)$};
-			\node (c5) at (5,-1) {$1_\A+c_1^\prime$};
+			\node (c5) at (5,-1) {$1_\A+c_1'$};
 			\node (d5) at (7.5,-2) {$\mathbb{E}(M_1)$};
@@
 			\node (b6) at (-0.5,-2) {$R(x_1)$};
-			\node (c6) at (5,-2) {$c_1^\prime$};
+			\node (c6) at (5,-2) {$c_1'$};
 			\path[->,font=\scriptsize,>=angle 90]
@@
 			(a) edge node[above]{$\eta_{1_\A}+R(i_1)\eta_{c_1}$} (b)
-			(c) edge node[above]{$\eta_{1_\A}+R(o_1)\eta_{c_1^\prime}$} (b)
+			(c) edge node[above]{$\eta_{1_\A}+R(o_1)\eta_{c_1'}$} (b)
                                 (a2) edge node[above]{$1+R(i_1)\eta_{c_1}$} (b2)
-			(c2) edge node[above]{$1+R(o_1)\eta_{c_1^\prime}$} (b2)
+			(c2) edge node[above]{$1+R(o_1)\eta_{c_1'}$} (b2)
                                 (a2) edge node[left]{$1$} (a)
@@
                                 (a3) edge node[above]{$R(i_1)\eta_{c_1}$} (b3)
-			(c3) edge node[above]{$R(o_1)\eta_{c_1^\prime}$} (b3)
+			(c3) edge node[above]{$R(o_1)\eta_{c_1'}$} (b3)
                                 (a2) edge node[left]{$\lambda_{\A}$} (a3)
@@
                                 (a5) edge node[above]{$(\mu_{L(1_\A),d_1})(\eta_{1_\A}+R(i_1)\eta_{c_1})$} (b5)
-			(c5) edge node[above]{$(\mu_{L(1_\A),d_1})(\eta_{1_\A}+R(o_1)\eta_{c_1^\prime})$} (b5)
+			(c5) edge node[above]{$(\mu_{L(1_\A),d_1})(\eta_{1_\A}+R(o_1)\eta_{c_1'})$} (b5)
                                 (a) edge node[left]{$1$} (a5)
@@
                                 (a6) edge node[above]{$R(i_1)\eta_{c_1}$} (b6)
-			(c6) edge node[above]{$R(o_1)\eta_{c_1^\prime}$} (b6)
+			(c6) edge node[above]{$R(o_1)\eta_{c_1'}$} (b6)
                                 (a5) edge node[left]{$\lambda_{\A}$} (a6)
@@
 (B') edge node[above]{$\mu_{M_1,M_2 \otimes M_3}$} (C')
-(A) edge node [left]{$a^\prime$} (A')
+(A) edge node [left]{$a'$} (A')
 (C) edge node [right]{$\mathbb{E}(a)$} (C');
@@
 			\node (b) at (2.5,0) {$(R(x_1)+R(x_2))+R(x_3)$};
-			\node (c) at (9.25,0) {$(c_1^\prime+c_2^\prime)+c_3^\prime$};
+			\node (c) at (9.25,0) {$(c_1'+c_2')+c_3'$};
 			\node (a2) at (-4.25,1) {$(c_1+c_2)+c_3$};
 			\node (b2) at (2.5,1) {$R(x_1+x_2)+R(x_3)$};
-			\node (c2) at (9.25,1) {$(c_1^\prime+c_2^\prime)+c_3^\prime$};
+			\node (c2) at (9.25,1) {$(c_1'+c_2')+c_3'$};
                                 \node (a3) at (-4.25,2) {$(c_1+c_2)+c_3$};
 			\node (b3) at (2.5,2) {$R((x_1+x_2)+x_3)$};
-			\node (c3) at (9.25,2) {$(c_1^\prime+c_2^\prime)+c_3^\prime$};
+			\node (c3) at (9.25,2) {$(c_1'+c_2')+c_3'$};
                                 \node (a4) at (-4.25,3) {$c_1+(c_2+c_3)$};
 			\node (b4) at (2.5,3) {$R(x_1+(x_2+x_3))$};
-			\node (c4) at (9.25,3) {$c_1^\prime + (c_2^\prime + c_3^\prime)$};
+			\node (c4) at (9.25,3) {$c_1' + (c_2' + c_3')$};
                                 \node (a5) at (-4.25,-1) {$c_1+(c_2+c_3)$};
 			\node (b5) at (2.5,-1) {$R(x_1)+(R(x_2)+R(x_3))$};
-			\node (c5) at (9.25,-1) {$c_1^\prime + (c_2^\prime + c_3^\prime)$};
+			\node (c5) at (9.25,-1) {$c_1' + (c_2' + c_3')$};
                                 \node (a6) at (-4.25,-2) {$c_1+(c_2+c_3)$};
 			\node (b6) at (2.5,-2) {$R(x_1)+R(x_2+x_3)$};
-			\node (c6) at (9.25,-2) {$c_1^\prime + (c_2^\prime + c_3^\prime)$};
+			\node (c6) at (9.25,-2) {$c_1' + (c_2' + c_3')$};
                                 \node (a7) at (-4.25,-3) {$c_1+(c_2+c_3)$};
 			\node (b7) at (2.5,-3) {$R(x_1+(x_2+x_3))$};
-			\node (c7) at (9.25,-3) {$c_1^\prime + (c_2^\prime + c_3^\prime)$};
+			\node (c7) at (9.25,-3) {$c_1' + (c_2' + c_3')$};
 			\path[->,font=\scriptsize,>=angle 90]
@@
 (d3) edge node[left] {$\mathbb{E}(a)$} (d4)
-(d) edge node[left] {$a^\prime$} (d5)
+(d) edge node[left] {$a'$} (d5)
 (d5) edge node[left] {$1 \otimes \mu_{M_2,M_3}$} (d6)
@@
 			(a) edge node[above]{$(R(i_1)\eta_{c_1}+R(i_2)\eta_{c_2})+R(i_3)\eta_{c_3}$} (b)
-			(c) edge node[above]{$(R(o_1)\eta_{c_1^\prime}+R(o_2)\eta_{c_2^\prime})+R(o_3)\eta_{c_3^\prime}$} (b)
+			(c) edge node[above]{$(R(o_1)\eta_{c_1'}+R(o_2)\eta_{c_2'})+R(o_3)\eta_{c_3'}$} (b)
                                 (a2) edge node[above]{$R(i_1+i_2)\eta_{c_1+c_2}+R(i_3)\eta_{c_3}$} (b2)
-			(c2) edge node[above]{$R(o_1+o_2)\eta_{c_1^\prime+c_2^\prime}+R(o_3)\eta_{c_3^\prime}$} (b2)
+			(c2) edge node[above]{$R(o_1+o_2)\eta_{c_1'+c_2'}+R(o_3)\eta_{c_3'}$} (b2)
                                 (a) edge node[left]{$1$} (a2)
@@
                                 (a3) edge node[above]{$R((i_1+i_2)+i_3)\eta_{(c_1+c_2)+c_3}$} (b3)
-			(c3) edge node[above]{$R((o_1+o_2)+o_3)\eta_{(c_1^\prime+c_2^\prime)+c_3^\prime}$} (b3)
+			(c3) edge node[above]{$R((o_1+o_2)+o_3)\eta_{(c_1'+c_2')+c_3'}$} (b3)
                                 (a2) edge node[left]{$1$} (a3)
@@
                                 (a4) edge node[above]{$R(i_1+(i_2+i_3))\eta_{c_1+(c_2+c_3)}$} (b4)
-			(c4) edge node[above]{$R(o_1+(o_2+o_3))\eta_{c_1^\prime+(c_2^\prime+c_3^\prime)}$} (b4)
+			(c4) edge node[above]{$R(o_1+(o_2+o_3))\eta_{c_1'+(c_2'+c_3')}$} (b4)
                                 (a3) edge node[left]{$a_\A$} (a4)
@@
                                 (a5) edge node[above]{$R(i_1)\eta_{c_1}+(R(i_2)\eta_{c_2}+R(i_3)\eta_{c_3})$} (b5)
-			(c5) edge node[above]{$R(o_1)\eta_{c_1^\prime}+(R(o_2)\eta_{c_2^\prime}+R(o_3)\eta_{c_3^\prime})$} (b5)
+			(c5) edge node[above]{$R(o_1)\eta_{c_1'}+(R(o_2)\eta_{c_2'}+R(o_3)\eta_{c_3'})$} (b5)
                                 (a) edge node[left]{$a_\A$} (a5)
@@
                                 (a6) edge node[above]{$R(i_1)\eta_{c_1}+R(i_2+i_3)\eta_{c_2+c_3}$} (b6)
-			(c6) edge node[above]{$R(o_1)\eta_{c_1^\prime}+R(o_2+o_3)\eta_{c_2^\prime+c_3^\prime}$} (b6)
+			(c6) edge node[above]{$R(o_1)\eta_{c_1'}+R(o_2+o_3)\eta_{c_2'+c_3'}$} (b6)
                                 (a5) edge node[left]{$1$} (a6)
@@
                                 (a7) edge node[above]{$R(i_1+(i_2+i_3))\eta_{c_1+(c_2+c_3)}$} (b7)
-			(c7) edge node[above]{$R(o_1+(o_2+o_3))\eta_{c_1^\prime+(c_2^\prime+c_3^\prime)}$} (b7)
+			(c7) edge node[above]{$R(o_1+(o_2+o_3))\eta_{c_1'+(c_2'+c_3')}$} (b7)
                                 (a6) edge node[left]{$1$} (a7)
@@
 \path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$\beta^\prime$} (B)
+(A) edge node[above]{$\beta'$} (B)
 (B) edge node[right]{$\mu_{M_2,M_1}$} (D)
@@
 			\node (b) at (0.5,0) {$R(x_1)+R(x_2)$};
-			\node (c) at (5,0) {$c_1^\prime+c_2^\prime$};
+			\node (c) at (5,0) {$c_1'+c_2'$};
 			\node (a2) at (-4,1) {$c_2+c_1$};
 			\node (b2) at (0.5,1) {$R(x_2)+R(x_1)$};
-			\node (c2) at (5,1) {$c_2^\prime+c_1^\prime$};
+			\node (c2) at (5,1) {$c_2'+c_1'$};
                                 \node (a3) at (-4,2) {$c_2+c_1$};
 			\node (b3) at (0.5,2) {$R(x_2+x_1)$};
-			\node (c3) at (5,2) {$c_2^\prime + c_1^\prime$};
+			\node (c3) at (5,2) {$c_2' + c_1'$};
                                 \node (a5) at (-4,-1) {$c_1+c_2$};
 			\node (b5) at (0.5,-1) {$R(x_1+x_2)$};
-			\node (c5) at (5,-1) {$c_1^\prime+c_2^\prime$};
+			\node (c5) at (5,-1) {$c_1'+c_2'$};
                                 \node (a6) at (-4,-2) {$c_2+c_1$};
 			\node (b6) at (0.5,-2) {$R(x_2+x_1)$};
-			\node (c6) at (5,-2) {$c_2^\prime + c_1^\prime$};
-			\path[->,font=\scriptsize,>=angle 90]
-(d) edge node[left]{$\beta^\prime$} (d2)
+			\node (c6) at (5,-2) {$c_2' + c_1'$};
+			\path[->,font=\scriptsize,>=angle 90]
+(d) edge node[left]{$\beta'$} (d2)
 (d2) edge node[left]{$\mu_{M_2,M_1}$}(d3)
@@
 			(a) edge node[above]{$R(i_1) \eta_{c_1} + R(i_2)\eta_{c_2}$} (b)
-			(c) edge node[above]{$R(o_1) \eta_{c_1^\prime} + R(o_2) \eta_{c_2^\prime}$} (b)
+			(c) edge node[above]{$R(o_1) \eta_{c_1'} + R(o_2) \eta_{c_2'}$} (b)
                                 (a2) edge node[above]{$R(i_2) \eta_{c_2} + R(i_1) \eta_{c_1}$} (b2)
-			(c2) edge node[above]{$R(o_2) \eta_{c_2^\prime} + R(o_1) \eta_{c_1^\prime}$} (b2)
+			(c2) edge node[above]{$R(o_2) \eta_{c_2'} + R(o_1) \eta_{c_1'}$} (b2)
                                 (a) edge node[left]{$\beta_\A$} (a2)
@@
                                 (a3) edge node[above]{$R(i_2+i_1)\eta_{c_2+c_1}$} (b3)
-			(c3) edge node[above]{$R(o_2+o_1)\eta_{c_2^\prime+c_1^\prime}$} (b3)
+			(c3) edge node[above]{$R(o_2+o_1)\eta_{c_2'+c_1'}$} (b3)
                                 (a2) edge node[left]{$1$} (a3)
@@
                                 (a5) edge node[above]{$R(i_1+i_2)\eta_{c_1+c_2}$} (b5)
-			(c5) edge node[above]{$R(o_1+o_2)\eta_{c_1^\prime+c_2^\prime}$} (b5)
+			(c5) edge node[above]{$R(o_1+o_2)\eta_{c_1'+c_2'}$} (b5)
                                 (a) edge node[left]{$1$} (a5)
@@
                                 (a6) edge node[above]{$R(i_2+i_1)\eta_{c_2+c_1}$} (b6)
-			(c6) edge node[above]{$R(o_2+o_1)\eta_{c_2^\prime+c_1^\prime}$} (b6)
+			(c6) edge node[above]{$R(o_2+o_1)\eta_{c_2'+c_1'}$} (b6)
                                 (a5) edge node[left]{$\beta_\A$} (a6)
@@
 The above square commutes because $$F((\kappa)(\beta_\A))(x_1+x_2) = F((R(\beta_\X))(\kappa))(x_1+x_2)$$ as the corresponding braiding square for the finite colimit preserving functor $R \maps (\X,1_\X,+) \to (\A,1_\A,+)$ commutes.
-Thus the double functor $\mathbb{E} \maps _L\mathbb{C}\textnormal{sp}(\X) \to F\mathbb{C}\textnormal{sp}$ is symmetric monoidal.
+Thus the double functor $\mathbb{E} \maps _L\lCsp(\X) \to F\lCsp$ is symmetric monoidal.
 \end{comment}
@@
 
-Using a result of Shulman \cite{Shul}, each of the isofibrant symmetric monoidal double categories $F\mathbb{C}\textnormal{sp}$ and $_L \mathbb{C}\textnormal{sp}(\mathrm{X})$ give rise to underlying symmetric monoidal bicategories, namely $F\mathbb{C}\textnormal{sp}$ induces a symmetric monoidal bicategory $F\mathbf{Csp} \mapseqq H(F\mathbb{C}\textnormal{sp})$ which has:
+Using a result of Shulman \cite{Shul}, each of the isofibrant symmetric monoidal double categories $F\lCsp$ and $_L \lCsp(\mathrm{X})$ give rise to underlying symmetric monoidal bicategories, namely $F\lCsp$ induces a symmetric monoidal bicategory $F\mathbf{Csp} \mapseqq H(F\lCsp)$ which has:
 \begin{enumerate}
 \item{objects as those of $\A$,}
-\item{morphisms as horizontal 1-cells of $F\mathbb{C}\textnormal{sp}$, and}
-\item{2-morphisms as globular 2-morphisms of $F\mathbb{C}\textnormal{sp}$.}
+\item{morphisms as horizontal 1-cells of $F\lCsp$, and}
+\item{2-morphisms as globular 2-morphisms of $F\lCsp$.}
 \end{enumerate} 
-Likewise, $_L \mathbb{C}\textnormal{sp}(\X)$ induces a symmetric monoidal bicategory $H( {_L \mathbb{C}\textnormal{sp}(\X)})$ which has:
+Likewise, $_L \lCsp(\X)$ induces a symmetric monoidal bicategory $H( {_L \lCsp(\X)})$ which has:
 \begin{enumerate}
 \item{objects as those of $\A$,}
-\item{morphisms as horizontal 1-cells of $_L \mathbb{C}\textnormal{sp}(\X)$, and}
-\item{2-morphisms as globular 2-morphisms of $_L \mathbb{C}\textnormal{sp}(\X)$.}
+\item{morphisms as horizontal 1-cells of $_L \lCsp(\X)$, and}
+\item{2-morphisms as globular 2-morphisms of $_L \lCsp(\X)$.}
 \end{enumerate}
@@
 \begin{cor}
-The bicategories $F\mathbf{Csp}$ and $H( {_L \mathbb{C}\textnormal{sp}(\X)})$ are biequivalent.
+The bicategories $F\mathbf{Csp}$ and $H( {_L \lCsp(\X)})$ are biequivalent.
 \end{cor}
@@
 \begin{comment}
-We can also define the part of the double equivalence $\mathbb{G} \maps F\mathbb{C}\textnormal{sp} \to {_L \mathbb{C} \textnormal{sp}(\X)}$ which goes in the other direction: again, the object component of this double functor will be $\mathbb{G}_0 = \id_{\A}$.
-
-Given a horizontal 1-cell $M$ of $F\mathbb{C}\textnormal{sp}$:
+We can also define the part of the double equivalence $\mathbb{G} \maps F\lCsp \to {_L \mathbb{C} \textnormal{sp}(\X)}$ which goes in the other direction: again, the object component of this double functor will be $\mathbb{G}_0 = \id_{\A}$.
+
+Given a horizontal 1-cell $M$ of $F\lCsp$:
 \[
@@
 \]
-the image $\mathbb{G}(M)$ is the horizontal 1-cell in $_L \mathbb{C}\textnormal{sp}(\X)$ given by:
+the image $\mathbb{G}(M)$ is the horizontal 1-cell in $_L \lCsp(\X)$ given by:
 \[
@@
 In other words, the trivial decoraction $!_{c}$ is initial in $F(c)$.
-Similarly, given a 2-morphism $(f,h,g,\tau) \maps M \to M^\prime$ of $F\mathbb{C}\textnormal{sp}$:
+Similarly, given a 2-morphism $(f,h,g,\tau) \maps M \to M'$ of $F\lCsp$:
 \[
@@
 \node (D) at (1,0.5) {$x \in F(c)$};
-\node (D') at (1,-1.5) {$x^\prime \in F(c^\prime)$};
+\node (D') at (1,-1.5) {$x' \in F(c')$};
 \node (A) at (0,0) {$c_1$};
@@
 \node (C) at (2,0) {$c_2$};
-\node (A') at (0,-1) {$c_1^\prime$};
-\node (B') at (1,-1) {$c^\prime$};
-\node (C') at (2,-1) {$c_2^\prime$};
+\node (A') at (0,-1) {$c_1'$};
+\node (B') at (1,-1) {$c'$};
+\node (C') at (2,-1) {$c_2'$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (C) edge node[above]{$O$} (B)
-(A') edge node[above]{$I^\prime$} (B')
-(C') edge node[above]{$O^\prime$} (B')
+(A') edge node[above]{$I'$} (B')
+(C') edge node[above]{$O'$} (B')
 (A) edge node [left]{$f$} (A')
@@
 \]
-$$\tau \maps F(h)(x) \to x^\prime$$
-the image $\mathbb{G}(f,h,g,\tau)$ in $_L \mathbb{C}\textnormal{sp}(\X)$ is given by the 2-morphism:
+$$\tau \maps F(h)(x) \to x'$$
+the image $\mathbb{G}(f,h,g,\tau)$ in $_L \lCsp(\X)$ is given by the 2-morphism:
 \[
@@
 \node (C) at (3,0) {$L(c_2)$};
-\node (A') at (0,-1) {$L(c_1^\prime)$};
-\node (B') at (1.5,-1) {$x^\prime$};
-\node (C') at (3,-1) {$L(c_2^\prime)$};
+\node (A') at (0,-1) {$L(c_1')$};
+\node (B') at (1.5,-1) {$x'$};
+\node (C') at (3,-1) {$L(c_2')$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (C) edge node[above]{$!_{c} L(O)$} (B)
-(A') edge node[above]{$!_{c^\prime} L(I^\prime)$} (B')
-(C') edge node[above]{$!_{c^\prime} L(O^\prime)$} (B')
+(A') edge node[above]{$!_{c'} L(I')$} (B')
+(C') edge node[above]{$!_{c'} L(O')$} (B')
 (A) edge node [left]{$L(f)$} (A')
@@
 \]
-where $\alpha \maps x \to x^\prime$ is the morphism in the Grothendieck construction of $F$ given by $\alpha = (h \maps c \to c^\prime, \tau \maps F(h)(x) \to x^\prime)$.
-
-Next, we exhibit natural isomorphisms $\eta \maps \id_{ _L \mathbb{C}\textnormal{sp}(\X)} \cong \mathbb{G} \mathbb{E}$ and $\epsilon \maps \mathbb{E} \mathbb{G} \cong \id_{F\mathbb{C}\textnormal{sp}}$.
+where $\alpha \maps x \to x'$ is the morphism in the Grothendieck construction of $F$ given by $\alpha = (h \maps c \to c', \tau \maps F(h)(x) \to x')$.
+
+Next, we exhibit natural isomorphisms $\eta \maps \id_{ _L \lCsp(\X)} \cong \mathbb{G} \mathbb{E}$ and $\epsilon \maps \mathbb{E} \mathbb{G} \cong \id_{F\lCsp}$.
 Specifically, these are double natural isomorphisms given by double transformations \cite{Shul2} $\eta$ and $\epsilon$ whose object and arrow components are natural isomorphisms.
@@
 
-On the other hand, given a horizontal 1-cell $N$ in $F\mathbb{C}\textnormal{sp}$:
+On the other hand, given a horizontal 1-cell $N$ in $F\lCsp$:
 \[
@@
 \]
-Then we have a 2-isomorphism $\epsilon_N \maps \mathbb{E} \mathbb{G} (N) \xrightarrow{\sim} N$ in $F\mathbb{C}\textnormal{sp}$ given by:
+Then we have a 2-isomorphism $\epsilon_N \maps \mathbb{E} \mathbb{G} (N) \xrightarrow{\sim} N$ in $F\lCsp$ given by:
 \[
@@
 The semantics of the activity at an open system's inputs and outputs is typically described in a category such as $\mathsf{LinRel}$ of finite dimensonal vector spaces and linear relations.
-Thus, in each case, black-boxing results in functors such as: $$\blacksquare_1 \maps \mathsf{Circ} \to \mathsf{LinRel}$$ $$\blacksquare_2 \maps \mathsf{Mark} \to \mathsf{LinRel}$$ $$\blacksquare_3 \maps \mathsf{Petri} \to \mathsf{LinRel}.$$ Each of these black-boxing functors also possess other convenient properties such as being symmetric monoidal.
+Thus, in each case, black-boxing results in functors such as: $$\blacksquare_1 \maps \mathsf{Circ} \to \mathsf{LinRel}$$ $$\blacksquare_2 \maps \mathsf{Mark} \to \mathsf{LinRel}$$ $$\blacksquare_3 \maps \Petri \to \mathsf{LinRel}.$$ Each of these black-boxing functors also possess other convenient properties such as being symmetric monoidal.
 The first two of these were first done using Fong's theory of decorated cospans and then extended by the first two authors using structured cospans.
@@
 Both $\mathsf{Set}$ and $\mathsf{Graph}$ are cocartesian monoidal and the functor $L \maps \mathsf{Set} \to \mathsf{Graph}$ is left adjoint to the forgetful functor $R \maps \mathsf{Graph} \to \mathsf{Set}$ which assigns to a graph $G$ its underlying set of vertices $U(G)$.
-Using structured cospans and appealing to Theorem \cref{SC}, we get a symmetric monoidal double category $_L \mathbb{C}\textnormal{sp}(\mathsf{Graph})$ which has:
+Using structured cospans and appealing to Theorem \cref{SC}, we get a symmetric monoidal double category $_L \lCsp(\mathsf{Graph})$ which has:
 \begin{enumerate}
@@
 Let $F \maps \mathsf{Set} \to \mathsf{Cat}$ be the symmetric lax monoidal pseudofunctor that assigns to a set $N$ the \emph{category} of all graph structures whose underlying set of vertices is $N$.
-Using Theorem \cref{DC}, we then obtain a symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$ which has:
+Using Theorem \cref{DC}, we then obtain a symmetric monoidal double category $F\lCsp$ which has:
 \begin{enumerate}
@@
 \end{enumerate}
-We thus have two symmetric monoidal double categories: $_L \mathbb{C}\textnormal{sp}(\mathsf{Graph})$ obtained from structured cospans and $F\mathbb{C}\textnormal{sp}$ obtained from decorated cospans.
-Both of these double categories have $\mathsf{Set}$ as their categories of objects, open graphs as horizontal 1-cells and maps of open graphs as 2-morphisms, and by Theorem \cref{Equiv}, we have an equivalence of symmetric monoidal double categories $$_L \mathbb{C}\textnormal{sp}(\mathsf{Graph}) \sim F\mathbb{C}\textnormal{sp}.$$
+We thus have two symmetric monoidal double categories: $_L \lCsp(\mathsf{Graph})$ obtained from structured cospans and $F\lCsp$ obtained from decorated cospans.
+Both of these double categories have $\mathsf{Set}$ as their categories of objects, open graphs as horizontal 1-cells and maps of open graphs as 2-morphisms, and by Theorem \cref{Equiv}, we have an equivalence of symmetric monoidal double categories $$_L \lCsp(\mathsf{Graph}) \sim F\lCsp.$$
 
@@
 
-Let $\mathsf{Graph}_k$ be the category whose objects are given by $k$-graphs and morphisms by morphisms of $k$-graphs, where a morphism of $k$-graphs is given by a pair of functions $f \maps E \to E^\prime$ and $g \maps V \to V^\prime$ between the edge sets and vertex sets, respectively, of two $k$-graphs that respect the source and target functions of each.
+Let $\mathsf{Graph}_k$ be the category whose objects are given by $k$-graphs and morphisms by morphisms of $k$-graphs, where a morphism of $k$-graphs is given by a pair of functions $f \maps E \to E'$ and $g \maps V \to V'$ between the edge sets and vertex sets, respectively, of two $k$-graphs that respect the source and target functions of each.
 In a previous work introducing structured cospans, the first two authors showed that the category $\mathsf{Graph}_k$ has finite colimits \cite{BC2}.
 We can then obtain a double category of open passive linear circuits by defining a left adjoint $L \maps \mathsf{Set} \to \mathsf{Graph}_k$ that assigns to a set $V$ the discrete passive linear circuit $L(V)$ given by passive linear circuit with $V$ as its set of vertices and no edges.
-The resulting symmetric monoidal double category $_L \mathbb{C}\textnormal{sp}(\mathsf{Graph}_k)$ has:
+The resulting symmetric monoidal double category $_L \lCsp(\mathsf{Graph}_k)$ has:
 \begin{enumerate}
@@
 (A) edge node[left]{$h$} (A')
-(C) edge node[left]{$h^\prime$} (C')
+(C) edge node[left]{$h'$} (C')
 (C') edge node [above] {$o_2$} (D)
@@
 \end{enumerate}
-We can also obtain a similar double category using decorated cospans: define a pseudofunctor $F \maps \mathsf{FinSet} \to \Cat$ that assigns to a finite set $V$ the category of all $k$-graph structures on the finite set $V$ and to a function $f \maps V \to V^\prime$ the corresponding functor $F(f) \maps F(V) \to F(V^\prime)$ between decoration categories.
+We can also obtain a similar double category using decorated cospans: define a pseudofunctor $F \maps \mathsf{FinSet} \to \Cat$ that assigns to a finite set $V$ the category of all $k$-graph structures on the finite set $V$ and to a function $f \maps V \to V'$ the corresponding functor $F(f) \maps F(V) \to F(V')$ between decoration categories.
 Both categories $\mathsf{FinSet}$ and $\Cat$ are symmetric monoidal and the pseudofunctor $F \maps \mathsf{FinSet} \to \Cat$ is symmetric lax monoidal, as given a $k$-graph structure on a finite set $V_1$ denoted by an element $K_1 \in F(V_1)$ and a $k$-graph structure on a finite set $V_2$ denoted by an element $K_2 \in F(V_2)$, we can consider the $k$-graph structures simultaneously as a single graph structure $\phi_{V_1,V_2}(K_1,K_2)$ on the finite set $V_1+V_2$.
@@
 \]
-Thus the pseudofunctor $F$ is symmetric lax monoidal and so by Theorem \cref{DC} we get a symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$ which has:
+Thus the pseudofunctor $F$ is symmetric lax monoidal and so by Theorem \cref{DC} we get a symmetric monoidal double category $F\lCsp$ which has:
 \begin{enumerate}
@@
 \end{enumerate}
-These two double categories $_L \mathbb{C}\textnormal{sp}(\mathsf{Graph}_k)$ and $F\mathbb{C}\textnormal{sp}$ are equivalent by Theorem \cref{Equiv}.
+These two double categories $_L \lCsp(\mathsf{Graph}_k)$ and $F\lCsp$ are equivalent by Theorem \cref{Equiv}.
 
@@
 This is done using a symmetric lax monoidal functor $F \maps \mathsf{FinSet} \to \mathsf{Set}$ which assigns to each finite set $N$ the (large) set of all Markov processes on $N$ as defined above.
-Viewing this functor $F$ as now a symmetric lax monoidal pseudofunctor $F \maps \mathsf{FinSet} \to \Cat$ that assigns to a finite set $N$ the \emph{category} $F(N)$ of all Markov processes on $N$, we then get by Theorem \cref{DC} a symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$ which has:
+Viewing this functor $F$ as now a symmetric lax monoidal pseudofunctor $F \maps \mathsf{FinSet} \to \Cat$ that assigns to a finite set $N$ the \emph{category} $F(N)$ of all Markov processes on $N$, we then get by Theorem \cref{DC} a symmetric monoidal double category $F\lCsp$ which has:
 \begin{enumerate}
@@
 (A) edge node[left]{$f$} (A')
-(C) edge node[left]{$f^\prime$} (C')
+(C) edge node[left]{$f'$} (C')
 (C') edge node [above] {$o_2$} (D)
@@
 \end{enumerate}
-A symmetric monoidal double category of open Markov processes can also be obtained using structured cospans by defining a functor $L \maps \mathsf{FinSet} \to \mathsf{Mark}$ which assigns to a finite set $N$ the discrete Markov process $L(N)$ with no edges and to a function $f \maps N \to N^\prime$ the induced map of discrete Markov processes.
+A symmetric monoidal double category of open Markov processes can also be obtained using structured cospans by defining a functor $L \maps \mathsf{FinSet} \to \mathsf{Mark}$ which assigns to a finite set $N$ the discrete Markov process $L(N)$ with no edges and to a function $f \maps N \to N'$ the induced map of discrete Markov processes.
 Both categories $\mathsf{FinSet}$ and $\mathsf{Mark}$ have finite colimits and the functor $L$ is left adjoint to the forgetful functor $R \maps \mathsf{Mark} \to \mathsf{FinSet}$ which maps a Markov process to its underlying finite set of states.
-By Theorem \cref{SC}, we get a symmetric monoidal double category $_L \mathbb{C}\textnormal{sp}(\mathsf{Mark})$ which has:
+By Theorem \cref{SC}, we get a symmetric monoidal double category $_L \lCsp(\mathsf{Mark})$ which has:
 \begin{enumerate}
@@
 \node (G) at (4,0) {$M$};
-\node (E') at (3,-1) {$L(N_1^\prime)$};
-\node (F') at (5,-1) {$L(N_2^\prime)$};
-\node (G') at (4,-1) {$M^\prime$};
+\node (E') at (3,-1) {$L(N_1')$};
+\node (F') at (5,-1) {$L(N_2')$};
+\node (G') at (4,-1) {$M'$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (E) edge node[above]{$I$} (G)
-(E') edge node[above]{$I^\prime$} (G')
-(F') edge node[above]{$O^\prime$} (G');
+(E') edge node[above]{$I'$} (G')
+(F') edge node[above]{$O'$} (G');
 \end{tikzpicture}
@@
 \end{enumerate}
-The two double categories $F\mathbb{C}\textnormal{sp}$ and $_L \mathbb{C} \textnormal{sp}(\mathsf{Mark})$ are equivalent by Theorem \cref{Equiv}.
+The two double categories $F\lCsp$ and $_L \mathbb{C} \textnormal{sp}(\mathsf{Mark})$ are equivalent by Theorem \cref{Equiv}.
 
@@
 Each set of species $S$ gives rise to a discrete Petri net $L(S)$ with $S$ as its set of species and no transitions.
-Master and the first author show the existence of a left adjoint $L \maps \mathsf{Set} \to \mathsf{Petri}$ where $\mathsf{Petri}$ is the category whose objects are Petri nets and whose `morphisms are morphisms of Petri nets'.
-They also show that $\mathsf{Petri}$ has finite colimits and thus using Theorem \cref{SC} obtain a symmetric monoidal double category $\mathbb{O}\mathbf{pen}(\mathrm{Petri})$ of open Petri nets which has:
+Master and the first author show the existence of a left adjoint $L \maps \mathsf{Set} \to \Petri$ where $\Petri$ is the category whose objects are Petri nets and whose `morphisms are morphisms of Petri nets'.
+They also show that $\Petri$ has finite colimits and thus using Theorem \cref{SC} obtain a symmetric monoidal double category $\lOpen(\Petri)$ of open Petri nets which has:
 \begin{enumerate}
@@
 \item{vertical 1-morphisms given by functions,}
-\item{horizontal 1-cells as open Petri nets which are given by cospans in $\mathsf{Petri}$ of the form:
+\item{horizontal 1-cells as open Petri nets which are given by cospans in $\Petri$ of the form:
 \[
@@
 and}
-\item{2-morphisms as maps of cospans in $\mathsf{Petri}$ of the form:
+\item{2-morphisms as maps of cospans in $\Petri$ of the form:
 \[
@@
 We can also obtain a similar double category using decorated cospans: define a pseudofunctor $F \maps \mathsf{Set} \to \Cat$ where given a set $s$, $F(s)$ is the category of all Petri net structures with $s$ as its set of species.
-This pseudofunctor $F$ is symmetric lax monoidal as both $(\mathsf{Set},+,\emptyset)$ and $(\Cat,\times,1)$ are symmetric monoidal and given Petri nets $P \in F(s)$ and $P^\prime \in F(s^\prime)$, we can place them side by side and consider them together as a single Petri net $P+P^\prime \in F(s+s^\prime)$ with set of species $s+s^\prime$, and thus we have natural transformations $\phi_{s,s^\prime} \maps F(s) \times F(s^\prime) \to F(s+s^\prime)$ for any two sets $s$ and $s^\prime$.
-The other structure morphism between monoidal units $\phi \maps 1_{\mathsf{Petri}} \to F(\emptyset)$ is defined by the unique morphism from the empty Petri net with the empty set forits set of species to the only possible Petri net on the empty set, which is also the empty Petri net.
+This pseudofunctor $F$ is symmetric lax monoidal as both $(\mathsf{Set},+,\emptyset)$ and $(\Cat,\times,1)$ are symmetric monoidal and given Petri nets $P \in F(s)$ and $P' \in F(s')$, we can place them side by side and consider them together as a single Petri net $P+P' \in F(s+s')$ with set of species $s+s'$, and thus we have natural transformations $\phi_{s,s'} \maps F(s) \times F(s') \to F(s+s')$ for any two sets $s$ and $s'$.
+The other structure morphism between monoidal units $\phi \maps 1_{\Petri} \to F(\emptyset)$ is defined by the unique morphism from the empty Petri net with the empty set forits set of species to the only possible Petri net on the empty set, which is also the empty Petri net.
 All of the diagrams that are required to commute are straightforward.
-Using Theorem \cref{DC}, we obtain a symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$ which has:
+Using Theorem \cref{DC}, we obtain a symmetric monoidal double category $F\lCsp$ which has:
 \begin{enumerate}
@@
 \end{enumerate}
-Thus we have a symmetric monoidal double category $\mathbb{O}\mathbf{pen}(\mathrm{Petri})$ of open Petri nets obtained from structured cospans and a symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$ of open Petri nets obtain from decorated cospans, and of course, we have an equivalence $\mathbb{O}\mathbf{pen}(\mathrm{Petri}) \sim F\mathbb{C}\textnormal{sp}$ of symmetric monoidal double categories by Theorem \cref{Equiv}.
+Thus we have a symmetric monoidal double category $\lOpen(\Petri)$ of open Petri nets obtained from structured cospans and a symmetric monoidal double category $F\lCsp$ of open Petri nets obtain from decorated cospans, and of course, we have an equivalence $\lOpen(\Petri) \sim F\lCsp$ of symmetric monoidal double categories by Theorem \cref{Equiv}.
 \end{comment}
@@
 %\path[->,font=\scriptsize,>=angle 90]
-%(A) edge node[above]{$a^\prime$} (A')
+%(A) edge node[above]{$a'$} (A')
 %(A) edge node[left]{$\psi 1_{\sigma_a}$} (B)
@@
 %(B) edge node[above]{$\sigma_{gf}$} (C')
-%(C) edge node [above] {${a^\prime}^{-1}$} (D)
+%(C) edge node [above] {${a'}^{-1}$} (D)
 %(D') edge node [above] {$1_{\sigma_c} \phi$} (C')
 %(D) edge node [above] {$\sigma_g 1_{F(f)}$} (F)
-%(F) edge node [right] {$a^\prime$} (D');
+%(F) edge node [right] {$a'$} (D');
 %\end{tikzpicture}
@@
 %(B) edge node[right]{$\sigma_{1_a}$} (C)
-%(A) edge node [left] {$\ell^\prime$} (D)
-%(D) edge node [above] {${\rho^\prime}^{-1}$} (E)
+%(A) edge node [left] {$\ell'$} (D)
+%(D) edge node [above] {${\rho'}^{-1}$} (E)
 %(E) edge node [right] {$1_{\sigma_a} \phi$} (C);
@@
 %Let $P \maps \ca{X} \to \ca{A}$ be a functor.
-A morphism $f \maps d_{1} \to d_{2}$ in the category $\mathrm{D}$ is \textbf{cocartesian (with respect to the functor P)} if for any object $d^\prime$ in $\mathrm{D}$ and morphism $g \maps d_{1} \to d^\prime$ and every $p \maps P(d_{2}) \to P(d^\prime)$ such that $P(g)=p P(f)$, there exists a unique $h \maps d_{2} \to d^\prime$ such that $g=hf$ and $p=P(h)$.
+A morphism $f \maps d_1 \to d_{2}$ in the category $\mathrm{D}$ is \textbf{cocartesian (with respect to the functor P)} if for any object $d'$ in $\mathrm{D}$ and morphism $g \maps d_1 \to d'$ and every $p \maps P(d_{2}) \to P(d')$ such that $P(g)=p P(f)$, there exists a unique $h \maps d_{2} \to d'$ such that $g=hf$ and $p=P(h)$.
 %\[
 %\begin{tikzpicture}[scale=1.5]
-%\node (A) at (0,0) {$d^\prime$};
+%\node (A) at (0,0) {$d'$};
 %\node (B) at (0,-1) {$d_{2}$};
-%\node (C) at (1.5,-1) {$d_{1}$};
+%\node (C) at (1.5,-1) {$d_1$};
 %\node (H) at (2,-0.25) {$P$};
 %\node (D) at (2,-.5) {$\mapsto$};
-%\node (E) at (3,0) {$P(d^\prime)$};
+%\node (E) at (3,0) {$P(d')$};
 %\node (F) at (3,-1) {$P(d_{2})$};
-%\node (G) at (4.5,-1) {$P(d_{1})$};
+%\node (G) at (4.5,-1) {$P(d_1)$};
 %\path[->,font=\scriptsize,>=angle 90]
@@
 %\begin{defn}
-%A functor $P \maps \mathrm{D} \to \mathrm{A}$ is a \textbf{(Grothendieck) opfibration} if for any object $d$ in $\mathbf{D}$ and morphism $f \maps c %\to P(d)$ there exists a cocartesian morphism $\phi \maps d^\prime \to d$ such that $P(\phi)=f$.
+%A functor $P \maps \mathrm{D} \to \mathrm{A}$ is a \textbf{(Grothendieck) opfibration} if for any object $d$ in $\mathbf{D}$ and morphism $f \maps c %\to P(d)$ there exists a cocartesian morphism $\phi \maps d' \to d$ such that $P(\phi)=f$.
 %\end{defn}
 %\begin{defn}
-%Let $P \maps \mathrm{D} \to \mathrm{A}$ and $P^\prime \maps \mathrm{D^\prime} \to \mathrm{A}$ be opfibrations over a category $\mathrm{A}$.
-A \define{morphism of opfibrations} is a functor $F \maps \mathrm{D} \to \mathrm{D}^\prime$ such that $F(p)$ is cocartesian with respect to $P^\prime$ if $p$ is cocartesian with respect to $P$ and $P=P^\prime F$.
+%Let $P \maps \mathrm{D} \to \mathrm{A}$ and $P' \maps \mathrm{D'} \to \mathrm{A}$ be opfibrations over a category $\mathrm{A}$.
+A \define{morphism of opfibrations} is a functor $F \maps \mathrm{D} \to \mathrm{D}'$ such that $F(p)$ is cocartesian with respect to $P'$ if $p$ is cocartesian with respect to $P$ and $P=P' F$.
 %\end{defn}
@@
 %\node (B) at (1,0.5) {$F(c)$};
-%\node (C) at (1,-0.5) {$F(c^\prime)$};
+%\node (C) at (1,-0.5) {$F(c')$};
 %\node (D) at (2,0.5) {$c$};
-%\node (E) at (2,-0.5) {$c^\prime$};
+%\node (E) at (2,-0.5) {$c'$};
 %\node (F) at (0.65,0) {$\Swarrow \alpha$};
@@
 %(B) edge node[right]{$F(f)$} (C)
-%(A) edge node[below]{$d^\prime$} (C)
+%(A) edge node[below]{$d'$} (C)
 %(D) edge node[left] {$f$} (E);
@@
 %Let $P \maps \mathbf{D} \to \mathrm{A}$ be a functor.
-A morphism $f \maps d_{1} \to d_{2}$ in the category $\mathbf{D}$ is \textbf{cartesian (with respect to the functor P)} if for any object $d^\prime$ in $\mathbf{D}$ and morphism $g \maps d^\prime \to d_{2}$ and every $p \maps P(d^\prime) \to P(d_{1})$ such that $P(g)=P(f)p$, there exists a unique $h \maps d^\prime \to d_{1}$ such that $g=fh$ and $p=P(h)$.
+A morphism $f \maps d_1 \to d_{2}$ in the category $\mathbf{D}$ is \textbf{cartesian (with respect to the functor P)} if for any object $d'$ in $\mathbf{D}$ and morphism $g \maps d' \to d_{2}$ and every $p \maps P(d') \to P(d_1)$ such that $P(g)=P(f)p$, there exists a unique $h \maps d' \to d_1$ such that $g=fh$ and $p=P(h)$.
 %\[
 %\begin{tikzpicture}[scale=1.5]
-%\node (A) at (0,0) {$d^\prime$};
-%\node (B) at (0,-1.5) {$d_{1}$};
+%\node (A) at (0,0) {$d'$};
+%\node (B) at (0,-1.5) {$d_1$};
 %\node (C) at (1.5,-1.5) {$d_{2}$};
@@
 %\node (D) at (2,-.75) {$\mapsto$};
-%\node (E) at (3,0) {$P(d^\prime)$};
-%\node (F) at (3,-1.5) {$P(d_{1})$};
+%\node (E) at (3,0) {$P(d')$};
+%\node (F) at (3,-1.5) {$P(d_1)$};
 %\node (G) at (4.5,-1.5) {$P(d_{2})$};
@@
 \begin{defn}\label{defn:double_category}
-A \textbf{pseudo double category} $\lD$, or $\textbf{double category}$ for short, consists of a category of objects $\mathbf{D_{0}}$ and a category of arrows $\mathbf{D_{1}}$ with the following functors
+A \textbf{pseudo double category} $\lD$, or $\textbf{double category}$ for short, consists of a category of objects $\mathbf{D_{0}}$ and a category of arrows $\mathbf{D_1}$ with the following functors
 \begin{center}
-$U\maps \mathbf{D_{0}} \to \mathbf{D_{1}}$\\
-$S,T \maps \mathbf{D_{1}} \rightrightarrows \mathbf{D_{0}}$\\
-$\odot \maps \mathbf{D_{1}} \times_{\mathbf{D_{0}}} \mathbf{D_{1}} \to \mathbf{D_{1}}$ (where the pullback is taken over $\mathbf{D_{1}} \xrightarrow[]{T} \mathbf{D_{0}} \xleftarrow[]{S} \mathbf{D_{1}}$) \\
+$U\maps \mathbf{D_{0}} \to \mathbf{D_1}$\\
+$S,T \maps \mathbf{D_1} \rightrightarrows \mathbf{D_{0}}$\\
+$\odot \maps \mathbf{D_1} \times_{\mathbf{D_{0}}} \mathbf{D_1} \to \mathbf{D_1}$ (where the pullback is taken over $\mathbf{D_1} \xrightarrow[]{T} \mathbf{D_{0}} \xleftarrow[]{S} \mathbf{D_1}$) \\
 \end{center}
@@
 Following the notation of Shulman, objects of $\mathbf{D_{0}}$ are called $\textbf{0-cells}$ and morphisms of $\mathbf{D_{0}}$ are called $\textbf{vertical 1-morphisms}$.
-Objects of $\mathbf{D_{1}}$ are called $\textbf{horizontal 1-cells}$ and morphisms of $\mathbf{D_{1}}$ are called $\textbf{2-morphisms}$.
+Objects of $\mathbf{D_1}$ are called $\textbf{horizontal 1-cells}$ and morphisms of $\mathbf{D_1}$ are called $\textbf{2-morphisms}$.
 The morphisms of $\mathbf{D_{0}}$, which are vertical 1-morphisms, will be denoted $f \maps A \to C$ and we denote a 1-cell $M$ with $S(M)=A,T(M)=B$ by $M \maps A \to B$.
-Then a 2-morphism $a \maps M \to N$ of $\mathbf{D_{1}}$ with $S(a)=f,T(a)=g$ would look like:
+Then a 2-morphism $a \maps M \to N$ of $\mathbf{D_1}$ with $S(a)=f,T(a)=g$ would look like:
 \[
@@
 
-Also, every object $a$ is equipped with a special globular 2-morphism $\phi_{a} \maps 1_{\mathbb{F}(a)} \to \mathbb{F}(1_{a})$ (the identity comparison), and every horizontal composition $N_{1} \odot N_{2}$ is equipped with a special globular 2-morphism $\phi(N_{1},N_{2}) \maps \mathbb{F}(N_{1}) \odot \mathbb{F}(N_{2}) \to \mathbb{F}(N_{1} \odot N_{2})$ (the composition comparison), in a coherent way.
+Also, every object $a$ is equipped with a special globular 2-morphism $\phi_{a} \maps 1_{\mathbb{F}(a)} \to \mathbb{F}(1_{a})$ (the identity comparison), and every horizontal composition $N_1 \odot N_{2}$ is equipped with a special globular 2-morphism $\phi(N_1,N_{2}) \maps \mathbb{F}(N_1) \odot \mathbb{F}(N_{2}) \to \mathbb{F}(N_1 \odot N_{2})$ (the composition comparison), in a coherent way.
 This means that the following diagrams commute.
@@
     \mathbb{F}(A) \ar[r]|{|}^{\mathbb{F}(N_{2})}  \ar[d] \ar@{}[dr]|{\mathbb{F}(\alpha)}&
-    \mathbb{F}(B) \ar[d] \ar[r]|{|}^{\mathbb{F}(N_{1})} \ar@{}[dr]|{\mathbb{F}(\beta)}&
+    \mathbb{F}(B) \ar[d] \ar[r]|{|}^{\mathbb{F}(N_1)} \ar@{}[dr]|{\mathbb{F}(\beta)}&
     \mathbb{F}(C) \ar[d] &
      &
-    \mathbb{F}(A) \ar[r]|{|}^{\mathbb{F}(N_{2})} \ar@{}[drr]|{\phi(N_{1},N_{2})} \ar[d]_{1} &
-    \mathbb{F}(B) \ar[r]|{|}^{\mathbb{F}(N_{1})} &
+    \mathbb{F}(A) \ar[r]|{|}^{\mathbb{F}(N_{2})} \ar@{}[drr]|{\phi(N_1,N_{2})} \ar[d]_1 &
+    \mathbb{F}(B) \ar[r]|{|}^{\mathbb{F}(N_1)} &
     \mathbb{F}(C) \ar[d]^{1} \\
-    \mathbb{F}(A') \ar[r]|{|}_{\mathbb{F}(N_{4})} \ar@{}[drr]|{\phi(N_{3},N_{4})} \ar[d]_{1}&
+    \mathbb{F}(A') \ar[r]|{|}_{\mathbb{F}(N_{4})} \ar@{}[drr]|{\phi(N_{3},N_{4})} \ar[d]_1&
     \mathbb{F}(B') \ar[r]|{|}_{\mathbb{F}(N_{3})} &
@@
     = &
-    \mathbb{F}(A) \ar[rr]|{|}^{\mathbb{F}(N_{1} \odot N_{2})} \ar[d] \ar@{}[drr]|{\mathbb{F}(\beta \odot \alpha)}&
+    \mathbb{F}(A) \ar[rr]|{|}^{\mathbb{F}(N_1 \odot N_{2})} \ar[d] \ar@{}[drr]|{\mathbb{F}(\beta \odot \alpha)}&
      &
@@
 
-\item For consecutive horizontal 1-cells $N_{1},N_{2}$ and $N_{3}$, the following diagram is commutative.
+\item For consecutive horizontal 1-cells $N_1,N_{2}$ and $N_{3}$, the following diagram is commutative.
 
  \[\xymatrix{
-    (\mathbb{F}(N_{1}) \odot \mathbb{F}(N_{2})) \odot \mathbb{F}(N_{3}) \ar[r]^{a'}\ar[d]_{\phi(N_{1},N_{2}) \odot 1}
-    & \mathbb{F}(N_{1}) \odot (\mathbb{F}(N_{2}) \odot \mathbb{F}(N_{3})) \ar[d]^{1 \odot \phi(N_{2},N_{3})}\\
-    \mathbb{F}(N_{1} \odot N_{2}) \odot \mathbb{F}(N_{3}) \ar[d]_{\phi(N_{1} \odot N_{2},N_{3})} &
-    \mathbb{F}(N_{1}) \odot \mathbb{F}(N_{2} \odot N_{3}) \ar[d]^{\phi(N_{1},N_{2} \odot N_{3})}\\
-    \mathbb{F}((N_{1} \odot N_{2}) \odot N_{3})\ar[r]^{\mathbb{F}a} &
-    \mathbb{F}(N_{1} \odot (N_{2} \odot N_{3}))}\]
+    (\mathbb{F}(N_1) \odot \mathbb{F}(N_{2})) \odot \mathbb{F}(N_{3}) \ar[r]^{a'}\ar[d]_{\phi(N_1,N_{2}) \odot 1}
+    & \mathbb{F}(N_1) \odot (\mathbb{F}(N_{2}) \odot \mathbb{F}(N_{3})) \ar[d]^{1 \odot \phi(N_{2},N_{3})}\\
+    \mathbb{F}(N_1 \odot N_{2}) \odot \mathbb{F}(N_{3}) \ar[d]_{\phi(N_1 \odot N_{2},N_{3})} &
+    \mathbb{F}(N_1) \odot \mathbb{F}(N_{2} \odot N_{3}) \ar[d]^{\phi(N_1,N_{2} \odot N_{3})}\\
+    \mathbb{F}((N_1 \odot N_{2}) \odot N_{3})\ar[r]^{\mathbb{F}a} &
+    \mathbb{F}(N_1 \odot (N_{2} \odot N_{3}))}\]
 \end{enumerate}
@@
 \begin{enumerate}
-\item $\mathbf{D_{0}}$ and $\mathbf{D_{1}}$ are both monoidal categories.
+\item $\mathbf{D_{0}}$ and $\mathbf{D_1}$ are both monoidal categories.
 \item If $I$ is the monoidal unit of $\mathbf{D_{0}}$, then $U_I$ is the
-  monoidal unit of $\mathbf{D_{1}}$.
+  monoidal unit of $\mathbf{D_1}$.
 \item The functors $S$ and $T$ are strict monoidal, i.e.\ $S(M\ten N)
@@
 		\setcounter{enumi}{\value{mondbl}}
-		\item $\dblcat{D}_{0}$ and $\dblcat{D}_{1}$ are braided monoidal categories.
+		\item $\dblcat{D}_{0}$ and $\dblcat{D}_1$ are braided monoidal categories.
 		\item The functors $S$ and $T$ are strict braided monoidal functors.
@@
 		\setcounter{enumi}{\value{mondbl}}
-		\item $\dblcat{D}_{0}$ and $\dblcat{D}_{1}$ are symmetric monoidal.
+		\item $\dblcat{D}_{0}$ and $\dblcat{D}_1$ are symmetric monoidal.
 	\end{enumerate}
@@
  \[\xymatrix{
-    (\mathbb{F}(A) \otimes \mathbb{F}(B)) \otimes \mathbb{F}(C) \ar[r]^{\alpha^\prime}\ar[d]_{\mu_{A,B} \otimes 1}
+    (\mathbb{F}(A) \otimes \mathbb{F}(B)) \otimes \mathbb{F}(C) \ar[r]^{\alpha'}\ar[d]_{\mu_{A,B} \otimes 1}
     & \mathbb{F}(A) \otimes (\mathbb{F}(B) \otimes \mathbb{F}(C)) \ar[d]^{1 \otimes \mu_{B,C}}\\
@@
 \]
-and for horizontal 1-cells $N_{1},N_{2}$ and $N_{3}$ of $\lC$,
+and for horizontal 1-cells $N_1,N_{2}$ and $N_{3}$ of $\lC$,
  \[\xymatrix{
-    (\mathbb{F}(N_{1}) \otimes \mathbb{F}(N_{2})) \otimes \mathbb{F}(N_{3}) \ar[r]^{\alpha^\prime}\ar[d]_{\nu_{N_{1},N_{2}} \otimes 1}
-    & \mathbb{F}(N_{1}) \otimes (\mathbb{F}(N_{2}) \otimes \mathbb{F}(N_{3})) \ar[d]^{1 \otimes \nu_{N_{2},N_{3}}}\\
-    \mathbb{F}(N_{1} \otimes N_{2}) \otimes \mathbb{F}(N_{3}) \ar[d]_{\nu_{N_{1} \otimes N_{2},N_{3}}} &
-    \mathbb{F}(N_{1}) \otimes \mathbb{F}(N_{2} \otimes N_{3}) \ar[d]^{\nu_{N_{1},N_{2} \otimes N_{3}}}\\
-    \mathbb{F}((N_{1} \otimes N_{2}) \otimes N_{3})\ar[r]^{\mathbb{F}\alpha} &
-    \mathbb{F}(N_{1} \otimes (N_{2} \otimes N_{3}))}\]
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,1) {$\mathbb{F}(N_{1}) \otimes U_{1_{\lD}}$};
-\node (C) at (3,1) {$\mathbb{F}(N_{1})$};
-\node (A') at (0,-1) {$\mathbb{F}(N_{1}) \otimes \mathbb{F}(U_{1_{\lC}})$};
-\node (C') at (3,-1) {$\mathbb{F}(N_{1} \otimes U_{1_{\lC}})$};
-\node (B) at (5,1) {$U_{1_{\lD}} \otimes \mathbb{F}(N_{1})$};
-\node (B') at (5,-1) {$\mathbb{F}(U_{1_{\lC}}) \otimes \mathbb{F}(N_{1})$};
-\node (D) at (8,1) {$\mathbb{F}(N_{1})$};
-\node (D') at (8,-1) {$\mathbb{F}(U_{1_{\lC}} \otimes N_{1})$};
+    (\mathbb{F}(N_1) \otimes \mathbb{F}(N_{2})) \otimes \mathbb{F}(N_{3}) \ar[r]^{\alpha'}\ar[d]_{\nu_{N_1,N_{2}} \otimes 1}
+    & \mathbb{F}(N_1) \otimes (\mathbb{F}(N_{2}) \otimes \mathbb{F}(N_{3})) \ar[d]^{1 \otimes \nu_{N_{2},N_{3}}}\\
+    \mathbb{F}(N_1 \otimes N_{2}) \otimes \mathbb{F}(N_{3}) \ar[d]_{\nu_{N_1 \otimes N_{2},N_{3}}} &
+    \mathbb{F}(N_1) \otimes \mathbb{F}(N_{2} \otimes N_{3}) \ar[d]^{\nu_{N_1,N_{2} \otimes N_{3}}}\\
+    \mathbb{F}((N_1 \otimes N_{2}) \otimes N_{3})\ar[r]^{\mathbb{F}\alpha} &
+    \mathbb{F}(N_1 \otimes (N_{2} \otimes N_{3}))}\]
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,1) {$\mathbb{F}(N_1) \otimes U_{1_{\lD}}$};
+\node (C) at (3,1) {$\mathbb{F}(N_1)$};
+\node (A') at (0,-1) {$\mathbb{F}(N_1) \otimes \mathbb{F}(U_{1_{\lC}})$};
+\node (C') at (3,-1) {$\mathbb{F}(N_1 \otimes U_{1_{\lC}})$};
+\node (B) at (5,1) {$U_{1_{\lD}} \otimes \mathbb{F}(N_1)$};
+\node (B') at (5,-1) {$\mathbb{F}(U_{1_{\lC}}) \otimes \mathbb{F}(N_1)$};
+\node (D) at (8,1) {$\mathbb{F}(N_1)$};
+\node (D') at (8,-1) {$\mathbb{F}(U_{1_{\lC}} \otimes N_1)$};
 \path[->,font=\scriptsize,>=angle 90]
 (A) edge node[left]{$1 \otimes \delta$} (A')
-(C') edge node[right]{$\mathbb{F}(r_{N_{1}})$} (C)
-(A) edge node[above]{$r_{\mathbb{F}(N_{1})}$} (C)
-(A') edge node[above]{$\nu_{N_{1},U_{1_{\lC}}}$} (C')
+(C') edge node[right]{$\mathbb{F}(r_{N_1})$} (C)
+(A) edge node[above]{$r_{\mathbb{F}(N_1)}$} (C)
+(A') edge node[above]{$\nu_{N_1,U_{1_{\lC}}}$} (C')
 (B) edge node[left]{$\delta \otimes 1$} (B')
-(B') edge node[above]{$\nu_{U_{1_{\lC}},N_{1}}$} (D')
-(B) edge node[above]{$\ell_{\mathbb{F}(N_{1})}$} (D)
-(D') edge node[right]{$\mathbb{F}(\ell_{N_{1}})$} (D);
+(B') edge node[above]{$\nu_{U_{1_{\lC}},N_1}$} (D')
+(B) edge node[above]{$\ell_{\mathbb{F}(N_1)}$} (D)
+(D') edge node[right]{$\mathbb{F}(\ell_{N_1})$} (D);
 \end{tikzpicture}

### 2020-11-11 cospans.tex
changed section title

@@
 
-\section{A symmetric monoidal double category of decorated cospans}\label{DecCospansDoubleCat}
+\section{Decorated cospans}\label{DecCospansDoubleCat}
 In this section we build the symmetric monoidal double category $F \mathbb{C}$sp mentioned in the introduction.

### 2020-11-12 cospans.tex
Polishing up Theorem 2.1

@@
 \section{Decorated cospans}\label{DecCospansDoubleCat}
-In this section we build the symmetric monoidal double category $F \mathbb{C}$sp mentioned in the introduction.
+In this section we build the symmetric monoidal double category $F \lCsp$ mentioned in the introduction.
 Then we obtain an underlying symmetric monoidal bicategory $F \mathbf{Csp}$ using a result of Shulman \cite{Shul} and finally decategorify this to obtain a symmetric monoidal category $F\mathsf{Csp}$ which is a generalization of Fong's original decorated cospan category \cite{Fong}.
@@
 \begin{thm}\label{thm:decoratedcospans}
-Let $\A$ be a category with finite colimits and $F \maps \A \to \Cat$ a lax monoidal pseudofunctor. Then there exists a double category $F\mathbb{C}$sp which has:
+Let $\A$ be a category with chosen finite colimits and $F \maps \A \to \Cat$ a lax monoidal pseudofunctor. Then there exists a double category $F\lCsp$ with:
 \begin{itemize}
-\item{objects as those of $\A$,}
-\item{vertical 1-morphisms as morphisms of $\A$,}
-\item{horizontal 1-cells as $F$-decorated cospans in $\A$ which are pairs
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a$};
+\item{objects of $\A$ as objects,}
+\item{morphisms of $\A$ as vertical 1-morphisms,}
+\item{$F$-decorated cospans as horizontal 1-cells, where an \define{$F$-decorated cospan} is a pair given by a cospan in $\A$ together with a decoration on the cospan's apex:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$(a$};
 \node (B) at (1,0) {$m$};
 \node (C) at (2,0) {$b,$};
-\node (D) at (3,0) {$x \in F(m)$};
+\node (D) at (2.6,0) {$x \in F(m))$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]}
-\item{2-morphisms as maps of $F$-decorated cospans in $\A$
+\item{maps of $F$-decorated cospans as 2-morphisms, where a \define{map of $F$-decorated cospans} is a pair given by a map of cospans in $\A$:
 \begin{equation}\label{eq:FCsp2morph}
@@
 \end{equation}
-together with a morphism $\tau \maps F(h)(m) \to m'$ in $F(m')$.}
+together with a \define{morphism of decorations} $\tau \maps F(h)(x) \to x'$ in $F(m')$.}
 \end{itemize}
@@
 \begin{proof}
-The unit structure functor $U \maps F\lCsp_0 \to F\lCsp_1$ is defined on objects as: 
+The definition of double category may be found in Definition \ref{defn:double_category}.
+To show that the pseudofunctor $F$ in the theorem statement induces a double category $F\lCsp$, we must first define the category of objects $F\lCsp_0$, the category of arrows $F\lCsp_1$, as well as the four structure functors which tie them together: the source and target functors $S,T \colon F\lCsp_1 \to F\lCsp_0$, the unit functor $U \colon F\lCsp_0 \to F\lCsp_1$ and the composition functor $\odot$ which says how to compose two composable horizontal 1-cells or two composable 2-morphisms horizontally: $$\odot \colon F\lCsp_1 \times_{F\lCsp_0} F\lCsp_1 \to F\lCsp_1.$$
+
+The category of objects $F\lCsp_0$ is simply the category $\A$.
+The category of arrows $F\lCsp_1$ has $F$-decorated cospans for objects and maps of $F$-decorated cospans as morphisms.
+Given two vertically composable $F$-decorated cospans:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0.5) {$a$};
+\node (A') at (0,-0.5) {$a'$};
+\node (B) at (1,0.5) {$m$};
+\node (C) at (2,0.5) {$b$};
+\node (C') at (2,-0.5) {$b'$};
+\node (D) at (1,-0.5) {$m'$};
+\node (E) at (3,0.5) {$x \in F(m)$};
+\node (F) at (3,-0.5) {$x' \in F(m')$};
+\node (G) at (1.5,-1) {$\tau \colon F(h)(x) \to x'$};
+\node (A'') at (0,-1.5) {$a$};
+\node (A''') at (0,-2.5) {$a'$};
+\node (B'') at (1,-1.5) {$m$};
+\node (C'') at (2,-1.5) {$b$};
+\node (C''') at (2,-2.5) {$b'$};
+\node (D'') at (1,-2.5) {$m'$};
+\node (E'') at (3,-1.5) {$x \in F(m)$};
+\node (F'') at (3,-2.5) {$x' \in F(m')$};
+\node (G'') at (1.5,-3) {$\tau' \colon F(h')(x') \to x''$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i$} (B)
+(C) edge node[above]{$o$} (B)
+(A) edge node[left]{$f$} (A')
+(C) edge node[right]{$g$} (C')
+(A') edge node[above] {$i'$} (D)
+(C') edge node[above] {$o'$} (D)
+(B) edge node [left] {$h$} (D)
+(A'') edge node[above]{$i'$} (B'')
+(C'') edge node[above]{$o'$} (B'')
+(A'') edge node[left]{$f'$} (A''')
+(C'') edge node[right]{$g'$} (C''')
+(A''') edge node[above] {$i''$} (D'')
+(C''') edge node[above] {$o''$} (D'')
+(B'') edge node [left] {$h'$} (D'');
+\end{tikzpicture}
+\]
+their composite is given by the composite of the two maps of cospans in $\A$
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0.5) {$a$};
+\node (A') at (0,-0.5) {$a''$};
+\node (B) at (1,0.5) {$m$};
+\node (C) at (2,0.5) {$b$};
+\node (C') at (2,-0.5) {$b''$};
+\node (D) at (1,-0.5) {$m''$};
+\node (E) at (3,0.5) {$x \in F(m)$};
+\node (F) at (3,-0.5) {$x'' \in F(m'')$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i$} (B)
+(C) edge node[above]{$o$} (B)
+(A) edge node[left]{$f'f$} (A')
+(C) edge node[right]{$g'g$} (C')
+(A') edge node[above] {$i''$} (D)
+(C') edge node[above] {$o''$} (D)
+(B) edge node [left] {$h'h$} (D);
+\end{tikzpicture}
+\]
+together with the composite morphism of decorations $\tau' \tau \colon F(h'h)(x) \to x'$ in $F(m'')$.
+This completes the descriptions of the category of objects $F\lCsp_0 = \A$ and the category of arrows $F\lCsp_1$.
+
+Next, we define the four structure functors $U,S,T$ and $\odot$. The unit functor $U \maps F\lCsp_0 \to F\lCsp_1$ is defined on objects as: 
 \[
@@
 \]
-where $!_a \in F(a)$ is the trivial decoration on $a$ given by the composite of the unique map $F(!) \maps F(0) \to F(a)$ and the morphism $\phi \maps 1 \to F(0)$  which comes from the structure of the lax monoidal pseudofunctor $F \maps \A \to \Cat$.
-For morphisms, the structure functor $U$ is defined as:
+where $!_a \in F(a)$ is the \define{trivial decoration} on $a$ given by the composite of the unique map $F(!) \maps F(0) \to F(a)$ and the morphism $\phi \maps 1 \to F(0)$  which comes from the structure of the lax monoidal pseudofunctor $F \maps \A \to \Cat$.
+For morphisms, the functor $U$ is defined as:
 \[
@@
 together with the morphism $\tau_{!_f} = F(f) F(!) \phi \maps 1 \to F(a')$.
-We also have source and target structure functors $S, T \maps F\lCsp_1 \to F\lCsp_0$ where the source of the horizontal 1-cell
+For the source and target functors $S, T \maps F\lCsp_1 \to F\lCsp_0$, given an object $F\lCsp_1$, which is an $F$-decorated cospan,
 \[
@@
 \]
-is the object $a$ in $\A$ and the source of the 2-morphism
+the source is the object $a$ and the target is the object $b$. Given a morphism of $F\lCsp_1$, which is a map of $F$-decorated cospans,
 \[
@@
 $$\tau \maps F(h)(m) \to m'$$
-is the source of the underlying map of cospans in $\A$, namely the morphism $f$ in $\A$; the target structure functor is defined similarly.
-These structure functors satisfy the equations $$SU(a)=\id_a=TU(a)$$for all objects $a$ of $\A$.
-
-Given two composable horizontal 1-cells $M$ and $N$:
+the source is the morphism $f$ and the target is the morphism $g$. The three functors $S,T$ and $U$ satisfy the equations $SU=\id_{\A}=TU$.
+
+Next we define the composite functor $\odot \colon F\lCsp_1 \times_{F\lCsp_0} F\lCsp_1 \to F\lCsp_1$, which amounts to defining how we compose two composable $F$-decorated cospans or two maps of $F$-decorated cospans with a common source and target.
+Given two composable $F$-decorated cospans which we respectively denote by $M$ and $N$, the capitals of their apices:
 \[
@@
 \]
-the composite $N \odot M$ is given by:
+the composite $M \odot N$ is given by taking the pushout of the two cospans in $\A$ over the shared foot which is the object $b$:
 \begin{equation}\label{eq:dcospanscomposition}
@@
 \end{equation}
-with the corresponding decoration of the apex $x \odot y \in F(m+_{b} n)$ given by:
-$$1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{x \times y} F(m) \times F(n) \xrightarrow{\phi_{m,n}} F(m+n) \xrightarrow{F(\psi)} F(m+_{b}n)$$
+The composite decoration $x \odot y$ on the apex $m+_b n$ is given by:
+$$x \odot y = 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{x \times y} F(m) \times F(n) \xrightarrow{\phi_{m,n}} F(m+n) \xrightarrow{F(\psi)} F(m+_{b}n)$$
 where $\psi \maps m + n \to m+_{b} n$ is the natural map from the coproduct to the pushout and $\phi_{m,n} \maps F(m) \times F(n) \to F(m+n)$ is the natural transformation coming from the structure of the lax monoidal pseudofunctor $F \maps \A \to \Cat$.
-Denoting the first and second of these horizontal 1-cells as $M$ and $N$, respectively, the source and target structure functors satisfy the equations $S(N \odot M)=S(M)$ and $T(N \odot M)=T(N)$.
+It is clear that the equations $S(M \odot N)=S(M)$ and $T(M \odot N)=T(N)$ hold.
+Given two horizontally composable maps of $F$-decorated cospans which we respectively denote by $\alpha$ and $\beta$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0.5) {$a$};
+\node (A') at (0,-0.5) {$a'$};
+\node (B) at (1,0.5) {$m$};
+\node (C) at (2,0.5) {$b$};
+\node (C') at (2,-0.5) {$b'$};
+\node (D) at (1,-0.5) {$m'$};
+\node (E) at (3,0.5) {$x \in F(m)$};
+\node (F) at (3,-0.5) {$x' \in F(m')$};
+\node (G) at (4,0.5) {$b$};
+\node (H) at (5,0.5) {$n$};
+\node (I) at (6,0.5) {$c$};
+\node (G') at (4,-0.5) {$b'$};
+\node (H') at (5,-0.5) {$n'$};
+\node (I') at (6,-0.5) {$c'$};
+\node (J) at (7,0.5) {$y \in F(n)$};
+\node (K) at (7,-0.5) {$y' \in F(n')$};
+\node (L) at (1,-1) {$\tau_\alpha \maps F(h_1)(x) \to x'$};
+\node (M) at (5,-1) {$\tau_\beta \maps F(h_2)(y) \to y'$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i_1$} (B)
+(C) edge node[above]{$o_1$} (B)
+(A) edge node[left]{$f$} (A')
+(C) edge node[right]{$g$} (C')
+(A') edge node[above] {$i_1'$} (D)
+(C') edge node[above] {$o_1'$} (D)
+(B) edge node [left] {$h_1$} (D)
+(G) edge node [above] {$i_2$} (H)
+(G) edge node [left] {$g$} (G')
+(H) edge node [left] {$h_2$} (H')
+(G') edge node [above] {$i_2'$} (H')
+(I) edge node [above] {$o_2$} (H)
+(I) edge node [right] {$k$} (I')
+(I') edge node [above] {$o_2'$} (H');
+\end{tikzpicture}
+\]
+\textbf{In progress...}
 

### 2020-11-13 cospans.tex
small improvements

@@
 \]
-We might hope to do this using symmetric lax monoidal functor $F \maps (\Fin\Set, +) \to (\Set, \times)$ assiging to each finite set $m$ the set of all graphs with $m$ as their set of nodes    But this hope is doomed, for reasons painstakingly explained in \cite[Sec.\ 5]{BC}.
+We might hope to do this using symmetric lax monoidal functor $F \maps (\Fin\Set, +) \to (\Set, \times)$ assigning to each finite set $m$ the set of all graphs with $m$ as their set of nodes    But this hope is doomed, for reasons painstakingly explained in \cite[Sec.\ 5]{BC}.
 There is really a \emph{category} of graphs with $m$ as their set of nodes, and trying to treat it as a mere set does not work.
@@
 
-%!!!John: So one thing we should do is give a little explanation of (the new) decorated cospans, introducing vocabulary.
-And another thing we should do is give a little explanation of double categories, mainly to introduce vocabulary and symbols.
-I bet there's a lot of this in the appendix but still we should try to be nice to our readers.
-
 \begin{thm}\label{thm:decoratedcospans}
-Let $\A$ be a category with chosen finite colimits and $F \maps \A \to \Cat$ a lax monoidal pseudofunctor. Then there exists a double category $F\lCsp$ with:
+Let $\A$ be a category with chosen finite colimits and $F \maps \A \to \Cat$ a lax monoidal pseudofunctor. Then there exists a double category $F\lCsp$ in which
 \begin{itemize}
-\item{objects of $\A$ as objects,}
-\item{morphisms of $\A$ as vertical 1-morphisms,}
-\item{$F$-decorated cospans as horizontal 1-cells, where an \define{$F$-decorated cospan} is a pair given by a cospan in $\A$ together with a decoration on the cospan's apex:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$(a$};
+\item an object is an object of $\A$,
+\item a vertical morphism is a morphism of $\A$,
+\item a horizontal 1-cell is an \define{$F$-decorated cospan}: that is, 
+a cospan in $\A$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$a$};
 \node (B) at (1,0) {$m$};
 \node (C) at (2,0) {$b,$};
-\node (D) at (2.6,0) {$x \in F(m))$};
+%\node (D) at (2.6,0) {$x \in F(m))$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \end{tikzpicture}
-\]}
-\item{maps of $F$-decorated cospans as 2-morphisms, where a \define{map of $F$-decorated cospans} is a pair given by a map of cospans in $\A$:
+\]
+together with a \define{decoration} $x \in F(m)$,
+\item a 2-morphism is a \define{map of $F$-decorated cospans}: that is, 
+a map of cospans in $\A$:
 \begin{equation}\label{eq:FCsp2morph}
@@
 \end{equation}
-together with a \define{morphism of decorations} $\tau \maps F(h)(x) \to x'$ in $F(m')$.}
+together with a \define{morphism of decorations} $\tau \maps F(h)(x) \to x'$ in $F(m')$.
 \end{itemize}
 \end{thm}
-%!!!Kenny: We should try to make this theorem shorter. 
-%!!!Christina: I agree!
-%!!!Kenny: On second thought, I'm not sure what we can cut out of this theorem. We're already saying "the standard monoidal category diagrams are satisfied" rather than displaying them.
-%!!!Christina: I think the proof can be simplified and made shorter in general, combined with John's comment that the reader should be eased in the terminology we use here like `unit structure functor', which could also be simplified to not using such notation, just describing for example the horizontal unit 1-cell and unit 2-cell.
-Kenny, would you like to give it a try?
-Or should I or John?
+
 \begin{proof}
@@
 \]
-together with the composite morphism of decorations $\tau' \tau \colon F(h'h)(x) \to x'$ in $F(m'')$.
+together with the composite morphism of decorations $\tau' F(\tau) \colon F(h'h)(x) \to x'$ in $F(m'')$.
+% this was:
+% together with the composite morphism of decorations $\tau' \tau \colon F(h'h)(x) \to x'$ in $F(m'')$
  This completes the descriptions of the category of objects $F\lCsp_0 = \A$ and the category of arrows $F\lCsp_1$.
@@
 \]
-where $!_a \in F(a)$ is the \define{trivial decoration} on $a$ given by the composite of the unique map $F(!) \maps F(0) \to F(a)$ and the morphism $\phi \maps 1 \to F(0)$  which comes from the structure of the lax monoidal pseudofunctor $F \maps \A \to \Cat$.
+where $!_a \in F(a)$ is the \define{trivial decoration} on $a$ given by the composite of the unique map $F(!) \maps F(0) \to F(a)$ and the morphism $\phi \maps 1 \to F(0)$  which comes from $F \maps \A \to \Cat$ being lax monoidal.
 For morphisms, the functor $U$ is defined as:
@@
 
-\section{An equivalence of symmetric monoidal double categories} \label{EquivDoubleCats}
+\section{Structured versus decorated cospans} \label{EquivDoubleCats}
 %\begin{comment}
@@
 \begin{gather}
-\textrm{lax monoidal pseudofunctors }F\maps(\A,+,0)\to(\bicat{Cat},\times,1) \notag\\
+\textrm{lax monoidal pseudofunctors }F\maps(\A,+,0)\to(\bicat{Cat},\times) \notag\\
 \Updownarrow \notag\\
-\textrm{monoidal opfibrations }U\maps(\X,\otimes,I)\to(\A,+,0) \label{monGroth}\\
+\textrm{monoidal opfibrations }U\maps(\X,\otimes)\to(\A,+) \label{monGroth}\\
 \Updownarrow \notag\\
@@
 4.8]{MV}.
-In that case, the monoidal opfibration clauses for $U\maps(\X,+,0)\to(\A,+,0)$ translate to the functor (strictly) preserving coproducts and the initial object, and bijectively correspond to pseudofunctors $F\maps\A\to\Rex $ into the 2-category of esian categories, functors that preserve coproducts and initial objects and natural transformations.
+In that case, the monoidal opfibration clauses for $U\maps(\X,+)\to(\A,+)$ translate to the functor (strictly) preserving coproducts and the initial object, and bijectively correspond to pseudofunctors $F\maps\A\to\Rex $ into the 2-category of esian categories, functors that preserve coproducts and initial objects and natural transformations.
 
@@
 \begin{proof}[Proof of \cref{Equiv}]
-Recall that the double category of decorated cospans $\dcsp{F}$ has objects and vertical 1-morphisms those of $\A$, horizontal 1-cells $a\tickar b$ are cospans $\cspn{a}{m}{b}{}{}$ in $\A$ along with $x\in F(m)$, and 2-morphisms are cospan maps $k\maps m\to m'$ together with a morphism $(Fk)(x)\to x'$, see \cref{eq:FCsp2morph}.
-
-By \cref{cor:fcocMonGroth}, when $F$ as an ordinary pseudofunctor factors through $\bicat{Rex}$, the (monoidal) Gro\-the\-ndieck construction gives rise to a finitely cocomplete $\inta F$ such that the corresponding opfibration $U_F\maps(\inta{F},+,0)\to(\A,+,0)$ preserves all finite colimits.
+Recall from \cref{thm:decoratedcospans} that the double category of decorated cospans $\dcsp{F}$ has objects and vertical 1-morphisms as in $\A$, while a horizontal 1-cell $a\tickar b$ is cospan $\cspn{a}{m}{b}{}{}$ in $\A$ decorated by an object $x\in F(m)$ and a 2-morphism is a map $k\maps m\to m'$ together with a morphism $(Fk)(x)\to x'$.
+
+By \cref{cor:fcocMonGroth}, when $F$ as an ordinary pseudofunctor factors through $\bicat{Rex}$, the (monoidal) Gro\-the\-ndieck construction gives rise to a finitely cocomplete $\inta F$ such that the corresponding opfibration $U_F\maps(\inta{F},+)\to(\A,+)$ preserves all finite colimits.
 %Christina: maybe the cocartesian structures are redundant to write here, since U_F really preserves all finite colimits anyways.

### 2020-11-13 cospans.tex
tiny
having a math symbol inside slash define created a problem for my compilere - if we want it to be bold we should use mathbf

@@
 %{\chris Amend at the end}
-%The outline for the paper is as follows: In Section \cref{DecCospansDoubleCat}, we construct the symmetric monoidal double category $F\lCsp$, obtain the underlying symmetric monoidal bicategory $F \mathbf{Csp}$ via a result of Shulman, and decategorify this symmetric monoidal bicategory to obtain the symmetric monoidal category $F$Csp.
-In Section \cref{MapsDecCospansDoubleCat} we define maps between decorated cospan double categories which are double functors of an appropriate type.
-In Section \cref{some other section} we investigate when a symmetric lax monoidal pseudofunctor gives rise to a left adjoint via the Grothendieck construction, which naturally leads to another compositional framework known as `Structured cospans'.
-In Section \cref{EquivDoubleCats} we briefly review the framework Structured cospans and prove that the double categorical versions of decorated cospans and structured cospans are equivalent when both are appropriate.
-Finally, in Section \cref{Applications}, we present a few examples that can be realized with either framework and discuss the realized equivalences.
+%The outline for the paper is as follows: In \cref{DecCospansDoubleCat}, we construct the symmetric monoidal double category $F\lCsp$, obtain the underlying symmetric monoidal bicategory $F \mathbf{Csp}$ via a result of Shulman, and decategorify this symmetric monoidal bicategory to obtain the symmetric monoidal category $F$Csp.
+In \cref{MapsDecCospansDoubleCat} we define maps between decorated cospan double categories which are double functors of an appropriate type.
+In \cref{some other section} we investigate when a symmetric lax monoidal pseudofunctor gives rise to a left adjoint via the Grothendieck construction, which naturally leads to another compositional framework known as `Structured cospans'.
+In \cref{EquivDoubleCats} we briefly review the framework Structured cospans and prove that the double categorical versions of decorated cospans and structured cospans are equivalent when both are appropriate.
+Finally, in \cref{Applications}, we present a few examples that can be realized with either framework and discuss the realized equivalences.
 
@@
 \item a vertical morphism is a morphism of $\A$,
-\item a horizontal 1-cell is an \define{$F$-decorated cospan}: that is, 
+\item a horizontal 1-cell is an $F$\define{-decorated cospan}: that is, 
 a cospan in $\A$:
@@
 together with a \define{decoration} $x \in F(m)$,
-\item a 2-morphism is a \define{map of $F$-decorated cospans}: that is, 
+\item a 2-morphism is a \define{map of} $F$\define{-decorated cospans}: that is, 
 a map of cospans in $\A$:

### 2020-11-13 cospans.tex
started working through chapter 3

@@
 In this section we build the symmetric monoidal double category $F \lCsp$ mentioned in the introduction.
-Then we obtain an underlying symmetric monoidal bicategory $F \mathbf{Csp}$ using a result of Shulman \cite{Shul} and finally decategorify this to obtain a symmetric monoidal category $F\mathsf{Csp}$ which is a generalization of Fong's original decorated cospan category \cite{Fong}.
+Then we obtain an underlying symmetric monoidal bicategory $F \mathbf{Csp}$ using a result of Shulman \cite{Shul}
+%!!!Christina: John suggested we might move all the horizontal bicategory and decategorified 1-category results together somewhere later/in the end.
+and finally decategorify this to obtain a symmetric monoidal category $F\mathsf{Csp}$ which is a generalization of Fong's original decorated cospan category \cite{Fong}.
 The definition of a lax monoidal pseudofunctor is recalled in \cref{sec:2cats}, and the basics of double categories are recalled in \cref{sec:doublecats}.
@@
 \section{Structured versus decorated cospans} \label{EquivDoubleCats}
-%\begin{comment}
-
-In \cite{BC2}, the first two authors introduces the symmetric monoidal double category of \emph{structured cospans} as a formalism to capture open networks.
+
+In \cite{BC2}, the first two authors introduce the symmetric monoidal double category of \emph{structured cospans} as a formalism to capture open networks.
 One of the main goals of this paper is to provide a monoidal double equivalence between this double category and that of \emph{decorated cospans}, described in detail in \cref{DecCospansDoubleCat}.
-Below we recall the double category structured cospans form.
+We first recall the double category structured cospans form.
 
 \begin{thm}\label{SC}
-Given a category $\X$ with finite colimits and a category $\A$ with finite coproducts and a finite coproduct preserving functor $L \maps \A \to \X$ with $\A$ and $\X$, there exists a symmetric monoidal double category $_L \lCsp(\X)$ which has:
+Given categories $\X$ and $\A$ with finite colimits and $L \maps \A \to \X$ a finitely cocontinuous functor, there exists a symmetric monoidal double category $_L\lCsp(\X)$ in which
 \begin{itemize}
-\item{objects given by objects of $\A$,}
-\item{vertical 1-morphisms given by morphisms of $\A$,}
-\item{horizontal 1-cells $a\tickar b$ given by cospans of $\X$ of the form:
+\item an object is an object of $\A$,
+\item a vertical morphism is a morphism of $\A$,
+\item a horizontal 1-cell $a\tickar b$ is a cospan in $\X$ of the form
 \begin{equation}\label{eq:structuredcospan}
@@
 \end{tikzpicture}
-\end{equation}}
-\item 2-morphisms given by maps of cospans of $\X$ of the form:
+\end{equation}
+\item a 2-morphism is a map of cospans of $\X$ of the form
 \begin{equation}\label{eq:2cellsStrCsp}
@@
 \end{itemize}
-Composition of horizontal 1-cells and 2-morphisms is given by pushouts in $\X$ and tensoring of objects is under binary coproducts in $\A$.
+The symmetric monoidal structure is formed by using binary coproducts and the initial object.
 \end{thm}
+
 \begin{proof}
-See the first two authors' work on structured cospans \cite{BC2}.
+All relevant details can be found in \cite[Thm.~2.3\&3.9]{BC2}.
+In particular, the double category structure only requires that $\X$ have pushouts, since this is how composition is formed.
+Moreover, the symmetric monoidal structure requires that $\X$ also have binary coproducts and an initial object (thus all finite colimits), and that $\A$ have and $L$ preserve finite coproducts, see \cite[Thm.~3.2.3]{CourserThesis}.
 \end{proof}

### 2020-11-13 cospans.tex
small edits

@@
 \end{equation}
-\item a 2-morphism is a map of cospans of $\X$ of the form
+\item a 2-morphism is a map of cospans in $\X$ of the form
 \begin{equation}\label{eq:2cellsStrCsp}
@@
 
-The desired equivalence between these two different double categorical network frameworks, namely structured cospans and decorated cospans,
-is established by the following theorem. We denote by $\bicat{Rex}$ the 2-category of finitely cocomplete categories and finitely cocontinuous functors.
+The following theorem establishes the desired equivalence between these two different double categorical network frameworks of structured and decorated cospans in a formal way.
+We denote by $\bicat{Rex}$ the 2-category of finitely cocomplete categories and finitely cocontinuous functors, and the symmetric monoidal double structure of decorated cospans is worked out in \cref{thm:decoratedcospans,DC}.
 
 \begin{thm}\label{Equiv}
-Suppose $\ca{A}$ is a finitely cocomplete category and $(F,\phi,\phi_0)\maps(\ca{A},+,0) \to (\bicat{Cat},\times,\mathbf{1})$ is a symmetric lax monoidal pseudofunctor that factors through $\bicat{Rex}$ as an ordinary pseudofunctor.
-Then the symmetric monoidal double category $F\lCsp$ of decorated cospans given in \cref{thm:decoratedcospans} is equivalent to the symmetric monoidal double category $\scsp{L_F}{\inta F}$ of structured cospans given in \cref{SC}, where $L_F \maps \A \to \inta{F}$ is the left adjoint of the induced Grothendieck opfibration $\U_F\maps \inta{F} \to \A$.
-%by \cref{thm:Grothendieck},
-%under the assumptions of \cref{cor:fcocMonGroth}.
+Suppose $\ca{A}$ has finite colimits and $(F,\phi,\phi_0)\maps(\ca{A},+,0) \to (\bicat{Cat},\times,\mathbf{1})$ is a symmetric lax monoidal pseudofunctor that factors through $\bicat{Rex}$ as an ordinary pseudofunctor.
+Then the symmetric monoidal double category $F\lCsp$ of decorated cospans is equivalent to the symmetric monoidal double category $_L\lCsp(\inta F)$ of structured cospans, where $L \maps \A \to \inta F$ is the left adjoint of the induced Grothendieck opfibration $\U\maps \inta F \to \A$.
 \end{thm}
@@
 The conditions of the above theorem relate to the existence of left adjoints for opfibrations; we first sketch this underlying framework, and then we proceed to the proof of the theorem.
-
 The basics of fibration theory needed for our purposes are recalled in \cref{sec:fibrations}.
-In \cite{MV}, the classic Grothendieck construction is generalized to the monoidal setting: lax monoidal structures on a pseudofunctor $F\maps\A\to\bicat{Cat}$ bijectively correspond to monoidal structures on the total category $\inta F$ such that the induced opfibration is a strict monoidal functor and $\otimes_{\inta F}$ preserves liftings, see \cite[Thm.
-3.10]{MV}.
+
+In \cite{MV}, the classical Grothendieck construction is generalized to the monoidal setting: lax monoidal structures on a pseudofunctor $F\maps\A\to\bicat{Cat}$ bijectively correspond to monoidal structures on the total category $\inta F$ such that the induced opfibration is a strict monoidal functor and $\otimes_{\inta F}$ preserves cocartesian liftings, see \cite[Thm.~3.13]{MV}.
 If the monoidal category $\A$ is in fact cocartesian, there is a further correspondence of the two structures with an ordinary pseudofunctor $F\maps\A\to\bicat{MonCat}$ into the 2-category of monoidal categories, strong monoidal functors and monoidal natural transformations, summarized as
@@
 A \define{lax monoidal} pseudofunctor between monoidal bicategories $F\maps\bicat{A}\to\bicat{B}$ is a pseudofunctor equipped with pseudonatural transformations with components $\mu_{a,b}\maps Fa\otimes Fb\to F(a\otimes b)$ and $\mu_0\maps I\to FI$ along with coherent invertible modifications for associativity and unitality.
-This is commonly also called `weak monoida' pseudofunctor.
+This is commonly also called `weak monoidal' pseudofunctor.
 A \define{symmetric lax monoidal} pseudofunctor between symmetric monoidal bicategories comes with invertible $F(b)\circ \mu_{a,b}\cong \mu_{b,a}\circ b$, where $b$ is the braiding.
@@
 
-\bibitem{MV} J.\ Moeller and C.\ Vasilakopoulou, Monoidal Grothendieck construction. Available as \href{https://arxiv.org/abs/1809.00727}{arXiv:1809.00727}.
+\bibitem{MV} J.\ Moeller and C.\ Vasilakopoulou, Monoidal Grothendieck construction, \emph{Theory Appl.\ Categ.} \textbf{35} (2020), no.
+31, 1159--1207.
+Available as \href{https://arxiv.org/abs/1809.00727}{arXiv:1809.00727}.
 

### 2020-11-13 cospans.tex
more work on 3

@@
 \item a vertical morphism is a morphism of $\A$,
-\item a horizontal 1-cell $a\tickar b$ is a cospan in $\X$ of the form
+\item a horizontal 1-cell from $a$ to $b$ is a cospan in $\X$ of the form
 \begin{equation}\label{eq:structuredcospan}
@@
 \begin{proof}
-All relevant details can be found in \cite[Thm.~2.3\&3.9]{BC2}.
+All relevant details can be found in \cite[Theorems~2.3\&3.9]{BC2}.
 In particular, the double category structure only requires that $\X$ have pushouts, since this is how composition is formed.
-Moreover, the symmetric monoidal structure requires that $\X$ also have binary coproducts and an initial object (thus all finite colimits), and that $\A$ have and $L$ preserve finite coproducts, see \cite[Thm.~3.2.3]{CourserThesis}.
+Moreover, the symmetric monoidal structure requires that $\X$ also have binary coproducts and an initial object (thus all finite colimits), and that $\A$ have and $L$ preserve finite coproducts, see \cite[Theorem~3.2.3]{CourserThesis}.
 \end{proof}
@@
 
-In \cite{MV}, the classical Grothendieck construction is generalized to the monoidal setting: lax monoidal structures on a pseudofunctor $F\maps\A\to\bicat{Cat}$ bijectively correspond to monoidal structures on the total category $\inta F$ such that the induced opfibration is a strict monoidal functor and $\otimes_{\inta F}$ preserves cocartesian liftings, see \cite[Thm.~3.13]{MV}.
-If the monoidal category $\A$ is in fact cocartesian, there is a further correspondence of the two structures with an ordinary pseudofunctor $F\maps\A\to\bicat{MonCat}$ into the 2-category of monoidal categories, strong monoidal functors and monoidal natural transformations, summarized as
+In \cite{MV}, the classical Grothendieck construction is generalized to the monoidal setting: lax monoidal structures on a pseudofunctor $F\maps\A\to\bicat{Cat}$ (called \emph{monoidal opindexed category}) bijectively correspond to monoidal structures on the total category $\inta F$ such that the induced opfibration is a strict monoidal functor and $\otimes_{\inta F}$ preserves cocartesian liftings (called \emph{monoidal fibration}).
+If the monoidal category $\A$ is in fact cocartesian, there is a further correspondence of the two structures with an ordinary pseudofunctor $F\maps\A\to\bicat{MonCat}$ into the 2-category of monoidal categories, strong monoidal functors and monoidal natural transformations.
+
+\begin{thm}
+ There is a 2-equivalence between the 2-categories of monoidal opfibrations and monoidal opindexed categories.
+If the base is cocartesian monoidal, there is a 2-equivalence between monoidal opfibrations and pseudofunctors into monoidal categories.
+\end{thm}
+
+\begin{proof}
+This is the content of \cite[Theorems~3.13\&4.1]{MV}. In summary, we have correspondences
 \begin{gather}
-\textrm{lax monoidal pseudofunctors }F\maps(\A,+,0)\to(\bicat{Cat},\times) \notag\\
+\textrm{lax monoidal pseudofunctors }F\maps(\A,+)\to(\bicat{Cat},\times) \notag\\
 \Updownarrow \notag\\
@@
 \end{gather}
-The second equivalence was in fact earlier observed by Shulman in \cite{Shul2}.
-In more detail, if $(\phi,\phi_0)$ is the lax monoidal structure of $F$, each fibre category $\X_a=F(a)$ obtains a monoidal structure via
-\begin{gather}\label{eq:explicitstructure1}
-\otimes_a\maps F(a)\times F(a)\xrightarrow{\phi_{a,a}}F(a+a)\xrightarrow{F(\nabla)}F(a)\\
-I_x\maps\mathbf{1}\xrightarrow{\phi_0}F(0)\xrightarrow{F(!)}F(a)\nonumber
-\end{gather}
-Moreover, these correspondences further restrict to the case when the Grothendieck category is specifically cocartesian monoidal itself; for more details, see \cite[Cor.
-4.8]{MV}.
-In that case, the monoidal opfibration clauses for $U\maps(\X,+)\to(\A,+)$ translate to the functor (strictly) preserving coproducts and the initial object, and bijectively correspond to pseudofunctors $F\maps\A\to\Rex $ into the 2-category of esian categories, functors that preserve coproducts and initial objects and natural transformations.
+The second equivalence was also earlier observed by Shulman in \cite{Shul2}.
+In more detail, if $(\mu,\mu_0)$ is the lax monoidal structure of the pseudofunctor $F$ as recalled in \cref{sec:2cats}, each fibre category $\X_a=F(a)$ obtains a monoidal structure via
+\begin{equation}\label{eq:explicitstructure1}
+\otimes_a\maps F(a)\times F(a)\xrightarrow{\mu_{a,a}}F(a+a)\xrightarrow{F(\nabla)}F(a),\quad
+I_a\maps\mathbf{1}\xrightarrow{\mu_0}F(0)\xrightarrow{F(!)}F(a)
+\end{equation}
+where $\nabla$ is the fold map. 
+\end{proof}
+
+These correspondences further restrict to the case when the Grothendieck category is specifically cocartesian monoidal itself. In that case, opfibrations
+$(\X,+)\to(\A,+)$ that (strictly) preserve coproducts and the initial object (and such that $+$ preserves cocartesian liftings) bijectively correspond to pseudofunctors into the 2-category of cocartesian categories; for more details, see \cite[Corollary 4.7]{MV} and the related discussion.
+%!!!
+Christina: someone wrote Rex there, perhaps it was me.
+This is a subcategory, not all finite colimits are there.
+
+{\chris In progress...}
 
@@
 
-\begin{prop}\cite[Prop.\ 4.4]{Gray} \label{prop:opfibtolari}
+\begin{prop}\cite[Proposition~4.4]{Gray} \label{prop:opfibtolari}
   Let $\U \maps\X \to \A$ be an opfibration. Then
@@
 
-\begin{lem}\label{prop:CV}\cite[Prop. \ 3.3]{CV}
+\begin{lem}\label{prop:CV}\cite[Proposition~3.3]{CV}
 Suppose $\U\maps\X\to\A$ is a right adjoint `left inverse'. If $\X$ and $\A$ have chosen pushouts and initial objects and $\U$ strictly preserves them, then $\U$ is an opfibration.
@@
 
-\section{Appendix}
-
-%!!!Christina: Here, I basically rearranged things to make them come in a certain order, and also added a few things for monoidal bicats, maybe more is needed or not.
-Didn't change Kenny's notation or writings almost at all
-
-In this chapter, we gather some well-known concepts required to make the material self-contained, as well as references to more detailed expositions.
+\appendix
+
+\section{}
+In this appendix, we gather some well-known concepts required to make the material self-contained, as well as references to more detailed expositions.
 
@@
 For standard 2-categorical material, we refer the reader to e.g. \cite{KS} or \cite{DS} for monoidal structures.
-
-Recall that a pseudofunctor $F\maps\bicat{A}\to\bicat{B}$ between bicategories $\bicat{A}$ and $\bicat{B}$ is functorial up to coherent natural isomorphism, namely for composable arrows we have $F(g\circ f)\cong Fg\circ Ff$ and $F(1_a)\cong1_{Fa}$ satisfying standard axioms.
+Recall that a \define{pseudofunctor} $F\maps\bicat{A}\to\bicat{B}$ between bicategories $\bicat{A}$ and $\bicat{B}$ is functorial up to coherent natural isomorphism, namely for composable arrows we have $F(g\circ f)\cong Fg\circ Ff$ and $F(1_a)\cong1_{Fa}$ satisfying standard axioms.
 Given pseudofunctors $F,G\maps \bicat{A} \to \bicat{B}$, a \define{pseudonatural transformation} $\sigma$ consists of
@@
 %\]
-%Christina: I removed the above, they are not needed I believe
+%Christina: I removed the above, they are not needed I believe. Check again in the end.
 We denote by $[\A,\bicat{Cat}]_\pse$ the 2-category 
@@
 
+A \define{monoidal} bicategory $\A$ comes with a pseudofunctor $\otimes\maps\A\times\A\to\A$ and a unit object $I$ that are associative and unital up to coherent equivalence.
+A \define{braided} monoidal bicategory comes with a pseudonatural equivalence $\beta_{a,b}\maps a\ot b\to b\ot a$ and appropriate invertible modifications; it is \define{sylleptic} if there is an appropriate invertible modification $1_{a\ot b}\Rrightarrow\beta_{b,a}\circ\beta_{a,b}$ and it is \define{symmetric} if one further axiom holds.
 A \define{lax monoidal} pseudofunctor between monoidal bicategories $F\maps\bicat{A}\to\bicat{B}$ is a pseudofunctor equipped with pseudonatural transformations with components $\mu_{a,b}\maps Fa\otimes Fb\to F(a\otimes b)$ and $\mu_0\maps I\to FI$ along with coherent invertible modifications for associativity and unitality.
 This is commonly also called `weak monoidal' pseudofunctor.
-A \define{symmetric lax monoidal} pseudofunctor between symmetric monoidal bicategories comes with invertible $F(b)\circ \mu_{a,b}\cong \mu_{b,a}\circ b$, where $b$ is the braiding.
-%!!!Christina: Hiding various details under the rug - e.g. what a symmetric monoidal bicategory is. Should be fine? Also, not sure if we need monoidal transformations?
+A \define{braided lax monoidal} pseudofunctor between symmetric monoidal bicategories comes with an invertible modification with components $F(\beta_{a,b})\circ \mu_{a,b}\cong\mu_{b,a}\circ \beta_{Fa,Fb}$.
 
@@
 
-\bibitem{Shul2} M.\ Shulman, Framed bicategories and monoidal fibrations. Available as \href{https://arxiv.org/abs/0706.1286}{arXiv:0706.1286}.
+\bibitem{Shul2} M.\ Shulman, Framed bicategories and monoidal fibrations, \emph{Theory Appl.Categ.} \textbf{20} (2008), no.
+18, 650 -- 738, 2008.
+Available as \href{https://arxiv.org/abs/0706.1286}{arXiv:0706.1286}.
 

### 2020-11-13 cospans.tex
More polishing of Theorem 2.1

@@
 (E) edge node [above] {$o'$} (D)
-(B) edge node [above] {$j$} (F)
-(D) edge node [above] {$j'$} (F)
+(B) edge node [above] {$j_m$} (F)
+(D) edge node [above] {$j_{n}'$} (F)
 (F) edge node [left] {$\psi$} (G)
-(A) edge[bend left] node [left] {$\psi j i$} (G)
-(E) edge[bend right] node [right] {$\psi j' o'$} (G);
+(A) edge[bend left] node [left] {$\psi j_m i$} (G)
+(E) edge[bend right] node [right] {$\psi j_{n}' o'$} (G);
 \end{tikzpicture}
@@
 where $\psi \maps m + n \to m+_{b} n$ is the natural map from the coproduct to the pushout and $\phi_{m,n} \maps F(m) \times F(n) \to F(m+n)$ is the natural transformation coming from the structure of the lax monoidal pseudofunctor $F \maps \A \to \Cat$.
-It is clear that the equations $S(M \odot N)=S(M)$ and $T(M \odot N)=T(N)$ hold.
 Given two horizontally composable maps of $F$-decorated cospans which we respectively denote by $\alpha$ and $\beta$:
@@
 \]
-\textbf{In progress...}
-
+their horizontal composite $\alpha \odot \beta$ is the pair given by first horizontally composing the two maps of cospans in $\A$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0.5) {$a$};
+\node (A') at (0,-0.5) {$a'$};
+\node (B) at (1.5,0.5) {$m+_{b} n$};
+\node (C) at (3,0.5) {$c$};
+\node (C') at (3,-0.5) {$c'$};
+\node (D) at (1.5,-0.5) {$m'+_{b'}n'$};
+\node (E) at (4.5,0.5) {$x \odot y \in F(m+_b n)$};
+\node (F) at (4.5,-0.5) {$x' \odot y' \in F(m' +_{b'} n')$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$\psi j_m i_1$} (B)
+(C) edge node[above]{$\psi j_n o_2$} (B)
+(A) edge node[left]{$f$} (A')
+(C) edge node[right]{$k$} (C')
+(A') edge node [above]{$\psi j_{m'} i_1'$} (D)
+(C') edge node [above]{$\psi j_{n'} o_2'$} (D)
+(B) edge node [left] {$h_1 +_g h_2$} (D);
+\end{tikzpicture}
+\]
+together with the morphism of decorations $\tau_{\alpha \odot \beta} \colon F(h_1 +_g h_2)(x \odot y) \to (x' \odot y')$ given by the following commutative diagram:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (4.75,0) {$\tau_\alpha \times \tau_\beta \Swarrow$};
+\node (D) at (3,0) {$1 \xrightarrow{\lambda^{-1}} 1 \times 1$};
+\node (E) at (5.5,0.5) {$F(m) \times F(n)$};
+\node (E') at (5.5,-0.5) {$F(m') \times F(n')$};
+\node (B) at (7.5,0.5) {$F(m+n)$};
+\node (B') at (7.5,-0.5) {$F(m' + n')$};
+\node (C) at (9.25,0.5) {$F(m+_{b} n)$};
+\node (C') at (9.25,-0.5) {$F(m' +_{b'} n')$};
+\path[->,font=\scriptsize,>=angle 90]
+(E) edge node [above] {$\phi_{m,n}$} (B)
+(E') edge node [above] {$\phi_{m',n'}$} (B')
+(B) edge node [above] {$F(\psi)$} (C)
+(B') edge node [above] {$F(\psi)$} (C')
+(C) edge node [right] {$F(h_1 +_g h_2)$} (C')
+(B) edge node [right] {$F(h_1 + h_2)$} (B')
+(D) edge node [above] {$x \times y$} (E)
+(D) edge node [below] {$x' \times y'$} (E')
+(E) edge node [right] {$F(h_1) \times F(h_2)$} (E');
+\end{tikzpicture}
+\]
+The middle square commutes since $F$ is a lax monoidal pseudofunctor and the right square commutes as the underlying square commutes.
+The decorations $x \odot y$ and $x' \odot y'$ are given respectively by the top and bottom composite of arrows and the morphism of decorations $\tau_{\alpha \odot \beta}$ is given by composing $\tau_\alpha \times \tau_\beta$ with the two commuting squares.
+It is clear that the equations $S(M \odot N)=S(M)$ and $T(M \odot N)=T(N)$ hold, and this finishes defining the four structure functors $U,S,T$ and $\odot$.
+
+Lastly, our double category is required to have an associator $\alpha$ (\textbf{over using alpha, ignoring for now}) and left and right unitors $\lambda$ and $\rho$ which are natural isomorphisms governing the composition of horizontal 1-cells that are required to satisfy the standard coherence axioms for a monoidal category, as well as $S(\alpha),S(\lambda),S(\rho),T(\alpha),T(\lambda)$ and $T(\rho)$ all being identities.
+We will only show the associator $\alpha$, left unitor $\lambda$ and the pentagon identity, as the remaining details will be similar to these.
+
+First we will build the associator $\alpha \colon \odot (\odot \times 1) \Rightarrow \odot (1 \times \odot)$, which will be a globular 2-morphism; in other words, a map of $F$-decorated cospans with identities on the sides.
 Given three composable horizontal 1-cells $M_1, M_2$ and $M_3$:
@@
 \node (C) at (2,0) {$b$};
-\node (D) at (1,-0.5) {$x \in F(m_1)$};
+\node (D) at (1,-0.5) {$x_1 \in F(m_1)$};
 \node (E) at (3,0) {$b$};
@@
 \]
-we get a natural isomorphism $a_{M_1,M_2,M_3} \maps (M_1 \odot M_2) \odot M_3 \to M_1 \odot (M_2 \odot M_3)$ which is a globular 2-morphism given by a map of cospans $(\id_{a_1},\sigma,\id_{a_4})$:
+we first compute $(M_1 \odot M_2) \odot M_3)$ by pushing out the first two cospans followed by the third:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$a$};
+\node (B) at (2,0) {$(m_1 +_b m_2) +_c m_3$};
+\node (C) at (4,0) {$b$};
+%\node (D) at (3,0) {$x \in F(m)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$$} (B)
+(C) edge node[above]{$$} (B);
+\end{tikzpicture}
+\]
+as well as the decoration $(x_1 \odot x_2) \odot x_3$ on the apex obtained as explained above.
+Explicitly, the decoration $(x_1 \odot x_2) \odot x_3) \in F((m_1+_b m_2) +_c m_3)$ is obtained as the composite $$ (x_1 \odot x_2) \odot x_3 \mapseqq 1 \xrightarrow{\zeta_1} F(m_1+_{b} m_2) \times F(m_3) \xrightarrow{\phi_{m_1+_{b} m_2, m_3}} F((m_1+_{b}m_2) +m_3) \xrightarrow{F(\psi)} F((m_1+_{b} m_2)+_{c} m_3)$$where$$\scriptstyle{\zeta_1 \mapseqq 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{x_1 \times x_2} F(m_1) \times F(m_2) \xrightarrow{\phi_{m_1,m_2}} F(m_1+m_2) \xrightarrow{F(j)} F(m_1+_b m_2) \xrightarrow {\rho^{-1}} F(m_1+_b m_2) \times 1 \xrightarrow{1 \times x_3} F(m_1+_b m_2) \times F(m_3).}$$
+The composite $M_1 \odot (M_2 \odot M_3)$ is obtained similarly:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$a$};
+\node (B) at (2,0) {$m_1 +_b (m_2 +_c m_3)$};
+\node (C) at (4,0) {$b$};
+%\node (D) at (3,0) {$x \in F(m)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$$} (B)
+(C) edge node[above]{$$} (B);
+\end{tikzpicture}
+\]
+as well as the decoration $x_1 \odot (x_2 \odot x_3)$ on the apex:
+$$x_1 \odot (x_2 \odot x_3) \mapseqq 1 \xrightarrow{\zeta_2} F(m_1) \times F(m_2 +_c m_3) \xrightarrow{\phi_{m_1, m_2 +_c m_3}} F(m_1+(m_2 +_c +m_3)) \xrightarrow{F(\psi)} F(m_1+_{b} (m_2+_{c} m_3))$$with $\zeta_2$ being similar to $\zeta_1$ above.
+The associator $\alpha$ is then given by the map of $F$-decorated cospans given by the map of cospans
 \[
@@
 \node (D) at (1.5,-0.5) {$m_1+_{b}(m_2 +_{c} m_3)$};
-\node (E) at (5.5,0.5) {$(x \odot y) \odot z \in F((m_1+_{b} m_2)+_{c} m_3)$};
-\node (F) at (5.5,-0.5) {$x \odot (y \odot z) \in F(m_1+_{b} (m_2 +_{c} m_3))$};
+\node (E) at (5.5,0.5) {$(x_1 \odot x_2) \odot x_3 \in F((m_1+_{b} m_2)+_{c} m_3)$};
+\node (F) at (5.5,-0.5) {$x_1 \odot (x_2 \odot x_3) \in F(m_1+_{b} (m_2 +_{c} m_3))$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (C') edge node {$$} (D)
-(B) edge node [left] {$\sigma$} (D);
-\end{tikzpicture}
-\]
-with the decorations on the cospan's apices given by:
-$$ (x \odot y) \odot z \mapseqq 1 \xrightarrow{\zeta_1} F(m_1+_{b} m_2) \times F(m_3) \xrightarrow{\phi_{m_1+_{b} m_2, m_3}} F((m_1+_{b}m_2) +m_3) \xrightarrow{F(j_{m_1+_{b} m_2,m_3})} F((m_1+_{b} m_2)+_{c} m_3)$$ $$\zeta_1 = (1 \times z) \rho^{-1} F(j_{m_1,m_2}) \phi_{m_1,m_2} (x \times y) \lambda^{-1}$$
-and
-$$ x \odot (y \odot z) \mapseqq 1 \xrightarrow{\zeta_2} F(m_1) \times F(m_2 +_{c} m_3) \xrightarrow{\phi_{m_1, m_2 +_{c} m_3}} F(m_1+(m_2 +_{c} m_3)) \xrightarrow{F(j_{m_1,m_2 +_{c} m_3})} F(m_1+_{b} (m_2+_{c} m_3))$$ $$\zeta_2 = (x \times 1) \lambda^{-1} F(j_{m_2,m_3}) \phi_{m_2,m_3} (y \odot z) \lambda^{-1}$$
-together with the isomorphism $\tau_\sigma \maps F(\sigma)((x \odot y) \odot z) \to x \odot (y \odot z)$.
+(B) edge node [left] {$\alpha$} (D);
+\end{tikzpicture}
+\]
+together with the morphism of decorations $\tau_\alpha \colon F(\alpha)((x_1 \odot x_2) \odot x_3) \to (x_1 \odot (x_2 \odot x_3))$ that is obtained by pasting various commutative squares together, as we did for a horizontal composite above.
+The associator $\alpha$ will then satisfy the pentagon identity:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (-1,0) {$((M_1 \odot M_2) \odot M_3) \odot M_4$};
+\node (B) at (3,1.05) {$(M_1 \odot (M_2 \odot M_3)) \odot M_4$};
+\node (C) at (7,0) {$M_1 \odot ((M_2 \odot M_3) \odot M_4)$};
+\node (D) at (1.5,-1.05) {$(M_1 \odot M_2) \odot (M_3 \odot M_4)$};
+\node (E) at (4.5,-1.05) {$M_1 \odot (M_2 \odot (M_3 \odot M_4))$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node [above] {$\alpha \times 1$}(B)
+(B) edge node [above] {$\alpha$}(C)
+(A) edge node [below] {$\alpha$}(D)
+(D) edge node [above] {$\alpha$}(E)
+(C) edge node [below] {$1 \times \alpha$}(E);
+\end{tikzpicture}
+\]
+which we may realize in two stages.
+First, for the underlying pentagon of maps of cospans in $\A$ commuting due to the fact that $\lCsp(\A)$ is a double category with its own associator that satisfies the pentagon identity, and second, for the pentagon of morphisms of decorations due to the pasting of various commutative squares in $\Cat$.
+
+\noindent
+\textbf{In progress...}
+%we get a natural isomorphism $a_{M_1,M_2,M_3} \maps (M_1 \odot M_2) \odot M_3 \to M_1 \odot (M_2 \odot M_3)$ which is a globular 2-morphism given by a map of cospans $(\id_{a_1},\sigma,\id_{a_4})$:
+%with the decorations on the cospan's apices given by:
+%$$ (x \odot y) \odot z \mapseqq 1 \xrightarrow{\zeta_1} F(m_1+_{b} m_2) \times F(m_3) \xrightarrow{\phi_{m_1+_{b} m_2, m_3}} F((m_1+_{b}m_2) +m_3) \xrightarrow{F(j_{m_1+_{b} m_2,m_3})} F((m_1+_{b} m_2)+_{c} m_3)$$ $$\zeta_1 = (1 \times z) \rho^{-1} F(j_{m_1,m_2}) \phi_{m_1,m_2} (x \times y) \lambda^{-1}$$
+%and
+%$$ x \odot (y \odot z) \mapseqq 1 \xrightarrow{\zeta_2} F(m_1) \times F(m_2 +_{c} m_3) \xrightarrow{\phi_{m_1, m_2 +_{c} m_3}} F(m_1+(m_2 +_{c} m_3)) \xrightarrow{F(j_{m_1,m_2 +_{c} m_3})} F(m_1+_{b} (m_2+_{c} m_3))$$ $$\zeta_2 = (x \times 1) \lambda^{-1} F(j_{m_2,m_3}) \phi_{m_2,m_3} (y \odot z) \lambda^{-1}$$
+%together with the isomorphism $\tau_\sigma \maps F(\sigma)((x \odot y) \odot z) \to x \odot (y \odot z)$.
 Note that the map $\sigma \maps (m_1+_{b} m_2)+_{c}m_3 \to m_1+_{b}(m_2+_{c}m_3)$ is the universal map between two colimits of the same diagram.
+
+\noindent
 We also have left and right unitors where given a horizontal 1-cell $M$:
@@
 \]
-To obtain the morphism of decorations for a horizontal composite, we have as initial data:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (4,0) {$\tau_\alpha \Swarrow$};
-\node (D) at (3,0) {$1$};
-\node (E) at (4.5,0.5) {$F(m)$};
-\node (E') at (4.5,-0.5) {$F(m')$};
-\node (A') at (6.5,0) {$\tau_\beta \Swarrow$};
-\node (D') at (5.5,0) {$1$};
-\node (E'') at (7,0.5) {$F(n)$};
-\node (E''') at (7,-0.5) {$F(n')$};
-\path[->,font=\scriptsize,>=angle 90]
-(D) edge node [above] {$x$} (E)
-(D) edge node [below] {$x'$} (E')
-(E) edge node [right] {$F(h_1)$} (E')
-(D') edge node [above] {$y$} (E'')
-(D') edge node [below] {$y'$} (E''')
-(E'') edge node [right] {$F(h_2)$} (E''');
-\end{tikzpicture}
-\]
-These two 2-morphisms $\tau_\alpha$ and $\tau_\beta$ are two 2-morphisms in the monoidal 2-category $(\Cat,\times,1)$ and so we can tensor them which results in:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (4.75,0) {$\tau_\alpha \times \tau_\beta \Swarrow$};
-\node (D) at (3,0) {$1 \xrightarrow{\lambda^{-1}} 1 \times 1$};
-\node (E) at (5.5,0.5) {$F(m) \times F(n)$};
-\node (E') at (5.5,-0.5) {$F(m') \times F(n')$};
-\node (B) at (7.5,0.5) {$F(m+n)$};
-\node (B') at (7.5,-0.5) {$F(m' + n')$};
-\node (C) at (9.25,0.5) {$F(m+_{b} n)$};
-\node (C') at (9.25,-0.5) {$F(m' +_{b'} n')$};
-\path[->,font=\scriptsize,>=angle 90]
-(E) edge node [above] {$\phi_{m,n}$} (B)
-(E') edge node [above] {$\phi_{m',n'}$} (B')
-(B) edge node [above] {$F(j_{m,n})$} (C)
-(B') edge node [above] {$F(j_{m',n'})$} (C')
-(C) edge node [right] {$F(h_1 +_g h_2)$} (C')
-(B) edge node [right] {$F(h_1 + h_2)$} (B')
-(D) edge node [above] {$x \times y$} (E)
-(D) edge node [below] {$x' \times y'$} (E')
-(E) edge node [right] {$F(h_1) \times F(h_2)$} (E');
-\end{tikzpicture}
-\]
-where the middle square commutes since $F$ is a lax monoidal pseudofunctor and the right square commutes as the underlying diagram commutes.
-The decorations $x \odot y$ and $x' \odot y'$ are given respectively by top and bottom composite of arrows and the morphism of decorations $\tau_{\alpha \odot \beta}$ is given by composing $\tau_\alpha \times \tau_\beta$ with the two commuting squares, which can equivalently be viewed as a morphism in $F(m' +_{b'} n')$.
+%To obtain the morphism of decorations for a horizontal composite, we have as initial data:
+%\[
+%\begin{tikzpicture}[scale=1.5]
+%\node (A) at (4,0) {$\tau_\alpha \Swarrow$};
+%\node (D) at (3,0) {$1$};
+%\node (E) at (4.5,0.5) {$F(m)$};
+%\node (E') at (4.5,-0.5) {$F(m')$};
+%\node (A') at (6.5,0) {$\tau_\beta \Swarrow$};
+%\node (D') at (5.5,0) {$1$};
+%\node (E'') at (7,0.5) {$F(n)$};
+%\node (E''') at (7,-0.5) {$F(n')$};
+%\path[->,font=\scriptsize,>=angle 90]
+%(D) edge node [above] {$x$} (E)
+%(D) edge node [below] {$x'$} (E')
+%(E) edge node [right] {$F(h_1)$} (E')
+%(D') edge node [above] {$y$} (E'')
+%(D') edge node [below] {$y'$} (E''')
+%(E'') edge node [right] {$F(h_2)$} (E''');
+%\end{tikzpicture}
+%\]
+%These two 2-morphisms $\tau_\alpha$ and $\tau_\beta$ are two 2-morphisms in the monoidal 2-category $(\Cat,\times,1)$ and so we can tensor them which results in:
 

### 2020-11-13 cospans.tex
Update cospans.tex

--- 2020-11-13 cospans.tex
@@
 % John Baez, Kenny Courser and Christina Vasilakopoulou
-% 2020/11/09 - JB
+% 2020/11/12 - JB
 
@@
 %{\chris Amend at the end}
-%The outline for the paper is as follows: In \cref{DecCospansDoubleCat}, we construct the symmetric monoidal double category $F\lCsp$, obtain the underlying symmetric monoidal bicategory $F \mathbf{Csp}$ via a result of Shulman, and decategorify this symmetric monoidal bicategory to obtain the symmetric monoidal category $F$Csp.
-In \cref{MapsDecCospansDoubleCat} we define maps between decorated cospan double categories which are double functors of an appropriate type.
-In \cref{some other section} we investigate when a symmetric lax monoidal pseudofunctor gives rise to a left adjoint via the Grothendieck construction, which naturally leads to another compositional framework known as `Structured cospans'.
-In \cref{EquivDoubleCats} we briefly review the framework Structured cospans and prove that the double categorical versions of decorated cospans and structured cospans are equivalent when both are appropriate.
-Finally, in \cref{Applications}, we present a few examples that can be realized with either framework and discuss the realized equivalences.
+%The outline for the paper is as follows: In Section \cref{DecCospansDoubleCat}, we construct the symmetric monoidal double category $F\lCsp$, obtain the underlying symmetric monoidal bicategory $F \mathbf{Csp}$ via a result of Shulman, and decategorify this symmetric monoidal bicategory to obtain the symmetric monoidal category $F$Csp.
+In Section \cref{MapsDecCospansDoubleCat} we define maps between decorated cospan double categories which are double functors of an appropriate type.
+In Section \cref{some other section} we investigate when a symmetric lax monoidal pseudofunctor gives rise to a left adjoint via the Grothendieck construction, which naturally leads to another compositional framework known as `Structured cospans'.
+In Section \cref{EquivDoubleCats} we briefly review the framework Structured cospans and prove that the double categorical versions of decorated cospans and structured cospans are equivalent when both are appropriate.
+Finally, in Section \cref{Applications}, we present a few examples that can be realized with either framework and discuss the realized equivalences.
 
@@
 In this section we build the symmetric monoidal double category $F \lCsp$ mentioned in the introduction.
-Then we obtain an underlying symmetric monoidal bicategory $F \mathbf{Csp}$ using a result of Shulman \cite{Shul}
-%!!!Christina: John suggested we might move all the horizontal bicategory and decategorified 1-category results together somewhere later/in the end.
-and finally decategorify this to obtain a symmetric monoidal category $F\mathsf{Csp}$ which is a generalization of Fong's original decorated cospan category \cite{Fong}.
+Then we obtain an underlying symmetric monoidal bicategory $F \mathbf{Csp}$ using a result of Shulman \cite{Shul} and finally decategorify this to obtain a symmetric monoidal category $F\mathsf{Csp}$ which is a generalization of Fong's original decorated cospan category \cite{Fong}.
 The definition of a lax monoidal pseudofunctor is recalled in \cref{sec:2cats}, and the basics of double categories are recalled in \cref{sec:doublecats}.
@@
 \item a vertical morphism is a morphism of $\A$,
-\item a horizontal 1-cell is an $F$\define{-decorated cospan}: that is, 
+\item a horizontal 1-cell is an \define{$F$-decorated cospan}: that is, 
 a cospan in $\A$:
@@
 together with a \define{decoration} $x \in F(m)$,
-\item a 2-morphism is a \define{map of} $F$\define{-decorated cospans}: that is, 
+\item a 2-morphism is a \define{map of $F$-decorated cospans}: that is, 
 a map of cospans in $\A$:
@@
 \section{Structured versus decorated cospans} \label{EquivDoubleCats}
-
-In \cite{BC2}, the first two authors introduce the symmetric monoidal double category of \emph{structured cospans} as a formalism to capture open networks.
+%\begin{comment}
+
+In \cite{BC2}, the first two authors introduces the symmetric monoidal double category of \emph{structured cospans} as a formalism to capture open networks.
 One of the main goals of this paper is to provide a monoidal double equivalence between this double category and that of \emph{decorated cospans}, described in detail in \cref{DecCospansDoubleCat}.
-We first recall the double category structured cospans form.
+Below we recall the double category structured cospans form.
 
 \begin{thm}\label{SC}
-Given categories $\X$ and $\A$ with finite colimits and $L \maps \A \to \X$ a finitely cocontinuous functor, there exists a symmetric monoidal double category $_L\lCsp(\X)$ in which
+Given a category $\X$ with finite colimits and a category $\A$ with finite coproducts and a finite coproduct preserving functor $L \maps \A \to \X$ with $\A$ and $\X$, there exists a symmetric monoidal double category $_L \lCsp(\X)$ which has:
 \begin{itemize}
-\item an object is an object of $\A$,
-\item a vertical morphism is a morphism of $\A$,
-\item a horizontal 1-cell $a\tickar b$ is a cospan in $\X$ of the form
+\item{objects given by objects of $\A$,}
+\item{vertical 1-morphisms given by morphisms of $\A$,}
+\item{horizontal 1-cells $a\tickar b$ given by cospans of $\X$ of the form:
 \begin{equation}\label{eq:structuredcospan}
@@
 \end{tikzpicture}
-\end{equation}
-\item a 2-morphism is a map of cospans in $\X$ of the form
+\end{equation}}
+\item 2-morphisms given by maps of cospans of $\X$ of the form:
 \begin{equation}\label{eq:2cellsStrCsp}
@@
 \end{itemize}
-The symmetric monoidal structure is formed by using binary coproducts and the initial object.
+Composition of horizontal 1-cells and 2-morphisms is given by pushouts in $\X$ and tensoring of objects is under binary coproducts in $\A$.
 \end{thm}
-
 \begin{proof}
-All relevant details can be found in \cite[Thm.~2.3\&3.9]{BC2}.
-In particular, the double category structure only requires that $\X$ have pushouts, since this is how composition is formed.
-Moreover, the symmetric monoidal structure requires that $\X$ also have binary coproducts and an initial object (thus all finite colimits), and that $\A$ have and $L$ preserve finite coproducts, see \cite[Thm.~3.2.3]{CourserThesis}.
+See the first two authors' work on structured cospans \cite{BC2}.
 \end{proof}
 
-The following theorem establishes the desired equivalence between these two different double categorical network frameworks of structured and decorated cospans in a formal way.
-We denote by $\bicat{Rex}$ the 2-category of finitely cocomplete categories and finitely cocontinuous functors, and the symmetric monoidal double structure of decorated cospans is worked out in \cref{thm:decoratedcospans,DC}.
+The desired equivalence between these two different double categorical network frameworks, namely structured cospans and decorated cospans,
+is established by the following theorem. We denote by $\bicat{Rex}$ the 2-category of finitely cocomplete categories and finitely cocontinuous functors.
 
 \begin{thm}\label{Equiv}
-Suppose $\ca{A}$ has finite colimits and $(F,\phi,\phi_0)\maps(\ca{A},+,0) \to (\bicat{Cat},\times,\mathbf{1})$ is a symmetric lax monoidal pseudofunctor that factors through $\bicat{Rex}$ as an ordinary pseudofunctor.
-Then the symmetric monoidal double category $F\lCsp$ of decorated cospans is equivalent to the symmetric monoidal double category $_L\lCsp(\inta F)$ of structured cospans, where $L \maps \A \to \inta F$ is the left adjoint of the induced Grothendieck opfibration $\U\maps \inta F \to \A$.
+Suppose $\ca{A}$ is a finitely cocomplete category and $(F,\phi,\phi_0)\maps(\ca{A},+,0) \to (\bicat{Cat},\times,\mathbf{1})$ is a symmetric lax monoidal pseudofunctor that factors through $\bicat{Rex}$ as an ordinary pseudofunctor.
+Then the symmetric monoidal double category $F\lCsp$ of decorated cospans given in \cref{thm:decoratedcospans} is equivalent to the symmetric monoidal double category $\scsp{L_F}{\inta F}$ of structured cospans given in \cref{SC}, where $L_F \maps \A \to \inta{F}$ is the left adjoint of the induced Grothendieck opfibration $\U_F\maps \inta{F} \to \A$.
+%by \cref{thm:Grothendieck},
+%under the assumptions of \cref{cor:fcocMonGroth}.
 \end{thm}
@@
 The conditions of the above theorem relate to the existence of left adjoints for opfibrations; we first sketch this underlying framework, and then we proceed to the proof of the theorem.
+
 The basics of fibration theory needed for our purposes are recalled in \cref{sec:fibrations}. 
-
-In \cite{MV}, the classical Grothendieck construction is generalized to the monoidal setting: lax monoidal structures on a pseudofunctor $F\maps\A\to\bicat{Cat}$ bijectively correspond to monoidal structures on the total category $\inta F$ such that the induced opfibration is a strict monoidal functor and $\otimes_{\inta F}$ preserves cocartesian liftings, see \cite[Thm.~3.13]{MV}.
+In \cite{MV}, the classic Grothendieck construction is generalized to the monoidal setting: lax monoidal structures on a pseudofunctor $F\maps\A\to\bicat{Cat}$ bijectively correspond to monoidal structures on the total category $\inta F$ such that the induced opfibration is a strict monoidal functor and $\otimes_{\inta F}$ preserves liftings, see \cite[Thm.
+3.10]{MV}.
 If the monoidal category $\A$ is in fact cocartesian, there is a further correspondence of the two structures with an ordinary pseudofunctor $F\maps\A\to\bicat{MonCat}$ into the 2-category of monoidal categories, strong monoidal functors and monoidal natural transformations, summarized as
@@
 A \define{lax monoidal} pseudofunctor between monoidal bicategories $F\maps\bicat{A}\to\bicat{B}$ is a pseudofunctor equipped with pseudonatural transformations with components $\mu_{a,b}\maps Fa\otimes Fb\to F(a\otimes b)$ and $\mu_0\maps I\to FI$ along with coherent invertible modifications for associativity and unitality.
-This is commonly also called `weak monoidal' pseudofunctor.
+This is commonly also called `weak monoida' pseudofunctor.
 A \define{symmetric lax monoidal} pseudofunctor between symmetric monoidal bicategories comes with invertible $F(b)\circ \mu_{a,b}\cong \mu_{b,a}\circ b$, where $b$ is the braiding.
@@
 
-\bibitem{MV} J.\ Moeller and C.\ Vasilakopoulou, Monoidal Grothendieck construction, \emph{Theory Appl.\ Categ.} \textbf{35} (2020), no.
-31, 1159--1207.
-Available as \href{https://arxiv.org/abs/1809.00727}{arXiv:1809.00727}.
+\bibitem{MV} J.\ Moeller and C.\ Vasilakopoulou, Monoidal Grothendieck construction. Available as \href{https://arxiv.org/abs/1809.00727}{arXiv:1809.00727}.
 

### 2020-11-14 cospans.tex
a lot of work on section 4

--- 2020-11-13 cospans.tex
@@
 From the accompanying left adjoint $L \maps \A \to \X$, we  construct a symmetric monoidal double category ${}_L \lCsp(\X)$ of structured cospans.
-Finally, in \cref{Equiv} we prove that this structured cospan double category ${}_L \lCsp(\X)$ is equivalent to the decorated cospan double category $F \lCospan$.
+Finally, in \cref{thm:equiv} we prove that this structured cospan double category ${}_L \lCsp(\X)$ is equivalent to the decorated cospan double category $F \lCospan$.
 
@@
 \section{Decorated cospans}\label{DecCospansDoubleCat}
-In this section we build the symmetric monoidal double category $F \lCsp$ mentioned in the introduction.
-Then we obtain an underlying symmetric monoidal bicategory $F \mathbf{Csp}$ using a result of Shulman \cite{Shul}
-%!!!Christina: John suggested we might move all the horizontal bicategory and decategorified 1-category results together somewhere later/in the end.
-and finally decategorify this to obtain a symmetric monoidal category $F\mathsf{Csp}$ which is a generalization of Fong's original decorated cospan category \cite{Fong}.
+
+In this section we build the symmetric monoidal double category $F \lCsp$ mentioned in the introduction, and then study the functoriality of this construction.
 The definition of a lax monoidal pseudofunctor is recalled in \cref{sec:2cats}, and the basics of double categories are recalled in \cref{sec:doublecats}.
 
-\begin{thm}\label{thm:decoratedcospans}
+\begin{thm}\label{thm:decorated_cospans}
 Let $\A$ be a category with chosen finite colimits and $F \maps \A \to \Cat$ a lax monoidal pseudofunctor. Then there exists a double category $F\lCsp$ in which
@@
 
+Regarding maps between symmetric monoidal double categories, consider another symmetric lax monoidal pseudofunctor $F' \maps \mathsf{A'} \to \Cat$%, we can obtain another symmetric monoidal double category $F' \lCsp$.
+a morphism from $F\lCsp$ to $F' \lCsp$ will then be a double functor $\mathbb{H} \maps F\lCsp \to F' \lCsp$ whose object component is given by a finite colimit preserving functor $\mathbb{H}_0 = H \maps \A \to \mathsf{A'}$ and whose arrow component is given by a functor $\mathbb{H}_1$ defined on horizontal 1-cells by:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$a$};
+\node (B) at (1,0) {$c$};
+\node (C) at (2,0) {$b$};
+\node (D) at (1,-0.5) {$d \in F(c)$};
+\node (E) at (2.75,0) {$\mapsto$};
+\node (A') at (3.5,0) {$H(a)$};
+\node (B') at (4.5,0) {$H(c)$};
+\node (C') at (5.5,0) {$H(b)$};
+\node (D') at (4.5,-0.5) {$\theta_c E(d) \phi \in F'(H(c))$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i$} (B)
+(C) edge node[above]{$o$} (B)
+(A') edge node[above]{$H(i)$} (B')
+(C') edge node[above]{$H(o)$} (B');
+\end{tikzpicture}
+\]
+and on 2-morphisms by:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0.5) {$a$};
+\node (A') at (0,-0.5) {$a'$};
+\node (B) at (1,0.5) {$c$};
+\node (C) at (2,0.5) {$b$};
+\node (C') at (2,-0.5) {$b'$};
+\node (D) at (1,-0.5) {$c'$};
+\node (E) at (3,0.5) {$d \in F(c)$};
+\node (F) at (3,-0.5) {$d' \in F(c')$};
+\node (G) at (1,-1) {$\tau \maps F(h)(d) \to d'$};
+\node (A'') at (4.25,0.5) {$H(a)$};
+\node (A''') at (4.25,-0.5) {$H(a')$};
+\node (B'') at (5.25,0.5) {$H(c)$};
+\node (C'') at (6.25,0.5) {$H(b)$};
+\node (C''') at (6.25,-0.5) {$H(b')$};
+\node (D'') at (5.25,-0.5) {$H(c')$};
+\node (E'') at (8,0.5) {$\theta_c E(d) \phi \in F'(H(c))$};
+\node (F'') at (8,-0.5) {$\theta_{c'} E(d') \phi \in F'(H(c'))$};
+\node (G'') at (5.25,-1) {$E(\tau) \maps F'(H(h))(\theta_c E(d)\phi) \to (\theta_{c'}E(d')\phi)$};
+\node (H) at (3.5,0) {$\mapsto$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$$} (B)
+(C) edge node[above]{$$} (B)
+(A) edge node[left]{$f$} (A')
+(C) edge node[right]{$g$} (C')
+(A') edge node {$$} (D)
+(C') edge node {$$} (D)
+(B) edge node [left] {$h$} (D)
+(A'') edge node[above]{$$} (B'')
+(C'') edge node[above]{$$} (B'')
+(A'') edge node[left]{$H(f)$} (A''')
+(C'') edge node[right]{$H(g)$} (C''')
+(A''') edge node {$$} (D'')
+(C''') edge node {$$} (D'')
+(B'') edge node [left] {$H(h)$} (D'');
+\end{tikzpicture}
+\]
+where $E \maps \Cat \to \Cat$ is a symmetric lax monoidal pseudofuctor such that the following diagram commutes up to isomorphism $\theta \maps EF \Rightarrow F'H$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$\A$};
+\node (B) at (1,0) {$\Cat$};
+\node (C) at (0,-1) {$\mathsf{A'}$};
+\node (D) at (1,-1) {$\Cat$};
+\node (E) at (0.5,-0.5) {$\Swarrow \theta$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$F$} (B)
+(A) edge node[left]{$H$} (C)
+(B) edge node[right]{$E$} (D)
+(C) edge node[above]{$F'$} (D);
+\end{tikzpicture}
+\]
+
+\begin{comment}
+Recall that we can think of the object $d \in F(c)$ as a morphism $d \maps 1 \to F(c)$ and the functor $\tau \maps F(h)(d) \to d'$ of $F(c')$ as a natural transformation  in $\Cat$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,-0.5) {$1$};
+\node (B) at (1,0) {$F(c)$};
+\node (D) at (1,-1) {$F(c')$};
+\node (C) at (0.75,-0.5) {$\Swarrow \tau$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$d$} (B)
+(A) edge node[below]{$d'$} (D)
+(B) edge node[right]{$F(h)$} (D);
+\end{tikzpicture}
+\]
+Applying the symmetric lax monoidal pseudofunctor $E \maps \Cat \to \Cat$ to this diagram yields:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,-0.5) {$1 \xrightarrow{\phi} E(1)$};
+\node (B) at (2,0) {$E(F(c))$};
+\node (D) at (2,-1) {$E(F(c'))$};
+\node (C) at (1.5,-0.5) {$\Swarrow E(\tau)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$E(d)$} (B)
+(A) edge node[below]{$E(d')$} (D)
+(B) edge node[right]{$E(F(h))$} (D);
+\end{tikzpicture}
+\]
+Then because the above square commutes up to the isomorphism $\theta \maps EF \Rightarrow F'H$, we get:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,-0.5) {$1 \xrightarrow{\phi} E(1)$};
+\node (B) at (2,0) {$E(F(c))$};
+\node (D) at (2,-1) {$E(F(c'))$};
+\node (C) at (1.5,-0.5) {$\Swarrow E(\tau)$};
+\node (E) at (4,0) {$F'(H(c))$};
+\node (F) at (4,-1) {$F'(H(c'))$};
+\path[->,font=\scriptsize,>=angle 90]
+(B) edge node [above] {$\theta_c$} (E)
+(D) edge node [above] {$\theta_{c'}$} (F)
+(E) edge node [right] {$F'(H(h))$} (F)
+(A) edge node[above]{$E(d)$} (B)
+(A) edge node[below]{$E(d')$} (D)
+(B) edge node[right]{$E(F((h))$} (D);
+\end{tikzpicture}
+\]
+which results in a 2-morphism $E(\tau) \maps F'(H(h))(\theta_c E(d)\phi) \to (\theta_{c'} E(d')\phi)$ in $F'(H(c'))$.
+To check that the above recipe is functorial, given two vertically composable 2-morphisms in $F\lCsp$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0.5) {$a$};
+\node (A') at (0,-0.5) {$a'$};
+\node (B) at (1.5,0.5) {$c$};
+\node (C) at (3,0.5) {$b$};
+\node (C') at (3,-0.5) {$b'$};
+\node (D) at (1.5,-0.5) {$c'$};
+\node (E) at (4.5,0.5) {$d \in F(c)$};
+\node (F) at (4.5,-0.5) {$d' \in F(c')$};
+\node (G) at (1.5,-1) {$\tau \maps F(h)(d) \to d'$};
+\node (A'') at (0,-1.5) {$a'$};
+\node (A''') at (0,-2.5) {$a''$};
+\node (B'') at (1.5,-1.5) {$c'$};
+\node (C'') at (3,-1.5) {$b'$};
+\node (C''') at (3,-2.5) {$b''$};
+\node (D'') at (1.5,-2.5) {$c''$};
+\node (E'') at (4.5,-1.5) {$d' \in F(c')$};
+\node (F'') at (4.5,-2.5) {$d'' \in F(c'')$};
+\node (G'') at (1.5,-3) {$\tau' \maps F(h')(d') \to d''$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$$} (B)
+(C) edge node[above]{$$} (B)
+(A) edge node[left]{$f$} (A')
+(C) edge node[right]{$g$} (C')
+(A') edge node [above]{$$} (D)
+(C') edge node [above]{$$} (D)
+(B) edge node [left] {$h$} (D)
+(A'') edge node[above]{$$} (B'')
+(C'') edge node[above]{$$} (B'')
+(A'') edge node[left]{$f'$} (A''')
+(C'') edge node[right]{$g'$} (C''')
+(A''') edge node [above]{$$} (D'')
+(C''') edge node [above]{$$} (D'')
+(B'') edge node [left] {$h'$} (D'');
+\end{tikzpicture}
+\]
+if we first compose these, the result is:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0.5) {$a$};
+\node (A') at (0,-0.5) {$a''$};
+\node (B) at (1.5,0.5) {$c$};
+\node (C) at (3,0.5) {$b$};
+\node (C') at (3,-0.5) {$b''$};
+\node (D) at (1.5,-0.5) {$c''$};
+\node (E) at (4.5,0.5) {$d \in F(c)$};
+\node (F) at (4.5,-0.5) {$d'' \in F(c'')$};
+\node (G) at (1.5,-1) {$\tau ' \tau \maps F(h' h)(d) \to d''$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$$} (B)
+(C) edge node[above]{$$} (B)
+(A) edge node[left]{$f' f$} (A')
+(C) edge node[right]{$g' g$} (C')
+(A') edge node [above]{$$} (D)
+(C') edge node [above]{$$} (D)
+(B) edge node [left] {$h' h$} (D);
+\end{tikzpicture}
+\]
+and then the image of this 2-morphism under the double functor $\mathbb{H}$ is given by:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0.5) {$H(a)$};
+\node (A') at (0,-0.5) {$H(a'')$};
+\node (B) at (1.5,0.5) {$H(c)$};
+\node (C) at (3,0.5) {$H(b)$};
+\node (C') at (3,-0.5) {$H(b'')$};
+\node (D) at (1.5,-0.5) {$H(c'')$};
+\node (E) at (5,0.5) {$\theta_c E(d) \phi \in F'(H(c))$};
+\node (F) at (5,-0.5) {$\theta_{c''} E(d'') \phi \in F'(H(c''))$};
+\node (G) at (1.5,-1) {$E(\tau ' \tau) \maps F'(H(h' h))(\theta_c E(d)\phi) \to (\theta_{c''}E(d'')\phi).$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$$} (B)
+(C) edge node[above]{$$} (B)
+(A) edge node[left]{$H(f' f)$} (A')
+(C) edge node[right]{$H(g' g)$} (C')
+(A') edge node [above]{$$} (D)
+(C') edge node [above]{$$} (D)
+(B) edge node [left] {$H(h' h)$} (D);
+\end{tikzpicture}
+\]
+On the other hand, applying the double functor $\mathbb{H}$ first gives:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0.5) {$H(a)$};
+\node (A') at (0,-0.5) {$H(a')$};
+\node (B) at (1.5,0.5) {$H(c)$};
+\node (C) at (3,0.5) {$H(b)$};
+\node (C') at (3,-0.5) {$H(b')$};
+\node (D) at (1.5,-0.5) {$H(c')$};
+\node (E) at (5,0.5) {$\theta_c E(d) \phi \in F'(H(c))$};
+\node (F) at (5,-0.5) {$\theta_{c'} E(d') \phi \in F'(H(c'))$};
+\node (G) at (1.5,-1) {$E(\tau) \maps F'(H(h))(\theta_c E(d)\phi) \to (\theta_{c'} E(d')\phi)$};
+\node (A'') at (0,-1.5) {$H(a')$};
+\node (A''') at (0,-2.5) {$H(a'')$};
+\node (B'') at (1.5,-1.5) {$H(c')$};
+\node (C'') at (3,-1.5) {$H(b')$};
+\node (C''') at (3,-2.5) {$H(b'')$};
+\node (D'') at (1.5,-2.5) {$H(c'')$};
+\node (E'') at (5,-1.5) {$\theta_{c'} E(d') \phi \in F'(H(c'))$};
+\node (F'') at (5,-2.5) {$\theta_{c''} E(d'') \phi \in F'(H(c''))$};
+\node (G'') at (1.5,-3) {$E(\tau') \maps F'(H(h'))(\theta_{c'} E(d')\phi) \to (\theta_{c''}E(d'')\phi)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$$} (B)
+(C) edge node[above]{$$} (B)
+(A) edge node[left]{$H(f)$} (A')
+(C) edge node[right]{$H(g)$} (C')
+(A') edge node [above]{$$} (D)
+(C') edge node [above]{$$} (D)
+(B) edge node [left] {$H(h)$} (D)
+(A'') edge node[above]{$$} (B'')
+(C'') edge node[above]{$$} (B'')
+(A'') edge node[left]{$H(f')$} (A''')
+(C'') edge node[right]{$H(g')$} (C''')
+(A''') edge node [above]{$$} (D'')
+(C''') edge node [above]{$$} (D'')
+(B'') edge node [left] {$H(h')$} (D'');
+\end{tikzpicture}
+\]
+and then composing these gives:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0.5) {$H(a)$};
+\node (A') at (0,-0.5) {$H(a'')$};
+\node (B) at (1.5,0.5) {$H(c)$};
+\node (C) at (3,0.5) {$H(b)$};
+\node (C') at (3,-0.5) {$H(b'')$};
+\node (D) at (1.5,-0.5) {$H(c'')$};
+\node (E) at (5,0.5) {$\theta_c E(d) \phi \in F'(H(c))$};
+\node (F) at (5,-0.5) {$\theta_{c''} E(d'') \phi \in F'(H(c''))$};
+\node (G) at (1.5,-1) {$E(\tau ' \tau) \maps F'(H(h' h))(\theta_c E(d)\phi) \to (\theta_{c''}E(d'')\phi).$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$$} (B)
+(C) edge node[above]{$$} (B)
+(A) edge node[left]{$H(f' f)$} (A')
+(C) edge node[right]{$H(g' g)$} (C')
+(A') edge node [above]{$$} (D)
+(C') edge node [above]{$$} (D)
+(B) edge node [left] {$H(h' h)$} (D);
+\end{tikzpicture}
+\]
+This double functor $\mathbb{H}$ satisfies the equations $S \mathbb{H}_1 = HS$ and $T \mathbb{H}_1=HT$.
+
+Given two composable horizontal 1-cells $M$ and $N$ in $F\lCsp$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$a_1$};
+\node (B) at (1,0) {$c_1$};
+\node (C) at (2,0) {$b$};
+\node (D) at (1,-0.5) {$d_M \in F(c_1)$};
+\node (E) at (3,0) {$b$};
+\node (F) at (4,0) {$c_2$};
+\node (G) at (5,0) {$a_2$};
+\node (H) at (4,-0.5) {$d_N \in F(c_2)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i_1$} (B)
+(C) edge node[above]{$o_1$} (B)
+(E) edge node[above]{$i_2$} (F)
+(G) edge node[above]{$o_2$} (F);
+\end{tikzpicture}
+\]
+composing first gives $M \odot N$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$a_1$};
+\node (B) at (1.5,0) {$c_1+_b c_2$};
+\node (C) at (3,0) {$a_2$};
+\node (D) at (1.5,-0.5) {$d_{M \odot N} \in F(c_1 +_b c_2)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$\psi j_{c_1} i_1$} (B)
+(C) edge node[above]{$\psi j_{c_2} o_2$} (B);
+\end{tikzpicture}
+\]
+where $$d \maps 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{d_1 \times d_2} F(c_1) \times F(c_2) \xrightarrow{\phi_{c_1,c_2}} F(c_1+c_2) \xrightarrow{F(j)}F(c_1 +_b c_2).$$ The image of this horizontal 1-cell is then given by $\mathbb{H}(M \odot N)$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$H(a_1)$};
+\node (B) at (2,0) {$H(c_1+_b c_2)$};
+\node (C) at (4,0) {$H(a_2)$};
+\node (D) at (2,-0.5) {$\mathbb{H}(M \odot N) = \theta_{c_1 +_b c_2}E(d_{M \odot N}) \phi \in F'(H(c_1 +_b c_2))$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$H(\psi j_{c_1} i_1)$} (B)
+(C) edge node[above]{$H(\psi j_{c_2} o_2)$} (B);
+\end{tikzpicture}
+\]
+where $$\mathbb{H}(M \odot N) = \theta_{c_1 +_b c_2} E(d_{M \odot N}) \phi \maps 1 \xrightarrow{\phi} E(1) \xrightarrow{E(d)} E(F(c_1 +_b c_2)) \xrightarrow{\theta_{c_1 +_b c_2}} F'(H(c_1 +_b c_2)).$$ On the other hand, the image of each horizontal 1-cell under the double functor $\mathbb{H}$ is given respectively by $\mathbb{H}(M)$ and $\mathbb{H}(N)$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$H(a_1)$};
+\node (B) at (1,0) {$H(c_1)$};
+\node (C) at (2,0) {$H(b)$};
+\node (D) at (1,-0.5) {$\theta_{c_1} E(d_M)\phi \in F'(H(c_1))$};
+\node (E) at (3,0) {$H(b)$};
+\node (F) at (4,0) {$H(c_2)$};
+\node (G) at (5,0) {$H(a_2)$};
+\node (H) at (4,-0.5) {$\theta_{c_2} E(d_N) \phi \in F'(H(c_2))$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$H(i_1)$} (B)
+(C) edge node[above]{$H(o_1)$} (B)
+(E) edge node[above]{$H(i_2)$} (F)
+(G) edge node[above]{$H(o_2)$} (F);
+\end{tikzpicture}
+\]
+Composing these then gives $\mathbb{H}(M) \odot \mathbb{H}(N)$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$H(a_1)$};
+\node (B) at (2.25,0) {$H(c_1)+_{H(b)} H(c_2)$};
+\node (C) at (4.5,0) {$H(a_2)$};
+\node (D) at (2.25,-0.5) {$d_{\mathbb{H}(M) \odot \mathbb{H}(N)} \in F'(H(c_1) +_{H(b)} H(c_2))$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$\Psi j_{H(c_1)} H(i_1)$} (B)
+(C) edge node[above]{$\Psi j_{H(c_2)} H(o_2)$} (B);
+\end{tikzpicture}
+\]
+where $$\hspace{-.4in}\scriptstyle{d_{\mathbb{H}(M) \odot \mathbb{H}(N)} \maps 1 \xrightarrow{(\theta_{c_1} \times \theta_{c_2})(E(d_M) \times E(d_N)) \phi} F'(H(c_1)) \times F'(H(c_2)) \xrightarrow{\Phi_{H(c_1),H(c_2)}} F'(H(c_1)+ H(c_2)) \xrightarrow{F' (J)} F'(H(c_1) +_{H(b)} H(c_2)).}$$
+We then have a comparison constraint: $$\mathbb{H}_{M,N} \maps \mathbb{H}(M) \odot \mathbb{H}(N) \xrightarrow{\sim} \mathbb{H}(M \odot N)$$given by the globular 2-isomorphism:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0.5) {$H(a_1)$};
+\node (A') at (0,-0.5) {$H(a_1)$};
+\node (B) at (2.5,0.5) {$H(c_1)+_{H(b)} H(c_2)$};
+\node (C) at (5,0.5) {$H(a_2)$};
+\node (C') at (5,-0.5) {$H(a_2)$};
+\node (D) at (2.5,-0.5) {$H(c_1 +_b c_2)$};
+\node (E) at (7.5,0.5) {$d_{\mathbb{H}(M) \odot \mathbb{H}(N)} \in F'(H(c_1)+_{H(b_1)}H(c_2))$};
+\node (F) at (7.5,-0.5) {$d_{\mathbb{H}(M \odot N)} \in F'(H(c_1 +_b c_2))$};
+\node (G) at (2.5,-1) {$\tau_{\kappa^{-1}} \maps F'(\kappa^{-1})(d_{\mathbb{H}(M) \odot \mathbb{H}(N)}) \to d_{\mathbb{H}(M \odot N)}.$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$\Psi j_{H(c_1)} H(i_1)$} (B)
+(C) edge node[above]{$\Psi j_{H(c_2)} H(o_2)$} (B)
+(A) edge node[left]{$1$} (A')
+(C) edge node[right]{$1$} (C')
+(A') edge node [above]{$H(\psi j_{c_1} i_1)$} (D)
+(C') edge node [above]{$H(\psi j_{c_2} o_2)$} (D)
+(B) edge node [left] {$\kappa^{-1}$} (D);
+\end{tikzpicture}
+\]
+where $\kappa$ is the isomorphism $$\kappa \maps H(c_1 +_b c_2) \xrightarrow{\sim} H(c_1) +_{H(b)} H(c_2)$$ which comes from the finite colimit preserving functor $H \maps \A \to \mathsf{A'}$.
+The above diagram commutes by a similar argument to the one used in \cref{thm:equiv}.
+Similarly, for every object $c \in \A$, we have a unit comparison constraint $$\mathbb{H}_U \maps U_{\mathbb{H}(c)} \to \mathbb{H}(U_c)$$ given by the globular 2-isomorphism:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0.5) {$H(c)$};
+\node (A') at (0,-0.5) {$H(c)$};
+\node (B) at (1.5,0.5) {$H(c)$};
+\node (C) at (3,0.5) {$H(c)$};
+\node (C') at (3,-0.5) {$H(c)$};
+\node (D) at (1.5,-0.5) {$H(c)$};
+\node (E) at (4.5,0.5) {$!_{H(c)} \in F'(H(c))$};
+\node (F) at (4.5,-0.5) {$\theta_c E(!_c) \phi \in F'(H(c))$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$1$} (B)
+(C) edge node[above]{$1$} (B)
+(A) edge node[left]{$1$} (A')
+(C) edge node[right]{$1$} (C')
+(A') edge node [above]{$1$} (D)
+(C') edge node [above]{$1$} (D)
+(B) edge node [left] {$1$} (D);
+\end{tikzpicture}
+\]
+where the morphism of decorations is the morphism $\tau \maps !_{H(c)} \to (\theta_c E(!_c) \phi)$ in $F'(H(c))$.
+These comparison constrains satisfy the coherence axioms of a monoidal category, namely:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0.5) {$(\mathbb{H}(M) \odot \mathbb{H}(N)) \odot \mathbb{H}(P)$};
+\node (B) at (0,-0.5) {$\mathbb{H}(M \odot N) \odot \mathbb{H}(P)$};
+\node (C) at (0,-1.5) {$\mathbb{H}((M \odot N) \odot P)$};
+\node (A') at (3,0.5) {$\mathbb{H}(M) \odot (\mathbb{H}(N) \odot \mathbb{H}(P))$};
+\node (B') at (3,-0.5) {$\mathbb{H}(M) \odot \mathbb{H}(N \odot P)$};
+\node (C') at (3,-1.5) {$\mathbb{H}(M \odot (N \odot P))$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[left]{$\mathbb{H}_{M,N} \odot 1$} (B)
+(B) edge node[left]{$\mathbb{H}_{M \odot N,P}$} (C)
+(A) edge node[above]{$a$} (A')
+(C) edge node [above] {$\mathbb{H}(a')$} (C')
+(B') edge node [right] {$\mathbb{H}_{M,N \odot P}$} (C')
+(A') edge node [right]{$1 \odot \mathbb{H}_{N,P}$} (B');
+\end{tikzpicture}
+\]
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$U_{\mathbb{H}(a)} \odot \mathbb{H}(M)$};
+\node (B) at (2.5,0) {$\mathbb{H}(U_a) \odot \mathbb{H}(M)$};
+\node (C) at (0,-1) {$\mathbb{H}(M)$};
+\node (D) at (2.5,-1) {$\mathbb{H}(U_a \odot M)$};
+\node (A') at (5,0) {$\mathbb{H}(M) \odot U_{\mathbb{H}(b)}$};
+\node (B') at (7.5,0) {$\mathbb{H}(M) \odot \mathbb{H}(U_b)$};
+\node (C') at (5,-1) {$\mathbb{H}(M)$};
+\node (D') at (7.5,-1) {$\mathbb{H}(M \odot U_b)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$\mathbb{H}_U \odot 1$} (B)
+(A) edge node[left]{$\lambda$} (C)
+(B) edge node[right]{$\mathbb{H}_{U_a,M}$} (D)
+(D) edge node[above]{$\mathbb{H}(\lambda')$} (C)
+(A') edge node[above]{$1 \odot \mathbb{H}_U$} (B')
+(A') edge node[left]{$\rho$} (C')
+(B') edge node[right]{$\mathbb{H}_{M,U_b}$} (D')
+(D') edge node[above]{$\mathbb{H}(\rho')$} (C');
+\end{tikzpicture}
+\]
+The diagrams involving the morphisms of decorations are similar to those in Theorem \cref{DC}.
+This shows that $\mathbb{H}=(H,E,\theta)$ is a double functor.
+Next we show that this double functor is symmetric monoidal.
+First, that the object component $\mathbb{H}_0=H$ is symmetric monoidal is clear as $H \maps \A \to \A'$ preserves finite colimits.
+As for the arrow component $\mathbb{H}_1$, given two horizontal 1-cells $M_1$ and $M_2$ in $F\lCsp$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$a_1$};
+\node (B) at (1,0) {$c_1$};
+\node (C) at (2,0) {$b_1$};
+\node (D) at (1,-0.5) {$d_{M_1}\in F(c_1)$};
+\node (E) at (3,0) {$a_2$};
+\node (F) at (4,0) {$c_2$};
+\node (G) at (5,0) {$b_2$};
+\node (H) at (4,-0.5) {$d_{M_2} \in F(c_2)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i_1$} (B)
+(C) edge node[above]{$o_1$} (B)
+(E) edge node[above]{$i_2$} (F)
+(G) edge node[above]{$o_2$} (F);
+\end{tikzpicture}
+\]
+their tensor product $M_1 \otimes M_2$ in $F\lCsp$ is given by:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$a_1+a_2$};
+\node (B) at (1.5,0) {$c_1+c_2$};
+\node (C) at (3,0) {$b_1+b_2$};
+\node (D) at (1.5,-0.5) {$d_{M_1 \otimes M_2} \in F(c_1+c_2)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i_1+i_2$} (B)
+(C) edge node[above]{$o_1+o_2$} (B);
+\end{tikzpicture}
+\]
+$$d_{M_1 \otimes M_2} \maps 1 \xrightarrow{d_1 \times d_2} F(c_1) \times F(c_2) \xrightarrow{\phi_{c_1,c_2}} F(c_1+c_2)$$
+and the image of this horizontal 1-cell under the double functor $\mathbb{H}$ is $\mathbb{H}(M_1 \otimes M_2)$ given by:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$H(a_1+a_2)$};
+\node (B) at (2,0) {$H(c_1+c_2)$};
+\node (C) at (4,0) {$H(b_1+b_2)$};
+\node (D) at (2,-0.5) {$d_{\mathbb{H}(M_1 \otimes M_2)} = \theta_{c_1+c_2} E(d_{M_1 \otimes M_2})\phi \in F'(H(c_1+c_2))$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$H(i_1+i_2)$} (B)
+(C) edge node[above]{$H(o_1+o_2)$} (B);
+\end{tikzpicture}
+\]
+On the other hand, the image of $M_1$ and $M_2$ is given by $\mathbb{H}(M_1)$ and $\mathbb{H}(M_2)$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$H(a_1)$};
+\node (B) at (1.5,0) {$H(c_1)$};
+\node (C) at (3,0) {$H(b_1)$};
+\node (D) at (1.5,-0.5) {$d_{\mathbb{H}(M_1)} = \theta_{c_1}E(d_{M_1})\phi \in F'(H(c_1))$};
+\node (E) at (4.5,0) {$H(a_2)$};
+\node (F) at (6,0) {$H(c_2)$};
+\node (G) at (7.5,0) {$H(b_2)$};
+\node (H) at (6,-0.5) {$d_{\mathbb{H}(M_2)} = \theta_{c_2}E(d_{M_2})\phi \in F'(H(c_2))$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$H(i_1)$} (B)
+(C) edge node[above]{$H(o_1)$} (B)
+(E) edge node[above]{$H(i_2)$} (F)
+(G) edge node[above]{$H(o_2)$} (F);
+\end{tikzpicture}
+\]
+and their tensor product $\mathbb{H}(M_1) \otimes \mathbb{H}(M_2)$ is given by:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$H(a_1)+H(a_2)$};
+\node (B) at (2.5,0) {$H(c_1)+H(c_2)$};
+\node (C) at (5,0) {$H(b_1)+H(b_2)$};
+\node (D) at (2.5,-0.5) {$d_{\mathbb{H}(M_1) \otimes \mathbb{H}(M_2)} \in F'(H(c_1)+H(c_2))$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$H(i_1)+H(i_2)$} (B)
+(C) edge node[above]{$H(o_1)+H(o_2)$} (B);
+\end{tikzpicture}
+\]
+$$\hspace{-.4in} \scriptstyle{d_{\mathbb{H}(M_1) \otimes \mathbb{H}(M_2)} \maps 1 \xrightarrow{(\phi \times \phi)(\lambda^{-1} \times \lambda^{-1})} E(1) \times E(1) \xrightarrow{(\theta_{c_1} \times \theta_{c_2})(E(d_{M_1}) \times E(d_{M_2}))} F'(H(c_1)) \times F'(H(c_2)) \xrightarrow{\Phi_{H(c_1),H(c_2)}} F' (H(c_1)+H(c_2)).}$$  We then have a natural 2-isomorphism $\mu_{M_1,M_2} \maps \mathbb{H}(M_1) \otimes \mathbb{H}(M_2) \to \mathbb{H}(M_1 \otimes M_2)$ in $F'\lCsp$ given by:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0.5) {$H(a_1)+H(a_2)$};
+\node (A') at (0,-0.5) {$H(a_1+a_2)$};
+\node (B) at (2.5,0.5) {$H(c_1)+H(c_2)$};
+\node (C) at (5,0.5) {$H(b_1)+H(b_2)$};
+\node (C') at (5,-0.5) {$H(b_1+b_2)$};
+\node (D) at (2.5,-0.5) {$H(c_1+c_2)$};
+\node (E) at (2.5,1) {$d_{\mathbb{H}(M_1) \otimes \mathbb{H}(M_2)} \in F'(H(c_1)+H(c_2))$};
+\node (F) at (2.5,-1) {$d_{\mathbb{H}(M_1 \otimes M_2)} \in F'(H(c_1+c_2))$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$H(i_1)+H(i_2)$} (B)
+(C) edge node[above]{$H(o_1)+H(o_2)$} (B)
+(A) edge node[left]{$\kappa$} (A')
+(C) edge node[left]{$\kappa$} (C')
+(A') edge node [above]{$H(i_1+i_2)$} (D)
+(C') edge node [above]{$H(o_1+o_2)$} (D)
+(B) edge node [left] {$\kappa$} (D);
+\end{tikzpicture}
+\]
+$$\tau_\kappa \maps F'(\kappa)(d_{\mathbb{H}(M_1) \otimes \mathbb{H}(M_2)}) \to d_{\mathbb{H}(M_1 \otimes M_2)}$$
+where $\kappa$ denotes the isomorphism arising from $H$ preserving finite colimits.
+This natural 2-isomorphism together with the associators of $F\lCsp$ and $F'\lCsp$, respectively $\alpha$ and $\alpha'$, make the following diagram commute:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0.5) {$(\mathbb{H}(M_1) \otimes \mathbb{H}(M_2)) \otimes \mathbb{H}(M_3)$};
+\node (B) at (0,-0.5) {$\mathbb{H}(M_1 \otimes M_2) \otimes \mathbb{H}(M_3)$};
+\node (C) at (0,-1.5) {$\mathbb{H}((M_1 \otimes M_2) \otimes M_3)$};
+\node (A') at (4,0.5) {$\mathbb{H}(M_1) \otimes (\mathbb{H}(M_2) \otimes \mathbb{H}(M_3))$};
+\node (B') at (4,-0.5) {$\mathbb{H}(M_1) \otimes \mathbb{H}(M_2 \otimes M_3)$};
+\node (C') at (4,-1.5) {$\mathbb{H}(M_1 \otimes (M_2 \otimes M_3))$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[left]{$\mu_{M_1,M_2} \otimes 1$} (B)
+(B) edge node[left]{$\mu_{M_1 \otimes M_2,M_3}$} (C)
+(A) edge node[above]{$\alpha'$} (A')
+(C) edge node [above] {$\mathbb{H}(\alpha)$} (C')
+(B') edge node [right] {$\mu_{M_1,M_2 \otimes M_3}$} (C')
+(A') edge node [right]{$1 \otimes \mu_{M_2 \otimes M_3}$} (B');
+\end{tikzpicture}
+\]
+with the corresponding diagram of decorations in $F'(H(c_1+(c_2+c_3)))$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0.5) {$F'(\alpha \kappa \kappa)(d_{(\mathbb{H}(M_1) \otimes \mathbb{H}(M_2)) \otimes \mathbb{H}(M_3)})$};
+\node (B) at (0,-0.5) {$F'(\alpha \kappa)(d_{\mathbb{H}(M_1 \otimes M_2) \otimes \mathbb{H}(M_3)})$};
+\node (C) at (0,-1.5) {$F'(\alpha)(d_{\mathbb{H}((M_1 \otimes M_2) \otimes M_3)})$};
+\node (A') at (5,0.5) {$F'(\kappa \kappa)(d_{\mathbb{H}(M_1) \otimes (\mathbb{H}(M_2) \otimes \mathbb{H}(M_3))})$};
+\node (B') at (5,-0.5) {$F'(\kappa)(d_{\mathbb{H}(M_1) \otimes \mathbb{H}(M_2 \otimes M_3)})$};
+\node (C') at (5,-1.5) {$d_{\mathbb{H}(M_1 \otimes (M_2 \otimes M_3))}$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[left]{$F'(\alpha \kappa)(\tau_\kappa + 1)$} (B)
+(B) edge node[left]{$F'(\alpha)(\tau_\kappa)$} (C)
+(A) edge node[above]{$F'(\kappa \kappa)(\tau_{\alpha'})$} (A')
+(C) edge node [above] {$\tau_\alpha$} (C')
+(B') edge node [right] {$\tau_\kappa$} (C')
+(A') edge node [right]{$F'(\kappa)(1+\tau_\kappa)$} (B');
+\end{tikzpicture}
+\]
+where $$F'(\alpha \kappa \kappa)(d_{(\mathbb{H}(M_1) \otimes \mathbb{H}(M_2)) \otimes \mathbb{H}(M_3)}) = F'(\kappa \kappa \alpha')(d_{(\mathbb{H}(M_1) \otimes \mathbb{H}(M_2)) \otimes \mathbb{H}(M_3)})$$
+as the corresponding hexagon for the finite colimit preserving functor $H \maps \A \to \mathsf{A'}$ commutes.
+The map $\mu_{M_1,M_2}$ is also compatible with the braidings $\beta$ and $\beta'$ of $F \lCsp_1$ and $F' \lCsp_1$, respectively, and make the necessary square commute as a consequence of the corresponding commutative square involving braidings from the finite colimit preserving functor $H \maps \A \to \mathsf{A'}$.
+
+We also have that the monoidal unit of $F\lCsp_1$ is given by:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$1_\A$};
+\node (B) at (1,0) {$1_\A$};
+\node (C) at (2,0) {$1_\A$};
+\node (D) at (1,-0.5) {$!_{1_\A} \in F(1_\A)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$1$} (B)
+(C) edge node[above]{$1$} (B);
+\end{tikzpicture}
+\]
+where $1_\A$ is the monoidal unit of the cocartesian category $\A$. The image of this horizontal 1-cell under $\mathbb{H}$ is given by:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$H(1_\A)$};
+\node (B) at (1,0) {$H(1_\A)$};
+\node (C) at (2,0) {$H(1_\A)$};
+%\node (E) at (3,0) {$=$};
+%\node (F) at (4,0) {$1_\mathsf{A'}$};
+%\node (G) at (5,0) {$1_\mathsf{A'}$};
+%\node (H) at (6,0) {$1_\mathsf{A'}$};
+%\node (I) at (5,-0.5) {$!_{1_{\mathsf{A'}}} \in F'(1_{\mathsf{A'}})$};
+\node (D) at (1,-0.5) {$\theta_{1_\A}E(!_{1_\A}) \phi \in F'(H(1_\A))$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$1$} (B)
+(C) edge node[above]{$1$} (B);
+%(F) edge node[above]{$1$} (G)
+%(H) edge node[above]{$1$} (G);
+\end{tikzpicture}
+\]
+as $H$ preserves finite colimits. We then have a 2-isomorphism in $F'\lCsp$ given by: $$\mu \maps 1_{F'\lCsp_1} \to \mathbb{H}(1_{F\lCsp_1})$$ 
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0.5) {$1_{\mathsf{A'}}$};
+\node (A') at (0,-0.5) {$H(1_\A)$};
+\node (B) at (1.5,0.5) {$1_{\mathsf{A'}}$};
+\node (C) at (3,0.5) {$1_{\mathsf{A'}}$};
+\node (C') at (3,-0.5) {$H(1_\A)$};
+\node (D) at (1.5,-0.5) {$H(1_\A)$};
+\node (E) at (5,0.5) {$!_{1_\mathsf{A'}} \in F'(1_\mathsf{A'})$};
+\node (F) at (5,-0.5) {$\theta_{1_\A} E(!_{1_\A}) \phi \in F'(H(1_\A))$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$1$} (B)
+(C) edge node[above]{$1$} (B)
+(A) edge node[left]{$\kappa$} (A')
+(C) edge node[right]{$\kappa$} (C')
+(A') edge node [above]{$1$} (D)
+(C') edge node [above]{$1$} (D)
+(B) edge node [left] {$\kappa$} (D);
+\end{tikzpicture}
+\]
+together with the morphism $\tau_\mu \maps F'(\kappa)(!_{1_\mathsf{A'}}) \to (\theta_{1_\A} E(!_{1_\A})\phi)$ in $F'(H(1_\A))$.
+The following square then commutes for any horizontal 1-cell $M$ of $F \lCsp$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$1_\mathsf{A'} \otimes \mathbb{H}(M)$};
+\node (B) at (2.5,0) {$\mathbb{H}(1_\A) \otimes \mathbb{H}(M)$};
+\node (C) at (0,-1) {$\mathbb{H}(M)$};
+\node (D) at (2.5,-1) {$\mathbb{H}(1_\A \otimes M)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$\mu \otimes 1$} (B)
+(A) edge node[left]{$\ell$} (C)
+(B) edge node[right]{$\mu_{1_\mathrm{A},M}$} (D)
+(D) edge node[above]{$\mathbb{H}(\ell')$} (C);
+\end{tikzpicture}
+\]
+where we have abbreviated the monoidal units of $F\lCsp_1$ and $F'\lCsp_1$ as $1_\A$ and $1_\mathsf{A'}$, respectively. The diagram of corresponding decorations is given by:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0.5) {$F'(\ell)(d_{!_{1_\mathsf{A'}}} \otimes d_{\mathbb{H}(M)})$};
+\node (B) at (0,-0.5) {$d_{\mathbb{H}(M)}$};
+\node (A') at (4,0.5) {$F'(H(\ell') \kappa)(d_{!_{\mathbb{H}(1_\A)}}\otimes d_{\mathbb{H}(M)})$};
+\node (B') at (4,-0.5) {$F'(H(\ell'))(d_{\mathbb{H}(1_\A \otimes M)})$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[left]{$\tau_\ell$} (B)
+(A) edge node[above]{$F'(H(\ell')\kappa)(\tau_{\mu \otimes 1})$} (A')
+(A') edge node [right]{$F'(H(\ell'))(\tau_\kappa)$} (B')
+(B') edge node [above] {$\tau_{H(\ell')}$} (B);
+\end{tikzpicture}
+\]
+where $$F'(\ell)(d_{!_{1_\mathsf{A'}}} \otimes d_{\mathbb{H}(M)})=F'(H(\ell')\kappa(\mu \otimes 1))(d_{!_{1_\mathsf{A'}}} \otimes d_{\mathbb{H}(M)})$$ since the corresponding square involving left unitors for the finite colimit preserving functor $H \maps \A \to \mathsf{A'}$ commutes.
+The other square involving the right unitors $r$ and $r'$ is similar.
+Note that because the comparison constraints $\mu$ and $\mu_{(\_ , \_)}$ are both isomorphisms, the symmetric monoidal double functor $\mathbb{H}$ is strong.
+
+\end{comment}
+
+\begin{thm}
+Given two finitely cocomplete categories $\A$ and $\A'$, two symmetric lax monoidal pseudofunctors $F \maps \A \to \Cat$ and $F' \maps \A' \to \Cat$, a finite colimit preserving functor $H \maps \A \to \A'$, a symmetric lax monoidal pseudofunctor $E \maps \Cat \to \Cat$ and a 2-isomorphism $\theta \maps EF \Rightarrow F' H$ as in the following diagram, the triple $(H,E,\theta)$ induces a symmetric monoidal (strong) double functor $\mathbb{H} \maps F\lCsp \to F'\lCsp$ as defined above.
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$\A$};
+\node (B) at (1,0) {$\Cat$};
+\node (C) at (0,-1) {$\mathsf{A'}$};
+\node (D) at (1,-1) {$\Cat$};
+\node (E) at (0.5,-0.5) {$\Swarrow \theta$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$F$} (B)
+(A) edge node[left]{$H$} (C)
+(B) edge node[right]{$E$} (D)
+(C) edge node[above]{$F'$} (D);
+\end{tikzpicture}
+\]
+\end{thm}
+
+Details of the constructions and the proof of the above theorem can be found at \cite{CourserThesis}.
+
+%\newpage
+%Scratch work for Petri net problem
+%\newline
+%Let $P = (s_1,t_1 \maps T_1 \to \mathbb{N}(S_1))$ and $Q = (s_2,t_2 \maps T_2 \to \mathbb{N}(S_2))$.
+We want to show that the functor $F \maps \textrm{Petri} \to \textrm{CMC}$ preserves pushouts of cospans of the form $$P \xleftarrow{} L(Y) \xrightarrow{} Q$$ meaning that $F(P+_{L(Y)} Q) \cong F(P) +_{F(L(Y))} F(Q)$.
+Here, $L \maps \textrm{Set} \to \textrm{Petri}$ is the left adjoint which sends a set $Y$ to the discrete Petri net with $Y$ as its set of species and no transitions.
+Thus no transitions are identified in the pushout $P+_{L(Y)} Q$, and so the set of transitions of $P+_{L(Y)} Q$ is given by $$\textrm{Trans}(P)+\textrm{Trans}(Q).$$ Thus the morphisms \emph{contributed from transitions} in both $F(P+_{L(Y)}Q)$ and $F(P)+_{F(L(Y)} F(Q)$ are the same.
+If we can show that $$\textrm{Ob}(F(P+_{L(Y)}Q) \cong \textrm{Ob}(F(P)+_{F(L(Y))} F(Q)$$ then the remaining morphisms in each commutative monoidal category will be canonically isomorphic as sets.
+
+%Now, what can we say about $\textrm{Ob}(F(P+_{L(Y)}Q))$ vs.
+$\textrm{Ob}(F(P)+_{F(L(Y))} F(Q))$?
+Well, $\textrm{Ob}(F(P+_{L(Y)}Q)) = \mathbb{N}(S_1+_Y S_2)$ and $\textrm{Ob}(F(P)+_{F(L(Y))} F(Q))= \mathbb{N}(S_1) +_{\mathbb{N}(Y)} \mathbb{N}(S_2)$.
+
+%\newpage
+
+%is given by $$1 \to F(c_1) \times F(c_2) \xrightarrow{} F(c_1 + c_2) \xrightarrow{} F(c_1 + _b c_2)$$ and then applying the functor $E$ results in $1 \to E(F(c_1+_b c_2))$, which by the comutative square is the same as $1 \to F'(H(c_1+_b c_2))$.
+On the other hand, applying the functor $E$ to each decoration results in $$1 \to E(F(c_1)) \times E(F(c_2)) \xrightarrow{} E(F(c_1) \times F(c_2)) \xrightarrow{} E(F(c_1+c_2)) \xrightarrow E(F(c_1+_b c_2)) \xrightarrow{} F'(H(c_1 +_b c_2))$$
+
+\section{Structured versus decorated cospans} \label{EquivDoubleCats}
+
+In \cite{BC2}, the first two authors introduce the symmetric monoidal double category of \emph{structured cospans} as a formalism to capture open networks.
+One of the main goals of this paper is to provide a monoidal double equivalence between this double category and that of \emph{decorated cospans}, described in detail in \cref{DecCospansDoubleCat}.
+We first recall the double category structured cospans form.
+
+\begin{thm}\label{SC}
+Given categories $\X$ and $\A$ with finite colimits and $L \maps \A \to \X$ a finitely cocontinuous functor, there exists a symmetric monoidal double category $_L\lCsp(\X)$ in which
+\begin{itemize}
+\item an object is an object of $\A$,
+\item a vertical morphism is a morphism of $\A$,
+\item a horizontal 1-cell from $a$ to $b$ is a cospan in $\X$ of the form
+\begin{equation}\label{eq:structuredcospan}
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$L(a)$};
+\node (B) at (1,0) {$x$};
+\node (C) at (2,0) {$L(b)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$$} (B)
+(C) edge node[above]{$$} (B);
+\end{tikzpicture}
+\end{equation}
+\item a 2-morphism is a map of cospans in $\X$ of the form
+\begin{equation}\label{eq:2cellsStrCsp}
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$L(a)$};
+\node (B) at (1,0) {$x$};
+\node (C) at (2,0) {$L(b)$};
+\node (A') at (0,-1) {$L(a')$};
+\node (B') at (1,-1) {$x'$};
+\node (C') at (2,-1) {$L(b')$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$$} (B)
+(C) edge node[above]{$$} (B)
+(A') edge node[above]{$$} (B')
+(C') edge node[above]{$$} (B')
+(A) edge node [left]{$L(f)$} (A')
+(B) edge node [left]{$\alpha$} (B')
+(C) edge node [right]{$L(g)$} (C');
+\end{tikzpicture}
+\end{equation}
+\end{itemize}
+The symmetric monoidal structure is formed by using binary coproducts and the initial object.
+\end{thm}
+
+\begin{proof}
+All relevant details can be found in \cite[Theorems~2.3\&3.9]{BC2}.
+In particular, the double category structure only requires that $\X$ have pushouts, since this is how composition is formed.
+Moreover, the symmetric monoidal structure requires that $\X$ also have binary coproducts and an initial object (thus all finite colimits), and that $\A$ have and $L$ preserve finite coproducts, see \cite[Theorem~3.2.3]{CourserThesis}.
+\end{proof}
+
+The following theorem establishes the desired equivalence between these two different double categorical network frameworks of structured and decorated cospans in a formal way.
+We denote by $\bicat{Rex}$ the 2-category of finitely cocomplete categories and finitely cocontinuous functors, and the symmetric monoidal double structure of decorated cospans is worked out in \cref{thm:decorated_cospans,DC}.
+
+\begin{thm} \label{thm:equiv}
+Suppose $\ca{A}$ has finite colimits and $(F,\phi,\phi_0)\maps(\ca{A},+) \to (\bicat{Cat},\times,1)$ is a symmetric lax monoidal pseudofunctor that factors through $\bicat{Rex}$ as an ordinary pseudofunctor.
+Then the symmetric monoidal double category $F\lCsp$ of decorated cospans is equivalent to the symmetric monoidal double category $_L\lCsp(\inta F)$ of structured cospans, where $L \maps \A \to \inta F$ is the left adjoint of the induced Grothendieck opfibration $\U\maps \inta F \to \A$.
+\end{thm}
+
+The conditions of the above theorem relate to the existence of left adjoints for opfibrations; we first sketch this underlying framework, and then we proceed to the proof of the theorem.
+The basics of fibration theory needed for our purposes are recalled in \cref{sec:fibrations}.
+
+In \cite{MV}, the classical Grothendieck construction is generalized to the monoidal setting: lax monoidal structures on a pseudofunctor $F\maps\A\to\bicat{Cat}$ (called \emph{monoidal opindexed categories}) bijectively correspond to monoidal structures on the total category $\inta F$ such that the induced opfibration is a strict monoidal functor and $\otimes_{\inta F}$ preserves cocartesian liftings (called \emph{monoidal fibrations}).
+If the monoidal category $\A$ is in fact cocartesian, there is a further correspondence of the two structures with an ordinary pseudofunctor $F\maps\A\to\bicat{MonCat}$ into the 2-category of monoidal categories, strong monoidal functors and monoidal natural transformations.
+
+\begin{lem}
+ There is a 2-equivalence between the 2-categories of monoidal opfibrations and monoidal opindexed categories.
+If the base is cocartesian monoidal, there is a 2-equivalence between monoidal opfibrations and pseudofunctors into monoidal categories.
+\end{lem}
+
+\begin{proof}
+This was shown by Moeller and the third author \cite[Theorems~3.13\&4.1]{MV}. In summary, we have correspondences
+\begin{gather}
+\textrm{lax monoidal pseudofunctors }F\maps(\A,+)\to(\bicat{Cat},\times) \notag\\
+\Updownarrow \notag\\
+\textrm{monoidal opfibrations }U\maps(\X,\otimes)\to(\A,+) \label{monGroth}\\
+\Updownarrow \notag\\
+\textrm{pseudofunctors }F\maps\A\to\bicat{MonCat} \notag
+\end{gather}
+The second equivalence was also earlier observed by Shulman \cite{Shul2008}.
+In more detail, if $(\mu,\mu_0)$ is the lax monoidal structure of the pseudofunctor $F$ as recalled in \cref{sec:2cats}, each fibre category $\X_a=F(a)$ obtains a monoidal structure via
+\begin{equation}\label{eq:explicitstructure1}
+\otimes_a\maps F(a)\times F(a)\xrightarrow{\mu_{a,a}}F(a+a)\xrightarrow{F(\nabla)}F(a),\quad
+I_a\maps\mathbf{1}\xrightarrow{\mu_0}F(0)\xrightarrow{F(!)}F(a)
+\end{equation}
+where $\nabla$ is the fold map. 
+\end{proof}
+
+These correspondences further restrict to the case when the Grothendieck category is specifically cocartesian monoidal itself. In that case, opfibrations
+$(\X,+)\to(\A,+)$ that strictly preserve chosen coproducts and initial object, and such that $+$ preserves cocartesian liftings, bijectively correspond to pseudofunctors into the 2-category of cocartesian categories; for more details, see \cite[Corollary 4.7]{MV} and the related discussion.
+%!!!
+Christina: someone wrote Rex there, perhaps it was me.
+This is a subcategory, not all finite colimits are there.
+
+{\chris In progress...}
+
+Finally, using the following result we can further restrict to our current case of interest, namely opfibrations that also preserve pushouts, i.e.
+all finite colimits.
+Of course, the following statement is more general since it relates the existence of any class of colimits in the total category of an opfibration to their existence in the fibres; for a more detailed exposition and proof, see \cite{Herm}.
+
+\begin{lem}\label{lem:fibrewiselimits}
+Suppose $\ca{J}$ is a small category and $\U\maps\X\to\A$ is an opfibration. If the base $\A$ has $\ca{J}$-colimits,
+the following are equivalent:
+\begin{enumerate}
+ \item all fibres have $\ca{J}$-colimits, and the reindexing functors preserve them;
+ \item the total $\X$ has $\ca{J}$-colimits, and $\U$ preserves them. %removed strict for now!
+\end{enumerate}
+\end{lem}
+
+The first part formulates the existence of colimits \emph{locally} in each fibre, which can equivalently be expressed by the corresponding pseudofunctor $F\maps\A\to\bicat{Cat}$ landing on the sub-2-category $\bicat{Rex}$ of finitely cocomplete categories and functors that preserve colimits.
+The second part formulates the existence of colimits \emph{globally} in the total category $\inta F$.
+Combining these, we can deduce the following.
+
+\begin{cor}\label{cor:fcocMonGroth}
+ Suppose $\A$ is a finitely cocomplete category and $F\maps(\A,+)\to(\bicat{Cat},\times)$ is a lax monoidal pseudofunctor. If its corresponding pseudofunctor $\A\to\bicat{MonCat}$ via \cref{monGroth} 
+ factors through $\bicat{Rex}$, then the Grothendieck category $\inta F$ has all finite colimits and the induced opfibration $\U_F\maps\inta F\to\A$ preserves them. 
+\end{cor}
+
+On a different but related subject, for our purposes we are interested in the existence of a left adjoint $L_F$ to the induced monoidal opfibration $ \inta{F} \to \A$ by the Grothendieck construction as discussed above.
+The following result provides sufficient conditions for that, which go hand-in-hand with \cref{cor:fcocMonGroth} and \cref{lem:fibrewiselimits}.
+
+\begin{prop}\cite[Proposition~4.4]{Gray} \label{prop:opfibtolari}
+  Let $\U \maps\X \to \A$ be an opfibration. Then
+  $\U$ is a right adjoint `left inverse', a.k.a the unit is the identity, if (and only if) its fibers have
+  initial objects which are preserved by the
+  reindexing functors.
+\end{prop}
+
+\begin{proof}\emph{(Sketch)}
+ The left adjoint $L\maps\A\to\X$ maps an object $a$ to the initial object in its fibre $\X_a$, denoted by $\bot_a$.
+By construction, $U(L(a))=U(\bot_a)=a$.
+On morphisms $f\maps a\to a'$, $L(f)$ is defined by
+ \begin{equation}\label{eq:Lonarrows}
+  \bot_a\xrightarrow{\Rex(f,\bot_a)}f_!(\bot_a)\xrightarrow{\;\stackrel{\chi_a}{\cong}\;}\bot_{a'}
+ \end{equation}
+where $\chi_a$ is the unique isomorphism between the initial objects in the fibre above $a'$ since $f_!$ preserves them.
+\end{proof}
+
+\begin{rmk}\label{rmk:important}
+Notice that under \cref{lem:fibrewiselimits}, if $\A$ has an initial object $0_\A$, the above conditions are equivalent to $\X$ having an initial object $0_\X$ above $0_\A$.
+%Christina: hiding strict preservence under the rug
+In this case, $\bot_a$ is precisely the cocartesian lifting of $0_\X$ along the unique map $u_a\maps0_\A\to a$ in the base category:
+\begin{displaymath}
+\xymatrix @C=.4in @R=.2in
+{0_\X \ar @{.>}[d]\ar[rr]^-{\mathrm{Cocart}(0_\X,u_a)} && (u_a)_!(0_X)=:\bot_a\ar @{.>}[d] & \textrm{in }\X  \\
+0_\A\ar[rr]^-{\exists!u_a} && a & \textrm{in }\A}
+\end{displaymath}
+Moreover, if $U=U_F$ for a pseudofunctor $F\maps\A\to\bicat{Cat}$ under \cref{thm:Grothendieck}, the reindexing functors $(u_a)_!$ of the opfibration are precisely $F(u_a)$, therefore $\bot_a=(a,F(u_a)(0_\X))$ in the Grothendieck category, for $u_a$ the unique map from $0_\A$ as above.
+
+Finally, if that pseudofunctor is lax monoidal $(F,\phi,\phi_0)\maps(\A,+)\to(\bicat{Cat},\times)$ to begin with, the monoidal Grothendieck construction in the cocartesian case discussed earlier \cref{eq:explicitstructure1} expresses $\bot_a$ as the image of the composite
+\begin{equation}\label{eq:initialinfibre}
+\mathbf{1}\xrightarrow{\phi_0}F(0_\A)\xrightarrow{F(u_a)}F(a) 
+\end{equation}
+\end{rmk}
+
+%will be a right adjoint to some adjoint , and moreover the unit of the adjunction is the identity; this is called \emph{lari} in [Gray].
+
+%!!!Christina: not sure if the below is needed after all
+In the opposite direction, we also have the following result. For a discussion on the unusual strict cocontinuity condition, we refer the reader to \cite{CV}.
+
+\begin{lem}\label{prop:CV}\cite[Proposition~3.3]{CV}
+Suppose $\U\maps\X\to\A$ is a right adjoint `left inverse'. If $\X$ and $\A$ have chosen pushouts and initial objects and $\U$ strictly preserves them, then $\U$ is an opfibration.
+\end{lem}
+%Christina: do we need this direction after all? Discuss.
+%\begin{thm}\label{thm:mainthmDX}\cite{CV}
+%Suppose that $\X$ and $\A$ have chosen pushouts and initial objects, and a functor $\U\maps\X\to\A$ strictly preserves them.
+Then $\U$ is a right %adjoint left inverse if and only if $\U$ is an opfibration.
+%\end{thm}
+
+We have now laid all the necessary background to formally construct an equivalence between the double category of decorated cospans and the double category of structured cospans, constructed from a symmetric lax monoidal pseudofunctor into $\bicat{Cat}$.
+
+\begin{proof}[Proof of \cref{thm:equiv}]
+Recall from \cref{thm:decorated_cospans} that the double category of decorated cospans $\dcsp{F}$ has objects and vertical 1-morphisms as in $\A$, while a horizontal 1-cell $a\tickar b$ is cospan $\cspn{a}{m}{b}{}{}$ in $\A$ decorated by an object $x\in F(m)$ and a 2-morphism is a map $k\maps m\to m'$ together with a morphism $(Fk)(x)\to x'$.
+
+By \cref{cor:fcocMonGroth}, when $F$ as an ordinary pseudofunctor factors through $\bicat{Rex}$, the (monoidal) Gro\-the\-ndieck construction gives rise to a finitely cocomplete $\inta F$ such that the corresponding opfibration $U_F\maps(\inta{F},+)\to(\A,+)$ preserves all finite colimits.
+%Christina: maybe the cocartesian structures are redundant to write here, since U_F really preserves all finite colimits anyways.
+Since in particular it preserves the initial object, \cref{prop:opfibtolari} through \cref{lem:fibrewiselimits} applies 
+%which equivalently means that all fibres have initial objects and the reindexing functors preserve them by , %Christina: there is a little bit of circularity here.
+We knew fibres have and reindexing functors preserve from the factorization already!
+Change Gray accordingly perhaps?
+to construct a left adjoint $L_F\maps\A\to\inta F$ which is also a right inverse, namely $U_FL_F=\mathrm{id}_\A$.
+Explicitly, this left adjoint is given by $L(a)=(a,\bot_a)$, picking the initial object in the finitely cocomplete fibre also expressed as $F(u_a)\circ\phi_0(*)$ in \cref{eq:initialinfibre}.
+Diagrammatically,
+\begin{displaymath}
+ F\maps\X\to\bicat{Cat}\quad\mapsto\quad\begin{tikzcd}[baseline=.3]\inta F\ar[d,"U_F"'] \\ \X \end{tikzcd}\quad\mapsto\quad\begin{tikzcd}\X\ar[r,bend left,pos=.55,"L_F"]\ar[r,phantom,"\bot"description] & \inta F\ar[l,bend left,pos=.45,"U_F"]\end{tikzcd}
+\end{displaymath}
+roughly describes the processes between the original $F$ and the resulting $L_F$.
+
+Using this functor $L_F$ between finitely cocomplete categories that preserves all colimits that exist (as a left adjoint), we can construct the double category of structured cospans $\scsp{L_F}{\inta F}$.
+Its objects and vertical morphisms are again those of the category $\A$, whereas horizontal 1-cells $a\tickar b$ as in \cref{eq:structuredcospan} are now cospans of the form $\cspn{L_F(a)}{v}{L_F(b)}{}{}$ in the Grothendieck category $\inta F$.
+Explicitly, they consist of two pairs of morphisms
+\begin{equation}\label{eq:scsphor1cell}
+ (a,\bot_a)\xrightarrow{\scalebox{0.7}{\(\begin{cases}i\maps a\to m &\textrm{in }\A \\!\maps F(i)(\bot_a)\to x &\textrm{in }F(m)\end{cases}\)}}(m,x)\xleftarrow{\scalebox{0.7}{\(\begin{cases}o\maps b\to m &\textrm{in }\A \\!\maps F(o)(\bot_b)\to x &\textrm{in }F(m)\end{cases}\)}}(b,\bot_b)
+\end{equation}
+where $x\in F(m)$, according to \cref{def:GrothCat}. Finally, the 2-morphisms in this double category are as described in \cref{eq:2cellsStrCsp}, in this context fully unravelled below:
+\begin{displaymath}
+ \begin{tikzcd}[sep=1.5in,ampersand replacement=\&]
+ (a,\bot_a)\ar[r,"{\begin{cases}i\maps a\to m &\textrm{in }\A \\!\maps F(i)(\bot_a)\to x &\textrm{in }F(m)\end{cases}}"]\ar[d,"{\begin{cases}f\maps a\to a' &\textrm{in }\A \\\chi_a\maps F(f)(\bot_a)\cong \bot_{a'} &\textrm{in }F(a')\end{cases}}"description] \& (m,x) \ar[d,"{\begin{cases}k\maps m\to m' &\textrm{in }\A \\ \tau\maps F(k)(x)\to x' &\textrm{in }F(m')\end{cases}}"description] \& (b,\bot_b)\ar[l,"{\begin{cases}o\maps b\to m &\textrm{in }\A \\!\maps F(o)(\bot_b)\to x &\textrm{in }F(m)\end{cases}}"']\ar[d,"{\begin{cases}g\maps b\to b' &\textrm{in }\A \\\chi_b\maps F(g)(\bot_b)\cong \bot_{b'} &\textrm{in }F(b')\end{cases}}"description] \\
+ (a',\bot_{a'})\ar[r,"{\begin{cases}i'\maps a'\to m' &\textrm{in }\A \\!\maps F(i')(\bot_{a'})\to x' &\textrm{in }F(m')\end{cases}}"'] \& (m',x') \& (b',\bot_{b'})\ar[l,"{\begin{cases}o'\maps b'\to m' &\textrm{in }\A \\!\maps F(o')(\bot_{b'})\to x' &\textrm{in }F(m')\end{cases}}"]
+ \end{tikzcd}
+\end{displaymath}
+where the outside vertical legs come from the definition of $L_F$ on arrows, \cref{eq:Lonarrows}. 
+%!!! The above diagram might be a bit overwhelming, but all info is there. Choose which parts are required for a smooth proof!
+The square commutativities translate to $k\circ i=i'\circ f$ and $k\circ o=o'\circ g$ in $\A$, and also by composition in the Grothendieck category, to
+\begin{gather}\label{eq:Grothcommutativity}
+ F(k\circ i)(\bot_a)\cong Fk(Fi(\bot_a))\xrightarrow{Fk(!)}Fk(x)\xrightarrow{\tau}x'= \\
+ F(i'\circ f)(\bot_a)\cong Fi'(Ff(\bot_a))\xrightarrow{Fi'(\chi_a)}Fi'(\bot_{a'})\xrightarrow{!}x'\nonumber
+\end{gather}
+in the category $F(m')$.
+However, since all maps are unique in the above equality, emanating from initial objects (since reindexing functors preserve those), this gives no extra conditions for the morphisms involved; similarly for the equality including $o, o'$.
+
+In order to prove that there is a double equivalence (\cref{ShulDubEquiv}) between $\dcsp{F}$ and $\scsp{L_F}{\inta F}$, we define a %n identity-on-objects and vertical morphism
+double functor
+\begin{displaymath}
+\mathbb{E}\maps\scsp{L_F}{\inta F} \longrightarrow\dcsp{F}
+\end{displaymath}
+as follows.
+The object component of $\mathbb{E}=(\mathbb{E}_0,\mathbb{E}_1)$ is $\mathbb{E}_0 = \id_{\A}$ since both double categories have $\A$ as their vertical category; trivially, $\mathbb{E}_0$ is an equivalence of categories.
+Given a horizontal 1-cell in $\scsp{L_F}{\inta F}$ like \cref{eq:scsphor1cell}, the arrow component $\mathbb{E}_1$ of the double functor simply maps it to the decorated cospan
+\begin{displaymath}
+ a\xrightarrow{\; i \;}m\xleftarrow{\; o \;}b\;\textrm{ with decoration }x\in F(m)
+\end{displaymath}
+Notice that this really is a bijective correspondence since the unique maps from the initial objects in the fibres provide no extra information.
+Finally, given a 2-morphism of $L_F$-structured cospans as described above, $\mathbb{E}_1$ maps it to the underlying cospan 2-morphism
+\begin{displaymath}
+ \begin{tikzcd}
+a\ar[r,"i"]\ar[d,"f"'] & m\ar[d,"k"] & b\ar[l,"o"']\ar[d,"g"] \\
+a'\ar[r,"i'"']& m' & b'\ar[l,"o'"]
+ \end{tikzcd}
+\end{displaymath}
+ in $\A$ along with the map $\tau\maps Fk(x)\to x'$ in $F(m')$, namely a decorated cospan 2-morphism as per \cref{eq:FCsp2morph}.
+Once again, this is a bijective correspondence since, as discussed above, the commutativity \cref{eq:Grothcommutativity} holds automatically by initiality of the domain.
+%!!!Christina: commented out big chunks of proof.
+They are right below if we want to revive parts of them, if we think the reader needs deeper level of detail.
+The idea is that the above description suffices as fully faithful and essentially surjective evidence, but perhaps we would like to spell that out more.
+On to strongness next.
+\begin{comment}
+which is a cospan in $\X$ of the form:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$L(c)$};
+\node (B) at (1,0) {$x$};
+\node (C) at (2,0) {$L(c')$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i$} (B)
+(C) edge node[above]{$o$} (B);
+\end{tikzpicture}
+\]
+the image $\mathbb{E}_1(M)$ is given by the pair:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$c$};
+\node (B) at (1,0) {$R(x)$};
+\node (C) at (2,0) {$c'$};
+\node (D) at (3,0) {$x \in F(R(x))$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$R(i) {\eta_c}$} (B)
+(C) edge node[above]{$R(o) {\eta_{c'}}$} (B);
+\end{tikzpicture}
+\]
+where $R\maps \X \to \A$ is the right adjoint to the functor $L \maps \A \to \X$ and $\eta \maps 1_{\A} \to RL$ is the unit of the adjunction $L \dashv R$ which is an isomorphism since $L$ is fully faithful.
+\textbf{Hopefully...actually, it's a `lari'!} Similarly, the image of a 2-morphism $\alpha \maps M \to N$ in $_L \lCsp(\X)$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$L(c_1)$};
+\node (B) at (1,0) {$x$};
+\node (C) at (2,0) {$L(c_2)$};
+\node (A') at (0,-1) {$L(c_1')$};
+\node (B') at (1,-1) {$x'$};
+\node (C') at (2,-1) {$L(c_2')$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i$} (B)
+(C) edge node[above]{$o$} (B)
+(A') edge node[above]{$i'$} (B')
+(C') edge node[above]{$o'$} (B')
+(A) edge node [left]{$L(f)$} (A')
+(B) edge node [left]{$\alpha$} (B')
+(C) edge node [right]{$L(g)$} (C');
+\end{tikzpicture}
+\]
+is given by the 2-morphism $\mathbb{E}_1(\alpha) \maps \mathbb{E}_1(M) \to \mathbb{E}_1(N)$ in $\mathbb{F}\textnormal{Cospan}(\A)$ given by:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$c_1$};
+\node (B) at (1,0) {$R(x)$};
+\node (C) at (2,0) {$c_2$};
+\node (A') at (0,-1) {$c_1'$};
+\node (B') at (1,-1) {$R(x')$};
+\node (C') at (2,-1) {$c_2'$};
+\node (D) at (3,0) {$x \in F(R(x))$};
+\node (D') at (3,-1) {$x' \in F(R(x'))$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$R(i) \eta_{c_1}$} (B)
+(C) edge node[above]{$R(o) \eta_{c_2}$} (B)
+(A') edge node[above]{$R(i') \eta_{c_1'}$} (B')
+(C') edge node[above]{$R(o') \eta_{c_2'}$} (B')
+(A) edge node [left]{$f$} (A')
+(B) edge node [left]{$R(\alpha)$} (B')
+(C) edge node [right]{$g$} (C');
+\end{tikzpicture}
+\]
+together with a morphism $\tau \maps F(R(\alpha))(x) \to x'$ in $F(R(x')) \subseteq \mathrm{X}$ which comes from the Grothendieck construction of the pseudofunctor $F \maps \A \to \Cat$.
+That $\mathbb{E}_0$ is a functor is clear.
+For $\mathbb{E}_1$, given two vertically composable 2-morphisms $M$ and $M'$ in $_L \lCsp(\X)$,
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$L(c_1)$};
+\node (B) at (1,0) {$x$};
+\node (C) at (2,0) {$L(c_2)$};
+\node (A') at (0,-1) {$L(c_1')$};
+\node (B') at (1,-1) {$x'$};
+\node (C') at (2,-1) {$L(c_2')$};
+\node (A'') at (0,-2) {$L(c_1')$};
+\node (B'') at (1,-2) {$x'$};
+\node (C'') at (2,-2) {$L(c_2')$};
+\node (A''') at (0,-3) {$L(c_1'')$};
+\node (B''') at (1,-3) {$x''$};
+\node (C''') at (2,-3) {$L(c_2'')$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i$} (B)
+(C) edge node[above]{$o$} (B)
+(A') edge node[above]{$i'$} (B')
+(C') edge node[above]{$o'$} (B')
+(A) edge node [left]{$L(f)$} (A')
+(B) edge node [left]{$\alpha$} (B')
+(C) edge node [right]{$L(g)$} (C')
+(A'') edge node[above]{$i'$} (B'')
+(C'') edge node[above]{$o'$} (B'')
+(A''') edge node[above]{$i''$} (B''')
+(C''') edge node[above]{$o''$} (B''')
+(A'') edge node [left]{$L(f')$} (A''')
+(B'') edge node [left]{$\alpha'$} (B''')
+(C'') edge node [right]{$L(g')$} (C''');
+\end{tikzpicture}
+\]
+their vertical composite $M'M$ is given by:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$L(c_1)$};
+\node (B) at (1,0) {$x$};
+\node (C) at (2,0) {$L(c_2)$};
+\node (A') at (0,-1) {$L(c_1'')$};
+\node (B') at (1,-1) {$x''$};
+\node (C') at (2,-1) {$L(c_2'')$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i$} (B)
+(C) edge node[above]{$o$} (B)
+(A') edge node[above]{$i''$} (B')
+(C') edge node[above]{$o''$} (B')
+(A) edge node [left]{$L(f'f)$} (A')
+(B) edge node [left]{$\alpha' \alpha$} (B')
+(C) edge node [right]{$L(g' g)$} (C');
+\end{tikzpicture}
+\]
+and the image of this 2-morphism $\mathbb{E}_1(M'M)$ is given by:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$c_1$};
+\node (B) at (1.5,0) {$R(x)$};
+\node (C) at (3,0) {$c_2$};
+\node (A') at (0,-1) {$c_1''$};
+\node (B') at (1.5,-1) {$R(x'')$};
+\node (C') at (3,-1) {$c_2''$};
+\node (D) at (4,0) {$x \in F(R(x))$};
+\node (D') at (4,-1) {$x'' \in F(R(x''))$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$R(i) \eta_{c_1}$} (B)
+(C) edge node[above]{$R(o) \eta_{c_2}$} (B)
+(A') edge node[above]{$R(i'') \eta_{c_1''}$} (B')
+(C') edge node[above]{$R(o'') \eta_{c_2''}$} (B')
+(A) edge node [left]{$f'f$} (A')
+(B) edge node [left]{$R(\alpha' \alpha)$} (B')
+(C) edge node [right]{$g'g$} (C');
+\end{tikzpicture}
+\]
+together with a morphism $\tau_{M' M} \maps F(R(\alpha' \alpha))(x) \to x''$ in $F(R(x''))$. On the other hand, the individual images $\mathbb{E}_1(M)$ and $\mathbb{E}_1(M')$ are given by:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$c_1$};
+\node (B) at (1.5,0) {$R(x)$};
+\node (C) at (3,0) {$c_2$};
+\node (A') at (0,-1) {$c_1'$};
+\node (B') at (1.5,-1) {$R(x')$};
+\node (C') at (3,-1) {$c_2'$};
+\node (D) at (4,0) {$x \in F(R(x))$};
+\node (D') at (4,-1) {$x' \in F(R(x'))$};
+\node (A'') at (0,-2) {$c_1'$};
+\node (B'') at (1.5,-2) {$R(x')$};
+\node (C'') at (3,-2) {$c_2'$};
+\node (A''') at (0,-3) {$c_1''$};
+\node (B''') at (1.5,-3) {$R(x'')$};
+\node (C''') at (3,-3) {$c_2''$};
+\node (D'') at (4,-2) {$x' \in F(R(x'))$};
+\node (D''') at (4,-3) {$x'' \in F(R(x''))$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$R(i) \eta_{c_1}$} (B)
+(C) edge node[above]{$R(o) \eta_{c_2}$} (B)
+(A') edge node[above]{$R(i') \eta_{c_1'}$} (B')
+(C') edge node[above]{$R(o') \eta_{c_2'}$} (B')
+(A) edge node [left]{$f$} (A')
+(B) edge node [left]{$R(\alpha)$} (B')
+(C) edge node [right]{$g$} (C')
+(A'') edge node[above]{$R(i') \eta_{c_1'}$} (B'')
+(C'') edge node[above]{$R(o') \eta_{c_2'}$} (B'')
+(A''') edge node[above]{$R(i'') \eta_{c_1''}$} (B''')
+(C''') edge node[above]{$R(o'') \eta_{c_2''}$} (B''')
+(A'') edge node [left]{$f'$} (A''')
+(B'') edge node [left]{$R(\alpha')$} (B''')
+(C'') edge node [right]{$g'$} (C''');
+\end{tikzpicture}
+\]
+together with morphisms $\tau_M \maps F(R(\alpha))(x) \to x'$ in $F(R(x'))$ and $\tau_{M'} \maps F(R(\alpha')(x') \to x''$ in $F(R(x''))$, respectively.
+The vertical composite $\mathbb{E}_1(M')\mathbb{E}_1(M)$ of the above two 2-morphisms is given by $\mathbb{E}_1(M'M)$ as $R$ is a functor and $\tau_{M'M}=\tau_{M'} \tau_M$.
+The functors $\mathbb{E}_0$ and $\mathbb{E}_1$ satisfy the equations $\mathbb{E}_0 S = S \mathbb{E}_1$ and $\mathbb{E}_0 T = T \mathbb{E}_1$.
+
+To see that this functor is essentially surjective, given a horizontal 1-cell in $F\lCsp$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$c_1$};
+\node (B) at (1,0) {$c$};
+\node (C) at (2,0) {$c_2$};
+\node (D) at (3,0) {$x \in F(c)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i$} (B)
+(C) edge node[above]{$o$} (B);
+\end{tikzpicture}
+\]
+we can find a 2-isomorphism in $F\lCsp$ whose codomain is the above horizontal 1-cell and whose domain is the image of the following horizontal 1-cell in $_L \lCsp(\X)$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$L(c_1)$};
+\node (B) at (1,0) {$x$};
+\node (C) at (2,0) {$L(c_2)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i'$} (B)
+(C) edge node[above]{$o'$} (B);
+\end{tikzpicture}
+\]
+with the 2-isomorphism in $F\lCsp$ given by:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$c_1$};
+\node (B) at (1,0) {$R(x)$};
+\node (C) at (2,0) {$c_2$};
+\node (A') at (0,-1) {$c_1$};
+\node (B') at (1,-1) {$c$};
+\node (C') at (2,-1) {$c_2$};
+\node (D) at (3,0) {$x \in F(R(x))$};
+\node (D') at (3,-1) {$x \in F(c)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$R(i') \eta_{c_1}$} (B)
+(C) edge node[above]{$R(o') \eta_{c_2}$} (B)
+(A') edge node[above]{$i$} (B')
+(C') edge node[above]{$o$} (B')
+(A) edge node [left]{$1$} (A')
+(B) edge node [left]{${(R(e) \eta_c)}^{-1}$} (B')
+(C) edge node [right]{$1$} (C');
+\end{tikzpicture}
+\]
+$$\tau \maps F({(R(e)\eta_c)}^{-1})(x) \to x$$
+where $e \maps L(c) \to x$ is given by the map from the trivial decoration on $c$ to $x \in F(c)$.
+%The object and arrow components $\mathbb{E}_0$ and $\mathbb{E}_1$ satisfy the equations $S \mathbb{E}_1 = \mathbb{E}_0 S$ and $T \mathbb{E}_1 = \mathbb{E}_0 T$.
+
+To show that the double functor $\mathbb{E}$ is fully faithful, we need to show that the map  $$\mathbb{E}_1 \maps _f { _L \lCsp(\X)}_g(M,N) \to {_{\mathbb{E}(f)} {F\lCsp}_{\mathbb{E}(g)}}(\mathbb{E}(M),\mathbb{E}(N))$$ is bijective for arbitrary vertical 1-morphisms $f$ and $g$ and horizontal 1-cells $M$ and $N$ of $_L \lCsp(\X)$.
+Consider a 2-morphism in $_L \lCsp(\X)$ with horizontal source and target $M$ and $N$, respectively and vertical source and target $f$ and $g$, respectively:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$L(c_1)$};
+\node (B) at (1,0) {$x$};
+\node (C) at (2,0) {$L(c_2)$};
+\node (A') at (0,-1) {$L(c_1')$};
+\node (B') at (1,-1) {$x'$};
+\node (C') at (2,-1) {$L(c_2')$};
+\node (D) at (1,0.5) {$M$};
+\node (E) at (-1,-0.5) {$f$};
+\node (F) at (1,-1.5) {$N$};
+\node (G) at (3,-0.5) {$g$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i$} (B)
+(C) edge node[above]{$o$} (B)
+(A') edge node[above]{$i'$} (B')
+(C') edge node[above]{$o'$} (B')
+(A) edge node [left]{$L(f)$} (A')
+(B) edge node [left]{$\alpha$} (B')
+(C) edge node [right]{$L(g)$} (C');
+\end{tikzpicture}
+\]
+Thus the set $$_f { _L \lCsp(\X)}_g(M,N)$$ consists of triples $$(f,\alpha,g)$$ rendering the above diagram commutative where $f$ and $g$ are morphisms of $\A$ and $\alpha$ is a morphism of $\X$.
+The image of the above 2-morphism under the double functor $\mathbb{E}$ is given by:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$c_1$};
+\node (B) at (1,0) {$R(x)$};
+\node (C) at (2,0) {$c_2$};
+\node (A') at (0,-1) {$c_1'$};
+\node (B') at (1,-1) {$R(x')$};
+\node (C') at (2,-1) {$c_2'$};
+\node (D) at (1,0.5) {$x \in F(R(x))$};
+\node (D') at (1,-1.5) {$x' \in F(R(x'))$};
+\node (E) at (1,1) {$\mathbb{E}(M)$};
+\node (F) at (-1,-0.5) {$\mathbb{E}(f)$};
+\node (G) at (1,-2) {$\mathbb{E}(N)$};
+\node (H) at (3,-0.5) {$\mathbb{E}(g)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$R(i)\eta_{c_1}$} (B)
+(C) edge node[above]{$R(o)\eta_{c_2}$} (B)
+(A') edge node[above]{$R(i')\eta_{c_1'}$} (B')
+(C') edge node[above]{$R(o')\eta_{c_2'}$} (B')
+(A) edge node [left]{$f$} (A')
+(B) edge node [left]{$R(\alpha)$} (B')
+(C) edge node [right]{$g$} (C');
+\end{tikzpicture}
+\]
+together with a morphism $\tau \maps F(R(\alpha))(x) \to x'$ of $F(R(x'))$.
+Thus the set $$_{\mathbb{E}(f)} {F\lCsp}_{\mathbb{E}(g)}(\mathbb{E}(M),\mathbb{E}(N))$$ consists of 4-tuples $$(f,R(\alpha),g,\tau)$$ rendering the above diagram commutative and where $f,g$ and $R(\alpha)$ are morphisms of $\A$ and $\tau$ is a morphism in $F(R(x'))$.
+The morphisms $R(\alpha) \maps R(x) \to R(x')$ and $\tau \maps F(R(\alpha))(x) \to x'$ together determine the morphism $\alpha \maps x \to x'$ in $\mathrm{X}$ and conversely; given two objects $x=(c,x \in F(c))$ and $x'=(c',x' \in F(c'))$ of $\X=\inta{F}$, a morphism from $\alpha \maps x \to x'$ is a pair $$(h \maps c \to c', \tau \maps F(h)(x) \to x')$$ where $h \maps c \to c'$ is given by $R(\alpha) \maps R(x) \to R(x')$.
+This shows that $\mathbb{E}$ is fully faithful.
+\textbf{At least in my favorite example...}
+\end{comment}
+Functoriality of $\mathbb{E}_1$ can be verified, and moreover $(\mathbb{E}_0,\mathbb{E}_1)$ indeed define a strong double functor: there exist natural isomorphisms
+\begin{gather*}
+ \mathbb{E}(M) \odot \mathbb{E}(N) \xrightarrow{\sim} \mathbb{E}(M \odot N) \\
+U_{\mathbb{E}m} \xrightarrow{\sim} \mathbb{E}(U_m)
+\end{gather*}
+for any pair of composable horizontal 1-cells $M=\cspn{(a,\bot_a)}{(m,x)}{(b,\bot_b)}{}{}$ and $N=\cspn{(b,\bot_b)}{(n,y)}{(c,\bot_c)}{}{}$ and any object $m$ of $\scsp{L_F}{\inta F}$.
+In more detail, $\mathbb{E}(M)\odot \mathbb{E}(N)$ is given as in \cref{eq:dcospanscomposition} via the pushout cospan and decoration
+\begin{displaymath}
+ \begin{tikzcd}
+  & m+_bn & \\
+  a\ar[ur,"j_m\circ i"] && b,\ar[ul,"j_n\circ o"']
+ \end{tikzcd}
+ \begin{tikzcd}
+  1\ar[r,"x\times y"]\ar[drr,dashed] & F(m)\times F(n)\ar[r,"\phi_{m,n}"] & F(m+ n)\ar[d,"F(j)"] \\ 
+  && F(m+_b n)
+ \end{tikzcd}
+\end{displaymath}
+where $j_m, j_n$ denote the maps into a pushout.
+On the other hand, first composing $M$ and $N$ in the Grothendieck category $\scsp{L_F}{\inta F}$ using fibrewise pushouts constructed using \cref{lem:fibrewiselimits} 
+%!!!Chris: I could make this specific construction into a lemma earlier if you want, I have it in my notes
+produces 
+\begin{displaymath}
+ \begin{tikzcd}
+ && (m+_b n,F(j_m)x+_{\bot_{m+_bn}}F(j_n)y) && \\
+ & (m,x) \ar[ur] && (n,y)\ar[ul] \\
+ (a,\bot_a)\ar[ur] && (b,\bot_b)\ar[ur]\ar[ul] && (c,\bot_c)\ar[ul]
+ \end{tikzcd}
+\end{displaymath}
+which is mapped, under $\mathbb{E}$, to precisely the cospan $\cspn{a}{m+_bn}{b}{}{}$ as above, and the decorations are the same 
+%!!!Christina: isomorphic would be enough but they look equal to me!
+due to the following commutative diagram
+\begin{displaymath}
+ \begin{tikzcd}
+F(m)\times F(n)\ar[rr,"\phi"]\ar[d,"F(j_m)\times F(j_n)"'] && F(m+n)\ar[d,"F(j)"] \\
+F(m+_bn)\times F(m+_bn)\ar[r,"\phi"] & F((m+_bn)+(m+_bn))\ar[r,"F\nabla"] & F(m+_bn)
+ \end{tikzcd}
+\end{displaymath}
+since taking a pushout over an initial object is really a coproduct, and the fibrewise coproduct in $F(m+_bn)$ is given as in \cref{eq:explicitstructure1}.
+
+Regarding the identity morphisms, $U_m$ is $\cspn{(m,\bot_m)}{(m,\bot_m)}{(m,\bot_m)}{}{}$ with $1_m$ as the $A$-component of the morphisms and isomorphisms between initial objects in the fibres.
+Thus $\mathbb{E}(U_m)$ is the identity cospan in $A$ together with the `initial decoration' $\bot_m\in F(m)$, whereas $U_{\mathbb{E}(m)}$ is exactly the same thing.
+
+%!!!Christina: Below, up to my next comment, is Kenny's earlier proof on the same thing.
+\begin{comment}
+For any object $c$, the horizontal 1-cell $\hat{U}_{\mathbb{E}(c)}$ is given by $\hat{U}_c$ which is given by the pair:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$c$};
+\node (B) at (1,0) {$c$};
+\node (C) at (2,0) {$c$};
+\node (D) at (3,0) {$!_c \in F(c)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$1$} (B)
+(C) edge node[above]{$1$} (B);
+\end{tikzpicture}
+\]
+The horizontal 1-cell $U_c$ is given by
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$L(c)$};
+\node (B) at (1,0) {$L(c)$};
+\node (C) at (2,0) {$L(c)$};
+%\node (D) at (3,0.5) {$!_c \in F(c)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$1$} (B)
+(C) edge node[above]{$1$} (B);
+\end{tikzpicture}
+\]
+and so $\mathbb{E}(U_c)$ is given by the pair:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$c$};
+\node (B) at (1,0) {$R(L(c))$};
+\node (C) at (2,0) {$c$};
+\node (D) at (3.25,0) {$!_c \in F(R(L(c)))$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$\eta_c$} (B)
+(C) edge node[above]{$\eta_c$} (B);
+\end{tikzpicture}
+\]
+Then we can obtain the natural isomorphism $\mathbb{E}_c \maps \hat{U}_{\mathbb{E}(c)} \xrightarrow{\sim} \mathbb{E}(U_c)$ as the 2-morphism
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$c$};
+\node (B) at (1,0) {$c$};
+\node (C) at (2,0) {$c$};
+\node (A') at (0,-1) {$c$};
+\node (B') at (1,-1) {$R(L(c))$};
+\node (C') at (2,-1) {$c$};
+\node (D) at (3,0) {$!_c \in F(c)$};
+\node (D') at (3.25,-1) {$!_{R(L(c))} \in F(R(L(c)))$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$1$} (B)
+(C) edge node[above]{$1$} (B)
+(A') edge node[above]{$\eta_c$} (B')
+(C') edge node[above]{$\eta_c$} (B')
+(A) edge node [left]{$1$} (A')
+(B) edge node [left]{$\eta_c$} (B')
+(C) edge node [left]{$1$} (C');
+\end{tikzpicture}
+\]
+$$\tau \maps F(\eta_c)(!_c) \xrightarrow{!} !_{R(L(c))}$$
+of $F\lCsp$.
+
+Next, given composable horizontal 1-cells $M$ and $N$ in $_L \lCsp(\X)$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$L(c_1)$};
+\node (B) at (1,0) {$x$};
+\node (C) at (2,0) {$L(c_2)$};
+\node (D) at (3,0) {$L(c_2)$};
+\node (E) at (4,0) {$x'$};
+\node (F) at (5,0) {$L(c_3)$};
+%\node (D) at (3,0.5) {$!_c \in F(c)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i$} (B)
+(C) edge node[above]{$o$} (B)
+(D) edge node[above]{$i'$} (E)
+(F) edge node[above]{$o'$} (E);
+\end{tikzpicture}
+\]
+their images $\mathbb{E}(M)$ and $\mathbb{E}(N)$ are given by:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$c_1$};
+\node (B) at (1,0) {$R(x)$};
+\node (C) at (2,0) {$c_2$};
+\node (D) at (3,0) {$c_2$};
+\node (E) at (4,0) {$R(x')$};
+\node (F) at (5,0) {$c_3$};
+\node (G) at (1,-0.5) {$x \in F(R(x))$};
+\node (H) at (4,-0.5) {$x' \in F(R(x'))$};
+%\node (D) at (3,0.5) {$!_c \in F(c)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$R(i) \eta_{c_1}$} (B)
+(C) edge node[above]{$R(o) \eta_{c_2}$} (B)
+(D) edge node[above]{$R(i') \eta_{c_2}$} (E)
+(F) edge node[above]{$R(o') \eta_{c_3}$} (E);
+\end{tikzpicture}
+\]
+and so $\mathbb{E}(M) \odot \mathbb{E}(N)$ is given by:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$c_1$};
+\node (B) at (1.5,0) {$R(x)+_{c_2}R(x')$};
+\node (C) at (3,0) {$c_3$};
+\node (G) at (1.5,-0.5) {$d_{\mathbb{E}(M) \odot \mathbb{E}(N)} = \hat{x} \in F(R(x)+_{c_2}R(x'))$};
+%\node (D) at (3,0.5) {$!_c \in F(c)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$j \psi R(i) \eta_{c_1}$} (B)
+(C) edge node[above]{$j \psi R(o') \eta_{c_3}$} (B);
+\end{tikzpicture}
+\]
+$$\hat{x} \maps 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{x \times x'} F(R(x)) \times F(R(x')) \xrightarrow{\phi_{R(x),R(x')}} F(R(x)+R(x')) \xrightarrow{F(j_{R(x),R(x')})} F(R(x)+_{c_2}R(x'))$$where $\psi$ denotes each natural map into the coproduct and $j$ denotes the natural map from the coproduct to the pushout.
+On the other hand, $M \odot N$ is given by
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$L(c_1)$};
+\node (B) at (1.25,0) {$x+_{L(c_2)}x'$};
+\node (C) at (2.5,0) {$L(c_3)$};
+%\node (G) at (1,-0.5) {$\hat{d} \in F(R(d)+_{c_2}R(d'))$};
+%\node (D) at (3,0.5) {$!_c \in F(c)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$J \zeta i$} (B)
+(C) edge node[above]{$J \zeta o'$} (B);
+\end{tikzpicture}
+\]
+where $\zeta$ is a natural map into a coproduct and $J$ is the natural map from the coproduct to the pushout. Then $E(M \odot N)$ is given by
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$c_1$};
+\node (B) at (1.5,0) {$R(x+_{L(c_2)}x')$};
+\node (C) at (3,0) {$c_3$};
+\node (G) at (1.5,-0.5) {$d_{\mathbb{E}(M \odot N)} = x+_{L(c_2)} x' \in F(R(x+_{L(c_2)}x'))$};
+%\node (D) at (3,0.5) {$!_c \in F(c)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$R(J \zeta i) \eta_{c_1}$} (B)
+(C) edge node[above]{$R(J \zeta o') \eta_{c_3}$} (B);
+\end{tikzpicture}
+\]
+and so $\mathbb{E}_{M,N} \maps \mathbb{E}(M) \odot \mathbb{E}(N) \xrightarrow{\sim} \mathbb{E}(M \odot N)$ is given by the 2-morphism:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$c_1$};
+\node (B) at (1.5,0) {$R(x)+_{c_2}R(x')$};
+\node (C) at (3,0) {$c_3$};
+\node (A') at (0,-1) {$c_1$};
+\node (B') at (1.5,-1) {$R(x+_{L(c_2)}x')$};
+\node (C') at (3,-1) {$c_3$};
+\node (D) at (5.5 ,0) {$d_{\mathbb{E}(M) \odot \mathbb{E}(N)} \in F(R(x)+_{c_2}R(x'))$};
+\node (D') at (5.5,-1) {$d_{\mathbb{E}(M \odot N)} \in F(R(x+_{L(c_2)}x'))$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$j \psi R(i) \eta_{c_1}$} (B)
+(C) edge node[above]{$j \psi R(o') \eta_{c_3}$} (B)
+(A') edge node[above]{$R(J \zeta i) \eta_{c_1}$} (B')
+(C') edge node[above]{$R(J \zeta o') \eta_{c_3}$} (B')
+(A) edge node [left]{$1$} (A')
+(B) edge node [left]{$\sigma$} (B')
+(C) edge node [left]{$1$} (C');
+\end{tikzpicture}
+\]
+together with a morphism of decorations which is obtained as follows.
+First, as $R \maps \X \to \A$ preserves finite colimits, we have an isomorphism $$\kappa \maps R(x) +_{R(L(c_2))} R(x') \to R(x+_{L(c_2)}x').$$ Also, since the left adjoint $L \maps \A \to \X$ is fully faithful, the unit of the adjunction $L \dashv R$ at the object $c_2$ gives an isomorphism $\eta_{c_2} \maps c_2 \to R(L(c_2))$ which results in an isomorphism $$j_{\eta_{c_2}} \maps R(x) +_{c_2} R(x') \to R(x) +_{R(L(c_2))} R(x').$$ Composing these two results in an isomorphism $$\sigma \mapseqq \kappa j_{\eta_{c_2}} \maps R(x) +_{c_2} R(x') \to R(x+_{L(c_2)}x').$$
+Next, to see that the above diagram commutes, it suffices to show that for the object $c_1 \in \mathrm{A}$, $$R(J)R(\zeta)R(i)\eta_{c_1}(c_1) = R(J \zeta i)\eta_{c_1}(c_1)  \stackrel{!}{=} \sigma j \psi R(i)\eta_{c_1}(c_1) = \kappa j_{\eta_{c_2}} \psi R(i) \eta_{c_1}(c_1).$$ This follows as $R(i) \eta_{c_1} \maps c_1 \to R(x)$ and the following diagram commutes:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (B) at (0,0) {$R(x)$};
+\node (C) at (2,0) {$R(x)+R(x')$};
+\node (A') at (4,0) {$R(x)+_{c_2}R(x')$};
+\node (B') at (4,-2) {$R(x+_{L(c_2)}x')$};
+\node (D) at (0,-2) {$R(x+x')$};
+\node (D') at (4,-1) {$R(x)+_{R(L(c_2))} R(x')$};
+\path[->,font=\scriptsize,>=angle 90]
+(C) edge node[above]{$j$} (A')
+(B) edge node[above]{$\psi$} (C)
+(D) edge node[above]{$R(J)$} (B')
+(B) edge node [left]{$R(\zeta)$} (D)
+(A') edge node [right]{$j_{\eta_{c_2}}$} (D')
+(A') edge [out=345,in=15] node [right]{$\sigma$} (B')
+(D') edge node [right]{$\kappa$} (B');
+\end{tikzpicture}
+\]
+Lastly, this map of cospans comes with an isomorphism $$\tau \maps F(\sigma)(d_{\mathbb{E}(M) \odot \mathbb{E}(N)}) \to d_{\mathbb{E}(M \odot N)}$$ in $F(R(x+_{L(c_2)}x'))$.
+This shows that $\mathbb{E}$ is strong, and so
+\end{comment}
+%!!!Christina: Up to here was Kenny's strong functoriality.
+
+Based on the above description of its mapping, it follows that the strong double functor $\mathbb{E}=(\mathbb{E}_0,\mathbb{E}_1)$ is full, faithful and essentially surjective on objects as per \cref{def:fullfaithful,def:essentiallysurj}.
+Therefore $\mathbb{E} \maps \scsp{L_F}{\inta F} \to \dcsp{F}$ is a double equivalence, by \cref{ShulDubEquiv}.
+%!!!Christina: In fact, Christina and Kenny believe it is an isomorphism of double categories! Bijective on all levels of objects and morphisms...should we say?
+
+%!!!Christina Have not edited below, but everything should be fine up to notation changes. Happy to do if needed in the future.
+
+Next, we show that if both double categories $_L \lCsp(\X)$ and $F\lCsp$ are symmetric monoidal, as they are if both $\A$ and $\X$ have finite colimits, then this equivalence of double categories $\mathbb{E} \maps _L \lCsp(\X) \to F\lCsp$ will be symmetric monoidal.
+First, note that we have an isomorphism $\epsilon \maps 1_{F\lCsp} \to \mathbb{E}(1_{_L \lCsp(\X)})$ and natural isomorphisms $\mu_{c_1,c_2} \maps \mathbb{E}(c_1) \otimes \mathbb{E}(c_2) \to \mathbb{E}(c_1 \otimes c_2)$ for every pair of objects $c_1,c_2 \in {_L \mathbb{C} \textnormal{sp}(\X)}$ both of which are given by identities since both double categories $_L \lCsp(\X)$ and $F\lCsp$ have $\A$ as their category of objects and $\mathbb{E}_0=\id_{\A}$.
+The diagrams utilizing these maps that are required to commute do so trivially.
+
+For the arrow component $\mathbb{E}_1$, we have an isomorphism $\delta \maps U_{1_{F\lCsp}} \to \mathbb{E}(U_{1_{_L \lCsp(\X)}})$ where the horizontal 1-cell $U_{1_{F\lCsp}}$ is given by:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$1_\A$};
+\node (B) at (1,0) {$1_\A$};
+\node (C) at (2,0) {$1_\A$};
+\node (D) at (3,0) {$!_{1_{\A}} \in F(1_\A)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$1$} (B)
+(C) edge node[above]{$1$} (B);
+\end{tikzpicture}
+\]
+where $!_{1_{\A}} = \phi \maps 1 \to F(1_\A)$ is the trivial decoration which comes from the structure of the symmetric lax monoidal pseudofunctor $F \maps \A \to \Cat$.
+The horizontal 1-cell $U_{1_{_L \lCsp(\X)}}$ is given by:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$L(1_\A)$};
+\node (B) at (1,0) {$L(1_\A)$};
+\node (C) at (2,0) {$L(1_\A)$};
+%\node (D) at (3,0.5) {$I \in F(1_\mathrm{A})$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$1$} (B)
+(C) edge node[above]{$1$} (B);
+\end{tikzpicture}
+\]
+where here we make use of the fact that the left adjoint $L \maps (\A,+,1_\A) \to (\X,+,1_\X)$ preserves all colimits and thus $L(1_\A) \cong 1_\X$.
+The horizontal 1-cell $\mathbb{E}(U_{1_{_L \mathbb{C} \textnormal{sp}(\X)}})$ is then given by the pair:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$1_\A$};
+\node (B) at (1.25,0) {$R(L(1_\A))$};
+\node (C) at (2.5,0) {$1_\A$};
+\node (D) at (4.5,0) {$!_{R(L(1_\A))} \in F(R(L(1_\A)))$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{${\eta_{1_\A}}$} (B)
+(C) edge node[above]{${\eta_{1_\A}}$} (B);
+\end{tikzpicture}
+\]
+The isomorphism $\delta$ is then given by the 2-morphism:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$1_\A$};
+\node (B) at (1,0) {$1_{\A}$};
+\node (C) at (2,0) {$1_\A$};
+\node (A') at (0,-1) {$1_\A$};
+\node (B') at (1,-1) {$R(L(1_\A))$};
+\node (C') at (2,-1) {$1_\A$};
+\node (D) at (3,0) {$!_{1_\A} \in F(1_\A)$};
+\node (D') at (3.75,-1) {$!_{R(L(1_\A))} \in F(R(L(1_\A)))$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$1$} (B)
+(C) edge node[above]{$1$} (B)
+(A') edge node[above]{${\eta_{1_\A}}$} (B')
+(C') edge node[above]{${\eta_{1_\A}}$} (B')
+(A) edge node [left]{$1$} (A')
+(B) edge node [left]{${\eta_{1_\A}}$} (B')
+(C) edge node [left]{$1$} (C');
+\end{tikzpicture}
+\]
+$$\tau_{{\eta_{1_\A}}} \maps F({\eta_{1_\A}})(!_{1_\A})) \to !_{R(L(1_\A))}$$
+of $F\lCsp$. This is just the natural isomorphism $\mathbb{E}_{1_\A}$ from earlier.
+
+Given two horizontal 1-cells $M$ and $N$ of $_L \lCsp(\X)$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$L(c_1)$};
+\node (B) at (1,0) {$x$};
+\node (C) at (2,0) {$L(c_2)$};
+\node (D) at (3,0) {$L(c_1')$};
+\node (E) at (4,0) {$x'$};
+\node (F) at (5,0) {$L(c_2')$};
+%\node (D) at (3,0.5) {$!_c \in F(c)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i$} (B)
+(C) edge node[above]{$o$} (B)
+(D) edge node[above]{$i'$} (E)
+(F) edge node[above]{$o'$} (E);
+\end{tikzpicture}
+\]
+their images $\mathbb{E}(M)$ and $\mathbb{E}(N)$ are given by:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$c_1$};
+\node (B) at (1,0) {$R(x)$};
+\node (C) at (2,0) {$c_2$};
+\node (D) at (3,0) {$c_1'$};
+\node (E) at (4,0) {$R(x')$};
+\node (F) at (5,0) {$c_2'$};
+\node (G) at (1,-0.5) {$x \in F(R(x))$};
+\node (H) at (4,-0.5) {$x' \in F(R(x'))$};
+%\node (D) at (3,0.5) {$!_c \in F(c)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$R(i) \eta_{c_1}$} (B)
+(C) edge node[above]{$R(o) \eta_{c_2}$} (B)
+(D) edge node[above]{$R(i') \eta_{c_1'}$} (E)
+(F) edge node[above]{$R(o') \eta_{c_2'}$} (E);
+\end{tikzpicture}
+\]
+and so $\mathbb{E}(M) \otimes \mathbb{E}(N)$ is given by:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$c_1+c_1'$};
+\node (B) at (3.25,0) {$R(x)+R(x')$};
+\node (C) at (6.5,0) {$c_2+c_2'$};
+\node (D) at (3.25,-0.5) {$d_{\mathbb{E}(M) \otimes \mathbb{E}(N)} \in F(R(x)+R(x'))$}; 
+%\node (D) at (3,0.5) {$!_c \in F(c)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$R(i) \eta_{c_1} +R(i') \eta_{c_1'}$} (B)
+(C) edge node[above]{$R(o) \eta_{c_2} + R(o) \eta_{c_2'}$} (B);
+\end{tikzpicture}
+\]
+where $$d_{\mathbb{E}(M) \otimes \mathbb{E}(N)} \maps 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{x \times x'} F(R(x)) \times F(R(x')) \xrightarrow{\phi_{R(x),R(x')}} F(R(x)+R(x')).$$ On the other hand, $M \otimes N$ is given by
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$L(c_1+c_1')$};
+\node (B) at (2,0) {$x+x'$};
+\node (C) at (4,0) {$L(c_2+c_2')$};
+%\node (D) at (3,0.5) {$!_c \in F(c)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$(i+i')\phi_{c_1,c_1'}^{-1}$} (B)
+(C) edge node[above]{$(o+o')\phi_{c_2,c_2'}^{-1}$} (B);
+\end{tikzpicture}
+\]
+and $\mathbb{E}(M \otimes N)$ is given by:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$c_1+c_1'$};
+\node (B) at (4,0) {$R(x+x')$};
+\node (C) at (8,0) {$c_2+c_2'$};
+\node (D) at (4,-0.5) {$d_{\mathbb{E}(M \odot N)} \in F(R(x+x')).$};
+%\node (D) at (3,0.5) {$!_c \in F(c)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$R((i+i')\phi_{c_1,c_1'}^{-1}) \eta_{c_1+c_1'}$} (B)
+(C) edge node[above]{$R((o+o')\phi_{c_2,c_2'}^{-1}) \eta_{c_2+c_2'}$} (B);
+\end{tikzpicture}
+\]
+We then have a 2-isomorphism $\mu_{M,N} \maps E(M) \otimes E(N) \xrightarrow{\sim} E(M \otimes N)$ in $F\lCsp$ given by:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (-2.5,0) {$c_1+c_1'$};
+\node (B) at (1,0) {$R(x)+R(x')$};
+\node (C) at (4.5,0) {$c_2+c_2'$};
+\node (A') at (-2.5,-1) {$c_1+c_1'$};
+\node (B') at (1,-1) {$R(x+x')$};
+\node (C') at (4.5,-1) {$c_2+c_2'$};
+\node (D) at (6.55,0) {$d_{\mathbb{E}(M) \otimes \mathbb{E}(N)} \in F(R(x)+R(x'))$};
+\node (D') at (6.55,-1) {$d_{\mathbb{E}(M \otimes N)} \in F(R(x+x'))$};
+\node (E) at (2,-1.5) {$\tau_\mu \maps F(\kappa)(d_{\mathbb{E}(M) \odot \mathbb{E}(N)}) \to d_{\mathbb{E}(M \odot N)}$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$R(i)\eta_{c_1} + R(i')\eta_{c_1'}$} (B)
+(C) edge node[above]{$R(o)\eta_{c_2} + R(o')\eta_{c_2'}$} (B)
+(A') edge node[above]{$R((i+i')\phi_{c_1,c_1'}^{-1}) \eta_{c_1+c_1'}$} (B')
+(C') edge node[above]{$R((o+o')\phi_{c_2,c_2'}^{-1}) \eta_{c_2+c_2'}$} (B')
+(A) edge node [left]{$1$} (A')
+(B) edge node [left]{$\kappa$} (B')
+(C) edge node [right]{$1$} (C');
+\end{tikzpicture}
+\]
+where $\kappa$ is the isomorphism which comes from $R \maps \X \to \A$ preserving finite colimits.
+
+The isomorphisms $\delta$ and $\mu$ satisfy the left and right unitality squares, associativity hexagon and braiding square. 
+%Kenny: I think this might be a good place to cut the monoidal stuff.
+%Christina: Deal! They are right below.
+
+\begin{comment}
+To see this, let $M_1,M_2$ and $M_3$ be horizontal 1-cells in $_L \lCsp(\X)$ given by:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$L(c_1)$};
+\node (B) at (1,0) {$x_1$};
+\node (C) at (2,0) {$L(c_1')$};
+\node (D) at (3,0) {$L(c_2)$};
+\node (E) at (4,0) {$x_2$};
+\node (F) at (5,0) {$L(c_2')$};
+\node (G) at (6,0) {$L(c_3)$};
+\node (H) at (7,0) {$x_3$};
+\node (I) at (8,0) {$L(c_3')$};
+%\node (D) at (3,0.5) {$!_c \in F(c)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i_1$} (B)
+(C) edge node[above]{$o_1$} (B)
+(D) edge node[above]{$i_2$} (E)
+(F) edge node[above]{$o_2$} (E)
+(G) edge node[above]{$i_3$} (H)
+(I) edge node[above]{$o_3$} (H);
+\end{tikzpicture}
+\]
+The left unitality square:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$1_{F\lCsp} \otimes \mathbb{E}(M_1)$};
+\node (B) at (3,0) {$\mathbb{E}(1_{ _L \lCsp(\X)}) \otimes \mathbb{E}(M_1)$};
+\node (C) at (0,-1) {$\mathbb{E}(M_1)$};
+\node (D) at (3,-1) {$\mathbb{E}(1_{ _L \lCsp(\X)} \otimes M_1)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$\delta \otimes 1$} (B)
+(B) edge node[right]{$\mu_{1,M_1}$} (D)
+(A) edge node[left]{$\lambda'$} (C)
+(D) edge node[above]{$\mathbb{E}(\lambda)$} (C);
+\end{tikzpicture}
+\]
+has an underlying diagram of maps of cospans given by:
+\[
+		\begin{tikzpicture}
+			\node (d) at (7.5,0) {$\mathbb{E}(1_{ _L \lCsp(\X)}) \otimes \mathbb{E}(M_1)$};
+			\node (a) at (-6,0) {$1_\A+c_1$};
+			\node (b) at (-0.5,0) {$R(L(1_\A)) + R(x_1)$};
+			\node (c) at (5,0) {$1_\A+c_1'$};
+			\node (d2) at (7.5,1) {$1_{F\lCsp} \otimes \mathbb{E}(M_1)$};
+			\node (a2) at (-6,1) {$1_\A+c_1$};
+			\node (b2) at (-0.5,1) {$1_\A+R(x_1)$};
+			\node (c2) at (5,1) {$1_\A+c_1'$};
+			\node (d3) at (7.5,2) {$\mathbb{E}(M_1)$};
+                                \node (a3) at (-6,2) {$c_1$};
+			\node (b3) at (-0.5,2) {$R(x_1)$};
+			\node (c3) at (5,2) {$c_1'$};
+			\node (d4) at (7.5,-1) {$\mathbb{E}(1_{ _L \lCsp(\X)} \otimes M_1)$};
+                                \node (a5) at (-6,-1) {$1_\A+c_1'$};
+			\node (b5) at (-0.5,-1) {$R(L(1_\A)+x_1)$};
+			\node (c5) at (5,-1) {$1_\A+c_1'$};
+			\node (d5) at (7.5,-2) {$\mathbb{E}(M_1)$};
+                                \node (a6) at (-6,-2) {$c_1$};
+			\node (b6) at (-0.5,-2) {$R(x_1)$};
+			\node (c6) at (5,-2) {$c_1'$};
+			\path[->,font=\scriptsize,>=angle 90]
+			(d2) edge node [left]{$\lambda$} (d3)
+			(d2) edge node [left] {$\delta \otimes 1$} (d)
+			(d) edge node [left] {$\mu_{1,M_1}$} (d4)
+			(d4) edge node [left] {$\mathbb{E}(\lambda)$} (d5)
+			(a) edge node[above]{$\eta_{1_\A}+R(i_1)\eta_{c_1}$} (b)
+			(c) edge node[above]{$\eta_{1_\A}+R(o_1)\eta_{c_1'}$} (b)
+                                (a2) edge node[above]{$1+R(i_1)\eta_{c_1}$} (b2)
+			(c2) edge node[above]{$1+R(o_1)\eta_{c_1'}$} (b2)
+                                (a2) edge node[left]{$1$} (a)
+                                (b2) edge node[left]{$\eta_{1_\A}+1$} (b)
+(b2) edge node[right]{$\tau_2$} (b)
+			(c2) edge node[right]{$1$} (c)
+                                (a3) edge node[above]{$R(i_1)\eta_{c_1}$} (b3)
+			(c3) edge node[above]{$R(o_1)\eta_{c_1'}$} (b3)
+                                (a2) edge node[left]{$\lambda_{\A}$} (a3)
+                                (b2) edge node[left]{$\lambda_{\A}$} (b3)
+(b2) edge node[right]{$\tau_1$} (b3)
+			(c2) edge node[right]{$\lambda_{\A}$} (c3)
+                                (a5) edge node[above]{$(\mu_{L(1_\A),d_1})(\eta_{1_\A}+R(i_1)\eta_{c_1})$} (b5)
+			(c5) edge node[above]{$(\mu_{L(1_\A),d_1})(\eta_{1_\A}+R(o_1)\eta_{c_1'})$} (b5)
+                                (a) edge node[left]{$1$} (a5)
+                                (b) edge node[left]{$\mu_{L(1_\A),x_1}$} (b5)
+(b) edge node[right]{$\tau_3$} (b5)
+			(c) edge node[right]{$1$} (c5)
+                                (a6) edge node[above]{$R(i_1)\eta_{c_1}$} (b6)
+			(c6) edge node[above]{$R(o_1)\eta_{c_1'}$} (b6)
+                                (a5) edge node[left]{$\lambda_{\A}$} (a6)
+                                (b5) edge node[left]{$R(\lambda_{\X})$} (b6)
+ (b5) edge node[right]{$\tau_4$} (b6)
+			(c5) edge node[right]{$\lambda_{\A}$} (c6);
+		\end{tikzpicture}
+	\]
+with the corresponding maps of decorations amounting to the following commutative diagram in $F(R(x_1))$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (-.5,0) {$F(\lambda_{\A})(!_{1_\A}+x_1)$};
+\node (C) at (4,0) {$F(R(\lambda_{\X})(\mu_{L(1_\A),x_1}))(!_{R(L(1_\A))} +x_1$)};
+\node (D) at (-.5,-1) {$x_1$};
+\node (E) at (4,-1) {$F(R(\lambda_\X))(x_{!+1})$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$F(R(\lambda_{\X})(\mu_{L(1_\A),x_1}))(\tau_2)$} (C)
+(A) edge node[left]{$\tau_1$} (D)
+(E) edge node[above]{$\tau_4$} (D)
+(C) edge node[right]{$F(R(\lambda_\X))(\tau_3)$} (E);
+\end{tikzpicture}
+\]
+where $x_{!+1}$ is the decoration $x_1$ on the object $R(L(1_\A)+x_1) \in \A$.
+The above square commutes because $$F(\lambda_\A)(!_{1_\A}+x_1) = F(R(\lambda_\X)(\mu_{L(1_\A),x_1})(\eta_{1_\A}+1))(!_{1_\A}+x_1)$$ as the corresponding left unitality square for the finite colimit preserving functor $R \maps (\X,1_\X,+) \to (\A,1_\A,+)$ commutes.
+The right unitality square is similar.
+The associator hexagon:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$(\mathbb{E}(M_1) \otimes \mathbb{E}(M_2)) \otimes \mathbb{E}(M_3)$};
+\node (B) at (3.5,0) {$\mathbb{E}(M_1 \otimes M_2) \otimes \mathbb{E}(M_3)$};
+\node (C) at (7,0) {$\mathbb{E}((M_1 \otimes M_2) \otimes M_3)$};
+\node (A') at (0,-1) {$\mathbb{E}(M_1) \otimes (\mathbb{E}(M_2) \otimes \mathbb{E}(M_3))$};
+\node (B') at (3.5,-1) {$\mathbb{E}(M_1) \otimes \mathbb{E}(M_2 \otimes M_3)$};
+\node (C') at (7,-1) {$\mathbb{E}(M_1 \otimes (M_2 \otimes M_3))$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$\mu_{M_1,M_2} \otimes 1$} (B)
+(B) edge node[above]{$\mu_{M_1 \otimes M_2,M_3}$} (C)
+(A') edge node[above]{$1 \otimes \mu_{M_2,M_3}$} (B')
+(B') edge node[above]{$\mu_{M_1,M_2 \otimes M_3}$} (C')
+(A) edge node [left]{$a'$} (A')
+(C) edge node [right]{$\mathbb{E}(a)$} (C');
+\end{tikzpicture}
+\]
+has underlying maps of cospans given by:
+\[
+		\begin{tikzpicture}
+\node(d) at (1.5,7) {$(\mathbb{E}(M_1) \otimes \mathbb{E}(M_2)) \otimes \mathbb{E}(M_3)$};
+\node (d2) at (1.5,8) {$\mathbb{E}(M_1 \otimes M_2) \otimes \mathbb{E}(M_3)$};
+\node (d3) at (1.5,9) {$\mathbb{E}((M_1 \otimes M_2) \otimes M_3)$};
+\node (d4) at (1.5,10) {$\mathbb{E}(M_1 \otimes (M_2 \otimes M_3))$};
+\node (d5) at (1.5,6) {$\mathbb{E}(M_1) \otimes (\mathbb{E}(M_2) \otimes \mathbb{E}(M_3))$};
+\node (d6) at (1.5,5) {$\mathbb{E}(M_1) \otimes \mathbb{E}(M_2 \otimes M_3)$};
+\node (d7) at (1.5,4) {$\mathbb{E}(M_1 \otimes (M_2 \otimes M_3))$};
+			\node (a) at (-4.25,0) {$(c_1+c_2)+c_3$};
+			\node (b) at (2.5,0) {$(R(x_1)+R(x_2))+R(x_3)$};
+			\node (c) at (9.25,0) {$(c_1'+c_2')+c_3'$};
+			\node (a2) at (-4.25,1) {$(c_1+c_2)+c_3$};
+			\node (b2) at (2.5,1) {$R(x_1+x_2)+R(x_3)$};
+			\node (c2) at (9.25,1) {$(c_1'+c_2')+c_3'$};
+                                \node (a3) at (-4.25,2) {$(c_1+c_2)+c_3$};
+			\node (b3) at (2.5,2) {$R((x_1+x_2)+x_3)$};
+			\node (c3) at (9.25,2) {$(c_1'+c_2')+c_3'$};
+                                \node (a4) at (-4.25,3) {$c_1+(c_2+c_3)$};
+			\node (b4) at (2.5,3) {$R(x_1+(x_2+x_3))$};
+			\node (c4) at (9.25,3) {$c_1' + (c_2' + c_3')$};
+                                \node (a5) at (-4.25,-1) {$c_1+(c_2+c_3)$};
+			\node (b5) at (2.5,-1) {$R(x_1)+(R(x_2)+R(x_3))$};
+			\node (c5) at (9.25,-1) {$c_1' + (c_2' + c_3')$};
+                                \node (a6) at (-4.25,-2) {$c_1+(c_2+c_3)$};
+			\node (b6) at (2.5,-2) {$R(x_1)+R(x_2+x_3)$};
+			\node (c6) at (9.25,-2) {$c_1' + (c_2' + c_3')$};
+                                \node (a7) at (-4.25,-3) {$c_1+(c_2+c_3)$};
+			\node (b7) at (2.5,-3) {$R(x_1+(x_2+x_3))$};
+			\node (c7) at (9.25,-3) {$c_1' + (c_2' + c_3')$};
+			\path[->,font=\scriptsize,>=angle 90]
+(d) edge node[left] {$\mu_{M_1,M_2} \otimes 1$} (d2)
+(d2) edge node[left] {$\mu_{M_1 \otimes M_2,M_3}$} (d3)
+(d3) edge node[left] {$\mathbb{E}(a)$} (d4)
+(d) edge node[left] {$a'$} (d5)
+(d5) edge node[left] {$1 \otimes \mu_{M_2,M_3}$} (d6)
+(d6) edge node[left] {$\mu_{M_1,M_2 \otimes M_3}$} (d7)
+			(a) edge node[above]{$(R(i_1)\eta_{c_1}+R(i_2)\eta_{c_2})+R(i_3)\eta_{c_3}$} (b)
+			(c) edge node[above]{$(R(o_1)\eta_{c_1'}+R(o_2)\eta_{c_2'})+R(o_3)\eta_{c_3'}$} (b)
+                                (a2) edge node[above]{$R(i_1+i_2)\eta_{c_1+c_2}+R(i_3)\eta_{c_3}$} (b2)
+			(c2) edge node[above]{$R(o_1+o_2)\eta_{c_1'+c_2'}+R(o_3)\eta_{c_3'}$} (b2)
+                                (a) edge node[left]{$1$} (a2)
+                                (b) edge node[left]{$\kappa + 1$} (b2)
+(b) edge node[right]{$\tau_1$} (b2)
+			(c) edge node[right]{$1$} (c2)
+                                (a3) edge node[above]{$R((i_1+i_2)+i_3)\eta_{(c_1+c_2)+c_3}$} (b3)
+			(c3) edge node[above]{$R((o_1+o_2)+o_3)\eta_{(c_1'+c_2')+c_3'}$} (b3)
+                                (a2) edge node[left]{$1$} (a3)
+                                (b2) edge node[left]{$\kappa$} (b3)
+(b2) edge node[right]{$\tau_2$} (b3)
+			(c2) edge node[right]{$1$} (c3)
+                                (a4) edge node[above]{$R(i_1+(i_2+i_3))\eta_{c_1+(c_2+c_3)}$} (b4)
+			(c4) edge node[above]{$R(o_1+(o_2+o_3))\eta_{c_1'+(c_2'+c_3')}$} (b4)
+                                (a3) edge node[left]{$a_\A$} (a4)
+                                (b3) edge node[left]{$R(a_\X)$} (b4)
+(b3) edge node[right]{$\tau_3$} (b4)
+			(c3) edge node[right]{$a_\A$} (c4)
+                                (a5) edge node[above]{$R(i_1)\eta_{c_1}+(R(i_2)\eta_{c_2}+R(i_3)\eta_{c_3})$} (b5)
+			(c5) edge node[above]{$R(o_1)\eta_{c_1'}+(R(o_2)\eta_{c_2'}+R(o_3)\eta_{c_3'})$} (b5)
+                                (a) edge node[left]{$a_\A$} (a5)
+                                (b) edge node[left]{$a_\A$} (b5)
+(b) edge node[right]{$\tau_4$} (b5)
+			(c) edge node[right]{$a_\A$} (c5)
+                                (a6) edge node[above]{$R(i_1)\eta_{c_1}+R(i_2+i_3)\eta_{c_2+c_3}$} (b6)
+			(c6) edge node[above]{$R(o_1)\eta_{c_1'}+R(o_2+o_3)\eta_{c_2'+c_3'}$} (b6)
+                                (a5) edge node[left]{$1$} (a6)
+                                (b5) edge node[left]{$1+\kappa$} (b6)
+ (b5) edge node[right]{$\tau_5$} (b6)
+			(c5) edge node[right]{$1$} (c6)
+                                (a7) edge node[above]{$R(i_1+(i_2+i_3))\eta_{c_1+(c_2+c_3)}$} (b7)
+			(c7) edge node[above]{$R(o_1+(o_2+o_3))\eta_{c_1'+(c_2'+c_3')}$} (b7)
+                                (a6) edge node[left]{$1$} (a7)
+                                (b6) edge node[left]{$\kappa$} (b7)
+(b6) edge node[right]{$\tau_6$} (b7)
+			(c6) edge node[right]{$1$} (c7);
+		\end{tikzpicture}
+	\]
+Here we have omitted the natural isomorphisms $\phi_{c_i,c_j} \maps L(c_i) + L(c_j) \to L(c_i + c_j)$ on the inward pointing morphisms which make up the legs of each cospan due to limited space.
+The corresponding maps of decorations amount to the following commutative diagram in $F(R(x_1+(x_2+x_3)))$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$F((\kappa)(1+\kappa)(a_\A))((x_1+x_2)+x_3)$};
+\node (B) at (5,0) {$F((R(a_\mathrm{X}))(\kappa))((x_1+x_2)+x_3)$};
+\node (C) at (5,-1) {$F(R(a_\mathrm{X}))((x_1+x_2)+x_3)$};
+\node (D) at (5,-2) {$x_1+(x_2+x_3)$};
+\node (E) at (0,-1) {$F((\kappa)(1+\kappa))((x_1+x_2)+x_3)$};
+\node (F) at (0,-2) {$F(\kappa)(x_1+(x_2+x_3))$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$F((R(a_\X))(\kappa))(\tau_1)$} (B)
+(B) edge node[right]{$F(R(a_\X))(\tau_2)$} (C)
+(C) edge node[right]{$\tau_3$} (D)
+(A) edge node[left]{$F((\kappa)(1+\kappa))(\tau_4)$} (E)
+(E) edge node[left]{$F(\kappa)(\tau_5)$} (F)
+(F) edge node[above]{$\tau_6$} (D);
+\end{tikzpicture}
+\]
+The above square commutes because $$F((\kappa)(1+\kappa)(a_\A))((x_1+x_2)+x_3) = F((R(a_\X))(\kappa)(\kappa+1))((x_1+x_2)+x_3)$$ as the corresponding associator hexagon for the finite colimit preserving functor $R \maps (\X,1_\X,+) \to (\A,1_\A,+)$ commutes.
+Lastly, the braiding square:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$\mathbb{E}(M_1) \otimes \mathbb{E}(M_2)$};
+\node (B) at (3,0) {$\mathbb{E}(M_2) \otimes \mathbb{E}(M_1)$};
+\node (C) at (0,-1) {$\mathbb{E}(M_1 \otimes M_2)$};
+\node (D) at (3,-1) {$\mathbb{E}(M_2 \otimes M_1)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$\beta'$} (B)
+(B) edge node[right]{$\mu_{M_2,M_1}$} (D)
+(A) edge node[left]{$\mu_{M_1,M_2}$} (C)
+(C) edge node[above]{$\mathbb{E}(\beta)$} (D);
+\end{tikzpicture}
+\]
+has underlying map of cospans given by:
+\[
+		\begin{tikzpicture}
+\node (d) at (7,0) {$\mathbb{E}(M_1) \otimes \mathbb{E}(M_2)$};
+\node (d2) at (7,1) {$\mathbb{E}(M_2) \otimes \mathbb{E}(M_1)$};
+\node (d3) at (7,2) {$\mathbb{E}(M_2 \otimes M_1)$};
+\node (d4) at (7,-1) {$\mathbb{E}(M_1 \otimes M_2)$};
+\node (d5) at (7,-2) {$\mathbb{E}(M_2 \otimes M_1)$};
+			\node (a) at (-4,0) {$c_1+c_2$};
+			\node (b) at (0.5,0) {$R(x_1)+R(x_2)$};
+			\node (c) at (5,0) {$c_1'+c_2'$};
+			\node (a2) at (-4,1) {$c_2+c_1$};
+			\node (b2) at (0.5,1) {$R(x_2)+R(x_1)$};
+			\node (c2) at (5,1) {$c_2'+c_1'$};
+                                \node (a3) at (-4,2) {$c_2+c_1$};
+			\node (b3) at (0.5,2) {$R(x_2+x_1)$};
+			\node (c3) at (5,2) {$c_2' + c_1'$};
+                                \node (a5) at (-4,-1) {$c_1+c_2$};
+			\node (b5) at (0.5,-1) {$R(x_1+x_2)$};
+			\node (c5) at (5,-1) {$c_1'+c_2'$};
+                                \node (a6) at (-4,-2) {$c_2+c_1$};
+			\node (b6) at (0.5,-2) {$R(x_2+x_1)$};
+			\node (c6) at (5,-2) {$c_2' + c_1'$};
+			\path[->,font=\scriptsize,>=angle 90]
+(d) edge node[left]{$\beta'$} (d2)
+(d2) edge node[left]{$\mu_{M_2,M_1}$}(d3)
+(d) edge node[left] {$\mu_{M_1,M_2}$}(d4)
+(d4)edge node[left]{$\mathbb{E}(\beta)$}(d5)
+			(a) edge node[above]{$R(i_1) \eta_{c_1} + R(i_2)\eta_{c_2}$} (b)
+			(c) edge node[above]{$R(o_1) \eta_{c_1'} + R(o_2) \eta_{c_2'}$} (b)
+                                (a2) edge node[above]{$R(i_2) \eta_{c_2} + R(i_1) \eta_{c_1}$} (b2)
+			(c2) edge node[above]{$R(o_2) \eta_{c_2'} + R(o_1) \eta_{c_1'}$} (b2)
+                                (a) edge node[left]{$\beta_\A$} (a2)
+                                (b) edge node[left]{$\beta_\A$} (b2)
+(b) edge node[right]{$\tau_1$} (b2)
+			(c) edge node[right]{$\beta_\A$} (c2)
+                                (a3) edge node[above]{$R(i_2+i_1)\eta_{c_2+c_1}$} (b3)
+			(c3) edge node[above]{$R(o_2+o_1)\eta_{c_2'+c_1'}$} (b3)
+                                (a2) edge node[left]{$1$} (a3)
+                                (b2) edge node[left]{$\kappa$} (b3)
+(b2) edge node[right]{$\tau_2$} (b3)
+			(c2) edge node[right]{$1$} (c3)
+                                (a5) edge node[above]{$R(i_1+i_2)\eta_{c_1+c_2}$} (b5)
+			(c5) edge node[above]{$R(o_1+o_2)\eta_{c_1'+c_2'}$} (b5)
+                                (a) edge node[left]{$1$} (a5)
+                                (b) edge node[left]{$\kappa$} (b5)
+(b) edge node[right]{$\tau_3$} (b5)
+			(c) edge node[right]{$1$} (c5)
+                                (a6) edge node[above]{$R(i_2+i_1)\eta_{c_2+c_1}$} (b6)
+			(c6) edge node[above]{$R(o_2+o_1)\eta_{c_2'+c_1'}$} (b6)
+                                (a5) edge node[left]{$\beta_\A$} (a6)
+                                (b5) edge node[left]{$R(\beta_\X)$} (b6)
+ (b5) edge node[right]{$\tau_4$} (b6)
+			(c5) edge node[right]{$\beta_\A$} (c6);
+		\end{tikzpicture}
+	\]
+Again, we have omitted the natural isomorphisms $\phi_{c_i,c_j}$ on the inward pointing morphisms on each cospan leg due to space restrictions.
+The corresponding maps of decorations amounting to the following commutative diagram in $F(R(x_2+x_1))$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (-.5,0) {$F((\kappa)(\beta_\A))(x_1+x_2)$};
+\node (C) at (4,0) {$F(\kappa)(x_2+x_1)$};
+\node (D) at (-.5,-1) {$F(R(\beta_\X))(x_1+x_2)$};
+\node (E) at (4,-1) {$x_2+x_1$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$F(\kappa)(\tau_1)$} (C)
+(A) edge node[left]{$F(R(\beta_\X))(\tau_3)$} (D)
+(D) edge node[above]{$\tau_4$} (E)
+(C) edge node[right]{$\tau_2$} (E);
+\end{tikzpicture}
+\]
+The above square commutes because $$F((\kappa)(\beta_\A))(x_1+x_2) = F((R(\beta_\X))(\kappa))(x_1+x_2)$$ as the corresponding braiding square for the finite colimit preserving functor $R \maps (\X,1_\X,+) \to (\A,1_\A,+)$ commutes.
+Thus the double functor $\mathbb{E} \maps _L\lCsp(\X) \to F\lCsp$ is symmetric monoidal.
+\end{comment}
+
+\end{proof}
+
+%!!!Kenny: Is this biequivalnce symmetric monoidal? Mike says yes, but it follows from a result that he has yet to officially publish. It's a result of a paper he's currently working on with someone.
+
+\begin{comment}
+We can also define the part of the double equivalence $\mathbb{G} \maps F\lCsp \to {_L \mathbb{C} \textnormal{sp}(\X)}$ which goes in the other direction: again, the object component of this double functor will be $\mathbb{G}_0 = \id_{\A}$.
+
+Given a horizontal 1-cell $M$ of $F\lCsp$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$c_1$};
+\node (B) at (1,0) {$c$};
+\node (C) at (2,0) {$c_2$};
+\node (D) at (1,-0.5) {$x \in F(c)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$I$} (B)
+(C) edge node[above]{$O$} (B);
+\end{tikzpicture}
+\]
+the image $\mathbb{G}(M)$ is the horizontal 1-cell in $_L \lCsp(\X)$ given by:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$L(c_1)$};
+\node (B) at (1,0) {$x$};
+\node (C) at (2,0) {$L(c_2)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$!_{c} L(I)$} (B)
+(C) edge node[above]{$!_{c} L(O)$} (B);
+\end{tikzpicture}
+\]
+where $!_{c} \maps L(c) \to x$ is the unique morphism from the trival decoration on $c$ given by $$!_{c} \mapseqq 1 \xrightarrow{\phi} F(0) \xrightarrow{F(!)} F(c)$$ to $x \in F(c)$.
+In other words, the trivial decoraction $!_{c}$ is initial in $F(c)$.
+Similarly, given a 2-morphism $(f,h,g,\tau) \maps M \to M'$ of $F\lCsp$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (D) at (1,0.5) {$x \in F(c)$};
+\node (D') at (1,-1.5) {$x' \in F(c')$};
+\node (A) at (0,0) {$c_1$};
+\node (B) at (1,0) {$c$};
+\node (C) at (2,0) {$c_2$};
+\node (A') at (0,-1) {$c_1'$};
+\node (B') at (1,-1) {$c'$};
+\node (C') at (2,-1) {$c_2'$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$I$} (B)
+(C) edge node[above]{$O$} (B)
+(A') edge node[above]{$I'$} (B')
+(C') edge node[above]{$O'$} (B')
+(A) edge node [left]{$f$} (A')
+(B) edge node [left]{$h$} (B')
+(C) edge node [right]{$g$} (C');
+\end{tikzpicture}
+\]
+$$\tau \maps F(h)(x) \to x'$$
+the image $\mathbb{G}(f,h,g,\tau)$ in $_L \lCsp(\X)$ is given by the 2-morphism:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$L(c_1)$};
+\node (B) at (1.5,0) {$x$};
+\node (C) at (3,0) {$L(c_2)$};
+\node (A') at (0,-1) {$L(c_1')$};
+\node (B') at (1.5,-1) {$x'$};
+\node (C') at (3,-1) {$L(c_2')$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$!_{c} L(I)$} (B)
+(C) edge node[above]{$!_{c} L(O)$} (B)
+(A') edge node[above]{$!_{c'} L(I')$} (B')
+(C') edge node[above]{$!_{c'} L(O')$} (B')
+(A) edge node [left]{$L(f)$} (A')
+(B) edge node [left]{$\alpha$} (B')
+(C) edge node [right]{$L(g)$} (C');
+\end{tikzpicture}
+\]
+where $\alpha \maps x \to x'$ is the morphism in the Grothendieck construction of $F$ given by $\alpha = (h \maps c \to c', \tau \maps F(h)(x) \to x')$.
+
+Next, we exhibit natural isomorphisms $\eta \maps \id_{ _L \lCsp(\X)} \cong \mathbb{G} \mathbb{E}$ and $\epsilon \maps \mathbb{E} \mathbb{G} \cong \id_{F\lCsp}$.
+Specifically, these are double natural isomorphisms given by double transformations \cite{Shul2} $\eta$ and $\epsilon$ whose object and arrow components are natural isomorphisms.
+
+First we compute the composites $\mathbb{G} \mathbb{E}$ and $\mathbb{E} \mathbb{G}$.
+On the object categories, both composites are $\id_\A$ and we have natural isomorphisms $\eta \maps \id_{\A} \cong \mathbb{G}_0 \mathbb{E}_0$ and $\epsilon \maps \mathbb{E}_0 \mathbb{G}_0 \cong \id_{\A}$.
+
+Given a horizontal 1-cell $M$ in $_L \mathbb{C} \textnormal{sp}(\X)$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$L(c_1)$};
+\node (B) at (1,0) {$x$};
+\node (C) at (2,0) {$L(c_2)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i$} (B)
+(C) edge node[above]{$o$} (B);
+\end{tikzpicture}
+\]
+the horizontal 1-cell $\mathbb{E}(M)$ is given by:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$c_1$};
+\node (B) at (1,0) {$R(x)$};
+\node (C) at (2,0) {$c_2$};
+\node (D) at (1,-0.5) {$x \in F(R(x))$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$R(i) \eta_{c_1}$} (B)
+(C) edge node[above]{$R(o) \eta_{c_2}$} (B);
+\end{tikzpicture}
+\]
+and then the horizontal 1-cell $\mathbb{G} \mathbb{E}(M)$ is given by:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$L(c_1)$};
+\node (B) at (1.5,0) {$x$};
+\node (C) at (3,0) {$L(c_2)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$!_{R(x)}L(R(i)\eta_{c_1})$} (B)
+(C) edge node[above]{$!_{R(x)}L(R(o)\eta_{c_2})$} (B);
+\end{tikzpicture}
+\]
+Then we can find a 2-isomorphism $\eta_M \maps M \xrightarrow{\sim} \mathbb{G}\mathbb{E}(M) $ in $_L \mathbb{C} \textnormal{sp}(\X)$ given by:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$L(c_1)$};
+\node (B) at (1.5,0) {$x$};
+\node (C) at (3,0) {$L(c_2)$};
+\node (A') at (0,-1) {$L(c_1)$};
+\node (B') at (1.5,-1) {$x$};
+\node (C') at (3,-1) {$L(c_2)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i$} (B)
+(C) edge node[above]{$o$} (B)
+(A') edge node[above]{$!_{R(x)}L(R(i)\eta_{c_1})$} (B')
+(C') edge node[above]{$!_{R(x)}L(R(o)\eta_{c_2})$} (B')
+(A) edge node [left]{$1$} (A')
+(B) edge node [left]{$1$} (B')
+(C) edge node [right]{$1$} (C');
+\end{tikzpicture}
+\]
+where
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (-0.5,0) {$L(c_1)$};
+\node (B) at (1,0) {$L(R(L(c_1)))$};
+\node (C) at (2.5,0) {$L(R(x))$};
+\node (D) at (3.5,0) {$x$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$L(\eta_{c_1})$} (B)
+(B) edge node[above]{$L(R(i))$} (C)
+(C) edge node[above]{$!_{R(x)}$} (D)
+(A) edge[bend right] node [above]{$i$} (D);
+\end{tikzpicture}
+\]
+commutes.
+
+On the other hand, given a horizontal 1-cell $N$ in $F\lCsp$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$c_1$};
+\node (B) at (1,0) {$c$};
+\node (C) at (2,0) {$c_2$};
+\node (D) at (1,-0.5) {$x \in F(c)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$I$} (B)
+(C) edge node[above]{$O$} (B);
+\end{tikzpicture}
+\]
+the horizontal 1-cell $\mathbb{G}(N)$ is given by:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$L(c_1)$};
+\node (B) at (1,0) {$x$};
+\node (C) at (2,0) {$L(c_2)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$!_c L(I)$} (B)
+(C) edge node[above]{$!_c L(O)$} (B);
+\end{tikzpicture}
+\]
+and then the horizontal 1-cell $\mathbb{E} \mathbb{G}(N)$ is given by:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$c_1$};
+\node (B) at (1.5,0) {$R(x)$};
+\node (C) at (3,0) {$c_2$};
+\node (D) at (1.5,-0.5) {$x \in F(R(x))$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$R(!_c L(I))\eta_{c_1}$} (B)
+(C) edge node[above]{$R(!_c L(O))\eta_{c_2}$} (B);
+\end{tikzpicture}
+\]
+Then we have a 2-isomorphism $\epsilon_N \maps \mathbb{E} \mathbb{G} (N) \xrightarrow{\sim} N$ in $F\lCsp$ given by:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (D) at (1.5,0.5) {$x \in F(R(x))$};
+\node (D') at (1.5,-1.5) {$x \in F(c)$};
+\node (A) at (0,0) {$c_1$};
+\node (B) at (1.5,0) {$R(x)$};
+\node (C) at (3,0) {$c_2$};
+\node (A') at (0,-1) {$c_1$};
+\node (B') at (1.5,-1) {$c$};
+\node (C') at (3,-1) {$c_2$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$R(!_c L(I))\eta_{c_1}$} (B)
+(C) edge node[above]{$R(!_c L(O))\eta_{c_2}$} (B)
+(A') edge node[above]{$I$} (B')
+(C') edge node[above]{$O$} (B')
+(A) edge node [left]{$1$} (A')
+(B) edge node [left]{$\hat{e}$} (B')
+(C) edge node [right]{$1$} (C');
+\end{tikzpicture}
+\]
+$$\tau \maps F(\hat{e})(x) \to x$$
+where 
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$c_1$};
+\node (B) at (1,0) {$R(L(c_1))$};
+\node (C) at (2.5,0) {$R(L(c))$};
+\node (D) at (3.5,0) {$R(x)$};
+\node (E) at (4.5,0) {$c$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$\eta_{c_1}$} (B)
+(B) edge node[above]{$R(L(I))$} (C)
+(C) edge node[above]{$R(!_c)$} (D)
+(D) edge node[above]{$\hat{e}$} (E)
+(A) edge[bend right] node [above]{$I$} (E);
+\end{tikzpicture}
+\]
+commutes.
+
+\end{comment}
+
+\section{Bicategorical and categorical aspects}
+\label{spinoffs}
+
+While double categories are a natural context for studying cospans, bicategories are more 
+familiar---and of course, mere \emph{categories} are even more so!   Luckily, all our results 
+phrased in the language of double categories have analogues for bicategories and categories.  
+We explain those here.
+
+As noted for example by Shulman \cite{Shulman2010}, any double category $\lX$ gives rise to a bicategory $\bX$ in which:
+\begin{itemize}
+\item objects are objects of $\lX$,
+\item morphisms are horizontal 1-cells of $\lX$,
+\item 2-morphisms are \define{globular} 2-morphisms of $\lX$, meaning 2-morphisms whose source and target vertical 1-morphisms are identities,
+\item composition of morphisms is given by horizontal composition of horizontal 1-cells in $\lX$,
+\item vertical and horizontal composition of 2-morphisms are given by vertical and horizontal
+composition of 2-morphisms in $\lX$.
+\end{itemize}
+Furthermore, any bicategory $\bX$ whatsoever gives rise to a category $\X$ in which:
+\begin{itemize}
+\item objects are objects of $\bX$,
+\item morphisms are isomorphism classes of morphisms of $\bX$.   
+\end{itemize}
+Thus, the double category $F\lCsp$ of structured cospans constructed in \cref{thm:decorated_cospans} automatically gives rise to a bicategory, which we call $F\bCsp$, and a category, which we call $F\Csp$.
+
+In \cref{DC} we gave conditions under which the double category $F\lCsp$ becomes symmetric
+monoidal.   We would like the bicategory $F\bCsp$ and the category $F\Csp$ to become symmetric
+monoidal under the same conditions, and indeed this is true.
+Shulman \cite[Thm.\ 1.2]{Shulman2010} showed that when $\lX$ is `fibrant', any symmetrical monoidal structure on $\lX$ gives one on $\bX$.
+We can apply this to decorated cospans as follows:
+
 \begin{lem}
@@
 \begin{proof}
-Let $f \maps c \to c'$ be a vertical 1-morphism in $F\lCsp$. We can lift $f$ to the companion horizontal 1-cell $\hat{f}$:
+Recall from \cref{defn:fibrant} that a double category is fibrant if every vertical 1-morphism has a `companion' and a `conjoint'.
+Let $f \maps c \to c'$ be a vertical 1-morphism in $F\lCsp$.
+We can lift $f$ to a companion horizontal 1-cell $\hat{f}$:
 \[
@@
 \]
+Just as $\hat{f}$ obeys the equations required of a companion, $\check{f}$ obeys the similar equations required of a conjoint.
 \end{proof}
 
-The property of being fibrant is what allows us to lift the monoidal structure from the object category of a double category to its arrow category and obtain a symmetric monoidal bicategory.
-The following result, which only requires fibrancy on vertical 1-isomorphisms (isofibrancy) is due to Shulman \cite{Shul}:
-
-\begin{lem}[Shulman]\label{Shul}
-Let $\mathbb{X}$ be an isofibrant symmetric monoidal pseudo double category. Then the horizontal bicategory $H(\mathbb{X})$ of $\mathbb{X}$ is a symmetric monoidal bicategory which has:
+\begin{thm}
+\label{thm:bicat}
+Let $\A$ be a category with finite colimits and $F \maps (\A, +) \to (\Cat,\times)$ a symmetric lax monoidal pseudofunctor. Then there exists a symmetric monoidal bicategory $F \mathbf{Csp}$ in which:
 \begin{enumerate}
-\item{objects as those of $\mathbb{X}$,}
-\item{morphisms as horizontal 1-cells of $\mathbb{X}$, and}
-\item{2-morphisms as globular 2-morphisms of $\mathbb{X}$.}
-\end{enumerate}
-\end{lem}
-
-\begin{thm}
-Let $\A$ be a category with finite colimits and $F \maps (\A, +) \to \Cat$ a symmetric lax monoidal pseudofunctor.
-Then there exists a symmetric monoidal bicategory $F \mathbf{Csp} \mapseqq H(F\lCsp)$ which has:
-\begin{enumerate}
-\item{objects as those of $\A$,}
-\item{morphisms as $F$-decorated cospans:
+\item objects are those of $\A$,
+\item morphisms are $F$-decorated cospans:
 \[
@@
 \node (C) at (2,0) {$b$};
-\node (D) at (4,0) {$d \in F(c)$};
+\node (D) at (4,0) {$d \in F(c)$,};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-and}
-\item{2-morphisms as maps of cospans in $\A$ of the form:
+\item a 2-morphism is a map of cospans in $\A$ 
 \[
@@
 \]
-together with a morphism $\tau \maps F(h)(d) \to d'$ in $F(c')$.}
+together with a morphism $\tau \maps F(h)(d) \to d'$ in $F(c')$.
 \end{enumerate}
@@
 \begin{proof}
-This follows immediately by applying \cref{Shul} to the fibrant symmetric monoidal double category $F\lCsp$.
+This follows by applying Shulman's result \cite[Thm.\ 1.2]{Shulman2010} to the fibrant symmetric monoidal double category $F\lCsp$.
 \end{proof}
 
-This symmetric monoidal bicategory $F\mathbf{Csp}$ is a superior version of the symmetric monoidal bicategory $F$Cospan$(\A)$ constructed earlier by the second author \cite{Courser} in that there is greater flexibility in what 2-morphisms are allowed.
+This symmetric monoidal bicategory $F\Csp$ is a superior version of the symmetric monoidal bicategory $F$Cospan$(\A)$ constructed earlier by the second author \cite{Courser}, in that there is greater flexibility in the allowed 2-morphisms.
 
@@
 
-We can then decategorify this symmetric monoidal bicategory to obtain a symmetric monoidal category similar to the one obtained using Fong's result, but with larger isomorphism classes:
+We can then decategorify this symmetric monoidal bicategory to obtain a symmetric monoidal category generalizing the kind considered by Fong \cite{Fong}:
 
 \begin{cor}
-Let $\A$ be a category with finite colimits and $F \maps (\A, +) \to \Cat$ a symmetric lax monoidal pseudofunctor.  Then there exists a symmetric monoidal category $F\textnormal{Csp}$ which has:
+Let $\A$ be a category with finite colimits and $F \maps (\A, +) \to (\Cat, \times)$ a symmetric lax monoidal pseudofunctor.  Then there exists a symmetric monoidal category $F\Csp$ in which:
 \begin{enumerate}
-\item{objects as those of $\A$ and}
-\item{morphisms as isomorphism classes of $F$-decorated cospans of $\A$, where an $F$-decorated cospan is given by a pair:
+\item objects are those of $\A$
+\item morphisms as isomorphism classes of $F$-decorated cospans of $\A$, where two
+$F$-decorated cospans
 \[
@@
 \]
-Given another $F$-decorated cospan:
 \[
@@
 \]
-these two $F$-decorated cospans are in the same isomorphism class if there exists an isomorphism $f \maps c \to c'$ such that following diagram commutes:
+are isomorphic if and only if there exists an isomorphism $f \maps c \to c'$ in $\A$ such that following diagram commutes:
 \[
@@
 \]
-and there exists an isomorphism $\tau \maps F(f)(d) \to d'$ in $F(c')$.}
+and there exists an isomorphism $\tau \maps F(f)(d) \to d'$ in $F(c')$.
 \end{enumerate}
 \end{cor}
-In this symmetric monoidal category, isomorphism classes are as they should morally be, and the instance of two graphs having different edge sets does not prevent them from being in the same isomorphism class due to the isomorphism $\tau$.
+
+In \cref{thm:equiv} we gave conditions under which the double category of \emph{decorated} cospans $F\lCsp$ is equivalent to the double category of \emph{structured} cospans ${}_L \lCsp(\int F)$.
+We now show that under the same conditions we get an equivalence of bicategories and of
+categories.
+
+We have just seen in \cref{thm:bicat} that the decorated cospan
+double category $F\lCsp$ gives rise to a bicategory $F\Csp$.   A similar result 
+is known for structured cospan double categories \cite[Cor.\ 3.10]{BC}.  Namely, if $\A$ and $\X$ are categories with (chosen???) finite colimits and $L \maps \A \to \X$ preserves colimits, the 
+the structured cospan double category ${}_L \lCsp(\X)$ is symmetric monoidal and cofibrant, so the resulting bicategory ${}_L \bCsp(\X)$ becomes symmetric monoidal as well.
+
+Another result of Shulman \cite{Shul2} is the following:
+\begin{lem}[Shulman, Prop.\ B.3]
+An equivalence of fibrant double categories induces a biequivalence of horizontal bicategories.
+\end{lem}
+
+\begin{cor}
+The bicategories $F\mathbf{Csp}$ and $H( {_L \lCsp(\X)})$ are biequivalent.
+\end{cor}
 
@@
 
-Regarding maps between symmetric monoidal double categories, consider another symmetric lax monoidal pseudofunctor $F' \maps \mathsf{A'} \to \Cat$%, we can obtain another symmetric monoidal double category $F' \lCsp$.
-a morphism from $F\lCsp$ to $F' \lCsp$ will then be a double functor $\mathbb{H} \maps F\lCsp \to F' \lCsp$ whose object component is given by a finite colimit preserving functor $\mathbb{H}_0 = H \maps \A \to \mathsf{A'}$ and whose arrow component is given by a functor $\mathbb{H}_1$ defined on horizontal 1-cells by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a$};
-\node (B) at (1,0) {$c$};
-\node (C) at (2,0) {$b$};
-\node (D) at (1,-0.5) {$d \in F(c)$};
-\node (E) at (2.75,0) {$\mapsto$};
-\node (A') at (3.5,0) {$H(a)$};
-\node (B') at (4.5,0) {$H(c)$};
-\node (C') at (5.5,0) {$H(b)$};
-\node (D') at (4.5,-0.5) {$\theta_c E(d) \phi \in F'(H(c))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i$} (B)
-(C) edge node[above]{$o$} (B)
-(A') edge node[above]{$H(i)$} (B')
-(C') edge node[above]{$H(o)$} (B');
-\end{tikzpicture}
-\]
-and on 2-morphisms by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$a$};
-\node (A') at (0,-0.5) {$a'$};
-\node (B) at (1,0.5) {$c$};
-\node (C) at (2,0.5) {$b$};
-\node (C') at (2,-0.5) {$b'$};
-\node (D) at (1,-0.5) {$c'$};
-\node (E) at (3,0.5) {$d \in F(c)$};
-\node (F) at (3,-0.5) {$d' \in F(c')$};
-\node (G) at (1,-1) {$\tau \maps F(h)(d) \to d'$};
-\node (A'') at (4.25,0.5) {$H(a)$};
-\node (A''') at (4.25,-0.5) {$H(a')$};
-\node (B'') at (5.25,0.5) {$H(c)$};
-\node (C'') at (6.25,0.5) {$H(b)$};
-\node (C''') at (6.25,-0.5) {$H(b')$};
-\node (D'') at (5.25,-0.5) {$H(c')$};
-\node (E'') at (8,0.5) {$\theta_c E(d) \phi \in F'(H(c))$};
-\node (F'') at (8,-0.5) {$\theta_{c'} E(d') \phi \in F'(H(c'))$};
-\node (G'') at (5.25,-1) {$E(\tau) \maps F'(H(h))(\theta_c E(d)\phi) \to (\theta_{c'}E(d')\phi)$};
-\node (H) at (3.5,0) {$\mapsto$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$$} (B)
-(C) edge node[above]{$$} (B)
-(A) edge node[left]{$f$} (A')
-(C) edge node[right]{$g$} (C')
-(A') edge node {$$} (D)
-(C') edge node {$$} (D)
-(B) edge node [left] {$h$} (D)
-(A'') edge node[above]{$$} (B'')
-(C'') edge node[above]{$$} (B'')
-(A'') edge node[left]{$H(f)$} (A''')
-(C'') edge node[right]{$H(g)$} (C''')
-(A''') edge node {$$} (D'')
-(C''') edge node {$$} (D'')
-(B'') edge node [left] {$H(h)$} (D'');
-\end{tikzpicture}
-\]
-where $E \maps \Cat \to \Cat$ is a symmetric lax monoidal pseudofuctor such that the following diagram commutes up to isomorphism $\theta \maps EF \Rightarrow F'H$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$\A$};
-\node (B) at (1,0) {$\Cat$};
-\node (C) at (0,-1) {$\mathsf{A'}$};
-\node (D) at (1,-1) {$\Cat$};
-\node (E) at (0.5,-0.5) {$\Swarrow \theta$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$F$} (B)
-(A) edge node[left]{$H$} (C)
-(B) edge node[right]{$E$} (D)
-(C) edge node[above]{$F'$} (D);
-\end{tikzpicture}
-\]
-
-\begin{comment}
-Recall that we can think of the object $d \in F(c)$ as a morphism $d \maps 1 \to F(c)$ and the functor $\tau \maps F(h)(d) \to d'$ of $F(c')$ as a natural transformation  in $\Cat$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,-0.5) {$1$};
-\node (B) at (1,0) {$F(c)$};
-\node (D) at (1,-1) {$F(c')$};
-\node (C) at (0.75,-0.5) {$\Swarrow \tau$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$d$} (B)
-(A) edge node[below]{$d'$} (D)
-(B) edge node[right]{$F(h)$} (D);
-\end{tikzpicture}
-\]
-Applying the symmetric lax monoidal pseudofunctor $E \maps \Cat \to \Cat$ to this diagram yields:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,-0.5) {$1 \xrightarrow{\phi} E(1)$};
-\node (B) at (2,0) {$E(F(c))$};
-\node (D) at (2,-1) {$E(F(c'))$};
-\node (C) at (1.5,-0.5) {$\Swarrow E(\tau)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$E(d)$} (B)
-(A) edge node[below]{$E(d')$} (D)
-(B) edge node[right]{$E(F(h))$} (D);
-\end{tikzpicture}
-\]
-Then because the above square commutes up to the isomorphism $\theta \maps EF \Rightarrow F'H$, we get:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,-0.5) {$1 \xrightarrow{\phi} E(1)$};
-\node (B) at (2,0) {$E(F(c))$};
-\node (D) at (2,-1) {$E(F(c'))$};
-\node (C) at (1.5,-0.5) {$\Swarrow E(\tau)$};
-\node (E) at (4,0) {$F'(H(c))$};
-\node (F) at (4,-1) {$F'(H(c'))$};
-\path[->,font=\scriptsize,>=angle 90]
-(B) edge node [above] {$\theta_c$} (E)
-(D) edge node [above] {$\theta_{c'}$} (F)
-(E) edge node [right] {$F'(H(h))$} (F)
-(A) edge node[above]{$E(d)$} (B)
-(A) edge node[below]{$E(d')$} (D)
-(B) edge node[right]{$E(F((h))$} (D);
-\end{tikzpicture}
-\]
-which results in a 2-morphism $E(\tau) \maps F'(H(h))(\theta_c E(d)\phi) \to (\theta_{c'} E(d')\phi)$ in $F'(H(c'))$.
-To check that the above recipe is functorial, given two vertically composable 2-morphisms in $F\lCsp$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$a$};
-\node (A') at (0,-0.5) {$a'$};
-\node (B) at (1.5,0.5) {$c$};
-\node (C) at (3,0.5) {$b$};
-\node (C') at (3,-0.5) {$b'$};
-\node (D) at (1.5,-0.5) {$c'$};
-\node (E) at (4.5,0.5) {$d \in F(c)$};
-\node (F) at (4.5,-0.5) {$d' \in F(c')$};
-\node (G) at (1.5,-1) {$\tau \maps F(h)(d) \to d'$};
-\node (A'') at (0,-1.5) {$a'$};
-\node (A''') at (0,-2.5) {$a''$};
-\node (B'') at (1.5,-1.5) {$c'$};
-\node (C'') at (3,-1.5) {$b'$};
-\node (C''') at (3,-2.5) {$b''$};
-\node (D'') at (1.5,-2.5) {$c''$};
-\node (E'') at (4.5,-1.5) {$d' \in F(c')$};
-\node (F'') at (4.5,-2.5) {$d'' \in F(c'')$};
-\node (G'') at (1.5,-3) {$\tau' \maps F(h')(d') \to d''$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$$} (B)
-(C) edge node[above]{$$} (B)
-(A) edge node[left]{$f$} (A')
-(C) edge node[right]{$g$} (C')
-(A') edge node [above]{$$} (D)
-(C') edge node [above]{$$} (D)
-(B) edge node [left] {$h$} (D)
-(A'') edge node[above]{$$} (B'')
-(C'') edge node[above]{$$} (B'')
-(A'') edge node[left]{$f'$} (A''')
-(C'') edge node[right]{$g'$} (C''')
-(A''') edge node [above]{$$} (D'')
-(C''') edge node [above]{$$} (D'')
-(B'') edge node [left] {$h'$} (D'');
-\end{tikzpicture}
-\]
-if we first compose these, the result is:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$a$};
-\node (A') at (0,-0.5) {$a''$};
-\node (B) at (1.5,0.5) {$c$};
-\node (C) at (3,0.5) {$b$};
-\node (C') at (3,-0.5) {$b''$};
-\node (D) at (1.5,-0.5) {$c''$};
-\node (E) at (4.5,0.5) {$d \in F(c)$};
-\node (F) at (4.5,-0.5) {$d'' \in F(c'')$};
-\node (G) at (1.5,-1) {$\tau ' \tau \maps F(h' h)(d) \to d''$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$$} (B)
-(C) edge node[above]{$$} (B)
-(A) edge node[left]{$f' f$} (A')
-(C) edge node[right]{$g' g$} (C')
-(A') edge node [above]{$$} (D)
-(C') edge node [above]{$$} (D)
-(B) edge node [left] {$h' h$} (D);
-\end{tikzpicture}
-\]
-and then the image of this 2-morphism under the double functor $\mathbb{H}$ is given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$H(a)$};
-\node (A') at (0,-0.5) {$H(a'')$};
-\node (B) at (1.5,0.5) {$H(c)$};
-\node (C) at (3,0.5) {$H(b)$};
-\node (C') at (3,-0.5) {$H(b'')$};
-\node (D) at (1.5,-0.5) {$H(c'')$};
-\node (E) at (5,0.5) {$\theta_c E(d) \phi \in F'(H(c))$};
-\node (F) at (5,-0.5) {$\theta_{c''} E(d'') \phi \in F'(H(c''))$};
-\node (G) at (1.5,-1) {$E(\tau ' \tau) \maps F'(H(h' h))(\theta_c E(d)\phi) \to (\theta_{c''}E(d'')\phi).$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$$} (B)
-(C) edge node[above]{$$} (B)
-(A) edge node[left]{$H(f' f)$} (A')
-(C) edge node[right]{$H(g' g)$} (C')
-(A') edge node [above]{$$} (D)
-(C') edge node [above]{$$} (D)
-(B) edge node [left] {$H(h' h)$} (D);
-\end{tikzpicture}
-\]
-On the other hand, applying the double functor $\mathbb{H}$ first gives:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$H(a)$};
-\node (A') at (0,-0.5) {$H(a')$};
-\node (B) at (1.5,0.5) {$H(c)$};
-\node (C) at (3,0.5) {$H(b)$};
-\node (C') at (3,-0.5) {$H(b')$};
-\node (D) at (1.5,-0.5) {$H(c')$};
-\node (E) at (5,0.5) {$\theta_c E(d) \phi \in F'(H(c))$};
-\node (F) at (5,-0.5) {$\theta_{c'} E(d') \phi \in F'(H(c'))$};
-\node (G) at (1.5,-1) {$E(\tau) \maps F'(H(h))(\theta_c E(d)\phi) \to (\theta_{c'} E(d')\phi)$};
-\node (A'') at (0,-1.5) {$H(a')$};
-\node (A''') at (0,-2.5) {$H(a'')$};
-\node (B'') at (1.5,-1.5) {$H(c')$};
-\node (C'') at (3,-1.5) {$H(b')$};
-\node (C''') at (3,-2.5) {$H(b'')$};
-\node (D'') at (1.5,-2.5) {$H(c'')$};
-\node (E'') at (5,-1.5) {$\theta_{c'} E(d') \phi \in F'(H(c'))$};
-\node (F'') at (5,-2.5) {$\theta_{c''} E(d'') \phi \in F'(H(c''))$};
-\node (G'') at (1.5,-3) {$E(\tau') \maps F'(H(h'))(\theta_{c'} E(d')\phi) \to (\theta_{c''}E(d'')\phi)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$$} (B)
-(C) edge node[above]{$$} (B)
-(A) edge node[left]{$H(f)$} (A')
-(C) edge node[right]{$H(g)$} (C')
-(A') edge node [above]{$$} (D)
-(C') edge node [above]{$$} (D)
-(B) edge node [left] {$H(h)$} (D)
-(A'') edge node[above]{$$} (B'')
-(C'') edge node[above]{$$} (B'')
-(A'') edge node[left]{$H(f')$} (A''')
-(C'') edge node[right]{$H(g')$} (C''')
-(A''') edge node [above]{$$} (D'')
-(C''') edge node [above]{$$} (D'')
-(B'') edge node [left] {$H(h')$} (D'');
-\end{tikzpicture}
-\]
-and then composing these gives:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$H(a)$};
-\node (A') at (0,-0.5) {$H(a'')$};
-\node (B) at (1.5,0.5) {$H(c)$};
-\node (C) at (3,0.5) {$H(b)$};
-\node (C') at (3,-0.5) {$H(b'')$};
-\node (D) at (1.5,-0.5) {$H(c'')$};
-\node (E) at (5,0.5) {$\theta_c E(d) \phi \in F'(H(c))$};
-\node (F) at (5,-0.5) {$\theta_{c''} E(d'') \phi \in F'(H(c''))$};
-\node (G) at (1.5,-1) {$E(\tau ' \tau) \maps F'(H(h' h))(\theta_c E(d)\phi) \to (\theta_{c''}E(d'')\phi).$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$$} (B)
-(C) edge node[above]{$$} (B)
-(A) edge node[left]{$H(f' f)$} (A')
-(C) edge node[right]{$H(g' g)$} (C')
-(A') edge node [above]{$$} (D)
-(C') edge node [above]{$$} (D)
-(B) edge node [left] {$H(h' h)$} (D);
-\end{tikzpicture}
-\]
-This double functor $\mathbb{H}$ satisfies the equations $S \mathbb{H}_1 = HS$ and $T \mathbb{H}_1=HT$.
-
-Given two composable horizontal 1-cells $M$ and $N$ in $F\lCsp$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a_1$};
-\node (B) at (1,0) {$c_1$};
-\node (C) at (2,0) {$b$};
-\node (D) at (1,-0.5) {$d_M \in F(c_1)$};
-\node (E) at (3,0) {$b$};
-\node (F) at (4,0) {$c_2$};
-\node (G) at (5,0) {$a_2$};
-\node (H) at (4,-0.5) {$d_N \in F(c_2)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i_1$} (B)
-(C) edge node[above]{$o_1$} (B)
-(E) edge node[above]{$i_2$} (F)
-(G) edge node[above]{$o_2$} (F);
-\end{tikzpicture}
-\]
-composing first gives $M \odot N$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a_1$};
-\node (B) at (1.5,0) {$c_1+_b c_2$};
-\node (C) at (3,0) {$a_2$};
-\node (D) at (1.5,-0.5) {$d_{M \odot N} \in F(c_1 +_b c_2)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$\psi j_{c_1} i_1$} (B)
-(C) edge node[above]{$\psi j_{c_2} o_2$} (B);
-\end{tikzpicture}
-\]
-where $$d \maps 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{d_1 \times d_2} F(c_1) \times F(c_2) \xrightarrow{\phi_{c_1,c_2}} F(c_1+c_2) \xrightarrow{F(j)}F(c_1 +_b c_2).$$ The image of this horizontal 1-cell is then given by $\mathbb{H}(M \odot N)$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$H(a_1)$};
-\node (B) at (2,0) {$H(c_1+_b c_2)$};
-\node (C) at (4,0) {$H(a_2)$};
-\node (D) at (2,-0.5) {$\mathbb{H}(M \odot N) = \theta_{c_1 +_b c_2}E(d_{M \odot N}) \phi \in F'(H(c_1 +_b c_2))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$H(\psi j_{c_1} i_1)$} (B)
-(C) edge node[above]{$H(\psi j_{c_2} o_2)$} (B);
-\end{tikzpicture}
-\]
-where $$\mathbb{H}(M \odot N) = \theta_{c_1 +_b c_2} E(d_{M \odot N}) \phi \maps 1 \xrightarrow{\phi} E(1) \xrightarrow{E(d)} E(F(c_1 +_b c_2)) \xrightarrow{\theta_{c_1 +_b c_2}} F'(H(c_1 +_b c_2)).$$ On the other hand, the image of each horizontal 1-cell under the double functor $\mathbb{H}$ is given respectively by $\mathbb{H}(M)$ and $\mathbb{H}(N)$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$H(a_1)$};
-\node (B) at (1,0) {$H(c_1)$};
-\node (C) at (2,0) {$H(b)$};
-\node (D) at (1,-0.5) {$\theta_{c_1} E(d_M)\phi \in F'(H(c_1))$};
-\node (E) at (3,0) {$H(b)$};
-\node (F) at (4,0) {$H(c_2)$};
-\node (G) at (5,0) {$H(a_2)$};
-\node (H) at (4,-0.5) {$\theta_{c_2} E(d_N) \phi \in F'(H(c_2))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$H(i_1)$} (B)
-(C) edge node[above]{$H(o_1)$} (B)
-(E) edge node[above]{$H(i_2)$} (F)
-(G) edge node[above]{$H(o_2)$} (F);
-\end{tikzpicture}
-\]
-Composing these then gives $\mathbb{H}(M) \odot \mathbb{H}(N)$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$H(a_1)$};
-\node (B) at (2.25,0) {$H(c_1)+_{H(b)} H(c_2)$};
-\node (C) at (4.5,0) {$H(a_2)$};
-\node (D) at (2.25,-0.5) {$d_{\mathbb{H}(M) \odot \mathbb{H}(N)} \in F'(H(c_1) +_{H(b)} H(c_2))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$\Psi j_{H(c_1)} H(i_1)$} (B)
-(C) edge node[above]{$\Psi j_{H(c_2)} H(o_2)$} (B);
-\end{tikzpicture}
-\]
-where $$\hspace{-.4in}\scriptstyle{d_{\mathbb{H}(M) \odot \mathbb{H}(N)} \maps 1 \xrightarrow{(\theta_{c_1} \times \theta_{c_2})(E(d_M) \times E(d_N)) \phi} F'(H(c_1)) \times F'(H(c_2)) \xrightarrow{\Phi_{H(c_1),H(c_2)}} F'(H(c_1)+ H(c_2)) \xrightarrow{F' (J)} F'(H(c_1) +_{H(b)} H(c_2)).}$$
-We then have a comparison constraint: $$\mathbb{H}_{M,N} \maps \mathbb{H}(M) \odot \mathbb{H}(N) \xrightarrow{\sim} \mathbb{H}(M \odot N)$$given by the globular 2-isomorphism:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$H(a_1)$};
-\node (A') at (0,-0.5) {$H(a_1)$};
-\node (B) at (2.5,0.5) {$H(c_1)+_{H(b)} H(c_2)$};
-\node (C) at (5,0.5) {$H(a_2)$};
-\node (C') at (5,-0.5) {$H(a_2)$};
-\node (D) at (2.5,-0.5) {$H(c_1 +_b c_2)$};
-\node (E) at (7.5,0.5) {$d_{\mathbb{H}(M) \odot \mathbb{H}(N)} \in F'(H(c_1)+_{H(b_1)}H(c_2))$};
-\node (F) at (7.5,-0.5) {$d_{\mathbb{H}(M \odot N)} \in F'(H(c_1 +_b c_2))$};
-\node (G) at (2.5,-1) {$\tau_{\kappa^{-1}} \maps F'(\kappa^{-1})(d_{\mathbb{H}(M) \odot \mathbb{H}(N)}) \to d_{\mathbb{H}(M \odot N)}.$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$\Psi j_{H(c_1)} H(i_1)$} (B)
-(C) edge node[above]{$\Psi j_{H(c_2)} H(o_2)$} (B)
-(A) edge node[left]{$1$} (A')
-(C) edge node[right]{$1$} (C')
-(A') edge node [above]{$H(\psi j_{c_1} i_1)$} (D)
-(C') edge node [above]{$H(\psi j_{c_2} o_2)$} (D)
-(B) edge node [left] {$\kappa^{-1}$} (D);
-\end{tikzpicture}
-\]
-where $\kappa$ is the isomorphism $$\kappa \maps H(c_1 +_b c_2) \xrightarrow{\sim} H(c_1) +_{H(b)} H(c_2)$$ which comes from the finite colimit preserving functor $H \maps \A \to \mathsf{A'}$.
-The above diagram commutes by a similar argument to the one used in Theorem \cref{Equiv}.
-Similarly, for every object $c \in \A$, we have a unit comparison constraint $$\mathbb{H}_U \maps U_{\mathbb{H}(c)} \to \mathbb{H}(U_c)$$ given by the globular 2-isomorphism:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$H(c)$};
-\node (A') at (0,-0.5) {$H(c)$};
-\node (B) at (1.5,0.5) {$H(c)$};
-\node (C) at (3,0.5) {$H(c)$};
-\node (C') at (3,-0.5) {$H(c)$};
-\node (D) at (1.5,-0.5) {$H(c)$};
-\node (E) at (4.5,0.5) {$!_{H(c)} \in F'(H(c))$};
-\node (F) at (4.5,-0.5) {$\theta_c E(!_c) \phi \in F'(H(c))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$1$} (B)
-(C) edge node[above]{$1$} (B)
-(A) edge node[left]{$1$} (A')
-(C) edge node[right]{$1$} (C')
-(A') edge node [above]{$1$} (D)
-(C') edge node [above]{$1$} (D)
-(B) edge node [left] {$1$} (D);
-\end{tikzpicture}
-\]
-where the morphism of decorations is the morphism $\tau \maps !_{H(c)} \to (\theta_c E(!_c) \phi)$ in $F'(H(c))$.
-These comparison constrains satisfy the coherence axioms of a monoidal category, namely:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$(\mathbb{H}(M) \odot \mathbb{H}(N)) \odot \mathbb{H}(P)$};
-\node (B) at (0,-0.5) {$\mathbb{H}(M \odot N) \odot \mathbb{H}(P)$};
-\node (C) at (0,-1.5) {$\mathbb{H}((M \odot N) \odot P)$};
-\node (A') at (3,0.5) {$\mathbb{H}(M) \odot (\mathbb{H}(N) \odot \mathbb{H}(P))$};
-\node (B') at (3,-0.5) {$\mathbb{H}(M) \odot \mathbb{H}(N \odot P)$};
-\node (C') at (3,-1.5) {$\mathbb{H}(M \odot (N \odot P))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[left]{$\mathbb{H}_{M,N} \odot 1$} (B)
-(B) edge node[left]{$\mathbb{H}_{M \odot N,P}$} (C)
-(A) edge node[above]{$a$} (A')
-(C) edge node [above] {$\mathbb{H}(a')$} (C')
-(B') edge node [right] {$\mathbb{H}_{M,N \odot P}$} (C')
-(A') edge node [right]{$1 \odot \mathbb{H}_{N,P}$} (B');
-\end{tikzpicture}
-\]
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$U_{\mathbb{H}(a)} \odot \mathbb{H}(M)$};
-\node (B) at (2.5,0) {$\mathbb{H}(U_a) \odot \mathbb{H}(M)$};
-\node (C) at (0,-1) {$\mathbb{H}(M)$};
-\node (D) at (2.5,-1) {$\mathbb{H}(U_a \odot M)$};
-\node (A') at (5,0) {$\mathbb{H}(M) \odot U_{\mathbb{H}(b)}$};
-\node (B') at (7.5,0) {$\mathbb{H}(M) \odot \mathbb{H}(U_b)$};
-\node (C') at (5,-1) {$\mathbb{H}(M)$};
-\node (D') at (7.5,-1) {$\mathbb{H}(M \odot U_b)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$\mathbb{H}_U \odot 1$} (B)
-(A) edge node[left]{$\lambda$} (C)
-(B) edge node[right]{$\mathbb{H}_{U_a,M}$} (D)
-(D) edge node[above]{$\mathbb{H}(\lambda')$} (C)
-(A') edge node[above]{$1 \odot \mathbb{H}_U$} (B')
-(A') edge node[left]{$\rho$} (C')
-(B') edge node[right]{$\mathbb{H}_{M,U_b}$} (D')
-(D') edge node[above]{$\mathbb{H}(\rho')$} (C');
-\end{tikzpicture}
-\]
-The diagrams involving the morphisms of decorations are similar to those in Theorem \cref{DC}.
-This shows that $\mathbb{H}=(H,E,\theta)$ is a double functor.
-Next we show that this double functor is symmetric monoidal.
-First, that the object component $\mathbb{H}_0=H$ is symmetric monoidal is clear as $H \maps \A \to \A'$ preserves finite colimits.
-As for the arrow component $\mathbb{H}_1$, given two horizontal 1-cells $M_1$ and $M_2$ in $F\lCsp$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a_1$};
-\node (B) at (1,0) {$c_1$};
-\node (C) at (2,0) {$b_1$};
-\node (D) at (1,-0.5) {$d_{M_1}\in F(c_1)$};
-\node (E) at (3,0) {$a_2$};
-\node (F) at (4,0) {$c_2$};
-\node (G) at (5,0) {$b_2$};
-\node (H) at (4,-0.5) {$d_{M_2} \in F(c_2)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i_1$} (B)
-(C) edge node[above]{$o_1$} (B)
-(E) edge node[above]{$i_2$} (F)
-(G) edge node[above]{$o_2$} (F);
-\end{tikzpicture}
-\]
-their tensor product $M_1 \otimes M_2$ in $F\lCsp$ is given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a_1+a_2$};
-\node (B) at (1.5,0) {$c_1+c_2$};
-\node (C) at (3,0) {$b_1+b_2$};
-\node (D) at (1.5,-0.5) {$d_{M_1 \otimes M_2} \in F(c_1+c_2)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i_1+i_2$} (B)
-(C) edge node[above]{$o_1+o_2$} (B);
-\end{tikzpicture}
-\]
-$$d_{M_1 \otimes M_2} \maps 1 \xrightarrow{d_1 \times d_2} F(c_1) \times F(c_2) \xrightarrow{\phi_{c_1,c_2}} F(c_1+c_2)$$
-and the image of this horizontal 1-cell under the double functor $\mathbb{H}$ is $\mathbb{H}(M_1 \otimes M_2)$ given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$H(a_1+a_2)$};
-\node (B) at (2,0) {$H(c_1+c_2)$};
-\node (C) at (4,0) {$H(b_1+b_2)$};
-\node (D) at (2,-0.5) {$d_{\mathbb{H}(M_1 \otimes M_2)} = \theta_{c_1+c_2} E(d_{M_1 \otimes M_2})\phi \in F'(H(c_1+c_2))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$H(i_1+i_2)$} (B)
-(C) edge node[above]{$H(o_1+o_2)$} (B);
-\end{tikzpicture}
-\]
-On the other hand, the image of $M_1$ and $M_2$ is given by $\mathbb{H}(M_1)$ and $\mathbb{H}(M_2)$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$H(a_1)$};
-\node (B) at (1.5,0) {$H(c_1)$};
-\node (C) at (3,0) {$H(b_1)$};
-\node (D) at (1.5,-0.5) {$d_{\mathbb{H}(M_1)} = \theta_{c_1}E(d_{M_1})\phi \in F'(H(c_1))$};
-\node (E) at (4.5,0) {$H(a_2)$};
-\node (F) at (6,0) {$H(c_2)$};
-\node (G) at (7.5,0) {$H(b_2)$};
-\node (H) at (6,-0.5) {$d_{\mathbb{H}(M_2)} = \theta_{c_2}E(d_{M_2})\phi \in F'(H(c_2))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$H(i_1)$} (B)
-(C) edge node[above]{$H(o_1)$} (B)
-(E) edge node[above]{$H(i_2)$} (F)
-(G) edge node[above]{$H(o_2)$} (F);
-\end{tikzpicture}
-\]
-and their tensor product $\mathbb{H}(M_1) \otimes \mathbb{H}(M_2)$ is given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$H(a_1)+H(a_2)$};
-\node (B) at (2.5,0) {$H(c_1)+H(c_2)$};
-\node (C) at (5,0) {$H(b_1)+H(b_2)$};
-\node (D) at (2.5,-0.5) {$d_{\mathbb{H}(M_1) \otimes \mathbb{H}(M_2)} \in F'(H(c_1)+H(c_2))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$H(i_1)+H(i_2)$} (B)
-(C) edge node[above]{$H(o_1)+H(o_2)$} (B);
-\end{tikzpicture}
-\]
-$$\hspace{-.4in} \scriptstyle{d_{\mathbb{H}(M_1) \otimes \mathbb{H}(M_2)} \maps 1 \xrightarrow{(\phi \times \phi)(\lambda^{-1} \times \lambda^{-1})} E(1) \times E(1) \xrightarrow{(\theta_{c_1} \times \theta_{c_2})(E(d_{M_1}) \times E(d_{M_2}))} F'(H(c_1)) \times F'(H(c_2)) \xrightarrow{\Phi_{H(c_1),H(c_2)}} F' (H(c_1)+H(c_2)).}$$  We then have a natural 2-isomorphism $\mu_{M_1,M_2} \maps \mathbb{H}(M_1) \otimes \mathbb{H}(M_2) \to \mathbb{H}(M_1 \otimes M_2)$ in $F'\lCsp$ given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$H(a_1)+H(a_2)$};
-\node (A') at (0,-0.5) {$H(a_1+a_2)$};
-\node (B) at (2.5,0.5) {$H(c_1)+H(c_2)$};
-\node (C) at (5,0.5) {$H(b_1)+H(b_2)$};
-\node (C') at (5,-0.5) {$H(b_1+b_2)$};
-\node (D) at (2.5,-0.5) {$H(c_1+c_2)$};
-\node (E) at (2.5,1) {$d_{\mathbb{H}(M_1) \otimes \mathbb{H}(M_2)} \in F'(H(c_1)+H(c_2))$};
-\node (F) at (2.5,-1) {$d_{\mathbb{H}(M_1 \otimes M_2)} \in F'(H(c_1+c_2))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$H(i_1)+H(i_2)$} (B)
-(C) edge node[above]{$H(o_1)+H(o_2)$} (B)
-(A) edge node[left]{$\kappa$} (A')
-(C) edge node[left]{$\kappa$} (C')
-(A') edge node [above]{$H(i_1+i_2)$} (D)
-(C') edge node [above]{$H(o_1+o_2)$} (D)
-(B) edge node [left] {$\kappa$} (D);
-\end{tikzpicture}
-\]
-$$\tau_\kappa \maps F'(\kappa)(d_{\mathbb{H}(M_1) \otimes \mathbb{H}(M_2)}) \to d_{\mathbb{H}(M_1 \otimes M_2)}$$
-where $\kappa$ denotes the isomorphism arising from $H$ preserving finite colimits.
-This natural 2-isomorphism together with the associators of $F\lCsp$ and $F'\lCsp$, respectively $\alpha$ and $\alpha'$, make the following diagram commute:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$(\mathbb{H}(M_1) \otimes \mathbb{H}(M_2)) \otimes \mathbb{H}(M_3)$};
-\node (B) at (0,-0.5) {$\mathbb{H}(M_1 \otimes M_2) \otimes \mathbb{H}(M_3)$};
-\node (C) at (0,-1.5) {$\mathbb{H}((M_1 \otimes M_2) \otimes M_3)$};
-\node (A') at (4,0.5) {$\mathbb{H}(M_1) \otimes (\mathbb{H}(M_2) \otimes \mathbb{H}(M_3))$};
-\node (B') at (4,-0.5) {$\mathbb{H}(M_1) \otimes \mathbb{H}(M_2 \otimes M_3)$};
-\node (C') at (4,-1.5) {$\mathbb{H}(M_1 \otimes (M_2 \otimes M_3))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[left]{$\mu_{M_1,M_2} \otimes 1$} (B)
-(B) edge node[left]{$\mu_{M_1 \otimes M_2,M_3}$} (C)
-(A) edge node[above]{$\alpha'$} (A')
-(C) edge node [above] {$\mathbb{H}(\alpha)$} (C')
-(B') edge node [right] {$\mu_{M_1,M_2 \otimes M_3}$} (C')
-(A') edge node [right]{$1 \otimes \mu_{M_2 \otimes M_3}$} (B');
-\end{tikzpicture}
-\]
-with the corresponding diagram of decorations in $F'(H(c_1+(c_2+c_3)))$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$F'(\alpha \kappa \kappa)(d_{(\mathbb{H}(M_1) \otimes \mathbb{H}(M_2)) \otimes \mathbb{H}(M_3)})$};
-\node (B) at (0,-0.5) {$F'(\alpha \kappa)(d_{\mathbb{H}(M_1 \otimes M_2) \otimes \mathbb{H}(M_3)})$};
-\node (C) at (0,-1.5) {$F'(\alpha)(d_{\mathbb{H}((M_1 \otimes M_2) \otimes M_3)})$};
-\node (A') at (5,0.5) {$F'(\kappa \kappa)(d_{\mathbb{H}(M_1) \otimes (\mathbb{H}(M_2) \otimes \mathbb{H}(M_3))})$};
-\node (B') at (5,-0.5) {$F'(\kappa)(d_{\mathbb{H}(M_1) \otimes \mathbb{H}(M_2 \otimes M_3)})$};
-\node (C') at (5,-1.5) {$d_{\mathbb{H}(M_1 \otimes (M_2 \otimes M_3))}$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[left]{$F'(\alpha \kappa)(\tau_\kappa + 1)$} (B)
-(B) edge node[left]{$F'(\alpha)(\tau_\kappa)$} (C)
-(A) edge node[above]{$F'(\kappa \kappa)(\tau_{\alpha'})$} (A')
-(C) edge node [above] {$\tau_\alpha$} (C')
-(B') edge node [right] {$\tau_\kappa$} (C')
-(A') edge node [right]{$F'(\kappa)(1+\tau_\kappa)$} (B');
-\end{tikzpicture}
-\]
-where $$F'(\alpha \kappa \kappa)(d_{(\mathbb{H}(M_1) \otimes \mathbb{H}(M_2)) \otimes \mathbb{H}(M_3)}) = F'(\kappa \kappa \alpha')(d_{(\mathbb{H}(M_1) \otimes \mathbb{H}(M_2)) \otimes \mathbb{H}(M_3)})$$
-as the corresponding hexagon for the finite colimit preserving functor $H \maps \A \to \mathsf{A'}$ commutes.
-The map $\mu_{M_1,M_2}$ is also compatible with the braidings $\beta$ and $\beta'$ of $F \lCsp_1$ and $F' \lCsp_1$, respectively, and make the necessary square commute as a consequence of the corresponding commutative square involving braidings from the finite colimit preserving functor $H \maps \A \to \mathsf{A'}$.
-
-We also have that the monoidal unit of $F\lCsp_1$ is given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$1_\A$};
-\node (B) at (1,0) {$1_\A$};
-\node (C) at (2,0) {$1_\A$};
-\node (D) at (1,-0.5) {$!_{1_\A} \in F(1_\A)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$1$} (B)
-(C) edge node[above]{$1$} (B);
-\end{tikzpicture}
-\]
-where $1_\A$ is the monoidal unit of the cocartesian category $\A$. The image of this horizontal 1-cell under $\mathbb{H}$ is given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$H(1_\A)$};
-\node (B) at (1,0) {$H(1_\A)$};
-\node (C) at (2,0) {$H(1_\A)$};
-%\node (E) at (3,0) {$=$};
-%\node (F) at (4,0) {$1_\mathsf{A'}$};
-%\node (G) at (5,0) {$1_\mathsf{A'}$};
-%\node (H) at (6,0) {$1_\mathsf{A'}$};
-%\node (I) at (5,-0.5) {$!_{1_{\mathsf{A'}}} \in F'(1_{\mathsf{A'}})$};
-\node (D) at (1,-0.5) {$\theta_{1_\A}E(!_{1_\A}) \phi \in F'(H(1_\A))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$1$} (B)
-(C) edge node[above]{$1$} (B);
-%(F) edge node[above]{$1$} (G)
-%(H) edge node[above]{$1$} (G);
-\end{tikzpicture}
-\]
-as $H$ preserves finite colimits. We then have a 2-isomorphism in $F'\lCsp$ given by: $$\mu \maps 1_{F'\lCsp_1} \to \mathbb{H}(1_{F\lCsp_1})$$ 
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$1_{\mathsf{A'}}$};
-\node (A') at (0,-0.5) {$H(1_\A)$};
-\node (B) at (1.5,0.5) {$1_{\mathsf{A'}}$};
-\node (C) at (3,0.5) {$1_{\mathsf{A'}}$};
-\node (C') at (3,-0.5) {$H(1_\A)$};
-\node (D) at (1.5,-0.5) {$H(1_\A)$};
-\node (E) at (5,0.5) {$!_{1_\mathsf{A'}} \in F'(1_\mathsf{A'})$};
-\node (F) at (5,-0.5) {$\theta_{1_\A} E(!_{1_\A}) \phi \in F'(H(1_\A))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$1$} (B)
-(C) edge node[above]{$1$} (B)
-(A) edge node[left]{$\kappa$} (A')
-(C) edge node[right]{$\kappa$} (C')
-(A') edge node [above]{$1$} (D)
-(C') edge node [above]{$1$} (D)
-(B) edge node [left] {$\kappa$} (D);
-\end{tikzpicture}
-\]
-together with the morphism $\tau_\mu \maps F'(\kappa)(!_{1_\mathsf{A'}}) \to (\theta_{1_\A} E(!_{1_\A})\phi)$ in $F'(H(1_\A))$.
-The following square then commutes for any horizontal 1-cell $M$ of $F \lCsp$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$1_\mathsf{A'} \otimes \mathbb{H}(M)$};
-\node (B) at (2.5,0) {$\mathbb{H}(1_\A) \otimes \mathbb{H}(M)$};
-\node (C) at (0,-1) {$\mathbb{H}(M)$};
-\node (D) at (2.5,-1) {$\mathbb{H}(1_\A \otimes M)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$\mu \otimes 1$} (B)
-(A) edge node[left]{$\ell$} (C)
-(B) edge node[right]{$\mu_{1_\mathrm{A},M}$} (D)
-(D) edge node[above]{$\mathbb{H}(\ell')$} (C);
-\end{tikzpicture}
-\]
-where we have abbreviated the monoidal units of $F\lCsp_1$ and $F'\lCsp_1$ as $1_\A$ and $1_\mathsf{A'}$, respectively. The diagram of corresponding decorations is given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$F'(\ell)(d_{!_{1_\mathsf{A'}}} \otimes d_{\mathbb{H}(M)})$};
-\node (B) at (0,-0.5) {$d_{\mathbb{H}(M)}$};
-\node (A') at (4,0.5) {$F'(H(\ell') \kappa)(d_{!_{\mathbb{H}(1_\A)}}\otimes d_{\mathbb{H}(M)})$};
-\node (B') at (4,-0.5) {$F'(H(\ell'))(d_{\mathbb{H}(1_\A \otimes M)})$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[left]{$\tau_\ell$} (B)
-(A) edge node[above]{$F'(H(\ell')\kappa)(\tau_{\mu \otimes 1})$} (A')
-(A') edge node [right]{$F'(H(\ell'))(\tau_\kappa)$} (B')
-(B') edge node [above] {$\tau_{H(\ell')}$} (B);
-\end{tikzpicture}
-\]
-where $$F'(\ell)(d_{!_{1_\mathsf{A'}}} \otimes d_{\mathbb{H}(M)})=F'(H(\ell')\kappa(\mu \otimes 1))(d_{!_{1_\mathsf{A'}}} \otimes d_{\mathbb{H}(M)})$$ since the corresponding square involving left unitors for the finite colimit preserving functor $H \maps \A \to \mathsf{A'}$ commutes.
-The other square involving the right unitors $r$ and $r'$ is similar.
-Note that because the comparison constraints $\mu$ and $\mu_{(\_ , \_)}$ are both isomorphisms, the symmetric monoidal double functor $\mathbb{H}$ is strong.
-
-\end{comment}
-
-\begin{thm}
-Given two finitely cocomplete categories $\A$ and $\A'$, two symmetric lax monoidal pseudofunctors $F \maps \A \to \Cat$ and $F' \maps \A' \to \Cat$, a finite colimit preserving functor $H \maps \A \to \A'$, a symmetric lax monoidal pseudofunctor $E \maps \Cat \to \Cat$ and a 2-isomorphism $\theta \maps EF \Rightarrow F' H$ as in the following diagram, the triple $(H,E,\theta)$ induces a symmetric monoidal (strong) double functor $\mathbb{H} \maps F\lCsp \to F'\lCsp$ as defined above.
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$\A$};
-\node (B) at (1,0) {$\Cat$};
-\node (C) at (0,-1) {$\mathsf{A'}$};
-\node (D) at (1,-1) {$\Cat$};
-\node (E) at (0.5,-0.5) {$\Swarrow \theta$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$F$} (B)
-(A) edge node[left]{$H$} (C)
-(B) edge node[right]{$E$} (D)
-(C) edge node[above]{$F'$} (D);
-\end{tikzpicture}
-\]
-\end{thm}
-
-Details of the constructions and the proof of the above theorem can be found at \cite{CourserThesis}.
-
-%\newpage
-%Scratch work for Petri net problem
-%\newline
-%Let $P = (s_1,t_1 \maps T_1 \to \mathbb{N}(S_1))$ and $Q = (s_2,t_2 \maps T_2 \to \mathbb{N}(S_2))$.
-We want to show that the functor $F \maps \textrm{Petri} \to \textrm{CMC}$ preserves pushouts of cospans of the form $$P \xleftarrow{} L(Y) \xrightarrow{} Q$$ meaning that $F(P+_{L(Y)} Q) \cong F(P) +_{F(L(Y))} F(Q)$.
-Here, $L \maps \textrm{Set} \to \textrm{Petri}$ is the left adjoint which sends a set $Y$ to the discrete Petri net with $Y$ as its set of species and no transitions.
-Thus no transitions are identified in the pushout $P+_{L(Y)} Q$, and so the set of transitions of $P+_{L(Y)} Q$ is given by $$\textrm{Trans}(P)+\textrm{Trans}(Q).$$ Thus the morphisms \emph{contributed from transitions} in both $F(P+_{L(Y)}Q)$ and $F(P)+_{F(L(Y)} F(Q)$ are the same.
-If we can show that $$\textrm{Ob}(F(P+_{L(Y)}Q) \cong \textrm{Ob}(F(P)+_{F(L(Y))} F(Q)$$ then the remaining morphisms in each commutative monoidal category will be canonically isomorphic as sets.
-
-%Now, what can we say about $\textrm{Ob}(F(P+_{L(Y)}Q))$ vs.
-$\textrm{Ob}(F(P)+_{F(L(Y))} F(Q))$?
-Well, $\textrm{Ob}(F(P+_{L(Y)}Q)) = \mathbb{N}(S_1+_Y S_2)$ and $\textrm{Ob}(F(P)+_{F(L(Y))} F(Q))= \mathbb{N}(S_1) +_{\mathbb{N}(Y)} \mathbb{N}(S_2)$.
-
-%\newpage
-
-%is given by $$1 \to F(c_1) \times F(c_2) \xrightarrow{} F(c_1 + c_2) \xrightarrow{} F(c_1 + _b c_2)$$ and then applying the functor $E$ results in $1 \to E(F(c_1+_b c_2))$, which by the comutative square is the same as $1 \to F'(H(c_1+_b c_2))$.
-On the other hand, applying the functor $E$ to each decoration results in $$1 \to E(F(c_1)) \times E(F(c_2)) \xrightarrow{} E(F(c_1) \times F(c_2)) \xrightarrow{} E(F(c_1+c_2)) \xrightarrow E(F(c_1+_b c_2)) \xrightarrow{} F'(H(c_1 +_b c_2))$$
-
-\section{Structured versus decorated cospans} \label{EquivDoubleCats}
-
-In \cite{BC2}, the first two authors introduce the symmetric monoidal double category of \emph{structured cospans} as a formalism to capture open networks.
-One of the main goals of this paper is to provide a monoidal double equivalence between this double category and that of \emph{decorated cospans}, described in detail in \cref{DecCospansDoubleCat}.
-We first recall the double category structured cospans form.
-
-\begin{thm}\label{SC}
-Given categories $\X$ and $\A$ with finite colimits and $L \maps \A \to \X$ a finitely cocontinuous functor, there exists a symmetric monoidal double category $_L\lCsp(\X)$ in which
-\begin{itemize}
-\item an object is an object of $\A$,
-\item a vertical morphism is a morphism of $\A$,
-\item a horizontal 1-cell from $a$ to $b$ is a cospan in $\X$ of the form
-\begin{equation}\label{eq:structuredcospan}
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$L(a)$};
-\node (B) at (1,0) {$x$};
-\node (C) at (2,0) {$L(b)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$$} (B)
-(C) edge node[above]{$$} (B);
-\end{tikzpicture}
-\end{equation}
-\item a 2-morphism is a map of cospans in $\X$ of the form
-\begin{equation}\label{eq:2cellsStrCsp}
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$L(a)$};
-\node (B) at (1,0) {$x$};
-\node (C) at (2,0) {$L(b)$};
-\node (A') at (0,-1) {$L(a')$};
-\node (B') at (1,-1) {$x'$};
-\node (C') at (2,-1) {$L(b')$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$$} (B)
-(C) edge node[above]{$$} (B)
-(A') edge node[above]{$$} (B')
-(C') edge node[above]{$$} (B')
-(A) edge node [left]{$L(f)$} (A')
-(B) edge node [left]{$\alpha$} (B')
-(C) edge node [right]{$L(g)$} (C');
-\end{tikzpicture}
-\end{equation}
-\end{itemize}
-The symmetric monoidal structure is formed by using binary coproducts and the initial object.
-\end{thm}
-
-\begin{proof}
-All relevant details can be found in \cite[Theorems~2.3\&3.9]{BC2}.
-In particular, the double category structure only requires that $\X$ have pushouts, since this is how composition is formed.
-Moreover, the symmetric monoidal structure requires that $\X$ also have binary coproducts and an initial object (thus all finite colimits), and that $\A$ have and $L$ preserve finite coproducts, see \cite[Theorem~3.2.3]{CourserThesis}.
-\end{proof}
-
-The following theorem establishes the desired equivalence between these two different double categorical network frameworks of structured and decorated cospans in a formal way.
-We denote by $\bicat{Rex}$ the 2-category of finitely cocomplete categories and finitely cocontinuous functors, and the symmetric monoidal double structure of decorated cospans is worked out in \cref{thm:decoratedcospans,DC}.
-
-\begin{thm}\label{Equiv}
-Suppose $\ca{A}$ has finite colimits and $(F,\phi,\phi_0)\maps(\ca{A},+,0) \to (\bicat{Cat},\times,\mathbf{1})$ is a symmetric lax monoidal pseudofunctor that factors through $\bicat{Rex}$ as an ordinary pseudofunctor.
-Then the symmetric monoidal double category $F\lCsp$ of decorated cospans is equivalent to the symmetric monoidal double category $_L\lCsp(\inta F)$ of structured cospans, where $L \maps \A \to \inta F$ is the left adjoint of the induced Grothendieck opfibration $\U\maps \inta F \to \A$.
-\end{thm}
-
-The conditions of the above theorem relate to the existence of left adjoints for opfibrations; we first sketch this underlying framework, and then we proceed to the proof of the theorem.
-The basics of fibration theory needed for our purposes are recalled in \cref{sec:fibrations}.
-
-In \cite{MV}, the classical Grothendieck construction is generalized to the monoidal setting: lax monoidal structures on a pseudofunctor $F\maps\A\to\bicat{Cat}$ (called \emph{monoidal opindexed category}) bijectively correspond to monoidal structures on the total category $\inta F$ such that the induced opfibration is a strict monoidal functor and $\otimes_{\inta F}$ preserves cocartesian liftings (called \emph{monoidal fibration}).
-If the monoidal category $\A$ is in fact cocartesian, there is a further correspondence of the two structures with an ordinary pseudofunctor $F\maps\A\to\bicat{MonCat}$ into the 2-category of monoidal categories, strong monoidal functors and monoidal natural transformations.
-
-\begin{thm}
- There is a 2-equivalence between the 2-categories of monoidal opfibrations and monoidal opindexed categories.
-If the base is cocartesian monoidal, there is a 2-equivalence between monoidal opfibrations and pseudofunctors into monoidal categories.
-\end{thm}
-
-\begin{proof}
-This is the content of \cite[Theorems~3.13\&4.1]{MV}. In summary, we have correspondences
-\begin{gather}
-\textrm{lax monoidal pseudofunctors }F\maps(\A,+)\to(\bicat{Cat},\times) \notag\\
-\Updownarrow \notag\\
-\textrm{monoidal opfibrations }U\maps(\X,\otimes)\to(\A,+) \label{monGroth}\\
-\Updownarrow \notag\\
-\textrm{pseudofunctors }F\maps\A\to\bicat{MonCat} \notag
-\end{gather}
-The second equivalence was also earlier observed by Shulman in \cite{Shul2}.
-In more detail, if $(\mu,\mu_0)$ is the lax monoidal structure of the pseudofunctor $F$ as recalled in \cref{sec:2cats}, each fibre category $\X_a=F(a)$ obtains a monoidal structure via
-\begin{equation}\label{eq:explicitstructure1}
-\otimes_a\maps F(a)\times F(a)\xrightarrow{\mu_{a,a}}F(a+a)\xrightarrow{F(\nabla)}F(a),\quad
-I_a\maps\mathbf{1}\xrightarrow{\mu_0}F(0)\xrightarrow{F(!)}F(a)
-\end{equation}
-where $\nabla$ is the fold map. 
-\end{proof}
-
-These correspondences further restrict to the case when the Grothendieck category is specifically cocartesian monoidal itself. In that case, opfibrations
-$(\X,+)\to(\A,+)$ that (strictly) preserve coproducts and the initial object (and such that $+$ preserves cocartesian liftings) bijectively correspond to pseudofunctors into the 2-category of cocartesian categories; for more details, see \cite[Corollary 4.7]{MV} and the related discussion.
-%!!!
-Christina: someone wrote Rex there, perhaps it was me.
-This is a subcategory, not all finite colimits are there.
-
-{\chris In progress...}
-
-Finally, using the following result we can further restrict to our current case of interest, namely opfibrations that also preserve pushouts, i.e.
-all finite colimits.
-Of course, the following statement is more general since it relates the existence of any class of colimits in the total category of an opfibration to their existence in the fibres; for a more detailed exposition and proof, see \cite{Herm}.
-
-\begin{lem}\label{lem:fibrewiselimits}
-Suppose $\ca{J}$ is a small category and $\U\maps\X\to\A$ is an opfibration. If the base $\A$ has $\ca{J}$-colimits,
-the following are equivalent:
-\begin{enumerate}
- \item all fibres have $\ca{J}$-colimits, and the reindexing functors preserve them;
- \item the total $\X$ has $\ca{J}$-colimits, and $\U$ preserves them. %removed strict for now!
-\end{enumerate}
-\end{lem}
-
-The first part formulates the existence of colimits \emph{locally} in each fibre, which can equivalently be expressed by the corresponding pseudofunctor $F\maps\A\to\bicat{Cat}$ landing on the sub-2-category $\bicat{Rex}$ of finitely cocomplete categories and functors that preserve colimits.
-The second part formulates the existence of colimits \emph{globally} in the total category $\inta F$.
-Combining these, we can deduce the following.
-
-\begin{cor}\label{cor:fcocMonGroth}
- Suppose $\A$ is a finitely cocomplete category and $F\maps(\A,+,0)\to(\bicat{Cat},\times,1)$ is a lax monoidal pseudofunctor.
-If its corresponding pseudofunctor $\A\to\bicat{MonCat}$ via \cref{monGroth}
- factors through $\bicat{Rex}$, then the Grothendieck category $\inta F$ has all finite colimits and the induced opfibration $\U_F\maps\inta F\to\A$ preserves them. 
-\end{cor}
-
-On a different but related subject, for our purposes we are interested in the existence of a left adjoint $L_F$ to the induced monoidal opfibration $ \inta{F} \to \A$ by the Grothendieck construction as discussed above.
-The following result provides sufficient conditions for that, which go hand-in-hand with \cref{cor:fcocMonGroth} and \cref{lem:fibrewiselimits}.
-
-\begin{prop}\cite[Proposition~4.4]{Gray} \label{prop:opfibtolari}
-  Let $\U \maps\X \to \A$ be an opfibration. Then
-  $\U$ is a right adjoint `left inverse', a.k.a the unit is the identity, if (and only if) its fibers have
-  initial objects which are preserved by the
-  reindexing functors.
-\end{prop}
-
-\begin{proof}\emph{(Sketch)}
- The left adjoint $L\maps\A\to\X$ maps an object $a$ to the initial object in its fibre $\X_a$, denoted by $\bot_a$.
-By construction, $U(L(a))=U(\bot_a)=a$.
-On morphisms $f\maps a\to a'$, $L(f)$ is defined by
- \begin{equation}\label{eq:Lonarrows}
-  \bot_a\xrightarrow{\Rex(f,\bot_a)}f_!(\bot_a)\xrightarrow{\;\stackrel{\chi_a}{\cong}\;}\bot_{a'}
- \end{equation}
-where $\chi_a$ is the unique isomorphism between the initial objects in the fibre above $a'$ since $f_!$ preserves them.
-\end{proof}
-
-\begin{rmk}\label{rmk:important}
-Notice that under \cref{lem:fibrewiselimits}, if $\A$ has an initial object $0_\A$, the above conditions are equivalent to $\X$ having an initial object $0_\X$ above $0_\A$.
-%Christina: hiding strict preservence under the rug
-In this case, $\bot_a$ is precisely the cocartesian lifting of $0_\X$ along the unique map $u_a\maps0_\A\to a$ in the base category:
-\begin{displaymath}
-\xymatrix @C=.4in @R=.2in
-{0_\X \ar @{.>}[d]\ar[rr]^-{\mathrm{Cocart}(0_\X,u_a)} && (u_a)_!(0_X)=:\bot_a\ar @{.>}[d] & \textrm{in }\X  \\
-0_\A\ar[rr]^-{\exists!u_a} && a & \textrm{in }\A}
-\end{displaymath}
-Moreover, if $U=U_F$ for a pseudofunctor $F\maps\A\to\bicat{Cat}$ under \cref{thm:Grothendieck}, the reindexing functors $(u_a)_!$ of the opfibration are precisely $F(u_a)$, therefore $\bot_a=(a,F(u_a)(0_\X))$ in the Grothendieck category, for $u_a$ the unique map from $0_\A$ as above.
-
-Finally, if that pseudofunctor is lax monoidal $(F,\phi,\phi_0)\maps(\A,+,0)\to(\bicat{Cat},\times,\mathbf{1})$ to begin with, the monoidal Grothendieck construction in the cocartesian case discussed earlier \cref{eq:explicitstructure1} expresses $\bot_a$ as the image of the composite
-\begin{equation}\label{eq:initialinfibre}
-\mathbf{1}\xrightarrow{\phi_0}F(0_\A)\xrightarrow{F(u_a)}F(a) 
-\end{equation}
-\end{rmk}
-
-%will be a right adjoint to some adjoint , and moreover the unit of the adjunction is the identity; this is called \emph{lari} in [Gray].
-
-%!!!Christina: not sure if the below is needed after all
-In the opposite direction, we also have the following result. For a discussion on the unusual strict cocontinuity condition, we refer the reader to \cite{CV}.
-
-\begin{lem}\label{prop:CV}\cite[Proposition~3.3]{CV}
-Suppose $\U\maps\X\to\A$ is a right adjoint `left inverse'. If $\X$ and $\A$ have chosen pushouts and initial objects and $\U$ strictly preserves them, then $\U$ is an opfibration.
-\end{lem}
-%Christina: do we need this direction after all? Discuss.
-%\begin{thm}\label{thm:mainthmDX}\cite{CV}
-%Suppose that $\X$ and $\A$ have chosen pushouts and initial objects, and a functor $\U\maps\X\to\A$ strictly preserves them.
-Then $\U$ is a right %adjoint left inverse if and only if $\U$ is an opfibration.
-%\end{thm}
-
-We have now laid all the necessary background to formally construct an equivalence between the double category of decorated cospans and the double category of structured cospans, constructed from a symmetric lax monoidal pseudofunctor into $\bicat{Cat}$.
-
-\begin{proof}[Proof of \cref{Equiv}]
-Recall from \cref{thm:decoratedcospans} that the double category of decorated cospans $\dcsp{F}$ has objects and vertical 1-morphisms as in $\A$, while a horizontal 1-cell $a\tickar b$ is cospan $\cspn{a}{m}{b}{}{}$ in $\A$ decorated by an object $x\in F(m)$ and a 2-morphism is a map $k\maps m\to m'$ together with a morphism $(Fk)(x)\to x'$.
-
-By \cref{cor:fcocMonGroth}, when $F$ as an ordinary pseudofunctor factors through $\bicat{Rex}$, the (monoidal) Gro\-the\-ndieck construction gives rise to a finitely cocomplete $\inta F$ such that the corresponding opfibration $U_F\maps(\inta{F},+)\to(\A,+)$ preserves all finite colimits.
-%Christina: maybe the cocartesian structures are redundant to write here, since U_F really preserves all finite colimits anyways.
-Since in particular it preserves the initial object, \cref{prop:opfibtolari} through \cref{lem:fibrewiselimits} applies 
-%which equivalently means that all fibres have initial objects and the reindexing functors preserve them by , %Christina: there is a little bit of circularity here.
-We knew fibres have and reindexing functors preserve from the factorization already!
-Change Gray accordingly perhaps?
-to construct a left adjoint $L_F\maps\A\to\inta F$ which is also a right inverse, namely $U_FL_F=\mathrm{id}_\A$.
-Explicitly, this left adjoint is given by $L(a)=(a,\bot_a)$, picking the initial object in the finitely cocomplete fibre also expressed as $F(u_a)\circ\phi_0(*)$ in \cref{eq:initialinfibre}.
-Diagrammatically,
-\begin{displaymath}
- F\maps\X\to\bicat{Cat}\quad\mapsto\quad\begin{tikzcd}[baseline=.3]\inta F\ar[d,"U_F"'] \\ \X \end{tikzcd}\quad\mapsto\quad\begin{tikzcd}\X\ar[r,bend left,pos=.55,"L_F"]\ar[r,phantom,"\bot"description] & \inta F\ar[l,bend left,pos=.45,"U_F"]\end{tikzcd}
-\end{displaymath}
-roughly describes the processes between the original $F$ and the resulting $L_F$.
-
-Using this functor $L_F$ between finitely cocomplete categories that preserves all colimits that exist (as a left adjoint), we can construct the double category of structured cospans $\scsp{L_F}{\inta F}$.
-Its objects and vertical morphisms are again those of the category $\A$, whereas horizontal 1-cells $a\tickar b$ as in \cref{eq:structuredcospan} are now cospans of the form $\cspn{L_F(a)}{v}{L_F(b)}{}{}$ in the Grothendieck category $\inta F$.
-Explicitly, they consist of two pairs of morphisms
-\begin{equation}\label{eq:scsphor1cell}
- (a,\bot_a)\xrightarrow{\scalebox{0.7}{\(\begin{cases}i\maps a\to m &\textrm{in }\A \\!\maps F(i)(\bot_a)\to x &\textrm{in }F(m)\end{cases}\)}}(m,x)\xleftarrow{\scalebox{0.7}{\(\begin{cases}o\maps b\to m &\textrm{in }\A \\!\maps F(o)(\bot_b)\to x &\textrm{in }F(m)\end{cases}\)}}(b,\bot_b)
-\end{equation}
-where $x\in F(m)$, according to \cref{def:GrothCat}. Finally, the 2-morphisms in this double category are as described in \cref{eq:2cellsStrCsp}, in this context fully unravelled below:
-\begin{displaymath}
- \begin{tikzcd}[sep=1.5in,ampersand replacement=\&]
- (a,\bot_a)\ar[r,"{\begin{cases}i\maps a\to m &\textrm{in }\A \\!\maps F(i)(\bot_a)\to x &\textrm{in }F(m)\end{cases}}"]\ar[d,"{\begin{cases}f\maps a\to a' &\textrm{in }\A \\\chi_a\maps F(f)(\bot_a)\cong \bot_{a'} &\textrm{in }F(a')\end{cases}}"description] \& (m,x) \ar[d,"{\begin{cases}k\maps m\to m' &\textrm{in }\A \\ \tau\maps F(k)(x)\to x' &\textrm{in }F(m')\end{cases}}"description] \& (b,\bot_b)\ar[l,"{\begin{cases}o\maps b\to m &\textrm{in }\A \\!\maps F(o)(\bot_b)\to x &\textrm{in }F(m)\end{cases}}"']\ar[d,"{\begin{cases}g\maps b\to b' &\textrm{in }\A \\\chi_b\maps F(g)(\bot_b)\cong \bot_{b'} &\textrm{in }F(b')\end{cases}}"description] \\
- (a',\bot_{a'})\ar[r,"{\begin{cases}i'\maps a'\to m' &\textrm{in }\A \\!\maps F(i')(\bot_{a'})\to x' &\textrm{in }F(m')\end{cases}}"'] \& (m',x') \& (b',\bot_{b'})\ar[l,"{\begin{cases}o'\maps b'\to m' &\textrm{in }\A \\!\maps F(o')(\bot_{b'})\to x' &\textrm{in }F(m')\end{cases}}"]
- \end{tikzcd}
-\end{displaymath}
-where the outside vertical legs come from the definition of $L_F$ on arrows, \cref{eq:Lonarrows}. 
-%!!! The above diagram might be a bit overwhelming, but all info is there. Choose which parts are required for a smooth proof!
-The square commutativities translate to $k\circ i=i'\circ f$ and $k\circ o=o'\circ g$ in $\A$, and also by composition in the Grothendieck category, to
-\begin{gather}\label{eq:Grothcommutativity}
- F(k\circ i)(\bot_a)\cong Fk(Fi(\bot_a))\xrightarrow{Fk(!)}Fk(x)\xrightarrow{\tau}x'= \\
- F(i'\circ f)(\bot_a)\cong Fi'(Ff(\bot_a))\xrightarrow{Fi'(\chi_a)}Fi'(\bot_{a'})\xrightarrow{!}x'\nonumber
-\end{gather}
-in the category $F(m')$.
-However, since all maps are unique in the above equality, emanating from initial objects (since reindexing functors preserve those), this gives no extra conditions for the morphisms involved; similarly for the equality including $o, o'$.
-
-In order to prove that there is a double equivalence (\cref{ShulDubEquiv}) between $\dcsp{F}$ and $\scsp{L_F}{\inta F}$, we define a %n identity-on-objects and vertical morphism
-double functor
-\begin{displaymath}
-\mathbb{E}\maps\scsp{L_F}{\inta F} \longrightarrow\dcsp{F}
-\end{displaymath}
-as follows.
-The object component of $\mathbb{E}=(\mathbb{E}_0,\mathbb{E}_1)$ is $\mathbb{E}_0 = \id_{\A}$ since both double categories have $\A$ as their vertical category; trivially, $\mathbb{E}_0$ is an equivalence of categories.
-Given a horizontal 1-cell in $\scsp{L_F}{\inta F}$ like \cref{eq:scsphor1cell}, the arrow component $\mathbb{E}_1$ of the double functor simply maps it to the decorated cospan
-\begin{displaymath}
- a\xrightarrow{\; i \;}m\xleftarrow{\; o \;}b\;\textrm{ with decoration }x\in F(m)
-\end{displaymath}
-Notice that this really is a bijective correspondence since the unique maps from the initial objects in the fibres provide no extra information.
-Finally, given a 2-morphism of $L_F$-structured cospans as described above, $\mathbb{E}_1$ maps it to the underlying cospan 2-morphism
-\begin{displaymath}
- \begin{tikzcd}
-a\ar[r,"i"]\ar[d,"f"'] & m\ar[d,"k"] & b\ar[l,"o"']\ar[d,"g"] \\
-a'\ar[r,"i'"']& m' & b'\ar[l,"o'"]
- \end{tikzcd}
-\end{displaymath}
- in $\A$ along with the map $\tau\maps Fk(x)\to x'$ in $F(m')$, namely a decorated cospan 2-morphism as per \cref{eq:FCsp2morph}.
-Once again, this is a bijective correspondence since, as discussed above, the commutativity \cref{eq:Grothcommutativity} holds automatically by initiality of the domain.
-%!!!Christina: commented out big chunks of proof.
-They are right below if we want to revive parts of them, if we think the reader needs deeper level of detail.
-The idea is that the above description suffices as fully faithful and essentially surjective evidence, but perhaps we would like to spell that out more.
-On to strongness next.
-\begin{comment}
-which is a cospan in $\X$ of the form:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$L(c)$};
-\node (B) at (1,0) {$x$};
-\node (C) at (2,0) {$L(c')$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i$} (B)
-(C) edge node[above]{$o$} (B);
-\end{tikzpicture}
-\]
-the image $\mathbb{E}_1(M)$ is given by the pair:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$c$};
-\node (B) at (1,0) {$R(x)$};
-\node (C) at (2,0) {$c'$};
-\node (D) at (3,0) {$x \in F(R(x))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$R(i) {\eta_c}$} (B)
-(C) edge node[above]{$R(o) {\eta_{c'}}$} (B);
-\end{tikzpicture}
-\]
-where $R\maps \X \to \A$ is the right adjoint to the functor $L \maps \A \to \X$ and $\eta \maps 1_{\A} \to RL$ is the unit of the adjunction $L \dashv R$ which is an isomorphism since $L$ is fully faithful.
-\textbf{Hopefully...actually, it's a `lari'!} Similarly, the image of a 2-morphism $\alpha \maps M \to N$ in $_L \lCsp(\X)$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$L(c_1)$};
-\node (B) at (1,0) {$x$};
-\node (C) at (2,0) {$L(c_2)$};
-\node (A') at (0,-1) {$L(c_1')$};
-\node (B') at (1,-1) {$x'$};
-\node (C') at (2,-1) {$L(c_2')$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i$} (B)
-(C) edge node[above]{$o$} (B)
-(A') edge node[above]{$i'$} (B')
-(C') edge node[above]{$o'$} (B')
-(A) edge node [left]{$L(f)$} (A')
-(B) edge node [left]{$\alpha$} (B')
-(C) edge node [right]{$L(g)$} (C');
-\end{tikzpicture}
-\]
-is given by the 2-morphism $\mathbb{E}_1(\alpha) \maps \mathbb{E}_1(M) \to \mathbb{E}_1(N)$ in $\mathbb{F}\textnormal{Cospan}(\A)$ given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$c_1$};
-\node (B) at (1,0) {$R(x)$};
-\node (C) at (2,0) {$c_2$};
-\node (A') at (0,-1) {$c_1'$};
-\node (B') at (1,-1) {$R(x')$};
-\node (C') at (2,-1) {$c_2'$};
-\node (D) at (3,0) {$x \in F(R(x))$};
-\node (D') at (3,-1) {$x' \in F(R(x'))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$R(i) \eta_{c_1}$} (B)
-(C) edge node[above]{$R(o) \eta_{c_2}$} (B)
-(A') edge node[above]{$R(i') \eta_{c_1'}$} (B')
-(C') edge node[above]{$R(o') \eta_{c_2'}$} (B')
-(A) edge node [left]{$f$} (A')
-(B) edge node [left]{$R(\alpha)$} (B')
-(C) edge node [right]{$g$} (C');
-\end{tikzpicture}
-\]
-together with a morphism $\tau \maps F(R(\alpha))(x) \to x'$ in $F(R(x')) \subseteq \mathrm{X}$ which comes from the Grothendieck construction of the pseudofunctor $F \maps \A \to \Cat$.
-That $\mathbb{E}_0$ is a functor is clear.
-For $\mathbb{E}_1$, given two vertically composable 2-morphisms $M$ and $M'$ in $_L \lCsp(\X)$,
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$L(c_1)$};
-\node (B) at (1,0) {$x$};
-\node (C) at (2,0) {$L(c_2)$};
-\node (A') at (0,-1) {$L(c_1')$};
-\node (B') at (1,-1) {$x'$};
-\node (C') at (2,-1) {$L(c_2')$};
-\node (A'') at (0,-2) {$L(c_1')$};
-\node (B'') at (1,-2) {$x'$};
-\node (C'') at (2,-2) {$L(c_2')$};
-\node (A''') at (0,-3) {$L(c_1'')$};
-\node (B''') at (1,-3) {$x''$};
-\node (C''') at (2,-3) {$L(c_2'')$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i$} (B)
-(C) edge node[above]{$o$} (B)
-(A') edge node[above]{$i'$} (B')
-(C') edge node[above]{$o'$} (B')
-(A) edge node [left]{$L(f)$} (A')
-(B) edge node [left]{$\alpha$} (B')
-(C) edge node [right]{$L(g)$} (C')
-(A'') edge node[above]{$i'$} (B'')
-(C'') edge node[above]{$o'$} (B'')
-(A''') edge node[above]{$i''$} (B''')
-(C''') edge node[above]{$o''$} (B''')
-(A'') edge node [left]{$L(f')$} (A''')
-(B'') edge node [left]{$\alpha'$} (B''')
-(C'') edge node [right]{$L(g')$} (C''');
-\end{tikzpicture}
-\]
-their vertical composite $M'M$ is given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$L(c_1)$};
-\node (B) at (1,0) {$x$};
-\node (C) at (2,0) {$L(c_2)$};
-\node (A') at (0,-1) {$L(c_1'')$};
-\node (B') at (1,-1) {$x''$};
-\node (C') at (2,-1) {$L(c_2'')$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i$} (B)
-(C) edge node[above]{$o$} (B)
-(A') edge node[above]{$i''$} (B')
-(C') edge node[above]{$o''$} (B')
-(A) edge node [left]{$L(f'f)$} (A')
-(B) edge node [left]{$\alpha' \alpha$} (B')
-(C) edge node [right]{$L(g' g)$} (C');
-\end{tikzpicture}
-\]
-and the image of this 2-morphism $\mathbb{E}_1(M'M)$ is given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$c_1$};
-\node (B) at (1.5,0) {$R(x)$};
-\node (C) at (3,0) {$c_2$};
-\node (A') at (0,-1) {$c_1''$};
-\node (B') at (1.5,-1) {$R(x'')$};
-\node (C') at (3,-1) {$c_2''$};
-\node (D) at (4,0) {$x \in F(R(x))$};
-\node (D') at (4,-1) {$x'' \in F(R(x''))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$R(i) \eta_{c_1}$} (B)
-(C) edge node[above]{$R(o) \eta_{c_2}$} (B)
-(A') edge node[above]{$R(i'') \eta_{c_1''}$} (B')
-(C') edge node[above]{$R(o'') \eta_{c_2''}$} (B')
-(A) edge node [left]{$f'f$} (A')
-(B) edge node [left]{$R(\alpha' \alpha)$} (B')
-(C) edge node [right]{$g'g$} (C');
-\end{tikzpicture}
-\]
-together with a morphism $\tau_{M' M} \maps F(R(\alpha' \alpha))(x) \to x''$ in $F(R(x''))$. On the other hand, the individual images $\mathbb{E}_1(M)$ and $\mathbb{E}_1(M')$ are given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$c_1$};
-\node (B) at (1.5,0) {$R(x)$};
-\node (C) at (3,0) {$c_2$};
-\node (A') at (0,-1) {$c_1'$};
-\node (B') at (1.5,-1) {$R(x')$};
-\node (C') at (3,-1) {$c_2'$};
-\node (D) at (4,0) {$x \in F(R(x))$};
-\node (D') at (4,-1) {$x' \in F(R(x'))$};
-\node (A'') at (0,-2) {$c_1'$};
-\node (B'') at (1.5,-2) {$R(x')$};
-\node (C'') at (3,-2) {$c_2'$};
-\node (A''') at (0,-3) {$c_1''$};
-\node (B''') at (1.5,-3) {$R(x'')$};
-\node (C''') at (3,-3) {$c_2''$};
-\node (D'') at (4,-2) {$x' \in F(R(x'))$};
-\node (D''') at (4,-3) {$x'' \in F(R(x''))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$R(i) \eta_{c_1}$} (B)
-(C) edge node[above]{$R(o) \eta_{c_2}$} (B)
-(A') edge node[above]{$R(i') \eta_{c_1'}$} (B')
-(C') edge node[above]{$R(o') \eta_{c_2'}$} (B')
-(A) edge node [left]{$f$} (A')
-(B) edge node [left]{$R(\alpha)$} (B')
-(C) edge node [right]{$g$} (C')
-(A'') edge node[above]{$R(i') \eta_{c_1'}$} (B'')
-(C'') edge node[above]{$R(o') \eta_{c_2'}$} (B'')
-(A''') edge node[above]{$R(i'') \eta_{c_1''}$} (B''')
-(C''') edge node[above]{$R(o'') \eta_{c_2''}$} (B''')
-(A'') edge node [left]{$f'$} (A''')
-(B'') edge node [left]{$R(\alpha')$} (B''')
-(C'') edge node [right]{$g'$} (C''');
-\end{tikzpicture}
-\]
-together with morphisms $\tau_M \maps F(R(\alpha))(x) \to x'$ in $F(R(x'))$ and $\tau_{M'} \maps F(R(\alpha')(x') \to x''$ in $F(R(x''))$, respectively.
-The vertical composite $\mathbb{E}_1(M')\mathbb{E}_1(M)$ of the above two 2-morphisms is given by $\mathbb{E}_1(M'M)$ as $R$ is a functor and $\tau_{M'M}=\tau_{M'} \tau_M$.
-The functors $\mathbb{E}_0$ and $\mathbb{E}_1$ satisfy the equations $\mathbb{E}_0 S = S \mathbb{E}_1$ and $\mathbb{E}_0 T = T \mathbb{E}_1$.
-
-To see that this functor is essentially surjective, given a horizontal 1-cell in $F\lCsp$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$c_1$};
-\node (B) at (1,0) {$c$};
-\node (C) at (2,0) {$c_2$};
-\node (D) at (3,0) {$x \in F(c)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i$} (B)
-(C) edge node[above]{$o$} (B);
-\end{tikzpicture}
-\]
-we can find a 2-isomorphism in $F\lCsp$ whose codomain is the above horizontal 1-cell and whose domain is the image of the following horizontal 1-cell in $_L \lCsp(\X)$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$L(c_1)$};
-\node (B) at (1,0) {$x$};
-\node (C) at (2,0) {$L(c_2)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i'$} (B)
-(C) edge node[above]{$o'$} (B);
-\end{tikzpicture}
-\]
-with the 2-isomorphism in $F\lCsp$ given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$c_1$};
-\node (B) at (1,0) {$R(x)$};
-\node (C) at (2,0) {$c_2$};
-\node (A') at (0,-1) {$c_1$};
-\node (B') at (1,-1) {$c$};
-\node (C') at (2,-1) {$c_2$};
-\node (D) at (3,0) {$x \in F(R(x))$};
-\node (D') at (3,-1) {$x \in F(c)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$R(i') \eta_{c_1}$} (B)
-(C) edge node[above]{$R(o') \eta_{c_2}$} (B)
-(A') edge node[above]{$i$} (B')
-(C') edge node[above]{$o$} (B')
-(A) edge node [left]{$1$} (A')
-(B) edge node [left]{${(R(e) \eta_c)}^{-1}$} (B')
-(C) edge node [right]{$1$} (C');
-\end{tikzpicture}
-\]
-$$\tau \maps F({(R(e)\eta_c)}^{-1})(x) \to x$$
-where $e \maps L(c) \to x$ is given by the map from the trivial decoration on $c$ to $x \in F(c)$.
-%The object and arrow components $\mathbb{E}_0$ and $\mathbb{E}_1$ satisfy the equations $S \mathbb{E}_1 = \mathbb{E}_0 S$ and $T \mathbb{E}_1 = \mathbb{E}_0 T$.
-
-To show that the double functor $\mathbb{E}$ is fully faithful, we need to show that the map  $$\mathbb{E}_1 \maps _f { _L \lCsp(\X)}_g(M,N) \to {_{\mathbb{E}(f)} {F\lCsp}_{\mathbb{E}(g)}}(\mathbb{E}(M),\mathbb{E}(N))$$ is bijective for arbitrary vertical 1-morphisms $f$ and $g$ and horizontal 1-cells $M$ and $N$ of $_L \lCsp(\X)$.
-Consider a 2-morphism in $_L \lCsp(\X)$ with horizontal source and target $M$ and $N$, respectively and vertical source and target $f$ and $g$, respectively:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$L(c_1)$};
-\node (B) at (1,0) {$x$};
-\node (C) at (2,0) {$L(c_2)$};
-\node (A') at (0,-1) {$L(c_1')$};
-\node (B') at (1,-1) {$x'$};
-\node (C') at (2,-1) {$L(c_2')$};
-\node (D) at (1,0.5) {$M$};
-\node (E) at (-1,-0.5) {$f$};
-\node (F) at (1,-1.5) {$N$};
-\node (G) at (3,-0.5) {$g$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i$} (B)
-(C) edge node[above]{$o$} (B)
-(A') edge node[above]{$i'$} (B')
-(C') edge node[above]{$o'$} (B')
-(A) edge node [left]{$L(f)$} (A')
-(B) edge node [left]{$\alpha$} (B')
-(C) edge node [right]{$L(g)$} (C');
-\end{tikzpicture}
-\]
-Thus the set $$_f { _L \lCsp(\X)}_g(M,N)$$ consists of triples $$(f,\alpha,g)$$ rendering the above diagram commutative where $f$ and $g$ are morphisms of $\A$ and $\alpha$ is a morphism of $\X$.
-The image of the above 2-morphism under the double functor $\mathbb{E}$ is given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$c_1$};
-\node (B) at (1,0) {$R(x)$};
-\node (C) at (2,0) {$c_2$};
-\node (A') at (0,-1) {$c_1'$};
-\node (B') at (1,-1) {$R(x')$};
-\node (C') at (2,-1) {$c_2'$};
-\node (D) at (1,0.5) {$x \in F(R(x))$};
-\node (D') at (1,-1.5) {$x' \in F(R(x'))$};
-\node (E) at (1,1) {$\mathbb{E}(M)$};
-\node (F) at (-1,-0.5) {$\mathbb{E}(f)$};
-\node (G) at (1,-2) {$\mathbb{E}(N)$};
-\node (H) at (3,-0.5) {$\mathbb{E}(g)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$R(i)\eta_{c_1}$} (B)
-(C) edge node[above]{$R(o)\eta_{c_2}$} (B)
-(A') edge node[above]{$R(i')\eta_{c_1'}$} (B')
-(C') edge node[above]{$R(o')\eta_{c_2'}$} (B')
-(A) edge node [left]{$f$} (A')
-(B) edge node [left]{$R(\alpha)$} (B')
-(C) edge node [right]{$g$} (C');
-\end{tikzpicture}
-\]
-together with a morphism $\tau \maps F(R(\alpha))(x) \to x'$ of $F(R(x'))$.
-Thus the set $$_{\mathbb{E}(f)} {F\lCsp}_{\mathbb{E}(g)}(\mathbb{E}(M),\mathbb{E}(N))$$ consists of 4-tuples $$(f,R(\alpha),g,\tau)$$ rendering the above diagram commutative and where $f,g$ and $R(\alpha)$ are morphisms of $\A$ and $\tau$ is a morphism in $F(R(x'))$.
-The morphisms $R(\alpha) \maps R(x) \to R(x')$ and $\tau \maps F(R(\alpha))(x) \to x'$ together determine the morphism $\alpha \maps x \to x'$ in $\mathrm{X}$ and conversely; given two objects $x=(c,x \in F(c))$ and $x'=(c',x' \in F(c'))$ of $\X=\inta{F}$, a morphism from $\alpha \maps x \to x'$ is a pair $$(h \maps c \to c', \tau \maps F(h)(x) \to x')$$ where $h \maps c \to c'$ is given by $R(\alpha) \maps R(x) \to R(x')$.
-This shows that $\mathbb{E}$ is fully faithful.
-\textbf{At least in my favorite example...}
-\end{comment}
-Functoriality of $\mathbb{E}_1$ can be verified, and moreover $(\mathbb{E}_0,\mathbb{E}_1)$ indeed define a strong double functor: there exist natural isomorphisms
-\begin{gather*}
- \mathbb{E}(M) \odot \mathbb{E}(N) \xrightarrow{\sim} \mathbb{E}(M \odot N) \\
-U_{\mathbb{E}m} \xrightarrow{\sim} \mathbb{E}(U_m)
-\end{gather*}
-for any pair of composable horizontal 1-cells $M=\cspn{(a,\bot_a)}{(m,x)}{(b,\bot_b)}{}{}$ and $N=\cspn{(b,\bot_b)}{(n,y)}{(c,\bot_c)}{}{}$ and any object $m$ of $\scsp{L_F}{\inta F}$.
-In more detail, $\mathbb{E}(M)\odot \mathbb{E}(N)$ is given as in \cref{eq:dcospanscomposition} via the pushout cospan and decoration
-\begin{displaymath}
- \begin{tikzcd}
-  & m+_bn & \\
-  a\ar[ur,"j_m\circ i"] && b,\ar[ul,"j_n\circ o"']
- \end{tikzcd}
- \begin{tikzcd}
-  1\ar[r,"x\times y"]\ar[drr,dashed] & F(m)\times F(n)\ar[r,"\phi_{m,n}"] & F(m+ n)\ar[d,"F(j)"] \\ 
-  && F(m+_b n)
- \end{tikzcd}
-\end{displaymath}
-where $j_m, j_n$ denote the maps into a pushout.
-On the other hand, first composing $M$ and $N$ in the Grothendieck category $\scsp{L_F}{\inta F}$ using fibrewise pushouts constructed using \cref{lem:fibrewiselimits} 
-%!!!Chris: I could make this specific construction into a lemma earlier if you want, I have it in my notes
-produces 
-\begin{displaymath}
- \begin{tikzcd}
- && (m+_b n,F(j_m)x+_{\bot_{m+_bn}}F(j_n)y) && \\
- & (m,x) \ar[ur] && (n,y)\ar[ul] \\
- (a,\bot_a)\ar[ur] && (b,\bot_b)\ar[ur]\ar[ul] && (c,\bot_c)\ar[ul]
- \end{tikzcd}
-\end{displaymath}
-which is mapped, under $\mathbb{E}$, to precisely the cospan $\cspn{a}{m+_bn}{b}{}{}$ as above, and the decorations are the same 
-%!!!Christina: isomorphic would be enough but they look equal to me!
-due to the following commutative diagram
-\begin{displaymath}
- \begin{tikzcd}
-F(m)\times F(n)\ar[rr,"\phi"]\ar[d,"F(j_m)\times F(j_n)"'] && F(m+n)\ar[d,"F(j)"] \\
-F(m+_bn)\times F(m+_bn)\ar[r,"\phi"] & F((m+_bn)+(m+_bn))\ar[r,"F\nabla"] & F(m+_bn)
- \end{tikzcd}
-\end{displaymath}
-since taking a pushout over an initial object is really a coproduct, and the fibrewise coproduct in $F(m+_bn)$ is given as in \cref{eq:explicitstructure1}.
-
-Regarding the identity morphisms, $U_m$ is $\cspn{(m,\bot_m)}{(m,\bot_m)}{(m,\bot_m)}{}{}$ with $1_m$ as the $A$-component of the morphisms and isomorphisms between initial objects in the fibres.
-Thus $\mathbb{E}(U_m)$ is the identity cospan in $A$ together with the `initial decoration' $\bot_m\in F(m)$, whereas $U_{\mathbb{E}(m)}$ is exactly the same thing.
-
-%!!!Christina: Below, up to my next comment, is Kenny's earlier proof on the same thing.
-\begin{comment}
-For any object $c$, the horizontal 1-cell $\hat{U}_{\mathbb{E}(c)}$ is given by $\hat{U}_c$ which is given by the pair:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$c$};
-\node (B) at (1,0) {$c$};
-\node (C) at (2,0) {$c$};
-\node (D) at (3,0) {$!_c \in F(c)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$1$} (B)
-(C) edge node[above]{$1$} (B);
-\end{tikzpicture}
-\]
-The horizontal 1-cell $U_c$ is given by
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$L(c)$};
-\node (B) at (1,0) {$L(c)$};
-\node (C) at (2,0) {$L(c)$};
-%\node (D) at (3,0.5) {$!_c \in F(c)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$1$} (B)
-(C) edge node[above]{$1$} (B);
-\end{tikzpicture}
-\]
-and so $\mathbb{E}(U_c)$ is given by the pair:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$c$};
-\node (B) at (1,0) {$R(L(c))$};
-\node (C) at (2,0) {$c$};
-\node (D) at (3.25,0) {$!_c \in F(R(L(c)))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$\eta_c$} (B)
-(C) edge node[above]{$\eta_c$} (B);
-\end{tikzpicture}
-\]
-Then we can obtain the natural isomorphism $\mathbb{E}_c \maps \hat{U}_{\mathbb{E}(c)} \xrightarrow{\sim} \mathbb{E}(U_c)$ as the 2-morphism
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$c$};
-\node (B) at (1,0) {$c$};
-\node (C) at (2,0) {$c$};
-\node (A') at (0,-1) {$c$};
-\node (B') at (1,-1) {$R(L(c))$};
-\node (C') at (2,-1) {$c$};
-\node (D) at (3,0) {$!_c \in F(c)$};
-\node (D') at (3.25,-1) {$!_{R(L(c))} \in F(R(L(c)))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$1$} (B)
-(C) edge node[above]{$1$} (B)
-(A') edge node[above]{$\eta_c$} (B')
-(C') edge node[above]{$\eta_c$} (B')
-(A) edge node [left]{$1$} (A')
-(B) edge node [left]{$\eta_c$} (B')
-(C) edge node [left]{$1$} (C');
-\end{tikzpicture}
-\]
-$$\tau \maps F(\eta_c)(!_c) \xrightarrow{!} !_{R(L(c))}$$
-of $F\lCsp$.
-
-Next, given composable horizontal 1-cells $M$ and $N$ in $_L \lCsp(\X)$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$L(c_1)$};
-\node (B) at (1,0) {$x$};
-\node (C) at (2,0) {$L(c_2)$};
-\node (D) at (3,0) {$L(c_2)$};
-\node (E) at (4,0) {$x'$};
-\node (F) at (5,0) {$L(c_3)$};
-%\node (D) at (3,0.5) {$!_c \in F(c)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i$} (B)
-(C) edge node[above]{$o$} (B)
-(D) edge node[above]{$i'$} (E)
-(F) edge node[above]{$o'$} (E);
-\end{tikzpicture}
-\]
-their images $\mathbb{E}(M)$ and $\mathbb{E}(N)$ are given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$c_1$};
-\node (B) at (1,0) {$R(x)$};
-\node (C) at (2,0) {$c_2$};
-\node (D) at (3,0) {$c_2$};
-\node (E) at (4,0) {$R(x')$};
-\node (F) at (5,0) {$c_3$};
-\node (G) at (1,-0.5) {$x \in F(R(x))$};
-\node (H) at (4,-0.5) {$x' \in F(R(x'))$};
-%\node (D) at (3,0.5) {$!_c \in F(c)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$R(i) \eta_{c_1}$} (B)
-(C) edge node[above]{$R(o) \eta_{c_2}$} (B)
-(D) edge node[above]{$R(i') \eta_{c_2}$} (E)
-(F) edge node[above]{$R(o') \eta_{c_3}$} (E);
-\end{tikzpicture}
-\]
-and so $\mathbb{E}(M) \odot \mathbb{E}(N)$ is given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$c_1$};
-\node (B) at (1.5,0) {$R(x)+_{c_2}R(x')$};
-\node (C) at (3,0) {$c_3$};
-\node (G) at (1.5,-0.5) {$d_{\mathbb{E}(M) \odot \mathbb{E}(N)} = \hat{x} \in F(R(x)+_{c_2}R(x'))$};
-%\node (D) at (3,0.5) {$!_c \in F(c)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$j \psi R(i) \eta_{c_1}$} (B)
-(C) edge node[above]{$j \psi R(o') \eta_{c_3}$} (B);
-\end{tikzpicture}
-\]
-$$\hat{x} \maps 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{x \times x'} F(R(x)) \times F(R(x')) \xrightarrow{\phi_{R(x),R(x')}} F(R(x)+R(x')) \xrightarrow{F(j_{R(x),R(x')})} F(R(x)+_{c_2}R(x'))$$where $\psi$ denotes each natural map into the coproduct and $j$ denotes the natural map from the coproduct to the pushout.
-On the other hand, $M \odot N$ is given by
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$L(c_1)$};
-\node (B) at (1.25,0) {$x+_{L(c_2)}x'$};
-\node (C) at (2.5,0) {$L(c_3)$};
-%\node (G) at (1,-0.5) {$\hat{d} \in F(R(d)+_{c_2}R(d'))$};
-%\node (D) at (3,0.5) {$!_c \in F(c)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$J \zeta i$} (B)
-(C) edge node[above]{$J \zeta o'$} (B);
-\end{tikzpicture}
-\]
-where $\zeta$ is a natural map into a coproduct and $J$ is the natural map from the coproduct to the pushout. Then $E(M \odot N)$ is given by
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$c_1$};
-\node (B) at (1.5,0) {$R(x+_{L(c_2)}x')$};
-\node (C) at (3,0) {$c_3$};
-\node (G) at (1.5,-0.5) {$d_{\mathbb{E}(M \odot N)} = x+_{L(c_2)} x' \in F(R(x+_{L(c_2)}x'))$};
-%\node (D) at (3,0.5) {$!_c \in F(c)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$R(J \zeta i) \eta_{c_1}$} (B)
-(C) edge node[above]{$R(J \zeta o') \eta_{c_3}$} (B);
-\end{tikzpicture}
-\]
-and so $\mathbb{E}_{M,N} \maps \mathbb{E}(M) \odot \mathbb{E}(N) \xrightarrow{\sim} \mathbb{E}(M \odot N)$ is given by the 2-morphism:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$c_1$};
-\node (B) at (1.5,0) {$R(x)+_{c_2}R(x')$};
-\node (C) at (3,0) {$c_3$};
-\node (A') at (0,-1) {$c_1$};
-\node (B') at (1.5,-1) {$R(x+_{L(c_2)}x')$};
-\node (C') at (3,-1) {$c_3$};
-\node (D) at (5.5 ,0) {$d_{\mathbb{E}(M) \odot \mathbb{E}(N)} \in F(R(x)+_{c_2}R(x'))$};
-\node (D') at (5.5,-1) {$d_{\mathbb{E}(M \odot N)} \in F(R(x+_{L(c_2)}x'))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$j \psi R(i) \eta_{c_1}$} (B)
-(C) edge node[above]{$j \psi R(o') \eta_{c_3}$} (B)
-(A') edge node[above]{$R(J \zeta i) \eta_{c_1}$} (B')
-(C') edge node[above]{$R(J \zeta o') \eta_{c_3}$} (B')
-(A) edge node [left]{$1$} (A')
-(B) edge node [left]{$\sigma$} (B')
-(C) edge node [left]{$1$} (C');
-\end{tikzpicture}
-\]
-together with a morphism of decorations which is obtained as follows.
-First, as $R \maps \X \to \A$ preserves finite colimits, we have an isomorphism $$\kappa \maps R(x) +_{R(L(c_2))} R(x') \to R(x+_{L(c_2)}x').$$ Also, since the left adjoint $L \maps \A \to \X$ is fully faithful, the unit of the adjunction $L \dashv R$ at the object $c_2$ gives an isomorphism $\eta_{c_2} \maps c_2 \to R(L(c_2))$ which results in an isomorphism $$j_{\eta_{c_2}} \maps R(x) +_{c_2} R(x') \to R(x) +_{R(L(c_2))} R(x').$$ Composing these two results in an isomorphism $$\sigma \mapseqq \kappa j_{\eta_{c_2}} \maps R(x) +_{c_2} R(x') \to R(x+_{L(c_2)}x').$$
-Next, to see that the above diagram commutes, it suffices to show that for the object $c_1 \in \mathrm{A}$, $$R(J)R(\zeta)R(i)\eta_{c_1}(c_1) = R(J \zeta i)\eta_{c_1}(c_1)  \stackrel{!}{=} \sigma j \psi R(i)\eta_{c_1}(c_1) = \kappa j_{\eta_{c_2}} \psi R(i) \eta_{c_1}(c_1).$$ This follows as $R(i) \eta_{c_1} \maps c_1 \to R(x)$ and the following diagram commutes:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (B) at (0,0) {$R(x)$};
-\node (C) at (2,0) {$R(x)+R(x')$};
-\node (A') at (4,0) {$R(x)+_{c_2}R(x')$};
-\node (B') at (4,-2) {$R(x+_{L(c_2)}x')$};
-\node (D) at (0,-2) {$R(x+x')$};
-\node (D') at (4,-1) {$R(x)+_{R(L(c_2))} R(x')$};
-\path[->,font=\scriptsize,>=angle 90]
-(C) edge node[above]{$j$} (A')
-(B) edge node[above]{$\psi$} (C)
-(D) edge node[above]{$R(J)$} (B')
-(B) edge node [left]{$R(\zeta)$} (D)
-(A') edge node [right]{$j_{\eta_{c_2}}$} (D')
-(A') edge [out=345,in=15] node [right]{$\sigma$} (B')
-(D') edge node [right]{$\kappa$} (B');
-\end{tikzpicture}
-\]
-Lastly, this map of cospans comes with an isomorphism $$\tau \maps F(\sigma)(d_{\mathbb{E}(M) \odot \mathbb{E}(N)}) \to d_{\mathbb{E}(M \odot N)}$$ in $F(R(x+_{L(c_2)}x'))$.
-This shows that $\mathbb{E}$ is strong, and so
-\end{comment}
-%!!!Christina: Up to here was Kenny's strong functoriality.
-
-Based on the above description of its mapping, it follows that the strong double functor $\mathbb{E}=(\mathbb{E}_0,\mathbb{E}_1)$ is full, faithful and essentially surjective on objects as per \cref{def:fullfaithful,def:essentiallysurj}.
-Therefore $\mathbb{E} \maps \scsp{L_F}{\inta F} \to \dcsp{F}$ is a double equivalence, by \cref{ShulDubEquiv}.
-%!!!Christina: In fact, Christina and Kenny believe it is an isomorphism of double categories! Bijective on all levels of objects and morphisms...should we say?
-
-%!!!Christina Have not edited below, but everything should be fine up to notation changes. Happy to do if needed in the future.
-
-Next, we show that if both double categories $_L \lCsp(\X)$ and $F\lCsp$ are symmetric monoidal, as they are if both $\A$ and $\X$ have finite colimits, then this equivalence of double categories $\mathbb{E} \maps _L \lCsp(\X) \to F\lCsp$ will be symmetric monoidal.
-First, note that we have an isomorphism $\epsilon \maps 1_{F\lCsp} \to \mathbb{E}(1_{_L \lCsp(\X)})$ and natural isomorphisms $\mu_{c_1,c_2} \maps \mathbb{E}(c_1) \otimes \mathbb{E}(c_2) \to \mathbb{E}(c_1 \otimes c_2)$ for every pair of objects $c_1,c_2 \in {_L \mathbb{C} \textnormal{sp}(\X)}$ both of which are given by identities since both double categories $_L \lCsp(\X)$ and $F\lCsp$ have $\A$ as their category of objects and $\mathbb{E}_0=\id_{\A}$.
-The diagrams utilizing these maps that are required to commute do so trivially.
-
-For the arrow component $\mathbb{E}_1$, we have an isomorphism $\delta \maps U_{1_{F\lCsp}} \to \mathbb{E}(U_{1_{_L \lCsp(\X)}})$ where the horizontal 1-cell $U_{1_{F\lCsp}}$ is given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$1_\A$};
-\node (B) at (1,0) {$1_\A$};
-\node (C) at (2,0) {$1_\A$};
-\node (D) at (3,0) {$!_{1_{\A}} \in F(1_\A)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$1$} (B)
-(C) edge node[above]{$1$} (B);
-\end{tikzpicture}
-\]
-where $!_{1_{\A}} = \phi \maps 1 \to F(1_\A)$ is the trivial decoration which comes from the structure of the symmetric lax monoidal pseudofunctor $F \maps \A \to \Cat$.
-The horizontal 1-cell $U_{1_{_L \lCsp(\X)}}$ is given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$L(1_\A)$};
-\node (B) at (1,0) {$L(1_\A)$};
-\node (C) at (2,0) {$L(1_\A)$};
-%\node (D) at (3,0.5) {$I \in F(1_\mathrm{A})$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$1$} (B)
-(C) edge node[above]{$1$} (B);
-\end{tikzpicture}
-\]
-where here we make use of the fact that the left adjoint $L \maps (\A,+,1_\A) \to (\X,+,1_\X)$ preserves all colimits and thus $L(1_\A) \cong 1_\X$.
-The horizontal 1-cell $\mathbb{E}(U_{1_{_L \mathbb{C} \textnormal{sp}(\X)}})$ is then given by the pair:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$1_\A$};
-\node (B) at (1.25,0) {$R(L(1_\A))$};
-\node (C) at (2.5,0) {$1_\A$};
-\node (D) at (4.5,0) {$!_{R(L(1_\A))} \in F(R(L(1_\A)))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{${\eta_{1_\A}}$} (B)
-(C) edge node[above]{${\eta_{1_\A}}$} (B);
-\end{tikzpicture}
-\]
-The isomorphism $\delta$ is then given by the 2-morphism:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$1_\A$};
-\node (B) at (1,0) {$1_{\A}$};
-\node (C) at (2,0) {$1_\A$};
-\node (A') at (0,-1) {$1_\A$};
-\node (B') at (1,-1) {$R(L(1_\A))$};
-\node (C') at (2,-1) {$1_\A$};
-\node (D) at (3,0) {$!_{1_\A} \in F(1_\A)$};
-\node (D') at (3.75,-1) {$!_{R(L(1_\A))} \in F(R(L(1_\A)))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$1$} (B)
-(C) edge node[above]{$1$} (B)
-(A') edge node[above]{${\eta_{1_\A}}$} (B')
-(C') edge node[above]{${\eta_{1_\A}}$} (B')
-(A) edge node [left]{$1$} (A')
-(B) edge node [left]{${\eta_{1_\A}}$} (B')
-(C) edge node [left]{$1$} (C');
-\end{tikzpicture}
-\]
-$$\tau_{{\eta_{1_\A}}} \maps F({\eta_{1_\A}})(!_{1_\A})) \to !_{R(L(1_\A))}$$
-of $F\lCsp$. This is just the natural isomorphism $\mathbb{E}_{1_\A}$ from earlier.
-
-Given two horizontal 1-cells $M$ and $N$ of $_L \lCsp(\X)$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$L(c_1)$};
-\node (B) at (1,0) {$x$};
-\node (C) at (2,0) {$L(c_2)$};
-\node (D) at (3,0) {$L(c_1')$};
-\node (E) at (4,0) {$x'$};
-\node (F) at (5,0) {$L(c_2')$};
-%\node (D) at (3,0.5) {$!_c \in F(c)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i$} (B)
-(C) edge node[above]{$o$} (B)
-(D) edge node[above]{$i'$} (E)
-(F) edge node[above]{$o'$} (E);
-\end{tikzpicture}
-\]
-their images $\mathbb{E}(M)$ and $\mathbb{E}(N)$ are given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$c_1$};
-\node (B) at (1,0) {$R(x)$};
-\node (C) at (2,0) {$c_2$};
-\node (D) at (3,0) {$c_1'$};
-\node (E) at (4,0) {$R(x')$};
-\node (F) at (5,0) {$c_2'$};
-\node (G) at (1,-0.5) {$x \in F(R(x))$};
-\node (H) at (4,-0.5) {$x' \in F(R(x'))$};
-%\node (D) at (3,0.5) {$!_c \in F(c)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$R(i) \eta_{c_1}$} (B)
-(C) edge node[above]{$R(o) \eta_{c_2}$} (B)
-(D) edge node[above]{$R(i') \eta_{c_1'}$} (E)
-(F) edge node[above]{$R(o') \eta_{c_2'}$} (E);
-\end{tikzpicture}
-\]
-and so $\mathbb{E}(M) \otimes \mathbb{E}(N)$ is given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$c_1+c_1'$};
-\node (B) at (3.25,0) {$R(x)+R(x')$};
-\node (C) at (6.5,0) {$c_2+c_2'$};
-\node (D) at (3.25,-0.5) {$d_{\mathbb{E}(M) \otimes \mathbb{E}(N)} \in F(R(x)+R(x'))$}; 
-%\node (D) at (3,0.5) {$!_c \in F(c)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$R(i) \eta_{c_1} +R(i') \eta_{c_1'}$} (B)
-(C) edge node[above]{$R(o) \eta_{c_2} + R(o) \eta_{c_2'}$} (B);
-\end{tikzpicture}
-\]
-where $$d_{\mathbb{E}(M) \otimes \mathbb{E}(N)} \maps 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{x \times x'} F(R(x)) \times F(R(x')) \xrightarrow{\phi_{R(x),R(x')}} F(R(x)+R(x')).$$ On the other hand, $M \otimes N$ is given by
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$L(c_1+c_1')$};
-\node (B) at (2,0) {$x+x'$};
-\node (C) at (4,0) {$L(c_2+c_2')$};
-%\node (D) at (3,0.5) {$!_c \in F(c)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$(i+i')\phi_{c_1,c_1'}^{-1}$} (B)
-(C) edge node[above]{$(o+o')\phi_{c_2,c_2'}^{-1}$} (B);
-\end{tikzpicture}
-\]
-and $\mathbb{E}(M \otimes N)$ is given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$c_1+c_1'$};
-\node (B) at (4,0) {$R(x+x')$};
-\node (C) at (8,0) {$c_2+c_2'$};
-\node (D) at (4,-0.5) {$d_{\mathbb{E}(M \odot N)} \in F(R(x+x')).$};
-%\node (D) at (3,0.5) {$!_c \in F(c)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$R((i+i')\phi_{c_1,c_1'}^{-1}) \eta_{c_1+c_1'}$} (B)
-(C) edge node[above]{$R((o+o')\phi_{c_2,c_2'}^{-1}) \eta_{c_2+c_2'}$} (B);
-\end{tikzpicture}
-\]
-We then have a 2-isomorphism $\mu_{M,N} \maps E(M) \otimes E(N) \xrightarrow{\sim} E(M \otimes N)$ in $F\lCsp$ given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (-2.5,0) {$c_1+c_1'$};
-\node (B) at (1,0) {$R(x)+R(x')$};
-\node (C) at (4.5,0) {$c_2+c_2'$};
-\node (A') at (-2.5,-1) {$c_1+c_1'$};
-\node (B') at (1,-1) {$R(x+x')$};
-\node (C') at (4.5,-1) {$c_2+c_2'$};
-\node (D) at (6.55,0) {$d_{\mathbb{E}(M) \otimes \mathbb{E}(N)} \in F(R(x)+R(x'))$};
-\node (D') at (6.55,-1) {$d_{\mathbb{E}(M \otimes N)} \in F(R(x+x'))$};
-\node (E) at (2,-1.5) {$\tau_\mu \maps F(\kappa)(d_{\mathbb{E}(M) \odot \mathbb{E}(N)}) \to d_{\mathbb{E}(M \odot N)}$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$R(i)\eta_{c_1} + R(i')\eta_{c_1'}$} (B)
-(C) edge node[above]{$R(o)\eta_{c_2} + R(o')\eta_{c_2'}$} (B)
-(A') edge node[above]{$R((i+i')\phi_{c_1,c_1'}^{-1}) \eta_{c_1+c_1'}$} (B')
-(C') edge node[above]{$R((o+o')\phi_{c_2,c_2'}^{-1}) \eta_{c_2+c_2'}$} (B')
-(A) edge node [left]{$1$} (A')
-(B) edge node [left]{$\kappa$} (B')
-(C) edge node [right]{$1$} (C');
-\end{tikzpicture}
-\]
-where $\kappa$ is the isomorphism which comes from $R \maps \X \to \A$ preserving finite colimits.
-
-The isomorphisms $\delta$ and $\mu$ satisfy the left and right unitality squares, associativity hexagon and braiding square. 
-%Kenny: I think this might be a good place to cut the monoidal stuff.
-%Christina: Deal! They are right below.
-
-\begin{comment}
-To see this, let $M_1,M_2$ and $M_3$ be horizontal 1-cells in $_L \lCsp(\X)$ given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$L(c_1)$};
-\node (B) at (1,0) {$x_1$};
-\node (C) at (2,0) {$L(c_1')$};
-\node (D) at (3,0) {$L(c_2)$};
-\node (E) at (4,0) {$x_2$};
-\node (F) at (5,0) {$L(c_2')$};
-\node (G) at (6,0) {$L(c_3)$};
-\node (H) at (7,0) {$x_3$};
-\node (I) at (8,0) {$L(c_3')$};
-%\node (D) at (3,0.5) {$!_c \in F(c)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i_1$} (B)
-(C) edge node[above]{$o_1$} (B)
-(D) edge node[above]{$i_2$} (E)
-(F) edge node[above]{$o_2$} (E)
-(G) edge node[above]{$i_3$} (H)
-(I) edge node[above]{$o_3$} (H);
-\end{tikzpicture}
-\]
-The left unitality square:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$1_{F\lCsp} \otimes \mathbb{E}(M_1)$};
-\node (B) at (3,0) {$\mathbb{E}(1_{ _L \lCsp(\X)}) \otimes \mathbb{E}(M_1)$};
-\node (C) at (0,-1) {$\mathbb{E}(M_1)$};
-\node (D) at (3,-1) {$\mathbb{E}(1_{ _L \lCsp(\X)} \otimes M_1)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$\delta \otimes 1$} (B)
-(B) edge node[right]{$\mu_{1,M_1}$} (D)
-(A) edge node[left]{$\lambda'$} (C)
-(D) edge node[above]{$\mathbb{E}(\lambda)$} (C);
-\end{tikzpicture}
-\]
-has an underlying diagram of maps of cospans given by:
-\[
-		\begin{tikzpicture}
-			\node (d) at (7.5,0) {$\mathbb{E}(1_{ _L \lCsp(\X)}) \otimes \mathbb{E}(M_1)$};
-			\node (a) at (-6,0) {$1_\A+c_1$};
-			\node (b) at (-0.5,0) {$R(L(1_\A)) + R(x_1)$};
-			\node (c) at (5,0) {$1_\A+c_1'$};
-			\node (d2) at (7.5,1) {$1_{F\lCsp} \otimes \mathbb{E}(M_1)$};
-			\node (a2) at (-6,1) {$1_\A+c_1$};
-			\node (b2) at (-0.5,1) {$1_\A+R(x_1)$};
-			\node (c2) at (5,1) {$1_\A+c_1'$};
-			\node (d3) at (7.5,2) {$\mathbb{E}(M_1)$};
-                                \node (a3) at (-6,2) {$c_1$};
-			\node (b3) at (-0.5,2) {$R(x_1)$};
-			\node (c3) at (5,2) {$c_1'$};
-			\node (d4) at (7.5,-1) {$\mathbb{E}(1_{ _L \lCsp(\X)} \otimes M_1)$};
-                                \node (a5) at (-6,-1) {$1_\A+c_1'$};
-			\node (b5) at (-0.5,-1) {$R(L(1_\A)+x_1)$};
-			\node (c5) at (5,-1) {$1_\A+c_1'$};
-			\node (d5) at (7.5,-2) {$\mathbb{E}(M_1)$};
-                                \node (a6) at (-6,-2) {$c_1$};
-			\node (b6) at (-0.5,-2) {$R(x_1)$};
-			\node (c6) at (5,-2) {$c_1'$};
-			\path[->,font=\scriptsize,>=angle 90]
-			(d2) edge node [left]{$\lambda$} (d3)
-			(d2) edge node [left] {$\delta \otimes 1$} (d)
-			(d) edge node [left] {$\mu_{1,M_1}$} (d4)
-			(d4) edge node [left] {$\mathbb{E}(\lambda)$} (d5)
-			(a) edge node[above]{$\eta_{1_\A}+R(i_1)\eta_{c_1}$} (b)
-			(c) edge node[above]{$\eta_{1_\A}+R(o_1)\eta_{c_1'}$} (b)
-                                (a2) edge node[above]{$1+R(i_1)\eta_{c_1}$} (b2)
-			(c2) edge node[above]{$1+R(o_1)\eta_{c_1'}$} (b2)
-                                (a2) edge node[left]{$1$} (a)
-                                (b2) edge node[left]{$\eta_{1_\A}+1$} (b)
-(b2) edge node[right]{$\tau_2$} (b)
-			(c2) edge node[right]{$1$} (c)
-                                (a3) edge node[above]{$R(i_1)\eta_{c_1}$} (b3)
-			(c3) edge node[above]{$R(o_1)\eta_{c_1'}$} (b3)
-                                (a2) edge node[left]{$\lambda_{\A}$} (a3)
-                                (b2) edge node[left]{$\lambda_{\A}$} (b3)
-(b2) edge node[right]{$\tau_1$} (b3)
-			(c2) edge node[right]{$\lambda_{\A}$} (c3)
-                                (a5) edge node[above]{$(\mu_{L(1_\A),d_1})(\eta_{1_\A}+R(i_1)\eta_{c_1})$} (b5)
-			(c5) edge node[above]{$(\mu_{L(1_\A),d_1})(\eta_{1_\A}+R(o_1)\eta_{c_1'})$} (b5)
-                                (a) edge node[left]{$1$} (a5)
-                                (b) edge node[left]{$\mu_{L(1_\A),x_1}$} (b5)
-(b) edge node[right]{$\tau_3$} (b5)
-			(c) edge node[right]{$1$} (c5)
-                                (a6) edge node[above]{$R(i_1)\eta_{c_1}$} (b6)
-			(c6) edge node[above]{$R(o_1)\eta_{c_1'}$} (b6)
-                                (a5) edge node[left]{$\lambda_{\A}$} (a6)
-                                (b5) edge node[left]{$R(\lambda_{\X})$} (b6)
- (b5) edge node[right]{$\tau_4$} (b6)
-			(c5) edge node[right]{$\lambda_{\A}$} (c6);
-		\end{tikzpicture}
-	\]
-with the corresponding maps of decorations amounting to the following commutative diagram in $F(R(x_1))$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (-.5,0) {$F(\lambda_{\A})(!_{1_\A}+x_1)$};
-\node (C) at (4,0) {$F(R(\lambda_{\X})(\mu_{L(1_\A),x_1}))(!_{R(L(1_\A))} +x_1$)};
-\node (D) at (-.5,-1) {$x_1$};
-\node (E) at (4,-1) {$F(R(\lambda_\X))(x_{!+1})$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$F(R(\lambda_{\X})(\mu_{L(1_\A),x_1}))(\tau_2)$} (C)
-(A) edge node[left]{$\tau_1$} (D)
-(E) edge node[above]{$\tau_4$} (D)
-(C) edge node[right]{$F(R(\lambda_\X))(\tau_3)$} (E);
-\end{tikzpicture}
-\]
-where $x_{!+1}$ is the decoration $x_1$ on the object $R(L(1_\A)+x_1) \in \A$.
-The above square commutes because $$F(\lambda_\A)(!_{1_\A}+x_1) = F(R(\lambda_\X)(\mu_{L(1_\A),x_1})(\eta_{1_\A}+1))(!_{1_\A}+x_1)$$ as the corresponding left unitality square for the finite colimit preserving functor $R \maps (\X,1_\X,+) \to (\A,1_\A,+)$ commutes.
-The right unitality square is similar.
-The associator hexagon:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$(\mathbb{E}(M_1) \otimes \mathbb{E}(M_2)) \otimes \mathbb{E}(M_3)$};
-\node (B) at (3.5,0) {$\mathbb{E}(M_1 \otimes M_2) \otimes \mathbb{E}(M_3)$};
-\node (C) at (7,0) {$\mathbb{E}((M_1 \otimes M_2) \otimes M_3)$};
-\node (A') at (0,-1) {$\mathbb{E}(M_1) \otimes (\mathbb{E}(M_2) \otimes \mathbb{E}(M_3))$};
-\node (B') at (3.5,-1) {$\mathbb{E}(M_1) \otimes \mathbb{E}(M_2 \otimes M_3)$};
-\node (C') at (7,-1) {$\mathbb{E}(M_1 \otimes (M_2 \otimes M_3))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$\mu_{M_1,M_2} \otimes 1$} (B)
-(B) edge node[above]{$\mu_{M_1 \otimes M_2,M_3}$} (C)
-(A') edge node[above]{$1 \otimes \mu_{M_2,M_3}$} (B')
-(B') edge node[above]{$\mu_{M_1,M_2 \otimes M_3}$} (C')
-(A) edge node [left]{$a'$} (A')
-(C) edge node [right]{$\mathbb{E}(a)$} (C');
-\end{tikzpicture}
-\]
-has underlying maps of cospans given by:
-\[
-		\begin{tikzpicture}
-\node(d) at (1.5,7) {$(\mathbb{E}(M_1) \otimes \mathbb{E}(M_2)) \otimes \mathbb{E}(M_3)$};
-\node (d2) at (1.5,8) {$\mathbb{E}(M_1 \otimes M_2) \otimes \mathbb{E}(M_3)$};
-\node (d3) at (1.5,9) {$\mathbb{E}((M_1 \otimes M_2) \otimes M_3)$};
-\node (d4) at (1.5,10) {$\mathbb{E}(M_1 \otimes (M_2 \otimes M_3))$};
-\node (d5) at (1.5,6) {$\mathbb{E}(M_1) \otimes (\mathbb{E}(M_2) \otimes \mathbb{E}(M_3))$};
-\node (d6) at (1.5,5) {$\mathbb{E}(M_1) \otimes \mathbb{E}(M_2 \otimes M_3)$};
-\node (d7) at (1.5,4) {$\mathbb{E}(M_1 \otimes (M_2 \otimes M_3))$};
-			\node (a) at (-4.25,0) {$(c_1+c_2)+c_3$};
-			\node (b) at (2.5,0) {$(R(x_1)+R(x_2))+R(x_3)$};
-			\node (c) at (9.25,0) {$(c_1'+c_2')+c_3'$};
-			\node (a2) at (-4.25,1) {$(c_1+c_2)+c_3$};
-			\node (b2) at (2.5,1) {$R(x_1+x_2)+R(x_3)$};
-			\node (c2) at (9.25,1) {$(c_1'+c_2')+c_3'$};
-                                \node (a3) at (-4.25,2) {$(c_1+c_2)+c_3$};
-			\node (b3) at (2.5,2) {$R((x_1+x_2)+x_3)$};
-			\node (c3) at (9.25,2) {$(c_1'+c_2')+c_3'$};
-                                \node (a4) at (-4.25,3) {$c_1+(c_2+c_3)$};
-			\node (b4) at (2.5,3) {$R(x_1+(x_2+x_3))$};
-			\node (c4) at (9.25,3) {$c_1' + (c_2' + c_3')$};
-                                \node (a5) at (-4.25,-1) {$c_1+(c_2+c_3)$};
-			\node (b5) at (2.5,-1) {$R(x_1)+(R(x_2)+R(x_3))$};
-			\node (c5) at (9.25,-1) {$c_1' + (c_2' + c_3')$};
-                                \node (a6) at (-4.25,-2) {$c_1+(c_2+c_3)$};
-			\node (b6) at (2.5,-2) {$R(x_1)+R(x_2+x_3)$};
-			\node (c6) at (9.25,-2) {$c_1' + (c_2' + c_3')$};
-                                \node (a7) at (-4.25,-3) {$c_1+(c_2+c_3)$};
-			\node (b7) at (2.5,-3) {$R(x_1+(x_2+x_3))$};
-			\node (c7) at (9.25,-3) {$c_1' + (c_2' + c_3')$};
-			\path[->,font=\scriptsize,>=angle 90]
-(d) edge node[left] {$\mu_{M_1,M_2} \otimes 1$} (d2)
-(d2) edge node[left] {$\mu_{M_1 \otimes M_2,M_3}$} (d3)
-(d3) edge node[left] {$\mathbb{E}(a)$} (d4)
-(d) edge node[left] {$a'$} (d5)
-(d5) edge node[left] {$1 \otimes \mu_{M_2,M_3}$} (d6)
-(d6) edge node[left] {$\mu_{M_1,M_2 \otimes M_3}$} (d7)
-			(a) edge node[above]{$(R(i_1)\eta_{c_1}+R(i_2)\eta_{c_2})+R(i_3)\eta_{c_3}$} (b)
-			(c) edge node[above]{$(R(o_1)\eta_{c_1'}+R(o_2)\eta_{c_2'})+R(o_3)\eta_{c_3'}$} (b)
-                                (a2) edge node[above]{$R(i_1+i_2)\eta_{c_1+c_2}+R(i_3)\eta_{c_3}$} (b2)
-			(c2) edge node[above]{$R(o_1+o_2)\eta_{c_1'+c_2'}+R(o_3)\eta_{c_3'}$} (b2)
-                                (a) edge node[left]{$1$} (a2)
-                                (b) edge node[left]{$\kappa + 1$} (b2)
-(b) edge node[right]{$\tau_1$} (b2)
-			(c) edge node[right]{$1$} (c2)
-                                (a3) edge node[above]{$R((i_1+i_2)+i_3)\eta_{(c_1+c_2)+c_3}$} (b3)
-			(c3) edge node[above]{$R((o_1+o_2)+o_3)\eta_{(c_1'+c_2')+c_3'}$} (b3)
-                                (a2) edge node[left]{$1$} (a3)
-                                (b2) edge node[left]{$\kappa$} (b3)
-(b2) edge node[right]{$\tau_2$} (b3)
-			(c2) edge node[right]{$1$} (c3)
-                                (a4) edge node[above]{$R(i_1+(i_2+i_3))\eta_{c_1+(c_2+c_3)}$} (b4)
-			(c4) edge node[above]{$R(o_1+(o_2+o_3))\eta_{c_1'+(c_2'+c_3')}$} (b4)
-                                (a3) edge node[left]{$a_\A$} (a4)
-                                (b3) edge node[left]{$R(a_\X)$} (b4)
-(b3) edge node[right]{$\tau_3$} (b4)
-			(c3) edge node[right]{$a_\A$} (c4)
-                                (a5) edge node[above]{$R(i_1)\eta_{c_1}+(R(i_2)\eta_{c_2}+R(i_3)\eta_{c_3})$} (b5)
-			(c5) edge node[above]{$R(o_1)\eta_{c_1'}+(R(o_2)\eta_{c_2'}+R(o_3)\eta_{c_3'})$} (b5)
-                                (a) edge node[left]{$a_\A$} (a5)
-                                (b) edge node[left]{$a_\A$} (b5)
-(b) edge node[right]{$\tau_4$} (b5)
-			(c) edge node[right]{$a_\A$} (c5)
-                                (a6) edge node[above]{$R(i_1)\eta_{c_1}+R(i_2+i_3)\eta_{c_2+c_3}$} (b6)
-			(c6) edge node[above]{$R(o_1)\eta_{c_1'}+R(o_2+o_3)\eta_{c_2'+c_3'}$} (b6)
-                                (a5) edge node[left]{$1$} (a6)
-                                (b5) edge node[left]{$1+\kappa$} (b6)
- (b5) edge node[right]{$\tau_5$} (b6)
-			(c5) edge node[right]{$1$} (c6)
-                                (a7) edge node[above]{$R(i_1+(i_2+i_3))\eta_{c_1+(c_2+c_3)}$} (b7)
-			(c7) edge node[above]{$R(o_1+(o_2+o_3))\eta_{c_1'+(c_2'+c_3')}$} (b7)
-                                (a6) edge node[left]{$1$} (a7)
-                                (b6) edge node[left]{$\kappa$} (b7)
-(b6) edge node[right]{$\tau_6$} (b7)
-			(c6) edge node[right]{$1$} (c7);
-		\end{tikzpicture}
-	\]
-Here we have omitted the natural isomorphisms $\phi_{c_i,c_j} \maps L(c_i) + L(c_j) \to L(c_i + c_j)$ on the inward pointing morphisms which make up the legs of each cospan due to limited space.
-The corresponding maps of decorations amount to the following commutative diagram in $F(R(x_1+(x_2+x_3)))$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$F((\kappa)(1+\kappa)(a_\A))((x_1+x_2)+x_3)$};
-\node (B) at (5,0) {$F((R(a_\mathrm{X}))(\kappa))((x_1+x_2)+x_3)$};
-\node (C) at (5,-1) {$F(R(a_\mathrm{X}))((x_1+x_2)+x_3)$};
-\node (D) at (5,-2) {$x_1+(x_2+x_3)$};
-\node (E) at (0,-1) {$F((\kappa)(1+\kappa))((x_1+x_2)+x_3)$};
-\node (F) at (0,-2) {$F(\kappa)(x_1+(x_2+x_3))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$F((R(a_\X))(\kappa))(\tau_1)$} (B)
-(B) edge node[right]{$F(R(a_\X))(\tau_2)$} (C)
-(C) edge node[right]{$\tau_3$} (D)
-(A) edge node[left]{$F((\kappa)(1+\kappa))(\tau_4)$} (E)
-(E) edge node[left]{$F(\kappa)(\tau_5)$} (F)
-(F) edge node[above]{$\tau_6$} (D);
-\end{tikzpicture}
-\]
-The above square commutes because $$F((\kappa)(1+\kappa)(a_\A))((x_1+x_2)+x_3) = F((R(a_\X))(\kappa)(\kappa+1))((x_1+x_2)+x_3)$$ as the corresponding associator hexagon for the finite colimit preserving functor $R \maps (\X,1_\X,+) \to (\A,1_\A,+)$ commutes.
-Lastly, the braiding square:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$\mathbb{E}(M_1) \otimes \mathbb{E}(M_2)$};
-\node (B) at (3,0) {$\mathbb{E}(M_2) \otimes \mathbb{E}(M_1)$};
-\node (C) at (0,-1) {$\mathbb{E}(M_1 \otimes M_2)$};
-\node (D) at (3,-1) {$\mathbb{E}(M_2 \otimes M_1)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$\beta'$} (B)
-(B) edge node[right]{$\mu_{M_2,M_1}$} (D)
-(A) edge node[left]{$\mu_{M_1,M_2}$} (C)
-(C) edge node[above]{$\mathbb{E}(\beta)$} (D);
-\end{tikzpicture}
-\]
-has underlying map of cospans given by:
-\[
-		\begin{tikzpicture}
-\node (d) at (7,0) {$\mathbb{E}(M_1) \otimes \mathbb{E}(M_2)$};
-\node (d2) at (7,1) {$\mathbb{E}(M_2) \otimes \mathbb{E}(M_1)$};
-\node (d3) at (7,2) {$\mathbb{E}(M_2 \otimes M_1)$};
-\node (d4) at (7,-1) {$\mathbb{E}(M_1 \otimes M_2)$};
-\node (d5) at (7,-2) {$\mathbb{E}(M_2 \otimes M_1)$};
-			\node (a) at (-4,0) {$c_1+c_2$};
-			\node (b) at (0.5,0) {$R(x_1)+R(x_2)$};
-			\node (c) at (5,0) {$c_1'+c_2'$};
-			\node (a2) at (-4,1) {$c_2+c_1$};
-			\node (b2) at (0.5,1) {$R(x_2)+R(x_1)$};
-			\node (c2) at (5,1) {$c_2'+c_1'$};
-                                \node (a3) at (-4,2) {$c_2+c_1$};
-			\node (b3) at (0.5,2) {$R(x_2+x_1)$};
-			\node (c3) at (5,2) {$c_2' + c_1'$};
-                                \node (a5) at (-4,-1) {$c_1+c_2$};
-			\node (b5) at (0.5,-1) {$R(x_1+x_2)$};
-			\node (c5) at (5,-1) {$c_1'+c_2'$};
-                                \node (a6) at (-4,-2) {$c_2+c_1$};
-			\node (b6) at (0.5,-2) {$R(x_2+x_1)$};
-			\node (c6) at (5,-2) {$c_2' + c_1'$};
-			\path[->,font=\scriptsize,>=angle 90]
-(d) edge node[left]{$\beta'$} (d2)
-(d2) edge node[left]{$\mu_{M_2,M_1}$}(d3)
-(d) edge node[left] {$\mu_{M_1,M_2}$}(d4)
-(d4)edge node[left]{$\mathbb{E}(\beta)$}(d5)
-			(a) edge node[above]{$R(i_1) \eta_{c_1} + R(i_2)\eta_{c_2}$} (b)
-			(c) edge node[above]{$R(o_1) \eta_{c_1'} + R(o_2) \eta_{c_2'}$} (b)
-                                (a2) edge node[above]{$R(i_2) \eta_{c_2} + R(i_1) \eta_{c_1}$} (b2)
-			(c2) edge node[above]{$R(o_2) \eta_{c_2'} + R(o_1) \eta_{c_1'}$} (b2)
-                                (a) edge node[left]{$\beta_\A$} (a2)
-                                (b) edge node[left]{$\beta_\A$} (b2)
-(b) edge node[right]{$\tau_1$} (b2)
-			(c) edge node[right]{$\beta_\A$} (c2)
-                                (a3) edge node[above]{$R(i_2+i_1)\eta_{c_2+c_1}$} (b3)
-			(c3) edge node[above]{$R(o_2+o_1)\eta_{c_2'+c_1'}$} (b3)
-                                (a2) edge node[left]{$1$} (a3)
-                                (b2) edge node[left]{$\kappa$} (b3)
-(b2) edge node[right]{$\tau_2$} (b3)
-			(c2) edge node[right]{$1$} (c3)
-                                (a5) edge node[above]{$R(i_1+i_2)\eta_{c_1+c_2}$} (b5)
-			(c5) edge node[above]{$R(o_1+o_2)\eta_{c_1'+c_2'}$} (b5)
-                                (a) edge node[left]{$1$} (a5)
-                                (b) edge node[left]{$\kappa$} (b5)
-(b) edge node[right]{$\tau_3$} (b5)
-			(c) edge node[right]{$1$} (c5)
-                                (a6) edge node[above]{$R(i_2+i_1)\eta_{c_2+c_1}$} (b6)
-			(c6) edge node[above]{$R(o_2+o_1)\eta_{c_2'+c_1'}$} (b6)
-                                (a5) edge node[left]{$\beta_\A$} (a6)
-                                (b5) edge node[left]{$R(\beta_\X)$} (b6)
- (b5) edge node[right]{$\tau_4$} (b6)
-			(c5) edge node[right]{$\beta_\A$} (c6);
-		\end{tikzpicture}
-	\]
-Again, we have omitted the natural isomorphisms $\phi_{c_i,c_j}$ on the inward pointing morphisms on each cospan leg due to space restrictions.
-The corresponding maps of decorations amounting to the following commutative diagram in $F(R(x_2+x_1))$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (-.5,0) {$F((\kappa)(\beta_\A))(x_1+x_2)$};
-\node (C) at (4,0) {$F(\kappa)(x_2+x_1)$};
-\node (D) at (-.5,-1) {$F(R(\beta_\X))(x_1+x_2)$};
-\node (E) at (4,-1) {$x_2+x_1$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$F(\kappa)(\tau_1)$} (C)
-(A) edge node[left]{$F(R(\beta_\X))(\tau_3)$} (D)
-(D) edge node[above]{$\tau_4$} (E)
-(C) edge node[right]{$\tau_2$} (E);
-\end{tikzpicture}
-\]
-The above square commutes because $$F((\kappa)(\beta_\A))(x_1+x_2) = F((R(\beta_\X))(\kappa))(x_1+x_2)$$ as the corresponding braiding square for the finite colimit preserving functor $R \maps (\X,1_\X,+) \to (\A,1_\A,+)$ commutes.
-Thus the double functor $\mathbb{E} \maps _L\lCsp(\X) \to F\lCsp$ is symmetric monoidal.
-\end{comment}
-
-\end{proof}
-
-Using a result of Shulman \cite{Shul}, each of the isofibrant symmetric monoidal double categories $F\lCsp$ and $_L \lCsp(\mathrm{X})$ give rise to underlying symmetric monoidal bicategories, namely $F\lCsp$ induces a symmetric monoidal bicategory $F\mathbf{Csp} \mapseqq H(F\lCsp)$ which has:
-\begin{enumerate}
-\item{objects as those of $\A$,}
-\item{morphisms as horizontal 1-cells of $F\lCsp$, and}
-\item{2-morphisms as globular 2-morphisms of $F\lCsp$.}
-\end{enumerate} 
-Likewise, $_L \lCsp(\X)$ induces a symmetric monoidal bicategory $H( {_L \lCsp(\X)})$ which has:
-\begin{enumerate}
-\item{objects as those of $\A$,}
-\item{morphisms as horizontal 1-cells of $_L \lCsp(\X)$, and}
-\item{2-morphisms as globular 2-morphisms of $_L \lCsp(\X)$.}
-\end{enumerate}
-Another result of Shulman \cite{Shul2} is the following:
-\begin{lem}[Shulman, Prop.\ B.3]
-An equivalence of fibrant double categories induces a biequivalence of horizontal bicategories.
-\end{lem}
-
-\begin{cor}
-The bicategories $F\mathbf{Csp}$ and $H( {_L \lCsp(\X)})$ are biequivalent.
-\end{cor}
-
-%!!!Kenny: Is this biequivalnce symmetric monoidal? Mike says yes, but it follows from a result that he has yet to officially publish. It's a result of a paper he's currently working on with someone.
-
-\begin{comment}
-We can also define the part of the double equivalence $\mathbb{G} \maps F\lCsp \to {_L \mathbb{C} \textnormal{sp}(\X)}$ which goes in the other direction: again, the object component of this double functor will be $\mathbb{G}_0 = \id_{\A}$.
-
-Given a horizontal 1-cell $M$ of $F\lCsp$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$c_1$};
-\node (B) at (1,0) {$c$};
-\node (C) at (2,0) {$c_2$};
-\node (D) at (1,-0.5) {$x \in F(c)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$I$} (B)
-(C) edge node[above]{$O$} (B);
-\end{tikzpicture}
-\]
-the image $\mathbb{G}(M)$ is the horizontal 1-cell in $_L \lCsp(\X)$ given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$L(c_1)$};
-\node (B) at (1,0) {$x$};
-\node (C) at (2,0) {$L(c_2)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$!_{c} L(I)$} (B)
-(C) edge node[above]{$!_{c} L(O)$} (B);
-\end{tikzpicture}
-\]
-where $!_{c} \maps L(c) \to x$ is the unique morphism from the trival decoration on $c$ given by $$!_{c} \mapseqq 1 \xrightarrow{\phi} F(0) \xrightarrow{F(!)} F(c)$$ to $x \in F(c)$.
-In other words, the trivial decoraction $!_{c}$ is initial in $F(c)$.
-Similarly, given a 2-morphism $(f,h,g,\tau) \maps M \to M'$ of $F\lCsp$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (D) at (1,0.5) {$x \in F(c)$};
-\node (D') at (1,-1.5) {$x' \in F(c')$};
-\node (A) at (0,0) {$c_1$};
-\node (B) at (1,0) {$c$};
-\node (C) at (2,0) {$c_2$};
-\node (A') at (0,-1) {$c_1'$};
-\node (B') at (1,-1) {$c'$};
-\node (C') at (2,-1) {$c_2'$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$I$} (B)
-(C) edge node[above]{$O$} (B)
-(A') edge node[above]{$I'$} (B')
-(C') edge node[above]{$O'$} (B')
-(A) edge node [left]{$f$} (A')
-(B) edge node [left]{$h$} (B')
-(C) edge node [right]{$g$} (C');
-\end{tikzpicture}
-\]
-$$\tau \maps F(h)(x) \to x'$$
-the image $\mathbb{G}(f,h,g,\tau)$ in $_L \lCsp(\X)$ is given by the 2-morphism:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$L(c_1)$};
-\node (B) at (1.5,0) {$x$};
-\node (C) at (3,0) {$L(c_2)$};
-\node (A') at (0,-1) {$L(c_1')$};
-\node (B') at (1.5,-1) {$x'$};
-\node (C') at (3,-1) {$L(c_2')$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$!_{c} L(I)$} (B)
-(C) edge node[above]{$!_{c} L(O)$} (B)
-(A') edge node[above]{$!_{c'} L(I')$} (B')
-(C') edge node[above]{$!_{c'} L(O')$} (B')
-(A) edge node [left]{$L(f)$} (A')
-(B) edge node [left]{$\alpha$} (B')
-(C) edge node [right]{$L(g)$} (C');
-\end{tikzpicture}
-\]
-where $\alpha \maps x \to x'$ is the morphism in the Grothendieck construction of $F$ given by $\alpha = (h \maps c \to c', \tau \maps F(h)(x) \to x')$.
-
-Next, we exhibit natural isomorphisms $\eta \maps \id_{ _L \lCsp(\X)} \cong \mathbb{G} \mathbb{E}$ and $\epsilon \maps \mathbb{E} \mathbb{G} \cong \id_{F\lCsp}$.
-Specifically, these are double natural isomorphisms given by double transformations \cite{Shul2} $\eta$ and $\epsilon$ whose object and arrow components are natural isomorphisms.
-
-First we compute the composites $\mathbb{G} \mathbb{E}$ and $\mathbb{E} \mathbb{G}$.
-On the object categories, both composites are $\id_\A$ and we have natural isomorphisms $\eta \maps \id_{\A} \cong \mathbb{G}_0 \mathbb{E}_0$ and $\epsilon \maps \mathbb{E}_0 \mathbb{G}_0 \cong \id_{\A}$.
-
-Given a horizontal 1-cell $M$ in $_L \mathbb{C} \textnormal{sp}(\X)$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$L(c_1)$};
-\node (B) at (1,0) {$x$};
-\node (C) at (2,0) {$L(c_2)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i$} (B)
-(C) edge node[above]{$o$} (B);
-\end{tikzpicture}
-\]
-the horizontal 1-cell $\mathbb{E}(M)$ is given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$c_1$};
-\node (B) at (1,0) {$R(x)$};
-\node (C) at (2,0) {$c_2$};
-\node (D) at (1,-0.5) {$x \in F(R(x))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$R(i) \eta_{c_1}$} (B)
-(C) edge node[above]{$R(o) \eta_{c_2}$} (B);
-\end{tikzpicture}
-\]
-and then the horizontal 1-cell $\mathbb{G} \mathbb{E}(M)$ is given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$L(c_1)$};
-\node (B) at (1.5,0) {$x$};
-\node (C) at (3,0) {$L(c_2)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$!_{R(x)}L(R(i)\eta_{c_1})$} (B)
-(C) edge node[above]{$!_{R(x)}L(R(o)\eta_{c_2})$} (B);
-\end{tikzpicture}
-\]
-Then we can find a 2-isomorphism $\eta_M \maps M \xrightarrow{\sim} \mathbb{G}\mathbb{E}(M) $ in $_L \mathbb{C} \textnormal{sp}(\X)$ given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$L(c_1)$};
-\node (B) at (1.5,0) {$x$};
-\node (C) at (3,0) {$L(c_2)$};
-\node (A') at (0,-1) {$L(c_1)$};
-\node (B') at (1.5,-1) {$x$};
-\node (C') at (3,-1) {$L(c_2)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i$} (B)
-(C) edge node[above]{$o$} (B)
-(A') edge node[above]{$!_{R(x)}L(R(i)\eta_{c_1})$} (B')
-(C') edge node[above]{$!_{R(x)}L(R(o)\eta_{c_2})$} (B')
-(A) edge node [left]{$1$} (A')
-(B) edge node [left]{$1$} (B')
-(C) edge node [right]{$1$} (C');
-\end{tikzpicture}
-\]
-where
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (-0.5,0) {$L(c_1)$};
-\node (B) at (1,0) {$L(R(L(c_1)))$};
-\node (C) at (2.5,0) {$L(R(x))$};
-\node (D) at (3.5,0) {$x$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$L(\eta_{c_1})$} (B)
-(B) edge node[above]{$L(R(i))$} (C)
-(C) edge node[above]{$!_{R(x)}$} (D)
-(A) edge[bend right] node [above]{$i$} (D);
-\end{tikzpicture}
-\]
-commutes.
-
-On the other hand, given a horizontal 1-cell $N$ in $F\lCsp$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$c_1$};
-\node (B) at (1,0) {$c$};
-\node (C) at (2,0) {$c_2$};
-\node (D) at (1,-0.5) {$x \in F(c)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$I$} (B)
-(C) edge node[above]{$O$} (B);
-\end{tikzpicture}
-\]
-the horizontal 1-cell $\mathbb{G}(N)$ is given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$L(c_1)$};
-\node (B) at (1,0) {$x$};
-\node (C) at (2,0) {$L(c_2)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$!_c L(I)$} (B)
-(C) edge node[above]{$!_c L(O)$} (B);
-\end{tikzpicture}
-\]
-and then the horizontal 1-cell $\mathbb{E} \mathbb{G}(N)$ is given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$c_1$};
-\node (B) at (1.5,0) {$R(x)$};
-\node (C) at (3,0) {$c_2$};
-\node (D) at (1.5,-0.5) {$x \in F(R(x))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$R(!_c L(I))\eta_{c_1}$} (B)
-(C) edge node[above]{$R(!_c L(O))\eta_{c_2}$} (B);
-\end{tikzpicture}
-\]
-Then we have a 2-isomorphism $\epsilon_N \maps \mathbb{E} \mathbb{G} (N) \xrightarrow{\sim} N$ in $F\lCsp$ given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (D) at (1.5,0.5) {$x \in F(R(x))$};
-\node (D') at (1.5,-1.5) {$x \in F(c)$};
-\node (A) at (0,0) {$c_1$};
-\node (B) at (1.5,0) {$R(x)$};
-\node (C) at (3,0) {$c_2$};
-\node (A') at (0,-1) {$c_1$};
-\node (B') at (1.5,-1) {$c$};
-\node (C') at (3,-1) {$c_2$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$R(!_c L(I))\eta_{c_1}$} (B)
-(C) edge node[above]{$R(!_c L(O))\eta_{c_2}$} (B)
-(A') edge node[above]{$I$} (B')
-(C') edge node[above]{$O$} (B')
-(A) edge node [left]{$1$} (A')
-(B) edge node [left]{$\hat{e}$} (B')
-(C) edge node [right]{$1$} (C');
-\end{tikzpicture}
-\]
-$$\tau \maps F(\hat{e})(x) \to x$$
-where 
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$c_1$};
-\node (B) at (1,0) {$R(L(c_1))$};
-\node (C) at (2.5,0) {$R(L(c))$};
-\node (D) at (3.5,0) {$R(x)$};
-\node (E) at (4.5,0) {$c$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$\eta_{c_1}$} (B)
-(B) edge node[above]{$R(L(I))$} (C)
-(C) edge node[above]{$R(!_c)$} (D)
-(D) edge node[above]{$\hat{e}$} (E)
-(A) edge[bend right] node [above]{$I$} (E);
-\end{tikzpicture}
-\]
-commutes.
-
-\end{comment}
-
 \section{Applications}\label{Applications}
@@
 We thus have two symmetric monoidal double categories: $_L \lCsp(\mathsf{Graph})$ obtained from structured cospans and $F\lCsp$ obtained from decorated cospans.
-Both of these double categories have $\mathsf{Set}$ as their categories of objects, open graphs as horizontal 1-cells and maps of open graphs as 2-morphisms, and by Theorem \cref{Equiv}, we have an equivalence of symmetric monoidal double categories $$_L \lCsp(\mathsf{Graph}) \sim F\lCsp.$$
+Both of these double categories have $\mathsf{Set}$ as their categories of objects, open graphs as horizontal 1-cells and maps of open graphs as 2-morphisms, and by Theorem \cref{thm:equiv}, we have an equivalence of symmetric monoidal double categories $$_L \lCsp(\mathsf{Graph}) \sim F\lCsp.$$
 
@@
 \end{enumerate}
-These two double categories $_L \lCsp(\mathsf{Graph}_k)$ and $F\lCsp$ are equivalent by Theorem \cref{Equiv}.
+These two double categories $_L \lCsp(\mathsf{Graph}_k)$ and $F\lCsp$ are equivalent by Theorem \cref{thm:equiv}.
 
@@
 \end{enumerate}
-The two double categories $F\lCsp$ and $_L \mathbb{C} \textnormal{sp}(\mathsf{Mark})$ are equivalent by Theorem \cref{Equiv}.
+The two double categories $F\lCsp$ and $_L \mathbb{C} \textnormal{sp}(\mathsf{Mark})$ are equivalent by Theorem \cref{thm:equiv}.
 
@@
 \end{enumerate}
-Thus we have a symmetric monoidal double category $\lOpen(\Petri)$ of open Petri nets obtained from structured cospans and a symmetric monoidal double category $F\lCsp$ of open Petri nets obtain from decorated cospans, and of course, we have an equivalence $\lOpen(\Petri) \sim F\lCsp$ of symmetric monoidal double categories by Theorem \cref{Equiv}.
+Thus we have a symmetric monoidal double category $\lOpen(\Petri)$ of open Petri nets obtained from structured cospans and a symmetric monoidal double category $F\lCsp$ of open Petri nets obtain from decorated cospans, and of course, we have an equivalence $\lOpen(\Petri) \sim F\lCsp$ of symmetric monoidal double categories by \cref{thm:equiv}.
 \end{comment}
@@
 \begin{defn}\label{def:companion}
-  Let \lD\ be a double category and $f\maps A\to B$ a vertical
+  Let $\lD$ be a double category and $f\maps A\to B$ a vertical
   1-morphism.  A \textbf{companion} of $f$ is a horizontal 1-cell
@@
   obtained by reversing the horizontal 1-cells, but not the vertical
-  1-morphisms, of \lD.
+  1-morphisms, of $\lD$.
 \end{defn}
@@
 In a pseudo double category, the second equation above requires an insertion of unit isomorphisms to make sense due to horizontal composition only holding up to isomorphism.
+
 \begin{defn}
+\label{defn:fibrant}
 We say that a double category is \textbf{fibrant} if every vertical
@@
 
+\bibitem{HS}  L.\ W.\ Hansen and M.\ Shulman, Constructing symmetric monoidal bicategories functorially.  Available as \href{https://arxiv.org/abs/1910.09240}{arXiv:1910.09240}.
+
 %\bibitem{Haug} R.\ Haugseng, Iterated spans and ``classical" topological field theories. Available as \href{https://arxiv.org/abs/1409.0837}{arXiv:1409.0837}.
@@
 
-\bibitem{Shul} M.\ Shulman, Constructing symmetric monoidal bicategories. Available as \href{http://arxiv.org/abs/1004.0993}{arXiv:1004.0993}.
-
-\bibitem{Shul2} M.\ Shulman, Framed bicategories and monoidal fibrations, \emph{Theory Appl.Categ.} \textbf{20} (2008), no.
+\bibitem{Shulman2008} M.\ Shulman, Framed bicategories and monoidal fibrations, \emph{Theory Appl.Categ.} \textbf{20} (2008), no.
 18, 650 -- 738, 2008.
@@
 
+\bibitem{Shulman2010} M.\ Shulman, Constructing symmetric monoidal bicategories. Available as \href{http://arxiv.org/abs/1004.0993}{arXiv:1004.0993}.
+
 %\bibitem{Stay} M.\ Stay, Compact closed bicategories.  Available as \href{http://arxiv.org/abs/1301.1053}{arXiv:1301.1053}.

### 2020-11-14 cospans.tex
More polishing up of Theorem 2.1

@@
 \item an object is an object of $\A$,
-\item a vertical morphism is a morphism of $\A$,
+\item a vertical 1-morphism is a morphism of $\A$,
 \item a horizontal 1-cell is an $F$\define{-decorated cospan}: that is, 
@@
 \node (G) at (1.5,-1) {$\tau \colon F(h)(x) \to x'$};
-\node (A'') at (0,-1.5) {$a$};
-\node (A''') at (0,-2.5) {$a'$};
-\node (B'') at (1,-1.5) {$m$};
-\node (C'') at (2,-1.5) {$b$};
-\node (C''') at (2,-2.5) {$b'$};
-\node (D'') at (1,-2.5) {$m'$};
-\node (E'') at (3,-1.5) {$x \in F(m)$};
-\node (F'') at (3,-2.5) {$x' \in F(m')$};
+\node (A'') at (0,-1.5) {$a'$};
+\node (A''') at (0,-2.5) {$a''$};
+\node (B'') at (1,-1.5) {$m'$};
+\node (C'') at (2,-1.5) {$b'$};
+\node (C''') at (2,-2.5) {$b''$};
+\node (D'') at (1,-2.5) {$m''$};
+\node (E'') at (3,-1.5) {$x' \in F(m')$};
+\node (F'') at (3,-2.5) {$x'' \in F(m'')$};
 \node (G'') at (1.5,-3) {$\tau' \colon F(h')(x') \to x''$};
@@
 % together with the composite morphism of decorations $\tau' \tau \colon F(h'h)(x) \to x'$ in $F(m'')$
+%% \tau' \tau was the notation that I was using, but I see why this was misleading. I believe it should be called \tau'(F(h')(\tau)) \instead of \tau' F(\tau), and also with target x''.
  This completes the descriptions of the category of objects $F\lCsp_0 = \A$ and the category of arrows $F\lCsp_1$.
@@
 \]
-$$\tau \maps F(h)(m) \to m'$$
+$$\tau \maps F(h)(x) \to x'$$
 the source is the morphism $f$ and the target is the morphism $g$. The three functors $S,T$ and $U$ satisfy the equations $SU=\id_{\A}=TU$.
 
-Next we define the composite functor $\odot \colon F\lCsp_1 \times_{F\lCsp_0} F\lCsp_1 \to F\lCsp_1$, which amounts to defining how we compose two composable $F$-decorated cospans or two maps of $F$-decorated cospans with a common source and target.
+Next we define the composite functor $\odot \colon F\lCsp_1 \times_{F\lCsp_0} F\lCsp_1 \to F\lCsp_1$, which amounts to defining how we compose two composable $F$-decorated cospans or horizontally compose two maps of $F$-decorated cospans with a common source and target.
 Given two composable $F$-decorated cospans which we respectively denote by $M$ and $N$, the capitals of their apices:
@@
 
-Lastly, our double category is required to have an associator $\alpha$ (\textbf{over using alpha, ignoring for now}) and left and right unitors $\lambda$ and $\rho$ which are natural isomorphisms governing the composition of horizontal 1-cells that are required to satisfy the standard coherence axioms for a monoidal category, as well as $S(\alpha),S(\lambda),S(\rho),T(\alpha),T(\lambda)$ and $T(\rho)$ all being identities.
+Lastly, our double category is required to have an associator $\alpha$ (\textbf{overusing alpha, ignoring for now}) and left and right unitors $\lambda$ and $\rho$ which are natural isomorphisms governing the composition of horizontal 1-cells that are required to satisfy the standard coherence axioms for a monoidal category, as well as $S(\alpha),S(\lambda),S(\rho),T(\alpha),T(\lambda)$ and $T(\rho)$ all being identities.
 We will only show the associator $\alpha$, left unitor $\lambda$ and the pentagon identity, as the remaining details will be similar to these.
@@
 \node (B) at (2,0) {$(m_1 +_b m_2) +_c m_3$};
-\node (C) at (4,0) {$b$};
+\node (C) at (4,0) {$d$};
 %\node (D) at (3,0) {$x \in F(m)$};
@@
 \node (B) at (2,0) {$m_1 +_b (m_2 +_c m_3)$};
-\node (C) at (4,0) {$b$};
+\node (C) at (4,0) {$d$};
 %\node (D) at (3,0) {$x \in F(m)$};
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (-1,0) {$((M_1 \odot M_2) \odot M_3) \odot M_4$};
+\node (A) at (-0.5,0) {$((M_1 \odot M_2) \odot M_3) \odot M_4$};
 \node (B) at (3,1.05) {$(M_1 \odot (M_2 \odot M_3)) \odot M_4$};
-\node (C) at (7,0) {$M_1 \odot ((M_2 \odot M_3) \odot M_4)$};
+\node (C) at (6.5,0) {$M_1 \odot ((M_2 \odot M_3) \odot M_4)$};
 \node (D) at (1.5,-1.05) {$(M_1 \odot M_2) \odot (M_3 \odot M_4)$};
@@
 
-\noindent
-\textbf{In progress...}
-%we get a natural isomorphism $a_{M_1,M_2,M_3} \maps (M_1 \odot M_2) \odot M_3 \to M_1 \odot (M_2 \odot M_3)$ which is a globular 2-morphism given by a map of cospans $(\id_{a_1},\sigma,\id_{a_4})$:
-%with the decorations on the cospan's apices given by:
-%$$ (x \odot y) \odot z \mapseqq 1 \xrightarrow{\zeta_1} F(m_1+_{b} m_2) \times F(m_3) \xrightarrow{\phi_{m_1+_{b} m_2, m_3}} F((m_1+_{b}m_2) +m_3) \xrightarrow{F(j_{m_1+_{b} m_2,m_3})} F((m_1+_{b} m_2)+_{c} m_3)$$ $$\zeta_1 = (1 \times z) \rho^{-1} F(j_{m_1,m_2}) \phi_{m_1,m_2} (x \times y) \lambda^{-1}$$
-%and
-%$$ x \odot (y \odot z) \mapseqq 1 \xrightarrow{\zeta_2} F(m_1) \times F(m_2 +_{c} m_3) \xrightarrow{\phi_{m_1, m_2 +_{c} m_3}} F(m_1+(m_2 +_{c} m_3)) \xrightarrow{F(j_{m_1,m_2 +_{c} m_3})} F(m_1+_{b} (m_2+_{c} m_3))$$ $$\zeta_2 = (x \times 1) \lambda^{-1} F(j_{m_2,m_3}) \phi_{m_2,m_3} (y \odot z) \lambda^{-1}$$
-%together with the isomorphism $\tau_\sigma \maps F(\sigma)((x \odot y) \odot z) \to x \odot (y \odot z)$.
-Note that the map $\sigma \maps (m_1+_{b} m_2)+_{c}m_3 \to m_1+_{b}(m_2+_{c}m_3)$ is the universal map between two colimits of the same diagram.
-
-\noindent
-We also have left and right unitors where given a horizontal 1-cell $M$:
+We next construct the left unitor. Given a horizontal 1-cell $M$:
 \[
@@
 \]
-if we, say, compose with the identity horizontal 1-cell of $b$ on the right:
+the left unitor will be a globular 2-morphism $\lambda \colon 1_a \odot M \to M$, where the identity horizontal 1-cell on the object $a$ will once again make use of the trivial decoration on an object introduced earlier.
 \[
@@
 \node (A) at (0,0) {$a$};
-\node (B) at (1,0) {$m$};
-\node (C) at (2,0) {$b$};
-\node (D) at (1,-0.5) {$x \in F(m)$};
-\node (E) at (3,0) {$b$};
-\node (F) at (4,0) {$b$};
-\node (G) at (5,0) {$b$};
-\node (H) at (4,-0.5) {$!_{b} \in F(b)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i$} (B)
-(C) edge node[above]{$o$} (B)
-(E) edge node[above]{$1$} (F)
-(G) edge node[above]{$1$} (F);
-\end{tikzpicture}
-\]
-where $!_{b} = F(!)  \phi \maps 1 \to F(b)$ is the trivial decoration on $b$, composing these then gives:
+\node (B) at (1,0) {$a$};
+\node (C) at (2,0) {$a$};
+\node (D) at (3,0) {$!_a \in F(a)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$\id_a$} (B)
+(C) edge node[above]{$\id_a$} (B);
+\end{tikzpicture}
+\]
+To compose $1_a$ and $M$, we first compose the two cospans in $\A$ by pushing out over their shared object $a$:
 \[
@@
 \node (A) at (0,0) {$a$};
-\node (B) at (1,0) {$m+_{b} b$};
-\node (C) at (2,0) {$b$};
-\node (D) at (3.5,0) {$x \odot !_b \in F(m +_{b} b)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$j \psi_m i$} (B)
-(C) edge node[above]{$j \psi_{b}$} (B);
-\end{tikzpicture}
-\]
-where $\psi_m \maps m \to m+b$ is the natural map into the coproduct and likewise for $\psi_{b}$ and $j \maps m+b \to m+_{b} b$ is the natural map from the coproduct to the pushout.
-The decoration $x \odot !_b \maps 1 \to F(m+_{b} b)$ is given by: $$1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{x \times !_{b}} F(m) \times F(b) \xrightarrow{\phi_{m,b}} F(m+b) \xrightarrow{F(j_{m,b})} F(m+_{b} b).$$ We then have that the right unitor $R \maps M \odot 1_{b} \xrightarrow{\sim} M$ is given by the globular 2-morphism $(\id_{a},r,\id_{b})$ from the above composite to $M$:
+\node (B) at (1,1) {$a$};
+\node (C) at (2,0) {$a$};
+\node (D) at (3,1) {$m$};
+\node (E) at (4,0) {$b$};
+\node (F) at (2,2) {$a+m$};
+\node (G) at (2,3) {$a+_{a} m$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$\id_a$} (B)
+(C) edge node[above]{$\id_a$} (B)
+(C) edge node [above] {$i$} (D)
+(E) edge node [above] {$o$} (D)
+(B) edge node [above] {$j_a$} (F)
+(D) edge node [above] {$j_m$} (F)
+(F) edge node [left] {$\psi$} (G)
+(A) edge[bend left] node [left] {$\psi j_a$} (G)
+(E) edge[bend right] node [right] {$\psi j_{m} o$} (G);
+\end{tikzpicture}
+\]
+The composite decoration $!_a \odot x$ will be given by the composite
+$$1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{!_a \times x} F(a) \times F(m) \xrightarrow{\phi_{a,m}} F(a+m) \xrightarrow{F(\psi)} F(a+_{a} m).$$
+The left unitor is then the map of $F$-decorated cospans determined by the following map of cospans in $\A$:
 \[
@@
 \node (A') at (0,-0.5) {$a$};
-\node (B) at (1.5,0.5) {$m+_{b} b$};
+\node (B) at (1.5,0.5) {$a+_{a} m$};
 \node (C) at (3,0.5) {$b$};
@@
 \node (D) at (1.5,-0.5) {$m$};
-\node (E) at (4.5,0.5) {$x \odot !_b \in F(m+_{b} b)$};
+\node (E) at (4.5,0.5) {$!_a \odot x \in F(a+_{a} m)$};
 \node (F) at (4.5,-0.5) {$x \in F(m)$};
 \path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$j \psi_m i$} (B)
-(C) edge node[above]{$j \psi_{b}$} (B)
+(A) edge node[above]{$\psi j_a$} (B)
+(C) edge node[above]{$\psi j_m o$} (B)
 (A) edge node[left]{$\id_{a}$} (A')
@@
 (C') edge node [above]{$o$} (D)
-(B) edge node [left] {$r$} (D);
-\end{tikzpicture}
-\]
-where $r \maps m+_{b} b \xrightarrow{\sim} m$ is a universal map together with the isomorphism $\tau_r \maps F(r)(x \odot !_b) \to x$.
-The left unitor is similar.
-The source and target functor applied to the left and right unitors and associators yield identities, and the left and right unitors together with the associator satisfy the standard pentagon and triangle identities of a monoidal category or bicategory.
-Finally, for the interchange law, given four 2-morphisms $\alpha, \beta, \alpha'$ and $\beta'$:
+(B) edge node [left] {$\ell$} (D);
+\end{tikzpicture}
+\]
+together with the morphism of decorations $\tau_\lambda \colon F(\ell)(!_a \odot x) \to x$; note, that $\ell \colon a+_a m \to m$ is a canonical isomorphism as both $a+_a m$ and $m$ are colimits of the span $a \xleftarrow{\id_a} a \xrightarrow{i} m$.
+The right unitor $\rho$ is similar, the two unitality squares are similar to the associator shown above, and it is clear that the source and target functors applied to the associator and left and right unitors yield identities.
+
+The final property that we will check is the interchange law for 2-morphisms. Suppose that we have four 2-morphisms $\alpha, \beta, \alpha'$ and $\beta'$ as shown below:
 \[
@@
 \]
-if we first compose horizontally we obtain:
+We may compose these first vertically and then horizontally, or first horizontally and then vertically, and we must show that these two ways of composing yield the same result.
+Composing first vertically and then horizontally results in:
 \[
@@
 \node (A) at (0,0.5) {$a$};
-\node (A') at (0,-0.5) {$a'$};
-\node (B) at (1.5,0.5) {$m+_{b} n$};
-\node (C) at (3,0.5) {$c$};
-\node (C') at (3,-0.5) {$c'$};
-\node (D) at (1.5,-0.5) {$m' +_{b'} n'$};
-\node (E) at (4.5,0.5) {$x \odot y \in F(m+_{b} n)$};
-\node (F) at (4.5,-0.5) {$x' \odot y' \in F(m' +_{b'} n')$};
-\node (G) at (1.5,-1) {$\tau_{\alpha \odot \beta} \maps F(h_1 +_g h_2)(x \odot y) \to x' \odot y'$};
-\node (A'') at (0,-1.5) {$a'$};
-\node (A''') at (0,-2.5) {$a''$};
-\node (B'') at (1.5,-1.5) {$m' +_{b\prime} n'$};
-\node (C'') at (3,-1.5) {$c'$};
-\node (C''') at (3,-2.5) {$c''$};
-\node (D'') at (1.5,-2.5) {$m'' +_{b''} n''$};
-\node (E'') at (4.5,-1.5) {$x' \odot y' \in F(m'+_{b'} n')$};
-\node (F'') at (4.5,-2.5) {$x'' \odot y'' \in F(m'' +_{b''} n'')$};
-\node (G'') at (1.5,-3) {$\tau_{\alpha' \odot \beta'} \maps F(h_1' +_{g'} h_2')(x' \odot y') \to x'' \odot y''.$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$j \psi_{m} i_1$} (B)
-(C) edge node[above]{$j \psi_{n} o_2$} (B)
-(A) edge node[left]{$f$} (A')
-(C) edge node[right]{$k$} (C')
-(A') edge node [above]{$j \psi_{m'} i_1'$} (D)
-(C') edge node [above]{$j \psi_{n'} o_2'$} (D)
-(B) edge node [left] {$h_1 +_g h_2$} (D)
-(A'') edge node[above]{$j \psi_{m'} i_1'$} (B'')
-(C'') edge node[above]{$j \psi_{n'} o_2'$} (B'')
-(A'') edge node[left]{$f'$} (A''')
-(C'') edge node[right]{$k'$} (C''')
-(A''') edge node [above]{$j \psi_{m''} i_1''$} (D'')
-(C''') edge node [above]{$j \psi_{n''} o_2''$} (D'')
-(B'') edge node [left] {$h_1' +_{g'} h_2'$} (D'');
-\end{tikzpicture}
-\]
+\node (A') at (0,-0.5) {$a''$};
+\node (B) at (2,0.5) {$m+_{b} n$};
+\node (C) at (4,0.5) {$c$};
+\node (C') at (4,-0.5) {$c''$};
+\node (D) at (2,-0.5) {$m'' +_{b''} n''$};
+\node (E) at (5.5,0.5) {$x \odot y \in F(m+_{b} n)$};
+\node (F) at (5.5,-0.5) {$x'' \odot y'' \in F(m'' +_{b''} n'')$};
+\node (G) at (2,-1) {$\tau_{(\alpha' \alpha) \odot (\beta' \beta)} \maps F((h_1' h_1)+_{g' g} (h_2' h_2))(x \odot y) \to x'' \odot y''$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$ \psi j_m i_1$} (B)
+(C) edge node[above]{$ \psi j_n o_2$} (B)
+(A) edge node[left]{$f' f$} (A')
+(C) edge node[right]{$k' k$} (C')
+(A') edge node [above]{$\psi j_{m''} i_1''$} (D)
+(C') edge node [above]{$\psi j_{n''} o_2''$} (D)
+(B) edge node [left] {$(h_1' h_1) +_{g' g} (h_2' h_2)$} (D);
+\end{tikzpicture}
+\]
+whereas first composing horizontally and then vertically results in:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0.5) {$a$};
+\node (A') at (0,-0.5) {$a''$};
+\node (B) at (2,0.5) {$m+_{b} n$};
+\node (C) at (4,0.5) {$c$};
+\node (C') at (4,-0.5) {$c''$};
+\node (D) at (2,-0.5) {$m'' +_{b''} n''$};
+\node (E) at (5.5,0.5) {$x \odot y \in F(m+_{b} n)$};
+\node (F) at (5.5,-0.5) {$x'' \odot y'' \in F(m'' +_{b''} n'')$};
+\node (G) at (2,-1) {$\tau_{(a' \odot \beta')(\alpha \odot \beta)} \maps F((h_1' +_{g'} h_2')(h_1 +_g h_2))(x \odot y) \to x'' \odot y''.$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$\psi j_{m} i_1$} (B)
+(C) edge node[above]{$\psi j_{n} o_2$} (B)
+(A) edge node[left]{$f' f$} (A')
+(C) edge node[right]{$k' k$} (C')
+(A') edge node [above]{$\psi j_{m''} i_1''$} (D)
+(C') edge node [above]{$\psi j_{n''} o_2''$} (D)
+(B) edge node [left] {$(h_1' +_{g'} h_2')(h_1 +_g h_2)$} (D);
+\end{tikzpicture}
+\]
+Everything about these two composites appears identical except for the two middle morphisms and the two morphisms of decorations.
+However, the two maps $(h_1' h_1) +_{g' g} (h_2' h_2) \maps m+_{b} n \to m'' +_{b''}n''$ and $(h_1' +_{g'} h_2')(h_1 +_g h_2) \maps m+_{b} n \to m'' +_{b''} n''$ are the same universal map realized in two different ways.
+The two morphisms of decorations $\tau_{(\alpha' \odot \beta')(\alpha \odot \beta)}$ and $\tau_{(\alpha' \alpha) \odot (\beta' \beta)}$ are also the same as they are obtained as two different compositions of four 2-morphisms in $\Cat$, namely first vertically and then horizontally and first horizontally and then vertically.
+The interchange law for $\Cat$ says that these two composites must be the same as well, and thus the interchange law for our double category $F\lCsp$ is also satisfied.
+ %\noindent
+%\textbf{In progress...}
+%we get a natural isomorphism $a_{M_1,M_2,M_3} \maps (M_1 \odot M_2) \odot M_3 \to M_1 \odot (M_2 \odot M_3)$ which is a globular 2-morphism given by a map of cospans $(\id_{a_1},\sigma,\id_{a_4})$:
+%with the decorations on the cospan's apices given by:
+%$$ (x \odot y) \odot z \mapseqq 1 \xrightarrow{\zeta_1} F(m_1+_{b} m_2) \times F(m_3) \xrightarrow{\phi_{m_1+_{b} m_2, m_3}} F((m_1+_{b}m_2) +m_3) \xrightarrow{F(j_{m_1+_{b} m_2,m_3})} F((m_1+_{b} m_2)+_{c} m_3)$$ $$\zeta_1 = (1 \times z) \rho^{-1} F(j_{m_1,m_2}) \phi_{m_1,m_2} (x \times y) \lambda^{-1}$$
+%and
+%$$ x \odot (y \odot z) \mapseqq 1 \xrightarrow{\zeta_2} F(m_1) \times F(m_2 +_{c} m_3) \xrightarrow{\phi_{m_1, m_2 +_{c} m_3}} F(m_1+(m_2 +_{c} m_3)) \xrightarrow{F(j_{m_1,m_2 +_{c} m_3})} F(m_1+_{b} (m_2+_{c} m_3))$$ $$\zeta_2 = (x \times 1) \lambda^{-1} F(j_{m_2,m_3}) \phi_{m_2,m_3} (y \odot z) \lambda^{-1}$$
+%together with the isomorphism $\tau_\sigma \maps F(\sigma)((x \odot y) \odot z) \to x \odot (y \odot z)$.
+Note that the map $\sigma \maps (m_1+_{b} m_2)+_{c}m_3 \to m_1+_{b}(m_2+_{c}m_3)$ is the universal map between two colimits of the same diagram.
+%\noindent
+%We also have left and right unitors where given a horizontal 1-cell $M$:
+%\[
+%\begin{tikzpicture}[scale=1.5]
+%\node (A) at (0,0) {$a$};
+%\node (B) at (1,0) {$m$};
+%\node (C) at (2,0) {$b$};
+%\node (D) at (3,0) {$x \in F(m)$};
+%\path[->,font=\scriptsize,>=angle 90]
+%(A) edge node[above]{$i$} (B)
+%(C) edge node[above]{$o$} (B);
+%\end{tikzpicture}
+%\]
+%if we, say, compose with the identity horizontal 1-cell of $b$ on the right:
+%\[
+%\begin{tikzpicture}[scale=1.5]
+%\node (A) at (0,0) {$a$};
+%\node (B) at (1,0) {$m$};
+%\node (C) at (2,0) {$b$};
+%\node (D) at (1,-0.5) {$x \in F(m)$};
+%\node (E) at (3,0) {$b$};
+%\node (F) at (4,0) {$b$};
+%\node (G) at (5,0) {$b$};
+%\node (H) at (4,-0.5) {$!_{b} \in F(b)$};
+%\path[->,font=\scriptsize,>=angle 90]
+%(A) edge node[above]{$i$} (B)
+%(C) edge node[above]{$o$} (B)
+%(E) edge node[above]{$1$} (F)
+%(G) edge node[above]{$1$} (F);
+%\end{tikzpicture}
+%\]
+%where $!_{b} = F(!)  \phi \maps 1 \to F(b)$ is the trivial decoration on $b$, composing these then gives:
+%\[
+%\begin{tikzpicture}[scale=1.5]
+%\node (A) at (0,0) {$a$};
+%\node (B) at (1,0) {$m+_{b} b$};
+%\node (C) at (2,0) {$b$};
+%\node (D) at (3.5,0) {$x \odot !_b \in F(m +_{b} b)$};
+%\path[->,font=\scriptsize,>=angle 90]
+%(A) edge node[above]{$j \psi_m i$} (B)
+%(C) edge node[above]{$j \psi_{b}$} (B);
+%\end{tikzpicture}
+%\]
+%where $\psi_m \maps m \to m+b$ is the natural map into the coproduct and likewise for $\psi_{b}$ and $j \maps m+b \to m+_{b} b$ is the natural map from the coproduct to the pushout.
+The decoration $x \odot !_b \maps 1 \to F(m+_{b} b)$ is given by: $$1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{x \times !_{b}} F(m) \times F(b) \xrightarrow{\phi_{m,b}} F(m+b) \xrightarrow{F(j_{m,b})} F(m+_{b} b).$$ We then have that the right unitor $R \maps M \odot 1_{b} \xrightarrow{\sim} M$ is given by the globular 2-morphism $(\id_{a},r,\id_{b})$ from the above composite to $M$:
+%\[
+%\begin{tikzpicture}[scale=1.5]
+%\node (A) at (0,0.5) {$a$};
+%\node (A') at (0,-0.5) {$a$};
+%\node (B) at (1.5,0.5) {$m+_{b} b$};
+%\node (C) at (3,0.5) {$b$};
+%\node (C') at (3,-0.5) {$b$};
+%\node (D) at (1.5,-0.5) {$m$};
+%\node (E) at (4.5,0.5) {$x \odot !_b \in F(m+_{b} b)$};
+%\node (F) at (4.5,-0.5) {$x \in F(m)$};
+%\path[->,font=\scriptsize,>=angle 90]
+%(A) edge node[above]{$j \psi_m i$} (B)
+%(C) edge node[above]{$j \psi_{b}$} (B)
+%(A) edge node[left]{$\id_{a}$} (A')
+%(C) edge node[right]{$\id_{b}$} (C')
+%(A') edge node [above]{$i$} (D)
+%(C') edge node [above]{$o$} (D)
+%(B) edge node [left] {$r$} (D);
+%\end{tikzpicture}
+%\]
+%where $r \maps m+_{b} b \xrightarrow{\sim} m$ is a universal map together with the isomorphism $\tau_r \maps F(r)(x \odot !_b) \to x$.
+The left unitor is similar.
+The source and target functor applied to the left and right unitors and associators yield identities, and the left and right unitors together with the associator satisfy the standard pentagon and triangle identities of a monoidal category or bicategory.
+Finally, for the interchange law, given four 2-morphisms $\alpha, \beta, \alpha'$ and $\beta'$:
+%if we first compose horizontally we obtain:
+%\[
+%\begin{tikzpicture}[scale=1.5]
+%\node (A) at (0,0.5) {$a$};
+%\node (A') at (0,-0.5) {$a'$};
+%\node (B) at (1.5,0.5) {$m+_{b} n$};
+%\node (C) at (3,0.5) {$c$};
+%\node (C') at (3,-0.5) {$c'$};
+%\node (D) at (1.5,-0.5) {$m' +_{b'} n'$};
+%\node (E) at (4.5,0.5) {$x \odot y \in F(m+_{b} n)$};
+%\node (F) at (4.5,-0.5) {$x' \odot y' \in F(m' +_{b'} n')$};
+%\node (G) at (1.5,-1) {$\tau_{\alpha \odot \beta} \maps F(h_1 +_g h_2)(x \odot y) \to x' \odot y'$};
+%\node (A'') at (0,-1.5) {$a'$};
+%\node (A''') at (0,-2.5) {$a''$};
+%\node (B'') at (1.5,-1.5) {$m' +_{b\prime} n'$};
+%\node (C'') at (3,-1.5) {$c'$};
+%\node (C''') at (3,-2.5) {$c''$};
+%\node (D'') at (1.5,-2.5) {$m'' +_{b''} n''$};
+%\node (E'') at (4.5,-1.5) {$x' \odot y' \in F(m'+_{b'} n')$};
+%\node (F'') at (4.5,-2.5) {$x'' \odot y'' \in F(m'' +_{b''} n'')$};
+%\node (G'') at (1.5,-3) {$\tau_{\alpha' \odot \beta'} \maps F(h_1' +_{g'} h_2')(x' \odot y') \to x'' \odot y''.$};
+%\path[->,font=\scriptsize,>=angle 90]
+%(A) edge node[above]{$j \psi_{m} i_1$} (B)
+%(C) edge node[above]{$j \psi_{n} o_2$} (B)
+%(A) edge node[left]{$f$} (A')
+%(C) edge node[right]{$k$} (C')
+%(A') edge node [above]{$j \psi_{m'} i_1'$} (D)
+%(C') edge node [above]{$j \psi_{n'} o_2'$} (D)
+%(B) edge node [left] {$h_1 +_g h_2$} (D)
+%(A'') edge node[above]{$j \psi_{m'} i_1'$} (B'')
+%(C'') edge node[above]{$j \psi_{n'} o_2'$} (B'')
+%(A'') edge node[left]{$f'$} (A''')
+%(C'') edge node[right]{$k'$} (C''')
+%(A''') edge node [above]{$j \psi_{m''} i_1''$} (D'')
+%(C''') edge node [above]{$j \psi_{n''} o_2''$} (D'')
+%(B'') edge node [left] {$h_1' +_{g'} h_2'$} (D'');
+%\end{tikzpicture}
+%\]
 %To obtain the morphism of decorations for a horizontal composite, we have as initial data:
@@
 %These two 2-morphisms $\tau_\alpha$ and $\tau_\beta$ are two 2-morphisms in the monoidal 2-category $(\Cat,\times,1)$ and so we can tensor them which results in:
-
-Returning to the interchange law, composing the two horizontal compositions above vertically then results in:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$a$};
-\node (A') at (0,-0.5) {$a''$};
-\node (B) at (2,0.5) {$m+_{b} n$};
-\node (C) at (4,0.5) {$c$};
-\node (C') at (4,-0.5) {$c''$};
-\node (D) at (2,-0.5) {$m'' +_{b''} n''$};
-\node (E) at (5.5,0.5) {$x \odot y \in F(m+_{b} n)$};
-\node (F) at (5.5,-0.5) {$x'' \odot y'' \in F(m'' +_{b''} n'')$};
-\node (G) at (2,-1) {$\tau_{(a' \odot \beta')(\alpha \odot \beta)} \maps F((h_1' +_{g'} h_2')(h_1 +_g h_2))(x \odot y) \to x'' \odot y''.$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$j \psi_{m} i_1$} (B)
-(C) edge node[above]{$j \psi_{n} o_2$} (B)
-(A) edge node[left]{$f' f$} (A')
-(C) edge node[right]{$k' k$} (C')
-(A') edge node [above]{$j \psi_{m''} i_1''$} (D)
-(C') edge node [above]{$j \psi_{n''} o_2''$} (D)
-(B) edge node [left] {$(h_1' +_{g'} h_2')(h_1 +_g h_2)$} (D);
-\end{tikzpicture}
-\]
-The vertical composite of two morphisms of decorations is straightforward. On the other hand, if we first compose vertically we obtain:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$a$};
-\node (A') at (0,-0.5) {$a''$};
-\node (B) at (1,0.5) {$m$};
-\node (C) at (2,0.5) {$b$};
-\node (C') at (2,-0.5) {$b''$};
-\node (D) at (1,-0.5) {$m''$};
-\node (E) at (3,0.5) {$x \in F(m)$};
-\node (F) at (3,-0.5) {$x'' \in F(m'')$};
-\node (G) at (4,0.5) {$b$};
-\node (H) at (5,0.5) {$n$};
-\node (I) at (6,0.5) {$c$};
-\node (G') at (4,-0.5) {$b''$};
-\node (H') at (5,-0.5) {$n''$};
-\node (I') at (6,-0.5) {$c''$};
-\node (J) at (7,0.5) {$y \in F(n)$};
-\node (K) at (7,-0.5) {$y'' \in F(n'')$};
-\node (L) at (1,-1) {$\tau_{\alpha' \alpha} \maps F(h_1' h_1)(x) \to x''$};
-\node (M) at (5,-1) {$\tau_{\beta' \beta} \maps F(h_2' h_2)(y) \to y''$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i_1$} (B)
-(C) edge node[above]{$o_1$} (B)
-(A) edge node[left]{$f' f$} (A')
-(C) edge node[right]{$g' g$} (C')
-(A') edge node[above] {$i_1''$} (D)
-(C') edge node[above] {$o_1''$} (D)
-(B) edge node [left] {$h_1' h_1$} (D)
-(G) edge node [above] {$i_2$} (H)
-(G) edge node [left] {$g' g$} (G')
-(H) edge node [left] {$h_2' h_2$} (H')
-(G') edge node [above] {$i_2''$} (H')
-(I) edge node [above] {$o_2$} (H)
-(I) edge node [right] {$k' k$} (I')
-(I') edge node [above] {$o_2''$} (H');
-\end{tikzpicture}
-\]
-and then composing horizontally results in:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$a$};
-\node (A') at (0,-0.5) {$a''$};
-\node (B) at (2,0.5) {$m+_{b} n$};
-\node (C) at (4,0.5) {$c$};
-\node (C') at (4,-0.5) {$c''$};
-\node (D) at (2,-0.5) {$m'' +_{b''} n''$};
-\node (E) at (5.5,0.5) {$x \odot y \in F(m+_{b} n)$};
-\node (F) at (5.5,-0.5) {$x'' \odot y'' \in F(m'' +_{b''} n'')$};
-\node (G) at (2,-1) {$\tau_{(\alpha' \alpha) \odot (\beta' \beta)} \maps F((h_1' h_1)+_{g' g} (h_2' h_2))(x \odot y) \to x'' \odot y''.$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$j \psi_{m} i_1$} (B)
-(C) edge node[above]{$j \psi_{n} o_2$} (B)
-(A) edge node[left]{$f' f$} (A')
-(C) edge node[right]{$k' k$} (C')
-(A') edge node [above]{$j \psi_{m''} i_1''$} (D)
-(C') edge node [above]{$j \psi_{n''} o_2''$} (D)
-(B) edge node [left] {$(h_1' h_1) +_{g' g} (h_2' h_2)$} (D);
-\end{tikzpicture}
-\]
+%Returning to the interchange law, composing the two horizontal compositions above vertically then results in:
+%\[
+%\begin{tikzpicture}[scale=1.5]
+%\node (A) at (0,0.5) {$a$};
+%\node (A') at (0,-0.5) {$a''$};
+%\node (B) at (2,0.5) {$m+_{b} n$};
+%\node (C) at (4,0.5) {$c$};
+%\node (C') at (4,-0.5) {$c''$};
+%\node (D) at (2,-0.5) {$m'' +_{b''} n''$};
+%\node (E) at (5.5,0.5) {$x \odot y \in F(m+_{b} n)$};
+%\node (F) at (5.5,-0.5) {$x'' \odot y'' \in F(m'' +_{b''} n'')$};
+%\node (G) at (2,-1) {$\tau_{(a' \odot \beta')(\alpha \odot \beta)} \maps F((h_1' +_{g'} h_2')(h_1 +_g h_2))(x \odot y) \to x'' \odot y''.$};
+%\path[->,font=\scriptsize,>=angle 90]
+%(A) edge node[above]{$j \psi_{m} i_1$} (B)
+%(C) edge node[above]{$j \psi_{n} o_2$} (B)
+%(A) edge node[left]{$f' f$} (A')
+%(C) edge node[right]{$k' k$} (C')
+%(A') edge node [above]{$j \psi_{m''} i_1''$} (D)
+%(C') edge node [above]{$j \psi_{n''} o_2''$} (D)
+%(B) edge node [left] {$(h_1' +_{g'} h_2')(h_1 +_g h_2)$} (D);
+%\end{tikzpicture}
+%\]
+%The vertical composite of two morphisms of decorations is straightforward. On the other hand, if we first compose vertically we obtain:
+%\[
+%\begin{tikzpicture}[scale=1.5]
+%\node (A) at (0,0.5) {$a$};
+%\node (A') at (0,-0.5) {$a''$};
+%\node (B) at (1,0.5) {$m$};
+%\node (C) at (2,0.5) {$b$};
+%\node (C') at (2,-0.5) {$b''$};
+%\node (D) at (1,-0.5) {$m''$};
+%\node (E) at (3,0.5) {$x \in F(m)$};
+%\node (F) at (3,-0.5) {$x'' \in F(m'')$};
+%\node (G) at (4,0.5) {$b$};
+%\node (H) at (5,0.5) {$n$};
+%\node (I) at (6,0.5) {$c$};
+%\node (G') at (4,-0.5) {$b''$};
+%\node (H') at (5,-0.5) {$n''$};
+%\node (I') at (6,-0.5) {$c''$};
+%\node (J) at (7,0.5) {$y \in F(n)$};
+%\node (K) at (7,-0.5) {$y'' \in F(n'')$};
+%\node (L) at (1,-1) {$\tau_{\alpha' \alpha} \maps F(h_1' h_1)(x) \to x''$};
+%\node (M) at (5,-1) {$\tau_{\beta' \beta} \maps F(h_2' h_2)(y) \to y''$};
+%\path[->,font=\scriptsize,>=angle 90]
+%(A) edge node[above]{$i_1$} (B)
+%(C) edge node[above]{$o_1$} (B)
+%(A) edge node[left]{$f' f$} (A')
+%(C) edge node[right]{$g' g$} (C')
+%(A') edge node[above] {$i_1''$} (D)
+%(C') edge node[above] {$o_1''$} (D)
+%(B) edge node [left] {$h_1' h_1$} (D)
+%(G) edge node [above] {$i_2$} (H)
+%(G) edge node [left] {$g' g$} (G')
+%(H) edge node [left] {$h_2' h_2$} (H')
+%(G') edge node [above] {$i_2''$} (H')
+%(I) edge node [above] {$o_2$} (H)
+%(I) edge node [right] {$k' k$} (I')
+%(I') edge node [above] {$o_2''$} (H');
+%\end{tikzpicture}
+%\]
+%and then composing horizontally results in:
+%\[
+%\begin{tikzpicture}[scale=1.5]
+%\node (A) at (0,0.5) {$a$};
+%\node (A') at (0,-0.5) {$a''$};
+%\node (B) at (2,0.5) {$m+_{b} n$};
+%\node (C) at (4,0.5) {$c$};
+%\node (C') at (4,-0.5) {$c''$};
+%\node (D) at (2,-0.5) {$m'' +_{b''} n''$};
+%\node (E) at (5.5,0.5) {$x \odot y \in F(m+_{b} n)$};
+%\node (F) at (5.5,-0.5) {$x'' \odot y'' \in F(m'' +_{b''} n'')$};
+%\node (G) at (2,-1) {$\tau_{(\alpha' \alpha) \odot (\beta' \beta)} \maps F((h_1' h_1)+_{g' g} (h_2' h_2))(x \odot y) \to x'' \odot y''.$};
+%\path[->,font=\scriptsize,>=angle 90]
+%(A) edge node[above]{$j \psi_{m} i_1$} (B)
+%(C) edge node[above]{$j \psi_{n} o_2$} (B)
+%(A) edge node[left]{$f' f$} (A')
+%(C) edge node[right]{$k' k$} (C')
+%(A') edge node [above]{$j \psi_{m''} i_1''$} (D)
+%(C') edge node [above]{$j \psi_{n''} o_2''$} (D)
+%(B) edge node [left] {$(h_1' h_1) +_{g' g} (h_2' h_2)$} (D);
+%\end{tikzpicture}
+%\]
 %The decorations of 
@@
 %\]
-As is usual concerning the interchange law of double categories of this nature, only the `interior' of the two composites appears different, but the two morphisms $(h_1' +_{g'} h_2')(h_1 +_g h_2) \maps m+_{b} n \to m'' +_{b''} n''$ and $(h_1' h_1) +_{g' g} (h_2' h_2) \maps m+_{b} n \to m'' +_{b''}n''$ are the same universal map realized in two different ways.
+%As is usual concerning the interchange law of double categories of this nature, only the `interior' of the two composites appears different, but the two morphisms $(h_1' +_{g'} h_2')(h_1 +_g h_2) \maps m+_{b} n \to m'' +_{b''} n''$ and $(h_1' h_1) +_{g' g} (h_2' h_2) \maps m+_{b} n \to m'' +_{b''}n''$ are the same universal map realized in two different ways.
 The two morphisms of decorations $\tau_{(\alpha' \odot \beta')(\alpha \odot \beta)}$ and $\tau_{(\alpha' \alpha) \odot (\beta' \beta)}$ are obtained as two different compositions of four 2-morphisms in $\Cat$, namely horizontally then vertically and vertically then horizontally.

### 2020-11-15 cospans.tex
Beginning to polish Theorem 2.2

@@
 \end{equation}
-together with a \define{morphism of decorations} $\tau \maps F(h)(x) \to x'$ in $F(m')$.
+together with a \define{decoration morphism} $\tau \maps F(h)(x) \to x'$ in $F(m')$.
 \end{itemize}
@@
 \]
-together with the composite morphism of decorations $\tau' F(\tau) \colon F(h'h)(x) \to x'$ in $F(m'')$.
+together with the composite decoration morphism $\tau' F(\tau) \colon F(h'h)(x) \to x'$ in $F(m'')$.
 % this was:
@@
 \]
-together with the morphism of decorations $\tau_{\alpha \odot \beta} \colon F(h_1 +_g h_2)(x \odot y) \to (x' \odot y')$ given by the following commutative diagram:
+together with the decoration morphism $\tau_{\alpha \odot \beta} \colon F(h_1 +_g h_2)(x \odot y) \to (x' \odot y')$ given by the following commutative diagram:
 \[
@@
 The middle square commutes since $F$ is a lax monoidal pseudofunctor and the right square commutes as the underlying square commutes.
-The decorations $x \odot y$ and $x' \odot y'$ are given respectively by the top and bottom composite of arrows and the morphism of decorations $\tau_{\alpha \odot \beta}$ is given by composing $\tau_\alpha \times \tau_\beta$ with the two commuting squares.
+The decorations $x \odot y$ and $x' \odot y'$ are given respectively by the top and bottom composite of arrows and the decoration morphism $\tau_{\alpha \odot \beta}$ is given by composing $\tau_\alpha \times \tau_\beta$ with the two commuting squares.
 It is clear that the equations $S(M \odot N)=S(M)$ and $T(M \odot N)=T(N)$ hold, and this finishes defining the four structure functors $U,S,T$ and $\odot$.
@@
 \]
-together with the morphism of decorations $\tau_\alpha \colon F(\alpha)((x_1 \odot x_2) \odot x_3) \to (x_1 \odot (x_2 \odot x_3))$ that is obtained by pasting various commutative squares together, as we did for a horizontal composite above.
+together with the decoration morphism $\tau_\alpha \colon F(\alpha)((x_1 \odot x_2) \odot x_3) \to (x_1 \odot (x_2 \odot x_3))$ that is obtained by pasting various commutative squares together, as we did for a horizontal composite above.
 The associator $\alpha$ will then satisfy the pentagon identity:
@@
 \]
-together with the morphism of decorations $\tau_\lambda \colon F(\ell)(!_a \odot x) \to x$; note, that $\ell \colon a+_a m \to m$ is a canonical isomorphism as both $a+_a m$ and $m$ are colimits of the span $a \xleftarrow{\id_a} a \xrightarrow{i} m$.
+together with the decoration morphism $\tau_\lambda \colon F(\ell)(!_a \odot x) \to x$; note, that $\ell \colon a+_a m \to m$ is a canonical isomorphism as both $a+_a m$ and $m$ are colimits of the span $a \xleftarrow{\id_a} a \xrightarrow{i} m$.
 The right unitor $\rho$ is similar, the two unitality squares are similar to the associator shown above, and it is clear that the source and target functors applied to the associator and left and right unitors yield identities.
@@
 \begin{thm}\label{DC}
-Let $\A$ be a category with finite colimits and $F \maps \A \to \Cat$ a symmetric lax monoidal pseudofunctor. Then the double category $F\mathbb{C}$sp is symmetric monoidal.
+Let $\A$ be a category with chosen finite colimits and $F \maps \A \to \Cat$ a symmetric lax monoidal pseudofunctor.
+Then the double category $F\lCsp$ of Theorem \ref{thm:decorated_cospans} is symmetric monoidal.
 \end{thm}
@@
 \begin{proof}
-First we note that the category of objects $F\lCsp_0=\A$ is symmetric monoidal under binary coproducts and the left and right unitors, associators and braidings are given as natural maps.
+The definition of symmetric monoidal double category may be found in Definition \ref{defn:smdc}.
+We must show that both the category of objects $F\lCsp_0$ and the category of arrows $F\lCsp_1$ are symmetric monoidal categories, show that the monoidal unit of $F\lCsp_0$ is preserved by the unit functor $U$, show that the source and target functors $S,T \colon F\lCsp_1 \to F\lCsp_0$ are strict symmetric monoidal functors which preserve the associativity and unit constraints, define the globular isomorphisms $\chi$ and $\mu$ that relate how composition and units interact with the tensor product, and check that the required axioms are satisfied.
+
+First we note that the category of objects $F\lCsp_0=\A$ is symmetric monoidal under chosen binary coproducts in $\A$ and the left and right unitors, associators and braidings are given as natural maps.
+Next we show that $F\lCsp_1$ is symmetric monoidal.
 The category of arrows $F\lCsp_1$ has:
 \begin{enumerate}
-\item{objects as $F$-decorated cospans which are pairs:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a$};
+\item{objects as $F$-decorated cospans, which are pairs:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$(a$};
 \node (B) at (1,0) {$m$};
-\node (C) at (2,0) {$b$};
-\node (D) at (3,0) {$x \in F(b)$};
+\node (C) at (2,0) {$b,$};
+\node (D) at (2.6,0) {$x \in F(m))$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 and}
-\item{morphisms as maps of cospans in $\A$
+\item{morphisms as maps of $F$-decorated cospans, which are cospans in $\A$
 \[
@@
 \]
-together with a morphism $\tau \maps F(h)(x) \to x'$.
+together with a decoration morphism $\tau \maps F(h)(x) \to x'$.
 }
 \end{enumerate}
-Given two objects $M_1$ and $M_2$ of $F\lCsp_1$:
+
+First we define the tensor product and monoidal unit of $F\lCsp_1$. Given two objects $M_1$ and $M_2$ of $F\lCsp_1$:
 \[
@@
 \]
-their tensor product $M_1 \otimes M_2$ is given by taking the coproducts of the cospans of $\A$
+their tensor product $M_1 \otimes M_2$ is given by taking the coproducts of the cospans in $\A$
 \[
@@
 \node (A) at (0,0) {$a_1+a_2$};
-\node (B) at (1.25,0) {$m_1+m_2$};
-\node (C) at (2.5,0) {$b_1+b_2$};
-\node (D) at (4.25,0) {$x_1+x_2 \in F(m_1+m_2)$};
+\node (B) at (1.5,0) {$m_1+m_2$};
+\node (C) at (3,0) {$b_1+b_2$};
+\node (D) at (4.55,0) {$x_1+x_2 \in F(m_1+m_2)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-and where the decoration on the apex is obtained using the natural transformation of the symmetric lax monoidal pseudofunctor $F:$ $$x_1+x_2 \mapseqq 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{x_1 \times x_2} F(m_1) \times F(m_2) \xrightarrow{\phi_{m_1,m_2}} F(m_1+m_2).$$The monoidal unit 0 is given by:
+and where the decoration on the apex is obtained using the natural transformation of the symmetric lax monoidal pseudofunctor $F$: $$x_1+x_2 \mapseqq 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{x_1 \times x_2} F(m_1) \times F(m_2) \xrightarrow{\phi_{m_1,m_2}} F(m_1+m_2).$$The monoidal unit $0_{F\lCsp_1}$ is given by:
 \[
@@
 where $0$ is the monoidal unit of $\A$ and $!_0 \maps 1 \to F(0)$ is the morphism which is part of the structure of the symmetric lax monoidal pseudofunctor $F \maps \A \to \Cat$.
-Tensoring an object with the monoidal unit, say, on the left:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$0$};
-\node (B) at (1,0) {$0$};
-\node (C) at (2,0) {$0$};
-\node (D) at (1,-0.5) {$!_0 \in F(0)$};
-\node (E) at (3,0) {$a$};
-\node (F) at (4,0) {$m$};
-\node (G) at (5,0) {$b$};
-\node (H) at (4,-0.5) {$x \in F(m)$};
-\node (I) at (2.5,0) {$\otimes$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$!$} (B)
-(C) edge node[above]{$!$} (B)
-(E) edge node[above]{$i$} (F)
-(G) edge node[above]{$o$} (F);
-\end{tikzpicture}
-\]
-results in:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$0+a$};
-\node (B) at (1,0) {$0+m$};
-\node (C) at (2,0) {$0+b$};
-\node (D) at (3.5,0) {$!_0 + x \in F(0+m)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$!+i$} (B)
-(C) edge node[above]{$!+o$} (B);
-\end{tikzpicture}
-\]
-where $!_0 + x \in F(0+m)$ is given by $$1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{!_0 \times x} F(0) \times F(m) \xrightarrow{\phi_{0,m}} F(0+m).$$The left unitor is then an isomorphism in $F\lCsp_1$ given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$0+a$};
-\node (A') at (0,-0.5) {$a$};
-\node (B) at (1,0.5) {$0+m$};
-\node (C) at (2,0.5) {$0+b$};
-\node (C') at (2,-0.5) {$b$};
-\node (D) at (1,-0.5) {$m$};
-\node (E) at (3.5,0.5) {$!_0 + x \in F(0+m)$};
-\node (F) at (3.5,-0.5) {$x \in F(m)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$!+i$} (B)
-(C) edge node[above]{$!+o$} (B)
-(A) edge node[left]{$\ell$} (A')
-(C) edge node[right]{$\ell$} (C')
-(A') edge node [above]{$i$} (D)
-(C') edge node [above]{$o$} (D)
-(B) edge node [left] {$\ell$} (D);
-\end{tikzpicture}
-\]
-where $\ell$ is the left unitor of $(\A,+,0)$, together with the isomorphism $\tau_{\lambda} \maps F(\ell)(!_0 + x) \to x$. The right unitor is similar.
-
-Given three objects $M_1, M_2$ and $M_3$ in $F\lCsp_1$:
+It is also clear that $U(0)=0_{F\lCsp_1}$.
+
+Next we define the associator and left unitor of $F\lCsp_1$, with the right unitor being similar to the left. Given three objects $M_1, M_2$ and $M_3$ of $F\lCsp_1$:
 \[
@@
 \node (A) at (0,0) {$(a_1+a_2)+a_3$};
-\node (B) at (2.25,0){$(m_1+m_2)+m_3$};
-\node (C) at (4.5,0) {$(b_1+b_2)+b_3$};
-\node (D) at (2.25,-0.5) {$(x_1+x_2)+x_3 \in F((m_1+m_2)+m_3)$};
+\node (B) at (2.5,0){$(m_1+m_2)+m_3$};
+\node (C) at (5,0) {$(b_1+b_2)+b_3$};
+\node (D) at (2.5,-0.5) {$(x_1+x_2)+x_3 \in F((m_1+m_2)+m_3)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-where $(x_1+x_2)+x_3 \maps 1 \to F((m_1+m_2)+m_3)$ is given by: $$1 \xrightarrow{(x_1 \times x_2) \times x_3} (F(m_1) \times F(m_2)) \times F(m_3) \xrightarrow{\phi_{m_1,m_2} \times 1} F(m_1+m_2) \times F(m_3) \xrightarrow{\phi_{m_1+m_2,m_3}} F((m_1+m_2)+m_3)$$whereas tensoring the last two and then the first results in $M_1 \otimes (M_2 \otimes M_3)$:
+where $(x_1+x_2)+x_3 \maps 1 \to F((m_1+m_2)+m_3)$ is given by: $$1 \xrightarrow{(x_1 \times x_2) \times x_3} (F(m_1) \times F(m_2)) \times F(m_3) \xrightarrow{\phi_{m_1,m_2} \times 1} F(m_1+m_2) \times F(m_3) \xrightarrow{\phi_{m_1+m_2,m_3}} F((m_1+m_2)+m_3).$$ The other parenthesization $M_1 \otimes (M_2 \otimes M_3)$ is given by:
 \[
@@
 \node (A) at (0,0) {$a_1+(a_2+a_3)$};
-\node (B) at (2.25,0) {$m_1+(m_2+m_3)$};
-\node (C) at (4.5,0) {$b_1+(b_2+b_3)$};
-\node (D) at (2.25,-0.5) {$x_1+(x_2+x_3) \in F(m_1+(m_2+m_3))$};
+\node (B) at (2.5,0) {$m_1+(m_2+m_3)$};
+\node (C) at (5,0) {$b_1+(b_2+b_3)$};
+\node (D) at (2.5,-0.5) {$x_1+(x_2+x_3) \in F(m_1+(m_2+m_3))$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-where $x_1+(x_2+x_3) \maps 1 \to F(m_1+(m_2+m_3))$ is given by: $$1 \xrightarrow{x_1 \times (x_2 \times x_3)} F(m_1) \times (F(m_2) \times F(m_3)) \xrightarrow{1 \times \phi_{m_2,m_3}} F(m_1) \times F(m_2+m_3) \xrightarrow{\phi_{m_1,m_2+m_3}} F(m_1+(m_2+m_3)).$$If we let $a$ denote the associator of $(\A,+,0)$, the associator of $F\lCsp_1$ is then a map of cospans in $\A$ from $(M_1 \otimes M_2) \otimes M_3$ to $M_1 \otimes (M_2 \otimes M_3)$ given by:
+where $x_1+(x_2+x_3) \maps 1 \to F(m_1+(m_2+m_3))$ is given by: $$1 \xrightarrow{x_1 \times (x_2 \times x_3)} F(m_1) \times (F(m_2) \times F(m_3)) \xrightarrow{1 \times \phi_{m_2,m_3}} F(m_1) \times F(m_2+m_3) \xrightarrow{\phi_{m_1,m_2+m_3}} F(m_1+(m_2+m_3)).$$
+\noindent
+\textbf{In progress}
+
+\noindent
+If we let $a$ denote the associator of $(\A,+,0)$, the associator of $F\lCsp_1$ is then a map of cospans in $\A$ from $(M_1 \otimes M_2) \otimes M_3$ to $M_1 \otimes (M_2 \otimes M_3)$ given by:
 \[
@@
 together with the isomorphism $\tau_a \maps F(a)((x_1+x_2)+x_3) \to x_1+(x_2+x_3)$.
+
+Tensoring an object with the monoidal unit, say, on the left:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$0$};
+\node (B) at (1,0) {$0$};
+\node (C) at (2,0) {$0$};
+\node (D) at (1,-0.5) {$!_0 \in F(0)$};
+\node (E) at (3,0) {$a$};
+\node (F) at (4,0) {$m$};
+\node (G) at (5,0) {$b$};
+\node (H) at (4,-0.5) {$x \in F(m)$};
+\node (I) at (2.5,0) {$\otimes$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$!$} (B)
+(C) edge node[above]{$!$} (B)
+(E) edge node[above]{$i$} (F)
+(G) edge node[above]{$o$} (F);
+\end{tikzpicture}
+\]
+results in:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$0+a$};
+\node (B) at (1,0) {$0+m$};
+\node (C) at (2,0) {$0+b$};
+\node (D) at (3.5,0) {$!_0 + x \in F(0+m)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$!+i$} (B)
+(C) edge node[above]{$!+o$} (B);
+\end{tikzpicture}
+\]
+where $!_0 + x \in F(0+m)$ is given by $$1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{!_0 \times x} F(0) \times F(m) \xrightarrow{\phi_{0,m}} F(0+m).$$The left unitor is then an isomorphism in $F\lCsp_1$ given by:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0.5) {$0+a$};
+\node (A') at (0,-0.5) {$a$};
+\node (B) at (1,0.5) {$0+m$};
+\node (C) at (2,0.5) {$0+b$};
+\node (C') at (2,-0.5) {$b$};
+\node (D) at (1,-0.5) {$m$};
+\node (E) at (3.5,0.5) {$!_0 + x \in F(0+m)$};
+\node (F) at (3.5,-0.5) {$x \in F(m)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$!+i$} (B)
+(C) edge node[above]{$!+o$} (B)
+(A) edge node[left]{$\ell$} (A')
+(C) edge node[right]{$\ell$} (C')
+(A') edge node [above]{$i$} (D)
+(C') edge node [above]{$o$} (D)
+(B) edge node [left] {$\ell$} (D);
+\end{tikzpicture}
+\]
+where $\ell$ is the left unitor of $(\A,+,0)$, together with the isomorphism $\tau_{\lambda} \maps F(\ell)(!_0 + x) \to x$. The right unitor is similar.
+
  These associators and left and right unitors together satisfy the pentagon and triangle identities of a monoidal category. 
@@
 
-\begin{defn}
+\begin{defn}\label{defn:smdc}
   A \textbf{monoidal double category} is a double category equipped the following

### 2020-11-16 cospans.tex
fixed some broken refs

@@
 
-In this paper, `double category' means `pseudo double category', as in \cref{defn:double_category}.   Following Shulman \cite{Shul}, vertical composition 
+In this paper, `double category' means `pseudo double category', as in \cref{defn:double_category}.   Following Shulman \cite{Shulman2008}, vertical composition 
 in our double categories is strictly associative, while horizontal composition need not be.
@@
 \end{gather}
-The second equivalence was also earlier observed by Shulman \cite{Shul2008}.
+The second equivalence was also earlier observed by Shulman \cite{Shulman2008}.
 In more detail, if $(\mu,\mu_0)$ is the lax monoidal structure of the pseudofunctor $F$ as recalled in \cref{sec:2cats}, each fibre category $\X_a=F(a)$ obtains a monoidal structure via
@@
 
-Another result of Shulman \cite{Shul2} is the following:
+Another result of Shulman \cite{Shulman2010} is the following:
 \begin{lem}[Shulman, Prop.\ B.3]
@@
 We will denote both kinds of morphisms and horizontal 1-cells as a single arrow, namely `$\to$'.
-We follow the notation of Shulman \cite{Shul} with the following definitions.
+We follow the notation of Shulman \cite{Shulman2008} with the following definitions.
 
@@
 
-Following the notation of Shulman \cite{Shul2}, given a double category $\mathbb{A}$, we write $_f \mathbb{A}_g(M,N)$ for the set of 2-morphisms in $\mathbb{A}$ of the form:
+Following the notation of Shulman \cite{Shulman2010}, given a double category $\mathbb{A}$, we write $_f \mathbb{A}_g(M,N)$ for the set of 2-morphisms in $\mathbb{A}$ of the form:
 \[

### 2020-11-16 cospans.tex
reviewed up to just before proof of 3.2

@@
 
-In this paper, `double category' means `pseudo double category', as in \cref{defn:double_category}.   Following Shulman \cite{Shulman2008}, vertical composition 
-in our double categories is strictly associative, while horizontal composition need not be.
-We use sans-serif font like $\C$ for categories, boldface like $\B$ for bicategories or
-2-categories, and blackboard bold like $\lD$ for double categories.   We also use blackboard
+In this paper, `double category' means `pseudo double category', as in \cref{defn:double_category}.
+Following Shulman \cite{Shulman2008}, vertical composition in our double categories is strictly associative, while horizontal composition need not be.
+We use sans-serif font like $\C$ for categories, boldface like $\B$ for bicategories or 2-categories, and blackboard bold like $\lD$ for double categories.
+We also use blackboard
 bold for weak category objects in any 2-category.
@@
 
-\begin{lem}
+\begin{lem}\label{lem:MonGroth}
  There is a 2-equivalence between the 2-categories of monoidal opfibrations and monoidal opindexed categories.
@@
 \begin{proof}
-This was shown by Moeller and the third author \cite[Theorems~3.13\&4.1]{MV}. In summary, we have correspondences
+This was shown by Moeller and the third author \cite[Theorems~3.13\&4.1]{MV}. In summary, for a cocartesian base we have correspondences
 \begin{gather}
@@
 These correspondences further restrict to the case when the Grothendieck category is specifically cocartesian monoidal itself. In that case, opfibrations
-$(\X,+)\to(\A,+)$ that strictly preserve chosen coproducts and initial object, and such that $+$ preserves cocartesian liftings, bijectively correspond to pseudofunctors into the 2-category of cocartesian categories; for more details, see \cite[Corollary 4.7]{MV} and the related discussion.
-%!!!
-Christina: someone wrote Rex there, perhaps it was me.
-This is a subcategory, not all finite colimits are there.
-
-{\chris In progress...}
-
-Finally, using the following result we can further restrict to our current case of interest, namely opfibrations that also preserve pushouts, i.e.
-all finite colimits.
-Of course, the following statement is more general since it relates the existence of any class of colimits in the total category of an opfibration to their existence in the fibres; for a more detailed exposition and proof, see \cite{Herm}.
+$(\X,+)\to(\A,+)$ that strictly preserve chosen coproducts and initial object
+%, and such that $+$ preserves cocartesian liftings, Christina: this should ALWAYS be the case, by universal properties!
+bijectively correspond to pseudofunctors into the 2-category of cocartesian categories; for more details, see \cite[Corollary 4.7]{MV} and the related discussion.
+
+Finally, we can further restrict to the setting of opfibrations that also preserve pushouts, i.e.
+all finite colimits, which is important for our purposes.
+The following result is in fact more general since it relates the existence of any class of colimits in the total category of an opfibration to their existence in the fibres; for a more detailed exposition, see \cite[Corollary~4.9]{Hermida1999}.
+%as well as Remark~4.11 therein regarding the non-necessary strictness condition. Is this obscuring or clarifying?
 
@@
  \item all fibres have $\ca{J}$-colimits, and the reindexing functors preserve them;
- \item the total $\X$ has $\ca{J}$-colimits, and $\U$ preserves them. %removed strict for now!
+ \item the total $\X$ has $\ca{J}$-colimits, and $\U$ (strictly) preserves them.
 \end{enumerate}
@@
 
-The first part formulates the existence of colimits \emph{locally} in each fibre, which can equivalently be expressed by the corresponding pseudofunctor $F\maps\A\to\bicat{Cat}$ landing on the sub-2-category $\bicat{Rex}$ of finitely cocomplete categories and functors that preserve colimits.
+The first part formulates the existence of colimits \emph{locally} in each fibre, which for $\ca{J}$ a finite category can equivalently be expressed by the corresponding pseudofunctor $F\maps\A\to\bicat{Cat}$ landing on the sub-2-category $\bicat{Rex}$ of finitely cocomplete categories and functors that preserve colimits.
 The second part formulates the existence of colimits \emph{globally} in the total category $\inta F$.
-Combining these, we can deduce the following.
+Combining this with \cref{lem:MonGroth}, we deduce the following.
 
@@
 
-On a different but related subject, for our purposes we are interested in the existence of a left adjoint $L_F$ to the induced monoidal opfibration $ \inta{F} \to \A$ by the Grothendieck construction as discussed above.
-The following result provides sufficient conditions for that, which go hand-in-hand with \cref{cor:fcocMonGroth} and \cref{lem:fibrewiselimits}.
-
-\begin{prop}\cite[Proposition~4.4]{Gray} \label{prop:opfibtolari}
+On a highly related note, in what follows we are also interested in the existence of a left adjoint $L_F$ to an induced monoidal opfibration; the following result provides sufficient conditions for that.
+%, which go hand-in-hand with \cref{cor:fcocMonGroth} and \cref{lem:fibrewiselimits}.
+
+\begin{lem}\label{prop:opfibtolari}
   Let $\U \maps\X \to \A$ be an opfibration. Then
@@
   reindexing functors.
-\end{prop}
+\end{lem}
 
 \begin{proof}\emph{(Sketch)}
+ This is \cite[Proposition~4.4]{Gray}.
 The left adjoint $L\maps\A\to\X$ maps an object $a$ to the initial object in its fibre $\X_a$, denoted by $\bot_a$.
@@
  \begin{equation}\label{eq:Lonarrows}
-  \bot_a\xrightarrow{\Rex(f,\bot_a)}f_!(\bot_a)\xrightarrow{\;\stackrel{\chi_a}{\cong}\;}\bot_{a'}
+  \bot_a\xrightarrow{\mathrm{Cocart}(f,\bot_a)}f_!(\bot_a)\stackrel{\chi_a}{\cong}\bot_{a'}
  \end{equation}
-where $\chi_a$ is the unique isomorphism between the initial objects in the fibre above $a'$ since $f_!$ preserves them.
+where $\mathrm{Cocart}(f,\bot_a)$ is the cocartesian lifting of $\bot_a$ along $f$ and $\chi_a$ is the unique isomorphism between the initial objects in the fibre above $a'$ since $f_!$ preserves them.
 \end{proof}
 
+Ongoing work \cite{CV} includes a related discussion as well as a result in the opposite direction.
+%For a discussion on the unusual strict cocontinuity condition...
+%\begin{lem}\label{prop:CV}\cite[Proposition~3.3]{CV}
+%Suppose $\U\maps\X\to\A$ is a right adjoint `left inverse'. If $\X$ and $\A$ have chosen pushouts and initial objects and $\U$ strictly preserves them, %then $\U$ is an opfibration.
+%\end{lem}
+
 \begin{rmk}\label{rmk:important}
-Notice that under \cref{lem:fibrewiselimits}, if $\A$ has an initial object $0_\A$, the above conditions are equivalent to $\X$ having an initial object $0_\X$ above $0_\A$.
-%Christina: hiding strict preservence under the rug
-In this case, $\bot_a$ is precisely the cocartesian lifting of $0_\X$ along the unique map $u_a\maps0_\A\to a$ in the base category:
+Notice that under \cref{lem:fibrewiselimits}, if the base category $\A$ has an initial object denoted $0_\A$, the above is equivalent to $\X$ having an initial object $0_\X$ above $0_\A$.
+The way in which these two conditions give one another in this case is as follows.
+The fibrewise initial object $\bot_a$ is precisely the cocartesian lifting of $0_\X$ along the unique map $u_a\maps0_\A\to a$ in the base category
 \begin{displaymath}
@@
 \end{displaymath}
-Moreover, if $U=U_F$ for a pseudofunctor $F\maps\A\to\bicat{Cat}$ under \cref{thm:Grothendieck}, the reindexing functors $(u_a)_!$ of the opfibration are precisely $F(u_a)$, therefore $\bot_a=(a,F(u_a)(0_\X))$ in the Grothendieck category, for $u_a$ the unique map from $0_\A$ as above.
-
-Finally, if that pseudofunctor is lax monoidal $(F,\phi,\phi_0)\maps(\A,+)\to(\bicat{Cat},\times)$ to begin with, the monoidal Grothendieck construction in the cocartesian case discussed earlier \cref{eq:explicitstructure1} expresses $\bot_a$ as the image of the composite
+Moreover, if the opfibration $U$ comes from the Grothendieck construction on a pseudofunctor $F\maps\A\to\bicat{Cat}$, the reindexing functors $(u_a)_!$ of the opfibration are precisely $F(u_a)$ therefore $\bot_a=(a,F(u_a)(0_\X))$ in the Grothendieck category notation (\cref{def:GrothCat}).
+
+Finally, if the original pseudofunctor is in fact lax monoidal $(F,\mu,\mu_0)$, the monoidal Grothendieck construction of \cref{lem:MonGroth} in the cocartesian case expresses $\bot_a$ as follows by \cref{eq:explicitstructure1}:
 \begin{equation}\label{eq:initialinfibre}
@@
 
-%will be a right adjoint to some adjoint , and moreover the unit of the adjunction is the identity; this is called \emph{lari} in [Gray].
-
-%!!!Christina: not sure if the below is needed after all
-In the opposite direction, we also have the following result. For a discussion on the unusual strict cocontinuity condition, we refer the reader to \cite{CV}.
-
-\begin{lem}\label{prop:CV}\cite[Proposition~3.3]{CV}
-Suppose $\U\maps\X\to\A$ is a right adjoint `left inverse'. If $\X$ and $\A$ have chosen pushouts and initial objects and $\U$ strictly preserves them, then $\U$ is an opfibration.
-\end{lem}
-%Christina: do we need this direction after all? Discuss.
-%\begin{thm}\label{thm:mainthmDX}\cite{CV}
-%Suppose that $\X$ and $\A$ have chosen pushouts and initial objects, and a functor $\U\maps\X\to\A$ strictly preserves them.
-Then $\U$ is a right %adjoint left inverse if and only if $\U$ is an opfibration.
-%\end{thm}
-
-We have now laid all the necessary background to formally construct an equivalence between the double category of decorated cospans and the double category of structured cospans, constructed from a symmetric lax monoidal pseudofunctor into $\bicat{Cat}$.
+We have now laid all the necessary background to formally construct an equivalence between the double category of decorated cospans and the double category of structured cospans, with starting point a symmetric lax monoidal pseudofunctor into $\bicat{Cat}$.
+
+{\chris In progress...}
 
@@
 We recall some basics regarding opfibrations and their relation to pseudofunctors into $\bicat{Cat}$ via the Grothendieck construction.
-Standard material on the theory of fibrations can be found for example in \cite{Herm}, \cite{Borc}.
+Standard material on the theory of fibrations can be found for example in \cite{Borc,Gray}.
 
@@
 %\xymatrix @C=.4in @R=.2in
-%{x \ar @{.>}[dd]\ar[rr]^\gamma \ar[drr]_-{\Rex(g,C)} && D &\\
+%{x \ar @{.>}[dd]\ar[rr]^\gamma \ar[drr]_-{\mathrm{Cocart}(g,C)} && D &\\
 %&& f_!C \ar @{-->}[u]_-{\delta} \ar @{.>}[d] & \textrm{in }\C  \\
@@
 
-\bibitem{Gray} J. \ Gray, Fibred and Cofibred categories, Proc. Conf. Categorical Algebra (La Jolla, California, 1965), 21---83, New York, 1966
+\bibitem{Gray} J. \ Gray, Fibred and Cofibred categories, \emph{Proc. Conf. Categorical Algebra} (La Jolla, California, 1965), 21---83, New York, 1966
 
@@
 \bibitem{Herm} C. \ Hermida, Fibrations, logical predicates and indeterminates, PhD Thesis, University of Edinburgh, 1993.
+
+\bibitem{Hermida1999} C. \ Hermida, Some properties of Fib as a fibred 2-category. \emph{J. Pure Appl. Algebra}, 134(1), 83 -- 109, 1999
 

### 2020-11-16 cospans.tex
few edits on fibrations background

@@
 \subsection{Fibrations}\label{sec:fibrations}
-We recall some basics regarding opfibrations and their relation to pseudofunctors into $\bicat{Cat}$ via the Grothendieck construction.
-Standard material on the theory of fibrations can be found for example in \cite{Borc,Gray}.
-
-A functor $U \maps \X \to \A$ is an \textbf{opfibration} if for every $x\in\X$ with $U(x)=a$ and $f \maps a \to b$ in $\A$, there exists a \textbf{cocartesian lifting} of $x$ along $f$, namely a morphism $\beta$ in $\X$ with domain $x$ above $f$ with the following universal property: for any $g\maps b\to b'$ in $\A$ and $\gamma\maps x\to y'$ in $\X$ above the composite $g\circ f$, there exists a unique $\delta\maps y\to y'$ such that $U(\delta)=g$ and $\gamma=\delta\circ\beta$ as shown below
+Basic material regarding the theory of fibrations can be found, for example, in \cite{Borc,Gray}.
+Recall that a functor $U \maps \X \to \A$ is an \textbf{opfibration} if for every $x\in\X$ with $U(x)=a$ and $f \maps a \to b$ in $\A$, there exists a \textbf{cocartesian lifting} of $x$ along $f$, namely a morphism $\beta$ in $\X$ with domain $x$ above $f$ with the following universal property: for any $g\maps b\to b'$ in $\A$ and $\gamma\maps x\to y'$ in $\X$ above the composite $g\circ f$, there exists a unique $\delta\maps y\to y'$ such that $U(\delta)=g$ and $\gamma=\delta\circ\beta$ as shown below
 \begin{displaymath}
@@
 \end{displaymath}
-
-%\begin{defn}
-%Let $P \maps \ca{X} \to \ca{A}$ be a functor.
-A morphism $f \maps d_1 \to d_{2}$ in the category $\mathrm{D}$ is \textbf{cocartesian (with respect to the functor P)} if for any object $d'$ in $\mathrm{D}$ and morphism $g \maps d_1 \to d'$ and every $p \maps P(d_{2}) \to P(d')$ such that $P(g)=p P(f)$, there exists a unique $h \maps d_{2} \to d'$ such that $g=hf$ and $p=P(h)$.
-%\[
-%\begin{tikzpicture}[scale=1.5]
-%\node (A) at (0,0) {$d'$};
-%\node (B) at (0,-1) {$d_{2}$};
-%\node (C) at (1.5,-1) {$d_1$};
-%\node (H) at (2,-0.25) {$P$};
-%\node (D) at (2,-.5) {$\mapsto$};
-%\node (E) at (3,0) {$P(d')$};
-%\node (F) at (3,-1) {$P(d_{2})$};
-%\node (G) at (4.5,-1) {$P(d_1)$};
-%\path[->,font=\scriptsize,>=angle 90]
-%(B) edge[dashed] node[above,left]{$\exists ! h$} (A)
-%(C) edge node[above,right]{$g$} (A)
-%(F) edge node[above,left]{$p=P(h)$} (E)
-%(G) edge node[above]{$P(f)$} (F)
-%(G) edge node[above,right]{$P(g)$} (E)
-%(C)edge node[above]{$f$}(B);
-%\end{tikzpicture}
-%\]
-%\end{defn}
-%\begin{defn}
-%A functor $P \maps \mathrm{D} \to \mathrm{A}$ is a \textbf{(Grothendieck) opfibration} if for any object $d$ in $\mathbf{D}$ and morphism $f \maps c %\to P(d)$ there exists a cocartesian morphism $\phi \maps d' \to d$ such that $P(\phi)=f$.
-%\end{defn}
-%\begin{defn}
-%Let $P \maps \mathrm{D} \to \mathrm{A}$ and $P' \maps \mathrm{D'} \to \mathrm{A}$ be opfibrations over a category $\mathrm{A}$.
-A \define{morphism of opfibrations} is a functor $F \maps \mathrm{D} \to \mathrm{D}'$ such that $F(p)$ is cocartesian with respect to $P'$ if $p$ is cocartesian with respect to $P$ and $P=P' F$.
-%\end{defn}
 The category $\X$ is called the \textbf{total} category and $\A$ is called the \textbf{base} category of the opfibration.
@@
 Assuming the axiom of choice, we may select a cocartesian arrow over each $f\maps a\to b$ in $\A$ and $x\in\X _a$, denoted by $\mathrm{Cocart}(f,x)\maps x\to f_!(x)$, rendering $U$ a so-called \textbf{cloven} opfibration.
-This choice induces \textbf{reindexing functors} $f_!\maps\X _a\to\X _b$ between the fibre categories, which by the liftings universal property adhere to natural $(1_a)_!\cong1_{\X _a}$ and $(f\circ g)_!\cong f_!\circ g_!$.
+This choice induces \textbf{reindexing functors} $f_!\maps\X _a\to\X _b$ between the fibre categories, which by the liftings universal property adhere to natural isomorphisms $(1_a)_!\cong1_{\X _a}$ and $(f\circ g)_!\cong f_!\circ g_!$.
 If these isomorphisms are equalities, we have the notion of a \textbf{split} opfibration.
+We chose to primarily present this dual notion to \define{fibration} due to the current work's needs.
 %Christina: decide later if needed
@@
 In fact, there is a 2-equivalence between opfibrations and pseudofunctors induced by the so-called \emph{Grothendieck construction}.
-%{\chris I don't mind this presentation of the Grothendieck construction which I admit not having seeing before.
-If we are to keep, we should put a reference.
-Otherwise we could stay more low level about this and just briefly describe what's going on.}
-%\begin{defn}
-%Let $\Cat_{\textnormal{lax},\star}$ denote the \define{2-category of lax-pointed categories} which has:
-%\begin{enumerate}
-%\item{objects as pairs $(\mathrm{A},c)$ where $\mathrm{A}$ is a category and $c$ is an object of $\mathrm{A}$, and}
-%\item{a morphism from $(\mathrm{A},c)$ to $(\mathrm{X},y)$ is a pair $(F,f)$ where $F \maps \mathrm{A} \to \mathrm{X}$ is a functor and $f \maps F(c) \to y$ is a morphism in $\mathrm{X}$.}
-%\end{enumerate}
-%\end{defn}
-%\begin{defn}
-%Given a pseudofunctor $F \maps \mathrm{A} \to \Cat$, the \define{Grothendieck construction of} $F$ is given by the `strict 2-pullback' of the following cospan:
-% \[
-%\begin{tikzpicture}[scale=1.5]
-%\node (D) at (1,1) {$\inta F$};
-%\node (A) at (0,0) {$\mathrm{A}$};
-%\node (B) at (1,-1) {$\Cat$};
-%\node (C) at (2,0) {$\Cat_{\textnormal{lax},\star}$};
-%\path[->,font=\scriptsize,>=angle 90]
-%(D) edge[dashed] node[above]{$p$} (A)
-%(D) edge[dashed] node[above]{$q$} (C)
-%(A) edge node[below]{$F$} (B)
-%(C) edge node[below]{$P$} (B);
-%\end{tikzpicture}
-%\]
-%where $P \maps \Cat_{\textnormal{lax},\star} \to \Cat$ is the forgetful functor. 
 \begin{defn}\label{def:GrothCat}
@@
 \end{itemize}
-%!!!Christina: Might need to write the composition rule? Depending on the final proof of Big Theorem.
 This is an opfibred category over $\A$ via the obvious forgetful functor, with fibre categories $(\inta F)_a=F(a)$ and reindexing functors $f_!=F(f)$.
 \end{defn}
-%This can also be thought of as a morphism and a 2-morphism:
-%\[
-%\begin{tikzpicture}[scale=1.5]
-%\node (A) at (0,0) {$\star$};
-%\node (B) at (1,0.5) {$F(c)$};
-%\node (C) at (1,-0.5) {$F(c')$};
-%\node (D) at (2,0.5) {$c$};
-%\node (E) at (2,-0.5) {$c'$};
-%\node (F) at (0.65,0) {$\Swarrow \alpha$};
-%\path[->,font=\scriptsize,>=angle 90]
-%(A) edge node[above]{$d$} (B)
-%(B) edge node[right]{$F(f)$} (C)
-%(A) edge node[below]{$d'$} (C)
-%(D) edge node[left] {$f$} (E);
-%\end{tikzpicture}
-%\]
 The above in fact provides the one direction of the following well-known equivalence.
-%gives rise to a 2-functor $[\A,\bicat{Cat}]_\pse\to \Cat/ \A$ which factors through the embedding $\OpFib(\A) \hookrightarrow \bicat{Cat} / \A$ as per the following theorem.
-%: $$\inta F \maps [ \mathrm{A}, \Cat ] \to \textnormal{Opfib}(\mathrm{A}) \hookrightarrow \Cat / \mathrm{A}.$$
 
@@
     \begin{enumerate}
-        \item Every opfibration $\U \maps \X \to \A$ gives rise to a pseudofunctor $F_U \maps \A \to \bicat{Cat}$.
-        \item Every pseudofunctor $F \maps \A \to \bicat{Cat}$ gives rise to  an opfibration $\U_F \maps \inta F\to\A$.
+        \item Every opfibration $\U \maps \X \to \A$ gives rise to a pseudofunctor $\A \to \bicat{Cat}$.
+        \item Every pseudofunctor $F \maps \A \to \bicat{Cat}$ gives rise to  an opfibration $\maps \inta F\to\A$.
         \item The above correspondences yield an equivalence of 2-categories 
@@
         \end{displaymath}
-        so that $F_{\U_F} \cong F$ and $\U_{F_\U} \cong \U$.
 %        \item The above 2-equivalence extends to one between 2-categories of arbitrary-base fibrations and arbitrary-domain indexed categories

### 2020-11-16 cospans.tex
a few edits

@@
 \address{$^3$Department of Mathematics, University of Patras, Greece 265 04}
-\email{baez@math.ucr.edu, kcour001@ucr.edu, cvasilak@math.upatrs.gr}
+\email{baez@math.ucr.edu, kcour001@ucr.edu, cvasilak@math.upatras.gr}
 
@@
 \begin{thm} \label{thm:equiv}
-Suppose $\ca{A}$ has finite colimits and $(F,\phi,\phi_0)\maps(\ca{A},+) \to (\bicat{Cat},\times,1)$ is a symmetric lax monoidal pseudofunctor that factors through $\bicat{Rex}$ as an ordinary pseudofunctor.
-Then the symmetric monoidal double category $F\lCsp$ of decorated cospans is equivalent to the symmetric monoidal double category $_L\lCsp(\inta F)$ of structured cospans, where $L \maps \A \to \inta F$ is the left adjoint of the induced Grothendieck opfibration $\U\maps \inta F \to \A$.
+Suppose $\ca{A}$ has finite colimits and $(F,\mu,\mu_0)\maps(\ca{A},+) \to (\bicat{Cat},\times)$ is a symmetric lax monoidal pseudofunctor that factors through $\bicat{Rex}$ as an ordinary pseudofunctor.
+Then the symmetric monoidal double categories $F\lCsp$ of decorated cospans and $_L\lCsp(\inta F)$ of structured cospans are equivalent, where $L \maps \A \to \inta F$ is a left adjoint of the induced Grothendieck opfibration $\U\maps \inta F \to \A$.
 \end{thm}
 
-The conditions of the above theorem relate to the existence of left adjoints for opfibrations; we first sketch this underlying framework, and then we proceed to the proof of the theorem.
+The conditions of the above theorem relate to the existence of colimits as well as left adjoints for opfibrations.
+We first sketch this underlying framework, and then we proceed to the proof of the theorem.
 The basics of fibration theory needed for our purposes are recalled in \cref{sec:fibrations}.
@@
 
-Ongoing work \cite{CV} includes a related discussion as well as a result in the opposite direction.
+Work in progress \cite{CV} includes a related discussion as well as a result in the opposite direction.
 %For a discussion on the unusual strict cocontinuity condition...
@@
 
-{\chris In progress...}
-
 \begin{proof}[Proof of \cref{thm:equiv}]
-Recall from \cref{thm:decorated_cospans} that the double category of decorated cospans $\dcsp{F}$ has objects and vertical 1-morphisms as in $\A$, while a horizontal 1-cell $a\tickar b$ is cospan $\cspn{a}{m}{b}{}{}$ in $\A$ decorated by an object $x\in F(m)$ and a 2-morphism is a map $k\maps m\to m'$ together with a morphism $(Fk)(x)\to x'$.
-
-By \cref{cor:fcocMonGroth}, when $F$ as an ordinary pseudofunctor factors through $\bicat{Rex}$, the (monoidal) Gro\-the\-ndieck construction gives rise to a finitely cocomplete $\inta F$ such that the corresponding opfibration $U_F\maps(\inta{F},+)\to(\A,+)$ preserves all finite colimits.
-%Christina: maybe the cocartesian structures are redundant to write here, since U_F really preserves all finite colimits anyways.
-Since in particular it preserves the initial object, \cref{prop:opfibtolari} through \cref{lem:fibrewiselimits} applies 
+Recall from \cref{thm:decorated_cospans} that the double category of decorated cospans $\dcsp{F}$ has objects and vertical 1-morphisms as in $\A$, while horizontal 1-cells are cospans $\cspn{a}{m}{b}{}{}$ in $\A$ decorated by an $x\in F(m)$ and 2-morphisms are maps of cospans $k\maps m\to m'$ together with $\tau\maps(Fk)(x)\to x'$ in $F(m')$.
+%!!!
+Christina: Should we call them `generalized maps of cospans'?
+Since maps of cospans are usually the ones with fixed (co)domains
+
+By \cref{cor:fcocMonGroth}, when $F$ as an ordinary pseudofunctor factors through $\bicat{Rex}$, the Gro\-the\-ndieck construction gives rise to a finitely cocomplete $\inta F$ such that the corresponding opfibration $U\maps\inta{F}\to\A$ preserves all finite colimits.
+Since in particular it preserves the initial object, \cref{lem:fibrewiselimits,prop:opfibtolari} apply 
 %which equivalently means that all fibres have initial objects and the reindexing functors preserve them by , %Christina: there is a little bit of circularity here.
@@
 Change Gray accordingly perhaps?
-to construct a left adjoint $L_F\maps\A\to\inta F$ which is also a right inverse, namely $U_FL_F=\mathrm{id}_\A$.
-Explicitly, this left adjoint is given by $L(a)=(a,\bot_a)$, picking the initial object in the finitely cocomplete fibre also expressed as $F(u_a)\circ\phi_0(*)$ in \cref{eq:initialinfibre}.
+and produce a left adjoint $L\maps\A\to\inta F$ to $U$, with $UL=1_\A$. 
 Diagrammatically,
 \begin{displaymath}
- F\maps\X\to\bicat{Cat}\quad\mapsto\quad\begin{tikzcd}[baseline=.3]\inta F\ar[d,"U_F"'] \\ \X \end{tikzcd}\quad\mapsto\quad\begin{tikzcd}\X\ar[r,bend left,pos=.55,"L_F"]\ar[r,phantom,"\bot"description] & \inta F\ar[l,bend left,pos=.45,"U_F"]\end{tikzcd}
+ F\maps\A\to\bicat{Cat}\quad\mapsto\quad\begin{tikzcd}[baseline=.3]\inta F\ar[d,"U"'] \\ \A \end{tikzcd}\quad\mapsto\quad\begin{tikzcd}\A\ar[r,bend left,pos=.55,"L"]\ar[r,phantom,"\bot"description] & \inta F\ar[l,bend left,pos=.45,"U"]\end{tikzcd}
 \end{displaymath}
-roughly describes the processes between the original $F$ and the resulting $L_F$.
+describes the construction of the adjunction from the original $F$.
+Explicitly, the left adjoint picks the initial object in the finitely cocomplete fibre $L(a)=(a,\bot_a)$, also expressed by $F(u_a)\circ\mu_0(*)$ as in \cref{eq:initialinfibre}.
+
+{\chris In progress...}
 
@@
 \subsection{2-categories}\label{sec:2cats}
-For standard 2-categorical material, we refer the reader to e.g. \cite{KS} or \cite{DS} for monoidal structures.
+For standard 2-categorical material, we refer the reader to e.g. \cite{KS} or \cite{DS} for monoidal structures. %!!!Christina: also John's paper on monoidal 2-structures?
 Recall that a \define{pseudofunctor} $F\maps\bicat{A}\to\bicat{B}$ between bicategories $\bicat{A}$ and $\bicat{B}$ is functorial up to coherent natural isomorphism, namely for composable arrows we have $F(g\circ f)\cong Fg\circ Ff$ and $F(1_a)\cong1_{Fa}$ satisfying standard axioms.
@@
 %Christina: I removed the above, they are not needed I believe. Check again in the end.
-We denote by $[\A,\bicat{Cat}]_\pse$ the 2-category 
-of pseudofunctors, pseudonatural transformations and modifications from an ordinary category $\A$ viewed as a 2-category with trivial 2-cells, into $\bicat{Cat}$.
-This is also referred to as the 2-category of \emph{opindexed categories}, since an indexed category is a contravariant pseudofunctor into $\bicat{Cat}$.
-
-A \define{monoidal} bicategory $\A$ comes with a pseudofunctor $\otimes\maps\A\times\A\to\A$ and a unit object $I$ that are associative and unital up to coherent equivalence.
+We denote by $[\bicat{A},\bicat{B}]_\pse$ the 2-category 
+of pseudofunctors, pseudonatural transformations and modifications.
+
+A \define{monoidal} bicategory $\bicat{A}$ comes with a pseudofunctor $\otimes\maps\bicat{A}\times\bicat{A}\to\bicat{A}$ and a unit object $I$ that are associative and unital up to coherent equivalence.
 A \define{braided} monoidal bicategory comes with a pseudonatural equivalence $\beta_{a,b}\maps a\ot b\to b\ot a$ and appropriate invertible modifications; it is \define{sylleptic} if there is an appropriate invertible modification $1_{a\ot b}\Rrightarrow\beta_{b,a}\circ\beta_{a,b}$ and it is \define{symmetric} if one further axiom holds.
@@
 This is commonly also called `weak monoidal' pseudofunctor.
-A \define{braided lax monoidal} pseudofunctor between symmetric monoidal bicategories comes with an invertible modification with components $F(\beta_{a,b})\circ \mu_{a,b}\cong\mu_{b,a}\circ \beta_{Fa,Fb}$.
+A \define{braided lax monoidal} pseudofunctor between braided monoidal bicategories comes with an appropriate invertible modification with components $F(\beta_{a,b})\circ \mu_{a,b}\cong\mu_{b,a}\circ \beta_{Fa,Fb}$; a \define{sylleptic lax monoidal} pseudofunctor satisfies one extra condition and a \define{symmetric lax monoidal} pseudofunctor between symmetric monoidal bicategories is just a sylleptic one.
+RIGHT???
 

### 2020-11-16 cospans.tex
Completed section 4 except for a question at the end.

--- 2020-11-16 cospans.tex
@@
 \begin{thm} \label{thm:equiv}
-Suppose $\ca{A}$ has finite colimits and $(F,\phi,\phi_0)\maps(\ca{A},+) \to (\bicat{Cat},\times,1)$ is a symmetric lax monoidal pseudofunctor that factors through $\bicat{Rex}$ as an ordinary pseudofunctor.
-Then the symmetric monoidal double category $F\lCsp$ of decorated cospans is equivalent to the symmetric monoidal double category $_L\lCsp(\inta F)$ of structured cospans, where $L \maps \A \to \inta F$ is the left adjoint of the induced Grothendieck opfibration $\U\maps \inta F \to \A$.
+Suppose $\ca{A}$ has finite colimits and $(F,\phi,\phi_0)\maps(\ca{A},+) \to (\bicat{Cat},\times)$ is a symmetric lax monoidal pseudofunctor that factors through $\bicat{Rex}$ as an ordinary pseudofunctor.
+Then the symmetric monoidal double category $F\lCsp$ of decorated cospans is equivalent to the symmetric monoidal double category $_L\lCsp(\inta F)$ of structured cospans, where $L \maps \A \to \inta F$ is the left adjoint of the induced Grothendieck opfibration $U \maps \inta F \to \A$.
 \end{thm}
@@
 
-As noted for example by Shulman \cite{Shulman2010}, any double category $\lX$ gives rise to a bicategory $\bX$ in which:
+As noted for example by Shulman \cite{Shulman2010}, any double category $\lX$ has a 
+\define{horizontal bicategory}, denoted $\bX$, in which:
 \begin{itemize}
@@
 \end{itemize}
-Furthermore, any bicategory $\bX$ whatsoever gives rise to a category $\X$ in which:
+The bicategory $\bX$ then has a \define{decategorification}, a category $\X$ in which:
 \begin{itemize}
@@
 Thus, the double category $F\lCsp$ of structured cospans constructed in \cref{thm:decorated_cospans} automatically gives rise to a bicategory, which we call $F\bCsp$, and a category, which we call $F\Csp$.
-
-In \cref{DC} we gave conditions under which the double category $F\lCsp$ becomes symmetric
-monoidal.   We would like the bicategory $F\bCsp$ and the category $F\Csp$ to become symmetric
-monoidal under the same conditions, and indeed this is true.
-Shulman \cite[Thm.\ 1.2]{Shulman2010} showed that when $\lX$ is `fibrant', any symmetrical monoidal structure on $\lX$ gives one on $\bX$.
+In \cref{DC} we gave conditions under which the double category $F\lCsp$ becomes symmetric monoidal.
+We would like the bicategory $F\bCsp$ and the category $F\Csp$ to become symmetric monoidal under the same conditions, and indeed this is true.
+
+A double category is `fibrant' if every vertical 1-morphism has a `companion' and a `conjoint'---concepts explained in \cref{def:companion}.
+Shulman \cite[Thm.\ 1.2]{Shulman2010} showed how when a double category $\lX$ is fibrant, any symmetrical monoidal structure on $\lX$ gives one on $\bX$.
 We can apply this to decorated cospans as follows:
@@
 \begin{proof}
-Recall from \cref{defn:fibrant} that a double category is fibrant if every vertical 1-morphism has a `companion' and a `conjoint'.
-Let $f \maps c \to c'$ be a vertical 1-morphism in $F\lCsp$.
-We can lift $f$ to a companion horizontal 1-cell $\hat{f}$:
+We show that any vertical 1-morphism $f \maps c \to c'$ in $F\lCsp$ has a companion and a conjoint.  This horizontal 1-cell $\hat{f}$:
 \[
@@
 \]
-and then obtain the following two 2-morphisms:
+is a companion of $f$ because the following two 2-morphisms, having $\hat{f}$ as
+source and target:
 \[
@@
 \node (F) at (3,-0.5) {$!_{c'} \in F(c')$};
-\node (G) at (4,0.5) {$c$};
-\node (H) at (5,0.5) {$c$};
-\node (I) at (6,0.5) {$c$};
-\node (G') at (4,-0.5) {$c$};
-\node (H') at (5,-0.5) {$c'$};
-\node (I') at (6,-0.5) {$c'$};
-\node (J) at (7,0.5) {$!_{c} \in F(c)$};
-\node (K) at (7,-0.5) {$!_{c'} \in F(c')$};
+\node (G) at (5,0.5) {$c$};
+\node (H) at (6,0.5) {$c$};
+\node (I) at (7,0.5) {$c$};
+\node (G') at (5,-0.5) {$c$};
+\node (H') at (6,-0.5) {$c'$};
+\node (I') at (7,-0.5) {$c'$};
+\node (J) at (8,0.5) {$!_{c} \in F(c)$};
+\node (K) at (8,-0.5) {$!_{c'} \in F(c')$};
 \node (L) at (1,-1) {$\tau_{1_{c'}} = 1_{!_{c'}}$};
-\node (M) at (5,-1) {$\tau_f \maps F(f)(!_c) \to !_{c'}$};
+\node (M) at (6,-1) {$\tau_f \maps F(f)(!_c) \to !_{c'}$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-which satisfy the equations:
+satisfy the equations required of a companion:
 \[
@@
 \]
-The right hand sides of the above two equations are given respectively by the 2-morphisms $U_f$ and $1_{\hat{f}}$.
-The conjoint of $f$ is given by the $F$-decorated cospan $\check{f}$ which is just the opposite of the companion above:
+and right hand sides of the above two equations are given respectively by the 2-morphisms $U_f$ and $1_{\hat{f}}$.
+The conjoint of $f$ is given by this horizontal 1-cell $\check{f}$, which is just the opposite of the companion above:
 \[
@@
 \]
-Just as $\hat{f}$ obeys the equations required of a companion, $\check{f}$ obeys the similar equations required of a conjoint.
+Just as $\hat{f}$ obeys the equations required of a companion, $\check{f}$ obeys the equations required of a conjoint.
 \end{proof}
@@
 
-This symmetric monoidal bicategory $F\Csp$ is a superior version of the symmetric monoidal bicategory $F$Cospan$(\A)$ constructed earlier by the second author \cite{Courser}, in that there is greater flexibility in the allowed 2-morphisms.
-
-%The previous bicategory constructed by the second author suffered even more so from the issue discussed in the introduction.
-Given a symmetric lax monoidal functor $F \maps \mathrm{A} \to \mathrm{Set}$, a result of Fong \cite{Fong} yields a symmetric monoidal category $F \textnormal{Cospan}(\mathrm{A})$ which has:
-%\begin{enumerate}
-%\item{objects as those of $\mathrm{A}$ and}
-%\item{morphisms as isomorphism classes of decorated cospans in $\mathrm{A}$.}
-%\end{enumerate}
-%The second author then using a result of Shulman \cite{Shul} extended this to a bicategory also called $F \textnormal{Cospan}(\mathrm{A})$ which has:
-%\begin{enumerate}
-%\item{objects as those of $\mathrm{A}$,}
-%\item{morphisms as now just decorated cospans in $\mathrm{A}$, and}
-%\item{2-morphisms as pairs of commuting diagrams:
-%\[
-%\begin{tikzpicture}[scale=1.5]
-%\node (A) at (0,0) {$a$};
-%\node (B) at (1,0.5) {$c$};
-%\node (B') at (1,-0.5) {$c'$};
-%\node (C) at (2,0) {$b$};
-%\node (D) at (3,0) {$1$};
-%\node (E) at (4,0.5) {$F(c)$};
-%\node (E') at (4,-0.5) {$F(c')$};
-%\path[->,font=\scriptsize,>=angle 90]
-%(A) edge node[above]{$i$} (B)
-%(C) edge node[above]{$o$} (B)
-%(A) edge node[below]{$i'$} (B')
-%(C) edge node[below]{$o'$} (B')
-%(B) edge node [left] {$f$} (B')
-%(D) edge node [above] {$d$} (E)
-%(D) edge node [below] {$d'$} (E')
-%(E) edge node [right] {$F(f)$} (E');
-%\end{tikzpicture}
-%\]
-%}
-%\end{enumerate}
-%This was discussed in the introduction and it was mentioned how in the symmetric monoidal category version of $F \textnormal{Cospan}(\mathrm{A})$, that the two single-edged graphs:
-%\[
-%\begin{tikzpicture}[scale=1.5]
-%\node (A) at (0,0) {$v_1$};
-%\node (B) at (1,0) {$v_2$};
-%\path[->,font=\scriptsize,>=angle 90]
-%(A) edge node[above]{$e$} (B);
-%\end{tikzpicture}
-%\]
-%and
-%\[
-%\begin{tikzpicture}[scale=1.5]
-%\node (A) at (0,0) {$v_1$};
-%\node (B) at (1,0) {$v_2.$};
-%\path[->,font=\scriptsize,>=angle 90]
-%(A) edge node[above]{$e'$} (B);
-%\end{tikzpicture}
-%\]
-%resided in distinct isomorphism classes.
-In the bicategorical version of $F \textnormal{Cospan}(\mathrm{A})$ where we are no longer considering decorated cospans up to isomorphism class, there is no 2-morphism between these two graphs due to the strict commutativity of the triangle to the right above.
-This problem does not occur in the symmetric monoidal bicategory $H(\mathbb{F}\textnormal{Cospan}(\mathrm{A}))$ and there is in fact a 2-(iso)morphism between these two graphs given by the map $\tau \maps F(f)(d) \to d'$ which maps the edge $e$ to the edge $e'$, where $f$ is the underlying map of vertices.
-
-%Again, let $F \maps \mathbf{FinSet} \to \mathbf{Set}$ be the symmetric lax monoidal functor that maps a finite set $N$ to the large set of all possible graph structures whose underlying set of vertices is $N$.
-Then a result of Fong \cite{Fong} yields a symmetric monoidal category $F\textnormal{Cospan}(\mathbf{FinSet})$ which has:
-%\begin{enumerate}
-%\item{finite sets as objects and}
-%\item{isomorphism classes of `open' graphs as morphisms, where an open graph is a cospan of finite sets whose apex is equipped with the structure of a graph.}
-%\end{enumerate}
-
-%An example of an open graph is:
-%\begin{center}
-%\begin{tikzpicture}[scale=2.15]
-%\node (N) at (0.5,-1.25) {$N=\{v_1,v_2,v_3\}$};
-%    \node[circle,draw,inner sep=1pt,fill=gray,color=gray]         (x) at (-1.4,-.43) {};
-%    \node at (-1.4,-.9) {$X$};
-%    \node       (A) at (0,0) {$v_1$};
-%    \node     (B) at (1,0) {$v_2$};
-%    \node        (C) at (0.5,-.86) {$v_3$};
-%    \node[circle,draw,inner sep=1pt,fill=gray,color=gray]         (y1) at (2.4,-.25) {};
-%    \node[circle,draw,inner sep=1pt,fill=gray,color=gray]         (y2) at (2.4,-.61) {};
-%    \node at (2.4,-.9) {$Y$};
-%    \path (B) edge  [bend right,->-] node[above] {$e_1$} (A);
-%    \path (A) edge  [bend right,->-] node[below] {$e_2$} (B);
-%    \path (A) edge  [->-] node[left] {$e_3$} (C);
-%    \path (C) edge  [->-] node[right] {$e_4$} (B);
-%    \path[color=gray, very thick, shorten >=10pt, shorten <=5pt, ->, >=stealth] (x) edge (A);
-%    \path[color=gray, very thick, shorten >=10pt, shorten <=5pt, ->, >=stealth] (y1) edge (B);
-%    \path[color=gray, very thick, shorten >=10pt, shorten <=5pt, ->, >=stealth] (y2) edge (B);
-%\end{tikzpicture}
-%\end{center}
-%Here, the sets $X$ and $Y$ serve as inputs and outputs. The second author then extended Fong's category using a result of Shulman \cite{Shul} to obtain a symmetric monoidal bicategory which has:
-
-%the following two single-edged graphs constituted distinct isomorphism classes:
-%\[
-%\begin{tikzpicture}[scale=1.5]
-%\node (A) at (0,0) {$v_1$};
-%\node (B) at (2,0) {$v_2$};
-%\node (C) at (0,-2) {$v_1$};
-%\node (D) at (2,-2) {$v_2$};
-%\path[->,font=\scriptsize,>=angle 90]
-%(A) edge node[above]{$e$} (B)
-%(C) edge node[above]{$e'$} (D);
-%\end{tikzpicture}
-%\]
-
-We can then decategorify this symmetric monoidal bicategory to obtain a symmetric monoidal category generalizing the kind considered by Fong \cite{Fong}:
+This symmetric monoidal bicategory $F\bCsp$ is a superior version of the one constructed earlier by the second author \cite{Courser}, in that there is greater flexibility in the allowed 2-morphisms.
+We can decategorify $F\bCsp$ to obtain a symmetric monoidal category generalizing the kind considered by Fong \cite{Fong}:
 
@@
 
-In \cref{thm:equiv} we gave conditions under which the double category of \emph{decorated} cospans $F\lCsp$ is equivalent to the double category of \emph{structured} cospans ${}_L \lCsp(\int F)$.
-We now show that under the same conditions we get an equivalence of bicategories and of
-categories.
-
-We have just seen in \cref{thm:bicat} that the decorated cospan
-double category $F\lCsp$ gives rise to a bicategory $F\Csp$.   A similar result 
-is known for structured cospan double categories \cite[Cor.\ 3.10]{BC}.  Namely, if $\A$ and $\X$ are categories with (chosen???) finite colimits and $L \maps \A \to \X$ preserves colimits, the 
-the structured cospan double category ${}_L \lCsp(\X)$ is symmetric monoidal and cofibrant, so the resulting bicategory ${}_L \bCsp(\X)$ becomes symmetric monoidal as well.
-
-Another result of Shulman \cite{Shulman2010} is the following:
-\begin{lem}[Shulman, Prop.\ B.3]
-An equivalence of fibrant double categories induces a biequivalence of horizontal bicategories.
-\end{lem}
-
-\begin{cor}
-The bicategories $F\mathbf{Csp}$ and $H( {_L \lCsp(\X)})$ are biequivalent.
-\end{cor}
+In \cref{thm:equiv} we gave conditions under which the symmetric monoidal double category of \emph{decorated} cospans $F\lCsp$ is equivalent to the  symmetric monoidal double category of \emph{structured} cospans ${}_L \lCsp(\int F)$.
+We now show that under the same conditions we get an equivalence of symmetric monoidal bicategories, and of categories.
+
+\begin{thm} \label{thm:bicat_equiv}
+Suppose $\ca{A}$ has finite colimits and $F \maps(\ca{A},+) \to (\bicat{Cat},\times)$ is a symmetric lax monoidal pseudofunctor that factors through $\bicat{Rex}$ as an ordinary pseudofunctor.
+Define the symmetric monoidal bicategory $_L\bCsp(\inta F)$ as in \cref{thm:equiv}.
+Then there is an equivalence of symmetric monoidal bicategories
+\[      F\bCsp \simeq {}_L \bCsp(\inta F)   \]
+of symmetric monoidal categories
+\[      F\Csp \simeq {}_L \Csp(\inta F)  . \]
+\end{thm}
+
+\begin{proof} Hansen and Shulman \cite{HS} showed that the passage from symmetric monoidal double categories to symmetric monoidal bicategories is  functorial in a suitable sense, implying
+that an equivalence of symmetric monoidal double categories $\lX \simeq \lY$ gives an equivalence of symmetric monoidal bicategories $\bX \simeq \bY$.
+Since the process of decategorifying a bicategory merely discards 2-morphisms and takes isomorphism classes of 1-morphisms, the equivalence of symmetric monoidal bicategories $\bX \simeq \bY$ in turn induces an equivalence of symmetric monoidal categories $\X \simeq \Y$.
+Thus, the theorem follows from \cref{thm:equiv}.
+\end{proof}
+
+CHECK THAT OUR SORT OF EQUIVALENCE OF SYMMETRIC MONOIDAL DOUBLE CATEGORIES IS REALLY THAT USED BY HANSEN AND SHULMAN!!!
 

### 2020-11-16 cospans.tex

@@
 \begin{thm} \label{thm:equiv}
-Suppose $\ca{A}$ has finite colimits and $(F,\phi,\phi_0)\maps(\ca{A},+) \to (\bicat{Cat},\times)$ is a symmetric lax monoidal pseudofunctor that factors through $\bicat{Rex}$ as an ordinary pseudofunctor.
+Suppose $\ca{A}$ has finite colimits and $F \maps(\ca{A},+) \to (\bicat{Cat},\times)$ is a symmetric lax monoidal pseudofunctor that factors through $\bicat{Rex}$ as an ordinary pseudofunctor.
 Then the symmetric monoidal double category $F\lCsp$ of decorated cospans is equivalent to the symmetric monoidal double category $_L\lCsp(\inta F)$ of structured cospans, where $L \maps \A \to \inta F$ is the left adjoint of the induced Grothendieck opfibration $U \maps \inta F \to \A$.
@@
 
-The conditions of the above theorem relate to the existence of left adjoints for opfibrations; we first sketch this underlying framework, and then we proceed to the proof of the theorem.
+The conditions of the above theorem relate to the existence of colimits as well as left adjoints for opfibrations.
+We first sketch this underlying framework, and then we proceed to the proof of the theorem.
 The basics of fibration theory needed for our purposes are recalled in \cref{sec:fibrations}.

### 2020-11-16 cospans.tex
Cleaning up Theorem 2.2

@@
 where $0$ is the monoidal unit of $\A$ and $!_0 \maps 1 \to F(0)$ is the morphism which is part of the structure of the symmetric lax monoidal pseudofunctor $F \maps \A \to \Cat$.
-It is also clear that $U(0)=0_{F\lCsp_1}$.
+It is also clear that $U(0)=0_{F\lCsp_1}$, where $0_{F\lCsp_1}$ is the monoidal unit of $F\lCsp_1$.
 
@@
 where $x_1+(x_2+x_3) \maps 1 \to F(m_1+(m_2+m_3))$ is given by: $$1 \xrightarrow{x_1 \times (x_2 \times x_3)} F(m_1) \times (F(m_2) \times F(m_3)) \xrightarrow{1 \times \phi_{m_2,m_3}} F(m_1) \times F(m_2+m_3) \xrightarrow{\phi_{m_1,m_2+m_3}} F(m_1+(m_2+m_3)).$$
-\noindent
-\textbf{In progress}
-
-\noindent
-If we let $a$ denote the associator of $(\A,+,0)$, the associator of $F\lCsp_1$ is then a map of cospans in $\A$ from $(M_1 \otimes M_2) \otimes M_3$ to $M_1 \otimes (M_2 \otimes M_3)$ given by:
+Denoting the associator of $(\A,+,0)$ by $\alpha$, the associator of $F\lCsp_1$ is then a map of cospans in $\A$ from $(M_1 \otimes M_2) \otimes M_3$ to $M_1 \otimes (M_2 \otimes M_3)$ given by:
 \[
@@
 (C) edge node[above]{$(o_1+o_2)+o_3$} (B)
-(A) edge node[left]{$a$} (A')
-(C) edge node[right]{$a$} (C')
+(A) edge node[left]{$\alpha$} (A')
+(C) edge node[right]{$\alpha$} (C')
 (A') edge node [above]{$i_1+(i_2+i_3)$} (D)
 (C') edge node [above]{$o_1+(o_2+o_3)$} (D)
-(B) edge node [left] {$a$} (D);
-\end{tikzpicture}
-\]
-together with the isomorphism $\tau_a \maps F(a)((x_1+x_2)+x_3) \to x_1+(x_2+x_3)$.
-
-Tensoring an object with the monoidal unit, say, on the left:
+(B) edge node [left] {$\alpha$} (D);
+\end{tikzpicture}
+\]
+together with the decoration isomorphism $\tau_\alpha \maps F(\alpha)((x_1+x_2)+x_3) \to x_1+(x_2+x_3)$.
+
+For the left unitor, we first compute $0_{F\lCsp_1} \otimes M$:
 \[
@@
 \]
-results in:
+which results in:
 \[
@@
 \]
-where $!_0 + x \in F(0+m)$ is given by $$1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{!_0 \times x} F(0) \times F(m) \xrightarrow{\phi_{0,m}} F(0+m).$$The left unitor is then an isomorphism in $F\lCsp_1$ given by:
+where $!_0 + x \in F(0+m)$ is given by $$1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{!_0 \times x} F(0) \times F(m) \xrightarrow{\phi_{0,m}} F(0+m).$$Denoting the left unitor of $(\A,+,0)$ by $\ell$, the left unitor of $F\lCsp_1$ is then an isomorphism in $F\lCsp_1$ given by the following map of cospans in $\A$:
 \[
@@
 \]
-where $\ell$ is the left unitor of $(\A,+,0)$, together with the isomorphism $\tau_{\lambda} \maps F(\ell)(!_0 + x) \to x$. The right unitor is similar.
-
- These associators and left and right unitors together satisfy the pentagon and triangle identities of a monoidal category. 
+together with the decoration isomorphism $\tau_{\ell} \maps F(\ell)(!_0 + x) \to x$.
+The right unitor is similar, and one can check that the associator and left and right unitors together satisfy the pentagon and triangle identities of a monoidal category.
+See the second author's thesis \cite{CourserThesis} for more details.
+
+To finish showing that $F\lCsp_1$ is symmetric monoidal, we next define the braiding of $F\lCsp_1$.
+Given two objects $M_1$ and $M_2$ of $F\lCsp_1$ and denoting the braiding of $(\A,+,0)$ by $\beta$, the braiding $\beta_{M_1,M_2}$ of $F\lCsp_1$ is then a map of cospans in $\A$ from $M_1 \otimes M_2$ to $M_2 \otimes M_1$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0.5) {$a_1+a_2$};
+\node (A') at (0,-0.5) {$a_2+a_1$};
+\node (B) at (2,0.5) {$m_1+m_2$};
+\node (C) at (4,0.5) {$b_1+b_2$};
+\node (C') at (4,-0.5) {$b_2+b_1$};
+\node (D) at (2,-0.5) {$m_2+m_1$};
+\node (E) at (5.5,0.5) {$x_1+x_2 \in F(m_1+m_2)$};
+\node (F) at (5.5,-0.5) {$x_2+x_1 \in F(m_2+m_1)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i_1+i_2$} (B)
+(C) edge node[above]{$o_1+o_2$} (B)
+(A) edge node[left]{$\beta$} (A')
+(C) edge node[left]{$\beta$} (C')
+(A') edge node [above]{$i_2+i_1$} (D)
+(C') edge node [above]{$o_2+o_1$} (D)
+(B) edge node [left] {$\beta$} (D);
+\end{tikzpicture}
+\]
+together with the decoration isomorphism $\tau_\beta \colon F(\beta)(x_1+x_2) \to x_2+x_1$.
+One can check that the braiding together with the associator satisfy the hexagon equations, and it is clear that $\beta_{M_1,M_2}=\beta_{M_2,M_1}^{-1}$.
+This completes the description of $F\lCsp_1$ as a symmetric monoidal category.
+
+Lastly, we require two globular 2-morphisms $\chi \colon (M_1 \otimes M_1) \odot (M_2 \otimes N_2) \to (M_1 \odot M_2) \otimes (N_1 \odot N_2)$ and $\mu \colon U_{a \otimes b} \to U_a \otimes U_b$, the first of which relates the double functors $\otimes$ and $\odot$ and the second of which relates the double functors $\otimes$ and $U$.
+The latter of these is easy to see: given two objects $a$ and $b$ in $F\lCsp_0=\A$, $\mu$ is given by the identity map of cospans in $\A$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0.5) {$a+b$};
+\node (A') at (0,-0.5) {$a+b$};
+\node (B) at (2,0.5) {$a+b$};
+\node (C) at (4,0.5) {$a+b$};
+\node (C') at (4,-0.5) {$a+b$};
+\node (D) at (2,-0.5) {$a+b$};
+\node (E) at (5.5,0.5) {$!_{a+b} \in F(a+b)$};
+\node (F) at (5.5,-0.5) {$!_a + !_b \in F(a+b)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$1_{a+b}$} (B)
+(C) edge node[above]{$1_{a+b}$} (B)
+(A) edge node[left]{$1$} (A')
+(C) edge node[right]{$1$} (C')
+(A') edge node [above]{$1_a + 1_b$} (D)
+(C') edge node [above]{$1_a + 1_b$} (D)
+(B) edge node [left] {$1$} (D);
+\end{tikzpicture}
+\]
+together with the decoration isomorphism $\tau_{a,b} \maps !_{a+b} \xrightarrow{\sim} !_a + !_b$ given by the unique map between the two initial objects $!_{a+b}$ and $!_a + !_b$ in $F(a+b)$.
+For the former globular 2-morphism $\chi$, we first introduce some notation for objects $M_1,M_2,N_1$ and $N_2$ of $F\lCsp_1$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$a$};
+\node (B) at (1,0) {$m_1$};
+\node (C) at (2,0) {$b$};
+\node (D) at (1,-0.5) {$x_1 \in F(m_1)$};
+\node (E) at (3,0) {$b$};
+\node (F) at (4,0) {$m_2$};
+\node (G) at (5,0) {$c$};
+\node (H) at (4,-0.5) {$x_2 \in F(m_2)$};
+\node (I) at (0,-1.5) {$a'$};
+\node (J) at (1,-1.5) {$n_1$};
+\node (K) at (2,-1.5) {$b'$};
+\node (L) at (1,-2) {$y_1 \in F(n_1)$};
+\node (M) at (3,-1.5) {$b'$};
+\node (N) at (4,-1.5) {$n_2$};
+\node (O) at (5,-1.5) {$c'$};
+\node (P) at (4,-2) {$y_2 \in F(n_2)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i_1$} (B)
+(C) edge node[above]{$o_1$} (B)
+(E) edge node[above]{$i_2$} (F)
+(G) edge node[above]{$o_2$} (F)
+(I) edge node[above]{$i_1'$} (J)
+(K) edge node[above]{$o_1'$} (J)
+(M) edge node[above]{$i_2'$} (N)
+(O) edge node[above]{$o_2'$} (N);
+\end{tikzpicture}
+\]
+\textbf{In progress}
 %!!! Kenny: Probably cut stuff out below this.

### 2020-11-16 cospans.tex
Started a section on applications

--- 2020-11-16 cospans.tex
@@
 Such categories were used to describe a variety of open systems: electrical circuits, Markov processes, chemical reaction networks and dynamical systems \cite{BF,BFP,BP}.
-Later the second author improved Fong's categories to symmetric monoidal double categories, eliminating the need to work with equivalence classes \cite{Courser}.
 
@@
 An example would be equipping a finite set $m$ with edges making its elements into the nodes of a graph.
-We would like the following `open graph' to be a decorated cospan with $m = \{n_1, n_2, n_3, n_4\}$:
+We would like the following `open graph' to be a decorated cospan where the apex is the finite set $m = \{n_1, n_2, n_3, n_4\}$:
 \[
@@
 \]
-This commutative triangle in $\mathsf{Set}$ in the context of the symmetric lax monoidal functor $F \maps \mathsf{FinSet} \to \mathsf{Set}$ says the following: given a decoration $d \in F(b)$, which is a graph structure with underlying set of vertices $b$, the function $F(f)$ pushes forward the graph structure $d$ to the graph structure $d' \in F(b')$ with underlying set of vertices $b'$, and \emph{precisely} this graph structure.
+This commutative triangle in $\Set$ in the context of the symmetric lax monoidal functor $F \maps \mathsf{FinSet} \to \Set$ says the following: given a decoration $d \in F(b)$, which is a graph structure with underlying set of vertices $b$, the function $F(f)$ pushes forward the graph structure $d$ to the graph structure $d' \in F(b')$ with underlying set of vertices $b'$, and \emph{precisely} this graph structure.
 The graph structure is given by set of edges of $d$.
@@
 In a previous work, the second author extended Fong's theory of decorated cospans to a symmetric monoidal bicategory of decorated cospans \cite{Courser}.
-Namely, under the same hypotheses used by Fong amounting to a category $\A$ with finite colimits and a symmetric lax monoidal functor $F \maps (\A,+,0) \to (\mathsf{Set}, \times, 1)$, there exists a symmetric monoidal bicategory $F\mathbf{Cospan}(\A)$ which has:
+Namely, under the same hypotheses used by Fong amounting to a category $\A$ with finite colimits and a symmetric lax monoidal functor $F \maps (\A,+,0) \to (\Set, \times, 1)$, there exists a symmetric monoidal bicategory $F\mathbf{Cospan}(\A)$ which has:
 \begin{enumerate}
@@
 and
-\item 2-morphisms as pairs of commuting diagrams where the left diagram is a map of cospans in $\A$ and the right diagram is a commutative triangle in $\mathsf{Set}$.
+\item 2-morphisms as pairs of commuting diagrams where the left diagram is a map of cospans in $\A$ and the right diagram is a commutative triangle in $\Set$.
 \[
@@
 \end{enumerate}
-Returning to the previous example where we take the functor $F$ to be the functor $F \maps \mathsf{FinSet} \to \mathsf{Set}$, the situation becomes more dire.
+Returning to the previous example where we take the functor $F$ to be the functor $F \maps \mathsf{FinSet} \to \Set$, the situation becomes more dire.
 Previously, in the ordinary symmetric monoidal category $F$Cospan$(\mathsf{FinSet})$ the following two $F$-decorated cospans resided in distinct isomorphism classes:
@@
 \]
-In the symmetric monoidal bicategory $F\mathbf{Cospan}(\mathsf{FinSet})$, the above two $F$-decorated cospans are two morphisms - with \emph{no 2-morphism between them!} The culprit for this is the same as before - the requirement that the triangle of decorations in $\mathsf{Set}$ commute `on the nose'.
+In the symmetric monoidal bicategory $F\mathbf{Cospan}(\mathsf{FinSet})$, the above two $F$-decorated cospans are two morphisms - with \emph{no 2-morphism between them!} The culprit for this is the same as before - the requirement that the triangle of decorations in $\Set$ commute `on the nose'.
 In this paper we construct a similar symmetric monoidal bicategory $F$Csp which will remedy this situation, and whose decategorification will remedy the analogous problem for decorated cospan categories above.
@@
 The following theorem establishes the desired equivalence between these two different double categorical network frameworks of structured and decorated cospans in a formal way.
-We denote by $\bicat{Rex}$ the 2-category of finitely cocomplete categories and finitely cocontinuous functors, and the symmetric monoidal double structure of decorated cospans is worked out in \cref{thm:decorated_cospans,DC}.
+We denote by $\Rex$ the 2-category of finitely cocomplete categories and finitely cocontinuous functors, and the symmetric monoidal double structure of decorated cospans is worked out in \cref{thm:decorated_cospans,DC}.
 
 \begin{thm} \label{thm:equiv}
-Suppose $\ca{A}$ has finite colimits and $F \maps(\ca{A},+) \to (\bicat{Cat},\times)$ is a symmetric lax monoidal pseudofunctor that factors through $\bicat{Rex}$ as an ordinary pseudofunctor.
+Suppose $\A$ has finite colimits and $F \maps(\A,+) \to (\Cat,\times)$ is a symmetric lax monoidal pseudofunctor that factors through $\Rex$ as an ordinary pseudofunctor.
 Then the symmetric monoidal double category $F\lCsp$ of decorated cospans is equivalent to the symmetric monoidal double category $_L\lCsp(\inta F)$ of structured cospans, where $L \maps \A \to \inta F$ is the left adjoint of the induced Grothendieck opfibration $U \maps \inta F \to \A$.
@@
 
-In \cite{MV}, the classical Grothendieck construction is generalized to the monoidal setting: lax monoidal structures on a pseudofunctor $F\maps\A\to\bicat{Cat}$ (called \emph{monoidal opindexed categories}) bijectively correspond to monoidal structures on the total category $\inta F$ such that the induced opfibration is a strict monoidal functor and $\otimes_{\inta F}$ preserves cocartesian liftings (called \emph{monoidal fibrations}).
+In \cite{MV}, the classical Grothendieck construction is generalized to the monoidal setting: lax monoidal structures on a pseudofunctor $F\maps\A\to\Cat$ (called \emph{monoidal opindexed categories}) bijectively correspond to monoidal structures on the total category $\inta F$ such that the induced opfibration is a strict monoidal functor and $\otimes_{\inta F}$ preserves cocartesian liftings (called \emph{monoidal fibrations}).
 If the monoidal category $\A$ is in fact cocartesian, there is a further correspondence of the two structures with an ordinary pseudofunctor $F\maps\A\to\bicat{MonCat}$ into the 2-category of monoidal categories, strong monoidal functors and monoidal natural transformations.
@@
 \begin{gather}
-\textrm{lax monoidal pseudofunctors }F\maps(\A,+)\to(\bicat{Cat},\times) \notag\\
+\textrm{lax monoidal pseudofunctors }F\maps(\A,+)\to(\Cat,\times) \notag\\
 \Updownarrow \notag\\
@@
 
-The first part formulates the existence of colimits \emph{locally} in each fibre, which for $\ca{J}$ a finite category can equivalently be expressed by the corresponding pseudofunctor $F\maps\A\to\bicat{Cat}$ landing on the sub-2-category $\bicat{Rex}$ of finitely cocomplete categories and functors that preserve colimits.
+The first part formulates the existence of colimits \emph{locally} in each fibre, which for $\ca{J}$ a finite category can equivalently be expressed by the corresponding pseudofunctor $F\maps\A\to\Cat$ landing on the sub-2-category $\Rex$ of finitely cocomplete categories and functors that preserve colimits.
 The second part formulates the existence of colimits \emph{globally} in the total category $\inta F$.
@@
 \begin{cor}\label{cor:fcocMonGroth}
- Suppose $\A$ is a finitely cocomplete category and $F\maps(\A,+)\to(\bicat{Cat},\times)$ is a lax monoidal pseudofunctor. If its corresponding pseudofunctor $\A\to\bicat{MonCat}$ via \cref{monGroth} 
- factors through $\bicat{Rex}$, then the Grothendieck category $\inta F$ has all finite colimits and the induced opfibration $\U_F\maps\inta F\to\A$ preserves them. 
+ Suppose $\A$ is a finitely cocomplete category and $F\maps(\A,+)\to(\Cat,\times)$ is a lax monoidal pseudofunctor. If its corresponding pseudofunctor $\A\to\bicat{MonCat}$ via \cref{monGroth} 
+ factors through $\Rex$, then the Grothendieck category $\inta F$ has all finite colimits and the induced opfibration $\U_F\maps\inta F\to\A$ preserves them. 
 \end{cor}
@@
 \end{displaymath}
-Moreover, if the opfibration $U$ comes from the Grothendieck construction on a pseudofunctor $F\maps\A\to\bicat{Cat}$, the reindexing functors $(u_a)_!$ of the opfibration are precisely $F(u_a)$ therefore $\bot_a=(a,F(u_a)(0_\X))$ in the Grothendieck category notation (\cref{def:GrothCat}).
+Moreover, if the opfibration $U$ comes from the Grothendieck construction on a pseudofunctor $F\maps\A\to\Cat$, the reindexing functors $(u_a)_!$ of the opfibration are precisely $F(u_a)$ therefore $\bot_a=(a,F(u_a)(0_\X))$ in the Grothendieck category notation (\cref{def:GrothCat}).
 
@@
 
-We have now laid all the necessary background to formally construct an equivalence between the double category of decorated cospans and the double category of structured cospans, with starting point a symmetric lax monoidal pseudofunctor into $\bicat{Cat}$.
+We have now laid all the necessary background to formally construct an equivalence between the double category of decorated cospans and the double category of structured cospans, with starting point a symmetric lax monoidal pseudofunctor into $\Cat$.
 
@@
 
-By \cref{cor:fcocMonGroth}, when $F$ as an ordinary pseudofunctor factors through $\bicat{Rex}$, the Gro\-the\-ndieck construction gives rise to a finitely cocomplete $\inta F$ such that the corresponding opfibration $U\maps\inta{F}\to\A$ preserves all finite colimits.
+By \cref{cor:fcocMonGroth}, when $F$ as an ordinary pseudofunctor factors through $\Rex$, the Gro\-the\-ndieck construction gives rise to a finitely cocomplete $\inta F$ such that the corresponding opfibration $U\maps\inta{F}\to\A$ preserves all finite colimits.
 Since in particular it preserves the initial object, \cref{lem:fibrewiselimits,prop:opfibtolari} apply 
@@
 \begin{displaymath}
- F\maps\A\to\bicat{Cat}\quad\mapsto\quad\begin{tikzcd}[baseline=.3]\inta F\ar[d,"U"'] \\ \A \end{tikzcd}\quad\mapsto\quad\begin{tikzcd}\A\ar[r,bend left,pos=.55,"L"]\ar[r,phantom,"\bot"description] & \inta F\ar[l,bend left,pos=.45,"U"]\end{tikzcd}
+ F\maps\A\to\Cat\quad\mapsto\quad\begin{tikzcd}[baseline=.3]\inta F\ar[d,"U"'] \\ \A \end{tikzcd}\quad\mapsto\quad\begin{tikzcd}\A\ar[r,bend left,pos=.55,"L"]\ar[r,phantom,"\bot"description] & \inta F\ar[l,bend left,pos=.45,"U"]\end{tikzcd}
 \end{displaymath}
@@
 \end{itemize}
-The bicategory $\bX$ then has a \define{decategorification}, a category $\X$ in which:
+The bicategory $\bX$ has a \define{decategorification}, a category $\X$ in which:
 \begin{itemize}
 \item objects are objects of $\bX$,
-\item morphisms are isomorphism classes of morphisms of $\bX$.   
+\item morphisms are isomorphism classes of 1-morphisms of $\bX$.   
 \end{itemize}
-Thus, the double category $F\lCsp$ of structured cospans constructed in \cref{thm:decorated_cospans} automatically gives rise to a bicategory, which we call $F\bCsp$, and a category, which we call $F\Csp$.
+Thus, the double category $F\lCsp$ of structured cospans constructed in \cref{thm:decorated_cospans} automatically gives rise to a bicategory $F\bCsp$, and a category $F\Csp$.
 In \cref{DC} we gave conditions under which the double category $F\lCsp$ becomes symmetric monoidal.
@@
 
-This symmetric monoidal bicategory $F\bCsp$ is a superior version of the one constructed earlier by the second author \cite{Courser}, in that there is greater flexibility in the allowed 2-morphisms.
+This symmetric monoidal bicategory $F\bCsp$ generalizes the one constructed by the second author \cite{Courser}.
 We can decategorify $F\bCsp$ to obtain a symmetric monoidal category generalizing the kind considered by Fong \cite{Fong}:
@@
 \begin{thm} \label{thm:bicat_equiv}
-Suppose $\ca{A}$ has finite colimits and $F \maps(\ca{A},+) \to (\bicat{Cat},\times)$ is a symmetric lax monoidal pseudofunctor that factors through $\bicat{Rex}$ as an ordinary pseudofunctor.
+Suppose $\A$ has finite colimits and $F \maps(\A,+) \to (\Cat,\times)$ is a symmetric lax monoidal pseudofunctor that factors through $\Rex$ as an ordinary pseudofunctor.
 Define the symmetric monoidal bicategory $_L\bCsp(\inta F)$ as in \cref{thm:equiv}.
@@
 \section{Applications}\label{Applications}
-\begin{comment}
-In this section we present several examples each of which may be realized in the context of decorated cospans or in the context of structured cospans.
-The first example regarding graphs was mentioned in the introduction and used as a reoccurring theme throughout the paper.
-The next three examples which take on more of an applied flavor, consists of electrical circuits, Markov processes and Petri nets.
-Each of these has been studied extensively by Baez, Fong, Master and Pollard by way of `black-boxing' \cite{BCR,BF,BFP,BM,BP}.
-Black-boxing is a way of interpreting the behavior of an open system, that is, a system with prescribed inputs and outputs such as the terminals of an electrical circuit, by observing the activity at the inputs and the outputs.
-The semantics of the activity at an open system's inputs and outputs is typically described in a category such as $\mathsf{LinRel}$ of finite dimensonal vector spaces and linear relations.
-Thus, in each case, black-boxing results in functors such as: $$\blacksquare_1 \maps \mathsf{Circ} \to \mathsf{LinRel}$$ $$\blacksquare_2 \maps \mathsf{Mark} \to \mathsf{LinRel}$$ $$\blacksquare_3 \maps \Petri \to \mathsf{LinRel}.$$ Each of these black-boxing functors also possess other convenient properties such as being symmetric monoidal.
-The first two of these were first done using Fong's theory of decorated cospans and then extended by the first two authors using structured cospans.
-The last two of these were also extended by being realized as double functors between double categories in recent works \cite{BC,BM}.
+
+In this section we present several examples.  The first was mentioned in the Introduction.
+
 \subsection{Graphs}
-As a first example that was also mentioned in the introduction, let $L \maps \mathsf{Set} \to \mathsf{Graph}$ be the functor that assigns to a set $N$ the \emph{discrete graph} on $N$ which is the edgeless graph $L(N)$ with no edges and $N$ as its set of vertices.
-Both $\mathsf{Set}$ and $\mathsf{Graph}$ are cocartesian monoidal and the functor $L \maps \mathsf{Set} \to \mathsf{Graph}$ is left adjoint to the forgetful functor $R \maps \mathsf{Graph} \to \mathsf{Set}$ which assigns to a graph $G$ its underlying set of vertices $U(G)$.
-Using structured cospans and appealing to Theorem \cref{SC}, we get a symmetric monoidal double category $_L \lCsp(\mathsf{Graph})$ which has:
-\begin{enumerate}
-\item{sets as objects,}
-\item{functions as vertical 1-morphisms,}
-\item{cospans of graphs, or, \emph{open} graphs of the form
+
+We describe the double category of open graphs using either structured cospans or decorated cospans.
+For us a \define{graph} will be a pair of functions $s,t\maps E \to N$ where $E$ and $N$ are arbitrary sets, though we could also restrict to finite sets.
+We call elements of $E$ \define{edges} and elements of $N$ \define{nodes}.
+There is a category $\Graph$ with graphs as objects, and with morphism from the graph $s,t\maps E \to N$ to the graph $s',t' \maps E' \to N'$ is defined to be a pair of functions $f \maps E \to E', g \maps N \to N'$ such that these diagrams commute:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$E$};
+\node (A') at (0,-1) {$E'$};
+\node (B) at (1,0) {$N$};
+\node (B') at (1,-1) {$N'$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$s$} (B)
+(A') edge node[above]{$s'$} (B')
+(A) edge node[left]{$f$} (A')
+(B) edge node[right]{$g$} (B');
+
+\node (C) at (2,0) {$E$};
+\node (C') at (2,-1) {$E'$};
+\node (D) at (3,0) {$N$};
+\node (D') at (3,-1) {$N'$.};
+\path[->,font=\scriptsize,>=angle 90]
+(C) edge node[above]{$t$} (D)
+(C') edge node[above]{$t'$} (D')
+(C) edge node[left]{$f$} (C')
+(D) edge node[right]{$g$} (D');
+\end{tikzpicture}
+\]
+
+Let $L \maps \Set \to \Graph$ be the functor that assigns to a set $N$ the \define{discrete graph} on $N$: the graph with no edges and $N$ as its set of vertices.
+Both $\Set$ and $\Graph$ have finite colimits, and the functor $L \maps \Set \to \Graph$ is left adjoint to the forgetful functor $R \maps \Graph \to \Set$ that assigns to a graph $G$ its underlying set of vertices $U(G)$.
+
+Thus, using structured cospans and appealing to \cref{SC}, we get a symmetric monoidal double category $_L \lCsp(\Graph)$ in which
+\begin{itemize}
+\item objects are finite sets,
+\item a vertical 1-morphism from $M$ to $N$ is a function $f \maps M \to N$
+\item a horizontal 1-cell from $M$ to $N$ is an \define{open graph} from $M$ to $N$, meaning a cospan in $\Graph$ of this form:
 \[
@@
 \path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$I$} (B)
-(C) edge node[above]{$O$} (B);
-\end{tikzpicture}
-\]
-as horizontal 1-cells, where $L(N)$ and $L(M)$ are discrete graphs on the sets $N$ and $M$, respectively, $G$ is a graph and $I$ and $O$ are graph morphisms, and}
-\item{maps of cospans of graphs of the form
+(A) edge node[above]{$i$} (B)
+(C) edge node[above]{$o$} (B);
+\end{tikzpicture}
+\]
+\item a 2-morphism is a commuting diagram in $\Graph$ of this form:
 \[
@@
 \]
-as 2-morphisms, where $L(f)$ and $L(g)$ are maps of discrete graphs induced by the underlying functions $f$ and $g$, respectively, and $\alpha \maps G_1 \to G_2$ is a graph morphism.
-}
-\end{enumerate}
-
-We can obtain a similar symmetric monoidal double category using decorated cospans.
-Let $F \maps \mathsf{Set} \to \mathsf{Cat}$ be the symmetric lax monoidal pseudofunctor that assigns to a set $N$ the \emph{category} of all graph structures whose underlying set of vertices is $N$.
-Using Theorem \cref{DC}, we then obtain a symmetric monoidal double category $F\lCsp$ which has:
-\begin{enumerate}
-\item{sets as objects,}
-\item{functions as vertical 1-morphisms,}
-\item{horizontal 1-cells as pairs:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$N$};
+\end{itemize}
+
+We can use decorated cospans to build an equivalent symmetric monoidal double category.    For any finite set $N$ there is a category $F(N)$ where:
+\begin{itemize}
+\item An object is a \define{graph structure} on $N$: that is, a graph $s,t \maps E \to N$.
+\item A morphism from $s,t \maps E \to N$ to $s',t' \maps E' \to N$ is a morphism of graphs that is
+the identity on $N$, i.e., a function $f \maps E \to E'$ such that these diagrams commute:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$E$};
+\node (A') at (0,-1) {$E'$};
+\node (B) at (1,-0.5) {$N$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$s$} (B)
+(A') edge node[above]{$s'$} (B)
+(A) edge node[left]{$f$} (A');
+\node (C) at (2,0) {$E$};
+\node (C') at (2,-1) {$E'$};
+\node (D) at (3,-0.5) {$N$};
+\path[->,font=\scriptsize,>=angle 90]
+(C) edge node[above]{$t$} (D)
+(C') edge node[above]{$t'$} (D)
+(C) edge node[left]{$f$} (C');
+\end{tikzpicture}
+\]
+\end{itemize}
+
+There is a symmetric lax monoidal pseudofunctor $F \maps (\Set, +) \to (\Cat,\times)$  that assigns to a set $N$ the category $F(N)$.
+This behaves in the obvious way on morphisms --- what's that???
+The lax monoidal structure arises from functors $\phi_{M,N} \maps F(M) \times F(N) \to F(M+N)$ and $\phi_0 \maps F(\emptyset) \to 1$ defined in the obvious way --- what's that???
+ Using  \cref{DC}, we thus obtain a symmetric monoidal double category $F\lCsp$ in which
+\begin{itemize}
+\item objects are sets,
+\item a vertical 1-morphism from $M$ to $N$ is a function $f: M \to N$,
+\item a horizontal 1-cell from $M$ to $N$ is a pair
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$M$};
 \node (B) at (1,0) {$P$};
-\node (C) at (2,0) {$M$};
+\node (C) at (2,0) {$N$};
 \node (D) at (3.25,0) {$G \in F(P)$};
@@
 \]
-which can also be thought of as open graphs, and}
-\item{2-morphisms as maps of cospans of sets
+which can also be thought of as an open graph, 
+\item a 2-morphism
 \[
@@
 \]
-together with a graph morphism $\tau \maps F(h)(G_1) \to G_2$ in $F(P_2)$.}
-\end{enumerate}
-We thus have two symmetric monoidal double categories: $_L \lCsp(\mathsf{Graph})$ obtained from structured cospans and $F\lCsp$ obtained from decorated cospans.
-Both of these double categories have $\mathsf{Set}$ as their categories of objects, open graphs as horizontal 1-cells and maps of open graphs as 2-morphisms, and by Theorem \cref{thm:equiv}, we have an equivalence of symmetric monoidal double categories $$_L \lCsp(\mathsf{Graph}) \sim F\lCsp.$$
-
-\subsection{Passive linear circuits}
+is a commuting diagram in $\Set$ together with a morphism $\tau \maps F(h)(G_1) \to G_2$ in $F(P_2)$.
+\end{itemize}
+
+We thus have two symmetric monoidal double categories: ${}_L \lCsp(\Graph)$ obtained from structured cospans and $F\lCsp$ obtained from decorated cospans.
+Both of these double categories have $\Set$ as their categories of objects, open graphs as horizontal 1-cells and maps of open graphs as 2-morphisms, and by Theorem \cref{thm:equiv}, we have an equivalence of symmetric monoidal double categories $$_L \lCsp(\Graph) \sim F\lCsp.$$
+
+\subsection{Labeled graphs}
+
+\begin{comment}
+
 In a previous work \cite{BP}, Fong and the first author used decorated cospans to construct a symmetric monoidal category of `open passive linear circuits'.
@@
 
-Let $\mathsf{Graph}_k$ be the category whose objects are given by $k$-graphs and morphisms by morphisms of $k$-graphs, where a morphism of $k$-graphs is given by a pair of functions $f \maps E \to E'$ and $g \maps V \to V'$ between the edge sets and vertex sets, respectively, of two $k$-graphs that respect the source and target functions of each.
-In a previous work introducing structured cospans, the first two authors showed that the category $\mathsf{Graph}_k$ has finite colimits \cite{BC2}.
-We can then obtain a double category of open passive linear circuits by defining a left adjoint $L \maps \mathsf{Set} \to \mathsf{Graph}_k$ that assigns to a set $V$ the discrete passive linear circuit $L(V)$ given by passive linear circuit with $V$ as its set of vertices and no edges.
-The resulting symmetric monoidal double category $_L \lCsp(\mathsf{Graph}_k)$ has:
+Let $\Graph_k$ be the category whose objects are given by $k$-graphs and morphisms by morphisms of $k$-graphs, where a morphism of $k$-graphs is given by a pair of functions $f \maps E \to E'$ and $g \maps V \to V'$ between the edge sets and vertex sets, respectively, of two $k$-graphs that respect the source and target functions of each.
+In a previous work introducing structured cospans, the first two authors showed that the category $\Graph_k$ has finite colimits \cite{BC2}.
+We can then obtain a double category of open passive linear circuits by defining a left adjoint $L \maps \Set \to \Graph_k$ that assigns to a set $V$ the discrete passive linear circuit $L(V)$ given by passive linear circuit with $V$ as its set of vertices and no edges.
+The resulting symmetric monoidal double category $_L \lCsp(\Graph_k)$ has:
 \begin{enumerate}
@@
 Both categories $\mathsf{FinSet}$ and $\Cat$ are symmetric monoidal and the pseudofunctor $F \maps \mathsf{FinSet} \to \Cat$ is symmetric lax monoidal, as given a $k$-graph structure on a finite set $V_1$ denoted by an element $K_1 \in F(V_1)$ and a $k$-graph structure on a finite set $V_2$ denoted by an element $K_2 \in F(V_2)$, we can consider the $k$-graph structures simultaneously as a single graph structure $\phi_{V_1,V_2}(K_1,K_2)$ on the finite set $V_1+V_2$.
-Thus we get a family of natural transformations $$\phi_{V_1,V_2} \maps F(V_1) \times F(V_2) \to F(V_1+V_2)$$ as well as a morphism $\phi \maps 1_{\mathsf{Graph}_k} \to F(\emptyset)$ which together satisfy the coherence conditions of a monoidal functor.
+Thus we get a family of natural transformations $$\phi_{V_1,V_2} \maps F(V_1) \times F(V_2) \to F(V_1+V_2)$$ as well as a morphism $\phi \maps 1_{\Graph_k} \to F(\emptyset)$ which together satisfy the coherence conditions of a monoidal functor.
 The braiding is also clear as the following diagram commutes:
@@
 \end{enumerate}
-These two double categories $_L \lCsp(\mathsf{Graph}_k)$ and $F\lCsp$ are equivalent by Theorem \cref{thm:equiv}.
+These two double categories $_L \lCsp(\Graph_k)$ and $F\lCsp$ are equivalent by Theorem \cref{thm:equiv}.
 
@@
 In another previous work \cite{BFP}, Fong, Pollard and the first author used decorated cospans to construct a symmetric monoidal category of `open Markov processes'.
-In this framework, a Markov process on a finite set $N$ is given by a diagram in $\mathsf{Set}$:
+In this framework, a Markov process on a finite set $N$ is given by a diagram in $\Set$:
 \[
@@
 \end{enumerate}
-This is done using a symmetric lax monoidal functor $F \maps \mathsf{FinSet} \to \mathsf{Set}$ which assigns to each finite set $N$ the (large) set of all Markov processes on $N$ as defined above.
+This is done using a symmetric lax monoidal functor $F \maps \mathsf{FinSet} \to \Set$ which assigns to each finite set $N$ the (large) set of all Markov processes on $N$ as defined above.
 Viewing this functor $F$ as now a symmetric lax monoidal pseudofunctor $F \maps \mathsf{FinSet} \to \Cat$ that assigns to a finite set $N$ the \emph{category} $F(N)$ of all Markov processes on $N$, we then get by Theorem \cref{DC} a symmetric monoidal double category $F\lCsp$ which has:
@@
 \subsection{Petri nets}
-In a previous work, Master and the first author used structured cospans to obtain a symmetric monoidal double category of `open Petri nets'.
-A Petri net is given by a diagram in $\mathsf{Set}$ of the form:
+In a previous work, Master and the first author used structured cospans to obtain a symmetric monoidal double category of `open Petri nets'. A Petri net is given by a diagram in $\Set$ of the form:
 \[
@@
 Each set of species $S$ gives rise to a discrete Petri net $L(S)$ with $S$ as its set of species and no transitions.
-Master and the first author show the existence of a left adjoint $L \maps \mathsf{Set} \to \Petri$ where $\Petri$ is the category whose objects are Petri nets and whose `morphisms are morphisms of Petri nets'.
+Master and the first author show the existence of a left adjoint $L \maps \Set \to \Petri$ where $\Petri$ is the category whose objects are Petri nets and whose `morphisms are morphisms of Petri nets'.
 They also show that $\Petri$ has finite colimits and thus using Theorem \cref{SC} obtain a symmetric monoidal double category $\lOpen(\Petri)$ of open Petri nets which has:
@@
 \end{enumerate}
-We can also obtain a similar double category using decorated cospans: define a pseudofunctor $F \maps \mathsf{Set} \to \Cat$ where given a set $s$, $F(s)$ is the category of all Petri net structures with $s$ as its set of species.
-This pseudofunctor $F$ is symmetric lax monoidal as both $(\mathsf{Set},+,\emptyset)$ and $(\Cat,\times,1)$ are symmetric monoidal and given Petri nets $P \in F(s)$ and $P' \in F(s')$, we can place them side by side and consider them together as a single Petri net $P+P' \in F(s+s')$ with set of species $s+s'$, and thus we have natural transformations $\phi_{s,s'} \maps F(s) \times F(s') \to F(s+s')$ for any two sets $s$ and $s'$.
+We can also obtain a similar double category using decorated cospans: define a pseudofunctor $F \maps \Set \to \Cat$ where given a set $s$, $F(s)$ is the category of all Petri net structures with $s$ as its set of species.
+This pseudofunctor $F$ is symmetric lax monoidal as both $(\Set,+,\emptyset)$ and $(\Cat,\times,1)$ are symmetric monoidal and given Petri nets $P \in F(s)$ and $P' \in F(s')$, we can place them side by side and consider them together as a single Petri net $P+P' \in F(s+s')$ with set of species $s+s'$, and thus we have natural transformations $\phi_{s,s'} \maps F(s) \times F(s') \to F(s+s')$ for any two sets $s$ and $s'$.
 The other structure morphism between monoidal units $\phi \maps 1_{\Petri} \to F(\emptyset)$ is defined by the unique morphism from the empty Petri net with the empty set forits set of species to the only possible Petri net on the empty set, which is also the empty Petri net.
@@
 and}
-\item{2-morphisms as maps of cospans in $\mathsf{Set}$:
+\item{2-morphisms as maps of cospans in $\Set$:
 \[
@@
 \end{comment}
+
+\section{Conclusions}\label{sec:conclusions}
+
+We conclude with some questions:
+
+\begin{itemize}
+\item We have given conditions under which a decorated cospan double category $F \bCsp$ is
+equivalent to a structured cospan category.    Is every structured cospan double category 
+equivalent to a decorated cospan double category?
+\item What are some interesting examples of decorated cospan double categories that are not structured cospan double categories?
+A candidate appears in the work of Pollard and the first author \cite{BP}.
+They construct a decorated cospan category $\Dynam$ where objects are finite sets and a morphism from $a$ to $b$ is a cospan of finite sets $a \leftarrow m \rightarrow b$ where the apex $m$ is decorated with a vector field on $\R^m$ whose coefficients are polynomial functions of the standard coordinates on this space.
+
+They constructed this decorated cospan category via Fong's original formalism, using a lax symmetric monoidal functor $F \maps (\Fin\Set, +) \to (\Set, \times)$.
+However, composing this with the inclusion $(\Set, \times) \to (\Cat, \times)$ mapping sets to discrete categories, we get the data needed to create a decorated cospan double category $\mathbb{D}\mathbf{ynam}$.
+We believe that this is not equivalent to a structured cospan double category, but can this be proved?
+If so, can this example be generalized?
+\end{itemize}
 
@@
 \begin{defn}\label{def:GrothCat}
-For any pseudofunctor $F\maps\A\to\bicat{Cat}$ where $\A$ is a category viewed as a 2-category with trivial 2-cells, the \textbf{Grothendieck category}
+For any pseudofunctor $F\maps\A\to\Cat$ where $\A$ is a category viewed as a 2-category with trivial 2-cells, the \textbf{Grothendieck category}
 $\inta F$ has
@@
     \begin{enumerate}
-        \item Every opfibration $\U \maps \X \to \A$ gives rise to a pseudofunctor $\A \to \bicat{Cat}$.
-        \item Every pseudofunctor $F \maps \A \to \bicat{Cat}$ gives rise to  an opfibration $\maps \inta F\to\A$.
+        \item Every opfibration $\U \maps \X \to \A$ gives rise to a pseudofunctor $\A \to \Cat$.
+        \item Every pseudofunctor $F \maps \A \to \Cat$ gives rise to  an opfibration $\maps \inta F\to\A$.
         \item The above correspondences yield an equivalence of 2-categories 
         \begin{displaymath}
-            [\A,\bicat{Cat}]_\pse \simeq \OpFib(\A)
+            [\A,\Cat]_\pse \simeq \OpFib(\A)
         \end{displaymath}

### 2020-11-17 cospans.tex
began writing Sec. 5.1, on circuits.

@@
 \begin{lem}\label{lem:fibrewiselimits}
-Suppose $\ca{J}$ is a small category and $\U\maps\X\to\A$ is an opfibration. If the base $\A$ has $\ca{J}$-colimits,
+Suppose $\ca{J}$ is a small category and $U\maps\X\to\A$ is an opfibration. If the base $\A$ has $\ca{J}$-colimits,
 the following are equivalent:
@@
  \item all fibres have $\ca{J}$-colimits, and the reindexing functors preserve them;
- \item the total $\X$ has $\ca{J}$-colimits, and $\U$ (strictly) preserves them.
+ \item the total $\X$ has $\ca{J}$-colimits, and $U$ (strictly) preserves them.
 \end{enumerate}
@@
  Suppose $\A$ is a finitely cocomplete category and $F\maps(\A,+)\to(\Cat,\times)$ is a lax monoidal pseudofunctor. If its corresponding pseudofunctor $\A\to\bicat{MonCat}$ via \cref{monGroth} 
- factors through $\Rex$, then the Grothendieck category $\inta F$ has all finite colimits and the induced opfibration $\U_F\maps\inta F\to\A$ preserves them. 
+ factors through $\Rex$, then the Grothendieck category $\inta F$ has all finite colimits and the induced opfibration $U_F\maps\inta F\to\A$ preserves them. 
 \end{cor}
@@
 \begin{lem}\label{prop:opfibtolari}
-  Let $\U \maps\X \to \A$ be an opfibration. Then
-  $\U$ is a right adjoint `left inverse', a.k.a the unit is the identity, if (and only if) its fibers have
+  Let $U \maps\X \to \A$ be an opfibration. Then
+  $U$ is a right adjoint `left inverse', a.k.a the unit is the identity, if (and only if) its fibers have
   initial objects which are preserved by the
@@
 While double categories are a natural context for studying cospans, bicategories are more 
-familiar---and of course, mere \emph{categories} are even more so!   Luckily, all our results 
+familiar---and of course, \emph{categories} are even more so!   Luckily, all our results 
 phrased in the language of double categories have analogues for bicategories and categories.  
@@
 \subsection{Graphs}
-
-We describe the double category of open graphs using either structured cospans or decorated cospans.
-For us a \define{graph} will be a pair of functions $s,t\maps E \to N$ where $E$ and $N$ are arbitrary sets, though we could also restrict to finite sets.
+\label{subsec:graphs}
+
+In earlier work \cite[Sec.\ 5]{BC} we explained the flaws in Fong's original construction of a category of open graphs using decorated cospans.
+We also showed how to fix them using structured cospans.
+Our new approach to decorated cospans provides another, equivalent way to fix these flaws.
+
+For us a \define{graph} will be a pair of functions $s,t\maps E \to N$ where $E$ and $N$ are arbitrary sets.
 We call elements of $E$ \define{edges} and elements of $N$ \define{nodes}.
@@
 
-Thus, using structured cospans and appealing to \cref{SC}, we get a symmetric monoidal double category $_L \lCsp(\Graph)$ in which
+Thus, using structured cospans and appealing to \cref{SC}, we get a symmetric monoidal double category $_L \lCsp(\Graph)$ in which:
 \begin{itemize}
 \item objects are finite sets,
-\item a vertical 1-morphism from $M$ to $N$ is a function $f \maps M \to N$
+\item a vertical 1-morphism from $M$ to $N$ is a function $f \maps M \to N$,
 \item a horizontal 1-cell from $M$ to $N$ is an \define{open graph} from $M$ to $N$, meaning a cospan in $\Graph$ of this form:
@@
 \node (B) at (1,0) {$G$};
-\node (C) at (2,0) {$L(M)$};
+\node (C) at (2,0) {$L(M)$,};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \node (B') at (1,-1) {$G_2$};
-\node (C') at (2,-1) {$L(M_2)$};
+\node (C') at (2,-1) {$L(M_2)$.};
 \path[->,font=\scriptsize,>=angle 90]
@@
 
-We can use decorated cospans to build an equivalent symmetric monoidal double category.    For any finite set $N$ there is a category $F(N)$ where:
+We can build an equivalent symmetric monoidal double category using decorated cospans.    For any finite set $N$ there is a category $F(N)$ where:
 \begin{itemize}
@@
 (A) edge node[above]{$s$} (B)
-(A') edge node[above]{$s'$} (B)
+(A') edge node[below]{$s'$} (B)
 (A) edge node[left]{$f$} (A');
@@
 (C) edge node[above]{$t$} (D)
-(C') edge node[above]{$t'$} (D)
+(C') edge node[below]{$t'$} (D)
 (C) edge node[left]{$f$} (C');
@@
 We thus have two symmetric monoidal double categories: ${}_L \lCsp(\Graph)$ obtained from structured cospans and $F\lCsp$ obtained from decorated cospans.
-Both of these double categories have $\Set$ as their categories of objects, open graphs as horizontal 1-cells and maps of open graphs as 2-morphisms, and by Theorem \cref{thm:equiv}, we have an equivalence of symmetric monoidal double categories $$_L \lCsp(\Graph) \sim F\lCsp.$$
-
-\subsection{Labeled graphs}
+Both of these double categories have $\Set$ as their categories of objects, open graphs as horizontal 1-cells and maps of open graphs as 2-morphisms, and by Theorem \cref{thm:equiv}, we have an equivalence of symmetric monoidal double categories $$_L \lCsp(\Graph) \simeq F\lCsp.$$
+
+\subsection{Circuits}
+\label{subsec:circuits}
+
+Building on work with Fong \cite{BF}, Coya, Rebro and the first author used structured
+cospans to describe electrical circuits with inputs and outputs \cite{BCR}.
+The key idea is to use graphs with labeled edges.
+The edge labels can stand for resistors with any chosen resistance, capacitors with any chosen capacitance, inductors with any chosen inductance, or other circuit elements.
+To study such circuits quite generally we start by fixing any set $\La$ to serve as edge labels.
+
+\begin{defn}
+Given a set $\La$ of \define{labels}, an \define{$\La$-graph} is a graph $s,t\maps E\to N$
+ equipped with a function $\ell \maps E \to \La$.
+ A \define{morphism} from the $\La$-graph 
+ \[ \xymatrix{\La & E \ar@<2.5pt>[r]^{s} \ar@<-2.5pt>[r]_{t} \ar[l]_{\ell} & N} \]
+ to the $\La$-graph 
+\[ \xymatrix{\La & E' \ar@<2.5pt>[r]^{s'} \ar@<-2.5pt>[r]_{t'} \ar[l]_{\ell'} & N'} \]
+is a pair of functions $f \maps E \to E', g \maps N \to N'$ such that these diagrams commute:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$E$};
+\node (A') at (0,-1) {$E'$};
+\node (B) at (1,0) {$N$};
+\node (B') at (1,-1) {$N'$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$s$} (B)
+(A') edge node[above]{$s'$} (B')
+(A) edge node[left]{$f$} (A')
+(B) edge node[right]{$g$} (B');
+
+\node (C) at (2,0) {$E$};
+\node (C') at (2,-1) {$E'$};
+\node (D) at (3,0) {$N$};
+\node (D') at (3,-1) {$N'$};
+\path[->,font=\scriptsize,>=angle 90]
+(C) edge node[above]{$t$} (D)
+(C') edge node[above]{$t'$} (D')
+(C) edge node[left]{$f$} (C')
+(D) edge node[right]{$g$} (D');
+
+\node (E) at (4,-0.5) {$\La$};
+\node (G) at (5,0) {$E$};
+\node (G') at (5,-1) {$E'$.};
+%\node[rotate=-90] at (4.1,-0.5) {$\sim$};
+\path[->,font=\scriptsize,>=angle 90]
+(G) edge node[above]{$\ell$} (E)
+(G) edge node[right]{$f$} (G')
+(G') edge node[below]{$\ell'$} (E);
+\end{tikzpicture}
+\]
+\end{defn}
+
+\begin{defn}
+\label{defn:Lgraph}
+We define $\Graph_\La$ to be the category of $\La$-graphs and morphisms between them, with composition given by
+\[  (f, g) \circ (f',g') = (f \circ f' , g \circ g')  .\]
+\end{defn}
+
+When $\La = 1$, an $\La$-graph reduces to a graph and $\Graph_\La$ reduces
+to the category $\Graph$ discussed in \cref{subsec:graphs}.  We now generalize the key
+ideas of that section from graphs to $\La$-graphs.   Everything works the same way, 
+but following previous work \cite{BCR} we call an open $\La$-graph an \define{$\La$-circuit}.
+
+There is a functor $U \maps \Graph_\La \to \Fin\Set$ that takes an $\La$-graph to its underlying set of nodes. This has a left adjoint $L \maps \Fin\Set \to \Graph_\La$ sending
+any set to the $\La$-graph with that set of nodes and no edges.
+Both $\Fin\Set$ and $\Graph_\La$ have colimits, and $L$ preserves them.
+Thus \cref{SC} gives us a symmetric monoidal double category ${}_L \lCsp(\Graph_\La)$ where:
+\begin{itemize}
+\item an object is a finite set,
+\item a morphism is an isomorphism class of $\La$-circuits, where an
+\define{$\La$-circuit} is a cospan in $\Graph_\La$ of this form:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$L(S)$};
+\node (B) at (1,0) {$G$};
+\node (C) at (2,0) {$L(T)$,};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above,left]{$$} (B)
+(C)edge node[above]{$$}(B);
+\end{tikzpicture}
+\]
+and an \define{isomorphism} of $\La$-circuits is a commutative diagram in $\Graph_\La$ 
+of this form:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (E) at (3,-0.5) {$L(S)$};
+\node (F) at (5,-0.5) {$L(T)$};
+\node (G) at (4,0) {$G$};
+\node (G') at (4,-1) {$G'$};
+\path[->,font=\scriptsize,>=angle 90]
+(F) edge node[above]{$o$} (G)
+(G) edge node[left]{$h$} (G')
+(E) edge node[above]{$i$} (G)
+(E) edge node[below]{$i'$} (G')
+(F) edge node[below]{$o'$} (G');
+\end{tikzpicture}
+\]
+where $h$ is an isomorphism.
+\end{itemize} 
+This category has a nice universal property, found by Rosebrugh, Sabadini and
+Walters \cite{RSW}.  To state this, it is convenient to use the language of props.
+% Replaced strict symmetric with symmetric strict three times below
+Recall that a \define{prop} is a symmetric strict monoidal category whose objects are natural
+numbers, with tensor product of objects given by addition.
+An \define{algebra} of a prop $\T$ in a symmetric strict monoidal category $\C$ is a symmetric strict monoidal functor $A \maps \T \to \C$.
+A \define{morphism} from the algebra $A \maps \T \to \C$ to the algebra
+$A' \maps \T \to \C$ is a monoidal natural transformation $\alpha \maps A \To A'$.
+
+\begin{lem} As a symmetric monoidal category, ${}_L \Csp(\Graph_\La)$ is equivalent to a prop $\Circ_\La$.    
+\end{lem}
+
+\begin{proof}
+This is \cite[Proposition 4.3]{BCR}.
+\end{proof}
+
+\begin{prop} 
+\label{prop:LCirc_algebra}
+An algebra of $\Circ_\La$ in a symmetric strict monoidal category $\C$ is a 
+special commutative Frobenius monoid in $\C$ whose underlying object $x$ is equipped
+with an endomorphism $\ell \maps x \to x$ for each element $\ell \in \La$. 
+A morphism of algebras of $\Circ_\La$ in $\C$ is a morphism of special commutative Frobenius monoids that also preserves all these endomorphisms.
+\end{prop}
+
+\begin{proof}
+This was proved by Rosebrugh, Sabadini and Walters \cite{RSW}, and appears
+in the above form in \cite[Proposition 7.2]{BCR}.  
+\end{proof}
+
+In applications to circuits, the morphisms $\ell \maps x \to x$ describe different
+circuit elements, while the special commutative Frobenius monoid structure is used to split and join wires.
+This framework is used to study a wide variety of electrical circuits in a paper with Coya and Rebro \cite{BCR}, so the reader can turn there for details.
+To illustrate the ideas let us consider circuits of resistors, where a label in $\La = (0,\infty)$ serves to indicate the resistance of a resistor.
+In this case a typical morphism from $1$ to $3$ in
+$\Circ_\La$ looks like this:
+\[
+\scalebox{0.6}{
+\begin{tikzpicture}
+	\begin{pgfonlayer}{nodelayer}
+		\node [contact] (n1) at (-2,0) {$\bullet$};
+		\node [style = none] at (-2.1,0.3) {$$};
+		\node [contact] (n2) at (0,1) {$\bullet$};
+		\node [style = none] at (0,1.3) {$$};
+		\node [contact] (n3) at (0,-1) {$\bullet$};
+		\node [style = none] at (0,-1.3) {$$};
+		\node [contact] (n4) at (2,1) {$\bullet$};
+		\node [style = none] at (2.1,0.3) {$$};
+		\node [contact] (n5) at (2,-1) {$\bullet$};
+		\node [style = none] at (2.1,0.3) {$$};
+
+		\node [style = none] at (-1,1.1) {$2.53$};
+		\node [style = none] at (-1,-1.1) {$0.71$};
+		\node [style = none] at (1,1.3) {$9.6$};
+		\node [style = none] at (1,-1.3) {$1.02$};
+	     \node [style = none] at (-0.4,0) {$12.4$};
+	     \node [style = none] at (1.6,0) {$6.3$};
+
+		\node [style=none] (1) at (-3,0) {};
+		\node [style=none] (4) at (3,0) {};
+
+		\node [style=none] (ATL) at (-3.4,1.4) {};
+		\node [style=none] (ATR) at (-2.6,1.4) {};
+		\node [style=none] (ABR) at (-2.6,-1.4) {};
+		\node [style=none] (ABL) at (-3.4,-1.4) {};
+
+		\node [style=none] (X) at (-3,1.8) {$1$};
+		\node [style=inputdot] (inI) at (-2.8,0) {};
+
+		\node [style=none] (Z) at (3,1.8) {$3$};
+	 \node [style=inputdot] (outI') at (2.8,1) {};
+	 \node [style=inputdot] (outI'') at (2.8,0) {};
+	 \node [style=inputdot] (outI''') at (2.8,-1) {};
+
+		\node [style=none] (MTL) at (2.6,1.4) {};
+		\node [style=none] (MTR) at (3.4,1.4) {};
+		\node [style=none] (MBR) at (3.4,-1.4) {};
+		\node [style=none] (MBL) at (2.6,-1.4) {};
+
+	\end{pgfonlayer}
+	\begin{pgfonlayer}{edgelayer}
+		\draw [style=inarrow, bend left=20, looseness=1.00] (n1) to (n2);
+		\draw [style=inarrow, bend right=20, looseness=1.00] (n1) to (n3);
+		\draw [style=inarrow, bend left=0, looseness=1.00] (n2) to (n4);
+		\draw [style=inarrow, bend right=0, looseness=1.00] (n3) to (n4);
+		\draw [style=inarrow, bend right=0, looseness=1.00] (n3) to (n5);
+		\draw [style=inarrow] (n2) to (n3);
+%		\draw [style=inarrow] (W) to (Water);
+%		\draw [style=inarrow, bend left=40, looseness=1.00] (Water2) to (Something);
+%		\draw [style=inarrow, bend right=40, looseness=1.00] (Water2) to (Something);
+%		\draw [style=inarrow, bend left=40, looseness=1.00] (Something) to (A);
+%		\draw [style=inarrow, bend right=40, looseness=1.00] (Something) to (B);
+		\draw [style=simple] (ATL.center) to (ATR.center);
+		\draw [style=simple] (ATR.center) to (ABR.center);
+		\draw [style=simple] (ABR.center) to (ABL.center);
+		\draw [style=simple] (ABL.center) to (ATL.center);
+%		\draw [style=simple] (BTL.center) to (BTR.center);
+%		\draw [style=simple] (BTR.center) to (BBR.center);
+%		\draw [style=simple] (BBR.center) to (BBL.center);
+%		\draw [style=simple] (BBL.center) to (BTL.center);
+		\draw [style=simple] (MTL.center) to (MTR.center);
+		\draw [style=simple] (MTR.center) to (MBR.center);
+		\draw [style=simple] (MBR.center) to (MBL.center);
+		\draw [style=simple] (MBL.center) to (MTL.center);
+%		\draw [style=inputarrow] (outI) to (A);
+%		\draw [style=inputarrow] (outS) to (B);
+		\draw [style=inputarrow] (inI) to (n1);
+		\draw [style=inputarrow] (outI') to (n4);
+		\draw [style=inputarrow] (outI'') to (n5);
+		\draw [style=inputarrow] (outI''') to (n5);
+%		\draw [style=inputarrow] (inI') to (Water2);
+%		\draw [style=inputarrow] (inS') to (Water2);
+	\end{pgfonlayer}
+\end{tikzpicture}
+}
+\]
+The edges here represent wires, and the positive real numbers labeling them describe
+the resistance of the resistor on each wire.
+The points in the boxes represent `terminals': that is, points where we allow ourselves to attach a wire from another circuit.
+The points in the left box are called `inputs' and the points in the right box are called `outputs'.
+In electrical engineering we associate two real numbers to each terminal, called `potential' and `current'.
+Any circuit of resistors imposes a specific relation between the potentials and currents at its inputs and those at its outputs.
+All these relations, for all circuits of resistors, can be described using a single functor as follows.
+
+There is a symmetric monoidal category $\Fin\Rel_\R$ where the objects are finite-dimensional real vector spaces and a morphism from $V$ to $W$ is a \define{linear relation} from $V$ to $W$: that is, a relation $L \subseteq V \times W$ that is a linear subspace of $V \times W$.
+Composition in $\Fin\Rel_\R$ is the usual composition of relations, and the symmetric monoidal structure is provided by direct sum.
+
+There is a symmetric monoidal functor
+\[   \blacksquare \maps \Circ_\La \to \Fin\Rel_\R  \]
+% Added the line "sending any finite set $S$ to the vector space 
+% $\mathbb{R}^S \oplus \mathbb{R}^S$ and" to say what the black-box functor does on objects
+% Changed Prop. to Proposition 
+sending any finite set $S$ to the vector space $\R^S \oplus \R^S$ and
+sending any circuit of resistors to the relation it imposes between the potentials and currents at its inputs and those at its outputs \cite[Section 9]{BCR}.
+We can construct this using Proposition \ref{prop:LCirc_algebra}, by choosing a special commutative Frobenius monoid in $\Fin\Rel_\R$ whose underlying object is equipped with an endomorphism for each resistance $R \in (0,\infty)$.
+The object $\R^2 \in \Fin\Rel_\R$ is a special commutative Frobenius monoid in a standard way \cite[Section\ 8]{BCR}, so we choose this one.
+To define $\blacksquare \maps \Circ_\La \to \Fin\Rel_\R$ it then suffices to choose for each $R \in (0,\infty)$ a linear relation from $\R^2$ to itself.
+We use this:
+\[ \left\{(\phi_1,I_1,\phi_2,I_2) : \; I_1 = I_2 , \; \phi_2-\phi_1 = R I_1\right\} 
+ \subseteq \R^2 \oplus \R^2.\]
+This expresses two laws of electrical engineering.   Kirchhoff's current law says that the 
+current flowing into a wire equals the current flowing out: $I_1 = I_2$.
+Ohm's law says that the voltage across a wire with a resistor on it, $\phi_2 - \phi_1$, is equal to the current flowing through the wire times the resistance $R$ of that resistor.
 
@@
     \begin{enumerate}
-        \item Every opfibration $\U \maps \X \to \A$ gives rise to a pseudofunctor $\A \to \Cat$.
+        \item Every opfibration $U \maps \X \to \A$ gives rise to a pseudofunctor $\A \to \Cat$.
         \item Every pseudofunctor $F \maps \A \to \Cat$ gives rise to  an opfibration $\maps \inta F\to\A$.
@@
 		\setcounter{enumi}{\value{mondbl}}
-		\item $\dblcat{D}_{0}$ and $\dblcat{D}_1$ are braided monoidal categories.
+		\item $\lD_{0}$ and $\lD_1$ are braided monoidal categories.
 		\item The functors $S$ and $T$ are strict braided monoidal functors.
@@
 		\setcounter{enumi}{\value{mondbl}}
-		\item $\dblcat{D}_{0}$ and $\dblcat{D}_1$ are symmetric monoidal.
+		\item $\lD_{0}$ and $\lD_1$ are symmetric monoidal.
 	\end{enumerate}
@@
 
-%\bibitem{RSW} R.\ Rosebrugh, N.\ Sabadini and R.\ F.\ C.\ Walters, Generic commutative separable algebras and cospans of graphs, \textsl{Theory Appl.
+\bibitem{RSW} R.\ Rosebrugh, N.\ Sabadini and R.\ F.\ C.\ Walters, Generic commutative separable algebras and cospans of graphs, \textsl{Theory Appl.
 Categ.} \textbf{15} (2005), 164--177.

### 2020-11-17 cospans.tex
worked more on Section 5.1

@@
 \begin{thm}\label{SC}
-Given categories $\X$ and $\A$ with finite colimits and $L \maps \A \to \X$ a finitely cocontinuous functor, there exists a symmetric monoidal double category $_L\lCsp(\X)$ in which
+Given categories $\X$ and $\A$ with finite colimits and $L \maps \A \to \X$ a functor preserving
+finite colimits, there is a symmetric monoidal double category $_L\lCsp(\X)$ in which
 \begin{itemize}
@@
 \begin{proof}
-All relevant details can be found in \cite[Theorems~2.3\&3.9]{BC2}.
+This was proved in \cite[Theorems~2.3 \& 3.9]{BC2}.
 In particular, the double category structure only requires that $\X$ have pushouts, since this is how composition is formed.
-Moreover, the symmetric monoidal structure requires that $\X$ also have binary coproducts and an initial object (thus all finite colimits), and that $\A$ have and $L$ preserve finite coproducts, see \cite[Theorem~3.2.3]{CourserThesis}.
+The symmetric monoidal structure requires also that $\X$  has binary coproducts and an initial object (and thus all finite colimits), and that $\A$ has and $L$ preserves finite coproducts \cite[Theorem~3.2.3]{CourserThesis}.
 \end{proof}
 
-The following theorem establishes the desired equivalence between these two different double categorical network frameworks of structured and decorated cospans in a formal way.
-We denote by $\Rex$ the 2-category of finitely cocomplete categories and finitely cocontinuous functors, and the symmetric monoidal double structure of decorated cospans is worked out in \cref{thm:decorated_cospans,DC}.
+The following theorem establishes the equivalence between structured and decorated cospan double categories under certain conditions.
+We denote by $\Rex$ the 2-category of finitely cocomplete categories, finitely cocontinuous functors and natural transformatoins.
 
@@
 A double category is `fibrant' if every vertical 1-morphism has a `companion' and a `conjoint'---concepts explained in \cref{def:companion}.
-Shulman \cite[Thm.\ 1.2]{Shulman2010} showed how when a double category $\lX$ is fibrant, any symmetrical monoidal structure on $\lX$ gives one on $\bX$.
+Shulman \cite[Thm.\ 1.2]{Shulman2010} proved that when a double category $\lX$ is fibrant, any symmetrical monoidal structure on $\lX$ gives one on $\bX$.
 We can apply this to decorated cospans as follows:
@@
 We call elements of $E$ \define{edges} and elements of $N$ \define{nodes}.
-There is a category $\Graph$ with graphs as objects, and with morphism from the graph $s,t\maps E \to N$ to the graph $s',t' \maps E' \to N'$ is defined to be a pair of functions $f \maps E \to E', g \maps N \to N'$ such that these diagrams commute:
+There is a category $\Graph$ with graphs as objects, where a morphism from the graph $s,t\maps E \to N$ to the graph $s',t' \maps E' \to N'$ is a pair of functions $f \maps E \to E', g \maps N \to N'$ such that these diagrams commute:
 \[
@@
 
+We can easily build a double category with `open graphs' as horizontal 1-cells using the machinery of structured cospans.
 Let $L \maps \Set \to \Graph$ be the functor that assigns to a set $N$ the \define{discrete graph} on $N$: the graph with no edges and $N$ as its set of vertices.
@@
 \item objects are finite sets,
-\item a vertical 1-morphism from $M$ to $N$ is a function $f \maps M \to N$,
-\item a horizontal 1-cell from $M$ to $N$ is an \define{open graph} from $M$ to $N$, meaning a cospan in $\Graph$ of this form:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$L(N)$};
+\item a vertical 1-morphism from $X$ to $Y$ is a function $f \maps X \to Y$,
+\item a horizontal 1-cell from $X$ to $Y$ is an \define{open graph} from $X$ to $Y$, meaning a cospan in $\Graph$ of this form:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$L(X)$};
 \node (B) at (1,0) {$G$};
-\node (C) at (2,0) {$L(M)$,};
+\node (C) at (2,0) {$L(Y)$,};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$L(N_1)$};
+\node (A) at (0,0) {$L(X_1)$};
 \node (B) at (1,0) {$G_1$};
-\node (C) at (2,0) {$L(M_1)$};
-\node (A') at (0,-1) {$L(N_2)$};
+\node (C) at (2,0) {$L(Y_1)$};
+\node (A') at (0,-1) {$L(X_2)$};
 \node (B') at (1,-1) {$G_2$};
-\node (C') at (2,-1) {$L(M_2)$.};
+\node (C') at (2,-1) {$L(Y_2)$.};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \end{itemize}
-
-We can build an equivalent symmetric monoidal double category using decorated cospans.    For any finite set $N$ there is a category $F(N)$ where:
+Here is an example of an open graph:
+\[
+\scalebox{0.8}{
+\begin{tikzpicture}
+	\begin{pgfonlayer}{nodelayer}
+		\node [contact] (n1) at (-2,0) {$\bullet$};
+		\node [style = none] at (-2.1,0.3) {$n_1$};
+		\node [contact] (n2) at (0,1) {$\bullet$};
+		\node [style = none] at (0,1.3) {$n_2$};
+		\node [contact] (n3) at (0,-1) {$\bullet$};
+		\node [style = none] at (0,-1.3) {$n_3$};
+		\node [contact] (n4) at (2,0) {$\bullet$};
+		\node [style = none] at (2.1,0.3) {$n_4$};
+
+		\node [style = none] at (-1,1) {$e_1$};
+		\node [style = none] at (-1,-1) {$e_2$};
+		\node [style = none] at (1,1) {$e_3$};
+		\node [style = none] at (1,-1) {$e_4$};
+	    \node [style = none] at (0.3,0) {$e_5$};
+
+		\node [style=none] (1) at (-3,0) {1};
+		\node [style=none] (4) at (3,0) {2};
+
+		\node [style=none] (ATL) at (-3.4,1.4) {};
+		\node [style=none] (ATR) at (-2.6,1.4) {};
+		\node [style=none] (ABR) at (-2.6,-1.4) {};
+		\node [style=none] (ABL) at (-3.4,-1.4) {};
+
+		\node [style=none] (X) at (-3,1.8) {$X$};
+		\node [style=inputdot] (inI) at (-2.8,0) {};
+
+		\node [style=none] (Z) at (3,1.8) {$Y$};
+	 \node [style=inputdot] (outI') at (2.8,0) {};
+
+		\node [style=none] (MTL) at (2.6,1.4) {};
+		\node [style=none] (MTR) at (3.4,1.4) {};
+		\node [style=none] (MBR) at (3.4,-1.4) {};
+		\node [style=none] (MBL) at (2.6,-1.4) {};
+
+	\end{pgfonlayer}
+	\begin{pgfonlayer}{edgelayer}
+		\draw [style=inarrow, bend left=20, looseness=1.00] (n1) to (n2);
+		\draw [style=inarrow, bend right=20, looseness=1.00] (n1) to (n3);
+		\draw [style=inarrow, bend left=20, looseness=1.00] (n2) to (n4);
+		\draw [style=inarrow, bend right=20, looseness=1.00] (n3) to (n4);
+		\draw [style=inarrow] (n2) to (n3);
+%		\draw [style=inarrow] (W) to (Water);
+%		\draw [style=inarrow, bend left=40, looseness=1.00] (Water2) to (Something);
+%		\draw [style=inarrow, bend right=40, looseness=1.00] (Water2) to (Something);
+%		\draw [style=inarrow, bend left=40, looseness=1.00] (Something) to (A);
+%		\draw [style=inarrow, bend right=40, looseness=1.00] (Something) to (B);
+		\draw [style=simple] (ATL.center) to (ATR.center);
+		\draw [style=simple] (ATR.center) to (ABR.center);
+		\draw [style=simple] (ABR.center) to (ABL.center);
+		\draw [style=simple] (ABL.center) to (ATL.center);
+%		\draw [style=simple] (BTL.center) to (BTR.center);
+%		\draw [style=simple] (BTR.center) to (BBR.center);
+%		\draw [style=simple] (BBR.center) to (BBL.center);
+%		\draw [style=simple] (BBL.center) to (BTL.center);
+		\draw [style=simple] (MTL.center) to (MTR.center);
+		\draw [style=simple] (MTR.center) to (MBR.center);
+		\draw [style=simple] (MBR.center) to (MBL.center);
+		\draw [style=simple] (MBL.center) to (MTL.center);
+%		\draw [style=inputarrow] (outI) to (A);
+%		\draw [style=inputarrow] (outS) to (B);
+		\draw [style=inputarrow] (inI) to (n1);
+		\draw [style=inputarrow] (outI') to (n4);
+%		\draw [style=inputarrow] (inI') to (Water2);
+%		\draw [style=inputarrow] (inS') to (Water2);
+	\end{pgfonlayer}
+\end{tikzpicture}
+}
+\]
+
+We can also build a double category with open graphs as horizontal 1-cells using decorated cospans.    For any set $N$ there is a category $F(N)$ where:
 \begin{itemize}
@@
 \item A morphism from $s,t \maps E \to N$ to $s',t' \maps E' \to N$ is a morphism of graphs that is
-the identity on $N$, i.e., a function $f \maps E \to E'$ such that these diagrams commute:
+the identity on $N$: that is, a function $f \maps E \to E'$ such that these diagrams commute:
 \[
@@
 \node (C') at (2,-1) {$E'$};
-\node (D) at (3,-0.5) {$N$};
+\node (D) at (3,-0.5) {$N$.};
 \path[->,font=\scriptsize,>=angle 90]
@@
 
-There is a symmetric lax monoidal pseudofunctor $F \maps (\Set, +) \to (\Cat,\times)$  that assigns to a set $N$ the category $F(N)$.
-This behaves in the obvious way on morphisms --- what's that???
-The lax monoidal structure arises from functors $\phi_{M,N} \maps F(M) \times F(N) \to F(M+N)$ and $\phi_0 \maps F(\emptyset) \to 1$ defined in the obvious way --- what's that???
- Using  \cref{DC}, we thus obtain a symmetric monoidal double category $F\lCsp$ in which
+In general, decorated cospans involve a pseudofunctor to $\Cat$, but in this example there is actually a functor $F \maps \Set \to \Cat$ that assigns to a set $N$ the above category $F(N)$.
+Given a function $f \maps M \to N$, we define $F(f) \maps F(M) \to F(N)$ to map any graph structure $s,t \maps E \to M$ to the graph structure $f \circ s, f \circ t \maps E \to N$.
+
+We obtain a symmetric lax monoidal functor $F \maps (\Set, +) \to (\Cat,\times)$ by equipping $F$ with suitable functors $\phi_{N,N'} \maps F(N) \times F(N') \to F(N+N')$ for every pair of sets $N$ and $N'$, and also a functor $\phi_0 \maps F(\emptyset) \to 1 \in \Set$.
+The functor $\phi_0$ is uniquely determined since $1$ is the terminal category.
+More interesting is $\phi_{N,N'}$, which is defined using disjoint union.
+This functor maps a pair of graph structures $s, t \maps E \to N$ and $s',t' \maps E' \to N'$ to the graph structure $s+s', t+t' \maps E+E' \to N+N'$.
+
+Given the symmetric lax monoidal functor $F \maps (\Set, +) \to (\Cat,\times)$, \cref{DC} gives us a symmetric monoidal double category $F\lCsp$ in which:
 \begin{itemize}
 \item objects are sets,
-\item a vertical 1-morphism from $M$ to $N$ is a function $f: M \to N$,
-\item a horizontal 1-cell from $M$ to $N$ is a pair
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$M$};
-\node (B) at (1,0) {$P$};
-\node (C) at (2,0) {$N$};
-\node (D) at (3.25,0) {$G \in F(P)$};
+\item a vertical 1-morphism from $X$ to $X'$ is a function $f \maps X \to X'$,
+\item a horizontal 1-cell from $X$ to $Y$ is a pair
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$X$};
+\node (B) at (1,0) {$N$};
+\node (C) at (2,0) {$Y$};
+\node (D) at (3.25,0) {$G \in F(N)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-which can also be thought of as an open graph, 
+which can also be thought of as an open graph from $X$ to $Y$,
 \item a 2-morphism
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$N_1$};
-\node (A') at (0,-1) {$N_2$};
-\node (C') at (2,-1) {$M_2$};
-\node (B) at (1,0) {$P_1$};
-\node (C) at (2,0) {$M_1$};
-\node (D) at (1,-1) {$P_2$};
-\node (E) at (3,0) {$G_1 \in F(P_1)$};
-\node (F) at (3,-1) {$G_2 \in F(P_2)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i_1$} (B)
-(C) edge node[above]{$o_1$} (B)
+\node (A) at (0,0) {$X$};
+\node (B) at (1,0) {$N$};
+\node (C) at (2,0) {$Y$};
+\node (A') at (0,-1) {$X'$};
+\node (C') at (2,-1) {$Y'$};
+\node (D) at (1,-1) {$N'$};
+\node (E) at (3,0) {$G \in F(N)$};
+\node (F) at (3,-1) {$G' \in F(N')$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i$} (B)
+(C) edge node[above]{$o$} (B)
 (A) edge node[left]{$f$} (A')
 (C) edge node[right]{$g$} (C')
-(C') edge node [above] {$o_2$} (D)
-(A') edge node [above] {$i_2$} (D)
+(C') edge node [above] {$o'$} (D)
+(A') edge node [above] {$i'$} (D)
 (B) edge node [left] {$h$} (D);
@@
 \]
-is a commuting diagram in $\Set$ together with a morphism $\tau \maps F(h)(G_1) \to G_2$ in $F(P_2)$.
+is a commuting diagram in $\Set$ together with a morphism $\tau \maps F(h)(G) \to G'$ in $F(N')$.
 \end{itemize}

### 2020-11-17 cospans.tex
more work on section 5.1

@@
 We thus have two symmetric monoidal double categories: ${}_L \lCsp(\Graph)$ obtained from structured cospans and $F\lCsp$ obtained from decorated cospans.
-Both of these double categories have $\Set$ as their categories of objects, open graphs as horizontal 1-cells and maps of open graphs as 2-morphisms, and by Theorem \cref{thm:equiv}, we have an equivalence of symmetric monoidal double categories $$_L \lCsp(\Graph) \simeq F\lCsp.$$
+Both of these double categories have $\Set$ as their categories of objects, open graphs as horizontal 1-cells and maps of open graphs as 2-morphisms.
+One can show using Theorem \cref{thm:equiv} that $_L \lCsp(\Graph)$ and $F\lCsp$ are equivalent as symmetric monoidal double categories.
 

### 2020-11-17 cospans.tex
fixing some older edit

@@
 \begin{thm} \label{thm:equiv}
-Suppose $\A$ has finite colimits and $F \maps(\A,+) \to (\Cat,\times)$ is a symmetric lax monoidal pseudofunctor that factors through $\Rex$ as an ordinary pseudofunctor.
-Then the symmetric monoidal double category $F\lCsp$ of decorated cospans is equivalent to the symmetric monoidal double category $_L\lCsp(\inta F)$ of structured cospans, where $L \maps \A \to \inta F$ is the left adjoint of the induced Grothendieck opfibration $U \maps \inta F \to \A$.
+Suppose $\ca{A}$ has finite colimits and $F\maps(\A,+) \to (\Cat,\times)$ is a symmetric lax monoidal pseudofunctor that factors through $\bicat{Rex}$ as an ordinary pseudofunctor.
+Then the symmetric monoidal double categories $F\lCsp$ of decorated cospans and $_L\lCsp(\inta F)$ of structured cospans are equivalent, where $L \maps \A \to \inta F$ is a left adjoint of the induced Grothendieck opfibration $U\maps \inta F \to \A$.
 \end{thm}
@@
 \begin{defn}
-Given a set $\La$ of \define{labels}, an \define{$\La$-graph} is a graph $s,t\maps E\to N$
+Given a set $\La$ of \define{labels}, an $\La$-\define{graph} is a graph $s,t\maps E\to N$
  equipped with a function $\ell \maps E \to \La$.
@@
 ideas of that section from graphs to $\La$-graphs.   Everything works the same way, 
-but following previous work \cite{BCR} we call an open $\La$-graph an \define{$\La$-circuit}.
+but following previous work \cite{BCR} we call an open $\La$-graph an $\La$-\define{circuit}.
 
@@
 \item a morphism is an isomorphism class of $\La$-circuits, where an
-\define{$\La$-circuit} is a cospan in $\Graph_\La$ of this form:
+$\La$-\define{circuit} is a cospan in $\Graph_\La$ of this form:
 \[
@@
 \subsection{Double categories}\label{sec:doublecats}
+%!!! Christina: Kenny, would you mind cleaning this section up to? I don't believe we need the full fledged definitions here by the way.
 

### 2020-11-17 cospans.tex
setting straight something that was bothering me, hopefully now it's fine

@@
 
+Notice a subtlety in the above formulation: \cref{lem:MonGroth} provides a specifically induced monoidal structure on the fibres which becomes \cref{eq:explicitstructure1} in the cocartesian base case.
+If that fibrewise monoidal structure happens to itself be cocartesian, then it is necessarily isomorphic to \emph{any} other cocartesian structure on the fibres, by universal property of colimits.
+Therefore, we can simplify the above formulation to the one of the very \cref{thm:equiv} without having to specify that the structures came from monoidality of the pseudofunctor.
+DOES THIS MAKE SENSE TO ALL??
+
 On a highly related note, in what follows we are also interested in the existence of a left adjoint $L_F$ to an induced monoidal opfibration; the following result provides sufficient conditions for that.
-%, which go hand-in-hand with \cref{cor:fcocMonGroth} and \cref{lem:fibrewiselimits}.
 
@@
 \begin{equation}\label{eq:initialinfibre}
-\mathbf{1}\xrightarrow{\phi_0}F(0_\A)\xrightarrow{F(u_a)}F(a) 
+\mathbf{1}\xrightarrow{\mu_0}F(0_\A)\xrightarrow{F(u_a)}F(a) 
 \end{equation}

### 2020-11-17 cospans.tex
more edits on 3

@@
 \item a horizontal 1-cell from $a$ to $b$ is a cospan in $\X$ of the form
-\begin{equation}\label{eq:structuredcospan}
+\begin{displaymath}
 \begin{tikzpicture}[scale=1.5]
@@
 \end{tikzpicture}
-\end{equation}
+\end{displaymath}
 \item a 2-morphism is a map of cospans in $\X$ of the form
-\begin{equation}\label{eq:2cellsStrCsp}
+\begin{displaymath}
 \begin{tikzpicture}[scale=1.5]
@@
 \end{tikzpicture}
-\end{equation}
+\end{displaymath}
 \end{itemize}
@@
 \begin{cor}\label{cor:fcocMonGroth}
- Suppose $\A$ is a finitely cocomplete category and $F\maps(\A,+)\to(\Cat,\times)$ is a lax monoidal pseudofunctor. If its corresponding pseudofunctor $\A\to\bicat{MonCat}$ via \cref{monGroth} 
- factors through $\Rex$, then the Grothendieck category $\inta F$ has all finite colimits and the induced opfibration $U_F\maps\inta F\to\A$ preserves them. 
+ Suppose $\A$ is a finitely cocomplete category and $F\maps(\A,+)\to(\Cat,\times)$ is a lax monoidal pseudofunctor.
+If its corresponding pseudofunctor $\A\to\bicat{MonCat}$ via \cref{monGroth} factors through $\Rex$, then the Grothendieck category $\inta F$ has all finite colimits and the induced opfibration $U_F\maps\inta F\to\A$ preserves them.
 \end{cor}
@@
 If that fibrewise monoidal structure happens to itself be cocartesian, then it is necessarily isomorphic to \emph{any} other cocartesian structure on the fibres, by universal property of colimits.
-Therefore, we can simplify the above formulation to the one of the very \cref{thm:equiv} without having to specify that the structures came from monoidality of the pseudofunctor.
-DOES THIS MAKE SENSE TO ALL??
+Therefore, we can simplify the above assumption to the one of the very \cref{thm:equiv} without having to specify that the structures came from monoidality of the pseudofunctor.
+However, we \emph{will} use the formulation of coproducts and initial object in terms of the monoidal structure of $F$, and that is why correspondence \cref{monGroth} is necessary.
+DOES THIS MAKE SENSE TO ALL?? %still, we ARE going to use the formation of coproducts as above. Otherwise someone might think that the monoidal Groth story was redundant here!
 
@@
 \begin{proof}[Proof of \cref{thm:equiv}]
-Recall from \cref{thm:decorated_cospans} that the double category of decorated cospans $\dcsp{F}$ has objects and vertical 1-morphisms as in $\A$, while horizontal 1-cells are cospans $\cspn{a}{m}{b}{}{}$ in $\A$ decorated by an $x\in F(m)$ and 2-morphisms are maps of cospans $k\maps m\to m'$ together with $\tau\maps(Fk)(x)\to x'$ in $F(m')$.
-%!!!
+Recall from \cref{thm:decorated_cospans} that the double category of decorated cospans $\dcsp{F}$ has objects and vertical 1-morphisms as in $\A$, while horizontal 1-cells are cospans $\cspn{a}{m}{b}{}{}$ in $\A$ decorated by an $x\in F(m)$ and 2-morphisms are maps of cospans $k\maps m\to m'$ together with $\tau\maps(Fk)(x)\to x'$ in $F(m')$.%!!!
 Christina: Should we call them `generalized maps of cospans'?
@@
 By \cref{cor:fcocMonGroth}, when $F$ as an ordinary pseudofunctor factors through $\Rex$, the Gro\-the\-ndieck construction gives rise to a finitely cocomplete $\inta F$ such that the corresponding opfibration $U\maps\inta{F}\to\A$ preserves all finite colimits.
-Since in particular it preserves the initial object, \cref{lem:fibrewiselimits,prop:opfibtolari} apply 
-%which equivalently means that all fibres have initial objects and the reindexing functors preserve them by , %Christina: there is a little bit of circularity here.
-We knew fibres have and reindexing functors preserve from the factorization already!
-Change Gray accordingly perhaps?
-and produce a left adjoint $L\maps\A\to\inta F$ to $U$, with $UL=1_\A$. 
+Moreover, by \cref{prop:opfibtolari}, $U$ has a left adjoint $L\maps\A\to\inta F$ with $UL=1_\A$.
 Diagrammatically,
@@
 describes the construction of the adjunction from the original $F$.
-Explicitly, the left adjoint picks the initial object in the finitely cocomplete fibre $L(a)=(a,\bot_a)$, also expressed by $F(u_a)\circ\mu_0(*)$ as in \cref{eq:initialinfibre}.
-
-{\chris In progress...}
-
-Using this functor $L_F$ between finitely cocomplete categories that preserves all colimits that exist (as a left adjoint), we can construct the double category of structured cospans $\scsp{L_F}{\inta F}$.
-Its objects and vertical morphisms are again those of the category $\A$, whereas horizontal 1-cells $a\tickar b$ as in \cref{eq:structuredcospan} are now cospans of the form $\cspn{L_F(a)}{v}{L_F(b)}{}{}$ in the Grothendieck category $\inta F$.
+Explicitly, the left adjoint picks the initial object in the finitely cocomplete fibre $L(a)=(a,\bot_a)$, also expressed as $F(u_a)\circ\mu_0(*)$ according to \cref{eq:initialinfibre} for $(\mu,\mu_0)$ the monoidal structure of $F$.
+
+As a left adjoint, this induced $L$ preserves all colimits that exist between the finitely cocomplete categories $\A$ and $\inta F$, so we can construct the double category of structured cospans $\scsp{L}{\inta F}$ of \cref{SC}.
+Its objects and vertical morphisms are those of the category $\A$ (as for $\dcsp{F}$ earlier), whereas horizontal 1-cells are now cospans of the form $\cspn{L(a)}{v}{L(b)}{}{}$ in the Grothendieck category $\inta F$ (\cref{def:GrothCat}).
 Explicitly, they consist of two pairs of morphisms
@@
 \end{equation}
-where $x\in F(m)$, according to \cref{def:GrothCat}. Finally, the 2-morphisms in this double category are as described in \cref{eq:2cellsStrCsp}, in this context fully unravelled below:
+with $x\in F(m)$; recall that the reindexing functors $F(i),F(o)$ preserve all finite colimits across the fibre categories.
+Finally, the 2-morphisms of this double category in this context unravel as follows
 \begin{displaymath}
- \begin{tikzcd}[sep=1.5in,ampersand replacement=\&]
+ \begin{tikzcd}[row sep=1.2in,column sep=1.7in,ampersand replacement=\&]
  (a,\bot_a)\ar[r,"{\begin{cases}i\maps a\to m &\textrm{in }\A \\!\maps F(i)(\bot_a)\to x &\textrm{in }F(m)\end{cases}}"]\ar[d,"{\begin{cases}f\maps a\to a' &\textrm{in }\A \\\chi_a\maps F(f)(\bot_a)\cong \bot_{a'} &\textrm{in }F(a')\end{cases}}"description] \& (m,x) \ar[d,"{\begin{cases}k\maps m\to m' &\textrm{in }\A \\ \tau\maps F(k)(x)\to x' &\textrm{in }F(m')\end{cases}}"description] \& (b,\bot_b)\ar[l,"{\begin{cases}o\maps b\to m &\textrm{in }\A \\!\maps F(o)(\bot_b)\to x &\textrm{in }F(m)\end{cases}}"']\ar[d,"{\begin{cases}g\maps b\to b' &\textrm{in }\A \\\chi_b\maps F(g)(\bot_b)\cong \bot_{b'} &\textrm{in }F(b')\end{cases}}"description] \\
@@
 \end{displaymath}
-where the outside vertical legs come from the definition of $L_F$ on arrows, \cref{eq:Lonarrows}. 
-%!!! The above diagram might be a bit overwhelming, but all info is there. Choose which parts are required for a smooth proof!
-The square commutativities translate to $k\circ i=i'\circ f$ and $k\circ o=o'\circ g$ in $\A$, and also by composition in the Grothendieck category, to
+where the outside vertical legs come from the definition of $L$ on arrows \cref{eq:Lonarrows}. 
+Explicitly, the above square commutativities translate to the conditions $k\circ i=i'\circ f$ and $k\circ o=o'\circ g$ in $\A$, and also to
 \begin{gather}\label{eq:Grothcommutativity}
@@
 \end{gather}
-in the category $F(m')$.
-However, since all maps are unique in the above equality, emanating from initial objects (since reindexing functors preserve those), this gives no extra conditions for the morphisms involved; similarly for the equality including $o, o'$.
+in the fibre category $F(m')$, by composition in the Grothendieck category \cref{eq:compGrothcat}.
+Since both morphisms emanate from the mapped initial object in $F(m')$ under the finitely cocontinuous reindexing functors, they are the unique such into $x'$ therefore this gives no extra conditions; similarly for the equality including $o,o'$.
+
+{\chris In progress...}
 
@@
 \item objects pairs $(a, x \in F(a))$ and
-\item a morphism from $(a, x \in F(a))$ to $(b, y\in F(b))$ is a pair $(f \maps a \to b,\delta \maps F(f)(x) \to y)\in\A\times F(b)$.
+\item a morphism from $(a, x \in F(a))$ to $(b, y\in F(b))$ is a pair $(f \maps a \to b,k \maps F(f)(x) \to y)\in\A\times F(b)$.
 \end{itemize}
+The unit is $(1_a\maps a\to a,F(1_a)(x)\cong x)$ and composition of $(f,k)\maps(a,x)\to(b,y)$ and $(g,\ell)\maps(b,y)\to(c,z)$ is
+\begin{equation}\label{eq:compGrothcat}
+\left(a\xrightarrow{f}b\xrightarrow{g}c, F(g\circ f)x\cong Fg(Ff(x))\xrightarrow{Ff(k)}Fg(y)\xrightarrow{\ell}z\right) 
+\end{equation}
 This is an opfibred category over $\A$ via the obvious forgetful functor, with fibre categories $(\inta F)_a=F(a)$ and reindexing functors $f_!=F(f)$.

### 2020-11-17 cospans.tex
ongoing work on theorem

@@
 a map of cospans in $\A$:
-\begin{equation}\label{eq:FCsp2morph}
+\begin{displaymath}
 \begin{tikzpicture}[scale=1.5]
@@
 \end{tikzpicture}
-\end{equation}
+\end{displaymath}
 together with a \define{decoration morphism} $\tau \maps F(h)(x) \to x'$ in $F(m')$.
@@
 \begin{displaymath}
- \begin{tikzcd}[row sep=1.2in,column sep=1.7in,ampersand replacement=\&]
+ \begin{tikzcd}[row sep=1in,column sep=1.7in,ampersand replacement=\&]
  (a,\bot_a)\ar[r,"{\begin{cases}i\maps a\to m &\textrm{in }\A \\!\maps F(i)(\bot_a)\to x &\textrm{in }F(m)\end{cases}}"]\ar[d,"{\begin{cases}f\maps a\to a' &\textrm{in }\A \\\chi_a\maps F(f)(\bot_a)\cong \bot_{a'} &\textrm{in }F(a')\end{cases}}"description] \& (m,x) \ar[d,"{\begin{cases}k\maps m\to m' &\textrm{in }\A \\ \tau\maps F(k)(x)\to x' &\textrm{in }F(m')\end{cases}}"description] \& (b,\bot_b)\ar[l,"{\begin{cases}o\maps b\to m &\textrm{in }\A \\!\maps F(o)(\bot_b)\to x &\textrm{in }F(m)\end{cases}}"']\ar[d,"{\begin{cases}g\maps b\to b' &\textrm{in }\A \\\chi_b\maps F(g)(\bot_b)\cong \bot_{b'} &\textrm{in }F(b')\end{cases}}"description] \\
@@
 
-{\chris In progress...}
-
-In order to prove that there is a double equivalence (\cref{ShulDubEquiv}) between $\dcsp{F}$ and $\scsp{L_F}{\inta F}$, we define a %n identity-on-objects and vertical morphism
-double functor
+Building up to an equivalence of the above described double categories, we now define a double functor
 \begin{displaymath}
-\mathbb{E}\maps\scsp{L_F}{\inta F} \longrightarrow\dcsp{F}
+\lE=(\lE_0,\lE_1)\maps\scsp{L}{\inta F} \longrightarrow\dcsp{F}
 \end{displaymath}
-as follows.
-The object component of $\mathbb{E}=(\mathbb{E}_0,\mathbb{E}_1)$ is $\mathbb{E}_0 = \id_{\A}$ since both double categories have $\A$ as their vertical category; trivially, $\mathbb{E}_0$ is an equivalence of categories.
-Given a horizontal 1-cell in $\scsp{L_F}{\inta F}$ like \cref{eq:scsphor1cell}, the arrow component $\mathbb{E}_1$ of the double functor simply maps it to the decorated cospan
-\begin{displaymath}
- a\xrightarrow{\; i \;}m\xleftarrow{\; o \;}b\;\textrm{ with decoration }x\in F(m)
-\end{displaymath}
-Notice that this really is a bijective correspondence since the unique maps from the initial objects in the fibres provide no extra information.
-Finally, given a 2-morphism of $L_F$-structured cospans as described above, $\mathbb{E}_1$ maps it to the underlying cospan 2-morphism
+which on vertical categories acts as the identity $\lE_0 = \id_{\A}$.
+Given a horizontal 1-cell in $\scsp{L}{\inta F}$ as in \cref{eq:scsphor1cell}, $\lE_1$ maps it to the decorated cospan $i\maps a\to m\leftarrow b:o$ with decoration $x\in F(m)$,
+%Notice that this really is a bijective correspondence since the unique maps from the initial objects in the fibres provide no extra information.
+whereas a 2-morphism of $L$-structured cospans as above is mapped to the underlying cospan 2-morphism in $\A$
 \begin{displaymath}
@@
 \end{displaymath}
- in $\A$ along with the map $\tau\maps Fk(x)\to x'$ in $F(m')$, namely a decorated cospan 2-morphism as per \cref{eq:FCsp2morph}.
-Once again, this is a bijective correspondence since, as discussed above, the commutativity \cref{eq:Grothcommutativity} holds automatically by initiality of the domain.
-%!!!Christina: commented out big chunks of proof.
-They are right below if we want to revive parts of them, if we think the reader needs deeper level of detail.
-The idea is that the above description suffices as fully faithful and essentially surjective evidence, but perhaps we would like to spell that out more.
-On to strongness next.
-\begin{comment}
-which is a cospan in $\X$ of the form:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$L(c)$};
-\node (B) at (1,0) {$x$};
-\node (C) at (2,0) {$L(c')$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i$} (B)
-(C) edge node[above]{$o$} (B);
-\end{tikzpicture}
-\]
-the image $\mathbb{E}_1(M)$ is given by the pair:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$c$};
-\node (B) at (1,0) {$R(x)$};
-\node (C) at (2,0) {$c'$};
-\node (D) at (3,0) {$x \in F(R(x))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$R(i) {\eta_c}$} (B)
-(C) edge node[above]{$R(o) {\eta_{c'}}$} (B);
-\end{tikzpicture}
-\]
-where $R\maps \X \to \A$ is the right adjoint to the functor $L \maps \A \to \X$ and $\eta \maps 1_{\A} \to RL$ is the unit of the adjunction $L \dashv R$ which is an isomorphism since $L$ is fully faithful.
-\textbf{Hopefully...actually, it's a `lari'!} Similarly, the image of a 2-morphism $\alpha \maps M \to N$ in $_L \lCsp(\X)$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$L(c_1)$};
-\node (B) at (1,0) {$x$};
-\node (C) at (2,0) {$L(c_2)$};
-\node (A') at (0,-1) {$L(c_1')$};
-\node (B') at (1,-1) {$x'$};
-\node (C') at (2,-1) {$L(c_2')$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i$} (B)
-(C) edge node[above]{$o$} (B)
-(A') edge node[above]{$i'$} (B')
-(C') edge node[above]{$o'$} (B')
-(A) edge node [left]{$L(f)$} (A')
-(B) edge node [left]{$\alpha$} (B')
-(C) edge node [right]{$L(g)$} (C');
-\end{tikzpicture}
-\]
-is given by the 2-morphism $\mathbb{E}_1(\alpha) \maps \mathbb{E}_1(M) \to \mathbb{E}_1(N)$ in $\mathbb{F}\textnormal{Cospan}(\A)$ given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$c_1$};
-\node (B) at (1,0) {$R(x)$};
-\node (C) at (2,0) {$c_2$};
-\node (A') at (0,-1) {$c_1'$};
-\node (B') at (1,-1) {$R(x')$};
-\node (C') at (2,-1) {$c_2'$};
-\node (D) at (3,0) {$x \in F(R(x))$};
-\node (D') at (3,-1) {$x' \in F(R(x'))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$R(i) \eta_{c_1}$} (B)
-(C) edge node[above]{$R(o) \eta_{c_2}$} (B)
-(A') edge node[above]{$R(i') \eta_{c_1'}$} (B')
-(C') edge node[above]{$R(o') \eta_{c_2'}$} (B')
-(A) edge node [left]{$f$} (A')
-(B) edge node [left]{$R(\alpha)$} (B')
-(C) edge node [right]{$g$} (C');
-\end{tikzpicture}
-\]
-together with a morphism $\tau \maps F(R(\alpha))(x) \to x'$ in $F(R(x')) \subseteq \mathrm{X}$ which comes from the Grothendieck construction of the pseudofunctor $F \maps \A \to \Cat$.
-That $\mathbb{E}_0$ is a functor is clear.
-For $\mathbb{E}_1$, given two vertically composable 2-morphisms $M$ and $M'$ in $_L \lCsp(\X)$,
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$L(c_1)$};
-\node (B) at (1,0) {$x$};
-\node (C) at (2,0) {$L(c_2)$};
-\node (A') at (0,-1) {$L(c_1')$};
-\node (B') at (1,-1) {$x'$};
-\node (C') at (2,-1) {$L(c_2')$};
-\node (A'') at (0,-2) {$L(c_1')$};
-\node (B'') at (1,-2) {$x'$};
-\node (C'') at (2,-2) {$L(c_2')$};
-\node (A''') at (0,-3) {$L(c_1'')$};
-\node (B''') at (1,-3) {$x''$};
-\node (C''') at (2,-3) {$L(c_2'')$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i$} (B)
-(C) edge node[above]{$o$} (B)
-(A') edge node[above]{$i'$} (B')
-(C') edge node[above]{$o'$} (B')
-(A) edge node [left]{$L(f)$} (A')
-(B) edge node [left]{$\alpha$} (B')
-(C) edge node [right]{$L(g)$} (C')
-(A'') edge node[above]{$i'$} (B'')
-(C'') edge node[above]{$o'$} (B'')
-(A''') edge node[above]{$i''$} (B''')
-(C''') edge node[above]{$o''$} (B''')
-(A'') edge node [left]{$L(f')$} (A''')
-(B'') edge node [left]{$\alpha'$} (B''')
-(C'') edge node [right]{$L(g')$} (C''');
-\end{tikzpicture}
-\]
-their vertical composite $M'M$ is given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$L(c_1)$};
-\node (B) at (1,0) {$x$};
-\node (C) at (2,0) {$L(c_2)$};
-\node (A') at (0,-1) {$L(c_1'')$};
-\node (B') at (1,-1) {$x''$};
-\node (C') at (2,-1) {$L(c_2'')$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i$} (B)
-(C) edge node[above]{$o$} (B)
-(A') edge node[above]{$i''$} (B')
-(C') edge node[above]{$o''$} (B')
-(A) edge node [left]{$L(f'f)$} (A')
-(B) edge node [left]{$\alpha' \alpha$} (B')
-(C) edge node [right]{$L(g' g)$} (C');
-\end{tikzpicture}
-\]
-and the image of this 2-morphism $\mathbb{E}_1(M'M)$ is given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$c_1$};
-\node (B) at (1.5,0) {$R(x)$};
-\node (C) at (3,0) {$c_2$};
-\node (A') at (0,-1) {$c_1''$};
-\node (B') at (1.5,-1) {$R(x'')$};
-\node (C') at (3,-1) {$c_2''$};
-\node (D) at (4,0) {$x \in F(R(x))$};
-\node (D') at (4,-1) {$x'' \in F(R(x''))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$R(i) \eta_{c_1}$} (B)
-(C) edge node[above]{$R(o) \eta_{c_2}$} (B)
-(A') edge node[above]{$R(i'') \eta_{c_1''}$} (B')
-(C') edge node[above]{$R(o'') \eta_{c_2''}$} (B')
-(A) edge node [left]{$f'f$} (A')
-(B) edge node [left]{$R(\alpha' \alpha)$} (B')
-(C) edge node [right]{$g'g$} (C');
-\end{tikzpicture}
-\]
-together with a morphism $\tau_{M' M} \maps F(R(\alpha' \alpha))(x) \to x''$ in $F(R(x''))$. On the other hand, the individual images $\mathbb{E}_1(M)$ and $\mathbb{E}_1(M')$ are given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$c_1$};
-\node (B) at (1.5,0) {$R(x)$};
-\node (C) at (3,0) {$c_2$};
-\node (A') at (0,-1) {$c_1'$};
-\node (B') at (1.5,-1) {$R(x')$};
-\node (C') at (3,-1) {$c_2'$};
-\node (D) at (4,0) {$x \in F(R(x))$};
-\node (D') at (4,-1) {$x' \in F(R(x'))$};
-\node (A'') at (0,-2) {$c_1'$};
-\node (B'') at (1.5,-2) {$R(x')$};
-\node (C'') at (3,-2) {$c_2'$};
-\node (A''') at (0,-3) {$c_1''$};
-\node (B''') at (1.5,-3) {$R(x'')$};
-\node (C''') at (3,-3) {$c_2''$};
-\node (D'') at (4,-2) {$x' \in F(R(x'))$};
-\node (D''') at (4,-3) {$x'' \in F(R(x''))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$R(i) \eta_{c_1}$} (B)
-(C) edge node[above]{$R(o) \eta_{c_2}$} (B)
-(A') edge node[above]{$R(i') \eta_{c_1'}$} (B')
-(C') edge node[above]{$R(o') \eta_{c_2'}$} (B')
-(A) edge node [left]{$f$} (A')
-(B) edge node [left]{$R(\alpha)$} (B')
-(C) edge node [right]{$g$} (C')
-(A'') edge node[above]{$R(i') \eta_{c_1'}$} (B'')
-(C'') edge node[above]{$R(o') \eta_{c_2'}$} (B'')
-(A''') edge node[above]{$R(i'') \eta_{c_1''}$} (B''')
-(C''') edge node[above]{$R(o'') \eta_{c_2''}$} (B''')
-(A'') edge node [left]{$f'$} (A''')
-(B'') edge node [left]{$R(\alpha')$} (B''')
-(C'') edge node [right]{$g'$} (C''');
-\end{tikzpicture}
-\]
-together with morphisms $\tau_M \maps F(R(\alpha))(x) \to x'$ in $F(R(x'))$ and $\tau_{M'} \maps F(R(\alpha')(x') \to x''$ in $F(R(x''))$, respectively.
-The vertical composite $\mathbb{E}_1(M')\mathbb{E}_1(M)$ of the above two 2-morphisms is given by $\mathbb{E}_1(M'M)$ as $R$ is a functor and $\tau_{M'M}=\tau_{M'} \tau_M$.
-The functors $\mathbb{E}_0$ and $\mathbb{E}_1$ satisfy the equations $\mathbb{E}_0 S = S \mathbb{E}_1$ and $\mathbb{E}_0 T = T \mathbb{E}_1$.
-
-To see that this functor is essentially surjective, given a horizontal 1-cell in $F\lCsp$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$c_1$};
-\node (B) at (1,0) {$c$};
-\node (C) at (2,0) {$c_2$};
-\node (D) at (3,0) {$x \in F(c)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i$} (B)
-(C) edge node[above]{$o$} (B);
-\end{tikzpicture}
-\]
-we can find a 2-isomorphism in $F\lCsp$ whose codomain is the above horizontal 1-cell and whose domain is the image of the following horizontal 1-cell in $_L \lCsp(\X)$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$L(c_1)$};
-\node (B) at (1,0) {$x$};
-\node (C) at (2,0) {$L(c_2)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i'$} (B)
-(C) edge node[above]{$o'$} (B);
-\end{tikzpicture}
-\]
-with the 2-isomorphism in $F\lCsp$ given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$c_1$};
-\node (B) at (1,0) {$R(x)$};
-\node (C) at (2,0) {$c_2$};
-\node (A') at (0,-1) {$c_1$};
-\node (B') at (1,-1) {$c$};
-\node (C') at (2,-1) {$c_2$};
-\node (D) at (3,0) {$x \in F(R(x))$};
-\node (D') at (3,-1) {$x \in F(c)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$R(i') \eta_{c_1}$} (B)
-(C) edge node[above]{$R(o') \eta_{c_2}$} (B)
-(A') edge node[above]{$i$} (B')
-(C') edge node[above]{$o$} (B')
-(A) edge node [left]{$1$} (A')
-(B) edge node [left]{${(R(e) \eta_c)}^{-1}$} (B')
-(C) edge node [right]{$1$} (C');
-\end{tikzpicture}
-\]
-$$\tau \maps F({(R(e)\eta_c)}^{-1})(x) \to x$$
-where $e \maps L(c) \to x$ is given by the map from the trivial decoration on $c$ to $x \in F(c)$.
-%The object and arrow components $\mathbb{E}_0$ and $\mathbb{E}_1$ satisfy the equations $S \mathbb{E}_1 = \mathbb{E}_0 S$ and $T \mathbb{E}_1 = \mathbb{E}_0 T$.
-
-To show that the double functor $\mathbb{E}$ is fully faithful, we need to show that the map  $$\mathbb{E}_1 \maps _f { _L \lCsp(\X)}_g(M,N) \to {_{\mathbb{E}(f)} {F\lCsp}_{\mathbb{E}(g)}}(\mathbb{E}(M),\mathbb{E}(N))$$ is bijective for arbitrary vertical 1-morphisms $f$ and $g$ and horizontal 1-cells $M$ and $N$ of $_L \lCsp(\X)$.
-Consider a 2-morphism in $_L \lCsp(\X)$ with horizontal source and target $M$ and $N$, respectively and vertical source and target $f$ and $g$, respectively:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$L(c_1)$};
-\node (B) at (1,0) {$x$};
-\node (C) at (2,0) {$L(c_2)$};
-\node (A') at (0,-1) {$L(c_1')$};
-\node (B') at (1,-1) {$x'$};
-\node (C') at (2,-1) {$L(c_2')$};
-\node (D) at (1,0.5) {$M$};
-\node (E) at (-1,-0.5) {$f$};
-\node (F) at (1,-1.5) {$N$};
-\node (G) at (3,-0.5) {$g$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i$} (B)
-(C) edge node[above]{$o$} (B)
-(A') edge node[above]{$i'$} (B')
-(C') edge node[above]{$o'$} (B')
-(A) edge node [left]{$L(f)$} (A')
-(B) edge node [left]{$\alpha$} (B')
-(C) edge node [right]{$L(g)$} (C');
-\end{tikzpicture}
-\]
-Thus the set $$_f { _L \lCsp(\X)}_g(M,N)$$ consists of triples $$(f,\alpha,g)$$ rendering the above diagram commutative where $f$ and $g$ are morphisms of $\A$ and $\alpha$ is a morphism of $\X$.
-The image of the above 2-morphism under the double functor $\mathbb{E}$ is given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$c_1$};
-\node (B) at (1,0) {$R(x)$};
-\node (C) at (2,0) {$c_2$};
-\node (A') at (0,-1) {$c_1'$};
-\node (B') at (1,-1) {$R(x')$};
-\node (C') at (2,-1) {$c_2'$};
-\node (D) at (1,0.5) {$x \in F(R(x))$};
-\node (D') at (1,-1.5) {$x' \in F(R(x'))$};
-\node (E) at (1,1) {$\mathbb{E}(M)$};
-\node (F) at (-1,-0.5) {$\mathbb{E}(f)$};
-\node (G) at (1,-2) {$\mathbb{E}(N)$};
-\node (H) at (3,-0.5) {$\mathbb{E}(g)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$R(i)\eta_{c_1}$} (B)
-(C) edge node[above]{$R(o)\eta_{c_2}$} (B)
-(A') edge node[above]{$R(i')\eta_{c_1'}$} (B')
-(C') edge node[above]{$R(o')\eta_{c_2'}$} (B')
-(A) edge node [left]{$f$} (A')
-(B) edge node [left]{$R(\alpha)$} (B')
-(C) edge node [right]{$g$} (C');
-\end{tikzpicture}
-\]
-together with a morphism $\tau \maps F(R(\alpha))(x) \to x'$ of $F(R(x'))$.
-Thus the set $$_{\mathbb{E}(f)} {F\lCsp}_{\mathbb{E}(g)}(\mathbb{E}(M),\mathbb{E}(N))$$ consists of 4-tuples $$(f,R(\alpha),g,\tau)$$ rendering the above diagram commutative and where $f,g$ and $R(\alpha)$ are morphisms of $\A$ and $\tau$ is a morphism in $F(R(x'))$.
-The morphisms $R(\alpha) \maps R(x) \to R(x')$ and $\tau \maps F(R(\alpha))(x) \to x'$ together determine the morphism $\alpha \maps x \to x'$ in $\mathrm{X}$ and conversely; given two objects $x=(c,x \in F(c))$ and $x'=(c',x' \in F(c'))$ of $\X=\inta{F}$, a morphism from $\alpha \maps x \to x'$ is a pair $$(h \maps c \to c', \tau \maps F(h)(x) \to x')$$ where $h \maps c \to c'$ is given by $R(\alpha) \maps R(x) \to R(x')$.
-This shows that $\mathbb{E}$ is fully faithful.
-\textbf{At least in my favorite example...}
-\end{comment}
-Functoriality of $\mathbb{E}_1$ can be verified, and moreover $(\mathbb{E}_0,\mathbb{E}_1)$ indeed define a strong double functor: there exist natural isomorphisms
-\begin{gather*}
- \mathbb{E}(M) \odot \mathbb{E}(N) \xrightarrow{\sim} \mathbb{E}(M \odot N) \\
-U_{\mathbb{E}m} \xrightarrow{\sim} \mathbb{E}(U_m)
-\end{gather*}
-for any pair of composable horizontal 1-cells $M=\cspn{(a,\bot_a)}{(m,x)}{(b,\bot_b)}{}{}$ and $N=\cspn{(b,\bot_b)}{(n,y)}{(c,\bot_c)}{}{}$ and any object $m$ of $\scsp{L_F}{\inta F}$.
-In more detail, $\mathbb{E}(M)\odot \mathbb{E}(N)$ is given as in \cref{eq:dcospanscomposition} via the pushout cospan and decoration
+in $\A$ along with the map $\tau\maps Fk(x)\to x'$ in $F(m')$, namely an $F$-decorated cospan 2-morphism. 
+% Once again, this is a bijective correspondence since, as discussed above, the commutativity \cref{eq:Grothcommutativity} holds automatically by initiality of the domain.
+With these definitions, $\lE$ is indeed a strong double functor as in \cref{def:doublefun}: both $\lE_0$ and $\lE_1$ are functors that appropriately commute with sources and targets, and there exist globular 2-isomorphisms $\lE(M) \odot \lE(N) \simrightarrow\lE(M \odot N)$, $U_{\lE m} \simrightarrow\lE(U_m)$
+for any pair of composable horizontal 1-cells $M=\cspn{(a,\bot_a)}{(m,x)}{(b,\bot_b)}{}{}$ and $N=\cspn{(b,\bot_b)}{(n,y)}{(c,\bot_c)}{}{}$ and any object $m$ of $\scsp{L}{\inta F}$.
+Explicitly, $\mathbb{E}(M)\odot \mathbb{E}(N)$ is given as in \cref{eq:dcospanscomposition} via the pushout cospan and decoration
 \begin{displaymath}
@@
   & m+_bn & \\
-  a\ar[ur,"j_m\circ i"] && b,\ar[ul,"j_n\circ o"']
- \end{tikzcd}
- \begin{tikzcd}
-  1\ar[r,"x\times y"]\ar[drr,dashed] & F(m)\times F(n)\ar[r,"\phi_{m,n}"] & F(m+ n)\ar[d,"F(j)"] \\ 
-  && F(m+_b n)
- \end{tikzcd}
+  a\ar[ur] && b,\ar[ul]
+ \end{tikzcd}\qquad
+  1\xrightarrow{x\times y}F(m)\times F(n)\xrightarrow{\phi_{m,n}}F(m+n)\xrightarrow{F(\psi)}F(m+_bn)
 \end{displaymath}
-where $j_m, j_n$ denote the maps into a pushout.
+{\chris In progress...}
+
 On the other hand, first composing $M$ and $N$ in the Grothendieck category $\scsp{L_F}{\inta F}$ using fibrewise pushouts constructed using \cref{lem:fibrewiselimits} 
@@
 
+\begin{comment}
+which is a cospan in $\X$ of the form:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$L(c)$};
+\node (B) at (1,0) {$x$};
+\node (C) at (2,0) {$L(c')$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i$} (B)
+(C) edge node[above]{$o$} (B);
+\end{tikzpicture}
+\]
+the image $\mathbb{E}_1(M)$ is given by the pair:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$c$};
+\node (B) at (1,0) {$R(x)$};
+\node (C) at (2,0) {$c'$};
+\node (D) at (3,0) {$x \in F(R(x))$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$R(i) {\eta_c}$} (B)
+(C) edge node[above]{$R(o) {\eta_{c'}}$} (B);
+\end{tikzpicture}
+\]
+where $R\maps \X \to \A$ is the right adjoint to the functor $L \maps \A \to \X$ and $\eta \maps 1_{\A} \to RL$ is the unit of the adjunction $L \dashv R$ which is an isomorphism since $L$ is fully faithful.
+\textbf{Hopefully...actually, it's a `lari'!} Similarly, the image of a 2-morphism $\alpha \maps M \to N$ in $_L \lCsp(\X)$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$L(c_1)$};
+\node (B) at (1,0) {$x$};
+\node (C) at (2,0) {$L(c_2)$};
+\node (A') at (0,-1) {$L(c_1')$};
+\node (B') at (1,-1) {$x'$};
+\node (C') at (2,-1) {$L(c_2')$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i$} (B)
+(C) edge node[above]{$o$} (B)
+(A') edge node[above]{$i'$} (B')
+(C') edge node[above]{$o'$} (B')
+(A) edge node [left]{$L(f)$} (A')
+(B) edge node [left]{$\alpha$} (B')
+(C) edge node [right]{$L(g)$} (C');
+\end{tikzpicture}
+\]
+is given by the 2-morphism $\mathbb{E}_1(\alpha) \maps \mathbb{E}_1(M) \to \mathbb{E}_1(N)$ in $\mathbb{F}\textnormal{Cospan}(\A)$ given by:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$c_1$};
+\node (B) at (1,0) {$R(x)$};
+\node (C) at (2,0) {$c_2$};
+\node (A') at (0,-1) {$c_1'$};
+\node (B') at (1,-1) {$R(x')$};
+\node (C') at (2,-1) {$c_2'$};
+\node (D) at (3,0) {$x \in F(R(x))$};
+\node (D') at (3,-1) {$x' \in F(R(x'))$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$R(i) \eta_{c_1}$} (B)
+(C) edge node[above]{$R(o) \eta_{c_2}$} (B)
+(A') edge node[above]{$R(i') \eta_{c_1'}$} (B')
+(C') edge node[above]{$R(o') \eta_{c_2'}$} (B')
+(A) edge node [left]{$f$} (A')
+(B) edge node [left]{$R(\alpha)$} (B')
+(C) edge node [right]{$g$} (C');
+\end{tikzpicture}
+\]
+together with a morphism $\tau \maps F(R(\alpha))(x) \to x'$ in $F(R(x')) \subseteq \mathrm{X}$ which comes from the Grothendieck construction of the pseudofunctor $F \maps \A \to \Cat$.
+That $\mathbb{E}_0$ is a functor is clear.
+For $\mathbb{E}_1$, given two vertically composable 2-morphisms $M$ and $M'$ in $_L \lCsp(\X)$,
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$L(c_1)$};
+\node (B) at (1,0) {$x$};
+\node (C) at (2,0) {$L(c_2)$};
+\node (A') at (0,-1) {$L(c_1')$};
+\node (B') at (1,-1) {$x'$};
+\node (C') at (2,-1) {$L(c_2')$};
+\node (A'') at (0,-2) {$L(c_1')$};
+\node (B'') at (1,-2) {$x'$};
+\node (C'') at (2,-2) {$L(c_2')$};
+\node (A''') at (0,-3) {$L(c_1'')$};
+\node (B''') at (1,-3) {$x''$};
+\node (C''') at (2,-3) {$L(c_2'')$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i$} (B)
+(C) edge node[above]{$o$} (B)
+(A') edge node[above]{$i'$} (B')
+(C') edge node[above]{$o'$} (B')
+(A) edge node [left]{$L(f)$} (A')
+(B) edge node [left]{$\alpha$} (B')
+(C) edge node [right]{$L(g)$} (C')
+(A'') edge node[above]{$i'$} (B'')
+(C'') edge node[above]{$o'$} (B'')
+(A''') edge node[above]{$i''$} (B''')
+(C''') edge node[above]{$o''$} (B''')
+(A'') edge node [left]{$L(f')$} (A''')
+(B'') edge node [left]{$\alpha'$} (B''')
+(C'') edge node [right]{$L(g')$} (C''');
+\end{tikzpicture}
+\]
+their vertical composite $M'M$ is given by:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$L(c_1)$};
+\node (B) at (1,0) {$x$};
+\node (C) at (2,0) {$L(c_2)$};
+\node (A') at (0,-1) {$L(c_1'')$};
+\node (B') at (1,-1) {$x''$};
+\node (C') at (2,-1) {$L(c_2'')$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i$} (B)
+(C) edge node[above]{$o$} (B)
+(A') edge node[above]{$i''$} (B')
+(C') edge node[above]{$o''$} (B')
+(A) edge node [left]{$L(f'f)$} (A')
+(B) edge node [left]{$\alpha' \alpha$} (B')
+(C) edge node [right]{$L(g' g)$} (C');
+\end{tikzpicture}
+\]
+and the image of this 2-morphism $\mathbb{E}_1(M'M)$ is given by:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$c_1$};
+\node (B) at (1.5,0) {$R(x)$};
+\node (C) at (3,0) {$c_2$};
+\node (A') at (0,-1) {$c_1''$};
+\node (B') at (1.5,-1) {$R(x'')$};
+\node (C') at (3,-1) {$c_2''$};
+\node (D) at (4,0) {$x \in F(R(x))$};
+\node (D') at (4,-1) {$x'' \in F(R(x''))$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$R(i) \eta_{c_1}$} (B)
+(C) edge node[above]{$R(o) \eta_{c_2}$} (B)
+(A') edge node[above]{$R(i'') \eta_{c_1''}$} (B')
+(C') edge node[above]{$R(o'') \eta_{c_2''}$} (B')
+(A) edge node [left]{$f'f$} (A')
+(B) edge node [left]{$R(\alpha' \alpha)$} (B')
+(C) edge node [right]{$g'g$} (C');
+\end{tikzpicture}
+\]
+together with a morphism $\tau_{M' M} \maps F(R(\alpha' \alpha))(x) \to x''$ in $F(R(x''))$. On the other hand, the individual images $\mathbb{E}_1(M)$ and $\mathbb{E}_1(M')$ are given by:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$c_1$};
+\node (B) at (1.5,0) {$R(x)$};
+\node (C) at (3,0) {$c_2$};
+\node (A') at (0,-1) {$c_1'$};
+\node (B') at (1.5,-1) {$R(x')$};
+\node (C') at (3,-1) {$c_2'$};
+\node (D) at (4,0) {$x \in F(R(x))$};
+\node (D') at (4,-1) {$x' \in F(R(x'))$};
+\node (A'') at (0,-2) {$c_1'$};
+\node (B'') at (1.5,-2) {$R(x')$};
+\node (C'') at (3,-2) {$c_2'$};
+\node (A''') at (0,-3) {$c_1''$};
+\node (B''') at (1.5,-3) {$R(x'')$};
+\node (C''') at (3,-3) {$c_2''$};
+\node (D'') at (4,-2) {$x' \in F(R(x'))$};
+\node (D''') at (4,-3) {$x'' \in F(R(x''))$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$R(i) \eta_{c_1}$} (B)
+(C) edge node[above]{$R(o) \eta_{c_2}$} (B)
+(A') edge node[above]{$R(i') \eta_{c_1'}$} (B')
+(C') edge node[above]{$R(o') \eta_{c_2'}$} (B')
+(A) edge node [left]{$f$} (A')
+(B) edge node [left]{$R(\alpha)$} (B')
+(C) edge node [right]{$g$} (C')
+(A'') edge node[above]{$R(i') \eta_{c_1'}$} (B'')
+(C'') edge node[above]{$R(o') \eta_{c_2'}$} (B'')
+(A''') edge node[above]{$R(i'') \eta_{c_1''}$} (B''')
+(C''') edge node[above]{$R(o'') \eta_{c_2''}$} (B''')
+(A'') edge node [left]{$f'$} (A''')
+(B'') edge node [left]{$R(\alpha')$} (B''')
+(C'') edge node [right]{$g'$} (C''');
+\end{tikzpicture}
+\]
+together with morphisms $\tau_M \maps F(R(\alpha))(x) \to x'$ in $F(R(x'))$ and $\tau_{M'} \maps F(R(\alpha')(x') \to x''$ in $F(R(x''))$, respectively.
+The vertical composite $\mathbb{E}_1(M')\mathbb{E}_1(M)$ of the above two 2-morphisms is given by $\mathbb{E}_1(M'M)$ as $R$ is a functor and $\tau_{M'M}=\tau_{M'} \tau_M$.
+The functors $\mathbb{E}_0$ and $\mathbb{E}_1$ satisfy the equations $\mathbb{E}_0 S = S \mathbb{E}_1$ and $\mathbb{E}_0 T = T \mathbb{E}_1$.
+
+To see that this functor is essentially surjective, given a horizontal 1-cell in $F\lCsp$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$c_1$};
+\node (B) at (1,0) {$c$};
+\node (C) at (2,0) {$c_2$};
+\node (D) at (3,0) {$x \in F(c)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i$} (B)
+(C) edge node[above]{$o$} (B);
+\end{tikzpicture}
+\]
+we can find a 2-isomorphism in $F\lCsp$ whose codomain is the above horizontal 1-cell and whose domain is the image of the following horizontal 1-cell in $_L \lCsp(\X)$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$L(c_1)$};
+\node (B) at (1,0) {$x$};
+\node (C) at (2,0) {$L(c_2)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i'$} (B)
+(C) edge node[above]{$o'$} (B);
+\end{tikzpicture}
+\]
+with the 2-isomorphism in $F\lCsp$ given by:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$c_1$};
+\node (B) at (1,0) {$R(x)$};
+\node (C) at (2,0) {$c_2$};
+\node (A') at (0,-1) {$c_1$};
+\node (B') at (1,-1) {$c$};
+\node (C') at (2,-1) {$c_2$};
+\node (D) at (3,0) {$x \in F(R(x))$};
+\node (D') at (3,-1) {$x \in F(c)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$R(i') \eta_{c_1}$} (B)
+(C) edge node[above]{$R(o') \eta_{c_2}$} (B)
+(A') edge node[above]{$i$} (B')
+(C') edge node[above]{$o$} (B')
+(A) edge node [left]{$1$} (A')
+(B) edge node [left]{${(R(e) \eta_c)}^{-1}$} (B')
+(C) edge node [right]{$1$} (C');
+\end{tikzpicture}
+\]
+$$\tau \maps F({(R(e)\eta_c)}^{-1})(x) \to x$$
+where $e \maps L(c) \to x$ is given by the map from the trivial decoration on $c$ to $x \in F(c)$.
+%The object and arrow components $\mathbb{E}_0$ and $\mathbb{E}_1$ satisfy the equations $S \mathbb{E}_1 = \mathbb{E}_0 S$ and $T \mathbb{E}_1 = \mathbb{E}_0 T$.
+
+To show that the double functor $\mathbb{E}$ is fully faithful, we need to show that the map  $$\mathbb{E}_1 \maps _f { _L \lCsp(\X)}_g(M,N) \to {_{\mathbb{E}(f)} {F\lCsp}_{\mathbb{E}(g)}}(\mathbb{E}(M),\mathbb{E}(N))$$ is bijective for arbitrary vertical 1-morphisms $f$ and $g$ and horizontal 1-cells $M$ and $N$ of $_L \lCsp(\X)$.
+Consider a 2-morphism in $_L \lCsp(\X)$ with horizontal source and target $M$ and $N$, respectively and vertical source and target $f$ and $g$, respectively:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$L(c_1)$};
+\node (B) at (1,0) {$x$};
+\node (C) at (2,0) {$L(c_2)$};
+\node (A') at (0,-1) {$L(c_1')$};
+\node (B') at (1,-1) {$x'$};
+\node (C') at (2,-1) {$L(c_2')$};
+\node (D) at (1,0.5) {$M$};
+\node (E) at (-1,-0.5) {$f$};
+\node (F) at (1,-1.5) {$N$};
+\node (G) at (3,-0.5) {$g$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i$} (B)
+(C) edge node[above]{$o$} (B)
+(A') edge node[above]{$i'$} (B')
+(C') edge node[above]{$o'$} (B')
+(A) edge node [left]{$L(f)$} (A')
+(B) edge node [left]{$\alpha$} (B')
+(C) edge node [right]{$L(g)$} (C');
+\end{tikzpicture}
+\]
+Thus the set $$_f { _L \lCsp(\X)}_g(M,N)$$ consists of triples $$(f,\alpha,g)$$ rendering the above diagram commutative where $f$ and $g$ are morphisms of $\A$ and $\alpha$ is a morphism of $\X$.
+The image of the above 2-morphism under the double functor $\mathbb{E}$ is given by:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$c_1$};
+\node (B) at (1,0) {$R(x)$};
+\node (C) at (2,0) {$c_2$};
+\node (A') at (0,-1) {$c_1'$};
+\node (B') at (1,-1) {$R(x')$};
+\node (C') at (2,-1) {$c_2'$};
+\node (D) at (1,0.5) {$x \in F(R(x))$};
+\node (D') at (1,-1.5) {$x' \in F(R(x'))$};
+\node (E) at (1,1) {$\mathbb{E}(M)$};
+\node (F) at (-1,-0.5) {$\mathbb{E}(f)$};
+\node (G) at (1,-2) {$\mathbb{E}(N)$};
+\node (H) at (3,-0.5) {$\mathbb{E}(g)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$R(i)\eta_{c_1}$} (B)
+(C) edge node[above]{$R(o)\eta_{c_2}$} (B)
+(A') edge node[above]{$R(i')\eta_{c_1'}$} (B')
+(C') edge node[above]{$R(o')\eta_{c_2'}$} (B')
+(A) edge node [left]{$f$} (A')
+(B) edge node [left]{$R(\alpha)$} (B')
+(C) edge node [right]{$g$} (C');
+\end{tikzpicture}
+\]
+together with a morphism $\tau \maps F(R(\alpha))(x) \to x'$ of $F(R(x'))$.
+Thus the set $$_{\mathbb{E}(f)} {F\lCsp}_{\mathbb{E}(g)}(\mathbb{E}(M),\mathbb{E}(N))$$ consists of 4-tuples $$(f,R(\alpha),g,\tau)$$ rendering the above diagram commutative and where $f,g$ and $R(\alpha)$ are morphisms of $\A$ and $\tau$ is a morphism in $F(R(x'))$.
+The morphisms $R(\alpha) \maps R(x) \to R(x')$ and $\tau \maps F(R(\alpha))(x) \to x'$ together determine the morphism $\alpha \maps x \to x'$ in $\mathrm{X}$ and conversely; given two objects $x=(c,x \in F(c))$ and $x'=(c',x' \in F(c'))$ of $\X=\inta{F}$, a morphism from $\alpha \maps x \to x'$ is a pair $$(h \maps c \to c', \tau \maps F(h)(x) \to x')$$ where $h \maps c \to c'$ is given by $R(\alpha) \maps R(x) \to R(x')$.
+This shows that $\mathbb{E}$ is fully faithful.
+\textbf{At least in my favorite example...}
+\end{comment}
+
 %!!!Christina: Below, up to my next comment, is Kenny's earlier proof on the same thing.
@@
 Therefore $\mathbb{E} \maps \scsp{L_F}{\inta F} \to \dcsp{F}$ is a double equivalence, by \cref{ShulDubEquiv}.
-%!!!Christina: In fact, Christina and Kenny believe it is an isomorphism of double categories! Bijective on all levels of objects and morphisms...should we say?
+Christina: In fact, Christina and Kenny believe it is an isomorphism of double categories! Bijective on all levels of objects and morphisms...should we say?
 
@@
 
-\begin{defn}
+\begin{defn}\label{def:doublefun}
 Let $\mathbb{A}$ and $\mathbb{B}$ be pseudo double categories.
@@
 
-%ChristinaL Pretty sure the def below can be incorporated above, however got a bit lost in different notation. Kenny Fix?
+%!!! Christina: Pretty sure the def below can be incorporated above, however got a bit lost in different notation. Kenny Fix?
 \begin{defn}
@@
 \begin{thm}\label{ShulDubEquiv}
-A strong double functor $\mathbb{F} \maps \mathbb{A} \to \mathbb{X}$ is part of a double equivalence if and only if it is full, faithful and essentially surjective. {\chris on objects?}
+A strong double functor $\mathbb{F} \maps \mathbb{A} \to \mathbb{X}$ is part of a double equivalence if and only if it is full, faithful and essentially surjective.
 \end{thm}

### 2020-11-17 cospans.tex
changed \mathbf{D_0} to \lD_0, etc.

--- 2020-11-17 cospans.tex
@@
 
-This double category is in fact fibrant and so a result of Shulman \cite{Shul} allows us to extract from this symmetric monoidal double category $F \mathbb{C}$sp a symmetric monoidal bicategory $F \mathbf{Csp} \mapseqq H(F \lCsp)$ as the `horizontal edge bicategory' of the double category $F \mathbb{C}$sp.
+This double category is in fact fibrant and so a result of Shulman \cite{Shul} allows us to extract from this symmetric monoidal double category $F \mathbb{C}$sp a symmetric monoidal bicategory $F \mathbf{Csp}$ as the `horizontal bicategory' of the double category $F \mathbb{C}$sp.
 This bicategory $F \mathbf{Csp}$ has:
@@
 \begin{thm} \label{thm:equiv}
-Suppose $\ca{A}$ has finite colimits and $F\maps(\A,+) \to (\Cat,\times)$ is a symmetric lax monoidal pseudofunctor that factors through $\bicat{Rex}$ as an ordinary pseudofunctor.
-Then the symmetric monoidal double categories $F\lCsp$ of decorated cospans and $_L\lCsp(\inta F)$ of structured cospans are equivalent, where $L \maps \A \to \inta F$ is a left adjoint of the induced Grothendieck opfibration $U\maps \inta F \to \A$.
+Suppose $\A$ has finite colimits and $F \maps(\A,+) \to (\Cat,\times)$ is a symmetric lax monoidal pseudofunctor that factors through $\Rex$ as an ordinary pseudofunctor.
+Then the symmetric monoidal double category $F\lCsp$ of decorated cospans is equivalent to the symmetric monoidal double category $_L\lCsp(\inta F)$ of structured cospans, where $L \maps \A \to \inta F$ is the left adjoint of the induced Grothendieck opfibration $U \maps \inta F \to \A$.
 \end{thm}
@@
 
-Notice a subtlety in the above formulation: \cref{lem:MonGroth} provides a specifically induced monoidal structure on the fibres which becomes \cref{eq:explicitstructure1} in the cocartesian base case.
-If that fibrewise monoidal structure happens to itself be cocartesian, then it is necessarily isomorphic to \emph{any} other cocartesian structure on the fibres, by universal property of colimits.
-Therefore, we can simplify the above formulation to the one of the very \cref{thm:equiv} without having to specify that the structures came from monoidality of the pseudofunctor.
-DOES THIS MAKE SENSE TO ALL??
-
 On a highly related note, in what follows we are also interested in the existence of a left adjoint $L_F$ to an induced monoidal opfibration; the following result provides sufficient conditions for that.
+%, which go hand-in-hand with \cref{cor:fcocMonGroth} and \cref{lem:fibrewiselimits}.
 
@@
 \begin{equation}\label{eq:initialinfibre}
-\mathbf{1}\xrightarrow{\mu_0}F(0_\A)\xrightarrow{F(u_a)}F(a) 
+\mathbf{1}\xrightarrow{\phi_0}F(0_\A)\xrightarrow{F(u_a)}F(a) 
 \end{equation}
@@
 \begin{defn}
-Given a set $\La$ of \define{labels}, an $\La$-\define{graph} is a graph $s,t\maps E\to N$
+Given a set $\La$ of \define{labels}, an \define{$\La$-graph} is a graph $s,t\maps E\to N$
  equipped with a function $\ell \maps E \to \La$.
@@
 ideas of that section from graphs to $\La$-graphs.   Everything works the same way, 
-but following previous work \cite{BCR} we call an open $\La$-graph an $\La$-\define{circuit}.
+but following previous work \cite{BCR} we call an open $\La$-graph an \define{$\La$-circuit}.
 
@@
 \item a morphism is an isomorphism class of $\La$-circuits, where an
-$\La$-\define{circuit} is a cospan in $\Graph_\La$ of this form:
+\define{$\La$-circuit} is a cospan in $\Graph_\La$ of this form:
 \[
@@
 \subsection{Double categories}\label{sec:doublecats}
-%!!! Christina: Kenny, would you mind cleaning this section up to? I don't believe we need the full fledged definitions here by the way.
-
-Before formally defining `pseudo double category', it is helpful to have the following picture in mind. A pseudo double category has 2-morphisms shaped like:
-
+
+Before formally defining a `double category', it is helpful to have the following picture in mind. A double category has 2-morphisms shaped like:
 \[
@@
 \]
-
-We call $A, B, C$ and $D$ \textbf{objects} or \textbf{0-cells}, $f$ and $g$ \textbf{vertical 1-morphisms}, $M$ and $N$ \textbf{horizontal 1-cells} and $a$ a \textbf{2-morphism}.
-Note that a vertical 1-morphism is a morphism between 0-cells and a 2-morphism is a morphism between horizontal 1-cells.
-We will denote both kinds of morphisms and horizontal 1-cells as a single arrow, namely `$\to$'.
+We call $A, B, C$ and $D$ \textbf{objects}, $f$ and $g$ \textbf{vertical 1-morphisms}, $M$ and $N$ \textbf{horizontal 1-cells} and $a$ a \textbf{2-morphism}.
+Note that a vertical 1-morphism is a morphism between objects and a 2-morphism is a morphism between horizontal 1-cells.
+%We will denote both kinds of morphisms and horizontal 1-cells as a single arrow, namely `$\to$'.
 We follow the notation of Shulman \cite{Shulman2008} with the following definitions.
@@
 \begin{defn}\label{defn:double_category}
-A \textbf{pseudo double category} $\lD$, or $\textbf{double category}$ for short, consists of a category of objects $\mathbf{D_{0}}$ and a category of arrows $\mathbf{D_1}$ with the following functors
+A \textbf{pseudo double category} $\lD$, or $\textbf{double category}$ for short, consists of a category of objects $\lD_0$ and a category of arrows $\lD_1$ with the following functors
 \begin{center}
-$U\maps \mathbf{D_{0}} \to \mathbf{D_1}$\\
-$S,T \maps \mathbf{D_1} \rightrightarrows \mathbf{D_{0}}$\\
-$\odot \maps \mathbf{D_1} \times_{\mathbf{D_{0}}} \mathbf{D_1} \to \mathbf{D_1}$ (where the pullback is taken over $\mathbf{D_1} \xrightarrow[]{T} \mathbf{D_{0}} \xleftarrow[]{S} \mathbf{D_1}$) \\
+$U\maps \lD_0 \to \lD_1$\\
+$S,T \maps \lD_1 \rightrightarrows \lD_0$\\
+$\odot \maps \lD_1 \times_{\lD_0} \lD_1 \to \lD_1$ (where the pullback is taken over $\lD_1 \xrightarrow[]{T} \lD_0 \xleftarrow[]{S} \lD_1$) \\
 \end{center}
@@
 such that $S(\alpha), S(\lambda), S(\rho), T(\alpha), T(\lambda)$ and $T(\rho)$ are all identities and that the coherence axioms of a monoidal category are satisfied.
-Following the notation of Shulman, objects of $\mathbf{D_{0}}$ are called $\textbf{0-cells}$ and morphisms of $\mathbf{D_{0}}$ are called $\textbf{vertical 1-morphisms}$.
-Objects of $\mathbf{D_1}$ are called $\textbf{horizontal 1-cells}$ and morphisms of $\mathbf{D_1}$ are called $\textbf{2-morphisms}$.
-The morphisms of $\mathbf{D_{0}}$, which are vertical 1-morphisms, will be denoted $f \maps A \to C$ and we denote a 1-cell $M$ with $S(M)=A,T(M)=B$ by $M \maps A \to B$.
-Then a 2-morphism $a \maps M \to N$ of $\mathbf{D_1}$ with $S(a)=f,T(a)=g$ would look like:
+Following the notation of Shulman, objects of $\lD_0$ are called $\textbf{0-cells}$ and morphisms of $\lD_0$ are called $\textbf{vertical 1-morphisms}$.
+Objects of $\lD_1$ are called $\textbf{horizontal 1-cells}$ and morphisms of $\lD_1$ are called $\textbf{2-morphisms}$.
+The morphisms of $\lD_1$, which are vertical 1-morphisms, will be denoted $f \maps A \to C$ and we denote a 1-cell $M$ with $S(M)=A,T(M)=B$ by $M \maps A \to B$.
+Then a 2-morphism $a \maps M \to N$ of $\lD_1$ with $S(a)=f,T(a)=g$ would look like:
 \[
@@
 \end{defn}
-
-The key difference between a `strict' double category and a pseudo double category is that in a pseudo double category, horizontal composition is associative and unital only up to natural isomorphism.
+A 2-morphism where $f$ and $g$ are identities is called a \textbf{globular 2-morphism}.
+
+%The key difference between a `strict' double category and a pseudo double category is that in a pseudo double category, horizontal composition is associative and unital only up to natural isomorphism.
 Equivalently, as a double category can be viewed as a category internal to $\Cat$, we can view a pseudo double category as a category `weakly' internal to $\Cat$.
@@
 
-\begin{defn}
-A 2-morphism where $f$ and $g$ are identities is called a \textbf{globular 2-morphism}.
-\end{defn}
-
-\begin{defn}
-Let $\lD$ be a pseudo double category.
+%\begin{defn}
+%Let $\lD$ be a pseudo double category.
 Then the $\textbf{horizontal bicategory}$ of $\lD$, which we denote as $H(\lD)$, is the bicategory consisting of objects of $\lD$, morphisms that are horizontal 1-cells of $\lD$ and 2-morphisms that are globular 2-morphisms of $\lD$.
-\end{defn}
+%\end{defn}
 
@@
 \begin{enumerate}
-\item $\mathbf{D_{0}}$ and $\mathbf{D_1}$ are both monoidal categories.
-\item If $I$ is the monoidal unit of $\mathbf{D_{0}}$, then $U_I$ is the
-  monoidal unit of $\mathbf{D_1}$.
+\item $\lD_0$ and $\lD_1$ are both monoidal categories.
+\item If $I$ is the monoidal unit of $\lD_0$, then $U_I$ is the
+  monoidal unit of $\lD_1$.
 \item The functors $S$ and $T$ are strict monoidal, i.e.\ $S(M\ten N)

### 2020-11-17 cospans.tex

--- 2020-11-17 cospans.tex
@@
 
-Before formally defining `pseudo double category', it is helpful to have the following picture in mind. A pseudo double category has 2-morphisms shaped like:
-
+Before formally defining a `double category', it is helpful to have the following picture in mind. A double category has 2-morphisms shaped like:
 \[

### 2020-11-17 cospans.tex
changed mus to phis

@@
 The second equivalence was also earlier observed by Shulman \cite{Shulman2008}.
-In more detail, if $(\mu,\mu_0)$ is the lax monoidal structure of the pseudofunctor $F$ as recalled in \cref{sec:2cats}, each fibre category $\X_a=F(a)$ obtains a monoidal structure via
+In more detail, if $(\phi,\phi_0)$ is the lax monoidal structure of the pseudofunctor $F$ as recalled in \cref{sec:2cats}, each fibre category $\X_a=F(a)$ obtains a monoidal structure via
 \begin{equation}\label{eq:explicitstructure1}
-\otimes_a\maps F(a)\times F(a)\xrightarrow{\mu_{a,a}}F(a+a)\xrightarrow{F(\nabla)}F(a),\quad
-I_a\maps\mathbf{1}\xrightarrow{\mu_0}F(0)\xrightarrow{F(!)}F(a)
+\otimes_a\maps F(a)\times F(a)\xrightarrow{\phi_{a,a}}F(a+a)\xrightarrow{F(\nabla)}F(a),\quad
+I_a\maps\mathbf{1}\xrightarrow{\phi_0}F(0)\xrightarrow{F(!)}F(a)
 \end{equation}
@@
 
-Finally, if the original pseudofunctor is in fact lax monoidal $(F,\mu,\mu_0)$, the monoidal Grothendieck construction of \cref{lem:MonGroth} in the cocartesian case expresses $\bot_a$ as follows by \cref{eq:explicitstructure1}:
+Finally, if the original pseudofunctor is in fact lax monoidal $(F,\phi,\phi_0)$, the monoidal Grothendieck construction of \cref{lem:MonGroth} in the cocartesian case expresses $\bot_a$ as follows by \cref{eq:explicitstructure1}:
 \begin{equation}\label{eq:initialinfibre}
-\mathbf{1}\xrightarrow{\mu_0}F(0_\A)\xrightarrow{F(u_a)}F(a) 
+\mathbf{1}\xrightarrow{\phi_0}F(0_\A)\xrightarrow{F(u_a)}F(a) 
 \end{equation}
@@
 describes the construction of the adjunction from the original $F$.
-Explicitly, the left adjoint picks the initial object in the finitely cocomplete fibre $L(a)=(a,\bot_a)$, also expressed as $F(u_a)\circ\mu_0(*)$ according to \cref{eq:initialinfibre} for $(\mu,\mu_0)$ the monoidal structure of $F$.
+Explicitly, the left adjoint picks the initial object in the finitely cocomplete fibre $L(a)=(a,\bot_a)$, also expressed as $F(u_a)\circ\phi_0(*)$ according to \cref{eq:initialinfibre} for $(\phi,\phi_0)$ the monoidal structure of $F$.
 
@@
 A \define{braided} monoidal bicategory comes with a pseudonatural equivalence $\beta_{a,b}\maps a\ot b\to b\ot a$ and appropriate invertible modifications; it is \define{sylleptic} if there is an appropriate invertible modification $1_{a\ot b}\Rrightarrow\beta_{b,a}\circ\beta_{a,b}$ and it is \define{symmetric} if one further axiom holds.
-A \define{lax monoidal} pseudofunctor between monoidal bicategories $F\maps\bicat{A}\to\bicat{B}$ is a pseudofunctor equipped with pseudonatural transformations with components $\mu_{a,b}\maps Fa\otimes Fb\to F(a\otimes b)$ and $\mu_0\maps I\to FI$ along with coherent invertible modifications for associativity and unitality.
+A \define{lax monoidal} pseudofunctor between monoidal bicategories $F\maps\bicat{A}\to\bicat{B}$ is a pseudofunctor equipped with pseudonatural transformations with components $\phi_{a,b}\maps Fa\otimes Fb\to F(a\otimes b)$ and $\phi_0\maps I\to FI$ along with coherent invertible modifications for associativity and unitality.
 This is commonly also called `weak monoidal' pseudofunctor.
-A \define{braided lax monoidal} pseudofunctor between braided monoidal bicategories comes with an appropriate invertible modification with components $F(\beta_{a,b})\circ \mu_{a,b}\cong\mu_{b,a}\circ \beta_{Fa,Fb}$; a \define{sylleptic lax monoidal} pseudofunctor satisfies one extra condition and a \define{symmetric lax monoidal} pseudofunctor between symmetric monoidal bicategories is just a sylleptic one.
+A \define{braided lax monoidal} pseudofunctor between braided monoidal bicategories comes with an appropriate invertible modification with components $F(\beta_{a,b})\circ \phi_{a,b}\cong\phi_{b,a}\circ \beta_{Fa,Fb}$; a \define{sylleptic lax monoidal} pseudofunctor satisfies one extra condition and a \define{symmetric lax monoidal} pseudofunctor between symmetric monoidal bicategories is just a sylleptic one.
 RIGHT???

### 2020-11-17 cospans.tex
shortened appendix a bit more

--- 2020-11-17 cospans.tex
@@
 
-Following the notation of Shulman \cite{Shulman2010}, given a double category $\mathbb{A}$, we write $_f \mathbb{A}_g(M,N)$ for the set of 2-morphisms in $\mathbb{A}$ of the form:
-\[
-  \xymatrix@-.5pc{
-    A \ar[r]|{|}^{M}  \ar[d]_f \ar@{}[dr]|{\Downarrow a}&
-    B\ar[d]^g\\
-    C \ar[r]|{|}_N & D
-  }
-\]
-We call $M$ and $N$ the \define{horizontal source and target} of the 2-morphism $a$, respectively, and likewise we call $f$ and $g$ the \define{vertical source and target} of the 2-morphism $a$, respectively.
+%Following the notation of Shulman \cite{Shulman2010}, given a double category $\mathbb{A}$, we write $_f \mathbb{A}_g(M,N)$ for the set of 2-morphisms in $\mathbb{A}$ of the form:
+%\[
+%  \xymatrix@-.5pc{
+%   A \ar[r]|{|}^{M}  \ar[d]_f \ar@{}[dr]|{\Downarrow a}&
+%    B\ar[d]^g\\
+%    C \ar[r]|{|}_N & D
+%  }
+%\]
+%We call $M$ and $N$ the \define{horizontal source and target} of the 2-morphism $a$, respectively, and likewise we call $f$ and $g$ the \define{vertical source and target} of the 2-morphism $a$, respectively.
 Thus $_f \mathbb{A}_g(M,N)$ denotes the set of 2-morphisms in $\mathbb{A}$ with horizontal source and target $M$ and $N$ and vertical source and target $f$ and $g$.
@@
 Formally, two strong double functors between two double categories form a \emph{double equivalence} if ...
-%{\chris their two-way composite is isomorphic to the identity, better expressed, possibly in a definition environment}. 
-Similarly to ordinary equivalence of categories, [Shulman,7.8] allows us to use the following equivalent characterization.
+%{\chris their two-way composite is isomorphic to the identity, better expressed, possibly in a definition environment}.   Say this or leave it out entirely!!!
+Similarly to ordinary equivalence of categories, \cite[Theorem 7.8]{Shulman2010} allows us to use the following equivalent characterization.
 

### 2020-11-17 cospans.tex
Cleaning up Theorem 2.2

@@
 
-Lastly, we require two globular 2-morphisms $\chi \colon (M_1 \otimes M_1) \odot (M_2 \otimes N_2) \to (M_1 \odot M_2) \otimes (N_1 \odot N_2)$ and $\mu \colon U_{a \otimes b} \to U_a \otimes U_b$, the first of which relates the double functors $\otimes$ and $\odot$ and the second of which relates the double functors $\otimes$ and $U$.
+Lastly, we require two globular 2-morphisms $\chi \colon (M_1 \otimes N_1) \odot (M_2 \otimes N_2) \to (M_1 \odot M_2) \otimes (N_1 \odot N_2)$ and $\mu \colon U_{a \otimes b} \to U_a \otimes U_b$, the first of which relates the double functors $\otimes$ and $\odot$ and the second of which relates the double functors $\otimes$ and $U$.
 The latter of these is easy to see: given two objects $a$ and $b$ in $F\lCsp_0=\A$, $\mu$ is given by the identity map of cospans in $\A$:
@@
 \]
+If we first tensor $M_1$ and $N_1$ as well as $M_2$ and $N_2$ and then compose these two, we obtain $(M_1 \otimes N_1) \odot (M_2 \otimes N_2)$, which is given by:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$a+a'$};
+\node (B) at (2.5,0) {$(m_1+n_1)+_{b+b'}(m_2+n_2)$};
+\node (C) at (5,0) {$c+c'$};
+\node (D) at (2.5,-0.5) {$(x_1+y_1)\odot(x_2+y_2) \in F((m_1+n_1)+_{b+b'}(m_2+n_2))$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$\psi j (i_1+i_1')$} (B)
+(C) edge node[above]{$\psi j (o_2 + o_2')$} (B);
+\end{tikzpicture}
+\]
+where the decoration $(x_1+y_1) \odot (x_2+y_2) \in F((m_1+n_1)+_{b+b'}(m_2+n_2))$ is given by:
+%$$\scriptscriptstyle{1 \xrightarrow{(\lambda^{-1} \times \lambda^{-1})\lambda^{-1}} (1 \times 1) \times (1 \times 1) \xrightarrow{(x_1 \times y_1) \times (x_2 \times y_2)} (F(m_1) \times F(n_1)) \times (F(m_2) \times F(n_2)) \xrightarrow{\phi_{m_1,n_1} \times \phi_{m_2,n_2}} F(m_1+n_1) \times F(m_2+n_2)} \xrightarrow{\phi_{m_1+n_1,m_2+n_2}} F((m_1+n_1)+(m_2+n_2)) \xrightarrow{F(\psi)} F((m_1+n_1)+_{b+b'}(m_2+n_2))$$
+$$\scriptstyle{1 \xrightarrow{} (F(m_1) \times F(n_1)) \times (F(m_2) \times F(n_2)) \xrightarrow{\phi_{m_1,n_1} \times \phi_{m_2,n_2}} F(m_1+n_1) \times F(m_2+n_2)} \xrightarrow{\phi_{m_1+n_1,m_2+n_2}} F((m_1+n_1)+(m_2+n_2)) \xrightarrow{F(\psi)} F((m_1+n_1)+_{b+b'}(m_2+n_2))$$
+where the first arrow is given by $$1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{\lambda^{-1} \times \lambda^{-1}} (1 \times 1) \times (1 \times 1) \xrightarrow{(x_1 \times y_1) \times (x_2 \times y_2)} (F(m_1) \times F(n_1)) \times (F(m_2) \times F(n_2)).$$
+%\[
+%\begin{tikzpicture}[scale=1.5]
+%\node (A) at (0,0) {$1$};
+%\node (B) at (0,-1) {$1 \times 1$};
+%\node (C) at (0,-2) {$(1 \times 1) \times (1 \times 1)$};
+%\node (D) at (0,-3) {$(F(m_1) \times F(n_1)) \times (F(m_2) \times F(n_2))$};
+%\node (E) at (0,-4) {$F(m_1+n_1) \times F(m_2+n_2)$};
+%\node (F) at (0,-5) {$F((m_1+n_1)+(m_2+n_2))$};
+%\node (G) at (0,-6) {$F((m_1+n_1)+_{b+b'}(m_2+n_2))$};
+%\path[->,font=\scriptsize,>=angle 90]
+%(A) edge node[left]{$\lambda^{-1}$} (B)
+%(B) edge node[left]{$\lambda^{-1} \times \lambda^{-1}$} (C)
+%(C) edge node[left]{$(x_1 \times y_1) \times (x_2 \times y_2)$} (D)
+%(D) edge node[left]{$\phi_{m_1,n_1} \times \phi_{m_2,n_2}$} (E)
+%(E) edge node[left]{$\phi_{m_1+n_1,m_2+n_2}$} (F)
+%(F) edge node[left]{$F(j_{m_1+n_1,m_2+n_2})$} (G);
+%\end{tikzpicture}
+%\]
+Interchanging the order in which we tensor and compose, we obtain $(M_1 \odot M_2) \otimes (N_1 \odot N_2)$, which is given by:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$a+a'$};
+\node (B) at (2.5,0) {$(m_1+_{b} m_2) + (n_1 +_{b'} n_2)$};
+\node (C) at (5,0) {$c+c'$};
+\node (D) at (2.5,-0.5) {$(x_1 \odot x_2) + (y_1 \odot y_2) \in F((m_1+_{b}m_2)+(n_1+_{b'}n_2))$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$(\psi j i_1)+(\psi j i_1')$} (B)
+(C) edge node[above]{$(\psi j o_2)+(\psi j o_2')$} (B);
+\end{tikzpicture}
+\]
+where the decoration $(x_1 \odot x_2) + (y_1 \odot y_2) \in F((m_1+_{b}m_2)+(n_1+_{b'}n_2))$ is given by:
+%$$\scriptscriptstyle{1 \xrightarrow{(\lambda^{-1} \times \lambda^{-1})\lambda^{-1}} (1 \times 1) \times (1 \times 1) \xrightarrow{(x_1 \times y_1) \times (x_2 \times y_2)} (F(m_1) \times F(n_1)) \times (F(m_2) \times F(n_2)) \xrightarrow{\phi_{m_1,n_1} \times \phi_{m_2,n_2}} F(m_1+n_1) \times F(m_2+n_2) \xrightarrow{F(\psi) \times F(\psi)} F(m_1 +_b m_2) \times F(n_1+_{b'}n_2) \xrightarrow{\phi_{m_1+_b m_2,n_1+_{b'}n_2}} F((m_1+_b m_2)+(n_1+_{b'}n_2))}$$
+$$\scriptstyle{1 \xrightarrow{} (F(m_1) \times F(n_1)) \times (F(m_2) \times F(n_2)) \xrightarrow{\phi_{m_1,n_1} \times \phi_{m_2,n_2}} F(m_1+n_1) \times F(m_2+n_2) \xrightarrow{F(\psi) \times F(\psi)} F(m_1 +_b m_2) \times F(n_1+_{b'}n_2) \xrightarrow{\phi_{m_1+_b m_2,n_1+_{b'}n_2}} F((m_1+_b m_2)+(n_1+_{b'}n_2))}$$
+with the first arrow being the same as the first arrow in the previous composite.
+%\[
+%\begin{tikzpicture}[scale=1.5]
+%\node (A) at (0,0) {$1$};
+%\node (B) at (0,-1) {$1 \times 1$};
+%\node (C) at (0,-2) {$(1 \times 1) \times (1 \times 1)$};
+%\node (D) at (0,-3) {$(F(m_1) \times F(m_2)) \times (F(n_1) \times F(n_2))$};
+%\node (E) at (0,-4) {$F(m_1+m_2) \times F(n_1+n_2)$};
+%\node (F) at (0,-5) {$F(m_1+_{b}m_2) \times F(n_1+_{b'}n_2)$};
+%\node (G) at (0,-6) {$F((m_1+_{b}m_2)+(n_1+_{b'}n_2))$};
+%\path[->,font=\scriptsize,>=angle 90]
+%(A) edge node[left]{$\lambda^{-1}$} (B)
+%(B) edge node[left]{$\lambda^{-1} \times \lambda^{-1}$} (C)
+%(C) edge node[left]{$(x_1 \times x_2) \times (y_1 \times y_2)$} (D)
+%(D) edge node[left]{$\phi_{m_1,m_2} \times \phi_{n_1,n_2}$} (E)
+%(E) edge node[left]{$F(j_{m_1,m_2}) \times F(j_{n_1,n_2})$} (F)
+%(F) edge node[left]{$\phi_{m_1+_{b}m_2,n_1+_{b'}n_2}$} (G);
+%\end{tikzpicture}
+%\]
+The globular 2-morphism $\chi \colon (M_1 \otimes N_1) \odot (M_2 \otimes N_2) \to (M_1 \odot M_2) \otimes (N_1 \odot N_2)$ is then given by the map of cospans in $\A$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0.5) {$a+a'$};
+\node (A') at (0,-0.5) {$a+a'$};
+\node (B) at (2.5,0.5) {$(m_1+n_1)+_{b+b'}(m_2+n_2)$};
+\node (C) at (5,0.5) {$c+c'$};
+\node (C') at (5,-0.5) {$c+c'$};
+\node (D) at (2.5,-0.5) {$(m_1+_{b}m_2)+(n_1+_{b'}n_2)$};
+\node (E) at (7.5,0.5) {$\scriptstyle{(x_1+y_1) \odot (x_2+y_2) \in F((m_1+n_1)+_{b+b'}(m_2+n_2))}$};
+\node (F) at (7.5,-0.5) {$\scriptstyle{(x_1 \odot x_2)+(y_1 \odot y_2) \in F((m_1+_{b}m_2)+(n_1+_{b'}n_2))}$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$\psi j(i_1+i_1')$} (B)
+(C) edge node[above]{$\psi j(o_2 + o_2')$} (B)
+(A) edge node[left]{$1$} (A')
+(C) edge node[right]{$1$} (C')
+(A') edge node [above]{$(\psi j i_1')+(\psi j i_1)$} (D)
+(C') edge node [above]{$(\psi j o_2)+(\psi j o_2')$} (D)
+(B) edge node [left] {$\hat{\chi}$} (D);
+\end{tikzpicture}
+\]
+together with decoration isomorphism $\tau_{\chi} \maps F(\hat{\chi})((x_1+y_1)\odot(x_2+y_2)) \to (x_1 \odot x_2)+(y_1 \odot y_2)$
+where $\hat{\chi}$ is the same interchange map $\chi$ for the symmetric double category $\lCsp(\A)$ given by the universal map between the colimit of the same diagram obtained in two different ways.
+This completes the description of the globular 2-morphisms $\chi$ and $\mu$, and the description of all of the structure of the symmetric monoidal double category $F\lCsp$.
+
+The remaining properties are coherence diagrams that make use of these maps $\chi$ and $\mu$, the previously defined symmetric monoidal structure maps $\alpha,\lambda,\rho$ and $\beta$ and the double category structure functors $U$ and $\odot$.
+We exhibit one of these diagrams to give the reader a sense of how they are verified, with more details able to be found in the second author's thesis \cite{CourserThesis}.
+The coherence diagram that we will check is given by:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$(M_1 \odot M_2) \otimes (N_1 \odot N_2)$};
+\node (B) at (3,0) {$(N_1 \odot N_2) \otimes (M_1 \odot M_2)$};
+\node (C) at (0,-.75) {$(M_1 \otimes N_1) \odot (M_2 \otimes N_2)$};
+\node (D) at (3,-.75) {$(N_1 \otimes M_1) \odot (N_2 \otimes M_2)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$\beta$} (B)
+(B) edge node[right]{$\chi$} (D)
+(A) edge node[left]{$\chi$} (C)
+(C) edge node[above]{$\beta \odot \beta$} (D);
+\end{tikzpicture}
+\]
+which expresses that the braiding is a transformation of double categories.
+
+\noindent
 \textbf{In progress}

### 2020-11-17 cospans.tex
fixed a typo

@@
 
-This double category is in fact fibrant and so a result of Shulman \cite{Shul} allows us to extract from this symmetric monoidal double category $F \mathbb{C}$sp a symmetric monoidal bicategory $F \mathbf{Csp}$ as the `horizontal bicategory' of the double category $F \mathbb{C}$sp.
+This double category is in fact fibrant and so a result of Shulman \cite{Shul} allows us to extract from this symmetric monoidal double category $F \mathbb{C}$sp a symmetric monoidal bicategory $F \mathbf{Csp} \mapseqq H(F \lCsp)$ as the `horizontal edge bicategory' of the double category $F \mathbb{C}$sp.
 This bicategory $F \mathbf{Csp}$ has:
@@
 
-Lastly, we require two globular 2-morphisms $\chi \colon (M_1 \otimes N_1) \odot (M_2 \otimes N_2) \to (M_1 \odot M_2) \otimes (N_1 \odot N_2)$ and $\mu \colon U_{a \otimes b} \to U_a \otimes U_b$, the first of which relates the double functors $\otimes$ and $\odot$ and the second of which relates the double functors $\otimes$ and $U$.
+Lastly, we require two globular 2-morphisms $\chi \colon (M_1 \otimes N_1) \odot (M_2 \otimes N_2) \to (M_1 \odot M_2) \otimes (N_1 \odot N_2)$ and $\mu \colon U_{a \otimes b} \to U_a \otimes U_b$, the first of which relates the double functor $\otimes$ with the functor $\odot$ and the second of which relates the double functor $\otimes$ with the functor $U$.
 The latter of these is easy to see: given two objects $a$ and $b$ in $F\lCsp_0=\A$, $\mu$ is given by the identity map of cospans in $\A$:
@@
 The second equivalence was also earlier observed by Shulman \cite{Shulman2008}.
-In more detail, if $(\phi,\phi_0)$ is the lax monoidal structure of the pseudofunctor $F$ as recalled in \cref{sec:2cats}, each fibre category $\X_a=F(a)$ obtains a monoidal structure via
+In more detail, if $(\mu,\mu_0)$ is the lax monoidal structure of the pseudofunctor $F$ as recalled in \cref{sec:2cats}, each fibre category $\X_a=F(a)$ obtains a monoidal structure via
 \begin{equation}\label{eq:explicitstructure1}
-\otimes_a\maps F(a)\times F(a)\xrightarrow{\phi_{a,a}}F(a+a)\xrightarrow{F(\nabla)}F(a),\quad
-I_a\maps\mathbf{1}\xrightarrow{\phi_0}F(0)\xrightarrow{F(!)}F(a)
+\otimes_a\maps F(a)\times F(a)\xrightarrow{\mu_{a,a}}F(a+a)\xrightarrow{F(\nabla)}F(a),\quad
+I_a\maps\mathbf{1}\xrightarrow{\mu_0}F(0)\xrightarrow{F(!)}F(a)
 \end{equation}
@@
 
-Finally, if the original pseudofunctor is in fact lax monoidal $(F,\phi,\phi_0)$, the monoidal Grothendieck construction of \cref{lem:MonGroth} in the cocartesian case expresses $\bot_a$ as follows by \cref{eq:explicitstructure1}:
+Finally, if the original pseudofunctor is in fact lax monoidal $(F,\mu,\mu_0)$, the monoidal Grothendieck construction of \cref{lem:MonGroth} in the cocartesian case expresses $\bot_a$ as follows by \cref{eq:explicitstructure1}:
 \begin{equation}\label{eq:initialinfibre}
-\mathbf{1}\xrightarrow{\phi_0}F(0_\A)\xrightarrow{F(u_a)}F(a) 
+\mathbf{1}\xrightarrow{\mu_0}F(0_\A)\xrightarrow{F(u_a)}F(a) 
 \end{equation}
@@
 describes the construction of the adjunction from the original $F$.
-Explicitly, the left adjoint picks the initial object in the finitely cocomplete fibre $L(a)=(a,\bot_a)$, also expressed as $F(u_a)\circ\phi_0(*)$ according to \cref{eq:initialinfibre} for $(\phi,\phi_0)$ the monoidal structure of $F$.
+Explicitly, the left adjoint picks the initial object in the finitely cocomplete fibre $L(a)=(a,\bot_a)$, also expressed as $F(u_a)\circ\mu_0(*)$ according to \cref{eq:initialinfibre} for $(\mu,\mu_0)$ the monoidal structure of $F$.
 
@@
 A \define{braided} monoidal bicategory comes with a pseudonatural equivalence $\beta_{a,b}\maps a\ot b\to b\ot a$ and appropriate invertible modifications; it is \define{sylleptic} if there is an appropriate invertible modification $1_{a\ot b}\Rrightarrow\beta_{b,a}\circ\beta_{a,b}$ and it is \define{symmetric} if one further axiom holds.
-A \define{lax monoidal} pseudofunctor between monoidal bicategories $F\maps\bicat{A}\to\bicat{B}$ is a pseudofunctor equipped with pseudonatural transformations with components $\phi_{a,b}\maps Fa\otimes Fb\to F(a\otimes b)$ and $\phi_0\maps I\to FI$ along with coherent invertible modifications for associativity and unitality.
+A \define{lax monoidal} pseudofunctor between monoidal bicategories $F\maps\bicat{A}\to\bicat{B}$ is a pseudofunctor equipped with pseudonatural transformations with components $\mu_{a,b}\maps Fa\otimes Fb\to F(a\otimes b)$ and $\mu_0\maps I\to FI$ along with coherent invertible modifications for associativity and unitality.
 This is commonly also called `weak monoidal' pseudofunctor.
-A \define{braided lax monoidal} pseudofunctor between braided monoidal bicategories comes with an appropriate invertible modification with components $F(\beta_{a,b})\circ \phi_{a,b}\cong\phi_{b,a}\circ \beta_{Fa,Fb}$; a \define{sylleptic lax monoidal} pseudofunctor satisfies one extra condition and a \define{symmetric lax monoidal} pseudofunctor between symmetric monoidal bicategories is just a sylleptic one.
+A \define{braided lax monoidal} pseudofunctor between braided monoidal bicategories comes with an appropriate invertible modification with components $F(\beta_{a,b})\circ \mu_{a,b}\cong\mu_{b,a}\circ \beta_{Fa,Fb}$; a \define{sylleptic lax monoidal} pseudofunctor satisfies one extra condition and a \define{symmetric lax monoidal} pseudofunctor between symmetric monoidal bicategories is just a sylleptic one.
 RIGHT???
@@
 
-Before formally defining a `double category', it is helpful to have the following picture in mind. A double category has 2-morphisms shaped like:
+Before formally defining `pseudo double category', it is helpful to have the following picture in mind. A pseudo double category has 2-morphisms shaped like:
+
 \[
@@
 \]
-We call $A, B, C$ and $D$ \textbf{objects}, $f$ and $g$ \textbf{vertical 1-morphisms}, $M$ and $N$ \textbf{horizontal 1-cells} and $a$ a \textbf{2-morphism}.
-Note that a vertical 1-morphism is a morphism between objects and a 2-morphism is a morphism between horizontal 1-cells.
-%We will denote both kinds of morphisms and horizontal 1-cells as a single arrow, namely `$\to$'.
+
+We call $A, B, C$ and $D$ \textbf{objects} or \textbf{0-cells}, $f$ and $g$ \textbf{vertical 1-morphisms}, $M$ and $N$ \textbf{horizontal 1-cells} and $a$ a \textbf{2-morphism}.
+Note that a vertical 1-morphism is a morphism between 0-cells and a 2-morphism is a morphism between horizontal 1-cells.
+We will denote both kinds of morphisms and horizontal 1-cells as a single arrow, namely `$\to$'.
 We follow the notation of Shulman \cite{Shulman2008} with the following definitions.
@@
 \begin{defn}\label{defn:double_category}
-A \textbf{pseudo double category} $\lD$, or $\textbf{double category}$ for short, consists of a category of objects $\lD_0$ and a category of arrows $\lD_1$ with the following functors
+A \textbf{pseudo double category} $\lD$, or $\textbf{double category}$ for short, consists of a category of objects $\mathbf{D_{0}}$ and a category of arrows $\mathbf{D_1}$ with the following functors
 \begin{center}
-$U\maps \lD_0 \to \lD_1$\\
-$S,T \maps \lD_1 \rightrightarrows \lD_0$\\
-$\odot \maps \lD_1 \times_{\lD_0} \lD_1 \to \lD_1$ (where the pullback is taken over $\lD_1 \xrightarrow[]{T} \lD_0 \xleftarrow[]{S} \lD_1$) \\
+$U\maps \mathbf{D_{0}} \to \mathbf{D_1}$\\
+$S,T \maps \mathbf{D_1} \rightrightarrows \mathbf{D_{0}}$\\
+$\odot \maps \mathbf{D_1} \times_{\mathbf{D_{0}}} \mathbf{D_1} \to \mathbf{D_1}$ (where the pullback is taken over $\mathbf{D_1} \xrightarrow[]{T} \mathbf{D_{0}} \xleftarrow[]{S} \mathbf{D_1}$) \\
 \end{center}
@@
 such that $S(\alpha), S(\lambda), S(\rho), T(\alpha), T(\lambda)$ and $T(\rho)$ are all identities and that the coherence axioms of a monoidal category are satisfied.
-Following the notation of Shulman, objects of $\lD_0$ are called $\textbf{0-cells}$ and morphisms of $\lD_0$ are called $\textbf{vertical 1-morphisms}$.
-Objects of $\lD_1$ are called $\textbf{horizontal 1-cells}$ and morphisms of $\lD_1$ are called $\textbf{2-morphisms}$.
-The morphisms of $\lD_1$, which are vertical 1-morphisms, will be denoted $f \maps A \to C$ and we denote a 1-cell $M$ with $S(M)=A,T(M)=B$ by $M \maps A \to B$.
-Then a 2-morphism $a \maps M \to N$ of $\lD_1$ with $S(a)=f,T(a)=g$ would look like:
+Following the notation of Shulman, objects of $\mathbf{D_{0}}$ are called $\textbf{0-cells}$ and morphisms of $\mathbf{D_{0}}$ are called $\textbf{vertical 1-morphisms}$.
+Objects of $\mathbf{D_1}$ are called $\textbf{horizontal 1-cells}$ and morphisms of $\mathbf{D_1}$ are called $\textbf{2-morphisms}$.
+The morphisms of $\mathbf{D_{0}}$, which are vertical 1-morphisms, will be denoted $f \maps A \to C$ and we denote a 1-cell $M$ with $S(M)=A,T(M)=B$ by $M \maps A \to B$.
+Then a 2-morphism $a \maps M \to N$ of $\mathbf{D_1}$ with $S(a)=f,T(a)=g$ would look like:
 \[
@@
 \end{defn}
-A 2-morphism where $f$ and $g$ are identities is called a \textbf{globular 2-morphism}.
-
-%The key difference between a `strict' double category and a pseudo double category is that in a pseudo double category, horizontal composition is associative and unital only up to natural isomorphism.
+
+The key difference between a `strict' double category and a pseudo double category is that in a pseudo double category, horizontal composition is associative and unital only up to natural isomorphism.
 Equivalently, as a double category can be viewed as a category internal to $\Cat$, we can view a pseudo double category as a category `weakly' internal to $\Cat$.
@@
 
-%\begin{defn}
-%Let $\lD$ be a pseudo double category.
+\begin{defn}
+A 2-morphism where $f$ and $g$ are identities is called a \textbf{globular 2-morphism}.
+\end{defn}
+
+\begin{defn}
+Let $\lD$ be a pseudo double category.
 Then the $\textbf{horizontal bicategory}$ of $\lD$, which we denote as $H(\lD)$, is the bicategory consisting of objects of $\lD$, morphisms that are horizontal 1-cells of $\lD$ and 2-morphisms that are globular 2-morphisms of $\lD$.
-%\end{defn}
+\end{defn}
 
@@
 
-%Following the notation of Shulman \cite{Shulman2010}, given a double category $\mathbb{A}$, we write $_f \mathbb{A}_g(M,N)$ for the set of 2-morphisms in $\mathbb{A}$ of the form:
-%\[
-%  \xymatrix@-.5pc{
-%   A \ar[r]|{|}^{M}  \ar[d]_f \ar@{}[dr]|{\Downarrow a}&
-%    B\ar[d]^g\\
-%    C \ar[r]|{|}_N & D
-%  }
-%\]
-%We call $M$ and $N$ the \define{horizontal source and target} of the 2-morphism $a$, respectively, and likewise we call $f$ and $g$ the \define{vertical source and target} of the 2-morphism $a$, respectively.
+Following the notation of Shulman \cite{Shulman2010}, given a double category $\mathbb{A}$, we write $_f \mathbb{A}_g(M,N)$ for the set of 2-morphisms in $\mathbb{A}$ of the form:
+\[
+  \xymatrix@-.5pc{
+    A \ar[r]|{|}^{M}  \ar[d]_f \ar@{}[dr]|{\Downarrow a}&
+    B\ar[d]^g\\
+    C \ar[r]|{|}_N & D
+  }
+\]
+We call $M$ and $N$ the \define{horizontal source and target} of the 2-morphism $a$, respectively, and likewise we call $f$ and $g$ the \define{vertical source and target} of the 2-morphism $a$, respectively.
 Thus $_f \mathbb{A}_g(M,N)$ denotes the set of 2-morphisms in $\mathbb{A}$ with horizontal source and target $M$ and $N$ and vertical source and target $f$ and $g$.
@@
 Formally, two strong double functors between two double categories form a \emph{double equivalence} if ...
-%{\chris their two-way composite is isomorphic to the identity, better expressed, possibly in a definition environment}.   Say this or leave it out entirely!!!
-Similarly to ordinary equivalence of categories, \cite[Theorem 7.8]{Shulman2010} allows us to use the following equivalent characterization.
+%{\chris their two-way composite is isomorphic to the identity, better expressed, possibly in a definition environment}. 
+Similarly to ordinary equivalence of categories, [Shulman,7.8] allows us to use the following equivalent characterization.
 
@@
 \begin{enumerate}
-\item $\lD_0$ and $\lD_1$ are both monoidal categories.
-\item If $I$ is the monoidal unit of $\lD_0$, then $U_I$ is the
-  monoidal unit of $\lD_1$.
+\item $\mathbf{D_{0}}$ and $\mathbf{D_1}$ are both monoidal categories.
+\item If $I$ is the monoidal unit of $\mathbf{D_{0}}$, then $U_I$ is the
+  monoidal unit of $\mathbf{D_1}$.
 \item The functors $S$ and $T$ are strict monoidal, i.e.\ $S(M\ten N)

### 2020-11-17 cospans.tex
slowly making progress in 3.2

@@
 Next, we define the four structure functors $U,S,T$ and $\odot$. The unit functor $U \maps F\lCsp_0 \to F\lCsp_1$ is defined on objects as: 
-\[
+\begin{equation}\label{eq:UFCsp}
 \begin{tikzpicture}[scale=1.5]
@@
 \end{tikzpicture}
-\]
+\end{equation}
 where $!_a \in F(a)$ is the \define{trivial decoration} on $a$ given by the composite of the unique map $F(!) \maps F(0) \to F(a)$ and the morphism $\phi \maps 1 \to F(0)$  which comes from $F \maps \A \to \Cat$ being lax monoidal.
@@
 \begin{rmk}\label{rmk:important}
-Notice that under \cref{lem:fibrewiselimits}, if the base category $\A$ has an initial object denoted $0_\A$, the above is equivalent to $\X$ having an initial object $0_\X$ above $0_\A$.
+Notice that under \cref{lem:fibrewiselimits}, if the base category $\A$ has an initial object denoted $0_\A$, the above lemma is equivalent to $\X$ having an initial object $0_\X$ above $0_\A$.
 The way in which these two conditions give one another in this case is as follows.
@@
 % Once again, this is a bijective correspondence since, as discussed above, the commutativity \cref{eq:Grothcommutativity} holds automatically by initiality of the domain.
-With these definitions, $\lE$ is indeed a strong double functor as in \cref{def:doublefun}: both $\lE_0$ and $\lE_1$ are functors that appropriately commute with sources and targets, and there exist globular 2-isomorphisms $\lE(M) \odot \lE(N) \simrightarrow\lE(M \odot N)$, $U_{\lE m} \simrightarrow\lE(U_m)$
+With these definitions, $\lE$ is indeed a (pseudo) double functor as in \cref{def:doublefun}: both $\lE_0$ and $\lE_1$ are functors that appropriately commute with sources and targets, and there exist globular 2-isomorphisms $\lE(M) \odot \lE(N) \simrightarrow\lE(M \odot N)$, $U_{\lE m} \simrightarrow\lE(U_m)$
 for any pair of composable horizontal 1-cells $M=\cspn{(a,\bot_a)}{(m,x)}{(b,\bot_b)}{}{}$ and $N=\cspn{(b,\bot_b)}{(n,y)}{(c,\bot_c)}{}{}$ and any object $m$ of $\scsp{L}{\inta F}$.
 Explicitly, $\mathbb{E}(M)\odot \mathbb{E}(N)$ is given as in \cref{eq:dcospanscomposition} via the pushout cospan and decoration
-\begin{displaymath}
+\begin{equation}\label{eq:1}
  \begin{tikzcd}
@@
  \end{tikzcd}\qquad
-  1\xrightarrow{x\times y}F(m)\times F(n)\xrightarrow{\phi_{m,n}}F(m+n)\xrightarrow{F(\psi)}F(m+_bn)
-\end{displaymath}
-{\chris In progress...}
-
-On the other hand, first composing $M$ and $N$ in the Grothendieck category $\scsp{L_F}{\inta F}$ using fibrewise pushouts constructed using \cref{lem:fibrewiselimits} 
-%!!!Chris: I could make this specific construction into a lemma earlier if you want, I have it in my notes
+  \mathbf{1}\xrightarrow{x\times y}F(m)\times F(n)\xrightarrow{\phi_{m,n}}F(m+n)\xrightarrow{F(\psi)}F(m+_bn)
+\end{equation}
+whereas first composing $M$ and $N$ in $\scsp{L}{\inta F}$ using pushouts in $\inta F$ (constructed by \cref{lem:fibrewiselimits}) %!!!
+Christina: would you like me to write how global pushouts are constructed from fiberwise ones and incorporate it earlier say at \cref{rmk:important} where we do so for initial objects?
 produces 
 \begin{displaymath}
- \begin{tikzcd}
- && (m+_b n,F(j_m)x+_{\bot_{m+_bn}}F(j_n)y) && \\
+ \begin{tikzcd}[column sep={.7in,between origins}]
+ && (m+_b n,F(\sigma_m)x+_{(\bot_{m+_bn})}F(\sigma_n)y) && \\
  & (m,x) \ar[ur] && (n,y)\ar[ul] \\
@@
 \end{displaymath}
-which is mapped, under $\mathbb{E}$, to precisely the cospan $\cspn{a}{m+_bn}{b}{}{}$ as above, and the decorations are the same 
-%!!!Christina: isomorphic would be enough but they look equal to me!
-due to the following commutative diagram
+where $\sigma$ are the canonical maps into the pushout. %overusing notation, streamline with earlier
+Under $\lE$ this is mapped to the underlying $\A$-cospan $\cspn{a}{m+_bn}{b}{}{}$ with decoration $F(\sigma_m)x+F(\sigma_n)y$ -- since a pushout over an initial object is really a coproduct -- which is isomorphic to \cref{eq:1} due to the following diagram
 \begin{displaymath}
  \begin{tikzcd}
-F(m)\times F(n)\ar[rr,"\phi"]\ar[d,"F(j_m)\times F(j_n)"'] && F(m+n)\ar[d,"F(j)"] \\
-F(m+_bn)\times F(m+_bn)\ar[r,"\phi"] & F((m+_bn)+(m+_bn))\ar[r,"F\nabla"] & F(m+_bn)
+F(m)\times F(n)\ar[rr,"\phi"]\ar[d,"F(\sigma_m)\times F(\sigma_n)"']\ar[dr,phantom,"\cong"] && F(m+n)\ar[d,"F(\psi)"]\ar[d,bend right=50, phantom,"\cong"']\ar[dl,"F(\sigma_m+\sigma_n)"description] \\
+F(m+_bn)\times F(m+_bn)\ar[r,"\phi"'] & F\left((m+_bn)+(m+_bn)\right)\ar[r,"F(\nabla)"'] & F(m+_bn)
  \end{tikzcd}
 \end{displaymath}
-since taking a pushout over an initial object is really a coproduct, and the fibrewise coproduct in $F(m+_bn)$ is given as in \cref{eq:explicitstructure1}.
-
-Regarding the identity morphisms, $U_m$ is $\cspn{(m,\bot_m)}{(m,\bot_m)}{(m,\bot_m)}{}{}$ with $1_m$ as the $A$-component of the morphisms and isomorphisms between initial objects in the fibres.
-Thus $\mathbb{E}(U_m)$ is the identity cospan in $A$ together with the `initial decoration' $\bot_m\in F(m)$, whereas $U_{\mathbb{E}(m)}$ is exactly the same thing.
+where the bottom composite is the fibrewise coproduct in $F(m+_bn)$ as in \cref{eq:explicitstructure1}.
+The left-hand side isomorphism is due to pseudonaturality of $\phi$ whereas the right-hand side isomorphism follows from universal properties and pseudofunctoriality of $F$.
+Regarding identities, $U_m$ is $\cspn{(m,\bot_m)}{(m,\bot_m)}{(m,\bot_m)}{}{}$ with $1_m$ as the $A$-components and isomorphisms between initial objects in the fibres.
+So $\lE(U_m)$ is the identity cospan in $A$ together with the `initial decoration' $\bot_m\in F(m)$, and so is $U_{\mathbb{E}(m)}$ as in \cref{eq:UFCsp}.
+
+{\chris IN progress...}
 
@@
 \textbf{At least in my favorite example...}
-\end{comment}
-
-%!!!Christina: Below, up to my next comment, is Kenny's earlier proof on the same thing.
-\begin{comment}
+
+.....
+
 For any object $c$, the horizontal 1-cell $\hat{U}_{\mathbb{E}(c)}$ is given by $\hat{U}_c$ which is given by the pair:
@@
 \end{comment}
-%!!!Christina: Up to here was Kenny's strong functoriality.
 

### 2020-11-17 cospans.tex
cleared a big commented out chunk of an earlier proof for a double functor in the opposite direction

@@
 
-\begin{comment}
-which is a cospan in $\X$ of the form:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$L(c)$};
-\node (B) at (1,0) {$x$};
-\node (C) at (2,0) {$L(c')$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i$} (B)
-(C) edge node[above]{$o$} (B);
-\end{tikzpicture}
-\]
-the image $\mathbb{E}_1(M)$ is given by the pair:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$c$};
-\node (B) at (1,0) {$R(x)$};
-\node (C) at (2,0) {$c'$};
-\node (D) at (3,0) {$x \in F(R(x))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$R(i) {\eta_c}$} (B)
-(C) edge node[above]{$R(o) {\eta_{c'}}$} (B);
-\end{tikzpicture}
-\]
-where $R\maps \X \to \A$ is the right adjoint to the functor $L \maps \A \to \X$ and $\eta \maps 1_{\A} \to RL$ is the unit of the adjunction $L \dashv R$ which is an isomorphism since $L$ is fully faithful.
-\textbf{Hopefully...actually, it's a `lari'!} Similarly, the image of a 2-morphism $\alpha \maps M \to N$ in $_L \lCsp(\X)$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$L(c_1)$};
-\node (B) at (1,0) {$x$};
-\node (C) at (2,0) {$L(c_2)$};
-\node (A') at (0,-1) {$L(c_1')$};
-\node (B') at (1,-1) {$x'$};
-\node (C') at (2,-1) {$L(c_2')$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i$} (B)
-(C) edge node[above]{$o$} (B)
-(A') edge node[above]{$i'$} (B')
-(C') edge node[above]{$o'$} (B')
-(A) edge node [left]{$L(f)$} (A')
-(B) edge node [left]{$\alpha$} (B')
-(C) edge node [right]{$L(g)$} (C');
-\end{tikzpicture}
-\]
-is given by the 2-morphism $\mathbb{E}_1(\alpha) \maps \mathbb{E}_1(M) \to \mathbb{E}_1(N)$ in $\mathbb{F}\textnormal{Cospan}(\A)$ given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$c_1$};
-\node (B) at (1,0) {$R(x)$};
-\node (C) at (2,0) {$c_2$};
-\node (A') at (0,-1) {$c_1'$};
-\node (B') at (1,-1) {$R(x')$};
-\node (C') at (2,-1) {$c_2'$};
-\node (D) at (3,0) {$x \in F(R(x))$};
-\node (D') at (3,-1) {$x' \in F(R(x'))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$R(i) \eta_{c_1}$} (B)
-(C) edge node[above]{$R(o) \eta_{c_2}$} (B)
-(A') edge node[above]{$R(i') \eta_{c_1'}$} (B')
-(C') edge node[above]{$R(o') \eta_{c_2'}$} (B')
-(A) edge node [left]{$f$} (A')
-(B) edge node [left]{$R(\alpha)$} (B')
-(C) edge node [right]{$g$} (C');
-\end{tikzpicture}
-\]
-together with a morphism $\tau \maps F(R(\alpha))(x) \to x'$ in $F(R(x')) \subseteq \mathrm{X}$ which comes from the Grothendieck construction of the pseudofunctor $F \maps \A \to \Cat$.
-That $\mathbb{E}_0$ is a functor is clear.
-For $\mathbb{E}_1$, given two vertically composable 2-morphisms $M$ and $M'$ in $_L \lCsp(\X)$,
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$L(c_1)$};
-\node (B) at (1,0) {$x$};
-\node (C) at (2,0) {$L(c_2)$};
-\node (A') at (0,-1) {$L(c_1')$};
-\node (B') at (1,-1) {$x'$};
-\node (C') at (2,-1) {$L(c_2')$};
-\node (A'') at (0,-2) {$L(c_1')$};
-\node (B'') at (1,-2) {$x'$};
-\node (C'') at (2,-2) {$L(c_2')$};
-\node (A''') at (0,-3) {$L(c_1'')$};
-\node (B''') at (1,-3) {$x''$};
-\node (C''') at (2,-3) {$L(c_2'')$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i$} (B)
-(C) edge node[above]{$o$} (B)
-(A') edge node[above]{$i'$} (B')
-(C') edge node[above]{$o'$} (B')
-(A) edge node [left]{$L(f)$} (A')
-(B) edge node [left]{$\alpha$} (B')
-(C) edge node [right]{$L(g)$} (C')
-(A'') edge node[above]{$i'$} (B'')
-(C'') edge node[above]{$o'$} (B'')
-(A''') edge node[above]{$i''$} (B''')
-(C''') edge node[above]{$o''$} (B''')
-(A'') edge node [left]{$L(f')$} (A''')
-(B'') edge node [left]{$\alpha'$} (B''')
-(C'') edge node [right]{$L(g')$} (C''');
-\end{tikzpicture}
-\]
-their vertical composite $M'M$ is given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$L(c_1)$};
-\node (B) at (1,0) {$x$};
-\node (C) at (2,0) {$L(c_2)$};
-\node (A') at (0,-1) {$L(c_1'')$};
-\node (B') at (1,-1) {$x''$};
-\node (C') at (2,-1) {$L(c_2'')$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i$} (B)
-(C) edge node[above]{$o$} (B)
-(A') edge node[above]{$i''$} (B')
-(C') edge node[above]{$o''$} (B')
-(A) edge node [left]{$L(f'f)$} (A')
-(B) edge node [left]{$\alpha' \alpha$} (B')
-(C) edge node [right]{$L(g' g)$} (C');
-\end{tikzpicture}
-\]
-and the image of this 2-morphism $\mathbb{E}_1(M'M)$ is given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$c_1$};
-\node (B) at (1.5,0) {$R(x)$};
-\node (C) at (3,0) {$c_2$};
-\node (A') at (0,-1) {$c_1''$};
-\node (B') at (1.5,-1) {$R(x'')$};
-\node (C') at (3,-1) {$c_2''$};
-\node (D) at (4,0) {$x \in F(R(x))$};
-\node (D') at (4,-1) {$x'' \in F(R(x''))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$R(i) \eta_{c_1}$} (B)
-(C) edge node[above]{$R(o) \eta_{c_2}$} (B)
-(A') edge node[above]{$R(i'') \eta_{c_1''}$} (B')
-(C') edge node[above]{$R(o'') \eta_{c_2''}$} (B')
-(A) edge node [left]{$f'f$} (A')
-(B) edge node [left]{$R(\alpha' \alpha)$} (B')
-(C) edge node [right]{$g'g$} (C');
-\end{tikzpicture}
-\]
-together with a morphism $\tau_{M' M} \maps F(R(\alpha' \alpha))(x) \to x''$ in $F(R(x''))$. On the other hand, the individual images $\mathbb{E}_1(M)$ and $\mathbb{E}_1(M')$ are given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$c_1$};
-\node (B) at (1.5,0) {$R(x)$};
-\node (C) at (3,0) {$c_2$};
-\node (A') at (0,-1) {$c_1'$};
-\node (B') at (1.5,-1) {$R(x')$};
-\node (C') at (3,-1) {$c_2'$};
-\node (D) at (4,0) {$x \in F(R(x))$};
-\node (D') at (4,-1) {$x' \in F(R(x'))$};
-\node (A'') at (0,-2) {$c_1'$};
-\node (B'') at (1.5,-2) {$R(x')$};
-\node (C'') at (3,-2) {$c_2'$};
-\node (A''') at (0,-3) {$c_1''$};
-\node (B''') at (1.5,-3) {$R(x'')$};
-\node (C''') at (3,-3) {$c_2''$};
-\node (D'') at (4,-2) {$x' \in F(R(x'))$};
-\node (D''') at (4,-3) {$x'' \in F(R(x''))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$R(i) \eta_{c_1}$} (B)
-(C) edge node[above]{$R(o) \eta_{c_2}$} (B)
-(A') edge node[above]{$R(i') \eta_{c_1'}$} (B')
-(C') edge node[above]{$R(o') \eta_{c_2'}$} (B')
-(A) edge node [left]{$f$} (A')
-(B) edge node [left]{$R(\alpha)$} (B')
-(C) edge node [right]{$g$} (C')
-(A'') edge node[above]{$R(i') \eta_{c_1'}$} (B'')
-(C'') edge node[above]{$R(o') \eta_{c_2'}$} (B'')
-(A''') edge node[above]{$R(i'') \eta_{c_1''}$} (B''')
-(C''') edge node[above]{$R(o'') \eta_{c_2''}$} (B''')
-(A'') edge node [left]{$f'$} (A''')
-(B'') edge node [left]{$R(\alpha')$} (B''')
-(C'') edge node [right]{$g'$} (C''');
-\end{tikzpicture}
-\]
-together with morphisms $\tau_M \maps F(R(\alpha))(x) \to x'$ in $F(R(x'))$ and $\tau_{M'} \maps F(R(\alpha')(x') \to x''$ in $F(R(x''))$, respectively.
-The vertical composite $\mathbb{E}_1(M')\mathbb{E}_1(M)$ of the above two 2-morphisms is given by $\mathbb{E}_1(M'M)$ as $R$ is a functor and $\tau_{M'M}=\tau_{M'} \tau_M$.
-The functors $\mathbb{E}_0$ and $\mathbb{E}_1$ satisfy the equations $\mathbb{E}_0 S = S \mathbb{E}_1$ and $\mathbb{E}_0 T = T \mathbb{E}_1$.
-
-To see that this functor is essentially surjective, given a horizontal 1-cell in $F\lCsp$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$c_1$};
-\node (B) at (1,0) {$c$};
-\node (C) at (2,0) {$c_2$};
-\node (D) at (3,0) {$x \in F(c)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i$} (B)
-(C) edge node[above]{$o$} (B);
-\end{tikzpicture}
-\]
-we can find a 2-isomorphism in $F\lCsp$ whose codomain is the above horizontal 1-cell and whose domain is the image of the following horizontal 1-cell in $_L \lCsp(\X)$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$L(c_1)$};
-\node (B) at (1,0) {$x$};
-\node (C) at (2,0) {$L(c_2)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i'$} (B)
-(C) edge node[above]{$o'$} (B);
-\end{tikzpicture}
-\]
-with the 2-isomorphism in $F\lCsp$ given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$c_1$};
-\node (B) at (1,0) {$R(x)$};
-\node (C) at (2,0) {$c_2$};
-\node (A') at (0,-1) {$c_1$};
-\node (B') at (1,-1) {$c$};
-\node (C') at (2,-1) {$c_2$};
-\node (D) at (3,0) {$x \in F(R(x))$};
-\node (D') at (3,-1) {$x \in F(c)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$R(i') \eta_{c_1}$} (B)
-(C) edge node[above]{$R(o') \eta_{c_2}$} (B)
-(A') edge node[above]{$i$} (B')
-(C') edge node[above]{$o$} (B')
-(A) edge node [left]{$1$} (A')
-(B) edge node [left]{${(R(e) \eta_c)}^{-1}$} (B')
-(C) edge node [right]{$1$} (C');
-\end{tikzpicture}
-\]
-$$\tau \maps F({(R(e)\eta_c)}^{-1})(x) \to x$$
-where $e \maps L(c) \to x$ is given by the map from the trivial decoration on $c$ to $x \in F(c)$.
-%The object and arrow components $\mathbb{E}_0$ and $\mathbb{E}_1$ satisfy the equations $S \mathbb{E}_1 = \mathbb{E}_0 S$ and $T \mathbb{E}_1 = \mathbb{E}_0 T$.
-
-To show that the double functor $\mathbb{E}$ is fully faithful, we need to show that the map  $$\mathbb{E}_1 \maps _f { _L \lCsp(\X)}_g(M,N) \to {_{\mathbb{E}(f)} {F\lCsp}_{\mathbb{E}(g)}}(\mathbb{E}(M),\mathbb{E}(N))$$ is bijective for arbitrary vertical 1-morphisms $f$ and $g$ and horizontal 1-cells $M$ and $N$ of $_L \lCsp(\X)$.
-Consider a 2-morphism in $_L \lCsp(\X)$ with horizontal source and target $M$ and $N$, respectively and vertical source and target $f$ and $g$, respectively:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$L(c_1)$};
-\node (B) at (1,0) {$x$};
-\node (C) at (2,0) {$L(c_2)$};
-\node (A') at (0,-1) {$L(c_1')$};
-\node (B') at (1,-1) {$x'$};
-\node (C') at (2,-1) {$L(c_2')$};
-\node (D) at (1,0.5) {$M$};
-\node (E) at (-1,-0.5) {$f$};
-\node (F) at (1,-1.5) {$N$};
-\node (G) at (3,-0.5) {$g$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i$} (B)
-(C) edge node[above]{$o$} (B)
-(A') edge node[above]{$i'$} (B')
-(C') edge node[above]{$o'$} (B')
-(A) edge node [left]{$L(f)$} (A')
-(B) edge node [left]{$\alpha$} (B')
-(C) edge node [right]{$L(g)$} (C');
-\end{tikzpicture}
-\]
-Thus the set $$_f { _L \lCsp(\X)}_g(M,N)$$ consists of triples $$(f,\alpha,g)$$ rendering the above diagram commutative where $f$ and $g$ are morphisms of $\A$ and $\alpha$ is a morphism of $\X$.
-The image of the above 2-morphism under the double functor $\mathbb{E}$ is given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$c_1$};
-\node (B) at (1,0) {$R(x)$};
-\node (C) at (2,0) {$c_2$};
-\node (A') at (0,-1) {$c_1'$};
-\node (B') at (1,-1) {$R(x')$};
-\node (C') at (2,-1) {$c_2'$};
-\node (D) at (1,0.5) {$x \in F(R(x))$};
-\node (D') at (1,-1.5) {$x' \in F(R(x'))$};
-\node (E) at (1,1) {$\mathbb{E}(M)$};
-\node (F) at (-1,-0.5) {$\mathbb{E}(f)$};
-\node (G) at (1,-2) {$\mathbb{E}(N)$};
-\node (H) at (3,-0.5) {$\mathbb{E}(g)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$R(i)\eta_{c_1}$} (B)
-(C) edge node[above]{$R(o)\eta_{c_2}$} (B)
-(A') edge node[above]{$R(i')\eta_{c_1'}$} (B')
-(C') edge node[above]{$R(o')\eta_{c_2'}$} (B')
-(A) edge node [left]{$f$} (A')
-(B) edge node [left]{$R(\alpha)$} (B')
-(C) edge node [right]{$g$} (C');
-\end{tikzpicture}
-\]
-together with a morphism $\tau \maps F(R(\alpha))(x) \to x'$ of $F(R(x'))$.
-Thus the set $$_{\mathbb{E}(f)} {F\lCsp}_{\mathbb{E}(g)}(\mathbb{E}(M),\mathbb{E}(N))$$ consists of 4-tuples $$(f,R(\alpha),g,\tau)$$ rendering the above diagram commutative and where $f,g$ and $R(\alpha)$ are morphisms of $\A$ and $\tau$ is a morphism in $F(R(x'))$.
-The morphisms $R(\alpha) \maps R(x) \to R(x')$ and $\tau \maps F(R(\alpha))(x) \to x'$ together determine the morphism $\alpha \maps x \to x'$ in $\mathrm{X}$ and conversely; given two objects $x=(c,x \in F(c))$ and $x'=(c',x' \in F(c'))$ of $\X=\inta{F}$, a morphism from $\alpha \maps x \to x'$ is a pair $$(h \maps c \to c', \tau \maps F(h)(x) \to x')$$ where $h \maps c \to c'$ is given by $R(\alpha) \maps R(x) \to R(x')$.
-This shows that $\mathbb{E}$ is fully faithful.
-\textbf{At least in my favorite example...}
-
-.....
-
-For any object $c$, the horizontal 1-cell $\hat{U}_{\mathbb{E}(c)}$ is given by $\hat{U}_c$ which is given by the pair:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$c$};
-\node (B) at (1,0) {$c$};
-\node (C) at (2,0) {$c$};
-\node (D) at (3,0) {$!_c \in F(c)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$1$} (B)
-(C) edge node[above]{$1$} (B);
-\end{tikzpicture}
-\]
-The horizontal 1-cell $U_c$ is given by
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$L(c)$};
-\node (B) at (1,0) {$L(c)$};
-\node (C) at (2,0) {$L(c)$};
-%\node (D) at (3,0.5) {$!_c \in F(c)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$1$} (B)
-(C) edge node[above]{$1$} (B);
-\end{tikzpicture}
-\]
-and so $\mathbb{E}(U_c)$ is given by the pair:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$c$};
-\node (B) at (1,0) {$R(L(c))$};
-\node (C) at (2,0) {$c$};
-\node (D) at (3.25,0) {$!_c \in F(R(L(c)))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$\eta_c$} (B)
-(C) edge node[above]{$\eta_c$} (B);
-\end{tikzpicture}
-\]
-Then we can obtain the natural isomorphism $\mathbb{E}_c \maps \hat{U}_{\mathbb{E}(c)} \xrightarrow{\sim} \mathbb{E}(U_c)$ as the 2-morphism
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$c$};
-\node (B) at (1,0) {$c$};
-\node (C) at (2,0) {$c$};
-\node (A') at (0,-1) {$c$};
-\node (B') at (1,-1) {$R(L(c))$};
-\node (C') at (2,-1) {$c$};
-\node (D) at (3,0) {$!_c \in F(c)$};
-\node (D') at (3.25,-1) {$!_{R(L(c))} \in F(R(L(c)))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$1$} (B)
-(C) edge node[above]{$1$} (B)
-(A') edge node[above]{$\eta_c$} (B')
-(C') edge node[above]{$\eta_c$} (B')
-(A) edge node [left]{$1$} (A')
-(B) edge node [left]{$\eta_c$} (B')
-(C) edge node [left]{$1$} (C');
-\end{tikzpicture}
-\]
-$$\tau \maps F(\eta_c)(!_c) \xrightarrow{!} !_{R(L(c))}$$
-of $F\lCsp$.
-
-Next, given composable horizontal 1-cells $M$ and $N$ in $_L \lCsp(\X)$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$L(c_1)$};
-\node (B) at (1,0) {$x$};
-\node (C) at (2,0) {$L(c_2)$};
-\node (D) at (3,0) {$L(c_2)$};
-\node (E) at (4,0) {$x'$};
-\node (F) at (5,0) {$L(c_3)$};
-%\node (D) at (3,0.5) {$!_c \in F(c)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i$} (B)
-(C) edge node[above]{$o$} (B)
-(D) edge node[above]{$i'$} (E)
-(F) edge node[above]{$o'$} (E);
-\end{tikzpicture}
-\]
-their images $\mathbb{E}(M)$ and $\mathbb{E}(N)$ are given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$c_1$};
-\node (B) at (1,0) {$R(x)$};
-\node (C) at (2,0) {$c_2$};
-\node (D) at (3,0) {$c_2$};
-\node (E) at (4,0) {$R(x')$};
-\node (F) at (5,0) {$c_3$};
-\node (G) at (1,-0.5) {$x \in F(R(x))$};
-\node (H) at (4,-0.5) {$x' \in F(R(x'))$};
-%\node (D) at (3,0.5) {$!_c \in F(c)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$R(i) \eta_{c_1}$} (B)
-(C) edge node[above]{$R(o) \eta_{c_2}$} (B)
-(D) edge node[above]{$R(i') \eta_{c_2}$} (E)
-(F) edge node[above]{$R(o') \eta_{c_3}$} (E);
-\end{tikzpicture}
-\]
-and so $\mathbb{E}(M) \odot \mathbb{E}(N)$ is given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$c_1$};
-\node (B) at (1.5,0) {$R(x)+_{c_2}R(x')$};
-\node (C) at (3,0) {$c_3$};
-\node (G) at (1.5,-0.5) {$d_{\mathbb{E}(M) \odot \mathbb{E}(N)} = \hat{x} \in F(R(x)+_{c_2}R(x'))$};
-%\node (D) at (3,0.5) {$!_c \in F(c)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$j \psi R(i) \eta_{c_1}$} (B)
-(C) edge node[above]{$j \psi R(o') \eta_{c_3}$} (B);
-\end{tikzpicture}
-\]
-$$\hat{x} \maps 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{x \times x'} F(R(x)) \times F(R(x')) \xrightarrow{\phi_{R(x),R(x')}} F(R(x)+R(x')) \xrightarrow{F(j_{R(x),R(x')})} F(R(x)+_{c_2}R(x'))$$where $\psi$ denotes each natural map into the coproduct and $j$ denotes the natural map from the coproduct to the pushout.
-On the other hand, $M \odot N$ is given by
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$L(c_1)$};
-\node (B) at (1.25,0) {$x+_{L(c_2)}x'$};
-\node (C) at (2.5,0) {$L(c_3)$};
-%\node (G) at (1,-0.5) {$\hat{d} \in F(R(d)+_{c_2}R(d'))$};
-%\node (D) at (3,0.5) {$!_c \in F(c)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$J \zeta i$} (B)
-(C) edge node[above]{$J \zeta o'$} (B);
-\end{tikzpicture}
-\]
-where $\zeta$ is a natural map into a coproduct and $J$ is the natural map from the coproduct to the pushout. Then $E(M \odot N)$ is given by
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$c_1$};
-\node (B) at (1.5,0) {$R(x+_{L(c_2)}x')$};
-\node (C) at (3,0) {$c_3$};
-\node (G) at (1.5,-0.5) {$d_{\mathbb{E}(M \odot N)} = x+_{L(c_2)} x' \in F(R(x+_{L(c_2)}x'))$};
-%\node (D) at (3,0.5) {$!_c \in F(c)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$R(J \zeta i) \eta_{c_1}$} (B)
-(C) edge node[above]{$R(J \zeta o') \eta_{c_3}$} (B);
-\end{tikzpicture}
-\]
-and so $\mathbb{E}_{M,N} \maps \mathbb{E}(M) \odot \mathbb{E}(N) \xrightarrow{\sim} \mathbb{E}(M \odot N)$ is given by the 2-morphism:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$c_1$};
-\node (B) at (1.5,0) {$R(x)+_{c_2}R(x')$};
-\node (C) at (3,0) {$c_3$};
-\node (A') at (0,-1) {$c_1$};
-\node (B') at (1.5,-1) {$R(x+_{L(c_2)}x')$};
-\node (C') at (3,-1) {$c_3$};
-\node (D) at (5.5 ,0) {$d_{\mathbb{E}(M) \odot \mathbb{E}(N)} \in F(R(x)+_{c_2}R(x'))$};
-\node (D') at (5.5,-1) {$d_{\mathbb{E}(M \odot N)} \in F(R(x+_{L(c_2)}x'))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$j \psi R(i) \eta_{c_1}$} (B)
-(C) edge node[above]{$j \psi R(o') \eta_{c_3}$} (B)
-(A') edge node[above]{$R(J \zeta i) \eta_{c_1}$} (B')
-(C') edge node[above]{$R(J \zeta o') \eta_{c_3}$} (B')
-(A) edge node [left]{$1$} (A')
-(B) edge node [left]{$\sigma$} (B')
-(C) edge node [left]{$1$} (C');
-\end{tikzpicture}
-\]
-together with a morphism of decorations which is obtained as follows.
-First, as $R \maps \X \to \A$ preserves finite colimits, we have an isomorphism $$\kappa \maps R(x) +_{R(L(c_2))} R(x') \to R(x+_{L(c_2)}x').$$ Also, since the left adjoint $L \maps \A \to \X$ is fully faithful, the unit of the adjunction $L \dashv R$ at the object $c_2$ gives an isomorphism $\eta_{c_2} \maps c_2 \to R(L(c_2))$ which results in an isomorphism $$j_{\eta_{c_2}} \maps R(x) +_{c_2} R(x') \to R(x) +_{R(L(c_2))} R(x').$$ Composing these two results in an isomorphism $$\sigma \mapseqq \kappa j_{\eta_{c_2}} \maps R(x) +_{c_2} R(x') \to R(x+_{L(c_2)}x').$$
-Next, to see that the above diagram commutes, it suffices to show that for the object $c_1 \in \mathrm{A}$, $$R(J)R(\zeta)R(i)\eta_{c_1}(c_1) = R(J \zeta i)\eta_{c_1}(c_1)  \stackrel{!}{=} \sigma j \psi R(i)\eta_{c_1}(c_1) = \kappa j_{\eta_{c_2}} \psi R(i) \eta_{c_1}(c_1).$$ This follows as $R(i) \eta_{c_1} \maps c_1 \to R(x)$ and the following diagram commutes:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (B) at (0,0) {$R(x)$};
-\node (C) at (2,0) {$R(x)+R(x')$};
-\node (A') at (4,0) {$R(x)+_{c_2}R(x')$};
-\node (B') at (4,-2) {$R(x+_{L(c_2)}x')$};
-\node (D) at (0,-2) {$R(x+x')$};
-\node (D') at (4,-1) {$R(x)+_{R(L(c_2))} R(x')$};
-\path[->,font=\scriptsize,>=angle 90]
-(C) edge node[above]{$j$} (A')
-(B) edge node[above]{$\psi$} (C)
-(D) edge node[above]{$R(J)$} (B')
-(B) edge node [left]{$R(\zeta)$} (D)
-(A') edge node [right]{$j_{\eta_{c_2}}$} (D')
-(A') edge [out=345,in=15] node [right]{$\sigma$} (B')
-(D') edge node [right]{$\kappa$} (B');
-\end{tikzpicture}
-\]
-Lastly, this map of cospans comes with an isomorphism $$\tau \maps F(\sigma)(d_{\mathbb{E}(M) \odot \mathbb{E}(N)}) \to d_{\mathbb{E}(M \odot N)}$$ in $F(R(x+_{L(c_2)}x'))$.
-This shows that $\mathbb{E}$ is strong, and so
-\end{comment}
-
 Based on the above description of its mapping, it follows that the strong double functor $\mathbb{E}=(\mathbb{E}_0,\mathbb{E}_1)$ is full, faithful and essentially surjective on objects as per \cref{def:fullfaithful,def:essentiallysurj}.

### 2020-11-17 cospans.tex
polished appendix

@@
 \A \to \textsf{X}$, which is typically a left adjoint, is used to replace the objects and vertical 1-morphisms of a given double category 
-$\mathbb{X}$ with the objects and morphisms, respectively, of the category $\A$. Horizontal 1-cells are then cospans in $\textsf{X}$ of a 
+$\lX$ with the objects and morphisms, respectively, of the category $\A$. Horizontal 1-cells are then cospans in $\textsf{X}$ of a 
 particular form with 2-morphisms given by maps of these cospans. Fong has also developed a similar framework utilizing cospans to study open 
@@
 \]
-
-We call $A, B, C$ and $D$ \textbf{objects} or \textbf{0-cells}, $f$ and $g$ \textbf{vertical 1-morphisms}, $M$ and $N$ \textbf{horizontal 1-cells} and $a$ a \textbf{2-morphism}.
+We call $A, B, C$ and $D$ \define{objects} or \define{0-cells}, $f$ and $g$ \define{vertical 1-morphisms}, $M$ and $N$ \define{horizontal 1-cells} and $a$ a \define{2-morphism}.
 Note that a vertical 1-morphism is a morphism between 0-cells and a 2-morphism is a morphism between horizontal 1-cells.
-We will denote both kinds of morphisms and horizontal 1-cells as a single arrow, namely `$\to$'.
+%We will denote both kinds of morphisms and horizontal 1-cells as a single arrow, namely `$\to$'???
+Or should we put a ``tick'' in here?
 We follow the notation of Shulman \cite{Shulman2008} with the following definitions.
@@
 \begin{defn}\label{defn:double_category}
-A \textbf{pseudo double category} $\lD$, or $\textbf{double category}$ for short, consists of a category of objects $\mathbf{D_{0}}$ and a category of arrows $\mathbf{D_1}$ with the following functors
+A \textbf{(pseudo) double category} $\lD$ consists of a category of objects $\lD_0$ and a category of arrows $\lD_1$ with the following functors
 \begin{center}
-$U\maps \mathbf{D_{0}} \to \mathbf{D_1}$\\
-$S,T \maps \mathbf{D_1} \rightrightarrows \mathbf{D_{0}}$\\
-$\odot \maps \mathbf{D_1} \times_{\mathbf{D_{0}}} \mathbf{D_1} \to \mathbf{D_1}$ (where the pullback is taken over $\mathbf{D_1} \xrightarrow[]{T} \mathbf{D_{0}} \xleftarrow[]{S} \mathbf{D_1}$) \\
+$U\maps \lD_0 \to \lD_1$\\
+$S,T \maps \lD_1 \rightrightarrows \lD_0$\\
+$\odot \maps \lD_1 \times_{\lD_0} \lD_1 \to \lD_1$ (where the pullback is taken over $\lD_1 \xrightarrow[]{T} \lD_0 \xleftarrow[]{S} \lD_1$) \\
 \end{center}
@@
 such that $S(\alpha), S(\lambda), S(\rho), T(\alpha), T(\lambda)$ and $T(\rho)$ are all identities and that the coherence axioms of a monoidal category are satisfied.
-Following the notation of Shulman, objects of $\mathbf{D_{0}}$ are called $\textbf{0-cells}$ and morphisms of $\mathbf{D_{0}}$ are called $\textbf{vertical 1-morphisms}$.
-Objects of $\mathbf{D_1}$ are called $\textbf{horizontal 1-cells}$ and morphisms of $\mathbf{D_1}$ are called $\textbf{2-morphisms}$.
-The morphisms of $\mathbf{D_{0}}$, which are vertical 1-morphisms, will be denoted $f \maps A \to C$ and we denote a 1-cell $M$ with $S(M)=A,T(M)=B$ by $M \maps A \to B$.
-Then a 2-morphism $a \maps M \to N$ of $\mathbf{D_1}$ with $S(a)=f,T(a)=g$ would look like:
+Following the notation of Shulman, objects of $\lD_0$ are called \define{0-cells} or \define{objects} and morphisms of $\lD_0$ are called \define{vertical 1-morphisms}.
+Objects of $\lD_1$ are called \define{horizontal 1-cells} and morphisms of $\lD_1$ are called \define{2-morphisms}.
+The morphisms of $\lD_0$, which are vertical 1-morphisms, will be denoted $f \maps A \to C$ and we denote a 1-cell $M$ with $S(M)=A,T(M)=B$ by $M \maps A \to B$.
+Then a 2-morphism $a \maps M \to N$ of $\lD_1$ with $S(a)=f,T(a)=g$ would look like:
 \[
@@
 
-\begin{defn}
-A 2-morphism where $f$ and $g$ are identities is called a \textbf{globular 2-morphism}.
-\end{defn}
-
-\begin{defn}
-Let $\lD$ be a pseudo double category.
+%\begin{defn}
+%Let $\lD$ be a pseudo double category.
 Then the $\textbf{horizontal bicategory}$ of $\lD$, which we denote as $H(\lD)$, is the bicategory consisting of objects of $\lD$, morphisms that are horizontal 1-cells of $\lD$ and 2-morphisms that are globular 2-morphisms of $\lD$.
-\end{defn}
+%\end{defn}
 
 \begin{defn}\label{def:doublefun}
-Let $\mathbb{A}$ and $\mathbb{B}$ be pseudo double categories.
-A \define{lax double functor} is a functor $\mathbb{F} \maps\mathbb{A}\to \mathbb{B}$ that takes items of $\mathbb{A}$ to items of $\mathbb{B}$ of the corresponding type, respecting vertical composition in the strict sense and the horizontal composition up to an assigned comparison $\phi$.
-This means that we have functors $\mathbb{F}_0 \maps \mathbb{A}_0 \to \mathbb{B}_0$ and $\mathbb{F}_1 \maps \mathbb{A}_1 \to \mathbb{B}_1$ such that the following equations are satisfied: $$S \circ \mathbb{F}_1 = \mathbb{F}_0 \circ S$$ $$T \circ \mathbb{F}_1 = \mathbb{F}_0 \circ T$$ Sometimes for brevity, we will omit the subscripts and simply say $\mathbb{F}$.
-As to whether we mean $\mathbb{F}_0$ or $\mathbb{F}_1$ will be clear from context.
-
-Also, every object $a$ is equipped with a special globular 2-morphism $\phi_{a} \maps 1_{\mathbb{F}(a)} \to \mathbb{F}(1_{a})$ (the identity comparison), and every horizontal composition $N_1 \odot N_{2}$ is equipped with a special globular 2-morphism $\phi(N_1,N_{2}) \maps \mathbb{F}(N_1) \odot \mathbb{F}(N_{2}) \to \mathbb{F}(N_1 \odot N_{2})$ (the composition comparison), in a coherent way.
+Let $\lA$ and $\lB$ be double categories.
+A \define{(pseudo) double functor} is a functor $\lF \maps\lA\to \lB$ that takes items of $\lA$ to items of $\lB$ of the corresponding type, respecting vertical composition in the strict sense and the horizontal composition up to an assigned comparison $\phi$.
+This means that we have functors $\lF_0 \maps \lA_0 \to \lB_0$ and $\lF_1 \maps \lA_1 \to \lB_1$ such that the following equations are satisfied:
+\[   S \circ \lF_1 = \lF_0 \circ S, \qquad  T \circ \lF_1 = \lF_0 \circ T. \]
+Sometimes for brevity we omit the subscripts and simply write $\lF$.
+
+Every object $a$ is equipped with a special globular 2-morphism $\phi_{a} \maps 1_{\lF(a)} \to \lF(1_{a})$ (the identity comparison), and every horizontal composition $N_1 \odot N_{2}$ is equipped with a special globular 2-morphism $\phi(N_1,N_{2}) \maps \lF(N_1) \odot \lF(N_{2}) \to \lF(N_1 \odot N_{2})$ (the composition comparison), in a coherent way.
 This means that the following diagrams commute.
@@
   \xymatrix@-.5pc{
-    \mathbb{F}(A) \ar[r]|{|}^{\mathbb{F}(N_{2})}  \ar[d] \ar@{}[dr]|{\mathbb{F}(\alpha)}&
-    \mathbb{F}(B) \ar[d] \ar[r]|{|}^{\mathbb{F}(N_1)} \ar@{}[dr]|{\mathbb{F}(\beta)}&
-    \mathbb{F}(C) \ar[d] &
+    \lF(A) \ar[r]|{|}^{\lF(N_{2})}  \ar[d] \ar@{}[dr]|{\lF(\alpha)}&
+    \lF(B) \ar[d] \ar[r]|{|}^{\lF(N_1)} \ar@{}[dr]|{\lF(\beta)}&
+    \lF(C) \ar[d] &
      &
-    \mathbb{F}(A) \ar[r]|{|}^{\mathbb{F}(N_{2})} \ar@{}[drr]|{\phi(N_1,N_{2})} \ar[d]_1 &
-    \mathbb{F}(B) \ar[r]|{|}^{\mathbb{F}(N_1)} &
-    \mathbb{F}(C) \ar[d]^{1} \\
-    \mathbb{F}(A') \ar[r]|{|}_{\mathbb{F}(N_{4})} \ar@{}[drr]|{\phi(N_{3},N_{4})} \ar[d]_1&
-    \mathbb{F}(B') \ar[r]|{|}_{\mathbb{F}(N_{3})} &
-    \mathbb{F}(C') \ar[d]^{1}&
+    \lF(A) \ar[r]|{|}^{\lF(N_{2})} \ar@{}[drr]|{\phi(N_1,N_{2})} \ar[d]_1 &
+    \lF(B) \ar[r]|{|}^{\lF(N_1)} &
+    \lF(C) \ar[d]^{1} \\
+    \lF(A') \ar[r]|{|}_{\lF(N_{4})} \ar@{}[drr]|{\phi(N_{3},N_{4})} \ar[d]_1&
+    \lF(B') \ar[r]|{|}_{\lF(N_{3})} &
+    \lF(C') \ar[d]^{1}&
     = &
-    \mathbb{F}(A) \ar[rr]|{|}^{\mathbb{F}(N_1 \odot N_{2})} \ar[d] \ar@{}[drr]|{\mathbb{F}(\beta \odot \alpha)}&
+    \lF(A) \ar[rr]|{|}^{\lF(N_1 \odot N_{2})} \ar[d] \ar@{}[drr]|{\lF(\beta \odot \alpha)}&
      &
-    \mathbb{F}(C) \ar[d] \\
-    \mathbb{F}(A') \ar[rr]|{|}_{\mathbb{F}(N_{3} \odot N_{4})} & 
+    \lF(C) \ar[d] \\
+    \lF(A') \ar[rr]|{|}_{\lF(N_{3} \odot N_{4})} & 
      & 
-    \mathbb{F}(C') &
+    \lF(C') &
      &
-    \mathbb{F}(A') \ar[rr]|{|}_{\mathbb{F}(N_{3} \odot N_{4})} &
+    \lF(A') \ar[rr]|{|}_{\lF(N_{3} \odot N_{4})} &
      &
-    \mathbb{F}(C') \\
+    \lF(C') \\
   }.
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (1,1) {$\mathbb{F}(N) \odot 1_{\mathbb{F}(A)}$};
-\node (C) at (3,1) {$\mathbb{F}(N)$};
-\node (A') at (1,-1) {$\mathbb{F}(N) \odot \mathbb{F}(1_{A})$};
-\node (C') at (3,-1) {$\mathbb{F}(N \odot 1_{A})$};
-\node (B) at (5,1) {$1_{\mathbb{F}(B)} \odot \mathbb{F}(N)$};
-\node (B') at (5,-1) {$\mathbb{F}(1_{B}) \odot \mathbb{F}(N)$};
-\node (D) at (7,1) {$\mathbb{F}(N)$};
-\node (D') at (7,-1) {$\mathbb{F}(1_{B} \odot N)$};
+\node (A) at (1,1) {$\lF(N) \odot 1_{\lF(A)}$};
+\node (C) at (3,1) {$\lF(N)$};
+\node (A') at (1,-1) {$\lF(N) \odot \lF(1_{A})$};
+\node (C') at (3,-1) {$\lF(N \odot 1_{A})$};
+\node (B) at (5,1) {$1_{\lF(B)} \odot \lF(N)$};
+\node (B') at (5,-1) {$\lF(1_{B}) \odot \lF(N)$};
+\node (D) at (7,1) {$\lF(N)$};
+\node (D') at (7,-1) {$\lF(1_{B} \odot N)$};
 \path[->,font=\scriptsize,>=angle 90]
 (A) edge node[left]{$1 \odot \phi_{A}$} (A')
-(C') edge node[right]{$\mathbb{F} \rho$} (C)
-(A) edge node[above]{$\rho_{\mathbb{F}(N)}$} (C)
+(C') edge node[right]{$\lF \rho$} (C)
+(A) edge node[above]{$\rho_{\lF(N)}$} (C)
 (A') edge node[above]{$\phi(N,1_{A})$} (C')
@@
 (B') edge node[above]{$\phi(1_{B},N)$} (D')
-(B) edge node[above]{$\lambda_{\mathbb{F}(N)}$} (D)
+(B) edge node[above]{$\lambda_{\lF(N)}$} (D)
 (D') edge node[right]{$F \lambda$} (D);
@@
  \[\xymatrix{
-    (\mathbb{F}(N_1) \odot \mathbb{F}(N_{2})) \odot \mathbb{F}(N_{3}) \ar[r]^{a'}\ar[d]_{\phi(N_1,N_{2}) \odot 1}
-    & \mathbb{F}(N_1) \odot (\mathbb{F}(N_{2}) \odot \mathbb{F}(N_{3})) \ar[d]^{1 \odot \phi(N_{2},N_{3})}\\
-    \mathbb{F}(N_1 \odot N_{2}) \odot \mathbb{F}(N_{3}) \ar[d]_{\phi(N_1 \odot N_{2},N_{3})} &
-    \mathbb{F}(N_1) \odot \mathbb{F}(N_{2} \odot N_{3}) \ar[d]^{\phi(N_1,N_{2} \odot N_{3})}\\
-    \mathbb{F}((N_1 \odot N_{2}) \odot N_{3})\ar[r]^{\mathbb{F}a} &
-    \mathbb{F}(N_1 \odot (N_{2} \odot N_{3}))}\]
+    (\lF(N_1) \odot \lF(N_{2})) \odot \lF(N_{3}) \ar[r]^{a'}\ar[d]_{\phi(N_1,N_{2}) \odot 1}
+    & \lF(N_1) \odot (\lF(N_{2}) \odot \lF(N_{3})) \ar[d]^{1 \odot \phi(N_{2},N_{3})}\\
+    \lF(N_1 \odot N_{2}) \odot \lF(N_{3}) \ar[d]_{\phi(N_1 \odot N_{2},N_{3})} &
+    \lF(N_1) \odot \lF(N_{2} \odot N_{3}) \ar[d]^{\phi(N_1,N_{2} \odot N_{3})}\\
+    \lF((N_1 \odot N_{2}) \odot N_{3})\ar[r]^{\lF(a)} &
+    \lF(N_1 \odot (N_{2} \odot N_{3}))}\]
 \end{enumerate}
-We say the double functor $\mathbb{F}$ is \define{strict} if the comparison constraints $\phi_a$ and $\phi_{N_1,N_2}$ are identities, \define{pseudo} if the comparison constraints are isomorphisms, and \define{oplax} if the comparison constraints go in the opposite direction.
+We say the double functor $\lF$ is \define{strict} if the comparison constraints $\phi_a$ and $\phi_{N_1,N_2}$ are identities, \define{pseudo} if the comparison constraints are isomorphisms, and \define{oplax} if the comparison constraints go in the opposite direction.
 \end{defn}
@@
 %!!! Christina: Pretty sure the def below can be incorporated above, however got a bit lost in different notation. Kenny Fix?
-\begin{defn}
-A double functor $\mathbb{F} \maps \mathbb{A} \to \mathbb{X}$ is \define{strong} if the comparison and unit constraints are globular isomorphisms, meaning that for each composable pair of horizontal 1-cells $M$ and $N$ we have a natural isomorphism $$\mathbb{F}_{M,N} \maps \mathbb{F}(M) \odot \mathbb{F}(N) \xrightarrow{\sim} \mathbb{F}(M \odot N)$$and for each object $a \in \mathbb{A}$ a natural isomorphism $$\mathbb{F}_a \maps \hat{U}_{\mathbb{F}(a)} \xrightarrow{\sim} \mathbb{F}(U_a).$$
-\end{defn}
-
-Following the notation of Shulman \cite{Shulman2010}, given a double category $\mathbb{A}$, we write $_f \mathbb{A}_g(M,N)$ for the set of 2-morphisms in $\mathbb{A}$ of the form:
-\[
-  \xymatrix@-.5pc{
-    A \ar[r]|{|}^{M}  \ar[d]_f \ar@{}[dr]|{\Downarrow a}&
-    B\ar[d]^g\\
-    C \ar[r]|{|}_N & D
-  }
-\]
+%\begin{defn}
+%A double functor $\lF \maps \lA \to \lX$ is \define{strong} if the comparison and unit constraints are globular isomorphisms, meaning that for each composable pair of horizontal 1-cells $M$ and $N$ we have a natural isomorphism $$\lF_{M,N} \maps \lF(M) \odot \lF(N) \xrightarrow{\sim} \lF(M \odot N)$$and for each object $a \in \lA$ a natural isomorphism $$\lF_a \maps \hat{U}_{\lF(a)} \xrightarrow{\sim} \lF(U_a).$$
+%\end{defn}
+
+%Following the notation of Shulman \cite{Shulman2010}, given a double category $\lA$, we write $_f \lA_g(M,N)$ for the set of 2-morphisms in $\lA$ of the form:
+%\[
+% \xymatrix@-.5pc{
+%   A \ar[r]|{|}^{M}  \ar[d]_f \ar@{}[dr]|{\Downarrow a}&
+%    B\ar[d]^g\\
+%    C \ar[r]|{|}_N & D
+%  }
+%\]
 We call $M$ and $N$ the \define{horizontal source and target} of the 2-morphism $a$, respectively, and likewise we call $f$ and $g$ the \define{vertical source and target} of the 2-morphism $a$, respectively.
-Thus $_f \mathbb{A}_g(M,N)$ denotes the set of 2-morphisms in $\mathbb{A}$ with horizontal source and target $M$ and $N$ and vertical source and target $f$ and $g$.
+Thus $_f \lA_g(M,N)$ denotes the set of 2-morphisms in $\lA$ with horizontal source and target $M$ and $N$ and vertical source and target $f$ and $g$.
+
 \begin{defn}\label{def:fullfaithful}
-A (possibly lax or oplax) double functor $\mathbb{F} \maps \mathbb{A} \to \mathbb{X}$ is \define{full} (respectively, \define{faithful}) if $\mathbb{F}_0 \maps \mathbb{A}_0 \to \mathbb{X}_0$ is full (respectively, faithful) and each map $$\mathbb{F}_1 \maps _f \mathbb{A}_g(M,N) \to _{\mathbb{F}(f)} \mathbb{X}_{\mathbb{F}(g)}(\mathbb{F}(M),\mathbb{F}(N))$$ is surjective (respectively, injective).
+A double functor $\lF \maps \lA \to \lX$ is \define{full} (respectively, \define{faithful}) if $\lF_0 \maps \lA_0 \to \lX_0$ is full (respectively, faithful) and each map $$\lF_1 \maps _f \lA_g(M,N) \to _{\lF(f)} \lX_{\lF(g)}(\lF(M),\lF(N))$$ is surjective (respectively, injective).
 \end{defn}
 \begin{defn}\label{def:essentiallysurj}
-A (possibly lax or oplax) double functor $\mathbb{F} \maps \mathbb{A} \to \mathbb{X}$ is \define{essentially surjective} if we can simultaneously make the following choices:
+A double functor $\lF \maps \lA \to \lX$ is \define{essentially surjective} if we can simultaneously make the following choices:
 \begin{enumerate}
-\item{For each object $x \in \mathbb{X}$, we can find an object $a \in \mathbb{A}$ together with a vertical 1-isomorphism $\alpha_x \maps \mathbb{F}(a) \to x$, and}
-\item{For each horizontal 1-cell $N \maps x_1 \tobar x_2$  of $\mathbb{X}$, we can find a horizontal 1-cell $M \maps a_1 \tobar a_2$ of $\mathbb{A}$ and a 2-isomorphism $a_{N}$ of $\mathbb{X}$ as in the following diagram:
+\item{For each object $x \in \lX$, we can find an object $a \in \lA$ together with a vertical 1-isomorphism $\alpha_x \maps \lF(a) \to x$, and}
+\item{For each horizontal 1-cell $N \maps x_1 \tobar x_2$  of $\lX$, we can find a horizontal 1-cell $M \maps a_1 \tobar a_2$ of $\lA$ and a 2-isomorphism $a_{N}$ of $\lX$ as in the following diagram:
 \[
   \xymatrix@-.5pc{
-    \mathbb{F}(a_1) \ar[r]|{|}^{\mathbb{F}(M)}  \ar[d]_{\alpha_{x_1}} \ar@{}[dr]|{\Downarrow a_N}&
-    \mathbb{F}(a_1) \ar[d]^{\alpha_{x_2}}\\
+    \lF(a_1) \ar[r]|{|}^{\lF(M)}  \ar[d]_{\alpha_{x_1}} \ar@{}[dr]|{\Downarrow a_N}&
+    \lF(a_1) \ar[d]^{\alpha_{x_2}}\\
     x_1 \ar[r]|{|}_N & x_2
@@
 Formally, two strong double functors between two double categories form a \emph{double equivalence} if ...
+% FINISH THIS OR DISCARD IT!!!
 %{\chris their two-way composite is isomorphic to the identity, better expressed, possibly in a definition environment}. 
-Similarly to ordinary equivalence of categories, [Shulman,7.8] allows us to use the following equivalent characterization.
-
-\begin{thm}\label{ShulDubEquiv}
-A strong double functor $\mathbb{F} \maps \mathbb{A} \to \mathbb{X}$ is part of a double equivalence if and only if it is full, faithful and essentially surjective.
+Much like equivalence of categories, equivalence of double categories has an alternative characterization:
+
+\begin{thm}{\cite[Thm.\ 7.8]{Shulman2010}}
+\label{ShulDubEquiv}
+A strong double functor $\lF \maps \lA \to \lX$ is part of a double equivalence if and only if it is full, faithful and essentially surjective.
 \end{thm}
 
-\begin{prop}
-Let $\mathbb{A}$ and $\mathbb{X}$ be symmetric monoidal double categories and let $\mathbb{F} \maps \mathbb{A} \to \mathbb{X}$ be a symmetric monoidal strong double functor.
-If $\mathbb{F}$ is part of a double equivalence, then $\mathbb{F}$ is in fact part of a symmetric monoidal double equivalence, and $\mathbb{A}$ and $\mathbb{X}$ are equivalent as symmetric monoidal double categories.
-\end{prop}
+\begin{thm}
+Let $\lA$ and $\lX$ be symmetric monoidal double categories and let $\lF \maps \lA \to \lX$ be a symmetric monoidal strong double functor.
+If $\lF$ is part of a double equivalence, then $\lF$ is in fact part of a symmetric monoidal double equivalence, and $\lA$ and $\lX$ are equivalent as symmetric monoidal double categories.
+\end{thm}
+
+\begin{proof} Where is this proved???  \end{proof}
 
@@
 		\setcounter{enumi}{\value{mondbl}}
-		\item $\lD_{0}$ and $\lD_1$ are braided monoidal categories.
+		\item $\lD_0$ and $\lD_1$ are braided monoidal categories.
 		\item The functors $S$ and $T$ are strict braided monoidal functors.
@@
 		\setcounter{enumi}{\value{mondbl}}
-		\item $\lD_{0}$ and $\lD_1$ are symmetric monoidal.
+		\item $\lD_0$ and $\lD_1$ are symmetric monoidal.
 	\end{enumerate}
@@
 We say that a double category is \textbf{fibrant} if every vertical
-1-morphism has both a companion and a conjoint and \define{isofibrant} if every vertical 1-isomorphism has both a companion and a conjoint.
+1-morphism has both a companion and a conjoint.  % and \define{isofibrant} if every vertical 1-isomorphism has both a companion and a conjoint.
 \end{defn}
@@
 \label{defn:monoidal_double_functor}
-A \define{(strong) monoidal lax double functor} $\mathbb{F} \maps \mathbb{C} \to \mathbb{D}$ between monoidal double categories $\mathbb{C}$ and $\mathbb{D}$ is a lax double functor $\mathbb{F} \maps \mathbb{C} \to \mathbb{D}$ such that
+A \define{(strong) monoidal double functor} $\lF \maps \mathbb{C} \to \mathbb{D}$ between monoidal double categories $\mathbb{C}$ and $\mathbb{D}$ is a double functor $\lF \maps \mathbb{C} \to \mathbb{D}$ such that
 	\begin{itemize}
-		\item $\mathbb{F}_0$ and $\mathbb{F}_1$ are monoidal functors, meaning that there exists
+		\item $\lF_0$ and $\lF_1$ are monoidal functors, meaning that there exists
 
 \begin{enumerate}
-\item{an isomorphism $\epsilon \maps 1_{\lD} \to \mathbb{F}(1_{\lC})$}
-\item{a natural isomorphism $\mu_{A,B} \maps \mathbb{F}(A) \otimes \mathbb{F}(B) \to \mathbb{F}(A \otimes B)$ for all objects $A$ and $B$ of $\lC$}
-\item{an isomorphism $\delta \maps U_{1_{\lD}} \to \mathbb{F}(U_{1_{\lC}})$}
-\item{a natural isomorphism $\nu_{M,N} \maps \mathbb{F}(M) \otimes \mathbb{F}(N) \to \mathbb{F}(M \otimes N)$ for all horizontal 1-cells $N$ and $M$ of $\lC$}
+\item{an isomorphism $\epsilon \maps 1_{\lD} \to \lF(1_{\lC})$}
+\item{a natural isomorphism $\mu_{A,B} \maps \lF(A) \otimes \lF(B) \to \lF(A \otimes B)$ for all objects $A$ and $B$ of $\lC$}
+\item{an isomorphism $\delta \maps U_{1_{\lD}} \to \lF(U_{1_{\lC}})$}
+\item{a natural isomorphism $\nu_{M,N} \maps \lF(M) \otimes \lF(N) \to \lF(M \otimes N)$ for all horizontal 1-cells $N$ and $M$ of $\lC$}
 \end{enumerate}
@@
  \[\xymatrix{
-    (\mathbb{F}(A) \otimes \mathbb{F}(B)) \otimes \mathbb{F}(C) \ar[r]^{\alpha'}\ar[d]_{\mu_{A,B} \otimes 1}
-    & \mathbb{F}(A) \otimes (\mathbb{F}(B) \otimes \mathbb{F}(C)) \ar[d]^{1 \otimes \mu_{B,C}}\\
-    \mathbb{F}(A \otimes B) \otimes \mathbb{F}(C) \ar[d]_{\mu_{A \otimes B,C}} &
-    \mathbb{F}(A) \otimes \mathbb{F}(B \otimes C) \ar[d]^{\mu_{A,B \otimes C}}\\
-    \mathbb{F}((A \otimes B) \otimes C)\ar[r]^{\mathbb{F}\alpha} &
-    \mathbb{F}(A \otimes (B \otimes C))}\]
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (1,1) {$\mathbb{F}(A) \otimes 1_{\lD}$};
-\node (C) at (3,1) {$\mathbb{F}(A)$};
-\node (A') at (1,-1) {$\mathbb{F}(A) \otimes \mathbb{F}(1_{\lC})$};
-\node (C') at (3,-1) {$\mathbb{F}(A \otimes 1_{\lC})$};
-\node (B) at (5,1) {$1_{\lD} \otimes \mathbb{F}(A)$};
-\node (B') at (5,-1) {$\mathbb{F}(1_{\lC}) \otimes \mathbb{F}(A)$};
-\node (D) at (7,1) {$\mathbb{F}(A)$};
-\node (D') at (7,-1) {$\mathbb{F}(1_{\lC} \otimes A)$};
+    (\lF(A) \otimes \lF(B)) \otimes \lF(C) \ar[r]^{\alpha'}\ar[d]_{\mu_{A,B} \otimes 1}
+    & \lF(A) \otimes (\lF(B) \otimes \lF(C)) \ar[d]^{1 \otimes \mu_{B,C}}\\
+    \lF(A \otimes B) \otimes \lF(C) \ar[d]_{\mu_{A \otimes B,C}} &
+    \lF(A) \otimes \lF(B \otimes C) \ar[d]^{\mu_{A,B \otimes C}}\\
+    \lF((A \otimes B) \otimes C)\ar[r]^{\lF\alpha} &
+    \lF(A \otimes (B \otimes C))}\]
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (1,1) {$\lF(A) \otimes 1_{\lD}$};
+\node (C) at (3,1) {$\lF(A)$};
+\node (A') at (1,-1) {$\lF(A) \otimes \lF(1_{\lC})$};
+\node (C') at (3,-1) {$\lF(A \otimes 1_{\lC})$};
+\node (B) at (5,1) {$1_{\lD} \otimes \lF(A)$};
+\node (B') at (5,-1) {$\lF(1_{\lC}) \otimes \lF(A)$};
+\node (D) at (7,1) {$\lF(A)$};
+\node (D') at (7,-1) {$\lF(1_{\lC} \otimes A)$};
 \path[->,font=\scriptsize,>=angle 90]
 (A) edge node[left]{$1 \otimes \epsilon$} (A')
-(C') edge node[right]{$\mathbb{F}(r_{A})$} (C)
-(A) edge node[above]{$r_{\mathbb{F}(A)}$} (C)
+(C') edge node[right]{$\lF(r_{A})$} (C)
+(A) edge node[above]{$r_{\lF(A)}$} (C)
 (A') edge node[above]{$\mu_{A,1_{\lC}}$} (C')
@@
 (B') edge node[above]{$\mu_{1_{\lC},A}$} (D')
-(B) edge node[above]{$\ell_{\mathbb{F}(A)}$} (D)
-(D') edge node[right]{$\mathbb{F}(\ell_{A})$} (D);
+(B) edge node[above]{$\ell_{\lF(A)}$} (D)
+(D') edge node[right]{$\lF(\ell_{A})$} (D);
 \end{tikzpicture}
@@
  \[\xymatrix{
-    (\mathbb{F}(N_1) \otimes \mathbb{F}(N_{2})) \otimes \mathbb{F}(N_{3}) \ar[r]^{\alpha'}\ar[d]_{\nu_{N_1,N_{2}} \otimes 1}
-    & \mathbb{F}(N_1) \otimes (\mathbb{F}(N_{2}) \otimes \mathbb{F}(N_{3})) \ar[d]^{1 \otimes \nu_{N_{2},N_{3}}}\\
-    \mathbb{F}(N_1 \otimes N_{2}) \otimes \mathbb{F}(N_{3}) \ar[d]_{\nu_{N_1 \otimes N_{2},N_{3}}} &
-    \mathbb{F}(N_1) \otimes \mathbb{F}(N_{2} \otimes N_{3}) \ar[d]^{\nu_{N_1,N_{2} \otimes N_{3}}}\\
-    \mathbb{F}((N_1 \otimes N_{2}) \otimes N_{3})\ar[r]^{\mathbb{F}\alpha} &
-    \mathbb{F}(N_1 \otimes (N_{2} \otimes N_{3}))}\]
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,1) {$\mathbb{F}(N_1) \otimes U_{1_{\lD}}$};
-\node (C) at (3,1) {$\mathbb{F}(N_1)$};
-\node (A') at (0,-1) {$\mathbb{F}(N_1) \otimes \mathbb{F}(U_{1_{\lC}})$};
-\node (C') at (3,-1) {$\mathbb{F}(N_1 \otimes U_{1_{\lC}})$};
-\node (B) at (5,1) {$U_{1_{\lD}} \otimes \mathbb{F}(N_1)$};
-\node (B') at (5,-1) {$\mathbb{F}(U_{1_{\lC}}) \otimes \mathbb{F}(N_1)$};
-\node (D) at (8,1) {$\mathbb{F}(N_1)$};
-\node (D') at (8,-1) {$\mathbb{F}(U_{1_{\lC}} \otimes N_1)$};
+    (\lF(N_1) \otimes \lF(N_{2})) \otimes \lF(N_{3}) \ar[r]^{\alpha'}\ar[d]_{\nu_{N_1,N_{2}} \otimes 1}
+    & \lF(N_1) \otimes (\lF(N_{2}) \otimes \lF(N_{3})) \ar[d]^{1 \otimes \nu_{N_{2},N_{3}}}\\
+    \lF(N_1 \otimes N_{2}) \otimes \lF(N_{3}) \ar[d]_{\nu_{N_1 \otimes N_{2},N_{3}}} &
+    \lF(N_1) \otimes \lF(N_{2} \otimes N_{3}) \ar[d]^{\nu_{N_1,N_{2} \otimes N_{3}}}\\
+    \lF((N_1 \otimes N_{2}) \otimes N_{3})\ar[r]^{\lF\alpha} &
+    \lF(N_1 \otimes (N_{2} \otimes N_{3}))}\]
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,1) {$\lF(N_1) \otimes U_{1_{\lD}}$};
+\node (C) at (3,1) {$\lF(N_1)$};
+\node (A') at (0,-1) {$\lF(N_1) \otimes \lF(U_{1_{\lC}})$};
+\node (C') at (3,-1) {$\lF(N_1 \otimes U_{1_{\lC}})$};
+\node (B) at (5,1) {$U_{1_{\lD}} \otimes \lF(N_1)$};
+\node (B') at (5,-1) {$\lF(U_{1_{\lC}}) \otimes \lF(N_1)$};
+\node (D) at (8,1) {$\lF(N_1)$};
+\node (D') at (8,-1) {$\lF(U_{1_{\lC}} \otimes N_1)$};
 \path[->,font=\scriptsize,>=angle 90]
 (A) edge node[left]{$1 \otimes \delta$} (A')
-(C') edge node[right]{$\mathbb{F}(r_{N_1})$} (C)
-(A) edge node[above]{$r_{\mathbb{F}(N_1)}$} (C)
+(C') edge node[right]{$\lF(r_{N_1})$} (C)
+(A) edge node[above]{$r_{\lF(N_1)}$} (C)
 (A') edge node[above]{$\nu_{N_1,U_{1_{\lC}}}$} (C')
@@
 (B') edge node[above]{$\nu_{U_{1_{\lC}},N_1}$} (D')
-(B) edge node[above]{$\ell_{\mathbb{F}(N_1)}$} (D)
-(D') edge node[right]{$\mathbb{F}(\ell_{N_1})$} (D);
-\end{tikzpicture}
-\]
-
-		\item $S\mathbb{F}_1= \mathbb{F}_0S$ and $T\mathbb{F}_1 = \mathbb{F}_0T$ are equations between monoidal functors, and
-		\item the composition and unit comparisons $\phi(N_1,N_2) \maps \mathbb{F}_1(N_1) \odot \mathbb{F}_1(N_2) \to \mathbb{F}_1(N_1\odot N_2)$ and $\phi_A \maps U_{\mathbb{F}_0 (A)} \to \mathbb{F}_1(U_A)$ are monoidal natural transformations.
+(B) edge node[above]{$\ell_{\lF(N_1)}$} (D)
+(D') edge node[right]{$\lF(\ell_{N_1})$} (D);
+\end{tikzpicture}
+\]
+
+		\item $S\lF_1= \lF_0S$ and $T\lF_1 = \lF_0T$ are equations between monoidal functors, and
+		\item the composition and unit comparisons $\phi(N_1,N_2) \maps \lF_1(N_1) \odot \lF_1(N_2) \to \lF_1(N_1\odot N_2)$ and $\phi_A \maps U_{\lF_0 (A)} \to \lF_1(U_A)$ are monoidal natural transformations.
 	\end{itemize}
-The monoidal lax double functor is \define{braided} if $\mathbb{F}_0$ and $\mathbb{F}_1$ are braided monoidal functors and \define{symmetric} if they are symmetric monoidal functors, and lax monoidal or oplax monoidal if the isomorphisms and families of natural isomorphisms of items (1)-(4) above are merely morphisms and natural transformations going in the appropriate directions.
+A monoidal double functor $\lF$ is \define{braided} if $\lF_0$ and $\lF_1$ are braided monoidal functors and \define{symmetric} if they are symmetric monoidal.
 \end{defn}

### 2020-11-17 cospans.tex
polished up material around Theorem 2.3

@@
 The coherence diagram that we will check is given by:
+The remaining properties are coherence laws that make use of these maps $\chi$ and $\mu$, the previously defined symmetric monoidal structure maps $\alpha,\lambda,\rho$ and $\beta$ and the double category structure functors $U$ and $\odot$.
+We exhibit one of these laws to give the reader a sense of how they are verified, with more details available in the second author's thesis \cite{CourserThesis}.
+The coherence law that we check says that this diagram commutes:
 \[

### 2020-11-17 cospans.tex
polished material around Theorem 2.3

@@
 which expresses that the braiding is a transformation of double categories.
+This expresses that the braiding is a transformation of double categories.
 
@@
 
+Our construction gives not only decorated cospan double categories, but maps betwen these.
+Suppose we have two symmetric lax monoidal pseudofunctors, $F \maps \A \to \Cat$ and
+$F' \maps \A' \to \Cat$.    Then we can obtain a map between their decorated cospan 
+double categories, $\lH \maps F\lCsp \to F' \lCsp$, from:
+\begin{itemize}
+\item a finitely cocontinous functor $H \maps \A \to \A'$, 
+\item a symmetric lax monoidal pseudofunctor $E \maps \Cat \to \Cat$, 
+\item an isomorphism $\theta \maps EF \Rightarrow F'H$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$\A$};
+\node (B) at (1,0) {$\Cat$};
+\node (C) at (0,-1) {$\A'$};
+\node (D) at (1,-1) {$\Cat$.};
+\node (E) at (0.5,-0.5) {$\Swarrow \theta$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$F$} (B)
+(A) edge node[left]{$H$} (C)
+(B) edge node[right]{$E$} (D)
+(C) edge node[above]{$F'$} (D);
+\end{tikzpicture}
+\]
+\end{itemize}
+
 Regarding maps between symmetric monoidal double categories, consider another symmetric lax monoidal pseudofunctor $F' \maps \mathsf{A'} \to \Cat$%, we can obtain another symmetric monoidal double category $F' \lCsp$.
@@
 \node (D) at (2,-0.5) {$\mathbb{H}(M \odot N) = \theta_{c_1 +_b c_2}E(d_{M \odot N}) \phi \in F'(H(c_1 +_b c_2))$};
+\node (D) at (2,-0.5) {$\lH(M \odot N) = \theta_{c_1 +_b c_2}E(d_{M \odot N}) \phi \in F'(H(c_1 +_b c_2))$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 where $$\mathbb{H}(M \odot N) = \theta_{c_1 +_b c_2} E(d_{M \odot N}) \phi \maps 1 \xrightarrow{\phi} E(1) \xrightarrow{E(d)} E(F(c_1 +_b c_2)) \xrightarrow{\theta_{c_1 +_b c_2}} F'(H(c_1 +_b c_2)).$$ On the other hand, the image of each horizontal 1-cell under the double functor $\mathbb{H}$ is given respectively by $\mathbb{H}(M)$ and $\mathbb{H}(N)$:
+where $$\lH(M \odot N) = \theta_{c_1 +_b c_2} E(d_{M \odot N}) \phi \maps 1 \xrightarrow{\phi} E(1) \xrightarrow{E(d)} E(F(c_1 +_b c_2)) \xrightarrow{\theta_{c_1 +_b c_2}} F'(H(c_1 +_b c_2)).$$ On the other hand, the image of each horizontal 1-cell under the double functor $\lH$ is given respectively by $\lH(M)$ and $\lH(N)$:
 \[
@@
 \node (G) at (2.5,-1) {$\tau_{\kappa^{-1}} \maps F'(\kappa^{-1})(d_{\mathbb{H}(M) \odot \mathbb{H}(N)}) \to d_{\mathbb{H}(M \odot N)}.$};
+\node (E) at (7.5,0.5) {$d_{\lH(M) \odot \lH(N)} \in F'(H(c_1)+_{H(b_1)}H(c_2))$};
+\node (F) at (7.5,-0.5) {$d_{\lH(M \odot N)} \in F'(H(c_1 +_b c_2))$};
+\node (G) at (2.5,-1) {$\tau_{\kappa^{-1}} \maps F'(\kappa^{-1})(d_{\lH(M) \odot \lH(N)}) \to d_{\lH(M \odot N)}.$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 Similarly, for every object $c \in \A$, we have a unit comparison constraint $$\mathbb{H}_U \maps U_{\mathbb{H}(c)} \to \mathbb{H}(U_c)$$ given by the globular 2-isomorphism:
+where $\kappa$ is the isomorphism $$\kappa \maps H(c_1 +_b c_2) \xrightarrow{\sim} H(c_1) +_{H(b)} H(c_2)$$ which comes from the finite colimit preserving functor $H \maps \A \to \A'$.
+The above diagram commutes by a similar argument to the one used in \cref{thm:equiv}.
+Similarly, for every object $c \in \A$, we have a unit comparison constraint $$\lH_U \maps U_{\lH(c)} \to \lH(U_c)$$ given by the globular 2-isomorphism:
 \[

### 2020-11-17 cospans.tex
Update cospans.tex

@@
 \node (D') at (7.5,-1) {$\mathbb{H}(M \odot U_b)$};
+\node (A) at (0,0) {$U_{\lH(a)} \odot \lH(M)$};
+\node (B) at (2.5,0) {$\lH(U_a) \odot \lH(M)$};
+\node (C) at (0,-1) {$\lH(M)$};
+\node (D) at (2.5,-1) {$\lH(U_a \odot M)$};
+\node (A') at (5,0) {$\lH(M) \odot U_{\lH(b)}$};
+\node (B') at (7.5,0) {$\lH(M) \odot \lH(U_b)$};
+\node (C') at (5,-1) {$\lH(M)$};
+\node (D') at (7.5,-1) {$\lH(M \odot U_b)$};
 \path[->,font=\scriptsize,>=angle 90]
 (A) edge node[above]{$\mathbb{H}_U \odot 1$} (B)
+(A) edge node[above]{$\lH_U \odot 1$} (B)
 (A) edge node[left]{$\lambda$} (C)
@@
 (A') edge node[above]{$1 \odot \mathbb{H}_U$} (B')
+(B) edge node[right]{$\lH_{U_a,M}$} (D)
+(D) edge node[above]{$\lH(\lambda')$} (C)
+(A') edge node[above]{$1 \odot \lH_U$} (B')
 (A') edge node[left]{$\rho$} (C')
@@
 (D') edge node[above]{$\mathbb{H}(\rho')$} (C');
+(B') edge node[right]{$\lH_{M,U_b}$} (D')
+(D') edge node[above]{$\lH(\rho')$} (C');
 \end{tikzpicture}
@@
 As for the arrow component $\mathbb{H}_1$, given two horizontal 1-cells $M_1$ and $M_2$ in $F\lCsp$:
+The diagrams involving the morphisms of decorations are similar to those in Theorem \cref{DC}.
+This shows that $\lH=(H,E,\theta)$ is a double functor.
+Next we show that this double functor is symmetric monoidal.
+First, that the object component $\lH_0=H$ is symmetric monoidal is clear as $H \maps \A \to \A'$ preserves finite colimits.
+As for the arrow component $\lH_1$, given two horizontal 1-cells $M_1$ and $M_2$ in $F\lCsp$:
 \[
@@
 and the image of this horizontal 1-cell under the double functor $\mathbb{H}$ is $\mathbb{H}(M_1 \otimes M_2)$ given by:
+and the image of this horizontal 1-cell under the double functor $\lH$ is $\lH(M_1 \otimes M_2)$ given by:
 \[
@@
 \node (D) at (2,-0.5) {$d_{\mathbb{H}(M_1 \otimes M_2)} = \theta_{c_1+c_2} E(d_{M_1 \otimes M_2})\phi \in F'(H(c_1+c_2))$};
+\node (D) at (2,-0.5) {$d_{\lH(M_1 \otimes M_2)} = \theta_{c_1+c_2} E(d_{M_1 \otimes M_2})\phi \in F'(H(c_1+c_2))$};
 \path[->,font=\scriptsize,>=angle 90]

### 2020-11-17 cospans.tex
Update cospans.tex

@@
 On the other hand, the image of $M_1$ and $M_2$ is given by $\mathbb{H}(M_1)$ and $\mathbb{H}(M_2)$:
+On the other hand, the image of $M_1$ and $M_2$ is given by $\lH(M_1)$ and $\lH(M_2)$:
 \[
@@
 \node (D) at (1.5,-0.5) {$d_{\mathbb{H}(M_1)} = \theta_{c_1}E(d_{M_1})\phi \in F'(H(c_1))$};
+\node (D) at (1.5,-0.5) {$d_{\lH(M_1)} = \theta_{c_1}E(d_{M_1})\phi \in F'(H(c_1))$};
 \node (E) at (4.5,0) {$H(a_2)$};
@@
 \node (H) at (6,-0.5) {$d_{\mathbb{H}(M_2)} = \theta_{c_2}E(d_{M_2})\phi \in F'(H(c_2))$};
+\node (H) at (6,-0.5) {$d_{\lH(M_2)} = \theta_{c_2}E(d_{M_2})\phi \in F'(H(c_2))$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 and their tensor product $\mathbb{H}(M_1) \otimes \mathbb{H}(M_2)$ is given by:
+and their tensor product $\lH(M_1) \otimes \lH(M_2)$ is given by:
 \[
@@
 \node (D) at (2.5,-0.5) {$d_{\mathbb{H}(M_1) \otimes \mathbb{H}(M_2)} \in F'(H(c_1)+H(c_2))$};
+\node (D) at (2.5,-0.5) {$d_{\lH(M_1) \otimes \lH(M_2)} \in F'(H(c_1)+H(c_2))$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 $$\hspace{-.4in} \scriptstyle{d_{\mathbb{H}(M_1) \otimes \mathbb{H}(M_2)} \maps 1 \xrightarrow{(\phi \times \phi)(\lambda^{-1} \times \lambda^{-1})} E(1) \times E(1) \xrightarrow{(\theta_{c_1} \times \theta_{c_2})(E(d_{M_1}) \times E(d_{M_2}))} F'(H(c_1)) \times F'(H(c_2)) \xrightarrow{\Phi_{H(c_1),H(c_2)}} F' (H(c_1)+H(c_2)).}$$  We then have a natural 2-isomorphism $\mu_{M_1,M_2} \maps \mathbb{H}(M_1) \otimes \mathbb{H}(M_2) \to \mathbb{H}(M_1 \otimes M_2)$ in $F'\lCsp$ given by:
+$$\hspace{-.4in} \scriptstyle{d_{\lH(M_1) \otimes \lH(M_2)} \maps 1 \xrightarrow{(\phi \times \phi)(\lambda^{-1} \times \lambda^{-1})} E(1) \times E(1) \xrightarrow{(\theta_{c_1} \times \theta_{c_2})(E(d_{M_1}) \times E(d_{M_2}))} F'(H(c_1)) \times F'(H(c_2)) \xrightarrow{\Phi_{H(c_1),H(c_2)}} F' (H(c_1)+H(c_2)).}$$  We then have a natural 2-isomorphism $\mu_{M_1,M_2} \maps \lH(M_1) \otimes \lH(M_2) \to \lH(M_1 \otimes M_2)$ in $F'\lCsp$ given by:
 \[
@@
 \node (F) at (2.5,-1) {$d_{\mathbb{H}(M_1 \otimes M_2)} \in F'(H(c_1+c_2))$};
+\node (E) at (2.5,1) {$d_{\lH(M_1) \otimes \lH(M_2)} \in F'(H(c_1)+H(c_2))$};
+\node (F) at (2.5,-1) {$d_{\lH(M_1 \otimes M_2)} \in F'(H(c_1+c_2))$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 $$\tau_\kappa \maps F'(\kappa)(d_{\mathbb{H}(M_1) \otimes \mathbb{H}(M_2)}) \to d_{\mathbb{H}(M_1 \otimes M_2)}$$
+$$\tau_\kappa \maps F'(\kappa)(d_{\lH(M_1) \otimes \lH(M_2)}) \to d_{\lH(M_1 \otimes M_2)}$$
 where $\kappa$ denotes the isomorphism arising from $H$ preserving finite colimits.
@@
 \node (C') at (4,-1.5) {$\mathbb{H}(M_1 \otimes (M_2 \otimes M_3))$};
+\node (A) at (0,0.5) {$(\lH(M_1) \otimes \lH(M_2)) \otimes \lH(M_3)$};
+\node (B) at (0,-0.5) {$\lH(M_1 \otimes M_2) \otimes \lH(M_3)$};
+\node (C) at (0,-1.5) {$\lH((M_1 \otimes M_2) \otimes M_3)$};
+\node (A') at (4,0.5) {$\lH(M_1) \otimes (\lH(M_2) \otimes \lH(M_3))$};
+\node (B') at (4,-0.5) {$\lH(M_1) \otimes \lH(M_2 \otimes M_3)$};
+\node (C') at (4,-1.5) {$\lH(M_1 \otimes (M_2 \otimes M_3))$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (C) edge node [above] {$\mathbb{H}(\alpha)$} (C')
+(C) edge node [above] {$\lH(\alpha)$} (C')
 (B') edge node [right] {$\mu_{M_1,M_2 \otimes M_3}$} (C')
@@
 \node (C') at (5,-1.5) {$d_{\mathbb{H}(M_1 \otimes (M_2 \otimes M_3))}$};
+\node (A) at (0,0.5) {$F'(\alpha \kappa \kappa)(d_{(\lH(M_1) \otimes \lH(M_2)) \otimes \lH(M_3)})$};
+\node (B) at (0,-0.5) {$F'(\alpha \kappa)(d_{\lH(M_1 \otimes M_2) \otimes \lH(M_3)})$};
+\node (C) at (0,-1.5) {$F'(\alpha)(d_{\lH((M_1 \otimes M_2) \otimes M_3)})$};
+\node (A') at (5,0.5) {$F'(\kappa \kappa)(d_{\lH(M_1) \otimes (\lH(M_2) \otimes \lH(M_3))})$};
+\node (B') at (5,-0.5) {$F'(\kappa)(d_{\lH(M_1) \otimes \lH(M_2 \otimes M_3)})$};
+\node (C') at (5,-1.5) {$d_{\lH(M_1 \otimes (M_2 \otimes M_3))}$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 The map $\mu_{M_1,M_2}$ is also compatible with the braidings $\beta$ and $\beta'$ of $F \lCsp_1$ and $F' \lCsp_1$, respectively, and make the necessary square commute as a consequence of the corresponding commutative square involving braidings from the finite colimit preserving functor $H \maps \A \to \mathsf{A'}$.
+where $$F'(\alpha \kappa \kappa)(d_{(\lH(M_1) \otimes \lH(M_2)) \otimes \lH(M_3)}) = F'(\kappa \kappa \alpha')(d_{(\lH(M_1) \otimes \lH(M_2)) \otimes \lH(M_3)})$$
+as the corresponding hexagon for the finite colimit preserving functor $H \maps \A \to \A'$ commutes.
+The map $\mu_{M_1,M_2}$ is also compatible with the braidings $\beta$ and $\beta'$ of $F \lCsp_1$ and $F' \lCsp_1$, respectively, and make the necessary square commute as a consequence of the corresponding commutative square involving braidings from the finite colimit preserving functor $H \maps \A \to \A'$.
 
@@
 where $1_\A$ is the monoidal unit of the cocartesian category $\A$. The image of this horizontal 1-cell under $\mathbb{H}$ is given by:
+where $1_\A$ is the monoidal unit of the cocartesian category $\A$. The image of this horizontal 1-cell under $\lH$ is given by:
 \[
@@
 %\node (I) at (5,-0.5) {$!_{1_{\mathsf{A'}}} \in F'(1_{\mathsf{A'}})$};
+%\node (F) at (4,0) {$1_\A'$};
+%\node (G) at (5,0) {$1_\A'$};
+%\node (H) at (6,0) {$1_\A'$};
+%\node (I) at (5,-0.5) {$!_{1_{\A'}} \in F'(1_{\A'})$};
 \node (D) at (1,-0.5) {$\theta_{1_\A}E(!_{1_\A}) \phi \in F'(H(1_\A))$};
@@
 as $H$ preserves finite colimits. We then have a 2-isomorphism in $F'\lCsp$ given by: $$\mu \maps 1_{F'\lCsp_1} \to \mathbb{H}(1_{F\lCsp_1})$$ 
+as $H$ preserves finite colimits. We then have a 2-isomorphism in $F'\lCsp$ given by: $$\mu \maps 1_{F'\lCsp_1} \to \lH(1_{F\lCsp_1})$$ 
 \[
@@
 \node (A) at (0,0.5) {$1_{\mathsf{A'}}$};
+\node (A) at (0,0.5) {$1_{\A'}$};
 \node (A') at (0,-0.5) {$H(1_\A)$};
@@
 \node (C) at (3,0.5) {$1_{\mathsf{A'}}$};
+\node (B) at (1.5,0.5) {$1_{\A'}$};
+\node (C) at (3,0.5) {$1_{\A'}$};
 \node (C') at (3,-0.5) {$H(1_\A)$};
@@
 \node (E) at (5,0.5) {$!_{1_\mathsf{A'}} \in F'(1_\mathsf{A'})$};
+\node (E) at (5,0.5) {$!_{1_\A'} \in F'(1_\A')$};
 \node (F) at (5,-0.5) {$\theta_{1_\A} E(!_{1_\A}) \phi \in F'(H(1_\A))$};
@@
 The following square then commutes for any horizontal 1-cell $M$ of $F \lCsp$:
+together with the morphism $\tau_\mu \maps F'(\kappa)(!_{1_\A'}) \to (\theta_{1_\A} E(!_{1_\A})\phi)$ in $F'(H(1_\A))$. The following square then commutes for any horizontal 1-cell $M$ of $F \lCsp$: 
 \[
@@
 \node (D) at (2.5,-1) {$\mathbb{H}(1_\A \otimes M)$};
+\node (A) at (0,0) {$1_\A' \otimes \lH(M)$};
+\node (B) at (2.5,0) {$\lH(1_\A) \otimes \lH(M)$};
+\node (C) at (0,-1) {$\lH(M)$};
+\node (D) at (2.5,-1) {$\lH(1_\A \otimes M)$};
 \path[->,font=\scriptsize,>=angle 90]

### 2020-11-17 cospans.tex
Update cospans.tex

@@
 Given two finitely cocomplete categories $\A$ and $\A'$, two symmetric lax monoidal pseudofunctors $F \maps \A \to \Cat$ and $F' \maps \A' \to \Cat$, a finite colimit preserving functor $H \maps \A \to \A'$, a symmetric lax monoidal pseudofunctor $E \maps \Cat \to \Cat$ and a 2-isomorphism $\theta \maps EF \Rightarrow F' H$ as in the following diagram, the triple $(H,E,\theta)$ induces a symmetric monoidal (strong) double functor $\mathbb{H} \maps F\lCsp \to F'\lCsp$ as defined above.
+Given two finitely cocomplete categories $\A$ and $\A'$, two symmetric lax monoidal pseudofunctors $F \maps \A \to \Cat$ and $F' \maps \A' \to \Cat$, a finite colimit preserving functor $H \maps \A \to \A'$, a symmetric lax monoidal pseudofunctor $E \maps \Cat \to \Cat$ and a 2-isomorphism $\theta \maps EF \Rightarrow F' H$ as in the following diagram, the triple $(H,E,\theta)$ induces a symmetric monoidal (strong) double functor $\lH \maps F\lCsp \to F'\lCsp$ as defined above.
 \[
@@
 \node (C) at (0,-1) {$\mathsf{A'}$};
+\node (C) at (0,-1) {$\A'$};
 \node (D) at (1,-1) {$\Cat$};
@@
   A \textbf{monoidal double category} is a double category equipped the following
+  A \textbf{monoidal double category} is a double category $\lD$ equipped with the following
 structure.

### 2020-11-17 cospans.tex
Update cospans.tex

@@
 \node (B') at (4,-0.5) {$F'(H(\ell'))(d_{\mathbb{H}(1_\A \otimes M)})$};
+\node (A) at (0,0.5) {$F'(\ell)(d_{!_{1_\A'}} \otimes d_{\lH(M)})$};
+\node (B) at (0,-0.5) {$d_{\lH(M)}$};
+\node (A') at (4,0.5) {$F'(H(\ell') \kappa)(d_{!_{\lH(1_\A)}}\otimes d_{\lH(M)})$};
+\node (B') at (4,-0.5) {$F'(H(\ell'))(d_{\lH(1_\A \otimes M)})$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 Note that because the comparison constraints $\mu$ and $\mu_{(\_ , \_)}$ are both isomorphisms, the symmetric monoidal double functor $\mathbb{H}$ is strong.
+where $$F'(\ell)(d_{!_{1_\A'}} \otimes d_{\lH(M)})=F'(H(\ell')\kappa(\mu \otimes 1))(d_{!_{1_\A'}} \otimes d_{\lH(M)})$$ since the corresponding square involving left unitors for the finite colimit preserving functor $H \maps \A \to \A'$ commutes.
+The other square involving the right unitors $r$ and $r'$ is similar.
+Note that because the comparison constraints $\mu$ and $\mu_{(\_ , \_)}$ are both isomorphisms, the symmetric monoidal double functor $\lH$ is strong.
 

### 2020-11-17 cospans.tex
used \lH for \mathbb{H}
Update cospans.tex

@@
 a morphism from $F\lCsp$ to $F' \lCsp$ will then be a double functor $\mathbb{H} \maps F\lCsp \to F' \lCsp$ whose object component is given by a finite colimit preserving functor $\mathbb{H}_0 = H \maps \A \to \mathsf{A'}$ and whose arrow component is given by a functor $\mathbb{H}_1$ defined on horizontal 1-cells by:
+We define the object component $\lH_0$ to be $H$ and define the arrow component $\lH_1$ on horizontal 1-cells by:
 \[
@@
 (D) edge node[above]{$\mathbb{H}(\ell')$} (C);
+(D) edge node[above]{$\lH(\ell')$} (C);
 \end{tikzpicture}
@@
 where we have abbreviated the monoidal units of $F\lCsp_1$ and $F'\lCsp_1$ as $1_\A$ and $1_\mathsf{A'}$, respectively. The diagram of corresponding decorations is given by:
+where we have abbreviated the monoidal units of $F\lCsp_1$ and $F'\lCsp_1$ as $1_\A$ and $1_\A'$, respectively. The diagram of corresponding decorations is given by:
 \[

### 2020-11-17 cospans.tex
Update cospans.tex

@@
 and then the image of this 2-morphism under the double functor $\mathbb{H}$ is given by:
+and then the image of this 2-morphism under the double functor $\lH$ is given by:
 \[
@@
 On the other hand, applying the double functor $\mathbb{H}$ first gives:
+On the other hand, applying the double functor $\lH$ first gives:
 \[
@@
 This double functor $\mathbb{H}$ satisfies the equations $S \mathbb{H}_1 = HS$ and $T \mathbb{H}_1=HT$.
+This double functor $\lH$ satisfies the equations $S \lH_1 = HS$ and $T \lH_1=HT$.
 
@@
 where $$d \maps 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{d_1 \times d_2} F(c_1) \times F(c_2) \xrightarrow{\phi_{c_1,c_2}} F(c_1+c_2) \xrightarrow{F(j)}F(c_1 +_b c_2).$$ The image of this horizontal 1-cell is then given by $\mathbb{H}(M \odot N)$:
+where $$d \maps 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{d_1 \times d_2} F(c_1) \times F(c_2) \xrightarrow{\phi_{c_1,c_2}} F(c_1+c_2) \xrightarrow{F(j)}F(c_1 +_b c_2).$$ The image of this horizontal 1-cell is then given by $\lH(M \odot N)$:
 \[

### 2020-11-18 cospans.tex
Update cospans.tex
double isomorphism in 3.2

@@
 Composing these then gives $\mathbb{H}(M) \odot \mathbb{H}(N)$:
+Composing these then gives $\lH(M) \odot \lH(N)$:
 \[
@@
 \node (D) at (2.25,-0.5) {$d_{\mathbb{H}(M) \odot \mathbb{H}(N)} \in F'(H(c_1) +_{H(b)} H(c_2))$};
+\node (D) at (2.25,-0.5) {$d_{\lH(M) \odot \lH(N)} \in F'(H(c_1) +_{H(b)} H(c_2))$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 We then have a comparison constraint: $$\mathbb{H}_{M,N} \maps \mathbb{H}(M) \odot \mathbb{H}(N) \xrightarrow{\sim} \mathbb{H}(M \odot N)$$given by the globular 2-isomorphism:
+where $$\hspace{-.4in}\scriptstyle{d_{\lH(M) \odot \lH(N)} \maps 1 \xrightarrow{(\theta_{c_1} \times \theta_{c_2})(E(d_M) \times E(d_N)) \phi} F'(H(c_1)) \times F'(H(c_2)) \xrightarrow{\Phi_{H(c_1),H(c_2)}} F'(H(c_1)+ H(c_2)) \xrightarrow{F' (J)} F'(H(c_1) +_{H(b)} H(c_2)).}$$
+We then have a comparison constraint: $$\lH_{M,N} \maps \lH(M) \odot \lH(N) \xrightarrow{\sim} \lH(M \odot N)$$given by the globular 2-isomorphism:
 \[
@@
 (B) edge node[left]{$\mathbb{H}_{M \odot N,P}$} (C)
+\node (A) at (0,0.5) {$(\lH(M) \odot \lH(N)) \odot \lH(P)$};
+\node (B) at (0,-0.5) {$\lH(M \odot N) \odot \lH(P)$};
+\node (C) at (0,-1.5) {$\lH((M \odot N) \odot P)$};
+\node (A') at (3,0.5) {$\lH(M) \odot (\lH(N) \odot \lH(P))$};
+\node (B') at (3,-0.5) {$\lH(M) \odot \lH(N \odot P)$};
+\node (C') at (3,-1.5) {$\lH(M \odot (N \odot P))$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[left]{$\lH_{M,N} \odot 1$} (B)
+(B) edge node[left]{$\lH_{M \odot N,P}$} (C)
 (A) edge node[above]{$a$} (A')
@@
 (A') edge node [right]{$1 \odot \mathbb{H}_{N,P}$} (B');
+(C) edge node [above] {$\lH(a')$} (C')
+(B') edge node [right] {$\lH_{M,N \odot P}$} (C')
+(A') edge node [right]{$1 \odot \lH_{N,P}$} (B');
 \end{tikzpicture}
@@
 In \cite{BC2}, the first two authors introduce the symmetric monoidal double category of \emph{structured cospans} as a formalism to capture open networks.
-One of the main goals of this paper is to provide a monoidal double equivalence between this double category and that of \emph{decorated cospans}, described in detail in \cref{DecCospansDoubleCat}.
+One of the main goals of this paper is to provide a monoidal double isomorphism between this double category and that of \emph{decorated cospans}, described in detail in \cref{DecCospansDoubleCat}.
 We first recall the double category structured cospans form.
@@
 This was proved in \cite[Theorems~2.3 \& 3.9]{BC2}.
-In particular, the double category structure only requires that $\X$ have pushouts, since this is how composition is formed.
-The symmetric monoidal structure requires also that $\X$  has binary coproducts and an initial object (and thus all finite colimits), and that $\A$ has and $L$ preserves finite coproducts \cite[Theorem~3.2.3]{CourserThesis}.
+Composition is formed by taking pushouts in $\X$ and identity horizontal 1-cells are $L(a)\xrightarrow{\raisebox{-3pt}[0pt][0pt]{=}}L(a)\xleftarrow{\raisebox{-3pt}[0pt][0pt]{=}}L(a)$.
+In particular, the double category structure only requires that $\X$ have pushouts, whereas the symmetric monoidal structure also requires that $\X$ has binary coproducts and an initial object (and thus all finite colimits), and that $\A$ has and $L$ preserves finite coproducts \cite[Theorem~3.2.3]{CourserThesis}.
 \end{proof}
 
-The following theorem establishes the equivalence between structured and decorated cospan double categories under certain conditions.
+The following theorem establishes the isomorphism between structured and decorated cospan double categories under certain conditions.
 We denote by $\Rex$ the 2-category of finitely cocomplete categories, finitely cocontinuous functors and natural transformatoins.
@@
 
-We have now laid all the necessary background to formally construct an equivalence between the double category of decorated cospans and the double category of structured cospans, with starting point a symmetric lax monoidal pseudofunctor into $\Cat$.
+We have now laid all the necessary background to formally construct an isomorphism between the double category of decorated cospans and the double category of structured cospans, with starting point a symmetric lax monoidal pseudofunctor into $\Cat$.
 
@@
 Finally, the 2-morphisms of this double category in this context unravel as follows
-\begin{displaymath}
+\begin{equation}\label{eq:2morphismLCspintaF}
  \begin{tikzcd}[row sep=1in,column sep=1.7in,ampersand replacement=\&]
@@
  \end{tikzcd}
-\end{displaymath}
+\end{equation}
 where the outside vertical legs come from the definition of $L$ on arrows \cref{eq:Lonarrows}. 
@@
 
-Building up to an equivalence of the above described double categories, we now define a double functor
+Building up to an isomorphism of the above described double categories, we now define a double functor
 \begin{displaymath}
@@
 Given a horizontal 1-cell in $\scsp{L}{\inta F}$ as in \cref{eq:scsphor1cell}, $\lE_1$ maps it to the decorated cospan $i\maps a\to m\leftarrow b:o$ with decoration $x\in F(m)$,
-%Notice that this really is a bijective correspondence since the unique maps from the initial objects in the fibres provide no extra information.
 whereas a 2-morphism of $L$-structured cospans as above is mapped to the underlying cospan 2-morphism in $\A$
@@
 in $\A$ along with the map $\tau\maps Fk(x)\to x'$ in $F(m')$, namely an $F$-decorated cospan 2-morphism. 
-% Once again, this is a bijective correspondence since, as discussed above, the commutativity \cref{eq:Grothcommutativity} holds automatically by initiality of the domain.
 With these definitions, $\lE$ is indeed a (pseudo) double functor as in \cref{def:doublefun}: both $\lE_0$ and $\lE_1$ are functors that appropriately commute with sources and targets, and there exist globular 2-isomorphisms $\lE(M) \odot \lE(N) \simrightarrow\lE(M \odot N)$, $U_{\lE m} \simrightarrow\lE(U_m)$
@@
 where $\sigma$ are the canonical maps into the pushout. %overusing notation, streamline with earlier
-Under $\lE$ this is mapped to the underlying $\A$-cospan $\cspn{a}{m+_bn}{b}{}{}$ with decoration $F(\sigma_m)x+F(\sigma_n)y$ -- since a pushout over an initial object is really a coproduct -- which is isomorphic to \cref{eq:1} due to the following diagram
+Under $\lE$ this is mapped to the underlying $\A$-cospan $\cspn{a}{m+_bn}{b}{}{}$ with decoration $F(\sigma_m)x+F(\sigma_n)y$, since a pushout over an initial object is really a coproduct.
+That decoration is isomorphic to that of \cref{eq:1} due to the following diagram
 \begin{displaymath}
@@
 The left-hand side isomorphism is due to pseudonaturality of $\phi$ whereas the right-hand side isomorphism follows from universal properties and pseudofunctoriality of $F$.
-Regarding identities, $U_m$ is $\cspn{(m,\bot_m)}{(m,\bot_m)}{(m,\bot_m)}{}{}$ with $1_m$ as the $A$-components and isomorphisms between initial objects in the fibres.
-So $\lE(U_m)$ is the identity cospan in $A$ together with the `initial decoration' $\bot_m\in F(m)$, and so is $U_{\mathbb{E}(m)}$ as in \cref{eq:UFCsp}.
-
-{\chris IN progress...}
-
-Based on the above description of its mapping, it follows that the strong double functor $\mathbb{E}=(\mathbb{E}_0,\mathbb{E}_1)$ is full, faithful and essentially surjective on objects as per \cref{def:fullfaithful,def:essentiallysurj}.
-Therefore $\mathbb{E} \maps \scsp{L_F}{\inta F} \to \dcsp{F}$ is a double equivalence, by \cref{ShulDubEquiv}.
-Christina: In fact, Christina and Kenny believe it is an isomorphism of double categories! Bijective on all levels of objects and morphisms...should we say?
+Regarding identities, the identity horizontal 1-cell $U_m$ in $_L\lCsp(\inta F)$ is $\cspn{(m,\bot_m)}{(m,\bot_m)}{(m,\bot_m)}{}{}$ with $1_m$ as the $A$-component and isomorphisms between initial objects in the fibres.
+Thus $\lE(U_m)$ is the identity cospan in $A$ together with the `initial decoration' $\bot_m\in F(m)$, and so is $U_{\mathbb{E}(m)}$ as in \cref{eq:UFCsp}.
+%Do we want to check that E is a double functor one last time?
+
+In fact, the double functor $\lE\maps _L\lCsp(\inta F)\to\dcsp{F}$ as defined above is bijective on objects and vertical 1-cells (trivially as an identity functor), and is also bijective on horizontal 1-cells and on 2-morphisms.
+Indeed, for \cref{eq:scsphor1cell}, the unique maps from the initial objects in the fibres provide no actual extra information, and similarly for 2-cells all extra data in \cref{eq:2morphismLCspintaF} is uniquely determined and \cref{eq:Grothcommutativity} holds automatically as discussed above.
+As a result, we have a double isomorphism $$\scsp{L_F}{\inta F} \cong \dcsp{F}.$$
 
@@
 
-Next, we show that if both double categories $_L \lCsp(\X)$ and $F\lCsp$ are symmetric monoidal, as they are if both $\A$ and $\X$ have finite colimits, then this equivalence of double categories $\mathbb{E} \maps _L \lCsp(\X) \to F\lCsp$ will be symmetric monoidal.
+Next, we show that if both double categories $_L \lCsp(\X)$ and $F\lCsp$ are symmetric monoidal, as they are if both $\A$ and $\X$ have finite colimits, then this isomorphism of double categories $\mathbb{E} \maps _L \lCsp(\X) \to F\lCsp$ will be symmetric monoidal.
 First, note that we have an isomorphism $\epsilon \maps 1_{F\lCsp} \to \mathbb{E}(1_{_L \lCsp(\X)})$ and natural isomorphisms $\mu_{c_1,c_2} \maps \mathbb{E}(c_1) \otimes \mathbb{E}(c_2) \to \mathbb{E}(c_1 \otimes c_2)$ for every pair of objects $c_1,c_2 \in {_L \mathbb{C} \textnormal{sp}(\X)}$ both of which are given by identities since both double categories $_L \lCsp(\X)$ and $F\lCsp$ have $\A$ as their category of objects and $\mathbb{E}_0=\id_{\A}$.
@@
 
-In \cref{thm:equiv} we gave conditions under which the symmetric monoidal double category of \emph{decorated} cospans $F\lCsp$ is equivalent to the  symmetric monoidal double category of \emph{structured} cospans ${}_L \lCsp(\int F)$.
-We now show that under the same conditions we get an equivalence of symmetric monoidal bicategories, and of categories.
+In \cref{thm:equiv} we gave conditions under which the symmetric monoidal double category of \emph{decorated} cospans $F\lCsp$ is isomorphic to the  symmetric monoidal double category of \emph{structured} cospans ${}_L \lCsp(\int F)$.
+We now show that under the same conditions we get an isomorphism of symmetric monoidal bicategories, and of categories.
 
@@
 Define the symmetric monoidal bicategory $_L\bCsp(\inta F)$ as in \cref{thm:equiv}.
-Then there is an equivalence of symmetric monoidal bicategories
+Then there is an isomorphism of symmetric monoidal bicategories
 \[      F\bCsp \simeq {}_L \bCsp(\inta F)   \]
@@
 CHECK THAT OUR SORT OF EQUIVALENCE OF SYMMETRIC MONOIDAL DOUBLE CATEGORIES IS REALLY THAT USED BY HANSEN AND SHULMAN!!!
+
+IN THE PROOF ABOVE, WE ACTUALLY POTENTIALLY NEED SYMMETRY. DOES IT FOLLOW?
 
@@
 
+WE NEED TO SAY BRIEFLY WHAT A DOUBLE ISOMORPHISM IS.
+
 \begin{thm}

### 2020-11-18 cospans.tex
fixing some macros

@@
 \begin{proof}[Proof of \cref{thm:equiv}]
-Recall from \cref{thm:decorated_cospans} that the double category of decorated cospans $\dcsp{F}$ has objects and vertical 1-morphisms as in $\A$, while horizontal 1-cells are cospans $\cspn{a}{m}{b}{}{}$ in $\A$ decorated by an $x\in F(m)$ and 2-morphisms are maps of cospans $k\maps m\to m'$ together with $\tau\maps(Fk)(x)\to x'$ in $F(m')$.%!!!
+Recall from \cref{thm:decorated_cospans} that the double category of decorated cospans $F\lCsp$ has objects and vertical 1-morphisms as in $\A$, while horizontal 1-cells are cospans $\cspn{a}{m}{b}{}{}$ in $\A$ decorated by an $x\in F(m)$ and 2-morphisms are maps of cospans $k\maps m\to m'$ together with $\tau\maps(Fk)(x)\to x'$ in $F(m')$.%!!!
 Christina: Should we call them `generalized maps of cospans'?
@@
 
-As a left adjoint, this induced $L$ preserves all colimits that exist between the finitely cocomplete categories $\A$ and $\inta F$, so we can construct the double category of structured cospans $\scsp{L}{\inta F}$ of \cref{SC}.
-Its objects and vertical morphisms are those of the category $\A$ (as for $\dcsp{F}$ earlier), whereas horizontal 1-cells are now cospans of the form $\cspn{L(a)}{v}{L(b)}{}{}$ in the Grothendieck category $\inta F$ (\cref{def:GrothCat}).
+As a left adjoint, this induced $L$ preserves all colimits that exist between the finitely cocomplete categories $\A$ and $\inta F$, so we can construct the double category of structured cospans $_L\lCsp(\inta F)$ of \cref{SC}.
+Its objects and vertical morphisms are those of the category $\A$ (as for $F\lCsp$ earlier), whereas horizontal 1-cells are now cospans of the form $\cspn{L(a)}{v}{L(b)}{}{}$ in the Grothendieck category $\inta F$ (\cref{def:GrothCat}).
 Explicitly, they consist of two pairs of morphisms
@@
 \begin{displaymath}
-\lE=(\lE_0,\lE_1)\maps\scsp{L}{\inta F} \longrightarrow\dcsp{F}
+\lE=(\lE_0,\lE_1)\maps _L\lCsp(\inta F) \longrightarrow F\lCsp
 \end{displaymath}
 which on vertical categories acts as the identity $\lE_0 = \id_{\A}$.
-Given a horizontal 1-cell in $\scsp{L}{\inta F}$ as in \cref{eq:scsphor1cell}, $\lE_1$ maps it to the decorated cospan $i\maps a\to m\leftarrow b:o$ with decoration $x\in F(m)$,
+Given a horizontal 1-cell in $_L\lCsp(\inta F)$ as in \cref{eq:scsphor1cell}, $\lE_1$ maps it to the decorated cospan $i\maps a\to m\leftarrow b:o$ with decoration $x\in F(m)$,
 whereas a 2-morphism of $L$-structured cospans as above is mapped to the underlying cospan 2-morphism in $\A$
@@
 With these definitions, $\lE$ is indeed a (pseudo) double functor as in \cref{def:doublefun}: both $\lE_0$ and $\lE_1$ are functors that appropriately commute with sources and targets, and there exist globular 2-isomorphisms $\lE(M) \odot \lE(N) \simrightarrow\lE(M \odot N)$, $U_{\lE m} \simrightarrow\lE(U_m)$
-for any pair of composable horizontal 1-cells $M=\cspn{(a,\bot_a)}{(m,x)}{(b,\bot_b)}{}{}$ and $N=\cspn{(b,\bot_b)}{(n,y)}{(c,\bot_c)}{}{}$ and any object $m$ of $\scsp{L}{\inta F}$.
+for any pair of composable horizontal 1-cells $M=\cspn{(a,\bot_a)}{(m,x)}{(b,\bot_b)}{}{}$ and $N=\cspn{(b,\bot_b)}{(n,y)}{(c,\bot_c)}{}{}$ and any object $m$ of $_L\lCsp(\inta F)$.
 Explicitly, $\mathbb{E}(M)\odot \mathbb{E}(N)$ is given as in \cref{eq:dcospanscomposition} via the pushout cospan and decoration
@@
 \end{equation}
-whereas first composing $M$ and $N$ in $\scsp{L}{\inta F}$ using pushouts in $\inta F$ (constructed by \cref{lem:fibrewiselimits}) %!!!
+whereas first composing $M$ and $N$ in $_L\lCsp(\inta F)$ using pushouts in $\inta F$ (constructed by \cref{lem:fibrewiselimits}) %!!!
 Christina: would you like me to write how global pushouts are constructed from fiberwise ones and incorporate it earlier say at \cref{rmk:important} where we do so for initial objects?
@@
 
-In fact, the double functor $\lE\maps _L\lCsp(\inta F)\to\dcsp{F}$ as defined above is bijective on objects and vertical 1-cells (trivially as an identity functor), and is also bijective on horizontal 1-cells and on 2-morphisms.
+In fact, the double functor $\lE\maps _L\lCsp(\inta F)\to F\lCsp$ as defined above is bijective on objects and vertical 1-cells (trivially as an identity functor), and is also bijective on horizontal 1-cells and on 2-morphisms.
 Indeed, for \cref{eq:scsphor1cell}, the unique maps from the initial objects in the fibres provide no actual extra information, and similarly for 2-cells all extra data in \cref{eq:2morphismLCspintaF} is uniquely determined and \cref{eq:Grothcommutativity} holds automatically as discussed above.
-As a result, we have a double isomorphism $$\scsp{L_F}{\inta F} \cong \dcsp{F}.$$
-
-%!!!Christina Have not edited below, but everything should be fine up to notation changes. Happy to do if needed in the future.
-
-Next, we show that if both double categories $_L \lCsp(\X)$ and $F\lCsp$ are symmetric monoidal, as they are if both $\A$ and $\X$ have finite colimits, then this isomorphism of double categories $\mathbb{E} \maps _L \lCsp(\X) \to F\lCsp$ will be symmetric monoidal.
+As a result, we have a double isomorphism $$_L\lCsp(\inta F) \cong F\lCsp.$$
+
+Since both double categories $_L \lCsp(\X)$ and $F\lCsp$ are symmetric monoidal, 
+{\chris in progress}
+
+as they are if both $\A$ and $\X$ have finite colimits, then this isomorphism of double categories $\mathbb{E} \maps _L \lCsp(\X) \to F\lCsp$ will be symmetric monoidal.
 First, note that we have an isomorphism $\epsilon \maps 1_{F\lCsp} \to \mathbb{E}(1_{_L \lCsp(\X)})$ and natural isomorphisms $\mu_{c_1,c_2} \maps \mathbb{E}(c_1) \otimes \mathbb{E}(c_2) \to \mathbb{E}(c_1 \otimes c_2)$ for every pair of objects $c_1,c_2 \in {_L \mathbb{C} \textnormal{sp}(\X)}$ both of which are given by identities since both double categories $_L \lCsp(\X)$ and $F\lCsp$ have $\A$ as their category of objects and $\mathbb{E}_0=\id_{\A}$.

### 2020-11-18 cospans.tex
small formatting changes

--- 2020-11-17 cospans.tex
@@
-% Structured and decorated cospans
 % John Baez, Kenny Courser and Christina Vasilakopoulou
 % 2020/11/12 - JB
+% 2020/11/17
 
@@
 \begin{enumerate}
+\begin{itemize}
 \item objects are those of $\A$,
@@
 \end{enumerate}
+\end{itemize}
 \end{thm}
@@
 
-\subsection{2-categories}\label{sec:2cats}
-For standard 2-categorical material, we refer the reader to e.g. \cite{KS} or \cite{DS} for monoidal structures. %!!!Christina: also John's paper on monoidal 2-structures?
-Recall that a \define{pseudofunctor} $F\maps\bicat{A}\to\bicat{B}$ between bicategories $\bicat{A}$ and $\bicat{B}$ is functorial up to coherent natural isomorphism, namely for composable arrows we have $F(g\circ f)\cong Fg\circ Ff$ and $F(1_a)\cong1_{Fa}$ satisfying standard axioms.
-Given pseudofunctors $F,G\maps \bicat{A} \to \bicat{B}$, a \define{pseudonatural transformation} $\sigma$ consists of
 \begin{itemize}
-\item for each object $a \in \bicat{A}$, a morphism $\sigma_a \maps F(a) \to G(a)$ in $\bicat{B}$ 
 \item 
@@
 %Christina: I removed the above, they are not needed I believe. Check again in the end.
-We denote by $[\bicat{A},\bicat{B}]_\pse$ the 2-category 
+We denote by $[\bA,\bB]_\pse$ the 2-category 
 of pseudofunctors, pseudonatural transformations and modifications.
@@
 RIGHT???
+A \define{monoidal} bicategory $\bA$ comes with a pseudofunctor $\otimes\maps\bA\times\bA\to\bA$ and a unit object $I$ that are associative and unital up to coherent equivalence.
+A \define{braided} monoidal bicategory comes with a pseudonatural equivalence $\beta_{a,b}\maps a\ot b\to b\ot a$ and appropriate invertible modifications; it is \define{sylleptic} if there is an appropriate invertible modification $1_{a\ot b}\Rrightarrow\beta_{b,a}\circ\beta_{a,b}$ and it is \define{symmetric} if one further axiom holds.
+A \define{lax monoidal} pseudofunctor between monoidal bicategories $F\maps\bA\to\bB$ is a pseudofunctor equipped with pseudonatural transformations with components $\mu_{a,b}\maps Fa\otimes Fb\to F(a\otimes b)$ and $\mu_0\maps I\to FI$ along with coherent invertible modifications for associativity and unitality.
+A \define{braided lax monoidal} pseudofunctor between braided monoidal bicategories comes with an appropriate invertible modification with components $F(\beta_{a,b})\circ \mu_{a,b}\cong\mu_{b,a}\circ \beta_{Fa,Fb}$; a \define{sylleptic lax monoidal} pseudofunctor satisfies one extra condition and a \define{symmetric lax monoidal} pseudofunctor between symmetric monoidal bicategories is just a sylleptic one.
 
@@
 Before formally defining `pseudo double category', it is helpful to have the following picture in mind. A pseudo double category has 2-morphisms shaped like:
+Before defining double categories, it is helpful to have the following picture in mind. A double category has 2-morphisms shaped like:
 

### 2020-11-18 cospans.tex
rewrote a bit of introductory stuff on mon Groth

@@
 % John Baez, Kenny Courser and Christina Vasilakopoulou
-% 2020/11/12 - JB
 % 2020/11/17
@@
 \begin{thm} \label{thm:equiv}
-Suppose $\ca{A}$ has finite colimits and $F\maps(\A,+) \to (\Cat,\times)$ is a symmetric lax monoidal pseudofunctor that factors through $\bicat{Rex}$ as an ordinary pseudofunctor.
+Suppose $\A$ has finite colimits and $F\maps(\A,+) \to (\Cat,\times)$ is a symmetric lax monoidal pseudofunctor that factors through $\Rex$ as an ordinary pseudofunctor.
 Then the symmetric monoidal double categories $F\lCsp$ of decorated cospans and $_L\lCsp(\inta F)$ of structured cospans are equivalent, where $L \maps \A \to \inta F$ is a left adjoint of the induced Grothendieck opfibration $U\maps \inta F \to \A$.
@@
 
-In \cite{MV}, the classical Grothendieck construction is generalized to the monoidal setting: lax monoidal structures on a pseudofunctor $F\maps\A\to\Cat$ (called \emph{monoidal opindexed categories}) bijectively correspond to monoidal structures on the total category $\inta F$ such that the induced opfibration is a strict monoidal functor and $\otimes_{\inta F}$ preserves cocartesian liftings (called \emph{monoidal fibrations}).
-If the monoidal category $\A$ is in fact cocartesian, there is a further correspondence of the two structures with an ordinary pseudofunctor $F\maps\A\to\bicat{MonCat}$ into the 2-category of monoidal categories, strong monoidal functors and monoidal natural transformations.
+In \cite{MV}, the classical Grothendieck construction is generalized to the monoidal setting: given a monoidal category $\A$ there is a bijection between
+\begin{itemize}
+\item 
+\define{monoidal opindexed categories}: lax monoidal pseudofunctors $F\maps\A\to\Cat$
+\end{itemize}
+and
+\begin{itemize}
+\item \define{monoidal opfibrations}: opfibrations
+$U \maps \X \to \A$ where $\X$ is monoidal, $U$ is strict monoidal, and $\otimes_\X$ preserves cocartesian liftings.
+\end{itemize}
+If the monoidal structure on $\A$ is in fact cocartesian, there is a further correspondence between either of these structures and ordinary pseudofunctors $F\maps\A\to\bicat{MonCat}$ into the 2-category of monoidal categories, strong monoidal functors and monoidal natural transformations.
 
@@
 Let $\A$ be a category with finite colimits and $F \maps (\A, +) \to (\Cat,\times)$ a symmetric lax monoidal pseudofunctor. Then there exists a symmetric monoidal bicategory $F \mathbf{Csp}$ in which:
-\begin{enumerate}
 \begin{itemize}
@@
 together with a morphism $\tau \maps F(h)(d) \to d'$ in $F(c')$.
-\end{enumerate}
 \end{itemize}

### 2020-11-18 cospans.tex
more work on opfibrations

@@
 
-In \cite{MV}, the classical Grothendieck construction is generalized to the monoidal setting: given a monoidal category $\A$ there is a bijection between
-\begin{itemize}
-\item 
-\define{monoidal opindexed categories}: lax monoidal pseudofunctors $F\maps\A\to\Cat$
-\end{itemize}
-and
-\begin{itemize}
-\item \define{monoidal opfibrations}: opfibrations
-$U \maps \X \to \A$ where $\X$ is monoidal, $U$ is strict monoidal, and $\otimes_\X$ preserves cocartesian liftings.
-\end{itemize}
-If the monoidal structure on $\A$ is in fact cocartesian, there is a further correspondence between either of these structures and ordinary pseudofunctors $F\maps\A\to\bicat{MonCat}$ into the 2-category of monoidal categories, strong monoidal functors and monoidal natural transformations.
+In \cite{MV}, the classical Grothendieck construction is generalized to the monoidal setting: given a monoidal category $\A$ there is a bijection between \define{monoidal opindexed categories}, which are lax monoidal pseudofunctors $F\maps\A\to\Cat$, and \define{monoidal opfibrations}, which are opfibrations $U \maps \X \to \A$ where $\X$ is monoidal, $U$ is strict monoidal, and $\otimes_\X$ preserves cocartesian liftings.
+This bijection sends a monoidal opindexed category $F \maps \A \to \Cat$ to its Grothendieck construction $U \maps \inta F \to \A$.
+If the monoidal structure on $\A$ is in fact cocartesian, there is a further correspondence between these structures and ordinary pseudofunctors $F\maps\A\to\bicat{MonCat}$ into the 2-category of monoidal categories, strong monoidal functors and monoidal natural transformations.
+Further, all these correspondences lift to 2-equivalences:
 
@@
 The second equivalence was also earlier observed by Shulman \cite{Shulman2008}.
-In more detail, if $(\mu,\mu_0)$ is the lax monoidal structure of the pseudofunctor $F$ as recalled in \cref{sec:2cats}, each fibre category $\X_a=F(a)$ obtains a monoidal structure via
+In more detail, if $(\mu,\mu_0)$ is the lax monoidal structure of the pseudofunctor $F$ as recalled in \cref{subsec:bicats}, each fibre category $\X_a=F(a)$ obtains a monoidal structure via
 \begin{equation}\label{eq:explicitstructure1}
@@
 
-These correspondences further restrict to the case when the Grothendieck category is specifically cocartesian monoidal itself. In that case, opfibrations
+These correspondences further restrict to the case when the Grothendieck category $(X,\otimes)$ is specifically cocartesian monoidal itself. In that case, opfibrations
 $(\X,+)\to(\A,+)$ that strictly preserve chosen coproducts and initial object
@@
 
-\begin{itemize}
-\item 
+\subsection{Bicategories}
+\label{subsec:bicats}
+
+%\begin{itemize}
+%\item 
 %for every pair of objects $a$ and $b$ of $\mathbf{A}$, we have natural isomorphisms
@@
 %where $(\sigma_a)^*$ and $(\sigma_b)_*$ are the functors induced by precomposition and postcompositon, respectively. Thus 
-for each morphism $f \maps a \to b$ in $\mathbf{A}$, an invertible natural 2-morphism $\sigma_f \maps G(f) \sigma_a \xrightarrow{\sim} \sigma_{b} F(f)$ in $\mathbf{B}$
+%for each morphism $f \maps a \to b$ in $\mathbf{A}$, an invertible natural 2-morphism $\sigma_f \maps G(f) \sigma_a \xrightarrow{\sim} \sigma_{b} F(f)$ in $\mathbf{B}$
 %:
@@
 %\]
-compatible with composition and identities.
-\end{itemize}
+%compatible with composition and identities.
+%end{itemize}
 %such that for each composable pair of morphisms $f \maps a \to b$ and $g \maps b \to c$ of $\mathbf{A}$, the following diagrams commute:
@@
 %Christina: I removed the above, they are not needed I believe. Check again in the end.
-We denote by $[\bA,\bB]_\pse$ the 2-category 
-of pseudofunctors, pseudonatural transformations and modifications.
 
@@
         \end{displaymath}
+           where $[\A,\Cat]_\pse$ is the 2-category 
+of pseudofunctors from $\A$ to $\Cat$, pseudonatural transformations, and modifications.
 %        \item The above 2-equivalence extends to one between 2-categories of arbitrary-base fibrations and arbitrary-domain indexed categories

### 2020-11-18 cospans.tex
small changes regarding mon. Groth. stuff

@@
 
-These correspondences further restrict to the case when the Grothendieck category $(X,\otimes)$ is specifically cocartesian monoidal itself. In that case, opfibrations
+These 2-equivalences further restrict to the case when the Grothendieck category $(X,\otimes)$ is specifically cocartesian monoidal itself. In that case, opfibrations
 $(\X,+)\to(\A,+)$ that strictly preserve chosen coproducts and initial object
@@
 
-Finally, we can further restrict to the setting of opfibrations that also preserve pushouts, i.e.
-all finite colimits, which is important for our purposes.
+Finally, we can further restrict to the setting of opfibrations that also preserve pushouts, i.e.\ all finite colimits, which is important for our purposes.
 The following result is in fact more general since it relates the existence of any class of colimits in the total category of an opfibration to their existence in the fibres; for a more detailed exposition, see \cite[Corollary~4.9]{Hermida1999}.

### 2020-11-18 cospans.tex
More work on Theorem 2.2

@@
 \node (C) at (2,0) {$a$};
-\node (D) at (3,0) {$!_a \in F(a)$};
+\node (D) at (3,0) {$\bot_a \in F(a)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \end{equation}
-where $!_a \in F(a)$ is the \define{trivial decoration} on $a$ given by the composite of the unique map $F(!) \maps F(0) \to F(a)$ and the morphism $\phi \maps 1 \to F(0)$  which comes from $F \maps \A \to \Cat$ being lax monoidal.
+where $\bot_a \in F(a)$ is the \define{trivial decoration} on $a$ given by the composite of the unique map $F(!) \maps F(0) \to F(a)$ and the morphism $\phi \maps 1 \to F(0)$  which comes from $F \maps \A \to \Cat$ being lax monoidal.
 For morphisms, the functor $U$ is defined as:
@@
 \node (D) at (1,-0.5) {$a'$};
-\node (E) at (3,0.5) {$!_a \in F(a)$};
-\node (F) at (3,-0.5) {$!_{a'} \in F(a')$};
+\node (E) at (3,0.5) {$\bot_a \in F(a)$};
+\node (F) at (3,-0.5) {$\bot_{a'} \in F(a')$};
 \node (H) at (-0.5,0) {$\mapsto$};
@@
 \]
-together with the morphism $\tau_{!_f} = F(f) F(!) \phi \maps 1 \to F(a')$.
+together with the morphism $\tau_{\bot_f} = F(f) F(!) \phi \maps 1 \to F(a')$.
 For the source and target functors $S, T \maps F\lCsp_1 \to F\lCsp_0$, given an object $F\lCsp_1$, which is an $F$-decorated cospan,
@@
 
-Lastly, our double category is required to have an associator $\alpha$ (\textbf{overusing alpha, ignoring for now}) and left and right unitors $\lambda$ and $\rho$ which are natural isomorphisms governing the composition of horizontal 1-cells that are required to satisfy the standard coherence axioms for a monoidal category, as well as $S(\alpha),S(\lambda),S(\rho),T(\alpha),T(\lambda)$ and $T(\rho)$ all being identities.
+Lastly, our double category is required to have an associator $\alpha$ and left and right unitors $\lambda$ and $\rho$ which are natural isomorphisms governing the composition of horizontal 1-cells that are required to satisfy the standard coherence axioms for a monoidal category, as well as $S(\alpha),S(\lambda),S(\rho),T(\alpha),T(\lambda)$ and $T(\rho)$ all being identities.
 We will only show the associator $\alpha$, left unitor $\lambda$ and the pentagon identity, as the remaining details will be similar to these.
@@
 \]
-The composite decoration $!_a \odot x$ will be given by the composite
-$$1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{!_a \times x} F(a) \times F(m) \xrightarrow{\phi_{a,m}} F(a+m) \xrightarrow{F(\psi)} F(a+_{a} m).$$
+The composite decoration $\bot_a \odot x$ will be given by the composite
+$$1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{\bot_a \times x} F(a) \times F(m) \xrightarrow{\phi_{a,m}} F(a+m) \xrightarrow{F(\psi)} F(a+_{a} m).$$
 The left unitor is then the map of $F$-decorated cospans determined by the following map of cospans in $\A$:
@@
 \node (D) at (1.5,-0.5) {$m$};
-\node (E) at (4.5,0.5) {$!_a \odot x \in F(a+_{a} m)$};
+\node (E) at (4.5,0.5) {$\bot_a \odot x \in F(a+_{a} m)$};
 \node (F) at (4.5,-0.5) {$x \in F(m)$};
@@
 \]
-together with the decoration morphism $\tau_\lambda \colon F(\ell)(!_a \odot x) \to x$; note, that $\ell \colon a+_a m \to m$ is a canonical isomorphism as both $a+_a m$ and $m$ are colimits of the span $a \xleftarrow{\id_a} a \xrightarrow{i} m$.
+together with the decoration morphism $\tau_\lambda \colon F(\ell)(\bot_a \odot x) \to x$; note, that $\ell \colon a+_a m \to m$ is a canonical isomorphism as both $a+_a m$ and $m$ are colimits of the span $a \xleftarrow{\id_a} a \xrightarrow{i} m$.
 The right unitor $\rho$ is similar, the two unitality squares are similar to the associator shown above, and it is clear that the source and target functors applied to the associator and left and right unitors yield identities.
@@
 Let $\A$ be a category with chosen finite colimits and $F \maps \A \to \Cat$ a symmetric lax monoidal pseudofunctor.
-Then the double category $F\lCsp$ of Theorem \ref{thm:decorated_cospans} is symmetric monoidal.
+Then the double category $F\lCsp$ of Theorem \ref{thm:decorated_cospans} is symmetric monoidal, where
+\begin{enumerate}
+\item{the tensor product of two objects $a$ and $b$ is their chosen coproduct $a+b$ in $\A$,}
+\item{the tensor product of two vertical 1-morphisms $f \colon a \to b$ and $f' \colon a' \to b'$ is the vertical 1-morphism $f+f' \colon a+a' \to b+b'$,}
+\item{the tensor product of two horizontal 1-cells $M$ and $N$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$a_1$};
+\node (B) at (1,0) {$m_1$};
+\node (C) at (2,0) {$b_1$};
+\node (D) at (1,-0.5) {$x_1 \in F(m_1)$};
+\node (E) at (3,0) {$a_2$};
+\node (F) at (4,0) {$m_2$};
+\node (G) at (5,0) {$b_2$};
+\node (H) at (4,-0.5) {$x_2 \in F(m_2)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i_1$} (B)
+(C) edge node[above]{$o_1$} (B)
+(E) edge node[above]{$i_2$} (F)
+(G) edge node[above]{$o_2$} (F);
+\end{tikzpicture}
+\]
+is the horizontal 1-cell $M \otimes N$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$a_1+a_2$};
+\node (B) at (1.5,0) {$m_1+m_2$};
+\node (C) at (3,0) {$b_1+b_2$};
+\node (D) at (4.55,0) {$x_1+x_2 \in F(m_1+m_2)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i_1+i_2$} (B)
+(C) edge node[above]{$o_1+o_2$} (B);
+\end{tikzpicture}
+\]
+$$x_1+x_2 \mapseqq 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{x_1 \times x_2} F(m_1) \times F(m_2) \xrightarrow{\phi_{m_1,m_2}} F(m_1+m_2)$$}
+\item{the tensor product of two 2-morphisms $\alpha$ and $\beta$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0.5) {$a$};
+\node (A') at (0,-0.5) {$a'$};
+\node (B) at (1,0.5) {$m$};
+\node (C) at (2,0.5) {$b$};
+\node (C') at (2,-0.5) {$b'$};
+\node (D) at (1,-0.5) {$m'$};
+\node (E) at (3,0.5) {$x \in F(m)$};
+\node (F) at (3,-0.5) {$x' \in F(m')$};
+\node (G) at (4,0.5) {$c$};
+\node (H) at (5,0.5) {$n$};
+\node (I) at (6,0.5) {$d$};
+\node (G') at (4,-0.5) {$c'$};
+\node (H') at (5,-0.5) {$n'$};
+\node (I') at (6,-0.5) {$d'$};
+\node (J) at (7,0.5) {$y \in F(n)$};
+\node (K) at (7,-0.5) {$y' \in F(n')$};
+\node (L) at (1,-1) {$\tau_\alpha \maps F(h)(x) \to x'$};
+\node (M) at (5,-1) {$\tau_\beta \maps F(h')(y) \to y'$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i_1$} (B)
+(C) edge node[above]{$o_1$} (B)
+(A) edge node[left]{$f$} (A')
+(C) edge node[right]{$g$} (C')
+(A') edge node[above] {$i_1'$} (D)
+(C') edge node[above] {$o_1'$} (D)
+(B) edge node [left] {$h$} (D)
+(G) edge node [above] {$i_2$} (H)
+(G) edge node [left] {$f'$} (G')
+(H) edge node [left] {$h'$} (H')
+(G') edge node [above] {$i_2'$} (H')
+(I) edge node [above] {$o_2$} (H)
+(I) edge node [right] {$g'$} (I')
+(I') edge node [above] {$o_2'$} (H');
+\end{tikzpicture}
+\]
+is the 2-morphism $\alpha \otimes \beta$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0.5) {$a+c$};
+\node (A') at (0,-0.5) {$a'+c'$};
+\node (B) at (2,0.5) {$m+n$};
+\node (C) at (4,0.5) {$b+d$};
+\node (C') at (4,-0.5) {$b'+d'$};
+\node (D) at (2,-0.5) {$m'+n'$};
+\node (E) at (5.5,0.5) {$x+y \in F(m+n)$};
+\node (F) at (5.5,-0.5) {$x'+y' \in F(m'+n')$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i_1+i_2$} (B)
+(C) edge node[above]{$o_1+o_2$} (B)
+(A) edge node[left]{$f+f'$} (A')
+(C) edge node[left]{$g+g'$} (C')
+(A') edge node [above]{$i_1'+i_2'$} (D)
+(C') edge node [above]{$o_1'+o_2'$} (D)
+(B) edge node [left] {$h+h'$} (D);
+\end{tikzpicture}
+\]
+$$\tau_{\alpha+\beta} \colon F(h+h')(x+y) \to x'+y'$$
+where the decoration morphism $\tau_{\alpha+\beta}$ comes from the pasted diagram:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (4.75,0) {$\tau_\alpha \times \tau_\beta \Swarrow$};
+\node (D) at (3,0) {$1 \xrightarrow{\lambda^{-1}} 1 \times 1$};
+\node (E) at (5.5,0.5) {$F(m) \times F(n)$};
+\node (E') at (5.5,-0.5) {$F(m') \times F(n')$};
+\node (B) at (7.5,0.5) {$F(m+n)$};
+\node (B') at (7.5,-0.5) {$F(m' + n')$};
+\path[->,font=\scriptsize,>=angle 90]
+(E) edge node [above] {$\phi_{m,n}$} (B)
+(E') edge node [above] {$\phi_{m',n'}$} (B')
+(B) edge node [right] {$F(h + h')$} (B')
+(D) edge node [above] {$x \times y$} (E)
+(D) edge node [below] {$x' \times y'$} (E')
+(E) edge node [right] {$F(h) \times F(h')$} (E');
+\end{tikzpicture}
+\]
+}
+\end{enumerate}
 \end{thm}
@@
 \end{enumerate}
-
 First we define the tensor product and monoidal unit of $F\lCsp_1$. Given two objects $M_1$ and $M_2$ of $F\lCsp_1$:
@@
 \]
-and where the decoration on the apex is obtained using the natural transformation of the symmetric lax monoidal pseudofunctor $F$: $$x_1+x_2 \mapseqq 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{x_1 \times x_2} F(m_1) \times F(m_2) \xrightarrow{\phi_{m_1,m_2}} F(m_1+m_2).$$The monoidal unit $0_{F\lCsp_1}$ is given by:
+where the decoration on the apex is obtained using the natural transformation of the symmetric lax monoidal pseudofunctor $F$: $$x_1+x_2 \mapseqq 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{x_1 \times x_2} F(m_1) \times F(m_2) \xrightarrow{\phi_{m_1,m_2}} F(m_1+m_2).$$The monoidal unit $0_{F\lCsp_1}$ is given by:
 \[
@@
 \node (C) at (2,0) {$0$};
-\node (D) at (3,0) {$!_0 \in F(0)$};
+\node (D) at (3,0) {$\bot_0 = \phi \in F(0)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-where $0$ is the monoidal unit of $\A$ and $!_0 \maps 1 \to F(0)$ is the morphism which is part of the structure of the symmetric lax monoidal pseudofunctor $F \maps \A \to \Cat$.
-It is also clear that $U(0)=0_{F\lCsp_1}$, where $0_{F\lCsp_1}$ is the monoidal unit of $F\lCsp_1$.
+where $0$ is the monoidal unit of $\A$ and $\phi \maps 1 \to F(0)$ is the morphism which is part of the structure of the symmetric lax monoidal pseudofunctor $F \maps \A \to \Cat$.
+It is also clear that $U(0)=0_{F\lCsp_1}$.
 
@@
 \node (C) at (2,0) {$0$};
-\node (D) at (1,-0.5) {$!_0 \in F(0)$};
+\node (D) at (1,-0.5) {$\bot_0 \in F(0)$};
 \node (E) at (3,0) {$a$};
@@
 \node (C) at (2,0) {$0+b$};
-\node (D) at (3.5,0) {$!_0 + x \in F(0+m)$};
+\node (D) at (3.5,0) {$\bot_0 + x \in F(0+m)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-where $!_0 + x \in F(0+m)$ is given by $$1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{!_0 \times x} F(0) \times F(m) \xrightarrow{\phi_{0,m}} F(0+m).$$Denoting the left unitor of $(\A,+,0)$ by $\ell$, the left unitor of $F\lCsp_1$ is then an isomorphism in $F\lCsp_1$ given by the following map of cospans in $\A$:
+where $\bot_0 + x \in F(0+m)$ is given by $$1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{\bot_0 \times x} F(0) \times F(m) \xrightarrow{\phi_{0,m}} F(0+m).$$Denoting the left unitor of $(\A,+,0)$ by $\ell$, the left unitor of $F\lCsp_1$ is then an isomorphism in $F\lCsp_1$ given by the following map of cospans in $\A$:
 \[
@@
 \node (D) at (1,-0.5) {$m$};
-\node (E) at (3.5,0.5) {$!_0 + x \in F(0+m)$};
+\node (E) at (3.5,0.5) {$\bot_0 + x \in F(0+m)$};
 \node (F) at (3.5,-0.5) {$x \in F(m)$};
@@
 \]
-together with the decoration isomorphism $\tau_{\ell} \maps F(\ell)(!_0 + x) \to x$.
+together with the decoration isomorphism $\tau_{\ell} \maps F(\ell)(\bot_0 + x) \to x$.
 The right unitor is similar, and one can check that the associator and left and right unitors together satisfy the pentagon and triangle identities of a monoidal category.
@@
 together with the decoration isomorphism $\tau_\beta \colon F(\beta)(x_1+x_2) \to x_2+x_1$.
+Note that obtaining the decoration isomorphism $\tau_\beta$ makes use of $F$ being symmetric.
 One can check that the braiding together with the associator satisfy the hexagon equations, and it is clear that $\beta_{M_1,M_2}=\beta_{M_2,M_1}^{-1}$.
@@
 \node (D) at (2,-0.5) {$a+b$};
-\node (E) at (5.5,0.5) {$!_{a+b} \in F(a+b)$};
-\node (F) at (5.5,-0.5) {$!_a + !_b \in F(a+b)$};
+\node (E) at (5.5,0.5) {$\bot_{a+b} \in F(a+b)$};
+\node (F) at (5.5,-0.5) {$\bot_a + \bot_b \in F(a+b)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-together with the decoration isomorphism $\tau_{a,b} \maps !_{a+b} \xrightarrow{\sim} !_a + !_b$ given by the unique map between the two initial objects $!_{a+b}$ and $!_a + !_b$ in $F(a+b)$.
+together with the decoration isomorphism $\tau_{a,b} \maps \bot_{a+b} \xrightarrow{\sim} \bot_a + \bot_b$ given by the unique map between the two initial objects $\bot_{a+b}$ and $\bot_a + \bot_b$ in $F(a+b)$.
 For the former globular 2-morphism $\chi$, we first introduce some notation for objects $M_1,M_2,N_1$ and $N_2$ of $F\lCsp_1$:
@@
 
-The remaining properties are coherence diagrams that make use of these maps $\chi$ and $\mu$, the previously defined symmetric monoidal structure maps $\alpha,\lambda,\rho$ and $\beta$ and the double category structure functors $U$ and $\odot$.
-We exhibit one of these diagrams to give the reader a sense of how they are verified, with more details able to be found in the second author's thesis \cite{CourserThesis}.
-The coherence diagram that we will check is given by:
 The remaining properties are coherence laws that make use of these maps $\chi$ and $\mu$, the previously defined symmetric monoidal structure maps $\alpha,\lambda,\rho$ and $\beta$ and the double category structure functors $U$ and $\odot$.
@@
 \]
-which expresses that the braiding is a transformation of double categories.
-This expresses that the braiding is a transformation of double categories.
-
-\noindent
-\textbf{In progress}
+This diagram expresses that the braiding is a transformation of double categories.
+We will see that this diagram commutes in two stages.
+First, for the underlying maps of cospans in $\A$.
+Using the notation previously introduced for the globular 2-morphism $\hat{\chi}$, the above diagram, modulo all of the decorations, is given by the following `flattened' commutative diagram in the symmetric monoidal double category $\lCsp(\A)$, where the top and the bottom cospans coincide.
+\[
+		\begin{tikzpicture}
+			\node (a) at (-4,0) {$a+a'$};
+			\node (b) at (1,0) {$(m_1+_b m_2) + (n_1+_{b'} n_2)$};
+			\node (c) at (6,0) {$c+c'$};
+			\node (a2) at (-4,1) {$a'+a$};
+			\node (b2) at (1,1) {$(n_1 +_{b'} n_2) + (m_1 +_b m_2)$};
+			\node (c2) at (6,1) {$c'+c$};
+                                \node (a3) at (-4,2) {$a'+a$};
+			\node (b3) at (1,2) {$(n_1+m_1) +_{(b'+b)} (n_2+m_2)$};
+			\node (c3) at (6,2) {$c'+c$};
+                                \node (a5) at (-4,-1) {$a+a'$};
+			\node (b5) at (1,-1) {$(m_1+n_1) +_{(b+b')} (m_2+n_2)$};
+			\node (c5) at (6,-1) {$c+c'$};
+                                \node (a6) at (-4,-2) {$a'+a$};
+			\node (b6) at (1,-2) {$(n_1+m_1) +_{(b'+b)} (n_2+m_2)$};
+			\node (c6) at (6,-2) {$c'+c$};
+			\path[->,font=\scriptsize,>=angle 90]
+			(a) edge node[above]{$$} (b)
+			(c) edge node[above]{$$} (b)
+                                (a2) edge node[above]{$$} (b2)
+			(c2) edge node[above]{$$} (b2)
+                                (a) edge node[left]{$\beta$} (a2)
+                                (b) edge node[left]{$\beta$} (b2)
+%(b) edge node[right]{$\tau_1$} (b2)
+			(c) edge node[right]{$\beta$} (c2)
+                                (a3) edge node[above]{$$} (b3)
+			(c3) edge node[above]{$$} (b3)
+                                (a2) edge node[above]{$$} (a3)
+                                (b2) edge node[left]{$\hat{\chi}$} (b3)
+%(b2) edge node[right]{$\tau_2$} (b3)
+			(c2) edge node[above]{$$} (c3)
+                                (a5) edge node[above]{$$} (b5)
+			(c5) edge node[above]{$$} (b5)
+                                (a) edge node[above]{$$} (a5)
+                                (b) edge node[left]{$\hat{\chi}$} (b5)
+%(b) edge node[right]{$\tau_4$} (b5)
+			(c) edge node[above]{$$} (c5)
+                                (a6) edge node[above]{$$} (b6)
+			(c6) edge node[above]{$$} (b6)
+                                (a5) edge node[left]{$\beta$} (a6)
+                                (b5) edge node[left]{$\beta \odot \beta$} (b6)
+ %(b5) edge node[right]{$\tau_5$} (b6)
+			(c5) edge node[left]{$\beta$} (c6);
+		\end{tikzpicture}
+	\]
+The unlabeled vertical 1-morphisms on the sides are identities, $\beta$ is the braiding of the symmetric monoidal category $\A$, the map $\hat{\chi}$ is the globular 2-morphism interchanging the tensor product and horizontal composition of the symmetric monoidal double category $\lCsp(\A)$, and the inwards pointing morphisms are natural maps from the each cospan's feet to its apex.
+
+For the decorations, each of the four maps of cospans constituting the above diagram has an associated decoration isomorphism with it, which we label with $\tau_i$ for $i=1,2,3,4$.
+\[
+		\begin{tikzpicture}
+%			\node (a) at (-4,0) {$a+a'$};
+			\node (b) at (1,0) {$(m_1+_b m_2) + (n_1+_{b'} n_2)$};
+			\node (c) at (8,0) {$(x_1 \odot x_2) + (y_1 \odot y_2) \in F((m_1+_b m_2)+(n_1+_{b'} n_2))$};
+%			\node (a2) at (-4,1) {$a'+a$};
+			\node (b2) at (1,1) {$(n_1 +_{b'} n_2) + (m_1 +_b m_2)$};
+			\node (c2) at (8,1) {$(y_1 \odot y_2) + (x_1 \odot x_2) \in F((n_1+_{b'} n_2)+(m_1+_b m_2))$};
+%                            \node (a3) at (-4,2) {$a'+a$};
+			\node (b3) at (1,2) {$(n_1+m_1) +_{(b'+b)} (n_2+m_2)$};
+			\node (c3) at (8,2) {$(y_1+x_1) \odot (y_2+x_2) \in F((n_1+m_1)+_{b'+b}(n_2+m_2))$};
+%                                \node (a5) at (-4,-1) {$a+a'$};
+			\node (b5) at (1,-1) {$(m_1+n_1) +_{(b+b')} (m_2+n_2)$};
+			\node (c5) at (8,-1) {$(x_1+y_1) \odot (x_2+y_2) \in F((m_1+n_1)+_{b+b'}(m_2+n_2))$};
+%                                \node (a6) at (-4,-2) {$a'+a$};
+			\node (b6) at (1,-2) {$(n_1+m_1) +_{(b'+b)} (n_2+m_2)$};
+			\node (c6) at (8,-2) {$(y_1+x_1) \odot (y_2+x_2) \in F((n_1+m_1)+_{b'+b}(n_2+m_2))$};
+			\path[->,font=\scriptsize,>=angle 90]
+%			(a) edge node[above]{$$} (b)
+%			(c) edge node[above]{$$} (b)
+%                                (a2) edge node[above]{$$} (b2)
+%			(c2) edge node[above]{$$} (b2)
+%                                (a) edge node[left]{$\beta$} (a2)
+                                (b) edge node[left]{$\beta$} (b2)
+(b) edge node[right]{$\tau_1$} (b2)
+%			(c) edge node[right]{$\beta$} (c2)
+%                                (a3) edge node[above]{$$} (b3)
+%			(c3) edge node[above]{$$} (b3)
+%                               (a2) edge node[above]{$$} (a3)
+                                (b2) edge node[left]{$\hat{\chi}$} (b3)
+(b2) edge node[right]{$\tau_2$} (b3)
+%			(c2) edge node[above]{$$} (c3)
+%                                (a5) edge node[above]{$$} (b5)
+%			(c5) edge node[above]{$$} (b5)
+%                                (a) edge node[above]{$$} (a5)
+                                (b) edge node[left]{$\hat{\chi}$} (b5)
+(b) edge node[right]{$\tau_3$} (b5)
+%			(c) edge node[above]{$$} (c5)
+%                               (a6) edge node[above]{$$} (b6)
+%			(c6) edge node[above]{$$} (b6)
+%                                (a5) edge node[left]{$\beta$} (a6)
+                                (b5) edge node[left]{$\beta \odot \beta$} (b6)
+ (b5) edge node[right]{$\tau_4$} (b6);
+%			(c5) edge node[left]{$\beta$} (c6);
+		\end{tikzpicture}
+	\]
+Explicitly, the four decoration isomorphisms are given by:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$\tau_1 \colon F(\beta)((x_1 \odot x_2)+(y_1 \odot y_2)) \to (y_1 \odot y_2)+(x_1 \odot x_2)$};
+\node (B) at (0,-.5) {$\tau_2 \colon F(\hat{\chi})((y_1 \odot y_2)+(x_1 \odot x_2)) \to (y_1+x_1) \odot (y_2+x_2)$};
+\node (C) at (0,-1) {$\tau_3 \colon F(\hat{\chi})((x_1 \odot x_2)+(y_1 \odot y_2)) \to (x_1+y_1) \odot (x_2+y_2)$};
+\node (D) at (0,-1.5) {$\tau_4 \colon F(\beta \odot \beta)((x_1+y_1)\odot(x_2+y_2)) \to (y_1+x_1)\odot(y_2+x_2)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge[color=white] node[above]{$$} (A);
+%(B) edge node[right]{$\chi$} (D)
+%(A) edge node[left]{$\chi$} (C)
+%(C) edge node[above]{$\beta \odot \beta$} (D);
+\end{tikzpicture}
+\]
+These decoration isomorphisms then form the following commutative diagram in the category $F((n_1+m_1)+_{b'+b}(n_2+m_2))$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$F(\hat{\chi} \beta)((x_1 \odot x_2)+(y_1 \odot y_2))$};
+\node (B) at (4,0) {$F(\hat{\chi})((y_1 \odot y_2)+(x_1 \odot x_2))$};
+\node (C) at (0,-1) {$F(\beta \odot \beta)((x_1+y_1) \odot (x_2 + y_2))$};
+\node (D) at (4,-1) {$(y_1+x_1) \odot (y_2+x_2)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$F(\hat{\chi})(\tau_1)$} (B)
+(B) edge node[right]{$\tau_2$} (D)
+(A) edge node[left]{$F(\beta \odot \beta)(\tau_3)$} (C)
+(C) edge node[above]{$\tau_4$} (D);
+\end{tikzpicture}
+\]
+where in the top left corner, we note that $$F(\hat{\chi} \beta)((x_1 \odot x_2)+(y_1 \odot y_2)) = F((\beta \odot \beta)\hat{\chi})((x_1 \odot x_2)+(y_1 \odot y_2))$$
+as the above diagram of maps of cospans commutes in $\A$ and then applying the pseudofunctor $F$ to this diagram yields a commutative diagram in $\Cat$.
+The other diagrams in the definition of symmetric monoidal double category can be shown to commute similarly.
 %!!! Kenny: Probably cut stuff out below this.

### 2020-11-19 cospans.tex
worked on the "Applications" section

--- 2020-11-18 cospans.tex
@@
+% Structured versus decorated cospans
 % John Baez, Kenny Courser and Christina Vasilakopoulou
-% 2020/11/17
+% in LaTeX
+% 2020/11/18
 
@@
 Unfortunately, many applications of decorated cospans were flawed.
-The problem is that while Fong's decorated cospans are good for decorating the apex $m$ with an element of a set $F(m)$, they are unable to decorate it with an object of a category.
+The problem is that while Fong's decorated cospans are good for decorating the apex $m$ of a cospan with an element of a set $F(m)$, they are unable to decorate it with an object of a category.
 An example would be equipping a finite set $m$ with edges making its elements into the nodes of a graph.
@@
 One of the main goals of this paper is to provide a monoidal double isomorphism between this double category and that of \emph{decorated cospans}, described in detail in \cref{DecCospansDoubleCat}.
-We first recall the double category structured cospans form.
-
-\begin{thm}\label{SC}
+We first recall the double category of structured cospans.
+
+\begin{thm}\label{thm:SC}
 Given categories $\X$ and $\A$ with finite colimits and $L \maps \A \to \X$ a functor preserving
@@
 The following theorem establishes the isomorphism between structured and decorated cospan double categories under certain conditions.
-We denote by $\Rex$ the 2-category of finitely cocomplete categories, finitely cocontinuous functors and natural transformatoins.
+We denote by $\Rex$ the 2-category of finitely cocomplete categories, finitely cocontinuous functors and natural transformations.
+(In \cite{BC} we took as objects finitely cocomplete categories with chosen finite colimits, just so we could turn these into symmetric monoidal categories without any further choices!!!
+Should we do that here???)
 
@@
 
-As a left adjoint, this induced $L$ preserves all colimits that exist between the finitely cocomplete categories $\A$ and $\inta F$, so we can construct the double category of structured cospans $_L\lCsp(\inta F)$ of \cref{SC}.
+As a left adjoint, this induced $L$ preserves all colimits that exist between the finitely cocomplete categories $\A$ and $\inta F$, so we can construct the double category of structured cospans $_L\lCsp(\inta F)$ of \cref{thm:SC}.
 Its objects and vertical morphisms are those of the category $\A$ (as for $F\lCsp$ earlier), whereas horizontal 1-cells are now cospans of the form $\cspn{L(a)}{v}{L(b)}{}{}$ in the Grothendieck category $\inta F$ (\cref{def:GrothCat}).
@@
 
-\begin{cor}
+\begin{cor} \label{cor:symmoncat}
 Let $\A$ be a category with finite colimits and $F \maps (\A, +) \to (\Cat, \times)$ a symmetric lax monoidal pseudofunctor.  Then there exists a symmetric monoidal category $F\Csp$ in which:
@@
 
-\section{Applications}\label{Applications}
-
-In this section we present several examples.  The first was mentioned in the Introduction.
-
-\subsection{Graphs}
+\section{Applications}\label{applications}
+
+In this section we present several examples.
+We treat `open graphs' in some detail since a graph is the simplest sort of network and this example was not correctly handled by Fong's original theory of decorated cospans.
+We then turn to circuits, open Petri nets and open Petri nets with rates, going through these more rapidly since they are all very similar.
+All these examples can be handled using either decorated or structured cospans: the two approaches give equivalent symmetric monoidal double categories by \cref{thm:equiv}, but it should be apparent that structured cospans are simpler.
+We conclude with the example of open dynamical systems, which can only be handled using decorated cospans.
+
+\subsection{Open graphs}
 \label{subsec:graphs}
 
-In earlier work \cite[Sec.\ 5]{BC} we explained the flaws in Fong's original construction of a category of open graphs using decorated cospans.
-We also showed how to fix them using structured cospans.
-Our new approach to decorated cospans provides another, equivalent way to fix these flaws.
-
-For us a \define{graph} will be a pair of functions $s,t\maps E \to N$ where $E$ and $N$ are arbitrary sets.
+In earlier work \cite[Sec.\ 5]{BC} we explained the flaws in Fong's original treatment \cite{Fong} of open graphs using decorated cospans.
+We also showed how to fix these flaws using structured cospans.
+Our new approach to decorated cospans provides another solution, which however is equivalent.
+
+For us a \define{graph} will be a pair of functions $s,t\maps E \to N$ where $E$ and $N$ are finite sets.
 We call elements of $E$ \define{edges} and elements of $N$ \define{nodes}.
@@
 We can easily build a double category with `open graphs' as horizontal 1-cells using the machinery of structured cospans.
-Let $L \maps \Set \to \Graph$ be the functor that assigns to a set $N$ the \define{discrete graph} on $N$: the graph with no edges and $N$ as its set of vertices.
-Both $\Set$ and $\Graph$ have finite colimits, and the functor $L \maps \Set \to \Graph$ is left adjoint to the forgetful functor $R \maps \Graph \to \Set$ that assigns to a graph $G$ its underlying set of vertices $U(G)$.
-
-Thus, using structured cospans and appealing to \cref{SC}, we get a symmetric monoidal double category $_L \lCsp(\Graph)$ in which:
+Let $L \maps \Fin\Set \to \Graph$ be the functor that assigns to a finite set $N$ the \define{discrete graph} on that set: the graph with no edges and $N$ as its set of vertices.
+Both $\Set$ and $\Graph$ have finite colimits, and the functor $L$ is left adjoint to the forgetful functor $R \maps \Fin\Graph \to \Set$ that assigns to a graph $G$ its underlying set of vertices $U(G)$.
+Thus, using structured cospans and appealing to \cref{thm:SC}, we get a symmetric monoidal double category $_L \lCsp(\Graph)$ in which:
 \begin{itemize}
@@
 \path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$I_1$} (B)
-(C) edge node[above]{$O_1$} (B)
-(A') edge node[above]{$I_2$} (B')
-(C') edge node[above]{$O_2$} (B')
+(A) edge node[above]{$i_1$} (B)
+(C) edge node[above]{$o_1$} (B)
+(A') edge node[above]{$i_2$} (B')
+(C') edge node[above]{$o_2$} (B')
 (A) edge node [left]{$L(f)$} (A')
@@
 
-We can also build a double category with open graphs as horizontal 1-cells using decorated cospans.    For any set $N$ there is a category $F(N)$ where:
+We can also build a double category with open graphs as horizontal 1-cells using decorated cospans.    For any finite set $N$ there is a category $F(N)$ where:
 \begin{itemize}
@@
 
-In general, decorated cospans involve a pseudofunctor to $\Cat$, but in this example there is actually a functor $F \maps \Set \to \Cat$ that assigns to a set $N$ the above category $F(N)$.
+In general, decorated cospans are defined using a pseudofunctor to $\Cat$, but in this example there is an honest functor $F \maps \Fin\Set \to \Cat$ that assigns to a set $N$ the above category $F(N)$.
 Given a function $f \maps M \to N$, we define $F(f) \maps F(M) \to F(N)$ to map any graph structure $s,t \maps E \to M$ to the graph structure $f \circ s, f \circ t \maps E \to N$.
 
-We obtain a symmetric lax monoidal functor $F \maps (\Set, +) \to (\Cat,\times)$ by equipping $F$ with suitable functors $\phi_{N,N'} \maps F(N) \times F(N') \to F(N+N')$ for every pair of sets $N$ and $N'$, and also a functor $\phi_0 \maps F(\emptyset) \to 1 \in \Set$.
+We obtain a symmetric lax monoidal functor $F \maps (\Fin\Set, +) \to (\Cat,\times)$ by equipping $F$ with suitable functors $\phi_{N,N'} \maps F(N) \times F(N') \to F(N+N')$ for every pair of sets $N$ and $N'$, and also a functor $\phi_0 \maps F(\emptyset) \to 1 \in \Set$.
 The functor $\phi_0$ is uniquely determined since $1$ is the terminal category.
@@
 
-Given the symmetric lax monoidal functor $F \maps (\Set, +) \to (\Cat,\times)$, \cref{DC} gives us a symmetric monoidal double category $F\lCsp$ in which:
+Starting from the symmetric lax monoidal functor $F \maps (\Fin\Set, +) \to (\Cat,\times)$, \cref{DC} gives us a symmetric monoidal double category $F\lCsp$ in which:
 \begin{itemize}
-\item objects are sets,
+\item objects are finite sets,
 \item a vertical 1-morphism from $X$ to $X'$ is a function $f \maps X \to X'$,
@@
 We thus have two symmetric monoidal double categories: ${}_L \lCsp(\Graph)$ obtained from structured cospans and $F\lCsp$ obtained from decorated cospans.
-Both of these double categories have $\Set$ as their categories of objects, open graphs as horizontal 1-cells and maps of open graphs as 2-morphisms.
-One can show using Theorem \cref{thm:equiv} that $_L \lCsp(\Graph)$ and $F\lCsp$ are equivalent as symmetric monoidal double categories.
+Both of these double categories have $\Fin\Set$ as their categories of objects, open graphs as horizontal 1-cells, and maps of open graphs as 2-morphisms.
+It is thus quite plausible that ${}_L \lCsp(\Graph)$ and $F\lCsp$ are equivalent as symmetric monoidal double categories.
+
+Indeed, this fact follows from \cref{thm:equiv}.
+To show this, first note that $\inta F \cong \Graph$.
+Then, note that the left adjoint of the Grothendieck fibration $U \maps \inta F \to \Fin\Set$, composed with the isomorphism $\inta F \cong \Graph$, is the functor $L \maps \Fin\Set \to \Graph$ mapping each finite set to the discrete graph on that set.
+Thus,  ${}_L \lCsp(\Graph)$ is equivalent to the symmetric monoidal double category ${}_L \lCsp(\inta F)$ constructed in \cref{thm:equiv}, which in turn is equivalent
+to $F\lCsp$.
 
@@
 The edge labels can stand for resistors with any chosen resistance, capacitors with any chosen capacitance, inductors with any chosen inductance, or other circuit elements.
+
 To study such circuits quite generally we start by fixing any set $\La$ to serve as edge labels.
-
-\begin{defn}
-Given a set $\La$ of \define{labels}, an $\La$-\define{graph} is a graph $s,t\maps E\to N$
- equipped with a function $\ell \maps E \to \La$.
- A \define{morphism} from the $\La$-graph 
+We then define an $\La$-\define{graph} to be a graph $s,t\maps E\to N$
+ equipped with a function $\ell \maps E \to \La$.    There is a category $\Graph_\La$ with $\La$-graphs as objects, where a morphism from the $\La$-graph 
  \[ \xymatrix{\La & E \ar@<2.5pt>[r]^{s} \ar@<-2.5pt>[r]_{t} \ar[l]_{\ell} & N} \]
@@
 \]
-\end{defn}
-
-\begin{defn}
-\label{defn:Lgraph}
-We define $\Graph_\La$ to be the category of $\La$-graphs and morphisms between them, with composition given by
-\[  (f, g) \circ (f',g') = (f \circ f' , g \circ g')  .\]
-\end{defn}
 
 When $\La = 1$, an $\La$-graph reduces to a graph and $\Graph_\La$ reduces
-to the category $\Graph$ discussed in \cref{subsec:graphs}.  We now generalize the key
-ideas of that section from graphs to $\La$-graphs.   Everything works the same way, 
+to the category $\Graph$ discussed in \cref{subsec:graphs}.  All the ideas of \cref{subsec:graphs} generalize straightforwardly from graphs to $\La$-graphs.   Everything works the same way, 
 but following previous work \cite{BCR} we call an open $\La$-graph an $\La$-\define{circuit}.
 
-There is a functor $U \maps \Graph_\La \to \Fin\Set$ that takes an $\La$-graph to its underlying set of nodes. This has a left adjoint $L \maps \Fin\Set \to \Graph_\La$ sending
-any set to the $\La$-graph with that set of nodes and no edges.
+There is a functor $U \maps \Graph_\La \to \Fin\Set$ that takes an $\La$-graph to its underlying set of nodes.
+This has a left adjoint $L \maps \Fin\Set \to \Graph_\La$ sending any set to the $\La$-graph with that set of nodes and no edges.
 Both $\Fin\Set$ and $\Graph_\La$ have colimits, and $L$ preserves them.
-Thus \cref{SC} gives us a symmetric monoidal double category ${}_L \lCsp(\Graph_\La)$ where:
+Thus \cref{thm:SC} gives us a symmetric monoidal double category ${}_L \lCsp(\Graph_\La)$ where:
 \begin{itemize}
 \item an object is a finite set,
-\item a morphism is an isomorphism class of $\La$-circuits, where an
-$\La$-\define{circuit} is a cospan in $\Graph_\La$ of this form:
+\item a horizontal 1-cell is an $\La$-\define{circuit}, meaning a cospan in $\Graph_\La$ of this form:
 \[
@@
 \]
-and an \define{isomorphism} of $\La$-circuits is a commutative diagram in $\Graph_\La$ 
-of this form:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (E) at (3,-0.5) {$L(S)$};
-\node (F) at (5,-0.5) {$L(T)$};
-\node (G) at (4,0) {$G$};
-\node (G') at (4,-1) {$G'$};
-\path[->,font=\scriptsize,>=angle 90]
-(F) edge node[above]{$o$} (G)
-(G) edge node[left]{$h$} (G')
-(E) edge node[above]{$i$} (G)
-(E) edge node[below]{$i'$} (G')
-(F) edge node[below]{$o'$} (G');
-\end{tikzpicture}
-\]
-where $h$ is an isomorphism.
-\end{itemize} 
-This category has a nice universal property, found by Rosebrugh, Sabadini and
-Walters \cite{RSW}.  To state this, it is convenient to use the language of props.
-% Replaced strict symmetric with symmetric strict three times below
-Recall that a \define{prop} is a symmetric strict monoidal category whose objects are natural
-numbers, with tensor product of objects given by addition.
-An \define{algebra} of a prop $\T$ in a symmetric strict monoidal category $\C$ is a symmetric strict monoidal functor $A \maps \T \to \C$.
-A \define{morphism} from the algebra $A \maps \T \to \C$ to the algebra
-$A' \maps \T \to \C$ is a monoidal natural transformation $\alpha \maps A \To A'$.
-
-\begin{lem} As a symmetric monoidal category, ${}_L \Csp(\Graph_\La)$ is equivalent to a prop $\Circ_\La$.    
-\end{lem}
-
-\begin{proof}
-This is \cite[Proposition 4.3]{BCR}.
-\end{proof}
-
-\begin{prop} 
-\label{prop:LCirc_algebra}
-An algebra of $\Circ_\La$ in a symmetric strict monoidal category $\C$ is a 
-special commutative Frobenius monoid in $\C$ whose underlying object $x$ is equipped
-with an endomorphism $\ell \maps x \to x$ for each element $\ell \in \La$. 
-A morphism of algebras of $\Circ_\La$ in $\C$ is a morphism of special commutative Frobenius monoids that also preserves all these endomorphisms.
-\end{prop}
-
-\begin{proof}
-This was proved by Rosebrugh, Sabadini and Walters \cite{RSW}, and appears
-in the above form in \cite[Proposition 7.2]{BCR}.  
-\end{proof}
-
-In applications to circuits, the morphisms $\ell \maps x \to x$ describe different
-circuit elements, while the special commutative Frobenius monoid structure is used to split and join wires.
-This framework is used to study a wide variety of electrical circuits in a paper with Coya and Rebro \cite{BCR}, so the reader can turn there for details.
-To illustrate the ideas let us consider circuits of resistors, where a label in $\La = (0,\infty)$ serves to indicate the resistance of a resistor.
-In this case a typical morphism from $1$ to $3$ in
-$\Circ_\La$ looks like this:
-\[
-\scalebox{0.6}{
-\begin{tikzpicture}
-	\begin{pgfonlayer}{nodelayer}
-		\node [contact] (n1) at (-2,0) {$\bullet$};
-		\node [style = none] at (-2.1,0.3) {$$};
-		\node [contact] (n2) at (0,1) {$\bullet$};
-		\node [style = none] at (0,1.3) {$$};
-		\node [contact] (n3) at (0,-1) {$\bullet$};
-		\node [style = none] at (0,-1.3) {$$};
-		\node [contact] (n4) at (2,1) {$\bullet$};
-		\node [style = none] at (2.1,0.3) {$$};
-		\node [contact] (n5) at (2,-1) {$\bullet$};
-		\node [style = none] at (2.1,0.3) {$$};
-
-		\node [style = none] at (-1,1.1) {$2.53$};
-		\node [style = none] at (-1,-1.1) {$0.71$};
-		\node [style = none] at (1,1.3) {$9.6$};
-		\node [style = none] at (1,-1.3) {$1.02$};
-	     \node [style = none] at (-0.4,0) {$12.4$};
-	     \node [style = none] at (1.6,0) {$6.3$};
-
-		\node [style=none] (1) at (-3,0) {};
-		\node [style=none] (4) at (3,0) {};
-
-		\node [style=none] (ATL) at (-3.4,1.4) {};
-		\node [style=none] (ATR) at (-2.6,1.4) {};
-		\node [style=none] (ABR) at (-2.6,-1.4) {};
-		\node [style=none] (ABL) at (-3.4,-1.4) {};
-
-		\node [style=none] (X) at (-3,1.8) {$1$};
-		\node [style=inputdot] (inI) at (-2.8,0) {};
-
-		\node [style=none] (Z) at (3,1.8) {$3$};
-	 \node [style=inputdot] (outI') at (2.8,1) {};
-	 \node [style=inputdot] (outI'') at (2.8,0) {};
-	 \node [style=inputdot] (outI''') at (2.8,-1) {};
-
-		\node [style=none] (MTL) at (2.6,1.4) {};
-		\node [style=none] (MTR) at (3.4,1.4) {};
-		\node [style=none] (MBR) at (3.4,-1.4) {};
-		\node [style=none] (MBL) at (2.6,-1.4) {};
-
-	\end{pgfonlayer}
-	\begin{pgfonlayer}{edgelayer}
-		\draw [style=inarrow, bend left=20, looseness=1.00] (n1) to (n2);
-		\draw [style=inarrow, bend right=20, looseness=1.00] (n1) to (n3);
-		\draw [style=inarrow, bend left=0, looseness=1.00] (n2) to (n4);
-		\draw [style=inarrow, bend right=0, looseness=1.00] (n3) to (n4);
-		\draw [style=inarrow, bend right=0, looseness=1.00] (n3) to (n5);
-		\draw [style=inarrow] (n2) to (n3);
-%		\draw [style=inarrow] (W) to (Water);
-%		\draw [style=inarrow, bend left=40, looseness=1.00] (Water2) to (Something);
-%		\draw [style=inarrow, bend right=40, looseness=1.00] (Water2) to (Something);
-%		\draw [style=inarrow, bend left=40, looseness=1.00] (Something) to (A);
-%		\draw [style=inarrow, bend right=40, looseness=1.00] (Something) to (B);
-		\draw [style=simple] (ATL.center) to (ATR.center);
-		\draw [style=simple] (ATR.center) to (ABR.center);
-		\draw [style=simple] (ABR.center) to (ABL.center);
-		\draw [style=simple] (ABL.center) to (ATL.center);
-%		\draw [style=simple] (BTL.center) to (BTR.center);
-%		\draw [style=simple] (BTR.center) to (BBR.center);
-%		\draw [style=simple] (BBR.center) to (BBL.center);
-%		\draw [style=simple] (BBL.center) to (BTL.center);
-		\draw [style=simple] (MTL.center) to (MTR.center);
-		\draw [style=simple] (MTR.center) to (MBR.center);
-		\draw [style=simple] (MBR.center) to (MBL.center);
-		\draw [style=simple] (MBL.center) to (MTL.center);
-%		\draw [style=inputarrow] (outI) to (A);
-%		\draw [style=inputarrow] (outS) to (B);
-		\draw [style=inputarrow] (inI) to (n1);
-		\draw [style=inputarrow] (outI') to (n4);
-		\draw [style=inputarrow] (outI'') to (n5);
-		\draw [style=inputarrow] (outI''') to (n5);
-%		\draw [style=inputarrow] (inI') to (Water2);
-%		\draw [style=inputarrow] (inS') to (Water2);
-	\end{pgfonlayer}
-\end{tikzpicture}
-}
-\]
-The edges here represent wires, and the positive real numbers labeling them describe
-the resistance of the resistor on each wire.
-The points in the boxes represent `terminals': that is, points where we allow ourselves to attach a wire from another circuit.
-The points in the left box are called `inputs' and the points in the right box are called `outputs'.
-In electrical engineering we associate two real numbers to each terminal, called `potential' and `current'.
-Any circuit of resistors imposes a specific relation between the potentials and currents at its inputs and those at its outputs.
-All these relations, for all circuits of resistors, can be described using a single functor as follows.
-
-There is a symmetric monoidal category $\Fin\Rel_\R$ where the objects are finite-dimensional real vector spaces and a morphism from $V$ to $W$ is a \define{linear relation} from $V$ to $W$: that is, a relation $L \subseteq V \times W$ that is a linear subspace of $V \times W$.
-Composition in $\Fin\Rel_\R$ is the usual composition of relations, and the symmetric monoidal structure is provided by direct sum.
-
-There is a symmetric monoidal functor
-\[   \blacksquare \maps \Circ_\La \to \Fin\Rel_\R  \]
-% Added the line "sending any finite set $S$ to the vector space 
-% $\mathbb{R}^S \oplus \mathbb{R}^S$ and" to say what the black-box functor does on objects
-% Changed Prop. to Proposition 
-sending any finite set $S$ to the vector space $\R^S \oplus \R^S$ and
-sending any circuit of resistors to the relation it imposes between the potentials and currents at its inputs and those at its outputs \cite[Section 9]{BCR}.
-We can construct this using Proposition \ref{prop:LCirc_algebra}, by choosing a special commutative Frobenius monoid in $\Fin\Rel_\R$ whose underlying object is equipped with an endomorphism for each resistance $R \in (0,\infty)$.
-The object $\R^2 \in \Fin\Rel_\R$ is a special commutative Frobenius monoid in a standard way \cite[Section\ 8]{BCR}, so we choose this one.
-To define $\blacksquare \maps \Circ_\La \to \Fin\Rel_\R$ it then suffices to choose for each $R \in (0,\infty)$ a linear relation from $\R^2$ to itself.
-We use this:
-\[ \left\{(\phi_1,I_1,\phi_2,I_2) : \; I_1 = I_2 , \; \phi_2-\phi_1 = R I_1\right\} 
- \subseteq \R^2 \oplus \R^2.\]
-This expresses two laws of electrical engineering.   Kirchhoff's current law says that the 
-current flowing into a wire equals the current flowing out: $I_1 = I_2$.
-Ohm's law says that the voltage across a wire with a resistor on it, $\phi_2 - \phi_1$, is equal to the current flowing through the wire times the resistance $R$ of that resistor.
-
-\begin{comment}
-
-In a previous work \cite{BP}, Fong and the first author used decorated cospans to construct a symmetric monoidal category of `open passive linear circuits'.
-Roughly speaking, given a field $k$, a passive linear circuit is given by a `$k$-graph' which is a diagram in $\mathsf{FinSet}$ of the form:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (B) at (1,0) {$E$};
-\node (C) at (2,0) {$V$};
-\node (A) at (0,0) {$k^+$};
-\path[->,font=\scriptsize,>=angle 90]
-(B)edge node[above] {$r$}(A)
-(B)edge[bend left] node[above]{$s$}(C)
-(B)edge[bend right] node[below]{$t$}(C);
-\end{tikzpicture}
-\]
-Here the finite sets $E$ and $V$ are the sets of edges and vertices, respectively, and if we take the field $k = \mathbb{R}$, the function $r \maps E \to \mathbb{R}^+$ assigns to each edge $e \in E$ a positive real number $r(e) \in \mathbb{R}^+$ which can be interpreted as the resistance at the edge $e$.
-An open passive linear circuit is then given by a cospan of finite sets
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (B) at (1,0) {$V$};
-\node (C) at (2,0) {$Y$};
-\node (A) at (0,0) {$X$};
-\path[->,font=\scriptsize,>=angle 90]
-(A)edge node[above] {$i$}(B)
-(C)edge node[above]{$o$}(B);
-\end{tikzpicture}
-\]
-where the apex $V$ is equipped with the structure of a passive linear circuit. See the original paper for more details \cite{BP}.
-
-Let $\Graph_k$ be the category whose objects are given by $k$-graphs and morphisms by morphisms of $k$-graphs, where a morphism of $k$-graphs is given by a pair of functions $f \maps E \to E'$ and $g \maps V \to V'$ between the edge sets and vertex sets, respectively, of two $k$-graphs that respect the source and target functions of each.
-In a previous work introducing structured cospans, the first two authors showed that the category $\Graph_k$ has finite colimits \cite{BC2}.
-We can then obtain a double category of open passive linear circuits by defining a left adjoint $L \maps \Set \to \Graph_k$ that assigns to a set $V$ the discrete passive linear circuit $L(V)$ given by passive linear circuit with $V$ as its set of vertices and no edges.
-The resulting symmetric monoidal double category $_L \lCsp(\Graph_k)$ has:
-\begin{enumerate}
-\item{finite sets as objects,}
-\item{functions as vertical 1-morphisms,}
-\item{open passive linear circuits as horizontal 1-cells
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (B) at (1,0) {$V$};
-\node (C) at (2,0) {$Y$};
-\node (A) at (0,0) {$X$};
-\node (D) at (3,0) {$k^+$};
-\node (E) at (4,0) {$E$};
-\node (F) at (5,0) {$V$};
-\path[->,font=\scriptsize,>=angle 90]
-(E) edge node [above] {$r$} (D)
-(E) edge [bend left] node [above] {$s$} (F)
-(E) edge [bend right] node [below] {$t$} (F)
-(A)edge node[above] {$i$}(B)
-(C)edge node[above]{$o$}(B);
-\end{tikzpicture}
-\]
-and}
-\item{maps of cospans as 2-morphisms together with a map of passive linear circuits between the apices.
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$X_1$};
-\node (A') at (0,-1) {$X_2$};
-\node (C') at (2,-1) {$Y_2$};
-\node (B) at (1,0) {$V_1$};
-\node (C) at (2,0) {$Y_1$};
-\node (D) at (1,-1) {$V_2$};
-\node (E) at (3,0) {$k^+$};
-\node (E') at (3,-1) {$k^+$};
-\node (F) at (4,0) {$E_1$};
-\node (F') at (4,-1) {$E_2$};
-\node (G) at (5,0) {$V_1$};
-\node (G') at (5,-1) {$V_2$};
-\path[->,font=\scriptsize,>=angle 90]
-(F) edge node[above] {$r_1$} (E)
-(F) edge [bend left] node [above] {$s_1$} (G)
-(F) edge [bend right] node [below] {$t_1$} (G)
-(F') edge node[above] {$r_2$} (E')
-(F') edge [bend left] node [above] {$s_2$} (G')
-(F') edge [bend right] node [below] {$t_2$} (G')
+\item a 2-morphism is a commuting diagram in $\Graph_\La$ of this form:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$L(X_1)$};
+\node (B) at (1,0) {$G_1$};
+\node (C) at (2,0) {$L(Y_1)$};
+\node (A') at (0,-1) {$L(X_2)$};
+\node (B') at (1,-1) {$G_2$};
+\node (C') at (2,-1) {$L(Y_2)$.};
+\path[->,font=\scriptsize,>=angle 90]
 (A) edge node[above]{$i_1$} (B)
 (C) edge node[above]{$o_1$} (B)
-(A) edge node[left]{$h$} (A')
-(C) edge node[left]{$h'$} (C')
-(C') edge node [above] {$o_2$} (D)
-(A') edge node [above] {$i_2$} (D)
-(B) edge node [left] {$g$} (D)
-(F) edge node [left] {$f$} (F')
-(G) edge node [right] {$g$} (G');
-\end{tikzpicture}
-\]
-}
-\end{enumerate}
-We can also obtain a similar double category using decorated cospans: define a pseudofunctor $F \maps \mathsf{FinSet} \to \Cat$ that assigns to a finite set $V$ the category of all $k$-graph structures on the finite set $V$ and to a function $f \maps V \to V'$ the corresponding functor $F(f) \maps F(V) \to F(V')$ between decoration categories.
-Both categories $\mathsf{FinSet}$ and $\Cat$ are symmetric monoidal and the pseudofunctor $F \maps \mathsf{FinSet} \to \Cat$ is symmetric lax monoidal, as given a $k$-graph structure on a finite set $V_1$ denoted by an element $K_1 \in F(V_1)$ and a $k$-graph structure on a finite set $V_2$ denoted by an element $K_2 \in F(V_2)$, we can consider the $k$-graph structures simultaneously as a single graph structure $\phi_{V_1,V_2}(K_1,K_2)$ on the finite set $V_1+V_2$.
-Thus we get a family of natural transformations $$\phi_{V_1,V_2} \maps F(V_1) \times F(V_2) \to F(V_1+V_2)$$ as well as a morphism $\phi \maps 1_{\Graph_k} \to F(\emptyset)$ which together satisfy the coherence conditions of a monoidal functor.
-The braiding is also clear as the following diagram commutes:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (E) at (3,0) {$F(V_1) \times F(V_2)$};
-\node (G) at (5,0) {$F(V_2) \times F(V_1)$};
-\node (E') at (3,-1) {$F(V_1+V_2)$};
-\node (G') at (5,-1) {$F(V_2+V_1)$};
-\path[->,font=\scriptsize,>=angle 90]
-(E) edge node[left]{$\phi_{V_1,V_2}$} (E')
-(G) edge node[right]{$\phi_{V_2,V_1}$} (G')
-(E) edge node[above]{$\beta_{V_1,V_2}$} (G)
-(E') edge node[above]{$F(\beta_{V_1,V_2})$} (G');
-\end{tikzpicture}
-\]
-Thus the pseudofunctor $F$ is symmetric lax monoidal and so by Theorem \cref{DC} we get a symmetric monoidal double category $F\lCsp$ which has:
-\begin{enumerate}
-\item{objects as finite sets,}
-\item{vertical 1-morphisms as functions,}
-\item{horizontal 1-cells as cospans of finite sets together with the structure of a $k$-graph given by an element of the image of the apex under the pseudofunctor $F$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (D) at (-3,0) {$U$};
-\node (E) at (-2,0) {$V$};
-\node (F) at (-1,0) {$W$};
-\node (A) at (0,0) {$K \in F(V)$};
-\path[->,font=\scriptsize,>=angle 90]
-(D) edge node [above] {$i$} (E)
-(F) edge node [above] {$o$} (E);
-\end{tikzpicture}
-\]
-and}
-\item{2-morphisms as maps of cospans of finite sets 
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (E) at (3,0) {$U_1$};
-\node (F) at (5,0) {$W_1$};
-\node (G) at (4,0) {$V_1$};
-\node (E') at (3,-1) {$U_2$};
-\node (F') at (5,-1) {$W_2$};
-\node (G') at (4,-1) {$V_2$};
-\node (A) at (6,0) {$K_1 \in F(V_1)$};
-\node (B) at (6,-1) {$K_2 \in F(V_2)$};
-\path[->,font=\scriptsize,>=angle 90]
-(F) edge node[above]{$o_1$} (G)
-(E) edge node[left]{$f$} (E')
-(F) edge node[right]{$g$} (F')
-(G) edge node[left]{$h$} (G')
-(E) edge node[above]{$i_1$} (G)
-(E') edge node[above]{$i_2$} (G')
-(F') edge node[above]{$o_2$} (G');
-\end{tikzpicture}
-\]
-together with a morphism of $k$-graphs $\tau \maps F(h)(K_1) \to K_2$ in $F(V_2)$.}
-\end{enumerate}
-These two double categories $_L \lCsp(\Graph_k)$ and $F\lCsp$ are equivalent by Theorem \cref{thm:equiv}.
-
-\subsection{Markov processes}
-In another previous work \cite{BFP}, Fong, Pollard and the first author used decorated cospans to construct a symmetric monoidal category of `open Markov processes'.
-In this framework, a Markov process on a finite set $N$ is given by a diagram in $\Set$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (D) at (3,0) {$(0,\infty)$};
-\node (E) at (4,0) {$E$};
-\node (F) at (5,0) {$N$};
-\path[->,font=\scriptsize,>=angle 90]
-(E) edge node [above] {$r$} (D)
-(E) edge [bend left] node [above] {$s$} (F)
-(E) edge [bend right] node [below] {$t$} (F);
-\end{tikzpicture}
-\]
-where $E$ and $N$ are finite sets of edges and nodes, respectively.
-This is really just a special case of the previous example of passive linear circuits with $k = \mathbb{R}$.
-An open Markov process is then of course a cospan of finite sets where the apex is equipped with a Markov process:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (B) at (1,0) {$N$};
-\node (C) at (2,0) {$Y$};
-\node (A) at (0,0) {$X$};
-\node (D) at (3,0) {$(0,\infty)$};
-\node (E) at (4,0) {$E$};
-\node (F) at (5,0) {$N$};
-\path[->,font=\scriptsize,>=angle 90]
-(E) edge node [above] {$r$} (D)
-(E) edge [bend left] node [above] {$s$} (F)
-(E) edge [bend right] node [below] {$t$} (F)
-(A)edge node[above] {$i$}(B)
-(C)edge node[above]{$o$}(B);
-\end{tikzpicture}
-\]
-For example:
-\[
-\begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=3.7cm,
-thick,main node/.style={circle,fill=white!20,draw,font=\sffamily\Large\bfseries},terminal/.style={circle,fill=blue!20,draw,font=\sffamily\Large\bfseries}]]
-\node[main node](1) {$b_1$};
-\node[main node](2) [left=0.8cm of 1] {$a_1$};.5
-\node[main node](3) [below right=0.7cm and 2.4cm of 1] {$c_2$};
-\node[main node](5) [above right=0.7cm and 2.4cm of 1] {$c_1$};
-\node[main node](4) [above right=0.7cm and 2.4cm of 3] {$d_1$};
-\node(A) [left=1cm of 2,circle,draw,inner sep=1pt,fill=gray,color=purple] {};
-\node(C) [right=1cm of 4,circle,draw,inner sep=1pt,fill=gray,color=purple] {};
-\node[left=1.25 cm of 2,color=purple] {$S$};
-\node[right=1.25 cm of 4,color=purple] {$T$};
-\path[every node/.style={font=\sffamily\small}, shorten >=1pt]
-(3) edge [bend right =15] node[below] {$e_6$} (4)
-(5) edge [bend left =15] node[below] {$e_5$} (4)
-(2) edge [bend left=15] node[below] {$e_1$} (1)
-(1) edge [bend left =15] node[below] {$e_2$} (5)
-(5) edge [bend right =15] node[right] {$e_4$} (3)
-(1) edge [bend right =15] node[below] {$e_3$} (3)
-(3) edge [bend right =15] node[above] {$6$} (4)
-(5) edge [bend left =15] node[above] {$6$} (4)
-(2) edge [bend left=15] node[above] {$5$} (1)
-(1) edge [bend left =15] node[above] {$8$} (5)
-(5) edge [bend right =15] node[left] {$4$} (3)
-(1) edge [bend right =15] node[above] {$8$} (3);
-\path[color=purple, very thick, shorten >=10pt, ->, >=stealth] (C) edge (4);
-\path[color=purple, very thick, shorten >=10pt, ->, >=stealth] (A) edge (2);
-\end{tikzpicture}
-\]
-Here we have an open Markov process on the finite set $N = \{a_1,b_1,c_1,c_2,d_1 \}$ with input and output sets given by the singletons $S$ and $T$, respectively.
-
+(A') edge node[above]{$i_2$} (B')
+(C') edge node[above]{$o_2$} (B')
+(A) edge node [left]{$L(f)$} (A')
+(B) edge node [left]{$\alpha$} (B')
+(C) edge node [left]{$L(g)$} (C');
+\end{tikzpicture}
+\]
+\end{itemize}
+
+By Theorem ???
+we obtain a symmetric monoidal category ${}_L \Csp(\Graph_\La)$.
+In fact this symmetric monoidal category is equivalent to a prop, and the algebras of this prop were described in \cite[Proposition 7.2]{BCR}, and applied to study electrical circuits.
+
+\begin{comment}
 Fong, Pollard and the first author then add extra structure to open Markov processes such as populations at each node to obtain a symmetric monoidal category $\mathsf{DetlBalMark}$ of open Markov processes in `detailed balance' and then construct a black box functor $\blacksquare \maps \mathsf{DetBalMark} \to \mathsf{LinRel}$ that describes the steady state behavior of an open Markov process in detailed balance.
@@
 Both categories $\mathsf{FinSet}$ and $\mathsf{Mark}$ have finite colimits and the functor $L$ is left adjoint to the forgetful functor $R \maps \mathsf{Mark} \to \mathsf{FinSet}$ which maps a Markov process to its underlying finite set of states.
-By Theorem \cref{SC}, we get a symmetric monoidal double category $_L \lCsp(\mathsf{Mark})$ which has:
+By Theorem \cref{thm:SC}, we get a symmetric monoidal double category $_L \lCsp(\mathsf{Mark})$ which has:
 \begin{enumerate}
@@
 Master and the first author show the existence of a left adjoint $L \maps \Set \to \Petri$ where $\Petri$ is the category whose objects are Petri nets and whose `morphisms are morphisms of Petri nets'.
-They also show that $\Petri$ has finite colimits and thus using Theorem \cref{SC} obtain a symmetric monoidal double category $\lOpen(\Petri)$ of open Petri nets which has:
+They also show that $\Petri$ has finite colimits and thus using \cref{thm:SC} obtain a symmetric monoidal double category $\lOpen(\Petri)$ of open Petri nets which has:
 \begin{enumerate}
@@
 
-A \define{monoidal} bicategory $\bicat{A}$ comes with a pseudofunctor $\otimes\maps\bicat{A}\times\bicat{A}\to\bicat{A}$ and a unit object $I$ that are associative and unital up to coherent equivalence.
-A \define{braided} monoidal bicategory comes with a pseudonatural equivalence $\beta_{a,b}\maps a\ot b\to b\ot a$ and appropriate invertible modifications; it is \define{sylleptic} if there is an appropriate invertible modification $1_{a\ot b}\Rrightarrow\beta_{b,a}\circ\beta_{a,b}$ and it is \define{symmetric} if one further axiom holds.
-A \define{lax monoidal} pseudofunctor between monoidal bicategories $F\maps\bicat{A}\to\bicat{B}$ is a pseudofunctor equipped with pseudonatural transformations with components $\mu_{a,b}\maps Fa\otimes Fb\to F(a\otimes b)$ and $\mu_0\maps I\to FI$ along with coherent invertible modifications for associativity and unitality.
-This is commonly also called `weak monoidal' pseudofunctor.
-A \define{braided lax monoidal} pseudofunctor between braided monoidal bicategories comes with an appropriate invertible modification with components $F(\beta_{a,b})\circ \mu_{a,b}\cong\mu_{b,a}\circ \beta_{Fa,Fb}$; a \define{sylleptic lax monoidal} pseudofunctor satisfies one extra condition and a \define{symmetric lax monoidal} pseudofunctor between symmetric monoidal bicategories is just a sylleptic one.
-RIGHT???
 A \define{monoidal} bicategory $\bA$ comes with a pseudofunctor $\otimes\maps\bA\times\bA\to\bA$ and a unit object $I$ that are associative and unital up to coherent equivalence.
@@
 \subsection{Fibrations}\label{sec:fibrations}
+
 Basic material regarding the theory of fibrations can be found, for example, in \cite{Borc,Gray}.

### 2020-11-19 cospans.tex
few leftover edits

@@
 
-Since both double categories $_L \lCsp(\X)$ and $F\lCsp$ are symmetric monoidal, 
-{\chris in progress}
-
-as they are if both $\A$ and $\X$ have finite colimits, then this isomorphism of double categories $\mathbb{E} \maps _L \lCsp(\X) \to F\lCsp$ will be symmetric monoidal.
+Since both double categories are symmetric monoidal under the running assumptions (\cref{DC,SC}), we will now show that this double isomorphism is a symmetric monoidal one, namely $\lE=(\lE_0,\lE_1)$ is a symmetric strong monoidal double functor as per \cref{defn:monoidal_double_functor}.
+Indeed, $\lE_0=\mathrm{id}_\A$ is a symmetric monoidal functor trivially
+
  First, note that we have an isomorphism $\epsilon \maps 1_{F\lCsp} \to \mathbb{E}(1_{_L \lCsp(\X)})$ and natural isomorphisms $\mu_{c_1,c_2} \maps \mathbb{E}(c_1) \otimes \mathbb{E}(c_2) \to \mathbb{E}(c_1 \otimes c_2)$ for every pair of objects $c_1,c_2 \in {_L \mathbb{C} \textnormal{sp}(\X)}$ both of which are given by identities since both double categories $_L \lCsp(\X)$ and $F\lCsp$ have $\A$ as their category of objects and $\mathbb{E}_0=\id_{\A}$.
@@
 
+DEFINITION OF SYMMETRIC MONOIDAL ISOMORPHISM, BRIEFLY?
+
 \begin{thebibliography}{100}

### 2020-11-19 cospans.tex
fixed broken refs

@@
 In this section we build the symmetric monoidal double category $F \lCsp$ mentioned in the introduction, and then study the functoriality of this construction.
-The definition of a lax monoidal pseudofunctor is recalled in \cref{sec:2cats}, and the basics of double categories are recalled in \cref{sec:doublecats}.
+The definition of a lax monoidal pseudofunctor is recalled in \cref{subsec:bicats}, and the basics of double categories are recalled in \cref{sec:doublecats}.
 
@@
 
-Since both double categories are symmetric monoidal under the running assumptions (\cref{DC,SC}), we will now show that this double isomorphism is a symmetric monoidal one, namely $\lE=(\lE_0,\lE_1)$ is a symmetric strong monoidal double functor as per \cref{defn:monoidal_double_functor}.
+Since both double categories are symmetric monoidal under the running assumptions (\cref{DC,thm:SC}), we will now show that this double isomorphism is a symmetric monoidal one, namely $\lE=(\lE_0,\lE_1)$ is a symmetric strong monoidal double functor as per \cref{defn:monoidal_double_functor}.
 Indeed, $\lE_0=\mathrm{id}_\A$ is a symmetric monoidal functor trivially

### 2020-11-19 cospans.tex
fixed mistake in comment
missing citations on monoidal bicategories stuff
further small edits

@@
 \path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$$} (B)
-(C) edge node[above]{$$} (B);
+(A) edge node[above]{$i$} (B)
+(C) edge node[above]{$o$} (B);
 \end{tikzpicture}
@@
 \end{itemize}
-The symmetric monoidal structure is formed by using binary coproducts and the initial object.
+Composition is formed by taking pushouts in $\X$ and identity horizontal 1-cells are $L(a)\xrightarrow{\raisebox{-3pt}[0pt][0pt]{$=$}}L(a)\xleftarrow{\raisebox{-3pt}[0pt][0pt]{$=$}}L(a)$. 
+Moreover, the vertical category is cocartesian monoidal $(\A,+,0_A)$ and the tensor of horizontal 1-cells is
+\begin{displaymath}
+\begin{tikzcd}[column sep={.4in,between origins}, row sep=.1in]
+& x &&&& x' &&&& x+x' & \\
+&&&\ot&&&& = &&&& \\
+L(a)\ar[uur,"i"]&& L(b)\ar[uul,"o"'] && L(a')\ar[uur,"i'"] && L(b')\ar[uul,"o'"'] && L(a+a')\ar[uur,"i+i'"] && L(b+b')\ar[uul,"o+o'"'] 
+\end{tikzcd}
+\end{displaymath}
+using that $L$ preserves coproducts, with monoidal unit $L(0_A)\xrightarrow{\raisebox{-3pt}[0pt][0pt]{$\sim$}}0_X\xleftarrow{\raisebox{-3pt}[0pt][0pt]{$\sim$}}L(0_A)$.
+%!!!
+{\chris Shouldn't the horizontal monoidal unit be the identity on the vertical monoidal unit?}
 \end{thm}
@@
 This was proved in \cite[Theorems~2.3 \& 3.9]{BC2}.
-Composition is formed by taking pushouts in $\X$ and identity horizontal 1-cells are $L(a)\xrightarrow{\raisebox{-3pt}[0pt][0pt]{=}}L(a)\xleftarrow{\raisebox{-3pt}[0pt][0pt]{=}}L(a)$.
 In particular, the double category structure only requires that $\X$ have pushouts, whereas the symmetric monoidal structure also requires that $\X$ has binary coproducts and an initial object (and thus all finite colimits), and that $\A$ has and $L$ preserves finite coproducts \cite[Theorem~3.2.3]{CourserThesis}.
@@
 (In \cite{BC} we took as objects finitely cocomplete categories with chosen finite colimits, just so we could turn these into symmetric monoidal categories without any further choices!!!
-Should we do that here???)
+Should we do that here???) {\chris Can you tell if we can get away without doing that?}
 
@@
 
-These 2-equivalences further restrict to the case when the Grothendieck category $(X,\otimes)$ is specifically cocartesian monoidal itself. In that case, opfibrations
-$(\X,+)\to(\A,+)$ that strictly preserve chosen coproducts and initial object
+These 2-equivalences further restrict to the case when the Grothendieck category $(X,\otimes)$ is specifically cocartesian monoidal itself.
+In that case, opfibrations $(\X,+)\to(\A,+)$ that (strictly) preserve (chosen) coproducts and initial object
 %, and such that $+$ preserves cocartesian liftings, Christina: this should ALWAYS be the case, by universal properties!
@@
 Finally, we can further restrict to the setting of opfibrations that also preserve pushouts, i.e.\ all finite colimits, which is important for our purposes.
-The following result is in fact more general since it relates the existence of any class of colimits in the total category of an opfibration to their existence in the fibres; for a more detailed exposition, see \cite[Corollary~4.9]{Hermida1999}.
-%as well as Remark~4.11 therein regarding the non-necessary strictness condition. Is this obscuring or clarifying?
+The following result is in fact more general since it relates the existence of any class of colimits in the total category of an opfibration to their existence in the fibres; for a more detailed exposition, as well as the non-necessary strictness condition, see \cite[Corollary~4.9\&Remark~4.11]{Hermida1999}.
+%Is this obscuring or clarifying?
 
@@
 However, we \emph{will} use the formulation of coproducts and initial object in terms of the monoidal structure of $F$, and that is why correspondence \cref{monGroth} is necessary.
-DOES THIS MAKE SENSE TO ALL?? %still, we ARE going to use the formation of coproducts as above. Otherwise someone might think that the monoidal Groth story was redundant here!
+DOES THIS MAKE SENSE TO ALL??
 
@@
 
-IN THE PROOF ABOVE, WE ACTUALLY POTENTIALLY NEED SYMMETRY. DOES IT FOLLOW?
+{\chris In the proof above, we probably need isomorphism. Does it follow?}
 
@@
 
-%\begin{itemize}
-%\item 
-%for every pair of objects $a$ and $b$ of $\mathbf{A}$, we have natural isomorphisms
-%\[
-%\begin{tikzpicture}[scale=1.5]
-%\node (A) at (0,0) {$\mathbf{A}(a,b)$};
-%\node (B) at (2,0) {$\mathbf{X}(F(a),F(b))$};
-%\node (C) at (0,-1) {$\mathbf{X}(G(a),G(b))$};
-%\node (D) at (2,-1) {$\mathbf{X}(F(a),G(b))$};
-%\node (E) at (1,-0.5) {$\sigma_{a,b} \Nearrow$};
-%\path[->,font=\scriptsize,>=angle 90]
-%(A) edge node[above]{$F$} (B)
-%(B) edge node[right]{$(\sigma_{b})_*$} (D)
-%(A) edge node[left]{$G$} (C)
-%(C) edge node[above]{$(\sigma_a)^*$} (D);
-%\end{tikzpicture}
-%\]
-%where $(\sigma_a)^*$ and $(\sigma_b)_*$ are the functors induced by precomposition and postcompositon, respectively. Thus 
-%for each morphism $f \maps a \to b$ in $\mathbf{A}$, an invertible natural 2-morphism $\sigma_f \maps G(f) \sigma_a \xrightarrow{\sim} \sigma_{b} F(f)$ in $\mathbf{B}$
-%:
-%\[
-%\begin{tikzpicture}[scale=1.5]
-%\node (A) at (0,0) {$F(a)$};
-%\node (B) at (1,0) {$F(b)$};
-%\node (C) at (0,-1) {$G(a)$};
-%\node (D) at (1,-1) {$G(b)$};
-%\node (E) at (0.5,-0.5) {$\sigma_f \Nearrow$};
-%\path[->,font=\scriptsize,>=angle 90]
-%(A) edge node[above]{$F(f)$} (B)
-%(B) edge node[right]{$\sigma_{b}$} (D)
-%(A) edge node[left]{$\sigma_a$} (C)
-%(C) edge node[above]{$G(f)$} (D);
-%\end{tikzpicture}
-%\]
-%compatible with composition and identities.
-%end{itemize}
-%such that for each composable pair of morphisms $f \maps a \to b$ and $g \maps b \to c$ of $\mathbf{A}$, the following diagrams commute:
-%\[
-%\begin{tikzpicture}[scale=1.5]
-%\node (A) at (0,0.5) {$(G(g)G(f))\sigma_a$};
-%\node (A') at (2,0.5) {$G(g)(G(f) \sigma_a)$};
-%\node (B) at (0,-0.5) {$G(gf) \sigma_a$};
-%\node (C) at (4,0.5) {$G(g) (\sigma_b F(f))$};
-%\node (C') at (4,-0.5) {$\sigma_c F(gf)$};
-%\node (D) at (6,0.5) {$(G(g) \sigma_b) F(f)$};
-%\node (D') at (8,-0.5) {$\sigma_c (F(g)F(f))$};
-%\node (F) at (8,0.5) {$(\sigma_c F(g)) F(f)$};
-%\path[->,font=\scriptsize,>=angle 90]
-%(A) edge node[above]{$a'$} (A')
-%(A) edge node[left]{$\psi 1_{\sigma_a}$} (B)
-%(A') edge node[above]{$1_{G(g)} \sigma_f$} (C)
-%(B) edge node[above]{$\sigma_{gf}$} (C')
-%(C) edge node [above] {${a'}^{-1}$} (D)
-%(D') edge node [above] {$1_{\sigma_c} \phi$} (C')
-%(D) edge node [above] {$\sigma_g 1_{F(f)}$} (F)
-%(F) edge node [right] {$a'$} (D');
-%\end{tikzpicture}
-%\]
-%\[
-%\begin{tikzpicture}[scale=1.5]
-%\node (A) at (0,0) {$1_{G(a)} \sigma_a$};
-%\node (B) at (1,1) {$G(1_a) \sigma_a$};
-%\node (C) at (2,0) {$\sigma_a F(1_a)$};
-%\node (D) at (0.5,-1) {$\sigma_a$};
-%\node (E) at (1.5,-1) {$\sigma_a 1_{F(a)}$};
-%\path[->,font=\scriptsize,>=angle 90]
-%(A) edge node[left]{$\psi 1_{\sigma_a}$} (B)
-%(B) edge node[right]{$\sigma_{1_a}$} (C)
-%(A) edge node [left] {$\ell'$} (D)
-%(D) edge node [above] {${\rho'}^{-1}$} (E)
-%(E) edge node [right] {$1_{\sigma_a} \phi$} (C);
-%\end{tikzpicture}
-%\]
-%Christina: I removed the above, they are not needed I believe. Check again in the end.
+{\chris There used to be references for more details on the material that follows. Why would we not provide them?}
 

### 2020-11-19 cospans.tex
added Grothendieck category tensor

@@
 Suppose $\A$ has finite colimits and $F\maps(\A,+) \to (\Cat,\times)$ is a symmetric lax monoidal pseudofunctor that factors through $\Rex$ as an ordinary pseudofunctor.
-Then the symmetric monoidal double categories $F\lCsp$ of decorated cospans and $_L\lCsp(\inta F)$ of structured cospans are equivalent, where $L \maps \A \to \inta F$ is a left adjoint of the induced Grothendieck opfibration $U\maps \inta F \to \A$.
+Then the symmetric monoidal double categories $F\lCsp$ of decorated cospans and $_L\lCsp(\inta F)$ of structured cospans are isomorphic, where $L \maps \A \to \inta F$ is a left adjoint of the induced Grothendieck opfibration $U\maps \inta F \to \A$.
 \end{thm}
@@
 The second equivalence was also earlier observed by Shulman \cite{Shulman2008}.
-In more detail, if $(\mu,\mu_0)$ is the lax monoidal structure of the pseudofunctor $F$ as recalled in \cref{subsec:bicats}, each fibre category $\X_a=F(a)$ obtains a monoidal structure via
+
+In more detail, if $(\mu,\mu_0)$ is the lax monoidal structure of the pseudofunctor $F$ as recalled in \cref{subsec:bicats}, the induced monoidal structure on the total Grothendieck category $\X=\inta F$ is given by
+\begin{equation}\label{eq:explicitstructure2}
+\Big(a,x\in F(a)\Big)\ot_{\X}\Big(b,y\in F(b)\Big)=\Big(a+b,\mu_{a,b}(x,y)\in F(a+b)\Big), \qquad I_{\X}=\Big(0_A,\mu_0\Big)
+\end{equation}
+Moreover, each fibre category $\X_a=F(a)$ obtains a monoidal structure via
 \begin{equation}\label{eq:explicitstructure1}
@@
 
-These 2-equivalences further restrict to the case when the Grothendieck category $(X,\otimes)$ is specifically cocartesian monoidal itself.
-In that case, opfibrations $(\X,+)\to(\A,+)$ that (strictly) preserve (chosen) coproducts and initial object
+These 2-equivalences further restrict to the case when the Grothendieck category $(X,\otimes)$ is specifically cocartesian monoidal itself, with coproducts built up from \cref{eq:explicitstructure2}.
+In that case, opfibrations $(\X,+)\to(\A,+)$ that (strictly) preserve coproducts and initial object
 %, and such that $+$ preserves cocartesian liftings, Christina: this should ALWAYS be the case, by universal properties!

### 2020-11-19 cospans.tex
changed mu's to phi's, again

@@
 
-In more detail, if $(\mu,\mu_0)$ is the lax monoidal structure of the pseudofunctor $F$ as recalled in \cref{subsec:bicats}, the induced monoidal structure on the total Grothendieck category $\X=\inta F$ is given by
+In more detail, if $(\phi,\phi_0)$ is the lax monoidal structure of the pseudofunctor $F$ as recalled in \cref{subsec:bicats}, the induced monoidal structure on the total Grothendieck category $\X=\inta F$ is given by
 \begin{equation}\label{eq:explicitstructure2}
-\Big(a,x\in F(a)\Big)\ot_{\X}\Big(b,y\in F(b)\Big)=\Big(a+b,\mu_{a,b}(x,y)\in F(a+b)\Big), \qquad I_{\X}=\Big(0_A,\mu_0\Big)
+\Big(a,x\in F(a)\Big)\ot_{\X}\Big(b,y\in F(b)\Big)=\Big(a+b,\phi_{a,b}(x,y)\in F(a+b)\Big), \qquad I_{\X}=\Big(0_A,\phi_0\Big)
 \end{equation}
@@
 \begin{equation}\label{eq:explicitstructure1}
-\otimes_a\maps F(a)\times F(a)\xrightarrow{\mu_{a,a}}F(a+a)\xrightarrow{F(\nabla)}F(a),\quad
-I_a\maps\mathbf{1}\xrightarrow{\mu_0}F(0)\xrightarrow{F(!)}F(a)
+\otimes_a\maps F(a)\times F(a)\xrightarrow{\phi_{a,a}}F(a+a)\xrightarrow{F(\nabla)}F(a),\quad
+I_a\maps\mathbf{1}\xrightarrow{\phi_0}F(0)\xrightarrow{F(!)}F(a)
 \end{equation}
@@
 A \define{braided} monoidal bicategory comes with a pseudonatural equivalence $\beta_{a,b}\maps a\ot b\to b\ot a$ and appropriate invertible modifications; it is \define{sylleptic} if there is an appropriate invertible modification $1_{a\ot b}\Rrightarrow\beta_{b,a}\circ\beta_{a,b}$ and it is \define{symmetric} if one further axiom holds.
-A \define{lax monoidal} pseudofunctor between monoidal bicategories $F\maps\bA\to\bB$ is a pseudofunctor equipped with pseudonatural transformations with components $\mu_{a,b}\maps Fa\otimes Fb\to F(a\otimes b)$ and $\mu_0\maps I\to FI$ along with coherent invertible modifications for associativity and unitality.
-A \define{braided lax monoidal} pseudofunctor between braided monoidal bicategories comes with an appropriate invertible modification with components $F(\beta_{a,b})\circ \mu_{a,b}\cong\mu_{b,a}\circ \beta_{Fa,Fb}$; a \define{sylleptic lax monoidal} pseudofunctor satisfies one extra condition and a \define{symmetric lax monoidal} pseudofunctor between symmetric monoidal bicategories is just a sylleptic one.
+A \define{lax monoidal} pseudofunctor between monoidal bicategories $F\maps\bA\to\bB$ is a pseudofunctor equipped with pseudonatural transformations with components $\phi_{a,b}\maps Fa\otimes Fb\to F(a\otimes b)$ and $\phi_0\maps I\to FI$ along with coherent invertible modifications for associativity and unitality.
+A \define{braided lax monoidal} pseudofunctor between braided monoidal bicategories comes with an appropriate invertible modification with components $F(\beta_{a,b})\circ \phi_{a,b}\cong\phi_{b,a}\circ \beta_{Fa,Fb}$; a \define{sylleptic lax monoidal} pseudofunctor satisfies one extra condition and a \define{symmetric lax monoidal} pseudofunctor between symmetric monoidal bicategories is just a sylleptic one.
 

### 2020-11-19 cospans.tex
monoidal structure of E1 looks like strict

@@
 \]
-$$x_1+x_2 \mapseqq 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{x_1 \times x_2} F(m_1) \times F(m_2) \xrightarrow{\phi_{m_1,m_2}} F(m_1+m_2)$$}
+\begin{equation}\label{eq:tensordecoration}
+x_1+x_2 \mapseqq 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{x_1 \times x_2} F(m_1) \times F(m_2) \xrightarrow{\phi_{m_1,m_2}} F(m_1+m_2)
+\end{equation}}
 \item{the tensor product of two 2-morphisms $\alpha$ and $\beta$:
@@
 Moreover, the vertical category is cocartesian monoidal $(\A,+,0_A)$ and the tensor of horizontal 1-cells is
-\begin{displaymath}
+\begin{equation}\label{eq:tensorstuctured}
 \begin{tikzcd}[column sep={.4in,between origins}, row sep=.1in]
@@
 \end{tikzcd}
-\end{displaymath}
+\end{equation}
 using that $L$ preserves coproducts, with monoidal unit $L(0_A)\xrightarrow{\raisebox{-3pt}[0pt][0pt]{$\sim$}}0_X\xleftarrow{\raisebox{-3pt}[0pt][0pt]{$\sim$}}L(0_A)$.
-%!!!
-{\chris Shouldn't the horizontal monoidal unit be the identity on the vertical monoidal unit?}
+{\chris Shouldn't the horizontal monoidal unit be precisely the identity on the vertical monoidal unit?}
 \end{thm}
@@
 (In \cite{BC} we took as objects finitely cocomplete categories with chosen finite colimits, just so we could turn these into symmetric monoidal categories without any further choices!!!
-Should we do that here???) {\chris Can you tell if we can get away without doing that?}
+Should we do that here???) {\chris Can you tell if we can get away without doing that?
+Perhaps after you read up to before the proof?}
 
@@
 Since both double categories are symmetric monoidal under the running assumptions (\cref{DC,thm:SC}), we will now show that this double isomorphism is a symmetric monoidal one, namely $\lE=(\lE_0,\lE_1)$ is a symmetric strong monoidal double functor as per \cref{defn:monoidal_double_functor}.
-Indeed, $\lE_0=\mathrm{id}_\A$ is a symmetric monoidal functor trivially
+Indeed, $\lE_0=\mathrm{id}_\A$ is a symmetric monoidal functor trivially.
+For $\lE_1$, given two structured cospans $M=(a,\bot_a)\to(m,x)\leftarrow(b,\bot_b)$ and $M'=(a',\bot_{a'})\to(m',x')\leftarrow(b',\bot_{b'})$ in $_L\lCsp(\inta F)$, we compute the appropriate decorated cospans
+\begin{align*}
+\lE(M)\ot\lE(M')&\;\stackrel{\cref{eq:tensordecoration}}{=}\;a+a'\xrightarrow{i+i'}m+m'\xleftarrow{o+o'}b+b' \textrm{ with }\mathbf{1}\xrightarrow{x\times x'}F(m)\times F(m')\xrightarrow{\phi_{m,m'}}F(m+m') \\
+\lE(M\ot M')&\;\stackrel{\cref{eq:tensorstuctured}}{=}\;\lE\Big((a+a',\bot_{a+a'})\to\underbrace{(m+m',\phi_{m,m'}(x,x'))}_{\cref{eq:explicitstructure2}}\leftarrow(b+b',\bot_{b+b'})\Big)%=a+a'\xrightarrow{i+i'}m+m'\xleftarrow{o+o'}b+b' \textrm{ with }\phi_{m,m'}(x,x')
+\end{align*}
+which are essentially the same.
+{\chris Well they look equal to me...thoughts?} Moreover, the monoidal unit for the category of arrows of $F\lCsp$ is $0_\A\xrightarrow{\raisebox{-3pt}[0pt][0pt]{$=$}}0_\A\xleftarrow{\raisebox{-3pt}[0pt][0pt]{$=$}}0_\A$ with the trivial decoration
+$$\mathbf{1}\xrightarrow{\phi_0}F(0_A)\xrightarrow{F(\mathrm{id})}F(0_A)$$
+which is essentially the same as $\lE((0_A,\phi_0)\xrightarrow{\raisebox{-3pt}[0pt][0pt]{$=$}}(0_A,\phi_0)\xleftarrow{\raisebox{-3pt}[0pt][0pt]{$=$}}(0_A,\phi_0))$ again by \cref{eq:explicitstructure2}.
 

### 2020-11-19 cospans.tex
erased previous proof (for different direction functor), refer here if we need anything

@@
 which is essentially the same as $\lE((0_A,\phi_0)\xrightarrow{\raisebox{-3pt}[0pt][0pt]{$=$}}(0_A,\phi_0)\xleftarrow{\raisebox{-3pt}[0pt][0pt]{$=$}}(0_A,\phi_0))$ again by \cref{eq:explicitstructure2}.
-
- First, note that we have an isomorphism $\epsilon \maps 1_{F\lCsp} \to \mathbb{E}(1_{_L \lCsp(\X)})$ and natural isomorphisms $\mu_{c_1,c_2} \maps \mathbb{E}(c_1) \otimes \mathbb{E}(c_2) \to \mathbb{E}(c_1 \otimes c_2)$ for every pair of objects $c_1,c_2 \in {_L \mathbb{C} \textnormal{sp}(\X)}$ both of which are given by identities since both double categories $_L \lCsp(\X)$ and $F\lCsp$ have $\A$ as their category of objects and $\mathbb{E}_0=\id_{\A}$.
-The diagrams utilizing these maps that are required to commute do so trivially.
-
-For the arrow component $\mathbb{E}_1$, we have an isomorphism $\delta \maps U_{1_{F\lCsp}} \to \mathbb{E}(U_{1_{_L \lCsp(\X)}})$ where the horizontal 1-cell $U_{1_{F\lCsp}}$ is given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$1_\A$};
-\node (B) at (1,0) {$1_\A$};
-\node (C) at (2,0) {$1_\A$};
-\node (D) at (3,0) {$!_{1_{\A}} \in F(1_\A)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$1$} (B)
-(C) edge node[above]{$1$} (B);
-\end{tikzpicture}
-\]
-where $!_{1_{\A}} = \phi \maps 1 \to F(1_\A)$ is the trivial decoration which comes from the structure of the symmetric lax monoidal pseudofunctor $F \maps \A \to \Cat$.
-The horizontal 1-cell $U_{1_{_L \lCsp(\X)}}$ is given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$L(1_\A)$};
-\node (B) at (1,0) {$L(1_\A)$};
-\node (C) at (2,0) {$L(1_\A)$};
-%\node (D) at (3,0.5) {$I \in F(1_\mathrm{A})$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$1$} (B)
-(C) edge node[above]{$1$} (B);
-\end{tikzpicture}
-\]
-where here we make use of the fact that the left adjoint $L \maps (\A,+,1_\A) \to (\X,+,1_\X)$ preserves all colimits and thus $L(1_\A) \cong 1_\X$.
-The horizontal 1-cell $\mathbb{E}(U_{1_{_L \mathbb{C} \textnormal{sp}(\X)}})$ is then given by the pair:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$1_\A$};
-\node (B) at (1.25,0) {$R(L(1_\A))$};
-\node (C) at (2.5,0) {$1_\A$};
-\node (D) at (4.5,0) {$!_{R(L(1_\A))} \in F(R(L(1_\A)))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{${\eta_{1_\A}}$} (B)
-(C) edge node[above]{${\eta_{1_\A}}$} (B);
-\end{tikzpicture}
-\]
-The isomorphism $\delta$ is then given by the 2-morphism:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$1_\A$};
-\node (B) at (1,0) {$1_{\A}$};
-\node (C) at (2,0) {$1_\A$};
-\node (A') at (0,-1) {$1_\A$};
-\node (B') at (1,-1) {$R(L(1_\A))$};
-\node (C') at (2,-1) {$1_\A$};
-\node (D) at (3,0) {$!_{1_\A} \in F(1_\A)$};
-\node (D') at (3.75,-1) {$!_{R(L(1_\A))} \in F(R(L(1_\A)))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$1$} (B)
-(C) edge node[above]{$1$} (B)
-(A') edge node[above]{${\eta_{1_\A}}$} (B')
-(C') edge node[above]{${\eta_{1_\A}}$} (B')
-(A) edge node [left]{$1$} (A')
-(B) edge node [left]{${\eta_{1_\A}}$} (B')
-(C) edge node [left]{$1$} (C');
-\end{tikzpicture}
-\]
-$$\tau_{{\eta_{1_\A}}} \maps F({\eta_{1_\A}})(!_{1_\A})) \to !_{R(L(1_\A))}$$
-of $F\lCsp$. This is just the natural isomorphism $\mathbb{E}_{1_\A}$ from earlier.
-
-Given two horizontal 1-cells $M$ and $N$ of $_L \lCsp(\X)$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$L(c_1)$};
-\node (B) at (1,0) {$x$};
-\node (C) at (2,0) {$L(c_2)$};
-\node (D) at (3,0) {$L(c_1')$};
-\node (E) at (4,0) {$x'$};
-\node (F) at (5,0) {$L(c_2')$};
-%\node (D) at (3,0.5) {$!_c \in F(c)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i$} (B)
-(C) edge node[above]{$o$} (B)
-(D) edge node[above]{$i'$} (E)
-(F) edge node[above]{$o'$} (E);
-\end{tikzpicture}
-\]
-their images $\mathbb{E}(M)$ and $\mathbb{E}(N)$ are given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$c_1$};
-\node (B) at (1,0) {$R(x)$};
-\node (C) at (2,0) {$c_2$};
-\node (D) at (3,0) {$c_1'$};
-\node (E) at (4,0) {$R(x')$};
-\node (F) at (5,0) {$c_2'$};
-\node (G) at (1,-0.5) {$x \in F(R(x))$};
-\node (H) at (4,-0.5) {$x' \in F(R(x'))$};
-%\node (D) at (3,0.5) {$!_c \in F(c)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$R(i) \eta_{c_1}$} (B)
-(C) edge node[above]{$R(o) \eta_{c_2}$} (B)
-(D) edge node[above]{$R(i') \eta_{c_1'}$} (E)
-(F) edge node[above]{$R(o') \eta_{c_2'}$} (E);
-\end{tikzpicture}
-\]
-and so $\mathbb{E}(M) \otimes \mathbb{E}(N)$ is given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$c_1+c_1'$};
-\node (B) at (3.25,0) {$R(x)+R(x')$};
-\node (C) at (6.5,0) {$c_2+c_2'$};
-\node (D) at (3.25,-0.5) {$d_{\mathbb{E}(M) \otimes \mathbb{E}(N)} \in F(R(x)+R(x'))$}; 
-%\node (D) at (3,0.5) {$!_c \in F(c)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$R(i) \eta_{c_1} +R(i') \eta_{c_1'}$} (B)
-(C) edge node[above]{$R(o) \eta_{c_2} + R(o) \eta_{c_2'}$} (B);
-\end{tikzpicture}
-\]
-where $$d_{\mathbb{E}(M) \otimes \mathbb{E}(N)} \maps 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{x \times x'} F(R(x)) \times F(R(x')) \xrightarrow{\phi_{R(x),R(x')}} F(R(x)+R(x')).$$ On the other hand, $M \otimes N$ is given by
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$L(c_1+c_1')$};
-\node (B) at (2,0) {$x+x'$};
-\node (C) at (4,0) {$L(c_2+c_2')$};
-%\node (D) at (3,0.5) {$!_c \in F(c)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$(i+i')\phi_{c_1,c_1'}^{-1}$} (B)
-(C) edge node[above]{$(o+o')\phi_{c_2,c_2'}^{-1}$} (B);
-\end{tikzpicture}
-\]
-and $\mathbb{E}(M \otimes N)$ is given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$c_1+c_1'$};
-\node (B) at (4,0) {$R(x+x')$};
-\node (C) at (8,0) {$c_2+c_2'$};
-\node (D) at (4,-0.5) {$d_{\mathbb{E}(M \odot N)} \in F(R(x+x')).$};
-%\node (D) at (3,0.5) {$!_c \in F(c)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$R((i+i')\phi_{c_1,c_1'}^{-1}) \eta_{c_1+c_1'}$} (B)
-(C) edge node[above]{$R((o+o')\phi_{c_2,c_2'}^{-1}) \eta_{c_2+c_2'}$} (B);
-\end{tikzpicture}
-\]
-We then have a 2-isomorphism $\mu_{M,N} \maps E(M) \otimes E(N) \xrightarrow{\sim} E(M \otimes N)$ in $F\lCsp$ given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (-2.5,0) {$c_1+c_1'$};
-\node (B) at (1,0) {$R(x)+R(x')$};
-\node (C) at (4.5,0) {$c_2+c_2'$};
-\node (A') at (-2.5,-1) {$c_1+c_1'$};
-\node (B') at (1,-1) {$R(x+x')$};
-\node (C') at (4.5,-1) {$c_2+c_2'$};
-\node (D) at (6.55,0) {$d_{\mathbb{E}(M) \otimes \mathbb{E}(N)} \in F(R(x)+R(x'))$};
-\node (D') at (6.55,-1) {$d_{\mathbb{E}(M \otimes N)} \in F(R(x+x'))$};
-\node (E) at (2,-1.5) {$\tau_\mu \maps F(\kappa)(d_{\mathbb{E}(M) \odot \mathbb{E}(N)}) \to d_{\mathbb{E}(M \odot N)}$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$R(i)\eta_{c_1} + R(i')\eta_{c_1'}$} (B)
-(C) edge node[above]{$R(o)\eta_{c_2} + R(o')\eta_{c_2'}$} (B)
-(A') edge node[above]{$R((i+i')\phi_{c_1,c_1'}^{-1}) \eta_{c_1+c_1'}$} (B')
-(C') edge node[above]{$R((o+o')\phi_{c_2,c_2'}^{-1}) \eta_{c_2+c_2'}$} (B')
-(A) edge node [left]{$1$} (A')
-(B) edge node [left]{$\kappa$} (B')
-(C) edge node [right]{$1$} (C');
-\end{tikzpicture}
-\]
-where $\kappa$ is the isomorphism which comes from $R \maps \X \to \A$ preserving finite colimits.
-
-The isomorphisms $\delta$ and $\mu$ satisfy the left and right unitality squares, associativity hexagon and braiding square. 
-%Kenny: I think this might be a good place to cut the monoidal stuff.
-%Christina: Deal! They are right below.
-
-\begin{comment}
-To see this, let $M_1,M_2$ and $M_3$ be horizontal 1-cells in $_L \lCsp(\X)$ given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$L(c_1)$};
-\node (B) at (1,0) {$x_1$};
-\node (C) at (2,0) {$L(c_1')$};
-\node (D) at (3,0) {$L(c_2)$};
-\node (E) at (4,0) {$x_2$};
-\node (F) at (5,0) {$L(c_2')$};
-\node (G) at (6,0) {$L(c_3)$};
-\node (H) at (7,0) {$x_3$};
-\node (I) at (8,0) {$L(c_3')$};
-%\node (D) at (3,0.5) {$!_c \in F(c)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i_1$} (B)
-(C) edge node[above]{$o_1$} (B)
-(D) edge node[above]{$i_2$} (E)
-(F) edge node[above]{$o_2$} (E)
-(G) edge node[above]{$i_3$} (H)
-(I) edge node[above]{$o_3$} (H);
-\end{tikzpicture}
-\]
-The left unitality square:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$1_{F\lCsp} \otimes \mathbb{E}(M_1)$};
-\node (B) at (3,0) {$\mathbb{E}(1_{ _L \lCsp(\X)}) \otimes \mathbb{E}(M_1)$};
-\node (C) at (0,-1) {$\mathbb{E}(M_1)$};
-\node (D) at (3,-1) {$\mathbb{E}(1_{ _L \lCsp(\X)} \otimes M_1)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$\delta \otimes 1$} (B)
-(B) edge node[right]{$\mu_{1,M_1}$} (D)
-(A) edge node[left]{$\lambda'$} (C)
-(D) edge node[above]{$\mathbb{E}(\lambda)$} (C);
-\end{tikzpicture}
-\]
-has an underlying diagram of maps of cospans given by:
-\[
-		\begin{tikzpicture}
-			\node (d) at (7.5,0) {$\mathbb{E}(1_{ _L \lCsp(\X)}) \otimes \mathbb{E}(M_1)$};
-			\node (a) at (-6,0) {$1_\A+c_1$};
-			\node (b) at (-0.5,0) {$R(L(1_\A)) + R(x_1)$};
-			\node (c) at (5,0) {$1_\A+c_1'$};
-			\node (d2) at (7.5,1) {$1_{F\lCsp} \otimes \mathbb{E}(M_1)$};
-			\node (a2) at (-6,1) {$1_\A+c_1$};
-			\node (b2) at (-0.5,1) {$1_\A+R(x_1)$};
-			\node (c2) at (5,1) {$1_\A+c_1'$};
-			\node (d3) at (7.5,2) {$\mathbb{E}(M_1)$};
-                                \node (a3) at (-6,2) {$c_1$};
-			\node (b3) at (-0.5,2) {$R(x_1)$};
-			\node (c3) at (5,2) {$c_1'$};
-			\node (d4) at (7.5,-1) {$\mathbb{E}(1_{ _L \lCsp(\X)} \otimes M_1)$};
-                                \node (a5) at (-6,-1) {$1_\A+c_1'$};
-			\node (b5) at (-0.5,-1) {$R(L(1_\A)+x_1)$};
-			\node (c5) at (5,-1) {$1_\A+c_1'$};
-			\node (d5) at (7.5,-2) {$\mathbb{E}(M_1)$};
-                                \node (a6) at (-6,-2) {$c_1$};
-			\node (b6) at (-0.5,-2) {$R(x_1)$};
-			\node (c6) at (5,-2) {$c_1'$};
-			\path[->,font=\scriptsize,>=angle 90]
-			(d2) edge node [left]{$\lambda$} (d3)
-			(d2) edge node [left] {$\delta \otimes 1$} (d)
-			(d) edge node [left] {$\mu_{1,M_1}$} (d4)
-			(d4) edge node [left] {$\mathbb{E}(\lambda)$} (d5)
-			(a) edge node[above]{$\eta_{1_\A}+R(i_1)\eta_{c_1}$} (b)
-			(c) edge node[above]{$\eta_{1_\A}+R(o_1)\eta_{c_1'}$} (b)
-                                (a2) edge node[above]{$1+R(i_1)\eta_{c_1}$} (b2)
-			(c2) edge node[above]{$1+R(o_1)\eta_{c_1'}$} (b2)
-                                (a2) edge node[left]{$1$} (a)
-                                (b2) edge node[left]{$\eta_{1_\A}+1$} (b)
-(b2) edge node[right]{$\tau_2$} (b)
-			(c2) edge node[right]{$1$} (c)
-                                (a3) edge node[above]{$R(i_1)\eta_{c_1}$} (b3)
-			(c3) edge node[above]{$R(o_1)\eta_{c_1'}$} (b3)
-                                (a2) edge node[left]{$\lambda_{\A}$} (a3)
-                                (b2) edge node[left]{$\lambda_{\A}$} (b3)
-(b2) edge node[right]{$\tau_1$} (b3)
-			(c2) edge node[right]{$\lambda_{\A}$} (c3)
-                                (a5) edge node[above]{$(\mu_{L(1_\A),d_1})(\eta_{1_\A}+R(i_1)\eta_{c_1})$} (b5)
-			(c5) edge node[above]{$(\mu_{L(1_\A),d_1})(\eta_{1_\A}+R(o_1)\eta_{c_1'})$} (b5)
-                                (a) edge node[left]{$1$} (a5)
-                                (b) edge node[left]{$\mu_{L(1_\A),x_1}$} (b5)
-(b) edge node[right]{$\tau_3$} (b5)
-			(c) edge node[right]{$1$} (c5)
-                                (a6) edge node[above]{$R(i_1)\eta_{c_1}$} (b6)
-			(c6) edge node[above]{$R(o_1)\eta_{c_1'}$} (b6)
-                                (a5) edge node[left]{$\lambda_{\A}$} (a6)
-                                (b5) edge node[left]{$R(\lambda_{\X})$} (b6)
- (b5) edge node[right]{$\tau_4$} (b6)
-			(c5) edge node[right]{$\lambda_{\A}$} (c6);
-		\end{tikzpicture}
-	\]
-with the corresponding maps of decorations amounting to the following commutative diagram in $F(R(x_1))$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (-.5,0) {$F(\lambda_{\A})(!_{1_\A}+x_1)$};
-\node (C) at (4,0) {$F(R(\lambda_{\X})(\mu_{L(1_\A),x_1}))(!_{R(L(1_\A))} +x_1$)};
-\node (D) at (-.5,-1) {$x_1$};
-\node (E) at (4,-1) {$F(R(\lambda_\X))(x_{!+1})$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$F(R(\lambda_{\X})(\mu_{L(1_\A),x_1}))(\tau_2)$} (C)
-(A) edge node[left]{$\tau_1$} (D)
-(E) edge node[above]{$\tau_4$} (D)
-(C) edge node[right]{$F(R(\lambda_\X))(\tau_3)$} (E);
-\end{tikzpicture}
-\]
-where $x_{!+1}$ is the decoration $x_1$ on the object $R(L(1_\A)+x_1) \in \A$.
-The above square commutes because $$F(\lambda_\A)(!_{1_\A}+x_1) = F(R(\lambda_\X)(\mu_{L(1_\A),x_1})(\eta_{1_\A}+1))(!_{1_\A}+x_1)$$ as the corresponding left unitality square for the finite colimit preserving functor $R \maps (\X,1_\X,+) \to (\A,1_\A,+)$ commutes.
-The right unitality square is similar.
-The associator hexagon:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$(\mathbb{E}(M_1) \otimes \mathbb{E}(M_2)) \otimes \mathbb{E}(M_3)$};
-\node (B) at (3.5,0) {$\mathbb{E}(M_1 \otimes M_2) \otimes \mathbb{E}(M_3)$};
-\node (C) at (7,0) {$\mathbb{E}((M_1 \otimes M_2) \otimes M_3)$};
-\node (A') at (0,-1) {$\mathbb{E}(M_1) \otimes (\mathbb{E}(M_2) \otimes \mathbb{E}(M_3))$};
-\node (B') at (3.5,-1) {$\mathbb{E}(M_1) \otimes \mathbb{E}(M_2 \otimes M_3)$};
-\node (C') at (7,-1) {$\mathbb{E}(M_1 \otimes (M_2 \otimes M_3))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$\mu_{M_1,M_2} \otimes 1$} (B)
-(B) edge node[above]{$\mu_{M_1 \otimes M_2,M_3}$} (C)
-(A') edge node[above]{$1 \otimes \mu_{M_2,M_3}$} (B')
-(B') edge node[above]{$\mu_{M_1,M_2 \otimes M_3}$} (C')
-(A) edge node [left]{$a'$} (A')
-(C) edge node [right]{$\mathbb{E}(a)$} (C');
-\end{tikzpicture}
-\]
-has underlying maps of cospans given by:
-\[
-		\begin{tikzpicture}
-\node(d) at (1.5,7) {$(\mathbb{E}(M_1) \otimes \mathbb{E}(M_2)) \otimes \mathbb{E}(M_3)$};
-\node (d2) at (1.5,8) {$\mathbb{E}(M_1 \otimes M_2) \otimes \mathbb{E}(M_3)$};
-\node (d3) at (1.5,9) {$\mathbb{E}((M_1 \otimes M_2) \otimes M_3)$};
-\node (d4) at (1.5,10) {$\mathbb{E}(M_1 \otimes (M_2 \otimes M_3))$};
-\node (d5) at (1.5,6) {$\mathbb{E}(M_1) \otimes (\mathbb{E}(M_2) \otimes \mathbb{E}(M_3))$};
-\node (d6) at (1.5,5) {$\mathbb{E}(M_1) \otimes \mathbb{E}(M_2 \otimes M_3)$};
-\node (d7) at (1.5,4) {$\mathbb{E}(M_1 \otimes (M_2 \otimes M_3))$};
-			\node (a) at (-4.25,0) {$(c_1+c_2)+c_3$};
-			\node (b) at (2.5,0) {$(R(x_1)+R(x_2))+R(x_3)$};
-			\node (c) at (9.25,0) {$(c_1'+c_2')+c_3'$};
-			\node (a2) at (-4.25,1) {$(c_1+c_2)+c_3$};
-			\node (b2) at (2.5,1) {$R(x_1+x_2)+R(x_3)$};
-			\node (c2) at (9.25,1) {$(c_1'+c_2')+c_3'$};
-                                \node (a3) at (-4.25,2) {$(c_1+c_2)+c_3$};
-			\node (b3) at (2.5,2) {$R((x_1+x_2)+x_3)$};
-			\node (c3) at (9.25,2) {$(c_1'+c_2')+c_3'$};
-                                \node (a4) at (-4.25,3) {$c_1+(c_2+c_3)$};
-			\node (b4) at (2.5,3) {$R(x_1+(x_2+x_3))$};
-			\node (c4) at (9.25,3) {$c_1' + (c_2' + c_3')$};
-                                \node (a5) at (-4.25,-1) {$c_1+(c_2+c_3)$};
-			\node (b5) at (2.5,-1) {$R(x_1)+(R(x_2)+R(x_3))$};
-			\node (c5) at (9.25,-1) {$c_1' + (c_2' + c_3')$};
-                                \node (a6) at (-4.25,-2) {$c_1+(c_2+c_3)$};
-			\node (b6) at (2.5,-2) {$R(x_1)+R(x_2+x_3)$};
-			\node (c6) at (9.25,-2) {$c_1' + (c_2' + c_3')$};
-                                \node (a7) at (-4.25,-3) {$c_1+(c_2+c_3)$};
-			\node (b7) at (2.5,-3) {$R(x_1+(x_2+x_3))$};
-			\node (c7) at (9.25,-3) {$c_1' + (c_2' + c_3')$};
-			\path[->,font=\scriptsize,>=angle 90]
-(d) edge node[left] {$\mu_{M_1,M_2} \otimes 1$} (d2)
-(d2) edge node[left] {$\mu_{M_1 \otimes M_2,M_3}$} (d3)
-(d3) edge node[left] {$\mathbb{E}(a)$} (d4)
-(d) edge node[left] {$a'$} (d5)
-(d5) edge node[left] {$1 \otimes \mu_{M_2,M_3}$} (d6)
-(d6) edge node[left] {$\mu_{M_1,M_2 \otimes M_3}$} (d7)
-			(a) edge node[above]{$(R(i_1)\eta_{c_1}+R(i_2)\eta_{c_2})+R(i_3)\eta_{c_3}$} (b)
-			(c) edge node[above]{$(R(o_1)\eta_{c_1'}+R(o_2)\eta_{c_2'})+R(o_3)\eta_{c_3'}$} (b)
-                                (a2) edge node[above]{$R(i_1+i_2)\eta_{c_1+c_2}+R(i_3)\eta_{c_3}$} (b2)
-			(c2) edge node[above]{$R(o_1+o_2)\eta_{c_1'+c_2'}+R(o_3)\eta_{c_3'}$} (b2)
-                                (a) edge node[left]{$1$} (a2)
-                                (b) edge node[left]{$\kappa + 1$} (b2)
-(b) edge node[right]{$\tau_1$} (b2)
-			(c) edge node[right]{$1$} (c2)
-                                (a3) edge node[above]{$R((i_1+i_2)+i_3)\eta_{(c_1+c_2)+c_3}$} (b3)
-			(c3) edge node[above]{$R((o_1+o_2)+o_3)\eta_{(c_1'+c_2')+c_3'}$} (b3)
-                                (a2) edge node[left]{$1$} (a3)
-                                (b2) edge node[left]{$\kappa$} (b3)
-(b2) edge node[right]{$\tau_2$} (b3)
-			(c2) edge node[right]{$1$} (c3)
-                                (a4) edge node[above]{$R(i_1+(i_2+i_3))\eta_{c_1+(c_2+c_3)}$} (b4)
-			(c4) edge node[above]{$R(o_1+(o_2+o_3))\eta_{c_1'+(c_2'+c_3')}$} (b4)
-                                (a3) edge node[left]{$a_\A$} (a4)
-                                (b3) edge node[left]{$R(a_\X)$} (b4)
-(b3) edge node[right]{$\tau_3$} (b4)
-			(c3) edge node[right]{$a_\A$} (c4)
-                                (a5) edge node[above]{$R(i_1)\eta_{c_1}+(R(i_2)\eta_{c_2}+R(i_3)\eta_{c_3})$} (b5)
-			(c5) edge node[above]{$R(o_1)\eta_{c_1'}+(R(o_2)\eta_{c_2'}+R(o_3)\eta_{c_3'})$} (b5)
-                                (a) edge node[left]{$a_\A$} (a5)
-                                (b) edge node[left]{$a_\A$} (b5)
-(b) edge node[right]{$\tau_4$} (b5)
-			(c) edge node[right]{$a_\A$} (c5)
-                                (a6) edge node[above]{$R(i_1)\eta_{c_1}+R(i_2+i_3)\eta_{c_2+c_3}$} (b6)
-			(c6) edge node[above]{$R(o_1)\eta_{c_1'}+R(o_2+o_3)\eta_{c_2'+c_3'}$} (b6)
-                                (a5) edge node[left]{$1$} (a6)
-                                (b5) edge node[left]{$1+\kappa$} (b6)
- (b5) edge node[right]{$\tau_5$} (b6)
-			(c5) edge node[right]{$1$} (c6)
-                                (a7) edge node[above]{$R(i_1+(i_2+i_3))\eta_{c_1+(c_2+c_3)}$} (b7)
-			(c7) edge node[above]{$R(o_1+(o_2+o_3))\eta_{c_1'+(c_2'+c_3')}$} (b7)
-                                (a6) edge node[left]{$1$} (a7)
-                                (b6) edge node[left]{$\kappa$} (b7)
-(b6) edge node[right]{$\tau_6$} (b7)
-			(c6) edge node[right]{$1$} (c7);
-		\end{tikzpicture}
-	\]
-Here we have omitted the natural isomorphisms $\phi_{c_i,c_j} \maps L(c_i) + L(c_j) \to L(c_i + c_j)$ on the inward pointing morphisms which make up the legs of each cospan due to limited space.
-The corresponding maps of decorations amount to the following commutative diagram in $F(R(x_1+(x_2+x_3)))$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$F((\kappa)(1+\kappa)(a_\A))((x_1+x_2)+x_3)$};
-\node (B) at (5,0) {$F((R(a_\mathrm{X}))(\kappa))((x_1+x_2)+x_3)$};
-\node (C) at (5,-1) {$F(R(a_\mathrm{X}))((x_1+x_2)+x_3)$};
-\node (D) at (5,-2) {$x_1+(x_2+x_3)$};
-\node (E) at (0,-1) {$F((\kappa)(1+\kappa))((x_1+x_2)+x_3)$};
-\node (F) at (0,-2) {$F(\kappa)(x_1+(x_2+x_3))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$F((R(a_\X))(\kappa))(\tau_1)$} (B)
-(B) edge node[right]{$F(R(a_\X))(\tau_2)$} (C)
-(C) edge node[right]{$\tau_3$} (D)
-(A) edge node[left]{$F((\kappa)(1+\kappa))(\tau_4)$} (E)
-(E) edge node[left]{$F(\kappa)(\tau_5)$} (F)
-(F) edge node[above]{$\tau_6$} (D);
-\end{tikzpicture}
-\]
-The above square commutes because $$F((\kappa)(1+\kappa)(a_\A))((x_1+x_2)+x_3) = F((R(a_\X))(\kappa)(\kappa+1))((x_1+x_2)+x_3)$$ as the corresponding associator hexagon for the finite colimit preserving functor $R \maps (\X,1_\X,+) \to (\A,1_\A,+)$ commutes.
-Lastly, the braiding square:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$\mathbb{E}(M_1) \otimes \mathbb{E}(M_2)$};
-\node (B) at (3,0) {$\mathbb{E}(M_2) \otimes \mathbb{E}(M_1)$};
-\node (C) at (0,-1) {$\mathbb{E}(M_1 \otimes M_2)$};
-\node (D) at (3,-1) {$\mathbb{E}(M_2 \otimes M_1)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$\beta'$} (B)
-(B) edge node[right]{$\mu_{M_2,M_1}$} (D)
-(A) edge node[left]{$\mu_{M_1,M_2}$} (C)
-(C) edge node[above]{$\mathbb{E}(\beta)$} (D);
-\end{tikzpicture}
-\]
-has underlying map of cospans given by:
-\[
-		\begin{tikzpicture}
-\node (d) at (7,0) {$\mathbb{E}(M_1) \otimes \mathbb{E}(M_2)$};
-\node (d2) at (7,1) {$\mathbb{E}(M_2) \otimes \mathbb{E}(M_1)$};
-\node (d3) at (7,2) {$\mathbb{E}(M_2 \otimes M_1)$};
-\node (d4) at (7,-1) {$\mathbb{E}(M_1 \otimes M_2)$};
-\node (d5) at (7,-2) {$\mathbb{E}(M_2 \otimes M_1)$};
-			\node (a) at (-4,0) {$c_1+c_2$};
-			\node (b) at (0.5,0) {$R(x_1)+R(x_2)$};
-			\node (c) at (5,0) {$c_1'+c_2'$};
-			\node (a2) at (-4,1) {$c_2+c_1$};
-			\node (b2) at (0.5,1) {$R(x_2)+R(x_1)$};
-			\node (c2) at (5,1) {$c_2'+c_1'$};
-                                \node (a3) at (-4,2) {$c_2+c_1$};
-			\node (b3) at (0.5,2) {$R(x_2+x_1)$};
-			\node (c3) at (5,2) {$c_2' + c_1'$};
-                                \node (a5) at (-4,-1) {$c_1+c_2$};
-			\node (b5) at (0.5,-1) {$R(x_1+x_2)$};
-			\node (c5) at (5,-1) {$c_1'+c_2'$};
-                                \node (a6) at (-4,-2) {$c_2+c_1$};
-			\node (b6) at (0.5,-2) {$R(x_2+x_1)$};
-			\node (c6) at (5,-2) {$c_2' + c_1'$};
-			\path[->,font=\scriptsize,>=angle 90]
-(d) edge node[left]{$\beta'$} (d2)
-(d2) edge node[left]{$\mu_{M_2,M_1}$}(d3)
-(d) edge node[left] {$\mu_{M_1,M_2}$}(d4)
-(d4)edge node[left]{$\mathbb{E}(\beta)$}(d5)
-			(a) edge node[above]{$R(i_1) \eta_{c_1} + R(i_2)\eta_{c_2}$} (b)
-			(c) edge node[above]{$R(o_1) \eta_{c_1'} + R(o_2) \eta_{c_2'}$} (b)
-                                (a2) edge node[above]{$R(i_2) \eta_{c_2} + R(i_1) \eta_{c_1}$} (b2)
-			(c2) edge node[above]{$R(o_2) \eta_{c_2'} + R(o_1) \eta_{c_1'}$} (b2)
-                                (a) edge node[left]{$\beta_\A$} (a2)
-                                (b) edge node[left]{$\beta_\A$} (b2)
-(b) edge node[right]{$\tau_1$} (b2)
-			(c) edge node[right]{$\beta_\A$} (c2)
-                                (a3) edge node[above]{$R(i_2+i_1)\eta_{c_2+c_1}$} (b3)
-			(c3) edge node[above]{$R(o_2+o_1)\eta_{c_2'+c_1'}$} (b3)
-                                (a2) edge node[left]{$1$} (a3)
-                                (b2) edge node[left]{$\kappa$} (b3)
-(b2) edge node[right]{$\tau_2$} (b3)
-			(c2) edge node[right]{$1$} (c3)
-                                (a5) edge node[above]{$R(i_1+i_2)\eta_{c_1+c_2}$} (b5)
-			(c5) edge node[above]{$R(o_1+o_2)\eta_{c_1'+c_2'}$} (b5)
-                                (a) edge node[left]{$1$} (a5)
-                                (b) edge node[left]{$\kappa$} (b5)
-(b) edge node[right]{$\tau_3$} (b5)
-			(c) edge node[right]{$1$} (c5)
-                                (a6) edge node[above]{$R(i_2+i_1)\eta_{c_2+c_1}$} (b6)
-			(c6) edge node[above]{$R(o_2+o_1)\eta_{c_2'+c_1'}$} (b6)
-                                (a5) edge node[left]{$\beta_\A$} (a6)
-                                (b5) edge node[left]{$R(\beta_\X)$} (b6)
- (b5) edge node[right]{$\tau_4$} (b6)
-			(c5) edge node[right]{$\beta_\A$} (c6);
-		\end{tikzpicture}
-	\]
-Again, we have omitted the natural isomorphisms $\phi_{c_i,c_j}$ on the inward pointing morphisms on each cospan leg due to space restrictions.
-The corresponding maps of decorations amounting to the following commutative diagram in $F(R(x_2+x_1))$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (-.5,0) {$F((\kappa)(\beta_\A))(x_1+x_2)$};
-\node (C) at (4,0) {$F(\kappa)(x_2+x_1)$};
-\node (D) at (-.5,-1) {$F(R(\beta_\X))(x_1+x_2)$};
-\node (E) at (4,-1) {$x_2+x_1$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$F(\kappa)(\tau_1)$} (C)
-(A) edge node[left]{$F(R(\beta_\X))(\tau_3)$} (D)
-(D) edge node[above]{$\tau_4$} (E)
-(C) edge node[right]{$\tau_2$} (E);
-\end{tikzpicture}
-\]
-The above square commutes because $$F((\kappa)(\beta_\A))(x_1+x_2) = F((R(\beta_\X))(\kappa))(x_1+x_2)$$ as the corresponding braiding square for the finite colimit preserving functor $R \maps (\X,1_\X,+) \to (\A,1_\A,+)$ commutes.
-Thus the double functor $\mathbb{E} \maps _L\lCsp(\X) \to F\lCsp$ is symmetric monoidal.
-\end{comment}
-
 \end{proof}

### 2020-11-19 cospans.tex
wrapped up 3.2, small invisible question to Kenny

@@
 Since both double categories are symmetric monoidal under the running assumptions (\cref{DC,thm:SC}), we will now show that this double isomorphism is a symmetric monoidal one, namely $\lE=(\lE_0,\lE_1)$ is a symmetric strong monoidal double functor as per \cref{defn:monoidal_double_functor}.
-Indeed, $\lE_0=\mathrm{id}_\A$ is a symmetric monoidal functor trivially.
+Indeed, $\lE_0=\mathrm{id}_\A$ is a braided monoidal functor trivially.
 For $\lE_1$, given two structured cospans $M=(a,\bot_a)\to(m,x)\leftarrow(b,\bot_b)$ and $M'=(a',\bot_{a'})\to(m',x')\leftarrow(b',\bot_{b'})$ in $_L\lCsp(\inta F)$, we compute the appropriate decorated cospans
@@
 \end{proof}
+It can be verified that with the above structure, $\lE_1$ is also a braided monoidal functor, and the rest of the axioms of \cref{defn:monoidal_double_functor} hold.
 
 %!!!Kenny: Is this biequivalnce symmetric monoidal? Mike says yes, but it follows from a result that he has yet to officially publish. It's a result of a paper he's currently working on with someone.
+%!!!Christina: Kenny, is the above comment still relevant? If not, feel free to erase!
 

### 2020-11-19 cospans.tex
erased earlier part of proof

@@
 
-\begin{comment}
-We can also define the part of the double equivalence $\mathbb{G} \maps F\lCsp \to {_L \mathbb{C} \textnormal{sp}(\X)}$ which goes in the other direction: again, the object component of this double functor will be $\mathbb{G}_0 = \id_{\A}$.
-
-Given a horizontal 1-cell $M$ of $F\lCsp$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$c_1$};
-\node (B) at (1,0) {$c$};
-\node (C) at (2,0) {$c_2$};
-\node (D) at (1,-0.5) {$x \in F(c)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$I$} (B)
-(C) edge node[above]{$O$} (B);
-\end{tikzpicture}
-\]
-the image $\mathbb{G}(M)$ is the horizontal 1-cell in $_L \lCsp(\X)$ given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$L(c_1)$};
-\node (B) at (1,0) {$x$};
-\node (C) at (2,0) {$L(c_2)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$!_{c} L(I)$} (B)
-(C) edge node[above]{$!_{c} L(O)$} (B);
-\end{tikzpicture}
-\]
-where $!_{c} \maps L(c) \to x$ is the unique morphism from the trival decoration on $c$ given by $$!_{c} \mapseqq 1 \xrightarrow{\phi} F(0) \xrightarrow{F(!)} F(c)$$ to $x \in F(c)$.
-In other words, the trivial decoraction $!_{c}$ is initial in $F(c)$.
-Similarly, given a 2-morphism $(f,h,g,\tau) \maps M \to M'$ of $F\lCsp$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (D) at (1,0.5) {$x \in F(c)$};
-\node (D') at (1,-1.5) {$x' \in F(c')$};
-\node (A) at (0,0) {$c_1$};
-\node (B) at (1,0) {$c$};
-\node (C) at (2,0) {$c_2$};
-\node (A') at (0,-1) {$c_1'$};
-\node (B') at (1,-1) {$c'$};
-\node (C') at (2,-1) {$c_2'$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$I$} (B)
-(C) edge node[above]{$O$} (B)
-(A') edge node[above]{$I'$} (B')
-(C') edge node[above]{$O'$} (B')
-(A) edge node [left]{$f$} (A')
-(B) edge node [left]{$h$} (B')
-(C) edge node [right]{$g$} (C');
-\end{tikzpicture}
-\]
-$$\tau \maps F(h)(x) \to x'$$
-the image $\mathbb{G}(f,h,g,\tau)$ in $_L \lCsp(\X)$ is given by the 2-morphism:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$L(c_1)$};
-\node (B) at (1.5,0) {$x$};
-\node (C) at (3,0) {$L(c_2)$};
-\node (A') at (0,-1) {$L(c_1')$};
-\node (B') at (1.5,-1) {$x'$};
-\node (C') at (3,-1) {$L(c_2')$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$!_{c} L(I)$} (B)
-(C) edge node[above]{$!_{c} L(O)$} (B)
-(A') edge node[above]{$!_{c'} L(I')$} (B')
-(C') edge node[above]{$!_{c'} L(O')$} (B')
-(A) edge node [left]{$L(f)$} (A')
-(B) edge node [left]{$\alpha$} (B')
-(C) edge node [right]{$L(g)$} (C');
-\end{tikzpicture}
-\]
-where $\alpha \maps x \to x'$ is the morphism in the Grothendieck construction of $F$ given by $\alpha = (h \maps c \to c', \tau \maps F(h)(x) \to x')$.
-
-Next, we exhibit natural isomorphisms $\eta \maps \id_{ _L \lCsp(\X)} \cong \mathbb{G} \mathbb{E}$ and $\epsilon \maps \mathbb{E} \mathbb{G} \cong \id_{F\lCsp}$.
-Specifically, these are double natural isomorphisms given by double transformations \cite{Shul2} $\eta$ and $\epsilon$ whose object and arrow components are natural isomorphisms.
-
-First we compute the composites $\mathbb{G} \mathbb{E}$ and $\mathbb{E} \mathbb{G}$.
-On the object categories, both composites are $\id_\A$ and we have natural isomorphisms $\eta \maps \id_{\A} \cong \mathbb{G}_0 \mathbb{E}_0$ and $\epsilon \maps \mathbb{E}_0 \mathbb{G}_0 \cong \id_{\A}$.
-
-Given a horizontal 1-cell $M$ in $_L \mathbb{C} \textnormal{sp}(\X)$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$L(c_1)$};
-\node (B) at (1,0) {$x$};
-\node (C) at (2,0) {$L(c_2)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i$} (B)
-(C) edge node[above]{$o$} (B);
-\end{tikzpicture}
-\]
-the horizontal 1-cell $\mathbb{E}(M)$ is given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$c_1$};
-\node (B) at (1,0) {$R(x)$};
-\node (C) at (2,0) {$c_2$};
-\node (D) at (1,-0.5) {$x \in F(R(x))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$R(i) \eta_{c_1}$} (B)
-(C) edge node[above]{$R(o) \eta_{c_2}$} (B);
-\end{tikzpicture}
-\]
-and then the horizontal 1-cell $\mathbb{G} \mathbb{E}(M)$ is given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$L(c_1)$};
-\node (B) at (1.5,0) {$x$};
-\node (C) at (3,0) {$L(c_2)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$!_{R(x)}L(R(i)\eta_{c_1})$} (B)
-(C) edge node[above]{$!_{R(x)}L(R(o)\eta_{c_2})$} (B);
-\end{tikzpicture}
-\]
-Then we can find a 2-isomorphism $\eta_M \maps M \xrightarrow{\sim} \mathbb{G}\mathbb{E}(M) $ in $_L \mathbb{C} \textnormal{sp}(\X)$ given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$L(c_1)$};
-\node (B) at (1.5,0) {$x$};
-\node (C) at (3,0) {$L(c_2)$};
-\node (A') at (0,-1) {$L(c_1)$};
-\node (B') at (1.5,-1) {$x$};
-\node (C') at (3,-1) {$L(c_2)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i$} (B)
-(C) edge node[above]{$o$} (B)
-(A') edge node[above]{$!_{R(x)}L(R(i)\eta_{c_1})$} (B')
-(C') edge node[above]{$!_{R(x)}L(R(o)\eta_{c_2})$} (B')
-(A) edge node [left]{$1$} (A')
-(B) edge node [left]{$1$} (B')
-(C) edge node [right]{$1$} (C');
-\end{tikzpicture}
-\]
-where
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (-0.5,0) {$L(c_1)$};
-\node (B) at (1,0) {$L(R(L(c_1)))$};
-\node (C) at (2.5,0) {$L(R(x))$};
-\node (D) at (3.5,0) {$x$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$L(\eta_{c_1})$} (B)
-(B) edge node[above]{$L(R(i))$} (C)
-(C) edge node[above]{$!_{R(x)}$} (D)
-(A) edge[bend right] node [above]{$i$} (D);
-\end{tikzpicture}
-\]
-commutes.
-
-On the other hand, given a horizontal 1-cell $N$ in $F\lCsp$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$c_1$};
-\node (B) at (1,0) {$c$};
-\node (C) at (2,0) {$c_2$};
-\node (D) at (1,-0.5) {$x \in F(c)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$I$} (B)
-(C) edge node[above]{$O$} (B);
-\end{tikzpicture}
-\]
-the horizontal 1-cell $\mathbb{G}(N)$ is given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$L(c_1)$};
-\node (B) at (1,0) {$x$};
-\node (C) at (2,0) {$L(c_2)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$!_c L(I)$} (B)
-(C) edge node[above]{$!_c L(O)$} (B);
-\end{tikzpicture}
-\]
-and then the horizontal 1-cell $\mathbb{E} \mathbb{G}(N)$ is given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$c_1$};
-\node (B) at (1.5,0) {$R(x)$};
-\node (C) at (3,0) {$c_2$};
-\node (D) at (1.5,-0.5) {$x \in F(R(x))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$R(!_c L(I))\eta_{c_1}$} (B)
-(C) edge node[above]{$R(!_c L(O))\eta_{c_2}$} (B);
-\end{tikzpicture}
-\]
-Then we have a 2-isomorphism $\epsilon_N \maps \mathbb{E} \mathbb{G} (N) \xrightarrow{\sim} N$ in $F\lCsp$ given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (D) at (1.5,0.5) {$x \in F(R(x))$};
-\node (D') at (1.5,-1.5) {$x \in F(c)$};
-\node (A) at (0,0) {$c_1$};
-\node (B) at (1.5,0) {$R(x)$};
-\node (C) at (3,0) {$c_2$};
-\node (A') at (0,-1) {$c_1$};
-\node (B') at (1.5,-1) {$c$};
-\node (C') at (3,-1) {$c_2$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$R(!_c L(I))\eta_{c_1}$} (B)
-(C) edge node[above]{$R(!_c L(O))\eta_{c_2}$} (B)
-(A') edge node[above]{$I$} (B')
-(C') edge node[above]{$O$} (B')
-(A) edge node [left]{$1$} (A')
-(B) edge node [left]{$\hat{e}$} (B')
-(C) edge node [right]{$1$} (C');
-\end{tikzpicture}
-\]
-$$\tau \maps F(\hat{e})(x) \to x$$
-where 
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$c_1$};
-\node (B) at (1,0) {$R(L(c_1))$};
-\node (C) at (2.5,0) {$R(L(c))$};
-\node (D) at (3.5,0) {$R(x)$};
-\node (E) at (4.5,0) {$c$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$\eta_{c_1}$} (B)
-(B) edge node[above]{$R(L(I))$} (C)
-(C) edge node[above]{$R(!_c)$} (D)
-(D) edge node[above]{$\hat{e}$} (E)
-(A) edge[bend right] node [above]{$I$} (E);
-\end{tikzpicture}
-\]
-commutes.
-
-\end{comment}
-
 \section{Bicategorical and categorical aspects}

### 2020-11-19 cospans.tex
added global pushout construction

@@
 
-In more detail, if $(\phi,\phi_0)$ is the lax monoidal structure of the pseudofunctor $F$ as recalled in \cref{subsec:bicats}, the induced monoidal structure on the total Grothendieck category $\X=\inta F$ is given by
+In more detail, if $(\phi,\phi_0)$ is the lax monoidal structure of the pseudofunctor $F$ as recalled in \cref{subsec:bicats}, the induced monoidal structure on the total Grothendieck category $\X=\inta F$ (\cref{def:GrothCat}) is given by
 \begin{equation}\label{eq:explicitstructure2}
@@
 The second part formulates the existence of colimits \emph{globally} in the total category $\inta F$.
-Combining this with \cref{lem:MonGroth}, we deduce the following.
+As an example, suppose that $\A$ has pushouts and a Grothendieck opfibration $U\colon\inta F\to\A$ has fibrewise pushouts preserved by its reindexing functors.
+We can construct pushouts in $\inta F$ as follows:
+\begin{equation}\label{eq:globalpushout}
+ \begin{tikzcd}[ampersand replacement=\&,column sep=1in,row sep=.5in]
+\& (a+_bc,w)\ar[dd,phantom, very near start,"\upback"description] \& \\
+(a,x)\ar[ur] \&\& (c,z)\ar[ul] \\
+\& (b,y)\ar[ul,"{\begin{cases}f\maps b\to a &\textrm{in }\A \\k\maps F(f)y\to x &\textrm{in }F(a)\end{cases}}"description]\ar[ur,"{\begin{cases}g\maps b\to c &\textrm{in }\A \\\ell\maps F(g)y\to z &\textrm{in }F(c)\end{cases}}"description] \&
+ \end{tikzcd}
+\end{equation}
+which is the pushout $\sigma_a\colon a\to a+_bc\leftarrow c:\sigma_c$ in $\A$ on the first variable, and $w$ is the pushout in the fibre $F(a+_bc)$
+\begin{displaymath}
+\begin{tikzcd}
+ & w \ar[dd,phantom, very near start,"\upback"description] & \\
+ F(\sigma_a)x\ar[ur] & & F(\sigma_c)z\ar[ul] \\
+ & F(\sigma_a)(Ff(y))\cong F(\sigma_n)(Fg(y))\ar[ul,"F(\sigma_a)k"]\ar[ur,"F(\sigma_c)\ell"'] &
+ \end{tikzcd}
+\end{displaymath}
+In similar ways we can construct the initial object and coproducts in a Grothendieck category.
+In our case of interest, the pseudofunctor $F$ will originally be lax monoidal; combining \cref{lem:MonGroth,lem:fibrewiselimits}, we deduce the following.
+%Christina: I suspect that's why for composition we get isomorphism below - using pushouts in which I cannot use the monoidal structure of the functor - whereas for coproducts and initial object we get equality since they were constructed in a very specific way.
+Related to the subtlety comment below.
 
@@
 \end{proof}
-
+Notice that under \cref{lem:fibrewiselimits}, if the base category $\A$ has an initial object denoted $0_\A$, the above lemma is equivalent to $\X$ having an initial object $0_\X$ above $0_\A$.
 Work in progress \cite{CV} includes a related discussion as well as a result in the opposite direction.
@@
 
-\begin{rmk}\label{rmk:important}
-Notice that under \cref{lem:fibrewiselimits}, if the base category $\A$ has an initial object denoted $0_\A$, the above lemma is equivalent to $\X$ having an initial object $0_\X$ above $0_\A$.
-The way in which these two conditions give one another in this case is as follows.
-The fibrewise initial object $\bot_a$ is precisely the cocartesian lifting of $0_\X$ along the unique map $u_a\maps0_\A\to a$ in the base category
-\begin{displaymath}
-\xymatrix @C=.4in @R=.2in
-{0_\X \ar @{.>}[d]\ar[rr]^-{\mathrm{Cocart}(0_\X,u_a)} && (u_a)_!(0_X)=:\bot_a\ar @{.>}[d] & \textrm{in }\X  \\
-0_\A\ar[rr]^-{\exists!u_a} && a & \textrm{in }\A}
-\end{displaymath}
-Moreover, if the opfibration $U$ comes from the Grothendieck construction on a pseudofunctor $F\maps\A\to\Cat$, the reindexing functors $(u_a)_!$ of the opfibration are precisely $F(u_a)$ therefore $\bot_a=(a,F(u_a)(0_\X))$ in the Grothendieck category notation (\cref{def:GrothCat}).
-
-Finally, if the original pseudofunctor is in fact lax monoidal $(F,\phi,\phi_0)$, the monoidal Grothendieck construction of \cref{lem:MonGroth} in the cocartesian case expresses $\bot_a$ as follows by \cref{eq:explicitstructure1}:
-\begin{equation}\label{eq:initialinfibre}
-\mathbf{1}\xrightarrow{\phi_0}F(0_\A)\xrightarrow{F(u_a)}F(a) 
-\end{equation}
-\end{rmk}
+%Christina: Don't think the following is needed, keep for now just in case.
+%\begin{rmk}\label{rmk:important}
+%The way in which these two conditions give one another in this case is as follows. 
+%The fibrewise initial object $\bot_a$ is precisely the cocartesian lifting of $0_\X$ along the unique map $u_a\maps0_\A\to a$ in the base category
+%\begin{displaymath}
+%\xymatrix @C=.4in @R=.2in
+%{0_\X \ar @{.>}[d]\ar[rr]^-{\mathrm{Cocart}(0_\X,u_a)} && (u_a)_!(0_X)=:\bot_a\ar @{.>}[d] & \textrm{in }\X  \\
+%0_\A\ar[rr]^-{\exists!u_a} && a & \textrm{in }\A}
+%\end{displaymath}
+%Moreover, i
+%If the opfibration $U$ comes from the Grothendieck construction on a pseudofunctor $F\maps\A\to\Cat$,
+%the reindexing functors $(u_a)_!$ of the opfibration are precisely $F(u_a)$ therefore 
+%the fibrewise initial object is $\bot_a=(a,F(u_a)(0_\X))$.
+%In fact, if the original pseudofunctor is lax monoidal $(F,\phi,\phi_0)$, the monoidal Grothendieck construction of \cref{lem:MonGroth} in the cocartesian case expresses $\bot_a$ as follows by \cref{eq:explicitstructure1}:
+%\begin{equation}\label{eq:initialinfibre}
+%\mathbf{1}\xrightarrow{\phi_0}F(0_\A)\xrightarrow{F(u_a)}F(a) 
+%\end{equation}
+%\end{rmk}
 
@@
 describes the construction of the adjunction from the original $F$.
-Explicitly, the left adjoint picks the initial object in the finitely cocomplete fibre $L(a)=(a,\bot_a)$, also expressed as $F(u_a)\circ\phi_0(*)$ according to \cref{eq:initialinfibre} for $(\phi,\phi_0)$ the monoidal structure of $F$.
+Explicitly, the left adjoint picks the initial object in the finitely cocomplete fibre $L(a)=(a,\bot_a)$, also expressed as $F(!_a)\circ\phi_0(*)$ according to \cref{eq:explicitstructure1} for $(\phi,\phi_0)$ the monoidal structure of $F$.
 
@@
 \end{equation}
-whereas first composing $M$ and $N$ in $_L\lCsp(\inta F)$ using pushouts in $\inta F$ (constructed by \cref{lem:fibrewiselimits}) %!!!
-Christina: would you like me to write how global pushouts are constructed from fiberwise ones and incorporate it earlier say at \cref{rmk:important} where we do so for initial objects?
+whereas first composing $M$ and $N$ in $_L\lCsp(\inta F)$ using pushouts in $\inta F$ \cref{eq:globalpushout}
 produces 

### 2020-11-19 cospans.tex
added reference for proof of Thm. 2.3 (in Kenny's thesis).

@@
 % in LaTeX
-% 2020/11/18
+% 2020/11/19
 
@@
 Given two finitely cocomplete categories $\A$ and $\A'$, two symmetric lax monoidal pseudofunctors $F \maps \A \to \Cat$ and $F' \maps \A' \to \Cat$, a finite colimit preserving functor $H \maps \A \to \A'$, a symmetric lax monoidal pseudofunctor $E \maps \Cat \to \Cat$ and a 2-isomorphism $\theta \maps EF \Rightarrow F' H$ as in the following diagram, the triple $(H,E,\theta)$ induces a symmetric monoidal (strong) double functor $\mathbb{H} \maps F\lCsp \to F'\lCsp$ as defined above.
-Given two finitely cocomplete categories $\A$ and $\A'$, two symmetric lax monoidal pseudofunctors $F \maps \A \to \Cat$ and $F' \maps \A' \to \Cat$, a finite colimit preserving functor $H \maps \A \to \A'$, a symmetric lax monoidal pseudofunctor $E \maps \Cat \to \Cat$ and a 2-isomorphism $\theta \maps EF \Rightarrow F' H$ as in the following diagram, the triple $(H,E,\theta)$ induces a symmetric monoidal (strong) double functor $\lH \maps F\lCsp \to F'\lCsp$ as defined above.
+Given two finitely cocomplete categories $\A$ and $\A'$, two symmetric lax monoidal pseudofunctors $F \maps \A \to \Cat$ and $F' \maps \A' \to \Cat$, a finite colimit preserving functor $H \maps \A \to \A'$, a symmetric lax monoidal pseudofunctor $E \maps \Cat \to \Cat$ and a 2-isomorphism $\theta \maps EF \Rightarrow F' H$ as in the following diagram, the triple $(H,E,\theta)$ induces a symmetric monoidal double functor $\lH \maps F\lCsp \to F'\lCsp$ as defined above.
 \[
@@
 
-Details of the constructions and the proof of the above theorem can be found at \cite{CourserThesis}.
+\begin{proof}  See \cite[Theorem 4.2.1]{CourserThesis}. \end{proof}
 

### 2020-11-19 cospans.tex
Added some details before Theorem 2.3

--- 2020-11-19 cospans.tex
@@
-% Structured versus decorated cospans
+% Structured and decorated cospans
 % John Baez, Kenny Courser and Christina Vasilakopoulou
 % in LaTeX
-% 2020/11/18
+% 2020/11/19
+% 2020/11/12 - JB
 
@@
 Unfortunately, many applications of decorated cospans were flawed.
-The problem is that while Fong's decorated cospans are good for decorating the apex $m$ of a cospan with an element of a set $F(m)$, they are unable to decorate it with an object of a category.
+The problem is that while Fong's decorated cospans are good for decorating the apex $m$ with an element of a set $F(m)$, they are unable to decorate it with an object of a category.
 An example would be equipping a finite set $m$ with edges making its elements into the nodes of a graph.
@@
 In this section we build the symmetric monoidal double category $F \lCsp$ mentioned in the introduction, and then study the functoriality of this construction.
-The definition of a lax monoidal pseudofunctor is recalled in \cref{subsec:bicats}, and the basics of double categories are recalled in \cref{sec:doublecats}.
+The definition of a lax monoidal pseudofunctor is recalled in \cref{sec:2cats}, and the basics of double categories are recalled in \cref{sec:doublecats}.
 
@@
 \]
-\begin{equation}\label{eq:tensordecoration}
-x_1+x_2 \mapseqq 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{x_1 \times x_2} F(m_1) \times F(m_2) \xrightarrow{\phi_{m_1,m_2}} F(m_1+m_2)
-\end{equation}}
+$$x_1+x_2 \mapseqq 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{x_1 \times x_2} F(m_1) \times F(m_2) \xrightarrow{\phi_{m_1,m_2}} F(m_1+m_2)$$}
 \item{the tensor product of two 2-morphisms $\alpha$ and $\beta$:
@@
 \end{itemize}
-
-Regarding maps between symmetric monoidal double categories, consider another symmetric lax monoidal pseudofunctor $F' \maps \mathsf{A'} \to \Cat$%, we can obtain another symmetric monoidal double category $F' \lCsp$.
-a morphism from $F\lCsp$ to $F' \lCsp$ will then be a double functor $\mathbb{H} \maps F\lCsp \to F' \lCsp$ whose object component is given by a finite colimit preserving functor $\mathbb{H}_0 = H \maps \A \to \mathsf{A'}$ and whose arrow component is given by a functor $\mathbb{H}_1$ defined on horizontal 1-cells by:
-We define the object component $\lH_0$ to be $H$ and define the arrow component $\lH_1$ on horizontal 1-cells by:
+The induced double functor $\lH \colon F\lCsp \to F'\lCsp$ is defined as follows:
+\begin{itemize}
+\item{the image of an object $a \in F\lCsp_0=\A$ is the object $H(a) \in F'\lCsp_0=\A'$,}
+\item{the image of a vertical 1-morphism $f \colon a \to b$ is the vertical 1-morphism $H(f) \colon H(a) \to H(b)$.
+In other words, the object component $\lH_0$ of the double functor $\lH$ is the functor $H$.}
+\item{Given a horizontal 1-cell $M$ in $F\lCsp$, which is an $F$-decorated cospan, the image will be the $F'$-decorated cospan $\lH(M)$ in $F'\lCsp$
 \[
@@
 \node (A) at (0,0) {$a$};
-\node (B) at (1,0) {$c$};
+\node (B) at (1,0) {$m$};
 \node (C) at (2,0) {$b$};
-\node (D) at (1,-0.5) {$d \in F(c)$};
+\node (D) at (1,-0.5) {$x \in F(m)$};
 \node (E) at (2.75,0) {$\mapsto$};
 \node (A') at (3.5,0) {$H(a)$};
-\node (B') at (4.5,0) {$H(c)$};
+\node (B') at (4.5,0) {$H(m)$};
 \node (C') at (5.5,0) {$H(b)$};
-\node (D') at (4.5,-0.5) {$\theta_c E(d) \phi \in F'(H(c))$};
+\node (D') at (4.5,-0.5) {$\theta_m E(x) \phi \in F'(H(m))$};
+\node (F) at (1,0.5) {$M$};
+\node (G) at (4.5,0.5) {$\lH(M)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-and on 2-morphisms by:
+where given a decoration $x \colon 1 \to F(m)$ on $m$, we obtain a decoration on $H(m)$ via the composite $$1 \xrightarrow{\phi} E(1) \xrightarrow{E(x)} E(F(m)) \xrightarrow{\theta_m} F'(H(m)).$$}
+\item{Given a 2-morphism $\alpha \colon M \to N$ in $F\lCsp$, which is a map of $F$-decorated cospans, the image will be the map of $F'$-decorated cospans $\lH(\alpha)$ in $F'\lCsp$
 \[
@@
 \node (A') at (0,-0.5) {$a'$};
-\node (B) at (1,0.5) {$c$};
+\node (B) at (1,0.5) {$m$};
 \node (C) at (2,0.5) {$b$};
 \node (C') at (2,-0.5) {$b'$};
-\node (D) at (1,-0.5) {$c'$};
-\node (E) at (3,0.5) {$d \in F(c)$};
-\node (F) at (3,-0.5) {$d' \in F(c')$};
-\node (G) at (1,-1) {$\tau \maps F(h)(d) \to d'$};
-\node (A'') at (4.25,0.5) {$H(a)$};
-\node (A''') at (4.25,-0.5) {$H(a')$};
-\node (B'') at (5.25,0.5) {$H(c)$};
-\node (C'') at (6.25,0.5) {$H(b)$};
-\node (C''') at (6.25,-0.5) {$H(b')$};
-\node (D'') at (5.25,-0.5) {$H(c')$};
-\node (E'') at (8,0.5) {$\theta_c E(d) \phi \in F'(H(c))$};
-\node (F'') at (8,-0.5) {$\theta_{c'} E(d') \phi \in F'(H(c'))$};
-\node (G'') at (5.25,-1) {$E(\tau) \maps F'(H(h))(\theta_c E(d)\phi) \to (\theta_{c'}E(d')\phi)$};
-\node (H) at (3.5,0) {$\mapsto$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$$} (B)
-(C) edge node[above]{$$} (B)
+\node (D) at (1,-0.5) {$n$};
+\node (E) at (3,0.5) {$x \in F(m)$};
+\node (F) at (3,-0.5) {$x' \in F(n)$};
+\node (G) at (1,-1) {$\tau \maps F(h)(x) \to x'$};
+\node (A'') at (4.75,0.5) {$H(a)$};
+\node (A''') at (4.75,-0.5) {$H(a')$};
+\node (B'') at (5.75,0.5) {$H(m)$};
+\node (C'') at (6.75,0.5) {$H(b)$};
+\node (C''') at (6.75,-0.5) {$H(b')$};
+\node (D'') at (5.75,-0.5) {$H(n)$};
+\node (E'') at (8.5,0.5) {$\theta_m E(x) \phi \in F'(H(m))$};
+\node (F'') at (8.5,-0.5) {$\theta_n E(x') \phi \in F'(H(n))$};
+\node (G'') at (5.75,-1) {$E(\tau) \maps F'(H(h))(\theta_m E(x)\phi) \to (\theta_n E(x')\phi)$};
+\node (H) at (3.75,0) {$\mapsto$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i$} (B)
+(C) edge node[above]{$o$} (B)
 (A) edge node[left]{$f$} (A')
 (C) edge node[right]{$g$} (C')
-(A') edge node {$$} (D)
-(C') edge node {$$} (D)
+(A') edge node[above] {$i'$} (D)
+(C') edge node[above] {$o'$} (D)
 (B) edge node [left] {$h$} (D)
-(A'') edge node[above]{$$} (B'')
-(C'') edge node[above]{$$} (B'')
+(A'') edge node[above]{$H(i)$} (B'')
+(C'') edge node[above]{$H(o)$} (B'')
 (A'') edge node[left]{$H(f)$} (A''')
 (C'') edge node[right]{$H(g)$} (C''')
-(A''') edge node {$$} (D'')
-(C''') edge node {$$} (D'')
+(A''') edge node[above] {$H(i')$} (D'')
+(C''') edge node[above] {$H(o')$} (D'')
 (B'') edge node [left] {$H(h)$} (D'');
@@
 \]
-where $E \maps \Cat \to \Cat$ is a symmetric lax monoidal pseudofuctor such that the following diagram commutes up to isomorphism $\theta \maps EF \Rightarrow F'H$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$\A$};
-\node (B) at (1,0) {$\Cat$};
-\node (C) at (0,-1) {$\mathsf{A'}$};
-\node (D) at (1,-1) {$\Cat$};
-\node (E) at (0.5,-0.5) {$\Swarrow \theta$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$F$} (B)
-(A) edge node[left]{$H$} (C)
-(B) edge node[right]{$E$} (D)
-(C) edge node[above]{$F'$} (D);
-\end{tikzpicture}
-\]
+where given a decoration morphism $\tau \colon F(h)(x) \to x'$, the decoration morphism $E(\tau)$ is defined as:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (G) at (-3.5,-0.5) {$1$};
+\node (H) at (-2,0) {$F(m)$};
+\node (I) at (-2,-1) {$F(n)$};
+\node (J) at (-2.5,-0.5) {$\Swarrow \tau$};
+\node (K) at (-1,-0.5) {$\mapsto$};
+\node (A) at (-0.25,-0.5) {$1$};
+\node (L) at (0.5,-0.5) {$E(1)$};
+\node (B) at (2,0) {$E(F(m))$};
+\node (D) at (2,-1) {$E(F(n))$};
+\node (C) at (1.5,-0.5) {$\Swarrow E(\tau)$};
+\node (E) at (4,0) {$F^\prime(H(m))$};
+\node (F) at (4,-1) {$F^\prime(H(n))$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node [above] {$\phi$} (L)
+(G) edge node [above] {$x$} (H)
+(G) edge node [below] {$x'$} (I)
+(H) edge node [right] {$F(h)$} (I)
+(B) edge node [above] {$\theta_m$} (E)
+(D) edge node [above] {$\theta_n$} (F)
+(E) edge node [right] {$F'(H(h))$} (F)
+(L) edge node[above]{$E(x)$} (B)
+(L) edge node[below]{$E(x')$} (D)
+(B) edge node[right]{$E(F((h))$} (D);
+\end{tikzpicture}
+\]}
+\end{itemize}
+%Regarding maps between symmetric monoidal double categories, consider another symmetric lax monoidal pseudofunctor $F' \maps \mathsf{A'} \to \Cat$%, we can obtain another symmetric monoidal double category $F' \lCsp$.
+%a morphism from $F\lCsp$ to $F' \lCsp$ will then be a double functor $\mathbb{H} \maps F\lCsp \to F' \lCsp$ whose object component is given by a finite colimit preserving functor $\mathbb{H}_0 = H \maps \A \to \mathsf{A'}$ and whose arrow component is given by a functor $\mathbb{H}_1$ defined on horizontal 1-cells by:
+%We define the object component $\lH_0$ to be $H$ and define the arrow component $\lH_1$ on horizontal 1-cells by:
+%\[
+%\begin{tikzpicture}[scale=1.5]
+%\node (A) at (0,0) {$a$};
+%\node (B) at (1,0) {$c$};
+%\node (C) at (2,0) {$b$};
+%\node (D) at (1,-0.5) {$d \in F(c)$};
+%\node (E) at (2.75,0) {$\mapsto$};
+%\node (A') at (3.5,0) {$H(a)$};
+%\node (B') at (4.5,0) {$H(c)$};
+%\node (C') at (5.5,0) {$H(b)$};
+%\node (D') at (4.5,-0.5) {$\theta_c E(d) \phi \in F'(H(c))$};
+%\path[->,font=\scriptsize,>=angle 90]
+%(A) edge node[above]{$i$} (B)
+%(C) edge node[above]{$o$} (B)
+%(A') edge node[above]{$H(i)$} (B')
+%(C') edge node[above]{$H(o)$} (B');
+%\end{tikzpicture}
+%\]
+%and on 2-morphisms by:
+%\[
+%\begin{tikzpicture}[scale=1.5]
+%\node (A) at (0,0.5) {$a$};
+%\node (A') at (0,-0.5) {$a'$};
+%\node (B) at (1,0.5) {$c$};
+%\node (C) at (2,0.5) {$b$};
+%\node (C') at (2,-0.5) {$b'$};
+%\node (D) at (1,-0.5) {$c'$};
+%\node (E) at (3,0.5) {$d \in F(c)$};
+%\node (F) at (3,-0.5) {$d' \in F(c')$};
+%\node (G) at (1,-1) {$\tau \maps F(h)(d) \to d'$};
+%\node (A'') at (4.25,0.5) {$H(a)$};
+%\node (A''') at (4.25,-0.5) {$H(a')$};
+%\node (B'') at (5.25,0.5) {$H(c)$};
+%\node (C'') at (6.25,0.5) {$H(b)$};
+%\node (C''') at (6.25,-0.5) {$H(b')$};
+%\node (D'') at (5.25,-0.5) {$H(c')$};
+%\node (E'') at (8,0.5) {$\theta_c E(d) \phi \in F'(H(c))$};
+%\node (F'') at (8,-0.5) {$\theta_{c'} E(d') \phi \in F'(H(c'))$};
+%\node (G'') at (5.25,-1) {$E(\tau) \maps F'(H(h))(\theta_c E(d)\phi) \to (\theta_{c'}E(d')\phi)$};
+%\node (H) at (3.5,0) {$\mapsto$};
+%\path[->,font=\scriptsize,>=angle 90]
+%(A) edge node[above]{$$} (B)
+%(C) edge node[above]{$$} (B)
+%(A) edge node[left]{$f$} (A')
+%(C) edge node[right]{$g$} (C')
+%(A') edge node {$$} (D)
+%(C') edge node {$$} (D)
+%(B) edge node [left] {$h$} (D)
+%(A'') edge node[above]{$$} (B'')
+%(C'') edge node[above]{$$} (B'')
+%(A'') edge node[left]{$H(f)$} (A''')
+%(C'') edge node[right]{$H(g)$} (C''')
+%(A''') edge node {$$} (D'')
+%(C''') edge node {$$} (D'')
+%(B'') edge node [left] {$H(h)$} (D'');
+%\end{tikzpicture}
+%\]
+%where $E \maps \Cat \to \Cat$ is a symmetric lax monoidal pseudofuctor such that the following diagram commutes up to isomorphism $\theta \maps EF \Rightarrow F'H$:
+%\[
+%\begin{tikzpicture}[scale=1.5]
+%\node (A) at (0,0) {$\A$};
+%\node (B) at (1,0) {$\Cat$};
+%\node (C) at (0,-1) {$\mathsf{A'}$};
+%\node (D) at (1,-1) {$\Cat$};
+%\node (E) at (0.5,-0.5) {$\Swarrow \theta$};
+%\path[->,font=\scriptsize,>=angle 90]
+%(A) edge node[above]{$F$} (B)
+%(A) edge node[left]{$H$} (C)
+%(B) edge node[right]{$E$} (D)
+%(C) edge node[above]{$F'$} (D);
+%\end{tikzpicture}
+%\]
 
@@
 \begin{thm}
-Given two finitely cocomplete categories $\A$ and $\A'$, two symmetric lax monoidal pseudofunctors $F \maps \A \to \Cat$ and $F' \maps \A' \to \Cat$, a finite colimit preserving functor $H \maps \A \to \A'$, a symmetric lax monoidal pseudofunctor $E \maps \Cat \to \Cat$ and a 2-isomorphism $\theta \maps EF \Rightarrow F' H$ as in the following diagram, the triple $(H,E,\theta)$ induces a symmetric monoidal (strong) double functor $\mathbb{H} \maps F\lCsp \to F'\lCsp$ as defined above.
-Given two finitely cocomplete categories $\A$ and $\A'$, two symmetric lax monoidal pseudofunctors $F \maps \A \to \Cat$ and $F' \maps \A' \to \Cat$, a finite colimit preserving functor $H \maps \A \to \A'$, a symmetric lax monoidal pseudofunctor $E \maps \Cat \to \Cat$ and a 2-isomorphism $\theta \maps EF \Rightarrow F' H$ as in the following diagram, the triple $(H,E,\theta)$ induces a symmetric monoidal (strong) double functor $\lH \maps F\lCsp \to F'\lCsp$ as defined above.
+Given two finitely cocomplete categories $\A$ and $\A'$, two symmetric lax monoidal pseudofunctors $F \maps \A \to \Cat$ and $F' \maps \A' \to \Cat$, a finite colimit preserving functor $H \maps \A \to \A'$, a symmetric lax monoidal pseudofunctor $E \maps \Cat \to \Cat$ and a 2-isomorphism $\theta \maps EF \Rightarrow F' H$ as in the following diagram,
 \[
@@
 \] 
+the triple $(H,E,\theta)$ induces a symmetric monoidal double functor $\lH \maps F\lCsp \to F'\lCsp$ as defined above.
 \end{thm}
-
-Details of the constructions and the proof of the above theorem can be found at \cite{CourserThesis}.
+\begin{proof}  See \cite[Theorem 4.2.1]{CourserThesis}. \end{proof}
 
@@
 One of the main goals of this paper is to provide a monoidal double isomorphism between this double category and that of \emph{decorated cospans}, described in detail in \cref{DecCospansDoubleCat}.
-We first recall the double category of structured cospans.
-
-\begin{thm}\label{thm:SC}
+We first recall the double category structured cospans form.
+
+\begin{thm}\label{SC}
 Given categories $\X$ and $\A$ with finite colimits and $L \maps \A \to \X$ a functor preserving
@@
 \path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i$} (B)
-(C) edge node[above]{$o$} (B);
+(A) edge node[above]{$$} (B)
+(C) edge node[above]{$$} (B);
 \end{tikzpicture}
@@
 \end{itemize}
-Composition is formed by taking pushouts in $\X$ and identity horizontal 1-cells are $L(a)\xrightarrow{\raisebox{-3pt}[0pt][0pt]{$=$}}L(a)\xleftarrow{\raisebox{-3pt}[0pt][0pt]{$=$}}L(a)$. 
-Moreover, the vertical category is cocartesian monoidal $(\A,+,0_A)$ and the tensor of horizontal 1-cells is
-\begin{equation}\label{eq:tensorstuctured}
-\begin{tikzcd}[column sep={.4in,between origins}, row sep=.1in]
-& x &&&& x' &&&& x+x' & \\
-&&&\ot&&&& = &&&& \\
-L(a)\ar[uur,"i"]&& L(b)\ar[uul,"o"'] && L(a')\ar[uur,"i'"] && L(b')\ar[uul,"o'"'] && L(a+a')\ar[uur,"i+i'"] && L(b+b')\ar[uul,"o+o'"'] 
-\end{tikzcd}
-\end{equation}
-using that $L$ preserves coproducts, with monoidal unit $L(0_A)\xrightarrow{\raisebox{-3pt}[0pt][0pt]{$\sim$}}0_X\xleftarrow{\raisebox{-3pt}[0pt][0pt]{$\sim$}}L(0_A)$.
-{\chris Shouldn't the horizontal monoidal unit be precisely the identity on the vertical monoidal unit?}
+The symmetric monoidal structure is formed by using binary coproducts and the initial object.
 \end{thm}
@@
 This was proved in \cite[Theorems~2.3 \& 3.9]{BC2}.
+Composition is formed by taking pushouts in $\X$ and identity horizontal 1-cells are $L(a)\xrightarrow{\raisebox{-3pt}[0pt][0pt]{=}}L(a)\xleftarrow{\raisebox{-3pt}[0pt][0pt]{=}}L(a)$.
 In particular, the double category structure only requires that $\X$ have pushouts, whereas the symmetric monoidal structure also requires that $\X$ has binary coproducts and an initial object (and thus all finite colimits), and that $\A$ has and $L$ preserves finite coproducts \cite[Theorem~3.2.3]{CourserThesis}.
@@
 The following theorem establishes the isomorphism between structured and decorated cospan double categories under certain conditions.
-We denote by $\Rex$ the 2-category of finitely cocomplete categories, finitely cocontinuous functors and natural transformations.
-(In \cite{BC} we took as objects finitely cocomplete categories with chosen finite colimits, just so we could turn these into symmetric monoidal categories without any further choices!!!
-Should we do that here???) {\chris Can you tell if we can get away without doing that?
-Perhaps after you read up to before the proof?}
+We denote by $\Rex$ the 2-category of finitely cocomplete categories, finitely cocontinuous functors and natural transformatoins.
 
 \begin{thm} \label{thm:equiv}
-Suppose $\A$ has finite colimits and $F\maps(\A,+) \to (\Cat,\times)$ is a symmetric lax monoidal pseudofunctor that factors through $\Rex$ as an ordinary pseudofunctor.
-Then the symmetric monoidal double categories $F\lCsp$ of decorated cospans and $_L\lCsp(\inta F)$ of structured cospans are isomorphic, where $L \maps \A \to \inta F$ is a left adjoint of the induced Grothendieck opfibration $U\maps \inta F \to \A$.
+Suppose $\ca{A}$ has finite colimits and $F\maps(\A,+) \to (\Cat,\times)$ is a symmetric lax monoidal pseudofunctor that factors through $\bicat{Rex}$ as an ordinary pseudofunctor.
+Then the symmetric monoidal double categories $F\lCsp$ of decorated cospans and $_L\lCsp(\inta F)$ of structured cospans are equivalent, where $L \maps \A \to \inta F$ is a left adjoint of the induced Grothendieck opfibration $U\maps \inta F \to \A$.
 \end{thm}
@@
 
-In \cite{MV}, the classical Grothendieck construction is generalized to the monoidal setting: given a monoidal category $\A$ there is a bijection between \define{monoidal opindexed categories}, which are lax monoidal pseudofunctors $F\maps\A\to\Cat$, and \define{monoidal opfibrations}, which are opfibrations $U \maps \X \to \A$ where $\X$ is monoidal, $U$ is strict monoidal, and $\otimes_\X$ preserves cocartesian liftings.
-This bijection sends a monoidal opindexed category $F \maps \A \to \Cat$ to its Grothendieck construction $U \maps \inta F \to \A$.
-If the monoidal structure on $\A$ is in fact cocartesian, there is a further correspondence between these structures and ordinary pseudofunctors $F\maps\A\to\bicat{MonCat}$ into the 2-category of monoidal categories, strong monoidal functors and monoidal natural transformations.
-Further, all these correspondences lift to 2-equivalences:
+In \cite{MV}, the classical Grothendieck construction is generalized to the monoidal setting: lax monoidal structures on a pseudofunctor $F\maps\A\to\Cat$ (called \emph{monoidal opindexed categories}) bijectively correspond to monoidal structures on the total category $\inta F$ such that the induced opfibration is a strict monoidal functor and $\otimes_{\inta F}$ preserves cocartesian liftings (called \emph{monoidal fibrations}).
+If the monoidal category $\A$ is in fact cocartesian, there is a further correspondence of the two structures with an ordinary pseudofunctor $F\maps\A\to\bicat{MonCat}$ into the 2-category of monoidal categories, strong monoidal functors and monoidal natural transformations.
 
@@
 The second equivalence was also earlier observed by Shulman \cite{Shulman2008}.
-
-In more detail, if $(\phi,\phi_0)$ is the lax monoidal structure of the pseudofunctor $F$ as recalled in \cref{subsec:bicats}, the induced monoidal structure on the total Grothendieck category $\X=\inta F$ is given by
-\begin{equation}\label{eq:explicitstructure2}
-\Big(a,x\in F(a)\Big)\ot_{\X}\Big(b,y\in F(b)\Big)=\Big(a+b,\phi_{a,b}(x,y)\in F(a+b)\Big), \qquad I_{\X}=\Big(0_A,\phi_0\Big)
-\end{equation}
-Moreover, each fibre category $\X_a=F(a)$ obtains a monoidal structure via
+In more detail, if $(\mu,\mu_0)$ is the lax monoidal structure of the pseudofunctor $F$ as recalled in \cref{sec:2cats}, each fibre category $\X_a=F(a)$ obtains a monoidal structure via
 \begin{equation}\label{eq:explicitstructure1}
-\otimes_a\maps F(a)\times F(a)\xrightarrow{\phi_{a,a}}F(a+a)\xrightarrow{F(\nabla)}F(a),\quad
-I_a\maps\mathbf{1}\xrightarrow{\phi_0}F(0)\xrightarrow{F(!)}F(a)
+\otimes_a\maps F(a)\times F(a)\xrightarrow{\mu_{a,a}}F(a+a)\xrightarrow{F(\nabla)}F(a),\quad
+I_a\maps\mathbf{1}\xrightarrow{\mu_0}F(0)\xrightarrow{F(!)}F(a)
 \end{equation}
@@
 
-These 2-equivalences further restrict to the case when the Grothendieck category $(X,\otimes)$ is specifically cocartesian monoidal itself, with coproducts built up from \cref{eq:explicitstructure2}.
-In that case, opfibrations $(\X,+)\to(\A,+)$ that (strictly) preserve coproducts and initial object
+These correspondences further restrict to the case when the Grothendieck category is specifically cocartesian monoidal itself. In that case, opfibrations
+$(\X,+)\to(\A,+)$ that strictly preserve chosen coproducts and initial object
 %, and such that $+$ preserves cocartesian liftings, Christina: this should ALWAYS be the case, by universal properties!
@@
 
-Finally, we can further restrict to the setting of opfibrations that also preserve pushouts, i.e.\ all finite colimits, which is important for our purposes.
-The following result is in fact more general since it relates the existence of any class of colimits in the total category of an opfibration to their existence in the fibres; for a more detailed exposition, as well as the non-necessary strictness condition, see \cite[Corollary~4.9\&Remark~4.11]{Hermida1999}.
-%Is this obscuring or clarifying?
+Finally, we can further restrict to the setting of opfibrations that also preserve pushouts, i.e.
+all finite colimits, which is important for our purposes.
+The following result is in fact more general since it relates the existence of any class of colimits in the total category of an opfibration to their existence in the fibres; for a more detailed exposition, see \cite[Corollary~4.9]{Hermida1999}.
+%as well as Remark~4.11 therein regarding the non-necessary strictness condition. Is this obscuring or clarifying?
 
@@
 However, we \emph{will} use the formulation of coproducts and initial object in terms of the monoidal structure of $F$, and that is why correspondence \cref{monGroth} is necessary.
-DOES THIS MAKE SENSE TO ALL??
+DOES THIS MAKE SENSE TO ALL?? %still, we ARE going to use the formation of coproducts as above. Otherwise someone might think that the monoidal Groth story was redundant here!
 
@@
 describes the construction of the adjunction from the original $F$.
-Explicitly, the left adjoint picks the initial object in the finitely cocomplete fibre $L(a)=(a,\bot_a)$, also expressed as $F(u_a)\circ\phi_0(*)$ according to \cref{eq:initialinfibre} for $(\phi,\phi_0)$ the monoidal structure of $F$.
-
-As a left adjoint, this induced $L$ preserves all colimits that exist between the finitely cocomplete categories $\A$ and $\inta F$, so we can construct the double category of structured cospans $_L\lCsp(\inta F)$ of \cref{thm:SC}.
+Explicitly, the left adjoint picks the initial object in the finitely cocomplete fibre $L(a)=(a,\bot_a)$, also expressed as $F(u_a)\circ\mu_0(*)$ according to \cref{eq:initialinfibre} for $(\mu,\mu_0)$ the monoidal structure of $F$.
+
+As a left adjoint, this induced $L$ preserves all colimits that exist between the finitely cocomplete categories $\A$ and $\inta F$, so we can construct the double category of structured cospans $_L\lCsp(\inta F)$ of \cref{SC}.
 Its objects and vertical morphisms are those of the category $\A$ (as for $F\lCsp$ earlier), whereas horizontal 1-cells are now cospans of the form $\cspn{L(a)}{v}{L(b)}{}{}$ in the Grothendieck category $\inta F$ (\cref{def:GrothCat}).
@@
 
-Since both double categories are symmetric monoidal under the running assumptions (\cref{DC,thm:SC}), we will now show that this double isomorphism is a symmetric monoidal one, namely $\lE=(\lE_0,\lE_1)$ is a symmetric strong monoidal double functor as per \cref{defn:monoidal_double_functor}.
-Indeed, $\lE_0=\mathrm{id}_\A$ is a braided monoidal functor trivially.
-For $\lE_1$, given two structured cospans $M=(a,\bot_a)\to(m,x)\leftarrow(b,\bot_b)$ and $M'=(a',\bot_{a'})\to(m',x')\leftarrow(b',\bot_{b'})$ in $_L\lCsp(\inta F)$, we compute the appropriate decorated cospans
-\begin{align*}
-\lE(M)\ot\lE(M')&\;\stackrel{\cref{eq:tensordecoration}}{=}\;a+a'\xrightarrow{i+i'}m+m'\xleftarrow{o+o'}b+b' \textrm{ with }\mathbf{1}\xrightarrow{x\times x'}F(m)\times F(m')\xrightarrow{\phi_{m,m'}}F(m+m') \\
-\lE(M\ot M')&\;\stackrel{\cref{eq:tensorstuctured}}{=}\;\lE\Big((a+a',\bot_{a+a'})\to\underbrace{(m+m',\phi_{m,m'}(x,x'))}_{\cref{eq:explicitstructure2}}\leftarrow(b+b',\bot_{b+b'})\Big)%=a+a'\xrightarrow{i+i'}m+m'\xleftarrow{o+o'}b+b' \textrm{ with }\phi_{m,m'}(x,x')
-\end{align*}
-which are essentially the same.
-{\chris Well they look equal to me...thoughts?} Moreover, the monoidal unit for the category of arrows of $F\lCsp$ is $0_\A\xrightarrow{\raisebox{-3pt}[0pt][0pt]{$=$}}0_\A\xleftarrow{\raisebox{-3pt}[0pt][0pt]{$=$}}0_\A$ with the trivial decoration
-$$\mathbf{1}\xrightarrow{\phi_0}F(0_A)\xrightarrow{F(\mathrm{id})}F(0_A)$$
-which is essentially the same as $\lE((0_A,\phi_0)\xrightarrow{\raisebox{-3pt}[0pt][0pt]{$=$}}(0_A,\phi_0)\xleftarrow{\raisebox{-3pt}[0pt][0pt]{$=$}}(0_A,\phi_0))$ again by \cref{eq:explicitstructure2}.
+Since both double categories $_L \lCsp(\X)$ and $F\lCsp$ are symmetric monoidal, 
+{\chris in progress}
+
+as they are if both $\A$ and $\X$ have finite colimits, then this isomorphism of double categories $\mathbb{E} \maps _L \lCsp(\X) \to F\lCsp$ will be symmetric monoidal.
+First, note that we have an isomorphism $\epsilon \maps 1_{F\lCsp} \to \mathbb{E}(1_{_L \lCsp(\X)})$ and natural isomorphisms $\mu_{c_1,c_2} \maps \mathbb{E}(c_1) \otimes \mathbb{E}(c_2) \to \mathbb{E}(c_1 \otimes c_2)$ for every pair of objects $c_1,c_2 \in {_L \mathbb{C} \textnormal{sp}(\X)}$ both of which are given by identities since both double categories $_L \lCsp(\X)$ and $F\lCsp$ have $\A$ as their category of objects and $\mathbb{E}_0=\id_{\A}$.
+The diagrams utilizing these maps that are required to commute do so trivially.
+
+For the arrow component $\mathbb{E}_1$, we have an isomorphism $\delta \maps U_{1_{F\lCsp}} \to \mathbb{E}(U_{1_{_L \lCsp(\X)}})$ where the horizontal 1-cell $U_{1_{F\lCsp}}$ is given by:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$1_\A$};
+\node (B) at (1,0) {$1_\A$};
+\node (C) at (2,0) {$1_\A$};
+\node (D) at (3,0) {$!_{1_{\A}} \in F(1_\A)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$1$} (B)
+(C) edge node[above]{$1$} (B);
+\end{tikzpicture}
+\]
+where $!_{1_{\A}} = \phi \maps 1 \to F(1_\A)$ is the trivial decoration which comes from the structure of the symmetric lax monoidal pseudofunctor $F \maps \A \to \Cat$.
+The horizontal 1-cell $U_{1_{_L \lCsp(\X)}}$ is given by:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$L(1_\A)$};
+\node (B) at (1,0) {$L(1_\A)$};
+\node (C) at (2,0) {$L(1_\A)$};
+%\node (D) at (3,0.5) {$I \in F(1_\mathrm{A})$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$1$} (B)
+(C) edge node[above]{$1$} (B);
+\end{tikzpicture}
+\]
+where here we make use of the fact that the left adjoint $L \maps (\A,+,1_\A) \to (\X,+,1_\X)$ preserves all colimits and thus $L(1_\A) \cong 1_\X$.
+The horizontal 1-cell $\mathbb{E}(U_{1_{_L \mathbb{C} \textnormal{sp}(\X)}})$ is then given by the pair:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$1_\A$};
+\node (B) at (1.25,0) {$R(L(1_\A))$};
+\node (C) at (2.5,0) {$1_\A$};
+\node (D) at (4.5,0) {$!_{R(L(1_\A))} \in F(R(L(1_\A)))$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{${\eta_{1_\A}}$} (B)
+(C) edge node[above]{${\eta_{1_\A}}$} (B);
+\end{tikzpicture}
+\]
+The isomorphism $\delta$ is then given by the 2-morphism:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$1_\A$};
+\node (B) at (1,0) {$1_{\A}$};
+\node (C) at (2,0) {$1_\A$};
+\node (A') at (0,-1) {$1_\A$};
+\node (B') at (1,-1) {$R(L(1_\A))$};
+\node (C') at (2,-1) {$1_\A$};
+\node (D) at (3,0) {$!_{1_\A} \in F(1_\A)$};
+\node (D') at (3.75,-1) {$!_{R(L(1_\A))} \in F(R(L(1_\A)))$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$1$} (B)
+(C) edge node[above]{$1$} (B)
+(A') edge node[above]{${\eta_{1_\A}}$} (B')
+(C') edge node[above]{${\eta_{1_\A}}$} (B')
+(A) edge node [left]{$1$} (A')
+(B) edge node [left]{${\eta_{1_\A}}$} (B')
+(C) edge node [left]{$1$} (C');
+\end{tikzpicture}
+\]
+$$\tau_{{\eta_{1_\A}}} \maps F({\eta_{1_\A}})(!_{1_\A})) \to !_{R(L(1_\A))}$$
+of $F\lCsp$. This is just the natural isomorphism $\mathbb{E}_{1_\A}$ from earlier.
+
+Given two horizontal 1-cells $M$ and $N$ of $_L \lCsp(\X)$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$L(c_1)$};
+\node (B) at (1,0) {$x$};
+\node (C) at (2,0) {$L(c_2)$};
+\node (D) at (3,0) {$L(c_1')$};
+\node (E) at (4,0) {$x'$};
+\node (F) at (5,0) {$L(c_2')$};
+%\node (D) at (3,0.5) {$!_c \in F(c)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i$} (B)
+(C) edge node[above]{$o$} (B)
+(D) edge node[above]{$i'$} (E)
+(F) edge node[above]{$o'$} (E);
+\end{tikzpicture}
+\]
+their images $\mathbb{E}(M)$ and $\mathbb{E}(N)$ are given by:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$c_1$};
+\node (B) at (1,0) {$R(x)$};
+\node (C) at (2,0) {$c_2$};
+\node (D) at (3,0) {$c_1'$};
+\node (E) at (4,0) {$R(x')$};
+\node (F) at (5,0) {$c_2'$};
+\node (G) at (1,-0.5) {$x \in F(R(x))$};
+\node (H) at (4,-0.5) {$x' \in F(R(x'))$};
+%\node (D) at (3,0.5) {$!_c \in F(c)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$R(i) \eta_{c_1}$} (B)
+(C) edge node[above]{$R(o) \eta_{c_2}$} (B)
+(D) edge node[above]{$R(i') \eta_{c_1'}$} (E)
+(F) edge node[above]{$R(o') \eta_{c_2'}$} (E);
+\end{tikzpicture}
+\]
+and so $\mathbb{E}(M) \otimes \mathbb{E}(N)$ is given by:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$c_1+c_1'$};
+\node (B) at (3.25,0) {$R(x)+R(x')$};
+\node (C) at (6.5,0) {$c_2+c_2'$};
+\node (D) at (3.25,-0.5) {$d_{\mathbb{E}(M) \otimes \mathbb{E}(N)} \in F(R(x)+R(x'))$}; 
+%\node (D) at (3,0.5) {$!_c \in F(c)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$R(i) \eta_{c_1} +R(i') \eta_{c_1'}$} (B)
+(C) edge node[above]{$R(o) \eta_{c_2} + R(o) \eta_{c_2'}$} (B);
+\end{tikzpicture}
+\]
+where $$d_{\mathbb{E}(M) \otimes \mathbb{E}(N)} \maps 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{x \times x'} F(R(x)) \times F(R(x')) \xrightarrow{\phi_{R(x),R(x')}} F(R(x)+R(x')).$$ On the other hand, $M \otimes N$ is given by
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$L(c_1+c_1')$};
+\node (B) at (2,0) {$x+x'$};
+\node (C) at (4,0) {$L(c_2+c_2')$};
+%\node (D) at (3,0.5) {$!_c \in F(c)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$(i+i')\phi_{c_1,c_1'}^{-1}$} (B)
+(C) edge node[above]{$(o+o')\phi_{c_2,c_2'}^{-1}$} (B);
+\end{tikzpicture}
+\]
+and $\mathbb{E}(M \otimes N)$ is given by:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$c_1+c_1'$};
+\node (B) at (4,0) {$R(x+x')$};
+\node (C) at (8,0) {$c_2+c_2'$};
+\node (D) at (4,-0.5) {$d_{\mathbb{E}(M \odot N)} \in F(R(x+x')).$};
+%\node (D) at (3,0.5) {$!_c \in F(c)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$R((i+i')\phi_{c_1,c_1'}^{-1}) \eta_{c_1+c_1'}$} (B)
+(C) edge node[above]{$R((o+o')\phi_{c_2,c_2'}^{-1}) \eta_{c_2+c_2'}$} (B);
+\end{tikzpicture}
+\]
+We then have a 2-isomorphism $\mu_{M,N} \maps E(M) \otimes E(N) \xrightarrow{\sim} E(M \otimes N)$ in $F\lCsp$ given by:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (-2.5,0) {$c_1+c_1'$};
+\node (B) at (1,0) {$R(x)+R(x')$};
+\node (C) at (4.5,0) {$c_2+c_2'$};
+\node (A') at (-2.5,-1) {$c_1+c_1'$};
+\node (B') at (1,-1) {$R(x+x')$};
+\node (C') at (4.5,-1) {$c_2+c_2'$};
+\node (D) at (6.55,0) {$d_{\mathbb{E}(M) \otimes \mathbb{E}(N)} \in F(R(x)+R(x'))$};
+\node (D') at (6.55,-1) {$d_{\mathbb{E}(M \otimes N)} \in F(R(x+x'))$};
+\node (E) at (2,-1.5) {$\tau_\mu \maps F(\kappa)(d_{\mathbb{E}(M) \odot \mathbb{E}(N)}) \to d_{\mathbb{E}(M \odot N)}$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$R(i)\eta_{c_1} + R(i')\eta_{c_1'}$} (B)
+(C) edge node[above]{$R(o)\eta_{c_2} + R(o')\eta_{c_2'}$} (B)
+(A') edge node[above]{$R((i+i')\phi_{c_1,c_1'}^{-1}) \eta_{c_1+c_1'}$} (B')
+(C') edge node[above]{$R((o+o')\phi_{c_2,c_2'}^{-1}) \eta_{c_2+c_2'}$} (B')
+(A) edge node [left]{$1$} (A')
+(B) edge node [left]{$\kappa$} (B')
+(C) edge node [right]{$1$} (C');
+\end{tikzpicture}
+\]
+where $\kappa$ is the isomorphism which comes from $R \maps \X \to \A$ preserving finite colimits.
+
+The isomorphisms $\delta$ and $\mu$ satisfy the left and right unitality squares, associativity hexagon and braiding square. 
+%Kenny: I think this might be a good place to cut the monoidal stuff.
+%Christina: Deal! They are right below.
+
+\begin{comment}
+To see this, let $M_1,M_2$ and $M_3$ be horizontal 1-cells in $_L \lCsp(\X)$ given by:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$L(c_1)$};
+\node (B) at (1,0) {$x_1$};
+\node (C) at (2,0) {$L(c_1')$};
+\node (D) at (3,0) {$L(c_2)$};
+\node (E) at (4,0) {$x_2$};
+\node (F) at (5,0) {$L(c_2')$};
+\node (G) at (6,0) {$L(c_3)$};
+\node (H) at (7,0) {$x_3$};
+\node (I) at (8,0) {$L(c_3')$};
+%\node (D) at (3,0.5) {$!_c \in F(c)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i_1$} (B)
+(C) edge node[above]{$o_1$} (B)
+(D) edge node[above]{$i_2$} (E)
+(F) edge node[above]{$o_2$} (E)
+(G) edge node[above]{$i_3$} (H)
+(I) edge node[above]{$o_3$} (H);
+\end{tikzpicture}
+\]
+The left unitality square:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$1_{F\lCsp} \otimes \mathbb{E}(M_1)$};
+\node (B) at (3,0) {$\mathbb{E}(1_{ _L \lCsp(\X)}) \otimes \mathbb{E}(M_1)$};
+\node (C) at (0,-1) {$\mathbb{E}(M_1)$};
+\node (D) at (3,-1) {$\mathbb{E}(1_{ _L \lCsp(\X)} \otimes M_1)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$\delta \otimes 1$} (B)
+(B) edge node[right]{$\mu_{1,M_1}$} (D)
+(A) edge node[left]{$\lambda'$} (C)
+(D) edge node[above]{$\mathbb{E}(\lambda)$} (C);
+\end{tikzpicture}
+\]
+has an underlying diagram of maps of cospans given by:
+\[
+		\begin{tikzpicture}
+			\node (d) at (7.5,0) {$\mathbb{E}(1_{ _L \lCsp(\X)}) \otimes \mathbb{E}(M_1)$};
+			\node (a) at (-6,0) {$1_\A+c_1$};
+			\node (b) at (-0.5,0) {$R(L(1_\A)) + R(x_1)$};
+			\node (c) at (5,0) {$1_\A+c_1'$};
+			\node (d2) at (7.5,1) {$1_{F\lCsp} \otimes \mathbb{E}(M_1)$};
+			\node (a2) at (-6,1) {$1_\A+c_1$};
+			\node (b2) at (-0.5,1) {$1_\A+R(x_1)$};
+			\node (c2) at (5,1) {$1_\A+c_1'$};
+			\node (d3) at (7.5,2) {$\mathbb{E}(M_1)$};
+                                \node (a3) at (-6,2) {$c_1$};
+			\node (b3) at (-0.5,2) {$R(x_1)$};
+			\node (c3) at (5,2) {$c_1'$};
+			\node (d4) at (7.5,-1) {$\mathbb{E}(1_{ _L \lCsp(\X)} \otimes M_1)$};
+                                \node (a5) at (-6,-1) {$1_\A+c_1'$};
+			\node (b5) at (-0.5,-1) {$R(L(1_\A)+x_1)$};
+			\node (c5) at (5,-1) {$1_\A+c_1'$};
+			\node (d5) at (7.5,-2) {$\mathbb{E}(M_1)$};
+                                \node (a6) at (-6,-2) {$c_1$};
+			\node (b6) at (-0.5,-2) {$R(x_1)$};
+			\node (c6) at (5,-2) {$c_1'$};
+			\path[->,font=\scriptsize,>=angle 90]
+			(d2) edge node [left]{$\lambda$} (d3)
+			(d2) edge node [left] {$\delta \otimes 1$} (d)
+			(d) edge node [left] {$\mu_{1,M_1}$} (d4)
+			(d4) edge node [left] {$\mathbb{E}(\lambda)$} (d5)
+			(a) edge node[above]{$\eta_{1_\A}+R(i_1)\eta_{c_1}$} (b)
+			(c) edge node[above]{$\eta_{1_\A}+R(o_1)\eta_{c_1'}$} (b)
+                                (a2) edge node[above]{$1+R(i_1)\eta_{c_1}$} (b2)
+			(c2) edge node[above]{$1+R(o_1)\eta_{c_1'}$} (b2)
+                                (a2) edge node[left]{$1$} (a)
+                                (b2) edge node[left]{$\eta_{1_\A}+1$} (b)
+(b2) edge node[right]{$\tau_2$} (b)
+			(c2) edge node[right]{$1$} (c)
+                                (a3) edge node[above]{$R(i_1)\eta_{c_1}$} (b3)
+			(c3) edge node[above]{$R(o_1)\eta_{c_1'}$} (b3)
+                                (a2) edge node[left]{$\lambda_{\A}$} (a3)
+                                (b2) edge node[left]{$\lambda_{\A}$} (b3)
+(b2) edge node[right]{$\tau_1$} (b3)
+			(c2) edge node[right]{$\lambda_{\A}$} (c3)
+                                (a5) edge node[above]{$(\mu_{L(1_\A),d_1})(\eta_{1_\A}+R(i_1)\eta_{c_1})$} (b5)
+			(c5) edge node[above]{$(\mu_{L(1_\A),d_1})(\eta_{1_\A}+R(o_1)\eta_{c_1'})$} (b5)
+                                (a) edge node[left]{$1$} (a5)
+                                (b) edge node[left]{$\mu_{L(1_\A),x_1}$} (b5)
+(b) edge node[right]{$\tau_3$} (b5)
+			(c) edge node[right]{$1$} (c5)
+                                (a6) edge node[above]{$R(i_1)\eta_{c_1}$} (b6)
+			(c6) edge node[above]{$R(o_1)\eta_{c_1'}$} (b6)
+                                (a5) edge node[left]{$\lambda_{\A}$} (a6)
+                                (b5) edge node[left]{$R(\lambda_{\X})$} (b6)
+ (b5) edge node[right]{$\tau_4$} (b6)
+			(c5) edge node[right]{$\lambda_{\A}$} (c6);
+		\end{tikzpicture}
+	\]
+with the corresponding maps of decorations amounting to the following commutative diagram in $F(R(x_1))$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (-.5,0) {$F(\lambda_{\A})(!_{1_\A}+x_1)$};
+\node (C) at (4,0) {$F(R(\lambda_{\X})(\mu_{L(1_\A),x_1}))(!_{R(L(1_\A))} +x_1$)};
+\node (D) at (-.5,-1) {$x_1$};
+\node (E) at (4,-1) {$F(R(\lambda_\X))(x_{!+1})$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$F(R(\lambda_{\X})(\mu_{L(1_\A),x_1}))(\tau_2)$} (C)
+(A) edge node[left]{$\tau_1$} (D)
+(E) edge node[above]{$\tau_4$} (D)
+(C) edge node[right]{$F(R(\lambda_\X))(\tau_3)$} (E);
+\end{tikzpicture}
+\]
+where $x_{!+1}$ is the decoration $x_1$ on the object $R(L(1_\A)+x_1) \in \A$.
+The above square commutes because $$F(\lambda_\A)(!_{1_\A}+x_1) = F(R(\lambda_\X)(\mu_{L(1_\A),x_1})(\eta_{1_\A}+1))(!_{1_\A}+x_1)$$ as the corresponding left unitality square for the finite colimit preserving functor $R \maps (\X,1_\X,+) \to (\A,1_\A,+)$ commutes.
+The right unitality square is similar.
+The associator hexagon:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$(\mathbb{E}(M_1) \otimes \mathbb{E}(M_2)) \otimes \mathbb{E}(M_3)$};
+\node (B) at (3.5,0) {$\mathbb{E}(M_1 \otimes M_2) \otimes \mathbb{E}(M_3)$};
+\node (C) at (7,0) {$\mathbb{E}((M_1 \otimes M_2) \otimes M_3)$};
+\node (A') at (0,-1) {$\mathbb{E}(M_1) \otimes (\mathbb{E}(M_2) \otimes \mathbb{E}(M_3))$};
+\node (B') at (3.5,-1) {$\mathbb{E}(M_1) \otimes \mathbb{E}(M_2 \otimes M_3)$};
+\node (C') at (7,-1) {$\mathbb{E}(M_1 \otimes (M_2 \otimes M_3))$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$\mu_{M_1,M_2} \otimes 1$} (B)
+(B) edge node[above]{$\mu_{M_1 \otimes M_2,M_3}$} (C)
+(A') edge node[above]{$1 \otimes \mu_{M_2,M_3}$} (B')
+(B') edge node[above]{$\mu_{M_1,M_2 \otimes M_3}$} (C')
+(A) edge node [left]{$a'$} (A')
+(C) edge node [right]{$\mathbb{E}(a)$} (C');
+\end{tikzpicture}
+\]
+has underlying maps of cospans given by:
+\[
+		\begin{tikzpicture}
+\node(d) at (1.5,7) {$(\mathbb{E}(M_1) \otimes \mathbb{E}(M_2)) \otimes \mathbb{E}(M_3)$};
+\node (d2) at (1.5,8) {$\mathbb{E}(M_1 \otimes M_2) \otimes \mathbb{E}(M_3)$};
+\node (d3) at (1.5,9) {$\mathbb{E}((M_1 \otimes M_2) \otimes M_3)$};
+\node (d4) at (1.5,10) {$\mathbb{E}(M_1 \otimes (M_2 \otimes M_3))$};
+\node (d5) at (1.5,6) {$\mathbb{E}(M_1) \otimes (\mathbb{E}(M_2) \otimes \mathbb{E}(M_3))$};
+\node (d6) at (1.5,5) {$\mathbb{E}(M_1) \otimes \mathbb{E}(M_2 \otimes M_3)$};
+\node (d7) at (1.5,4) {$\mathbb{E}(M_1 \otimes (M_2 \otimes M_3))$};
+			\node (a) at (-4.25,0) {$(c_1+c_2)+c_3$};
+			\node (b) at (2.5,0) {$(R(x_1)+R(x_2))+R(x_3)$};
+			\node (c) at (9.25,0) {$(c_1'+c_2')+c_3'$};
+			\node (a2) at (-4.25,1) {$(c_1+c_2)+c_3$};
+			\node (b2) at (2.5,1) {$R(x_1+x_2)+R(x_3)$};
+			\node (c2) at (9.25,1) {$(c_1'+c_2')+c_3'$};
+                                \node (a3) at (-4.25,2) {$(c_1+c_2)+c_3$};
+			\node (b3) at (2.5,2) {$R((x_1+x_2)+x_3)$};
+			\node (c3) at (9.25,2) {$(c_1'+c_2')+c_3'$};
+                                \node (a4) at (-4.25,3) {$c_1+(c_2+c_3)$};
+			\node (b4) at (2.5,3) {$R(x_1+(x_2+x_3))$};
+			\node (c4) at (9.25,3) {$c_1' + (c_2' + c_3')$};
+                                \node (a5) at (-4.25,-1) {$c_1+(c_2+c_3)$};
+			\node (b5) at (2.5,-1) {$R(x_1)+(R(x_2)+R(x_3))$};
+			\node (c5) at (9.25,-1) {$c_1' + (c_2' + c_3')$};
+                                \node (a6) at (-4.25,-2) {$c_1+(c_2+c_3)$};
+			\node (b6) at (2.5,-2) {$R(x_1)+R(x_2+x_3)$};
+			\node (c6) at (9.25,-2) {$c_1' + (c_2' + c_3')$};
+                                \node (a7) at (-4.25,-3) {$c_1+(c_2+c_3)$};
+			\node (b7) at (2.5,-3) {$R(x_1+(x_2+x_3))$};
+			\node (c7) at (9.25,-3) {$c_1' + (c_2' + c_3')$};
+			\path[->,font=\scriptsize,>=angle 90]
+(d) edge node[left] {$\mu_{M_1,M_2} \otimes 1$} (d2)
+(d2) edge node[left] {$\mu_{M_1 \otimes M_2,M_3}$} (d3)
+(d3) edge node[left] {$\mathbb{E}(a)$} (d4)
+(d) edge node[left] {$a'$} (d5)
+(d5) edge node[left] {$1 \otimes \mu_{M_2,M_3}$} (d6)
+(d6) edge node[left] {$\mu_{M_1,M_2 \otimes M_3}$} (d7)
+			(a) edge node[above]{$(R(i_1)\eta_{c_1}+R(i_2)\eta_{c_2})+R(i_3)\eta_{c_3}$} (b)
+			(c) edge node[above]{$(R(o_1)\eta_{c_1'}+R(o_2)\eta_{c_2'})+R(o_3)\eta_{c_3'}$} (b)
+                                (a2) edge node[above]{$R(i_1+i_2)\eta_{c_1+c_2}+R(i_3)\eta_{c_3}$} (b2)
+			(c2) edge node[above]{$R(o_1+o_2)\eta_{c_1'+c_2'}+R(o_3)\eta_{c_3'}$} (b2)
+                                (a) edge node[left]{$1$} (a2)
+                                (b) edge node[left]{$\kappa + 1$} (b2)
+(b) edge node[right]{$\tau_1$} (b2)
+			(c) edge node[right]{$1$} (c2)
+                                (a3) edge node[above]{$R((i_1+i_2)+i_3)\eta_{(c_1+c_2)+c_3}$} (b3)
+			(c3) edge node[above]{$R((o_1+o_2)+o_3)\eta_{(c_1'+c_2')+c_3'}$} (b3)
+                                (a2) edge node[left]{$1$} (a3)
+                                (b2) edge node[left]{$\kappa$} (b3)
+(b2) edge node[right]{$\tau_2$} (b3)
+			(c2) edge node[right]{$1$} (c3)
+                                (a4) edge node[above]{$R(i_1+(i_2+i_3))\eta_{c_1+(c_2+c_3)}$} (b4)
+			(c4) edge node[above]{$R(o_1+(o_2+o_3))\eta_{c_1'+(c_2'+c_3')}$} (b4)
+                                (a3) edge node[left]{$a_\A$} (a4)
+                                (b3) edge node[left]{$R(a_\X)$} (b4)
+(b3) edge node[right]{$\tau_3$} (b4)
+			(c3) edge node[right]{$a_\A$} (c4)
+                                (a5) edge node[above]{$R(i_1)\eta_{c_1}+(R(i_2)\eta_{c_2}+R(i_3)\eta_{c_3})$} (b5)
+			(c5) edge node[above]{$R(o_1)\eta_{c_1'}+(R(o_2)\eta_{c_2'}+R(o_3)\eta_{c_3'})$} (b5)
+                                (a) edge node[left]{$a_\A$} (a5)
+                                (b) edge node[left]{$a_\A$} (b5)
+(b) edge node[right]{$\tau_4$} (b5)
+			(c) edge node[right]{$a_\A$} (c5)
+                                (a6) edge node[above]{$R(i_1)\eta_{c_1}+R(i_2+i_3)\eta_{c_2+c_3}$} (b6)
+			(c6) edge node[above]{$R(o_1)\eta_{c_1'}+R(o_2+o_3)\eta_{c_2'+c_3'}$} (b6)
+                                (a5) edge node[left]{$1$} (a6)
+                                (b5) edge node[left]{$1+\kappa$} (b6)
+ (b5) edge node[right]{$\tau_5$} (b6)
+			(c5) edge node[right]{$1$} (c6)
+                                (a7) edge node[above]{$R(i_1+(i_2+i_3))\eta_{c_1+(c_2+c_3)}$} (b7)
+			(c7) edge node[above]{$R(o_1+(o_2+o_3))\eta_{c_1'+(c_2'+c_3')}$} (b7)
+                                (a6) edge node[left]{$1$} (a7)
+                                (b6) edge node[left]{$\kappa$} (b7)
+(b6) edge node[right]{$\tau_6$} (b7)
+			(c6) edge node[right]{$1$} (c7);
+		\end{tikzpicture}
+	\]
+Here we have omitted the natural isomorphisms $\phi_{c_i,c_j} \maps L(c_i) + L(c_j) \to L(c_i + c_j)$ on the inward pointing morphisms which make up the legs of each cospan due to limited space.
+The corresponding maps of decorations amount to the following commutative diagram in $F(R(x_1+(x_2+x_3)))$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$F((\kappa)(1+\kappa)(a_\A))((x_1+x_2)+x_3)$};
+\node (B) at (5,0) {$F((R(a_\mathrm{X}))(\kappa))((x_1+x_2)+x_3)$};
+\node (C) at (5,-1) {$F(R(a_\mathrm{X}))((x_1+x_2)+x_3)$};
+\node (D) at (5,-2) {$x_1+(x_2+x_3)$};
+\node (E) at (0,-1) {$F((\kappa)(1+\kappa))((x_1+x_2)+x_3)$};
+\node (F) at (0,-2) {$F(\kappa)(x_1+(x_2+x_3))$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$F((R(a_\X))(\kappa))(\tau_1)$} (B)
+(B) edge node[right]{$F(R(a_\X))(\tau_2)$} (C)
+(C) edge node[right]{$\tau_3$} (D)
+(A) edge node[left]{$F((\kappa)(1+\kappa))(\tau_4)$} (E)
+(E) edge node[left]{$F(\kappa)(\tau_5)$} (F)
+(F) edge node[above]{$\tau_6$} (D);
+\end{tikzpicture}
+\]
+The above square commutes because $$F((\kappa)(1+\kappa)(a_\A))((x_1+x_2)+x_3) = F((R(a_\X))(\kappa)(\kappa+1))((x_1+x_2)+x_3)$$ as the corresponding associator hexagon for the finite colimit preserving functor $R \maps (\X,1_\X,+) \to (\A,1_\A,+)$ commutes.
+Lastly, the braiding square:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$\mathbb{E}(M_1) \otimes \mathbb{E}(M_2)$};
+\node (B) at (3,0) {$\mathbb{E}(M_2) \otimes \mathbb{E}(M_1)$};
+\node (C) at (0,-1) {$\mathbb{E}(M_1 \otimes M_2)$};
+\node (D) at (3,-1) {$\mathbb{E}(M_2 \otimes M_1)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$\beta'$} (B)
+(B) edge node[right]{$\mu_{M_2,M_1}$} (D)
+(A) edge node[left]{$\mu_{M_1,M_2}$} (C)
+(C) edge node[above]{$\mathbb{E}(\beta)$} (D);
+\end{tikzpicture}
+\]
+has underlying map of cospans given by:
+\[
+		\begin{tikzpicture}
+\node (d) at (7,0) {$\mathbb{E}(M_1) \otimes \mathbb{E}(M_2)$};
+\node (d2) at (7,1) {$\mathbb{E}(M_2) \otimes \mathbb{E}(M_1)$};
+\node (d3) at (7,2) {$\mathbb{E}(M_2 \otimes M_1)$};
+\node (d4) at (7,-1) {$\mathbb{E}(M_1 \otimes M_2)$};
+\node (d5) at (7,-2) {$\mathbb{E}(M_2 \otimes M_1)$};
+			\node (a) at (-4,0) {$c_1+c_2$};
+			\node (b) at (0.5,0) {$R(x_1)+R(x_2)$};
+			\node (c) at (5,0) {$c_1'+c_2'$};
+			\node (a2) at (-4,1) {$c_2+c_1$};
+			\node (b2) at (0.5,1) {$R(x_2)+R(x_1)$};
+			\node (c2) at (5,1) {$c_2'+c_1'$};
+                                \node (a3) at (-4,2) {$c_2+c_1$};
+			\node (b3) at (0.5,2) {$R(x_2+x_1)$};
+			\node (c3) at (5,2) {$c_2' + c_1'$};
+                                \node (a5) at (-4,-1) {$c_1+c_2$};
+			\node (b5) at (0.5,-1) {$R(x_1+x_2)$};
+			\node (c5) at (5,-1) {$c_1'+c_2'$};
+                                \node (a6) at (-4,-2) {$c_2+c_1$};
+			\node (b6) at (0.5,-2) {$R(x_2+x_1)$};
+			\node (c6) at (5,-2) {$c_2' + c_1'$};
+			\path[->,font=\scriptsize,>=angle 90]
+(d) edge node[left]{$\beta'$} (d2)
+(d2) edge node[left]{$\mu_{M_2,M_1}$}(d3)
+(d) edge node[left] {$\mu_{M_1,M_2}$}(d4)
+(d4)edge node[left]{$\mathbb{E}(\beta)$}(d5)
+			(a) edge node[above]{$R(i_1) \eta_{c_1} + R(i_2)\eta_{c_2}$} (b)
+			(c) edge node[above]{$R(o_1) \eta_{c_1'} + R(o_2) \eta_{c_2'}$} (b)
+                                (a2) edge node[above]{$R(i_2) \eta_{c_2} + R(i_1) \eta_{c_1}$} (b2)
+			(c2) edge node[above]{$R(o_2) \eta_{c_2'} + R(o_1) \eta_{c_1'}$} (b2)
+                                (a) edge node[left]{$\beta_\A$} (a2)
+                                (b) edge node[left]{$\beta_\A$} (b2)
+(b) edge node[right]{$\tau_1$} (b2)
+			(c) edge node[right]{$\beta_\A$} (c2)
+                                (a3) edge node[above]{$R(i_2+i_1)\eta_{c_2+c_1}$} (b3)
+			(c3) edge node[above]{$R(o_2+o_1)\eta_{c_2'+c_1'}$} (b3)
+                                (a2) edge node[left]{$1$} (a3)
+                                (b2) edge node[left]{$\kappa$} (b3)
+(b2) edge node[right]{$\tau_2$} (b3)
+			(c2) edge node[right]{$1$} (c3)
+                                (a5) edge node[above]{$R(i_1+i_2)\eta_{c_1+c_2}$} (b5)
+			(c5) edge node[above]{$R(o_1+o_2)\eta_{c_1'+c_2'}$} (b5)
+                                (a) edge node[left]{$1$} (a5)
+                                (b) edge node[left]{$\kappa$} (b5)
+(b) edge node[right]{$\tau_3$} (b5)
+			(c) edge node[right]{$1$} (c5)
+                                (a6) edge node[above]{$R(i_2+i_1)\eta_{c_2+c_1}$} (b6)
+			(c6) edge node[above]{$R(o_2+o_1)\eta_{c_2'+c_1'}$} (b6)
+                                (a5) edge node[left]{$\beta_\A$} (a6)
+                                (b5) edge node[left]{$R(\beta_\X)$} (b6)
+ (b5) edge node[right]{$\tau_4$} (b6)
+			(c5) edge node[right]{$\beta_\A$} (c6);
+		\end{tikzpicture}
+	\]
+Again, we have omitted the natural isomorphisms $\phi_{c_i,c_j}$ on the inward pointing morphisms on each cospan leg due to space restrictions.
+The corresponding maps of decorations amounting to the following commutative diagram in $F(R(x_2+x_1))$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (-.5,0) {$F((\kappa)(\beta_\A))(x_1+x_2)$};
+\node (C) at (4,0) {$F(\kappa)(x_2+x_1)$};
+\node (D) at (-.5,-1) {$F(R(\beta_\X))(x_1+x_2)$};
+\node (E) at (4,-1) {$x_2+x_1$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$F(\kappa)(\tau_1)$} (C)
+(A) edge node[left]{$F(R(\beta_\X))(\tau_3)$} (D)
+(D) edge node[above]{$\tau_4$} (E)
+(C) edge node[right]{$\tau_2$} (E);
+\end{tikzpicture}
+\]
+The above square commutes because $$F((\kappa)(\beta_\A))(x_1+x_2) = F((R(\beta_\X))(\kappa))(x_1+x_2)$$ as the corresponding braiding square for the finite colimit preserving functor $R \maps (\X,1_\X,+) \to (\A,1_\A,+)$ commutes.
+Thus the double functor $\mathbb{E} \maps _L\lCsp(\X) \to F\lCsp$ is symmetric monoidal.
+\end{comment}
+
 \end{proof}
-It can be verified that with the above structure, $\lE_1$ is also a braided monoidal functor, and the rest of the axioms of \cref{defn:monoidal_double_functor} hold.
 
 %!!!Kenny: Is this biequivalnce symmetric monoidal? Mike says yes, but it follows from a result that he has yet to officially publish. It's a result of a paper he's currently working on with someone.
-%!!!Christina: Kenny, is the above comment still relevant? If not, feel free to erase!
+
+\begin{comment}
+We can also define the part of the double equivalence $\mathbb{G} \maps F\lCsp \to {_L \mathbb{C} \textnormal{sp}(\X)}$ which goes in the other direction: again, the object component of this double functor will be $\mathbb{G}_0 = \id_{\A}$.
+
+Given a horizontal 1-cell $M$ of $F\lCsp$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$c_1$};
+\node (B) at (1,0) {$c$};
+\node (C) at (2,0) {$c_2$};
+\node (D) at (1,-0.5) {$x \in F(c)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$I$} (B)
+(C) edge node[above]{$O$} (B);
+\end{tikzpicture}
+\]
+the image $\mathbb{G}(M)$ is the horizontal 1-cell in $_L \lCsp(\X)$ given by:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$L(c_1)$};
+\node (B) at (1,0) {$x$};
+\node (C) at (2,0) {$L(c_2)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$!_{c} L(I)$} (B)
+(C) edge node[above]{$!_{c} L(O)$} (B);
+\end{tikzpicture}
+\]
+where $!_{c} \maps L(c) \to x$ is the unique morphism from the trival decoration on $c$ given by $$!_{c} \mapseqq 1 \xrightarrow{\phi} F(0) \xrightarrow{F(!)} F(c)$$ to $x \in F(c)$.
+In other words, the trivial decoraction $!_{c}$ is initial in $F(c)$.
+Similarly, given a 2-morphism $(f,h,g,\tau) \maps M \to M'$ of $F\lCsp$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (D) at (1,0.5) {$x \in F(c)$};
+\node (D') at (1,-1.5) {$x' \in F(c')$};
+\node (A) at (0,0) {$c_1$};
+\node (B) at (1,0) {$c$};
+\node (C) at (2,0) {$c_2$};
+\node (A') at (0,-1) {$c_1'$};
+\node (B') at (1,-1) {$c'$};
+\node (C') at (2,-1) {$c_2'$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$I$} (B)
+(C) edge node[above]{$O$} (B)
+(A') edge node[above]{$I'$} (B')
+(C') edge node[above]{$O'$} (B')
+(A) edge node [left]{$f$} (A')
+(B) edge node [left]{$h$} (B')
+(C) edge node [right]{$g$} (C');
+\end{tikzpicture}
+\]
+$$\tau \maps F(h)(x) \to x'$$
+the image $\mathbb{G}(f,h,g,\tau)$ in $_L \lCsp(\X)$ is given by the 2-morphism:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$L(c_1)$};
+\node (B) at (1.5,0) {$x$};
+\node (C) at (3,0) {$L(c_2)$};
+\node (A') at (0,-1) {$L(c_1')$};
+\node (B') at (1.5,-1) {$x'$};
+\node (C') at (3,-1) {$L(c_2')$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$!_{c} L(I)$} (B)
+(C) edge node[above]{$!_{c} L(O)$} (B)
+(A') edge node[above]{$!_{c'} L(I')$} (B')
+(C') edge node[above]{$!_{c'} L(O')$} (B')
+(A) edge node [left]{$L(f)$} (A')
+(B) edge node [left]{$\alpha$} (B')
+(C) edge node [right]{$L(g)$} (C');
+\end{tikzpicture}
+\]
+where $\alpha \maps x \to x'$ is the morphism in the Grothendieck construction of $F$ given by $\alpha = (h \maps c \to c', \tau \maps F(h)(x) \to x')$.
+
+Next, we exhibit natural isomorphisms $\eta \maps \id_{ _L \lCsp(\X)} \cong \mathbb{G} \mathbb{E}$ and $\epsilon \maps \mathbb{E} \mathbb{G} \cong \id_{F\lCsp}$.
+Specifically, these are double natural isomorphisms given by double transformations \cite{Shul2} $\eta$ and $\epsilon$ whose object and arrow components are natural isomorphisms.
+
+First we compute the composites $\mathbb{G} \mathbb{E}$ and $\mathbb{E} \mathbb{G}$.
+On the object categories, both composites are $\id_\A$ and we have natural isomorphisms $\eta \maps \id_{\A} \cong \mathbb{G}_0 \mathbb{E}_0$ and $\epsilon \maps \mathbb{E}_0 \mathbb{G}_0 \cong \id_{\A}$.
+
+Given a horizontal 1-cell $M$ in $_L \mathbb{C} \textnormal{sp}(\X)$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$L(c_1)$};
+\node (B) at (1,0) {$x$};
+\node (C) at (2,0) {$L(c_2)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i$} (B)
+(C) edge node[above]{$o$} (B);
+\end{tikzpicture}
+\]
+the horizontal 1-cell $\mathbb{E}(M)$ is given by:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$c_1$};
+\node (B) at (1,0) {$R(x)$};
+\node (C) at (2,0) {$c_2$};
+\node (D) at (1,-0.5) {$x \in F(R(x))$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$R(i) \eta_{c_1}$} (B)
+(C) edge node[above]{$R(o) \eta_{c_2}$} (B);
+\end{tikzpicture}
+\]
+and then the horizontal 1-cell $\mathbb{G} \mathbb{E}(M)$ is given by:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$L(c_1)$};
+\node (B) at (1.5,0) {$x$};
+\node (C) at (3,0) {$L(c_2)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$!_{R(x)}L(R(i)\eta_{c_1})$} (B)
+(C) edge node[above]{$!_{R(x)}L(R(o)\eta_{c_2})$} (B);
+\end{tikzpicture}
+\]
+Then we can find a 2-isomorphism $\eta_M \maps M \xrightarrow{\sim} \mathbb{G}\mathbb{E}(M) $ in $_L \mathbb{C} \textnormal{sp}(\X)$ given by:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$L(c_1)$};
+\node (B) at (1.5,0) {$x$};
+\node (C) at (3,0) {$L(c_2)$};
+\node (A') at (0,-1) {$L(c_1)$};
+\node (B') at (1.5,-1) {$x$};
+\node (C') at (3,-1) {$L(c_2)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i$} (B)
+(C) edge node[above]{$o$} (B)
+(A') edge node[above]{$!_{R(x)}L(R(i)\eta_{c_1})$} (B')
+(C') edge node[above]{$!_{R(x)}L(R(o)\eta_{c_2})$} (B')
+(A) edge node [left]{$1$} (A')
+(B) edge node [left]{$1$} (B')
+(C) edge node [right]{$1$} (C');
+\end{tikzpicture}
+\]
+where
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (-0.5,0) {$L(c_1)$};
+\node (B) at (1,0) {$L(R(L(c_1)))$};
+\node (C) at (2.5,0) {$L(R(x))$};
+\node (D) at (3.5,0) {$x$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$L(\eta_{c_1})$} (B)
+(B) edge node[above]{$L(R(i))$} (C)
+(C) edge node[above]{$!_{R(x)}$} (D)
+(A) edge[bend right] node [above]{$i$} (D);
+\end{tikzpicture}
+\]
+commutes.
+
+On the other hand, given a horizontal 1-cell $N$ in $F\lCsp$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$c_1$};
+\node (B) at (1,0) {$c$};
+\node (C) at (2,0) {$c_2$};
+\node (D) at (1,-0.5) {$x \in F(c)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$I$} (B)
+(C) edge node[above]{$O$} (B);
+\end{tikzpicture}
+\]
+the horizontal 1-cell $\mathbb{G}(N)$ is given by:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$L(c_1)$};
+\node (B) at (1,0) {$x$};
+\node (C) at (2,0) {$L(c_2)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$!_c L(I)$} (B)
+(C) edge node[above]{$!_c L(O)$} (B);
+\end{tikzpicture}
+\]
+and then the horizontal 1-cell $\mathbb{E} \mathbb{G}(N)$ is given by:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$c_1$};
+\node (B) at (1.5,0) {$R(x)$};
+\node (C) at (3,0) {$c_2$};
+\node (D) at (1.5,-0.5) {$x \in F(R(x))$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$R(!_c L(I))\eta_{c_1}$} (B)
+(C) edge node[above]{$R(!_c L(O))\eta_{c_2}$} (B);
+\end{tikzpicture}
+\]
+Then we have a 2-isomorphism $\epsilon_N \maps \mathbb{E} \mathbb{G} (N) \xrightarrow{\sim} N$ in $F\lCsp$ given by:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (D) at (1.5,0.5) {$x \in F(R(x))$};
+\node (D') at (1.5,-1.5) {$x \in F(c)$};
+\node (A) at (0,0) {$c_1$};
+\node (B) at (1.5,0) {$R(x)$};
+\node (C) at (3,0) {$c_2$};
+\node (A') at (0,-1) {$c_1$};
+\node (B') at (1.5,-1) {$c$};
+\node (C') at (3,-1) {$c_2$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$R(!_c L(I))\eta_{c_1}$} (B)
+(C) edge node[above]{$R(!_c L(O))\eta_{c_2}$} (B)
+(A') edge node[above]{$I$} (B')
+(C') edge node[above]{$O$} (B')
+(A) edge node [left]{$1$} (A')
+(B) edge node [left]{$\hat{e}$} (B')
+(C) edge node [right]{$1$} (C');
+\end{tikzpicture}
+\]
+$$\tau \maps F(\hat{e})(x) \to x$$
+where 
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$c_1$};
+\node (B) at (1,0) {$R(L(c_1))$};
+\node (C) at (2.5,0) {$R(L(c))$};
+\node (D) at (3.5,0) {$R(x)$};
+\node (E) at (4.5,0) {$c$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$\eta_{c_1}$} (B)
+(B) edge node[above]{$R(L(I))$} (C)
+(C) edge node[above]{$R(!_c)$} (D)
+(D) edge node[above]{$\hat{e}$} (E)
+(A) edge[bend right] node [above]{$I$} (E);
+\end{tikzpicture}
+\]
+commutes.
+
+\end{comment}
 
@@
 Let $\A$ be a category with finite colimits and $F \maps (\A, +) \to (\Cat,\times)$ a symmetric lax monoidal pseudofunctor. Then there exists a symmetric monoidal bicategory $F \mathbf{Csp}$ in which:
-\begin{itemize}
+\begin{enumerate}
 \item objects are those of $\A$,
@@
 together with a morphism $\tau \maps F(h)(d) \to d'$ in $F(c')$.
-\end{itemize}
+\end{enumerate}
 \end{thm}
@@
 
-\begin{cor} \label{cor:symmoncat}
+\begin{cor}
 Let $\A$ be a category with finite colimits and $F \maps (\A, +) \to (\Cat, \times)$ a symmetric lax monoidal pseudofunctor.  Then there exists a symmetric monoidal category $F\Csp$ in which:
@@
 
-{\chris In the proof above, we probably need isomorphism. Does it follow?}
+IN THE PROOF ABOVE, WE ACTUALLY POTENTIALLY NEED SYMMETRY. DOES IT FOLLOW?
 
@@
 
-\section{Applications}\label{applications}
-
-In this section we present several examples.
-We treat `open graphs' in some detail since a graph is the simplest sort of network and this example was not correctly handled by Fong's original theory of decorated cospans.
-We then turn to circuits, open Petri nets and open Petri nets with rates, going through these more rapidly since they are all very similar.
-All these examples can be handled using either decorated or structured cospans: the two approaches give equivalent symmetric monoidal double categories by \cref{thm:equiv}, but it should be apparent that structured cospans are simpler.
-We conclude with the example of open dynamical systems, which can only be handled using decorated cospans.
-
-\subsection{Open graphs}
+\section{Applications}\label{Applications}
+
+In this section we present several examples.  The first was mentioned in the Introduction.
+
+\subsection{Graphs}
 \label{subsec:graphs}
 
-In earlier work \cite[Sec.\ 5]{BC} we explained the flaws in Fong's original treatment \cite{Fong} of open graphs using decorated cospans.
-We also showed how to fix these flaws using structured cospans.
-Our new approach to decorated cospans provides another solution, which however is equivalent.
-
-For us a \define{graph} will be a pair of functions $s,t\maps E \to N$ where $E$ and $N$ are finite sets.
+In earlier work \cite[Sec.\ 5]{BC} we explained the flaws in Fong's original construction of a category of open graphs using decorated cospans.
+We also showed how to fix them using structured cospans.
+Our new approach to decorated cospans provides another, equivalent way to fix these flaws.
+
+For us a \define{graph} will be a pair of functions $s,t\maps E \to N$ where $E$ and $N$ are arbitrary sets.
 We call elements of $E$ \define{edges} and elements of $N$ \define{nodes}.
@@
 We can easily build a double category with `open graphs' as horizontal 1-cells using the machinery of structured cospans.
-Let $L \maps \Fin\Set \to \Graph$ be the functor that assigns to a finite set $N$ the \define{discrete graph} on that set: the graph with no edges and $N$ as its set of vertices.
-Both $\Set$ and $\Graph$ have finite colimits, and the functor $L$ is left adjoint to the forgetful functor $R \maps \Fin\Graph \to \Set$ that assigns to a graph $G$ its underlying set of vertices $U(G)$.
-Thus, using structured cospans and appealing to \cref{thm:SC}, we get a symmetric monoidal double category $_L \lCsp(\Graph)$ in which:
+Let $L \maps \Set \to \Graph$ be the functor that assigns to a set $N$ the \define{discrete graph} on $N$: the graph with no edges and $N$ as its set of vertices.
+Both $\Set$ and $\Graph$ have finite colimits, and the functor $L \maps \Set \to \Graph$ is left adjoint to the forgetful functor $R \maps \Graph \to \Set$ that assigns to a graph $G$ its underlying set of vertices $U(G)$.
+
+Thus, using structured cospans and appealing to \cref{SC}, we get a symmetric monoidal double category $_L \lCsp(\Graph)$ in which:
 \begin{itemize}
@@
 \path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i_1$} (B)
-(C) edge node[above]{$o_1$} (B)
-(A') edge node[above]{$i_2$} (B')
-(C') edge node[above]{$o_2$} (B')
+(A) edge node[above]{$I_1$} (B)
+(C) edge node[above]{$O_1$} (B)
+(A') edge node[above]{$I_2$} (B')
+(C') edge node[above]{$O_2$} (B')
 (A) edge node [left]{$L(f)$} (A')
@@
 
-We can also build a double category with open graphs as horizontal 1-cells using decorated cospans.    For any finite set $N$ there is a category $F(N)$ where:
+We can also build a double category with open graphs as horizontal 1-cells using decorated cospans.    For any set $N$ there is a category $F(N)$ where:
 \begin{itemize}
@@
 
-In general, decorated cospans are defined using a pseudofunctor to $\Cat$, but in this example there is an honest functor $F \maps \Fin\Set \to \Cat$ that assigns to a set $N$ the above category $F(N)$.
+In general, decorated cospans involve a pseudofunctor to $\Cat$, but in this example there is actually a functor $F \maps \Set \to \Cat$ that assigns to a set $N$ the above category $F(N)$.
 Given a function $f \maps M \to N$, we define $F(f) \maps F(M) \to F(N)$ to map any graph structure $s,t \maps E \to M$ to the graph structure $f \circ s, f \circ t \maps E \to N$.
 
-We obtain a symmetric lax monoidal functor $F \maps (\Fin\Set, +) \to (\Cat,\times)$ by equipping $F$ with suitable functors $\phi_{N,N'} \maps F(N) \times F(N') \to F(N+N')$ for every pair of sets $N$ and $N'$, and also a functor $\phi_0 \maps F(\emptyset) \to 1 \in \Set$.
+We obtain a symmetric lax monoidal functor $F \maps (\Set, +) \to (\Cat,\times)$ by equipping $F$ with suitable functors $\phi_{N,N'} \maps F(N) \times F(N') \to F(N+N')$ for every pair of sets $N$ and $N'$, and also a functor $\phi_0 \maps F(\emptyset) \to 1 \in \Set$.
 The functor $\phi_0$ is uniquely determined since $1$ is the terminal category.
@@
 
-Starting from the symmetric lax monoidal functor $F \maps (\Fin\Set, +) \to (\Cat,\times)$, \cref{DC} gives us a symmetric monoidal double category $F\lCsp$ in which:
+Given the symmetric lax monoidal functor $F \maps (\Set, +) \to (\Cat,\times)$, \cref{DC} gives us a symmetric monoidal double category $F\lCsp$ in which:
 \begin{itemize}
-\item objects are finite sets,
+\item objects are sets,
 \item a vertical 1-morphism from $X$ to $X'$ is a function $f \maps X \to X'$,
@@
 We thus have two symmetric monoidal double categories: ${}_L \lCsp(\Graph)$ obtained from structured cospans and $F\lCsp$ obtained from decorated cospans.
-Both of these double categories have $\Fin\Set$ as their categories of objects, open graphs as horizontal 1-cells, and maps of open graphs as 2-morphisms.
-It is thus quite plausible that ${}_L \lCsp(\Graph)$ and $F\lCsp$ are equivalent as symmetric monoidal double categories.
-
-Indeed, this fact follows from \cref{thm:equiv}.
-To show this, first note that $\inta F \cong \Graph$.
-Then, note that the left adjoint of the Grothendieck fibration $U \maps \inta F \to \Fin\Set$, composed with the isomorphism $\inta F \cong \Graph$, is the functor $L \maps \Fin\Set \to \Graph$ mapping each finite set to the discrete graph on that set.
-Thus,  ${}_L \lCsp(\Graph)$ is equivalent to the symmetric monoidal double category ${}_L \lCsp(\inta F)$ constructed in \cref{thm:equiv}, which in turn is equivalent
-to $F\lCsp$.
+Both of these double categories have $\Set$ as their categories of objects, open graphs as horizontal 1-cells and maps of open graphs as 2-morphisms.
+One can show using Theorem \cref{thm:equiv} that $_L \lCsp(\Graph)$ and $F\lCsp$ are equivalent as symmetric monoidal double categories.
 
@@
 The edge labels can stand for resistors with any chosen resistance, capacitors with any chosen capacitance, inductors with any chosen inductance, or other circuit elements.
-
 To study such circuits quite generally we start by fixing any set $\La$ to serve as edge labels.
-We then define an $\La$-\define{graph} to be a graph $s,t\maps E\to N$
- equipped with a function $\ell \maps E \to \La$.    There is a category $\Graph_\La$ with $\La$-graphs as objects, where a morphism from the $\La$-graph 
+
+\begin{defn}
+Given a set $\La$ of \define{labels}, an $\La$-\define{graph} is a graph $s,t\maps E\to N$
+ equipped with a function $\ell \maps E \to \La$.
+ A \define{morphism} from the $\La$-graph 
  \[ \xymatrix{\La & E \ar@<2.5pt>[r]^{s} \ar@<-2.5pt>[r]_{t} \ar[l]_{\ell} & N} \]
@@
 \]
+\end{defn}
+
+\begin{defn}
+\label{defn:Lgraph}
+We define $\Graph_\La$ to be the category of $\La$-graphs and morphisms between them, with composition given by
+\[  (f, g) \circ (f',g') = (f \circ f' , g \circ g')  .\]
+\end{defn}
 
 When $\La = 1$, an $\La$-graph reduces to a graph and $\Graph_\La$ reduces
-to the category $\Graph$ discussed in \cref{subsec:graphs}.  All the ideas of \cref{subsec:graphs} generalize straightforwardly from graphs to $\La$-graphs.   Everything works the same way, 
+to the category $\Graph$ discussed in \cref{subsec:graphs}.  We now generalize the key
+ideas of that section from graphs to $\La$-graphs.   Everything works the same way, 
 but following previous work \cite{BCR} we call an open $\La$-graph an $\La$-\define{circuit}.
 
-There is a functor $U \maps \Graph_\La \to \Fin\Set$ that takes an $\La$-graph to its underlying set of nodes.
-This has a left adjoint $L \maps \Fin\Set \to \Graph_\La$ sending any set to the $\La$-graph with that set of nodes and no edges.
+There is a functor $U \maps \Graph_\La \to \Fin\Set$ that takes an $\La$-graph to its underlying set of nodes. This has a left adjoint $L \maps \Fin\Set \to \Graph_\La$ sending
+any set to the $\La$-graph with that set of nodes and no edges.
 Both $\Fin\Set$ and $\Graph_\La$ have colimits, and $L$ preserves them.
-Thus \cref{thm:SC} gives us a symmetric monoidal double category ${}_L \lCsp(\Graph_\La)$ where:
+Thus \cref{SC} gives us a symmetric monoidal double category ${}_L \lCsp(\Graph_\La)$ where:
 \begin{itemize}
 \item an object is a finite set,
-\item a horizontal 1-cell is an $\La$-\define{circuit}, meaning a cospan in $\Graph_\La$ of this form:
+\item a morphism is an isomorphism class of $\La$-circuits, where an
+$\La$-\define{circuit} is a cospan in $\Graph_\La$ of this form:
 \[
@@
 \]
-\item a 2-morphism is a commuting diagram in $\Graph_\La$ of this form:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$L(X_1)$};
-\node (B) at (1,0) {$G_1$};
-\node (C) at (2,0) {$L(Y_1)$};
-\node (A') at (0,-1) {$L(X_2)$};
-\node (B') at (1,-1) {$G_2$};
-\node (C') at (2,-1) {$L(Y_2)$.};
-\path[->,font=\scriptsize,>=angle 90]
+and an \define{isomorphism} of $\La$-circuits is a commutative diagram in $\Graph_\La$ 
+of this form:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (E) at (3,-0.5) {$L(S)$};
+\node (F) at (5,-0.5) {$L(T)$};
+\node (G) at (4,0) {$G$};
+\node (G') at (4,-1) {$G'$};
+\path[->,font=\scriptsize,>=angle 90]
+(F) edge node[above]{$o$} (G)
+(G) edge node[left]{$h$} (G')
+(E) edge node[above]{$i$} (G)
+(E) edge node[below]{$i'$} (G')
+(F) edge node[below]{$o'$} (G');
+\end{tikzpicture}
+\]
+where $h$ is an isomorphism.
+\end{itemize} 
+This category has a nice universal property, found by Rosebrugh, Sabadini and
+Walters \cite{RSW}.  To state this, it is convenient to use the language of props.
+% Replaced strict symmetric with symmetric strict three times below
+Recall that a \define{prop} is a symmetric strict monoidal category whose objects are natural
+numbers, with tensor product of objects given by addition.
+An \define{algebra} of a prop $\T$ in a symmetric strict monoidal category $\C$ is a symmetric strict monoidal functor $A \maps \T \to \C$.
+A \define{morphism} from the algebra $A \maps \T \to \C$ to the algebra
+$A' \maps \T \to \C$ is a monoidal natural transformation $\alpha \maps A \To A'$.
+
+\begin{lem} As a symmetric monoidal category, ${}_L \Csp(\Graph_\La)$ is equivalent to a prop $\Circ_\La$.    
+\end{lem}
+
+\begin{proof}
+This is \cite[Proposition 4.3]{BCR}.
+\end{proof}
+
+\begin{prop} 
+\label{prop:LCirc_algebra}
+An algebra of $\Circ_\La$ in a symmetric strict monoidal category $\C$ is a 
+special commutative Frobenius monoid in $\C$ whose underlying object $x$ is equipped
+with an endomorphism $\ell \maps x \to x$ for each element $\ell \in \La$. 
+A morphism of algebras of $\Circ_\La$ in $\C$ is a morphism of special commutative Frobenius monoids that also preserves all these endomorphisms.
+\end{prop}
+
+\begin{proof}
+This was proved by Rosebrugh, Sabadini and Walters \cite{RSW}, and appears
+in the above form in \cite[Proposition 7.2]{BCR}.  
+\end{proof}
+
+In applications to circuits, the morphisms $\ell \maps x \to x$ describe different
+circuit elements, while the special commutative Frobenius monoid structure is used to split and join wires.
+This framework is used to study a wide variety of electrical circuits in a paper with Coya and Rebro \cite{BCR}, so the reader can turn there for details.
+To illustrate the ideas let us consider circuits of resistors, where a label in $\La = (0,\infty)$ serves to indicate the resistance of a resistor.
+In this case a typical morphism from $1$ to $3$ in
+$\Circ_\La$ looks like this:
+\[
+\scalebox{0.6}{
+\begin{tikzpicture}
+	\begin{pgfonlayer}{nodelayer}
+		\node [contact] (n1) at (-2,0) {$\bullet$};
+		\node [style = none] at (-2.1,0.3) {$$};
+		\node [contact] (n2) at (0,1) {$\bullet$};
+		\node [style = none] at (0,1.3) {$$};
+		\node [contact] (n3) at (0,-1) {$\bullet$};
+		\node [style = none] at (0,-1.3) {$$};
+		\node [contact] (n4) at (2,1) {$\bullet$};
+		\node [style = none] at (2.1,0.3) {$$};
+		\node [contact] (n5) at (2,-1) {$\bullet$};
+		\node [style = none] at (2.1,0.3) {$$};
+
+		\node [style = none] at (-1,1.1) {$2.53$};
+		\node [style = none] at (-1,-1.1) {$0.71$};
+		\node [style = none] at (1,1.3) {$9.6$};
+		\node [style = none] at (1,-1.3) {$1.02$};
+	     \node [style = none] at (-0.4,0) {$12.4$};
+	     \node [style = none] at (1.6,0) {$6.3$};
+
+		\node [style=none] (1) at (-3,0) {};
+		\node [style=none] (4) at (3,0) {};
+
+		\node [style=none] (ATL) at (-3.4,1.4) {};
+		\node [style=none] (ATR) at (-2.6,1.4) {};
+		\node [style=none] (ABR) at (-2.6,-1.4) {};
+		\node [style=none] (ABL) at (-3.4,-1.4) {};
+
+		\node [style=none] (X) at (-3,1.8) {$1$};
+		\node [style=inputdot] (inI) at (-2.8,0) {};
+
+		\node [style=none] (Z) at (3,1.8) {$3$};
+	 \node [style=inputdot] (outI') at (2.8,1) {};
+	 \node [style=inputdot] (outI'') at (2.8,0) {};
+	 \node [style=inputdot] (outI''') at (2.8,-1) {};
+
+		\node [style=none] (MTL) at (2.6,1.4) {};
+		\node [style=none] (MTR) at (3.4,1.4) {};
+		\node [style=none] (MBR) at (3.4,-1.4) {};
+		\node [style=none] (MBL) at (2.6,-1.4) {};
+
+	\end{pgfonlayer}
+	\begin{pgfonlayer}{edgelayer}
+		\draw [style=inarrow, bend left=20, looseness=1.00] (n1) to (n2);
+		\draw [style=inarrow, bend right=20, looseness=1.00] (n1) to (n3);
+		\draw [style=inarrow, bend left=0, looseness=1.00] (n2) to (n4);
+		\draw [style=inarrow, bend right=0, looseness=1.00] (n3) to (n4);
+		\draw [style=inarrow, bend right=0, looseness=1.00] (n3) to (n5);
+		\draw [style=inarrow] (n2) to (n3);
+%		\draw [style=inarrow] (W) to (Water);
+%		\draw [style=inarrow, bend left=40, looseness=1.00] (Water2) to (Something);
+%		\draw [style=inarrow, bend right=40, looseness=1.00] (Water2) to (Something);
+%		\draw [style=inarrow, bend left=40, looseness=1.00] (Something) to (A);
+%		\draw [style=inarrow, bend right=40, looseness=1.00] (Something) to (B);
+		\draw [style=simple] (ATL.center) to (ATR.center);
+		\draw [style=simple] (ATR.center) to (ABR.center);
+		\draw [style=simple] (ABR.center) to (ABL.center);
+		\draw [style=simple] (ABL.center) to (ATL.center);
+%		\draw [style=simple] (BTL.center) to (BTR.center);
+%		\draw [style=simple] (BTR.center) to (BBR.center);
+%		\draw [style=simple] (BBR.center) to (BBL.center);
+%		\draw [style=simple] (BBL.center) to (BTL.center);
+		\draw [style=simple] (MTL.center) to (MTR.center);
+		\draw [style=simple] (MTR.center) to (MBR.center);
+		\draw [style=simple] (MBR.center) to (MBL.center);
+		\draw [style=simple] (MBL.center) to (MTL.center);
+%		\draw [style=inputarrow] (outI) to (A);
+%		\draw [style=inputarrow] (outS) to (B);
+		\draw [style=inputarrow] (inI) to (n1);
+		\draw [style=inputarrow] (outI') to (n4);
+		\draw [style=inputarrow] (outI'') to (n5);
+		\draw [style=inputarrow] (outI''') to (n5);
+%		\draw [style=inputarrow] (inI') to (Water2);
+%		\draw [style=inputarrow] (inS') to (Water2);
+	\end{pgfonlayer}
+\end{tikzpicture}
+}
+\]
+The edges here represent wires, and the positive real numbers labeling them describe
+the resistance of the resistor on each wire.
+The points in the boxes represent `terminals': that is, points where we allow ourselves to attach a wire from another circuit.
+The points in the left box are called `inputs' and the points in the right box are called `outputs'.
+In electrical engineering we associate two real numbers to each terminal, called `potential' and `current'.
+Any circuit of resistors imposes a specific relation between the potentials and currents at its inputs and those at its outputs.
+All these relations, for all circuits of resistors, can be described using a single functor as follows.
+
+There is a symmetric monoidal category $\Fin\Rel_\R$ where the objects are finite-dimensional real vector spaces and a morphism from $V$ to $W$ is a \define{linear relation} from $V$ to $W$: that is, a relation $L \subseteq V \times W$ that is a linear subspace of $V \times W$.
+Composition in $\Fin\Rel_\R$ is the usual composition of relations, and the symmetric monoidal structure is provided by direct sum.
+
+There is a symmetric monoidal functor
+\[   \blacksquare \maps \Circ_\La \to \Fin\Rel_\R  \]
+% Added the line "sending any finite set $S$ to the vector space 
+% $\mathbb{R}^S \oplus \mathbb{R}^S$ and" to say what the black-box functor does on objects
+% Changed Prop. to Proposition 
+sending any finite set $S$ to the vector space $\R^S \oplus \R^S$ and
+sending any circuit of resistors to the relation it imposes between the potentials and currents at its inputs and those at its outputs \cite[Section 9]{BCR}.
+We can construct this using Proposition \ref{prop:LCirc_algebra}, by choosing a special commutative Frobenius monoid in $\Fin\Rel_\R$ whose underlying object is equipped with an endomorphism for each resistance $R \in (0,\infty)$.
+The object $\R^2 \in \Fin\Rel_\R$ is a special commutative Frobenius monoid in a standard way \cite[Section\ 8]{BCR}, so we choose this one.
+To define $\blacksquare \maps \Circ_\La \to \Fin\Rel_\R$ it then suffices to choose for each $R \in (0,\infty)$ a linear relation from $\R^2$ to itself.
+We use this:
+\[ \left\{(\phi_1,I_1,\phi_2,I_2) : \; I_1 = I_2 , \; \phi_2-\phi_1 = R I_1\right\} 
+ \subseteq \R^2 \oplus \R^2.\]
+This expresses two laws of electrical engineering.   Kirchhoff's current law says that the 
+current flowing into a wire equals the current flowing out: $I_1 = I_2$.
+Ohm's law says that the voltage across a wire with a resistor on it, $\phi_2 - \phi_1$, is equal to the current flowing through the wire times the resistance $R$ of that resistor.
+
+\begin{comment}
+
+In a previous work \cite{BP}, Fong and the first author used decorated cospans to construct a symmetric monoidal category of `open passive linear circuits'.
+Roughly speaking, given a field $k$, a passive linear circuit is given by a `$k$-graph' which is a diagram in $\mathsf{FinSet}$ of the form:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (B) at (1,0) {$E$};
+\node (C) at (2,0) {$V$};
+\node (A) at (0,0) {$k^+$};
+\path[->,font=\scriptsize,>=angle 90]
+(B)edge node[above] {$r$}(A)
+(B)edge[bend left] node[above]{$s$}(C)
+(B)edge[bend right] node[below]{$t$}(C);
+\end{tikzpicture}
+\]
+Here the finite sets $E$ and $V$ are the sets of edges and vertices, respectively, and if we take the field $k = \mathbb{R}$, the function $r \maps E \to \mathbb{R}^+$ assigns to each edge $e \in E$ a positive real number $r(e) \in \mathbb{R}^+$ which can be interpreted as the resistance at the edge $e$.
+An open passive linear circuit is then given by a cospan of finite sets
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (B) at (1,0) {$V$};
+\node (C) at (2,0) {$Y$};
+\node (A) at (0,0) {$X$};
+\path[->,font=\scriptsize,>=angle 90]
+(A)edge node[above] {$i$}(B)
+(C)edge node[above]{$o$}(B);
+\end{tikzpicture}
+\]
+where the apex $V$ is equipped with the structure of a passive linear circuit. See the original paper for more details \cite{BP}.
+
+Let $\Graph_k$ be the category whose objects are given by $k$-graphs and morphisms by morphisms of $k$-graphs, where a morphism of $k$-graphs is given by a pair of functions $f \maps E \to E'$ and $g \maps V \to V'$ between the edge sets and vertex sets, respectively, of two $k$-graphs that respect the source and target functions of each.
+In a previous work introducing structured cospans, the first two authors showed that the category $\Graph_k$ has finite colimits \cite{BC2}.
+We can then obtain a double category of open passive linear circuits by defining a left adjoint $L \maps \Set \to \Graph_k$ that assigns to a set $V$ the discrete passive linear circuit $L(V)$ given by passive linear circuit with $V$ as its set of vertices and no edges.
+The resulting symmetric monoidal double category $_L \lCsp(\Graph_k)$ has:
+\begin{enumerate}
+\item{finite sets as objects,}
+\item{functions as vertical 1-morphisms,}
+\item{open passive linear circuits as horizontal 1-cells
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (B) at (1,0) {$V$};
+\node (C) at (2,0) {$Y$};
+\node (A) at (0,0) {$X$};
+\node (D) at (3,0) {$k^+$};
+\node (E) at (4,0) {$E$};
+\node (F) at (5,0) {$V$};
+\path[->,font=\scriptsize,>=angle 90]
+(E) edge node [above] {$r$} (D)
+(E) edge [bend left] node [above] {$s$} (F)
+(E) edge [bend right] node [below] {$t$} (F)
+(A)edge node[above] {$i$}(B)
+(C)edge node[above]{$o$}(B);
+\end{tikzpicture}
+\]
+and}
+\item{maps of cospans as 2-morphisms together with a map of passive linear circuits between the apices.
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$X_1$};
+\node (A') at (0,-1) {$X_2$};
+\node (C') at (2,-1) {$Y_2$};
+\node (B) at (1,0) {$V_1$};
+\node (C) at (2,0) {$Y_1$};
+\node (D) at (1,-1) {$V_2$};
+\node (E) at (3,0) {$k^+$};
+\node (E') at (3,-1) {$k^+$};
+\node (F) at (4,0) {$E_1$};
+\node (F') at (4,-1) {$E_2$};
+\node (G) at (5,0) {$V_1$};
+\node (G') at (5,-1) {$V_2$};
+\path[->,font=\scriptsize,>=angle 90]
+(F) edge node[above] {$r_1$} (E)
+(F) edge [bend left] node [above] {$s_1$} (G)
+(F) edge [bend right] node [below] {$t_1$} (G)
+(F') edge node[above] {$r_2$} (E')
+(F') edge [bend left] node [above] {$s_2$} (G')
+(F') edge [bend right] node [below] {$t_2$} (G')
 (A) edge node[above]{$i_1$} (B)
 (C) edge node[above]{$o_1$} (B)
-(A') edge node[above]{$i_2$} (B')
-(C') edge node[above]{$o_2$} (B')
-(A) edge node [left]{$L(f)$} (A')
-(B) edge node [left]{$\alpha$} (B')
-(C) edge node [left]{$L(g)$} (C');
-\end{tikzpicture}
-\]
-\end{itemize}
-
-By Theorem ???
-we obtain a symmetric monoidal category ${}_L \Csp(\Graph_\La)$.
-In fact this symmetric monoidal category is equivalent to a prop, and the algebras of this prop were described in \cite[Proposition 7.2]{BCR}, and applied to study electrical circuits.
-
-\begin{comment}
+(A) edge node[left]{$h$} (A')
+(C) edge node[left]{$h'$} (C')
+(C') edge node [above] {$o_2$} (D)
+(A') edge node [above] {$i_2$} (D)
+(B) edge node [left] {$g$} (D)
+(F) edge node [left] {$f$} (F')
+(G) edge node [right] {$g$} (G');
+\end{tikzpicture}
+\]
+}
+\end{enumerate}
+We can also obtain a similar double category using decorated cospans: define a pseudofunctor $F \maps \mathsf{FinSet} \to \Cat$ that assigns to a finite set $V$ the category of all $k$-graph structures on the finite set $V$ and to a function $f \maps V \to V'$ the corresponding functor $F(f) \maps F(V) \to F(V')$ between decoration categories.
+Both categories $\mathsf{FinSet}$ and $\Cat$ are symmetric monoidal and the pseudofunctor $F \maps \mathsf{FinSet} \to \Cat$ is symmetric lax monoidal, as given a $k$-graph structure on a finite set $V_1$ denoted by an element $K_1 \in F(V_1)$ and a $k$-graph structure on a finite set $V_2$ denoted by an element $K_2 \in F(V_2)$, we can consider the $k$-graph structures simultaneously as a single graph structure $\phi_{V_1,V_2}(K_1,K_2)$ on the finite set $V_1+V_2$.
+Thus we get a family of natural transformations $$\phi_{V_1,V_2} \maps F(V_1) \times F(V_2) \to F(V_1+V_2)$$ as well as a morphism $\phi \maps 1_{\Graph_k} \to F(\emptyset)$ which together satisfy the coherence conditions of a monoidal functor.
+The braiding is also clear as the following diagram commutes:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (E) at (3,0) {$F(V_1) \times F(V_2)$};
+\node (G) at (5,0) {$F(V_2) \times F(V_1)$};
+\node (E') at (3,-1) {$F(V_1+V_2)$};
+\node (G') at (5,-1) {$F(V_2+V_1)$};
+\path[->,font=\scriptsize,>=angle 90]
+(E) edge node[left]{$\phi_{V_1,V_2}$} (E')
+(G) edge node[right]{$\phi_{V_2,V_1}$} (G')
+(E) edge node[above]{$\beta_{V_1,V_2}$} (G)
+(E') edge node[above]{$F(\beta_{V_1,V_2})$} (G');
+\end{tikzpicture}
+\]
+Thus the pseudofunctor $F$ is symmetric lax monoidal and so by Theorem \cref{DC} we get a symmetric monoidal double category $F\lCsp$ which has:
+\begin{enumerate}
+\item{objects as finite sets,}
+\item{vertical 1-morphisms as functions,}
+\item{horizontal 1-cells as cospans of finite sets together with the structure of a $k$-graph given by an element of the image of the apex under the pseudofunctor $F$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (D) at (-3,0) {$U$};
+\node (E) at (-2,0) {$V$};
+\node (F) at (-1,0) {$W$};
+\node (A) at (0,0) {$K \in F(V)$};
+\path[->,font=\scriptsize,>=angle 90]
+(D) edge node [above] {$i$} (E)
+(F) edge node [above] {$o$} (E);
+\end{tikzpicture}
+\]
+and}
+\item{2-morphisms as maps of cospans of finite sets 
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (E) at (3,0) {$U_1$};
+\node (F) at (5,0) {$W_1$};
+\node (G) at (4,0) {$V_1$};
+\node (E') at (3,-1) {$U_2$};
+\node (F') at (5,-1) {$W_2$};
+\node (G') at (4,-1) {$V_2$};
+\node (A) at (6,0) {$K_1 \in F(V_1)$};
+\node (B) at (6,-1) {$K_2 \in F(V_2)$};
+\path[->,font=\scriptsize,>=angle 90]
+(F) edge node[above]{$o_1$} (G)
+(E) edge node[left]{$f$} (E')
+(F) edge node[right]{$g$} (F')
+(G) edge node[left]{$h$} (G')
+(E) edge node[above]{$i_1$} (G)
+(E') edge node[above]{$i_2$} (G')
+(F') edge node[above]{$o_2$} (G');
+\end{tikzpicture}
+\]
+together with a morphism of $k$-graphs $\tau \maps F(h)(K_1) \to K_2$ in $F(V_2)$.}
+\end{enumerate}
+These two double categories $_L \lCsp(\Graph_k)$ and $F\lCsp$ are equivalent by Theorem \cref{thm:equiv}.
+
+\subsection{Markov processes}
+In another previous work \cite{BFP}, Fong, Pollard and the first author used decorated cospans to construct a symmetric monoidal category of `open Markov processes'.
+In this framework, a Markov process on a finite set $N$ is given by a diagram in $\Set$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (D) at (3,0) {$(0,\infty)$};
+\node (E) at (4,0) {$E$};
+\node (F) at (5,0) {$N$};
+\path[->,font=\scriptsize,>=angle 90]
+(E) edge node [above] {$r$} (D)
+(E) edge [bend left] node [above] {$s$} (F)
+(E) edge [bend right] node [below] {$t$} (F);
+\end{tikzpicture}
+\]
+where $E$ and $N$ are finite sets of edges and nodes, respectively.
+This is really just a special case of the previous example of passive linear circuits with $k = \mathbb{R}$.
+An open Markov process is then of course a cospan of finite sets where the apex is equipped with a Markov process:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (B) at (1,0) {$N$};
+\node (C) at (2,0) {$Y$};
+\node (A) at (0,0) {$X$};
+\node (D) at (3,0) {$(0,\infty)$};
+\node (E) at (4,0) {$E$};
+\node (F) at (5,0) {$N$};
+\path[->,font=\scriptsize,>=angle 90]
+(E) edge node [above] {$r$} (D)
+(E) edge [bend left] node [above] {$s$} (F)
+(E) edge [bend right] node [below] {$t$} (F)
+(A)edge node[above] {$i$}(B)
+(C)edge node[above]{$o$}(B);
+\end{tikzpicture}
+\]
+For example:
+\[
+\begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=3.7cm,
+thick,main node/.style={circle,fill=white!20,draw,font=\sffamily\Large\bfseries},terminal/.style={circle,fill=blue!20,draw,font=\sffamily\Large\bfseries}]]
+\node[main node](1) {$b_1$};
+\node[main node](2) [left=0.8cm of 1] {$a_1$};.5
+\node[main node](3) [below right=0.7cm and 2.4cm of 1] {$c_2$};
+\node[main node](5) [above right=0.7cm and 2.4cm of 1] {$c_1$};
+\node[main node](4) [above right=0.7cm and 2.4cm of 3] {$d_1$};
+\node(A) [left=1cm of 2,circle,draw,inner sep=1pt,fill=gray,color=purple] {};
+\node(C) [right=1cm of 4,circle,draw,inner sep=1pt,fill=gray,color=purple] {};
+\node[left=1.25 cm of 2,color=purple] {$S$};
+\node[right=1.25 cm of 4,color=purple] {$T$};
+\path[every node/.style={font=\sffamily\small}, shorten >=1pt]
+(3) edge [bend right =15] node[below] {$e_6$} (4)
+(5) edge [bend left =15] node[below] {$e_5$} (4)
+(2) edge [bend left=15] node[below] {$e_1$} (1)
+(1) edge [bend left =15] node[below] {$e_2$} (5)
+(5) edge [bend right =15] node[right] {$e_4$} (3)
+(1) edge [bend right =15] node[below] {$e_3$} (3)
+(3) edge [bend right =15] node[above] {$6$} (4)
+(5) edge [bend left =15] node[above] {$6$} (4)
+(2) edge [bend left=15] node[above] {$5$} (1)
+(1) edge [bend left =15] node[above] {$8$} (5)
+(5) edge [bend right =15] node[left] {$4$} (3)
+(1) edge [bend right =15] node[above] {$8$} (3);
+\path[color=purple, very thick, shorten >=10pt, ->, >=stealth] (C) edge (4);
+\path[color=purple, very thick, shorten >=10pt, ->, >=stealth] (A) edge (2);
+\end{tikzpicture}
+\]
+Here we have an open Markov process on the finite set $N = \{a_1,b_1,c_1,c_2,d_1 \}$ with input and output sets given by the singletons $S$ and $T$, respectively.
+
 Fong, Pollard and the first author then add extra structure to open Markov processes such as populations at each node to obtain a symmetric monoidal category $\mathsf{DetlBalMark}$ of open Markov processes in `detailed balance' and then construct a black box functor $\blacksquare \maps \mathsf{DetBalMark} \to \mathsf{LinRel}$ that describes the steady state behavior of an open Markov process in detailed balance.
@@
 Both categories $\mathsf{FinSet}$ and $\mathsf{Mark}$ have finite colimits and the functor $L$ is left adjoint to the forgetful functor $R \maps \mathsf{Mark} \to \mathsf{FinSet}$ which maps a Markov process to its underlying finite set of states.
-By Theorem \cref{thm:SC}, we get a symmetric monoidal double category $_L \lCsp(\mathsf{Mark})$ which has:
+By Theorem \cref{SC}, we get a symmetric monoidal double category $_L \lCsp(\mathsf{Mark})$ which has:
 \begin{enumerate}
@@
 Master and the first author show the existence of a left adjoint $L \maps \Set \to \Petri$ where $\Petri$ is the category whose objects are Petri nets and whose `morphisms are morphisms of Petri nets'.
-They also show that $\Petri$ has finite colimits and thus using \cref{thm:SC} obtain a symmetric monoidal double category $\lOpen(\Petri)$ of open Petri nets which has:
+They also show that $\Petri$ has finite colimits and thus using Theorem \cref{SC} obtain a symmetric monoidal double category $\lOpen(\Petri)$ of open Petri nets which has:
 \begin{enumerate}
@@
 
-\subsection{Bicategories}
-\label{subsec:bicats}
-
-{\chris There used to be references for more details on the material that follows. Why would we not provide them?}
-
-A \define{monoidal} bicategory $\bA$ comes with a pseudofunctor $\otimes\maps\bA\times\bA\to\bA$ and a unit object $I$ that are associative and unital up to coherent equivalence.
+\subsection{2-categories}\label{sec:2cats}
+For standard 2-categorical material, we refer the reader to e.g. \cite{KS} or \cite{DS} for monoidal structures. %!!!Christina: also John's paper on monoidal 2-structures?
+Recall that a \define{pseudofunctor} $F\maps\bicat{A}\to\bicat{B}$ between bicategories $\bicat{A}$ and $\bicat{B}$ is functorial up to coherent natural isomorphism, namely for composable arrows we have $F(g\circ f)\cong Fg\circ Ff$ and $F(1_a)\cong1_{Fa}$ satisfying standard axioms.
+Given pseudofunctors $F,G\maps \bicat{A} \to \bicat{B}$, a \define{pseudonatural transformation} $\sigma$ consists of
+\begin{itemize}
+\item for each object $a \in \bicat{A}$, a morphism $\sigma_a \maps F(a) \to G(a)$ in $\bicat{B}$ 
+\item 
+%for every pair of objects $a$ and $b$ of $\mathbf{A}$, we have natural isomorphisms
+%\[
+%\begin{tikzpicture}[scale=1.5]
+%\node (A) at (0,0) {$\mathbf{A}(a,b)$};
+%\node (B) at (2,0) {$\mathbf{X}(F(a),F(b))$};
+%\node (C) at (0,-1) {$\mathbf{X}(G(a),G(b))$};
+%\node (D) at (2,-1) {$\mathbf{X}(F(a),G(b))$};
+%\node (E) at (1,-0.5) {$\sigma_{a,b} \Nearrow$};
+%\path[->,font=\scriptsize,>=angle 90]
+%(A) edge node[above]{$F$} (B)
+%(B) edge node[right]{$(\sigma_{b})_*$} (D)
+%(A) edge node[left]{$G$} (C)
+%(C) edge node[above]{$(\sigma_a)^*$} (D);
+%\end{tikzpicture}
+%\]
+%where $(\sigma_a)^*$ and $(\sigma_b)_*$ are the functors induced by precomposition and postcompositon, respectively. Thus 
+for each morphism $f \maps a \to b$ in $\mathbf{A}$, an invertible natural 2-morphism $\sigma_f \maps G(f) \sigma_a \xrightarrow{\sim} \sigma_{b} F(f)$ in $\mathbf{B}$
+%:
+%\[
+%\begin{tikzpicture}[scale=1.5]
+%\node (A) at (0,0) {$F(a)$};
+%\node (B) at (1,0) {$F(b)$};
+%\node (C) at (0,-1) {$G(a)$};
+%\node (D) at (1,-1) {$G(b)$};
+%\node (E) at (0.5,-0.5) {$\sigma_f \Nearrow$};
+%\path[->,font=\scriptsize,>=angle 90]
+%(A) edge node[above]{$F(f)$} (B)
+%(B) edge node[right]{$\sigma_{b}$} (D)
+%(A) edge node[left]{$\sigma_a$} (C)
+%(C) edge node[above]{$G(f)$} (D);
+%\end{tikzpicture}
+%\]
+compatible with composition and identities.
+\end{itemize}
+%such that for each composable pair of morphisms $f \maps a \to b$ and $g \maps b \to c$ of $\mathbf{A}$, the following diagrams commute:
+%\[
+%\begin{tikzpicture}[scale=1.5]
+%\node (A) at (0,0.5) {$(G(g)G(f))\sigma_a$};
+%\node (A') at (2,0.5) {$G(g)(G(f) \sigma_a)$};
+%\node (B) at (0,-0.5) {$G(gf) \sigma_a$};
+%\node (C) at (4,0.5) {$G(g) (\sigma_b F(f))$};
+%\node (C') at (4,-0.5) {$\sigma_c F(gf)$};
+%\node (D) at (6,0.5) {$(G(g) \sigma_b) F(f)$};
+%\node (D') at (8,-0.5) {$\sigma_c (F(g)F(f))$};
+%\node (F) at (8,0.5) {$(\sigma_c F(g)) F(f)$};
+%\path[->,font=\scriptsize,>=angle 90]
+%(A) edge node[above]{$a'$} (A')
+%(A) edge node[left]{$\psi 1_{\sigma_a}$} (B)
+%(A') edge node[above]{$1_{G(g)} \sigma_f$} (C)
+%(B) edge node[above]{$\sigma_{gf}$} (C')
+%(C) edge node [above] {${a'}^{-1}$} (D)
+%(D') edge node [above] {$1_{\sigma_c} \phi$} (C')
+%(D) edge node [above] {$\sigma_g 1_{F(f)}$} (F)
+%(F) edge node [right] {$a'$} (D');
+%\end{tikzpicture}
+%\]
+%\[
+%\begin{tikzpicture}[scale=1.5]
+%\node (A) at (0,0) {$1_{G(a)} \sigma_a$};
+%\node (B) at (1,1) {$G(1_a) \sigma_a$};
+%\node (C) at (2,0) {$\sigma_a F(1_a)$};
+%\node (D) at (0.5,-1) {$\sigma_a$};
+%\node (E) at (1.5,-1) {$\sigma_a 1_{F(a)}$};
+%\path[->,font=\scriptsize,>=angle 90]
+%(A) edge node[left]{$\psi 1_{\sigma_a}$} (B)
+%(B) edge node[right]{$\sigma_{1_a}$} (C)
+%(A) edge node [left] {$\ell'$} (D)
+%(D) edge node [above] {${\rho'}^{-1}$} (E)
+%(E) edge node [right] {$1_{\sigma_a} \phi$} (C);
+%\end{tikzpicture}
+%\]
+%Christina: I removed the above, they are not needed I believe. Check again in the end.
+We denote by $[\bicat{A},\bicat{B}]_\pse$ the 2-category 
+of pseudofunctors, pseudonatural transformations and modifications.
+
+A \define{monoidal} bicategory $\bicat{A}$ comes with a pseudofunctor $\otimes\maps\bicat{A}\times\bicat{A}\to\bicat{A}$ and a unit object $I$ that are associative and unital up to coherent equivalence.
 A \define{braided} monoidal bicategory comes with a pseudonatural equivalence $\beta_{a,b}\maps a\ot b\to b\ot a$ and appropriate invertible modifications; it is \define{sylleptic} if there is an appropriate invertible modification $1_{a\ot b}\Rrightarrow\beta_{b,a}\circ\beta_{a,b}$ and it is \define{symmetric} if one further axiom holds.
-A \define{lax monoidal} pseudofunctor between monoidal bicategories $F\maps\bA\to\bB$ is a pseudofunctor equipped with pseudonatural transformations with components $\phi_{a,b}\maps Fa\otimes Fb\to F(a\otimes b)$ and $\phi_0\maps I\to FI$ along with coherent invertible modifications for associativity and unitality.
-A \define{braided lax monoidal} pseudofunctor between braided monoidal bicategories comes with an appropriate invertible modification with components $F(\beta_{a,b})\circ \phi_{a,b}\cong\phi_{b,a}\circ \beta_{Fa,Fb}$; a \define{sylleptic lax monoidal} pseudofunctor satisfies one extra condition and a \define{symmetric lax monoidal} pseudofunctor between symmetric monoidal bicategories is just a sylleptic one.
+A \define{lax monoidal} pseudofunctor between monoidal bicategories $F\maps\bicat{A}\to\bicat{B}$ is a pseudofunctor equipped with pseudonatural transformations with components $\mu_{a,b}\maps Fa\otimes Fb\to F(a\otimes b)$ and $\mu_0\maps I\to FI$ along with coherent invertible modifications for associativity and unitality.
+This is commonly also called `weak monoidal' pseudofunctor.
+A \define{braided lax monoidal} pseudofunctor between braided monoidal bicategories comes with an appropriate invertible modification with components $F(\beta_{a,b})\circ \mu_{a,b}\cong\mu_{b,a}\circ \beta_{Fa,Fb}$; a \define{sylleptic lax monoidal} pseudofunctor satisfies one extra condition and a \define{symmetric lax monoidal} pseudofunctor between symmetric monoidal bicategories is just a sylleptic one.
+RIGHT???
 
 \subsection{Fibrations}\label{sec:fibrations}
-
 Basic material regarding the theory of fibrations can be found, for example, in \cite{Borc,Gray}.
@@
         \end{displaymath}
-           where $[\A,\Cat]_\pse$ is the 2-category 
-of pseudofunctors from $\A$ to $\Cat$, pseudonatural transformations, and modifications.
 %        \item The above 2-equivalence extends to one between 2-categories of arbitrary-base fibrations and arbitrary-domain indexed categories
@@
 Before formally defining `pseudo double category', it is helpful to have the following picture in mind. A pseudo double category has 2-morphisms shaped like:
-Before defining double categories, it is helpful to have the following picture in mind. A double category has 2-morphisms shaped like:
 
@@
 
-DEFINITION OF SYMMETRIC MONOIDAL ISOMORPHISM, BRIEFLY?
-
 \begin{thebibliography}{100}

### 2020-11-19 cospans.tex
changed mu to phi in many places; worked on Thm. 3.2

@@
 \begin{itemize}
-\item{the image of an object $a \in F\lCsp_0=\A$ is the object $H(a) \in F'\lCsp_0=\A'$,}
-\item{the image of a vertical 1-morphism $f \colon a \to b$ is the vertical 1-morphism $H(f) \colon H(a) \to H(b)$.
-In other words, the object component $\lH_0$ of the double functor $\lH$ is the functor $H$.}
-\item{Given a horizontal 1-cell $M$ in $F\lCsp$, which is an $F$-decorated cospan, the image will be the $F'$-decorated cospan $\lH(M)$ in $F'\lCsp$
+\item The image of an object $a \in F\lCsp_0=\A$ is the object $H(a) \in F'\lCsp_0=\A'$,
+\item The image of a vertical 1-morphism $f \colon a \to b$ is the vertical 1-morphism $H(f) \colon H(a) \to H(b)$.
+In other words, the object component $\lH_0$ of the double functor $\lH$ is the functor $H$.
+\item Given a horizontal 1-cell $M$ in $F\lCsp$, which is an $F$-decorated cospan, the image will be the $F'$-decorated cospan $\lH(M)$ in $F'\lCsp$
 \[
@@
 \]
-where given a decoration $x \colon 1 \to F(m)$ on $m$, we obtain a decoration on $H(m)$ via the composite $$1 \xrightarrow{\phi} E(1) \xrightarrow{E(x)} E(F(m)) \xrightarrow{\theta_m} F'(H(m)).$$}
-\item{Given a 2-morphism $\alpha \colon M \to N$ in $F\lCsp$, which is a map of $F$-decorated cospans, the image will be the map of $F'$-decorated cospans $\lH(\alpha)$ in $F'\lCsp$
+where given a decoration $x \colon 1 \to F(m)$ on $m$, we obtain a decoration on $H(m)$ via the composite 
+\[ 1 \xrightarrow{\phi} E(1) \xrightarrow{E(x)} E(F(m)) \xrightarrow{\theta_m} F'(H(m)).\]
+\item Given a 2-morphism $\alpha \colon M \to N$ in $F\lCsp$, which is a map of $F$-decorated cospans, the image will be the map of $F'$-decorated cospans $\lH(\alpha)$ in $F'\lCsp$
 \[
@@
 \end{tikzpicture}
-\]}
+\]
 \end{itemize}
@@
 
-In \cite{BC2}, the first two authors introduce the symmetric monoidal double category of \emph{structured cospans} as a formalism to capture open networks.
-One of the main goals of this paper is to provide a monoidal double isomorphism between this double category and that of \emph{decorated cospans}, described in detail in \cref{DecCospansDoubleCat}.
-We first recall the double category structured cospans form.
+In \cite{BC2}, the first two authors introduced the symmetric monoidal double category of \emph{structured cospans} as a formalism to describe open networks.
+One of the main goals of this paper is to provide a monoidal double isomorphism between this double category and that of \emph{decorated cospans}, described in \cref{DecCospansDoubleCat}.
+We first recall the double category of structured cospans.
 
@@
 \end{itemize}
-The symmetric monoidal structure is formed by using binary coproducts and the initial object.
+Composition of horizontal 1-cells and 2-cells is done using pushouts in $\X$, and the
+symmetric monoidal structure is defined using binary coproducts and the initial object in $\A$ and $\X$.
 \end{thm}
@@
 \begin{proof}
-This was proved in \cite[Theorems~2.3 \& 3.9]{BC2}.
-Composition is formed by taking pushouts in $\X$ and identity horizontal 1-cells are $L(a)\xrightarrow{\raisebox{-3pt}[0pt][0pt]{=}}L(a)\xleftarrow{\raisebox{-3pt}[0pt][0pt]{=}}L(a)$.
-In particular, the double category structure only requires that $\X$ have pushouts, whereas the symmetric monoidal structure also requires that $\X$ has binary coproducts and an initial object (and thus all finite colimits), and that $\A$ has and $L$ preserves finite coproducts \cite[Theorem~3.2.3]{CourserThesis}.
+This was proved in \cite[Theorems~2.3 \& 3.9]{BC2}, where all the structures are specified in detail.
+In fact the double category structure only requires that $\X$ have pushouts, whereas the symmetric monoidal structure also requires that $\X$ has binary coproducts and an initial object (and thus all finite colimits), and that $\A$ has and $L$ preserves finite coproducts \cite[Theorem~3.2.3]{CourserThesis}.
 \end{proof}
@@
 The following theorem establishes the isomorphism between structured and decorated cospan double categories under certain conditions.
-We denote by $\Rex$ the 2-category of finitely cocomplete categories, finitely cocontinuous functors and natural transformatoins.
+We denote by $\Rex$ the 2-category of finitely cocomplete categories, finitely cocontinuous functors and natural transformations.
 
 \begin{thm} \label{thm:equiv}
-Suppose $\ca{A}$ has finite colimits and $F\maps(\A,+) \to (\Cat,\times)$ is a symmetric lax monoidal pseudofunctor that factors through $\bicat{Rex}$ as an ordinary pseudofunctor.
+Suppose $\A$ has finite colimits and $F\maps(\A,+) \to (\Cat,\times)$ is a symmetric lax monoidal pseudofunctor that factors through $\Rex$ as an ordinary pseudofunctor.
 Then the symmetric monoidal double categories $F\lCsp$ of decorated cospans and $_L\lCsp(\inta F)$ of structured cospans are equivalent, where $L \maps \A \to \inta F$ is a left adjoint of the induced Grothendieck opfibration $U\maps \inta F \to \A$.
@@
 
-In \cite{MV}, the classical Grothendieck construction is generalized to the monoidal setting: lax monoidal structures on a pseudofunctor $F\maps\A\to\Cat$ (called \emph{monoidal opindexed categories}) bijectively correspond to monoidal structures on the total category $\inta F$ such that the induced opfibration is a strict monoidal functor and $\otimes_{\inta F}$ preserves cocartesian liftings (called \emph{monoidal fibrations}).
-If the monoidal category $\A$ is in fact cocartesian, there is a further correspondence of the two structures with an ordinary pseudofunctor $F\maps\A\to\bicat{MonCat}$ into the 2-category of monoidal categories, strong monoidal functors and monoidal natural transformations.
+In \cite{MV}, the classical Grothendieck construction is generalized to the monoidal setting.  Suppose $\A$ is a monoidal category.     Then there is a bijection between:
+\begin{itemize}
+\item lax monoidal structures on a pseudofunctor $F\maps\A\to\Cat$, and
+\item monoidal structures on $\inta F$ such that $U \maps \inta F \to \A$ is strict monoidal and the tensor product in $\inta F$ preserves cocartesian liftings.  
+\end{itemize}
+We call the former \define{monoidal opindexed categories}, and the latter \define{monoidal opfibrations}.
+If the monoidal structure of $\A$ is cocartesian, there is a further correspondence between these structures and ordinary pseudofunctors $F\maps\A\to\bicat{MonCat}$ into the 2-category of monoidal categories, strong monoidal functors and monoidal natural transformations.
+These correspondences can be enhanced to 2-equivalences:
 
@@
 These correspondences further restrict to the case when the Grothendieck category is specifically cocartesian monoidal itself. In that case, opfibrations
-$(\X,+)\to(\A,+)$ that strictly preserve chosen coproducts and initial object
+$U \maps (\X,+)\to(\A,+)$ that strictly preserve chosen coproducts and initial object
 %, and such that $+$ preserves cocartesian liftings, Christina: this should ALWAYS be the case, by universal properties!
-bijectively correspond to pseudofunctors into the 2-category of cocartesian categories; for more details, see \cite[Corollary 4.7]{MV} and the related discussion.
-
-Finally, we can further restrict to the setting of opfibrations that also preserve pushouts, i.e.
-all finite colimits, which is important for our purposes.
-The following result is in fact more general since it relates the existence of any class of colimits in the total category of an opfibration to their existence in the fibres; for a more detailed exposition, see \cite[Corollary~4.9]{Hermida1999}.
+bijectively correspond to pseudofunctors into the 2-category of cocartesian categories.  For more details, see \cite[Corollary 4.7]{MV} and the related discussion.
+
+Finally, we can further restrict to the setting of opfibrations that also preserve pushouts, and thus all finite colimits, thanks to the following result.
 %as well as Remark~4.11 therein regarding the non-necessary strictness condition. Is this obscuring or clarifying?
 
-\begin{lem}\label{lem:fibrewiselimits}
-Suppose $\ca{J}$ is a small category and $U\maps\X\to\A$ is an opfibration. If the base $\A$ has $\ca{J}$-colimits,
+\begin{lem}[Hermida] \label{lem:fibrewiselimits}
+Suppose $\J$ is a small category and $U\maps\X\to\A$ is an opfibration. If the base $\A$ has $\J$-colimits,
 the following are equivalent:
 \begin{enumerate}
- \item all fibres have $\ca{J}$-colimits, and the reindexing functors preserve them;
- \item the total $\X$ has $\ca{J}$-colimits, and $U$ (strictly) preserves them.
+ \item all fibres have $\J$-colimits, and the reindexing functors preserve them;
+ \item the total category $\X$ has $\J$-colimits, and $U$ preserves them.
 \end{enumerate}
@@
 
-The first part formulates the existence of colimits \emph{locally} in each fibre, which for $\ca{J}$ a finite category can equivalently be expressed by the corresponding pseudofunctor $F\maps\A\to\Cat$ landing on the sub-2-category $\Rex$ of finitely cocomplete categories and functors that preserve colimits.
-The second part formulates the existence of colimits \emph{globally} in the total category $\inta F$.
-Combining this with \cref{lem:MonGroth}, we deduce the following.
+\begin{proof}  See \cite[Corollary~4.9]{Hermida1999}.   \end{proof}
+
+The first part formulates the existence of colimits \emph{locally} in each fibre, and if we let $\J$ range over all finite categories it says that the corresponding pseudofunctor $F\maps\A\to\Cat$ lands in the sub-2-category $\Rex$.
+The second part formulates the existence of colimits \emph{globally} in the total category $\inta F$, and if we let $\J$ range over all finite
+categories it says that $\X$ is finitely cocomplete and $U$ preserves all finite colimits.  Combining this with \cref{lem:MonGroth}, we deduce the following.
 
@@
  Suppose $\A$ is a finitely cocomplete category and $F\maps(\A,+)\to(\Cat,\times)$ is a lax monoidal pseudofunctor.
-If its corresponding pseudofunctor $\A\to\bicat{MonCat}$ via \cref{monGroth} factors through $\Rex$, then the Grothendieck category $\inta F$ has all finite colimits and the induced opfibration $U_F\maps\inta F\to\A$ preserves them.
+If the corresponding pseudofunctor $\A\to\bicat{MonCat}$ given in \cref{monGroth} factors through $\Rex$, then $\inta F$ has all finite colimits and the induced opfibration $U_F\maps\inta F\to\A$ preserves them.
 \end{cor}
@@
 
-Finally, if the original pseudofunctor is in fact lax monoidal $(F,\mu,\mu_0)$, the monoidal Grothendieck construction of \cref{lem:MonGroth} in the cocartesian case expresses $\bot_a$ as follows by \cref{eq:explicitstructure1}:
+Finally, if we start with a lax monoidal pseudofunctor $(F,\phi,\phi_0)$, the monoidal Grothendieck construction of \cref{lem:MonGroth} in the cocartesian case expresses $\bot_a$ as follows by \cref{eq:explicitstructure1}:
 \begin{equation}\label{eq:initialinfibre}
-\mathbf{1}\xrightarrow{\mu_0}F(0_\A)\xrightarrow{F(u_a)}F(a) 
+\mathbf{1}\xrightarrow{\phi_0}F(0_\A)\xrightarrow{F(u_a)}F(a) 
 \end{equation}
@@
 describes the construction of the adjunction from the original $F$.
-Explicitly, the left adjoint picks the initial object in the finitely cocomplete fibre $L(a)=(a,\bot_a)$, also expressed as $F(u_a)\circ\mu_0(*)$ according to \cref{eq:initialinfibre} for $(\mu,\mu_0)$ the monoidal structure of $F$.
+Explicitly, the left adjoint picks the initial object in the finitely cocomplete fibre $L(a)=(a,\bot_a)$, also expressed as $F(u_a)\circ\\phi_0(*)$ according to \cref{eq:initialinfibre} for $(\phi,\phi_0)$ the monoidal structure of $F$.
 
@@
 as they are if both $\A$ and $\X$ have finite colimits, then this isomorphism of double categories $\mathbb{E} \maps _L \lCsp(\X) \to F\lCsp$ will be symmetric monoidal.
-First, note that we have an isomorphism $\epsilon \maps 1_{F\lCsp} \to \mathbb{E}(1_{_L \lCsp(\X)})$ and natural isomorphisms $\mu_{c_1,c_2} \maps \mathbb{E}(c_1) \otimes \mathbb{E}(c_2) \to \mathbb{E}(c_1 \otimes c_2)$ for every pair of objects $c_1,c_2 \in {_L \mathbb{C} \textnormal{sp}(\X)}$ both of which are given by identities since both double categories $_L \lCsp(\X)$ and $F\lCsp$ have $\A$ as their category of objects and $\mathbb{E}_0=\id_{\A}$.
+First, note that we have an isomorphism $\epsilon \maps 1_{F\lCsp} \to \mathbb{E}(1_{_L \lCsp(\X)})$ and natural isomorphisms $\phi_{c_1,c_2} \maps \mathbb{E}(c_1) \otimes \mathbb{E}(c_2) \to \mathbb{E}(c_1 \otimes c_2)$ for every pair of objects $c_1,c_2 \in {_L \mathbb{C} \textnormal{sp}(\X)}$ both of which are given by identities since both double categories $_L \lCsp(\X)$ and $F\lCsp$ have $\A$ as their category of objects and $\mathbb{E}_0=\id_{\A}$.
 The diagrams utilizing these maps that are required to commute do so trivially.
@@
 \]
-We then have a 2-isomorphism $\mu_{M,N} \maps E(M) \otimes E(N) \xrightarrow{\sim} E(M \otimes N)$ in $F\lCsp$ given by:
+We then have a 2-isomorphism $\phi_{M,N} \maps E(M) \otimes E(N) \xrightarrow{\sim} E(M \otimes N)$ in $F\lCsp$ given by:
 \[
@@
 Let $\OpFib(\A)$ denote the 2-subcategory of the slice 2-category $\Cat/ \A$ of opfibrations over $\A$, functors that preserve cocartesian liftings and natural transformations with vertical components.
-In fact, there is a 2-equivalence between opfibrations and pseudofunctors induced by the so-called \emph{Grothendieck construction}.
+In fact, there is a 2-equivalence between opfibrations and pseudofunctors induced by the so-called `Grothendieck construction'.
 \begin{defn}\label{def:GrothCat}

### 2020-11-20 cospans.tex
more small formatting changes

@@
 
-In \cite{MV}, the classical Grothendieck construction is generalized to the monoidal setting.  Suppose $\A$ is a monoidal category.     Then there is a bijection between:
+In \cite{MV}, the classical Grothendieck construction is generalized to the monoidal setting.  Suppose $\A$ is a monoidal category.     Then there is a bijection between the following two things:
 \begin{itemize}
-\item lax monoidal structures on a pseudofunctor $F\maps\A\to\Cat$, and
+\item lax monoidal structures on a pseudofunctor $F\maps\A\to\Cat$
 \item monoidal structures on $\inta F$ such that $U \maps \inta F \to \A$ is strict monoidal and the tensor product in $\inta F$ preserves cocartesian liftings.  
@@
 \Updownarrow \notag\\
-\textrm{monoidal opfibrations }U\maps(\X,\otimes)\to(\A,+) \label{monGroth}\\
+\textrm{monoidal opfibrations }U\maps(\X,\otimes)\to(\A,+) \notag\\
 \Updownarrow \notag\\
-\textrm{pseudofunctors }F\maps\A\to\bicat{MonCat} \notag
+\textrm{pseudofunctors } \tilde{F} \maps \A\to\bicat{MonCat} \notag
 \end{gather}
@@
  Suppose $\A$ is a finitely cocomplete category and $F\maps(\A,+)\to(\Cat,\times)$ is a lax monoidal pseudofunctor.
-If the corresponding pseudofunctor $\A\to\bicat{MonCat}$ given in \cref{monGroth} factors through $\Rex$, then $\inta F$ has all finite colimits and the induced opfibration $U_F\maps\inta F\to\A$ preserves them.
+If the corresponding pseudofunctor $\tilde{F} \maps \A\to\bicat{MonCat}$ given in \cref{lem:MonGroth} factors through $\Rex$, then $\inta F$ has all finite colimits and the induced opfibration $U\maps\inta F\to\A$ preserves them.
 \end{cor}
 
-Notice a subtlety in the above formulation: \cref{lem:MonGroth} provides a specifically induced monoidal structure on the fibres which becomes \cref{eq:explicitstructure1} in the cocartesian base case.
-If that fibrewise monoidal structure happens to itself be cocartesian, then it is necessarily isomorphic to \emph{any} other cocartesian structure on the fibres, by universal property of colimits.
-Therefore, we can simplify the above assumption to the one of the very \cref{thm:equiv} without having to specify that the structures came from monoidality of the pseudofunctor.
-However, we \emph{will} use the formulation of coproducts and initial object in terms of the monoidal structure of $F$, and that is why correspondence \cref{monGroth} is necessary.
+Notice a subtlety in the above formulation.
+\cref{lem:MonGroth} provides a specific monoidal structure on the fibres which becomes \cref{eq:explicitstructure1} when the base $\A$ is cocartesian monoidal.
+If this fibrewise monoidal structure happens to itself be cocartesian, then it is necessarily isomorphic to any other cocartesian monoidal structure on the fibres, by the universal property of colimits.
+Therefore, we can simplify the above assumption to that in \cref{thm:equiv} without having to specify that the structures came from monoidality of the pseudofunctor.
+However, we \emph{will} use the formulation of coproducts and initial object in terms of the monoidal structure of $F$, and that is why the correspondence in \cref{lem:MonGroth} is necessary.
 DOES THIS MAKE SENSE TO ALL?? %still, we ARE going to use the formation of coproducts as above. Otherwise someone might think that the monoidal Groth story was redundant here!
@@
 
-\begin{lem}\label{prop:opfibtolari}
+\begin{lem}[Gray] \label{prop:opfibtolari}
   Let $U \maps\X \to \A$ be an opfibration. Then
@@
 
-\begin{proof}\emph{(Sketch)}
+\begin{proof}
  This is \cite[Proposition~4.4]{Gray}.
@@
 
-Work in progress \cite{CV} includes a related discussion as well as a result in the opposite direction.
+%Work in progress \cite{CV} includes a related discussion as well as a result in the opposite direction.
+
 %For a discussion on the unusual strict cocontinuity condition...
@@
 
-\begin{rmk}\label{rmk:important}
 Notice that under \cref{lem:fibrewiselimits}, if the base category $\A$ has an initial object denoted $0_\A$, the above lemma is equivalent to $\X$ having an initial object $0_\X$ above $0_\A$.
@@
 \end{equation}
-\end{rmk}
 

### 2020-11-20 cospans.tex
changed \mathbb{H} to \H (again!)

@@
 %Regarding maps between symmetric monoidal double categories, consider another symmetric lax monoidal pseudofunctor $F' \maps \mathsf{A'} \to \Cat$%, we can obtain another symmetric monoidal double category $F' \lCsp$.
-%a morphism from $F\lCsp$ to $F' \lCsp$ will then be a double functor $\mathbb{H} \maps F\lCsp \to F' \lCsp$ whose object component is given by a finite colimit preserving functor $\mathbb{H}_0 = H \maps \A \to \mathsf{A'}$ and whose arrow component is given by a functor $\mathbb{H}_1$ defined on horizontal 1-cells by:
+%a morphism from $F\lCsp$ to $F' \lCsp$ will then be a double functor $\H \maps F\lCsp \to F' \lCsp$ whose object component is given by a finite colimit preserving functor $\H_0 = H \maps \A \to \mathsf{A'}$ and whose arrow component is given by a functor $\H_1$ defined on horizontal 1-cells by:
 %We define the object component $\lH_0$ to be $H$ and define the arrow component $\lH_1$ on horizontal 1-cells by:
@@
 \]
-and then the image of this 2-morphism under the double functor $\mathbb{H}$ is given by:
+and then the image of this 2-morphism under the double functor $\H$ is given by:
 and then the image of this 2-morphism under the double functor $\lH$ is given by:
@@
 \]
-On the other hand, applying the double functor $\mathbb{H}$ first gives:
+On the other hand, applying the double functor $\H$ first gives:
 On the other hand, applying the double functor $\lH$ first gives:
@@
 \]
-This double functor $\mathbb{H}$ satisfies the equations $S \mathbb{H}_1 = HS$ and $T \mathbb{H}_1=HT$.
+This double functor $\H$ satisfies the equations $S \H_1 = HS$ and $T \H_1=HT$.
 This double functor $\lH$ satisfies the equations $S \lH_1 = HS$ and $T \lH_1=HT$.
@@
 \]
-where $$d \maps 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{d_1 \times d_2} F(c_1) \times F(c_2) \xrightarrow{\phi_{c_1,c_2}} F(c_1+c_2) \xrightarrow{F(j)}F(c_1 +_b c_2).$$ The image of this horizontal 1-cell is then given by $\mathbb{H}(M \odot N)$:
+where $$d \maps 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{d_1 \times d_2} F(c_1) \times F(c_2) \xrightarrow{\phi_{c_1,c_2}} F(c_1+c_2) \xrightarrow{F(j)}F(c_1 +_b c_2).$$ The image of this horizontal 1-cell is then given by $\H(M \odot N)$:
 where $$d \maps 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{d_1 \times d_2} F(c_1) \times F(c_2) \xrightarrow{\phi_{c_1,c_2}} F(c_1+c_2) \xrightarrow{F(j)}F(c_1 +_b c_2).$$ The image of this horizontal 1-cell is then given by $\lH(M \odot N)$:
@@
 \node (C) at (4,0) {$H(a_2)$};
-\node (D) at (2,-0.5) {$\mathbb{H}(M \odot N) = \theta_{c_1 +_b c_2}E(d_{M \odot N}) \phi \in F'(H(c_1 +_b c_2))$};
+\node (D) at (2,-0.5) {$\H(M \odot N) = \theta_{c_1 +_b c_2}E(d_{M \odot N}) \phi \in F'(H(c_1 +_b c_2))$};
 \node (D) at (2,-0.5) {$\lH(M \odot N) = \theta_{c_1 +_b c_2}E(d_{M \odot N}) \phi \in F'(H(c_1 +_b c_2))$};
@@
 \]
-where $$\mathbb{H}(M \odot N) = \theta_{c_1 +_b c_2} E(d_{M \odot N}) \phi \maps 1 \xrightarrow{\phi} E(1) \xrightarrow{E(d)} E(F(c_1 +_b c_2)) \xrightarrow{\theta_{c_1 +_b c_2}} F'(H(c_1 +_b c_2)).$$ On the other hand, the image of each horizontal 1-cell under the double functor $\mathbb{H}$ is given respectively by $\mathbb{H}(M)$ and $\mathbb{H}(N)$:
+where $$\H(M \odot N) = \theta_{c_1 +_b c_2} E(d_{M \odot N}) \phi \maps 1 \xrightarrow{\phi} E(1) \xrightarrow{E(d)} E(F(c_1 +_b c_2)) \xrightarrow{\theta_{c_1 +_b c_2}} F'(H(c_1 +_b c_2)).$$ On the other hand, the image of each horizontal 1-cell under the double functor $\H$ is given respectively by $\H(M)$ and $\H(N)$:
 where $$\lH(M \odot N) = \theta_{c_1 +_b c_2} E(d_{M \odot N}) \phi \maps 1 \xrightarrow{\phi} E(1) \xrightarrow{E(d)} E(F(c_1 +_b c_2)) \xrightarrow{\theta_{c_1 +_b c_2}} F'(H(c_1 +_b c_2)).$$ On the other hand, the image of each horizontal 1-cell under the double functor $\lH$ is given respectively by $\lH(M)$ and $\lH(N)$:
@@
 \]
-Composing these then gives $\mathbb{H}(M) \odot \mathbb{H}(N)$:
+Composing these then gives $\H(M) \odot \H(N)$:
 Composing these then gives $\lH(M) \odot \lH(N)$:
@@
 \node (C) at (4.5,0) {$H(a_2)$};
-\node (D) at (2.25,-0.5) {$d_{\mathbb{H}(M) \odot \mathbb{H}(N)} \in F'(H(c_1) +_{H(b)} H(c_2))$};
+\node (D) at (2.25,-0.5) {$d_{\H(M) \odot \H(N)} \in F'(H(c_1) +_{H(b)} H(c_2))$};
 \node (D) at (2.25,-0.5) {$d_{\lH(M) \odot \lH(N)} \in F'(H(c_1) +_{H(b)} H(c_2))$};
@@
 \]
-where $$\hspace{-.4in}\scriptstyle{d_{\mathbb{H}(M) \odot \mathbb{H}(N)} \maps 1 \xrightarrow{(\theta_{c_1} \times \theta_{c_2})(E(d_M) \times E(d_N)) \phi} F'(H(c_1)) \times F'(H(c_2)) \xrightarrow{\Phi_{H(c_1),H(c_2)}} F'(H(c_1)+ H(c_2)) \xrightarrow{F' (J)} F'(H(c_1) +_{H(b)} H(c_2)).}$$
-We then have a comparison constraint: $$\mathbb{H}_{M,N} \maps \mathbb{H}(M) \odot \mathbb{H}(N) \xrightarrow{\sim} \mathbb{H}(M \odot N)$$given by the globular 2-isomorphism:
+where $$\hspace{-.4in}\scriptstyle{d_{\H(M) \odot \H(N)} \maps 1 \xrightarrow{(\theta_{c_1} \times \theta_{c_2})(E(d_M) \times E(d_N)) \phi} F'(H(c_1)) \times F'(H(c_2)) \xrightarrow{\Phi_{H(c_1),H(c_2)}} F'(H(c_1)+ H(c_2)) \xrightarrow{F' (J)} F'(H(c_1) +_{H(b)} H(c_2)).}$$
+We then have a comparison constraint: $$\H_{M,N} \maps \H(M) \odot \H(N) \xrightarrow{\sim} \H(M \odot N)$$given by the globular 2-isomorphism:
 where $$\hspace{-.4in}\scriptstyle{d_{\lH(M) \odot \lH(N)} \maps 1 \xrightarrow{(\theta_{c_1} \times \theta_{c_2})(E(d_M) \times E(d_N)) \phi} F'(H(c_1)) \times F'(H(c_2)) \xrightarrow{\Phi_{H(c_1),H(c_2)}} F'(H(c_1)+ H(c_2)) \xrightarrow{F' (J)} F'(H(c_1) +_{H(b)} H(c_2)).}$$
@@
 \node (D) at (2.5,-0.5) {$H(c_1 +_b c_2)$};
-\node (E) at (7.5,0.5) {$d_{\mathbb{H}(M) \odot \mathbb{H}(N)} \in F'(H(c_1)+_{H(b_1)}H(c_2))$};
-\node (F) at (7.5,-0.5) {$d_{\mathbb{H}(M \odot N)} \in F'(H(c_1 +_b c_2))$};
-\node (G) at (2.5,-1) {$\tau_{\kappa^{-1}} \maps F'(\kappa^{-1})(d_{\mathbb{H}(M) \odot \mathbb{H}(N)}) \to d_{\mathbb{H}(M \odot N)}.$};
+\node (E) at (7.5,0.5) {$d_{\H(M) \odot \H(N)} \in F'(H(c_1)+_{H(b_1)}H(c_2))$};
+\node (F) at (7.5,-0.5) {$d_{\H(M \odot N)} \in F'(H(c_1 +_b c_2))$};
+\node (G) at (2.5,-1) {$\tau_{\kappa^{-1}} \maps F'(\kappa^{-1})(d_{\H(M) \odot \H(N)}) \to d_{\H(M \odot N)}.$};
 \node (E) at (7.5,0.5) {$d_{\lH(M) \odot \lH(N)} \in F'(H(c_1)+_{H(b_1)}H(c_2))$};
@@
 The above diagram commutes by a similar argument to the one used in \cref{thm:equiv}.
-Similarly, for every object $c \in \A$, we have a unit comparison constraint $$\mathbb{H}_U \maps U_{\mathbb{H}(c)} \to \mathbb{H}(U_c)$$ given by the globular 2-isomorphism:
+Similarly, for every object $c \in \A$, we have a unit comparison constraint $$\H_U \maps U_{\H(c)} \to \H(U_c)$$ given by the globular 2-isomorphism:
 where $\kappa$ is the isomorphism $$\kappa \maps H(c_1 +_b c_2) \xrightarrow{\sim} H(c_1) +_{H(b)} H(c_2)$$ which comes from the finite colimit preserving functor $H \maps \A \to \A'$.
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$(\mathbb{H}(M) \odot \mathbb{H}(N)) \odot \mathbb{H}(P)$};
-\node (B) at (0,-0.5) {$\mathbb{H}(M \odot N) \odot \mathbb{H}(P)$};
-\node (C) at (0,-1.5) {$\mathbb{H}((M \odot N) \odot P)$};
-\node (A') at (3,0.5) {$\mathbb{H}(M) \odot (\mathbb{H}(N) \odot \mathbb{H}(P))$};
-\node (B') at (3,-0.5) {$\mathbb{H}(M) \odot \mathbb{H}(N \odot P)$};
-\node (C') at (3,-1.5) {$\mathbb{H}(M \odot (N \odot P))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[left]{$\mathbb{H}_{M,N} \odot 1$} (B)
-(B) edge node[left]{$\mathbb{H}_{M \odot N,P}$} (C)
+\node (A) at (0,0.5) {$(\H(M) \odot \H(N)) \odot \H(P)$};
+\node (B) at (0,-0.5) {$\H(M \odot N) \odot \H(P)$};
+\node (C) at (0,-1.5) {$\H((M \odot N) \odot P)$};
+\node (A') at (3,0.5) {$\H(M) \odot (\H(N) \odot \H(P))$};
+\node (B') at (3,-0.5) {$\H(M) \odot \H(N \odot P)$};
+\node (C') at (3,-1.5) {$\H(M \odot (N \odot P))$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[left]{$\H_{M,N} \odot 1$} (B)
+(B) edge node[left]{$\H_{M \odot N,P}$} (C)
 \node (A) at (0,0.5) {$(\lH(M) \odot \lH(N)) \odot \lH(P)$};
@@
 (A) edge node[above]{$a$} (A')
-(C) edge node [above] {$\mathbb{H}(a')$} (C')
-(B') edge node [right] {$\mathbb{H}_{M,N \odot P}$} (C')
-(A') edge node [right]{$1 \odot \mathbb{H}_{N,P}$} (B');
+(C) edge node [above] {$\H(a')$} (C')
+(B') edge node [right] {$\H_{M,N \odot P}$} (C')
+(A') edge node [right]{$1 \odot \H_{N,P}$} (B');
 (C) edge node [above] {$\lH(a')$} (C')
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$U_{\mathbb{H}(a)} \odot \mathbb{H}(M)$};
-\node (B) at (2.5,0) {$\mathbb{H}(U_a) \odot \mathbb{H}(M)$};
-\node (C) at (0,-1) {$\mathbb{H}(M)$};
-\node (D) at (2.5,-1) {$\mathbb{H}(U_a \odot M)$};
-\node (A') at (5,0) {$\mathbb{H}(M) \odot U_{\mathbb{H}(b)}$};
-\node (B') at (7.5,0) {$\mathbb{H}(M) \odot \mathbb{H}(U_b)$};
-\node (C') at (5,-1) {$\mathbb{H}(M)$};
-\node (D') at (7.5,-1) {$\mathbb{H}(M \odot U_b)$};
+\node (A) at (0,0) {$U_{\H(a)} \odot \H(M)$};
+\node (B) at (2.5,0) {$\H(U_a) \odot \H(M)$};
+\node (C) at (0,-1) {$\H(M)$};
+\node (D) at (2.5,-1) {$\H(U_a \odot M)$};
+\node (A') at (5,0) {$\H(M) \odot U_{\H(b)}$};
+\node (B') at (7.5,0) {$\H(M) \odot \H(U_b)$};
+\node (C') at (5,-1) {$\H(M)$};
+\node (D') at (7.5,-1) {$\H(M \odot U_b)$};
 \node (A) at (0,0) {$U_{\lH(a)} \odot \lH(M)$};
@@
 \path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$\mathbb{H}_U \odot 1$} (B)
+(A) edge node[above]{$\H_U \odot 1$} (B)
 (A) edge node[above]{$\lH_U \odot 1$} (B)
 (A) edge node[left]{$\lambda$} (C)
-(B) edge node[right]{$\mathbb{H}_{U_a,M}$} (D)
-(D) edge node[above]{$\mathbb{H}(\lambda')$} (C)
-(A') edge node[above]{$1 \odot \mathbb{H}_U$} (B')
+(B) edge node[right]{$\H_{U_a,M}$} (D)
+(D) edge node[above]{$\H(\lambda')$} (C)
+(A') edge node[above]{$1 \odot \H_U$} (B')
 (B) edge node[right]{$\lH_{U_a,M}$} (D)
@@
 (A') edge node[left]{$\rho$} (C')
-(B') edge node[right]{$\mathbb{H}_{M,U_b}$} (D')
-(D') edge node[above]{$\mathbb{H}(\rho')$} (C');
+(B') edge node[right]{$\H_{M,U_b}$} (D')
+(D') edge node[above]{$\H(\rho')$} (C');
 (B') edge node[right]{$\lH_{M,U_b}$} (D')
@@
 The diagrams involving the morphisms of decorations are similar to those in Theorem \cref{DC}.
-This shows that $\mathbb{H}=(H,E,\theta)$ is a double functor.
+This shows that $\H=(H,E,\theta)$ is a double functor.
 Next we show that this double functor is symmetric monoidal.
-First, that the object component $\mathbb{H}_0=H$ is symmetric monoidal is clear as $H \maps \A \to \A'$ preserves finite colimits.
-As for the arrow component $\mathbb{H}_1$, given two horizontal 1-cells $M_1$ and $M_2$ in $F\lCsp$:
+First, that the object component $\H_0=H$ is symmetric monoidal is clear as $H \maps \A \to \A'$ preserves finite colimits.
+As for the arrow component $\H_1$, given two horizontal 1-cells $M_1$ and $M_2$ in $F\lCsp$:
 The diagrams involving the morphisms of decorations are similar to those in Theorem \cref{DC}.
@@
 $$d_{M_1 \otimes M_2} \maps 1 \xrightarrow{d_1 \times d_2} F(c_1) \times F(c_2) \xrightarrow{\phi_{c_1,c_2}} F(c_1+c_2)$$
-and the image of this horizontal 1-cell under the double functor $\mathbb{H}$ is $\mathbb{H}(M_1 \otimes M_2)$ given by:
+and the image of this horizontal 1-cell under the double functor $\H$ is $\H(M_1 \otimes M_2)$ given by:
 and the image of this horizontal 1-cell under the double functor $\lH$ is $\lH(M_1 \otimes M_2)$ given by:
@@
 \node (C) at (4,0) {$H(b_1+b_2)$};
-\node (D) at (2,-0.5) {$d_{\mathbb{H}(M_1 \otimes M_2)} = \theta_{c_1+c_2} E(d_{M_1 \otimes M_2})\phi \in F'(H(c_1+c_2))$};
+\node (D) at (2,-0.5) {$d_{\H(M_1 \otimes M_2)} = \theta_{c_1+c_2} E(d_{M_1 \otimes M_2})\phi \in F'(H(c_1+c_2))$};
 \node (D) at (2,-0.5) {$d_{\lH(M_1 \otimes M_2)} = \theta_{c_1+c_2} E(d_{M_1 \otimes M_2})\phi \in F'(H(c_1+c_2))$};
@@
 \]
-On the other hand, the image of $M_1$ and $M_2$ is given by $\mathbb{H}(M_1)$ and $\mathbb{H}(M_2)$:
+On the other hand, the image of $M_1$ and $M_2$ is given by $\H(M_1)$ and $\H(M_2)$:
 On the other hand, the image of $M_1$ and $M_2$ is given by $\lH(M_1)$ and $\lH(M_2)$:
@@
 \node (C) at (3,0) {$H(b_1)$};
-\node (D) at (1.5,-0.5) {$d_{\mathbb{H}(M_1)} = \theta_{c_1}E(d_{M_1})\phi \in F'(H(c_1))$};
+\node (D) at (1.5,-0.5) {$d_{\H(M_1)} = \theta_{c_1}E(d_{M_1})\phi \in F'(H(c_1))$};
 \node (D) at (1.5,-0.5) {$d_{\lH(M_1)} = \theta_{c_1}E(d_{M_1})\phi \in F'(H(c_1))$};
@@
 \node (G) at (7.5,0) {$H(b_2)$};
-\node (H) at (6,-0.5) {$d_{\mathbb{H}(M_2)} = \theta_{c_2}E(d_{M_2})\phi \in F'(H(c_2))$};
+\node (H) at (6,-0.5) {$d_{\H(M_2)} = \theta_{c_2}E(d_{M_2})\phi \in F'(H(c_2))$};
 \node (H) at (6,-0.5) {$d_{\lH(M_2)} = \theta_{c_2}E(d_{M_2})\phi \in F'(H(c_2))$};
@@
 \]
-and their tensor product $\mathbb{H}(M_1) \otimes \mathbb{H}(M_2)$ is given by:
+and their tensor product $\H(M_1) \otimes \H(M_2)$ is given by:
 and their tensor product $\lH(M_1) \otimes \lH(M_2)$ is given by:
@@
 \node (C) at (5,0) {$H(b_1)+H(b_2)$};
-\node (D) at (2.5,-0.5) {$d_{\mathbb{H}(M_1) \otimes \mathbb{H}(M_2)} \in F'(H(c_1)+H(c_2))$};
+\node (D) at (2.5,-0.5) {$d_{\H(M_1) \otimes \H(M_2)} \in F'(H(c_1)+H(c_2))$};
 \node (D) at (2.5,-0.5) {$d_{\lH(M_1) \otimes \lH(M_2)} \in F'(H(c_1)+H(c_2))$};
@@
 \]
-$$\hspace{-.4in} \scriptstyle{d_{\mathbb{H}(M_1) \otimes \mathbb{H}(M_2)} \maps 1 \xrightarrow{(\phi \times \phi)(\lambda^{-1} \times \lambda^{-1})} E(1) \times E(1) \xrightarrow{(\theta_{c_1} \times \theta_{c_2})(E(d_{M_1}) \times E(d_{M_2}))} F'(H(c_1)) \times F'(H(c_2)) \xrightarrow{\Phi_{H(c_1),H(c_2)}} F' (H(c_1)+H(c_2)).}$$  We then have a natural 2-isomorphism $\mu_{M_1,M_2} \maps \mathbb{H}(M_1) \otimes \mathbb{H}(M_2) \to \mathbb{H}(M_1 \otimes M_2)$ in $F'\lCsp$ given by:
+$$\hspace{-.4in} \scriptstyle{d_{\H(M_1) \otimes \H(M_2)} \maps 1 \xrightarrow{(\phi \times \phi)(\lambda^{-1} \times \lambda^{-1})} E(1) \times E(1) \xrightarrow{(\theta_{c_1} \times \theta_{c_2})(E(d_{M_1}) \times E(d_{M_2}))} F'(H(c_1)) \times F'(H(c_2)) \xrightarrow{\Phi_{H(c_1),H(c_2)}} F' (H(c_1)+H(c_2)).}$$  We then have a natural 2-isomorphism $\mu_{M_1,M_2} \maps \H(M_1) \otimes \H(M_2) \to \H(M_1 \otimes M_2)$ in $F'\lCsp$ given by:
 $$\hspace{-.4in} \scriptstyle{d_{\lH(M_1) \otimes \lH(M_2)} \maps 1 \xrightarrow{(\phi \times \phi)(\lambda^{-1} \times \lambda^{-1})} E(1) \times E(1) \xrightarrow{(\theta_{c_1} \times \theta_{c_2})(E(d_{M_1}) \times E(d_{M_2}))} F'(H(c_1)) \times F'(H(c_2)) \xrightarrow{\Phi_{H(c_1),H(c_2)}} F' (H(c_1)+H(c_2)).}$$  We then have a natural 2-isomorphism $\mu_{M_1,M_2} \maps \lH(M_1) \otimes \lH(M_2) \to \lH(M_1 \otimes M_2)$ in $F'\lCsp$ given by:
@@
 \node (D) at (2.5,-0.5) {$H(c_1+c_2)$};
-\node (E) at (2.5,1) {$d_{\mathbb{H}(M_1) \otimes \mathbb{H}(M_2)} \in F'(H(c_1)+H(c_2))$};
-\node (F) at (2.5,-1) {$d_{\mathbb{H}(M_1 \otimes M_2)} \in F'(H(c_1+c_2))$};
+\node (E) at (2.5,1) {$d_{\H(M_1) \otimes \H(M_2)} \in F'(H(c_1)+H(c_2))$};
+\node (F) at (2.5,-1) {$d_{\H(M_1 \otimes M_2)} \in F'(H(c_1+c_2))$};
 \node (E) at (2.5,1) {$d_{\lH(M_1) \otimes \lH(M_2)} \in F'(H(c_1)+H(c_2))$};
@@
 \]
-$$\tau_\kappa \maps F'(\kappa)(d_{\mathbb{H}(M_1) \otimes \mathbb{H}(M_2)}) \to d_{\mathbb{H}(M_1 \otimes M_2)}$$
+$$\tau_\kappa \maps F'(\kappa)(d_{\H(M_1) \otimes \H(M_2)}) \to d_{\H(M_1 \otimes M_2)}$$
 $$\tau_\kappa \maps F'(\kappa)(d_{\lH(M_1) \otimes \lH(M_2)}) \to d_{\lH(M_1 \otimes M_2)}$$
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$(\mathbb{H}(M_1) \otimes \mathbb{H}(M_2)) \otimes \mathbb{H}(M_3)$};
-\node (B) at (0,-0.5) {$\mathbb{H}(M_1 \otimes M_2) \otimes \mathbb{H}(M_3)$};
-\node (C) at (0,-1.5) {$\mathbb{H}((M_1 \otimes M_2) \otimes M_3)$};
-\node (A') at (4,0.5) {$\mathbb{H}(M_1) \otimes (\mathbb{H}(M_2) \otimes \mathbb{H}(M_3))$};
-\node (B') at (4,-0.5) {$\mathbb{H}(M_1) \otimes \mathbb{H}(M_2 \otimes M_3)$};
-\node (C') at (4,-1.5) {$\mathbb{H}(M_1 \otimes (M_2 \otimes M_3))$};
+\node (A) at (0,0.5) {$(\H(M_1) \otimes \H(M_2)) \otimes \H(M_3)$};
+\node (B) at (0,-0.5) {$\H(M_1 \otimes M_2) \otimes \H(M_3)$};
+\node (C) at (0,-1.5) {$\H((M_1 \otimes M_2) \otimes M_3)$};
+\node (A') at (4,0.5) {$\H(M_1) \otimes (\H(M_2) \otimes \H(M_3))$};
+\node (B') at (4,-0.5) {$\H(M_1) \otimes \H(M_2 \otimes M_3)$};
+\node (C') at (4,-1.5) {$\H(M_1 \otimes (M_2 \otimes M_3))$};
 \node (A) at (0,0.5) {$(\lH(M_1) \otimes \lH(M_2)) \otimes \lH(M_3)$};
@@
 (A) edge node[above]{$\alpha'$} (A')
-(C) edge node [above] {$\mathbb{H}(\alpha)$} (C')
+(C) edge node [above] {$\H(\alpha)$} (C')
 (C) edge node [above] {$\lH(\alpha)$} (C')
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$F'(\alpha \kappa \kappa)(d_{(\mathbb{H}(M_1) \otimes \mathbb{H}(M_2)) \otimes \mathbb{H}(M_3)})$};
-\node (B) at (0,-0.5) {$F'(\alpha \kappa)(d_{\mathbb{H}(M_1 \otimes M_2) \otimes \mathbb{H}(M_3)})$};
-\node (C) at (0,-1.5) {$F'(\alpha)(d_{\mathbb{H}((M_1 \otimes M_2) \otimes M_3)})$};
-\node (A') at (5,0.5) {$F'(\kappa \kappa)(d_{\mathbb{H}(M_1) \otimes (\mathbb{H}(M_2) \otimes \mathbb{H}(M_3))})$};
-\node (B') at (5,-0.5) {$F'(\kappa)(d_{\mathbb{H}(M_1) \otimes \mathbb{H}(M_2 \otimes M_3)})$};
-\node (C') at (5,-1.5) {$d_{\mathbb{H}(M_1 \otimes (M_2 \otimes M_3))}$};
+\node (A) at (0,0.5) {$F'(\alpha \kappa \kappa)(d_{(\H(M_1) \otimes \H(M_2)) \otimes \H(M_3)})$};
+\node (B) at (0,-0.5) {$F'(\alpha \kappa)(d_{\H(M_1 \otimes M_2) \otimes \H(M_3)})$};
+\node (C) at (0,-1.5) {$F'(\alpha)(d_{\H((M_1 \otimes M_2) \otimes M_3)})$};
+\node (A') at (5,0.5) {$F'(\kappa \kappa)(d_{\H(M_1) \otimes (\H(M_2) \otimes \H(M_3))})$};
+\node (B') at (5,-0.5) {$F'(\kappa)(d_{\H(M_1) \otimes \H(M_2 \otimes M_3)})$};
+\node (C') at (5,-1.5) {$d_{\H(M_1 \otimes (M_2 \otimes M_3))}$};
 \node (A) at (0,0.5) {$F'(\alpha \kappa \kappa)(d_{(\lH(M_1) \otimes \lH(M_2)) \otimes \lH(M_3)})$};
@@
 \]
-where $$F'(\alpha \kappa \kappa)(d_{(\mathbb{H}(M_1) \otimes \mathbb{H}(M_2)) \otimes \mathbb{H}(M_3)}) = F'(\kappa \kappa \alpha')(d_{(\mathbb{H}(M_1) \otimes \mathbb{H}(M_2)) \otimes \mathbb{H}(M_3)})$$
+where $$F'(\alpha \kappa \kappa)(d_{(\H(M_1) \otimes \H(M_2)) \otimes \H(M_3)}) = F'(\kappa \kappa \alpha')(d_{(\H(M_1) \otimes \H(M_2)) \otimes \H(M_3)})$$
 as the corresponding hexagon for the finite colimit preserving functor $H \maps \A \to \mathsf{A'}$ commutes.
@@
 \]
-where $1_\A$ is the monoidal unit of the cocartesian category $\A$. The image of this horizontal 1-cell under $\mathbb{H}$ is given by:
+where $1_\A$ is the monoidal unit of the cocartesian category $\A$. The image of this horizontal 1-cell under $\H$ is given by:
 where $1_\A$ is the monoidal unit of the cocartesian category $\A$. The image of this horizontal 1-cell under $\lH$ is given by:
@@
 \]
-as $H$ preserves finite colimits. We then have a 2-isomorphism in $F'\lCsp$ given by: $$\mu \maps 1_{F'\lCsp_1} \to \mathbb{H}(1_{F\lCsp_1})$$ 
+as $H$ preserves finite colimits. We then have a 2-isomorphism in $F'\lCsp$ given by: $$\mu \maps 1_{F'\lCsp_1} \to \H(1_{F\lCsp_1})$$ 
 as $H$ preserves finite colimits. We then have a 2-isomorphism in $F'\lCsp$ given by: $$\mu \maps 1_{F'\lCsp_1} \to \lH(1_{F\lCsp_1})$$ 
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$1_\mathsf{A'} \otimes \mathbb{H}(M)$};
-\node (B) at (2.5,0) {$\mathbb{H}(1_\A) \otimes \mathbb{H}(M)$};
-\node (C) at (0,-1) {$\mathbb{H}(M)$};
-\node (D) at (2.5,-1) {$\mathbb{H}(1_\A \otimes M)$};
+\node (A) at (0,0) {$1_\mathsf{A'} \otimes \H(M)$};
+\node (B) at (2.5,0) {$\H(1_\A) \otimes \H(M)$};
+\node (C) at (0,-1) {$\H(M)$};
+\node (D) at (2.5,-1) {$\H(1_\A \otimes M)$};
 \node (A) at (0,0) {$1_\A' \otimes \lH(M)$};
@@
 (B) edge node[right]{$\mu_{1_\mathrm{A},M}$} (D)
-(D) edge node[above]{$\mathbb{H}(\ell')$} (C);
+(D) edge node[above]{$\H(\ell')$} (C);
 (D) edge node[above]{$\lH(\ell')$} (C);
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$F'(\ell)(d_{!_{1_\mathsf{A'}}} \otimes d_{\mathbb{H}(M)})$};
-\node (B) at (0,-0.5) {$d_{\mathbb{H}(M)}$};
-\node (A') at (4,0.5) {$F'(H(\ell') \kappa)(d_{!_{\mathbb{H}(1_\A)}}\otimes d_{\mathbb{H}(M)})$};
-\node (B') at (4,-0.5) {$F'(H(\ell'))(d_{\mathbb{H}(1_\A \otimes M)})$};
+\node (A) at (0,0.5) {$F'(\ell)(d_{!_{1_\mathsf{A'}}} \otimes d_{\H(M)})$};
+\node (B) at (0,-0.5) {$d_{\H(M)}$};
+\node (A') at (4,0.5) {$F'(H(\ell') \kappa)(d_{!_{\H(1_\A)}}\otimes d_{\H(M)})$};
+\node (B') at (4,-0.5) {$F'(H(\ell'))(d_{\H(1_\A \otimes M)})$};
 \node (A) at (0,0.5) {$F'(\ell)(d_{!_{1_\A'}} \otimes d_{\lH(M)})$};
@@
 \]
-where $$F'(\ell)(d_{!_{1_\mathsf{A'}}} \otimes d_{\mathbb{H}(M)})=F'(H(\ell')\kappa(\mu \otimes 1))(d_{!_{1_\mathsf{A'}}} \otimes d_{\mathbb{H}(M)})$$ since the corresponding square involving left unitors for the finite colimit preserving functor $H \maps \A \to \mathsf{A'}$ commutes.
+where $$F'(\ell)(d_{!_{1_\mathsf{A'}}} \otimes d_{\H(M)})=F'(H(\ell')\kappa(\mu \otimes 1))(d_{!_{1_\mathsf{A'}}} \otimes d_{\H(M)})$$ since the corresponding square involving left unitors for the finite colimit preserving functor $H \maps \A \to \mathsf{A'}$ commutes.
 The other square involving the right unitors $r$ and $r'$ is similar.
-Note that because the comparison constraints $\mu$ and $\mu_{(\_ , \_)}$ are both isomorphisms, the symmetric monoidal double functor $\mathbb{H}$ is strong.
+Note that because the comparison constraints $\mu$ and $\mu_{(\_ , \_)}$ are both isomorphisms, the symmetric monoidal double functor $\H$ is strong.
 where $$F'(\ell)(d_{!_{1_\A'}} \otimes d_{\lH(M)})=F'(H(\ell')\kappa(\mu \otimes 1))(d_{!_{1_\A'}} \otimes d_{\lH(M)})$$ since the corresponding square involving left unitors for the finite colimit preserving functor $H \maps \A \to \A'$ commutes.
@@
 Both of these double categories have $\Set$ as their categories of objects, open graphs as horizontal 1-cells and maps of open graphs as 2-morphisms.
-One can show using Theorem \cref{thm:equiv} that $_L \lCsp(\Graph)$ and $F\lCsp$ are equivalent as symmetric monoidal double categories.
+One can show using \cref{thm:equiv} that $_L \lCsp(\Graph)$ and $F\lCsp$ are equivalent as symmetric monoidal double categories.
 

### 2020-11-20 cospans.tex
fixed up Section 5.1  - again!

@@
 
-In earlier work \cite[Sec.\ 5]{BC} we explained the flaws in Fong's original construction of a category of open graphs using decorated cospans.
-We also showed how to fix them using structured cospans.
-Our new approach to decorated cospans provides another, equivalent way to fix these flaws.
-
-For us a \define{graph} will be a pair of functions $s,t\maps E \to N$ where $E$ and $N$ are arbitrary sets.
+In earlier work we explained the problems with Fong's original decorated cospan category of open graphs  \cite[Sec.\ 5]{BC}.
+We also showed how to fix these using structured cospans.
+Our new approach to decorated cospans provides another, equivalent solution to these problems.
+
+For us a \define{graph} will be a pair of functions $s,t\maps E \to N$ where $E$ and $N$ are finite sets.
 We call elements of $E$ \define{edges} and elements of $N$ \define{nodes}.
@@
 We can easily build a double category with `open graphs' as horizontal 1-cells using the machinery of structured cospans.
-Let $L \maps \Set \to \Graph$ be the functor that assigns to a set $N$ the \define{discrete graph} on $N$: the graph with no edges and $N$ as its set of vertices.
-Both $\Set$ and $\Graph$ have finite colimits, and the functor $L \maps \Set \to \Graph$ is left adjoint to the forgetful functor $R \maps \Graph \to \Set$ that assigns to a graph $G$ its underlying set of vertices $U(G)$.
-
+Let $L \maps \Fin\Set \to \Graph$ be the functor that assigns to a finite set $N$ the \define{discrete graph} on $N$: the graph with no edges and $N$ as its set of vertices.
+Both $\Set$ and $\Graph$ have finite colimits, and the functor $L \maps \Fin\Set \to \Graph$ is left adjoint to the forgetful functor $R \maps \Graph \to \Fin\Set$ that assigns to a graph $G$ its underlying set of vertices $U(G)$.
 Thus, using structured cospans and appealing to \cref{SC}, we get a symmetric monoidal double category $_L \lCsp(\Graph)$ in which:
@@
 
-In general, decorated cospans involve a pseudofunctor to $\Cat$, but in this example there is actually a functor $F \maps \Set \to \Cat$ that assigns to a set $N$ the above category $F(N)$.
-Given a function $f \maps M \to N$, we define $F(f) \maps F(M) \to F(N)$ to map any graph structure $s,t \maps E \to M$ to the graph structure $f \circ s, f \circ t \maps E \to N$.
-
-We obtain a symmetric lax monoidal functor $F \maps (\Set, +) \to (\Cat,\times)$ by equipping $F$ with suitable functors $\phi_{N,N'} \maps F(N) \times F(N') \to F(N+N')$ for every pair of sets $N$ and $N'$, and also a functor $\phi_0 \maps F(\emptyset) \to 1 \in \Set$.
+In general, decorated cospans involve a pseudofunctor to $\Cat$, but in this example there is actually an honest functor $F \maps \Set \to \Cat$ that assigns to a set $N$ the above category $F(N)$.
+Given a function $f \maps M \to N$, we define $F(f) \maps F(M) \to F(N)$ to any graph structure $s,t \maps E \to M$ to the graph structure $f s, f t \maps E \to N$.
+
+We can obtain a symmetric lax monoidal functor $F \maps (\Set, +) \to (\Cat,\times)$ by equipping $F$ with suitable functors $\phi_{N,N'} \maps F(N) \times F(N') \to F(N+N')$ for every pair of finite sets $N$ and $N'$, and also a functor $\phi_0 \maps F(\emptyset) \to 1 \in \Cat$.
 The functor $\phi_0$ is uniquely determined since $1$ is the terminal category.
-More interesting is $\phi_{N,N'}$, which is defined using disjoint union.
+More interesting is $\phi_{N,N'}$.
 This functor maps a pair of graph structures $s, t \maps E \to N$ and $s',t' \maps E' \to N'$ to the graph structure $s+s', t+t' \maps E+E' \to N+N'$.
-
-Given the symmetric lax monoidal functor $F \maps (\Set, +) \to (\Cat,\times)$, \cref{DC} gives us a symmetric monoidal double category $F\lCsp$ in which:
+In other words, it sends a pair of graph structures to their `disjoint union'.
+
+It is well-known, and easy to check, that the Grothendieck category $\inta F$ is isomorphic to the category $\Graph$.
+The other side of this observation is that the opfibration $U \maps \inta F \to \Fin\Set$ is isomorphic to the forgetful functor $R \maps \Graph \to \Fin\Set$.
+In fact one can check that $U \maps \inta F \to \Fin\Set$ and $R \maps \Graph \to \Fin\Set$ are isomorphic as symmetric monoidal opfibrations.
+
+Starting from the symmetric lax monoidal functor $F \maps (\Set, +) \to (\Cat,\times)$, \cref{DC} gives us a symmetric monoidal double category $F\lCsp$ in which:
 \begin{itemize}
@@
 We thus have two symmetric monoidal double categories: ${}_L \lCsp(\Graph)$ obtained from structured cospans and $F\lCsp$ obtained from decorated cospans.
-Both of these double categories have $\Set$ as their categories of objects, open graphs as horizontal 1-cells and maps of open graphs as 2-morphisms.
-One can show using \cref{thm:equiv} that $_L \lCsp(\Graph)$ and $F\lCsp$ are equivalent as symmetric monoidal double categories.
+Each of these double categories has $\Set$ as its category of objects, open graphs as horizontal 1-cells and maps of open graphs as 2-morphisms.
+This suggests that ${}_L \lCsp(\Graph)$  and $F\lCsp$ are isomorphic as symmetric monoidal double categories, and indeed this is true.
+This follows from \cref{thm:equiv} together with the fact that $U \maps \inta F \to \Fin\Set$ and $R \maps \Graph \to \Fin\Set$ are isomorphic as symmetric monoidal opfibrations.
 

### 2020-11-20 cospans.tex
more work on section 5

@@
 
-We can also build a double category with open graphs as horizontal 1-cells using decorated cospans.    For any finite set $N$ there is a category $F(N)$ where:
+We can also build a double category with open graphs as horizontal 1-cells using decorated cospans.    For any finite set $N$, there is a category $F(N)$ where:
 \begin{itemize}
@@
 
-We can obtain a symmetric lax monoidal functor $F \maps (\Set, +) \to (\Cat,\times)$ by equipping $F$ with suitable functors $\phi_{N,N'} \maps F(N) \times F(N') \to F(N+N')$ for every pair of finite sets $N$ and $N'$, and also a functor $\phi_0 \maps F(\emptyset) \to 1 \in \Cat$.
+We can make $F$ into a symmetric lax monoidal functor $F \maps (\Fin\Set, +) \to (\Cat,\times)$ by equipping it with suitable functors 
+\[   \phi_{N,N'} \maps F(N) \times F(N') \to F(N+N'), \qquad \phi_0 \maps F(\emptyset) \to 1 \in \Cat. \]  
 The functor $\phi_0$ is uniquely determined since $1$ is the terminal category.
@@
 The other side of this observation is that the opfibration $U \maps \inta F \to \Fin\Set$ is isomorphic to the forgetful functor $R \maps \Graph \to \Fin\Set$.
-In fact one can check that $U \maps \inta F \to \Fin\Set$ and $R \maps \Graph \to \Fin\Set$ are isomorphic as symmetric monoidal opfibrations.
-
-Starting from the symmetric lax monoidal functor $F \maps (\Set, +) \to (\Cat,\times)$, \cref{DC} gives us a symmetric monoidal double category $F\lCsp$ in which:
+In fact one can check that $U \maps \inta F \to \Fin\Set$ and $R \maps \Graph \to \Fin\Set$ are isomorphic as symmetric monoidal opfibrations, where all the categories involved are given cocartesian monoidal structures.
+
+Starting from the symmetric lax monoidal functor $F \maps (\Fin\Set, +) \to (\Cat,\times)$, \cref{DC} gives us a symmetric monoidal double category $F\lCsp$ in which:
 \begin{itemize}
@@
 We thus have two symmetric monoidal double categories: ${}_L \lCsp(\Graph)$ obtained from structured cospans and $F\lCsp$ obtained from decorated cospans.
-Each of these double categories has $\Set$ as its category of objects, open graphs as horizontal 1-cells and maps of open graphs as 2-morphisms.
-This suggests that ${}_L \lCsp(\Graph)$  and $F\lCsp$ are isomorphic as symmetric monoidal double categories, and indeed this is true.
+Each of these double categories has $\Set$ as its category of objects, open graphs as horizontal 1-cells, and maps of open graphs as 2-morphisms.
+This suggests that ${}_L \lCsp(\Graph)$  and $F\lCsp$ are isomorphic as symmetric monoidal double categories---and indeed this is true.
 This follows from \cref{thm:equiv} together with the fact that $U \maps \inta F \to \Fin\Set$ and $R \maps \Graph \to \Fin\Set$ are isomorphic as symmetric monoidal opfibrations.
@@
 
-Building on work with Fong \cite{BF}, Coya, Rebro and the first author used structured
-cospans to describe electrical circuits with inputs and outputs \cite{BCR}.
-The key idea is to use graphs with labeled edges.
-The edge labels can stand for resistors with any chosen resistance, capacitors with any chosen capacitance, inductors with any chosen inductance, or other circuit elements.
-To study such circuits quite generally we start by fixing any set $\La$ to serve as edge labels.
-
-\begin{defn}
-Given a set $\La$ of \define{labels}, an $\La$-\define{graph} is a graph $s,t\maps E\to N$
- equipped with a function $\ell \maps E \to \La$.
- A \define{morphism} from the $\La$-graph 
+We can also use structured or decorated cospans to describe electrical circuits \cite{BC,BCR,BF}.
+The key idea is to use graphs with labeled edges, where the labels can stand for resistors with any chosen resistance, capacitors with any chosen capacitance, or other circuit elements.
+The whole theory of open graphs discussed in the previous section can be recapitulated for labeled graphs.
+Since everything works the same way, we can be brief.
+
+Fix a set $\La$ to serve as edge labels.
+Define an $\La$-\define{graph} to be a graph $s,t\maps E\to N$ equipped with a function $\ell \maps E \to \La$.
+There is a category $\Graph_\La$ with $\La$-graphs as objects, where a morphism from the $\La$-graph
  \[ \xymatrix{\La & E \ar@<2.5pt>[r]^{s} \ar@<-2.5pt>[r]_{t} \ar[l]_{\ell} & N} \]
@@
 \]
-\end{defn}
-
-\begin{defn}
-\label{defn:Lgraph}
-We define $\Graph_\La$ to be the category of $\La$-graphs and morphisms between them, with composition given by
-\[  (f, g) \circ (f',g') = (f \circ f' , g \circ g')  .\]
-\end{defn}
-
-When $\La = 1$, an $\La$-graph reduces to a graph and $\Graph_\La$ reduces
-to the category $\Graph$ discussed in \cref{subsec:graphs}.  We now generalize the key
-ideas of that section from graphs to $\La$-graphs.   Everything works the same way, 
-but following previous work \cite{BCR} we call an open $\La$-graph an $\La$-\define{circuit}.
-
-There is a functor $U \maps \Graph_\La \to \Fin\Set$ that takes an $\La$-graph to its underlying set of nodes. This has a left adjoint $L \maps \Fin\Set \to \Graph_\La$ sending
-any set to the $\La$-graph with that set of nodes and no edges.
+There is a functor $U \maps \Graph_\La \to \Fin\Set$ that takes an $\La$-graph to its underlying set of nodes.
+This has a left adjoint $L \maps \Fin\Set \to \Graph_\La$ sending any set to the $\La$-graph with that set of nodes and no edges.
 Both $\Fin\Set$ and $\Graph_\La$ have colimits, and $L$ preserves them.
-Thus \cref{SC} gives us a symmetric monoidal double category ${}_L \lCsp(\Graph_\La)$ where:
-\begin{itemize}
-\item an object is a finite set,
-\item a morphism is an isomorphism class of $\La$-circuits, where an
-$\La$-\define{circuit} is a cospan in $\Graph_\La$ of this form:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$L(S)$};
+
+This sets the stage for structured cospans: \cref{SC} gives us a symmetric monoidal double category ${}_L \lCsp(\Graph_\La)$ where a horizontal 1-cell is an \define{open $\La$-graph}, also called an \define{$\La$-circuit}: that is, a cospan in $\Graph_\La$ of this form:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$L(X)$};
 \node (B) at (1,0) {$G$};
-\node (C) at (2,0) {$L(T)$,};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above,left]{$$} (B)
-(C)edge node[above]{$$}(B);
-\end{tikzpicture}
-\]
-and an \define{isomorphism} of $\La$-circuits is a commutative diagram in $\Graph_\La$ 
-of this form:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (E) at (3,-0.5) {$L(S)$};
-\node (F) at (5,-0.5) {$L(T)$};
-\node (G) at (4,0) {$G$};
-\node (G') at (4,-1) {$G'$};
-\path[->,font=\scriptsize,>=angle 90]
-(F) edge node[above]{$o$} (G)
-(G) edge node[left]{$h$} (G')
-(E) edge node[above]{$i$} (G)
-(E) edge node[below]{$i'$} (G')
-(F) edge node[below]{$o'$} (G');
-\end{tikzpicture}
-\]
-where $h$ is an isomorphism.
-\end{itemize} 
-This category has a nice universal property, found by Rosebrugh, Sabadini and
-Walters \cite{RSW}.  To state this, it is convenient to use the language of props.
-% Replaced strict symmetric with symmetric strict three times below
-Recall that a \define{prop} is a symmetric strict monoidal category whose objects are natural
-numbers, with tensor product of objects given by addition.
-An \define{algebra} of a prop $\T$ in a symmetric strict monoidal category $\C$ is a symmetric strict monoidal functor $A \maps \T \to \C$.
-A \define{morphism} from the algebra $A \maps \T \to \C$ to the algebra
-$A' \maps \T \to \C$ is a monoidal natural transformation $\alpha \maps A \To A'$.
-
-\begin{lem} As a symmetric monoidal category, ${}_L \Csp(\Graph_\La)$ is equivalent to a prop $\Circ_\La$.    
-\end{lem}
-
-\begin{proof}
-This is \cite[Proposition 4.3]{BCR}.
-\end{proof}
-
-\begin{prop} 
-\label{prop:LCirc_algebra}
-An algebra of $\Circ_\La$ in a symmetric strict monoidal category $\C$ is a 
-special commutative Frobenius monoid in $\C$ whose underlying object $x$ is equipped
-with an endomorphism $\ell \maps x \to x$ for each element $\ell \in \La$. 
-A morphism of algebras of $\Circ_\La$ in $\C$ is a morphism of special commutative Frobenius monoids that also preserves all these endomorphisms.
-\end{prop}
-
-\begin{proof}
-This was proved by Rosebrugh, Sabadini and Walters \cite{RSW}, and appears
-in the above form in \cite[Proposition 7.2]{BCR}.  
-\end{proof}
-
-In applications to circuits, the morphisms $\ell \maps x \to x$ describe different
-circuit elements, while the special commutative Frobenius monoid structure is used to split and join wires.
-This framework is used to study a wide variety of electrical circuits in a paper with Coya and Rebro \cite{BCR}, so the reader can turn there for details.
-To illustrate the ideas let us consider circuits of resistors, where a label in $\La = (0,\infty)$ serves to indicate the resistance of a resistor.
-In this case a typical morphism from $1$ to $3$ in
-$\Circ_\La$ looks like this:
+\node (C) at (2,0) {$L(Y)$.};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i$} (B)
+(C) edge node[above]{$o$} (B);
+\end{tikzpicture}
+\]
+For example, here is a $\La$-circuit with $\La = (0,\infty)$:
 \[
@@
 		\draw [style=inarrow] (n2) to (n3);
-%		\draw [style=inarrow] (W) to (Water);
-%		\draw [style=inarrow, bend left=40, looseness=1.00] (Water2) to (Something);
-%		\draw [style=inarrow, bend right=40, looseness=1.00] (Water2) to (Something);
-%		\draw [style=inarrow, bend left=40, looseness=1.00] (Something) to (A);
-%		\draw [style=inarrow, bend right=40, looseness=1.00] (Something) to (B);
 		\draw [style=simple] (ATL.center) to (ATR.center);
@@
 		\draw [style=simple] (ABL.center) to (ATL.center);
-%		\draw [style=simple] (BTL.center) to (BTR.center);
-%		\draw [style=simple] (BTR.center) to (BBR.center);
-%		\draw [style=simple] (BBR.center) to (BBL.center);
-%		\draw [style=simple] (BBL.center) to (BTL.center);
 		\draw [style=simple] (MTL.center) to (MTR.center);
@@
 		\draw [style=simple] (MBL.center) to (MTL.center);
-%		\draw [style=inputarrow] (outI) to (A);
-%		\draw [style=inputarrow] (outS) to (B);
 		\draw [style=inputarrow] (inI) to (n1);
@@
 		\draw [style=inputarrow] (outI''') to (n5);
-%		\draw [style=inputarrow] (inI') to (Water2);
-%		\draw [style=inputarrow] (inS') to (Water2);
 	\end{pgfonlayer}
@@
 \]
-The edges here represent wires, and the positive real numbers labeling them describe
-the resistance of the resistor on each wire.
+The edges here can represent wires, with the positive real numbers labeling them serving to describe the resistance of a resistor on each wire.
 The points in the boxes represent `terminals': that is, points where we allow ourselves to attach a wire from another circuit.
-The points in the left box are called `inputs' and the points in the right box are called `outputs'.
-In electrical engineering we associate two real numbers to each terminal, called `potential' and `current'.
-Any circuit of resistors imposes a specific relation between the potentials and currents at its inputs and those at its outputs.
-All these relations, for all circuits of resistors, can be described using a single functor as follows.
-
-There is a symmetric monoidal category $\Fin\Rel_\R$ where the objects are finite-dimensional real vector spaces and a morphism from $V$ to $W$ is a \define{linear relation} from $V$ to $W$: that is, a relation $L \subseteq V \times W$ that is a linear subspace of $V \times W$.
-Composition in $\Fin\Rel_\R$ is the usual composition of relations, and the symmetric monoidal structure is provided by direct sum.
-
-There is a symmetric monoidal functor
-\[   \blacksquare \maps \Circ_\La \to \Fin\Rel_\R  \]
-% Added the line "sending any finite set $S$ to the vector space 
-% $\mathbb{R}^S \oplus \mathbb{R}^S$ and" to say what the black-box functor does on objects
-% Changed Prop. to Proposition 
-sending any finite set $S$ to the vector space $\R^S \oplus \R^S$ and
-sending any circuit of resistors to the relation it imposes between the potentials and currents at its inputs and those at its outputs \cite[Section 9]{BCR}.
-We can construct this using Proposition \ref{prop:LCirc_algebra}, by choosing a special commutative Frobenius monoid in $\Fin\Rel_\R$ whose underlying object is equipped with an endomorphism for each resistance $R \in (0,\infty)$.
-The object $\R^2 \in \Fin\Rel_\R$ is a special commutative Frobenius monoid in a standard way \cite[Section\ 8]{BCR}, so we choose this one.
-To define $\blacksquare \maps \Circ_\La \to \Fin\Rel_\R$ it then suffices to choose for each $R \in (0,\infty)$ a linear relation from $\R^2$ to itself.
-We use this:
-\[ \left\{(\phi_1,I_1,\phi_2,I_2) : \; I_1 = I_2 , \; \phi_2-\phi_1 = R I_1\right\} 
- \subseteq \R^2 \oplus \R^2.\]
-This expresses two laws of electrical engineering.   Kirchhoff's current law says that the 
-current flowing into a wire equals the current flowing out: $I_1 = I_2$.
-Ohm's law says that the voltage across a wire with a resistor on it, $\phi_2 - \phi_1$, is equal to the current flowing through the wire times the resistance $R$ of that resistor.
-
-\begin{comment}
-
-In a previous work \cite{BP}, Fong and the first author used decorated cospans to construct a symmetric monoidal category of `open passive linear circuits'.
-Roughly speaking, given a field $k$, a passive linear circuit is given by a `$k$-graph' which is a diagram in $\mathsf{FinSet}$ of the form:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (B) at (1,0) {$E$};
-\node (C) at (2,0) {$V$};
-\node (A) at (0,0) {$k^+$};
-\path[->,font=\scriptsize,>=angle 90]
-(B)edge node[above] {$r$}(A)
+
+We can also describe $\La$-circuits using decorated cospans.
+There is a symmetric lax monoidal functor $F \maps (\Fin\Set, +) \to (\Cat, \times)$ such that for any finite set $N$, the category $F(N)$ has:
+\begin{itemize}
+\item objects being \define{$\La$-graph structures} on $N$: that is, $\La$-graphs where the set of nodes is $N$,
+\item morphisms are morphisms of $\La$-graphs that are the identity on the set of nodes.
+\end{itemize}
+This gives a symmetric monoidal double category $F \lCsp$, and using \cref{thm:equiv} we can show that this is equivalent, as a symmetric monoidal double category, to ${}_L \lCsp(\Graph_\La)$.
+
+\subsection{Petri nets}
+In a previous work, Master and the first author used structured cospans to obtain a symmetric monoidal double category of `open Petri nets' \cite{BM}.
+A Petri net is given by a diagram in $\Set$ of the form:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (B) at (1,0) {$T$};
+\node (C) at (2,0) {$\mathbb{N}[S].$};
+\path[->,font=\scriptsize,>=angle 90]
 (B)edge[bend left] node[above]{$s$}(C)
@@
 \]
-Here the finite sets $E$ and $V$ are the sets of edges and vertices, respectively, and if we take the field $k = \mathbb{R}$, the function $r \maps E \to \mathbb{R}^+$ assigns to each edge $e \in E$ a positive real number $r(e) \in \mathbb{R}^+$ which can be interpreted as the resistance at the edge $e$.
-An open passive linear circuit is then given by a cospan of finite sets
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (B) at (1,0) {$V$};
-\node (C) at (2,0) {$Y$};
-\node (A) at (0,0) {$X$};
-\path[->,font=\scriptsize,>=angle 90]
-(A)edge node[above] {$i$}(B)
-(C)edge node[above]{$o$}(B);
-\end{tikzpicture}
-\]
-where the apex $V$ is equipped with the structure of a passive linear circuit. See the original paper for more details \cite{BP}.
-
-Let $\Graph_k$ be the category whose objects are given by $k$-graphs and morphisms by morphisms of $k$-graphs, where a morphism of $k$-graphs is given by a pair of functions $f \maps E \to E'$ and $g \maps V \to V'$ between the edge sets and vertex sets, respectively, of two $k$-graphs that respect the source and target functions of each.
-In a previous work introducing structured cospans, the first two authors showed that the category $\Graph_k$ has finite colimits \cite{BC2}.
-We can then obtain a double category of open passive linear circuits by defining a left adjoint $L \maps \Set \to \Graph_k$ that assigns to a set $V$ the discrete passive linear circuit $L(V)$ given by passive linear circuit with $V$ as its set of vertices and no edges.
-The resulting symmetric monoidal double category $_L \lCsp(\Graph_k)$ has:
-\begin{enumerate}
-\item{finite sets as objects,}
-\item{functions as vertical 1-morphisms,}
-\item{open passive linear circuits as horizontal 1-cells
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (B) at (1,0) {$V$};
-\node (C) at (2,0) {$Y$};
-\node (A) at (0,0) {$X$};
-\node (D) at (3,0) {$k^+$};
-\node (E) at (4,0) {$E$};
-\node (F) at (5,0) {$V$};
-\path[->,font=\scriptsize,>=angle 90]
-(E) edge node [above] {$r$} (D)
-(E) edge [bend left] node [above] {$s$} (F)
-(E) edge [bend right] node [below] {$t$} (F)
-(A)edge node[above] {$i$}(B)
-(C)edge node[above]{$o$}(B);
-\end{tikzpicture}
-\]
-and}
-\item{maps of cospans as 2-morphisms together with a map of passive linear circuits between the apices.
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$X_1$};
-\node (A') at (0,-1) {$X_2$};
-\node (C') at (2,-1) {$Y_2$};
-\node (B) at (1,0) {$V_1$};
-\node (C) at (2,0) {$Y_1$};
-\node (D) at (1,-1) {$V_2$};
-\node (E) at (3,0) {$k^+$};
-\node (E') at (3,-1) {$k^+$};
-\node (F) at (4,0) {$E_1$};
-\node (F') at (4,-1) {$E_2$};
-\node (G) at (5,0) {$V_1$};
-\node (G') at (5,-1) {$V_2$};
-\path[->,font=\scriptsize,>=angle 90]
-(F) edge node[above] {$r_1$} (E)
-(F) edge [bend left] node [above] {$s_1$} (G)
-(F) edge [bend right] node [below] {$t_1$} (G)
-(F') edge node[above] {$r_2$} (E')
-(F') edge [bend left] node [above] {$s_2$} (G')
-(F') edge [bend right] node [below] {$t_2$} (G')
-(A) edge node[above]{$i_1$} (B)
-(C) edge node[above]{$o_1$} (B)
-(A) edge node[left]{$h$} (A')
-(C) edge node[left]{$h'$} (C')
-(C') edge node [above] {$o_2$} (D)
-(A') edge node [above] {$i_2$} (D)
-(B) edge node [left] {$g$} (D)
-(F) edge node [left] {$f$} (F')
-(G) edge node [right] {$g$} (G');
-\end{tikzpicture}
-\]
-}
-\end{enumerate}
-We can also obtain a similar double category using decorated cospans: define a pseudofunctor $F \maps \mathsf{FinSet} \to \Cat$ that assigns to a finite set $V$ the category of all $k$-graph structures on the finite set $V$ and to a function $f \maps V \to V'$ the corresponding functor $F(f) \maps F(V) \to F(V')$ between decoration categories.
-Both categories $\mathsf{FinSet}$ and $\Cat$ are symmetric monoidal and the pseudofunctor $F \maps \mathsf{FinSet} \to \Cat$ is symmetric lax monoidal, as given a $k$-graph structure on a finite set $V_1$ denoted by an element $K_1 \in F(V_1)$ and a $k$-graph structure on a finite set $V_2$ denoted by an element $K_2 \in F(V_2)$, we can consider the $k$-graph structures simultaneously as a single graph structure $\phi_{V_1,V_2}(K_1,K_2)$ on the finite set $V_1+V_2$.
-Thus we get a family of natural transformations $$\phi_{V_1,V_2} \maps F(V_1) \times F(V_2) \to F(V_1+V_2)$$ as well as a morphism $\phi \maps 1_{\Graph_k} \to F(\emptyset)$ which together satisfy the coherence conditions of a monoidal functor.
-The braiding is also clear as the following diagram commutes:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (E) at (3,0) {$F(V_1) \times F(V_2)$};
-\node (G) at (5,0) {$F(V_2) \times F(V_1)$};
-\node (E') at (3,-1) {$F(V_1+V_2)$};
-\node (G') at (5,-1) {$F(V_2+V_1)$};
-\path[->,font=\scriptsize,>=angle 90]
-(E) edge node[left]{$\phi_{V_1,V_2}$} (E')
-(G) edge node[right]{$\phi_{V_2,V_1}$} (G')
-(E) edge node[above]{$\beta_{V_1,V_2}$} (G)
-(E') edge node[above]{$F(\beta_{V_1,V_2})$} (G');
-\end{tikzpicture}
-\]
-Thus the pseudofunctor $F$ is symmetric lax monoidal and so by Theorem \cref{DC} we get a symmetric monoidal double category $F\lCsp$ which has:
-\begin{enumerate}
-\item{objects as finite sets,}
-\item{vertical 1-morphisms as functions,}
-\item{horizontal 1-cells as cospans of finite sets together with the structure of a $k$-graph given by an element of the image of the apex under the pseudofunctor $F$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (D) at (-3,0) {$U$};
-\node (E) at (-2,0) {$V$};
-\node (F) at (-1,0) {$W$};
-\node (A) at (0,0) {$K \in F(V)$};
-\path[->,font=\scriptsize,>=angle 90]
-(D) edge node [above] {$i$} (E)
-(F) edge node [above] {$o$} (E);
-\end{tikzpicture}
-\]
-and}
-\item{2-morphisms as maps of cospans of finite sets 
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (E) at (3,0) {$U_1$};
-\node (F) at (5,0) {$W_1$};
-\node (G) at (4,0) {$V_1$};
-\node (E') at (3,-1) {$U_2$};
-\node (F') at (5,-1) {$W_2$};
-\node (G') at (4,-1) {$V_2$};
-\node (A) at (6,0) {$K_1 \in F(V_1)$};
-\node (B) at (6,-1) {$K_2 \in F(V_2)$};
-\path[->,font=\scriptsize,>=angle 90]
-(F) edge node[above]{$o_1$} (G)
-(E) edge node[left]{$f$} (E')
-(F) edge node[right]{$g$} (F')
-(G) edge node[left]{$h$} (G')
-(E) edge node[above]{$i_1$} (G)
-(E') edge node[above]{$i_2$} (G')
-(F') edge node[above]{$o_2$} (G');
-\end{tikzpicture}
-\]
-together with a morphism of $k$-graphs $\tau \maps F(h)(K_1) \to K_2$ in $F(V_2)$.}
-\end{enumerate}
-These two double categories $_L \lCsp(\Graph_k)$ and $F\lCsp$ are equivalent by Theorem \cref{thm:equiv}.
-
-\subsection{Markov processes}
-In another previous work \cite{BFP}, Fong, Pollard and the first author used decorated cospans to construct a symmetric monoidal category of `open Markov processes'.
-In this framework, a Markov process on a finite set $N$ is given by a diagram in $\Set$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (D) at (3,0) {$(0,\infty)$};
-\node (E) at (4,0) {$E$};
-\node (F) at (5,0) {$N$};
-\path[->,font=\scriptsize,>=angle 90]
-(E) edge node [above] {$r$} (D)
-(E) edge [bend left] node [above] {$s$} (F)
-(E) edge [bend right] node [below] {$t$} (F);
-\end{tikzpicture}
-\]
-where $E$ and $N$ are finite sets of edges and nodes, respectively.
-This is really just a special case of the previous example of passive linear circuits with $k = \mathbb{R}$.
-An open Markov process is then of course a cospan of finite sets where the apex is equipped with a Markov process:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (B) at (1,0) {$N$};
-\node (C) at (2,0) {$Y$};
-\node (A) at (0,0) {$X$};
-\node (D) at (3,0) {$(0,\infty)$};
-\node (E) at (4,0) {$E$};
-\node (F) at (5,0) {$N$};
-\path[->,font=\scriptsize,>=angle 90]
-(E) edge node [above] {$r$} (D)
-(E) edge [bend left] node [above] {$s$} (F)
-(E) edge [bend right] node [below] {$t$} (F)
-(A)edge node[above] {$i$}(B)
-(C)edge node[above]{$o$}(B);
-\end{tikzpicture}
-\]
-For example:
-\[
-\begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=3.7cm,
-thick,main node/.style={circle,fill=white!20,draw,font=\sffamily\Large\bfseries},terminal/.style={circle,fill=blue!20,draw,font=\sffamily\Large\bfseries}]]
-\node[main node](1) {$b_1$};
-\node[main node](2) [left=0.8cm of 1] {$a_1$};.5
-\node[main node](3) [below right=0.7cm and 2.4cm of 1] {$c_2$};
-\node[main node](5) [above right=0.7cm and 2.4cm of 1] {$c_1$};
-\node[main node](4) [above right=0.7cm and 2.4cm of 3] {$d_1$};
-\node(A) [left=1cm of 2,circle,draw,inner sep=1pt,fill=gray,color=purple] {};
-\node(C) [right=1cm of 4,circle,draw,inner sep=1pt,fill=gray,color=purple] {};
-\node[left=1.25 cm of 2,color=purple] {$S$};
-\node[right=1.25 cm of 4,color=purple] {$T$};
-\path[every node/.style={font=\sffamily\small}, shorten >=1pt]
-(3) edge [bend right =15] node[below] {$e_6$} (4)
-(5) edge [bend left =15] node[below] {$e_5$} (4)
-(2) edge [bend left=15] node[below] {$e_1$} (1)
-(1) edge [bend left =15] node[below] {$e_2$} (5)
-(5) edge [bend right =15] node[right] {$e_4$} (3)
-(1) edge [bend right =15] node[below] {$e_3$} (3)
-(3) edge [bend right =15] node[above] {$6$} (4)
-(5) edge [bend left =15] node[above] {$6$} (4)
-(2) edge [bend left=15] node[above] {$5$} (1)
-(1) edge [bend left =15] node[above] {$8$} (5)
-(5) edge [bend right =15] node[left] {$4$} (3)
-(1) edge [bend right =15] node[above] {$8$} (3);
-\path[color=purple, very thick, shorten >=10pt, ->, >=stealth] (C) edge (4);
-\path[color=purple, very thick, shorten >=10pt, ->, >=stealth] (A) edge (2);
-\end{tikzpicture}
-\]
-Here we have an open Markov process on the finite set $N = \{a_1,b_1,c_1,c_2,d_1 \}$ with input and output sets given by the singletons $S$ and $T$, respectively.
-
-Fong, Pollard and the first author then add extra structure to open Markov processes such as populations at each node to obtain a symmetric monoidal category $\mathsf{DetlBalMark}$ of open Markov processes in `detailed balance' and then construct a black box functor $\blacksquare \maps \mathsf{DetBalMark} \to \mathsf{LinRel}$ that describes the steady state behavior of an open Markov process in detailed balance.
-On the way to doing this, one of the categories they construct using Fong's decorated cospan machinery is a symmetric monoidal category $\mathsf{Mark}$ which has:
-\begin{enumerate}
-\item{objects as finite sets and}
-\item{morphisms as isomorphism classes of open Markov processes, where composition is by pushout.}
-\end{enumerate}
-This is done using a symmetric lax monoidal functor $F \maps \mathsf{FinSet} \to \Set$ which assigns to each finite set $N$ the (large) set of all Markov processes on $N$ as defined above.
-Viewing this functor $F$ as now a symmetric lax monoidal pseudofunctor $F \maps \mathsf{FinSet} \to \Cat$ that assigns to a finite set $N$ the \emph{category} $F(N)$ of all Markov processes on $N$, we then get by Theorem \cref{DC} a symmetric monoidal double category $F\lCsp$ which has:
-\begin{enumerate}
-\item{finite sets as objects,}
-\item{functions as vertical 1-morphisms,}
-\item{open Markov processes as horizontal 1-cells, and}
-\item{maps of open Markov processes as 2-morphisms which are given by maps of cospans of finite sets:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$X_1$};
-\node (A') at (0,-1) {$X_2$};
-\node (C') at (2,-1) {$Y_2$};
-\node (B) at (1,0) {$N_1$};
-\node (C) at (2,0) {$Y_1$};
-\node (D) at (1,-1) {$N_2$};
-\node (E) at (3,0) {$M_1 \in F(N_1)$};
-\node (E') at (3,-1) {$M_2 \in F(N_2)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i_1$} (B)
-(C) edge node[above]{$o_1$} (B)
-(A) edge node[left]{$f$} (A')
-(C) edge node[left]{$f'$} (C')
-(C') edge node [above] {$o_2$} (D)
-(A') edge node [above] {$i_2$} (D)
-(B) edge node [left] {$h$} (D);
-\end{tikzpicture}
-\]
-together with a map of Markov processes $\tau \maps F(h)(M_1) \to M_2$ in $F(N_2)$, where a map between two Markov processes to be given by a pair of functions $(g,h)$ that make the following diagram commute:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (E) at (3,0) {$(0,\infty)$};
-\node (E') at (3,-1) {$(0,\infty)$};
-\node (F) at (4,0) {$E_1$};
-\node (F') at (4,-1) {$E_2$};
-\node (G) at (5,0) {$N_1$};
-\node (G') at (5,-1) {$N_2$};
-\path[->,font=\scriptsize,>=angle 90]
-(F) edge node[above] {$r_1$} (E)
-(F) edge [bend left] node [above] {$s_1$} (G)
-(F) edge [bend right] node [below] {$t_1$} (G)
-(F') edge node[above] {$r_2$} (E')
-(F') edge [bend left] node [above] {$s_2$} (G')
-(F') edge [bend right] node [below] {$t_2$} (G')
-(F) edge node [left] {$g$} (F')
-(G) edge node [right] {$h$} (G');
-\end{tikzpicture}
-\]
-}
-\end{enumerate}
-A symmetric monoidal double category of open Markov processes can also be obtained using structured cospans by defining a functor $L \maps \mathsf{FinSet} \to \mathsf{Mark}$ which assigns to a finite set $N$ the discrete Markov process $L(N)$ with no edges and to a function $f \maps N \to N'$ the induced map of discrete Markov processes.
-Both categories $\mathsf{FinSet}$ and $\mathsf{Mark}$ have finite colimits and the functor $L$ is left adjoint to the forgetful functor $R \maps \mathsf{Mark} \to \mathsf{FinSet}$ which maps a Markov process to its underlying finite set of states.
-By Theorem \cref{SC}, we get a symmetric monoidal double category $_L \lCsp(\mathsf{Mark})$ which has:
-\begin{enumerate}
-\item{objects as finite sets,}
-\item{vertical 1-morphisms as functions,}
-\item{horizontal 1-cells as cospans in $\mathrm{Mark}$ of the form:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (D) at (-3,0) {$L(N_1)$};
-\node (E) at (-2,0) {$M$};
-\node (F) at (-1,0) {$L(N_2)$};
-\path[->,font=\scriptsize,>=angle 90]
-(D) edge node [above] {$I$} (E)
-(F) edge node [above] {$O$} (E);
-\end{tikzpicture}
-\]
-and}
-\item{2-morphisms as maps of cospans in $\mathrm{Mark}$.
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (E) at (3,0) {$L(N_1)$};
-\node (F) at (5,0) {$L(N_2)$};
-\node (G) at (4,0) {$M$};
-\node (E') at (3,-1) {$L(N_1')$};
-\node (F') at (5,-1) {$L(N_2')$};
-\node (G') at (4,-1) {$M'$};
-\path[->,font=\scriptsize,>=angle 90]
-(F) edge node[above]{$O$} (G)
-(E) edge node[left]{$L(f_1)$} (E')
-(F) edge node[right]{$L(f_2)$} (F')
-(G) edge node[left]{$(g,h)$} (G')
-(E) edge node[above]{$I$} (G)
-(E') edge node[above]{$I'$} (G')
-(F') edge node[above]{$O'$} (G');
-\end{tikzpicture}
-\]
-}
-\end{enumerate}
-The two double categories $F\lCsp$ and $_L \mathbb{C} \textnormal{sp}(\mathsf{Mark})$ are equivalent by Theorem \cref{thm:equiv}.
-
-In a more recent work \cite{BC}, the first two authors have constructed a symmetric monoidal double category of `open Markov processes' and `coarse-grainings', where roughly speaking, a coarse-graining is a way of approximating a larger open Markov process by a smaller one by partitioning the set of states into `lumps'.
-This construction uses neither decorated cospans nor structured cospans.
-
-\subsection{Petri nets}
-In a previous work, Master and the first author used structured cospans to obtain a symmetric monoidal double category of `open Petri nets'. A Petri net is given by a diagram in $\Set$ of the form:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (B) at (1,0) {$T$};
-\node (C) at (2,0) {$\mathbb{N}[S].$};
-\path[->,font=\scriptsize,>=angle 90]
-(B)edge[bend left] node[above]{$s$}(C)
-(B)edge[bend right] node[below]{$t$}(C);
-\end{tikzpicture}
-\]
-Here, $T$ is the set of \emph{transitions} and $S$ is the set of \emph{species}, and then $\mathbb{N}[S]$ is the free commutative monoid on the set $S$.
+Here $S$ is the set of \define{places}, $T$ is the set of \define{transitions}, and $\mathbb{N}[S]$ is the underlying set of the free commutative monoid on $S$.
 Each transition then has a formal linear combination of species given by an element of $\mathbb{N}[S]$ as its source and target as prescribed by the functions $s$ and $t$, respectively.
@@
 This Petri net has a single transition $\alpha$ with $2\textnormal{H}+\textnormal{O}$ as its source and $\textnormal{H}_2 \textnormal{O}$ as its target.
-See the original paper for more details on Petri nets \cite{BM}.
 
@@
 \end{enumerate}
-Thus we have a symmetric monoidal double category $\lOpen(\Petri)$ of open Petri nets obtained from structured cospans and a symmetric monoidal double category $F\lCsp$ of open Petri nets obtain from decorated cospans, and of course, we have an equivalence $\lOpen(\Petri) \sim F\lCsp$ of symmetric monoidal double categories by \cref{thm:equiv}.
-\end{comment}
+Thus we have a symmetric monoidal double category $\lOpen(\Petri)$ of open Petri nets obtained from structured cospans and a symmetric monoidal double category $F\lCsp$ of open Petri nets obtain from decorated cospans, and of course, we have an equivalence $\lOpen(\Petri) \simeq F\lCsp$ of symmetric monoidal double categories by \cref{thm:equiv}.
 

### 2020-11-20 cospans.tex
revived old edits in section 3 and subsection A.1

@@
 \]
-$$x_1+x_2 \mapseqq 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{x_1 \times x_2} F(m_1) \times F(m_2) \xrightarrow{\phi_{m_1,m_2}} F(m_1+m_2)$$}
+\begin{equation}\label{eq:tensordecoration}
+x_1+x_2 \mapseqq 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{x_1 \times x_2} F(m_1) \times F(m_2) \xrightarrow{\phi_{m_1,m_2}} F(m_1+m_2)
+\end{equation}
+}
 \item{the tensor product of two 2-morphisms $\alpha$ and $\beta$:
@@
 
-In \cite{BC2}, the first two authors introduced the symmetric monoidal double category of \emph{structured cospans} as a formalism to describe open networks.
-One of the main goals of this paper is to provide a monoidal double isomorphism between this double category and that of \emph{decorated cospans}, described in \cref{DecCospansDoubleCat}.
+In \cite{BC2}, the first two authors introduce the symmetric monoidal double category of \emph{structured cospans} as a formalism to capture open networks.
+One of the main goals of this paper is to provide a monoidal double isomorphism between this double category and that of \emph{decorated cospans}, described in detail in \cref{DecCospansDoubleCat}.
 We first recall the double category of structured cospans.
 
-\begin{thm}\label{SC}
+\begin{thm}\label{thm:SC}
 Given categories $\X$ and $\A$ with finite colimits and $L \maps \A \to \X$ a functor preserving
@@
 Composition of horizontal 1-cells and 2-cells is done using pushouts in $\X$, and the
-symmetric monoidal structure is defined using binary coproducts and the initial object in $\A$ and $\X$.
+symmetric monoidal structure is defined using binary coproducts and the initial object in $\A$ and $\X$: 
+the tensor of horizontal 1-cells is
+\begin{equation}\label{eq:tensorstuctured}
+\begin{tikzcd}[column sep={.4in,between origins}, row sep=.1in]
+& x &&&& x' &&&& x+x' & \\
+&&&\ot&&&& = &&&& \\
+L(a)\ar[uur,"i"]&& L(b)\ar[uul,"o"'] && L(a')\ar[uur,"i'"] && L(b')\ar[uul,"o'"'] && L(a+a')\ar[uur,"i+i'"] && L(b+b')\ar[uul,"o+o'"'] 
+\end{tikzcd}
+\end{equation}
+using that $L$ preserves coproducts.
 \end{thm}
@@
 We denote by $\Rex$ the 2-category of finitely cocomplete categories, finitely cocontinuous functors and natural transformations.
+(In \cite{BC} we took as objects finitely cocomplete categories with chosen finite colimits, just so we could turn these into symmetric monoidal categories without any further choices!!!
+Should we do that here???) {\chris Can you tell if we can get away without doing that?
+Perhaps after you read up to before the proof?}
 
@@
 These correspondences can be enhanced to 2-equivalences:
+%-In \cite{MV}, the classical Grothendieck construction is generalized to the monoidal setting: given a monoidal category $\A$ there is a bijection between \define{monoidal opindexed categories}, which are lax monoidal pseudofunctors $F\maps\A\to\Cat$, and \define{monoidal opfibrations}, which are opfibrations $U \maps \X \to \A$ where $\X$ is monoidal, $U$ is strict monoidal, and $\otimes_\X$ preserves cocartesian liftings.
+This bijection sends a monoidal opindexed category $F \maps \A \to \Cat$ to its Grothendieck construction $U \maps \inta F \to \A$.
+If the monoidal structure on $\A$ is in fact cocartesian, there is a further correspondence between these structures and ordinary pseudofunctors $F\maps\A\to\bicat{MonCat}$ into the 2-category of monoidal categories, strong monoidal functors and monoidal natural transformations.
+Further, all these correspondences lift to 2-equivalences:
+{\chris There is a commented out passage of your earlier take here.
+I think I preferred your earlier more discussional version.
+Now having the two bullets above almost totally coincides with the three lines with arrows between them in the sketch of proof below.
+Feels like saying the same thing twice, whereas earlier you were really just giving brief definitions before diving in the theorem.}
 
@@
 The second equivalence was also earlier observed by Shulman \cite{Shulman2008}.
-In more detail, if $(\phi,\phi_0)$ is the lax monoidal structure of the pseudofunctor $F$ as recalled in \cref{sec:2cats}, each fibre category $\X_a=F(a)$ obtains a monoidal structure via
+
+In more detail, if $(\phi,\phi_0)$ is the lax monoidal structure of the pseudofunctor $F$ as recalled in \cref{subsec:bicats}, the induced monoidal structure on the total Grothendieck category $\X=\inta F$ (\cref{def:GrothCat}) is given by
+\begin{equation}\label{eq:explicitstructure2}
+\Big(a,x\in F(a)\Big)\ot_{\X}\Big(b,y\in F(b)\Big)=\Big(a+b,\phi_{a,b}(x,y)\in F(a+b)\Big), \qquad I_{\X}=\Big(0_A,\phi_0\Big)
+\end{equation}
+Moreover, each fibre category $\X_a=F(a)$ obtains a monoidal structure via 
 \begin{equation}\label{eq:explicitstructure1}
@@
 
-These correspondences further restrict to the case when the Grothendieck category is specifically cocartesian monoidal itself. In that case, opfibrations
-$U \maps (\X,+)\to(\A,+)$ that strictly preserve chosen coproducts and initial object
-%, and such that $+$ preserves cocartesian liftings, Christina: this should ALWAYS be the case, by universal properties!
-bijectively correspond to pseudofunctors into the 2-category of cocartesian categories.  For more details, see \cite[Corollary 4.7]{MV} and the related discussion.
-
-Finally, we can further restrict to the setting of opfibrations that also preserve pushouts, and thus all finite colimits, thanks to the following result.
-%as well as Remark~4.11 therein regarding the non-necessary strictness condition. Is this obscuring or clarifying?
+These 2-equivalences further restrict to the case when the Grothendieck category $(X,\otimes)$ is specifically cocartesian monoidal itself, with coproducts built up from \cref{eq:explicitstructure2}.
+In that case, opfibrations $(\X,+)\to(\A,+)$ that (strictly) preserve coproducts and initial object bijectively correspond to pseudofunctors into the 2-category of cocartesian categories.
+For more details, see \cite[Corollary 4.7]{MV} and the related discussion.
+
+Finally, we can further restrict to the setting of opfibrations that also preserve pushouts, and thus all finite colimits, thanks to the following more general result.
 
@@
  \item all fibres have $\J$-colimits, and the reindexing functors preserve them;
- \item the total category $\X$ has $\J$-colimits, and $U$ preserves them.
+ \item the total category $\X$ has $\J$-colimits, and $U$ (strictly) preserves them.
 \end{enumerate}
@@
 
-\begin{proof}  See \cite[Corollary~4.9]{Hermida1999}.   \end{proof}
+\begin{proof}
+See \cite[Corollary~4.9]{Hermida1999} as well as \cite[Remark~4.11]{Hermida1999} for the non-necessary strictness condition.
+\end{proof}
 
 The first part formulates the existence of colimits \emph{locally} in each fibre, and if we let $\J$ range over all finite categories it says that the corresponding pseudofunctor $F\maps\A\to\Cat$ lands in the sub-2-category $\Rex$.
-The second part formulates the existence of colimits \emph{globally} in the total category $\inta F$, and if we let $\J$ range over all finite
-categories it says that $\X$ is finitely cocomplete and $U$ preserves all finite colimits.  Combining this with \cref{lem:MonGroth}, we deduce the following.
+The second part formulates the existence of colimits \emph{globally} in the total category $\inta F$, and if we let $\J$ range over all finite categories it says that $\X$ is finitely cocomplete and $U$ preserves all finite colimits.
+As an example, suppose that $\A$ has pushouts and a Grothendieck opfibration $U\colon\inta F\to\A$ has fibrewise pushouts preserved by its reindexing functors.
+We can construct pushouts in $\inta F$ as follows:
+\begin{equation}\label{eq:globalpushout}
+ \begin{tikzcd}[ampersand replacement=\&,column sep=1in,row sep=.5in]
+\& (a+_bc,w)\ar[dd,phantom, very near start,"\upback"description] \& \\
+(a,x)\ar[ur] \&\& (c,z)\ar[ul] \\
+\& (b,y)\ar[ul,"{\begin{cases}f\maps b\to a &\textrm{in }\A \\k\maps F(f)y\to x &\textrm{in }F(a)\end{cases}}"description]\ar[ur,"{\begin{cases}g\maps b\to c &\textrm{in }\A \\\ell\maps F(g)y\to z &\textrm{in }F(c)\end{cases}}"description] \&
+ \end{tikzcd}
+\end{equation}
+which is the pushout $\sigma_a\colon a\to a+_bc\leftarrow c:\sigma_c$ in $\A$ on the first variable, and $w$ is the pushout in the fibre $F(a+_bc)$
+\begin{displaymath}
+\begin{tikzcd}
+ & w \ar[dd,phantom, very near start,"\upback"description] & \\
+ F(\sigma_a)x\ar[ur] & & F(\sigma_c)z\ar[ul] \\
+ & F(\sigma_a)(Ff(y))\cong F(\sigma_n)(Fg(y))\ar[ul,"F(\sigma_a)k"]\ar[ur,"F(\sigma_c)\ell"'] &
+ \end{tikzcd}
+\end{displaymath}
+In similar ways we can construct the initial object and coproducts in a Grothendieck category.
+
+In our case of interest, the pseudofunctor $F$ will originally be lax monoidal; combining \cref{lem:MonGroth,lem:fibrewiselimits}, we deduce the following.
+%Christina: I suspect that's why for composition we get isomorphism below - using pushouts in which I cannot use the monoidal structure of the functor - whereas for coproducts and initial object we get equality since they were constructed in a very specific way.
+Related to the subtlety comment below.
 
@@
 However, we \emph{will} use the formulation of coproducts and initial object in terms of the monoidal structure of $F$, and that is why the correspondence in \cref{lem:MonGroth} is necessary.
-DOES THIS MAKE SENSE TO ALL?? %still, we ARE going to use the formation of coproducts as above. Otherwise someone might think that the monoidal Groth story was redundant here!
-
-On a highly related note, in what follows we are also interested in the existence of a left adjoint $L_F$ to an induced monoidal opfibration; the following result provides sufficient conditions for that.
+DOES THIS MAKE SENSE TO ALL??
+
+On a highly related note, in what follows we are also interested in the existence of a left adjoint $L$ to an induced monoidal opfibration; the following result provides sufficient conditions for that.
 
@@
 
+%Notice that under \cref{lem:fibrewiselimits}, if the base category $\A$ has an initial object denoted $0_\A$, the above lemma is equivalent to $\X$ having an initial object $0_\X$ above $0_\A$.
+
 %Work in progress \cite{CV} includes a related discussion as well as a result in the opposite direction.
 
-%For a discussion on the unusual strict cocontinuity condition...
-%\begin{lem}\label{prop:CV}\cite[Proposition~3.3]{CV}
-%Suppose $\U\maps\X\to\A$ is a right adjoint `left inverse'. If $\X$ and $\A$ have chosen pushouts and initial objects and $\U$ strictly preserves them, %then $\U$ is an opfibration.
-%\end{lem}
-
-Notice that under \cref{lem:fibrewiselimits}, if the base category $\A$ has an initial object denoted $0_\A$, the above lemma is equivalent to $\X$ having an initial object $0_\X$ above $0_\A$.
+%Christina: I don't think the following is needed.
+%Notice that under \cref{lem:fibrewiselimits}, if the base category $\A$ has an initial object denoted $0_\A$, the above lemma is equivalent to $\X$ having an initial object $0_\X$ above $0_\A$.
 The way in which these two conditions give one another in this case is as follows.
-The fibrewise initial object $\bot_a$ is precisely the cocartesian lifting of $0_\X$ along the unique map $u_a\maps0_\A\to a$ in the base category
-\begin{displaymath}
-\xymatrix @C=.4in @R=.2in
-{0_\X \ar @{.>}[d]\ar[rr]^-{\mathrm{Cocart}(0_\X,u_a)} && (u_a)_!(0_X)=:\bot_a\ar @{.>}[d] & \textrm{in }\X  \\
-0_\A\ar[rr]^-{\exists!u_a} && a & \textrm{in }\A}
-\end{displaymath}
-Moreover, if the opfibration $U$ comes from the Grothendieck construction on a pseudofunctor $F\maps\A\to\Cat$, the reindexing functors $(u_a)_!$ of the opfibration are precisely $F(u_a)$ therefore $\bot_a=(a,F(u_a)(0_\X))$ in the Grothendieck category notation (\cref{def:GrothCat}).
-
-Finally, if we start with a lax monoidal pseudofunctor $(F,\phi,\phi_0)$, the monoidal Grothendieck construction of \cref{lem:MonGroth} in the cocartesian case expresses $\bot_a$ as follows by \cref{eq:explicitstructure1}:
-\begin{equation}\label{eq:initialinfibre}
-\mathbf{1}\xrightarrow{\phi_0}F(0_\A)\xrightarrow{F(u_a)}F(a) 
-\end{equation}
+%The fibrewise initial object $\bot_a$ is precisely the cocartesian lifting of $0_\X$ along the unique map $u_a\maps0_\A\to a$ in the base category
+%\begin{displaymath}
+%\xymatrix @C=.4in @R=.2in
+%{0_\X \ar @{.>}[d]\ar[rr]^-{\mathrm{Cocart}(0_\X,u_a)} && (u_a)_!(0_X)=:\bot_a\ar @{.>}[d] & \textrm{in }\X  \\
+%0_\A\ar[rr]^-{\exists!u_a} && a & \textrm{in }\A}
+%\end{displaymath}
+%Moreover, if the opfibration $U$ comes from the Grothendieck construction on a pseudofunctor $F\maps\A\to\Cat$, the reindexing functors $(u_a)_!$ of the %opfibration are precisely $F(u_a)$ therefore $\bot_a=(a,F(u_a)(0_\X))$ in the Grothendieck category notation (\cref{def:GrothCat}).
+
+%Finally, if we start with a lax monoidal pseudofunctor $(F,\phi,\phi_0)$, the monoidal Grothendieck construction of \cref{lem:MonGroth} in the cocartesian case expresses $\bot_a$ as follows by \cref{eq:explicitstructure1}:
+%\begin{equation}\label{eq:initialinfibre}
+%\mathbf{1}\xrightarrow{\phi_0}F(0_\A)\xrightarrow{F(u_a)}F(a) 
+%\end{equation}
 
@@
 describes the construction of the adjunction from the original $F$.
-Explicitly, the left adjoint picks the initial object in the finitely cocomplete fibre $L(a)=(a,\bot_a)$, also expressed as $F(u_a)\circ\\phi_0(*)$ according to \cref{eq:initialinfibre} for $(\phi,\phi_0)$ the monoidal structure of $F$.
-
-As a left adjoint, this induced $L$ preserves all colimits that exist between the finitely cocomplete categories $\A$ and $\inta F$, so we can construct the double category of structured cospans $_L\lCsp(\inta F)$ of \cref{SC}.
+Explicitly, the left adjoint picks the initial object in the finitely cocomplete fibre $L(a)=(a,\bot_a)$, also expressed as $F(!_a)\circ\phi_0(*)$ according to \cref{eq:explicitstructure1} for $(\phi,\phi_0)$ the monoidal structure of $F$.
+%Christina: If each adjoint picks one isomorphic initial object, can we choose the one with that choice?
+Well they are all isomorphic and that could help with the monoidal structure later...
+
+As a left adjoint, this induced $L$ preserves all colimits that exist between the finitely cocomplete categories $\A$ and $\inta F$, so we can construct the double category of structured cospans $_L\lCsp(\inta F)$ of \cref{thm:SC}.
 Its objects and vertical morphisms are those of the category $\A$ (as for $F\lCsp$ earlier), whereas horizontal 1-cells are now cospans of the form $\cspn{L(a)}{v}{L(b)}{}{}$ in the Grothendieck category $\inta F$ (\cref{def:GrothCat}).
@@
 \end{equation}
-whereas first composing $M$ and $N$ in $_L\lCsp(\inta F)$ using pushouts in $\inta F$ (constructed by \cref{lem:fibrewiselimits}) %!!!
-Christina: would you like me to write how global pushouts are constructed from fiberwise ones and incorporate it earlier say at \cref{rmk:important} where we do so for initial objects?
-produces 
+whereas first composing $M$ and $N$ in $_L\lCsp(\inta F)$ using pushouts in $\inta F$ as in \cref{eq:globalpushout} produces 
 \begin{displaymath}
@@
 
-Since both double categories $_L \lCsp(\X)$ and $F\lCsp$ are symmetric monoidal, 
-{\chris in progress}
-
-as they are if both $\A$ and $\X$ have finite colimits, then this isomorphism of double categories $\mathbb{E} \maps _L \lCsp(\X) \to F\lCsp$ will be symmetric monoidal.
-First, note that we have an isomorphism $\epsilon \maps 1_{F\lCsp} \to \mathbb{E}(1_{_L \lCsp(\X)})$ and natural isomorphisms $\phi_{c_1,c_2} \maps \mathbb{E}(c_1) \otimes \mathbb{E}(c_2) \to \mathbb{E}(c_1 \otimes c_2)$ for every pair of objects $c_1,c_2 \in {_L \mathbb{C} \textnormal{sp}(\X)}$ both of which are given by identities since both double categories $_L \lCsp(\X)$ and $F\lCsp$ have $\A$ as their category of objects and $\mathbb{E}_0=\id_{\A}$.
-The diagrams utilizing these maps that are required to commute do so trivially.
-
-For the arrow component $\mathbb{E}_1$, we have an isomorphism $\delta \maps U_{1_{F\lCsp}} \to \mathbb{E}(U_{1_{_L \lCsp(\X)}})$ where the horizontal 1-cell $U_{1_{F\lCsp}}$ is given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$1_\A$};
-\node (B) at (1,0) {$1_\A$};
-\node (C) at (2,0) {$1_\A$};
-\node (D) at (3,0) {$!_{1_{\A}} \in F(1_\A)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$1$} (B)
-(C) edge node[above]{$1$} (B);
-\end{tikzpicture}
-\]
-where $!_{1_{\A}} = \phi \maps 1 \to F(1_\A)$ is the trivial decoration which comes from the structure of the symmetric lax monoidal pseudofunctor $F \maps \A \to \Cat$.
-The horizontal 1-cell $U_{1_{_L \lCsp(\X)}}$ is given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$L(1_\A)$};
-\node (B) at (1,0) {$L(1_\A)$};
-\node (C) at (2,0) {$L(1_\A)$};
-%\node (D) at (3,0.5) {$I \in F(1_\mathrm{A})$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$1$} (B)
-(C) edge node[above]{$1$} (B);
-\end{tikzpicture}
-\]
-where here we make use of the fact that the left adjoint $L \maps (\A,+,1_\A) \to (\X,+,1_\X)$ preserves all colimits and thus $L(1_\A) \cong 1_\X$.
-The horizontal 1-cell $\mathbb{E}(U_{1_{_L \mathbb{C} \textnormal{sp}(\X)}})$ is then given by the pair:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$1_\A$};
-\node (B) at (1.25,0) {$R(L(1_\A))$};
-\node (C) at (2.5,0) {$1_\A$};
-\node (D) at (4.5,0) {$!_{R(L(1_\A))} \in F(R(L(1_\A)))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{${\eta_{1_\A}}$} (B)
-(C) edge node[above]{${\eta_{1_\A}}$} (B);
-\end{tikzpicture}
-\]
-The isomorphism $\delta$ is then given by the 2-morphism:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$1_\A$};
-\node (B) at (1,0) {$1_{\A}$};
-\node (C) at (2,0) {$1_\A$};
-\node (A') at (0,-1) {$1_\A$};
-\node (B') at (1,-1) {$R(L(1_\A))$};
-\node (C') at (2,-1) {$1_\A$};
-\node (D) at (3,0) {$!_{1_\A} \in F(1_\A)$};
-\node (D') at (3.75,-1) {$!_{R(L(1_\A))} \in F(R(L(1_\A)))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$1$} (B)
-(C) edge node[above]{$1$} (B)
-(A') edge node[above]{${\eta_{1_\A}}$} (B')
-(C') edge node[above]{${\eta_{1_\A}}$} (B')
-(A) edge node [left]{$1$} (A')
-(B) edge node [left]{${\eta_{1_\A}}$} (B')
-(C) edge node [left]{$1$} (C');
-\end{tikzpicture}
-\]
-$$\tau_{{\eta_{1_\A}}} \maps F({\eta_{1_\A}})(!_{1_\A})) \to !_{R(L(1_\A))}$$
-of $F\lCsp$. This is just the natural isomorphism $\mathbb{E}_{1_\A}$ from earlier.
-
-Given two horizontal 1-cells $M$ and $N$ of $_L \lCsp(\X)$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$L(c_1)$};
-\node (B) at (1,0) {$x$};
-\node (C) at (2,0) {$L(c_2)$};
-\node (D) at (3,0) {$L(c_1')$};
-\node (E) at (4,0) {$x'$};
-\node (F) at (5,0) {$L(c_2')$};
-%\node (D) at (3,0.5) {$!_c \in F(c)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i$} (B)
-(C) edge node[above]{$o$} (B)
-(D) edge node[above]{$i'$} (E)
-(F) edge node[above]{$o'$} (E);
-\end{tikzpicture}
-\]
-their images $\mathbb{E}(M)$ and $\mathbb{E}(N)$ are given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$c_1$};
-\node (B) at (1,0) {$R(x)$};
-\node (C) at (2,0) {$c_2$};
-\node (D) at (3,0) {$c_1'$};
-\node (E) at (4,0) {$R(x')$};
-\node (F) at (5,0) {$c_2'$};
-\node (G) at (1,-0.5) {$x \in F(R(x))$};
-\node (H) at (4,-0.5) {$x' \in F(R(x'))$};
-%\node (D) at (3,0.5) {$!_c \in F(c)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$R(i) \eta_{c_1}$} (B)
-(C) edge node[above]{$R(o) \eta_{c_2}$} (B)
-(D) edge node[above]{$R(i') \eta_{c_1'}$} (E)
-(F) edge node[above]{$R(o') \eta_{c_2'}$} (E);
-\end{tikzpicture}
-\]
-and so $\mathbb{E}(M) \otimes \mathbb{E}(N)$ is given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$c_1+c_1'$};
-\node (B) at (3.25,0) {$R(x)+R(x')$};
-\node (C) at (6.5,0) {$c_2+c_2'$};
-\node (D) at (3.25,-0.5) {$d_{\mathbb{E}(M) \otimes \mathbb{E}(N)} \in F(R(x)+R(x'))$}; 
-%\node (D) at (3,0.5) {$!_c \in F(c)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$R(i) \eta_{c_1} +R(i') \eta_{c_1'}$} (B)
-(C) edge node[above]{$R(o) \eta_{c_2} + R(o) \eta_{c_2'}$} (B);
-\end{tikzpicture}
-\]
-where $$d_{\mathbb{E}(M) \otimes \mathbb{E}(N)} \maps 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{x \times x'} F(R(x)) \times F(R(x')) \xrightarrow{\phi_{R(x),R(x')}} F(R(x)+R(x')).$$ On the other hand, $M \otimes N$ is given by
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$L(c_1+c_1')$};
-\node (B) at (2,0) {$x+x'$};
-\node (C) at (4,0) {$L(c_2+c_2')$};
-%\node (D) at (3,0.5) {$!_c \in F(c)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$(i+i')\phi_{c_1,c_1'}^{-1}$} (B)
-(C) edge node[above]{$(o+o')\phi_{c_2,c_2'}^{-1}$} (B);
-\end{tikzpicture}
-\]
-and $\mathbb{E}(M \otimes N)$ is given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$c_1+c_1'$};
-\node (B) at (4,0) {$R(x+x')$};
-\node (C) at (8,0) {$c_2+c_2'$};
-\node (D) at (4,-0.5) {$d_{\mathbb{E}(M \odot N)} \in F(R(x+x')).$};
-%\node (D) at (3,0.5) {$!_c \in F(c)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$R((i+i')\phi_{c_1,c_1'}^{-1}) \eta_{c_1+c_1'}$} (B)
-(C) edge node[above]{$R((o+o')\phi_{c_2,c_2'}^{-1}) \eta_{c_2+c_2'}$} (B);
-\end{tikzpicture}
-\]
-We then have a 2-isomorphism $\phi_{M,N} \maps E(M) \otimes E(N) \xrightarrow{\sim} E(M \otimes N)$ in $F\lCsp$ given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (-2.5,0) {$c_1+c_1'$};
-\node (B) at (1,0) {$R(x)+R(x')$};
-\node (C) at (4.5,0) {$c_2+c_2'$};
-\node (A') at (-2.5,-1) {$c_1+c_1'$};
-\node (B') at (1,-1) {$R(x+x')$};
-\node (C') at (4.5,-1) {$c_2+c_2'$};
-\node (D) at (6.55,0) {$d_{\mathbb{E}(M) \otimes \mathbb{E}(N)} \in F(R(x)+R(x'))$};
-\node (D') at (6.55,-1) {$d_{\mathbb{E}(M \otimes N)} \in F(R(x+x'))$};
-\node (E) at (2,-1.5) {$\tau_\mu \maps F(\kappa)(d_{\mathbb{E}(M) \odot \mathbb{E}(N)}) \to d_{\mathbb{E}(M \odot N)}$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$R(i)\eta_{c_1} + R(i')\eta_{c_1'}$} (B)
-(C) edge node[above]{$R(o)\eta_{c_2} + R(o')\eta_{c_2'}$} (B)
-(A') edge node[above]{$R((i+i')\phi_{c_1,c_1'}^{-1}) \eta_{c_1+c_1'}$} (B')
-(C') edge node[above]{$R((o+o')\phi_{c_2,c_2'}^{-1}) \eta_{c_2+c_2'}$} (B')
-(A) edge node [left]{$1$} (A')
-(B) edge node [left]{$\kappa$} (B')
-(C) edge node [right]{$1$} (C');
-\end{tikzpicture}
-\]
-where $\kappa$ is the isomorphism which comes from $R \maps \X \to \A$ preserving finite colimits.
-
-The isomorphisms $\delta$ and $\mu$ satisfy the left and right unitality squares, associativity hexagon and braiding square. 
-%Kenny: I think this might be a good place to cut the monoidal stuff.
-%Christina: Deal! They are right below.
-
-\begin{comment}
-To see this, let $M_1,M_2$ and $M_3$ be horizontal 1-cells in $_L \lCsp(\X)$ given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$L(c_1)$};
-\node (B) at (1,0) {$x_1$};
-\node (C) at (2,0) {$L(c_1')$};
-\node (D) at (3,0) {$L(c_2)$};
-\node (E) at (4,0) {$x_2$};
-\node (F) at (5,0) {$L(c_2')$};
-\node (G) at (6,0) {$L(c_3)$};
-\node (H) at (7,0) {$x_3$};
-\node (I) at (8,0) {$L(c_3')$};
-%\node (D) at (3,0.5) {$!_c \in F(c)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i_1$} (B)
-(C) edge node[above]{$o_1$} (B)
-(D) edge node[above]{$i_2$} (E)
-(F) edge node[above]{$o_2$} (E)
-(G) edge node[above]{$i_3$} (H)
-(I) edge node[above]{$o_3$} (H);
-\end{tikzpicture}
-\]
-The left unitality square:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$1_{F\lCsp} \otimes \mathbb{E}(M_1)$};
-\node (B) at (3,0) {$\mathbb{E}(1_{ _L \lCsp(\X)}) \otimes \mathbb{E}(M_1)$};
-\node (C) at (0,-1) {$\mathbb{E}(M_1)$};
-\node (D) at (3,-1) {$\mathbb{E}(1_{ _L \lCsp(\X)} \otimes M_1)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$\delta \otimes 1$} (B)
-(B) edge node[right]{$\mu_{1,M_1}$} (D)
-(A) edge node[left]{$\lambda'$} (C)
-(D) edge node[above]{$\mathbb{E}(\lambda)$} (C);
-\end{tikzpicture}
-\]
-has an underlying diagram of maps of cospans given by:
-\[
-		\begin{tikzpicture}
-			\node (d) at (7.5,0) {$\mathbb{E}(1_{ _L \lCsp(\X)}) \otimes \mathbb{E}(M_1)$};
-			\node (a) at (-6,0) {$1_\A+c_1$};
-			\node (b) at (-0.5,0) {$R(L(1_\A)) + R(x_1)$};
-			\node (c) at (5,0) {$1_\A+c_1'$};
-			\node (d2) at (7.5,1) {$1_{F\lCsp} \otimes \mathbb{E}(M_1)$};
-			\node (a2) at (-6,1) {$1_\A+c_1$};
-			\node (b2) at (-0.5,1) {$1_\A+R(x_1)$};
-			\node (c2) at (5,1) {$1_\A+c_1'$};
-			\node (d3) at (7.5,2) {$\mathbb{E}(M_1)$};
-                                \node (a3) at (-6,2) {$c_1$};
-			\node (b3) at (-0.5,2) {$R(x_1)$};
-			\node (c3) at (5,2) {$c_1'$};
-			\node (d4) at (7.5,-1) {$\mathbb{E}(1_{ _L \lCsp(\X)} \otimes M_1)$};
-                                \node (a5) at (-6,-1) {$1_\A+c_1'$};
-			\node (b5) at (-0.5,-1) {$R(L(1_\A)+x_1)$};
-			\node (c5) at (5,-1) {$1_\A+c_1'$};
-			\node (d5) at (7.5,-2) {$\mathbb{E}(M_1)$};
-                                \node (a6) at (-6,-2) {$c_1$};
-			\node (b6) at (-0.5,-2) {$R(x_1)$};
-			\node (c6) at (5,-2) {$c_1'$};
-			\path[->,font=\scriptsize,>=angle 90]
-			(d2) edge node [left]{$\lambda$} (d3)
-			(d2) edge node [left] {$\delta \otimes 1$} (d)
-			(d) edge node [left] {$\mu_{1,M_1}$} (d4)
-			(d4) edge node [left] {$\mathbb{E}(\lambda)$} (d5)
-			(a) edge node[above]{$\eta_{1_\A}+R(i_1)\eta_{c_1}$} (b)
-			(c) edge node[above]{$\eta_{1_\A}+R(o_1)\eta_{c_1'}$} (b)
-                                (a2) edge node[above]{$1+R(i_1)\eta_{c_1}$} (b2)
-			(c2) edge node[above]{$1+R(o_1)\eta_{c_1'}$} (b2)
-                                (a2) edge node[left]{$1$} (a)
-                                (b2) edge node[left]{$\eta_{1_\A}+1$} (b)
-(b2) edge node[right]{$\tau_2$} (b)
-			(c2) edge node[right]{$1$} (c)
-                                (a3) edge node[above]{$R(i_1)\eta_{c_1}$} (b3)
-			(c3) edge node[above]{$R(o_1)\eta_{c_1'}$} (b3)
-                                (a2) edge node[left]{$\lambda_{\A}$} (a3)
-                                (b2) edge node[left]{$\lambda_{\A}$} (b3)
-(b2) edge node[right]{$\tau_1$} (b3)
-			(c2) edge node[right]{$\lambda_{\A}$} (c3)
-                                (a5) edge node[above]{$(\mu_{L(1_\A),d_1})(\eta_{1_\A}+R(i_1)\eta_{c_1})$} (b5)
-			(c5) edge node[above]{$(\mu_{L(1_\A),d_1})(\eta_{1_\A}+R(o_1)\eta_{c_1'})$} (b5)
-                                (a) edge node[left]{$1$} (a5)
-                                (b) edge node[left]{$\mu_{L(1_\A),x_1}$} (b5)
-(b) edge node[right]{$\tau_3$} (b5)
-			(c) edge node[right]{$1$} (c5)
-                                (a6) edge node[above]{$R(i_1)\eta_{c_1}$} (b6)
-			(c6) edge node[above]{$R(o_1)\eta_{c_1'}$} (b6)
-                                (a5) edge node[left]{$\lambda_{\A}$} (a6)
-                                (b5) edge node[left]{$R(\lambda_{\X})$} (b6)
- (b5) edge node[right]{$\tau_4$} (b6)
-			(c5) edge node[right]{$\lambda_{\A}$} (c6);
-		\end{tikzpicture}
-	\]
-with the corresponding maps of decorations amounting to the following commutative diagram in $F(R(x_1))$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (-.5,0) {$F(\lambda_{\A})(!_{1_\A}+x_1)$};
-\node (C) at (4,0) {$F(R(\lambda_{\X})(\mu_{L(1_\A),x_1}))(!_{R(L(1_\A))} +x_1$)};
-\node (D) at (-.5,-1) {$x_1$};
-\node (E) at (4,-1) {$F(R(\lambda_\X))(x_{!+1})$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$F(R(\lambda_{\X})(\mu_{L(1_\A),x_1}))(\tau_2)$} (C)
-(A) edge node[left]{$\tau_1$} (D)
-(E) edge node[above]{$\tau_4$} (D)
-(C) edge node[right]{$F(R(\lambda_\X))(\tau_3)$} (E);
-\end{tikzpicture}
-\]
-where $x_{!+1}$ is the decoration $x_1$ on the object $R(L(1_\A)+x_1) \in \A$.
-The above square commutes because $$F(\lambda_\A)(!_{1_\A}+x_1) = F(R(\lambda_\X)(\mu_{L(1_\A),x_1})(\eta_{1_\A}+1))(!_{1_\A}+x_1)$$ as the corresponding left unitality square for the finite colimit preserving functor $R \maps (\X,1_\X,+) \to (\A,1_\A,+)$ commutes.
-The right unitality square is similar.
-The associator hexagon:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$(\mathbb{E}(M_1) \otimes \mathbb{E}(M_2)) \otimes \mathbb{E}(M_3)$};
-\node (B) at (3.5,0) {$\mathbb{E}(M_1 \otimes M_2) \otimes \mathbb{E}(M_3)$};
-\node (C) at (7,0) {$\mathbb{E}((M_1 \otimes M_2) \otimes M_3)$};
-\node (A') at (0,-1) {$\mathbb{E}(M_1) \otimes (\mathbb{E}(M_2) \otimes \mathbb{E}(M_3))$};
-\node (B') at (3.5,-1) {$\mathbb{E}(M_1) \otimes \mathbb{E}(M_2 \otimes M_3)$};
-\node (C') at (7,-1) {$\mathbb{E}(M_1 \otimes (M_2 \otimes M_3))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$\mu_{M_1,M_2} \otimes 1$} (B)
-(B) edge node[above]{$\mu_{M_1 \otimes M_2,M_3}$} (C)
-(A') edge node[above]{$1 \otimes \mu_{M_2,M_3}$} (B')
-(B') edge node[above]{$\mu_{M_1,M_2 \otimes M_3}$} (C')
-(A) edge node [left]{$a'$} (A')
-(C) edge node [right]{$\mathbb{E}(a)$} (C');
-\end{tikzpicture}
-\]
-has underlying maps of cospans given by:
-\[
-		\begin{tikzpicture}
-\node(d) at (1.5,7) {$(\mathbb{E}(M_1) \otimes \mathbb{E}(M_2)) \otimes \mathbb{E}(M_3)$};
-\node (d2) at (1.5,8) {$\mathbb{E}(M_1 \otimes M_2) \otimes \mathbb{E}(M_3)$};
-\node (d3) at (1.5,9) {$\mathbb{E}((M_1 \otimes M_2) \otimes M_3)$};
-\node (d4) at (1.5,10) {$\mathbb{E}(M_1 \otimes (M_2 \otimes M_3))$};
-\node (d5) at (1.5,6) {$\mathbb{E}(M_1) \otimes (\mathbb{E}(M_2) \otimes \mathbb{E}(M_3))$};
-\node (d6) at (1.5,5) {$\mathbb{E}(M_1) \otimes \mathbb{E}(M_2 \otimes M_3)$};
-\node (d7) at (1.5,4) {$\mathbb{E}(M_1 \otimes (M_2 \otimes M_3))$};
-			\node (a) at (-4.25,0) {$(c_1+c_2)+c_3$};
-			\node (b) at (2.5,0) {$(R(x_1)+R(x_2))+R(x_3)$};
-			\node (c) at (9.25,0) {$(c_1'+c_2')+c_3'$};
-			\node (a2) at (-4.25,1) {$(c_1+c_2)+c_3$};
-			\node (b2) at (2.5,1) {$R(x_1+x_2)+R(x_3)$};
-			\node (c2) at (9.25,1) {$(c_1'+c_2')+c_3'$};
-                                \node (a3) at (-4.25,2) {$(c_1+c_2)+c_3$};
-			\node (b3) at (2.5,2) {$R((x_1+x_2)+x_3)$};
-			\node (c3) at (9.25,2) {$(c_1'+c_2')+c_3'$};
-                                \node (a4) at (-4.25,3) {$c_1+(c_2+c_3)$};
-			\node (b4) at (2.5,3) {$R(x_1+(x_2+x_3))$};
-			\node (c4) at (9.25,3) {$c_1' + (c_2' + c_3')$};
-                                \node (a5) at (-4.25,-1) {$c_1+(c_2+c_3)$};
-			\node (b5) at (2.5,-1) {$R(x_1)+(R(x_2)+R(x_3))$};
-			\node (c5) at (9.25,-1) {$c_1' + (c_2' + c_3')$};
-                                \node (a6) at (-4.25,-2) {$c_1+(c_2+c_3)$};
-			\node (b6) at (2.5,-2) {$R(x_1)+R(x_2+x_3)$};
-			\node (c6) at (9.25,-2) {$c_1' + (c_2' + c_3')$};
-                                \node (a7) at (-4.25,-3) {$c_1+(c_2+c_3)$};
-			\node (b7) at (2.5,-3) {$R(x_1+(x_2+x_3))$};
-			\node (c7) at (9.25,-3) {$c_1' + (c_2' + c_3')$};
-			\path[->,font=\scriptsize,>=angle 90]
-(d) edge node[left] {$\mu_{M_1,M_2} \otimes 1$} (d2)
-(d2) edge node[left] {$\mu_{M_1 \otimes M_2,M_3}$} (d3)
-(d3) edge node[left] {$\mathbb{E}(a)$} (d4)
-(d) edge node[left] {$a'$} (d5)
-(d5) edge node[left] {$1 \otimes \mu_{M_2,M_3}$} (d6)
-(d6) edge node[left] {$\mu_{M_1,M_2 \otimes M_3}$} (d7)
-			(a) edge node[above]{$(R(i_1)\eta_{c_1}+R(i_2)\eta_{c_2})+R(i_3)\eta_{c_3}$} (b)
-			(c) edge node[above]{$(R(o_1)\eta_{c_1'}+R(o_2)\eta_{c_2'})+R(o_3)\eta_{c_3'}$} (b)
-                                (a2) edge node[above]{$R(i_1+i_2)\eta_{c_1+c_2}+R(i_3)\eta_{c_3}$} (b2)
-			(c2) edge node[above]{$R(o_1+o_2)\eta_{c_1'+c_2'}+R(o_3)\eta_{c_3'}$} (b2)
-                                (a) edge node[left]{$1$} (a2)
-                                (b) edge node[left]{$\kappa + 1$} (b2)
-(b) edge node[right]{$\tau_1$} (b2)
-			(c) edge node[right]{$1$} (c2)
-                                (a3) edge node[above]{$R((i_1+i_2)+i_3)\eta_{(c_1+c_2)+c_3}$} (b3)
-			(c3) edge node[above]{$R((o_1+o_2)+o_3)\eta_{(c_1'+c_2')+c_3'}$} (b3)
-                                (a2) edge node[left]{$1$} (a3)
-                                (b2) edge node[left]{$\kappa$} (b3)
-(b2) edge node[right]{$\tau_2$} (b3)
-			(c2) edge node[right]{$1$} (c3)
-                                (a4) edge node[above]{$R(i_1+(i_2+i_3))\eta_{c_1+(c_2+c_3)}$} (b4)
-			(c4) edge node[above]{$R(o_1+(o_2+o_3))\eta_{c_1'+(c_2'+c_3')}$} (b4)
-                                (a3) edge node[left]{$a_\A$} (a4)
-                                (b3) edge node[left]{$R(a_\X)$} (b4)
-(b3) edge node[right]{$\tau_3$} (b4)
-			(c3) edge node[right]{$a_\A$} (c4)
-                                (a5) edge node[above]{$R(i_1)\eta_{c_1}+(R(i_2)\eta_{c_2}+R(i_3)\eta_{c_3})$} (b5)
-			(c5) edge node[above]{$R(o_1)\eta_{c_1'}+(R(o_2)\eta_{c_2'}+R(o_3)\eta_{c_3'})$} (b5)
-                                (a) edge node[left]{$a_\A$} (a5)
-                                (b) edge node[left]{$a_\A$} (b5)
-(b) edge node[right]{$\tau_4$} (b5)
-			(c) edge node[right]{$a_\A$} (c5)
-                                (a6) edge node[above]{$R(i_1)\eta_{c_1}+R(i_2+i_3)\eta_{c_2+c_3}$} (b6)
-			(c6) edge node[above]{$R(o_1)\eta_{c_1'}+R(o_2+o_3)\eta_{c_2'+c_3'}$} (b6)
-                                (a5) edge node[left]{$1$} (a6)
-                                (b5) edge node[left]{$1+\kappa$} (b6)
- (b5) edge node[right]{$\tau_5$} (b6)
-			(c5) edge node[right]{$1$} (c6)
-                                (a7) edge node[above]{$R(i_1+(i_2+i_3))\eta_{c_1+(c_2+c_3)}$} (b7)
-			(c7) edge node[above]{$R(o_1+(o_2+o_3))\eta_{c_1'+(c_2'+c_3')}$} (b7)
-                                (a6) edge node[left]{$1$} (a7)
-                                (b6) edge node[left]{$\kappa$} (b7)
-(b6) edge node[right]{$\tau_6$} (b7)
-			(c6) edge node[right]{$1$} (c7);
-		\end{tikzpicture}
-	\]
-Here we have omitted the natural isomorphisms $\phi_{c_i,c_j} \maps L(c_i) + L(c_j) \to L(c_i + c_j)$ on the inward pointing morphisms which make up the legs of each cospan due to limited space.
-The corresponding maps of decorations amount to the following commutative diagram in $F(R(x_1+(x_2+x_3)))$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$F((\kappa)(1+\kappa)(a_\A))((x_1+x_2)+x_3)$};
-\node (B) at (5,0) {$F((R(a_\mathrm{X}))(\kappa))((x_1+x_2)+x_3)$};
-\node (C) at (5,-1) {$F(R(a_\mathrm{X}))((x_1+x_2)+x_3)$};
-\node (D) at (5,-2) {$x_1+(x_2+x_3)$};
-\node (E) at (0,-1) {$F((\kappa)(1+\kappa))((x_1+x_2)+x_3)$};
-\node (F) at (0,-2) {$F(\kappa)(x_1+(x_2+x_3))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$F((R(a_\X))(\kappa))(\tau_1)$} (B)
-(B) edge node[right]{$F(R(a_\X))(\tau_2)$} (C)
-(C) edge node[right]{$\tau_3$} (D)
-(A) edge node[left]{$F((\kappa)(1+\kappa))(\tau_4)$} (E)
-(E) edge node[left]{$F(\kappa)(\tau_5)$} (F)
-(F) edge node[above]{$\tau_6$} (D);
-\end{tikzpicture}
-\]
-The above square commutes because $$F((\kappa)(1+\kappa)(a_\A))((x_1+x_2)+x_3) = F((R(a_\X))(\kappa)(\kappa+1))((x_1+x_2)+x_3)$$ as the corresponding associator hexagon for the finite colimit preserving functor $R \maps (\X,1_\X,+) \to (\A,1_\A,+)$ commutes.
-Lastly, the braiding square:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$\mathbb{E}(M_1) \otimes \mathbb{E}(M_2)$};
-\node (B) at (3,0) {$\mathbb{E}(M_2) \otimes \mathbb{E}(M_1)$};
-\node (C) at (0,-1) {$\mathbb{E}(M_1 \otimes M_2)$};
-\node (D) at (3,-1) {$\mathbb{E}(M_2 \otimes M_1)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$\beta'$} (B)
-(B) edge node[right]{$\mu_{M_2,M_1}$} (D)
-(A) edge node[left]{$\mu_{M_1,M_2}$} (C)
-(C) edge node[above]{$\mathbb{E}(\beta)$} (D);
-\end{tikzpicture}
-\]
-has underlying map of cospans given by:
-\[
-		\begin{tikzpicture}
-\node (d) at (7,0) {$\mathbb{E}(M_1) \otimes \mathbb{E}(M_2)$};
-\node (d2) at (7,1) {$\mathbb{E}(M_2) \otimes \mathbb{E}(M_1)$};
-\node (d3) at (7,2) {$\mathbb{E}(M_2 \otimes M_1)$};
-\node (d4) at (7,-1) {$\mathbb{E}(M_1 \otimes M_2)$};
-\node (d5) at (7,-2) {$\mathbb{E}(M_2 \otimes M_1)$};
-			\node (a) at (-4,0) {$c_1+c_2$};
-			\node (b) at (0.5,0) {$R(x_1)+R(x_2)$};
-			\node (c) at (5,0) {$c_1'+c_2'$};
-			\node (a2) at (-4,1) {$c_2+c_1$};
-			\node (b2) at (0.5,1) {$R(x_2)+R(x_1)$};
-			\node (c2) at (5,1) {$c_2'+c_1'$};
-                                \node (a3) at (-4,2) {$c_2+c_1$};
-			\node (b3) at (0.5,2) {$R(x_2+x_1)$};
-			\node (c3) at (5,2) {$c_2' + c_1'$};
-                                \node (a5) at (-4,-1) {$c_1+c_2$};
-			\node (b5) at (0.5,-1) {$R(x_1+x_2)$};
-			\node (c5) at (5,-1) {$c_1'+c_2'$};
-                                \node (a6) at (-4,-2) {$c_2+c_1$};
-			\node (b6) at (0.5,-2) {$R(x_2+x_1)$};
-			\node (c6) at (5,-2) {$c_2' + c_1'$};
-			\path[->,font=\scriptsize,>=angle 90]
-(d) edge node[left]{$\beta'$} (d2)
-(d2) edge node[left]{$\mu_{M_2,M_1}$}(d3)
-(d) edge node[left] {$\mu_{M_1,M_2}$}(d4)
-(d4)edge node[left]{$\mathbb{E}(\beta)$}(d5)
-			(a) edge node[above]{$R(i_1) \eta_{c_1} + R(i_2)\eta_{c_2}$} (b)
-			(c) edge node[above]{$R(o_1) \eta_{c_1'} + R(o_2) \eta_{c_2'}$} (b)
-                                (a2) edge node[above]{$R(i_2) \eta_{c_2} + R(i_1) \eta_{c_1}$} (b2)
-			(c2) edge node[above]{$R(o_2) \eta_{c_2'} + R(o_1) \eta_{c_1'}$} (b2)
-                                (a) edge node[left]{$\beta_\A$} (a2)
-                                (b) edge node[left]{$\beta_\A$} (b2)
-(b) edge node[right]{$\tau_1$} (b2)
-			(c) edge node[right]{$\beta_\A$} (c2)
-                                (a3) edge node[above]{$R(i_2+i_1)\eta_{c_2+c_1}$} (b3)
-			(c3) edge node[above]{$R(o_2+o_1)\eta_{c_2'+c_1'}$} (b3)
-                                (a2) edge node[left]{$1$} (a3)
-                                (b2) edge node[left]{$\kappa$} (b3)
-(b2) edge node[right]{$\tau_2$} (b3)
-			(c2) edge node[right]{$1$} (c3)
-                                (a5) edge node[above]{$R(i_1+i_2)\eta_{c_1+c_2}$} (b5)
-			(c5) edge node[above]{$R(o_1+o_2)\eta_{c_1'+c_2'}$} (b5)
-                                (a) edge node[left]{$1$} (a5)
-                                (b) edge node[left]{$\kappa$} (b5)
-(b) edge node[right]{$\tau_3$} (b5)
-			(c) edge node[right]{$1$} (c5)
-                                (a6) edge node[above]{$R(i_2+i_1)\eta_{c_2+c_1}$} (b6)
-			(c6) edge node[above]{$R(o_2+o_1)\eta_{c_2'+c_1'}$} (b6)
-                                (a5) edge node[left]{$\beta_\A$} (a6)
-                                (b5) edge node[left]{$R(\beta_\X)$} (b6)
- (b5) edge node[right]{$\tau_4$} (b6)
-			(c5) edge node[right]{$\beta_\A$} (c6);
-		\end{tikzpicture}
-	\]
-Again, we have omitted the natural isomorphisms $\phi_{c_i,c_j}$ on the inward pointing morphisms on each cospan leg due to space restrictions.
-The corresponding maps of decorations amounting to the following commutative diagram in $F(R(x_2+x_1))$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (-.5,0) {$F((\kappa)(\beta_\A))(x_1+x_2)$};
-\node (C) at (4,0) {$F(\kappa)(x_2+x_1)$};
-\node (D) at (-.5,-1) {$F(R(\beta_\X))(x_1+x_2)$};
-\node (E) at (4,-1) {$x_2+x_1$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$F(\kappa)(\tau_1)$} (C)
-(A) edge node[left]{$F(R(\beta_\X))(\tau_3)$} (D)
-(D) edge node[above]{$\tau_4$} (E)
-(C) edge node[right]{$\tau_2$} (E);
-\end{tikzpicture}
-\]
-The above square commutes because $$F((\kappa)(\beta_\A))(x_1+x_2) = F((R(\beta_\X))(\kappa))(x_1+x_2)$$ as the corresponding braiding square for the finite colimit preserving functor $R \maps (\X,1_\X,+) \to (\A,1_\A,+)$ commutes.
-Thus the double functor $\mathbb{E} \maps _L\lCsp(\X) \to F\lCsp$ is symmetric monoidal.
-\end{comment}
-
+Since both double categories are symmetric monoidal under the running assumptions (\cref{DC,thm:SC}), we will now show that this double isomorphism is a symmetric monoidal one, namely $\lE=(\lE_0,\lE_1)$ is a symmetric strong monoidal double functor as per \cref{defn:monoidal_double_functor}.
+Indeed, $\lE_0=\mathrm{id}_\A$ is a braided monoidal functor trivially.
+For $\lE_1$, given two structured cospans $M=(a,\bot_a)\to(m,x)\leftarrow(b,\bot_b)$ and $M'=(a',\bot_{a'})\to(m',x')\leftarrow(b',\bot_{b'})$ in $_L\lCsp(\inta F)$, we compute the appropriate decorated cospans
+\begin{align*}
+\lE(M)\ot\lE(M')&\;\stackrel{\cref{eq:tensordecoration}}{=}\;a+a'\xrightarrow{i+i'}m+m'\xleftarrow{o+o'}b+b' \textrm{ with }\mathbf{1}\xrightarrow{x\times x'}F(m)\times F(m')\xrightarrow{\phi_{m,m'}}F(m+m') \\
+\lE(M\ot M')&\;\stackrel{\cref{eq:tensorstuctured}}{=}\;\lE\Big((a+a',\bot_{a+a'})\to\underbrace{(m+m',\phi_{m,m'}(x,x'))}_{\cref{eq:explicitstructure2}}\leftarrow(b+b',\bot_{b+b'})\Big)%=a+a'\xrightarrow{i+i'}m+m'\xleftarrow{o+o'}b+b' \textrm{ with }\phi_{m,m'}(x,x')
+\end{align*}
+which are essentially the same.
+{\chris Well they look equal to me...thoughts?} Moreover, the monoidal unit for the category of arrows of $F\lCsp$ is $0_\A\xrightarrow{\raisebox{-3pt}[0pt][0pt]{$=$}}0_\A\xleftarrow{\raisebox{-3pt}[0pt][0pt]{$=$}}0_\A$ with the trivial decoration
+$$\mathbf{1}\xrightarrow{\phi_0}F(0_A)\xrightarrow{F(\mathrm{id})}F(0_A)$$
+which is essentially the same as $\lE((0_A,\phi_0)\xrightarrow{\raisebox{-3pt}[0pt][0pt]{$=$}}(0_A,\phi_0)\xleftarrow{\raisebox{-3pt}[0pt][0pt]{$=$}}(0_A,\phi_0))$ again by \cref{eq:explicitstructure2}.
+It can be verified that with the above structure, $\lE_1$ is also a braided monoidal functor, and the rest of the axioms of \cref{defn:monoidal_double_functor} hold.
 \end{proof}
@@
 %!!!Kenny: Is this biequivalnce symmetric monoidal? Mike says yes, but it follows from a result that he has yet to officially publish. It's a result of a paper he's currently working on with someone.
-
-\begin{comment}
-We can also define the part of the double equivalence $\mathbb{G} \maps F\lCsp \to {_L \mathbb{C} \textnormal{sp}(\X)}$ which goes in the other direction: again, the object component of this double functor will be $\mathbb{G}_0 = \id_{\A}$.
-
-Given a horizontal 1-cell $M$ of $F\lCsp$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$c_1$};
-\node (B) at (1,0) {$c$};
-\node (C) at (2,0) {$c_2$};
-\node (D) at (1,-0.5) {$x \in F(c)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$I$} (B)
-(C) edge node[above]{$O$} (B);
-\end{tikzpicture}
-\]
-the image $\mathbb{G}(M)$ is the horizontal 1-cell in $_L \lCsp(\X)$ given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$L(c_1)$};
-\node (B) at (1,0) {$x$};
-\node (C) at (2,0) {$L(c_2)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$!_{c} L(I)$} (B)
-(C) edge node[above]{$!_{c} L(O)$} (B);
-\end{tikzpicture}
-\]
-where $!_{c} \maps L(c) \to x$ is the unique morphism from the trival decoration on $c$ given by $$!_{c} \mapseqq 1 \xrightarrow{\phi} F(0) \xrightarrow{F(!)} F(c)$$ to $x \in F(c)$.
-In other words, the trivial decoraction $!_{c}$ is initial in $F(c)$.
-Similarly, given a 2-morphism $(f,h,g,\tau) \maps M \to M'$ of $F\lCsp$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (D) at (1,0.5) {$x \in F(c)$};
-\node (D') at (1,-1.5) {$x' \in F(c')$};
-\node (A) at (0,0) {$c_1$};
-\node (B) at (1,0) {$c$};
-\node (C) at (2,0) {$c_2$};
-\node (A') at (0,-1) {$c_1'$};
-\node (B') at (1,-1) {$c'$};
-\node (C') at (2,-1) {$c_2'$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$I$} (B)
-(C) edge node[above]{$O$} (B)
-(A') edge node[above]{$I'$} (B')
-(C') edge node[above]{$O'$} (B')
-(A) edge node [left]{$f$} (A')
-(B) edge node [left]{$h$} (B')
-(C) edge node [right]{$g$} (C');
-\end{tikzpicture}
-\]
-$$\tau \maps F(h)(x) \to x'$$
-the image $\mathbb{G}(f,h,g,\tau)$ in $_L \lCsp(\X)$ is given by the 2-morphism:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$L(c_1)$};
-\node (B) at (1.5,0) {$x$};
-\node (C) at (3,0) {$L(c_2)$};
-\node (A') at (0,-1) {$L(c_1')$};
-\node (B') at (1.5,-1) {$x'$};
-\node (C') at (3,-1) {$L(c_2')$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$!_{c} L(I)$} (B)
-(C) edge node[above]{$!_{c} L(O)$} (B)
-(A') edge node[above]{$!_{c'} L(I')$} (B')
-(C') edge node[above]{$!_{c'} L(O')$} (B')
-(A) edge node [left]{$L(f)$} (A')
-(B) edge node [left]{$\alpha$} (B')
-(C) edge node [right]{$L(g)$} (C');
-\end{tikzpicture}
-\]
-where $\alpha \maps x \to x'$ is the morphism in the Grothendieck construction of $F$ given by $\alpha = (h \maps c \to c', \tau \maps F(h)(x) \to x')$.
-
-Next, we exhibit natural isomorphisms $\eta \maps \id_{ _L \lCsp(\X)} \cong \mathbb{G} \mathbb{E}$ and $\epsilon \maps \mathbb{E} \mathbb{G} \cong \id_{F\lCsp}$.
-Specifically, these are double natural isomorphisms given by double transformations \cite{Shul2} $\eta$ and $\epsilon$ whose object and arrow components are natural isomorphisms.
-
-First we compute the composites $\mathbb{G} \mathbb{E}$ and $\mathbb{E} \mathbb{G}$.
-On the object categories, both composites are $\id_\A$ and we have natural isomorphisms $\eta \maps \id_{\A} \cong \mathbb{G}_0 \mathbb{E}_0$ and $\epsilon \maps \mathbb{E}_0 \mathbb{G}_0 \cong \id_{\A}$.
-
-Given a horizontal 1-cell $M$ in $_L \mathbb{C} \textnormal{sp}(\X)$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$L(c_1)$};
-\node (B) at (1,0) {$x$};
-\node (C) at (2,0) {$L(c_2)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i$} (B)
-(C) edge node[above]{$o$} (B);
-\end{tikzpicture}
-\]
-the horizontal 1-cell $\mathbb{E}(M)$ is given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$c_1$};
-\node (B) at (1,0) {$R(x)$};
-\node (C) at (2,0) {$c_2$};
-\node (D) at (1,-0.5) {$x \in F(R(x))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$R(i) \eta_{c_1}$} (B)
-(C) edge node[above]{$R(o) \eta_{c_2}$} (B);
-\end{tikzpicture}
-\]
-and then the horizontal 1-cell $\mathbb{G} \mathbb{E}(M)$ is given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$L(c_1)$};
-\node (B) at (1.5,0) {$x$};
-\node (C) at (3,0) {$L(c_2)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$!_{R(x)}L(R(i)\eta_{c_1})$} (B)
-(C) edge node[above]{$!_{R(x)}L(R(o)\eta_{c_2})$} (B);
-\end{tikzpicture}
-\]
-Then we can find a 2-isomorphism $\eta_M \maps M \xrightarrow{\sim} \mathbb{G}\mathbb{E}(M) $ in $_L \mathbb{C} \textnormal{sp}(\X)$ given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$L(c_1)$};
-\node (B) at (1.5,0) {$x$};
-\node (C) at (3,0) {$L(c_2)$};
-\node (A') at (0,-1) {$L(c_1)$};
-\node (B') at (1.5,-1) {$x$};
-\node (C') at (3,-1) {$L(c_2)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i$} (B)
-(C) edge node[above]{$o$} (B)
-(A') edge node[above]{$!_{R(x)}L(R(i)\eta_{c_1})$} (B')
-(C') edge node[above]{$!_{R(x)}L(R(o)\eta_{c_2})$} (B')
-(A) edge node [left]{$1$} (A')
-(B) edge node [left]{$1$} (B')
-(C) edge node [right]{$1$} (C');
-\end{tikzpicture}
-\]
-where
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (-0.5,0) {$L(c_1)$};
-\node (B) at (1,0) {$L(R(L(c_1)))$};
-\node (C) at (2.5,0) {$L(R(x))$};
-\node (D) at (3.5,0) {$x$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$L(\eta_{c_1})$} (B)
-(B) edge node[above]{$L(R(i))$} (C)
-(C) edge node[above]{$!_{R(x)}$} (D)
-(A) edge[bend right] node [above]{$i$} (D);
-\end{tikzpicture}
-\]
-commutes.
-
-On the other hand, given a horizontal 1-cell $N$ in $F\lCsp$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$c_1$};
-\node (B) at (1,0) {$c$};
-\node (C) at (2,0) {$c_2$};
-\node (D) at (1,-0.5) {$x \in F(c)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$I$} (B)
-(C) edge node[above]{$O$} (B);
-\end{tikzpicture}
-\]
-the horizontal 1-cell $\mathbb{G}(N)$ is given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$L(c_1)$};
-\node (B) at (1,0) {$x$};
-\node (C) at (2,0) {$L(c_2)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$!_c L(I)$} (B)
-(C) edge node[above]{$!_c L(O)$} (B);
-\end{tikzpicture}
-\]
-and then the horizontal 1-cell $\mathbb{E} \mathbb{G}(N)$ is given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$c_1$};
-\node (B) at (1.5,0) {$R(x)$};
-\node (C) at (3,0) {$c_2$};
-\node (D) at (1.5,-0.5) {$x \in F(R(x))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$R(!_c L(I))\eta_{c_1}$} (B)
-(C) edge node[above]{$R(!_c L(O))\eta_{c_2}$} (B);
-\end{tikzpicture}
-\]
-Then we have a 2-isomorphism $\epsilon_N \maps \mathbb{E} \mathbb{G} (N) \xrightarrow{\sim} N$ in $F\lCsp$ given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (D) at (1.5,0.5) {$x \in F(R(x))$};
-\node (D') at (1.5,-1.5) {$x \in F(c)$};
-\node (A) at (0,0) {$c_1$};
-\node (B) at (1.5,0) {$R(x)$};
-\node (C) at (3,0) {$c_2$};
-\node (A') at (0,-1) {$c_1$};
-\node (B') at (1.5,-1) {$c$};
-\node (C') at (3,-1) {$c_2$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$R(!_c L(I))\eta_{c_1}$} (B)
-(C) edge node[above]{$R(!_c L(O))\eta_{c_2}$} (B)
-(A') edge node[above]{$I$} (B')
-(C') edge node[above]{$O$} (B')
-(A) edge node [left]{$1$} (A')
-(B) edge node [left]{$\hat{e}$} (B')
-(C) edge node [right]{$1$} (C');
-\end{tikzpicture}
-\]
-$$\tau \maps F(\hat{e})(x) \to x$$
-where 
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$c_1$};
-\node (B) at (1,0) {$R(L(c_1))$};
-\node (C) at (2.5,0) {$R(L(c))$};
-\node (D) at (3.5,0) {$R(x)$};
-\node (E) at (4.5,0) {$c$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$\eta_{c_1}$} (B)
-(B) edge node[above]{$R(L(I))$} (C)
-(C) edge node[above]{$R(!_c)$} (D)
-(D) edge node[above]{$\hat{e}$} (E)
-(A) edge[bend right] node [above]{$I$} (E);
-\end{tikzpicture}
-\]
-commutes.
-
-\end{comment}
+%!!!Christina: Kenny, is the above comment still relevant? If not, feel free to erase!
 
@@
 CHECK THAT OUR SORT OF EQUIVALENCE OF SYMMETRIC MONOIDAL DOUBLE CATEGORIES IS REALLY THAT USED BY HANSEN AND SHULMAN!!!
-
-IN THE PROOF ABOVE, WE ACTUALLY POTENTIALLY NEED SYMMETRY. DOES IT FOLLOW?
+{\chris In the proof above, we probably need isomorphism. Does it follow?}
 
@@
 Both $\Set$ and $\Graph$ have finite colimits, and the functor $L \maps \Fin\Set \to \Graph$ is left adjoint to the forgetful functor $R \maps \Graph \to \Fin\Set$ that assigns to a graph $G$ its underlying set of vertices $U(G)$.
-Thus, using structured cospans and appealing to \cref{SC}, we get a symmetric monoidal double category $_L \lCsp(\Graph)$ in which:
+Thus, using structured cospans and appealing to \cref{thm:SC}, we get a symmetric monoidal double category $_L \lCsp(\Graph)$ in which:
 \begin{itemize}
@@
 
-This sets the stage for structured cospans: \cref{SC} gives us a symmetric monoidal double category ${}_L \lCsp(\Graph_\La)$ where a horizontal 1-cell is an \define{open $\La$-graph}, also called an \define{$\La$-circuit}: that is, a cospan in $\Graph_\La$ of this form:
+This sets the stage for structured cospans: \cref{thm:SC} gives us a symmetric monoidal double category ${}_L \lCsp(\Graph_\La)$ where a horizontal 1-cell is an \define{open} $\La$-\define{graph}, also called an $\La$-\define{circuit}: that is, a cospan in $\Graph_\La$ of this form:
 \[
@@
 \begin{itemize}
-\item objects being \define{$\La$-graph structures} on $N$: that is, $\La$-graphs where the set of nodes is $N$,
+\item objects being $\La$-\define{graph structures} on $N$: that is, $\La$-graphs where the set of nodes is $N$,
 \item morphisms are morphisms of $\La$-graphs that are the identity on the set of nodes.
@@
 Master and the first author show the existence of a left adjoint $L \maps \Set \to \Petri$ where $\Petri$ is the category whose objects are Petri nets and whose `morphisms are morphisms of Petri nets'.
-They also show that $\Petri$ has finite colimits and thus using Theorem \cref{SC} obtain a symmetric monoidal double category $\lOpen(\Petri)$ of open Petri nets which has:
+They also show that $\Petri$ has finite colimits and thus using Theorem \cref{thm:SC} obtain a symmetric monoidal double category $\lOpen(\Petri)$ of open Petri nets which has:
 \begin{enumerate}
@@
 
-\subsection{2-categories}\label{sec:2cats}
-For standard 2-categorical material, we refer the reader to e.g. \cite{KS} or \cite{DS} for monoidal structures. %!!!Christina: also John's paper on monoidal 2-structures?
-Recall that a \define{pseudofunctor} $F\maps\bicat{A}\to\bicat{B}$ between bicategories $\bicat{A}$ and $\bicat{B}$ is functorial up to coherent natural isomorphism, namely for composable arrows we have $F(g\circ f)\cong Fg\circ Ff$ and $F(1_a)\cong1_{Fa}$ satisfying standard axioms.
-Given pseudofunctors $F,G\maps \bicat{A} \to \bicat{B}$, a \define{pseudonatural transformation} $\sigma$ consists of
-\begin{itemize}
-\item for each object $a \in \bicat{A}$, a morphism $\sigma_a \maps F(a) \to G(a)$ in $\bicat{B}$ 
-\item 
-%for every pair of objects $a$ and $b$ of $\mathbf{A}$, we have natural isomorphisms
-%\[
-%\begin{tikzpicture}[scale=1.5]
-%\node (A) at (0,0) {$\mathbf{A}(a,b)$};
-%\node (B) at (2,0) {$\mathbf{X}(F(a),F(b))$};
-%\node (C) at (0,-1) {$\mathbf{X}(G(a),G(b))$};
-%\node (D) at (2,-1) {$\mathbf{X}(F(a),G(b))$};
-%\node (E) at (1,-0.5) {$\sigma_{a,b} \Nearrow$};
-%\path[->,font=\scriptsize,>=angle 90]
-%(A) edge node[above]{$F$} (B)
-%(B) edge node[right]{$(\sigma_{b})_*$} (D)
-%(A) edge node[left]{$G$} (C)
-%(C) edge node[above]{$(\sigma_a)^*$} (D);
-%\end{tikzpicture}
-%\]
-%where $(\sigma_a)^*$ and $(\sigma_b)_*$ are the functors induced by precomposition and postcompositon, respectively. Thus 
-for each morphism $f \maps a \to b$ in $\mathbf{A}$, an invertible natural 2-morphism $\sigma_f \maps G(f) \sigma_a \xrightarrow{\sim} \sigma_{b} F(f)$ in $\mathbf{B}$
-%:
-%\[
-%\begin{tikzpicture}[scale=1.5]
-%\node (A) at (0,0) {$F(a)$};
-%\node (B) at (1,0) {$F(b)$};
-%\node (C) at (0,-1) {$G(a)$};
-%\node (D) at (1,-1) {$G(b)$};
-%\node (E) at (0.5,-0.5) {$\sigma_f \Nearrow$};
-%\path[->,font=\scriptsize,>=angle 90]
-%(A) edge node[above]{$F(f)$} (B)
-%(B) edge node[right]{$\sigma_{b}$} (D)
-%(A) edge node[left]{$\sigma_a$} (C)
-%(C) edge node[above]{$G(f)$} (D);
-%\end{tikzpicture}
-%\]
-compatible with composition and identities.
-\end{itemize}
-%such that for each composable pair of morphisms $f \maps a \to b$ and $g \maps b \to c$ of $\mathbf{A}$, the following diagrams commute:
-%\[
-%\begin{tikzpicture}[scale=1.5]
-%\node (A) at (0,0.5) {$(G(g)G(f))\sigma_a$};
-%\node (A') at (2,0.5) {$G(g)(G(f) \sigma_a)$};
-%\node (B) at (0,-0.5) {$G(gf) \sigma_a$};
-%\node (C) at (4,0.5) {$G(g) (\sigma_b F(f))$};
-%\node (C') at (4,-0.5) {$\sigma_c F(gf)$};
-%\node (D) at (6,0.5) {$(G(g) \sigma_b) F(f)$};
-%\node (D') at (8,-0.5) {$\sigma_c (F(g)F(f))$};
-%\node (F) at (8,0.5) {$(\sigma_c F(g)) F(f)$};
-%\path[->,font=\scriptsize,>=angle 90]
-%(A) edge node[above]{$a'$} (A')
-%(A) edge node[left]{$\psi 1_{\sigma_a}$} (B)
-%(A') edge node[above]{$1_{G(g)} \sigma_f$} (C)
-%(B) edge node[above]{$\sigma_{gf}$} (C')
-%(C) edge node [above] {${a'}^{-1}$} (D)
-%(D') edge node [above] {$1_{\sigma_c} \phi$} (C')
-%(D) edge node [above] {$\sigma_g 1_{F(f)}$} (F)
-%(F) edge node [right] {$a'$} (D');
-%\end{tikzpicture}
-%\]
-%\[
-%\begin{tikzpicture}[scale=1.5]
-%\node (A) at (0,0) {$1_{G(a)} \sigma_a$};
-%\node (B) at (1,1) {$G(1_a) \sigma_a$};
-%\node (C) at (2,0) {$\sigma_a F(1_a)$};
-%\node (D) at (0.5,-1) {$\sigma_a$};
-%\node (E) at (1.5,-1) {$\sigma_a 1_{F(a)}$};
-%\path[->,font=\scriptsize,>=angle 90]
-%(A) edge node[left]{$\psi 1_{\sigma_a}$} (B)
-%(B) edge node[right]{$\sigma_{1_a}$} (C)
-%(A) edge node [left] {$\ell'$} (D)
-%(D) edge node [above] {${\rho'}^{-1}$} (E)
-%(E) edge node [right] {$1_{\sigma_a} \phi$} (C);
-%\end{tikzpicture}
-%\]
-%Christina: I removed the above, they are not needed I believe. Check again in the end.
-We denote by $[\bicat{A},\bicat{B}]_\pse$ the 2-category 
-of pseudofunctors, pseudonatural transformations and modifications.
-
-A \define{monoidal} bicategory $\bicat{A}$ comes with a pseudofunctor $\otimes\maps\bicat{A}\times\bicat{A}\to\bicat{A}$ and a unit object $I$ that are associative and unital up to coherent equivalence.
+\subsection{Bicategories}
+\label{subsec:bicats}
+
+{\chris There used to be references for more details on the material that follows. Why would we not provide them?}
+A \define{monoidal} bicategory $\bA$ comes with a pseudofunctor $\otimes\maps\bA\times\bA\to\bA$ and a unit object $I$ that are associative and unital up to coherent equivalence.
 A \define{braided} monoidal bicategory comes with a pseudonatural equivalence $\beta_{a,b}\maps a\ot b\to b\ot a$ and appropriate invertible modifications; it is \define{sylleptic} if there is an appropriate invertible modification $1_{a\ot b}\Rrightarrow\beta_{b,a}\circ\beta_{a,b}$ and it is \define{symmetric} if one further axiom holds.
-A \define{lax monoidal} pseudofunctor between monoidal bicategories $F\maps\bicat{A}\to\bicat{B}$ is a pseudofunctor equipped with pseudonatural transformations with components $\mu_{a,b}\maps Fa\otimes Fb\to F(a\otimes b)$ and $\mu_0\maps I\to FI$ along with coherent invertible modifications for associativity and unitality.
-This is commonly also called `weak monoidal' pseudofunctor.
-A \define{braided lax monoidal} pseudofunctor between braided monoidal bicategories comes with an appropriate invertible modification with components $F(\beta_{a,b})\circ \mu_{a,b}\cong\mu_{b,a}\circ \beta_{Fa,Fb}$; a \define{sylleptic lax monoidal} pseudofunctor satisfies one extra condition and a \define{symmetric lax monoidal} pseudofunctor between symmetric monoidal bicategories is just a sylleptic one.
-RIGHT???
+A \define{lax monoidal} pseudofunctor between monoidal bicategories $F\maps\bA\to\bB$ is a pseudofunctor equipped with pseudonatural transformations with components $\phi_{a,b}\maps Fa\otimes Fb\to F(a\otimes b)$ and $\phi_0\maps I\to FI$ along with coherent invertible modifications for associativity and unitality.
+A \define{braided lax monoidal} pseudofunctor between braided monoidal bicategories comes with an appropriate invertible modification with components $F(\beta_{a,b})\circ \phi_{a,b}\cong\phi_{b,a}\circ \beta_{Fa,Fb}$; a \define{sylleptic lax monoidal} pseudofunctor satisfies one extra condition and a \define{symmetric lax monoidal} pseudofunctor between symmetric monoidal bicategories is just a sylleptic one.
 

### 2020-11-20 cospans.tex
proof of 3.2 should be complete!

@@
 \end{displaymath}
-In similar ways we can construct the initial object and coproducts in a Grothendieck category.
+In similar ways we can construct the initial object and coproducts in a Grothendieck category, namely
+\begin{equation}\label{eq:fibrewisecoprod}
+(a,x)+(b,y)=\left(a+ b,F(\iota_a)x+F(\iota_b)y\right), \qquad 
+ 0_{\inta F}=\left(0_A,0_{F(0_A)}\right)
+\end{equation}
+where $\iota_a:a\to a+b\leftarrow b:\iota_b$ are the sum inclusions in $\A$.
 
@@
 
+\begin{rmk}\label{rmk:interestingrmk}
 Notice a subtlety in the above formulation.
@@
 If this fibrewise monoidal structure happens to itself be cocartesian, then it is necessarily isomorphic to any other cocartesian monoidal structure on the fibres, by the universal property of colimits.
-Therefore, we can simplify the above assumption to that in \cref{thm:equiv} without having to specify that the structures came from monoidality of the pseudofunctor.
-However, we \emph{will} use the formulation of coproducts and initial object in terms of the monoidal structure of $F$, and that is why the correspondence in \cref{lem:MonGroth} is necessary.
-DOES THIS MAKE SENSE TO ALL??
+Therefore, we can simplify the above assumption to that in \cref{thm:equiv} without having to specify that the structures came from monoidality of the pseudofunctor, although we \emph{will} use the formulation of coproducts and initial object in terms of the monoidal structure of $F$.
+For example, in that case, the coproducts induced in the Grothendieck category by the fibrewise ones as in \cref{eq:fibrewisecoprod} are equivalently given by \cref{eq:explicitstructure2}.
+\end{rmk}
 
@@
 That decoration is isomorphic to that of \cref{eq:1} due to the following diagram
-\begin{displaymath}
+\begin{equation}\label{eq:isomorphismdiag}
  \begin{tikzcd}
@@
  \end{tikzcd}
-\end{displaymath}
+\end{equation}
 where the bottom composite is the fibrewise coproduct in $F(m+_bn)$ as in \cref{eq:explicitstructure1}.
@@
 \lE(M)\ot\lE(M')&\;\stackrel{\cref{eq:tensordecoration}}{=}\;a+a'\xrightarrow{i+i'}m+m'\xleftarrow{o+o'}b+b' \textrm{ with }\mathbf{1}\xrightarrow{x\times x'}F(m)\times F(m')\xrightarrow{\phi_{m,m'}}F(m+m') \\
-\lE(M\ot M')&\;\stackrel{\cref{eq:tensorstuctured}}{=}\;\lE\Big((a+a',\bot_{a+a'})\to\underbrace{(m+m',\phi_{m,m'}(x,x'))}_{\cref{eq:explicitstructure2}}\leftarrow(b+b',\bot_{b+b'})\Big)%=a+a'\xrightarrow{i+i'}m+m'\xleftarrow{o+o'}b+b' \textrm{ with }\phi_{m,m'}(x,x')
+\lE(M\ot M')&\;\stackrel{\cref{eq:tensorstuctured}}{=}\;\lE\Big((a+a',\bot_{a+a'})\to\underbrace{(m+m',F(\iota_m)x+F(\iota_{m'})x')}_{\cref{eq:fibrewisecoprod}}\leftarrow(b+b',\bot_{b+b'})\Big)%=a+a'\xrightarrow{i+i'}m+m'\xleftarrow{o+o'}b+b' \textrm{ with }\phi_{m,m'}(x,x')
 \end{align*}
-which are essentially the same.
-{\chris Well they look equal to me...thoughts?} Moreover, the monoidal unit for the category of arrows of $F\lCsp$ is $0_\A\xrightarrow{\raisebox{-3pt}[0pt][0pt]{$=$}}0_\A\xleftarrow{\raisebox{-3pt}[0pt][0pt]{$=$}}0_\A$ with the trivial decoration
-$$\mathbf{1}\xrightarrow{\phi_0}F(0_A)\xrightarrow{F(\mathrm{id})}F(0_A)$$
-which is essentially the same as $\lE((0_A,\phi_0)\xrightarrow{\raisebox{-3pt}[0pt][0pt]{$=$}}(0_A,\phi_0)\xleftarrow{\raisebox{-3pt}[0pt][0pt]{$=$}}(0_A,\phi_0))$ again by \cref{eq:explicitstructure2}.
+which are uniquely isomorphic $F(\iota_m)x+F(\iota_{m'})\cong \phi_{m,m'}(x,x')$ in an analogous way to \cref{eq:isomorphismdiag}, as also discussed in \cref{rmk:interestingrmk}.
+Moreover, the monoidal unit for the category of arrows of $F\lCsp$ is $0_\A\xrightarrow{\raisebox{-3pt}[0pt][0pt]{$=$}}0_\A\xleftarrow{\raisebox{-3pt}[0pt][0pt]{$=$}}0_\A$ with the trivial decoration $\phi_0\maps \mathbf{1}\to F(0_A)$,
+which is an initial object and as such isomorphic to $0_{F(0)}$
+%=\lE((0_A,)\xrightarrow{\raisebox{-3pt}[0pt][0pt]{$=$}}(0_A,\phi_0)\xleftarrow{\raisebox{-3pt}[0pt][0pt]{$=$}}(0_A,\phi_0))$
+again by \cref{eq:explicitstructure2} and the discussion in \cref{rmk:interestingrmk}.
 It can be verified that with the above structure, $\lE_1$ is also a braided monoidal functor, and the rest of the axioms of \cref{defn:monoidal_double_functor} hold.

### 2020-11-20 cospans.tex
lots more changes...

@@
 % in LaTeX
-% 2020/11/19
-% 2020/11/12 - JB
+% 2020/11/20
 
@@
 %\newline
-%Let $P = (s_1,t_1 \maps T_1 \to \mathbb{N}(S_1))$ and $Q = (s_2,t_2 \maps T_2 \to \mathbb{N}(S_2))$.
+%Let $P = (s_1,t_1 \maps T_1 \to \N(S_1))$ and $Q = (s_2,t_2 \maps T_2 \to \N(S_2))$.
 We want to show that the functor $F \maps \textrm{Petri} \to \textrm{CMC}$ preserves pushouts of cospans of the form $$P \xleftarrow{} L(Y) \xrightarrow{} Q$$ meaning that $F(P+_{L(Y)} Q) \cong F(P) +_{F(L(Y))} F(Q)$.
@@
 $\textrm{Ob}(F(P)+_{F(L(Y))} F(Q))$?
-Well, $\textrm{Ob}(F(P+_{L(Y)}Q)) = \mathbb{N}(S_1+_Y S_2)$ and $\textrm{Ob}(F(P)+_{F(L(Y))} F(Q))= \mathbb{N}(S_1) +_{\mathbb{N}(Y)} \mathbb{N}(S_2)$.
+Well, $\textrm{Ob}(F(P+_{L(Y)}Q)) = \N(S_1+_Y S_2)$ and $\textrm{Ob}(F(P)+_{F(L(Y))} F(Q))= \N(S_1) +_{\N(Y)} \N(S_2)$.
 
@@
 
-\begin{rmk}\label{rmk:interestingrmk}
 Notice a subtlety in the above formulation.
@@
 For example, in that case, the coproducts induced in the Grothendieck category by the fibrewise ones as in \cref{eq:fibrewisecoprod} are equivalently given by \cref{eq:explicitstructure2}.
-\end{rmk}
 
@@
 \end{align*}
-which are uniquely isomorphic $F(\iota_m)x+F(\iota_{m'})\cong \phi_{m,m'}(x,x')$ in an analogous way to \cref{eq:isomorphismdiag}, as also discussed in \cref{rmk:interestingrmk}.
+which are uniquely isomorphic $F(\iota_m)x+F(\iota_{m'})\cong \phi_{m,m'}(x,x')$ in an analogous way to \cref{eq:isomorphismdiag}, as also discussed after \cref{cor:fcocMonGroth}.
 Moreover, the monoidal unit for the category of arrows of $F\lCsp$ is $0_\A\xrightarrow{\raisebox{-3pt}[0pt][0pt]{$=$}}0_\A\xleftarrow{\raisebox{-3pt}[0pt][0pt]{$=$}}0_\A$ with the trivial decoration $\phi_0\maps \mathbf{1}\to F(0_A)$,
@@
 %=\lE((0_A,)\xrightarrow{\raisebox{-3pt}[0pt][0pt]{$=$}}(0_A,\phi_0)\xleftarrow{\raisebox{-3pt}[0pt][0pt]{$=$}}(0_A,\phi_0))$
-again by \cref{eq:explicitstructure2} and the discussion in \cref{rmk:interestingrmk}.
+again by \cref{eq:explicitstructure2} and the discussion after \cref{cor:fcocMonGroth}.
 It can be verified that with the above structure, $\lE_1$ is also a braided monoidal functor, and the rest of the axioms of \cref{defn:monoidal_double_functor} hold.
@@
 We call elements of $E$ \define{edges} and elements of $N$ \define{nodes}.
-There is a category $\Graph$ with graphs as objects, where a morphism from the graph $s,t\maps E \to N$ to the graph $s',t' \maps E' \to N'$ is a pair of functions $f \maps E \to E', g \maps N \to N'$ such that these diagrams commute:
+There is a category $\Graph$ where the objects are graphs and a morphism from the graph $s,t\maps E \to N$ to the graph $s',t' \maps E' \to N'$ is a pair of functions $f \maps E \to E', g \maps N \to N'$ such that these diagrams commute:
 \[
@@
 
-We can make $F$ into a symmetric lax monoidal functor $F \maps (\Fin\Set, +) \to (\Cat,\times)$ by equipping it with suitable functors 
+We can make $F$ into a symmetric lax monoidal pseudofunctor $F \maps (\Fin\Set, +) \to (\Cat,\times)$ by equipping it with suitable functors 
 \[   \phi_{N,N'} \maps F(N) \times F(N') \to F(N+N'), \qquad \phi_0 \maps F(\emptyset) \to 1 \in \Cat. \]  
@@
 In other words, it sends a pair of graph structures to their `disjoint union'.
-
-It is well-known, and easy to check, that the Grothendieck category $\inta F$ is isomorphic to the category $\Graph$.
+MORE ABOUT THE WEAK MONOIDALITY!!!
+
+It is well known, and easy to check, that the Grothendieck category $\inta F$ is isomorphic to the category $\Graph$.
 The other side of this observation is that the opfibration $U \maps \inta F \to \Fin\Set$ is isomorphic to the forgetful functor $R \maps \Graph \to \Fin\Set$.
@@
 
-We can also use structured or decorated cospans to describe electrical circuits \cite{BC,BCR,BF}.
-The key idea is to use graphs with labeled edges, where the labels can stand for resistors with any chosen resistance, capacitors with any chosen capacitance, or other circuit elements.
+Structured and decorated cospans are a powerful tool for studying categories where the morphisms are electrical circuits---see \cite{BCR,BF} and \cite[Section 6.1]{BC}.
+The key idea is to use open graphs with labeled edges to describe circuits, where the labels can stand for resistors with any chosen resistance, capacitors with any chosen capacitance, or other circuit elements.
 The whole theory of open graphs discussed in the previous section can be recapitulated for labeled graphs.
-Since everything works the same way, we can be brief.
+Since the abstract formalism works the same way, we can be brief.
+Concrete applications of this formalism are discussed in the references.
 
@@
 Define an $\La$-\define{graph} to be a graph $s,t\maps E\to N$ equipped with a function $\ell \maps E \to \La$.
-There is a category $\Graph_\La$ with $\La$-graphs as objects, where a morphism from the $\La$-graph
+There is a category $\Graph_\La$ where the objects are $\La$-graphs and a morphism from the $\La$-graph
  \[ \xymatrix{\La & E \ar@<2.5pt>[r]^{s} \ar@<-2.5pt>[r]_{t} \ar[l]_{\ell} & N} \]
@@
 \[
-\scalebox{0.6}{
+\scalebox{1}{
 \begin{tikzpicture}
@@
 
-		\node [style=none] (X) at (-3,1.8) {$1$};
+		\node [style=none] (X) at (-3,1.8) {$X$};
 		\node [style=inputdot] (inI) at (-2.8,0) {};
 
-		\node [style=none] (Z) at (3,1.8) {$3$};
+		\node [style=none] (Z) at (3,1.8) {$Y$};
 	 \node [style=inputdot] (outI') at (2.8,1) {};
@@
 \]
-The edges here can represent wires, with the positive real numbers labeling them serving to describe the resistance of a resistor on each wire.
-The points in the boxes represent `terminals': that is, points where we allow ourselves to attach a wire from another circuit.
+The edges here represent wires, with the positive real numbers labeling them serving to describe the resistance of resistors on the wires.
+The elements of the sets $X$ and $Y$ represent `terminals': that is, points where we allow ourselves to attach a wire from another circuit.
 
@@
 \subsection{Petri nets}
-In a previous work, Master and the first author used structured cospans to obtain a symmetric monoidal double category of `open Petri nets' \cite{BM}.
-A Petri net is given by a diagram in $\Set$ of the form:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (B) at (1,0) {$T$};
-\node (C) at (2,0) {$\mathbb{N}[S].$};
-\path[->,font=\scriptsize,>=angle 90]
-(B)edge[bend left] node[above]{$s$}(C)
-(B)edge[bend right] node[below]{$t$}(C);
-\end{tikzpicture}
-\]
-Here $S$ is the set of \define{places}, $T$ is the set of \define{transitions}, and $\mathbb{N}[S]$ is the underlying set of the free commutative monoid on $S$.
-Each transition then has a formal linear combination of species given by an element of $\mathbb{N}[S]$ as its source and target as prescribed by the functions $s$ and $t$, respectively.
-An example of a Petri net is given by:
+\label{subsec:petri}
+
+Petri nets are widely used as models of systems in computer science, chemistry, population biology and epidemiology \cite{GiraultValk,Peterson}.
+Structured cospans have been used to define a symmetric monoidal double category of `open Petri nets' \cite{BM}.
+We can also use decorated cospans to construct this double category.
+Again this example is very similar to the example of open graphs.
+
+ A \define{Petri net} is a pair of sets $S$ and $T$ and functions $s,t \maps T \to \N[S]$.
+Here $S$ is the set of \define{places}, $T$ is the set of \define{transitions}, and $\N[S]$ is the underlying set of the free commutative monoid on $S$.
+Each transition thus has a formal sum of places as its source and target as prescribed by the functions $s$ and $t$, respectively.
+Here is an example:
 \[
@@
 		\node [style=species] (T) at (0,-1) {O};
-		\node [style=transition] (W) at (2,0) {$\alpha$};
+		\node [style=transition] (W) at (2,0) {$\phantom{\Big|}\alpha$\phantom{\Big|}};
 		\node [style=species] (Water) at (4,0) {$\textnormal{H}_2$O};
@@
 
+\bibitem{GiraultValk} C.\ Girault and R.\ Valk, \textsl{Petri Nets for Systems Engineering: a Guide to Modeling, Verification, and Applications}, Springer, Berlin, 2013.
+
 \bibitem{Gray} J. \ Gray, Fibred and Cofibred categories, \emph{Proc. Conf. Categorical Algebra} (La Jolla, California, 1965), 21---83, New York, 1966
@@
 %\bibitem{Panan} F.\ Clerc, H.\ Humphrey and P.\ Panangaden, Bicategories of Markov processes,  to appear.
+
+\bibitem{Peterson} J.\ L.\ Peterson, \textit{Petri Net Theory and the Modeling of Systems}, Prentice--Hall, New Jersey, 1981.
 

### 2020-11-21 cospans.tex
work on Petri net section

@@
 
-Each set of species $S$ gives rise to a discrete Petri net $L(S)$ with $S$ as its set of species and no transitions.
-Master and the first author show the existence of a left adjoint $L \maps \Set \to \Petri$ where $\Petri$ is the category whose objects are Petri nets and whose `morphisms are morphisms of Petri nets'.
-They also show that $\Petri$ has finite colimits and thus using Theorem \cref{thm:SC} obtain a symmetric monoidal double category $\lOpen(\Petri)$ of open Petri nets which has:
-\begin{enumerate}
-\item{objects given by sets,}
-\item{vertical 1-morphisms given by functions,}
-\item{horizontal 1-cells as open Petri nets which are given by cospans in $\Petri$ of the form:
+There is a category $\Petri$ with Petri nets as objects, where a morphism from the Petri net 
+$s, t \maps T \to \N[S]$ to the Petri net $s', t' \maps T' \to \N[S']$ is a pair of functions $f \maps T \to T', g \maps S \to S'$ such that the following diagrams commute:
+	\[
+	\xymatrix{ 
+		T \ar[d]_f  \ar[r]^-{s} & \N[S] \ar[d]^-{\N[g]} \\	
+		T' \ar[r]^-{s'} & \N[S'] 
+	}
+	\qquad
+	\xymatrix{ 
+		T \ar[d]_f  \ar[r]^-{t} & \N[S] \ar[d]^-{\N[g]} \\	
+		T' \ar[r]^-{t'} & \N[S'] . 
+	}
+	\]
+There is a functor $R \maps \Petri \to \Set$ sending any Petri net to its set of places, and this has
+a left adjoint $L \maps \Set \to \Petri$ sending any set $S$ to the Petri net with $S$ as its set of species and no transitions \cite[Lemma 11]{BM}.
+Since both $\Set$ and $\Petri$ have finite colimits and $L$ preserves them, Theorem \cref{thm:SC} yields a symmetric monoidal double category $\lOpen(\Petri)$ of open Petri nets which has:
+\begin{itemize}
+\item objects given by sets,
+\item vertical 1-morphisms given by functions,
+\item horizontal 1-cells as \define{open Petri nets}, which are cospans in $\Petri$ of the form:
 \[
@@
 \path[->,font=\scriptsize,>=angle 90]
-(D) edge node [above] {$I$} (E)
-(F) edge node [above] {$O$} (E);
-\end{tikzpicture}
-\]
-and}
-\item{2-morphisms as maps of cospans in $\Petri$ of the form:
+(D) edge node [above] {$i$} (E)
+(F) edge node [above] {$o$} (E);
+\end{tikzpicture}
+\]
+\item 2-morphisms as maps of cospans in $\Petri$ of the form:
 \[
@@
 \node (E') at (3,-1) {$L(X_2)$};
-\node (F') at (5,-1) {$L(Y_2)$};
+\node (F') at (5,-1) {$L(Y_2)$.};
 \node (G') at (4,-1) {$P_2$};
@@
 \]
-}
-\end{enumerate}
+\end{itemize}
 We can also obtain a similar double category using decorated cospans: define a pseudofunctor $F \maps \Set \to \Cat$ where given a set $s$, $F(s)$ is the category of all Petri net structures with $s$ as its set of species.

### 2020-11-22 cospans.tex
Fixed some small typos all throughout the paper

@@
 This led Fong to develop a theory of `decorated' cospans \cite{Fong}.
-Given a category $\A$ with finite colimits, a symmetric lax monoidal functor $F \maps (\A,+) \to (\textsf{Set},\times)$ can be used to equip the apex $m$ of a cospan in $\A$ with some extra data: an element $d \in F(m)$, which we call a \textbf{decoration}.
+Given a category $\A$ with finite colimits, a symmetric lax monoidal functor $F \maps (\A,+) \to (\textsf{Set},\times)$ can be used to equip the apex $m$ of a cospan in $\A$ with some extra data: an element $x \in F(m)$, which we call a \textbf{decoration}.
 Thus a \define{decorated cospan} is a pair:
@@
 \node (C) at (2,0) {$b$,};
-\node (E) at (4,0) {$d \in F(m)$.};
+\node (E) at (4,0) {$x \in F(m)$.};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-We might hope to do this using symmetric lax monoidal functor $F \maps (\Fin\Set, +) \to (\Set, \times)$ assigning to each finite set $m$ the set of all graphs with $m$ as their set of nodes    But this hope is doomed, for reasons painstakingly explained in \cite[Sec.\ 5]{BC}.
+We might hope to do this using a symmetric lax monoidal functor $F \maps (\Fin\Set, +) \to (\Set, \times)$ assigning to each finite set $m$ the set of all graphs with $m$ as their set of nodes    But this hope is doomed, for reasons painstakingly explained in \cite[Sec.\ 5]{BC}.
 There is really a \emph{category} of graphs with $m$ as their set of nodes, and trying to treat it as a mere set does not work.
@@
 \]
-together with a morphism $\tau \maps F(h)(m) \to m'$ in $F(m')$.
+together with a morphism $\tau \maps F(h)(x) \to m'$ in $F(x')$.
 \end{itemize}
@@
 (F) edge node[above]{$o$} (G)
-(E) edge node[left]{$L(\alpha)$} (E')
-(F) edge node[right]{$L(\beta)$} (F')
-(G) edge node[left]{$f$} (G')
+(E) edge node[left]{$L(f)$} (E')
+(F) edge node[right]{$L(g)$} (F')
+(G) edge node[left]{$\alpha$} (G')
 (E) edge node[above]{$i$} (G)
@@
 We also give sufficient conditions for a decorated cospan double category to be equivalent to a structured cospan double category. 
-Suppose $\A$ has finite colimits and $F \maps (\A , +) \to (\Cat, \times)$ is 
+Suppose $\A$ has finite colimits and $F \maps (\A , +) \to (\Cat, \times)$ is a 
 symmetric lax monoidal pseudofunctor.   Any such pseudofunctor gives an opfibration 
@@
 From the accompanying left adjoint $L \maps \A \to \X$, we  construct a symmetric monoidal double category ${}_L \lCsp(\X)$ of structured cospans.
-Finally, in \cref{thm:equiv} we prove that this structured cospan double category ${}_L \lCsp(\X)$ is equivalent to the decorated cospan double category $F \lCospan$.
+Finally, in \cref{thm:equiv} we prove that this structured cospan double category ${}_L \lCsp(\X)$ is equivalent to the decorated cospan double category $F \lCsp$.
 
@@
 Following Shulman \cite{Shulman2008}, vertical composition in our double categories is strictly associative, while horizontal composition need not be.
-We use sans-serif font like $\C$ for categories, boldface like $\B$ for bicategories or 2-categories, and blackboard bold like $\lD$ for double categories.
+We use sans-serif font like $\C$ for categories, boldface like $\mathbf{B}$ for bicategories or 2-categories, and blackboard bold like $\lD$ for double categories.
 We also use blackboard
@@
 \begin{thm}\label{thm:decorated_cospans}
-Let $\A$ be a category with chosen finite colimits and $F \maps \A \to \Cat$ a lax monoidal pseudofunctor. Then there exists a double category $F\lCsp$ in which
+Let $\A$ be a category with finite colimits and $F \maps \A \to \Cat$ a lax monoidal pseudofunctor. Then there exists a double category $F\lCsp$ in which
 \begin{itemize}
@@
 \begin{thm}\label{DC}
-Let $\A$ be a category with chosen finite colimits and $F \maps \A \to \Cat$ a symmetric lax monoidal pseudofunctor.
+Let $\A$ be a category with finite colimits and $F \maps \A \to \Cat$ a symmetric lax monoidal pseudofunctor.
 Then the double category $F\lCsp$ of Theorem \ref{thm:decorated_cospans} is symmetric monoidal, where
 \begin{enumerate}
-\item{the tensor product of two objects $a$ and $b$ is their chosen coproduct $a+b$ in $\A$,}
+\item{the tensor product of two objects $a$ and $b$ is their coproduct $a+b$ in $\A$,}
 \item{the tensor product of two vertical 1-morphisms $f \colon a \to b$ and $f' \colon a' \to b'$ is the vertical 1-morphism $f+f' \colon a+a' \to b+b'$,}
-\item{the tensor product of two horizontal 1-cells $M$ and $N$:
+\item{the tensor product of two horizontal 1-cells $M_1$ and $M_2$:
 \[
@@
 \]
-is the horizontal 1-cell $M \otimes N$:
+is the horizontal 1-cell $M_1 \otimes M_2$:
 \[
@@
 \begin{thm}\label{thm:SC}
-Given categories $\X$ and $\A$ with finite colimits and $L \maps \A \to \X$ a functor preserving
+Given categories $\A$ and $\X$ with finite colimits and $L \maps \A \to \X$ a functor preserving
 finite colimits, there is a symmetric monoidal double category $_L\lCsp(\X)$ in which
@@
 \item an object is an object of $\A$,
-\item a vertical morphism is a morphism of $\A$,
+\item a vertical 1-morphism is a morphism of $\A$,
 \item a horizontal 1-cell from $a$ to $b$ is a cospan in $\X$ of the form
@@
  F(\sigma_a)x\ar[ur] & & F(\sigma_c)z\ar[ul] \\
- & F(\sigma_a)(Ff(y))\cong F(\sigma_n)(Fg(y))\ar[ul,"F(\sigma_a)k"]\ar[ur,"F(\sigma_c)\ell"'] &
+ & F(\sigma_a)(Ff(y))\cong F(\sigma_c)(Fg(y))\ar[ul,"F(\sigma_a)k"]\ar[ur,"F(\sigma_c)\ell"'] &
  \end{tikzcd}
@@
 Explicitly, they consist of two pairs of morphisms
+%%% Not sure what v is in the above line unless you mean x?
 \begin{equation}\label{eq:scsphor1cell}
@@
 whereas a 2-morphism of $L$-structured cospans as above is mapped to the underlying cospan 2-morphism in $\A$
+%%% We should call these "cospan 2-morphism"s maps of cospans to be consistent with previous work
 \begin{displaymath}
@@
 \begin{proof}
-We show that any vertical 1-morphism $f \maps c \to c'$ in $F\lCsp$ has a companion and a conjoint.  This horizontal 1-cell $\hat{f}$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$c$};
-\node (B) at (1,0) {$c'$};
-\node (C) at (2,0) {$c'$};
-\node (D) at (1,-0.5) {$!_{c'} \in F(c')$};
+We show that any vertical 1-morphism $f \maps a \to b'$ in $F\lCsp$ has a companion and a conjoint.  This horizontal 1-cell $\hat{f}$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$a$};
+\node (B) at (1,0) {$b$};
+\node (C) at (2,0) {$b$};
+\node (D) at (1,-0.5) {$\bot_{b} \in F(b)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$c$};
-\node (A') at (0,-0.5) {$c'$};
-\node (B) at (1,0.5) {$c'$};
-\node (C) at (2,0.5) {$c'$};
-\node (C') at (2,-0.5) {$c'$};
-\node (D) at (1,-0.5) {$c'$};
-\node (E) at (3,0.5) {$!_{c'} \in F(c')$};
-\node (F) at (3,-0.5) {$!_{c'} \in F(c')$};
-\node (G) at (5,0.5) {$c$};
-\node (H) at (6,0.5) {$c$};
-\node (I) at (7,0.5) {$c$};
-\node (G') at (5,-0.5) {$c$};
-\node (H') at (6,-0.5) {$c'$};
-\node (I') at (7,-0.5) {$c'$};
-\node (J) at (8,0.5) {$!_{c} \in F(c)$};
-\node (K) at (8,-0.5) {$!_{c'} \in F(c')$};
-\node (L) at (1,-1) {$\tau_{1_{c'}} = 1_{!_{c'}}$};
-\node (M) at (6,-1) {$\tau_f \maps F(f)(!_c) \to !_{c'}$};
+\node (A) at (0,0.5) {$a$};
+\node (A') at (0,-0.5) {$b$};
+\node (B) at (1,0.5) {$b$};
+\node (C) at (2,0.5) {$b$};
+\node (C') at (2,-0.5) {$b$};
+\node (D) at (1,-0.5) {$b$};
+\node (E) at (3,0.5) {$\bot_{b} \in F(b)$};
+\node (F) at (3,-0.5) {$\bot_{b} \in F(b)$};
+\node (G) at (5,0.5) {$a$};
+\node (H) at (6,0.5) {$a$};
+\node (I) at (7,0.5) {$a$};
+\node (G') at (5,-0.5) {$a$};
+\node (H') at (6,-0.5) {$b$};
+\node (I') at (7,-0.5) {$b$};
+\node (J) at (8,0.5) {$\bot_{a} \in F(a)$};
+\node (K) at (8,-0.5) {$\bot_{b} \in F(b)$};
+\node (L) at (1,-1) {$\tau_{1_{b}} = 1_{\bot_{b}}$};
+\node (M) at (6,-1) {$\tau_f \maps F(f)(\bot_a) \to \bot_{b}$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \begin{tikzpicture}[scale=1.5]
-\node (N) at (0,1.5) {$c$};
-\node (O) at (1,1.5) {$c$};
-\node (P) at (2,1.5) {$c$};
-\node (Q) at (-1,1.5) {$!_c \in F(c)$};
-\node (A) at (0,0.5) {$c$};
-\node (A') at (0,-0.5) {$c'$};
-\node (B) at (1,0.5) {$c'$};
-\node (C) at (2,0.5) {$c'$};
-\node (C') at (2,-0.5) {$c'$};
-\node (D) at (1,-0.5) {$c'$};
-\node (E) at (-1,0.5) {$!_{c'} \in F(c')$};
-\node (F) at (-1,-0.5) {$!_{c'} \in F(c')$};
-\node (G) at (4,1) {$c$};
-\node (H) at (5,1) {$c$};
-\node (I) at (6,1) {$c$};
-\node (G') at (4,0) {$c'$};
-\node (H') at (5,0) {$c'$};
-\node (I') at (6,0) {$c'$};
-\node (J) at (7,1) {$!_{c} \in F(c)$};
-\node (K) at (7,0) {$!_{c'} \in F(c')$};
-\node (Q) at (1,-1) {$\tau_f \maps F(f)(!_c) \to !_{c'}$};
-\node (L) at (1,-1.5) {$\tau_{c'} = 1_{!_{c'}}$};
-\node (M) at (5,-0.5) {$\tau_f \maps F(f)(!_c) \to !_{c'}$};
+\node (N) at (0,1.5) {$a$};
+\node (O) at (1,1.5) {$a$};
+\node (P) at (2,1.5) {$a$};
+\node (Q) at (-1,1.5) {$\bot_a \in F(a)$};
+\node (A) at (0,0.5) {$a$};
+\node (A') at (0,-0.5) {$b$};
+\node (B) at (1,0.5) {$b$};
+\node (C) at (2,0.5) {$b$};
+\node (C') at (2,-0.5) {$b$};
+\node (D) at (1,-0.5) {$b$};
+\node (E) at (-1,0.5) {$\bot_{b} \in F(b)$};
+\node (F) at (-1,-0.5) {$\bot_{b} \in F(b)$};
+\node (G) at (4,1) {$a$};
+\node (H) at (5,1) {$a$};
+\node (I) at (6,1) {$a$};
+\node (G') at (4,0) {$b$};
+\node (H') at (5,0) {$b$};
+\node (I') at (6,0) {$b$};
+\node (J) at (7,1) {$\bot_{a} \in F(a)$};
+\node (K) at (7,0) {$\bot_{b} \in F(b)$};
+\node (Q) at (1,-1) {$\tau_f \maps F(f)(\bot_a) \to \bot_{b}$};
+\node (L) at (1,-1.5) {$\tau_{b} = 1_{\bot_{b}}$};
+\node (M) at (5,-0.5) {$\tau_f \maps F(f)(\bot_a) \to \bot_{b}$};
 \node (R) at (3,0.5) {$=$};
@@
 \begin{tikzpicture}[scale=1.5]
-\node (G) at (-1,0.5) {$c$};
-\node (H) at (-1,-0.5)  {$c'$};
-\node (I) at (-2,0.5) {$c$};
-\node (J) at (-2,-0.5) {$c$};
-\node (A) at (0,0.5) {$c$};
-\node (A') at (0,-0.5) {$c'$};
-\node (B) at (1,0.5) {$c'$};
-\node (C) at (2,0.5) {$c'$};
-\node (C') at (2,-0.5) {$c'$};
-\node (D) at (1,-0.5) {$c'$};
-\node (E) at (1,1) {$!_{c'} \in F(c')$};
-\node (F) at (1,-1) {$!_{c'} \in F(c')$};
-
-\node (L) at (1,-1.5) {$\tau_{c'} = 1_{!_{c'}}$};
-\node (E') at (-1,1) {$!_{c} \in F(c)$};
-\node (F') at (-1,-1) {$!_{c'} \in F(c')$};
-
-\node (L') at (-1,-1.5) {$\tau_{f} \maps F(f)(!_c) \to !_{c'}$};
-
+\node (G) at (-1,0.5) {$a$};
+\node (H) at (-1,-0.5)  {$b$};
+\node (I) at (-2,0.5) {$a$};
+\node (J) at (-2,-0.5) {$a$};
+\node (A) at (0,0.5) {$a$};
+\node (A') at (0,-0.5) {$b$};
+\node (B) at (1,0.5) {$b$};
+\node (C) at (2,0.5) {$b$};
+\node (C') at (2,-0.5) {$b$};
+\node (D) at (1,-0.5) {$b$};
+\node (E) at (1,1) {$\bot_{b} \in F(b)$};
+\node (F) at (1,-1) {$\bot_{b} \in F(b)$};
+\node (L) at (1,-1.5) {$\tau_{b} = 1_{\bot_{b}}$};
+\node (E') at (-1,1) {$\bot_{a} \in F(a)$};
+\node (F') at (-1,-1) {$\bot_{b} \in F(b)$};
+\node (L') at (-1,-1.5) {$\tau_{f} \maps F(f)(\bot_a) \to \bot_{b}$};
 \node (M) at (2.5,0) {$=$};
-\node (N) at (3,0.5) {$c$};
-\node (O) at (3,-0.5) {$c$};
-\node (P) at (4,0.5) {$c'$};
-\node (Q) at (4,-0.5) {$c'$};
-\node (R) at (5,0.5) {$c'$};
-\node (S) at (5,-0.5) {$c'$};
-\node (T) at (4,1) {$!_{c'} \in F(c')$};
-\node (U) at (4,-1) {$!_{c'} \in F(c')$};
-\node (V) at (4,-1.5) {$\tau_{c'} = 1_{!_{c'}}$};
-
+\node (N) at (3,0.5) {$a$};
+\node (O) at (3,-0.5) {$a$};
+\node (P) at (4,0.5) {$b$};
+\node (Q) at (4,-0.5) {$b$};
+\node (R) at (5,0.5) {$b$};
+\node (S) at (5,-0.5) {$b$};
+\node (T) at (4,1) {$\bot_{b} \in F(b)$};
+\node (U) at (4,-1) {$\bot_{b} \in F(b)$};
+\node (V) at (4,-1.5) {$\tau_{b} = 1_{\bot_{b}}$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (S) edge node[above]{$1$} (Q)
-
 (A) edge node[above]{$f$} (B)
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$c'$};
-\node (B) at (1,0) {$c'$};
-\node (C) at (2,0) {$c$};
-\node (D) at (4,0) {$!_{c'} \in F(c')$};
+\node (A) at (0,0) {$b$};
+\node (B) at (1,0) {$b$};
+\node (C) at (2,0) {$a$};
+\node (D) at (4,0) {$\bot_{b} \in F(b)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \node (A) at (0,0) {$a$};
-\node (B) at (1,0) {$c$};
+\node (B) at (1,0) {$m$};
 \node (C) at (2,0) {$b$};
-\node (D) at (4,0) {$d \in F(c)$,};
+\node (D) at (4,0) {$x \in F(m)$,};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \node (A) at (0,0) {$a$};
-\node (B) at (1,0.5) {$c$};
+\node (B) at (1,0.5) {$m$};
 \node (C) at (2,0) {$b$};
-\node (E) at (1,-0.5) {$c'$};
-\node (D) at (3,0.5) {$d \in F(c)$};
-\node (F) at (3,-0.5) {$d' \in F(c')$};
+\node (E) at (1,-0.5) {$m'$};
+\node (D) at (3,0.5) {$x \in F(m)$};
+\node (F) at (3,-0.5) {$x' \in F(m')$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-together with a morphism $\tau \maps F(h)(d) \to d'$ in $F(c')$.
+together with a morphism $\tau \maps F(h)(x) \to x'$ in $F(m')$.
 \end{enumerate}
@@
 \node (A) at (0,0) {$a$};
-\node (B) at (1,0) {$c$};
+\node (B) at (1,0) {$m$};
 \node (C) at (2,0) {$b$};
-\node (D) at (4,0) {$d \in F(c)$};
+\node (D) at (4,0) {$x \in F(m)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \node (A) at (0,0) {$a$};
-\node (B) at (1,0) {$c'$};
+\node (B) at (1,0) {$m'$};
 \node (C) at (2,0) {$b$};
-\node (D) at (4,0) {$d' \in F(c')$};
+\node (D) at (4,0) {$x' \in F(m')$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-are isomorphic if and only if there exists an isomorphism $f \maps c \to c'$ in $\A$ such that following diagram commutes:
+are isomorphic if and only if there exists an isomorphism $f \maps m \to m'$ in $\A$ such that following diagram commutes:
 \[
@@
 \node (A) at (0,0) {$a$};
-\node (B') at (1,0.5) {$c$};
-\node (B) at (1,-0.5) {$c'$};
+\node (B') at (1,0.5) {$m$};
+\node (B) at (1,-0.5) {$m'$};
 \node (C) at (2,0) {$b$};
@@
 \]
-and there exists an isomorphism $\tau \maps F(f)(d) \to d'$ in $F(c')$.
+and there exists an isomorphism $\tau \maps F(f)(x) \to x'$ in $F(m')$.
 \end{enumerate}
@@
 \[      F\bCsp \simeq {}_L \bCsp(\inta F)   \]
-of symmetric monoidal categories
+and of symmetric monoidal categories
 \[      F\Csp \simeq {}_L \Csp(\inta F)  . \]
@@
 Let $L \maps \Fin\Set \to \Graph$ be the functor that assigns to a finite set $N$ the \define{discrete graph} on $N$: the graph with no edges and $N$ as its set of vertices.
-Both $\Set$ and $\Graph$ have finite colimits, and the functor $L \maps \Fin\Set \to \Graph$ is left adjoint to the forgetful functor $R \maps \Graph \to \Fin\Set$ that assigns to a graph $G$ its underlying set of vertices $U(G)$.
+Both $\Fin\Set$ and $\Graph$ have finite colimits, and the functor $L \maps \Fin\Set \to \Graph$ is left adjoint to the forgetful functor $R \maps \Graph \to \Fin\Set$ that assigns to a graph $G$ its underlying set of vertices $R(G)$.
 Thus, using structured cospans and appealing to \cref{thm:SC}, we get a symmetric monoidal double category $_L \lCsp(\Graph)$ in which:
@@
 \]
-is a commuting diagram in $\Set$ together with a morphism $\tau \maps F(h)(G) \to G'$ in $F(N')$.
+is a commuting diagram in $\Fin\Set$ together with a morphism $\tau \maps F(h)(G) \to G'$ in $F(N')$.
 \end{itemize}
@@
 We thus have two symmetric monoidal double categories: ${}_L \lCsp(\Graph)$ obtained from structured cospans and $F\lCsp$ obtained from decorated cospans.
-Each of these double categories has $\Set$ as its category of objects, open graphs as horizontal 1-cells, and maps of open graphs as 2-morphisms.
+Each of these double categories has $\Fin\Set$ as its category of objects, open graphs as horizontal 1-cells, and maps of open graphs as 2-morphisms.
 This suggests that ${}_L \lCsp(\Graph)$  and $F\lCsp$ are isomorphic as symmetric monoidal double categories---and indeed this is true.
@@
 This pseudofunctor $F$ is symmetric lax monoidal as both $(\Set,+,\emptyset)$ and $(\Cat,\times,1)$ are symmetric monoidal and given Petri nets $P \in F(s)$ and $P' \in F(s')$, we can place them side by side and consider them together as a single Petri net $P+P' \in F(s+s')$ with set of species $s+s'$, and thus we have natural transformations $\phi_{s,s'} \maps F(s) \times F(s') \to F(s+s')$ for any two sets $s$ and $s'$.
-The other structure morphism between monoidal units $\phi \maps 1_{\Petri} \to F(\emptyset)$ is defined by the unique morphism from the empty Petri net with the empty set forits set of species to the only possible Petri net on the empty set, which is also the empty Petri net.
+The other structure morphism between monoidal units $\phi \maps 1_{\Petri} \to F(\emptyset)$ is defined by the unique morphism from the empty Petri net with the empty set for its set of species to the only possible Petri net on the empty set, which is also the empty Petri net.
 All of the diagrams that are required to commute are straightforward.
@@
 \begin{itemize}
-\item We have given conditions under which a decorated cospan double category $F \bCsp$ is
-equivalent to a structured cospan category.    Is every structured cospan double category 
+\item We have given conditions under which a decorated cospan double category $F \lCsp$ is
+equivalent to a structured cospan double category.    Is every structured cospan double category 
 equivalent to a decorated cospan double category?
@@
 A candidate appears in the work of Pollard and the first author \cite{BP}.
-They construct a decorated cospan category $\Dynam$ where objects are finite sets and a morphism from $a$ to $b$ is a cospan of finite sets $a \leftarrow m \rightarrow b$ where the apex $m$ is decorated with a vector field on $\R^m$ whose coefficients are polynomial functions of the standard coordinates on this space.
+They construct a decorated cospan category $\Dynam$ where objects are finite sets and a morphism from $a$ to $b$ is a cospan of finite sets $a \rightarrow m \leftarrow b$ where the apex $m$ is decorated with a vector field on $\R^m$ whose coefficients are polynomial functions of the standard coordinates on this space.
 
@@
 \begin{equation}\label{eq:compGrothcat}
-\left(a\xrightarrow{f}b\xrightarrow{g}c, F(g\circ f)x\cong Fg(Ff(x))\xrightarrow{Ff(k)}Fg(y)\xrightarrow{\ell}z\right) 
+\left(a\xrightarrow{f}b\xrightarrow{g}c, F(g\circ f)x\cong Fg(Ff(x))\xrightarrow{Fg(k)}Fg(y)\xrightarrow{\ell}z\right) 
 \end{equation}
@@
 such that $S(\alpha), S(\lambda), S(\rho), T(\alpha), T(\lambda)$ and $T(\rho)$ are all identities and that the coherence axioms of a monoidal category are satisfied.
-Following the notation of Shulman, objects of $\lD_0$ are called \define{0-cells} or \define{objects} and morphisms of $\lD_0$ are called \define{vertical 1-morphisms}.
+Following the notation of Shulman, objects of $\lD_0$ are called \define{objects} or \define{0-cells}
+%%% I'm tempted to delete 0-cells since we never use that term anywhere in any paper, but I do like the idea that "n+1 morphisms go between n cells".
+and morphisms of $\lD_0$ are called \define{vertical 1-morphisms}.
 Objects of $\lD_1$ are called \define{horizontal 1-cells} and morphisms of $\lD_1$ are called \define{2-morphisms}.
@@
 \begin{defn}\label{def:fullfaithful}
-A double functor $\lF \maps \lA \to \lX$ is \define{full} (respectively, \define{faithful}) if $\lF_0 \maps \lA_0 \to \lX_0$ is full (respectively, faithful) and each map $$\lF_1 \maps _f \lA_g(M,N) \to _{\lF(f)} \lX_{\lF(g)}(\lF(M),\lF(N))$$ is surjective (respectively, injective).
+A double functor $\lF \maps \lA \to \lX$ is \define{full} (respectively, \define{faithful}) if $\lF_0 \maps \lA_0 \to \lX_0$ is full (respectively, faithful) and each map $$\lF_1 \maps _f \lA_g(M,N) \to {_{\lF(f)} \lX_{\lF(g)}}(\lF(M),\lF(N))$$ is surjective (respectively, injective).
 \end{defn}
@@
 \item{For each object $x \in \lX$, we can find an object $a \in \lA$ together with a vertical 1-isomorphism $\alpha_x \maps \lF(a) \to x$, and}
-\item{For each horizontal 1-cell $N \maps x_1 \tobar x_2$  of $\lX$, we can find a horizontal 1-cell $M \maps a_1 \tobar a_2$ of $\lA$ and a 2-isomorphism $a_{N}$ of $\lX$ as in the following diagram:
+\item{For each horizontal 1-cell $N \maps x_1 \tobar x_2$  of $\lX$, we can find a horizontal 1-cell $M \maps a_1 \tobar a_2$ of $\lA$ and a 2-isomorphism $a_{N} \colon \lF(M) \to N$ in $\lX$ as in the following diagram:
 \[
@@
 \label{ShulDubEquiv}
-A strong double functor $\lF \maps \lA \to \lX$ is part of a double equivalence if and only if it is full, faithful and essentially surjective.
+A pseudo double functor $\lF \maps \lA \to \lX$ is part of a double equivalence if and only if it is full, faithful and essentially surjective.
 \end{thm}
@@
 \begin{defn}\label{defn:smdc}
-  A \textbf{monoidal double category} is a double category equipped the following
+%  A \textbf{monoidal double category} is a double category equipped the following
   A \textbf{monoidal double category} is a double category $\lD$ equipped with the following
@@
 			\path[->,font=\scriptsize]
-				(UL) edge node[above]{$\chi \odot 1$} (UR) 
+				(UL) edge node[above]{$\mu \odot 1$} (UR) 
 				(UL) edge node[left]{$\lambda$} (LL)
@@
 		\node (A') at (0,0) {$A$};
-		\node (B) at (1,1) {$A$};
-		\node (B') at (1,0) {$B$};
-		\node (C) at (2,1) {$B$};
-		\node (C') at (2,0) {$B$};
+		\node (B) at (1.4,1) {$A$};
+		\node (B') at (1.4,0) {$B$};
+		\node (C) at (2.8,1) {$B$};
+		\node (C') at (2.8,0) {$B$};
+		\node (A'') at (0,-1) {$A$};
+		\node (C'') at (2.8,-1) {$B$};
 		%
@@
 			(A) edge node[left]{$1$} (A')
-			(B) edge node[left]{$f$} (B')
+			(B) edge node [left] {$f$} (B')
 			(C) edge node[right]{$1$} (C')
 			(A) edge node[above]{$U_A$} (B)
-			(B) edge node[above]{$\widehat{f}$} (C)
-			(A') edge node[below]{$\widehat{f}$} (B')
-			(B') edge node[below]{$U_B$} (C');
+			(B) edge node[above]{$\hat{f}$} (C)
+			(A') edge (B')
+			(B') edge (C')
+			(A'') edge node[below]{$\hat{f}$} (C'')
+			(A') edge node[left]{$1$} (A'')
+			(C') edge node[right]{$1$} (C'');
 		%
@@
 	%	\draw (0.5,-.075) -- (0.5,.075);
-		\node () at (0.5,0.5) {\scriptsize{$\Downarrow$}};
-		\node () at (1.5,0.5) {\scriptsize{$\Downarrow$}};
+	\draw[line width=2mm,white] (0.7,-.05) -- (0.7,.05);
+	\draw[line width=4.4mm,white] (2.1,-.05) -- (2.1,.05);
+%	\draw[line width=2mm,white] (1.4,.35) -- (1.4,.65);
+		\node () at (0.7,0.5) {\scriptsize{$\Downarrow$}};
+		\node () at (2.1,0.5) {\scriptsize{$\Downarrow$}};
+		\node () at (1.4,-0.6) {\scriptsize{$\Downarrow \lambda_{\hat{f}}$}};
+		\node () at (0.7,0) {$\hat{f}$};
+%		\node () at (1.4,.5) {$\scriptstyle{f}$};
+		\node () at (2.1,0) {$\scriptsize{U_B}$};
+
 	\end{tikzpicture}
@@
 	\begin{tikzpicture}
+	     \node (A0) at (0,2) {$A$};
+	     \node (B0) at (1,2) {$A$};
+		\node (C0) at (2,2) {$B$};
 		\node (A) at (0,1) {$A$};
-		\node (B) at (1,1) {$B$};
-		\node (A') at (0,0) {$A$};
-		\node (B') at (1,0) {$B$};
+		\node (C) at (2,1) {$B$};
+	%	\node (A') at (0,0) {$a$};
+	%	\node (C') at (2,0) {$b$};
 		%
 		\path[->,font=\scriptsize,>=angle 90]
-			(A) edge node[left]{$1$} (A')
-			(B) edge node[right]{$1$} (B')
-			(A) edge node[above]{$\widehat{f}$} (B)
-			(A') edge node[below]{$\widehat{f}$} (B');
+			(A0) edge node[above]{$U_A$} (B0)
+			(B0) edge node[above]{$\hat{f}$} (C0)
+			(A0) edge node[left]{$1$} (A)
+			(C0) edge node[right]{$1$} (C)
+		%	(A) edge node[left]{$1$} (A')
+		%	(C) edge node[right]{$1$} (C')
+			(A) edge node[below]{$\hat{f}$} (C);
+		%	(A') edge node[below]{$\hat{f}$} (C');
 		%
@@
 	%	\draw (0.5,-.075) -- (0.5,.075);
-		\node () at (0.5,0.5) {\scriptsize{$\Downarrow \id_{\widehat{f}}$}};
+	%	\node () at (1,0.5) {\scriptsize{$\Downarrow 1$}};
+		\node () at (1,1.4) {\scriptsize{$\Downarrow \rho_f$}};
 	\end{tikzpicture}
@@
 \noindent
-In a pseudo double category, the second equation above requires an insertion of unit isomorphisms to make sense due to horizontal composition only holding up to isomorphism.
+%In a pseudo double category, the second equation above requires an insertion of unit isomorphisms to make sense due to horizontal composition only holding up to isomorphism.
 
@@
 
-\bibitem{BC2} J.\ C.\ Baez and K.\ Courser, Structured cospans,  \textsl{Theory Appl.\ Categ.\ }\textbf{35} (2020), 1771–1822.   Available as \href{http://arxiv.org/abs/1911.04630}{arXiv:1911.04630}.
+\bibitem{BC2} J.\ C.\ Baez and K.\ Courser, Structured cospans,  \textsl{Theory Appl.\ Categ.\ }\textbf{35} (2020), 1771--1822.   Available as \href{http://arxiv.org/abs/1911.04630}{arXiv:1911.04630}.
 
@@
 
-\bibitem{Brown2} R.\ Brown, K.\ Hardie, H.\ Kamps and T.\ Porter, The homotopy double groupoid of a Hausdorff space, \textsl{Th.\ Appl.\ Categ.} \textbf{10} (2002), 71--93.
+\bibitem{Brown2} R.\ Brown, K.\ Hardie, H.\ Kamps and T.\ Porter, The homotopy double groupoid of a Hausdorff space, \textsl{Theory Appl.\ Categ.} \textbf{10} (2002), 71--93.
 
@@
 \bibitem{CourserThesis} K.\ Courser, \textsl{Open Systems: a Double Categorical Perspective}, Ph.D.\ thesis, Department of Mathematics, U.\ C.\ Riverside, 2020.
-Available as \href{https://arxiv.org/abs/2008.02394}{arxiv:2008.02394}.
+Available as \href{https://arxiv.org/abs/2008.02394}{arXiv:2008.02394}.
 
@@
 
-\bibitem{MV} J.\ Moeller and C.\ Vasilakopoulou, Monoidal Grothendieck construction, \emph{Theory Appl.\ Categ.} \textbf{35} (2020), no.
-31, 1159--1207.
+\bibitem{MV} J.\ Moeller and C.\ Vasilakopoulou, Monoidal Grothendieck construction, \emph{Theory Appl.\ Categ.} \textbf{35} (2020), 1159--1207.
 Available as \href{https://arxiv.org/abs/1809.00727}{arXiv:1809.00727}.
@@
 
-\bibitem{Shulman2008} M.\ Shulman, Framed bicategories and monoidal fibrations, \emph{Theory Appl.Categ.} \textbf{20} (2008), no.
-18, 650 -- 738, 2008.
+\bibitem{Shulman2008} M.\ Shulman, Framed bicategories and monoidal fibrations, \emph{Theory Appl.Categ.} \textbf{20} (2008), 650--738.
 Available as \href{https://arxiv.org/abs/0706.1286}{arXiv:0706.1286}.

### 2020-11-23 cospans.tex
tiny compiling edit
responses to Kenny

@@
 As a left adjoint, this induced $L$ preserves all colimits that exist between the finitely cocomplete categories $\A$ and $\inta F$, so we can construct the double category of structured cospans $_L\lCsp(\inta F)$ of \cref{thm:SC}.
-Its objects and vertical morphisms are those of the category $\A$ (as for $F\lCsp$ earlier), whereas horizontal 1-cells are now cospans of the form $\cspn{L(a)}{v}{L(b)}{}{}$ in the Grothendieck category $\inta F$ (\cref{def:GrothCat}).
+Its objects and vertical morphisms are those of the category $\A$ (as for $F\lCsp$ earlier), whereas horizontal 1-cells are now cospans of the form $\cspn{L(a)}{(m,x)}{L(b)}{}{}$ in the Grothendieck category $\inta F$ (\cref{def:GrothCat}).
 Explicitly, they consist of two pairs of morphisms
 %%% Not sure what v is in the above line unless you mean x?
+%%% I mean an arbitrary object in the Grothendieck category. I just made it a pair to be clearer, is it OK? Erase these comments whenever you want.
 \begin{equation}\label{eq:scsphor1cell}
@@
 Given a horizontal 1-cell in $_L\lCsp(\inta F)$ as in \cref{eq:scsphor1cell}, $\lE_1$ maps it to the decorated cospan $i\maps a\to m\leftarrow b:o$ with decoration $x\in F(m)$,
-whereas a 2-morphism of $L$-structured cospans as above is mapped to the underlying cospan 2-morphism in $\A$
+whereas a 2-morphism of $L$-structured cospans as above is mapped to the underlying map of cospans in $\A$
 %%% We should call these "cospan 2-morphism"s maps of cospans to be consistent with previous work
+%%% Alright!
 \begin{displaymath}
@@
 %%% I'm tempted to delete 0-cells since we never use that term anywhere in any paper, but I do like the idea that "n+1 morphisms go between n cells".
+%%% Christina: I am up for deletion of 0-cells
 and morphisms of $\lD_0$ are called \define{vertical 1-morphisms}.
@@
 %		\node () at (1.4,.5) {$\scriptstyle{f}$};
-		\node () at (2.1,0) {$\scriptsize{U_B}$};
+		\node () at (2.1,0) {\scriptsize{$U_B$}};
 

### 2020-11-23 cospans.tex
small edits in intro

@@
 We can also `tensor' cospans using coproducts: this describes setting open systems side by side, in parallel.
-Via these operations we obtain a symmetric monoidal double category with cospans in $\A$ as its horizontal 1-cells \cite{Courser,Niefield}.
+Via these operations we obtain a symmetric monoidal double category
+%%%Christina: add the notation bb{C}sp(A) since it will be central to what follows?
+with cospans in $\A$ as its horizontal 1-cells \cite{Courser,Niefield}.
+%%% Christina: I would be inclined to first cite Niefield and then Courser due to the chronological order.
 
@@
 \]
-We might hope to do this using a symmetric lax monoidal functor $F \maps (\Fin\Set, +) \to (\Set, \times)$ assigning to each finite set $m$ the set of all graphs with $m$ as their set of nodes    But this hope is doomed, for reasons painstakingly explained in \cite[Sec.\ 5]{BC}.
+We might hope to do this using a symmetric lax monoidal functor $F \maps (\Fin\Set, +) \to (\Set, \times)$ assigning to each finite set $m$ the set of all graphs with $m$ as their set of nodes.
+But this hope is doomed, for reasons painstakingly explained in \cite[Sec.\ 5]{BC2}.
 There is really a \emph{category} of graphs with $m$ as their set of nodes, and trying to treat it as a mere set does not work.
@@
 Instead of basing the theory of decorated cospans on a symmetric lax monoidal functor $F \maps (\A, +) \to (\Set, \times)$, we use a symmetric lax monoidal pseudofunctor $F \maps (\A, +) \to (\Cat, \times)$.
-In \cref{DC} we use this
+In \cref{thm:decorated_cospans,DC}, we use this
 data to construct a symmetric monoidal double category $F\lCsp$ in which:
@@
 
-In fact another solution to the problem is already known: the theory of structured cospans \cite{BC,CourserThesis}.
+In fact another solution to the problem is already known: the theory of structured cospans \cite{BC2,CourserThesis}.
 Given a functor $L \maps \A \to \X$, a \define{structured cospan} is a cospan in $\X$ whose feet come from a pair of objects in $\A$:
@@
 Many of the flawed applications of decorated cospans have been fixed using structured cospans
-\cite[Sec.\ 6]{BC}.
-
-We show that our new solution subsumes the old one: structured cospan double categories are always equivalent to decorated cospan double categories.  (REALLY????)
+\cite[Sec.\ 6]{BC2}.
+
+We show that our new solution subsumes the old one: structured cospan double categories are always equivalent to decorated cospan double categories.
+(REALLY????)   %%%Christina: Not sure what this refers to.
+The paragraph below is more to the point.
+If this is supposed to provide the opposite direction, I would expect that to also hold under certain assumptions, similar to the ones below.
 
@@
 symmetric lax monoidal pseudofunctor.   Any such pseudofunctor gives an opfibration 
-$R \maps \X \to \A$ where $\X = \int F$ is defined by the Grothendieck construction.
+$U \maps \X \to \A$ where $\X = \inta F$ is defined by the Grothendieck construction.
 Let $\Rex$ be the 2-category of finitely cocomplete categories, finite-colimit-preserving
 functors and natural transformations.  We show that if $F$ factors through $\mathbf{Rex}$ as
-a pseudofunctor, the opfibration $R \maps \X \to \A$ is also a right adjoint.
+a pseudofunctor, the opfibration $U \maps \X \to \A$ is also a right adjoint.
 From the accompanying left adjoint $L \maps \A \to \X$, we  construct a symmetric monoidal double category ${}_L \lCsp(\X)$ of structured cospans.
@@
 
-\iffalse
-To obtain a decoration on the composition of two composable decorated cospans:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a_1$};
-\node (B) at (1,0) {$b$};
-\node (C) at (2,0) {$a_2$};
-\node (F) at (3,0) {$a_2$};
-\node (G) at (4,0) {$b'$};
-\node (H) at (5,0) {$a_3$};
-\node (D) at (0.5,-0.5) {$1$};
-\node (E) at (1.5,-0.5) {$F(b)$};
-\node (D') at (3.5,-0.5) {$1$};
-\node (E') at (4.5,-0.5) {$F(b')$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i$} (B)
-(C) edge node[above]{$o$} (B)
-(F) edge node[above]{$i'$} (G)
-(H) edge node[above]{$o'$} (G)
-(D) edge node [above] {$d_1$} (E)
-(D') edge node [above] {$d_2$} (E');
-\end{tikzpicture}
-\]
-we use the natural map from a coproduct to a pushout as well as the structure maps, or `laxators', that come as part of the structure of a lax monoidal functor:
-\[
-1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{d_1 \times d_2} F(b) \times F(b') \xrightarrow{\phi_{b,b'}} F(b+ b') \xrightarrow{F(j_{b,b'})} F(b+_{a_2} b').
-\]
-Using this idea, Fong constructed a symmetric monoidal category $F\textnormal{Cospan}(\A)$ which has:
-\begin{enumerate}
-\item{objects as those of $\A$ and}
-\item{morphisms as isomorphism classes of $F$-decorated cospans, where an $F$-decorated cospan is given as above, and two $F$-decorated cospans are in the same isomorphism class if there exists an isomorphism $f \maps b \to b'$ between the apices such that the following diagrams commute:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a_1$};
-\node (B) at (1,1) {$b$};
-\node (B') at (1,-1) {$b'$};
-\node (C) at (2,0) {$a_2$};
-\node (D) at (3,0) {$1$};
-\node (E) at (4,0.5) {$F(b)$};
-\node (E') at (4,-0.5) {$F(b')$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i$} (B)
-(C) edge node[above]{$o$} (B)
-(A) edge node[below]{$i'$} (B')
-(C) edge node[below]{$o'$} (B')
-(B) edge node [left] {$f$} (B')
-(B) edge node [right] {$\sim$} (B')
-(D) edge node [above] {$d$} (E)
-(D) edge node [below] {$d'$} (E')
-(E) edge node [right] {$F(f)$} (E');
-\end{tikzpicture}
-\]
-}
-\end{enumerate}
-
-As an example, let $F \maps \textsf{FinSet} \to \textsf{Set}$ be the symmetric lax monoidal functor that assigns to a finite set $b$ the (large) set of all possible graph structures on the finite set $b$, where a graph structure on $b$ is given by a diagram in $\textsf{Set}$ of the form:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$E$};
-\node (B) at (1,0) {$b.$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge[bend left] node[above]{$s$} (B)
-(A) edge[bend right] node[below]{$t$} (B);
-\end{tikzpicture}
-\]
-Let $b=\{ v_1,v_2 \}$ be a two element set.
-Then one element of the (large) set $F(b)$, which is the collection of all graph structures on the finite set $b$, is given by a single edge $e$ whose source and target are $v_1$ and $v_2$, respectively.
-\[
-\begin{tikzpicture}
-  [scale=.8,auto=left]
-  \node [style={circle,fill=teal}] (n1) at (1,10) {$v_1$};
-  \node[style={circle,fill=teal}] (n2) at (4,10)  {$v_2$};
-\path[->,font=\scriptsize,>=angle 90]
-(n1) edge node[above]{$e$} (n2);
-\end{tikzpicture}
-\]
-%\[
-%\begin{tikzpicture}[scale=1.5]
-%\node (A) at (0,0) {$v_1$};
-%\node (B) at (1,0) {$v_2$};
-%\path[->,font=\scriptsize,>=angle 90]
-%(A) edge node[above]{$e$} (B);
-%\end{tikzpicture}
-%\]
-Denote this element of $F(b)$ as $d \maps 1 \to F(b)$.
-Let $a_1=\{ 1 \}$ and $a_2=\{2,3\}$ and define functions $i \maps a_1 \to b$ and $o \maps a_2 \to b$ by $i(1)=v_1$ and $o(2)=o(3)=v_2$.
-Then we have an $F$-decorated cospan:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a_1$};
-\node (B) at (1,0) {$b$};
-\node (C) at (2,0) {$a_2$};
-\node (D) at (3,0) {$1$};
-\node (E) at (4,0) {$F(b)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i$} (B)
-(C) edge node[above]{$o$} (B)
-(D) edge node [above] {$d$} (E);
-\end{tikzpicture}
-\]
-which is given by the open graph:
-\[
-\begin{tikzpicture}
-  [scale=.8,auto=left]
-\node (a) at (-2,10) {$1$};
-\node (b) at (7,10.5) {$2$};
-\node (c) at (7,9.5) {$3$};
-\node (i) at (-0.5,11) {$i$};
-\node (o) at (5.5,11) {$o$};
-  \node [style={circle,fill=teal}] (n1) at (1,10) {$v_1$};
-  \node[style={circle,fill=teal}] (n2) at (4,10)  {$v_2$};
-\path[->,font=\scriptsize,>=angle 90]
-(a) edge[dashed] node[above] {$$} (n1)
-(b) edge[dashed] node[below] {$$} (n2)
-(c) edge[dashed] node[above] {$$} (n2)
-(n1) edge node[above]{$e$} (n2);
-\end{tikzpicture}
-\]
-We can compose this open graph with another whose set inputs coincide with the set of outputs of the above open graph, namely the set $a_2=\{2,3\}$. For example:
-\[
-\begin{tikzpicture}
-  [scale=.8,auto=left]
-%\node (a) at (-2,10) {$1$};
-\node (b) at (7,10.5) {$2$};
-\node (c) at (7,9.5) {$3$};
-%\node (i) at (-0.5,11) {$i$};
-\node (o) at (8.5,11.5) {$i'$};
-\node (d) at (16,10) {$4$};
-\node (e) at (14.5,11.5) {$o'$};
-  \node [style={circle,fill=teal}] (n1) at (10,11.5) {$v_4$};
-  \node[style={circle,fill=teal}] (n2) at (10,8.5)  {$v_3$};
-  \node[style={circle,fill=teal}] (n3) at (13,10)  {$v_5$};
-\path[->,font=\scriptsize,>=angle 90]
-%(a) edge[dashed] node[above] {$$} (n1)
-(b) edge[dashed] node[below] {$$} (n1)
-(c) edge[dashed] node[above] {$$} (n2)
-(n1) edge[bend left] node[above]{$e_2$} (n3)
-(n3) edge[bend left] node[below]{$e_3$} (n2)
-(n2) edge[bend left] node[left]{$e_1$} (n1)
-(d) edge[dashed] node[above]{$$}(n3);
-\end{tikzpicture}
-\]
-This second open graph can be represented by the $F$-decorated cospan:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a_2$};
-\node (B) at (1,0) {$b'$};
-\node (C) at (2,0) {$a_3$};
-\node (D) at (3,0) {$1$};
-\node (E) at (4,0) {$F(b')$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i'$} (B)
-(C) edge node[above]{$o'$} (B)
-(D) edge node [above] {$d'$} (E);
-\end{tikzpicture}
-\]
-The composite of these two open graphs is then given by:
-\[
-\begin{tikzpicture}
-  [scale=.8,auto=left]
-\node (a) at (-2,10) {$1$};
-%\node (b) at (7,10.5) {$2$};
-\node (c) at (10,10) {$4$};
-\node (i) at (-0.5,11) {$i$};
-\node (o) at (8.5,11) {$o'$};
-  \node [style={circle,fill=teal}] (n1) at (1,10) {$v_1$};
-  \node[style={circle,fill=teal}] (n2) at (4,10)  {$v_2$};
-  \node[style={circle,fill=teal}] (n3) at (7,10)  {$v_5$};
-\path[->,font=\scriptsize,>=angle 90]
-(a) edge[dashed] node[above] {$$} (n1)
-%(b) edge[dashed] node[below] {$$} (n2)
-(c) edge[dashed] node[above] {$$} (n3)
-(n1) edge node[above]{$e$} (n2)
-(n2) edge[bend left] node[above]{$e_2$} (n3)
-(n2) edge[loop below]node{$e_1$} (n2)
-(n3) edge[bend left] node[below]{$e_3$} (n2);
-\end{tikzpicture}
-\]
-where we identify $v_2=v_3=v_4$ in taking the pushout of the two cospans of finite sets. The composite open graph is represented by the $F$-decorated cospan:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a_1$};
-\node (B) at (1.25,0) {$b+_{a_2}b'$};
-\node (C) at (2.5,0) {$a_3$};
-\node (D) at (3,0) {$1$};
-\node (E) at (4,0) {$F(b+_{a_2}b')$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$\psi j_b i$} (B)
-(C) edge node[above]{$\psi j_{b'} o'$} (B)
-(D) edge node [above] {$d''$} (E);
-\end{tikzpicture}
-\]
-where $j$ is the natural map into a coproduct and $\psi$ the natural map from a coproduct into a pushout.
-
-We can also consider the above two open graphs in parallel:
-\[
-\begin{tikzpicture}
-  [scale=.8,auto=left]
-\node (a') at (7,12.5) {$1$};
-\node (b') at (16,12.5) {$2$};
-\node (c') at (16,11.5) {$3$};
-\node (i') at (8.5,13.5) {$i+i'$};
-\node (o') at (14.5,13.5) {$o+o'$};
-  \node [style={circle,fill=teal}] (n1') at (10,13) {$v_1$};
-  \node[style={circle,fill=teal}] (n2') at (13,13)  {$v_2$};
-\node (b) at (7,11.5) {$2$};
-\node (c) at (7,10.5) {$3$};
-\node (d) at (16,10.5) {$4$};
-  \node [style={circle,fill=teal}] (n1) at (10,11.5) {$v_4$};
-  \node[style={circle,fill=teal}] (n2) at (10,8.5)  {$v_3$};
-  \node[style={circle,fill=teal}] (n3) at (13,10)  {$v_5$};
-\path[->,font=\scriptsize,>=angle 90]
-(a') edge[dashed] node[above] {$$} (n1')
-(b') edge[dashed] node[below] {$$} (n2')
-(c') edge[dashed] node[above] {$$} (n2')
-(n1') edge node[above]{$e$} (n2')
-(b) edge[dashed] node[below] {$$} (n1)
-(c) edge[dashed] node[above] {$$} (n2)
-(n1) edge[bend left] node[above]{$e_2$} (n3)
-(n3) edge[bend left] node[below]{$e_3$} (n2)
-(n2) edge[bend left] node[left]{$e_1$} (n1)
-(d) edge[dashed] node[above]{$$}(n3);
-\end{tikzpicture}
-\]
-which is represented by the tensor product of the above two $F$-decorated cospans:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a_1+a_2$};
-\node (B) at (1.25,0) {$b+b'$};
-\node (C) at (2.5,0) {$a_2+a_3$};
-\node (D) at (3.5,0) {$1$};
-\node (E) at (4.5,0) {$F(b+b')$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i+i'$} (B)
-(C) edge node[above]{$o+ o'$} (B)
-(D) edge node [above] {$d+d'$} (E);
-\end{tikzpicture}
-\]
-
-There are some subtleties to this framework; consider two decorated cospans with the same inputs and outputs.
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a_1$};
-\node (B) at (1,0) {$b$};
-\node (C) at (2,0) {$a_2$};
-\node (F) at (3,0) {$a_1$};
-\node (G) at (4,0) {$b'$};
-\node (H) at (5,0) {$a_2$};
-\node (D) at (0.5,-0.5) {$1$};
-\node (E) at (1.5,-0.5) {$F(b)$};
-\node (D') at (3.5,-0.5) {$1$};
-\node (E') at (4.5,-0.5) {$F(b')$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i$} (B)
-(C) edge node[above]{$o$} (B)
-(F) edge node[above]{$i'$} (G)
-(H) edge node[above]{$o'$} (G)
-(D) edge node [above] {$d$} (E)
-(D') edge node [above] {$d'$} (E');
-\end{tikzpicture}
-\]
-For these two $F$-decorated cospans to be in the same isomorphism class, the following triangle is to commute:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (D) at (3,0) {$1$};
-\node (E) at (4,0.5) {$F(b)$};
-\node (E') at (4,-0.5) {$F(b')$};
-\path[->,font=\scriptsize,>=angle 90]
-(D) edge node [above] {$d$} (E)
-(D) edge node [below] {$d'$} (E')
-(E) edge node [right] {$F(f)$} (E');
-\end{tikzpicture}
-\]
-This commutative triangle in $\Set$ in the context of the symmetric lax monoidal functor $F \maps \mathsf{FinSet} \to \Set$ says the following: given a decoration $d \in F(b)$, which is a graph structure with underlying set of vertices $b$, the function $F(f)$ pushes forward the graph structure $d$ to the graph structure $d' \in F(b')$ with underlying set of vertices $b'$, and \emph{precisely} this graph structure.
-The graph structure is given by set of edges of $d$.
-For example, if we take $b = \{v_1 ,v_2\}$ as before and let $d \in F(b)$ be given by:
-\[
-\begin{tikzpicture}
-  [scale=.8,auto=left]
-\node (a) at (-2,10) {$1$};
-\node (b) at (7,10) {$2$};
-\node (i) at (-0.5,11) {$i$};
-\node (o) at (5.5,11) {$o$};
-  \node [style={circle,fill=teal}] (n1) at (1,10) {$v_1$};
-  \node[style={circle,fill=teal}] (n2) at (4,10)  {$v_2$};
-\path[->,font=\scriptsize,>=angle 90]
-(a) edge[dashed] node[above] {$$} (n1)
-(b) edge[dashed] node[below] {$$} (n2)
-(n1) edge node[above]{$e$} (n2);
-\end{tikzpicture}
-\]
-Let $b' = \{w_1,w_2\}$ and a define bijection $f \maps b \to b'$ by $f(v_i)=w_i$ for $i=1,2$. Then the requirement $F(f)(d)=d'$ says that $d' \in F(b')$ must be given by:
-\[
-\begin{tikzpicture}
-  [scale=.8,auto=left]
-\node (a) at (-2,10) {$1$};
-\node (b) at (7,10) {$2$};
-\node (i) at (-0.5,11) {$i'$};
-\node (o) at (5.5,11) {$o'$};
-  \node [style={circle,fill=teal}] (n1) at (1,10) {$w_1$};
-  \node[style={circle,fill=teal}] (n2) at (4,10)  {$w_2$};
-\path[->,font=\scriptsize,>=angle 90]
-(a) edge[dashed] node[above] {$$} (n1)
-(b) edge[dashed] node[below] {$$} (n2)
-(n1) edge node[above]{$e$} (n2);
-\end{tikzpicture}
-\]
-The point to be made here is that the single edge of $d'$ must also be $e$.
-If we were to label it say, $e'$, there is no bijection $f \maps b \to b'$ such that the triangle on the right commutes, and hence no isomorphism between these two $F$-decorated cospans.
-\[
-\begin{tikzpicture}\label{distinctisoclasses}
-  [scale=.8,auto=left]
-\node (D) at (9,11.5) {$1$};
-\node (E) at (11,12.5) {$F(b)$};
-\node (E') at (11,10.5) {$F(b')$};
-\node (a) at (-2,11.5) {$1$};
-\node (b) at (7,11.5) {$2$};
-\node (i) at (-0.5,12.5) {$i$};
-\node (o) at (5.5,12.5) {$o$};
-\node (i') at (-0.5,10.5) {$i'$};
-\node (o') at (5.5,10.5) {$o'$};
-\node (A) at (2.5,11.5) {$\nexists F(f) \Downarrow$};
-  \node [style={circle,fill=teal}] (n1) at (1,13) {$v_1$};
-  \node[style={circle,fill=teal}] (n2) at (4,13)  {$v_2$};
-  \node [style={circle,fill=red}] (n1') at (1,10) {$w_1$};
-  \node[style={circle,fill=red}] (n2') at (4,10)  {$w_2$};
-\path[->,font=\scriptsize,>=angle 90]
-(D) edge node [above] {$d$} (E)
-(D) edge node [below] {$d'$} (E')
-(E) edge[dashed] node [right] {$\nexists F(f)$} (E')
-(a) edge[dashed] node[above] {$$} (n1)
-(b) edge[dashed] node[above] {$$} (n2)
-(a) edge[dashed] node[below] {$$} (n1')
-(b) edge[dashed] node[below] {$$} (n2')
-(n1) edge node[above]{$e$} (n2)
-(n1') edge node[above]{$e'$} (n2');
-\end{tikzpicture}
-\]
-Thus these two $F$-decorated cospans constitute distinct isomorphism classes. This nuisance is amplified when viewed from a higher categorical perspective.
-
-In a previous work, the second author extended Fong's theory of decorated cospans to a symmetric monoidal bicategory of decorated cospans \cite{Courser}.
-Namely, under the same hypotheses used by Fong amounting to a category $\A$ with finite colimits and a symmetric lax monoidal functor $F \maps (\A,+,0) \to (\Set, \times, 1)$, there exists a symmetric monoidal bicategory $F\mathbf{Cospan}(\A)$ which has:
-\begin{enumerate}
-\item objects as those of $\A$,
-\item morphisms as $F$-decorated cospans in $\A$, which again are pairs
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a_1$};
-\node (B) at (1,0) {$b$};
-\node (C) at (2,0) {$a_2$};
-\node (D) at (3,0) {$1$};
-\node (E) at (4,0) {$F(b)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i$} (B)
-(C) edge node[above]{$o$} (B)
-(D) edge node [above] {$d$} (E);
-\end{tikzpicture}
-\]
-and
-\item 2-morphisms as pairs of commuting diagrams where the left diagram is a map of cospans in $\A$ and the right diagram is a commutative triangle in $\Set$.
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a_1$};
-\node (B) at (1,1) {$b$};
-\node (B') at (1,-1) {$b'$};
-\node (C) at (2,0) {$a_2$};
-\node (D) at (3,0) {$1$};
-\node (E) at (4,0.5) {$F(b)$};
-\node (E') at (4,-0.5) {$F(b')$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i$} (B)
-(C) edge node[above]{$o$} (B)
-(A) edge node[below]{$i'$} (B')
-(C) edge node[below]{$o'$} (B')
-(B) edge node [left] {$f$} (B')
-%(B) edge node [right] {$\sim$} (B')
-(D) edge node [above] {$d$} (E)
-(D) edge node [below] {$d'$} (E')
-(E) edge node [right] {$F(f)$} (E');
-\end{tikzpicture}
-\]
-\end{enumerate}
-Returning to the previous example where we take the functor $F$ to be the functor $F \maps \mathsf{FinSet} \to \Set$, the situation becomes more dire.
-Previously, in the ordinary symmetric monoidal category $F$Cospan$(\mathsf{FinSet})$ the following two $F$-decorated cospans resided in distinct isomorphism classes:
-\[
-\begin{tikzpicture}\label{no2morphism}
-  [scale=.8,auto=left]
-%\node (D) at (9,11.5) {$1$};
-\node (E) at (9,13) {$d \in F(b)$};
-\node (E') at (9,10) {$d' \in F(b')$};
-\node (a) at (-2,13) {$1$};
-\node (a') at (-2,10) {$1$};
-\node (b) at (7,13) {$2$};
-\node (b') at (7,10) {$2$};
-\node (i) at (-0.5,13.5) {$i$};
-\node (o) at (5.5,13.5) {$o$};
-\node (i') at (-0.5,10.5) {$i'$};
-\node (o') at (5.5,10.5) {$o'$};
-%\node (A) at (2.5,11.5) {$\nexists F(f) \Downarrow$};
-  \node [style={circle,fill=teal}] (n1) at (1,13) {$v_1$};
-  \node[style={circle,fill=teal}] (n2) at (4,13)  {$v_2$};
-  \node [style={circle,fill=red}] (n1') at (1,10) {$w_1$};
-  \node[style={circle,fill=red}] (n2') at (4,10)  {$w_2$};
-\path[->,font=\scriptsize,>=angle 90]
-%(D) edge node [above] {$d$} (E)
-%(D) edge node [below] {$d'$} (E')
-%(E) edge[dashed] node [right] {$\nexists F(f)$} (E')
-(a) edge[dashed] node[above] {$$} (n1)
-(b) edge[dashed] node[above] {$$} (n2)
-(a') edge[dashed] node[below] {$$} (n1')
-(b') edge[dashed] node[below] {$$} (n2')
-(n1) edge node[above]{$e$} (n2)
-(n1') edge node[above]{$e'$} (n2');
-\end{tikzpicture}
-\]
-In the symmetric monoidal bicategory $F\mathbf{Cospan}(\mathsf{FinSet})$, the above two $F$-decorated cospans are two morphisms - with \emph{no 2-morphism between them!} The culprit for this is the same as before - the requirement that the triangle of decorations in $\Set$ commute `on the nose'.
-In this paper we construct a similar symmetric monoidal bicategory $F$Csp which will remedy this situation, and whose decategorification will remedy the analogous problem for decorated cospan categories above.
-
-It is worth noting that in both examples involving sets and graphs above, we are decorating each finite set with extra \emph{stuff}.
-This phenomenon does not occur when the decorations only involve extra structure, and this has been utilized in other works \cite{BFP,BP,Yass}.
-
-Our approach is to instead view the functor $F$ as a pseudofunctor $F \maps \textrm{A} \to \Cat$ and take advantage of the 2-categorical structure of $\Cat$.
-Given an object $a \in \A$, this then allows us to view $F(a)$ not as a \emph{set} of decorations on the object $a$ but as a \emph{category} of decorations on the object $a$.
-From this pseudofunctor, we construct a symmetric monoidal double category $F \mathbb{C}$sp.
-Double categories were first introduced by Ehresmann \cite{Ehresmann63, Ehresmann65} and symmetric monoidal double categories by Shulman \cite{Shul}.
-They have long been used in topology and other branches of pure mathematics \cite{Brown1,Brown2}.
-More recently they have been used to study open dynamical systems \cite{LS} and open Markov processes \cite{BC}.
-While a mere category has only objects and morphisms, a double category has a few more types of entities:
-\[
-\begin{tikzpicture}[scale=1]
-\node (D) at (-4,0.5) {$A$};
-\node (E) at (-2,0.5) {$B$};
-\node (F) at (-4,-1) {$C$};
-\node (A) at (-2,-1) {$D$};
-\node (B) at (-3,-0.25) {$\Downarrow a$};
-\path[->,font=\scriptsize,>=angle 90]
-(D) edge node [above]{$M$}(E)
-(E) edge node [right]{$g$}(A)
-(D) edge node [left]{$f$}(F)
-(F) edge node [above]{$N$} (A);
-\end{tikzpicture}
-\]
-We call $A, B, C$ and $D$ `objects', $f$ and $g$ `vertical 1-morphisms', $M$ and $N$ `horizontal 1-cells', and $a$ a `2-morphism'.
-We can compose vertical 1-morphisms to get new vertical 1-morphisms and compose horizontal 1-cells to get new horizontal 1-cells.
-We can compose the 2-morphisms in two ways: horizontally by setting squares side by side, and vertically by setting one on top of the other.
-In a `strict' double category all these forms of composition are associative.
-In a `pseudo' double category, horizontal 1-cells compose in a weakly associative manner: that is, the associative law holds only up to an invertible 2-morphism, called the `associator', which obeys a coherence law.
-
-The symmetric monoidal double category $F \mathbb{C}$sp we construct has:
-\begin{enumerate}
-\item{objects as those of $\mathrm{A}$,}
-\item{vertical 1-morphisms as morphisms of $\mathrm{A}$,}
-\item{horizontal 1-cells as $F$-decorated cospans in $\mathrm{A}$
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a_1$};
-\node (B) at (1,0) {$b$};
-\node (C) at (2,0) {$a_2$};
-\node (D) at (3,0) {$d \in F(b)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i$} (B)
-(C) edge node[above]{$o$} (B);
-\end{tikzpicture}
-\]
-and}
-\item{2-morphisms as maps of cospans together with a natural transformation.
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$a_1$};
-\node (A') at (0,-0.5) {$a_1'$};
-\node (B) at (1,0.5) {$b$};
-\node (B') at (1,-0.5) {$b'$};
-\node (C) at (2,0.5) {$a_2$};
-\node (C') at (2,-0.5) {$a_2;$};
-\node (D) at (3,0) {$1$};
-\node (E) at (4,0.5) {$F(b)$};
-\node (E') at (4,-0.5) {$F(b')$};
-\node (F) at (3.65,0) {$\Swarrow \tau$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i$} (B)
-(C) edge node[above]{$o$} (B)
-(A) edge node {$$} (A')
-(C) edge node {$$} (C')
-(A') edge node[above]{$i'$} (B')
-(C') edge node[above]{$o'$} (B')
-(B) edge node [left] {$f$} (B')
-(D) edge node [above] {$d$} (E)
-(D) edge node [below] {$d'$} (E')
-(E) edge node [right] {$F(f)$} (E');
-\end{tikzpicture}
-\]
-}
-\end{enumerate}
-Note that the natural transformation is a family of morphisms in the category $F(b')$ indexed by $1$, and so is the same as just a morphism $\tau \maps F(f)(d) \to d'$ in $F(b')$.
-We will typically write the transformation $\tau$ in later sections as a morphism in $F(b')$ to conserve space.
-In the context of the example above involving graphs, this morphism $\tau$ will be a map between two possibly distinct sets of edges and thus already solves the problem.
-
-This double category is in fact fibrant and so a result of Shulman \cite{Shul} allows us to extract from this symmetric monoidal double category $F \mathbb{C}$sp a symmetric monoidal bicategory $F \mathbf{Csp} \mapseqq H(F \lCsp)$ as the `horizontal edge bicategory' of the double category $F \mathbb{C}$sp.
-This bicategory $F \mathbf{Csp}$ has:
-\begin{enumerate}
-\item{objects as those of $\mathrm{A}$,}
-\item{morphisms as the horizontal 1-cells of $F\mathbb{C}$sp, which are $F$-decorated cospans of $\A$
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a_1$};
-\node (B) at (1,0) {$b$};
-\node (C) at (2,0) {$a_2$};
-\node (D) at (3,0) {$d \in F(b)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i$} (B)
-(C) edge node[above]{$o$} (B);
-\end{tikzpicture}
-\]
-and}
-\item{2-morphisms as maps of $F$-decorated cospans in $\A$ with the same feet together with a natrual transformation.
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a_1$};
-\node (B) at (1,1) {$b$};
-\node (B') at (1,-1) {$b'$};
-\node (C) at (2,0) {$a_2$};
-\node (D) at (3,0) {$1$};
-\node (E) at (4,0.5) {$F(b)$};
-\node (E') at (4,-0.5) {$F(b')$};
-\node (F) at (3.65,0) {$\Swarrow \tau$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i$} (B)
-(C) edge node[above]{$o$} (B)
-(A) edge node[below]{$i'$} (B')
-(C) edge node[below]{$o'$} (B')
-(B) edge node [left] {$f$} (B')
-(D) edge node [above] {$d$} (E)
-(D) edge node [below] {$d'$} (E')
-(E) edge node [right] {$F(f)$} (E');
-\end{tikzpicture}
-\]
-}
-\end{enumerate}
-This bicategory $F\mathbf{Csp}$ is superior to the original bicategory $F$Cospan$(A)$ constructed by the second author \cite{Courser} in that it has the 2-morphisms that one would expect such a bicategory to have, such as (\ref{no2morphism}).
-
-Finally, we can decategorify the symmetric monoidal bicategory $F \mathbf{Csp}$ to obtain a symmetric monoidal category $F \textnormal{Csp} \mapseqq D(F\mathbf{Csp})$.
-This symmetric monoidal category $F$Csp has:
-
-\begin{enumerate}
-\item{objects as those of $\A$ and}
-\item{morphisms as isomorphism classes of $F$-decorated cospans in $\A$ with the same feet together with a natural isomorphism, where two $F$-decorated cospans are in the same isomorphism class if $f$ and $\tau$ are isomorphisms.
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a_1$};
-\node (B) at (1,1) {$b$};
-\node (B') at (1,-1) {$b'$};
-\node (C) at (2,0) {$a_2$};
-\node (D) at (3,0) {$1$};
-\node (E) at (4,0.5) {$F(b)$};
-\node (E') at (4,-0.5) {$F(b')$};
-\node (F) at (3.5,0) {$\Swarrow \tau$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i$} (B)
-(C) edge node[above]{$o$} (B)
-(A) edge node[below]{$i'$} (B')
-(C) edge node[below]{$o'$} (B')
-(B) edge node [left] {$f$} (B')
-(B) edge node [right] {$\sim$} (B')
-(D) edge node [above] {$d$} (E)
-(D) edge node [below] {$d'$} (E')
-(E) edge node [right] {$F(f)$} (E')
-(E) edge node [left] {$\sim$} (E');
-\end{tikzpicture}
-\]
-}
-\end{enumerate}
-This symmetric monoidal category $F$Csp has isomorphism classes as one would expect, and in the context of the example with finite sets and graphs above solves the problem in (\ref{distinctisoclasses}).
-In this particular example, $\tau \maps F(f)(d) \xrightarrow{\sim} d'$ is a bijection between possibly different sets of edges which respects the source and target of each edge.
-\fi
-
 \subsection*{Outline}
 
-%{\chris Amend at the end}
-%The outline for the paper is as follows: In \cref{DecCospansDoubleCat}, we construct the symmetric monoidal double category $F\lCsp$, obtain the underlying symmetric monoidal bicategory $F \mathbf{Csp}$ via a result of Shulman, and decategorify this symmetric monoidal bicategory to obtain the symmetric monoidal category $F$Csp.
-In \cref{MapsDecCospansDoubleCat} we define maps between decorated cospan double categories which are double functors of an appropriate type.
-In \cref{some other section} we investigate when a symmetric lax monoidal pseudofunctor gives rise to a left adjoint via the Grothendieck construction, which naturally leads to another compositional framework known as `Structured cospans'.
-In \cref{EquivDoubleCats} we briefly review the framework Structured cospans and prove that the double categorical versions of decorated cospans and structured cospans are equivalent when both are appropriate.
+In \cref{DecCospansDoubleCat}, we construct the symmetric monoidal double category $F\lCsp$ and we define maps between decorated cospan double categories.
+In \cref{EquivDoubleCats}, we briefly review the structured cospans framework and prove that the double categorical versions of decorated cospans and structured cospans are equivalent under suitable conditions.
+In \cref{spinoffs}, we establish the equivalence between structured and decorated cospans on the horizontal bicategory and the ordinary category level (via decategorification).
 Finally, in \cref{Applications}, we present a few examples that can be realized with either framework and discuss the realized equivalences.
@@
 
+In this paper, we use sans-serif font like $\C$ for categories, boldface like $\mathbf{B}$ for bicategories or 2-categories, and blackboard bold like $\lD$ for double categories.
+For double categories with names having more than one letter, like $\lCsp(\X)$, only the first letter is in blackboard bold.
 In this paper, `double category' means `pseudo double category', as in \cref{defn:double_category}.
-Following Shulman \cite{Shulman2008}, vertical composition in our double categories is strictly associative, while horizontal composition need not be.
-We use sans-serif font like $\C$ for categories, boldface like $\mathbf{B}$ for bicategories or 2-categories, and blackboard bold like $\lD$ for double categories.
-We also use blackboard
-bold for weak category objects in any 2-category.
-For double categories with names having more than one letter, like $\lCsp(\X)$, only the first letter is in blackboard bold.
 A double category $\lD$ has a category of objects and a category of arrows, and we call these $\lD_0$ and $\lD_1$ despite the fact that they are categories.
+Vertical composition in our double categories is strictly associative, while horizontal composition need not be.
 
@@
 \end{thm}
-%!!!Kenny: We should try to make this proof shorter.
-%Christina: Yes!
-Again, I think that it can be simplified and easier for the reader to follow.
-Should tackle after we do the previous theorem.
-Also notice that a big part of the following proof is commented out below.
+
 \begin{proof}
@@
 The other diagrams in the definition of symmetric monoidal double category can be shown to commute similarly.
-%!!! Kenny: Probably cut stuff out below this.
-% Christina: Commented them out for now, but should definitely have a close look to see if anything is needed when we go over and remake this proof.
+%%% Kenny: Probably cut stuff out below this.
+%%% Christina: Commented them out for now, but should definitely have a close look to see if anything is needed when we go over and remake this proof.
 \begin{comment}
@@
 \begin{proof}[Proof of \cref{thm:equiv}]
-Recall from \cref{thm:decorated_cospans} that the double category of decorated cospans $F\lCsp$ has objects and vertical 1-morphisms as in $\A$, while horizontal 1-cells are cospans $\cspn{a}{m}{b}{}{}$ in $\A$ decorated by an $x\in F(m)$ and 2-morphisms are maps of cospans $k\maps m\to m'$ together with $\tau\maps(Fk)(x)\to x'$ in $F(m')$.%!!!
-Christina: Should we call them `generalized maps of cospans'?
-Since maps of cospans are usually the ones with fixed (co)domains
+Recall from \cref{thm:decorated_cospans} that the double category of decorated cospans $F\lCsp$ has objects and vertical 1-morphisms as in $\A$, while horizontal 1-cells are cospans $\cspn{a}{m}{b}{}{}$ in $\A$ decorated by an $x\in F(m)$ and 2-morphisms are maps of cospans $k\maps m\to m'$ together with $\tau\maps(Fk)(x)\to x'$ in $F(m')$.
 
@@
 
-%!!!Kenny: Is this biequivalnce symmetric monoidal? Mike says yes, but it follows from a result that he has yet to officially publish. It's a result of a paper he's currently working on with someone.
-%!!!Christina: Kenny, is the above comment still relevant? If not, feel free to erase!
+%%% Is this biequivalnce symmetric monoidal? Mike says yes, but it follows from a result that he has yet to officially publish. It's a result of a paper he's currently working on with someone.
+%%% Christina: Kenny, is the above comment still relevant? If not, feel free to erase!
 
@@
 \subsection{Double categories}\label{sec:doublecats}
-%!!! Christina: Kenny, would you mind cleaning this section up to? I don't believe we need the full fledged definitions here by the way.
+%%% Christina: Kenny, would you mind cleaning this section up to? I don't believe we need the full fledged definitions here by the way.
 
@@
 
-%!!! Christina: Pretty sure the def below can be incorporated above, however got a bit lost in different notation. Kenny Fix?
+%%% Christina: Pretty sure the def below can be incorporated above, however got a bit lost in different notation. Kenny Fix?
 %\begin{defn}

### 2020-11-23 cospans.tex
going through 2.1

@@
 \item a vertical 1-morphism is a morphism of $\A$,
-\item a horizontal 1-cell is an $F$\define{-decorated cospan}: that is, 
+\item a horizontal 1-cell is an $F$\define{-decorated cospan}, that is, 
 a cospan in $\A$:
@@
 together with a \define{decoration} $x \in F(m)$,
-\item a 2-morphism is a \define{map of} $F$\define{-decorated cospans}: that is, 
+\item a 2-morphism is a \define{map of} $F$\define{-decorated cospans}, that is, 
 a map of cospans in $\A$:
-\begin{displaymath}
+\begin{equation}\label{eq:mapofdec}
 \begin{tikzpicture}[scale=1.5]
@@
 \end{tikzpicture}
-\end{displaymath}
+\end{equation}
 together with a \define{decoration morphism} $\tau \maps F(h)(x) \to x'$ in $F(m')$.
@@
 \begin{proof}
-The definition of double category may be found in Definition \ref{defn:double_category}.
-To show that the pseudofunctor $F$ in the theorem statement induces a double category $F\lCsp$, we must first define the category of objects $F\lCsp_0$, the category of arrows $F\lCsp_1$, as well as the four structure functors which tie them together: the source and target functors $S,T \colon F\lCsp_1 \to F\lCsp_0$, the unit functor $U \colon F\lCsp_0 \to F\lCsp_1$ and the composition functor $\odot$ which says how to compose two composable horizontal 1-cells or two composable 2-morphisms horizontally: $$\odot \colon F\lCsp_1 \times_{F\lCsp_0} F\lCsp_1 \to F\lCsp_1.$$
-
-The category of objects $F\lCsp_0$ is simply the category $\A$.
-The category of arrows $F\lCsp_1$ has $F$-decorated cospans for objects and maps of $F$-decorated cospans as morphisms.
-Given two vertically composable $F$-decorated cospans:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$a$};
-\node (A') at (0,-0.5) {$a'$};
-\node (B) at (1,0.5) {$m$};
-\node (C) at (2,0.5) {$b$};
-\node (C') at (2,-0.5) {$b'$};
-\node (D) at (1,-0.5) {$m'$};
-\node (E) at (3,0.5) {$x \in F(m)$};
-\node (F) at (3,-0.5) {$x' \in F(m')$};
-\node (G) at (1.5,-1) {$\tau \colon F(h)(x) \to x'$};
-\node (A'') at (0,-1.5) {$a'$};
-\node (A''') at (0,-2.5) {$a''$};
-\node (B'') at (1,-1.5) {$m'$};
-\node (C'') at (2,-1.5) {$b'$};
-\node (C''') at (2,-2.5) {$b''$};
-\node (D'') at (1,-2.5) {$m''$};
-\node (E'') at (3,-1.5) {$x' \in F(m')$};
-\node (F'') at (3,-2.5) {$x'' \in F(m'')$};
-\node (G'') at (1.5,-3) {$\tau' \colon F(h')(x') \to x''$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i$} (B)
-(C) edge node[above]{$o$} (B)
-(A) edge node[left]{$f$} (A')
-(C) edge node[right]{$g$} (C')
-(A') edge node[above] {$i'$} (D)
-(C') edge node[above] {$o'$} (D)
-(B) edge node [left] {$h$} (D)
-(A'') edge node[above]{$i'$} (B'')
-(C'') edge node[above]{$o'$} (B'')
-(A'') edge node[left]{$f'$} (A''')
-(C'') edge node[right]{$g'$} (C''')
-(A''') edge node[above] {$i''$} (D'')
-(C''') edge node[above] {$o''$} (D'')
-(B'') edge node [left] {$h'$} (D'');
-\end{tikzpicture}
-\]
-their composite is given by the composite of the two maps of cospans in $\A$
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$a$};
-\node (A') at (0,-0.5) {$a''$};
-\node (B) at (1,0.5) {$m$};
-\node (C) at (2,0.5) {$b$};
-\node (C') at (2,-0.5) {$b''$};
-\node (D) at (1,-0.5) {$m''$};
-\node (E) at (3,0.5) {$x \in F(m)$};
-\node (F) at (3,-0.5) {$x'' \in F(m'')$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i$} (B)
-(C) edge node[above]{$o$} (B)
-(A) edge node[left]{$f'f$} (A')
-(C) edge node[right]{$g'g$} (C')
-(A') edge node[above] {$i''$} (D)
-(C') edge node[above] {$o''$} (D)
-(B) edge node [left] {$h'h$} (D);
-\end{tikzpicture}
-\]
-together with the composite decoration morphism $\tau' F(\tau) \colon F(h'h)(x) \to x'$ in $F(m'')$.
-% this was:
-% together with the composite morphism of decorations $\tau' \tau \colon F(h'h)(x) \to x'$ in $F(m'')$
-%% \tau' \tau was the notation that I was using, but I see why this was misleading. I believe it should be called \tau'(F(h')(\tau)) \instead of \tau' F(\tau), and also with target x''.
- This completes the descriptions of the category of objects $F\lCsp_0 = \A$ and the category of arrows $F\lCsp_1$.
-
-Next, we define the four structure functors $U,S,T$ and $\odot$. The unit functor $U \maps F\lCsp_0 \to F\lCsp_1$ is defined on objects as: 
+According to \cref{defn:double_category}, we will define the category of objects $F\lCsp_0$, the category of arrows $F\lCsp_1$, as well as the four structure functors which tie them together: the source and target functors $S,T \colon F\lCsp_1 \to F\lCsp_0$, the composition functor
+$\odot \colon F\lCsp_1 \times_{F\lCsp_0} F\lCsp_1 \to F\lCsp_1$ and the unit functor $U \colon F\lCsp_0 \to F\lCsp_1$.
+
+The category of objects $F\lCsp_0$ is simply the category $\A$, whereas $F$-decorated cospans and maps between them form the category of arrows $F\lCsp_1$.
+For example, the (vertical) composition of two $F$-decorated cospans maps is
+\begin{displaymath}
+ \begin{tikzcd}
+a\ar[r,"i"]\ar[d,"f"'] & m\ar[d,"h"] & b\ar[l,"o"]\ar[d,"g"]  & x\in F(m) \\
+a'\ar[r,"{i'}"]\ar[d,"{f'}"] & m'\ar[d,"{h'}"] & b'\ar[l,"{o'}"']\ar[d,"{g'}"] & x'\in F(m') \\
+a''\ar[r,"{i''}"'] & m'' & b''\ar[l,"{o''}"'] & x''\in F(m'')
+ \end{tikzcd}\;=\;
+ \begin{tikzcd}[column sep=.4in]
+a\ar[r,"i"]\ar[dd,"{f'f}"'] & m\ar[dd,"{h'h}"] & b\ar[l,"o"]\ar[dd,"{g'g}"]  & x\in F(m) \\
+\hole \\
+a''\ar[r,"{i''}"] & m'' & b''\ar[l,"{o''}"'] & x''\in F(m'')  
+ \end{tikzcd}
+\end{displaymath}
+where if $\tau \colon F(h)(x) \to x'$ and $\tau' \colon F(h')(x') \to x''$ are the decoration morphisms, $\tau' F(\tau) \colon F(h'h)(x) \to x''$ is the composite one.
+The source and target functors map an $F$-decorated cospan to the source and target of the cospan and a map of decorated cospans \cref{eq:mapofdec} to $f$ and $g$ respectively.
+
+The unit functor $U \maps F\lCsp_0 \to F\lCsp_1$ is defined on objects as: 
 \begin{equation}\label{eq:UFCsp}
@@
 together with the morphism $\tau_{\bot_f} = F(f) F(!) \phi \maps 1 \to F(a')$.
-For the source and target functors $S, T \maps F\lCsp_1 \to F\lCsp_0$, given an object $F\lCsp_1$, which is an $F$-decorated cospan,
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a$};
-\node (B) at (1,0) {$m$};
-\node (C) at (2,0) {$b$};
-\node (D) at (3,0) {$x \in F(m)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i$} (B)
-(C) edge node[above]{$o$} (B);
-\end{tikzpicture}
-\]
-the source is the object $a$ and the target is the object $b$. Given a morphism of $F\lCsp_1$, which is a map of $F$-decorated cospans,
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$a$};
-\node (A') at (0,-0.5) {$a'$};
-\node (B) at (1,0.5) {$m$};
-\node (C) at (2,0.5) {$b$};
-\node (C') at (2,-0.5) {$b'$};
-\node (D) at (1,-0.5) {$m'$};
-\node (E) at (3,0.5) {$x \in F(m)$};
-\node (F) at (3,-0.5) {$x' \in F(m')$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i$} (B)
-(C) edge node[above]{$o$} (B)
-(A) edge node[left]{$f$} (A')
-(C) edge node[right]{$g$} (C')
-(A') edge node[above] {$i'$} (D)
-(C') edge node[above] {$o'$} (D)
-(B) edge node [left] {$h$} (D);
-\end{tikzpicture}
-\]
-$$\tau \maps F(h)(x) \to x'$$
-the source is the morphism $f$ and the target is the morphism $g$. The three functors $S,T$ and $U$ satisfy the equations $SU=\id_{\A}=TU$.
 
@@
 The interchange law for $\Cat$ says that these two composites must be the same as well, and thus the interchange law for our double category $F\lCsp$ is also satisfied.
- %\noindent
-%\textbf{In progress...}
-%we get a natural isomorphism $a_{M_1,M_2,M_3} \maps (M_1 \odot M_2) \odot M_3 \to M_1 \odot (M_2 \odot M_3)$ which is a globular 2-morphism given by a map of cospans $(\id_{a_1},\sigma,\id_{a_4})$:
-%with the decorations on the cospan's apices given by:
-%$$ (x \odot y) \odot z \mapseqq 1 \xrightarrow{\zeta_1} F(m_1+_{b} m_2) \times F(m_3) \xrightarrow{\phi_{m_1+_{b} m_2, m_3}} F((m_1+_{b}m_2) +m_3) \xrightarrow{F(j_{m_1+_{b} m_2,m_3})} F((m_1+_{b} m_2)+_{c} m_3)$$ $$\zeta_1 = (1 \times z) \rho^{-1} F(j_{m_1,m_2}) \phi_{m_1,m_2} (x \times y) \lambda^{-1}$$
-%and
-%$$ x \odot (y \odot z) \mapseqq 1 \xrightarrow{\zeta_2} F(m_1) \times F(m_2 +_{c} m_3) \xrightarrow{\phi_{m_1, m_2 +_{c} m_3}} F(m_1+(m_2 +_{c} m_3)) \xrightarrow{F(j_{m_1,m_2 +_{c} m_3})} F(m_1+_{b} (m_2+_{c} m_3))$$ $$\zeta_2 = (x \times 1) \lambda^{-1} F(j_{m_2,m_3}) \phi_{m_2,m_3} (y \odot z) \lambda^{-1}$$
-%together with the isomorphism $\tau_\sigma \maps F(\sigma)((x \odot y) \odot z) \to x \odot (y \odot z)$.
-Note that the map $\sigma \maps (m_1+_{b} m_2)+_{c}m_3 \to m_1+_{b}(m_2+_{c}m_3)$ is the universal map between two colimits of the same diagram.
-%\noindent
-%We also have left and right unitors where given a horizontal 1-cell $M$:
-%\[
-%\begin{tikzpicture}[scale=1.5]
-%\node (A) at (0,0) {$a$};
-%\node (B) at (1,0) {$m$};
-%\node (C) at (2,0) {$b$};
+\begin{comment}
+ The definition of double category may be found in Definition \ref{defn:double_category}.
+To show that the pseudofunctor $F$ in the theorem statement induces a double category $F\lCsp$, we must first define the category of objects $F\lCsp_0$, the category of arrows $F\lCsp_1$, as well as the four structure functors which tie them together: the source and target functors $S,T \colon F\lCsp_1 \to F\lCsp_0$, the unit functor $U \colon F\lCsp_0 \to F\lCsp_1$ and the composition functor $\odot$ which says how to compose two composable horizontal 1-cells or two composable 2-morphisms horizontally: $$\odot \colon F\lCsp_1 \times_{F\lCsp_0} F\lCsp_1 \to F\lCsp_1.$$
+
+The category of objects $F\lCsp_0$ is simply the category $\A$.
+The category of arrows $F\lCsp_1$ has $F$-decorated cospans for objects and maps of $F$-decorated cospans as morphisms.
+Given two vertically composable $F$-decorated cospans:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0.5) {$a$};
+\node (A') at (0,-0.5) {$a'$};
+\node (B) at (1,0.5) {$m$};
+\node (C) at (2,0.5) {$b$};
+\node (C') at (2,-0.5) {$b'$};
+\node (D) at (1,-0.5) {$m'$};
+\node (E) at (3,0.5) {$x \in F(m)$};
+\node (F) at (3,-0.5) {$x' \in F(m')$};
+\node (G) at (1.5,-1) {$\tau \colon F(h)(x) \to x'$};
+\node (A'') at (0,-1.5) {$a'$};
+\node (A''') at (0,-2.5) {$a''$};
+\node (B'') at (1,-1.5) {$m'$};
+\node (C'') at (2,-1.5) {$b'$};
+\node (C''') at (2,-2.5) {$b''$};
+\node (D'') at (1,-2.5) {$m''$};
+\node (E'') at (3,-1.5) {$x' \in F(m')$};
+\node (F'') at (3,-2.5) {$x'' \in F(m'')$};
+\node (G'') at (1.5,-3) {$\tau' \colon F(h')(x') \to x''$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i$} (B)
+(C) edge node[above]{$o$} (B)
+(A) edge node[left]{$f$} (A')
+(C) edge node[right]{$g$} (C')
+(A') edge node[above] {$i'$} (D)
+(C') edge node[above] {$o'$} (D)
+(B) edge node [left] {$h$} (D)
+(A'') edge node[above]{$i'$} (B'')
+(C'') edge node[above]{$o'$} (B'')
+(A'') edge node[left]{$f'$} (A''')
+(C'') edge node[right]{$g'$} (C''')
+(A''') edge node[above] {$i''$} (D'')
+(C''') edge node[above] {$o''$} (D'')
+(B'') edge node [left] {$h'$} (D'');
+\end{tikzpicture}
+\]
+their composite is given by the composite of the two maps of cospans in $\A$
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0.5) {$a$};
+\node (A') at (0,-0.5) {$a''$};
+\node (B) at (1,0.5) {$m$};
+\node (C) at (2,0.5) {$b$};
+\node (C') at (2,-0.5) {$b''$};
+\node (D) at (1,-0.5) {$m''$};
+\node (E) at (3,0.5) {$x \in F(m)$};
+\node (F) at (3,-0.5) {$x'' \in F(m'')$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i$} (B)
+(C) edge node[above]{$o$} (B)
+(A) edge node[left]{$f'f$} (A')
+(C) edge node[right]{$g'g$} (C')
+(A') edge node[above] {$i''$} (D)
+(C') edge node[above] {$o''$} (D)
+(B) edge node [left] {$h'h$} (D);
+\end{tikzpicture}
+\]
+together with the composite decoration morphism $\tau' F(\tau) \colon F(h'h)(x) \to x'$ in $F(m'')$.
+% this was:
+% together with the composite morphism of decorations $\tau' \tau \colon F(h'h)(x) \to x'$ in $F(m'')$
+%% \tau' \tau was the notation that I was using, but I see why this was misleading. I believe it should be called \tau'(F(h')(\tau)) \instead of \tau' F(\tau), and also with target x''.
+ This completes the descriptions of the category of objects $F\lCsp_0 = \A$ and the category of arrows $F\lCsp_1$.
+
+Next, we define the four structure functors $U,S,T$ and $\odot$. The unit functor $U \maps F\lCsp_0 \to F\lCsp_1$ is defined on objects as: 
+\begin{equation}\label{eq:UFCsp}
+\begin{tikzpicture}[scale=1.5]
+\node (E) at (-1,0) {$a$};
+\node (F) at (-.5,0) {$\mapsto$};
+\node (A) at (0,0) {$a$};
+\node (B) at (1,0) {$a$};
+\node (C) at (2,0) {$a$};
+\node (D) at (3,0) {$\bot_a \in F(a)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$1$} (B)
+(C) edge node[above]{$1$} (B);
+\end{tikzpicture}
+\end{equation}
+where $\bot_a \in F(a)$ is the \define{trivial decoration} on $a$ given by the composite of the unique map $F(!) \maps F(0) \to F(a)$ and the morphism $\phi \maps 1 \to F(0)$  which comes from $F \maps \A \to \Cat$ being lax monoidal.
+For morphisms, the functor $U$ is defined as:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (G) at (-1,0.5) {$a$};
+\node (G') at (-1,-0.5) {$a'$};
+\node (A) at (0,0.5) {$a$};
+\node (A') at (0,-0.5) {$a'$};
+\node (B) at (1,0.5) {$a$};
+\node (C) at (2,0.5) {$a$};
+\node (C') at (2,-0.5) {$a'$};
+\node (D) at (1,-0.5) {$a'$};
+\node (E) at (3,0.5) {$\bot_a \in F(a)$};
+\node (F) at (3,-0.5) {$\bot_{a'} \in F(a')$};
+\node (H) at (-0.5,0) {$\mapsto$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$1$} (B)
+(C) edge node[above]{$1$} (B)
+(A) edge node[left]{$f$} (A')
+(C) edge node[right]{$f$} (C')
+(A') edge node[above] {$1$} (D)
+(C') edge node[above] {$1$} (D)
+(B) edge node [left] {$f$} (D)
+(G) edge node [left] {$f$} (G');
+\end{tikzpicture}
+\]
+together with the morphism $\tau_{\bot_f} = F(f) F(!) \phi \maps 1 \to F(a')$.
+For the source and target functors $S, T \maps F\lCsp_1 \to F\lCsp_0$, given an object $F\lCsp_1$, which is an $F$-decorated cospan,
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$a$};
+\node (B) at (1,0) {$m$};
+\node (C) at (2,0) {$b$};
+\node (D) at (3,0) {$x \in F(m)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i$} (B)
+(C) edge node[above]{$o$} (B);
+\end{tikzpicture}
+\]
+the source is the object $a$ and the target is the object $b$. Given a morphism of $F\lCsp_1$, which is a map of $F$-decorated cospans,
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0.5) {$a$};
+\node (A') at (0,-0.5) {$a'$};
+\node (B) at (1,0.5) {$m$};
+\node (C) at (2,0.5) {$b$};
+\node (C') at (2,-0.5) {$b'$};
+\node (D) at (1,-0.5) {$m'$};
+\node (E) at (3,0.5) {$x \in F(m)$};
+\node (F) at (3,-0.5) {$x' \in F(m')$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i$} (B)
+(C) edge node[above]{$o$} (B)
+(A) edge node[left]{$f$} (A')
+(C) edge node[right]{$g$} (C')
+(A') edge node[above] {$i'$} (D)
+(C') edge node[above] {$o'$} (D)
+(B) edge node [left] {$h$} (D);
+\end{tikzpicture}
+\]
+$$\tau \maps F(h)(x) \to x'$$
+the source is the morphism $f$ and the target is the morphism $g$. The three functors $S,T$ and $U$ satisfy the equations $SU=\id_{\A}=TU$.
+
+Next we define the composite functor $\odot \colon F\lCsp_1 \times_{F\lCsp_0} F\lCsp_1 \to F\lCsp_1$, which amounts to defining how we compose two composable $F$-decorated cospans or horizontally compose two maps of $F$-decorated cospans with a common source and target.
+Given two composable $F$-decorated cospans which we respectively denote by $M$ and $N$, the capitals of their apices:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$a$};
+\node (B) at (1,0) {$m$};
+\node (C) at (2,0) {$b$};
+\node (D) at (1,-0.5) {$x \in F(m)$};
+\node (E) at (3,0) {$b$};
+\node (F) at (4,0) {$n$};
+\node (G) at (5,0) {$c$};
+\node (H) at (4,-0.5) {$y \in F(n)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i$} (B)
+(C) edge node[above]{$o$} (B)
+(E) edge node[above]{$i'$} (F)
+(G) edge node[above]{$o'$} (F);
+\end{tikzpicture}
+\]
+the composite $M \odot N$ is given by taking the pushout of the two cospans in $\A$ over the shared foot which is the object $b$:
+\begin{equation}\label{eq:dcospanscomposition}
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$a$};
+\node (B) at (1,1) {$m$};
+\node (C) at (2,0) {$b$};
+\node (D) at (3,1) {$n$};
+\node (E) at (4,0) {$c$};
+\node (F) at (2,2) {$m+n$};
+\node (G) at (2,3) {$m+_{b} n$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i$} (B)
+(C) edge node[above]{$o$} (B)
+(C) edge node [above] {$i'$} (D)
+(E) edge node [above] {$o'$} (D)
+(B) edge node [above] {$j_m$} (F)
+(D) edge node [above] {$j_{n}'$} (F)
+(F) edge node [left] {$\psi$} (G)
+(A) edge[bend left] node [left] {$\psi j_m i$} (G)
+(E) edge[bend right] node [right] {$\psi j_{n}' o'$} (G);
+\end{tikzpicture}
+\end{equation}
+The composite decoration $x \odot y$ on the apex $m+_b n$ is given by:
+$$x \odot y = 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{x \times y} F(m) \times F(n) \xrightarrow{\phi_{m,n}} F(m+n) \xrightarrow{F(\psi)} F(m+_{b}n)$$
+where $\psi \maps m + n \to m+_{b} n$ is the natural map from the coproduct to the pushout and $\phi_{m,n} \maps F(m) \times F(n) \to F(m+n)$ is the natural transformation coming from the structure of the lax monoidal pseudofunctor $F \maps \A \to \Cat$.
+Given two horizontally composable maps of $F$-decorated cospans which we respectively denote by $\alpha$ and $\beta$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0.5) {$a$};
+\node (A') at (0,-0.5) {$a'$};
+\node (B) at (1,0.5) {$m$};
+\node (C) at (2,0.5) {$b$};
+\node (C') at (2,-0.5) {$b'$};
+\node (D) at (1,-0.5) {$m'$};
+\node (E) at (3,0.5) {$x \in F(m)$};
+\node (F) at (3,-0.5) {$x' \in F(m')$};
+\node (G) at (4,0.5) {$b$};
+\node (H) at (5,0.5) {$n$};
+\node (I) at (6,0.5) {$c$};
+\node (G') at (4,-0.5) {$b'$};
+\node (H') at (5,-0.5) {$n'$};
+\node (I') at (6,-0.5) {$c'$};
+\node (J) at (7,0.5) {$y \in F(n)$};
+\node (K) at (7,-0.5) {$y' \in F(n')$};
+\node (L) at (1,-1) {$\tau_\alpha \maps F(h_1)(x) \to x'$};
+\node (M) at (5,-1) {$\tau_\beta \maps F(h_2)(y) \to y'$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i_1$} (B)
+(C) edge node[above]{$o_1$} (B)
+(A) edge node[left]{$f$} (A')
+(C) edge node[right]{$g$} (C')
+(A') edge node[above] {$i_1'$} (D)
+(C') edge node[above] {$o_1'$} (D)
+(B) edge node [left] {$h_1$} (D)
+(G) edge node [above] {$i_2$} (H)
+(G) edge node [left] {$g$} (G')
+(H) edge node [left] {$h_2$} (H')
+(G') edge node [above] {$i_2'$} (H')
+(I) edge node [above] {$o_2$} (H)
+(I) edge node [right] {$k$} (I')
+(I') edge node [above] {$o_2'$} (H');
+\end{tikzpicture}
+\]
+their horizontal composite $\alpha \odot \beta$ is the pair given by first horizontally composing the two maps of cospans in $\A$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0.5) {$a$};
+\node (A') at (0,-0.5) {$a'$};
+\node (B) at (1.5,0.5) {$m+_{b} n$};
+\node (C) at (3,0.5) {$c$};
+\node (C') at (3,-0.5) {$c'$};
+\node (D) at (1.5,-0.5) {$m'+_{b'}n'$};
+\node (E) at (4.5,0.5) {$x \odot y \in F(m+_b n)$};
+\node (F) at (4.5,-0.5) {$x' \odot y' \in F(m' +_{b'} n')$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$\psi j_m i_1$} (B)
+(C) edge node[above]{$\psi j_n o_2$} (B)
+(A) edge node[left]{$f$} (A')
+(C) edge node[right]{$k$} (C')
+(A') edge node [above]{$\psi j_{m'} i_1'$} (D)
+(C') edge node [above]{$\psi j_{n'} o_2'$} (D)
+(B) edge node [left] {$h_1 +_g h_2$} (D);
+\end{tikzpicture}
+\]
+together with the decoration morphism $\tau_{\alpha \odot \beta} \colon F(h_1 +_g h_2)(x \odot y) \to (x' \odot y')$ given by the following commutative diagram:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (4.75,0) {$\tau_\alpha \times \tau_\beta \Swarrow$};
+\node (D) at (3,0) {$1 \xrightarrow{\lambda^{-1}} 1 \times 1$};
+\node (E) at (5.5,0.5) {$F(m) \times F(n)$};
+\node (E') at (5.5,-0.5) {$F(m') \times F(n')$};
+\node (B) at (7.5,0.5) {$F(m+n)$};
+\node (B') at (7.5,-0.5) {$F(m' + n')$};
+\node (C) at (9.25,0.5) {$F(m+_{b} n)$};
+\node (C') at (9.25,-0.5) {$F(m' +_{b'} n')$};
+\path[->,font=\scriptsize,>=angle 90]
+(E) edge node [above] {$\phi_{m,n}$} (B)
+(E') edge node [above] {$\phi_{m',n'}$} (B')
+(B) edge node [above] {$F(\psi)$} (C)
+(B') edge node [above] {$F(\psi)$} (C')
+(C) edge node [right] {$F(h_1 +_g h_2)$} (C')
+(B) edge node [right] {$F(h_1 + h_2)$} (B')
+(D) edge node [above] {$x \times y$} (E)
+(D) edge node [below] {$x' \times y'$} (E')
+(E) edge node [right] {$F(h_1) \times F(h_2)$} (E');
+\end{tikzpicture}
+\]
+The middle square commutes since $F$ is a lax monoidal pseudofunctor and the right square commutes as the underlying square commutes.
+The decorations $x \odot y$ and $x' \odot y'$ are given respectively by the top and bottom composite of arrows and the decoration morphism $\tau_{\alpha \odot \beta}$ is given by composing $\tau_\alpha \times \tau_\beta$ with the two commuting squares.
+It is clear that the equations $S(M \odot N)=S(M)$ and $T(M \odot N)=T(N)$ hold, and this finishes defining the four structure functors $U,S,T$ and $\odot$.
+
+Lastly, our double category is required to have an associator $\alpha$ and left and right unitors $\lambda$ and $\rho$ which are natural isomorphisms governing the composition of horizontal 1-cells that are required to satisfy the standard coherence axioms for a monoidal category, as well as $S(\alpha),S(\lambda),S(\rho),T(\alpha),T(\lambda)$ and $T(\rho)$ all being identities.
+We will only show the associator $\alpha$, left unitor $\lambda$ and the pentagon identity, as the remaining details will be similar to these.
+
+First we will build the associator $\alpha \colon \odot (\odot \times 1) \Rightarrow \odot (1 \times \odot)$, which will be a globular 2-morphism; in other words, a map of $F$-decorated cospans with identities on the sides.
+Given three composable horizontal 1-cells $M_1, M_2$ and $M_3$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$a$};
+\node (B) at (1,0) {$m_1$};
+\node (C) at (2,0) {$b$};
+\node (D) at (1,-0.5) {$x_1 \in F(m_1)$};
+\node (E) at (3,0) {$b$};
+\node (F) at (4,0) {$m_2$};
+\node (G) at (5,0) {$c$};
+\node (H) at (4,-0.5) {$x_2 \in F(m_2)$};
+\node (I) at (6,0) {$c$};
+\node (J) at (7,0) {$m_3$};
+\node (K) at (8,0) {$d$};
+\node (L) at (7,-0.5) {$x_3 \in F(m_3)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i$} (B)
+(C) edge node[above]{$o$} (B)
+(E) edge node[above]{$i'$} (F)
+(G) edge node[above]{$o'$} (F)
+(I) edge node[above]{$i''$} (J)
+(K) edge node[above]{$o''$} (J);
+\end{tikzpicture}
+\]
+we first compute $(M_1 \odot M_2) \odot M_3)$ by pushing out the first two cospans followed by the third:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$a$};
+\node (B) at (2,0) {$(m_1 +_b m_2) +_c m_3$};
+\node (C) at (4,0) {$d$};
 %\node (D) at (3,0) {$x \in F(m)$};
-%\path[->,font=\scriptsize,>=angle 90]
-%(A) edge node[above]{$i$} (B)
-%(C) edge node[above]{$o$} (B);
-%\end{tikzpicture}
-%\]
-%if we, say, compose with the identity horizontal 1-cell of $b$ on the right:
-%\[
-%\begin{tikzpicture}[scale=1.5]
-%\node (A) at (0,0) {$a$};
-%\node (B) at (1,0) {$m$};
-%\node (C) at (2,0) {$b$};
-%\node (D) at (1,-0.5) {$x \in F(m)$};
-%\node (E) at (3,0) {$b$};
-%\node (F) at (4,0) {$b$};
-%\node (G) at (5,0) {$b$};
-%\node (H) at (4,-0.5) {$!_{b} \in F(b)$};
-%\path[->,font=\scriptsize,>=angle 90]
-%(A) edge node[above]{$i$} (B)
-%(C) edge node[above]{$o$} (B)
-%(E) edge node[above]{$1$} (F)
-%(G) edge node[above]{$1$} (F);
-%\end{tikzpicture}
-%\]
-%where $!_{b} = F(!)  \phi \maps 1 \to F(b)$ is the trivial decoration on $b$, composing these then gives:
-%\[
-%\begin{tikzpicture}[scale=1.5]
-%\node (A) at (0,0) {$a$};
-%\node (B) at (1,0) {$m+_{b} b$};
-%\node (C) at (2,0) {$b$};
-%\node (D) at (3.5,0) {$x \odot !_b \in F(m +_{b} b)$};
-%\path[->,font=\scriptsize,>=angle 90]
-%(A) edge node[above]{$j \psi_m i$} (B)
-%(C) edge node[above]{$j \psi_{b}$} (B);
-%\end{tikzpicture}
-%\]
-%where $\psi_m \maps m \to m+b$ is the natural map into the coproduct and likewise for $\psi_{b}$ and $j \maps m+b \to m+_{b} b$ is the natural map from the coproduct to the pushout.
-The decoration $x \odot !_b \maps 1 \to F(m+_{b} b)$ is given by: $$1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{x \times !_{b}} F(m) \times F(b) \xrightarrow{\phi_{m,b}} F(m+b) \xrightarrow{F(j_{m,b})} F(m+_{b} b).$$ We then have that the right unitor $R \maps M \odot 1_{b} \xrightarrow{\sim} M$ is given by the globular 2-morphism $(\id_{a},r,\id_{b})$ from the above composite to $M$:
-%\[
-%\begin{tikzpicture}[scale=1.5]
-%\node (A) at (0,0.5) {$a$};
-%\node (A') at (0,-0.5) {$a$};
-%\node (B) at (1.5,0.5) {$m+_{b} b$};
-%\node (C) at (3,0.5) {$b$};
-%\node (C') at (3,-0.5) {$b$};
-%\node (D) at (1.5,-0.5) {$m$};
-%\node (E) at (4.5,0.5) {$x \odot !_b \in F(m+_{b} b)$};
-%\node (F) at (4.5,-0.5) {$x \in F(m)$};
-%\path[->,font=\scriptsize,>=angle 90]
-%(A) edge node[above]{$j \psi_m i$} (B)
-%(C) edge node[above]{$j \psi_{b}$} (B)
-%(A) edge node[left]{$\id_{a}$} (A')
-%(C) edge node[right]{$\id_{b}$} (C')
-%(A') edge node [above]{$i$} (D)
-%(C') edge node [above]{$o$} (D)
-%(B) edge node [left] {$r$} (D);
-%\end{tikzpicture}
-%\]
-%where $r \maps m+_{b} b \xrightarrow{\sim} m$ is a universal map together with the isomorphism $\tau_r \maps F(r)(x \odot !_b) \to x$.
-The left unitor is similar.
-The source and target functor applied to the left and right unitors and associators yield identities, and the left and right unitors together with the associator satisfy the standard pentagon and triangle identities of a monoidal category or bicategory.
-Finally, for the interchange law, given four 2-morphisms $\alpha, \beta, \alpha'$ and $\beta'$:
-%if we first compose horizontally we obtain:
-%\[
-%\begin{tikzpicture}[scale=1.5]
-%\node (A) at (0,0.5) {$a$};
-%\node (A') at (0,-0.5) {$a'$};
-%\node (B) at (1.5,0.5) {$m+_{b} n$};
-%\node (C) at (3,0.5) {$c$};
-%\node (C') at (3,-0.5) {$c'$};
-%\node (D) at (1.5,-0.5) {$m' +_{b'} n'$};
-%\node (E) at (4.5,0.5) {$x \odot y \in F(m+_{b} n)$};
-%\node (F) at (4.5,-0.5) {$x' \odot y' \in F(m' +_{b'} n')$};
-%\node (G) at (1.5,-1) {$\tau_{\alpha \odot \beta} \maps F(h_1 +_g h_2)(x \odot y) \to x' \odot y'$};
-%\node (A'') at (0,-1.5) {$a'$};
-%\node (A''') at (0,-2.5) {$a''$};
-%\node (B'') at (1.5,-1.5) {$m' +_{b\prime} n'$};
-%\node (C'') at (3,-1.5) {$c'$};
-%\node (C''') at (3,-2.5) {$c''$};
-%\node (D'') at (1.5,-2.5) {$m'' +_{b''} n''$};
-%\node (E'') at (4.5,-1.5) {$x' \odot y' \in F(m'+_{b'} n')$};
-%\node (F'') at (4.5,-2.5) {$x'' \odot y'' \in F(m'' +_{b''} n'')$};
-%\node (G'') at (1.5,-3) {$\tau_{\alpha' \odot \beta'} \maps F(h_1' +_{g'} h_2')(x' \odot y') \to x'' \odot y''.$};
-%\path[->,font=\scriptsize,>=angle 90]
-%(A) edge node[above]{$j \psi_{m} i_1$} (B)
-%(C) edge node[above]{$j \psi_{n} o_2$} (B)
-%(A) edge node[left]{$f$} (A')
-%(C) edge node[right]{$k$} (C')
-%(A') edge node [above]{$j \psi_{m'} i_1'$} (D)
-%(C') edge node [above]{$j \psi_{n'} o_2'$} (D)
-%(B) edge node [left] {$h_1 +_g h_2$} (D)
-%(A'') edge node[above]{$j \psi_{m'} i_1'$} (B'')
-%(C'') edge node[above]{$j \psi_{n'} o_2'$} (B'')
-%(A'') edge node[left]{$f'$} (A''')
-%(C'') edge node[right]{$k'$} (C''')
-%(A''') edge node [above]{$j \psi_{m''} i_1''$} (D'')
-%(C''') edge node [above]{$j \psi_{n''} o_2''$} (D'')
-%(B'') edge node [left] {$h_1' +_{g'} h_2'$} (D'');
-%\end{tikzpicture}
-%\]
-%To obtain the morphism of decorations for a horizontal composite, we have as initial data:
-%\[
-%\begin{tikzpicture}[scale=1.5]
-%\node (A) at (4,0) {$\tau_\alpha \Swarrow$};
-%\node (D) at (3,0) {$1$};
-%\node (E) at (4.5,0.5) {$F(m)$};
-%\node (E') at (4.5,-0.5) {$F(m')$};
-%\node (A') at (6.5,0) {$\tau_\beta \Swarrow$};
-%\node (D') at (5.5,0) {$1$};
-%\node (E'') at (7,0.5) {$F(n)$};
-%\node (E''') at (7,-0.5) {$F(n')$};
-%\path[->,font=\scriptsize,>=angle 90]
-%(D) edge node [above] {$x$} (E)
-%(D) edge node [below] {$x'$} (E')
-%(E) edge node [right] {$F(h_1)$} (E')
-%(D') edge node [above] {$y$} (E'')
-%(D') edge node [below] {$y'$} (E''')
-%(E'') edge node [right] {$F(h_2)$} (E''');
-%\end{tikzpicture}
-%\]
-%These two 2-morphisms $\tau_\alpha$ and $\tau_\beta$ are two 2-morphisms in the monoidal 2-category $(\Cat,\times,1)$ and so we can tensor them which results in:
-%Returning to the interchange law, composing the two horizontal compositions above vertically then results in:
-%\[
-%\begin{tikzpicture}[scale=1.5]
-%\node (A) at (0,0.5) {$a$};
-%\node (A') at (0,-0.5) {$a''$};
-%\node (B) at (2,0.5) {$m+_{b} n$};
-%\node (C) at (4,0.5) {$c$};
-%\node (C') at (4,-0.5) {$c''$};
-%\node (D) at (2,-0.5) {$m'' +_{b''} n''$};
-%\node (E) at (5.5,0.5) {$x \odot y \in F(m+_{b} n)$};
-%\node (F) at (5.5,-0.5) {$x'' \odot y'' \in F(m'' +_{b''} n'')$};
-%\node (G) at (2,-1) {$\tau_{(a' \odot \beta')(\alpha \odot \beta)} \maps F((h_1' +_{g'} h_2')(h_1 +_g h_2))(x \odot y) \to x'' \odot y''.$};
-%\path[->,font=\scriptsize,>=angle 90]
-%(A) edge node[above]{$j \psi_{m} i_1$} (B)
-%(C) edge node[above]{$j \psi_{n} o_2$} (B)
-%(A) edge node[left]{$f' f$} (A')
-%(C) edge node[right]{$k' k$} (C')
-%(A') edge node [above]{$j \psi_{m''} i_1''$} (D)
-%(C') edge node [above]{$j \psi_{n''} o_2''$} (D)
-%(B) edge node [left] {$(h_1' +_{g'} h_2')(h_1 +_g h_2)$} (D);
-%\end{tikzpicture}
-%\]
-%The vertical composite of two morphisms of decorations is straightforward. On the other hand, if we first compose vertically we obtain:
-%\[
-%\begin{tikzpicture}[scale=1.5]
-%\node (A) at (0,0.5) {$a$};
-%\node (A') at (0,-0.5) {$a''$};
-%\node (B) at (1,0.5) {$m$};
-%\node (C) at (2,0.5) {$b$};
-%\node (C') at (2,-0.5) {$b''$};
-%\node (D) at (1,-0.5) {$m''$};
-%\node (E) at (3,0.5) {$x \in F(m)$};
-%\node (F) at (3,-0.5) {$x'' \in F(m'')$};
-%\node (G) at (4,0.5) {$b$};
-%\node (H) at (5,0.5) {$n$};
-%\node (I) at (6,0.5) {$c$};
-%\node (G') at (4,-0.5) {$b''$};
-%\node (H') at (5,-0.5) {$n''$};
-%\node (I') at (6,-0.5) {$c''$};
-%\node (J) at (7,0.5) {$y \in F(n)$};
-%\node (K) at (7,-0.5) {$y'' \in F(n'')$};
-%\node (L) at (1,-1) {$\tau_{\alpha' \alpha} \maps F(h_1' h_1)(x) \to x''$};
-%\node (M) at (5,-1) {$\tau_{\beta' \beta} \maps F(h_2' h_2)(y) \to y''$};
-%\path[->,font=\scriptsize,>=angle 90]
-%(A) edge node[above]{$i_1$} (B)
-%(C) edge node[above]{$o_1$} (B)
-%(A) edge node[left]{$f' f$} (A')
-%(C) edge node[right]{$g' g$} (C')
-%(A') edge node[above] {$i_1''$} (D)
-%(C') edge node[above] {$o_1''$} (D)
-%(B) edge node [left] {$h_1' h_1$} (D)
-%(G) edge node [above] {$i_2$} (H)
-%(G) edge node [left] {$g' g$} (G')
-%(H) edge node [left] {$h_2' h_2$} (H')
-%(G') edge node [above] {$i_2''$} (H')
-%(I) edge node [above] {$o_2$} (H)
-%(I) edge node [right] {$k' k$} (I')
-%(I') edge node [above] {$o_2''$} (H');
-%\end{tikzpicture}
-%\]
-%and then composing horizontally results in:
-%\[
-%\begin{tikzpicture}[scale=1.5]
-%\node (A) at (0,0.5) {$a$};
-%\node (A') at (0,-0.5) {$a''$};
-%\node (B) at (2,0.5) {$m+_{b} n$};
-%\node (C) at (4,0.5) {$c$};
-%\node (C') at (4,-0.5) {$c''$};
-%\node (D) at (2,-0.5) {$m'' +_{b''} n''$};
-%\node (E) at (5.5,0.5) {$x \odot y \in F(m+_{b} n)$};
-%\node (F) at (5.5,-0.5) {$x'' \odot y'' \in F(m'' +_{b''} n'')$};
-%\node (G) at (2,-1) {$\tau_{(\alpha' \alpha) \odot (\beta' \beta)} \maps F((h_1' h_1)+_{g' g} (h_2' h_2))(x \odot y) \to x'' \odot y''.$};
-%\path[->,font=\scriptsize,>=angle 90]
-%(A) edge node[above]{$j \psi_{m} i_1$} (B)
-%(C) edge node[above]{$j \psi_{n} o_2$} (B)
-%(A) edge node[left]{$f' f$} (A')
-%(C) edge node[right]{$k' k$} (C')
-%(A') edge node [above]{$j \psi_{m''} i_1''$} (D)
-%(C') edge node [above]{$j \psi_{n''} o_2''$} (D)
-%(B) edge node [left] {$(h_1' h_1) +_{g' g} (h_2' h_2)$} (D);
-%\end{tikzpicture}
-%\]
-%The decorations of 
-%\[
-%\begin{tikzpicture}[scale=1.5]
-%\node (A) at (0,0) {$1$};
-%\node (B) at (2,0) {$F(c) \times F(e)$};
-%\node (C) at (4,0) {$F(c+e)$};
-%\node (D) at (4,-1) {$F(c+_b e)$};
-%\node (E) at (4,-2) {$F(c'' +_{b''} e'')$};
-%\node (F) at (0,-1) {$F(c) \times F(e)$};
-%\node (G) at (0,-2) {$F(c'') \times F(e'')$};
-%\node (H) at (2,-2) {$F(c'' + e'')$};
-%\path[->,font=\scriptsize,>=angle 90]
-%(A) edge node [above]{$d_1 \times d_2$} (B)
-%(B) edge node [above] {$\phi_{c,e}$} (C)
-%(C) edge node [right]{$F(j_{c,e})$} (D)
-%(D) edge node [right] {$F((h_1' +_{g'} h_2')(h_1 +_g h_2))$} (E)
-%(A) edge node [left] {$d_1 \times d_2$} (F)
-%(F) edge node [left] {$F((h_1' h_1) \times (h_2' h_2))$} (G)
-%(G) edge node [above] {$\phi_{c'',e''}$} (H)
-%(H) edge node [above] {$F(j_{c'',e''})$} (E);
-%\end{tikzpicture}
-%\]
-%As is usual concerning the interchange law of double categories of this nature, only the `interior' of the two composites appears different, but the two morphisms $(h_1' +_{g'} h_2')(h_1 +_g h_2) \maps m+_{b} n \to m'' +_{b''} n''$ and $(h_1' h_1) +_{g' g} (h_2' h_2) \maps m+_{b} n \to m'' +_{b''}n''$ are the same universal map realized in two different ways.
-The two morphisms of decorations $\tau_{(\alpha' \odot \beta')(\alpha \odot \beta)}$ and $\tau_{(\alpha' \alpha) \odot (\beta' \beta)}$ are obtained as two different compositions of four 2-morphisms in $\Cat$, namely horizontally then vertically and vertically then horizontally.
-As $\Cat$ is a 2-category, the interchange law for these 2-morphisms already holds, and as a result, the morphisms $$\tau_{(\alpha' \odot \beta')(\alpha \odot \beta)} \maps F((h_1' +_{g'} h_2')(h_1 +_g h_2))(x \odot y) \to x'' \odot y''$$ and $$\tau_{(\alpha' \alpha)\odot(\beta' \beta)} \maps F((h_1' h_1)+_{g' g} (h_2' h_2))(x \odot y) \to x'' \odot y''$$ are also the same.
-Thus the interchange law for 2-morphisms holds and $F\mathbb{C}$sp is a double category.
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$$} (B)
+(C) edge node[above]{$$} (B);
+\end{tikzpicture}
+\]
+as well as the decoration $(x_1 \odot x_2) \odot x_3$ on the apex obtained as explained above.
+Explicitly, the decoration $(x_1 \odot x_2) \odot x_3) \in F((m_1+_b m_2) +_c m_3)$ is obtained as the composite $$ (x_1 \odot x_2) \odot x_3 \mapseqq 1 \xrightarrow{\zeta_1} F(m_1+_{b} m_2) \times F(m_3) \xrightarrow{\phi_{m_1+_{b} m_2, m_3}} F((m_1+_{b}m_2) +m_3) \xrightarrow{F(\psi)} F((m_1+_{b} m_2)+_{c} m_3)$$where$$\scriptstyle{\zeta_1 \mapseqq 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{x_1 \times x_2} F(m_1) \times F(m_2) \xrightarrow{\phi_{m_1,m_2}} F(m_1+m_2) \xrightarrow{F(j)} F(m_1+_b m_2) \xrightarrow {\rho^{-1}} F(m_1+_b m_2) \times 1 \xrightarrow{1 \times x_3} F(m_1+_b m_2) \times F(m_3).}$$
+The composite $M_1 \odot (M_2 \odot M_3)$ is obtained similarly:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$a$};
+\node (B) at (2,0) {$m_1 +_b (m_2 +_c m_3)$};
+\node (C) at (4,0) {$d$};
+%\node (D) at (3,0) {$x \in F(m)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$$} (B)
+(C) edge node[above]{$$} (B);
+\end{tikzpicture}
+\]
+as well as the decoration $x_1 \odot (x_2 \odot x_3)$ on the apex:
+$$x_1 \odot (x_2 \odot x_3) \mapseqq 1 \xrightarrow{\zeta_2} F(m_1) \times F(m_2 +_c m_3) \xrightarrow{\phi_{m_1, m_2 +_c m_3}} F(m_1+(m_2 +_c +m_3)) \xrightarrow{F(\psi)} F(m_1+_{b} (m_2+_{c} m_3))$$with $\zeta_2$ being similar to $\zeta_1$ above.
+The associator $\alpha$ is then given by the map of $F$-decorated cospans given by the map of cospans
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0.5) {$a$};
+\node (A') at (0,-0.5) {$a$};
+\node (B) at (1.5,0.5) {$(m_1+_{b} m_2)+_{c} m_3$};
+\node (C) at (3,0.5) {$d$};
+\node (C') at (3,-0.5) {$d$};
+\node (D) at (1.5,-0.5) {$m_1+_{b}(m_2 +_{c} m_3)$};
+\node (E) at (5.5,0.5) {$(x_1 \odot x_2) \odot x_3 \in F((m_1+_{b} m_2)+_{c} m_3)$};
+\node (F) at (5.5,-0.5) {$x_1 \odot (x_2 \odot x_3) \in F(m_1+_{b} (m_2 +_{c} m_3))$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$$} (B)
+(C) edge node[above]{$$} (B)
+(A) edge node[left]{$\id_a$} (A')
+(C) edge node[right]{$\id_d$} (C')
+(A') edge node {$$} (D)
+(C') edge node {$$} (D)
+(B) edge node [left] {$\alpha$} (D);
+\end{tikzpicture}
+\]
+together with the decoration morphism $\tau_\alpha \colon F(\alpha)((x_1 \odot x_2) \odot x_3) \to (x_1 \odot (x_2 \odot x_3))$ that is obtained by pasting various commutative squares together, as we did for a horizontal composite above.
+The associator $\alpha$ will then satisfy the pentagon identity:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (-0.5,0) {$((M_1 \odot M_2) \odot M_3) \odot M_4$};
+\node (B) at (3,1.05) {$(M_1 \odot (M_2 \odot M_3)) \odot M_4$};
+\node (C) at (6.5,0) {$M_1 \odot ((M_2 \odot M_3) \odot M_4)$};
+\node (D) at (1.5,-1.05) {$(M_1 \odot M_2) \odot (M_3 \odot M_4)$};
+\node (E) at (4.5,-1.05) {$M_1 \odot (M_2 \odot (M_3 \odot M_4))$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node [above] {$\alpha \times 1$}(B)
+(B) edge node [above] {$\alpha$}(C)
+(A) edge node [below] {$\alpha$}(D)
+(D) edge node [above] {$\alpha$}(E)
+(C) edge node [below] {$1 \times \alpha$}(E);
+\end{tikzpicture}
+\]
+which we may realize in two stages.
+First, for the underlying pentagon of maps of cospans in $\A$ commuting due to the fact that $\lCsp(\A)$ is a double category with its own associator that satisfies the pentagon identity, and second, for the pentagon of morphisms of decorations due to the pasting of various commutative squares in $\Cat$.
+
+We next construct the left unitor. Given a horizontal 1-cell $M$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$a$};
+\node (B) at (1,0) {$m$};
+\node (C) at (2,0) {$b$};
+\node (D) at (3,0) {$x \in F(m)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i$} (B)
+(C) edge node[above]{$o$} (B);
+\end{tikzpicture}
+\]
+the left unitor will be a globular 2-morphism $\lambda \colon 1_a \odot M \to M$, where the identity horizontal 1-cell on the object $a$ will once again make use of the trivial decoration on an object introduced earlier.
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$a$};
+\node (B) at (1,0) {$a$};
+\node (C) at (2,0) {$a$};
+\node (D) at (3,0) {$\bot_a \in F(a)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$\id_a$} (B)
+(C) edge node[above]{$\id_a$} (B);
+\end{tikzpicture}
+\]
+To compose $1_a$ and $M$, we first compose the two cospans in $\A$ by pushing out over their shared object $a$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$a$};
+\node (B) at (1,1) {$a$};
+\node (C) at (2,0) {$a$};
+\node (D) at (3,1) {$m$};
+\node (E) at (4,0) {$b$};
+\node (F) at (2,2) {$a+m$};
+\node (G) at (2,3) {$a+_{a} m$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$\id_a$} (B)
+(C) edge node[above]{$\id_a$} (B)
+(C) edge node [above] {$i$} (D)
+(E) edge node [above] {$o$} (D)
+(B) edge node [above] {$j_a$} (F)
+(D) edge node [above] {$j_m$} (F)
+(F) edge node [left] {$\psi$} (G)
+(A) edge[bend left] node [left] {$\psi j_a$} (G)
+(E) edge[bend right] node [right] {$\psi j_{m} o$} (G);
+\end{tikzpicture}
+\]
+The composite decoration $\bot_a \odot x$ will be given by the composite
+$$1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{\bot_a \times x} F(a) \times F(m) \xrightarrow{\phi_{a,m}} F(a+m) \xrightarrow{F(\psi)} F(a+_{a} m).$$
+The left unitor is then the map of $F$-decorated cospans determined by the following map of cospans in $\A$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0.5) {$a$};
+\node (A') at (0,-0.5) {$a$};
+\node (B) at (1.5,0.5) {$a+_{a} m$};
+\node (C) at (3,0.5) {$b$};
+\node (C') at (3,-0.5) {$b$};
+\node (D) at (1.5,-0.5) {$m$};
+\node (E) at (4.5,0.5) {$\bot_a \odot x \in F(a+_{a} m)$};
+\node (F) at (4.5,-0.5) {$x \in F(m)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$\psi j_a$} (B)
+(C) edge node[above]{$\psi j_m o$} (B)
+(A) edge node[left]{$\id_{a}$} (A')
+(C) edge node[right]{$\id_{b}$} (C')
+(A') edge node [above]{$i$} (D)
+(C') edge node [above]{$o$} (D)
+(B) edge node [left] {$\ell$} (D);
+\end{tikzpicture}
+\]
+together with the decoration morphism $\tau_\lambda \colon F(\ell)(\bot_a \odot x) \to x$; note, that $\ell \colon a+_a m \to m$ is a canonical isomorphism as both $a+_a m$ and $m$ are colimits of the span $a \xleftarrow{\id_a} a \xrightarrow{i} m$.
+The right unitor $\rho$ is similar, the two unitality squares are similar to the associator shown above, and it is clear that the source and target functors applied to the associator and left and right unitors yield identities.
+
+The final property that we will check is the interchange law for 2-morphisms. Suppose that we have four 2-morphisms $\alpha, \beta, \alpha'$ and $\beta'$ as shown below:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0.5) {$a$};
+\node (A') at (0,-0.5) {$a'$};
+\node (B) at (1,0.5) {$m$};
+\node (C) at (2,0.5) {$b$};
+\node (C') at (2,-0.5) {$b'$};
+\node (D) at (1,-0.5) {$m'$};
+\node (E) at (3,0.5) {$x \in F(m)$};
+\node (F) at (3,-0.5) {$x' \in F(m')$};
+\node (G) at (4,0.5) {$b$};
+\node (H) at (5,0.5) {$n$};
+\node (I) at (6,0.5) {$c$};
+\node (G') at (4,-0.5) {$b'$};
+\node (H') at (5,-0.5) {$n'$};
+\node (I') at (6,-0.5) {$c'$};
+\node (J) at (7,0.5) {$y \in F(n)$};
+\node (K) at (7,-0.5) {$y' \in F(n')$};
+\node (L) at (1,-1) {$\tau_\alpha \maps F(h_1)(x) \to x'$};
+\node (M) at (5,-1) {$\tau_\beta \maps F(h_2)(y) \to y'$};
+\node (A'') at (0,-1.5) {$a'$};
+\node (A''') at (0,-2.5) {$a''$};
+\node (B'') at (1,-1.5) {$m'$};
+\node (C'') at (2,-1.5) {$b'$};
+\node (C''') at (2,-2.5) {$b''$};
+\node (D'') at (1,-2.5) {$m''$};
+\node (E'') at (3,-1.5) {$x' \in F(m')$};
+\node (F'') at (3,-2.5) {$x'' \in F(m'')$};
+\node (G'') at (4,-1.5) {$b'$};
+\node (H'') at (5,-1.5) {$n'$};
+\node (I'') at (6,-1.5) {$c'$};
+\node (G''') at (4,-2.5) {$b''$};
+\node (H''') at (5,-2.5) {$n''$};
+\node (I''') at (6,-2.5) {$c''$};
+\node (J'') at (7,-1.5) {$y' \in F(n')$};
+\node (K'') at (7,-2.5) {$y'' \in F(n'')$};
+\node (L'') at (1,-3) {$\tau_{\alpha'} \maps F(h_1')(x') \to x''$};
+\node (M'') at (5,-3) {$\tau_{\beta'} \maps F(h_2')(y') \to y''$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i_1$} (B)
+(C) edge node[above]{$o_1$} (B)
+(A) edge node[left]{$f$} (A')
+(C) edge node[right]{$g$} (C')
+(A') edge node[above] {$i_1'$} (D)
+(C') edge node[above] {$o_1'$} (D)
+(B) edge node [left] {$h_1$} (D)
+(G) edge node [above] {$i_2$} (H)
+(G) edge node [left] {$g$} (G')
+(H) edge node [left] {$h_2$} (H')
+(G') edge node [above] {$i_2'$} (H')
+(I) edge node [above] {$o_2$} (H)
+(I) edge node [right] {$k$} (I')
+(I') edge node [above] {$o_2'$} (H')
+(A'') edge node[above]{$i_1'$} (B'')
+(C'') edge node[above]{$o_1'$} (B'')
+(A'') edge node[left]{$f'$} (A''')
+(C'') edge node[right]{$g'$} (C''')
+(A''') edge node[above] {$i_1''$} (D'')
+(C''') edge node[above] {$o_1''$} (D'')
+(B'') edge node [left] {$h_1'$} (D'')
+(G'') edge node [above] {$i_2'$} (H'')
+(G'') edge node [left] {$g'$} (G''')
+(H'') edge node [left] {$h_2'$} (H''')
+(G''') edge node [above] {$i_2''$} (H''')
+(I'') edge node [above] {$o_2'$} (H'')
+(I'') edge node [right] {$k'$} (I''')
+(I''') edge node [above] {$o_2''$} (H''');
+\end{tikzpicture}
+\]
+We may compose these first vertically and then horizontally, or first horizontally and then vertically, and we must show that these two ways of composing yield the same result.
+Composing first vertically and then horizontally results in:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0.5) {$a$};
+\node (A') at (0,-0.5) {$a''$};
+\node (B) at (2,0.5) {$m+_{b} n$};
+\node (C) at (4,0.5) {$c$};
+\node (C') at (4,-0.5) {$c''$};
+\node (D) at (2,-0.5) {$m'' +_{b''} n''$};
+\node (E) at (5.5,0.5) {$x \odot y \in F(m+_{b} n)$};
+\node (F) at (5.5,-0.5) {$x'' \odot y'' \in F(m'' +_{b''} n'')$};
+\node (G) at (2,-1) {$\tau_{(\alpha' \alpha) \odot (\beta' \beta)} \maps F((h_1' h_1)+_{g' g} (h_2' h_2))(x \odot y) \to x'' \odot y''$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$ \psi j_m i_1$} (B)
+(C) edge node[above]{$ \psi j_n o_2$} (B)
+(A) edge node[left]{$f' f$} (A')
+(C) edge node[right]{$k' k$} (C')
+(A') edge node [above]{$\psi j_{m''} i_1''$} (D)
+(C') edge node [above]{$\psi j_{n''} o_2''$} (D)
+(B) edge node [left] {$(h_1' h_1) +_{g' g} (h_2' h_2)$} (D);
+\end{tikzpicture}
+\]
+whereas first composing horizontally and then vertically results in:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0.5) {$a$};
+\node (A') at (0,-0.5) {$a''$};
+\node (B) at (2,0.5) {$m+_{b} n$};
+\node (C) at (4,0.5) {$c$};
+\node (C') at (4,-0.5) {$c''$};
+\node (D) at (2,-0.5) {$m'' +_{b''} n''$};
+\node (E) at (5.5,0.5) {$x \odot y \in F(m+_{b} n)$};
+\node (F) at (5.5,-0.5) {$x'' \odot y'' \in F(m'' +_{b''} n'')$};
+\node (G) at (2,-1) {$\tau_{(a' \odot \beta')(\alpha \odot \beta)} \maps F((h_1' +_{g'} h_2')(h_1 +_g h_2))(x \odot y) \to x'' \odot y''.$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$\psi j_{m} i_1$} (B)
+(C) edge node[above]{$\psi j_{n} o_2$} (B)
+(A) edge node[left]{$f' f$} (A')
+(C) edge node[right]{$k' k$} (C')
+(A') edge node [above]{$\psi j_{m''} i_1''$} (D)
+(C') edge node [above]{$\psi j_{n''} o_2''$} (D)
+(B) edge node [left] {$(h_1' +_{g'} h_2')(h_1 +_g h_2)$} (D);
+\end{tikzpicture}
+\]
+Everything about these two composites appears identical except for the two middle morphisms and the two morphisms of decorations.
+However, the two maps $(h_1' h_1) +_{g' g} (h_2' h_2) \maps m+_{b} n \to m'' +_{b''}n''$ and $(h_1' +_{g'} h_2')(h_1 +_g h_2) \maps m+_{b} n \to m'' +_{b''} n''$ are the same universal map realized in two different ways.
+The two morphisms of decorations $\tau_{(\alpha' \odot \beta')(\alpha \odot \beta)}$ and $\tau_{(\alpha' \alpha) \odot (\beta' \beta)}$ are also the same as they are obtained as two different compositions of four 2-morphisms in $\Cat$, namely first vertically and then horizontally and first horizontally and then vertically.
+The interchange law for $\Cat$ says that these two composites must be the same as well, and thus the interchange law for our double category $F\lCsp$ is also satisfied.
+\end{comment}
 \end{proof}

### 2020-11-23 cospans.tex
finished new suggested 2.1

@@
 \begin{proof}
-According to \cref{defn:double_category}, we will define the category of objects $F\lCsp_0$, the category of arrows $F\lCsp_1$, as well as the four structure functors which tie them together: the source and target functors $S,T \colon F\lCsp_1 \to F\lCsp_0$, the composition functor
-$\odot \colon F\lCsp_1 \times_{F\lCsp_0} F\lCsp_1 \to F\lCsp_1$ and the unit functor $U \colon F\lCsp_0 \to F\lCsp_1$.
+According to \cref{defn:double_category}, for a lax monoidal pseudofunctor $(F,\phi,\phi_0)$ we will define the category of objects $F\lCsp_0$, the category of arrows $F\lCsp_1$, as well as the four structure functors which tie them together: the source and target functors $S,T \colon F\lCsp_1 \to F\lCsp_0$, the composition functor $\odot \colon F\lCsp_1 \times_{F\lCsp_0} F\lCsp_1 \to F\lCsp_1$ and the unit functor $U \colon F\lCsp_0 \to F\lCsp_1$.
 
 The category of objects $F\lCsp_0$ is simply the category $\A$, whereas $F$-decorated cospans and maps between them form the category of arrows $F\lCsp_1$.
-For example, the (vertical) composition of two $F$-decorated cospans maps is
+The (vertical) composition of two $F$-decorated cospans maps is
 \begin{displaymath}
  \begin{tikzcd}
-a\ar[r,"i"]\ar[d,"f"'] & m\ar[d,"h"] & b\ar[l,"o"]\ar[d,"g"]  & x\in F(m) \\
+a\ar[r,"i"]\ar[d,"f"'] & m\ar[d,"h"] & b\ar[l,"o"']\ar[d,"g"]  & x\in F(m) \\
 a'\ar[r,"{i'}"]\ar[d,"{f'}"] & m'\ar[d,"{h'}"] & b'\ar[l,"{o'}"']\ar[d,"{g'}"] & x'\in F(m') \\
-a''\ar[r,"{i''}"'] & m'' & b''\ar[l,"{o''}"'] & x''\in F(m'')
+a''\ar[r,"{i''}"] & m'' & b''\ar[l,"{o''}"'] & x''\in F(m'')
  \end{tikzcd}\;=\;
  \begin{tikzcd}[column sep=.4in]
-a\ar[r,"i"]\ar[dd,"{f'f}"'] & m\ar[dd,"{h'h}"] & b\ar[l,"o"]\ar[dd,"{g'g}"]  & x\in F(m) \\
+a\ar[r,"i"]\ar[dd,"{f'f}"'] & m\ar[dd,"{h'h}"] & b\ar[l,"o"']\ar[dd,"{g'g}"]  & x\in F(m) \\
 \hole \\
@@
 \end{displaymath}
-where if $\tau \colon F(h)(x) \to x'$ and $\tau' \colon F(h')(x') \to x''$ are the decoration morphisms, $\tau' F(\tau) \colon F(h'h)(x) \to x''$ is the composite one.
+where if $\tau \colon F(h)(x) \to x'$ and $\tau' \colon F(h')(x') \to x''$ are the decoration morphisms, 
+$$F(h'h)(x)\cong F(h')F(h)(x)\xrightarrow{F(h')(\tau)}F(h')(x')\xrightarrow{\tau'}x''$$ is the composite one.
 The source and target functors map an $F$-decorated cospan to the source and target of the cospan and a map of decorated cospans \cref{eq:mapofdec} to $f$ and $g$ respectively.
-
-The unit functor $U \maps F\lCsp_0 \to F\lCsp_1$ is defined on objects as: 
+The unit functor maps an object $a$ to
 \begin{equation}\label{eq:UFCsp}
-\begin{tikzpicture}[scale=1.5]
-\node (E) at (-1,0) {$a$};
-\node (F) at (-.5,0) {$\mapsto$};
-\node (A) at (0,0) {$a$};
-\node (B) at (1,0) {$a$};
-\node (C) at (2,0) {$a$};
-\node (D) at (3,0) {$\bot_a \in F(a)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$1$} (B)
-(C) edge node[above]{$1$} (B);
-\end{tikzpicture}
+\begin{tikzcd}
+a\ar[r,"1_a"] & a & a,\ar[l,"1_a"'] & \bot_a:=1\xrightarrow{\phi_0}F(0)\xrightarrow{F(!_a)}F(a)
+\end{tikzcd}
 \end{equation}
-where $\bot_a \in F(a)$ is the \define{trivial decoration} on $a$ given by the composite of the unique map $F(!) \maps F(0) \to F(a)$ and the morphism $\phi \maps 1 \to F(0)$  which comes from $F \maps \A \to \Cat$ being lax monoidal.
-For morphisms, the functor $U$ is defined as:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (G) at (-1,0.5) {$a$};
-\node (G') at (-1,-0.5) {$a'$};
+where $\bot_a \in F(a)$ is called the \define{trivial decoration}, and a vertical 1-morphism $f\maps a\to a'$ to
+\[
+\begin{tikzpicture}[scale=1.5]
 \node (A) at (0,0.5) {$a$};
@@
 \node (F) at (3,-0.5) {$\bot_{a'} \in F(a')$};
-\node (H) at (-0.5,0) {$\mapsto$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$1$} (B)
-(C) edge node[above]{$1$} (B)
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$1_a$} (B)
+(C) edge node[above]{$1_a$} (B)
 (A) edge node[left]{$f$} (A')
 (C) edge node[right]{$f$} (C')
-(A') edge node[above] {$1$} (D)
-(C') edge node[above] {$1$} (D)
-(B) edge node [left] {$f$} (D)
-(G) edge node [left] {$f$} (G');
-\end{tikzpicture}
-\]
-together with the morphism $\tau_{\bot_f} = F(f) F(!) \phi \maps 1 \to F(a')$.
-
-Next we define the composite functor $\odot \colon F\lCsp_1 \times_{F\lCsp_0} F\lCsp_1 \to F\lCsp_1$, which amounts to defining how we compose two composable $F$-decorated cospans or horizontally compose two maps of $F$-decorated cospans with a common source and target.
-Given two composable $F$-decorated cospans which we respectively denote by $M$ and $N$, the capitals of their apices:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a$};
-\node (B) at (1,0) {$m$};
-\node (C) at (2,0) {$b$};
-\node (D) at (1,-0.5) {$x \in F(m)$};
-\node (E) at (3,0) {$b$};
-\node (F) at (4,0) {$n$};
-\node (G) at (5,0) {$c$};
-\node (H) at (4,-0.5) {$y \in F(n)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i$} (B)
-(C) edge node[above]{$o$} (B)
-(E) edge node[above]{$i'$} (F)
-(G) edge node[above]{$o'$} (F);
-\end{tikzpicture}
-\]
-the composite $M \odot N$ is given by taking the pushout of the two cospans in $\A$ over the shared foot which is the object $b$:
+(A') edge node[above] {$1_{a'}$} (D)
+(C') edge node[above] {$1_{a'}$} (D)
+(B) edge node [left] {$f$} (D);
+\end{tikzpicture}
+\]
+together with the decoration morphism $F(f)F(!_a)\phi_0(*)\cong F(!_{a'})\phi_0(*)$.
+%%% Christina: the previous formula $\tau_{\bot_f} = F(f) F(!) \phi \maps 1 \to F(a')$ doesn't typecheck to me.
+Finally, the (horizontal) composition functor $\odot$ maps two composable $F$-decorated cospans $\left(a\to m\leftarrow b,x\in F(m)\right)$ and $\left(b\to n\leftarrow c,y\in F(n)\right)$ to their pushout in $\A$ over their shared foot
 \begin{equation}\label{eq:dcospanscomposition}
-\begin{tikzpicture}[scale=1.5]
+\begin{tikzpicture}
 \node (A) at (0,0) {$a$};
@@
 (F) edge node [left] {$\psi$} (G)
-(A) edge[bend left] node [left] {$\psi j_m i$} (G)
-(E) edge[bend right] node [right] {$\psi j_{n}' o'$} (G);
+(A) edge[dashed,bend left] node [left] {} (G)
+(E) edge[dashed,bend right] node [right] {} (G);
 \end{tikzpicture}
 \end{equation}
-The composite decoration $x \odot y$ on the apex $m+_b n$ is given by:
-$$x \odot y = 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{x \times y} F(m) \times F(n) \xrightarrow{\phi_{m,n}} F(m+n) \xrightarrow{F(\psi)} F(m+_{b}n)$$
-where $\psi \maps m + n \to m+_{b} n$ is the natural map from the coproduct to the pushout and $\phi_{m,n} \maps F(m) \times F(n) \to F(m+n)$ is the natural transformation coming from the structure of the lax monoidal pseudofunctor $F \maps \A \to \Cat$.
-Given two horizontally composable maps of $F$-decorated cospans which we respectively denote by $\alpha$ and $\beta$:
+with decoration
+$$x\odot y:= 1\cong1 \times 1 \xrightarrow{x \times y} F(m) \times F(n) \xrightarrow{\phi_{m,n}} F(m+n) \xrightarrow{F(\psi)} F(m+_{b}n)$$
+where $\psi \maps m + n \to m+_{b} n$ is the natural map from the coproduct to the pushout and $\phi_{m,n} \maps F(m) \times F(n) \to F(m+n)$ are the lax monoidal structure maps of $F$.
+Moreover, given two horizontally composable maps of $F$-decorated cospans $\alpha$ and $\beta$
 \[
@@
 \]
-their horizontal composite $\alpha \odot \beta$ is the pair given by first horizontally composing the two maps of cospans in $\A$:
+their composite $\alpha \odot \beta$ is horizontal cospan composition in $\A$
 \[
@@
 \path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$\psi j_m i_1$} (B)
-(C) edge node[above]{$\psi j_n o_2$} (B)
+(A) edge node[above]{} (B)
+(C) edge node[above]{} (B)
 (A) edge node[left]{$f$} (A')
 (C) edge node[right]{$k$} (C')
-(A') edge node [above]{$\psi j_{m'} i_1'$} (D)
-(C') edge node [above]{$\psi j_{n'} o_2'$} (D)
+(A') edge node [above]{} (D)
+(C') edge node [above]{} (D)
 (B) edge node [left] {$h_1 +_g h_2$} (D);
@@
 \]
-together with the decoration morphism $\tau_{\alpha \odot \beta} \colon F(h_1 +_g h_2)(x \odot y) \to (x' \odot y')$ given by the following commutative diagram:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (4.75,0) {$\tau_\alpha \times \tau_\beta \Swarrow$};
-\node (D) at (3,0) {$1 \xrightarrow{\lambda^{-1}} 1 \times 1$};
+together with the decoration morphism $\tau_{\alpha \odot \beta} \colon F(h_1 +_g h_2)(x \odot y) \to (x' \odot y')$ given by the diagram:
+\[
+\begin{tikzpicture}[scale=1.7]
+\node (A) at (4.75,0) {$\scriptstyle\Downarrow \tau_\alpha \times \tau_\beta$};
+\node (D) at (3,0) {$1 \cong 1 \times 1$};
 \node (E) at (5.5,0.5) {$F(m) \times F(n)$};
+\node () at (6.5,0) {$\cong$};
+\node () at (8.5,0) {$\cong$};
 \node (E') at (5.5,-0.5) {$F(m') \times F(n')$};
@@
 \node (B') at (7.5,-0.5) {$F(m' + n')$};
-\node (C) at (9.25,0.5) {$F(m+_{b} n)$};
-\node (C') at (9.25,-0.5) {$F(m' +_{b'} n')$};
+\node (C) at (9.5,0.5) {$F(m+_{b} n)$};
+\node (C') at (9.5,-0.5) {$F(m' +_{b'} n')$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (B') edge node [above] {$F(\psi)$} (C')
-(C) edge node [right] {$F(h_1 +_g h_2)$} (C')
-(B) edge node [right] {$F(h_1 + h_2)$} (B')
+(C) edge node  [fill=white] {$F(h_1 +_g h_2)$} (C')
+(B) edge node [fill=white] {$F(h_1 + h_2)$} (B')
 (D) edge node [above] {$x \times y$} (E)
 (D) edge node [below] {$x' \times y'$} (E')
-(E) edge node [right] {$F(h_1) \times F(h_2)$} (E');
-\end{tikzpicture}
-\]
-The middle square commutes since $F$ is a lax monoidal pseudofunctor and the right square commutes as the underlying square commutes.
-The decorations $x \odot y$ and $x' \odot y'$ are given respectively by the top and bottom composite of arrows and the decoration morphism $\tau_{\alpha \odot \beta}$ is given by composing $\tau_\alpha \times \tau_\beta$ with the two commuting squares.
-It is clear that the equations $S(M \odot N)=S(M)$ and $T(M \odot N)=T(N)$ hold, and this finishes defining the four structure functors $U,S,T$ and $\odot$.
-
-Lastly, our double category is required to have an associator $\alpha$ and left and right unitors $\lambda$ and $\rho$ which are natural isomorphisms governing the composition of horizontal 1-cells that are required to satisfy the standard coherence axioms for a monoidal category, as well as $S(\alpha),S(\lambda),S(\rho),T(\alpha),T(\lambda)$ and $T(\rho)$ all being identities.
-We will only show the associator $\alpha$, left unitor $\lambda$ and the pentagon identity, as the remaining details will be similar to these.
-
-First we will build the associator $\alpha \colon \odot (\odot \times 1) \Rightarrow \odot (1 \times \odot)$, which will be a globular 2-morphism; in other words, a map of $F$-decorated cospans with identities on the sides.
-Given three composable horizontal 1-cells $M_1, M_2$ and $M_3$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a$};
+(E) edge node [fill=white] {$F(h_1) \times F(h_2)$} (E');
+\end{tikzpicture}
+\]
+where the middle isomorphism is due to pseudonaturality of $\phi$ and the right-hand side isomorphism is due to pseudofunctoriality of $F$.
+
+The associator $\alpha \colon \odot (\odot \times 1) \Rightarrow \odot (1 \times \odot)$ is formed as follows: for three composable horizontal 1-cells
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$M_1=a$};
 \node (B) at (1,0) {$m_1$};
@@
 \node (D) at (1,-0.5) {$x_1 \in F(m_1)$};
-\node (E) at (3,0) {$b$};
+\node (E) at (3,0) {$M_2=b$};
 \node (F) at (4,0) {$m_2$};
@@
 \node (H) at (4,-0.5) {$x_2 \in F(m_2)$};
-\node (I) at (6,0) {$c$};
+\node (I) at (6,0) {$M_3=c$};
 \node (J) at (7,0) {$m_3$};
@@
 \]
-we first compute $(M_1 \odot M_2) \odot M_3)$ by pushing out the first two cospans followed by the third:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a$};
-\node (B) at (2,0) {$(m_1 +_b m_2) +_c m_3$};
-\node (C) at (4,0) {$d$};
-%\node (D) at (3,0) {$x \in F(m)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$$} (B)
-(C) edge node[above]{$$} (B);
-\end{tikzpicture}
-\]
-as well as the decoration $(x_1 \odot x_2) \odot x_3$ on the apex obtained as explained above.
-Explicitly, the decoration $(x_1 \odot x_2) \odot x_3) \in F((m_1+_b m_2) +_c m_3)$ is obtained as the composite $$ (x_1 \odot x_2) \odot x_3 \mapseqq 1 \xrightarrow{\zeta_1} F(m_1+_{b} m_2) \times F(m_3) \xrightarrow{\phi_{m_1+_{b} m_2, m_3}} F((m_1+_{b}m_2) +m_3) \xrightarrow{F(\psi)} F((m_1+_{b} m_2)+_{c} m_3)$$where$$\scriptstyle{\zeta_1 \mapseqq 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{x_1 \times x_2} F(m_1) \times F(m_2) \xrightarrow{\phi_{m_1,m_2}} F(m_1+m_2) \xrightarrow{F(j)} F(m_1+_b m_2) \xrightarrow {\rho^{-1}} F(m_1+_b m_2) \times 1 \xrightarrow{1 \times x_3} F(m_1+_b m_2) \times F(m_3).}$$
-The composite $M_1 \odot (M_2 \odot M_3)$ is obtained similarly:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a$};
-\node (B) at (2,0) {$m_1 +_b (m_2 +_c m_3)$};
-\node (C) at (4,0) {$d$};
-%\node (D) at (3,0) {$x \in F(m)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$$} (B)
-(C) edge node[above]{$$} (B);
-\end{tikzpicture}
-\]
-as well as the decoration $x_1 \odot (x_2 \odot x_3)$ on the apex:
-$$x_1 \odot (x_2 \odot x_3) \mapseqq 1 \xrightarrow{\zeta_2} F(m_1) \times F(m_2 +_c m_3) \xrightarrow{\phi_{m_1, m_2 +_c m_3}} F(m_1+(m_2 +_c +m_3)) \xrightarrow{F(\psi)} F(m_1+_{b} (m_2+_{c} m_3))$$with $\zeta_2$ being similar to $\zeta_1$ above.
-The associator $\alpha$ is then given by the map of $F$-decorated cospans given by the map of cospans
+the isomorphism $(M_1\odot M_2)\odot M_3\cong M_1\odot (M_2\odot M_3)$ is the isomorphism of cospans 
 \[
@@
 (C') edge node {$$} (D)
-(B) edge node [left] {$\alpha$} (D);
-\end{tikzpicture}
-\]
-together with the decoration morphism $\tau_\alpha \colon F(\alpha)((x_1 \odot x_2) \odot x_3) \to (x_1 \odot (x_2 \odot x_3))$ that is obtained by pasting various commutative squares together, as we did for a horizontal composite above.
-The associator $\alpha$ will then satisfy the pentagon identity:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (-0.5,0) {$((M_1 \odot M_2) \odot M_3) \odot M_4$};
-\node (B) at (3,1.05) {$(M_1 \odot (M_2 \odot M_3)) \odot M_4$};
-\node (C) at (6.5,0) {$M_1 \odot ((M_2 \odot M_3) \odot M_4)$};
-\node (D) at (1.5,-1.05) {$(M_1 \odot M_2) \odot (M_3 \odot M_4)$};
-\node (E) at (4.5,-1.05) {$M_1 \odot (M_2 \odot (M_3 \odot M_4))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node [above] {$\alpha \times 1$}(B)
-(B) edge node [above] {$\alpha$}(C)
-(A) edge node [below] {$\alpha$}(D)
-(D) edge node [above] {$\alpha$}(E)
-(C) edge node [below] {$1 \times \alpha$}(E);
-\end{tikzpicture}
-\]
-which we may realize in two stages.
-First, for the underlying pentagon of maps of cospans in $\A$ commuting due to the fact that $\lCsp(\A)$ is a double category with its own associator that satisfies the pentagon identity, and second, for the pentagon of morphisms of decorations due to the pasting of various commutative squares in $\Cat$.
-
-We next construct the left unitor. Given a horizontal 1-cell $M$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a$};
-\node (B) at (1,0) {$m$};
-\node (C) at (2,0) {$b$};
-\node (D) at (3,0) {$x \in F(m)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i$} (B)
-(C) edge node[above]{$o$} (B);
-\end{tikzpicture}
-\]
-the left unitor will be a globular 2-morphism $\lambda \colon 1_a \odot M \to M$, where the identity horizontal 1-cell on the object $a$ will once again make use of the trivial decoration on an object introduced earlier.
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a$};
-\node (B) at (1,0) {$a$};
-\node (C) at (2,0) {$a$};
-\node (D) at (3,0) {$\bot_a \in F(a)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$\id_a$} (B)
-(C) edge node[above]{$\id_a$} (B);
-\end{tikzpicture}
-\]
-To compose $1_a$ and $M$, we first compose the two cospans in $\A$ by pushing out over their shared object $a$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a$};
-\node (B) at (1,1) {$a$};
-\node (C) at (2,0) {$a$};
-\node (D) at (3,1) {$m$};
-\node (E) at (4,0) {$b$};
-\node (F) at (2,2) {$a+m$};
-\node (G) at (2,3) {$a+_{a} m$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$\id_a$} (B)
-(C) edge node[above]{$\id_a$} (B)
-(C) edge node [above] {$i$} (D)
-(E) edge node [above] {$o$} (D)
-(B) edge node [above] {$j_a$} (F)
-(D) edge node [above] {$j_m$} (F)
-(F) edge node [left] {$\psi$} (G)
-(A) edge[bend left] node [left] {$\psi j_a$} (G)
-(E) edge[bend right] node [right] {$\psi j_{m} o$} (G);
-\end{tikzpicture}
-\]
-The composite decoration $\bot_a \odot x$ will be given by the composite
-$$1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{\bot_a \times x} F(a) \times F(m) \xrightarrow{\phi_{a,m}} F(a+m) \xrightarrow{F(\psi)} F(a+_{a} m).$$
-The left unitor is then the map of $F$-decorated cospans determined by the following map of cospans in $\A$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$a$};
-\node (A') at (0,-0.5) {$a$};
-\node (B) at (1.5,0.5) {$a+_{a} m$};
-\node (C) at (3,0.5) {$b$};
-\node (C') at (3,-0.5) {$b$};
-\node (D) at (1.5,-0.5) {$m$};
-\node (E) at (4.5,0.5) {$\bot_a \odot x \in F(a+_{a} m)$};
-\node (F) at (4.5,-0.5) {$x \in F(m)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$\psi j_a$} (B)
-(C) edge node[above]{$\psi j_m o$} (B)
-(A) edge node[left]{$\id_{a}$} (A')
-(C) edge node[right]{$\id_{b}$} (C')
-(A') edge node [above]{$i$} (D)
-(C') edge node [above]{$o$} (D)
-(B) edge node [left] {$\ell$} (D);
-\end{tikzpicture}
-\]
-together with the decoration morphism $\tau_\lambda \colon F(\ell)(\bot_a \odot x) \to x$; note, that $\ell \colon a+_a m \to m$ is a canonical isomorphism as both $a+_a m$ and $m$ are colimits of the span $a \xleftarrow{\id_a} a \xrightarrow{i} m$.
-The right unitor $\rho$ is similar, the two unitality squares are similar to the associator shown above, and it is clear that the source and target functors applied to the associator and left and right unitors yield identities.
-
-The final property that we will check is the interchange law for 2-morphisms. Suppose that we have four 2-morphisms $\alpha, \beta, \alpha'$ and $\beta'$ as shown below:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$a$};
-\node (A') at (0,-0.5) {$a'$};
-\node (B) at (1,0.5) {$m$};
-\node (C) at (2,0.5) {$b$};
-\node (C') at (2,-0.5) {$b'$};
-\node (D) at (1,-0.5) {$m'$};
-\node (E) at (3,0.5) {$x \in F(m)$};
-\node (F) at (3,-0.5) {$x' \in F(m')$};
-\node (G) at (4,0.5) {$b$};
-\node (H) at (5,0.5) {$n$};
-\node (I) at (6,0.5) {$c$};
-\node (G') at (4,-0.5) {$b'$};
-\node (H') at (5,-0.5) {$n'$};
-\node (I') at (6,-0.5) {$c'$};
-\node (J) at (7,0.5) {$y \in F(n)$};
-\node (K) at (7,-0.5) {$y' \in F(n')$};
-\node (L) at (1,-1) {$\tau_\alpha \maps F(h_1)(x) \to x'$};
-\node (M) at (5,-1) {$\tau_\beta \maps F(h_2)(y) \to y'$};
-\node (A'') at (0,-1.5) {$a'$};
-\node (A''') at (0,-2.5) {$a''$};
-\node (B'') at (1,-1.5) {$m'$};
-\node (C'') at (2,-1.5) {$b'$};
-\node (C''') at (2,-2.5) {$b''$};
-\node (D'') at (1,-2.5) {$m''$};
-\node (E'') at (3,-1.5) {$x' \in F(m')$};
-\node (F'') at (3,-2.5) {$x'' \in F(m'')$};
-\node (G'') at (4,-1.5) {$b'$};
-\node (H'') at (5,-1.5) {$n'$};
-\node (I'') at (6,-1.5) {$c'$};
-\node (G''') at (4,-2.5) {$b''$};
-\node (H''') at (5,-2.5) {$n''$};
-\node (I''') at (6,-2.5) {$c''$};
-\node (J'') at (7,-1.5) {$y' \in F(n')$};
-\node (K'') at (7,-2.5) {$y'' \in F(n'')$};
-\node (L'') at (1,-3) {$\tau_{\alpha'} \maps F(h_1')(x') \to x''$};
-\node (M'') at (5,-3) {$\tau_{\beta'} \maps F(h_2')(y') \to y''$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i_1$} (B)
-(C) edge node[above]{$o_1$} (B)
-(A) edge node[left]{$f$} (A')
-(C) edge node[right]{$g$} (C')
-(A') edge node[above] {$i_1'$} (D)
-(C') edge node[above] {$o_1'$} (D)
-(B) edge node [left] {$h_1$} (D)
-(G) edge node [above] {$i_2$} (H)
-(G) edge node [left] {$g$} (G')
-(H) edge node [left] {$h_2$} (H')
-(G') edge node [above] {$i_2'$} (H')
-(I) edge node [above] {$o_2$} (H)
-(I) edge node [right] {$k$} (I')
-(I') edge node [above] {$o_2'$} (H')
-(A'') edge node[above]{$i_1'$} (B'')
-(C'') edge node[above]{$o_1'$} (B'')
-(A'') edge node[left]{$f'$} (A''')
-(C'') edge node[right]{$g'$} (C''')
-(A''') edge node[above] {$i_1''$} (D'')
-(C''') edge node[above] {$o_1''$} (D'')
-(B'') edge node [left] {$h_1'$} (D'')
-(G'') edge node [above] {$i_2'$} (H'')
-(G'') edge node [left] {$g'$} (G''')
-(H'') edge node [left] {$h_2'$} (H''')
-(G''') edge node [above] {$i_2''$} (H''')
-(I'') edge node [above] {$o_2'$} (H'')
-(I'') edge node [right] {$k'$} (I''')
-(I''') edge node [above] {$o_2''$} (H''');
-\end{tikzpicture}
-\]
-We may compose these first vertically and then horizontally, or first horizontally and then vertically, and we must show that these two ways of composing yield the same result.
-Composing first vertically and then horizontally results in:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$a$};
-\node (A') at (0,-0.5) {$a''$};
-\node (B) at (2,0.5) {$m+_{b} n$};
-\node (C) at (4,0.5) {$c$};
-\node (C') at (4,-0.5) {$c''$};
-\node (D) at (2,-0.5) {$m'' +_{b''} n''$};
-\node (E) at (5.5,0.5) {$x \odot y \in F(m+_{b} n)$};
-\node (F) at (5.5,-0.5) {$x'' \odot y'' \in F(m'' +_{b''} n'')$};
-\node (G) at (2,-1) {$\tau_{(\alpha' \alpha) \odot (\beta' \beta)} \maps F((h_1' h_1)+_{g' g} (h_2' h_2))(x \odot y) \to x'' \odot y''$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$ \psi j_m i_1$} (B)
-(C) edge node[above]{$ \psi j_n o_2$} (B)
-(A) edge node[left]{$f' f$} (A')
-(C) edge node[right]{$k' k$} (C')
-(A') edge node [above]{$\psi j_{m''} i_1''$} (D)
-(C') edge node [above]{$\psi j_{n''} o_2''$} (D)
-(B) edge node [left] {$(h_1' h_1) +_{g' g} (h_2' h_2)$} (D);
-\end{tikzpicture}
-\]
-whereas first composing horizontally and then vertically results in:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$a$};
-\node (A') at (0,-0.5) {$a''$};
-\node (B) at (2,0.5) {$m+_{b} n$};
-\node (C) at (4,0.5) {$c$};
-\node (C') at (4,-0.5) {$c''$};
-\node (D) at (2,-0.5) {$m'' +_{b''} n''$};
-\node (E) at (5.5,0.5) {$x \odot y \in F(m+_{b} n)$};
-\node (F) at (5.5,-0.5) {$x'' \odot y'' \in F(m'' +_{b''} n'')$};
-\node (G) at (2,-1) {$\tau_{(a' \odot \beta')(\alpha \odot \beta)} \maps F((h_1' +_{g'} h_2')(h_1 +_g h_2))(x \odot y) \to x'' \odot y''.$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$\psi j_{m} i_1$} (B)
-(C) edge node[above]{$\psi j_{n} o_2$} (B)
-(A) edge node[left]{$f' f$} (A')
-(C) edge node[right]{$k' k$} (C')
-(A') edge node [above]{$\psi j_{m''} i_1''$} (D)
-(C') edge node [above]{$\psi j_{n''} o_2''$} (D)
-(B) edge node [left] {$(h_1' +_{g'} h_2')(h_1 +_g h_2)$} (D);
-\end{tikzpicture}
-\]
-Everything about these two composites appears identical except for the two middle morphisms and the two morphisms of decorations.
-However, the two maps $(h_1' h_1) +_{g' g} (h_2' h_2) \maps m+_{b} n \to m'' +_{b''}n''$ and $(h_1' +_{g'} h_2')(h_1 +_g h_2) \maps m+_{b} n \to m'' +_{b''} n''$ are the same universal map realized in two different ways.
-The two morphisms of decorations $\tau_{(\alpha' \odot \beta')(\alpha \odot \beta)}$ and $\tau_{(\alpha' \alpha) \odot (\beta' \beta)}$ are also the same as they are obtained as two different compositions of four 2-morphisms in $\Cat$, namely first vertically and then horizontally and first horizontally and then vertically.
-The interchange law for $\Cat$ says that these two composites must be the same as well, and thus the interchange law for our double category $F\lCsp$ is also satisfied.
+(B) edge node [left] {$\stackrel{\alpha}{\cong}$} (D);
+\end{tikzpicture}
+\]
+together with an isomorphism $F(\alpha)((x_1 \odot x_2) \odot x_3) \cong (x_1 \odot (x_2 \odot x_3))$ between the decorations 
+\begin{gather*}
+\scalebox{.8}{$1\xrightarrow{x_1\times x_2}F(m_1)\times F(m_2)\xrightarrow{\phi}F(m_1+m_2)\to F(m_1+_bm_2)\xrightarrow{1\times x_3}F(m_1+_bm_2)\times F(m_3)\xrightarrow{\phi}F((m_1+_bm_2)+m_3)\to F((m_1+_bm_2)+_cm_3)\cong F(m_1+_b(m_2+_cm_3))$} \\
+\scalebox{.8}{$1\xrightarrow{x_2\times x_3}F(m_2)\times F(m_3)\xrightarrow{\phi}F(m_2+m_3)\to F(m_2+_cm_3)\xrightarrow{x_1\times1}F(m_1)\times F(m_2+_cm_3)\xrightarrow{\phi}F(m_1\times(m_2+_cm_3))\to F(m_1+_b(m_2+_cm_3))$}
+\end{gather*}
+which is constructed by pasting structure isomorphisms like above.
+Similarly the right and left unitors can be constructed, and all data satisfy the axioms of a double category.
+For full details of these arguments, see \cite[Theorem~4.1.1]{CourserThesis}.
 \begin{comment}

### 2020-11-23 cospans.tex
abstract's first take

@@
 \begin{abstract}
-\noindent
-The first two authors have developed a compositional framework well-suited for studying networks that are built out of finite sets equipped 
-with extra stuff. This framework, which goes by the name of `structured cospans', utilizes double categories where the objects are seen as 
-inputs and outputs, horizontal 1-cells are `open networks', and 2-morphisms are maps between open networks. In this setup a functor $L \maps 
-\A \to \textsf{X}$, which is typically a left adjoint, is used to replace the objects and vertical 1-morphisms of a given double category 
-$\lX$ with the objects and morphisms, respectively, of the category $\A$. Horizontal 1-cells are then cospans in $\textsf{X}$ of a 
-particular form with 2-morphisms given by maps of these cospans. Fong has also developed a similar framework utilizing cospans to study open 
-networks which goes by the name of `decorated cospans'. In this setup, a lax monoidal functor $F \maps \A \to \textsf{Set}$ is used to 
-`decorate' the apices of cospans in $\A$ with elements of $\textsf{Set}$ giving the cospans extra structure. Using a slight variation of 
-Fong's framework, we prove that these two frameworks are equivalent in the situation where a left adjoint can be obtained from a lax 
-monoidal pseudofunctor using a well known construction of Grothendieck.
+The first two authors have recently developed a compositional framework by the name of `structured cospans' which is well-suited for studying networks.
+This framework utilizes double categories where the objects are seen as inputs and outputs and horizontal 1-cells are ‘open networks’ written as cospans, where a typically left adjoint functor $L\maps \A\to\X$ is used to replace the objects and vertical 1-morphisms of a given double category $\lX$ with those of a category $\A$.
+Fong has also developed a similar framework utilizing cospans to study open networks which goes by the name of ‘decorated cospans’.
+In this setup, a lax monoidal functor $F\maps \A\to\Set$ is used to "decorate" the apices of cospans in $\A$ with elements of $\Set$ giving the cospans extra structure.
+Using a slight variation of Fong’s framework, we prove that these two frameworks are equivalent in the situation where a left adjoint can be obtained from a lax monoidal pseudofunctor using a well known construction of Grothendieck.
 \end{abstract}

### 2020-11-23 cospans.tex
unit categor

@@
 \begin{tikzcd}
-a\ar[r,"1_a"] & a & a,\ar[l,"1_a"'] & \bot_a:=1\xrightarrow{\phi_0}F(0)\xrightarrow{F(!_a)}F(a)
+a\ar[r,"1_a"] & a & a,\ar[l,"1_a"'] & \bot_a:=\one\xrightarrow{\phi_0}F(0)\xrightarrow{F(!_a)}F(a)
 \end{tikzcd}
@@
 with decoration
-$$x\odot y:= 1\cong1 \times 1 \xrightarrow{x \times y} F(m) \times F(n) \xrightarrow{\phi_{m,n}} F(m+n) \xrightarrow{F(\psi)} F(m+_{b}n)$$
+$$x\odot y:= \one\cong\one \times \one \xrightarrow{x \times y} F(m) \times F(n) \xrightarrow{\phi_{m,n}} F(m+n) \xrightarrow{F(\psi)} F(m+_{b}n)$$
 where $\psi \maps m + n \to m+_{b} n$ is the natural map from the coproduct to the pushout and $\phi_{m,n} \maps F(m) \times F(n) \to F(m+n)$ are the lax monoidal structure maps of $F$.
@@
 \node (A) at (4.75,0) {$\scriptstyle\Downarrow \tau_\alpha \times \tau_\beta$};
-\node (D) at (3,0) {$1 \cong 1 \times 1$};
+\node (D) at (3,0) {$\one \cong \one \times \one$};
 \node (E) at (5.5,0.5) {$F(m) \times F(n)$};
@@
 \begin{gather*}
-\scalebox{.8}{$1\xrightarrow{x_1\times x_2}F(m_1)\times F(m_2)\xrightarrow{\phi}F(m_1+m_2)\to F(m_1+_bm_2)\xrightarrow{1\times x_3}F(m_1+_bm_2)\times F(m_3)\xrightarrow{\phi}F((m_1+_bm_2)+m_3)\to F((m_1+_bm_2)+_cm_3)\cong F(m_1+_b(m_2+_cm_3))$} \\
-\scalebox{.8}{$1\xrightarrow{x_2\times x_3}F(m_2)\times F(m_3)\xrightarrow{\phi}F(m_2+m_3)\to F(m_2+_cm_3)\xrightarrow{x_1\times1}F(m_1)\times F(m_2+_cm_3)\xrightarrow{\phi}F(m_1\times(m_2+_cm_3))\to F(m_1+_b(m_2+_cm_3))$}
+\scalebox{.8}{$\one\xrightarrow{x_1\times x_2}F(m_1)\times F(m_2)\xrightarrow{\phi}F(m_1+m_2)\to F(m_1+_bm_2)\xrightarrow{1\times x_3}F(m_1+_bm_2)\times F(m_3)\xrightarrow{\phi}F((m_1+_bm_2)+m_3)\to F((m_1+_bm_2)+_cm_3)\cong F(m_1+_b(m_2+_cm_3))$} \\
+\scalebox{.8}{$\one\xrightarrow{x_2\times x_3}F(m_2)\times F(m_3)\xrightarrow{\phi}F(m_2+m_3)\to F(m_2+_cm_3)\xrightarrow{x_1\times1}F(m_1)\times F(m_2+_cm_3)\xrightarrow{\phi}F(m_1\times(m_2+_cm_3))\to F(m_1+_b(m_2+_cm_3))$}
 \end{gather*}
 which is constructed by pasting structure isomorphisms like above.
-Similarly the right and left unitors can be constructed, and all data satisfy the axioms of a double category.
+Similarly the right and left unitors can be constructed, and all data satisfy the axioms of a double category -- essentially breaking down to those of the cospan double category of $\A$ and axioms of the lax monoidal pseudofunctor $F$.
 For full details of these arguments, see \cite[Theorem~4.1.1]{CourserThesis}.
@@
 \otimes_a\maps F(a)\times F(a)\xrightarrow{\phi_{a,a}}F(a+a)\xrightarrow{F(\nabla)}F(a),\quad
-I_a\maps\mathbf{1}\xrightarrow{\phi_0}F(0)\xrightarrow{F(!)}F(a)
+I_a\maps\one\xrightarrow{\phi_0}F(0)\xrightarrow{F(!)}F(a)
 \end{equation}
@@
  \end{tikzcd}\qquad
-  \mathbf{1}\xrightarrow{x\times y}F(m)\times F(n)\xrightarrow{\phi_{m,n}}F(m+n)\xrightarrow{F(\psi)}F(m+_bn)
+  \one\xrightarrow{x\times y}F(m)\times F(n)\xrightarrow{\phi_{m,n}}F(m+n)\xrightarrow{F(\psi)}F(m+_bn)
 \end{equation}
@@
 \begin{align*}
-\lE(M)\ot\lE(M')&\;\stackrel{\cref{eq:tensordecoration}}{=}\;a+a'\xrightarrow{i+i'}m+m'\xleftarrow{o+o'}b+b' \textrm{ with }\mathbf{1}\xrightarrow{x\times x'}F(m)\times F(m')\xrightarrow{\phi_{m,m'}}F(m+m') \\
+\lE(M)\ot\lE(M')&\;\stackrel{\cref{eq:tensordecoration}}{=}\;a+a'\xrightarrow{i+i'}m+m'\xleftarrow{o+o'}b+b' \textrm{ with }\one\xrightarrow{x\times x'}F(m)\times F(m')\xrightarrow{\phi_{m,m'}}F(m+m') \\
 \lE(M\ot M')&\;\stackrel{\cref{eq:tensorstuctured}}{=}\;\lE\Big((a+a',\bot_{a+a'})\to\underbrace{(m+m',F(\iota_m)x+F(\iota_{m'})x')}_{\cref{eq:fibrewisecoprod}}\leftarrow(b+b',\bot_{b+b'})\Big)%=a+a'\xrightarrow{i+i'}m+m'\xleftarrow{o+o'}b+b' \textrm{ with }\phi_{m,m'}(x,x')
@@
 which are uniquely isomorphic $F(\iota_m)x+F(\iota_{m'})\cong \phi_{m,m'}(x,x')$ in an analogous way to \cref{eq:isomorphismdiag}, as also discussed after \cref{cor:fcocMonGroth}.
-Moreover, the monoidal unit for the category of arrows of $F\lCsp$ is $0_\A\xrightarrow{\raisebox{-3pt}[0pt][0pt]{$=$}}0_\A\xleftarrow{\raisebox{-3pt}[0pt][0pt]{$=$}}0_\A$ with the trivial decoration $\phi_0\maps \mathbf{1}\to F(0_A)$,
+Moreover, the monoidal unit for the category of arrows of $F\lCsp$ is $0_\A\xrightarrow{\raisebox{-3pt}[0pt][0pt]{$=$}}0_\A\xleftarrow{\raisebox{-3pt}[0pt][0pt]{$=$}}0_\A$ with the trivial decoration $\phi_0\maps \one\to F(0_A)$,
 which is an initial object and as such isomorphic to $0_{F(0)}$

### 2020-11-23 cospans.tex
Shortening Appendix A.3

@@
 %%%Christina: add the notation bb{C}sp(A) since it will be central to what follows?
-with cospans in $\A$ as its horizontal 1-cells \cite{Courser,Niefield}.
+with cospans in $\A$ as its horizontal 1-cells \cite{Niefield}.
 %%% Christina: I would be inclined to first cite Niefield and then Courser due to the chronological order.
+%%% Kenny: I think when we \cite{...}, we list the references alphabetically, but let's just cite Niefield here and achieve both.
 
@@
 %%% Christina: the previous formula $\tau_{\bot_f} = F(f) F(!) \phi \maps 1 \to F(a')$ doesn't typecheck to me.
+%%% Kenny: \phi:1-->F(0), F(!):F(0)-->F(a), F(f):F(a)-->F(a')? Or did I make a mistake somewhere?
 Finally, the (horizontal) composition functor $\odot$ maps two composable $F$-decorated cospans $\left(a\to m\leftarrow b,x\in F(m)\right)$ and $\left(b\to n\leftarrow c,y\in F(n)\right)$ to their pushout in $\A$ over their shared foot
@@
 %%% I mean an arbitrary object in the Grothendieck category. I just made it a pair to be clearer, is it OK? Erase these comments whenever you want.
+%%% Oh, gotchya'
 \begin{equation}\label{eq:scsphor1cell}
@@
 
-%%% Is this biequivalnce symmetric monoidal? Mike says yes, but it follows from a result that he has yet to officially publish. It's a result of a paper he's currently working on with someone.
-%%% Christina: Kenny, is the above comment still relevant? If not, feel free to erase!
-
 \section{Bicategorical and categorical aspects}
@@
 %%% Christina: Kenny, would you mind cleaning this section up to? I don't believe we need the full fledged definitions here by the way.
-
-Before formally defining `pseudo double category', it is helpful to have the following picture in mind. A pseudo double category has 2-morphisms shaped like:
+%%% Kenny: Sure!
+
+Before formally defining `pseudo double category', it is helpful to have the following picture in mind. A pseudo double category $\lA$ has 2-morphisms shaped like:
 
@@
 \]
-We call $A, B, C$ and $D$ \define{objects} or \define{0-cells}, $f$ and $g$ \define{vertical 1-morphisms}, $M$ and $N$ \define{horizontal 1-cells} and $a$ a \define{2-morphism}.
-Note that a vertical 1-morphism is a morphism between 0-cells and a 2-morphism is a morphism between horizontal 1-cells.
-%We will denote both kinds of morphisms and horizontal 1-cells as a single arrow, namely `$\to$'???
-Or should we put a ``tick'' in here?
-We follow the notation of Shulman \cite{Shulman2008} with the following definitions.
+We call $A, B, C$ and $D$ \define{objects}, $f$ and $g$ \define{vertical 1-morphisms}, $M$ and $N$ \define{horizontal 1-cells} and $a$ a \define{2-morphism}. 
+%Note that a vertical 1-morphism is a morphism between 0-cells and a 2-morphism is a morphism between horizontal 1-cells. 
+%We will denote both kinds of morphisms and horizontal 1-cells as a single arrow, namely `$\to$'???   Or should we put a ``tick'' in here?
+A 2-morphism where $f$ and $g$ are identities is called a \textbf{globular 2-morphism}.
+We call $M$ and $N$ the \define{horizontal source and target} of the 2-morphism $a$, respectively, and likewise we call $f$ and $g$ the \define{vertical source and target} of the 2-morphism $a$, respectively.
+Thus $_f \lA_g(M,N)$ denotes the set of 2-morphisms in $\lA$ with horizontal source and target $M$ and $N$ and vertical source and target $f$ and $g$.
+%We follow the notation of Shulman \cite{Shulman2008} with the following definitions.
+
+\begin{defn}\label{defn:double_category}
+A \define{(pseudo) double category} $\lA$ is a category object internal to the 2-category $\Cat$.
+\end{defn}
+
+\begin{comment}
 
@@
 such that $S(\alpha), S(\lambda), S(\rho), T(\alpha), T(\lambda)$ and $T(\rho)$ are all identities and that the coherence axioms of a monoidal category are satisfied.
-Following the notation of Shulman, objects of $\lD_0$ are called \define{objects} or \define{0-cells}
+Following the notation of Shulman, objects of $\lD_0$ are called \define{objects}
 %%% I'm tempted to delete 0-cells since we never use that term anywhere in any paper, but I do like the idea that "n+1 morphisms go between n cells".
 %%% Christina: I am up for deletion of 0-cells
+%%% Kenny: Okay, I deleted it.
 and morphisms of $\lD_0$ are called \define{vertical 1-morphisms}.
@@
 \end{defn}
-A 2-morphism where $f$ and $g$ are identities is called a \textbf{globular 2-morphism}.
+%A 2-morphism where $f$ and $g$ are identities is called a \textbf{globular 2-morphism}.
+We call $M$ and $N$ the \define{horizontal source and target} of the 2-morphism $a$, respectively, and likewise we call $f$ and $g$ the \define{vertical source and target} of the 2-morphism $a$, respectively.
+Thus $_f \lA_g(M,N)$ denotes the set of 2-morphisms in $\lA$ with horizontal source and target $M$ and $N$ and vertical source and target $f$ and $g$.
 
@@
 We will sometimes omit the word pseudo and simply say double category.
+
+\end{comment}
 
@@
 %\end{defn}
-
+\begin{defn}\label{def:doublefun}
+Given double categories $\lA$ and $\lX$, a \define{(pseudo) double functor} $\lF \colon\lA \to \lX$ consists of:
+\begin{enumerate}
+\item{functors $\lF_0 \colon \lA_0 \to \lX_0$ and $\lF_1 \colon \lA_1 \to \lX_1$ such that $S \lF_1 = \lF_0 S$ and $T \lF_1 = \lF_0 T$, and}
+\item{for every composable pair of horizontal 1-cells $M$ and $N$ in $\lA$, a natural transformation $\phi_{M,N} \colon \lF(M) \odot \lF(N) \to \lF(M \odot N)$ called the \define{composite comparison} and for every object $a$ in $\lA$, a natural transformation $\phi_a \colon U_{\lF_0(a)} \to \lF_1(U_a)$ called the \define{unit comparison}.
+The components of each of these natural transformations are globular isomorphisms which satisfy the usual coherence axioms for a monoidal functor.}
+\end{enumerate}
+\end{defn}
+
+\begin{defn}
+Given double functors $(\lF,\phi),(\mathbb{G},\psi) \colon \lA \to \lX$, a \define{double transformation} $\alpha \colon \lF \Rightarrow \mathbb{G}$ consists of transformations $\alpha_0 \colon \lF_0 \Rightarrow \mathbb{G}_0$ and $\alpha_1 \colon \lF_1 \Rightarrow \mathbb{G}_1$ such that $S(\alpha_M) = \alpha_{S(M)}$ and $T(\alpha_M) = \alpha_{T(M)}$, and for two composable horizontal 1-cells $M$ and $N$ of $\lA$, $\alpha \circ \phi_{M,N} = \psi \circ (\alpha_M \odot \alpha_N)$ and $\alpha \circ \phi_a = \psi_a \circ \alpha$.
+\end{defn}
+
+\begin{comment}
 \begin{defn}\label{def:doublefun}
@@
 \end{defn}
+\end{comment}
 
@@
 %\]
-We call $M$ and $N$ the \define{horizontal source and target} of the 2-morphism $a$, respectively, and likewise we call $f$ and $g$ the \define{vertical source and target} of the 2-morphism $a$, respectively.
-Thus $_f \lA_g(M,N)$ denotes the set of 2-morphisms in $\lA$ with horizontal source and target $M$ and $N$ and vertical source and target $f$ and $g$.
 
@@
 \begin{thm}
-Let $\lA$ and $\lX$ be symmetric monoidal double categories and let $\lF \maps \lA \to \lX$ be a symmetric monoidal strong double functor.
+Let $\lA$ and $\lX$ be symmetric monoidal double categories and let $\lF \maps \lA \to \lX$ be a symmetric monoidal pseudo double functor.
 If $\lF$ is part of a double equivalence, then $\lF$ is in fact part of a symmetric monoidal double equivalence, and $\lA$ and $\lX$ are equivalent as symmetric monoidal double categories.
@@
 \begin{proof} Where is this proved???  \end{proof}
-
+%%% Kenny: This isn't proved anywhere formally, as far as I know.
+
+Let $\mathbf{Dbl}$ denote the 2-category of double categories, double functors and double transformations.
+One can check that $\mathbf{Dbl}$ has finite products, and in any 2-category with finite products we can define a `pseudomonoid' or a `weak' monoid, which is a categorified analogue of a monoid in which the left and right unitors and associators are not identities but natural isomorphisms.
+It is the 2-categorical structure of $\mathbf{Dbl}$, or more generally, any 2-category with finite limits, that enables us to do this.
+For example, a pseudomonoid in $\mathbf{Cat}$ is a monoidal category.
+We are primarily concerned with the (weak) monoidal double categories in which the associators and left and right unitors are natural isomorphisms.
+\begin{defn}\label{defn:smdc}
+A \define{monoidal double category} is a pseudomonoid internal to the monoidal 2-category $\mathbf{Dbl}$.
+Similarly, a \define{braided monoidal double category} is a braided pseudomonoid internal to $\mathbf{Dbl}$ and a \define{symmetric monoidal double category} is a symmetric pseudomonoid internal to $\mathbf{Dbl}$.
+\end{defn}
+For more details on the definition of (braided, symmetric) monoidal double category, we refer to Hansen and Shulman \cite{HS}.
+
+\begin{comment}
 \begin{defn}\label{defn:smdc}
 %  A \textbf{monoidal double category} is a double category equipped the following
-  A \textbf{monoidal double category} is a double category $\lD$ equipped with the following
+  A \textbf{monoidal double category} is a double category $\lA$ equipped with the following
 structure.
@@
 \end{defn}
+\end{comment}
 
 \begin{defn}\label{def:companion}
-  Let $\lD$ be a double category and $f\maps A\to B$ a vertical
+  Let $\lA$ be a double category and $f\maps A\to B$ a vertical
   1-morphism.  A \textbf{companion} of $f$ is a horizontal 1-cell
@@
   A \textbf{conjoint} of $f$, denoted $\fchk \maps B\to A$, is a
-  companion of $f$ in the double category $\lD^{h\cdot\mathrm{op}}$
+  companion of $f$ in the double category $\lA^{h\cdot\mathrm{op}}$
   obtained by reversing the horizontal 1-cells, but not the vertical
-  1-morphisms, of $\lD$.
+  1-morphisms, of $\lA$.
 \end{defn}
@@
 \end{defn}
+
+\begin{defn}\label{defn:monoidal_double_functor}
+Given (braided, symmetric) monoidal double categories $\lA$ and $\lX$, a \define{(braided, symmetric) monoidal double functor} $\lF \colon \lA \to \lX$ is a double functor $\lF$ together with transformations $\theta \colon {\otimes \circ (\lF,\lF)} \to \lF \circ \otimes$ and $\theta_U \colon 1_\lX \to \lF \circ 1_\lA$ that satisfy the usual coherence axioms for a (braided, symmetric) monoidal functor with respect to $\otimes$.
+\end{defn}
+
+For more details on the definition of (braided, symmetric) monoidal functor, we refer to Hansen and Shulman \cite{HS}.
+
+\begin{comment}
 
@@
 
+\end{comment}
+
 DEFINITION OF SYMMETRIC MONOIDAL ISOMORPHISM, BRIEFLY?

### 2020-11-24 cospans.tex
rewrote abstract

@@
 % in LaTeX
-% 2020/11/20
+% 2020/11/23
 
@@
 \begin{abstract}
-The first two authors have recently developed a compositional framework by the name of `structured cospans' which is well-suited for studying networks.
-This framework utilizes double categories where the objects are seen as inputs and outputs and horizontal 1-cells are ‘open networks’ written as cospans, where a typically left adjoint functor $L\maps \A\to\X$ is used to replace the objects and vertical 1-morphisms of a given double category $\lX$ with those of a category $\A$.
-Fong has also developed a similar framework utilizing cospans to study open networks which goes by the name of ‘decorated cospans’.
-In this setup, a lax monoidal functor $F\maps \A\to\Set$ is used to "decorate" the apices of cospans in $\A$ with elements of $\Set$ giving the cospans extra structure.
-Using a slight variation of Fong’s framework, we prove that these two frameworks are equivalent in the situation where a left adjoint can be obtained from a lax monoidal pseudofunctor using a well known construction of Grothendieck.
+One goal of applied category theory is to understand open systems.
+We compare two ways of describing open systems as cospans equipped with extra data.
+First, given a functor $L \maps \A \to \X$, a `structured cospan' is a diagram in $\A$ of the form $L(a) \rightarrow x \leftarrow L(b)$.
+If $\A$ and $\X$ have finite colimits and $L$ preserves them, it is known that there is a symmetric monoidal double category whose objects are those of $\A$ and whose horizontal 1-cells are structured cospans.
+Second, if $\A$ has finite colimits and $F \maps (\A,+) \to (\Cat,\times)$ is a symmetric lax monoidal pseudofunctor , a `decorated cospan' is a diagram in $\A$ of the form $a \rightarrow s \leftarrow b$ together with an object of $F(s)$.
+Generalizing the work of Fong, we show that in this situation there is a symmetric monoidal double category whose objects are those of $\A$ and whose horizontal 1-cells are structured cospans.
+We prove that under certain conditions these two consstructions are equivalent when we take $\X = \int F$ to be the Grothendieck category of $F$.
+We illustrate these ideas with applications to electrical circuits, Petri nets, reaction networks and dynamical systems.
 \end{abstract}
@@
 
+%%%DISCUSS OPEN COMMUTATIVE MONOIDAL CATEGORIES!!!
+
+\subsection{Reaction networks}
+
+%%% Do reaction networks and dynamical systems (which do NOT come from structured cospans).
+
 \section{Conclusions}\label{sec:conclusions}
@@
 
-{\chris There used to be references for more details on the material that follows. Why would we not provide them?}
-A \define{monoidal} bicategory $\bA$ comes with a pseudofunctor $\otimes\maps\bA\times\bA\to\bA$ and a unit object $I$ that are associative and unital up to coherent equivalence.
+For standard 2-categorical material, we refer the reader to \cite{KS}.
+For monoidal 2-categories see \cite{DS}, and for detailed definitions concerning monoidal bicategories see \cite{GPS, McCrudden,Stay}.
+Briefly, a \define{monoidal} bicategory $\bA$ comes with a pseudofunctor $\otimes\maps\bA\times\bA\to\bA$ and a unit object $I$ that are associative and unital up to coherent equivalence.
 A \define{braided} monoidal bicategory comes with a pseudonatural equivalence $\beta_{a,b}\maps a\ot b\to b\ot a$ and appropriate invertible modifications; it is \define{sylleptic} if there is an appropriate invertible modification $1_{a\ot b}\Rrightarrow\beta_{b,a}\circ\beta_{a,b}$ and it is \define{symmetric} if one further axiom holds.
@@
 
-\bibitem{Courser} K.\ Courser, A bicategory of decorated cospans, \emph{Theory Appl.\ Categ.} \textbf{32} (2017), 995--1027. Available as \href{https://arxiv.org/abs/1605.08100}{arXiv:1605.08100}.
+\bibitem{Courser} K.\ Courser, A bicategory of decorated cospans, \textsl{Theory Appl.\ Categ.} \textbf{32} (2017), 995--1027. Available as \href{https://arxiv.org/abs/1605.08100}{arXiv:1605.08100}.
 
@@
 
-\bibitem{Gray} J. \ Gray, Fibred and Cofibred categories, \emph{Proc. Conf. Categorical Algebra} (La Jolla, California, 1965), 21---83, New York, 1966
+\bibitem{Gray} J. \ Gray, Fibred and Cofibred categories, \textsl{Proc.\ Conf.\ Categorical Algebra} (La Jolla, California, 1965), 21---83, New York, 1966
 
@@
 
-\bibitem{Hermida1999} C. \ Hermida, Some properties of Fib as a fibred 2-category. \emph{J. Pure Appl. Algebra}, 134(1), 83 -- 109, 1999
+\bibitem{Hermida1999} C. \ Hermida, Some properties of Fib as a fibred 2-category, \textsl{J.\ Pure Appl.\ Alg.\ } \textbf{134}, 83 -- 109, 1999
 
@@
 
-\bibitem{KS} G.\ Kelly and R.\ Street, Review of the elements of 2-categories, \emph{Lecture Notes in Mathematics} vol. 40, pages 75---103, Springer Berlin/Heidelberg, 1974.
+\bibitem{KS} G.\ Kelly and R.\ Street, Review of the elements of 2-categories, \textsl{Lecture Notes in Mathematics} vol. 40, pages 75---103, Springer Berlin/Heidelberg, 1974.
 
@@
 
-%\bibitem{Lack} S.\ Lack, Limits for lax morphisms, \emph{Applied Categorical Structures} $\mathbf{30}$ (2005), 189--203.
+%\bibitem{Lack} S.\ Lack, Limits for lax morphisms, \textsl{Applied Categorical Structures} $\mathbf{30}$ (2005), 189--203.
 Available %at \href{http://maths.mq.edu.au/~slack/papers/talgl.pdf}{http://maths.mq.edu.au/$\sim$slack/papers/talgl.pdf}.
@@
 
-\bibitem{MV} J.\ Moeller and C.\ Vasilakopoulou, Monoidal Grothendieck construction, \emph{Theory Appl.\ Categ.} \textbf{35} (2020), 1159--1207.
+\bibitem{McCrudden} P.\ McCrudden, Balanced coalgebroids, \textsl{Theory Appl.\ Categ.\ } \textbf{ 7} (2000), 71--147.
+
+\bibitem{MV} J.\ Moeller and C.\ Vasilakopoulou, Monoidal Grothendieck construction, \textsl{Theory Appl.\ Categ.\ }\textbf{35} (2020), 1159--1207.
 Available as \href{https://arxiv.org/abs/1809.00727}{arXiv:1809.00727}.
@@
 
-\bibitem{Shulman2008} M.\ Shulman, Framed bicategories and monoidal fibrations, \emph{Theory Appl.Categ.} \textbf{20} (2008), 650--738.
+\bibitem{Shulman2008} M.\ Shulman, Framed bicategories and monoidal fibrations, \textsl{Theory Appl.Categ.} \textbf{20} (2008), 650--738.
 Available as \href{https://arxiv.org/abs/0706.1286}{arXiv:0706.1286}.
@@
 
-%\bibitem{Stay} M.\ Stay, Compact closed bicategories.  Available as \href{http://arxiv.org/abs/1301.1053}{arXiv:1301.1053}.
-
-\bibitem{Yass} A.\ Yassine, Open Systems in Classical Mechanics. Available as \href{https://arxiv.org/abs/1710.11392}{arXiv:1710.11392}.
+\bibitem{Stay} M.\ Stay, Compact closed bicategories, \textsl{Theory Appl.\ Categ.\ }\textbf{31} (2016), 755--798.   Available as \href{http://arxiv.org/abs/1301.1053}{arXiv:1301.1053}.
 

### 2020-11-24 cospans.tex
added references to bicategory section of the Appendix

@@
 For standard 2-categorical material, we refer the reader to \cite{KS}.
-For monoidal 2-categories see \cite{DS}, and for detailed definitions concerning monoidal bicategories see \cite{GPS, McCrudden,Stay}.
+For monoidal 2-categories see \cite{DS}, and for detailed definitions concerning monoidal bicategories see \cite{GPS,McCrudden,Stay}.
 Briefly, a \define{monoidal} bicategory $\bA$ comes with a pseudofunctor $\otimes\maps\bA\times\bA\to\bA$ and a unit object $I$ that are associative and unital up to coherent equivalence.
@@
 
-\bibitem{Gray} J. \ Gray, Fibred and Cofibred categories, \textsl{Proc.\ Conf.\ Categorical Algebra} (La Jolla, California, 1965), 21---83, New York, 1966
+\bibitem{GPS} R.\ Gordon, A.\ J.\ Power and R.\ Street, \textsl{Coherence for Tricategories}, \textsl{Mem.\ Amer.\ Math.\ Soc.\ }\textbf{558}, 1995.
+
+\bibitem{Gray} J. \ Gray, Fibred and cofibred categories, \textsl{Proc.\ Conf.\ Categorical Algebra} (La Jolla, California, 1965), 21---83, New York, 1966
 
@@
 
-\bibitem{Herm} C. \ Hermida, Fibrations, logical predicates and indeterminates, PhD Thesis, University of Edinburgh, 1993.
+\bibitem{Herm} C. \ Hermida, \textsl{Fibrations, Logical Predicates and Undeterminates}, Ph.D.\ thesis, Deparment of Mathematics, University of Edinburgh, 1993.
 
@@
 %\bibitem{Hoff} A.\ Hoffnung, Spans in 2-categories: a monoidal tricategory. Available as \href{http://arxiv.org/abs/1112.0560}{arXiv:1112.0560}.
-
-\bibitem{JM} J.\ C.\ Baez and J.\ Master, A compositional framework for Petri nets. In preparation.
 

### 2020-11-24 cospans.tex
replies to comments and some cleaning up

@@
 %%% Kenny: I think when we \cite{...}, we list the references alphabetically, but let's just cite Niefield here and achieve both.
+%%% Christina: Sounds good!
 
@@
 %%% Kenny: \phi:1-->F(0), F(!):F(0)-->F(a), F(f):F(a)-->F(a')? Or did I make a mistake somewhere?
+%%% Christina: Actually indeed it typechecks, I must have been thinking it does not give me the actual morphism, just one of the two or something. No issue now!
 Finally, the (horizontal) composition functor $\odot$ maps two composable $F$-decorated cospans $\left(a\to m\leftarrow b,x\in F(m)\right)$ and $\left(b\to n\leftarrow c,y\in F(n)\right)$ to their pushout in $\A$ over their shared foot
@@
 The other diagrams in the definition of symmetric monoidal double category can be shown to commute similarly.
-%%% Kenny: Probably cut stuff out below this.
-%%% Christina: Commented them out for now, but should definitely have a close look to see if anything is needed when we go over and remake this proof.
-\begin{comment}
-If we denote the above associator simply as $a$ and the left and right unitors as $\lambda$ and $\rho$, respectively, then given four objects in $F\lCsp_1$, say $M_1, M_2, M_3$ and $M_4$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a_1$};
-\node (B) at (1,0) {$m_1$};
-\node (C) at (2,0) {$b_1$};
-\node (D) at (1,-0.5) {$x_1 \in F(m_1)$};
-\node (E) at (3,0) {$a_2$};
-\node (F) at (4,0) {$m_2$};
-\node (G) at (5,0) {$b_2$};
-\node (H) at (4,-0.5) {$x_2 \in F(m_2)$};
-\node (I) at (0,-1.5) {$a_3$};
-\node (J) at (1,-1.5) {$m_3$};
-\node (K) at (2,-1.5) {$b_3$};
-\node (L) at (1,-2) {$x_3 \in F(m_3)$};
-\node (M) at (3,-1.5) {$a_4$};
-\node (N) at (4,-1.5) {$m_4$};
-\node (O) at (5,-1.5) {$b_4$};
-\node (P) at (4,-2) {$x_4 \in F(m_4)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i_1$} (B)
-(C) edge node[above]{$o_1$} (B)
-(E) edge node[above]{$i_2$} (F)
-(G) edge node[above]{$o_2$} (F)
-(I) edge node[above]{$i_3$} (J)
-(K) edge node[above]{$o_3$} (J)
-(M) edge node[above]{$i_4$} (N)
-(O) edge node[above]{$o_4$} (N);
-\end{tikzpicture}
-\]
-then as $\lCsp(\A)$ is a symmetric monoidal double category, the following pentagon of underlying cospans and maps of cospans commutes:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$((M_1 \otimes M_2) \otimes M_3) \otimes M_4$};
-\node (B) at (2.25,1) {$(M_1 \otimes M_2) \otimes (M_3 \otimes M_4)$};
-\node (C) at (4.5,0) {$M_1 \otimes (M_2 \otimes (M_3 \otimes M_4))$};
-\node (D) at (.75,-1.5) {$(M_1 \otimes (M_2 \otimes M_3)) \otimes M_4$};
-\node (E) at (3.75,-1.5) {$M_1 \otimes ((M_2 \otimes M_3) \otimes M_4)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$a$} (B)
-(B) edge node[above]{$a$} (C)
-(A) edge node[left]{$a \otimes 1$} (D)
-(D) edge node[above]{$a$} (E)
-(E) edge node[right]{$1 \otimes a$} (C);
-\end{tikzpicture}
-\]
-as well as the following pentagon of corresponding decorations in the category $F(m_1 +(m_2 +(m_3+m_4)))$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (-.5,0) {$F(aa)(((x_1+x_2)+x_3)+x_4) $};
-\node (B) at (2.25,1) {$F(a)((x_1+x_2)+(x_3+x_4))$};
-\node (C) at (5,0) {$x_1+(x_2+(x_3+x_4))$};
-\node (D) at (-.5,-1) {$F((1 \otimes a)a)((x_1+(x_2+x_3))+x_4) $};
-\node (E) at (5,-1) {$F(1 \otimes a)(x_1+((x_2+x_3)+x_4)) $};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$F(a)(\tau_a)$} (B)
-(B) edge node[above]{$\tau_a$} (C)
-(A) edge node[left]{$F((1 \otimes a)a)(\tau_{a \otimes 1})$} (D)
-(D) edge node[above]{$F(1 \otimes a)(\tau_a)$} (E)
-(E) edge node[right]{$\tau_{1 \otimes a}$} (C);
-\end{tikzpicture}
-\]
-since $$F(aa)(((x_1+x_2)+x_3)+x_4)=F((1 \otimes a)a(a \otimes 1))(((x_1+x_2)+x_3)+x_4)$$ as the corresponding pentagon in the symmetric monoidal category $(\A,+,0)$ commutes, and then appliying the pseudofunctor $F$ to said pentagon yields a commutative pentagon in $\Cat$.
-
-Similarly, if we denote the left and right unitors as $\lambda$ and $\rho$, respectively, then the following triangle of cospans and underlying maps of cospans commutes:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$(M_1 \otimes 0) \otimes M_2$};
-\node (B) at (2.25,1) {$M_1 \otimes M_2$};
-\node (C) at (4.5,0) {$M_1 \otimes (0 \otimes M_2)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$\rho \otimes 1$} (B)
-(C) edge node[above]{$1 \otimes \lambda$} (B)
-(A) edge node[above]{$a$} (C);
-\end{tikzpicture}
-\]
-as well as the following triangle of corresponding decorations in the category $F(m_1+m_2)$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$F(\rho \otimes 1)((x_1+0)+x_2)$};
-\node (B) at (2.25,1) {$x_1+x_2$};
-\node (C) at (4.5,0) {$F(1 \otimes \lambda)(x_1+(0+x_2)) $};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[left]{$\tau_{\rho \otimes 1}$} (B)
-(C) edge node[right]{$\tau_{1 \otimes \lambda}$} (B)
-(A) edge node[above]{$F(1 \otimes \lambda)(\tau_a)$} (C);
-\end{tikzpicture}
-\]
-since $$F(\rho \otimes 1)((x_1+0)+x_2)=F((1 \otimes \lambda)a)((x_1+0)+x_2)$$ as the corresponding triangle in the symmetric monoidal category $(\A,+,0)$ commutes and applying the pseudofunctor $F$ to this commutative triangle results in a commutative triangle in $\Cat$.
-
-For a tensor product of objects $M_1 \otimes M_2$ in $F\lCsp_1$, the source and target structure functors $S,T \maps F\lCsp_1 \to F\lCsp_0$ satisfy the following equations: $$S(M_1 \otimes M_2)=S(M_1) \otimes S(M_2)$$ $$T(M_1 \otimes M_2)=T(M_1) \otimes T(M_2).$$
-For two objects $M_1$ and $M_2$ in $F\lCsp_1$, we have a braiding $\beta_{M_1,M_2} \maps M_1 \otimes M_2 \to M_2 \otimes M_1$ given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$a_1+a_2$};
-\node (A') at (0,-0.5) {$a_2+a_1$};
-\node (B) at (2,0.5) {$m_1+m_2$};
-\node (C) at (4,0.5) {$b_1+b_2$};
-\node (C') at (4,-0.5) {$b_2+b_1$};
-\node (D) at (2,-0.5) {$m_2+m_1$};
-\node (E) at (5.5,0.5) {$x_1+x_2 \in F(m_1+m_2)$};
-\node (F) at (5.5,-0.5) {$x_2+x_1 \in F(m_2+m_1)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i_1+i_2$} (B)
-(C) edge node[above]{$o_1+o_2$} (B)
-(A) edge node[left]{$\beta_{a_1,a_2}$} (A')
-(C) edge node[left]{$\beta_{b_1,b_2}$} (C')
-(A') edge node [above]{$i_2+i_1$} (D)
-(C') edge node [above]{$o_2+o_1$} (D)
-(B) edge node [left] {$\beta_{m_1,m_2}$} (D);
-\end{tikzpicture}
-\]
-$$\tau_{\beta_{M_1,M_2}} \maps F(\beta_{m_1,m_2})(x_1+x_2) \xrightarrow{\sim} x_2+x_1$$ where the vertical 1-morphisms are given by braidings in $(\A,+,0)$.
-This braiding makes the following triangle of underlying cospans commute:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$M_1 \otimes M_2$};
-\node (B) at (2.25,1) {$M_1 \otimes M_2$};
-\node (C) at (4.5,0) {$M_2 \otimes M_1$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$1$} (B)
-(C) edge node[above]{$\beta_{M_2,M_1}$} (B)
-(A) edge node[above]{$\beta_{M_1,M_2}$} (C);
-\end{tikzpicture}
-\]
-as well as the following diagram of corresponding decorations in the category $F(m_1+m_2)$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$x_1+x_2$};
-\node (B) at (2.25,1) {$x_1+x_2$};
-\node (C) at (4.5,0) {$F(\beta_{m_2,m_1})(x_2+x_1)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$1$} (B)
-(C) edge node[right]{$\tau_{\beta_{M_2,M_1}}$} (B)
-(A) edge node[above]{$F(\beta_{m_2,m_1})(\tau_{\beta_{M_1,M_2}})$} (C);
-\end{tikzpicture}
-\]
-since $F(\beta_{m_2,m_1} \beta_{m_1,m_2}) (x_1+x_2) = x_1+x_2$. Thus $F\lCsp_1$ is also symmetric monoidal.
-
-Next we derive the globular isomorphisms required in the definition of a symmetric monoidal double category relating horizontal composition and the tensor product.
-Given four horizontal 1-cells $M_1, M_2, N_1$ and $N_2$ respectively by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a$};
-\node (B) at (1,0) {$m_1$};
-\node (C) at (2,0) {$b$};
-\node (D) at (1,-0.5) {$x_1 \in F(m_1)$};
-\node (E) at (3,0) {$b$};
-\node (F) at (4,0) {$m_2$};
-\node (G) at (5,0) {$c$};
-\node (H) at (4,-0.5) {$x_2 \in F(m_2)$};
-\node (I) at (0,-1.5) {$a'$};
-\node (J) at (1,-1.5) {$n_1$};
-\node (K) at (2,-1.5) {$b'$};
-\node (L) at (1,-2) {$y_1 \in F(n_1)$};
-\node (M) at (3,-1.5) {$b'$};
-\node (N) at (4,-1.5) {$n_2$};
-\node (O) at (5,-1.5) {$c'$};
-\node (P) at (4,-2) {$y_2 \in F(n_2)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i_1$} (B)
-(C) edge node[above]{$o_1$} (B)
-(E) edge node[above]{$i_2$} (F)
-(G) edge node[above]{$o_2$} (F)
-(I) edge node[above]{$i_1'$} (J)
-(K) edge node[above]{$o_1'$} (J)
-(M) edge node[above]{$i_2'$} (N)
-(O) edge node[above]{$o_2'$} (N);
-\end{tikzpicture}
-\]
-we have that $(M_1 \otimes N_1) \odot (M_2 \otimes N_2)$ is given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a+a'$};
-\node (B) at (2.5,0) {$(m_1+n_1)+_{b+b'}(m_2+n_2)$};
-\node (C) at (5,0) {$c+c'$};
-\node (D) at (2.5,-0.5) {$(x_1+y_1)\odot(x_2+y_2) \in F((m_1+n_1)+_{b+b'}(m_2+n_2))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$j \psi(i_1+i_1')$} (B)
-(C) edge node[above]{$j \psi(o_2 + o_2')$} (B);
-\end{tikzpicture}
-\]
-where the decoration $(x_1+y_1) \odot (x_2+y_2) \in F((m_1+n_1)+_{b+b'}(m_2+n_2))$ is given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$1$};
-\node (B) at (0,-1) {$1 \times 1$};
-\node (C) at (0,-2) {$(1 \times 1) \times (1 \times 1)$};
-\node (D) at (0,-3) {$(F(m_1) \times F(n_1)) \times (F(m_2) \times F(n_2))$};
-\node (E) at (0,-4) {$F(m_1+n_1) \times F(m_2+n_2)$};
-\node (F) at (0,-5) {$F((m_1+n_1)+(m_2+n_2))$};
-\node (G) at (0,-6) {$F((m_1+n_1)+_{b+b'}(m_2+n_2))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[left]{$\lambda^{-1}$} (B)
-(B) edge node[left]{$\lambda^{-1} \times \lambda^{-1}$} (C)
-(C) edge node[left]{$(x_1 \times y_1) \times (x_2 \times y_2)$} (D)
-(D) edge node[left]{$\phi_{m_1,n_1} \times \phi_{m_2,n_2}$} (E)
-(E) edge node[left]{$\phi_{m_1+n_1,m_2+n_2}$} (F)
-(F) edge node[left]{$F(j_{m_1+n_1,m_2+n_2})$} (G);
-\end{tikzpicture}
-\]
-and $(M_1 \odot M_2) \otimes (N_1 \odot N_2)$ is given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a+a'$};
-\node (B) at (2.5,0) {$(m_1+_{b} m_2) + (n_1 +_{b'} n_2)$};
-\node (C) at (5,0) {$c+c'$};
-\node (D) at (2.5,-0.5) {$(x_1 \odot x_2) + (y_1 \odot y_2) \in F((m_1+_{b}m_2)+(n_1+_{b'}n_2))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$(j \psi i_1)+(j \psi i_1')$} (B)
-(C) edge node[above]{$(j \psi o_2)+(j \psi o_2')$} (B);
-\end{tikzpicture}
-\]
-where the decoration $(x_1 \odot x_2) + (y_1 \odot y_2) \in F((m_1+_{b}m_2)+(n_1+_{b'}n_2))$ is given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$1$};
-\node (B) at (0,-1) {$1 \times 1$};
-\node (C) at (0,-2) {$(1 \times 1) \times (1 \times 1)$};
-\node (D) at (0,-3) {$(F(m_1) \times F(m_2)) \times (F(n_1) \times F(n_2))$};
-\node (E) at (0,-4) {$F(m_1+m_2) \times F(n_1+n_2)$};
-\node (F) at (0,-5) {$F(m_1+_{b}m_2) \times F(n_1+_{b'}n_2)$};
-\node (G) at (0,-6) {$F((m_1+_{b}m_2)+(n_1+_{b'}n_2))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[left]{$\lambda^{-1}$} (B)
-(B) edge node[left]{$\lambda^{-1} \times \lambda^{-1}$} (C)
-(C) edge node[left]{$(x_1 \times x_2) \times (y_1 \times y_2)$} (D)
-(D) edge node[left]{$\phi_{m_1,m_2} \times \phi_{n_1,n_2}$} (E)
-(E) edge node[left]{$F(j_{m_1,m_2}) \times F(j_{n_1,n_2})$} (F)
-(F) edge node[left]{$\phi_{m_1+_{b}m_2,n_1+_{b'}n_2}$} (G);
-\end{tikzpicture}
-\]
-and where $\psi$ and $j$ are the natural maps into a coproduct and from a coproduct into a pushout, respectively.
-We then get a globular 2-morphism $$\chi \maps (M_1 \otimes N_1) \odot (M_2 \otimes N_2) \to (M_1 \odot M_2) \otimes (N_1 \odot N_2)$$ given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$a+a'$};
-\node (A') at (0,-0.5) {$a+a'$};
-\node (B) at (2.5,0.5) {$(m_1+n_1)+_{b+b'}(m_2+n_2)$};
-\node (C) at (5,0.5) {$c+c'$};
-\node (C') at (5,-0.5) {$c+c'$};
-\node (D) at (2.5,-0.5) {$(m_1+_{b}m_2)+(n_1+_{b'}n_2)$};
-\node (E) at (2.5,1) {$(x_1+y_1) \odot (x_2+y_2) \in F((m_1+n_1)+_{b+b'}(m_2+n_2))$};
-\node (F) at (2.5,-1) {$(x_1 \odot x_2)+(y_1 \odot y_2) \in F((m_1+_{b}m_2)+(n_1+_{b'}n_2))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$j \psi (i_1+i_1')$} (B)
-(C) edge node[above]{$j \psi (o_2 + o_2')$} (B)
-(A) edge node[left]{$1$} (A')
-(C) edge node[right]{$1$} (C')
-(A') edge node [above]{$(j \psi i_1')+(j \psi i_1)$} (D)
-(C') edge node [above]{$(j \psi o_2)+(j \psi o_2')$} (D)
-(B) edge node [left] {$\hat{\chi}$} (D);
-\end{tikzpicture}
-\]
-$$\tau_{\hat{\chi}} \maps F(\hat{\chi})((x_1+y_1)\odot(x_2+y_2)) \to (x_1 \odot x_2)+(y_1 \odot y_2)$$
-where $\hat{\chi}$ is the universal map between two colimits of the same diagram.
-For two objects $a,b \in \mathrm{A}$, $U_{a+b}$ is given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a+b$};
-\node (B) at (1,0) {$a+b$};
-\node (C) at (2,0) {$a+b$};
-\node (D) at (1,-0.5) {$!_{a+b} \in F(a+b)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$1_{a+b}$} (B)
-(C) edge node[above]{$1_{a+b}$} (B);
-\end{tikzpicture}
-\]
-where $$!_{a+b} \maps 1 \xrightarrow{\phi} F(0) \xrightarrow{F(!_{a+b})}  F(a+b).$$
-Similarly, we have $U_a$ and $U_b$ given respectively by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a$};
-\node (B) at (1,0) {$a$};
-\node (C) at (2,0) {$a$};
-\node (D) at (1,-0.5) {$!_a \in F(a)$};
-\node (E) at (3,0) {$b$};
-\node (F) at (4,0) {$b$};
-\node (G) at (5,0) {$b$};
-\node (H) at (4,-0.5) {$!_b \in F(b)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$1_a$} (B)
-(C) edge node[above]{$1_a$} (B)
-(E) edge node[above]{$1_b$} (F)
-(G) edge node[above]{$1_b$} (F);
-\end{tikzpicture}
-\]
-and then $U_a + U_b$ is given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a+b$};
-\node (B) at (1.25,0) {$a+b$};
-\node (C) at (2.5,0) {$a+b$};
-\node (D) at (1.25,-0.5) {$!_a + !_b \in F(a+b)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$1_a + 1_b$} (B)
-(C) edge node[above]{$1_a + 1_b$} (B);
-\end{tikzpicture}
-\]
-where
-$$!_a + !_b \maps 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{\phi \times \phi} F(0) \times F(0) \xrightarrow{F(!_a) \times F(!_b)} F(a) \times F(b) \xrightarrow{\phi_{a,b}} F(a+b).$$
-We then have another globular isomorphism $$\mu_{a,b} \maps U_{a+b} \to U_a + U_b$$ given by the identity 2-morphism:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$a+b$};
-\node (A') at (0,-0.5) {$a+b$};
-\node (B) at (2,0.5) {$a+b$};
-\node (C) at (4,0.5) {$a+b$};
-\node (C') at (4,-0.5) {$a+b$};
-\node (D) at (2,-0.5) {$a+b$};
-\node (E) at (5.5,0.5) {$!_{a+b} \in F(a+b)$};
-\node (F) at (5.5,-0.5) {$!_a + !_b \in F(a+b)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$1_{a+b}$} (B)
-(C) edge node[above]{$1_{a+b}$} (B)
-(A) edge node[left]{$1$} (A')
-(C) edge node[right]{$1$} (C')
-(A') edge node [above]{$1_a + 1_b$} (D)
-(C') edge node [above]{$1_a + 1_b$} (D)
-(B) edge node [left] {$1$} (D);
-\end{tikzpicture}
-\]
-$$\tau_{a,b} \maps !_{a+b} \xrightarrow{\sim} !_a + !_b$$
-where $!_{a+b}$ and $!_a + !_b$ are both initial objects in $F(a+b)$, hence isomorphic.
-
-There are a fair amount of coherence diagrams to verify, many of which are similar in flavor and make use of the two above globular ismorphisms.
-We check a few to give a sense of what these are like.
-For example,  given horizontal 1-cells $M_i,N_i,P_i$ for $i=1,2$, the following commutative diagram expresses the associativity isomorphism as a transformation of double categories.
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$((M_1 \otimes N_1) \otimes P_1) \odot ((M_2 \otimes N_2) \otimes P_2)$};
-\node (A') at (4.5,0.5) {$(M_1 \otimes (N_1 \otimes P_1)) \odot (M_2 \otimes (N_2 \otimes P_2))$};
-\node (B) at (0,-0.25) {$((M_1 \otimes N_1) \odot (M_2 \otimes N_2)) \otimes (P_1 \odot P_2)$};
-\node (C) at (4.5,-0.25) {$(M_1 \odot M_2) \otimes ((N_1 \otimes P_1) \odot (N_2 \otimes P_2))$};
-\node (C') at (0,-1) {$((M_1 \odot M_2) \otimes (N_1 \odot N_2)) \otimes (P_1 \odot P_2)$};
-\node (D) at (4.5,-1) {$(M_1 \odot M_2) \otimes ((N_1 \odot N_2) \otimes (P_1 \odot P_2))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$a \odot a$} (A')
-(A) edge node[left]{$\chi$} (B)
-(A') edge node[right]{$\chi$} (C)
-(B) edge node[left]{$\chi \otimes 1$} (C')
-(C) edge node [right] {$1 \otimes \chi$} (D)
-(C') edge node [above] {$a$} (D);
-\end{tikzpicture}
-\]
-Here, $a$ is the associator of $F\lCsp_1$ and $\chi$ is the first globular isomorphism above.
-To see that this diagram does indeed commute, we first consider this diagram with respect to only the underlying cospans of each horizontal 1-cell.
-For notation:
-	\[
-		\begin{tikzpicture}
-			\node (k) at (0,0) {$a$};
-			\node (l) at (1,0) {$m_1$};
-			\node (m) at (2,0) {$b$};
-			\node (M1) at (-1,0) {$M_1 =$};
-			\node (N1) at (3,0) {$N_1 =$};
-			\node (q) at (4,0) {$a'$};
-			\node (r) at (5,0) {$n_1$};
-			\node (s) at (6,0) {$b'$};
-			\node (P1) at (7,0) {$P_1 =$};
-			\node (v) at (8,0) {$a''$};
-			\node (w) at (9,0) {$p_1$};
-			\node (x) at (10,0) {$b''$};
-			\node (m2) at (0,-1.5) {$b$};
-			\node (n) at (1,-1.5) {$m_2$};
-			\node (p) at (2,-1.5) {$c$};
-			\node (M2) at (-1,-1.5) {$M_2 =$};
-			\node (N2) at (3,-1.5) {$N_2 =$};
-			\node (s2) at (4,-1.5) {$b'$};
-			\node (t) at (5,-1.5) {$n_2$};
-			\node (u) at (6,-1.5) {$c'$};
-			\node (P2) at (7,-1.5) {$P_2 =$};
-			\node (x2) at (8,-1.5) {$b''$};
-			\node (y) at (9,-1.5) {$p_2$};
-			\node (z) at (10,-1.5) {$c''$};
-\node (dM1) at (1,-0.5) {$x_1 \in F(m_1)$};
-\node (dM2) at (1,-2) {$x_2 \in F(m_2)$};
-\node (dN1) at (5,-0.5) {$y_1 \in F(n_1)$};
-\node (dN2) at (5,-2) {$y_2 \in F(n_2)$};
-\node (dP1) at (9,-0.5) {$z_1 \in F(p_1)$};
-\node (dP2) at (9,-2) {$z_2 \in F(p_2)$};
-			\path[->,font=\scriptsize,>=angle 90]
-			(k) edge node[above]{$$} (l)
-			(m) edge node[above]{$$} (l)
-			(q) edge node[above]{$$} (r)
-			(s) edge node[above]{$$} (r)
-			(v) edge node[above]{$$} (w)
-			(x) edge node[above]{$$} (w)
-			(m2) edge node[above]{$$} (n)
-			(p) edge node[above]{$$} (n)
-			(s2) edge node[above]{$$} (t)
-			(u) edge node[above]{$$} (t)
-			(x2) edge node[above]{$$} (y)
-			(z) edge node[above]{$$} (y);
-		\end{tikzpicture}
-	\]
-The above diagram then becomes:
-\[
-		\begin{tikzpicture}
-			\node (a) at (-4,0) {$(a+a')+a''$};
-			\node (b) at (1,0) {$((m_1+n_1)+p_1) +_{((b+b')+b'')}((m_2+n_2)+p_2)$};
-			\node (c) at (6,0) {$(c+c')+c''$};
-			\node (a2) at (-4,1) {$a+(a'+a'')$};
-			\node (b2) at (1,1) {$(m_1+(n_1+p_1)) +_{(b+(b'+b''))}(m_2+(n_2+p_2))$};
-			\node (c2) at (6,1) {$c+(c'+c'')$};
-                                \node (a3) at (-4,2) {$a+(a'+a'')$};
-			\node (b3) at (1,2) {$(m_1+_b m_2)+((n_1+p_1)+_{(b'+b'')}(n_2+p_2))$};
-			\node (c3) at (6,2) {$c+(c'+c'')$};
-                                \node (a4) at (-4,3) {$a+(a'+a'')$};
-			\node (b4) at (1,3) {$(m_1+_b m_2)+((n_1+_{b'} n_2)+(p_1+_{b''} p_2))$};
-			\node (c4) at (6,3) {$c+(c'+c'')$};
-                                \node (a5) at (-4,-1) {$(a+a')+a''$};
-			\node (b5) at (1,-1) {$((m_1+n_1)+_{(b+b')}(m_2+n_2))+(p_1+_{b''} p_2)$};
-			\node (c5) at (6,-1) {$(c+c')+c''$};
-                                \node (a6) at (-4,-2) {$(a+a')+a''$};
-			\node (b6) at (1,-2) {$((m_1+_b m_2)+(n_1+_{b'} n_2))+(p_1+_{b''} p_2)$};
-			\node (c6) at (6,-2) {$(c+c')+c''$};
-                                \node (a7) at (-4,-3) {$a+(a'+a'')$};
-			\node (b7) at (1,-3) {$(m_1+_b m_2)+((n_1+_{b'} n_2)+(p_1+_{b''} p_2))$};
-			\node (c7) at (6,-3) {$c+(c'+c'')$};
-			\path[->,font=\scriptsize,>=angle 90]
-			(a) edge node[above]{$$} (b)
-			(c) edge node[above]{$$} (b)
-                                (a2) edge node[above]{$$} (b2)
-			(c2) edge node[above]{$$} (b2)
-                                (a) edge node[left]{$$} (a2)
-                                (b) edge node[left]{$a \odot a$} (b2)
-(b) edge node[right]{$\tau_1$} (b2)
-			(c) edge node[above]{$$} (c2)
-                                (a3) edge node[above]{$$} (b3)
-			(c3) edge node[above]{$$} (b3)
-                                (a2) edge node[above]{$$} (a3)
-                                (b2) edge node[left]{$\chi$} (b3)
-(b2) edge node[right]{$\tau_2$} (b3)
-			(c2) edge node[above]{$$} (c3)
-                                (a4) edge node[above]{$$} (b4)
-			(c4) edge node[above]{$$} (b4)
-                                (a3) edge node[above]{$$} (a4)
-                                (b3) edge node[left]{$1 \otimes \chi$} (b4)
-(b3) edge node[right]{$\tau_3$} (b4)
-			(c3) edge node[above]{$$} (c4)
-                                (a5) edge node[above]{$$} (b5)
-			(c5) edge node[above]{$$} (b5)
-                                (a) edge node[above]{$$} (a5)
-                                (b) edge node[left]{$\chi$} (b5)
-(b) edge node[right]{$\tau_4$} (b5)
-			(c) edge node[above]{$$} (c5)
-                                (a6) edge node[above]{$$} (b6)
-			(c6) edge node[above]{$$} (b6)
-                                (a5) edge node[above]{$$} (a6)
-                                (b5) edge node[left]{$\chi \otimes 1$} (b6)
- (b5) edge node[right]{$\tau_5$} (b6)
-			(c5) edge node[above]{$$} (c6)
-                                (a7) edge node[above]{$$} (b7)
-			(c7) edge node[above]{$$} (b7)
-                                (a6) edge node[above]{$$} (a7)
-                                (b6) edge node[left]{$a$} (b7)
-(b6) edge node[right]{$\tau_6$} (b7)
-			(c6) edge node[above]{$$} (c7);
-		\end{tikzpicture}
-	\]
-Here all of the vertical 1-morphisms on the left and right are associators or identities, the middle vertical 1-morphisms labeled on the left are the 2-morphisms from the previous commutative diagram, and the horizontal vertical 1-morphisms pointing towards the middle are natural maps into each colimit, all of which are naturally isomorphic to each other as all the middle objects are colimits of the same diagram, namely the previous collection of cospans, taken in various ways.
-The above diagram of maps of cospans can then be visualized as a hexagonal prism in which all the faces commute by identifying the top and the bottom as the same.
-As for the morphisms of decorations, which are labeled on the right of the interior vertical 1-morphisms, each isomorphism $\tau_n$ goes from the domain under the image of the functor $F$ applied to natural isomorphism adjacent to it to the codomain as written, meaning that, for example: $$\tau_1 \maps F(a \odot a)(((x_1+y_1)+z_1) \odot ((x_2+y_2)+z_2)) \to (x_1+(y_1+z_1)) \odot (x_2+(y_2+z_2)).$$  The following diagram commutes in the category $F((m_1+_b m_2) + ((n_1+_{b'} n_2) + (p_1+_{b''} p_2)))$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$F( a (\chi \otimes 1)\chi)(((x_1+y_1)+z_1) \odot ((x_2+y_2)+z_2))$};
-\node (A') at (6,0.5) {$F((1 \otimes \chi) \chi)((x_1+(y_1+z_1)) \odot (x_2+(y_2+z_2)))$};
-\node (B) at (0,-0.5) {$F(a(\chi  \otimes 1))(((x_1+y_1) \odot (x_2+y_2)) + (z_1 \odot z_2))$};
-\node (C) at (6,-0.5) {$F(1 \otimes \chi)((x_1 \odot x_2) + ((y_1+z_1) \odot (y_2+z_2)))$};
-\node (C') at (0,-1.5) {$F(a)(((x_1 \odot x_2)+(y_1 \odot y_2)) + (z_1 \odot z_2))$};
-\node (D) at (6,-1.5) {$(x_1 \odot x_2) + ((y_1 \odot y_2) + (z_1 \odot z_2))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$F((1 \otimes \chi) \chi)(\tau_1)$} (A')
-(A) edge node[left]{$F(a(\chi \otimes 1))(\tau_4)$} (B)
-(A') edge node[right]{$F(1 \otimes \chi)(\tau_2)$} (C)
-(B) edge node[left]{$F(a)(\tau_5)$} (C')
-(C) edge node [right] {$\tau_3$} (D)
-(C') edge node [above] {$\tau_6$} (D);
-\end{tikzpicture}
-\]
-since $$F(a(\chi \otimes 1)\chi)(((x_1+y_1)+z_1) \odot ((x_2+y_2)+z_2)) = F((1 \otimes \chi) \chi (a \odot a))(((x_1+y_1)+z_1) \odot ((x_2+y_2)+z_2))$$
-as the above underlying diagram of maps of cospans commutes and then applying the pseudofunctor $F$ yields a commutative diagram in $\Cat$.
-
-Another requirement for a double category to be symmetric monoidal is that the braiding $$\beta_{ ( \_, \_ ) } \maps F\lCsp_1 \times F\lCsp_1 \to F\lCsp_1 \times F\lCsp_1$$ be a transformation of double categories, and one of the diagrams that is required to commute is the following:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$(M_1 \odot M_2) \otimes (N_1 \odot N_2)$};
-\node (B) at (3,0) {$(N_1 \odot N_2) \otimes (M_1 \odot M_2)$};
-\node (C) at (0,-.75) {$(M_1 \otimes N_1) \odot (M_2 \otimes N_2)$};
-\node (D) at (3,-.75) {$(N_1 \otimes M_1) \odot (N_2 \otimes M_2)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$\beta$} (B)
-(B) edge node[right]{$\chi$} (D)
-(A) edge node[left]{$\chi$} (C)
-(C) edge node[above]{$\beta \odot \beta$} (D);
-\end{tikzpicture}
-\]
-Using the same notation as the previous coherence diagram, the diagram for the underlying maps of cospans becomes:
-\[
-		\begin{tikzpicture}
-			\node (a) at (-4,0) {$a+a'$};
-			\node (b) at (1,0) {$(m_1+_b m_2) + (n_1+_{b'} n_2)$};
-			\node (c) at (6,0) {$c+c'$};
-			\node (a2) at (-4,1) {$a'+a$};
-			\node (b2) at (1,1) {$(n_1 +_{b'} n_2) + (m_1 +_b m_2)$};
-			\node (c2) at (6,1) {$c'+c$};
-                                \node (a3) at (-4,2) {$a'+a$};
-			\node (b3) at (1,2) {$(n_1+m_1) +_{(b'+b)} (n_2+m_2)$};
-			\node (c3) at (6,2) {$c'+c$};
-                                \node (a5) at (-4,-1) {$a+a'$};
-			\node (b5) at (1,-1) {$(m_1+n_1) +_{(b+b')} (m_2+n_2)$};
-			\node (c5) at (6,-1) {$c+c'$};
-                                \node (a6) at (-4,-2) {$a'+a$};
-			\node (b6) at (1,-2) {$(n_1+m_1) +_{(b'+b)} (n_2+m_2)$};
-			\node (c6) at (6,-2) {$c'+c$};
-			\path[->,font=\scriptsize,>=angle 90]
-			(a) edge node[above]{$$} (b)
-			(c) edge node[above]{$$} (b)
-                                (a2) edge node[above]{$$} (b2)
-			(c2) edge node[above]{$$} (b2)
-                                (a) edge node[above]{$$} (a2)
-                                (b) edge node[left]{$\beta$} (b2)
-(b) edge node[right]{$\tau_1$} (b2)
-			(c) edge node[above]{$$} (c2)
-                                (a3) edge node[above]{$$} (b3)
-			(c3) edge node[above]{$$} (b3)
-                                (a2) edge node[above]{$$} (a3)
-                                (b2) edge node[left]{$\chi$} (b3)
-(b2) edge node[right]{$\tau_2$} (b3)
-			(c2) edge node[above]{$$} (c3)
-                                (a5) edge node[above]{$$} (b5)
-			(c5) edge node[above]{$$} (b5)
-                                (a) edge node[above]{$$} (a5)
-                                (b) edge node[left]{$\chi$} (b5)
-(b) edge node[right]{$\tau_4$} (b5)
-			(c) edge node[above]{$$} (c5)
-                                (a6) edge node[above]{$$} (b6)
-			(c6) edge node[above]{$$} (b6)
-                                (a5) edge node[above]{$$} (a6)
-                                (b5) edge node[left]{$\beta \odot \beta$} (b6)
- (b5) edge node[right]{$\tau_5$} (b6)
-			(c5) edge node[above]{$$} (c6);
-		\end{tikzpicture}
-	\]
-All the comments about the previous underlying coherence diagram of maps of cospans apply to this one.
-As for the decorations, the following diagram commutes in the category $F((y_1+x_1)+_{(b'+b)}(y_2+x_2))$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$F(\chi \beta)((x_1 \odot x_2)+(y_1 \odot y_2))$};
-\node (B) at (4,0) {$F(\chi)((y_1 \odot y_2)+(x_1 \odot x_2))$};
-\node (C) at (0,-1) {$F(\beta \odot \beta)((x_1+y_1) \odot (x_2 + y_2))$};
-\node (D) at (4,-1) {$(y_1+x_1) \odot (y_2+x_2)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$F(\chi)(\tau_1)$} (B)
-(B) edge node[right]{$\tau_2$} (D)
-(A) edge node[left]{$F(\beta \odot \beta)(\tau_3)$} (C)
-(C) edge node[above]{$\tau_4$} (D);
-\end{tikzpicture}
-\]
-since $$F(\chi \beta)((x_1 \odot x_2)+(y_1 \odot y_2)) = F((\beta \odot \beta)\chi)((x_1 \odot x_2)+(y_1 \odot y_2))$$
-as the above underlying diagram of maps of cospans commutes and then applying the pseudofunctor $F$ to this diagram yields a commutative diagram in $\Cat$.
-The other diagrams are shown to commute similarly.
-\end{comment}
 \end{proof}
@@
 Explicitly, they consist of two pairs of morphisms
-%%% Not sure what v is in the above line unless you mean x?
-%%% I mean an arbitrary object in the Grothendieck category. I just made it a pair to be clearer, is it OK? Erase these comments whenever you want.
-%%% Oh, gotchya'
 \begin{equation}\label{eq:scsphor1cell}
@@
 whereas a 2-morphism of $L$-structured cospans as above is mapped to the underlying map of cospans in $\A$
-%%% We should call these "cospan 2-morphism"s maps of cospans to be consistent with previous work
-%%% Alright!
 \begin{displaymath}
@@
 \subsection{Double categories}\label{sec:doublecats}
-%%% Christina: Kenny, would you mind cleaning this section up to? I don't believe we need the full fledged definitions here by the way.
-%%% Kenny: Sure!
 
@@
 Following the notation of Shulman, objects of $\lD_0$ are called \define{objects}
-%%% I'm tempted to delete 0-cells since we never use that term anywhere in any paper, but I do like the idea that "n+1 morphisms go between n cells".
-%%% Christina: I am up for deletion of 0-cells
-%%% Kenny: Okay, I deleted it.
 and morphisms of $\lD_0$ are called \define{vertical 1-morphisms}.

### 2020-11-24 cospans.tex
filled in some details about lax mon pseudofunctor

@@
 A \define{braided} monoidal bicategory comes with a pseudonatural equivalence $\beta_{a,b}\maps a\ot b\to b\ot a$ and appropriate invertible modifications; it is \define{sylleptic} if there is an appropriate invertible modification $1_{a\ot b}\Rrightarrow\beta_{b,a}\circ\beta_{a,b}$ and it is \define{symmetric} if one further axiom holds.
-A \define{lax monoidal} pseudofunctor between monoidal bicategories $F\maps\bA\to\bB$ is a pseudofunctor equipped with pseudonatural transformations with components $\phi_{a,b}\maps Fa\otimes Fb\to F(a\otimes b)$ and $\phi_0\maps I\to FI$ along with coherent invertible modifications for associativity and unitality.
+
+A \define{lax monoidal} pseudofunctor (called \emph{weak monoidal} homomorphism in earlier references) between monoidal bicategories $F\maps\bA\to\bB$ is a pseudofunctor equipped with pseudonatural transformations with components $\phi_{a,b}\maps Fa\otimes Fb\to F(a\otimes b)$ and $\phi_0\maps I\to FI$ along with invertible modifications for associativity and unitality with components
+\begin{equation}\label{eq:omega}
+\begin{tikzcd}[column sep=.8in, row sep=.3in]
+(F a\ot F b)\ot F c\ar[ddr,phantom,"{\cong}"]\ar[r,"{\phi_{a,b}\ot1}"]\ar[d,sloped,"\sim"'] & F (a\ot b)\ot F 
+c\ar[d,"{\phi_{a\ot b,c}}"] \\
+F a\ot( F b\ot F c)\ar[d,"{1\ot\phi_{b,c}}"'] & 
+F ((a\ot b)\ot c)\ar[d,sloped,"\sim"] \\
+F a\ot F(b\ot c)\ar[r,"{\phi_{a,b\ot c}}"'] &
+F (a\ot(b\ot c))
+\end{tikzcd}
+\end{equation}
+\begin{displaymath}
+\begin{tikzcd}[column sep=.3in,row sep=.3in]
+F a\ar[r,"\sim"]\ar[drr,sloped,"\sim"'] & F a\otimes I\ar[r,"1\otimes\mu_0"]\ar[dr,phantom,"\cong"] & F 
+a\otimes F I\ar[d,"\mu_{a,I}"] \\
+&& F(a\ot I)
+\end{tikzcd}\qquad
+\begin{tikzcd}[column sep=.3in,row sep=.3in]
+F a\ar[r,"\sim"]\ar[drr,sloped,"\sim"'] & I\otimes F a \ar[r,"\mu_0\otimes1"]\ar[dr,phantom,"\cong"] & F 
+I\otimes F a\ar[d,"\mu_{I,a}"] \\
+&& F(I\ot a)
+\end{tikzcd}
+\end{displaymath}
+subject to coherence conditions. In particular, pseudonaturality of the monoidal structure means that it comes with isomorphisms (natural in $f,g$)
+\begin{equation}
+\begin{tikzcd}[column sep=.5in]
+ Fa\ot Fb\ar[r,"Ff\ot Fg"]\ar[d,"\phi_{a,b}"']\ar[dr,phantom,"\cong"] & Fa'\ot Fb'\ar[d,"\phi_{a',b'}"] \\
+ F(a\ot b)\ar[r,"F(f\ot g)"'] & F(a'\ot b')
+ \end{tikzcd}
+\end{equation}
 A \define{braided lax monoidal} pseudofunctor between braided monoidal bicategories comes with an appropriate invertible modification with components $F(\beta_{a,b})\circ \phi_{a,b}\cong\phi_{b,a}\circ \beta_{Fa,Fb}$; a \define{sylleptic lax monoidal} pseudofunctor satisfies one extra condition and a \define{symmetric lax monoidal} pseudofunctor between symmetric monoidal bicategories is just a sylleptic one.

### 2020-11-24 cospans.tex
Added a few definitions in A.3

@@
 Given double categories $\lA$ and $\lX$, a \define{(pseudo) double functor} $\lF \colon\lA \to \lX$ consists of:
-\begin{enumerate}
+\begin{itemize}
 \item{functors $\lF_0 \colon \lA_0 \to \lX_0$ and $\lF_1 \colon \lA_1 \to \lX_1$ such that $S \lF_1 = \lF_0 S$ and $T \lF_1 = \lF_0 T$, and}
@@
 The components of each of these natural transformations are globular isomorphisms which satisfy the usual coherence axioms for a monoidal functor.}
-\end{enumerate}
+\end{itemize}
 \end{defn}
@@
 \begin{defn}
-Given double functors $(\lF,\phi),(\mathbb{G},\psi) \colon \lA \to \lX$, a \define{double transformation} $\alpha \colon \lF \Rightarrow \mathbb{G}$ consists of transformations $\alpha_0 \colon \lF_0 \Rightarrow \mathbb{G}_0$ and $\alpha_1 \colon \lF_1 \Rightarrow \mathbb{G}_1$ such that $S(\alpha_M) = \alpha_{S(M)}$ and $T(\alpha_M) = \alpha_{T(M)}$, and for two composable horizontal 1-cells $M$ and $N$ of $\lA$, $\alpha \circ \phi_{M,N} = \psi \circ (\alpha_M \odot \alpha_N)$ and $\alpha \circ \phi_a = \psi_a \circ \alpha$.
+Given double functors $(\lF,\phi),(\mathbb{G},\psi) \colon \lA \to \lX$, a \define{double natural transformation} $\alpha \colon \lF \Rightarrow \mathbb{G}$ consists of natural transformations $\alpha_0 \colon \lF_0 \Rightarrow \mathbb{G}_0$ and $\alpha_1 \colon \lF_1 \Rightarrow \mathbb{G}_1$ such that:
+\begin{itemize}
+\item{$S(\alpha_M) = \alpha_{S(M)}$ and $T(\alpha_M) = \alpha_{T(M)}$ for all horizontal 1-cells $M$ of $\lA$,}
+\item{$\alpha \circ \phi_{M,N} = \psi \circ (\alpha_M \odot \alpha_N)$ for all composable pairs $M$ and $N$ of horizontal 1-cells in $\lA$, and}
+\item{$\alpha \circ \phi_a = \psi_a \circ \alpha$ for all objects $a$ of $\lA$.}
+\end{itemize} 
+%$S(\alpha_M) = \alpha_{S(M)}$ and $T(\alpha_M) = \alpha_{T(M)}$, and for two composable horizontal 1-cells $M$ and $N$ of $\lA$, $\alpha \circ \phi_{M,N} = \psi \circ (\alpha_M \odot \alpha_N)$ and $\alpha \circ \phi_a = \psi_a \circ \alpha$.
+The double natural transformation $\alpha$ is a \define{double natural isomorphism} if both $\alpha_0$ and $\alpha_1$ are natural isomorphisms.
 \end{defn}
@@
 
-Formally, two strong double functors between two double categories form a \emph{double equivalence} if ...
+\begin{defn}
+Two pseudo double functors $\lF \colon \lA \to \lX$ and $\mathbb{G} \colon \lX \to \lA$ form a \define{double equivalence} if there exist double natural transformations $\mathbb{G} \lF \cong 1_\lA$ and $\lF \mathbb{G} \cong 1_\lX$.
+\end{defn}
 % FINISH THIS OR DISCARD IT!!!

### 2020-11-25 cospans.tex
a lot of changes in the appendix

@@
 % in LaTeX
-% 2020/11/23
+% 2020/11/24
 
@@
 Second, if $\A$ has finite colimits and $F \maps (\A,+) \to (\Cat,\times)$ is a symmetric lax monoidal pseudofunctor , a `decorated cospan' is a diagram in $\A$ of the form $a \rightarrow s \leftarrow b$ together with an object of $F(s)$.
-Generalizing the work of Fong, we show that in this situation there is a symmetric monoidal double category whose objects are those of $\A$ and whose horizontal 1-cells are structured cospans.
-We prove that under certain conditions these two consstructions are equivalent when we take $\X = \int F$ to be the Grothendieck category of $F$.
+Generalizing the work of Fong, we show that in this situation there is a symmetric monoidal double category whose objects are those of $\A$ and whose horizontal 1-cells are decorated cospans.
+We prove that under certain conditions these two constructions are equivalent when we take $\X = \int F$ to be the Grothendieck category of $F$.
 We illustrate these ideas with applications to electrical circuits, Petri nets, reaction networks and dynamical systems.
@@
 Briefly, a \define{monoidal} bicategory $\bA$ comes with a pseudofunctor $\otimes\maps\bA\times\bA\to\bA$ and a unit object $I$ that are associative and unital up to coherent equivalence.
-A \define{braided} monoidal bicategory comes with a pseudonatural equivalence $\beta_{a,b}\maps a\ot b\to b\ot a$ and appropriate invertible modifications; it is \define{sylleptic} if there is an appropriate invertible modification $1_{a\ot b}\Rrightarrow\beta_{b,a}\circ\beta_{a,b}$ and it is \define{symmetric} if one further axiom holds.
+.A \define{braided} monoidal bicategory also comes with a pseudonatural equivalence $\beta_{a,b}\maps a\ot b\to b\ot a$ and appropriate invertible modifications obeying certain equations; it is \define{sylleptic} if there is an invertible modification $1_{a\ot b}\Rrightarrow\beta_{b,a}\circ\beta_{a,b}$ its own equation, \define{symmetric} if one further axiom holds.
 
@@
         \end{displaymath}
+where $[\A,\Cat]_\pse$ is the 2-category of pseudofunctors from $\A$ to $\Cat$, pseudonatural transformations, and modifications.
 %        \item The above 2-equivalence extends to one between 2-categories of arbitrary-base fibrations and arbitrary-domain indexed categories
@@
 \end{thm}
+
+\begin{proof}  CITE A PROOF!!!  \end{proof}
 
@@
 
-Before formally defining `pseudo double category', it is helpful to have the following picture in mind. A pseudo double category $\lA$ has 2-morphisms shaped like:
-
+%We will denote both kinds of morphisms and horizontal 1-cells as a single arrow, namely `$\to$'???   Or should we put a ``tick'' in here?
+
+For double categories we follow the notation of our paper on structured cospans \cite{BC}, which in turn follows that of Shulman \cite{Shulman2010}.
+
+\begin{defn}\label{defn:double_category}
+A \define{double category} $\lD$ consists of a \define{category of objects}
+$\lD_0$, a \define{category of arrows} $\lD_1$, functors 
+\[    U\maps \lD_0 \to \lD_1, \; S,T \maps \lD_1 \to \lD_0 , \textrm{ and }
+   \odot \maps \lD_1 \times_{\lD_0} \lD_1 \to \lD_1\]
+such that 
+\[  S(U_{A})=A=T(U_{A}),  \quad S(M \odot N)=S(N), \quad T(M \odot N)=T(M), \]
+and natural isomorphisms called the \define{associator}
+\[ \alpha_{L,M,N} \maps (L \odot M) \odot N \to L \odot (M \odot N) , \]
+and \define{left and right unitors}
+\[		\lambda_N \maps U_{T(N)} \odot N \to N, \qquad
+     \rho_N \maps N \odot U_{S(N)} \to N \]
+such that $S(\alpha), S(\lambda), S(\rho), T(\alpha), T(\lambda)$ and $T(\rho)$ are all identities,
+such that the standard coherence laws hold: the pentagon identity for the 
+associator and the triangle identity for the left and right unitor.
+\end{defn}
+
+Objects of $\lD_0$ are called \define{objects} and morphisms of $\lD_0$ are called \define{vertical 1-morphisms}.
+Objects of $\lD_1$ are called \define{horizontal 1-cells} and morphisms of $\lD_1$ are called \define{2-morphisms}.
+We can draw a 2-morphism $a \maps M \to N$ with $S(a)=f,T(a)=g$ as follows:
 \[
@@
 \]
-We call $A, B, C$ and $D$ \define{objects}, $f$ and $g$ \define{vertical 1-morphisms}, $M$ and $N$ \define{horizontal 1-cells} and $a$ a \define{2-morphism}. 
-%Note that a vertical 1-morphism is a morphism between 0-cells and a 2-morphism is a morphism between horizontal 1-cells. 
-%We will denote both kinds of morphisms and horizontal 1-cells as a single arrow, namely `$\to$'???   Or should we put a ``tick'' in here?
-A 2-morphism where $f$ and $g$ are identities is called a \textbf{globular 2-morphism}.
-We call $M$ and $N$ the \define{horizontal source and target} of the 2-morphism $a$, respectively, and likewise we call $f$ and $g$ the \define{vertical source and target} of the 2-morphism $a$, respectively.
-Thus $_f \lA_g(M,N)$ denotes the set of 2-morphisms in $\lA$ with horizontal source and target $M$ and $N$ and vertical source and target $f$ and $g$.
-%We follow the notation of Shulman \cite{Shulman2008} with the following definitions.
-
-\begin{defn}\label{defn:double_category}
-A \define{(pseudo) double category} $\lA$ is a category object internal to the 2-category $\Cat$.
-\end{defn}
-
-\begin{comment}
-
-\begin{defn}\label{defn:double_category}
-A \textbf{(pseudo) double category} $\lD$ consists of a category of objects $\lD_0$ and a category of arrows $\lD_1$ with the following functors
-\begin{center}
-$U\maps \lD_0 \to \lD_1$\\
-$S,T \maps \lD_1 \rightrightarrows \lD_0$\\
-$\odot \maps \lD_1 \times_{\lD_0} \lD_1 \to \lD_1$ (where the pullback is taken over $\lD_1 \xrightarrow[]{T} \lD_0 \xleftarrow[]{S} \lD_1$) \\
-\end{center}
- such that \\
-\begin{center}
-$S(U_{A})=A=T(U_{A})$\\
-$S(M \odot N)=SN$\\
-$T(M \odot N)=TM$\\
-\end{center}
-equipped with natural isomorphisms
-\begin{center}
-
-$\alpha \maps (M \odot N) \odot P \xrightarrow{\sim} M \odot (N \odot P)$\\
-$\lambda \maps U_{B} \odot M \xrightarrow{\sim} M$\\
-$\rho \maps M \odot U_{A} \xrightarrow{\sim} M$
-
-\end{center}
-such that $S(\alpha), S(\lambda), S(\rho), T(\alpha), T(\lambda)$ and $T(\rho)$ are all identities and that the coherence axioms of a monoidal category are satisfied.
-Following the notation of Shulman, objects of $\lD_0$ are called \define{objects}
-and morphisms of $\lD_0$ are called \define{vertical 1-morphisms}.
-Objects of $\lD_1$ are called \define{horizontal 1-cells} and morphisms of $\lD_1$ are called \define{2-morphisms}.
-The morphisms of $\lD_0$, which are vertical 1-morphisms, will be denoted $f \maps A \to C$ and we denote a 1-cell $M$ with $S(M)=A,T(M)=B$ by $M \maps A \to B$.
-Then a 2-morphism $a \maps M \to N$ of $\lD_1$ with $S(a)=f,T(a)=g$ would look like:
-\[
-\begin{tikzpicture}[scale=1]
-\node (D) at (-4,0.5) {$A$};
-\node (E) at (-2,0.5) {$B$};
-\node (F) at (-4,-1) {$C$};
-\node (A) at (-2,-1) {$D$};
-\node (B) at (-3,-0.25) {$\Downarrow a$};
-\path[->,font=\scriptsize,>=angle 90]
-(D) edge node [above]{$M$}(E)
-(E) edge node [right]{$g$}(A)
-(D) edge node [left]{$f$}(F)
-(F) edge node [above]{$N$} (A);
-\end{tikzpicture}
-\]
-\end{defn}
-%A 2-morphism where $f$ and $g$ are identities is called a \textbf{globular 2-morphism}.
-We call $M$ and $N$ the \define{horizontal source and target} of the 2-morphism $a$, respectively, and likewise we call $f$ and $g$ the \define{vertical source and target} of the 2-morphism $a$, respectively.
-Thus $_f \lA_g(M,N)$ denotes the set of 2-morphisms in $\lA$ with horizontal source and target $M$ and $N$ and vertical source and target $f$ and $g$.
-
-%The key difference between a `strict' double category and a pseudo double category is that in a pseudo double category, horizontal composition is associative and unital only up to natural isomorphism.
-Equivalently, as a double category can be viewed as a category internal to $\Cat$, we can view a pseudo double category as a category `weakly' internal to $\Cat$.
-We will sometimes omit the word pseudo and simply say double category.
-
-\end{comment}
+We call $M$ and $N$ the \define{horizontal source and target} of $a$ respectively, and call $f$ and $g$ its \define{vertical source and target}.
+A 2-morphism where $f$ and $g$ are identities is called \textbf{globular}.
+For example, the associator and unitors in a double category are globular 2-morphisms.
 
@@
 \begin{defn}\label{def:doublefun}
-Given double categories $\lA$ and $\lX$, a \define{(pseudo) double functor} $\lF \colon\lA \to \lX$ consists of:
+Given double categories $\lA$ and $\lX$, a \define{double functor} $\lF \colon\lA \to \lX$ consists of:
 \begin{itemize}
@@
 \item{for every composable pair of horizontal 1-cells $M$ and $N$ in $\lA$, a natural transformation $\phi_{M,N} \colon \lF(M) \odot \lF(N) \to \lF(M \odot N)$ called the \define{composite comparison} and for every object $a$ in $\lA$, a natural transformation $\phi_a \colon U_{\lF_0(a)} \to \lF_1(U_a)$ called the \define{unit comparison}.
-The components of each of these natural transformations are globular isomorphisms which satisfy the usual coherence axioms for a monoidal functor.}
+The components of each of these natural transformations are globular isomorphisms which satisfy coherence axioms analogous to those of a monoidal functor.}
 \end{itemize}
@@
 
-\begin{comment}
-\begin{defn}\label{def:doublefun}
-Let $\lA$ and $\lB$ be double categories.
-A \define{(pseudo) double functor} is a functor $\lF \maps\lA\to \lB$ that takes items of $\lA$ to items of $\lB$ of the corresponding type, respecting vertical composition in the strict sense and the horizontal composition up to an assigned comparison $\phi$.
-This means that we have functors $\lF_0 \maps \lA_0 \to \lB_0$ and $\lF_1 \maps \lA_1 \to \lB_1$ such that the following equations are satisfied:
-\[   S \circ \lF_1 = \lF_0 \circ S, \qquad  T \circ \lF_1 = \lF_0 \circ T. \]
-Sometimes for brevity we omit the subscripts and simply write $\lF$.
-
-Every object $a$ is equipped with a special globular 2-morphism $\phi_{a} \maps 1_{\lF(a)} \to \lF(1_{a})$ (the identity comparison), and every horizontal composition $N_1 \odot N_{2}$ is equipped with a special globular 2-morphism $\phi(N_1,N_{2}) \maps \lF(N_1) \odot \lF(N_{2}) \to \lF(N_1 \odot N_{2})$ (the composition comparison), in a coherent way.
-This means that the following diagrams commute.
-
-\begin{enumerate}
-
-\item For a horizontal composite, $\beta \odot \alpha$,
-
-\begin{equation}\label{eq:square}
-  \xymatrix@-.5pc{
-    \lF(A) \ar[r]|{|}^{\lF(N_{2})}  \ar[d] \ar@{}[dr]|{\lF(\alpha)}&
-    \lF(B) \ar[d] \ar[r]|{|}^{\lF(N_1)} \ar@{}[dr]|{\lF(\beta)}&
-    \lF(C) \ar[d] &
-     &
-    \lF(A) \ar[r]|{|}^{\lF(N_{2})} \ar@{}[drr]|{\phi(N_1,N_{2})} \ar[d]_1 &
-    \lF(B) \ar[r]|{|}^{\lF(N_1)} &
-    \lF(C) \ar[d]^{1} \\
-    \lF(A') \ar[r]|{|}_{\lF(N_{4})} \ar@{}[drr]|{\phi(N_{3},N_{4})} \ar[d]_1&
-    \lF(B') \ar[r]|{|}_{\lF(N_{3})} &
-    \lF(C') \ar[d]^{1}&
-    = &
-    \lF(A) \ar[rr]|{|}^{\lF(N_1 \odot N_{2})} \ar[d] \ar@{}[drr]|{\lF(\beta \odot \alpha)}&
-     &
-    \lF(C) \ar[d] \\
-    \lF(A') \ar[rr]|{|}_{\lF(N_{3} \odot N_{4})} & 
-     & 
-    \lF(C') &
-     &
-    \lF(A') \ar[rr]|{|}_{\lF(N_{3} \odot N_{4})} &
-     &
-    \lF(C') \\
-  }.
-\end{equation}
-
-\item For a horizontal 1-cell $N \maps A \to B$, the following diagrams are commutative (under horizontal composition).
-
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (1,1) {$\lF(N) \odot 1_{\lF(A)}$};
-\node (C) at (3,1) {$\lF(N)$};
-\node (A') at (1,-1) {$\lF(N) \odot \lF(1_{A})$};
-\node (C') at (3,-1) {$\lF(N \odot 1_{A})$};
-\node (B) at (5,1) {$1_{\lF(B)} \odot \lF(N)$};
-\node (B') at (5,-1) {$\lF(1_{B}) \odot \lF(N)$};
-\node (D) at (7,1) {$\lF(N)$};
-\node (D') at (7,-1) {$\lF(1_{B} \odot N)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[left]{$1 \odot \phi_{A}$} (A')
-(C') edge node[right]{$\lF \rho$} (C)
-(A) edge node[above]{$\rho_{\lF(N)}$} (C)
-(A') edge node[above]{$\phi(N,1_{A})$} (C')
-(B) edge node[left]{$\phi_{B} \odot 1$} (B')
-(B') edge node[above]{$\phi(1_{B},N)$} (D')
-(B) edge node[above]{$\lambda_{\lF(N)}$} (D)
-(D') edge node[right]{$F \lambda$} (D);
-\end{tikzpicture}
-\]
-
-\item For consecutive horizontal 1-cells $N_1,N_{2}$ and $N_{3}$, the following diagram is commutative.
-
- \[\xymatrix{
-    (\lF(N_1) \odot \lF(N_{2})) \odot \lF(N_{3}) \ar[r]^{a'}\ar[d]_{\phi(N_1,N_{2}) \odot 1}
-    & \lF(N_1) \odot (\lF(N_{2}) \odot \lF(N_{3})) \ar[d]^{1 \odot \phi(N_{2},N_{3})}\\
-    \lF(N_1 \odot N_{2}) \odot \lF(N_{3}) \ar[d]_{\phi(N_1 \odot N_{2},N_{3})} &
-    \lF(N_1) \odot \lF(N_{2} \odot N_{3}) \ar[d]^{\phi(N_1,N_{2} \odot N_{3})}\\
-    \lF((N_1 \odot N_{2}) \odot N_{3})\ar[r]^{\lF(a)} &
-    \lF(N_1 \odot (N_{2} \odot N_{3}))}\]
-\end{enumerate}
-We say the double functor $\lF$ is \define{strict} if the comparison constraints $\phi_a$ and $\phi_{N_1,N_2}$ are identities, \define{pseudo} if the comparison constraints are isomorphisms, and \define{oplax} if the comparison constraints go in the opposite direction.
-\end{defn}
-\end{comment}
-
 %%% Christina: Pretty sure the def below can be incorporated above, however got a bit lost in different notation. Kenny Fix?
@@
 \begin{defn}\label{def:fullfaithful}
-A double functor $\lF \maps \lA \to \lX$ is \define{full} (respectively, \define{faithful}) if $\lF_0 \maps \lA_0 \to \lX_0$ is full (respectively, faithful) and each map $$\lF_1 \maps _f \lA_g(M,N) \to {_{\lF(f)} \lX_{\lF(g)}}(\lF(M),\lF(N))$$ is surjective (respectively, injective).
+A double functor $\lF \maps \lA \to \lX$ is \define{full} (resp.\ \define{faithful}) if $\lF_0 \maps \lA_0 \to \lX_0$ is full (resp.\ faithful) and each map 
+\[   lF_1 \maps _f \lA_g(M,N) \to {_{\lF(f)} \lX_{\lF(g)}}(\lF(M),\lF(N))\] 
+is surjective (respectively, injective), where $_f \lA_g(M,N)$ is set of 2-morphisms in $\A$ whose horizontal source is $M$ and whose horizontal target is $N$, and similarly for ${_{\lF(f)} \lX_{\lF(g)}}(\lF(M),\lF(N))$.
 \end{defn}
+
 \begin{defn}\label{def:essentiallysurj}
 A double functor $\lF \maps \lA \to \lX$ is \define{essentially surjective} if we can simultaneously make the following choices:
-\begin{enumerate}
+\begin{itemize}
 \item{For each object $x \in \lX$, we can find an object $a \in \lA$ together with a vertical 1-isomorphism $\alpha_x \maps \lF(a) \to x$, and}
@@
 }
-\end{enumerate}
+\end{itemize}
 \end{defn}
@@
 \begin{defn}
-Two pseudo double functors $\lF \colon \lA \to \lX$ and $\mathbb{G} \colon \lX \to \lA$ form a \define{double equivalence} if there exist double natural transformations $\mathbb{G} \lF \cong 1_\lA$ and $\lF \mathbb{G} \cong 1_\lX$.
+Two double functors $\lF \colon \lA \to \lX$ and $\mathbb{G} \colon \lX \to \lA$ form a \define{double equivalence} if there exist double natural transformations $\mathbb{G} \lF \cong 1_\lA$ and $\lF \mathbb{G} \cong 1_\lX$.
 \end{defn}
-% FINISH THIS OR DISCARD IT!!!
-%{\chris their two-way composite is isomorphic to the identity, better expressed, possibly in a definition environment}. 
-Much like equivalence of categories, equivalence of double categories has an alternative characterization:
+
+Like equivalence of categories, equivalence of double categories has an alternative characterization:
 
@@
 
-WE NEED TO SAY BRIEFLY WHAT A DOUBLE ISOMORPHISM IS.
-
-\begin{thm}
-Let $\lA$ and $\lX$ be symmetric monoidal double categories and let $\lF \maps \lA \to \lX$ be a symmetric monoidal pseudo double functor.
+Let $\Dbl$ denote the 2-category of double categories, double functors and double transformations.
+One can check that $\Dbl$ has finite products, and in any 2-category with finite products we can define a `pseudomonoid', which is a categorified analogue of a monoid \cite{DS}.
+For example, a pseudomonoid in $\Cat$ is a monoidal category.
+We can also define braided and symmetric pseudomonoids, which in $\Cat$ are braided and symmetric monoidal categories.
+
+\begin{defn}
+\label{defn:monoidal_double_category}
+A \define{monoidal double category} is a pseudomonoid in $\Dbl$.
+Explicitly, it is a double category equipped with double functors $\otimes \maps \lD \times \lD \to \lD$ and $I \maps 1 \to \lD$ where $1$ is the terminal double category, along with invertible transformations called the \define{associator}:
+\[  \alpha \maps \otimes \, \circ \; (1_{\lD} \times \otimes ) \Rightarrow \otimes \; \circ \; (\otimes \times 1_{\lD}) ,\]
+\define{left unitor}:
+\[ \ell \maps \otimes \, \circ \; (1_{\lD} \times I) \Rightarrow 1_{\lD} ,\]
+and \define{right unitor}:
+\[ r \maps \otimes \,\circ\; (I \times 1_{\lD}) \Rightarrow 1_{\lD} \]
+satisfying the pentagon and triangle identities.
+\end{defn}
+
+\begin{defn}
+\label{defn:symmetric_monoidal_double_category}
+A \define{braided monoidal double category} is a braided pseudomonoid in $\Dbl$.  Explicitly,
+it is a monoidal double category equipped with an invertible transformation
+\[ \beta \maps \otimes \Rightarrow \otimes \circ \tau \]
+called the \define{braiding}, where $\tau \maps \lD \times \lD \to \lD \times \lD$ is the twist double functor sending pairs in the object and arrow categories to the same pairs in the opposite order.
+The braiding is required to satisfy the usual two hexagon identities.
+If the braiding is self-inverse we say that $\lD$ is a \define{symmetric monoidal double category}.
+\end{defn}
+
+\begin{defn}\label{defn:monoidal_double_functor}
+Given symmetric monoidal double categories $\lA$ and $\lX$, a \define{symmetric monoidal double functor} $\lF \colon \lA \to \lX$ is a double functor $\lF$ together with transformations $\theta \colon {\otimes \circ (\lF,\lF)} \to \lF \circ \otimes$ and $\theta_U \colon 1_\lX \to \lF \circ 1_\lA$ that satisfy the usual coherence axioms for a symmetric monoidal functor with respect to $\otimes$.
+\end{defn}
+
+Unpacking these definitions further one obtains a large number of diagrams \cite{HS}.
+
+WE NEED TO SAY BRIEFLY WHAT A SYMMETRIC MONOIDAL DOUBLE ISOMORPHISM, IF WE USE THIS CONCEPT IN OUR BIG RESULT, \cref{thm:equiv}.
+CLAIM: $\lA$ and $\lX$ be symmetric monoidal double categories and let $\lF \maps \lA \to \lX$ be a symmetric monoidal double functor.
 If $\lF$ is part of a double equivalence, then $\lF$ is in fact part of a symmetric monoidal double equivalence, and $\lA$ and $\lX$ are equivalent as symmetric monoidal double categories.
-\end{thm}
-
-\begin{proof} Where is this proved???  \end{proof}
-%%% Kenny: This isn't proved anywhere formally, as far as I know.
-
-Let $\mathbf{Dbl}$ denote the 2-category of double categories, double functors and double transformations.
-One can check that $\mathbf{Dbl}$ has finite products, and in any 2-category with finite products we can define a `pseudomonoid' or a `weak' monoid, which is a categorified analogue of a monoid in which the left and right unitors and associators are not identities but natural isomorphisms.
-It is the 2-categorical structure of $\mathbf{Dbl}$, or more generally, any 2-category with finite limits, that enables us to do this.
-For example, a pseudomonoid in $\mathbf{Cat}$ is a monoidal category.
-We are primarily concerned with the (weak) monoidal double categories in which the associators and left and right unitors are natural isomorphisms.
-\begin{defn}\label{defn:smdc}
-A \define{monoidal double category} is a pseudomonoid internal to the monoidal 2-category $\mathbf{Dbl}$.
-Similarly, a \define{braided monoidal double category} is a braided pseudomonoid internal to $\mathbf{Dbl}$ and a \define{symmetric monoidal double category} is a symmetric pseudomonoid internal to $\mathbf{Dbl}$.
-\end{defn}
-For more details on the definition of (braided, symmetric) monoidal double category, we refer to Hansen and Shulman \cite{HS}.
-
-\begin{comment}
-\begin{defn}\label{defn:smdc}
-%  A \textbf{monoidal double category} is a double category equipped the following
-  A \textbf{monoidal double category} is a double category $\lA$ equipped with the following
-structure.
-\begin{enumerate}
-\item $\lD_0$ and $\lD_1$ are both monoidal categories.
-\item If $I$ is the monoidal unit of $\lD_0$, then $U_I$ is the
-  monoidal unit of $\lD_1$.
-\item The functors $S$ and $T$ are strict monoidal, i.e.\ $S(M\ten N)
-  = SM\ten SN$ and $T(M\ten N)=TM\ten TN$ and $S$ and $T$ also
-  preserve the associativity and unit constraints.
-\item We have globular isomorphisms
-  \[\chi \maps (M_1\ten N_1)\odot (M_2\ten N_2)\too[\sim] (M_1\odot M_2)\ten (N_1\odot N_2)\]
-  and
-  \[\mu\maps U_{A\ten B} \too[\sim] (U_A \ten U_B)\]
-  such that the following diagrams commute:
-		\item \label{diag:MonDblCat}
-			The following diagrams commute expressing the constraint data for the double functor $\otimes$.
-			\[
-			\begin{tikzpicture}
-				\node (A) at (0,3) {\footnotesize{
-							$((M_1\otimes N_1)\odot (M_2\otimes N_2)) \odot (M_3\otimes N_3)$}
-				};
-				\node (B) at (7,3) {\footnotesize{
-						$((M_1\odot M_2)\otimes (N_1\odot N_2)) \odot (M_3\otimes N_3) $}
-				};
-				\node (A') at (0,1.5) {\footnotesize{
-						$(M_1\otimes N_1)\odot ((M_2\otimes N_2) \odot (M_3\otimes N_3)) $}
-				};
-				\node (B') at (7,1.5) {\footnotesize{
-						$((M_1\odot M_2)\odot M_3) \otimes ((N_1\odot N_2)\odot N_3)$}
-				};
-				\node (A'') at (0,0) {\footnotesize{
-						$(M_1\otimes N_1) \odot ((M_2\odot M_3) \otimes (N_2\odot N_3))$}
-				};
-				\node (B'') at (7,0) {\footnotesize{
-						$(M_1\odot (M_2\odot M_3)) \otimes (N_1\odot (N_2\odot N_3))$}
-				};
-			%
-			\path[->,font=\scriptsize]
-				(A) edge node[left]{$\alpha$} (A')
-				(A') edge node[left]{$1 \odot \chi$} (A'')
-				(B) edge node[right]{$\chi$} (B')
-				(B') edge node[right]{$\alpha \otimes \alpha$} (B'')
-				(A) edge node[above]{$\chi \odot 1$} (B)
-				(A'') edge node[above]{$\chi$} (B'');
-		\end{tikzpicture}
-		\]
-		\[
-		\begin{tikzpicture}
-			\node (UL) at (0,1.5) {\footnotesize{
-					$(M\otimes N) \odot U_{C\otimes D}$}
-			};
-			\node (LL) at (0,0) {\footnotesize{
-					$M\otimes N$}
-			};
-			\node (UR) at (3.5,1.5) {\footnotesize{
-					$(M\otimes N)\odot (U_C\otimes U_D)$}
-			};
-			\node (LR) at (3.5,0) {\footnotesize{
-					$(M\odot U_C) \otimes (N\odot U_D)$}
-			};
-			%
-			\path[->,font=\scriptsize]
-				(UL) edge node[above]{$1 \odot \mu$} (UR) 
-				(UL) edge node[left]{$\rho$} (LL)
-				(LR) edge node[above]{$\rho \otimes \rho$} (LL)
-				(UR) edge node[right]{$\chi$} (LR);
-		\end{tikzpicture}
-		%
-		\quad
-		%
-		\begin{tikzpicture}
-			\node (UL) at (0,1.5) {\scriptsize{$U_{A\otimes B}\odot (M\otimes N)$}};
-			\node (LL) at (0,0) {\scriptsize{$M\otimes N$}};
-			\node (UR) at (3.5,1.5) {\scriptsize{$(U_A\otimes U_B)\odot (M\otimes N)$}};
-			\node (LR) at (3.5,0) {\scriptsize{$(U_A \odot M) \otimes (U_B\odot N)$}};
-			%
-			\path[->,font=\scriptsize]
-				(UL) edge node[above]{$\mu \odot 1$} (UR) 
-				(UL) edge node[left]{$\lambda$} (LL)
-				(LR) edge node[above]{$\lambda \otimes \lambda$} (LL)
-				(UR) edge node[right]{$\chi$} (LR);
-		\end{tikzpicture}
-		\]
-		%
-		\item The following diagrams commute expressing 
-		the associativity isomorphism for $\otimes$ is a transformation of double categories.
-		\[
-		\begin{tikzpicture}
-			\node (A) at (0,3) {\footnotesize{
-					$((M_1\otimes N_1)\otimes P_1) \odot ((M_2\otimes N_2)\otimes P_2)$}
-			};
-			\node (B) at (7,3) {\footnotesize{
-					$(M_1\otimes (N_1\otimes P_1)) \odot (M_2\otimes (N_2\otimes P_2))$}
-			};
-			\node (A') at (0,1.5) {\footnotesize{
-					$((M_1\otimes N_1) \odot (M_2\otimes N_2)) \otimes (P_1\odot P_2)$}
-			};
-			\node (B') at (7,1.5) {\footnotesize{
-					$(M_1\odot M_2) \otimes ((N_1\otimes P_1)\odot (N_2\otimes P_2))$}
-			};
-			\node (A'') at (0,0) {\footnotesize{
-					$((M_1\odot M_2) \otimes(N_1\odot N_2)) \otimes (P_1\odot P_2)$}
-			};
-			\node (B'') at (7,0) {\footnotesize{
-					$(M_1\odot M_2) \otimes ((N_1\odot N_2)\otimes (P_1\odot P_2))$}
-			};
-			%
-			\path[->,font=\scriptsize]
-				(A) edge node[left]{$\chi$} (A')
-				(A') edge node[left]{$\chi \otimes 1$} (A'')
-				(B) edge node[right]{$\chi$} (B')
-				(B') edge node[right]{$1 \otimes \chi$} (B'')
-				(A) edge node[above]{$\alpha \odot \alpha$} (B)
-				(A'') edge node[above]{$\alpha$} (B'');
-		\end{tikzpicture}
-		\]
-		\[
-		\begin{tikzpicture}
-			\node (A) at (0,3) {\footnotesize{$U_{(A\otimes B)\otimes C}$}};
-			\node (B) at (4,3) {\footnotesize{$U_{A\otimes (B\otimes C)} $}};
-			\node (A') at (0,1.5) {\footnotesize{$U_{A\otimes B} \otimes U_C $}};
-			\node (B') at (4,1.5) {\footnotesize{$U_A\otimes U_{B\otimes C}$}};
-			\node (A'') at (0,0) {\footnotesize{$(U_A\otimes U_B)\otimes U_C$}};
-			\node (B'') at (4,0) {\footnotesize{$U_A\otimes (U_B\otimes U_C) $}};
-			%
-			\path[->,font=\scriptsize]
-				(A) edge node[left]{$\mu$} (A')
-				(A') edge node[left]{$\mu \otimes 1$} (A'')
-				(B) edge node[right]{$\mu$} (B')
-				(B') edge node[right]{$1 \otimes \mu$} (B'')
-				(A) edge node[above]{$U_{\alpha}$} (B)
-				(A'') edge node[above]{$\alpha$} (B'');
-		\end{tikzpicture}
-		\]
-		\item The following diagrams commute expressing that 
-		the unit isomorphisms for $\otimes$ are transformations of double categories. 
-		\[
-		\begin{tikzpicture}
-			\node (A) at (0,1.5) {\footnotesize{$(M\otimes U_I)\odot (N\otimes U_I)$}};
-			\node (A') at (0,0) {\footnotesize{$M\odot N $}};
-			\node (B) at (4,1.5) {\footnotesize{$(M\odot N)\otimes (U_I \odot U_I) $}};
-			\node (B') at (4,0) {\footnotesize{$(M\odot N)\otimes U_I $}};
-			%
-			\path[->,font=\scriptsize]
-				(A) edge node[left]{$r \odot r$} (A')
-				(A) edge node[above]{$\chi$} (B)
-				(B) edge node[right]{$1 \otimes \rho$} (B')
-				(B') edge node[above]{$r$} (A');
-		\end{tikzpicture}
-		%
-		\quad
-		%
-		\begin{tikzpicture}
-			\node (A) at (0,0.75) {\footnotesize{$U_{A\otimes I} $}};
-			\node (B) at (1.5,1.5) {\footnotesize{$U_A\otimes U_I $}};
-			\node (B') at (1.5,0) {\footnotesize{$U_A$}};
-			%
-			\path[->,font=\scriptsize]
-				(A) edge node[above]{$\mu$} (B)
-				(A) edge node[below]{$U_{r}$} (B')
-				(B) edge node[right]{$r$} (B');
-		\end{tikzpicture}
-		\]
-		%
-		%
-		%
-		%
-		\[
-		\begin{tikzpicture}
-			\node (A) at (0,1.5) {\footnotesize{$(U_I\otimes M)\odot (U_I\otimes N)$}};
-			\node (A') at (0,0) {\footnotesize{$M\odot N$}};
-			\node (B) at (4,1.5) {\footnotesize{$(U_I \odot U_I) \otimes (M\odot N)$}};
-			\node (B') at (4,0) {\footnotesize{$U_I\otimes (M\odot N) $}};
-			%
-			\path[->,font=\scriptsize]
-				(A) edge node[left]{$\ell \odot \ell$} (A')
-				(A) edge node[above]{$\chi$} (B)
-				(B) edge node[right]{$\lambda \otimes 1$} (B')
-				(B') edge node[above]{$\ell$} (A');
-		\end{tikzpicture}
-		%
-		\quad
-		\begin{tikzpicture}
-			\node (A) at (0,0.75) {\footnotesize{$U_{I\otimes A}$}};
-			\node (B) at (1.5,1.5) {\footnotesize{$U_I\otimes U_A$}};
-			\node (B') at (1.5,0) {\footnotesize{$U_A$}};
-			%
-			\path[->,font=\scriptsize]
-				(A) edge node[above]{$\mu$} (B)
-				(A) edge node[below]{$U_{\ell}$} (B')
-				(B) edge node[right]{$\ell$} (B');
-		\end{tikzpicture}
-		\]
-		\newcounter{mondbl}
-		\setcounter{mondbl}{\value{enumi}}
-	\end{enumerate}
-	A \textbf{braided monoidal double category} 
-	is a monoidal double category 
-	such that:
-	\begin{enumerate}
-		\setcounter{enumi}{\value{mondbl}}
-		\item $\lD_0$ and $\lD_1$ are braided monoidal categories.
-		\item The functors $S$ and $T$ are strict braided monoidal functors.
-		\item The following diagrams commute expressing that the braiding is a transformation of double categories.
-		\[
-		\begin{tikzpicture}
-			\node (A) at (0,1.5) {\footnotesize{$(M_1 \odot M_2) \otimes (N_1 \odot N_2)$}};
-			\node (A') at (0,0) {\footnotesize{$(M_1\otimes N_1) \odot (M_2\otimes N_2)$}};
-			\node (B) at (5,1.5) {\footnotesize{$(N_1\odot N_2) \otimes (M_1 \odot M_2)$}};
-			\node (B') at (5,0) {\footnotesize{$(N_1 \otimes M_1) \odot (N_2 \otimes M_2)$}};
-			%
-			\path[->,font=\scriptsize]
-				(A) edge node[left]{$\chi$} (A')
-				(A) edge node[above]{$\beta$} (B)
-				(B) edge node[right]{$\chi$} (B')
-				(A') edge node[above]{$\beta \odot \beta$} (B');
-		\end{tikzpicture}
-		%
-		\quad
-		%
-		\begin{tikzpicture}
-			\node (A) at (0,1.5) {\footnotesize{$U_A \otimes U_B$}};
-			\node (A') at (0,0) {\footnotesize{$U_B\otimes U_A$}};
-			\node (B) at (2,1.5) {\footnotesize{$U_{A\otimes B} $}};
-			\node (B') at (2,0) {\footnotesize{$U_{B\otimes A}$}};
-			%
-			\path[->,font=\scriptsize]
-				(A) edge node[left]{$\beta$} (A')
-				(B) edge node[above]{$\mu$} (A)
-				(B) edge node[right]{$U_\beta$} (B')
-				(B') edge node[above]{$\mu$} (A');
-		\end{tikzpicture}
-		\]
-		\setcounter{mondbl}{\value{enumi}}
-	\end{enumerate}
-	Finally, a \textbf{symmetric monoidal double category} 
-	is a braided monoidal double category $\mathbb{D}$ such that:
-	\begin{enumerate}
-		\setcounter{enumi}{\value{mondbl}}
-		\item $\lD_0$ and $\lD_1$ are symmetric monoidal.
-	\end{enumerate}
-\end{defn}
-\end{comment}
 
@@
 
-\begin{defn}\label{defn:monoidal_double_functor}
-Given (braided, symmetric) monoidal double categories $\lA$ and $\lX$, a \define{(braided, symmetric) monoidal double functor} $\lF \colon \lA \to \lX$ is a double functor $\lF$ together with transformations $\theta \colon {\otimes \circ (\lF,\lF)} \to \lF \circ \otimes$ and $\theta_U \colon 1_\lX \to \lF \circ 1_\lA$ that satisfy the usual coherence axioms for a (braided, symmetric) monoidal functor with respect to $\otimes$.
-\end{defn}
-
-For more details on the definition of (braided, symmetric) monoidal functor, we refer to Hansen and Shulman \cite{HS}.
-
-\begin{comment}
-
-\begin{defn}
-\label{defn:monoidal_double_functor}
-A \define{(strong) monoidal double functor} $\lF \maps \mathbb{C} \to \mathbb{D}$ between monoidal double categories $\mathbb{C}$ and $\mathbb{D}$ is a double functor $\lF \maps \mathbb{C} \to \mathbb{D}$ such that
-	\begin{itemize}
-		\item $\lF_0$ and $\lF_1$ are monoidal functors, meaning that there exists
-
-\begin{enumerate}
-\item{an isomorphism $\epsilon \maps 1_{\lD} \to \lF(1_{\lC})$}
-\item{a natural isomorphism $\mu_{A,B} \maps \lF(A) \otimes \lF(B) \to \lF(A \otimes B)$ for all objects $A$ and $B$ of $\lC$}
-\item{an isomorphism $\delta \maps U_{1_{\lD}} \to \lF(U_{1_{\lC}})$}
-\item{a natural isomorphism $\nu_{M,N} \maps \lF(M) \otimes \lF(N) \to \lF(M \otimes N)$ for all horizontal 1-cells $N$ and $M$ of $\lC$}
-\end{enumerate}
-such that the following diagrams commute: for objects $A,B$ and $C$ of $\lC$,
- \[\xymatrix{
-    (\lF(A) \otimes \lF(B)) \otimes \lF(C) \ar[r]^{\alpha'}\ar[d]_{\mu_{A,B} \otimes 1}
-    & \lF(A) \otimes (\lF(B) \otimes \lF(C)) \ar[d]^{1 \otimes \mu_{B,C}}\\
-    \lF(A \otimes B) \otimes \lF(C) \ar[d]_{\mu_{A \otimes B,C}} &
-    \lF(A) \otimes \lF(B \otimes C) \ar[d]^{\mu_{A,B \otimes C}}\\
-    \lF((A \otimes B) \otimes C)\ar[r]^{\lF\alpha} &
-    \lF(A \otimes (B \otimes C))}\]
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (1,1) {$\lF(A) \otimes 1_{\lD}$};
-\node (C) at (3,1) {$\lF(A)$};
-\node (A') at (1,-1) {$\lF(A) \otimes \lF(1_{\lC})$};
-\node (C') at (3,-1) {$\lF(A \otimes 1_{\lC})$};
-\node (B) at (5,1) {$1_{\lD} \otimes \lF(A)$};
-\node (B') at (5,-1) {$\lF(1_{\lC}) \otimes \lF(A)$};
-\node (D) at (7,1) {$\lF(A)$};
-\node (D') at (7,-1) {$\lF(1_{\lC} \otimes A)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[left]{$1 \otimes \epsilon$} (A')
-(C') edge node[right]{$\lF(r_{A})$} (C)
-(A) edge node[above]{$r_{\lF(A)}$} (C)
-(A') edge node[above]{$\mu_{A,1_{\lC}}$} (C')
-(B) edge node[left]{$\epsilon \otimes 1$} (B')
-(B') edge node[above]{$\mu_{1_{\lC},A}$} (D')
-(B) edge node[above]{$\ell_{\lF(A)}$} (D)
-(D') edge node[right]{$\lF(\ell_{A})$} (D);
-\end{tikzpicture}
-\]
-and for horizontal 1-cells $N_1,N_{2}$ and $N_{3}$ of $\lC$,
- \[\xymatrix{
-    (\lF(N_1) \otimes \lF(N_{2})) \otimes \lF(N_{3}) \ar[r]^{\alpha'}\ar[d]_{\nu_{N_1,N_{2}} \otimes 1}
-    & \lF(N_1) \otimes (\lF(N_{2}) \otimes \lF(N_{3})) \ar[d]^{1 \otimes \nu_{N_{2},N_{3}}}\\
-    \lF(N_1 \otimes N_{2}) \otimes \lF(N_{3}) \ar[d]_{\nu_{N_1 \otimes N_{2},N_{3}}} &
-    \lF(N_1) \otimes \lF(N_{2} \otimes N_{3}) \ar[d]^{\nu_{N_1,N_{2} \otimes N_{3}}}\\
-    \lF((N_1 \otimes N_{2}) \otimes N_{3})\ar[r]^{\lF\alpha} &
-    \lF(N_1 \otimes (N_{2} \otimes N_{3}))}\]
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,1) {$\lF(N_1) \otimes U_{1_{\lD}}$};
-\node (C) at (3,1) {$\lF(N_1)$};
-\node (A') at (0,-1) {$\lF(N_1) \otimes \lF(U_{1_{\lC}})$};
-\node (C') at (3,-1) {$\lF(N_1 \otimes U_{1_{\lC}})$};
-\node (B) at (5,1) {$U_{1_{\lD}} \otimes \lF(N_1)$};
-\node (B') at (5,-1) {$\lF(U_{1_{\lC}}) \otimes \lF(N_1)$};
-\node (D) at (8,1) {$\lF(N_1)$};
-\node (D') at (8,-1) {$\lF(U_{1_{\lC}} \otimes N_1)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[left]{$1 \otimes \delta$} (A')
-(C') edge node[right]{$\lF(r_{N_1})$} (C)
-(A) edge node[above]{$r_{\lF(N_1)}$} (C)
-(A') edge node[above]{$\nu_{N_1,U_{1_{\lC}}}$} (C')
-(B) edge node[left]{$\delta \otimes 1$} (B')
-(B') edge node[above]{$\nu_{U_{1_{\lC}},N_1}$} (D')
-(B) edge node[above]{$\ell_{\lF(N_1)}$} (D)
-(D') edge node[right]{$\lF(\ell_{N_1})$} (D);
-\end{tikzpicture}
-\]
-
-		\item $S\lF_1= \lF_0S$ and $T\lF_1 = \lF_0T$ are equations between monoidal functors, and
-		\item the composition and unit comparisons $\phi(N_1,N_2) \maps \lF_1(N_1) \odot \lF_1(N_2) \to \lF_1(N_1\odot N_2)$ and $\phi_A \maps U_{\lF_0 (A)} \to \lF_1(U_A)$ are monoidal natural transformations.
-	\end{itemize}
-A monoidal double functor $\lF$ is \define{braided} if $\lF_0$ and $\lF_1$ are braided monoidal functors and \define{symmetric} if they are symmetric monoidal.
-\end{defn}
-
-\end{comment}
-
-DEFINITION OF SYMMETRIC MONOIDAL ISOMORPHISM, BRIEFLY?
-
 \begin{thebibliography}{100}
@@
 
-\bibitem{McCrudden} P.\ McCrudden, Balanced coalgebroids, \textsl{Theory Appl.\ Categ.\ } \textbf{ 7} (2000), 71--147.
+\bibitem{McCrudden} P.\ McCrudden, Balanced coalgebroids, \textsl{Theory Appl.\ Categ.\ }\textbf{ 7} (2000), 71--147.
 

### 2020-11-25 cospans.tex
Some changes to Section 3

@@
 
-In \cite{MV}, the classical Grothendieck construction is generalized to the monoidal setting.  Suppose $\A$ is a monoidal category. Then there is a bijection between the following two things:
-\begin{itemize}
-\item lax monoidal structures on a pseudofunctor $F\maps\A\to\Cat$
-\item monoidal structures on $\inta F$ such that $U \maps \inta F \to \A$ is strict monoidal and the tensor product in $\inta F$ preserves cocartesian liftings.  
-\end{itemize}
-We call the former \define{monoidal opindexed categories}, and the latter \define{monoidal opfibrations}.
-If the monoidal structure of $\A$ is cocartesian, there is a further correspondence between these structures and ordinary pseudofunctors $F\maps\A\to\bicat{MonCat}$ into the 2-category of monoidal categories, strong monoidal functors and monoidal natural transformations.
-These correspondences can be enhanced to 2-equivalences:
-%-In \cite{MV}, the classical Grothendieck construction is generalized to the monoidal setting: given a monoidal category $\A$ there is a bijection between \define{monoidal opindexed categories}, which are lax monoidal pseudofunctors $F\maps\A\to\Cat$, and \define{monoidal opfibrations}, which are opfibrations $U \maps \X \to \A$ where $\X$ is monoidal, $U$ is strict monoidal, and $\otimes_\X$ preserves cocartesian liftings.
+In \cite{MV}, the classical Grothendieck construction is generalized to the monoidal setting: given a monoidal category $\A$ there is a bijection between \define{monoidal opindexed categories}, which are lax monoidal pseudofunctors $F\maps\A\to\Cat$, and \define{monoidal opfibrations}, which are opfibrations $U \maps \X \to \A$ where $\X$ is monoidal, $U$ is strict monoidal, and $\otimes_\X$ preserves cocartesian liftings.
 This bijection sends a monoidal opindexed category $F \maps \A \to \Cat$ to its Grothendieck construction $U \maps \inta F \to \A$.
-If the monoidal structure on $\A$ is in fact cocartesian, there is a further correspondence between these structures and ordinary pseudofunctors $F\maps\A\to\bicat{MonCat}$ into the 2-category of monoidal categories, strong monoidal functors and monoidal natural transformations.
+If the monoidal structure on $\A$ is in fact cocartesian, there is a further correspondence between these structures and ordinary pseudofunctors $F\maps\A\to\bicat{MonCat}$ where $\bicat{MonCat}$ is 2-category of monoidal categories, strong monoidal functors and monoidal natural transformations.
 Further, all these correspondences lift to 2-equivalences:
-{\chris There is a commented out passage of your earlier take here.
+%{\chris There is a commented out passage of your earlier take here.
 I think I preferred your earlier more discussional version.
@@
 \begin{proof}
-This was shown by Moeller and the third author \cite[Theorems~3.13\&4.1]{MV}. In summary, for a cocartesian base we have correspondences
+This was shown by Moeller and the third author \cite[Theorems~3.13\&4.1]{MV}. In summary, for a cocartesian base $\A$ we have correspondences
 \begin{gather}
@@
 
-We have now laid all the necessary background to formally construct an isomorphism between the double category of decorated cospans and the double category of structured cospans, with starting point a symmetric lax monoidal pseudofunctor into $\Cat$.
+We have now have all the necessary background to formally construct an isomorphism between the double category of decorated cospans and the double category of structured cospans, starting from a symmetric lax monoidal pseudofunctor $F \maps (\A, +) \to (\Cat, \times)$ that factors through $\Rex$ as a pseudofunctor.
 

### 2020-11-25 cospans.tex
tiny

@@
 \begin{proof}
-The definition of symmetric monoidal double category may be found in Definition \ref{defn:smdc}.
+The definition of symmetric monoidal double category may be found in Definition \ref{defn:symmetric_monoidal_double_category}.
 We must show that both the category of objects $F\lCsp_0$ and the category of arrows $F\lCsp_1$ are symmetric monoidal categories, show that the monoidal unit of $F\lCsp_0$ is preserved by the unit functor $U$, show that the source and target functors $S,T \colon F\lCsp_1 \to F\lCsp_0$ are strict symmetric monoidal functors which preserve the associativity and unit constraints, define the globular isomorphisms $\chi$ and $\mu$ that relate how composition and units interact with the tensor product, and check that the required axioms are satisfied.
@@
 If the monoidal structure on $\A$ is in fact cocartesian, there is a further correspondence between these structures and ordinary pseudofunctors $F\maps\A\to\bicat{MonCat}$ where $\bicat{MonCat}$ is 2-category of monoidal categories, strong monoidal functors and monoidal natural transformations.
-Further, all these correspondences lift to 2-equivalences:
-%{\chris There is a commented out passage of your earlier take here.
-I think I preferred your earlier more discussional version.
-Now having the two bullets above almost totally coincides with the three lines with arrows between them in the sketch of proof below.
-Feels like saying the same thing twice, whereas earlier you were really just giving brief definitions before diving in the theorem.}
+Further, all these correspondences lift to 2-equivalences.
 
@@
 \begin{proof}
-This was shown by Moeller and the third author \cite[Theorems~3.13\&4.1]{MV}. In summary, for a cocartesian base $\A$ we have correspondences
+This was shown by Moeller and the third author \cite[Theorems~3.13\&4.2]{MV}. In summary, for a cocartesian base $\A$ we have correspondences
 \begin{gather}
@@
 Briefly, a \define{monoidal} bicategory $\bA$ comes with a pseudofunctor $\otimes\maps\bA\times\bA\to\bA$ and a unit object $I$ that are associative and unital up to coherent equivalence.
-.A \define{braided} monoidal bicategory also comes with a pseudonatural equivalence $\beta_{a,b}\maps a\ot b\to b\ot a$ and appropriate invertible modifications obeying certain equations; it is \define{sylleptic} if there is an invertible modification $1_{a\ot b}\Rrightarrow\beta_{b,a}\circ\beta_{a,b}$ its own equation, \define{symmetric} if one further axiom holds.
+A \define{braided} monoidal bicategory also comes with a pseudonatural equivalence $\beta_{a,b}\maps a\ot b\to b\ot a$ and appropriate invertible modifications obeying certain equations; it is \define{sylleptic} if there is an invertible modification $1_{a\ot b}\Rrightarrow\beta_{b,a}\circ\beta_{a,b}$ its own equation, \define{symmetric} if one further axiom holds.
 
@@
 We chose to primarily present this dual notion to \define{fibration} due to the current work's needs.
-%Christina: decide later if needed
-%Notice that as a result,
-%any arrow in the total category of an opfibration factorizes uniquely into a vertical morphism (above the identity) followed by a (co)cartesian one:
-%\[
-%\xymatrix @C=.4in @R=.2in
-%{x \ar @{.>}[dd]\ar[rr]^\gamma \ar[drr]_-{\mathrm{Cocart}(g,C)} && D &\\
-%&& f_!C \ar @{-->}[u]_-{\delta} \ar @{.>}[d] & \textrm{in }\C  \\
-%X\ar[rr]_-{g} && Y & \textrm{in }\X.}
-%\]
 
@@
 where $[\A,\Cat]_\pse$ is the 2-category of pseudofunctors from $\A$ to $\Cat$, pseudonatural transformations, and modifications.
-%        \item The above 2-equivalence extends to one between 2-categories of arbitrary-base fibrations and arbitrary-domain indexed categories
-%        \begin{equation}\label{eq:Gr_equiv}
-%        \ICat\simeq\Fib    
-%        \end{equation}
 \end{enumerate}
@@
 
-\begin{proof}  CITE A PROOF!!!  \end{proof}
-
-%\begin{defn}
-%Let $P \maps \mathbf{D} \to \mathrm{A}$ be a functor.
-A morphism $f \maps d_1 \to d_{2}$ in the category $\mathbf{D}$ is \textbf{cartesian (with respect to the functor P)} if for any object $d'$ in $\mathbf{D}$ and morphism $g \maps d' \to d_{2}$ and every $p \maps P(d') \to P(d_1)$ such that $P(g)=P(f)p$, there exists a unique $h \maps d' \to d_1$ such that $g=fh$ and $p=P(h)$.
-%\[
-%\begin{tikzpicture}[scale=1.5]
-%\node (A) at (0,0) {$d'$};
-%\node (B) at (0,-1.5) {$d_1$};
-%\node (C) at (1.5,-1.5) {$d_{2}$};
-%\node (H) at (2,-0.5) {$P$};
-%\node (D) at (2,-.75) {$\mapsto$};
-%\node (E) at (3,0) {$P(d')$};
-%\node (F) at (3,-1.5) {$P(d_1)$};
-%\node (G) at (4.5,-1.5) {$P(d_{2})$};
-%\path[->,font=\scriptsize,>=angle 90]
-%(A) edge[dashed] node[above,left]{$\exists ! h$} (B)
-%(A) edge node[above]{$g$} (C)
-%(E) edge node[above,left]{$p=P(h)$} (F)
-%(F) edge node[above]{$P(f)$} (G)
-%(E) edge node[above,right]{$P(g)$} (G)
-%(B)edge node[above]{$f$}(C);
-%\end{tikzpicture}
-%\]
-%\end{defn}
+\begin{proof}  
+This is due to Grothendieck; a proof can be found, for example, in \cite[\S~1.10]{Jacobs}.
+\end{proof}
 
 \subsection{Double categories}\label{sec:doublecats}
-
-%We will denote both kinds of morphisms and horizontal 1-cells as a single arrow, namely `$\to$'???   Or should we put a ``tick'' in here?
-
 For double categories we follow the notation of our paper on structured cospans \cite{BC}, which in turn follows that of Shulman \cite{Shulman2010}.
@@
 \[
-\begin{tikzpicture}[scale=1]
-\node (D) at (-4,0.5) {$A$};
-\node (E) at (-2,0.5) {$B$};
-\node (F) at (-4,-1) {$C$};
-\node (A) at (-2,-1) {$D$};
-\node (B) at (-3,-0.25) {$\Downarrow a$};
-\path[->,font=\scriptsize,>=angle 90]
-(D) edge node [above]{$M$}(E)
-(E) edge node [right]{$g$}(A)
-(D) edge node [left]{$f$}(F)
-(F) edge node [above]{$N$} (A);
-\end{tikzpicture}
-\]
+\begin{tikzcd}
+A\ar[r,"M"]\ar[d,"f"']\ar[dr,phantom,"\scriptstyle\Downarrow\alpha"] & B\ar[d,"g"] \\
+C\ar[r,"N"'] & D
+\end{tikzcd}
+\]
+%Christina: changed the code above to match the squares later better
 We call $M$ and $N$ the \define{horizontal source and target} of $a$ respectively, and call $f$ and $g$ its \define{vertical source and target}.
@@
 \begin{itemize}
-\item{For each object $x \in \lX$, we can find an object $a \in \lA$ together with a vertical 1-isomorphism $\alpha_x \maps \lF(a) \to x$, and}
-\item{For each horizontal 1-cell $N \maps x_1 \tobar x_2$  of $\lX$, we can find a horizontal 1-cell $M \maps a_1 \tobar a_2$ of $\lA$ and a 2-isomorphism $a_{N} \colon \lF(M) \to N$ in $\lX$ as in the following diagram:
-\[
-  \xymatrix@-.5pc{
-    \lF(a_1) \ar[r]|{|}^{\lF(M)}  \ar[d]_{\alpha_{x_1}} \ar@{}[dr]|{\Downarrow a_N}&
-    \lF(a_1) \ar[d]^{\alpha_{x_2}}\\
-    x_1 \ar[r]|{|}_N & x_2
-  }
-\]
-}
+\item For each object $x \in \lX$, we can find an object $a \in \lA$ together with a vertical 1-isomorphism $\alpha_x \maps \lF(a) \to x$, and
+\item For each horizontal 1-cell $N \maps x_1 \to x_2$  of $\lX$, we can find a horizontal 1-cell $M \maps a_1 \to a_2$ of $\lA$ and a 2-isomorphism $a_{N} \colon \lF(M) \to N$ in $\lX$ as in the following diagram:
+\[
+ \begin{tikzcd}
+\lF(a_1) \ar[r,"\lF(M)"]  \ar[d,"\alpha_{x_1}"'] \ar[dr,phantom,"\scriptstyle\Downarrow a_N"] & \lF(a_1) \ar[d,"\alpha_{x_2}"]\\
+ x_1 \ar[r,"N"'] & x_2
+ \end{tikzcd}
+\]
 \end{itemize}
@@
 
+\bibitem{Jacobs} B. \ Jacobs, Categorical logic and type theory, \textsl{Studies in Logic and the Foundations of Mathematics} \textbf{141}, 1999
+
+%@book {,
+%    AUTHOR = {Jacobs, Bart},
+% PUBLISHER = {North-Holland Publishing Co.},
+%   ADDRESS = {Amsterdam},
+%     PAGES = {xviii+760},
+%      ISBN = {0-444-50170-3},
+%}
+
 \bibitem{KS} G.\ Kelly and R.\ Street, Review of the elements of 2-categories, \textsl{Lecture Notes in Mathematics} vol. 40, pages 75---103, Springer Berlin/Heidelberg, 1974.

### 2020-11-25 cospans.tex
fixed typos in bibliography

@@
 
-\bibitem{CV} D.\ Cicala and C.\ Vasilakopoulou, On Adjoints and fibrations. In preparation.
+\bibitem{CV} D.\ Cicala and C.\ Vasilakopoulou, On adjoints and fibrations. In preparation.
 
@@
 
-\bibitem{Gray} J. \ Gray, Fibred and cofibred categories, \textsl{Proc.\ Conf.\ Categorical Algebra} (La Jolla, California, 1965), 21---83, New York, 1966
+\bibitem{Gray} J.
+\ Gray, Fibred and cofibred categories, \textsl{Eilenberg, Samuel, et al., eds.
+Proceedings of the Conference on Categorical Algebra: La Jolla 1965},  Springer, Berlin, 1966, pp.\ 21--83.
 
@@
 
-\bibitem{RSW} R.\ Rosebrugh, N.\ Sabadini and R.\ F.\ C.\ Walters, Generic commutative separable algebras and cospans of graphs, \textsl{Theory Appl.
-Categ.} \textbf{15} (2005), 164--177.
+\bibitem{RSW} R.\ Rosebrugh, N.\ Sabadini and R.\ F.\ C.\ Walters, Generic commutative separable algebras and cospans of graphs, \textsl{Theory Appl.\ Categ.\ }\textbf{15} (2005), 164--177.
 Available at \href{http:/.www.tac.mta.ca/tac/volumes/15/6/15-06.pdf}{http:/.www.tac.mta.ca/tac/volumes/15/6/15-06.pdf}.
@@
 
-\bibitem{Shulman2008} M.\ Shulman, Framed bicategories and monoidal fibrations, \textsl{Theory Appl.Categ.} \textbf{20} (2008), 650--738.
+\bibitem{Shulman2008} M.\ Shulman, Framed bicategories and monoidal fibrations, \textsl{Theory Appl.\ Categ.\ }\textbf{20} (2008), 650--738.
 Available as \href{https://arxiv.org/abs/0706.1286}{arXiv:0706.1286}.

### 2020-11-25 cospans.tex
fixed typo in references

@@
 
+\bibitem{GiraultValk} C.\ Girault and R.\ Valk, \textsl{Petri Nets for Systems Engineering: a Guide to Modeling, Verification, and Applications}, Springer, Berlin, 2013.
+
+\bibitem{GPS} R.\ Gordon, A.\ J.\ Power and R.\ Street, \textsl{Coherence for Tricategories}, \textsl{Mem.\ Amer.\ Math.\ Soc.\ }\textbf{558}, 1995.
+
 %\bibitem{GP1} M.\ Grandis and R.\ Par\'e, Limits in double categories, \textsl{Cah.\ Top.\ G\'eom.\ Diff.} \textbf{40} (1999), 162--220.
@@
 
-\bibitem{GiraultValk} C.\ Girault and R.\ Valk, \textsl{Petri Nets for Systems Engineering: a Guide to Modeling, Verification, and Applications}, Springer, Berlin, 2013.
-
-\bibitem{GPS} R.\ Gordon, A.\ J.\ Power and R.\ Street, \textsl{Coherence for Tricategories}, \textsl{Mem.\ Amer.\ Math.\ Soc.\ }\textbf{558}, 1995.
-
 \bibitem{Gray} J.
-\ Gray, Fibred and cofibred categories, \textsl{Eilenberg, Samuel, et al., eds.
-Proceedings of the Conference on Categorical Algebra: La Jolla 1965},  Springer, Berlin, 1966, pp.\ 21--83.
+\ Gray, Fibred and cofibred categories, in \textsl{Proceedings of the Conference on Categorical Algebra: La Jolla 1965}, eds.\ S.\ Eilenberg \textit{et al}, Springer, Berlin, 1966, pp.\ 21--83.
 

### 2020-11-25 cospans.tex
small fixes

@@
 
-\begin{lem}[Hermida] \label{lem:fibrewiselimits}
+\begin{lem}[\textbf{Hermida}] \label{lem:fibrewiselimits}
 Suppose $\J$ is a small category and $U\maps\X\to\A$ is an opfibration. If the base $\A$ has $\J$-colimits,
@@
 
-\begin{lem}[Gray] \label{prop:opfibtolari}
+\begin{lem}[\textbf{Gray}] \label{prop:opfibtolari}
   Let $U \maps\X \to \A$ be an opfibration. Then
@@
 \begin{proof}  
-This is due to Grothendieck; a proof can be found, for example, in \cite[\S~1.10]{Jacobs}.
+The idea goes back to Grothendieck; a proof can be found in, for example, \cite[Section 1.10]{Jacobs}.
 \end{proof}

### 2020-11-26 cospans.tex
tiny in refs
edits re Kenny's comments

@@
 a\ar[r,"i"]\ar[d,"f"'] & m\ar[d,"h"] & b\ar[l,"o"']\ar[d,"g"]  & x\in F(m) \\
-a'\ar[r,"{i'}"]\ar[d,"{f'}"] & m'\ar[d,"{h'}"] & b'\ar[l,"{o'}"']\ar[d,"{g'}"] & x'\in F(m') \\
+a'\ar[r,"{i'}"]\ar[d,"{f'}"'] & m'\ar[d,"{h'}"] & b'\ar[l,"{o'}"']\ar[d,"{g'}"] & x'\in F(m') \\
 a''\ar[r,"{i''}"] & m'' & b''\ar[l,"{o''}"'] & x''\in F(m'')
@@
 (B) edge node [above] {$j_m$} (F)
-(D) edge node [above] {$j_{n}'$} (F)
+(D) edge node [above] {$j_{n}$} (F)
 (F) edge node [left] {$\psi$} (G)
@@
 together with an isomorphism $F(\alpha)((x_1 \odot x_2) \odot x_3) \cong (x_1 \odot (x_2 \odot x_3))$ between the decorations 
-\begin{gather*}
-\scalebox{.8}{$\one\xrightarrow{x_1\times x_2}F(m_1)\times F(m_2)\xrightarrow{\phi}F(m_1+m_2)\to F(m_1+_bm_2)\xrightarrow{1\times x_3}F(m_1+_bm_2)\times F(m_3)\xrightarrow{\phi}F((m_1+_bm_2)+m_3)\to F((m_1+_bm_2)+_cm_3)\cong F(m_1+_b(m_2+_cm_3))$} \\
-\scalebox{.8}{$\one\xrightarrow{x_2\times x_3}F(m_2)\times F(m_3)\xrightarrow{\phi}F(m_2+m_3)\to F(m_2+_cm_3)\xrightarrow{x_1\times1}F(m_1)\times F(m_2+_cm_3)\xrightarrow{\phi}F(m_1\times(m_2+_cm_3))\to F(m_1+_b(m_2+_cm_3))$}
-\end{gather*}
+\begin{align*}
+\scalebox{.8}{$\one\xrightarrow{x_1\times x_2}F(m_1)\times F(m_2)\xrightarrow{\phi}F(m_1+m_2)\to F(m_1+_bm_2)\xrightarrow{1\times x_3}F(m_1+_bm_2)\times F(m_3)\xrightarrow{\phi}F((m_1+_bm_2)+m_3)$}&\scalebox{.8}{$\to F((m_1+_bm_2)+_cm_3)$} \\
+&\scalebox{.8}{$\stackrel{F(\alpha)}{\cong} F(m_1+_b(m_2+_cm_3))$} \\
+\scalebox{.8}{$\one\xrightarrow{x_2\times x_3}F(m_2)\times F(m_3)\xrightarrow{\phi}F(m_2+m_3)\to F(m_2+_cm_3)\xrightarrow{x_1\times1}F(m_1)\times F(m_2+_cm_3)\xrightarrow{\phi}F(m_1\times(m_2+_cm_3))$}&\scalebox{.8}{$\to F(m_1+_b(m_2+_cm_3))$}
+\end{align*}
 which is constructed by pasting structure isomorphisms like above.
@@
 
-%\bibitem{Ehresmann63} C.\ Ehresmann, Cat\'egories structur\'ees III: Quintettes et applications covariantes,  \textsl{Cah.\ Top.\ G\'eom.\ Diff.} \textbf{5} (1963), 1--22.
-
 %\bibitem{Ehresmann65} C.\ Ehresmann, {\sl Cat\'egories et Structures,} Dunod, Paris, 1965.
@@
 
-\bibitem{Herm} C. \ Hermida, \textsl{Fibrations, Logical Predicates and Undeterminates}, Ph.D.\ thesis, Deparment of Mathematics, University of Edinburgh, 1993.
-
 \bibitem{Hermida1999} C. \ Hermida, Some properties of Fib as a fibred 2-category, \textsl{J.\ Pure Appl.\ Alg.\ } \textbf{134}, 83 -- 109, 1999
@@
 \bibitem{Jacobs} B. \ Jacobs, Categorical logic and type theory, \textsl{Studies in Logic and the Foundations of Mathematics} \textbf{141}, 1999
-
-%@book {,
-%    AUTHOR = {Jacobs, Bart},
-% PUBLISHER = {North-Holland Publishing Co.},
-%   ADDRESS = {Amsterdam},
-%     PAGES = {xviii+760},
-%      ISBN = {0-444-50170-3},
-%}
 

### 2020-11-26 cospans.tex
a first take on related work

@@
 
-In this section we present several examples.  The first was mentioned in the Introduction.
+In this section we present several examples, drawing the relation between the formalisms of structured and decorated cospans.
+Before we exhibit these formalisms in action, let us briefly remark that this work is part of a more general endeavor to apply categorical ideas to the theory and analysis of systems in a broad sense.
+Various capproaches to different problems have been followed; thinking about systems and processes categorically dates back to early works like \cite{Lawvere,JNW,BF2,KSW} and references therein.
+As mentioned in the introduction, the current material constitutes part of the line of work initiated by Fong \cite{Fong,FongThesis} and evolved and applied in different settings through a number of publications (here cite papers/theses that surround decorated and structured cospans in a broad sense).
+A different line of work employs algebras of wiring diagrams and sheaves to capture compositional and time features of dynamical systems, initiated by Spivak and progressed also onto cyber-physical directions \cite{VSL,SSV,BFV}.
+(Another line of work could be props used for systems?
+John?) Another approach uses graphical languages and signal flow diagrams \cite{FRS,BPSZ} to understand systems of a more behavioral taste \cite{Willems}.
+
+Having discussed some by no means exhaustive related work in the field, we are ready to set out to the examples of our framework.
 
@@
 
+{\chris Shouldn't we give Shulman's result that the horizontal bicategory of a symmetric monoidal double category is symmetric monoidal?}
+
 \begin{thebibliography}{100}
@@
 
+\bibitem{BFV} G.\ Bakirtzis, C.\ H.\ Fleming and C.\ Vasilakopoulou, Categorical Semantics of Cyber-Physical Systems Theory. Available as 
+\href{https://arxiv.org/abs/2010.08003}{arXiv:2010.08003}.
+
+\bibitem{BPSZ} F.\ Bonchi, R.\ Piedeleu, P.\ Sobocinski and F.\ Zanasi, Contextual Equivalence for Signal Flow Graphs, \textsl{FoSSaCS} (2020).
+Available as \href{https://arxiv.org/abs/2002.08874}{arXiv:2002.08874}.
+
 \bibitem{Borc} F. \ Borceux, \textsl{Handbook of Categorical Algebra}, vol.\ 2, 
@@
 %\bibitem{Brown2} R.\ Brown, K.\ Hardie, H.\ Kamps and T.\ Porter, The homotopy double groupoid of a Hausdorff space, \textsl{Th.\ Appl.\ Categ.} \textbf{10} (2002), 71--93.
+
+\bibitem{BF2} M.\ Bunge and M.\ Fiore, Unique factorisation lifting functors and categories of linearly-controlled processes, \textsl{Math.\ Struct.\ Comput.\ Sci.\ } \textbf{10} (2000), 137--163.
 
@@
 
+\bibitem{FRS} B.\ Fong, P.\ Rapisarda, P.\ Sobocinski, \textsl{A categorical approach to open and interconnected dynamical systems}, LICS, 2016.
+Available as \href{http://arxiv.org/abs/510.05076}{arXiv:1510.05076}.
+
 \bibitem{GiraultValk} C.\ Girault and R.\ Valk, \textsl{Petri Nets for Systems Engineering: a Guide to Modeling, Verification, and Applications}, Springer, Berlin, 2013.
@@
 
+\bibitem{JNW} A.\ Joyal, M.\ Nielsen and G.\ Winskel, Bisimulation from Open Maps, \textsl{Information and Computation} \textbf{127} (1996) 164 -- 185.
+
+\bibitem{KSW} P.\ Katis, N.\ Sabadini and R.\ F.\ C.\ Walters, On the algebra of systems with feedback and boundary, \textsl{Rendiconti del Circolo Matematico di Palermo Serie II} \textbf{63} (2000) 123 -- 156.
+
 \bibitem{KS} G.\ Kelly and R.\ Street, Review of the elements of 2-categories, \textsl{Lecture Notes in Mathematics} vol. 40, pages 75---103, Springer Berlin/Heidelberg, 1974.
+
+\bibitem{Lawvere} F.\ W.\ Lawvere, State categories and response functors, unpublished manuscript (1986)
 
@@
 
+\bibitem{SSV} P.\ Schultz, D.\ Spivak and C.\ Vasilakopoulou, Dynamical systems and sheaves, \textsl{Appl.\ Cat.\ Struct.\ }\textbf{28} (2020), 1--57.
+Available as \href{https://arxiv.org/abs/1609.08086}{arXiv:1609.08086}.
+
 \bibitem{Shulman2008} M.\ Shulman, Framed bicategories and monoidal fibrations, \textsl{Theory Appl.\ Categ.\ }\textbf{20} (2008), 650--738.
@@
 
+\bibitem{VSL} D.\ Vagner, D.\ Spivak and E.\ Lerman, Algebras of open dynamical systems on the operad of wiring diagrams, \textsl{Theory Appl.\ Categ.\ } \textbf{30} (2015), 1793--1822.
+Available as \href{https://arxiv.org/abs/1408.1598}{arXiv:1408.1598}.
+
+\bibitem{Willems} J.\ C.\ Willems, The behavioral approach to open and interconnected systems, \textsl{IEEE Control Systems Magazine} (2007)
+
 \end{thebibliography}

### 2020-11-26 cospans.tex
fixed Definition A.10 - monoidal double category

@@
 A \define{monoidal double category} is a pseudomonoid in $\Dbl$. 
-Explicitly, it is a double category equipped with double functors $\otimes \maps \lD \times \lD \to \lD$ and $I \maps 1 \to \lD$ where $1$ is the terminal double category, along with invertible transformations called the \define{associator}:
-\[  \alpha \maps \otimes \, \circ \; (1_{\lD} \times \otimes ) \Rightarrow \otimes \; \circ \; (\otimes \times 1_{\lD}) ,\]
-\define{left unitor}:
-\[ \ell \maps \otimes \, \circ \; (1_{\lD} \times I) \Rightarrow 1_{\lD} ,\]
-and \define{right unitor}:
-\[ r \maps \otimes \,\circ\; (I \times 1_{\lD}) \Rightarrow 1_{\lD} \]
-satisfying the pentagon and triangle identities.
 \end{defn}
+
+This definition neatly packages a large quantity of information.   When we unpack it, we see a monoidal double category is a double category $\lD$ with:
+\begin{itemize}
+\item monoidal structures on both $\lD_0$
+and $\lD_1$, each with tensor product $\otimes$, associator $a$, left unitor $\ell$ and right unitor $r$, obeying the pentagon and triangle identities,
+\item the structure of a double functor on $\otimes$:
+that is, invertible globular 2-morphisms
+\[ \chi \maps (M_1\otimes N_1)\odot (M_2\otimes N_2) \xrightarrow{\sim}
+(M_1\odot M_2)\otimes (N_1\odot N_2)\]
+\[ \mu \maps U_{A\otimes B} \xrightarrow{\sim} (U_A \otimes U_B)\]
+\end{itemize}
+These structures must obey a number of equations, which can be found after \cite[Definition 2.10]{HS} and also \cite[Definition A.5]{BC}.
 

### 2020-11-26 cospans.tex
worked on Theorems 2.1, 2.2, 2.3.

@@
 \begin{thm}\label{thm:decorated_cospans}
-Let $\A$ be a category with finite colimits and $F \maps \A \to \Cat$ a lax monoidal pseudofunctor. Then there exists a double category $F\lCsp$ in which
+Let $\A$ be a category with finite colimits, made monoidal with a choice of initial object and binary coproducts.
+Let $F \maps (\A,+) \to (\Cat,\times)$ be a lax monoidal pseudofunctor.
+Then there exists a double category $F\lCsp$ in which
 \begin{itemize}
@@
 \begin{proof}
-According to \cref{defn:double_category}, for a lax monoidal pseudofunctor $(F,\phi,\phi_0)$ we will define the category of objects $F\lCsp_0$, the category of arrows $F\lCsp_1$, as well as the four structure functors which tie them together: the source and target functors $S,T \colon F\lCsp_1 \to F\lCsp_0$, the composition functor $\odot \colon F\lCsp_1 \times_{F\lCsp_0} F\lCsp_1 \to F\lCsp_1$ and the unit functor $U \colon F\lCsp_0 \to F\lCsp_1$.
-
-The category of objects $F\lCsp_0$ is simply the category $\A$, whereas $F$-decorated cospans and maps between them form the category of arrows $F\lCsp_1$.
+Take $\A$ to have finite colimits and let $(F,\phi,\phi_0) \maps (A,+,0) \to (\Cat,\times, 1)$ be a lax monoidal pseudofunctor as defined in \cref{defn:double_category}.
+We shall define the category of objects $F\lCsp_0$, the category of arrows $F\lCsp_1$, as well as the four structure functors which tie them together: the source and target functors $S,T \colon F\lCsp_1 \to F\lCsp_0$, the composition functor $\odot \colon F\lCsp_1 \times_{F\lCsp_0} F\lCsp_1 \to F\lCsp_1$ and the unit functor $U \colon F\lCsp_0 \to F\lCsp_1$.
+
+The category of objects $F\lCsp_0$ is simply $\A$, whereas $F$-decorated cospans and maps between them form the category of arrows $F\lCsp_1$.
 The (vertical) composition of two $F$-decorated cospans maps is
@@
 Similarly the right and left unitors can be constructed, and all data satisfy the axioms of a double category -- essentially breaking down to those of the cospan double category of $\A$ and axioms of the lax monoidal pseudofunctor $F$.
-For full details of these arguments, see \cite[Theorem~4.1.1]{CourserThesis}.
+For full details of these arguments, see the second author's thesis \cite[Theorem~4.1.1]{CourserThesis}.
 \begin{comment}
@@
 \begin{thm}\label{DC}
-Let $\A$ be a category with finite colimits and $F \maps \A \to \Cat$ a symmetric lax monoidal pseudofunctor.
+Let $\A$ be a category with finite colimits, made symmetric monoidal with a choice of initial object and binary coproducts.
+Let $F \maps (\A,+)\to (\Cat,\times)$ be symmetric lax monoidal pseudofunctor.
 Then the double category $F\lCsp$ of Theorem \ref{thm:decorated_cospans} is symmetric monoidal, where
@@
 \begin{proof}
-The definition of symmetric monoidal double category may be found in Definition \ref{defn:symmetric_monoidal_double_category}.
-We must show that both the category of objects $F\lCsp_0$ and the category of arrows $F\lCsp_1$ are symmetric monoidal categories, show that the monoidal unit of $F\lCsp_0$ is preserved by the unit functor $U$, show that the source and target functors $S,T \colon F\lCsp_1 \to F\lCsp_0$ are strict symmetric monoidal functors which preserve the associativity and unit constraints, define the globular isomorphisms $\chi$ and $\mu$ that relate how composition and units interact with the tensor product, and check that the required axioms are satisfied.
+Monoidal and symmetric monoidal double categories are introduced in Definitions \ref{defn:monoidal_double_category} and \ref{defn:symmetric_monoidal_double_category}.
+To make $F\lCsp$ into a symmetric monoidal double category, we must show that both the category of objects $F\lCsp_0$ and the category of arrows $F\lCsp_1$ are symmetric monoidal, show that the monoidal unit of $F\lCsp_0$ is preserved by the unit functor $U$, show that the source and target functors $S,T \colon F\lCsp_1 \to F\lCsp_0$ are strict symmetric monoidal functors which preserve the associativity and unit constraints, define the globular isomorphisms $\chi$ and $\mu$ that relate how composition and units interact with the tensor product, and check that the required axioms are satisfied.
 
@@
 \node (C) at (2,0) {$0$};
-\node (D) at (3,0) {$\bot_0 = \phi \in F(0)$};
+\node (D) at (3,0) {$\bot_0 \in F(0)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-where $0$ is the monoidal unit of $\A$ and $\phi \maps 1 \to F(0)$ is the morphism which is part of the structure of the symmetric lax monoidal pseudofunctor $F \maps \A \to \Cat$.
+where $0$ is the monoidal unit of $\A$ and the element $\bot_0$ is another name for $\phi \maps 1 \to F(0)$, the morphism that arises from the lax monoidal structure of $F \maps (\A,+) \to (\Cat,\times)$.
 It is also clear that $U(0)=0_{F\lCsp_1}$.
@@
 \]
-where $(x_1+x_2)+x_3 \maps 1 \to F((m_1+m_2)+m_3)$ is given by: $$1 \xrightarrow{(x_1 \times x_2) \times x_3} (F(m_1) \times F(m_2)) \times F(m_3) \xrightarrow{\phi_{m_1,m_2} \times 1} F(m_1+m_2) \times F(m_3) \xrightarrow{\phi_{m_1+m_2,m_3}} F((m_1+m_2)+m_3).$$ The other parenthesization $M_1 \otimes (M_2 \otimes M_3)$ is given by:
+where $(x_1+x_2)+x_3 \maps 1 \to F((m_1+m_2)+m_3)$ is the composite
+\[ 1 \xrightarrow{(x_1 \times x_2) \times x_3} (F(m_1) \times F(m_2)) \times F(m_3) \xrightarrow{\phi_{m_1,m_2} \times 1} F(m_1+m_2) \times F(m_3) \xrightarrow{\phi_{m_1+m_2,m_3}} F((m_1+m_2)+m_3).\] 
+The other parenthesization $M_1 \otimes (M_2 \otimes M_3)$ is given by:
 \[
@@
 \]
-where $x_1+(x_2+x_3) \maps 1 \to F(m_1+(m_2+m_3))$ is given by: $$1 \xrightarrow{x_1 \times (x_2 \times x_3)} F(m_1) \times (F(m_2) \times F(m_3)) \xrightarrow{1 \times \phi_{m_2,m_3}} F(m_1) \times F(m_2+m_3) \xrightarrow{\phi_{m_1,m_2+m_3}} F(m_1+(m_2+m_3)).$$
-Denoting the associator of $(\A,+,0)$ by $\alpha$, the associator of $F\lCsp_1$ is then a map of cospans in $\A$ from $(M_1 \otimes M_2) \otimes M_3$ to $M_1 \otimes (M_2 \otimes M_3)$ given by:
+where the element $x_1+(x_2+x_3) \maps 1 \to F(m_1+(m_2+m_3))$ is the composite
+\[  1 \xrightarrow{x_1 \times (x_2 \times x_3)} F(m_1) \times (F(m_2) \times F(m_3)) \xrightarrow{1 \times \phi_{m_2,m_3}} F(m_1) \times F(m_2+m_3) \xrightarrow{\phi_{m_1,m_2+m_3}} F(m_1+(m_2+m_3)).\]
+Denoting the associator of $(\A,+,0)$ by $\alpha$, the associator of $F\lCsp_1$ is then the map of cospans in $\A$ from $(M_1 \otimes M_2) \otimes M_3$ to $M_1 \otimes (M_2 \otimes M_3)$ given by
 \[
@@
 The right unitor is similar, and one can check that the associator and left and right unitors together satisfy the pentagon and triangle identities of a monoidal category.
-See the second author's thesis \cite{CourserThesis} for more details.
+For more details se the second author's thesis \cite[Theorem 4.1.3]{CourserThesis}.
 
@@
 \]
-where the decoration $(x_1+y_1) \odot (x_2+y_2) \in F((m_1+n_1)+_{b+b'}(m_2+n_2))$ is given by:
+where the decoration $(x_1+y_1) \odot (x_2+y_2) \in F((m_1+n_1)+_{b+b'}(m_2+n_2))$ is the composite
 %$$\scriptscriptstyle{1 \xrightarrow{(\lambda^{-1} \times \lambda^{-1})\lambda^{-1}} (1 \times 1) \times (1 \times 1) \xrightarrow{(x_1 \times y_1) \times (x_2 \times y_2)} (F(m_1) \times F(n_1)) \times (F(m_2) \times F(n_2)) \xrightarrow{\phi_{m_1,n_1} \times \phi_{m_2,n_2}} F(m_1+n_1) \times F(m_2+n_2)} \xrightarrow{\phi_{m_1+n_1,m_2+n_2}} F((m_1+n_1)+(m_2+n_2)) \xrightarrow{F(\psi)} F((m_1+n_1)+_{b+b'}(m_2+n_2))$$
-$$\scriptstyle{1 \xrightarrow{} (F(m_1) \times F(n_1)) \times (F(m_2) \times F(n_2)) \xrightarrow{\phi_{m_1,n_1} \times \phi_{m_2,n_2}} F(m_1+n_1) \times F(m_2+n_2)} \xrightarrow{\phi_{m_1+n_1,m_2+n_2}} F((m_1+n_1)+(m_2+n_2)) \xrightarrow{F(\psi)} F((m_1+n_1)+_{b+b'}(m_2+n_2))$$
-where the first arrow is given by $$1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{\lambda^{-1} \times \lambda^{-1}} (1 \times 1) \times (1 \times 1) \xrightarrow{(x_1 \times y_1) \times (x_2 \times y_2)} (F(m_1) \times F(n_1)) \times (F(m_2) \times F(n_2)).$$
+\[ \scriptstyle{1 \xrightarrow{} (F(m_1) \times F(n_1)) \times (F(m_2) \times F(n_2)) \xrightarrow{\phi_{m_1,n_1} \times \phi_{m_2,n_2}} F(m_1+n_1) \times F(m_2+n_2)} \xrightarrow{\phi_{m_1+n_1,m_2+n_2}} F((m_1+n_1)+(m_2+n_2)) \xrightarrow{F(\psi)} F((m_1+n_1)+_{b+b'}(m_2+n_2)) \]
+where the first arrow is given by 
+\[ 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{\lambda^{-1} \times \lambda^{-1}} (1 \times 1) \times (1 \times 1) \xrightarrow{(x_1 \times y_1) \times (x_2 \times y_2)} (F(m_1) \times F(n_1)) \times (F(m_2) \times F(n_2)).\]
 %\[
@@
 
-The remaining properties are coherence laws that make use of these maps $\chi$ and $\mu$, the previously defined symmetric monoidal structure maps $\alpha,\lambda,\rho$ and $\beta$ and the double category structure functors $U$ and $\odot$.
-We exhibit one of these laws to give the reader a sense of how they are verified, with more details available in the second author's thesis \cite{CourserThesis}.
+The remaining properties are coherence laws that make use of these maps $\chi$ and $\mu$, the previously defined symmetric monoidal structure maps $a,\ell,r$ and $\beta$ and the double category structure functors $U$ and $\odot$.
+We exhibit one of these laws to give the reader a sense of how they are verified, with more details available in \cite[Theorem 4.1.3]{CourserThesis}.
 The coherence law that we check says that this diagram commutes:
@@
 We will see that this diagram commutes in two stages.
-First, for the underlying maps of cospans in $\A$.
+First we consider the underlying maps of cospans in $\A$.
 Using the notation previously introduced for the globular 2-morphism $\hat{\chi}$, the above diagram, modulo all of the decorations, is given by the following `flattened' commutative diagram in the symmetric monoidal double category $\lCsp(\A)$, where the top and the bottom cospans coincide.
@@
 as the above diagram of maps of cospans commutes in $\A$ and then applying the pseudofunctor $F$ to this diagram yields a commutative diagram in $\Cat$. 
-The other diagrams in the definition of symmetric monoidal double category can be shown to commute similarly.
 \end{proof}
@@
 \item monoidal structures on both $\lD_0$
-and $\lD_1$, each with tensor product $\otimes$, associator $a$, left unitor $\ell$ and right unitor $r$, obeying the pentagon and triangle identities,
+and $\lD_1$, each with tensor product denoted $\otimes$, associator $a$, left unitor $\ell$ and right unitor $r$, such that the unit object of $\lD_0$ is preserved by the unit functor $U$, and the source and target functors $S,T \maps \lD_1 \to \lD_0$ are strict symmetric monoidal,
 \item the structure of a double functor on $\otimes$:
@@
 
-Unpacking these definitions further one obtains a large number of diagrams \cite{HS}.
+Unpacking this definition one obtains a number of diagrams which can be found after \cite[Definition 2.4]{HS}.
 

### 2020-11-26 cospans.tex
Worked on Theorems 2.1, 2.2, 2.3.

@@
 Monoidal and symmetric monoidal double categories are introduced in Definitions \ref{defn:monoidal_double_category} and \ref{defn:symmetric_monoidal_double_category}.
-To make $F\lCsp$ into a symmetric monoidal double category, we must show that both the category of objects $F\lCsp_0$ and the category of arrows $F\lCsp_1$ are symmetric monoidal, show that the monoidal unit of $F\lCsp_0$ is preserved by the unit functor $U$, show that the source and target functors $S,T \colon F\lCsp_1 \to F\lCsp_0$ are strict symmetric monoidal functors which preserve the associativity and unit constraints, define the globular isomorphisms $\chi$ and $\mu$ that relate how composition and units interact with the tensor product, and check that the required axioms are satisfied.
+To make $F\lCsp$ into a symmetric monoidal double category, we must show that both the category of objects $F\lCsp_0$ and the category of arrows $F\lCsp_1$ are symmetric monoidal, show that the monoidal unit of $F\lCsp_0$ is preserved by the unit functor $U \maps F\lCsp_0 \to F\lCsp_1$, show that the source and target functors $S,T \colon F\lCsp_1 \to F\lCsp_0$ are strict symmetric monoidal, define the globular isomorphisms $\chi$ and $\mu$ that relate how composition and units interact with the tensor product, and check that the required axioms are satisfied.
 

### 2020-11-26 cospans.tex
changes to Section 5.1 - lax monoidal pseudofunctor stuff

@@
 
-In general, decorated cospans involve a pseudofunctor to $\Cat$, but in this example there is actually an honest functor $F \maps \Set \to \Cat$ that assigns to a set $N$ the above category $F(N)$.
+In general, decorated cospans involve a pseudofunctor to $\Cat$, but in this example there is actually an honest functor $F \maps \Fin\Set \to \Cat$ that assigns to a set $N$ the above category $F(N)$.
 Given a function $f \maps M \to N$, we define $F(f) \maps F(M) \to F(N)$ to any graph structure $s,t \maps E \to M$ to the graph structure $f s, f t \maps E \to N$.
@@
 In other words, it sends a pair of graph structures to their `disjoint union'.
-MORE ABOUT THE WEAK MONOIDALITY!!!
+Even though $F \maps \Fin\Set \to \Cat$ is a functor (e.g., composition is strictly preserved), this choice of $\phi_0$ and $\phi_{N,N'}$ does not make $F$ into a symmetric lax monoidal functor, since the required laws hold only up to a natural isomorphism.
+See \cite[Section 5]{BC} for a proof that these laws fail to hold `on the nose'.
+This fact necessitates a generalization of Fong's original formalism.
 

### 2020-11-26 cospans.tex
wrorked on Section 5.1 - lax monoidal pseudofunctor

@@
 In other words, it sends a pair of graph structures to their `disjoint union'.
-Even though $F \maps \Fin\Set \to \Cat$ is a functor (e.g., composition is strictly preserved), this choice of $\phi_0$ and $\phi_{N,N'}$ does not make $F$ into a symmetric lax monoidal functor, since the required laws hold only up to a natural isomorphism.
-See \cite[Section 5]{BC} for a proof that these laws fail to hold `on the nose'.
+Surprisngly, though $F \maps \Fin\Set \to \Cat$ is a functor---for example, composition is strictly preserved---this choice of $\phi_{N,N'}$ does not make $F$ into a symmetric lax monoidal functor, since the required laws hold only up to natural isomorphism.
+See \cite[Section 5]{BC} for a proof that these laws fail to hold on the nose.
 This fact necessitates a generalization of Fong's original formalism.

### 2020-11-26 cospans.tex
work on Section 5.1 - lax monoidal pseudofunctor

@@
 In other words, it sends a pair of graph structures to their `disjoint union'.
-Surprisngly, though $F \maps \Fin\Set \to \Cat$ is a functor---for example, composition is strictly preserved---this choice of $\phi_{N,N'}$ does not make $F$ into a symmetric lax monoidal functor, since the required laws hold only up to natural isomorphism.
+Surprisngly, though $F$ is a functor---for example, composition is strictly preserved---this choice of $\phi_{N,N'}$ does not make $F$ into a symmetric lax monoidal functor, since the required laws hold only up to natural isomorphism.
 See \cite[Section 5]{BC} for a proof that these laws fail to hold on the nose.

### 2020-11-26 cospans.tex
Trying to help with Section 5.4

@@
 %%% Do reaction networks and dynamical systems (which do NOT come from structured cospans).
+A dynamical system is a vector field from the perspective of a system of first-order ordinary differential equations.
+Chemical reaction networks are a specific kind of dynamical system in which the vector field is algebraic, meaning that its coefficients are polynomials.
+Using Fong's original incarnation of decorated cospans, Pollard and the first author \cite{BP} constructed a symmetric monoidal category $\mathsf{OpenDynam}$ for which the morphisms are open dynamical systems.
+This category $\mathsf{OpenDynam}$ has:
+\begin{itemize}
+\item{objects as finite sets, and}
+\item{morphisms as equivalence classes of cospans of finite sets whose apices are equipped with an algebraic vector field.
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (D) at (-3,0) {$a$};
+\node (E) at (-2,0) {$s$};
+\node (F) at (-1,0) {$b$};
+\node (A) at (0,0) {$v_s \colon \lR^s \to \lR^s$};
+\path[->,font=\scriptsize,>=angle 90]
+(D) edge node [above] {$i$} (E)
+(F) edge node [above] {$o$} (E);
+\end{tikzpicture}
+\]
+}
+\end{itemize}
+This category is constructed from a symmetric lax monoidal functor $F \colon \Fin\Set \to \Set$ that assigns to a finite set $s$ the set $F(s)$ of algebraic vector fields on $s$ and a to function $f \colon s \to s'$ the function $F(f) \colon F(s) \to F(s')$ defined by $$F(f)(v_s)=f_* v_s f^*$$
+where $f^\ast \colon \mathbb{R}^{s'} \to \mathbb{R}^{s}$ is the \define{pullback} defined by 
+$$f^\ast (c_{s'})(\sigma)=c_{s}(f(\sigma))$$ 
+and $f_{\ast} \colon \mathbb{R}^s \to \mathbb{R}^{s'}$ is the \define{pushforward} defined by 
+$$f_{\ast}(c_{s'})(\sigma^\prime) = \sum_{\{\sigma \in s : \; f(\sigma) = \sigma^\prime\}} c_{s}(\sigma)$$
+for $c_{s} \in \mathbb{R}^{s}$ and $c_{s'} \in \mathbb{R}^{s'}$
+Functoriality of $F$ comes the pushforward being covariant and the pullback being contravariant, and the lax monoidal structure of $F$ stems from the canonical isomorphism $\lR^s \times \lR^{s'} \cong \lR^{s+s'}$ which is used to map a pair of vector fields $v_s \colon \lR^s \to \lR^{s}$ and $v_{s'} \colon \lR^{s'} \to \lR^{s'}$ to the vector field $v_{s+s'} \colon \lR^{s+s'} \to \lR^{s+s'}$.
+We now show that open dynamical systems of this nature are an example of open systems that are able to be characterized by decorated cospans but not structured cospans.
+
+Let $\mathsf{Dynam}$ be the category for which:
+\begin{itemize}
+\item{an object is a pair $(s,v_s)$ where $s$ is a finite set and $v_s$ is an algebraic vector field $v_s \colon \lR^s \to \lR^s$ on the finite set $s$, and}
+\item{a morphism from $(s,v_s)$ to $(s',v_{s'})$ is a function $f \colon s \to s'$ such that $v_{s'} = f_* v_s f^*$.}
+\end{itemize}
+
+A well-known result is the following:
+\begin{lem}
+A functor $U \colon \A \to \X$ admits a left adjoint if and only if for every $x \in \X$, the comma category $x \downarrow U$ has an initial object.
+\end{lem}
+Using this result, one can show that the forgetful functor $U \colon \mathsf{Dynam} \to \Fin\Set$ is not a right adjoint.
+In particular, by taking $x$ to be the empty set, the comma category $\emptyset \downarrow U$ has:
+\begin{itemize}
+\item{objects given as pairs $((s,v_s),! \colon \emptyset \to s)$, and}
+\item{a morphism from $((s,v_s),!
+\colon \emptyset \to s)$ to $((s',v_{s'}),!
+\colon \emptyset \to s')$ is a morphism $f \colon (s,v_s) \to (s',v_{s'})$ in $\mathsf{Dynam}$ such that $U(f) \circ !
+= !$ in $\Fin\Set$, a condition which amounts to simply being a morphism in $\mathsf{Dynam}$.}
+\end{itemize}
+In particular, the object $((\emptyset,v_\emptyset),!
+\colon \emptyset \to \emptyset)$ resides in the comma category $\emptyset \downarrow U$, where $v_\emptyset$ is the only possible vector field on the empty set --- namely, the dengerate vector field.
+Given any other object $((s,v_s),!
+\colon \emptyset \to s)$ in $\emptyset \downarrow U$, there exists no morphisms $!
+\colon \emptyset \to s$ from the first object to the second unless $s$ is also the empty set as the vector field $$!_* v_\emptyset !^*$$will also always be degenerate and not equal to $v_s$.
+Clearly there are also no morphisms in the other direction for $s \neq \emptyset$ as $f$ must be a function.
+Thus the forgetful functor $U$ has no left adjoint $L \colon \Fin\Set \to \mathsf{Dynam}$, and hence we cannot construct a structured cospan category ${_L \Csp(\mathsf{Dynam})}$ whose morphisms are equivalence classes of open dynamical systems of this type.
 

### 2020-11-27 cospans.tex
More on lax monoidal pseudofunctors in Section 5.1

--- 2020-11-26 cospans.tex
@@
 In other words, it sends a pair of graph structures to their `disjoint union'.
-Surprisngly, though $F$ is a functor---for example, composition is strictly preserved---this choice of $\phi_{N,N'}$ does not make $F$ into a symmetric lax monoidal functor, since the required laws hold only up to natural isomorphism.
+Surprisingly, though $F$ is a functor---for example, composition is strictly preserved---this choice of $\phi_{N,N'}$ does not make $F$ into a symmetric lax monoidal functor, since it obeys the required laws only up to natural isomorphism, as in Equation \cref{eq:omega}.
 See \cite[Section 5]{BC} for a proof that these laws fail to hold on the nose.
-This fact necessitates a generalization of Fong's original formalism.
+This fact necessitates a generalization of Fong's original approach to decorated cospans.
 

### 2020-11-27 cospans.tex
Added a diagram for the associator for horizontal 1-cell composition in Theorem 2.2

--- 2020-11-26 cospans.tex
@@
 \begin{thm}\label{thm:decorated_cospans}
-Let $\A$ be a category with finite colimits, made monoidal with a choice of initial object and binary coproducts.
-Let $F \maps (\A,+) \to (\Cat,\times)$ be a lax monoidal pseudofunctor.
-Then there exists a double category $F\lCsp$ in which
+Let $\A$ be a category with finite colimits and $F \maps \A \to \Cat$ a lax monoidal pseudofunctor. Then there exists a double category $F\lCsp$ in which
 \begin{itemize}
@@
 \begin{proof}
-Take $\A$ to have finite colimits and let $(F,\phi,\phi_0) \maps (A,+,0) \to (\Cat,\times, 1)$ be a lax monoidal pseudofunctor as defined in \cref{defn:double_category}.
-We shall define the category of objects $F\lCsp_0$, the category of arrows $F\lCsp_1$, as well as the four structure functors which tie them together: the source and target functors $S,T \colon F\lCsp_1 \to F\lCsp_0$, the composition functor $\odot \colon F\lCsp_1 \times_{F\lCsp_0} F\lCsp_1 \to F\lCsp_1$ and the unit functor $U \colon F\lCsp_0 \to F\lCsp_1$.
-
-The category of objects $F\lCsp_0$ is simply $\A$, whereas $F$-decorated cospans and maps between them form the category of arrows $F\lCsp_1$.
+According to \cref{defn:double_category}, for a lax monoidal pseudofunctor $(F,\phi,\phi_0)$ we will define the category of objects $F\lCsp_0$, the category of arrows $F\lCsp_1$, as well as the four structure functors which tie them together: the source and target functors $S,T \colon F\lCsp_1 \to F\lCsp_0$, the composition functor $\odot \colon F\lCsp_1 \times_{F\lCsp_0} F\lCsp_1 \to F\lCsp_1$ and the unit functor $U \colon F\lCsp_0 \to F\lCsp_1$.
+
+The category of objects $F\lCsp_0$ is simply the category $\A$, whereas $F$-decorated cospans and maps between them form the category of arrows $F\lCsp_1$.
 The (vertical) composition of two $F$-decorated cospans maps is
@@
 \end{align*}
-which is constructed by pasting structure isomorphisms like above.
+%%% Kenny: I think we should call this \alpha something else like \kappa, since it's only a component used in building the associator for horizontal composition (which we are calling \alpha), not the entire thing on its own.
+\[
+\begin{tikzpicture}[scale=1.7]
+\node (A) at (3.75,0) {$\scriptstyle{\cong \tau_a}$};
+\node (D) at (3,0) {$\scriptstyle{\one}$};
+\node (E) at (6.25,0.5) {$\scriptstyle{F(m_1 + m_2) \times F(m_3)}$};
+\node () at (7.625,0) {$\cong$};
+%\node () at (8.75,0) {$\cong$};
+\node (E') at (6.25,-0.5) {$\scriptstyle{F(m_1) \times F(m_2 + m_3)}$};
+\node (B) at (8,0.5) {$\scriptstyle{F((m_1 + m_2) + m_3)}$};
+\node (B') at (8,-0.5) {$\scriptstyle{F(m_1 + (m_2 + m_3))}$};
+\node (C) at (9.5,0.5) {$\scriptstyle{F((m_1+_b m_2)+m_3)}$};
+\node (C') at (9.5,-0.5) {$\scriptstyle{F(m_1 + (m_2+_c m_3))}$};
+\node (F) at (11,0.5) {$\scriptstyle{F((m_1+_b m_2)+_c m_3)}$};
+\node (F') at (11,-0.5) {$\scriptstyle{F(m_1+_b(m_2+_c m_3))}$};
+\node (G) at (4.25,0.5) {$\scriptstyle{(F(m_1) \times F(m_2)) \times F(m_3)}$};
+\node (G') at (4.25,-0.5) {$\scriptstyle{F(m_1) \times (F(m_2) \times F(m_3))}$};
+\node (M) at (3.25,0.3) {$\scriptstyle{(x_1 \times x_2) \times x_3}$};
+\node (M') at (3.25,-0.3) {$\scriptstyle{x_1 \times (x_2 \times x_3)}$};
+\path[->,font=\scriptsize,>=angle 90]
+(C) edge node [above] {$F(\psi)$} (F)
+(C') edge node [above] {$F(\psi)$} (F')
+(F) edge node [right] {$F(\kappa)$} (F')
+(E) edge node [above] {$\phi_{m_1+m_2,m_3}$} (B)
+(E') edge node [above] {$\phi_{m_1,m_2+m_3}$} (B')
+(B) edge node [above] {$F(\psi)$} (C)
+(B') edge node [above] {$F(\psi)$} (C')
+%(C) edge node  [fill=white] {$F(h_1 +_g h_2)$} (C')
+%(B) edge node [fill=white] {$F(h_1 + h_2)$} (B')
+(G) edge node [above] {$\phi_{m_1,m_2} \times 1$} (E)
+(G') edge node [above] {$1 \times \phi_{m_2,m_3}$} (E')
+(G) edge node [fill=white] {$a$} (G')
+(D) edge node [left,above] {$$} (G)
+(D) edge node [below] {$$} (G');
+%(E) edge node [fill=white] {$F(h_1) \times F(h_2)$} (E');
+\end{tikzpicture}
+\]
+where $a$ is the associator of $\Cat$ and $\kappa$ is the canonical isomorphism between two colimits of the same diagram in $\A$.
 Similarly the right and left unitors can be constructed, and all data satisfy the axioms of a double category -- essentially breaking down to those of the cospan double category of $\A$ and axioms of the lax monoidal pseudofunctor $F$.
-For full details of these arguments, see the second author's thesis \cite[Theorem~4.1.1]{CourserThesis}.
+For full details of these arguments, see \cite[Theorem~4.1.1]{CourserThesis}.
 \begin{comment}
@@
 \begin{thm}\label{DC}
-Let $\A$ be a category with finite colimits, made symmetric monoidal with a choice of initial object and binary coproducts.
-Let $F \maps (\A,+)\to (\Cat,\times)$ be symmetric lax monoidal pseudofunctor.
+Let $\A$ be a category with finite colimits and $F \maps \A \to \Cat$ a symmetric lax monoidal pseudofunctor.
 Then the double category $F\lCsp$ of Theorem \ref{thm:decorated_cospans} is symmetric monoidal, where
@@
 \begin{proof}
-Monoidal and symmetric monoidal double categories are introduced in Definitions \ref{defn:monoidal_double_category} and \ref{defn:symmetric_monoidal_double_category}.
-To make $F\lCsp$ into a symmetric monoidal double category, we must show that both the category of objects $F\lCsp_0$ and the category of arrows $F\lCsp_1$ are symmetric monoidal, show that the monoidal unit of $F\lCsp_0$ is preserved by the unit functor $U \maps F\lCsp_0 \to F\lCsp_1$, show that the source and target functors $S,T \colon F\lCsp_1 \to F\lCsp_0$ are strict symmetric monoidal, define the globular isomorphisms $\chi$ and $\mu$ that relate how composition and units interact with the tensor product, and check that the required axioms are satisfied.
+The definition of symmetric monoidal double category may be found in Definition \ref{defn:symmetric_monoidal_double_category}.
+We must show that both the category of objects $F\lCsp_0$ and the category of arrows $F\lCsp_1$ are symmetric monoidal categories, show that the monoidal unit of $F\lCsp_0$ is preserved by the unit functor $U$, show that the source and target functors $S,T \colon F\lCsp_1 \to F\lCsp_0$ are strict symmetric monoidal functors which preserve the associativity and unit constraints, define the globular isomorphisms $\chi$ and $\mu$ that relate how composition and units interact with the tensor product, and check that the required axioms are satisfied.
 
@@
 \node (C) at (2,0) {$0$};
-\node (D) at (3,0) {$\bot_0 \in F(0)$};
+\node (D) at (3,0) {$\bot_0 = \phi \in F(0)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-where $0$ is the monoidal unit of $\A$ and the element $\bot_0$ is another name for $\phi \maps 1 \to F(0)$, the morphism that arises from the lax monoidal structure of $F \maps (\A,+) \to (\Cat,\times)$.
+where $0$ is the monoidal unit of $\A$ and $\phi \maps 1 \to F(0)$ is the morphism which is part of the structure of the symmetric lax monoidal pseudofunctor $F \maps \A \to \Cat$.
 It is also clear that $U(0)=0_{F\lCsp_1}$.
@@
 \]
-where $(x_1+x_2)+x_3 \maps 1 \to F((m_1+m_2)+m_3)$ is the composite
-\[ 1 \xrightarrow{(x_1 \times x_2) \times x_3} (F(m_1) \times F(m_2)) \times F(m_3) \xrightarrow{\phi_{m_1,m_2} \times 1} F(m_1+m_2) \times F(m_3) \xrightarrow{\phi_{m_1+m_2,m_3}} F((m_1+m_2)+m_3).\] 
-The other parenthesization $M_1 \otimes (M_2 \otimes M_3)$ is given by:
+where $(x_1+x_2)+x_3 \maps 1 \to F((m_1+m_2)+m_3)$ is given by: $$1 \xrightarrow{(x_1 \times x_2) \times x_3} (F(m_1) \times F(m_2)) \times F(m_3) \xrightarrow{\phi_{m_1,m_2} \times 1} F(m_1+m_2) \times F(m_3) \xrightarrow{\phi_{m_1+m_2,m_3}} F((m_1+m_2)+m_3).$$ The other parenthesization $M_1 \otimes (M_2 \otimes M_3)$ is given by:
 \[
@@
 \]
-where the element $x_1+(x_2+x_3) \maps 1 \to F(m_1+(m_2+m_3))$ is the composite
-\[  1 \xrightarrow{x_1 \times (x_2 \times x_3)} F(m_1) \times (F(m_2) \times F(m_3)) \xrightarrow{1 \times \phi_{m_2,m_3}} F(m_1) \times F(m_2+m_3) \xrightarrow{\phi_{m_1,m_2+m_3}} F(m_1+(m_2+m_3)).\]
-Denoting the associator of $(\A,+,0)$ by $\alpha$, the associator of $F\lCsp_1$ is then the map of cospans in $\A$ from $(M_1 \otimes M_2) \otimes M_3$ to $M_1 \otimes (M_2 \otimes M_3)$ given by
+where $x_1+(x_2+x_3) \maps 1 \to F(m_1+(m_2+m_3))$ is given by: $$1 \xrightarrow{x_1 \times (x_2 \times x_3)} F(m_1) \times (F(m_2) \times F(m_3)) \xrightarrow{1 \times \phi_{m_2,m_3}} F(m_1) \times F(m_2+m_3) \xrightarrow{\phi_{m_1,m_2+m_3}} F(m_1+(m_2+m_3)).$$
+Denoting the associator of $(\A,+,0)$ by $\alpha$, the associator of $F\lCsp_1$ is then a map of cospans in $\A$ from $(M_1 \otimes M_2) \otimes M_3$ to $M_1 \otimes (M_2 \otimes M_3)$ given by:
 \[
@@
 The right unitor is similar, and one can check that the associator and left and right unitors together satisfy the pentagon and triangle identities of a monoidal category.
-For more details se the second author's thesis \cite[Theorem 4.1.3]{CourserThesis}.
+See the second author's thesis \cite{CourserThesis} for more details.
 
@@
 \]
-where the decoration $(x_1+y_1) \odot (x_2+y_2) \in F((m_1+n_1)+_{b+b'}(m_2+n_2))$ is the composite
+where the decoration $(x_1+y_1) \odot (x_2+y_2) \in F((m_1+n_1)+_{b+b'}(m_2+n_2))$ is given by:
 %$$\scriptscriptstyle{1 \xrightarrow{(\lambda^{-1} \times \lambda^{-1})\lambda^{-1}} (1 \times 1) \times (1 \times 1) \xrightarrow{(x_1 \times y_1) \times (x_2 \times y_2)} (F(m_1) \times F(n_1)) \times (F(m_2) \times F(n_2)) \xrightarrow{\phi_{m_1,n_1} \times \phi_{m_2,n_2}} F(m_1+n_1) \times F(m_2+n_2)} \xrightarrow{\phi_{m_1+n_1,m_2+n_2}} F((m_1+n_1)+(m_2+n_2)) \xrightarrow{F(\psi)} F((m_1+n_1)+_{b+b'}(m_2+n_2))$$
-\[ \scriptstyle{1 \xrightarrow{} (F(m_1) \times F(n_1)) \times (F(m_2) \times F(n_2)) \xrightarrow{\phi_{m_1,n_1} \times \phi_{m_2,n_2}} F(m_1+n_1) \times F(m_2+n_2)} \xrightarrow{\phi_{m_1+n_1,m_2+n_2}} F((m_1+n_1)+(m_2+n_2)) \xrightarrow{F(\psi)} F((m_1+n_1)+_{b+b'}(m_2+n_2)) \]
-where the first arrow is given by 
-\[ 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{\lambda^{-1} \times \lambda^{-1}} (1 \times 1) \times (1 \times 1) \xrightarrow{(x_1 \times y_1) \times (x_2 \times y_2)} (F(m_1) \times F(n_1)) \times (F(m_2) \times F(n_2)).\]
+$$\scriptstyle{1 \xrightarrow{} (F(m_1) \times F(n_1)) \times (F(m_2) \times F(n_2)) \xrightarrow{\phi_{m_1,n_1} \times \phi_{m_2,n_2}} F(m_1+n_1) \times F(m_2+n_2)} \xrightarrow{\phi_{m_1+n_1,m_2+n_2}} F((m_1+n_1)+(m_2+n_2)) \xrightarrow{F(\psi)} F((m_1+n_1)+_{b+b'}(m_2+n_2))$$
+where the first arrow is given by $$1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{\lambda^{-1} \times \lambda^{-1}} (1 \times 1) \times (1 \times 1) \xrightarrow{(x_1 \times y_1) \times (x_2 \times y_2)} (F(m_1) \times F(n_1)) \times (F(m_2) \times F(n_2)).$$
 %\[
@@
 
-The remaining properties are coherence laws that make use of these maps $\chi$ and $\mu$, the previously defined symmetric monoidal structure maps $a,\ell,r$ and $\beta$ and the double category structure functors $U$ and $\odot$.
-We exhibit one of these laws to give the reader a sense of how they are verified, with more details available in \cite[Theorem 4.1.3]{CourserThesis}.
+The remaining properties are coherence laws that make use of these maps $\chi$ and $\mu$, the previously defined symmetric monoidal structure maps $\alpha,\lambda,\rho$ and $\beta$ and the double category structure functors $U$ and $\odot$.
+We exhibit one of these laws to give the reader a sense of how they are verified, with more details available in the second author's thesis \cite{CourserThesis}.
 The coherence law that we check says that this diagram commutes:
@@
 We will see that this diagram commutes in two stages.
-First we consider the underlying maps of cospans in $\A$.
+First, for the underlying maps of cospans in $\A$.
 Using the notation previously introduced for the globular 2-morphism $\hat{\chi}$, the above diagram, modulo all of the decorations, is given by the following `flattened' commutative diagram in the symmetric monoidal double category $\lCsp(\A)$, where the top and the bottom cospans coincide.
@@
 as the above diagram of maps of cospans commutes in $\A$ and then applying the pseudofunctor $F$ to this diagram yields a commutative diagram in $\Cat$.
+The other diagrams in the definition of symmetric monoidal double category can be shown to commute similarly.
 \end{proof}
@@
 
-In general, decorated cospans involve a pseudofunctor to $\Cat$, but in this example there is actually an honest functor $F \maps \Fin\Set \to \Cat$ that assigns to a set $N$ the above category $F(N)$.
+In general, decorated cospans involve a pseudofunctor to $\Cat$, but in this example there is actually an honest functor $F \maps \Set \to \Cat$ that assigns to a set $N$ the above category $F(N)$.
 Given a function $f \maps M \to N$, we define $F(f) \maps F(M) \to F(N)$ to any graph structure $s,t \maps E \to M$ to the graph structure $f s, f t \maps E \to N$.
@@
 In other words, it sends a pair of graph structures to their `disjoint union'.
-Surprisngly, though $F$ is a functor---for example, composition is strictly preserved---this choice of $\phi_{N,N'}$ does not make $F$ into a symmetric lax monoidal functor, since the required laws hold only up to natural isomorphism.
-See \cite[Section 5]{BC} for a proof that these laws fail to hold on the nose.
-This fact necessitates a generalization of Fong's original formalism.
+MORE ABOUT THE WEAK MONOIDALITY!!!
 
@@
 A \define{monoidal double category} is a pseudomonoid in $\Dbl$.
+Explicitly, it is a double category equipped with double functors $\otimes \maps \lD \times \lD \to \lD$ and $I \maps 1 \to \lD$ where $1$ is the terminal double category, along with invertible transformations called the \define{associator}:
+\[  \alpha \maps \otimes \, \circ \; (1_{\lD} \times \otimes ) \Rightarrow \otimes \; \circ \; (\otimes \times 1_{\lD}) ,\]
+\define{left unitor}:
+\[ \ell \maps \otimes \, \circ \; (1_{\lD} \times I) \Rightarrow 1_{\lD} ,\]
+and \define{right unitor}:
+\[ r \maps \otimes \,\circ\; (I \times 1_{\lD}) \Rightarrow 1_{\lD} \]
+satisfying the pentagon and triangle identities.
 \end{defn}
-
-This definition neatly packages a large quantity of information.   When we unpack it, we see a monoidal double category is a double category $\lD$ with:
-\begin{itemize}
-\item monoidal structures on both $\lD_0$
-and $\lD_1$, each with tensor product denoted $\otimes$, associator $a$, left unitor $\ell$ and right unitor $r$, such that the unit object of $\lD_0$ is preserved by the unit functor $U$, and the source and target functors $S,T \maps \lD_1 \to \lD_0$ are strict symmetric monoidal,
-\item the structure of a double functor on $\otimes$:
-that is, invertible globular 2-morphisms
-\[ \chi \maps (M_1\otimes N_1)\odot (M_2\otimes N_2) \xrightarrow{\sim}
-(M_1\odot M_2)\otimes (N_1\odot N_2)\]
-\[ \mu \maps U_{A\otimes B} \xrightarrow{\sim} (U_A \otimes U_B)\]
-\end{itemize}
-These structures must obey a number of equations, which can be found after \cite[Definition 2.10]{HS} and also \cite[Definition A.5]{BC}.
 
@@
 
-Unpacking this definition one obtains a number of diagrams which can be found after \cite[Definition 2.4]{HS}.
+Unpacking these definitions further one obtains a large number of diagrams \cite{HS}.
 

### 2020-11-28 cospans.tex
worked on beginning of section 5 and also lax monoidal pseudofunctor stuff in 5.1

@@
 % in LaTeX
-% 2020/11/24
+% 2020/11/27
 
@@
 \begin{document}
+
 \begin{abstract}
@@
 Generalizing the work of Fong, we show that in this situation there is a symmetric monoidal double category whose objects are those of $\A$ and whose horizontal 1-cells are decorated cospans.
-We prove that under certain conditions these two constructions are equivalent when we take $\X = \int F$ to be the Grothendieck category of $F$.
+We prove that under certain conditions these two constructions become equivalent when we take $\X = \int F$ to be the Grothendieck category of $F$.
 We illustrate these ideas with applications to electrical circuits, Petri nets, reaction networks and dynamical systems.
@@
 where $a$ is the associator of $\Cat$ and $\kappa$ is the canonical isomorphism between two colimits of the same diagram in $\A$.
-Similarly the right and left unitors can be constructed, and all data satisfy the axioms of a double category -- essentially breaking down to those of the cospan double category of $\A$ and axioms of the lax monoidal pseudofunctor $F$.
+Similarly the right and left unitors can be constructed, and all data satisfy the axioms of a double category---essentially breaking down to those of the cospan double category of $\A$ and axioms of the lax monoidal pseudofunctor $F$.
 For full details of these arguments, see \cite[Theorem~4.1.1]{CourserThesis}.
@@
 
-In this section we present several examples, drawing the relation between the formalisms of structured and decorated cospans.
-Before we exhibit these formalisms in action, let us briefly remark that this work is part of a more general endeavor to apply categorical ideas to the theory and analysis of systems in a broad sense.
-Various capproaches to different problems have been followed; thinking about systems and processes categorically dates back to early works like \cite{Lawvere,JNW,BF2,KSW} and references therein.
-As mentioned in the introduction, the current material constitutes part of the line of work initiated by Fong \cite{Fong,FongThesis} and evolved and applied in different settings through a number of publications (here cite papers/theses that surround decorated and structured cospans in a broad sense).
-A different line of work employs algebras of wiring diagrams and sheaves to capture compositional and time features of dynamical systems, initiated by Spivak and progressed also onto cyber-physical directions \cite{VSL,SSV,BFV}.
-(Another line of work could be props used for systems?
-John?) Another approach uses graphical languages and signal flow diagrams \cite{FRS,BPSZ} to understand systems of a more behavioral taste \cite{Willems}.
-
-Having discussed some by no means exhaustive related work in the field, we are ready to set out to the examples of our framework.
+ Thinking about systems and processes categorically dates back to early works by Lawvere \cite{Lawvere}, Bunge--Fiore \cite{BungeFiore}, Joyal--Nielsen--Winskel \cite{JNW}, Katis--Sabadini--Walters \cite{KSW} and others.
+Spivak and others have used wiring diagrams and sheaves to capture compositional features of dynamical systems, \cite{BFV,SSV,VSL}.
+Another approach uses signal flow diagrams and other string diagrams \cite{BE,BSZ,FRS} to understand systems behaviorally, following ideas of Willems \cite{Willems}.
+
+Decorated cospans were introduced by Fong \cite{Fong,FongThesis} to describe open systems as cospans equipped with extra data; they were then applied to open electrical circuits \cite{BF}, Markov processes \cite{BFP}, and chemical reaction networks \cite{BP}.
+Unfortunately, some of these applications were marred by technical flaws, which were later fixed using structured cospans \cite[Sec.\ 5]{BC}.
+Our new approach to decorated cospans provides another solution to these problems.
+Here we compare the two approaches in applications to graphs, electrical circuits, Petri nets, reaction networks and dynamical systems.
+In many cases \cref{thm:equiv} shows that the structured and decorated cospan approaches are equivalent, but we show that open dynamical systems can only be treated using decorated cospans.
 
@@
 
-In earlier work we explained the problems with Fong's original decorated cospan category of open graphs  \cite[Sec.\ 5]{BC}.
-We also showed how to fix these using structured cospans.
-Our new approach to decorated cospans provides another, equivalent solution to these problems.
-
+One of the simplest kinds of network is a graph.
 For us a \define{graph} will be a pair of functions $s,t\maps E \to N$ where $E$ and $N$ are finite sets.
@@
 In other words, it sends a pair of graph structures to their `disjoint union'.
-MORE ABOUT THE WEAK MONOIDALITY!!!
+Surprisingly, though $F$ is a functor---for example, composition is strictly preserved---this choice of $\phi_{N,N'}$ does not make $F$ into a symmetric lax monoidal functor, since it obeys the required laws only up to natural isomorphism, as in Equation \cref{eq:omega}.
+See \cite[Section 5]{BC} for a proof that these laws fail to hold on the nose.
+This fact necessitates a generalization of Fong's original approach to decorated cospans.
 
@@
 
+\bibitem{BE} J.\ C.\ Baez and J.\ Erbele, Categories in control, \textsl{Theory Appl.\ Categ.} {\bf 30} (2015), 836--881. Available as \href{http://arxiv.org/abs/1405.6881}{arXiv:1405.6881}.
+
 \bibitem{BF}  J.\ C.\ Baez and B.\ Fong, A compositional framework for passive linear networks, \textsl{Theory Appl.\ Categ.\ }\textbf{33} (2018), 1158--1222.
@@
 
-\bibitem{BFV} G.\ Bakirtzis, C.\ H.\ Fleming and C.\ Vasilakopoulou, Categorical Semantics of Cyber-Physical Systems Theory. Available as 
+\bibitem{BFV} G.\ Bakirtzis, C.\ H.\ Fleming and C.\ Vasilakopoulou, Categorical semantics of cyber-physical systems theory. Available as 
 \href{https://arxiv.org/abs/2010.08003}{arXiv:2010.08003}.
 
-\bibitem{BPSZ} F.\ Bonchi, R.\ Piedeleu, P.\ Sobocinski and F.\ Zanasi, Contextual Equivalence for Signal Flow Graphs, \textsl{FoSSaCS} (2020).
-Available as \href{https://arxiv.org/abs/2002.08874}{arXiv:2002.08874}.
+\bibitem{BSZ} Filippo Bonchi, Pawe\l~Soboci\'nski and Fabio Zanasi, A categorical semantics of signal flow graphs, in \textsl{CONCUR 2014--Concurrency Theory}, eds.\ P.\ Baldan and D.\ Gorla, \textsl{Lecture Notes in Computer Science} vol.\ 8704, Springer, Berlin, 2014, pp.\ 435--450.
+Also available at \href{http://users.ecs.soton.ac.uk/ps/papers/sfg.pdf}{http://users.ecs.soton.ac.uk/ps/papers/sfg.pdf}.
 
@@
 
-\bibitem{BF2} M.\ Bunge and M.\ Fiore, Unique factorisation lifting functors and categories of linearly-controlled processes, \textsl{Math.\ Struct.\ Comput.\ Sci.\ } \textbf{10} (2000), 137--163.
+\bibitem{BungeFiore} M.\ Bunge and M.\ Fiore, Unique factorisation lifting functors and categories of linearly-controlled processes, \textsl{Math.\ Struct.\ Comput.\ Sci.\ } \textbf{10} (2000), 137--163.
 
@@
 
-\bibitem{FRS} B.\ Fong, P.\ Rapisarda, P.\ Sobocinski, \textsl{A categorical approach to open and interconnected dynamical systems}, LICS, 2016.
+\bibitem{FRS} B.\ Fong, P.\ Rapisarda and P.\ Sobocinski, A categorical approach to open and interconnected dynamical systems, in \textsl{Proceedings of the 31st Annual ACM/IEEE Symposium on Logic in Computer Science (LICS)}, IEEE, New York, 2016, pp.\ 1--10.
 Available as \href{http://arxiv.org/abs/510.05076}{arXiv:1510.05076}.
@@
 
-\bibitem{GPS} R.\ Gordon, A.\ J.\ Power and R.\ Street, \textsl{Coherence for Tricategories}, \textsl{Mem.\ Amer.\ Math.\ Soc.\ }\textbf{558}, 1995.
+\bibitem{GPS} R.\ Gordon, A.\ J.\ Power and R.\ Street, Coherence for tricategories, \textsl{Mem.\ Amer.\ Math.\ Soc.\ }\textbf{558}, 1995.
 
@@
 
-%\bibitem{Haug} R.\ Haugseng, Iterated spans and ``classical" topological field theories. Available as \href{https://arxiv.org/abs/1409.0837}{arXiv:1409.0837}.
-
-\bibitem{Hermida1999} C. \ Hermida, Some properties of Fib as a fibred 2-category, \textsl{J.\ Pure Appl.\ Alg.\ } \textbf{134}, 83 -- 109, 1999
-
-%\bibitem{Hoff} A.\ Hoffnung, Spans in 2-categories: a monoidal tricategory. Available as \href{http://arxiv.org/abs/1112.0560}{arXiv:1112.0560}.
-
-\bibitem{Jacobs} B. \ Jacobs, Categorical logic and type theory, \textsl{Studies in Logic and the Foundations of Mathematics} \textbf{141}, 1999
-
-\bibitem{JNW} A.\ Joyal, M.\ Nielsen and G.\ Winskel, Bisimulation from Open Maps, \textsl{Information and Computation} \textbf{127} (1996) 164 -- 185.
-
-\bibitem{KSW} P.\ Katis, N.\ Sabadini and R.\ F.\ C.\ Walters, On the algebra of systems with feedback and boundary, \textsl{Rendiconti del Circolo Matematico di Palermo Serie II} \textbf{63} (2000) 123 -- 156.
-
-\bibitem{KS} G.\ Kelly and R.\ Street, Review of the elements of 2-categories, \textsl{Lecture Notes in Mathematics} vol. 40, pages 75---103, Springer Berlin/Heidelberg, 1974.
-
-\bibitem{Lawvere} F.\ W.\ Lawvere, State categories and response functors, unpublished manuscript (1986)
+\bibitem{Hermida1999} C. \ Hermida, Some properties of Fib as a fibred 2-category, \textsl{J.\ Pure Appl.\ Alg.\ } \textbf{134} (1999), 83--109.
+
+\bibitem{Jacobs} B. \ Jacobs, \textsl{Categorical Logic and Type Theory}, Elsevier, Amsterdam, 1999.
+
+\bibitem{JNW} A.\ Joyal, M.\ Nielsen and G.\ Winskel, Bisimulation from open maps, \textsl{Inf.\ Comput.\ }\textbf{127} (1996), 164--185.
+
+\bibitem{KSW} P.\ Katis, N.\ Sabadini and R.\ F.\ C.\ Walters, On the algebra of systems with feedback and boundary, \textsl{Rendiconti del Circolo Matematico di Palermo Serie II} \textbf{63} (2000), 123--156.
+
+\bibitem{KS} G.\ Kelly and R.\ Street, Review of the elements of 2-categories, in \textsl{Category Seminar}, Lecture Notes in Mathematics 40, Springer, Berlin, 1974, 
+pp.\ 75--103.
+
+\bibitem{Lawvere} F.\ W.\ Lawvere, State categories and response functors, unpublished manuscript, 1986.
+Available at \href{https://tinyurl.com/state}{https://tinyurl.com/state-}  \href{https://tinyurl.com/state-categories}{categories}.
 
@@
 
-\bibitem{McCrudden} P.\ McCrudden, Balanced coalgebroids, \textsl{Theory Appl.\ Categ.\ }\textbf{ 7} (2000), 71--147.
+\bibitem{McCrudden} P.\ McCrudden, Balanced coalgebroids, \textsl{Theory Appl.\ Categ.\ } \textbf{7} (2000), 71--147.
 
@@
 
-\bibitem{Peterson} J.\ L.\ Peterson, \textit{Petri Net Theory and the Modeling of Systems}, Prentice--Hall, New Jersey, 1981.
+\bibitem{Peterson} J.\ L.\ Peterson, \textit{Petri Net Theory and the Modeling of Systems}, Prentice-Hall, New Jersey, 1981.
 
@@
 \bibitem{RSW} R.\ Rosebrugh, N.\ Sabadini and R.\ F.\ C.\ Walters, Generic commutative separable algebras and cospans of graphs, \textsl{Theory Appl.\ Categ.\ }\textbf{15} (2005), 164--177.
-Available at \href{http:/.www.tac.mta.ca/tac/volumes/15/6/15-06.pdf}{http:/.www.tac.mta.ca/tac/volumes/15/6/15-06.pdf}.
 

### 2020-11-28 cospans.tex
re-made a bunch of changes that had been lost!

@@
 
-The category of objects $F\lCsp_0$ is simply the category $\A$.
+The category of objects $F\lCsp_0$ is simply $\A$.
 The category of arrows $F\lCsp_1$ has $F$-decorated cospans for objects and maps of $F$-decorated cospans as morphisms.
@@
 \begin{thm}\label{DC}
-Let $\A$ be a category with finite colimits and $F \maps \A \to \Cat$ a symmetric lax monoidal pseudofunctor.
+Let $\A$ be a category with finite colimits and let $F \maps (\A,+) \to (\Cat,\times)$ a symmetric lax monoidal pseudofunctor.
 Then the double category $F\lCsp$ of Theorem \ref{thm:decorated_cospans} is symmetric monoidal, where
@@
 \]
-where $(x_1+x_2)+x_3 \maps 1 \to F((m_1+m_2)+m_3)$ is given by: $$1 \xrightarrow{(x_1 \times x_2) \times x_3} (F(m_1) \times F(m_2)) \times F(m_3) \xrightarrow{\phi_{m_1,m_2} \times 1} F(m_1+m_2) \times F(m_3) \xrightarrow{\phi_{m_1+m_2,m_3}} F((m_1+m_2)+m_3).$$ The other parenthesization $M_1 \otimes (M_2 \otimes M_3)$ is given by:
+where $(x_1+x_2)+x_3 \maps 1 \to F((m_1+m_2)+m_3)$ is the composite
+\[  1 \xrightarrow{(x_1 \times x_2) \times x_3} (F(m_1) \times F(m_2)) \times F(m_3) \xrightarrow{\phi_{m_1,m_2} \times 1} F(m_1+m_2) \times F(m_3) \xrightarrow{\phi_{m_1+m_2,m_3}} F((m_1+m_2)+m_3).\]
+The other parenthesization $M_1 \otimes (M_2 \otimes M_3)$ is given by:
 \[
@@
 \]
-where $x_1+(x_2+x_3) \maps 1 \to F(m_1+(m_2+m_3))$ is given by: $$1 \xrightarrow{x_1 \times (x_2 \times x_3)} F(m_1) \times (F(m_2) \times F(m_3)) \xrightarrow{1 \times \phi_{m_2,m_3}} F(m_1) \times F(m_2+m_3) \xrightarrow{\phi_{m_1,m_2+m_3}} F(m_1+(m_2+m_3)).$$
-Denoting the associator of $(\A,+,0)$ by $\alpha$, the associator of $F\lCsp_1$ is then a map of cospans in $\A$ from $(M_1 \otimes M_2) \otimes M_3$ to $M_1 \otimes (M_2 \otimes M_3)$ given by:
+where $x_1+(x_2+x_3) \maps 1 \to F(m_1+(m_2+m_3))$ is the composite
+\[  1 \xrightarrow{x_1 \times (x_2 \times x_3)} F(m_1) \times (F(m_2) \times F(m_3)) \xrightarrow{1 \times \phi_{m_2,m_3}} F(m_1) \times F(m_2+m_3) \xrightarrow{\phi_{m_1,m_2+m_3}} F(m_1+(m_2+m_3)).\]
+Denoting the associator of $(\A,+)$ by $\alpha$, the associator of $F\lCsp_1$ is then a map of cospans in $\A$ from $(M_1 \otimes M_2) \otimes M_3$ to $M_1 \otimes (M_2 \otimes M_3)$ given by:
 \[
@@
 \]
-where the decoration $(x_1+y_1) \odot (x_2+y_2) \in F((m_1+n_1)+_{b+b'}(m_2+n_2))$ is given by:
+where the decoration $(x_1+y_1) \odot (x_2+y_2) \in F((m_1+n_1)+_{b+b'}(m_2+n_2))$ is given by
 %$$\scriptscriptstyle{1 \xrightarrow{(\lambda^{-1} \times \lambda^{-1})\lambda^{-1}} (1 \times 1) \times (1 \times 1) \xrightarrow{(x_1 \times y_1) \times (x_2 \times y_2)} (F(m_1) \times F(n_1)) \times (F(m_2) \times F(n_2)) \xrightarrow{\phi_{m_1,n_1} \times \phi_{m_2,n_2}} F(m_1+n_1) \times F(m_2+n_2)} \xrightarrow{\phi_{m_1+n_1,m_2+n_2}} F((m_1+n_1)+(m_2+n_2)) \xrightarrow{F(\psi)} F((m_1+n_1)+_{b+b'}(m_2+n_2))$$
-$$\scriptstyle{1 \xrightarrow{} (F(m_1) \times F(n_1)) \times (F(m_2) \times F(n_2)) \xrightarrow{\phi_{m_1,n_1} \times \phi_{m_2,n_2}} F(m_1+n_1) \times F(m_2+n_2)} \xrightarrow{\phi_{m_1+n_1,m_2+n_2}} F((m_1+n_1)+(m_2+n_2)) \xrightarrow{F(\psi)} F((m_1+n_1)+_{b+b'}(m_2+n_2))$$
-where the first arrow is given by $$1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{\lambda^{-1} \times \lambda^{-1}} (1 \times 1) \times (1 \times 1) \xrightarrow{(x_1 \times y_1) \times (x_2 \times y_2)} (F(m_1) \times F(n_1)) \times (F(m_2) \times F(n_2)).$$
+\[ \scriptstyle{1 \xrightarrow{} (F(m_1) \times F(n_1)) \times (F(m_2) \times F(n_2)) \xrightarrow{\phi_{m_1,n_1} \times \phi_{m_2,n_2}} F(m_1+n_1) \times F(m_2+n_2)} \xrightarrow{\phi_{m_1+n_1,m_2+n_2}} F((m_1+n_1)+(m_2+n_2)) \xrightarrow{F(\psi)} F((m_1+n_1)+_{b+b'}(m_2+n_2)) \]
+where the first arrow is the composite
+\[1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{\lambda^{-1} \times \lambda^{-1}} (1 \times 1) \times (1 \times 1) \xrightarrow{(x_1 \times y_1) \times (x_2 \times y_2)} (F(m_1) \times F(n_1)) \times (F(m_2) \times F(n_2)).
+\]
 %\[
@@
 This diagram expresses that the braiding is a transformation of double categories.
-We will see that this diagram commutes in two stages.
+We show that this diagram commutes in two stages.
 First, for the underlying maps of cospans in $\A$.
@@
 The above diagram commutes by a similar argument to the one used in \cref{thm:equiv}.
-Similarly, for every object $c \in \A$, we have a unit comparison constraint $$\H_U \maps U_{\H(c)} \to \H(U_c)$$ given by the globular 2-isomorphism:
-where $\kappa$ is the isomorphism $$\kappa \maps H(c_1 +_b c_2) \xrightarrow{\sim} H(c_1) +_{H(b)} H(c_2)$$ which comes from the finite colimit preserving functor $H \maps \A \to \A'$.
+Similarly, for every object $c \in \A$, we have a unit comparison constraint \\[ \H_U \maps U_{\H(c)} \to \H(U_c)\]
+given by the globular 2-isomorphism:
+where $\kappa$ is the isomorphism 
+\[  \kappa \maps H(c_1 +_b c_2) \xrightarrow{\sim} H(c_1) +_{H(b)} H(c_2)\] 
+which comes from the finite colimit preserving functor $H \maps \A \to \A'$.
 The above diagram commutes by a similar argument to the one used in \cref{thm:equiv}.
-Similarly, for every object $c \in \A$, we have a unit comparison constraint $$\lH_U \maps U_{\lH(c)} \to \lH(U_c)$$ given by the globular 2-isomorphism:
+Similarly, for every object $c \in \A$, we have a unit comparison constraint
+\[ \lH_U \maps U_{\lH(c)} \to \lH(U_c)\] 
+given by the globular 2-isomorphism:
 \[
@@
 \begin{thm} \label{thm:equiv}
-Suppose $\A$ has finite colimits and $F\maps(\A,+) \to (\Cat,\times)$ is a symmetric lax monoidal pseudofunctor that factors through $\Rex$ as an ordinary pseudofunctor.
+Suppose $\A$ has finite colimits and $F \maps (\A,+) \to (\Cat,\times)$ is a symmetric lax monoidal pseudofunctor that factors through $\Rex$ as an ordinary pseudofunctor.
 Then the symmetric monoidal double categories $F\lCsp$ of decorated cospans and $_L\lCsp(\inta F)$ of structured cospans are isomorphic, where $L \maps \A \to \inta F$ is a left adjoint of the induced Grothendieck opfibration $U\maps \inta F \to \A$.
@@
 All of the diagrams that are required to commute are straightforward.
-Using Theorem \cref{DC}, we obtain a symmetric monoidal double category $F\lCsp$ which has:
+Using \cref{DC}, we obtain a symmetric monoidal double category $F\lCsp$ which has:
 \begin{enumerate}
@@
 
+Let $\Dbl$ denote the 2-category of double categories, double functors and double transformations.
+One can check that $\Dbl$ has finite products, and in any 2-category with finite products we can define a `pseudomonoid', which is a categorified analogue of a monoid \cite{DS}.
+For example, a pseudomonoid in $\Cat$ is a monoidal category.
+We can also define braided and symmetric pseudomonoids, which in $\Cat$ are braided and symmetric monoidal categories.
+
 \begin{defn}
@@
 A \define{monoidal double category} is a pseudomonoid in $\Dbl$. 
-Explicitly, it is a double category equipped with double functors $\otimes \maps \lD \times \lD \to \lD$ and $I \maps 1 \to \lD$ where $1$ is the terminal double category, along with invertible transformations called the \define{associator}:
-\[  \alpha \maps \otimes \, \circ \; (1_{\lD} \times \otimes ) \Rightarrow \otimes \; \circ \; (\otimes \times 1_{\lD}) ,\]
-\define{left unitor}:
-\[ \ell \maps \otimes \, \circ \; (1_{\lD} \times I) \Rightarrow 1_{\lD} ,\]
-and \define{right unitor}:
-\[ r \maps \otimes \,\circ\; (I \times 1_{\lD}) \Rightarrow 1_{\lD} \]
-satisfying the pentagon and triangle identities.
 \end{defn}
+
+This definition neatly packages a large quantity of information.   When we unpack it, we see a monoidal double category is a double category $\lD$ with:
+\begin{itemize}
+\item monoidal structures on both $\lD_0$
+and $\lD_1$, each with tensor product denoted $\otimes$, associator $a$, left unitor $\ell$ and right unitor $r$, such that the unit object of $\lD_0$ is preserved by the unit functor $U$, and the source and target functors $S,T \maps \lD_1 \to \lD_0$ are strict symmetric monoidal,
+\item the structure of a double functor on $\otimes$:
+that is, invertible globular 2-morphisms
+\[ \chi \maps (M_1\otimes N_1)\odot (M_2\otimes N_2) \xrightarrow{\sim}
+(M_1\odot M_2)\otimes (N_1\odot N_2)\]
+\[ \mu \maps U_{A\otimes B} \xrightarrow{\sim} (U_A \otimes U_B)\]
+\end{itemize}
+These structures must obey a number of equations, which can be found after \cite[Definition 2.10]{HS} and also \cite[Definition A.5]{BC}.
 

### 2020-12-01 cospans.tex
removed duplicate paragraph regarding $\Dbl$ in appendix
continue working on 2

@@
 \begin{proof}
-Take $\A$ to have finite colimits and let $(F,\phi,\phi_0) \maps (A,+,0) \to (\Cat,\times, 1)$ be a lax monoidal pseudofunctor as defined in \cref{defn:double_category}.
+Take $\A$ to have finite colimits and let $(F,\phi,\phi_0) \maps (A,+,0) \to (\Cat,\times, 1)$ be a lax monoidal pseudofunctor.
 We shall define the category of objects $F\lCsp_0$, the category of arrows $F\lCsp_1$, as well as the four structure functors which tie them together: the source and target functors $S,T \colon F\lCsp_1 \to F\lCsp_0$, the composition functor $\odot \colon F\lCsp_1 \times_{F\lCsp_0} F\lCsp_1 \to F\lCsp_1$ and the unit functor $U \colon F\lCsp_0 \to F\lCsp_1$.
@@
 where if $\tau \colon F(h)(x) \to x'$ and $\tau' \colon F(h')(x') \to x''$ are the decoration morphisms, 
-$$F(h'h)(x)\cong F(h')F(h)(x)\xrightarrow{F(h')(\tau)}F(h')(x')\xrightarrow{\tau'}x''$$ is the composite one.
+$$F(h'h)(x)\cong F(h')F(h)(x)\xrightarrow{F(h')(\tau)}F(h')(x')\xrightarrow{\tau'}x''$$ is the decoration of the composite.
 The source and target functors map an $F$-decorated cospan to the source and target of the cospan and a map of decorated cospans \cref{eq:mapofdec} to $f$ and $g$ respectively.
@@
 (C') edge node {$$} (D)
-(B) edge node [left] {$\stackrel{\alpha}{\cong}$} (D);
-\end{tikzpicture}
-\]
-together with an isomorphism $F(\alpha)((x_1 \odot x_2) \odot x_3) \cong (x_1 \odot (x_2 \odot x_3))$ between the decorations 
-\begin{align*}
-\scalebox{.8}{$\one\xrightarrow{x_1\times x_2}F(m_1)\times F(m_2)\xrightarrow{\phi}F(m_1+m_2)\to F(m_1+_bm_2)\xrightarrow{1\times x_3}F(m_1+_bm_2)\times F(m_3)\xrightarrow{\phi}F((m_1+_bm_2)+m_3)$}&\scalebox{.8}{$\to F((m_1+_bm_2)+_cm_3)$} \\
-&\scalebox{.8}{$\stackrel{F(\alpha)}{\cong} F(m_1+_b(m_2+_cm_3))$} \\
-\scalebox{.8}{$\one\xrightarrow{x_2\times x_3}F(m_2)\times F(m_3)\xrightarrow{\phi}F(m_2+m_3)\to F(m_2+_cm_3)\xrightarrow{x_1\times1}F(m_1)\times F(m_2+_cm_3)\xrightarrow{\phi}F(m_1\times(m_2+_cm_3))$}&\scalebox{.8}{$\to F(m_1+_b(m_2+_cm_3))$}
-\end{align*}
-%%% Kenny: I think we should call this \alpha something else like \kappa, since it's only a component used in building the associator for horizontal composition (which we are calling \alpha), not the entire thing on its own.
+(B) edge node [left] {$\stackrel{\kappa}{\cong}$} (D);
+\end{tikzpicture}
+\]
+together with an isomorphism $F(\kappa)((x_1 \odot x_2) \odot x_3) \cong (x_1 \odot (x_2 \odot x_3))$ between the decorations 
+%\begin{align*}
+%\scalebox{.8}{$\one\xrightarrow{x_1\times x_2}F(m_1)\times F(m_2)\xrightarrow{\phi}F(m_1+m_2)\to F(m_1+_bm_2)\xrightarrow{1\times x_3}F(m_1+_bm_2)\times %F(m_3)\xrightarrow{\phi}F((m_1+_bm_2)+m_3)$}&\scalebox{.8}{$\to F((m_1+_bm_2)+_cm_3)$} \\
+%&\scalebox{.8}{$\stackrel{F(\alpha)}{\cong} F(m_1+_b(m_2+_cm_3))$} \\
+%\scalebox{.8}{$\one\xrightarrow{x_2\times x_3}F(m_2)\times F(m_3)\xrightarrow{\phi}F(m_2+m_3)\to F(m_2+_cm_3)\xrightarrow{x_1\times1}F(m_1)\times %F(m_2+_cm_3)\xrightarrow{\phi}F(m_1\times(m_2+_cm_3))$}&\scalebox{.8}{$\to F(m_1+_b(m_2+_cm_3))$}
+%\end{align*}
 \[
 \begin{tikzpicture}[scale=1.7]
-\node (A) at (3.75,0) {$\scriptstyle{\cong \tau_a}$};
+\node (A) at (3.75,0) {$\scriptstyle{\cong}$};
 \node (D) at (3,0) {$\scriptstyle{\one}$};
 \node (E) at (6.25,0.5) {$\scriptstyle{F(m_1 + m_2) \times F(m_3)}$};
-\node () at (7.625,0) {$\cong$};
+\node () at (7.625,0) {$\scriptstyle\cong$};
 %\node () at (8.75,0) {$\cong$};
@@
 \path[->,font=\scriptsize,>=angle 90]
-(C) edge node [above] {$F(\psi)$} (F)
-(C') edge node [above] {$F(\psi)$} (F')
+(C) edge node [above] {} (F)
+(C') edge node [above] {} (F')
 (F) edge node [right] {$F(\kappa)$} (F')
@@
 (E') edge node [above] {$\phi_{m_1,m_2+m_3}$} (B')
-(B) edge node [above] {$F(\psi)$} (C)
-(B') edge node [above] {$F(\psi)$} (C')
+(B) edge node [above] {} (C)
+(B') edge node [above] {} (C')
 %(C) edge node  [fill=white] {$F(h_1 +_g h_2)$} (C')
 %(B) edge node [fill=white] {$F(h_1 + h_2)$} (B')
-(G) edge node [above] {$\phi_{m_1,m_2} \times 1$} (E)
-(G') edge node [above] {$1 \times \phi_{m_2,m_3}$} (E')
+(G) edge node [above] {$\phi_{m_1,m_2} {\times} 1$} (E)
+(G') edge node [above] {$1 {\times} \phi_{m_2,m_3}$} (E')
 (G) edge node [fill=white] {$a$} (G')
@@
 \]
+%%% Christina: I erased tau, and also Fpsi because they were not accurate and those arrows are OK to understand - the universal maps from a 'smaller' colimit to a 'bigger' one.
+If we kept Fpsi's we should write them like F(psi+1) for the first arrow at the top, and that would make the whole thing a bit heavier.
 where $a$ is the associator of $\Cat$ and $\kappa$ is the canonical isomorphism between two colimits of the same diagram in $\A$.
@@
 For full details of these arguments, see \cite[Theorem~4.1.1]{CourserThesis}.
-\begin{comment}
- The definition of double category may be found in Definition \ref{defn:double_category}.
-To show that the pseudofunctor $F$ in the theorem statement induces a double category $F\lCsp$, we must first define the category of objects $F\lCsp_0$, the category of arrows $F\lCsp_1$, as well as the four structure functors which tie them together: the source and target functors $S,T \colon F\lCsp_1 \to F\lCsp_0$, the unit functor $U \colon F\lCsp_0 \to F\lCsp_1$ and the composition functor $\odot$ which says how to compose two composable horizontal 1-cells or two composable 2-morphisms horizontally: $$\odot \colon F\lCsp_1 \times_{F\lCsp_0} F\lCsp_1 \to F\lCsp_1.$$
-
-The category of objects $F\lCsp_0$ is simply $\A$.
-The category of arrows $F\lCsp_1$ has $F$-decorated cospans for objects and maps of $F$-decorated cospans as morphisms.
-Given two vertically composable $F$-decorated cospans:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$a$};
-\node (A') at (0,-0.5) {$a'$};
-\node (B) at (1,0.5) {$m$};
-\node (C) at (2,0.5) {$b$};
-\node (C') at (2,-0.5) {$b'$};
-\node (D) at (1,-0.5) {$m'$};
-\node (E) at (3,0.5) {$x \in F(m)$};
-\node (F) at (3,-0.5) {$x' \in F(m')$};
-\node (G) at (1.5,-1) {$\tau \colon F(h)(x) \to x'$};
-\node (A'') at (0,-1.5) {$a'$};
-\node (A''') at (0,-2.5) {$a''$};
-\node (B'') at (1,-1.5) {$m'$};
-\node (C'') at (2,-1.5) {$b'$};
-\node (C''') at (2,-2.5) {$b''$};
-\node (D'') at (1,-2.5) {$m''$};
-\node (E'') at (3,-1.5) {$x' \in F(m')$};
-\node (F'') at (3,-2.5) {$x'' \in F(m'')$};
-\node (G'') at (1.5,-3) {$\tau' \colon F(h')(x') \to x''$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i$} (B)
-(C) edge node[above]{$o$} (B)
-(A) edge node[left]{$f$} (A')
-(C) edge node[right]{$g$} (C')
-(A') edge node[above] {$i'$} (D)
-(C') edge node[above] {$o'$} (D)
-(B) edge node [left] {$h$} (D)
-(A'') edge node[above]{$i'$} (B'')
-(C'') edge node[above]{$o'$} (B'')
-(A'') edge node[left]{$f'$} (A''')
-(C'') edge node[right]{$g'$} (C''')
-(A''') edge node[above] {$i''$} (D'')
-(C''') edge node[above] {$o''$} (D'')
-(B'') edge node [left] {$h'$} (D'');
-\end{tikzpicture}
-\]
-their composite is given by the composite of the two maps of cospans in $\A$
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$a$};
-\node (A') at (0,-0.5) {$a''$};
-\node (B) at (1,0.5) {$m$};
-\node (C) at (2,0.5) {$b$};
-\node (C') at (2,-0.5) {$b''$};
-\node (D) at (1,-0.5) {$m''$};
-\node (E) at (3,0.5) {$x \in F(m)$};
-\node (F) at (3,-0.5) {$x'' \in F(m'')$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i$} (B)
-(C) edge node[above]{$o$} (B)
-(A) edge node[left]{$f'f$} (A')
-(C) edge node[right]{$g'g$} (C')
-(A') edge node[above] {$i''$} (D)
-(C') edge node[above] {$o''$} (D)
-(B) edge node [left] {$h'h$} (D);
-\end{tikzpicture}
-\]
-together with the composite decoration morphism $\tau' F(\tau) \colon F(h'h)(x) \to x'$ in $F(m'')$.
-% this was:
-% together with the composite morphism of decorations $\tau' \tau \colon F(h'h)(x) \to x'$ in $F(m'')$
-%% \tau' \tau was the notation that I was using, but I see why this was misleading. I believe it should be called \tau'(F(h')(\tau)) \instead of \tau' F(\tau), and also with target x''.
- This completes the descriptions of the category of objects $F\lCsp_0 = \A$ and the category of arrows $F\lCsp_1$.
-
-Next, we define the four structure functors $U,S,T$ and $\odot$. The unit functor $U \maps F\lCsp_0 \to F\lCsp_1$ is defined on objects as: 
-\begin{equation}\label{eq:UFCsp}
-\begin{tikzpicture}[scale=1.5]
-\node (E) at (-1,0) {$a$};
-\node (F) at (-.5,0) {$\mapsto$};
-\node (A) at (0,0) {$a$};
-\node (B) at (1,0) {$a$};
-\node (C) at (2,0) {$a$};
-\node (D) at (3,0) {$\bot_a \in F(a)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$1$} (B)
-(C) edge node[above]{$1$} (B);
-\end{tikzpicture}
-\end{equation}
-where $\bot_a \in F(a)$ is the \define{trivial decoration} on $a$ given by the composite of the unique map $F(!) \maps F(0) \to F(a)$ and the morphism $\phi \maps 1 \to F(0)$  which comes from $F \maps \A \to \Cat$ being lax monoidal.
-For morphisms, the functor $U$ is defined as:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (G) at (-1,0.5) {$a$};
-\node (G') at (-1,-0.5) {$a'$};
-\node (A) at (0,0.5) {$a$};
-\node (A') at (0,-0.5) {$a'$};
-\node (B) at (1,0.5) {$a$};
-\node (C) at (2,0.5) {$a$};
-\node (C') at (2,-0.5) {$a'$};
-\node (D) at (1,-0.5) {$a'$};
-\node (E) at (3,0.5) {$\bot_a \in F(a)$};
-\node (F) at (3,-0.5) {$\bot_{a'} \in F(a')$};
-\node (H) at (-0.5,0) {$\mapsto$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$1$} (B)
-(C) edge node[above]{$1$} (B)
-(A) edge node[left]{$f$} (A')
-(C) edge node[right]{$f$} (C')
-(A') edge node[above] {$1$} (D)
-(C') edge node[above] {$1$} (D)
-(B) edge node [left] {$f$} (D)
-(G) edge node [left] {$f$} (G');
-\end{tikzpicture}
-\]
-together with the morphism $\tau_{\bot_f} = F(f) F(!) \phi \maps 1 \to F(a')$.
-For the source and target functors $S, T \maps F\lCsp_1 \to F\lCsp_0$, given an object $F\lCsp_1$, which is an $F$-decorated cospan,
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a$};
-\node (B) at (1,0) {$m$};
-\node (C) at (2,0) {$b$};
-\node (D) at (3,0) {$x \in F(m)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i$} (B)
-(C) edge node[above]{$o$} (B);
-\end{tikzpicture}
-\]
-the source is the object $a$ and the target is the object $b$. Given a morphism of $F\lCsp_1$, which is a map of $F$-decorated cospans,
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$a$};
-\node (A') at (0,-0.5) {$a'$};
-\node (B) at (1,0.5) {$m$};
-\node (C) at (2,0.5) {$b$};
-\node (C') at (2,-0.5) {$b'$};
-\node (D) at (1,-0.5) {$m'$};
-\node (E) at (3,0.5) {$x \in F(m)$};
-\node (F) at (3,-0.5) {$x' \in F(m')$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i$} (B)
-(C) edge node[above]{$o$} (B)
-(A) edge node[left]{$f$} (A')
-(C) edge node[right]{$g$} (C')
-(A') edge node[above] {$i'$} (D)
-(C') edge node[above] {$o'$} (D)
-(B) edge node [left] {$h$} (D);
-\end{tikzpicture}
-\]
-$$\tau \maps F(h)(x) \to x'$$
-the source is the morphism $f$ and the target is the morphism $g$. The three functors $S,T$ and $U$ satisfy the equations $SU=\id_{\A}=TU$.
-
-Next we define the composite functor $\odot \colon F\lCsp_1 \times_{F\lCsp_0} F\lCsp_1 \to F\lCsp_1$, which amounts to defining how we compose two composable $F$-decorated cospans or horizontally compose two maps of $F$-decorated cospans with a common source and target.
-Given two composable $F$-decorated cospans which we respectively denote by $M$ and $N$, the capitals of their apices:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a$};
-\node (B) at (1,0) {$m$};
-\node (C) at (2,0) {$b$};
-\node (D) at (1,-0.5) {$x \in F(m)$};
-\node (E) at (3,0) {$b$};
-\node (F) at (4,0) {$n$};
-\node (G) at (5,0) {$c$};
-\node (H) at (4,-0.5) {$y \in F(n)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i$} (B)
-(C) edge node[above]{$o$} (B)
-(E) edge node[above]{$i'$} (F)
-(G) edge node[above]{$o'$} (F);
-\end{tikzpicture}
-\]
-the composite $M \odot N$ is given by taking the pushout of the two cospans in $\A$ over the shared foot which is the object $b$:
-\begin{equation}\label{eq:dcospanscomposition}
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a$};
-\node (B) at (1,1) {$m$};
-\node (C) at (2,0) {$b$};
-\node (D) at (3,1) {$n$};
-\node (E) at (4,0) {$c$};
-\node (F) at (2,2) {$m+n$};
-\node (G) at (2,3) {$m+_{b} n$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i$} (B)
-(C) edge node[above]{$o$} (B)
-(C) edge node [above] {$i'$} (D)
-(E) edge node [above] {$o'$} (D)
-(B) edge node [above] {$j_m$} (F)
-(D) edge node [above] {$j_{n}'$} (F)
-(F) edge node [left] {$\psi$} (G)
-(A) edge[bend left] node [left] {$\psi j_m i$} (G)
-(E) edge[bend right] node [right] {$\psi j_{n}' o'$} (G);
-\end{tikzpicture}
-\end{equation}
-The composite decoration $x \odot y$ on the apex $m+_b n$ is given by:
-$$x \odot y = 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{x \times y} F(m) \times F(n) \xrightarrow{\phi_{m,n}} F(m+n) \xrightarrow{F(\psi)} F(m+_{b}n)$$
-where $\psi \maps m + n \to m+_{b} n$ is the natural map from the coproduct to the pushout and $\phi_{m,n} \maps F(m) \times F(n) \to F(m+n)$ is the natural transformation coming from the structure of the lax monoidal pseudofunctor $F \maps \A \to \Cat$.
-Given two horizontally composable maps of $F$-decorated cospans which we respectively denote by $\alpha$ and $\beta$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$a$};
-\node (A') at (0,-0.5) {$a'$};
-\node (B) at (1,0.5) {$m$};
-\node (C) at (2,0.5) {$b$};
-\node (C') at (2,-0.5) {$b'$};
-\node (D) at (1,-0.5) {$m'$};
-\node (E) at (3,0.5) {$x \in F(m)$};
-\node (F) at (3,-0.5) {$x' \in F(m')$};
-\node (G) at (4,0.5) {$b$};
-\node (H) at (5,0.5) {$n$};
-\node (I) at (6,0.5) {$c$};
-\node (G') at (4,-0.5) {$b'$};
-\node (H') at (5,-0.5) {$n'$};
-\node (I') at (6,-0.5) {$c'$};
-\node (J) at (7,0.5) {$y \in F(n)$};
-\node (K) at (7,-0.5) {$y' \in F(n')$};
-\node (L) at (1,-1) {$\tau_\alpha \maps F(h_1)(x) \to x'$};
-\node (M) at (5,-1) {$\tau_\beta \maps F(h_2)(y) \to y'$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i_1$} (B)
-(C) edge node[above]{$o_1$} (B)
-(A) edge node[left]{$f$} (A')
-(C) edge node[right]{$g$} (C')
-(A') edge node[above] {$i_1'$} (D)
-(C') edge node[above] {$o_1'$} (D)
-(B) edge node [left] {$h_1$} (D)
-(G) edge node [above] {$i_2$} (H)
-(G) edge node [left] {$g$} (G')
-(H) edge node [left] {$h_2$} (H')
-(G') edge node [above] {$i_2'$} (H')
-(I) edge node [above] {$o_2$} (H)
-(I) edge node [right] {$k$} (I')
-(I') edge node [above] {$o_2'$} (H');
-\end{tikzpicture}
-\]
-their horizontal composite $\alpha \odot \beta$ is the pair given by first horizontally composing the two maps of cospans in $\A$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$a$};
-\node (A') at (0,-0.5) {$a'$};
-\node (B) at (1.5,0.5) {$m+_{b} n$};
-\node (C) at (3,0.5) {$c$};
-\node (C') at (3,-0.5) {$c'$};
-\node (D) at (1.5,-0.5) {$m'+_{b'}n'$};
-\node (E) at (4.5,0.5) {$x \odot y \in F(m+_b n)$};
-\node (F) at (4.5,-0.5) {$x' \odot y' \in F(m' +_{b'} n')$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$\psi j_m i_1$} (B)
-(C) edge node[above]{$\psi j_n o_2$} (B)
-(A) edge node[left]{$f$} (A')
-(C) edge node[right]{$k$} (C')
-(A') edge node [above]{$\psi j_{m'} i_1'$} (D)
-(C') edge node [above]{$\psi j_{n'} o_2'$} (D)
-(B) edge node [left] {$h_1 +_g h_2$} (D);
-\end{tikzpicture}
-\]
-together with the decoration morphism $\tau_{\alpha \odot \beta} \colon F(h_1 +_g h_2)(x \odot y) \to (x' \odot y')$ given by the following commutative diagram:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (4.75,0) {$\tau_\alpha \times \tau_\beta \Swarrow$};
-\node (D) at (3,0) {$1 \xrightarrow{\lambda^{-1}} 1 \times 1$};
-\node (E) at (5.5,0.5) {$F(m) \times F(n)$};
-\node (E') at (5.5,-0.5) {$F(m') \times F(n')$};
-\node (B) at (7.5,0.5) {$F(m+n)$};
-\node (B') at (7.5,-0.5) {$F(m' + n')$};
-\node (C) at (9.25,0.5) {$F(m+_{b} n)$};
-\node (C') at (9.25,-0.5) {$F(m' +_{b'} n')$};
-\path[->,font=\scriptsize,>=angle 90]
-(E) edge node [above] {$\phi_{m,n}$} (B)
-(E') edge node [above] {$\phi_{m',n'}$} (B')
-(B) edge node [above] {$F(\psi)$} (C)
-(B') edge node [above] {$F(\psi)$} (C')
-(C) edge node [right] {$F(h_1 +_g h_2)$} (C')
-(B) edge node [right] {$F(h_1 + h_2)$} (B')
-(D) edge node [above] {$x \times y$} (E)
-(D) edge node [below] {$x' \times y'$} (E')
-(E) edge node [right] {$F(h_1) \times F(h_2)$} (E');
-\end{tikzpicture}
-\]
-The middle square commutes since $F$ is a lax monoidal pseudofunctor and the right square commutes as the underlying square commutes.
-The decorations $x \odot y$ and $x' \odot y'$ are given respectively by the top and bottom composite of arrows and the decoration morphism $\tau_{\alpha \odot \beta}$ is given by composing $\tau_\alpha \times \tau_\beta$ with the two commuting squares.
-It is clear that the equations $S(M \odot N)=S(M)$ and $T(M \odot N)=T(N)$ hold, and this finishes defining the four structure functors $U,S,T$ and $\odot$.
-
-Lastly, our double category is required to have an associator $\alpha$ and left and right unitors $\lambda$ and $\rho$ which are natural isomorphisms governing the composition of horizontal 1-cells that are required to satisfy the standard coherence axioms for a monoidal category, as well as $S(\alpha),S(\lambda),S(\rho),T(\alpha),T(\lambda)$ and $T(\rho)$ all being identities.
-We will only show the associator $\alpha$, left unitor $\lambda$ and the pentagon identity, as the remaining details will be similar to these.
-
-First we will build the associator $\alpha \colon \odot (\odot \times 1) \Rightarrow \odot (1 \times \odot)$, which will be a globular 2-morphism; in other words, a map of $F$-decorated cospans with identities on the sides.
-Given three composable horizontal 1-cells $M_1, M_2$ and $M_3$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a$};
-\node (B) at (1,0) {$m_1$};
-\node (C) at (2,0) {$b$};
-\node (D) at (1,-0.5) {$x_1 \in F(m_1)$};
-\node (E) at (3,0) {$b$};
-\node (F) at (4,0) {$m_2$};
-\node (G) at (5,0) {$c$};
-\node (H) at (4,-0.5) {$x_2 \in F(m_2)$};
-\node (I) at (6,0) {$c$};
-\node (J) at (7,0) {$m_3$};
-\node (K) at (8,0) {$d$};
-\node (L) at (7,-0.5) {$x_3 \in F(m_3)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i$} (B)
-(C) edge node[above]{$o$} (B)
-(E) edge node[above]{$i'$} (F)
-(G) edge node[above]{$o'$} (F)
-(I) edge node[above]{$i''$} (J)
-(K) edge node[above]{$o''$} (J);
-\end{tikzpicture}
-\]
-we first compute $(M_1 \odot M_2) \odot M_3)$ by pushing out the first two cospans followed by the third:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a$};
-\node (B) at (2,0) {$(m_1 +_b m_2) +_c m_3$};
-\node (C) at (4,0) {$d$};
-%\node (D) at (3,0) {$x \in F(m)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$$} (B)
-(C) edge node[above]{$$} (B);
-\end{tikzpicture}
-\]
-as well as the decoration $(x_1 \odot x_2) \odot x_3$ on the apex obtained as explained above.
-Explicitly, the decoration $(x_1 \odot x_2) \odot x_3) \in F((m_1+_b m_2) +_c m_3)$ is obtained as the composite $$ (x_1 \odot x_2) \odot x_3 \mapseqq 1 \xrightarrow{\zeta_1} F(m_1+_{b} m_2) \times F(m_3) \xrightarrow{\phi_{m_1+_{b} m_2, m_3}} F((m_1+_{b}m_2) +m_3) \xrightarrow{F(\psi)} F((m_1+_{b} m_2)+_{c} m_3)$$where$$\scriptstyle{\zeta_1 \mapseqq 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{x_1 \times x_2} F(m_1) \times F(m_2) \xrightarrow{\phi_{m_1,m_2}} F(m_1+m_2) \xrightarrow{F(j)} F(m_1+_b m_2) \xrightarrow {\rho^{-1}} F(m_1+_b m_2) \times 1 \xrightarrow{1 \times x_3} F(m_1+_b m_2) \times F(m_3).}$$
-The composite $M_1 \odot (M_2 \odot M_3)$ is obtained similarly:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a$};
-\node (B) at (2,0) {$m_1 +_b (m_2 +_c m_3)$};
-\node (C) at (4,0) {$d$};
-%\node (D) at (3,0) {$x \in F(m)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$$} (B)
-(C) edge node[above]{$$} (B);
-\end{tikzpicture}
-\]
-as well as the decoration $x_1 \odot (x_2 \odot x_3)$ on the apex:
-$$x_1 \odot (x_2 \odot x_3) \mapseqq 1 \xrightarrow{\zeta_2} F(m_1) \times F(m_2 +_c m_3) \xrightarrow{\phi_{m_1, m_2 +_c m_3}} F(m_1+(m_2 +_c +m_3)) \xrightarrow{F(\psi)} F(m_1+_{b} (m_2+_{c} m_3))$$with $\zeta_2$ being similar to $\zeta_1$ above.
-The associator $\alpha$ is then given by the map of $F$-decorated cospans given by the map of cospans
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$a$};
-\node (A') at (0,-0.5) {$a$};
-\node (B) at (1.5,0.5) {$(m_1+_{b} m_2)+_{c} m_3$};
-\node (C) at (3,0.5) {$d$};
-\node (C') at (3,-0.5) {$d$};
-\node (D) at (1.5,-0.5) {$m_1+_{b}(m_2 +_{c} m_3)$};
-\node (E) at (5.5,0.5) {$(x_1 \odot x_2) \odot x_3 \in F((m_1+_{b} m_2)+_{c} m_3)$};
-\node (F) at (5.5,-0.5) {$x_1 \odot (x_2 \odot x_3) \in F(m_1+_{b} (m_2 +_{c} m_3))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$$} (B)
-(C) edge node[above]{$$} (B)
-(A) edge node[left]{$\id_a$} (A')
-(C) edge node[right]{$\id_d$} (C')
-(A') edge node {$$} (D)
-(C') edge node {$$} (D)
-(B) edge node [left] {$\alpha$} (D);
-\end{tikzpicture}
-\]
-together with the decoration morphism $\tau_\alpha \colon F(\alpha)((x_1 \odot x_2) \odot x_3) \to (x_1 \odot (x_2 \odot x_3))$ that is obtained by pasting various commutative squares together, as we did for a horizontal composite above.
-The associator $\alpha$ will then satisfy the pentagon identity:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (-0.5,0) {$((M_1 \odot M_2) \odot M_3) \odot M_4$};
-\node (B) at (3,1.05) {$(M_1 \odot (M_2 \odot M_3)) \odot M_4$};
-\node (C) at (6.5,0) {$M_1 \odot ((M_2 \odot M_3) \odot M_4)$};
-\node (D) at (1.5,-1.05) {$(M_1 \odot M_2) \odot (M_3 \odot M_4)$};
-\node (E) at (4.5,-1.05) {$M_1 \odot (M_2 \odot (M_3 \odot M_4))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node [above] {$\alpha \times 1$}(B)
-(B) edge node [above] {$\alpha$}(C)
-(A) edge node [below] {$\alpha$}(D)
-(D) edge node [above] {$\alpha$}(E)
-(C) edge node [below] {$1 \times \alpha$}(E);
-\end{tikzpicture}
-\]
-which we may realize in two stages.
-First, for the underlying pentagon of maps of cospans in $\A$ commuting due to the fact that $\lCsp(\A)$ is a double category with its own associator that satisfies the pentagon identity, and second, for the pentagon of morphisms of decorations due to the pasting of various commutative squares in $\Cat$.
-
-We next construct the left unitor. Given a horizontal 1-cell $M$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a$};
-\node (B) at (1,0) {$m$};
-\node (C) at (2,0) {$b$};
-\node (D) at (3,0) {$x \in F(m)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i$} (B)
-(C) edge node[above]{$o$} (B);
-\end{tikzpicture}
-\]
-the left unitor will be a globular 2-morphism $\lambda \colon 1_a \odot M \to M$, where the identity horizontal 1-cell on the object $a$ will once again make use of the trivial decoration on an object introduced earlier.
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a$};
-\node (B) at (1,0) {$a$};
-\node (C) at (2,0) {$a$};
-\node (D) at (3,0) {$\bot_a \in F(a)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$\id_a$} (B)
-(C) edge node[above]{$\id_a$} (B);
-\end{tikzpicture}
-\]
-To compose $1_a$ and $M$, we first compose the two cospans in $\A$ by pushing out over their shared object $a$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a$};
-\node (B) at (1,1) {$a$};
-\node (C) at (2,0) {$a$};
-\node (D) at (3,1) {$m$};
-\node (E) at (4,0) {$b$};
-\node (F) at (2,2) {$a+m$};
-\node (G) at (2,3) {$a+_{a} m$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$\id_a$} (B)
-(C) edge node[above]{$\id_a$} (B)
-(C) edge node [above] {$i$} (D)
-(E) edge node [above] {$o$} (D)
-(B) edge node [above] {$j_a$} (F)
-(D) edge node [above] {$j_m$} (F)
-(F) edge node [left] {$\psi$} (G)
-(A) edge[bend left] node [left] {$\psi j_a$} (G)
-(E) edge[bend right] node [right] {$\psi j_{m} o$} (G);
-\end{tikzpicture}
-\]
-The composite decoration $\bot_a \odot x$ will be given by the composite
-$$1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{\bot_a \times x} F(a) \times F(m) \xrightarrow{\phi_{a,m}} F(a+m) \xrightarrow{F(\psi)} F(a+_{a} m).$$
-The left unitor is then the map of $F$-decorated cospans determined by the following map of cospans in $\A$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$a$};
-\node (A') at (0,-0.5) {$a$};
-\node (B) at (1.5,0.5) {$a+_{a} m$};
-\node (C) at (3,0.5) {$b$};
-\node (C') at (3,-0.5) {$b$};
-\node (D) at (1.5,-0.5) {$m$};
-\node (E) at (4.5,0.5) {$\bot_a \odot x \in F(a+_{a} m)$};
-\node (F) at (4.5,-0.5) {$x \in F(m)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$\psi j_a$} (B)
-(C) edge node[above]{$\psi j_m o$} (B)
-(A) edge node[left]{$\id_{a}$} (A')
-(C) edge node[right]{$\id_{b}$} (C')
-(A') edge node [above]{$i$} (D)
-(C') edge node [above]{$o$} (D)
-(B) edge node [left] {$\ell$} (D);
-\end{tikzpicture}
-\]
-together with the decoration morphism $\tau_\lambda \colon F(\ell)(\bot_a \odot x) \to x$; note, that $\ell \colon a+_a m \to m$ is a canonical isomorphism as both $a+_a m$ and $m$ are colimits of the span $a \xleftarrow{\id_a} a \xrightarrow{i} m$.
-The right unitor $\rho$ is similar, the two unitality squares are similar to the associator shown above, and it is clear that the source and target functors applied to the associator and left and right unitors yield identities.
-
-The final property that we will check is the interchange law for 2-morphisms. Suppose that we have four 2-morphisms $\alpha, \beta, \alpha'$ and $\beta'$ as shown below:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$a$};
-\node (A') at (0,-0.5) {$a'$};
-\node (B) at (1,0.5) {$m$};
-\node (C) at (2,0.5) {$b$};
-\node (C') at (2,-0.5) {$b'$};
-\node (D) at (1,-0.5) {$m'$};
-\node (E) at (3,0.5) {$x \in F(m)$};
-\node (F) at (3,-0.5) {$x' \in F(m')$};
-\node (G) at (4,0.5) {$b$};
-\node (H) at (5,0.5) {$n$};
-\node (I) at (6,0.5) {$c$};
-\node (G') at (4,-0.5) {$b'$};
-\node (H') at (5,-0.5) {$n'$};
-\node (I') at (6,-0.5) {$c'$};
-\node (J) at (7,0.5) {$y \in F(n)$};
-\node (K) at (7,-0.5) {$y' \in F(n')$};
-\node (L) at (1,-1) {$\tau_\alpha \maps F(h_1)(x) \to x'$};
-\node (M) at (5,-1) {$\tau_\beta \maps F(h_2)(y) \to y'$};
-\node (A'') at (0,-1.5) {$a'$};
-\node (A''') at (0,-2.5) {$a''$};
-\node (B'') at (1,-1.5) {$m'$};
-\node (C'') at (2,-1.5) {$b'$};
-\node (C''') at (2,-2.5) {$b''$};
-\node (D'') at (1,-2.5) {$m''$};
-\node (E'') at (3,-1.5) {$x' \in F(m')$};
-\node (F'') at (3,-2.5) {$x'' \in F(m'')$};
-\node (G'') at (4,-1.5) {$b'$};
-\node (H'') at (5,-1.5) {$n'$};
-\node (I'') at (6,-1.5) {$c'$};
-\node (G''') at (4,-2.5) {$b''$};
-\node (H''') at (5,-2.5) {$n''$};
-\node (I''') at (6,-2.5) {$c''$};
-\node (J'') at (7,-1.5) {$y' \in F(n')$};
-\node (K'') at (7,-2.5) {$y'' \in F(n'')$};
-\node (L'') at (1,-3) {$\tau_{\alpha'} \maps F(h_1')(x') \to x''$};
-\node (M'') at (5,-3) {$\tau_{\beta'} \maps F(h_2')(y') \to y''$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i_1$} (B)
-(C) edge node[above]{$o_1$} (B)
-(A) edge node[left]{$f$} (A')
-(C) edge node[right]{$g$} (C')
-(A') edge node[above] {$i_1'$} (D)
-(C') edge node[above] {$o_1'$} (D)
-(B) edge node [left] {$h_1$} (D)
-(G) edge node [above] {$i_2$} (H)
-(G) edge node [left] {$g$} (G')
-(H) edge node [left] {$h_2$} (H')
-(G') edge node [above] {$i_2'$} (H')
-(I) edge node [above] {$o_2$} (H)
-(I) edge node [right] {$k$} (I')
-(I') edge node [above] {$o_2'$} (H')
-(A'') edge node[above]{$i_1'$} (B'')
-(C'') edge node[above]{$o_1'$} (B'')
-(A'') edge node[left]{$f'$} (A''')
-(C'') edge node[right]{$g'$} (C''')
-(A''') edge node[above] {$i_1''$} (D'')
-(C''') edge node[above] {$o_1''$} (D'')
-(B'') edge node [left] {$h_1'$} (D'')
-(G'') edge node [above] {$i_2'$} (H'')
-(G'') edge node [left] {$g'$} (G''')
-(H'') edge node [left] {$h_2'$} (H''')
-(G''') edge node [above] {$i_2''$} (H''')
-(I'') edge node [above] {$o_2'$} (H'')
-(I'') edge node [right] {$k'$} (I''')
-(I''') edge node [above] {$o_2''$} (H''');
-\end{tikzpicture}
-\]
-We may compose these first vertically and then horizontally, or first horizontally and then vertically, and we must show that these two ways of composing yield the same result.
-Composing first vertically and then horizontally results in:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$a$};
-\node (A') at (0,-0.5) {$a''$};
-\node (B) at (2,0.5) {$m+_{b} n$};
-\node (C) at (4,0.5) {$c$};
-\node (C') at (4,-0.5) {$c''$};
-\node (D) at (2,-0.5) {$m'' +_{b''} n''$};
-\node (E) at (5.5,0.5) {$x \odot y \in F(m+_{b} n)$};
-\node (F) at (5.5,-0.5) {$x'' \odot y'' \in F(m'' +_{b''} n'')$};
-\node (G) at (2,-1) {$\tau_{(\alpha' \alpha) \odot (\beta' \beta)} \maps F((h_1' h_1)+_{g' g} (h_2' h_2))(x \odot y) \to x'' \odot y''$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$ \psi j_m i_1$} (B)
-(C) edge node[above]{$ \psi j_n o_2$} (B)
-(A) edge node[left]{$f' f$} (A')
-(C) edge node[right]{$k' k$} (C')
-(A') edge node [above]{$\psi j_{m''} i_1''$} (D)
-(C') edge node [above]{$\psi j_{n''} o_2''$} (D)
-(B) edge node [left] {$(h_1' h_1) +_{g' g} (h_2' h_2)$} (D);
-\end{tikzpicture}
-\]
-whereas first composing horizontally and then vertically results in:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$a$};
-\node (A') at (0,-0.5) {$a''$};
-\node (B) at (2,0.5) {$m+_{b} n$};
-\node (C) at (4,0.5) {$c$};
-\node (C') at (4,-0.5) {$c''$};
-\node (D) at (2,-0.5) {$m'' +_{b''} n''$};
-\node (E) at (5.5,0.5) {$x \odot y \in F(m+_{b} n)$};
-\node (F) at (5.5,-0.5) {$x'' \odot y'' \in F(m'' +_{b''} n'')$};
-\node (G) at (2,-1) {$\tau_{(a' \odot \beta')(\alpha \odot \beta)} \maps F((h_1' +_{g'} h_2')(h_1 +_g h_2))(x \odot y) \to x'' \odot y''.$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$\psi j_{m} i_1$} (B)
-(C) edge node[above]{$\psi j_{n} o_2$} (B)
-(A) edge node[left]{$f' f$} (A')
-(C) edge node[right]{$k' k$} (C')
-(A') edge node [above]{$\psi j_{m''} i_1''$} (D)
-(C') edge node [above]{$\psi j_{n''} o_2''$} (D)
-(B) edge node [left] {$(h_1' +_{g'} h_2')(h_1 +_g h_2)$} (D);
-\end{tikzpicture}
-\]
-Everything about these two composites appears identical except for the two middle morphisms and the two morphisms of decorations.
-However, the two maps $(h_1' h_1) +_{g' g} (h_2' h_2) \maps m+_{b} n \to m'' +_{b''}n''$ and $(h_1' +_{g'} h_2')(h_1 +_g h_2) \maps m+_{b} n \to m'' +_{b''} n''$ are the same universal map realized in two different ways.
-The two morphisms of decorations $\tau_{(\alpha' \odot \beta')(\alpha \odot \beta)}$ and $\tau_{(\alpha' \alpha) \odot (\beta' \beta)}$ are also the same as they are obtained as two different compositions of four 2-morphisms in $\Cat$, namely first vertically and then horizontally and first horizontally and then vertically.
-The interchange law for $\Cat$ says that these two composites must be the same as well, and thus the interchange law for our double category $F\lCsp$ is also satisfied.
-\end{comment}
 \end{proof}
@@
 
-Let $\Dbl$ denote the 2-category of double categories, double functors and double transformations.
-One can check that $\Dbl$ has finite products, and in any 2-category with finite products we can define a `pseudomonoid', which is a categorified analogue of a monoid \cite{DS}.
-For example, a pseudomonoid in $\Cat$ is a monoidal category.
-We can also define braided and symmetric pseudomonoids, which in $\Cat$ are braided and symmetric monoidal categories.
-
 \begin{defn}

### 2020-12-01 cospans.tex
started with 2.2

@@
 In this section we build the symmetric monoidal double category $F \lCsp$ mentioned in the introduction, and then study the functoriality of this construction.
-The definition of a lax monoidal pseudofunctor is recalled in \cref{subsec:bicats}, and the basics of double categories are recalled in \cref{sec:doublecats}.
+The definition of a lax monoidal pseudofunctor is recalled in \cref{subsec:bicats}, and the definition of a double category is recalled in \cref{defn:double_category}.
 
 \begin{thm}\label{thm:decorated_cospans}
-Let $\A$ be a category with finite colimits and $F \maps \A \to \Cat$ a lax monoidal pseudofunctor. Then there exists a double category $F\lCsp$ in which
+Let $\A$ be a category with finite colimits and $F \maps (\A,+) \to (\Cat,\times)$ a lax monoidal pseudofunctor. Then there exists a double category $F\lCsp$ in which
 \begin{itemize}
@@
 \begin{proof}
-Take $\A$ to have finite colimits and let $(F,\phi,\phi_0) \maps (A,+,0) \to (\Cat,\times, 1)$ be a lax monoidal pseudofunctor.
+Take $\A$ to have finite colimits and let $(F,\phi,\phi_0) \maps (A,+) \to (\Cat,\times)$ be a lax monoidal pseudofunctor.
 We shall define the category of objects $F\lCsp_0$, the category of arrows $F\lCsp_1$, as well as the four structure functors which tie them together: the source and target functors $S,T \colon F\lCsp_1 \to F\lCsp_0$, the composition functor $\odot \colon F\lCsp_1 \times_{F\lCsp_0} F\lCsp_1 \to F\lCsp_1$ and the unit functor $U \colon F\lCsp_0 \to F\lCsp_1$.
@@
 
+The following result establishes that under the same assumptions as \cref{thm:decorated_cospans}, the formed double category of decorated cospans is monoidal; it becomes symmetric when the lax monoidal pseudofunctor is.
+The definitions of (symmetric) monoidal double categories are recalled in \cref{defn:monoidal_double_category,defn:symmetric_monoidal_double_category}.
+
 \begin{thm}\label{DC}
 Let $\A$ be a category with finite colimits and let $F \maps (\A,+) \to (\Cat,\times)$ a symmetric lax monoidal pseudofunctor.
-Then the double category $F\lCsp$ of Theorem \ref{thm:decorated_cospans} is symmetric monoidal, where
-\begin{enumerate}
-\item{the tensor product of two objects $a$ and $b$ is their coproduct $a+b$ in $\A$,}
-\item{the tensor product of two vertical 1-morphisms $f \colon a \to b$ and $f' \colon a' \to b'$ is the vertical 1-morphism $f+f' \colon a+a' \to b+b'$,}
-\item{the tensor product of two horizontal 1-cells $M_1$ and $M_2$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a_1$};
-\node (B) at (1,0) {$m_1$};
-\node (C) at (2,0) {$b_1$};
-\node (D) at (1,-0.5) {$x_1 \in F(m_1)$};
-\node (E) at (3,0) {$a_2$};
-\node (F) at (4,0) {$m_2$};
-\node (G) at (5,0) {$b_2$};
-\node (H) at (4,-0.5) {$x_2 \in F(m_2)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i_1$} (B)
-(C) edge node[above]{$o_1$} (B)
-(E) edge node[above]{$i_2$} (F)
-(G) edge node[above]{$o_2$} (F);
-\end{tikzpicture}
-\]
-is the horizontal 1-cell $M_1 \otimes M_2$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a_1+a_2$};
-\node (B) at (1.5,0) {$m_1+m_2$};
-\node (C) at (3,0) {$b_1+b_2$};
-\node (D) at (4.55,0) {$x_1+x_2 \in F(m_1+m_2)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i_1+i_2$} (B)
-(C) edge node[above]{$o_1+o_2$} (B);
-\end{tikzpicture}
-\]
+Then the double category $F\lCsp$ is symmetric monoidal, where the tensor product
+\begin{itemize}
+\item of two objects $a$ and $b$ is their coproduct $a+b$ in $\A$,
+\item of two vertical 1-morphisms $f \maps a \to b$ and $f' \maps a' \to b'$ is $f+f' \maps a+a' \to b+b'$ in $\A$,
+\item of two horizontal 1-cells $(a_1\to m_1\leftarrow b_1,x_1\in F(m_1))$ and $(a_2\to m_2\leftarrow b_2,x_2\in F(m_2))$ is 
 \begin{equation}\label{eq:tensordecoration}
-x_1+x_2 \mapseqq 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{x_1 \times x_2} F(m_1) \times F(m_2) \xrightarrow{\phi_{m_1,m_2}} F(m_1+m_2)
+\begin{tikzcd}
+& m_1+m_2 & \\
+a_1+a_2\ar[ur,"i_1+i_2"] && b_1+b_2,\ar[ul,"o_1+o_2"']
+\end{tikzcd}\qquad1\xrightarrow{x_1\times x_2}F(m_1)\times F(m_2)\xrightarrow{\phi_{m_1,m_2}}F(m_1+m_2)
 \end{equation}
-}
-\item{the tensor product of two 2-morphisms $\alpha$ and $\beta$:
-\[
-\begin{tikzpicture}[scale=1.5]
+%$M_1$ and $M_2$:
+%\[
+%\begin{tikzpicture}[scale=1.5]
+%\node (A) at (0,0) {$a_1$};
+%\node (B) at (1,0) {$m_1$};
+%\node (C) at (2,0) {$b_1$};
+%\node (D) at (1,-0.5) {$x_1 \in F(m_1)$};
+%\node (E) at (3,0) {$a_2$};
+%\node (F) at (4,0) {$m_2$};
+%\node (G) at (5,0) {$b_2$};
+%\node (H) at (4,-0.5) {$x_2 \in F(m_2)$};
+%\path[->,font=\scriptsize,>=angle 90]
+%(A) edge node[above]{$i_1$} (B)
+%(C) edge node[above]{$o_1$} (B)
+%(E) edge node[above]{$i_2$} (F)
+%(G) edge node[above]{$o_2$} (F);
+%\end{tikzpicture}
+%\]
+%is the horizontal 1-cell $M_1 \otimes M_2$:
+%\[
+%\begin{tikzpicture}[scale=1.5]
+%\node (A) at (0,0) {$a_1+a_2$};
+%\node (B) at (1.5,0) {$m_1+m_2$};
+%\node (C) at (3,0) {$b_1+b_2$};
+%\node (D) at (4.55,0) {$x_1+x_2 \in F(m_1+m_2)$};
+%\path[->,font=\scriptsize,>=angle 90]
+%(A) edge node[above]{$i_1+i_2$} (B)
+%(C) edge node[above]{$o_1+o_2$} (B);
+%\end{tikzpicture}
+%\]
+%\begin{equation}
+%x_1+x_2 \mapseqq 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{x_1 \times x_2} F(m_1) \times F(m_2) \xrightarrow{\phi_{m_1,m_2}} F(m_1+m_2)
+%\end{equation}
+
+\item of two 2-morphisms $\alpha$ and $\beta$ is:
+\[
+\begin{tikzpicture}[scale=1.2]
 \node (A) at (0,0.5) {$a$};
@@
 \node (D) at (1,-0.5) {$m'$};
-\node (E) at (3,0.5) {$x \in F(m)$};
-\node (F) at (3,-0.5) {$x' \in F(m')$};
-\node (G) at (4,0.5) {$c$};
-\node (H) at (5,0.5) {$n$};
-\node (I) at (6,0.5) {$d$};
-\node (G') at (4,-0.5) {$c'$};
-\node (H') at (5,-0.5) {$n'$};
-\node (I') at (6,-0.5) {$d'$};
-\node (J) at (7,0.5) {$y \in F(n)$};
-\node (K) at (7,-0.5) {$y' \in F(n')$};
-\node (L) at (1,-1) {$\tau_\alpha \maps F(h)(x) \to x'$};
-\node (M) at (5,-1) {$\tau_\beta \maps F(h')(y) \to y'$};
+%\node (E) at (2.7,0.5) {$\scriptstyle x \in F(m)$};
+\node () at (2.7,0) {$\otimes$};
+\node () at (6.2,0) {$=$};
+%\node (F) at (2.7,-0.5) {$\scriptstyle x' \in F(m')$};
+\node (G) at (3.5,0.5) {$c$};
+\node (H) at (4.5,0.5) {$n$};
+\node (I) at (5.5,0.5) {$d$};
+\node (G') at (3.5,-0.5) {$c'$};
+\node (H') at (4.5,-0.5) {$n'$};
+\node (I') at (5.5,-0.5) {$d'$};
+%\node (J) at (6.7,0.5) {$\scriptstyle y \in F(n)$};
+%\node (K) at (6.7,-0.5) {$\scriptstyle y' \in F(n')$};
+\node (L) at (1,-1.2) {$\scriptstyle\tau_\alpha \maps F(h)(x) \to x'\textrm{ in } F(m')$};
+\node (M) at (4.5,-1.2) {$\scriptstyle\tau_\beta \maps F(h')(y) \to y'\textrm{ in } F(n')$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (C) edge node[right]{$g$} (C')
-(A') edge node[above] {$i_1'$} (D)
-(C') edge node[above] {$o_1'$} (D)
+(A') edge node[below] {$i_1'$} (D)
+(C') edge node[below] {$o_1'$} (D)
 (B) edge node [left] {$h$} (D)
@@
 (H) edge node [left] {$h'$} (H')
-(G') edge node [above] {$i_2'$} (H')
+(G') edge node [below] {$i_2'$} (H')
 (I) edge node [above] {$o_2$} (H)
 (I) edge node [right] {$g'$} (I')
-(I') edge node [above] {$o_2'$} (H');
-\end{tikzpicture}
-\]
-is the 2-morphism $\alpha \otimes \beta$:
-\[
-\begin{tikzpicture}[scale=1.5]
+(I') edge node [below] {$o_2'$} (H');
+\end{tikzpicture}
+\begin{tikzpicture}[scale=1.1]
 \node (A) at (0,0.5) {$a+c$};
@@
 \node (D) at (2,-0.5) {$m'+n'$};
-\node (E) at (5.5,0.5) {$x+y \in F(m+n)$};
-\node (F) at (5.5,-0.5) {$x'+y' \in F(m'+n')$};
+%\node (E) at (5.2,0.5) {$\scriptstyle \phi_{m,n}(x,y)$};
+%\node (F) at (5.2,-0.5) {$\scriptstyle \phi_{m',n'}(x',y')$};
+\node () at (2,-1.3) {$\scriptstyle\tau_{\alpha\ot\beta}\maps F(h+h')(\phi_{m',n'}(x',y'))\to \phi_{m,n}(x,y)\textrm{ in }F(m'+n')$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (A) edge node[left]{$f+f'$} (A')
-(C) edge node[left]{$g+g'$} (C')
-(A') edge node [above]{$i_1'+i_2'$} (D)
-(C') edge node [above]{$o_1'+o_2'$} (D)
+(C) edge node[right]{$g+g'$} (C')
+(A') edge node [below]{$i_1'+i_2'$} (D)
+(C') edge node [below]{$o_1'+o_2'$} (D)
 (B) edge node [left] {$h+h'$} (D);
@@
 \]
-$$\tau_{\alpha+\beta} \colon F(h+h')(x+y) \to x'+y'$$
-where the decoration morphism $\tau_{\alpha+\beta}$ comes from the pasted diagram:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (4.75,0) {$\tau_\alpha \times \tau_\beta \Swarrow$};
-\node (D) at (3,0) {$1 \xrightarrow{\lambda^{-1}} 1 \times 1$};
-\node (E) at (5.5,0.5) {$F(m) \times F(n)$};
-\node (E') at (5.5,-0.5) {$F(m') \times F(n')$};
-\node (B) at (7.5,0.5) {$F(m+n)$};
-\node (B') at (7.5,-0.5) {$F(m' + n')$};
-\path[->,font=\scriptsize,>=angle 90]
-(E) edge node [above] {$\phi_{m,n}$} (B)
-(E') edge node [above] {$\phi_{m',n'}$} (B')
-(B) edge node [right] {$F(h + h')$} (B')
-(D) edge node [above] {$x \times y$} (E)
-(D) edge node [below] {$x' \times y'$} (E')
-(E) edge node [right] {$F(h) \times F(h')$} (E');
-\end{tikzpicture}
-\]
-}
-\end{enumerate}
+with decoration morphism $\tau_{\alpha\otimes\beta}$ given by the following diagram:
+\begin{displaymath}
+ \begin{tikzcd}[column sep=.5in, row sep=.1in]
+& F(m)\times F(n)\ar[r,"\phi_{m,n}"]\ar[dd,"F(h)\times F(h')"description]\ar[ddr,phantom,"\cong"] & F(m+n)\ar[dd,"F(h+h')"] \\
+1\ar[ur,"x\times y"]\ar[dr,"x'\times y'"']\ar[r,phantom,"\scriptstyle\Downarrow\tau_\alpha\times\tau_\beta"] & \phantom{A} && \\
+& F(m')\times F(n')\ar[r,"\phi_{m',n'}"'] & F(m'+n')
+ \end{tikzcd}
+\end{displaymath}
+\end{itemize}
 \end{thm}
@@
 \begin{proof}
-The definition of symmetric monoidal double category may be found in Definition \ref{defn:symmetric_monoidal_double_category}.
 We must show that both the category of objects $F\lCsp_0$ and the category of arrows $F\lCsp_1$ are symmetric monoidal categories, show that the monoidal unit of $F\lCsp_0$ is preserved by the unit functor $U$, show that the source and target functors $S,T \colon F\lCsp_1 \to F\lCsp_0$ are strict symmetric monoidal functors which preserve the associativity and unit constraints, define the globular isomorphisms $\chi$ and $\mu$ that relate how composition and units interact with the tensor product, and check that the required axioms are satisfied.
@@
 \label{defn:monoidal_double_category}
-A \define{monoidal double category} is a pseudomonoid in $\Dbl$. 
-\end{defn}
-
-This definition neatly packages a large quantity of information.   When we unpack it, we see a monoidal double category is a double category $\lD$ with:
+A \define{monoidal double category} is a pseudomonoid in $\Dbl$. Explicitly, it is a double category $\lD$ with:
 \begin{itemize}
 \item monoidal structures on both $\lD_0$
-and $\lD_1$, each with tensor product denoted $\otimes$, associator $a$, left unitor $\ell$ and right unitor $r$, such that the unit object of $\lD_0$ is preserved by the unit functor $U$, and the source and target functors $S,T \maps \lD_1 \to \lD_0$ are strict symmetric monoidal,
+and $\lD_1$, each with tensor product denoted $\otimes$, associator $a$, left unitor $\ell$ and right unitor $r$, such that the unit object of $\lD_0$ is preserved by the unit functor $U$, and the source and target functors $S,T \maps \lD_1 \to \lD_0$ are strict monoidal,
 \item the structure of a double functor on $\otimes$:
@@
 These structures must obey a number of equations, which can be found after \cite[Definition 2.10]{HS} and also \cite[Definition A.5]{BC}.
+\end{defn}
+%This definition neatly packages a large quantity of information.   When we unpack it, we see
 

### 2020-12-01 cospans.tex
working through proof of 2.2

@@
 
-The associator $\alpha \colon \odot (\odot \times 1) \Rightarrow \odot (1 \times \odot)$ is formed as follows: for three composable horizontal 1-cells
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$M_1=a$};
-\node (B) at (1,0) {$m_1$};
-\node (C) at (2,0) {$b$};
-\node (D) at (1,-0.5) {$x_1 \in F(m_1)$};
-\node (E) at (3,0) {$M_2=b$};
-\node (F) at (4,0) {$m_2$};
-\node (G) at (5,0) {$c$};
-\node (H) at (4,-0.5) {$x_2 \in F(m_2)$};
-\node (I) at (6,0) {$M_3=c$};
-\node (J) at (7,0) {$m_3$};
-\node (K) at (8,0) {$d$};
-\node (L) at (7,-0.5) {$x_3 \in F(m_3)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i$} (B)
-(C) edge node[above]{$o$} (B)
-(E) edge node[above]{$i'$} (F)
-(G) edge node[above]{$o'$} (F)
-(I) edge node[above]{$i''$} (J)
-(K) edge node[above]{$o''$} (J);
-\end{tikzpicture}
-\]
+The associator for horizontal composition
+%$\alpha \colon \odot (\odot \times 1) \Rightarrow \odot (1 \times \odot)$ 
+is formed as follows: for three composable horizontal 1-cells $M_1=(a\to m_1\leftarrow b,x_1\in F(m_1))$, $M_2=(b\to m_2\leftarrow c,x_2\in F(m_2)$ and $M_3=(c\to m_3\leftarrow d,x_3\in F(m_3)),$
+%\[
+%\begin{tikzpicture}[scale=1.5]
+%\node (A) at (0,0) {$M_1=a$};
+%\node (B) at (1,0) {$m_1$};
+%\node (C) at (2,0) {$b$};
+%\node (D) at (1,-0.5) {$x_1 \in F(m_1)$};
+%\node (E) at (3,0) {$M_2=b$};
+%\node (F) at (4,0) {$m_2$};
+%\node (G) at (5,0) {$c$};
+%\node (H) at (4,-0.5) {$x_2 \in F(m_2)$};
+%\node (I) at (6,0) {$M_3=c$};
+%\node (J) at (7,0) {$m_3$};
+%\node (K) at (8,0) {$d$};
+%\node (L) at (7,-0.5) {$x_3 \in F(m_3)$};
+%\path[->,font=\scriptsize,>=angle 90]
+%(A) edge node[above]{$i$} (B)
+%(C) edge node[above]{$o$} (B)
+%(E) edge node[above]{$i'$} (F)
+%(G) edge node[above]{$o'$} (F)
+%(I) edge node[above]{$i''$} (J)
+%(K) edge node[above]{$o''$} (J);
+%\end{tikzpicture}
+%\]
 the isomorphism $(M_1\odot M_2)\odot M_3\cong M_1\odot (M_2\odot M_3)$ is the isomorphism of cospans 
@@
 %\end{align*}
-\[
+\begin{equation}\label{eq:decoiso}
 \begin{tikzpicture}[scale=1.7]
@@
 \node (E) at (6.25,0.5) {$\scriptstyle{F(m_1 + m_2) \times F(m_3)}$};
-\node () at (7.625,0) {$\scriptstyle\cong$};
+\node () at (6,0) {$\scriptstyle\stackrel{\cref{eq:omega}}{\cong}$};
+\node () at (9.5,0) {$\scriptstyle\cong$};
 %\node () at (8.75,0) {$\cong$};
@@
 \path[->,font=\scriptsize,>=angle 90]
+(B) edge node [above] {} (B')
 (C) edge node [above] {} (F)
@@
 \end{tikzpicture}
-\]
+\end{equation}
 %%% Christina: I erased tau, and also Fpsi because they were not accurate and those arrows are OK to understand - the universal maps from a 'smaller' colimit to a 'bigger' one.
@@
 \begin{thm}\label{DC}
-Let $\A$ be a category with finite colimits and let $F \maps (\A,+) \to (\Cat,\times)$ a symmetric lax monoidal pseudofunctor.
+Let $\A$ be a category with finite colimits and let $(F,\phi,\phi_0)\maps (\A,+) \to (\Cat,\times)$ a symmetric lax monoidal pseudofunctor.
 Then the double category $F\lCsp$ is symmetric monoidal, where the tensor product
@@
 a_1+a_2\ar[ur,"i_1+i_2"] && b_1+b_2,\ar[ul,"o_1+o_2"']
-\end{tikzcd}\qquad1\xrightarrow{x_1\times x_2}F(m_1)\times F(m_2)\xrightarrow{\phi_{m_1,m_2}}F(m_1+m_2)
+\end{tikzcd}\qquad x_1\oplus x_2:=1\xrightarrow{x_1\times x_2}F(m_1)\times F(m_2)\xrightarrow{\phi_{m_1,m_2}}F(m_1+m_2)
 \end{equation}
@@
 \begin{proof}
-We must show that both the category of objects $F\lCsp_0$ and the category of arrows $F\lCsp_1$ are symmetric monoidal categories, show that the monoidal unit of $F\lCsp_0$ is preserved by the unit functor $U$, show that the source and target functors $S,T \colon F\lCsp_1 \to F\lCsp_0$ are strict symmetric monoidal functors which preserve the associativity and unit constraints, define the globular isomorphisms $\chi$ and $\mu$ that relate how composition and units interact with the tensor product, and check that the required axioms are satisfied.
-
-First we note that the category of objects $F\lCsp_0=\A$ is symmetric monoidal under chosen binary coproducts in $\A$ and the left and right unitors, associators and braidings are given as natural maps.
-Next we show that $F\lCsp_1$ is symmetric monoidal.
+%We must show that both the category of objects $F\lCsp_0$ and the category of arrows $F\lCsp_1$ are symmetric monoidal categories, show that the monoidal unit of $F\lCsp_0$ is preserved by the unit functor $U$, show that the source and target functors $S,T \colon F\lCsp_1 \to F\lCsp_0$ are strict symmetric monoidal functors which preserve the associativity and unit constraints, define the globular isomorphisms $\chi$ and $\mu$ that relate how composition and units interact with the tensor product, and check that the required axioms are satisfied.
+We first show that the categories of objects and arrows are symmetric monoidal, and that the source and target functors are symmetric strict monoidal.
+Indeed, the category of objects $F\lCsp_0=\A$ is symmetric monoidal under (chosen) binary coproducts in $\A$. The category of arrows
+$F\lCsp_1$ is also symmetric monoidal, with tensor product as in \cref{eq:tensordecoration} and monoidal unit
+\begin{comment}
 The category of arrows $F\lCsp_1$ has:
@@
 \]
-where the decoration on the apex is obtained using the natural transformation of the symmetric lax monoidal pseudofunctor $F$: $$x_1+x_2 \mapseqq 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{x_1 \times x_2} F(m_1) \times F(m_2) \xrightarrow{\phi_{m_1,m_2}} F(m_1+m_2).$$The monoidal unit $0_{F\lCsp_1}$ is given by:
+where the decoration on the apex is obtained using the natural transformation of the symmetric lax monoidal pseudofunctor $F$: $$x_1+x_2 \mapseqq 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{x_1 \times x_2} F(m_1) \times F(m_2) \xrightarrow{\phi_{m_1,m_2}} F(m_1+m_2).$$
+The monoidal unit $0_{F\lCsp_1}$ is given by:
 \[
@@
 \node (B) at (1,0) {$0$};
-\node (C) at (2,0) {$0$};
-\node (D) at (3,0) {$\bot_0 = \phi \in F(0)$};
+\node (C) at (2,0) {$0,$};
+\node (D) at (3,0) {\bot_0 = \phi \in F(0)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-where $0$ is the monoidal unit of $\A$ and $\phi \maps 1 \to F(0)$ is the morphism which is part of the structure of the symmetric lax monoidal pseudofunctor $F \maps \A \to \Cat$.
-It is also clear that $U(0)=0_{F\lCsp_1}$.
-
-Next we define the associator and left unitor of $F\lCsp_1$, with the right unitor being similar to the left. Given three objects $M_1, M_2$ and $M_3$ of $F\lCsp_1$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a_1$};
-\node (B) at (1,0) {$m_1$};
-\node (C) at (2,0) {$b_1$};
-\node (D) at (1,-0.5) {$x_1 \in F(m_1)$};
-\node (E) at (3,0) {$a_2$};
-\node (F) at (4,0) {$m_2$};
-\node (G) at (5,0) {$b_2$};
-\node (H) at (4,-0.5) {$x_2 \in F(m_2)$};
-\node (I) at (6,0) {$a_3$};
-\node (J) at (7,0) {$m_3$};
-\node (K) at (8,0) {$b_3$};
-\node (L) at (7,-0.5) {$x_3 \in F(m_3)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i_1$} (B)
-(C) edge node[above]{$o_1$} (B)
-(E) edge node[above]{$i_2$} (F)
-(G) edge node[above]{$o_2$} (F)
-(I) edge node[above]{$i_3$} (J)
-(K) edge node[above]{$o_3$} (J);
-\end{tikzpicture}
-\]
+\end{comment}
+\begin{displaymath}
+0\xrightarrow{!}0\xleftarrow{!}0,\quad 1\xrightarrow{\phi_0}F(0)
+\end{displaymath}
+where $0$ is the initial object in $\A$. Notice that this unit is $U_0$ as required. The associator of $F\lCsp_1$ is formed as follows: for three objects
+$M_1=(a_1\to m_1\leftarrow b_1,x_1\in F(m_1))$, $M_2=(a_2\to m_2\leftarrow b_2,x_2\in F(m_2))$ and $M_3=(a_3\to m_3\leftarrow b_3,x_3\in F(m_3),$
+%\[
+%\begin{tikzpicture}[scale=1.5]
+%\node (A) at (0,0) {$a_1$};
+%\node (B) at (1,0) {$m_1$};
+%\node (C) at (2,0) {$b_1$};
+%\node (D) at (1,-0.5) {$x_1 \in F(m_1)$};
+%\node (E) at (3,0) {$a_2$};
+%\node (F) at (4,0) {$m_2$};
+%\node (G) at (5,0) {$b_2$};
+%\node (H) at (4,-0.5) {$x_2 \in F(m_2)$};
+%\node (I) at (6,0) {$a_3$};
+%\node (J) at (7,0) {$m_3$};
+%\node (K) at (8,0) {$b_3$};
+%\node (L) at (7,-0.5) {$x_3 \in F(m_3)$};
+%\path[->,font=\scriptsize,>=angle 90]
+%(A) edge node[above]{$i_1$} (B)
+%(C) edge node[above]{$o_1$} (B)
+%(E) edge node[above]{$i_2$} (F)
+%(G) edge node[above]{$o_2$} (F)
+%(I) edge node[above]{$i_3$} (J)
+%(K) edge node[above]{$o_3$} (J);
+%\end{tikzpicture}
+%\]
+the isomorphism $(M_1\ot M_2)\ot M_3\cong M_1\ot(M_2\ot M_3)$ is the isomorphism of cospans
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0.5) {$(a_1+a_2)+a_3$};
+\node (A') at (0,-0.5) {$a_1+(a_2+a_3)$};
+\node (B) at (2.25,0.5) {$(m_1+m_2)+m_3$};
+\node (C) at (4.5,0.5) {$(b_1+b_2)+b_3$};
+\node (C') at (4.5,-0.5) {$b_1+(b_2+b_3)$};
+\node (D) at (2.25,-0.5) {$m_1+(m_2+m_3)$};
+\node (E) at (7,0.5) {$(x_1\oplus x_2)\oplus x_3 \in F((m_1{+}m_2){+}m_3)$};
+%{$\scriptstyle\phi_{m_1{+}m_2,m_3}(\phi_{m_1,m_2}(x_1,x_2),x_3) \in F((m_1{+}m_2){+}m_3)$};
+\node (F) at (7,-0.5) {$x_1\oplus (x_2\oplus x_3)\in F(m_1{+}(m_2{+}m_3))$};
+%{$\scriptstyle\phi_{m_1,m_2{+}m_3}(x_1,\phi_{m_2,m_3}(x_2,x_3))  \in F(m_1{+}(m_2{+}m_3))$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$(i_1{+}i_2){+}i_3$} (B)
+(C) edge node[above]{$(o_1{+}o_2){+}o_3$} (B)
+(A) edge node[left]{$\stackrel{\alpha}{\cong}$} (A')
+(C) edge node[right]{$\stackrel{\alpha}{\cong}$} (C')
+(A') edge node [below]{$i_1{+}(i_2{+}i_3)$} (D)
+(C') edge node [below]{$o_1{+}(o_2{+}o_3)$} (D)
+(B) edge node [left] {$\stackrel{\alpha}{\cong}$} (D);
+\end{tikzpicture}
+\]
+%%% Christina: I earlier dropped notation x+y for decorations because + is already overused and I find it potentially misleading for the reader. I hope the new symbol is OK?
+together with the decoration isomorphism $F(\alpha)(\phi_{m_1{+}m_2,m_3}(\phi_{m_1,m_2}(x_1,x_2),x_3))\cong\phi_{m_1,m_2{+}m_3}(x_1,\phi_{m_2,m_3}(x_2,x_3))$ formed in the same way as the left two parts of \cref{eq:decoiso}.
+\begin{comment}
 tensoring the first two and then the third results in $(M_1 \otimes M_2) \otimes M_3$:
@@
 together with the decoration isomorphism $\tau_\alpha \maps F(\alpha)((x_1+x_2)+x_3) \to x_1+(x_2+x_3)$.
+\end{comment}
+
+{\chris In progress}
 
@@
 \begin{itemize}
-\item monoidal structures on both $\lD_0$
-and $\lD_1$, each with tensor product denoted $\otimes$, associator $a$, left unitor $\ell$ and right unitor $r$, such that the unit object of $\lD_0$ is preserved by the unit functor $U$, and the source and target functors $S,T \maps \lD_1 \to \lD_0$ are strict monoidal,
+\item monoidal structures on both $\lD_0$ and $\lD_1$, each with tensor product denoted $\otimes$, associator $a$, left unitor $\ell$ and right unitor $r$, where if $I$ is the unit object of $\lD_0$ then $U_I$ is the unit of $\lD_1$, and such that the source and target functors $S,T \maps \lD_1 \to \lD_0$ are strict monoidal,
 \item the structure of a double functor on $\otimes$:

### 2020-12-01 cospans.tex
Improved definitions A.10 and A.11

@@
 % in LaTeX
-% 2020/11/27
+% 2020/12/1
 
@@
 They constructed this decorated cospan category via Fong's original formalism, using a lax symmetric monoidal functor $F \maps (\Fin\Set, +) \to (\Set, \times)$.
-However, composing this with the inclusion $(\Set, \times) \to (\Cat, \times)$ mapping sets to discrete categories, we get the data needed to create a decorated cospan double category $\mathbb{D}\mathbf{ynam}$.
+However, composing this with the inclusion $(\Set, \times) \to (\Cat, \times)$ mapping sets to discrete categories, we get the data needed to create a decorated cospan double category $\lD\mathbf{ynam}$.
 We believe that this is not equivalent to a structured cospan double category, but can this be proved?
@@
 \label{defn:monoidal_double_category}
-A \define{monoidal double category} is a pseudomonoid in $\Dbl$. Explicitly, it is a double category $\lD$ with:
+A \define{monoidal double category} is a pseudomonoid in $\Dbl$. 
+\end{defn} 
+\noindent
+Explicitly, a monoidal double category is a double category $\lD$ with:
 \begin{itemize}
-\item monoidal structures on both $\lD_0$ and $\lD_1$, each with tensor product denoted $\otimes$, associator $a$, left unitor $\ell$ and right unitor $r$, where if $I$ is the unit object of $\lD_0$ then $U_I$ is the unit of $\lD_1$, and such that the source and target functors $S,T \maps \lD_1 \to \lD_0$ are strict monoidal,
+\item monoidal structures on both $\lD_0$ and $\lD_1$, each with tensor product denoted $\otimes$, associator $a$, left unitor $\ell$ and right unitor $r$, such that if $I$ is the unit object of $\lD_0$ then $U_I$ is the unit of $\lD_1$, and such that the source and target functors $S,T \maps \lD_1 \to \lD_0$ are strict monoidal,
 \item the structure of a double functor on $\otimes$:
@@
 (M_1\odot M_2)\otimes (N_1\odot N_2)\]
-\[ \mu \maps U_{A\otimes B} \xrightarrow{\sim} (U_A \otimes U_B)\]
+\[ \mu \maps U_{A\otimes B} \xrightarrow{\sim} U_A \otimes U_B\]
+obeying a list of equations that can be found after \cite[Definition 2.10]{HS} and also \cite[Definition A.5]{BC}.
 \end{itemize}
-These structures must obey a number of equations, which can be found after \cite[Definition 2.10]{HS} and also \cite[Definition A.5]{BC}.
-\end{defn}
-%This definition neatly packages a large quantity of information.   When we unpack it, we see
 
@@
 \label{defn:symmetric_monoidal_double_category}
-A \define{braided monoidal double category} is a braided pseudomonoid in $\Dbl$.  Explicitly,
-it is a monoidal double category equipped with an invertible transformation
-\[ \beta \maps \otimes \Rightarrow \otimes \circ \tau \]
-called the \define{braiding}, where $\tau \maps \lD \times \lD \to \lD \times \lD$ is the twist double functor sending pairs in the object and arrow categories to the same pairs in the opposite order.
-The braiding is required to satisfy the usual two hexagon identities.
-If the braiding is self-inverse we say that $\lD$ is a \define{symmetric monoidal double category}.
+A \define{symmetric monoidal double category} is a symmetric pseudomonoid in $\Dbl$. 
 \end{defn}
+\noindent
+Explicitly, a symmetric monoidal double category is a monoidal double category $\lD$ such that:
+\begin{itemize}
+		\item $\lD_0$ and $\lD_1$ are symmetric monoidal categories, with braidings both denoted $\beta$.
+		\item The functors $S$ and $T$ are symmetric strict monoidal functors.
+		\item The following diagrams commute, expressing that the braiding is a transformation of double categories:
+		\[
+		\begin{tikzpicture}
+			\node (A) at (0,1.5) {\footnotesize{$(M_1 \odot M_2) \otimes (N_1 \odot N_2)$}};
+			\node (A') at (0,0) {\footnotesize{$(M_1\otimes N_1) \odot (M_2\otimes N_2)$}};
+			\node (B) at (5,1.5) {\footnotesize{$(N_1\odot N_2) \otimes (M_1 \odot M_2)$}};
+			\node (B') at (5,0) {\footnotesize{$(N_1 \otimes M_1) \odot (N_2 \otimes M_2)$}};
+			%
+			\path[->,font=\scriptsize]
+				(A) edge node[left]{$\chi$} (A')
+				(A) edge node[above]{$\beta$} (B)
+				(B) edge node[right]{$\chi$} (B')
+				(A') edge node[above]{$\beta \odot \beta$} (B');
+		\end{tikzpicture}
+		%
+		\quad
+		%
+		\begin{tikzpicture}
+			\node (A) at (0,1.5) {\footnotesize{$U_A \otimes U_B$}};
+			\node (A') at (0,0) {\footnotesize{$U_B\otimes U_A$}};
+			\node (B) at (2,1.5) {\footnotesize{$U_{A\otimes B} $}};
+			\node (B') at (2,0) {\footnotesize{$U_{B\otimes A}$}};
+			%
+			\path[->,font=\scriptsize]
+				(A) edge node[left]{$\beta$} (A')
+				(B) edge node[above]{$\mu$} (A)
+				(B) edge node[right]{$U_\beta$} (B')
+				(B') edge node[above]{$\mu$} (A');
+		\end{tikzpicture}
+		\]
+\end{itemize}
 
@@
 \end{defn}
-
-Unpacking this definition one obtains a number of diagrams which can be found after \cite[Definition 2.4]{HS}.
+\noindent
+Unpacking this definition one obtains a number of diagrams that can be found after \cite[Definition 2.4]{HS}.
 

### 2020-12-01 cospans.tex
eliminated stuff about braided pseudomonoids
finished section 5.4, on open Petri nets

@@
 \begin{thm}
+\label{thm:functoriality}
 Given two finitely cocomplete categories $\A$ and $\A'$, two symmetric lax monoidal pseudofunctors $F \maps \A \to \Cat$ and $F' \maps \A' \to \Cat$, a finite colimit preserving functor $H \maps \A \to \A'$, a symmetric lax monoidal pseudofunctor $E \maps \Cat \to \Cat$ and a 2-isomorphism $\theta \maps EF \Rightarrow F' H$ as in the following diagram,
@@
 \end{thm}
+
 \begin{proof}  See \cite[Theorem 4.2.1]{CourserThesis}. \end{proof}
@@
 again by \cref{eq:explicitstructure2} and the discussion after \cref{cor:fcocMonGroth}.
-It can be verified that with the above structure, $\lE_1$ is also a braided monoidal functor, and the rest of the axioms of \cref{defn:monoidal_double_functor} hold.
+It can be verified that with the above structure, $\lE_1$ is also a symmetric monoidal functor, and the rest of the axioms of \cref{defn:monoidal_double_functor} hold.
 \end{proof}
@@
 
-Decorated cospans were introduced by Fong \cite{Fong,FongThesis} to describe open systems as cospans equipped with extra data; they were then applied to open electrical circuits \cite{BF}, Markov processes \cite{BFP}, and chemical reaction networks \cite{BP}.
+Decorated cospans were introduced by Fong \cite{Fong,FongThesis} to describe open systems as cospans equipped with extra data.
+They were then applied to open electrical circuits \cite{BF}, Markov processes \cite{BFP}, and chemical reaction networks \cite{BP}.
 Unfortunately, some of these applications were marred by technical flaws, which were later fixed using structured cospans \cite[Sec.\ 5]{BC}.
@@
 
-Starting from the symmetric lax monoidal functor $F \maps (\Fin\Set, +) \to (\Cat,\times)$, \cref{DC} gives us a symmetric monoidal double category $F\lCsp$ in which:
+Starting from the symmetric lax monoidal pseudofunctor $F \maps (\Fin\Set, +) \to (\Cat,\times)$, \cref{DC} gives us a symmetric monoidal double category $F\lCsp$ in which:
 \begin{itemize}
@@
 We can also describe $\La$-circuits using decorated cospans.
-There is a symmetric lax monoidal functor $F \maps (\Fin\Set, +) \to (\Cat, \times)$ such that for any finite set $N$, the category $F(N)$ has:
+There is a symmetric lax monoidal pseudofunctor $F \maps (\Fin\Set, +) \to (\Cat, \times)$ such that for any finite set $N$, the category $F(N)$ has:
 \begin{itemize}
 \item objects being $\La$-\define{graph structures} on $N$: that is, $\La$-graphs where the set of nodes is $N$,
-\item morphisms are morphisms of $\La$-graphs that are the identity on the set of nodes.
+\item morphisms being morphisms of $\La$-graphs that are the identity on the set of nodes.
 \end{itemize}
@@
 	\]
-There is a functor $R \maps \Petri \to \Set$ sending any Petri net to its set of places, and this has
-a left adjoint $L \maps \Set \to \Petri$ sending any set $S$ to the Petri net with $S$ as its set of species and no transitions \cite[Lemma 11]{BM}.
-Since both $\Set$ and $\Petri$ have finite colimits and $L$ preserves them, Theorem \cref{thm:SC} yields a symmetric monoidal double category $\lOpen(\Petri)$ of open Petri nets which has:
+There is a functor $R \maps \Petri \to \Set$ sending any Petri net to its set of places, and this has a left adjoint $L \maps \Set \to \Petri$ sending any set $S$ to the Petri net with $S$ as its set of species and no transitions \cite[Lemma 11]{BM}.
+Since both $\Set$ and $\Petri$ have finite colimits and $L$ preserves them, \cref{thm:SC} yields a symmetric monoidal double category ${}_L \lCsp(\Petri)$ in which:
 \begin{itemize}
-\item objects given by sets,
-\item vertical 1-morphisms given by functions,
+\item objects are finite sets,
+\item vertical 1-morphisms are functions,
 \item horizontal 1-cells as \define{open Petri nets}, which are cospans in $\Petri$ of the form:
@@
 \]
-\item 2-morphisms as maps of cospans in $\Petri$ of the form:
+\item 2-morphisms are maps of cospans in $\Petri$ of the form:
 \[
@@
 \end{itemize}
-We can also obtain a similar double category using decorated cospans: define a pseudofunctor $F \maps \Set \to \Cat$ where given a set $s$, $F(s)$ is the category of all Petri net structures with $s$ as its set of species.
-This pseudofunctor $F$ is symmetric lax monoidal as both $(\Set,+,\emptyset)$ and $(\Cat,\times,1)$ are symmetric monoidal and given Petri nets $P \in F(s)$ and $P' \in F(s')$, we can place them side by side and consider them together as a single Petri net $P+P' \in F(s+s')$ with set of species $s+s'$, and thus we have natural transformations $\phi_{s,s'} \maps F(s) \times F(s') \to F(s+s')$ for any two sets $s$ and $s'$.
-The other structure morphism between monoidal units $\phi \maps 1_{\Petri} \to F(\emptyset)$ is defined by the unique morphism from the empty Petri net with the empty set for its set of species to the only possible Petri net on the empty set, which is also the empty Petri net.
-All of the diagrams that are required to commute are straightforward.
-Using \cref{DC}, we obtain a symmetric monoidal double category $F\lCsp$ which has:
-\begin{enumerate}
-\item{objects given by sets,}
-\item{vertical 1-morphisms given by functions,}
-\item{horizontal 1-cells given by pairs:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (D) at (-3,0) {$X$};
-\node (E) at (-2,0) {$Z$};
-\node (F) at (-1,0) {$Y$};
-\node (A) at (0,0) {$P \in F(Z)$};
-\path[->,font=\scriptsize,>=angle 90]
-(D) edge node [above] {$i$} (E)
-(F) edge node [above] {$o$} (E);
-\end{tikzpicture}
-\]
-and}
-\item{2-morphisms as maps of cospans in $\Set$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (E) at (3,0) {$X_1$};
-\node (F) at (5,0) {$Y_1$};
-\node (G) at (4,0) {$Z_1$};
-\node (E') at (3,-1) {$X_2$};
-\node (F') at (5,-1) {$Y_2$};
-\node (G') at (4,-1) {$Z_2$};
-\node (A) at (6,0) {$P_1 \in F(Z_1)$};
-\node (B) at (6,-1) {$P_2 \in F(Z_2)$};
-\path[->,font=\scriptsize,>=angle 90]
-(F) edge node[above]{$o_1$} (G)
-(E) edge node[left]{$f$} (E')
-(F) edge node[right]{$g$} (F')
-(G) edge node[left]{$h$} (G')
-(E) edge node[above]{$i_1$} (G)
-(E') edge node[above]{$i_2$} (G')
-(F') edge node[above]{$o_2$} (G');
-\end{tikzpicture}
-\]
-together with a morphism of Petri nets $\tau \maps F(h)(P_1) \to P_2$ in $F(Z_2)$.}
-\end{enumerate}
-Thus we have a symmetric monoidal double category $\lOpen(\Petri)$ of open Petri nets obtained from structured cospans and a symmetric monoidal double category $F\lCsp$ of open Petri nets obtain from decorated cospans, and of course, we have an equivalence $\lOpen(\Petri) \simeq F\lCsp$ of symmetric monoidal double categories by \cref{thm:equiv}.
-
-%%%DISCUSS OPEN COMMUTATIVE MONOIDAL CATEGORIES!!!
+
+We can equivalently describe open Petri nets using decorated cospans.
+This works very much like the previous examples.
+There is a symmetric lax monoidal pseudofunctor $F \maps (\Fin\Set, +) \to (\Cat, \times)$ such that for any finite set $S$, the category $F(S)$ has:
+\begin{itemize}
+\item objects given by Petri nets whose set of places is $S$,
+\item morphisms given by morphisms of Petri nets that are the identity on the set of places.
+\end{itemize}
+This gives a symmetric monoidal double category $F \lCsp$, and using \cref{thm:equiv} we can show that this is equivalent, as a symmetric monoidal double category, to ${}_L \lCsp(\Petri)$.
+
+The machinery of structured cospans has been used to provide a semantics for open Petri nets \cite{BM}: a symmetric monoidal double functor from ${}_L \lCsp(\Petri)$ to  a symmetric monoidal double category of `open commutative monoidal categories'.
+Presumably this double functor can equivalently be obtained using the machinery of decorated cospans, with the help of \cref{thm:functoriality}.
+However, it should be clear by now that in cases where either structured or decorated cospans can be used, structured cospans are simpler.
+We next turn to an example where decorated cospans are necessary.
 
@@
 For example, a pseudomonoid in $\Cat$ is a monoidal category.
-We can also define braided and symmetric pseudomonoids, which in $\Cat$ are braided and symmetric monoidal categories.
+We can also define symmetric pseudomonoids, which in $\Cat$ are symmetric monoidal categories.
 

### 2020-12-02 cospans.tex
worked on Section 5.4: open Petri nets with rates

@@
 \item vertical 1-morphisms are functions,
-\item horizontal 1-cells as \define{open Petri nets}, which are cospans in $\Petri$ of the form:
+\item horizontal 1-cells are \define{open Petri nets}, which are cospans in $\Petri$ of the form:
 \[
@@
 \]
-\item 2-morphisms are maps of cospans in $\Petri$ of the form:
+\item 2-morphisms are diagrams in $\Petri$ of the form:
 \[
@@
 
-\subsection{Reaction networks}
-
-%%% Do reaction networks and dynamical systems (which do NOT come from structured cospans).
-A dynamical system is a vector field from the perspective of a system of first-order ordinary differential equations.
-Chemical reaction networks are a specific kind of dynamical system in which the vector field is algebraic, meaning that its coefficients are polynomials.
-Using Fong's original incarnation of decorated cospans, Pollard and the first author \cite{BP} constructed a symmetric monoidal category $\mathsf{OpenDynam}$ for which the morphisms are open dynamical systems.
-This category $\mathsf{OpenDynam}$ has:
+\subsection{Petri nets with rates}
+
+Chemists sometimes use Petri nets where the places represent `chemical species'---types of molecules, ions and the like---and the transitions represent chemical reactions.
+In these Petri nets, which we shall call `Petri nets with rates', the transitions are labelled with positive real numbers called `rate constants'.
+This allows one to systematically construct a dynamical system from any Petri net with rates, and mathematical chemists have proved deep theorems relating the topology of Petri nets with rates to the qualitative behavior of their dynamical systems.
+Pollard and the first author showed how to construct an `open' dynamical system from an `open' Petri net with rates---meaning one where chemicals can flow in and out at certain places \cite{BP}.
+We used the formalism of decorated cospans to do this, and to define a functor from a category with open Petri nets with rates as morphisms to one with open dynamical systems as morphisms.
+Later, the first two authors used structured cospans to promote the first of these categories to a double category \cite[Sec.\ 6.16]{BC}.
+Here we show the second, the category with open dynamical systems as morphism, \emph{cannot} be made into a double category using structured cospans---but we can do it using decorated cospans.
+
+A \define{Petri net with rates} is a Petri net $s,t \maps T \to \N[S]$ together with a function $r \maps T \to (0,\infty)$ assigning to each transition $\tau \in T$ a positive real number called its \define{rate constant}.
+There is a category $\Petri_r$ whose objects are Petri nets with rates, where a morphism from
+\[   \xymatrix{ (0,\infty) & T \ar[l]_-r \ar@<-.5ex>[r]_-t \ar@<.5ex>[r]^-s & \N[S] }\]
+ to 
+ \[   \xymatrix{ (0,\infty) & T' \ar[l]_-r \ar@<-.5ex>[r]_-t \ar@<.5ex>[r]^-s & \N[S'] }\]
+is a morphism of the underlying Petri nets such that the following diagram also commutes:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (E) at (3,-0.5) {$(0,\infty)$};
+\node (G) at (4,0) {$T$};
+\node (G') at (4,-1) {$T'$};
+\path[->,font=\scriptsize,>=angle 90]
+(G) edge node[right]{$f$} (G')
+(G) edge node[above]{$r$} (E)
+(G') edge node[below]{$r'$} (E);
+\end{tikzpicture}
+\]
+There is a functor $R \maps \Petri_r \to \Set$ sending any Petri net with rates to its set of places, and this has a left adjoint $L \maps \Set \to \Petri_r$ sending any set $S$ to the Petri net with $S$ as its set of species and no transitions \cite[Lemma 6.18]{BC}.
+Since $\Petri_r$ has finite colimits \cite[Lemma 6.19]{BC}, it follows that there is a symmetric monoidal double category ${}_L \lCsp(\Petri_r)$ where:
 \begin{itemize}
-\item{objects as finite sets, and}
-\item{morphisms as equivalence classes of cospans of finite sets whose apices are equipped with an algebraic vector field.
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (D) at (-3,0) {$a$};
-\node (E) at (-2,0) {$s$};
-\node (F) at (-1,0) {$b$};
-\node (A) at (0,0) {$v_s \colon \lR^s \to \lR^s$};
+\item objects are finite sets,
+\item vertical 1-morphisms are functions,
+\item horizontal 1-cells are \define{open Petri nets with rates}:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (D) at (-3,0) {$L(X)$};
+\node (E) at (-2,0) {$P$};
+\node (F) at (-1,0) {$L(Y)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-}
+\item 2-morphisms are diagrams in $\Petri_r$ of the form:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (E) at (3,0) {$L(X_1)$};
+\node (F) at (5,0) {$L(Y_1)$};
+\node (G) at (4,0) {$P_1$};
+\node (E') at (3,-1) {$L(X_2)$};
+\node (F') at (5,-1) {$L(Y_2)$.};
+\node (G') at (4,-1) {$P_2$};
+\path[->,font=\scriptsize,>=angle 90]
+(F) edge node[above]{$O_1$} (G)
+(E) edge node[left]{$L(f)$} (E')
+(F) edge node[right]{$L(g)$} (F')
+(G) edge node[left]{$\alpha$} (G')
+(E) edge node[above]{$I_1$} (G)
+(E') edge node[above]{$I_2$} (G')
+(F') edge node[above]{$O_2$} (G');
+\end{tikzpicture}
+\]
 \end{itemize}
-This category is constructed from a symmetric lax monoidal functor $F \colon \Fin\Set \to \Set$ that assigns to a finite set $s$ the set $F(s)$ of algebraic vector fields on $s$ and a to function $f \colon s \to s'$ the function $F(f) \colon F(s) \to F(s')$ defined by $$F(f)(v_s)=f_* v_s f^*$$
-where $f^\ast \colon \mathbb{R}^{s'} \to \mathbb{R}^{s}$ is the \define{pullback} defined by 
-$$f^\ast (c_{s'})(\sigma)=c_{s}(f(\sigma))$$ 
-and $f_{\ast} \colon \mathbb{R}^s \to \mathbb{R}^{s'}$ is the \define{pushforward} defined by 
-$$f_{\ast}(c_{s'})(\sigma^\prime) = \sum_{\{\sigma \in s : \; f(\sigma) = \sigma^\prime\}} c_{s}(\sigma)$$
-for $c_{s} \in \mathbb{R}^{s}$ and $c_{s'} \in \mathbb{R}^{s'}$
-Functoriality of $F$ comes the pushforward being covariant and the pullback being contravariant, and the lax monoidal structure of $F$ stems from the canonical isomorphism $\lR^s \times \lR^{s'} \cong \lR^{s+s'}$ which is used to map a pair of vector fields $v_s \colon \lR^s \to \lR^{s}$ and $v_{s'} \colon \lR^{s'} \to \lR^{s'}$ to the vector field $v_{s+s'} \colon \lR^{s+s'} \to \lR^{s+s'}$.
+
+We can equivalently describe open Petri nets with rates using decorated cospans.
+There is a symmetric lax monoidal pseudofunctor $F \maps (\Fin\Set, +) \to (\Cat, \times)$ such that for any finite set $S$, the category $F(S)$ has:
+\begin{itemize}
+\item objects given by Petri nets with rates whose set of places is $S$,
+\item morphisms given by morphisms of Petri nets with rates that are the identity on the set of places.
+\end{itemize}
+This gives a symmetric monoidal double category $F \lCsp$, and using \cref{thm:equiv} we can show that this is equivalent, as a symmetric monoidal double category, to ${}_L \lCsp(\Petri_r)$.
+
+All this so far is boringly familiar.  More interesting is the symmetric monoidal double
+category of open dynamical systems.
+A dynamical system is a vector field from the perspective of a system of first-order ordinary differential equation.
+An Petri net with rates gives a special sort of dynamical system: an \define{algebraic} vector field on $\R^n$, meaning one where the components of the vector field are polynomials in the coordinates.
+We shall think of such a vector field as a special sort of function $v \maps \R^n \to \R^n$.
+
+Using Fong's original approach to decorated cospans, Pollard and the first author constructed a symmetric monoidal category for which the morphisms are open dynamical systems \cite[Theorem 17]{BP}.
+This category is constructed from a symmetric lax monoidal functor
+$D \maps \Fin\Set \to \Set$ such that:
+\begin{itemize}
+\item $D$ maps any finite set $S$ to 
+\[ D(S) = \{ v \maps \R^S \to \R^S : \; v \textrm{ is algebraic}  \}. \] 
+\item $D$ maps any function $f \maps S \to S'$ between finite sets to the function $D(f) \maps D(S) \to D(S')$ given as follows:
+\[ D(f)(v) = f_* \circ v \circ f^* \]
+where the pullback $ f^* \maps \R^{S'} \to \R^S $ is given by
+\[ f^*(c)(\sigma) = c(f(\sigma)) \] 
+while the pushforward $ f_* \maps \R^{S} \to \R^{S'} $ is given by
+\[ f_*(c)(\sigma') = \sum_{ \{ \sigma \in S : f(\sigma) = \sigma' \} } c(\sigma). \]
+\end{itemize}
+The functorality of $D$ is proved in \cite[Lemma 15]{BP} while the lax symmetric monoidal stucture is given in Lemma 16.
+
+Since every set gives a discrete category with that set of objects, we can reinterpret $D$ as a lax monoidal pseudofunctor $D \maps (\Fin\Set, +) \to (\Cat, \times)$.
+Applying \cref{DC} we obtain a symmetric monoidal double category $D \lCsp$ where:
+\begin{itemize}
+\item objects are finite sets,
+\item vertical 1-morphisms are functions,
+\item horizontal 1-cells are \define{open dynamical systems}:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (D) at (-3,0) {$X$};
+\node (E) at (-2,0) {$S$};
+\node (F) at (-1,0) {$Y$};
+\path[->,font=\scriptsize,>=angle 90]
+(D) edge node [above] {$i$} (E)
+(F) edge node [above] {$o$} (E);
+\end{tikzpicture}, \qquad v \in D(S) 
+\]
+\item 2-morphisms are....
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (E) at (3,0) {$L(X_1)$};
+\node (F) at (5,0) {$L(Y_1)$};
+\node (G) at (4,0) {$P_1$};
+\node (E') at (3,-1) {$L(X_2)$};
+\node (F') at (5,-1) {$L(Y_2)$.};
+\node (G') at (4,-1) {$P_2$};
+\path[->,font=\scriptsize,>=angle 90]
+(F) edge node[above]{$O_1$} (G)
+(E) edge node[left]{$L(f)$} (E')
+(F) edge node[right]{$L(g)$} (F')
+(G) edge node[left]{$\alpha$} (G')
+(E) edge node[above]{$I_1$} (G)
+(E') edge node[above]{$I_2$} (G')
+(F') edge node[above]{$O_2$} (G');
+\end{tikzpicture}
+\]
+\end{itemize}
+
 We now show that open dynamical systems of this nature are an example of open systems that are able to be characterized by decorated cospans but not structured cospans.

### 2020-12-02 cospans.tex
small changes in Section 5.4

@@
 This allows one to systematically construct a dynamical system from any Petri net with rates, and mathematical chemists have proved deep theorems relating the topology of Petri nets with rates to the qualitative behavior of their dynamical systems.
-Pollard and the first author showed how to construct an `open' dynamical system from an `open' Petri net with rates---meaning one where chemicals can flow in and out at certain places \cite{BP}.
-We used the formalism of decorated cospans to do this, and to define a functor from a category with open Petri nets with rates as morphisms to one with open dynamical systems as morphisms.
-Later, the first two authors used structured cospans to promote the first of these categories to a double category \cite[Sec.\ 6.16]{BC}.
-Here we show the second, the category with open dynamical systems as morphism, \emph{cannot} be made into a double category using structured cospans---but we can do it using decorated cospans.
+Pollard and the first author showed how to construct an `open' dynamical system from an `open' Petri net with rates, meaning one where chemicals can flow in and out at certain places \cite{BP}.
+They used the formalism of decorated cospans to do this, and to define a functor from a category with open Petri nets with rates as morphisms to one with `open dynamical systems' as morphisms.
+Later, structured cospans were used to promote the first of these categories to a double category \cite[Sec.\ 6.16]{BC}.
+Here we show the second, the category with open dynamical systems as morphisms, \emph{cannot} be made into a double category using structured cospans---but we can do it using decorated cospans!
 

### 2020-12-02 cospans.tex
More work on Applications section... almost done!

@@
 This allows one to systematically construct a dynamical system from any Petri net with rates, and mathematical chemists have proved deep theorems relating the topology of Petri nets with rates to the qualitative behavior of their dynamical systems.
-Pollard and the first author showed how to construct an `open' dynamical system from an `open' Petri net with rates, meaning one where chemicals can flow in and out at certain places \cite{BP}.
-They used the formalism of decorated cospans to do this, and to define a functor from a category with open Petri nets with rates as morphisms to one with `open dynamical systems' as morphisms.
+
+Pollard and the first author showed how to construct an `open dynamical system' from an `open' Petri net with rates, meaning one where chemicals can flow in and out at certain places \cite{BP}.
+They used the formalism of decorated cospans to do this, and to define a functor from a category with open Petri nets with rates as morphisms to one with open dynamical systems as morphisms.
 Later, structured cospans were used to promote the first of these categories to a double category \cite[Sec.\ 6.16]{BC}.
-Here we show the second, the category with open dynamical systems as morphisms, \emph{cannot} be made into a double category using structured cospans---but we can do it using decorated cospans!
+Here we show that the second, the category with open dynamical systems as morphisms, \emph{cannot} be made into a double category using structured cospans---but we \emph{can} do it using decorated cospans!
 
@@
 \item vertical 1-morphisms are functions,
-\item horizontal 1-cells are \define{open dynamical systems}:
+\item a horizontal 1-cell from $X$ to $Y$ is an \define{open dynamical system}, that is, a cospan
 \[
@@
 (F) edge node [above] {$o$} (E);
-\end{tikzpicture}, \qquad v \in D(S) 
-\]
-\item 2-morphisms are....
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (E) at (3,0) {$L(X_1)$};
-\node (F) at (5,0) {$L(Y_1)$};
-\node (G) at (4,0) {$P_1$};
-\node (E') at (3,-1) {$L(X_2)$};
-\node (F') at (5,-1) {$L(Y_2)$.};
-\node (G') at (4,-1) {$P_2$};
-\path[->,font=\scriptsize,>=angle 90]
-(F) edge node[above]{$O_1$} (G)
-(E) edge node[left]{$L(f)$} (E')
-(F) edge node[right]{$L(g)$} (F')
-(G) edge node[left]{$\alpha$} (G')
-(E) edge node[above]{$I_1$} (G)
-(E') edge node[above]{$I_2$} (G')
-(F') edge node[above]{$O_2$} (G');
-\end{tikzpicture}
-\]
+\end{tikzpicture}
+\]
+in $\Fin\Set$ together with an algebraic vector field $v \in D(S)$,
+\item a 2-morphism from
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (D) at (-3,0) {$X$};
+\node (E) at (-2,0) {$S$};
+\node (F) at (-1,0) {$Y,$};
+\node (G) at (0,0) {$v \in D(S)$};
+\path[->,font=\scriptsize,>=angle 90]
+(D) edge node [above] {$i$} (E)
+(F) edge node [above] {$o$} (E);
+\end{tikzpicture}
+\]
+to
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (D) at (-3,0) {$X'$};
+\node (E) at (-2,0) {$S'$};
+\node (F) at (-1,0) {$Y'$};
+\node (G) at (0,0) {$v' \in D(S')$};
+\path[->,font=\scriptsize,>=angle 90]
+(D) edge node [above] {$i'$} (E)
+(F) edge node [above] {$o'$} (E);
+\end{tikzpicture}
+\]
+is a diagram
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (E) at (3,0) {$X$};
+\node (F) at (5,0) {$Y$};
+\node (G) at (4,0) {$S$};
+\node (E') at (3,-1) {$X'$};
+\node (F') at (5,-1) {$Y'$};
+\node (G') at (4,-1) {$S'$};
+\path[->,font=\scriptsize,>=angle 90]
+(F) edge node[above]{$o$} (G)
+(E) edge node[left]{$f$} (E')
+(F) edge node[right]{$g$} (F')
+(G) edge node[left]{$h$} (G')
+(E) edge node[above]{$i$} (G)
+(E') edge node[above]{$i'$} (G')
+(F') edge node[above]{$o'$} (G');
+\end{tikzpicture}
+\]
+in $\Fin\Set$ such that $D(h)(v) = v'$.
 \end{itemize}
+
+{\chris The rest is not done yet...}
 

### 2020-12-02 cospans.tex
working through 2.2

@@
 \item of two vertical 1-morphisms $f \maps a \to b$ and $f' \maps a' \to b'$ is $f+f' \maps a+a' \to b+b'$ in $\A$,
-\item of two horizontal 1-cells $(a_1\to m_1\leftarrow b_1,x_1\in F(m_1))$ and $(a_2\to m_2\leftarrow b_2,x_2\in F(m_2))$ is 
+\item of two horizontal 1-cells $(a_1\to m_1\leftarrow b_1,x_1\in F(m_1))$ and $(a_2\to m_2\leftarrow b_2,x_2\in F(m_2))$ is:
 \begin{equation}\label{eq:tensordecoration}
@@
  \begin{tikzcd}[column sep=.5in, row sep=.1in]
-& F(m)\times F(n)\ar[r,"\phi_{m,n}"]\ar[dd,"F(h)\times F(h')"description]\ar[ddr,phantom,"\cong"] & F(m+n)\ar[dd,"F(h+h')"] \\
+& F(m)\times F(n)\ar[r,"\phi_{m,n}"]\ar[dd,"F(h)\times F(h')"description]\ar[ddr,phantom,"\stackrel{\cref{eq:pseudonaturality}}{\cong}"] & F(m+n)\ar[dd,"F(h+h')"] \\
 1\ar[ur,"x\times y"]\ar[dr,"x'\times y'"']\ar[r,phantom,"\scriptstyle\Downarrow\tau_\alpha\times\tau_\beta"] & \phantom{A} && \\
@@
 \begin{displaymath}
-0\xrightarrow{!}0\xleftarrow{!}0,\quad 1\xrightarrow{\phi_0}F(0)
+I_1=\left(0\xrightarrow{!}0\xleftarrow{!}0, 1\xrightarrow{\phi_0}F(0)\right)
 \end{displaymath}
-where $0$ is the initial object in $\A$. Notice that this unit is $U_0$ as required. The associator of $F\lCsp_1$ is formed as follows: for three objects
+where $0$ is the initial object in $\A$. Notice that this unit $I_1$ is (isomorphic to) $U_0$ as required. The associator is formed as follows: for three objects
 $M_1=(a_1\to m_1\leftarrow b_1,x_1\in F(m_1))$, $M_2=(a_2\to m_2\leftarrow b_2,x_2\in F(m_2))$ and $M_3=(a_3\to m_3\leftarrow b_3,x_3\in F(m_3),$
@@
 %%% Christina: I earlier dropped notation x+y for decorations because + is already overused and I find it potentially misleading for the reader. I hope the new symbol is OK?
-together with the decoration isomorphism $F(\alpha)(\phi_{m_1{+}m_2,m_3}(\phi_{m_1,m_2}(x_1,x_2),x_3))\cong\phi_{m_1,m_2{+}m_3}(x_1,\phi_{m_2,m_3}(x_2,x_3))$ formed in the same way as the left two parts of \cref{eq:decoiso}.
+together with the decoration isomorphism between $F(\alpha)((x_1\oplus x_2)\oplus x_3)\stackrel{\cref{eq:tensordecoration}}{=}F(\alpha)(\phi_{m_1{+}m_2,m_3}(\phi_{m_1,m_2}(x_1,x_2),x_3))$ and $x_1\oplus(x_2\oplus x_3)=\phi_{m_1,m_2{+}m_3}(x_1,\phi_{m_2,m_3}(x_2,x_3))$ formed in the same way as the left two-piece part of \cref{eq:decoiso}.
 \begin{comment}
@@
 \end{comment}
-
-{\chris In progress}
-
+For the left and right unitors $I_1\ot M\cong M\cong M\ot I_1$ for any $M=(a\to m\leftarrow b,x\in F(m)$, we have span isomorphisms
+\begin{displaymath}
+ \begin{tikzcd}[column sep=.3in]
+0+a\ar[rr,"1+i"]\ar[d,"\stackrel{\ell}{\cong}"'] && 0+m\ar[d,"\stackrel{\ell}{\cong}"'] && 0+b\ar[ll,"1+o"']\ar[d,"\stackrel{\ell}{\cong}"] &&1\ar[r,"\phi_0\times x"] & F(0)\times F(m)\ar[r,"\phi_{0,m}"] & F(0+m) \\
+a\ar[rr,"i"] && m && b\ar[ll,"o"'] && 1\ar[r,"x"] & F(m)\\
+a+0\ar[rr,"i+1"']\ar[u,"\stackrel{r}{\cong}"] && m+0\ar[u,"\stackrel{r}{\cong}"] && b+0\ar[ll,"o+1"]\ar[u,"\stackrel{r}{\cong}"']
+&&1\ar[r,"x\times\phi_0"] & F(m)\times F(0)\ar[r,"\phi_{m,0}"] & F(m+0)
+ \end{tikzcd}
+\end{displaymath}
+with isomorphisms between decorations precisely given by \cref{eq:unitality}.
+\begin{comment}
 For the left unitor, we first compute $0_{F\lCsp_1} \otimes M$:
@@
 See the second author's thesis \cite{CourserThesis} for more details.
-
-To finish showing that $F\lCsp_1$ is symmetric monoidal, we next define the braiding of $F\lCsp_1$.
+\end{comment}
+Finally, the symmetric monoidal structure of $F\lCsp_1$ is inherited from that in $\A$ and $F$, with braiding the cospan isomorphism
+%To finish showing that $F\lCsp_1$ is symmetric monoidal, we next define the braiding of $F\lCsp_1$.
 Given two objects $M_1$ and $M_2$ of $F\lCsp_1$ and denoting the braiding of $(\A,+,0)$ by $\beta$, the braiding $\beta_{M_1,M_2}$ of $F\lCsp_1$ is then a map of cospans in $\A$ from $M_1 \otimes M_2$ to $M_2 \otimes M_1$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$a_1+a_2$};
-\node (A') at (0,-0.5) {$a_2+a_1$};
-\node (B) at (2,0.5) {$m_1+m_2$};
-\node (C) at (4,0.5) {$b_1+b_2$};
-\node (C') at (4,-0.5) {$b_2+b_1$};
-\node (D) at (2,-0.5) {$m_2+m_1$};
-\node (E) at (5.5,0.5) {$x_1+x_2 \in F(m_1+m_2)$};
-\node (F) at (5.5,-0.5) {$x_2+x_1 \in F(m_2+m_1)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i_1+i_2$} (B)
-(C) edge node[above]{$o_1+o_2$} (B)
-(A) edge node[left]{$\beta$} (A')
-(C) edge node[left]{$\beta$} (C')
-(A') edge node [above]{$i_2+i_1$} (D)
-(C') edge node [above]{$o_2+o_1$} (D)
-(B) edge node [left] {$\beta$} (D);
-\end{tikzpicture}
-\]
-together with the decoration isomorphism $\tau_\beta \colon F(\beta)(x_1+x_2) \to x_2+x_1$.
+%\[
+%\begin{tikzpicture}[scale=1.5]
+%\node (A) at (0,0.5) {$a_1+a_2$};
+%\node (A') at (0,-0.5) {$a_2+a_1$};
+%\node (B) at (2,0.5) {$m_1+m_2$};
+%\node (C) at (4,0.5) {$b_1+b_2$};
+%\node (C') at (4,-0.5) {$b_2+b_1$};
+%\node (D) at (2,-0.5) {$m_2+m_1$};
+%\node (E) at (6,0.5) {$x_1\oplus x_2 \in F(m_1+m_2)$};
+%\node (F) at (6,-0.5) {$x_2\oplus x_1 \in F(m_2+m_1)$};
+%\path[->,font=\scriptsize,>=angle 90]
+%(A) edge node[above]{$i_1+i_2$} (B)
+%(C) edge node[above]{$o_1+o_2$} (B)
+%(A) edge node[left]{$\stackrel{\beta}{\cong}$} (A')
+%(C) edge node[left]{$\stackrel{\beta}{\cong}$} (C')
+%(A') edge node [above]{$i_2+i_1$} (D)
+%(C') edge node [above]{$o_2+o_1$} (D)
+%(B) edge node [right] {$\stackrel{\beta}{\cong}$} (D);
+%\end{tikzpicture}
+%\]
+\begin{displaymath}
+ \begin{tikzcd}[column sep=.25in]
+a_1+a_2\ar[rr,"i_1+i_2"]\ar[d,"\stackrel{\beta}{\cong}"'] && m_1+m_2\ar[d,"\stackrel{\beta}{\cong}"'] && b_1+b_2\ar[ll,"o_1+o_2"']\ar[d,"\stackrel{\beta}{\cong}"] &&1\ar[r,"x_1\times x_2"] & F(m_1)\times F(m_2)\ar[r,"\phi_{m_1,m_2}"] & F(m_1+m_2) \\
+a_2+a_1\ar[rr,"i_2+i_1"'] && m_2+m_1 && b_2+b_1\ar[ll,"o_2+o_1"] &&1\ar[r,"x_2\times x_1"] & F(m_2)\times F(m_1)\ar[r,"\phi_{m_2,m_1}"] & F(m_2+m_1)
+ \end{tikzcd}
+\end{displaymath}
+together with the decoration isomorphism formed by \cref{eq:braidedpseudofun} of the symmetric monoidal pseudofunctor.
+%$F(\beta)(x_1+x_2) \to x_2+x_1$.
 Note that obtaining the decoration isomorphism $\tau_\beta$ makes use of $F$ being symmetric.
@@
 This completes the description of $F\lCsp_1$ as a symmetric monoidal category.
+All axioms for a symmetric monoidal category can be verified, see \cite[Theorem 4.1.3]{CourserThesis}, and it is easy to see that with these structures, the source and target functors $S,T\colon F\lCsp_1\to F\lCsp_0$ are symmetric strict monoidal.
 
@@
 \end{equation}
-\begin{displaymath}
+\begin{equation}\label{eq:unitality}
 \begin{tikzcd}[column sep=.3in,row sep=.3in]
-F a\ar[r,"\sim"]\ar[drr,sloped,"\sim"'] & F a\otimes I\ar[r,"1\otimes\mu_0"]\ar[dr,phantom,"\cong"] & F 
-a\otimes F I\ar[d,"\mu_{a,I}"] \\
+F a\ar[r,"\sim"]\ar[drr,sloped,"\sim"'] & F a\otimes I\ar[r,"1\otimes\phi_0"]\ar[dr,phantom,"\cong"] & F 
+a\otimes F I\ar[d,"\phi_{a,I}"] \\
 && F(a\ot I)
@@
 \begin{tikzcd}[column sep=.3in,row sep=.3in]
-F a\ar[r,"\sim"]\ar[drr,sloped,"\sim"'] & I\otimes F a \ar[r,"\mu_0\otimes1"]\ar[dr,phantom,"\cong"] & F 
-I\otimes F a\ar[d,"\mu_{I,a}"] \\
+F a\ar[r,"\sim"]\ar[drr,sloped,"\sim"'] & I\otimes F a \ar[r,"\phi_0\otimes1"]\ar[dr,phantom,"\cong"] & F 
+I\otimes F a\ar[d,"\phi_{I,a}"] \\
 && F(I\ot a)
 \end{tikzcd}
-\end{displaymath}
+\end{equation}
 subject to coherence conditions. In particular, pseudonaturality of the monoidal structure means that it comes with isomorphisms (natural in $f,g$)
-\begin{equation}
+\begin{equation}\label{eq:pseudonaturality}
 \begin{tikzcd}[column sep=.5in]
@@
 \end{equation}
-A \define{braided lax monoidal} pseudofunctor between braided monoidal bicategories comes with an appropriate invertible modification with components $F(\beta_{a,b})\circ \phi_{a,b}\cong\phi_{b,a}\circ \beta_{Fa,Fb}$; a \define{sylleptic lax monoidal} pseudofunctor satisfies one extra condition and a \define{symmetric lax monoidal} pseudofunctor between symmetric monoidal bicategories is just a sylleptic one.
+A \define{braided lax monoidal} pseudofunctor between braided monoidal bicategories comes with an appropriate invertible modification with components %$F(\beta_{a,b})\circ \phi_{a,b}\cong\phi_{b,a}\circ \beta_{Fa,Fb}$.
+\begin{equation}\label{eq:braidedpseudofun}
+ \begin{tikzcd}
+Fa\otimes Fb\ar[r,"\phi_{a,b}"]\ar[d,"\beta_{Fa,Fb}"']\ar[dr,phantom,"\scriptstyle\cong"] & F(a\ot b)\ar[d,"F(\beta_{a,b})"] \\
+Fb\otimes Fa\ar[r,"\phi_{b,a}"'] & F(b\ot a)
+ \end{tikzcd}
+\end{equation}
+A \define{sylleptic lax monoidal} pseudofunctor satisfies one extra condition and a \define{symmetric lax monoidal} pseudofunctor between symmetric monoidal bicategories is just a sylleptic one.
 
@@
 \begin{itemize}
-\item monoidal structures on both $\lD_0$ and $\lD_1$, each with tensor product denoted $\otimes$, associator $a$, left unitor $\ell$ and right unitor $r$, such that if $I$ is the unit object of $\lD_0$ then $U_I$ is the unit of $\lD_1$, and such that the source and target functors $S,T \maps \lD_1 \to \lD_0$ are strict monoidal,
+\item monoidal structures on both $\lD_0$ and $\lD_1$, each with tensor product denoted $\otimes$, associator $a$, left unitor $\ell$ and right unitor $r$, such that if $I$ is the unit object of $\lD_0$ then $U_I$ is\footnote{\chris In reality, just isomorphic is OK!} the unit of $\lD_1$, and such that the source and target functors $S,T \maps \lD_1 \to \lD_0$ are strict monoidal,
 \item the structure of a double functor on $\otimes$:

### 2020-12-02 cospans.tex
finished with all structure for theorem 2.2

@@
 \begin{equation}\label{eq:dcospanscomposition}
-\begin{tikzpicture}
+\begin{tikzpicture}[scale=1.2,baseline=(current bounding box.center)]
 \node (A) at (0,0) {$a$};
@@
 (E) edge node [above] {$o'$} (D)
-(B) edge node [above] {$j_m$} (F)
-(D) edge node [above] {$j_{n}$} (F)
-(F) edge node [left] {$\psi$} (G)
+(B) edge node [below] {$j_m$} (F)
+(D) edge node [below] {$j_{n}$} (F)
+(B) edge[bend left=10] node [above] {$u_m\;$} (G)
+(D) edge[bend right=10] node [above] {$\;u_n$} (G)
+(F) edge node [fill=white] {$\psi$} (G)
 (A) edge[dashed,bend left] node [left] {} (G)
@@
 %$\alpha \colon \odot (\odot \times 1) \Rightarrow \odot (1 \times \odot)$ 
-is formed as follows: for three composable horizontal 1-cells $M_1=(a\to m_1\leftarrow b,x_1\in F(m_1))$, $M_2=(b\to m_2\leftarrow c,x_2\in F(m_2)$ and $M_3=(c\to m_3\leftarrow d,x_3\in F(m_3)),$
+is formed as follows: for three composable horizontal 1-cells $M_1=(a\to m_1\leftarrow b,x_1\in F(m_1))$, $M_2=(b\to m_2\leftarrow c,x_2\in F(m_2))$ and $M_3=(c\to m_3\leftarrow d,x_3\in F(m_3)),$
 %\[
@@
 
-Lastly, we require two globular 2-morphisms $\chi \colon (M_1 \otimes N_1) \odot (M_2 \otimes N_2) \to (M_1 \odot M_2) \otimes (N_1 \odot N_2)$ and $\mu \colon U_{a \otimes b} \to U_a \otimes U_b$, the first of which relates the double functor $\otimes$ with the functor $\odot$ and the second of which relates the double functor $\otimes$ with the functor $U$.
+Lastly, according to \cref{defn:monoidal_double_category} we construct two globular 2-isomorphisms $(M_2 \otimes N_2)\odot (M_1 \otimes N_1) \simrightarrow(M_2\odot M_1) \otimes (N_2\odot N_1)$ and $U_{a + b} \simrightarrow U_a \otimes U_b$ that express compatibility of the tensor with horizontal composition and units.
+For any appropriate four decorated cospans
+\begin{gather*}
+M_1=\left(a\xrightarrow{i_1}m_1\xleftarrow{o_1}b,x_1\in F(m_1)\right),\;\; M_2=\left(b\xrightarrow{i_2}m_2\xleftarrow{o_2}c,x_2\in F(m_2)\right) \\
+N_1=\left(a'\xrightarrow{i'_1}n_1\xleftarrow{o'_1}b',y_1\in F(n_1)\right),\;\; N_2=\left(b'\xrightarrow{i'_2}n_2\xleftarrow{o'_2}c',y_2\in F(n_2)\right)
+\end{gather*}
+first tensoring $M_1\ot N_1$, $M_2\ot N_2$ by \cref{eq:tensordecoration} and then horizontally composing them by \cref{eq:dcospanscomposition} gives
+\begin{displaymath}
+\scalebox{.8}{\begin{tikzcd}[column sep={.6in,between origins},ampersand replacement=\&]
+\&\& (m_1+n_1)+_{b{+}b'}(m_2+n_2) \&\& \\
+\& m_1+n_1\ar[ur] \&\& m_2+n_2\ar[ul] \& \\
+a+a'\ar[ur,"{i_1+i'_1}"] \&\& b+b'\ar[ul,"{o_1+o'_1}"']\ar[ur,"{i_2+i'_2}"] \&\& c+c'\ar[ul,"{o_2+o'_2}"']
+\end{tikzcd}}
+\scalebox{.8}{\begin{tikzcd}[ampersand replacement=\&,column sep=.5in]
+1\ar[ddrr,dashed,"{(x_1\oplus y_1)\odot(x_2\oplus y_2)}"']\ar[r,"x_1{\times}y_1{\times}x_2{\times}y_2"] \& F(m_1){\times}F(n_1){\times}F(m_2){\times}F(n_2)\ar[r,"\phi_{m_1,n_1}\times\phi_{m_2,n_2}"] \& F(m_1{+}n_1){\times}F(m_2{+}n_2) \ar[d,"\phi_{m_1+n_1,m_2+n_2}"] \\
+\&\& F(m_1+n_1+m_2+n_2)\ar[d,"F\psi"] \\
+\&\& F((m_1+n_1)+_{b+b'}(m_2+n_2))
+\end{tikzcd}}
+\end{displaymath}
+If we first horizontally compose $M_2\odot M_1$, $N_2\odot N_1$ and then tensor the result, we obtain
+\begin{displaymath}
+  \scalebox{.8}{\begin{tikzcd}[column sep=.3in,ampersand replacement=\&]
+ \& (m_1+_b m_2)+(n_1+_{b'}n_2) \& \\
+ \hole \\
+ a+a'\ar[uur]%,"{u_{m_1}i_1+u_{n_1}i'_1}"] 
+ \&\& c+c'\ar[uul]%,"{u_{m_2}o_2+u_{n_2}o'_2}"']  
+ \end{tikzcd}}
+ \scalebox{.8}{\begin{tikzcd}[ampersand replacement=\&,column sep=.4in]
+1\ar[ddrr,dashed,"{(x_1\odot x_2)\oplus(y_1\odot y_2)}"']\ar[r,"x_1{\times}x_2{\times}y_1{\times}y_2"] \& F(m_1){\times}F(m_2){\times}F(n_1){\times}F(n_2)\ar[r,"\phi_{m_1,m_2}\times\phi_{n_1,n_2}"] \& F(m_1{+}m_2){\times}F(n_1{+}n_2) \ar[d, "F\psi\times F\psi"] \\
+\&\& F(m_1+_bm_2)\times F(n_1+_{b'}n_2)\ar[d,"\phi_{m_1+_bm_2,n_1+_{b'}n_2}"] \\
+\&\& F((m_1+_bm_2)+F(n_1+_{b'}n_2))
+\end{tikzcd}}
+\end{displaymath}
+where the legs of the cospan are the sums of the dashed ones of the appropriate diagrams \cref{eq:dcospanscomposition}.
+Thus the (globular) cospan isomorphism is the canonical universal map between the colimit of the same diagram obtained in two different ways $(m_1+n_1)+_{b+b'}(m_2+n_2)\cong(m_1+_b m_2)+(n_1+_{b'}n_2)$, and the decoration isomorphism can be built in a similar way using coherent isomorphisms essentially due to pseudonaturality of $\phi$.
+{\chris Should we give more details here?}
+Similarly, for units $U_{a+b}$ and $U_a\ot U_b$ it is easy to see that as cospans they are both the identity $\id:a+b\to a+b\leftarrow a+b:\id$, and there is a canonical isomorphism between their trivial decorations \cref{eq:UFCsp}, namely $F(!_{a+b})\phi_0\cong\phi_{a,b}(F(!_a)\times F(!_b))(\phi_0\times\phi_0)$ via the structure isomorphisms for $(\phi,\phi_0)$.
+
+\begin{comment}
+, the first of which relates the double functor $\otimes$ with the functor $\odot$ and the second of which relates the double functor $\otimes$ with the functor $U$. 
 The latter of these is easy to see: given two objects $a$ and $b$ in $F\lCsp_0=\A$, $\mu$ is given by the identity map of cospans in $\A$:
@@
 together with the decoration isomorphism $\tau_{a,b} \maps \bot_{a+b} \xrightarrow{\sim} \bot_a + \bot_b$ given by the unique map between the two initial objects $\bot_{a+b}$ and $\bot_a + \bot_b$ in $F(a+b)$.
+%%%Christina: we do not have any such information at this point!
+We have not talked about the categories F(a) being cocomplete, and it's not deduced from the assumptions.
+We will show this is the case much later!
 For the former globular 2-morphism $\chi$, we first introduce some notation for objects $M_1,M_2,N_1$ and $N_2$ of $F\lCsp_1$:
@@
 This completes the description of the globular 2-morphisms $\chi$ and $\mu$, and the description of all of the structure of the symmetric monoidal double category $F\lCsp$.
+\end{comment}
+
+{\chris IN progress}
 
@@
 \end{equation}
-which is the pushout $\sigma_a\colon a\to a+_bc\leftarrow c:\sigma_c$ in $\A$ on the first variable, and $w$ is the pushout in the fibre $F(a+_bc)$
+which is the pushout $u_a\colon a\to a+_bc\leftarrow c:u_c$ in $\A$ on the first variable, and $w$ is the pushout in the fibre $F(a+_bc)$
 \begin{displaymath}
@@
  & w \ar[dd,phantom, very near start,"\upback"description] & \\
- F(\sigma_a)x\ar[ur] & & F(\sigma_c)z\ar[ul] \\
- & F(\sigma_a)(Ff(y))\cong F(\sigma_c)(Fg(y))\ar[ul,"F(\sigma_a)k"]\ar[ur,"F(\sigma_c)\ell"'] &
+ F(u_a)x\ar[ur] & & F(u_c)z\ar[ul] \\
+ & F(u_a)(Ff(y))\cong F(u_c)(Fg(y))\ar[ul,"F(u_a)k"]\ar[ur,"F(u_c)\ell"'] &
  \end{tikzcd}
@@
  \begin{tikzcd}[column sep={.7in,between origins}]
- && (m+_b n,F(\sigma_m)x+_{(\bot_{m+_bn})}F(\sigma_n)y) && \\
+ && (m+_b n,F(u_m)x+_{(\bot_{m+_bn})}F(u_n)y) && \\
  & (m,x) \ar[ur] && (n,y)\ar[ul] \\
@@
 \end{displaymath}
-where $\sigma$ are the canonical maps into the pushout. %overusing notation, streamline with earlier
-Under $\lE$ this is mapped to the underlying $\A$-cospan $\cspn{a}{m+_bn}{b}{}{}$ with decoration $F(\sigma_m)x+F(\sigma_n)y$, since a pushout over an initial object is really a coproduct.
+where $u$ are the canonical maps into the pushout.
+Under $\lE$ this is mapped to the underlying $\A$-cospan $\cspn{a}{m+_bn}{b}{}{}$ with decoration $F(u_m)x+F(u_n)y$, since a pushout over an initial object is really a coproduct.
 That decoration is isomorphic to that of \cref{eq:1} due to the following diagram
@@
  \begin{tikzcd}
-F(m)\times F(n)\ar[rr,"\phi"]\ar[d,"F(\sigma_m)\times F(\sigma_n)"']\ar[dr,phantom,"\cong"] && F(m+n)\ar[d,"F(\psi)"]\ar[d,bend right=50, phantom,"\cong"']\ar[dl,"F(\sigma_m+\sigma_n)"description] \\
+F(m)\times F(n)\ar[rr,"\phi"]\ar[d,"F(u_m)\times F(u_n)"']\ar[dr,phantom,"\cong"] && F(m+n)\ar[d,"F(\psi)"]\ar[d,bend right=50, phantom,"\cong"']\ar[dl,"F(u_m+u_n)"description] \\
 F(m+_bn)\times F(m+_bn)\ar[r,"\phi"'] & F\left((m+_bn)+(m+_bn)\right)\ar[r,"F(\nabla)"'] & F(m+_bn)
@@
 
-{\chris The rest is not done yet...}
+%{\chris The rest is not done yet...} %%%Christina I have no clue where this comment came from!
 

### 2020-12-02 cospans.tex
finished with 2.2

@@
 This completes the description of $F\lCsp_1$ as a symmetric monoidal category.
-All axioms for a symmetric monoidal category can be verified, see \cite[Theorem 4.1.3]{CourserThesis}, and it is easy to see that with these structures, the source and target functors $S,T\colon F\lCsp_1\to F\lCsp_0$ are symmetric strict monoidal.
+All axioms for a symmetric monoidal category can be verified, %see \cite[Theorem 4.1.3]{CourserThesis}, 
+and it is easy to see that with these structures, the source and target functors $S,T\colon F\lCsp_1\to F\lCsp_0$ are symmetric strict monoidal.
 
@@
 Similarly, for units $U_{a+b}$ and $U_a\ot U_b$ it is easy to see that as cospans they are both the identity $\id:a+b\to a+b\leftarrow a+b:\id$, and there is a canonical isomorphism between their trivial decorations \cref{eq:UFCsp}, namely $F(!_{a+b})\phi_0\cong\phi_{a,b}(F(!_a)\times F(!_b))(\phi_0\times\phi_0)$ via the structure isomorphisms for $(\phi,\phi_0)$.
-
 \begin{comment}
@@
 
-{\chris IN progress}
-
-The remaining properties are coherence laws that make use of these maps $\chi$ and $\mu$, the previously defined symmetric monoidal structure maps $\alpha,\lambda,\rho$ and $\beta$ and the double category structure functors $U$ and $\odot$.
+It can be verified with this structure, $F\lCsp$ is indeed a symmetric monoidal double category, namely all coherence laws are satisfied.
+The details can be found in \cite[Theorem 4.1.3]{CourserThesis}, but in order to give the reader a sense of what these checks entail, we provide an explicit proof of the fact that the braiding is a transformation of double categories, i.e.
+establish the commutativity of the left-hand side diagram \cref{eq:braidingaxiom}, in \cref{eq:proofofaxiom} so as to not interrupt the main narrative.
+
+%The remaining properties are coherence laws that make use of these maps $\chi$ and $\mu$, the previously defined symmetric monoidal structure maps $\alpha,\lambda,\rho$ and $\beta$ and the double category structure functors $U$ and $\odot$.
 We exhibit one of these laws to give the reader a sense of how they are verified, with more details available in the second author's thesis \cite{CourserThesis}.
-The coherence law that we check says that this diagram commutes:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$(M_1 \odot M_2) \otimes (N_1 \odot N_2)$};
-\node (B) at (3,0) {$(N_1 \odot N_2) \otimes (M_1 \odot M_2)$};
-\node (C) at (0,-.75) {$(M_1 \otimes N_1) \odot (M_2 \otimes N_2)$};
-\node (D) at (3,-.75) {$(N_1 \otimes M_1) \odot (N_2 \otimes M_2)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$\beta$} (B)
-(B) edge node[right]{$\chi$} (D)
-(A) edge node[left]{$\chi$} (C)
-(C) edge node[above]{$\beta \odot \beta$} (D);
-\end{tikzpicture}
-\]
-This diagram expresses that the braiding is a transformation of double categories.
-We show that this diagram commutes in two stages.
-First, for the underlying maps of cospans in $\A$.
-Using the notation previously introduced for the globular 2-morphism $\hat{\chi}$, the above diagram, modulo all of the decorations, is given by the following `flattened' commutative diagram in the symmetric monoidal double category $\lCsp(\A)$, where the top and the bottom cospans coincide.
-\[
-		\begin{tikzpicture}
-			\node (a) at (-4,0) {$a+a'$};
-			\node (b) at (1,0) {$(m_1+_b m_2) + (n_1+_{b'} n_2)$};
-			\node (c) at (6,0) {$c+c'$};
-			\node (a2) at (-4,1) {$a'+a$};
-			\node (b2) at (1,1) {$(n_1 +_{b'} n_2) + (m_1 +_b m_2)$};
-			\node (c2) at (6,1) {$c'+c$};
-                                \node (a3) at (-4,2) {$a'+a$};
-			\node (b3) at (1,2) {$(n_1+m_1) +_{(b'+b)} (n_2+m_2)$};
-			\node (c3) at (6,2) {$c'+c$};
-                                \node (a5) at (-4,-1) {$a+a'$};
-			\node (b5) at (1,-1) {$(m_1+n_1) +_{(b+b')} (m_2+n_2)$};
-			\node (c5) at (6,-1) {$c+c'$};
-                                \node (a6) at (-4,-2) {$a'+a$};
-			\node (b6) at (1,-2) {$(n_1+m_1) +_{(b'+b)} (n_2+m_2)$};
-			\node (c6) at (6,-2) {$c'+c$};
-			\path[->,font=\scriptsize,>=angle 90]
-			(a) edge node[above]{$$} (b)
-			(c) edge node[above]{$$} (b)
-                                (a2) edge node[above]{$$} (b2)
-			(c2) edge node[above]{$$} (b2)
-                                (a) edge node[left]{$\beta$} (a2)
-                                (b) edge node[left]{$\beta$} (b2)
-%(b) edge node[right]{$\tau_1$} (b2)
-			(c) edge node[right]{$\beta$} (c2)
-                                (a3) edge node[above]{$$} (b3)
-			(c3) edge node[above]{$$} (b3)
-                                (a2) edge node[above]{$$} (a3)
-                                (b2) edge node[left]{$\hat{\chi}$} (b3)
-%(b2) edge node[right]{$\tau_2$} (b3)
-			(c2) edge node[above]{$$} (c3)
-                                (a5) edge node[above]{$$} (b5)
-			(c5) edge node[above]{$$} (b5)
-                                (a) edge node[above]{$$} (a5)
-                                (b) edge node[left]{$\hat{\chi}$} (b5)
-%(b) edge node[right]{$\tau_4$} (b5)
-			(c) edge node[above]{$$} (c5)
-                                (a6) edge node[above]{$$} (b6)
-			(c6) edge node[above]{$$} (b6)
-                                (a5) edge node[left]{$\beta$} (a6)
-                                (b5) edge node[left]{$\beta \odot \beta$} (b6)
- %(b5) edge node[right]{$\tau_5$} (b6)
-			(c5) edge node[left]{$\beta$} (c6);
-		\end{tikzpicture}
-	\]
-The unlabeled vertical 1-morphisms on the sides are identities, $\beta$ is the braiding of the symmetric monoidal category $\A$, the map $\hat{\chi}$ is the globular 2-morphism interchanging the tensor product and horizontal composition of the symmetric monoidal double category $\lCsp(\A)$, and the inwards pointing morphisms are natural maps from the each cospan's feet to its apex.
-
-For the decorations, each of the four maps of cospans constituting the above diagram has an associated decoration isomorphism with it, which we label with $\tau_i$ for $i=1,2,3,4$.
-\[
-		\begin{tikzpicture}
-%			\node (a) at (-4,0) {$a+a'$};
-			\node (b) at (1,0) {$(m_1+_b m_2) + (n_1+_{b'} n_2)$};
-			\node (c) at (8,0) {$(x_1 \odot x_2) + (y_1 \odot y_2) \in F((m_1+_b m_2)+(n_1+_{b'} n_2))$};
-%			\node (a2) at (-4,1) {$a'+a$};
-			\node (b2) at (1,1) {$(n_1 +_{b'} n_2) + (m_1 +_b m_2)$};
-			\node (c2) at (8,1) {$(y_1 \odot y_2) + (x_1 \odot x_2) \in F((n_1+_{b'} n_2)+(m_1+_b m_2))$};
-%                            \node (a3) at (-4,2) {$a'+a$};
-			\node (b3) at (1,2) {$(n_1+m_1) +_{(b'+b)} (n_2+m_2)$};
-			\node (c3) at (8,2) {$(y_1+x_1) \odot (y_2+x_2) \in F((n_1+m_1)+_{b'+b}(n_2+m_2))$};
-%                                \node (a5) at (-4,-1) {$a+a'$};
-			\node (b5) at (1,-1) {$(m_1+n_1) +_{(b+b')} (m_2+n_2)$};
-			\node (c5) at (8,-1) {$(x_1+y_1) \odot (x_2+y_2) \in F((m_1+n_1)+_{b+b'}(m_2+n_2))$};
-%                                \node (a6) at (-4,-2) {$a'+a$};
-			\node (b6) at (1,-2) {$(n_1+m_1) +_{(b'+b)} (n_2+m_2)$};
-			\node (c6) at (8,-2) {$(y_1+x_1) \odot (y_2+x_2) \in F((n_1+m_1)+_{b'+b}(n_2+m_2))$};
-			\path[->,font=\scriptsize,>=angle 90]
-%			(a) edge node[above]{$$} (b)
-%			(c) edge node[above]{$$} (b)
-%                                (a2) edge node[above]{$$} (b2)
-%			(c2) edge node[above]{$$} (b2)
-%                                (a) edge node[left]{$\beta$} (a2)
-                                (b) edge node[left]{$\beta$} (b2)
-(b) edge node[right]{$\tau_1$} (b2)
-%			(c) edge node[right]{$\beta$} (c2)
-%                                (a3) edge node[above]{$$} (b3)
-%			(c3) edge node[above]{$$} (b3)
-%                               (a2) edge node[above]{$$} (a3)
-                                (b2) edge node[left]{$\hat{\chi}$} (b3)
-(b2) edge node[right]{$\tau_2$} (b3)
-%			(c2) edge node[above]{$$} (c3)
-%                                (a5) edge node[above]{$$} (b5)
-%			(c5) edge node[above]{$$} (b5)
-%                                (a) edge node[above]{$$} (a5)
-                                (b) edge node[left]{$\hat{\chi}$} (b5)
-(b) edge node[right]{$\tau_3$} (b5)
-%			(c) edge node[above]{$$} (c5)
-%                               (a6) edge node[above]{$$} (b6)
-%			(c6) edge node[above]{$$} (b6)
-%                                (a5) edge node[left]{$\beta$} (a6)
-                                (b5) edge node[left]{$\beta \odot \beta$} (b6)
- (b5) edge node[right]{$\tau_4$} (b6);
-%			(c5) edge node[left]{$\beta$} (c6);
-		\end{tikzpicture}
-	\]
-Explicitly, the four decoration isomorphisms are given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$\tau_1 \colon F(\beta)((x_1 \odot x_2)+(y_1 \odot y_2)) \to (y_1 \odot y_2)+(x_1 \odot x_2)$};
-\node (B) at (0,-.5) {$\tau_2 \colon F(\hat{\chi})((y_1 \odot y_2)+(x_1 \odot x_2)) \to (y_1+x_1) \odot (y_2+x_2)$};
-\node (C) at (0,-1) {$\tau_3 \colon F(\hat{\chi})((x_1 \odot x_2)+(y_1 \odot y_2)) \to (x_1+y_1) \odot (x_2+y_2)$};
-\node (D) at (0,-1.5) {$\tau_4 \colon F(\beta \odot \beta)((x_1+y_1)\odot(x_2+y_2)) \to (y_1+x_1)\odot(y_2+x_2)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge[color=white] node[above]{$$} (A);
-%(B) edge node[right]{$\chi$} (D)
-%(A) edge node[left]{$\chi$} (C)
-%(C) edge node[above]{$\beta \odot \beta$} (D);
-\end{tikzpicture}
-\]
-These decoration isomorphisms then form the following commutative diagram in the category $F((n_1+m_1)+_{b'+b}(n_2+m_2))$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$F(\hat{\chi} \beta)((x_1 \odot x_2)+(y_1 \odot y_2))$};
-\node (B) at (4,0) {$F(\hat{\chi})((y_1 \odot y_2)+(x_1 \odot x_2))$};
-\node (C) at (0,-1) {$F(\beta \odot \beta)((x_1+y_1) \odot (x_2 + y_2))$};
-\node (D) at (4,-1) {$(y_1+x_1) \odot (y_2+x_2)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$F(\hat{\chi})(\tau_1)$} (B)
-(B) edge node[right]{$\tau_2$} (D)
-(A) edge node[left]{$F(\beta \odot \beta)(\tau_3)$} (C)
-(C) edge node[above]{$\tau_4$} (D);
-\end{tikzpicture}
-\]
-where in the top left corner, we note that $$F(\hat{\chi} \beta)((x_1 \odot x_2)+(y_1 \odot y_2)) = F((\beta \odot \beta)\hat{\chi})((x_1 \odot x_2)+(y_1 \odot y_2))$$
-as the above diagram of maps of cospans commutes in $\A$ and then applying the pseudofunctor $F$ to this diagram yields a commutative diagram in $\Cat$.
-The other diagrams in the definition of symmetric monoidal double category can be shown to commute similarly.
 \end{proof}
@@
 		\item The following diagrams commute, expressing that the braiding is a transformation of double categories:
-		\[
-		\begin{tikzpicture}
+		\begin{equation}
+		\begin{tikzpicture}\label{eq:braidingaxiom}
 			\node (A) at (0,1.5) {\footnotesize{$(M_1 \odot M_2) \otimes (N_1 \odot N_2)$}};
@@
 		\end{tikzpicture}
-		\]
+		\end{equation}
 \end{itemize}
@@
 
+\subsection{Coherence law for \cref{DC}}\label{eq:proofofaxiom}
+
+All relevant structure for decorated cospans is as described in \cref{thm:decorated_cospans,DC}. The coherence law that we check says that this diagram commutes:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$(M_1 \odot M_2) \otimes (N_1 \odot N_2)$};
+\node (B) at (3,0) {$(N_1 \odot N_2) \otimes (M_1 \odot M_2)$};
+\node (C) at (0,-.75) {$(M_1 \otimes N_1) \odot (M_2 \otimes N_2)$};
+\node (D) at (3,-.75) {$(N_1 \otimes M_1) \odot (N_2 \otimes M_2)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$\beta$} (B)
+(B) edge node[right]{$\chi$} (D)
+(A) edge node[left]{$\chi$} (C)
+(C) edge node[above]{$\beta \odot \beta$} (D);
+\end{tikzpicture}
+\]
+First of all, if we only consider the underlying cospans without their decorations, we obtain the following `flattened' commutative diagram in the symmetric monoidal double category $\lCsp(\A)$, where the top and the bottom cospans coincide:
+\[
+		\begin{tikzpicture}
+			\node (a) at (-4,0) {$a+a'$};
+			\node (b) at (1,0) {$(m_1+_b m_2) + (n_1+_{b'} n_2)$};
+			\node (c) at (6,0) {$c+c'$};
+			\node (a2) at (-4,1) {$a'+a$};
+			\node (b2) at (1,1) {$(n_1 +_{b'} n_2) + (m_1 +_b m_2)$};
+			\node (c2) at (6,1) {$c'+c$};
+            \node (a3) at (-4,2) {$a'+a$};
+			\node (b3) at (1,2) {$(n_1+m_1) +_{(b'+b)} (n_2+m_2)$};
+			\node (c3) at (6,2) {$c'+c$};
+            \node (a5) at (-4,-1) {$a+a'$};
+			\node (b5) at (1,-1) {$(m_1+n_1) +_{(b+b')} (m_2+n_2)$};
+			\node (c5) at (6,-1) {$c+c'$};
+            \node (a6) at (-4,-2) {$a'+a$};
+			\node (b6) at (1,-2) {$(n_1+m_1) +_{(b'+b)} (n_2+m_2)$};
+			\node (c6) at (6,-2) {$c'+c$};
+			\path[->,font=\scriptsize,>=angle 90]
+			(a) edge node[above]{$$} (b)
+			(c) edge node[above]{$$} (b)
+            (a2) edge node[above]{$$} (b2)
+			(c2) edge node[above]{$$} (b2)
+            (a) edge node[left]{$\beta$} (a2)
+            (b) edge node[left]{$\beta$} (b2)
+%(b) edge node[right]{$\tau_1$} (b2)
+			(c) edge node[right]{$\beta$} (c2)
+            (a3) edge node[above]{$$} (b3)
+			(c3) edge node[above]{$$} (b3)
+            (a2) edge node[left]{$\id$} (a3)
+            (b2) edge node[left]{$\hat{\chi}$} (b3)
+%(b2) edge node[right]{$\tau_2$} (b3)
+			(c2) edge node[right]{$\id$} (c3)
+            (a5) edge node[above]{$$} (b5)
+			(c5) edge node[above]{$$} (b5)
+            (a) edge node[left]{$\id$} (a5)
+            (b) edge node[left]{$\hat{\chi}$} (b5)
+%(b) edge node[right]{$\tau_4$} (b5)
+			(c) edge node[right]{$\id$} (c5)
+            (a6) edge node[above]{$$} (b6)
+			(c6) edge node[above]{$$} (b6)
+            (a5) edge node[left]{$\beta$} (a6)
+            (b5) edge node[left]{$\beta \odot \beta$} (b6)
+ %(b5) edge node[right]{$\tau_5$} (b6)
+			(c5) edge node[right]{$\beta$} (c6);
+		\end{tikzpicture}
+	\]
+where $\beta$ is the braiding of the symmetric monoidal category $\A$, $\hat{\chi}$ is the globular 2-morphism interchanging the tensor product and horizontal composition of the symmetric monoidal double category $\lCsp(\A)$, and the inwards pointing morphisms are natural maps from the each cospan's feet to its apex.
+
+For the decorations, each of the four maps of cospans constituting the above diagram has an associated decoration isomorphism with it, which we label with $\tau_i$ for $i=1,2,3,4$.
+\[
+		\begin{tikzpicture}
+%			\node (a) at (-4,0) {$a+a'$};
+			\node (b) at (1,0) {$(m_1+_b m_2) + (n_1+_{b'} n_2)$};
+			\node (c) at (8,0) {$(x_1 \odot x_2) \oplus (y_1 \odot y_2) \in F((m_1+_b m_2)+(n_1+_{b'} n_2))$};
+%			\node (a2) at (-4,1) {$a'+a$};
+			\node (b2) at (1,1) {$(n_1 +_{b'} n_2) + (m_1 +_b m_2)$};
+			\node (c2) at (8,1) {$(y_1 \odot y_2) \oplus (x_1 \odot x_2) \in F((n_1+_{b'} n_2)+(m_1+_b m_2))$};
+%                            \node (a3) at (-4,2) {$a'+a$};
+			\node (b3) at (1,2) {$(n_1+m_1) +_{(b'+b)} (n_2+m_2)$};
+			\node (c3) at (8,2) {$(y_1\oplus x_1) \odot (y_2\oplus x_2) \in F((n_1+m_1)+_{b'+b}(n_2+m_2))$};
+%                                \node (a5) at (-4,-1) {$a+a'$};
+			\node (b5) at (1,-1) {$(m_1+n_1) +_{(b+b')} (m_2+n_2)$};
+			\node (c5) at (8,-1) {$(x_1\oplus y_1) \odot (x_2\oplus y_2) \in F((m_1+n_1)+_{b+b'}(m_2+n_2))$};
+%                                \node (a6) at (-4,-2) {$a'+a$};
+			\node (b6) at (1,-2) {$(n_1+m_1) +_{(b'+b)} (n_2+m_2)$};
+			\node (c6) at (8,-2) {$(y_1\oplus x_1) \odot (y_2\oplus x_2) \in F((n_1+m_1)+_{b'+b}(n_2+m_2))$};
+			\path[->,font=\scriptsize,>=angle 90]
+%			(a) edge node[above]{$$} (b)
+%			(c) edge node[above]{$$} (b)
+%                                (a2) edge node[above]{$$} (b2)
+%			(c2) edge node[above]{$$} (b2)
+%                                (a) edge node[left]{$\beta$} (a2)
+                                (b) edge node[left]{$\beta$} (b2)
+(b) edge node[right]{$\tau_1$} (b2)
+%			(c) edge node[right]{$\beta$} (c2)
+%                                (a3) edge node[above]{$$} (b3)
+%			(c3) edge node[above]{$$} (b3)
+%                               (a2) edge node[above]{$$} (a3)
+                                (b2) edge node[left]{$\hat{\chi}$} (b3)
+(b2) edge node[right]{$\tau_2$} (b3)
+%			(c2) edge node[above]{$$} (c3)
+%                                (a5) edge node[above]{$$} (b5)
+%			(c5) edge node[above]{$$} (b5)
+%                                (a) edge node[above]{$$} (a5)
+                                (b) edge node[left]{$\hat{\chi}$} (b5)
+(b) edge node[right]{$\tau_3$} (b5)
+%			(c) edge node[above]{$$} (c5)
+%                               (a6) edge node[above]{$$} (b6)
+%			(c6) edge node[above]{$$} (b6)
+%                                (a5) edge node[left]{$\beta$} (a6)
+                                (b5) edge node[left]{$\beta \odot \beta$} (b6)
+ (b5) edge node[right]{$\tau_4$} (b6);
+%			(c5) edge node[left]{$\beta$} (c6);
+		\end{tikzpicture}
+	\]
+Explicitly, the four decoration isomorphisms are given by:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$\tau_1 \colon F(\beta)((x_1 \odot x_2)\oplus(y_1 \odot y_2)) \to (y_1 \odot y_2)\oplus(x_1 \odot x_2)$};
+\node (B) at (0,-.5) {$\tau_2 \colon F(\hat{\chi})((y_1 \odot y_2)\oplus(x_1 \odot x_2)) \to (y_1\oplus x_1) \odot (y_2\oplus x_2)$};
+\node (C) at (0,-1) {$\tau_3 \colon F(\hat{\chi})((x_1 \odot x_2)\oplus(y_1 \odot y_2)) \to (x_1\oplus y_1) \odot (x_2\oplus y_2)$};
+\node (D) at (0,-1.5) {$\tau_4 \colon F(\beta \odot \beta)((x_1\oplus y_1)\odot(x_2\oplus y_2)) \to (y_1\oplus x_1)\odot(y_2\oplus x_2)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge[color=white] node[above]{$$} (A);
+%(B) edge node[right]{$\chi$} (D)
+%(A) edge node[left]{$\chi$} (C)
+%(C) edge node[above]{$\beta \odot \beta$} (D);
+\end{tikzpicture}
+\]
+These decoration isomorphisms then form the following commutative diagram in the category $F((n_1+m_1)+_{b'+b}(n_2+m_2))$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$F(\hat{\chi} \beta)((x_1 \odot x_2)\oplus(y_1 \odot y_2))$};
+\node (B) at (4,0) {$F(\hat{\chi})((y_1 \odot y_2)\oplus(x_1 \odot x_2))$};
+\node (C) at (0,-1) {$F(\beta \odot \beta)((x_1\oplus y_1) \odot (x_2 \oplus  y_2))$};
+\node (D) at (4,-1) {$(y_1\oplus x_1) \odot (y_2\oplus x_2)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$F(\hat{\chi})(\tau_1)$} (B)
+(B) edge node[right]{$\tau_2$} (D)
+(A) edge node[left]{$F(\beta \odot \beta)(\tau_3)$} (C)
+(C) edge node[above]{$\tau_4$} (D);
+\end{tikzpicture}
+\]
+where in the top left corner, we note that $$F(\hat{\chi} \beta)((x_1 \odot x_2)\oplus (y_1 \odot y_2)) = F((\beta \odot \beta)\hat{\chi})((x_1 \odot x_2)\oplus (y_1 \odot y_2))$$
+as the above diagram of maps of cospans commutes in $\A$ and then applying the pseudofunctor $F$ to this diagram yields a commutative diagram in $\Cat$. 
+{\chris Well only up to isomorphism since F is a pseudofunctor. Does this matter?}
+{\chris I would here expect big pasted diagrams of isomorphisms coming from the braided lax monoidal pseudofunctor and using its axioms to actually show that two such isomorphisms are equal...}
+
 \begin{thebibliography}{100}

### 2020-12-02 cospans.tex
finished going through whole of 2

@@
 together with the decoration morphism $F(f)F(!_a)\phi_0(*)\cong F(!_{a'})\phi_0(*)$.
-%%% Christina: the previous formula $\tau_{\bot_f} = F(f) F(!) \phi \maps 1 \to F(a')$ doesn't typecheck to me.
-%%% Kenny: \phi:1-->F(0), F(!):F(0)-->F(a), F(f):F(a)-->F(a')? Or did I make a mistake somewhere?
-%%% Christina: Actually indeed it typechecks, I must have been thinking it does not give me the actual morphism, just one of the two or something. No issue now!
 Finally, the (horizontal) composition functor $\odot$ maps two composable $F$-decorated cospans $\left(a\to m\leftarrow b,x\in F(m)\right)$ and $\left(b\to n\leftarrow c,y\in F(n)\right)$ to their pushout in $\A$ over their shared foot
@@
 a_1+a_2\ar[ur,"i_1+i_2"] && b_1+b_2,\ar[ul,"o_1+o_2"']
-\end{tikzcd}\qquad x_1\oplus x_2:=1\xrightarrow{x_1\times x_2}F(m_1)\times F(m_2)\xrightarrow{\phi_{m_1,m_2}}F(m_1+m_2)
+\end{tikzcd}\qquad x_1\oplus x_2:=\one \xrightarrow{x_1\times x_2}F(m_1)\times F(m_2)\xrightarrow{\phi_{m_1,m_2}}F(m_1+m_2)
 \end{equation}
@@
 & F(m)\times F(n)\ar[r,"\phi_{m,n}"]\ar[dd,"F(h)\times F(h')"description]\ar[ddr,phantom,"\stackrel{\cref{eq:pseudonaturality}}{\cong}"] & F(m+n)\ar[dd,"F(h+h')"] \\
-1\ar[ur,"x\times y"]\ar[dr,"x'\times y'"']\ar[r,phantom,"\scriptstyle\Downarrow\tau_\alpha\times\tau_\beta"] & \phantom{A} && \\
+\one \ar[ur,"x\times y"]\ar[dr,"x'\times y'"']\ar[r,phantom,"\scriptstyle\Downarrow\tau_\alpha\times\tau_\beta"] & \phantom{A} && \\
 & F(m')\times F(n')\ar[r,"\phi_{m',n'}"'] & F(m'+n')
@@
 \begin{displaymath}
-I_1=\left(0\xrightarrow{!}0\xleftarrow{!}0, 1\xrightarrow{\phi_0}F(0)\right)
+I_1=\left(0\xrightarrow{!}0\xleftarrow{!}0, \one \xrightarrow{\phi_0}F(0)\right)
 \end{displaymath}
@@
 0+a\ar[rr,"1+i"]\ar[d,"\stackrel{\ell}{\cong}"'] && 0+m\ar[d,"\stackrel{\ell}{\cong}"'] && 0+b\ar[ll,"1+o"']\ar[d,"\stackrel{\ell}{\cong}"] &&1\ar[r,"\phi_0\times x"] & F(0)\times F(m)\ar[r,"\phi_{0,m}"] & F(0+m) \\
-a\ar[rr,"i"] && m && b\ar[ll,"o"'] && 1\ar[r,"x"] & F(m)\\
+a\ar[rr,"i"] && m && b\ar[ll,"o"'] && \one \ar[r,"x"] & F(m)\\
 a+0\ar[rr,"i+1"']\ar[u,"\stackrel{r}{\cong}"] && m+0\ar[u,"\stackrel{r}{\cong}"] && b+0\ar[ll,"o+1"]\ar[u,"\stackrel{r}{\cong}"']
-&&1\ar[r,"x\times\phi_0"] & F(m)\times F(0)\ar[r,"\phi_{m,0}"] & F(m+0)
+&&\one \ar[r,"x\times\phi_0"] & F(m)\times F(0)\ar[r,"\phi_{m,0}"] & F(m+0)
  \end{tikzcd}
@@
 a_1+a_2\ar[rr,"i_1+i_2"]\ar[d,"\stackrel{\beta}{\cong}"'] && m_1+m_2\ar[d,"\stackrel{\beta}{\cong}"'] && b_1+b_2\ar[ll,"o_1+o_2"']\ar[d,"\stackrel{\beta}{\cong}"] &&1\ar[r,"x_1\times x_2"] & F(m_1)\times F(m_2)\ar[r,"\phi_{m_1,m_2}"] & F(m_1+m_2) \\
-a_2+a_1\ar[rr,"i_2+i_1"'] && m_2+m_1 && b_2+b_1\ar[ll,"o_2+o_1"] &&1\ar[r,"x_2\times x_1"] & F(m_2)\times F(m_1)\ar[r,"\phi_{m_2,m_1}"] & F(m_2+m_1)
+a_2+a_1\ar[rr,"i_2+i_1"'] && m_2+m_1 && b_2+b_1\ar[ll,"o_2+o_1"] &&\one \ar[r,"x_2\times x_1"] & F(m_2)\times F(m_1)\ar[r,"\phi_{m_2,m_1}"] & F(m_2+m_1)
  \end{tikzcd}
@@
 \scalebox{.8}{\begin{tikzcd}[ampersand replacement=\&,column sep=.5in]
-1\ar[ddrr,dashed,"{(x_1\oplus y_1)\odot(x_2\oplus y_2)}"']\ar[r,"x_1{\times}y_1{\times}x_2{\times}y_2"] \& F(m_1){\times}F(n_1){\times}F(m_2){\times}F(n_2)\ar[r,"\phi_{m_1,n_1}\times\phi_{m_2,n_2}"] \& F(m_1{+}n_1){\times}F(m_2{+}n_2) \ar[d,"\phi_{m_1+n_1,m_2+n_2}"] \\
+\one \ar[ddrr,dashed,"{(x_1\oplus y_1)\odot(x_2\oplus y_2)}"']\ar[r,"x_1{\times}y_1{\times}x_2{\times}y_2"] \& F(m_1){\times}F(n_1){\times}F(m_2){\times}F(n_2)\ar[r,"\phi_{m_1,n_1}\times\phi_{m_2,n_2}"] \& F(m_1{+}n_1){\times}F(m_2{+}n_2) \ar[d,"\phi_{m_1+n_1,m_2+n_2}"] \\
 \&\& F(m_1+n_1+m_2+n_2)\ar[d,"F\psi"] \\
@@
  \scalebox{.8}{\begin{tikzcd}[ampersand replacement=\&,column sep=.4in]
-1\ar[ddrr,dashed,"{(x_1\odot x_2)\oplus(y_1\odot y_2)}"']\ar[r,"x_1{\times}x_2{\times}y_1{\times}y_2"] \& F(m_1){\times}F(m_2){\times}F(n_1){\times}F(n_2)\ar[r,"\phi_{m_1,m_2}\times\phi_{n_1,n_2}"] \& F(m_1{+}m_2){\times}F(n_1{+}n_2) \ar[d, "F\psi\times F\psi"] \\
+\one \ar[ddrr,dashed,"{(x_1\odot x_2)\oplus(y_1\odot y_2)}"']\ar[r,"x_1{\times}x_2{\times}y_1{\times}y_2"] \& F(m_1){\times}F(m_2){\times}F(n_1){\times}F(n_2)\ar[r,"\phi_{m_1,m_2}\times\phi_{n_1,n_2}"] \& F(m_1{+}m_2){\times}F(n_1{+}n_2) \ar[d, "F\psi\times F\psi"] \\
 \&\& F(m_1+_bm_2)\times F(n_1+_{b'}n_2)\ar[d,"\phi_{m_1+_bm_2,n_1+_{b'}n_2}"] \\
@@
 
-Our construction gives not only decorated cospan double categories, but maps betwen these.
+Our construction gives not only decorated cospan double categories, but maps betwen these as in \cref{def:doublefun}.
 Suppose we have two symmetric lax monoidal pseudofunctors, $F \maps \A \to \Cat$ and
@@
 \item a finitely cocontinous functor $H \maps \A \to \A'$, 
-\item a symmetric lax monoidal pseudofunctor $E \maps \Cat \to \Cat$, 
-\item an isomorphism $\theta \maps EF \Rightarrow F'H$:
+\item a symmetric lax monoidal pseudofunctor $(E,\phi,\phi_0) \maps \Cat \to \Cat$, 
+\item an isomorphism $\theta \maps EF \Rightarrow F'H$: {\chris is this natural or pseudonatural? It should be clarified.}
 \[
@@
 \node (D) at (1,-1) {$\Cat$.};
-\node (E) at (0.5,-0.5) {$\Swarrow \theta$};
+\node (E) at (0.5,-0.5) {$\Downarrow\theta$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \item The image of a vertical 1-morphism $f \colon a \to b$ is the vertical 1-morphism $H(f) \colon H(a) \to H(b)$. 
+\end{itemize}
 In other words, the object component $\lH_0$ of the double functor $\lH$ is the functor $H$.
-\item Given a horizontal 1-cell $M$ in $F\lCsp$, which is an $F$-decorated cospan, the image will be the $F'$-decorated cospan $\lH(M)$ in $F'\lCsp$
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a$};
-\node (B) at (1,0) {$m$};
-\node (C) at (2,0) {$b$};
-\node (D) at (1,-0.5) {$x \in F(m)$};
-\node (E) at (2.75,0) {$\mapsto$};
-\node (A') at (3.5,0) {$H(a)$};
-\node (B') at (4.5,0) {$H(m)$};
-\node (C') at (5.5,0) {$H(b)$};
-\node (D') at (4.5,-0.5) {$\theta_m E(x) \phi \in F'(H(m))$};
-\node (F) at (1,0.5) {$M$};
-\node (G) at (4.5,0.5) {$\lH(M)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i$} (B)
-(C) edge node[above]{$o$} (B)
-(A') edge node[above]{$H(i)$} (B')
-(C') edge node[above]{$H(o)$} (B');
-\end{tikzpicture}
-\]
-where given a decoration $x \colon 1 \to F(m)$ on $m$, we obtain a decoration on $H(m)$ via the composite 
-\[ 1 \xrightarrow{\phi} E(1) \xrightarrow{E(x)} E(F(m)) \xrightarrow{\theta_m} F'(H(m)).\]
-\item Given a 2-morphism $\alpha \colon M \to N$ in $F\lCsp$, which is a map of $F$-decorated cospans, the image will be the map of $F'$-decorated cospans $\lH(\alpha)$ in $F'\lCsp$
+\begin{itemize}
+\item The image of an $F$-decorated cospan $M$ in $F\lCsp$ is the $F'$-decorated cospan $\lH(M)$ in $F'\lCsp$
+\begin{align*}
+ M=\left(a\xrightarrow{i}m\xleftarrow{o}b,x\in F(m)\right)\mapsto \lH(M)=\left(H(a)\xrightarrow{H(i)}H(m)\xleftarrow{H(o)}H(b),\bar{x}\in F'(H(m))\right)& \textrm{ where } \\
+\bar{x}:=\one \xrightarrow{\phi_0} E(\one) \xrightarrow{E(x)} E(F(m)) \xrightarrow{\theta_m} F'(H(m)) &
+\end{align*}
+%\[
+%\begin{tikzpicture}[scale=1.5]
+%\node (A) at (0,0) {$a$};
+%\node (B) at (1,0) {$m$};
+%\node (C) at (2,0) {$b$};
+%\node (D) at (1,-0.5) {$x \in F(m)$};
+%\node (E) at (2.75,0) {$\mapsto$};
+%\node (A') at (3.5,0) {$H(a)$};
+%\node (B') at (4.5,0) {$H(m)$};
+%\node (C') at (5.5,0) {$H(b)$};
+%\node (D') at (4.5,-0.5) {$\theta_m E(x) \phi \in F'(H(m))$};
+%\node (F) at (1,0.5) {$M$};
+%\node (G) at (4.5,0.5) {$\lH(M)$};
+%\path[->,font=\scriptsize,>=angle 90]
+%(A) edge node[above]{$i$} (B)
+%(C) edge node[above]{$o$} (B)
+%(A') edge node[above]{$H(i)$} (B')
+%(C') edge node[above]{$H(o)$} (B');
+%\end{tikzpicture}
+%\]
+%where given a decoration $x \colon 1 \to F(m)$ on $m$, we obtain a decoration on $H(m)$ via the composite 
+%\[ 1 \xrightarrow{\phi} E(1) \xrightarrow{E(x)} E(F(m)) \xrightarrow{\theta_m} F'(H(m)).\]
+\item The image of a map of decorated cospans $\alpha \colon M \to N$ in $F\lCsp$ is the map of $F'$-decorated cospans $\lH(\alpha)$ in $F'\lCsp$
 \[
@@
 \node (F) at (3,-0.5) {$x' \in F(n)$};
-\node (G) at (1,-1) {$\tau \maps F(h)(x) \to x'$};
+%\node (G) at (1,-1) {$\tau \maps F(h)(x) \to x'$};
 \node (A'') at (4.75,0.5) {$H(a)$};
@@
 \node (D'') at (5.75,-0.5) {$H(n)$};
-\node (E'') at (8.5,0.5) {$\theta_m E(x) \phi \in F'(H(m))$};
-\node (F'') at (8.5,-0.5) {$\theta_n E(x') \phi \in F'(H(n))$};
-\node (G'') at (5.75,-1) {$E(\tau) \maps F'(H(h))(\theta_m E(x)\phi) \to (\theta_n E(x')\phi)$};
+\node (E'') at (8.5,0.5) {$\theta_m E(x) \phi_0 \in F'(H(m))$};
+\node (F'') at (8.5,-0.5) {$\theta_n E(x') \phi_0 \in F'(H(n))$};
+%\node (G'') at (5.75,-1) {$E(\tau) \maps F'(H(h))(\theta_m E(x)\phi) \to (\theta_n E(x')\phi)$}; %%%Christina: E(tau) is a bad name since it already means something!
 \node (H) at (3.75,0) {$\mapsto$};
@@
 \]
-where given a decoration morphism $\tau \colon F(h)(x) \to x'$, the decoration morphism $E(\tau)$ is defined as:
+where given a decoration morphism $\tau \colon F(h)(x) \to x'$, the induced decoration morphism is:
 \[
@@
 \node (I) at (-2,-1) {$F(n)$};
-\node (J) at (-2.5,-0.5) {$\Swarrow \tau$};
+\node (J) at (-2.5,-0.5) {$\scriptstyle\Downarrow\tau$};
 \node (K) at (-1,-0.5) {$\mapsto$};
@@
 \node (D) at (2,-1) {$E(F(n))$};
-\node (C) at (1.5,-0.5) {$\Swarrow E(\tau)$};
+\node (C) at (1.5,-0.5) {$\scriptstyle\Downarrow E(\tau)$};
 \node (E) at (4,0) {$F^\prime(H(m))$};
@@
 \]
+{\chris There should be an iso on the right if we go with pseudonatural isomorphism}
 \end{itemize}
@@
 \node (D) at (1,-1) {$\Cat$};
-\node (E) at (0.5,-0.5) {$\Swarrow \theta$};
+\node (E) at (0.5,-0.5) {$\Downarrow \theta$};
 \path[->,font=\scriptsize,>=angle 90]

### 2020-12-02 cospans.tex
minor edits while going over section 3

@@
 
-The following theorem establishes the isomorphism between structured and decorated cospan double categories under certain conditions.
+The following theorem establishes an isomorphism between structured and decorated cospan double categories under certain conditions.
 We denote by $\Rex$ the 2-category of finitely cocomplete categories, finitely cocontinuous functors and natural transformations.
@@
 
-In \cite{MV}, the classical Grothendieck construction is generalized to the monoidal setting: given a monoidal category $\A$ there is a bijection between \define{monoidal opindexed categories}, which are lax monoidal pseudofunctors $F\maps\A\to\Cat$, and \define{monoidal opfibrations}, which are opfibrations $U \maps \X \to \A$ where $\X$ is monoidal, $U$ is strict monoidal, and $\otimes_\X$ preserves cocartesian liftings.
-This bijection sends a monoidal opindexed category $F \maps \A \to \Cat$ to its Grothendieck construction $U \maps \inta F \to \A$.
+In \cite{MV}, the classical Grothendieck construction is generalized to the monoidal setting: given a monoidal category $\A$ there is a bijection between \define{monoidal opindexed categories}, which are lax monoidal pseudofunctors $F\maps\A\to\Cat$, and \define{monoidal opfibrations}, which are opfibrations $U \maps \X \to \A$ where $\X$, $\A$ are monoidal, $U$ is strict monoidal, and $\otimes_\X$ preserves cocartesian liftings.
+This bijection sends a monoidal opindexed category $F \maps \A \to \Cat$ to its Grothendieck monoidal opfibration $U \maps \inta F \to \A$.
 If the monoidal structure on $\A$ is in fact cocartesian, there is a further correspondence between these structures and ordinary pseudofunctors $F\maps\A\to\bicat{MonCat}$ where $\bicat{MonCat}$ is 2-category of monoidal categories, strong monoidal functors and monoidal natural transformations.
-Further, all these correspondences lift to 2-equivalences.
+In fact, all these correspondences lift to 2-equivalences.
 
@@
 \end{equation}
-which is the pushout $u_a\colon a\to a+_bc\leftarrow c:u_c$ in $\A$ on the first variable, and $w$ is the pushout in the fibre $F(a+_bc)$
+which on the first variable is given by the pushout in $\A$ on the left below, and the object $w$ is formed as the pushout in the fibre category $F(a+_bc)$ on the right below:
 \begin{displaymath}
+\begin{tikzcd}
+& a+_bc\ar[dd,phantom, very near start,"\upback"description] & \\
+a\ar[ur,"u_a"] && c\ar[ul,"u_c"'] \\
+& b\ar[ul,"f"]\ar[ur,"g"'] &
+\end{tikzcd}\qquad
 \begin{tikzcd}
@@
 \end{displaymath}
-In similar ways we can construct the initial object and coproducts in a Grothendieck category, namely
+In a similar way we can construct the initial object and coproducts in a Grothendieck category from those in the fibres, namely
 \begin{equation}\label{eq:fibrewisecoprod}
@@
 \end{equation}
-where $\iota_a:a\to a+b\leftarrow b:\iota_b$ are the sum inclusions in $\A$.
+where $\iota_a:a\to a+b\leftarrow b:\iota_b$ are the sum inclusions in $\A$ and the sum on the second variable is in the fibre $F(a+b)$.
 
@@
 Therefore, we can simplify the above assumption to that in \cref{thm:equiv} without having to specify that the structures came from monoidality of the pseudofunctor, although we \emph{will} use the formulation of coproducts and initial object in terms of the monoidal structure of $F$.
-For example, in that case, the coproducts induced in the Grothendieck category by the fibrewise ones as in \cref{eq:fibrewisecoprod} are equivalently given by \cref{eq:explicitstructure2}.
+For example, in that case, the coproducts induced in the Grothendieck category from the fibrewise ones as in \cref{eq:fibrewisecoprod} are equivalently given by \cref{eq:explicitstructure2}.
 
@@
 
-We have now have all the necessary background to formally construct an isomorphism between the double category of decorated cospans and the double category of structured cospans, starting from a symmetric lax monoidal pseudofunctor $F \maps (\A, +) \to (\Cat, \times)$ that factors through $\Rex$ as a pseudofunctor.
+We now have all the necessary background to formally construct an isomorphism between the double category of decorated cospans and the double category of structured cospans, starting from a symmetric lax monoidal pseudofunctor $F \maps (\A, +) \to (\Cat, \times)$ that factors through $\Rex$ as a pseudofunctor.
 
@@
 As a left adjoint, this induced $L$ preserves all colimits that exist between the finitely cocomplete categories $\A$ and $\inta F$, so we can construct the double category of structured cospans $_L\lCsp(\inta F)$ of \cref{thm:SC}.
-Its objects and vertical morphisms are those of the category $\A$ (as for $F\lCsp$ earlier), whereas horizontal 1-cells are now cospans of the form $\cspn{L(a)}{(m,x)}{L(b)}{}{}$ in the Grothendieck category $\inta F$ (\cref{def:GrothCat}).
+Its objects and vertical morphisms are those of the category $\A$ (same as for $F\lCsp$), whereas horizontal 1-cells are now cospans of the form $\cspn{L(a)}{(m,x)}{L(b)}{}{}$ in the Grothendieck category $\inta F$ (\cref{def:GrothCat}).
 Explicitly, they consist of two pairs of morphisms
@@
 Given a horizontal 1-cell in $_L\lCsp(\inta F)$ as in \cref{eq:scsphor1cell}, $\lE_1$ maps it to the decorated cospan $i\maps a\to m\leftarrow b:o$ with decoration $x\in F(m)$,
-whereas a 2-morphism of $L$-structured cospans as above is mapped to the underlying map of cospans in $\A$
+whereas a 2-morphism of $L$-structured cospans as in \cref{eq:2morphismLCspintaF} is mapped to the underlying map of cospans in $\A$
 \begin{displaymath}
@@
 \end{displaymath}
-in $\A$ along with the map $\tau\maps Fk(x)\to x'$ in $F(m')$, namely an $F$-decorated cospan 2-morphism. 
-With these definitions, $\lE$ is indeed a (pseudo) double functor as in \cref{def:doublefun}: both $\lE_0$ and $\lE_1$ are functors that appropriately commute with sources and targets, and there exist globular 2-isomorphisms $\lE(M) \odot \lE(N) \simrightarrow\lE(M \odot N)$, $U_{\lE m} \simrightarrow\lE(U_m)$
+in $\A$ along with the map $\tau\maps Fk(x)\to x'$ in $F(m')$ coming from the middle arrow above, namely an $F$-decorated cospan 2-morphism. 
+With these definitions, $\lE$ is indeed a double functor as in \cref{def:doublefun}: both $\lE_0$ and $\lE_1$ are functors that appropriately commute with sources and targets, and there exist globular 2-isomorphisms $\lE(M) \odot \lE(N) \simrightarrow\lE(M \odot N)$, $U_{\lE m} \simrightarrow\lE(U_m)$
 for any pair of composable horizontal 1-cells $M=\cspn{(a,\bot_a)}{(m,x)}{(b,\bot_b)}{}{}$ and $N=\cspn{(b,\bot_b)}{(n,y)}{(c,\bot_c)}{}{}$ and any object $m$ of $_L\lCsp(\inta F)$.
@@
 Since both double categories are symmetric monoidal under the running assumptions (\cref{DC,thm:SC}), we will now show that this double isomorphism is a symmetric monoidal one, namely $\lE=(\lE_0,\lE_1)$ is a symmetric strong monoidal double functor as per \cref{defn:monoidal_double_functor}.
-Indeed, $\lE_0=\mathrm{id}_\A$ is a braided monoidal functor trivially.
+Indeed, $\lE_0=\mathrm{id}_\A$ is a symmetric monoidal functor trivially.
 For $\lE_1$, given two structured cospans $M=(a,\bot_a)\to(m,x)\leftarrow(b,\bot_b)$ and $M'=(a',\bot_{a'})\to(m',x')\leftarrow(b',\bot_{b'})$ in $_L\lCsp(\inta F)$, we compute the appropriate decorated cospans

### 2020-12-03 cospans.tex
worked on issues of "chosen colimits"

@@
 % in LaTeX
-% 2020/12/1
+% 2020/12/2
 
@@
 We prove that under certain conditions these two constructions become equivalent when we take $\X = \int F$ to be the Grothendieck category of $F$.
-We illustrate these ideas with applications to electrical circuits, Petri nets, reaction networks and dynamical systems.
+We illustrate these ideas with applications to electrical circuits, Petri nets, chemistry and dynamical systems.
 \end{abstract}
@@
 But this hope is doomed, for reasons painstakingly explained in \cite[Sec.\ 5]{BC2}.
-There is really a \emph{category} of graphs with $m$ as their set of nodes, and trying to treat it as a mere set does not work.
+There is really a \emph{category} of graphs with $m$ as their set of nodes---and surprisingly, trying to treat this category as a mere set does not work, despite all the tricks one might try.
 
@@
 \end{itemize}
-Many of the flawed applications of decorated cospans have been fixed using structured cospans
-\cite[Sec.\ 6]{BC2}.
-
-We show that our new solution subsumes the old one: structured cospan double categories are always equivalent to decorated cospan double categories.
-(REALLY????)   %%%Christina: Not sure what this refers to.
-The paragraph below is more to the point.
-If this is supposed to provide the opposite direction, I would expect that to also hold under certain assumptions, similar to the ones below.
-
-We also give sufficient conditions for a decorated cospan double category to be equivalent to a structured cospan double category. 
-Suppose $\A$ has finite colimits and $F \maps (\A , +) \to (\Cat, \times)$ is a 
-symmetric lax monoidal pseudofunctor.   Any such pseudofunctor gives an opfibration 
-$U \maps \X \to \A$ where $\X = \inta F$ is defined by the Grothendieck construction.
-Let $\Rex$ be the 2-category of finitely cocomplete categories, finite-colimit-preserving
-functors and natural transformations.  We show that if $F$ factors through $\mathbf{Rex}$ as
-a pseudofunctor, the opfibration $U \maps \X \to \A$ is also a right adjoint.
+Many of the flawed applications of decorated cospans have been fixed using structured cospans \cite[Sec.\ 6]{BC2}, but not all decorated cospans can handled using structured cospans.
+
+Here we give sufficient conditions for a decorated cospan double category to be equivalent to a structured cospan double category.
+Suppose $\A$ has finite colimits and $F \maps (\A , +) \to (\Cat, \times)$ is a symmetric lax monoidal pseudofunctor.
+Any such pseudofunctor gives an opfibration $U \maps \X \to \A$ where $\X = \inta F$ is defined by the Grothendieck construction.
+Let $\Rex$ be the 2-category of categories with finite colimits, functors preserving finite colimits, and natural transformations.
+We show that if $F$ factors through $\mathbf{Rex}$ as a pseudofunctor, the opfibration $U \maps \X \to \A$ is also a right adjoint.
 From the accompanying left adjoint $L \maps \A \to \X$, we  construct a symmetric monoidal double category ${}_L \lCsp(\X)$ of structured cospans.
@@
 In \cref{EquivDoubleCats}, we briefly review the structured cospans framework and prove that the double categorical versions of decorated cospans and structured cospans are equivalent under suitable conditions.
-In \cref{spinoffs}, we establish the equivalence between structured and decorated cospans on the horizontal bicategory and the ordinary category level (via decategorification).
-Finally, in \cref{Applications}, we present a few examples that can be realized with either framework and discuss the realized equivalences.
+In \cref{spinoffs}, we establish the equivalence between structured and decorated cospans at the level of bicategories and categories (via decategorification).
+Finally, in \cref{Applications}, we describe applications to electrical circuits, Petri nets, chemistry and dynamical systems.
 
@@
 
-In this paper, we use sans-serif font like $\C$ for categories, boldface like $\mathbf{B}$ for bicategories or 2-categories, and blackboard bold like $\lD$ for double categories.
+In this paper, we use a sans-serif font like $\C$ for categories, boldface like $\mathbf{B}$ for bicategories or 2-categories, and blackboard bold like $\lD$ for double categories.
 For double categories with names having more than one letter, like $\lCsp(\X)$, only the first letter is in blackboard bold.
@@
 \subsection*{Acknowledgements}
-Daniel Cicala, Brendan Fong...
+
+We thank Daniel Cicala, Brendan Fong, and Joe Moeller for helpful conversations.
 
@@
 
-In this section we build the symmetric monoidal double category $F \lCsp$ mentioned in the introduction, and then study the functoriality of this construction.
+In this section we build symmetric monoidal double categories of decorated cospans, and then study the functoriality of this construction.
 The definition of a lax monoidal pseudofunctor is recalled in \cref{subsec:bicats}, and the definition of a double category is recalled in \cref{defn:double_category}.
+
+In all that follows, when we say a category `has finite colimits' we mean it is equipped with a choice of colimit for every finite diagram.
+Thus, if $\A$ has finite colimits it gives a cocartesian monoidal category $(\A,+)$: a symmetric monoidal category where the monoidal structure is given by the chosen binary coproducts and initial object.
+However, when we say a functor `preserves finite colimits', it need only do this up to canonical isomorphism, unless otherwise specified.
 
@@
 
-The following result establishes that under the same assumptions as \cref{thm:decorated_cospans}, the formed double category of decorated cospans is monoidal; it becomes symmetric when the lax monoidal pseudofunctor is.
-The definitions of (symmetric) monoidal double categories are recalled in \cref{defn:monoidal_double_category,defn:symmetric_monoidal_double_category}.
+The following result establishes that under the same assumptions as \cref{thm:decorated_cospans}, the double category of decorated cospans is monoidal; it becomes symmetric when the lax monoidal pseudofunctor is.
+Monoidal and symmetric monoidal double categories are recalled in \cref{defn:monoidal_double_category,defn:symmetric_monoidal_double_category}.
 
@@
 %%%Christina: we do not have any such information at this point!
-We have not talked about the categories F(a) being cocomplete, and it's not deduced from the assumptions.
+We have not talked about the categories F(a) having finite colimits, and it's not deduced from the assumptions.
 We will show this is the case much later!
@@
 It can be verified with this structure, $F\lCsp$ is indeed a symmetric monoidal double category, namely all coherence laws are satisfied.
-The details can be found in \cite[Theorem 4.1.3]{CourserThesis}, but in order to give the reader a sense of what these checks entail, we provide an explicit proof of the fact that the braiding is a transformation of double categories, i.e.
-establish the commutativity of the left-hand side diagram \cref{eq:braidingaxiom}, in \cref{eq:proofofaxiom} so as to not interrupt the main narrative.
+The details can be found in \cite[Theorem 4.1.3]{CourserThesis}, but in order to give the reader a sense of what these checks entail, we provide an explicit proof of the fact that the braiding is a transformation of double categories in \cref{eq:proofofaxiom}.
+\end{proof}
 
@@
 We exhibit one of these laws to give the reader a sense of how they are verified, with more details available in the second author's thesis \cite{CourserThesis}.
-\end{proof}
-
-Our construction gives not only decorated cospan double categories, but maps betwen these as in \cref{def:doublefun}.
-Suppose we have two symmetric lax monoidal pseudofunctors, $F \maps \A \to \Cat$ and
-$F' \maps \A' \to \Cat$.    Then we can obtain a map between their decorated cospan 
-double categories, $\lH \maps F\lCsp \to F' \lCsp$, from:
+
+Our construction gives not only decorated cospan double categories, but  also maps between these: that is, symmetric monoidal double functors, as in \cref{def:doublefun}.
+Suppose we have two categories $\A,A'$ with finite colimits and two symmetric lax monoidal pseudofunctors $F \maps \A \to \Cat$ and $F' \maps \A' \to \Cat$.
+Then we can obtain a map between their decorated cospan double categories, $\lH \maps F\lCsp \to F' \lCsp$, from:
 \begin{itemize}
-\item a finitely cocontinous functor $H \maps \A \to \A'$, 
+\item a functor $H \maps \A \to \A'$ that preserves finite limits.
 \item a symmetric lax monoidal pseudofunctor $(E,\phi,\phi_0) \maps \Cat \to \Cat$, 
@@
 \label{thm:functoriality}
-Given two finitely cocomplete categories $\A$ and $\A'$, two symmetric lax monoidal pseudofunctors $F \maps \A \to \Cat$ and $F' \maps \A' \to \Cat$, a finite colimit preserving functor $H \maps \A \to \A'$, a symmetric lax monoidal pseudofunctor $E \maps \Cat \to \Cat$ and a 2-isomorphism $\theta \maps EF \Rightarrow F' H$ as in the following diagram,
+Given two categories $\A$ and $\A'$ with finite colimits, two symmetric lax monoidal pseudofunctors $F \maps \A \to \Cat$ and $F' \maps \A' \to \Cat$, a finite colimit preserving functor $H \maps \A \to \A'$, a symmetric lax monoidal pseudofunctor $E \maps \Cat \to \Cat$ and a 2-isomorphism $\theta \maps EF \Rightarrow F' H$ as in the following diagram,
 \[
@@
 \begin{thm}\label{thm:SC}
-Given categories $\A$ and $\X$ with finite colimits and $L \maps \A \to \X$ a functor preserving
-finite colimits, there is a symmetric monoidal double category $_L\lCsp(\X)$ in which
+Given categories $\A$ and $\X$ with finite colimits and $L \maps \A \to \X$ a functor preserving finite colimits there is a symmetric monoidal double category $_L\lCsp(\X)$ in which
 \begin{itemize}
@@
 The following theorem establishes an isomorphism between structured and decorated cospan double categories under certain conditions.
-We denote by $\Rex$ the 2-category of finitely cocomplete categories, finitely cocontinuous functors and natural transformations.
-(In \cite{BC} we took as objects finitely cocomplete categories with chosen finite colimits, just so we could turn these into symmetric monoidal categories without any further choices!!!
-Should we do that here???) {\chris Can you tell if we can get away without doing that?
-Perhaps after you read up to before the proof?}
+We denote by $\Rex$ the 2-category of categories with finite colimits, functors preserving finite colimits, and natural transformations.
+Recall that for us a category $\A \in \Rex$ comes with a choice of finite colimits, so it gives a cocartesian monoidal category $(\A,+)$.
 
@@
 
-In \cite{MV}, the classical Grothendieck construction is generalized to the monoidal setting: given a monoidal category $\A$ there is a bijection between \define{monoidal opindexed categories}, which are lax monoidal pseudofunctors $F\maps\A\to\Cat$, and \define{monoidal opfibrations}, which are opfibrations $U \maps \X \to \A$ where $\X$, $\A$ are monoidal, $U$ is strict monoidal, and $\otimes_\X$ preserves cocartesian liftings.
-This bijection sends a monoidal opindexed category $F \maps \A \to \Cat$ to its Grothendieck monoidal opfibration $U \maps \inta F \to \A$.
+In \cite{MV}, the classical Grothendieck construction is generalized to the monoidal setting: given a monoidal category $\A$ there is a bijection between \define{monoidal opindexed categories}, which are lax monoidal pseudofunctors $F\maps (\A, \otimes_A) \to (\Cat, \times)$, and \define{monoidal opfibrations}, which are opfibrations $U \maps \X \to \A$ where $\X$, $\A$ are monoidal, $U$ is strict monoidal, and $\otimes_\X$ preserves cocartesian liftings.
+This bijection sends a monoidal opindexed category $F \maps (\A,\otimes_A) \to (\Cat, \times)$ to its Grothendieck monoidal opfibration $U \maps \inta F \to \A$.
 If the monoidal structure on $\A$ is in fact cocartesian, there is a further correspondence between these structures and ordinary pseudofunctors $F\maps\A\to\bicat{MonCat}$ where $\bicat{MonCat}$ is 2-category of monoidal categories, strong monoidal functors and monoidal natural transformations.
@@
 \Updownarrow \notag\\
-\textrm{monoidal opfibrations }U\maps(\X,\otimes)\to(\A,+) \notag\\
+\textrm{monoidal opfibrations }U\maps(\X,\otimes_\X)\to(\A,+) \notag\\
 \Updownarrow \notag\\
@@
 \end{gather}
-The second equivalence was also earlier observed by Shulman \cite{Shulman2008}.
+The second equivalence was observed earlier by Shulman \cite{Shulman2008}.
 
@@
 
-These 2-equivalences further restrict to the case when the Grothendieck category $(X,\otimes)$ is specifically cocartesian monoidal itself, with coproducts built up from \cref{eq:explicitstructure2}.
-In that case, opfibrations $(\X,+)\to(\A,+)$ that (strictly) preserve coproducts and initial object bijectively correspond to pseudofunctors into the 2-category of cocartesian categories.
+These 2-equivalences further restrict to the case when the Grothendieck category $(X,\otimes_\X)$ is specifically cocartesian monoidal itself, with coproducts built up from \cref{eq:explicitstructure2}.
+In that case, opfibrations $(\X,+)\to(\A,+)$ that strictly preserve coproducts and initial object bijectively correspond to pseudofunctors into the 2-category of cocartesian categories.
 For more details, see \cite[Corollary 4.7]{MV} and the related discussion.
@@
  \item all fibres have $\J$-colimits, and the reindexing functors preserve them;
- \item the total category $\X$ has $\J$-colimits, and $U$ (strictly) preserves them.
+ \item the total category $\X$ has $\J$-colimits, and $U$ preserves them.
+Moreover in this situation the $\J$-colimits in $\X$ and $\J$ can be chosen so that $U$ strictly preserves them.   %%% CHECK AND MAYBE FIX THIS!!!
 \end{enumerate}
@@
 \begin{proof}
-See \cite[Corollary~4.9]{Hermida1999} as well as \cite[Remark~4.11]{Hermida1999} for the non-necessary strictness condition.
+See \cite[Corollary~4.9]{Hermida1999}, and for the final statement \cite[Remark~4.11]{Hermida1999}.
 \end{proof}
@@
 The first part formulates the existence of colimits \emph{locally} in each fibre, and if we let $\J$ range over all finite categories it says that the corresponding pseudofunctor $F\maps\A\to\Cat$ lands in the sub-2-category $\Rex$.
-The second part formulates the existence of colimits \emph{globally} in the total category $\inta F$, and if we let $\J$ range over all finite categories it says that $\X$ is finitely cocomplete and $U$ preserves all finite colimits.
+The second part formulates the existence of colimits \emph{globally} in the total category $\inta F$, and if we let $\J$ range over all finite categories it says that $\X$ has finite colimits and $U$ preserves all finite colimits.
 As an example, suppose that $\A$ has pushouts and a Grothendieck opfibration $U\colon\inta F\to\A$ has fibrewise pushouts preserved by its reindexing functors.
@@
 \begin{cor}\label{cor:fcocMonGroth}
- Suppose $\A$ is a finitely cocomplete category and $F\maps(\A,+)\to(\Cat,\times)$ is a lax monoidal pseudofunctor.
+ Suppose $\A$ has finite colimits and $F\maps(\A,+)\to(\Cat,\times)$ is a lax monoidal pseudofunctor.
 If the corresponding pseudofunctor $\tilde{F} \maps \A\to\bicat{MonCat}$ given in \cref{lem:MonGroth} factors through $\Rex$, then $\inta F$ has all finite colimits and the induced opfibration $U\maps\inta F\to\A$ preserves them.
+STRICTLY???
+%%%!!!
 \end{cor}
@@
 
-By \cref{cor:fcocMonGroth}, when $F$ as an ordinary pseudofunctor factors through $\Rex$, the Gro\-the\-ndieck construction gives rise to a finitely cocomplete $\inta F$ such that the corresponding opfibration $U\maps\inta{F}\to\A$ preserves all finite colimits.
+By \cref{cor:fcocMonGroth}, when $F$ as an ordinary pseudofunctor factors through $\Rex$, the Gro\-the\-ndieck construction gives rise to a category $\inta F$ with finite colimits such that the corresponding opfibration $U\maps\inta{F}\to\A$ preserves all finite colimits.
 Moreover, by \cref{prop:opfibtolari}, $U$ has a left adjoint $L\maps\A\to\inta F$ with $UL=1_\A$.
@@
 describes the construction of the adjunction from the original $F$.
-Explicitly, the left adjoint picks the initial object in the finitely cocomplete fibre $L(a)=(a,\bot_a)$, also expressed as $F(!_a)\circ\phi_0(*)$ according to \cref{eq:explicitstructure1} for $(\phi,\phi_0)$ the monoidal structure of $F$.
+Explicitly, the left adjoint picks the initial object in the fibre $L(a)=(a,\bot_a)$, also expressed as $F(!_a)\circ\phi_0(*)$ according to \cref{eq:explicitstructure1} for $(\phi,\phi_0)$ the monoidal structure of $F$.
 %Christina: If each adjoint picks one isomorphic initial object, can we choose the one with that choice?
@@
 
-As a left adjoint, this induced $L$ preserves all colimits that exist between the finitely cocomplete categories $\A$ and $\inta F$, so we can construct the double category of structured cospans $_L\lCsp(\inta F)$ of \cref{thm:SC}.
+As a left adjoint, this induced $L$ preserves all colimits that exist between the categories $\A$ and $\inta F$, which have finite colimits, so we can construct the double category of structured cospans $_L\lCsp(\inta F)$ of \cref{thm:SC}.
 Its objects and vertical morphisms are those of the category $\A$ (same as for $F\lCsp$), whereas horizontal 1-cells are now cospans of the form $\cspn{L(a)}{(m,x)}{L(b)}{}{}$ in the Grothendieck category $\inta F$ (\cref{def:GrothCat}).
@@
 in the fibre category $F(m')$, by composition in the Grothendieck category \cref{eq:compGrothcat}.
-Since both morphisms emanate from the mapped initial object in $F(m')$ under the finitely cocontinuous reindexing functors, they are the unique such into $x'$ therefore this gives no extra conditions; similarly for the equality including $o,o'$.
+Since both morphisms emanate from the mapped initial object in $F(m')$ under the finite-colimit-preserving reindexing functors, they are the unique such into $x'$ therefore this gives no extra conditions; similarly for the equality including $o,o'$.
 
@@
 In other words, it sends a pair of graph structures to their `disjoint union'.
-Surprisingly, though $F$ is a functor---for example, composition is strictly preserved---this choice of $\phi_{N,N'}$ does not make $F$ into a symmetric lax monoidal functor, since it obeys the required laws only up to natural isomorphism, as in Equation \cref{eq:omega}.
+Surprisingly, though $F$ is a functor---for example, composition is strictly preserved---this choice of $\phi_{N,N'}$ does not make $F$ into a symmetric lax monoidal functor, since it obeys the required laws only up to natural isomorphism, as in \cref{eq:omega}.
 See \cite[Section 5]{BC} for a proof that these laws fail to hold on the nose.
-This fact necessitates a generalization of Fong's original approach to decorated cospans.
+This fact is what necessitated a generalization of Fong's original approach to decorated cospans.
 
@@
 \end{equation}
-subject to coherence conditions. In particular, pseudonaturality of the monoidal structure means that it comes with isomorphisms (natural in $f,g$)
+subject to coherence conditions. 
+%%% Give reference describing these conditions!!!
+In particular, pseudonaturality of the monoidal structure means that it comes with isomorphisms (natural in $f,g$)
 \begin{equation}\label{eq:pseudonaturality}
@@
 
-\subsection{Coherence law for \cref{DC}}\label{eq:proofofaxiom}
-
+\section{} \label{eq:proofofaxiom}
+
+Here we show a sample check of a coherence law for the proof of \cref{DC}.
 All relevant structure for decorated cospans is as described in \cref{thm:decorated_cospans,DC}. The coherence law that we check says that this diagram commutes:

### 2020-12-03 cospans.tex
changing order of composition

@@
 We thank Daniel Cicala, Brendan Fong, and Joe Moeller for helpful conversations.
+The third author would  like  to  thank  the  General  Secretariat  for  Research  and Technology (GSRT) and the Hellenic Foundation for Research and Innovation (HFRI).
 
@@
 together with the decoration morphism $F(f)F(!_a)\phi_0(*)\cong F(!_{a'})\phi_0(*)$.
-Finally, the (horizontal) composition functor $\odot$ maps two composable $F$-decorated cospans $\left(a\to m\leftarrow b,x\in F(m)\right)$ and $\left(b\to n\leftarrow c,y\in F(n)\right)$ to their pushout in $\A$ over their shared foot
+Finally, the (horizontal) composition functor $\odot$ maps two composable $F$-decorated cospans $M=\left(a\to m\leftarrow b,x\in F(m)\right),N=\left(b\to n\leftarrow c,y\in F(n)\right)$ to $N\odot M$, which as a cospan is their pushout in $\A$ over their shared foot
 \begin{equation}\label{eq:dcospanscomposition}
@@
 \end{equation}
-with decoration
-$$x\odot y:= \one\cong\one \times \one \xrightarrow{x \times y} F(m) \times F(n) \xrightarrow{\phi_{m,n}} F(m+n) \xrightarrow{F(\psi)} F(m+_{b}n)$$
+equipped with the decoration
+$$y\odot x:= \one\cong\one \times \one \xrightarrow{x \times y} F(m) \times F(n) \xrightarrow{\phi_{m,n}} F(m+n) \xrightarrow{F(\psi)} F(m+_{b}n)$$
 where $\psi \maps m + n \to m+_{b} n$ is the natural map from the coproduct to the pushout and $\phi_{m,n} \maps F(m) \times F(n) \to F(m+n)$ are the lax monoidal structure maps of $F$.
@@
 \]
-their composite $\alpha \odot \beta$ is horizontal cospan composition in $\A$
+their composite $\beta\odot \alpha$ is horizontal cospan composition in $\A$
 \[
@@
 \]
-together with the decoration morphism $\tau_{\alpha \odot \beta} \colon F(h_1 +_g h_2)(x \odot y) \to (x' \odot y')$ given by the diagram:
+together with the decoration morphism $\tau_{\beta \odot \alpha} \colon F(h_1 +_g h_2)(y \odot x) \to (y' \odot x')$ given by the diagram:
 \[
@@
 %\]
-the isomorphism $(M_1\odot M_2)\odot M_3\cong M_1\odot (M_2\odot M_3)$ is the isomorphism of cospans 
+the isomorphism $(M_3\odot M_2)\odot M_1\cong M_3\odot (M_2\odot M_1)$ is the isomorphism of cospans 
 \[
@@
 \node (D) at (1.5,-0.5) {$m_1+_{b}(m_2 +_{c} m_3)$};
-\node (E) at (5.5,0.5) {$(x_1 \odot x_2) \odot x_3 \in F((m_1+_{b} m_2)+_{c} m_3)$};
-\node (F) at (5.5,-0.5) {$x_1 \odot (x_2 \odot x_3) \in F(m_1+_{b} (m_2 +_{c} m_3))$};
+\node (E) at (5.5,0.5) {$(x_3 \odot x_2) \odot x_1 \in F((m_1+_{b} m_2)+_{c} m_3)$};
+\node (F) at (5.5,-0.5) {$x_3 \odot (x_2 \odot x_1) \in F(m_1+_{b} (m_2 +_{c} m_3))$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-together with an isomorphism $F(\kappa)((x_1 \odot x_2) \odot x_3) \cong (x_1 \odot (x_2 \odot x_3))$ between the decorations 
+together with an isomorphism $F(\kappa)((x_3 \odot x_2) \odot x_1) \cong (x_3 \odot (x_2 \odot x_1))$ between the decorations 
 %\begin{align*}
@@
 \end{thm}
+%%% Christina: note to self, now our functor factors through that specific Rex means that each category F(a) which later becomes the fibre comes with a specific choice of colimits.
+We do not know what this choice is, but of course such colimits in the fibres will be isomorphic to any other we may stumble upon!
 
@@
 in $\A$ along with the map $\tau\maps Fk(x)\to x'$ in $F(m')$ coming from the middle arrow above, namely an $F$-decorated cospan 2-morphism. 
-With these definitions, $\lE$ is indeed a double functor as in \cref{def:doublefun}: both $\lE_0$ and $\lE_1$ are functors that appropriately commute with sources and targets, and there exist globular 2-isomorphisms $\lE(M) \odot \lE(N) \simrightarrow\lE(M \odot N)$, $U_{\lE m} \simrightarrow\lE(U_m)$
+With these definitions, $\lE$ is indeed a double functor as in \cref{def:doublefun}: both $\lE_0$ and $\lE_1$ are functors that appropriately commute with sources and targets, and there exist globular 2-isomorphisms $\lE(N) \odot \lE(M) \simrightarrow\lE(N \odot M)$, $U_{\lE m} \simrightarrow\lE(U_m)$
 for any pair of composable horizontal 1-cells $M=\cspn{(a,\bot_a)}{(m,x)}{(b,\bot_b)}{}{}$ and $N=\cspn{(b,\bot_b)}{(n,y)}{(c,\bot_c)}{}{}$ and any object $m$ of $_L\lCsp(\inta F)$.
-Explicitly, $\mathbb{E}(M)\odot \mathbb{E}(N)$ is given as in \cref{eq:dcospanscomposition} via the pushout cospan and decoration
+Explicitly, $\mathbb{E}(N)\odot \mathbb{E}(M)$ is given as in \cref{eq:dcospanscomposition} via the pushout cospan and decoration
 \begin{equation}\label{eq:1}
@@
 \item{functors $\lF_0 \colon \lA_0 \to \lX_0$ and $\lF_1 \colon \lA_1 \to \lX_1$ such that $S \lF_1 = \lF_0 S$ and $T \lF_1 = \lF_0 T$, and}
-\item{for every composable pair of horizontal 1-cells $M$ and $N$ in $\lA$, a natural transformation $\phi_{M,N} \colon \lF(M) \odot \lF(N) \to \lF(M \odot N)$ called the \define{composite comparison} and for every object $a$ in $\lA$, a natural transformation $\phi_a \colon U_{\lF_0(a)} \to \lF_1(U_a)$ called the \define{unit comparison}.
+\item{for every composable pair of horizontal 1-cells $M$ and $N$ in $\lA$, a natural transformation $\phi_{M,N} \colon \lF(N) \odot \lF(M) \to \lF(N \odot M)$ called the \define{composite comparison} and for every object $a$ in $\lA$, a natural transformation $\phi_a \colon U_{\lF_0(a)} \to \lF_1(U_a)$ called the \define{unit comparison}.
 The components of each of these natural transformations are globular isomorphisms which satisfy coherence axioms analogous to those of a monoidal functor.}
@@
 that is, invertible globular 2-morphisms
-\[ \chi \maps (M_1\otimes N_1)\odot (M_2\otimes N_2) \xrightarrow{\sim}
-(M_1\odot M_2)\otimes (N_1\odot N_2)\]
+\[ \chi \maps (M_2\otimes N_2)\odot(M_1\otimes N_1)  \xrightarrow{\sim}
+(M_2\odot M_1)\otimes (N_2\odot N_1)\]
 \[ \mu \maps U_{A\otimes B} \xrightarrow{\sim} U_A \otimes U_B\]
@@
 		\begin{tikzpicture}\label{eq:braidingaxiom}
-			\node (A) at (0,1.5) {\footnotesize{$(M_1 \odot M_2) \otimes (N_1 \odot N_2)$}};
-			\node (A') at (0,0) {\footnotesize{$(M_1\otimes N_1) \odot (M_2\otimes N_2)$}};
-			\node (B) at (5,1.5) {\footnotesize{$(N_1\odot N_2) \otimes (M_1 \odot M_2)$}};
-			\node (B') at (5,0) {\footnotesize{$(N_1 \otimes M_1) \odot (N_2 \otimes M_2)$}};
+			\node (A) at (0,1.5) {\footnotesize{$(M_2 \odot M_1) \otimes (N_2 \odot N_1)$}};
+			\node (A') at (0,0) {\footnotesize{$ (M_2\otimes N_2)\odot (M_1\otimes N_1)$}};
+			\node (B) at (5,1.5) {\footnotesize{$(N_2\odot N_1) \otimes (M_2\odot M_1)$}};
+			\node (B') at (5,0) {\footnotesize{$ (N_2 \otimes M_2)\odot (N_1 \otimes M_1)$}};
 			%
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$(M_1 \odot M_2) \otimes (N_1 \odot N_2)$};
-\node (B) at (3,0) {$(N_1 \odot N_2) \otimes (M_1 \odot M_2)$};
-\node (C) at (0,-.75) {$(M_1 \otimes N_1) \odot (M_2 \otimes N_2)$};
-\node (D) at (3,-.75) {$(N_1 \otimes M_1) \odot (N_2 \otimes M_2)$};
+\node (A) at (0,0) {$(M_2 \odot M_1) \otimes (N_2 \odot N_1)$};
+\node (B) at (3,0) {$(N_2 \odot N_1) \otimes (M_2 \odot M_1)$};
+\node (C) at (0,-.75) {$(M_2 \otimes N_2) \odot (M_1 \otimes N_1)$};
+\node (D) at (3,-.75) {$(N_2 \otimes M_2) \odot (N_1 \otimes M_1)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
+{\chris Chai's in the definition of a monoidal double category have a different direction. Since it is an isomorphism it doesn't really change anything, but consider changing to keep them right}
 First of all, if we only consider the underlying cospans without their decorations, we obtain the following `flattened' commutative diagram in the symmetric monoidal double category $\lCsp(\A)$, where the top and the bottom cospans coincide:

### 2020-12-03 cospans.tex
minor edits in section 4

@@
 The (vertical) composition of two $F$-decorated cospans maps is
-\begin{displaymath}
+\begin{equation}\label{eq:verticalcompo}
  \begin{tikzcd}
@@
  \end{tikzcd}
-\end{displaymath}
+\end{equation}
 where if $\tau \colon F(h)(x) \to x'$ and $\tau' \colon F(h')(x') \to x''$ are the decoration morphisms, 
@@
 their composite $\beta\odot \alpha$ is horizontal cospan composition in $\A$
-\[
+\begin{equation}\label{eq:horizontalcompo}
 \begin{tikzpicture}[scale=1.5]
@@
 \end{tikzpicture}
-\]
+\end{equation}
 together with the decoration morphism $\tau_{\beta \odot \alpha} \colon F(h_1 +_g h_2)(y \odot x) \to (y' \odot x')$ given by the diagram:
@@
 
-As noted for example by Shulman \cite{Shulman2010}, any double category $\lX$ has a 
+As noted for example by Shulman \cite{Shulman2010},
+%%%Christina: this should be a much older, very well-known fact.
+I suggest for removal of reference completely (given that we describe this thing from scratch) or instead insert a much older reference than that.
+any double category $\lX$ has a 
+{\chris How come we changed from D to X as our basic letter for double cats?}
 \define{horizontal bicategory}, denoted $\bX$, in which:
@@
 A double category is `fibrant' if every vertical 1-morphism has a `companion' and a `conjoint'---concepts explained in \cref{def:companion}.
-Shulman \cite[Thm.\ 1.2]{Shulman2010} proved that when a double category $\lX$ is fibrant, any symmetrical monoidal structure on $\lX$ gives one on $\bX$.
+Shulman (\cref{Shulhorizontalbicat}) proved that when a double category $\lX$ is fibrant, any symmetrical monoidal structure on $\lX$ gives one on $\bX$.
 We can apply this to decorated cospans as follows:
@@
 We show that any vertical 1-morphism $f \maps a \to b'$ in $F\lCsp$ has a companion and a conjoint.  This horizontal 1-cell $\hat{f}$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a$};
-\node (B) at (1,0) {$b$};
-\node (C) at (2,0) {$b$};
-\node (D) at (1,-0.5) {$\bot_{b} \in F(b)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$f$} (B)
-(C) edge node[above]{$1$} (B);
-\end{tikzpicture}
-\]
-is a companion of $f$ because the following two 2-morphisms, having $\hat{f}$ as
+\begin{displaymath}
+ a\xrightarrow{f}b\xleftarrow{1}b,\quad \bot_{b} \in F(b)
+\end{displaymath}
+%\[
+%\begin{tikzpicture}[scale=1.5]
+%\node (A) at (0,0) {$a$};
+%\node (B) at (1,0) {$b$};
+%\node (C) at (2,0) {$b$};
+%\node (D) at (1,-0.5) {$\bot_{b} \in F(b)$};
+%\path[->,font=\scriptsize,>=angle 90]
+%(A) edge node[above]{$f$} (B)
+%(C) edge node[above]{$1$} (B);
+%\end{tikzpicture}
+%\]
+where $\bot_b$ is the trivial decoration as in \cref{eq:UFCsp}, is a companion of $f$ because the following two 2-morphisms, having $\hat{f}$ as
 source and target:
@@
 \]
-satisfy the equations required of a companion:
+{\chris The decoration morphisms should be both isomorphisms due to pseudofunctoriality of F...}
+satisfy the equations required of a companion \cref{eq:CompanionEq}, using vertical \cref{eq:verticalcompo} and horizontal \cref{eq:horizontalcompo} composition of 2-cells in this double category:
 \[
@@
 The conjoint of $f$ is given by this horizontal 1-cell $\check{f}$, which is just the opposite of the companion above:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$b$};
-\node (B) at (1,0) {$b$};
-\node (C) at (2,0) {$a$};
-\node (D) at (4,0) {$\bot_{b} \in F(b)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$1$} (B)
-(C) edge node[above]{$f$} (B);
-\end{tikzpicture}
-\]
+\begin{displaymath}
+ b\xrightarrow{1}b\xleftarrow{f}b,\quad \bot_{b} \in F(b)
+\end{displaymath}
+%\[
+%\begin{tikzpicture}[scale=1.5]
+%\node (A) at (0,0) {$b$};
+%\node (B) at (1,0) {$b$};
+%\node (C) at (2,0) {$a$};
+%\node (D) at (4,0) {$\bot_{b} \in F(b)$};
+%\path[->,font=\scriptsize,>=angle 90]
+%(A) edge node[above]{$1$} (B)
+%(C) edge node[above]{$f$} (B);
+%\end{tikzpicture}
+%\]
 Just as $\hat{f}$ obeys the equations required of a companion, $\check{f}$ obeys the equations required of a conjoint.
@@
 CHECK THAT OUR SORT OF EQUIVALENCE OF SYMMETRIC MONOIDAL DOUBLE CATEGORIES IS REALLY THAT USED BY HANSEN AND SHULMAN!!!
-{\chris In the proof above, we probably need isomorphism. Does it follow?}
 
@@
 
-{\chris Shouldn't we give Shulman's result that the horizontal bicategory of a symmetric monoidal double category is symmetric monoidal?}
+\begin{thm}{\cite[Theorem 1.2]{Shulman2010}}
+\label{Shulhorizontalbicat}
+If $\lD$ is a fibrant monoidal double category, then its horizontal bicategory $\bD$ is a monoidal bicategory. If $\lD$ is braided or symmetric, then so is $\bD$. 
+\end{thm}
 

### 2020-12-03 cospans.tex
fixed refs to Shulman, changed \lA, \lX to \lD, \lE.

@@
 % in LaTeX
-% 2020/12/2
+% 2020/12/3
 
@@
 
-As noted for example by Shulman \cite{Shulman2010},
-%%%Christina: this should be a much older, very well-known fact.
-I suggest for removal of reference completely (given that we describe this thing from scratch) or instead insert a much older reference than that.
-any double category $\lX$ has a 
-{\chris How come we changed from D to X as our basic letter for double cats?}
-\define{horizontal bicategory}, denoted $\bX$, in which:
+As discussed for example by Shulman \cite{Shulman2010}, any double category $\lD$ has a 
+\define{horizontal bicategory}, denoted $\bD$, in which:
 \begin{itemize}
-\item objects are objects of $\lX$,
-\item morphisms are horizontal 1-cells of $\lX$,
-\item 2-morphisms are \define{globular} 2-morphisms of $\lX$, meaning 2-morphisms whose source and target vertical 1-morphisms are identities,
-\item composition of morphisms is given by horizontal composition of horizontal 1-cells in $\lX$,
+\item objects are objects of $\lD$,
+\item morphisms are horizontal 1-cells of $\lD$,
+\item 2-morphisms are \define{globular} 2-morphisms of $\lD$, meaning 2-morphisms whose source and target vertical 1-morphisms are identities,
+\item composition of morphisms is given by horizontal composition of horizontal 1-cells in $\lD$,
 \item vertical and horizontal composition of 2-morphisms are given by vertical and horizontal
-composition of 2-morphisms in $\lX$.
+composition of 2-morphisms in $\lD$.
 \end{itemize}
-The bicategory $\bX$ has a \define{decategorification}, a category $\X$ in which:
+The bicategory $\bD$ has a \define{decategorification}, a category $\D$ in which:
 \begin{itemize}
-\item objects are objects of $\bX$,
-\item morphisms are isomorphism classes of 1-morphisms of $\bX$.   
+\item objects are objects of $\bD$,
+\item morphisms are isomorphism classes of 1-morphisms of $\bD$.   
 \end{itemize}
@@
 A double category is `fibrant' if every vertical 1-morphism has a `companion' and a `conjoint'---concepts explained in \cref{def:companion}.
-Shulman (\cref{Shulhorizontalbicat}) proved that when a double category $\lX$ is fibrant, any symmetrical monoidal structure on $\lX$ gives one on $\bX$.
+Shulman (\cref{Shulhorizontalbicat}) proved that when a double category $\lD$ is fibrant, any symmetrical monoidal structure on $\lD$ gives one on $\bD$.
 We can apply this to decorated cospans as follows:
@@
 Define the symmetric monoidal bicategory $_L\bCsp(\inta F)$ as in \cref{thm:equiv}.
-Then there is an isomorphism of symmetric monoidal bicategories
+Then there is an equivalence of symmetric monoidal bicategories
 \[      F\bCsp \simeq {}_L \bCsp(\inta F)   \]
@@
 
-\begin{proof} Hansen and Shulman \cite{HS} showed that the passage from symmetric monoidal double categories to symmetric monoidal bicategories is  functorial in a suitable sense, implying
-that an equivalence of symmetric monoidal double categories $\lX \simeq \lY$ gives an equivalence of symmetric monoidal bicategories $\bX \simeq \bY$.
-Since the process of decategorifying a bicategory merely discards 2-morphisms and takes isomorphism classes of 1-morphisms, the equivalence of symmetric monoidal bicategories $\bX \simeq \bY$ in turn induces an equivalence of symmetric monoidal categories $\X \simeq \Y$.
+\begin{proof} 
+Hansen and Shulman \cite{HS} showed that the passage from symmetric monoidal double categories to symmetric monoidal bicategories is  functorial in a suitable sense, implying that an equivalence of symmetric monoidal double categories $\lD \simeq \lD'$ gives an equivalence of symmetric monoidal bicategories $\bD \simeq \bD'$.
+Since the process of decategorifying a bicategory merely discards 2-morphisms and takes isomorphism classes of 1-morphisms, the equivalence of symmetric monoidal bicategories $\bD \simeq \bD'$ in turn induces an equivalence of symmetric monoidal categories $\D \simeq \D'$.
 Thus, the theorem follows from \cref{thm:equiv}.
 \end{proof}
-
-CHECK THAT OUR SORT OF EQUIVALENCE OF SYMMETRIC MONOIDAL DOUBLE CATEGORIES IS REALLY THAT USED BY HANSEN AND SHULMAN!!!
-
-%Let $F \maps \A \to \Cat$ be a symmetric lax monoidal pseudofunctor.
-Then by Theorem \cref{DC} of the previous section, we get a symmetric monoidal double category $F\lCsp$.
-This symmetric monoidal double category has:
-%\begin{enumerate}
-%\item{objects as those of $\A$,}
-%\item{vertical 1-morphisms as morphisms of $\A$,}
-%\item{horizontal 1-cells as pairs:
-%\[
-%\begin{tikzpicture}[scale=1.5]
-%\node (A) at (0,0) {$a$};
-%\node (B) at (1,0) {$c$};
-%\node (C) at (2,0) {$b$};
-%\node (D) at (4,0) {$d \in F(c)$};
-%\path[->,font=\scriptsize,>=angle 90]
-%(A) edge node[above]{$i$} (B)
-%(C) edge node[above]{$o$} (B);
-%\end{tikzpicture}
-%\]
-%and}
-%\item{2-morphisms as maps of cospans in $\A$
-%\[
-%\begin{tikzpicture}[scale=1.5]
-%\node (A) at (0,0.5) {$a$};
-%\node (A') at (0,-0.5) {$a'$};
-%\node (B) at (1,0.5) {$c$};
-%\node (C) at (2,0.5) {$b$};
-%\node (C') at (2,-0.5) {$b'$};
-%\node (D) at (1,-0.5) {$c'$};
-%\node (E) at (3,0.5) {$d \in F(c)$};
-%\node (F) at (3,-0.5) {$d' \in F(c')$};
-%\path[->,font=\scriptsize,>=angle 90]
-%(A) edge node[above]{$$} (B)
-%(C) edge node[above]{$$} (B)
-%(A) edge node[left]{$f$} (A')
-%(C) edge node[left]{$g$} (C')
-%(A') edge node {$$} (D)
-%(C') edge node {$$} (D)
-%(B) edge node [left] {$h$} (D);
-%\end{tikzpicture}
-%\]
-%together with a morphism $\tau \maps F(h)(d) \to d'$ in $F(c')$.}
-%\end{enumerate}
 
@@
 \subsection{Double categories}\label{sec:doublecats}
-For double categories we follow the notation of our paper on structured cospans \cite{BC}, which in turn follows that of Shulman \cite{Shulman2010}.
+
+For double categories we follow the notation of our paper on structured cospans \cite{BC}, which in turn follows that of Hansen and Shulman \cite{HS,Shulman2010}.
 
@@
 
-%\begin{defn}
-%Let $\lD$ be a pseudo double category.
-Then the $\textbf{horizontal bicategory}$ of $\lD$, which we denote as $H(\lD)$, is the bicategory consisting of objects of $\lD$, morphisms that are horizontal 1-cells of $\lD$ and 2-morphisms that are globular 2-morphisms of $\lD$.
-%\end{defn}
 \begin{defn}\label{def:doublefun}
-Given double categories $\lA$ and $\lX$, a \define{double functor} $\lF \colon\lA \to \lX$ consists of:
+Given double categories $\lD$ and $\lE$, a \define{double functor} $\lF \maps \lD \to \lE$ consists of:
 \begin{itemize}
-\item{functors $\lF_0 \colon \lA_0 \to \lX_0$ and $\lF_1 \colon \lA_1 \to \lX_1$ such that $S \lF_1 = \lF_0 S$ and $T \lF_1 = \lF_0 T$, and}
-\item{for every composable pair of horizontal 1-cells $M$ and $N$ in $\lA$, a natural transformation $\phi_{M,N} \colon \lF(N) \odot \lF(M) \to \lF(N \odot M)$ called the \define{composite comparison} and for every object $a$ in $\lA$, a natural transformation $\phi_a \colon U_{\lF_0(a)} \to \lF_1(U_a)$ called the \define{unit comparison}.
+\item{functors $\lF_0 \maps \lD_0 \to \lE_0$ and $\lF_1 \maps \lD_1 \to \lE_1$ such that $S \lF_1 = \lF_0 S$ and $T \lF_1 = \lF_0 T$, and}
+\item{for every composable pair of horizontal 1-cells $M$ and $N$ in $\lD$, a natural transformation $\phi_{M,N} \maps \lF(N) \odot \lF(M) \to \lF(N \odot M)$ called the \define{composite comparison} and for every object $a$ in $\lD$, a natural transformation $\phi_a \maps U_{\lF_0(a)} \to \lF_1(U_a)$ called the \define{unit comparison}.
 The components of each of these natural transformations are globular isomorphisms which satisfy coherence axioms analogous to those of a monoidal functor.}
@@
 \begin{defn}
-Given double functors $(\lF,\phi),(\mathbb{G},\psi) \colon \lA \to \lX$, a \define{double natural transformation} $\alpha \colon \lF \Rightarrow \mathbb{G}$ consists of natural transformations $\alpha_0 \colon \lF_0 \Rightarrow \mathbb{G}_0$ and $\alpha_1 \colon \lF_1 \Rightarrow \mathbb{G}_1$ such that:
+Given double functors $(\lF,\phi),(\mathbb{G},\psi) \maps \lD \to \lE$, a \define{double natural transformation} $\alpha \maps \lF \Rightarrow \mathbb{G}$ consists of natural transformations $\alpha_0 \maps \lF_0 \Rightarrow \mathbb{G}_0$ and $\alpha_1 \maps \lF_1 \Rightarrow \mathbb{G}_1$ such that:
 \begin{itemize}
-\item{$S(\alpha_M) = \alpha_{S(M)}$ and $T(\alpha_M) = \alpha_{T(M)}$ for all horizontal 1-cells $M$ of $\lA$,}
-\item{$\alpha \circ \phi_{M,N} = \psi \circ (\alpha_M \odot \alpha_N)$ for all composable pairs $M$ and $N$ of horizontal 1-cells in $\lA$, and}
-\item{$\alpha \circ \phi_a = \psi_a \circ \alpha$ for all objects $a$ of $\lA$.}
+\item{$S(\alpha_M) = \alpha_{S(M)}$ and $T(\alpha_M) = \alpha_{T(M)}$ for all horizontal 1-cells $M$ of $\lD$,}
+\item{$\alpha \circ \phi_{M,N} = \psi \circ (\alpha_M \odot \alpha_N)$ for all composable pairs $M$ and $N$ of horizontal 1-cells in $\lD$, and}
+\item{$\alpha \circ \phi_a = \psi_a \circ \alpha$ for all objects $a$ of $\lD$.}
 \end{itemize} 
-%$S(\alpha_M) = \alpha_{S(M)}$ and $T(\alpha_M) = \alpha_{T(M)}$, and for two composable horizontal 1-cells $M$ and $N$ of $\lA$, $\alpha \circ \phi_{M,N} = \psi \circ (\alpha_M \odot \alpha_N)$ and $\alpha \circ \phi_a = \psi_a \circ \alpha$.
+%$S(\alpha_M) = \alpha_{S(M)}$ and $T(\alpha_M) = \alpha_{T(M)}$, and for two composable horizontal 1-cells $M$ and $N$ of $\lD$, $\alpha \circ \phi_{M,N} = \psi \circ (\alpha_M \odot \alpha_N)$ and $\alpha \circ \phi_a = \psi_a \circ \alpha$.
 The double natural transformation $\alpha$ is a \define{double natural isomorphism} if both $\alpha_0$ and $\alpha_1$ are natural isomorphisms.
@@
 %\begin{defn}
-%A double functor $\lF \maps \lA \to \lX$ is \define{strong} if the comparison and unit constraints are globular isomorphisms, meaning that for each composable pair of horizontal 1-cells $M$ and $N$ we have a natural isomorphism $$\lF_{M,N} \maps \lF(M) \odot \lF(N) \xrightarrow{\sim} \lF(M \odot N)$$and for each object $a \in \lA$ a natural isomorphism $$\lF_a \maps \hat{U}_{\lF(a)} \xrightarrow{\sim} \lF(U_a).$$
+%A double functor $\lF \maps \lD \to \lE$ is \define{strong} if the comparison and unit constraints are globular isomorphisms, meaning that for each composable pair of horizontal 1-cells $M$ and $N$ we have a natural isomorphism $$\lF_{M,N} \maps \lF(M) \odot \lF(N) \xrightarrow{\sim} \lF(M \odot N)$$ and for each object $a \in \lD$ a natural isomorphism $$\lF_a \maps \hat{U}_{\lF(a)} \xrightarrow{\sim} \lF(U_a).$$
 %\end{defn}
 
-%Following the notation of Shulman \cite{Shulman2010}, given a double category $\lA$, we write $_f \lA_g(M,N)$ for the set of 2-morphisms in $\lA$ of the form:
+%Following the notation of Shulman \cite{Shulman2010}, given a double category $\lD$, we write $_f \lD_g(M,N)$ for the set of 2-morphisms in $\lD$ of the form:
 %\[
@@
 \begin{defn}\label{def:fullfaithful}
-A double functor $\lF \maps \lA \to \lX$ is \define{full} (resp.\ \define{faithful}) if $\lF_0 \maps \lA_0 \to \lX_0$ is full (resp.\ faithful) and each map 
-\[   lF_1 \maps _f \lA_g(M,N) \to {_{\lF(f)} \lX_{\lF(g)}}(\lF(M),\lF(N))\] 
-is surjective (respectively, injective), where $_f \lA_g(M,N)$ is set of 2-morphisms in $\A$ whose horizontal source is $M$ and whose horizontal target is $N$, and similarly for ${_{\lF(f)} \lX_{\lF(g)}}(\lF(M),\lF(N))$.
+A double functor $\lF \maps \lD \to \lE$ is \define{full} (resp.\ \define{faithful}) if $\lF_0 \maps \lD_0 \to \lE_0$ is full (resp.\ faithful) and each map 
+\[   lF_1 \maps _f \lD_g(M,N) \to {_{\lF(f)} \lE_{\lF(g)}}(\lF(M),\lF(N))\] 
+is surjective (respectively, injective), where $_f \lD_g(M,N)$ is set of 2-morphisms in $\A$ whose horizontal source is $M$ and whose horizontal target is $N$, and similarly for ${_{\lF(f)} \lE_{\lF(g)}}(\lF(M),\lF(N))$.
 \end{defn}
@@
 \begin{defn}\label{def:essentiallysurj}
-A double functor $\lF \maps \lA \to \lX$ is \define{essentially surjective} if we can simultaneously make the following choices:
+A double functor $\lF \maps \lD \to \lE$ is \define{essentially surjective} if we can simultaneously make the following choices:
 \begin{itemize}
-\item For each object $x \in \lX$, we can find an object $a \in \lA$ together with a vertical 1-isomorphism $\alpha_x \maps \lF(a) \to x$, and
-\item For each horizontal 1-cell $N \maps x_1 \to x_2$  of $\lX$, we can find a horizontal 1-cell $M \maps a_1 \to a_2$ of $\lA$ and a 2-isomorphism $a_{N} \colon \lF(M) \to N$ in $\lX$ as in the following diagram:
+\item For each object $x \in \lE$, we can find an object $a \in \lD$ together with a vertical 1-isomorphism $\alpha_x \maps \lF(a) \to x$, and
+\item For each horizontal 1-cell $N \maps x_1 \to x_2$  of $\lE$, we can find a horizontal 1-cell $M \maps a_1 \to a_2$ of $\lD$ and a 2-isomorphism $a_{N} \colon \lF(M) \to N$ in $\lE$ as in the following diagram:
 \[
@@
 \begin{defn}
-Two double functors $\lF \colon \lA \to \lX$ and $\mathbb{G} \colon \lX \to \lA$ form a \define{double equivalence} if there exist double natural transformations $\mathbb{G} \lF \cong 1_\lA$ and $\lF \mathbb{G} \cong 1_\lX$.
+Two double functors $\lF \colon \lD \to \lE$ and $\lG \colon \lE \to \lD$ form a \define{double equivalence} if there exist double natural transformations $\mathbb{G} \lF \cong 1_\lD$ and $\lF \mathbb{G} \cong 1_\lE$.
 \end{defn}
@@
 
-\begin{thm}{\cite[Thm.\ 7.8]{Shulman2010}}
+\begin{thm}{\cite[Thm.\ 7.8]{Shulman2008}}
 \label{ShulDubEquiv}
-A pseudo double functor $\lF \maps \lA \to \lX$ is part of a double equivalence if and only if it is full, faithful and essentially surjective.
+A pseudo double functor $\lF \maps \lD \to \lE$ is part of a double equivalence if and only if it is full, faithful and essentially surjective.
 \end{thm}
@@
 \begin{defn}\label{defn:monoidal_double_functor}
-Given symmetric monoidal double categories $\lA$ and $\lX$, a \define{symmetric monoidal double functor} $\lF \colon \lA \to \lX$ is a double functor $\lF$ together with transformations $\theta \colon {\otimes \circ (\lF,\lF)} \to \lF \circ \otimes$ and $\theta_U \colon 1_\lX \to \lF \circ 1_\lA$ that satisfy the usual coherence axioms for a symmetric monoidal functor with respect to $\otimes$.
+Given symmetric monoidal double categories $\lD$ and $\lE$, a \define{symmetric monoidal double functor} $\lF \colon \lD \to \lE$ is a double functor $\lF$ together with transformations $\theta \colon {\otimes \circ (\lF,\lF)} \to \lF \circ \otimes$ and $\theta_U \colon 1_\lE \to \lF \circ 1_\lD$ that satisfy the usual coherence axioms for a symmetric monoidal functor with respect to $\otimes$.
 \end{defn}
@@
 WE NEED TO SAY BRIEFLY WHAT A SYMMETRIC MONOIDAL DOUBLE ISOMORPHISM, IF WE USE THIS CONCEPT IN OUR BIG RESULT, \cref{thm:equiv}.
-CLAIM: $\lA$ and $\lX$ be symmetric monoidal double categories and let $\lF \maps \lA \to \lX$ be a symmetric monoidal double functor.
-If $\lF$ is part of a double equivalence, then $\lF$ is in fact part of a symmetric monoidal double equivalence, and $\lA$ and $\lX$ are equivalent as symmetric monoidal double categories.
+CLAIM: $\lD$ and $\lE$ be symmetric monoidal double categories and let $\lF \maps \lD \to \lE$ be a symmetric monoidal double functor.
+If $\lF$ is part of a double equivalence, then $\lF$ is in fact part of a symmetric monoidal double equivalence, and $\lD$ and $\lE$ are equivalent as symmetric monoidal double categories.
 
 \begin{defn}\label{def:companion}
-  Let $\lA$ be a double category and $f\maps A\to B$ a vertical
+  Let $\lD$ be a double category and $f\maps A\to B$ a vertical
   1-morphism.  A \textbf{companion} of $f$ is a horizontal 1-cell
@@
   A \textbf{conjoint} of $f$, denoted $\fchk \maps B\to A$, is a
-  companion of $f$ in the double category $\lA^{h\cdot\mathrm{op}}$
+  companion of $f$ in the double category 
   obtained by reversing the horizontal 1-cells, but not the vertical
-  1-morphisms, of $\lA$.
+  1-morphisms, of $\lD$.
 \end{defn}
 \noindent
-%In a pseudo double category, the second equation above requires an insertion of unit isomorphisms to make sense due to horizontal composition only holding up to isomorphism.
 
@@
 We say that a double category is \textbf{fibrant} if every vertical
-1-morphism has both a companion and a conjoint.  % and \define{isofibrant} if every vertical 1-isomorphism has both a companion and a conjoint.
+1-morphism has both a companion and a conjoint.  
 \end{defn}
 
-\begin{thm}{\cite[Theorem 1.2]{Shulman2010}}
+\begin{thm}{\cite[Theorem 1.1]{HS}}
 \label{Shulhorizontalbicat}
@@
 \]
-{\chris Chai's in the definition of a monoidal double category have a different direction. Since it is an isomorphism it doesn't really change anything, but consider changing to keep them right}
+{\chris $\chi$'s in the definition of a monoidal double category have a different direction. Since it is an isomorphism it doesn't really change anything, but consider changing to keep them right}
 First of all, if we only consider the underlying cospans without their decorations, we obtain the following `flattened' commutative diagram in the symmetric monoidal double category $\lCsp(\A)$, where the top and the bottom cospans coincide:

### 2020-12-04 cospans.tex
a few small changes

@@
 
-All this so far is boringly familiar.  More interesting is the symmetric monoidal double
-category of open dynamical systems.
+All this so far is very similar to the previous examples.
+More interesting is the symmetric monoidal double category of open dynamical systems.
 A dynamical system is a vector field from the perspective of a system of first-order ordinary differential equation.
@@
 
-%{\chris The rest is not done yet...} %%%Christina I have no clue where this comment came from!
-
-We now show that open dynamical systems of this nature are an example of open systems that are able to be characterized by decorated cospans but not structured cospans.
+We now show that while open dynamical systems of this sort are morphisms in a decorated cospan category, they do not arise from a structured cospan category via \cref{thm:equiv}.
 
@@
 
-We conclude with some questions:
-
-\begin{itemize}
-\item We have given conditions under which a decorated cospan double category $F \lCsp$ is
-equivalent to a structured cospan double category.    Is every structured cospan double category 
-equivalent to a decorated cospan double category?
-\item What are some interesting examples of decorated cospan double categories that are not structured cospan double categories?
-A candidate appears in the work of Pollard and the first author \cite{BP}.
-They construct a decorated cospan category $\Dynam$ where objects are finite sets and a morphism from $a$ to $b$ is a cospan of finite sets $a \rightarrow m \leftarrow b$ where the apex $m$ is decorated with a vector field on $\R^m$ whose coefficients are polynomial functions of the standard coordinates on this space.
-
-They constructed this decorated cospan category via Fong's original formalism, using a lax symmetric monoidal functor $F \maps (\Fin\Set, +) \to (\Set, \times)$.
-However, composing this with the inclusion $(\Set, \times) \to (\Cat, \times)$ mapping sets to discrete categories, we get the data needed to create a decorated cospan double category $\lD\mathbf{ynam}$.
-We believe that this is not equivalent to a structured cospan double category, but can this be proved?
-If so, can this example be generalized?
-\end{itemize}
+We have given conditions under which a decorated cospan double category is
+equivalent to a structured cospan double category.
+The converse question is also interesting: is every structured cospan double category equivalent to a decorated cospan double category?
+SAY STUFF!!!
 
@@
 
-\section{}
+\section{Definitions}
 In this appendix, we gather some well-known concepts required to make the material self-contained, as well as references to more detailed expositions.
@@
 \end{equation}
-subject to coherence conditions. 
-%%% Give reference describing these conditions!!!
-In particular, pseudonaturality of the monoidal structure means that it comes with isomorphisms (natural in $f,g$)
+subject to coherence conditions listed in \cite[Definition 2]{DayStreet}.
+In particular, pseudonaturality of the monoidal structure means that it comes with isomorphisms of this form:
 \begin{equation}\label{eq:pseudonaturality}
@@
 \end{equation}
+ natural in $f$ and $g$.
 A \define{braided lax monoidal} pseudofunctor between braided monoidal bicategories comes with an appropriate invertible modification with components %$F(\beta_{a,b})\circ \phi_{a,b}\cong\phi_{b,a}\circ \beta_{Fa,Fb}$.
@@
 \subsection{Fibrations}\label{sec:fibrations}
+
 Basic material regarding the theory of fibrations can be found, for example, in \cite{Borc,Gray}.
-Recall that a functor $U \maps \X \to \A$ is an \textbf{opfibration} if for every $x\in\X$ with $U(x)=a$ and $f \maps a \to b$ in $\A$, there exists a \textbf{cocartesian lifting} of $x$ along $f$, namely a morphism $\beta$ in $\X$ with domain $x$ above $f$ with the following universal property: for any $g\maps b\to b'$ in $\A$ and $\gamma\maps x\to y'$ in $\X$ above the composite $g\circ f$, there exists a unique $\delta\maps y\to y'$ such that $U(\delta)=g$ and $\gamma=\delta\circ\beta$ as shown below
+Recall that a functor $U \maps \X \to \A$ is an \textbf{opfibration} if for every $x\in\X$ with $U(x)=a$ and $f \maps a \to b$ in $\A$, there exists a \textbf{cocartesian lifting} of $f$ to $x$, namely a morphism $\beta$ in $\X$ with domain $x$ with $U(\beta) = f$ and the following universal property: for any $g\maps b\to b'$ in $\A$ and $\gamma\maps x\to y'$ in $\X$ above the composite $g\circ f$, there exists a unique $\delta\maps y\to y'$ such that $U(\delta)=g$ and $\gamma=\delta\circ\beta$ as shown below
 \begin{displaymath}
@@
 && b' &&\\
-a\ar[r]_-{f=U\beta} \ar[urr]^-{g\circ f=U\gamma}
+a\ar[r]_-{f=U(\beta)} \ar[urr]^-{g\circ f=U(\gamma)}
  & b \ar[ur]_-g && \textrm{in }\A}
@@
 The category $\X$ is called the \textbf{total} category and $\A$ is called the \textbf{base} category of the opfibration.
-For any $a\in\A$, the \textbf{fibre category} $\X_a$ consists of all objects that map to $a$ and vertical morphisms between them, i.e.
-mapping to $1_a$.
-Assuming the axiom of choice, we may select a cocartesian arrow over each $f\maps a\to b$ in $\A$ and $x\in\X _a$, denoted by $\mathrm{Cocart}(f,x)\maps x\to f_!(x)$, rendering $U$ a so-called \textbf{cloven} opfibration.
-This choice induces \textbf{reindexing functors} $f_!\maps\X _a\to\X _b$ between the fibre categories, which by the liftings universal property adhere to natural isomorphisms $(1_a)_!\cong1_{\X _a}$ and $(f\circ g)_!\cong f_!\circ g_!$.
-If these isomorphisms are equalities, we have the notion of a \textbf{split} opfibration.
-We chose to primarily present this dual notion to \define{fibration} due to the current work's needs.
-
-Let $\OpFib(\A)$ denote the 2-subcategory of the slice 2-category $\Cat/ \A$ of opfibrations over $\A$, functors that preserve cocartesian liftings and natural transformations with vertical components.
+For any $a\in\A$, the \textbf{fibre category} $\X_a$ consists of all objects that map to $a$ and \define{vertical} morphisms between them, i.e., morphisms mapping to $1_a$.
+
+Assuming the axiom of choice, we may select a cocartesian lifting of each morphism $f\maps a\to b$ in $\A$ to each $x\in\X _a$, denoted by $\mathrm{Cocart}(f,x)\maps x\to f_!(x)$, rendering $U$ a so-called \textbf{cloven} opfibration.
+This choice induces \textbf{reindexing functors} $f_!\maps\X _a\to\X _b$ between the fibre categories, which by the lifting's universal property come equipped with natural isomorphisms $(1_a)_!\cong 1_{\X _a}$ and $(f\circ g)_!\cong f_!\circ g_!$.
+With the help of these, any cloven opfibration $U \maps \X \to \A$ gives a pseudofunctor $F \maps \A \to \Cat$, where $\A$ viewed as a 2-category with trivial 2-cells, $F(a) = \X_a$ for each object $a \in \A$, and $F(f) = f_!$ for each morphism $f$ in $\A$.
+
 In fact, there is a 2-equivalence between opfibrations and pseudofunctors induced by the so-called `Grothendieck construction'.
+Let $\OpFib(\A)$ denote the 2-subcategory of the slice 2-category $\Cat/ \A$ of opfibrations over $\A$, functors that preserve cocartesian liftings, and natural transformations with vertical components.
 \begin{defn}\label{def:GrothCat}
@@
 \end{defn}
-The above in fact provides the one direction of the following well-known equivalence.
+The constructions sketched so far---the Grothendieck construction and the construction of a pseudofunctor into $\Cat$ from a cloven opfibration---are the two halves of the following equivalence.
 
@@
 \begin{enumerate}
-\item Every opfibration $U \maps \X \to \A$ gives rise to a pseudofunctor $\A \to \Cat$.
-\item Every pseudofunctor $F \maps \A \to \Cat$ gives rise to  an opfibration $\maps \inta F\to\A$.
+\item Every opfibration $\X \to \A$ gives rise to a pseudofunctor $\A \to \Cat$.
+\item Every pseudofunctor $\A \to \Cat$ gives rise to an opfibration $\inta F \to\A$.
 \item The above correspondences yield an equivalence of 2-categories 
@@
 \noindent
-Unpacking this definition one obtains a number of diagrams that can be found after \cite[Definition 2.4]{HS}.
+Unpacking this definition, one obtains a number of diagrams which can be found after \cite[Definition 2.4]{HS}.
 

### 2020-12-04 cospans.tex
changed a few identities

@@
 (C) edge node[above]{$$} (B)
-(A) edge node[left]{$\id_a$} (A')
-(C) edge node[right]{$\id_d$} (C')
+(A) edge node[left]{$1_a$} (A')
+(C) edge node[right]{$1_d$} (C')
 (A') edge node {$$} (D)
@@
 {\chris Should we give more details here?}
-Similarly, for units $U_{a+b}$ and $U_a\ot U_b$ it is easy to see that as cospans they are both the identity $\id:a+b\to a+b\leftarrow a+b:\id$, and there is a canonical isomorphism between their trivial decorations \cref{eq:UFCsp}, namely $F(!_{a+b})\phi_0\cong\phi_{a,b}(F(!_a)\times F(!_b))(\phi_0\times\phi_0)$ via the structure isomorphisms for $(\phi,\phi_0)$.
+Similarly, for units $U_{a+b}$ and $U_a\ot U_b$ it is easy to see that as cospans they are both the identity $1_{a+b}:a+b\to a+b\leftarrow a+b:1_{a+b}$, and there is a canonical isomorphism between their trivial decorations \cref{eq:UFCsp}, namely $F(!_{a+b})\phi_0\cong\phi_{a,b}(F(!_a)\times F(!_b))(\phi_0\times\phi_0)$ via the structure isomorphisms for $(\phi,\phi_0)$.
 \begin{comment}
@@
 \end{equation}
-subject to coherence conditions listed in \cite[Definition 2]{DayStreet}.
+subject to coherence conditions listed in \cite[Definition 2]{DS}.
 In particular, pseudonaturality of the monoidal structure means that it comes with isomorphisms of this form:
@@
 			(c3) edge node[above]{$$} (b3)
-            (a2) edge node[left]{$\id$} (a3)
+            (a2) edge node[left]{$1$} (a3)
             (b2) edge node[left]{$\hat{\chi}$} (b3)
 %(b2) edge node[right]{$\tau_2$} (b3)
-			(c2) edge node[right]{$\id$} (c3)
+			(c2) edge node[right]{$1$} (c3)
             (a5) edge node[above]{$$} (b5)
 			(c5) edge node[above]{$$} (b5)
-            (a) edge node[left]{$\id$} (a5)
+            (a) edge node[left]{$1$} (a5)
             (b) edge node[left]{$\hat{\chi}$} (b5)
 %(b) edge node[right]{$\tau_4$} (b5)
-			(c) edge node[right]{$\id$} (c5)
+			(c) edge node[right]{$1$} (c5)
             (a6) edge node[above]{$$} (b6)

### 2020-12-04 cospans.tex
conclusions in progress

@@
 Diagrammatically,
-\begin{displaymath}
+\begin{equation}\label{eq:FtoL}
  F\maps\A\to\Cat\quad\mapsto\quad\begin{tikzcd}[baseline=.3]\inta F\ar[d,"U"'] \\ \A \end{tikzcd}\quad\mapsto\quad\begin{tikzcd}\A\ar[r,bend left,pos=.55,"L"]\ar[r,phantom,"\bot"description] & \inta F\ar[l,bend left,pos=.45,"U"]\end{tikzcd}
-\end{displaymath}
+\end{equation}
 describes the construction of the adjunction from the original $F$.
@@
 \section{Conclusions}\label{sec:conclusions}
-
-We have given conditions under which a decorated cospan double category is
-equivalent to a structured cospan double category.
+%%Christina: Or future directions or something?
+Unless we at some point conclude about something for the two frameworks, i.e they are close enough that we can choose which one to work with according to our application or something?
+I did something along those lines at the very end....
+
+We have given conditions under which a decorated cospan double category is isomorphic to a structured cospan double category, in \cref{thm:equiv}.
 The converse question is also interesting: is every structured cospan double category equivalent to a decorated cospan double category?
-SAY STUFF!!!
+The answer is similar to the previous one: affirmative, under certain conditions that essentially allow us to make the passage from an appropriate functor $L\colon \A\to \X$ to an appropriate pseudofunctor $F\colon \A\to\Cat$, namely in the reverse direction than the earlier passage \cref{eq:FtoL}.
+
+....
+
+{\chris I don't know if the part below should be included or not, perhaps it is too speculative and not dead important.}
+
+Even though for both \cref{thm:equiv} and the above described setting, the conditions required are only sufficient, they provide certain indication that under a suitable ``condition intersection'' in a sense, we could establish a functorial picture
+\begin{displaymath}
+\begin{tikzpicture}
+\node (A) { \{Lax monoidal pseudofunctors $(\A,+)\to(\Cat,\times)$\} };
+\node[below right=1.5 and 1.5 of A] (C)  { \{Symmetric monoidal double categories\} };
+\node[below=1  of A] (D)  { \{Special opfibrations\} };
+\node[below=2  of A] (E)  { \{Special laris\} };
+\node[below=3 of A] (B)  { \{ Finitely cocomplete functors $A\to\X$\} };
+\node[below=.05 of D] {$\cong$};
+\path[->,font=\scriptsize]
+(A) edge[bend left] node[above,sloped]{$F\mapsto F\lCsp$}  (C)
+(D) edge (A)
+(E) edge (B)
+(B) edge[bend right] node[below,sloped]{$L\mapsto {}_{L}\lCsp$} (C);
+\end{tikzpicture}
+\end{displaymath}
+with an actual natural isomorphism in the middle.
+This would imply that starting from an appropriate middle ground, employing the structured or the decorated cospan formalism is actually the same.
+We leave such considerations for future work.
 

### 2020-12-04 cospans.tex
first take on conclusions

@@
 The converse question is also interesting: is every structured cospan double category equivalent to a decorated cospan double category?
-The answer is similar to the previous one: affirmative, under certain conditions that essentially allow us to make the passage from an appropriate functor $L\colon \A\to \X$ to an appropriate pseudofunctor $F\colon \A\to\Cat$, namely in the reverse direction than the earlier passage \cref{eq:FtoL}.
-
-....
-
-{\chris I don't know if the part below should be included or not, perhaps it is too speculative and not dead important.}
+The answer is similar to the previous one: affirmative, under certain conditions that allow us to make the passage from an appropriate functor $L\colon \A\to \X$ to an appropriate pseudofunctor $F\colon \A\to\Cat$, namely in the reverse direction of the earlier \cref{eq:FtoL}.
+
+Let us now give a sketch of the relevant story.
+Suppose $\A$ and $\X$ have finite colimits and $L\maps\A\to\X$ is a finite-colimit preserving functor -- which by \cref{thm:SC} are the required conditions for constructing the symmetric monoidal double category of structured cospans.
+If $L$ has a right adjoint `left inverse' (meaning the unit is the identity) $U\maps\X\to\A$, which moreover strictly preserves the choice of pushouts in $\A$ and $\X$, it can be shown\footnote{This will appear in the forthcoming paper \cite{CV}.} that $U$ is an opfibration.
+Consequently, $U$ corresponds to a pseudofunctor $F\colon \A\to\Cat$ by the reverse of the Grothendieck construction, i.e.
+the second part of \cref{thm:Grothendieck}.
+Furthermore, if $U$ preserves finite coproducts, by the special case of the cocartesian monoidal Grothendieck construction discussed under \cref{lem:MonGroth}, the corresponding pseudofunctor $F$ has a lax monoidal structure $(\A,+)\to(\Cat,\times)$.
+As a result, by \cref{DC}, $F$ has now enough structure to induce the symmetric monoidal double category of decorated cospans $F\lCsp$, and further it can then be verified that it is isomorphic to the one of structured cospans.
+
+{\chris Give some sort of excuse why we don't do the full result here?? Because of missing - for us now - steps? Or other things?}
+
+To give a better sense of how this lax monoidal pseudofunctor $F\maps\A\to\Cat$ is constructed, $F(a)$ is defined to be the pre-image of $a$ under $U$, namely the category of all objects in $x\in\X$ such that $U(x)=a$ and morphisms $k\maps x\to y\in\X$ such that $U(k)=1_a$.
+Given a morphism $f\maps a\to b$, there is a functor $F(f)\maps F(a)\to F(b)$ that maps some $x$ to the following pushout
+\begin{displaymath}
+ \begin{tikzcd}
+La\ar[r,"Lf"]\ar[d,"\varepsilon_x"']\ar[dr,phantom,near end,"\ulcorner"] & Lb\ar[d] & \\
+x\ar[d,dotted]\ar[r] & x+_{La}Lb\ar[d,dotted] & \textrm{in }\X \\
+a\ar[r,"f"'] & b & \textrm{in }\A
+ \end{tikzcd}
+\end{displaymath}
+where $\varepsilon_x\colon LU(x)=L(a)\to x$ is the counit of $L\dashv U$. The fact that $U$ strictly preserves pushouts is necessary to show that the pushout is mapped, via $U$, directly down to $b$.
+
+{\chris I don't know if the part below should be included or not, perhaps it is too speculative and not dead important. 
+%If we keep, I can add a bit more information about what these special opfibs and special laris are, if we think it helps -- or not if it's OK now. 
+Bear in mind that me and Daniel are supposed to clarify the middle category isomorphism in this other paper too!}
 
@@
 \begin{tikzpicture}
-\node (A) { \{Lax monoidal pseudofunctors $(\A,+)\to(\Cat,\times)$\} };
-\node[below right=1.5 and 1.5 of A] (C)  { \{Symmetric monoidal double categories\} };
-\node[below=1  of A] (D)  { \{Special opfibrations\} };
-\node[below=2  of A] (E)  { \{Special laris\} };
-\node[below=3 of A] (B)  { \{ Finitely cocomplete functors $A\to\X$\} };
-\node[below=.05 of D] {$\cong$};
+\node [align=center,draw] (A) { Lax monoidal pseudofunctors \\ $(\A,+)\to(\Cat,\times)$};
+\node[below right=1.5 and 1.5 of A,align=center,draw] (C)  { Symmetric monoidal \\double categories };
+\node[below left=1 and .5  of A,draw] (D)  {Special opfibrations};
+\node[below left=2 and 1 of A,draw] (E)  {Special laris};
+\node[below=3 of A,align=center,draw] (B)  {Finitely cocomplete \\ functors $A\to\X$};
+\node[below=.01 of D] {\rotatebox{90}{$\cong$}};
 \path[->,font=\scriptsize]
-(A) edge[bend left] node[above,sloped]{$F\mapsto F\lCsp$}  (C)
+(A) edge node[above,sloped]{$F\mapsto F\lCsp$}  (C)
 (D) edge (A)
 (E) edge (B)
-(B) edge[bend right] node[below,sloped]{$L\mapsto {}_{L}\lCsp$} (C);
+(B) edge node[below,sloped]{$L\mapsto {}_{L}\lCsp$} (C);
 \end{tikzpicture}
@@
 with an actual natural isomorphism in the middle.
-This would imply that starting from an appropriate middle ground, employing the structured or the decorated cospan formalism is actually the same.
+This would imply that starting from an appropriate middle ground, employing the structured or the decorated cospan formalism is essentially the same.
 We leave such considerations for future work.

### 2020-12-04 cospans.tex
Changed the direction of the chi's

@@
 		\begin{tikzpicture}\label{eq:braidingaxiom}
-			\node (A) at (0,1.5) {\footnotesize{$(M_2 \odot M_1) \otimes (N_2 \odot N_1)$}};
-			\node (A') at (0,0) {\footnotesize{$ (M_2\otimes N_2)\odot (M_1\otimes N_1)$}};
-			\node (B) at (5,1.5) {\footnotesize{$(N_2\odot N_1) \otimes (M_2\odot M_1)$}};
-			\node (B') at (5,0) {\footnotesize{$ (N_2 \otimes M_2)\odot (N_1 \otimes M_1)$}};
+			\node (A) at (0,1.5) {\footnotesize{$ (M_2\otimes N_2)\odot (M_1\otimes N_1)$}};
+			\node (A') at (0,0) {\footnotesize{$(M_2 \odot M_1) \otimes (N_2 \odot N_1)$}};
+			\node (B) at (5,1.5) {\footnotesize{$ (N_2 \otimes M_2)\odot (N_1 \otimes M_1)$}};
+			\node (B') at (5,0) {\footnotesize{$(N_2\odot N_1) \otimes (M_2\odot M_1)$}};
 			%
@@
 				(A) edge node[left]{$\chi$} (A')
-				(A) edge node[above]{$\beta$} (B)
+				(A) edge node[above]{$\beta \odot \beta$} (B)
 				(B) edge node[right]{$\chi$} (B')
-				(A') edge node[above]{$\beta \odot \beta$} (B');
+				(A') edge node[above]{$\beta$} (B');
 		\end{tikzpicture}
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$(M_2 \odot M_1) \otimes (N_2 \odot N_1)$};
-\node (B) at (3,0) {$(N_2 \odot N_1) \otimes (M_2 \odot M_1)$};
-\node (C) at (0,-.75) {$(M_2 \otimes N_2) \odot (M_1 \otimes N_1)$};
-\node (D) at (3,-.75) {$(N_2 \otimes M_2) \odot (N_1 \otimes M_1)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$\beta$} (B)
+\node (A) at (0,0) {$(M_2 \otimes N_2) \odot (M_1 \otimes N_1)$};
+\node (B) at (3,0) {$(N_2 \otimes M_2) \odot (N_1 \otimes M_1)$};
+\node (C) at (0,-.75) {$(M_2 \odot M_1) \otimes (N_2 \odot N_1)$};
+\node (D) at (3,-.75) {$(N_2 \odot N_1) \otimes (M_2 \odot M_1)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$\beta \odot \beta$} (B)
 (B) edge node[right]{$\chi$} (D)
 (A) edge node[left]{$\chi$} (C)
-(C) edge node[above]{$\beta \odot \beta$} (D);
+(C) edge node[above]{$\beta$} (D);
 \end{tikzpicture}
@@
 			\node (a) at (-4,0) {$a+a'$};
-			\node (b) at (1,0) {$(m_1+_b m_2) + (n_1+_{b'} n_2)$};
+			\node (b) at (1,0) {$(m_1+n_1) +_{(b+b')} (m_2+n_2)$};
 			\node (c) at (6,0) {$c+c'$};
 			\node (a2) at (-4,1) {$a'+a$};
-			\node (b2) at (1,1) {$(n_1 +_{b'} n_2) + (m_1 +_b m_2)$};
+			\node (b2) at (1,1) {$(n_1+m_1) +_{(b'+b)} (n_2+m_2)$};
 			\node (c2) at (6,1) {$c'+c$};
             \node (a3) at (-4,2) {$a'+a$};
-			\node (b3) at (1,2) {$(n_1+m_1) +_{(b'+b)} (n_2+m_2)$};
+			\node (b3) at (1,2) {$(n_1 +_{b'} n_2) + (m_1 +_b m_2)$};
 			\node (c3) at (6,2) {$c'+c$};
             \node (a5) at (-4,-1) {$a+a'$};
-			\node (b5) at (1,-1) {$(m_1+n_1) +_{(b+b')} (m_2+n_2)$};
+			\node (b5) at (1,-1) {$(m_1+_b m_2) + (n_1+_{b'} n_2)$};
 			\node (c5) at (6,-1) {$c+c'$};
             \node (a6) at (-4,-2) {$a'+a$};
-			\node (b6) at (1,-2) {$(n_1+m_1) +_{(b'+b)} (n_2+m_2)$};
+			\node (b6) at (1,-2) {$(n_1 +_{b'} n_2) + (m_1 +_b m_2)$};
 			\node (c6) at (6,-2) {$c'+c$};
@@
             (a) edge node[left]{$\beta$} (a2)
-            (b) edge node[left]{$\beta$} (b2)
+            (b) edge node[left]{$\beta \odot \beta$} (b2)
 %(b) edge node[right]{$\tau_1$} (b2)
@@
             (a5) edge node[left]{$\beta$} (a6)
-            (b5) edge node[left]{$\beta \odot \beta$} (b6)
+            (b5) edge node[left]{$\beta$} (b6)
  %(b5) edge node[right]{$\tau_5$} (b6)
@@
 %			\node (a) at (-4,0) {$a+a'$};
-			\node (b) at (1,0) {$(m_1+_b m_2) + (n_1+_{b'} n_2)$};
-			\node (c) at (8,0) {$(x_1 \odot x_2) \oplus (y_1 \odot y_2) \in F((m_1+_b m_2)+(n_1+_{b'} n_2))$};
+			\node (b) at (1,0) {$(m_1+n_1) +_{(b+b')} (m_2+n_2)$};
+			\node (c) at (8,0) {$(x_1\oplus y_1) \odot (x_2\oplus y_2) \in F((m_1+n_1)+_{b+b'}(m_2+n_2))$};
 %			\node (a2) at (-4,1) {$a'+a$};
-			\node (b2) at (1,1) {$(n_1 +_{b'} n_2) + (m_1 +_b m_2)$};
-			\node (c2) at (8,1) {$(y_1 \odot y_2) \oplus (x_1 \odot x_2) \in F((n_1+_{b'} n_2)+(m_1+_b m_2))$};
+			\node (b2) at (1,1) {$(n_1+m_1) +_{(b'+b)} (n_2+m_2)$};
+			\node (c2) at (8,1) {$(y_1\oplus x_1) \odot (y_2\oplus x_2) \in F((n_1+m_1)+_{b'+b}(n_2+m_2))$};
 %                            \node (a3) at (-4,2) {$a'+a$};
-			\node (b3) at (1,2) {$(n_1+m_1) +_{(b'+b)} (n_2+m_2)$};
-			\node (c3) at (8,2) {$(y_1\oplus x_1) \odot (y_2\oplus x_2) \in F((n_1+m_1)+_{b'+b}(n_2+m_2))$};
+			\node (b3) at (1,2) {$(n_1 +_{b'} n_2) + (m_1 +_b m_2)$};
+			\node (c3) at (8,2) {$(y_1 \odot y_2) \oplus (x_1 \odot x_2) \in F((n_1+_{b'} n_2)+(m_1+_b m_2))$};
 %                                \node (a5) at (-4,-1) {$a+a'$};
-			\node (b5) at (1,-1) {$(m_1+n_1) +_{(b+b')} (m_2+n_2)$};
-			\node (c5) at (8,-1) {$(x_1\oplus y_1) \odot (x_2\oplus y_2) \in F((m_1+n_1)+_{b+b'}(m_2+n_2))$};
+			\node (b5) at (1,-1) {$(m_1+_b m_2) + (n_1+_{b'} n_2)$};
+			\node (c5) at (8,-1) {$(x_1 \odot x_2) \oplus (y_1 \odot y_2) \in F((m_1+_b m_2)+(n_1+_{b'} n_2))$};
 %                                \node (a6) at (-4,-2) {$a'+a$};
-			\node (b6) at (1,-2) {$(n_1+m_1) +_{(b'+b)} (n_2+m_2)$};
-			\node (c6) at (8,-2) {$(y_1\oplus x_1) \odot (y_2\oplus x_2) \in F((n_1+m_1)+_{b'+b}(n_2+m_2))$};
+			\node (b6) at (1,-2) {$(n_1 +_{b'} n_2) + (m_1 +_b m_2)$};
+			\node (c6) at (8,-2) {$(y_1 \odot y_2) \oplus (x_1 \odot x_2) \in F((n_1+_{b'} n_2)+(m_1+_b m_2))$};
 			\path[->,font=\scriptsize,>=angle 90]
@@
 %                                (a) edge node[left]{$\beta$} (a2)
-                                (b) edge node[left]{$\beta$} (b2)
+                                (b) edge node[left]{$\beta \odot \beta$} (b2)
 (b) edge node[right]{$\tau_1$} (b2)
@@
 %                                (a5) edge node[left]{$\beta$} (a6)
-                                (b5) edge node[left]{$\beta \odot \beta$} (b6)
+                                (b5) edge node[left]{$\beta$} (b6)
  (b5) edge node[right]{$\tau_4$} (b6);
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$\tau_1 \colon F(\beta)((x_1 \odot x_2)\oplus(y_1 \odot y_2)) \to (y_1 \odot y_2)\oplus(x_1 \odot x_2)$};
-\node (B) at (0,-.5) {$\tau_2 \colon F(\hat{\chi})((y_1 \odot y_2)\oplus(x_1 \odot x_2)) \to (y_1\oplus x_1) \odot (y_2\oplus x_2)$};
-\node (C) at (0,-1) {$\tau_3 \colon F(\hat{\chi})((x_1 \odot x_2)\oplus(y_1 \odot y_2)) \to (x_1\oplus y_1) \odot (x_2\oplus y_2)$};
-\node (D) at (0,-1.5) {$\tau_4 \colon F(\beta \odot \beta)((x_1\oplus y_1)\odot(x_2\oplus y_2)) \to (y_1\oplus x_1)\odot(y_2\oplus x_2)$};
+\node (A) at (0,0) {$\tau_1 \colon F(\beta \odot \beta)((x_1\oplus y_1)\odot(x_2\oplus y_2)) \to (y_1\oplus x_1)\odot(y_2\oplus x_2)$};
+\node (B) at (0,-.5) {$\tau_2 \colon F(\hat{\chi})((y_1 \oplus x_1)\odot(y_2 \oplus x_2)) \to (y_1\odot y_2) \oplus (x_1\odot x_2)$};
+\node (C) at (0,-1) {$\tau_3 \colon F(\hat{\chi})((x_1 \oplus y_1)\odot(x_2 \oplus y_2)) \to (x_1\odot x_2) \oplus (y_1\odot y_2)$};
+\node (D) at (0,-1.5) {$\tau_4 \colon F(\beta)((x_1\odot x_2)\oplus(y_1\odot y_2)) \to (y_1\odot y_2)\oplus(x_1\odot x_2)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-These decoration isomorphisms then form the following commutative diagram in the category $F((n_1+m_1)+_{b'+b}(n_2+m_2))$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$F(\hat{\chi} \beta)((x_1 \odot x_2)\oplus(y_1 \odot y_2))$};
-\node (B) at (4,0) {$F(\hat{\chi})((y_1 \odot y_2)\oplus(x_1 \odot x_2))$};
-\node (C) at (0,-1) {$F(\beta \odot \beta)((x_1\oplus y_1) \odot (x_2 \oplus  y_2))$};
-\node (D) at (4,-1) {$(y_1\oplus x_1) \odot (y_2\oplus x_2)$};
+These decoration isomorphisms then form the following commutative diagram in the category $F({(n_1+_{b'}n_2)}+{(m_1+_b m_2)})$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$F(\hat{\chi} (\beta \odot \beta))((x_1 \oplus y_1)\odot(x_2 \oplus y_2))$};
+\node (B) at (4,0) {$F(\hat{\chi})((y_1 \oplus x_1)\odot(y_2 \oplus x_2))$};
+\node (C) at (0,-1) {$F(\beta)((x_1\odot x_2) \oplus (y_1 \odot y_2))$};
+\node (D) at (4,-1) {$(y_1\odot y_2) \oplus (x_1\odot x_2)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (B) edge node[right]{$\tau_2$} (D)
-(A) edge node[left]{$F(\beta \odot \beta)(\tau_3)$} (C)
+(A) edge node[left]{$F(\beta)(\tau_3)$} (C)
 (C) edge node[above]{$\tau_4$} (D);
@@
 \]
-where in the top left corner, we note that $$F(\hat{\chi} \beta)((x_1 \odot x_2)\oplus (y_1 \odot y_2)) = F((\beta \odot \beta)\hat{\chi})((x_1 \odot x_2)\oplus (y_1 \odot y_2))$$
+where in the top left corner, we note that $$F(\hat{\chi} (\beta \odot \beta))((x_1 \oplus y_1)\odot(x_2 \oplus y_2)) = F(\beta\hat{\chi})((x_1 \oplus y_1)\odot (x_2 \oplus y_2))$$
 as the above diagram of maps of cospans commutes in $\A$ and then applying the pseudofunctor $F$ to this diagram yields a commutative diagram in $\Cat$. 

### 2020-12-04 cospans.tex
worked on Conclusions

@@
 % in LaTeX
-% 2020/12/3
+% 2020/12/4
 
@@
 The converse question is also interesting: is every structured cospan double category equivalent to a decorated cospan double category?
-The answer is similar to the previous one: affirmative, under certain conditions that allow us to make the passage from an appropriate functor $L\colon \A\to \X$ to an appropriate pseudofunctor $F\colon \A\to\Cat$, namely in the reverse direction of the earlier \cref{eq:FtoL}.
-
-Let us now give a sketch of the relevant story.
-Suppose $\A$ and $\X$ have finite colimits and $L\maps\A\to\X$ is a finite-colimit preserving functor -- which by \cref{thm:SC} are the required conditions for constructing the symmetric monoidal double category of structured cospans.
-If $L$ has a right adjoint `left inverse' (meaning the unit is the identity) $U\maps\X\to\A$, which moreover strictly preserves the choice of pushouts in $\A$ and $\X$, it can be shown\footnote{This will appear in the forthcoming paper \cite{CV}.} that $U$ is an opfibration.
-Consequently, $U$ corresponds to a pseudofunctor $F\colon \A\to\Cat$ by the reverse of the Grothendieck construction, i.e.
-the second part of \cref{thm:Grothendieck}.
-Furthermore, if $U$ preserves finite coproducts, by the special case of the cocartesian monoidal Grothendieck construction discussed under \cref{lem:MonGroth}, the corresponding pseudofunctor $F$ has a lax monoidal structure $(\A,+)\to(\Cat,\times)$.
-As a result, by \cref{DC}, $F$ has now enough structure to induce the symmetric monoidal double category of decorated cospans $F\lCsp$, and further it can then be verified that it is isomorphic to the one of structured cospans.
-
-{\chris Give some sort of excuse why we don't do the full result here?? Because of missing - for us now - steps? Or other things?}
-
-To give a better sense of how this lax monoidal pseudofunctor $F\maps\A\to\Cat$ is constructed, $F(a)$ is defined to be the pre-image of $a$ under $U$, namely the category of all objects in $x\in\X$ such that $U(x)=a$ and morphisms $k\maps x\to y\in\X$ such that $U(k)=1_a$.
-Given a morphism $f\maps a\to b$, there is a functor $F(f)\maps F(a)\to F(b)$ that maps some $x$ to the following pushout
+The answer is similar to the previous one: yes, under certain conditions that let us pass from an appropriate functor $L \maps \A \to \X$ to an appropriate pseudofunctor $F \maps \A \to \Cat$.
+
+Let us now sketch the story; details will appear in a forthcoming paper \cite{CV}.
+Suppose the conditions hold for constructing the double category of structured cospans ${}_L \lCsp(\X)$ as in \cref{thm:SC}.
+That is, suppose $\A$ and $\X$ have finite colimits and $L \maps \A \to \X$ preserves them.
+If $L$ also has a right adjoint `left inverse' (meaning the unit is the identity) $U \maps \X \to \A$, which moreover strictly preserves the chosen pushouts, it can be shown that $U$ is an opfibration.
+Consequently, $U$ corresponds to a pseudofunctor $F \maps \A \to \Cat$ by the inverse Grothendieck construction, as in the second part of \cref{thm:Grothendieck}.
+Furthermore, if $U$ preserves finite coproducts, $F$ acquires the structure of a lax monoidal pseudofunctor $F \maps (\A,+) \to (\Cat,\times)$ by the special case of the cocartesian monoidal Grothendieck construction discussed under \cref{lem:MonGroth}.
+As a result, $F$ has now enough structure to induce a double category of decorated cospans $F\lCsp$  as in \cref{DC}.
+Finally, it can be shown that the structured and decorated cospan double categories categories are equivalent as symmetric monoidal double categories: ${}_L \lCsp(\X) \simeq F\Csp$.
+
+To give a better sense of how the pseudofunctor $F \maps \A \to\Cat$ is constructed: for each object $a \in A$, $F(a)$ is defined to be the fiber of $U$ over $a$, namely the category of all objects in $x \in \X$ such that $U(x)=a$ and morphisms $k\maps x\to y$ such that $U(k)=1_a$.
+Given a morphism $f \maps a \to b$, there is a functor $F(f) \maps F(a)\to F(b)$ that maps $x \in F(a)$ to the following pushout:
 \begin{displaymath}
@@
 \end{displaymath}
-where $\varepsilon_x\colon LU(x)=L(a)\to x$ is the counit of $L\dashv U$. The fact that $U$ strictly preserves pushouts is necessary to show that the pushout is mapped, via $U$, directly down to $b$.
+where $\varepsilon_x\colon LU(x)=L(a)\to x$ is the counit of the adjunction $L\dashv U$.
+The fact that $U$ strictly preserves pushouts is necessary to show that the pushout is mapped, via $U$, directly down to $b$.
 

### 2020-12-05 cospans.tex
more small changes

@@
 Petri nets are widely used as models of systems in computer science, chemistry, population biology and epidemiology \cite{GiraultValk,Peterson}.
-Structured cospans have been used to define a symmetric monoidal double category of `open Petri nets' \cite{BM}.
-We can also use decorated cospans to construct this double category.
+Structured cospans have been used to define a symmetric monoidal double category of `open Petri nets' \cite{BM}, which lets us build large Petri nets out of smaller pieces.
+We can also use decorated cospans to create a double category of open Petri nets.
 Again this example is very similar to the example of open graphs.
@@
 In these Petri nets, which we shall call `Petri nets with rates', the transitions are labelled with positive real numbers called `rate constants'.
-This allows one to systematically construct a dynamical system from any Petri net with rates, and mathematical chemists have proved deep theorems relating the topology of Petri nets with rates to the qualitative behavior of their dynamical systems.
+This allows one to systematically construct a dynamical system from any Petri net with rates.
+Mathematical chemists have proved deep theorems relating the topology of Petri nets with rates to the qualitative behavior of their dynamical systems \cite{CTF}.
 
@@
 
-We now show that while open dynamical systems of this sort are morphisms in a decorated cospan category, they do not arise from a structured cospan category via \cref{thm:equiv}.
+We now show that while open dynamical systems are morphisms in a decorated cospan category, they do not arise from a structured cospan category via \cref{thm:equiv}.
+To do this, recall that in this result we start with the data required for a decorated cospan category, namely a symmetric lax monoidal pseudofunctor $F \maps (\A,+) \to (\Cat,\times)$, and show the resulting opfibration $U \maps \inta F \to \A$ has a left adjoint $L \maps \A \to \X$.
+We shall show that in the case at hand, where $F = D$, the opfibration $U \maps \inta F \to \A$ does \emph{not} have a left adjoint.
 
@@
 
-\section{Definitions}
+\section{}
 In this appendix, we gather some well-known concepts required to make the material self-contained, as well as references to more detailed expositions.
@@
 \]
-{\chris $\chi$'s in the definition of a monoidal double category have a different direction. Since it is an isomorphism it doesn't really change anything, but consider changing to keep them right}
 First of all, if we only consider the underlying cospans without their decorations, we obtain the following `flattened' commutative diagram in the symmetric monoidal double category $\lCsp(\A)$, where the top and the bottom cospans coincide:
@@
 as the above diagram of maps of cospans commutes in $\A$ and then applying the pseudofunctor $F$ to this diagram yields a commutative diagram in $\Cat$.
-{\chris Well only up to isomorphism since F is a pseudofunctor. Does this matter?}
-{\chris I would here expect big pasted diagrams of isomorphisms coming from the braided lax monoidal pseudofunctor and using its axioms to actually show that two such isomorphisms are equal...}
 
@@
 
+\bibitem{CTF} Gheorghe Craciun, Yangzhong Tang and Martin Feinberg, Understanding bistability in complex enzyme-driven reaction networks, \textsl{PNAS} \textbf{103} (2006), 8697--8702.
+
 \bibitem{DS} B.\ Day and R.\ Street, Monoidal Bicategories and Hopf algebroids, \textsl{Adv.\ Math.} \textbf{129} (1997), 99--157.
@@
 \ Gray, Fibred and cofibred categories, in \textsl{Proceedings of the Conference on Categorical Algebra: La Jolla 1965}, eds.\ S.\ Eilenberg \textit{et al}, Springer, Berlin, 1966, pp.\ 21--83.
+
+\bibitem{HP} M.\ Halter and E.\ Patterson, Compositional epidemiological modeling using structured cospans, 2020.
+Available at \href{https://www.algebraicjulia.org/blog/post/2020/10/structured-cospans}{https://www.algebraicjulia.org/blog/post/2020/10/structured-cospans}.
 

### 2020-12-05 cospans.tex
minor edits in 6

@@
 \section{Conclusions}\label{sec:conclusions}
-%%Christina: Or future directions or something?
+%%% Christina: Or future directions or something?
 Unless we at some point conclude about something for the two frameworks, i.e they are close enough that we can choose which one to work with according to our application or something?
@@
 If $L$ also has a right adjoint `left inverse' (meaning the unit is the identity) $U \maps \X \to \A$, which moreover strictly preserves the chosen pushouts, it can be shown that $U$ is an opfibration.
-Consequently, $U$ corresponds to a pseudofunctor $F \maps \A \to \Cat$ by the inverse Grothendieck construction, as in the second part of \cref{thm:Grothendieck}.
+Consequently, $U$ corresponds to a pseudofunctor $F \maps \A \to \Cat$ by the inverse Grothendieck construction, as in the first part of \cref{thm:Grothendieck}.
 Furthermore, if $U$ preserves finite coproducts, $F$ acquires the structure of a lax monoidal pseudofunctor $F \maps (\A,+) \to (\Cat,\times)$ by the special case of the cocartesian monoidal Grothendieck construction discussed under \cref{lem:MonGroth}.
@@
 
-{\chris I don't know if the part below should be included or not, perhaps it is too speculative and not dead important. 
-%If we keep, I can add a bit more information about what these special opfibs and special laris are, if we think it helps -- or not if it's OK now. 
-Bear in mind that me and Daniel are supposed to clarify the middle category isomorphism in this other paper too!}
-
 Even though for both \cref{thm:equiv} and the above described setting, the conditions required are only sufficient, they provide certain indication that under a suitable ``condition intersection'' in a sense, we could establish a functorial picture
@@
 \node[below left=1 and .5  of A,draw] (D)  {Special opfibrations};
-\node[below left=2 and 1 of A,draw] (E)  {Special laris};
-\node[below=3 of A,align=center,draw] (B)  {Finitely cocomplete \\ functors $A\to\X$};
-\node[below=.01 of D] {\rotatebox{90}{$\cong$}};
+\node[below left=2 and 1 of A,draw] (E)  {Special ralis};
+\node[below=3 of A,align=center,draw] (B)  {Finite colimit preserving \\ functors $A\to\X$};
+\node[below=.01 of D] {\rotatebox{90}{$\simeq$}};
 \path[->,font=\scriptsize]

### 2020-12-05 cospans.tex
Added some diagrams to Appendix B

@@
 \]
+The morphisms $\tau_1$ and $\tau_2$ may be composed as $$\tau_2 F(\hat{\chi})(\tau_1) \colon F(\hat{\chi})F(\beta \odot \beta)((x_1 \oplus y_1) \odot (x_2 \oplus y_2)) \to (y_1 \odot y_2) \oplus (x_1 \odot x_2)$$ which is given by the diagram:
+\[
+\begin{tikzpicture}[scale=1.7]
+%\node (A) at (3.85,0) {$\scriptstyle{\cong}$};
+%\node (A') at (3.85,-1) {$\scriptstyle{\cong}$};
+\node (D) at (3,-0.5) {$\scriptstyle{\one}$};
+\node (E) at (6.75,0.5) {$\scriptstyle{F(m_1 + n_1) \times F(m_2+n_2)}$};
+\node () at (5.5,0) {$\scriptstyle\stackrel{\cref{eq:braidedpseudofun}}{\cong}$};
+\node () at (7.875,0) {$\scriptstyle\stackrel{\cref{eq:pseudonaturality}}{\cong}$};
+\node () at (10.25,0) {$\scriptstyle{\cong}$};
+\node () at (7.875,-1) {$\scriptstyle{\cong}$};
+\node (E') at (6.75,-0.5) {$\scriptstyle{F(n_1+m_1) \times F(n_2+m_2)}$};
+\node (B) at (9,0.5) {$\scriptstyle{F((m_1+n_1)+(m_2+n_2))}$};
+\node (B') at (9,-0.5) {$\scriptstyle{F((n_1+m_1)+(n_2+m_2))}$};
+\node (C) at (11.5,0.5) {$\scriptstyle{F((m_1+n_1)+_{b+b'}(m_2+n_2))}$};
+\node (C') at (11.5,-0.5) {$\scriptstyle{F((n_1+m_1)+_{b'+b}(n_2+m_2))}$};
+\node (G) at (4.25,0.5) {$\scriptstyle{F(m_1) \times F(n_1) \times F(m_2) \times F(n_2)}$};
+\node (G') at (4.25,-0.5) {$\scriptstyle{F(n_1) \times F(m_1) \times F(n_2) \times F(m_2)}$};
+\node (G'') at (4.25,-1.5) {$\scriptstyle{F(n_1) \times F(n_2) \times F(m_1) \times F(m_2)}$};
+\node (E'') at (6.75,-1.5) {$\scriptstyle{F(n_1+n_2) \times F(m_1+m_2)}$};
+\node (B'') at (9,-1.5) {$\scriptstyle{F((n_1+n_2)+ (m_1+ m_2))}$};
+\node (C'') at (11.5,-1.5) {$\scriptstyle{F((n_1+_{b'}n_2)+(m_1+_b m_2))}$};
+\node (X) at (3.4,0.2) {$\scriptscriptstyle{x_1 \times y_1 \times x_2 \times y_2}$};
+\node (X') at (3.4,-0.35) {$\scriptscriptstyle{y_1 \times x_1 \times y_2 \times x_2}$};
+\node (X'') at (3.4,-1.2) {$\scriptscriptstyle{y_1 \times y_2 \times x_1 \times x_2}$};
+\path[->,font=\scriptsize,>=angle 90]
+(B) edge node [fill=white] {$F(\beta+\beta)$} (B')
+(E) edge node [fill=white] {$F(\beta) \times F(\beta)$} (E')
+(E) edge node [above] {$\phi_{m_1+n_1,m_2+n_2}$} (B)
+(E'') edge node [above] {$\phi_{n_1+n_2,m_1+m_2}$} (B'')
+(E') edge node [above] {$\phi_{n_1+m_1,n_2+m_2}$} (B')
+(B) edge node [above] {$F(\psi)$} (C)
+(B'') edge node [above] {$F(\psi + \psi)$} (C'')
+(B') edge node [above] {$F(\psi)$} (C')
+(C) edge node [fill=white] {$F(\beta \odot \beta)$} (C')
+(C') edge node [fill=white] {$F(\hat{\chi})$} (C'')
+(G) edge node [above] {$\phi_{m_1,n_1} {\times} \phi_{m_2,n_2}$} (E)
+(G'') edge node [above] {$\phi_{n_1,n_2} {\times} \phi_{m_1,m_2}$} (E'')
+(G') edge node [above] {$\phi_{n_1,m_1} \times \phi_{n_2,m_2}$} (E')
+(G) edge node [fill=white] {$\beta \times \beta$} (G')
+(G') edge node [fill=white] {$1 \times \beta \times 1$} (G'')
+(D) edge[out=90,in=180] node [left,above] {$$} (G)
+(D) edge[out=270,in=180] node [left,above] {$$} (G'')
+(D) edge node [below] {$$} (G');
+\end{tikzpicture}
+\]
+and the morphisms $\tau_3$ and $\tau_4$ may be composed as $$\tau_4 F(\beta)(\tau_3) \colon F(\beta) F(\hat{\chi}) \colon F(\beta)F(\hat{\chi})((x_1 \oplus y_1)\odot(x_2 \oplus y_2)) \to (y_1 \odot y_2) \oplus (x_1 \odot x_2)$$ which is given by the diagram:
+\[
+\begin{tikzpicture}[scale=1.7]
+%\node (A) at (3.85,0) {$\scriptstyle{\cong}$};
+%\node (A') at (3.85,-1) {$\scriptstyle{\cong}$};
+\node (D) at (3,-0.5) {$\scriptstyle{\one}$};
+\node (E) at (6.75,0.5) {$\scriptstyle{F(m_1 + n_1) \times F(m_2+n_2)}$};
+\node () at (5.5,-1) {$\scriptstyle{\cong}$};
+\node () at (7.875,-1) {$\scriptstyle\stackrel{\cref{eq:braidedpseudofun}}{\cong}$};
+\node () at (10.25,-1) {$\scriptstyle{\cong}$};
+\node () at (7.875,0) {$\scriptstyle{\cong}$};
+\node (E') at (6.75,-0.5) {$\scriptstyle{F(m_1+m_2) \times F(n_1+n_2)}$};
+\node (B) at (9,0.5) {$\scriptstyle{F((m_1+n_1)+(m_2+n_2))}$};
+\node (B') at (9,-0.5) {$\scriptstyle{F((m_1+ m_2)+(n_1+n_2))}$};
+\node (C) at (11.5,0.5) {$\scriptstyle{F((m_1+n_1)+_{b+b'}(m_2+n_2))}$};
+\node (C') at (11.5,-0.5) {$\scriptstyle{F((m_1+_b m_2)+ (n_1+_{b'} n_2))}$};
+\node (G) at (4.25,0.5) {$\scriptstyle{F(m_1) \times F(n_1) \times F(m_2) \times F(n_2)}$};
+\node (G') at (4.25,-0.5) {$\scriptstyle{F(m_1) \times F(m_2) \times F(n_1) \times F(n_2)}$};
+\node (G'') at (4.25,-1.5) {$\scriptstyle{F(n_1) \times F(n_2) \times F(m_1) \times F(m_2)}$};
+\node (E'') at (6.75,-1.5) {$\scriptstyle{F(n_1+n_2) \times F(m_1+m_2)}$};
+\node (B'') at (9,-1.5) {$\scriptstyle{F((n_1+n_2)+(m_1+ m_2))}$};
+\node (C'') at (11.5,-1.5) {$\scriptstyle{F((n_1+_{b'}n_2)+(m_1+_b m_2))}$};
+\node (X) at (3.4,0.2) {$\scriptscriptstyle{x_1 \times y_1 \times x_2 \times y_2}$};
+\node (X') at (3.4,-0.35) {$\scriptscriptstyle{x_1 \times x_2 \times y_1 \times y_2}$};
+\node (X'') at (3.4,-1.2) {$\scriptscriptstyle{y_1 \times y_2 \times x_1 \times x_2}$};
+\path[->,font=\scriptsize,>=angle 90]
+(B') edge node [fill=white] {$F(\beta)$} (B'')
+(E') edge node [fill=white] {$\beta$} (E'')
+(E) edge node [above] {$\phi_{m_1+n_1,m_2+n_2}$} (B)
+(E'') edge node [above] {$\phi_{n_1+n_2,m_1+m_2}$} (B'')
+(E') edge node [above] {$\phi_{m_1+m_2,n_1+n_2}$} (B')
+(B) edge node [above] {$F(\psi)$} (C)
+(B'') edge node [above] {$F(\psi+\psi)$} (C'')
+(B') edge node [above] {$F(\psi+\psi)$} (C')
+(C) edge node [fill=white] {$F(\hat{\chi})$} (C')
+(C') edge node [fill=white] {$F(\beta)$} (C'')
+(G) edge node [above] {$\phi_{m_1,n_1} {\times} \phi_{m_2,n_2}$} (E)
+(G'') edge node [above] {$\phi_{n_1,n_2} {\times} \phi_{m_1,m_2}$} (E'')
+(G') edge node [above] {$\phi_{m_1,m_2} \times \phi_{n_1,n_2}$} (E')
+(G) edge node [fill=white] {$1 \times \beta \times 1$} (G')
+(G') edge node [fill=white] {$\beta$} (G'')
+(D) edge[out=90,in=180] node [left,above] {$$} (G)
+(D) edge[out=270,in=180] node [left,above] {$$} (G'')
+(D) edge node [below] {$$} (G');
+\end{tikzpicture}
+\]
+
+\begin{comment}
 These decoration isomorphisms then form the following commutative diagram in the category $F({(n_1+_{b'}n_2)}+{(m_1+_b m_2)})$:
@@
 as the above diagram of maps of cospans commutes in $\A$ and then applying the pseudofunctor $F$ to this diagram yields a commutative diagram in $\Cat$. 
+\end{comment}
 

### 2020-12-06 cospans.tex
modeling systems using open Petri nets with rates

--- 2020-12-05 cospans.tex
@@
 % in LaTeX
-% 2020/12/4
+% 2020/12/5
 
@@
 
-Petri nets are widely used as models of systems in computer science, chemistry, population biology and epidemiology \cite{GiraultValk,Peterson}.
+Petri nets are widely used as models of systems in engineering and computer science \cite{GiraultValk, Peterson}.
 Structured cospans have been used to define a symmetric monoidal double category of `open Petri nets' \cite{BM}, which lets us build large Petri nets out of smaller pieces.
@@
 
-Chemists sometimes use Petri nets where the places represent `chemical species'---types of molecules, ions and the like---and the transitions represent chemical reactions.
-In these Petri nets, which we shall call `Petri nets with rates', the transitions are labelled with positive real numbers called `rate constants'.
-This allows one to systematically construct a dynamical system from any Petri net with rates.
+In chemistry, population biology, epidemiology and other fields, modelers often use `Petri nets with rates', where the transitions are labelled with positive real numbers called `rate constants' \cite{Haas,Koch,Wilkinson}.
+From any Petri net with rates one can systematically construct a dynamical system.
 Mathematical chemists have proved deep theorems relating the topology of Petri nets with rates to the qualitative behavior of their dynamical systems \cite{CTF}.
 
-Pollard and the first author showed how to construct an `open dynamical system' from an `open' Petri net with rates, meaning one where chemicals can flow in and out at certain places \cite{BP}.
-They used the formalism of decorated cospans to do this, and to define a functor from a category with open Petri nets with rates as morphisms to one with open dynamical systems as morphisms.
+Recently Pollard and the first author showed how to construct an `open' dynamical system from an `open' Petri net with rates, and define a functor from a category with open Petri nets with rates as morphisms to one with open dynamical systems as morphisms \cite{BP}.
  Later, structured cospans were used to promote the first of these categories to a double category \cite[Sec.\ 6.16]{BC}.
-Here we show that the second, the category with open dynamical systems as morphisms, \emph{cannot} be made into a double category using structured cospans---but we \emph{can} do it using decorated cospans!
-
+Here we show that the second of these categories, with open dynamical systems as morphisms, \emph{cannot} be made into a double category using structured cospans---but we \emph{can} do it using decorated cospans!
+
+First, to briefly illustrate these ideas, here is an open Petri net with rates:
+\[
+\begin{tikzpicture}
+	\begin{pgfonlayer}{nodelayer}
+\node [style=inputdot] (1a) at (-5.3, 0.5) {};
+\node [style=inputdot] (1b) at (-5.3, 0) {};
+\node [style=inputdot] (2) at (-5.3, -0.5) {};
+\node [style=inputdot] (3) at (1.3, 0) {};
+\node [style=none] (1'a) at (-4.4, 0.5) {};
+\node [style=none] (1'b) at (-4.4, 0.5) {};
+\node [style=none] (2') at (-4.4, -0.5) {};
+\node [style=none] (3') at (0.4, 0) {};
+\node [style=species] (S) at (-4, 0.5) {$S$};
+\node [style=species] (I) at (-4, -0.5) {$I$};
+\node [style=species] (R) at (0, 0) {$R$};
+		\node [style=transition] (tau1) at (-1.5, 0.7) {$r_1$};
+            \node [style=transition] (tau2) at (-1.5,-1) {$r_2$};
+		\node [style=none] (I1a) at (-5.6, 0.5) {$i_1$};
+		 \node [style=none] (I1b) at (-5.6, 0) {$i_2$};
+           \node [style=none] (I2) at (-5.6, -0.5) {$i_3$};
+		\node [style=none] (O3) at (1.65, 0) {$o_1$};
+		\node [style=none] (ATL) at (-5.8,1.4) {};
+		\node [style=none] (ATR) at (-5,1.4) {};
+		\node [style=none] (ABR) at (-5,-1.4) {};
+		\node [style=none] (ABL) at (-5.8,-1.4) {};
+		\node [style=none] (MTL) at (1,1.4) {};
+		\node [style=none] (MTR) at (1.8,1.4) {};
+		\node [style=none] (MBR) at (1.8,-1.4) {};
+		\node [style=none] (MBL) at (1,-1.4) {};
+		\node [style=none] (X) at (-5.4,1.8) {$X$};		
+		\node [style=none] (Z) at (1.4,1.8) {$Y$};
+
+	\end{pgfonlayer}
+	\begin{pgfonlayer}{edgelayer}
+		\draw [style=inarrow, bend left =10, looseness=1.00] (S) to (tau1);
+		\draw [style=inarrow, bend left=15, looseness=1.00] (I) to (tau1);
+		\draw [style=inarrow, bend left=25, looseness=1.00] (tau1) to (I);
+		\draw [style=inarrow, bend left=40, looseness=1.00] (tau1) to (I);
+	       \draw [style=inarrow, bend right=25, looseness=1.00] (I) to (tau2);
+             \draw [style=inarrow, bend right=15, looseness=1.00] (tau2) to (R); 
+\path[color=purple, very thick, shorten >=2pt, shorten <=2pt, ->, >=stealth] (1a) edge (1'a);
+\path[color=purple, very thick, shorten >=2pt, shorten <=2pt, ->, >=stealth] (1b) edge (1'b);
+\path[color=purple, very thick, shorten >=2pt, shorten <=2pt, ->, >=stealth] (2) edge (2');	
+\path[color=purple, very thick, shorten >=2pt, shorten <=2pt, ->, >=stealth] (3) edge (3');
+		\draw [style=simple] (ATL.center) to (ATR.center);
+		\draw [style=simple] (ATR.center) to (ABR.center);
+		\draw [style=simple] (ABR.center) to (ABL.center);
+		\draw [style=simple] (ABL.center) to (ATL.center);
+		\draw [style=simple] (MTL.center) to (MTR.center);
+		\draw [style=simple] (MTR.center) to (MBR.center);
+		\draw [style=simple] (MBR.center) to (MBL.center);
+		\draw [style=simple] (MBL.center) to (MTL.center);
+	\end{pgfonlayer}
+\end{tikzpicture}
+\]
+It is an open Petri net where the transitions are labelled with rate constants $r_1, r_2 > 0$.
+Here is the corresponding open dynamical system:
+\[   \begin{array}{ccl} \displaystyle{\frac{dS(t)}{dt}} &=& -r_1 \, S(t)I(t)  + I_1(t) + I_2(t) \\ \\
+\displaystyle{\frac{dI(t)}{dt}}  &=& r_1\, S(t)I(t) - r_2 \, I(t) + I_3(t)  \\  \\
+\displaystyle{\frac{dR(t)}{dt}}  &=&   r_2 \, I(t)  - O_1(t).
+\end{array}
+\]
+If we drop the `inflow' and `outflow' terms $I_i$ and $O_i$ we obtain a system of coupled nonlinear first-order ordinary differential equations.
+In fact these equations are a famous model of infectious disease, the `SIR model', where $S(t)$, $I(t)$ and $R(t)$ describe the populations of susceptible, infected and recovered individuals, respectively.
+The inflow and outflow terms allow individuals to enter or leave the population.
+This in turn lets us couple the SIR model to other models, and build complex models from smaller pieces.
+Recently Halter, and Patterson \cite{HP} implemented this idea in software using structured cospans.
+They illustrated the use of this tool by rebuilding part of the model that the UK has been using to make policy decisions about COVID-19.
+
+Now let us turn to the mathematics.
 A \define{Petri net with rates} is a Petri net $s,t \maps T \to \N[S]$ together with a function $r \maps T \to (0,\infty)$ assigning to each transition $\tau \in T$ a positive real number called its \define{rate constant}.
@@
 
+\bibitem{Haas} P.\ J.\ Haas, \textsl{Stochastic Petri Nets: Modelling, Stability, Simulation},
+Springer, Berlin, 2002.
+
 \bibitem{HP} M.\ Halter and E.\ Patterson, Compositional epidemiological modeling using structured cospans, 2020.
@@
 pp.\ 75--103.
+
+\bibitem{Koch} I.\ Koch, Petri nets---a mathematical formalism to analyze chemical reaction
+networks, \textsl{Mol.\ Inform.\  }\textbf{29} (2010), 838--843.
 
@@
 
+\bibitem{Wilkinson} D.\ J.\ Wilkinson, \textsl{Stochastic Modelling for Systems Biology},
+Taylor and Francis, New York, 2006.
+
 \bibitem{Willems} J.\ C.\ Willems, The behavioral approach to open and interconnected systems, \textsl{IEEE Control Systems Magazine} (2007)

### 2020-12-06 cospans.tex
polished up Kenny's argument that open dynamical systems aren't a structured cospan double category

@@
 
-Recently Pollard and the first author showed how to construct an `open' dynamical system from an `open' Petri net with rates, and define a functor from a category with open Petri nets with rates as morphisms to one with open dynamical systems as morphisms \cite{BP}.
+Pollard and the first author have used decorated cospans to construct an `open' dynamical system from any `open' Petri net with rates, thus defining a functor from a category with open Petri nets with rates as morphisms to one with open dynamical systems as morphisms \cite{BP}.
 Later, structured cospans were used to promote the first of these categories to a double category \cite[Sec.\ 6.16]{BC}.
-Here we show that the second of these categories, with open dynamical systems as morphisms, \emph{cannot} be made into a double category using structured cospans---but we \emph{can} do it using decorated cospans!
+Here we show that the second of these categories, with open dynamical systems as morphisms, \emph{cannot} be made into a double category using structured cospans.
+However, we \emph{can} do it using decorated cospans.
 
@@
 This in turn lets us couple the SIR model to other models, and build complex models from smaller pieces.
-Recently Halter, and Patterson \cite{HP} implemented this idea in software using structured cospans.
-They illustrated the use of this tool by rebuilding part of the model that the UK has been using to make policy decisions about COVID-19.
-
-Now let us turn to the mathematics.
+Recently Halter and Patterson \cite{HP} implemented this idea in software using structured cospans.
+They illustrated the use of this tool by rebuilding part of the COVID-19 model that the UK has been using to make policy decisions.
+
+Now let us turn to the details.
 A \define{Petri net with rates} is a Petri net $s,t \maps T \to \N[S]$ together with a function $r \maps T \to (0,\infty)$ assigning to each transition $\tau \in T$ a positive real number called its \define{rate constant}.
@@
 \end{itemize}
-The functorality of $D$ is proved in \cite[Lemma 15]{BP} while the lax symmetric monoidal stucture is given in Lemma 16.
+The functorality of $D$ is proved in \cite[Lemma 15]{BP} while the lax symmetric monoidal stucture is given in Lemma 16 of that paper.
 
@@
 
-We now show that while open dynamical systems are morphisms in a decorated cospan category, they do not arise from a structured cospan category via \cref{thm:equiv}.
-To do this, recall that in this result we start with the data required for a decorated cospan category, namely a symmetric lax monoidal pseudofunctor $F \maps (\A,+) \to (\Cat,\times)$, and show the resulting opfibration $U \maps \inta F \to \A$ has a left adjoint $L \maps \A \to \X$.
-We shall show that in the case at hand, where $F = D$, the opfibration $U \maps \inta F \to \A$ does \emph{not} have a left adjoint.
-
-Let $\mathsf{Dynam}$ be the category for which:
+We now show that while open dynamical systems are morphisms in a decorated cospan category, this does not arise from a structured cospan category via \cref{thm:equiv}.
+To do this, recall that in that theorem we start with the data required to build a decorated cospan category, namely a symmetric lax monoidal pseudofunctor $F \maps (\A,+) \to (\Cat,\times)$, and show that under certain conditions the resulting opfibration $U \maps \inta F \to \A$ has a left adjoint $L \maps \A \to \X$.
+We then obtain an equivalence between decorated and structured cospan double categories, $F \lCsp \simeq {}_L \Csp(\X)$.
+We now show that in the case at hand, where $F = D$, $U$ does \emph{not} have a left adjoint.
+Thus, the conditions of \cref{thm:equiv} do not hold in this case.
+
+Taking $D$ as above, it is easy to see that in the category $\inta D$
 \begin{itemize}
-\item{an object is a pair $(s,v_s)$ where $s$ is a finite set and $v_s$ is an algebraic vector field $v_s \colon \lR^s \to \lR^s$ on the finite set $s$, and}
-\item{a morphism from $(s,v_s)$ to $(s',v_{s'})$ is a function $f \colon s \to s'$ such that $v_{s'} = f_* v_s f^*$.}
+\item an object is a pair $(S,v)$ where $S$ is a finite set and $v$ is an algebraic vector field $v \maps \R^S \to \R^S$,
+\item a morphism from $(S,v)$ to $(S',v')$ is a function $f \maps S \to S'$ such that $v' = f_* \circ v \circ f^*$.
 \end{itemize}
-
-A well-known result is the following:
-\begin{lem}
-A functor $U \colon \A \to \X$ admits a left adjoint if and only if for every $x \in \X$, the comma category $x \downarrow U$ has an initial object.
+with the usual composition of functions.   The forgetful functor $U \maps \inta D \to \Fin\Set$ acts as follows:
+\begin{itemize}
+\item on objects, $D(S,v) = S$,
+\item on morphisms, $D(f) = f$.
+\end{itemize}
+
+To show that $U$ does not have a left adjoint, we use the following well-known result:
+\begin{lem} \label{lem:initial}
+A functor $U \maps \A \to \X$ admits a left adjoint if and only if for every $x \in \X$, the comma category $x \downarrow U$ has an initial object.
 \end{lem}
-Using this result, one can show that the forgetful functor $U \colon \mathsf{Dynam} \to \Fin\Set$ is not a right adjoint.
-In particular, by taking $x$ to be the empty set, the comma category $\emptyset \downarrow U$ has:
-\begin{itemize}
-\item{objects given as pairs $((s,v_s),! \colon \emptyset \to s)$, and}
-\item{a morphism from $((s,v_s),!
-\colon \emptyset \to s)$ to $((s',v_{s'}),!
-\colon \emptyset \to s')$ is a morphism $f \colon (s,v_s) \to (s',v_{s'})$ in $\mathsf{Dynam}$ such that $U(f) \circ !
-= !$ in $\Fin\Set$, a condition which amounts to simply being a morphism in $\mathsf{Dynam}$.}
-\end{itemize}
-In particular, the object $((\emptyset,v_\emptyset),!
-\colon \emptyset \to \emptyset)$ resides in the comma category $\emptyset \downarrow U$, where $v_\emptyset$ is the only possible vector field on the empty set --- namely, the dengerate vector field.
-Given any other object $((s,v_s),!
-\colon \emptyset \to s)$ in $\emptyset \downarrow U$, there exists no morphisms $!
-\colon \emptyset \to s$ from the first object to the second unless $s$ is also the empty set as the vector field $$!_* v_\emptyset !^*$$will also always be degenerate and not equal to $v_s$.
-Clearly there are also no morphisms in the other direction for $s \neq \emptyset$ as $f$ must be a function.
-Thus the forgetful functor $U$ has no left adjoint $L \colon \Fin\Set \to \mathsf{Dynam}$, and hence we cannot construct a structured cospan category ${_L \Csp(\mathsf{Dynam})}$ whose morphisms are equivalence classes of open dynamical systems of this type.
+Because the empty set is initial in $\Fin\Set$, the comma category 
+$\emptyset \downarrow U$ is just $\inta D$.
+This contains an object $(\emptyset, v_\emptyset)$, where $v_\emptyset$ is the only possible vector field on $\R^\emptyset$, namely, the zero vector field.
+The only object in $\inta D$ with any morphisms to $(\emptyset, v_\emptyset)$ is $(\emptyset, v_\emptyset)$ itself, so no other object can be initial.
+However $(\emptyset, v_\emptyset)$ is not initial either, because it has no morphisms to an object $(S,v)$ unless $v$ is the zero vector field on $\R^S$.
+Thus by \cref{lem:initial}, $U$ does not have a left adjoint.
 
 \section{Conclusions}\label{sec:conclusions}
-%%% Christina: Or future directions or something?
-Unless we at some point conclude about something for the two frameworks, i.e they are close enough that we can choose which one to work with according to our application or something?
-I did something along those lines at the very end....
 

### 2020-12-06 cospans.tex
began work on gray-boxing in 5.4

@@
 \node (B) at (1,0) {$\Cat$};
-\node (C) at (0,-1) {$\mathsf{A'}$};
 \node (C) at (0,-1) {$\A'$};
@@
 
-In chemistry, population biology, epidemiology and other fields, modelers often use `Petri nets with rates', where the transitions are labelled with positive real numbers called `rate constants' \cite{Haas,Koch,Wilkinson}.
+In chemistry, population biology, epidemiology and other fields, modelers use `Petri nets with rates', where the transitions are labelled with positive real numbers called `rate constants' \cite{Haas,Koch,Wilkinson}.
 From any Petri net with rates one can systematically construct a dynamical system.
@@
 
-Now let us turn to the details.
+Now we turn to the details.
 A \define{Petri net with rates} is a Petri net $s,t \maps T \to \N[S]$ together with a function $r \maps T \to (0,\infty)$ assigning to each transition $\tau \in T$ a positive real number called its \define{rate constant}.
@@
 
-We now show that while open dynamical systems are morphisms in a decorated cospan category, this does not arise from a structured cospan category via \cref{thm:equiv}.
-To do this, recall that in that theorem we start with the data required to build a decorated cospan category, namely a symmetric lax monoidal pseudofunctor $F \maps (\A,+) \to (\Cat,\times)$, and show that under certain conditions the resulting opfibration $U \maps \inta F \to \A$ has a left adjoint $L \maps \A \to \X$.
+Next, we can define a symmetric monoidal double functor
+\[      \graysquare \maps F \lCsp \to D \lCsp \]
+sending any open Petri net with rates to its corresponding open dynamical system.
+This was already defined as a functor between categories by Pollard and the first author \cite[Section 7]{BP}, who called it `gray-boxing'.
+To boost this result to the double category level we use \cref{thm:functoriality}, taking the square in that theorem as follows:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$\Fin\Set$};
+\node (B) at (1,0) {$\Cat$};
+\node (C) at (0,-1) {$\Fin\Set$};
+\node (D) at (1,-1) {$\Cat$};
+\node (E) at (0.5,-0.5) {$\Downarrow \theta$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$F$} (B)
+(A) edge node[left]{$1$} (C)
+(B) edge node[right]{$E$} (D)
+(C) edge node[above]{$D$} (D);
+\end{tikzpicture}
+\] 
+%%% continue this....
+
+We now show that decorated cospan double category $D \lCsp$ of open dynamical systems is not equivalent to a structured cospan double category via \cref{thm:equiv}.
+Recall that in that theorem we start with the data required to build a decorated cospan category, namely a symmetric lax monoidal pseudofunctor $F \maps (\A,+) \to (\Cat,\times)$, and show that under certain conditions the resulting opfibration $U \maps \X = \inta F \to \A$ has a left adjoint $L \maps \A \to \X$.
 We then obtain an equivalence between decorated and structured cospan double categories, $F \lCsp \simeq {}_L \Csp(\X)$.
-We now show that in the case at hand, where $F = D$, $U$ does \emph{not} have a left adjoint.
+We now show that in the case at hand, where $F = D$,  the opfibration $U$ does \emph{not} have a left adjoint.
 Thus, the conditions of \cref{thm:equiv} do not hold in this case.
@@
 \node [align=center,draw] (A) { Lax monoidal pseudofunctors \\ $(\A,+)\to(\Cat,\times)$};
-\node[below right=1.5 and 1.5 of A,align=center,draw] (C)  { Symmetric monoidal \\double categories };
-\node[below left=1 and .5  of A,draw] (D)  {Special opfibrations};
+\node[below right=1 and 1.5 of A,align=center,draw] (C)  { Symmetric monoidal \\double categories };
+\node[below left=1.05 and .5  of A,draw] (D)  {Special opfibrations};
 \node[below left=2 and 1 of A,draw] (E)  {Special ralis};
 \node[below=3 of A,align=center,draw] (B)  {Finite colimit preserving \\ functors $A\to\X$};
-\node[below=.01 of D] {\rotatebox{90}{$\simeq$}};
+\node[below=0 of D] {\rotatebox{90}{$\simeq$}};
 \path[->,font=\scriptsize]
@@
 (E) edge (B)
-(B) edge node[below,sloped]{$L\mapsto {}_{L}\lCsp$} (C);
+(B) edge node[below,sloped]{$L\mapsto {}_{L}\lCsp(\X)$} (C);
 \end{tikzpicture}

### 2020-12-06 cospans.tex
finished work on Petri nets with rates in 5.4

@@
 
-Pollard and the first author have used decorated cospans to construct an `open' dynamical system from any `open' Petri net with rates, thus defining a functor from a category with open Petri nets with rates as morphisms to one with open dynamical systems as morphisms \cite{BP}.
+Pollard and the first author showed how to construct an `open' dynamical system from any `open' Petri net with rates,  thus defining a functor from a category with open Petri nets with rates as morphisms to one with open dynamical systems as morphisms \cite{BP}.
+They used Fong's original decorated cospans to do this.
 Later, structured cospans were used to promote the first of these categories to a double category \cite[Sec.\ 6.16]{BC}.
@@
 
-Since every set gives a discrete category with that set of objects, we can reinterpret $D$ as a lax monoidal pseudofunctor $D \maps (\Fin\Set, +) \to (\Cat, \times)$.
+Since every set gives a discrete category with that set of objects, we can reinterpret $D$ as a symmetric lax monoidal pseudofunctor $D \maps (\Fin\Set, +) \to (\Cat, \times)$ which happens to actually be a functor.
 Applying \cref{DC} we obtain a symmetric monoidal double category $D \lCsp$ where:
@@
 sending any open Petri net with rates to its corresponding open dynamical system.
-This was already defined as a functor between categories by Pollard and the first author \cite[Section 7]{BP}, who called it `gray-boxing'.
-To boost this result to the double category level we use \cref{thm:functoriality}, taking the square in that theorem as follows:
+This was already defined at the level of categories by Pollard and the first author \cite[Section 7]{BP}, who called it `gray-boxing'.
+To boost this result to the double category level we use \cref{thm:functoriality}, taking the square in that theorem to be
 \[
@@
 \node (C) at (0,-1) {$\Fin\Set$};
-\node (D) at (1,-1) {$\Cat$};
+\node (D) at (1,-1) {$\Cat$.};
 \node (E) at (0.5,-0.5) {$\Downarrow \theta$};
@@
 (A) edge node[left]{$1$} (C)
-(B) edge node[right]{$E$} (D)
+(B) edge node[right]{$1$} (D)
 (C) edge node[above]{$D$} (D);
@@
 \] 
-%%% continue this....
+Here $\theta$ is a monoidal natural isomorphism given as follows.  For any finite set $S$, $\theta_S \maps F(S) \to D(S)$ maps any Petri nets with rates 
+\[   \xymatrix{ (0,\infty) & T \ar[l]_-r \ar@<-.5ex>[r]_-t \ar@<.5ex>[r]^-s & \N[S] }\]
+to an algebraic vector field on $\R^S$, say $v$.
+This vector field is defined using a standard prescription taken from chemistry, called `the law of mass action'.
+Namely, for any $c \in \R^s$, we set
+\[  
+v(c) = \sum_{\tau \in T} r(\tau) \, ( t(\tau) - s(\tau) ) c^{s(\tau)} 
+\]
+where 
+\[     c^{s(\tau)} = \prod_{i \in S} {c_i}^{s(\tau)_i}  \]
+and we think of $t(\tau), s(\tau) \in \N[S]$ as vectors in $\R^S$.
+This formula is explained in the paper with Pollard, where it is also shown that $\theta$ defines a monoidal natural isomorphism between functors to $\Set$ \cite[Theorem 18]{BP}.
+As such, it trivially becomes a monoidal natural isomorphism between the functors $F, D \maps \Fin\Set \to \Cat$.
 

### 2020-12-07 cospans.tex
switch to fibers

@@
 \end{thm}
-%%% Christina: note to self, now our functor factors through that specific Rex means that each category F(a) which later becomes the fibre comes with a specific choice of colimits.
-We do not know what this choice is, but of course such colimits in the fibres will be isomorphic to any other we may stumble upon!
+%%% Christina: note to self, now our functor factors through that specific Rex means that each category F(a) which later becomes the fiber comes with a specific choice of colimits.
+We do not know what this choice is, but of course such colimits in the fibers will be isomorphic to any other we may stumble upon!
 
@@
 \end{equation}
-Moreover, each fibre category $\X_a=F(a)$ obtains a monoidal structure via 
+Moreover, each fiber category $\X_a=F(a)$ obtains a monoidal structure via 
 \begin{equation}\label{eq:explicitstructure1}
@@
 \begin{enumerate}
- \item all fibres have $\J$-colimits, and the reindexing functors preserve them;
+ \item all fibers have $\J$-colimits, and the reindexing functors preserve them;
  \item the total category $\X$ has $\J$-colimits, and $U$ preserves them.
@@
 
-The first part formulates the existence of colimits \emph{locally} in each fibre, and if we let $\J$ range over all finite categories it says that the corresponding pseudofunctor $F\maps\A\to\Cat$ lands in the sub-2-category $\Rex$.
+The first part formulates the existence of colimits \emph{locally} in each fiber, and if we let $\J$ range over all finite categories it says that the corresponding pseudofunctor $F\maps\A\to\Cat$ lands in the sub-2-category $\Rex$.
 The second part formulates the existence of colimits \emph{globally} in the total category $\inta F$, and if we let $\J$ range over all finite categories it says that $\X$ has finite colimits and $U$ preserves all finite colimits.
@@
 \end{equation}
-which on the first variable is given by the pushout in $\A$ on the left below, and the object $w$ is formed as the pushout in the fibre category $F(a+_bc)$ on the right below:
+which on the first variable is given by the pushout in $\A$ on the left below, and the object $w$ is formed as the pushout in the fiber category $F(a+_bc)$ on the right below:
 \begin{displaymath}
@@
 \end{displaymath}
-In a similar way we can construct the initial object and coproducts in a Grothendieck category from those in the fibres, namely
+In a similar way we can construct the initial object and coproducts in a Grothendieck category from those in the fibers, namely
 \begin{equation}\label{eq:fibrewisecoprod}
@@
 \end{equation}
-where $\iota_a:a\to a+b\leftarrow b:\iota_b$ are the sum inclusions in $\A$ and the sum on the second variable is in the fibre $F(a+b)$.
+where $\iota_a:a\to a+b\leftarrow b:\iota_b$ are the sum inclusions in $\A$ and the sum on the second variable is in the fiber $F(a+b)$.
 
@@
 Notice a subtlety in the above formulation.
-\cref{lem:MonGroth} provides a specific monoidal structure on the fibres which becomes \cref{eq:explicitstructure1} when the base $\A$ is cocartesian monoidal.
-If this fibrewise monoidal structure happens to itself be cocartesian, then it is necessarily isomorphic to any other cocartesian monoidal structure on the fibres, by the universal property of colimits.
+\cref{lem:MonGroth} provides a specific monoidal structure on the fibers which becomes \cref{eq:explicitstructure1} when the base $\A$ is cocartesian monoidal.
+If this fibrewise monoidal structure happens to itself be cocartesian, then it is necessarily isomorphic to any other cocartesian monoidal structure on the fibers, by the universal property of colimits.
 Therefore, we can simplify the above assumption to that in \cref{thm:equiv} without having to specify that the structures came from monoidality of the pseudofunctor, although we \emph{will} use the formulation of coproducts and initial object in terms of the monoidal structure of $F$.
@@
  This is \cite[Proposition~4.4]{Gray}.
-The left adjoint $L\maps\A\to\X$ maps an object $a$ to the initial object in its fibre $\X_a$, denoted by $\bot_a$.
+The left adjoint $L\maps\A\to\X$ maps an object $a$ to the initial object in its fiber $\X_a$, denoted by $\bot_a$.
 By construction, $U(L(a))=U(\bot_a)=a$.
@@
  \end{equation}
-where $\mathrm{Cocart}(f,\bot_a)$ is the cocartesian lifting of $\bot_a$ along $f$ and $\chi_a$ is the unique isomorphism between the initial objects in the fibre above $a'$ since $f_!$ preserves them.
+where $\mathrm{Cocart}(f,\bot_a)$ is the cocartesian lifting of $\bot_a$ along $f$ and $\chi_a$ is the unique isomorphism between the initial objects in the fiber above $a'$ since $f_!$ preserves them.
 \end{proof}
@@
 describes the construction of the adjunction from the original $F$.
-Explicitly, the left adjoint picks the initial object in the fibre $L(a)=(a,\bot_a)$, also expressed as $F(!_a)\circ\phi_0(*)$ according to \cref{eq:explicitstructure1} for $(\phi,\phi_0)$ the monoidal structure of $F$.
+Explicitly, the left adjoint picks the initial object in the fiber $L(a)=(a,\bot_a)$, also expressed as $F(!_a)\circ\phi_0(*)$ according to \cref{eq:explicitstructure1} for $(\phi,\phi_0)$ the monoidal structure of $F$.
 %Christina: If each adjoint picks one isomorphic initial object, can we choose the one with that choice?
@@
 \end{equation}
-with $x\in F(m)$; recall that the reindexing functors $F(i),F(o)$ preserve all finite colimits across the fibre categories.
+with $x\in F(m)$; recall that the reindexing functors $F(i),F(o)$ preserve all finite colimits across the fiber categories.
 Finally, the 2-morphisms of this double category in this context unravel as follows
@@
 \end{gather}
-in the fibre category $F(m')$, by composition in the Grothendieck category \cref{eq:compGrothcat}.
+in the fiber category $F(m')$, by composition in the Grothendieck category \cref{eq:compGrothcat}.
 Since both morphisms emanate from the mapped initial object in $F(m')$ under the finite-colimit-preserving reindexing functors, they are the unique such into $x'$ therefore this gives no extra conditions; similarly for the equality including $o,o'$.
@@
 The left-hand side isomorphism is due to pseudonaturality of $\phi$ whereas the right-hand side isomorphism follows from universal properties and pseudofunctoriality of $F$.
-Regarding identities, the identity horizontal 1-cell $U_m$ in $_L\lCsp(\inta F)$ is $\cspn{(m,\bot_m)}{(m,\bot_m)}{(m,\bot_m)}{}{}$ with $1_m$ as the $A$-component and isomorphisms between initial objects in the fibres.
+Regarding identities, the identity horizontal 1-cell $U_m$ in $_L\lCsp(\inta F)$ is $\cspn{(m,\bot_m)}{(m,\bot_m)}{(m,\bot_m)}{}{}$ with $1_m$ as the $A$-component and isomorphisms between initial objects in the fibers.
 Thus $\lE(U_m)$ is the identity cospan in $A$ together with the `initial decoration' $\bot_m\in F(m)$, and so is $U_{\mathbb{E}(m)}$ as in \cref{eq:UFCsp}.
@@
 In fact, the double functor $\lE\maps _L\lCsp(\inta F)\to F\lCsp$ as defined above is bijective on objects and vertical 1-cells (trivially as an identity functor), and is also bijective on horizontal 1-cells and on 2-morphisms.
-Indeed, for \cref{eq:scsphor1cell}, the unique maps from the initial objects in the fibres provide no actual extra information, and similarly for 2-cells all extra data in \cref{eq:2morphismLCspintaF} is uniquely determined and \cref{eq:Grothcommutativity} holds automatically as discussed above.
+Indeed, for \cref{eq:scsphor1cell}, the unique maps from the initial objects in the fibers provide no actual extra information, and similarly for 2-cells all extra data in \cref{eq:2morphismLCspintaF} is uniquely determined and \cref{eq:Grothcommutativity} holds automatically as discussed above.
 As a result, we have a double isomorphism $$_L\lCsp(\inta F) \cong F\lCsp.$$
@@
 The category $\X$ is called the \textbf{total} category and $\A$ is called the \textbf{base} category of the opfibration.
-For any $a\in\A$, the \textbf{fibre category} $\X_a$ consists of all objects that map to $a$ and \define{vertical} morphisms between them, i.e., morphisms mapping to $1_a$.
+For any $a\in\A$, the \textbf{fiber category} $\X_a$ consists of all objects that map to $a$ and \define{vertical} morphisms between them, i.e., morphisms mapping to $1_a$.
 
 Assuming the axiom of choice, we may select a cocartesian lifting of each morphism $f\maps a\to b$ in $\A$ to each $x\in\X _a$, denoted by $\mathrm{Cocart}(f,x)\maps x\to f_!(x)$, rendering $U$ a so-called \textbf{cloven} opfibration.
-This choice induces \textbf{reindexing functors} $f_!\maps\X _a\to\X _b$ between the fibre categories, which by the lifting's universal property come equipped with natural isomorphisms $(1_a)_!\cong 1_{\X _a}$ and $(f\circ g)_!\cong f_!\circ g_!$.
+This choice induces \textbf{reindexing functors} $f_!\maps\X _a\to\X _b$ between the fiber categories, which by the lifting's universal property come equipped with natural isomorphisms $(1_a)_!\cong 1_{\X _a}$ and $(f\circ g)_!\cong f_!\circ g_!$.
 With the help of these, any cloven opfibration $U \maps \X \to \A$ gives a pseudofunctor $F \maps \A \to \Cat$, where $\A$ viewed as a 2-category with trivial 2-cells, $F(a) = \X_a$ for each object $a \in \A$, and $F(f) = f_!$ for each morphism $f$ in $\A$.
@@
 \end{equation}
-This is an opfibred category over $\A$ via the obvious forgetful functor, with fibre categories $(\inta F)_a=F(a)$ and reindexing functors $f_!=F(f)$.
+This is an opfibred category over $\A$ via the obvious forgetful functor, with fiber categories $(\inta F)_a=F(a)$ and reindexing functors $f_!=F(f)$.
 \end{defn}

### 2020-12-07 cospans.tex
going over proof in Appendix B

@@
 \begin{equation}\label{eq:mapofdec}
-\begin{tikzpicture}[scale=1.5]
+\begin{tikzpicture}[scale=1.5,baseline=(current bounding box.center)]
 \node (A) at (0,0.5) {$a$};
@@
  \end{tikzcd}\;=\;
- \begin{tikzcd}[column sep=.4in]
+ \begin{tikzcd}[column sep=.3in]
 a\ar[r,"i"]\ar[dd,"{f'f}"'] & m\ar[dd,"{h'h}"] & b\ar[l,"o"']\ar[dd,"{g'g}"]  & x\in F(m) \\
@@
 where if $\tau \colon F(h)(x) \to x'$ and $\tau' \colon F(h')(x') \to x''$ are the decoration morphisms, 
-$$F(h'h)(x)\cong F(h')F(h)(x)\xrightarrow{F(h')(\tau)}F(h')(x')\xrightarrow{\tau'}x''$$ is the decoration of the composite.
+\begin{equation}\label{eq:tauofverticalcomposite}
+F(h'h)(x)\cong F(h')F(h)(x)\xrightarrow{F(h')(\tau)}F(h')(x')\xrightarrow{\tau'}x''
+\end{equation}
+is the decoration of the composite.
 The source and target functors map an $F$-decorated cospan to the source and target of the cospan and a map of decorated cospans \cref{eq:mapofdec} to $f$ and $g$ respectively.
@@
 \begin{equation}\label{eq:horizontalcompo}
-\begin{tikzpicture}[scale=1.5]
+\begin{tikzpicture}[scale=1.5,baseline=(current bounding box.center)]
 \node (A) at (0,0.5) {$a$};
@@
 together with the decoration morphism $\tau_{\beta \odot \alpha} \colon F(h_1 +_g h_2)(y \odot x) \to (y' \odot x')$ given by the diagram:
-\[
-\begin{tikzpicture}[scale=1.7]
+\begin{equation}\label{eq:decohorizontalcompo}
+\begin{tikzpicture}[scale=1.7,baseline=(current bounding box.center)]
 \node (A) at (4.75,0) {$\scriptstyle\Downarrow \tau_\alpha \times \tau_\beta$};
@@
 \end{tikzpicture}
-\]
+\end{equation}
 where the middle isomorphism is due to pseudonaturality of $\phi$ and the right-hand side isomorphism is due to pseudofunctoriality of $F$.
@@
 \begin{equation}\label{eq:decoiso}
-\begin{tikzpicture}[scale=1.7]
+\begin{tikzpicture}[scale=1.7,baseline=(current bounding box.center)]
 \node (A) at (3.75,0) {$\scriptstyle{\cong}$};
@@
 \end{comment}
-Finally, the symmetric monoidal structure of $F\lCsp_1$ is inherited from that in $\A$ and $F$, with braiding the cospan isomorphism
+Finally, the symmetric monoidal structure of $F\lCsp_1$ is inherited from that in $\A$ and $F$, with braiding $\beta\maps M_1\ot M_2\to M_2\ot M_1$ the cospan isomorphism
 %To finish showing that $F\lCsp_1$ is symmetric monoidal, we next define the braiding of $F\lCsp_1$.
@@
 %\]
-\begin{displaymath}
+\begin{equation}\label{eq:braidingFCsp1}
  \begin{tikzcd}[column sep=.25in]
-a_1+a_2\ar[rr,"i_1+i_2"]\ar[d,"\stackrel{\beta}{\cong}"'] && m_1+m_2\ar[d,"\stackrel{\beta}{\cong}"'] && b_1+b_2\ar[ll,"o_1+o_2"']\ar[d,"\stackrel{\beta}{\cong}"] &&1\ar[r,"x_1\times x_2"] & F(m_1)\times F(m_2)\ar[r,"\phi_{m_1,m_2}"] & F(m_1+m_2) \\
-a_2+a_1\ar[rr,"i_2+i_1"'] && m_2+m_1 && b_2+b_1\ar[ll,"o_2+o_1"] &&\one \ar[r,"x_2\times x_1"] & F(m_2)\times F(m_1)\ar[r,"\phi_{m_2,m_1}"] & F(m_2+m_1)
+a_1+a_2\ar[rr,"i_1+i_2"]\ar[d,"\stackrel{\beta}{\cong}"'] && m_1+m_2\ar[d,"\stackrel{\beta}{\cong}"'] && b_1+b_2\ar[ll,"o_1+o_2"']\ar[d,"\stackrel{\beta}{\cong}"] &\one\ar[r,"x_1\times x_2"] & F(m_1)\times F(m_2)\ar[r,"\phi_{m_1,m_2}"] & F(m_1+m_2) \\
+a_2+a_1\ar[rr,"i_2+i_1"'] && m_2+m_1 && b_2+b_1\ar[ll,"o_2+o_1"] &\one \ar[r,"x_2\times x_1"] & F(m_2)\times F(m_1)\ar[r,"\phi_{m_2,m_1}"] & F(m_2+m_1)
  \end{tikzcd}
-\end{displaymath}
-together with the decoration isomorphism formed by \cref{eq:braidedpseudofun} of the symmetric monoidal pseudofunctor.
+\end{equation}
+together with the decoration isomorphism 
+\begin{equation}\label{eq:decobraiding}
+ \begin{tikzcd}
+  1\ar[r,"x_1\times x_2"]\ar[dr,"x_2\times x_1"'] & F(m_1)\times F(m_2)\ar[d,"\beta"']\ar[r,"\phi_{m_1,m_2}"]\ar[dr,phantom,"\stackrel{\cref{eq:braidedpseudofun}}{\cong}"] & F(m_1+m_2)\ar[d,"F(\beta)"] \\
+  & F(m_2)\times F(m_1)\ar[r,"\phi_{m_2,m_1}"'] & F(m_2+m_1)
+ \end{tikzcd}
+\end{equation}
 %$F(\beta)(x_1+x_2) \to x_2+x_1$.
@@
 For any appropriate four decorated cospans
-\begin{gather*}
+\begin{gather}\label{eq:4deccospans}
 M_1=\left(a\xrightarrow{i_1}m_1\xleftarrow{o_1}b,x_1\in F(m_1)\right),\;\; M_2=\left(b\xrightarrow{i_2}m_2\xleftarrow{o_2}c,x_2\in F(m_2)\right) \\
-N_1=\left(a'\xrightarrow{i'_1}n_1\xleftarrow{o'_1}b',y_1\in F(n_1)\right),\;\; N_2=\left(b'\xrightarrow{i'_2}n_2\xleftarrow{o'_2}c',y_2\in F(n_2)\right)
-\end{gather*}
+N_1=\left(a'\xrightarrow{i'_1}n_1\xleftarrow{o'_1}b',y_1\in F(n_1)\right),\;\; N_2=\left(b'\xrightarrow{i'_2}n_2\xleftarrow{o'_2}c',y_2\in F(n_2)\right)\nonumber
+\end{gather}
 first tensoring $M_1\ot N_1$, $M_2\ot N_2$ by \cref{eq:tensordecoration} and then horizontally composing them by \cref{eq:dcospanscomposition} gives
-\begin{displaymath}
+\begin{equation}\label{eq:bigeq1}
 \scalebox{.8}{\begin{tikzcd}[column sep={.6in,between origins},ampersand replacement=\&]
-\&\& (m_1+n_1)+_{b{+}b'}(m_2+n_2) \&\& \\
+\&\& (m_1+n_1)+_{b{+}b'}(m_2+n_2)\ar[dd,phantom,near start,"\upback"] \&\& \\
 \& m_1+n_1\ar[ur] \&\& m_2+n_2\ar[ul] \& \\
 a+a'\ar[ur,"{i_1+i'_1}"] \&\& b+b'\ar[ul,"{o_1+o'_1}"']\ar[ur,"{i_2+i'_2}"] \&\& c+c'\ar[ul,"{o_2+o'_2}"']
-\end{tikzcd}}
+\end{tikzcd}}\hspace{-.2in}
 \scalebox{.8}{\begin{tikzcd}[ampersand replacement=\&,column sep=.5in]
-\one \ar[ddrr,dashed,"{(x_1\oplus y_1)\odot(x_2\oplus y_2)}"']\ar[r,"x_1{\times}y_1{\times}x_2{\times}y_2"] \& F(m_1){\times}F(n_1){\times}F(m_2){\times}F(n_2)\ar[r,"\phi_{m_1,n_1}\times\phi_{m_2,n_2}"] \& F(m_1{+}n_1){\times}F(m_2{+}n_2) \ar[d,"\phi_{m_1+n_1,m_2+n_2}"] \\
+\one \ar[ddrr,dashed,"{(x_2\oplus y_2)\odot(x_1\oplus y_1)}"']\ar[r,"x_1{\times}y_1{\times}x_2{\times}y_2"] \& F(m_1){\times}F(n_1){\times}F(m_2){\times}F(n_2)\ar[r,"\phi_{m_1,n_1}\times\phi_{m_2,n_2}"] \& F(m_1{+}n_1){\times}F(m_2{+}n_2) \ar[d,"\phi_{m_1+n_1,m_2+n_2}"] \\
 \&\& F(m_1+n_1+m_2+n_2)\ar[d,"F\psi"] \\
@@
 \end{tikzcd}}
-\end{displaymath}
+\end{equation}
 If we first horizontally compose $M_2\odot M_1$, $N_2\odot N_1$ and then tensor the result, we obtain
-\begin{displaymath}
+\begin{equation}\label{eq:bigeq2}
   \scalebox{.8}{\begin{tikzcd}[column sep=.3in,ampersand replacement=\&]
@@
  \&\& c+c'\ar[uul]%,"{u_{m_2}o_2+u_{n_2}o'_2}"']  
+ \end{tikzcd}}\hspace{-.2in}
+ \scalebox{.8}{\begin{tikzcd}[ampersand replacement=\&,column sep=.4in]
+\one \ar[ddrr,dashed,"{(x_2\odot x_1)\oplus(y_2\odot y_1)}"']\ar[r,"x_1{\times}x_2{\times}y_1{\times}y_2"] \& F(m_1){\times}F(m_2){\times}F(n_1){\times}F(n_2)\ar[r,"\phi_{m_1,m_2}\times\phi_{n_1,n_2}"] \& F(m_1{+}m_2){\times}F(n_1{+}n_2) \ar[d, "F\psi\times F\psi"] \\
+\&\& F(m_1+_bm_2)\times F(n_1+_{b'}n_2)\ar[d,"\phi_{m_1+_bm_2,n_1+_{b'}n_2}"] \\
+\&\& F((m_1+_bm_2)+(n_1+_{b'}n_2))
 \end{tikzcd}}
- \scalebox{.8}{\begin{tikzcd}[ampersand replacement=\&,column sep=.4in]
-\one \ar[ddrr,dashed,"{(x_1\odot x_2)\oplus(y_1\odot y_2)}"']\ar[r,"x_1{\times}x_2{\times}y_1{\times}y_2"] \& F(m_1){\times}F(m_2){\times}F(n_1){\times}F(n_2)\ar[r,"\phi_{m_1,m_2}\times\phi_{n_1,n_2}"] \& F(m_1{+}m_2){\times}F(n_1{+}n_2) \ar[d, "F\psi\times F\psi"] \\
-\&\& F(m_1+_bm_2)\times F(n_1+_{b'}n_2)\ar[d,"\phi_{m_1+_bm_2,n_1+_{b'}n_2}"] \\
-\&\& F((m_1+_bm_2)+F(n_1+_{b'}n_2))
+\end{equation}
+where the legs of the cospan are the sums of the dashed ones of the appropriate diagrams \cref{eq:dcospanscomposition}.
+Thus the (globular) cospan isomorphism is the canonical universal map between the colimit of the same diagram obtained in two different ways $\hat{\chi}\colon(m_1+n_1)+_{b+b'}(m_2+n_2)\cong(m_1+_b m_2)+(n_1+_{b'}n_2)$, and the decoration isomorphism can be built in a similar way using coherent isomorphisms as follows:
+\begin{equation}\label{eq:interchangedeco}
+ \scalebox{.75}{\begin{tikzcd}[ampersand replacement=\&,column sep=.3in,row sep=.1in]
+\& F(m_1)\times F(n_2)\times F(m_2)\times F(n_2)\ar[dd,"1\times\beta\times1"]\ar[ddrr,phantom,"\cong"]\ar[rr,"\phi_{m_1,n_1}\times\phi_{m_2,n_2}"] \&\& F(m_1+n_1)\times F(m_2+n_2)\ar[rr,"\phi_{m_1+n_1,m_2+n_2}"] \&\& F(m_1+n_1+m_2+n_2)\ar[dd,"F\psi"]\ar[ddll,"F(1\times\beta\times1)"'] \\
+\one \ar[ur,"{x_1\times y_1\times x_2\times y_2}"]\ar[dr,"{x_1\times x_2\times y_1\times y_2}"'] \&\&\&\& \\
+\& F(m_1)\times F(m_2)\times F(n_1)\times F(n_2)\ar[dd,"\phi_{m_1,m_2}\times\phi_{n_1,n_2}"']\&\& F(m_1+m_2+n_1+n_2)\ar[ddrr,"F(\psi+\psi)"']\ar[dd,phantom,"\stackrel{\cref{eq:pseudonaturality}}{\cong}"] \ar[rr,phantom,"\cong"]\&\& F((m_1+n_1)+_{b+b'}(m_2+n_2))\ar[dd,"F(\hat{\chi})"] \\
+\hole \\
+\& F(m_1+m_2)\times F(n_1+n_2)\ar[uurr,"\phi_{m_1+m_2,n_1+n_2}"']\ar[rr,"F\psi\times F\psi"'] \&\& F(m_1+_bm_2)\times F(n_1+_{b'}n_2)\ar[rr,"\phi_{m_1+_b m_2,n_1+_{b'}n_2}"'] \&\& F((m_1+_bm_2)+(n_1+_{b'}n_2))
 \end{tikzcd}}
-\end{displaymath}
-where the legs of the cospan are the sums of the dashed ones of the appropriate diagrams \cref{eq:dcospanscomposition}.
-Thus the (globular) cospan isomorphism is the canonical universal map between the colimit of the same diagram obtained in two different ways $(m_1+n_1)+_{b+b'}(m_2+n_2)\cong(m_1+_b m_2)+(n_1+_{b'}n_2)$, and the decoration isomorphism can be built in a similar way using coherent isomorphisms essentially due to pseudonaturality of $\phi$.
-{\chris Should we give more details here?}
+\end{equation}
+where the left-hand side isomorphism combines pseudoassociativity \cref{eq:omega} and braided monoidal structure \cref{eq:braidedpseudofun} of the pseudofunctor $F$, and the right hand side follows from the universal property of colimits and pseudofunctoriality of $F$.
 Similarly, for units $U_{a+b}$ and $U_a\ot U_b$ it is easy to see that as cospans they are both the identity $1_{a+b}:a+b\to a+b\leftarrow a+b:1_{a+b}$, and there is a canonical isomorphism between their trivial decorations \cref{eq:UFCsp}, namely $F(!_{a+b})\phi_0\cong\phi_{a,b}(F(!_a)\times F(!_b))(\phi_0\times\phi_0)$ via the structure isomorphisms for $(\phi,\phi_0)$.
@@
  natural in $f$ and $g$.
-A \define{braided lax monoidal} pseudofunctor between braided monoidal bicategories comes with an appropriate invertible modification with components %$F(\beta_{a,b})\circ \phi_{a,b}\cong\phi_{b,a}\circ \beta_{Fa,Fb}$.
+A \define{braided lax monoidal} pseudofunctor between braided monoidal bicategories comes with an invertible modification with components
 \begin{equation}\label{eq:braidedpseudofun}
@@
 \end{equation}
+subject to two axioms found e.g. in \cite[Definition 14]{DS}.
 A \define{sylleptic lax monoidal} pseudofunctor satisfies one extra condition and a \define{symmetric lax monoidal} pseudofunctor between symmetric monoidal bicategories is just a sylleptic one.
@@
 All relevant structure for decorated cospans is as described in \cref{thm:decorated_cospans,DC}. The coherence law that we check says that this diagram commutes:
-\[
+\begin{equation}\label{eq:thisdiagram}
 \begin{tikzpicture}[scale=1.5]
@@
 \end{tikzpicture}
-\]
-First of all, if we only consider the underlying cospans without their decorations, we obtain the following `flattened' commutative diagram in the symmetric monoidal double category $\lCsp(\A)$, where the top and the bottom cospans coincide:
+\end{equation}
+where $M_1,M_2,N_1,N_2$ are as in \cref{eq:4deccospans}, $\chi$ is as described right below therein and $\beta$ is the braiding defined as in \cref{eq:braidingFCsp1} -- although the letter $\beta$ is also used for the braiding in $\A$.
+First of all, if we only consider the underlying cospans without their decorations, we obtain the following `flattened' commutative diagram in $\A$ -- which verifies the corresponding axiom for the symmetric monoidal double category $\lCsp(\A)$:
+%%% Kenny any good reference for that?
+Not just cospans, which I can find in Niefield, but the interchange law as well for cospans only.
+Is it in your thesis?
+Somewhere in Shulman?
+Had a look but couldn't dig up anything...I know it is easy but would look nicer if we had some reference here
 \[
@@
             (a) edge node[left]{$\beta$} (a2)
-            (b) edge node[left]{$\beta \odot \beta$} (b2)
+            (b) edge node[left]{$\beta +_\beta \beta$} (b2)
 %(b) edge node[right]{$\tau_1$} (b2)
@@
 	\]
-where $\beta$ is the braiding of the symmetric monoidal category $\A$, $\hat{\chi}$ is the globular 2-morphism interchanging the tensor product and horizontal composition of the symmetric monoidal double category $\lCsp(\A)$, and the inwards pointing morphisms are natural maps from the each cospan's feet to its apex.
-
-For the decorations, each of the four maps of cospans constituting the above diagram has an associated decoration isomorphism with it, which we label with $\tau_i$ for $i=1,2,3,4$.
+The top and the bottom cospans coincide, and $\hat{\chi}$ is the canonical isomorphism by the universal property of colimits
+%globular 2-morphism interchanging the tensor product and horizontal composition of the symmetric monoidal double category $\lCsp(\A)$,
+and the inwards pointing morphisms are natural maps from the each cospan's feet to its apex.
+
+Regarding decorations, each of the above four maps of cospans has an associated map, which we label with $\tau_i$ for $i=1,2,3,4$, between the corresponding decorations:
 \[
@@
 			\node (b) at (1,0) {$(m_1+n_1) +_{(b+b')} (m_2+n_2)$};
-			\node (c) at (8,0) {$(x_1\oplus y_1) \odot (x_2\oplus y_2) \in F((m_1+n_1)+_{b+b'}(m_2+n_2))$};
+			\node (c) at (8,0) {$ (x_2\oplus y_2)\odot (x_1\oplus y_1)  \in F((m_1+n_1)+_{b+b'}(m_2+n_2))$};
 %			\node (a2) at (-4,1) {$a'+a$};
 			\node (b2) at (1,1) {$(n_1+m_1) +_{(b'+b)} (n_2+m_2)$};
-			\node (c2) at (8,1) {$(y_1\oplus x_1) \odot (y_2\oplus x_2) \in F((n_1+m_1)+_{b'+b}(n_2+m_2))$};
+			\node (c2) at (8,1) {$(y_2\oplus x_2)\odot(y_1\oplus x_1) \in F((n_1+m_1)+_{b'+b}(n_2+m_2))$};
 %                            \node (a3) at (-4,2) {$a'+a$};
 			\node (b3) at (1,2) {$(n_1 +_{b'} n_2) + (m_1 +_b m_2)$};
-			\node (c3) at (8,2) {$(y_1 \odot y_2) \oplus (x_1 \odot x_2) \in F((n_1+_{b'} n_2)+(m_1+_b m_2))$};
+			\node (c3) at (8,2) {$(y_2 \odot y_1) \oplus (x_2 \odot x_1) \in F((n_1+_{b'} n_2)+(m_1+_b m_2))$};
 %                                \node (a5) at (-4,-1) {$a+a'$};
 			\node (b5) at (1,-1) {$(m_1+_b m_2) + (n_1+_{b'} n_2)$};
-			\node (c5) at (8,-1) {$(x_1 \odot x_2) \oplus (y_1 \odot y_2) \in F((m_1+_b m_2)+(n_1+_{b'} n_2))$};
+			\node (c5) at (8,-1) {$(x_2 \odot x_1) \oplus (y_2 \odot y_1) \in F((m_1+_b m_2)+(n_1+_{b'} n_2))$};
 %                                \node (a6) at (-4,-2) {$a'+a$};
 			\node (b6) at (1,-2) {$(n_1 +_{b'} n_2) + (m_1 +_b m_2)$};
-			\node (c6) at (8,-2) {$(y_1 \odot y_2) \oplus (x_1 \odot x_2) \in F((n_1+_{b'} n_2)+(m_1+_b m_2))$};
+			\node (c6) at (8,-2) {$(y_2 \odot y_1) \oplus (x_2 \odot x_1) \in F((n_1+_{b'} n_2)+(m_1+_b m_2))$};
 			\path[->,font=\scriptsize,>=angle 90]
@@
 %                                (a) edge node[left]{$\beta$} (a2)
-                                (b) edge node[left]{$\beta \odot \beta$} (b2)
+                                (b) edge node[left]{$\beta +_\beta \beta$} (b2)
 (b) edge node[right]{$\tau_1$} (b2)
@@
 	\]
-Explicitly, the four decoration isomorphisms are given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$\tau_1 \colon F(\beta \odot \beta)((x_1\oplus y_1)\odot(x_2\oplus y_2)) \to (y_1\oplus x_1)\odot(y_2\oplus x_2)$};
-\node (B) at (0,-.5) {$\tau_2 \colon F(\hat{\chi})((y_1 \oplus x_1)\odot(y_2 \oplus x_2)) \to (y_1\odot y_2) \oplus (x_1\odot x_2)$};
-\node (C) at (0,-1) {$\tau_3 \colon F(\hat{\chi})((x_1 \oplus y_1)\odot(x_2 \oplus y_2)) \to (x_1\odot x_2) \oplus (y_1\odot y_2)$};
-\node (D) at (0,-1.5) {$\tau_4 \colon F(\beta)((x_1\odot x_2)\oplus(y_1\odot y_2)) \to (y_1\odot y_2)\oplus(x_1\odot x_2)$};
+and are explicitly appropriate isomorphisms of the form:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$\tau_1 \colon F(\beta +_\beta \beta)((x_2\oplus y_2)\odot(x_1\oplus y_1)) \to (y_2\oplus x_2)\odot(y_1\oplus x_1)$};
+\node (B) at (0,-.5) {$\tau_2 \colon F(\hat{\chi})((y_2 \oplus x_2)\odot(y_1 \oplus x_1)) \to (y_2\odot y_1) \oplus (x_2\odot x_1)$};
+\node (C) at (0,-1) {$\tau_3 \colon F(\hat{\chi})((x_2 \oplus y_2)\odot(x_1 \oplus y_1)) \to (x_2\odot x_1) \oplus (y_2\odot y_1)$};
+\node (D) at (0,-1.5) {$\tau_4 \colon F(\beta)((x_2\odot x_1)\oplus(y_2\odot y_1)) \to (y_2\odot y_1)\oplus(x_2\odot x_1)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-The morphisms $\tau_1$ and $\tau_2$ may be composed as $$\tau_2 F(\hat{\chi})(\tau_1) \colon F(\hat{\chi})F(\beta \odot \beta)((x_1 \oplus y_1) \odot (x_2 \oplus y_2)) \to (y_1 \odot y_2) \oplus (x_1 \odot x_2)$$ which is given by the diagram:
-\[
-\begin{tikzpicture}[scale=1.7]
+Firstly, performing the (vertical) composition of $\chi$ and $\beta$ of $\cref{eq:thisdiagram}$ gives the composite decoration $\tau_4\tau_3$ computed by the formula \cref{eq:tauofverticalcomposite} to be
+\begin{displaymath}
+\scalebox{.8}{$F(\beta\hat{\chi})((x_2 \oplus y_2)\odot(x_1 \oplus y_1))\cong F(\beta)(F\hat{\chi})((x_2 \oplus y_2)\odot(x_1 \oplus y_1))\xrightarrow{F(\beta)(\tau_3)}F(\beta)((x_2\odot x_1) \oplus (y_2\odot y_1))\xrightarrow{\tau_4}(y_2 \odot y_1) \oplus (x_2 \odot x_1)$}
+\end{displaymath}
+Using the formulas for the involved decorations \cref{eq:bigeq1,eq:bigeq2}, as well as the decoration morphisms of $\chi$ \cref{eq:interchangedeco} and $\beta$ \cref{eq:decobraiding}, we form:
+\[
+\begin{tikzpicture}[scale=1.6]
 %\node (A) at (3.85,0) {$\scriptstyle{\cong}$};
 %\node (A') at (3.85,-1) {$\scriptstyle{\cong}$};
+\node () at (12,-1) {$\scriptstyle\cong$};
 \node (D) at (3,-0.5) {$\scriptstyle{\one}$};
 \node (E) at (6.75,0.5) {$\scriptstyle{F(m_1 + n_1) \times F(m_2+n_2)}$};
-\node () at (5.5,0) {$\scriptstyle\stackrel{\cref{eq:braidedpseudofun}}{\cong}$};
-\node () at (7.875,0) {$\scriptstyle\stackrel{\cref{eq:pseudonaturality}}{\cong}$};
-\node () at (10.25,0) {$\scriptstyle{\cong}$};
-\node () at (7.875,-1) {$\scriptstyle{\cong}$};
-\node (E') at (6.75,-0.5) {$\scriptstyle{F(n_1+m_1) \times F(n_2+m_2)}$};
+\node () at (10.25,-1) {$\scriptstyle\stackrel{\cref{eq:braidedpseudofun}}{\cong}$};
+\node () at (7.875,0) {$\scriptstyle\stackrel{\cref{eq:interchangedeco}}{\cong}$};
+\node (E') at (6.75,-0.5) {$\scriptstyle{F(m_1+m_2) \times F(n_1+n_2)}$};
 \node (B) at (9,0.5) {$\scriptstyle{F((m_1+n_1)+(m_2+n_2))}$};
-\node (B') at (9,-0.5) {$\scriptstyle{F((n_1+m_1)+(n_2+m_2))}$};
+\node (B') at (9,-0.5) {$\scriptstyle{F(m_1+_b m_2)\times F(n_1+_{b'}n_2)}$};
 \node (C) at (11.5,0.5) {$\scriptstyle{F((m_1+n_1)+_{b+b'}(m_2+n_2))}$};
-\node (C') at (11.5,-0.5) {$\scriptstyle{F((n_1+m_1)+_{b'+b}(n_2+m_2))}$};
+\node (C') at (11.5,-0.5) {$\scriptstyle{F((m_1+_b m_2)+ (n_1+_{b'} n_2))}$};
 \node (G) at (4.25,0.5) {$\scriptstyle{F(m_1) \times F(n_1) \times F(m_2) \times F(n_2)}$};
-\node (G') at (4.25,-0.5) {$\scriptstyle{F(n_1) \times F(m_1) \times F(n_2) \times F(m_2)}$};
+\node (G') at (4.25,-0.5) {$\scriptstyle{F(m_1) \times F(m_2) \times F(n_1) \times F(n_2)}$};
 \node (G'') at (4.25,-1.5) {$\scriptstyle{F(n_1) \times F(n_2) \times F(m_1) \times F(m_2)}$};
 \node (E'') at (6.75,-1.5) {$\scriptstyle{F(n_1+n_2) \times F(m_1+m_2)}$};
-\node (B'') at (9,-1.5) {$\scriptstyle{F((n_1+n_2)+ (m_1+ m_2))}$};
+\node (B'') at (9,-1.5) {$\scriptstyle{F(n_1+_{b'}n_2)+F(m_1+_b m_2)}$};
 \node (C'') at (11.5,-1.5) {$\scriptstyle{F((n_1+_{b'}n_2)+(m_1+_b m_2))}$};
 \node (X) at (3.4,0.2) {$\scriptscriptstyle{x_1 \times y_1 \times x_2 \times y_2}$};
-\node (X') at (3.4,-0.35) {$\scriptscriptstyle{y_1 \times x_1 \times y_2 \times x_2}$};
+\node (X') at (3.4,-0.35) {$\scriptscriptstyle{x_1 \times x_2 \times y_1 \times y_2}$};
 \node (X'') at (3.4,-1.2) {$\scriptscriptstyle{y_1 \times y_2 \times x_1 \times x_2}$};
 \path[->,font=\scriptsize,>=angle 90]
-(B) edge node [fill=white] {$F(\beta+\beta)$} (B')
-(E) edge node [fill=white] {$F(\beta) \times F(\beta)$} (E')
+(B') edge node [fill=white] {$\beta$} (B'')
 (E) edge node [above] {$\phi_{m_1+n_1,m_2+n_2}$} (B)
-(E'') edge node [above] {$\phi_{n_1+n_2,m_1+m_2}$} (B'')
-(E') edge node [above] {$\phi_{n_1+m_1,n_2+m_2}$} (B')
+(E'') edge node [below] {$F\psi\times F\psi$} (B'')
+(E') edge node [above] {$F\psi\times F\psi$} (B')
 (B) edge node [above] {$F(\psi)$} (C)
-(B'') edge node [above] {$F(\psi + \psi)$} (C'')
-(B') edge node [above] {$F(\psi)$} (C')
-(C) edge node [fill=white] {$F(\beta \odot \beta)$} (C')
-(C') edge node [fill=white] {$F(\hat{\chi})$} (C'')
+(B'') edge node [below] {$\phi_{n_1+_{b'}n_2,m_1+_bm_2}$} (C'')
+(B') edge node [above] {$\phi_{m_1+_bm_2,n_1+_{b'}n_2}$} (C')
+(C) edge node [fill=white] {$F(\hat{\chi})$} (C')
+(C') edge node [fill=white] {$F(\beta)$} (C'')
 (G) edge node [above] {$\phi_{m_1,n_1} {\times} \phi_{m_2,n_2}$} (E)
-(G'') edge node [above] {$\phi_{n_1,n_2} {\times} \phi_{m_1,m_2}$} (E'')
-(G') edge node [above] {$\phi_{n_1,m_1} \times \phi_{n_2,m_2}$} (E')
-(G) edge node [fill=white] {$\beta \times \beta$} (G')
-(G') edge node [fill=white] {$1 \times \beta \times 1$} (G'')
+(G'') edge node [below] {$\phi_{n_1,n_2} {\times} \phi_{m_1,m_2}$} (E'')
+(G') edge node [above] {$\phi_{m_1,m_2} \times \phi_{n_1,n_2}$} (E')
+(G) edge node [fill=white] {$1 \times \beta \times 1$} (G')
+(G') edge node [fill=white] {$\beta$} (G'')
 (D) edge[out=90,in=180] node [left,above] {$$} (G)
 (D) edge[out=270,in=180] node [left,above] {$$} (G'')
-(D) edge node [below] {$$} (G');
-\end{tikzpicture}
-\]
-and the morphisms $\tau_3$ and $\tau_4$ may be composed as $$\tau_4 F(\beta)(\tau_3) \colon F(\beta) F(\hat{\chi}) \colon F(\beta)F(\hat{\chi})((x_1 \oplus y_1)\odot(x_2 \oplus y_2)) \to (y_1 \odot y_2) \oplus (x_1 \odot x_2)$$ which is given by the diagram:
-\[
-\begin{tikzpicture}[scale=1.7]
+(D) edge node [below] {$$} (G')
+(C) edge[bend left=80] node [fill=white] {$F(\beta\hat{\chi})$} (C'')
+;
+\end{tikzpicture}
+\]
+{\chris Kenny please see difference in diagrams (the rightmost part is not important, just to make the two decoration isomorphism have the same border).
+The blue is the old one.
+The new diagram \cref{eq:interchangedeco} should be the one we disagreed, namely its codomain.
+But also on the down part of the diagram, coming from the decoration morphism of the braiding \cref{eq:decobraiding}, mine is much ``easier''.}
+{\color{blue}
+\[
+\begin{tikzpicture}[scale=1.6]
 %\node (A) at (3.85,0) {$\scriptstyle{\cong}$};
@@
 \node () at (10.25,-1) {$\scriptstyle{\cong}$};
-\node () at (7.875,0) {$\scriptstyle{\cong}$};
+\node () at (7.875,0) {$\scriptstyle\stackrel{\cref{eq:interchangedeco}}{\cong}$};
 \node (E') at (6.75,-0.5) {$\scriptstyle{F(m_1+m_2) \times F(n_1+n_2)}$};
@@
 \]
-
+}
+For the other (vertical) composition of \cref{eq:thisdiagram}, that of $\beta\odot\beta$ followed by $\chi$, the composite decoration $\tau_2\tau_1$ is
+\begin{displaymath}
+\scalebox{.8}{$F(\hat{\chi}(\beta +_\beta \beta))( (x_2 \oplus y_2)\odot (x_1 \oplus y_1))\cong F(\hat{\chi})F(\beta +_\beta \beta)( (x_2 \oplus y_2)\odot (x_1 \oplus y_1)) \xrightarrow{F(\hat{\chi})(\tau_1)}F(\hat{\chi})(y_2\oplus x_2)\odot(y_1\oplus x_1)\xrightarrow{\tau_2}(y_2 \odot y_1) \oplus (x_2 \odot x_1)$}
+\end{displaymath}
+Once again, using the tensor and composite formulas for decorations, as well the horizontal composite formulas \cref{eq:decohorizontalcompo}
+for $\beta\odot\beta$, the above is explicitly given by the pasted isomorphism:
+\[
+\begin{tikzpicture}[scale=1.6]
+%\node (A) at (3.85,0) {$\scriptstyle{\cong}$};
+%\node (A') at (3.85,-1) {$\scriptstyle{\cong}$};
+\node (D) at (3,-0.5) {$\scriptstyle{\one}$};
+\node (E) at (6.75,0.5) {$\scriptstyle{F(m_1 + n_1) \times F(m_2+n_2)}$};
+\node () at (5.5,0) {$\scriptstyle\stackrel{\cref{eq:braidedpseudofun}}{\cong}$};
+\node () at (7.875,0) {$\scriptstyle\stackrel{\cref{eq:pseudonaturality}}{\cong}$};
+\node () at (10.25,0) {$\scriptstyle{\cong}$};
+\node () at (7.875,-1) {$\scriptstyle\stackrel{\cref{eq:interchangedeco}}{\cong}$};
+\node () at (12,-1) {$\scriptstyle\cong$};
+\node (E') at (6.75,-0.5) {$\scriptstyle{F(n_1+m_1) \times F(n_2+m_2)}$};
+\node (B) at (9,0.5) {$\scriptstyle{F((m_1+n_1)+(m_2+n_2))}$};
+\node (B') at (9,-0.5) {$\scriptstyle{F((n_1+m_1)+(n_2+m_2))}$};
+\node (C) at (11.5,0.5) {$\scriptstyle{F((m_1+n_1)+_{b+b'}(m_2+n_2))}$};
+\node (C') at (11.5,-0.5) {$\scriptstyle{F((n_1+m_1)+_{b'+b}(n_2+m_2))}$};
+\node (G) at (4.25,0.5) {$\scriptstyle{F(m_1) \times F(n_1) \times F(m_2) \times F(n_2)}$};
+\node (G') at (4.25,-0.5) {$\scriptstyle{F(n_1) \times F(m_1) \times F(n_2) \times F(m_2)}$};
+\node (G'') at (4.25,-1.5) {$\scriptstyle{F(n_1) \times F(n_2) \times F(m_1) \times F(m_2)}$};
+\node (E'') at (6.75,-1.5) {$\scriptstyle{F(n_1+n_2) \times F(m_1+m_2)}$};
+\node (B'') at (9,-1.5) {$\scriptstyle{F(n_1+_{b'}n_2)+ F(m_1+_b m_2))}$};
+\node (C'') at (11.5,-1.5) {$\scriptstyle{F((n_1+_{b'}n_2)+(m_1+_b m_2))}$};
+\node (X) at (3.4,0.2) {$\scriptscriptstyle{x_1 \times y_1 \times x_2 \times y_2}$};
+\node (X') at (3.4,-0.35) {$\scriptscriptstyle{y_1 \times x_1 \times y_2 \times x_2}$};
+\node (X'') at (3.4,-1.2) {$\scriptscriptstyle{y_1 \times y_2 \times x_1 \times x_2}$};
+\path[->,font=\scriptsize,>=angle 90]
+(B) edge node [fill=white] {$F(\beta+\beta)$} (B')
+(E) edge node [fill=white] {$F(\beta) \times F(\beta)$} (E')
+(E) edge node [above] {$\phi_{m_1+n_1,m_2+n_2}$} (B)
+(E'') edge node [below] {$F\psi\times F\psi)$} (B'')
+(E') edge node [above] {$\phi_{n_1+m_1,n_2+m_2}$} (B')
+(B) edge node [above] {$F(\psi)$} (C)
+(B'') edge node [below] {$\phi_{n_1+_{b'}n_2,m_1+_{b}m_2}$} (C'')
+(B') edge node [above] {$F(\psi)$} (C')
+(C) edge node [fill=white] {$F(\beta +_\beta \beta)$} (C')
+(C') edge node [fill=white] {$F(\hat{\chi})$} (C'')
+(G) edge node [above] {$\phi_{m_1,n_1} {\times} \phi_{m_2,n_2}$} (E)
+(G'') edge node [below] {$\phi_{n_1,n_2} {\times} \phi_{m_1,m_2}$} (E'')
+(G') edge node [above] {$\phi_{n_1,m_1} \times \phi_{n_2,m_2}$} (E')
+(G) edge node [fill=white] {$\beta \times \beta$} (G')
+(G') edge node [fill=white] {$1 \times \beta \times 1$} (G'')
+(D) edge[out=90,in=180] node [left,above] {$$} (G)
+(D) edge[out=270,in=180] node [left,above] {$$} (G'')
+(D) edge node [below] {$$} (G')
+(C) edge[bend left=80] node [fill=white] {$F(\hat{\chi}(\beta+_\beta\beta))$} (C'')
+;
+\end{tikzpicture}
+\]
+{\chris The closing sentence for the proof to be complete should be that these two decorations are EQUAL for the diagram \cref{eq:thisdiagram} to commute!
+Right?
+Is the sentence below satisfactory Kenny?
+Do you see the logic?}
+
+The fact that these two pasted isomorphisms are equal follows from the axioms of a braided lax monoidal pseudofunctor and as a result, \cref{eq:thisdiagram} commutes and the axiom holds.
 \begin{comment}

### 2020-12-07 cospans.tex
Fixing small typos mainly in Appendix B

@@
  \scalebox{.75}{\begin{tikzcd}[ampersand replacement=\&,column sep=.3in,row sep=.1in]
-\& F(m_1)\times F(n_2)\times F(m_2)\times F(n_2)\ar[dd,"1\times\beta\times1"]\ar[ddrr,phantom,"\cong"]\ar[rr,"\phi_{m_1,n_1}\times\phi_{m_2,n_2}"] \&\& F(m_1+n_1)\times F(m_2+n_2)\ar[rr,"\phi_{m_1+n_1,m_2+n_2}"] \&\& F(m_1+n_1+m_2+n_2)\ar[dd,"F\psi"]\ar[ddll,"F(1\times\beta\times1)"'] \\
+\& F(m_1)\times F(n_1)\times F(m_2)\times F(n_2)\ar[dd,"1\times\beta\times1"]\ar[ddrr,phantom,"\cong"]\ar[rr,"\phi_{m_1,n_1}\times\phi_{m_2,n_2}"] \&\& F(m_1+n_1)\times F(m_2+n_2)\ar[rr,"\phi_{m_1+n_1,m_2+n_2}"] \&\& F(m_1+n_1+m_2+n_2)\ar[dd,"F\psi"]\ar[ddll,"F(1+\beta+1)"'] \\
 \one \ar[ur,"{x_1\times y_1\times x_2\times y_2}"]\ar[dr,"{x_1\times x_2\times y_1\times y_2}"'] \&\&\&\& \\
@@
 As a result, $F$ has now enough structure to induce a double category of decorated cospans $F\lCsp$  as in \cref{DC}.
-Finally, it can be shown that the structured and decorated cospan double categories categories are equivalent as symmetric monoidal double categories: ${}_L \lCsp(\X) \simeq F\Csp$.
+Finally, it can be shown that the structured and decorated cospan double categories are equivalent as symmetric monoidal double categories: ${}_L \lCsp(\X) \simeq F\lCsp$.
 
@@
 			\node (a) at (-4,0) {$a+a'$};
-			\node (b) at (1,0) {$(m_1+n_1) +_{(b+b')} (m_2+n_2)$};
+			\node (b) at (1,0) {$(m_2+n_2) +_{(b+b')} (m_1+n_1)$};
 			\node (c) at (6,0) {$c+c'$};
 			\node (a2) at (-4,1) {$a'+a$};
-			\node (b2) at (1,1) {$(n_1+m_1) +_{(b'+b)} (n_2+m_2)$};
+			\node (b2) at (1,1) {$(n_2+m_2) +_{(b'+b)} (n_1+m_1)$};
 			\node (c2) at (6,1) {$c'+c$};
             \node (a3) at (-4,2) {$a'+a$};
-			\node (b3) at (1,2) {$(n_1 +_{b'} n_2) + (m_1 +_b m_2)$};
+			\node (b3) at (1,2) {$(n_2 +_{b'} n_1) + (m_2 +_b m_1)$};
 			\node (c3) at (6,2) {$c'+c$};
             \node (a5) at (-4,-1) {$a+a'$};
-			\node (b5) at (1,-1) {$(m_1+_b m_2) + (n_1+_{b'} n_2)$};
+			\node (b5) at (1,-1) {$(m_2+_b m_1) + (n_2+_{b'} n_1)$};
 			\node (c5) at (6,-1) {$c+c'$};
             \node (a6) at (-4,-2) {$a'+a$};
-			\node (b6) at (1,-2) {$(n_1 +_{b'} n_2) + (m_1 +_b m_2)$};
+			\node (b6) at (1,-2) {$(n_2 +_{b'} n_1) + (m_2 +_b m_1)$};
 			\node (c6) at (6,-2) {$c'+c$};
@@
 %			\node (a) at (-4,0) {$a+a'$};
-			\node (b) at (1,0) {$(m_1+n_1) +_{(b+b')} (m_2+n_2)$};
-			\node (c) at (8,0) {$ (x_2\oplus y_2)\odot (x_1\oplus y_1)  \in F((m_1+n_1)+_{b+b'}(m_2+n_2))$};
+			\node (b) at (1,0) {$(m_2+n_2) +_{(b+b')} (m_1+n_1)$};
+			\node (c) at (8,0) {$ (x_2\oplus y_2)\odot (x_1\oplus y_1)  \in F((m_2+n_2)+_{b+b'}(m_1+n_1))$};
 %			\node (a2) at (-4,1) {$a'+a$};
-			\node (b2) at (1,1) {$(n_1+m_1) +_{(b'+b)} (n_2+m_2)$};
-			\node (c2) at (8,1) {$(y_2\oplus x_2)\odot(y_1\oplus x_1) \in F((n_1+m_1)+_{b'+b}(n_2+m_2))$};
+			\node (b2) at (1,1) {$(n_2+m_2) +_{(b'+b)} (n_1+m_1)$};
+			\node (c2) at (8,1) {$(y_2\oplus x_2)\odot(y_1\oplus x_1) \in F((n_2+m_2)+_{b'+b}(n_1+m_1))$};
 %                            \node (a3) at (-4,2) {$a'+a$};
-			\node (b3) at (1,2) {$(n_1 +_{b'} n_2) + (m_1 +_b m_2)$};
-			\node (c3) at (8,2) {$(y_2 \odot y_1) \oplus (x_2 \odot x_1) \in F((n_1+_{b'} n_2)+(m_1+_b m_2))$};
+			\node (b3) at (1,2) {$(n_2 +_{b'} n_1) + (m_2 +_b m_1)$};
+			\node (c3) at (8,2) {$(y_2 \odot y_1) \oplus (x_2 \odot x_1) \in F((n_2+_{b'} n_1)+(m_2+_b m_1))$};
 %                                \node (a5) at (-4,-1) {$a+a'$};
-			\node (b5) at (1,-1) {$(m_1+_b m_2) + (n_1+_{b'} n_2)$};
-			\node (c5) at (8,-1) {$(x_2 \odot x_1) \oplus (y_2 \odot y_1) \in F((m_1+_b m_2)+(n_1+_{b'} n_2))$};
+			\node (b5) at (1,-1) {$(m_2+_b m_1) + (n_2+_{b'} n_1)$};
+			\node (c5) at (8,-1) {$(x_2 \odot x_1) \oplus (y_2 \odot y_1) \in F((m_2+_b m_1)+(n_2+_{b'} n_1))$};
 %                                \node (a6) at (-4,-2) {$a'+a$};
-			\node (b6) at (1,-2) {$(n_1 +_{b'} n_2) + (m_1 +_b m_2)$};
-			\node (c6) at (8,-2) {$(y_2 \odot y_1) \oplus (x_2 \odot x_1) \in F((n_1+_{b'} n_2)+(m_1+_b m_2))$};
+			\node (b6) at (1,-2) {$(n_2 +_{b'} n_1) + (m_2 +_b m_1)$};
+			\node (c6) at (8,-2) {$(y_2 \odot y_1) \oplus (x_2 \odot x_1) \in F((n_2+_{b'} n_1)+(m_2+_b m_1))$};
 			\path[->,font=\scriptsize,>=angle 90]
@@
 \node (D) at (3,-0.5) {$\scriptstyle{\one}$};
-\node (E) at (6.75,0.5) {$\scriptstyle{F(m_1 + n_1) \times F(m_2+n_2)}$};
+\node (E) at (6.75,0.5) {$\scriptstyle{F(m_2 + n_2) \times F(m_1+n_1)}$};
 \node () at (10.25,-1) {$\scriptstyle\stackrel{\cref{eq:braidedpseudofun}}{\cong}$};
 \node () at (7.875,0) {$\scriptstyle\stackrel{\cref{eq:interchangedeco}}{\cong}$};
-\node (E') at (6.75,-0.5) {$\scriptstyle{F(m_1+m_2) \times F(n_1+n_2)}$};
-\node (B) at (9,0.5) {$\scriptstyle{F((m_1+n_1)+(m_2+n_2))}$};
-\node (B') at (9,-0.5) {$\scriptstyle{F(m_1+_b m_2)\times F(n_1+_{b'}n_2)}$};
-\node (C) at (11.5,0.5) {$\scriptstyle{F((m_1+n_1)+_{b+b'}(m_2+n_2))}$};
-\node (C') at (11.5,-0.5) {$\scriptstyle{F((m_1+_b m_2)+ (n_1+_{b'} n_2))}$};
-\node (G) at (4.25,0.5) {$\scriptstyle{F(m_1) \times F(n_1) \times F(m_2) \times F(n_2)}$};
-\node (G') at (4.25,-0.5) {$\scriptstyle{F(m_1) \times F(m_2) \times F(n_1) \times F(n_2)}$};
-\node (G'') at (4.25,-1.5) {$\scriptstyle{F(n_1) \times F(n_2) \times F(m_1) \times F(m_2)}$};
-\node (E'') at (6.75,-1.5) {$\scriptstyle{F(n_1+n_2) \times F(m_1+m_2)}$};
-\node (B'') at (9,-1.5) {$\scriptstyle{F(n_1+_{b'}n_2)+F(m_1+_b m_2)}$};
-\node (C'') at (11.5,-1.5) {$\scriptstyle{F((n_1+_{b'}n_2)+(m_1+_b m_2))}$};
-\node (X) at (3.4,0.2) {$\scriptscriptstyle{x_1 \times y_1 \times x_2 \times y_2}$};
-\node (X') at (3.4,-0.35) {$\scriptscriptstyle{x_1 \times x_2 \times y_1 \times y_2}$};
-\node (X'') at (3.4,-1.2) {$\scriptscriptstyle{y_1 \times y_2 \times x_1 \times x_2}$};
+\node (E') at (6.75,-0.5) {$\scriptstyle{F(m_2+m_1) \times F(n_2+n_1)}$};
+\node (B) at (9,0.5) {$\scriptstyle{F((m_2+n_2)+(m_1+n_1))}$};
+\node (B') at (9,-0.5) {$\scriptstyle{F(m_2+_b m_1)\times F(n_2+_{b'}n_1)}$};
+\node (C) at (11.5,0.5) {$\scriptstyle{F((m_2+n_2)+_{b+b'}(m_1+n_1))}$};
+\node (C') at (11.5,-0.5) {$\scriptstyle{F((m_2+_b m_1)+ (n_2+_{b'} n_1))}$};
+\node (G) at (4.25,0.5) {$\scriptstyle{F(m_2) \times F(n_2) \times F(m_1) \times F(n_1)}$};
+\node (G') at (4.25,-0.5) {$\scriptstyle{F(m_2) \times F(m_1) \times F(n_2) \times F(n_1)}$};
+\node (G'') at (4.25,-1.5) {$\scriptstyle{F(n_2) \times F(n_1) \times F(m_2) \times F(m_1)}$};
+\node (E'') at (6.75,-1.5) {$\scriptstyle{F(n_2+n_1) \times F(m_2+m_1)}$};
+\node (B'') at (9,-1.5) {$\scriptstyle{F(n_2+_{b'}n_1) \times F(m_2+_b m_1)}$};
+\node (C'') at (11.5,-1.5) {$\scriptstyle{F((n_2+_{b'}n_1)+(m_2+_b m_1))}$};
+\node (X) at (3.4,0.2) {$\scriptscriptstyle{x_2 \times y_2 \times x_1 \times y_1}$};
+\node (X') at (3.4,-0.35) {$\scriptscriptstyle{x_2 \times x_1 \times y_2 \times y_1}$};
+\node (X'') at (3.4,-1.2) {$\scriptscriptstyle{y_2 \times y_1 \times x_2 \times x_1}$};
 \path[->,font=\scriptsize,>=angle 90]
 (B') edge node [fill=white] {$\beta$} (B'')
-(E) edge node [above] {$\phi_{m_1+n_1,m_2+n_2}$} (B)
+(E) edge node [above] {$\phi_{m_2+n_2,m_1+n_1}$} (B)
 (E'') edge node [below] {$F\psi\times F\psi$} (B'')
@@
 (B) edge node [above] {$F(\psi)$} (C)
-(B'') edge node [below] {$\phi_{n_1+_{b'}n_2,m_1+_bm_2}$} (C'')
-(B') edge node [above] {$\phi_{m_1+_bm_2,n_1+_{b'}n_2}$} (C')
+(B'') edge node [below] {$\phi_{n_2+_{b'}n_1,m_2+_b m_1}$} (C'')
+(B') edge node [above] {$\phi_{m_2+_b m_1,n_2+_{b'}n_1}$} (C')
 (C) edge node [fill=white] {$F(\hat{\chi})$} (C')
 (C') edge node [fill=white] {$F(\beta)$} (C'')
-(G) edge node [above] {$\phi_{m_1,n_1} {\times} \phi_{m_2,n_2}$} (E)
-(G'') edge node [below] {$\phi_{n_1,n_2} {\times} \phi_{m_1,m_2}$} (E'')
-(G') edge node [above] {$\phi_{m_1,m_2} \times \phi_{n_1,n_2}$} (E')
+(G) edge node [above] {$\phi_{m_2,n_2} {\times} \phi_{m_1,n_1}$} (E)
+(G'') edge node [below] {$\phi_{n_2,n_1} {\times} \phi_{m_2,m_1}$} (E'')
+(G') edge node [above] {$\phi_{m_2,m_1} \times \phi_{n_2,n_1}$} (E')
 (G) edge node [fill=white] {$1 \times \beta \times 1$} (G')
@@
 \node (D) at (3,-0.5) {$\scriptstyle{\one}$};
-\node (E) at (6.75,0.5) {$\scriptstyle{F(m_1 + n_1) \times F(m_2+n_2)}$};
+\node (E) at (6.75,0.5) {$\scriptstyle{F(m_2 + n_2) \times F(m_1+n_1)}$};
 \node () at (5.5,-1) {$\scriptstyle{\cong}$};
@@
 \node () at (7.875,0) {$\scriptstyle\stackrel{\cref{eq:interchangedeco}}{\cong}$};
-\node (E') at (6.75,-0.5) {$\scriptstyle{F(m_1+m_2) \times F(n_1+n_2)}$};
-\node (B) at (9,0.5) {$\scriptstyle{F((m_1+n_1)+(m_2+n_2))}$};
-\node (B') at (9,-0.5) {$\scriptstyle{F((m_1+ m_2)+(n_1+n_2))}$};
-\node (C) at (11.5,0.5) {$\scriptstyle{F((m_1+n_1)+_{b+b'}(m_2+n_2))}$};
-\node (C') at (11.5,-0.5) {$\scriptstyle{F((m_1+_b m_2)+ (n_1+_{b'} n_2))}$};
-\node (G) at (4.25,0.5) {$\scriptstyle{F(m_1) \times F(n_1) \times F(m_2) \times F(n_2)}$};
-\node (G') at (4.25,-0.5) {$\scriptstyle{F(m_1) \times F(m_2) \times F(n_1) \times F(n_2)}$};
-\node (G'') at (4.25,-1.5) {$\scriptstyle{F(n_1) \times F(n_2) \times F(m_1) \times F(m_2)}$};
-\node (E'') at (6.75,-1.5) {$\scriptstyle{F(n_1+n_2) \times F(m_1+m_2)}$};
-\node (B'') at (9,-1.5) {$\scriptstyle{F((n_1+n_2)+(m_1+ m_2))}$};
-\node (C'') at (11.5,-1.5) {$\scriptstyle{F((n_1+_{b'}n_2)+(m_1+_b m_2))}$};
-\node (X) at (3.4,0.2) {$\scriptscriptstyle{x_1 \times y_1 \times x_2 \times y_2}$};
-\node (X') at (3.4,-0.35) {$\scriptscriptstyle{x_1 \times x_2 \times y_1 \times y_2}$};
-\node (X'') at (3.4,-1.2) {$\scriptscriptstyle{y_1 \times y_2 \times x_1 \times x_2}$};
+\node (E') at (6.75,-0.5) {$\scriptstyle{F(m_2+m_1) \times F(n_2+n_1)}$};
+\node (B) at (9,0.5) {$\scriptstyle{F((m_2+n_2)+(m_1+n_1))}$};
+\node (B') at (9,-0.5) {$\scriptstyle{F((m_2+ m_1)+(n_2+n_1))}$};
+\node (C) at (11.5,0.5) {$\scriptstyle{F((m_2+n_2)+_{b+b'}(m_1+n_1))}$};
+\node (C') at (11.5,-0.5) {$\scriptstyle{F((m_2+_b m_1)+ (n_2+_{b'} n_1))}$};
+\node (G) at (4.25,0.5) {$\scriptstyle{F(m_2) \times F(n_2) \times F(m_1) \times F(n_1)}$};
+\node (G') at (4.25,-0.5) {$\scriptstyle{F(m_2) \times F(m_1) \times F(n_2) \times F(n_1)}$};
+\node (G'') at (4.25,-1.5) {$\scriptstyle{F(n_2) \times F(n_1) \times F(m_2) \times F(m_1)}$};
+\node (E'') at (6.75,-1.5) {$\scriptstyle{F(n_2+n_1) \times F(m_2+m_1)}$};
+\node (B'') at (9,-1.5) {$\scriptstyle{F((n_2+n_1)+(m_2+ m_1))}$};
+\node (C'') at (11.5,-1.5) {$\scriptstyle{F((n_2+_{b'}n_1)+(m_2+_b m_1))}$};
+\node (X) at (3.4,0.2) {$\scriptscriptstyle{x_2 \times y_2 \times x_1 \times y_1}$};
+\node (X') at (3.4,-0.35) {$\scriptscriptstyle{x_2 \times x_1 \times y_2 \times y_1}$};
+\node (X'') at (3.4,-1.2) {$\scriptscriptstyle{y_2 \times y_1 \times x_2 \times x_1}$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (E') edge node [fill=white] {$\beta$} (E'')
-(E) edge node [above] {$\phi_{m_1+n_1,m_2+n_2}$} (B)
-(E'') edge node [above] {$\phi_{n_1+n_2,m_1+m_2}$} (B'')
-(E') edge node [above] {$\phi_{m_1+m_2,n_1+n_2}$} (B')
+(E) edge node [above] {$\phi_{m_2+n_2,m_1+n_1}$} (B)
+(E'') edge node [above] {$\phi_{n_2+n_1,m_2+m_1}$} (B'')
+(E') edge node [above] {$\phi_{m_2+m_1,n_2+n_1}$} (B')
 (B) edge node [above] {$F(\psi)$} (C)
@@
 (C') edge node [fill=white] {$F(\beta)$} (C'')
-(G) edge node [above] {$\phi_{m_1,n_1} {\times} \phi_{m_2,n_2}$} (E)
-(G'') edge node [above] {$\phi_{n_1,n_2} {\times} \phi_{m_1,m_2}$} (E'')
-(G') edge node [above] {$\phi_{m_1,m_2} \times \phi_{n_1,n_2}$} (E')
+(G) edge node [above] {$\phi_{m_2,n_2} {\times} \phi_{m_1,n_1}$} (E)
+(G'') edge node [above] {$\phi_{n_2,n_1} {\times} \phi_{m_2,m_1}$} (E'')
+(G') edge node [above] {$\phi_{m_2,m_1} \times \phi_{n_2,n_1}$} (E')
 (G) edge node [fill=white] {$1 \times \beta \times 1$} (G')
@@
 \node (D) at (3,-0.5) {$\scriptstyle{\one}$};
-\node (E) at (6.75,0.5) {$\scriptstyle{F(m_1 + n_1) \times F(m_2+n_2)}$};
+\node (E) at (6.75,0.5) {$\scriptstyle{F(m_2 + n_2) \times F(m_1+n_1)}$};
 \node () at (5.5,0) {$\scriptstyle\stackrel{\cref{eq:braidedpseudofun}}{\cong}$};
@@
 \node () at (12,-1) {$\scriptstyle\cong$};
-\node (E') at (6.75,-0.5) {$\scriptstyle{F(n_1+m_1) \times F(n_2+m_2)}$};
-\node (B) at (9,0.5) {$\scriptstyle{F((m_1+n_1)+(m_2+n_2))}$};
-\node (B') at (9,-0.5) {$\scriptstyle{F((n_1+m_1)+(n_2+m_2))}$};
-\node (C) at (11.5,0.5) {$\scriptstyle{F((m_1+n_1)+_{b+b'}(m_2+n_2))}$};
-\node (C') at (11.5,-0.5) {$\scriptstyle{F((n_1+m_1)+_{b'+b}(n_2+m_2))}$};
-\node (G) at (4.25,0.5) {$\scriptstyle{F(m_1) \times F(n_1) \times F(m_2) \times F(n_2)}$};
-\node (G') at (4.25,-0.5) {$\scriptstyle{F(n_1) \times F(m_1) \times F(n_2) \times F(m_2)}$};
-\node (G'') at (4.25,-1.5) {$\scriptstyle{F(n_1) \times F(n_2) \times F(m_1) \times F(m_2)}$};
-\node (E'') at (6.75,-1.5) {$\scriptstyle{F(n_1+n_2) \times F(m_1+m_2)}$};
-\node (B'') at (9,-1.5) {$\scriptstyle{F(n_1+_{b'}n_2)+ F(m_1+_b m_2))}$};
-\node (C'') at (11.5,-1.5) {$\scriptstyle{F((n_1+_{b'}n_2)+(m_1+_b m_2))}$};
-\node (X) at (3.4,0.2) {$\scriptscriptstyle{x_1 \times y_1 \times x_2 \times y_2}$};
-\node (X') at (3.4,-0.35) {$\scriptscriptstyle{y_1 \times x_1 \times y_2 \times x_2}$};
-\node (X'') at (3.4,-1.2) {$\scriptscriptstyle{y_1 \times y_2 \times x_1 \times x_2}$};
+\node (E') at (6.75,-0.5) {$\scriptstyle{F(n_2+m_2) \times F(n_1+m_1)}$};
+\node (B) at (9,0.5) {$\scriptstyle{F((m_2+n_2)+(m_1+n_1))}$};
+\node (B') at (9,-0.5) {$\scriptstyle{F((n_2+m_2)+(n_1+m_1))}$};
+\node (C) at (11.5,0.5) {$\scriptstyle{F((m_2+n_2)+_{b+b'}(m_1+n_1))}$};
+\node (C') at (11.5,-0.5) {$\scriptstyle{F((n_2+m_2)+_{b'+b}(n_1+m_1))}$};
+\node (G) at (4.25,0.5) {$\scriptstyle{F(m_2) \times F(n_2) \times F(m_1) \times F(n_1)}$};
+\node (G') at (4.25,-0.5) {$\scriptstyle{F(n_2) \times F(m_2) \times F(n_1) \times F(m_1)}$};
+\node (G'') at (4.25,-1.5) {$\scriptstyle{F(n_2) \times F(n_1) \times F(m_2) \times F(m_1)}$};
+\node (E'') at (6.75,-1.5) {$\scriptstyle{F(n_2+n_1) \times F(m_2+m_1)}$};
+\node (B'') at (9,-1.5) {$\scriptstyle{F(n_2+_{b'}n_1)\times F(m_2+_b m_1)}$};
+\node (C'') at (11.5,-1.5) {$\scriptstyle{F((n_2+_{b'}n_1)+(m_2+_b m_1))}$};
+\node (X) at (3.4,0.2) {$\scriptscriptstyle{x_2 \times y_2 \times x_1 \times y_1}$};
+\node (X') at (3.4,-0.35) {$\scriptscriptstyle{y_2 \times x_2 \times y_1 \times x_1}$};
+\node (X'') at (3.4,-1.2) {$\scriptscriptstyle{y_2 \times y_1 \times x_2 \times x_1}$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (E) edge node [fill=white] {$F(\beta) \times F(\beta)$} (E')
-(E) edge node [above] {$\phi_{m_1+n_1,m_2+n_2}$} (B)
+(E) edge node [above] {$\phi_{m_2+n_2,m_1+n_1}$} (B)
 (E'') edge node [below] {$F\psi\times F\psi)$} (B'')
-(E') edge node [above] {$\phi_{n_1+m_1,n_2+m_2}$} (B')
+(E') edge node [above] {$\phi_{n_2+m_2,n_1+m_1}$} (B')
 (B) edge node [above] {$F(\psi)$} (C)
-(B'') edge node [below] {$\phi_{n_1+_{b'}n_2,m_1+_{b}m_2}$} (C'')
+(B'') edge node [below] {$\phi_{n_2+_{b'}n_1,m_2+_{b}m_1}$} (C'')
 (B') edge node [above] {$F(\psi)$} (C')
@@
 (C') edge node [fill=white] {$F(\hat{\chi})$} (C'')
-(G) edge node [above] {$\phi_{m_1,n_1} {\times} \phi_{m_2,n_2}$} (E)
-(G'') edge node [below] {$\phi_{n_1,n_2} {\times} \phi_{m_1,m_2}$} (E'')
-(G') edge node [above] {$\phi_{n_1,m_1} \times \phi_{n_2,m_2}$} (E')
+(G) edge node [above] {$\phi_{m_2,n_2} {\times} \phi_{m_1,n_1}$} (E)
+(G'') edge node [below] {$\phi_{n_2,n_1} {\times} \phi_{m_2,m_1}$} (E'')
+(G') edge node [above] {$\phi_{n_2,m_2} \times \phi_{n_1,m_1}$} (E')
 (G) edge node [fill=white] {$\beta \times \beta$} (G')

### 2020-12-07 cospans.tex
changed statement of Lemma 3.4, statement and proof of Lemma 3.6

@@
 % in LaTeX
-% 2020/12/5
+% 2020/12/7
 
@@
 These 2-equivalences further restrict to the case when the Grothendieck category $(X,\otimes_\X)$ is specifically cocartesian monoidal itself, with coproducts built up from \cref{eq:explicitstructure2}.
-In that case, opfibrations $(\X,+)\to(\A,+)$ that strictly preserve coproducts and initial object bijectively correspond to pseudofunctors into the 2-category of cocartesian categories.
+In that case, opfibrations $(\X,+) \to (\A,+)$ that strictly preserve coproducts and initial object bijectively correspond to pseudofunctors into the 2-category of cocartesian categories.
 For more details, see \cite[Corollary 4.7]{MV} and the related discussion.
@@
  \item the total category $\X$ has $\J$-colimits, and $U$ preserves them.
-Moreover in this situation the $\J$-colimits in $\X$ and $\J$ can be chosen so that $U$ strictly preserves them.   %%% CHECK AND MAYBE FIX THIS!!!
+Moreover in this situation the $\J$-colimits in $\X$ can be chosen so that $U$ strictly preserves them.  
 \end{enumerate}
@@
 
-On a highly related note, in what follows we are also interested in the existence of a left adjoint $L$ to an induced monoidal opfibration; the following result provides sufficient conditions for that.
+On a highly related note, in what follows we are also interested in the existence of a left adjoint $L$ to an induced monoidal opfibration.
+The following result provides sufficient conditions for that.
+Following Gray \cite{Gray}, let us define a `right adjoint left inverse' or  \define{rali} to be a right adjoint in an adjunction for which the unit is the identity.
 
 \begin{lem}[\textbf{Gray}] \label{prop:opfibtolari}
-  Let $U \maps\X \to \A$ be an opfibration. Then
-  $U$ is a right adjoint `left inverse', a.k.a the unit is the identity, if (and only if) its fibers have
-  initial objects which are preserved by the
-  reindexing functors.
+  Let $U \maps\X \to \A$ be an opfibration. Then $U$ is a rali if (and only if) fibers are equipped with initial objects that are preserved up to isomorphism by the reindexing functors.
 \end{lem}
@@
 \begin{proof}
- This is \cite[Proposition~4.4]{Gray}.
-The left adjoint $L\maps\A\to\X$ maps an object $a$ to the initial object in its fiber $\X_a$, denoted by $\bot_a$.
-By construction, $U(L(a))=U(\bot_a)=a$.
-On morphisms $f\maps a\to a'$, $L(f)$ is defined by
+ This is \cite[Proposition~4.4]{Gray}; we only need the ``if'' direction here.
+Suppose each fiber $\X_a$ of the opfibration $U$ is equipped with an initial object $\bot_a$, and these objects are preserved by the reindexing functors.
+Define $L\maps\A\to\X$ on objects $a \in \A$ by $L(a) = \bot_a$.
+Define $L$ on morphisms as follows: given $f\maps a\to a'$, $L(f)$ is the composite
  \begin{equation}\label{eq:Lonarrows}
@@
  \end{equation}
-where $\mathrm{Cocart}(f,\bot_a)$ is the cocartesian lifting of $\bot_a$ along $f$ and $\chi_a$ is the unique isomorphism between the initial objects in the fiber above $a'$ since $f_!$ preserves them.
+where $\mathrm{Cocart}(f,\bot_a)$ is the cocartesian lifting of $f$ to $\bot_a$  and $\chi_a$ is the unique isomorphism between the initial objects in the fiber above $a'$, since $f_!$ preserves them.
+One can make $U$ into a right adjoint of $L$ with unit $a \mapsto U(L(a))$ being the identity, using the fact that $U(L(a)) = U(\bot_a) = a$.
 \end{proof}
@@
 and we think of $t(\tau), s(\tau) \in \N[S]$ as vectors in $\R^S$.
-This formula is explained in the paper with Pollard, where it is also shown that $\theta$ defines a monoidal natural isomorphism between functors to $\Set$ \cite[Theorem 18]{BP}.
-As such, it trivially becomes a monoidal natural isomorphism between the functors $F, D \maps \Fin\Set \to \Cat$.
+This formula is explained in the paper with Pollard, where it is also shown that $\theta$ defines a monoidal natural isomorphism between functors to $(\Set,\times)$ \cite[Theorem 18]{BP}.
+As such, it automatically becomes a monoidal natural isomorphism between the functors $F, D \maps (\Fin\Set,+) \to (\Cat,\times)$.
 
@@
 
-Even though for both \cref{thm:equiv} and the above described setting, the conditions required are only sufficient, they provide certain indication that under a suitable ``condition intersection'' in a sense, we could establish a functorial picture
+Even though for both \cref{thm:equiv} and the above result the conditions required are only sufficient, they suggest that with work we could establish a functorial picture
 \begin{displaymath}
@@
 with an actual natural isomorphism in the middle.  
-This would imply that starting from an appropriate middle ground, employing the structured or the decorated cospan formalism is essentially the same.
-We leave such considerations for future work.
+This would imply that starting from an appropriate middle ground, employing the structured or the decorated cospan formalism is essentially the same. We leave such considerations for future work.
 

### 2020-12-07 cospans.tex
Changed statement of Lem. 3.4, statement and proof of Lem. 3.6

@@
 \begin{lem}[\textbf{Gray}] \label{prop:opfibtolari}
-  Let $U \maps\X \to \A$ be an opfibration. Then $U$ is a rali if (and only if) fibers are equipped with initial objects that are preserved up to isomorphism by the reindexing functors.
+Let $U \maps\X \to \A$ be an opfibration. Then to make $U$ into a rali, it suffices to equip
+its fibers with initial objects that are preserved up to isomorphism by the reindexing functors.
 \end{lem}
@@
 \begin{proof}
- This is \cite[Proposition~4.4]{Gray}; we only need the ``if'' direction here.
+ This is \cite[Proposition~4.4]{Gray}.
 Suppose each fiber $\X_a$ of the opfibration $U$ is equipped with an initial object $\bot_a$, and these objects are preserved by the reindexing functors.
@@
 where $\mathrm{Cocart}(f,\bot_a)$ is the cocartesian lifting of $f$ to $\bot_a$  and $\chi_a$ is the unique isomorphism between the initial objects in the fiber above $a'$, since $f_!$ preserves them.
-One can make $U$ into a right adjoint of $L$ with unit $a \mapsto U(L(a))$ being the identity, using the fact that $U(L(a)) = U(\bot_a) = a$.
+One can then make $U$ into a right adjoint of $L$ with unit $\iota_a \maps a \to U(L(a))$ being the identity, using the fact that $U(L(a)) = U(\bot_a) = a$.
 \end{proof}

### 2020-12-07 cospans.tex
Changed statement of Lem. 3.4, statement and proof of Lem. 3.6

@@
  This is \cite[Proposition~4.4]{Gray}.
-Suppose each fiber $\X_a$ of the opfibration $U$ is equipped with an initial object $\bot_a$, and these objects are preserved by the reindexing functors.
+Suppose each fiber $\X_a$ of the opfibration $U$ is equipped with an initial object $\bot_a$, and these objects are preserved up to isomorphism by the reindexing functors.
 Define $L\maps\A\to\X$ on objects $a \in \A$ by $L(a) = \bot_a$.
-Define $L$ on morphisms as follows: given $f\maps a\to a'$, $L(f)$ is the composite
+Given a morphism $f\maps a\to a'$ in $\A$, define $L(f)$ to be the composite
  \begin{equation}\label{eq:Lonarrows}
-  \bot_a\xrightarrow{\mathrm{Cocart}(f,\bot_a)}f_!(\bot_a)\stackrel{\chi_a}{\cong}\bot_{a'}
+  \bot_a\xrightarrow{\mathrm{Cocart}(f,\bot_a)}f_!(\bot_a)\xrightarrow{\;\chi_a\;}\bot_{a'}
  \end{equation}
-where $\mathrm{Cocart}(f,\bot_a)$ is the cocartesian lifting of $f$ to $\bot_a$  and $\chi_a$ is the unique isomorphism between the initial objects in the fiber above $a'$, since $f_!$ preserves them.
+where $\mathrm{Cocart}(f,\bot_a)$ is the cocartesian lifting of $f$ to $\bot_a$  and $\chi_a$ is the unique isomorphism between these two initial objects in the fiber above $a'$.
 One can then make $U$ into a right adjoint of $L$ with unit $\iota_a \maps a \to U(L(a))$ being the identity, using the fact that $U(L(a)) = U(\bot_a) = a$.

### 2020-12-07 cospans.tex
Changed statement of Lem. 3.4, statement and proof of Lem. 3.6

@@
  \end{equation}
-where $\mathrm{Cocart}(f,\bot_a)$ is the cocartesian lifting of $f$ to $\bot_a$  and $\chi_a$ is the unique isomorphism between these two initial objects in the fiber above $a'$.
+where $\mathrm{Cocart}(f,\bot_a)$ is the cocartesian lifting of $f$ to $\bot_a$  and $\chi_a$ is the unique isomorphism between two initial objects in the fiber above $a'$.
 One can then make $U$ into a right adjoint of $L$ with unit $\iota_a \maps a \to U(L(a))$ being the identity, using the fact that $U(L(a)) = U(\bot_a) = a$.

### 2020-12-08 cospans.tex
tiny

@@
  \scalebox{.75}{\begin{tikzcd}[ampersand replacement=\&,column sep=.3in,row sep=.1in]
-\& F(m_1)\times F(n_1)\times F(m_2)\times F(n_2)\ar[dd,"1\times\beta\times1"]\ar[ddrr,phantom,"\cong"]\ar[rr,"\phi_{m_1,n_1}\times\phi_{m_2,n_2}"] \&\& F(m_1+n_1)\times F(m_2+n_2)\ar[rr,"\phi_{m_1+n_1,m_2+n_2}"] \&\& F(m_1+n_1+m_2+n_2)\ar[dd,"F\psi"]\ar[ddll,"F(1+\beta+1)"'] \\
+\& F(m_1)\times F(n_1)\times F(m_2)\times F(n_2)\ar[dd,"1\times\beta\times1"']\ar[ddrr,phantom,"\cong"]\ar[rr,"\phi_{m_1,n_1}\times\phi_{m_2,n_2}"] \&\& F(m_1+n_1)\times F(m_2+n_2)\ar[rr,"\phi_{m_1+n_1,m_2+n_2}"] \&\& F(m_1+n_1+m_2+n_2)\ar[dd,"F\psi"]\ar[ddll,"F(1+\beta+1)"'] \\
 \one \ar[ur,"{x_1\times y_1\times x_2\times y_2}"]\ar[dr,"{x_1\times x_2\times y_1\times y_2}"'] \&\&\&\& \\
@@
 \end{equation}
-where the left-hand side isomorphism combines pseudoassociativity \cref{eq:omega} and braided monoidal structure \cref{eq:braidedpseudofun} of the pseudofunctor $F$, and the right hand side follows from the universal property of colimits and pseudofunctoriality of $F$.
+where the left-hand side isomorphism combines pseudoassociativity \cref{eq:omega} and braided monoidal structure \cref{eq:braidedpseudofun} of the pseudofunctor $F$ (and can be explicitly found in e.g.
+\cite[Page 125]{DS}), and the right hand side follows from the universal property of colimits and pseudofunctoriality of $F$.
 Similarly, for units $U_{a+b}$ and $U_a\ot U_b$ it is easy to see that as cospans they are both the identity $1_{a+b}:a+b\to a+b\leftarrow a+b:1_{a+b}$, and there is a canonical isomorphism between their trivial decorations \cref{eq:UFCsp}, namely $F(!_{a+b})\phi_0\cong\phi_{a,b}(F(!_a)\times F(!_b))(\phi_0\times\phi_0)$ via the structure isomorphisms for $(\phi,\phi_0)$.

### 2020-12-08 cospans.tex
various edits and comments up to 5.4

@@
 We might hope to do this using a symmetric lax monoidal functor $F \maps (\Fin\Set, +) \to (\Set, \times)$ assigning to each finite set $m$ the set of all graphs with $m$ as their set of nodes.
-But this hope is doomed, for reasons painstakingly explained in \cite[Sec.\ 5]{BC2}.
+But this hope is doomed, for reasons painstakingly explained in \cite[Section 5]{BC2}.
 There is really a \emph{category} of graphs with $m$ as their set of nodes---and surprisingly, trying to treat this category as a mere set does not work, despite all the tricks one might try.
@@
 \end{itemize}
-Many of the flawed applications of decorated cospans have been fixed using structured cospans \cite[Sec.\ 6]{BC2}, but not all decorated cospans can handled using structured cospans.
+Many of the flawed applications of decorated cospans have been fixed using structured cospans \cite[Section 6]{BC2}, but not all decorated cospans can handled using structured cospans.
 
@@
 The second part formulates the existence of colimits \emph{globally} in the total category $\inta F$, and if we let $\J$ range over all finite categories it says that $\X$ has finite colimits and $U$ preserves all finite colimits.
-As an example, suppose that $\A$ has pushouts and a Grothendieck opfibration $U\colon\inta F\to\A$ has fibrewise pushouts preserved by its reindexing functors.
+As an example, suppose that $\A$ has pushouts and a Grothendieck opfibration $U\colon\inta F\to\A$ has fiberwise pushouts preserved by its reindexing functors.
 We can construct pushouts in $\inta F$ as follows:
@@
 \cref{lem:MonGroth} provides a specific monoidal structure on the fibers which becomes \cref{eq:explicitstructure1} when the base $\A$ is cocartesian monoidal.
-If this fibrewise monoidal structure happens to itself be cocartesian, then it is necessarily isomorphic to any other cocartesian monoidal structure on the fibers, by the universal property of colimits.
+If this fiberwise monoidal structure happens to itself be cocartesian, then it is necessarily isomorphic to any other cocartesian monoidal structure on the fibers, by the universal property of colimits.
 Therefore, we can simplify the above assumption to that in \cref{thm:equiv} without having to specify that the structures came from monoidality of the pseudofunctor, although we \emph{will} use the formulation of coproducts and initial object in terms of the monoidal structure of $F$.
-For example, in that case, the coproducts induced in the Grothendieck category from the fibrewise ones as in \cref{eq:fibrewisecoprod} are equivalently given by \cref{eq:explicitstructure2}.
+For example, in that case, the coproducts induced in the Grothendieck category from the fiberwise ones as in \cref{eq:fibrewisecoprod} are equivalently given by \cref{eq:explicitstructure2}.
 
@@
 \end{equation}
-where the bottom composite is the fibrewise coproduct in $F(m+_bn)$ as in \cref{eq:explicitstructure1}.
+where the bottom composite is the fiberwise coproduct in $F(m+_bn)$ as in \cref{eq:explicitstructure1}.
 The left-hand side isomorphism is due to pseudonaturality of $\phi$ whereas the right-hand side isomorphism follows from universal properties and pseudofunctoriality of $F$.
@@
 \begin{proof}
-This follows by applying Shulman's result \cite[Thm.\ 1.2]{Shulman2010} to the fibrant symmetric monoidal double category $F\lCsp$.
+This follows by applying Shulman's result \cite[Theorem 1.2]{Shulman2010} to the fibrant symmetric monoidal double category $F\lCsp$.
 \end{proof}
@@
 They were then applied to open electrical circuits \cite{BF}, Markov processes \cite{BFP}, and chemical reaction networks \cite{BP}.
-Unfortunately, some of these applications were marred by technical flaws, which were later fixed using structured cospans \cite[Sec.\ 5]{BC}.
-Our new approach to decorated cospans provides another solution to these problems.
-Here we compare the two approaches in applications to graphs, electrical circuits, Petri nets, reaction networks and dynamical systems.
-In many cases \cref{thm:equiv} shows that the structured and decorated cospan approaches are equivalent, but we show that open dynamical systems can only be treated using decorated cospans.
+Unfortunately, some of these applications were marred by technical flaws, which were later fixed using structured cospans \cite[Section 5]{BC2}.
+Here we explain how to also fix them using our new decorated cospans, since they provide another another solution to these problems.
+Below we compare the two approaches in applications to graphs, electrical circuits, Petri nets, reaction networks and dynamical systems.
+In many cases, \cref{thm:equiv} shows that the structured and decorated cospan approaches are equivalent; that is why \cref{subsec:graphs,subsec:circuits,subsec:petri} are on the brief side.
+However, in \cref{subsec:petrirates} we elaborate and show that open dynamical systems can only be treated using decorated cospans.
 
@@
 
-We can easily build a double category with `open graphs' as horizontal 1-cells using the machinery of structured cospans.
+We can easily build a double category with `open graphs' as horizontal 1-cells using the machinery of structured cospans, see \cite[Section 5]{BC2}.
 Let $L \maps \Fin\Set \to \Graph$ be the functor that assigns to a finite set $N$ the \define{discrete graph} on $N$: the graph with no edges and $N$ as its set of vertices.
@@
 We can make $F$ into a symmetric lax monoidal pseudofunctor $F \maps (\Fin\Set, +) \to (\Cat,\times)$ by equipping it with suitable functors 
-\[   \phi_{N,N'} \maps F(N) \times F(N') \to F(N+N'), \qquad \phi_0 \maps F(\emptyset) \to 1 \in \Cat. \]  
-The functor $\phi_0$ is uniquely determined since $1$ is the terminal category.
+\[   \phi_{N,N'} \maps F(N) \times F(N') \to F(N+N'), \qquad \phi_0 \maps F(\emptyset) \to \one \in \Cat. \]  
+{\chris Shouldn't the laxator for the units go in the other direction??}
+
+The functor $\phi_0$ is uniquely determined since $\one$ is the terminal category.
 More interesting is $\phi_{N,N'}$.
@@
 In other words, it sends a pair of graph structures to their `disjoint union'.
-Surprisingly, though $F$ is a functor---for example, composition is strictly preserved---this choice of $\phi_{N,N'}$ does not make $F$ into a symmetric lax monoidal functor, since it obeys the required laws only up to natural isomorphism, as in \cref{eq:omega}.
-See \cite[Section 5]{BC} for a proof that these laws fail to hold on the nose.
+Surprisingly, though $F$ is a functor---for example, composition is strictly preserved---
+%%%Christina: we already said that very recently, perhaps there is no need for explaining it again?
+this choice of $\phi_{N,N'}$ does not make $F$ into a symmetric lax monoidal functor, since it obeys the required laws only up to natural isomorphism, as in \cref{eq:omega}.
+See \cite[Section 5]{BC2} for a proof that these laws fail to hold on the nose.
 This fact is what necessitated a generalization of Fong's original approach to decorated cospans.
@@
 
-Structured and decorated cospans are a powerful tool for studying categories where the morphisms are electrical circuits---see \cite{BCR,BF} and \cite[Section 6.1]{BC}.
+Structured and decorated cospans are a powerful tool for studying categories where the morphisms are electrical circuits---see \cite[Section 6.1]{BC2} and \cite{BCR,BF}.
 The key idea is to use open graphs with labeled edges to describe circuits, where the labels can stand for resistors with any chosen resistance, capacitors with any chosen capacitance, or other circuit elements.
@@
 
-We can also describe $\La$-circuits using decorated cospans.
+We can now also describe $\La$-circuits using our new approach to decorated cospans.
 There is a symmetric lax monoidal pseudofunctor $F \maps (\Fin\Set, +) \to (\Cat, \times)$ such that for any finite set $N$, the category $F(N)$ has:
@@
 \subsection{Petri nets with rates}
+\label{subsec:petrirates}
 
@@
 They used Fong's original decorated cospans to do this.
-Later, structured cospans were used to promote the first of these categories to a double category \cite[Sec.\ 6.16]{BC}.
+Later, structured cospans were used to promote the first of these categories to a double category \cite[Section 6.16]{BC2}.
 Here we show that the second of these categories, with open dynamical systems as morphisms, \emph{cannot} be made into a double category using structured cospans.
@@
 \]
+{\chris Perhaps explain the difference between lower case $i_i$ and $o_i$ and upper case? I don't get it at first sight.}
+
 If we drop the `inflow' and `outflow' terms $I_i$ and $O_i$ we obtain a system of coupled nonlinear first-order ordinary differential equations.
@@
 \]
-There is a functor $R \maps \Petri_r \to \Set$ sending any Petri net with rates to its set of places, and this has a left adjoint $L \maps \Set \to \Petri_r$ sending any set $S$ to the Petri net with $S$ as its set of species and no transitions \cite[Lemma 6.18]{BC}.
-Since $\Petri_r$ has finite colimits \cite[Lemma 6.19]{BC}, it follows that there is a symmetric monoidal double category ${}_L \lCsp(\Petri_r)$ where:
+There is a functor $R \maps \Petri_r \to \Set$ sending any Petri net with rates to its set of places, and this has a left adjoint $L \maps \Set \to \Petri_r$ sending any set $S$ to the Petri net with $S$ as its set of species and no transitions \cite[Lemma 6.18]{BC2}.
+Since $\Petri_r$ has finite colimits \cite[Lemma 6.19]{BC2}, it follows that there is a symmetric monoidal double category ${}_L \lCsp(\Petri_r)$ where:
 \begin{itemize}
@@
 \end{equation}
-This is an opfibred category over $\A$ via the obvious forgetful functor, with fiber categories $(\inta F)_a=F(a)$ and reindexing functors $f_!=F(f)$.
+This is an opfibered category over $\A$ via the obvious forgetful functor, with fiber categories $(\inta F)_a=F(a)$ and reindexing functors $f_!=F(f)$.
 \end{defn}
@@
 
-For double categories we follow the notation of our paper on structured cospans \cite{BC}, which in turn follows that of Hansen and Shulman \cite{HS,Shulman2010}.
+For double categories we follow the notation of our paper on structured cospans \cite{BC2}, which in turn follows that of Hansen and Shulman \cite{HS,Shulman2010}.
 
@@
 
-\begin{thm}{\cite[Thm.\ 7.8]{Shulman2008}}
+\begin{thm}{\cite[Theorem 7.8]{Shulman2008}}
 \label{ShulDubEquiv}
@@
 \[ \mu \maps U_{A\otimes B} \xrightarrow{\sim} U_A \otimes U_B\]
-obeying a list of equations that can be found after \cite[Definition 2.10]{HS} and also \cite[Definition A.5]{BC}.
+obeying a list of equations that can be found after \cite[Definition 2.10]{HS} and also \cite[Definition A.5]{BC2}.
 \end{itemize}
@@
 \]
-{\chris The closing sentence for the proof to be complete should be that these two decorations are EQUAL for the diagram \cref{eq:thisdiagram} to commute!
+{\chris The closing sentence for the proof to be complete should be that these two decoration maps are EQUAL for the diagram \cref{eq:thisdiagram} to commute!
 Right?
@@
 
-\bibitem{BC} J.\ C.\ Baez and K.\ Courser, Coarse-graining open Markov processes, \textsl{Theory Appl.\ Categ.\ }\textbf{33} (2018), 1223--1268.
+%\bibitem{BC} J.\ C.\ Baez and K.\ Courser, Coarse-graining open Markov processes, \textsl{Theory Appl.\ Categ.\ }\textbf{33} (2018), 1223--1268.
 Available as \href{https://arxiv.org/abs/1710.11343}{arXiv:1710.11343}.

### 2020-12-08 cospans.tex
Undoing my 1-2 subscript changes in Appendix B from yesterday
Update cospans.tex

@@
 % in LaTeX
-% 2020/12/7
+% 2020/12/8
 
@@
 \end{equation}
-Moreover, each fiber category $\X_a=F(a)$ obtains a monoidal structure via 
+Moreover, each fiber $\X_a=F(a)$ obtains a monoidal structure via 
 \begin{equation}\label{eq:explicitstructure1}
@@
 \end{equation}
-which on the first variable is given by the pushout in $\A$ on the left below, and the object $w$ is formed as the pushout in the fiber category $F(a+_bc)$ on the right below:
+which on the first variable is given by the pushout in $\A$ on the left below, and the object $w$ is formed as the pushout in the fiber $F(a+_bc)$ on the right below:
 \begin{displaymath}
@@
 The following result provides sufficient conditions for that.
-Following Gray \cite{Gray}, let us define a `right adjoint left inverse' or  \define{rali} to be a right adjoint in an adjunction for which the unit is the identity.
+Following Gray \cite{Gray}, we say a functor has a `left adjoint right inverse' or \define{lari} if it has a left adjoint where the unit of the adjunction is the identity.
 
 \begin{lem}[\textbf{Gray}] \label{prop:opfibtolari}
-Let $U \maps\X \to \A$ be an opfibration. Then to make $U$ into a rali, it suffices to equip
-its fibers with initial objects that are preserved up to isomorphism by the reindexing functors.
+Let $U \maps\X \to \A$ be an opfibration.   Then $U$ has a lari if its fibers have initial objects
+that are preserved by the reindexing functors.
 \end{lem}
@@
  This is \cite[Proposition~4.4]{Gray}.
-Suppose each fiber $\X_a$ of the opfibration $U$ is equipped with an initial object $\bot_a$, and these objects are preserved up to isomorphism by the reindexing functors.
-Define $L\maps\A\to\X$ on objects $a \in \A$ by $L(a) = \bot_a$.
+Suppose each fiber $\X_a$ of the opfibration $U$ has an initial object $\bot_a$ and these objects are preserved (up to isomorphism) by the reindexing functors.
+Define $L \maps \A \to \X$ on objects $a \in \A$ by $L(a) = \bot_a$.
 Given a morphism $f\maps a\to a'$ in $\A$, define $L(f)$ to be the composite
@@
 where $\mathrm{Cocart}(f,\bot_a)$ is the cocartesian lifting of $f$ to $\bot_a$ and $\chi_a$ is the unique isomorphism between two initial objects in the fiber above $a'$.
-One can then make $U$ into a right adjoint of $L$ with unit $\iota_a \maps a \to U(L(a))$ being the identity, using the fact that $U(L(a)) = U(\bot_a) = a$.
+The functor $L$ then becomes left adjoint to $R$ with unit $\iota_a \maps a \to U(L(a))$ being the identity, using the fact that $U(L(a)) = U(\bot_a) = a$.
 \end{proof}
@@
 \end{equation}
-with $x\in F(m)$; recall that the reindexing functors $F(i),F(o)$ preserve all finite colimits across the fiber categories.
+with $x\in F(m)$; recall that the reindexing functors $F(i),F(o)$ preserve all finite colimits across the fibers.
 Finally, the 2-morphisms of this double category in this context unravel as follows
@@
 \end{gather}
-in the fiber category $F(m')$, by composition in the Grothendieck category \cref{eq:compGrothcat}.
+in the fiber $F(m')$, by composition in the Grothendieck category \cref{eq:compGrothcat}.
 Since both morphisms emanate from the mapped initial object in $F(m')$ under the finite-colimit-preserving reindexing functors, they are the unique such into $x'$ therefore this gives no extra conditions; similarly for the equality including $o,o'$.
@@
 \node[below left=1.05 and .5  of A,draw] (D)  {Special opfibrations};
-\node[below left=2 and 1 of A,draw] (E)  {Special ralis};
+\node[below left=2 and 1 of A,draw] (E)  {Special laris};
 \node[below=3 of A,align=center,draw] (B)  {Finite colimit preserving \\ functors $A\to\X$};
@@
 The category $\X$ is called the \textbf{total} category and $\A$ is called the \textbf{base} category of the opfibration.
-For any $a\in\A$, the \textbf{fiber category} $\X_a$ consists of all objects that map to $a$ and \define{vertical} morphisms between them, i.e., morphisms mapping to $1_a$.
+For any $a\in\A$, the \textbf{fiber} above $a$ is the category $\X_a$ consisting of all objects that map to $a$ and \define{vertical} morphisms between them, i.e., morphisms mapping to $1_a$.
 
 Assuming the axiom of choice, we may select a cocartesian lifting of each morphism $f\maps a\to b$ in $\A$ to each $x\in\X _a$, denoted by $\mathrm{Cocart}(f,x)\maps x\to f_!(x)$, rendering $U$ a so-called \textbf{cloven} opfibration.
-This choice induces \textbf{reindexing functors} $f_!\maps\X _a\to\X _b$ between the fiber categories, which by the lifting's universal property come equipped with natural isomorphisms $(1_a)_!\cong 1_{\X _a}$ and $(f\circ g)_!\cong f_!\circ g_!$.
+This choice induces \textbf{reindexing functors} $f_!\maps\X _a\to\X _b$ between the fibers, which by the lifting's universal property come equipped with natural isomorphisms $(1_a)_!\cong 1_{\X _a}$ and $(f\circ g)_!\cong f_!\circ g_!$.
 With the help of these, any cloven opfibration $U \maps \X \to \A$ gives a pseudofunctor $F \maps \A \to \Cat$, where $\A$ viewed as a 2-category with trivial 2-cells, $F(a) = \X_a$ for each object $a \in \A$, and $F(f) = f_!$ for each morphism $f$ in $\A$.
@@
 \end{equation}
-This is an opfibered category over $\A$ via the obvious forgetful functor, with fiber categories $(\inta F)_a=F(a)$ and reindexing functors $f_!=F(f)$.
+This is an opfibered category over $\A$ via the obvious forgetful functor, with fibers $(\inta F)_a=F(a)$ and reindexing functors $f_!=F(f)$.
 \end{defn}

### 2020-12-09 cospans.tex
Undoing changes continued
small edits and comments in section 5

@@
 They were then applied to open electrical circuits \cite{BF}, Markov processes \cite{BFP}, and chemical reaction networks \cite{BP}.
-Unfortunately, some of these applications were marred by technical flaws, which were later fixed using structured cospans \cite[Section 5]{BC2}.
+Unfortunately, some of these applications were marred by technical flaws, which were later fixed using structured cospans \cite{BC2}.
 Here we explain how to also fix them using our new decorated cospans, since they provide another another solution to these problems.
 Below we compare the two approaches in applications to graphs, electrical circuits, Petri nets, reaction networks and dynamical systems.
-In many cases, \cref{thm:equiv} shows that the structured and decorated cospan approaches are equivalent; that is why \cref{subsec:graphs,subsec:circuits,subsec:petri} are on the brief side.
-However, in \cref{subsec:petrirates} we elaborate and show that open dynamical systems can only be treated using decorated cospans.
+In many cases, \cref{thm:equiv} shows that the structured and decorated cospan approaches are equivalent: \cref{subsec:graphs,subsec:circuits,subsec:petri} briefly illustrate that.
+However, in \cref{subsec:petrirates} we show that open dynamical systems can only be treated using decorated cospans.
 
@@
 Surprisingly, though $F$ is a functor---for example, composition is strictly preserved---
-%%%Christina: we already said that very recently, perhaps there is no need for explaining it again?
+{\chris we already said that very recently, perhaps there is no need for explaining it again?}
 this choice of $\phi_{N,N'}$ does not make $F$ into a symmetric lax monoidal functor, since it obeys the required laws only up to natural isomorphism, as in \cref{eq:omega}.
@@
 Presumably this double functor can equivalently be obtained using the machinery of decorated cospans, with the help of \cref{thm:functoriality}.
-However, it should be clear by now that in cases where either structured or decorated cospans can be used, structured cospans are simpler.
+However, it should be clear by now that so far, in cases where either structured or decorated cospans can be used, structured cospans are simpler.
 We next turn to an example where decorated cospans are necessary.
@@
 \]
-{\chris Perhaps explain the difference between lower case $i_i$ and $o_i$ and upper case? I don't get it at first sight.}
-
+where $I_j(t)$ and $O_j(t)$ are arbitrary smooth functions of time, which describe inflows and outflows at the points $i_j \in X$ and $o_j \in Y$.
 If we drop the `inflow' and `outflow' terms $I_i$ and $O_i$ we obtain a system of coupled nonlinear first-order ordinary differential equations.
@@
 \item $D$ maps any finite set $S$ to 
-\[ D(S) = \{ v \maps \R^S \to \R^S : \; v \textrm{ is algebraic}  \}. \] 
+\[ D(S) = \{ v \maps \R^S \to \R^S | \; v \textrm{ is algebraic}  \}. \]
+{\chris Changed : to $|$ in the set, is that OK?}
 \item $D$ maps any function $f \maps S \to S'$ between finite sets to the function $D(f) \maps D(S) \to D(S')$ given as follows:
@@
 			\node (a) at (-4,0) {$a+a'$};
-			\node (b) at (1,0) {$(m_2+n_2) +_{(b+b')} (m_1+n_1)$};
+			\node (b) at (1,0) {$(m_1+n_1) +_{(b+b')} (m_2+n_2)$};
 			\node (c) at (6,0) {$c+c'$};
 			\node (a2) at (-4,1) {$a'+a$};
-			\node (b2) at (1,1) {$(n_2+m_2) +_{(b'+b)} (n_1+m_1)$};
+			\node (b2) at (1,1) {$(n_1+m_1) +_{(b'+b)} (n_2+m_2)$};
 			\node (c2) at (6,1) {$c'+c$};
             \node (a3) at (-4,2) {$a'+a$};
-			\node (b3) at (1,2) {$(n_2 +_{b'} n_1) + (m_2 +_b m_1)$};
+			\node (b3) at (1,2) {$(n_1 +_{b'} n_2) + (m_1 +_b m_2)$};
 			\node (c3) at (6,2) {$c'+c$};
             \node (a5) at (-4,-1) {$a+a'$};
-			\node (b5) at (1,-1) {$(m_2+_b m_1) + (n_2+_{b'} n_1)$};
+			\node (b5) at (1,-1) {$(m_1+_b m_2) + (n_1+_{b'} n_2)$};
 			\node (c5) at (6,-1) {$c+c'$};
             \node (a6) at (-4,-2) {$a'+a$};
-			\node (b6) at (1,-2) {$(n_2 +_{b'} n_1) + (m_2 +_b m_1)$};
+			\node (b6) at (1,-2) {$(n_1 +_{b'} n_2) + (m_1 +_b m_2)$};
 			\node (c6) at (6,-2) {$c'+c$};
@@
 %			\node (a) at (-4,0) {$a+a'$};
-			\node (b) at (1,0) {$(m_2+n_2) +_{(b+b')} (m_1+n_1)$};
-			\node (c) at (8,0) {$ (x_2\oplus y_2)\odot (x_1\oplus y_1)  \in F((m_2+n_2)+_{b+b'}(m_1+n_1))$};
+			\node (b) at (1,0) {$(m_1+n_1) +_{(b+b')} (m_2+n_2)$};
+			\node (c) at (8,0) {$ (x_1\oplus y_1)\odot (x_2\oplus y_2)  \in F((m_1+n_1)+_{b+b'}(m_2+n_2))$};
 %			\node (a2) at (-4,1) {$a'+a$};
-			\node (b2) at (1,1) {$(n_2+m_2) +_{(b'+b)} (n_1+m_1)$};
-			\node (c2) at (8,1) {$(y_2\oplus x_2)\odot(y_1\oplus x_1) \in F((n_2+m_2)+_{b'+b}(n_1+m_1))$};
+			\node (b2) at (1,1) {$(n_1+m_1) +_{(b'+b)} (n_2+m_2)$};
+			\node (c2) at (8,1) {$(y_1\oplus x_1)\odot(y_2\oplus x_2) \in F((n_1+m_1)+_{b'+b}(n_2+m_2))$};
 %                            \node (a3) at (-4,2) {$a'+a$};
-			\node (b3) at (1,2) {$(n_2 +_{b'} n_1) + (m_2 +_b m_1)$};
-			\node (c3) at (8,2) {$(y_2 \odot y_1) \oplus (x_2 \odot x_1) \in F((n_2+_{b'} n_1)+(m_2+_b m_1))$};
+			\node (b3) at (1,2) {$(n_1 +_{b'} n_2) + (m_1 +_b m_2)$};
+			\node (c3) at (8,2) {$(y_1 \odot y_2) \oplus (x_1 \odot x_2) \in F((n_1+_{b'} n_2)+(m_1+_b m_2))$};
 %                                \node (a5) at (-4,-1) {$a+a'$};
-			\node (b5) at (1,-1) {$(m_2+_b m_1) + (n_2+_{b'} n_1)$};
-			\node (c5) at (8,-1) {$(x_2 \odot x_1) \oplus (y_2 \odot y_1) \in F((m_2+_b m_1)+(n_2+_{b'} n_1))$};
+			\node (b5) at (1,-1) {$(m_1+_b m_2) + (n_1+_{b'} n_2)$};
+			\node (c5) at (8,-1) {$(x_1 \odot x_2) \oplus (y_1 \odot y_2) \in F((m_1+_b m_2)+(n_1+_{b'} n_2))$};
 %                                \node (a6) at (-4,-2) {$a'+a$};
-			\node (b6) at (1,-2) {$(n_2 +_{b'} n_1) + (m_2 +_b m_1)$};
-			\node (c6) at (8,-2) {$(y_2 \odot y_1) \oplus (x_2 \odot x_1) \in F((n_2+_{b'} n_1)+(m_2+_b m_1))$};
+			\node (b6) at (1,-2) {$(n_1 +_{b'} n_2) + (m_1 +_b m_2)$};
+			\node (c6) at (8,-2) {$(y_1 \odot y_2) \oplus (x_1 \odot x_2) \in F((n_1+_{b'} n_2)+(m_1+_b m_2))$};
 			\path[->,font=\scriptsize,>=angle 90]
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$\tau_1 \colon F(\beta +_\beta \beta)((x_2\oplus y_2)\odot(x_1\oplus y_1)) \to (y_2\oplus x_2)\odot(y_1\oplus x_1)$};
-\node (B) at (0,-.5) {$\tau_2 \colon F(\hat{\chi})((y_2 \oplus x_2)\odot(y_1 \oplus x_1)) \to (y_2\odot y_1) \oplus (x_2\odot x_1)$};
-\node (C) at (0,-1) {$\tau_3 \colon F(\hat{\chi})((x_2 \oplus y_2)\odot(x_1 \oplus y_1)) \to (x_2\odot x_1) \oplus (y_2\odot y_1)$};
-\node (D) at (0,-1.5) {$\tau_4 \colon F(\beta)((x_2\odot x_1)\oplus(y_2\odot y_1)) \to (y_2\odot y_1)\oplus(x_2\odot x_1)$};
+\node (A) at (0,0) {$\tau_1 \colon F(\beta +_\beta \beta)((x_1\oplus y_1)\odot(x_2\oplus y_2)) \to (y_1\oplus x_1)\odot(y_2\oplus x_2)$};
+\node (B) at (0,-.5) {$\tau_2 \colon F(\hat{\chi})((y_1 \oplus x_1)\odot(y_2 \oplus x_2)) \to (y_1\odot y_2) \oplus (x_1\odot x_2)$};
+\node (C) at (0,-1) {$\tau_3 \colon F(\hat{\chi})((x_1 \oplus y_1)\odot(x_2 \oplus y_2)) \to (x_1\odot x_2) \oplus (y_1\odot y_2)$};
+\node (D) at (0,-1.5) {$\tau_4 \colon F(\beta)((x_1\odot x_2)\oplus(y_1\odot y_2)) \to (y_1\odot y_2)\oplus(x_1\odot x_2)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \begin{displaymath}
-\scalebox{.8}{$F(\beta\hat{\chi})((x_2 \oplus y_2)\odot(x_1 \oplus y_1))\cong F(\beta)(F\hat{\chi})((x_2 \oplus y_2)\odot(x_1 \oplus y_1))\xrightarrow{F(\beta)(\tau_3)}F(\beta)((x_2\odot x_1) \oplus (y_2\odot y_1))\xrightarrow{\tau_4}(y_2 \odot y_1) \oplus (x_2 \odot x_1)$}
+\scalebox{.8}{$F(\beta\hat{\chi})((x_1 \oplus y_1)\odot(x_2 \oplus y_2))\cong F(\beta)(F\hat{\chi})((x_1 \oplus y_1)\odot(x_2 \oplus y_2))\xrightarrow{F(\beta)(\tau_3)}F(\beta)((x_1\odot x_2) \oplus (y_1\odot y_2))\xrightarrow{\tau_4}(y_1 \odot y_2) \oplus (x_1 \odot x_2)$}
 \end{displaymath}
@@
 \node (D) at (3,-0.5) {$\scriptstyle{\one}$};
-\node (E) at (6.75,0.5) {$\scriptstyle{F(m_2 + n_2) \times F(m_1+n_1)}$};
+\node (E) at (6.75,0.5) {$\scriptstyle{F(m_1 + n_1) \times F(m_2+n_2)}$};
 \node () at (10.25,-1) {$\scriptstyle\stackrel{\cref{eq:braidedpseudofun}}{\cong}$};
 \node () at (7.875,0) {$\scriptstyle\stackrel{\cref{eq:interchangedeco}}{\cong}$};
-\node (E') at (6.75,-0.5) {$\scriptstyle{F(m_2+m_1) \times F(n_2+n_1)}$};
-\node (B) at (9,0.5) {$\scriptstyle{F((m_2+n_2)+(m_1+n_1))}$};
-\node (B') at (9,-0.5) {$\scriptstyle{F(m_2+_b m_1)\times F(n_2+_{b'}n_1)}$};
-\node (C) at (11.5,0.5) {$\scriptstyle{F((m_2+n_2)+_{b+b'}(m_1+n_1))}$};
-\node (C') at (11.5,-0.5) {$\scriptstyle{F((m_2+_b m_1)+ (n_2+_{b'} n_1))}$};
-\node (G) at (4.25,0.5) {$\scriptstyle{F(m_2) \times F(n_2) \times F(m_1) \times F(n_1)}$};
-\node (G') at (4.25,-0.5) {$\scriptstyle{F(m_2) \times F(m_1) \times F(n_2) \times F(n_1)}$};
-\node (G'') at (4.25,-1.5) {$\scriptstyle{F(n_2) \times F(n_1) \times F(m_2) \times F(m_1)}$};
-\node (E'') at (6.75,-1.5) {$\scriptstyle{F(n_2+n_1) \times F(m_2+m_1)}$};
-\node (B'') at (9,-1.5) {$\scriptstyle{F(n_2+_{b'}n_1) \times F(m_2+_b m_1)}$};
-\node (C'') at (11.5,-1.5) {$\scriptstyle{F((n_2+_{b'}n_1)+(m_2+_b m_1))}$};
-\node (X) at (3.4,0.2) {$\scriptscriptstyle{x_2 \times y_2 \times x_1 \times y_1}$};
-\node (X') at (3.4,-0.35) {$\scriptscriptstyle{x_2 \times x_1 \times y_2 \times y_1}$};
-\node (X'') at (3.4,-1.2) {$\scriptscriptstyle{y_2 \times y_1 \times x_2 \times x_1}$};
+\node (E') at (6.75,-0.5) {$\scriptstyle{F(m_1+m_2) \times F(n_1+n_2)}$};
+\node (B) at (9,0.5) {$\scriptstyle{F((m_1+n_1)+(m_2+n_2))}$};
+\node (B') at (9,-0.5) {$\scriptstyle{F(m_1+_b m_2)\times F(n_1+_{b'}n_2)}$};
+\node (C) at (11.5,0.5) {$\scriptstyle{F((m_1+n_1)+_{b+b'}(m_2+n_2))}$};
+\node (C') at (11.5,-0.5) {$\scriptstyle{F((m_1+_b m_2)+ (n_1+_{b'} n_2))}$};
+\node (G) at (4.25,0.5) {$\scriptstyle{F(m_1) \times F(n_1) \times F(m_2) \times F(n_2)}$};
+\node (G') at (4.25,-0.5) {$\scriptstyle{F(m_1) \times F(m_2) \times F(n_1) \times F(n_2)}$};
+\node (G'') at (4.25,-1.5) {$\scriptstyle{F(n_1) \times F(n_2) \times F(m_1) \times F(m_2)}$};
+\node (E'') at (6.75,-1.5) {$\scriptstyle{F(n_1+n_2) \times F(m_1+m_2)}$};
+\node (B'') at (9,-1.5) {$\scriptstyle{F(n_1+_{b'}n_2) \times F(m_1+_b m_2)}$};
+\node (C'') at (11.5,-1.5) {$\scriptstyle{F((n_1+_{b'}n_2)+(m_1+_b m_2))}$};
+\node (X) at (3.4,0.2) {$\scriptscriptstyle{x_1 \times y_1 \times x_2 \times y_2}$};
+\node (X') at (3.4,-0.35) {$\scriptscriptstyle{x_1 \times x_2 \times y_1 \times y_2}$};
+\node (X'') at (3.4,-1.2) {$\scriptscriptstyle{y_1 \times y_2 \times x_1 \times x_2}$};
 \path[->,font=\scriptsize,>=angle 90]
 (B') edge node [fill=white] {$\beta$} (B'')
-(E) edge node [above] {$\phi_{m_2+n_2,m_1+n_1}$} (B)
+(E) edge node [above] {$\phi_{m_1+n_1,m_2+n_2}$} (B)
 (E'') edge node [below] {$F\psi\times F\psi$} (B'')
@@
 (B) edge node [above] {$F(\psi)$} (C)
-(B'') edge node [below] {$\phi_{n_2+_{b'}n_1,m_2+_b m_1}$} (C'')
-(B') edge node [above] {$\phi_{m_2+_b m_1,n_2+_{b'}n_1}$} (C')
+(B'') edge node [below] {$\phi_{n_1+_{b'}n_2,m_1+_b m_2}$} (C'')
+(B') edge node [above] {$\phi_{m_1+_b m_2,n_1+_{b'}n_2}$} (C')
 (C) edge node [fill=white] {$F(\hat{\chi})$} (C')
 (C') edge node [fill=white] {$F(\beta)$} (C'')
-(G) edge node [above] {$\phi_{m_2,n_2} {\times} \phi_{m_1,n_1}$} (E)
-(G'') edge node [below] {$\phi_{n_2,n_1} {\times} \phi_{m_2,m_1}$} (E'')
-(G') edge node [above] {$\phi_{m_2,m_1} \times \phi_{n_2,n_1}$} (E')
+(G) edge node [above] {$\phi_{m_1,n_1} {\times} \phi_{m_2,n_2}$} (E)
+(G'') edge node [below] {$\phi_{n_1,n_2} {\times} \phi_{m_1,m_2}$} (E'')
+(G') edge node [above] {$\phi_{m_1,m_2} \times \phi_{n_1,n_2}$} (E')
 (G) edge node [fill=white] {$1 \times \beta \times 1$} (G')
@@
 \node (D) at (3,-0.5) {$\scriptstyle{\one}$};
-\node (E) at (6.75,0.5) {$\scriptstyle{F(m_2 + n_2) \times F(m_1+n_1)}$};
+\node (E) at (6.75,0.5) {$\scriptstyle{F(m_1 + n_1) \times F(m_2+n_2)}$};
 \node () at (5.5,-1) {$\scriptstyle{\cong}$};
@@
 \node () at (7.875,0) {$\scriptstyle\stackrel{\cref{eq:interchangedeco}}{\cong}$};
-\node (E') at (6.75,-0.5) {$\scriptstyle{F(m_2+m_1) \times F(n_2+n_1)}$};
-\node (B) at (9,0.5) {$\scriptstyle{F((m_2+n_2)+(m_1+n_1))}$};
-\node (B') at (9,-0.5) {$\scriptstyle{F((m_2+ m_1)+(n_2+n_1))}$};
-\node (C) at (11.5,0.5) {$\scriptstyle{F((m_2+n_2)+_{b+b'}(m_1+n_1))}$};
-\node (C') at (11.5,-0.5) {$\scriptstyle{F((m_2+_b m_1)+ (n_2+_{b'} n_1))}$};
-\node (G) at (4.25,0.5) {$\scriptstyle{F(m_2) \times F(n_2) \times F(m_1) \times F(n_1)}$};
-\node (G') at (4.25,-0.5) {$\scriptstyle{F(m_2) \times F(m_1) \times F(n_2) \times F(n_1)}$};
-\node (G'') at (4.25,-1.5) {$\scriptstyle{F(n_2) \times F(n_1) \times F(m_2) \times F(m_1)}$};
-\node (E'') at (6.75,-1.5) {$\scriptstyle{F(n_2+n_1) \times F(m_2+m_1)}$};
-\node (B'') at (9,-1.5) {$\scriptstyle{F((n_2+n_1)+(m_2+ m_1))}$};
-\node (C'') at (11.5,-1.5) {$\scriptstyle{F((n_2+_{b'}n_1)+(m_2+_b m_1))}$};
-\node (X) at (3.4,0.2) {$\scriptscriptstyle{x_2 \times y_2 \times x_1 \times y_1}$};
-\node (X') at (3.4,-0.35) {$\scriptscriptstyle{x_2 \times x_1 \times y_2 \times y_1}$};
-\node (X'') at (3.4,-1.2) {$\scriptscriptstyle{y_2 \times y_1 \times x_2 \times x_1}$};
+\node (E') at (6.75,-0.5) {$\scriptstyle{F(m_1+m_2) \times F(n_1+n_2)}$};
+\node (B) at (9,0.5) {$\scriptstyle{F((m_1+n_1)+(m_2+n_2))}$};
+\node (B') at (9,-0.5) {$\scriptstyle{F((m_1+ m_2)+(n_1+n_2))}$};
+\node (C) at (11.5,0.5) {$\scriptstyle{F((m_1+n_1)+_{b+b'}(m_2+n_2))}$};
+\node (C') at (11.5,-0.5) {$\scriptstyle{F((m_1+_b m_2)+ (n_1+_{b'} n_2))}$};
+\node (G) at (4.25,0.5) {$\scriptstyle{F(m_1) \times F(n_1) \times F(m_2) \times F(n_2)}$};
+\node (G') at (4.25,-0.5) {$\scriptstyle{F(m_1) \times F(m_2) \times F(n_1) \times F(n_2)}$};
+\node (G'') at (4.25,-1.5) {$\scriptstyle{F(n_1) \times F(n_2) \times F(m_1) \times F(m_2)}$};
+\node (E'') at (6.75,-1.5) {$\scriptstyle{F(n_1+n_2) \times F(m_1+m_2)}$};
+\node (B'') at (9,-1.5) {$\scriptstyle{F((n_1+n_2)+(m_1+ m_2))}$};
+\node (C'') at (11.5,-1.5) {$\scriptstyle{F((n_1+_{b'}n_2)+(m_1+_b m_2))}$};
+\node (X) at (3.4,0.2) {$\scriptscriptstyle{x_1 \times y_1 \times x_2 \times y_2}$};
+\node (X') at (3.4,-0.35) {$\scriptscriptstyle{x_1 \times x_2 \times y_1 \times y_2}$};
+\node (X'') at (3.4,-1.2) {$\scriptscriptstyle{y_1 \times y_2 \times x_1 \times x_2}$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (E') edge node [fill=white] {$\beta$} (E'')
-(E) edge node [above] {$\phi_{m_2+n_2,m_1+n_1}$} (B)
-(E'') edge node [above] {$\phi_{n_2+n_1,m_2+m_1}$} (B'')
-(E') edge node [above] {$\phi_{m_2+m_1,n_2+n_1}$} (B')
+(E) edge node [above] {$\phi_{m_1+n_1,m_2+n_2}$} (B)
+(E'') edge node [above] {$\phi_{n_1+n_2,m_1+m_2}$} (B'')
+(E') edge node [above] {$\phi_{m_1+m_2,n_1+n_2}$} (B')
 (B) edge node [above] {$F(\psi)$} (C)
@@
 (C') edge node [fill=white] {$F(\beta)$} (C'')
-(G) edge node [above] {$\phi_{m_2,n_2} {\times} \phi_{m_1,n_1}$} (E)
-(G'') edge node [above] {$\phi_{n_2,n_1} {\times} \phi_{m_2,m_1}$} (E'')
-(G') edge node [above] {$\phi_{m_2,m_1} \times \phi_{n_2,n_1}$} (E')
+(G) edge node [above] {$\phi_{m_1,n_1} {\times} \phi_{m_2,n_2}$} (E)
+(G'') edge node [above] {$\phi_{n_1,n_2} {\times} \phi_{m_1,m_2}$} (E'')
+(G') edge node [above] {$\phi_{m_1,m_2} \times \phi_{n_1,n_2}$} (E')
 (G) edge node [fill=white] {$1 \times \beta \times 1$} (G')
@@
 \begin{displaymath}
-\scalebox{.8}{$F(\hat{\chi}(\beta +_\beta \beta))( (x_2 \oplus y_2)\odot (x_1 \oplus y_1))\cong F(\hat{\chi})F(\beta +_\beta \beta)( (x_2 \oplus y_2)\odot (x_1 \oplus y_1)) \xrightarrow{F(\hat{\chi})(\tau_1)}F(\hat{\chi})(y_2\oplus x_2)\odot(y_1\oplus x_1)\xrightarrow{\tau_2}(y_2 \odot y_1) \oplus (x_2 \odot x_1)$}
+\scalebox{.8}{$F(\hat{\chi}(\beta +_\beta \beta))( (x_1 \oplus y_1)\odot (x_2 \oplus y_2))\cong F(\hat{\chi})F(\beta +_\beta \beta)( (x_1 \oplus y_1)\odot (x_2 \oplus y_2)) \xrightarrow{F(\hat{\chi})(\tau_1)}F(\hat{\chi})(y_1\oplus x_1)\odot(y_2\oplus x_2)\xrightarrow{\tau_2}(y_1 \odot y_2) \oplus (x_1 \odot x_2)$}
 \end{displaymath}
@@
 \node (D) at (3,-0.5) {$\scriptstyle{\one}$};
-\node (E) at (6.75,0.5) {$\scriptstyle{F(m_2 + n_2) \times F(m_1+n_1)}$};
+\node (E) at (6.75,0.5) {$\scriptstyle{F(m_1 + n_1) \times F(m_2+n_2)}$};
 \node () at (5.5,0) {$\scriptstyle\stackrel{\cref{eq:braidedpseudofun}}{\cong}$};
@@
 \node () at (12,-1) {$\scriptstyle\cong$};
-\node (E') at (6.75,-0.5) {$\scriptstyle{F(n_2+m_2) \times F(n_1+m_1)}$};
-\node (B) at (9,0.5) {$\scriptstyle{F((m_2+n_2)+(m_1+n_1))}$};
-\node (B') at (9,-0.5) {$\scriptstyle{F((n_2+m_2)+(n_1+m_1))}$};
-\node (C) at (11.5,0.5) {$\scriptstyle{F((m_2+n_2)+_{b+b'}(m_1+n_1))}$};
-\node (C') at (11.5,-0.5) {$\scriptstyle{F((n_2+m_2)+_{b'+b}(n_1+m_1))}$};
-\node (G) at (4.25,0.5) {$\scriptstyle{F(m_2) \times F(n_2) \times F(m_1) \times F(n_1)}$};
-\node (G') at (4.25,-0.5) {$\scriptstyle{F(n_2) \times F(m_2) \times F(n_1) \times F(m_1)}$};
-\node (G'') at (4.25,-1.5) {$\scriptstyle{F(n_2) \times F(n_1) \times F(m_2) \times F(m_1)}$};
-\node (E'') at (6.75,-1.5) {$\scriptstyle{F(n_2+n_1) \times F(m_2+m_1)}$};
-\node (B'') at (9,-1.5) {$\scriptstyle{F(n_2+_{b'}n_1)\times F(m_2+_b m_1)}$};
-\node (C'') at (11.5,-1.5) {$\scriptstyle{F((n_2+_{b'}n_1)+(m_2+_b m_1))}$};
-\node (X) at (3.4,0.2) {$\scriptscriptstyle{x_2 \times y_2 \times x_1 \times y_1}$};
-\node (X') at (3.4,-0.35) {$\scriptscriptstyle{y_2 \times x_2 \times y_1 \times x_1}$};
-\node (X'') at (3.4,-1.2) {$\scriptscriptstyle{y_2 \times y_1 \times x_2 \times x_1}$};
+\node (E') at (6.75,-0.5) {$\scriptstyle{F(n_1+m_1) \times F(n_2+m_2)}$};
+\node (B) at (9,0.5) {$\scriptstyle{F((m_1+n_1)+(m_2+n_2))}$};
+\node (B') at (9,-0.5) {$\scriptstyle{F((n_1+m_1)+(n_2+m_2))}$};
+\node (C) at (11.5,0.5) {$\scriptstyle{F((m_1+n_1)+_{b+b'}(m_2+n_2))}$};
+\node (C') at (11.5,-0.5) {$\scriptstyle{F((n_1+m_1)+_{b'+b}(n_2+m_2))}$};
+\node (G) at (4.25,0.5) {$\scriptstyle{F(m_1) \times F(n_1) \times F(m_2) \times F(n_2)}$};
+\node (G') at (4.25,-0.5) {$\scriptstyle{F(n_1) \times F(m_1) \times F(n_2) \times F(m_2)}$};
+\node (G'') at (4.25,-1.5) {$\scriptstyle{F(n_1) \times F(n_2) \times F(m_1) \times F(m_2)}$};
+\node (E'') at (6.75,-1.5) {$\scriptstyle{F(n_1+n_2) \times F(m_1+m_2)}$};
+\node (B'') at (9,-1.5) {$\scriptstyle{F(n_1+_{b'}n_2)\times F(m_1+_b m_2)}$};
+\node (C'') at (11.5,-1.5) {$\scriptstyle{F((n_1+_{b'}n_2)+(m_1+_b m_2))}$};
+\node (X) at (3.4,0.2) {$\scriptscriptstyle{x_1 \times y_1 \times x_2 \times y_2}$};
+\node (X') at (3.4,-0.35) {$\scriptscriptstyle{y_1 \times x_1 \times y_2 \times x_2}$};
+\node (X'') at (3.4,-1.2) {$\scriptscriptstyle{y_1 \times y_2 \times x_1 \times x_2}$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (E) edge node [fill=white] {$F(\beta) \times F(\beta)$} (E')
-(E) edge node [above] {$\phi_{m_2+n_2,m_1+n_1}$} (B)
+(E) edge node [above] {$\phi_{m_1+n_1,m_2+n_2}$} (B)
 (E'') edge node [below] {$F\psi\times F\psi)$} (B'')
-(E') edge node [above] {$\phi_{n_2+m_2,n_1+m_1}$} (B')
+(E') edge node [above] {$\phi_{n_1+m_1,n_2+m_2}$} (B')
 (B) edge node [above] {$F(\psi)$} (C)
-(B'') edge node [below] {$\phi_{n_2+_{b'}n_1,m_2+_{b}m_1}$} (C'')
+(B'') edge node [below] {$\phi_{n_1+_{b'}n_2,m_1+_{b}m_2}$} (C'')
 (B') edge node [above] {$F(\psi)$} (C')
@@
 (C') edge node [fill=white] {$F(\hat{\chi})$} (C'')
-(G) edge node [above] {$\phi_{m_2,n_2} {\times} \phi_{m_1,n_1}$} (E)
-(G'') edge node [below] {$\phi_{n_2,n_1} {\times} \phi_{m_2,m_1}$} (E'')
-(G') edge node [above] {$\phi_{n_2,m_2} \times \phi_{n_1,m_1}$} (E')
+(G) edge node [above] {$\phi_{m_1,n_1} {\times} \phi_{m_2,n_2}$} (E)
+(G'') edge node [below] {$\phi_{n_1,n_2} {\times} \phi_{m_1,m_2}$} (E'')
+(G') edge node [above] {$\phi_{n_1,m_1} \times \phi_{n_2,m_2}$} (E')
 (G) edge node [fill=white] {$\beta \times \beta$} (G')
@@
 
-\bibitem{LS} E.\ Lerman and D.\ Spivak, An algebra of open continuous time dynamical systems and networks. Available as \href{http://arxiv.org/abs/1602.01017}{arXiv:1602.01017}.
+%\bibitem{LS} E.\ Lerman and D.\ Spivak, An algebra of open continuous time dynamical systems and networks. Available as \href{http://arxiv.org/abs/1602.01017}{arXiv:1602.01017}.
 

### 2020-12-09 cospans.tex
work on Lemma 3.4 - Lemma 3.6

@@
-% Structured and decorated cospans
+% Structured versus decorated cospans
 % John Baez, Kenny Courser and Christina Vasilakopoulou
 % in LaTeX
-% 2020/12/8
+% 2020/12/9
 
@@
 \begin{itemize}
-\item a functor $H \maps \A \to \A'$ that preserves finite limits.
+\item a functor $H \maps \A \to \A'$ that preserves finite limits,
 \item a symmetric lax monoidal pseudofunctor $(E,\phi,\phi_0) \maps \Cat \to \Cat$, 
-\item an isomorphism $\theta \maps EF \Rightarrow F'H$: {\chris is this natural or pseudonatural? It should be clarified.}
+\item a natural isomorphism $\theta \maps EF \Rightarrow F'H$: 
 \[
@@
 \begin{itemize}
-\item The image of an object $a \in F\lCsp_0=\A$ is the object $H(a) \in F'\lCsp_0=\A'$,
+\item The image of an object $a \in F\lCsp_0=\A$ is the object $H(a) \in F'\lCsp_0=\A'$.
 \item The image of a vertical 1-morphism $f \colon a \to b$ is the vertical 1-morphism $H(f) \colon H(a) \to H(b)$. 
@@
 \]
-where given a decoration morphism $\tau \colon F(h)(x) \to x'$, the induced decoration morphism is:
+where a decoration morphism $\tau \colon F(h)(x) \to x'$ is mapped to a 
+decoration morphism as follows:
 \[
@@
 \]
-{\chris There should be an iso on the right if we go with pseudonatural isomorphism}
 \end{itemize}
-%Regarding maps between symmetric monoidal double categories, consider another symmetric lax monoidal pseudofunctor $F' \maps \mathsf{A'} \to \Cat$%, we can obtain another symmetric monoidal double category $F' \lCsp$.
-%a morphism from $F\lCsp$ to $F' \lCsp$ will then be a double functor $\H \maps F\lCsp \to F' \lCsp$ whose object component is given by a finite colimit preserving functor $\H_0 = H \maps \A \to \mathsf{A'}$ and whose arrow component is given by a functor $\H_1$ defined on horizontal 1-cells by:
-%We define the object component $\lH_0$ to be $H$ and define the arrow component $\lH_1$ on horizontal 1-cells by:
-%\[
-%\begin{tikzpicture}[scale=1.5]
-%\node (A) at (0,0) {$a$};
-%\node (B) at (1,0) {$c$};
-%\node (C) at (2,0) {$b$};
-%\node (D) at (1,-0.5) {$d \in F(c)$};
-%\node (E) at (2.75,0) {$\mapsto$};
-%\node (A') at (3.5,0) {$H(a)$};
-%\node (B') at (4.5,0) {$H(c)$};
-%\node (C') at (5.5,0) {$H(b)$};
-%\node (D') at (4.5,-0.5) {$\theta_c E(d) \phi \in F'(H(c))$};
-%\path[->,font=\scriptsize,>=angle 90]
-%(A) edge node[above]{$i$} (B)
-%(C) edge node[above]{$o$} (B)
-%(A') edge node[above]{$H(i)$} (B')
-%(C') edge node[above]{$H(o)$} (B');
-%\end{tikzpicture}
-%\]
-%and on 2-morphisms by:
-%\[
-%\begin{tikzpicture}[scale=1.5]
-%\node (A) at (0,0.5) {$a$};
-%\node (A') at (0,-0.5) {$a'$};
-%\node (B) at (1,0.5) {$c$};
-%\node (C) at (2,0.5) {$b$};
-%\node (C') at (2,-0.5) {$b'$};
-%\node (D) at (1,-0.5) {$c'$};
-%\node (E) at (3,0.5) {$d \in F(c)$};
-%\node (F) at (3,-0.5) {$d' \in F(c')$};
-%\node (G) at (1,-1) {$\tau \maps F(h)(d) \to d'$};
-%\node (A'') at (4.25,0.5) {$H(a)$};
-%\node (A''') at (4.25,-0.5) {$H(a')$};
-%\node (B'') at (5.25,0.5) {$H(c)$};
-%\node (C'') at (6.25,0.5) {$H(b)$};
-%\node (C''') at (6.25,-0.5) {$H(b')$};
-%\node (D'') at (5.25,-0.5) {$H(c')$};
-%\node (E'') at (8,0.5) {$\theta_c E(d) \phi \in F'(H(c))$};
-%\node (F'') at (8,-0.5) {$\theta_{c'} E(d') \phi \in F'(H(c'))$};
-%\node (G'') at (5.25,-1) {$E(\tau) \maps F'(H(h))(\theta_c E(d)\phi) \to (\theta_{c'}E(d')\phi)$};
-%\node (H) at (3.5,0) {$\mapsto$};
-%\path[->,font=\scriptsize,>=angle 90]
-%(A) edge node[above]{$$} (B)
-%(C) edge node[above]{$$} (B)
-%(A) edge node[left]{$f$} (A')
-%(C) edge node[right]{$g$} (C')
-%(A') edge node {$$} (D)
-%(C') edge node {$$} (D)
-%(B) edge node [left] {$h$} (D)
-%(A'') edge node[above]{$$} (B'')
-%(C'') edge node[above]{$$} (B'')
-%(A'') edge node[left]{$H(f)$} (A''')
-%(C'') edge node[right]{$H(g)$} (C''')
-%(A''') edge node {$$} (D'')
-%(C''') edge node {$$} (D'')
-%(B'') edge node [left] {$H(h)$} (D'');
-%\end{tikzpicture}
-%\]
-%where $E \maps \Cat \to \Cat$ is a symmetric lax monoidal pseudofuctor such that the following diagram commutes up to isomorphism $\theta \maps EF \Rightarrow F'H$:
-%\[
-%\begin{tikzpicture}[scale=1.5]
-%\node (A) at (0,0) {$\A$};
-%\node (B) at (1,0) {$\Cat$};
-%\node (C) at (0,-1) {$\mathsf{A'}$};
-%\node (D) at (1,-1) {$\Cat$};
-%\node (E) at (0.5,-0.5) {$\Swarrow \theta$};
-%\path[->,font=\scriptsize,>=angle 90]
-%(A) edge node[above]{$F$} (B)
-%(A) edge node[left]{$H$} (C)
-%(B) edge node[right]{$E$} (D)
-%(C) edge node[above]{$F'$} (D);
-%\end{tikzpicture}
-%\]
-
-\begin{comment}
-Recall that we can think of the object $d \in F(c)$ as a morphism $d \maps 1 \to F(c)$ and the functor $\tau \maps F(h)(d) \to d'$ of $F(c')$ as a natural transformation  in $\Cat$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,-0.5) {$1$};
-\node (B) at (1,0) {$F(c)$};
-\node (D) at (1,-1) {$F(c')$};
-\node (C) at (0.75,-0.5) {$\Swarrow \tau$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$d$} (B)
-(A) edge node[below]{$d'$} (D)
-(B) edge node[right]{$F(h)$} (D);
-\end{tikzpicture}
-\]
-Applying the symmetric lax monoidal pseudofunctor $E \maps \Cat \to \Cat$ to this diagram yields:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,-0.5) {$1 \xrightarrow{\phi} E(1)$};
-\node (B) at (2,0) {$E(F(c))$};
-\node (D) at (2,-1) {$E(F(c'))$};
-\node (C) at (1.5,-0.5) {$\Swarrow E(\tau)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$E(d)$} (B)
-(A) edge node[below]{$E(d')$} (D)
-(B) edge node[right]{$E(F(h))$} (D);
-\end{tikzpicture}
-\]
-Then because the above square commutes up to the isomorphism $\theta \maps EF \Rightarrow F'H$, we get:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,-0.5) {$1 \xrightarrow{\phi} E(1)$};
-\node (B) at (2,0) {$E(F(c))$};
-\node (D) at (2,-1) {$E(F(c'))$};
-\node (C) at (1.5,-0.5) {$\Swarrow E(\tau)$};
-\node (E) at (4,0) {$F'(H(c))$};
-\node (F) at (4,-1) {$F'(H(c'))$};
-\path[->,font=\scriptsize,>=angle 90]
-(B) edge node [above] {$\theta_c$} (E)
-(D) edge node [above] {$\theta_{c'}$} (F)
-(E) edge node [right] {$F'(H(h))$} (F)
-(A) edge node[above]{$E(d)$} (B)
-(A) edge node[below]{$E(d')$} (D)
-(B) edge node[right]{$E(F((h))$} (D);
-\end{tikzpicture}
-\]
-which results in a 2-morphism $E(\tau) \maps F'(H(h))(\theta_c E(d)\phi) \to (\theta_{c'} E(d')\phi)$ in $F'(H(c'))$.
-To check that the above recipe is functorial, given two vertically composable 2-morphisms in $F\lCsp$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$a$};
-\node (A') at (0,-0.5) {$a'$};
-\node (B) at (1.5,0.5) {$c$};
-\node (C) at (3,0.5) {$b$};
-\node (C') at (3,-0.5) {$b'$};
-\node (D) at (1.5,-0.5) {$c'$};
-\node (E) at (4.5,0.5) {$d \in F(c)$};
-\node (F) at (4.5,-0.5) {$d' \in F(c')$};
-\node (G) at (1.5,-1) {$\tau \maps F(h)(d) \to d'$};
-\node (A'') at (0,-1.5) {$a'$};
-\node (A''') at (0,-2.5) {$a''$};
-\node (B'') at (1.5,-1.5) {$c'$};
-\node (C'') at (3,-1.5) {$b'$};
-\node (C''') at (3,-2.5) {$b''$};
-\node (D'') at (1.5,-2.5) {$c''$};
-\node (E'') at (4.5,-1.5) {$d' \in F(c')$};
-\node (F'') at (4.5,-2.5) {$d'' \in F(c'')$};
-\node (G'') at (1.5,-3) {$\tau' \maps F(h')(d') \to d''$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$$} (B)
-(C) edge node[above]{$$} (B)
-(A) edge node[left]{$f$} (A')
-(C) edge node[right]{$g$} (C')
-(A') edge node [above]{$$} (D)
-(C') edge node [above]{$$} (D)
-(B) edge node [left] {$h$} (D)
-(A'') edge node[above]{$$} (B'')
-(C'') edge node[above]{$$} (B'')
-(A'') edge node[left]{$f'$} (A''')
-(C'') edge node[right]{$g'$} (C''')
-(A''') edge node [above]{$$} (D'')
-(C''') edge node [above]{$$} (D'')
-(B'') edge node [left] {$h'$} (D'');
-\end{tikzpicture}
-\]
-if we first compose these, the result is:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$a$};
-\node (A') at (0,-0.5) {$a''$};
-\node (B) at (1.5,0.5) {$c$};
-\node (C) at (3,0.5) {$b$};
-\node (C') at (3,-0.5) {$b''$};
-\node (D) at (1.5,-0.5) {$c''$};
-\node (E) at (4.5,0.5) {$d \in F(c)$};
-\node (F) at (4.5,-0.5) {$d'' \in F(c'')$};
-\node (G) at (1.5,-1) {$\tau ' \tau \maps F(h' h)(d) \to d''$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$$} (B)
-(C) edge node[above]{$$} (B)
-(A) edge node[left]{$f' f$} (A')
-(C) edge node[right]{$g' g$} (C')
-(A') edge node [above]{$$} (D)
-(C') edge node [above]{$$} (D)
-(B) edge node [left] {$h' h$} (D);
-\end{tikzpicture}
-\]
-and then the image of this 2-morphism under the double functor $\H$ is given by:
-and then the image of this 2-morphism under the double functor $\lH$ is given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$H(a)$};
-\node (A') at (0,-0.5) {$H(a'')$};
-\node (B) at (1.5,0.5) {$H(c)$};
-\node (C) at (3,0.5) {$H(b)$};
-\node (C') at (3,-0.5) {$H(b'')$};
-\node (D) at (1.5,-0.5) {$H(c'')$};
-\node (E) at (5,0.5) {$\theta_c E(d) \phi \in F'(H(c))$};
-\node (F) at (5,-0.5) {$\theta_{c''} E(d'') \phi \in F'(H(c''))$};
-\node (G) at (1.5,-1) {$E(\tau ' \tau) \maps F'(H(h' h))(\theta_c E(d)\phi) \to (\theta_{c''}E(d'')\phi).$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$$} (B)
-(C) edge node[above]{$$} (B)
-(A) edge node[left]{$H(f' f)$} (A')
-(C) edge node[right]{$H(g' g)$} (C')
-(A') edge node [above]{$$} (D)
-(C') edge node [above]{$$} (D)
-(B) edge node [left] {$H(h' h)$} (D);
-\end{tikzpicture}
-\]
-On the other hand, applying the double functor $\H$ first gives:
-On the other hand, applying the double functor $\lH$ first gives:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$H(a)$};
-\node (A') at (0,-0.5) {$H(a')$};
-\node (B) at (1.5,0.5) {$H(c)$};
-\node (C) at (3,0.5) {$H(b)$};
-\node (C') at (3,-0.5) {$H(b')$};
-\node (D) at (1.5,-0.5) {$H(c')$};
-\node (E) at (5,0.5) {$\theta_c E(d) \phi \in F'(H(c))$};
-\node (F) at (5,-0.5) {$\theta_{c'} E(d') \phi \in F'(H(c'))$};
-\node (G) at (1.5,-1) {$E(\tau) \maps F'(H(h))(\theta_c E(d)\phi) \to (\theta_{c'} E(d')\phi)$};
-\node (A'') at (0,-1.5) {$H(a')$};
-\node (A''') at (0,-2.5) {$H(a'')$};
-\node (B'') at (1.5,-1.5) {$H(c')$};
-\node (C'') at (3,-1.5) {$H(b')$};
-\node (C''') at (3,-2.5) {$H(b'')$};
-\node (D'') at (1.5,-2.5) {$H(c'')$};
-\node (E'') at (5,-1.5) {$\theta_{c'} E(d') \phi \in F'(H(c'))$};
-\node (F'') at (5,-2.5) {$\theta_{c''} E(d'') \phi \in F'(H(c''))$};
-\node (G'') at (1.5,-3) {$E(\tau') \maps F'(H(h'))(\theta_{c'} E(d')\phi) \to (\theta_{c''}E(d'')\phi)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$$} (B)
-(C) edge node[above]{$$} (B)
-(A) edge node[left]{$H(f)$} (A')
-(C) edge node[right]{$H(g)$} (C')
-(A') edge node [above]{$$} (D)
-(C') edge node [above]{$$} (D)
-(B) edge node [left] {$H(h)$} (D)
-(A'') edge node[above]{$$} (B'')
-(C'') edge node[above]{$$} (B'')
-(A'') edge node[left]{$H(f')$} (A''')
-(C'') edge node[right]{$H(g')$} (C''')
-(A''') edge node [above]{$$} (D'')
-(C''') edge node [above]{$$} (D'')
-(B'') edge node [left] {$H(h')$} (D'');
-\end{tikzpicture}
-\]
-and then composing these gives:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$H(a)$};
-\node (A') at (0,-0.5) {$H(a'')$};
-\node (B) at (1.5,0.5) {$H(c)$};
-\node (C) at (3,0.5) {$H(b)$};
-\node (C') at (3,-0.5) {$H(b'')$};
-\node (D) at (1.5,-0.5) {$H(c'')$};
-\node (E) at (5,0.5) {$\theta_c E(d) \phi \in F'(H(c))$};
-\node (F) at (5,-0.5) {$\theta_{c''} E(d'') \phi \in F'(H(c''))$};
-\node (G) at (1.5,-1) {$E(\tau ' \tau) \maps F'(H(h' h))(\theta_c E(d)\phi) \to (\theta_{c''}E(d'')\phi).$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$$} (B)
-(C) edge node[above]{$$} (B)
-(A) edge node[left]{$H(f' f)$} (A')
-(C) edge node[right]{$H(g' g)$} (C')
-(A') edge node [above]{$$} (D)
-(C') edge node [above]{$$} (D)
-(B) edge node [left] {$H(h' h)$} (D);
-\end{tikzpicture}
-\]
-This double functor $\H$ satisfies the equations $S \H_1 = HS$ and $T \H_1=HT$.
-This double functor $\lH$ satisfies the equations $S \lH_1 = HS$ and $T \lH_1=HT$.
-
-Given two composable horizontal 1-cells $M$ and $N$ in $F\lCsp$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a_1$};
-\node (B) at (1,0) {$c_1$};
-\node (C) at (2,0) {$b$};
-\node (D) at (1,-0.5) {$d_M \in F(c_1)$};
-\node (E) at (3,0) {$b$};
-\node (F) at (4,0) {$c_2$};
-\node (G) at (5,0) {$a_2$};
-\node (H) at (4,-0.5) {$d_N \in F(c_2)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i_1$} (B)
-(C) edge node[above]{$o_1$} (B)
-(E) edge node[above]{$i_2$} (F)
-(G) edge node[above]{$o_2$} (F);
-\end{tikzpicture}
-\]
-composing first gives $M \odot N$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a_1$};
-\node (B) at (1.5,0) {$c_1+_b c_2$};
-\node (C) at (3,0) {$a_2$};
-\node (D) at (1.5,-0.5) {$d_{M \odot N} \in F(c_1 +_b c_2)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$\psi j_{c_1} i_1$} (B)
-(C) edge node[above]{$\psi j_{c_2} o_2$} (B);
-\end{tikzpicture}
-\]
-where $$d \maps 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{d_1 \times d_2} F(c_1) \times F(c_2) \xrightarrow{\phi_{c_1,c_2}} F(c_1+c_2) \xrightarrow{F(j)}F(c_1 +_b c_2).$$ The image of this horizontal 1-cell is then given by $\H(M \odot N)$:
-where $$d \maps 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{d_1 \times d_2} F(c_1) \times F(c_2) \xrightarrow{\phi_{c_1,c_2}} F(c_1+c_2) \xrightarrow{F(j)}F(c_1 +_b c_2).$$ The image of this horizontal 1-cell is then given by $\lH(M \odot N)$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$H(a_1)$};
-\node (B) at (2,0) {$H(c_1+_b c_2)$};
-\node (C) at (4,0) {$H(a_2)$};
-\node (D) at (2,-0.5) {$\H(M \odot N) = \theta_{c_1 +_b c_2}E(d_{M \odot N}) \phi \in F'(H(c_1 +_b c_2))$};
-\node (D) at (2,-0.5) {$\lH(M \odot N) = \theta_{c_1 +_b c_2}E(d_{M \odot N}) \phi \in F'(H(c_1 +_b c_2))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$H(\psi j_{c_1} i_1)$} (B)
-(C) edge node[above]{$H(\psi j_{c_2} o_2)$} (B);
-\end{tikzpicture}
-\]
-where $$\H(M \odot N) = \theta_{c_1 +_b c_2} E(d_{M \odot N}) \phi \maps 1 \xrightarrow{\phi} E(1) \xrightarrow{E(d)} E(F(c_1 +_b c_2)) \xrightarrow{\theta_{c_1 +_b c_2}} F'(H(c_1 +_b c_2)).$$ On the other hand, the image of each horizontal 1-cell under the double functor $\H$ is given respectively by $\H(M)$ and $\H(N)$:
-where $$\lH(M \odot N) = \theta_{c_1 +_b c_2} E(d_{M \odot N}) \phi \maps 1 \xrightarrow{\phi} E(1) \xrightarrow{E(d)} E(F(c_1 +_b c_2)) \xrightarrow{\theta_{c_1 +_b c_2}} F'(H(c_1 +_b c_2)).$$ On the other hand, the image of each horizontal 1-cell under the double functor $\lH$ is given respectively by $\lH(M)$ and $\lH(N)$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$H(a_1)$};
-\node (B) at (1,0) {$H(c_1)$};
-\node (C) at (2,0) {$H(b)$};
-\node (D) at (1,-0.5) {$\theta_{c_1} E(d_M)\phi \in F'(H(c_1))$};
-\node (E) at (3,0) {$H(b)$};
-\node (F) at (4,0) {$H(c_2)$};
-\node (G) at (5,0) {$H(a_2)$};
-\node (H) at (4,-0.5) {$\theta_{c_2} E(d_N) \phi \in F'(H(c_2))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$H(i_1)$} (B)
-(C) edge node[above]{$H(o_1)$} (B)
-(E) edge node[above]{$H(i_2)$} (F)
-(G) edge node[above]{$H(o_2)$} (F);
-\end{tikzpicture}
-\]
-Composing these then gives $\H(M) \odot \H(N)$:
-Composing these then gives $\lH(M) \odot \lH(N)$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$H(a_1)$};
-\node (B) at (2.25,0) {$H(c_1)+_{H(b)} H(c_2)$};
-\node (C) at (4.5,0) {$H(a_2)$};
-\node (D) at (2.25,-0.5) {$d_{\H(M) \odot \H(N)} \in F'(H(c_1) +_{H(b)} H(c_2))$};
-\node (D) at (2.25,-0.5) {$d_{\lH(M) \odot \lH(N)} \in F'(H(c_1) +_{H(b)} H(c_2))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$\Psi j_{H(c_1)} H(i_1)$} (B)
-(C) edge node[above]{$\Psi j_{H(c_2)} H(o_2)$} (B);
-\end{tikzpicture}
-\]
-where $$\hspace{-.4in}\scriptstyle{d_{\H(M) \odot \H(N)} \maps 1 \xrightarrow{(\theta_{c_1} \times \theta_{c_2})(E(d_M) \times E(d_N)) \phi} F'(H(c_1)) \times F'(H(c_2)) \xrightarrow{\Phi_{H(c_1),H(c_2)}} F'(H(c_1)+ H(c_2)) \xrightarrow{F' (J)} F'(H(c_1) +_{H(b)} H(c_2)).}$$
-We then have a comparison constraint: $$\H_{M,N} \maps \H(M) \odot \H(N) \xrightarrow{\sim} \H(M \odot N)$$given by the globular 2-isomorphism:
-where $$\hspace{-.4in}\scriptstyle{d_{\lH(M) \odot \lH(N)} \maps 1 \xrightarrow{(\theta_{c_1} \times \theta_{c_2})(E(d_M) \times E(d_N)) \phi} F'(H(c_1)) \times F'(H(c_2)) \xrightarrow{\Phi_{H(c_1),H(c_2)}} F'(H(c_1)+ H(c_2)) \xrightarrow{F' (J)} F'(H(c_1) +_{H(b)} H(c_2)).}$$
-We then have a comparison constraint: $$\lH_{M,N} \maps \lH(M) \odot \lH(N) \xrightarrow{\sim} \lH(M \odot N)$$given by the globular 2-isomorphism:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$H(a_1)$};
-\node (A') at (0,-0.5) {$H(a_1)$};
-\node (B) at (2.5,0.5) {$H(c_1)+_{H(b)} H(c_2)$};
-\node (C) at (5,0.5) {$H(a_2)$};
-\node (C') at (5,-0.5) {$H(a_2)$};
-\node (D) at (2.5,-0.5) {$H(c_1 +_b c_2)$};
-\node (E) at (7.5,0.5) {$d_{\H(M) \odot \H(N)} \in F'(H(c_1)+_{H(b_1)}H(c_2))$};
-\node (F) at (7.5,-0.5) {$d_{\H(M \odot N)} \in F'(H(c_1 +_b c_2))$};
-\node (G) at (2.5,-1) {$\tau_{\kappa^{-1}} \maps F'(\kappa^{-1})(d_{\H(M) \odot \H(N)}) \to d_{\H(M \odot N)}.$};
-\node (E) at (7.5,0.5) {$d_{\lH(M) \odot \lH(N)} \in F'(H(c_1)+_{H(b_1)}H(c_2))$};
-\node (F) at (7.5,-0.5) {$d_{\lH(M \odot N)} \in F'(H(c_1 +_b c_2))$};
-\node (G) at (2.5,-1) {$\tau_{\kappa^{-1}} \maps F'(\kappa^{-1})(d_{\lH(M) \odot \lH(N)}) \to d_{\lH(M \odot N)}.$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$\Psi j_{H(c_1)} H(i_1)$} (B)
-(C) edge node[above]{$\Psi j_{H(c_2)} H(o_2)$} (B)
-(A) edge node[left]{$1$} (A')
-(C) edge node[right]{$1$} (C')
-(A') edge node [above]{$H(\psi j_{c_1} i_1)$} (D)
-(C') edge node [above]{$H(\psi j_{c_2} o_2)$} (D)
-(B) edge node [left] {$\kappa^{-1}$} (D);
-\end{tikzpicture}
-\]
-where $\kappa$ is the isomorphism $$\kappa \maps H(c_1 +_b c_2) \xrightarrow{\sim} H(c_1) +_{H(b)} H(c_2)$$ which comes from the finite colimit preserving functor $H \maps \A \to \mathsf{A'}$.
-The above diagram commutes by a similar argument to the one used in \cref{thm:equiv}.
-Similarly, for every object $c \in \A$, we have a unit comparison constraint \\[ \H_U \maps U_{\H(c)} \to \H(U_c)\]
-given by the globular 2-isomorphism:
-where $\kappa$ is the isomorphism 
-\[  \kappa \maps H(c_1 +_b c_2) \xrightarrow{\sim} H(c_1) +_{H(b)} H(c_2)\] 
-which comes from the finite colimit preserving functor $H \maps \A \to \A'$.
-The above diagram commutes by a similar argument to the one used in \cref{thm:equiv}.
-Similarly, for every object $c \in \A$, we have a unit comparison constraint
-\[ \lH_U \maps U_{\lH(c)} \to \lH(U_c)\] 
-given by the globular 2-isomorphism:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$H(c)$};
-\node (A') at (0,-0.5) {$H(c)$};
-\node (B) at (1.5,0.5) {$H(c)$};
-\node (C) at (3,0.5) {$H(c)$};
-\node (C') at (3,-0.5) {$H(c)$};
-\node (D) at (1.5,-0.5) {$H(c)$};
-\node (E) at (4.5,0.5) {$!_{H(c)} \in F'(H(c))$};
-\node (F) at (4.5,-0.5) {$\theta_c E(!_c) \phi \in F'(H(c))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$1$} (B)
-(C) edge node[above]{$1$} (B)
-(A) edge node[left]{$1$} (A')
-(C) edge node[right]{$1$} (C')
-(A') edge node [above]{$1$} (D)
-(C') edge node [above]{$1$} (D)
-(B) edge node [left] {$1$} (D);
-\end{tikzpicture}
-\]
-where the morphism of decorations is the morphism $\tau \maps !_{H(c)} \to (\theta_c E(!_c) \phi)$ in $F'(H(c))$.
-These comparison constrains satisfy the coherence axioms of a monoidal category, namely:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$(\H(M) \odot \H(N)) \odot \H(P)$};
-\node (B) at (0,-0.5) {$\H(M \odot N) \odot \H(P)$};
-\node (C) at (0,-1.5) {$\H((M \odot N) \odot P)$};
-\node (A') at (3,0.5) {$\H(M) \odot (\H(N) \odot \H(P))$};
-\node (B') at (3,-0.5) {$\H(M) \odot \H(N \odot P)$};
-\node (C') at (3,-1.5) {$\H(M \odot (N \odot P))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[left]{$\H_{M,N} \odot 1$} (B)
-(B) edge node[left]{$\H_{M \odot N,P}$} (C)
-\node (A) at (0,0.5) {$(\lH(M) \odot \lH(N)) \odot \lH(P)$};
-\node (B) at (0,-0.5) {$\lH(M \odot N) \odot \lH(P)$};
-\node (C) at (0,-1.5) {$\lH((M \odot N) \odot P)$};
-\node (A') at (3,0.5) {$\lH(M) \odot (\lH(N) \odot \lH(P))$};
-\node (B') at (3,-0.5) {$\lH(M) \odot \lH(N \odot P)$};
-\node (C') at (3,-1.5) {$\lH(M \odot (N \odot P))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[left]{$\lH_{M,N} \odot 1$} (B)
-(B) edge node[left]{$\lH_{M \odot N,P}$} (C)
-(A) edge node[above]{$a$} (A')
-(C) edge node [above] {$\H(a')$} (C')
-(B') edge node [right] {$\H_{M,N \odot P}$} (C')
-(A') edge node [right]{$1 \odot \H_{N,P}$} (B');
-(C) edge node [above] {$\lH(a')$} (C')
-(B') edge node [right] {$\lH_{M,N \odot P}$} (C')
-(A') edge node [right]{$1 \odot \lH_{N,P}$} (B');
-\end{tikzpicture}
-\]
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$U_{\H(a)} \odot \H(M)$};
-\node (B) at (2.5,0) {$\H(U_a) \odot \H(M)$};
-\node (C) at (0,-1) {$\H(M)$};
-\node (D) at (2.5,-1) {$\H(U_a \odot M)$};
-\node (A') at (5,0) {$\H(M) \odot U_{\H(b)}$};
-\node (B') at (7.5,0) {$\H(M) \odot \H(U_b)$};
-\node (C') at (5,-1) {$\H(M)$};
-\node (D') at (7.5,-1) {$\H(M \odot U_b)$};
-\node (A) at (0,0) {$U_{\lH(a)} \odot \lH(M)$};
-\node (B) at (2.5,0) {$\lH(U_a) \odot \lH(M)$};
-\node (C) at (0,-1) {$\lH(M)$};
-\node (D) at (2.5,-1) {$\lH(U_a \odot M)$};
-\node (A') at (5,0) {$\lH(M) \odot U_{\lH(b)}$};
-\node (B') at (7.5,0) {$\lH(M) \odot \lH(U_b)$};
-\node (C') at (5,-1) {$\lH(M)$};
-\node (D') at (7.5,-1) {$\lH(M \odot U_b)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$\H_U \odot 1$} (B)
-(A) edge node[above]{$\lH_U \odot 1$} (B)
-(A) edge node[left]{$\lambda$} (C)
-(B) edge node[right]{$\H_{U_a,M}$} (D)
-(D) edge node[above]{$\H(\lambda')$} (C)
-(A') edge node[above]{$1 \odot \H_U$} (B')
-(B) edge node[right]{$\lH_{U_a,M}$} (D)
-(D) edge node[above]{$\lH(\lambda')$} (C)
-(A') edge node[above]{$1 \odot \lH_U$} (B')
-(A') edge node[left]{$\rho$} (C')
-(B') edge node[right]{$\H_{M,U_b}$} (D')
-(D') edge node[above]{$\H(\rho')$} (C');
-(B') edge node[right]{$\lH_{M,U_b}$} (D')
-(D') edge node[above]{$\lH(\rho')$} (C');
-\end{tikzpicture}
-\]
-The diagrams involving the morphisms of decorations are similar to those in Theorem \cref{DC}.
-This shows that $\H=(H,E,\theta)$ is a double functor.
-Next we show that this double functor is symmetric monoidal.
-First, that the object component $\H_0=H$ is symmetric monoidal is clear as $H \maps \A \to \A'$ preserves finite colimits.
-As for the arrow component $\H_1$, given two horizontal 1-cells $M_1$ and $M_2$ in $F\lCsp$:
-The diagrams involving the morphisms of decorations are similar to those in Theorem \cref{DC}.
-This shows that $\lH=(H,E,\theta)$ is a double functor.
-Next we show that this double functor is symmetric monoidal.
-First, that the object component $\lH_0=H$ is symmetric monoidal is clear as $H \maps \A \to \A'$ preserves finite colimits.
-As for the arrow component $\lH_1$, given two horizontal 1-cells $M_1$ and $M_2$ in $F\lCsp$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a_1$};
-\node (B) at (1,0) {$c_1$};
-\node (C) at (2,0) {$b_1$};
-\node (D) at (1,-0.5) {$d_{M_1}\in F(c_1)$};
-\node (E) at (3,0) {$a_2$};
-\node (F) at (4,0) {$c_2$};
-\node (G) at (5,0) {$b_2$};
-\node (H) at (4,-0.5) {$d_{M_2} \in F(c_2)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i_1$} (B)
-(C) edge node[above]{$o_1$} (B)
-(E) edge node[above]{$i_2$} (F)
-(G) edge node[above]{$o_2$} (F);
-\end{tikzpicture}
-\]
-their tensor product $M_1 \otimes M_2$ in $F\lCsp$ is given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a_1+a_2$};
-\node (B) at (1.5,0) {$c_1+c_2$};
-\node (C) at (3,0) {$b_1+b_2$};
-\node (D) at (1.5,-0.5) {$d_{M_1 \otimes M_2} \in F(c_1+c_2)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i_1+i_2$} (B)
-(C) edge node[above]{$o_1+o_2$} (B);
-\end{tikzpicture}
-\]
-$$d_{M_1 \otimes M_2} \maps 1 \xrightarrow{d_1 \times d_2} F(c_1) \times F(c_2) \xrightarrow{\phi_{c_1,c_2}} F(c_1+c_2)$$
-and the image of this horizontal 1-cell under the double functor $\H$ is $\H(M_1 \otimes M_2)$ given by:
-and the image of this horizontal 1-cell under the double functor $\lH$ is $\lH(M_1 \otimes M_2)$ given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$H(a_1+a_2)$};
-\node (B) at (2,0) {$H(c_1+c_2)$};
-\node (C) at (4,0) {$H(b_1+b_2)$};
-\node (D) at (2,-0.5) {$d_{\H(M_1 \otimes M_2)} = \theta_{c_1+c_2} E(d_{M_1 \otimes M_2})\phi \in F'(H(c_1+c_2))$};
-\node (D) at (2,-0.5) {$d_{\lH(M_1 \otimes M_2)} = \theta_{c_1+c_2} E(d_{M_1 \otimes M_2})\phi \in F'(H(c_1+c_2))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$H(i_1+i_2)$} (B)
-(C) edge node[above]{$H(o_1+o_2)$} (B);
-\end{tikzpicture}
-\]
-On the other hand, the image of $M_1$ and $M_2$ is given by $\H(M_1)$ and $\H(M_2)$:
-On the other hand, the image of $M_1$ and $M_2$ is given by $\lH(M_1)$ and $\lH(M_2)$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$H(a_1)$};
-\node (B) at (1.5,0) {$H(c_1)$};
-\node (C) at (3,0) {$H(b_1)$};
-\node (D) at (1.5,-0.5) {$d_{\H(M_1)} = \theta_{c_1}E(d_{M_1})\phi \in F'(H(c_1))$};
-\node (D) at (1.5,-0.5) {$d_{\lH(M_1)} = \theta_{c_1}E(d_{M_1})\phi \in F'(H(c_1))$};
-\node (E) at (4.5,0) {$H(a_2)$};
-\node (F) at (6,0) {$H(c_2)$};
-\node (G) at (7.5,0) {$H(b_2)$};
-\node (H) at (6,-0.5) {$d_{\H(M_2)} = \theta_{c_2}E(d_{M_2})\phi \in F'(H(c_2))$};
-\node (H) at (6,-0.5) {$d_{\lH(M_2)} = \theta_{c_2}E(d_{M_2})\phi \in F'(H(c_2))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$H(i_1)$} (B)
-(C) edge node[above]{$H(o_1)$} (B)
-(E) edge node[above]{$H(i_2)$} (F)
-(G) edge node[above]{$H(o_2)$} (F);
-\end{tikzpicture}
-\]
-and their tensor product $\H(M_1) \otimes \H(M_2)$ is given by:
-and their tensor product $\lH(M_1) \otimes \lH(M_2)$ is given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$H(a_1)+H(a_2)$};
-\node (B) at (2.5,0) {$H(c_1)+H(c_2)$};
-\node (C) at (5,0) {$H(b_1)+H(b_2)$};
-\node (D) at (2.5,-0.5) {$d_{\H(M_1) \otimes \H(M_2)} \in F'(H(c_1)+H(c_2))$};
-\node (D) at (2.5,-0.5) {$d_{\lH(M_1) \otimes \lH(M_2)} \in F'(H(c_1)+H(c_2))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$H(i_1)+H(i_2)$} (B)
-(C) edge node[above]{$H(o_1)+H(o_2)$} (B);
-\end{tikzpicture}
-\]
-$$\hspace{-.4in} \scriptstyle{d_{\H(M_1) \otimes \H(M_2)} \maps 1 \xrightarrow{(\phi \times \phi)(\lambda^{-1} \times \lambda^{-1})} E(1) \times E(1) \xrightarrow{(\theta_{c_1} \times \theta_{c_2})(E(d_{M_1}) \times E(d_{M_2}))} F'(H(c_1)) \times F'(H(c_2)) \xrightarrow{\Phi_{H(c_1),H(c_2)}} F' (H(c_1)+H(c_2)).}$$  We then have a natural 2-isomorphism $\mu_{M_1,M_2} \maps \H(M_1) \otimes \H(M_2) \to \H(M_1 \otimes M_2)$ in $F'\lCsp$ given by:
-$$\hspace{-.4in} \scriptstyle{d_{\lH(M_1) \otimes \lH(M_2)} \maps 1 \xrightarrow{(\phi \times \phi)(\lambda^{-1} \times \lambda^{-1})} E(1) \times E(1) \xrightarrow{(\theta_{c_1} \times \theta_{c_2})(E(d_{M_1}) \times E(d_{M_2}))} F'(H(c_1)) \times F'(H(c_2)) \xrightarrow{\Phi_{H(c_1),H(c_2)}} F' (H(c_1)+H(c_2)).}$$  We then have a natural 2-isomorphism $\mu_{M_1,M_2} \maps \lH(M_1) \otimes \lH(M_2) \to \lH(M_1 \otimes M_2)$ in $F'\lCsp$ given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$H(a_1)+H(a_2)$};
-\node (A') at (0,-0.5) {$H(a_1+a_2)$};
-\node (B) at (2.5,0.5) {$H(c_1)+H(c_2)$};
-\node (C) at (5,0.5) {$H(b_1)+H(b_2)$};
-\node (C') at (5,-0.5) {$H(b_1+b_2)$};
-\node (D) at (2.5,-0.5) {$H(c_1+c_2)$};
-\node (E) at (2.5,1) {$d_{\H(M_1) \otimes \H(M_2)} \in F'(H(c_1)+H(c_2))$};
-\node (F) at (2.5,-1) {$d_{\H(M_1 \otimes M_2)} \in F'(H(c_1+c_2))$};
-\node (E) at (2.5,1) {$d_{\lH(M_1) \otimes \lH(M_2)} \in F'(H(c_1)+H(c_2))$};
-\node (F) at (2.5,-1) {$d_{\lH(M_1 \otimes M_2)} \in F'(H(c_1+c_2))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$H(i_1)+H(i_2)$} (B)
-(C) edge node[above]{$H(o_1)+H(o_2)$} (B)
-(A) edge node[left]{$\kappa$} (A')
-(C) edge node[left]{$\kappa$} (C')
-(A') edge node [above]{$H(i_1+i_2)$} (D)
-(C') edge node [above]{$H(o_1+o_2)$} (D)
-(B) edge node [left] {$\kappa$} (D);
-\end{tikzpicture}
-\]
-$$\tau_\kappa \maps F'(\kappa)(d_{\H(M_1) \otimes \H(M_2)}) \to d_{\H(M_1 \otimes M_2)}$$
-$$\tau_\kappa \maps F'(\kappa)(d_{\lH(M_1) \otimes \lH(M_2)}) \to d_{\lH(M_1 \otimes M_2)}$$
-where $\kappa$ denotes the isomorphism arising from $H$ preserving finite colimits.
-This natural 2-isomorphism together with the associators of $F\lCsp$ and $F'\lCsp$, respectively $\alpha$ and $\alpha'$, make the following diagram commute:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$(\H(M_1) \otimes \H(M_2)) \otimes \H(M_3)$};
-\node (B) at (0,-0.5) {$\H(M_1 \otimes M_2) \otimes \H(M_3)$};
-\node (C) at (0,-1.5) {$\H((M_1 \otimes M_2) \otimes M_3)$};
-\node (A') at (4,0.5) {$\H(M_1) \otimes (\H(M_2) \otimes \H(M_3))$};
-\node (B') at (4,-0.5) {$\H(M_1) \otimes \H(M_2 \otimes M_3)$};
-\node (C') at (4,-1.5) {$\H(M_1 \otimes (M_2 \otimes M_3))$};
-\node (A) at (0,0.5) {$(\lH(M_1) \otimes \lH(M_2)) \otimes \lH(M_3)$};
-\node (B) at (0,-0.5) {$\lH(M_1 \otimes M_2) \otimes \lH(M_3)$};
-\node (C) at (0,-1.5) {$\lH((M_1 \otimes M_2) \otimes M_3)$};
-\node (A') at (4,0.5) {$\lH(M_1) \otimes (\lH(M_2) \otimes \lH(M_3))$};
-\node (B') at (4,-0.5) {$\lH(M_1) \otimes \lH(M_2 \otimes M_3)$};
-\node (C') at (4,-1.5) {$\lH(M_1 \otimes (M_2 \otimes M_3))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[left]{$\mu_{M_1,M_2} \otimes 1$} (B)
-(B) edge node[left]{$\mu_{M_1 \otimes M_2,M_3}$} (C)
-(A) edge node[above]{$\alpha'$} (A')
-(C) edge node [above] {$\H(\alpha)$} (C')
-(C) edge node [above] {$\lH(\alpha)$} (C')
-(B') edge node [right] {$\mu_{M_1,M_2 \otimes M_3}$} (C')
-(A') edge node [right]{$1 \otimes \mu_{M_2 \otimes M_3}$} (B');
-\end{tikzpicture}
-\]
-with the corresponding diagram of decorations in $F'(H(c_1+(c_2+c_3)))$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$F'(\alpha \kappa \kappa)(d_{(\H(M_1) \otimes \H(M_2)) \otimes \H(M_3)})$};
-\node (B) at (0,-0.5) {$F'(\alpha \kappa)(d_{\H(M_1 \otimes M_2) \otimes \H(M_3)})$};
-\node (C) at (0,-1.5) {$F'(\alpha)(d_{\H((M_1 \otimes M_2) \otimes M_3)})$};
-\node (A') at (5,0.5) {$F'(\kappa \kappa)(d_{\H(M_1) \otimes (\H(M_2) \otimes \H(M_3))})$};
-\node (B') at (5,-0.5) {$F'(\kappa)(d_{\H(M_1) \otimes \H(M_2 \otimes M_3)})$};
-\node (C') at (5,-1.5) {$d_{\H(M_1 \otimes (M_2 \otimes M_3))}$};
-\node (A) at (0,0.5) {$F'(\alpha \kappa \kappa)(d_{(\lH(M_1) \otimes \lH(M_2)) \otimes \lH(M_3)})$};
-\node (B) at (0,-0.5) {$F'(\alpha \kappa)(d_{\lH(M_1 \otimes M_2) \otimes \lH(M_3)})$};
-\node (C) at (0,-1.5) {$F'(\alpha)(d_{\lH((M_1 \otimes M_2) \otimes M_3)})$};
-\node (A') at (5,0.5) {$F'(\kappa \kappa)(d_{\lH(M_1) \otimes (\lH(M_2) \otimes \lH(M_3))})$};
-\node (B') at (5,-0.5) {$F'(\kappa)(d_{\lH(M_1) \otimes \lH(M_2 \otimes M_3)})$};
-\node (C') at (5,-1.5) {$d_{\lH(M_1 \otimes (M_2 \otimes M_3))}$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[left]{$F'(\alpha \kappa)(\tau_\kappa + 1)$} (B)
-(B) edge node[left]{$F'(\alpha)(\tau_\kappa)$} (C)
-(A) edge node[above]{$F'(\kappa \kappa)(\tau_{\alpha'})$} (A')
-(C) edge node [above] {$\tau_\alpha$} (C')
-(B') edge node [right] {$\tau_\kappa$} (C')
-(A') edge node [right]{$F'(\kappa)(1+\tau_\kappa)$} (B');
-\end{tikzpicture}
-\]
-where $$F'(\alpha \kappa \kappa)(d_{(\H(M_1) \otimes \H(M_2)) \otimes \H(M_3)}) = F'(\kappa \kappa \alpha')(d_{(\H(M_1) \otimes \H(M_2)) \otimes \H(M_3)})$$
-as the corresponding hexagon for the finite colimit preserving functor $H \maps \A \to \mathsf{A'}$ commutes.
-The map $\mu_{M_1,M_2}$ is also compatible with the braidings $\beta$ and $\beta'$ of $F \lCsp_1$ and $F' \lCsp_1$, respectively, and make the necessary square commute as a consequence of the corresponding commutative square involving braidings from the finite colimit preserving functor $H \maps \A \to \mathsf{A'}$.
-where $$F'(\alpha \kappa \kappa)(d_{(\lH(M_1) \otimes \lH(M_2)) \otimes \lH(M_3)}) = F'(\kappa \kappa \alpha')(d_{(\lH(M_1) \otimes \lH(M_2)) \otimes \lH(M_3)})$$
-as the corresponding hexagon for the finite colimit preserving functor $H \maps \A \to \A'$ commutes.
-The map $\mu_{M_1,M_2}$ is also compatible with the braidings $\beta$ and $\beta'$ of $F \lCsp_1$ and $F' \lCsp_1$, respectively, and make the necessary square commute as a consequence of the corresponding commutative square involving braidings from the finite colimit preserving functor $H \maps \A \to \A'$.
-
-We also have that the monoidal unit of $F\lCsp_1$ is given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$1_\A$};
-\node (B) at (1,0) {$1_\A$};
-\node (C) at (2,0) {$1_\A$};
-\node (D) at (1,-0.5) {$!_{1_\A} \in F(1_\A)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$1$} (B)
-(C) edge node[above]{$1$} (B);
-\end{tikzpicture}
-\]
-where $1_\A$ is the monoidal unit of the cocartesian category $\A$. The image of this horizontal 1-cell under $\H$ is given by:
-where $1_\A$ is the monoidal unit of the cocartesian category $\A$. The image of this horizontal 1-cell under $\lH$ is given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$H(1_\A)$};
-\node (B) at (1,0) {$H(1_\A)$};
-\node (C) at (2,0) {$H(1_\A)$};
-%\node (E) at (3,0) {$=$};
-%\node (F) at (4,0) {$1_\mathsf{A'}$};
-%\node (G) at (5,0) {$1_\mathsf{A'}$};
-%\node (H) at (6,0) {$1_\mathsf{A'}$};
-%\node (I) at (5,-0.5) {$!_{1_{\mathsf{A'}}} \in F'(1_{\mathsf{A'}})$};
-%\node (F) at (4,0) {$1_\A'$};
-%\node (G) at (5,0) {$1_\A'$};
-%\node (H) at (6,0) {$1_\A'$};
-%\node (I) at (5,-0.5) {$!_{1_{\A'}} \in F'(1_{\A'})$};
-\node (D) at (1,-0.5) {$\theta_{1_\A}E(!_{1_\A}) \phi \in F'(H(1_\A))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$1$} (B)
-(C) edge node[above]{$1$} (B);
-%(F) edge node[above]{$1$} (G)
-%(H) edge node[above]{$1$} (G);
-\end{tikzpicture}
-\]
-as $H$ preserves finite colimits. We then have a 2-isomorphism in $F'\lCsp$ given by: $$\mu \maps 1_{F'\lCsp_1} \to \H(1_{F\lCsp_1})$$ 
-as $H$ preserves finite colimits. We then have a 2-isomorphism in $F'\lCsp$ given by: $$\mu \maps 1_{F'\lCsp_1} \to \lH(1_{F\lCsp_1})$$ 
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$1_{\mathsf{A'}}$};
-\node (A) at (0,0.5) {$1_{\A'}$};
-\node (A') at (0,-0.5) {$H(1_\A)$};
-\node (B) at (1.5,0.5) {$1_{\mathsf{A'}}$};
-\node (C) at (3,0.5) {$1_{\mathsf{A'}}$};
-\node (B) at (1.5,0.5) {$1_{\A'}$};
-\node (C) at (3,0.5) {$1_{\A'}$};
-\node (C') at (3,-0.5) {$H(1_\A)$};
-\node (D) at (1.5,-0.5) {$H(1_\A)$};
-\node (E) at (5,0.5) {$!_{1_\mathsf{A'}} \in F'(1_\mathsf{A'})$};
-\node (E) at (5,0.5) {$!_{1_\A'} \in F'(1_\A')$};
-\node (F) at (5,-0.5) {$\theta_{1_\A} E(!_{1_\A}) \phi \in F'(H(1_\A))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$1$} (B)
-(C) edge node[above]{$1$} (B)
-(A) edge node[left]{$\kappa$} (A')
-(C) edge node[right]{$\kappa$} (C')
-(A') edge node [above]{$1$} (D)
-(C') edge node [above]{$1$} (D)
-(B) edge node [left] {$\kappa$} (D);
-\end{tikzpicture}
-\]
-together with the morphism $\tau_\mu \maps F'(\kappa)(!_{1_\mathsf{A'}}) \to (\theta_{1_\A} E(!_{1_\A})\phi)$ in $F'(H(1_\A))$.
-The following square then commutes for any horizontal 1-cell $M$ of $F \lCsp$:
-together with the morphism $\tau_\mu \maps F'(\kappa)(!_{1_\A'}) \to (\theta_{1_\A} E(!_{1_\A})\phi)$ in $F'(H(1_\A))$. The following square then commutes for any horizontal 1-cell $M$ of $F \lCsp$: 
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$1_\mathsf{A'} \otimes \H(M)$};
-\node (B) at (2.5,0) {$\H(1_\A) \otimes \H(M)$};
-\node (C) at (0,-1) {$\H(M)$};
-\node (D) at (2.5,-1) {$\H(1_\A \otimes M)$};
-\node (A) at (0,0) {$1_\A' \otimes \lH(M)$};
-\node (B) at (2.5,0) {$\lH(1_\A) \otimes \lH(M)$};
-\node (C) at (0,-1) {$\lH(M)$};
-\node (D) at (2.5,-1) {$\lH(1_\A \otimes M)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$\mu \otimes 1$} (B)
-(A) edge node[left]{$\ell$} (C)
-(B) edge node[right]{$\mu_{1_\mathrm{A},M}$} (D)
-(D) edge node[above]{$\H(\ell')$} (C);
-(D) edge node[above]{$\lH(\ell')$} (C);
-\end{tikzpicture}
-\]
-where we have abbreviated the monoidal units of $F\lCsp_1$ and $F'\lCsp_1$ as $1_\A$ and $1_\mathsf{A'}$, respectively. The diagram of corresponding decorations is given by:
-where we have abbreviated the monoidal units of $F\lCsp_1$ and $F'\lCsp_1$ as $1_\A$ and $1_\A'$, respectively. The diagram of corresponding decorations is given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$F'(\ell)(d_{!_{1_\mathsf{A'}}} \otimes d_{\H(M)})$};
-\node (B) at (0,-0.5) {$d_{\H(M)}$};
-\node (A') at (4,0.5) {$F'(H(\ell') \kappa)(d_{!_{\H(1_\A)}}\otimes d_{\H(M)})$};
-\node (B') at (4,-0.5) {$F'(H(\ell'))(d_{\H(1_\A \otimes M)})$};
-\node (A) at (0,0.5) {$F'(\ell)(d_{!_{1_\A'}} \otimes d_{\lH(M)})$};
-\node (B) at (0,-0.5) {$d_{\lH(M)}$};
-\node (A') at (4,0.5) {$F'(H(\ell') \kappa)(d_{!_{\lH(1_\A)}}\otimes d_{\lH(M)})$};
-\node (B') at (4,-0.5) {$F'(H(\ell'))(d_{\lH(1_\A \otimes M)})$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[left]{$\tau_\ell$} (B)
-(A) edge node[above]{$F'(H(\ell')\kappa)(\tau_{\mu \otimes 1})$} (A')
-(A') edge node [right]{$F'(H(\ell'))(\tau_\kappa)$} (B')
-(B') edge node [above] {$\tau_{H(\ell')}$} (B);
-\end{tikzpicture}
-\]
-where $$F'(\ell)(d_{!_{1_\mathsf{A'}}} \otimes d_{\H(M)})=F'(H(\ell')\kappa(\mu \otimes 1))(d_{!_{1_\mathsf{A'}}} \otimes d_{\H(M)})$$ since the corresponding square involving left unitors for the finite colimit preserving functor $H \maps \A \to \mathsf{A'}$ commutes.
-The other square involving the right unitors $r$ and $r'$ is similar.
-Note that because the comparison constraints $\mu$ and $\mu_{(\_ , \_)}$ are both isomorphisms, the symmetric monoidal double functor $\H$ is strong.
-where $$F'(\ell)(d_{!_{1_\A'}} \otimes d_{\lH(M)})=F'(H(\ell')\kappa(\mu \otimes 1))(d_{!_{1_\A'}} \otimes d_{\lH(M)})$$ since the corresponding square involving left unitors for the finite colimit preserving functor $H \maps \A \to \A'$ commutes.
-The other square involving the right unitors $r$ and $r'$ is similar.
-Note that because the comparison constraints $\mu$ and $\mu_{(\_ , \_)}$ are both isomorphisms, the symmetric monoidal double functor $\lH$ is strong.
-
-\end{comment}
 
@@
 \label{thm:functoriality}
-Given two categories $\A$ and $\A'$ with finite colimits, two symmetric lax monoidal pseudofunctors $F \maps \A \to \Cat$ and $F' \maps \A' \to \Cat$, a finite colimit preserving functor $H \maps \A \to \A'$, a symmetric lax monoidal pseudofunctor $E \maps \Cat \to \Cat$ and a 2-isomorphism $\theta \maps EF \Rightarrow F' H$ as in the following diagram,
+Given two categories $\A$ and $\A'$ with finite colimits, two symmetric lax monoidal pseudofunctors $F \maps \A \to \Cat$ and $F' \maps \A' \to \Cat$, a finite colimit preserving functor $H \maps \A \to \A'$, a symmetric lax monoidal pseudofunctor $E \maps \Cat \to \Cat$ and a natural isomorphism $\theta \maps EF \Rightarrow F' H$ as in the following diagram:
 \[
@@
 
-%\newpage
-%Scratch work for Petri net problem
-%\newline
-%Let $P = (s_1,t_1 \maps T_1 \to \N(S_1))$ and $Q = (s_2,t_2 \maps T_2 \to \N(S_2))$.
-We want to show that the functor $F \maps \textrm{Petri} \to \textrm{CMC}$ preserves pushouts of cospans of the form $$P \xleftarrow{} L(Y) \xrightarrow{} Q$$ meaning that $F(P+_{L(Y)} Q) \cong F(P) +_{F(L(Y))} F(Q)$.
-Here, $L \maps \textrm{Set} \to \textrm{Petri}$ is the left adjoint which sends a set $Y$ to the discrete Petri net with $Y$ as its set of species and no transitions.
-Thus no transitions are identified in the pushout $P+_{L(Y)} Q$, and so the set of transitions of $P+_{L(Y)} Q$ is given by $$\textrm{Trans}(P)+\textrm{Trans}(Q).$$ Thus the morphisms \emph{contributed from transitions} in both $F(P+_{L(Y)}Q)$ and $F(P)+_{F(L(Y)} F(Q)$ are the same.
-If we can show that $$\textrm{Ob}(F(P+_{L(Y)}Q) \cong \textrm{Ob}(F(P)+_{F(L(Y))} F(Q)$$ then the remaining morphisms in each commutative monoidal category will be canonically isomorphic as sets.
-
-%Now, what can we say about $\textrm{Ob}(F(P+_{L(Y)}Q))$ vs.
-$\textrm{Ob}(F(P)+_{F(L(Y))} F(Q))$?
-Well, $\textrm{Ob}(F(P+_{L(Y)}Q)) = \N(S_1+_Y S_2)$ and $\textrm{Ob}(F(P)+_{F(L(Y))} F(Q))= \N(S_1) +_{\N(Y)} \N(S_2)$.
-
-%\newpage
-
-%is given by $$1 \to F(c_1) \times F(c_2) \xrightarrow{} F(c_1 + c_2) \xrightarrow{} F(c_1 + _b c_2)$$ and then applying the functor $E$ results in $1 \to E(F(c_1+_b c_2))$, which by the comutative square is the same as $1 \to F'(H(c_1+_b c_2))$.
-On the other hand, applying the functor $E$ to each decoration results in $$1 \to E(F(c_1)) \times E(F(c_2)) \xrightarrow{} E(F(c_1) \times F(c_2)) \xrightarrow{} E(F(c_1+c_2)) \xrightarrow E(F(c_1+_b c_2)) \xrightarrow{} F'(H(c_1 +_b c_2))$$
+This theorem should generalize to the case when $\theta$ is a pseudonatural
+isomorphism, but the weaker version suffices for our application in \cref{subsec:petrirates}.
 
@@
  \item the total category $\X$ has $\J$-colimits, and $U$ preserves them.
-Moreover in this situation the $\J$-colimits in $\X$ can be chosen so that $U$ strictly preserves them.  
 \end{enumerate}
+Given these conditions, for any choice of $\J$-colimits in $\A$ the $\J$-colimits in $\X$ can be chosen so that $U$ strictly preserves them.
 \end{lem}
@@
 \end{equation}
-which on the first variable is given by the pushout in $\A$ on the left below, and the object $w$ is formed as the pushout in the fiber $F(a+_bc)$ on the right below:
+where $a+_b c$ is defined using the pushout in $\A$ shown at left below, and $w$ is formed as the pushout in the fiber $F(a+_bc)$ at the right below:
 \begin{displaymath}
@@
  F(u_a)x\ar[ur] & & F(u_c)z\ar[ul] \\
- & F(u_a)(Ff(y))\cong F(u_c)(Fg(y))\ar[ul,"F(u_a)k"]\ar[ur,"F(u_c)\ell"'] &
+ & F(u_a)(F(f)(y))\cong F(u_c)(F(g)(y))\ar[ul,"F(u_a)k"]\ar[ur,"F(u_c)\ell"'] &
  \end{tikzcd}
 \end{displaymath}
-In a similar way we can construct the initial object and coproducts in a Grothendieck category from those in the fibers, namely
+In a similar way we can construct the initial object and coproducts in $\int F$ from those in the fibers, namely
 \begin{equation}\label{eq:fibrewisecoprod}
@@
 \end{equation}
-where $\iota_a:a\to a+b\leftarrow b:\iota_b$ are the sum inclusions in $\A$ and the sum on the second variable is in the fiber $F(a+b)$.
-
-In our case of interest, the pseudofunctor $F$ will originally be lax monoidal; combining \cref{lem:MonGroth,lem:fibrewiselimits}, we deduce the following.
+where $\iota_a \maps a\to a+b$ and $\iota_b \maps a \to a+b$ are the sum inclusions in $\A$ and the sum on the second variable is in the fiber $F(a+b)$.
+
+In the case we are interested in, the pseudofunctor $F$ is lax monoidal; combining \cref{lem:MonGroth,lem:fibrewiselimits}, we deduce the following.
 %Christina: I suspect that's why for composition we get isomorphism below - using pushouts in which I cannot use the monoidal structure of the functor - whereas for coproducts and initial object we get equality since they were constructed in a very specific way.
@@
 If the corresponding pseudofunctor $\tilde{F} \maps \A\to\bicat{MonCat}$ given in \cref{lem:MonGroth} factors through $\Rex$, then $\inta F$ has all finite colimits and the induced opfibration $U\maps\inta F\to\A$ preserves them.
-STRICTLY???
-%%%!!!
+Moreover, for any choice of finite colimits in $\A$, finite colimits in $\inta F$ can be chosen so that that $U$ strictly preserves them.
 \end{cor}

### 2020-12-09 cospans.tex
added explanation of open rate equation to 5.4

@@
 We prove that under certain conditions these two constructions become equivalent when we take $\X = \int F$ to be the Grothendieck category of $F$.
-We illustrate these ideas with applications to electrical circuits, Petri nets, chemistry and dynamical systems.
+We illustrate these ideas with applications to electrical circuits, Petri nets, epidemiology and dynamical systems.
 \end{abstract}
@@
 In \cref{spinoffs}, we establish the equivalence between structured and decorated cospans at the level of bicategories and categories (via decategorification).
-Finally, in \cref{Applications}, we describe applications to electrical circuits, Petri nets, chemistry and dynamical systems.
+Finally, in \cref{Applications}, we describe applications to electrical circuits, Petri nets, epidemiology and dynamical systems.
 
@@
 As a left adjoint, this induced $L$ preserves all colimits that exist between the categories $\A$ and $\inta F$, which have finite colimits, so we can construct the double category of structured cospans $_L\lCsp(\inta F)$ of \cref{thm:SC}.
-Its objects and vertical morphisms are those of the category $\A$ (same as for $F\lCsp$), whereas horizontal 1-cells are now cospans of the form $\cspn{L(a)}{(m,x)}{L(b)}{}{}$ in the Grothendieck category $\inta F$ (\cref{def:GrothCat}).
+Its objects and vertical morphisms are those of the category $\A$ (just as for $F\lCsp$), whereas its horizontal 1-cells are now cospans of the form $\cspn{L(a)}{(m,x)}{L(b)}{}{}$ in the Grothendieck category $\inta F$ (see \cref{def:GrothCat}).
 Explicitly, they consist of two pairs of morphisms
@@
 with $x\in F(m)$; recall that the reindexing functors $F(i),F(o)$ preserve all finite colimits across the fibers.
-Finally, the 2-morphisms of this double category in this context unravel as follows
+Finally, the 2-morphisms of this double category in this context unravel as follows:
 \begin{equation}\label{eq:2morphismLCspintaF}
@@
 Here is the corresponding open dynamical system:
-\[   \begin{array}{ccl} \displaystyle{\frac{dS(t)}{dt}} &=& -r_1 \, S(t)I(t)  + I_1(t) + I_2(t) \\ \\
+\begin{equation}
+\label{eq:openPetrir}
+  \begin{array}{ccl} \displaystyle{\frac{dS(t)}{dt}} &=& -r_1 \, S(t)I(t)  + I_1(t) + I_2(t) \\ \\
 \displaystyle{\frac{dI(t)}{dt}}  &=& r_1\, S(t)I(t) - r_2 \, I(t) + I_3(t)  \\  \\
@@
 \end{array}
-\]
-where $I_j(t)$ and $O_j(t)$ are arbitrary smooth functions of time, which describe inflows and outflows at the points $i_j \in X$ and $o_j \in Y$.
-If we drop the `inflow' and `outflow' terms $I_i$ and $O_i$ we obtain a system of coupled nonlinear first-order ordinary differential equations.
+\end{equation}
+Here $I_1(t),I_2(t),I_3(t)$ and $O_1(t)$ are arbitrary smooth functions of time, which describe inflows and outflows at the points $i_1,i_2,i_3 \in X$ and $o_1 \in Y$.
+If we drop these inflow and outflow terms, we obtain an autonomous system of coupled nonlinear first-order ordinary differential equations.
 In fact these equations are a famous model of infectious disease, the `SIR model', where $S(t)$, $I(t)$ and $R(t)$ describe the populations of susceptible, infected and recovered individuals, respectively.
@@
 \item vertical 1-morphisms are functions,
-\item horizontal 1-cells are \define{open Petri nets with rates}:
+\item horizontal 1-cells are \define{open Petri nets with rates}, namely diagrams in $\Petri_r$ of the form
 \[
@@
 \node (E) at (-2,0) {$P$};
-\node (F) at (-1,0) {$L(Y)$};
+\node (F) at (-1,0) {$L(Y)$,};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-\item 2-morphisms are diagrams in $\Petri_r$ of the form:
+\item 2-morphisms are diagrams in $\Petri_r$ of the form
 \[
@@
 \[ D(S) = \{ v \maps \R^S \to \R^S | \; v \textrm{ is algebraic}  \}. \]
-{\chris Changed : to $|$ in the set, is that OK?}
 \item $D$ maps any function $f \maps S \to S'$ between finite sets to the function $D(f) \maps D(S) \to D(S')$ given as follows:
@@
 As such, it automatically becomes a monoidal natural isomorphism between the functors $F, D \maps (\Fin\Set,+) \to (\Cat,\times)$.
+
+Given a Petri net with rates $P$ and defining $v$ as above, this system of first-order ordinary differential equations for a function $c \maps \R \to \R^S$:
+\[    \frac{d}{dt} c(t) = v(c(t))   \]
+is called the \define{rate equation}.    When $P$ is part of an open Petri net with rates
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (D) at (-3,0) {$L(X)$};
+\node (E) at (-2,0) {$P$};
+\node (F) at (-1,0) {$L(Y)$,};
+\path[->,font=\scriptsize,>=angle 90]
+(D) edge node [above] {$i$} (E)
+(F) edge node [above] {$o$} (E);
+\end{tikzpicture}
+\]
+we get the \define{open rate equation}
+\[     \frac{d}{dt} c(t) = v(c(t))  + i_*(I(t)) - o_*(O(t)) \]
+where $I \maps \R \to \R^X$ and $O \maps \R \to \R^X$ are arbitrary smooth functions describing \define{inflows} and \define{outflows}, respectively.
+Applying this prescription to the open Petri net with rates shown at the start of this section one gets the differential equations \cref{eq:openPetrir}.
+Other examples are worked out in \cite{BP}.
 
@@
 
-\section{} \label{eq:proofofaxiom}
+\section{Checking a coherence law} \label{eq:proofofaxiom}
 

### 2020-12-09 cospans.tex
added explanation of open rate equation to 5.4
updated end of Conclusions

@@
 \]
-we get the \define{open rate equation}
+we get an open dynamical system called the \define{open rate equation}:
 \[     \frac{d}{dt} c(t) = v(c(t))  + i_*(I(t)) - o_*(O(t)) \]
@@
 
-Even though for both \cref{thm:equiv} and the above result the conditions required are only sufficient, they suggest that with work we could establish a functorial picture
+Even though for both \cref{thm:equiv} and the above result the conditions stated are only sufficient, they suggest that with work we could establish this functorial picture:
 \begin{displaymath}
@@
 \end{displaymath}
-with an actual natural isomorphism in the middle.  
-This would imply that starting from an appropriate middle ground, employing the structured or the decorated cospan formalism is essentially the same. We leave such considerations for future work.
+with a natural isomorphism in the middle.
+The connection between opfibrations and laris goes back to Gray's \cref{prop:opfibtolari}, but we need to specialize it to a class suitable for both the structured and decorated cospan constructions.
+This would imply that starting from an appropriate middle ground, the structured and decorated cospan formalisms are essentially the same.
+We leave such considerations for future work.
 

### 2020-12-09 cospans.tex
modified end of Conclusions

@@
 with a natural isomorphism in the middle.
-The connection between opfibrations and laris goes back to Gray's \cref{prop:opfibtolari}, but we need to specialize it to a class suitable for both the structured and decorated cospan constructions.
-This would imply that starting from an appropriate middle ground, the structured and decorated cospan formalisms are essentially the same.
+The connection between opfibrations and laris goes back to Gray's \cref{prop:opfibtolari}, but we need to specialize it to a class suitable for both the structured and decorated cospan formalisms.
+This would imply that starting from an appropriate middle ground, these two formalisms are essentially the same.
 We leave such considerations for future work.

### 2020-12-09 cospans.tex
rewrote end of Conclusions

@@
 \path[->,font=\scriptsize]
-(A) edge node[above,sloped]{$F\mapsto F\lCsp$}  (C)
+(A) edge node[above,sloped, midway]{$\quad F\mapsto F\lCsp$}  (C)
 (D) edge (A)
 (E) edge (B)
-(B) edge node[below,sloped]{$L\mapsto {}_{L}\lCsp(\X)$} (C);
+(B) edge node[below,sloped, midway]{$\quad L\mapsto {}_{L}\lCsp(\X)$} (C);
 \end{tikzpicture}

### 2020-12-10 cospans.tex
fixed remark at end of Section 2

@@
 
-This theorem should generalize to the case when $\theta$ is a pseudonatural
-isomorphism, but the weaker version suffices for our application in \cref{subsec:petrirates}.
+This theorem should generalize to the case when $\theta$ is a pseudonatural equivalence, but the weaker version suffices for our application in \cref{subsec:petrirates}.
 

### 2020-12-10 cospans.tex
tiny leftover from yesterday
a few edits on 3, waiting for feedback from others on Zulip

@@
 
-In the case we are interested in, the pseudofunctor $F$ is lax monoidal; combining \cref{lem:MonGroth,lem:fibrewiselimits}, we deduce the following.
-%Christina: I suspect that's why for composition we get isomorphism below - using pushouts in which I cannot use the monoidal structure of the functor - whereas for coproducts and initial object we get equality since they were constructed in a very specific way.
-Related to the subtlety comment below.
-
 \begin{cor}\label{cor:fcocMonGroth}
  Suppose $\A$ has finite colimits and $F\maps(\A,+)\to(\Cat,\times)$ is a lax monoidal pseudofunctor.
+If $F\maps\A\to\Cat$ as a pseudofunctor factors through $\Rex$, then $\inta F$ has all finite colimits and the induced opfibration $U\maps\inta F\to\A$ preserves them.
+ %Moreover, for any choice of finite colimits in $\A$, finite colimits in $\inta F$ can be chosen so that that $U$ strictly preserves them.
+\end{cor}
+
+{\chris Decide on the specific assumptions of \cref{cor:fcocMonGroth} and \cref{thm:equiv} after discussing with John and Kenny}
+
+Notice that by \cref{lem:MonGroth}, since $\A$ is cocartesian monoidal, the initial lax monoidal pseudofunc\-tor structure $(F,\phi,\phi_0)\maps(\A,+)\to(\Cat,\times)$ gives rise to a specific monoidal structure on the fibers $F(a)$ in terms of $\phi,\phi_0$, given explicitly by \cref{eq:explicitstructure1}.
+If this fiberwise monoidal structure happens to itself be cocartesian, namely \cref{eq:explicitstructure1} gives coproducts and an initial object in each $F(a)$,
+%e.g. when the induced total category is cocartesian
+those are clearly isomorphic to the arbitrary choice of finite coproducts in $F(a)$ coming from the above assumption that as a pseudofunctor, $F\colon \A\to\Rex$. 
+For example, in that case, the coproducts induced in the Grothendieck category from the fiberwise ones as in \cref{eq:fibrewisecoprod} are equivalently given by \cref{eq:explicitstructure2}.
+
+%In the case we are interested in, the pseudofunctor $F$ is lax monoidal; combining \cref{lem:MonGroth,lem:fibrewiselimits}, we deduce the following. 
+%\begin{cor}\label{cor:fcocMonGroth}
+% Suppose $\A$ has finite colimits and $F\maps(\A,+)\to(\Cat,\times)$ is a lax monoidal pseudofunctor.
 If the corresponding pseudofunctor $\tilde{F} \maps \A\to\bicat{MonCat}$ given in \cref{lem:MonGroth} factors through $\Rex$, then $\inta F$ has all finite colimits and the induced opfibration $U\maps\inta F\to\A$ preserves them.
 Moreover, for any choice of finite colimits in $\A$, finite colimits in $\inta F$ can be chosen so that that $U$ strictly preserves them.
-\end{cor}
-
-Notice a subtlety in the above formulation.
+%\end{cor}
+
+%Notice a subtlety in the above formulation.
 \cref{lem:MonGroth} provides a specific monoidal structure on the fibers which becomes \cref{eq:explicitstructure1} when the base $\A$ is cocartesian monoidal.
@@
 and the inwards pointing morphisms are natural maps from the each cospan's feet to its apex.
+It follows that $\beta\hat{\chi}=\hat{\chi}(\beta+_\beta\beta)$ as the unique map between the involved colimits.
 

### 2020-12-11 cospans.tex
changed MonCat to SymMonCat, and related changes

@@
 We might hope to do this using a symmetric lax monoidal functor $F \maps (\Fin\Set, +) \to (\Set, \times)$ assigning to each finite set $m$ the set of all graphs with $m$ as their set of nodes.
-But this hope is doomed, for reasons painstakingly explained in \cite[Section 5]{BC2}.
+But this hope is doomed, for reasons painstakingly explained in \cite[Section 5]{BC}.
 There is really a \emph{category} of graphs with $m$ as their set of nodes---and surprisingly, trying to treat this category as a mere set does not work, despite all the tricks one might try.
@@
 
-In fact another solution to the problem is already known: the theory of structured cospans \cite{BC2,CourserThesis}.
+In fact another solution to the problem is already known: the theory of structured cospans \cite{BC,CourserThesis}.
 Given a functor $L \maps \A \to \X$, a \define{structured cospan} is a cospan in $\X$ whose feet come from a pair of objects in $\A$:
@@
 \end{itemize}
-Many of the flawed applications of decorated cospans have been fixed using structured cospans \cite[Section 6]{BC2}, but not all decorated cospans can handled using structured cospans.
+Many of the flawed applications of decorated cospans have been fixed using structured cospans \cite[Section 6]{BC}, but not all decorated cospans can handled using structured cospans.
 
@@
 
-In \cite{BC2}, the first two authors introduce the symmetric monoidal double category of \emph{structured cospans} as a formalism to capture open networks.
+In \cite{BC}, the first two authors introduce the symmetric monoidal double category of \emph{structured cospans} as a formalism to capture open networks.
 One of the main goals of this paper is to provide a monoidal double isomorphism between this double category and that of \emph{decorated cospans}, described in detail in \cref{DecCospansDoubleCat}.
@@
 \begin{proof}
-This was proved in \cite[Theorems~2.3 \& 3.9]{BC2}, where all the structures are specified in detail.
+This was proved in \cite[Theorems~2.3 \& 3.9]{BC}, where all the structures are specified in detail.
 In fact the double category structure only requires that $\X$ have pushouts, whereas the symmetric monoidal structure also requires that $\X$ has binary coproducts and an initial object (and thus all finite colimits), and that $\A$ has and $L$ preserves finite coproducts \cite[Theorem~3.2.3]{CourserThesis}.
@@
 
-In \cite{MV}, the classical Grothendieck construction is generalized to the monoidal setting: given a monoidal category $\A$ there is a bijection between \define{monoidal opindexed categories}, which are lax monoidal pseudofunctors $F\maps (\A, \otimes_A) \to (\Cat, \times)$, and \define{monoidal opfibrations}, which are opfibrations $U \maps \X \to \A$ where $\X$, $\A$ are monoidal, $U$ is strict monoidal, and $\otimes_\X$ preserves cocartesian liftings.
-This bijection sends a monoidal opindexed category $F \maps (\A,\otimes_A) \to (\Cat, \times)$ to its Grothendieck monoidal opfibration $U \maps \inta F \to \A$.
-If the monoidal structure on $\A$ is in fact cocartesian, there is a further correspondence between these structures and ordinary pseudofunctors $F\maps\A\to\bicat{MonCat}$ where $\bicat{MonCat}$ is 2-category of monoidal categories, strong monoidal functors and monoidal natural transformations.
+In \cite{MV}, the classical Grothendieck construction is generalized to the monoidal setting: given a symmetric monoidal category $\A$ there is a bijection between \define{symmetric monoidal opindexed categories}, which are symmetric lax monoidal pseudofunctors $F\maps (\A, \otimes_A) \to (\Cat, \times)$, and \define{symmetric monoidal opfibrations}, which are opfibrations $U \maps \X \to \A$ where $\X$, $\A$ are monoidal, $U$ is strict symmetric monoidal, %%% must it preserve the symmetries strictly too?
+and $\otimes_\X$ preserves cocartesian liftings.
+This bijection sends a symmetric monoidal opindexed category $F \maps (\A,\otimes_A) \to (\Cat, \times)$ to the symmetric monoidal opfibration $U \maps \inta F \to \A$.
+If the symmetric monoidal structure on $\A$ is in fact cocartesian, there is a further correspondence between these structures and ordinary pseudofunctors $F\maps \A \to \SMC$, where $\SMC$ is 2-category of symmetric monoidal categories, strong symmetric monoidal functors and monoidal natural transformations.
+
  In fact, all these correspondences lift to 2-equivalences.
@@
 \begin{lem}\label{lem:MonGroth}
-There is a 2-equivalence between the 2-categories of monoidal opfibrations and monoidal opindexed categories.
-If the base is cocartesian monoidal, there is a 2-equivalence between monoidal opfibrations and pseudofunctors into monoidal categories.
+There is a 2-equivalence between the 2-categories of symmetric monoidal opfibrations and symmetric monoidal opindexed categories.
+If the base is cocartesian monoidal, there is a 2-equivalence between symmetric monoidal opfibrations and pseudofunctors into $\SMC$.
 \end{lem}
@@
 \begin{gather}
-\textrm{lax monoidal pseudofunctors }F\maps(\A,+)\to(\Cat,\times) \notag\\
+\textrm{symmetric lax monoidal pseudofunctors }F\maps(\A,+)\to(\Cat,\times) \notag\\
 \Updownarrow \notag\\
-\textrm{monoidal opfibrations }U\maps(\X,\otimes_\X)\to(\A,+) \notag\\
+\textrm{symmetric monoidal opfibrations }U\maps(\X,\otimes_\X)\to(\A,+) \notag\\
 \Updownarrow \notag\\
-\textrm{pseudofunctors } \tilde{F} \maps \A\to\bicat{MonCat} \notag
+\textrm{pseudofunctors } \tilde{F} \maps \A\to \SMC \notag
 \end{gather}
@@
 \end{equation}
-where $\nabla$ is the fold map. 
+where $\nabla$ is the fold map.   SYMMETRIC MONOIDAL STRUCTURE??? %%%!!!
 \end{proof}
@@
 \end{enumerate}
-Given these conditions, for any choice of $\J$-colimits in $\A$ the $\J$-colimits in $\X$ can be chosen so that $U$ strictly preserves them.
+Given these conditions, for any choice of $\J$-colimits in $\A$ the $\J$-colimits in $\X$ can be chosen so that $U$ strictly preserves them.   NEEDS FIXING!!!  %%%!!!
 \end{lem}
@@
 
-The first part formulates the existence of colimits \emph{locally} in each fiber, and if we let $\J$ range over all finite categories it says that the corresponding pseudofunctor $F\maps\A\to\Cat$ lands in the sub-2-category $\Rex$.
+The first part formulates the existence of colimits \emph{locally} in each fiber, and if we let $\J$ range over all finite categories it says that the corresponding pseudofunctor $F \maps \A \to \Cat$ lands in the sub-2-category $\Rex$.
 The second part formulates the existence of colimits \emph{globally} in the total category $\inta F$, and if we let $\J$ range over all finite categories it says that $\X$ has finite colimits and $U$ preserves all finite colimits.
-As an example, suppose that $\A$ has pushouts and a Grothendieck opfibration $U\colon\inta F\to\A$ has fiberwise pushouts preserved by its reindexing functors.
+As an example, suppose that $\A$ has pushouts and a Grothendieck opfibration $U \colon \inta F \to\A$ has fiberwise pushouts preserved by its reindexing functors.
 We can construct pushouts in $\inta F$ as follows:
@@
 \begin{cor}\label{cor:fcocMonGroth}
- Suppose $\A$ has finite colimits and $F\maps(\A,+)\to(\Cat,\times)$ is a lax monoidal pseudofunctor.
-If $F\maps\A\to\Cat$ as a pseudofunctor factors through $\Rex$, then $\inta F$ has all finite colimits and the induced opfibration $U\maps\inta F\to\A$ preserves them.
+ Suppose $\A$ has finite colimits and $F \maps (\A,+) \to (\Cat,\times)$ is a symmetric lax monoidal pseudofunctor.
+If $F  \maps \A \to \Cat$ as a pseudofunctor factors through $\Rex$, then $\inta F$ has all finite colimits and the induced opfibration $U\maps \inta F \to \A$ preserves them.
  %Moreover, for any choice of finite colimits in $\A$, finite colimits in $\inta F$ can be chosen so that that $U$ strictly preserves them.
@@
 
-Notice that by \cref{lem:MonGroth}, since $\A$ is cocartesian monoidal, the initial lax monoidal pseudofunc\-tor structure $(F,\phi,\phi_0)\maps(\A,+)\to(\Cat,\times)$ gives rise to a specific monoidal structure on the fibers $F(a)$ in terms of $\phi,\phi_0$, given explicitly by \cref{eq:explicitstructure1}.
+Notice that by \cref{lem:MonGroth}, since $\A$ is cocartesian monoidal, the initial lax monoidal pseudofunc\-tor structure $(F,\phi,\phi_0) \maps (\A,+) \to (\Cat,\times)$ gives rise to a specific symmetric monoidal structure on the fibers $F(a)$ in terms of $\phi,\phi_0$, given explicitly by \cref{eq:explicitstructure1}.
 If this fiberwise monoidal structure happens to itself be cocartesian, namely \cref{eq:explicitstructure1} gives coproducts and an initial object in each $F(a)$,
@@
 They were then applied to open electrical circuits \cite{BF}, Markov processes \cite{BFP}, and chemical reaction networks \cite{BP}.
-Unfortunately, some of these applications were marred by technical flaws, which were later fixed using structured cospans \cite{BC2}.
+Unfortunately, some of these applications were marred by technical flaws, which were later fixed using structured cospans \cite{BC}.
 Here we explain how to also fix them using our new decorated cospans, since they provide another another solution to these problems.
@@
 
-We can easily build a double category with `open graphs' as horizontal 1-cells using the machinery of structured cospans, see \cite[Section 5]{BC2}.
+We can easily build a double category with `open graphs' as horizontal 1-cells using the machinery of structured cospans, see \cite[Section 5]{BC}.
 Let $L \maps \Fin\Set \to \Graph$ be the functor that assigns to a finite set $N$ the \define{discrete graph} on $N$: the graph with no edges and $N$ as its set of vertices.
@@
 this choice of $\phi_{N,N'}$ does not make $F$ into a symmetric lax monoidal functor, since it obeys the required laws only up to natural isomorphism, as in \cref{eq:omega}.
-See \cite[Section 5]{BC2} for a proof that these laws fail to hold on the nose.
+See \cite[Section 5]{BC} for a proof that these laws fail to hold on the nose.
 This fact is what necessitated a generalization of Fong's original approach to decorated cospans.
@@
 
-Structured and decorated cospans are a powerful tool for studying categories where the morphisms are electrical circuits---see \cite[Section 6.1]{BC2} and \cite{BCR,BF}.
+Structured and decorated cospans are a powerful tool for studying categories where the morphisms are electrical circuits---see \cite[Section 6.1]{BC} and \cite{BCR,BF}.
 The key idea is to use open graphs with labeled edges to describe circuits, where the labels can stand for resistors with any chosen resistance, capacitors with any chosen capacitance, or other circuit elements.
@@
 They used Fong's original decorated cospans to do this.
-Later, structured cospans were used to promote the first of these categories to a double category \cite[Section 6.16]{BC2}.
+Later, structured cospans were used to promote the first of these categories to a double category \cite[Section 6.16]{BC}.
 Here we show that the second of these categories, with open dynamical systems as morphisms, \emph{cannot} be made into a double category using structured cospans.
@@
 \]
-There is a functor $R \maps \Petri_r \to \Set$ sending any Petri net with rates to its set of places, and this has a left adjoint $L \maps \Set \to \Petri_r$ sending any set $S$ to the Petri net with $S$ as its set of species and no transitions \cite[Lemma 6.18]{BC2}.
-Since $\Petri_r$ has finite colimits \cite[Lemma 6.19]{BC2}, it follows that there is a symmetric monoidal double category ${}_L \lCsp(\Petri_r)$ where:
+There is a functor $R \maps \Petri_r \to \Set$ sending any Petri net with rates to its set of places, and this has a left adjoint $L \maps \Set \to \Petri_r$ sending any set $S$ to the Petri net with $S$ as its set of species and no transitions \cite[Lemma 6.18]{BC}.
+Since $\Petri_r$ has finite colimits \cite[Lemma 6.19]{BC}, it follows that there is a symmetric monoidal double category ${}_L \lCsp(\Petri_r)$ where:
 \begin{itemize}
@@
 
-For double categories we follow the notation of our paper on structured cospans \cite{BC2}, which in turn follows that of Hansen and Shulman \cite{HS,Shulman2010}.
+For double categories we follow the notation of our paper on structured cospans \cite{BC}, which in turn follows that of Hansen and Shulman \cite{HS,Shulman2010}.
 
@@
 \[ \mu \maps U_{A\otimes B} \xrightarrow{\sim} U_A \otimes U_B\]
-obeying a list of equations that can be found after \cite[Definition 2.10]{HS} and also \cite[Definition A.5]{BC2}.
+obeying a list of equations that can be found after \cite[Definition 2.10]{HS} and also \cite[Definition A.5]{BC}.
 \end{itemize}
@@
 
-%\bibitem{BC} J.\ C.\ Baez and K.\ Courser, Coarse-graining open Markov processes, \textsl{Theory Appl.\ Categ.\ }\textbf{33} (2018), 1223--1268.
-Available as \href{https://arxiv.org/abs/1710.11343}{arXiv:1710.11343}.
-
-\bibitem{BC2} J.\ C.\ Baez and K.\ Courser, Structured cospans,  \textsl{Theory Appl.\ Categ.\ }\textbf{35} (2020), 1771--1822.   Available as \href{http://arxiv.org/abs/1911.04630}{arXiv:1911.04630}.
+\bibitem{BC} J.\ C.\ Baez and K.\ Courser, Structured cospans,  \textsl{Theory Appl.\ Categ.\ }\textbf{35} (2020), 1771--1822.   Available as \href{http://arxiv.org/abs/1911.04630}{arXiv:1911.04630}.
 

### 2020-12-11 cospans.tex
tried to fix Lemma 3.4 - check it!

@@
 % in LaTeX
-% 2020/12/9
+% 2020/12/10
 
@@
 
+SEE IF THIS IS RIGHT:  %%%!!!
 \begin{lem}[\textbf{Hermida}] \label{lem:fibrewiselimits}
-Suppose $\J$ is a small category and $U\maps\X\to\A$ is an opfibration. If the base $\A$ has $\J$-colimits,
-the following are equivalent:
+Suppose $\J$ is a small category and $U \maps \X \to \A$ is an opfibration where the base 
+$\A$ has $\J$-colimits.  Then the following are equivalent:
 \begin{enumerate}
- \item all fibers have $\J$-colimits, and the reindexing functors preserve them;
- \item the total category $\X$ has $\J$-colimits, and $U$ preserves them.
+ \item all fibers have $\J$-colimits, and the reindexing functors strictly preserve them;
+ \item the total category $\X$ has $\J$-colimits and $U$ strictly preserves them.
 \end{enumerate}
-Given these conditions, for any choice of $\J$-colimits in $\A$ the $\J$-colimits in $\X$ can be chosen so that $U$ strictly preserves them.   NEEDS FIXING!!!  %%%!!!
+Moreover, if $\X$ has $\J$-colimits and $U$ preserves them, they can be chosen so that $U$ strictly preserves them.   
 \end{lem}

### 2020-12-11 cospans.tex
removed unused references

@@
 
-\bibitem{Brown1} R.\ Brown and C.\ B.\ Spencer, Double groupoids and crossed modules, 
-\textsl{Cah.\ Top.\ G\'eom.\ Diff.} \textbf{17} (1976), 343--362.
-
-\bibitem{Brown2} R.\ Brown, K.\ Hardie, H.\ Kamps and T.\ Porter, The homotopy double groupoid of a Hausdorff space, \textsl{Theory Appl.\ Categ.} \textbf{10} (2002), 71--93.
+%\bibitem{Brown1} R.\ Brown and C.\ B.\ Spencer, Double groupoids and crossed modules, 
+%\textsl{Cah.\ Top.\ G\'eom.\ Diff.} \textbf{17} (1976), 343--362.
+
+%\bibitem{Brown2} R.\ Brown, K.\ Hardie, H.\ Kamps and T.\ Porter, The homotopy double groupoid of a Hausdorff space, \textsl{Theory Appl.\ Categ.} \textbf{10} (2002), 71--93.
 
@@
 
-%\bibitem{Brown1} R.\ Brown and C.\ B.\ Spencer, Double groupoids and crossed modules, 
-%\textsl{Cah.\ Top.\ G\'eom.\ Diff.} \textbf{17} (1976), 343--362.
-
-%\bibitem{Brown2} R.\ Brown, K.\ Hardie, H.\ Kamps and T.\ Porter, The homotopy double groupoid of a Hausdorff space, \textsl{Th.\ Appl.\ Categ.} \textbf{10} (2002), 71--93.
-
 \bibitem{BungeFiore} M.\ Bunge and M.\ Fiore, Unique factorisation lifting functors and categories of linearly-controlled processes, \textsl{Math.\ Struct.\ Comput.\ Sci.\ } \textbf{10} (2000), 137--163.
@@
 
+%\bibitem{Ehresmann63} C.\ Ehresmann, Cat\'egories structur\'ees III: Quintettes et applications covariantes,  \textsl{Cah.\ Top.\ G\'eom.\ Diff.} \textbf{5} (1963), 1--22.
+
 %\bibitem{Ehresmann65} C.\ Ehresmann, {\sl Cat\'egories et Structures,} Dunod, Paris, 1965.
-
-\bibitem{Ehresmann63} C.\ Ehresmann, Cat\'egories structur\'ees III: Quintettes et applications covariantes,  \textsl{Cah.\ Top.\ G\'eom.\ Diff.} \textbf{5} (1963), 1--22.
-
-\bibitem{Ehresmann65} C.\ Ehresmann, {\sl Cat\'egories et Structures,} Dunod, Paris, 1965.
 
@@
 
-\bibitem{RSW} R.\ Rosebrugh, N.\ Sabadini and R.\ F.\ C.\ Walters, Generic commutative separable algebras and cospans of graphs, \textsl{Theory Appl.\ Categ.\ }\textbf{15} (2005), 164--177.
+%\bibitem{RSW} R.\ Rosebrugh, N.\ Sabadini and R.\ F.\ C.\ Walters, Generic commutative separable algebras and cospans of graphs, \textsl{Theory Appl.\ Categ.\ }\textbf{15} (2005), 164--177.
 

### 2020-12-11 cospans.tex
edits up to 3.2, notice the change in theorem's statement please

@@
 \begin{thm}\label{thm:SC}
-Given categories $\A$ and $\X$ with finite colimits and $L \maps \A \to \X$ a functor preserving finite colimits there is a symmetric monoidal double category $_L\lCsp(\X)$ in which
+Given categories $\A$ and $\X$ with finite colimits and $L \maps \A \to \X$ a functor preserving finite colimits, there is a symmetric monoidal double category $_L\lCsp(\X)$ in which
 \begin{itemize}
@@
 \path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$$} (B)
-(C) edge node[above]{$$} (B)
-(A') edge node[above]{$$} (B')
-(C') edge node[above]{$$} (B')
+(A) edge node[above]{$i$} (B)
+(C) edge node[above]{$o$} (B)
+(A') edge node[above]{$i'$} (B')
+(C') edge node[above]{$o'$} (B')
 (A) edge node [left]{$L(f)$} (A')
@@
 Composition of horizontal 1-cells and 2-cells is done using pushouts in $\X$, and the
-symmetric monoidal structure is defined using binary coproducts and the initial object in $\A$ and $\X$: 
+symmetric monoidal structure is defined using finite coproducts in $\A$ and $\X$: 
 the tensor of horizontal 1-cells is
@@
 This was proved in \cite[Theorems~2.3 \& 3.9]{BC}, where all the structures are specified in detail.
-In fact the double category structure only requires that $\X$ have pushouts, whereas the symmetric monoidal structure also requires that $\X$ has binary coproducts and an initial object (and thus all finite colimits), and that $\A$ has and $L$ preserves finite coproducts \cite[Theorem~3.2.3]{CourserThesis}.
+{\chris grammatical error follows} In fact, the double category structure only requires that $\X$ have pushouts, whereas the symmetric monoidal structure also requires that $\X$ has binary coproducts and an initial object (and thus all finite colimits), and that $\A$ has and $L$ preserves finite coproducts \cite[Theorem~3.2.3]{CourserThesis}.
 \end{proof}
@@
 We denote by $\Rex$ the 2-category of categories with finite colimits, functors preserving finite colimits, and natural transformations.
-Recall that for us a category $\A \in \Rex$ comes with a choice of finite colimits, so it gives a cocartesian monoidal category $(\A,+)$.
+Recall that for us a category $\C \in \Rex$ comes with a choice of finite colimits, so it gives a cocartesian monoidal category $(\C,+)$; this induces a well-defined 2-functor $\Rex\to\SMC$.
 
 \begin{thm} \label{thm:equiv}
-Suppose $\A$ has finite colimits and $F \maps (\A,+) \to (\Cat,\times)$ is a symmetric lax monoidal pseudofunctor that factors through $\Rex$ as an ordinary pseudofunctor.
-Then the symmetric monoidal double categories $F\lCsp$ of decorated cospans and $_L\lCsp(\inta F)$ of structured cospans are isomorphic, where $L \maps \A \to \inta F$ is a left adjoint of the induced Grothendieck opfibration $U\maps \inta F \to \A$.
+Suppose $\A$ has finite colimits and $F \maps (\A,+) \to (\Cat,\times)$ is a symmetric lax monoidal pseudofunctor.
+If its corresponding ordinary pseudofunctor (via the monoidal Grothendieck construction) {\chris SHOULD THIS PARENTHESIS STAY OR NOT?} $F\colon \A\to\SMC$ factors through $\Rex$, then the symmetric monoidal double categories $F\lCsp$ of decorated cospans and $_L\lCsp(\inta F)$ of structured cospans are isomorphic, where $L \maps \A \to \inta F$ is a left adjoint of the induced Grothendieck opfibration $U\maps \inta F \to \A$.
 \end{thm}

### 2020-12-11 cospans.tex
fixed parts of 3 before proof of 3.2

@@
 \end{thm}
-%%% Christina: note to self, now our functor factors through that specific Rex means that each category F(a) which later becomes the fiber comes with a specific choice of colimits.
-We do not know what this choice is, but of course such colimits in the fibers will be isomorphic to any other we may stumble upon!
 
@@
 
+In \cite{MV}, the classical Grothendieck construction is generalized to the monoidal setting: given a monoidal category $\A$ there is a bijection between \define{monoidal opindexed categories}, which are lax monoidal pseudofunctors $F\maps (\A, \otimes_A) \to (\Cat, \times)$, and \define{monoidal opfibrations}, which are opfibrations $U \maps \X \to \A$ where $\X$, $\A$ are monoidal, $U$ is strict monoidal,
+and $\otimes_\X$ preserves cocartesian liftings.
+This bijection sends a monoidal opindexed category $F \maps (\A,\otimes_A) \to (\Cat, \times)$ to the monoidal opfibration $U \maps \inta F \to \A$.
+If the monoidal structure on $\A$ is in fact cocartesian, there is a further correspondence between these structures and ordinary pseudofunctors $F\maps \A \to \MonCat$, where $\MonCat$ is 2-category of monoidal categories, strong monoidal functors and monoidal natural transformations.
+
+In fact, all these correspondences lift to 2-equivalences, and symmetry can also be incorporated.
+
+\begin{lem}\label{lem:MonGroth}
+There is a 2-equivalence between the 2-categories of monoidal opfibrations and monoidal opindexed categories.
+If the base is cocartesian monoidal, there is a 2-equivalence between monoidal opfibrations and pseudofunctors into $\MonCat$.
+%Moreover, symmetric monoidal opfibrations are equivalent to symmetric monoidal opindexed categories, and when the base is cocartesian monoidal these also correspond to pseudofunctors into $\SMC$.
+\end{lem}
+
+\begin{proof}
+This was shown by Moeller and the third author \cite[Theorems~3.13\&4.2]{MV}. In summary, for a cocartesian base $\A$ we have correspondences
+\begin{gather}
+\textrm{lax monoidal pseudofunctors }F\maps(\A,+)\to(\Cat,\times) \notag\\
+\Updownarrow \notag\\
+\textrm{monoidal opfibrations }U\maps(\X,\otimes_\X)\to(\A,+) \notag\\
+\Updownarrow \notag\\
+\textrm{pseudofunctors } \tilde{F} \maps \A\to \MonCat \notag
+\end{gather}
+The second equivalence was observed earlier by Shulman \cite{Shulman2008}.
+Moreover, symmetric lax monoidal pseudofunctors correspond to symmetric monoidal opfibrations, and those to pseudofunctors into $\SMC$.
+
+In more detail, if $(\phi,\phi_0)$ is the lax monoidal structure of the pseudofunctor $F$ as recalled in \cref{subsec:bicats}, the induced monoidal structure on the total Grothendieck category $\X=\inta F$ (\cref{def:GrothCat}) is given by
+\begin{equation}\label{eq:explicitstructure2}
+\Big(a,x\in F(a)\Big)\ot_{\X}\Big(b,y\in F(b)\Big)=\Big(a+b,\phi_{a,b}(x,y)\in F(a+b)\Big), \qquad I_{\X}=\Big(0_A,\phi_0\Big)
+\end{equation}
+If $F$ is a symmetric lax monoidal pseudofunctor, the induced monoidal structure in $\inta F$ is symmetric via
+$$\left(\beta_{a,b},(u_{a,b})_{x,y}\right)\colon \left(a+b,\phi_{a,b}(x,y)\right)\simrightarrow\left(b+a,\phi_{b,a}(y,x)\right)$$ where $\beta$ is the canonical symmetry for $\A$ and $u$ is the natural isomorphism of \cref{eq:braidedpseudofun}.
+
+Moreover, each fiber $\X_a=F(a)$ obtains a monoidal structure via 
+\begin{equation}\label{eq:explicitstructure1}
+\otimes_a\maps F(a)\times F(a)\xrightarrow{\phi_{a,a}}F(a+a)\xrightarrow{F(\nabla)}F(a),\quad
+I_a\maps\one\xrightarrow{\phi_0}F(0)\xrightarrow{F(!)}F(a)
+\end{equation}
+where $\nabla$ is the fold map, which is symmetric when $F$ is again via the components of $u_{a,a}$.
+\end{proof}
+
+\begin{comment} %%%John's version with symmetries
 In \cite{MV}, the classical Grothendieck construction is generalized to the monoidal setting: given a symmetric monoidal category $\A$ there is a bijection between \define{symmetric monoidal opindexed categories}, which are symmetric lax monoidal pseudofunctors $F\maps (\A, \otimes_A) \to (\Cat, \times)$, and \define{symmetric monoidal opfibrations}, which are opfibrations $U \maps \X \to \A$ where $\X$, $\A$ are monoidal, $U$ is strict symmetric monoidal, %%% must it preserve the symmetries strictly too?
@@
 \end{proof}
+\end{comment}
 
@@
 
-SEE IF THIS IS RIGHT:  %%%!!!
 \begin{lem}[\textbf{Hermida}] \label{lem:fibrewiselimits}
@@
 \begin{enumerate}
- \item all fibers have $\J$-colimits, and the reindexing functors strictly preserve them;
+ \item all fibers have $\J$-colimits, and the reindexing functors preserve them;
  \item the total category $\X$ has $\J$-colimits and $U$ strictly preserves them.
@@
  Suppose $\A$ has finite colimits and $F \maps (\A,+) \to (\Cat,\times)$ is a symmetric lax monoidal pseudofunctor.
-If $F  \maps \A \to \Cat$ as a pseudofunctor factors through $\Rex$, then $\inta F$ has all finite colimits and the induced opfibration $U\maps \inta F \to \A$ preserves them.
+If the corresponding pseudofunctor $F  \maps \A \to \SMC$ from \cref{lem:MonGroth} factors through $\Rex$, then $\inta F$ has all finite colimits and the induced opfibration $U\maps \inta F \to \A$ preserves them.
  %Moreover, for any choice of finite colimits in $\A$, finite colimits in $\inta F$ can be chosen so that that $U$ strictly preserves them.
@@
 
-{\chris Decide on the specific assumptions of \cref{cor:fcocMonGroth} and \cref{thm:equiv} after discussing with John and Kenny}
-
-Notice that by \cref{lem:MonGroth}, since $\A$ is cocartesian monoidal, the initial lax monoidal pseudofunc\-tor structure $(F,\phi,\phi_0) \maps (\A,+) \to (\Cat,\times)$ gives rise to a specific symmetric monoidal structure on the fibers $F(a)$ in terms of $\phi,\phi_0$, given explicitly by \cref{eq:explicitstructure1}.
-If this fiberwise monoidal structure happens to itself be cocartesian, namely \cref{eq:explicitstructure1} gives coproducts and an initial object in each $F(a)$,
-%e.g. when the induced total category is cocartesian
-those are clearly isomorphic to the arbitrary choice of finite coproducts in $F(a)$ coming from the above assumption that as a pseudofunctor, $F\colon \A\to\Rex$. 
+Regarding the assumptions of the above corollary, notice that since $\A$ is cocartesian monoidal, the initial lax monoidal pseudofunc\-tor structure $(F,\phi,\phi_0)$ gives rise to a specific symmetric monoidal structure on the fibers $F(a)$ in terms of $\phi,\phi_0$, given explicitly by \cref{eq:explicitstructure1}.
+Since we now ask that the pseudofunctor $F\colon \A\to\SMC$ factors through $\Rex$, this fiberwise monoidal structure is required to be cocartesian, namely \cref{eq:explicitstructure1} gives coproducts and an initial object in each $F(a)$.
+%,  those are clearly isomorphic to the arbitrary choice of finite coproducts in $F(a)$ coming from the above assumption that as a pseudofunctor, $F\colon \A\to\Rex$.
 For example, in that case, the coproducts induced in the Grothendieck category from the fiberwise ones as in \cref{eq:fibrewisecoprod} are equivalently given by \cref{eq:explicitstructure2}.
 
+%%% Initial version
 %In the case we are interested in, the pseudofunctor $F$ is lax monoidal; combining \cref{lem:MonGroth,lem:fibrewiselimits}, we deduce the following. 
@@
 \begin{tikzcd}[column sep=.5in]
- Fa\ot Fb\ar[r,"Ff\ot Fg"]\ar[d,"\phi_{a,b}"']\ar[dr,phantom,"\cong"] & Fa'\ot Fb'\ar[d,"\phi_{a',b'}"] \\
+ Fa\ot Fb\ar[r,"Ff\ot Fg"]\ar[d,"\phi_{a,b}"']\ar[dr,phantom,"\stackrel{\phi_{a,b}}{\cong}"] & Fa'\ot Fb'\ar[d,"\phi_{a',b'}"] \\
  F(a\ot b)\ar[r,"F(f\ot g)"'] & F(a'\ot b')
@@
  \begin{tikzcd}
-Fa\otimes Fb\ar[r,"\phi_{a,b}"]\ar[d,"\beta_{Fa,Fb}"']\ar[dr,phantom,"\scriptstyle\cong"] & F(a\ot b)\ar[d,"F(\beta_{a,b})"] \\
+Fa\otimes Fb\ar[r,"\phi_{a,b}"]\ar[d,"\beta_{Fa,Fb}"']\ar[dr,phantom,"\stackrel{u_{a,b}}{\cong}"] & F(a\ot b)\ar[d,"F(\beta_{a,b})"] \\
 Fb\otimes Fa\ar[r,"\phi_{b,a}"'] & F(b\ot a)

### 2020-12-11 cospans.tex
tiny

@@
 Suppose $\A$ has finite colimits and $F \maps (\A,+) \to (\Cat,\times)$ is a symmetric lax monoidal pseudofunctor.
-If its corresponding ordinary pseudofunctor (via the monoidal Grothendieck construction) {\chris SHOULD THIS PARENTHESIS STAY OR NOT?} $F\colon \A\to\SMC$ factors through $\Rex$, then the symmetric monoidal double categories $F\lCsp$ of decorated cospans and $_L\lCsp(\inta F)$ of structured cospans are isomorphic, where $L \maps \A \to \inta F$ is a left adjoint of the induced Grothendieck opfibration $U\maps \inta F \to \A$.
+If its corresponding ordinary pseudofunctor %(via the monoidal Grothendieck construction) {\chris SHOULD THIS PARENTHESIS STAY OR NOT?}
+$F\colon \A\to\SMC$ factors through $\Rex$, then the symmetric monoidal double categories $F\lCsp$ of decorated cospans and $_L\lCsp(\inta F)$ of structured cospans are isomorphic, where $L \maps \A \to \inta F$ is a left adjoint of the induced Grothendieck opfibration $U\maps \inta F \to \A$.
 \end{thm}
 
-The conditions of the above theorem relate to the existence of colimits as well as left adjoints for opfibrations.
-We first sketch this underlying framework, and then we proceed to the proof of the theorem.
+The ``corresponding pseudofunctor'' comes from the so-called monoidal Grothendieck construction, and the conditions of this theorem related to the existence of colimits as well as left adjoints for opfibrations.
+We first sketch the relevant underlying framework in detail, and then we proceed to the proof of the theorem.
 The basics of fibration theory needed for our purposes are recalled in \cref{sec:fibrations}.

### 2020-12-11 cospans.tex
tiny

@@
 
-We now have all the necessary background to formally construct an isomorphism between the double category of decorated cospans and the double category of structured cospans, starting from a symmetric lax monoidal pseudofunctor $F \maps (\A, +) \to (\Cat, \times)$ that factors through $\Rex$ as a pseudofunctor.
+We now have all the necessary background to formally construct an isomorphism between the double category of decorated cospans and the double category of structured cospans, starting from a symmetric lax monoidal pseudofunctor $F \maps (\A, +) \to (\Cat, \times)$ whose corresponding pseudofunctor $F\colon \A\to\SMC$ factors through $\Rex$.
 
@@
 
+{\chris Below, if the fiberwise coproducts are directly from the monoidal Grothendieck construction, we may end up with stricter monoidal double functor.}
 Since both double categories are symmetric monoidal under the running assumptions (\cref{DC,thm:SC}), we will now show that this double isomorphism is a symmetric monoidal one, namely $\lE=(\lE_0,\lE_1)$ is a symmetric strong monoidal double functor as per \cref{defn:monoidal_double_functor}.

### 2020-12-12 cospans.tex
corrected problems Christina noted in Sec. 5

@@
 % in LaTeX
-% 2020/12/10
+% 2020/12/11
 
@@
 Below we compare the two approaches in applications to graphs, electrical circuits, Petri nets, reaction networks and dynamical systems.
-In many cases, \cref{thm:equiv} shows that the structured and decorated cospan approaches are equivalent: \cref{subsec:graphs,subsec:circuits,subsec:petri} briefly illustrate that.
+In many cases, \cref{thm:equiv} shows that the structured and decorated cospan approaches are equivalent: \cref{subsec:graphs,subsec:circuits,subsec:petri} illustrate this.
 However, in \cref{subsec:petrirates} we show that open dynamical systems can only be treated using decorated cospans.
@@
 We can make $F$ into a symmetric lax monoidal pseudofunctor $F \maps (\Fin\Set, +) \to (\Cat,\times)$ by equipping it with suitable functors 
-\[   \phi_{N,N'} \maps F(N) \times F(N') \to F(N+N'), \qquad \phi_0 \maps F(\emptyset) \to \one \in \Cat. \]  
-{\chris Shouldn't the laxator for the units go in the other direction??}
+\[   \phi_{N,N'} \maps F(N) \times F(N') \to F(N+N'), \qquad \phi_0 \maps  \one \to F(\emptyset) . \]
 
@@
 In other words, it sends a pair of graph structures to their `disjoint union'.
-Surprisingly, though $F$ is a functor---for example, composition is strictly preserved---
-{\chris we already said that very recently, perhaps there is no need for explaining it again?}
-this choice of $\phi_{N,N'}$ does not make $F$ into a symmetric lax monoidal functor, since it obeys the required laws only up to natural isomorphism, as in \cref{eq:omega}.
+Surprisingly, though $F$ is a functor, this choice of $\phi_{N,N'}$ does not make $F$ into a symmetric lax monoidal functor, but only a symmetric lax monoidal pseudofunctor, since it obeys the required laws only up to natural isomorphism, as in \cref{eq:omega}.
 See \cite[Section 5]{BC} for a proof that these laws fail to hold on the nose.

### 2020-12-14 cospans.tex
fixed sentence abotut laxator in 5.1
concluded proof, please have a look

@@
 % in LaTeX
-% 2020/12/11
+% 2020/12/12
 
@@
  \scalebox{.75}{\begin{tikzcd}[ampersand replacement=\&,column sep=.3in,row sep=.1in]
-\& F(m_1)\times F(n_1)\times F(m_2)\times F(n_2)\ar[dd,"1\times\beta\times1"']\ar[ddrr,phantom,"\cong"]\ar[rr,"\phi_{m_1,n_1}\times\phi_{m_2,n_2}"] \&\& F(m_1+n_1)\times F(m_2+n_2)\ar[rr,"\phi_{m_1+n_1,m_2+n_2}"] \&\& F(m_1+n_1+m_2+n_2)\ar[dd,"F\psi"]\ar[ddll,"F(1+\beta+1)"'] \\
+\& F(m_1)\times F(n_1)\times F(m_2)\times F(n_2)\ar[dd,"1\times\beta\times1"']\ar[ddrr,phantom,"\stackrel{\cref{eq:thetaa}}{\cong}"]\ar[rr,"\phi_{m_1,n_1}\times\phi_{m_2,n_2}"] \&\& F(m_1+n_1)\times F(m_2+n_2)\ar[rr,"\phi_{m_1+n_1,m_2+n_2}"] \&\& F(m_1+n_1+m_2+n_2)\ar[dd,"F\psi"]\ar[ddll,"F(1+\beta+1)"'] \\
 \one \ar[ur,"{x_1\times y_1\times x_2\times y_2}"]\ar[dr,"{x_1\times x_2\times y_1\times y_2}"'] \&\&\&\& \\
@@
 \end{equation}
-where the left-hand side isomorphism combines pseudoassociativity \cref{eq:omega} and braided monoidal structure \cref{eq:braidedpseudofun} of the pseudofunctor $F$ (and can be explicitly found in e.g.
-\cite[Page 125]{DS}), and the right hand side follows from the universal property of colimits and pseudofunctoriality of $F$.
+where the left-hand side isomorphism combines pseudoassociativity \cref{eq:omega} and braided monoidal structure \cref{eq:braidedpseudofun} of the pseudofunctor $F$ as seen in detail in the appendix, and the right hand side follows from the universal property of colimits and pseudofunctoriality of $F$.
 Similarly, for units $U_{a+b}$ and $U_a\ot U_b$ it is easy to see that as cospans they are both the identity $1_{a+b}:a+b\to a+b\leftarrow a+b:1_{a+b}$, and there is a canonical isomorphism between their trivial decorations \cref{eq:UFCsp}, namely $F(!_{a+b})\phi_0\cong\phi_{a,b}(F(!_a)\times F(!_b))(\phi_0\times\phi_0)$ via the structure isomorphisms for $(\phi,\phi_0)$.
@@
 
-The functor $\phi_0$ is uniquely determined since $\one$ is the terminal category.
+The functor $\phi_0$ is uniquely determined since $F(\emptyset)$ is the terminal category.
 More interesting is $\phi_{N,N'}$.
@@
 \begin{tikzcd}[column sep=.5in]
- Fa\ot Fb\ar[r,"Ff\ot Fg"]\ar[d,"\phi_{a,b}"']\ar[dr,phantom,"\stackrel{\phi_{a,b}}{\cong}"] & Fa'\ot Fb'\ar[d,"\phi_{a',b'}"] \\
+ Fa\ot Fb\ar[r,"Ff\ot Fg"]\ar[d,"\phi_{a,b}"']\ar[dr,phantom,"\stackrel{\phi_{f,g}}{\cong}"] & Fa'\ot Fb'\ar[d,"\phi_{a',b'}"] \\
  F(a\ot b)\ar[r,"F(f\ot g)"'] & F(a'\ot b')
@@
 \node (E) at (6.75,0.5) {$\scriptstyle{F(m_1 + n_1) \times F(m_2+n_2)}$};
-\node () at (10.25,-1) {$\scriptstyle\stackrel{\cref{eq:braidedpseudofun}}{\cong}$};
-\node () at (7.875,0) {$\scriptstyle\stackrel{\cref{eq:interchangedeco}}{\cong}$};
+\node () at (10.25,-1) {$\scriptstyle\stackrel[\cref{eq:braidedpseudofun}]{u}{\cong}$};
+\node () at (7.875,0) {$\scriptstyle\stackrel[\cref{eq:interchangedeco}]{}{\cong}$};
 \node (E') at (6.75,-0.5) {$\scriptstyle{F(m_1+m_2) \times F(n_1+n_2)}$};
@@
 \]
-{\chris Kenny please see difference in diagrams (the rightmost part is not important, just to make the two decoration isomorphism have the same border).
+%{\chris Kenny please see difference in diagrams (the rightmost part is not important, just to make the two decoration isomorphism have the same border).
 The blue is the old one.
@@
 But also on the down part of the diagram, coming from the decoration morphism of the braiding \cref{eq:decobraiding}, mine is much ``easier''.}
-{\color{blue}
-\[
-\begin{tikzpicture}[scale=1.6]
-%\node (A) at (3.85,0) {$\scriptstyle{\cong}$};
-%\node (A') at (3.85,-1) {$\scriptstyle{\cong}$};
-\node (D) at (3,-0.5) {$\scriptstyle{\one}$};
-\node (E) at (6.75,0.5) {$\scriptstyle{F(m_1 + n_1) \times F(m_2+n_2)}$};
-\node () at (5.5,-1) {$\scriptstyle{\cong}$};
-\node () at (7.875,-1) {$\scriptstyle\stackrel{\cref{eq:braidedpseudofun}}{\cong}$};
-\node () at (10.25,-1) {$\scriptstyle{\cong}$};
-\node () at (7.875,0) {$\scriptstyle\stackrel{\cref{eq:interchangedeco}}{\cong}$};
-\node (E') at (6.75,-0.5) {$\scriptstyle{F(m_1+m_2) \times F(n_1+n_2)}$};
-\node (B) at (9,0.5) {$\scriptstyle{F((m_1+n_1)+(m_2+n_2))}$};
-\node (B') at (9,-0.5) {$\scriptstyle{F((m_1+ m_2)+(n_1+n_2))}$};
-\node (C) at (11.5,0.5) {$\scriptstyle{F((m_1+n_1)+_{b+b'}(m_2+n_2))}$};
-\node (C') at (11.5,-0.5) {$\scriptstyle{F((m_1+_b m_2)+ (n_1+_{b'} n_2))}$};
-\node (G) at (4.25,0.5) {$\scriptstyle{F(m_1) \times F(n_1) \times F(m_2) \times F(n_2)}$};
-\node (G') at (4.25,-0.5) {$\scriptstyle{F(m_1) \times F(m_2) \times F(n_1) \times F(n_2)}$};
-\node (G'') at (4.25,-1.5) {$\scriptstyle{F(n_1) \times F(n_2) \times F(m_1) \times F(m_2)}$};
-\node (E'') at (6.75,-1.5) {$\scriptstyle{F(n_1+n_2) \times F(m_1+m_2)}$};
-\node (B'') at (9,-1.5) {$\scriptstyle{F((n_1+n_2)+(m_1+ m_2))}$};
-\node (C'') at (11.5,-1.5) {$\scriptstyle{F((n_1+_{b'}n_2)+(m_1+_b m_2))}$};
-\node (X) at (3.4,0.2) {$\scriptscriptstyle{x_1 \times y_1 \times x_2 \times y_2}$};
-\node (X') at (3.4,-0.35) {$\scriptscriptstyle{x_1 \times x_2 \times y_1 \times y_2}$};
-\node (X'') at (3.4,-1.2) {$\scriptscriptstyle{y_1 \times y_2 \times x_1 \times x_2}$};
-\path[->,font=\scriptsize,>=angle 90]
-(B') edge node [fill=white] {$F(\beta)$} (B'')
-(E') edge node [fill=white] {$\beta$} (E'')
-(E) edge node [above] {$\phi_{m_1+n_1,m_2+n_2}$} (B)
-(E'') edge node [above] {$\phi_{n_1+n_2,m_1+m_2}$} (B'')
-(E') edge node [above] {$\phi_{m_1+m_2,n_1+n_2}$} (B')
-(B) edge node [above] {$F(\psi)$} (C)
-(B'') edge node [above] {$F(\psi+\psi)$} (C'')
-(B') edge node [above] {$F(\psi+\psi)$} (C')
-(C) edge node [fill=white] {$F(\hat{\chi})$} (C')
-(C') edge node [fill=white] {$F(\beta)$} (C'')
-(G) edge node [above] {$\phi_{m_1,n_1} {\times} \phi_{m_2,n_2}$} (E)
-(G'') edge node [above] {$\phi_{n_1,n_2} {\times} \phi_{m_1,m_2}$} (E'')
-(G') edge node [above] {$\phi_{m_1,m_2} \times \phi_{n_1,n_2}$} (E')
-(G) edge node [fill=white] {$1 \times \beta \times 1$} (G')
-(G') edge node [fill=white] {$\beta$} (G'')
-(D) edge[out=90,in=180] node [left,above] {$$} (G)
-(D) edge[out=270,in=180] node [left,above] {$$} (G'')
-(D) edge node [below] {$$} (G');
-\end{tikzpicture}
-\]
-}
+%{\color{blue}
+%\[
+%\begin{tikzpicture}[scale=1.6]
+%%\node (A) at (3.85,0) {$\scriptstyle{\cong}$};
+%%\node (A') at (3.85,-1) {$\scriptstyle{\cong}$};
+%\node (D) at (3,-0.5) {$\scriptstyle{\one}$};
+%\node (E) at (6.75,0.5) {$\scriptstyle{F(m_1 + n_1) \times F(m_2+n_2)}$};
+%\node () at (5.5,-1) {$\scriptstyle{\cong}$};
+%\node () at (7.875,-1) {$\scriptstyle\stackrel{\cref{eq:braidedpseudofun}}{\cong}$};
+%\node () at (10.25,-1) {$\scriptstyle{\cong}$};
+%\node () at (7.875,0) {$\scriptstyle\stackrel{\cref{eq:interchangedeco}}{\cong}$};
+%\node (E') at (6.75,-0.5) {$\scriptstyle{F(m_1+m_2) \times F(n_1+n_2)}$};
+%\node (B) at (9,0.5) {$\scriptstyle{F((m_1+n_1)+(m_2+n_2))}$};
+%\node (B') at (9,-0.5) {$\scriptstyle{F((m_1+ m_2)+(n_1+n_2))}$};
+%\node (C) at (11.5,0.5) {$\scriptstyle{F((m_1+n_1)+_{b+b'}(m_2+n_2))}$};
+%\node (C') at (11.5,-0.5) {$\scriptstyle{F((m_1+_b m_2)+ (n_1+_{b'} n_2))}$};
+%\node (G) at (4.25,0.5) {$\scriptstyle{F(m_1) \times F(n_1) \times F(m_2) \times F(n_2)}$};
+%\node (G') at (4.25,-0.5) {$\scriptstyle{F(m_1) \times F(m_2) \times F(n_1) \times F(n_2)}$};
+%\node (G'') at (4.25,-1.5) {$\scriptstyle{F(n_1) \times F(n_2) \times F(m_1) \times F(m_2)}$};
+%\node (E'') at (6.75,-1.5) {$\scriptstyle{F(n_1+n_2) \times F(m_1+m_2)}$};
+%\node (B'') at (9,-1.5) {$\scriptstyle{F((n_1+n_2)+(m_1+ m_2))}$};
+%\node (C'') at (11.5,-1.5) {$\scriptstyle{F((n_1+_{b'}n_2)+(m_1+_b m_2))}$};
+%\node (X) at (3.4,0.2) {$\scriptscriptstyle{x_1 \times y_1 \times x_2 \times y_2}$};
+%\node (X') at (3.4,-0.35) {$\scriptscriptstyle{x_1 \times x_2 \times y_1 \times y_2}$};
+%\node (X'') at (3.4,-1.2) {$\scriptscriptstyle{y_1 \times y_2 \times x_1 \times x_2}$};
+%\path[->,font=\scriptsize,>=angle 90]
+%(B') edge node [fill=white] {$F(\beta)$} (B'')
+%(E') edge node [fill=white] {$\beta$} (E'')
+%(E) edge node [above] {$\phi_{m_1+n_1,m_2+n_2}$} (B)
+%(E'') edge node [above] {$\phi_{n_1+n_2,m_1+m_2}$} (B'')
+%(E') edge node [above] {$\phi_{m_1+m_2,n_1+n_2}$} (B')
+%(B) edge node [above] {$F(\psi)$} (C)
+%(B'') edge node [above] {$F(\psi+\psi)$} (C'')
+%(B') edge node [above] {$F(\psi+\psi)$} (C')
+%(C) edge node [fill=white] {$F(\hat{\chi})$} (C')
+%(C') edge node [fill=white] {$F(\beta)$} (C'')
+%(G) edge node [above] {$\phi_{m_1,n_1} {\times} \phi_{m_2,n_2}$} (E)
+%(G'') edge node [above] {$\phi_{n_1,n_2} {\times} \phi_{m_1,m_2}$} (E'')
+%(G') edge node [above] {$\phi_{m_1,m_2} \times \phi_{n_1,n_2}$} (E')
+%(G) edge node [fill=white] {$1 \times \beta \times 1$} (G')
+%(G') edge node [fill=white] {$\beta$} (G'')
+%(D) edge[out=90,in=180] node [left,above] {$$} (G)
+%(D) edge[out=270,in=180] node [left,above] {$$} (G'')
+%(D) edge node [below] {$$} (G');
+%\end{tikzpicture}
+%\]
+%}
 For the other (vertical) composition of \cref{eq:thisdiagram}, that of $\beta\odot\beta$ followed by $\chi$, the composite decoration $\tau_2\tau_1$ is
@@
 \node (E) at (6.75,0.5) {$\scriptstyle{F(m_1 + n_1) \times F(m_2+n_2)}$};
-\node () at (5.5,0) {$\scriptstyle\stackrel{\cref{eq:braidedpseudofun}}{\cong}$};
-\node () at (7.875,0) {$\scriptstyle\stackrel{\cref{eq:pseudonaturality}}{\cong}$};
+\node () at (5.5,0) {$\scriptstyle\stackrel[\cref{eq:braidedpseudofun}]{u\times u}{\cong}$};
+\node () at (7.875,0) {$\scriptstyle\stackrel[\cref{eq:pseudonaturality}]{\phi_{\beta,\beta}}{\cong}$};
 \node () at (10.25,0) {$\scriptstyle{\cong}$};
-\node () at (7.875,-1) {$\scriptstyle\stackrel{\cref{eq:interchangedeco}}{\cong}$};
+\node () at (7.875,-1) {$\scriptstyle\stackrel[\cref{eq:interchangedeco}]{}{\cong}$};
 \node () at (12,-1) {$\scriptstyle\cong$};
@@
 (E) edge node [above] {$\phi_{m_1+n_1,m_2+n_2}$} (B)
-(E'') edge node [below] {$F\psi\times F\psi)$} (B'')
+(E'') edge node [below] {$F\psi\times F\psi$} (B'')
 (E') edge node [above] {$\phi_{n_1+m_1,n_2+m_2}$} (B')
@@
 \]
-{\chris The closing sentence for the proof to be complete should be that these two decoration maps are EQUAL for the diagram \cref{eq:thisdiagram} to commute!
+%{\chris The closing sentence for the proof to be complete should be that these two decoration maps are EQUAL for the diagram \cref{eq:thisdiagram} to commute!
 Right?
@@
 Do you see the logic?}
-
-The fact that these two pasted isomorphisms are equal follows from the axioms of a braided lax monoidal pseudofunctor and as a result, \cref{eq:thisdiagram} commutes and the axiom holds.
+In order to verify that these two pasted isomorphisms are equal, we first of all need to expand the isomorphism \cref{eq:interchangedeco}, whose left half part is explicitly written as follows (also found in \cite[Page 125]{DS}):
+\begin{equation}\label{eq:thetaa}
+\scalebox{.8}{
+\begin{tikzcd}[column sep=.05in,ampersand replacement=\&]
+Fm_1{\times} Fn_1{\times} Fm_2{\times} Fn_2\ar[ddr,phantom,bend right,"{\scriptstyle\stackrel[\cref{eq:braidedpseudofun}]{1\times u\times1}{\cong}}"]\ar[dr,"1\times\phi\times1"]\ar[rr,"\phi\times\phi"]\ar[ddd,"1\times\beta\times1"'] \&\& F(m_1{+}n_1){\times} F(m_2{+}n_2)\ar[d,phantom,"\scriptstyle{\cong}"]\ar[ddd,phantom,"{\scriptstyle\stackrel[\cref{eq:pseudonaturality}]{1\times\phi_{\beta,1}}{\cong}}"]\ar[rr,"\phi"] \&\& F(m_1{+}n_1{+}m_2{+}n_2)\ar[ddd,"F(1+\beta+1)"]\ar[ddl,bend left,phantom,"{\scriptstyle\stackrel[\cref{eq:pseudonaturality}]{\phi_{1,\beta+1}}{\cong}}"] \\
+\& Fm_1{\times} F(n_1 {+} m_2){\times} Fn_2\ar[rr,"{1\times\phi}"]\ar[d,"{1\times F\beta\times1}"'] \&\phantom{A}\& Fm_1{\times} F(n_1 {+} m_2 {+} n_2)\ar[d,"{1\times F(\beta+1)}"]\ar[ur,"\phi"] \& \\
+\& Fm_1{\times} F(m_2{+}n_1){\times} Fn_2\ar[rr,"1\times\phi"'] \&\phantom{A}\ar[d,phantom,"\scriptstyle\cong"]\& Fm_1{\times} F(m_2{+}n_1{+}n_2)\ar[dr,"\phi"'] \& \\
+Fm_1{\times} Fm_2{\times} Fn_1{\times} Fn_2\ar[ur,"1\times\phi\times1"']\ar[rr,"\phi\times\phi"'] \&\& F(m_1{+}m_2){\times} F(n_1{+}n_2)\ar[rr,"\phi"'] \&\& F(m_1{+}m_2{+}n_1{+}n_2)
+\end{tikzcd}}
+\end{equation}
+where the unnammed isomorphisms are appropriate composites of the pseudoassociativity of $F$ \cref{eq:omega}.
+The result now follows from lengthy pasted diagram calculations using the axioms of a sylleptic lax monoidal pseudofunctor.
 \begin{comment}

### 2020-12-14 cospans.tex
changed date on top
fixed typo in Appendix A
small corrections

@@
 % in LaTeX
-% 2020/12/12
+% 2020/12/14
 
@@
 Suppose $\A$ has finite colimits and $F \maps (\A,+) \to (\Cat,\times)$ is a symmetric lax monoidal pseudofunctor.
-If its corresponding ordinary pseudofunctor %(via the monoidal Grothendieck construction) {\chris SHOULD THIS PARENTHESIS STAY OR NOT?}
+If the corresponding ordinary pseudofunctor %(via the monoidal Grothendieck construction) {\chris SHOULD THIS PARENTHESIS STAY OR NOT?}
 $F\colon \A\to\SMC$ factors through $\Rex$, then the symmetric monoidal double categories $F\lCsp$ of decorated cospans and $_L\lCsp(\inta F)$ of structured cospans are isomorphic, where $L \maps \A \to \inta F$ is a left adjoint of the induced Grothendieck opfibration $U\maps \inta F \to \A$.
@@
 with a natural isomorphism in the middle.
-The connection between opfibrations and laris goes back to Gray's \cref{prop:opfibtolari}, but we need to specialize it to a class suitable for both the structured and decorated cospan formalisms.
-This would imply that starting from an appropriate middle ground, these two formalisms are essentially the same.
+The connection between opfibrations and laris goes back to Gray's \cref{prop:opfibtolari}, but we need to specialize it to a class suitable for both the structured and decorated cospan constructions.
+This would imply that starting from an appropriate middle ground, these two constructions are essentially the same.
 We leave such considerations for future work.
@@
 \end{equation}
-where the unnammed isomorphisms are appropriate composites of the pseudoassociativity of $F$ \cref{eq:omega}.
+where the unnamed isomorphisms are appropriate composites of the pseudoassociativity of $F$ \cref{eq:omega}.
 The result now follows from lengthy pasted diagram calculations using the axioms of a sylleptic lax monoidal pseudofunctor.

### 2020-12-14 cospans.tex
changes to Thm. 3.1, Thm. 3.2 and Lemma 3.3.

@@
 This was proved in \cite[Theorems~2.3 \& 3.9]{BC}, where all the structures are specified in detail.
-{\chris grammatical error follows} In fact, the double category structure only requires that $\X$ have pushouts, whereas the symmetric monoidal structure also requires that $\X$ has binary coproducts and an initial object (and thus all finite colimits), and that $\A$ has and $L$ preserves finite coproducts \cite[Theorem~3.2.3]{CourserThesis}.
+In fact, the double category structure only requires that $\X$ have pushouts, whereas the symmetric monoidal structure also requires that $\X$ and $\A$ have finite colimits and that $L$ preserves finite coproducts \cite[Theorem~3.2.3]{CourserThesis}.
 \end{proof}
@@
 The following theorem establishes an isomorphism between structured and decorated cospan double categories under certain conditions.
-We denote by $\Rex$ the 2-category of categories with finite colimits, functors preserving finite colimits, and natural transformations.
-Recall that for us a category $\C \in \Rex$ comes with a choice of finite colimits, so it gives a cocartesian monoidal category $(\C,+)$; this induces a well-defined 2-functor $\Rex\to\SMC$.
+Let $\Rex$ be the 2-category of categories with finite colimits, functors preserving finite colimits, and natural transformations.
+Let $\SMC$ be the 2-category of symmetric monoidal categories, strong symmetric monoidal functors and natural transformations.
+Recall that for us a category $\C \in \Rex$ comes with a choice of finite colimits, so it gives a specific cocartesian monoidal category $(\C,+)$, and this induces a 2-functor $\Rex \to \SMC$.
 
@@
 Suppose $\A$ has finite colimits and $F \maps (\A,+) \to (\Cat,\times)$ is a symmetric lax monoidal pseudofunctor.
-If the corresponding ordinary pseudofunctor %(via the monoidal Grothendieck construction) {\chris SHOULD THIS PARENTHESIS STAY OR NOT?}
-$F\colon \A\to\SMC$ factors through $\Rex$, then the symmetric monoidal double categories $F\lCsp$ of decorated cospans and $_L\lCsp(\inta F)$ of structured cospans are isomorphic, where $L \maps \A \to \inta F$ is a left adjoint of the induced Grothendieck opfibration $U\maps \inta F \to \A$.
+If the corresponding pseudofunctor $F \maps \A \to \SMC$ factors through $\Rex$, then the symmetric monoidal double categories $F\lCsp$ of decorated cospans and $_L\lCsp(\inta F)$ of structured cospans are isomorphic, where $L \maps \A \to \inta F$ is a left adjoint of the induced Grothendieck opfibration $U\maps \inta F \to \A$.
 \end{thm}
@@
 
-In \cite{MV}, the classical Grothendieck construction is generalized to the monoidal setting: given a monoidal category $\A$ there is a bijection between \define{monoidal opindexed categories}, which are lax monoidal pseudofunctors $F\maps (\A, \otimes_A) \to (\Cat, \times)$, and \define{monoidal opfibrations}, which are opfibrations $U \maps \X \to \A$ where $\X$, $\A$ are monoidal, $U$ is strict monoidal,
-and $\otimes_\X$ preserves cocartesian liftings.
+In \cite{MV}, the classical Grothendieck construction is generalized to the monoidal setting: given a monoidal category $\A$ there is a bijection between \define{monoidal opindexed categories}, which are lax monoidal pseudofunctors $F\maps (\A, \otimes_A) \to (\Cat, \times)$, and \define{monoidal opfibrations}, which are opfibrations $U \maps \X \to \A$ where $\X$, $\A$ are monoidal, $U$ is strict monoidal, and $\otimes_\X$ preserves cocartesian liftings.
 This bijection sends a monoidal opindexed category $F \maps (\A,\otimes_A) \to (\Cat, \times)$ to the monoidal opfibration $U \maps \inta F \to \A$.
@@
 \begin{lem}\label{lem:MonGroth}
-There is a 2-equivalence between the 2-categories of monoidal opfibrations and monoidal opindexed categories.
-If the base is cocartesian monoidal, there is a 2-equivalence between monoidal opfibrations and pseudofunctors into $\MonCat$.
-%Moreover, symmetric monoidal opfibrations are equivalent to symmetric monoidal opindexed categories, and when the base is cocartesian monoidal these also correspond to pseudofunctors into $\SMC$.
+There is a 2-equivalence between the 2-categories of monoidal opfibrations and monoidal opindexed categories with a fixed base, and if the base is cocartesian monoidal, there is a 2-equivalence between these and pseudofunctors into $\MonCat$.
+Similarly there is a 2-equivalence between symmetric monoidal opfibrations and symmetric monoidal opindexed categories with a fixed base, and if the base is cocartesian monoidal also a 2-equivalence between these and pseudofunctors into $\SMC$.
 \end{lem}
@@
 \begin{proof}
-This was shown by Moeller and the third author \cite[Theorems~3.13\&4.2]{MV}. In summary, for a cocartesian base $\A$ we have correspondences
+This was shown by Moeller and the third author \cite[Theorems~3.13 \& 4.2]{MV}. In summary, for a cocartesian base $\A$ we have correspondences
 \begin{gather}

### 2020-12-14 cospans.tex
Changed Thm. 3.1, Thm. 3.2 and Lem. 3.3.

@@
 This was proved in \cite[Theorems~2.3 \& 3.9]{BC}, where all the structures are specified in detail.
-In fact, the double category structure only requires that $\X$ have pushouts, whereas the symmetric monoidal structure also requires that $\X$ and $\A$ have finite colimits and that $L$ preserves finite coproducts \cite[Theorem~3.2.3]{CourserThesis}.
+In fact, the double category structure only requires that $\X$ have pushouts, whereas the symmetric monoidal structure also requires that $\X$ and $\A$ have finite colimits and that $L$ preserve finite coproducts \cite[Theorem~3.2.3]{CourserThesis}.
 \end{proof}

### 2020-12-15 cospans.tex
various edits mainly in 3

@@
 (D) edge node [below] {$j_{n}$} (F)
-(B) edge[bend left=10] node [above] {$u_m\;$} (G)
-(D) edge[bend right=10] node [above] {$\;u_n$} (G)
+(B) edge[bend left=10] node [above] {$v_m\;$} (G)
+(D) edge[bend right=10] node [above] {$\;v_n$} (G)
 (F) edge node [fill=white] {$\psi$} (G)
@@
 
-In \cite{MV}, the classical Grothendieck construction is generalized to the monoidal setting: given a monoidal category $\A$ there is a bijection between \define{monoidal opindexed categories}, which are lax monoidal pseudofunctors $F\maps (\A, \otimes_A) \to (\Cat, \times)$, and \define{monoidal opfibrations}, which are opfibrations $U \maps \X \to \A$ where $\X$, $\A$ are monoidal, $U$ is strict monoidal, and $\otimes_\X$ preserves cocartesian liftings.
+In \cite{MV}, the classical Grothendieck construction is generalized to the monoidal setting: given a (symmetric) monoidal category $\A$, there is a bijection between \define{(symmetric) monoidal opindexed categories}, which are (symmetric) lax monoidal pseudofunctors $F\maps (\A, \otimes_A) \to (\Cat, \times)$, and \define{(symmetric) monoidal opfibrations}, which are opfibrations $U \maps \X \to \A$ where $\X$, $\A$ are (symmetric) monoidal, $U$ is (symmetric) strict monoidal, and $\otimes_\X$ preserves cocartesian liftings.
 This bijection sends a monoidal opindexed category $F \maps (\A,\otimes_A) \to (\Cat, \times)$ to the monoidal opfibration $U \maps \inta F \to \A$.
-If the monoidal structure on $\A$ is in fact cocartesian, there is a further correspondence between these structures and ordinary pseudofunctors $F\maps \A \to \MonCat$, where $\MonCat$ is 2-category of monoidal categories, strong monoidal functors and monoidal natural transformations.
-
-In fact, all these correspondences lift to 2-equivalences, and symmetry can also be incorporated.
+If the monoidal structure on $\A$ is in fact cocartesian, there is a further correspondence between these structures and ordinary pseudofunctors $F\maps \A \to \MonCat$ (or to $\SMC$ in the symmetric case).
+%Christina removed the explanation of what MonCat is, because we gave a clear explanation of what SymMonCat is earlier!
+
+In fact, all these correspondences lift to 2-equivalences.
 
@@
 & a+_bc\ar[dd,phantom, very near start,"\upback"description] & \\
-a\ar[ur,"u_a"] && c\ar[ul,"u_c"'] \\
+a\ar[ur,"v_a"] && c\ar[ul,"v_c"'] \\
 & b\ar[ul,"f"]\ar[ur,"g"'] &
@@
  & w \ar[dd,phantom, very near start,"\upback"description] & \\
- F(u_a)x\ar[ur] & & F(u_c)z\ar[ul] \\
- & F(u_a)(F(f)(y))\cong F(u_c)(F(g)(y))\ar[ul,"F(u_a)k"]\ar[ur,"F(u_c)\ell"'] &
+ F(v_a)x\ar[ur] & & F(v_c)z\ar[ul] \\
+ & F(v_a)(F(f)(y))\cong F(v_c)(F(g)(y))\ar[ul,"F(v_a)k"]\ar[ur,"F(v_c)\ell"'] &
  \end{tikzcd}
@@
 
-By \cref{cor:fcocMonGroth}, when $F$ as an ordinary pseudofunctor factors through $\Rex$, the Gro\-the\-ndieck construction gives rise to a category $\inta F$ with finite colimits such that the corresponding opfibration $U\maps\inta{F}\to\A$ preserves all finite colimits.
+By \cref{cor:fcocMonGroth}, when the corresponding pseudofunctor $F\colon\A\to\SMC$ factors through $\Rex$, the Gro\-the\-ndieck construction gives rise to a category $\inta F$ with finite colimits such that the corresponding opfibration $U\maps\inta{F}\to\A$ (strictly) preserves them.
 Moreover, by \cref{prop:opfibtolari}, $U$ has a left adjoint $L\maps\A\to\inta F$ with $UL=1_\A$.
@@
 Explicitly, the left adjoint picks the initial object in the fiber $L(a)=(a,\bot_a)$, also expressed as $F(!_a)\circ\phi_0(*)$ according to \cref{eq:explicitstructure1} for $(\phi,\phi_0)$ the monoidal structure of $F$.
-%Christina: If each adjoint picks one isomorphic initial object, can we choose the one with that choice?
-Well they are all isomorphic and that could help with the monoidal structure later...
+%There are many laris, one for each choice of initial object.
+Having fixed our choice of colimits, there is really only one lari, correct?
+Also, is that ``also...'' part used anywhere?
 
@@
 
-Building up to an isomorphism of the above described double categories, we now define a double functor
+Building towards an isomorphism of the above described double categories, we now define a double functor
 \begin{displaymath}
@@
 in $\A$ along with the map $\tau\maps Fk(x)\to x'$ in $F(m')$ coming from the middle arrow above, namely an $F$-decorated cospan 2-morphism. 
-With these definitions, $\lE$ is indeed a double functor as in \cref{def:doublefun}: both $\lE_0$ and $\lE_1$ are functors that appropriately commute with sources and targets, and there exist globular 2-isomorphisms $\lE(N) \odot \lE(M) \simrightarrow\lE(N \odot M)$, $U_{\lE m} \simrightarrow\lE(U_m)$
+With these mappings, $\lE$ is indeed a double functor as in \cref{def:doublefun}.
+First of all, both $\lE_0$ and $\lE_1$ are functors that appropriately commute with sources and targets.
+Moreover, there exist globular 2-isomorphisms $\lE(N) \odot \lE(M) \simrightarrow\lE(N \odot M)$, $U_{\lE m} \simrightarrow\lE(U_m)$
 for any pair of composable horizontal 1-cells $M=\cspn{(a,\bot_a)}{(m,x)}{(b,\bot_b)}{}{}$ and $N=\cspn{(b,\bot_b)}{(n,y)}{(c,\bot_c)}{}{}$ and any object $m$ of $_L\lCsp(\inta F)$.
@@
  \begin{tikzcd}[column sep={.7in,between origins}]
- && (m+_b n,F(u_m)x+_{(\bot_{m+_bn})}F(u_n)y) && \\
+ && (m+_b n,F(v_m)x+_{(\bot_{m+_bn})}F(v_n)y) && \\
  & (m,x) \ar[ur] && (n,y)\ar[ul] \\
@@
 \end{displaymath}
-where $u$ are the canonical maps into the pushout.
-Under $\lE$ this is mapped to the underlying $\A$-cospan $\cspn{a}{m+_bn}{b}{}{}$ with decoration $F(u_m)x+F(u_n)y$, since a pushout over an initial object is really a coproduct.
+where $v_m,v_n$ are the canonical maps into the pushout.
+Under $\lE$ this is mapped to the underlying $\A$-cospan $\cspn{a}{m+_bn}{b}{}{}$ with decoration $F(v_m)x+F(v_n)y$, since a pushout over an initial object is really a coproduct.
 That decoration is isomorphic to that of \cref{eq:1} due to the following diagram
@@
  \begin{tikzcd}
-F(m)\times F(n)\ar[rr,"\phi"]\ar[d,"F(u_m)\times F(u_n)"']\ar[dr,phantom,"\cong"] && F(m+n)\ar[d,"F(\psi)"]\ar[d,bend right=50, phantom,"\cong"']\ar[dl,"F(u_m+u_n)"description] \\
-F(m+_bn)\times F(m+_bn)\ar[r,"\phi"'] & F\left((m+_bn)+(m+_bn)\right)\ar[r,"F(\nabla)"'] & F(m+_bn)
+F(m)\times F(n)\ar[rr,"\phi_{m,n}"]\ar[d,"F(v_m)\times F(v_n)"']\ar[dr,phantom,"\cong"] && F(m+n)\ar[d,"F(\psi)"]\ar[d,bend right=50, phantom,"\cong"']\ar[dl,"F(v_m+v_n)"description] \\
+F(m+_bn)\times F(m+_bn)\ar[r,"\phi_{m+_bn,m+_bn}"']\ar[rr,dashed,bend right=15] & F\left((m+_bn)+(m+_bn)\right)\ar[r,"F(\nabla)"'] & F(m+_bn)
  \end{tikzcd}
 \end{equation}
-where the bottom composite is the fiberwise coproduct in $F(m+_bn)$ as in \cref{eq:explicitstructure1}.
-The left-hand side isomorphism is due to pseudonaturality of $\phi$ whereas the right-hand side isomorphism follows from universal properties and pseudofunctoriality of $F$.
+where the dashed bottom composite is the fiberwise coproduct in $F(m+_bn)$ as in \cref{eq:explicitstructure1}.
+The left-hand side isomorphism is \cref{eq:pseudonaturality} from pseudonaturality of $\phi$ whereas the right-hand side isomorphism follows from universal properties and pseudofunctoriality of $F$.
 Regarding identities, the identity horizontal 1-cell $U_m$ in $_L\lCsp(\inta F)$ is $\cspn{(m,\bot_m)}{(m,\bot_m)}{(m,\bot_m)}{}{}$ with $1_m$ as the $A$-component and isomorphisms between initial objects in the fibers.
 Thus $\lE(U_m)$ is the identity cospan in $A$ together with the `initial decoration' $\bot_m\in F(m)$, and so is $U_{\mathbb{E}(m)}$ as in \cref{eq:UFCsp}.
-%Do we want to check that E is a double functor one last time?
 
@@
 
-{\chris Below, if the fiberwise coproducts are directly from the monoidal Grothendieck construction, we may end up with stricter monoidal double functor.}
 Since both double categories are symmetric monoidal under the running assumptions (\cref{DC,thm:SC}), we will now show that this double isomorphism is a symmetric monoidal one, namely $\lE=(\lE_0,\lE_1)$ is a symmetric strong monoidal double functor as per \cref{defn:monoidal_double_functor}.
@@
 \begin{align*}
-\lE(M)\ot\lE(M')&\;\stackrel{\cref{eq:tensordecoration}}{=}\;a+a'\xrightarrow{i+i'}m+m'\xleftarrow{o+o'}b+b' \textrm{ with }\one\xrightarrow{x\times x'}F(m)\times F(m')\xrightarrow{\phi_{m,m'}}F(m+m') \\
-\lE(M\ot M')&\;\stackrel{\cref{eq:tensorstuctured}}{=}\;\lE\Big((a+a',\bot_{a+a'})\to\underbrace{(m+m',F(\iota_m)x+F(\iota_{m'})x')}_{\cref{eq:fibrewisecoprod}}\leftarrow(b+b',\bot_{b+b'})\Big)%=a+a'\xrightarrow{i+i'}m+m'\xleftarrow{o+o'}b+b' \textrm{ with }\phi_{m,m'}(x,x')
+\lE(M)\ot\lE(M')&\;\stackrel{\cref{eq:tensordecoration}}{=}\;a+a'\xrightarrow{i+i'}m+m'\xleftarrow{o+o'}b+b' \textrm{ with }\phi_{m,m'}(x,x')\in F(m+m')
+%\one\xrightarrow{x\times x'}F(m)\times F(m')\xrightarrow{\phi_{m,m'}}F(m+m')
+\\
+\lE(M\ot M')&\;\stackrel{\cref{eq:tensorstuctured}}{=}\;\lE\Big((a+a',\bot_{a+a'})\to\underbrace{(m+m',F(\iota_m)x+F(\iota_{m'})x')}_{\cref{eq:fibrewisecoprod}}\leftarrow(b+b',\bot_{b+b'})\Big) \\
+&=a+a'\xrightarrow{i+i'}m+m'\xleftarrow{o+o'}b+b' \textrm{ with }F(\iota_m)x+F(\iota_{m'})x'\in F(m+m')
 \end{align*}
-which are uniquely isomorphic $F(\iota_m)x+F(\iota_{m'})\cong \phi_{m,m'}(x,x')$ in an analogous way to \cref{eq:isomorphismdiag}, as also discussed after \cref{cor:fcocMonGroth}.
-Moreover, the monoidal unit for the category of arrows of $F\lCsp$ is $0_\A\xrightarrow{\raisebox{-3pt}[0pt][0pt]{$=$}}0_\A\xleftarrow{\raisebox{-3pt}[0pt][0pt]{$=$}}0_\A$ with the trivial decoration $\phi_0\maps \one\to F(0_A)$,
+The cospan part is equal, whereas we have an isomorphism between the decorations $F(\iota_m)x+F(\iota_{m'})\cong \phi_{m,m'}(x,x')$ in an analogous way to \cref{eq:isomorphismdiag} as follows
+\begin{displaymath}
+\begin{tikzcd}
+F(m)\times F(m')\ar[rr,"\phi_{m,m'}"]\ar[d,"F(i_m)\times F(i_{m'})"']\ar[dr,phantom,"\stackrel{\cref{eq:pseudonaturality}}{\cong}"] && F(m+m')\ar[d,equal]\ar[d,bend right=50, phantom,"\cong"']\ar[dl,"F(i_m+i_{m'})"description] \\
+F(m+m')\times F(m+m')\ar[r,"\phi_{m+m',m+m'}"']\ar[rr,dashed,bend right=15] & F\left((m+m')+(m+m')\right)\ar[r,"F(\nabla)"'] & F(m+m')
+ \end{tikzcd}
+\end{displaymath}
+Notice that this isomorphism is in fact unique, since both sides express a coproduct in the Grothendieck category $\inta F$ by formulas \cref{eq:fibrewisecoprod,eq:explicitstructure2}.
+{\chris IS THIS CLEAR?}
+
+{\chris Kenny, I am a bit confused with all the units and monoidal units around.
+Could you go through in detail, and phrase correctly, the following part?
+Following the definition of a monoidal double functors and related structures precisely?
+For example, shouldn't we start from the monoidal unit of structured cospans?
+How do you write that?}
+Moreover, the monoidal unit for the category of arrows of $F\lCsp$ is $0_\A\xrightarrow{\raisebox{-3pt}[0pt][0pt]{$=$}}0_\A\xleftarrow{\raisebox{-3pt}[0pt][0pt]{$=$}}0_\A$ with the trivial decoration $\phi_0\maps \one\to F(0_A)\to F(0_A)$,
 which is an initial object and as such isomorphic to $0_{F(0)}$
 %=\lE((0_A,)\xrightarrow{\raisebox{-3pt}[0pt][0pt]{$=$}}(0_A,\phi_0)\xleftarrow{\raisebox{-3pt}[0pt][0pt]{$=$}}(0_A,\phi_0))$
-again by \cref{eq:explicitstructure2} and the discussion after \cref{cor:fcocMonGroth}.
+again by \cref{eq:explicitstructure2}.
 It can be verified that with the above structure, $\lE_1$ is also a symmetric monoidal functor, and the rest of the axioms of \cref{defn:monoidal_double_functor} hold.
@@
 \end{defn}
+{\chris Those units in the definition should be monoidal units not unit functors...}
 \noindent
-Unpacking this definition, one obtains a number of diagrams which can be found after \cite[Definition 2.4]{HS}.
+Unpacking this definition, one obtains a number of diagrams which can be found after \cite[Definition 2.14]{HS}.
 

### 2020-12-15 cospans.tex
small change

@@
 \end{align*}
-The cospan part is equal, whereas we have an isomorphism between the decorations $F(\iota_m)x+F(\iota_{m'})\cong \phi_{m,m'}(x,x')$ in an analogous way to \cref{eq:isomorphismdiag} as follows
+The cospan part is equal, whereas we have an isomorphism between the decorations $F(\iota_m)x+F(\iota_{m'})x'\cong \phi_{m,m'}(x,x')$ in an analogous way to \cref{eq:isomorphismdiag} as follows
 \begin{displaymath}
@@
 \end{displaymath}
-Notice that this isomorphism is in fact unique, since both sides express a coproduct in the Grothendieck category $\inta F$ by formulas \cref{eq:fibrewisecoprod,eq:explicitstructure2}.
-{\chris IS THIS CLEAR?}
+Notice that both sides above express a coproduct in the Grothendieck category $\inta F$ by formulas \cref{eq:fibrewisecoprod,eq:explicitstructure2},  so this isomorphism is in the canonical unique one that commutes with the respective cocones.
+{\chris IS THIS CLEAR?
+OR HELPFUL?
+Could omit.}
 

### 2020-12-15 cospans.tex
clarified diagram in theorem 2.1

@@
 \node (D) at (1.5,-0.5) {$m'+_{b'}n'$};
-\node (E) at (4.5,0.5) {$x \odot y \in F(m+_b n)$};
-\node (F) at (4.5,-0.5) {$x' \odot y' \in F(m' +_{b'} n')$};
+\node (E) at (4.5,0.5) {$y \odot x \in F(m+_b n)$};
+\node (F) at (4.5,-0.5) {$y' \odot x' \in F(m' +_{b'} n')$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \end{equation}
-where the middle isomorphism is due to pseudonaturality of $\phi$ and the right-hand side isomorphism is due to pseudofunctoriality of $F$.
+where the middle isomorphism is \cref{eq:pseudonaturality} from pseudonaturality of $\phi$ and the right-hand side isomorphism is due to pseudofunctoriality of $F$.
 
@@
 \node (A') at (0,-0.5) {$a$};
-\node (B) at (1.5,0.5) {$(m_1+_{b} m_2)+_{c} m_3$};
+\node (B) at (1.5,0.5) {$m_1+_{b}(m_2 +_{c} m_3)$};
 \node (C) at (3,0.5) {$d$};
 \node (C') at (3,-0.5) {$d$};
-\node (D) at (1.5,-0.5) {$m_1+_{b}(m_2 +_{c} m_3)$};
-\node (E) at (5.5,0.5) {$(x_3 \odot x_2) \odot x_1 \in F((m_1+_{b} m_2)+_{c} m_3)$};
-\node (F) at (5.5,-0.5) {$x_3 \odot (x_2 \odot x_1) \in F(m_1+_{b} (m_2 +_{c} m_3))$};
+\node (D) at (1.5,-0.5) {$(m_1+_{b} m_2)+_{c} m_3$};
+\node (E) at (5.5,0.5) {$(x_3 \odot x_2) \odot x_1 \in F(m_1+_{b} (m_2 +_{c} m_3))$};
+\node (F) at (5.5,-0.5) {$x_3 \odot (x_2 \odot x_1) \in F((m_1+_{b} m_2)+_{c} m_3)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
+{\chris Old version
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0.5) {$a$};
+\node (A') at (0,-0.5) {$a$};
+\node (B) at (1.5,0.5) {$(m_1+_{b} m_2)+_{c} m_3$};
+\node (C) at (3,0.5) {$d$};
+\node (C') at (3,-0.5) {$d$};
+\node (D) at (1.5,-0.5) {$m_1+_{b}(m_2 +_{c} m_3)$};
+\node (E) at (5.5,0.5) {$(x_3 \odot x_2) \odot x_1 \in F((m_1+_{b} m_2)+_{c} m_3)$};
+\node (F) at (5.5,-0.5) {$x_3 \odot (x_2 \odot x_1) \in F(m_1+_{b} (m_2 +_{c} m_3))$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$$} (B)
+(C) edge node[above]{$$} (B)
+(A) edge node[left]{$1_a$} (A')
+(C) edge node[right]{$1_d$} (C')
+(A') edge node {$$} (D)
+(C') edge node {$$} (D)
+(B) edge node [left] {$\stackrel{\kappa}{\cong}$} (D);
+\end{tikzpicture}
+\]}
 together with an isomorphism $F(\kappa)((x_3 \odot x_2) \odot x_1) \cong (x_3 \odot (x_2 \odot x_1))$ between the decorations 
@@
 \begin{equation}\label{eq:decoiso}
+\scalebox{.8}
+{\begin{tikzcd}[ampersand replacement=\&]
+\& F(m_1){\times}(F(m_2){\times}F(m_3))\ar[dddrr,phantom,"\stackrel{\cref{eq:omega}}{\cong}"]\ar[r,"1\times\phi_{m_2,m_3}"]\ar[ddd,"\alpha"description] \& F(m_1){\times}F(m_2{+}m_3)\ar[r,"1\times F(\psi)"]\ar[dr,"\phi_{m_1,m_2+m_3}"'] \& F(m_1){\times}F(m_2{+_c}m_3)\ar[d,phantom,"\stackrel{\cref{eq:pseudonaturality}}{\cong}"]\ar[r,"\phi_{m_1,m_2+_cm_3}"] \& F(m_1{+}(m_2{+_c}m_3))\ar[r,"F(\psi)"]\ar[dddr,phantom,"\cong"] \& F(m_1{+_b}(m_2{+_c}m_3))\ar[ddd,"F(\kappa)"] \\
+\one\ar[ur,"x_1\times(x_2\times x_3)"]\ar[d,equal] \&\&\& F(m_1{+}(m_2{+}m_3))\ar[ur,"F(1+\psi)"']\ar[d,"F\alpha"] \& \\
+\one\ar[dr,"(x_1\times x_2)\times x_3)"']\&\&\& F((m_1{+}m_2){+}m_3)\ar[dr,"F(\psi+1)"]\ar[d,phantom,"\stackrel{\cref{eq:pseudonaturality}}{\cong}"] \& \\
+\& (F(m_1){\times}F(m_2)){\times}F(m_3)\ar[r,"\phi_{m_1,m_2}\times1"'] \& F(m_1{+}m_2){\times}m_3\ar[ur,"\phi_{m_1+m_2,m_3}"]\ar[r,"F(\psi)\times1"'] \& F(m_1{+_b}m_2){\times} F(m_3)\ar[r,"\phi_{m_1{+_b}m_2,m_3}"'] \& F((m_1{+_b}m_2){+}m_3)\ar[r,"F\psi"'] \& F((m_1{+_b}m_2){+_c}m_3)
+\end{tikzcd}}
+\end{equation}
+{\chris Old version
+\begin{displaymath}
 \begin{tikzpicture}[scale=1.7,baseline=(current bounding box.center)]
@@
 \end{tikzpicture}
-\end{equation}
+\end{displaymath}}
 %%% Christina: I erased tau, and also Fpsi because they were not accurate and those arrows are OK to understand - the universal maps from a 'smaller' colimit to a 'bigger' one.
 If we kept Fpsi's we should write them like F(psi+1) for the first arrow at the top, and that would make the whole thing a bit heavier.
-where $a$ is the associator of $\Cat$ and $\kappa$ is the canonical isomorphism between two colimits of the same diagram in $\A$.
+where $a$ are the associators of $\Cat$ and $\A$ and $\kappa$ is the canonical isomorphism between two colimits of the same diagram in $\A$.
 Similarly the right and left unitors can be constructed, and all data satisfy the axioms of a double category---essentially breaking down to those of the cospan double category of $\A$ and axioms of the lax monoidal pseudofunctor $F$.

### 2020-12-15 cospans.tex
tiny

@@
 \one\ar[ur,"x_1\times(x_2\times x_3)"]\ar[d,equal] \&\&\& F(m_1{+}(m_2{+}m_3))\ar[ur,"F(1+\psi)"']\ar[d,"F\alpha"] \& \\
-\one\ar[dr,"(x_1\times x_2)\times x_3)"']\&\&\& F((m_1{+}m_2){+}m_3)\ar[dr,"F(\psi+1)"]\ar[d,phantom,"\stackrel{\cref{eq:pseudonaturality}}{\cong}"] \& \\
+\one\ar[dr,"(x_1\times x_2)\times x_3"']\&\&\& F((m_1{+}m_2){+}m_3)\ar[dr,"F(\psi+1)"]\ar[d,phantom,"\stackrel{\cref{eq:pseudonaturality}}{\cong}"] \& \\
 \& (F(m_1){\times}F(m_2)){\times}F(m_3)\ar[r,"\phi_{m_1,m_2}\times1"'] \& F(m_1{+}m_2){\times}m_3\ar[ur,"\phi_{m_1+m_2,m_3}"]\ar[r,"F(\psi)\times1"'] \& F(m_1{+_b}m_2){\times} F(m_3)\ar[r,"\phi_{m_1{+_b}m_2,m_3}"'] \& F((m_1{+_b}m_2){+}m_3)\ar[r,"F\psi"'] \& F((m_1{+_b}m_2){+_c}m_3)
@@
 where $v_m,v_n$ are the canonical maps into the pushout.
-Under $\lE$ this is mapped to the underlying $\A$-cospan $\cspn{a}{m+_bn}{b}{}{}$ with decoration $F(v_m)x+F(v_n)y$, since a pushout over an initial object is really a coproduct.
+Under $\lE$ this is mapped to the underlying $\A$-cospan $\cspn{a}{m+_bn}{b}{}{}$ with decoration $F(v_m)x+F(v_n)y$ in the fiber $F(m+_bn)$, since a pushout over an initial object is really a coproduct.
 That decoration is isomorphic to that of \cref{eq:1} due to the following diagram

### 2020-12-15 cospans.tex
Added a bit about monoidal units at the end of Theorem 3.2

@@
 It can be verified that with the above structure, $\lE_1$ is also a symmetric monoidal functor, and the rest of the axioms of \cref{defn:monoidal_double_functor} hold.
+
+\textbf{Kenny: This is what I would say regarding the monoidal units:} Moreover, the monoidal unit $I_{F\lCsp}$ for the category of arrows of $F\lCsp$ is given by the identity cospan $0_\A \rightarrow 0_\A \leftarrow 0_\A$ on the monoidal unit of $\A$ together with the trivial decoration $\bot_{0_\A} = \phi_0 \colon 1 \to F(0_\A)$ on $0_\A$, and the monoidal unit $I_{{_L \lCsp(\int F)}}$ for the category of arrows of ${ _L \lCsp(\int F)}$ is given by $(0_\A,\bot_{0_\A}) \rightarrow (0_\A,\bot_{0_\A}) \leftarrow (0_\A,\bot_{0_\A})$, with $\lE(I_{{ _L \lCsp(\int F)}})$ also being given by the identity cospan on $0_\A$ with the trivial decoration on its apex so that the transformation $\theta_U \colon I_{F\lCsp} \to \lE \circ I_{{_L \lCsp (\int F)}}$ is an identity.
 \end{proof}
@@
 \begin{defn}\label{defn:monoidal_double_functor}
-Given symmetric monoidal double categories $\lD$ and $\lE$, a \define{symmetric monoidal double functor} $\lF \colon \lD \to \lE$ is a double functor $\lF$ together with transformations $\theta \colon {\otimes \circ (\lF,\lF)} \to \lF \circ \otimes$ and $\theta_U \colon 1_\lE \to \lF \circ 1_\lD$ that satisfy the usual coherence axioms for a symmetric monoidal functor with respect to $\otimes$.
+Given symmetric monoidal double categories $\lD$ and $\lE$, a \define{symmetric monoidal double functor} $\lF \colon \lD \to \lE$ is a double functor $\lF$ together with transformations $\theta \colon {\otimes \circ (\lF,\lF)} \to \lF \circ \otimes$ and $\theta_U \colon I_\lE \to \lF \circ I_\lD$ that satisfy the usual coherence axioms for a symmetric monoidal functor with respect to $\otimes$.
 \end{defn}
 {\chris Those units in the definition should be monoidal units not unit functors...}
+%%% Kenny: How about I instead of 1?
 \noindent

### 2020-12-16 cospans.tex
changed date at top of file
I deleted the much-hated tilde
microscopic unnoticeable change

@@
 % in LaTeX
-% 2020/12/14
+% 2020/12/15
 
@@
 If the monoidal structure on $\A$ is in fact cocartesian, there is a further correspondence between these structures and ordinary pseudofunctors $F\maps \A \to \MonCat$ (or to $\SMC$ in the symmetric case).
-%Christina removed the explanation of what MonCat is, because we gave a clear explanation of what SymMonCat is earlier!
 
@@
 \Updownarrow \notag\\
-\textrm{pseudofunctors } \tilde{F} \maps \A\to \MonCat \notag
+\textrm{pseudofunctors } F \maps \A\to \MonCat \notag
 \end{gather}
@@
 \Updownarrow \notag\\
-\textrm{pseudofunctors } \tilde{F} \maps \A\to \SMC \notag
+\textrm{pseudofunctors } F \maps \A\to \SMC \notag
 \end{gather}
@@
 % Suppose $\A$ has finite colimits and $F\maps(\A,+)\to(\Cat,\times)$ is a lax monoidal pseudofunctor.
-If the corresponding pseudofunctor $\tilde{F} \maps \A\to\bicat{MonCat}$ given in \cref{lem:MonGroth} factors through $\Rex$, then $\inta F$ has all finite colimits and the induced opfibration $U\maps\inta F\to\A$ preserves them.
+If the corresponding pseudofunctor $F \maps \A\to\bicat{MonCat}$ given in \cref{lem:MonGroth} factors through $\Rex$, then $\inta F$ has all finite colimits and the induced opfibration $U\maps\inta F\to\A$ preserves them.
 Moreover, for any choice of finite colimits in $\A$, finite colimits in $\inta F$ can be chosen so that that $U$ strictly preserves them.
@@
 
-Since both double categories are symmetric monoidal under the running assumptions (\cref{DC,thm:SC}), we will now show that this double isomorphism is a symmetric monoidal one, namely $\lE=(\lE_0,\lE_1)$ is a symmetric strong monoidal double functor as per \cref{defn:monoidal_double_functor}.
-Indeed, $\lE_0=\mathrm{id}_\A$ is a symmetric monoidal functor trivially.
+Since both double categories are symmetric monoidal under the running assumptions (\cref{DC,thm:SC}), we now show that this double isomorphism is a symmetric monoidal one, namely that $\lE=(\lE_0,\lE_1)$ is a symmetric strong monoidal double functor as per \cref{defn:monoidal_double_functor}.
+Indeed, $\lE_0= \id_\A$ is a symmetric monoidal functor trivially.
 For $\lE_1$, given two structured cospans $M=(a,\bot_a)\to(m,x)\leftarrow(b,\bot_b)$ and $M'=(a',\bot_{a'})\to(m',x')\leftarrow(b',\bot_{b'})$ in $_L\lCsp(\inta F)$, we compute the appropriate decorated cospans

### 2020-12-16 cospans.tex
diagram 8 and surroundings fixed

@@
 % in LaTeX
-% 2020/12/15
+% 2020/12/16
 
@@
 \node (E) at (5.5,0.5) {$F(m) \times F(n)$};
-\node () at (6.5,0) {$\cong$};
+\node () at (6.5,0) {$\stackrel{\phi_{h_1,h_2}}{\cong}$};
 \node () at (8.5,0) {$\cong$};
@@
 The associator for horizontal composition
-%$\alpha \colon \odot (\odot \times 1) \Rightarrow \odot (1 \times \odot)$ 
 is formed as follows: for three composable horizontal 1-cells $M_1=(a\to m_1\leftarrow b,x_1\in F(m_1))$, $M_2=(b\to m_2\leftarrow c,x_2\in F(m_2))$ and $M_3=(c\to m_3\leftarrow d,x_3\in F(m_3)),$
-%\[
-%\begin{tikzpicture}[scale=1.5]
-%\node (A) at (0,0) {$M_1=a$};
-%\node (B) at (1,0) {$m_1$};
-%\node (C) at (2,0) {$b$};
-%\node (D) at (1,-0.5) {$x_1 \in F(m_1)$};
-%\node (E) at (3,0) {$M_2=b$};
-%\node (F) at (4,0) {$m_2$};
-%\node (G) at (5,0) {$c$};
-%\node (H) at (4,-0.5) {$x_2 \in F(m_2)$};
-%\node (I) at (6,0) {$M_3=c$};
-%\node (J) at (7,0) {$m_3$};
-%\node (K) at (8,0) {$d$};
-%\node (L) at (7,-0.5) {$x_3 \in F(m_3)$};
-%\path[->,font=\scriptsize,>=angle 90]
-%(A) edge node[above]{$i$} (B)
-%(C) edge node[above]{$o$} (B)
-%(E) edge node[above]{$i'$} (F)
-%(G) edge node[above]{$o'$} (F)
-%(I) edge node[above]{$i''$} (J)
-%(K) edge node[above]{$o''$} (J);
-%\end{tikzpicture}
-%\]
 the isomorphism $(M_3\odot M_2)\odot M_1\cong M_3\odot (M_2\odot M_1)$ is the isomorphism of cospans 
@@
 \]
-{\chris Old version
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$a$};
-\node (A') at (0,-0.5) {$a$};
-\node (B) at (1.5,0.5) {$(m_1+_{b} m_2)+_{c} m_3$};
-\node (C) at (3,0.5) {$d$};
-\node (C') at (3,-0.5) {$d$};
-\node (D) at (1.5,-0.5) {$m_1+_{b}(m_2 +_{c} m_3)$};
-\node (E) at (5.5,0.5) {$(x_3 \odot x_2) \odot x_1 \in F((m_1+_{b} m_2)+_{c} m_3)$};
-\node (F) at (5.5,-0.5) {$x_3 \odot (x_2 \odot x_1) \in F(m_1+_{b} (m_2 +_{c} m_3))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$$} (B)
-(C) edge node[above]{$$} (B)
-(A) edge node[left]{$1_a$} (A')
-(C) edge node[right]{$1_d$} (C')
-(A') edge node {$$} (D)
-(C') edge node {$$} (D)
-(B) edge node [left] {$\stackrel{\kappa}{\cong}$} (D);
-\end{tikzpicture}
-\]}
 together with an isomorphism $F(\kappa)((x_3 \odot x_2) \odot x_1) \cong (x_3 \odot (x_2 \odot x_1))$ between the decorations 
-%\begin{align*}
-%\scalebox{.8}{$\one\xrightarrow{x_1\times x_2}F(m_1)\times F(m_2)\xrightarrow{\phi}F(m_1+m_2)\to F(m_1+_bm_2)\xrightarrow{1\times x_3}F(m_1+_bm_2)\times %F(m_3)\xrightarrow{\phi}F((m_1+_bm_2)+m_3)$}&\scalebox{.8}{$\to F((m_1+_bm_2)+_cm_3)$} \\
-%&\scalebox{.8}{$\stackrel{F(\alpha)}{\cong} F(m_1+_b(m_2+_cm_3))$} \\
-%\scalebox{.8}{$\one\xrightarrow{x_2\times x_3}F(m_2)\times F(m_3)\xrightarrow{\phi}F(m_2+m_3)\to F(m_2+_cm_3)\xrightarrow{x_1\times1}F(m_1)\times %F(m_2+_cm_3)\xrightarrow{\phi}F(m_1\times(m_2+_cm_3))$}&\scalebox{.8}{$\to F(m_1+_b(m_2+_cm_3))$}
-%\end{align*}
 \begin{equation}\label{eq:decoiso}
-\scalebox{.8}
+\scalebox{.7}
 {\begin{tikzcd}[ampersand replacement=\&]
@@
 \end{equation}
-{\chris Old version
-\begin{displaymath}
-\begin{tikzpicture}[scale=1.7,baseline=(current bounding box.center)]
-\node (A) at (3.75,0) {$\scriptstyle{\cong}$};
-\node (D) at (3,0) {$\scriptstyle{\one}$};
-\node (E) at (6.25,0.5) {$\scriptstyle{F(m_1 + m_2) \times F(m_3)}$};
-\node () at (6,0) {$\scriptstyle\stackrel{\cref{eq:omega}}{\cong}$};
-\node () at (9.5,0) {$\scriptstyle\cong$};
-%\node () at (8.75,0) {$\cong$};
-\node (E') at (6.25,-0.5) {$\scriptstyle{F(m_1) \times F(m_2 + m_3)}$};
-\node (B) at (8,0.5) {$\scriptstyle{F((m_1 + m_2) + m_3)}$};
-\node (B') at (8,-0.5) {$\scriptstyle{F(m_1 + (m_2 + m_3))}$};
-\node (C) at (9.5,0.5) {$\scriptstyle{F((m_1+_b m_2)+m_3)}$};
-\node (C') at (9.5,-0.5) {$\scriptstyle{F(m_1 + (m_2+_c m_3))}$};
-\node (F) at (11,0.5) {$\scriptstyle{F((m_1+_b m_2)+_c m_3)}$};
-\node (F') at (11,-0.5) {$\scriptstyle{F(m_1+_b(m_2+_c m_3))}$};
-\node (G) at (4.25,0.5) {$\scriptstyle{(F(m_1) \times F(m_2)) \times F(m_3)}$};
-\node (G') at (4.25,-0.5) {$\scriptstyle{F(m_1) \times (F(m_2) \times F(m_3))}$};
-\node (M) at (3.25,0.3) {$\scriptstyle{(x_1 \times x_2) \times x_3}$};
-\node (M') at (3.25,-0.3) {$\scriptstyle{x_1 \times (x_2 \times x_3)}$};
-\path[->,font=\scriptsize,>=angle 90]
-(B) edge node [above] {} (B')
-(C) edge node [above] {} (F)
-(C') edge node [above] {} (F')
-(F) edge node [right] {$F(\kappa)$} (F')
-(E) edge node [above] {$\phi_{m_1+m_2,m_3}$} (B)
-(E') edge node [above] {$\phi_{m_1,m_2+m_3}$} (B')
-(B) edge node [above] {} (C)
-(B') edge node [above] {} (C')
-%(C) edge node  [fill=white] {$F(h_1 +_g h_2)$} (C')
-%(B) edge node [fill=white] {$F(h_1 + h_2)$} (B')
-(G) edge node [above] {$\phi_{m_1,m_2} {\times} 1$} (E)
-(G') edge node [above] {$1 {\times} \phi_{m_2,m_3}$} (E')
-(G) edge node [fill=white] {$a$} (G')
-(D) edge node [left,above] {$$} (G)
-(D) edge node [below] {$$} (G');
-%(E) edge node [fill=white] {$F(h_1) \times F(h_2)$} (E');
-\end{tikzpicture}
-\end{displaymath}}
-%%% Christina: I erased tau, and also Fpsi because they were not accurate and those arrows are OK to understand - the universal maps from a 'smaller' colimit to a 'bigger' one.
-If we kept Fpsi's we should write them like F(psi+1) for the first arrow at the top, and that would make the whole thing a bit heavier.
 where $a$ are the associators of $\Cat$ and $\A$ and $\kappa$ is the canonical isomorphism between two colimits of the same diagram in $\A$.

### 2020-12-16 cospans.tex
small edits and reply to Kenny

@@
 \node (E) at (5.5,0.5) {$F(m) \times F(n)$};
-\node () at (6.5,0) {$\stackrel{\phi_{h_1,h_2}}{\cong}$};
+\node () at (6.5,0) {$\cong$};%{$\stackrel{\phi_{h_1,h_2}}{\cong}$};
 \node () at (8.5,0) {$\cong$};
@@
 \end{comment}
-\begin{displaymath}
+\begin{equation}\label{eq:monoidalunitFCsp}
 I_1=\left(0\xrightarrow{!}0\xleftarrow{!}0, \one \xrightarrow{\phi_0}F(0)\right)
-\end{displaymath}
+\end{equation}
 where $0$ is the initial object in $\A$. Notice that this unit $I_1$ is (isomorphic to) $U_0$ as required. The associator is formed as follows: for three objects
@@
 describes the construction of the adjunction from the original $F$.
-Explicitly, the left adjoint picks the initial object in the fiber $L(a)=(a,\bot_a)$, also expressed as $F(!_a)\circ\phi_0(*)$ according to \cref{eq:explicitstructure1} for $(\phi,\phi_0)$ the monoidal structure of $F$.
+Explicitly, the left adjoint picks the initial object in the fiber $L(a)=(a,\bot_a)$, which is expressed as $F(!_a)\circ\phi_0(*)$ according to \cref{eq:explicitstructure1} for $(\phi,\phi_0)$ the monoidal structure of $F$.
 %There are many laris, one for each choice of initial object.
 Having fixed our choice of colimits, there is really only one lari, correct?
-Also, is that ``also...'' part used anywhere?
 
@@
 OR HELPFUL?
-Could omit.}
-
-{\chris Kenny, I am a bit confused with all the units and monoidal units around.
-Could you go through in detail, and phrase correctly, the following part?
-Following the definition of a monoidal double functors and related structures precisely?
-For example, shouldn't we start from the monoidal unit of structured cospans?
-How do you write that?}
-Moreover, the monoidal unit for the category of arrows of $F\lCsp$ is $0_\A\xrightarrow{\raisebox{-3pt}[0pt][0pt]{$=$}}0_\A\xleftarrow{\raisebox{-3pt}[0pt][0pt]{$=$}}0_\A$ with the trivial decoration $\phi_0\maps \one\to F(0_A)\to F(0_A)$,
-which is an initial object and as such isomorphic to $0_{F(0)}$
-%=\lE((0_A,)\xrightarrow{\raisebox{-3pt}[0pt][0pt]{$=$}}(0_A,\phi_0)\xleftarrow{\raisebox{-3pt}[0pt][0pt]{$=$}}(0_A,\phi_0))$
-again by \cref{eq:explicitstructure2}.
+Could omit.} We thus constructed isomorphism $\lE(M)\otimes\lE(M')\cong\lE(M\otimes M')$ for any $M,M'$.
+
+Moreover, the monoidal unit for the category of arrows of $F\lCsp$ is \cref{eq:monoidalunitFCsp}, given by the identity cospan $0_\A \rightarrow 0_\A \leftarrow 0_\A$ on the monoidal unit of $\A$ together with the trivial decoration $\bot_{0_\A} = \phi_0 \colon 1 \to F(0_\A)$ on $0_\A$, and the monoidal unit for the category of arrows of ${ _L \lCsp(\inta F)}$ is given by $(0_\A,\bot_{0_\A}) \rightarrow (0_\A,\bot_{0_\A}) \leftarrow (0_\A,\bot_{0_\A})$.
+This is mapped under $\lE$ again to the identity cospan on $0_\A$ with the trivial decoration on its apex, so that the structure map %$I_{F\lCsp_1}\to\lE(I_{{_L \lCsp (\int F)}_1})$
+$I\to\lE(I)$ is the identity.
+
 It can be verified that with the above structure, $\lE_1$ is also a symmetric monoidal functor, and the rest of the axioms of \cref{defn:monoidal_double_functor} hold.
-
-\textbf{Kenny: This is what I would say regarding the monoidal units:} Moreover, the monoidal unit $I_{F\lCsp}$ for the category of arrows of $F\lCsp$ is given by the identity cospan $0_\A \rightarrow 0_\A \leftarrow 0_\A$ on the monoidal unit of $\A$ together with the trivial decoration $\bot_{0_\A} = \phi_0 \colon 1 \to F(0_\A)$ on $0_\A$, and the monoidal unit $I_{{_L \lCsp(\int F)}}$ for the category of arrows of ${ _L \lCsp(\int F)}$ is given by $(0_\A,\bot_{0_\A}) \rightarrow (0_\A,\bot_{0_\A}) \leftarrow (0_\A,\bot_{0_\A})$, with $\lE(I_{{ _L \lCsp(\int F)}})$ also being given by the identity cospan on $0_\A$ with the trivial decoration on its apex so that the transformation $\theta_U \colon I_{F\lCsp} \to \lE \circ I_{{_L \lCsp (\int F)}}$ is an identity.
 \end{proof}
@@
 %%% Kenny: How about I instead of 1?
+%%% Christina: Sure but I was NOT in the definition of symmetric monoidal double category above...could you streamline??
 \noindent
 Unpacking this definition, one obtains a number of diagrams which can be found after \cite[Definition 2.14]{HS}.
+{\chris Also, could we expand this definition in terms of the functors $\lF_0$ and $\lF_1$ as we usually do?}
 

### 2020-12-16 cospans.tex
colimit argument for associativity of monoidal structure of E

@@
 \end{displaymath}
-Notice that both sides above express a coproduct in the Grothendieck category $\inta F$ by formulas \cref{eq:fibrewisecoprod,eq:explicitstructure2},  so this isomorphism is in the canonical unique one that commutes with the respective cocones.
-{\chris IS THIS CLEAR?
-OR HELPFUL?
-Could omit.} We thus constructed isomorphism $\lE(M)\otimes\lE(M')\cong\lE(M\otimes M')$ for any $M,M'$.
+We thus constructed isomorphisms $\lE(M)\otimes\lE(M')\cong\lE(M\otimes M')$ for any $M,M'$.
+Notice that both sides in the diagram above, combined with the same object $(m+m')$ in $\A$, express a coproduct in the Grothendieck category $\inta F$ by formulas \cref{eq:fibrewisecoprod,eq:explicitstructure2}.
+Therefore the pasted isomorphism is the canonical unique one that commutes with the respective cocones.
+This is useful when checking associativity for example: there is only one such isomorphism $\lE(M)\otimes\lE(M')\otimes\lE(M'')\simrightarrow\lE(M\ot M'\ot M'')$ for any three structured cospans.
 

### 2020-12-16 cospans.tex
small changes

--- 2020-12-16 cospans.tex
@@
 % in LaTeX
-% 2020/12/16
+% 2020/12/15
 
@@
 \node (E) at (5.5,0.5) {$F(m) \times F(n)$};
-\node () at (6.5,0) {$\stackrel{\phi_{h_1,h_2}}{\cong}$};
+\node () at (6.5,0) {$\cong$};
 \node () at (8.5,0) {$\cong$};
@@
 The associator for horizontal composition
+%$\alpha \colon \odot (\odot \times 1) \Rightarrow \odot (1 \times \odot)$ 
 is formed as follows: for three composable horizontal 1-cells $M_1=(a\to m_1\leftarrow b,x_1\in F(m_1))$, $M_2=(b\to m_2\leftarrow c,x_2\in F(m_2))$ and $M_3=(c\to m_3\leftarrow d,x_3\in F(m_3)),$
+%\[
+%\begin{tikzpicture}[scale=1.5]
+%\node (A) at (0,0) {$M_1=a$};
+%\node (B) at (1,0) {$m_1$};
+%\node (C) at (2,0) {$b$};
+%\node (D) at (1,-0.5) {$x_1 \in F(m_1)$};
+%\node (E) at (3,0) {$M_2=b$};
+%\node (F) at (4,0) {$m_2$};
+%\node (G) at (5,0) {$c$};
+%\node (H) at (4,-0.5) {$x_2 \in F(m_2)$};
+%\node (I) at (6,0) {$M_3=c$};
+%\node (J) at (7,0) {$m_3$};
+%\node (K) at (8,0) {$d$};
+%\node (L) at (7,-0.5) {$x_3 \in F(m_3)$};
+%\path[->,font=\scriptsize,>=angle 90]
+%(A) edge node[above]{$i$} (B)
+%(C) edge node[above]{$o$} (B)
+%(E) edge node[above]{$i'$} (F)
+%(G) edge node[above]{$o'$} (F)
+%(I) edge node[above]{$i''$} (J)
+%(K) edge node[above]{$o''$} (J);
+%\end{tikzpicture}
+%\]
 the isomorphism $(M_3\odot M_2)\odot M_1\cong M_3\odot (M_2\odot M_1)$ is the isomorphism of cospans 
@@
 \]
+{\chris Old version
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0.5) {$a$};
+\node (A') at (0,-0.5) {$a$};
+\node (B) at (1.5,0.5) {$(m_1+_{b} m_2)+_{c} m_3$};
+\node (C) at (3,0.5) {$d$};
+\node (C') at (3,-0.5) {$d$};
+\node (D) at (1.5,-0.5) {$m_1+_{b}(m_2 +_{c} m_3)$};
+\node (E) at (5.5,0.5) {$(x_3 \odot x_2) \odot x_1 \in F((m_1+_{b} m_2)+_{c} m_3)$};
+\node (F) at (5.5,-0.5) {$x_3 \odot (x_2 \odot x_1) \in F(m_1+_{b} (m_2 +_{c} m_3))$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$$} (B)
+(C) edge node[above]{$$} (B)
+(A) edge node[left]{$1_a$} (A')
+(C) edge node[right]{$1_d$} (C')
+(A') edge node {$$} (D)
+(C') edge node {$$} (D)
+(B) edge node [left] {$\stackrel{\kappa}{\cong}$} (D);
+\end{tikzpicture}
+\]}
 together with an isomorphism $F(\kappa)((x_3 \odot x_2) \odot x_1) \cong (x_3 \odot (x_2 \odot x_1))$ between the decorations 
+%\begin{align*}
+%\scalebox{.8}{$\one\xrightarrow{x_1\times x_2}F(m_1)\times F(m_2)\xrightarrow{\phi}F(m_1+m_2)\to F(m_1+_bm_2)\xrightarrow{1\times x_3}F(m_1+_bm_2)\times %F(m_3)\xrightarrow{\phi}F((m_1+_bm_2)+m_3)$}&\scalebox{.8}{$\to F((m_1+_bm_2)+_cm_3)$} \\
+%&\scalebox{.8}{$\stackrel{F(\alpha)}{\cong} F(m_1+_b(m_2+_cm_3))$} \\
+%\scalebox{.8}{$\one\xrightarrow{x_2\times x_3}F(m_2)\times F(m_3)\xrightarrow{\phi}F(m_2+m_3)\to F(m_2+_cm_3)\xrightarrow{x_1\times1}F(m_1)\times %F(m_2+_cm_3)\xrightarrow{\phi}F(m_1\times(m_2+_cm_3))$}&\scalebox{.8}{$\to F(m_1+_b(m_2+_cm_3))$}
+%\end{align*}
 \begin{equation}\label{eq:decoiso}
-\scalebox{.7}
+\scalebox{.8}
 {\begin{tikzcd}[ampersand replacement=\&]
@@
 \end{equation}
+{\chris Old version
+\begin{displaymath}
+\begin{tikzpicture}[scale=1.7,baseline=(current bounding box.center)]
+\node (A) at (3.75,0) {$\scriptstyle{\cong}$};
+\node (D) at (3,0) {$\scriptstyle{\one}$};
+\node (E) at (6.25,0.5) {$\scriptstyle{F(m_1 + m_2) \times F(m_3)}$};
+\node () at (6,0) {$\scriptstyle\stackrel{\cref{eq:omega}}{\cong}$};
+\node () at (9.5,0) {$\scriptstyle\cong$};
+%\node () at (8.75,0) {$\cong$};
+\node (E') at (6.25,-0.5) {$\scriptstyle{F(m_1) \times F(m_2 + m_3)}$};
+\node (B) at (8,0.5) {$\scriptstyle{F((m_1 + m_2) + m_3)}$};
+\node (B') at (8,-0.5) {$\scriptstyle{F(m_1 + (m_2 + m_3))}$};
+\node (C) at (9.5,0.5) {$\scriptstyle{F((m_1+_b m_2)+m_3)}$};
+\node (C') at (9.5,-0.5) {$\scriptstyle{F(m_1 + (m_2+_c m_3))}$};
+\node (F) at (11,0.5) {$\scriptstyle{F((m_1+_b m_2)+_c m_3)}$};
+\node (F') at (11,-0.5) {$\scriptstyle{F(m_1+_b(m_2+_c m_3))}$};
+\node (G) at (4.25,0.5) {$\scriptstyle{(F(m_1) \times F(m_2)) \times F(m_3)}$};
+\node (G') at (4.25,-0.5) {$\scriptstyle{F(m_1) \times (F(m_2) \times F(m_3))}$};
+\node (M) at (3.25,0.3) {$\scriptstyle{(x_1 \times x_2) \times x_3}$};
+\node (M') at (3.25,-0.3) {$\scriptstyle{x_1 \times (x_2 \times x_3)}$};
+\path[->,font=\scriptsize,>=angle 90]
+(B) edge node [above] {} (B')
+(C) edge node [above] {} (F)
+(C') edge node [above] {} (F')
+(F) edge node [right] {$F(\kappa)$} (F')
+(E) edge node [above] {$\phi_{m_1+m_2,m_3}$} (B)
+(E') edge node [above] {$\phi_{m_1,m_2+m_3}$} (B')
+(B) edge node [above] {} (C)
+(B') edge node [above] {} (C')
+%(C) edge node  [fill=white] {$F(h_1 +_g h_2)$} (C')
+%(B) edge node [fill=white] {$F(h_1 + h_2)$} (B')
+(G) edge node [above] {$\phi_{m_1,m_2} {\times} 1$} (E)
+(G') edge node [above] {$1 {\times} \phi_{m_2,m_3}$} (E')
+(G) edge node [fill=white] {$a$} (G')
+(D) edge node [left,above] {$$} (G)
+(D) edge node [below] {$$} (G');
+%(E) edge node [fill=white] {$F(h_1) \times F(h_2)$} (E');
+\end{tikzpicture}
+\end{displaymath}}
+%%% Christina: I erased tau, and also Fpsi because they were not accurate and those arrows are OK to understand - the universal maps from a 'smaller' colimit to a 'bigger' one.
+If we kept Fpsi's we should write them like F(psi+1) for the first arrow at the top, and that would make the whole thing a bit heavier.
 where $a$ are the associators of $\Cat$ and $\A$ and $\kappa$ is the canonical isomorphism between two colimits of the same diagram in $\A$.
@@
 It can be verified with this structure, $F\lCsp$ is indeed a symmetric monoidal double category, namely all coherence laws are satisfied.
-The details can be found in \cite[Theorem 4.1.3]{CourserThesis}, but in order to give the reader a sense of what these checks entail, we provide an explicit proof of the fact that the braiding is a transformation of double categories in \cref{eq:proofofaxiom}.
+In order to give the reader a sense of what these checks entail, we provide an explicit proof of the fact that the braiding is a transformation of double categories in \cref{eq:proofofaxiom}.
 \end{proof}
-
-%The remaining properties are coherence laws that make use of these maps $\chi$ and $\mu$, the previously defined symmetric monoidal structure maps $\alpha,\lambda,\rho$ and $\beta$ and the double category structure functors $U$ and $\odot$.
-We exhibit one of these laws to give the reader a sense of how they are verified, with more details available in the second author's thesis \cite{CourserThesis}.
 

### 2020-12-16 cospans.tex
tiny but important leftover

@@
 We thus constructed isomorphisms $\lE(M)\otimes\lE(M')\cong\lE(M\otimes M')$ for any $M,M'$.
-Notice that both sides in the diagram above, combined with the same object $(m+m')$ in $\A$, express a coproduct in the Grothendieck category $\inta F$ by formulas \cref{eq:fibrewisecoprod,eq:explicitstructure2}.
+Notice that both sides in the diagram above, combined with the same object $m+m'$ in $\A$, express a coproduct in the Grothendieck category $\inta F$ by formulas \cref{eq:fibrewisecoprod,eq:explicitstructure2}.
 Therefore the pasted isomorphism is the canonical unique one that commutes with the respective cocones.

### 2020-12-16 cospans.tex
changed \oplus to \otimes (for decorations)

--- 2020-12-16 cospans.tex
@@
 a_1+a_2\ar[ur,"i_1+i_2"] && b_1+b_2,\ar[ul,"o_1+o_2"']
-\end{tikzcd}\qquad x_1\oplus x_2:=\one \xrightarrow{x_1\times x_2}F(m_1)\times F(m_2)\xrightarrow{\phi_{m_1,m_2}}F(m_1+m_2)
+\end{tikzcd}\qquad x_1\otimes x_2:=\one \xrightarrow{x_1\times x_2}F(m_1)\times F(m_2)\xrightarrow{\phi_{m_1,m_2}}F(m_1+m_2)
 \end{equation}
@@
 \node (D) at (2.25,-0.5) {$m_1+(m_2+m_3)$};
-\node (E) at (7,0.5) {$(x_1\oplus x_2)\oplus x_3 \in F((m_1{+}m_2){+}m_3)$};
-%{$\scriptstyle\phi_{m_1{+}m_2,m_3}(\phi_{m_1,m_2}(x_1,x_2),x_3) \in F((m_1{+}m_2){+}m_3)$};
-\node (F) at (7,-0.5) {$x_1\oplus (x_2\oplus x_3)\in F(m_1{+}(m_2{+}m_3))$};
-%{$\scriptstyle\phi_{m_1,m_2{+}m_3}(x_1,\phi_{m_2,m_3}(x_2,x_3))  \in F(m_1{+}(m_2{+}m_3))$};
+\node (E) at (7,0.5) {$(x_1 \otimes x_2) \otimes x_3 \in F((m_1{+}m_2){+}m_3)$};
+\node (F) at (7,-0.5) {$x_1 \otimes (x_2 \otimes x_3)\in F(m_1{+}(m_2{+}m_3))$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-%%% Christina: I earlier dropped notation x+y for decorations because + is already overused and I find it potentially misleading for the reader. I hope the new symbol is OK?
-together with the decoration isomorphism between $F(\alpha)((x_1\oplus x_2)\oplus x_3)\stackrel{\cref{eq:tensordecoration}}{=}F(\alpha)(\phi_{m_1{+}m_2,m_3}(\phi_{m_1,m_2}(x_1,x_2),x_3))$ and $x_1\oplus(x_2\oplus x_3)=\phi_{m_1,m_2{+}m_3}(x_1,\phi_{m_2,m_3}(x_2,x_3))$ formed in the same way as the left two-piece part of \cref{eq:decoiso}.
+together with the decoration isomorphism between $F(\alpha)((x_1 \otimes x_2) \otimes x_3)\stackrel{\cref{eq:tensordecoration}}{=}F(\alpha)(\phi_{m_1{+}m_2,m_3}(\phi_{m_1,m_2}(x_1,x_2),x_3))$ and $x_1 \otimes (x_2 \otimes x_3)=\phi_{m_1,m_2{+}m_3}(x_1,\phi_{m_2,m_3}(x_2,x_3))$ formed in the same way as the left two-piece part of \cref{eq:decoiso}.
 \begin{comment}
@@
 %\node (D) at (2,-0.5) {$m_2+m_1$};
-%\node (E) at (6,0.5) {$x_1\oplus x_2 \in F(m_1+m_2)$};
-%\node (F) at (6,-0.5) {$x_2\oplus x_1 \in F(m_2+m_1)$};
+%\node (E) at (6,0.5) {$x_1 \otimes x_2 \in F(m_1+m_2)$};
+%\node (F) at (6,-0.5) {$x_2 \otimes x_1 \in F(m_2+m_1)$};
 %\path[->,font=\scriptsize,>=angle 90]
@@
 \scalebox{.8}{\begin{tikzcd}[ampersand replacement=\&,column sep=.5in]
-\one \ar[ddrr,dashed,"{(x_2\oplus y_2)\odot(x_1\oplus y_1)}"']\ar[r,"x_1{\times}y_1{\times}x_2{\times}y_2"] \& F(m_1){\times}F(n_1){\times}F(m_2){\times}F(n_2)\ar[r,"\phi_{m_1,n_1}\times\phi_{m_2,n_2}"] \& F(m_1{+}n_1){\times}F(m_2{+}n_2) \ar[d,"\phi_{m_1+n_1,m_2+n_2}"] \\
+\one \ar[ddrr,dashed,"{(x_2 \otimes y_2)\odot(x_1 \otimes y_1)}"']\ar[r,"x_1{\times}y_1{\times}x_2{\times}y_2"] \& F(m_1){\times}F(n_1){\times}F(m_2){\times}F(n_2)\ar[r,"\phi_{m_1,n_1}\times\phi_{m_2,n_2}"] \& F(m_1{+}n_1){\times}F(m_2{+}n_2) \ar[d,"\phi_{m_1+n_1,m_2+n_2}"] \\
 \&\& F(m_1+n_1+m_2+n_2)\ar[d,"F\psi"] \\
@@
  \scalebox{.8}{\begin{tikzcd}[ampersand replacement=\&,column sep=.4in]
-\one \ar[ddrr,dashed,"{(x_2\odot x_1)\oplus(y_2\odot y_1)}"']\ar[r,"x_1{\times}x_2{\times}y_1{\times}y_2"] \& F(m_1){\times}F(m_2){\times}F(n_1){\times}F(n_2)\ar[r,"\phi_{m_1,m_2}\times\phi_{n_1,n_2}"] \& F(m_1{+}m_2){\times}F(n_1{+}n_2) \ar[d, "F\psi\times F\psi"] \\
+\one \ar[ddrr,dashed,"{(x_2\odot x_1) \otimes (y_2\odot y_1)}"']\ar[r,"x_1{\times}x_2{\times}y_1{\times}y_2"] \& F(m_1){\times}F(m_2){\times}F(n_1){\times}F(n_2)\ar[r,"\phi_{m_1,m_2}\times\phi_{n_1,n_2}"] \& F(m_1{+}m_2){\times}F(n_1{+}n_2) \ar[d, "F\psi\times F\psi"] \\
 \&\& F(m_1+_bm_2)\times F(n_1+_{b'}n_2)\ar[d,"\phi_{m_1+_bm_2,n_1+_{b'}n_2}"] \\
@@
 			\node (b) at (1,0) {$(m_1+n_1) +_{(b+b')} (m_2+n_2)$};
-			\node (c) at (8,0) {$ (x_1\oplus y_1)\odot (x_2\oplus y_2)  \in F((m_1+n_1)+_{b+b'}(m_2+n_2))$};
+			\node (c) at (8,0) {$ (x_1 \otimes y_1) \odot (x_2 \otimes y_2)  \in F((m_1+n_1)+_{b+b'}(m_2+n_2))$};
 %			\node (a2) at (-4,1) {$a'+a$};
 			\node (b2) at (1,1) {$(n_1+m_1) +_{(b'+b)} (n_2+m_2)$};
-			\node (c2) at (8,1) {$(y_1\oplus x_1)\odot(y_2\oplus x_2) \in F((n_1+m_1)+_{b'+b}(n_2+m_2))$};
+			\node (c2) at (8,1) {$(y_1\otimes x_1) \odot (y_2 \otimes x_2) \in F((n_1+m_1)+_{b'+b}(n_2+m_2))$};
 %                            \node (a3) at (-4,2) {$a'+a$};
 			\node (b3) at (1,2) {$(n_1 +_{b'} n_2) + (m_1 +_b m_2)$};
-			\node (c3) at (8,2) {$(y_1 \odot y_2) \oplus (x_1 \odot x_2) \in F((n_1+_{b'} n_2)+(m_1+_b m_2))$};
+			\node (c3) at (8,2) {$(y_1 \odot y_2) \otimes (x_1 \odot x_2) \in F((n_1+_{b'} n_2)+(m_1+_b m_2))$};
 %                                \node (a5) at (-4,-1) {$a+a'$};
 			\node (b5) at (1,-1) {$(m_1+_b m_2) + (n_1+_{b'} n_2)$};
-			\node (c5) at (8,-1) {$(x_1 \odot x_2) \oplus (y_1 \odot y_2) \in F((m_1+_b m_2)+(n_1+_{b'} n_2))$};
+			\node (c5) at (8,-1) {$(x_1 \odot x_2) \otimes (y_1 \odot y_2) \in F((m_1+_b m_2)+(n_1+_{b'} n_2))$};
 %                                \node (a6) at (-4,-2) {$a'+a$};
 			\node (b6) at (1,-2) {$(n_1 +_{b'} n_2) + (m_1 +_b m_2)$};
-			\node (c6) at (8,-2) {$(y_1 \odot y_2) \oplus (x_1 \odot x_2) \in F((n_1+_{b'} n_2)+(m_1+_b m_2))$};
+			\node (c6) at (8,-2) {$(y_1 \odot y_2) \otimes (x_1 \odot x_2) \in F((n_1+_{b'} n_2)+(m_1+_b m_2))$};
 			\path[->,font=\scriptsize,>=angle 90]
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$\tau_1 \colon F(\beta +_\beta \beta)((x_1\oplus y_1)\odot(x_2\oplus y_2)) \to (y_1\oplus x_1)\odot(y_2\oplus x_2)$};
-\node (B) at (0,-.5) {$\tau_2 \colon F(\hat{\chi})((y_1 \oplus x_1)\odot(y_2 \oplus x_2)) \to (y_1\odot y_2) \oplus (x_1\odot x_2)$};
-\node (C) at (0,-1) {$\tau_3 \colon F(\hat{\chi})((x_1 \oplus y_1)\odot(x_2 \oplus y_2)) \to (x_1\odot x_2) \oplus (y_1\odot y_2)$};
-\node (D) at (0,-1.5) {$\tau_4 \colon F(\beta)((x_1\odot x_2)\oplus(y_1\odot y_2)) \to (y_1\odot y_2)\oplus(x_1\odot x_2)$};
+\node (A) at (0,0) {$\tau_1 \colon F(\beta +_\beta \beta)((x_1 \otimes y_1)\odot(x_2\otimes y_2)) \to (y_1 \otimes x_1) \odot (y_2 \otimes x_2)$};
+\node (B) at (0,-.5) {$\tau_2 \colon F(\hat{\chi})((y_1 \otimes x_1)\odot(y_2 \otimes x_2)) \to (y_1 \odot y_2) \otimes (x_1 \odot x_2)$};
+\node (C) at (0,-1) {$\tau_3 \colon F(\hat{\chi})((x_1 \otimes y_1)\odot(x_2 \otimes y_2)) \to (x_1 \odot x_2) \otimes (y_1 \odot y_2)$};
+\node (D) at (0,-1.5) {$\tau_4 \colon F(\beta)((x_1\odot x_2)\otimes(y_1\odot y_2)) \to (y_1\odot y_2) \otimes (x_1\odot x_2)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \begin{displaymath}
-\scalebox{.8}{$F(\beta\hat{\chi})((x_1 \oplus y_1)\odot(x_2 \oplus y_2))\cong F(\beta)(F\hat{\chi})((x_1 \oplus y_1)\odot(x_2 \oplus y_2))\xrightarrow{F(\beta)(\tau_3)}F(\beta)((x_1\odot x_2) \oplus (y_1\odot y_2))\xrightarrow{\tau_4}(y_1 \odot y_2) \oplus (x_1 \odot x_2)$}
+\scalebox{.8}{$F(\beta\hat{\chi})((x_1 \otimes y_1)\odot(x_2 \otimes y_2))\cong F(\beta)(F\hat{\chi})((x_1 \otimes y_1)\odot(x_2 \otimes y_2))\xrightarrow{F(\beta)(\tau_3)}F(\beta)((x_1\odot x_2) \otimes (y_1\odot y_2))\xrightarrow{\tau_4}(y_1 \odot y_2) \otimes (x_1 \odot x_2)$}
 \end{displaymath}
@@
 \begin{displaymath}
-\scalebox{.8}{$F(\hat{\chi}(\beta +_\beta \beta))( (x_1 \oplus y_1)\odot (x_2 \oplus y_2))\cong F(\hat{\chi})F(\beta +_\beta \beta)( (x_1 \oplus y_1)\odot (x_2 \oplus y_2)) \xrightarrow{F(\hat{\chi})(\tau_1)}F(\hat{\chi})(y_1\oplus x_1)\odot(y_2\oplus x_2)\xrightarrow{\tau_2}(y_1 \odot y_2) \oplus (x_1 \odot x_2)$}
+\scalebox{.8}{$F(\hat{\chi}(\beta +_\beta \beta))( (x_1 \otimes y_1)\odot (x_2 \otimes y_2))\cong F(\hat{\chi})F(\beta +_\beta \beta)( (x_1 \otimes y_1)\odot (x_2 \otimes y_2)) \xrightarrow{F(\hat{\chi})(\tau_1)}F(\hat{\chi})(y_1\otimes x_1)\odot(y_2\otimes x_2)\xrightarrow{\tau_2}(y_1 \odot y_2) \otimes (x_1 \odot x_2)$}
 \end{displaymath}
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$F(\hat{\chi} (\beta \odot \beta))((x_1 \oplus y_1)\odot(x_2 \oplus y_2))$};
-\node (B) at (4,0) {$F(\hat{\chi})((y_1 \oplus x_1)\odot(y_2 \oplus x_2))$};
-\node (C) at (0,-1) {$F(\beta)((x_1\odot x_2) \oplus (y_1 \odot y_2))$};
-\node (D) at (4,-1) {$(y_1\odot y_2) \oplus (x_1\odot x_2)$};
+\node (A) at (0,0) {$F(\hat{\chi} (\beta \odot \beta))((x_1 \otimes y_1)\odot(x_2 \otimes y_2))$};
+\node (B) at (4,0) {$F(\hat{\chi})((y_1 \otimes x_1)\odot(y_2 \otimes x_2))$};
+\node (C) at (0,-1) {$F(\beta)((x_1\odot x_2) \otimes (y_1 \odot y_2))$};
+\node (D) at (4,-1) {$(y_1\odot y_2) \otimes (x_1\odot x_2)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-where in the top left corner, we note that $$F(\hat{\chi} (\beta \odot \beta))((x_1 \oplus y_1)\odot(x_2 \oplus y_2)) = F(\beta\hat{\chi})((x_1 \oplus y_1)\odot (x_2 \oplus y_2))$$
+where in the top left corner, we note that $$F(\hat{\chi} (\beta \odot \beta))((x_1 \otimes y_1)\odot(x_2 \otimes y_2)) = F(\beta\hat{\chi})((x_1 \otimes y_1)\odot (x_2 \otimes y_2))$$
 as the above diagram of maps of cospans commutes in $\A$ and then applying the pseudofunctor $F$ to this diagram yields a commutative diagram in $\Cat$. 

### 2020-12-16 cospans.tex
updated refs on double categories

@@
 For double categories we follow the notation of our paper on structured cospans \cite{BC}, which in turn follows that of Hansen and Shulman \cite{HS,Shulman2010}.
+Our double categories are always `pseudo' double categories, where composition of horizontal 1-cells is unital and associative only up to coherent isomorphism \cite{GP1,GP2,Shulman2008}.
 
@@
 
-%\bibitem{GP1} M.\ Grandis and R.\ Par\'e, Limits in double categories, \textsl{Cah.\ Top.\ G\'eom.\ Diff.} \textbf{40} (1999), 162--220.
-
-%\bibitem{GP2} M.\ Grandis and R.\ Par\'e, Adjoints for double categories, 
-% \textsl{Cah.\ Top.\ G\'eom.\ Diff.} \textbf{45} (2004), 193--240.
+\bibitem{GP1} M.\ Grandis and R.\ Par\'e, Limits in double categories, \textsl{Cah.\ Top.\ G\'eom.\ Diff.} \textbf{40} (1999), 162--220.
+
+\bibitem{GP2} M.\ Grandis and R.\ Par\'e, Adjoints for double categories, 
+ \textsl{Cah.\ Top.\ G\'eom.\ Diff.} \textbf{45} (2004), 193--240.
 

### 2020-12-17 cospans.tex
tiny

@@
 Vertical composition in our double categories is strictly associative, while horizontal composition need not be.
+{\chris Could we add a small sentence that our convention for monoidal categories will be $(\mathsf{V},\otimes)$ omitting the unit?}
 
@@
 describes the construction of the adjunction from the original $F$.
-Explicitly, the left adjoint picks the initial object in the fiber $L(a)=(a,\bot_a)$, which is expressed as $F(!_a)\circ\phi_0(*)$ according to \cref{eq:explicitstructure1} for $(\phi,\phi_0)$ the monoidal structure of $F$.
-%There are many laris, one for each choice of initial object.
+Explicitly, the left adjoint picks the initial object in the fiber of $a$, namely $L(a)=(a,\bot_a)$ which is expressed as $F(!_a)\circ\phi_0(*)$ according to \cref{eq:explicitstructure1} for $(\phi,\phi_0)$ the monoidal structure of $F$.
+%%% There are many laris, one for each choice of initial object.
 Having fixed our choice of colimits, there is really only one lari, correct?

### 2020-12-17 cospans.tex
changed date on top of file
changes in big diagrams on pp. 13-14, and text after second one.

@@
 % in LaTeX
-% 2020/12/16
+% 2020/12/17
 
@@
 Similarly the right and left unitors can be constructed, and all data satisfy the axioms of a double category---essentially breaking down to those of the cospan double category of $\A$ and axioms of the lax monoidal pseudofunctor $F$.
-For full details of these arguments, see \cite[Theorem~4.1.1]{CourserThesis}.
+For details of these arguments, see \cite[Theorem~4.1.1]{CourserThesis}.
 \end{proof}
@@
 \one \ar[ddrr,dashed,"{(x_2 \otimes y_2)\odot(x_1 \otimes y_1)}"']\ar[r,"x_1{\times}y_1{\times}x_2{\times}y_2"] \& F(m_1){\times}F(n_1){\times}F(m_2){\times}F(n_2)\ar[r,"\phi_{m_1,n_1}\times\phi_{m_2,n_2}"] \& F(m_1{+}n_1){\times}F(m_2{+}n_2) \ar[d,"\phi_{m_1+n_1,m_2+n_2}"] \\
-\&\& F(m_1+n_1+m_2+n_2)\ar[d,"F\psi"] \\
+\&\& F(m_1+n_1+m_2+n_2)\ar[d,"F(\psi)"] \\
 \&\& F((m_1+n_1)+_{b+b'}(m_2+n_2))
@@
  \scalebox{.8}{\begin{tikzcd}[ampersand replacement=\&,column sep=.4in]
-\one \ar[ddrr,dashed,"{(x_2\odot x_1) \otimes (y_2\odot y_1)}"']\ar[r,"x_1{\times}x_2{\times}y_1{\times}y_2"] \& F(m_1){\times}F(m_2){\times}F(n_1){\times}F(n_2)\ar[r,"\phi_{m_1,m_2}\times\phi_{n_1,n_2}"] \& F(m_1{+}m_2){\times}F(n_1{+}n_2) \ar[d, "F\psi\times F\psi"] \\
+\one \ar[ddrr,dashed,"{(x_2\odot x_1) \otimes (y_2\odot y_1)}"']\ar[r,"x_1{\times}x_2{\times}y_1{\times}y_2"] \& F(m_1){\times}F(m_2){\times}F(n_1){\times}F(n_2)\ar[r,"\phi_{m_1,m_2}\times\phi_{n_1,n_2}"] \& F(m_1{+}m_2){\times}F(n_1{+}n_2) \ar[d, "F(\psi) \times F(\psi)"] \\
 \&\& F(m_1+_bm_2)\times F(n_1+_{b'}n_2)\ar[d,"\phi_{m_1+_bm_2,n_1+_{b'}n_2}"] \\
@@
  \scalebox{.75}{\begin{tikzcd}[ampersand replacement=\&,column sep=.3in,row sep=.1in]
-\& F(m_1)\times F(n_1)\times F(m_2)\times F(n_2)\ar[dd,"1\times\beta\times1"']\ar[ddrr,phantom,"\stackrel{\cref{eq:thetaa}}{\cong}"]\ar[rr,"\phi_{m_1,n_1}\times\phi_{m_2,n_2}"] \&\& F(m_1+n_1)\times F(m_2+n_2)\ar[rr,"\phi_{m_1+n_1,m_2+n_2}"] \&\& F(m_1+n_1+m_2+n_2)\ar[dd,"F\psi"]\ar[ddll,"F(1+\beta+1)"'] \\
+\& F(m_1)\times F(n_1)\times F(m_2)\times F(n_2)\ar[dd,"1\times\beta\times1"']\ar[ddrr,phantom,"\stackrel{\cref{eq:thetaa}}{\cong}"]\ar[rr,"\phi_{m_1,n_1}\times\phi_{m_2,n_2}"] \&\& F(m_1+n_1)\times F(m_2+n_2)\ar[rr,"\phi_{m_1+n_1,m_2+n_2}"] \&\& F(m_1+n_1+m_2+n_2)\ar[dd,"F(\psi)"]\ar[ddll,"F(1+\beta+1)"'] \\
 \one \ar[ur,"{x_1\times y_1\times x_2\times y_2}"]\ar[dr,"{x_1\times x_2\times y_1\times y_2}"'] \&\&\&\& \\
@@
 \end{equation}
-where the left-hand side isomorphism combines pseudoassociativity \cref{eq:omega} and braided monoidal structure \cref{eq:braidedpseudofun} of the pseudofunctor $F$ as seen in detail in the appendix, and the right hand side follows from the universal property of colimits and pseudofunctoriality of $F$.
-Similarly, for units $U_{a+b}$ and $U_a\ot U_b$ it is easy to see that as cospans they are both the identity $1_{a+b}:a+b\to a+b\leftarrow a+b:1_{a+b}$, and there is a canonical isomorphism between their trivial decorations \cref{eq:UFCsp}, namely $F(!_{a+b})\phi_0\cong\phi_{a,b}(F(!_a)\times F(!_b))(\phi_0\times\phi_0)$ via the structure isomorphisms for $(\phi,\phi_0)$.
+where the left-hand side isomorphism combines the pseudoassociativity \cref{eq:omega} and braided monoidal structure \cref{eq:braidedpseudofun} of the pseudofunctor $F$ as seen in detail in the appendix, and the right hand side follows from the universal property of colimits and pseudofunctoriality of $F$.
+Similarly, for the units $U_{a+b}$ and $U_a\ot U_b$ it is easy to see that as cospans they are both the identity $1_{a+b} \maps a+b\to a+b\leftarrow a+b:1_{a+b}$, and there is a canonical isomorphism between their trivial decorations \cref{eq:UFCsp}, namely $F(!_{a+b})\phi_0\cong\phi_{a,b}(F(!_a)\times F(!_b))(\phi_0\times\phi_0)$ via the structure isomorphisms for $(\phi,\phi_0)$.
 \begin{comment}
@@
 Under $\lE$ this is mapped to the underlying $\A$-cospan $\cspn{a}{m+_bn}{b}{}{}$ with decoration $F(v_m)x+F(v_n)y$ in the fiber $F(m+_bn)$, since a pushout over an initial object is really a coproduct.
-That decoration is isomorphic to that of \cref{eq:1} due to the following diagram
+This decoration has a canonical isomorphism to that of \cref{eq:1} due to the following diagram
 \begin{equation}\label{eq:isomorphismdiag}
@@
 F(m)\times F(n)\ar[rr,"\phi_{m,n}"]\ar[d,"F(v_m)\times F(v_n)"']\ar[dr,phantom,"\cong"] && F(m+n)\ar[d,"F(\psi)"]\ar[d,bend right=50, phantom,"\cong"']\ar[dl,"F(v_m+v_n)"description] \\
-F(m+_bn)\times F(m+_bn)\ar[r,"\phi_{m+_bn,m+_bn}"']\ar[rr,dashed,bend right=15] & F\left((m+_bn)+(m+_bn)\right)\ar[r,"F(\nabla)"'] & F(m+_bn)
+F(m+_bn)\times F(m+_bn)\ar[r,"\phi_{m+_bn,m+_bn}"'] & F\left((m+_bn)+(m+_bn)\right)\ar[r,"F(\nabla)"'] & F(m+_bn)
  \end{tikzcd}
 \end{equation}
-where the dashed bottom composite is the fiberwise coproduct in $F(m+_bn)$ as in \cref{eq:explicitstructure1}.
-The left-hand side isomorphism is \cref{eq:pseudonaturality} from pseudonaturality of $\phi$ whereas the right-hand side isomorphism follows from universal properties and pseudofunctoriality of $F$.
+where the composite of the bottom two arrows is the coproduct $+ \maps F(m+_bn) \times F(m+_bn) \to F(m+_bn)$ as in \cref{eq:explicitstructure1}.
+The left-hand isomorphism arises from the pseudonaturality of $\phi$ as in \cref{eq:pseudonaturality}, whereas the right-hand isomorphism follows from universal properties and the pseudofunctoriality of $F$.
 Regarding identities, the identity horizontal 1-cell $U_m$ in $_L\lCsp(\inta F)$ is $\cspn{(m,\bot_m)}{(m,\bot_m)}{(m,\bot_m)}{}{}$ with $1_m$ as the $A$-component and isomorphisms between initial objects in the fibers.
@@
 \end{align*}
-The cospan part is equal, whereas we have an isomorphism between the decorations $F(\iota_m)x+F(\iota_{m'})x'\cong \phi_{m,m'}(x,x')$ in an analogous way to \cref{eq:isomorphismdiag} as follows
+The cospan part is equal, whereas we have an isomorphism between the decorations, $F(\iota_m)x+F(\iota_{m'})x'\cong \phi_{m,m'}(x,x')$, given in an analogous way to \cref{eq:isomorphismdiag} as follows:
 \begin{displaymath}
@@
 F(m)\times F(m')\ar[rr,"\phi_{m,m'}"]\ar[d,"F(i_m)\times F(i_{m'})"']\ar[dr,phantom,"\stackrel{\cref{eq:pseudonaturality}}{\cong}"] && F(m+m')\ar[d,equal]\ar[d,bend right=50, phantom,"\cong"']\ar[dl,"F(i_m+i_{m'})"description] \\
-F(m+m')\times F(m+m')\ar[r,"\phi_{m+m',m+m'}"']\ar[rr,dashed,bend right=15] & F\left((m+m')+(m+m')\right)\ar[r,"F(\nabla)"'] & F(m+m')
+F(m+m')\times F(m+m')\ar[r,"\phi_{m+m',m+m'}"'] & F\left((m+m')+(m+m')\right)\ar[r,"F(\nabla)"'] & F(m+m')
  \end{tikzcd}
 \end{displaymath}
-We thus constructed isomorphisms $\lE(M)\otimes\lE(M')\cong\lE(M\otimes M')$ for any $M,M'$.
+where the composite of the bottom two arrows is the coproduct operation in $F(m+m')$.
+We thus have constructed an isomorphism $\lE(M)\otimes\lE(M') \simrightarrow \lE(M\otimes M')$ for each $M,M'$.
 Notice that both sides in the diagram above, combined with the same object $m+m'$ in $\A$, express a coproduct in the Grothendieck category $\inta F$ by formulas \cref{eq:fibrewisecoprod,eq:explicitstructure2}.
-Therefore the pasted isomorphism is the canonical unique one that commutes with the respective cocones.
+Therefore the isomorphism $F(\iota_m)x+F(\iota_{m'})x '\cong \phi_{m,m'}(x,x')$ given by this diagram is the unique one that commutes with the respective cocones.
 This is useful when checking associativity for example: there is only one such isomorphism $\lE(M)\otimes\lE(M')\otimes\lE(M'')\simrightarrow\lE(M\ot M'\ot M'')$ for any three structured cospans.

### 2020-12-18 cospans.tex
added a paragraph after the proof of Theorem 2.2

@@
 It can be verified with this structure, $F\lCsp$ is indeed a symmetric monoidal double category, namely all coherence laws are satisfied.
-In order to give the reader a sense of what these checks entail, we provide an explicit proof of the fact that the braiding is a transformation of double categories in \cref{eq:proofofaxiom}.
+In order to give the reader a sense of what these checks entail, we provide a proof of the fact that the braiding is a transformation of double categories in \cref{eq:proofofaxiom}.
 \end{proof}
+
+There is a much simpler proof of the above theorem when the hypothesis of \cref{thm:equiv} hold.
+In this case we show, in the proof of that theorem, that the decorated cospan double category $F \lCsp$ is isomorphic to a certain double category ${}_L \lCsp(\inta  F)$ constructed using \emph{structured} cospans.
+We also show that under this isomorphism, all the symmetric monoidal structure of $F \lCsp$---the tensor product, associator, etc.---matches that for  ${}_L \lCsp(\inta  F)$, which we have shown independently obeys the axioms of symmetric monoidal double category (see \cref{thm:SC}).
+It follows that $F \lCsp$ is a symmetric monoidal category.
 

### 2020-12-18 cospans.tex
specified the appendix, and cleared some unused text

@@
 \end{equation}
-%$M_1$ and $M_2$:
-%\[
-%\begin{tikzpicture}[scale=1.5]
-%\node (A) at (0,0) {$a_1$};
-%\node (B) at (1,0) {$m_1$};
-%\node (C) at (2,0) {$b_1$};
-%\node (D) at (1,-0.5) {$x_1 \in F(m_1)$};
-%\node (E) at (3,0) {$a_2$};
-%\node (F) at (4,0) {$m_2$};
-%\node (G) at (5,0) {$b_2$};
-%\node (H) at (4,-0.5) {$x_2 \in F(m_2)$};
-%\path[->,font=\scriptsize,>=angle 90]
-%(A) edge node[above]{$i_1$} (B)
-%(C) edge node[above]{$o_1$} (B)
-%(E) edge node[above]{$i_2$} (F)
-%(G) edge node[above]{$o_2$} (F);
-%\end{tikzpicture}
-%\]
-%is the horizontal 1-cell $M_1 \otimes M_2$:
-%\[
-%\begin{tikzpicture}[scale=1.5]
-%\node (A) at (0,0) {$a_1+a_2$};
-%\node (B) at (1.5,0) {$m_1+m_2$};
-%\node (C) at (3,0) {$b_1+b_2$};
-%\node (D) at (4.55,0) {$x_1+x_2 \in F(m_1+m_2)$};
-%\path[->,font=\scriptsize,>=angle 90]
-%(A) edge node[above]{$i_1+i_2$} (B)
-%(C) edge node[above]{$o_1+o_2$} (B);
-%\end{tikzpicture}
-%\]
-%\begin{equation}
-%x_1+x_2 \mapseqq 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{x_1 \times x_2} F(m_1) \times F(m_2) \xrightarrow{\phi_{m_1,m_2}} F(m_1+m_2)
-%\end{equation}
 
@@
 \begin{proof}
-%We must show that both the category of objects $F\lCsp_0$ and the category of arrows $F\lCsp_1$ are symmetric monoidal categories, show that the monoidal unit of $F\lCsp_0$ is preserved by the unit functor $U$, show that the source and target functors $S,T \colon F\lCsp_1 \to F\lCsp_0$ are strict symmetric monoidal functors which preserve the associativity and unit constraints, define the globular isomorphisms $\chi$ and $\mu$ that relate how composition and units interact with the tensor product, and check that the required axioms are satisfied.
 We first show that the categories of objects and arrows are symmetric monoidal, and that the source and target functors are symmetric strict monoidal.
@@
 $F\lCsp_1$ is also symmetric monoidal, with tensor product as in \cref{eq:tensordecoration} and monoidal unit
-\begin{comment}
-The category of arrows $F\lCsp_1$ has:
-\begin{enumerate}
-\item{objects as $F$-decorated cospans, which are pairs:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$(a$};
-\node (B) at (1,0) {$m$};
-\node (C) at (2,0) {$b,$};
-\node (D) at (2.6,0) {$x \in F(m))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i$} (B)
-(C) edge node[above]{$o$} (B);
-\end{tikzpicture}
-\]
-and}
-\item{morphisms as maps of $F$-decorated cospans, which are cospans in $\A$
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$a$};
-\node (A') at (0,-0.5) {$a'$};
-\node (B) at (1,0.5) {$m$};
-\node (C) at (2,0.5) {$b$};
-\node (C') at (2,-0.5) {$b'$};
-\node (D) at (1,-0.5) {$m'$};
-\node (E) at (3,0.5) {$x \in F(m)$};
-\node (F) at (3,-0.5) {$x' \in F(m')$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i$} (B)
-(C) edge node[above]{$o$} (B)
-(A) edge node[left]{$f$} (A')
-(C) edge node[right]{$g$} (C')
-(A') edge node [above]{$i'$} (D)
-(C') edge node [above]{$o'$} (D)
-(B) edge node [left] {$h$} (D);
-\end{tikzpicture}
-\]
-together with a decoration morphism $\tau \maps F(h)(x) \to x'$.
-}
-\end{enumerate}
-First we define the tensor product and monoidal unit of $F\lCsp_1$. Given two objects $M_1$ and $M_2$ of $F\lCsp_1$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a_1$};
-\node (B) at (1,0) {$m_1$};
-\node (C) at (2,0) {$b_1$};
-\node (D) at (1,-0.5) {$x_1 \in F(m_1)$};
-\node (E) at (3,0) {$a_2$};
-\node (F) at (4,0) {$m_2$};
-\node (G) at (5,0) {$b_2$};
-\node (H) at (4,-0.5) {$x_2 \in F(m_2)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i_1$} (B)
-(C) edge node[above]{$o_1$} (B)
-(E) edge node[above]{$i_2$} (F)
-(G) edge node[above]{$o_2$} (F);
-\end{tikzpicture}
-\]
-their tensor product $M_1 \otimes M_2$ is given by taking the coproducts of the cospans in $\A$
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a_1+a_2$};
-\node (B) at (1.5,0) {$m_1+m_2$};
-\node (C) at (3,0) {$b_1+b_2$};
-\node (D) at (4.55,0) {$x_1+x_2 \in F(m_1+m_2)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i_1+i_2$} (B)
-(C) edge node[above]{$o_1+o_2$} (B);
-\end{tikzpicture}
-\]
-where the decoration on the apex is obtained using the natural transformation of the symmetric lax monoidal pseudofunctor $F$: $$x_1+x_2 \mapseqq 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{x_1 \times x_2} F(m_1) \times F(m_2) \xrightarrow{\phi_{m_1,m_2}} F(m_1+m_2).$$
-The monoidal unit $0_{F\lCsp_1}$ is given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$0$};
-\node (B) at (1,0) {$0$};
-\node (C) at (2,0) {$0,$};
-\node (D) at (3,0) {\bot_0 = \phi \in F(0)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$!$} (B)
-(C) edge node[above]{$!$} (B);
-\end{tikzpicture}
-\]
-\end{comment}
 \begin{equation}\label{eq:monoidalunitFCsp}
@@
 $M_1=(a_1\to m_1\leftarrow b_1,x_1\in F(m_1))$, $M_2=(a_2\to m_2\leftarrow b_2,x_2\in F(m_2))$ and $M_3=(a_3\to m_3\leftarrow b_3,x_3\in F(m_3),$
-%\[
-%\begin{tikzpicture}[scale=1.5]
-%\node (A) at (0,0) {$a_1$};
-%\node (B) at (1,0) {$m_1$};
-%\node (C) at (2,0) {$b_1$};
-%\node (D) at (1,-0.5) {$x_1 \in F(m_1)$};
-%\node (E) at (3,0) {$a_2$};
-%\node (F) at (4,0) {$m_2$};
-%\node (G) at (5,0) {$b_2$};
-%\node (H) at (4,-0.5) {$x_2 \in F(m_2)$};
-%\node (I) at (6,0) {$a_3$};
-%\node (J) at (7,0) {$m_3$};
-%\node (K) at (8,0) {$b_3$};
-%\node (L) at (7,-0.5) {$x_3 \in F(m_3)$};
-%\path[->,font=\scriptsize,>=angle 90]
-%(A) edge node[above]{$i_1$} (B)
-%(C) edge node[above]{$o_1$} (B)
-%(E) edge node[above]{$i_2$} (F)
-%(G) edge node[above]{$o_2$} (F)
-%(I) edge node[above]{$i_3$} (J)
-%(K) edge node[above]{$o_3$} (J);
-%\end{tikzpicture}
-%\]
 the isomorphism $(M_1\ot M_2)\ot M_3\cong M_1\ot(M_2\ot M_3)$ is the isomorphism of cospans
@@
 together with the decoration isomorphism between $F(\alpha)((x_1 \otimes x_2) \otimes x_3)\stackrel{\cref{eq:tensordecoration}}{=}F(\alpha)(\phi_{m_1{+}m_2,m_3}(\phi_{m_1,m_2}(x_1,x_2),x_3))$ and $x_1 \otimes (x_2 \otimes x_3)=\phi_{m_1,m_2{+}m_3}(x_1,\phi_{m_2,m_3}(x_2,x_3))$ formed in the same way as the left two-piece part of \cref{eq:decoiso}.
-\begin{comment}
-tensoring the first two and then the third results in $(M_1 \otimes M_2) \otimes M_3$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$(a_1+a_2)+a_3$};
-\node (B) at (2.5,0){$(m_1+m_2)+m_3$};
-\node (C) at (5,0) {$(b_1+b_2)+b_3$};
-\node (D) at (2.5,-0.5) {$(x_1+x_2)+x_3 \in F((m_1+m_2)+m_3)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$(i_1+i_2)+i_3$} (B)
-(C) edge node[above]{$(o_1+o_2)+o_3$} (B);
-\end{tikzpicture}
-\]
-where $(x_1+x_2)+x_3 \maps 1 \to F((m_1+m_2)+m_3)$ is the composite
-\[  1 \xrightarrow{(x_1 \times x_2) \times x_3} (F(m_1) \times F(m_2)) \times F(m_3) \xrightarrow{\phi_{m_1,m_2} \times 1} F(m_1+m_2) \times F(m_3) \xrightarrow{\phi_{m_1+m_2,m_3}} F((m_1+m_2)+m_3).\]
-The other parenthesization $M_1 \otimes (M_2 \otimes M_3)$ is given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a_1+(a_2+a_3)$};
-\node (B) at (2.5,0) {$m_1+(m_2+m_3)$};
-\node (C) at (5,0) {$b_1+(b_2+b_3)$};
-\node (D) at (2.5,-0.5) {$x_1+(x_2+x_3) \in F(m_1+(m_2+m_3))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i_1+(i_2+i_3)$} (B)
-(C) edge node[above]{$o_1+(o_2+o_3)$} (B);
-\end{tikzpicture}
-\]
-where $x_1+(x_2+x_3) \maps 1 \to F(m_1+(m_2+m_3))$ is the composite
-\[  1 \xrightarrow{x_1 \times (x_2 \times x_3)} F(m_1) \times (F(m_2) \times F(m_3)) \xrightarrow{1 \times \phi_{m_2,m_3}} F(m_1) \times F(m_2+m_3) \xrightarrow{\phi_{m_1,m_2+m_3}} F(m_1+(m_2+m_3)).\]
-Denoting the associator of $(\A,+)$ by $\alpha$, the associator of $F\lCsp_1$ is then a map of cospans in $\A$ from $(M_1 \otimes M_2) \otimes M_3$ to $M_1 \otimes (M_2 \otimes M_3)$ given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$(a_1+a_2)+a_3$};
-\node (A') at (0,-0.5) {$a_1+(a_2+a_3)$};
-\node (B) at (2.25,0.5) {$(m_1+m_2)+m_3$};
-\node (C) at (4.5,0.5) {$(b_1+b_2)+b_3$};
-\node (C') at (4.5,-0.5) {$b_1+(b_2+b_3)$};
-\node (D) at (2.25,-0.5) {$m_1+(m_2+m_3)$};
-\node (E) at (7,0.5) {$(x_1+x_2)+x_3 \in F((m_1+m_2)+m_3)$};
-\node (F) at (7,-0.5) {$x_1+(x_2+x_3) \in F(m_1+(m_2+m_3))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$(i_1+i_2)+i_3$} (B)
-(C) edge node[above]{$(o_1+o_2)+o_3$} (B)
-(A) edge node[left]{$\alpha$} (A')
-(C) edge node[right]{$\alpha$} (C')
-(A') edge node [above]{$i_1+(i_2+i_3)$} (D)
-(C') edge node [above]{$o_1+(o_2+o_3)$} (D)
-(B) edge node [left] {$\alpha$} (D);
-\end{tikzpicture}
-\]
-together with the decoration isomorphism $\tau_\alpha \maps F(\alpha)((x_1+x_2)+x_3) \to x_1+(x_2+x_3)$.
-\end{comment}
 For the left and right unitors $I_1\ot M\cong M\cong M\ot I_1$ for any $M=(a\to m\leftarrow b,x\in F(m)$, we have span isomorphisms
@@
 with isomorphisms between decorations precisely given by \cref{eq:unitality}.
-\begin{comment}
-For the left unitor, we first compute $0_{F\lCsp_1} \otimes M$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$0$};
-\node (B) at (1,0) {$0$};
-\node (C) at (2,0) {$0$};
-\node (D) at (1,-0.5) {$\bot_0 \in F(0)$};
-\node (E) at (3,0) {$a$};
-\node (F) at (4,0) {$m$};
-\node (G) at (5,0) {$b$};
-\node (H) at (4,-0.5) {$x \in F(m)$};
-\node (I) at (2.5,0) {$\otimes$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$!$} (B)
-(C) edge node[above]{$!$} (B)
-(E) edge node[above]{$i$} (F)
-(G) edge node[above]{$o$} (F);
-\end{tikzpicture}
-\]
-which results in:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$0+a$};
-\node (B) at (1,0) {$0+m$};
-\node (C) at (2,0) {$0+b$};
-\node (D) at (3.5,0) {$\bot_0 + x \in F(0+m)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$!+i$} (B)
-(C) edge node[above]{$!+o$} (B);
-\end{tikzpicture}
-\]
-where $\bot_0 + x \in F(0+m)$ is given by $$1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{\bot_0 \times x} F(0) \times F(m) \xrightarrow{\phi_{0,m}} F(0+m).$$Denoting the left unitor of $(\A,+,0)$ by $\ell$, the left unitor of $F\lCsp_1$ is then an isomorphism in $F\lCsp_1$ given by the following map of cospans in $\A$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$0+a$};
-\node (A') at (0,-0.5) {$a$};
-\node (B) at (1,0.5) {$0+m$};
-\node (C) at (2,0.5) {$0+b$};
-\node (C') at (2,-0.5) {$b$};
-\node (D) at (1,-0.5) {$m$};
-\node (E) at (3.5,0.5) {$\bot_0 + x \in F(0+m)$};
-\node (F) at (3.5,-0.5) {$x \in F(m)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$!+i$} (B)
-(C) edge node[above]{$!+o$} (B)
-(A) edge node[left]{$\ell$} (A')
-(C) edge node[right]{$\ell$} (C')
-(A') edge node [above]{$i$} (D)
-(C') edge node [above]{$o$} (D)
-(B) edge node [left] {$\ell$} (D);
-\end{tikzpicture}
-\]
-together with the decoration isomorphism $\tau_{\ell} \maps F(\ell)(\bot_0 + x) \to x$.
-The right unitor is similar, and one can check that the associator and left and right unitors together satisfy the pentagon and triangle identities of a monoidal category.
-See the second author's thesis \cite{CourserThesis} for more details.
-\end{comment}
 Finally, the symmetric monoidal structure of $F\lCsp_1$ is inherited from that in $\A$ and $F$, with braiding $\beta\maps M_1\ot M_2\to M_2\ot M_1$ the cospan isomorphism
-%To finish showing that $F\lCsp_1$ is symmetric monoidal, we next define the braiding of $F\lCsp_1$.
-Given two objects $M_1$ and $M_2$ of $F\lCsp_1$ and denoting the braiding of $(\A,+,0)$ by $\beta$, the braiding $\beta_{M_1,M_2}$ of $F\lCsp_1$ is then a map of cospans in $\A$ from $M_1 \otimes M_2$ to $M_2 \otimes M_1$:
-%\[
-%\begin{tikzpicture}[scale=1.5]
-%\node (A) at (0,0.5) {$a_1+a_2$};
-%\node (A') at (0,-0.5) {$a_2+a_1$};
-%\node (B) at (2,0.5) {$m_1+m_2$};
-%\node (C) at (4,0.5) {$b_1+b_2$};
-%\node (C') at (4,-0.5) {$b_2+b_1$};
-%\node (D) at (2,-0.5) {$m_2+m_1$};
-%\node (E) at (6,0.5) {$x_1 \otimes x_2 \in F(m_1+m_2)$};
-%\node (F) at (6,-0.5) {$x_2 \otimes x_1 \in F(m_2+m_1)$};
-%\path[->,font=\scriptsize,>=angle 90]
-%(A) edge node[above]{$i_1+i_2$} (B)
-%(C) edge node[above]{$o_1+o_2$} (B)
-%(A) edge node[left]{$\stackrel{\beta}{\cong}$} (A')
-%(C) edge node[left]{$\stackrel{\beta}{\cong}$} (C')
-%(A') edge node [above]{$i_2+i_1$} (D)
-%(C') edge node [above]{$o_2+o_1$} (D)
-%(B) edge node [right] {$\stackrel{\beta}{\cong}$} (D);
-%\end{tikzpicture}
-%\]
 \begin{equation}\label{eq:braidingFCsp1}
@@
 \end{equation}
-%$F(\beta)(x_1+x_2) \to x_2+x_1$.
-Note that obtaining the decoration isomorphism $\tau_\beta$ makes use of $F$ being symmetric.
-One can check that the braiding together with the associator satisfy the hexagon equations, and it is clear that $\beta_{M_1,M_2}=\beta_{M_2,M_1}^{-1}$.
-This completes the description of $F\lCsp_1$ as a symmetric monoidal category.
 All axioms for a symmetric monoidal category can be verified, %see \cite[Theorem 4.1.3]{CourserThesis}, 
@@
 \end{equation}
-where the left-hand side isomorphism combines the pseudoassociativity \cref{eq:omega} and braided monoidal structure \cref{eq:braidedpseudofun} of the pseudofunctor $F$ as seen in detail in the appendix, and the right hand side follows from the universal property of colimits and pseudofunctoriality of $F$.
+where the left-hand side isomorphism \cref{eq:thetaa} is spelled out in detail in \cref{eq:proofofaxiom} and combines the pseudoassociativity \cref{eq:omega} and braided monoidal structure \cref{eq:braidedpseudofun} of the pseudofunctor $F$, and the right hand side isomorphism follows from the universal property of colimits and pseudofunctoriality of $F$.
 Similarly, for the units $U_{a+b}$ and $U_a\ot U_b$ it is easy to see that as cospans they are both the identity $1_{a+b} \maps a+b\to a+b\leftarrow a+b:1_{a+b}$, and there is a canonical isomorphism between their trivial decorations \cref{eq:UFCsp}, namely $F(!_{a+b})\phi_0\cong\phi_{a,b}(F(!_a)\times F(!_b))(\phi_0\times\phi_0)$ via the structure isomorphisms for $(\phi,\phi_0)$.
-\begin{comment}
-, the first of which relates the double functor $\otimes$ with the functor $\odot$ and the second of which relates the double functor $\otimes$ with the functor $U$. 
-The latter of these is easy to see: given two objects $a$ and $b$ in $F\lCsp_0=\A$, $\mu$ is given by the identity map of cospans in $\A$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$a+b$};
-\node (A') at (0,-0.5) {$a+b$};
-\node (B) at (2,0.5) {$a+b$};
-\node (C) at (4,0.5) {$a+b$};
-\node (C') at (4,-0.5) {$a+b$};
-\node (D) at (2,-0.5) {$a+b$};
-\node (E) at (5.5,0.5) {$\bot_{a+b} \in F(a+b)$};
-\node (F) at (5.5,-0.5) {$\bot_a + \bot_b \in F(a+b)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$1_{a+b}$} (B)
-(C) edge node[above]{$1_{a+b}$} (B)
-(A) edge node[left]{$1$} (A')
-(C) edge node[right]{$1$} (C')
-(A') edge node [above]{$1_a + 1_b$} (D)
-(C') edge node [above]{$1_a + 1_b$} (D)
-(B) edge node [left] {$1$} (D);
-\end{tikzpicture}
-\]
-together with the decoration isomorphism $\tau_{a,b} \maps \bot_{a+b} \xrightarrow{\sim} \bot_a + \bot_b$ given by the unique map between the two initial objects $\bot_{a+b}$ and $\bot_a + \bot_b$ in $F(a+b)$.
-%%%Christina: we do not have any such information at this point!
-We have not talked about the categories F(a) having finite colimits, and it's not deduced from the assumptions.
-We will show this is the case much later!
-For the former globular 2-morphism $\chi$, we first introduce some notation for objects $M_1,M_2,N_1$ and $N_2$ of $F\lCsp_1$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a$};
-\node (B) at (1,0) {$m_1$};
-\node (C) at (2,0) {$b$};
-\node (D) at (1,-0.5) {$x_1 \in F(m_1)$};
-\node (E) at (3,0) {$b$};
-\node (F) at (4,0) {$m_2$};
-\node (G) at (5,0) {$c$};
-\node (H) at (4,-0.5) {$x_2 \in F(m_2)$};
-\node (I) at (0,-1.5) {$a'$};
-\node (J) at (1,-1.5) {$n_1$};
-\node (K) at (2,-1.5) {$b'$};
-\node (L) at (1,-2) {$y_1 \in F(n_1)$};
-\node (M) at (3,-1.5) {$b'$};
-\node (N) at (4,-1.5) {$n_2$};
-\node (O) at (5,-1.5) {$c'$};
-\node (P) at (4,-2) {$y_2 \in F(n_2)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i_1$} (B)
-(C) edge node[above]{$o_1$} (B)
-(E) edge node[above]{$i_2$} (F)
-(G) edge node[above]{$o_2$} (F)
-(I) edge node[above]{$i_1'$} (J)
-(K) edge node[above]{$o_1'$} (J)
-(M) edge node[above]{$i_2'$} (N)
-(O) edge node[above]{$o_2'$} (N);
-\end{tikzpicture}
-\]
-If we first tensor $M_1$ and $N_1$ as well as $M_2$ and $N_2$ and then compose these two, we obtain $(M_1 \otimes N_1) \odot (M_2 \otimes N_2)$, which is given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a+a'$};
-\node (B) at (2.5,0) {$(m_1+n_1)+_{b+b'}(m_2+n_2)$};
-\node (C) at (5,0) {$c+c'$};
-\node (D) at (2.5,-0.5) {$(x_1+y_1)\odot(x_2+y_2) \in F((m_1+n_1)+_{b+b'}(m_2+n_2))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$\psi j (i_1+i_1')$} (B)
-(C) edge node[above]{$\psi j (o_2 + o_2')$} (B);
-\end{tikzpicture}
-\]
-where the decoration $(x_1+y_1) \odot (x_2+y_2) \in F((m_1+n_1)+_{b+b'}(m_2+n_2))$ is given by
-%$$\scriptscriptstyle{1 \xrightarrow{(\lambda^{-1} \times \lambda^{-1})\lambda^{-1}} (1 \times 1) \times (1 \times 1) \xrightarrow{(x_1 \times y_1) \times (x_2 \times y_2)} (F(m_1) \times F(n_1)) \times (F(m_2) \times F(n_2)) \xrightarrow{\phi_{m_1,n_1} \times \phi_{m_2,n_2}} F(m_1+n_1) \times F(m_2+n_2)} \xrightarrow{\phi_{m_1+n_1,m_2+n_2}} F((m_1+n_1)+(m_2+n_2)) \xrightarrow{F(\psi)} F((m_1+n_1)+_{b+b'}(m_2+n_2))$$
-\[ \scriptstyle{1 \xrightarrow{} (F(m_1) \times F(n_1)) \times (F(m_2) \times F(n_2)) \xrightarrow{\phi_{m_1,n_1} \times \phi_{m_2,n_2}} F(m_1+n_1) \times F(m_2+n_2)} \xrightarrow{\phi_{m_1+n_1,m_2+n_2}} F((m_1+n_1)+(m_2+n_2)) \xrightarrow{F(\psi)} F((m_1+n_1)+_{b+b'}(m_2+n_2)) \]
-where the first arrow is the composite
-\[1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{\lambda^{-1} \times \lambda^{-1}} (1 \times 1) \times (1 \times 1) \xrightarrow{(x_1 \times y_1) \times (x_2 \times y_2)} (F(m_1) \times F(n_1)) \times (F(m_2) \times F(n_2)).
-\]
-%\[
-%\begin{tikzpicture}[scale=1.5]
-%\node (A) at (0,0) {$1$};
-%\node (B) at (0,-1) {$1 \times 1$};
-%\node (C) at (0,-2) {$(1 \times 1) \times (1 \times 1)$};
-%\node (D) at (0,-3) {$(F(m_1) \times F(n_1)) \times (F(m_2) \times F(n_2))$};
-%\node (E) at (0,-4) {$F(m_1+n_1) \times F(m_2+n_2)$};
-%\node (F) at (0,-5) {$F((m_1+n_1)+(m_2+n_2))$};
-%\node (G) at (0,-6) {$F((m_1+n_1)+_{b+b'}(m_2+n_2))$};
-%\path[->,font=\scriptsize,>=angle 90]
-%(A) edge node[left]{$\lambda^{-1}$} (B)
-%(B) edge node[left]{$\lambda^{-1} \times \lambda^{-1}$} (C)
-%(C) edge node[left]{$(x_1 \times y_1) \times (x_2 \times y_2)$} (D)
-%(D) edge node[left]{$\phi_{m_1,n_1} \times \phi_{m_2,n_2}$} (E)
-%(E) edge node[left]{$\phi_{m_1+n_1,m_2+n_2}$} (F)
-%(F) edge node[left]{$F(j_{m_1+n_1,m_2+n_2})$} (G);
-%\end{tikzpicture}
-%\]
-Interchanging the order in which we tensor and compose, we obtain $(M_1 \odot M_2) \otimes (N_1 \odot N_2)$, which is given by:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a+a'$};
-\node (B) at (2.5,0) {$(m_1+_{b} m_2) + (n_1 +_{b'} n_2)$};
-\node (C) at (5,0) {$c+c'$};
-\node (D) at (2.5,-0.5) {$(x_1 \odot x_2) + (y_1 \odot y_2) \in F((m_1+_{b}m_2)+(n_1+_{b'}n_2))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$(\psi j i_1)+(\psi j i_1')$} (B)
-(C) edge node[above]{$(\psi j o_2)+(\psi j o_2')$} (B);
-\end{tikzpicture}
-\]
-where the decoration $(x_1 \odot x_2) + (y_1 \odot y_2) \in F((m_1+_{b}m_2)+(n_1+_{b'}n_2))$ is given by:
-%$$\scriptscriptstyle{1 \xrightarrow{(\lambda^{-1} \times \lambda^{-1})\lambda^{-1}} (1 \times 1) \times (1 \times 1) \xrightarrow{(x_1 \times y_1) \times (x_2 \times y_2)} (F(m_1) \times F(n_1)) \times (F(m_2) \times F(n_2)) \xrightarrow{\phi_{m_1,n_1} \times \phi_{m_2,n_2}} F(m_1+n_1) \times F(m_2+n_2) \xrightarrow{F(\psi) \times F(\psi)} F(m_1 +_b m_2) \times F(n_1+_{b'}n_2) \xrightarrow{\phi_{m_1+_b m_2,n_1+_{b'}n_2}} F((m_1+_b m_2)+(n_1+_{b'}n_2))}$$
-$$\scriptstyle{1 \xrightarrow{} (F(m_1) \times F(n_1)) \times (F(m_2) \times F(n_2)) \xrightarrow{\phi_{m_1,n_1} \times \phi_{m_2,n_2}} F(m_1+n_1) \times F(m_2+n_2) \xrightarrow{F(\psi) \times F(\psi)} F(m_1 +_b m_2) \times F(n_1+_{b'}n_2) \xrightarrow{\phi_{m_1+_b m_2,n_1+_{b'}n_2}} F((m_1+_b m_2)+(n_1+_{b'}n_2))}$$
-with the first arrow being the same as the first arrow in the previous composite.
-%\[
-%\begin{tikzpicture}[scale=1.5]
-%\node (A) at (0,0) {$1$};
-%\node (B) at (0,-1) {$1 \times 1$};
-%\node (C) at (0,-2) {$(1 \times 1) \times (1 \times 1)$};
-%\node (D) at (0,-3) {$(F(m_1) \times F(m_2)) \times (F(n_1) \times F(n_2))$};
-%\node (E) at (0,-4) {$F(m_1+m_2) \times F(n_1+n_2)$};
-%\node (F) at (0,-5) {$F(m_1+_{b}m_2) \times F(n_1+_{b'}n_2)$};
-%\node (G) at (0,-6) {$F((m_1+_{b}m_2)+(n_1+_{b'}n_2))$};
-%\path[->,font=\scriptsize,>=angle 90]
-%(A) edge node[left]{$\lambda^{-1}$} (B)
-%(B) edge node[left]{$\lambda^{-1} \times \lambda^{-1}$} (C)
-%(C) edge node[left]{$(x_1 \times x_2) \times (y_1 \times y_2)$} (D)
-%(D) edge node[left]{$\phi_{m_1,m_2} \times \phi_{n_1,n_2}$} (E)
-%(E) edge node[left]{$F(j_{m_1,m_2}) \times F(j_{n_1,n_2})$} (F)
-%(F) edge node[left]{$\phi_{m_1+_{b}m_2,n_1+_{b'}n_2}$} (G);
-%\end{tikzpicture}
-%\]
-The globular 2-morphism $\chi \colon (M_1 \otimes N_1) \odot (M_2 \otimes N_2) \to (M_1 \odot M_2) \otimes (N_1 \odot N_2)$ is then given by the map of cospans in $\A$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$a+a'$};
-\node (A') at (0,-0.5) {$a+a'$};
-\node (B) at (2.5,0.5) {$(m_1+n_1)+_{b+b'}(m_2+n_2)$};
-\node (C) at (5,0.5) {$c+c'$};
-\node (C') at (5,-0.5) {$c+c'$};
-\node (D) at (2.5,-0.5) {$(m_1+_{b}m_2)+(n_1+_{b'}n_2)$};
-\node (E) at (7.5,0.5) {$\scriptstyle{(x_1+y_1) \odot (x_2+y_2) \in F((m_1+n_1)+_{b+b'}(m_2+n_2))}$};
-\node (F) at (7.5,-0.5) {$\scriptstyle{(x_1 \odot x_2)+(y_1 \odot y_2) \in F((m_1+_{b}m_2)+(n_1+_{b'}n_2))}$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$\psi j(i_1+i_1')$} (B)
-(C) edge node[above]{$\psi j(o_2 + o_2')$} (B)
-(A) edge node[left]{$1$} (A')
-(C) edge node[right]{$1$} (C')
-(A') edge node [above]{$(\psi j i_1')+(\psi j i_1)$} (D)
-(C') edge node [above]{$(\psi j o_2)+(\psi j o_2')$} (D)
-(B) edge node [left] {$\hat{\chi}$} (D);
-\end{tikzpicture}
-\]
-together with decoration isomorphism $\tau_{\chi} \maps F(\hat{\chi})((x_1+y_1)\odot(x_2+y_2)) \to (x_1 \odot x_2)+(y_1 \odot y_2)$
-where $\hat{\chi}$ is the same interchange map $\chi$ for the symmetric double category $\lCsp(\A)$ given by the universal map between the colimit of the same diagram obtained in two different ways.
-This completes the description of the globular 2-morphisms $\chi$ and $\mu$, and the description of all of the structure of the symmetric monoidal double category $F\lCsp$.
-\end{comment}
 

### 2020-12-18 cospans.tex
inclusions into sums are iota
tiny
tweaked comments about \cref{defn:monoidal_double_category} in Theorem 2.2

@@
 % in LaTeX
-% 2020/12/17
+% 2020/12/18
 
@@
 (E) edge node [above] {$o'$} (D)
-(B) edge node [below] {$j_m$} (F)
-(D) edge node [below] {$j_{n}$} (F)
+(B) edge node [below] {$\iota_m$} (F)
+(D) edge node [below] {$\iota_{n}$} (F)
 (B) edge[bend left=10] node [above] {$v_m\;$} (G)
@@
 
-Lastly, according to \cref{defn:monoidal_double_category} we construct two globular 2-isomorphisms $(M_2 \otimes N_2)\odot (M_1 \otimes N_1) \simrightarrow(M_2\odot M_1) \otimes (N_2\odot N_1)$ and $U_{a + b} \simrightarrow U_a \otimes U_b$ that express compatibility of the tensor with horizontal composition and units.
+Lastly, according to \cref{defn:monoidal_double_category} we need to construct two globular 2-isomorphisms $(M_2 \otimes N_2)\odot (M_1 \otimes N_1) \simrightarrow(M_2\odot M_1) \otimes (N_2\odot N_1)$ and $U_{a + b} \simrightarrow U_a \otimes U_b$ that express compatibility of the tensor product with horizontal composition and units.
 For any appropriate four decorated cospans
@@
 We also show that under this isomorphism, all the symmetric monoidal structure of $F \lCsp$---the tensor product, associator, etc.---matches that for  ${}_L \lCsp(\inta  F)$, which we have shown independently obeys the axioms of symmetric monoidal double category (see \cref{thm:SC}).
-It follows that $F \lCsp$ is a symmetric monoidal category.
+It follows that $F \lCsp$ is a symmetric monoidal double category.
 

### 2020-12-18 cospans.tex
explained dashed arrows in equation (5)

@@
 Vertical composition in our double categories is strictly associative, while horizontal composition need not be.
-{\chris Could we add a small sentence that our convention for monoidal categories will be $(\mathsf{V},\otimes)$ omitting the unit?}
+We use $(\C,\otimes)$ to stand for a monoidal or perhaps symmetric monoidal category with $\otimes$ as its tensor product.
 
@@
 together with the decoration morphism $F(f)F(!_a)\phi_0(*)\cong F(!_{a'})\phi_0(*)$.
-Finally, the (horizontal) composition functor $\odot$ maps two composable $F$-decorated cospans $M=\left(a\to m\leftarrow b,x\in F(m)\right),N=\left(b\to n\leftarrow c,y\in F(n)\right)$ to $N\odot M$, which as a cospan is their pushout in $\A$ over their shared foot
+Finally, the (horizonta)l composition functor $\odot$ maps two composable $F$-decorated cospans 
+\[  M=\left(a\to m\leftarrow b,x\in F(m)\right), \qquad N=\left(b\to n\leftarrow c,y\in F(n)\right)\] 
+to $N\odot M$, which as a cospan is their pushout in $\A$ over their shared foot, shown in dashed arrows here:
 \begin{equation}\label{eq:dcospanscomposition}
@@
 equipped with the decoration
-$$y\odot x:= \one\cong\one \times \one \xrightarrow{x \times y} F(m) \times F(n) \xrightarrow{\phi_{m,n}} F(m+n) \xrightarrow{F(\psi)} F(m+_{b}n)$$
+\[  y\odot x:= \one\cong\one \times \one \xrightarrow{x \times y} F(m) \times F(n) \xrightarrow{\phi_{m,n}} F(m+n) \xrightarrow{F(\psi)} F(m+_{b}n) \]
 where $\psi \maps m + n \to m+_{b} n$ is the natural map from the coproduct to the pushout and $\phi_{m,n} \maps F(m) \times F(n) \to F(m+n)$ are the lax monoidal structure maps of $F$.

### 2020-12-18 cospans.tex
changed equation (9) and improved defs of structured and decorated cospan double cats

@@
 \item a horizontal 1-cell is an $F$\define{-decorated cospan}, that is, 
-a cospan in $\A$:
+a diagram in $\A$ of the form
 \[
@@
 \item a 2-morphism is a \define{map of} $F$\define{-decorated cospans}, that is, 
-a map of cospans in $\A$:
+a commutative diagram in $\A$ of the form
 \begin{equation}\label{eq:mapofdec}
@@
 \item of two vertical 1-morphisms $f \maps a \to b$ and $f' \maps a' \to b'$ is $f+f' \maps a+a' \to b+b'$ in $\A$,
-\item of two horizontal 1-cells $(a_1\to m_1\leftarrow b_1,x_1\in F(m_1))$ and $(a_2\to m_2\leftarrow b_2,x_2\in F(m_2))$ is:
+\item of two horizontal 1-cells $(a \to m \leftarrow b ,x \in F(m))$ and $(c \to n \leftarrow d, y\in F(n))$ is
+\begin{equation}\label{eq:tensordecoration}
+\begin{tikzcd}
+& m+n & \\
+a+c\ar[ur,"i_1+i_2"] && b+d,\ar[ul,"o_1+o_2"']
+\end{tikzcd}\qquad x \otimes y:=  \phi_{m,n}(x,y) \in F(m + n) 
+\end{equation}
+
+\begin{comment}
 \begin{equation}\label{eq:tensordecoration}
@@
 \end{equation}
+\end{comment}
 
@@
 \item a vertical 1-morphism is a morphism of $\A$,
-\item a horizontal 1-cell from $a$ to $b$ is a cospan in $\X$ of the form
+\item a horizontal 1-cell from $a$ to $b$ is a \define{$L$-structured cospan}, that is,
+a diagram in $\X$ of the form
 \begin{displaymath}
@@
 \node (B) at (1,0) {$x$};
-\node (C) at (2,0) {$L(b)$};
+\node (C) at (2,0) {$L(b)$,};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \end{displaymath}
-\item a 2-morphism is a map of cospans in $\X$ of the form
+\item a 2-morphism is a \define{map of $L$-structured cospans}, that is, a commutative diagram in $\X$ of the form
 \begin{displaymath}
@@
 \node (B') at (1,-1) {$x'$};
-\node (C') at (2,-1) {$L(b')$};
+\node (C') at (2,-1) {$L(b')$.};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \begin{displaymath}
-\lE=(\lE_0,\lE_1)\maps _L\lCsp(\inta F) \longrightarrow F\lCsp
+\lE=(\lE_0,\lE_1)\maps _L\lCsp(\inta F) \longrightarrow F\lCsp.
 \end{displaymath}
-which on vertical categories acts as the identity $\lE_0 = \id_{\A}$.
-Given a horizontal 1-cell in $_L\lCsp(\inta F)$ as in \cref{eq:scsphor1cell}, $\lE_1$ maps it to the decorated cospan $i\maps a\to m\leftarrow b:o$ with decoration $x\in F(m)$,
-whereas a 2-morphism of $L$-structured cospans as in \cref{eq:2morphismLCspintaF} is mapped to the underlying map of cospans in $\A$
-\begin{displaymath}
+We set $\lE_0$ to be the identity on $\A$, and decree that $\lE_1$ sends any
+$L$-structured cospan as in \cref{eq:scsphor1cell} to the decorated cospan
+$a \xrightarrow{i} m \xleftarrow{o} b$ with decoration $x\in F(m)$, whereas $\lE_1$ sends 
+any map of $L$-structured cospans as in \cref{eq:2morphismLCspintaF} to the
+map of $F$-decorated cospans given by
+\[
 \begin{tikzcd}
@@
 \end{tikzcd}
-\end{displaymath}
-in $\A$ along with the map $\tau\maps Fk(x)\to x'$ in $F(m')$ coming from the middle arrow above, namely an $F$-decorated cospan 2-morphism. 
-With these mappings, $\lE$ is indeed a double functor as in \cref{def:doublefun}.
-First of all, both $\lE_0$ and $\lE_1$ are functors that appropriately commute with sources and targets.
-Moreover, there exist globular 2-isomorphisms $\lE(N) \odot \lE(M) \simrightarrow\lE(N \odot M)$, $U_{\lE m} \simrightarrow\lE(U_m)$
+\]
+along with the morphism of decorations $\tau\maps F(k)(x) \to x'$ in $F(m')$ coming from the middle arrow above.
+We then make $\lE$ into double functor as in \cref{def:doublefun}.
+First, both $\lE_0$ and $\lE_1$ are functors that appropriately commute with sources and targets.
+Second, we equip $\lE$ with globular 2-isomorphisms $\lE(N) \odot \lE(M) \simrightarrow\lE(N \odot M)$, $U_{\lE m} \simrightarrow\lE(U_m)$
 for any pair of composable horizontal 1-cells $M=\cspn{(a,\bot_a)}{(m,x)}{(b,\bot_b)}{}{}$ and $N=\cspn{(b,\bot_b)}{(n,y)}{(c,\bot_c)}{}{}$ and any object $m$ of $_L\lCsp(\inta F)$.
@@
  \end{tikzcd}\qquad
-  \one\xrightarrow{x\times y}F(m)\times F(n)\xrightarrow{\phi_{m,n}}F(m+n)\xrightarrow{F(\psi)}F(m+_bn)
-\end{equation}
-whereas first composing $M$ and $N$ in $_L\lCsp(\inta F)$ using pushouts in $\inta F$ as in \cref{eq:globalpushout} produces 
+  \one\xrightarrow{x\times y}F(m)\times F(n)\xrightarrow{\phi_{m,n}}F(m+n)\xrightarrow{F(\psi)}F(m+_bn).
+\end{equation}
+On the other hand, $N \odot M$ computed as in \cref{eq:globalpushout} is 
 \begin{displaymath}
@@
 where $v_m,v_n$ are the canonical maps into the pushout.
-Under $\lE$ this is mapped to the underlying $\A$-cospan $\cspn{a}{m+_bn}{b}{}{}$ with decoration $F(v_m)x+F(v_n)y$ in the fiber $F(m+_bn)$, since a pushout over an initial object is really a coproduct.
-This decoration has a canonical isomorphism to that of \cref{eq:1} due to the following diagram
+Under $\lE$ this is mapped to the cospan $\cspn{a}{m+_bn}{b}{}{}$ with decoration $F(v_m)x+F(v_n)y$ in the fiber $F(m+_bn)$.
+This decoration is canonically isomorphic to that of \cref{eq:1} due to the following diagram
 \begin{equation}\label{eq:isomorphismdiag}
@@
 The left-hand isomorphism arises from the pseudonaturality of $\phi$ as in \cref{eq:pseudonaturality}, whereas the right-hand isomorphism follows from universal properties and the pseudofunctoriality of $F$.
+Thus, we have a canonical globular 2-isomorphism  $\lE(N) \odot \lE(M) \simrightarrow\lE(N \odot M)$.
 Regarding identities, the identity horizontal 1-cell $U_m$ in $_L\lCsp(\inta F)$ is $\cspn{(m,\bot_m)}{(m,\bot_m)}{(m,\bot_m)}{}{}$ with $1_m$ as the $A$-component and isomorphisms between initial objects in the fibers.

### 2020-12-19 cospans.tex
small change in wording in paragraph after Thm. 2.2

@@
 \begin{comment}
+%old version:
 \begin{equation}\label{eq:tensordecoration}
@@
 In this case we show, in the proof of that theorem, that the decorated cospan double category $F \lCsp$ is isomorphic to a certain double category ${}_L \lCsp(\inta  F)$ constructed using \emph{structured} cospans.
-We also show that under this isomorphism, all the symmetric monoidal structure of $F \lCsp$---the tensor product, associator, etc.---matches that for  ${}_L \lCsp(\inta  F)$, which we have shown independently obeys the axioms of symmetric monoidal double category (see \cref{thm:SC}).
+We also show that under this isomorphism, all the symmetric monoidal structure of $F \lCsp$---the tensor product, associator, etc.---matches that for  ${}_L \lCsp(\inta  F)$, which we have proved to obey the axioms of a symmetric monoidal double category (see \cref{thm:SC}).
 It follows that $F \lCsp$ is a symmetric monoidal double category.
@@
 \item a vertical 1-morphism is a morphism of $\A$,
-\item a horizontal 1-cell from $a$ to $b$ is a \define{$L$-structured cospan}, that is,
+\item a horizontal 1-cell from $a$ to $b$ is an \define{$L$-structured cospan}, that is,
 a diagram in $\X$ of the form
@@
 \end{displaymath}
-We set $\lE_0$ to be the identity on $\A$, and decree that $\lE_1$ sends any
+We set $\lE_0 \maps \A \to \A$ to be the identity, and decree that $\lE_1$ sends any
 $L$-structured cospan as in \cref{eq:scsphor1cell} to the decorated cospan

### 2020-12-19 cospans.tex
tiny compiler fix

@@
 \item a vertical 1-morphism is a morphism of $\A$,
-\item a horizontal 1-cell from $a$ to $b$ is an \define{$L$-structured cospan}, that is,
+\item a horizontal 1-cell from $a$ to $b$ is an $L$-\define{structured cospan}, that is,
 a diagram in $\X$ of the form
@@
 \end{displaymath}
-\item a 2-morphism is a \define{map of $L$-structured cospans}, that is, a commutative diagram in $\X$ of the form
+\item a 2-morphism is a \define{map of} $L$-\define{structured cospans}, that is, a commutative diagram in $\X$ of the form
 \begin{displaymath}

### 2020-12-19 cospans.tex
reworded the infamous Lemma 3.4

@@
 % in LaTeX
-% 2020/12/18
+% 2020/12/19
 
@@
  \item all fibers have $\J$-colimits, and the reindexing functors preserve them;
- \item the total category $\X$ has $\J$-colimits and $U$ strictly preserves them.
+ \item the total category $\X$ has $\J$-colimits, and $U$ preserves them.
 \end{enumerate}
-Moreover, if $\X$ has $\J$-colimits and $U$ preserves them, they can be chosen so that $U$ strictly preserves them.   
+Moreover, if $\X$ has $\J$-colimits and $U$ preserves them, for any choice of $\J$-colimits in $\A$ they can be chosen in $\X$ in such a way that $U$ strictly preserves them.   
 \end{lem}

### 2020-12-21 cospans.tex
tiny change
small edit and addition for universality argument

--- 2020-12-19 cospans.tex
@@
 We thus have constructed an isomorphism $\lE(M)\otimes\lE(M') \simrightarrow \lE(M\otimes M')$ for each $M,M'$. 
-Notice that both sides in the diagram above, combined with the same object $m+m'$ in $\A$, express a coproduct in the Grothendieck category $\inta F$ by formulas \cref{eq:fibrewisecoprod,eq:explicitstructure2}.
-Therefore the isomorphism $F(\iota_m)x+F(\iota_{m'})x '\cong \phi_{m,m'}(x,x')$ given by this diagram is the unique one that commutes with the respective cocones.
-This is useful when checking associativity for example: there is only one such isomorphism $\lE(M)\otimes\lE(M')\otimes\lE(M'')\simrightarrow\lE(M\ot M'\ot M'')$ for any three structured cospans.
+Notice that since the target decoration is part of the sum $\left(m+m',F(\iota_m)x+F(\iota_{m'})x'\right)$ in the Grothendieck category $\inta F$ by \cref{eq:fibrewisecoprod}, this isomorphism we constructured is the canonical such that it commutes with the inclusions into the sum.
+This is useful when checking associativity for example: there is only one such canonical isomorphism $\lE(M)\otimes\lE(M')\otimes\lE(M'')\simrightarrow\lE(M\ot M'\ot M'')$ for any three structured cospans\footnote{A similar argument establishes that there is only one canonical isomorphism $\lE(M)\odot\lE(M')\odot\lE(M'')\to\lE(M\odot M'\odot M'')$ for any three composable structured cospans earlier, since the target decoration of \cref{eq:isomorphismdiag} forms a pushout in the Grothendieck category.}.
 

### 2020-12-21 cospans.tex

@@
 \begin{lem}[\textbf{Hermida}] \label{lem:fibrewiselimits}
-Suppose $\J$ is a small category and $U \maps \X \to \A$ is an opfibration where the base 
-$\A$ has $\J$-colimits.  Then the following are equivalent:
+Suppose $\J$ is a small category and $U \maps \X \to \A$ is an opfibration where the base $\A$ has $\J$-colimits.  Then the following are equivalent:
 \begin{enumerate}
  \item all fibers have $\J$-colimits, and the reindexing functors preserve them;
- \item the total category $\X$ has $\J$-colimits and $U$ strictly preserves them.
+ \item the total category $\X$ has $\J$-colimits, and $U$ preserves them.
 \end{enumerate}
-Moreover, if $\X$ has $\J$-colimits and $U$ preserves them, they can be chosen so that $U$ strictly preserves them.   
+Moreover, if $\X$ has $\J$-colimits and $U$ preserves them, for any choice of $\J$-colimits in $\A$ they can be chosen in $\X$ in such a way that $U$ strictly preserves them.   
 \end{lem}

### 2020-12-22 cospans.tex
a few edits in proof of 3.2, general cleaning up

--- 2020-12-19 cospans.tex
@@
 Via these operations we obtain a symmetric monoidal double category
-%%%Christina: add the notation bb{C}sp(A) since it will be central to what follows?
 with cospans in $\A$ as its horizontal 1-cells \cite{Niefield}.
-%%% Christina: I would be inclined to first cite Niefield and then Courser due to the chronological order.
-%%% Kenny: I think when we \cite{...}, we list the references alphabetically, but let's just cite Niefield here and achieve both.
-%%% Christina: Sounds good!
 
@@
 \end{align*}
-%\[
-%\begin{tikzpicture}[scale=1.5]
-%\node (A) at (0,0) {$a$};
-%\node (B) at (1,0) {$m$};
-%\node (C) at (2,0) {$b$};
-%\node (D) at (1,-0.5) {$x \in F(m)$};
-%\node (E) at (2.75,0) {$\mapsto$};
-%\node (A') at (3.5,0) {$H(a)$};
-%\node (B') at (4.5,0) {$H(m)$};
-%\node (C') at (5.5,0) {$H(b)$};
-%\node (D') at (4.5,-0.5) {$\theta_m E(x) \phi \in F'(H(m))$};
-%\node (F) at (1,0.5) {$M$};
-%\node (G) at (4.5,0.5) {$\lH(M)$};
-%\path[->,font=\scriptsize,>=angle 90]
-%(A) edge node[above]{$i$} (B)
-%(C) edge node[above]{$o$} (B)
-%(A') edge node[above]{$H(i)$} (B')
-%(C') edge node[above]{$H(o)$} (B');
-%\end{tikzpicture}
-%\]
-%where given a decoration $x \colon 1 \to F(m)$ on $m$, we obtain a decoration on $H(m)$ via the composite 
-%\[ 1 \xrightarrow{\phi} E(1) \xrightarrow{E(x)} E(F(m)) \xrightarrow{\theta_m} F'(H(m)).\]
 \item The image of a map of decorated cospans $\alpha \colon M \to N$ in $F\lCsp$ is the map of $F'$-decorated cospans $\lH(\alpha)$ in $F'\lCsp$
@@
 \node (F'') at (8.5,-0.5) {$\theta_n E(x') \phi_0 \in F'(H(n))$};
-%\node (G'') at (5.75,-1) {$E(\tau) \maps F'(H(h))(\theta_m E(x)\phi) \to (\theta_n E(x')\phi)$}; %%%Christina: E(tau) is a bad name since it already means something!
 \node (H) at (3.75,0) {$\mapsto$};
@@
 
-\begin{comment} %%%John's version with symmetries
-In \cite{MV}, the classical Grothendieck construction is generalized to the monoidal setting: given a symmetric monoidal category $\A$ there is a bijection between \define{symmetric monoidal opindexed categories}, which are symmetric lax monoidal pseudofunctors $F\maps (\A, \otimes_A) \to (\Cat, \times)$, and \define{symmetric monoidal opfibrations}, which are opfibrations $U \maps \X \to \A$ where $\X$, $\A$ are monoidal, $U$ is strict symmetric monoidal, %%% must it preserve the symmetries strictly too?
-and $\otimes_\X$ preserves cocartesian liftings.
-This bijection sends a symmetric monoidal opindexed category $F \maps (\A,\otimes_A) \to (\Cat, \times)$ to the symmetric monoidal opfibration $U \maps \inta F \to \A$.
-If the symmetric monoidal structure on $\A$ is in fact cocartesian, there is a further correspondence between these structures and ordinary pseudofunctors $F\maps \A \to \SMC$, where $\SMC$ is 2-category of symmetric monoidal categories, strong symmetric monoidal functors and monoidal natural transformations.
-
- In fact, all these correspondences lift to 2-equivalences.
-
-\begin{lem}\label{lem:MonGroth}
-There is a 2-equivalence between the 2-categories of symmetric monoidal opfibrations and symmetric monoidal opindexed categories.
-If the base is cocartesian monoidal, there is a 2-equivalence between symmetric monoidal opfibrations and pseudofunctors into $\SMC$.
-\end{lem}
-
-\begin{proof}
-This was shown by Moeller and the third author \cite[Theorems~3.13\&4.2]{MV}. In summary, for a cocartesian base $\A$ we have correspondences
-\begin{gather}
-\textrm{symmetric lax monoidal pseudofunctors }F\maps(\A,+)\to(\Cat,\times) \notag\\
-\Updownarrow \notag\\
-\textrm{symmetric monoidal opfibrations }U\maps(\X,\otimes_\X)\to(\A,+) \notag\\
-\Updownarrow \notag\\
-\textrm{pseudofunctors } F \maps \A\to \SMC \notag
-\end{gather}
-The second equivalence was observed earlier by Shulman \cite{Shulman2008}.
-
-In more detail, if $(\phi,\phi_0)$ is the lax monoidal structure of the pseudofunctor $F$ as recalled in \cref{subsec:bicats}, the induced monoidal structure on the total Grothendieck category $\X=\inta F$ (\cref{def:GrothCat}) is given by
-\begin{equation}\label{eq:explicitstructure2}
-\Big(a,x\in F(a)\Big)\ot_{\X}\Big(b,y\in F(b)\Big)=\Big(a+b,\phi_{a,b}(x,y)\in F(a+b)\Big), \qquad I_{\X}=\Big(0_A,\phi_0\Big)
-\end{equation}
-Moreover, each fiber $\X_a=F(a)$ obtains a monoidal structure via 
-\begin{equation}\label{eq:explicitstructure1}
-\otimes_a\maps F(a)\times F(a)\xrightarrow{\phi_{a,a}}F(a+a)\xrightarrow{F(\nabla)}F(a),\quad
-I_a\maps\one\xrightarrow{\phi_0}F(0)\xrightarrow{F(!)}F(a)
-\end{equation}
-where $\nabla$ is the fold map.   SYMMETRIC MONOIDAL STRUCTURE??? %%%!!!
-\end{proof}
-\end{comment}
-
 These 2-equivalences further restrict to the case when the Grothendieck category $(X,\otimes_\X)$ is specifically cocartesian monoidal itself, with coproducts built up from \cref{eq:explicitstructure2}.
@@
 \begin{lem}[\textbf{Hermida}] \label{lem:fibrewiselimits}
-Suppose $\J$ is a small category and $U \maps \X \to \A$ is an opfibration where the base 
-$\A$ has $\J$-colimits.  Then the following are equivalent:
+Suppose $\J$ is a small category and $U \maps \X \to \A$ is an opfibration where the base $\A$ has $\J$-colimits.  Then the following are equivalent:
 \begin{enumerate}
@@
 If the corresponding pseudofunctor $F  \maps \A \to \SMC$ from \cref{lem:MonGroth} factors through $\Rex$, then $\inta F$ has all finite colimits and the induced opfibration $U\maps \inta F \to \A$ preserves them.
- %Moreover, for any choice of finite colimits in $\A$, finite colimits in $\inta F$ can be chosen so that that $U$ strictly preserves them.
 \end{cor}
@@
 Since we now ask that the pseudofunctor $F\colon \A\to\SMC$ factors through $\Rex$, this fiberwise monoidal structure is required to be cocartesian, namely \cref{eq:explicitstructure1} gives coproducts and an initial object in each $F(a)$.
-%,  those are clearly isomorphic to the arbitrary choice of finite coproducts in $F(a)$ coming from the above assumption that as a pseudofunctor, $F\colon \A\to\Rex$.
-For example, in that case, the coproducts induced in the Grothendieck category from the fiberwise ones as in \cref{eq:fibrewisecoprod} are equivalently given by \cref{eq:explicitstructure2}.
-
-%%% Initial version
-%In the case we are interested in, the pseudofunctor $F$ is lax monoidal; combining \cref{lem:MonGroth,lem:fibrewiselimits}, we deduce the following. 
-%\begin{cor}\label{cor:fcocMonGroth}
-% Suppose $\A$ has finite colimits and $F\maps(\A,+)\to(\Cat,\times)$ is a lax monoidal pseudofunctor.
-If the corresponding pseudofunctor $F \maps \A\to\bicat{MonCat}$ given in \cref{lem:MonGroth} factors through $\Rex$, then $\inta F$ has all finite colimits and the induced opfibration $U\maps\inta F\to\A$ preserves them.
-Moreover, for any choice of finite colimits in $\A$, finite colimits in $\inta F$ can be chosen so that that $U$ strictly preserves them.
-%\end{cor}
-
-%Notice a subtlety in the above formulation.
-\cref{lem:MonGroth} provides a specific monoidal structure on the fibers which becomes \cref{eq:explicitstructure1} when the base $\A$ is cocartesian monoidal.
-If this fiberwise monoidal structure happens to itself be cocartesian, then it is necessarily isomorphic to any other cocartesian monoidal structure on the fibers, by the universal property of colimits.
-Therefore, we can simplify the above assumption to that in \cref{thm:equiv} without having to specify that the structures came from monoidality of the pseudofunctor, although we \emph{will} use the formulation of coproducts and initial object in terms of the monoidal structure of $F$.
-For example, in that case, the coproducts induced in the Grothendieck category from the fiberwise ones as in \cref{eq:fibrewisecoprod} are equivalently given by \cref{eq:explicitstructure2}.
 
@@
 \end{proof}
-
-%Notice that under \cref{lem:fibrewiselimits}, if the base category $\A$ has an initial object denoted $0_\A$, the above lemma is equivalent to $\X$ having an initial object $0_\X$ above $0_\A$.
-
-%Work in progress \cite{CV} includes a related discussion as well as a result in the opposite direction.
-
-%Christina: I don't think the following is needed.
-%Notice that under \cref{lem:fibrewiselimits}, if the base category $\A$ has an initial object denoted $0_\A$, the above lemma is equivalent to $\X$ having an initial object $0_\X$ above $0_\A$.
-The way in which these two conditions give one another in this case is as follows.
-%The fibrewise initial object $\bot_a$ is precisely the cocartesian lifting of $0_\X$ along the unique map $u_a\maps0_\A\to a$ in the base category
-%\begin{displaymath}
-%\xymatrix @C=.4in @R=.2in
-%{0_\X \ar @{.>}[d]\ar[rr]^-{\mathrm{Cocart}(0_\X,u_a)} && (u_a)_!(0_X)=:\bot_a\ar @{.>}[d] & \textrm{in }\X  \\
-%0_\A\ar[rr]^-{\exists!u_a} && a & \textrm{in }\A}
-%\end{displaymath}
-%Moreover, if the opfibration $U$ comes from the Grothendieck construction on a pseudofunctor $F\maps\A\to\Cat$, the reindexing functors $(u_a)_!$ of the %opfibration are precisely $F(u_a)$ therefore $\bot_a=(a,F(u_a)(0_\X))$ in the Grothendieck category notation (\cref{def:GrothCat}).
-
-%Finally, if we start with a lax monoidal pseudofunctor $(F,\phi,\phi_0)$, the monoidal Grothendieck construction of \cref{lem:MonGroth} in the cocartesian case expresses $\bot_a$ as follows by \cref{eq:explicitstructure1}:
-%\begin{equation}\label{eq:initialinfibre}
-%\mathbf{1}\xrightarrow{\phi_0}F(0_\A)\xrightarrow{F(u_a)}F(a) 
-%\end{equation}
 
@@
 \begin{equation}\label{eq:isomorphismdiag}
- \begin{tikzcd}
-F(m)\times F(n)\ar[rr,"\phi_{m,n}"]\ar[d,"F(v_m)\times F(v_n)"']\ar[dr,phantom,"\cong"] && F(m+n)\ar[d,"F(\psi)"]\ar[d,bend right=50, phantom,"\cong"']\ar[dl,"F(v_m+v_n)"description] \\
+ \begin{tikzcd}[sep=.4in]
+F(m)\times F(n)\ar[r,"\phi_{m,n}"]\ar[d,"F(v_m)\times F(v_n)"']\ar[dr,phantom,"\stackrel{\phi_{v_m,v_n}}{\cong}"] & F(m+n)\ar[r,"F(\psi)"]\ar[dr,phantom,"\cong"']\ar[d,"F(v_m+v_n)"] & F(m+_bn)\ar[d,"F(1)"]\\
 F(m+_bn)\times F(m+_bn)\ar[r,"\phi_{m+_bn,m+_bn}"'] & F\left((m+_bn)+(m+_bn)\right)\ar[r,"F(\nabla)"'] & F(m+_bn)
@@
 where the composite of the bottom two arrows is the coproduct $+ \maps F(m+_bn) \times F(m+_bn) \to F(m+_bn)$ as in \cref{eq:explicitstructure1}.
-The left-hand isomorphism arises from the pseudonaturality of $\phi$ as in \cref{eq:pseudonaturality}, whereas the right-hand isomorphism follows from universal properties and the pseudofunctoriality of $F$.
-Thus, we have a canonical globular 2-isomorphism  $\lE(N) \odot \lE(M) \simrightarrow\lE(N \odot M)$.
+The left-hand isomorphism comes from pseudonaturality of $\phi$ as in \cref{eq:pseudonaturality}, whereas the right-hand isomorphism follows from universal properties and pseudofunctoriality of $F$.
+Thus, we have a globular 2-isomorphism  $\lE(N) \odot \lE(M) \simrightarrow\lE(N \odot M)$.
+Notice that since the target decoration is part of the above pushout in the Grothendieck category $\inta F$, this isomorphism we construced is the canonical such that it commutes with the respective cocones.
+This is useful when checking associativity for example: there is only one such canonical isomorphism $\lE(P)\odot\lE(N)\odot\lE(M)\to\lE(P\odot N\odot M)$ for any three composable structured cospans.
+
 Regarding identities, the identity horizontal 1-cell $U_m$ in $_L\lCsp(\inta F)$ is $\cspn{(m,\bot_m)}{(m,\bot_m)}{(m,\bot_m)}{}{}$ with $1_m$ as the $A$-component and isomorphisms between initial objects in the fibers.
@@
 \begin{displaymath}
-\begin{tikzcd}
-F(m)\times F(m')\ar[rr,"\phi_{m,m'}"]\ar[d,"F(i_m)\times F(i_{m'})"']\ar[dr,phantom,"\stackrel{\cref{eq:pseudonaturality}}{\cong}"] && F(m+m')\ar[d,equal]\ar[d,bend right=50, phantom,"\cong"']\ar[dl,"F(i_m+i_{m'})"description] \\
+\begin{tikzcd}[sep=.4in]
+F(m)\times F(m')\ar[r,"\phi_{m,m'}"]\ar[d,"F(\iota_m)\times F(\iota_{m'})"']
+\ar[dr,phantom,"{\stackrel[\cref{eq:pseudonaturality}]{\phi_{\iota_m,\iota_n}}{\cong}}"] & F(m+m')\ar[dr,"F(1)"]\ar[d,bend left=60, phantom,"\cong"']\ar[d,"F(\iota_m+\iota_{m'})"']  & \\
 F(m+m')\times F(m+m')\ar[r,"\phi_{m+m',m+m'}"'] & F\left((m+m')+(m+m')\right)\ar[r,"F(\nabla)"'] & F(m+m')
@@
 We thus have constructed an isomorphism $\lE(M)\otimes\lE(M') \simrightarrow \lE(M\otimes M')$ for each $M,M'$. 
-Notice that both sides in the diagram above, combined with the same object $m+m'$ in $\A$, express a coproduct in the Grothendieck category $\inta F$ by formulas \cref{eq:fibrewisecoprod,eq:explicitstructure2}.
-Therefore the isomorphism $F(\iota_m)x+F(\iota_{m'})x '\cong \phi_{m,m'}(x,x')$ given by this diagram is the unique one that commutes with the respective cocones.
-This is useful when checking associativity for example: there is only one such isomorphism $\lE(M)\otimes\lE(M')\otimes\lE(M'')\simrightarrow\lE(M\ot M'\ot M'')$ for any three structured cospans.
+Again, notice that since the target decoration is part of the sum $\left(m+m',F(\iota_m)x+F(\iota_{m'})x'\right)$ in the Grothendieck category $\inta F$ by \cref{eq:fibrewisecoprod}, this isomorphism we constructured is the canonical such that it commutes with the respective inclusions into the sum, and there is only one such canonical isomorphism $\lE(M)\otimes\lE(M')\otimes\lE(M'')\simrightarrow\lE(M\ot M'\ot M'')$ for any three structured cospans, proving associativity.
 
@@
 $I\to\lE(I)$ is the identity.
+{\chris It is not the identity!
+Fix after we decide: keep \cref{eq:monoidalunitFCsp} as is and make this into an isomorphism using $F(1)\cong 1_F$ or change \cref{eq:monoidalunitFCsp} to the actual $U_0$ in the notation therein, and have equality of structures here.}
 
@@
 \end{displaymath}
-%\[
-%\begin{tikzpicture}[scale=1.5]
-%\node (A) at (0,0) {$a$};
-%\node (B) at (1,0) {$b$};
-%\node (C) at (2,0) {$b$};
-%\node (D) at (1,-0.5) {$\bot_{b} \in F(b)$};
-%\path[->,font=\scriptsize,>=angle 90]
-%(A) edge node[above]{$f$} (B)
-%(C) edge node[above]{$1$} (B);
-%\end{tikzpicture}
-%\]
 where $\bot_b$ is the trivial decoration as in \cref{eq:UFCsp}, is a companion of $f$ because the following two 2-morphisms, having $\hat{f}$ as
@@
 \end{displaymath}
-%\[
-%\begin{tikzpicture}[scale=1.5]
-%\node (A) at (0,0) {$b$};
-%\node (B) at (1,0) {$b$};
-%\node (C) at (2,0) {$a$};
-%\node (D) at (4,0) {$\bot_{b} \in F(b)$};
-%\path[->,font=\scriptsize,>=angle 90]
-%(A) edge node[above]{$1$} (B)
-%(C) edge node[above]{$f$} (B);
-%\end{tikzpicture}
-%\]
 Just as $\hat{f}$ obeys the equations required of a companion, $\check{f}$ obeys the equations required of a conjoint.
@@
 
-%%% Christina: Pretty sure the def below can be incorporated above, however got a bit lost in different notation. Kenny Fix?
-%\begin{defn}
-%A double functor $\lF \maps \lD \to \lE$ is \define{strong} if the comparison and unit constraints are globular isomorphisms, meaning that for each composable pair of horizontal 1-cells $M$ and $N$ we have a natural isomorphism $$\lF_{M,N} \maps \lF(M) \odot \lF(N) \xrightarrow{\sim} \lF(M \odot N)$$ and for each object $a \in \lD$ a natural isomorphism $$\lF_a \maps \hat{U}_{\lF(a)} \xrightarrow{\sim} \lF(U_a).$$
-%\end{defn}
-
-%Following the notation of Shulman \cite{Shulman2010}, given a double category $\lD$, we write $_f \lD_g(M,N)$ for the set of 2-morphisms in $\lD$ of the form:
-%\[
-% \xymatrix@-.5pc{
-%   A \ar[r]|{|}^{M}  \ar[d]_f \ar@{}[dr]|{\Downarrow a}&
-%    B\ar[d]^g\\
-%    C \ar[r]|{|}_N & D
-%  }
-%\]
-
 \begin{defn}\label{def:fullfaithful}
@@
 %%% Kenny: How about I instead of 1?
-%%% Christina: Sure but I was NOT in the definition of symmetric monoidal double category above...could you streamline??
+%%% Christina: Sure but that was NOT in the definition of symmetric monoidal double category above...could you streamline??
 \noindent
@@
 First of all, if we only consider the underlying cospans without their decorations, we obtain the following `flattened' commutative diagram in $\A$ -- which verifies the corresponding axiom for the symmetric monoidal double category $\lCsp(\A)$:
-%%% Kenny any good reference for that?
-Not just cospans, which I can find in Niefield, but the interchange law as well for cospans only.
-Is it in your thesis?
-Somewhere in Shulman?
-Had a look but couldn't dig up anything...I know it is easy but would look nicer if we had some reference here
 \[
@@
 \]
-%{\chris Kenny please see difference in diagrams (the rightmost part is not important, just to make the two decoration isomorphism have the same border).
-The blue is the old one.
-The new diagram \cref{eq:interchangedeco} should be the one we disagreed, namely its codomain.
-But also on the down part of the diagram, coming from the decoration morphism of the braiding \cref{eq:decobraiding}, mine is much ``easier''.}
-%{\color{blue}
-%\[
-%\begin{tikzpicture}[scale=1.6]
-%%\node (A) at (3.85,0) {$\scriptstyle{\cong}$};
-%%\node (A') at (3.85,-1) {$\scriptstyle{\cong}$};
-%\node (D) at (3,-0.5) {$\scriptstyle{\one}$};
-%\node (E) at (6.75,0.5) {$\scriptstyle{F(m_1 + n_1) \times F(m_2+n_2)}$};
-%\node () at (5.5,-1) {$\scriptstyle{\cong}$};
-%\node () at (7.875,-1) {$\scriptstyle\stackrel{\cref{eq:braidedpseudofun}}{\cong}$};
-%\node () at (10.25,-1) {$\scriptstyle{\cong}$};
-%\node () at (7.875,0) {$\scriptstyle\stackrel{\cref{eq:interchangedeco}}{\cong}$};
-%\node (E') at (6.75,-0.5) {$\scriptstyle{F(m_1+m_2) \times F(n_1+n_2)}$};
-%\node (B) at (9,0.5) {$\scriptstyle{F((m_1+n_1)+(m_2+n_2))}$};
-%\node (B') at (9,-0.5) {$\scriptstyle{F((m_1+ m_2)+(n_1+n_2))}$};
-%\node (C) at (11.5,0.5) {$\scriptstyle{F((m_1+n_1)+_{b+b'}(m_2+n_2))}$};
-%\node (C') at (11.5,-0.5) {$\scriptstyle{F((m_1+_b m_2)+ (n_1+_{b'} n_2))}$};
-%\node (G) at (4.25,0.5) {$\scriptstyle{F(m_1) \times F(n_1) \times F(m_2) \times F(n_2)}$};
-%\node (G') at (4.25,-0.5) {$\scriptstyle{F(m_1) \times F(m_2) \times F(n_1) \times F(n_2)}$};
-%\node (G'') at (4.25,-1.5) {$\scriptstyle{F(n_1) \times F(n_2) \times F(m_1) \times F(m_2)}$};
-%\node (E'') at (6.75,-1.5) {$\scriptstyle{F(n_1+n_2) \times F(m_1+m_2)}$};
-%\node (B'') at (9,-1.5) {$\scriptstyle{F((n_1+n_2)+(m_1+ m_2))}$};
-%\node (C'') at (11.5,-1.5) {$\scriptstyle{F((n_1+_{b'}n_2)+(m_1+_b m_2))}$};
-%\node (X) at (3.4,0.2) {$\scriptscriptstyle{x_1 \times y_1 \times x_2 \times y_2}$};
-%\node (X') at (3.4,-0.35) {$\scriptscriptstyle{x_1 \times x_2 \times y_1 \times y_2}$};
-%\node (X'') at (3.4,-1.2) {$\scriptscriptstyle{y_1 \times y_2 \times x_1 \times x_2}$};
-%\path[->,font=\scriptsize,>=angle 90]
-%(B') edge node [fill=white] {$F(\beta)$} (B'')
-%(E') edge node [fill=white] {$\beta$} (E'')
-%(E) edge node [above] {$\phi_{m_1+n_1,m_2+n_2}$} (B)
-%(E'') edge node [above] {$\phi_{n_1+n_2,m_1+m_2}$} (B'')
-%(E') edge node [above] {$\phi_{m_1+m_2,n_1+n_2}$} (B')
-%(B) edge node [above] {$F(\psi)$} (C)
-%(B'') edge node [above] {$F(\psi+\psi)$} (C'')
-%(B') edge node [above] {$F(\psi+\psi)$} (C')
-%(C) edge node [fill=white] {$F(\hat{\chi})$} (C')
-%(C') edge node [fill=white] {$F(\beta)$} (C'')
-%(G) edge node [above] {$\phi_{m_1,n_1} {\times} \phi_{m_2,n_2}$} (E)
-%(G'') edge node [above] {$\phi_{n_1,n_2} {\times} \phi_{m_1,m_2}$} (E'')
-%(G') edge node [above] {$\phi_{m_1,m_2} \times \phi_{n_1,n_2}$} (E')
-%(G) edge node [fill=white] {$1 \times \beta \times 1$} (G')
-%(G') edge node [fill=white] {$\beta$} (G'')
-%(D) edge[out=90,in=180] node [left,above] {$$} (G)
-%(D) edge[out=270,in=180] node [left,above] {$$} (G'')
-%(D) edge node [below] {$$} (G');
-%\end{tikzpicture}
-%\]
-%}
 For the other (vertical) composition of \cref{eq:thisdiagram}, that of $\beta\odot\beta$ followed by $\chi$, the composite decoration $\tau_2\tau_1$ is
@@
 \]
-%{\chris The closing sentence for the proof to be complete should be that these two decoration maps are EQUAL for the diagram \cref{eq:thisdiagram} to commute!
-Right?
-Is the sentence below satisfactory Kenny?
-Do you see the logic?}
 In order to verify that these two pasted isomorphisms are equal, we first of all need to expand the isomorphism \cref{eq:interchangedeco}, whose left half part is explicitly written as follows (also found in \cite[Page 125]{DS}):
@@
 The result now follows from lengthy pasted diagram calculations using the axioms of a sylleptic lax monoidal pseudofunctor.
-\begin{comment}
-These decoration isomorphisms then form the following commutative diagram in the category $F({(n_1+_{b'}n_2)}+{(m_1+_b m_2)})$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$F(\hat{\chi} (\beta \odot \beta))((x_1 \otimes y_1)\odot(x_2 \otimes y_2))$};
-\node (B) at (4,0) {$F(\hat{\chi})((y_1 \otimes x_1)\odot(y_2 \otimes x_2))$};
-\node (C) at (0,-1) {$F(\beta)((x_1\odot x_2) \otimes (y_1 \odot y_2))$};
-\node (D) at (4,-1) {$(y_1\odot y_2) \otimes (x_1\odot x_2)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$F(\hat{\chi})(\tau_1)$} (B)
-(B) edge node[right]{$\tau_2$} (D)
-(A) edge node[left]{$F(\beta)(\tau_3)$} (C)
-(C) edge node[above]{$\tau_4$} (D);
-\end{tikzpicture}
-\]
-where in the top left corner, we note that $$F(\hat{\chi} (\beta \odot \beta))((x_1 \otimes y_1)\odot(x_2 \otimes y_2)) = F(\beta\hat{\chi})((x_1 \otimes y_1)\odot (x_2 \otimes y_2))$$
-as the above diagram of maps of cospans commutes in $\A$ and then applying the pseudofunctor $F$ to this diagram yields a commutative diagram in $\Cat$. 
-\end{comment}
 

### 2020-12-23 cospans.tex
small changes

@@
 % in LaTeX
-% 2020/12/19
+% 2020/12/22
 
@@
 Via these operations we obtain a symmetric monoidal double category
-with cospans in $\A$ as its horizontal 1-cells \cite{Niefield}.
+with cospans in $\A$ as its horizontal 1-cells \cite{Courser,Niefield}.
 
@@
 Take $\A$ to have finite colimits and let $(F,\phi,\phi_0) \maps (A,+) \to (\Cat,\times)$ be a lax monoidal pseudofunctor.
-We shall define the category of objects $F\lCsp_0$, the category of arrows $F\lCsp_1$, as well as the four structure functors which tie them together: the source and target functors $S,T \colon F\lCsp_1 \to F\lCsp_0$, the composition functor $\odot \colon F\lCsp_1 \times_{F\lCsp_0} F\lCsp_1 \to F\lCsp_1$ and the unit functor $U \colon F\lCsp_0 \to F\lCsp_1$.
+We shall define the category of objects $F\lCsp_0$, the category of arrows $F\lCsp_1$, as well as the four structure functors which tie them together: the source and target functors $S,T \colon F\lCsp_1 \to F\lCsp_0$, the unit functor $U \colon F\lCsp_0 \to F\lCsp_1$, and the composition functor $\odot \colon F\lCsp_1 \times_{F\lCsp_0} F\lCsp_1 \to F\lCsp_1$.
 
 The category of objects $F\lCsp_0$ is simply $\A$, whereas $F$-decorated cospans and maps between them form the category of arrows $F\lCsp_1$.
-The (vertical) composition of two $F$-decorated cospans maps is
+The (vertical) composition of two $F$-decorated cospan maps is
 \begin{equation}\label{eq:verticalcompo}
@@
 \begin{equation}\label{eq:tauofverticalcomposite}
-F(h'h)(x)\cong F(h')F(h)(x)\xrightarrow{F(h')(\tau)}F(h')(x')\xrightarrow{\tau'}x''
+F(h'h)(x) \simrightarrow F(h')F(h)(x)\xrightarrow{F(h')(\tau)}F(h')(x')\xrightarrow{\tau'}x''
 \end{equation}
 is the decoration of the composite.
-The source and target functors map an $F$-decorated cospan to the source and target of the cospan and a map of decorated cospans \cref{eq:mapofdec} to $f$ and $g$ respectively.
-The unit functor maps an object $a$ to
+
+The source and target functors $S$ and $T$ map an $F$-decorated cospan to the source and target of the cospan and a map of decorated cospans \cref{eq:mapofdec} to $f$ and $g$ respectively.
+The unit functor $U$ maps an object $a$ to
 \begin{equation}\label{eq:UFCsp}
@@
 that is, invertible globular 2-morphisms
-\[ \chi \maps (M_2\otimes N_2)\odot(M_1\otimes N_1)  \xrightarrow{\sim}
+\[ \chi \maps (M_2\otimes N_2)\odot(M_1\otimes N_1)  \simrightarrow
 (M_2\odot M_1)\otimes (N_2\odot N_1)\]
-\[ \mu \maps U_{A\otimes B} \xrightarrow{\sim} U_A \otimes U_B\]
+\[ \mu \maps U_{A\otimes B} \simrightarrow U_A \otimes U_B\]
 obeying a list of equations that can be found after \cite[Definition 2.10]{HS} and also \cite[Definition A.5]{BC}.

### 2020-12-23 cospans.tex
tiny
fixed stuff about units - see comments marked "jb"

@@
 together with the decoration morphism $F(f)F(!_a)\phi_0(*)\cong F(!_{a'})\phi_0(*)$.
-Finally, the (horizonta)l composition functor $\odot$ maps two composable $F$-decorated cospans 
+Finally, the (horizontal) composition functor $\odot$ maps two composable $F$-decorated cospans 
 \[  M=\left(a\to m\leftarrow b,x\in F(m)\right), \qquad N=\left(b\to n\leftarrow c,y\in F(n)\right)\] 
@@
 We first show that the categories of objects and arrows are symmetric monoidal, and that the source and target functors are symmetric strict monoidal.
-Indeed, the category of objects $F\lCsp_0=\A$ is symmetric monoidal under (chosen) binary coproducts in $\A$. The category of arrows
-$F\lCsp_1$ is also symmetric monoidal, with tensor product as in \cref{eq:tensordecoration} and monoidal unit
+Indeed, the category of objects $F\lCsp_0=\A$ is symmetric monoidal under the chosen binary coproducts in $\A$.
+The category of arrows $F\lCsp_1$ is also symmetric monoidal, with tensor product as in \cref{eq:tensordecoration} and monoidal unit
+\[
+I_1=\left(0\xrightarrow{!}0 \xleftarrow{!}0, \one \xrightarrow{\phi_0}F(0) \xrightarrow{F(!_0)} F(0) \right) 
+\]
+where $0$ is the initial object in $\A$.  By \cref{eq:UFCsp}, this unit $I_1$ is equal to $U_{0}$ as required.   In all that follows, we shall assume that $F(!_0)$ is the identity, so that
 \begin{equation}\label{eq:monoidalunitFCsp}
-I_1=\left(0\xrightarrow{!}0\xleftarrow{!}0, \one \xrightarrow{\phi_0}F(0)\right)
-\end{equation}
-where $0$ is the initial object in $\A$. Notice that this unit $I_1$ is (isomorphic to) $U_0$ as required. The associator is formed as follows: for three objects
+I_1=\left(0\xrightarrow{!}0 \xleftarrow{!}0, \one \xrightarrow{\phi_0}F(0)\right).
+\end{equation}
+This can always be achieved by replacing $F$ by an equivalent pseudofunctor that strictly preserves identity morphisms, but we do this merely to reduce the size of diagrams to come; the reader can reinsert the morphism $F(!_0)$ where needed.
+%%% see if you like this!
+I'd like to add a ref that says any 2-functors is equivalent to a normalized one.
+- jb
+The associator is formed as follows: for three objects
 $M_1=(a_1\to m_1\leftarrow b_1,x_1\in F(m_1))$, $M_2=(a_2\to m_2\leftarrow b_2,x_2\in F(m_2))$ and $M_3=(a_3\to m_3\leftarrow b_3,x_3\in F(m_3),$
@@
 
-Moreover, the monoidal unit for the category of arrows of $F\lCsp$ is \cref{eq:monoidalunitFCsp}, given by the identity cospan $0_\A \rightarrow 0_\A \leftarrow 0_\A$ on the monoidal unit of $\A$ together with the trivial decoration $\bot_{0_\A} = \phi_0 \colon 1 \to F(0_\A)$ on $0_\A$, and the monoidal unit for the category of arrows of ${ _L \lCsp(\inta F)}$ is given by $(0_\A,\bot_{0_\A}) \rightarrow (0_\A,\bot_{0_\A}) \leftarrow (0_\A,\bot_{0_\A})$.
-This is mapped under $\lE$ again to the identity cospan on $0_\A$ with the trivial decoration on its apex, so that the structure map %$I_{F\lCsp_1}\to\lE(I_{{_L \lCsp (\int F)}_1})$
-$I\to\lE(I)$ is the identity.
-{\chris It is not the identity!
-Fix after we decide: keep \cref{eq:monoidalunitFCsp} as is and make this into an isomorphism using $F(1)\cong 1_F$ or change \cref{eq:monoidalunitFCsp} to the actual $U_0$ in the notation therein, and have equality of structures here.}
+Moreover, the monoidal unit $I_1$ for $F\lCsp_1$ is \cref{eq:monoidalunitFCsp}, given by the identity cospan $0_\A \rightarrow 0_\A \leftarrow 0_\A$ on the monoidal unit of $\A$ together with the trivial decoration $\bot_{0_\A} = \phi_0 \colon 1 \to F(0_\A)$ on $0_\A$, and the monoidal unit for the category of arrows of ${ _L \lCsp(\inta F)}$ is given by $(0_\A,\bot_{0_\A}) \rightarrow (0_\A,\bot_{0_\A}) \leftarrow (0_\A,\bot_{0_\A})$.
+This is mapped under $\lE$ again to the identity cospan on $0_\A$ with the trivial decoration on its apex, so $\lE_1$ strictly preserves the monoidal unit.
+%%% Now it's really the identity!
+Can we shorten this calculation, now that it actually works?
+It's not so interesting now that it works.
+- jb
 
@@
 $\lD_0$, a \define{category of arrows} $\lD_1$, functors 
-\[    U\maps \lD_0 \to \lD_1, \; S,T \maps \lD_1 \to \lD_0 , \textrm{ and }
+\[   S,T \maps \lD_1 \to \lD_0, \;  U\maps \lD_0 \to \lD_1, \; \textrm{ and }
    \odot \maps \lD_1 \times_{\lD_0} \lD_1 \to \lD_1\]
-such that 
+called the \define{source} and \define{target}, \define{unit} and \define{composition}
+functors, respectively, such that 
 \[  S(U_{A})=A=T(U_{A}),  \quad S(M \odot N)=S(N), \quad T(M \odot N)=T(M), \]
 and natural isomorphisms called the \define{associator}
-\[ \alpha_{L,M,N} \maps (L \odot M) \odot N \to L \odot (M \odot N) , \]
+\[ \alpha_{L,M,N} \maps (L \odot M) \odot N \to L \odot (M \odot N)  \]
 and \define{left and right unitors}
@@
 \begin{itemize}
-\item monoidal structures on both $\lD_0$ and $\lD_1$, each with tensor product denoted $\otimes$, associator $a$, left unitor $\ell$ and right unitor $r$, such that if $I$ is the unit object of $\lD_0$ then $U_I$ is\footnote{\chris In reality, just isomorphic is OK!} the unit of $\lD_1$, and such that the source and target functors $S,T \maps \lD_1 \to \lD_0$ are strict monoidal,
+\item monoidal structures on both $\lD_0$ and $\lD_1$ (each with tensor product denoted $\otimes$, associator $a$, left unitor $\ell$ and right unitor $r$), such that $U \maps \lD_0 \to \lD_1$ strictly preserves the unit object and $S,T \maps \lD_1 \to \lD_0$ are strict monoidal,    %%% got rid of footnote saying that "isomorphic is okay" - jb
 \item the structure of a double functor on $\otimes$:

### 2020-12-23 cospans.tex
fixed three things related to units - see comments marked "jb"

@@
 
-Moreover, the monoidal unit $I_1$ for $F\lCsp_1$ is \cref{eq:monoidalunitFCsp}, given by the identity cospan $0_\A \rightarrow 0_\A \leftarrow 0_\A$ on the monoidal unit of $\A$ together with the trivial decoration $\bot_{0_\A} = \phi_0 \colon 1 \to F(0_\A)$ on $0_\A$, and the monoidal unit for the category of arrows of ${ _L \lCsp(\inta F)}$ is given by $(0_\A,\bot_{0_\A}) \rightarrow (0_\A,\bot_{0_\A}) \leftarrow (0_\A,\bot_{0_\A})$.
-This is mapped under $\lE$ again to the identity cospan on $0_\A$ with the trivial decoration on its apex, so $\lE_1$ strictly preserves the monoidal unit.
-%%% Now it's really the identity!
-Can we shorten this calculation, now that it actually works?
-It's not so interesting now that it works.
+Moreover, the monoidal unit $I_1$ for $F\lCsp_1$, given by \cref{eq:monoidalunitFCsp}, is mapped under $\lE_1$ to the identity cospan on $0_\A$ with the trivial decoration on its apex, so $\lE_1$ strictly preserves the monoidal unit.
+%%% Under our new assumptions it's really true!
 - jb

### 2020-12-23 cospans.tex
changed 3 things related to eq. (10); see comments marked "jb"

@@
 \end{equation}
-This can always be achieved by replacing $F$ by an equivalent pseudofunctor that strictly preserves identity morphisms, but we do this merely to reduce the size of diagrams to come; the reader can reinsert the morphism $F(!_0)$ where needed.
+This can always be achieved by replacing $F$ by an equivalent pseudofunctor that strictly preserves identity morphisms \cite[Proposition 5.2]{LP}.
+We do this merely to reduce the size of  our diagrams; the reader can reinsert the morphism $F(!_0)$ where needed.
 %%% see if you like this!
-I'd like to add a ref that says any 2-functors is equivalent to a normalized one.
 - jb
-The associator is formed as follows: for three objects
+The associator in is formed as follows: for three objects
 $M_1=(a_1\to m_1\leftarrow b_1,x_1\in F(m_1))$, $M_2=(a_2\to m_2\leftarrow b_2,x_2\in F(m_2))$ and $M_3=(a_3\to m_3\leftarrow b_3,x_3\in F(m_3),$
@@
 with isomorphisms between decorations precisely given by \cref{eq:unitality}.
-Finally, the symmetric monoidal structure of $F\lCsp_1$ is inherited from that in $\A$ and $F$, with braiding $\beta\maps M_1\ot M_2\to M_2\ot M_1$ the cospan isomorphism
+Finally, the braiding in $F\lCsp_1$ is inherited from that in $\A$ and $F$, with braiding $\beta\maps M_1\ot M_2\to M_2\ot M_1$ the cospan isomorphism
 \begin{equation}\label{eq:braidingFCsp1}
@@
 
+\bibitem{LP} S.\ Lack and S.\ Paoli, 2-nerves for bicategories, \textsl{$K$-Theory} \textbf{38} (2008), 153--175.
+
 \bibitem{Lawvere} F.\ W.\ Lawvere, State categories and response functors, unpublished manuscript, 1986.

### 2020-12-24 cospans.tex
changed date in paper
various edits

@@
 % in LaTeX
-% 2020/12/22
+% 2020/12/24
 
@@
 - jb
-The associator in is formed as follows: for three objects
+%%% Christina: looks nice!
+
+The associator for the monoidal structure in $F\lCsp$ is formed as follows: for three objects
 $M_1=(a_1\to m_1\leftarrow b_1,x_1\in F(m_1))$, $M_2=(a_2\to m_2\leftarrow b_2,x_2\in F(m_2))$ and $M_3=(a_3\to m_3\leftarrow b_3,x_3\in F(m_3),$
@@
 where the left-hand side isomorphism \cref{eq:thetaa} is spelled out in detail in \cref{eq:proofofaxiom} and combines the pseudoassociativity \cref{eq:omega} and braided monoidal structure \cref{eq:braidedpseudofun} of the pseudofunctor $F$, and the right hand side isomorphism follows from the universal property of colimits and pseudofunctoriality of $F$.
-Similarly, for the units $U_{a+b}$ and $U_a\ot U_b$ it is easy to see that as cospans they are both the identity $1_{a+b} \maps a+b\to a+b\leftarrow a+b:1_{a+b}$, and there is a canonical isomorphism between their trivial decorations \cref{eq:UFCsp}, namely $F(!_{a+b})\phi_0\cong\phi_{a,b}(F(!_a)\times F(!_b))(\phi_0\times\phi_0)$ via the structure isomorphisms for $(\phi,\phi_0)$.
+
+Similarly, for the comparison isomorphism between the units $U_{a+b}$ and $U_a\ot U_b$, it is easy to see that as cospans they are both the identity $1_{a+b} \maps a+b\to a+b\leftarrow a+b:1_{a+b}$, and there is a canonical isomorphism between their decorations
+\begin{displaymath}
+\begin{tikzcd}[column sep=.55in]
+\one\ar[r,"\phi_0"]\ar[dr,phantom,near start,"{\scriptstyle\stackrel{\cref{eq:pseudonaturality}}{\cong}}"]\ar[d,"\phi_0\times\phi_0"'] & F(0)\ar[dr,phantom,"{\scriptstyle\stackrel{\cref{eq:pseudonaturality}}{\cong}}"]\ar[r,"F(!_{a+b})"] & F(a+b)\ar[d,"F(1)"] \\
+F(0)\times F(0)\ar[r,"F(!_a)\times F(!_n)"']\ar[ur,"\phi_{0,0}"description] & F(a)\times F(b)\ar[r,"\phi_{a,b}"'] & F(a+b)
+\end{tikzcd}
+\end{displaymath}
+where the top composite is $\bot_{a+b}$ by \cref{eq:UFCsp} and the bottom composite is $\phi_{a,b}(\bot_a,\bot_b)$ from \cref{eq:tensordecoration}.
+%, namely $F(!_{a+b})\phi_0\cong\phi_{a,b}(F(!_a)\times F(!_b))(\phi_0\times\phi_0)$ via the structure isomorphisms for $(\phi,\phi_0)$.
 
@@
 Indeed, for \cref{eq:scsphor1cell}, the unique maps from the initial objects in the fibers provide no actual extra information, and similarly for 2-cells all extra data in \cref{eq:2morphismLCspintaF} is uniquely determined and \cref{eq:Grothcommutativity} holds automatically as discussed above.
-As a result, we have a double isomorphism $$_L\lCsp(\inta F) \cong F\lCsp.$$
+As a result, we have a double isomorphism
+\begin{equation}\label{eq:doubleiso}
+_L\lCsp(\inta F) \cong F\lCsp.
+\end{equation}
 
@@
 - jb
-
-It can be verified that with the above structure, $\lE_1$ is also a symmetric monoidal functor, and the rest of the axioms of \cref{defn:monoidal_double_functor} hold.
+%%% Christina: sorry I think E_1 goes in the opposite direction!
+It can be verified that with this structure, $\lE_1$ is also a symmetric monoidal functor.
+
+Finally, the rest of the axioms of \cref{defn:monoidal_double_functor} hold and thus the double isomorphism \cref{eq:doubleiso} is an isomorphism of symmetric monoidal double categories. 
 \end{proof}
@@
 \begin{itemize}
-\item monoidal structures on both $\lD_0$ and $\lD_1$ (each with tensor product denoted $\otimes$, associator $a$, left unitor $\ell$ and right unitor $r$), such that $U \maps \lD_0 \to \lD_1$ strictly preserves the unit object and $S,T \maps \lD_1 \to \lD_0$ are strict monoidal,    %%% got rid of footnote saying that "isomorphic is okay" - jb
+\item monoidal structures on both $\lD_0$ and $\lD_1$ (each with tensor product denoted $\otimes$, associator $a$, left unitor $\ell$ and right unitor $r$), such that $U \maps \lD_0 \to \lD_1$ strictly preserves the unit object and $S,T \maps \lD_1 \to \lD_0$ are strict monoidal,    %%% got rid of footnote saying that "isomorphic is okay" - jb %%% Great.
 \item the structure of a double functor on $\otimes$:

### 2020-12-24 cospans.tex
tiny

@@
 \end{displaymath}
-where the top composite is $\bot_{a+b}$ by \cref{eq:UFCsp} and the bottom composite is $\phi_{a,b}(\bot_a,\bot_b)$ from \cref{eq:tensordecoration}.
+where the top composite is $\bot_{a+b}$ by \cref{eq:UFCsp} and the bottom composite is $\phi_{a,b}(\bot_a,\bot_b)$ by \cref{eq:tensordecoration}.
 %, namely $F(!_{a+b})\phi_0\cong\phi_{a,b}(F(!_a)\times F(!_b))(\phi_0\times\phi_0)$ via the structure isomorphisms for $(\phi,\phi_0)$.

### 2020-12-24 cospans.tex
clarified what's "that  Theorem".

@@
 There is a much simpler proof of the above theorem when the hypothesis of \cref{thm:equiv} hold.
-In this case we show, in the proof of that theorem, that the decorated cospan double category $F \lCsp$ is isomorphic to a certain double category ${}_L \lCsp(\inta  F)$ constructed using \emph{structured} cospans.
+In this case we show, in the proof of\cref{thm:equiv}, that the decorated cospan double category $F \lCsp$ is isomorphic to a certain double category ${}_L \lCsp(\inta  F)$ constructed using \emph{structured} cospans.
 We also show that under this isomorphism, all the symmetric monoidal structure of $F \lCsp$---the tensor product, associator, etc.---matches that for  ${}_L \lCsp(\inta  F)$, which we have proved to obey the axioms of a symmetric monoidal double category (see \cref{thm:SC}).

### 2020-12-25 cospans.tex
Added a bit to the definition of symmetric monoidal double functor

@@
 \end{defn}
-{\chris Those units in the definition should be monoidal units not unit functors...}
+%{\chris Those units in the definition should be monoidal units not unit functors...}
 %%% Kenny: How about I instead of 1?
@@
 \noindent
-Unpacking this definition, one obtains a number of diagrams which can be found after \cite[Definition 2.14]{HS}.
+Explicitly, a symmetric monoidal double functor is a double functor $\lF \colon \lD \to \lE$ such that:
+\begin{itemize}
+\item{$\lF_0$ and $\lF_1$ are symmetric monoidal functors,}
+\item{we have equalities $\lF_0 S_{\lD} = S_{\lE} \lF_1$ and $\lF_0 T_{\lD} = T_{\lE} \lF_1$ of monoidal functors, and}
+\item{the following diagrams commute, expressing that $\phi$ is a transformation of double categories:
+		\begin{equation}
+		\begin{tikzpicture}
+			\node (A) at (0,1.5) {\footnotesize{$ (\lF(M_2)\otimes \lF(N_2))\odot (\lF(M_1)\otimes \lF(N_1))$}};
+			\node (A') at (0,0) {\footnotesize{$(\lF(M_2) \odot \lF(M_1)) \otimes (\lF(N_2) \odot \lF(N_1))$}};
+			\node (B) at (5,1.5) {\footnotesize{$\lF(M_2 \otimes N_2)\odot \lF(M_1 \otimes N_1)$}};
+			\node (B') at (5,0) {\footnotesize{$\lF((M_2 \otimes N_2)\odot(M_1 \otimes N_1))$}};
+			\node (A'') at (0,-1.5) {\footnotesize{$\lF(M_2 \odot M_1) \otimes \lF(N_2 \odot N_1)$}};
+			\node (B'') at (5,-1.5) {\footnotesize{$\lF((M_2 \odot M_1)\otimes(N_2 \odot N_1))$}};
+			%
+			\path[->,font=\scriptsize]
+				(A) edge node[left]{$\chi$} (A')
+				(A) edge node[above]{$\phi \odot \phi$} (B)
+				(B) edge node[right]{$\lF_\odot$} (B')
+				(A') edge node [left] {$\lF_\odot \otimes \lF_\odot$} (A'')
+				(B') edge node [right] {$\lF(\chi)$} (B'')
+				(A'') edge node[above]{$\phi$} (B'');
+		\end{tikzpicture}
+		%
+		\quad
+		%
+		\begin{tikzpicture}
+			\node (A) at (0,1.5) {\footnotesize{$U_{\lF(a)} \otimes U_{\lF(b)}$}};
+			\node (A') at (0,0) {\footnotesize{$U_{\lF(a)} \otimes U_{\lF(b)}$}};
+			\node (B) at (2,1.5) {\footnotesize{$U_{\lF(a \otimes b)} $}};
+			\node (B') at (2,0) {\footnotesize{$\lF(U_{a \otimes b})$}};
+			\node (A'') at (0,-1.5) {\footnotesize{$\lF(U_a) \otimes \lF(U_b)$}};
+			\node (B'') at (2,-1.5) {\footnotesize{$\lF(U_a \otimes U_b) $}};
+			%
+			\path[->,font=\scriptsize]
+				(A) edge node[left]{$\mu$} (A')
+				(A') edge node [left] {$\lF_\mu \otimes \lF_\mu$} (A'')
+				(B') edge node [right] {$\lF \circ \mu$} (B'')
+				(A) edge node[above]{$U_\phi$} (B)
+				(B) edge node[right]{$\lF_U$} (B')
+				(A'') edge node[above]{$\phi$} (B'');
+		\end{tikzpicture}
+		\end{equation}
+}
+\end{itemize}
+%\noindent
+%Unpacking this definition, one obtains a number of diagrams which can be found after \cite[Definition 2.14]{HS}.
 {\chris Also, could we expand this definition in terms of the functors $\lF_0$ and $\lF_1$ as we usually do?}

### 2020-12-29 cospans.tex
small edits

@@
 
-The ``corresponding pseudofunctor'' comes from the so-called monoidal Grothendieck construction, and the conditions of this theorem related to the existence of colimits as well as left adjoints for opfibrations.
+The ``corresponding pseudofunctor'' comes from the so-called monoidal Grothendieck construction, and the conditions of this theorem relate to the existence of colimits as well as left adjoints for opfibrations.
 We first sketch the relevant underlying framework in detail, and then we proceed to the proof of the theorem.
@@
 
-Finally, the rest of the axioms of \cref{defn:monoidal_double_functor} hold and thus the double isomorphism \cref{eq:doubleiso} is an isomorphism of symmetric monoidal double categories. 
+Finally, the rest of the axioms of \cref{defn:monoidal_double_functor} hold: on the cospan level they are easy to verify, whereas on the decoration level they entail non-trivial calculations involving universal property arguments.
+In conclusion, the double isomorphism \cref{eq:doubleiso} is an isomorphism of symmetric monoidal double categories.
 \end{proof}

### 2020-12-29 cospans.tex
varios changes, including Def. A.9

@@
 % in LaTeX
-% 2020/12/24
+% 2020/12/29
 
@@
 We prove that under certain conditions these two constructions become equivalent when we take $\X = \int F$ to be the Grothendieck category of $F$.
-We illustrate these ideas with applications to electrical circuits, Petri nets, epidemiology and dynamical systems.
+We illustrate these ideas with applications to electrical circuits, Petri nets, dynamical systems and epidemiological modeling.
 \end{abstract}
@@
 We do this merely to reduce the size of  our diagrams; the reader can reinsert the morphism $F(!_0)$ where needed.
-%%% see if you like this!
-- jb
-%%% Christina: looks nice!
 
@@
 
-Regarding the assumptions of the above corollary, notice that since $\A$ is cocartesian monoidal, the initial lax monoidal pseudofunc\-tor structure $(F,\phi,\phi_0)$ gives rise to a specific symmetric monoidal structure on the fibers $F(a)$ in terms of $\phi,\phi_0$, given explicitly by \cref{eq:explicitstructure1}.
-Since we now ask that the pseudofunctor $F\colon \A\to\SMC$ factors through $\Rex$, this fiberwise monoidal structure is required to be cocartesian, namely \cref{eq:explicitstructure1} gives coproducts and an initial object in each $F(a)$.
+Regarding the assumptions of the above corollary, notice that since $\A$ is cocartesian monoidal, the lax monoidal pseudofunc\-tor structure $(F,\phi,\phi_0)$ gives rise to a specific symmetric monoidal structure on the fibers $F(a)$ in terms of $\phi,\phi_0$, given explicitly by \cref{eq:explicitstructure1}.
+Since we now ask that the pseudofunctor $F\maps \A\to\SMC$ factors through $\Rex$, this fiberwise monoidal structure is required to be cocartesian, namely \cref{eq:explicitstructure1} gives coproducts and an initial object in each $F(a)$.
 
@@
 
-By \cref{cor:fcocMonGroth}, when the corresponding pseudofunctor $F\colon\A\to\SMC$ factors through $\Rex$, the Gro\-the\-ndieck construction gives rise to a category $\inta F$ with finite colimits such that the corresponding opfibration $U\maps\inta{F}\to\A$ (strictly) preserves them.
-Moreover, by \cref{prop:opfibtolari}, $U$ has a left adjoint $L\maps\A\to\inta F$ with $UL=1_\A$.
-Diagrammatically,
+By \cref{cor:fcocMonGroth}, since the corresponding pseudofunctor $F\maps\A\to\SMC$ factors through $\Rex$, the Gro\-the\-ndieck construction gives rise to a category $\inta F$ with finite colimits such that the corresponding opfibration $U\maps\inta{F}\to\A$ preserves them.
+Using \cref{lem:fibrewiselimits} we choose finite colimits in $\inta{F}$ such that
+$U$ strictly preserves these chosen colimits (which were already chosen in $A$).  By \cref{prop:opfibtolari}, $U$ has a left adjoint $L\maps\A\to\inta F$ with $UL=1_\A$. Diagrammatically,
 \begin{equation}\label{eq:FtoL}
@@
 
-Building towards an isomorphism of the above described double categories, we now define a double functor
+Building towards an isomorphism of the above described double categories, we now define a double functor sending structured cospans to decorated cospans:
 \begin{displaymath}
@@
 
-Moreover, the monoidal unit $I_1$ for $F\lCsp_1$, given by \cref{eq:monoidalunitFCsp}, is mapped under $\lE_1$ to the identity cospan on $0_\A$ with the trivial decoration on its apex, so $\lE_1$ strictly preserves the monoidal unit.
-%%% Under our new assumptions it's really true!
+Moreover, the monoidal unit $I_1$ for ${}_L \int \lCsp(\int F)$ is mapped under $\lE_1$ to the decorated cospan given in \cref{eq:monoidalunitFCsp}, so $\lE_1$ strictly preserves the monoidal unit.
+%%% I think I have it right now.
 - jb
-%%% Christina: sorry I think E_1 goes in the opposite direction!
 It can be verified that with this structure, $\lE_1$ is also a symmetric monoidal functor.
 
-Finally, the rest of the axioms of \cref{defn:monoidal_double_functor} hold: on the cospan level they are easy to verify, whereas on the decoration level they entail non-trivial calculations involving universal property arguments.
+Finally, the rest of the axioms of \cref{defn:monoidal_double_functor} hold: on the cospan level they are easy to verify, whereas on the decoration level they entail nontrivial calculations involving universal property arguments.
 In conclusion, the double isomorphism \cref{eq:doubleiso} is an isomorphism of symmetric monoidal double categories.
@@
 \item{for every composable pair of horizontal 1-cells $M$ and $N$ in $\lD$, a natural transformation $\phi_{M,N} \maps \lF(N) \odot \lF(M) \to \lF(N \odot M)$ called the \define{composite comparison} and for every object $a$ in $\lD$, a natural transformation $\phi_a \maps U_{\lF_0(a)} \to \lF_1(U_a)$ called the \define{unit comparison}.
-The components of each of these natural transformations are globular isomorphisms which satisfy coherence axioms analogous to those of a monoidal functor.}
+The components of each of these natural transformations are globular isomorphisms that must obey coherence laws analogous to those of a monoidal functor.}
 \end{itemize}
@@
 
+\begin{comment}
 \begin{defn}\label{def:fullfaithful}
@@
 \end{thm}
+\end{comment}
 
@@
 \end{itemize}
-%\noindent
-%Unpacking this definition, one obtains a number of diagrams which can be found after \cite[Definition 2.14]{HS}.
-{\chris Also, could we expand this definition in terms of the functors $\lF_0$ and $\lF_1$ as we usually do?}
-
-WE NEED TO SAY BRIEFLY WHAT A SYMMETRIC MONOIDAL DOUBLE ISOMORPHISM, IF WE USE THIS CONCEPT IN OUR BIG RESULT, \cref{thm:equiv}.
-CLAIM: $\lD$ and $\lE$ be symmetric monoidal double categories and let $\lF \maps \lD \to \lE$ be a symmetric monoidal double functor.
-If $\lF$ is part of a double equivalence, then $\lF$ is in fact part of a symmetric monoidal double equivalence, and $\lD$ and $\lE$ are equivalent as symmetric monoidal double categories.
+\noindent
+
+\begin{defn}\label{def:isomorphism}
+An \define{isomorphism} of symmetric monoidal categories is a symmetric monoidal 
+double functor $\lF \maps \lD \to \lE$ that has an inverse.
+\end{defn}
+
+A symmetric monoidal double functor is an isomorphism if
+it is bijective on objects, vertical 1-morphisms, horizontal 1-cells and 2-morphisms.
 

### 2020-12-30 cospans.tex
small fixed: \colon -> \maps, etc.

@@
 Take $\A$ to have finite colimits and let $(F,\phi,\phi_0) \maps (A,+) \to (\Cat,\times)$ be a lax monoidal pseudofunctor.
-We shall define the category of objects $F\lCsp_0$, the category of arrows $F\lCsp_1$, as well as the four structure functors which tie them together: the source and target functors $S,T \colon F\lCsp_1 \to F\lCsp_0$, the unit functor $U \colon F\lCsp_0 \to F\lCsp_1$, and the composition functor $\odot \colon F\lCsp_1 \times_{F\lCsp_0} F\lCsp_1 \to F\lCsp_1$.
+We shall define the category of objects $F\lCsp_0$, the category of arrows $F\lCsp_1$, as well as the four structure functors which tie them together: the source and target functors $S,T \maps F\lCsp_1 \to F\lCsp_0$, the unit functor $U \maps F\lCsp_0 \to F\lCsp_1$, and the composition functor $\odot \maps F\lCsp_1 \times_{F\lCsp_0} F\lCsp_1 \to F\lCsp_1$.
 
@@
 \end{equation}
-where if $\tau \colon F(h)(x) \to x'$ and $\tau' \colon F(h')(x') \to x''$ are the decoration morphisms, 
+where if $\tau \maps F(h)(x) \to x'$ and $\tau' \maps F(h')(x') \to x''$ are the decoration morphisms, 
 \begin{equation}\label{eq:tauofverticalcomposite}
@@
 \end{equation}
-together with the decoration morphism $\tau_{\beta \odot \alpha} \colon F(h_1 +_g h_2)(y \odot x) \to (y' \odot x')$ given by the diagram:
+together with the decoration morphism $\tau_{\beta \odot \alpha} \maps F(h_1 +_g h_2)(y \odot x) \to (y' \odot x')$ given by the diagram:
 \begin{equation}\label{eq:decohorizontalcompo}
@@
 All axioms for a symmetric monoidal category can be verified, %see \cite[Theorem 4.1.3]{CourserThesis}, 
-and it is easy to see that with these structures, the source and target functors $S,T\colon F\lCsp_1\to F\lCsp_0$ are symmetric strict monoidal.
+and it is easy to see that with these structures, the source and target functors $S,T\maps F\lCsp_1\to F\lCsp_0$ are symmetric strict monoidal.
 
@@
 where the legs of the cospan are the sums of the dashed ones of the appropriate diagrams \cref{eq:dcospanscomposition}.
-Thus the (globular) cospan isomorphism is the canonical universal map between the colimit of the same diagram obtained in two different ways $\hat{\chi}\colon(m_1+n_1)+_{b+b'}(m_2+n_2)\cong(m_1+_b m_2)+(n_1+_{b'}n_2)$, and the decoration isomorphism can be built in a similar way using coherent isomorphisms as follows:
+Thus the (globular) cospan isomorphism is the canonical universal map between the colimit of the same diagram obtained in two different ways $\hat{\chi}\maps (m_1+n_1)+_{b+b'}(m_2+n_2)\cong(m_1+_b m_2)+(n_1+_{b'}n_2)$, and the decoration isomorphism can be built in a similar way using coherent isomorphisms as follows:
 \begin{equation}\label{eq:interchangedeco}
@@
 \end{itemize}
-The induced double functor $\lH \colon F\lCsp \to F'\lCsp$ is defined as follows:
+The induced double functor $\lH \maps F\lCsp \to F'\lCsp$ is defined as follows:
 \begin{itemize}
 \item The image of an object $a \in F\lCsp_0=\A$ is the object $H(a) \in F'\lCsp_0=\A'$.
-\item The image of a vertical 1-morphism $f \colon a \to b$ is the vertical 1-morphism $H(f) \colon H(a) \to H(b)$. 
+\item The image of a vertical 1-morphism $f \maps a \to b$ is the vertical 1-morphism $H(f) \maps H(a) \to H(b)$. 
 \end{itemize}
@@
 \end{align*}
-\item The image of a map of decorated cospans $\alpha \colon M \to N$ in $F\lCsp$ is the map of $F'$-decorated cospans $\lH(\alpha)$ in $F'\lCsp$
+\item The image of a map of decorated cospans $\alpha \maps M \to N$ in $F\lCsp$ is the map of $F'$-decorated cospans $\lH(\alpha)$ in $F'\lCsp$
 \[
@@
 \]
-where a decoration morphism $\tau \colon F(h)(x) \to x'$ is mapped to a 
+where a decoration morphism $\tau \maps F(h)(x) \to x'$ is mapped to a 
 decoration morphism as follows:
@@
 If $F$ is a symmetric lax monoidal pseudofunctor, the induced monoidal structure in $\inta F$ is symmetric via
-$$\left(\beta_{a,b},(u_{a,b})_{x,y}\right)\colon \left(a+b,\phi_{a,b}(x,y)\right)\simrightarrow\left(b+a,\phi_{b,a}(y,x)\right)$$ where $\beta$ is the canonical symmetry for $\A$ and $u$ is the natural isomorphism of \cref{eq:braidedpseudofun}.
+$$\left(\beta_{a,b},(u_{a,b})_{x,y}\right)\maps \left(a+b,\phi_{a,b}(x,y)\right)\simrightarrow\left(b+a,\phi_{b,a}(y,x)\right)$$ where $\beta$ is the canonical symmetry for $\A$ and $u$ is the natural isomorphism of \cref{eq:braidedpseudofun}.
 
@@
 The second part formulates the existence of colimits \emph{globally} in the total category $\inta F$, and if we let $\J$ range over all finite categories it says that $\X$ has finite colimits and $U$ preserves all finite colimits.
-As an example, suppose that $\A$ has pushouts and a Grothendieck opfibration $U \colon \inta F \to\A$ has fiberwise pushouts preserved by its reindexing functors.
+As an example, suppose that $\A$ has pushouts and a Grothendieck opfibration $U \maps \inta F \to\A$ has fiberwise pushouts preserved by its reindexing functors.
 We can construct pushouts in $\inta F$ as follows:
@@
 
-We now have all the necessary background to formally construct an isomorphism between the double category of decorated cospans and the double category of structured cospans, starting from a symmetric lax monoidal pseudofunctor $F \maps (\A, +) \to (\Cat, \times)$ whose corresponding pseudofunctor $F\colon \A\to\SMC$ factors through $\Rex$.
+We now have all the necessary background to formally construct an isomorphism between the double category of decorated cospans and the double category of structured cospans, starting from a symmetric lax monoidal pseudofunctor $F \maps (\A, +) \to (\Cat, \times)$ whose corresponding pseudofunctor $ F\maps \A \to \SMC$ factors through $\Rex$.
 
@@
 \end{displaymath}
-where $\varepsilon_x\colon LU(x)=L(a)\to x$ is the counit of the adjunction $L\dashv U$.
+where $\varepsilon_x \maps LU(x)=L(a)\to x$ is the counit of the adjunction $L\dashv U$.
 The fact that $U$ strictly preserves pushouts is necessary to show that the pushout is mapped, via $U$, directly down to $b$.
@@
 \item For each object $x \in \lE$, we can find an object $a \in \lD$ together with a vertical 1-isomorphism $\alpha_x \maps \lF(a) \to x$, and
-\item For each horizontal 1-cell $N \maps x_1 \to x_2$  of $\lE$, we can find a horizontal 1-cell $M \maps a_1 \to a_2$ of $\lD$ and a 2-isomorphism $a_{N} \colon \lF(M) \to N$ in $\lE$ as in the following diagram:
+\item For each horizontal 1-cell $N \maps x_1 \to x_2$  of $\lE$, we can find a horizontal 1-cell $M \maps a_1 \to a_2$ of $\lD$ and a 2-isomorphism $a_{N} \maps \lF(M) \to N$ in $\lE$ as in the following diagram:
 \[
@@
 \begin{defn}
-Two double functors $\lF \colon \lD \to \lE$ and $\lG \colon \lE \to \lD$ form a \define{double equivalence} if there exist double natural transformations $\mathbb{G} \lF \cong 1_\lD$ and $\lF \mathbb{G} \cong 1_\lE$.
+Two double functors $\lF \maps \lD \to \lE$ and $\lG \maps \lE \to \lD$ form a \define{double equivalence} if there exist double natural transformations $\mathbb{G} \lF \cong 1_\lD$ and $\lF \mathbb{G} \cong 1_\lE$.
 \end{defn}
@@
 \begin{defn}\label{defn:monoidal_double_functor}
-Given symmetric monoidal double categories $\lD$ and $\lE$, a \define{symmetric monoidal double functor} $\lF \colon \lD \to \lE$ is a double functor $\lF$ together with transformations $\theta \colon {\otimes \circ (\lF,\lF)} \to \lF \circ \otimes$ and $\theta_U \colon I_\lE \to \lF \circ I_\lD$ that satisfy the usual coherence axioms for a symmetric monoidal functor with respect to $\otimes$.
+Given symmetric monoidal double categories $\lD$ and $\lE$, a \define{symmetric monoidal double functor} $\lF \maps \lD \to \lE$ is a double functor $\lF$ together with transformations $\theta \maps {\otimes \circ (\lF,\lF)} \to \lF \circ \otimes$ and $\theta_U \maps I_\lE \to \lF \circ I_\lD$ that satisfy the usual coherence axioms for a symmetric monoidal functor with respect to $\otimes$.
 \end{defn}
@@
 \noindent
-Explicitly, a symmetric monoidal double functor is a double functor $\lF \colon \lD \to \lE$ such that:
+Explicitly, a symmetric monoidal double functor is a double functor $\lF \maps \lD \to \lE$ such that:
 \begin{itemize}
@@
 		\path[->,font=\scriptsize,>=angle 90]
-			(A) edge node[above]{$\widehat{f}$} (B)
+			(A) edge node[above]{$\hat{f}$} (B)
 			(A) edge node[left]{$f$} (A')
@@
 			(B) edge node[right]{$f$} (B')
-			(A') edge node[below]{ $\widehat{f}$} (B');
+			(A') edge node[below]{ $\hat{f}$} (B');
 		%
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$\tau_1 \colon F(\beta +_\beta \beta)((x_1 \otimes y_1)\odot(x_2\otimes y_2)) \to (y_1 \otimes x_1) \odot (y_2 \otimes x_2)$};
-\node (B) at (0,-.5) {$\tau_2 \colon F(\hat{\chi})((y_1 \otimes x_1)\odot(y_2 \otimes x_2)) \to (y_1 \odot y_2) \otimes (x_1 \odot x_2)$};
-\node (C) at (0,-1) {$\tau_3 \colon F(\hat{\chi})((x_1 \otimes y_1)\odot(x_2 \otimes y_2)) \to (x_1 \odot x_2) \otimes (y_1 \odot y_2)$};
-\node (D) at (0,-1.5) {$\tau_4 \colon F(\beta)((x_1\odot x_2)\otimes(y_1\odot y_2)) \to (y_1\odot y_2) \otimes (x_1\odot x_2)$};
+\node (A) at (0,0) {$\tau_1 \maps F(\beta +_\beta \beta)((x_1 \otimes y_1)\odot(x_2\otimes y_2)) \to (y_1 \otimes x_1) \odot (y_2 \otimes x_2)$};
+\node (B) at (0,-.5) {$\tau_2 \maps F(\hat{\chi})((y_1 \otimes x_1)\odot(y_2 \otimes x_2)) \to (y_1 \odot y_2) \otimes (x_1 \odot x_2)$};
+\node (C) at (0,-1) {$\tau_3 \maps F(\hat{\chi})((x_1 \otimes y_1)\odot(x_2 \otimes y_2)) \to (x_1 \odot x_2) \otimes (y_1 \odot y_2)$};
+\node (D) at (0,-1.5) {$\tau_4 \maps F(\beta)((x_1\odot x_2)\otimes(y_1\odot y_2)) \to (y_1\odot y_2) \otimes (x_1\odot x_2)$};
 \path[->,font=\scriptsize,>=angle 90]

### 2020-12-30 cospans.tex
Changed proof of Lemma 4.1; explained decoration morphism tau_f there

@@
 \begin{proof}
-We show that any vertical 1-morphism $f \maps a \to b'$ in $F\lCsp$ has a companion and a conjoint.  This horizontal 1-cell $\hat{f}$:
+We show that any vertical 1-morphism $f \maps a \to b'$ in $F\lCsp$ has a companion and a conjoint.  First, we can make ths horizontal 1-cell $\hat{f}$:
 \begin{displaymath}
- a\xrightarrow{f}b\xleftarrow{1}b,\quad \bot_{b} \in F(b)
+ a\xrightarrow{\;f\;}b\xleftarrow{\;1\;}b,\quad \bot_{b} \in F(b)
 \end{displaymath}
-where $\bot_b$ is the trivial decoration as in \cref{eq:UFCsp}, is a companion of $f$ because the following two 2-morphisms, having $\hat{f}$ as
-source and target:
+where $\bot_b$ is the trivial decoration as in \cref{eq:UFCsp}, into a companion of $f$ using the following 2-morphisms:
 \[
@@
 \]
-{\chris The decoration morphisms should be both isomorphisms due to pseudofunctoriality of F...}
-satisfy the equations required of a companion \cref{eq:CompanionEq}, using vertical \cref{eq:verticalcompo} and horizontal \cref{eq:horizontalcompo} composition of 2-cells in this double category:
+where the decoration morphism $\tau_f$ is the isomorphism given by the pseudofunctoriality of $F$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$\one$};
+\node (B) at (1,0) {$F(0)$};
+\node (C) at (2.2,0.5) {$F(a)$};
+\node (C') at (2.2,-0.5) {$F(b)$};
+\node (D) at (1.8,0) {{\rotatebox{90}{$\cong$}}$\Downarrow$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$\phi_0$} (B)
+(B) edge node[above]{$F(!_a)\;$} (C)
+(B) edge node[below]{$F(!_b)\;\;$} (C')
+(C) edge node[right]{$F(f)$} (C');
+\end{tikzpicture}
+\]
+These 2-morphisms satisfy equations required of a companion \cref{eq:CompanionEq}, using vertical \cref{eq:verticalcompo} and horizontal \cref{eq:horizontalcompo} composition of 2-cells in this double category:
 \[
@@
 \]
-and right hand sides of the above two equations are given respectively by the 2-morphisms $U_f$ and $1_{\hat{f}}$.
+since the right hand sides of the above two equations are given respectively by the 2-morphisms $U_f$ and $1_{\hat{f}}$.
 The conjoint of $f$ is given by this horizontal 1-cell $\check{f}$, which is just the opposite of the companion above:

### 2020-12-30 cospans.tex
rewrote proof of Lemma 4.1 and added description of tau_f
various small edits

@@
 % in LaTeX
-% 2020/12/29
+% 2020/12/30
 
@@
 There is a much simpler proof of the above theorem when the hypothesis of \cref{thm:equiv} hold.
-In this case we show, in the proof of\cref{thm:equiv}, that the decorated cospan double category $F \lCsp$ is isomorphic to a certain double category ${}_L \lCsp(\inta  F)$ constructed using \emph{structured} cospans.
+In this case we show, in the proof of \cref{thm:equiv}, that the decorated cospan double category $F \lCsp$ is isomorphic to a certain double category ${}_L \lCsp(\inta  F)$ constructed using \emph{structured} cospans.
 We also show that under this isomorphism, all the symmetric monoidal structure of $F \lCsp$---the tensor product, associator, etc.---matches that for  ${}_L \lCsp(\inta  F)$, which we have proved to obey the axioms of a symmetric monoidal double category (see \cref{thm:SC}).
@@
 
+%%% Combining \cref{lem:MonGroth,lem:fibrewiselimits}, we obtain the following corollary that sets up the statement of \cref{thm:equiv}.
+
 \begin{cor}\label{cor:fcocMonGroth}
  Suppose $\A$ has finite colimits and $F \maps (\A,+) \to (\Cat,\times)$ is a symmetric lax monoidal pseudofunctor.
-If the corresponding pseudofunctor $F  \maps \A \to \SMC$ from \cref{lem:MonGroth} factors through $\Rex$, then $\inta F$ has all finite colimits and the induced opfibration $U\maps \inta F \to \A$ preserves them.
+If the corresponding pseudofunctor $F  \maps \A \to \SMC$ from \cref{lem:MonGroth} factors through $\Rex$, then $\inta F$ has all finite colimits
+ %%% which can be chosen in a way that the induced opfibration strictly preserves them.
+ and the induced opfibration $U\maps \inta F \to \A$ preserves them.
 \end{cor}
@@
 Using \cref{lem:fibrewiselimits} we choose finite colimits in $\inta{F}$ such that
-$U$ strictly preserves these chosen colimits (which were already chosen in $A$).  By \cref{prop:opfibtolari}, $U$ has a left adjoint $L\maps\A\to\inta F$ with $UL=1_\A$. Diagrammatically,
+$U$ strictly preserves these chosen colimits (which were already chosen in $A$).  
+%%% By \cref{cor:fcocMonGroth}, since the corresponding pseudofunctor $F\maps\A\to\SMC$ factors through $\Rex$, the Gro\-the\-ndieck construction gives rise to a category $\inta F$ where we can choose finite colimits in a way that the corresponding opfibration $U\maps\inta{F}\to\A$ strictly preserves them.
+
+By \cref{prop:opfibtolari}, $U$ has a left adjoint $L\maps\A\to\inta F$ with $UL=1_\A$. Diagrammatically,
 \begin{equation}\label{eq:FtoL}
@@
 
-Moreover, the monoidal unit $I_1$ for ${}_L \int \lCsp(\int F)$ is mapped under $\lE_1$ to the decorated cospan given in \cref{eq:monoidalunitFCsp}, so $\lE_1$ strictly preserves the monoidal unit.
-%%% I think I have it right now.
-- jb
+Moreover, the monoidal unit $I_1$ for ${}_L \lCsp(\inta F)$ is mapped under $\lE_1$ to the decorated cospan given in \cref{eq:monoidalunitFCsp}, so $\lE_1$ strictly preserves the monoidal unit.
 It can be verified that with this structure, $\lE_1$ is also a symmetric monoidal functor.
@@
 \begin{proof}
-We show that any vertical 1-morphism $f \maps a \to b'$ in $F\lCsp$ has a companion and a conjoint.  First, we can make ths horizontal 1-cell $\hat{f}$:
-\begin{displaymath}
- a\xrightarrow{\;f\;}b\xleftarrow{\;1\;}b,\quad \bot_{b} \in F(b)
-\end{displaymath}
+We show that any vertical 1-morphism $f \maps a \to b'$ in $F\lCsp$ has a companion and a conjoint.  First, we can make this horizontal 1-cell $\hat{f}$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$a$};
+\node (B) at (1,0) {$b$};
+\node (C) at (2,0) {$b$};
+\node (D) at (4,0) {$\bot_b \in F(b)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$f$} (B)
+(C) edge node[above]{$1$} (B);
+\end{tikzpicture}
+\]
 where $\bot_b$ is the trivial decoration as in \cref{eq:UFCsp}, into a companion of $f$ using the following 2-morphisms:
@@
 \node (C') at (2.2,-0.5) {$F(b)$};
-\node (D) at (1.8,0) {{\rotatebox{90}{$\cong$}}$\Downarrow$};
+\node (D) at (1.8,0) {$\cong$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 The conjoint of $f$ is given by this horizontal 1-cell $\check{f}$, which is just the opposite of the companion above:
-\begin{displaymath}
- b\xrightarrow{1}b\xleftarrow{f}b,\quad \bot_{b} \in F(b)
-\end{displaymath}
-Just as $\hat{f}$ obeys the equations required of a companion, $\check{f}$ obeys the equations required of a conjoint.
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$b$};
+\node (B) at (1,0) {$b$};
+\node (C) at (2,0) {$a$};
+\node (D) at (4,0) {$\bot_b \in F(b)$.};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$1$} (B)
+(C) edge node[above]{$f$} (B);
+\end{tikzpicture}
+\]
+Just as $\hat{f}$ obeys the equations required of a companion, $\check{f}$ obeys the equations required of a conjoint with similar structure 2-morphisms to those of a companion above.
 \end{proof}

### 2020-12-30 cospans.tex
changed "equivalent/equivalence" to "isomorphic/isomorphism" where needed

@@
 Generalizing the work of Fong, we show that in this situation there is a symmetric monoidal double category whose objects are those of $\A$ and whose horizontal 1-cells are decorated cospans.
-We prove that under certain conditions these two constructions become equivalent when we take $\X = \int F$ to be the Grothendieck category of $F$.
+We prove that under certain conditions these two constructions become isomorphic when we take $\X = \int F$ to be the Grothendieck category of $F$.
 We illustrate these ideas with applications to electrical circuits, Petri nets, dynamical systems and epidemiological modeling.
@@
 
-Here we give sufficient conditions for a decorated cospan double category to be equivalent to a structured cospan double category.
+Here we give sufficient conditions for a decorated cospan double category to be equivalent---and in fact, isomorphic---to a structured cospan double category.
 Suppose $\A$ has finite colimits and $F \maps (\A , +) \to (\Cat, \times)$ is a symmetric lax monoidal pseudofunctor.
@@
 From the accompanying left adjoint $L \maps \A \to \X$, we  construct a symmetric monoidal double category ${}_L \lCsp(\X)$ of structured cospans.
-Finally, in \cref{thm:equiv} we prove that this structured cospan double category ${}_L \lCsp(\X)$ is equivalent to the decorated cospan double category $F \lCsp$.
+Finally, in \cref{thm:equiv} we prove that this structured cospan double category ${}_L \lCsp(\X)$ is isomorphic to the decorated cospan double category $F \lCsp$.
 
@@
 In \cref{DecCospansDoubleCat}, we construct the symmetric monoidal double category $F\lCsp$ and we define maps between decorated cospan double categories.
-In \cref{EquivDoubleCats}, we briefly review the structured cospans framework and prove that the double categorical versions of decorated cospans and structured cospans are equivalent under suitable conditions.
-In \cref{spinoffs}, we establish the equivalence between structured and decorated cospans at the level of bicategories and categories (via decategorification).
+In \cref{EquivDoubleCats}, we briefly review the structured cospans framework and prove that the double categorical versions of decorated cospans and structured cospans are isomorphic under suitable conditions.
+In \cref{spinoffs}, we establish the isomorphism between structured and decorated cospans at the level of bicategories and categories (via decategorification).
 Finally, in \cref{Applications}, we describe applications to electrical circuits, Petri nets, epidemiology and dynamical systems.
@@
 \begin{proof} 
-Hansen and Shulman \cite{HS} showed that the passage from symmetric monoidal double categories to symmetric monoidal bicategories is  functorial in a suitable sense, implying that an equivalence of symmetric monoidal double categories $\lD \simeq \lD'$ gives an equivalence of symmetric monoidal bicategories $\bD \simeq \bD'$.
-Since the process of decategorifying a bicategory merely discards 2-morphisms and takes isomorphism classes of 1-morphisms, the equivalence of symmetric monoidal bicategories $\bD \simeq \bD'$ in turn induces an equivalence of symmetric monoidal categories $\D \simeq \D'$.
+Hansen and Shulman \cite{HS} showed that the passage from symmetric monoidal double categories to symmetric monoidal bicategories is functorial in a suitable sense.
+This implies that an isomorphism of symmetric monoidal double categories $\lD \simeq \lD'$ gives an isomorphism of symmetric monoidal bicategories $\bD \simeq \bD'$.
+Since the process of decategorifying a bicategory merely discards 2-morphisms and takes isomorphism classes of 1-morphisms, the isomorphism of symmetric monoidal bicategories $\bD \simeq \bD'$ in turn induces an isomorphism of symmetric monoidal categories $\D \simeq \D'$.
 Thus, the theorem follows from \cref{thm:equiv}.
@@
 Below we compare the two approaches in applications to graphs, electrical circuits, Petri nets, reaction networks and dynamical systems.
-In many cases, \cref{thm:equiv} shows that the structured and decorated cospan approaches are equivalent: \cref{subsec:graphs,subsec:circuits,subsec:petri} illustrate this.
+In many cases, \cref{thm:equiv} shows that the structured and decorated cospan approaches are equivalent: \cref{subsec:graphs, subsec:circuits,subsec:petri} illustrate this.
 However, in \cref{subsec:petrirates} we show that open dynamical systems can only be treated using decorated cospans.
@@
 \end{itemize}
-This gives a symmetric monoidal double category $F \lCsp$, and using \cref{thm:equiv} we can show that this is equivalent, as a symmetric monoidal double category, to ${}_L \lCsp(\Graph_\La)$.
+This gives a symmetric monoidal double category $F \lCsp$, and using \cref{thm:equiv} we can show that this is isomorphic, as a symmetric monoidal double category, to ${}_L \lCsp(\Graph_\La)$.
 
@@
 \end{itemize}
-This gives a symmetric monoidal double category $F \lCsp$, and using \cref{thm:equiv} we can show that this is equivalent, as a symmetric monoidal double category, to ${}_L \lCsp(\Petri)$.
+This gives a symmetric monoidal double category $F \lCsp$, and using \cref{thm:equiv} we can show that this is isomorphic, as a symmetric monoidal double category, to ${}_L \lCsp(\Petri)$.
 
@@
 \end{itemize}
-This gives a symmetric monoidal double category $F \lCsp$, and using \cref{thm:equiv} we can show that this is equivalent, as a symmetric monoidal double category, to ${}_L \lCsp(\Petri_r)$.
+This gives a symmetric monoidal double category $F \lCsp$, and using \cref{thm:equiv} we can show that this is isomorphic, as a symmetric monoidal double category, to ${}_L \lCsp(\Petri_r)$.
 
@@
 
-We now show that decorated cospan double category $D \lCsp$ of open dynamical systems is not equivalent to a structured cospan double category via \cref{thm:equiv}.
+We now show that decorated cospan double category $D \lCsp$ of open dynamical systems is not isomorphic to a structured cospan double category via \cref{thm:equiv}.
 Recall that in that theorem we start with the data required to build a decorated cospan category, namely a symmetric lax monoidal pseudofunctor $F \maps (\A,+) \to (\Cat,\times)$, and show that under certain conditions the resulting opfibration $U \maps \X = \inta F \to \A$ has a left adjoint $L \maps \A \to \X$.
-We then obtain an equivalence between decorated and structured cospan double categories, $F \lCsp \simeq {}_L \Csp(\X)$.
+We then obtain an isomorphism between decorated and structured cospan double categories, $F \lCsp \simeq {}_L \Csp(\X)$.
 We now show that in the case at hand, where $F = D$,  the opfibration $U$ does \emph{not} have a left adjoint.
@@
 We have given conditions under which a decorated cospan double category is isomorphic to a structured cospan double category, in \cref{thm:equiv}.
-The converse question is also interesting: is every structured cospan double category equivalent to a decorated cospan double category?
+The converse question is also interesting: is every structured cospan double category isomorphic to a decorated cospan double category?
 The answer is similar to the previous one: yes, under certain conditions that let us pass from an appropriate functor $L \maps \A \to \X$ to an appropriate pseudofunctor $F \maps \A \to \Cat$.
@@
 As a result, $F$ has now enough structure to induce a double category of decorated cospans $F\lCsp$  as in \cref{DC}.
-Finally, it can be shown that the structured and decorated cospan double categories are equivalent as symmetric monoidal double categories: ${}_L \lCsp(\X) \simeq F\lCsp$.
+Finally, it can be shown that the structured and decorated cospan double categories are isomorphic as symmetric monoidal double categories: ${}_L \lCsp(\X) \simeq F\lCsp$.
 

### 2020-12-30 cospans.tex
dealt with "strict preservation of finite colimits" in Cor. 3.5 and start of proof of Thm. 3.2

@@
 
-%%% Combining \cref{lem:MonGroth,lem:fibrewiselimits}, we obtain the following corollary that sets up the statement of \cref{thm:equiv}.
-
 \begin{cor}\label{cor:fcocMonGroth}
- Suppose $\A$ has finite colimits and $F \maps (\A,+) \to (\Cat,\times)$ is a symmetric lax monoidal pseudofunctor.
-If the corresponding pseudofunctor $F  \maps \A \to \SMC$ from \cref{lem:MonGroth} factors through $\Rex$, then $\inta F$ has all finite colimits
- %%% which can be chosen in a way that the induced opfibration strictly preserves them.
- and the induced opfibration $U\maps \inta F \to \A$ preserves them.
+ Suppose $\A$ has finite colimits and $F \maps (\A,+) \to (\Cat,\times)$ is a symmetric lax monoidal pseudofunctor for which the corresponding pseudofunctor $F  \maps \A \to \SMC$ from \cref{lem:MonGroth} factors through $\Rex$.
+Then $\inta F$ has all finite colimits and  the induced opfibration $U\maps \inta F \to \A$ preserves them.
+Moreover we can choose finite colimits in $\inta F$ so that $U$ preserves them strictly.
 \end{cor}
@@
 
-By \cref{cor:fcocMonGroth}, since the corresponding pseudofunctor $F\maps\A\to\SMC$ factors through $\Rex$, the Gro\-the\-ndieck construction gives rise to a category $\inta F$ with finite colimits such that the corresponding opfibration $U\maps\inta{F}\to\A$ preserves them.
-Using \cref{lem:fibrewiselimits} we choose finite colimits in $\inta{F}$ such that
-$U$ strictly preserves these chosen colimits (which were already chosen in $A$).  
-%%% By \cref{cor:fcocMonGroth}, since the corresponding pseudofunctor $F\maps\A\to\SMC$ factors through $\Rex$, the Gro\-the\-ndieck construction gives rise to a category $\inta F$ where we can choose finite colimits in a way that the corresponding opfibration $U\maps\inta{F}\to\A$ strictly preserves them.
+Since the corresponding pseudofunctor $F \maps \A \to \SMC$ factors through $\Rex$, 
+the Gro\-the\-ndieck construction gives rise to a category $\inta F$ with finite colimits, and 
+we can choose these in such a way that the corresponding opfibration $U \maps \inta F \to \A$ strictly preserves them.  We do this in what follows.
 
@@
 \begin{itemize}
-\item monoidal structures on both $\lD_0$ and $\lD_1$ (each with tensor product denoted $\otimes$, associator $a$, left unitor $\ell$ and right unitor $r$), such that $U \maps \lD_0 \to \lD_1$ strictly preserves the unit object and $S,T \maps \lD_1 \to \lD_0$ are strict monoidal,    %%% got rid of footnote saying that "isomorphic is okay" - jb %%% Great.
+\item monoidal structures on both $\lD_0$ and $\lD_1$ (each with tensor product denoted $\otimes$, associator $a$, left unitor $\ell$ and right unitor $r$), such that $U \maps \lD_0 \to \lD_1$ strictly preserves the unit object and $S,T \maps \lD_1 \to \lD_0$ are strict monoidal,
 \item the structure of a double functor on $\otimes$:

### 2020-12-30 cospans.tex
Update cospans.tex

@@
 Generalizing the work of Fong, we show that in this situation there is a symmetric monoidal double category whose objects are those of $\A$ and whose horizontal 1-cells are decorated cospans.
-We prove that under certain conditions these two constructions become isomorphic when we take $\X = \int F$ to be the Grothendieck category of $F$.
+We prove that under certain conditions these two constructions become isomorphic when we take $\X = \inta F$ to be the Grothendieck category of $F$.
 We illustrate these ideas with applications to electrical circuits, Petri nets, dynamical systems and epidemiological modeling.
@@
 Let $\Rex$ be the 2-category of categories with finite colimits, functors preserving finite colimits, and natural transformations.
-We show that if $F$ factors through $\mathbf{Rex}$ as a pseudofunctor, the opfibration $U \maps \X \to \A$ is also a right adjoint.
+We show that if $F$ factors through $\Rex$ as a pseudofunctor, the opfibration $U \maps \X \to \A$ is also a right adjoint.
 From the accompanying left adjoint $L \maps \A \to \X$, we  construct a symmetric monoidal double category ${}_L \lCsp(\X)$ of structured cospans.
 Finally, in \cref{thm:equiv} we prove that this structured cospan double category ${}_L \lCsp(\X)$ is isomorphic to the decorated cospan double category $F \lCsp$.
+In fact, they are isomorphic as symmetric monoidal double categories.
 
@@
 In \cref{spinoffs}, we establish the isomorphism between structured and decorated cospans at the level of bicategories and categories (via decategorification).
-Finally, in \cref{Applications}, we describe applications to electrical circuits, Petri nets, epidemiology and dynamical systems.
+Finally, in \cref{Applications}, we describe applications to electrical circuits, Petri nets, dynamical systems and epidemiological modeling.
 
@@
 \end{displaymath}
-In a similar way we can construct the initial object and coproducts in $\int F$ from those in the fibers, namely
+In a similar way we can construct the initial object and coproducts in $\inta F$ from those in the fibers, namely
 \begin{equation}\label{eq:fibrewisecoprod}
@@
 
-In \cref{thm:equiv} we gave conditions under which the symmetric monoidal double category of \emph{decorated} cospans $F\lCsp$ is isomorphic to the  symmetric monoidal double category of \emph{structured} cospans ${}_L \lCsp(\int F)$.
+In \cref{thm:equiv} we gave conditions under which the symmetric monoidal double category of \emph{decorated} cospans $F\lCsp$ is isomorphic to the  symmetric monoidal double category of \emph{structured} cospans ${}_L \lCsp(\inta F)$.
 We now show that under the same conditions we get an isomorphism of symmetric monoidal bicategories, and of categories.

### 2020-12-30 cospans.tex
added a tiny bit more about epidemiological models in Sec. 5.4

@@
 Here $I_1(t),I_2(t),I_3(t)$ and $O_1(t)$ are arbitrary smooth functions of time, which describe inflows and outflows at the points $i_1,i_2,i_3 \in X$ and $o_1 \in Y$.
-If we drop these inflow and outflow terms, we obtain an autonomous system of coupled nonlinear first-order ordinary differential equations.
+If we drop these inflow and outflow terms, we obtain a dynamical system: an autonomous system of coupled nonlinear first-order ordinary differential equations.
 In fact these equations are a famous model of infectious disease, the `SIR model', where $S(t)$, $I(t)$ and $R(t)$ describe the populations of susceptible, infected and recovered individuals, respectively.
 The inflow and outflow terms allow individuals to enter or leave the population.
-This in turn lets us couple the SIR model to other models, and build complex models from smaller pieces.
-Recently Halter and Patterson \cite{HP} implemented this idea in software using structured cospans.
-They illustrated the use of this tool by rebuilding part of the COVID-19 model that the UK has been using to make policy decisions.
+This in turn lets us couple the SIR model to other models, and build larger models from smaller pieces.
+
+Recently Halter and Patterson \cite{HP} implemented this idea in a software tool that lets the user build epidemiological models.
+They illustrated the use of their tool by rebuilding part of the COVID-19 model that the UK has been using to make policy decisions.
+The advantage of structured (or decorated) cospans is they let one build complex models like this from smaller parts in a mathematically disciplined way, so one can easily add and change parts, and better understand the effect of doing this.
 

### 2020-12-30 cospans.tex
polished paragraph on Halter-Patterson

@@
 
-Recently Halter and Patterson \cite{HP} implemented this idea in a software tool that lets the user build epidemiological models.
-They illustrated the use of their tool by rebuilding part of the COVID-19 model that the UK has been using to make policy decisions.
-The advantage of structured (or decorated) cospans is they let one build complex models like this from smaller parts in a mathematically disciplined way, so one can easily add and change parts, and better understand the effect of doing this.
+Recently Halter and Patterson \cite{HP} implemented this idea in a software tool that makes it easy to build epidemiological models using structured cospans.
+They used this to rebuild part of the COVID-19 model that the UK has been using to make policy decisions.
+The advantage of using structured or decorated cospans is that one can build complex models from smaller pieces, so one can easily add or change parts, and better understand the effects of doing this.
 

### 2020-12-31 cospans.tex
tiny ref fix

@@
 Below we compare the two approaches in applications to graphs, electrical circuits, Petri nets, reaction networks and dynamical systems.
-In many cases, \cref{thm:equiv} shows that the structured and decorated cospan approaches are equivalent: \cref{subsec:graphs, subsec:circuits,subsec:petri} illustrate this.
+In many cases, \cref{thm:equiv} shows that the structured and decorated cospan approaches are equivalent: \cref{subsec:graphs,subsec:circuits,subsec:petri} illustrate this.
 However, in \cref{subsec:petrirates} we show that open dynamical systems can only be treated using decorated cospans.

### 2020-12-31 cospans.tex
added one unitor in 2.1

@@
 % in LaTeX
-% 2020/12/30
+% 2020/12/31
 
@@
 where $a$ are the associators of $\Cat$ and $\A$ and $\kappa$ is the canonical isomorphism between two colimits of the same diagram in $\A$.
-Similarly the right and left unitors can be constructed, and all data satisfy the axioms of a double category---essentially breaking down to those of the cospan double category of $\A$ and axioms of the lax monoidal pseudofunctor $F$.
-For details of these arguments, see \cite[Theorem~4.1.1]{CourserThesis}.
+
+Similarly the right and left unitors can be constructed: for example, for a horizontal 1-cell $M=(a\to m \leftarrow b,x\in F(m))$, the isomorphism $M\odot U_a\cong M$ is given by the canonical map of cospans $\kappa\colon a+_am\cong m$ along with the isomorphism between decorations
+\begin{displaymath}
+ \scalebox{.9}
+{\begin{tikzcd}[row sep=.15in,ampersand replacement=\&]
+1\ar[r,"\phi_0\times x"]\ar[dd,equal] \& F(0)\times F(m)\ar[dd,phantom,"{\stackrel{\cref{eq:unitality}}{\cong}}"] \ar[dr,"\phi_{0,m}"']\ar[r,"F(!_a)\times 1"] \& F(a)\times F(m)\ar[d,phantom,"{\stackrel{\cref{eq:pseudonaturality}}{\cong}}"]\ar[r,"\phi_{m,a}"] \& F(a+m)\ar[ddr,phantom,"{\cong}"]\ar[r,"F\psi"] \& F(a+_am)\ar[dd,"F(\kappa)"]\\
+\&\& F(0+m)\ar[drr]\ar[ur,"F(!_a\times1)"'] \&\&  \\
+1\ar[rrrr,"x"] \&\phantom{A}\&\&\& F(m)
+ \end{tikzcd}}
+\end{displaymath}
+All data can be verified to satisfy the axioms of a double category---essentially breaking down to those of the cospan double category of $\A$ and axioms of the lax monoidal pseudofunctor $F$.
 \end{proof}

### 2020-12-31 cospans.tex
added ref to Cor. 3.5 near start of proof of Thm. 3.2

@@
 
-\begin{cor}\label{cor:fcocMonGroth}
+\begin{cor} \label{cor:fcocMonGroth}
  Suppose $\A$ has finite colimits and $F \maps (\A,+) \to (\Cat,\times)$ is a symmetric lax monoidal pseudofunctor for which the corresponding pseudofunctor $F  \maps \A \to \SMC$ from \cref{lem:MonGroth} factors through $\Rex$.
@@
 Since the corresponding pseudofunctor $F \maps \A \to \SMC$ factors through $\Rex$, 
-the Gro\-the\-ndieck construction gives rise to a category $\inta F$ with finite colimits, and 
-we can choose these in such a way that the corresponding opfibration $U \maps \inta F \to \A$ strictly preserves them.  We do this in what follows.
+\cref{cor:fcocMonGroth} implies that the Gro\-the\-ndieck construction gives rise to a category $\inta F$ with finite colimits, and we can choose these in such a way that the corresponding opfibration $U \maps \inta F \to \A$ strictly preserves them.
+We do this in what follows.
 

### 2020-12-31 cospans.tex
improved introduction to Section 5

@@
 Below we compare the two approaches in applications to graphs, electrical circuits, Petri nets, reaction networks and dynamical systems.
+
 In many cases, \cref{thm:equiv} shows that the structured and decorated cospan approaches are equivalent: \cref{subsec:graphs,subsec:circuits,subsec:petri} illustrate this.
-However, in \cref{subsec:petrirates} we show that open dynamical systems can only be treated using decorated cospans.
+However, in\cref{subsec:petrirates} we describe a map from `open Petri nets with rates' to open dynamical systems.
+The former are conveniently described using structured cospans, while the latter can only be treated using decorated cospans.
+Here \cref{thm:equiv} serves as a bridge that lets us connect the two formalisms.
 

### 2021-01-02 cospans.tex
Changed the second equation in Lemma 4.1
tiny

@@
 1\ar[r,"\phi_0\times x"]\ar[dd,equal] \& F(0)\times F(m)\ar[dd,phantom,"{\stackrel{\cref{eq:unitality}}{\cong}}"] \ar[dr,"\phi_{0,m}"']\ar[r,"F(!_a)\times 1"] \& F(a)\times F(m)\ar[d,phantom,"{\stackrel{\cref{eq:pseudonaturality}}{\cong}}"]\ar[r,"\phi_{m,a}"] \& F(a+m)\ar[ddr,phantom,"{\cong}"]\ar[r,"F\psi"] \& F(a+_am)\ar[dd,"F(\kappa)"]\\
-\&\& F(0+m)\ar[drr]\ar[ur,"F(!_a\times1)"'] \&\&  \\
-1\ar[rrrr,"x"] \&\phantom{A}\&\&\& F(m)
+\&\& F(0+m)\ar[drr,sloped,"\sim"]\ar[ur,"F(!_a\times1)"'] \&\&  \\
+1\ar[rrrr,"x"'] \&\phantom{A}\&\&\& F(m)
  \end{tikzcd}}
@@
 Explicitly, the left adjoint picks the initial object in the fiber of $a$, namely $L(a)=(a,\bot_a)$ which is expressed as $F(!_a)\circ\phi_0(*)$ according to \cref{eq:explicitstructure1} for $(\phi,\phi_0)$ the monoidal structure of $F$.
-%%% There are many laris, one for each choice of initial object.
-Having fixed our choice of colimits, there is really only one lari, correct?
 
@@
 \]
+%%% Kenny: Commenting out previous equation.
+\begin{comment}
 \[
@@
 \]
-since the right hand sides of the above two equations are given respectively by the 2-morphisms $U_f$ and $1_{\hat{f}}$.
+\end{comment}
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (G) at (-0.75,0.5) {$a$};
+\node (H) at (-0.75,-0.5)  {$b$};
+\node (I) at (-1.5,0.5) {$a$};
+\node (J) at (-1.5,-0.5) {$a$};
+\node (A) at (0,0.5) {$a$};
+\node (A') at (0,-0.5) {$b$};
+\node (B) at (0.75,0.5) {$b$};
+\node (C) at (1.5,0.5) {$b$};
+\node (C') at (1.5,-0.5) {$b$};
+\node (D) at (0.75,-0.5) {$b$};
+\node (E) at (0.75,1) {$\scriptstyle{\bot_{b} \in F(b)}$};
+\node (F) at (2,-0.5) {$\scriptstyle{\bot_{b} \in F(b)}$};
+\node (L) at (2,0) {$\scriptstyle{\tau_{b} = 1_{\bot_{b}}}$};
+\node (E') at (-0.75,1) {$\scriptstyle{\bot_{a} \in F(a)}$};
+\node (F') at (-2.25,-0.5) {$\scriptstyle{\bot_{b} \in F(b)}$};
+\node (L') at (-2.5,0) {$\scriptstyle{\tau_{f} \maps F(f)(\bot_a) \to \bot_{b}}$};
+\node (M) at (2.5,-0.5) {$\scriptstyle{=}$};
+\node (N) at (4.5,0) {$a$};
+\node (O) at (4.5,-1) {$b$};
+\node (P) at (5.25,0) {$b$};
+\node (R) at (6,0) {$b$};
+\node (S) at (6,-1) {$b$};
+\node (T) at (5.25,0.5) {$\scriptstyle{\bot_{b} \in F(b)}$};
+\node (T') at (3.75,0.5) {$\scriptstyle{\bot_a \in F(a)}$};
+\node (U) at (4.5,-1.5) {$\scriptstyle{\bot_{b} \in F(b)}$};
+\node (V) at (4.5,-1.75) {$\scriptstyle{\tau_{\rho_{\hat{f}}} \colon (\bot_b \odot \bot_a) \to \bot_b}$};
+\node (K) at (-1.5,-1.5) {$a$};
+\node (L') at (0,-1.5) {$b$};
+\node (M') at (1.5,-1.5) {$b$};
+\node (N') at (0,-2) {$\scriptstyle{\bot_b \in F(b)}$};
+\node (O') at (0,-2.25) {$\scriptstyle{\tau_{\lambda_{\hat{f}}} \colon (\bot_b \odot \bot_b) \to \bot_b}$};
+\node (W) at (3.75,0) {$a$};
+\node (Y) at (3,0) {$a$};
+\node (Z) at (3,-1) {$a$};
+\path[->,font=\scriptsize,>=angle 90]
+(Y) edge node [left] {$1$} (Z)
+(Y) edge node [above] {$1$} (W)
+(Z) edge node [above] {$f$} (O)
+(N) edge node [above] {$1$} (W)
+(J) edge node [left] {$1$} (K)
+(A') edge node [left] {$1$} (L')
+(C') edge node [left] {$1$} (M')
+(K) edge node[above] {$f$} (L')
+(M') edge node [above] {$1$} (L')
+(N) edge node[left]{$f$} (O)
+(R) edge node[left]{$1$} (S)
+(N) edge node[above]{$f$} (P)
+(R) edge node[above]{$1$} (P)
+(S) edge node[above]{$1$} (O)
+(A) edge node[above]{$f$} (B)
+(C) edge node[above]{$1$} (B)
+(A) edge node[left]{$f$} (A')
+(C) edge node[left]{$1$} (C')
+(A') edge node[above] {$1$} (D)
+(C') edge node[above] {$1$} (D)
+(B) edge node [left] {$1$} (D)
+(A) edge node[above]{$1$} (G)
+(G) edge node[left]{$f$} (H)
+(A') edge node[above]{$1$} (H)
+(J) edge node[above] {$f$} (H)
+(I) edge node[left] {$1$} (J)
+(I) edge node [above] {$1$} (G);
+\end{tikzpicture}
+\]
+%since the right hand sides of the above two equations are given respectively by the 2-morphisms $U_f$ and $1_{\hat{f}}$. 
+since the right hand side of the first equation is given by $U_f$ and the right hand side of the second equation is given as in Definition \ref{def:companion}.
 The conjoint of $f$ is given by this horizontal 1-cell $\check{f}$, which is just the opposite of the companion above:
@@
 In many cases, \cref{thm:equiv} shows that the structured and decorated cospan approaches are equivalent: \cref{subsec:graphs,subsec:circuits,subsec:petri} illustrate this.
-However, in\cref{subsec:petrirates} we describe a map from `open Petri nets with rates' to open dynamical systems.
+However, in \cref{subsec:petrirates} we describe a map from `open Petri nets with rates' to open dynamical systems.
 The former are conveniently described using structured cospans, while the latter can only be treated using decorated cospans.

### 2021-01-02 cospans.tex
Added ref to Christina's unitor in Lemma 4.1

@@
 Similarly the right and left unitors can be constructed: for example, for a horizontal 1-cell $M=(a\to m \leftarrow b,x\in F(m))$, the isomorphism $M\odot U_a\cong M$ is given by the canonical map of cospans $\kappa\colon a+_am\cong m$ along with the isomorphism between decorations
-\begin{displaymath}
+\begin{equation}\label{eq:decunitor}
  \scalebox{.9}
 {\begin{tikzcd}[row sep=.15in,ampersand replacement=\&]
-1\ar[r,"\phi_0\times x"]\ar[dd,equal] \& F(0)\times F(m)\ar[dd,phantom,"{\stackrel{\cref{eq:unitality}}{\cong}}"] \ar[dr,"\phi_{0,m}"']\ar[r,"F(!_a)\times 1"] \& F(a)\times F(m)\ar[d,phantom,"{\stackrel{\cref{eq:pseudonaturality}}{\cong}}"]\ar[r,"\phi_{m,a}"] \& F(a+m)\ar[ddr,phantom,"{\cong}"]\ar[r,"F\psi"] \& F(a+_am)\ar[dd,"F(\kappa)"]\\
-\&\& F(0+m)\ar[drr,sloped,"\sim"]\ar[ur,"F(!_a\times1)"'] \&\&  \\
+1\ar[r,"\phi_0\times x"]\ar[dd,equal] \& F(0)\times F(m)\ar[dd,phantom,"{\stackrel{\cref{eq:unitality}}{\cong}}"] \ar[dr,"\phi_{0,m}"']\ar[r,"F(!_a)\times 1"] \& F(a)\times F(m)\ar[d,phantom,"{\stackrel{\cref{eq:pseudonaturality}}{\cong}}"]\ar[r,"\phi_{a,m}"] \& F(a+m)\ar[ddr,phantom,"{\cong}"]\ar[r,"F\psi"] \& F(a+_am)\ar[dd,"F(\kappa)"]\\
+\&\& F(0+m)\ar[drr,sloped,"\sim"]\ar[ur,"F(!_a+1)"'] \&\&  \\
 1\ar[rrrr,"x"'] \&\phantom{A}\&\&\& F(m)
  \end{tikzcd}}
-\end{displaymath}
+\end{equation}
 All data can be verified to satisfy the axioms of a double category---essentially breaking down to those of the cospan double category of $\A$ and axioms of the lax monoidal pseudofunctor $F$.
@@
 %since the right hand sides of the above two equations are given respectively by the 2-morphisms $U_f$ and $1_{\hat{f}}$. 
-since the right hand side of the first equation is given by $U_f$ and the right hand side of the second equation is given as in Definition \ref{def:companion}.
+since the right hand side of the first equation is given by $U_f$ and the second equation utilizing the left and right unitors of $\odot$, which may be found in (\ref{eq:decunitor}), is given as in Definition \ref{def:companion}.
 The conjoint of $f$ is given by this horizontal 1-cell $\check{f}$, which is just the opposite of the companion above:

### 2021-01-04 cospans.tex
small changes

--- 2021-01-02 cospans.tex
@@
 % in LaTeX
-% 2020/12/31
+% 2021/1/2
 
@@
 
-Similarly the right and left unitors can be constructed: for example, for a horizontal 1-cell $M=(a\to m \leftarrow b,x\in F(m))$, the isomorphism $M\odot U_a\cong M$ is given by the canonical map of cospans $\kappa\colon a+_am\cong m$ along with the isomorphism between decorations
+The right and left unitors are defined similarly: for example, for a horizontal 1-cell $M=(a\to m \leftarrow b,x\in F(m))$, the isomorphism $M\odot U_a\cong M$ is given by the canonical map of cospans $\kappa\colon a+_am\cong m$ along with this isomorphism between decorations:
 \begin{displaymath}
@@
 \&\& F(0+m)\ar[drr,sloped,"\sim"]\ar[ur,"F(!_a\times1)"'] \&\&  \\
-1\ar[rrrr,"x"'] \&\phantom{A}\&\&\& F(m)
+1\ar[rrrr,"x"'] \&\phantom{A}\&\&\& F(m).
  \end{tikzcd}}

### 2021-01-04 cospans.tex
attempted to resolve conflicts

@@
 The right and left unitors are defined similarly: for example, for a horizontal 1-cell $M=(a\to m \leftarrow b,x\in F(m))$, the isomorphism $M\odot U_a\cong M$ is given by the canonical map of cospans $\kappa\colon a+_am\cong m$ along with this isomorphism between decorations:
-\begin{displaymath}
+\begin{equation}
  \scalebox{.9}
@@
  \end{tikzcd}}
-\end{displaymath}
-All data can be verified to satisfy the axioms of a double category---essentially breaking down to those of the cospan double category of $\A$ and axioms of the lax monoidal pseudofunctor $F$.
+\end{equation}
+All this data can be shown to obey the axioms of a double category, using the cospan double category of $\A$ and axioms of the lax monoidal pseudofunctor $F$.
 \end{proof}

### 2021-01-04 cospans.tex
revived missing label
small but important typo

@@
 The right and left unitors are defined similarly: for example, for a horizontal 1-cell $M=(a\to m \leftarrow b,x\in F(m))$, the isomorphism $M\odot U_a\cong M$ is given by the canonical map of cospans $\kappa\colon a+_am\cong m$ along with this isomorphism between decorations:
-\begin{equation}
+\begin{equation}\label{eq:decunitor}
  \scalebox{.9}
@@
 \begin{tikzcd}[column sep=.55in]
-\one\ar[r,"\phi_0"]\ar[dr,phantom,near start,"{\scriptstyle\stackrel{\cref{eq:pseudonaturality}}{\cong}}"]\ar[d,"\phi_0\times\phi_0"'] & F(0)\ar[dr,phantom,"{\scriptstyle\stackrel{\cref{eq:pseudonaturality}}{\cong}}"]\ar[r,"F(!_{a+b})"] & F(a+b)\ar[d,"F(1)"] \\
+\one\ar[r,"\phi_0"]\ar[dr,phantom,near start,"{\scriptstyle\stackrel{\cref{eq:unitality}}{\cong}}"]\ar[d,"\phi_0\times\phi_0"'] & F(0)\ar[dr,phantom,"{\scriptstyle\stackrel{\cref{eq:pseudonaturality}}{\cong}}"]\ar[r,"F(!_{a+b})"] & F(a+b)\ar[d,"F(1)"] \\
 F(0)\times F(0)\ar[r,"F(!_a)\times F(!_n)"']\ar[ur,"\phi_{0,0}"description] & F(a)\times F(b)\ar[r,"\phi_{a,b}"'] & F(a+b)

### 2021-01-04 cospans.tex
changed "all this data can be shown to obey the axioms of a double category..."

--- 2021-01-04 cospans.tex
@@
 % in LaTeX
-% 2021/1/2
+% 2021/1/3
 
@@
 \end{equation}
-All this data can be shown to obey the axioms of a double category, using the cospan double category of $\A$ and axioms of the lax monoidal pseudofunctor $F$.
+All the double category axioms can be verified using the fact that cospans in $\A$ form a double category and $F$ is a lax monoidal pseudofunctor.
 \end{proof}

### 2021-01-07 cospans.tex
tiny changes
small general edits

@@
 If $\A$ and $\X$ have finite colimits and $L$ preserves them, it is known that there is a symmetric monoidal double category whose objects are those of $\A$ and whose horizontal 1-cells are structured cospans.
-Second, if $\A$ has finite colimits and $F \maps (\A,+) \to (\Cat,\times)$ is a symmetric lax monoidal pseudofunctor , a `decorated cospan' is a diagram in $\A$ of the form $a \rightarrow s \leftarrow b$ together with an object of $F(s)$.
+Second, given a pseudofunctor $F\maps\A\to\Cat$, a `decorated cospan' is a diagram in $\A$ of the form $a \rightarrow s \leftarrow b$ together with an object of $F(s)$.
+Generalizing the work of Fong, we show that if $\A$ has finite colimits and $F \maps (\A,+) \to (\Cat,\times)$ is symmetric lax monoidal, there is a symmetric monoidal double category whose objects are those of $\A$ and whose horizontal 1-cells are decorated cospans.
+%Second, if $\A$ has finite colimits and $F \maps (\A,+) \to (\Cat,\times)$ is a symmetric lax monoidal pseudofunctor, a `decorated cospan' is a diagram in $\A$ of the form $a \rightarrow s \leftarrow b$ together with an object of $F(s)$.
 Generalizing the work of Fong, we show that in this situation there is a symmetric monoidal double category whose objects are those of $\A$ and whose horizontal 1-cells are decorated cospans.
-We prove that under certain conditions these two constructions become isomorphic when we take $\X = \inta F$ to be the Grothendieck category of $F$.
+We prove that under certain conditions, these two constructions become isomorphic when we take $\X = \inta F$ to be the Grothendieck category of $F$.
 We illustrate these ideas with applications to electrical circuits, Petri nets, dynamical systems and epidemiological modeling.
@@
 We show that if $F$ factors through $\Rex$ as a pseudofunctor, the opfibration $U \maps \X \to \A$ is also a right adjoint.
+%%%
+{\chris This is not a hundred percent true, because we want the corresponding F via the MonGroth to do so. This is the introduction though so we could be simpler, but more accurate perhaps?}
 From the accompanying left adjoint $L \maps \A \to \X$, we  construct a symmetric monoidal double category ${}_L \lCsp(\X)$ of structured cospans.
@@
 In fact, they are isomorphic as symmetric monoidal double categories.
+%%%
+{\chris Perhaps some ending statement saying something like ``this provides a passage between those two approaches, which we see in action in some of the main applications of the cospan frameworks'' or something?
+Right now it feels a bit like the paper finishes with theorem 3.2.}
 
@@
 \end{equation}
-is the decoration of the composite.
+is the decoration of the composite, where the first isomorphism comes from pseudofunctoriality of $F$.
 
@@
 \[  y\odot x:= \one\cong\one \times \one \xrightarrow{x \times y} F(m) \times F(n) \xrightarrow{\phi_{m,n}} F(m+n) \xrightarrow{F(\psi)} F(m+_{b}n) \]
-where $\psi \maps m + n \to m+_{b} n$ is the natural map from the coproduct to the pushout and $\phi_{m,n} \maps F(m) \times F(n) \to F(m+n)$ are the lax monoidal structure maps of $F$.
-Moreover, given two horizontally composable maps of $F$-decorated cospans $\alpha$ and $\beta$
+where $\psi \maps m + n \to m+_{b} n$ is the natural map from the coproduct to the pushout. Moreover, given two horizontally composable maps of $F$-decorated cospans $\alpha$ and $\beta$ 
 \[
@@
 \node (E) at (5.5,0.5) {$F(m) \times F(n)$};
-\node () at (6.5,0) {$\cong$};%{$\stackrel{\phi_{h_1,h_2}}{\cong}$};
+\node () at (6.5,0) {$\stackrel{\phi_{h_1,h_2}}{\cong}$};
 \node () at (8.5,0) {$\cong$};
@@
  \begin{tikzcd}[column sep=.5in, row sep=.1in]
-& F(m)\times F(n)\ar[r,"\phi_{m,n}"]\ar[dd,"F(h)\times F(h')"description]\ar[ddr,phantom,"\stackrel{\cref{eq:pseudonaturality}}{\cong}"] & F(m+n)\ar[dd,"F(h+h')"] \\
+& F(m)\times F(n)\ar[r,"\phi_{m,n}"]\ar[dd,"F(h)\times F(h')"description]\ar[ddr,phantom,"{\stackrel[\cref{eq:pseudonaturality}]{\phi_{h,h'}}{\cong}}"] & F(m+n)\ar[dd,"F(h+h')"] \\
 \one \ar[ur,"x\times y"]\ar[dr,"x'\times y'"']\ar[r,phantom,"\scriptstyle\Downarrow\tau_\alpha\times\tau_\beta"] & \phantom{A} && \\
@@
 \end{equation}
-This can always be achieved by replacing $F$ by an equivalent pseudofunctor that strictly preserves identity morphisms \cite[Proposition 5.2]{LP}.
+This can always be achieved by replacing $F$ by an equivalent normal pseudofunctor, namely one that strictly preserves identity morphisms \cite[Proposition 5.2]{LP}.
 We do this merely to reduce the size of  our diagrams; the reader can reinsert the morphism $F(!_0)$ where needed.
@@
  \begin{tikzcd}
-  1\ar[r,"x_1\times x_2"]\ar[dr,"x_2\times x_1"'] & F(m_1)\times F(m_2)\ar[d,"\beta"']\ar[r,"\phi_{m_1,m_2}"]\ar[dr,phantom,"\stackrel{\cref{eq:braidedpseudofun}}{\cong}"] & F(m_1+m_2)\ar[d,"F(\beta)"] \\
+  1\ar[r,"x_1\times x_2"]\ar[dr,"x_2\times x_1"'] & F(m_1)\times F(m_2)\ar[d,"\beta"']\ar[r,"\phi_{m_1,m_2}"]\ar[dr,phantom,"{\stackrel[\cref{eq:braidedpseudofun}]{u_{a,b}}{\cong}}"] & F(m_1+m_2)\ar[d,"F(\beta)"] \\
   & F(m_2)\times F(m_1)\ar[r,"\phi_{m_2,m_1}"'] & F(m_2+m_1)
@@
 \end{equation}
-All axioms for a symmetric monoidal category can be verified, %see \cite[Theorem 4.1.3]{CourserThesis}, 
+All axioms for a symmetric monoidal category can be verified,
 and it is easy to see that with these structures, the source and target functors $S,T\maps F\lCsp_1\to F\lCsp_0$ are symmetric strict monoidal.
@@
 \one\ar[r,"\phi_0"]\ar[dr,phantom,near start,"{\scriptstyle\stackrel{\cref{eq:unitality}}{\cong}}"]\ar[d,"\phi_0\times\phi_0"'] & F(0)\ar[dr,phantom,"{\scriptstyle\stackrel{\cref{eq:pseudonaturality}}{\cong}}"]\ar[r,"F(!_{a+b})"] & F(a+b)\ar[d,"F(1)"] \\
-F(0)\times F(0)\ar[r,"F(!_a)\times F(!_n)"']\ar[ur,"\phi_{0,0}"description] & F(a)\times F(b)\ar[r,"\phi_{a,b}"'] & F(a+b)
+F(0)\times F(0)\ar[r,"F(!_a)\times F(!_b)"']\ar[ur,"\phi_{0,0}"description] & F(a)\times F(b)\ar[r,"\phi_{a,b}"'] & F(a+b)
 \end{tikzcd}
@@
 where the top composite is $\bot_{a+b}$ by \cref{eq:UFCsp} and the bottom composite is $\phi_{a,b}(\bot_a,\bot_b)$ by \cref{eq:tensordecoration}.
-%, namely $F(!_{a+b})\phi_0\cong\phi_{a,b}(F(!_a)\times F(!_b))(\phi_0\times\phi_0)$ via the structure isomorphisms for $(\phi,\phi_0)$.
 
@@
 Our construction gives not only decorated cospan double categories, but  also maps between these: that is, symmetric monoidal double functors, as in \cref{def:doublefun}.
-Suppose we have two categories $\A,A'$ with finite colimits and two symmetric lax monoidal pseudofunctors $F \maps \A \to \Cat$ and $F' \maps \A' \to \Cat$.
+Suppose we have two categories $\A,\A'$ with finite colimits and two symmetric lax monoidal pseudofunctors $F \maps \A \to \Cat$ and $F' \maps \A' \to \Cat$.
 Then we can obtain a map between their decorated cospan double categories, $\lH \maps F\lCsp \to F' \lCsp$, from:
@@
 
-In fact, all these correspondences lift to 2-equivalences.
+In fact, all these correspondences lift to 2-equivalences between appropriate 2-categories.
 
 \begin{lem}\label{lem:MonGroth}
-There is a 2-equivalence between the 2-categories of monoidal opfibrations and monoidal opindexed categories with a fixed base, and if the base is cocartesian monoidal, there is a 2-equivalence between these and pseudofunctors into $\MonCat$.
-Similarly there is a 2-equivalence between symmetric monoidal opfibrations and symmetric monoidal opindexed categories with a fixed base, and if the base is cocartesian monoidal also a 2-equivalence between these and pseudofunctors into $\SMC$.
+There is a 2-equivalence between the 2-categories of monoidal opfibrations and monoidal opindexed categories, and if the base is cocartesian monoidal, there is a 2-equivalence between these and pseudofunctors into $\MonCat$.
+Similarly there is a 2-equivalence between symmetric monoidal opfibrations and symmetric monoidal opindexed categories, and if the base is cocartesian monoidal also a 2-equivalence between these and pseudofunctors into $\SMC$.
 \end{lem}
@@
 where the outside vertical legs come from the definition of $L$ on arrows \cref{eq:Lonarrows}. 
-Explicitly, the above square commutativities translate to the conditions $k\circ i=i'\circ f$ and $k\circ o=o'\circ g$ in $\A$, and also to
+Explicitly, the commutativity of the above squares translates to the conditions $k\circ i=i'\circ f$ and $k\circ o=o'\circ g$ in $\A$, and also to
 \begin{gather}\label{eq:Grothcommutativity}
@@
   & m+_bn & \\
-  a\ar[ur] && b,\ar[ul]
+  a\ar[ur] && b\ar[ul]
  \end{tikzcd}\qquad

### 2021-01-07 cospans.tex
removed unnecessary commented-out text in abstract

@@
 % in LaTeX
-% 2021/1/3
+% 2021/1/7
 
@@
 If $\A$ and $\X$ have finite colimits and $L$ preserves them, it is known that there is a symmetric monoidal double category whose objects are those of $\A$ and whose horizontal 1-cells are structured cospans.
-Second, given a pseudofunctor $F\maps\A\to\Cat$, a `decorated cospan' is a diagram in $\A$ of the form $a \rightarrow s \leftarrow b$ together with an object of $F(s)$.
+Second, given a pseudofunctor $F \maps \A \to \Cat$, a `decorated cospan' is a diagram in $\A$ of the form $a \rightarrow s \leftarrow b$ together with an object of $F(s)$.
 Generalizing the work of Fong, we show that if $\A$ has finite colimits and $F \maps (\A,+) \to (\Cat,\times)$ is symmetric lax monoidal, there is a symmetric monoidal double category whose objects are those of $\A$ and whose horizontal 1-cells are decorated cospans.
-%Second, if $\A$ has finite colimits and $F \maps (\A,+) \to (\Cat,\times)$ is a symmetric lax monoidal pseudofunctor, a `decorated cospan' is a diagram in $\A$ of the form $a \rightarrow s \leftarrow b$ together with an object of $F(s)$.
-Generalizing the work of Fong, we show that in this situation there is a symmetric monoidal double category whose objects are those of $\A$ and whose horizontal 1-cells are decorated cospans.
 We prove that under certain conditions, these two constructions become isomorphic when we take $\X = \inta F$ to be the Grothendieck category of $F$.

### 2021-01-08 cospans.tex
"much simpler proof" |-> "alternative proof"
various small edits and comments, finished my review

@@
 
-There is a much simpler proof of the above theorem when the hypothesis of \cref{thm:equiv} hold.
+There is an alternative proof of the above theorem when the hypothesis of \cref{thm:equiv} hold.
 In this case we show, in the proof of \cref{thm:equiv}, that the decorated cospan double category $F \lCsp$ is isomorphic to a certain double category ${}_L \lCsp(\inta  F)$ constructed using \emph{structured} cospans.
@@
 \begin{equation}\label{eq:2morphismLCspintaF}
- \begin{tikzcd}[row sep=1in,column sep=1.7in,ampersand replacement=\&]
+\scalebox{.9}
+ {\begin{tikzcd}[row sep=1in,column sep=1.7in,ampersand replacement=\&]
  (a,\bot_a)\ar[r,"{\begin{cases}i\maps a\to m &\textrm{in }\A \\!\maps F(i)(\bot_a)\to x &\textrm{in }F(m)\end{cases}}"]\ar[d,"{\begin{cases}f\maps a\to a' &\textrm{in }\A \\\chi_a\maps F(f)(\bot_a)\cong \bot_{a'} &\textrm{in }F(a')\end{cases}}"description] \& (m,x) \ar[d,"{\begin{cases}k\maps m\to m' &\textrm{in }\A \\ \tau\maps F(k)(x)\to x' &\textrm{in }F(m')\end{cases}}"description] \& (b,\bot_b)\ar[l,"{\begin{cases}o\maps b\to m &\textrm{in }\A \\!\maps F(o)(\bot_b)\to x &\textrm{in }F(m)\end{cases}}"']\ar[d,"{\begin{cases}g\maps b\to b' &\textrm{in }\A \\\chi_b\maps F(g)(\bot_b)\cong \bot_{b'} &\textrm{in }F(b')\end{cases}}"description] \\
  (a',\bot_{a'})\ar[r,"{\begin{cases}i'\maps a'\to m' &\textrm{in }\A \\!\maps F(i')(\bot_{a'})\to x' &\textrm{in }F(m')\end{cases}}"'] \& (m',x') \& (b',\bot_{b'})\ar[l,"{\begin{cases}o'\maps b'\to m' &\textrm{in }\A \\!\maps F(o')(\bot_{b'})\to x' &\textrm{in }F(m')\end{cases}}"]
- \end{tikzcd}
+ \end{tikzcd}}
 \end{equation}
@@
 \]
-along with the morphism of decorations $\tau\maps F(k)(x) \to x'$ in $F(m')$ coming from the middle arrow above.
+along with the morphism of decorations $\tau\maps F(k)(x) \to x'$ in $F(m')$ coming from the middle arrow of \cref{eq:2morphismLCspintaF}.
 We then make $\lE$ into double functor as in \cref{def:doublefun}.
 First, both $\lE_0$ and $\lE_1$ are functors that appropriately commute with sources and targets.
-Second, we equip $\lE$ with globular 2-isomorphisms $\lE(N) \odot \lE(M) \simrightarrow\lE(N \odot M)$, $U_{\lE m} \simrightarrow\lE(U_m)$
+Second, we equip $\lE$ with globular 2-isomorphisms $\lE(N) \odot \lE(M) \simrightarrow\lE(N \odot M)$
 for any pair of composable horizontal 1-cells $M=\cspn{(a,\bot_a)}{(m,x)}{(b,\bot_b)}{}{}$ and $N=\cspn{(b,\bot_b)}{(n,y)}{(c,\bot_c)}{}{}$ and any object $m$ of $_L\lCsp(\inta F)$.
@@
 where $v_m,v_n$ are the canonical maps into the pushout.
-Under $\lE$ this is mapped to the cospan $\cspn{a}{m+_bn}{b}{}{}$ with decoration $F(v_m)x+F(v_n)y$ in the fiber $F(m+_bn)$.
+Under $\lE$ this is mapped to the cospan $\cspn{a}{m+_bn}{b}{}{}$ with decoration $F(v_m)x+F(v_n)y$ in the fiber $F(m+_bn)$ -- since a pushout over an initial object is just a sum.
 This decoration is canonically isomorphic to that of \cref{eq:1} due to the following diagram
@@
 
-Regarding identities, the identity horizontal 1-cell $U_m$ in $_L\lCsp(\inta F)$ is $\cspn{(m,\bot_m)}{(m,\bot_m)}{(m,\bot_m)}{}{}$ with $1_m$ as the $A$-component and isomorphisms between initial objects in the fibers.
+Finally, we construct a globular 2-isomorphism $U_{\lE (m)} \simrightarrow\lE(U_m)$.
+The identity horizontal 1-cell $U_m$ in $_L\lCsp(\inta F)$ is $\cspn{(m,\bot_m)}{(m,\bot_m)}{(m,\bot_m)}{}{}$ with $1_m$ as the $A$-component and isomorphisms between initial objects in the fibers.
 Thus $\lE(U_m)$ is the identity cospan in $A$ together with the `initial decoration' $\bot_m\in F(m)$, and so is $U_{\mathbb{E}(m)}$ as in \cref{eq:UFCsp}.
@@
 
-Since both double categories are symmetric monoidal under the running assumptions (\cref{DC,thm:SC}), we now show that this double isomorphism is a symmetric monoidal one, namely that $\lE=(\lE_0,\lE_1)$ is a symmetric strong monoidal double functor as per \cref{defn:monoidal_double_functor}.
+Since both double categories are symmetric monoidal under the running assumptions (\cref{DC,thm:SC}), we now show that this double isomorphism is a symmetric monoidal one, namely that $\lE=(\lE_0,\lE_1)$ is a symmetric monoidal double functor as per \cref{defn:monoidal_double_functor}.
 Indeed, $\lE_0= \id_\A$ is a symmetric monoidal functor trivially.
@@
 \begin{proof}
-This follows by applying Shulman's result \cite[Theorem 1.2]{Shulman2010} to the fibrant symmetric monoidal double category $F\lCsp$.
+This follows by applying Shulman's result (\cref{Shulhorizontalbicat}) to the fibrant symmetric monoidal double category $F\lCsp$.
 \end{proof}
@@
 Then there is an isomorphism of symmetric monoidal bicategories
-\[      F\bCsp \simeq {}_L \bCsp(\inta F)   \]
+\[      F\bCsp \cong {}_L \bCsp(\inta F)   \]
 and of symmetric monoidal categories
-\[      F\Csp \simeq {}_L \Csp(\inta F)  . \]
+\[      F\Csp \cong {}_L \Csp(\inta F)  . \]
 \end{thm}
@@
 Hansen and Shulman \cite{HS} showed that the passage from symmetric monoidal double categories to symmetric monoidal bicategories is functorial in a suitable sense.
-This implies that an isomorphism of symmetric monoidal double categories $\lD \simeq \lD'$ gives an isomorphism of symmetric monoidal bicategories $\bD \simeq \bD'$.
-Since the process of decategorifying a bicategory merely discards 2-morphisms and takes isomorphism classes of 1-morphisms, the isomorphism of symmetric monoidal bicategories $\bD \simeq \bD'$ in turn induces an isomorphism of symmetric monoidal categories $\D \simeq \D'$.
+This implies that an isomorphism of symmetric monoidal double categories $\lD \cong \lD'$ gives an isomorphism of symmetric monoidal bicategories $\bD \cong \bD'$.
+Since the process of decategorifying a bicategory merely discards 2-morphisms and takes isomorphism classes of 1-morphisms, the isomorphism of symmetric monoidal bicategories $\bD \cong \bD'$ in turn induces an isomorphism of symmetric monoidal categories $\D \cong \D'$.
 Thus, the theorem follows from \cref{thm:equiv}.
@@
 This follows from \cref{thm:equiv} together with the fact that $U \maps \inta F \to \Fin\Set$ and $R \maps \Graph \to \Fin\Set$ are isomorphic as symmetric monoidal opfibrations.
+%%% Christina: I don't understand why the last part of this sentence is needed.
+The isomorphism should be obtained straight away from our theorem no?
+I *kinda* see the point but it looks like a technicality that it could be more obscuring than clarifying...
 
@@
 Other examples are worked out in \cite{BP}.
+%%% Christina: is this where the description of the black box double functor ends?
+Should we add a finishing line to that end?
 
@@
 Recall that in that theorem we start with the data required to build a decorated cospan category, namely a symmetric lax monoidal pseudofunctor $F \maps (\A,+) \to (\Cat,\times)$, and show that under certain conditions the resulting opfibration $U \maps \X = \inta F \to \A$ has a left adjoint $L \maps \A \to \X$.
-We then obtain an isomorphism between decorated and structured cospan double categories, $F \lCsp \simeq {}_L \Csp(\X)$.
+We then obtain an isomorphism between decorated and structured cospan double categories, $F \lCsp \cong {}_L \Csp(\X)$.
 We now show that in the case at hand, where $F = D$,  the opfibration $U$ does \emph{not} have a left adjoint.
@@
 Thus by \cref{lem:initial}, $U$ does not have a left adjoint.
+%%% Christina: that's nice and clear, but could we also pinpoint which assumption from the Theorem fails exactly?
+Because having an adjoint is a RESULT of the initial conditions.
+We don't need to elaborate, just point it out - it is presumably that F does not factor through Rex?
 
@@
 As a result, $F$ has now enough structure to induce a double category of decorated cospans $F\lCsp$  as in \cref{DC}.
-Finally, it can be shown that the structured and decorated cospan double categories are isomorphic as symmetric monoidal double categories: ${}_L \lCsp(\X) \simeq F\lCsp$.
+Finally, it can be shown that the structured and decorated cospan double categories are isomorphic as symmetric monoidal double categories: ${}_L \lCsp(\X) \cong F\lCsp$.
 
@@
 Briefly, a \define{monoidal} bicategory $\bA$ comes with a pseudofunctor $\otimes\maps\bA\times\bA\to\bA$ and a unit object $I$ that are associative and unital up to coherent equivalence.
-A \define{braided} monoidal bicategory also comes with a pseudonatural equivalence $\beta_{a,b}\maps a\ot b\to b\ot a$ and appropriate invertible modifications obeying certain equations; it is \define{sylleptic} if there is an invertible modification $1_{a\ot b}\Rrightarrow\beta_{b,a}\circ\beta_{a,b}$ its own equation, \define{symmetric} if one further axiom holds.
+A \define{braided} monoidal bicategory also comes with a pseudonatural equivalence $\beta_{a,b}\maps a\ot b\to b\ot a$ and appropriate invertible modifications obeying certain equations; it is \define{sylleptic} if there is an invertible modification $1_{a\ot b}\Rrightarrow\beta_{b,a}\circ\beta_{a,b}$ its own equation, %%%Christina: something is missing in that sentence syntactically?
+\define{symmetric} if one further axiom holds.
 
@@
 \begin{defn}\label{defn:monoidal_double_functor}
-Given symmetric monoidal double categories $\lD$ and $\lE$, a \define{symmetric monoidal double functor} $\lF \maps \lD \to \lE$ is a double functor $\lF$ together with transformations $\theta \maps {\otimes \circ (\lF,\lF)} \to \lF \circ \otimes$ and $\theta_U \maps I_\lE \to \lF \circ I_\lD$ that satisfy the usual coherence axioms for a symmetric monoidal functor with respect to $\otimes$.
+Given symmetric monoidal double categories $\lD$ and $\lE$, a \define{symmetric monoidal double functor} $\lF \maps \lD \to \lE$ is a double functor $\lF$ together with invertible transformations $\theta \maps {\otimes \circ (\lF,\lF)} \to \lF \circ \otimes$ and $\theta_U \maps I_\lE \to \lF \circ I_\lD$ that satisfy the usual coherence axioms for a symmetric monoidal functor with respect to $\otimes$.
 \end{defn}
@@
 	%	\node () at (1,0.5) {\scriptsize{$\Downarrow 1$}};
-		\node () at (1,1.4) {\scriptsize{$\Downarrow \rho_f$}};
+		\node () at (1,1.4) {\scriptsize{$\Downarrow \rho_{\hat{f}}$}};
 	\end{tikzpicture}
@@
 \begin{equation}\label{eq:thisdiagram}
-\begin{tikzpicture}[scale=1.5]
+\begin{tikzpicture}[scale=1.5,baseline=(current bounding box.center)]
 \node (A) at (0,0) {$(M_2 \otimes N_2) \odot (M_1 \otimes N_1)$};
@@
 where the unnamed isomorphisms are appropriate composites of the pseudoassociativity of $F$ \cref{eq:omega}.
-The result now follows from lengthy pasted diagram calculations using the axioms of a sylleptic lax monoidal pseudofunctor.
+The fact that the two pasted 2-isomorphisms are equal now follows from lengthy pasted diagram calculations using the axioms of a sylleptic lax monoidal pseudofunctor \cite[Definition 16]{DS}.
 

### 2021-01-11 cospans.tex
date
in Theorem 3.1: "finite colimits" |-> "finite coproducts"

@@
 % in LaTeX
-% 2021/1/7
+% 2021/1/8
 
@@
 This was proved in \cite[Theorems~2.3 \& 3.9]{BC}, where all the structures are specified in detail.
-In fact, the double category structure only requires that $\X$ have pushouts, whereas the symmetric monoidal structure also requires that $\X$ and $\A$ have finite colimits and that $L$ preserve finite coproducts \cite[Theorem~3.2.3]{CourserThesis}.
+In fact, the double category structure only requires that $\X$ have pushouts, whereas the symmetric monoidal structure also requires that $\X$ and $\A$ have finite coproducts and that $L$ preserve finite coproducts \cite[Theorem~3.2.3]{CourserThesis}.
 \end{proof}

### 2021-01-11 cospans.tex
Theorem 3.1: "finite colimits" |-> "finite coproducts"

@@
 This was proved in \cite[Theorems~2.3 \& 3.9]{BC}, where all the structures are specified in detail.
-In fact, the double category structure only requires that $\X$ have pushouts, whereas the symmetric monoidal structure also requires that $\X$ and $\A$ have finite coproducts and that $L$ preserve finite coproducts \cite[Theorem~3.2.3]{CourserThesis}.
+In fact, the double category structure only requires that $\X$ have pushouts, whereas the symmetric monoidal structure also requires that $\X$ and $\A$ have finite coproducts and that $L$ preserve these \cite[Theorem~3.2.3]{CourserThesis}.
 \end{proof}

### 2021-01-12 cospans.tex
various edits according to yesterday's meeting

@@
 % in LaTeX
-% 2021/1/8
+% 2021/1/12
 
@@
 On the other hand, $N \odot M$ computed as in \cref{eq:globalpushout} is 
-\begin{displaymath}
+\begin{equation}\label{eq:pushoutissum}
  \begin{tikzcd}[column sep={.7in,between origins}]
@@
  \end{tikzcd}
-\end{displaymath}
+\end{equation}
 where $v_m,v_n$ are the canonical maps into the pushout.
@@
  \begin{tikzcd}[sep=.4in]
-F(m)\times F(n)\ar[r,"\phi_{m,n}"]\ar[d,"F(v_m)\times F(v_n)"']\ar[dr,phantom,"\stackrel{\phi_{v_m,v_n}}{\cong}"] & F(m+n)\ar[r,"F(\psi)"]\ar[dr,phantom,"\cong"']\ar[d,"F(v_m+v_n)"] & F(m+_bn)\ar[d,"F(1)"]\\
+F(m)\times F(n)\ar[r,"\phi_{m,n}"]\ar[d,"F(v_m)\times F(v_n)"']\ar[dr,phantom,"\stackrel{\phi_{v_m,v_n}}{\cong}"] & F(m+n)\ar[r,"F(\psi)"]\ar[dr,phantom,"\cong"']\ar[d,"F(v_m+v_n)"] & F(m+_bn)\ar[d]\\
 F(m+_bn)\times F(m+_bn)\ar[r,"\phi_{m+_bn,m+_bn}"'] & F\left((m+_bn)+(m+_bn)\right)\ar[r,"F(\nabla)"'] & F(m+_bn)
@@
 The left-hand isomorphism comes from pseudonaturality of $\phi$ as in \cref{eq:pseudonaturality}, whereas the right-hand isomorphism follows from universal properties and pseudofunctoriality of $F$.
-Thus, we have a globular 2-isomorphism  $\lE(N) \odot \lE(M) \simrightarrow\lE(N \odot M)$.
-Notice that since the target decoration is part of the above pushout in the Grothendieck category $\inta F$, this isomorphism we construced is the canonical such that it commutes with the respective cocones.
-This is useful when checking associativity for example: there is only one such canonical isomorphism $\lE(P)\odot\lE(N)\odot\lE(M)\to\lE(P\odot N\odot M)$ for any three composable structured cospans.
+Thus, we have a globular 2-isomorphism  $\lE_\odot\colon\lE(N) \odot \lE(M) \simrightarrow\lE(N \odot M)$.
 
@@
 Thus $\lE(U_m)$ is the identity cospan in $A$ together with the `initial decoration' $\bot_m\in F(m)$, and so is $U_{\mathbb{E}(m)}$ as in \cref{eq:UFCsp}.
-
-In fact, the double functor $\lE\maps _L\lCsp(\inta F)\to F\lCsp$ as defined above is bijective on objects and vertical 1-cells (trivially as an identity functor), and is also bijective on horizontal 1-cells and on 2-morphisms.
+It can be verified that with this structure, $\lE$ satisfies the axioms of a double functor.
+
+In fact, this double functor $\lE\maps _L\lCsp(\inta F)\to F\lCsp$ is bijective on objects and vertical 1-cells (trivially as an identity functor), and is also bijective on horizontal 1-cells and on 2-morphisms.
 Indeed, for \cref{eq:scsphor1cell}, the unique maps from the initial objects in the fibers provide no actual extra information, and similarly for 2-cells all extra data in \cref{eq:2morphismLCspintaF} is uniquely determined and \cref{eq:Grothcommutativity} holds automatically as discussed above.
@@
 The cospan part is equal, whereas we have an isomorphism between the decorations, $F(\iota_m)x+F(\iota_{m'})x'\cong \phi_{m,m'}(x,x')$, given in an analogous way to \cref{eq:isomorphismdiag} as follows:
-\begin{displaymath}
+\begin{equation}\label{eq:Elaxator}
 \begin{tikzcd}[sep=.4in]
 F(m)\times F(m')\ar[r,"\phi_{m,m'}"]\ar[d,"F(\iota_m)\times F(\iota_{m'})"']
-\ar[dr,phantom,"{\stackrel[\cref{eq:pseudonaturality}]{\phi_{\iota_m,\iota_n}}{\cong}}"] & F(m+m')\ar[dr,"F(1)"]\ar[d,bend left=60, phantom,"\cong"']\ar[d,"F(\iota_m+\iota_{m'})"']  & \\
+\ar[dr,phantom,"{\stackrel[\cref{eq:pseudonaturality}]{\phi_{\iota_m,\iota_{m'}}}{\cong}}"] & F(m+m')\ar[dr]\ar[d,bend left=60, phantom,"\cong"']\ar[d,"F(\iota_m+\iota_{m'})"']  & \\
 F(m+m')\times F(m+m')\ar[r,"\phi_{m+m',m+m'}"'] & F\left((m+m')+(m+m')\right)\ar[r,"F(\nabla)"'] & F(m+m')
  \end{tikzcd}
-\end{displaymath}
+\end{equation}
 where the composite of the bottom two arrows is the coproduct operation in $F(m+m')$.
-We thus have constructed an isomorphism $\lE(M)\otimes\lE(M') \simrightarrow \lE(M\otimes M')$ for each $M,M'$. 
-Again, notice that since the target decoration is part of the sum $\left(m+m',F(\iota_m)x+F(\iota_{m'})x'\right)$ in the Grothendieck category $\inta F$ by \cref{eq:fibrewisecoprod}, this isomorphism we constructured is the canonical such that it commutes with the respective inclusions into the sum, and there is only one such canonical isomorphism $\lE(M)\otimes\lE(M')\otimes\lE(M'')\simrightarrow\lE(M\ot M'\ot M'')$ for any three structured cospans, proving associativity.
+We thus have constructed an isomorphism $\lE_\otimes\colon\lE(M)\otimes\lE(M') \simrightarrow \lE(M\otimes M')$ for each $M,M'$.
 
@@
 It can be verified that with this structure, $\lE_1$ is also a symmetric monoidal functor.
-
-Finally, the rest of the axioms of \cref{defn:monoidal_double_functor} hold: on the cospan level they are easy to verify, whereas on the decoration level they entail nontrivial calculations involving universal property arguments.
+For example, the associativity axiom ensuring that the two ways to go from $\lE (M)\ot\lE(M')\ot\lE(M'')$ to $\lE(M\ot M'\ot M'')$ using the above structure isomorphisms are equal, can in fact be deduced from the more general 2-equivalence between monoidal opfibrations and pseudofunctors into $\MonCat$ already discussed in \cite[Theorem 2.7]{Shulman2008}, for the induced global monoidal structure given by $(\phi,\phi_0)$ as discussed in \cref{lem:MonGroth}.
+Moreover, the earlier associativity axiom for the double functor structure isomorphism $\lE_\odot$ can be deduced using the one for $\lE_\otimes$, by observing that \cref{eq:isomorphismdiag} factors through \cref{eq:Elaxator} as follows
+\begin{displaymath}
+\begin{tikzcd}[column sep=.4in]
+F(m)\times F(n)\ar[r,"\phi_{m,n}"]\ar[d,"F(\iota_m)\times F(\iota_{n})"']\ar[dd,bend right=80,out=-90,in=-90,"F(v_m)\times F(v_n)"',"\textstyle\cong"]
+\ar[dr,phantom,"{\stackrel{\phi_{\iota_m,\iota_n}}{\cong}}"] & F(m+n)\ar[dr]\ar[d,bend left=60, phantom,"\cong"']\ar[d,"F(\iota_m+\iota_{n})"']  & \\
+F(m+n)\times F(m+n)\ar[d,"F(\psi)\times F(\psi)"']\ar[dr,phantom,"\stackrel{\phi_{\psi,\psi}}{\cong}"]\ar[r,"\phi_{m+n,m+n}"'] & F\left((m+n)+(m+n)\right)\ar[r,"F(\nabla)"']\ar[d,"F(\psi+\psi)"']\ar[dr,phantom,"\cong"] & F(m+n)\ar[d,"F(\psi)"] \\
+F(m+_bn)\times F(m+_bn)\ar[r,"\phi_{m+_bn,m+_bn}"'] & F((m+_bn)+(m+_bn))\ar[r,"F(\nabla)"'] & F(m+_bn)
+\end{tikzcd}
+\end{displaymath}
+due $\phi$ being a pseudonatural transformation, where $v=\psi\circ\iota$ as in \cref{eq:dcospanscomposition} and the bottom right isomorphism comes from naturality of $\nabla$.
+
+In a similar way, the rest of the axioms of \cref{defn:monoidal_double_functor} hold: on the cospan level they are easy to verify, whereas on the decoration level they entail nontrivial calculations based on the involved structures.
 In conclusion, the double isomorphism \cref{eq:doubleiso} is an isomorphism of symmetric monoidal double categories.
 \end{proof}
+
+Notice that in the above proof, when we compose two structured cospans namely horizontal 1-cells in the double category ${}_L\lCsp(\inta F)$ as in \cref{eq:pushoutissum}, the resulting composite cospan apex ends up being a sum on the second variable due to the definition of the left adjoint functor $L$ which forces the feet of all cospans to involve a fiberwise initial object.
+Consequently, one could remark that in fact, the assumptions of \cref{thm:equiv} should only state that the corresponding pseudofunctor $F\colon \A\to\SMC$ factors through categories with finite coproducts rather than $\Rex$.
+We leave the statement as is in order to match the general assumptions of \cref{thm:SC} for the definition of the structured cospan symmetric monoidal double category.
 
@@
 \noindent
+%%% Christina: the notation is not streamlined.
+We occasionally use $F_\otimes$ and $F_\odot$ (which I prefer) and in the definitions above we use various greek letters like $\phi$ (which is definitely overused in our paper).
+Could this be fixed throughout the document?
+Similarly for the unit comparison maps.
 

### 2021-01-12 cospans.tex
small changes

--- 2021-01-11 cospans.tex
@@
 Suppose $\A$ has finite colimits and $F \maps (\A,+) \to (\Cat,\times)$ is a symmetric lax monoidal pseudofunctor.
-If the corresponding pseudofunctor $F \maps \A \to \SMC$ factors through $\Rex$, then the symmetric monoidal double categories $F\lCsp$ of decorated cospans and $_L\lCsp(\inta F)$ of structured cospans are isomorphic, where $L \maps \A \to \inta F$ is a left adjoint of the induced Grothendieck opfibration $U\maps \inta F \to \A$.
+If the corresponding pseudofunctor $F \maps \A \to \SMC$ factors through $\Rex$, then the symmetric monoidal double categories $F\lCsp$ of decorated cospans and ${}_L\lCsp(\inta F)$ of structured cospans are isomorphic, where $L \maps \A \to \inta F$ is a left adjoint of the induced Grothendieck opfibration $U\maps \inta F \to \A$.
 \end{thm}

### 2021-01-13 cospans.tex
fixed end of introduction

@@
 Any such pseudofunctor gives an opfibration $U \maps \X \to \A$ where $\X = \inta F$ is defined by the Grothendieck construction.
+Furthermore, each category $F(a)$ for $a \in A$ becomes symmetric monoidal, and $F$ becomes a pseudofunctor $F \maps \A \to \SMC$.
 Let $\Rex$ be the 2-category of categories with finite colimits, functors preserving finite colimits, and natural transformations.
-We show that if $F$ factors through $\Rex$ as a pseudofunctor, the opfibration $U \maps \X \to \A$ is also a right adjoint.
-%%%
-{\chris This is not a hundred percent true, because we want the corresponding F via the MonGroth to do so. This is the introduction though so we could be simpler, but more accurate perhaps?}
+We show that if $F \maps \A \to \SMC$ factors through $\Rex$ as a pseudofunctor, the opfibration $U \maps \X \to \A$ is also a right adjoint.
 From the accompanying left adjoint $L \maps \A \to \X$, we  construct a symmetric monoidal double category ${}_L \lCsp(\X)$ of structured cospans.
@@
 In fact, they are isomorphic as symmetric monoidal double categories.
-%%%
-{\chris Perhaps some ending statement saying something like ``this provides a passage between those two approaches, which we see in action in some of the main applications of the cospan frameworks'' or something?
-Right now it feels a bit like the paper finishes with theorem 3.2.}
+
+This result shows that under certain conditions, structured and decorated cospans provide equivalent ways of describing open systems.
+We illustrate this with applications to electrical circuits, Petri nets, dynamical systems, and epidemiological modeling.
+In particular, we describe a map from open Petri nets with rates to open dynamical systems that takes advantage of \emph{both} structured and decorated cospans.
 
@@
 In \cref{spinoffs}, we establish the isomorphism between structured and decorated cospans at the level of bicategories and categories (via decategorification).
-Finally, in \cref{Applications}, we describe applications to electrical circuits, Petri nets, dynamical systems and epidemiological modeling.
+Finally, in \cref{Applications}, we describe applications.
 
@@
 
-Pollard and the first author showed how to construct an `open' dynamical system from any `open' Petri net with rates,  thus defining a functor from a category with open Petri nets with rates as morphisms to one with open dynamical systems as morphisms \cite{BP}.
+Pollard and the first author showed how to construct an open dynamical system from any open Petri net with rates,  thus defining a functor from a category with open Petri nets with rates as morphisms to one with open dynamical systems as morphisms \cite{BP}.
 They used Fong's original decorated cospans to do this.

### 2021-01-13 cospans.tex
fixed the end of the introduction

@@
 From the accompanying left adjoint $L \maps \A \to \X$, we  construct a symmetric monoidal double category ${}_L \lCsp(\X)$ of structured cospans.
-Finally, in \cref{thm:equiv} we prove that this structured cospan double category ${}_L \lCsp(\X)$ is isomorphic to the decorated cospan double category $F \lCsp$.
+In \cref{thm:equiv} we prove that this structured cospan double category ${}_L \lCsp(\X)$ is isomorphic to the decorated cospan double category $F \lCsp$.
 In fact, they are isomorphic as symmetric monoidal double categories.

### 2021-01-14 cospans.tex
changed date in paper to 1/13
polished description of Thm. 3.2 in intro

@@
 % in LaTeX
-% 2021/1/12
+% 2021/1/14
 
@@
 Suppose $\A$ has finite colimits and $F \maps (\A , +) \to (\Cat, \times)$ is a symmetric lax monoidal pseudofunctor.
-Any such pseudofunctor gives an opfibration $U \maps \X \to \A$ where $\X = \inta F$ is defined by the Grothendieck construction.
-Furthermore, each category $F(a)$ for $a \in A$ becomes symmetric monoidal, and $F$ becomes a pseudofunctor $F \maps \A \to \SMC$.
+Then each category $F(a)$ for $a \in A$ becomes symmetric monoidal, and $F$ becomes a pseudofunctor $F \maps \A \to \SMC$.
+Using the Grothendieck construction, $F$ also gives an opfibration $U \maps \X \to \A$ where $\X = \inta F$.
 Let $\Rex$ be the 2-category of categories with finite colimits, functors preserving finite colimits, and natural transformations.

### 2021-01-15 cospans.tex
tiny
important observation for proof

@@
 % in LaTeX
-% 2021/1/14
+% 2021/1/15
 
@@
 \end{equation}
-where $\nabla$ is the fold map, which is symmetric when $F$ is again via the components of $u_{a,a}$.
+where $\nabla$ is the fold map, which is symmetric when $F$ is again via the components of $u_{a,a}$. Also each reindexing functor $f_!=F(f)$ obtains a strong monoidal structure with
+\begin{equation}\label{eq:strongreindexing}
+\begin{tikzcd}[row sep=.35in]
+ F(a)\times F(a)\ar[r,"\phi_{a,a}"]\ar[d,"F(f)\times F(f)"']\ar[dr,phantom,"{\stackrel[\cref{eq:pseudonaturality}]{\phi_{f,f}}{\cong}}"] & 
+ F(a+a)\ar[r,"F(\nabla)"]\ar[d,"F(f+f)"description]\ar[dr,phantom,"\cong"] & F(a)\ar[d,"Ff"] \\
+ F(b)\times F(b)\ar[r,"\phi_{a,b}"'] & F(b+b)\ar[r,"F(\nabla)"'] & F(b)
+\end{tikzcd}
+\end{equation}
 \end{proof}
@@
 due $\phi$ being a pseudonatural transformation, where $v=\psi\circ\iota$ as in \cref{eq:dcospanscomposition} and the bottom right isomorphism comes from naturality of $\nabla$.
+Notice that the bottom two-part composite isomorphism is the induced strong monoidal structure on the reindexing functor $F(\psi)$ as in \cref{eq:strongreindexing}.
 
@@
 \]
-%%% Kenny: Commenting out previous equation.
-\begin{comment}
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (G) at (-1,0.5) {$a$};
-\node (H) at (-1,-0.5)  {$b$};
-\node (I) at (-2,0.5) {$a$};
-\node (J) at (-2,-0.5) {$a$};
-\node (A) at (0,0.5) {$a$};
-\node (A') at (0,-0.5) {$b$};
-\node (B) at (1,0.5) {$b$};
-\node (C) at (2,0.5) {$b$};
-\node (C') at (2,-0.5) {$b$};
-\node (D) at (1,-0.5) {$b$};
-\node (E) at (1,1) {$\bot_{b} \in F(b)$};
-\node (F) at (1,-1) {$\bot_{b} \in F(b)$};
-\node (L) at (1,-1.5) {$\tau_{b} = 1_{\bot_{b}}$};
-\node (E') at (-1,1) {$\bot_{a} \in F(a)$};
-\node (F') at (-1,-1) {$\bot_{b} \in F(b)$};
-\node (L') at (-1,-1.5) {$\tau_{f} \maps F(f)(\bot_a) \to \bot_{b}$};
-\node (M) at (2.5,0) {$=$};
-\node (N) at (3,0.5) {$a$};
-\node (O) at (3,-0.5) {$a$};
-\node (P) at (4,0.5) {$b$};
-\node (Q) at (4,-0.5) {$b$};
-\node (R) at (5,0.5) {$b$};
-\node (S) at (5,-0.5) {$b$};
-\node (T) at (4,1) {$\bot_{b} \in F(b)$};
-\node (U) at (4,-1) {$\bot_{b} \in F(b)$};
-\node (V) at (4,-1.5) {$\tau_{b} = 1_{\bot_{b}}$};
-\path[->,font=\scriptsize,>=angle 90]
-(N) edge node[left]{$1$} (O)
-(P) edge node[left]{$1$} (Q)
-(R) edge node[left]{$1$} (S)
-(N) edge node[above]{$f$} (P)
-(O) edge node[above]{$f$} (Q)
-(R) edge node[above]{$1$} (P)
-(S) edge node[above]{$1$} (Q)
-(A) edge node[above]{$f$} (B)
-(C) edge node[above]{$1$} (B)
-(A) edge node[left]{$f$} (A')
-(C) edge node[left]{$1$} (C')
-(A') edge node[above] {$1$} (D)
-(C') edge node[above] {$1$} (D)
-(B) edge node [left] {$1$} (D)
-(A) edge node[above]{$1$} (G)
-(G) edge node[left]{$f$} (H)
-(A') edge node[above]{$1$} (H)
-(J) edge node[above] {$f$} (H)
-(I) edge node[left] {$1$} (J)
-(I) edge node [above] {$1$} (G);
-\end{tikzpicture}
-\]
-\end{comment}
+%%%Christina: if I am not mistaken, John had some comments on how these cospans are written and whether our convention is clear.
 \[

### 2021-01-19 cospans.tex
dealt with various comments marked %%% - see Zulip

@@
 % in LaTeX
-% 2021/1/15
+% 2021/1/18
 
@@
 \]
-These 2-morphisms satisfy equations required of a companion \cref{eq:CompanionEq}, using vertical \cref{eq:verticalcompo} and horizontal \cref{eq:horizontalcompo} composition of 2-cells in this double category:
+These 2-morphisms satisfy the equations \cref{eq:CompanionEq} required of a companion, involving vertical \cref{eq:verticalcompo} and horizontal \cref{eq:horizontalcompo} composition of 2-cells in this double category:
 \[
@@
 \]
-%%%Christina: if I am not mistaken, John had some comments on how these cospans are written and whether our convention is clear.
 \[
@@
 \]
-%since the right hand sides of the above two equations are given respectively by the 2-morphisms $U_f$ and $1_{\hat{f}}$. 
-since the right hand side of the first equation is given by $U_f$ and the second equation utilizing the left and right unitors of $\odot$, which may be found in (\ref{eq:decunitor}), is given as in Definition \ref{def:companion}.
+Note that the right hand side of the first equation is $U_f$, while the second equation involves the left and right unitors for $\odot$, which may be found in (\ref{eq:decunitor}): these are maps from a horizontal composite of two decorated cospans to a single decorated cospan.
 The conjoint of $f$ is given by this horizontal 1-cell $\check{f}$, which is just the opposite of the companion above:
@@
 Each of these double categories has $\Fin\Set$ as its category of objects, open graphs as horizontal 1-cells, and maps of open graphs as 2-morphisms.
-This suggests that ${}_L \lCsp(\Graph)$  and $F\lCsp$ are isomorphic as symmetric monoidal double categories---and indeed this is true.
-This follows from \cref{thm:equiv} together with the fact that $U \maps \inta F \to \Fin\Set$ and $R \maps \Graph \to \Fin\Set$ are isomorphic as symmetric monoidal opfibrations.
-%%% Christina: I don't understand why the last part of this sentence is needed.
-The isomorphism should be obtained straight away from our theorem no?
-I *kinda* see the point but it looks like a technicality that it could be more obscuring than clarifying...
+This suggests that ${}_L \lCsp(\Graph)$  and $F\lCsp$ are isomorphic as symmetric monoidal double categories---and indeed this follows from \cref{thm:equiv}.
 
@@
 As such, it automatically becomes a monoidal natural isomorphism between the functors $F, D \maps (\Fin\Set,+) \to (\Cat,\times)$.
-
-Given a Petri net with rates $P$ and defining $v$ as above, this system of first-order ordinary differential equations for a function $c \maps \R \to \R^S$:
-\[    \frac{d}{dt} c(t) = v(c(t))   \]
-is called the \define{rate equation}.    When $P$ is part of an open Petri net with rates
+Thus, it defines a symmetric monoidal double functor $\graysquare \maps F \lCsp \to D \lCsp$.
+
+In applications, this double functor lets us turn an open Petri net with rates into an open dynamical system as follows.  Given a Petri net with rates $P$ and defining $v$ as above, we
+obtain a system first-order ordinary differential equations for a function $c \maps \R \to \R^S$ 
+called the \define{rate equation}:
+\[    \frac{d}{dt} c(t) = v(c(t)) .  \]
+More generally, when $P$ is part of an open Petri net with rates
 \[
@@
 Other examples are worked out in \cite{BP}.
-%%% Christina: is this where the description of the black box double functor ends?
-Should we add a finishing line to that end?
 
 We now show that decorated cospan double category $D \lCsp$ of open dynamical systems is not isomorphic to a structured cospan double category via \cref{thm:equiv}.
-Recall that in that theorem we start with the data required to build a decorated cospan category, namely a symmetric lax monoidal pseudofunctor $F \maps (\A,+) \to (\Cat,\times)$, and show that under certain conditions the resulting opfibration $U \maps \X = \inta F \to \A$ has a left adjoint $L \maps \A \to \X$.
+Recall that in that theorem we start with the data required to build a decorated cospan category, namely a symmetric lax monoidal pseudofunctor $F \maps (\A,+) \to (\Cat,\times)$, and show that if $F$ factors through $\Rex$ the resulting opfibration $U \maps \X = \inta F \to \A$ has a left adjoint $L \maps \A \to \X$.
 We then obtain an isomorphism between decorated and structured cospan double categories, $F \lCsp \cong {}_L \Csp(\X)$.
 We now show that in the case at hand, where $F = D$, the opfibration $U$ does \emph{not} have a left adjoint.
-Thus, the conditions of \cref{thm:equiv} do not hold in this case.
+Thus, the conditions of \cref{thm:equiv} do not hold in this case: $F$ does not factor through $\Rex$.
 

### 2021-01-19 cospans.tex
dealt with some comments marked %%% - see Zulip

@@
 We now show that decorated cospan double category $D \lCsp$ of open dynamical systems is not isomorphic to a structured cospan double category via \cref{thm:equiv}.
-Recall that in that theorem we start with the data required to build a decorated cospan category, namely a symmetric lax monoidal pseudofunctor $F \maps (\A,+) \to (\Cat,\times)$, and show that if $F$ factors through $\Rex$ the resulting opfibration $U \maps \X = \inta F \to \A$ has a left adjoint $L \maps \A \to \X$.
+Recall that in that theorem we start with the data required to build a decorated cospan category, namely a symmetric lax monoidal pseudofunctor $F \maps (\A,+) \to (\Cat,\times)$, and show that if the resulting pseudofunctor $F \maps \A \to \SMC$ factors through $\Rex$ the opfibration $U \maps \X = \inta F \to \A$ has a left adjoint $L \maps \A \to \X$.
 We then obtain an isomorphism between decorated and structured cospan double categories, $F \lCsp \cong {}_L \Csp(\X)$.

### 2021-01-19 cospans.tex
dealt with more comments marked %%% - see Zulip

@@
 Thus by \cref{lem:initial}, $U$ does not have a left adjoint.
-%%% Christina: that's nice and clear, but could we also pinpoint which assumption from the Theorem fails exactly?
-Because having an adjoint is a RESULT of the initial conditions.
-We don't need to elaborate, just point it out - it is presumably that F does not factor through Rex?
 
@@
 Briefly, a \define{monoidal} bicategory $\bA$ comes with a pseudofunctor $\otimes\maps\bA\times\bA\to\bA$ and a unit object $I$ that are associative and unital up to coherent equivalence.
-A \define{braided} monoidal bicategory also comes with a pseudonatural equivalence $\beta_{a,b}\maps a\ot b\to b\ot a$ and appropriate invertible modifications obeying certain equations; it is \define{sylleptic} if there is an invertible modification $1_{a\ot b}\Rrightarrow\beta_{b,a}\circ\beta_{a,b}$ its own equation, %%%Christina: something is missing in that sentence syntactically?
-\define{symmetric} if one further axiom holds.
+A \define{braided} monoidal bicategory also comes with a pseudonatural equivalence $\beta_{a,b}\maps a\ot b\to b\ot a$ and appropriate invertible modifications obeying certain equations; it is \define{sylleptic} if there is an invertible modification $1_{a\ot b}\Rrightarrow\beta_{b,a}\circ\beta_{a,b}$ obeying its own equation, and \define{symmetric} if one further axiom holds.
 

### 2021-01-19 cospans.tex
tiny

@@
 
-We now show that decorated cospan double category $D \lCsp$ of open dynamical systems is not isomorphic to a structured cospan double category via \cref{thm:equiv}.
+We now show that the decorated cospan double category $D \lCsp$ of open dynamical systems is not isomorphic to a structured cospan double category via \cref{thm:equiv}.
 Recall that in that theorem we start with the data required to build a decorated cospan category, namely a symmetric lax monoidal pseudofunctor $F \maps (\A,+) \to (\Cat,\times)$, and show that if the resulting pseudofunctor $F \maps \A \to \SMC$ factors through $\Rex$ the opfibration $U \maps \X = \inta F \to \A$ has a left adjoint $L \maps \A \to \X$.

### 2021-01-21 cospans.tex
changed date at top of paper
streamlining notation and fixing tiny typos throughout the paper

@@
 % in LaTeX
-% 2021/1/18
+% 2021/1/20
 
@@
 We compare two ways of describing open systems as cospans equipped with extra data.
-First, given a functor $L \maps \A \to \X$, a `structured cospan' is a diagram in $\A$ of the form $L(a) \rightarrow x \leftarrow L(b)$.
+First, given a functor $L \maps \A \to \X$, a `structured cospan' is a diagram in $\X$ of the form $L(a) \rightarrow x \leftarrow L(b)$.
 If $\A$ and $\X$ have finite colimits and $L$ preserves them, it is known that there is a symmetric monoidal double category whose objects are those of $\A$ and whose horizontal 1-cells are structured cospans.
@@
 \]
-together with a morphism $\tau \maps F(h)(x) \to m'$ in $F(x')$.
+together with a morphism $\tau \maps F(h)(x) \to x'$ in $F(m')$.
 \end{itemize}
@@
 The category of objects $F\lCsp_0$ is simply $\A$, whereas $F$-decorated cospans and maps between them form the category of arrows $F\lCsp_1$.
-The (vertical) composition of two $F$-decorated cospan maps is
+The (vertical) composition of two maps of $F$-decorated cospan is
 \begin{equation}\label{eq:verticalcompo}
@@
 \]
-their composite $\beta\odot \alpha$ is horizontal cospan composition in $\A$
+their composite $\beta\odot \alpha$ is the horizontal composite of the two cospans in $\A$
 \begin{equation}\label{eq:horizontalcompo}
@@
 \& F(m_1){\times}(F(m_2){\times}F(m_3))\ar[dddrr,phantom,"\stackrel{\cref{eq:omega}}{\cong}"]\ar[r,"1\times\phi_{m_2,m_3}"]\ar[ddd,"\alpha"description] \& F(m_1){\times}F(m_2{+}m_3)\ar[r,"1\times F(\psi)"]\ar[dr,"\phi_{m_1,m_2+m_3}"'] \& F(m_1){\times}F(m_2{+_c}m_3)\ar[d,phantom,"\stackrel{\cref{eq:pseudonaturality}}{\cong}"]\ar[r,"\phi_{m_1,m_2+_cm_3}"] \& F(m_1{+}(m_2{+_c}m_3))\ar[r,"F(\psi)"]\ar[dddr,phantom,"\cong"] \& F(m_1{+_b}(m_2{+_c}m_3))\ar[ddd,"F(\kappa)"] \\
-\one\ar[ur,"x_1\times(x_2\times x_3)"]\ar[d,equal] \&\&\& F(m_1{+}(m_2{+}m_3))\ar[ur,"F(1+\psi)"']\ar[d,"F\alpha"] \& \\
+\one\ar[ur,"x_1\times(x_2\times x_3)"]\ar[d,equal] \&\&\& F(m_1{+}(m_2{+}m_3))\ar[ur,"F(1+\psi)"']\ar[d,"F(\alpha)"] \& \\
 \one\ar[dr,"(x_1\times x_2)\times x_3"']\&\&\& F((m_1{+}m_2){+}m_3)\ar[dr,"F(\psi+1)"]\ar[d,phantom,"\stackrel{\cref{eq:pseudonaturality}}{\cong}"] \& \\
-\& (F(m_1){\times}F(m_2)){\times}F(m_3)\ar[r,"\phi_{m_1,m_2}\times1"'] \& F(m_1{+}m_2){\times}m_3\ar[ur,"\phi_{m_1+m_2,m_3}"]\ar[r,"F(\psi)\times1"'] \& F(m_1{+_b}m_2){\times} F(m_3)\ar[r,"\phi_{m_1{+_b}m_2,m_3}"'] \& F((m_1{+_b}m_2){+}m_3)\ar[r,"F\psi"'] \& F((m_1{+_b}m_2){+_c}m_3)
+\& (F(m_1){\times}F(m_2)){\times}F(m_3)\ar[r,"\phi_{m_1,m_2}\times1"'] \& F(m_1{+}m_2){\times}m_3\ar[ur,"\phi_{m_1+m_2,m_3}"]\ar[r,"F(\psi)\times1"'] \& F(m_1{+_b}m_2){\times} F(m_3)\ar[r,"\phi_{m_1{+_b}m_2,m_3}"'] \& F((m_1{+_b}m_2){+}m_3)\ar[r,"F(\psi)"'] \& F((m_1{+_b}m_2){+_c}m_3)
 \end{tikzcd}}
 \end{equation}
-where $a$ are the associators of $\Cat$ and $\A$ and $\kappa$ is the canonical isomorphism between two colimits of the same diagram in $\A$.
+where $\alpha$ are the associators of $\Cat$ and $\A$ and $\kappa$ is the canonical isomorphism between two colimits of the same diagram in $\A$.
 
@@
 {\begin{tikzcd}[row sep=.15in,ampersand replacement=\&]
-1\ar[r,"\phi_0\times x"]\ar[dd,equal] \& F(0)\times F(m)\ar[dd,phantom,"{\stackrel{\cref{eq:unitality}}{\cong}}"] \ar[dr,"\phi_{0,m}"']\ar[r,"F(!_a)\times 1"] \& F(a)\times F(m)\ar[d,phantom,"{\stackrel{\cref{eq:pseudonaturality}}{\cong}}"]\ar[r,"\phi_{m,a}"] \& F(a+m)\ar[ddr,phantom,"{\cong}"]\ar[r,"F\psi"] \& F(a+_am)\ar[dd,"F(\kappa)"]\\
-\&\& F(0+m)\ar[drr,sloped,"\sim"]\ar[ur,"F(!_a\times1)"'] \&\&  \\
+1\ar[r,"\phi_0\times x"]\ar[dd,equal] \& F(0)\times F(m)\ar[dd,phantom,"{\stackrel{\cref{eq:unitality}}{\cong}}"] \ar[dr,"\phi_{0,m}"']\ar[r,"F(!_a)\times 1"] \& F(a)\times F(m)\ar[d,phantom,"{\stackrel{\cref{eq:pseudonaturality}}{\cong}}"]\ar[r,"\phi_{a,m}"] \& F(a+m)\ar[ddr,phantom,"{\cong}"]\ar[r,"F(\psi)"] \& F(a+_am)\ar[dd,"F(\kappa)"]\\
+\&\& F(0+m)\ar[drr,sloped,"\sim"]\ar[ur,"F(!_a+1)"'] \&\&  \\
 1\ar[rrrr,"x"'] \&\phantom{A}\&\&\& F(m).
@@
 \begin{thm}\label{DC}
-Let $\A$ be a category with finite colimits and let $(F,\phi,\phi_0)\maps (\A,+) \to (\Cat,\times)$ a symmetric lax monoidal pseudofunctor.
+Let $\A$ be a category with finite colimits and let $(F,\phi,\phi_0)\maps (\A,+) \to (\Cat,\times)$ be a symmetric lax monoidal pseudofunctor.
 Then the double category $F\lCsp$ is symmetric monoidal, where the tensor product
@@
 %\node (F) at (5.2,-0.5) {$\scriptstyle \phi_{m',n'}(x',y')$};
-\node () at (2,-1.3) {$\scriptstyle\tau_{\alpha\ot\beta}\maps F(h+h')(\phi_{m',n'}(x',y'))\to \phi_{m,n}(x,y)\textrm{ in }F(m'+n')$};
+\node () at (2,-1.3) {$\scriptstyle\tau_{\alpha\ot\beta}\maps F(h+h')(\phi_{m,n}(x,y))\to \phi_{m',n'}(x',y')\textrm{ in }F(m'+n')$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 The associator for the monoidal structure in $F\lCsp$ is formed as follows: for three objects
-$M_1=(a_1\to m_1\leftarrow b_1,x_1\in F(m_1))$, $M_2=(a_2\to m_2\leftarrow b_2,x_2\in F(m_2))$ and $M_3=(a_3\to m_3\leftarrow b_3,x_3\in F(m_3),$
+$M_1=(a_1\to m_1\leftarrow b_1,x_1\in F(m_1))$, $M_2=(a_2\to m_2\leftarrow b_2,x_2\in F(m_2))$ and $M_3=(a_3\to m_3\leftarrow b_3,x_3\in F(m_3))$,
 the isomorphism $(M_1\ot M_2)\ot M_3\cong M_1\ot(M_2\ot M_3)$ is the isomorphism of cospans
@@
 together with the decoration isomorphism between $F(\alpha)((x_1 \otimes x_2) \otimes x_3)\stackrel{\cref{eq:tensordecoration}}{=}F(\alpha)(\phi_{m_1{+}m_2,m_3}(\phi_{m_1,m_2}(x_1,x_2),x_3))$ and $x_1 \otimes (x_2 \otimes x_3)=\phi_{m_1,m_2{+}m_3}(x_1,\phi_{m_2,m_3}(x_2,x_3))$ formed in the same way as the left two-piece part of \cref{eq:decoiso}.
-For the left and right unitors $I_1\ot M\cong M\cong M\ot I_1$ for any $M=(a\to m\leftarrow b,x\in F(m)$, we have span isomorphisms
+For the left and right unitors $I_1\ot M\cong M\cong M\ot I_1$ for any $M=(a\to m\leftarrow b,x\in F(m))$, we have isomorphisms of cospans
 \begin{displaymath}
@@
 \hole \\
-\& F(m_1+m_2)\times F(n_1+n_2)\ar[uurr,"\phi_{m_1+m_2,n_1+n_2}"']\ar[rr,"F\psi\times F\psi"'] \&\& F(m_1+_bm_2)\times F(n_1+_{b'}n_2)\ar[rr,"\phi_{m_1+_b m_2,n_1+_{b'}n_2}"'] \&\& F((m_1+_bm_2)+(n_1+_{b'}n_2))
+\& F(m_1+m_2)\times F(n_1+n_2)\ar[uurr,"\phi_{m_1+m_2,n_1+n_2}"']\ar[rr,"F(\psi)\times F(\psi)"'] \&\& F(m_1+_bm_2)\times F(n_1+_{b'}n_2)\ar[rr,"\phi_{m_1+_b m_2,n_1+_{b'}n_2}"'] \&\& F((m_1+_bm_2)+(n_1+_{b'}n_2))
 \end{tikzcd}}
@@
 
-It can be verified with this structure, $F\lCsp$ is indeed a symmetric monoidal double category, namely all coherence laws are satisfied.
+It can be verified that with this structure, $F\lCsp$ is indeed a symmetric monoidal double category, namely all coherence laws are satisfied.
 In order to give the reader a sense of what these checks entail, we provide a proof of the fact that the braiding is a transformation of double categories in \cref{eq:proofofaxiom}.
@@
 In this case we show, in the proof of \cref{thm:equiv}, that the decorated cospan double category $F \lCsp$ is isomorphic to a certain double category ${}_L \lCsp(\inta  F)$ constructed using \emph{structured} cospans.
-We also show that under this isomorphism, all the symmetric monoidal structure of $F \lCsp$---the tensor product, associator, etc.---matches that for  ${}_L \lCsp(\inta  F)$, which we have proved to obey the axioms of a symmetric monoidal double category (see \cref{thm:SC}).
+We also show that under this isomorphism, all the symmetric monoidal structure of $F \lCsp$---the tensor product, associator, etc.---matches that of  ${}_L \lCsp(\inta  F)$, which we have proved to obey the axioms of a symmetric monoidal double category (see \cref{thm:SC}).
 It follows that $F \lCsp$ is a symmetric monoidal double category.
@@
 symmetric monoidal structure is defined using finite coproducts in $\A$ and $\X$: 
-the tensor of horizontal 1-cells is
+the tensor of two horizontal 1-cells is
 \begin{equation}\label{eq:tensorstuctured}
@@
 \end{equation}
-using that $L$ preserves coproducts.
+using that $L$ preserves finite coproducts.
 \end{thm}
@@
 There is a 2-equivalence between the 2-categories of monoidal opfibrations and monoidal opindexed categories, and if the base is cocartesian monoidal, there is a 2-equivalence between these and pseudofunctors into $\MonCat$.
-Similarly there is a 2-equivalence between symmetric monoidal opfibrations and symmetric monoidal opindexed categories, and if the base is cocartesian monoidal also a 2-equivalence between these and pseudofunctors into $\SMC$.
+Similarly there is a 2-equivalence between symmetric monoidal opfibrations and symmetric monoidal opindexed categories, and if the base is cocartesian monoidal, also a 2-equivalence between these and pseudofunctors into $\SMC$.
 \end{lem}
@@
 \otimes_a\maps F(a)\times F(a)\xrightarrow{\phi_{a,a}}F(a+a)\xrightarrow{F(\nabla)}F(a),\quad
-I_a\maps\one\xrightarrow{\phi_0}F(0)\xrightarrow{F(!)}F(a)
-\end{equation}
-where $\nabla$ is the fold map, which is symmetric when $F$ is again via the components of $u_{a,a}$. Also each reindexing functor $f_!=F(f)$ obtains a strong monoidal structure with
+I_a\maps\one\xrightarrow{\phi_0}F(0)\xrightarrow{F(!_a)}F(a)
+\end{equation}
+where $\nabla$ is the fold map, which is symmetric when $F$ is again via the components of $u_{a,a}$. Also, each reindexing functor $f_!=F(f)$ obtains a strong monoidal structure with
 \begin{equation}\label{eq:strongreindexing}
@@
  F(a+a)\ar[r,"F(\nabla)"]\ar[d,"F(f+f)"description]\ar[dr,phantom,"\cong"] & F(a)\ar[d,"Ff"] \\
- F(b)\times F(b)\ar[r,"\phi_{a,b}"'] & F(b+b)\ar[r,"F(\nabla)"'] & F(b)
+ F(b)\times F(b)\ar[r,"\phi_{b,b}"'] & F(b+b)\ar[r,"F(\nabla)"'] & F(b)
 \end{tikzcd}
@@
 \end{enumerate}
-Moreover, if $\X$ has $\J$-colimits and $U$ preserves them, for any choice of $\J$-colimits in $\A$ they can be chosen in $\X$ in such a way that $U$ strictly preserves them.   
+Moreover, if $\X$ has $\J$-colimits and $U$ preserves them, for any choice of $\J$-colimits in $\A$, they can be chosen in $\X$ in such a way that $U$ strictly preserves them.   
 \end{lem}
@@
 \end{equation}
-where $\iota_a \maps a\to a+b$ and $\iota_b \maps a \to a+b$ are the sum inclusions in $\A$ and the sum on the second variable is in the fiber $F(a+b)$.
+where $\iota_a \maps a\to a+b$ and $\iota_b \maps b \to a+b$ are the sum inclusions in $\A$ and the sum on the second variable is in the fiber $F(a+b)$.
 
@@
 As a left adjoint, this induced $L$ preserves all colimits that exist between the categories $\A$ and $\inta F$, which have finite colimits, so we can construct the double category of structured cospans $_L\lCsp(\inta F)$ of \cref{thm:SC}.
-Its objects and vertical morphisms are those of the category $\A$ (just as for $F\lCsp$), whereas its horizontal 1-cells are now cospans of the form $\cspn{L(a)}{(m,x)}{L(b)}{}{}$ in the Grothendieck category $\inta F$ (see \cref{def:GrothCat}).
+Its objects and vertical 1-morphisms are those of the category $\A$ (just as for $F\lCsp$), whereas its horizontal 1-cells are now cospans of the form $\cspn{L(a)}{(m,x)}{L(b)}{}{}$ in the Grothendieck category $\inta F$ (see \cref{def:GrothCat}).
 Explicitly, they consist of two pairs of morphisms
@@
 Second, we equip $\lE$ with globular 2-isomorphisms $\lE(N) \odot \lE(M) \simrightarrow\lE(N \odot M)$
-for any pair of composable horizontal 1-cells $M=\cspn{(a,\bot_a)}{(m,x)}{(b,\bot_b)}{}{}$ and $N=\cspn{(b,\bot_b)}{(n,y)}{(c,\bot_c)}{}{}$ and any object $m$ of $_L\lCsp(\inta F)$.
+for any pair of composable horizontal 1-cells $M=\cspn{(a,\bot_a)}{(m,x)}{(b,\bot_b)}{}{}$ and $N=\cspn{(b,\bot_b)}{(n,y)}{(c,\bot_c)}{}{}$ and $U_{\lE (m)} \simrightarrow\lE(U_m)$ for any object $m$ of $_L\lCsp(\inta F)$.
 Explicitly, $\mathbb{E}(N)\odot \mathbb{E}(M)$ is given as in \cref{eq:dcospanscomposition} via the pushout cospan and decoration
@@
 \end{displaymath}
-due $\phi$ being a pseudonatural transformation, where $v=\psi\circ\iota$ as in \cref{eq:dcospanscomposition} and the bottom right isomorphism comes from naturality of $\nabla$.
+due to $\phi$ being a pseudonatural transformation, where $v=\psi\circ\iota$ as in \cref{eq:dcospanscomposition} and the bottom right isomorphism comes from naturality of $\nabla$.
 Notice that the bottom two-part composite isomorphism is the induced strong monoidal structure on the reindexing functor $F(\psi)$ as in \cref{eq:strongreindexing}.
@@
 
-Notice that in the above proof, when we compose two structured cospans namely horizontal 1-cells in the double category ${}_L\lCsp(\inta F)$ as in \cref{eq:pushoutissum}, the resulting composite cospan apex ends up being a sum on the second variable due to the definition of the left adjoint functor $L$ which forces the feet of all cospans to involve a fiberwise initial object.
+Notice that in the above proof, when we compose two structured cospans, namely two horizontal 1-cells in the double category ${}_L\lCsp(\inta F)$ as in \cref{eq:pushoutissum}, the resulting composite cospan apex ends up being a sum on the second variable due to the definition of the left adjoint functor $L$ which forces the feet of all cospans to involve a fiberwise initial object.
 Consequently, one could remark that in fact, the assumptions of \cref{thm:equiv} should only state that the corresponding pseudofunctor $F\colon \A\to\SMC$ factors through categories with finite coproducts rather than $\Rex$.
@@
 \item 2-morphisms are \define{globular} 2-morphisms of $\lD$, meaning 2-morphisms whose source and target vertical 1-morphisms are identities,
-\item composition of morphisms is given by horizontal composition of horizontal 1-cells in $\lD$,
+\item composition of morphisms is given by composition of horizontal 1-cells in $\lD$,
 \item vertical and horizontal composition of 2-morphisms are given by vertical and horizontal
@@
 \item objects are objects of $\bD$,
-\item morphisms are isomorphism classes of 1-morphisms of $\bD$.   
+\item morphisms are isomorphism classes of morphisms of $\bD$.   
 \end{itemize}
@@
 \begin{proof}
-We show that any vertical 1-morphism $f \maps a \to b'$ in $F\lCsp$ has a companion and a conjoint.  First, we can make this horizontal 1-cell $\hat{f}$:
+We show that any vertical 1-morphism $f \maps a \to b$ in $F\lCsp$ has a companion and a conjoint.  First, we can make this horizontal 1-cell $\hat{f}$:
 \[
@@
 \]
-These 2-morphisms satisfy the equations \cref{eq:CompanionEq} required of a companion, involving vertical \cref{eq:verticalcompo} and horizontal \cref{eq:horizontalcompo} composition of 2-cells in this double category:
+These 2-morphisms satisfy the equations \cref{eq:CompanionEq} required of a companion, involving vertical \cref{eq:verticalcompo} and horizontal \cref{eq:horizontalcompo} composition of 2-morphisms in this double category:
 \[
@@
 \item objects are those of $\A$
-\item morphisms as isomorphism classes of $F$-decorated cospans of $\A$, where two
+\item morphisms are isomorphism classes of $F$-decorated cospans of $\A$, where two
 $F$-decorated cospans
@@
 Unfortunately, some of these applications were marred by technical flaws, which were later fixed using structured cospans \cite{BC}.
-Here we explain how to also fix them using our new decorated cospans, since they provide another another solution to these problems.
+Here we explain how to also fix them using our new decorated cospans, since they provide another solution to these problems.
 Below we compare the two approaches in applications to graphs, electrical circuits, Petri nets, reaction networks and dynamical systems.
@@
 \item A morphism from $s,t \maps E \to N$ to $s',t' \maps E' \to N$ is a morphism of graphs that is
-the identity on $N$: that is, a function $f \maps E \to E'$ such that these diagrams commute:
+the identity on $N$: that is, a function $g \maps E \to E'$ such that these diagrams commute:
 \[
@@
 (A') edge node[below]{$s'$} (B)
-(A) edge node[left]{$f$} (A');
+(A) edge node[left]{$g$} (A');
 \node (C) at (2,0) {$E$};
@@
 (C') edge node[below]{$t'$} (D)
-(C) edge node[left]{$f$} (C');
+(C) edge node[left]{$g$} (C');
 \end{tikzpicture}
@@
 In general, decorated cospans involve a pseudofunctor to $\Cat$, but in this example there is actually an honest functor $F \maps \Set \to \Cat$ that assigns to a set $N$ the above category $F(N)$.
-Given a function $f \maps M \to N$, we define $F(f) \maps F(M) \to F(N)$ to any graph structure $s,t \maps E \to M$ to the graph structure $f s, f t \maps E \to N$.
+Given a function $f \maps M \to N$, we define $F(f) \maps F(M) \to F(N)$ as the functor that maps any graph structure $s,t \maps E \to M$ to the graph structure $f s, f t \maps E \to N$.
 
@@
 	\]
-There is a functor $R \maps \Petri \to \Set$ sending any Petri net to its set of places, and this has a left adjoint $L \maps \Set \to \Petri$ sending any set $S$ to the Petri net with $S$ as its set of species and no transitions \cite[Lemma 11]{BM}.
+There is a functor $R \maps \Petri \to \Set$ sending any Petri net to its set of places, and this has a left adjoint $L \maps \Set \to \Petri$ sending any set $S$ to the Petri net with $S$ as its set of places and no transitions \cite[Lemma 11]{BM}.
 Since both $\Set$ and $\Petri$ have finite colimits and $L$ preserves them, \cref{thm:SC} yields a symmetric monoidal double category ${}_L \lCsp(\Petri)$ in which:
@@
  to 
- \[   \xymatrix{ (0,\infty) & T' \ar[l]_-r \ar@<-.5ex>[r]_-t \ar@<.5ex>[r]^-s & \N[S'] }\]
+ \[   \xymatrix{ (0,\infty) & T' \ar[l]_-{r'} \ar@<-.5ex>[r]_-{t'} \ar@<.5ex>[r]^-{s'} & \N[S'] }\]
 is a morphism of the underlying Petri nets such that the following diagram also commutes:
@@
 \]
-There is a functor $R \maps \Petri_r \to \Set$ sending any Petri net with rates to its set of places, and this has a left adjoint $L \maps \Set \to \Petri_r$ sending any set $S$ to the Petri net with $S$ as its set of species and no transitions \cite[Lemma 6.18]{BC}.
+There is a functor $R \maps \Petri_r \to \Set$ sending any Petri net with rates to its set of places, and this has a left adjoint $L \maps \Set \to \Petri_r$ sending any set $S$ to the Petri net with $S$ as its set of places and no transitions \cite[Lemma 6.18]{BC}.
 Since $\Petri_r$ has finite colimits \cite[Lemma 6.19]{BC}, it follows that there is a symmetric monoidal double category ${}_L \lCsp(\Petri_r)$ where:
@@
 More interesting is the symmetric monoidal double category of open dynamical systems.
-A dynamical system is a vector field from the perspective of a system of first-order ordinary differential equation.
-An Petri net with rates gives a special sort of dynamical system: an \define{algebraic} vector field on $\R^n$, meaning one where the components of the vector field are polynomials in the coordinates.
+A dynamical system is a vector field from the perspective of a system of first-order ordinary differential equations.
+A Petri net with rates gives a special sort of dynamical system: an \define{algebraic} vector field on $\R^n$, meaning one where the components of the vector field are polynomials in the coordinates.
 We shall think of such a vector field as a special sort of function $v \maps \R^n \to \R^n$.
@@
 In applications, this double functor lets us turn an open Petri net with rates into an open dynamical system as follows.  Given a Petri net with rates $P$ and defining $v$ as above, we
-obtain a system first-order ordinary differential equations for a function $c \maps \R \to \R^S$ 
+obtain a system of first-order ordinary differential equations for a function $c \maps \R \to \R^S$ 
 called the \define{rate equation}:
@@
 We now show that the decorated cospan double category $D \lCsp$ of open dynamical systems is not isomorphic to a structured cospan double category via \cref{thm:equiv}.
-Recall that in that theorem we start with the data required to build a decorated cospan category, namely a symmetric lax monoidal pseudofunctor $F \maps (\A,+) \to (\Cat,\times)$, and show that if the resulting pseudofunctor $F \maps \A \to \SMC$ factors through $\Rex$ the opfibration $U \maps \X = \inta F \to \A$ has a left adjoint $L \maps \A \to \X$.
-We then obtain an isomorphism between decorated and structured cospan double categories, $F \lCsp \cong {}_L \Csp(\X)$.
+Recall that in that theorem we start with the data required to build a decorated cospan category, namely a symmetric lax monoidal pseudofunctor $F \maps (\A,+) \to (\Cat,\times)$, and show that if the resulting pseudofunctor $F \maps \A \to \SMC$ factors through $\Rex$, then the opfibration $U \maps \X = \inta F \to \A$ has a left adjoint $L \maps \A \to \X$.
+We then obtain an isomorphism between decorated and structured cospan double categories, $F \lCsp \cong {}_L \lCsp(\X)$.
 We now show that in the case at hand, where $F = D$, the opfibration $U$ does \emph{not} have a left adjoint.
@@
 Furthermore, if $U$ preserves finite coproducts, $F$ acquires the structure of a lax monoidal pseudofunctor $F \maps (\A,+) \to (\Cat,\times)$ by the special case of the cocartesian monoidal Grothendieck construction discussed under \cref{lem:MonGroth}.
-As a result, $F$ has now enough structure to induce a double category of decorated cospans $F\lCsp$  as in \cref{DC}.
+As a result, $F$ now has enough structure to induce a double category of decorated cospans $F\lCsp$  as in \cref{DC}.
 Finally, it can be shown that the structured and decorated cospan double categories are isomorphic as symmetric monoidal double categories: ${}_L \lCsp(\X) \cong F\lCsp$.
@@
 This choice induces \textbf{reindexing functors} $f_!\maps\X _a\to\X _b$ between the fibers, which by the lifting's universal property come equipped with natural isomorphisms $(1_a)_!\cong 1_{\X _a}$ and $(f\circ g)_!\cong f_!\circ g_!$.
-With the help of these, any cloven opfibration $U \maps \X \to \A$ gives a pseudofunctor $F \maps \A \to \Cat$, where $\A$ viewed as a 2-category with trivial 2-cells, $F(a) = \X_a$ for each object $a \in \A$, and $F(f) = f_!$ for each morphism $f$ in $\A$.
+With the help of these, any cloven opfibration $U \maps \X \to \A$ gives a pseudofunctor $F \maps \A \to \Cat$, where $\A$ is viewed as a 2-category with trivial 2-morphisms, $F(a) = \X_a$ for each object $a \in \A$, and $F(f) = f_!$ for each morphism $f$ in $\A$.
 
@@
 \begin{defn}\label{def:GrothCat}
-For any pseudofunctor $F\maps\A\to\Cat$ where $\A$ is a category viewed as a 2-category with trivial 2-cells, the \textbf{Grothendieck category}
+For any pseudofunctor $F\maps\A\to\Cat$ where $\A$ is a category viewed as a 2-category with trivial 2-morphisms, the \textbf{Grothendieck category}
 $\inta F$ has
@@
 \item{functors $\lF_0 \maps \lD_0 \to \lE_0$ and $\lF_1 \maps \lD_1 \to \lE_1$ such that $S \lF_1 = \lF_0 S$ and $T \lF_1 = \lF_0 T$, and}
-\item{for every composable pair of horizontal 1-cells $M$ and $N$ in $\lD$, a natural transformation $\phi_{M,N} \maps \lF(N) \odot \lF(M) \to \lF(N \odot M)$ called the \define{composite comparison} and for every object $a$ in $\lD$, a natural transformation $\phi_a \maps U_{\lF_0(a)} \to \lF_1(U_a)$ called the \define{unit comparison}.
+\item{for every composable pair of horizontal 1-cells $M$ and $N$ in $\lD$, a natural transformation $\mathbb{F}_\odot \maps \lF(N) \odot \lF(M) \to \lF(N \odot M)$ called the \define{composite comparison} and for every object $a$ in $\lD$, a natural transformation $\mathbb{F}_U \maps U_{\lF_0(a)} \to \lF_1(U_a)$ called the \define{unit comparison}.
 The components of each of these natural transformations are globular isomorphisms that must obey coherence laws analogous to those of a monoidal functor.}
@@
 \begin{defn}
-Given double functors $(\lF,\phi),(\mathbb{G},\psi) \maps \lD \to \lE$, a \define{double natural transformation} $\alpha \maps \lF \Rightarrow \mathbb{G}$ consists of natural transformations $\alpha_0 \maps \lF_0 \Rightarrow \mathbb{G}_0$ and $\alpha_1 \maps \lF_1 \Rightarrow \mathbb{G}_1$ such that:
+Given double functors $\lF,\mathbb{G} \maps \lD \to \lE$, a \define{double natural transformation} $\alpha \maps \lF \Rightarrow \mathbb{G}$ consists of natural transformations $\alpha_0 \maps \lF_0 \Rightarrow \mathbb{G}_0$ and $\alpha_1 \maps \lF_1 \Rightarrow \mathbb{G}_1$ such that:
 \begin{itemize}
 \item{$S(\alpha_M) = \alpha_{S(M)}$ and $T(\alpha_M) = \alpha_{T(M)}$ for all horizontal 1-cells $M$ of $\lD$,}
-\item{$\alpha \circ \phi_{M,N} = \psi \circ (\alpha_M \odot \alpha_N)$ for all composable pairs $M$ and $N$ of horizontal 1-cells in $\lD$, and}
-\item{$\alpha \circ \phi_a = \psi_a \circ \alpha$ for all objects $a$ of $\lD$.}
+\item{$\alpha \circ \lF_\odot = \mathbb{G}_\odot \circ (\alpha_M \odot \alpha_N)$ for all composable pairs $M$ and $N$ of horizontal 1-cells in $\lD$, and}
+\item{$\alpha \circ \lF_U = \mathbb{G}_U \circ \alpha$ for all objects $a$ of $\lD$.}
 \end{itemize} 
@@
 \begin{itemize}
-\item monoidal structures on both $\lD_0$ and $\lD_1$ (each with tensor product denoted $\otimes$, associator $a$, left unitor $\ell$ and right unitor $r$), such that $U \maps \lD_0 \to \lD_1$ strictly preserves the unit object and $S,T \maps \lD_1 \to \lD_0$ are strict monoidal,
+\item monoidal structures on both $\lD_0$ and $\lD_1$ (each with tensor product denoted $\otimes$, associator $a$, left unitor $\ell$ and right unitor $r$ and unit object $I_\lD$), such that $U \maps \lD_0 \to \lD_1$ strictly preserves the unit objects and $S,T \maps \lD_1 \to \lD_0$ are strict monoidal,
 \item the structure of a double functor on $\otimes$:
@@
 				(A) edge node[left]{$\chi$} (A')
-				(A) edge node[above]{$\phi \odot \phi$} (B)
+				(A) edge node[above]{$\lF_\otimes \odot \lF_\otimes$} (B)
 				(B) edge node[right]{$\lF_\odot$} (B')
@@
 				(B') edge node [right] {$\lF(\chi)$} (B'')
-				(A'') edge node[above]{$\phi$} (B'');
+				(A'') edge node[above]{$\lF_\otimes$} (B'');
 		\end{tikzpicture}
@@
 		\begin{tikzpicture}
-			\node (A) at (0,1.5) {\footnotesize{$U_{\lF(a)} \otimes U_{\lF(b)}$}};
+			\node (A) at (0,1.5) {\footnotesize{$U_{\lF(a) \otimes \lF(b)}$}};
 			\node (A') at (0,0) {\footnotesize{$U_{\lF(a)} \otimes U_{\lF(b)}$}};
@@
 				(A) edge node[left]{$\mu$} (A')
-				(A') edge node [left] {$\lF_\mu \otimes \lF_\mu$} (A'')
-				(B') edge node [right] {$\lF \circ \mu$} (B'')
-				(A) edge node[above]{$U_\phi$} (B)
+				(A') edge node [left] {$\lF_U \otimes \lF_U$} (A'')
+				(B') edge node [right] {$\lF(\mu)$} (B'')
+				(A) edge node[above]{$U_{\lF_\otimes}$} (B)
 				(B) edge node[right]{$\lF_U$} (B')
-				(A'') edge node[above]{$\phi$} (B'');
+				(A'') edge node[above]{$\lF_\otimes$} (B'');
 		\end{tikzpicture}
@@
 (E) edge node [above] {$\phi_{m_1+n_1,m_2+n_2}$} (B)
-(E'') edge node [below] {$F\psi\times F\psi$} (B'')
-(E') edge node [above] {$F\psi\times F\psi$} (B')
+(E'') edge node [below] {$F(\psi)\times F(\psi)$} (B'')
+(E') edge node [above] {$F(\psi)\times F(\psi)$} (B')
 (B) edge node [above] {$F(\psi)$} (C)
@@
 (E) edge node [above] {$\phi_{m_1+n_1,m_2+n_2}$} (B)
-(E'') edge node [below] {$F\psi\times F\psi$} (B'')
+(E'') edge node [below] {$F(\psi)\times F(\psi)$} (B'')
 (E') edge node [above] {$\phi_{n_1+m_1,n_2+m_2}$} (B')
@@
 \begin{tikzcd}[column sep=.05in,ampersand replacement=\&]
-Fm_1{\times} Fn_1{\times} Fm_2{\times} Fn_2\ar[ddr,phantom,bend right,"{\scriptstyle\stackrel[\cref{eq:braidedpseudofun}]{1\times u\times1}{\cong}}"]\ar[dr,"1\times\phi\times1"]\ar[rr,"\phi\times\phi"]\ar[ddd,"1\times\beta\times1"'] \&\& F(m_1{+}n_1){\times} F(m_2{+}n_2)\ar[d,phantom,"\scriptstyle{\cong}"]\ar[ddd,phantom,"{\scriptstyle\stackrel[\cref{eq:pseudonaturality}]{1\times\phi_{\beta,1}}{\cong}}"]\ar[rr,"\phi"] \&\& F(m_1{+}n_1{+}m_2{+}n_2)\ar[ddd,"F(1+\beta+1)"]\ar[ddl,bend left,phantom,"{\scriptstyle\stackrel[\cref{eq:pseudonaturality}]{\phi_{1,\beta+1}}{\cong}}"] \\
-\& Fm_1{\times} F(n_1 {+} m_2){\times} Fn_2\ar[rr,"{1\times\phi}"]\ar[d,"{1\times F\beta\times1}"'] \&\phantom{A}\& Fm_1{\times} F(n_1 {+} m_2 {+} n_2)\ar[d,"{1\times F(\beta+1)}"]\ar[ur,"\phi"] \& \\
-\& Fm_1{\times} F(m_2{+}n_1){\times} Fn_2\ar[rr,"1\times\phi"'] \&\phantom{A}\ar[d,phantom,"\scriptstyle\cong"]\& Fm_1{\times} F(m_2{+}n_1{+}n_2)\ar[dr,"\phi"'] \& \\
-Fm_1{\times} Fm_2{\times} Fn_1{\times} Fn_2\ar[ur,"1\times\phi\times1"']\ar[rr,"\phi\times\phi"'] \&\& F(m_1{+}m_2){\times} F(n_1{+}n_2)\ar[rr,"\phi"'] \&\& F(m_1{+}m_2{+}n_1{+}n_2)
+F(m_1){\times} F(n_1){\times} F(m_2){\times} F(n_2)\ar[ddr,phantom,bend right,"{\scriptstyle\stackrel[\cref{eq:braidedpseudofun}]{1\times u\times1}{\cong}}"]\ar[dr,"1\times\phi\times1"]\ar[rr,"\phi\times\phi"]\ar[ddd,"1\times\beta\times1"'] \&\& F(m_1{+}n_1){\times} F(m_2{+}n_2)\ar[d,phantom,"\scriptstyle{\cong}"]\ar[ddd,phantom,"{\scriptstyle\stackrel[\cref{eq:pseudonaturality}]{1\times\phi_{\beta,1}}{\cong}}"]\ar[rr,"\phi"] \&\& F(m_1{+}n_1{+}m_2{+}n_2)\ar[ddd,"F(1+\beta+1)"]\ar[ddl,bend left,phantom,"{\scriptstyle\stackrel[\cref{eq:pseudonaturality}]{\phi_{1,\beta+1}}{\cong}}"] \\
+\& F(m_1){\times} F(n_1 {+} m_2){\times} F(n_2)\ar[rr,"{1\times\phi}"]\ar[d,"{1\times F(\beta)\times1}"'] \&\phantom{A}\& F(m_1){\times} F(n_1 {+} m_2 {+} n_2)\ar[d,"{1\times F(\beta+1)}"]\ar[ur,"\phi"] \& \\
+\& F(m_1){\times} F(m_2{+}n_1){\times} F(n_2)\ar[rr,"1\times\phi"'] \&\phantom{A}\ar[d,phantom,"\scriptstyle\cong"]\& F(m_1){\times} F(m_2{+}n_1{+}n_2)\ar[dr,"\phi"'] \& \\
+F(m_1){\times} F(m_2){\times} F(n_1){\times} F(n_2)\ar[ur,"1\times\phi\times1"']\ar[rr,"\phi\times\phi"'] \&\& F(m_1{+}m_2){\times} F(n_1{+}n_2)\ar[rr,"\phi"'] \&\& F(m_1{+}m_2{+}n_1{+}n_2)
 \end{tikzcd}}
@@
 \bibitem{Borc} F. \ Borceux, \textsl{Handbook of Categorical Algebra}, vol.\ 2, 
-Cambridge University Press, Cambridge, 1994
+Cambridge University Press, Cambridge, 1994.
 

### 2021-01-21 cospans.tex
dealt with corrections Kenny noted on Zulip but did not make himself

@@
 If $\A$ and $\X$ have finite colimits and $L$ preserves them, it is known that there is a symmetric monoidal double category whose objects are those of $\A$ and whose horizontal 1-cells are structured cospans.
-Second, given a pseudofunctor $F \maps \A \to \Cat$, a `decorated cospan' is a diagram in $\A$ of the form $a \rightarrow s \leftarrow b$ together with an object of $F(s)$.
+Second, given a pseudofunctor $F \maps \A \to \Cat$, a `decorated cospan' is a diagram in $\A$ of the form $a \rightarrow m \leftarrow b$ together with an object of $F(m)$.
 Generalizing the work of Fong, we show that if $\A$ has finite colimits and $F \maps (\A,+) \to (\Cat,\times)$ is symmetric lax monoidal, there is a symmetric monoidal double category whose objects are those of $\A$ and whose horizontal 1-cells are decorated cospans.
@@
 
-In \cite{BC}, the first two authors introduce the symmetric monoidal double category of \emph{structured cospans} as a formalism to capture open networks.
-One of the main goals of this paper is to provide a monoidal double isomorphism between this double category and that of \emph{decorated cospans}, described in detail in \cref{DecCospansDoubleCat}.
+In \cite{BC}, the first two authors introduce the symmetric monoidal double category of structured cospans as a formalism to capture open networks.
+One of the main goals of this paper is to provide a monoidal double isomorphism between this double category and that of decorated cospans, described in detail in \cref{DecCospansDoubleCat}.
 We first recall the double category of structured cospans.
@@
 \begin{itemize}
-\item An object is a \define{graph structure} on $N$: that is, a graph $s,t \maps E \to N$.
-\item A morphism from $s,t \maps E \to N$ to $s',t' \maps E' \to N$ is a morphism of graphs that is
-the identity on $N$: that is, a function $g \maps E \to E'$ such that these diagrams commute:
+\item an object is a \define{graph structure} on $N$: that is, a graph $s,t \maps E \to N$,
+\item a morphism from $s,t \maps E \to N$ to $s',t' \maps E' \to N$ is a morphism of graphs that is the identity on $N$: that is, a function $g \maps E \to E'$ such that these diagrams commute:
 \[
@@
 
-In chemistry, population biology, epidemiology and other fields, modelers use `Petri nets with rates', where the transitions are labelled with positive real numbers called `rate constants' \cite{Haas,Koch,Wilkinson}.
+In chemistry, population biology, epidemiology and other fields, modelers use `Petri nets with rates', where the transitions are labeled with positive real numbers called `rate constants' \cite{Haas,Koch,Wilkinson}.
 From any Petri net with rates one can systematically construct a dynamical system.
@@
 \]
-It is an open Petri net where the transitions are labelled with rate constants $r_1, r_2 > 0$.
+It is an open Petri net where the transitions are labeled with rate constants $r_1, r_2 > 0$.
 Here is the corresponding open dynamical system:
@@
 
-A \define{lax monoidal} pseudofunctor (called \emph{weak monoidal} homomorphism in earlier references) between monoidal bicategories $F\maps\bA\to\bB$ is a pseudofunctor equipped with pseudonatural transformations with components $\phi_{a,b}\maps Fa\otimes Fb\to F(a\otimes b)$ and $\phi_0\maps I\to FI$ along with invertible modifications for associativity and unitality with components
+A \define{lax monoidal} pseudofunctor (called \emph{weak monoidal} homomorphism in some earlier references) between monoidal bicategories $F\maps\bA\to\bB$ is a pseudofunctor equipped with pseudonatural transformations with components $\phi_{a,b}\maps Fa\otimes Fb\to F(a\otimes b)$ and $\phi_0\maps I\to FI$ along with invertible modifications for associativity and unitality with components
 \begin{equation}\label{eq:omega}
 \begin{tikzcd}[column sep=.8in, row sep=.3in]
-(F a\ot F b)\ot F c\ar[ddr,phantom,"{\cong}"]\ar[r,"{\phi_{a,b}\ot1}"]\ar[d,sloped,"\sim"'] & F (a\ot b)\ot F 
+(F a\ot F b)\ot F c\ar[ddr,phantom,"{\cong}"]\ar[r,"{\phi_{a,b}\ot1}"]\ar[d,anchor=center,swap,"\sim"] & F (a\ot b)\ot F 
 c\ar[d,"{\phi_{a\ot b,c}}"] \\
 F a\ot( F b\ot F c)\ar[d,"{1\ot\phi_{b,c}}"'] & 
-F ((a\ot b)\ot c)\ar[d,sloped,"\sim"] \\
+F ((a\ot b)\ot c)\ar[d,anchor=center,"\sim"] \\
 F a\ot F(b\ot c)\ar[r,"{\phi_{a,b\ot c}}"'] &
@@
 \begin{tikzcd}[column sep=.3in,row sep=.3in]
-F a\ar[r,"\sim"]\ar[drr,sloped,"\sim"'] & F a\otimes I\ar[r,"1\otimes\phi_0"]\ar[dr,phantom,"\cong"] & F 
+F a\ar[r,"\sim"]\ar[drr,"\sim"'] & F a\otimes I\ar[r,"1\otimes\phi_0"]\ar[dr,phantom,"\cong"] & F 
 a\otimes F I\ar[d,"\phi_{a,I}"] \\
@@
 \begin{tikzcd}[column sep=.3in,row sep=.3in]
-F a\ar[r,"\sim"]\ar[drr,sloped,"\sim"'] & I\otimes F a \ar[r,"\phi_0\otimes1"]\ar[dr,phantom,"\cong"] & F 
+F a\ar[r,"\sim"]\ar[drr,"\sim"'] & I\otimes F a \ar[r,"\phi_0\otimes1"]\ar[dr,phantom,"\cong"] & F 
 I\otimes F a\ar[d,"\phi_{I,a}"] \\
@@
 
-\bibitem{BSZ} Filippo Bonchi, Pawe\l~Soboci\'nski and Fabio Zanasi, A categorical semantics of signal flow graphs, in \textsl{CONCUR 2014--Concurrency Theory}, eds.\ P.\ Baldan and D.\ Gorla, \textsl{Lecture Notes in Computer Science} vol.\ 8704, Springer, Berlin, 2014, pp.\ 435--450.
+\bibitem{BSZ} Filippo Bonchi, Pawe\l~Soboci\'nski and Fabio Zanasi, A categorical semantics of signal flow graphs, in \textsl{CONCUR 2014--Concurrency Theory}, eds.\ P.\ Baldan and D.\ Gorla, Lecture Notes in Computer Science \textbf{8704}, Springer, Berlin, 2014, pp.\ 435--450.
 Also available at \href{http://users.ecs.soton.ac.uk/ps/papers/sfg.pdf}{http://users.ecs.soton.ac.uk/ps/papers/sfg.pdf}.
@@
 %\bibitem{Be} J.\ B\'enabou, Introduction to bicategories, in {\sl Reports
-%of the Midwest Category Seminar}, Lecture Notes in Mathematics, vol.\ \textbf{47}, Springer, Berlin, 1967, pp.\ 1--77.
+%of the Midwest Category Seminar}, Lecture Notes in Mathematics \textbf{47}, Springer, Berlin, 1967, pp.\ 1--77.
 
@@
 
-\bibitem{DS} B.\ Day and R.\ Street, Monoidal Bicategories and Hopf algebroids, \textsl{Adv.\ Math.} \textbf{129} (1997), 99--157.
+\bibitem{DS} B.\ Day and R.\ Street, Monoidal bicategories and Hopf algebroids, \textsl{Adv.\ Math.} \textbf{129} (1997), 99--157.
 
@@
 
-\bibitem{KS} G.\ Kelly and R.\ Street, Review of the elements of 2-categories, in \textsl{Category Seminar}, Lecture Notes in Mathematics 40, Springer, Berlin, 1974, 
-pp.\ 75--103.
+\bibitem{KS} G.\ M.\ Kelly and R.\ Street, Review of the elements of 2-categories, in \textsl{Category Seminar}, ed.\ G.\ M.\ Kelly, Lecture Notes in Mathematics \textbf{40}, Springer, Berlin, 1974, pp.\ 75--103.
 

### 2021-01-21 cospans.tex
Rewrote first full paragraph on top of page 3.

@@
 \end{itemize}
-Many of the flawed applications of decorated cospans have been fixed using structured cospans \cite[Section 6]{BC}, but not all decorated cospans can handled using structured cospans.
-
+
+Many of the flawed applications of decorated cospans have been fixed using structured cospans \cite[Section 6]{BC}, but not all decorated cospan double categories are equivalent to structured cospan double categories.
 Here we give sufficient conditions for a decorated cospan double category to be equivalent---and in fact, isomorphic---to a structured cospan double category.
+
 Suppose $\A$ has finite colimits and $F \maps (\A , +) \to (\Cat, \times)$ is a symmetric lax monoidal pseudofunctor.  

### 2021-01-21 cospans.tex
small edits

@@
 \begin{tikzcd}[column sep=.8in, row sep=.3in]
-(F a\ot F b)\ot F c\ar[ddr,phantom,"{\cong}"]\ar[r,"{\phi_{a,b}\ot1}"]\ar[d,anchor=center,swap,"\sim"] & F (a\ot b)\ot F 
+(F a\ot F b)\ot F c\ar[ddr,phantom,"{\cong}"]\ar[r,"{\phi_{a,b}\ot1}"]\ar[d,anchor=center,sloped,swap,"\sim"] & F (a\ot b)\ot F 
 c\ar[d,"{\phi_{a\ot b,c}}"] \\
 F a\ot( F b\ot F c)\ar[d,"{1\ot\phi_{b,c}}"'] & 
-F ((a\ot b)\ot c)\ar[d,anchor=center,"\sim"] \\
+F ((a\ot b)\ot c)\ar[d,anchor=center,sloped,"\sim"] \\
 F a\ot F(b\ot c)\ar[r,"{\phi_{a,b\ot c}}"'] &
@@
 \begin{tikzcd}[column sep=.3in,row sep=.3in]
-F a\ar[r,"\sim"]\ar[drr,"\sim"'] & F a\otimes I\ar[r,"1\otimes\phi_0"]\ar[dr,phantom,"\cong"] & F 
+F a\ar[r,"\sim"]\ar[drr,sloped,"\sim"'] & F a\otimes I\ar[r,"1\otimes\phi_0"]\ar[dr,phantom,"\cong"] & F 
 a\otimes F I\ar[d,"\phi_{a,I}"] \\
@@
 \begin{tikzcd}[column sep=.3in,row sep=.3in]
-F a\ar[r,"\sim"]\ar[drr,"\sim"'] & I\otimes F a \ar[r,"\phi_0\otimes1"]\ar[dr,phantom,"\cong"] & F 
+F a\ar[r,"\sim"]\ar[drr,sloped,"\sim"'] & I\otimes F a \ar[r,"\phi_0\otimes1"]\ar[dr,phantom,"\cong"] & F 
 I\otimes F a\ar[d,"\phi_{I,a}"] \\
@@
 \label{defn:monoidal_double_category}
-A \define{monoidal double category} is a pseudomonoid in $\Dbl$. 
+A \define{monoidal double category} is a pseudomonoid in $\Dbl$, namely it is equipped with double functors $\otimes\colon\lD\times\lD\to\lD$, $I\colon\one\to\lD$ and invertible double transformations $\otimes\circ(1\times\otimes)\cong\otimes\circ(\otimes\times1)$, $\otimes\circ(1\times I)\cong1\cong\otimes\circ(I\times1)$ satisfying standard axioms.
 \end{defn} 
@@
 \begin{itemize}
-\item monoidal structures on both $\lD_0$ and $\lD_1$ (each with tensor product denoted $\otimes$, associator $a$, left unitor $\ell$ and right unitor $r$ and unit object $I_\lD$), such that $U \maps \lD_0 \to \lD_1$ strictly preserves the unit objects and $S,T \maps \lD_1 \to \lD_0$ are strict monoidal,
+\item monoidal structures on both $\lD_0$ and $\lD_1$ (each with tensor product denoted $\otimes$, associator $a$, left unitor $\ell$ and right unitor $r$ and unit object $I$), such that $U \maps \lD_0 \to \lD_1$ strictly preserves the unit objects and $S,T \maps \lD_1 \to \lD_0$ are strict monoidal,
 \item the structure of a double functor on $\otimes$:
@@
 \begin{defn}\label{defn:monoidal_double_functor}
-Given symmetric monoidal double categories $\lD$ and $\lE$, a \define{symmetric monoidal double functor} $\lF \maps \lD \to \lE$ is a double functor $\lF$ together with invertible transformations $\theta \maps {\otimes \circ (\lF,\lF)} \to \lF \circ \otimes$ and $\theta_U \maps I_\lE \to \lF \circ I_\lD$ that satisfy the usual coherence axioms for a symmetric monoidal functor with respect to $\otimes$.
+Given symmetric monoidal double categories $\lD$ and $\lE$, a \define{symmetric monoidal double functor} $\lF \maps \lD \to \lE$ is a double functor $\lF$ together with invertible transformations $\lF_\otimes\maps {\otimes \circ (\lF,\lF)} \to \lF \circ \otimes$ and $I_\lE \to \lF \circ I_\lD$ that satisfy the usual coherence axioms for a symmetric monoidal functor.
 \end{defn}
-%{\chris Those units in the definition should be monoidal units not unit functors...}
-%%% Kenny: How about I instead of 1?
-%%% Christina: Sure but that was NOT in the definition of symmetric monoidal double category above...could you streamline??
 \noindent

### 2021-01-22 cospans.tex
erased %%%
small fixes

@@
 % in LaTeX
-% 2021/1/20
+% 2021/1/21
 
@@
 
-Many of the flawed applications of decorated cospans have been fixed using structured cospans \cite[Section 6]{BC}, but not all decorated cospan double categories are equivalent to structured cospan double categories.
+Many of the flawed applications of decorated cospans have been fixed using structured cospans \cite[Section 6]{BC}, but not every decorated cospan double category is equivalent to a structured cospan double category.
 Here we give sufficient conditions for a decorated cospan double category to be equivalent---and in fact, isomorphic---to a structured cospan double category.
@@
 In \cref{spinoffs}, we establish the isomorphism between structured and decorated cospans at the level of bicategories and categories (via decategorification).
-Finally, in \cref{Applications}, we describe applications.
+Finally, in \cref{Applications}, we describe applications, and show that open dynamical system can be described using decorated cospans but not structured cospans.
 
@@
 
-Notice that in the above proof, when we compose two structured cospans, namely two horizontal 1-cells in the double category ${}_L\lCsp(\inta F)$ as in \cref{eq:pushoutissum}, the resulting composite cospan apex ends up being a sum on the second variable due to the definition of the left adjoint functor $L$ which forces the feet of all cospans to involve a fiberwise initial object.
-Consequently, one could remark that in fact, the assumptions of \cref{thm:equiv} should only state that the corresponding pseudofunctor $F\colon \A\to\SMC$ factors through categories with finite coproducts rather than $\Rex$.
-We leave the statement as is in order to match the general assumptions of \cref{thm:SC} for the definition of the structured cospan symmetric monoidal double category.
+%Notice that in the above proof, when we compose two structured cospans, namely two horizontal 1-cells in the double category ${}_L\lCsp(\inta F)$ as in \cref{eq:pushoutissum}, the resulting composite cospan apex ends up being a sum on the second variable due to the definition of the left adjoint functor $L$ which forces the feet of all cospans to involve a fiberwise initial object.Thus in fact the assumptions of \cref{thm:equiv} could be weakened to state that the pseudofunctor $F\colon \A\to\SMC$ factors through the 2-category of categories with finite coproducts.
 
@@
 \end{itemize}
-\noindent
-%%% Christina: the notation is not streamlined.
-We occasionally use $F_\otimes$ and $F_\odot$ (which I prefer) and in the definitions above we use various greek letters like $\phi$ (which is definitely overused in our paper).
-Could this be fixed throughout the document?
-Similarly for the unit comparison maps.
 

### 2021-01-22 cospans_arxiv_1.tex
first arXiv version (polished remarks after Theorem 3.2)

--- 2021-01-22 cospans.tex
@@
 % in LaTeX
-% 2021/1/21
+% 2021/1/22 - first arXiv version
 
@@
 
-In a similar way, the rest of the axioms of \cref{defn:monoidal_double_functor} hold: on the cospan level they are easy to verify, whereas on the decoration level they entail nontrivial calculations based on the involved structures.
+In a similar way, the rest of the axioms of \cref{defn:monoidal_double_functor} hold: on the cospan level they are easy to verify, whereas on the decoration level they entail nontrivial calculations based on the structures involved.
 In conclusion, the double isomorphism \cref{eq:doubleiso} is an isomorphism of symmetric monoidal double categories.
@@
 
-%Notice that in the above proof, when we compose two structured cospans, namely two horizontal 1-cells in the double category ${}_L\lCsp(\inta F)$ as in \cref{eq:pushoutissum}, the resulting composite cospan apex ends up being a sum on the second variable due to the definition of the left adjoint functor $L$ which forces the feet of all cospans to involve a fiberwise initial object.Thus in fact the assumptions of \cref{thm:equiv} could be weakened to state that the pseudofunctor $F\colon \A\to\SMC$ factors through the 2-category of categories with finite coproducts.
+In fact, a careful examination of the proof reveals that the assumptions of \cref{thm:equiv} could be weakened to state that the pseudofunctor $F \maps \A \to \SMC$ factors through the 2-category $\mathbf{Cocart}$ of cocartesian monoidal categories.
+The reason is that when we compose two structured cospans as in \cref{eq:pushoutissum}, the apex of the composite cospan ends up being a sum in the second variable due to the definition of the left adjoint functor $L$ which forces the feet of all cospans to involve a fiberwise initial object.
+However, in the interesting examples so far, when $F$ factors through $\mathbf{Cocart}$ it also factors through $\Rex$.
 

### 2021-01-22 cospans.tex
small edit

@@
 
-\bibitem{McCrudden} P.\ McCrudden, Balanced coalgebroids, \textsl{Theory Appl.\ Categ.\ } \textbf{7} (2000), 71--147.
+\bibitem{McCrudden} P.\ McCrudden, Balanced coalgebroids, \textsl{Theory Appl.\ Categ.\ }\textbf{7} (2000), 71--147.
 

### 2021-01-22 cospans_arxiv_1.tex
first arxiv version (with preamble built in)

@@
 \documentclass[reqno]{amsart}
-\input{Equiv_preamble.tex}
+
+\usepackage{amssymb,amsmath,stmaryrd,txfonts,mathrsfs,amsthm}
+\usepackage{comment}
+\usepackage[neveradjust]{paralist}
+\usepackage{mathtools}
+\usepackage{multirow}
+\usepackage[outline]{contour}
+\contourlength{1.2pt}
+\usepackage{tikz}
+\usetikzlibrary{intersections,arrows.meta,calc,quotes,math,decorations.pathreplacing,decorations.markings,cd,arrows,positioning,fit,matrix,
+shapes.geometric,external,decorations.pathmorphing,backgrounds,circuits,circuits.ee.IEC,shapes}
+\usepackage[a4paper,top=3cm,bottom=3cm,inner=3cm,outer=3cm]{geometry}
+\usepackage[foot]{amsaddr}
+\usepackage{graphicx}
+\usepackage{stackrel}
+
+% colors
+\usepackage{xcolor}
+\usepackage{framed,color}
+
+\definecolor{shadecolor}{rgb}{1,0.8,0.3}
+\definecolor{myurlcolor}{rgb}{0.5,0,0}
+\definecolor{mycitecolor}{rgb}{0,0,0.7}
+\definecolor{myrefcolor}{rgb}{0,0,0.7}
+\definecolor{hyperrefcolor}{rgb}{0.5,0,0}
+
+% hyperlinks
+
+\usepackage{hyperref}
+\hypersetup{
+	colorlinks,
+	linkcolor={hyperrefcolor},
+	citecolor={hyperrefcolor},
+	urlcolor={hyperrefcolor}
+}
+
+\newcommand{\backref}[1]{(Referred to on page #1.)}
+
+\usepackage[draft]{fixme}
+\usepackage[capitalize]{cleveref}
+\crefname{equation}{}{}
+\crefname{defn}{Definition}{Definitions}
+\crefname{thm}{Theorem}{Theorems}
+\crefname{lem}{Lemma}{Lemmas}
+
+\definecolor{rewritecolor}{rgb}{0,.9,1}
+\tikzset{rewritenode/.style={shape=circle,fill=rewritecolor,scale=0.25,font=\Huge}}
+\tikzset{RWopen/.style={shape=circle,draw=black,fill=white,scale=0.5,font=\Huge}}
+\tikzset{RWclosed/.style={shape=circle,fill=black,scale=0.5,font=\Huge}}
+\tikzset{CDnode/.style={shape=circle,fill=white,scale=.5}}
+\makeatletter
+\let\ea\expandafter
+
+\pgfdeclarelayer{edgelayer}
+\pgfdeclarelayer{nodelayer}
+\pgfsetlayers{edgelayer,nodelayer,main}
+
+% Petri nets
+\definecolor{lblue}{rgb}{0,250,255}
+\tikzstyle{species}=[circle,fill=yellow,draw=black,scale=1.15]
+\tikzstyle{transition}=[rectangle,fill=lblue,draw=black,scale=1.15]
+\tikzstyle{inarrow}=[->, >=stealth, shorten >=.03cm,line width=1.5]
+\tikzstyle{empty}=[circle,fill=none, draw=none]
+\tikzstyle{inputdot}=[circle,fill=purple,draw=purple, scale=.25]
+\tikzstyle{inputarrow}=[->,draw=purple, shorten >=.05cm]
+\tikzstyle{simple}=[-,draw=purple,line width=1.000]
+\tikzstyle{none}=[inner sep=0pt]
+
+\tikzset{->-/.style={decoration={
+  markings,
+  mark=at position .5 with {\arrow{>}}},postaction={decorate}}}
+
+%% Defining commands that are always in math mode.
+\def\mdef#1#2{\ea\ea\ea\gdef\ea\ea\noexpand#1\ea{\ea\ensuremath\ea{#2}}}
+\def\alwaysmath#1{\ea\ea\ea\global\ea\ea\ea\let\ea\ea\csname your@#1\endcsname\csname #1\endcsname
+  \ea\def\csname #1\endcsname{\ensuremath{\csname your@#1\endcsname}}}
+
+\mdef\fahat{\hat{\fa}}
+
+% MISCELLANEOUS SYMBOLS
+\newcommand{\inv}{^{-1}}
+\newcommand{\op}{^{\mathit{op}}}
+\newcommand{\co}{^{\mathit{co}}}
+\newcommand{\coop}{^{\mathit{coop}}}
+\newcommand{\id}{\mathrm{id}}
+\let\adj\dashv
+\newcommand{\pullbackcorner}[1][dr]{\save*!/#1-1.2pc/#1:(-1,1)@^{|-}\restore}
+\let\iso\cong
+\let\eqv\simeq
+\let\cng\equiv
+\alwaysmath{ell}
+\alwaysmath{infty}
+\alwaysmath{odot}
+\def\frc#1/#2.{\frac{#1}{#2}}   % \frc x^2+1 / x^2-1 .
+\mdef\ten{\mathrel{\otimes}}
+\newcommand{\simrightarrow}{\xrightarrow{\raisebox{-3pt}[0pt][0pt]{\ensuremath{\sim}}}}
+
+\newcommand{\N}{\mathbb{N}}
+\newcommand{\R}{\mathbb{R}}
+\newcommand{\Ob}{\mathrm{Ob}}
+\newcommand{\Mor}{\mathrm{Mor}}
+
+\newcommand*{\graysquare}{\textcolor{lightgray}{\blacksquare}}
+
+%% OPERATORS
+\DeclareMathOperator\colim{colim}
+\DeclareMathOperator\eq{eq}
+\DeclareMathOperator\Aut{Aut}
+\DeclareMathOperator\End{End}
+\DeclareMathOperator\Hom{Hom}
+\DeclareMathOperator\Map{Map}
+
+%% ARROWS
+% \to already exists
+\newcommand{\too}[1][]{\ensuremath{\overset{#1}{\longrightarrow}}}
+\newcommand{\oot}[1][]{\ensuremath{\overset{#1}{\longleftarrow}}}
+\let\toot\rightleftarrows
+\let\otto\leftrightarrows
+\let\maps\colon
+
+%% EXTENSIBLE ARROWS
+\let\xto\xrightarrow
+\let\xot\xleftarrow
+
+% THEOREM-TYPE ENVIRONMENTS, hacked to
+%% (a) number all with the same numbers, and
+%% (b) have the right names for autoref
+\def\defthm#1#2{%
+  \newtheorem{#1}{#2}[section]%
+  \expandafter\def\csname #1autorefname\endcsname{#2}%
+  \expandafter\let\csname c@#1\endcsname\c@thm}
+\newtheorem{thm}{Theorem}[section]
+\newcommand{\thmautorefname}{Theorem}
+\defthm{cor}{Corollary}
+\defthm{prop}{Proposition}
+\defthm{lem}{Lemma}
+\defthm{conj}{Conjecture}
+\defthm{hyp}{Hypothesis}
+\defthm{fact}{Fact}
+\theoremstyle{definition}
+\defthm{defn}{Definition}
+\defthm{notn}{Notation}
+\theoremstyle{remark}
+\defthm{rmk}{Remark}
+\defthm{eg}{Example}
+
+\newcommand{\fhat}{\ensuremath{\hat{f}}}
+
+% Also number formulas with the theorem counter
+%\let\c@equation\c@thm
+%\numberwithin{equation}{section}
+
+% Only show numbers for equations that are actually referenced (or
+% whose tags are specified manually) - uses mathtools. %Christina: for some reason, the command below made it impossible to label any equation!
+%\mathtoolsset{showonlyrefs,showmanualtags}
+
+\def\tobar{\mathrel{\mkern3mu  \vcenter{\hbox{$\scriptscriptstyle+$}}%
+                    \mkern-12mu{\to}}}
+
+%\input{decls}
+%\UseAllTwocells
+
+\mdef\fchk{\check{f}}
+
+\definecolor{purple(x11)}{rgb}{0.5, 0.0, 0.5}
+\def\purple{\color{purple(x11)}}
+\def\chris{\purple}
+\newcommand{\upback}{\mathbin{\rotatebox[origin=c]{135}{$\ulcorner$}}}
+
+% xypic
+\usepackage[all,2cell,cmtip]{xy}
+%\input{decls}
+\UseAllTwocells
+
+% sets
+
+\newcommand{\La}{\mathcal{L}}
+
+% categories
+
+\newcommand{\ca}{\mathsf}
+\newcommand{\Set}{\mathsf{Set}}
+\newcommand{\Graph}{\mathsf{Graph}}
+\newcommand{\Dynam}{\mathsf{Dynam}}
+\newcommand{\Mark}{\mathsf{Mark}}
+\newcommand{\Petri}{\mathsf{Petri}}
+\newcommand{\B}{\mathsf{B}}
+\newcommand{\A}{\mathsf{A}}
+\newcommand{\C}{\mathsf{C}}
+\newcommand{\J}{\mathsf{J}}
+\newcommand{\T}{\mathsf{T}}
+\newcommand{\D}{\mathsf{D}}
+\newcommand{\X}{\mathsf{X}}
+\newcommand{\Y}{\mathsf{Y}}
+\newcommand{\Z}{\mathsf{Z}}
+\newcommand{\Lag}{\mathsf{Lag}}
+\newcommand{\SemiAlg}{\mathsf{SemiAlg}}
+\newcommand{\Fin}{\mathsf{Fin}}
+\newcommand{\Rel}{\mathsf{Rel}}
+\newcommand{\Cospan}{\mathsf{Cospan}}
+\newcommand{\Csp}{\mathsf{Csp}}
+\newcommand{\Circ}{\mathsf{Circ}}
+\newcommand{\CMC}{\mathsf{CMC}}
+\newcommand{\RxNet}{\mathsf{RxNet}}
+\newcommand{\one}{\mathsf{1}}
+
+% bicategories
+
+\newcommand{\bicat}{\mathbf}
+\newcommand{\Dbl}{\bicat{Dbl}}
+\newcommand{\bCsp}{\bicat{Csp}}
+\newcommand{\bA}{\bicat{A}}
+\newcommand{\bB}{\bicat{B}}
+\newcommand{\bX}{\bicat{X}}
+\newcommand{\bY}{\bicat{Y}}
+\newcommand{\bD}{\bicat{D}}
+\newcommand{\Cat}{\bicat{Cat}}
+\newcommand{\MonCat}{\bicat{MonCat}}
+\newcommand{\Rex}{\bicat{Rex}}
+\newcommand{\SMC}{\bicat{SymMonCat}}
+\newcommand{\OpICat}{\bicat{OpICat}}%probably too much to use?
+\newcommand{\OpFib}{\bicat{OpFib}}
+
+% double categories
+
+\newcommand{\double}[1]{\mathbf{\mathbb #1}}
+\newcommand{\lCsp}{\double{Csp}}
+\newcommand{\lCospan}{\double{Cospan}}
+\newcommand{\lOpen}{\double{Open}}
+\newcommand{\lA}{\double{A}}
+\newcommand{\lB}{\double{B}}
+\newcommand{\lC}{\double{C}}
+\newcommand{\lD}{\double{D}}
+\newcommand{\lE}{\double{E}}
+\newcommand{\lF}{\double{F}}
+\newcommand{\lG}{\double{G}}
+\newcommand{\lH}{\double{H}}
+\newcommand{\lR}{\double{R}}
+\newcommand{\lX}{\double{X}}
+\newcommand{\lY}{\double{Y}}
+
+% this puts definitions in boldface
+
+\newcommand{\define}[1]{{\bf \boldmath{#1}}}
+
+% other gunk
+
+\newcommand{\dcsp}[1]{{#1}\mathbb{C}\textnormal{sp}}
+\newcommand{\scsp}[2]{_{#1}\mathbb{C}\textnormal{sp}\left(#2\right)}
+\tikzset{tick/.style={postaction={decorate,decoration={markings,
+mark=at position 0.4 with {\draw[-] (0,.4ex) -- (0,-.4ex);}}}}}
+\newcommand{\tickar}{\begin{tikzcd}[baseline=-0.5ex,cramped,sep=small,ampersand replacement=\&]{}\ar[r,tick]\&{}\end{tikzcd}}
+\newcommand{\cspn}[5]{\begin{tikzcd}[baseline=-0.5ex,cramped,sep=small,ampersand replacement=\&]{#1}\ar[r,"#4"] \& {#2} \& {#3}\ar[l,"#5"']\end{tikzcd}}
+
+\newcommand{\inta}{\raisebox{.3\depth}{$\smallint\hspace{-.01in}$}}
+\newcommand{\pse}{\mathrm{ps}}
+\newcommand{\mapseqq}{:=}
+\newcommand{\ot}{\otimes}
+\newcommand{\To}{\Rightarrow}
 
@@
 The reason is that when we compose two structured cospans as in \cref{eq:pushoutissum}, the apex of the composite cospan ends up being a sum in the second variable due to the definition of the left adjoint functor $L$ which forces the feet of all cospans to involve a fiberwise initial object.
-However, in the interesting examples so far, when $F$ factors through $\mathbf{Cocart}$ it also factors through $\Rex$.
+However, in the most interesting examples seen so far, when $F$ factors through $\mathbf{Cocart}$ it also factors through $\Rex$.
 

### 2021-01-23 to_ams_editor_1.tex
first AMS version and letter to editor

\documentclass{ucrmath}
\signature{John Baez}
\address{Department of Mathematics \\ University of California \\ Riverside, CA}

\begin{document}

\begin{letter}{}
\opening{Dear Henri Darmon:}

This is a paper in the field of applied category theory.   It proves that two constructions of a double category of cospans equipped with extra structure are equivalent under certain conditions, and it illustrates the applications of these constructions in a number of fields.   I'm submitting it to you because the AMS website says you're the editor for ``unclassified'' papers at \textsl{Transactions of the American Mathematical Society}, and this paper doesn't fit squarely in the other classifications.

\closing{Sincerely,}

\end{letter}

\end{document}

### 2021-01-30 cospans.tex
1st arXiv version (polished paragraph after proof of Thm. 3.2)
fixed typo

@@
 % in LaTeX
-% 2021/1/22 - first arXiv version
+% 2021/1/29 - changes after first arXiv version
 
@@
 The category of objects $F\lCsp_0$ is simply $\A$, whereas $F$-decorated cospans and maps between them form the category of arrows $F\lCsp_1$.
-The (vertical) composition of two maps of $F$-decorated cospan is
+The (vertical) composite of two maps of $F$-decorated cospan is
 \begin{equation}\label{eq:verticalcompo}

### 2021-02-15 cospans.tex
change last diagram in proof of Theorem 2.1

@@
 % in LaTeX
-% 2021/1/29 - changes after first arXiv version
+% 2021/2/15 - changes after first arXiv version
 
@@
 \begin{tikzcd}[column sep=.55in]
-\one\ar[r,"\phi_0"]\ar[dr,phantom,near start,"{\scriptstyle\stackrel{\cref{eq:unitality}}{\cong}}"]\ar[d,"\phi_0\times\phi_0"'] & F(0)\ar[dr,phantom,"{\scriptstyle\stackrel{\cref{eq:pseudonaturality}}{\cong}}"]\ar[r,"F(!_{a+b})"] & F(a+b)\ar[d,"F(1)"] \\
+\one\ar[r,"\phi_0"]\ar[dr,phantom,near start,"{\scriptstyle\stackrel{\cref{eq:unitality}}{\cong}}"]\ar[d,"\phi_0\times\phi_0"'] & F(0)\ar[dr,phantom,"{\scriptstyle\stackrel{\cref{eq:pseudonaturality}}{\cong}}"]\ar[r,"F(!_{a+b})"] & F(a+b)\ar[d,"1"] \\
 F(0)\times F(0)\ar[r,"F(!_a)\times F(!_b)"']\ar[ur,"\phi_{0,0}"description] & F(a)\times F(b)\ar[r,"\phi_{a,b}"'] & F(a+b)
@@
 \end{displaymath}
+%%% changed F(1) to 1 in the righthand vertical arrow - jb
 where the top composite is $\bot_{a+b}$ by \cref{eq:UFCsp} and the bottom composite is $\phi_{a,b}(\bot_a,\bot_b)$ by \cref{eq:tensordecoration}.

### 2021-03-15 cospans_new.tex
started new version "cospans_new.tex"

--- 2021-01-22 cospans_arxiv_1.tex
@@
 % in LaTeX
-% 2021/1/22 - first arXiv version
+% 2021/3/15 - attempt at new version
 
@@
 \newcommand{\inv}{^{-1}}
-\newcommand{\op}{^{\mathit{op}}}
-\newcommand{\co}{^{\mathit{co}}}
+\newcommand{\op}{^{\mathrm{op}}}
+\newcommand{\co}{^{\mathrm{co}}}
 \newcommand{\coop}{^{\mathit{coop}}}
@@
 \newcommand{\lOpen}{\double{Open}}
+\newcommand{\Fr}{\double{Fr}}
 \newcommand{\lA}{\double{A}}
@@
 Instead of basing the theory of decorated cospans on a symmetric lax monoidal functor $F \maps (\A, +) \to (\Set, \times)$, we use a symmetric lax monoidal pseudofunctor $F \maps (\A, +) \to (\Cat, \times)$.
-In \cref{thm:decorated_cospans,DC}, we use this
+In \cref{thm:decorated_cospans,thm:decorated_cospans_2}, we use this
 data to construct a symmetric monoidal double category $F\lCsp$ in which:
@@
 
-We thank Daniel Cicala, Brendan Fong, and Joe Moeller for helpful conversations.
+We thank Daniel Cicala, Brendan Fong, Joe Moeller and especially Michael Shulman for helpful conversations.
 The third author would like to thank the General Secretariat for Research  and Technology (GSRT) and the Hellenic Foundation for Research and Innovation (HFRI).
@@
 In this section we build symmetric monoidal double categories of decorated cospans, and then study the functoriality of this construction.
-The definition of a lax monoidal pseudofunctor is recalled in \cref{subsec:bicats}, and the definition of a double category is recalled in \cref{defn:double_category}.
+\cref{thm:decorated_cospans} explains how to construct a double category of decorated cospans from a lax monoidal pseudofunctor $F \maps (\A,+) \to (\Cat, \times)$  whenever $A$ has finite colimits ({\bf or is just cocartesian?}).
+\cref{thm:decorated_cospans_2} gives conditions under which this double category is symmetric monoidal.
+The definition of lax monoidal pseudofunctor is recalled in \cref{subsec:bicats}, and the definition of symmetric monoidal double category is recalled in \cref{defn:double_category}.
 
@@
 
-\begin{thm}\label{thm:decorated_cospans}
+\begin{thm}\label{thm:decorated_cospans_1}
 Let $\A$ be a category with finite colimits and $F \maps (\A,+) \to (\Cat,\times)$ a lax monoidal pseudofunctor. Then there exists a double category $F\lCsp$ in which
@@
 
-\begin{proof}
-Take $\A$ to have finite colimits and let $(F,\phi,\phi_0) \maps (A,+) \to (\Cat,\times)$ be a lax monoidal pseudofunctor.
-We shall define the category of objects $F\lCsp_0$, the category of arrows $F\lCsp_1$, as well as the four structure functors which tie them together: the source and target functors $S,T \maps F\lCsp_1 \to F\lCsp_0$, the unit functor $U \maps F\lCsp_0 \to F\lCsp_1$, and the composition functor $\odot \maps F\lCsp_1 \times_{F\lCsp_0} F\lCsp_1 \to F\lCsp_1$.
-
-The category of objects $F\lCsp_0$ is simply $\A$, whereas $F$-decorated cospans and maps between them form the category of arrows $F\lCsp_1$.
-The (vertical) composition of two maps of $F$-decorated cospan is
-\begin{equation}\label{eq:verticalcompo}
- \begin{tikzcd}
-a\ar[r,"i"]\ar[d,"f"'] & m\ar[d,"h"] & b\ar[l,"o"']\ar[d,"g"]  & x\in F(m) \\
-a'\ar[r,"{i'}"]\ar[d,"{f'}"'] & m'\ar[d,"{h'}"] & b'\ar[l,"{o'}"']\ar[d,"{g'}"] & x'\in F(m') \\
-a''\ar[r,"{i''}"] & m'' & b''\ar[l,"{o''}"'] & x''\in F(m'')
- \end{tikzcd}\;=\;
- \begin{tikzcd}[column sep=.3in]
-a\ar[r,"i"]\ar[dd,"{f'f}"'] & m\ar[dd,"{h'h}"] & b\ar[l,"o"']\ar[dd,"{g'g}"]  & x\in F(m) \\
-\hole \\
-a''\ar[r,"{i''}"] & m'' & b''\ar[l,"{o''}"'] & x''\in F(m'')  
- \end{tikzcd}
-\end{equation}
-where if $\tau \maps F(h)(x) \to x'$ and $\tau' \maps F(h')(x') \to x''$ are the decoration morphisms, 
-\begin{equation}\label{eq:tauofverticalcomposite}
-F(h'h)(x) \simrightarrow F(h')F(h)(x)\xrightarrow{F(h')(\tau)}F(h')(x')\xrightarrow{\tau'}x''
-\end{equation}
-is the decoration of the composite, where the first isomorphism comes from pseudofunctoriality of $F$.
-
-The source and target functors $S$ and $T$ map an $F$-decorated cospan to the source and target of the cospan and a map of decorated cospans \cref{eq:mapofdec} to $f$ and $g$ respectively.
-The unit functor $U$ maps an object $a$ to
-\begin{equation}\label{eq:UFCsp}
-\begin{tikzcd}
-a\ar[r,"1_a"] & a & a,\ar[l,"1_a"'] & \bot_a:=\one\xrightarrow{\phi_0}F(0)\xrightarrow{F(!_a)}F(a)
-\end{tikzcd}
-\end{equation}
-where $\bot_a \in F(a)$ is called the \define{trivial decoration}, and a vertical 1-morphism $f\maps a\to a'$ to
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$a$};
-\node (A') at (0,-0.5) {$a'$};
-\node (B) at (1,0.5) {$a$};
-\node (C) at (2,0.5) {$a$};
-\node (C') at (2,-0.5) {$a'$};
-\node (D) at (1,-0.5) {$a'$};
-\node (E) at (3,0.5) {$\bot_a \in F(a)$};
-\node (F) at (3,-0.5) {$\bot_{a'} \in F(a')$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$1_a$} (B)
-(C) edge node[above]{$1_a$} (B)
-(A) edge node[left]{$f$} (A')
-(C) edge node[right]{$f$} (C')
-(A') edge node[above] {$1_{a'}$} (D)
-(C') edge node[above] {$1_{a'}$} (D)
-(B) edge node [left] {$f$} (D);
-\end{tikzpicture}
-\]
-together with the decoration morphism $F(f)F(!_a)\phi_0(*)\cong F(!_{a'})\phi_0(*)$.
-Finally, the (horizontal) composition functor $\odot$ maps two composable $F$-decorated cospans 
-\[  M=\left(a\to m\leftarrow b,x\in F(m)\right), \qquad N=\left(b\to n\leftarrow c,y\in F(n)\right)\] 
-to $N\odot M$, which as a cospan is their pushout in $\A$ over their shared foot, shown in dashed arrows here:
-\begin{equation}\label{eq:dcospanscomposition}
-\begin{tikzpicture}[scale=1.2,baseline=(current bounding box.center)]
-\node (A) at (0,0) {$a$};
-\node (B) at (1,1) {$m$};
-\node (C) at (2,0) {$b$};
-\node (D) at (3,1) {$n$};
-\node (E) at (4,0) {$c$};
-\node (F) at (2,2) {$m+n$};
-\node (G) at (2,3) {$m+_{b} n$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i$} (B)
-(C) edge node[above]{$o$} (B)
-(C) edge node [above] {$i'$} (D)
-(E) edge node [above] {$o'$} (D)
-(B) edge node [below] {$\iota_m$} (F)
-(D) edge node [below] {$\iota_{n}$} (F)
-(B) edge[bend left=10] node [above] {$v_m\;$} (G)
-(D) edge[bend right=10] node [above] {$\;v_n$} (G)
-(F) edge node [fill=white] {$\psi$} (G)
-(A) edge[dashed,bend left] node [left] {} (G)
-(E) edge[dashed,bend right] node [right] {} (G);
-\end{tikzpicture}
-\end{equation}
-equipped with the decoration
-\[  y\odot x:= \one\cong\one \times \one \xrightarrow{x \times y} F(m) \times F(n) \xrightarrow{\phi_{m,n}} F(m+n) \xrightarrow{F(\psi)} F(m+_{b}n) \]
-where $\psi \maps m + n \to m+_{b} n$ is the natural map from the coproduct to the pushout. Moreover, given two horizontally composable maps of $F$-decorated cospans $\alpha$ and $\beta$ 
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$a$};
-\node (A') at (0,-0.5) {$a'$};
-\node (B) at (1,0.5) {$m$};
-\node (C) at (2,0.5) {$b$};
-\node (C') at (2,-0.5) {$b'$};
-\node (D) at (1,-0.5) {$m'$};
-\node (E) at (3,0.5) {$x \in F(m)$};
-\node (F) at (3,-0.5) {$x' \in F(m')$};
-\node (G) at (4,0.5) {$b$};
-\node (H) at (5,0.5) {$n$};
-\node (I) at (6,0.5) {$c$};
-\node (G') at (4,-0.5) {$b'$};
-\node (H') at (5,-0.5) {$n'$};
-\node (I') at (6,-0.5) {$c'$};
-\node (J) at (7,0.5) {$y \in F(n)$};
-\node (K) at (7,-0.5) {$y' \in F(n')$};
-\node (L) at (1,-1) {$\tau_\alpha \maps F(h_1)(x) \to x'$};
-\node (M) at (5,-1) {$\tau_\beta \maps F(h_2)(y) \to y'$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i_1$} (B)
-(C) edge node[above]{$o_1$} (B)
-(A) edge node[left]{$f$} (A')
-(C) edge node[right]{$g$} (C')
-(A') edge node[above] {$i_1'$} (D)
-(C') edge node[above] {$o_1'$} (D)
-(B) edge node [left] {$h_1$} (D)
-(G) edge node [above] {$i_2$} (H)
-(G) edge node [left] {$g$} (G')
-(H) edge node [left] {$h_2$} (H')
-(G') edge node [above] {$i_2'$} (H')
-(I) edge node [above] {$o_2$} (H)
-(I) edge node [right] {$k$} (I')
-(I') edge node [above] {$o_2'$} (H');
-\end{tikzpicture}
-\]
-their composite $\beta\odot \alpha$ is the horizontal composite of the two cospans in $\A$
-\begin{equation}\label{eq:horizontalcompo}
-\begin{tikzpicture}[scale=1.5,baseline=(current bounding box.center)]
-\node (A) at (0,0.5) {$a$};
-\node (A') at (0,-0.5) {$a'$};
-\node (B) at (1.5,0.5) {$m+_{b} n$};
-\node (C) at (3,0.5) {$c$};
-\node (C') at (3,-0.5) {$c'$};
-\node (D) at (1.5,-0.5) {$m'+_{b'}n'$};
-\node (E) at (4.5,0.5) {$y \odot x \in F(m+_b n)$};
-\node (F) at (4.5,-0.5) {$y' \odot x' \in F(m' +_{b'} n')$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{} (B)
-(C) edge node[above]{} (B)
-(A) edge node[left]{$f$} (A')
-(C) edge node[right]{$k$} (C')
-(A') edge node [above]{} (D)
-(C') edge node [above]{} (D)
-(B) edge node [left] {$h_1 +_g h_2$} (D);
-\end{tikzpicture}
-\end{equation}
-together with the decoration morphism $\tau_{\beta \odot \alpha} \maps F(h_1 +_g h_2)(y \odot x) \to (y' \odot x')$ given by the diagram:
-\begin{equation}\label{eq:decohorizontalcompo}
-\begin{tikzpicture}[scale=1.7,baseline=(current bounding box.center)]
-\node (A) at (4.75,0) {$\scriptstyle\Downarrow \tau_\alpha \times \tau_\beta$};
-\node (D) at (3,0) {$\one \cong \one \times \one$};
-\node (E) at (5.5,0.5) {$F(m) \times F(n)$};
-\node () at (6.5,0) {$\stackrel{\phi_{h_1,h_2}}{\cong}$};
-\node () at (8.5,0) {$\cong$};
-\node (E') at (5.5,-0.5) {$F(m') \times F(n')$};
-\node (B) at (7.5,0.5) {$F(m+n)$};
-\node (B') at (7.5,-0.5) {$F(m' + n')$};
-\node (C) at (9.5,0.5) {$F(m+_{b} n)$};
-\node (C') at (9.5,-0.5) {$F(m' +_{b'} n')$};
-\path[->,font=\scriptsize,>=angle 90]
-(E) edge node [above] {$\phi_{m,n}$} (B)
-(E') edge node [above] {$\phi_{m',n'}$} (B')
-(B) edge node [above] {$F(\psi)$} (C)
-(B') edge node [above] {$F(\psi)$} (C')
-(C) edge node  [fill=white] {$F(h_1 +_g h_2)$} (C')
-(B) edge node [fill=white] {$F(h_1 + h_2)$} (B')
-(D) edge node [above] {$x \times y$} (E)
-(D) edge node [below] {$x' \times y'$} (E')
-(E) edge node [fill=white] {$F(h_1) \times F(h_2)$} (E');
-\end{tikzpicture}
-\end{equation}
-where the middle isomorphism is \cref{eq:pseudonaturality} from pseudonaturality of $\phi$ and the right-hand side isomorphism is due to pseudofunctoriality of $F$.
-
-The associator for horizontal composition
-is formed as follows: for three composable horizontal 1-cells $M_1=(a\to m_1\leftarrow b,x_1\in F(m_1))$, $M_2=(b\to m_2\leftarrow c,x_2\in F(m_2))$ and $M_3=(c\to m_3\leftarrow d,x_3\in F(m_3)),$
-the isomorphism $(M_3\odot M_2)\odot M_1\cong M_3\odot (M_2\odot M_1)$ is the isomorphism of cospans 
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$a$};
-\node (A') at (0,-0.5) {$a$};
-\node (B) at (1.5,0.5) {$m_1+_{b}(m_2 +_{c} m_3)$};
-\node (C) at (3,0.5) {$d$};
-\node (C') at (3,-0.5) {$d$};
-\node (D) at (1.5,-0.5) {$(m_1+_{b} m_2)+_{c} m_3$};
-\node (E) at (5.5,0.5) {$(x_3 \odot x_2) \odot x_1 \in F(m_1+_{b} (m_2 +_{c} m_3))$};
-\node (F) at (5.5,-0.5) {$x_3 \odot (x_2 \odot x_1) \in F((m_1+_{b} m_2)+_{c} m_3)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$$} (B)
-(C) edge node[above]{$$} (B)
-(A) edge node[left]{$1_a$} (A')
-(C) edge node[right]{$1_d$} (C')
-(A') edge node {$$} (D)
-(C') edge node {$$} (D)
-(B) edge node [left] {$\stackrel{\kappa}{\cong}$} (D);
-\end{tikzpicture}
-\]
-together with an isomorphism $F(\kappa)((x_3 \odot x_2) \odot x_1) \cong (x_3 \odot (x_2 \odot x_1))$ between the decorations 
-\begin{equation}\label{eq:decoiso}
-\scalebox{.7}
-{\begin{tikzcd}[ampersand replacement=\&]
-\& F(m_1){\times}(F(m_2){\times}F(m_3))\ar[dddrr,phantom,"\stackrel{\cref{eq:omega}}{\cong}"]\ar[r,"1\times\phi_{m_2,m_3}"]\ar[ddd,"\alpha"description] \& F(m_1){\times}F(m_2{+}m_3)\ar[r,"1\times F(\psi)"]\ar[dr,"\phi_{m_1,m_2+m_3}"'] \& F(m_1){\times}F(m_2{+_c}m_3)\ar[d,phantom,"\stackrel{\cref{eq:pseudonaturality}}{\cong}"]\ar[r,"\phi_{m_1,m_2+_cm_3}"] \& F(m_1{+}(m_2{+_c}m_3))\ar[r,"F(\psi)"]\ar[dddr,phantom,"\cong"] \& F(m_1{+_b}(m_2{+_c}m_3))\ar[ddd,"F(\kappa)"] \\
-\one\ar[ur,"x_1\times(x_2\times x_3)"]\ar[d,equal] \&\&\& F(m_1{+}(m_2{+}m_3))\ar[ur,"F(1+\psi)"']\ar[d,"F(\alpha)"] \& \\
-\one\ar[dr,"(x_1\times x_2)\times x_3"']\&\&\& F((m_1{+}m_2){+}m_3)\ar[dr,"F(\psi+1)"]\ar[d,phantom,"\stackrel{\cref{eq:pseudonaturality}}{\cong}"] \& \\
-\& (F(m_1){\times}F(m_2)){\times}F(m_3)\ar[r,"\phi_{m_1,m_2}\times1"'] \& F(m_1{+}m_2){\times}m_3\ar[ur,"\phi_{m_1+m_2,m_3}"]\ar[r,"F(\psi)\times1"'] \& F(m_1{+_b}m_2){\times} F(m_3)\ar[r,"\phi_{m_1{+_b}m_2,m_3}"'] \& F((m_1{+_b}m_2){+}m_3)\ar[r,"F(\psi)"'] \& F((m_1{+_b}m_2){+_c}m_3)
-\end{tikzcd}}
-\end{equation}
-where $\alpha$ are the associators of $\Cat$ and $\A$ and $\kappa$ is the canonical isomorphism between two colimits of the same diagram in $\A$.
-
-The right and left unitors are defined similarly: for example, for a horizontal 1-cell $M=(a\to m \leftarrow b,x\in F(m))$, the isomorphism $M\odot U_a\cong M$ is given by the canonical map of cospans $\kappa\colon a+_am\cong m$ along with this isomorphism between decorations:
-\begin{equation}\label{eq:decunitor}
- \scalebox{.9}
-{\begin{tikzcd}[row sep=.15in,ampersand replacement=\&]
-1\ar[r,"\phi_0\times x"]\ar[dd,equal] \& F(0)\times F(m)\ar[dd,phantom,"{\stackrel{\cref{eq:unitality}}{\cong}}"] \ar[dr,"\phi_{0,m}"']\ar[r,"F(!_a)\times 1"] \& F(a)\times F(m)\ar[d,phantom,"{\stackrel{\cref{eq:pseudonaturality}}{\cong}}"]\ar[r,"\phi_{a,m}"] \& F(a+m)\ar[ddr,phantom,"{\cong}"]\ar[r,"F(\psi)"] \& F(a+_am)\ar[dd,"F(\kappa)"]\\
-\&\& F(0+m)\ar[drr,sloped,"\sim"]\ar[ur,"F(!_a+1)"'] \&\&  \\
-1\ar[rrrr,"x"'] \&\phantom{A}\&\&\& F(m).
- \end{tikzcd}}
-\end{equation}
-All the double category axioms can be verified using the fact that cospans in $\A$ form a double category and $F$ is a lax monoidal pseudofunctor.
-\end{proof}
-
-The following result establishes that under the same assumptions as \cref{thm:decorated_cospans}, the double category of decorated cospans is monoidal; it becomes symmetric when the lax monoidal pseudofunctor is.
-Monoidal and symmetric monoidal double categories are recalled in \cref{defn:monoidal_double_category,defn:symmetric_monoidal_double_category}.
-
-\begin{thm}\label{DC}
+\begin{thm}\label{thm:decorated_cospans_2}
 Let $\A$ be a category with finite colimits and let $(F,\phi,\phi_0)\maps (\A,+) \to (\Cat,\times)$ be a symmetric lax monoidal pseudofunctor.
@@
 \end{equation}
-
-\begin{comment}
-%old version:
-\begin{equation}\label{eq:tensordecoration}
-\begin{tikzcd}
-& m_1+m_2 & \\
-a_1+a_2\ar[ur,"i_1+i_2"] && b_1+b_2,\ar[ul,"o_1+o_2"']
-\end{tikzcd}\qquad x_1\otimes x_2:=\one \xrightarrow{x_1\times x_2}F(m_1)\times F(m_2)\xrightarrow{\phi_{m_1,m_2}}F(m_1+m_2)
-\end{equation}
-\end{comment}
-
 \item of two 2-morphisms $\alpha$ and $\beta$ is:
@@
 
-\begin{proof}
-We first show that the categories of objects and arrows are symmetric monoidal, and that the source and target functors are symmetric strict monoidal.
-Indeed, the category of objects $F\lCsp_0=\A$ is symmetric monoidal under the chosen binary coproducts in $\A$.
-The category of arrows $F\lCsp_1$ is also symmetric monoidal, with tensor product as in \cref{eq:tensordecoration} and monoidal unit
-\[
-I_1=\left(0\xrightarrow{!}0 \xleftarrow{!}0, \one \xrightarrow{\phi_0}F(0) \xrightarrow{F(!_0)} F(0) \right) 
-\]
-where $0$ is the initial object in $\A$.  By \cref{eq:UFCsp}, this unit $I_1$ is equal to $U_{0}$ as required.   In all that follows, we shall assume that $F(!_0)$ is the identity, so that
-\begin{equation}\label{eq:monoidalunitFCsp}
-I_1=\left(0\xrightarrow{!}0 \xleftarrow{!}0, \one \xrightarrow{\phi_0}F(0)\right).
-\end{equation}
-This can always be achieved by replacing $F$ by an equivalent normal pseudofunctor, namely one that strictly preserves identity morphisms \cite[Proposition 5.2]{LP}.
-We do this merely to reduce the size of  our diagrams; the reader can reinsert the morphism $F(!_0)$ where needed.
-
-The associator for the monoidal structure in $F\lCsp$ is formed as follows: for three objects
-$M_1=(a_1\to m_1\leftarrow b_1,x_1\in F(m_1))$, $M_2=(a_2\to m_2\leftarrow b_2,x_2\in F(m_2))$ and $M_3=(a_3\to m_3\leftarrow b_3,x_3\in F(m_3))$,
-the isomorphism $(M_1\ot M_2)\ot M_3\cong M_1\ot(M_2\ot M_3)$ is the isomorphism of cospans
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0.5) {$(a_1+a_2)+a_3$};
-\node (A') at (0,-0.5) {$a_1+(a_2+a_3)$};
-\node (B) at (2.25,0.5) {$(m_1+m_2)+m_3$};
-\node (C) at (4.5,0.5) {$(b_1+b_2)+b_3$};
-\node (C') at (4.5,-0.5) {$b_1+(b_2+b_3)$};
-\node (D) at (2.25,-0.5) {$m_1+(m_2+m_3)$};
-\node (E) at (7,0.5) {$(x_1 \otimes x_2) \otimes x_3 \in F((m_1{+}m_2){+}m_3)$};
-\node (F) at (7,-0.5) {$x_1 \otimes (x_2 \otimes x_3)\in F(m_1{+}(m_2{+}m_3))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$(i_1{+}i_2){+}i_3$} (B)
-(C) edge node[above]{$(o_1{+}o_2){+}o_3$} (B)
-(A) edge node[left]{$\stackrel{\alpha}{\cong}$} (A')
-(C) edge node[right]{$\stackrel{\alpha}{\cong}$} (C')
-(A') edge node [below]{$i_1{+}(i_2{+}i_3)$} (D)
-(C') edge node [below]{$o_1{+}(o_2{+}o_3)$} (D)
-(B) edge node [left] {$\stackrel{\alpha}{\cong}$} (D);
-\end{tikzpicture}
-\]
-together with the decoration isomorphism between $F(\alpha)((x_1 \otimes x_2) \otimes x_3)\stackrel{\cref{eq:tensordecoration}}{=}F(\alpha)(\phi_{m_1{+}m_2,m_3}(\phi_{m_1,m_2}(x_1,x_2),x_3))$ and $x_1 \otimes (x_2 \otimes x_3)=\phi_{m_1,m_2{+}m_3}(x_1,\phi_{m_2,m_3}(x_2,x_3))$ formed in the same way as the left two-piece part of \cref{eq:decoiso}.
-For the left and right unitors $I_1\ot M\cong M\cong M\ot I_1$ for any $M=(a\to m\leftarrow b,x\in F(m))$, we have isomorphisms of cospans
-\begin{displaymath}
- \begin{tikzcd}[column sep=.3in]
-0+a\ar[rr,"1+i"]\ar[d,"\stackrel{\ell}{\cong}"'] && 0+m\ar[d,"\stackrel{\ell}{\cong}"'] && 0+b\ar[ll,"1+o"']\ar[d,"\stackrel{\ell}{\cong}"] &&1\ar[r,"\phi_0\times x"] & F(0)\times F(m)\ar[r,"\phi_{0,m}"] & F(0+m) \\
-a\ar[rr,"i"] && m && b\ar[ll,"o"'] && \one \ar[r,"x"] & F(m)\\
-a+0\ar[rr,"i+1"']\ar[u,"\stackrel{r}{\cong}"] && m+0\ar[u,"\stackrel{r}{\cong}"] && b+0\ar[ll,"o+1"]\ar[u,"\stackrel{r}{\cong}"']
-&&\one \ar[r,"x\times\phi_0"] & F(m)\times F(0)\ar[r,"\phi_{m,0}"] & F(m+0)
- \end{tikzcd}
-\end{displaymath}
-with isomorphisms between decorations precisely given by \cref{eq:unitality}.
-Finally, the braiding in $F\lCsp_1$ is inherited from that in $\A$ and $F$, with braiding $\beta\maps M_1\ot M_2\to M_2\ot M_1$ the cospan isomorphism
-\begin{equation}\label{eq:braidingFCsp1}
- \begin{tikzcd}[column sep=.25in]
-a_1+a_2\ar[rr,"i_1+i_2"]\ar[d,"\stackrel{\beta}{\cong}"'] && m_1+m_2\ar[d,"\stackrel{\beta}{\cong}"'] && b_1+b_2\ar[ll,"o_1+o_2"']\ar[d,"\stackrel{\beta}{\cong}"] &\one\ar[r,"x_1\times x_2"] & F(m_1)\times F(m_2)\ar[r,"\phi_{m_1,m_2}"] & F(m_1+m_2) \\
-a_2+a_1\ar[rr,"i_2+i_1"'] && m_2+m_1 && b_2+b_1\ar[ll,"o_2+o_1"] &\one \ar[r,"x_2\times x_1"] & F(m_2)\times F(m_1)\ar[r,"\phi_{m_2,m_1}"] & F(m_2+m_1)
- \end{tikzcd}
-\end{equation}
-together with the decoration isomorphism 
-\begin{equation}\label{eq:decobraiding}
- \begin{tikzcd}
-  1\ar[r,"x_1\times x_2"]\ar[dr,"x_2\times x_1"'] & F(m_1)\times F(m_2)\ar[d,"\beta"']\ar[r,"\phi_{m_1,m_2}"]\ar[dr,phantom,"{\stackrel[\cref{eq:braidedpseudofun}]{u_{a,b}}{\cong}}"] & F(m_1+m_2)\ar[d,"F(\beta)"] \\
-  & F(m_2)\times F(m_1)\ar[r,"\phi_{m_2,m_1}"'] & F(m_2+m_1)
- \end{tikzcd}
-\end{equation}
-All axioms for a symmetric monoidal category can be verified,
-and it is easy to see that with these structures, the source and target functors $S,T\maps F\lCsp_1\to F\lCsp_0$ are symmetric strict monoidal.
-
-Lastly, according to \cref{defn:monoidal_double_category} we need to construct two globular 2-isomorphisms $(M_2 \otimes N_2)\odot (M_1 \otimes N_1) \simrightarrow(M_2\odot M_1) \otimes (N_2\odot N_1)$ and $U_{a + b} \simrightarrow U_a \otimes U_b$ that express compatibility of the tensor product with horizontal composition and units.
-For any appropriate four decorated cospans
-\begin{gather}\label{eq:4deccospans}
-M_1=\left(a\xrightarrow{i_1}m_1\xleftarrow{o_1}b,x_1\in F(m_1)\right),\;\; M_2=\left(b\xrightarrow{i_2}m_2\xleftarrow{o_2}c,x_2\in F(m_2)\right) \\
-N_1=\left(a'\xrightarrow{i'_1}n_1\xleftarrow{o'_1}b',y_1\in F(n_1)\right),\;\; N_2=\left(b'\xrightarrow{i'_2}n_2\xleftarrow{o'_2}c',y_2\in F(n_2)\right)\nonumber
-\end{gather}
-first tensoring $M_1\ot N_1$, $M_2\ot N_2$ by \cref{eq:tensordecoration} and then horizontally composing them by \cref{eq:dcospanscomposition} gives
-\begin{equation}\label{eq:bigeq1}
-\scalebox{.8}{\begin{tikzcd}[column sep={.6in,between origins},ampersand replacement=\&]
-\&\& (m_1+n_1)+_{b{+}b'}(m_2+n_2)\ar[dd,phantom,near start,"\upback"] \&\& \\
-\& m_1+n_1\ar[ur] \&\& m_2+n_2\ar[ul] \& \\
-a+a'\ar[ur,"{i_1+i'_1}"] \&\& b+b'\ar[ul,"{o_1+o'_1}"']\ar[ur,"{i_2+i'_2}"] \&\& c+c'\ar[ul,"{o_2+o'_2}"']
-\end{tikzcd}}\hspace{-.2in}
-\scalebox{.8}{\begin{tikzcd}[ampersand replacement=\&,column sep=.5in]
-\one \ar[ddrr,dashed,"{(x_2 \otimes y_2)\odot(x_1 \otimes y_1)}"']\ar[r,"x_1{\times}y_1{\times}x_2{\times}y_2"] \& F(m_1){\times}F(n_1){\times}F(m_2){\times}F(n_2)\ar[r,"\phi_{m_1,n_1}\times\phi_{m_2,n_2}"] \& F(m_1{+}n_1){\times}F(m_2{+}n_2) \ar[d,"\phi_{m_1+n_1,m_2+n_2}"] \\
-\&\& F(m_1+n_1+m_2+n_2)\ar[d,"F(\psi)"] \\
-\&\& F((m_1+n_1)+_{b+b'}(m_2+n_2))
-\end{tikzcd}}
-\end{equation}
-If we first horizontally compose $M_2\odot M_1$, $N_2\odot N_1$ and then tensor the result, we obtain
-\begin{equation}\label{eq:bigeq2}
-  \scalebox{.8}{\begin{tikzcd}[column sep=.3in,ampersand replacement=\&]
- \& (m_1+_b m_2)+(n_1+_{b'}n_2) \& \\
- \hole \\
- a+a'\ar[uur]%,"{u_{m_1}i_1+u_{n_1}i'_1}"] 
- \&\& c+c'\ar[uul]%,"{u_{m_2}o_2+u_{n_2}o'_2}"']  
- \end{tikzcd}}\hspace{-.2in}
- \scalebox{.8}{\begin{tikzcd}[ampersand replacement=\&,column sep=.4in]
-\one \ar[ddrr,dashed,"{(x_2\odot x_1) \otimes (y_2\odot y_1)}"']\ar[r,"x_1{\times}x_2{\times}y_1{\times}y_2"] \& F(m_1){\times}F(m_2){\times}F(n_1){\times}F(n_2)\ar[r,"\phi_{m_1,m_2}\times\phi_{n_1,n_2}"] \& F(m_1{+}m_2){\times}F(n_1{+}n_2) \ar[d, "F(\psi) \times F(\psi)"] \\
-\&\& F(m_1+_bm_2)\times F(n_1+_{b'}n_2)\ar[d,"\phi_{m_1+_bm_2,n_1+_{b'}n_2}"] \\
-\&\& F((m_1+_bm_2)+(n_1+_{b'}n_2))
-\end{tikzcd}}
-\end{equation}
-where the legs of the cospan are the sums of the dashed ones of the appropriate diagrams \cref{eq:dcospanscomposition}.
-Thus the (globular) cospan isomorphism is the canonical universal map between the colimit of the same diagram obtained in two different ways $\hat{\chi}\maps (m_1+n_1)+_{b+b'}(m_2+n_2)\cong(m_1+_b m_2)+(n_1+_{b'}n_2)$, and the decoration isomorphism can be built in a similar way using coherent isomorphisms as follows:
-\begin{equation}\label{eq:interchangedeco}
- \scalebox{.75}{\begin{tikzcd}[ampersand replacement=\&,column sep=.3in,row sep=.1in]
-\& F(m_1)\times F(n_1)\times F(m_2)\times F(n_2)\ar[dd,"1\times\beta\times1"']\ar[ddrr,phantom,"\stackrel{\cref{eq:thetaa}}{\cong}"]\ar[rr,"\phi_{m_1,n_1}\times\phi_{m_2,n_2}"] \&\& F(m_1+n_1)\times F(m_2+n_2)\ar[rr,"\phi_{m_1+n_1,m_2+n_2}"] \&\& F(m_1+n_1+m_2+n_2)\ar[dd,"F(\psi)"]\ar[ddll,"F(1+\beta+1)"'] \\
-\one \ar[ur,"{x_1\times y_1\times x_2\times y_2}"]\ar[dr,"{x_1\times x_2\times y_1\times y_2}"'] \&\&\&\& \\
-\& F(m_1)\times F(m_2)\times F(n_1)\times F(n_2)\ar[dd,"\phi_{m_1,m_2}\times\phi_{n_1,n_2}"']\&\& F(m_1+m_2+n_1+n_2)\ar[ddrr,"F(\psi+\psi)"']\ar[dd,phantom,"\stackrel{\cref{eq:pseudonaturality}}{\cong}"] \ar[rr,phantom,"\cong"]\&\& F((m_1+n_1)+_{b+b'}(m_2+n_2))\ar[dd,"F(\hat{\chi})"] \\
-\hole \\
-\& F(m_1+m_2)\times F(n_1+n_2)\ar[uurr,"\phi_{m_1+m_2,n_1+n_2}"']\ar[rr,"F(\psi)\times F(\psi)"'] \&\& F(m_1+_bm_2)\times F(n_1+_{b'}n_2)\ar[rr,"\phi_{m_1+_b m_2,n_1+_{b'}n_2}"'] \&\& F((m_1+_bm_2)+(n_1+_{b'}n_2))
-\end{tikzcd}}
-\end{equation}
-where the left-hand side isomorphism \cref{eq:thetaa} is spelled out in detail in \cref{eq:proofofaxiom} and combines the pseudoassociativity \cref{eq:omega} and braided monoidal structure \cref{eq:braidedpseudofun} of the pseudofunctor $F$, and the right hand side isomorphism follows from the universal property of colimits and pseudofunctoriality of $F$.
-
-Similarly, for the comparison isomorphism between the units $U_{a+b}$ and $U_a\ot U_b$, it is easy to see that as cospans they are both the identity $1_{a+b} \maps a+b\to a+b\leftarrow a+b:1_{a+b}$, and there is a canonical isomorphism between their decorations
-\begin{displaymath}
-\begin{tikzcd}[column sep=.55in]
-\one\ar[r,"\phi_0"]\ar[dr,phantom,near start,"{\scriptstyle\stackrel{\cref{eq:unitality}}{\cong}}"]\ar[d,"\phi_0\times\phi_0"'] & F(0)\ar[dr,phantom,"{\scriptstyle\stackrel{\cref{eq:pseudonaturality}}{\cong}}"]\ar[r,"F(!_{a+b})"] & F(a+b)\ar[d,"F(1)"] \\
-F(0)\times F(0)\ar[r,"F(!_a)\times F(!_b)"']\ar[ur,"\phi_{0,0}"description] & F(a)\times F(b)\ar[r,"\phi_{a,b}"'] & F(a+b)
-\end{tikzcd}
-\end{displaymath}
-where the top composite is $\bot_{a+b}$ by \cref{eq:UFCsp} and the bottom composite is $\phi_{a,b}(\bot_a,\bot_b)$ by \cref{eq:tensordecoration}.
-
-It can be verified that with this structure, $F\lCsp$ is indeed a symmetric monoidal double category, namely all coherence laws are satisfied.
-In order to give the reader a sense of what these checks entail, we provide a proof of the fact that the braiding is a transformation of double categories in \cref{eq:proofofaxiom}.
+We prove both these theorems using the work of Shulman \cite{Shulman2008}, which we recall here.   First we need a few concepts.   Opfibrations are recalled in \cref{subsec:fibrations}, 
+and fibrations are defined dually, with a functor $\Phi \maps \C \to \A$ being a fibration if and only
+if $\Phi\op \maps \C\op \to \A\op$ is an opfibration.
+A functor $\Phi \maps \C \to \A$ is a \define{bifibration} if it is both a fibration and an opfibration.
+If $\Phi \maps \C \to \A$ an opfibration we have for any morphism $f \maps a \to b$ in $\A$ a covariant reindexing functor
+\[    f_! \maps \C_a \to \C_b \]
+between the fibers of $\Phi$, as recalled in \cref{subsec:fibrations}.  Similarly, if $\Phi$ is a fibration we have a contravariant reindexing functor
+\[    f^\ast \maps \C_b \to \C_a .\]
+Thus, in a bifibration we have both covariant and contravariant reindexing functors, and in 
+fact $f^\ast$ is left adjoint to $f_\ast$ \cite[Proposition 3.9]{Shulman2008}.   Using this one can easily show that for any commutative square in $\A$
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$a$};
+\node (B) at (1,0) {$b$};
+\node (C) at (0,-1) {$c$};
+\node (D) at (1,-1) {$d$};
+%\node (E) at (0.5,-0.5) {$\Downarrow\theta$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$h$} (B)
+(A) edge node[left]{$k$} (C)
+(B) edge node[right]{$g$} (D)
+(C) edge node[below]{$f$} (D);
+\end{tikzpicture}
+\]
+the following square commutes up to a natural transformation:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$\C_a$};
+\node (B) at (1,0) {$\C_b$};
+\node (C) at (0,-1) {$\C_c$};
+\node (D) at (1,-1) {$\C_d$};
+\node (E) at (0.5,-0.5) {$\Searrow \theta$};
+\path[->,font=\scriptsize,>=angle 90]
+(B) edge node[above]{$h^\ast$} (A)
+(A) edge node[left]{$k_!$} (C)
+(B) edge node[right]{$g_!$} (D)
+(D) edge node[below]{$f^\ast$} (C);
+\end{tikzpicture}
+\]
+If $\theta$ is a natural isomorphism whenever the original square in $\A$ was
+a pushout, we say $\Phi$ is \define{Beck--Chevalley}.
+
+\begin{lem}[\textbf{Shulman}] \label{lem:shulman}
+Suppose $\A$ has finite colimits and $\Phi \maps \C \to \A$ is a Beck--Chevalley bifibration.  Then there is a double category $\Fr(\Phi)$ in which
+
+\begin{itemize}
+\item an object is an object of $\A$,
+\item a vertical 1-morphism is a morphism of $\A$,
+\item a horizontal 1-cell is a pair of objects $a,b \in \A$ together with an
+object $c \in C$ with $\Phi(c) = a + b$.
+\item a 2-morphism is a pair of morphisms $f \maps a \to a'$, $g \maps b \to b'$ 
+in $\A$ together with a morphism $h \maps c \to c'$ with $\Phi(h) = f + g$.
+\end{itemize}
+If $\Phi$ is a symmetric monoidal bifibration then $\Fr(\Phi)$ becomes a symmetric
+monoidal double category.
+\end{lem}
+
+\begin{proof} This is \cite[Theorem 14.9]{Shulman2008}; Shulman proves the dual version in more detail in his Theorem 14.4.  
 \end{proof}
 
-There is an alternative proof of the above theorem when the hypothesis of \cref{thm:equiv} hold.
-In this case we show, in the proof of \cref{thm:equiv}, that the decorated cospan double category $F \lCsp$ is isomorphic to a certain double category ${}_L \lCsp(\inta  F)$ constructed using \emph{structured} cospans.
-We also show that under this isomorphism, all the symmetric monoidal structure of $F \lCsp$---the tensor product, associator, etc.---matches that of  ${}_L \lCsp(\inta  F)$, which we have proved to obey the axioms of a symmetric monoidal double category (see \cref{thm:SC}).
-It follows that $F \lCsp$ is a symmetric monoidal double category.
+\begin{proof}[Proof of \cref{thm:decorated_cospans_1}] We apply \cref{lem:shulman} to ....
+\end{proof}
+
+\begin{proof}[Proof of \cref{thm:decorated_cospans_2}] We apply \cref{lem:shulman} to ....
+\end{proof}
+
+\begin{comment}
+We can draw the 2-morphism as follows, {\bf but with ticks on the horizontal arrows!}:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$a$};
+\node (B) at (1,0) {$a'$};
+\node (C) at (0,-1) {$b$};
+\node (D) at (1,-1) {$b'$};
+\node (E) at (0.5,-0.5) {$\Downarrow\theta$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$c$} (B)
+(A) edge node[left]{$f$} (C)
+(B) edge node[right]{$g$} (D)
+(C) edge node[above]{$c'$} (D);
+\end{tikzpicture}
+\]
+\end{comment}
 
@@
 (B) edge node[right]{$E$} (D)
-(C) edge node[above]{$F'$} (D);
+(C) edge node[below]{$F'$} (D);
 \end{tikzpicture}
@@
 One of the main goals of this paper is to provide a monoidal double isomorphism between this double category and that of decorated cospans, described in detail in \cref{DecCospansDoubleCat}.
-We first recall the double category of structured cospans.
+We first recall the double category of structured cospans, along with a new construction of it.
 
@@
 In fact, the double category structure only requires that $\X$ have pushouts, whereas the symmetric monoidal structure also requires that $\X$ and $\A$ have finite coproducts and that $L$ preserve these \cite[Theorem~3.2.3]{CourserThesis}.
+
+{\bf NEW PROOF.}
 \end{proof}
@@
 
-The ``corresponding pseudofunctor'' comes from the so-called monoidal Grothendieck construction, and the conditions of this theorem relate to the existence of colimits as well as left adjoints for opfibrations.
+The `corresponding pseudofunctor' comes from the so-called monoidal Grothendieck construction, and the conditions of this theorem relate to the existence of colimits as well as left adjoints for opfibrations.
 We first sketch the relevant underlying framework in detail, and then we proceed to the proof of the theorem.
-The basics of fibration theory needed for our purposes are recalled in \cref{sec:fibrations}.
+The basics of fibration theory needed for our purposes are recalled in \cref{subsec:fibrations}.
 
@@
 As a left adjoint, this induced $L$ preserves all colimits that exist between the categories $\A$ and $\inta F$, which have finite colimits, so we can construct the double category of structured cospans $_L\lCsp(\inta F)$ of \cref{thm:SC}.
-Its objects and vertical 1-morphisms are those of the category $\A$ (just as for $F\lCsp$), whereas its horizontal 1-cells are now cospans of the form $\cspn{L(a)}{(m,x)}{L(b)}{}{}$ in the Grothendieck category $\inta F$ (see \cref{def:GrothCat}).
-Explicitly, they consist of two pairs of morphisms
-\begin{equation}\label{eq:scsphor1cell}
- (a,\bot_a)\xrightarrow{\scalebox{0.7}{\(\begin{cases}i\maps a\to m &\textrm{in }\A \\!\maps F(i)(\bot_a)\to x &\textrm{in }F(m)\end{cases}\)}}(m,x)\xleftarrow{\scalebox{0.7}{\(\begin{cases}o\maps b\to m &\textrm{in }\A \\!\maps F(o)(\bot_b)\to x &\textrm{in }F(m)\end{cases}\)}}(b,\bot_b)
-\end{equation}
-with $x\in F(m)$; recall that the reindexing functors $F(i),F(o)$ preserve all finite colimits across the fibers.
-Finally, the 2-morphisms of this double category in this context unravel as follows:
-\begin{equation}\label{eq:2morphismLCspintaF}
-\scalebox{.9}
- {\begin{tikzcd}[row sep=1in,column sep=1.7in,ampersand replacement=\&]
- (a,\bot_a)\ar[r,"{\begin{cases}i\maps a\to m &\textrm{in }\A \\!\maps F(i)(\bot_a)\to x &\textrm{in }F(m)\end{cases}}"]\ar[d,"{\begin{cases}f\maps a\to a' &\textrm{in }\A \\\chi_a\maps F(f)(\bot_a)\cong \bot_{a'} &\textrm{in }F(a')\end{cases}}"description] \& (m,x) \ar[d,"{\begin{cases}k\maps m\to m' &\textrm{in }\A \\ \tau\maps F(k)(x)\to x' &\textrm{in }F(m')\end{cases}}"description] \& (b,\bot_b)\ar[l,"{\begin{cases}o\maps b\to m &\textrm{in }\A \\!\maps F(o)(\bot_b)\to x &\textrm{in }F(m)\end{cases}}"']\ar[d,"{\begin{cases}g\maps b\to b' &\textrm{in }\A \\\chi_b\maps F(g)(\bot_b)\cong \bot_{b'} &\textrm{in }F(b')\end{cases}}"description] \\
- (a',\bot_{a'})\ar[r,"{\begin{cases}i'\maps a'\to m' &\textrm{in }\A \\!\maps F(i')(\bot_{a'})\to x' &\textrm{in }F(m')\end{cases}}"'] \& (m',x') \& (b',\bot_{b'})\ar[l,"{\begin{cases}o'\maps b'\to m' &\textrm{in }\A \\!\maps F(o')(\bot_{b'})\to x' &\textrm{in }F(m')\end{cases}}"]
- \end{tikzcd}}
-\end{equation}
-where the outside vertical legs come from the definition of $L$ on arrows \cref{eq:Lonarrows}. 
-Explicitly, the commutativity of the above squares translates to the conditions $k\circ i=i'\circ f$ and $k\circ o=o'\circ g$ in $\A$, and also to
-\begin{gather}\label{eq:Grothcommutativity}
- F(k\circ i)(\bot_a)\cong Fk(Fi(\bot_a))\xrightarrow{Fk(!)}Fk(x)\xrightarrow{\tau}x'= \\
- F(i'\circ f)(\bot_a)\cong Fi'(Ff(\bot_a))\xrightarrow{Fi'(\chi_a)}Fi'(\bot_{a'})\xrightarrow{!}x'\nonumber
-\end{gather}
-in the fiber $F(m')$, by composition in the Grothendieck category \cref{eq:compGrothcat}.
-Since both morphisms emanate from the mapped initial object in $F(m')$ under the finite-colimit-preserving reindexing functors, they are the unique such into $x'$ therefore this gives no extra conditions; similarly for the equality including $o,o'$.
-
-Building towards an isomorphism of the above described double categories, we now define a double functor sending structured cospans to decorated cospans:
-\begin{displaymath}
-\lE=(\lE_0,\lE_1)\maps _L\lCsp(\inta F) \longrightarrow F\lCsp.
-\end{displaymath}
-We set $\lE_0 \maps \A \to \A$ to be the identity, and decree that $\lE_1$ sends any
-$L$-structured cospan as in \cref{eq:scsphor1cell} to the decorated cospan
-$a \xrightarrow{i} m \xleftarrow{o} b$ with decoration $x\in F(m)$, whereas $\lE_1$ sends 
-any map of $L$-structured cospans as in \cref{eq:2morphismLCspintaF} to the
-map of $F$-decorated cospans given by
-\[
-\begin{tikzcd}
-a\ar[r,"i"]\ar[d,"f"'] & m\ar[d,"k"] & b\ar[l,"o"']\ar[d,"g"] \\
-a'\ar[r,"i'"']& m' & b'\ar[l,"o'"]
-\end{tikzcd}
-\]
-along with the morphism of decorations $\tau\maps F(k)(x) \to x'$ in $F(m')$ coming from the middle arrow of \cref{eq:2morphismLCspintaF}.
-We then make $\lE$ into double functor as in \cref{def:doublefun}.
-First, both $\lE_0$ and $\lE_1$ are functors that appropriately commute with sources and targets.
-Second, we equip $\lE$ with globular 2-isomorphisms $\lE(N) \odot \lE(M) \simrightarrow\lE(N \odot M)$
-for any pair of composable horizontal 1-cells $M=\cspn{(a,\bot_a)}{(m,x)}{(b,\bot_b)}{}{}$ and $N=\cspn{(b,\bot_b)}{(n,y)}{(c,\bot_c)}{}{}$ and $U_{\lE (m)} \simrightarrow\lE(U_m)$ for any object $m$ of $_L\lCsp(\inta F)$.
-Explicitly, $\mathbb{E}(N)\odot \mathbb{E}(M)$ is given as in \cref{eq:dcospanscomposition} via the pushout cospan and decoration
-\begin{equation}\label{eq:1}
- \begin{tikzcd}
-  & m+_bn & \\
-  a\ar[ur] && b\ar[ul]
- \end{tikzcd}\qquad
-  \one\xrightarrow{x\times y}F(m)\times F(n)\xrightarrow{\phi_{m,n}}F(m+n)\xrightarrow{F(\psi)}F(m+_bn).
-\end{equation}
-On the other hand, $N \odot M$ computed as in \cref{eq:globalpushout} is 
-\begin{equation}\label{eq:pushoutissum}
- \begin{tikzcd}[column sep={.7in,between origins}]
- && (m+_b n,F(v_m)x+_{(\bot_{m+_bn})}F(v_n)y) && \\
- & (m,x) \ar[ur] && (n,y)\ar[ul] \\
- (a,\bot_a)\ar[ur] && (b,\bot_b)\ar[ur]\ar[ul] && (c,\bot_c)\ar[ul]
- \end{tikzcd}
-\end{equation}
-where $v_m,v_n$ are the canonical maps into the pushout.
-Under $\lE$ this is mapped to the cospan $\cspn{a}{m+_bn}{b}{}{}$ with decoration $F(v_m)x+F(v_n)y$ in the fiber $F(m+_bn)$ -- since a pushout over an initial object is just a sum.
-This decoration is canonically isomorphic to that of \cref{eq:1} due to the following diagram
-\begin{equation}\label{eq:isomorphismdiag}
- \begin{tikzcd}[sep=.4in]
-F(m)\times F(n)\ar[r,"\phi_{m,n}"]\ar[d,"F(v_m)\times F(v_n)"']\ar[dr,phantom,"\stackrel{\phi_{v_m,v_n}}{\cong}"] & F(m+n)\ar[r,"F(\psi)"]\ar[dr,phantom,"\cong"']\ar[d,"F(v_m+v_n)"] & F(m+_bn)\ar[d]\\
-F(m+_bn)\times F(m+_bn)\ar[r,"\phi_{m+_bn,m+_bn}"'] & F\left((m+_bn)+(m+_bn)\right)\ar[r,"F(\nabla)"'] & F(m+_bn)
- \end{tikzcd}
-\end{equation}
-where the composite of the bottom two arrows is the coproduct $+ \maps F(m+_bn) \times F(m+_bn) \to F(m+_bn)$ as in \cref{eq:explicitstructure1}.
-The left-hand isomorphism comes from pseudonaturality of $\phi$ as in \cref{eq:pseudonaturality}, whereas the right-hand isomorphism follows from universal properties and pseudofunctoriality of $F$.
-Thus, we have a globular 2-isomorphism  $\lE_\odot\colon\lE(N) \odot \lE(M) \simrightarrow\lE(N \odot M)$.
-
-Finally, we construct a globular 2-isomorphism $U_{\lE (m)} \simrightarrow\lE(U_m)$.
-The identity horizontal 1-cell $U_m$ in $_L\lCsp(\inta F)$ is $\cspn{(m,\bot_m)}{(m,\bot_m)}{(m,\bot_m)}{}{}$ with $1_m$ as the $A$-component and isomorphisms between initial objects in the fibers.
-Thus $\lE(U_m)$ is the identity cospan in $A$ together with the `initial decoration' $\bot_m\in F(m)$, and so is $U_{\mathbb{E}(m)}$ as in \cref{eq:UFCsp}.
-It can be verified that with this structure, $\lE$ satisfies the axioms of a double functor.
-
-In fact, this double functor $\lE\maps _L\lCsp(\inta F)\to F\lCsp$ is bijective on objects and vertical 1-cells (trivially as an identity functor), and is also bijective on horizontal 1-cells and on 2-morphisms.
-Indeed, for \cref{eq:scsphor1cell}, the unique maps from the initial objects in the fibers provide no actual extra information, and similarly for 2-cells all extra data in \cref{eq:2morphismLCspintaF} is uniquely determined and \cref{eq:Grothcommutativity} holds automatically as discussed above.
-As a result, we have a double isomorphism
-\begin{equation}\label{eq:doubleiso}
-_L\lCsp(\inta F) \cong F\lCsp.
-\end{equation}
-
-Since both double categories are symmetric monoidal under the running assumptions (\cref{DC,thm:SC}), we now show that this double isomorphism is a symmetric monoidal one, namely that $\lE=(\lE_0,\lE_1)$ is a symmetric monoidal double functor as per \cref{defn:monoidal_double_functor}.
-Indeed, $\lE_0= \id_\A$ is a symmetric monoidal functor trivially.
-For $\lE_1$, given two structured cospans $M=(a,\bot_a)\to(m,x)\leftarrow(b,\bot_b)$ and $M'=(a',\bot_{a'})\to(m',x')\leftarrow(b',\bot_{b'})$ in $_L\lCsp(\inta F)$, we compute the appropriate decorated cospans
-\begin{align*}
-\lE(M)\ot\lE(M')&\;\stackrel{\cref{eq:tensordecoration}}{=}\;a+a'\xrightarrow{i+i'}m+m'\xleftarrow{o+o'}b+b' \textrm{ with }\phi_{m,m'}(x,x')\in F(m+m')
-%\one\xrightarrow{x\times x'}F(m)\times F(m')\xrightarrow{\phi_{m,m'}}F(m+m')
-\\
-\lE(M\ot M')&\;\stackrel{\cref{eq:tensorstuctured}}{=}\;\lE\Big((a+a',\bot_{a+a'})\to\underbrace{(m+m',F(\iota_m)x+F(\iota_{m'})x')}_{\cref{eq:fibrewisecoprod}}\leftarrow(b+b',\bot_{b+b'})\Big) \\
-&=a+a'\xrightarrow{i+i'}m+m'\xleftarrow{o+o'}b+b' \textrm{ with }F(\iota_m)x+F(\iota_{m'})x'\in F(m+m')
-\end{align*}
-The cospan part is equal, whereas we have an isomorphism between the decorations, $F(\iota_m)x+F(\iota_{m'})x'\cong \phi_{m,m'}(x,x')$, given in an analogous way to \cref{eq:isomorphismdiag} as follows:
-\begin{equation}\label{eq:Elaxator}
-\begin{tikzcd}[sep=.4in]
-F(m)\times F(m')\ar[r,"\phi_{m,m'}"]\ar[d,"F(\iota_m)\times F(\iota_{m'})"']
-\ar[dr,phantom,"{\stackrel[\cref{eq:pseudonaturality}]{\phi_{\iota_m,\iota_{m'}}}{\cong}}"] & F(m+m')\ar[dr]\ar[d,bend left=60, phantom,"\cong"']\ar[d,"F(\iota_m+\iota_{m'})"']  & \\
-F(m+m')\times F(m+m')\ar[r,"\phi_{m+m',m+m'}"'] & F\left((m+m')+(m+m')\right)\ar[r,"F(\nabla)"'] & F(m+m')
- \end{tikzcd}
-\end{equation}
-where the composite of the bottom two arrows is the coproduct operation in $F(m+m')$.
-We thus have constructed an isomorphism $\lE_\otimes\colon\lE(M)\otimes\lE(M') \simrightarrow \lE(M\otimes M')$ for each $M,M'$.
-
-Moreover, the monoidal unit $I_1$ for ${}_L \lCsp(\inta F)$ is mapped under $\lE_1$ to the decorated cospan given in \cref{eq:monoidalunitFCsp}, so $\lE_1$ strictly preserves the monoidal unit.
-It can be verified that with this structure, $\lE_1$ is also a symmetric monoidal functor.
-For example, the associativity axiom ensuring that the two ways to go from $\lE (M)\ot\lE(M')\ot\lE(M'')$ to $\lE(M\ot M'\ot M'')$ using the above structure isomorphisms are equal, can in fact be deduced from the more general 2-equivalence between monoidal opfibrations and pseudofunctors into $\MonCat$ already discussed in \cite[Theorem 2.7]{Shulman2008}, for the induced global monoidal structure given by $(\phi,\phi_0)$ as discussed in \cref{lem:MonGroth}.
-Moreover, the earlier associativity axiom for the double functor structure isomorphism $\lE_\odot$ can be deduced using the one for $\lE_\otimes$, by observing that \cref{eq:isomorphismdiag} factors through \cref{eq:Elaxator} as follows
-\begin{displaymath}
-\begin{tikzcd}[column sep=.4in]
-F(m)\times F(n)\ar[r,"\phi_{m,n}"]\ar[d,"F(\iota_m)\times F(\iota_{n})"']\ar[dd,bend right=80,out=-90,in=-90,"F(v_m)\times F(v_n)"',"\textstyle\cong"]
-\ar[dr,phantom,"{\stackrel{\phi_{\iota_m,\iota_n}}{\cong}}"] & F(m+n)\ar[dr]\ar[d,bend left=60, phantom,"\cong"']\ar[d,"F(\iota_m+\iota_{n})"']  & \\
-F(m+n)\times F(m+n)\ar[d,"F(\psi)\times F(\psi)"']\ar[dr,phantom,"\stackrel{\phi_{\psi,\psi}}{\cong}"]\ar[r,"\phi_{m+n,m+n}"'] & F\left((m+n)+(m+n)\right)\ar[r,"F(\nabla)"']\ar[d,"F(\psi+\psi)"']\ar[dr,phantom,"\cong"] & F(m+n)\ar[d,"F(\psi)"] \\
-F(m+_bn)\times F(m+_bn)\ar[r,"\phi_{m+_bn,m+_bn}"'] & F((m+_bn)+(m+_bn))\ar[r,"F(\nabla)"'] & F(m+_bn)
-\end{tikzcd}
-\end{displaymath}
-due to $\phi$ being a pseudonatural transformation, where $v=\psi\circ\iota$ as in \cref{eq:dcospanscomposition} and the bottom right isomorphism comes from naturality of $\nabla$.
-Notice that the bottom two-part composite isomorphism is the induced strong monoidal structure on the reindexing functor $F(\psi)$ as in \cref{eq:strongreindexing}.
-
-In a similar way, the rest of the axioms of \cref{defn:monoidal_double_functor} hold: on the cospan level they are easy to verify, whereas on the decoration level they entail nontrivial calculations based on the structures involved.
-In conclusion, the double isomorphism \cref{eq:doubleiso} is an isomorphism of symmetric monoidal double categories.
 \end{proof}
@@
 Thus, the double category $F\lCsp$ of structured cospans constructed in \cref{thm:decorated_cospans} automatically gives rise to a bicategory $F\bCsp$, and a category $F\Csp$.
-In \cref{DC} we gave conditions under which the double category $F\lCsp$ becomes symmetric monoidal.
+In \cref{thm:decorated_cospans_2} we gave conditions under which the double category $F\lCsp$ becomes symmetric monoidal.
 We would like the bicategory $F\bCsp$ and the category $F\Csp$ to become symmetric monoidal under the same conditions, and indeed this is true.
@@
 \]
-These 2-morphisms satisfy the equations \cref{eq:CompanionEq} required of a companion, involving vertical \cref{eq:verticalcompo} and horizontal \cref{eq:horizontalcompo} composition of 2-morphisms in this double category:
+These 2-morphisms satisfy the equations \cref{eq:CompanionEq} required of a companion, involving vertical and horizontal composition of 2-morphisms in this double category:
 \[
@@
 \]
-Note that the right hand side of the first equation is $U_f$, while the second equation involves the left and right unitors for $\odot$, which may be found in (\ref{eq:decunitor}): these are maps from a horizontal composite of two decorated cospans to a single decorated cospan.
+Note that the right hand side of the first equation is $U_f$, while the second equation involves the left and right unitors for $\odot$: these are maps from a horizontal composite of two decorated cospans to a single decorated cospan.
 The conjoint of $f$ is given by this horizontal 1-cell $\check{f}$, which is just the opposite of the companion above:
@@
 
-Starting from the symmetric lax monoidal pseudofunctor $F \maps (\Fin\Set, +) \to (\Cat,\times)$, \cref{DC} gives us a symmetric monoidal double category $F\lCsp$ in which:
+Starting from the symmetric lax monoidal pseudofunctor $F \maps (\Fin\Set, +) \to (\Cat,\times)$, \cref{thm:decorated_cospans_2} gives us a symmetric monoidal double category $F\lCsp$ in which:
 \begin{itemize}
@@
 Since every set gives a discrete category with that set of objects, we can reinterpret $D$ as a symmetric lax monoidal pseudofunctor $D \maps (\Fin\Set, +) \to (\Cat, \times)$ which happens to actually be a functor.
-Applying \cref{DC} we obtain a symmetric monoidal double category $D \lCsp$ where:
+Applying \cref{thm:decorated_cospans_2} we obtain a symmetric monoidal double category $D \lCsp$ where:
 \begin{itemize}
@@
 Furthermore, if $U$ preserves finite coproducts, $F$ acquires the structure of a lax monoidal pseudofunctor $F \maps (\A,+) \to (\Cat,\times)$ by the special case of the cocartesian monoidal Grothendieck construction discussed under \cref{lem:MonGroth}.
-As a result, $F$ now has enough structure to induce a double category of decorated cospans $F\lCsp$  as in \cref{DC}.
+As a result, $F$ now has enough structure to induce a double category of decorated cospans $F\lCsp$  as in \cref{thm:decorated_cospans_2}.
 Finally, it can be shown that the structured and decorated cospan double categories are isomorphic as symmetric monoidal double categories: ${}_L \lCsp(\X) \cong F\lCsp$.
@@
 
-\subsection{Fibrations}\label{sec:fibrations}
+\subsection{Fibrations}\label{subsec:fibrations}
 
@@
 \begin{tikzcd}
-A\ar[r,"M"]\ar[d,"f"']\ar[dr,phantom,"\scriptstyle\Downarrow\alpha"] & B\ar[d,"g"] \\
-C\ar[r,"N"'] & D
+A\ar[tick,r,"M"]\ar[d,"f"']\ar[dr,phantom,"\scriptstyle\Downarrow\alpha"] & B\ar[d,"g"] \\
+C\ar[tick,r,"N"'] & D
 \end{tikzcd}
@@
 
-\section{Checking a coherence law} \label{eq:proofofaxiom}
-
-Here we show a sample check of a coherence law for the proof of \cref{DC}.
-All relevant structure for decorated cospans is as described in \cref{thm:decorated_cospans,DC}. The coherence law that we check says that this diagram commutes:
-\begin{equation}\label{eq:thisdiagram}
-\begin{tikzpicture}[scale=1.5,baseline=(current bounding box.center)]
-\node (A) at (0,0) {$(M_2 \otimes N_2) \odot (M_1 \otimes N_1)$};
-\node (B) at (3,0) {$(N_2 \otimes M_2) \odot (N_1 \otimes M_1)$};
-\node (C) at (0,-.75) {$(M_2 \odot M_1) \otimes (N_2 \odot N_1)$};
-\node (D) at (3,-.75) {$(N_2 \odot N_1) \otimes (M_2 \odot M_1)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$\beta \odot \beta$} (B)
-(B) edge node[right]{$\chi$} (D)
-(A) edge node[left]{$\chi$} (C)
-(C) edge node[above]{$\beta$} (D);
-\end{tikzpicture}
-\end{equation}
-where $M_1,M_2,N_1,N_2$ are as in \cref{eq:4deccospans}, $\chi$ is as described right below therein and $\beta$ is the braiding defined as in \cref{eq:braidingFCsp1} -- although the letter $\beta$ is also used for the braiding in $\A$.
-First of all, if we only consider the underlying cospans without their decorations, we obtain the following `flattened' commutative diagram in $\A$ -- which verifies the corresponding axiom for the symmetric monoidal double category $\lCsp(\A)$:
-\[
-		\begin{tikzpicture}
-			\node (a) at (-4,0) {$a+a'$};
-			\node (b) at (1,0) {$(m_1+n_1) +_{(b+b')} (m_2+n_2)$};
-			\node (c) at (6,0) {$c+c'$};
-			\node (a2) at (-4,1) {$a'+a$};
-			\node (b2) at (1,1) {$(n_1+m_1) +_{(b'+b)} (n_2+m_2)$};
-			\node (c2) at (6,1) {$c'+c$};
-            \node (a3) at (-4,2) {$a'+a$};
-			\node (b3) at (1,2) {$(n_1 +_{b'} n_2) + (m_1 +_b m_2)$};
-			\node (c3) at (6,2) {$c'+c$};
-            \node (a5) at (-4,-1) {$a+a'$};
-			\node (b5) at (1,-1) {$(m_1+_b m_2) + (n_1+_{b'} n_2)$};
-			\node (c5) at (6,-1) {$c+c'$};
-            \node (a6) at (-4,-2) {$a'+a$};
-			\node (b6) at (1,-2) {$(n_1 +_{b'} n_2) + (m_1 +_b m_2)$};
-			\node (c6) at (6,-2) {$c'+c$};
-			\path[->,font=\scriptsize,>=angle 90]
-			(a) edge node[above]{$$} (b)
-			(c) edge node[above]{$$} (b)
-            (a2) edge node[above]{$$} (b2)
-			(c2) edge node[above]{$$} (b2)
-            (a) edge node[left]{$\beta$} (a2)
-            (b) edge node[left]{$\beta +_\beta \beta$} (b2)
-%(b) edge node[right]{$\tau_1$} (b2)
-			(c) edge node[right]{$\beta$} (c2)
-            (a3) edge node[above]{$$} (b3)
-			(c3) edge node[above]{$$} (b3)
-            (a2) edge node[left]{$1$} (a3)
-            (b2) edge node[left]{$\hat{\chi}$} (b3)
-%(b2) edge node[right]{$\tau_2$} (b3)
-			(c2) edge node[right]{$1$} (c3)
-            (a5) edge node[above]{$$} (b5)
-			(c5) edge node[above]{$$} (b5)
-            (a) edge node[left]{$1$} (a5)
-            (b) edge node[left]{$\hat{\chi}$} (b5)
-%(b) edge node[right]{$\tau_4$} (b5)
-			(c) edge node[right]{$1$} (c5)
-            (a6) edge node[above]{$$} (b6)
-			(c6) edge node[above]{$$} (b6)
-            (a5) edge node[left]{$\beta$} (a6)
-            (b5) edge node[left]{$\beta$} (b6)
- %(b5) edge node[right]{$\tau_5$} (b6)
-			(c5) edge node[right]{$\beta$} (c6);
-		\end{tikzpicture}
-	\]
-The top and the bottom cospans coincide, and $\hat{\chi}$ is the canonical isomorphism by the universal property of colimits
-%globular 2-morphism interchanging the tensor product and horizontal composition of the symmetric monoidal double category $\lCsp(\A)$,
-and the inwards pointing morphisms are natural maps from the each cospan's feet to its apex.
-It follows that $\beta\hat{\chi}=\hat{\chi}(\beta+_\beta\beta)$ as the unique map between the involved colimits.
-
-Regarding decorations, each of the above four maps of cospans has an associated map, which we label with $\tau_i$ for $i=1,2,3,4$, between the corresponding decorations:
-\[
-		\begin{tikzpicture}
-%			\node (a) at (-4,0) {$a+a'$};
-			\node (b) at (1,0) {$(m_1+n_1) +_{(b+b')} (m_2+n_2)$};
-			\node (c) at (8,0) {$ (x_1 \otimes y_1) \odot (x_2 \otimes y_2)  \in F((m_1+n_1)+_{b+b'}(m_2+n_2))$};
-%			\node (a2) at (-4,1) {$a'+a$};
-			\node (b2) at (1,1) {$(n_1+m_1) +_{(b'+b)} (n_2+m_2)$};
-			\node (c2) at (8,1) {$(y_1\otimes x_1) \odot (y_2 \otimes x_2) \in F((n_1+m_1)+_{b'+b}(n_2+m_2))$};
-%                            \node (a3) at (-4,2) {$a'+a$};
-			\node (b3) at (1,2) {$(n_1 +_{b'} n_2) + (m_1 +_b m_2)$};
-			\node (c3) at (8,2) {$(y_1 \odot y_2) \otimes (x_1 \odot x_2) \in F((n_1+_{b'} n_2)+(m_1+_b m_2))$};
-%                                \node (a5) at (-4,-1) {$a+a'$};
-			\node (b5) at (1,-1) {$(m_1+_b m_2) + (n_1+_{b'} n_2)$};
-			\node (c5) at (8,-1) {$(x_1 \odot x_2) \otimes (y_1 \odot y_2) \in F((m_1+_b m_2)+(n_1+_{b'} n_2))$};
-%                                \node (a6) at (-4,-2) {$a'+a$};
-			\node (b6) at (1,-2) {$(n_1 +_{b'} n_2) + (m_1 +_b m_2)$};
-			\node (c6) at (8,-2) {$(y_1 \odot y_2) \otimes (x_1 \odot x_2) \in F((n_1+_{b'} n_2)+(m_1+_b m_2))$};
-			\path[->,font=\scriptsize,>=angle 90]
-%			(a) edge node[above]{$$} (b)
-%			(c) edge node[above]{$$} (b)
-%                                (a2) edge node[above]{$$} (b2)
-%			(c2) edge node[above]{$$} (b2)
-%                                (a) edge node[left]{$\beta$} (a2)
-                                (b) edge node[left]{$\beta +_\beta \beta$} (b2)
-(b) edge node[right]{$\tau_1$} (b2)
-%			(c) edge node[right]{$\beta$} (c2)
-%                                (a3) edge node[above]{$$} (b3)
-%			(c3) edge node[above]{$$} (b3)
-%                               (a2) edge node[above]{$$} (a3)
-                                (b2) edge node[left]{$\hat{\chi}$} (b3)
-(b2) edge node[right]{$\tau_2$} (b3)
-%			(c2) edge node[above]{$$} (c3)
-%                                (a5) edge node[above]{$$} (b5)
-%			(c5) edge node[above]{$$} (b5)
-%                                (a) edge node[above]{$$} (a5)
-                                (b) edge node[left]{$\hat{\chi}$} (b5)
-(b) edge node[right]{$\tau_3$} (b5)
-%			(c) edge node[above]{$$} (c5)
-%                               (a6) edge node[above]{$$} (b6)
-%			(c6) edge node[above]{$$} (b6)
-%                                (a5) edge node[left]{$\beta$} (a6)
-                                (b5) edge node[left]{$\beta$} (b6)
- (b5) edge node[right]{$\tau_4$} (b6);
-%			(c5) edge node[left]{$\beta$} (c6);
-		\end{tikzpicture}
-	\]
-and are explicitly appropriate isomorphisms of the form:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$\tau_1 \maps F(\beta +_\beta \beta)((x_1 \otimes y_1)\odot(x_2\otimes y_2)) \to (y_1 \otimes x_1) \odot (y_2 \otimes x_2)$};
-\node (B) at (0,-.5) {$\tau_2 \maps F(\hat{\chi})((y_1 \otimes x_1)\odot(y_2 \otimes x_2)) \to (y_1 \odot y_2) \otimes (x_1 \odot x_2)$};
-\node (C) at (0,-1) {$\tau_3 \maps F(\hat{\chi})((x_1 \otimes y_1)\odot(x_2 \otimes y_2)) \to (x_1 \odot x_2) \otimes (y_1 \odot y_2)$};
-\node (D) at (0,-1.5) {$\tau_4 \maps F(\beta)((x_1\odot x_2)\otimes(y_1\odot y_2)) \to (y_1\odot y_2) \otimes (x_1\odot x_2)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge[color=white] node[above]{$$} (A);
-%(B) edge node[right]{$\chi$} (D)
-%(A) edge node[left]{$\chi$} (C)
-%(C) edge node[above]{$\beta \odot \beta$} (D);
-\end{tikzpicture}
-\]
-Firstly, performing the (vertical) composition of $\chi$ and $\beta$ of $\cref{eq:thisdiagram}$ gives the composite decoration $\tau_4\tau_3$ computed by the formula \cref{eq:tauofverticalcomposite} to be
-\begin{displaymath}
-\scalebox{.8}{$F(\beta\hat{\chi})((x_1 \otimes y_1)\odot(x_2 \otimes y_2))\cong F(\beta)(F\hat{\chi})((x_1 \otimes y_1)\odot(x_2 \otimes y_2))\xrightarrow{F(\beta)(\tau_3)}F(\beta)((x_1\odot x_2) \otimes (y_1\odot y_2))\xrightarrow{\tau_4}(y_1 \odot y_2) \otimes (x_1 \odot x_2)$}
-\end{displaymath}
-Using the formulas for the involved decorations \cref{eq:bigeq1,eq:bigeq2}, as well as the decoration morphisms of $\chi$ \cref{eq:interchangedeco} and $\beta$ \cref{eq:decobraiding}, we form:
-\[
-\begin{tikzpicture}[scale=1.6]
-%\node (A) at (3.85,0) {$\scriptstyle{\cong}$};
-%\node (A') at (3.85,-1) {$\scriptstyle{\cong}$};
-\node () at (12,-1) {$\scriptstyle\cong$};
-\node (D) at (3,-0.5) {$\scriptstyle{\one}$};
-\node (E) at (6.75,0.5) {$\scriptstyle{F(m_1 + n_1) \times F(m_2+n_2)}$};
-\node () at (10.25,-1) {$\scriptstyle\stackrel[\cref{eq:braidedpseudofun}]{u}{\cong}$};
-\node () at (7.875,0) {$\scriptstyle\stackrel[\cref{eq:interchangedeco}]{}{\cong}$};
-\node (E') at (6.75,-0.5) {$\scriptstyle{F(m_1+m_2) \times F(n_1+n_2)}$};
-\node (B) at (9,0.5) {$\scriptstyle{F((m_1+n_1)+(m_2+n_2))}$};
-\node (B') at (9,-0.5) {$\scriptstyle{F(m_1+_b m_2)\times F(n_1+_{b'}n_2)}$};
-\node (C) at (11.5,0.5) {$\scriptstyle{F((m_1+n_1)+_{b+b'}(m_2+n_2))}$};
-\node (C') at (11.5,-0.5) {$\scriptstyle{F((m_1+_b m_2)+ (n_1+_{b'} n_2))}$};
-\node (G) at (4.25,0.5) {$\scriptstyle{F(m_1) \times F(n_1) \times F(m_2) \times F(n_2)}$};
-\node (G') at (4.25,-0.5) {$\scriptstyle{F(m_1) \times F(m_2) \times F(n_1) \times F(n_2)}$};
-\node (G'') at (4.25,-1.5) {$\scriptstyle{F(n_1) \times F(n_2) \times F(m_1) \times F(m_2)}$};
-\node (E'') at (6.75,-1.5) {$\scriptstyle{F(n_1+n_2) \times F(m_1+m_2)}$};
-\node (B'') at (9,-1.5) {$\scriptstyle{F(n_1+_{b'}n_2) \times F(m_1+_b m_2)}$};
-\node (C'') at (11.5,-1.5) {$\scriptstyle{F((n_1+_{b'}n_2)+(m_1+_b m_2))}$};
-\node (X) at (3.4,0.2) {$\scriptscriptstyle{x_1 \times y_1 \times x_2 \times y_2}$};
-\node (X') at (3.4,-0.35) {$\scriptscriptstyle{x_1 \times x_2 \times y_1 \times y_2}$};
-\node (X'') at (3.4,-1.2) {$\scriptscriptstyle{y_1 \times y_2 \times x_1 \times x_2}$};
-\path[->,font=\scriptsize,>=angle 90]
-(B') edge node [fill=white] {$\beta$} (B'')
-(E) edge node [above] {$\phi_{m_1+n_1,m_2+n_2}$} (B)
-(E'') edge node [below] {$F(\psi)\times F(\psi)$} (B'')
-(E') edge node [above] {$F(\psi)\times F(\psi)$} (B')
-(B) edge node [above] {$F(\psi)$} (C)
-(B'') edge node [below] {$\phi_{n_1+_{b'}n_2,m_1+_b m_2}$} (C'')
-(B') edge node [above] {$\phi_{m_1+_b m_2,n_1+_{b'}n_2}$} (C')
-(C) edge node [fill=white] {$F(\hat{\chi})$} (C')
-(C') edge node [fill=white] {$F(\beta)$} (C'')
-(G) edge node [above] {$\phi_{m_1,n_1} {\times} \phi_{m_2,n_2}$} (E)
-(G'') edge node [below] {$\phi_{n_1,n_2} {\times} \phi_{m_1,m_2}$} (E'')
-(G') edge node [above] {$\phi_{m_1,m_2} \times \phi_{n_1,n_2}$} (E')
-(G) edge node [fill=white] {$1 \times \beta \times 1$} (G')
-(G') edge node [fill=white] {$\beta$} (G'')
-(D) edge[out=90,in=180] node [left,above] {$$} (G)
-(D) edge[out=270,in=180] node [left,above] {$$} (G'')
-(D) edge node [below] {$$} (G')
-(C) edge[bend left=80] node [fill=white] {$F(\beta\hat{\chi})$} (C'')
-;
-\end{tikzpicture}
-\]
-For the other (vertical) composition of \cref{eq:thisdiagram}, that of $\beta\odot\beta$ followed by $\chi$, the composite decoration $\tau_2\tau_1$ is
-\begin{displaymath}
-\scalebox{.8}{$F(\hat{\chi}(\beta +_\beta \beta))( (x_1 \otimes y_1)\odot (x_2 \otimes y_2))\cong F(\hat{\chi})F(\beta +_\beta \beta)( (x_1 \otimes y_1)\odot (x_2 \otimes y_2)) \xrightarrow{F(\hat{\chi})(\tau_1)}F(\hat{\chi})(y_1\otimes x_1)\odot(y_2\otimes x_2)\xrightarrow{\tau_2}(y_1 \odot y_2) \otimes (x_1 \odot x_2)$}
-\end{displaymath}
-Once again, using the tensor and composite formulas for decorations, as well the horizontal composite formulas \cref{eq:decohorizontalcompo}
-for $\beta\odot\beta$, the above is explicitly given by the pasted isomorphism:
-\[
-\begin{tikzpicture}[scale=1.6]
-%\node (A) at (3.85,0) {$\scriptstyle{\cong}$};
-%\node (A') at (3.85,-1) {$\scriptstyle{\cong}$};
-\node (D) at (3,-0.5) {$\scriptstyle{\one}$};
-\node (E) at (6.75,0.5) {$\scriptstyle{F(m_1 + n_1) \times F(m_2+n_2)}$};
-\node () at (5.5,0) {$\scriptstyle\stackrel[\cref{eq:braidedpseudofun}]{u\times u}{\cong}$};
-\node () at (7.875,0) {$\scriptstyle\stackrel[\cref{eq:pseudonaturality}]{\phi_{\beta,\beta}}{\cong}$};
-\node () at (10.25,0) {$\scriptstyle{\cong}$};
-\node () at (7.875,-1) {$\scriptstyle\stackrel[\cref{eq:interchangedeco}]{}{\cong}$};
-\node () at (12,-1) {$\scriptstyle\cong$};
-\node (E') at (6.75,-0.5) {$\scriptstyle{F(n_1+m_1) \times F(n_2+m_2)}$};
-\node (B) at (9,0.5) {$\scriptstyle{F((m_1+n_1)+(m_2+n_2))}$};
-\node (B') at (9,-0.5) {$\scriptstyle{F((n_1+m_1)+(n_2+m_2))}$};
-\node (C) at (11.5,0.5) {$\scriptstyle{F((m_1+n_1)+_{b+b'}(m_2+n_2))}$};
-\node (C') at (11.5,-0.5) {$\scriptstyle{F((n_1+m_1)+_{b'+b}(n_2+m_2))}$};
-\node (G) at (4.25,0.5) {$\scriptstyle{F(m_1) \times F(n_1) \times F(m_2) \times F(n_2)}$};
-\node (G') at (4.25,-0.5) {$\scriptstyle{F(n_1) \times F(m_1) \times F(n_2) \times F(m_2)}$};
-\node (G'') at (4.25,-1.5) {$\scriptstyle{F(n_1) \times F(n_2) \times F(m_1) \times F(m_2)}$};
-\node (E'') at (6.75,-1.5) {$\scriptstyle{F(n_1+n_2) \times F(m_1+m_2)}$};
-\node (B'') at (9,-1.5) {$\scriptstyle{F(n_1+_{b'}n_2)\times F(m_1+_b m_2)}$};
-\node (C'') at (11.5,-1.5) {$\scriptstyle{F((n_1+_{b'}n_2)+(m_1+_b m_2))}$};
-\node (X) at (3.4,0.2) {$\scriptscriptstyle{x_1 \times y_1 \times x_2 \times y_2}$};
-\node (X') at (3.4,-0.35) {$\scriptscriptstyle{y_1 \times x_1 \times y_2 \times x_2}$};
-\node (X'') at (3.4,-1.2) {$\scriptscriptstyle{y_1 \times y_2 \times x_1 \times x_2}$};
-\path[->,font=\scriptsize,>=angle 90]
-(B) edge node [fill=white] {$F(\beta+\beta)$} (B')
-(E) edge node [fill=white] {$F(\beta) \times F(\beta)$} (E')
-(E) edge node [above] {$\phi_{m_1+n_1,m_2+n_2}$} (B)
-(E'') edge node [below] {$F(\psi)\times F(\psi)$} (B'')
-(E') edge node [above] {$\phi_{n_1+m_1,n_2+m_2}$} (B')
-(B) edge node [above] {$F(\psi)$} (C)
-(B'') edge node [below] {$\phi_{n_1+_{b'}n_2,m_1+_{b}m_2}$} (C'')
-(B') edge node [above] {$F(\psi)$} (C')
-(C) edge node [fill=white] {$F(\beta +_\beta \beta)$} (C')
-(C') edge node [fill=white] {$F(\hat{\chi})$} (C'')
-(G) edge node [above] {$\phi_{m_1,n_1} {\times} \phi_{m_2,n_2}$} (E)
-(G'') edge node [below] {$\phi_{n_1,n_2} {\times} \phi_{m_1,m_2}$} (E'')
-(G') edge node [above] {$\phi_{n_1,m_1} \times \phi_{n_2,m_2}$} (E')
-(G) edge node [fill=white] {$\beta \times \beta$} (G')
-(G') edge node [fill=white] {$1 \times \beta \times 1$} (G'')
-(D) edge[out=90,in=180] node [left,above] {$$} (G)
-(D) edge[out=270,in=180] node [left,above] {$$} (G'')
-(D) edge node [below] {$$} (G')
-(C) edge[bend left=80] node [fill=white] {$F(\hat{\chi}(\beta+_\beta\beta))$} (C'')
-;
-\end{tikzpicture}
-\]
-In order to verify that these two pasted isomorphisms are equal, we first of all need to expand the isomorphism \cref{eq:interchangedeco}, whose left half part is explicitly written as follows (also found in \cite[Page 125]{DS}):
-\begin{equation}\label{eq:thetaa}
-\scalebox{.8}{
-\begin{tikzcd}[column sep=.05in,ampersand replacement=\&]
-F(m_1){\times} F(n_1){\times} F(m_2){\times} F(n_2)\ar[ddr,phantom,bend right,"{\scriptstyle\stackrel[\cref{eq:braidedpseudofun}]{1\times u\times1}{\cong}}"]\ar[dr,"1\times\phi\times1"]\ar[rr,"\phi\times\phi"]\ar[ddd,"1\times\beta\times1"'] \&\& F(m_1{+}n_1){\times} F(m_2{+}n_2)\ar[d,phantom,"\scriptstyle{\cong}"]\ar[ddd,phantom,"{\scriptstyle\stackrel[\cref{eq:pseudonaturality}]{1\times\phi_{\beta,1}}{\cong}}"]\ar[rr,"\phi"] \&\& F(m_1{+}n_1{+}m_2{+}n_2)\ar[ddd,"F(1+\beta+1)"]\ar[ddl,bend left,phantom,"{\scriptstyle\stackrel[\cref{eq:pseudonaturality}]{\phi_{1,\beta+1}}{\cong}}"] \\
-\& F(m_1){\times} F(n_1 {+} m_2){\times} F(n_2)\ar[rr,"{1\times\phi}"]\ar[d,"{1\times F(\beta)\times1}"'] \&\phantom{A}\& F(m_1){\times} F(n_1 {+} m_2 {+} n_2)\ar[d,"{1\times F(\beta+1)}"]\ar[ur,"\phi"] \& \\
-\& F(m_1){\times} F(m_2{+}n_1){\times} F(n_2)\ar[rr,"1\times\phi"'] \&\phantom{A}\ar[d,phantom,"\scriptstyle\cong"]\& F(m_1){\times} F(m_2{+}n_1{+}n_2)\ar[dr,"\phi"'] \& \\
-F(m_1){\times} F(m_2){\times} F(n_1){\times} F(n_2)\ar[ur,"1\times\phi\times1"']\ar[rr,"\phi\times\phi"'] \&\& F(m_1{+}m_2){\times} F(n_1{+}n_2)\ar[rr,"\phi"'] \&\& F(m_1{+}m_2{+}n_1{+}n_2)
-\end{tikzcd}}
-\end{equation}
-where the unnamed isomorphisms are appropriate composites of the pseudoassociativity of $F$ \cref{eq:omega}.
-The fact that the two pasted 2-isomorphisms are equal now follows from lengthy pasted diagram calculations using the axioms of a sylleptic lax monoidal pseudofunctor \cite[Definition 16]{DS}.
-
 \begin{thebibliography}{100}

### 2021-03-15 cospans_new.tex
started new version: cospans_new.tex

@@
 
-{\bf NEW PROOF.}
+{\bf NEW PROOF HERE.}  We apply \cref{lem:shulman} to ....
 \end{proof}
@@
 \begin{proof}[Proof of \cref{thm:equiv}]
-Recall from \cref{thm:decorated_cospans} that the double category of decorated cospans $F\lCsp$ has objects and vertical 1-morphisms as in $\A$, while horizontal 1-cells are cospans $\cspn{a}{m}{b}{}{}$ in $\A$ decorated by an $x\in F(m)$ and 2-morphisms are maps of cospans $k\maps m\to m'$ together with $\tau\maps(Fk)(x)\to x'$ in $F(m')$.
-
-Since the corresponding pseudofunctor $F \maps \A \to \SMC$ factors through $\Rex$, 
+Since we are assuming the pseudofunctor $F \maps \A \to \SMC$ factors through $\Rex$, 
 \cref{cor:fcocMonGroth} implies that the Gro\-the\-ndieck construction gives rise to a category $\inta F$ with finite colimits, and we can choose these in such a way that the corresponding opfibration $U \maps \inta F \to \A$ strictly preserves them.
@@
 As a left adjoint, this induced $L$ preserves all colimits that exist between the categories $\A$ and $\inta F$, which have finite colimits, so we can construct the double category of structured cospans $_L\lCsp(\inta F)$ of \cref{thm:SC}.
+
+{\textbf NEW PROOF HERE.}
 \end{proof}

### 2021-03-22 cospans_new.tex
added Shulman's name for "Beck-Chevalley"
added stuff about new proofs

@@
 If $\theta$ is a natural isomorphism whenever the original square in $\A$ was
-a pushout, we say $\Phi$ is \define{Beck--Chevalley}.
+a pushout, we say $\Phi$ is \define{Beck--Chevalley}.  (Shulman says `strongly co-Beck--Chevalley'.)
 
@@
 
-\begin{proof}[Proof of \cref{thm:decorated_cospans_1}] We apply \cref{lem:shulman} to ....
+\begin{proof}[Proof of \cref{thm:decorated_cospans_1}] We apply \cref{lem:shulman} to $A/U \to A$: why is this a fibration, a cofibration, and Beck--Chevalley?
 \end{proof}
 
-\begin{proof}[Proof of \cref{thm:decorated_cospans_2}] We apply \cref{lem:shulman} to ....
+\begin{proof}[Proof of \cref{thm:decorated_cospans_2}] We apply \cref{lem:shulman} to $A/U \to A$: why is this a symmetric monoidal bifibration?
 \end{proof}
@@
 
-{\bf NEW PROOF HERE.}  We apply \cref{lem:shulman} to ....
+{\bf NEW PROOF HERE.}  We apply \cref{lem:shulman} to $L/X \to A$.   Why is this a fibration, cofibration, Beck--Chevalley and symmetric monoidal?
 \end{proof}

### 2021-03-28 cospans_new.tex
Added a proof of Theorem 2.1

@@
 
-\begin{proof}[Proof of \cref{thm:decorated_cospans_1}] We apply \cref{lem:shulman} to $A/U \to A$: why is this a fibration, a cofibration, and Beck--Chevalley?
+\begin{proof}[Proof of \cref{thm:decorated_cospans_1}] We apply \cref{lem:shulman} to the Beck-Chevalley monoidal bifibration $U_1 \colon (\A/U) \to \A$ which we now define.
+Let $(\A/U)$ be the comma category in which:
+\begin{enumerate}
+\item{an object is a triple $(a,x,a \xrightarrow{i} U(x))$, and}
+\item{a morphism from $(a,x,a \xrightarrow{i} U(x))$ to $(a',x',a' \xrightarrow{i'} U(x'))$ is a pair of morphisms $f \colon a \to a'$ and $\alpha \colon x \to x'$ such that the following square commutes:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$a$};
+\node (B) at (1,0) {$a'$};
+\node (C) at (0,-1) {$U(x)$};
+\node (D) at (1,-1) {$U(x')$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$f$} (B)
+(A) edge node[left]{$i$} (C)
+(B) edge node[right]{$i'$} (D)
+(C) edge node[above]{$U(\alpha)$} (D);
+\end{tikzpicture}
+\]}
+\end{enumerate}
+The functor $U_1$ is defined on objects by $U_1(a,x,a \xrightarrow{i} U(x))=a$ and on morphisms by $U_1(f,\alpha)=f$.
+We have a monoidal structure on the comma category $(\A/U)$ where the tensor product of two objects $(a_1,x_1,a_1 \xrightarrow{i_1} U(x_1))$ and $(a_2,x_2,a_2 \xrightarrow{i_2} U(x_2))$ is given by $$(a_1,x_1,a_1 \xrightarrow{i_1} U(x_1)) \otimes (a_2,x_2,a_2 \xrightarrow{i_2} U(x_2)) = (a_1+a_2,x_1+x_2,a_1+a_2 \xrightarrow{i_1+i_2} U(x_1+x_2))$$making use of the natural isomorphism $U(x_1)+U(x_2) \cong U(x_1+x_2)$ which we omit in the above definition.
+The monoidal unit is given by $(0_\A,0_\X,0_\A \to U(0_\X))$.
+It is easy to see that the functor $U_1$ can be made into a strict monoidal functor using this tensor product.
+
+The functor $U_1$ is a fibration where given a morphism $f \colon a \to b$ in $\A$ with $(b,y,b \xrightarrow{i} U(y))$ over $b$ in $\int F$, the cartesian lifting of $f$ is given by $$(f,\id) \colon (a,y,a \xrightarrow{i \circ f} U(y)) \to (b,y,b \xrightarrow{i} U(y)).$$Denoting the cartesian lifting of a morphism $f$ by $\textnormal{cart}(f)$, the tensor product of $(\A/U)$ strictly preserves cartesian liftings in the sense that $\textnormal{cart}(f_1) \otimes \textnormal{cart}(f_2)=\textnormal{cart}(f_1+f_2)$.
+
+The functor $U_1$ is also an opfibration where given a morphism $f \colon a \to b$ with $(a,x,a \xrightarrow{i} U(x))$ over $a$, the cocartesian lifting of $f$ is given by $$(f,\theta) \colon (a,x,a \to U(x)) \to (b,z,b \xrightarrow{\phi} U(z))$$where $\theta$ and $\phi$ arise from the following pushout square in $\A$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$a$};
+\node (B) at (1.5,0) {$b$};
+\node (C) at (0,-1) {$U(x)$};
+\node (D) at (1.5,-1) {$U(x)+_a b$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$f$} (B)
+(A) edge node[left]{$i$} (C)
+(B) edge [dashed] node[right]{$\phi$} (D)
+(C) edge [dashed] node[above]{$\theta$} (D);
+\end{tikzpicture}
+\]
+and the object $z$ arises from the cocartesian lifting of $\theta$ through $U$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$a$};
+\node (B) at (2.5,0) {$c$};
+\node (C) at (1.5,1) {$b$};
+\node (D) at (0,-2) {$U(x)$};
+\node (E) at (2.5,-2) {$U(y)$};
+\node (F) at (1.5,-1) {$U(z) = U(x)+_a b$};
+\path[->,font=\scriptsize,>=angle 90]
+(D) edge node [above] {$\theta$} (F)
+(F) edge [dashed] node [left] {$\exists ! \psi$} (E)
+(D) edge node [above] {$U(g')$} (E)
+(A) edge node [left] {$i$} (D)
+(C) edge [dashed] node [right,near end] {$\phi$} (F)
+(B) edge node {$$} (E)
+(A) edge node[above]{$f'$} (B)
+(C) edge node [right] {$p$} (B)
+(A) edge node[left]{$f$} (C);
+%(B) edge [dashed] node[right]{$$} (D)
+%(C) edge [dashed] node[above]{$$} (D);
+\end{tikzpicture}
+\]
+Denoting the cocartesian lifting of a morphism $f$ by $\textnormal{cocart}(f)$, we have that $\textnormal{cocart}(f_1) \otimes \textnormal{cocart}(f_2) \cong \textnormal{cocart}(f_1+f_2)$ by the universal map between two colimits of the same diagram: $$(U(x_1)+_{a_1}b_1)+(U(x_2)+_{a_2}b_2) \cong U(x_1+x_2)+_{a_1+a_2}(b_1+b_2).$$
+
+Lastly, the monoidal bifibration $U_1$ satisfies the Beck-Chevalley condition. Given a pushout square in $\A$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$a$};
+\node (B) at (1,0) {$b$};
+\node (C) at (0,-1) {$c$};
+\node (D) at (1,-1) {$d$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$h$} (B)
+(A) edge node[left]{$k$} (C)
+(B) edge node[right]{$g$} (D)
+(C) edge node[above]{$f$} (D);
+\end{tikzpicture}
+\]
+one can show that the following square commutes up to a natural isomorphism:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$(\A/U)_a$};
+\node (B) at (2,0) {$(\A/U)_b$};
+\node (C) at (0,-1) {$(\A/U)_c$};
+\node (D) at (2,-1) {$(\A/U)_d$};
+\node (E) at (1,-0.5) {$\Searrow$};
+\path[->,font=\scriptsize,>=angle 90]
+(B) edge node[above]{$h^*$} (A)
+(A) edge node[left]{$k_!$} (C)
+(B) edge node[right]{$g_!$} (D)
+(D) edge node[above]{$f^*$} (C);
+\end{tikzpicture}
+\]
+Let $(b,x,b \xrightarrow{i} U(x))$ be an object of $(\A/U)_b$.
+Going right, we precompose with $h \colon a \to b$ to obtain the object $(a,x,a \xrightarrow{i \circ h} U(x))$ in $(\A/U)_a$.
+Then, going down, we pushforward along $k \colon a \to c$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$a$};
+\node (B) at (2,0) {$U(x)$};
+\node (C) at (0,-1) {$c$};
+\node (D) at (2,-1) {$c+_{a}U(x)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i \circ h$} (B)
+(A) edge node[left]{$k$} (C)
+(B) edge node[right]{$$} (D)
+(C) edge node[above]{$\psi$} (D);
+\end{tikzpicture}
+\]
+to obtain the object $(c,z,c \to U(z))$ of $(\A/U)_c$ where $z \in \int F$ such that $U(z)=c+_a U(x)$.
+In particular, $z=L(c)+_{L(a)}x$ and as $U$ preserves finite colimits and $UL=1_\A$, we have that $$U(z)=U(L(c)+_{L(a)}x)=U(L(c))+_{U(L(a))}U(x)=c+_a U(x).$$ For the other route, first going down, we pushforward the object $(b,x,b \xrightarrow{i} U(x))$ along $g \colon b \to d$ by taking the following pushout:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$b$};
+\node (B) at (2,0) {$U(x)$};
+\node (C) at (0,-1) {$d$};
+\node (D) at (2,-1) {$d+_{b}U(x)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i$} (B)
+(A) edge node[left]{$g$} (C)
+(B) edge node[right]{$$} (D)
+(C) edge node[above]{$\theta$} (D);
+\end{tikzpicture}
+\]
+which yields the object $(d,z',d \to U(z'))$ of $(\A/U)_d$ where $z' \in \int F$ such that $U(z')=d+_b U(x)$.
+In particular, $z'$ is given by $z'=L(d)+_{L(b)}x$.
+We then precompose with $f \colon c \to d$ to obtain the object $(c,z',c \to U(z'))$ of $(\A/U)_c$.
+
+Now we seek a natural isomorphism between the two objects $(c,z,c \to c+_a U(x))$ and $(c,z',c \to d+_b U(x))$ in $(\A/U)_c$.
+It suffices to obtain a natural isomorphism between the two objects $z=L(c)+_{L(a)} x$ and $z'=L(d)+_{L(b)} x$ in $\X$.
+The following two squares are pushouts:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$L(a)$};
+\node (B) at (2,0) {$x$};
+\node (C) at (0,-1) {$L(c)$};
+\node (D) at (2,-1) {$L(c)+_{L(a)}x$};
+\node (A') at (3,0) {$L(b)$};
+\node (B') at (5,0) {$x$};
+\node (C') at (3,-1) {$L(d)$};
+\node (D') at (5,-1) {$L(d)+_{L(b)}x$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$I \circ L(h)$} (B)
+(A) edge node[left]{$L(k)$} (C)
+(B) edge node[right]{$$} (D)
+(C) edge node[above]{$\psi$} (D)
+(A') edge node[above]{$I$} (B')
+(A') edge node[left]{$L(g)$} (C')
+(B') edge node[right]{$$} (D')
+(C') edge node[above]{$\theta$} (D');
+\end{tikzpicture}
+\]
+the left of which exhibits $L(c)+_{L(a)}x$ as a colimit of the span $$L(c) \xleftarrow{L(k)} L(a) \xrightarrow{I \circ L(h)} x$$in $\X$.
+As $L$ preserves pushouts, the following square is also a pushout:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$L(a)$};
+\node (B) at (1,0) {$L(b)$};
+\node (C) at (0,-1) {$L(c)$};
+\node (D) at (1,-1) {$L(d)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$L(h)$} (B)
+(A) edge node[left]{$L(k)$} (C)
+(B) edge node[right]{$L(g)$} (D)
+(C) edge node[above]{$L(f)$} (D);
+\end{tikzpicture}
+\]
+which we may then paste to the left of the above pushout square on the right to obtain another pushout square:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$L(b)$};
+\node (B) at (2,0) {$x$};
+\node (C) at (0,-1) {$L(d)$};
+\node (D) at (2,-1) {$L(d)+_{L(b)}x$};
+\node (E) at (-1,0) {$L(a)$};
+\node (F) at (-1,-1) {$L(c)$};
+\path[->,font=\scriptsize,>=angle 90]
+(E) edge node [left] {$L(k)$} (F)
+(E) edge node [above] {$L(h)$} (A)
+(F) edge node [above] {$L(f)$} (C)
+(A) edge node[above]{$I$} (B)
+(A) edge node[left]{$L(g)$} (C)
+(B) edge node[right]{$$} (D)
+(C) edge node[above]{$\theta$} (D);
+\end{tikzpicture}
+\]
+which exhibits $L(d)+_{L(b)} x$ also as a colimit of the same span in $\X$, and hence the desired natural isomorphism between our two objects of $(\A/U)_c$ showing that $U_1$ satisfies the Beck-Chevalley condition.
 \end{proof}

### 2021-03-29 cospans_new.tex
a few small improvements to Kenny's new (3/28/2021) version

@@
 % in LaTeX
-% 2021/3/15 - attempt at new version
+% 2021/3/29 - Kenny's changes
 
@@
 The functor $U_1$ is defined on objects by $U_1(a,x,a \xrightarrow{i} U(x))=a$ and on morphisms by $U_1(f,\alpha)=f$.
-We have a monoidal structure on the comma category $(\A/U)$ where the tensor product of two objects $(a_1,x_1,a_1 \xrightarrow{i_1} U(x_1))$ and $(a_2,x_2,a_2 \xrightarrow{i_2} U(x_2))$ is given by $$(a_1,x_1,a_1 \xrightarrow{i_1} U(x_1)) \otimes (a_2,x_2,a_2 \xrightarrow{i_2} U(x_2)) = (a_1+a_2,x_1+x_2,a_1+a_2 \xrightarrow{i_1+i_2} U(x_1+x_2))$$making use of the natural isomorphism $U(x_1)+U(x_2) \cong U(x_1+x_2)$ which we omit in the above definition.
+We have a monoidal structure on the comma category $(\A/U)$ where the tensor product of two objects $(a_1,x_1,a_1 \xrightarrow{i_1} U(x_1))$ and $(a_2,x_2,a_2 \xrightarrow{i_2} U(x_2))$ is given by
+ $$(a_1,x_1,a_1 \xrightarrow{i_1} U(x_1)) \otimes (a_2,x_2,a_2 \xrightarrow{i_2} U(x_2)) = (a_1+a_2,x_1+x_2,a_1+a_2 \xrightarrow{i_1+i_2} U(x_1+x_2))$$
+where the natural isomorphism $U(x_1)+U(x_2) \cong U(x_1+x_2)$ is implicit
+ in the above composite, for reasons of space.
 The monoidal unit is given by $(0_\A,0_\X,0_\A \to U(0_\X))$.

### 2021-04-05 cospans_new.tex
a few extra changes after Kenny's 3/28/2021 version
Trying to reapply Dr. Baez's change
Added drafts of proofs Theorems 3.1 and 3.2

@@
 % in LaTeX
-% 2021/3/29 - Kenny's changes
+% 2021/3/29 - Kenny's changes and a few more
 
@@
 The functor $U_1$ is defined on objects by $U_1(a,x,a \xrightarrow{i} U(x))=a$ and on morphisms by $U_1(f,\alpha)=f$.
-We have a monoidal structure on the comma category $(\A/U)$ where the tensor product of two objects $(a_1,x_1,a_1 \xrightarrow{i_1} U(x_1))$ and $(a_2,x_2,a_2 \xrightarrow{i_2} U(x_2))$ is given by
- $$(a_1,x_1,a_1 \xrightarrow{i_1} U(x_1)) \otimes (a_2,x_2,a_2 \xrightarrow{i_2} U(x_2)) = (a_1+a_2,x_1+x_2,a_1+a_2 \xrightarrow{i_1+i_2} U(x_1+x_2))$$
-where the natural isomorphism $U(x_1)+U(x_2) \cong U(x_1+x_2)$ is implicit
- in the above composite, for reasons of space.
+We have a monoidal structure on the comma category $(\A/U)$ where the tensor product of two objects $(a_1,x_1,a_1 \xrightarrow{i_1} U(x_1))$ and $(a_2,x_2,a_2 \xrightarrow{i_2} U(x_2))$ is given by $$(a_1,x_1,a_1 \xrightarrow{i_1} U(x_1)) \otimes (a_2,x_2,a_2 \xrightarrow{i_2} U(x_2)) = (a_1+a_2,x_1+x_2,a_1+a_2 \xrightarrow{i_1+i_2} U(x_1+x_2))$$ where the natural  isomorphism $U(x_1)+U(x_2) \cong U(x_1+x_2)$ is implicit in the above composite, for reasons of space.
 The monoidal unit is given by $(0_\A,0_\X,0_\A \to U(0_\X))$.
@@
 {\bf NEW PROOF HERE.}  We apply \cref{lem:shulman} to $L/X \to A$.   Why is this a fibration, cofibration, Beck--Chevalley and symmetric monoidal?
+
+The proof is analogous to the proof of \cref{thm:decorated_cospans_1} in that we apply \cref{lem:shulman} to the Beck-Chevalley monoidal bifibration $U_2 \colon (L/\X) \to \A$ which we now define.
+Let $(L/\X)$ be the comma category in which:
+\begin{enumerate}
+\item{an object is a triple $(a,x,L(a) \xrightarrow{I} x)$, and}
+\item{a morphism from $(a,x,L(a) \xrightarrow{I} x)$ to $(a',x',L(a') \xrightarrow{I'} x')$ is a pair of morphisms $f \colon a \to a'$ and $\alpha \colon x \to x'$ such that the following square commutes:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$L(a)$};
+\node (B) at (1,0) {$L(a')$};
+\node (C) at (0,-1) {$x$};
+\node (D) at (1,-1) {$x'$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$L(f)$} (B)
+(A) edge node[left]{$I$} (C)
+(B) edge node[right]{$I'$} (D)
+(C) edge node[above]{$\alpha$} (D);
+\end{tikzpicture}
+\]}
+\end{enumerate}
+The functor $U_2$ is defined on objects by $U_2(a,x,L(a) \xrightarrow{I} x)=a$ and on morphisms by $U_2(f,\alpha)=f$.
+The monoidal structure of $(L/\X)$ is similar to the monoidal structure of $(\A/U)$ of \cref{thm:decorated_cospans_1} in that the tensor product of two objects $(a_1,x_1,L(a_1) \xrightarrow{I_1} x_1)$ and $(a_2,x_2,L(a_2) \xrightarrow{I_2} x_2)$ is given by
+$$(a_1,x_1,L(a_1) \xrightarrow{I_1} x_1) \otimes (a_2,x_2,L(a_2) \xrightarrow{I_1} x_2)=(a_1+a_2,x_1+x_2,L(a_1+a_2) \xrightarrow{I_1+I_2} x_1+x_2)$$
+where again the natural isomorphism $L(a_1)+L(a_2) \cong L(a_1+a_2)$ is implicit.
+The monoidal unit is ${(0_\A,0_\X,{L(0_\A) \to 0_\X})}$, and it is clear that $U_2$ is a strict monoidal functor using this tensor product.
+
+The functor $U_2$ is both a fibration and an opfibration. Given a morphism $f \colon a \to b$ in $\A$ with ${(b,x,L(b) \xrightarrow{I} x)}$ over $b$ in $\X$, the cartesian lifting of $f$ is given by
+$$(f,\id_x) \colon (a,x,L(a) \xrightarrow{I \circ L(f)} x) \to (b,x,L(b) \xrightarrow{I} x).$$
+With $(a,x,L(a) \xrightarrow{I} x)$ over $a$ in $\X$, the cocartesian lifting of $f$ is given by
+$$(f,\kappa) \colon (a,x,L(a) \xrightarrow{I} x) \to (b,x+_{L(a)} L(b),L(b) \xrightarrow{\theta} x+_{L(a)} L(b))$$
+where $\kappa$ and $\theta$ are as in the following diagram:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$L(a)$};
+\node (B) at (2.25,0) {$L(c)$};
+\node (C) at (1.5,1) {$L(b)$};
+\node (D) at (0,-2) {$x$};
+\node (E) at (2.25,-2) {$y$};
+\node (F) at (1.5,-1) {$x+_{L(a)} L(b)$};
+\path[->,font=\scriptsize,>=angle 90]
+(D) edge [dashed] node [above] {$\kappa$} (F)
+(F) edge [dashed] node [left] {$\exists ! \psi$} (E)
+(D) edge node [above] {$g'$} (E)
+(A) edge node [left] {$I$} (D)
+(C) edge [dashed] node [left,near end] {$\theta$} (F)
+(B) edge node {$$} (E)
+(A) edge node[above]{$L(f')$} (B)
+(C) edge node [right] {$L(p)$} (B)
+(A) edge node[left]{$L(f)$} (C);
+\end{tikzpicture}
+\]
+Both cartesian and cocartesian liftings are preserved by the tensor product of $(L/\X)$.
+
+Lastly, we show that $U_2 \colon (L/ \X) \to \A$ satisfies the Beck-Chevalley condition. Given a pushout square in $\A$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$a$};
+\node (B) at (1,0) {$b$};
+\node (C) at (0,-1) {$c$};
+\node (D) at (1,-1) {$d$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$h$} (B)
+(A) edge node[left]{$k$} (C)
+(B) edge node[right]{$g$} (D)
+(C) edge node[above]{$f$} (D);
+\end{tikzpicture}
+\]
+we show that the following square commutes up to a natural isomorphism:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$(L/\X)_a$};
+\node (B) at (2,0) {$(L/\X)_b$};
+\node (C) at (0,-1) {$(L/\X)_c$};
+\node (D) at (2,-1) {$(L/\X)_d$};
+\node (E) at (1,-0.5) {$\cong$};
+\path[->,font=\scriptsize,>=angle 90]
+(B) edge node[above]{$h^*$} (A)
+(A) edge node[left]{$k_!$} (C)
+(B) edge node[right]{$g_!$} (D)
+(D) edge node[above]{$f^*$} (C);
+\end{tikzpicture}
+\]
+Let $(b,x,L(b) \xrightarrow{I} x)$ be an object of $(L/\X)_b$.
+Going right, we precompose with $L(h) \colon L(a) \to L(b)$ to obtain the object $(a,x,L(a) \xrightarrow{I \circ L(h)} x)$ in $(L/\X)_a$.
+Then, going down, we pushforward along $L(k) \colon L(a) \to L(c)$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$L(a)$};
+\node (B) at (2,0) {$x$};
+\node (C) at (0,-1) {$L(c)$};
+\node (D) at (2,-1) {$L(c)+_{L(a)}x$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$I \circ L(h)$} (B)
+(A) edge node[left]{$L(k)$} (C)
+(B) edge node[right]{$$} (D)
+(C) edge node[above]{$\psi$} (D);
+\end{tikzpicture}
+\]
+to obtain the object $(c,L(c)+_{L(a)} x,L(c) \xrightarrow{\psi} L(c)+_{L(a)} x)$ in $(L/ \X)_c$.
+For the other route, first going down, we pushforward the object $(b,x,L(b) \xrightarrow{I} x)$ along $L(g) \colon L(b) \to L(d)$ by taking the following pushout:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$L(b)$};
+\node (B) at (2,0) {$x$};
+\node (C) at (0,-1) {$L(d)$};
+\node (D) at (2,-1) {$L(d)+_{L(b)}x$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$I$} (B)
+(A) edge node[left]{$L(g)$} (C)
+(B) edge node[right]{$$} (D)
+(C) edge node[above]{$\theta$} (D);
+\end{tikzpicture}
+\]
+which yields the object $(d,L(d)+_{L(b)}x,L(d) \xrightarrow{\theta} L(d)+_{L(b)} x)$ of $(L/\X)_d$.
+We then precompose with $L(f) \colon L(c) \to L(d)$ to obtain the object $(c,L(d)+_{L(b)} x,L(c) \xrightarrow{\theta \circ L(f)} L(d)+_{L(b)} x)$ of $(L/\X)_c$.
+
+To establish a natural isomorphism between the two objects $(c,L(c)+_{L(a)} x,L(c) \xrightarrow{\psi} L(c)+_{L(a)} x)$ and $(c,L(d)+_{L(b)} x,L(c) \xrightarrow{\theta \circ L(f)} L(d)+_{L(b)} x)$ in $(L/\X)_c$, it suffices to establish a natural isomorphism between the objects $L(c)+_{L(a)} x$ and $L(d)+_{L(b)} x$ in $\X$.
+The first pushout square above exhibits $L(c)+_{L(a)}x$ as a colimit of the span $$L(c) \xleftarrow{L(k)} L(a) \xrightarrow{I \circ L(h)} x$$in $\X$.
+On the other hand, as $L$ is a left adjoint, $L$ preserves pushout squares, and so the following square is also a pushout:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$L(a)$};
+\node (B) at (1,0) {$L(b)$};
+\node (C) at (0,-1) {$L(c)$};
+\node (D) at (1,-1) {$L(d)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$L(h)$} (B)
+(A) edge node[left]{$L(k)$} (C)
+(B) edge node[right]{$L(g)$} (D)
+(C) edge node[above]{$L(f)$} (D);
+\end{tikzpicture}
+\]
+which we may then paste to the left of the second above pushout square to obtain another pushout square:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$L(b)$};
+\node (B) at (2,0) {$x$};
+\node (C) at (0,-1) {$L(d)$};
+\node (D) at (2,-1) {$L(d)+_{L(b)}x$};
+\node (E) at (-1,0) {$L(a)$};
+\node (F) at (-1,-1) {$L(c)$};
+\path[->,font=\scriptsize,>=angle 90]
+(E) edge node [left] {$L(k)$} (F)
+(E) edge node [above] {$L(h)$} (A)
+(F) edge node [above] {$L(f)$} (C)
+(A) edge node[above]{$I$} (B)
+(A) edge node[left]{$L(g)$} (C)
+(B) edge node[right]{$$} (D)
+(C) edge node[above]{$\theta$} (D);
+\end{tikzpicture}
+\]
+which exhibits $L(d)+_{L(b)} x$ also as a colimit of the same span in $\X$, and hence the desired natural isomorphism between our two objects of $(L /\X)_c$.
+Thus $U_2$ satisfies the Beck-Chevalley condition.
 \end{proof}
@@
 {\textbf NEW PROOF HERE.}
+To show that the symmetric monoidal double categories $F\lCsp$ and $_L \lCsp(\inta F)$ of Theorems \ref{thm:decorated_cospans_2} and \ref{thm:SC} are isomorphic, we make use of a result of Shulman \cite[Theorem~14.11]{Shulman2010} which states that there exists a 2-functor $\mathbf{Fr} \colon \mathbf{FMF} \to \mathbf{FDbl}$.
+Here, $\mathbf{FMF}$ is the 2-category consisting of
+\begin{enumerate}
+\item{monoidal bifibrations satisfying the Beck-Chevalley condition,}
+\item{strong monoidal morphisms of bifibrations, and}
+\item{monoidal transformations of bifibrations.}
+\end{enumerate}
+and $\mathbf{FDbl}$ is the 2-category of fibrant double categories, double functors and double transformations.
+Given two monoidal bifibrations $\Phi \colon \A \to \mathsf{B}$ and $\Phi' \colon \A' \to \mathsf{B}'$, a \define{strong monoidal morphism of bifibrations} from $\Phi$ to $\Phi'$ consists of a pair of strong monoidal functors $F_1$ and $F_2$ making the following square commute:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$\A$};
+\node (B) at (1,0) {$\A'$};
+\node (C) at (0,-1) {$\mathsf{B}$};
+\node (D) at (1,-1) {$\mathsf{B}'$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$F_1$} (B)
+(A) edge node[left]{$\Phi$} (C)
+(B) edge node[right]{$\Phi$} (D)
+(C) edge node[above]{$F_2$} (D);
+\end{tikzpicture}
+\]
+and such that the identity $\Phi' F_1 = F_2 \Phi$ is a monoidal transformation.
+The two monoidal fibrations in question are the functors $U_1$ and $U_2$ of Theorems \ref{thm:decorated_cospans_2} and \ref{thm:SC}, respectively, which share $\A$ as a common base, and thus we only need a single strong monoidal functor $F \colon (\A/U) \to (L/\X)$ making the following diagram commute:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$(\A/U)$};
+\node (B) at (2,0) {$(L/ \inta F)$};
+\node (C) at (1,-1.5) {$\A$};
+%\node (D) at (2,-1) {$\A$};
+%\node (E) at (1,0) {$\Downarrow \alpha_1$};
+%\node (F) at (1,-1) {$\Downarrow \alpha_2$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$\stackrel{F}\cong$} (B)
+%(B) edge [bend left] node[above]{$$} (A)
+(A) edge node[left]{$U_1$} (C)
+(B) edge node[right]{$U_2$} (C);
+%(C) edge [bend left] node[above]{$G_1$} (C)
+%(C) edge [bend right] node[above]{$G_2$} (C);
+\end{tikzpicture}
+\]
+with $U_2 F=U_1$ a monoidal transformation. The functor $F \colon (\A/U) \to (L/\inta F)$ is expressed by the natural isomorphism of an adjunction, namely:
+$$F(a,x,a \to U(x))=(a,x,L(a) \to x)$$
+and is the identity on pairs of morphisms making the required squares commute.
+It is clear that $F$ is strong monoidal via component-wise binary coproducts which are preserved by both $L$ and $U$, and that the identity $U_2 F=U_1$ is a monoidal transformation.
+As $F$ is an isomorphism, we obtain an isomorphism $$\mathbf{Fr}(F) \colon \mathbf{Fr}(U_1) \to \mathbf{Fr}(U_2)$$ between the two symmetric monoidal double categories $\mathbb{F}\mathbf{r}(U_1)=F\lCsp$ and $\mathbf{F}\mathbf{r}(U_2)= _L \lCsp(\inta F)$ of Theorems \ref{thm:decorated_cospans_2} and \ref{thm:SC}, respectively.
 \end{proof}

### 2021-04-05 cospans_new.tex
got rid of "stashed changes" in paper

@@
 \def\chris{\purple}
+\def\john{\color{red}}
 \newcommand{\upback}{\mathbin{\rotatebox[origin=c]{135}{$\ulcorner$}}}
@@
 In this section we build symmetric monoidal double categories of decorated cospans, and then study the functoriality of this construction.
-\cref{thm:decorated_cospans} explains how to construct a double category of decorated cospans from a lax monoidal pseudofunctor $F \maps (\A,+) \to (\Cat, \times)$  whenever $A$ has finite colimits ({\bf or is just cocartesian?}).
+\cref{thm:decorated_cospans_1} explains how to construct a double category of decorated cospans from a lax monoidal pseudofunctor $F \maps (\A,+) \to (\Cat, \times)$  whenever $A$ is a cocartesian.
 \cref{thm:decorated_cospans_2} gives conditions under which this double category is symmetric monoidal.
@@
 
-In all that follows, when we say a category `has finite colimits' we mean it is equipped with a choice of colimit for every finite diagram.
-Thus, if $\A$ has finite colimits it gives a cocartesian monoidal category $(\A,+)$: a symmetric monoidal category where the monoidal structure is given by the chosen binary coproducts and initial object.
+In what follows, we define a \define{cocartesian monoidal category} $(\A,+)$ to be a symmetric
+monoidal category where the monoidal structure is given by chosen binary coproducts, with a chosen initial object serving as the unit for the monoidal structure.
+Any category with finite coproducts can be made into a cocartesian monoidal category by arbitrarily choosing finite coproduct and a unit object.
+
+%In all that follows, when we say a category `has finite colimits' we mean it is equipped with a choice of colimit for every finite diagram.
+Thus, if $\A$ has coproducts it gives a cocartesian monoidal category $(\A,+)$: that is, a symmetric monoidal category where the monoidal structure is given by the chosen binary coproducts and initial object.
 However, when we say a functor `preserves finite colimits', it need only do this up to canonical isomorphism, unless otherwise specified.
+MAY NEED THIS LATER, BUT NOT HERE!!!
 
 \begin{thm}\label{thm:decorated_cospans_1}
-Let $\A$ be a category with finite colimits and $F \maps (\A,+) \to (\Cat,\times)$ a lax monoidal pseudofunctor. Then there exists a double category $F\lCsp$ in which
+Let $(\A,+)$ be cocartesian monoidal and $F \maps (\A,+) \to (\Cat,\times)$ a lax monoidal pseudofunctor. Then there exists a double category $F\lCsp$ in which
 \begin{itemize}
@@
 (C) edge node[right]{$g$} (C')
-(A') edge node[above] {$i'$} (D)
-(C') edge node[above] {$o'$} (D)
+(A') edge node[below] {$i'$} (D)
+(C') edge node[below] {$o'$} (D)
 (B) edge node [left] {$h$} (D);
@@
 \begin{thm}\label{thm:decorated_cospans_2}
-Let $\A$ be a category with finite colimits and let $(F,\phi,\phi_0)\maps (\A,+) \to (\Cat,\times)$ be a symmetric lax monoidal pseudofunctor.
+Let $(\A,+)$ be a cocartesian monoidal category and let $(F,\phi,\phi_0)\maps (\A,+) \to (\Cat,\times)$ be a symmetric lax monoidal pseudofunctor.
 Then the double category $F\lCsp$ is symmetric monoidal, where the tensor product
@@
 A functor $\Phi \maps \C \to \A$ is a \define{bifibration} if it is both a fibration and an opfibration.
-If $\Phi \maps \C \to \A$ an opfibration we have for any morphism $f \maps a \to b$ in $\A$ a covariant reindexing functor
+If $\C$ and $\A$ are monoidal categories, a \define{monoidal} bifibration $\Phi \colon \C \to \A$ is a bifibration that is also a strict monoidal functor.
+Similarly, if $\C$ and $\A$ are symmetric monoidal, a \define{symmetric monoidal} bifibration is a bifibration $\Phi \colon \C \to \A$ that is a symmetric strict monoidal functor.
+
+If $\Phi \maps \C \to \A$ an opfibration, for any morphism $f \maps a \to b$ in $\A$ there is a covariant reindexing functor
 \[    f_! \maps \C_a \to \C_b \]
-between the fibers of $\Phi$, as recalled in \cref{subsec:fibrations}.  Similarly, if $\Phi$ is a fibration we have a contravariant reindexing functor
+between the fibers of $\Phi$, as recalled in \cref{subsec:fibrations}.  Similarly, if $\Phi$ is a fibration there is a contravariant reindexing functor
 \[    f^\ast \maps \C_b \to \C_a .\]
@@
 \node (A) at (0,0) {$a$};
-\node (B) at (1,0) {$b$};
+\node (B) at (1.5,0) {$b$};
 \node (C) at (0,-1) {$c$};
-\node (D) at (1,-1) {$d$};
+\node (D) at (1.5,-1) {$d$};
 %\node (E) at (0.5,-0.5) {$\Downarrow\theta$};
@@
 \]
-the following square commutes up to a natural transformation:
+the following square commutes up to a specified natural transformation, built
 \[
@@
 \node (A) at (0,0) {$\C_a$};
-\node (B) at (1,0) {$\C_b$};
+\node (B) at (1.5,0) {$\C_b$};
 \node (C) at (0,-1) {$\C_c$};
-\node (D) at (1,-1) {$\C_d$};
-\node (E) at (0.5,-0.5) {$\Searrow \theta$};
+\node (D) at (1.5,-1) {$\C_d$};
+\node (E) at (0.75,-0.5) {$\Searrow \theta$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-If $\theta$ is a natural isomorphism whenever the original square in $\A$ was
+If $\theta$ is a natural isomorphism whenever the original square in $\A$ is
 a pushout, we say $\Phi$ is \define{Beck--Chevalley}.  (Shulman says `strongly co-Beck--Chevalley'.)
@@
 \begin{lem}[\textbf{Shulman}] \label{lem:shulman}
-Suppose $\A$ has finite colimits and $\Phi \maps \C \to \A$ is a Beck--Chevalley bifibration.  Then there is a double category $\Fr(\Phi)$ in which
+Suppose $(\A,+)$ is cocartesian monoidal and $\Phi \maps (\C,\otimes) \to (\A,+)$ is a Beck--Chevalley monoidal bifibration.  Then there is a double category $\Fr(\Phi)$ in which
 
@@
 
-\begin{proof}[Proof of \cref{thm:decorated_cospans_1}] We apply \cref{lem:shulman} to the Beck-Chevalley monoidal bifibration $U_1 \colon (\A/U) \to \A$ which we now define.
-Let $(\A/U)$ be the comma category in which:
+\begin{proof}[Proof of \cref{thm:decorated_cospans_1}] 
+We apply \cref{lem:shulman} to a bifibration $\Phi \maps (\A/U) \to \A$ which we now define. Let $(\A/U)$ be the comma category in which:
 \begin{enumerate}
@@
 \node (A) at (0,0) {$a$};
-\node (B) at (1,0) {$a'$};
+\node (B) at (1.5,0) {$a'$};
 \node (C) at (0,-1) {$U(x)$};
-\node (D) at (1,-1) {$U(x')$};
+\node (D) at (1.5,-1) {$U(x')$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (B) edge node[right]{$i'$} (D)
-(C) edge node[above]{$U(\alpha)$} (D);
+(C) edge node[below]{$U(\alpha)$} (D);
 \end{tikzpicture}
@@
 \end{enumerate}
-The functor $U_1$ is defined on objects by $U_1(a,x,a \xrightarrow{i} U(x))=a$ and on morphisms by $U_1(f,\alpha)=f$.
-We have a monoidal structure on the comma category $(\A/U)$ where the tensor product of two objects $(a_1,x_1,a_1 \xrightarrow{i_1} U(x_1))$ and $(a_2,x_2,a_2 \xrightarrow{i_2} U(x_2))$ is given by $$(a_1,x_1,a_1 \xrightarrow{i_1} U(x_1)) \otimes (a_2,x_2,a_2 \xrightarrow{i_2} U(x_2)) = (a_1+a_2,x_1+x_2,a_1+a_2 \xrightarrow{i_1+i_2} U(x_1+x_2))$$ where the natural  isomorphism $U(x_1)+U(x_2) \cong U(x_1+x_2)$ is implicit in the above composite, for reasons of space.
+The functor $\Phi$ is defined on objects by $\Phi(a,x,a \xrightarrow{i} U(x))=a$ and on morphisms by $\Phi(f,\alpha)=f$.
+We have a monoidal structure on the comma category $(\A/U)$ where the tensor product of two objects $(a_1,x_1,a_1 \xrightarrow{i_1} U(x_1))$ and $(a_2,x_2,a_2 \xrightarrow{i_2} U(x_2))$ is given by
+\[  (a_1,x_1,a_1 \xrightarrow{i_1} U(x_1)) \otimes (a_2,x_2,a_2 \xrightarrow{i_2} U(x_2)) = (a_1+a_2,x_1+x_2,a_1+a_2 \xrightarrow{i_1+i_2} U(x_1+x_2)) \]
+where we have left the natural isomorphism $U(x_1)+U(x_2) \cong U(x_1+x_2)$  implicit
+ in the above composite, for reasons of space.
 The monoidal unit is given by $(0_\A,0_\X,0_\A \to U(0_\X))$.
@@
 
-The functor $U_1$ is a fibration where given a morphism $f \colon a \to b$ in $\A$ with $(b,y,b \xrightarrow{i} U(y))$ over $b$ in $\int F$, the cartesian lifting of $f$ is given by $$(f,\id) \colon (a,y,a \xrightarrow{i \circ f} U(y)) \to (b,y,b \xrightarrow{i} U(y)).$$Denoting the cartesian lifting of a morphism $f$ by $\textnormal{cart}(f)$, the tensor product of $(\A/U)$ strictly preserves cartesian liftings in the sense that $\textnormal{cart}(f_1) \otimes \textnormal{cart}(f_2)=\textnormal{cart}(f_1+f_2)$.
-
-The functor $U_1$ is also an opfibration where given a morphism $f \colon a \to b$ with $(a,x,a \xrightarrow{i} U(x))$ over $a$, the cocartesian lifting of $f$ is given by $$(f,\theta) \colon (a,x,a \to U(x)) \to (b,z,b \xrightarrow{\phi} U(z))$$where $\theta$ and $\phi$ arise from the following pushout square in $\A$:
+The functor $\Phi$ is a fibration where given a morphism $f \maps a \to b$ in $\A$ with $(b,y,b \xrightarrow{i} U(y))$ over $b$ in $\int F$, the cartesian lifting of $f$ is given by 
+\[ (f,\id) \maps (a,y,a \xrightarrow{i \circ f} U(y)) \to (b,y,b \xrightarrow{i} U(y)). \]
+Denoting the cartesian lifting of a morphism $f$ by $\textnormal{cart}(f)$, the tensor product of $(\A/U)$ strictly preserves cartesian liftings in the sense that $\textnormal{cart}(f_1) \otimes \textnormal{cart}(f_2)=\textnormal{cart}(f_1+f_2)$.
+
+The functor $\Phi$ is also an opfibration where given a morphism $f \maps a \to b$ with $(a,x,a \xrightarrow{i} U(x))$ over $a$, the cocartesian lifting of $f$ is given by 
+\[ (f,\theta) \maps (a,x,a \to U(x)) \to (b,z,b \xrightarrow{\phi} U(z)) \]
+where $\theta$ and $\phi$ arise from the following pushout square in $\A$:
 \[
@@
 \]
-Denoting the cocartesian lifting of a morphism $f$ by $\textnormal{cocart}(f)$, we have that $\textnormal{cocart}(f_1) \otimes \textnormal{cocart}(f_2) \cong \textnormal{cocart}(f_1+f_2)$ by the universal map between two colimits of the same diagram: $$(U(x_1)+_{a_1}b_1)+(U(x_2)+_{a_2}b_2) \cong U(x_1+x_2)+_{a_1+a_2}(b_1+b_2).$$
-
-Lastly, the monoidal bifibration $U_1$ satisfies the Beck-Chevalley condition. Given a pushout square in $\A$:
+Denoting the cocartesian lifting of a morphism $f$ by $\textnormal{cocart}(f)$, we have that $\textnormal{cocart}(f_1) \otimes \textnormal{cocart}(f_2) \cong \textnormal{cocart}(f_1+f_2)$ by the universal map between two colimits of the same diagram:
+\[  (U(x_1)+_{a_1}b_1)+(U(x_2)+_{a_2}b_2) \cong U(x_1+x_2)+_{a_1+a_2}(b_1+b_2). \]
+
+Lastly, the monoidal bifibration $U_1$ satisfies the Beck--Chevalley condition. Given a pushout square in $\A$:
 \[
@@
 \node (A) at (0,0) {$a$};
-\node (B) at (1,0) {$b$};
+\node (B) at (1.5,0) {$b$};
 \node (C) at (0,-1) {$c$};
-\node (D) at (1,-1) {$d$};
+\node (D) at (1.5,-1) {$d$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (B) edge node[right]{$g$} (D)
-(C) edge node[above]{$f$} (D);
-\end{tikzpicture}
-\]
-one can show that the following square commutes up to a natural isomorphism:
+(C) edge node[below]{$f$} (D);
+\end{tikzpicture}
+\]
+we need to show that the following square commutes up to a natural isomorphism:
 \[
@@
 \node (A) at (0,0) {$(\A/U)_a$};
-\node (B) at (2,0) {$(\A/U)_b$};
+\node (B) at (1.5,0) {$(\A/U)_b$};
 \node (C) at (0,-1) {$(\A/U)_c$};
-\node (D) at (2,-1) {$(\A/U)_d$};
-\node (E) at (1,-0.5) {$\Searrow$};
+\node (D) at (1.5,-1) {$(\A/U)_d$};
+\node (E) at (0.75,-0.5) {$\Searrow$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (B) edge node[right]{$g_!$} (D)
-(D) edge node[above]{$f^*$} (C);
+(D) edge node[below]{$f^*$} (C);
 \end{tikzpicture}
@@
 Going right, we precompose with $h \colon a \to b$ to obtain the object $(a,x,a \xrightarrow{i \circ h} U(x))$ in $(\A/U)_a$.
-Then, going down, we pushforward along $k \colon a \to c$:
+Then going down, we push forward along $k$:
 \[
@@
 \node (A) at (0,0) {$a$};
-\node (B) at (2,0) {$U(x)$};
+\node (B) at (1.5,0) {$U(x)$};
 \node (C) at (0,-1) {$c$};
-\node (D) at (2,-1) {$c+_{a}U(x)$};
+\node (D) at (1.5,-1) {$c+_{a}U(x)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (B) edge node[right]{$$} (D)
-(C) edge node[above]{$\psi$} (D);
-\end{tikzpicture}
-\]
-to obtain the object $(c,z,c \to U(z))$ of $(\A/U)_c$ where $z \in \int F$ such that $U(z)=c+_a U(x)$.
-In particular, $z=L(c)+_{L(a)}x$ and as $U$ preserves finite colimits and $UL=1_\A$, we have that $$U(z)=U(L(c)+_{L(a)}x)=U(L(c))+_{U(L(a))}U(x)=c+_a U(x).$$ For the other route, first going down, we pushforward the object $(b,x,b \xrightarrow{i} U(x))$ along $g \colon b \to d$ by taking the following pushout:
+(C) edge node[below]{$\psi$} (D);
+\end{tikzpicture}
+\]
+to obtain the object $(c,z,c \to U(z))$ of $(\A/U)_c$, where $z \in \int F$ has $U(z)=c+_a U(x)$. In particular, $z=L(c)+_{L(a)}x$ and as $U$ preserves finite colimits and $UL=1_\A$, we have that 
+\[  U(z)=U(L(c)+_{L(a)}x)=U(L(c))+_{U(L(a))}U(x)=c+_a U(x).\]
+{\john Need to refer to a proposition where we show $U$ preserves pushouts strictly.}
+ For the other route, first going down, we push the object $(b,x,b \xrightarrow{i} U(x))$ forward along $g \colon b \to d$ by taking the following pushout:
 \[
@@
 \node (A) at (0,0) {$b$};
-\node (B) at (2,0) {$U(x)$};
+\node (B) at (1.5,0) {$U(x)$};
 \node (C) at (0,-1) {$d$};
-\node (D) at (2,-1) {$d+_{b}U(x)$};
+\node (D) at (1.5,-1) {$d+_{b}U(x)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (B) edge node[right]{$$} (D)
-(C) edge node[above]{$\theta$} (D);
+(C) edge node[below]{$\theta$} (D);
 \end{tikzpicture}
@@
 It suffices to obtain a natural isomorphism between the two objects $z=L(c)+_{L(a)} x$ and $z'=L(d)+_{L(b)} x$ in $\X$.
-The following two squares are pushouts:
+This pushout square:
 \[
@@
 \node (A) at (0,0) {$L(a)$};
-\node (B) at (2,0) {$x$};
+\node (B) at (1.5,0) {$x$};
 \node (C) at (0,-1) {$L(c)$};
-\node (D) at (2,-1) {$L(c)+_{L(a)}x$};
-\node (A') at (3,0) {$L(b)$};
-\node (B') at (5,0) {$x$};
-\node (C') at (3,-1) {$L(d)$};
-\node (D') at (5,-1) {$L(d)+_{L(b)}x$};
+\node (D) at (1.5,-1) {$L(c)+_{L(a)}x$};
+%\node (A') at (4,0) {$L(b)$};
+%\node (B') at (6,0) {$x$};
+%\node (C') at (4,-1) {$L(d)$};
+%\node (D') at (6,-1) {$L(d)+_{L(b)}x$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (B) edge node[right]{$$} (D)
-(C) edge node[above]{$\psi$} (D)
-(A') edge node[above]{$I$} (B')
-(A') edge node[left]{$L(g)$} (C')
-(B') edge node[right]{$$} (D')
-(C') edge node[above]{$\theta$} (D');
-\end{tikzpicture}
-\]
-the left of which exhibits $L(c)+_{L(a)}x$ as a colimit of the span $$L(c) \xleftarrow{L(k)} L(a) \xrightarrow{I \circ L(h)} x$$in $\X$.
-As $L$ preserves pushouts, the following square is also a pushout:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$L(a)$};
-\node (B) at (1,0) {$L(b)$};
-\node (C) at (0,-1) {$L(c)$};
-\node (D) at (1,-1) {$L(d)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$L(h)$} (B)
-(A) edge node[left]{$L(k)$} (C)
-(B) edge node[right]{$L(g)$} (D)
-(C) edge node[above]{$L(f)$} (D);
-\end{tikzpicture}
-\]
-which we may then paste to the left of the above pushout square on the right to obtain another pushout square:
+(C) edge node[below]{$\psi$} (D);
+%(A') edge node[above]{$I$} (B')
+%(A') edge node[left]{$L(g)$} (C')
+%(B') edge node[right]{$$} (D')
+%(C') edge node[below]{$\theta$} (D');
+\end{tikzpicture}
+\]
+exhibits $z$ as a pushout of the span 
+\[  L(c) \xleftarrow{L(k)} L(a) \xrightarrow{I \circ L(h)} x 
+\]
+in $\X$. As $L$ preserves pushouts, we may apply it to the original pushout square in $\A$
+and paste on another pushout square:
 \[
@@
 \node (A) at (0,0) {$L(b)$};
-\node (B) at (2,0) {$x$};
+\node (B) at (1.5,0) {$x$};
 \node (C) at (0,-1) {$L(d)$};
-\node (D) at (2,-1) {$L(d)+_{L(b)}x$};
-\node (E) at (-1,0) {$L(a)$};
-\node (F) at (-1,-1) {$L(c)$};
+\node (D) at (1.5,-1) {$L(d)+_{L(b)}x$};
+\node (E) at (-1.5,0) {$L(a)$};
+\node (F) at (-1.5,-1) {$L(c)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (E) edge node [above] {$L(h)$} (A)
-(F) edge node [above] {$L(f)$} (C)
+(F) edge node [below] {$L(f)$} (C)
 (A) edge node[above]{$I$} (B)
@@
 (B) edge node[right]{$$} (D)
-(C) edge node[above]{$\theta$} (D);
-\end{tikzpicture}
-\]
-which exhibits $L(d)+_{L(b)} x$ also as a colimit of the same span in $\X$, and hence the desired natural isomorphism between our two objects of $(\A/U)_c$ showing that $U_1$ satisfies the Beck-Chevalley condition.
+(C) edge node[below]{$\theta$} (D);
+\end{tikzpicture}
+\]
+obtaining a pushout square 
+which exhibits $z'$ as a pushout of the same span in $\X$.  The resulting natural isomorphism
+between $z$ and $z'$ gives the desired natural isomorphism between our two objects of $(\A/U)_c$, showing that $U_1$ satisfies the Beck--Chevalley condition.
 \end{proof}
@@
 \node (D) at (1,-1) {$\Cat$.};
-\node (E) at (0.5,-0.5) {$\Downarrow\theta$};
+\node (E) at (0.5,-0.5) {$\Swarrow\theta$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (C) edge node[right]{$g$} (C')
-(A') edge node[above] {$i'$} (D)
-(C') edge node[above] {$o'$} (D)
+(A') edge node[below] {$i'$} (D)
+(C') edge node[below] {$o'$} (D)
 (B) edge node [left] {$h$} (D)
@@
 (C'') edge node[right]{$H(g)$} (C''')
-(A''') edge node[above] {$H(i')$} (D'')
-(C''') edge node[above] {$H(o')$} (D'')
+(A''') edge node[below] {$H(i')$} (D'')
+(C''') edge node[below] {$H(o')$} (D'')
 (B'') edge node [left] {$H(h)$} (D'');
@@
 (B) edge node [above] {$\theta_m$} (E)
-(D) edge node [above] {$\theta_n$} (F)
+(D) edge node [below] {$\theta_n$} (F)
 (E) edge node [right] {$F'(H(h))$} (F)
@@
 \node (D) at (1,-1) {$\Cat$};
-\node (E) at (0.5,-0.5) {$\Downarrow \theta$};
+\node (E) at (0.5,-0.5) {$\Swarrow \theta$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (C) edge node[above]{$o$} (B)
-(A') edge node[above]{$i'$} (B')
-(C') edge node[above]{$o'$} (B')
+(A') edge node[below]{$i'$} (B')
+(C') edge node[below]{$o'$} (B')
 (A) edge node [left]{$L(f)$} (A')
@@
 symmetric monoidal structure is defined using finite coproducts in $\A$ and $\X$: 
-the tensor of two horizontal 1-cells is
+the tensor product of two horizontal 1-cells is
 \begin{equation}\label{eq:tensorstuctured}
-\begin{tikzcd}[column sep={.4in,between origins}, row sep=.1in]
+\begin{tikzcd}[column sep={.4in,between origins}, row sep=.08in]
 & x &&&& x' &&&& x+x' & \\
 &&&\ot&&&& = &&&& \\
-L(a)\ar[uur,"i"]&& L(b)\ar[uul,"o"'] && L(a')\ar[uur,"i'"] && L(b')\ar[uul,"o'"'] && L(a+a')\ar[uur,"i+i'"] && L(b+b')\ar[uul,"o+o'"'] 
+L(a)\ar[uur,"i" pos=0.3]&& L(b)\ar[uul,"o"' pos=0.3] && L(a')\ar[uur,"i'" pos=0.3] && L(b')\ar[uul,"o'"' pos=0.3] && L(a+a')\ar[uur,"i+i'" pos=0.3] && L(b+b')\ar[uul,"o+o'"' pos=0.3] 
 \end{tikzcd}

### 2021-04-06 cospans_new.tex
Second attempt at proving Theorem 2.1

@@
 Let $(b,x,b \xrightarrow{i} U(x))$ be an object of $(\A/U)_b$.
-Going right, we precompose with $h \colon a \to b$ to obtain the object $(a,x,a \xrightarrow{i \circ h} U(x))$ in $(\A/U)_a$.
+Going left, we precompose with $h \colon a \to b$ to obtain the object $(a,x,a \xrightarrow{i \circ h} U(x))$ of $(\A/U)_a$.
 Then going down, we push forward along $k$:
@@
 \]
-to obtain the object $(c,z,c \to U(z))$ of $(\A/U)_c$, where $z \in \int F$ has $U(z)=c+_a U(x)$. In particular, $z=L(c)+_{L(a)}x$ and as $U$ preserves finite colimits and $UL=1_\A$, we have that 
-\[  U(z)=U(L(c)+_{L(a)}x)=U(L(c))+_{U(L(a))}U(x)=c+_a U(x).\]
+to obtain the object $(c,z,c \xrightarrow{\psi} U(z))$ of $(\A/U)_c$, where $z \in \int F$ is given by $z=\bot_c+_{\bot_a}x$. Explicitly, $z$ is given by
+\[ 1 \xrightarrow{x} F(U(x)) \xrightarrow{F(\zeta)} F(0+_0 U(x)) \xrightarrow{F(!_c +_{!_a} 1)} F(c+_a U(x)) \]
+and so by construction, we have that 
+\[  U(z)=U(\bot_c+_{\bot_a}x)=c+_a U(x).\]
 {\john Need to refer to a proposition where we show $U$ preserves pushouts strictly.}
@@
 \]
-which yields the object $(d,z',d \to U(z'))$ of $(\A/U)_d$ where $z' \in \int F$ such that $U(z')=d+_b U(x)$.
-In particular, $z'$ is given by $z'=L(d)+_{L(b)}x$.
-We then precompose with $f \colon c \to d$ to obtain the object $(c,z',c \to U(z'))$ of $(\A/U)_c$.
-
-Now we seek a natural isomorphism between the two objects $(c,z,c \to c+_a U(x))$ and $(c,z',c \to d+_b U(x))$ in $(\A/U)_c$.
-It suffices to obtain a natural isomorphism between the two objects $z=L(c)+_{L(a)} x$ and $z'=L(d)+_{L(b)} x$ in $\X$.
+which yields the object $(d,z',d \xrightarrow{\theta} U(z'))$ of $(\A/U)_d$ where $z' \in \int F$ is given by $z'=\bot_d+_{\bot_b}x$.
+We then precompose with $f \colon c \to d$ to obtain the object $(c,z',c \xrightarrow{\theta \circ f} U(z'))$ of $(\A/U)_c$.
+
+Now we seek a natural isomorphism between the two objects $(c,z,c \xrightarrow{\psi} c+_a U(x))$ and $(c,z',c \xrightarrow{\theta \circ f} d+_b U(x))$ in $(\A/U)_c$.
+It suffices to obtain a natural isomorphism between the two objects $z=\bot_c+_{\bot_a} x$ and $z'=\bot_d+_{\bot_b} x$ in $\X$.
 This pushout square:
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$L(a)$};
-\node (B) at (1.5,0) {$x$};
-\node (C) at (0,-1) {$L(c)$};
-\node (D) at (1.5,-1) {$L(c)+_{L(a)}x$};
+\node (A) at (0,0) {$a$};
+\node (B) at (1.5,0) {$U(x)$};
+\node (C) at (0,-1) {$c$};
+\node (D) at (1.5,-1) {$c+_{a}U(x)$};
 %\node (A') at (4,0) {$L(b)$};
@@
 \path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$I \circ L(h)$} (B)
-(A) edge node[left]{$L(k)$} (C)
+(A) edge node[above]{$i \circ h$} (B)
+(A) edge node[left]{$k$} (C)
 (B) edge node[right]{$$} (D)
@@
 \]
-exhibits $z$ as a pushout of the span 
-\[  L(c) \xleftarrow{L(k)} L(a) \xrightarrow{I \circ L(h)} x 
-\]
-in $\X$. As $L$ preserves pushouts, we may apply it to the original pushout square in $\A$
-and paste on another pushout square:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$L(b)$};
-\node (B) at (1.5,0) {$x$};
-\node (C) at (0,-1) {$L(d)$};
-\node (D) at (1.5,-1) {$L(d)+_{L(b)}x$};
-\node (E) at (-1.5,0) {$L(a)$};
-\node (F) at (-1.5,-1) {$L(c)$};
-\path[->,font=\scriptsize,>=angle 90]
-(E) edge node [left] {$L(k)$} (F)
-(E) edge node [above] {$L(h)$} (A)
-(F) edge node [below] {$L(f)$} (C)
-(A) edge node[above]{$I$} (B)
-(A) edge node[left]{$L(g)$} (C)
+exhibits $c+_a U(x)$ as a pushout of the span 
+\[  c \xleftarrow{k} a \xrightarrow{i \circ h} U(x) 
+\]
+in $\A$. We may also take the first pushout square above and paste it with the original pushout square in $\A$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$b$};
+\node (B) at (1.5,0) {$U(x)$};
+\node (C) at (0,-1) {$d$};
+\node (D) at (1.5,-1) {$d+_{b}U(x)$};
+\node (E) at (-1.5,0) {$a$};
+\node (F) at (-1.5,-1) {$c$};
+\path[->,font=\scriptsize,>=angle 90]
+(E) edge node [left] {$k$} (F)
+(E) edge node [above] {$h$} (A)
+(F) edge node [below] {$f$} (C)
+(A) edge node[above]{$i$} (B)
+(A) edge node[left]{$g$} (C)
 (B) edge node[right]{$$} (D)
@@
 obtaining a pushout square 
-which exhibits $z'$ as a pushout of the same span in $\X$.  The resulting natural isomorphism
-between $z$ and $z'$ gives the desired natural isomorphism between our two objects of $(\A/U)_c$, showing that $U_1$ satisfies the Beck--Chevalley condition.
+which exhibits $d+_b U(x)$ as a pushout of the same span in $\A$.
+The resulting natural isomorphism $\kappa$ between $c+_a U(x)$ and $d+_b U(x)$ then extends to a natural isomorphism between $z=\bot_c +_{\bot_a} x$ and $z'=\bot_d +_{\bot_b} x$ in $\X$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node () at (5,0) {$\cong$};
+\node (A) at (0,0) {$1$};
+
+\node (A1) at (2,0.5) {$F(U(x))$};
+\node (A2) at (4,0.5) {$F(0+_0 U(x))$};
+\node (A3) at (6,0.5) {$F(c+_a U(x))$};
+
+\node (B1) at (2,-0.5) {$F(U(x))$};
+\node (B2) at (4,-0.5) {$F(0+_0 U(x))$};
+\node (B3) at (6,-0.5) {$F(d+_b U(x))$};
+
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[fill=white]{$x$} (A1)
+(A) edge node[fill=white]{$x$} (B1)
+
+(A1) edge node [above] {$F(\zeta)$} (A2)
+(A2) edge node [above] {$F(!_c +_{!_a} 1)$} (A3)
+
+(A1) edge node [fill=white] {$1$} (B1)
+(A2) edge node [fill=white] {$1$} (B2)
+(A3) edge node [fill=white] {$F(\kappa)$} (B3)
+
+(B1) edge node [above] {$F(\zeta)$} (B2)
+(B2) edge node [above] {$F(!_d +_{!_b} 1)$} (B3);
+
+\end{tikzpicture}
+\]
+and consequently a natural isomorphism between our two objects of $(\A/U)_c$, showing that $U_1$ satisfies the Beck--Chevalley condition.
 \end{proof}

### 2021-04-07 cospans_new.tex
Started a functorial approach proof to Theorem 2.4

@@
 
-\begin{proof}  See \cite[Theorem 4.2.1]{CourserThesis}. \end{proof}
+\begin{proof}  See \cite[Theorem 4.2.1]{CourserThesis}.
+
+From the symmetric lax monoidal pseudofunctor $F \colon \A \to \Cat$, we can obtain a Beck-Chevalley symmetric monoidal opfibration $\Phi \colon (\A/U) \to \A$ as in \cref{thm:decorated_cospans_1}, where $U \colon \int F \to \A$ is the associated monoidal opfibration of the pseudofunctor $F$.
+We can do the same for the other symmetric lax monoidal pseudofunctor $F' \colon \A' \to \Cat$ to obtain another Beck-Chevalley symmetric monoidal opfibration $\Phi' \colon (\A'/U') \to \A'$.
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$(\A/U)$};
+\node (B) at (2,0) {$(\A'/U')$};
+\node (C) at (0,-1.5) {$\A$};
+\node (D) at (2,-1.5) {$\A'$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[left]{$\Phi$} (C)
+(B) edge node[right]{$\Phi'$} (D)
+(C) edge node[above]{$H$} (D);
+\end{tikzpicture}
+\]
+We construct a strong monoidal functor $F \colon (\A/U) \to (\A'/U')$ between the monoidal comma categories $(\A/U)$ and $(\A'/U')$ that will make the induced square commute.
+Such a commutative square is a morphism in the 2-category $\mathbf{FMF}$ of monoidal bifibrations satisfying the Beck-Chevalley condition which then by a 2-functor $\mathbf{Fr} \colon \mathbf{FMF} \to \mathbf{FDbl}$ due to Shulman \cite[Theorem 14.11]{Shulman2008} will yield a map $$\mathbf{Fr}(F,H) \colon \mathbf{Fr}(\Phi) \to \mathbf{Fr}(\Phi')$$between the fibrant symmetric monoidal double categories $\mathbf{Fr}(\Phi)=F\lCsp$ and $\mathbf{Fr}(\Phi')= F'\lCsp$.
+
+The monoidal comma category $(\A/U)$ has:
+\begin{enumerate}
+\item{objects as triples $(a,x,a \to U(x))$, and}
+\item{a morphism from $(a,x,a \to U(x))$ to $(b,y,b \to U(y))$ is a pair of morphisms $f \colon a \to b$ and $\tau \colon x \to y$ that make the following square commute:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$a$};
+\node (B) at (1,0) {$b$};
+\node (C) at (0,-1) {$U(x)$};
+\node (D) at (1,-1) {$U(y)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$f$} (B)
+(A) edge node[left]{$$} (C)
+(B) edge node[right]{$$} (D)
+(C) edge node[above]{$U(\tau)$} (D);
+\end{tikzpicture}
+\]
+}
+\end{enumerate}
+The tensor product of two objects $(a_1,x_1,a_1 \to U(x_1))$ and $(a_2,x_2,a_2 \to U(x_2))$ is given by $$(a_1,x_1,a_1 \to U(x_1)) \otimes (a_2,x_2,a_2 \to U(x_2)) = (a_1+a_2,x_1+x_2,a_1+a_2 \to U(x_1+x_2)).$$The monoidal unit of $(\A/U)$ is given by $(0_\A,0_\X,0_\A \to U(0_\X))$.
+Those of $(\A'/U')$ are analogous.
+
+On objects, the strong monoidal functor $F \colon (\A/U) \to (\A'/U')$ is defined as follows:
+\begin{enumerate}
+\item{given $(a,x,a \to U(x))$ in $(\A/U)$, $$F(a,x,a \to U(x)) = (H(a),\theta_m E(x) \phi,H(a) \to U'(\theta_m E(x) \phi))$$where if $1 \xrightarrow{x} F(m)$, then $U(x)=m$ and $\theta_m E(x) \phi$ is given by
+$$1 \xrightarrow{\phi} E(1) \xrightarrow{E(x)} E(F(m)) \xrightarrow{\theta_m} F'(H(m))$$
+so that $U'(\theta_m E(x) \phi)=H(m)$, }
+\item{given a pair of morphisms $(f,\tau)$ that make the following square commute:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$a$};
+\node (B) at (1,0) {$b$};
+\node (C) at (0,-1) {$U(x)$};
+\node (D) at (1,-1) {$U(y)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$f$} (B)
+(A) edge node[left]{$$} (C)
+(B) edge node[right]{$$} (D)
+(C) edge node[above]{$U(\tau)$} (D);
+\end{tikzpicture}
+\]
+we define $$F(f,\tau)=(H(f),\theta_h E(\tau) \phi).$$
+which make the following square in $(\A'/U')$ commute:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$H(a)$};
+\node (B) at (3,0) {$H(b)$};
+\node (C) at (0,-1) {$U'(\theta_m E(x) \phi)$};
+\node (D) at (3,-1) {$U'(\theta_n E(y) \phi))$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$H(f)$} (B)
+(A) edge node[left]{$$} (C)
+(B) edge node[right]{$$} (D)
+(C) edge node[above]{$U'(\theta_h E(\tau) \phi)$} (D);
+\end{tikzpicture}
+\]
+where $\tau$ and $\theta_h E(\tau) \phi$ are given respectively by:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (G) at (-3.5,-0.5) {$1$};
+\node (H) at (-2,0) {$F(m)$};
+\node (I) at (-2,-1) {$F(n)$};
+\node (J) at (-2.5,-0.5) {$\scriptstyle\Downarrow\tau$};
+\node (A) at (-0.25,-0.5) {$1$};
+\node (L) at (0.5,-0.5) {$E(1)$};
+\node (B) at (2,0) {$E(F(m))$};
+\node (D) at (2,-1) {$E(F(n))$};
+\node (C) at (1.5,-0.5) {$\scriptstyle\Downarrow E(\tau)$};
+\node (E) at (4,0) {$F^\prime(H(m))$};
+\node (F) at (4,-1) {$F^\prime(H(n))$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node [above] {$\phi$} (L)
+(G) edge node [above] {$x$} (H)
+(G) edge node [below] {$y$} (I)
+(H) edge node [right] {$F(h)$} (I)
+(B) edge node [above] {$\theta_m$} (E)
+(D) edge node [above] {$\theta_n$} (F)
+(E) edge node [right] {$F'(H(h))$} (F)
+(L) edge node[above]{$E(x)$} (B)
+(L) edge node[below]{$E(y)$} (D)
+(B) edge node[right]{$E(F(h))$} (D);
+\end{tikzpicture}
+\]
+}
+\end{enumerate}
+One can show that the induced laxator and unit morphism given by these prescribed tensor products satisfy the four required coherence laws of a symmetric strong monoidal functor.
+\end{proof}
 

### 2021-04-08 cospans_new.tex
Added laxator and unit morphism diagrams to Theorem 2.4

--- 2021-04-06 cospans_new.tex
@@
 
-\begin{proof}  See \cite[Theorem 4.2.1]{CourserThesis}. \end{proof}
+\begin{proof}  See \cite[Theorem 4.2.1]{CourserThesis}.
+
+From the symmetric lax monoidal pseudofunctor $F \colon \A \to \Cat$, we can obtain a Beck-Chevalley symmetric monoidal opfibration $\Phi \colon (\A/U) \to \A$ as in \cref{thm:decorated_cospans_1}, where $U \colon \int F \to \A$ is the associated monoidal opfibration of the pseudofunctor $F$.
+We can do the same for the other symmetric lax monoidal pseudofunctor $F' \colon \A' \to \Cat$ to obtain another Beck-Chevalley symmetric monoidal opfibration $\Phi' \colon (\A'/U') \to \A'$.
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$(\A/U)$};
+\node (B) at (2,0) {$(\A'/U')$};
+\node (C) at (0,-1.5) {$\A$};
+\node (D) at (2,-1.5) {$\A'$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[left]{$\Phi$} (C)
+(B) edge node[right]{$\Phi'$} (D)
+(C) edge node[above]{$H$} (D);
+\end{tikzpicture}
+\]
+We construct a strong monoidal functor $G \colon (\A/U) \to (\A'/U')$ between the monoidal comma categories $(\A/U)$ and $(\A'/U')$ that will make the induced square commute.
+Such a commutative square is a morphism in the 2-category $\mathbf{FMF}$ of monoidal bifibrations satisfying the Beck-Chevalley condition which then by a 2-functor $\mathbf{Fr} \colon \mathbf{FMF} \to \mathbf{FDbl}$ due to Shulman \cite[Theorem 14.11]{Shulman2008} will yield a map $$\mathbf{Fr}(G,H) \colon \mathbf{Fr}(\Phi) \to \mathbf{Fr}(\Phi')$$between the fibrant symmetric monoidal double categories $\mathbf{Fr}(\Phi)=F\lCsp$ and $\mathbf{Fr}(\Phi')= F'\lCsp$.
+
+The monoidal comma category $(\A/U)$ has:
+\begin{enumerate}
+\item{objects as triples $(a,x,a \to U(x))$, and}
+\item{a morphism from $(a,x,a \to U(x))$ to $(b,y,b \to U(y))$ is a pair of morphisms $f \colon a \to b$ and $\tau \colon x \to y$ that make the following square commute:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$a$};
+\node (B) at (1,0) {$b$};
+\node (C) at (0,-1) {$U(x)$};
+\node (D) at (1,-1) {$U(y)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$f$} (B)
+(A) edge node[left]{$$} (C)
+(B) edge node[right]{$$} (D)
+(C) edge node[above]{$U(\tau)$} (D);
+\end{tikzpicture}
+\]
+}
+\end{enumerate}
+The tensor product of two objects $(a_1,x_1,a_1 \to U(x_1))$ and $(a_2,x_2,a_2 \to U(x_2))$ is given by $$(a_1,x_1,a_1 \to U(x_1)) \otimes (a_2,x_2,a_2 \to U(x_2)) = (a_1+a_2,x_1+x_2,a_1+a_2 \to U(x_1+x_2)).$$The monoidal unit of $(\A/U)$ is given by $(0_\A,0_\X,0_\A \to U(0_\X))$.
+Those of $(\A'/U')$ are analogous.
+
+On objects, the strong monoidal functor $F \colon (\A/U) \to (\A'/U')$ is defined as follows:
+\begin{enumerate}
+\item{given $(a,x,a \to U(x))$ in $(\A/U)$, $$G(a,x,a \to U(x)) = (H(a),\theta_m E(x) \phi,H(a) \to U'(\theta_m E(x) \phi))$$where if $1 \xrightarrow{x} F(m)$, then $U(x)=m$ and $\theta_m E(x) \phi$ is given by
+$$1 \xrightarrow{\phi} E(1) \xrightarrow{E(x)} E(F(m)) \xrightarrow{\theta_m} F'(H(m))$$
+so that $U'(\theta_m E(x) \phi)=H(m)$, }
+\item{given a pair of morphisms $(f,\tau)$ that make the following square commute:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$a$};
+\node (B) at (1,0) {$b$};
+\node (C) at (0,-1) {$U(x)$};
+\node (D) at (1,-1) {$U(y)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$f$} (B)
+(A) edge node[left]{$$} (C)
+(B) edge node[right]{$$} (D)
+(C) edge node[above]{$U(\tau)$} (D);
+\end{tikzpicture}
+\]
+we define $$G(f,\tau)=(H(f),\theta_h E(\tau) \phi).$$
+which make the following square in $(\A'/U')$ commute:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$H(a)$};
+\node (B) at (3,0) {$H(b)$};
+\node (C) at (0,-1) {$U'(\theta_m E(x) \phi)$};
+\node (D) at (3,-1) {$U'(\theta_n E(y) \phi))$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$H(f)$} (B)
+(A) edge node[left]{$$} (C)
+(B) edge node[right]{$$} (D)
+(C) edge node[above]{$U'(\theta_h E(\tau) \phi)$} (D);
+\end{tikzpicture}
+\]
+where $\tau$ and $\theta_h E(\tau) \phi$ are given respectively by:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (G) at (-3.5,-0.5) {$1$};
+\node (H) at (-2,0) {$F(m)$};
+\node (I) at (-2,-1) {$F(n)$};
+\node (J) at (-2.5,-0.5) {$\scriptstyle\Downarrow\tau$};
+\node (A) at (-0.25,-0.5) {$1$};
+\node (L) at (0.5,-0.5) {$E(1)$};
+\node (B) at (2,0) {$E(F(m))$};
+\node (D) at (2,-1) {$E(F(n))$};
+\node (C) at (1.5,-0.5) {$\scriptstyle\Downarrow E(\tau)$};
+\node (E) at (4,0) {$F^\prime(H(m))$};
+\node (F) at (4,-1) {$F^\prime(H(n))$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node [above] {$\phi$} (L)
+(G) edge node [above] {$x$} (H)
+(G) edge node [below] {$y$} (I)
+(H) edge node [right] {$F(h)$} (I)
+(B) edge node [above] {$\theta_m$} (E)
+(D) edge node [above] {$\theta_n$} (F)
+(E) edge node [right] {$F'(H(h))$} (F)
+(L) edge node[above]{$E(x)$} (B)
+(L) edge node[below]{$E(y)$} (D)
+(B) edge node[right]{$E(F(h))$} (D);
+\end{tikzpicture}
+\]
+}
+\end{enumerate}
+The laxator is given by the following natural isomorphism between $\theta_m E(x) \phi + \theta_n E(y) \phi$ and $\theta_{m+n} E(x+y) \phi$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\hspace{-.6in}
+\node () at (3,-0.5) {$\scriptscriptstyle{\stackrel{E_{x_1,x_2}} \cong}$};
+\node () at (1.25,-0.5) {$\scriptscriptstyle{\stackrel{\lambda} \cong}$};
+\node (L1) at (0.5,0) {$\scriptscriptstyle{1 \times E(1)}$};
+\node (L2) at (0.5,-1) {$\scriptscriptstyle{E(1)}$};
+\node (K) at (-1,0) {$\scriptscriptstyle{1 \times 1}$};
+\node (K2) at (-1,-1) {$\scriptscriptstyle{1}$};
+\node (B) at (2,0) {$\scriptscriptstyle{E(1) \times E(1)}$};
+\node (D) at (2,-1) {$\scriptscriptstyle{E(1 \times 1)}$};
+\node (E) at (4,0) {$\scriptscriptstyle{E(F(m)) \times E(F(n))}$};
+\node (F) at (4,-1) {$\scriptscriptstyle{E(F(m) \times F(n))}$};
+\node (G) at (7,0) {$\scriptscriptstyle{F'(H(m)) \times F'(H(n))}$};
+\node (H) at (10,0) {$\scriptscriptstyle{F'(H(m)+H(n))}$};
+\node (I) at (7,-1) {$\scriptscriptstyle{E(F(m+n))}$};
+\node (J) at (10,-1) {$\scriptscriptstyle{F'(H(m+n))}$};
+\path[->,font=\scriptsize,>=angle 90]
+(K) edge node [left] {$\lambda$} (K2)
+(K) edge node [above] {$1 \times E_0$} (L1)
+(K2) edge node [above] {$E_0$} (L2)
+(H) edge node [right] {$F'(H_{m,n})$} (J)
+(E) edge node [above] {$\theta_m \times \theta_n$} (G)
+(G) edge node [above] {$\phi'_{H(m),H(n)}$} (H) 
+(F) edge node [above] {$E(\phi_{m,n})$} (I)
+(I) edge node [above] {$\theta_{m+n}$} (J)
+(B) edge node [above] {$E(x) \times E(y)$} (E)
+(D) edge node [above] {$E(x \times y)$} (F)
+(E) edge node [right] {$E_{F(m),F(n)}$} (F)
+(L1) edge node[above]{$E_0 \times 1$} (B)
+(L1) edge node [left] {$\lambda$} (L2)
+(L2) edge node[above]{$E(\lambda^{-1})$} (D)
+(B) edge node[right]{$E_{1,1}$} (D);
+\end{tikzpicture}
+\]
+and we also have a natural isomorphism between $0_{\inta F'}$ and $G(0_{\inta F})$ given by:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (-1,0.5) {$\scriptscriptstyle{1}$};
+\node () at (4,0.66) {$\scriptscriptstyle{\cong}$};
+\node (A1) at (0,0) {$\scriptscriptstyle{E(1)}$};
+\node (A2) at (2,0) {$\scriptscriptstyle{E(F(0_\A))}$};
+\node (A3) at (4,0) {$\scriptscriptstyle{E(F(0_\A))}$};
+\node (A4) at (6,0) {$\scriptscriptstyle{F'(H(0_\A))}$};
+\node (A') at (2,0.5) {$\scriptscriptstyle{F'(H(0_\A))}$};
+\node (B1) at (0,1) {$\scriptscriptstyle{F'(0_{\A'})}$};
+\node (B2) at (6,1) {$\scriptscriptstyle{F'(0_{\A'})}$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node [below] {$\scriptscriptstyle{E_0}$} (A1)
+(A) edge node [above] {$\scriptscriptstyle{\phi_0'}$} (B1)
+(A1) edge node [above] {$\scriptscriptstyle{E(\phi_0)}$} (A2)
+(A2) edge node [above] {$\scriptscriptstyle{E(F(!_{0_\A}))}$} (A3)
+(A3) edge node [below] {$\scriptscriptstyle{\theta_{0_\A}}$} (A4)
+(A2) edge node [left] {$\scriptscriptstyle{\theta_{0_\A}}$} (A')
+(B1) edge node [fill=white] {$\scriptscriptstyle{F'(H_0)}$} (A')
+(A') edge node [fill=white] {$\scriptscriptstyle{F'(H(!_{0_\A}))}$} (A4)
+(B2) edge node [right] {$\scriptscriptstyle{F'(H_0)}$} (A4)
+(B1) edge node [above] {$\scriptscriptstyle{F'(!_{0_{\A'}})}$} (B2);
+\end{tikzpicture}
+\]
+One can show that this laxator and unit morphism satisfy the four required coherence laws of a symmetric strong monoidal functor.
+\end{proof}
 

### 2021-04-18 cospans_new.tex
Minor changes

@@
 \begin{proof}[Proof of \cref{thm:decorated_cospans_1}] 
-We apply \cref{lem:shulman} to a bifibration $\Phi \maps (\A/U) \to \A$ which we now define. Let $(\A/U)$ be the comma category in which:
+We apply \cref{lem:shulman} to a bifibration $\Phi \maps (\A/U) \to \A$ which we now define.
+The functor $U \colon \inta F \to \A$ is the associated monoidal opfibration of the symmetric lax monoidal pseudofunctor $F \colon \A \to \Cat$.
+Let $(\A/U)$ be the comma category in which:
 \begin{enumerate}
-\item{an object is a triple $(a,x,a \xrightarrow{i} U(x))$, and}
-\item{a morphism from $(a,x,a \xrightarrow{i} U(x))$ to $(a',x',a' \xrightarrow{i'} U(x'))$ is a pair of morphisms $f \colon a \to a'$ and $\alpha \colon x \to x'$ such that the following square commutes:
+\item{an object is a triple $(a,x,a \xrightarrow{i} U(x))$ with $a \in \A$ and $x=(a',p) \in \A \times F(a')$, and}
+\item{a morphism from $(a,x,a \xrightarrow{i} U(x))$ to $(b,x',b \xrightarrow{i'} U(x'))$ is a pair of morphisms $f \colon a \to b$ and $\alpha \colon x \to x'$ such that the following square commutes:
 \[
@@
 \node (A) at (0,0) {$a$};
-\node (B) at (1.5,0) {$a'$};
+\node (B) at (1.5,0) {$b$};
 \node (C) at (0,-1) {$U(x)$};
@@
 We have a monoidal structure on the comma category $(\A/U)$ where the tensor product of two objects $(a_1,x_1,a_1 \xrightarrow{i_1} U(x_1))$ and $(a_2,x_2,a_2 \xrightarrow{i_2} U(x_2))$ is given by
-\[  (a_1,x_1,a_1 \xrightarrow{i_1} U(x_1)) \otimes (a_2,x_2,a_2 \xrightarrow{i_2} U(x_2)) = (a_1+a_2,x_1+x_2,a_1+a_2 \xrightarrow{i_1+i_2} U(x_1+x_2)) \]
-where we have left the natural isomorphism $U(x_1)+U(x_2) \cong U(x_1+x_2)$  implicit
- in the above composite, for reasons of space.
+\[  (a_1,x_1,a_1 \xrightarrow{i_1} U(x_1)) \otimes (a_2,x_2,a_2 \xrightarrow{i_2} U(x_2)) = (a_1+a_2,x_1 \otimes x_2,a_1+a_2 \xrightarrow{i_1+i_2} U(x_1 \otimes x_2)) \]
+where we have left the equality $U(x_1)+U(x_2) = U(x_1 \otimes x_2)$ implicit in the above composite, for reasons of space.
 The monoidal unit is given by $(0_\A,0_\X,0_\A \to U(0_\X))$.
-It is easy to see that the functor $U_1$ can be made into a strict monoidal functor using this tensor product.
+It is easy to see that the functor $\Phi$ can be made into a strict monoidal functor using this tensor product.
 
@@
 Denoting the cocartesian lifting of a morphism $f$ by $\textnormal{cocart}(f)$, we have that $\textnormal{cocart}(f_1) \otimes \textnormal{cocart}(f_2) \cong \textnormal{cocart}(f_1+f_2)$ by the universal map between two colimits of the same diagram:
-\[  (U(x_1)+_{a_1}b_1)+(U(x_2)+_{a_2}b_2) \cong U(x_1+x_2)+_{a_1+a_2}(b_1+b_2). \]
-
-Lastly, the monoidal bifibration $U_1$ satisfies the Beck--Chevalley condition. Given a pushout square in $\A$:
+\[  (U(x_1)+_{a_1}b_1)+(U(x_2)+_{a_2}b_2) \cong U(x_1 \otimes x_2)+_{a_1+a_2}(b_1+b_2). \]
+
+Lastly, the monoidal bifibration $\Phi$ satisfies the Beck--Chevalley condition. Given a pushout square in $\A$:
 \[
@@
 \]
-Let $(b,x,b \xrightarrow{i} U(x))$ be an object of $(\A/U)_b$.
+Let $(b,x,b \xrightarrow{i} U(x))$ be an object of $(\A/U)_b$ where $x=(b',p) \in \A \times F(b')$ so that $U(x)=b'$.
 Going left, we precompose with $h \colon a \to b$ to obtain the object $(a,x,a \xrightarrow{i \circ h} U(x))$ of $(\A/U)_a$.
@@
 \]
-to obtain the object $(c,z,c \xrightarrow{\psi} U(z))$ of $(\A/U)_c$, where $z \in \int F$ is given by $z=\bot_c+_{\bot_a}x$. Explicitly, $z$ is given by
-\[ 1 \xrightarrow{x} F(U(x)) \xrightarrow{F(\zeta)} F(0+_0 U(x)) \xrightarrow{F(!_c +_{!_a} 1)} F(c+_a U(x)) \]
-and so by construction, we have that 
-\[  U(z)=U(\bot_c+_{\bot_a}x)=c+_a U(x).\]
-{\john Need to refer to a proposition where we show $U$ preserves pushouts strictly.}
+to obtain the object $(c,z,c \xrightarrow{\psi} U(z))$ of $(\A/U)_c$, where $z \in \A \times F(c+_a U(x))$ is given by $z=(c+_a U(x),q)$ where $q$ is given by
+\[ 1 \xrightarrow{p} F(U(x)) \xrightarrow{F(\zeta)} F(0+_0 U(x)) \xrightarrow{F(!_c +_{!_a} 1)} F(c+_a U(x)). \]
+%and so by construction, we have that 
+%\[  U(z)=U(\bot_c+_{\bot_a}x)=c+_a U(x).\]
+%{\john Need to refer to a proposition where we show $U$ preserves pushouts strictly.}
  For the other route, first going down, we push the object $(b,x,b \xrightarrow{i} U(x))$ forward along $g \colon b \to d$ by taking the following pushout:
@@
 \]
-which yields the object $(d,z',d \xrightarrow{\theta} U(z'))$ of $(\A/U)_d$ where $z' \in \int F$ is given by $z'=\bot_d+_{\bot_b}x$.
+which yields the object $(d,z',d \xrightarrow{\theta} U(z'))$ of $(\A/U)_d$ where $z' \in \A \times F(d+_b U(x))$ is given by ${z'=(d+_b U(x),q')}$ where $q'$ is given by 
+\[ 1 \xrightarrow{p} F(U(x)) \xrightarrow{F(\zeta)} F(0+_0 U(x)) \xrightarrow{F(!_d +_{!_b} 1)} F(d+_b U(x)). \]
 We then precompose with $f \colon c \to d$ to obtain the object $(c,z',c \xrightarrow{\theta \circ f} U(z'))$ of $(\A/U)_c$.
@@
 Now we seek a natural isomorphism between the two objects $(c,z,c \xrightarrow{\psi} c+_a U(x))$ and $(c,z',c \xrightarrow{\theta \circ f} d+_b U(x))$ in $(\A/U)_c$.
-It suffices to obtain a natural isomorphism between the two objects $z=\bot_c+_{\bot_a} x$ and $z'=\bot_d+_{\bot_b} x$ in $\X$.
+It suffices to obtain a natural isomorphism between the two objects $z$ and $z'$ in $\X$.
 This pushout square:
@@
 which exhibits $d+_b U(x)$ as a pushout of the same span in $\A$.
-The resulting natural isomorphism $\kappa$ between $c+_a U(x)$ and $d+_b U(x)$ then extends to a natural isomorphism between $z=\bot_c +_{\bot_a} x$ and $z'=\bot_d +_{\bot_b} x$ in $\X$:
+The resulting natural isomorphism $\kappa$ between $c+_a U(x)$ and $d+_b U(x)$ then extends to a natural isomorphism between $z=(c+_a U(x),q)$ and $z'=(d+_b U(x),q')$ in $\X$:
 \[
@@
 \path[->,font=\scriptsize,>=angle 90]
-(A) edge node[fill=white]{$x$} (A1)
-(A) edge node[fill=white]{$x$} (B1)
+(A) edge node[fill=white]{$p$} (A1)
+(A) edge node[fill=white]{$p$} (B1)
 
@@
 \]
-and consequently a natural isomorphism between our two objects of $(\A/U)_c$, showing that $U_1$ satisfies the Beck--Chevalley condition.
+and consequently a natural isomorphism between our two objects of $(\A/U)_c$, showing that $\Phi$ satisfies the Beck--Chevalley condition.
 \end{proof}
@@
 We construct a strong monoidal functor $G \colon (\A/U) \to (\A'/U')$ between the monoidal comma categories $(\A/U)$ and $(\A'/U')$ that will make the induced square commute.
-Such a commutative square is a morphism in the 2-category $\mathbf{FMF}$ of monoidal bifibrations satisfying the Beck-Chevalley condition which then by a 2-functor $\mathbf{Fr} \colon \mathbf{FMF} \to \mathbf{FDbl}$ due to Shulman \cite[Theorem 14.11]{Shulman2008} will yield a map $$\mathbf{Fr}(G,H) \colon \mathbf{Fr}(\Phi) \to \mathbf{Fr}(\Phi')$$between the fibrant symmetric monoidal double categories $\mathbf{Fr}(\Phi)=F\lCsp$ and $\mathbf{Fr}(\Phi')= F'\lCsp$.
+Such a commutative square is a morphism in the 2-category $\mathbf{FMF}$ of monoidal bifibrations satisfying the Beck-Chevalley condition which then, by a 2-functor $\mathbb{F}\mathbf{r} \colon \mathbf{FMF} \to \mathbf{FDbl}$ due to Shulman \cite[Theorem 14.11]{Shulman2008}, will yield a map $$\mathbb{F}\mathbf{r}(G,H) \colon \mathbb{F}\mathbf{r}(\Phi) \to \mathbb{F}\mathbf{r}(\Phi')$$between the fibrant symmetric monoidal double categories $\mathbb{F}\mathbf{r}(\Phi)=F\lCsp$ and $\mathbb{F}\mathbf{r}(\Phi')= F'\lCsp$.
 
@@
 \end{enumerate}
-The tensor product of two objects $(a_1,x_1,a_1 \to U(x_1))$ and $(a_2,x_2,a_2 \to U(x_2))$ is given by $$(a_1,x_1,a_1 \to U(x_1)) \otimes (a_2,x_2,a_2 \to U(x_2)) = (a_1+a_2,x_1+x_2,a_1+a_2 \to U(x_1+x_2)).$$The monoidal unit of $(\A/U)$ is given by $(0_\A,0_\X,0_\A \to U(0_\X))$.
+The tensor product of two objects $(a_1,x_1,a_1 \to U(x_1))$ and $(a_2,x_2,a_2 \to U(x_2))$ is given by $$(a_1,x_1,a_1 \to U(x_1)) \otimes (a_2,x_2,a_2 \to U(x_2)) = (a_1+a_2,x_1+x_2,a_1+a_2 \to U(x_1 \otimes x_2)).$$The monoidal unit of $(\A/U)$ is given by $(0_\A,0_\X,0_\A \to U(0_\X))$.
 Those of $(\A'/U')$ are analogous.
@@
 \begin{enumerate}
-\item{given $(a,x,a \to U(x))$ in $(\A/U)$, $$G(a,x,a \to U(x)) = (H(a),\theta_m E(x) \phi,H(a) \to U'(\theta_m E(x) \phi))$$where if $1 \xrightarrow{x} F(m)$, then $U(x)=m$ and $\theta_m E(x) \phi$ is given by
-$$1 \xrightarrow{\phi} E(1) \xrightarrow{E(x)} E(F(m)) \xrightarrow{\theta_m} F'(H(m))$$
-so that $U'(\theta_m E(x) \phi)=H(m)$, }
+\item{given $(a,x,a \to U(x))$ in $(\A/U)$ where $x=(m,p) \in \A \times F(m)$, $$G(a,x,a \to U(x)) = (H(a),\theta_m E(p) \phi,H(a) \to U'(\theta_m E(p) \phi))$$ where $\theta_m E(p) \phi$ is given by 
+$$1 \xrightarrow{\phi} E(1) \xrightarrow{E(p)} E(F(m)) \xrightarrow{\theta_m} F'(H(m))$$
+so that $U'(\theta_m E(p) \phi)=H(m)$, }
 \item{given a pair of morphisms $(f,\tau)$ that make the following square commute:
@@
 \node (B) at (3,0) {$H(b)$};
-\node (C) at (0,-1) {$U'(\theta_m E(x) \phi)$};
-\node (D) at (3,-1) {$U'(\theta_n E(y) \phi))$};
+\node (C) at (0,-1) {$U'(\theta_m E(p) \phi)$};
+\node (D) at (3,-1) {$U'(\theta_n E(q) \phi))$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (A) edge node [above] {$\phi$} (L)
-(G) edge node [above] {$x$} (H)
-(G) edge node [below] {$y$} (I)
+(G) edge node [above] {$p$} (H)
+(G) edge node [below] {$q$} (I)
 (H) edge node [right] {$F(h)$} (I)
@@
 (E) edge node [right] {$F'(H(h))$} (F)
-(L) edge node[above]{$E(x)$} (B)
-(L) edge node[below]{$E(y)$} (D)
+(L) edge node[above]{$E(p)$} (B)
+(L) edge node[below]{$E(q)$} (D)
 (B) edge node[right]{$E(F(h))$} (D);
@@
 \end{enumerate}
-The laxator is given by the following natural isomorphism between $\theta_m E(x) \phi + \theta_n E(y) \phi$ and $\theta_{m+n} E(x+y) \phi$:
+The laxator is given by the following natural isomorphism between $\theta_m E(p) \phi \times \theta_n E(q) \phi$ and $\theta_{m+n} E(p \times q) \phi$:
 \[
@@
 \hspace{-.6in}
-\node () at (3,-0.5) {$\scriptscriptstyle{\stackrel{E_{x_1,x_2}} \cong}$};
+\node () at (3,-0.5) {$\scriptscriptstyle{\stackrel{E_{p,q}} \cong}$};
 \node () at (1.25,-0.5) {$\scriptscriptstyle{\stackrel{\lambda} \cong}$};
@@
 (I) edge node [above] {$\theta_{m+n}$} (J)
-(B) edge node [above] {$E(x) \times E(y)$} (E)
-(D) edge node [above] {$E(x \times y)$} (F)
+(B) edge node [above] {$E(p) \times E(q)$} (E)
+(D) edge node [above] {$E(p \times q)$} (F)
 (E) edge node [right] {$E_{F(m),F(n)}$} (F)
@@
 (A1) edge node [above] {$\scriptscriptstyle{E(\phi_0)}$} (A2)
-(A2) edge node [above] {$\scriptscriptstyle{E(F(!_{0_\A}))}$} (A3)
+(A2) edge node [below] {$\scriptscriptstyle{E(F(!_{0_\A}))}$} (A3)
 (A3) edge node [below] {$\scriptscriptstyle{\theta_{0_\A}}$} (A4)
@@
 
-The proof is analogous to the proof of \cref{thm:decorated_cospans_1} in that we apply \cref{lem:shulman} to the Beck-Chevalley monoidal bifibration $U_2 \colon (L/\X) \to \A$ which we now define.
+The proof is analogous to the proof of \cref{thm:decorated_cospans_1} in that we apply \cref{lem:shulman} to the Beck-Chevalley symmetric monoidal bifibration $\Psi \colon (L/\X) \to \A$ which we now define.
 Let $(L/\X)$ be the comma category in which:
@@
 \end{enumerate}
-The functor $U_2$ is defined on objects by $U_2(a,x,L(a) \xrightarrow{I} x)=a$ and on morphisms by $U_2(f,\alpha)=f$.
+The functor $\Psi$ is defined on objects by $\Psi(a,x,L(a) \xrightarrow{I} x)=a$ and on morphisms by $\Psi(f,\alpha)=f$.
 The monoidal structure of $(L/\X)$ is similar to the monoidal structure of $(\A/U)$ of \cref{thm:decorated_cospans_1} in that the tensor product of two objects $(a_1,x_1,L(a_1) \xrightarrow{I_1} x_1)$ and $(a_2,x_2,L(a_2) \xrightarrow{I_2} x_2)$ is given by
@@
 where again the natural isomorphism $L(a_1)+L(a_2) \cong L(a_1+a_2)$ is implicit.
-The monoidal unit is ${(0_\A,0_\X,{L(0_\A) \to 0_\X})}$, and it is clear that $U_2$ is a strict monoidal functor using this tensor product.
-
-The functor $U_2$ is both a fibration and an opfibration. Given a morphism $f \colon a \to b$ in $\A$ with ${(b,x,L(b) \xrightarrow{I} x)}$ over $b$ in $\X$, the cartesian lifting of $f$ is given by
+The monoidal unit is ${(0_\A,0_\X,{L(0_\A) \to 0_\X})}$, and it is clear that $\Psi$ is a strict monoidal functor using this tensor product.
+
+The functor $\Psi$ is both a fibration and an opfibration. Given a morphism $f \colon a \to b$ in $\A$ with ${(b,x,L(b) \xrightarrow{I} x)}$ in $\X$ over $b$, the cartesian lifting of $f$ is given by
 $$(f,\id_x) \colon (a,x,L(a) \xrightarrow{I \circ L(f)} x) \to (b,x,L(b) \xrightarrow{I} x).$$
-With $(a,x,L(a) \xrightarrow{I} x)$ over $a$ in $\X$, the cocartesian lifting of $f$ is given by
+With $(a,x,L(a) \xrightarrow{I} x)$ in $\X$ over $a$, the cocartesian lifting of $f$ is given by
 $$(f,\kappa) \colon (a,x,L(a) \xrightarrow{I} x) \to (b,x+_{L(a)} L(b),L(b) \xrightarrow{\theta} x+_{L(a)} L(b))$$
@@
 
-Lastly, we show that $U_2 \colon (L/ \X) \to \A$ satisfies the Beck-Chevalley condition. Given a pushout square in $\A$:
+Lastly, we show that $\Psi \colon (L/ \X) \to \A$ satisfies the Beck-Chevalley condition. Given a pushout square in $\A$:
 \[
@@
 which exhibits $L(d)+_{L(b)} x$ also as a colimit of the same span in $\X$, and hence the desired natural isomorphism between our two objects of $(L /\X)_c$.
-Thus $U_2$ satisfies the Beck-Chevalley condition.
+Thus $\Psi$ satisfies the Beck-Chevalley condition.
 \end{proof}
@@
 {\textbf NEW PROOF HERE.}
-To show that the symmetric monoidal double categories $F\lCsp$ and $_L \lCsp(\inta F)$ of Theorems \ref{thm:decorated_cospans_2} and \ref{thm:SC} are isomorphic, we make use of a result of Shulman \cite[Theorem~14.11]{Shulman2010} which states that there exists a 2-functor $\mathbf{Fr} \colon \mathbf{FMF} \to \mathbf{FDbl}$.
+To show that the symmetric monoidal double categories $F\lCsp$ and $_L \lCsp(\inta F)$ of Theorems \ref{thm:decorated_cospans_2} and \ref{thm:SC} are isomorphic, we make use of a result of Shulman \cite[Theorem~14.11]{Shulman2010} which states that there exists a 2-functor $\mathbb{F}\mathbf{r} \colon \mathbf{FMF} \to \mathbf{FDbl}$.
 Here, $\mathbf{FMF}$ is the 2-category consisting of
@@
 (A) edge node[left]{$\Phi$} (C)
-(B) edge node[right]{$\Phi$} (D)
+(B) edge node[right]{$\Phi'$} (D)
 (C) edge node[above]{$F_2$} (D);
@@
 and such that the identity $\Phi' F_1 = F_2 \Phi$ is a monoidal transformation.
-The two monoidal fibrations in question are the functors $U_1$ and $U_2$ of Theorems \ref{thm:decorated_cospans_2} and \ref{thm:SC}, respectively, which share $\A$ as a common base, and thus we only need a single strong monoidal functor $F \colon (\A/U) \to (L/\X)$ making the following diagram commute:
+The two monoidal fibrations in question are the functors $\Phi$ and $\Psi$ of Theorems \ref{thm:decorated_cospans_2} and \ref{thm:SC}, respectively, which share $\A$ as a common base, and thus we only need a single strong monoidal functor $F \colon (\A/U) \to (L/\X)$ making the following diagram commute:
 \[
@@
 \node (A) at (0,0) {$(\A/U)$};
-\node (B) at (2,0) {$(L/ \inta F)$};
+\node (B) at (2,0) {$(L/ \X)$};
 \node (C) at (1,-1.5) {$\A$};
@@
 %(B) edge [bend left] node[above]{$$} (A)
-(A) edge node[left]{$U_1$} (C)
-(B) edge node[right]{$U_2$} (C);
+(A) edge node[left]{$\Phi$} (C)
+(B) edge node[right]{$\Psi$} (C);
 %(C) edge [bend left] node[above]{$G_1$} (C)
@@
 \]
-with $U_2 F=U_1$ a monoidal transformation. The functor $F \colon (\A/U) \to (L/\inta F)$ is expressed by the natural isomorphism of an adjunction, namely:
+with $\Psi F=\Phi$ a monoidal transformation. The functor $F \colon (\A/U) \to (L/\X)$ is expressed by the natural isomorphism of an adjunction, namely:
 $$F(a,x,a \to U(x))=(a,x,L(a) \to x)$$
 and is the identity on pairs of morphisms making the required squares commute.
-It is clear that $F$ is strong monoidal via component-wise binary coproducts which are preserved by both $L$ and $U$, and that the identity $U_2 F=U_1$ is a monoidal transformation.
-As $F$ is an isomorphism, we obtain an isomorphism $$\mathbf{Fr}(F) \colon \mathbf{Fr}(U_1) \to \mathbf{Fr}(U_2)$$ between the two symmetric monoidal double categories $\mathbb{F}\mathbf{r}(U_1)=F\lCsp$ and $\mathbf{F}\mathbf{r}(U_2)= _L \lCsp(\inta F)$ of Theorems \ref{thm:decorated_cospans_2} and \ref{thm:SC}, respectively.
+It is clear that $F$ is strong monoidal via component-wise binary coproducts which are preserved by both $L$ and $U$, and that the identity $\Psi F=\Phi$ is a monoidal transformation.
+As $F$ is an isomorphism, we obtain an isomorphism $$\mathbb{F}\mathbf{r}(F) \colon \mathbb{F}\mathbf{r}(\Phi) \to \mathbb{F}\mathbf{r}(\Psi)$$ between the two symmetric monoidal double categories $\mathbb{F}\mathbf{r}(\Phi)=F\lCsp$ and $\mathbb{F}\mathbf{r}(\Psi)= _L \lCsp(\inta F)$ of Theorems \ref{thm:decorated_cospans_2} and \ref{thm:SC}, respectively.
 \end{proof}

### 2021-04-19 cospans_new.tex
edited Kenny's proof of Theorem 2.1 up to the material in red

@@
 
-In what follows, we define a \define{cocartesian monoidal category} $(\A,+)$ to be a symmetric
-monoidal category where the monoidal structure is given by chosen binary coproducts, with a chosen initial object serving as the unit for the monoidal structure.
-Any category with finite coproducts can be made into a cocartesian monoidal category by arbitrarily choosing finite coproduct and a unit object.
-
-%In all that follows, when we say a category `has finite colimits' we mean it is equipped with a choice of colimit for every finite diagram.
+In all that follows, when we say a category `has finite colimits' we mean it is equipped with a choice of colimit for every finite diagram.
 Thus, if $\A$ has coproducts it gives a cocartesian monoidal category $(\A,+)$: that is, a symmetric monoidal category where the monoidal structure is given by the chosen binary coproducts and initial object.
 However, when we say a functor `preserves finite colimits', it need only do this up to canonical isomorphism, unless otherwise specified.
-MAY NEED THIS LATER, BUT NOT HERE!!!
 
 \begin{thm}\label{thm:decorated_cospans_1}
-Let $(\A,+)$ be cocartesian monoidal and $F \maps (\A,+) \to (\Cat,\times)$ a lax monoidal pseudofunctor. Then there exists a double category $F\lCsp$ in which
+Let $\A$ be a category with finite colimits and $F \maps (\A,+) \to (\Cat,\times)$ a lax monoidal pseudofunctor. Then there exists a double category $F\lCsp$ in which
 \begin{itemize}
@@
 
-We prove both these theorems using the work of Shulman \cite{Shulman2008}, which we recall here.   First we need a few concepts.   Opfibrations are recalled in \cref{subsec:fibrations}, 
-and fibrations are defined dually, with a functor $\Phi \maps \C \to \A$ being a fibration if and only
-if $\Phi\op \maps \C\op \to \A\op$ is an opfibration.
+We prove both these theorems using the work of Shulman \cite{Shulman2008}, which we recall here.
+First we need a few concepts.
+Opfibrations are recalled in \cref{subsec:fibrations}, and fibrations are defined dually, with a functor $\Phi \maps \C \to \A$ being a fibration if and only if $\Phi\op \maps \C\op \to \A\op$ is an opfibration.
 A functor $\Phi \maps \C \to \A$ is a \define{bifibration} if it is both a fibration and an opfibration.
-If $\C$ and $\A$ are monoidal categories, a \define{monoidal} bifibration $\Phi \colon \C \to \A$ is a bifibration that is also a strict monoidal functor.
-Similarly, if $\C$ and $\A$ are symmetric monoidal, a \define{symmetric monoidal} bifibration is a bifibration $\Phi \colon \C \to \A$ that is a symmetric strict monoidal functor.
+If $\C$ and $\A$ are monoidal categories, a \define{monoidal} bifibration $\Phi \maps \C \to \A$ is a bifibration that is also a strict monoidal functor.
+Similarly, if $\C$ and $\A$ are symmetric monoidal, a \define{symmetric monoidal} bifibration is a bifibration $\Phi \maps \C \to \A$ that is a symmetric strict monoidal functor.
 
@@
 \]
-the following square commutes up to a specified natural transformation, built
+the following square commutes up to a specified natural transformation:
 \[
@@
 \]
+where $\theta$ is built as a composite involving the unit of the adjunction between
+$g_!$ and $g^\ast$ and the counit of the adjunction between $k_!$ and $k^\ast$:
+\[    k_! h^\ast \To k_! h^\ast g^\ast g_! = k_! k^\ast f^\ast g^! \To f^\ast g_! .\] 
 If $\theta$ is a natural isomorphism whenever the original square in $\A$ is
-a pushout, we say $\Phi$ is \define{Beck--Chevalley}.  (Shulman says `strongly co-Beck--Chevalley'.)
+a pushout, we shall say $\Phi$ is \define{Beck--Chevalley}.  (Shulman says `strongly co-Beck--Chevalley'.)
 
@@
 
+We  prove Theorems \ref{thm:decorated_cospans_1} and \ref{thm:decorated_cospans_2} by applying this lemma to a particular monoidal bifibration.
+To get our hands on this starting from our lax monoidal pseudofunctor $F \maps (A,+) \to (\Cat,\times)$, we need a monoidal version of the Grothendieck construction \cite{MV}.
+We recall the Grothendieck construction in \ref{subsec:fibrations}; briefly,
+this gives a bijection between pseudofunctors $F \maps \A \to \Cat$ and opfibrations
+$U \maps \inta F \to \A$.   Moeller and the third author \cite{MV} showed that
+similarly, given a (symmetric) monoidal category $\A$, there is a bijection between 
+\begin{itemize}
+\item \define{(symmetric) monoidal opindexed categories}: (symmetric) lax monoidal pseudofunctors \hfill \break $F\maps (\A, \otimes_A) \to (\Cat, \times)$
+\end{itemize}
+and 
+\begin{itemize}
+\item \define{(symmetric) monoidal opfibrations}: opfibrations $U \maps \X \to \A$ where $\X$ and $\A$ are (symmetric) monoidal, $U$ is (symmetric) strict monoidal, and $\otimes_\X$ preserves cocartesian liftings.
+\end{itemize}  
+If the monoidal structure on $\A$ is in fact cocartesian, as it is in our case, there is a further correspondence between these structures and ordinary pseudofunctors $F\maps \A \to \MonCat$ (or to $\SMC$ in the symmetric case).
+
+In fact, all these correspondences lift to 2-equivalences between appropriate 2-categories:
+
+\begin{lem}
+\label{lem:MonGroth}
+There is a 2-equivalence between the 2-categories of monoidal opfibrations and monoidal opindexed categories, and if the base is cocartesian monoidal, there is a 2-equivalence between these and pseudofunctors into $\MonCat$.
+Similarly there is a 2-equivalence between symmetric monoidal opfibrations and symmetric monoidal opindexed categories, and if the base is cocartesian monoidal, also a 2-equivalence between these and pseudofunctors into $\SMC$.
+\end{lem}
+
+\begin{proof}
+This was shown by Moeller and the third author \cite[Theorems~3.13 \& 4.2]{MV}. In summary, for a cocartesian base $\A$ we have correspondences
+\begin{gather}
+\textrm{lax monoidal pseudofunctors }F\maps(\A,+)\to(\Cat,\times) \notag\\
+\Updownarrow \notag\\
+\textrm{monoidal opfibrations }U\maps(\X,\otimes_\X)\to(\A,+) \notag\\
+\Updownarrow \notag\\
+\textrm{pseudofunctors } F \maps \A\to \MonCat \notag
+\end{gather}
+The second equivalence was observed earlier by Shulman \cite{Shulman2008}.
+Moreover, symmetric lax monoidal pseudofunctors correspond to symmetric monoidal opfibrations, and those to pseudofunctors into $\SMC$.
+
+In more detail, if $(\phi,\phi_0)$ is the lax monoidal structure of the pseudofunctor $F$ as recalled in \cref{subsec:bicats}, the induced monoidal structure on the total Grothendieck category $\X=\inta F$ (\cref{def:GrothCat}) is given by
+\begin{equation}\label{eq:explicitstructure2}
+\Big(a,x\in F(a)\Big)\ot_{\X}\Big(b,y\in F(b)\Big)=\Big(a+b,\phi_{a,b}(x,y)\in F(a+b)\Big), \qquad I_{\X}=\Big(0_A,\phi_0\Big)
+\end{equation}
+If $F$ is a symmetric lax monoidal pseudofunctor, the induced monoidal structure in $\inta F$ is symmetric via
+$$\left(\beta_{a,b},(u_{a,b})_{x,y}\right)\maps \left(a+b,\phi_{a,b}(x,y)\right)\simrightarrow\left(b+a,\phi_{b,a}(y,x)\right)$$ where $\beta$ is the canonical symmetry for $\A$ and $u$ is the natural isomorphism of \cref{eq:braidedpseudofun}.
+
+Moreover, each fiber $\X_a=F(a)$ obtains a monoidal structure via 
+\begin{equation}\label{eq:explicitstructure1}
+\otimes_a\maps F(a)\times F(a)\xrightarrow{\phi_{a,a}}F(a+a)\xrightarrow{F(\nabla)}F(a),\quad
+I_a\maps\one\xrightarrow{\phi_0}F(0)\xrightarrow{F(!_a)}F(a)
+\end{equation}
+where $\nabla$ is the fold map, which is symmetric when $F$ is again via the components of $u_{a,a}$. Also, each reindexing functor $f_!=F(f)$ obtains a strong monoidal structure with
+\begin{equation}\label{eq:strongreindexing}
+\begin{tikzcd}[row sep=.35in]
+ F(a)\times F(a)\ar[r,"\phi_{a,a}"]\ar[d,"F(f)\times F(f)"']\ar[dr,phantom,"{\stackrel[\cref{eq:pseudonaturality}]{\phi_{f,f}}{\cong}}"] & 
+ F(a+a)\ar[r,"F(\nabla)"]\ar[d,"F(f+f)"description]\ar[dr,phantom,"\cong"] & F(a)\ar[d,"Ff"] \\
+ F(b)\times F(b)\ar[r,"\phi_{b,b}"'] & F(b+b)\ar[r,"F(\nabla)"'] & F(b)
+\end{tikzcd}
+\end{equation}
+\end{proof}
+
 \begin{proof}[Proof of \cref{thm:decorated_cospans_1}] 
-We apply \cref{lem:shulman} to a bifibration $\Phi \maps (\A/U) \to \A$ which we now define.
-The functor $U \colon \inta F \to \A$ is the associated monoidal opfibration of the symmetric lax monoidal pseudofunctor $F \colon \A \to \Cat$.
-Let $(\A/U)$ be the comma category in which:
-\begin{enumerate}
-\item{an object is a triple $(a,x,a \xrightarrow{i} U(x))$ with $a \in \A$ and $x=(a',p) \in \A \times F(a')$, and}
-\item{a morphism from $(a,x,a \xrightarrow{i} U(x))$ to $(b,x',b \xrightarrow{i'} U(x'))$ is a pair of morphisms $f \colon a \to b$ and $\alpha \colon x \to x'$ such that the following square commutes:
+To obtain the desired double category we apply \cref{lem:shulman} to a bifibration $\Phi \maps \A/U \to \A$ which we now define.
+Let $U \maps \inta F \to \A$ be the monoidal opfibration associated to the lax monoidal pseudofunctor $F \maps \A \to \Cat$.
+Thus:
+\begin{itemize}
+\item an object of $\inta F$ is a pair $(b,p)$ where $b \in \A$ and $p \in F(A)$;
+\item a morphism in $\inta F$ from $(b,p)$ to $(b',p')$ is a pair $(g,\zeta)$
+where $g \maps b \to b'$ is a morphism in $\A$ and $\zeta \maps F(f)(p) \to p'$ is
+a morphism in $F(b')$.
+\end{itemize}
+The functor $U$ maps objects and morphisms to their first component.   We thus obtain an explicit description of the comma category $\A/U$:
+\begin{itemize}
+\item an object of $\A/U$ is a triple $(a,x,a \xrightarrow{i} U(x))$ with $a \in \A$ and $x=(b,p) \in \inta F$;
+\item a morphism in $\A/U$ from $(a,x,a \xrightarrow{i} U(x))$ to $(a',x',a' \xrightarrow{i'} U(x'))$ is a pair $(f,\theta)$ where $f \maps a \to a'$ is a morphism in $\A$ and $\theta \maps x \to x'$ is a morphism in $\inta F$ such that the following square commutes:
 \[
@@
 \node (A) at (0,0) {$a$};
-\node (B) at (1.5,0) {$b$};
+\node (B) at (1.5,0) {$a'$};
 \node (C) at (0,-1) {$U(x)$};
-\node (D) at (1.5,-1) {$U(x')$};
+\node (D) at (1.5,-1) {$U(x')$.};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (B) edge node[right]{$i'$} (D)
-(C) edge node[below]{$U(\alpha)$} (D);
-\end{tikzpicture}
-\]}
-\end{enumerate}
-The functor $\Phi$ is defined on objects by $\Phi(a,x,a \xrightarrow{i} U(x))=a$ and on morphisms by $\Phi(f,\alpha)=f$.
-We have a monoidal structure on the comma category $(\A/U)$ where the tensor product of two objects $(a_1,x_1,a_1 \xrightarrow{i_1} U(x_1))$ and $(a_2,x_2,a_2 \xrightarrow{i_2} U(x_2))$ is given by
+(C) edge node[below]{$U(\theta)$} (D);
+\end{tikzpicture}
+\]
+\end{itemize}
+The functor $\Phi \maps \A/U \to \A$ is defined on objects by $\Phi(a,x,a \xrightarrow{i} U(x))=a$ and on morphisms by $\Phi(f,\alpha)=f$.
+We have a monoidal structure on $\A/U$ where the tensor product of two objects $(a_1,x_1,a_1 \xrightarrow{i_1} U(x_1))$ and $(a_2,x_2,a_2 \xrightarrow{i_2} U(x_2))$ is given by
 \[  (a_1,x_1,a_1 \xrightarrow{i_1} U(x_1)) \otimes (a_2,x_2,a_2 \xrightarrow{i_2} U(x_2)) = (a_1+a_2,x_1 \otimes x_2,a_1+a_2 \xrightarrow{i_1+i_2} U(x_1 \otimes x_2)) \]
@@
 The monoidal unit is given by $(0_\A,0_\X,0_\A \to U(0_\X))$.
-It is easy to see that the functor $\Phi$ can be made into a strict monoidal functor using this tensor product.
-
-The functor $\Phi$ is a fibration where given a morphism $f \maps a \to b$ in $\A$ with $(b,y,b \xrightarrow{i} U(y))$ over $b$ in $\int F$, the cartesian lifting of $f$ is given by 
-\[ (f,\id) \maps (a,y,a \xrightarrow{i \circ f} U(y)) \to (b,y,b \xrightarrow{i} U(y)). \]
-Denoting the cartesian lifting of a morphism $f$ by $\textnormal{cart}(f)$, the tensor product of $(\A/U)$ strictly preserves cartesian liftings in the sense that $\textnormal{cart}(f_1) \otimes \textnormal{cart}(f_2)=\textnormal{cart}(f_1+f_2)$.
-
-The functor $\Phi$ is also an opfibration where given a morphism $f \maps a \to b$ with $(a,x,a \xrightarrow{i} U(x))$ over $a$, the cocartesian lifting of $f$ is given by 
-\[ (f,\theta) \maps (a,x,a \to U(x)) \to (b,z,b \xrightarrow{\phi} U(z)) \]
-where $\theta$ and $\phi$ arise from the following pushout square in $\A$:
+It is easy to see that the functor $\Phi$ is a strict monoidal using this tensor product.
+
+One can easily check that $\Phi$ is a fibration.  Given a morphism $f \maps a \to b$ in $\A$ and an object $(b,y,b \xrightarrow{i} U(y)) \in \A/U$ over $b$, a cartesian lifting of $f$ is given by 
+\[ (f,\id) \maps (a,y,a \xrightarrow{i \circ f} U(y)) \, \to \, (b,y,b \xrightarrow{i} U(y)). \]
+Denoting this cartesian lifting by $\textnormal{cart}(f)$, the tensor product of $\A/U$ strictly preserves such cartesian liftings in the sense that $\textnormal{cart}(f_1) \otimes \textnormal{cart}(f_2)=\textnormal{cart}(f_1+f_2)$.
+
+One can also check that the functor $\Phi$ is also opfibration, but this takes a bit more work.
+Given a morphism $f \maps a \to a'$ in $\A$ and an object $(a,x,a \xrightarrow{i} U(x)) \in \A/U$ over $a$, we shall show that a cocartesian lifting of $f$ is given by
+\[ (f,\theta) \maps (a,x,a \xrightarrow{i} U(x)) \, \to \, (a',x', a' \xrightarrow{i'} U(x')). \]
+Here $i'$ arises from the following pushout square in $\A$:
 \[
@@
 \node (A) at (0,0) {$a$};
-\node (B) at (1.5,0) {$b$};
+\node (B) at (2,0) {$a'$};
 \node (C) at (0,-1) {$U(x)$};
-\node (D) at (1.5,-1) {$U(x)+_a b$};
+\node (D) at (2,-1) {$U(x)+_a a'$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (A) edge node[left]{$i$} (C)
-(B) edge [dashed] node[right]{$\phi$} (D)
-(C) edge [dashed] node[above]{$\theta$} (D);
-\end{tikzpicture}
-\]
-and the object $z$ arises from the cocartesian lifting of $\theta$ through $U$:
+(B) edge [dashed] node[right]{$i'$} (D)
+(C) edge [dashed] node[below]{$g$} (D);
+\end{tikzpicture}
+\]
+The object $x' \in \inta F$ is defined as follows.  Recall that $x \in \inta F$ is a
+pair $(b,p)$ with $b\in \A$ and $p \in F(b)$, and note that $U(x) = b$.   Define 
+$x'$ to be the pair $(b',p')$ where $b' = U(x)+_a a'$ is the pushout in the above
+diagram and $p' = F(g)(p)$.  Then $U(x') = b'$ so we have 
+$i' \maps a' \to U(x')$ as desired.  Finally, we define $\theta \maps x \to x'$ to be 
+the morphism in $\inta F$ given by the pair $(g,\id)$ where $g \maps b \to b'$ is
+given in the above diagram and $\id \maps F(f)(p) \to p'$ is the identity.
+
+{\john To show that $(f,\theta)$ is a cocartesian lifting of $f$, suppose...
+Then use this picture somehow:}
 \[
@@
 \node (B) at (2.5,0) {$c$};
-\node (C) at (1.5,1) {$b$};
+\node (C) at (1.5,1) {$a'$};
 \node (D) at (0,-2) {$U(x)$};
 \node (E) at (2.5,-2) {$U(y)$};
-\node (F) at (1.5,-1) {$U(z) = U(x)+_a b$};
+\node (F) at (1.5,-1) {$U(x') = U(x)+_a a'$};
 \path[->,font=\scriptsize,>=angle 90]
 (D) edge node [above] {$\theta$} (F)
-(F) edge [dashed] node [left] {$\exists ! \psi$} (E)
+(F) edge [dashed] node [right] {$\exists ! \psi$} (E)
 (D) edge node [above] {$U(g')$} (E)
 (A) edge node [left] {$i$} (D)
-(C) edge [dashed] node [right,near end] {$\phi$} (F)
+(C) edge node [right,near end] {$i'$} (F)
 (B) edge node {$$} (E)
@@
 \]
+
 Denoting the cocartesian lifting of a morphism $f$ by $\textnormal{cocart}(f)$, we have that $\textnormal{cocart}(f_1) \otimes \textnormal{cocart}(f_2) \cong \textnormal{cocart}(f_1+f_2)$ by the universal map between two colimits of the same diagram:
@@
 \node (A) at (0,0) {$(\A/U)_a$};
-\node (B) at (1.5,0) {$(\A/U)_b$};
+\node (B) at (1.5,0) {$\A/U)_b$};
 \node (C) at (0,-1) {$(\A/U)_c$};
@@
 Let $(b,x,b \xrightarrow{i} U(x))$ be an object of $(\A/U)_b$ where $x=(b',p) \in \A \times F(b')$ so that $U(x)=b'$.
-Going left, we precompose with $h \colon a \to b$ to obtain the object $(a,x,a \xrightarrow{i \circ h} U(x))$ of $(\A/U)_a$.
+Going left, we precompose with $h \maps a \to b$ to obtain the object $(a,x,a \xrightarrow{i \circ h} U(x))$ of $(\A/U)_a$.
 Then going down, we push forward along $k$:
@@
 %{\john Need to refer to a proposition where we show $U$ preserves pushouts strictly.}
- For the other route, first going down, we push the object $(b,x,b \xrightarrow{i} U(x))$ forward along $g \colon b \to d$ by taking the following pushout:
+ For the other route, first going down, we push the object $(b,x,b \xrightarrow{i} U(x))$ forward along $g \maps b \to d$ by taking the following pushout:
 \[
@@
 \[ 1 \xrightarrow{p} F(U(x)) \xrightarrow{F(\zeta)} F(0+_0 U(x)) \xrightarrow{F(!_d +_{!_b} 1)} F(d+_b U(x)). \]
-We then precompose with $f \colon c \to d$ to obtain the object $(c,z',c \xrightarrow{\theta \circ f} U(z'))$ of $(\A/U)_c$.
+We then precompose with $f \maps c \to d$ to obtain the object $(c,z',c \xrightarrow{\theta \circ f} U(z'))$ of $(\A/U)_c$.
 
@@
 
-From the symmetric lax monoidal pseudofunctor $F \colon \A \to \Cat$, we can obtain a Beck-Chevalley symmetric monoidal opfibration $\Phi \colon (\A/U) \to \A$ as in \cref{thm:decorated_cospans_1}, where $U \colon \int F \to \A$ is the associated monoidal opfibration of the pseudofunctor $F$.
-We can do the same for the other symmetric lax monoidal pseudofunctor $F' \colon \A' \to \Cat$ to obtain another Beck-Chevalley symmetric monoidal opfibration $\Phi' \colon (\A'/U') \to \A'$.
+From the symmetric lax monoidal pseudofunctor $F \maps \A \to \Cat$, we can obtain a Beck-Chevalley symmetric monoidal opfibration $\Phi \maps (\A/U) \to \A$ as in \cref{thm:decorated_cospans_1}, where $U \maps \int F \to \A$ is the associated monoidal opfibration of the pseudofunctor $F$.
+We can do the same for the other symmetric lax monoidal pseudofunctor $F' \maps \A' \to \Cat$ to obtain another Beck-Chevalley symmetric monoidal opfibration $\Phi' \maps (\A'/U') \to \A'$.
 \[
@@
 \]
-We construct a strong monoidal functor $G \colon (\A/U) \to (\A'/U')$ between the monoidal comma categories $(\A/U)$ and $(\A'/U')$ that will make the induced square commute.
-Such a commutative square is a morphism in the 2-category $\mathbf{FMF}$ of monoidal bifibrations satisfying the Beck-Chevalley condition which then, by a 2-functor $\mathbb{F}\mathbf{r} \colon \mathbf{FMF} \to \mathbf{FDbl}$ due to Shulman \cite[Theorem 14.11]{Shulman2008}, will yield a map $$\mathbb{F}\mathbf{r}(G,H) \colon \mathbb{F}\mathbf{r}(\Phi) \to \mathbb{F}\mathbf{r}(\Phi')$$between the fibrant symmetric monoidal double categories $\mathbb{F}\mathbf{r}(\Phi)=F\lCsp$ and $\mathbb{F}\mathbf{r}(\Phi')= F'\lCsp$.
+We construct a strong monoidal functor $G \maps (\A/U) \to (\A'/U')$ between the monoidal comma categories $(\A/U)$ and $(\A'/U')$ that will make the induced square commute.
+Such a commutative square is a morphism in the 2-category $\mathbf{FMF}$ of monoidal bifibrations satisfying the Beck-Chevalley condition which then, by a 2-functor $\mathbb{F}\mathbf{r} \maps \mathbf{FMF} \to \mathbf{FDbl}$ due to Shulman \cite[Theorem 14.11]{Shulman2008}, will yield a map $$\mathbb{F}\mathbf{r}(G,H) \maps \mathbb{F}\mathbf{r}(\Phi) \to \mathbb{F}\mathbf{r}(\Phi')$$between the fibrant symmetric monoidal double categories $\mathbb{F}\mathbf{r}(\Phi)=F\lCsp$ and $\mathbb{F}\mathbf{r}(\Phi')= F'\lCsp$.
 
@@
 \item{objects as triples $(a,x,a \to U(x))$, and}
-\item{a morphism from $(a,x,a \to U(x))$ to $(b,y,b \to U(y))$ is a pair of morphisms $f \colon a \to b$ and $\tau \colon x \to y$ that make the following square commute:
+\item{a morphism from $(a,x,a \to U(x))$ to $(b,y,b \to U(y))$ is a pair of morphisms $f \maps a \to b$ and $\tau \maps x \to y$ that make the following square commute:
 \[
@@
 
-On objects, the strong monoidal functor $F \colon (\A/U) \to (\A'/U')$ is defined as follows:
+On objects, the strong monoidal functor $F \maps (\A/U) \to (\A'/U')$ is defined as follows:
 \begin{enumerate}
@@
 
-The proof is analogous to the proof of \cref{thm:decorated_cospans_1} in that we apply \cref{lem:shulman} to the Beck-Chevalley symmetric monoidal bifibration $\Psi \colon (L/\X) \to \A$ which we now define.
+The proof is analogous to the proof of \cref{thm:decorated_cospans_1} in that we apply \cref{lem:shulman} to the Beck-Chevalley symmetric monoidal bifibration $\Psi \maps (L/\X) \to \A$ which we now define.
 Let $(L/\X)$ be the comma category in which:
@@
 \item{an object is a triple $(a,x,L(a) \xrightarrow{I} x)$, and}
-\item{a morphism from $(a,x,L(a) \xrightarrow{I} x)$ to $(a',x',L(a') \xrightarrow{I'} x')$ is a pair of morphisms $f \colon a \to a'$ and $\alpha \colon x \to x'$ such that the following square commutes:
+\item{a morphism from $(a,x,L(a) \xrightarrow{I} x)$ to $(a',x',L(a') \xrightarrow{I'} x')$ is a pair of morphisms $f \maps a \to a'$ and $\alpha \maps x \to x'$ such that the following square commutes:
 \[
@@
 
-The functor $\Psi$ is both a fibration and an opfibration. Given a morphism $f \colon a \to b$ in $\A$ with ${(b,x,L(b) \xrightarrow{I} x)}$ in $\X$ over $b$, the cartesian lifting of $f$ is given by
-$$(f,\id_x) \colon (a,x,L(a) \xrightarrow{I \circ L(f)} x) \to (b,x,L(b) \xrightarrow{I} x).$$
+The functor $\Psi$ is both a fibration and an opfibration. Given a morphism $f \maps a \to b$ in $\A$ with ${(b,x,L(b) \xrightarrow{I} x)}$ in $\X$ over $b$, the cartesian lifting of $f$ is given by
+$$(f,\id_x) \maps (a,x,L(a) \xrightarrow{I \circ L(f)} x) \to (b,x,L(b) \xrightarrow{I} x).$$
 With $(a,x,L(a) \xrightarrow{I} x)$ in $\X$ over $a$, the cocartesian lifting of $f$ is given by
-$$(f,\kappa) \colon (a,x,L(a) \xrightarrow{I} x) \to (b,x+_{L(a)} L(b),L(b) \xrightarrow{\theta} x+_{L(a)} L(b))$$
+$$(f,\kappa) \maps (a,x,L(a) \xrightarrow{I} x) \to (b,x+_{L(a)} L(b),L(b) \xrightarrow{\theta} x+_{L(a)} L(b))$$
 where $\kappa$ and $\theta$ are as in the following diagram:
@@
 
-Lastly, we show that $\Psi \colon (L/ \X) \to \A$ satisfies the Beck-Chevalley condition. Given a pushout square in $\A$:
+Lastly, we show that $\Psi \maps (L/ \X) \to \A$ satisfies the Beck-Chevalley condition. Given a pushout square in $\A$:
 \[
@@
 Let $(b,x,L(b) \xrightarrow{I} x)$ be an object of $(L/\X)_b$.
-Going right, we precompose with $L(h) \colon L(a) \to L(b)$ to obtain the object $(a,x,L(a) \xrightarrow{I \circ L(h)} x)$ in $(L/\X)_a$.
-Then, going down, we pushforward along $L(k) \colon L(a) \to L(c)$:
+Going right, we precompose with $L(h) \maps L(a) \to L(b)$ to obtain the object $(a,x,L(a) \xrightarrow{I \circ L(h)} x)$ in $(L/\X)_a$.
+Then, going down, we pushforward along $L(k) \maps L(a) \to L(c)$:
 \[
@@
 to obtain the object $(c,L(c)+_{L(a)} x,L(c) \xrightarrow{\psi} L(c)+_{L(a)} x)$ in $(L/ \X)_c$.
-For the other route, first going down, we pushforward the object $(b,x,L(b) \xrightarrow{I} x)$ along $L(g) \colon L(b) \to L(d)$ by taking the following pushout:
+For the other route, first going down, we pushforward the object $(b,x,L(b) \xrightarrow{I} x)$ along $L(g) \maps L(b) \to L(d)$ by taking the following pushout:
 \[
@@
 which yields the object $(d,L(d)+_{L(b)}x,L(d) \xrightarrow{\theta} L(d)+_{L(b)} x)$ of $(L/\X)_d$.
-We then precompose with $L(f) \colon L(c) \to L(d)$ to obtain the object $(c,L(d)+_{L(b)} x,L(c) \xrightarrow{\theta \circ L(f)} L(d)+_{L(b)} x)$ of $(L/\X)_c$.
+We then precompose with $L(f) \maps L(c) \to L(d)$ to obtain the object $(c,L(d)+_{L(b)} x,L(c) \xrightarrow{\theta \circ L(f)} L(d)+_{L(b)} x)$ of $(L/\X)_c$.
 
@@
 
-In \cite{MV}, the classical Grothendieck construction is generalized to the monoidal setting: given a (symmetric) monoidal category $\A$, there is a bijection between \define{(symmetric) monoidal opindexed categories}, which are (symmetric) lax monoidal pseudofunctors $F\maps (\A, \otimes_A) \to (\Cat, \times)$, and \define{(symmetric) monoidal opfibrations}, which are opfibrations $U \maps \X \to \A$ where $\X$, $\A$ are (symmetric) monoidal, $U$ is (symmetric) strict monoidal, and $\otimes_\X$ preserves cocartesian liftings.
-This bijection sends a monoidal opindexed category $F \maps (\A,\otimes_A) \to (\Cat, \times)$ to the monoidal opfibration $U \maps \inta F \to \A$.
-If the monoidal structure on $\A$ is in fact cocartesian, there is a further correspondence between these structures and ordinary pseudofunctors $F\maps \A \to \MonCat$ (or to $\SMC$ in the symmetric case).
-
-In fact, all these correspondences lift to 2-equivalences between appropriate 2-categories.
-
-\begin{lem}\label{lem:MonGroth}
-There is a 2-equivalence between the 2-categories of monoidal opfibrations and monoidal opindexed categories, and if the base is cocartesian monoidal, there is a 2-equivalence between these and pseudofunctors into $\MonCat$.
-Similarly there is a 2-equivalence between symmetric monoidal opfibrations and symmetric monoidal opindexed categories, and if the base is cocartesian monoidal, also a 2-equivalence between these and pseudofunctors into $\SMC$.
-\end{lem}
-
-\begin{proof}
-This was shown by Moeller and the third author \cite[Theorems~3.13 \& 4.2]{MV}. In summary, for a cocartesian base $\A$ we have correspondences
-\begin{gather}
-\textrm{lax monoidal pseudofunctors }F\maps(\A,+)\to(\Cat,\times) \notag\\
-\Updownarrow \notag\\
-\textrm{monoidal opfibrations }U\maps(\X,\otimes_\X)\to(\A,+) \notag\\
-\Updownarrow \notag\\
-\textrm{pseudofunctors } F \maps \A\to \MonCat \notag
-\end{gather}
-The second equivalence was observed earlier by Shulman \cite{Shulman2008}.
-Moreover, symmetric lax monoidal pseudofunctors correspond to symmetric monoidal opfibrations, and those to pseudofunctors into $\SMC$.
-
-In more detail, if $(\phi,\phi_0)$ is the lax monoidal structure of the pseudofunctor $F$ as recalled in \cref{subsec:bicats}, the induced monoidal structure on the total Grothendieck category $\X=\inta F$ (\cref{def:GrothCat}) is given by
-\begin{equation}\label{eq:explicitstructure2}
-\Big(a,x\in F(a)\Big)\ot_{\X}\Big(b,y\in F(b)\Big)=\Big(a+b,\phi_{a,b}(x,y)\in F(a+b)\Big), \qquad I_{\X}=\Big(0_A,\phi_0\Big)
-\end{equation}
-If $F$ is a symmetric lax monoidal pseudofunctor, the induced monoidal structure in $\inta F$ is symmetric via
-$$\left(\beta_{a,b},(u_{a,b})_{x,y}\right)\maps \left(a+b,\phi_{a,b}(x,y)\right)\simrightarrow\left(b+a,\phi_{b,a}(y,x)\right)$$ where $\beta$ is the canonical symmetry for $\A$ and $u$ is the natural isomorphism of \cref{eq:braidedpseudofun}.
-
-Moreover, each fiber $\X_a=F(a)$ obtains a monoidal structure via 
-\begin{equation}\label{eq:explicitstructure1}
-\otimes_a\maps F(a)\times F(a)\xrightarrow{\phi_{a,a}}F(a+a)\xrightarrow{F(\nabla)}F(a),\quad
-I_a\maps\one\xrightarrow{\phi_0}F(0)\xrightarrow{F(!_a)}F(a)
-\end{equation}
-where $\nabla$ is the fold map, which is symmetric when $F$ is again via the components of $u_{a,a}$. Also, each reindexing functor $f_!=F(f)$ obtains a strong monoidal structure with
-\begin{equation}\label{eq:strongreindexing}
-\begin{tikzcd}[row sep=.35in]
- F(a)\times F(a)\ar[r,"\phi_{a,a}"]\ar[d,"F(f)\times F(f)"']\ar[dr,phantom,"{\stackrel[\cref{eq:pseudonaturality}]{\phi_{f,f}}{\cong}}"] & 
- F(a+a)\ar[r,"F(\nabla)"]\ar[d,"F(f+f)"description]\ar[dr,phantom,"\cong"] & F(a)\ar[d,"Ff"] \\
- F(b)\times F(b)\ar[r,"\phi_{b,b}"'] & F(b+b)\ar[r,"F(\nabla)"'] & F(b)
-\end{tikzcd}
-\end{equation}
-\end{proof}
-
-These 2-equivalences further restrict to the case when the Grothendieck category $(X,\otimes_\X)$ is specifically cocartesian monoidal itself, with coproducts built up from \cref{eq:explicitstructure2}.
+FIX ABOVE PARAGRAPH.
+
+The 2-equivalence of \cref{lem:MonGroth} has an important special case where the Grothendieck category $(X,\otimes_\X)$ is cocartesian monoidal itself, with coproducts built up from \cref{eq:explicitstructure2}.
 In that case, opfibrations $(\X,+) \to (\A,+)$ that strictly preserve coproducts and initial object bijectively correspond to pseudofunctors into the 2-category of cocartesian categories.
@@
 
-Finally, we can further restrict to the setting of opfibrations that also preserve pushouts, and thus all finite colimits, thanks to the following more general result.
+We can further restrict to the case of opfibrations that also preserve pushouts, and thus all finite colimits, thanks to the following more general result.
 
@@
 {\textbf NEW PROOF HERE.}
-To show that the symmetric monoidal double categories $F\lCsp$ and $_L \lCsp(\inta F)$ of Theorems \ref{thm:decorated_cospans_2} and \ref{thm:SC} are isomorphic, we make use of a result of Shulman \cite[Theorem~14.11]{Shulman2010} which states that there exists a 2-functor $\mathbb{F}\mathbf{r} \colon \mathbf{FMF} \to \mathbf{FDbl}$.
+To show that the symmetric monoidal double categories $F\lCsp$ and $_L \lCsp(\inta F)$ of Theorems \ref{thm:decorated_cospans_2} and \ref{thm:SC} are isomorphic, we make use of a result of Shulman \cite[Theorem~14.11]{Shulman2010} which states that there exists a 2-functor $\mathbb{F}\mathbf{r} \maps \mathbf{FMF} \to \mathbf{FDbl}$.
 Here, $\mathbf{FMF}$ is the 2-category consisting of
@@
 and $\mathbf{FDbl}$ is the 2-category of fibrant double categories, double functors and double transformations.
-Given two monoidal bifibrations $\Phi \colon \A \to \mathsf{B}$ and $\Phi' \colon \A' \to \mathsf{B}'$, a \define{strong monoidal morphism of bifibrations} from $\Phi$ to $\Phi'$ consists of a pair of strong monoidal functors $F_1$ and $F_2$ making the following square commute:
+Given two monoidal bifibrations $\Phi \maps \A \to \mathsf{B}$ and $\Phi' \maps \A' \to \mathsf{B}'$, a \define{strong monoidal morphism of bifibrations} from $\Phi$ to $\Phi'$ consists of a pair of strong monoidal functors $F_1$ and $F_2$ making the following square commute:
 \[
@@
 and such that the identity $\Phi' F_1 = F_2 \Phi$ is a monoidal transformation.
-The two monoidal fibrations in question are the functors $\Phi$ and $\Psi$ of Theorems \ref{thm:decorated_cospans_2} and \ref{thm:SC}, respectively, which share $\A$ as a common base, and thus we only need a single strong monoidal functor $F \colon (\A/U) \to (L/\X)$ making the following diagram commute:
+The two monoidal fibrations in question are the functors $\Phi$ and $\Psi$ of Theorems \ref{thm:decorated_cospans_2} and \ref{thm:SC}, respectively, which share $\A$ as a common base, and thus we only need a single strong monoidal functor $F \maps (\A/U) \to (L/\X)$ making the following diagram commute:
 \[
@@
 \]
-with $\Psi F=\Phi$ a monoidal transformation. The functor $F \colon (\A/U) \to (L/\X)$ is expressed by the natural isomorphism of an adjunction, namely:
+with $\Psi F=\Phi$ a monoidal transformation. The functor $F \maps (\A/U) \to (L/\X)$ is expressed by the natural isomorphism of an adjunction, namely:
 $$F(a,x,a \to U(x))=(a,x,L(a) \to x)$$
@@
 It is clear that $F$ is strong monoidal via component-wise binary coproducts which are preserved by both $L$ and $U$, and that the identity $\Psi F=\Phi$ is a monoidal transformation.
-As $F$ is an isomorphism, we obtain an isomorphism $$\mathbb{F}\mathbf{r}(F) \colon \mathbb{F}\mathbf{r}(\Phi) \to \mathbb{F}\mathbf{r}(\Psi)$$ between the two symmetric monoidal double categories $\mathbb{F}\mathbf{r}(\Phi)=F\lCsp$ and $\mathbb{F}\mathbf{r}(\Psi)= _L \lCsp(\inta F)$ of Theorems \ref{thm:decorated_cospans_2} and \ref{thm:SC}, respectively.
+As $F$ is an isomorphism, we obtain an isomorphism $$\mathbb{F}\mathbf{r}(F) \maps \mathbb{F}\mathbf{r}(\Phi) \to \mathbb{F}\mathbf{r}(\Psi)$$ between the two symmetric monoidal double categories $\mathbb{F}\mathbf{r}(\Phi)=F\lCsp$ and $\mathbb{F}\mathbf{r}(\Psi)= _L \lCsp(\inta F)$ of Theorems \ref{thm:decorated_cospans_2} and \ref{thm:SC}, respectively.
 \end{proof}
@@
 \node (U) at (4.5,-1.5) {$\scriptstyle{\bot_{b} \in F(b)}$};
-\node (V) at (4.5,-1.75) {$\scriptstyle{\tau_{\rho_{\hat{f}}} \colon (\bot_b \odot \bot_a) \to \bot_b}$};
+\node (V) at (4.5,-1.75) {$\scriptstyle{\tau_{\rho_{\hat{f}}} \maps (\bot_b \odot \bot_a) \to \bot_b}$};
 \node (K) at (-1.5,-1.5) {$a$};
@@
 \node (N') at (0,-2) {$\scriptstyle{\bot_b \in F(b)}$};
-\node (O') at (0,-2.25) {$\scriptstyle{\tau_{\lambda_{\hat{f}}} \colon (\bot_b \odot \bot_b) \to \bot_b}$};
+\node (O') at (0,-2.25) {$\scriptstyle{\tau_{\lambda_{\hat{f}}} \maps (\bot_b \odot \bot_b) \to \bot_b}$};
 \node (W) at (3.75,0) {$a$};
@@
 \label{defn:monoidal_double_category}
-A \define{monoidal double category} is a pseudomonoid in $\Dbl$, namely it is equipped with double functors $\otimes\colon\lD\times\lD\to\lD$, $I\colon\one\to\lD$ and invertible double transformations $\otimes\circ(1\times\otimes)\cong\otimes\circ(\otimes\times1)$, $\otimes\circ(1\times I)\cong1\cong\otimes\circ(I\times1)$ satisfying standard axioms.
+A \define{monoidal double category} is a pseudomonoid in $\Dbl$, namely it is equipped with double functors $\otimes\maps\lD\times\lD\to\lD$, $I\maps\one\to\lD$ and invertible double transformations $\otimes\circ(1\times\otimes)\cong\otimes\circ(\otimes\times1)$, $\otimes\circ(1\times I)\cong1\cong\otimes\circ(I\times1)$ satisfying standard axioms.
 \end{defn} 

### 2021-04-19 cospans_new.tex
edited the proof of Theorem 2.1 up to the stuff in red
rewrote proof of Theorem 2.1 up to the material in red

@@
 \end{itemize}
-The functor $\Phi \maps \A/U \to \A$ is defined on objects by $\Phi(a,x,a \xrightarrow{i} U(x))=a$ and on morphisms by $\Phi(f,\alpha)=f$.
+The functor $\Phi \maps \A/U \to \A$ is defined on objects by $\Phi(a,x,a \xrightarrow{i} U(x))=a$ and on morphisms by $\Phi(f,\theta)=f$.
 We have a monoidal structure on $\A/U$ where the tensor product of two objects $(a_1,x_1,a_1 \xrightarrow{i_1} U(x_1))$ and $(a_2,x_2,a_2 \xrightarrow{i_2} U(x_2))$ is given by
@@
 
-One can also check that the functor $\Phi$ is also opfibration, but this takes a bit more work.
+One can also check that the functor $\Phi$ is an opfibration, but this takes a bit more work.
 Given a morphism $f \maps a \to a'$ in $\A$ and an object $(a,x,a \xrightarrow{i} U(x)) \in \A/U$ over $a$, we shall show that a cocartesian lifting of $f$ is given by
@@
 \node (A) at (0,0) {$a$};
-\node (B) at (2,0) {$a'$};
+\node (B) at (1.5,0) {$a'$};
 \node (C) at (0,-1) {$U(x)$};
-\node (D) at (2,-1) {$U(x)+_a a'$};
+\node (D) at (1.5,-1) {$U(x)+_a a'$};
 \path[->,font=\scriptsize,>=angle 90]

### 2021-04-20 cospans_new.tex
a few inline comments

@@
 
+{\chris I suggest to move the sentence about fibrations and bifibrations to the appendix.
+
+A monoidal bifibration moreover has a global tensor product that preserves cartesian and cocartesian liftings.
+
+I also suggest that the whole text introducing the Beck Chevalley condition for a bifibration is also moved to the appndix.}
+
 We prove both these theorems using the work of Shulman \cite{Shulman2008}, which we recall here.
@@
 this gives a bijection between pseudofunctors $F \maps \A \to \Cat$ and opfibrations
-$U \maps \inta F \to \A$.   Moeller and the third author \cite{MV} showed that
+$U \maps \inta F \to \A$.
+
+{\chris It feels like there is some repetition in the material below and the sketch of the proof of 2.4.
+I believe the previous version of the paper had a briefer text here.
+No problem if you want to keep as is.}
+
+Moeller and the third author \cite{MV} showed that
 similarly, given a (symmetric) monoidal category $\A$, there is a bijection between 
@@
 
+{\chris Some text saying that we have now set up the necessary framework to use Mike's result and obtain our double categories would be nice here}
+
 \begin{proof}[Proof of \cref{thm:decorated_cospans_1}] 
@@
 Let $U \maps \inta F \to \A$ be the monoidal opfibration associated to the lax monoidal pseudofunctor $F \maps \A \to \Cat$.
-Thus:
+{\chris Couldn't we just recall the appendix here?}  Thus:
 \begin{itemize}
@@
 \end{itemize}
-The functor $U$ maps objects and morphisms to their first component.   We thus obtain an explicit description of the comma category $\A/U$:
+The functor $U$ maps objects and morphisms to their first component.
+We thus obtain an explicit description of the comma category $\A/U$ {\chris well the arrows are described like that in any slice category, there is nothing special for the Grothendieck category?
+Perhaps the slice description could be omitted or more brief?}:
 \begin{itemize}
@@
 One can also check that the functor $\Phi$ is an opfibration, but this takes a bit more work.
-Given a morphism $f \maps a \to a'$ in $\A$ and an object $(a,x,a \xrightarrow{i} U(x)) \in \A/U$ over $a$, we shall show that a cocartesian lifting of $f$ is given by
+{\chris ...or ``is less straightforward'' to express more formally perhaps?} Given a morphism $f \maps a \to a'$ in $\A$ and an object $(a,x,a \xrightarrow{i} U(x)) \in \A/U$ over $a$, we shall show that a cocartesian lifting of $f$ is given by
 \[ (f,\theta) \maps (a,x,a \xrightarrow{i} U(x)) \, \to \, (a',x', a' \xrightarrow{i'} U(x')). \]

### 2021-04-20 cospans_new.tex
A few comments and typo fixes

@@
 \begin{itemize}
-\item an object of $\inta F$ is a pair $(b,p)$ where $b \in \A$ and $p \in F(A)$;
+\item an object of $\inta F$ is a pair $(b,p)$ where $b \in \A$ and $p \in F(b)$;
 \item a morphism in $\inta F$ from $(b,p)$ to $(b',p')$ is a pair $(g,\zeta)$
@@
 \end{itemize}
+%%% Kenny: The f and g in the second item above need to be the same
 The functor $U$ maps objects and morphisms to their first component.
@@
 \[ (f,\theta) \maps (a,x,a \xrightarrow{i} U(x)) \, \to \, (a',x', a' \xrightarrow{i'} U(x')). \]
+%%% Kenny: Just an observation: we're using a morphism f:a-->b for the fibration part and a morphism f:a-->a' for the opfibration part.
 Here $i'$ arises from the following pushout square in $\A$:
@@
 the morphism in $\inta F$ given by the pair $(g,\id)$ where $g \maps b \to b'$ is
-given in the above diagram and $\id \maps F(f)(p) \to p'$ is the identity.
+given in the above diagram and $\id \maps F(g)(p) \to p'$ is the identity.
 

### 2021-06-14 cospans_new.tex
getting ready to finish up the paper
dealt with Christina's suggestions and some mistakes

@@
 % in LaTeX
-% 2021/3/29 - Kenny's changes and a few more
+% 2021/6/8 - Finishing up
 
@@
 Instead of basing the theory of decorated cospans on a symmetric lax monoidal functor $F \maps (\A, +) \to (\Set, \times)$, we use a symmetric lax monoidal pseudofunctor $F \maps (\A, +) \to (\Cat, \times)$.
-In \cref{thm:decorated_cospans,thm:decorated_cospans_2}, we use this
+In \cref{thm:decorated_cospans_1,thm:decorated_cospans_2}, we use this
 data to construct a symmetric monoidal double category $F\lCsp$ in which:
@@
 
-{\chris I suggest to move the sentence about fibrations and bifibrations to the appendix.
-
-A monoidal bifibration moreover has a global tensor product that preserves cartesian and cocartesian liftings.
-
-I also suggest that the whole text introducing the Beck Chevalley condition for a bifibration is also moved to the appndix.}
-
-We prove both these theorems using the work of Shulman \cite{Shulman2008}, which we recall here.
-First we need a few concepts.
-Opfibrations are recalled in \cref{subsec:fibrations}, and fibrations are defined dually, with a functor $\Phi \maps \C \to \A$ being a fibration if and only if $\Phi\op \maps \C\op \to \A\op$ is an opfibration.
-A functor $\Phi \maps \C \to \A$ is a \define{bifibration} if it is both a fibration and an opfibration.
-If $\C$ and $\A$ are monoidal categories, a \define{monoidal} bifibration $\Phi \maps \C \to \A$ is a bifibration that is also a strict monoidal functor.
-Similarly, if $\C$ and $\A$ are symmetric monoidal, a \define{symmetric monoidal} bifibration is a bifibration $\Phi \maps \C \to \A$ that is a symmetric strict monoidal functor.
-
-If $\Phi \maps \C \to \A$ an opfibration, for any morphism $f \maps a \to b$ in $\A$ there is a covariant reindexing functor
-\[    f_! \maps \C_a \to \C_b \]
-between the fibers of $\Phi$, as recalled in \cref{subsec:fibrations}.  Similarly, if $\Phi$ is a fibration there is a contravariant reindexing functor
-\[    f^\ast \maps \C_b \to \C_a .\]
-Thus, in a bifibration we have both covariant and contravariant reindexing functors, and in 
-fact $f^\ast$ is left adjoint to $f_\ast$ \cite[Proposition 3.9]{Shulman2008}.   Using this one can easily show that for any commutative square in $\A$
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a$};
-\node (B) at (1.5,0) {$b$};
-\node (C) at (0,-1) {$c$};
-\node (D) at (1.5,-1) {$d$};
-%\node (E) at (0.5,-0.5) {$\Downarrow\theta$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$h$} (B)
-(A) edge node[left]{$k$} (C)
-(B) edge node[right]{$g$} (D)
-(C) edge node[below]{$f$} (D);
-\end{tikzpicture}
-\]
-the following square commutes up to a specified natural transformation:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$\C_a$};
-\node (B) at (1.5,0) {$\C_b$};
-\node (C) at (0,-1) {$\C_c$};
-\node (D) at (1.5,-1) {$\C_d$};
-\node (E) at (0.75,-0.5) {$\Searrow \theta$};
-\path[->,font=\scriptsize,>=angle 90]
-(B) edge node[above]{$h^\ast$} (A)
-(A) edge node[left]{$k_!$} (C)
-(B) edge node[right]{$g_!$} (D)
-(D) edge node[below]{$f^\ast$} (C);
-\end{tikzpicture}
-\]
-where $\theta$ is built as a composite involving the unit of the adjunction between
-$g_!$ and $g^\ast$ and the counit of the adjunction between $k_!$ and $k^\ast$:
-\[    k_! h^\ast \To k_! h^\ast g^\ast g_! = k_! k^\ast f^\ast g^! \To f^\ast g_! .\] 
-If $\theta$ is a natural isomorphism whenever the original square in $\A$ is
-a pushout, we shall say $\Phi$ is \define{Beck--Chevalley}.  (Shulman says `strongly co-Beck--Chevalley'.)
+We prove both these theorems using the work of Shulman \cite{Shulman2008}, which we recall here.   The concept of `Beck--Chevalley monoidal bifibration' is explained in \cref{subsec:fibrations}.
 
@@
 
+All the above concepts and results have analogues for fibrations.
+A functor $\Phi \maps \X \to \A$ a \define{fibration} if and only if $\Phi\op \maps \X\op \to \A\op$ is an opfibration.
+Equivalently, $\Phi$ is a fibration if and only if for every $y \in \X$ with $U(y) = a$ and $f \maps a \to b$ in $\A$ there exists a cartesian lifting of $f$ to $x$, where this concept is defined dually to cocartesian lifting.
+Furthermore, if $\Phi$ is a fibration there is a contravariant reindexing functor
+\[    f^\ast \maps \X_b \to \X_a \]
+for each morphism $f \maps a \to b$.
+
+A functor $\Phi \maps \X \to \A$ is a \define{bifibration} if it is both a fibration and an opfibration.
+If $\X$ and $\A$ are monoidal categories, a \define{monoidal} bifibration $\Phi \maps \X \to \A$ is a bifibration that is also a strict monoidal functor, such that the tensor product of $\A$ preserves cartesian and cocartesian liftings.
+Similarly, if $\C$ and $\A$ are symmetric monoidal, a \define{symmetric monoidal} bifibration is a bifibration $\Phi \maps \C \to \A$ that is a symmetric strict monoidal functor.
+
+In a bifibration we have both covariant and contravariant reindexing functors, and in 
+fact $f_!$ is left adjoint to $f^*$ \cite[Proposition 3.9]{Shulman2008}.   Using this one can easily show that for any commutative square in $\A$
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$a$};
+\node (B) at (1.5,0) {$b$};
+\node (C) at (0,-1) {$c$};
+\node (D) at (1.5,-1) {$d$};
+%\node (E) at (0.5,-0.5) {$\Downarrow\theta$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$h$} (B)
+(A) edge node[left]{$k$} (C)
+(B) edge node[right]{$g$} (D)
+(C) edge node[below]{$f$} (D);
+\end{tikzpicture}
+\]
+the following square commutes up to a specified natural transformation:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$\C_a$};
+\node (B) at (1.5,0) {$\C_b$};
+\node (C) at (0,-1) {$\C_c$};
+\node (D) at (1.5,-1) {$\C_d$};
+\node (E) at (0.75,-0.5) {$\Searrow \theta$};
+\path[->,font=\scriptsize,>=angle 90]
+(B) edge node[above]{$h^\ast$} (A)
+(A) edge node[left]{$k_!$} (C)
+(B) edge node[right]{$g_!$} (D)
+(D) edge node[below]{$f^\ast$} (C);
+\end{tikzpicture}
+\]
+where $\theta$ is built as a composite involving the unit of the adjunction between
+$g_!$ and $g^\ast$ and the counit of the adjunction between $k_!$ and $k^\ast$:
+\[    k_! h^\ast \To k_! h^\ast g^\ast g_! = k_! k^\ast f^\ast g^! \To f^\ast g_! .\] 
+If $\theta$ is a natural isomorphism whenever the original square in $\A$ is
+a pushout, we shall say $\Phi$ is \define{Beck--Chevalley}.  (Shulman  uses the term `strongly co-BC' \cite[Definition 13.21] {Shulman2008}.)
+
 \subsection{Double categories}\label{sec:doublecats}

### 2021-06-15 cospans_new.tex
worked on material in and around Thms. 2.1-2.2

@@
 \cref{thm:decorated_cospans_2} gives conditions under which this double category is symmetric monoidal.
-The definition of lax monoidal pseudofunctor is recalled in \cref{subsec:bicats}, and the definition of symmetric monoidal double category is recalled in \cref{defn:double_category}.
+(We recall the definition of lax monoidal pseudofunctor in \cref{subsec:bicats}, and the definition of symmetric monoidal double category in \cref{defn:double_category}.)
 
 In all that follows, when we say a category `has finite colimits' we mean it is equipped with a choice of colimit for every finite diagram.
-Thus, if $\A$ has coproducts it gives a cocartesian monoidal category $(\A,+)$: that is, a symmetric monoidal category where the monoidal structure is given by the chosen binary coproducts and initial object.
+Thus, if $\A$ has finite colimits it gives a cocartesian monoidal category $(\A,+)$: that is, a symmetric monoidal category where the monoidal structure is given by the chosen binary coproducts and initial object.
 However, when we say a functor `preserves finite colimits', it need only do this up to canonical isomorphism, unless otherwise specified.
@@
 
-We prove both these theorems using the work of Shulman \cite{Shulman2008}, which we recall here.   The concept of `Beck--Chevalley monoidal bifibration' is explained in \cref{subsec:fibrations}.
+We prove both these theorems using the work of Shulman \cite{Shulman2008}.
+Shulman gives a general way to construct double categories from `Beck--Chevalley monoidal bifibrations'---a concept we explain in \cref{subsec:fibrations}.
 
@@
 \item a horizontal 1-cell is a pair of objects $a,b \in \A$ together with an
-object $c \in C$ with $\Phi(c) = a + b$.
+object $c \in \C$ with $\Phi(c) = a + b$.
 \item a 2-morphism is a pair of morphisms $f \maps a \to a'$, $g \maps b \to b'$ 
@@
 \end{itemize}
-If $\Phi$ is a symmetric monoidal bifibration then $\Fr(\Phi)$ becomes a symmetric
+If $\Phi$ is a Beck--Chevalley symmetric monoidal bifibration then $\Fr(\Phi)$ becomes a symmetric
 monoidal double category.
@@
 
-We  prove Theorems \ref{thm:decorated_cospans_1} and \ref{thm:decorated_cospans_2} by applying this lemma to a particular monoidal bifibration.
-To get our hands on this starting from our lax monoidal pseudofunctor $F \maps (A,+) \to (\Cat,\times)$, we need a monoidal version of the Grothendieck construction \cite{MV}.
-We recall the Grothendieck construction in \ref{subsec:fibrations}; briefly,
-this gives a bijection between pseudofunctors $F \maps \A \to \Cat$ and opfibrations
-$U \maps \inta F \to \A$.
-
-{\chris It feels like there is some repetition in the material below and the sketch of the proof of 2.4.
-I believe the previous version of the paper had a briefer text here.
-No problem if you want to keep as is.}
-
-Moeller and the third author \cite{MV} showed that
-similarly, given a (symmetric) monoidal category $\A$, there is a bijection between 
-\begin{itemize}
-\item \define{(symmetric) monoidal opindexed categories}: (symmetric) lax monoidal pseudofunctors \hfill \break $F\maps (\A, \otimes_A) \to (\Cat, \times)$
-\end{itemize}
-and 
-\begin{itemize}
-\item \define{(symmetric) monoidal opfibrations}: opfibrations $U \maps \X \to \A$ where $\X$ and $\A$ are (symmetric) monoidal, $U$ is (symmetric) strict monoidal, and $\otimes_\X$ preserves cocartesian liftings.
-\end{itemize}  
-If the monoidal structure on $\A$ is in fact cocartesian, as it is in our case, there is a further correspondence between these structures and ordinary pseudofunctors $F\maps \A \to \MonCat$ (or to $\SMC$ in the symmetric case).
-
-In fact, all these correspondences lift to 2-equivalences between appropriate 2-categories:
+Note that when $\C$ is the arrow category of $\A$ and $\Phi$ maps any arrow in $\A$ to its
+domain, an object of $\Fr(\Phi)$ simply amounts to a cospan in $\C$.
+Thus, in this case $\Fr(\Phi)$ is the double category of cospans in $\C$.
+We shall use variations on this idea to define double categories of decorated and structured cospans, and also prove that under certain conditions these double categories are equivalent.
+
+We start with decorated cospans, proving Theorems \ref{thm:decorated_cospans_1} and \ref{thm:decorated_cospans_2} by applying Shulman's result to a particular monoidal bifibration built
+from a lax monoidal pseudofunctor $F \maps (A,+) \to (\Cat,\times)$.
+The Grothendieck construction gives a bijection between pseudofunctors $F \maps \A \to \Cat$ and opfibrations $U \maps \inta F \to \A$.
+We need two refinements of this construction: one that gives monoidal obfibrations, and one that gives symmetric monoidal opfibrations.
+We explain the Grothendieck construction and all these related concepts in \cref{subsec:fibrations}; here we simply recall the result we need.
 
@@
 \label{lem:MonGroth}
-There is a 2-equivalence between the 2-categories of monoidal opfibrations and monoidal opindexed categories, and if the base is cocartesian monoidal, there is a 2-equivalence between these and pseudofunctors into $\MonCat$.
+There is a 2-equivalence between the 2-categories of monoidal opfibrations and monoidal opindexed categories with a given base, and if the base is cocartesian monoidal, there is a 2-equivalence between these and pseudofunctors into $\MonCat$.
 Similarly there is a 2-equivalence between symmetric monoidal opfibrations and symmetric monoidal opindexed categories, and if the base is cocartesian monoidal, also a 2-equivalence between these and pseudofunctors into $\SMC$.
@@
 
-{\chris Some text saying that we have now set up the necessary framework to use Mike's result and obtain our double categories would be nice here}
+Now we are ready to use Shulman's result to prove  \cref{thm:decorated_cospans_1} and  \cref{thm:decorated_cospans_2}.
 
@@
 To obtain the desired double category we apply \cref{lem:shulman} to a bifibration $\Phi \maps \A/U \to \A$ which we now define.
-Let $U \maps \inta F \to \A$ be the monoidal opfibration associated to the lax monoidal pseudofunctor $F \maps \A \to \Cat$.
-{\chris Couldn't we just recall the appendix here?}  Thus:
+Let $U \maps \inta F \to \A$ be the monoidal opfibration associated to the lax monoidal pseudofunctor $F \maps (\A,+) \to (\Cat, \times)$.
+As in \cref{subsec:fibrations},
 \begin{itemize}
 \item an object of $\inta F$ is a pair $(b,p)$ where $b \in \A$ and $p \in F(b)$;
-\item a morphism in $\inta F$ from $(b,p)$ to $(b',p')$ is a pair $(g,\zeta)$
-where $g \maps b \to b'$ is a morphism in $\A$ and $\zeta \maps F(f)(p) \to p'$ is
+\item a morphism in $\inta F$ from $(b,p)$ to $(b',p')$ is a pair $(f,\zeta)$
+where $g \maps b \to b'$ is a morphism in $\A$ and $\zeta \maps F(g)(p) \to p'$ is
 a morphism in $F(b')$.
 \end{itemize}
-%%% Kenny: The f and g in the second item above need to be the same
-The functor $U$ maps objects and morphisms to their first component.
-We thus obtain an explicit description of the comma category $\A/U$ {\chris well the arrows are described like that in any slice category, there is nothing special for the Grothendieck category?
-Perhaps the slice description could be omitted or more brief?}:
+The functor $U$ maps objects and morphisms to their first component, so in the comma
+category $\A/U$, 
 \begin{itemize}
-\item an object of $\A/U$ is a triple $(a,x,a \xrightarrow{i} U(x))$ with $a \in \A$ and $x=(b,p) \in \inta F$;
-\item a morphism in $\A/U$ from $(a,x,a \xrightarrow{i} U(x))$ to $(a',x',a' \xrightarrow{i'} U(x'))$ is a pair $(f,\theta)$ where $f \maps a \to a'$ is a morphism in $\A$ and $\theta \maps x \to x'$ is a morphism in $\inta F$ such that the following square commutes:
+\item an object is a triple $(a,x,a \xrightarrow{i} U(x))$ with $a \in \A$ and $x=(b,p) \in \inta F$;
+\item a morphism from $(a,x,a \xrightarrow{i} U(x))$ to $(a',x',a' \xrightarrow{i'} U(x'))$ is a pair $(f,\theta)$ where $f \maps a \to a'$ is a morphism in $\A$ and $\theta \maps x \to x'$ is a morphism in $\inta F$ such that the following square commutes:
 \[
@@
 One can also check that the functor $\Phi$ is an opfibration, but this takes a bit more work.
-{\chris ...or ``is less straightforward'' to express more formally perhaps?} Given a morphism $f \maps a \to a'$ in $\A$ and an object $(a,x,a \xrightarrow{i} U(x)) \in \A/U$ over $a$, we shall show that a cocartesian lifting of $f$ is given by
+Given a morphism $f \maps a \to a'$ in $\A$ and an object $(a,x,a \xrightarrow{i} U(x)) \in \A/U$ over $a$, we shall show that a cocartesian lifting of $f$ is given by
 \[ (f,\theta) \maps (a,x,a \xrightarrow{i} U(x)) \, \to \, (a',x', a' \xrightarrow{i'} U(x')). \]
@@
 \node (A) at (0,0) {$(\A/U)_a$};
-\node (B) at (1.5,0) {$\A/U)_b$};
+\node (B) at (1.5,0) {$(\A/U)_b$};
 \node (C) at (0,-1) {$(\A/U)_c$};
 \node (D) at (1.5,-1) {$(\A/U)_d$};
-\node (E) at (0.75,-0.5) {$\Searrow$};
+\node (E) at (0.75,-0.5) {$\Searrow \theta$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 
-\begin{proof}[Proof of \cref{thm:decorated_cospans_2}] We apply \cref{lem:shulman} to $A/U \to A$: why is this a symmetric monoidal bifibration?
+\begin{proof}[Proof of \cref{thm:decorated_cospans_2}] 
+When the lax monoidal pseudofunctor $F \maps (\A,+) \to (\Cat, \times)$ of \cref{thm:decorated_cospans_1} is symmetric, the monoidal bifibration $\Phi \maps \A/U \to A$
+is symmetric, so \cref{lem:shulman} implies that the double category $F\Csp$ becomes symmetric
+monoidal as described.
 \end{proof}
@@
 
-\subsection{Fibrations}\label{subsec:fibrations}
+\subsection{Fibrations and opfibrations}\label{subsec:fibrations}
 
@@
 If $\theta$ is a natural isomorphism whenever the original square in $\A$ is
-a pushout, we shall say $\Phi$ is \define{Beck--Chevalley}.  (Shulman  uses the term `strongly co-BC' \cite[Definition 13.21] {Shulman2008}.)
+a pushout, we say $\Phi$ is \define{Beck--Chevalley}.  (Shulman  uses the term `strongly co-BC' \cite[Definition 13.21] {Shulman2008}.)
 

### 2021-06-15 cospans_new.tex
changes in and around Thms. 2.1 and 2.2

@@
 The Grothendieck construction gives a bijection between pseudofunctors $F \maps \A \to \Cat$ and opfibrations $U \maps \inta F \to \A$.
-We need two refinements of this construction: one that gives monoidal obfibrations, and one that gives symmetric monoidal opfibrations.
+We need two refinements of this construction: one that gives monoidal ofibrations, and one that gives symmetric monoidal opfibrations.
 We explain the Grothendieck construction and all these related concepts in \cref{subsec:fibrations}; here we simply recall the result we need.
@@
 Let $U \maps \inta F \to \A$ be the monoidal opfibration associated to the lax monoidal pseudofunctor $F \maps (\A,+) \to (\Cat, \times)$.
-As in \cref{subsec:fibrations},
+As in \cref{def:GrothCat},
 \begin{itemize}
@@
 \item an object is a triple $(a,x,a \xrightarrow{i} U(x))$ with $a \in \A$ and $x=(b,p) \in \inta F$;
-\item a morphism from $(a,x,a \xrightarrow{i} U(x))$ to $(a',x',a' \xrightarrow{i'} U(x'))$ is a pair $(f,\theta)$ where $f \maps a \to a'$ is a morphism in $\A$ and $\theta \maps x \to x'$ is a morphism in $\inta F$ such that the following square commutes:
+\item a morphism from $(a,x,a \xrightarrow{i} U(x))$ to $(a',x',a' \xrightarrow{i'} U(x'))$ is a pair $(f,\theta)$ where $f \maps a \to a'$ is a morphism in $\A$ and $\theta \maps x \to x'$ is a morphism in $\inta F$ such that this square commutes:
 \[
@@
 \end{itemize}
-The functor $\Phi \maps \A/U \to \A$ is defined on objects by $\Phi(a,x,a \xrightarrow{i} U(x))=a$ and on morphisms by $\Phi(f,\theta)=f$.
-We have a monoidal structure on $\A/U$ where the tensor product of two objects $(a_1,x_1,a_1 \xrightarrow{i_1} U(x_1))$ and $(a_2,x_2,a_2 \xrightarrow{i_2} U(x_2))$ is given by
+We define the functor $\Phi \maps \A/U \to \A$ on objects by $\Phi(a,x,a \xrightarrow{i} U(x))=a$ and on morphisms by $\Phi(f,\theta)=f$.
+
+There is a monoidal structure on $\A/U$ where the tensor product of two objects $(a_1,x_1,a_1 \xrightarrow{i_1} U(x_1))$ and $(a_2,x_2,a_2 \xrightarrow{i_2} U(x_2))$ is given by
 \[  (a_1,x_1,a_1 \xrightarrow{i_1} U(x_1)) \otimes (a_2,x_2,a_2 \xrightarrow{i_2} U(x_2)) = (a_1+a_2,x_1 \otimes x_2,a_1+a_2 \xrightarrow{i_1+i_2} U(x_1 \otimes x_2)) \]
@@
 
-One can easily check that $\Phi$ is a fibration.  Given a morphism $f \maps a \to b$ in $\A$ and an object $(b,y,b \xrightarrow{i} U(y)) \in \A/U$ over $b$, a cartesian lifting of $f$ is given by 
-\[ (f,\id) \maps (a,y,a \xrightarrow{i \circ f} U(y)) \, \to \, (b,y,b \xrightarrow{i} U(y)). \]
+One can check that $\Phi$ is a fibration.  Given a morphism $f \maps a \to a'$ in $\A$ and an object $(a',x',a' \xrightarrow{i'} U(x')) \in \A/U$ over $a'$, a cartesian lifting of $f$ is given by 
+\[ (f,\id) \maps (a,x',a \xrightarrow{i' \circ f} U(x')) \, \to \, (a',x',a' \xrightarrow{i'} U(x')). \]
 Denoting this cartesian lifting by $\textnormal{cart}(f)$, the tensor product of $\A/U$ strictly preserves such cartesian liftings in the sense that $\textnormal{cart}(f_1) \otimes \textnormal{cart}(f_2)=\textnormal{cart}(f_1+f_2)$.
@@
 \[ (f,\theta) \maps (a,x,a \xrightarrow{i} U(x)) \, \to \, (a',x', a' \xrightarrow{i'} U(x')). \]
-%%% Kenny: Just an observation: we're using a morphism f:a-->b for the fibration part and a morphism f:a-->a' for the opfibration part.
-Here $i'$ arises from the following pushout square in $\A$:
+where $i'$ arises from the following pushout square in $\A$:
 \[
@@
 diagram and $p' = F(g)(p)$.  Then $U(x') = b'$ so we have 
-$i' \maps a' \to U(x')$ as desired.  Finally, we define $\theta \maps x \to x'$ to be 
+$i' \maps a' \to U(x')$ as desired.  Finally, define $\theta \maps x \to x'$ to be 
 the morphism in $\inta F$ given by the pair $(g,\id)$ where $g \maps b \to b'$ is
-given in the above diagram and $\id \maps F(g)(p) \to p'$ is the identity.
-
-{\john To show that $(f,\theta)$ is a cocartesian lifting of $f$, suppose...
-Then use this picture somehow:}
+given as above and $\id \maps F(g)(p) \to p'$ is the identity.
+
+To show that $(f,\theta)$ is an cocartesian lifting of $f$, suppose
+
+Then use this picture somehow:
 \[
@@
 \]
-and consequently a natural isomorphism between our two objects of $(\A/U)_c$, showing that $\Phi$ satisfies the Beck--Chevalley condition.
+and consequently a natural isomorphism between our two objects of $(\A/U)_c$, showing that $\Phi$ satisfies the Beck--Chevalley condition.   We then define $F\lCsp$ to be $\Fr(\Phi)$.
 \end{proof}
@@
 When the lax monoidal pseudofunctor $F \maps (\A,+) \to (\Cat, \times)$ of \cref{thm:decorated_cospans_1} is symmetric, the monoidal bifibration $\Phi \maps \A/U \to A$
-is symmetric, so \cref{lem:shulman} implies that the double category $F\Csp$ becomes symmetric
-monoidal as described.
+is symmetric, so \cref{lem:shulman} implies that the double category $F\lCsp = \Fr(\Phi)$ is symmetric monoidal as described.
 \end{proof}

### 2021-06-16 cospans_new.tex
Worked on proof of Thm. 2.1

@@
 \begin{itemize}
-\item an object of $\inta F$ is a pair $(b,p)$ where $b \in \A$ and $p \in F(b)$;
-\item a morphism in $\inta F$ from $(b,p)$ to $(b',p')$ is a pair $(f,\zeta)$
-where $g \maps b \to b'$ is a morphism in $\A$ and $\zeta \maps F(g)(p) \to p'$ is
+\item an object of $\inta F$ is a pair $(b,x)$ where $b \in \A$ and $x \in F(b)$;
+\item a morphism in $\inta F$ from $(b,x)$ to $(b',x')$ is a pair $(g,h)$
+where $g \maps b \to b'$ is a morphism in $\A$ and $h \maps F(g)(x) \to x'$ is
 a morphism in $F(b')$.
 \end{itemize}
-The functor $U$ maps objects and morphisms to their first component, so in the comma
-category $\A/U$, 
+The functor $U$ maps objects and morphisms to their first component, so one can describe
+the comma category $\A/U$ as follows:
 \begin{itemize}
-\item an object is a triple $(a,x,a \xrightarrow{i} U(x))$ with $a \in \A$ and $x=(b,p) \in \inta F$;
-\item a morphism from $(a,x,a \xrightarrow{i} U(x))$ to $(a',x',a' \xrightarrow{i'} U(x'))$ is a pair $(f,\theta)$ where $f \maps a \to a'$ is a morphism in $\A$ and $\theta \maps x \to x'$ is a morphism in $\inta F$ such that this square commutes:
+\item an object is a pair $(a \xrightarrow{i} b, x)$ consisting of a morphism in $\A$ and an
+object $x \in F(b)$;
+\item a morphism from $(a \xrightarrow{i} b, x)$ to $(a' \xrightarrow{i'} b', x')$ is a triple $(f,g,h)$ where $f \maps a \to a'$ and $g \maps b \to b'$ are morphisms in $\A$ such that this square commutes:
 \[
@@
 \node (B) at (1.5,0) {$a'$};
-\node (C) at (0,-1) {$U(x)$};
-\node (D) at (1.5,-1) {$U(x')$.};
+\node (C) at (0,-1) {$b$};
+\node (D) at (1.5,-1) {$b'$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (B) edge node[right]{$i'$} (D)
-(C) edge node[below]{$U(\theta)$} (D);
-\end{tikzpicture}
-\]
+(C) edge node[below]{$g$} (D);
+\end{tikzpicture}
+\]
+and $h \maps F(g)(x) \to x'$ is a morphism in $F(b')$.
 \end{itemize}
-We define the functor $\Phi \maps \A/U \to \A$ on objects by $\Phi(a,x,a \xrightarrow{i} U(x))=a$ and on morphisms by $\Phi(f,\theta)=f$.
-
-There is a monoidal structure on $\A/U$ where the tensor product of two objects $(a_1,x_1,a_1 \xrightarrow{i_1} U(x_1))$ and $(a_2,x_2,a_2 \xrightarrow{i_2} U(x_2))$ is given by
-\[  (a_1,x_1,a_1 \xrightarrow{i_1} U(x_1)) \otimes (a_2,x_2,a_2 \xrightarrow{i_2} U(x_2)) = (a_1+a_2,x_1 \otimes x_2,a_1+a_2 \xrightarrow{i_1+i_2} U(x_1 \otimes x_2)) \]
-where we have left the equality $U(x_1)+U(x_2) = U(x_1 \otimes x_2)$ implicit in the above composite, for reasons of space.
-The monoidal unit is given by $(0_\A,0_\X,0_\A \to U(0_\X))$.
-It is easy to see that the functor $\Phi$ is a strict monoidal using this tensor product.
-
-One can check that $\Phi$ is a fibration.  Given a morphism $f \maps a \to a'$ in $\A$ and an object $(a',x',a' \xrightarrow{i'} U(x')) \in \A/U$ over $a'$, a cartesian lifting of $f$ is given by 
-\[ (f,\id) \maps (a,x',a \xrightarrow{i' \circ f} U(x')) \, \to \, (a',x',a' \xrightarrow{i'} U(x')). \]
+As in any comma category we have a functor $\Phi \maps \A/U \to \A$; this is given on objects by $\Phi(a \xrightarrow{i} b, x)=a$ and on morphisms by $\Phi(f,g,h)=f$.
+
+There is a monoidal structure on $\A/U$ coming from the monoidality of $U$.  On objects
+this is given by
+\[  (a \xrightarrow{i} b, x) \otimes (a' \xrightarrow{i'} b', x') = (a+a' \xrightarrow{i+i'} b+b', 
+\phi_{a,b}(d,d') )\]
+where $\phi$ is the laxator for $F$.  The monoidal unit is given by $(0_\A \xrightarrow{!} 0_\A, x)$
+where $x \in F(0_\A)$ is the element given by $\phi_0 \maps \one \to F(0_\A)$.   With this monoidal structure it is easy to check that the functor $\Phi$ is strict monoidal.
+
+One can check that $\Phi$ is a fibration.  Given a morphism $f \maps a \to a'$ in $\A$ and an object $(a' \xrightarrow{i'} b', x') \in \A/U$ over $a'$, a cartesian lifting of $f$ is given by 
+\[ (f,1,1) \maps (a \xrightarrow{i' f} b' , x')\; \to \; (a' \xrightarrow{i'} b', x'). \]
 Denoting this cartesian lifting by $\textnormal{cart}(f)$, the tensor product of $\A/U$ strictly preserves such cartesian liftings in the sense that $\textnormal{cart}(f_1) \otimes \textnormal{cart}(f_2)=\textnormal{cart}(f_1+f_2)$.
 
-One can also check that the functor $\Phi$ is an opfibration, but this takes a bit more work.
-Given a morphism $f \maps a \to a'$ in $\A$ and an object $(a,x,a \xrightarrow{i} U(x)) \in \A/U$ over $a$, we shall show that a cocartesian lifting of $f$ is given by
-\[ (f,\theta) \maps (a,x,a \xrightarrow{i} U(x)) \, \to \, (a',x', a' \xrightarrow{i'} U(x')). \]
-where $i'$ arises from the following pushout square in $\A$:
+One can also check that $\Phi$ is an opfibration.
+Given a morphism $f \maps a \to a'$ in $\A$ and an object $(a \xrightarrow{i}b, x) \in \A/U$ over $a$, we shall show that a cocartesian lifting of $f$ is given by
+\[ (f,g,1) \maps (a \xrightarrow{i} b, x) \, \to \, (a' \xrightarrow{i'} b+_a a', F(g)(x)). \]
+where $b +_a a'$, $i'$ and $g$ arise from the following pushout square in $\A$:
 \[
@@
 \node (B) at (1.5,0) {$a'$};
-\node (C) at (0,-1) {$U(x)$};
-\node (D) at (1.5,-1) {$U(x)+_a a'$};
+\node (C) at (0,-1) {$b$};
+\node (D) at (1.5,-1) {$b+_a a'$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-The object $x' \in \inta F$ is defined as follows.  Recall that $x \in \inta F$ is a
-pair $(b,p)$ with $b\in \A$ and $p \in F(b)$, and note that $U(x) = b$.   Define 
-$x'$ to be the pair $(b',p')$ where $b' = U(x)+_a a'$ is the pushout in the above
-diagram and $p' = F(g)(p)$.  Then $U(x') = b'$ so we have 
-$i' \maps a' \to U(x')$ as desired.  Finally, define $\theta \maps x \to x'$ to be 
-the morphism in $\inta F$ given by the pair $(g,\id)$ where $g \maps b \to b'$ is
-given as above and $\id \maps F(g)(p) \to p'$ is the identity.
-
-To show that $(f,\theta)$ is an cocartesian lifting of $f$, suppose
-
-Then use this picture somehow:
+To show that $(f,g,1)$ is an cocartesian lifting of $f$, suppose we are given a morphism 
+\[    (f'',g'',h'') \maps (a \xrightarrow{i} b, x) \; \to \; (a'' \xrightarrow{i''} b'', x'')   \]
+in $\A/U$ and a morphism $k \maps a \to a''$ in $\A$ such that $\Phi(f'',g'',h'') = k \circ f$.   To
+show $\Phi$ is an opfibration, we need to show there exists a unique morphism
+\[     (\tilde{f}, \tilde{g}, \tilde{h}) \maps (a' \xrightarrow{i'} b +_a a', F(g)(x)) \; \to \; (a'' \xrightarrow{i''} b'', x'') \]
+such that $\Phi(\tilde{f}, \tilde{g}, \tilde{h}) = k$ and 
+\[       (\tilde{f}, \tilde{g}, \tilde{h}) \circ (f,g,1) = (f'',g'',h'') .\]
+To achieve this set $\tilde{f} = k$, $\tilde{h} = h''$, and define $\tilde{g}$ using
+the universal property of the pushout:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$a$};
+\node (B) at (1.5,0) {$a'$};
+\node (C) at (0,-1) {$b$};
+\node (D) at (1.5,-1) {$b+_a a'$};
+\node (E) at (2.5,-1.5) {$b''$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$f$} (B)
+(A) edge node[left]{$i$} (C)
+(B) edge node[left]{$i'$} (D)
+(C) edge node[above]{$g$} (D)
+(C) edge [bend right] node[below]{$g''$} (E)
+(B) edge [bend left] node[right]{$i'' k$} (E)
+(D) edge [dashed] node[left]{$\exists! \, \tilde{g} \phantom{a}$} (E);
+\end{tikzpicture}
+\]
+after noting that $g'' i = i' f'' = i'' k f $ by the commuting square condition for the morphisms
+in $\A/U$.   One can check that with these choices, $(\tilde{f},\tilde{g}, \tilde{h})$ obeys the desired conditions and is the unique morphism to do so.
+
+\iffalse
 \[
@@
 \]
+\fi
 

### 2021-06-17 cospans_new.tex
working on the proof of Thm. 2.1

@@
 One can also check that $\Phi$ is an opfibration.
-Given a morphism $f \maps a \to a'$ in $\A$ and an object $(a \xrightarrow{i}b, x) \in \A/U$ over $a$, we shall show that a cocartesian lifting of $f$ is given by
+Given a morphism $f \maps a \to a'$ in $\A$ and an object $(a \xrightarrow{i}b, x) \in \A/U$ over $a$, we claim that a cocartesian lifting of $f$ is given by
 \[ (f,g,1) \maps (a \xrightarrow{i} b, x) \, \to \, (a' \xrightarrow{i'} b+_a a', F(g)(x)). \]
-where $b +_a a'$, $i'$ and $g$ arise from the following pushout square in $\A$:
+where $g, i'$ and $b +_a a'$ arise from this pushout square in $\A$:
 \[
@@
 \node (C) at (0,-1) {$b$};
-\node (D) at (1.5,-1) {$b+_a a'$};
+\node (D) at (1.5,-1) {$b+_a a'$.};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-To show that $(f,g,1)$ is an cocartesian lifting of $f$, suppose we are given a morphism 
+Suppose we are given a morphism 
 \[    (f'',g'',h'') \maps (a \xrightarrow{i} b, x) \; \to \; (a'' \xrightarrow{i''} b'', x'')   \]
-in $\A/U$ and a morphism $k \maps a \to a''$ in $\A$ such that $\Phi(f'',g'',h'') = k \circ f$.   To
-show $\Phi$ is an opfibration, we need to show there exists a unique morphism
+in $\A/U$ and a morphism $k \maps a \to a''$ in $\A$ such that $\Phi(f'',g'',h'') = k \circ f$.   To show that $(f,g,1)$ is a cocartesian lifting of $f$, we need to show there exists a unique morphism
 \[     (\tilde{f}, \tilde{g}, \tilde{h}) \maps (a' \xrightarrow{i'} b +_a a', F(g)(x)) \; \to \; (a'' \xrightarrow{i''} b'', x'') \]
@@
 \[       (\tilde{f}, \tilde{g}, \tilde{h}) \circ (f,g,1) = (f'',g'',h'') .\]
-To achieve this set $\tilde{f} = k$, $\tilde{h} = h''$, and define $\tilde{g}$ using
+To achieve this we choose $\tilde{f} = k$, $\tilde{h} = h''$, and define $\tilde{g}$ using
 the universal property of the pushout:
@@
 (B) edge [bend left] node[right]{$i'' k$} (E)
-(D) edge [dashed] node[left]{$\exists! \, \tilde{g} \phantom{a}$} (E);
+(D) edge [dashed] node[below left]{$\exists! \, \tilde{g} \phantom{a}$} (E);
 \end{tikzpicture}
@@
 in $\A/U$.   One can check that with these choices, $(\tilde{f},\tilde{g}, \tilde{h})$ obeys the desired conditions and is the unique morphism to do so.
+
+It follows that $\Phi$ is a bifibration.
+Denoting the cocartesian lifting of a morphism $f$ by $\textnormal{cocart}(f)$, we have that $\textnormal{cocart}(f_1) \otimes \textnormal{cocart}(f_2) \cong \textnormal{cocart}(f_1+f_2)$ by the universal map between two colimits of the same diagram.
+Thus, $\Phi$ is a monoidal bifibration.
 
@@
 
-Denoting the cocartesian lifting of a morphism $f$ by $\textnormal{cocart}(f)$, we have that $\textnormal{cocart}(f_1) \otimes \textnormal{cocart}(f_2) \cong \textnormal{cocart}(f_1+f_2)$ by the universal map between two colimits of the same diagram:
-\[  (U(x_1)+_{a_1}b_1)+(U(x_2)+_{a_2}b_2) \cong U(x_1 \otimes x_2)+_{a_1+a_2}(b_1+b_2). \]
-
-Lastly, the monoidal bifibration $\Phi$ satisfies the Beck--Chevalley condition. Given a pushout square in $\A$:
+Lastly, we need to check that $\Phi$ satisfies the Beck--Chevalley condition. Given a pushout square in $\A$:
 \[
@@
 \]
-we need to show that the following square commutes up to a natural isomorphism:
+we need to show that the natural transformation $\theta$, defined as in \cref{subsec:fibrations}, is an isomorphism:
 \[
@@
 \node (C) at (0,-1) {$(\A/U)_c$};
-\node (D) at (1.5,-1) {$(\A/U)_d$};
+\node (D) at (1.5,-1) {$(\A/U)_d$.};
 \node (E) at (0.75,-0.5) {$\Searrow \theta$};
@@
 \]
-Let $(b,x,b \xrightarrow{i} U(x))$ be an object of $(\A/U)_b$ where $x=(b',p) \in \A \times F(b')$ so that $U(x)=b'$.
-Going left, we precompose with $h \maps a \to b$ to obtain the object $(a,x,a \xrightarrow{i \circ h} U(x))$ of $(\A/U)_a$.
+Let $(b \xrightarrow{i} e, x)$ be an object of $(\A/U)_b$.
+Going left, we precompose with $h \maps a \to b$ to obtain the object $(a \xrightarrow{i \circ h} e, z)$ of $(\A/U)_a$.
 Then going down, we push forward along $k$:
@@
 \node (A) at (0,0) {$a$};
-\node (B) at (1.5,0) {$U(x)$};
+\node (B) at (1.5,0) {$e$};
 \node (C) at (0,-1) {$c$};
-\node (D) at (1.5,-1) {$c+_{a}U(x)$};
+\node (D) at (1.5,-1) {$c+_{a}e$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-to obtain the object $(c,z,c \xrightarrow{\psi} U(z))$ of $(\A/U)_c$, where $z \in \A \times F(c+_a U(x))$ is given by $z=(c+_a U(x),q)$ where $q$ is given by
-\[ 1 \xrightarrow{p} F(U(x)) \xrightarrow{F(\zeta)} F(0+_0 U(x)) \xrightarrow{F(!_c +_{!_a} 1)} F(c+_a U(x)). \]
+to obtain the object $(c \xrightarrow{\psi} c+_a e, F(\psi)(x))$ of $(\A/U)_c$.
 %and so by construction, we have that 
@@
 \]
-and consequently a natural isomorphism between our two objects of $(\A/U)_c$, showing that $\Phi$ satisfies the Beck--Chevalley condition.   We then define $F\lCsp$ to be $\Fr(\Phi)$.
+and consequently a natural isomorphism between our two objects of $(\A/U)_c$, showing that $\Phi$ satisfies the Beck--Chevalley condition.
+
+Having checked the hypotheses of \cref{lem:shulman}, we then define $F\lCsp$ to be $\Fr(\Phi)$.
 \end{proof}

### 2021-06-17 cospans_new.tex
completed proofs of Thms. 2.1 and 2.2

@@
 We need two refinements of this construction: one that gives monoidal ofibrations, and one that gives symmetric monoidal opfibrations.
-We explain the Grothendieck construction and all these related concepts in \cref{subsec:fibrations}; here we simply recall the result we need.
+We explain the Grothendieck construction and these related concepts in \cref{subsec:fibrations}; here we simply recall the result we need.
 
@@
 
-Now we are ready to use Shulman's result to prove  \cref{thm:decorated_cospans_1} and  \cref{thm:decorated_cospans_2}.
+Now we are ready to use Shulman's result to prove  \cref{thm:decorated_cospans_1} and  \cref{thm:decorated_cospans_2}.  An $F$-decorated cospan from $a \in \A$ to $b \in \A$
+is a cospan 
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$a$};
+\node (B) at (1,0) {$m$};
+\node (C) at (2,0) {$b$};
+%\node (D) at (2.6,0) {$x \in F(m))$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$$} (B)
+(C) edge node[above]{$$} (B);
+\end{tikzpicture}
+\]
+in $\A$ together with an object $x \in F(m)$.
+This can be seen as a pair $(e \to m, x \in F(m))$ such that $e$ equals $a + b$.
+But $(m,x \in F(m))$ is precisely an object of the Grothendieck category $\inta F$, and the opfibration $U \maps \inta F \to \A$ sends this object to $m$.
+Thus, $(e \to m, x \in F(m))$ can be seen as an object of the comma category $\A/U$.
+Let $\Phi \maps \A/U \to \A$ be the functor sending any object $(e \to m,x \in F(m)) \in \A/U$ to $e$.
+Then an $F$-decorated cospan from $a$ to $b$ amounts to an object $c \in \A/U$ such that $\Phi(c) = a + b$.
+With this choice of $\Phi$, Shulman's result gives the double category of $F$-decorated cospans.
 
 \begin{proof}[Proof of \cref{thm:decorated_cospans_1}] 
-To obtain the desired double category we apply \cref{lem:shulman} to a bifibration $\Phi \maps \A/U \to \A$ which we now define.
 Let $U \maps \inta F \to \A$ be the monoidal opfibration associated to the lax monoidal pseudofunctor $F \maps (\A,+) \to (\Cat, \times)$.
-As in \cref{def:GrothCat},
-\begin{itemize}
-\item an object of $\inta F$ is a pair $(b,x)$ where $b \in \A$ and $x \in F(b)$;
-\item a morphism in $\inta F$ from $(b,x)$ to $(b',x')$ is a pair $(g,h)$
-where $g \maps b \to b'$ is a morphism in $\A$ and $h \maps F(g)(x) \to x'$ is
-a morphism in $F(b')$.
-\end{itemize}
-The functor $U$ maps objects and morphisms to their first component, so one can describe
-the comma category $\A/U$ as follows:
+To obtain the desired double category we apply Shulman's \cref{lem:shulman} to the functor $\Phi \maps \A/U \to \A$, which we now describe in more detail.
+In the comma category $\A/U$:
 \begin{itemize}
@@
 
-There is a monoidal structure on $\A/U$ coming from the monoidality of $U$.  On objects
-this is given by
+To apply \cref{lem:shulman} it suffices to prove that $\Phi$ is a Beck--Chevalley monoidal opfibration.
+First, there is a monoidal structure on $\A/U$ coming from the monoidality of $U$.
+On objects this is given by
 \[  (a \xrightarrow{i} b, x) \otimes (a' \xrightarrow{i'} b', x') = (a+a' \xrightarrow{i+i'} b+b', 
 \phi_{a,b}(d,d') )\]
-where $\phi$ is the laxator for $F$.  The monoidal unit is given by $(0_\A \xrightarrow{!} 0_\A, x)$
-where $x \in F(0_\A)$ is the element given by $\phi_0 \maps \one \to F(0_\A)$.   With this monoidal structure it is easy to check that the functor $\Phi$ is strict monoidal.
-
-One can check that $\Phi$ is a fibration.  Given a morphism $f \maps a \to a'$ in $\A$ and an object $(a' \xrightarrow{i'} b', x') \in \A/U$ over $a'$, a cartesian lifting of $f$ is given by 
+where $\phi$ is the laxator for $F$.  The monoidal unit is $(0_\A \xrightarrow{!} 0_\A, x)$
+where $x \in F(0_\A)$ is the element given by $\phi_0 \maps \one \to F(0_\A)$.   With this monoidal structure it is easy to see that $\Phi$ is strict monoidal.
+
+Next, one can check that $\Phi$ is a fibration.  Given a morphism $f \maps a \to a'$ in $\A$ and an object $(a' \xrightarrow{i'} b', x') \in \A/U$ over $a'$, a cartesian lifting of $f$ is given by 
 \[ (f,1,1) \maps (a \xrightarrow{i' f} b' , x')\; \to \; (a' \xrightarrow{i'} b', x'). \]
@@
 
-\iffalse
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a$};
-\node (B) at (2.5,0) {$c$};
-\node (C) at (1.5,1) {$a'$};
-\node (D) at (0,-2) {$U(x)$};
-\node (E) at (2.5,-2) {$U(y)$};
-\node (F) at (1.5,-1) {$U(x') = U(x)+_a a'$};
-\path[->,font=\scriptsize,>=angle 90]
-(D) edge node [above] {$\theta$} (F)
-(F) edge [dashed] node [right] {$\exists ! \psi$} (E)
-(D) edge node [above] {$U(g')$} (E)
-(A) edge node [left] {$i$} (D)
-(C) edge node [right,near end] {$i'$} (F)
-(B) edge node {$$} (E)
-(A) edge node[above]{$f'$} (B)
-(C) edge node [right] {$p$} (B)
-(A) edge node[left]{$f$} (C);
-%(B) edge [dashed] node[right]{$$} (D)
-%(C) edge [dashed] node[above]{$$} (D);
-\end{tikzpicture}
-\]
-\fi
-
-Lastly, we need to check that $\Phi$ satisfies the Beck--Chevalley condition. Given a pushout square in $\A$:
+Lastly, we need to check that $\Phi$ satisfies the Beck--Chevalley condition.  Merely from the fact that $\Phi$ is a bifibration, for any commutative square in $\A$:
 \[
@@
 \node (D) at (1.5,-1) {$d$};
+\label{bc-square}
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-we need to show that the natural transformation $\theta$, defined as in \cref{subsec:fibrations}, is an isomorphism:
+there is a natural transformation
 \[
@@
 \]
+as defined at the end of \cref{subsec:fibrations}.   We need to prove that when the square in $\A$ is 
+a pushout, $\theta$ is a natural isomorphism.
+
+We start by describing $\theta$ more concretely.
 Let $(b \xrightarrow{i} e, x)$ be an object of $(\A/U)_b$.
-Going left, we precompose with $h \maps a \to b$ to obtain the object $(a \xrightarrow{i \circ h} e, z)$ of $(\A/U)_a$.
+Going left, we precompose with $h \maps a \to b$ to obtain the object $(a \xrightarrow{i h} e, z)$ of $(\A/U)_a$.
 Then going down, we push forward along $k$:
@@
 \node (D) at (1.5,-1) {$c+_{a}e$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i \circ h$} (B)
+\node at (1.2,-0.8) {\Large{$\ulcorner$}};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i h$} (B)
 (A) edge node[left]{$k$} (C)
@@
 to obtain the object $(c \xrightarrow{\psi} c+_a e, F(\psi)(x))$ of $(\A/U)_c$.
-%and so by construction, we have that 
-%\[  U(z)=U(\bot_c+_{\bot_a}x)=c+_a U(x).\]
-%{\john Need to refer to a proposition where we show $U$ preserves pushouts strictly.}
 For the other route, first going down, we push the object $(b,x,b \xrightarrow{i} U(x))$ forward along $g \maps b \to d$ by taking the following pushout:
@@
 \node (C) at (0,-1) {$d$};
-\node (D) at (1.5,-1) {$d+_{b}U(x)$};
+\node (D) at (1.5,-1) {$d+_b e$};
+\node at (1.2,-0.8) {\Large{$\ulcorner$}};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (B) edge node[right]{$$} (D)
-(C) edge node[below]{$\theta$} (D);
-\end{tikzpicture}
-\]
-which yields the object $(d,z',d \xrightarrow{\theta} U(z'))$ of $(\A/U)_d$ where $z' \in \A \times F(d+_b U(x))$ is given by ${z'=(d+_b U(x),q')}$ where $q'$ is given by 
-\[ 1 \xrightarrow{p} F(U(x)) \xrightarrow{F(\zeta)} F(0+_0 U(x)) \xrightarrow{F(!_d +_{!_b} 1)} F(d+_b U(x)). \]
-We then precompose with $f \maps c \to d$ to obtain the object $(c,z',c \xrightarrow{\theta \circ f} U(z'))$ of $(\A/U)_c$.
-
-Now we seek a natural isomorphism between the two objects $(c,z,c \xrightarrow{\psi} c+_a U(x))$ and $(c,z',c \xrightarrow{\theta \circ f} d+_b U(x))$ in $(\A/U)_c$.
-It suffices to obtain a natural isomorphism between the two objects $z$ and $z'$ in $\X$.
-This pushout square:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a$};
-\node (B) at (1.5,0) {$U(x)$};
-\node (C) at (0,-1) {$c$};
-\node (D) at (1.5,-1) {$c+_{a}U(x)$};
-%\node (A') at (4,0) {$L(b)$};
-%\node (B') at (6,0) {$x$};
-%\node (C') at (4,-1) {$L(d)$};
-%\node (D') at (6,-1) {$L(d)+_{L(b)}x$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i \circ h$} (B)
-(A) edge node[left]{$k$} (C)
-(B) edge node[right]{$$} (D)
-(C) edge node[below]{$\psi$} (D);
-%(A') edge node[above]{$I$} (B')
-%(A') edge node[left]{$L(g)$} (C')
-%(B') edge node[right]{$$} (D')
-%(C') edge node[below]{$\theta$} (D');
-\end{tikzpicture}
-\]
-exhibits $c+_a U(x)$ as a pushout of the span 
-\[  c \xleftarrow{k} a \xrightarrow{i \circ h} U(x) 
-\]
-in $\A$. We may also take the first pushout square above and paste it with the original pushout square in $\A$:
+(C) edge node[below]{$\phi$} (D);
+\end{tikzpicture}
+\]
+which yields the object $(d \xrightarrow{\phi} d+_b e, F(\phi)(x))$ of $(\A/U)_d$.
+Then going left, we precompose with $f \maps c \to d$ to obtain the object $(c \xrightarrow{\phi f} d+_b e, F(\phi)(x))$ of $(\A/U)_c$.
+
+The natural transformation $\theta$ gives a morphism
+\[    \theta \maps   (c \xrightarrow{\psi} c+_a e, F(\psi)(x)) \; \to \; (c \xrightarrow{\phi f} d+_b e, F(\phi)(x))  \]
+in $(\A/U)_c$.   Concretely, this arises from the universal property of the pushout:
 \[
@@
 \node (A) at (0,0) {$b$};
-\node (B) at (1.5,0) {$U(x)$};
+\node (B) at (1.5,0) {$e$};
 \node (C) at (0,-1) {$d$};
-\node (D) at (1.5,-1) {$d+_{b}U(x)$};
+\node (D) at (1.5,-1) {$d+_{b}e$};
 \node (E) at (-1.5,0) {$a$};
 \node (F) at (-1.5,-1) {$c$};
+\node (G) at (2.5,-2) {$c+_{a}e$};
+\node at (1.2,-0.8) {\Large{$\ulcorner$}};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (B) edge node[right]{$$} (D)
-(C) edge node[below]{$\theta$} (D);
-\end{tikzpicture}
-\]
-obtaining a pushout square 
-which exhibits $d+_b U(x)$ as a pushout of the same span in $\A$.
-The resulting natural isomorphism $\kappa$ between $c+_a U(x)$ and $d+_b U(x)$ then extends to a natural isomorphism between $z=(c+_a U(x),q)$ and $z'=(d+_b U(x),q')$ in $\X$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node () at (5,0) {$\cong$};
-\node (A) at (0,0) {$1$};
-
-\node (A1) at (2,0.5) {$F(U(x))$};
-\node (A2) at (4,0.5) {$F(0+_0 U(x))$};
-\node (A3) at (6,0.5) {$F(c+_a U(x))$};
-
-\node (B1) at (2,-0.5) {$F(U(x))$};
-\node (B2) at (4,-0.5) {$F(0+_0 U(x))$};
-\node (B3) at (6,-0.5) {$F(d+_b U(x))$};
-
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[fill=white]{$p$} (A1)
-(A) edge node[fill=white]{$p$} (B1)
-
-(A1) edge node [above] {$F(\zeta)$} (A2)
-(A2) edge node [above] {$F(!_c +_{!_a} 1)$} (A3)
-
-(A1) edge node [fill=white] {$1$} (B1)
-(A2) edge node [fill=white] {$1$} (B2)
-(A3) edge node [fill=white] {$F(\kappa)$} (B3)
-
-(B1) edge node [above] {$F(\zeta)$} (B2)
-(B2) edge node [above] {$F(!_d +_{!_b} 1)$} (B3);
-
-\end{tikzpicture}
-\]
-and consequently a natural isomorphism between our two objects of $(\A/U)_c$, showing that $\Phi$ satisfies the Beck--Chevalley condition.
-
-Having checked the hypotheses of \cref{lem:shulman}, we then define $F\lCsp$ to be $\Fr(\Phi)$.
+(C) edge node[below]{$\phi$} (D)
+(F) edge [bend right] node[below]{$\psi$} (G)
+(G) edge [dashed] node[below left]{$\exists ! \;\zeta $} (D)
+(B) edge [bend left] (G);
+\end{tikzpicture}
+\]
+Namely, we have $\theta = (1, \zeta, 1)$.   But when the original square in $\A$ (at upper left 
+in the diagram above) is a pushout, its pasting with the other pushout gives a pushout, so $\zeta$ and hence $\theta$ is isomorphism.
+
+This shows that $\Phi$ obeys the Beck--Chevalley condition.  Having checked all the hypotheses of \cref{lem:shulman}, we can define $F\lCsp$ to be $\Fr(\Phi)$.
 \end{proof}
@@
 
+\begin{defn}
 A functor $\Phi \maps \X \to \A$ is a \define{bifibration} if it is both a fibration and an opfibration.     
+\end{defn}
+
+\begin{defn}
  If $\X$ and $\A$ are monoidal categories, a \define{monoidal} bifibration $\Phi \maps \X \to \A$ is a bifibration that is also a strict monoidal functor, such that the tensor product of $\A$ preserves cartesian and cocartesian liftings.
 Similarly, if $\C$ and $\A$ are symmetric monoidal, a \define{symmetric monoidal} bifibration is a bifibration $\Phi \maps \C \to \A$ that is a symmetric strict monoidal functor.
+\end{defn}
 

### 2021-06-17 cospans_new.tex
started work on Thm. 2.5 - don't look at it yet.

@@
 \usepackage{comment}
+\usepackage[mathscr]{euscript}
 \usepackage[neveradjust]{paralist}
@@
 
-We start with decorated cospans, proving Theorems \ref{thm:decorated_cospans_1} and \ref{thm:decorated_cospans_2} by applying Shulman's result to a particular monoidal bifibration built
-from a lax monoidal pseudofunctor $F \maps (A,+) \to (\Cat,\times)$.
+We start with decorated cospans, proving Theorem \ref{thm:decorated_cospans_1} and 
+\ref{thm:decorated_cospans_2} by applying Shulman's result to a particular monoidal bifibration built from a lax monoidal pseudofunctor $F \maps (A,+) \to (\Cat,\times)$.
 The Grothendieck construction gives a bijection between pseudofunctors $F \maps \A \to \Cat$ and opfibrations $U \maps \inta F \to \A$.
-We need two refinements of this construction: one that gives monoidal ofibrations, and one that gives symmetric monoidal opfibrations.
-We explain the Grothendieck construction and these related concepts in \cref{subsec:fibrations}; here we simply recall the result we need.
+We need two refinements of this construction: one that gives monoidal opfibrations, and one that gives symmetric monoidal opfibrations.
+We recall the Grothendieck construction and these related concepts in \cref{subsec:fibrations}; here we simply state the result we need.
 
@@
 
-Our construction gives not only decorated cospan double categories, but  also maps between these: that is, symmetric monoidal double functors, as in \cref{def:doublefun}.
-Suppose we have two categories $\A,\A'$ with finite colimits and two symmetric lax monoidal pseudofunctors $F \maps \A \to \Cat$ and $F' \maps \A' \to \Cat$.
-Then we can obtain a map between their decorated cospan double categories, $\lH \maps F\lCsp \to F' \lCsp$, from:
+Our construction gives not only decorated cospan double categories, but  also maps between these.
+For simplicity we only consider the monoidal case.
+Suppose we have two categories $\A,\A'$ with finite colimits and two lax monoidal pseudofunctors $F \maps \A \to \Cat$ and $F' \maps \A' \to \Cat$.
+Then we can obtain a map between their decorated cospan double categories, namely a double functor $\lH \maps F\lCsp \to F' \lCsp$, from:
 \begin{itemize}
 \item a functor $H \maps \A \to \A'$ that preserves finite limits,
-\item a symmetric lax monoidal pseudofunctor $(E,\phi,\phi_0) \maps \Cat \to \Cat$, 
+\item a lax monoidal pseudofunctor $(E,\phi,\phi_0) \maps \Cat \to \Cat$, 
 \item a natural isomorphism $\theta \maps EF \Rightarrow F'H$: 
@@
 \end{itemize}
-The induced double functor $\lH \maps F\lCsp \to F'\lCsp$ is defined as follows:
+The double functor $\lH \maps F\lCsp \to F'\lCsp$ is defined as follows:
 \begin{itemize}
@@
 \begin{itemize}
-\item The image of an $F$-decorated cospan $M$ in $F\lCsp$ is the $F'$-decorated cospan $\lH(M)$ in $F'\lCsp$
-\begin{align*}
- M=\left(a\xrightarrow{i}m\xleftarrow{o}b,x\in F(m)\right)\mapsto \lH(M)=\left(H(a)\xrightarrow{H(i)}H(m)\xleftarrow{H(o)}H(b),\bar{x}\in F'(H(m))\right)& \textrm{ where } \\
-\bar{x}:=\one \xrightarrow{\phi_0} E(\one) \xrightarrow{E(x)} E(F(m)) \xrightarrow{\theta_m} F'(H(m)) &
-\end{align*}
-\item The image of a map of decorated cospans $\alpha \maps M \to N$ in $F\lCsp$ is the map of $F'$-decorated cospans $\lH(\alpha)$ in $F'\lCsp$
+\item The image of an $F$-decorated cospan
+\[ M= (a\xrightarrow{i}m\xleftarrow{o}b, \; x\in F(m)) \]
+is the following $F'$-decorated cospan:
+\[ \lH(M)= (H(a)\xrightarrow{H(i)}H(m)\xleftarrow{H(o)}H(b), \;\bar{x}\in F'(H(m))) \]
+ where
+\[
+\bar{x}:=\one \xrightarrow{\phi_0} E(\one) \xrightarrow{E(x)} E(F(m)) \xrightarrow{\theta_m} F'(H(m)).\]
+\item The image of a map of decorated cospans in $F\lCsp$ 
 \[
@@
 \node (F) at (3,-0.5) {$x' \in F(n)$};
-%\node (G) at (1,-1) {$\tau \maps F(h)(x) \to x'$};
+\node (G) at (5,0) {$\tau \maps F(h)(x) \to x'$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i$} (B)
+(C) edge node[above]{$o$} (B)
+(A) edge node[left]{$f$} (A')
+(C) edge node[right]{$g$} (C')
+(A') edge node[below] {$i'$} (D)
+(C') edge node[below] {$o'$} (D)
+(B) edge node [left] {$h$} (D);
+\end{tikzpicture}
+\]
+is the following map of $F'$-decorated cospans $\lH(\alpha)$ in $F'\lCsp$:
+\[
+\begin{tikzpicture}[scale=1.5]
 \node (A'') at (4.75,0.5) {$H(a)$};
@@
 \node (F'') at (8.5,-0.5) {$\theta_n E(x') \phi_0 \in F'(H(n))$};
-\node (H) at (3.75,0) {$\mapsto$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i$} (B)
-(C) edge node[above]{$o$} (B)
-(A) edge node[left]{$f$} (A')
-(C) edge node[right]{$g$} (C')
-(A') edge node[below] {$i'$} (D)
-(C') edge node[below] {$o'$} (D)
-(B) edge node [left] {$h$} (D)
+\path[->,font=\scriptsize,>=angle 90]
 (A'') edge node[above]{$H(i)$} (B'')
@@
 \]
-where a decoration morphism $\tau \maps F(h)(x) \to x'$ is mapped to a 
-decoration morphism as follows:
+where the decoration morphism $\tau$ is mapped to a decoration morphism as follows:
 \[
@@
 \label{thm:functoriality}
-Given two categories $\A$ and $\A'$ with finite colimits, two symmetric lax monoidal pseudofunctors $F \maps \A \to \Cat$ and $F' \maps \A' \to \Cat$, a finite colimit preserving functor $H \maps \A \to \A'$, a symmetric lax monoidal pseudofunctor $E \maps \Cat \to \Cat$ and a natural isomorphism $\theta \maps EF \Rightarrow F' H$ as in the following diagram:
+Given two categories $\A$ and $\A'$ with finite colimits, two lax monoidal pseudofunctors $F \maps \A \to \Cat$ and $F' \maps \A' \to \Cat$, a finite colimit preserving functor $H \maps \A \to \A'$, a lax monoidal pseudofunctor $E \maps \Cat \to \Cat$ and a natural isomorphism $\theta \maps EF \Rightarrow F' H$ as in the following diagram:
 \[
@@
 \] 
-the triple $(H,E,\theta)$ induces a symmetric monoidal double functor $\lH \maps F\lCsp \to F'\lCsp$ as defined above.
+the triple $(H,E,\theta)$ induces a double functor $\lH \maps F\lCsp \to F'\lCsp$ as defined above.
 \end{thm}
 
-\begin{proof}  See \cite[Theorem 4.2.1]{CourserThesis}.
-
-From the symmetric lax monoidal pseudofunctor $F \maps \A \to \Cat$, we can obtain a Beck-Chevalley symmetric monoidal opfibration $\Phi \maps (\A/U) \to \A$ as in \cref{thm:decorated_cospans_1}, where $U \maps \int F \to \A$ is the associated monoidal opfibration of the pseudofunctor $F$.
-We can do the same for the other symmetric lax monoidal pseudofunctor $F' \maps \A' \to \Cat$ to obtain another Beck-Chevalley symmetric monoidal opfibration $\Phi' \maps (\A'/U') \to \A'$.
+\begin{proof}   From the lax monoidal pseudofunctor $F \maps \A \to \Cat$, we obtain a Beck--Chevalley monoidal bifibration $\Phi \maps (\A/U) \to \A$ as in \cref{thm:decorated_cospans_1}.
+We do the same for the lax monoidal pseudofunctor $F' \maps \A' \to \Cat$ to obtain a Beck--Chevalley monoidal bifibration $\Phi' \maps (\A'/U') \to \A'$.
 \[
@@
 \]
-We construct a strong monoidal functor $G \maps (\A/U) \to (\A'/U')$ between the monoidal comma categories $(\A/U)$ and $(\A'/U')$ that will make the induced square commute.
-Such a commutative square is a morphism in the 2-category $\mathbf{FMF}$ of monoidal bifibrations satisfying the Beck-Chevalley condition which then, by a 2-functor $\mathbb{F}\mathbf{r} \maps \mathbf{FMF} \to \mathbf{FDbl}$ due to Shulman \cite[Theorem 14.11]{Shulman2008}, will yield a map $$\mathbb{F}\mathbf{r}(G,H) \maps \mathbb{F}\mathbf{r}(\Phi) \to \mathbb{F}\mathbf{r}(\Phi')$$between the fibrant symmetric monoidal double categories $\mathbb{F}\mathbf{r}(\Phi)=F\lCsp$ and $\mathbb{F}\mathbf{r}(\Phi')= F'\lCsp$.
-
-The monoidal comma category $(\A/U)$ has:
-\begin{enumerate}
-\item{objects as triples $(a,x,a \to U(x))$, and}
-\item{a morphism from $(a,x,a \to U(x))$ to $(b,y,b \to U(y))$ is a pair of morphisms $f \maps a \to b$ and $\tau \maps x \to y$ that make the following square commute:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a$};
-\node (B) at (1,0) {$b$};
-\node (C) at (0,-1) {$U(x)$};
-\node (D) at (1,-1) {$U(y)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$f$} (B)
-(A) edge node[left]{$$} (C)
-(B) edge node[right]{$$} (D)
-(C) edge node[above]{$U(\tau)$} (D);
-\end{tikzpicture}
-\]
-}
-\end{enumerate}
-The tensor product of two objects $(a_1,x_1,a_1 \to U(x_1))$ and $(a_2,x_2,a_2 \to U(x_2))$ is given by $$(a_1,x_1,a_1 \to U(x_1)) \otimes (a_2,x_2,a_2 \to U(x_2)) = (a_1+a_2,x_1+x_2,a_1+a_2 \to U(x_1 \otimes x_2)).$$The monoidal unit of $(\A/U)$ is given by $(0_\A,0_\X,0_\A \to U(0_\X))$.
-Those of $(\A'/U')$ are analogous.
-
-On objects, the strong monoidal functor $F \maps (\A/U) \to (\A'/U')$ is defined as follows:
-\begin{enumerate}
-\item{given $(a,x,a \to U(x))$ in $(\A/U)$ where $x=(m,p) \in \A \times F(m)$, $$G(a,x,a \to U(x)) = (H(a),\theta_m E(p) \phi,H(a) \to U'(\theta_m E(p) \phi))$$ where $\theta_m E(p) \phi$ is given by 
-$$1 \xrightarrow{\phi} E(1) \xrightarrow{E(p)} E(F(m)) \xrightarrow{\theta_m} F'(H(m))$$
-so that $U'(\theta_m E(p) \phi)=H(m)$, }
-\item{given a pair of morphisms $(f,\tau)$ that make the following square commute:
+Next we construct a strong monoidal functor $G \maps \A/U \to \A'/U'$  that makes the resulting square commute.
+Such a commutating square is a morphism in Shulman's 2-category $\mathscr{MF}^{\textrm{fr}}$ of Beck--Chevalley monoidal bifibrations.
+Appying Shulman's 2-functor $\mathbb{F}\mathbf{r} \maps \mathscr{MF}^{\textrm{fr}} \to \mathscr{F}r\mathscr{B}i$ to this morphism, \cite[Theorem 14.11]{Shulman2008}, we obtain the desired double functor
+\[ \mathbb{H} \maps  F\lCsp \to F'\lCsp .\]
+
+We described $\A/U$ and its monoidal structure in the proof of \cref{thm:decorated_cospans_1}, 
+and of course the case of $\A'/U'$ is analogous.
+We define a strong monoidal functor $G \maps \A/U \to \A'/U'$ as follows.
+First suppose we are given a object $(a \xrightarrow{i} b, x)$ in $(\A/U)$, where recall $x \in F(x)$.
+Then we define
+\[  G(a \xrightarrow{i} b, x) = (H(a) \xrightarrow{H(i)} H(b), x') \]
+where the object $x' \in F'(H(b))$ is picked out by the composite
+\[  1 \xrightarrow{\phi} E(1) \xrightarrow{E(p)} E(F(m)) \xrightarrow{\theta_m} F'(H(m)) \]
+so that $U'(\theta_m E(p) \phi)=H(m)$, 
+Given a pair of morphisms $(f,\tau)$ that make the following square commute:
 \[
@@
 \]
-}
-\end{enumerate}
+
 The laxator is given by the following natural isomorphism between $\theta_m E(p) \phi \times \theta_n E(q) \phi$ and $\theta_{m+n} E(p \times q) \phi$:

### 2021-06-18 cospans_new.tex
Working on the proof of Thm. 2.5 - don't look at it yet.

@@
 \node (D) at (1.5,-1) {$b+_a a'$.};
+\node at (1.2,-0.8) {\Large{$\ulcorner$}};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (A) edge node[left]{$i$} (C)
-(B) edge [dashed] node[right]{$i'$} (D)
-(C) edge [dashed] node[below]{$g$} (D);
+(B) edge node[right]{$i'$} (D)
+(C) edge node[below]{$g$} (D);
 \end{tikzpicture}
@@
 \node (E) at (2.5,-1.5) {$b''$};
+\node at (1.2,-0.8) {\Large{$\ulcorner$}};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (A) edge node[left]{$i$} (C)
-(B) edge node[left]{$i'$} (D)
-(C) edge node[above]{$g$} (D)
+(B) edge node[right]{$i'$} (D)
+(C) edge node[below]{$g$} (D)
 (C) edge [bend right] node[below]{$g''$} (E)
@@
 \label{thm:functoriality}
-Given two categories $\A$ and $\A'$ with finite colimits, two lax monoidal pseudofunctors $F \maps \A \to \Cat$ and $F' \maps \A' \to \Cat$, a finite colimit preserving functor $H \maps \A \to \A'$, a lax monoidal pseudofunctor $E \maps \Cat \to \Cat$ and a natural isomorphism $\theta \maps EF \Rightarrow F' H$ as in the following diagram:
+Given two categories $\A$ and $\A'$ with finite colimits, two lax monoidal pseudofunctors $F, F' \maps (\A',+) \to (\Cat,\times)$, a finite colimit preserving functor $H \maps \A \to \A'$, a lax monoidal pseudofunctor $E \maps (\Cat,\times) \to (\Cat,\times)$ and a {\john monoidal???} natural isomorphism $\theta$ as in the following diagram:
 \[
@@
 
-\begin{proof}   From the lax monoidal pseudofunctor $F \maps \A \to \Cat$, we obtain a Beck--Chevalley monoidal bifibration $\Phi \maps (\A/U) \to \A$ as in \cref{thm:decorated_cospans_1}.
-We do the same for the lax monoidal pseudofunctor $F' \maps \A' \to \Cat$ to obtain a Beck--Chevalley monoidal bifibration $\Phi' \maps (\A'/U') \to \A'$.
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$(\A/U)$};
-\node (B) at (2,0) {$(\A'/U')$};
-\node (C) at (0,-1.5) {$\A$};
-\node (D) at (2,-1.5) {$\A'$};
-\path[->,font=\scriptsize,>=angle 90]
+\begin{proof}   
+From the lax monoidal pseudofunctor $F$ we obtain a Beck--Chevalley monoidal bifibration $\Phi \maps \A/U \to \A$ as in \cref{thm:decorated_cospans_1}.
+Similarly the lax monoidal pseudofunctor $F'$ gives a Beck--Chevalley monoidal bifibration $\Phi' \maps \A'/U' \to \A'$.
+Next we construct a strong monoidal functor $G \maps \A/U \to \A'/U'$  that makes this square commute:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$\A/U$};
+\node (B) at (1,0) {$\A'/U'$};
+\node (C) at (0,-1) {$\A$};
+\node (D) at (1,-1) {$\A'$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$G$} (B)
 (A) edge node[left]{$\Phi$} (C)
 (B) edge node[right]{$\Phi'$} (D)
-(C) edge node[above]{$H$} (D);
-\end{tikzpicture}
-\]
-Next we construct a strong monoidal functor $G \maps \A/U \to \A'/U'$  that makes the resulting square commute.
-Such a commutating square is a morphism in Shulman's 2-category $\mathscr{MF}^{\textrm{fr}}$ of Beck--Chevalley monoidal bifibrations.
-Appying Shulman's 2-functor $\mathbb{F}\mathbf{r} \maps \mathscr{MF}^{\textrm{fr}} \to \mathscr{F}r\mathscr{B}i$ to this morphism, \cite[Theorem 14.11]{Shulman2008}, we obtain the desired double functor
+(C) edge node[below]{$H$} (D);
+\end{tikzpicture}
+\]
+Such a commuting square is a morphism in Shulman's 2-category of Beck--Chevalley monoidal bifibrations.
+Appying Shulman's 2-functor $\mathbb{F}\mathbf{r}$ to this morphism \cite[Theorem 14.11]{Shulman2008}, we obtain the desired double functor
 \[ \mathbb{H} \maps  F\lCsp \to F'\lCsp .\]
@@
 We described $\A/U$ and its monoidal structure in the proof of \cref{thm:decorated_cospans_1}, 
-and of course the case of $\A'/U'$ is analogous.
-We define a strong monoidal functor $G \maps \A/U \to \A'/U'$ as follows.
-First suppose we are given a object $(a \xrightarrow{i} b, x)$ in $(\A/U)$, where recall $x \in F(x)$.
-Then we define
-\[  G(a \xrightarrow{i} b, x) = (H(a) \xrightarrow{H(i)} H(b), x') \]
+and of course the case of $\A'/U'$ is analogous.   We define the strong monoidal functor $G \maps \A/U \to \A'/U'$ as follows.  First we define $G$ on an object $(a \xrightarrow{i} b, x)$ of $\A/U$.
+We can treat $x \in F(b)$ as a morphism $x \maps 1 \to F(b)$.    Then we define
+\[  G(a \xrightarrow{i} b, x) := (H(a) \xrightarrow{H(i)} H(b), x') \]
 where the object $x' \in F'(H(b))$ is picked out by the composite
-\[  1 \xrightarrow{\phi} E(1) \xrightarrow{E(p)} E(F(m)) \xrightarrow{\theta_m} F'(H(m)) \]
-so that $U'(\theta_m E(p) \phi)=H(m)$, 
-Given a pair of morphisms $(f,\tau)$ that make the following square commute:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a$};
-\node (B) at (1,0) {$b$};
-\node (C) at (0,-1) {$U(x)$};
-\node (D) at (1,-1) {$U(y)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$f$} (B)
-(A) edge node[left]{$$} (C)
-(B) edge node[right]{$$} (D)
-(C) edge node[above]{$U(\tau)$} (D);
-\end{tikzpicture}
-\]
-we define $$G(f,\tau)=(H(f),\theta_h E(\tau) \phi).$$
-which make the following square in $(\A'/U')$ commute:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$H(a)$};
-\node (B) at (3,0) {$H(b)$};
-\node (C) at (0,-1) {$U'(\theta_m E(p) \phi)$};
-\node (D) at (3,-1) {$U'(\theta_n E(q) \phi))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$H(f)$} (B)
-(A) edge node[left]{$$} (C)
-(B) edge node[right]{$$} (D)
-(C) edge node[above]{$U'(\theta_h E(\tau) \phi)$} (D);
-\end{tikzpicture}
-\]
+\[  1 \xrightarrow{\phi_0} E(1) \xrightarrow{E(x)} E(F(b)) \xrightarrow{\;\theta_b\;} F'(H(b)) .\]
+Then we define $G$ on a morphism
+\[   (f,g,h) \maps (a \xrightarrow{i} b, x) \; \to \; (a' \xrightarrow{i'} b', x') \]
+in $\A/U$.   For this we set
+\[   G(f,g,h) = (H(f),H(g),???) \]
+
 where $\tau$ and $\theta_h E(\tau) \phi$ are given respectively by:

### 2021-06-18 cospans_new.tex
fixed typo in proof of Theorem 2.2

@@
 to obtain the object $(c \xrightarrow{\psi} c+_a e, F(\psi)(x))$ of $(\A/U)_c$.
-For the other route, first going down, we push the object $(b,x,b \xrightarrow{i} U(x))$ forward along $g \maps b \to d$ by taking the following pushout:
+For the other route, first going down, we push the object $(b \xrightarrow{i} e,x)$ forward along $g \maps b \to d$ by taking the following pushout:
 \[

### 2021-06-18 cospans_new.tex
Fixed more typos in the proof of Theorem 2.1

@@
 
-In more detail, if $(\phi,\phi_0)$ is the lax monoidal structure of the pseudofunctor $F$ as recalled in \cref{subsec:bicats}, the induced monoidal structure on the total Grothendieck category $\X=\inta F$ (\cref{def:GrothCat}) is given by
+In more detail, if $(\phi,\phi_0)$ is the lax monoidal structure of the pseudofunctor $F$ as recalled in \cref{subsec:bicats}, the induced monoidal structure on the Grothendieck category $\X=\inta F$ (\cref{def:GrothCat}) is given by
 \begin{equation}\label{eq:explicitstructure2}
@@
 
-Now we are ready to use Shulman's result to prove  \cref{thm:decorated_cospans_1} and  \cref{thm:decorated_cospans_2}.  An $F$-decorated cospan from $a \in \A$ to $b \in \A$
+Now we are ready to use Shulman's result to prove  \cref{thm:decorated_cospans_1} and  \cref{thm:decorated_cospans_2}.  An $F$-decorated cospan from $a$ to $b$ 
 is a cospan 
@@
 \[  (a \xrightarrow{i} b, x) \otimes (a' \xrightarrow{i'} b', x') = (a+a' \xrightarrow{i+i'} b+b', 
-\phi_{a,b}(d,d') )\]
-where $\phi$ is the laxator for $F$.  The monoidal unit is $(0_\A \xrightarrow{!} 0_\A, x)$
-where $x \in F(0_\A)$ is the element given by $\phi_0 \maps \one \to F(0_\A)$.   With this monoidal structure it is easy to see that $\Phi$ is strict monoidal.
+\phi_{a,b}(x,x') )\]
+where $\phi$ is the laxator for $F$.  The monoidal unit is $(0_\A \xrightarrow{!} 0_\A, 0)$
+where $0 \in F(0_\A)$ is the object given by $\phi_0 \maps \one \to F(0_\A)$.   With this monoidal structure it is easy to see that $\Phi$ is strict monoidal.
 
@@
 \]
-is the following map of $F'$-decorated cospans $\lH(\alpha)$ in $F'\lCsp$:
+is the following map of $F'$-decorated cospans in $F'\lCsp$:
 \[
@@
 \]
-where the decoration morphism $\tau$ is mapped to a decoration morphism as follows:
+where the decoration morphism $\tau$ is mapped to a decoration morphism $\lH(\tau)$ as follows.  We can think of $\tau$ as a natural transformation
 \[
@@
 \node (J) at (-2.5,-0.5) {$\scriptstyle\Downarrow\tau$};
-\node (K) at (-1,-0.5) {$\mapsto$};
+\path[->,font=\scriptsize,>=angle 90]
+(G) edge node [above] {$x$} (H)
+(G) edge node [below] {$x'$} (I)
+(H) edge node [right] {$F(h)$} (I);
+\end{tikzpicture}
+\]
+and in the same style of notation $\lH(\tau)$ is given by
+\[
+\begin{tikzpicture}[scale=1.5]
 \node (A) at (-0.25,-0.5) {$1$};
@@
 \node (E) at (4,0) {$F^\prime(H(m))$};
-\node (F) at (4,-1) {$F^\prime(H(n))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node [above] {$\phi$} (L)
-(G) edge node [above] {$x$} (H)
-(G) edge node [below] {$x'$} (I)
-(H) edge node [right] {$F(h)$} (I)
+\node (F) at (4,-1) {$F^\prime(H(n))$.};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node [above] {$\phi_0$} (L)
 (B) edge node [above] {$\theta_m$} (E)
@@
 \end{itemize}
+The square at right commutes strictly because $\theta$ is a natural isomorphism.
+Perhaps we could generalize our construction to handle the case where $\theta$ is a pseudonatural equivalence, making this square commute up to a natural isomorphism.
+However, the following result suffices
+for the application in \cref{subsec:petrirates}.
 
@@
 \label{thm:functoriality}
-Given two categories $\A$ and $\A'$ with finite colimits, two lax monoidal pseudofunctors $F, F' \maps (\A',+) \to (\Cat,\times)$, a finite colimit preserving functor $H \maps \A \to \A'$, a lax monoidal pseudofunctor $E \maps (\Cat,\times) \to (\Cat,\times)$ and a {\john monoidal???} natural isomorphism $\theta$ as in the following diagram:
+Given categories $\A$ and $\A'$ with finite colimits, lax monoidal pseudofunctors $F, F' \maps (\A',+) \to (\Cat,\times)$, a finite colimit preserving functor $H \maps \A \to \A'$, a lax monoidal pseudofunctor $E \maps (\Cat,\times) \to (\Cat,\times)$ and a {\john monoidal???} natural isomorphism $\theta$ as in the following diagram:
 \[
@@
 \] 
-the triple $(H,E,\theta)$ induces a double functor $\lH \maps F\lCsp \to F'\lCsp$ as defined above.
+the triple $(H,E,\theta)$ induces a double functor $\lH \maps F\lCsp \to F'\lCsp$ defined as above.
 \end{thm}
@@
 We described $\A/U$ and its monoidal structure in the proof of \cref{thm:decorated_cospans_1}, 
-and of course the case of $\A'/U'$ is analogous.   We define the strong monoidal functor $G \maps \A/U \to \A'/U'$ as follows.  First we define $G$ on an object $(a \xrightarrow{i} b, x)$ of $\A/U$.
-We can treat $x \in F(b)$ as a morphism $x \maps 1 \to F(b)$.    Then we define
-\[  G(a \xrightarrow{i} b, x) := (H(a) \xrightarrow{H(i)} H(b), x') \]
-where the object $x' \in F'(H(b))$ is picked out by the composite
+and of course the case of $\A'/U'$ is analogous.   We define $G \maps \A/U \to \A'/U'$ as follows.  First we define $G$ on any object $(a \xrightarrow{i} b, x)$ of $\A/U$ as follows:
+\[  G(a \xrightarrow{i} b, x) \; = \; (H(a) \xrightarrow{H(i)} H(b), \underline{x}). \]
+To define $\underline{x}$, we treat the object $x \in F(b)$ as a functor 
+$x \maps 1 \to F(b)$, and let $\underline{x} \in F'(H(b))$ be given by this functor:
 \[  1 \xrightarrow{\phi_0} E(1) \xrightarrow{E(x)} E(F(b)) \xrightarrow{\;\theta_b\;} F'(H(b)) .\]
-Then we define $G$ on a morphism
+Next we define $G$ on any morphism
 \[   (f,g,h) \maps (a \xrightarrow{i} b, x) \; \to \; (a' \xrightarrow{i'} b', x') \]
 in $\A/U$.   For this we set
-\[   G(f,g,h) = (H(f),H(g),???) \]
-
-where $\tau$ and $\theta_h E(\tau) \phi$ are given respectively by:
+\[   G(f,g,h) = (H(f),H(g),\underline{h}) .\]
+To define $\underline{h}$, we treat $h \maps F(g)(x) \to x'$ as a natural transformation:
 \[
@@
 \node (G) at (-3.5,-0.5) {$1$};
-\node (H) at (-2,0) {$F(m)$};
-\node (I) at (-2,-1) {$F(n)$};
+\node (H) at (-2,0) {$F(b)$};
+\node (I) at (-2,-1) {$F(b')$};
 \node (J) at (-2.5,-0.5) {$\scriptstyle\Downarrow\tau$};
+\path[->,font=\scriptsize,>=angle 90]
+(G) edge node [above] {$x$} (H)
+(G) edge node [below] {$x'$} (I)
+(H) edge node [right] {$F(g)$} (I);
+\end{tikzpicture}
+\]
+and let $\underline{h} \maps F'(H(g))(\underline{x}) \to \underline{x}'$ be given by this
+natural transformation:
+\[
+\begin{tikzpicture}[scale=1.5]
 \node (A) at (-0.25,-0.5) {$1$};
 \node (L) at (0.5,-0.5) {$E(1)$};
-\node (B) at (2,0) {$E(F(m))$};
-\node (D) at (2,-1) {$E(F(n))$};
+\node (B) at (2,0) {$E(F(b))$};
+\node (D) at (2,-1) {$E(F(b'))$};
 \node (C) at (1.5,-0.5) {$\scriptstyle\Downarrow E(\tau)$};
-\node (E) at (4,0) {$F^\prime(H(m))$};
-\node (F) at (4,-1) {$F^\prime(H(n))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node [above] {$\phi$} (L)
-(G) edge node [above] {$p$} (H)
-(G) edge node [below] {$q$} (I)
-(H) edge node [right] {$F(h)$} (I)
-(B) edge node [above] {$\theta_m$} (E)
-(D) edge node [above] {$\theta_n$} (F)
+\node (E) at (4,0) {$F^\prime(H(b))$};
+\node (F) at (4,-1) {$F^\prime(H(b'))$.};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node [above] {$\phi_0$} (L)
+(B) edge node [above] {$\theta_b$} (E)
+(D) edge node [above] {$\theta_{b'}$} (F)
 (E) edge node [right] {$F'(H(h))$} (F)
-(L) edge node[above]{$E(p)$} (B)
-(L) edge node[below]{$E(q)$} (D)
+(L) edge node[above]{$E(x)$} (B)
+(L) edge node[below]{$E(x')$} (D)
 (B) edge node[right]{$E(F(h))$} (D);
@@
 \]
+One can check that with these definitions $G$ is a functor.
+
+To make $G$ into a strong monoidal functor, we need to equip it with a natural isomorphism
 
@@
 \end{proof}
-
-This theorem should generalize to the case when $\theta$ is a pseudonatural equivalence, but the weaker version suffices for our application in \cref{subsec:petrirates}.
 

### 2021-06-19 cospans_new.tex
Fixed another typo in the proof of Thm. 2.1

@@
 \[  (a \xrightarrow{i} b, x) \otimes (a' \xrightarrow{i'} b', x') = (a+a' \xrightarrow{i+i'} b+b', 
-\phi_{a,b}(x,x') )\]
+\phi_{b,b'}(x,x') )\]
 where $\phi$ is the laxator for $F$.  The monoidal unit is $(0_\A \xrightarrow{!} 0_\A, 0)$
@@
 \] 
-the triple $(H,E,\theta)$ induces a double functor $\lH \maps F\lCsp \to F'\lCsp$ defined as above.
+we obtain a double functor $\lH \maps F\lCsp \to F'\lCsp$ defined as above.
 \end{thm}
@@
 \begin{proof}   
-From the lax monoidal pseudofunctor $F$ we obtain a Beck--Chevalley monoidal bifibration $\Phi \maps \A/U \to \A$ as in \cref{thm:decorated_cospans_1}.
-Similarly the lax monoidal pseudofunctor $F'$ gives a Beck--Chevalley monoidal bifibration $\Phi' \maps \A'/U' \to \A'$.
-Next we construct a strong monoidal functor $G \maps \A/U \to \A'/U'$  that makes this square commute:
+From the lax monoidal pseudofunctors $F$ and $F'$ we obtain Beck--Chevalley monoidal bifibrations $\Phi \maps \A/U \to \A$ and $\Phi' \maps \A'/U' \to \A'$ as in \cref{thm:decorated_cospans_1}.
+In what follows we construct a strong monoidal functor $G \maps \A/U \to \A'/U'$ that makes this square commute:
 \[
@@
 To make $G$ into a strong monoidal functor, we need to equip it with a natural isomorphism
+\[  \gamma \maps G(a \xrightarrow{i} b, x) \otimes G(a' \xrightarrow{i'} b', x') \; 
+\xrightarrow{\sim} \; G((a \xrightarrow{i} b, x) \otimes (a' \xrightarrow{i'} b', x')).\]
 

### 2021-06-19 cospans_new.tex
more improvements of the first part of Section 2

@@
 \cref{thm:decorated_cospans_2} gives conditions under which this double category is symmetric monoidal.
-(We recall the definition of lax monoidal pseudofunctor in \cref{subsec:bicats}, and the definition of symmetric monoidal double category in \cref{defn:double_category}.)
+These results build on earlier work of Fong \cite{Fong}, and we recommend his thesis for intuitive explanations of the key ideas \cite{FongThesis}.
 
@@
 \begin{thm}\label{thm:decorated_cospans_1}
-Let $\A$ be a category with finite colimits and $F \maps (\A,+) \to (\Cat,\times)$ a lax monoidal pseudofunctor. Then there exists a double category $F\lCsp$ in which
+Let $\A$ be a category with finite colimits and $(F,\phi,\phi_0) \maps (\A,+) \to (\Cat,\times)$ a lax monoidal pseudofunctor. Then there exists a double category $F\lCsp$ in which
 \begin{itemize}
@@
 \end{thm}
+
+Vertical composition in $F\lCsp$ is done using composition in $\A$.  The horizontal composite of $F$-decorated cospans
+\[ \left(a\to m\leftarrow b,x\in F(m)\right), \qquad \left(b\to n\leftarrow c,y\in F(n)\right)\] 
+is the composite of their underlying cospans, shown in dashed arrows here:
+\[
+\begin{tikzpicture}[scale=1.2,baseline=(current bounding box.center)]
+\node (A) at (0,0) {$a$};
+\node (B) at (1,0.8) {$m$};
+\node (C) at (2,0) {$b$};
+\node (D) at (3,0.8) {$n$};
+\node (E) at (4,0) {$c$};
+\node (F) at (2,1.6) {$m+n$};
+\node (G) at (2,2.6) {$m+_{b} n$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i$} (B)
+(C) edge node[above]{$o$} (B)
+(C) edge node [above] {$i'$} (D)
+(E) edge node [above] {$o'$} (D)
+(B) edge node [below] {$$} (F)
+(D) edge node [below] {$$} (F)
+%(B) edge[bend left=10] node [above] {$v_m\;$} (G)
+%(D) edge[bend right=10] node [above] {$\;v_n$} (G)
+(F) edge node [left] {$\psi$} (G)
+(A) edge[dashed,bend left] node [left] {} (G)
+(E) edge[dashed,bend right] node [right] {} (G);
+\end{tikzpicture}
+\]
+together with the decoration in $F(m +_b n)$ specified by this functor:
+\[  \one\cong\one \times \one \xrightarrow{x \times y} F(m) \times F(n) \xrightarrow{\phi_{m,n}} F(m+n) \xrightarrow{F(\psi)} F(m+_{b}n). \]
 
@@
 
-We prove both these theorems using the work of Shulman \cite{Shulman2008}.
-Shulman gives a general way to construct double categories from `Beck--Chevalley monoidal bifibrations'---a concept we explain in \cref{subsec:fibrations}.
+We prove both these theorems using the work of Shulman \cite{Shulman2008}, who gives a general way to construct double categories from `Beck--Chevalley monoidal bifibrations'---a concept we explain in \cref{subsec:fibrations}.
 
@@
 domain, an object of $\Fr(\Phi)$ simply amounts to a cospan in $\C$.
-Thus, in this case $\Fr(\Phi)$ is the double category of cospans in $\C$.
-We shall use variations on this idea to define double categories of decorated and structured cospans, and also prove that under certain conditions these double categories are equivalent.
-
-We start with decorated cospans, proving Theorem \ref{thm:decorated_cospans_1} and 
-\ref{thm:decorated_cospans_2} by applying Shulman's result to a particular monoidal bifibration built from a lax monoidal pseudofunctor $F \maps (A,+) \to (\Cat,\times)$.
+In this case $\Fr(\Phi)$ is the double category of cospans in $\C$.
+We shall use variations on this idea to construct double categories of decorated and structured cospans, and to prove that under certain conditions these double categories are equivalent.
+Here we consider decorated cospans, proving Theorem \ref{thm:decorated_cospans_1} and \ref{thm:decorated_cospans_2} by applying Shulman's result to a particular monoidal bifibration built from a lax monoidal pseudofunctor $F \maps (A,+) \to (\Cat,\times)$.
+
  The Grothendieck construction gives a bijection between pseudofunctors $F \maps \A \to \Cat$ and opfibrations $U \maps \inta F \to \A$.
 We need two refinements of this construction: one that gives monoidal opfibrations, and one that gives symmetric monoidal opfibrations.
-We recall the Grothendieck construction and these related concepts in \cref{subsec:fibrations}; here we simply state the result we need.
+We recall these ideas in \cref{subsec:fibrations}; here we simply state the result we need.
 
@@
 
-Now we are ready to use Shulman's result to prove  \cref{thm:decorated_cospans_1} and  \cref{thm:decorated_cospans_2}.  An $F$-decorated cospan from $a$ to $b$ 
+Now we are ready to use Shulman's result to prove Theorems \ref{thm:decorated_cospans_1} and  \ref{thm:decorated_cospans_2}.  An $F$-decorated cospan from $a$ to $b$ 
 is a cospan 
@@
 \begin{itemize}
-\item a functor $H \maps \A \to \A'$ that preserves finite limits,
+\item a functor $H \maps \A \to \A'$ that preserves finite colimits,
 \item a lax monoidal pseudofunctor $(E,\phi,\phi_0) \maps \Cat \to \Cat$, 
@@
 We described $\A/U$ and its monoidal structure in the proof of \cref{thm:decorated_cospans_1}, 
-and of course the case of $\A'/U'$ is analogous.   We define $G \maps \A/U \to \A'/U'$ as follows.  First we define $G$ on any object $(a \xrightarrow{i} b, x)$ of $\A/U$ as follows:
-\[  G(a \xrightarrow{i} b, x) \; = \; (H(a) \xrightarrow{H(i)} H(b), \underline{x}). \]
-To define $\underline{x}$, we treat the object $x \in F(b)$ as a functor 
-$x \maps 1 \to F(b)$, and let $\underline{x} \in F'(H(b))$ be given by this functor:
+and of course the case of $\A'/U'$ is analogous.   We define $G \maps \A/U \to \A'/U'$ as follows.  On objects $G$ is given by
+\[  G(a \xrightarrow{i} b, x) \; = \; (H(a) \xrightarrow{H(i)} H(b), \underline{x}), \]
+where to define $\underline{x}$ we treat $x \in F(b)$ as a functor 
+$x \maps 1 \to F(b)$ and let $\underline{x} \in F'(H(b))$ be the composite functor
 \[  1 \xrightarrow{\phi_0} E(1) \xrightarrow{E(x)} E(F(b)) \xrightarrow{\;\theta_b\;} F'(H(b)) .\]
-Next we define $G$ on any morphism
-\[   (f,g,h) \maps (a \xrightarrow{i} b, x) \; \to \; (a' \xrightarrow{i'} b', x') \]
-in $\A/U$.   For this we set
-\[   G(f,g,h) = (H(f),H(g),\underline{h}) .\]
-To define $\underline{h}$, we treat $h \maps F(g)(x) \to x'$ as a natural transformation:
+On morphisms $(f,g,h) \maps (a \xrightarrow{i} b, x) \; \to \; 
+(a' \xrightarrow{i'} b', x')$, $G$ is given by
+\[   G(f,g,h) = (H(f),H(g),\underline{h}) \]
+where to define $\underline{h}$ we treat $h \maps F(g)(x) \to x'$ as a natural transformation
 \[
@@
 \]
-and let $\underline{h} \maps F'(H(g))(\underline{x}) \to \underline{x}'$ be given by this
+and let $\underline{h} \maps F'(H(g))(\underline{x}) \to \underline{x}'$ be this
 natural transformation:
@@
 \xrightarrow{\sim} \; G((a \xrightarrow{i} b, x) \otimes (a' \xrightarrow{i'} b', x')).\]
+Note that
+\[   G(a \xrightarrow{i} b, x) \otimes G(a' \xrightarrow{i'} b', x') = 
+\left(H(a) + H(a') \xrightarrow{H(i) + H(i')} H(b) + H(b') , \; \phi'_{H(b), H(b')}(\underline{x},
+\underline{x}')\right) \]
+where $\phi'$ is the laxator for $F'$, while
+\[    G((a \xrightarrow{i} b, x) \otimes (a' \xrightarrow{i'} b', x')) =
+\left(H(a+a') \xrightarrow{H(i+i')} H(b+b'), \; \underline{\phi_{b,b'}(x,x')} \right)
+\]
+where $\phi$ is the laxator for $F$.  Since $H$ preserves finite colimits, the isomorphism
+$\gamma$ is obvious except
 
@@
 
-\section{Structured versus decorated cospans} \label{EquivDoubleCats}
-
-In \cite{BC}, the first two authors introduce the symmetric monoidal double category of structured cospans as a formalism to capture open networks.
-One of the main goals of this paper is to provide a monoidal double isomorphism between this double category and that of decorated cospans, described in detail in \cref{DecCospansDoubleCat}.
-We first recall the double category of structured cospans, along with a new construction of it.
+\section{Structured cospans} \label{Structured}
+
+In \cite{BC}, the first two authors introduced structured cospans as a formalism to describe open networks.   Here we recall this and give a new construction of the double category of structured
+cospans that, in the next section, we use to clarify their relation to decorated cospans.
 
@@
 
-The following theorem establishes an isomorphism between structured and decorated cospan double categories under certain conditions.
+\section{Structured versus decorated cospans} \label{EquivDoubleCats}
+
+We now show that structured and decorated cospan double categories are isomorphic under certain conditions.
 Let $\Rex$ be the 2-category of categories with finite colimits, functors preserving finite colimits, and natural transformations.

### 2021-06-19 cospans_new.tex
I added more explanation of decorated cospan double categories after Thm. 2.1.

@@
 \cref{thm:decorated_cospans_2} gives conditions under which this double category is symmetric monoidal.
-These results build on earlier work of Fong \cite{Fong}, and we recommend his thesis for intuitive explanations of the key ideas \cite{FongThesis}.
+These results build on earlier work of Fong \cite{Fong}, and we recommend his thesis for intuitive explanations of the fundamental ideas \cite{FongThesis}.
 
@@
 a commutative diagram in $\A$ of the form
-\begin{equation}\label{eq:mapofdec}
+\[
 \begin{tikzpicture}[scale=1.5,baseline=(current bounding box.center)]
@@
 \end{tikzpicture}
-\end{equation}
+\]
 together with a \define{decoration morphism} $\tau \maps F(h)(x) \to x'$ in $F(m')$.
@@
 \[ \left(a\to m\leftarrow b,x\in F(m)\right), \qquad \left(b\to n\leftarrow c,y\in F(n)\right)\] 
-is the composite of their underlying cospans, shown in dashed arrows here:
+is the usual composite via pushout of their underlying cospans, shown in dashed arrows here:
 \[
@@
 \]
-together with the decoration in $F(m +_b n)$ specified by this functor:
-\[  \one\cong\one \times \one \xrightarrow{x \times y} F(m) \times F(n) \xrightarrow{\phi_{m,n}} F(m+n) \xrightarrow{F(\psi)} F(m+_{b}n). \]
+together with the decoration in $y \odot x \in F(m +_b n)$ specified by this functor:
+\[  \one\cong\one \times \one \xrightarrow{x \times y} F(n) \times F(m) \xrightarrow{\phi_{n,m}} F(m+n) \xrightarrow{F(\psi)} F(m +_{b}n). \]
+Given two horizontally composable maps of $F$-decorated cospans $\alpha$ and $\beta$:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0.5) {$a$};
+\node (A') at (0,-0.5) {$a'$};
+\node (B) at (1,0.5) {$m$};
+\node (C) at (2,0.5) {$b$};
+\node (C') at (2,-0.5) {$b'$};
+\node (D) at (1,-0.5) {$m'$};
+\node (E) at (3,0.5) {$x \in F(m)$};
+\node (F) at (3,-0.5) {$x' \in F(m')$};
+\node (G) at (4,0.5) {$b$};
+\node (H) at (5,0.5) {$n$};
+\node (I) at (6,0.5) {$c$};
+\node (G') at (4,-0.5) {$b'$};
+\node (H') at (5,-0.5) {$n'$};
+\node (I') at (6,-0.5) {$c'$};
+\node (J) at (7,0.5) {$y \in F(n)$};
+\node (K) at (7,-0.5) {$y' \in F(n')$};
+\node (L) at (1,-1) {$\tau_\alpha \maps F(h_1)(x) \to x'$};
+\node (M) at (5,-1) {$\tau_\beta \maps F(h_2)(y) \to y'$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i_1$} (B)
+(C) edge node[above]{$o_1$} (B)
+(A) edge node[left]{$f$} (A')
+(C) edge node[right]{$g$} (C')
+(A') edge node[above] {$i_1'$} (D)
+(C') edge node[above] {$o_1'$} (D)
+(B) edge node [left] {$h_1$} (D)
+(G) edge node [above] {$i_2$} (H)
+(G) edge node [left] {$g$} (G')
+(H) edge node [left] {$h_2$} (H')
+(G') edge node [above] {$i_2'$} (H')
+(I) edge node [above] {$o_2$} (H)
+(I) edge node [right] {$k$} (I')
+(I') edge node [above] {$o_2'$} (H');
+\end{tikzpicture}
+\]
+their composite $\beta\odot \alpha$ is the horizontal composite of the two maps of cospans in $\A$:
+\[
+\begin{tikzpicture}[scale=1.5,baseline=(current bounding box.center)]
+\node (A) at (0,0.5) {$a$};
+\node (A') at (0,-0.5) {$a'$};
+\node (B) at (1.5,0.5) {$m+_{b} n$};
+\node (C) at (3,0.5) {$c$};
+\node (C') at (3,-0.5) {$c'$};
+\node (D) at (1.5,-0.5) {$m'+_{b'}n'$};
+\node (E) at (4.5,0.5) {$y \odot x \in F(m+_b n)$};
+\node (F) at (4.5,-0.5) {$y' \odot x' \in F(m' +_{b'} n')$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{} (B)
+(C) edge node[above]{} (B)
+(A) edge node[left]{$f$} (A')
+(C) edge node[right]{$k$} (C')
+(A') edge node [above]{} (D)
+(C') edge node [above]{} (D)
+(B) edge node [left] {$h_1 +_g h_2$} (D);
+\end{tikzpicture}
+\]
+together with the decoration morphism $\tau_{\beta \odot \alpha} \maps F(h_1 +_g h_2)(y \odot x) \to (y' \odot x')$ specified by this natural transformation:
+\[
+\begin{tikzpicture}[scale=1.7,baseline=(current bounding box.center)]
+\node (A) at (4.75,0) {$\scriptstyle\Downarrow \tau_\alpha \times \tau_\beta$};
+\node (D) at (3,0) {$\one \cong \one \times \one$};
+\node (E) at (5.5,0.5) {$F(m) \times F(n)$};
+\node () at (6.5,0) {$\stackrel{\phi_{h_1,h_2}}{\cong}$};
+\node () at (8.5,0) {$\cong$};
+\node (E') at (5.5,-0.5) {$F(m') \times F(n')$};
+\node (B) at (7.5,0.5) {$F(m+n)$};
+\node (B') at (7.5,-0.5) {$F(m' + n')$};
+\node (C) at (9.5,0.5) {$F(m+_{b} n)$};
+\node (C') at (9.5,-0.5) {$F(m' +_{b'} n')$};
+\path[->,font=\scriptsize,>=angle 90]
+(E) edge node [above] {$\phi_{m,n}$} (B)
+(E') edge node [above] {$\phi_{m',n'}$} (B')
+(B) edge node [above] {$F(\psi)$} (C)
+(B') edge node [above] {$F(\psi)$} (C')
+(C) edge node  [fill=white] {$F(h_1 +_g h_2)$} (C')
+(B) edge node [fill=white] {$F(h_1 + h_2)$} (B')
+(D) edge node [above] {$x \times y$} (E)
+(D) edge node [below] {$x' \times y'$} (E')
+(E) edge node [fill=white] {$F(h_1) \times F(h_2)$} (E');
+\end{tikzpicture}
+\]
+where the middle isomorphism is \cref{eq:pseudonaturality} from pseudonaturality of $\phi$ and the right-hand isomorphism comes from the pseudofunctoriality of $F$.
 
@@
 \item of two horizontal 1-cells $(a \to m \leftarrow b ,x \in F(m))$ and $(c \to n \leftarrow d, y\in F(n))$ is
-\begin{equation}\label{eq:tensordecoration}
+\[
 \begin{tikzcd}
@@
 \end{tikzcd}\qquad x \otimes y:=  \phi_{m,n}(x,y) \in F(m + n) 
-\end{equation}
+\]
 \item of two 2-morphisms $\alpha$ and $\beta$ is:
@@
 Now we are ready to use Shulman's result to prove Theorems \ref{thm:decorated_cospans_1} and  \ref{thm:decorated_cospans_2}.  An $F$-decorated cospan from $a$ to $b$ 
-is a cospan 
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$a$};
-\node (B) at (1,0) {$m$};
-\node (C) at (2,0) {$b$};
-%\node (D) at (2.6,0) {$x \in F(m))$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$$} (B)
-(C) edge node[above]{$$} (B);
-\end{tikzpicture}
-\]
-in $\A$ together with an object $x \in F(m)$.
+is a cospan $a \to m \leftarrow b$ in $\A$ together with an object $x \in F(m)$.
 This can be seen as a pair $(e \to m, x \in F(m))$ such that $e$ equals $a + b$.

### 2021-06-20 cospans_new.tex
Completed proof of Theorem 2.5, but see stuff in red.

@@
 \] 
-we obtain a double functor $\lH \maps F\lCsp \to F'\lCsp$ defined as above.
+we obtain a double functor $\lH \maps F\lCsp \to F'\lCsp$ defined as above.  If $F, F'$ and $E$ are symmetric, then $\|H \maps F\lCsp \to F'\lCsp$ is a symmetric monoidal double functor. 
 \end{thm}
@@
 
-To make $G$ into a strong monoidal functor, we need to equip it with a natural isomorphism
+To make $G$ into a monoidal functor, we need to equip it with a laxator
 \[  \gamma \maps G(a \xrightarrow{i} b, x) \otimes G(a' \xrightarrow{i'} b', x') \; 
-\xrightarrow{\sim} \; G((a \xrightarrow{i} b, x) \otimes (a' \xrightarrow{i'} b', x')).\]
+\to \; G((a \xrightarrow{i} b, x) \otimes (a' \xrightarrow{i'} b', x')).\]
 Note that
@@
 \]
-where $\phi$ is the laxator for $F$.  Since $H$ preserves finite colimits, the isomorphism
-$\gamma$ is obvious except
-
-The laxator is given by the following natural isomorphism between $\theta_m E(p) \phi \times \theta_n E(q) \phi$ and $\theta_{m+n} E(p \times q) \phi$:
-\[
-\begin{tikzpicture}[scale=1.5]
-\hspace{-.6in}
-\node () at (3,-0.5) {$\scriptscriptstyle{\stackrel{E_{p,q}} \cong}$};
-\node () at (1.25,-0.5) {$\scriptscriptstyle{\stackrel{\lambda} \cong}$};
-\node (L1) at (0.5,0) {$\scriptscriptstyle{1 \times E(1)}$};
-\node (L2) at (0.5,-1) {$\scriptscriptstyle{E(1)}$};
-\node (K) at (-1,0) {$\scriptscriptstyle{1 \times 1}$};
-\node (K2) at (-1,-1) {$\scriptscriptstyle{1}$};
+where $\phi$ is the laxator for $F$.  Since $H$ preserves finite colimits, the laxator
+$\gamma$ is obvious except for the morphism from $\phi'_{H(b), H(b')}(\underline{x},
+\underline{x}')$ to $\underline{\phi_{b,b'}(x,x')}$.   This is given by the following natural
+transformation:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node () at (3,-0.5) {$\scriptscriptstyle{\stackrel{E_{x,x'}} \cong}$};
+\node () at (1.5,-0.5) {$\scriptscriptstyle{\stackrel{\lambda} \cong}$};
+\node (L1) at (1,0) {$\scriptscriptstyle{1 \times E(1)}$};
+\node (L2) at (1,-1) {$\scriptscriptstyle{E(1)}$};
+\node (K) at (0,0) {$\scriptscriptstyle{1 \times 1}$};
+\node (K2) at (0,-1) {$\scriptscriptstyle{1}$};
 \node (B) at (2,0) {$\scriptscriptstyle{E(1) \times E(1)}$};
 \node (D) at (2,-1) {$\scriptscriptstyle{E(1 \times 1)}$};
-\node (E) at (4,0) {$\scriptscriptstyle{E(F(m)) \times E(F(n))}$};
-\node (F) at (4,-1) {$\scriptscriptstyle{E(F(m) \times F(n))}$};
-\node (G) at (7,0) {$\scriptscriptstyle{F'(H(m)) \times F'(H(n))}$};
-\node (H) at (10,0) {$\scriptscriptstyle{F'(H(m)+H(n))}$};
-\node (I) at (7,-1) {$\scriptscriptstyle{E(F(m+n))}$};
-\node (J) at (10,-1) {$\scriptscriptstyle{F'(H(m+n))}$};
+\node (E) at (4,0) {$\scriptscriptstyle{E(F(b)) \times E(F(b'))}$};
+\node (F) at (4,-1) {$\scriptscriptstyle{E(F(b) \times F(b'))}$};
+\node (G) at (6,0) {$\scriptscriptstyle{F'(H(b)) \times F'(H(b'))}$};
+\node (H) at (8,0) {$\scriptscriptstyle{F'(H(b)+H(b'))}$};
+\node (I) at (6,-1) {$\scriptscriptstyle{E(F(b+b'))}$};
+\node (J) at (8,-1) {$\scriptscriptstyle{F'(H(b+b'))}$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (K) edge node [above] {$1 \times E_0$} (L1)
-(K2) edge node [above] {$E_0$} (L2)
-(H) edge node [right] {$F'(H_{m,n})$} (J)
-(E) edge node [above] {$\theta_m \times \theta_n$} (G)
-(G) edge node [above] {$\phi'_{H(m),H(n)}$} (H) 
-(F) edge node [above] {$E(\phi_{m,n})$} (I)
-(I) edge node [above] {$\theta_{m+n}$} (J)
-(B) edge node [above] {$E(p) \times E(q)$} (E)
-(D) edge node [above] {$E(p \times q)$} (F)
-(E) edge node [right] {$E_{F(m),F(n)}$} (F)
+(K2) edge node [below] {$E_0$} (L2)
+(H) edge node [right] {$F'(H_{b,b'})$.} (J)
+(E) edge node [above] {$\theta_b \times \theta_{b'}$} (G)
+(G) edge node [above] {$\phi'_{H(b),H(b')}$} (H) 
+(F) edge node [below] {$E(\phi_{b,b'})$} (I)
+(I) edge node [below] {$\theta_{b+b'}$} (J)
+(B) edge node [above] {$E(x) \times E(x')$} (E)
+(D) edge node [below] {$E(x \times x')$} (F)
+(E) edge node [right] {$E_{F(b),F(b')}$} (F)
 (L1) edge node[above]{$E_0 \times 1$} (B)
 (L1) edge node [left] {$\lambda$} (L2)
-(L2) edge node[above]{$E(\lambda^{-1})$} (D)
+(L2) edge node[below]{$E(\lambda^{-1})$} (D)
 (B) edge node[right]{$E_{1,1}$} (D);
@@
 \]
-and we also have a natural isomorphism between $0_{\inta F'}$ and $G(0_{\inta F})$ given by:
+We also need a natural transformation expressing lax preservation of the unit object by $G$, which
+is defined similarly.
+One can show that this laxator and unit morphism satisfy the coherence laws of a lax monoidal functor, and they are invertible, so $G$ is strong monoidal functor.
+\john{If furthermore $F, F'$ and $E$ are symmetric, one can check that $G$ is symmetric monoidal, and that $\lH$ is a symmetric monoidal double functor.}
+\end{proof}
+
+\iffalse
+we have a natural isomorphism between $0_{\inta F'}$ and $G(0_{\inta F})$ given by:
 \[
@@
 \]
-One can show that this laxator and unit morphism satisfy the four required coherence laws of a symmetric strong monoidal functor.
-\end{proof}
+\fi
 

### 2021-06-20 cospans_new.tex
Completed proof of Thm. 2.5, but see stuff in red.
Working on the proof of Thm. 3.1

@@
 % in LaTeX
-% 2021/6/8 - Finishing up
+% 2021/6/20 - Finishing up
 
@@
 
-Next, one can check that $\Phi$ is a fibration.  Given a morphism $f \maps a \to a'$ in $\A$ and an object $(a' \xrightarrow{i'} b', x') \in \A/U$ over $a'$, a cartesian lifting of $f$ is given by 
+Next, one can check that $\Phi$ is a fibration.
+Given a morphism $f \maps a \to a'$ in $\A$ and an object $(a' \xrightarrow{i'} b', x') \in \A/U$ over $a'$, a cartesian lifting of $f$ to this object is given by
 \[ (f,1,1) \maps (a \xrightarrow{i' f} b' , x')\; \to \; (a' \xrightarrow{i'} b', x'). \]
-Denoting this cartesian lifting by $\textnormal{cart}(f)$, the tensor product of $\A/U$ strictly preserves such cartesian liftings in the sense that $\textnormal{cart}(f_1) \otimes \textnormal{cart}(f_2)=\textnormal{cart}(f_1+f_2)$.
+Denoting the cartesian lifting of $f$ to the object $z \in \A/U$ by $\mathrm{Cart}(f,z)$, the tensor product of $\A/U$ strictly preserves such cartesian liftings in the sense that $\mathrm{Cart}(f_1,z_1) \otimes \mathrm{Cart}(f_2,z_2)=\mathrm{Cart}(f_1 \otimes f_2, z_1 \otimes z_2)$.
 
@@
 It follows that $\Phi$ is a bifibration.
-Denoting the cocartesian lifting of a morphism $f$ by $\textnormal{cocart}(f)$, we have that $\textnormal{cocart}(f_1) \otimes \textnormal{cocart}(f_2) \cong \textnormal{cocart}(f_1+f_2)$ by the universal map between two colimits of the same diagram.
+Denoting the cocartesian lifting of a morphism $f$ to an object $z \in \A/U$ by $\mathrm{Cocart}(f,z)$, we have that $\mathrm{Cocart}(f_1,z_1) \otimes \mathrm{Cocart}(f_2,z_2) \cong \mathrm{Cocart}(f_1 \otimes f_2,z_1 \otimes z_2)$ by the universal map between two colimits of the same diagram.
 Thus, $\Phi$ is a monoidal bifibration.
@@
 \]
-as defined at the end of \cref{subsec:fibrations}.   We need to prove that when the square in $\A$ is 
+defined in Equation \eqref{theta}.   We need to prove that when the square in $\A$ is 
 a pushout, $\theta$ is a natural isomorphism.
@@
 \label{thm:functoriality}
-Given categories $\A$ and $\A'$ with finite colimits, lax monoidal pseudofunctors $F, F' \maps (\A',+) \to (\Cat,\times)$, a finite colimit preserving functor $H \maps \A \to \A'$, a lax monoidal pseudofunctor $E \maps (\Cat,\times) \to (\Cat,\times)$ and a {\john monoidal???} natural isomorphism $\theta$ as in the following diagram:
+Given categories $\A$ and $\A'$ with finite colimits, lax monoidal pseudofunctors $F, F' \maps (\A',+) \to (\Cat,\times)$, a finite colimit preserving functor $H \maps \A \to \A'$, a lax monoidal pseudofunctor $E \maps (\Cat,\times) \to (\Cat,\times)$ and a natural isomorphism $\theta$ as in the following diagram:
 \[
@@
 
-In \cite{BC}, the first two authors introduced structured cospans as a formalism to describe open networks.   Here we recall this and give a new construction of the double category of structured
-cospans that, in the next section, we use to clarify their relation to decorated cospans.
+Structured cospans are an alternative approach to equipping the apex of a cospan with 
+extra data \cite{BC}.
+Here we recall this formalism and give a new construction of the double category of structured cospans that clarifies their relation to decorated cospans.
+This new construction again uses Shulman's \cref{lem:shulman}.
 
@@
 \end{itemize}
-Composition of horizontal 1-cells and 2-cells is done using pushouts in $\X$, and the
-symmetric monoidal structure is defined using finite coproducts in $\A$ and $\X$: 
-the tensor product of two horizontal 1-cells is
-\begin{equation}\label{eq:tensorstuctured}
+Vertical composition is done using composition in $\A$, while horizontal composition 
+is done using pushouts in $\X$. The tensor product of two horizontal 1-cells is
+\[
 \begin{tikzcd}[column sep={.4in,between origins}, row sep=.08in]
@@
 \end{tikzcd}
-\end{equation}
-using that $L$ preserves finite coproducts.
+\]
+where $i + i'$ and $o + o'$ are defined using the fact that $L$ preserves binary coproducts, and tensor product of two 2-morphisms is given by:
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (E) at (3,0) {$L(a_1)$};
+\node (F) at (5,0) {$L(b_1)$};
+\node (G) at (4,0) {$x_1$};
+\node (E') at (3,-1) {$L(a_2)$};
+\node (F') at (5,-1) {$L(b_2)$};
+\node (G') at (4,-1) {$x_2$};
+\node (E'') at (6.5,0) {$L(a_1')$};
+\node (F'') at (8.5,0) {$L(b_1')$};
+\node (G'') at (7.5,0) {$x_1'$};
+\node (E''') at (6.5,-1) {$L(a_2')$};
+\node (F''') at (8.5,-1) {$L(b_2')$};
+\node (G''') at (7.5,-1) {$x_2'$};
+\node (X) at (5.75,-0.5) {$\otimes$};
+\node (E'''') at (4,-2) {$L(a_1 + a_1')$};
+\node (F'''') at (7.5,-2) {$L(b_1 + b_1')$};
+\node (G'''') at (5.75,-2) {$x_1 + x_1'$};
+\node (E''''') at (4,-3) {$L(a_2 + a_2')$};
+\node (F''''') at (7.5,-3) {$L(b_2 + b_2').$};
+\node (G''''') at (5.75,-3) {$x_2 + x_2'$};
+\node (Y) at (3,-2.5) {$=$};
+\path[->,font=\scriptsize,>=angle 90]
+(F) edge node[above]{$o_1$} (G)
+(E) edge node[left]{$L(f)$} (E')
+(F) edge node[right]{$L(g)$} (F')
+(G) edge node[left]{$\alpha$} (G')
+(E) edge node[above]{$i_1$} (G)
+(E') edge node[below]{$i_2$} (G')
+(F') edge node[below]{$o_2$} (G')
+(F'') edge node[above]{$o_1'$} (G'')
+(E'') edge node[left]{$L(f')$} (E''')
+(F'') edge node[right]{$L(g')$} (F''')
+(G'') edge node[left]{$\alpha'$} (G''')
+(E'') edge node[above]{$i_1'$} (G'')
+(E''') edge node[below]{$i_2'$} (G''')
+(F''') edge node[below]{$o_2'$} (G''')
+(F'''') edge node[above]{$o_1 + o_1'$} (G'''')
+(E'''') edge node[left]{$L(f + f')$} (E''''')
+(F'''') edge node[right]{$L(g + g')$} (F''''')
+(G'''') edge node[left]{$\alpha + \alpha'$} (G''''')
+(E'''') edge node[above]{$i_1 + i_1'$} (G'''')
+(E''''') edge node[below]{$i_2 + i_2'$} (G''''')
+(F''''') edge node[below]{$o_2 + o_2'$} (G''''');
+\end{tikzpicture}
+\]
 \end{thm}
@@
 
-{\bf NEW PROOF HERE.}  We apply \cref{lem:shulman} to $L/X \to A$.   Why is this a fibration, cofibration, Beck--Chevalley and symmetric monoidal?
-
-The proof is analogous to the proof of \cref{thm:decorated_cospans_1} in that we apply \cref{lem:shulman} to the Beck-Chevalley symmetric monoidal bifibration $\Psi \maps (L/\X) \to \A$ which we now define.
-Let $(L/\X)$ be the comma category in which:
-\begin{enumerate}
-\item{an object is a triple $(a,x,L(a) \xrightarrow{I} x)$, and}
-\item{a morphism from $(a,x,L(a) \xrightarrow{I} x)$ to $(a',x',L(a') \xrightarrow{I'} x')$ is a pair of morphisms $f \maps a \to a'$ and $\alpha \maps x \to x'$ such that the following square commutes:
+Our new proof is analogous to that of \cref{thm:decorated_cospans_1} in that we apply \cref{lem:shulman} to a Beck--Chevalley symmetric monoidal bifibration $\Psi \maps L/\X \to \A$,
+and define ${}_L \lCsp(\X)$ to be $\Fr(\Psi)$.    First, note that in the comma category $L/\X$:
+\begin{itemize}
+\item an object is a pair $(a, L(a) \xrightarrow{} x)$ consisting of an object $a \in \A$ and a morphism $L(a) \xrightarrow{i} x$ in $\X$;
+\item a morphism from $(a,L(a) \xrightarrow{i} x)$ to $(a',L(a') \xrightarrow{i'} x')$ is a pair $(f,g)$ of morphisms $f \maps a \to a'$ and $g \maps x \to x'$ such that this square commutes:
 \[
@@
 \node (A) at (0,0) {$L(a)$};
-\node (B) at (1,0) {$L(a')$};
+\node (B) at (1.5,0) {$L(a')$};
 \node (C) at (0,-1) {$x$};
-\node (D) at (1,-1) {$x'$};
+\node (D) at (1.5,-1) {$x'$.};
 \path[->,font=\scriptsize,>=angle 90]
 (A) edge node[above]{$L(f)$} (B)
-(A) edge node[left]{$I$} (C)
-(B) edge node[right]{$I'$} (D)
-(C) edge node[above]{$\alpha$} (D);
-\end{tikzpicture}
-\]}
-\end{enumerate}
-The functor $\Psi$ is defined on objects by $\Psi(a,x,L(a) \xrightarrow{I} x)=a$ and on morphisms by $\Psi(f,\alpha)=f$.
-The monoidal structure of $(L/\X)$ is similar to the monoidal structure of $(\A/U)$ of \cref{thm:decorated_cospans_1} in that the tensor product of two objects $(a_1,x_1,L(a_1) \xrightarrow{I_1} x_1)$ and $(a_2,x_2,L(a_2) \xrightarrow{I_2} x_2)$ is given by
-$$(a_1,x_1,L(a_1) \xrightarrow{I_1} x_1) \otimes (a_2,x_2,L(a_2) \xrightarrow{I_1} x_2)=(a_1+a_2,x_1+x_2,L(a_1+a_2) \xrightarrow{I_1+I_2} x_1+x_2)$$
-where again the natural isomorphism $L(a_1)+L(a_2) \cong L(a_1+a_2)$ is implicit.
-The monoidal unit is ${(0_\A,0_\X,{L(0_\A) \to 0_\X})}$, and it is clear that $\Psi$ is a strict monoidal functor using this tensor product.
-
-The functor $\Psi$ is both a fibration and an opfibration. Given a morphism $f \maps a \to b$ in $\A$ with ${(b,x,L(b) \xrightarrow{I} x)}$ in $\X$ over $b$, the cartesian lifting of $f$ is given by
-$$(f,\id_x) \maps (a,x,L(a) \xrightarrow{I \circ L(f)} x) \to (b,x,L(b) \xrightarrow{I} x).$$
-With $(a,x,L(a) \xrightarrow{I} x)$ in $\X$ over $a$, the cocartesian lifting of $f$ is given by
-$$(f,\kappa) \maps (a,x,L(a) \xrightarrow{I} x) \to (b,x+_{L(a)} L(b),L(b) \xrightarrow{\theta} x+_{L(a)} L(b))$$
-where $\kappa$ and $\theta$ are as in the following diagram:
+(A) edge node[left]{$i$} (C)
+(B) edge node[right]{$i'$} (D)
+(C) edge node[below]{$g$} (D);
+\end{tikzpicture}
+\]
+\end{itemize}
+Next, we define the functor $\Psi \maps L/\X \to \A$ on objects by $\Psi(a,L(a) \xrightarrow{i} x)=a$ and on morphisms by $\Psi(f,g)=f$.
+
+The monoidal structure of $L/\X$ is similar to the monoidal structure of $\A/U$ of \cref{thm:decorated_cospans_1} in that the tensor product of two objects $(a,L(a) \xrightarrow{i} x)$ and $(a,L(a) \xrightarrow{i'} x')$ is given by
+\[  (a,L(a) \xrightarrow{i} x) \otimes (a',L(a') \xrightarrow{i'} x')=(a+a',x+x',L(a+a') \xrightarrow{i+i'} x+x') \]
+where again the natural isomorphism $L(a)+L(a') \cong L(a+a')$ is implicit.
+The monoidal unit is ${(0_\A,0_\X,{L(0_\A) \to 0_\X})}$.
+It is clear that $\Psi \maps (L/\X, \otimes) \maps (\A,+)$ is a strict monoidal functor.
+{\john Is the tensor product on $L/\X$ also just $+$?
+If so, let's say that and call it $+$.}
+
+The functor $\Psi$ is both a fibration and an opfibration.
+Suppose we are given a morphism $f \maps a \to b$ in $\A$.
+For any object $(b,L(b) \xrightarrow{i} x) \in L/\X$ over $b$, a cartesian lifting of $f$ is given by
+\[ (f,1_x) \maps (a,L(a) \xrightarrow{i L(f)} x) \; \to \; (b,L(b) \xrightarrow{i} x) . \]
+For any object $(a,L(a) \xrightarrow{i} x)$ in $L/\X$ over $a$, a cocartesian lifting of $f$ is given by
+\[ (f,\kappa) \maps (a,L(a) \xrightarrow{i} x) \to (b,L(b) \xrightarrow{\theta} x+_{L(a)} L(b)) \]
+where $\kappa$ and $\theta$ arise from the pushout in this diagram:
 \[
@@
 \]
-Both cartesian and cocartesian liftings are preserved by the tensor product of $(L/\X)$.
-
-Lastly, we show that $\Psi \maps (L/ \X) \to \A$ satisfies the Beck-Chevalley condition. Given a pushout square in $\A$:
+This diagram also gives the proof that $(f,\kappa)$ is a cocartesian lifting of $f$.
+Both cartesian and cocartesian liftings are clearly preserved by the tensor product of $L/\X$, so
+$\Psi$ is a monoidal bifibration.
+
+Lastly, we show that $\Psi \maps L/\X \to \A$ satisfies the Beck--Chevalley condition. 
+For this, given a pushout square in $\A$:
 \[
@@
 \]
-we show that the following square commutes up to a natural isomorphism:
+we need to show that the natural transformation 
 \[
@@
 \node (A) at (0,0) {$(L/\X)_a$};
-\node (B) at (2,0) {$(L/\X)_b$};
+\node (B) at (1.5,0) {$(L/\X)_b$};
 \node (C) at (0,-1) {$(L/\X)_c$};
-\node (D) at (2,-1) {$(L/\X)_d$};
-\node (E) at (1,-0.5) {$\cong$};
+\node (D) at (1.5,-1) {$(L/\X)_d$};
+\node (E) at (0.75,-0.5) {$\Searrow \theta$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (B) edge node[right]{$g_!$} (D)
-(D) edge node[above]{$f^*$} (C);
-\end{tikzpicture}
-\]
-Let $(b,x,L(b) \xrightarrow{I} x)$ be an object of $(L/\X)_b$.
-Going right, we precompose with $L(h) \maps L(a) \to L(b)$ to obtain the object $(a,x,L(a) \xrightarrow{I \circ L(h)} x)$ in $(L/\X)_a$.
-Then, going down, we pushforward along $L(k) \maps L(a) \to L(c)$:
+(D) edge node[below]{$f^*$} (C);
+\end{tikzpicture}
+\]
+defined in Equation \eqref{theta} is an isomorphism.
+Let $(b,L(b) \xrightarrow{i} x)$ be an object of $(L/\X)_b$.
+Going left, we precompose with $L(h) \maps L(a) \to L(b)$ to obtain the object $(a,L(a) \xrightarrow{i  L(h)} x)$ in $(L/\X)_a$.
+Then going down, we push forward along $L(k) \maps L(a) \to L(c)$:
 \[
@@
 \node (A) at (0,0) {$L(a)$};
-\node (B) at (2,0) {$x$};
+\node (B) at (1.5,0) {$x$};
 \node (C) at (0,-1) {$L(c)$};
-\node (D) at (2,-1) {$L(c)+_{L(a)}x$};
+\node (D) at (1.5,-1) {$L(c)+_{L(a)}x$};
+\node at (1.1,-0.7) {\Large{$\ulcorner$}};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-to obtain the object $(c,L(c)+_{L(a)} x,L(c) \xrightarrow{\psi} L(c)+_{L(a)} x)$ in $(L/ \X)_c$.
-For the other route, first going down, we pushforward the object $(b,x,L(b) \xrightarrow{I} x)$ along $L(g) \maps L(b) \to L(d)$ by taking the following pushout:
+to obtain the object $(c,L(c) \xrightarrow{\psi} L(c)+_{L(a)} x)$ of $(L/ \X)_c$.
+For the other route, first going down, we push the object $(b,x,L(b) \xrightarrow{I} x)$ forward along $L(g) \maps L(b) \to L(d)$ by taking the following pushout:
 \[
@@
 \node (A) at (0,0) {$L(b)$};
-\node (B) at (2,0) {$x$};
+\node (B) at (1.5,0) {$x$};
 \node (C) at (0,-1) {$L(d)$};
-\node (D) at (2,-1) {$L(d)+_{L(b)}x$};
+\node (D) at (1.5,-1) {$L(d)+_{L(b)}x$};
+\node at (1.1,-0.7) {\Large{$\ulcorner$}};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (B) edge node[right]{$$} (D)
-(C) edge node[above]{$\theta$} (D);
-\end{tikzpicture}
-\]
-which yields the object $(d,L(d)+_{L(b)}x,L(d) \xrightarrow{\theta} L(d)+_{L(b)} x)$ of $(L/\X)_d$.
-We then precompose with $L(f) \maps L(c) \to L(d)$ to obtain the object $(c,L(d)+_{L(b)} x,L(c) \xrightarrow{\theta \circ L(f)} L(d)+_{L(b)} x)$ of $(L/\X)_c$.
+(C) edge node[above]{$\phi$} (D);
+\end{tikzpicture}
+\]
+which yields the object $(d,L(d) \xrightarrow{\theta} L(d)+_{L(b)} x)$ of $(L/\X)_d$.
+Then going left, we precompose with $L(f) \maps L(c) \to L(d)$ to obtain the object $(c,L(c) \xrightarrow{\phi L(f)} L(d)+_{L(b)} x)$ of $(L/\X)_c$.
 
@@
 The first pushout square above exhibits $L(c)+_{L(a)}x$ as a colimit of the span $$L(c) \xleftarrow{L(k)} L(a) \xrightarrow{I \circ L(h)} x$$in $\X$.
-On the other hand, as $L$ is a left adjoint, $L$ preserves pushout squares, and so the following square is also a pushout:
+On the other hand, as $L$ preserves finite colimits, $L$ preserves pushout squares, and so the following square is also a pushout:
 \[
@@
 which exhibits $L(d)+_{L(b)} x$ also as a colimit of the same span in $\X$, and hence the desired natural isomorphism between our two objects of $(L /\X)_c$.
-Thus $\Psi$ satisfies the Beck-Chevalley condition.
+Thus $\Psi$ satisfies the Beck--Chevalley condition.
 \end{proof}
@@
 \begin{defn}
- If $\X$ and $\A$ are monoidal categories, a \define{monoidal} bifibration $\Phi \maps \X \to \A$ is a bifibration that is also a strict monoidal functor, such that the tensor product of $\A$ preserves cartesian and cocartesian liftings.
+ If $\X$ and $\A$ are monoidal categories, a \define{monoidal} bifibration $\Phi \maps \X \to \A$ is a bifibration that is also a strict monoidal functor, such that the tensor product preserves cartesian and cocartesian liftings.
 Similarly, if $\C$ and $\A$ are symmetric monoidal, a \define{symmetric monoidal} bifibration is a bifibration $\Phi \maps \C \to \A$ that is a symmetric strict monoidal functor.
@@
 $g_!$ and $g^\ast$ and the counit of the adjunction between $k_!$ and $k^\ast$:
-\[    k_! h^\ast \To k_! h^\ast g^\ast g_! = k_! k^\ast f^\ast g^! \To f^\ast g_! .\] 
+\begin{equation}
+\label{theta}
+   k_! h^\ast \To k_! h^\ast g^\ast g_! = k_! k^\ast f^\ast g^! \To f^\ast g_! . 
+\end{equation}
 If $\theta$ is a natural isomorphism whenever the original square in $\A$ is

### 2021-06-21 cospans_new.tex
completed proof of Thm. 3.1.

@@
 (B) edge node[right]{$g$} (D)
-(C) edge node[above]{$f$} (D);
+(C) edge node[below]{$f$} (D);
 \end{tikzpicture}
@@
 (B) edge node[right]{$$} (D)
-(C) edge node[above]{$\psi$} (D);
+(C) edge node[below]{$\psi$} (D);
 \end{tikzpicture}
@@
 (B) edge node[right]{$$} (D)
-(C) edge node[above]{$\phi$} (D);
+(C) edge node[below]{$\phi$} (D);
 \end{tikzpicture}
@@
 
-To establish a natural isomorphism between the two objects $(c,L(c)+_{L(a)} x,L(c) \xrightarrow{\psi} L(c)+_{L(a)} x)$ and $(c,L(d)+_{L(b)} x,L(c) \xrightarrow{\theta \circ L(f)} L(d)+_{L(b)} x)$ in $(L/\X)_c$, it suffices to establish a natural isomorphism between the objects $L(c)+_{L(a)} x$ and $L(d)+_{L(b)} x$ in $\X$.
-The first pushout square above exhibits $L(c)+_{L(a)}x$ as a colimit of the span $$L(c) \xleftarrow{L(k)} L(a) \xrightarrow{I \circ L(h)} x$$in $\X$.
-On the other hand, as $L$ preserves finite colimits, $L$ preserves pushout squares, and so the following square is also a pushout:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$L(a)$};
-\node (B) at (1,0) {$L(b)$};
-\node (C) at (0,-1) {$L(c)$};
-\node (D) at (1,-1) {$L(d)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$L(h)$} (B)
-(A) edge node[left]{$L(k)$} (C)
-(B) edge node[right]{$L(g)$} (D)
-(C) edge node[above]{$L(f)$} (D);
-\end{tikzpicture}
-\]
-which we may then paste to the left of the second above pushout square to obtain another pushout square:
+The natural transformation $\theta$ gives a morphism
+\[   \theta \maps (c,L(c) \xrightarrow{\psi} L(c)+_{L(a)} x) \; \to \; (c,L(c) \xrightarrow{\phi  L(f)} L(d)+_{L(b)} x) \]
+in $(L/\X)_c$.   As in the proof of \cref{thm:decorated_cospans_1}, this arises from the universal property of the pushout:
 \[
@@
 \node (A) at (0,0) {$L(b)$};
-\node (B) at (2,0) {$x$};
+\node (B) at (1.5,0) {$x$};
 \node (C) at (0,-1) {$L(d)$};
-\node (D) at (2,-1) {$L(d)+_{L(b)}x$};
-\node (E) at (-1,0) {$L(a)$};
-\node (F) at (-1,-1) {$L(c)$};
+\node (D) at (1.5,-1) {$L(d)+_{L(b)}x$};
+\node (E) at (-1.5,0) {$L(a)$};
+\node (F) at (-1.5,-1) {$L(c)$};
+\node (G) at (2.5,-2) {$L(c)+_{L(a)}x$};
+\node at (1.1,-0.7) {\Large{$\ulcorner$}};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (E) edge node [above] {$L(h)$} (A)
-(F) edge node [above] {$L(f)$} (C)
-(A) edge node[above]{$I$} (B)
+(F) edge node [below] {$L(f)$} (C)
+(A) edge node[above]{$i$} (B)
 (A) edge node[left]{$L(g)$} (C)
 (B) edge node[right]{$$} (D)
-(C) edge node[above]{$\theta$} (D);
-\end{tikzpicture}
-\]
-which exhibits $L(d)+_{L(b)} x$ also as a colimit of the same span in $\X$, and hence the desired natural isomorphism between our two objects of $(L /\X)_c$.
-Thus $\Psi$ satisfies the Beck--Chevalley condition.
+(C) edge node[below]{$\phi$} (D)
+(F) edge [bend right] node[below]{$\psi$} (G)
+(G) edge [dashed] node[below left]{$\exists ! \;\zeta $} (D)
+(B) edge [bend left] (G);
+\end{tikzpicture}
+\]
+Namely, we have $\theta = (1,\zeta)$.   But when the original square in $A$ is a pushout,
+the square at left above is also a pushout, since $L$ preserves finite colimits.  Since the pasting
+of pushout squares is a pushout, $\zeta$ and hence $\theta$ is an isomorphism, so $\Psi$ satisfies the Beck--Chevalley condition.
 \end{proof}

### 2021-06-21 cospans_new.tex
added new acknowledgement of Shulman

@@
 % \to already exists
+\newcommand{\To}{\Rightarrow}
 \newcommand{\too}[1][]{\ensuremath{\overset{#1}{\longrightarrow}}}
@@
 \newcommand{\ot}{\otimes}
-\newcommand{\To}{\Rightarrow}
 
@@
 
-We thank Daniel Cicala, Brendan Fong, Joe Moeller and especially Michael Shulman for helpful conversations.
+We thank Daniel Cicala, Brendan Fong and Joe Moeller for helpful conversations.
+We especially thank Michael Shulman for suggesting a better proof strategy.
 The third author would like to thank the General Secretariat for Research  and Technology (GSRT) and the Hellenic Foundation for Research and Innovation (HFRI).
@@
 
-The monoidal structure of $L/\X$ is similar to the monoidal structure of $\A/U$ of \cref{thm:decorated_cospans_1} in that the tensor product of two objects $(a,L(a) \xrightarrow{i} x)$ and $(a,L(a) \xrightarrow{i'} x')$ is given by
-\[  (a,L(a) \xrightarrow{i} x) \otimes (a',L(a') \xrightarrow{i'} x')=(a+a',x+x',L(a+a') \xrightarrow{i+i'} x+x') \]
-where again the natural isomorphism $L(a)+L(a') \cong L(a+a')$ is implicit.
-The monoidal unit is ${(0_\A,0_\X,{L(0_\A) \to 0_\X})}$.
-It is clear that $\Psi \maps (L/\X, \otimes) \maps (\A,+)$ is a strict monoidal functor.
-{\john Is the tensor product on $L/\X$ also just $+$?
-If so, let's say that and call it $+$.}
+The comma category $L/\X$ has finite colimits because $A$ and $X$ have finite colimits and $L$ 
+preserves them.
+It thus becomes symmetric monoidal with the chosen finite coproducts providing the monoidal structure.
+The tensor product of two objects $(a,L(a) \xrightarrow{i} x)$ and $(a,L(a) \xrightarrow{i'} x')$ is given by
+\[  (a,L(a) \xrightarrow{i} x) + (a',L(a') \xrightarrow{i'} x')=(a+a',x+x',L(a+a')  \xrightarrow{\sim} L(a)+L(a') \xrightarrow{i+i'} x+x'). \]
+The monoidal unit is ${(0_\A,0_\X,{L(0_\A) \to 0_\X})}$.  It is clear that $\Psi \maps (L/\X, +) \to (\A,+)$ is a strict monoidal functor.
 
@@
 
-The `corresponding pseudofunctor' comes from the so-called monoidal Grothendieck construction, and the conditions of this theorem relate to the existence of colimits as well as left adjoints for opfibrations.
-We first sketch the relevant underlying framework in detail, and then we proceed to the proof of the theorem.
-The basics of fibration theory needed for our purposes are recalled in \cref{subsec:fibrations}.
-
-FIX ABOVE PARAGRAPH.
-
+The `corresponding pseudofunctor'   $F \maps \A \to \SMC$  comes from \cref{lem:MonGroth}.
+
+\iffalse
 The 2-equivalence of \cref{lem:MonGroth} has an important special case where the Grothendieck category $(X,\otimes_\X)$ is cocartesian monoidal itself, with coproducts built up from \cref{eq:explicitstructure2}.
@@
 For more details, see \cite[Corollary 4.7]{MV} and the related discussion.
-
-We can further restrict to the case of opfibrations that also preserve pushouts, and thus all finite colimits, thanks to the following more general result.
+\fi
+
+It will be important to know that under the hypotheses of \cref{thm:equiv} the opfibration $U$ preserves all finite colimits.   For this we need the following lemma.
 
@@
 
-On a highly related note, in what follows we are also interested in the existence of a left adjoint $L$ to an induced monoidal opfibration.
+On a highly related note, in what follows we are also interested in the existence of a left adjoint $L$ to the opfibration $U$.
 The following result provides sufficient conditions for that.
@@
 
-We now have all the necessary background to formally construct an isomorphism between the double category of decorated cospans and the double category of structured cospans, starting from a symmetric lax monoidal pseudofunctor $F \maps (\A, +) \to (\Cat, \times)$ whose corresponding pseudofunctor $ F\maps \A \to \SMC$ factors through $\Rex$.
+We now have all the necessary background to construct an isomorphism between the double category of decorated cospans and the double category of structured cospans, starting from a symmetric lax monoidal pseudofunctor $F \maps (\A, +) \to (\Cat, \times)$ whose corresponding pseudofunctor $ F\maps \A \to \SMC$ factors through $\Rex$.
 
@@
 \end{itemize}
-Thus, the double category $F\lCsp$ of structured cospans constructed in \cref{thm:decorated_cospans} automatically gives rise to a bicategory $F\bCsp$, and a category $F\Csp$.
+Thus, the double category $F\lCsp$ of structured cospans constructed in \cref{thm:decorated_cospans_1} automatically gives rise to a bicategory $F\bCsp$, and a category $F\Csp$.
 In \cref{thm:decorated_cospans_2} we gave conditions under which the double category $F\lCsp$ becomes symmetric monoidal.

### 2021-06-21 cospans_new.tex
changed names of decorations in Section 2 to letters like s and t.

@@
 \]
-together with a \define{decoration} $x \in F(m)$,
+together with a \define{decoration} $s \in F(m)$,
 \item a 2-morphism is a \define{map of} $F$\define{-decorated cospans}, that is, 
@@
 \node (D) at (1,-0.5) {$m'$};
-\node (E) at (3,0.5) {$x \in F(m)$};
-\node (F) at (3,-0.5) {$x' \in F(m')$};
+\node (E) at (3,0.5) {$s \in F(m)$};
+\node (F) at (3,-0.5) {$s' \in F(m')$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-together with a \define{decoration morphism} $\tau \maps F(h)(x) \to x'$ in $F(m')$.
+together with a \define{decoration morphism} $\tau \maps F(h)(s) \to s'$ in $F(s')$.
 \end{itemize}
@@
 Vertical composition in $F\lCsp$ is done using composition in $\A$.  The horizontal composite of $F$-decorated cospans
-\[ \left(a\to m\leftarrow b,x\in F(m)\right), \qquad \left(b\to n\leftarrow c,y\in F(n)\right)\] 
+\[ \left(a\to m\leftarrow b,s\in F(m)\right), \qquad \left(b\to n\leftarrow c,t\in F(n)\right)\] 
 is the usual composite via pushout of their underlying cospans, shown in dashed arrows here:
@@
 \]
-together with the decoration in $y \odot x \in F(m +_b n)$ specified by this functor:
-\[  \one\cong\one \times \one \xrightarrow{x \times y} F(n) \times F(m) \xrightarrow{\phi_{n,m}} F(m+n) \xrightarrow{F(\psi)} F(m +_{b}n). \]
+together with the decoration $t \odot s \in F(m +_b n)$ specified by this functor:
+\[  \one\cong\one \times \one \xrightarrow{s \, \times \, t} F(n) \times F(m) \xrightarrow{\phi_{n,m}} F(m+n) \xrightarrow{F(\psi)} F(m +_{b}n). \]
 Given two horizontally composable maps of $F$-decorated cospans $\alpha$ and $\beta$:
@@
 \node (D) at (1,-0.5) {$m'$};
-\node (E) at (3,0.5) {$x \in F(m)$};
-\node (F) at (3,-0.5) {$x' \in F(m')$};
+\node (E) at (3,0.5) {$s \in F(m)$};
+\node (F) at (3,-0.5) {$s' \in F(m')$};
 \node (G) at (4,0.5) {$b$};
@@
 \node (I') at (6,-0.5) {$c'$};
-\node (J) at (7,0.5) {$y \in F(n)$};
-\node (K) at (7,-0.5) {$y' \in F(n')$};
-\node (L) at (1,-1) {$\tau_\alpha \maps F(h_1)(x) \to x'$};
-\node (M) at (5,-1) {$\tau_\beta \maps F(h_2)(y) \to y'$};
+\node (J) at (7,0.5) {$t \in F(n)$};
+\node (K) at (7,-0.5) {$t' \in F(n')$};
+\node (L) at (1,-1) {$\tau_\alpha \maps F(h_1)(s) \to s'$};
+\node (M) at (5,-1) {$\tau_\beta \maps F(h_2)(t) \to t'$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \node (D) at (1.5,-0.5) {$m'+_{b'}n'$};
-\node (E) at (4.5,0.5) {$y \odot x \in F(m+_b n)$};
-\node (F) at (4.5,-0.5) {$y' \odot x' \in F(m' +_{b'} n')$};
+\node (E) at (4.5,0.5) {$t \odot s \in F(m+_b n)$};
+\node (F) at (4.5,-0.5) {$t' \odot s' \in F(m' +_{b'} n')$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-together with the decoration morphism $\tau_{\beta \odot \alpha} \maps F(h_1 +_g h_2)(y \odot x) \to (y' \odot x')$ specified by this natural transformation:
+together with the decoration morphism $\tau_{\beta \odot \alpha} \maps F(h_1 +_g h_2)(t \odot s) \to (t' \odot s')$ specified by this natural transformation:
 \[
@@
 (B) edge node [fill=white] {$F(h_1 + h_2)$} (B')
-(D) edge node [above] {$x \times y$} (E)
-(D) edge node [below] {$x' \times y'$} (E')
+(D) edge node [above] {$s \times t$} (E)
+(D) edge node [below] {$s' \times t'$} (E')
 (E) edge node [fill=white] {$F(h_1) \times F(h_2)$} (E');
@@
 \]
-where the middle isomorphism is \cref{eq:pseudonaturality} from pseudonaturality of $\phi$ and the right-hand isomorphism comes from the pseudofunctoriality of $F$.
+where the middle isomorphism is \cref{eq:pseudonaturality} from the pseudonaturality of $\phi$ and the right-hand isomorphism comes from the pseudofunctoriality of $F$.
 
@@
 \item of two vertical 1-morphisms $f \maps a \to b$ and $f' \maps a' \to b'$ is $f+f' \maps a+a' \to b+b'$ in $\A$,
-\item of two horizontal 1-cells $(a \to m \leftarrow b ,x \in F(m))$ and $(c \to n \leftarrow d, y\in F(n))$ is
+\item of two horizontal 1-cells $(a \to m \leftarrow b, s \in F(m))$ and $(c \to n \leftarrow d, t \in F(n))$ is
 \[
@@
 a+c\ar[ur,"i_1+i_2"] && b+d,\ar[ul,"o_1+o_2"']
-\end{tikzcd}\qquad x \otimes y:=  \phi_{m,n}(x,y) \in F(m + n) 
+\end{tikzcd}\qquad s \otimes t:=  \phi_{m,n}(s,t) \in F(m + n) 
 \]
@@
 %\node (K) at (6.7,-0.5) {$\scriptstyle y' \in F(n')$};
-\node (L) at (1,-1.2) {$\scriptstyle\tau_\alpha \maps F(h)(x) \to x'\textrm{ in } F(m')$};
-\node (M) at (4.5,-1.2) {$\scriptstyle\tau_\beta \maps F(h')(y) \to y'\textrm{ in } F(n')$};
+\node (L) at (1,-1.2) {$\scriptstyle\tau_\alpha \maps F(h)(s) \to s' \textrm{ in } F(m')$};
+\node (M) at (4.5,-1.2) {$\scriptstyle\tau_\beta \maps F(h')(t) \to t'\textrm{ in } F(n')$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 %\node (F) at (5.2,-0.5) {$\scriptstyle \phi_{m',n'}(x',y')$};
-\node () at (2,-1.3) {$\scriptstyle\tau_{\alpha\ot\beta}\maps F(h+h')(\phi_{m,n}(x,y))\to \phi_{m',n'}(x',y')\textrm{ in }F(m'+n')$};
+\node () at (2,-1.3) {$\scriptstyle\tau_{\alpha\ot\beta}\maps F(h+h')(\phi_{m,n}(s,t))\to \phi_{m',n'}(s',t')\textrm{ in }F(m'+n')$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 & F(m)\times F(n)\ar[r,"\phi_{m,n}"]\ar[dd,"F(h)\times F(h')"description]\ar[ddr,phantom,"{\stackrel[\cref{eq:pseudonaturality}]{\phi_{h,h'}}{\cong}}"] & F(m+n)\ar[dd,"F(h+h')"] \\
-\one \ar[ur,"x\times y"]\ar[dr,"x'\times y'"']\ar[r,phantom,"\scriptstyle\Downarrow\tau_\alpha\times\tau_\beta"] & \phantom{A} && \\
+\one \ar[ur,"s\,\times \, t"]\ar[dr,"s' \,\times \, t' "']\ar[r,phantom,"\scriptstyle\Downarrow\tau_\alpha\times\tau_\beta"] & \phantom{A} && \\
 & F(m')\times F(n')\ar[r,"\phi_{m',n'}"'] & F(m'+n')
@@
 
-We prove both these theorems using the work of Shulman \cite{Shulman2008}, who gives a general way to construct double categories from `Beck--Chevalley monoidal bifibrations'---a concept we explain in \cref{subsec:fibrations}.
+We prove both these theorems using the work of Shulman \cite{Shulman2008}, who gives a general way to construct a double category from a `Beck--Chevalley monoidal bifibration'---a concept recalled in \cref{subsec:fibrations}.
 
@@
 
-Note that when $\C$ is the arrow category of $\A$ and $\Phi$ maps any arrow in $\A$ to its
-domain, an object of $\Fr(\Phi)$ simply amounts to a cospan in $\C$.
-In this case $\Fr(\Phi)$ is the double category of cospans in $\C$.
+Note that when $\C$ is the arrow category of $\A$ and $\Phi$ maps any arrow in $\C$ to its
+domain, an object of $\Fr(\Phi)$ simply amounts to a cospan in $\A$.
+In this case $\Fr(\Phi)$ is the double category of cospans in $\A$.
 We shall use variations on this idea to construct double categories of decorated and structured cospans, and to prove that under certain conditions these double categories are equivalent.
-Here we consider decorated cospans, proving Theorem \ref{thm:decorated_cospans_1} and \ref{thm:decorated_cospans_2} by applying Shulman's result to a particular monoidal bifibration built from a lax monoidal pseudofunctor $F \maps (A,+) \to (\Cat,\times)$.
+We begin with decorated cospans, proving Theorem \ref{thm:decorated_cospans_1} and \ref{thm:decorated_cospans_2} by applying Shulman's result to a particular monoidal bifibration built from a lax monoidal pseudofunctor $F \maps (A,+) \to (\Cat,\times)$.
 
@@
 \begin{equation}\label{eq:explicitstructure2}
-\Big(a,x\in F(a)\Big)\ot_{\X}\Big(b,y\in F(b)\Big)=\Big(a+b,\phi_{a,b}(x,y)\in F(a+b)\Big), \qquad I_{\X}=\Big(0_A,\phi_0\Big)
+\Big(a,s\in F(a)\Big)\ot_{\X}\Big(b,t\in F(b)\Big)=\Big(a+b,\phi_{a,b}(s,t)\in F(a+b)\Big), \qquad I_{\X}=\Big(0_A,\phi_0\Big)
 \end{equation}
 If $F$ is a symmetric lax monoidal pseudofunctor, the induced monoidal structure in $\inta F$ is symmetric via
-$$\left(\beta_{a,b},(u_{a,b})_{x,y}\right)\maps \left(a+b,\phi_{a,b}(x,y)\right)\simrightarrow\left(b+a,\phi_{b,a}(y,x)\right)$$ where $\beta$ is the canonical symmetry for $\A$ and $u$ is the natural isomorphism of \cref{eq:braidedpseudofun}.
+$$\left(\beta_{a,b},(u_{a,b})_{s,t}\right)\maps \left(a+b,\phi_{a,b}(s,t)\right)\simrightarrow\left(b+a,\phi_{b,a}(t,s)\right)$$ where $\beta$ is the canonical symmetry for $\A$ and $u$ is the natural isomorphism of \cref{eq:braidedpseudofun}.
 
@@
 \end{equation}
-where $\nabla$ is the fold map, which is symmetric when $F$ is again via the components of $u_{a,a}$. Also, each reindexing functor $f_!=F(f)$ obtains a strong monoidal structure with
+where $\nabla$ is the fold map, which is symmetric when $F$ is, again via the components of $u_{a,a}$. Also, each reindexing functor $f_!=F(f)$ obtains a strong monoidal structure with
 \begin{equation}\label{eq:strongreindexing}
@@
 Now we are ready to use Shulman's result to prove Theorems \ref{thm:decorated_cospans_1} and  \ref{thm:decorated_cospans_2}.  An $F$-decorated cospan from $a$ to $b$ 
-is a cospan $a \to m \leftarrow b$ in $\A$ together with an object $x \in F(m)$.
-This can be seen as a pair $(e \to m, x \in F(m))$ such that $e$ equals $a + b$.
-But $(m,x \in F(m))$ is precisely an object of the Grothendieck category $\inta F$, and the opfibration $U \maps \inta F \to \A$ sends this object to $m$.
-Thus, $(e \to m, x \in F(m))$ can be seen as an object of the comma category $\A/U$.
-Let $\Phi \maps \A/U \to \A$ be the functor sending any object $(e \to m,x \in F(m)) \in \A/U$ to $e$.
+is a cospan $a \to m \leftarrow b$ in $\A$ together with an object $s \in F(m)$.
+This can be seen as a pair $(e \to m, s \in F(m))$ such that $e$ equals $a + b$.
+But $(m,s \in F(m))$ is precisely an object of the Grothendieck category $\inta F$, and the opfibration $U \maps \inta F \to \A$ sends this object to $m$.
+Thus, $(e \to m, s \in F(m))$ can be seen as an object of the comma category $\A/U$.
+Let $\Phi \maps \A/U \to \A$ be the functor with
+\[    \Phi(e \to m,s \in F(m)) = e .\]
 Then an $F$-decorated cospan from $a$ to $b$ amounts to an object $c \in \A/U$ such that $\Phi(c) = a + b$.
@@
 \begin{itemize}
-\item an object is a pair $(a \xrightarrow{i} b, x)$ consisting of a morphism in $\A$ and an
-object $x \in F(b)$;
-\item a morphism from $(a \xrightarrow{i} b, x)$ to $(a' \xrightarrow{i'} b', x')$ is a triple $(f,g,h)$ where $f \maps a \to a'$ and $g \maps b \to b'$ are morphisms in $\A$ such that this square commutes:
+\item an object is a pair $(a \xrightarrow{i} b, s)$ consisting of a morphism in $\A$ and an
+object $s \in F(b)$;
+\item a morphism from $(a \xrightarrow{i} b, s)$ to $(a' \xrightarrow{i'} b', s')$ is a triple $(f,g,h)$ where $f \maps a \to a'$ and $g \maps b \to b'$ are morphisms in $\A$ such that this square commutes:
 \[
@@
 \]
-and $h \maps F(g)(x) \to x'$ is a morphism in $F(b')$.
+and $h \maps F(g)(s) \to s'$ is a morphism in $F(b')$.
 \end{itemize}
@@
 On objects this is given by
-\[  (a \xrightarrow{i} b, x) \otimes (a' \xrightarrow{i'} b', x') = (a+a' \xrightarrow{i+i'} b+b', 
-\phi_{b,b'}(x,x') )\]
+\[  (a \xrightarrow{i} b, s) \otimes (a' \xrightarrow{i'} b', s') = (a+a' \xrightarrow{i+i'} b+b', 
+\phi_{b,b'}(s,s') )\]
 where $\phi$ is the laxator for $F$.  The monoidal unit is $(0_\A \xrightarrow{!} 0_\A, 0)$
@@
 Next, one can check that $\Phi$ is a fibration.
-Given a morphism $f \maps a \to a'$ in $\A$ and an object $(a' \xrightarrow{i'} b', x') \in \A/U$ over $a'$, a cartesian lifting of $f$ to this object is given by
-\[ (f,1,1) \maps (a \xrightarrow{i' f} b' , x')\; \to \; (a' \xrightarrow{i'} b', x'). \]
-Denoting the cartesian lifting of $f$ to the object $z \in \A/U$ by $\mathrm{Cart}(f,z)$, the tensor product of $\A/U$ strictly preserves such cartesian liftings in the sense that $\mathrm{Cart}(f_1,z_1) \otimes \mathrm{Cart}(f_2,z_2)=\mathrm{Cart}(f_1 \otimes f_2, z_1 \otimes z_2)$.
+Given a morphism $f \maps a \to a'$ in $\A$ and an object $(a' \xrightarrow{i'} b', s') \in \A/U$ over $a'$, a cartesian lifting of $f$ to this object is given by
+\[ (f,1,1) \maps (a \xrightarrow{i' f} b' , s')\; \to \; (a' \xrightarrow{i'} b', s'). \]
+Denoting the cartesian lifting of $f$ to an object $z \in \A/U$ by $\mathrm{Cart}(f,z)$, the tensor product of $\A/U$ strictly preserves such cartesian liftings in the sense that $\mathrm{Cart}(f_1,z_1) \otimes \mathrm{Cart}(f_2,z_2)=\mathrm{Cart}(f_1 \otimes f_2, z_1 \otimes z_2)$.
 
 One can also check that $\Phi$ is an opfibration.
-Given a morphism $f \maps a \to a'$ in $\A$ and an object $(a \xrightarrow{i}b, x) \in \A/U$ over $a$, we claim that a cocartesian lifting of $f$ is given by
-\[ (f,g,1) \maps (a \xrightarrow{i} b, x) \, \to \, (a' \xrightarrow{i'} b+_a a', F(g)(x)). \]
+Given a morphism $f \maps a \to a'$ in $\A$ and an object $(a \xrightarrow{i}b, s) \in \A/U$ over $a$, we claim that a cocartesian lifting of $f$ is given by
+\[ (f,g,1) \maps (a \xrightarrow{i} b, s) \, \to \, (a' \xrightarrow{i'} b+_a a', F(g)(s)). \]
 where $g, i'$ and $b +_a a'$ arise from this pushout square in $\A$:
@@
 Suppose we are given a morphism 
-\[    (f'',g'',h'') \maps (a \xrightarrow{i} b, x) \; \to \; (a'' \xrightarrow{i''} b'', x'')   \]
-in $\A/U$ and a morphism $k \maps a \to a''$ in $\A$ such that $\Phi(f'',g'',h'') = k \circ f$.   To show that $(f,g,1)$ is a cocartesian lifting of $f$, we need to show there exists a unique morphism
-\[     (\tilde{f}, \tilde{g}, \tilde{h}) \maps (a' \xrightarrow{i'} b +_a a', F(g)(x)) \; \to \; (a'' \xrightarrow{i''} b'', x'') \]
+\[    (f'',g'',h'') \maps (a \xrightarrow{i} b, s) \; \to \; (a'' \xrightarrow{i''} b'', s'')   \]
+in $\A/U$ and a morphism $k \maps a \to a''$ in $\A$ such that $\Phi(f'',g'',h'') = k f$.   To show that $(f,g,1)$ is a cocartesian lifting of $f$, we need to show there exists a unique morphism
+\[     (\tilde{f}, \tilde{g}, \tilde{h}) \maps (a' \xrightarrow{i'} b +_a a', F(g)(s)) \; \to \; (a'' \xrightarrow{i''} b'', s'') \]
 such that $\Phi(\tilde{f}, \tilde{g}, \tilde{h}) = k$ and 
@@
 \]
-after noting that $g'' i = i' f'' = i'' k f $ by the commuting square condition for the morphisms
+after noting that $g'' i = i' f'' = i'' k f $ by the commuting square condition obeyed by morphisms
 in $\A/U$.   One can check that with these choices, $(\tilde{f},\tilde{g}, \tilde{h})$ obeys the desired conditions and is the unique morphism to do so.
@@
 \]
-defined in Equation \eqref{theta}.   We need to prove that when the square in $\A$ is 
+defined in \eqref{theta}.   We need to prove that when the square in $\A$ is 
 a pushout, $\theta$ is a natural isomorphism.
@@
 We start by describing $\theta$ more concretely.
-Let $(b \xrightarrow{i} e, x)$ be an object of $(\A/U)_b$.
-Going left, we precompose with $h \maps a \to b$ to obtain the object $(a \xrightarrow{i h} e, z)$ of $(\A/U)_a$.
+Let $(b \xrightarrow{i} e, s)$ be an object of $(\A/U)_b$.
+Going left, we precompose with $h \maps a \to b$ to obtain the object $(a \xrightarrow{i h} e, s)$ of $(\A/U)_a$.
 Then going down, we push forward along $k$:
@@
 \]
-to obtain the object $(c \xrightarrow{\psi} c+_a e, F(\psi)(x))$ of $(\A/U)_c$.
-For the other route, first going down, we push the object $(b \xrightarrow{i} e,x)$ forward along $g \maps b \to d$ by taking the following pushout:
+to obtain the object $(c \xrightarrow{\psi} c+_a e, F(\psi)(s))$ of $(\A/U)_c$.
+For the other route, first going down, we push the object $(b \xrightarrow{i} e,s)$ forward along $g \maps b \to d$ by taking the following pushout:
 \[
@@
 \node (A) at (0,0) {$b$};
-\node (B) at (1.5,0) {$U(x)$};
+\node (B) at (1.5,0) {$e$};
 \node (C) at (0,-1) {$d$};
@@
 \]
-which yields the object $(d \xrightarrow{\phi} d+_b e, F(\phi)(x))$ of $(\A/U)_d$.
-Then going left, we precompose with $f \maps c \to d$ to obtain the object $(c \xrightarrow{\phi f} d+_b e, F(\phi)(x))$ of $(\A/U)_c$.
+which yields the object $(d \xrightarrow{\phi} d+_b e, F(\phi)(s))$ of $(\A/U)_d$.
+Then going left, we precompose with $f \maps c \to d$ to obtain the object $(c \xrightarrow{\phi f} d+_b e, F(\phi)(s))$ of $(\A/U)_c$.
 
 The natural transformation $\theta$ gives a morphism
-\[    \theta \maps   (c \xrightarrow{\psi} c+_a e, F(\psi)(x)) \; \to \; (c \xrightarrow{\phi f} d+_b e, F(\phi)(x))  \]
+\[    \theta \maps   (c \xrightarrow{\psi} c+_a e, F(\psi)(s)) \; \to \; (c \xrightarrow{\phi f} d+_b e, F(\phi)(s))  \]
 in $(\A/U)_c$.   Concretely, this arises from the universal property of the pushout:
@@
 Namely, we have $\theta = (1, \zeta, 1)$.   But when the original square in $\A$ (at upper left 
-in the diagram above) is a pushout, its pasting with the other pushout gives a pushout, so $\zeta$ and hence $\theta$ is isomorphism.
+above) is a pushout, its pasting with the other pushout gives a pushout, so $\zeta$ and hence $\theta$ is isomorphism.
 
@@
 \item The image of an $F$-decorated cospan
-\[ M= (a\xrightarrow{i}m\xleftarrow{o}b, \; x\in F(m)) \]
+\[ M= (a\xrightarrow{i}m\xleftarrow{o}b, \; s \in F(m)) \]
 is the following $F'$-decorated cospan:
-\[ \lH(M)= (H(a)\xrightarrow{H(i)}H(m)\xleftarrow{H(o)}H(b), \;\bar{x}\in F'(H(m))) \]
+\[ \lH(M)= (H(a)\xrightarrow{H(i)}H(m)\xleftarrow{H(o)}H(b), \;\bar{s}\in F'(H(m))) \]
  where
 \[
-\bar{x}:=\one \xrightarrow{\phi_0} E(\one) \xrightarrow{E(x)} E(F(m)) \xrightarrow{\theta_m} F'(H(m)).\]
+\bar{s}:=\one \xrightarrow{\phi_0} E(\one) \xrightarrow{E(s)} E(F(m)) \xrightarrow{\theta_m} F'(H(m)).\]
 \item The image of a map of decorated cospans in $F\lCsp$ 
@@
 \node (D) at (1,-0.5) {$n$};
-\node (E) at (3,0.5) {$x \in F(m)$};
-\node (F) at (3,-0.5) {$x' \in F(n)$};
-\node (G) at (5,0) {$\tau \maps F(h)(x) \to x'$};
+\node (E) at (3,0.5) {$s \in F(m)$};
+\node (F) at (3,-0.5) {$s' \in F(n)$};
+\node (G) at (1,-1) {$\tau \maps F(h)(s) \to s'$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \node (D'') at (5.75,-0.5) {$H(n)$};
-\node (E'') at (8.5,0.5) {$\theta_m E(x) \phi_0 \in F'(H(m))$};
-\node (F'') at (8.5,-0.5) {$\theta_n E(x') \phi_0 \in F'(H(n))$};
+\node (E'') at (8.5,0.5) {$\overline{s}\in F'(H(m))$};
+\node (F'') at (8.5,-0.5) {$\overline{s'} \in F'(H(n))$};
+\node (G) at (5.75,-1) {$\lH(\tau) \maps F'(H(h))(\overline{s}) \to \overline{s'}$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-where the decoration morphism $\tau$ is mapped to a decoration morphism $\lH(\tau)$ as follows.  We can think of $\tau$ as a natural transformation
+where the decoration morphism $\lH(\tau)$ is defined as follows.  We can think of $\tau$ as a natural transformation
 \[
@@
 The square at right commutes strictly because $\theta$ is a natural isomorphism.
-Perhaps we could generalize our construction to handle the case where $\theta$ is a pseudonatural equivalence, making this square commute up to a natural isomorphism.
-However, the following result suffices
-for the application in \cref{subsec:petrirates}.
+\iffalse Perhaps we could generalize our construction to handle the case where $\theta$ is a pseudonatural equivalence, making this square commute up to a natural isomorphism.
+However, the following result suffices for the application in \cref{subsec:petrirates}.
+\fi
 
@@
 and of course the case of $\A'/U'$ is analogous.   We define $G \maps \A/U \to \A'/U'$ as follows.  On objects $G$ is given by
-\[  G(a \xrightarrow{i} b, x) \; = \; (H(a) \xrightarrow{H(i)} H(b), \underline{x}), \]
-where to define $\underline{x}$ we treat $x \in F(b)$ as a functor 
-$x \maps 1 \to F(b)$ and let $\underline{x} \in F'(H(b))$ be the composite functor
+\[  G(a \xrightarrow{i} b, s) \; = \; (H(a) \xrightarrow{H(i)} H(b), \underline{s}), \]
+where to define $\underline{x}$ we treat $s \in F(b)$ as a functor 
+$x \maps 1 \to F(b)$ and let $\underline{s} \in F'(H(b))$ be the composite functor
 \[  1 \xrightarrow{\phi_0} E(1) \xrightarrow{E(x)} E(F(b)) \xrightarrow{\;\theta_b\;} F'(H(b)) .\]
-On morphisms $(f,g,h) \maps (a \xrightarrow{i} b, x) \; \to \; 
-(a' \xrightarrow{i'} b', x')$, $G$ is given by
+On morphisms $(f,g,h) \maps (a \xrightarrow{i} b, s) \; \to \; 
+(a' \xrightarrow{i'} b', s')$, $G$ is given by
 \[   G(f,g,h) = (H(f),H(g),\underline{h}) \]
-where to define $\underline{h}$ we treat $h \maps F(g)(x) \to x'$ as a natural transformation
+where to define $\underline{h}$ we treat $h \maps F(g)(s) \to s'$ as a natural transformation
 \[
@@
 \]
-and let $\underline{h} \maps F'(H(g))(\underline{x}) \to \underline{x}'$ be this
+and let $\underline{h} \maps F'(H(g))(\underline{s}) \to \underline{s}'$ be this
 natural transformation:
@@
 To make $G$ into a monoidal functor, we need to equip it with a laxator
-\[  \gamma \maps G(a \xrightarrow{i} b, x) \otimes G(a' \xrightarrow{i'} b', x') \; 
-\to \; G((a \xrightarrow{i} b, x) \otimes (a' \xrightarrow{i'} b', x')).\]
+\[  \gamma \maps G(a \xrightarrow{i} b, s) \otimes G(a' \xrightarrow{i'} b', s') \; 
+\to \; G((a \xrightarrow{i} b, s) \otimes (a' \xrightarrow{i'} b', s')).\]
 Note that
-\[   G(a \xrightarrow{i} b, x) \otimes G(a' \xrightarrow{i'} b', x') = 
-\left(H(a) + H(a') \xrightarrow{H(i) + H(i')} H(b) + H(b') , \; \phi'_{H(b), H(b')}(\underline{x},
-\underline{x}')\right) \]
+\[   G(a \xrightarrow{i} b, s) \otimes G(a' \xrightarrow{i'} b', s') = 
+\left(H(a) + H(a') \xrightarrow{H(i) + H(i')} H(b) + H(b') , \; \phi'_{H(b), H(b')}(\underline{s},
+\underline{s}')\right) \]
 where $\phi'$ is the laxator for $F'$, while
-\[    G((a \xrightarrow{i} b, x) \otimes (a' \xrightarrow{i'} b', x')) =
-\left(H(a+a') \xrightarrow{H(i+i')} H(b+b'), \; \underline{\phi_{b,b'}(x,x')} \right)
+\[    G((a \xrightarrow{i} b, s) \otimes (a' \xrightarrow{i'} b', s')) =
+\left(H(a+a') \xrightarrow{H(i+i')} H(b+b'), \; \underline{\phi_{b,b'}(s,s')} \right)
 \]
 where $\phi$ is the laxator for $F$.  Since $H$ preserves finite colimits, the laxator
-$\gamma$ is obvious except for the morphism from $\phi'_{H(b), H(b')}(\underline{x},
-\underline{x}')$ to $\underline{\phi_{b,b'}(x,x')}$.   This is given by the following natural
+$\gamma$ is obvious except for the morphism from $\phi'_{H(b), H(b')}(\underline{s},
+\underline{s}')$ to $\underline{\phi_{b,b'}(s,s')}$.   This is given by the following natural
 transformation:
@@
 \begin{tikzpicture}[scale=1.5]
-\node () at (3,-0.5) {$\scriptscriptstyle{\stackrel{E_{x,x'}} \cong}$};
+\node () at (3,-0.5) {$\scriptscriptstyle{\stackrel{E_{s,s'}} \cong}$};
 \node () at (1.5,-0.5) {$\scriptscriptstyle{\stackrel{\lambda} \cong}$};
@@
 (I) edge node [below] {$\theta_{b+b'}$} (J)
-(B) edge node [above] {$E(x) \times E(x')$} (E)
-(D) edge node [below] {$E(x \times x')$} (F)
+(B) edge node [above] {$E(s) \times E(s')$} (E)
+(D) edge node [below] {$E(s \times s')$} (F)
 (E) edge node [right] {$E_{F(b),F(b')}$} (F)
@@
 \]
-defined in Equation \eqref{theta} is an isomorphism.
+defined in \eqref{theta} is an isomorphism.
 Let $(b,L(b) \xrightarrow{i} x)$ be an object of $(L/\X)_b$.
@@
 \begin{thm} \label{thm:equiv}
-Suppose $\A$ has finite colimits and $F \maps (\A,+) \to (\Cat,\times)$ is a symmetric lax monoidal pseudofunctor.
-If the corresponding pseudofunctor $F \maps \A \to \SMC$ factors through $\Rex$, then the symmetric monoidal double categories $F\lCsp$ of decorated cospans and ${}_L\lCsp(\inta F)$ of structured cospans are isomorphic, where $L \maps \A \to \inta F$ is a left adjoint of the induced Grothendieck opfibration $U\maps \inta F \to \A$.
+Suppose $\A$ has finite colimits and $F \maps (\A,+) \to (\Cat,\times)$ is a symmetric lax monoidal pseudofunctor. If the corresponding pseudofunctor $F \maps \A \to \SMC$ from \cref{lem:MonGroth}
+ factors through $\Rex$, then the symmetric monoidal double categories $F\lCsp$ of decorated cospans and ${}_L\lCsp(\inta F)$ of structured cospans are isomorphic, where $L \maps \A \to \inta F$ is a left adjoint of the induced Grothendieck opfibration $U\maps \inta F \to \A$.
 \end{thm}
-
-The `corresponding pseudofunctor'   $F \maps \A \to \SMC$  comes from \cref{lem:MonGroth}.
 
@@
 
-The first part formulates the existence of colimits \emph{locally} in each fiber, and if we let $\J$ range over all finite categories it says that the corresponding pseudofunctor $F \maps \A \to \Cat$ lands in the sub-2-category $\Rex$.
+The first part of this lemma asserts the existence of colimits \emph{locally} in each fiber, and if we let $\J$ range over all finite categories it says that the corresponding pseudofunctor $F \maps \A \to \Cat$ lands in the sub-2-category $\Rex$.
 The second part formulates the existence of colimits \emph{globally} in the total category $\inta F$, and if we let $\J$ range over all finite categories it says that $\X$ has finite colimits and $U$ preserves all finite colimits.
@@
 \end{equation}
-where $\iota_a \maps a\to a+b$ and $\iota_b \maps b \to a+b$ are the sum inclusions in $\A$ and the sum on the second variable is in the fiber $F(a+b)$.
+where $\iota_a \maps a\to a+b$ and $\iota_b \maps b \to a+b$ are the coproduct inclusions in $\A$ and the coproduct in the second component is in the fiber $F(a+b)$.
 
@@
 Regarding the assumptions of the above corollary, notice that since $\A$ is cocartesian monoidal, the lax monoidal pseudofunc\-tor structure $(F,\phi,\phi_0)$ gives rise to a specific symmetric monoidal structure on the fibers $F(a)$ in terms of $\phi,\phi_0$, given explicitly by \cref{eq:explicitstructure1}.
-Since we now ask that the pseudofunctor $F\maps \A\to\SMC$ factors through $\Rex$, this fiberwise monoidal structure is required to be cocartesian, namely \cref{eq:explicitstructure1} gives coproducts and an initial object in each $F(a)$.
-
-On a highly related note, in what follows we are also interested in the existence of a left adjoint $L$ to the opfibration $U$.
+Since we now ask that the pseudofunctor $F\maps \A\to\SMC$ factors through $\Rex$, this fiberwise monoidal structure is required to be cocartesian, namely that \cref{eq:explicitstructure1} gives coproducts and an initial object in each $F(a)$.
+
+In what follows we also need a left adjoint $L$ to the opfibration $U$.
 The following result provides sufficient conditions for that.
@@
 By \cref{prop:opfibtolari}, $U$ has a left adjoint $L\maps\A\to\inta F$ with $UL=1_\A$. Diagrammatically,
-\begin{equation}\label{eq:FtoL}
+\[
  F\maps\A\to\Cat\quad\mapsto\quad\begin{tikzcd}[baseline=.3]\inta F\ar[d,"U"'] \\ \A \end{tikzcd}\quad\mapsto\quad\begin{tikzcd}\A\ar[r,bend left,pos=.55,"L"]\ar[r,phantom,"\bot"description] & \inta F\ar[l,bend left,pos=.45,"U"]\end{tikzcd}
-\end{equation}
+\]
 describes the construction of the adjunction from the original $F$.
-Explicitly, the left adjoint picks the initial object in the fiber of $a$, namely $L(a)=(a,\bot_a)$ which is expressed as $F(!_a)\circ\phi_0(*)$ according to \cref{eq:explicitstructure1} for $(\phi,\phi_0)$ the monoidal structure of $F$.
-
-As a left adjoint, this induced $L$ preserves all colimits that exist between the categories $\A$ and $\inta F$, which have finite colimits, so we can construct the double category of structured cospans $_L\lCsp(\inta F)$ of \cref{thm:SC}.
-
-{\textbf NEW PROOF HERE.}
-To show that the symmetric monoidal double categories $F\lCsp$ and $_L \lCsp(\inta F)$ of Theorems \ref{thm:decorated_cospans_2} and \ref{thm:SC} are isomorphic, we make use of a result of Shulman \cite[Theorem~14.11]{Shulman2010} which states that there exists a 2-functor $\mathbb{F}\mathbf{r} \maps \mathbf{FMF} \to \mathbf{FDbl}$.
-Here, $\mathbf{FMF}$ is the 2-category consisting of
+Explicitly, the left adjoint maps each object $a \in \A$ to the initial object in its fiber $\X_a$, namely $L(a)=(a,\bot_a)$, which is expressed as $F(!_a)\circ\phi_0(*)$ according to \cref{eq:explicitstructure1}, where $(\phi,\phi_0)$ the lax monoidal structure of $F$.
+
+As a left adjoint, $L$ preserves all colimits that exist between the categories $\A$ and $\inta F$, which have finite colimits, so we can construct the double category of structured cospans $_L\lCsp(\inta F)$ of \cref{thm:SC}.
+
+To show that the symmetric monoidal double categories $F\lCsp$ and $_L \lCsp(\inta F)$ of Theorems \ref{thm:decorated_cospans_2} and \ref{thm:SC} are isomorphic, we make use of a result of Shulman \cite[Theorem~14.11]{Shulman2010}.
+Namely, the $\mathbb{F}\mathbf{r}$ construction described in \cref{lem:shulman} extends to a 2-functor
+\[ \mathbb{F}\mathbf{r} \maps \mathbf{FMF} \to \mathbf{FDbl} \]
+where $\mathbf{FMF}$ is the 2-category consisting of
 \begin{enumerate}
-\item{monoidal bifibrations satisfying the Beck-Chevalley condition,}
-\item{strong monoidal morphisms of bifibrations, and}
-\item{monoidal transformations of bifibrations.}
+\item Beck--Chevalley monoidal bifibrations,
+\item strong monoidal morphisms of bifibrations, and
+\item monoidal transformations of bifibrations
 \end{enumerate}
@@
 \]
-with $\Psi F=\Phi$ a monoidal transformation. The functor $F \maps (\A/U) \to (L/\X)$ is expressed by the natural isomorphism of an adjunction, namely:
-$$F(a,x,a \to U(x))=(a,x,L(a) \to x)$$
+with $\Psi F=\Phi$ a monoidal transformation. On objects the functor $F \maps \A/U \to L/\X$ is expressed by the natural isomorphism of an adjunction, namely:
+\[  F(a \xrightarrow{i} b, x)=(a,L(a) ????????? x) \]
 and is the identity on pairs of morphisms making the required squares commute.
-It is clear that $F$ is strong monoidal via component-wise binary coproducts which are preserved by both $L$ and $U$, and that the identity $\Psi F=\Phi$ is a monoidal transformation.
-As $F$ is an isomorphism, we obtain an isomorphism $$\mathbb{F}\mathbf{r}(F) \maps \mathbb{F}\mathbf{r}(\Phi) \to \mathbb{F}\mathbf{r}(\Psi)$$ between the two symmetric monoidal double categories $\mathbb{F}\mathbf{r}(\Phi)=F\lCsp$ and $\mathbb{F}\mathbf{r}(\Psi)= _L \lCsp(\inta F)$ of Theorems \ref{thm:decorated_cospans_2} and \ref{thm:SC}, respectively.
+It is clear that $F$ is strong monoidal via componentwise binary coproducts which are preserved by both $L$ and $U$, and that the identity $\Psi F=\Phi$ is a monoidal transformation.
+As $F$ is an isomorphism, we obtain an isomorphism $$\mathbb{F}\mathbf{r}(F) \maps \mathbb{F}\mathbf{r}(\Phi) \to \mathbb{F}\mathbf{r}(\Psi)$$ between the two symmetric monoidal double categories $\mathbb{F}\mathbf{r}(\Phi)=F\lCsp$ and $\mathbb{F}\mathbf{r}(\Psi)= _L \lCsp(\inta F)$ of Theorems \ref{thm:decorated_cospans_2} and \ref{thm:structured_cospans}, respectively.
 \end{proof}
 
+\iffalse
 In fact, a careful examination of the proof reveals that the assumptions of \cref{thm:equiv} could be weakened to state that the pseudofunctor $F \maps \A \to \SMC$ factors through the 2-category $\mathbf{Cocart}$ of cocartesian monoidal categories.
@@
 However, in the most interesting examples seen so far, when $F$ factors through $\mathbf{Cocart}$ it also factors through $\Rex$.
+\fi
 

### 2021-06-22 cospans_new.tex
work on Section 5

@@
 
-\begin{thm}\label{thm:SC}
+\begin{thm}\label{thm:structured_cospans}
 Given categories $\A$ and $\X$ with finite colimits and $L \maps \A \to \X$ a functor preserving finite colimits, there is a symmetric monoidal double category $_L\lCsp(\X)$ in which
@@
 
-We now show that structured and decorated cospan double categories are isomorphic under certain conditions.
-Let $\Rex$ be the 2-category of categories with finite colimits, functors preserving finite colimits, and natural transformations.
-Let $\SMC$ be the 2-category of symmetric monoidal categories, strong symmetric monoidal functors and natural transformations.
+We now compare structured and decorated cospans.
+In \cref{thm:decorated_cospans_1} we built a double category of decorated cospans from a functor $\Phi \maps \A/U \to \A$.
+In \cref{thm:structured_cospans} we built a double category of structured cospans from a functor $\Psi \maps L/\X \to \A$.
+We now show that under certain conditions $L$ is left adjoint to $U$.
+Whenever this happens, $\A/U$ is isomorphic to $L/\X$, by a general fact about arrow categories.
+The bifibrations $\Phi$ and $\Psi$ are then also isomorphic.
+By the functoriality
+of Shulman's construction in \cref{lem:shulman}, it follows that the double category of decorated cospans is isomorphic to the double category of structured cospans.
+
+The key issue is thus to determine when $L$ is left adjoint to $U$.
+For this, let $\Rex$ be the 2-category of categories with finite colimits, functors preserving finite colimits, and natural transformations.
+Also let $\SMC$ be the 2-category of symmetric monoidal categories, strong symmetric monoidal functors and natural transformations.
 Recall that for us a category $\C \in \Rex$ comes with a choice of finite colimits, so it gives a specific cocartesian monoidal category $(\C,+)$, and this induces a 2-functor $\Rex \to \SMC$.
+
+Our main resut is this:
 
@@
 Suppose $\A$ has finite colimits and $F \maps (\A,+) \to (\Cat,\times)$ is a symmetric lax monoidal pseudofunctor. If the corresponding pseudofunctor $F \maps \A \to \SMC$ from \cref{lem:MonGroth}
- factors through $\Rex$, then the symmetric monoidal double categories $F\lCsp$ of decorated cospans and ${}_L\lCsp(\inta F)$ of structured cospans are isomorphic, where $L \maps \A \to \inta F$ is a left adjoint of the induced Grothendieck opfibration $U\maps \inta F \to \A$.
+ factors through $\Rex$, then the symmetric monoidal double categories $F\lCsp$ of decorated cospans and ${}_L\lCsp(\inta F)$ of structured cospans are isomorphic, where $L \maps \A \to \inta F$ is a left adjoint of the induced Grothendieck opfibration $U \maps \inta F \to \A$.
 \end{thm}
@@
 
-As a left adjoint, $L$ preserves all colimits that exist between the categories $\A$ and $\inta F$, which have finite colimits, so we can construct the double category of structured cospans $_L\lCsp(\inta F)$ of \cref{thm:SC}.
-
-To show that the symmetric monoidal double categories $F\lCsp$ and $_L \lCsp(\inta F)$ of Theorems \ref{thm:decorated_cospans_2} and \ref{thm:SC} are isomorphic, we make use of a result of Shulman \cite[Theorem~14.11]{Shulman2010}.
+As a left adjoint, $L$ preserves all colimits that exist between the categories $\A$ and $\inta F$, which have finite colimits, so we can construct the double category of structured cospans $_L\lCsp(\inta F)$ of \cref{thm:structured_cospans}.
+
+To show that the symmetric monoidal double categories $F\lCsp$ and $_L \lCsp(\inta F)$ of Theorems \ref{thm:decorated_cospans_2} and \ref{thm:structured_cospans} are isomorphic, we make use of a result of Shulman \cite[Theorem~14.11]{Shulman2010}.
 Namely, the $\mathbb{F}\mathbf{r}$ construction described in \cref{lem:shulman} extends to a 2-functor
@@
 and such that the identity $\Phi' F_1 = F_2 \Phi$ is a monoidal transformation.
-The two monoidal fibrations in question are the functors $\Phi$ and $\Psi$ of Theorems \ref{thm:decorated_cospans_2} and \ref{thm:SC}, respectively, which share $\A$ as a common base, and thus we only need a single strong monoidal functor $F \maps (\A/U) \to (L/\X)$ making the following diagram commute:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$(\A/U)$};
-\node (B) at (2,0) {$(L/ \X)$};
+The two monoidal bifibrations in question are the functors $\Phi$ and $\Psi$ of Theorems \ref{thm:decorated_cospans_2} and \ref{thm:structured_cospans}, respectively, which share $\A$ as a common base, and thus we only need a single strong monoidal functor $F \maps \A/U \to L/\X$ making this diagram commute:
+\[
+\begin{tikzpicture}[scale=1.0]
+\node (A) at (0,0) {$\A/U$};
+\node (B) at (2,0) {$L/ \X$};
 \node (C) at (1,-1.5) {$\A$};
@@
 \path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$\stackrel{F}\cong$} (B)
+(A) edge node[above]{$F$} (B)
 %(B) edge [bend left] node[above]{$$} (A)
@@
 \]
-with $\Psi F=\Phi$ a monoidal transformation. On objects the functor $F \maps \A/U \to L/\X$ is expressed by the natural isomorphism of an adjunction, namely:
-\[  F(a \xrightarrow{i} b, x)=(a,L(a) ????????? x) \]
-and is the identity on pairs of morphisms making the required squares commute.
-It is clear that $F$ is strong monoidal via componentwise binary coproducts which are preserved by both $L$ and $U$, and that the identity $\Psi F=\Phi$ is a monoidal transformation.
-As $F$ is an isomorphism, we obtain an isomorphism $$\mathbb{F}\mathbf{r}(F) \maps \mathbb{F}\mathbf{r}(\Phi) \to \mathbb{F}\mathbf{r}(\Psi)$$ between the two symmetric monoidal double categories $\mathbb{F}\mathbf{r}(\Phi)=F\lCsp$ and $\mathbb{F}\mathbf{r}(\Psi)= _L \lCsp(\inta F)$ of Theorems \ref{thm:decorated_cospans_2} and \ref{thm:structured_cospans}, respectively.
+{\john with $\Psi F=\Phi$ a monoidal transformation.}  There is an isomorphism $F \maps \A/U \to L/\X$ arising from the fact that $U$ is right adjoint to $L$.
+It is clear that $F$ is strong monoidal via componentwise binary coproducts which are preserved by both $L$ and $U$, {\john and that the identity $\Psi F=\Phi$ is a monoidal transformation.} As $F$ is an isomorphism, we obtain an isomorphism
+\[  \mathbb{F}\mathbf{r}(F) \maps \mathbb{F}\mathbf{r}(\Phi) \to \mathbb{F}\mathbf{r}(\Psi)\] between the two monoidal double categories $\mathbb{F}\mathbf{r}(\Phi)=F\lCsp$ and $\mathbb{F}\mathbf{r}(\Psi)= {}_L \lCsp(\inta F)$ of Theorems \ref{thm:decorated_cospans_2} and \ref{thm:structured_cospans}, respectively.
+{\john One can check by hand that this isomorphism
+is symmetric monoidal.}
 \end{proof}
@@
 \]
-where $\bot_b$ is the trivial decoration as in \cref{eq:UFCsp}, into a companion of $f$ using the following 2-morphisms:
+where $\bot_b$ is the trivial decoration given by
+\[    \one \xrightarrow{\phi_0} F(0_\A) \xrightarrow{F(!)} F(b) , \]
+into a companion of $f$ using the following 2-morphisms:
 \[
@@
 \node (C) at (2,0) {$b$};
-\node (D) at (4,0) {$x \in F(m)$,};
+\node (D) at (4,0) {$s \in F(m)$,};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \node (E) at (1,-0.5) {$m'$};
-\node (D) at (3,0.5) {$x \in F(m)$};
-\node (F) at (3,-0.5) {$x' \in F(m')$};
+\node (D) at (3,0.5) {$s \in F(m)$};
+\node (F) at (3,-0.5) {$s' \in F(m')$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-together with a morphism $\tau \maps F(h)(x) \to x'$ in $F(m')$.
+together with a morphism $\tau \maps F(h)(s) \to s'$ in $F(m')$.
 \end{enumerate}
@@
 \begin{proof}
-This follows by applying Shulman's result (\cref{Shulhorizontalbicat}) to the fibrant symmetric monoidal double category $F\lCsp$.
+This follows by applying \cref{Shulhorizontalbicat} to the fibrant symmetric monoidal double category $F\lCsp$.
 \end{proof}
 
-This symmetric monoidal bicategory $F\bCsp$ generalizes the one constructed by the second author \cite{Courser}.
-We can decategorify $F\bCsp$ to obtain a symmetric monoidal category generalizing the kind considered by Fong \cite{Fong}:
+This symmetric monoidal bicategory $F\bCsp$ generalizes one constructed by the second author \cite{Courser}.    We can decategorify $F\bCsp$ to obtain a symmetric monoidal category of 
+decorated cospans generalizing those considered by Fong \cite{Fong}:
 
@@
 \node (C) at (2,0) {$b$};
-\node (D) at (4,0) {$x \in F(m)$};
+\node (D) at (4,0) {$s \in F(m)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \node (C) at (2,0) {$b$};
-\node (D) at (4,0) {$x' \in F(m')$};
+\node (D) at (4,0) {$s' \in F(m')$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-and there exists an isomorphism $\tau \maps F(f)(x) \to x'$ in $F(m')$.
+and there exists an isomorphism $\tau \maps F(f)(s) \to s'$ in $F(m')$.
 \end{enumerate}
@@
 Both $\Fin\Set$ and $\Graph$ have finite colimits, and the functor $L \maps \Fin\Set \to \Graph$ is left adjoint to the forgetful functor $R \maps \Graph \to \Fin\Set$ that assigns to a graph $G$ its underlying set of vertices $R(G)$.
-Thus, using structured cospans and appealing to \cref{thm:SC}, we get a symmetric monoidal double category $_L \lCsp(\Graph)$ in which:
+Thus, using structured cospans and appealing to \cref{thm:structured_cospans}, we get a symmetric monoidal double category $_L \lCsp(\Graph)$ in which:
 \begin{itemize}
@@
 
-This sets the stage for structured cospans: \cref{thm:SC} gives us a symmetric monoidal double category ${}_L \lCsp(\Graph_\La)$ where a horizontal 1-cell is an \define{open} $\La$-\define{graph}, also called an $\La$-\define{circuit}: that is, a cospan in $\Graph_\La$ of this form:
+This sets the stage for structured cospans: \cref{thm:structured_cospans} gives us a symmetric monoidal double category ${}_L \lCsp(\Graph_\La)$ where a horizontal 1-cell is an \define{open} $\La$-\define{graph}, also called an $\La$-\define{circuit}: that is, a cospan in $\Graph_\La$ of this form:
 \[
@@
 There is a functor $R \maps \Petri \to \Set$ sending any Petri net to its set of places, and this has a left adjoint $L \maps \Set \to \Petri$ sending any set $S$ to the Petri net with $S$ as its set of places and no transitions \cite[Lemma 11]{BM}.
-Since both $\Set$ and $\Petri$ have finite colimits and $L$ preserves them, \cref{thm:SC} yields a symmetric monoidal double category ${}_L \lCsp(\Petri)$ in which:
+Since both $\Set$ and $\Petri$ have finite colimits and $L$ preserves them, \cref{thm:structured_cospans} yields a symmetric monoidal double category ${}_L \lCsp(\Petri)$ in which:
 \begin{itemize}
@@
 Let us now sketch the story; details will appear in a forthcoming paper \cite{CV}.
-Suppose the conditions hold for constructing the double category of structured cospans ${}_L \lCsp(\X)$ as in \cref{thm:SC}.
+Suppose the conditions hold for constructing the double category of structured cospans ${}_L \lCsp(\X)$ as in \cref{thm:structured_cospans}.
 That is, suppose $\A$ and $\X$ have finite colimits and $L \maps \A \to \X$ preserves them.

### 2021-06-22 cospans_new.tex
corrected a lot of problems Kenny found in his email

@@
 In this section we build symmetric monoidal double categories of decorated cospans, and then study the functoriality of this construction.
-\cref{thm:decorated_cospans_1} explains how to construct a double category of decorated cospans from a lax monoidal pseudofunctor $F \maps (\A,+) \to (\Cat, \times)$  whenever $A$ is a cocartesian.
+\cref{thm:decorated_cospans_1} explains how to construct a double category of decorated cospans from a lax monoidal pseudofunctor $F \maps (\A,+) \to (\Cat, \times)$ whenever $A$ has finite colimits.
 \cref{thm:decorated_cospans_2} gives conditions under which this double category is symmetric monoidal.
@@
 together with the decoration $t \odot s \in F(m +_b n)$ specified by this functor:
-\[  \one\cong\one \times \one \xrightarrow{s \, \times \, t} F(n) \times F(m) \xrightarrow{\phi_{n,m}} F(m+n) \xrightarrow{F(\psi)} F(m +_{b}n). \]
+\[  \one\cong\one \times \one \xrightarrow{s \, \times \, t} F(m) \times F(n) \xrightarrow{\phi_{m,n}} F(m+n) \xrightarrow{F(\psi)} F(m +_{b}n). \]
 Given two horizontally composable maps of $F$-decorated cospans $\alpha$ and $\beta$:
@@
 \begin{thm}\label{thm:decorated_cospans_2}
-Let $(\A,+)$ be a cocartesian monoidal category and let $(F,\phi,\phi_0)\maps (\A,+) \to (\Cat,\times)$ be a symmetric lax monoidal pseudofunctor.
-Then the double category $F\lCsp$ is symmetric monoidal, where the tensor product
+Let $\A$ be a category with finite colimits and let $(F,\phi,\phi_0)\maps (\A,+) \to (\Cat,\times)$ be a symmetric lax monoidal pseudofunctor.
+Then the double category $F\lCsp$ of \cref{thm:decorated_cospans_1} is symmetric monoidal, where the tensor product
 \begin{itemize}
@@
 \item of two vertical 1-morphisms $f \maps a \to b$ and $f' \maps a' \to b'$ is $f+f' \maps a+a' \to b+b'$ in $\A$,
-\item of two horizontal 1-cells $(a \to m \leftarrow b, s \in F(m))$ and $(c \to n \leftarrow d, t \in F(n))$ is
+\item of two horizontal 1-cells $(a \xrightarrow{i_1} m \xleftarrow{o_1} b, s \in F(m))$ and $(c \xrightarrow{i_2} n \xleftarrow{o_2} d, t \in F(n))$ is
 \[
@@
 \item a horizontal 1-cell is a pair of objects $a,b \in \A$ together with an
-object $c \in \C$ with $\Phi(c) = a + b$.
+object $c \in \C$ with $\Phi(c) = a + b$,
 \item a 2-morphism is a pair of morphisms $f \maps a \to a'$, $g \maps b \to b'$ 
@@
 Note that when $\C$ is the arrow category of $\A$ and $\Phi$ maps any arrow in $\C$ to its
-domain, an object of $\Fr(\Phi)$ simply amounts to a cospan in $\A$.
+domain, a horizontal 1-cell $\Fr(\Phi)$ simply amounts to a cospan in $\A$.
 In this case $\Fr(\Phi)$ is the double category of cospans in $\A$.
 We shall use variations on this idea to construct double categories of decorated and structured cospans, and to prove that under certain conditions these double categories are equivalent.
-We begin with decorated cospans, proving Theorem \ref{thm:decorated_cospans_1} and \ref{thm:decorated_cospans_2} by applying Shulman's result to a particular monoidal bifibration built from a lax monoidal pseudofunctor $F \maps (A,+) \to (\Cat,\times)$.
+We begin with decorated cospans, proving Theorem \ref{thm:decorated_cospans_1} and \ref{thm:decorated_cospans_2} by applying Shulman's result to a particular monoidal bifibration built from a lax monoidal pseudofunctor $F \maps (\A,+) \to (\Cat,\times)$.
 
@@
  F(a)\times F(a)\ar[r,"\phi_{a,a}"]\ar[d,"F(f)\times F(f)"']\ar[dr,phantom,"{\stackrel[\cref{eq:pseudonaturality}]{\phi_{f,f}}{\cong}}"] & 
- F(a+a)\ar[r,"F(\nabla)"]\ar[d,"F(f+f)"description]\ar[dr,phantom,"\cong"] & F(a)\ar[d,"Ff"] \\
+ F(a+a)\ar[r,"F(\nabla)"]\ar[d,"F(f+f)"description]\ar[dr,phantom,"\cong"] & F(a)\ar[d,"F(f)"] \\
  F(b)\times F(b)\ar[r,"\phi_{b,b}"'] & F(b+b)\ar[r,"F(\nabla)"'] & F(b)
@@
 \[ (f,1,1) \maps (a \xrightarrow{i' f} b' , s')\; \to \; (a' \xrightarrow{i'} b', s'). \]
-Denoting the cartesian lifting of $f$ to an object $z \in \A/U$ by $\mathrm{Cart}(f,z)$, the tensor product of $\A/U$ strictly preserves such cartesian liftings in the sense that $\mathrm{Cart}(f_1,z_1) \otimes \mathrm{Cart}(f_2,z_2)=\mathrm{Cart}(f_1 \otimes f_2, z_1 \otimes z_2)$.
+Denoting the cartesian lifting of $f$ to an object $z \in \A/U$ by $\mathrm{Cart}(f,z)$, the tensor product of $\A/U$ strictly preserves such cartesian liftings in the sense that $\mathrm{Cart}(f_1,z_1) \otimes \mathrm{Cart}(f_2,z_2)=\mathrm{Cart}(f_1 + f_2, z_1 \otimes z_2)$.
 
@@
 \]
-Suppose we are given a morphism 
+To show that $(f,g,1)$ is a cocartesian lifting of $f$, suppose we are given a morphism 
 \[    (f'',g'',h'') \maps (a \xrightarrow{i} b, s) \; \to \; (a'' \xrightarrow{i''} b'', s'')   \]
-in $\A/U$ and a morphism $k \maps a \to a''$ in $\A$ such that $\Phi(f'',g'',h'') = k f$.   To show that $(f,g,1)$ is a cocartesian lifting of $f$, we need to show there exists a unique morphism
+in $\A/U$ and a morphism $k \maps a' \to a''$ in $\A$ such that $\Phi(f'',g'',h'') = k f$.   We need to show there exists a unique morphism
 \[     (\tilde{f}, \tilde{g}, \tilde{h}) \maps (a' \xrightarrow{i'} b +_a a', F(g)(s)) \; \to \; (a'' \xrightarrow{i''} b'', s'') \]
@@
 It follows that $\Phi$ is a bifibration.
-Denoting the cocartesian lifting of a morphism $f$ to an object $z \in \A/U$ by $\mathrm{Cocart}(f,z)$, we have that $\mathrm{Cocart}(f_1,z_1) \otimes \mathrm{Cocart}(f_2,z_2) \cong \mathrm{Cocart}(f_1 \otimes f_2,z_1 \otimes z_2)$ by the universal map between two colimits of the same diagram.
+Denoting the cocartesian lifting of a morphism $f$ to an object $z \in \A/U$ by $\mathrm{Cocart}(f,z)$, we have that $\mathrm{Cocart}(f_1,z_1) \otimes \mathrm{Cocart}(f_2,z_2) \cong \mathrm{Cocart}(f_1 + f_2,z_1 \otimes z_2)$ by the universal map between two colimits of the same diagram.
 Thus, $\Phi$ is a monoidal bifibration.
@@
 \node (C) at (0,-1) {$(\A/U)_c$};
-\node (D) at (1.5,-1) {$(\A/U)_d$.};
+\node (D) at (1.5,-1) {$(\A/U)_d$};
 \node (E) at (0.75,-0.5) {$\Searrow \theta$};
@@
 \label{thm:functoriality}
-Given categories $\A$ and $\A'$ with finite colimits, lax monoidal pseudofunctors $F, F' \maps (\A',+) \to (\Cat,\times)$, a finite colimit preserving functor $H \maps \A \to \A'$, a lax monoidal pseudofunctor $E \maps (\Cat,\times) \to (\Cat,\times)$ and a natural isomorphism $\theta$ as in the following diagram:
+Given categories $\A$ and $\A'$ with finite colimits, lax monoidal pseudofunctors $F, F' \maps (\A',+) \to (\Cat,\times)$, a finite colimit preserving functor $H \maps \A \to \A'$, a lax monoidal pseudofunctor $E \maps (\Cat,\times) \to (\Cat,\times)$ and a monoidal natural isomorphism $\theta$ as in the following diagram:
 \[
@@
 \] 
-we obtain a double functor $\lH \maps F\lCsp \to F'\lCsp$ defined as above.  If $F, F'$ and $E$ are symmetric, then $\|H \maps F\lCsp \to F'\lCsp$ is a symmetric monoidal double functor. 
+we obtain a double functor $\lH \maps F\lCsp \to F'\lCsp$ defined as above.  If $F, F'$ and $E$ are symmetric, then $\lH \maps F\lCsp \to F'\lCsp$ is a symmetric monoidal double functor. 
 \end{thm}
@@
 The tensor product of two objects $(a,L(a) \xrightarrow{i} x)$ and $(a,L(a) \xrightarrow{i'} x')$ is given by
-\[  (a,L(a) \xrightarrow{i} x) + (a',L(a') \xrightarrow{i'} x')=(a+a',x+x',L(a+a')  \xrightarrow{\sim} L(a)+L(a') \xrightarrow{i+i'} x+x'). \]
-The monoidal unit is ${(0_\A,0_\X,{L(0_\A) \to 0_\X})}$.  It is clear that $\Psi \maps (L/\X, +) \to (\A,+)$ is a strict monoidal functor.
+\[  (a,L(a) \xrightarrow{i} x) + (a',L(a') \xrightarrow{i'} x')=(a+a',L(a+a')  \xrightarrow{\sim} L(a)+L(a') \xrightarrow{i+i'} x+x'). \]
+The monoidal unit is ${(0_\A,0_\X,{L(0_\A) \xrightarrow{!} 0_\X})}$.  It is clear that $\Psi \maps (L/\X, +) \to (\A,+)$ is a strict monoidal functor.
 
@@
 (D) edge node [above] {$g'$} (E)
-(A) edge node [left] {$I$} (D)
+(A) edge node [left] {$i$} (D)
 (C) edge [dashed] node [left,near end] {$\theta$} (F)
@@
 \path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$I \circ L(h)$} (B)
+(A) edge node[above]{$i L(h)$} (B)
 (A) edge node[left]{$L(k)$} (C)
@@
 to obtain the object $(c,L(c) \xrightarrow{\psi} L(c)+_{L(a)} x)$ of $(L/ \X)_c$.
-For the other route, first going down, we push the object $(b,x,L(b) \xrightarrow{I} x)$ forward along $L(g) \maps L(b) \to L(d)$ by taking the following pushout:
+For the other route, first going down, we push the object $(b,L(b) \xrightarrow{i} x)$ forward along $L(g) \maps L(b) \to L(d)$ by taking the following pushout:
 \[
@@
 \path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$I$} (B)
+(A) edge node[above]{$i$} (B)
 (A) edge node[left]{$L(g)$} (C)
@@
 \]
-which yields the object $(d,L(d) \xrightarrow{\theta} L(d)+_{L(b)} x)$ of $(L/\X)_d$.
+which yields the object $(d,L(d) \xrightarrow{\phi} L(d)+_{L(b)} x)$ of $(L/\X)_d$.
 Then going left, we precompose with $L(f) \maps L(c) \to L(d)$ to obtain the object $(c,L(c) \xrightarrow{\phi L(f)} L(d)+_{L(b)} x)$ of $(L/\X)_c$.
@@
 To show that the symmetric monoidal double categories $F\lCsp$ and $_L \lCsp(\inta F)$ of Theorems \ref{thm:decorated_cospans_2} and \ref{thm:structured_cospans} are isomorphic, we make use of a result of Shulman \cite[Theorem~14.11]{Shulman2010}.
-Namely, the $\mathbb{F}\mathbf{r}$ construction described in \cref{lem:shulman} extends to a 2-functor
+Namely, he showed that the $\mathbb{F}\mathbf{r}$ construction of \cref{lem:shulman} extends to a 2-functor
 \[ \mathbb{F}\mathbf{r} \maps \mathbf{FMF} \to \mathbf{FDbl} \]
 where $\mathbf{FMF}$ is the 2-category consisting of
-\begin{enumerate}
+\begin{itemize}
 \item Beck--Chevalley monoidal bifibrations,
@@
 \item monoidal transformations of bifibrations
-\end{enumerate}
-and $\mathbf{FDbl}$ is the 2-category of fibrant double categories, double functors and double transformations.
+\end{itemize}
+while $\mathbf{FDbl}$ is the 2-category of 
+\begin{itemize}
+\item fibrant double categories, 
+\item double functors, and 
+\item double transformations. 
+\end{itemize}
 Given two monoidal bifibrations $\Phi \maps \A \to \mathsf{B}$ and $\Phi' \maps \A' \to \mathsf{B}'$, a \define{strong monoidal morphism of bifibrations} from $\Phi$ to $\Phi'$ consists of a pair of strong monoidal functors $F_1$ and $F_2$ making the following square commute:
@@
 \node (C) at (2,0) {$b$};
-\node (D) at (4,0) {$\bot_b \in F(b)$};
+\node (D) at (4,0) {$\bot_b \in F(b),$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 where $\bot_b$ is the trivial decoration given by
-\[    \one \xrightarrow{\phi_0} F(0_\A) \xrightarrow{F(!)} F(b) , \]
+\[    \one \xrightarrow{\phi_0} F(0_\A) \xrightarrow{F(!_b)} F(b), \]
 into a companion of $f$ using the following 2-morphisms:
@@
 Unfortunately, some of these applications were marred by technical flaws, which were later fixed using structured cospans \cite{BC}.
-Here we explain how to also fix them using our new decorated cospans, since they provide another solution to these problems.
-Below we compare the two approaches in applications to graphs, electrical circuits, Petri nets, reaction networks and dynamical systems.
+Here we explain how they can also be fixed using our new decorated cospans.
+We compare the two approaches in applications to graphs, electrical circuits, Petri nets, reaction networks and dynamical systems.
 
 In many cases, \cref{thm:equiv} shows that the structured and decorated cospan approaches are equivalent: \cref{subsec:graphs,subsec:circuits,subsec:petri} illustrate this.
-However, in \cref{subsec:petrirates} we describe a map from `open Petri nets with rates' to open dynamical systems.
+However, in \cref{subsec:petrirates} we describe a map from open Petri nets with rates to open dynamical systems.
 The former are conveniently described using structured cospans, while the latter can only be treated using decorated cospans.

### 2021-06-22 cospans_new.tex
A bit more work on the intro of Section 4.

@@
 We now compare structured and decorated cospans.
-In \cref{thm:decorated_cospans_1} we built a double category of decorated cospans from a functor $\Phi \maps \A/U \to \A$.
-In \cref{thm:structured_cospans} we built a double category of structured cospans from a functor $\Psi \maps L/\X \to \A$.
+In \cref{thm:decorated_cospans_1} we built a double category of decorated cospans from a bifibration $\Phi \maps \A/U \to \A$.
+In \cref{thm:structured_cospans}, we built a double category of structured cospans from a bifibration $\Psi \maps L/\X \to \A$ in a very similar way.
 We now show that under certain conditions $L$ is left adjoint to $U$.
-Whenever this happens, $\A/U$ is isomorphic to $L/\X$, by a general fact about arrow categories.
-The bifibrations $\Phi$ and $\Psi$ are then also isomorphic.
-By the functoriality
-of Shulman's construction in \cref{lem:shulman}, it follows that the double category of decorated cospans is isomorphic to the double category of structured cospans.
+Whenever this happens, $\A/U$ is isomorphic to $L/\X$, by a simple and general fact about arrow categories.
+The bifibrations $\Phi$ and $\Psi$ are also isomorphic.
+By the functoriality of Shulman's construction in \cref{lem:shulman}, it follows that the double category of decorated cospans is isomorphic to the double category of structured cospans.
 

### 2021-06-22 cospans_new.tex
a few comments

@@
 \def\purple{\color{purple(x11)}}
-\def\chris{\purple}
+\def\chris{\purple Christina: }
 \def\john{\color{red}}
@@
 In \cref{EquivDoubleCats}, we briefly review the structured cospans framework and prove that the double categorical versions of decorated cospans and structured cospans are isomorphic under suitable conditions.
-In \cref{spinoffs}, we establish the isomorphism between structured and decorated cospans at the level of bicategories and categories (via decategorification).
+{\chris Section 3 is missing!} In \cref{spinoffs}, we establish the isomorphism between structured and decorated cospans at the level of bicategories and categories (via decategorification).
 Finally, in \cref{Applications}, we describe applications, and show that open dynamical system can be described using decorated cospans but not structured cospans.
@@
 However, when we say a functor `preserves finite colimits', it need only do this up to canonical isomorphism, unless otherwise specified.
+{\chris Shouldn't we say that the definition of a lax monoidal pseudofunctor is recalled there in the appendix?}
 
@@
 domain, a horizontal 1-cell $\Fr(\Phi)$ simply amounts to a cospan in $\A$.
-In this case $\Fr(\Phi)$ is the double category of cospans in $\A$.
+{\chris Perhaps a bit more spelling out here --using specific names of objects and arrows--could help the reader go through that important statement more easily.
+Optional.
+} In this case $\Fr(\Phi)$ is the double category of cospans in $\A$.
 We shall use variations on this idea to construct double categories of decorated and structured cospans, and to prove that under certain conditions these double categories are equivalent.
@@
 We recall these ideas in \cref{subsec:fibrations}; here we simply state the result we need.
+{\chris Well we don't recall the monoidal Grothendieck construction in the appendix, just the ordinary one, and the definition of a monoidal fibration.
+Slightly rephrase?
+And also add the definition of a monoidal indexed category in the appendix?}
 
@@
 \begin{proof}[Proof of \cref{thm:decorated_cospans_1}] 
-Let $U \maps \inta F \to \A$ be the monoidal opfibration associated to the lax monoidal pseudofunctor $F \maps (\A,+) \to (\Cat, \times)$.
-To obtain the desired double category we apply Shulman's \cref{lem:shulman} to the functor $\Phi \maps \A/U \to \A$, which we now describe in more detail.
+Let $U \maps \inta F \to \A$ be the monoidal opfibration associated to the lax monoidal pseudofunctor $F \maps (\A,+) \to (\Cat, \times)$ {\chris via \cref{lem:MonGroth}}.
+To obtain the desired double category we apply Shulman's {\chris it's OK to skip ``Shulman's'' here?} \cref{lem:shulman} to the functor $\Phi \maps \A/U \to \A$, which we now describe in more detail.
 In the comma category $\A/U$:
@@
 \end{itemize}
-As in any comma category we have a functor $\Phi \maps \A/U \to \A$; this is given on objects by $\Phi(a \xrightarrow{i} b, x)=a$ and on morphisms by $\Phi(f,g,h)=f$.
+As in any comma category we have a functor $\Phi \maps \A/U \to \A$ given on objects by $\Phi(a \xrightarrow{i} b, x)=a$ and on morphisms by $\Phi(f,g,h)=f$.
 
@@
 where $\phi$ is the laxator for $F$.  The monoidal unit is $(0_\A \xrightarrow{!} 0_\A, 0)$
-where $0 \in F(0_\A)$ is the object given by $\phi_0 \maps \one \to F(0_\A)$.   With this monoidal structure it is easy to see that $\Phi$ is strict monoidal.
+where $0 \in F(0_\A)$ is the object given by $\phi_0 \maps \one \to F(0_\A)$.   With this monoidal structure on $\A/U$, it is easy to see that $\Phi$ is a strict monoidal functor.
 
@@
 Denoting the cartesian lifting of $f$ to an object $z \in \A/U$ by $\mathrm{Cart}(f,z)$, the tensor product of $\A/U$ strictly preserves such cartesian liftings in the sense that $\mathrm{Cart}(f_1,z_1) \otimes \mathrm{Cart}(f_2,z_2)=\mathrm{Cart}(f_1 + f_2, z_1 \otimes z_2)$.
+{\chris We could put ``strictly'' in a parenthesis since even if it is true, it is not required for the definition of a monoidal fibration.
+In fact it is for the definition of monoidal split fibration but this is not relevant here.}
 
@@
 \node (D) at (1.5,-1) {$(\A/U)_d$};
-\node (E) at (0.75,-0.5) {$\Searrow \theta$};
+\node (E) at (0.75,-0.5) {$\scriptstyle\Downarrow \theta$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-defined in \eqref{theta}.   We need to prove that when the square in $\A$ is 
+defined in \eqref{theta}. {\chris I changed the two cell inside the square to match others in the paper.}  We need to prove that when the square in $\A$ is 
 a pushout, $\theta$ is a natural isomorphism.
@@
 
-This shows that $\Phi$ obeys the Beck--Chevalley condition.  Having checked all the hypotheses of \cref{lem:shulman}, we can define $F\lCsp$ to be $\Fr(\Phi)$.
+This shows that $\Phi$ obeys the Beck--Chevalley condition.
+Having checked all the hypotheses of \cref{lem:shulman}, we can define $F\lCsp$ to be $\Fr(\Phi)$ and conclude the proof of \cref{thm:decorated_cospans_1}.
 \end{proof}
@@
 
-Our construction gives not only decorated cospan double categories, but  also maps between these.
+Our construction {\chris it might not be a completely clear what we mean by ``our construction'' here.} gives not only decorated cospan double categories, but  also maps between these.
 For simplicity we only consider the monoidal case.
-Suppose we have two categories $\A,\A'$ with finite colimits and two lax monoidal pseudofunctors $F \maps \A \to \Cat$ and $F' \maps \A' \to \Cat$.
+{\chris we mean ``non-symmetric''?
+Although it seems we also talk about the symmetric case below!} Suppose we have two categories $\A,\A'$ with finite colimits and two lax monoidal pseudofunctors $F \maps \A \to \Cat$ and $F' \maps \A' \to \Cat$.
 Then we can obtain a map between their decorated cospan double categories, namely a double functor $\lH \maps F\lCsp \to F' \lCsp$, from:
@@
 \node (D) at (1,-1) {$\Cat$.};
-\node (E) at (0.5,-0.5) {$\Swarrow\theta$};
+\node (E) at (0.5,-0.5) {$\scriptstyle\Downarrow\theta$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \node (D) at (1,-1) {$\Cat$};
-\node (E) at (0.5,-0.5) {$\Swarrow \theta$};
+\node (E) at (0.5,-0.5) {$\scriptstyle\Downarrow\theta$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 
+{\chris Since a fibration and an opfibration were not in a definition environment, I think bifibration does not need to be in one as well.}
+
 \begin{defn}
@@
 
+{\chris Since we still use monoidal opfibrations in the main text, it could be better to say what a monoidal opfibration and fibration is first, and then the monoidal bifibration. Suggestion:
+
+If $\X$ and $\A$ are (symmetric) monoidal categories, a \define{(symmetric) monoidal fibration} $\Phi \maps \X \to \A$ is a fibration that is also a (symmetric) strict monoidal functor, such that the tensor product of $\X$ preserves cartesian liftings.
+Similarly, a \define{(symmetric) monoidal opfibration} is an opfibration that is also a (symmetric) strict monoidal functor, such that the tensor product of the total category preserves cocartesian liftings, whereas for a \define{(symmetric) monoidal bifibration} the tensor product preserves both cartesian and cocartesian liftings.
+}
+
 In a bifibration we have both covariant and contravariant reindexing functors, and in 
-fact $f_!$ is left adjoint to $f^*$ \cite[Proposition 3.9]{Shulman2008}.   Using this one can easily show that for any commutative square in $\A$
+fact $f_!$ is left adjoint to $f^*$ \cite[Proposition 3.9]{Shulman2008}.   Using this, one can easily show that for any commutative square in $\A$
 \[
@@
 \node (D) at (1.5,-1) {$\C_d$};
-\node (E) at (0.75,-0.5) {$\Searrow \theta$};
+\node (E) at (0.75,-0.5) {$\scriptstyle\Downarrow \theta$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \label{theta}
-   k_! h^\ast \To k_! h^\ast g^\ast g_! = k_! k^\ast f^\ast g^! \To f^\ast g_! . 
+   k_! h^\ast \To k_! h^\ast g^\ast g_! = k_! k^\ast f^\ast g_! \To f^\ast g_! . 
 \end{equation}
+{\chris Shouldn't the middle equality be an isomorphism?}
 If $\theta$ is a natural isomorphism whenever the original square in $\A$ is
-a pushout, we say $\Phi$ is \define{Beck--Chevalley}.  (Shulman  uses the term `strongly co-BC' \cite[Definition 13.21] {Shulman2008}.)
+a pushout, we say that the bifibration $\Phi$ is \define{Beck--Chevalley}.  (Shulman  uses the term `strongly co-BC' \cite[Definition 13.21] {Shulman2008}.)
 

### 2021-06-22 cospans_new.tex
edits

@@
 \]
-Namely, we have $\theta = (1, \zeta, 1)$.   But when the original square in $\A$ (at upper left 
+Namely, we have $\theta = (1, \zeta, 1)$. {\chris Should this really be a triple?}   But when the original square in $\A$ (at upper left 
 above) is a pushout, its pasting with the other pushout gives a pushout, so $\zeta$ and hence $\theta$ is isomorphism.
@@
 Here we recall this formalism and give a new construction of the double category of structured cospans that clarifies their relation to decorated cospans.
-This new construction again uses Shulman's \cref{lem:shulman}.
+{\chris Do we want to briefly mention that in the abstact?} This new construction again uses Shulman's \cref{lem:shulman}.
 
@@
 \node (D) at (1.5,-1) {$(L/\X)_d$};
-\node (E) at (0.75,-0.5) {$\Searrow \theta$};
+\node (E) at (0.75,-0.5) {$\scriptstyle\Downarrow \theta$};
 \path[->,font=\scriptsize,>=angle 90]

### 2021-06-22 cospans_new.tex
edits

@@
 The bifibrations $\Phi$ and $\Psi$ are also isomorphic.
-By the functoriality of Shulman's construction in \cref{lem:shulman}, it follows that the double category of decorated cospans is isomorphic to the double category of structured cospans.
+By the functoriality of Shulman's construction in \cref{lem:shulman}, {\chris but this functoriality is not spelled out there at the moment!
+We should probably add it, see next next comment.} it follows that the double category of decorated cospans is isomorphic to the double category of structured cospans.
 
@@
 For this, let $\Rex$ be the 2-category of categories with finite colimits, functors preserving finite colimits, and natural transformations.
-Also let $\SMC$ be the 2-category of symmetric monoidal categories, strong symmetric monoidal functors and natural transformations.
+Also let $\SMC$ be the 2-category of symmetric monoidal categories, strong symmetric monoidal functors {\chris symmetric strong mon funs?} and natural transformations.
 Recall that for us a category $\C \in \Rex$ comes with a choice of finite colimits, so it gives a specific cocartesian monoidal category $(\C,+)$, and this induces a 2-functor $\Rex \to \SMC$.
@@
 To show that the symmetric monoidal double categories $F\lCsp$ and $_L \lCsp(\inta F)$ of Theorems \ref{thm:decorated_cospans_2} and \ref{thm:structured_cospans} are isomorphic, we make use of a result of Shulman \cite[Theorem~14.11]{Shulman2010}.
-Namely, he showed that the $\mathbb{F}\mathbf{r}$ construction of \cref{lem:shulman} extends to a 2-functor
+{\chris Shouldn't this material be moved outside the proof environment, probably earlier?} Namely, he showed that the $\mathbb{F}\mathbf{r}$ construction of \cref{lem:shulman} extends to a 2-functor
 \[ \mathbb{F}\mathbf{r} \maps \mathbf{FMF} \to \mathbf{FDbl} \]
@@
 is symmetric monoidal.}
+{\chris Even so, shouldn't we also add some of the explicit isomorphism mapping to make the isomorphism between those two double categories more concrete?}
 \end{proof}

### 2021-06-22 cospans_new.tex
tiny changes

--- 2021-06-22 cospans_new.tex
@@
 % in LaTeX
-% 2021/6/20 - Finishing up
+% 2021/6/22 - Finishing up
 
@@
 \def\purple{\color{purple(x11)}}
-\def\chris{\purple Christina: }
+\def\chris{\purple}
 \def\john{\color{red}}
@@
 In \cref{EquivDoubleCats}, we briefly review the structured cospans framework and prove that the double categorical versions of decorated cospans and structured cospans are isomorphic under suitable conditions.
-{\chris Section 3 is missing!} In \cref{spinoffs}, we establish the isomorphism between structured and decorated cospans at the level of bicategories and categories (via decategorification).
+In \cref{spinoffs}, we establish the isomorphism between structured and decorated cospans at the level of bicategories and categories (via decategorification).
 Finally, in \cref{Applications}, we describe applications, and show that open dynamical system can be described using decorated cospans but not structured cospans.
@@
 However, when we say a functor `preserves finite colimits', it need only do this up to canonical isomorphism, unless otherwise specified.
-{\chris Shouldn't we say that the definition of a lax monoidal pseudofunctor is recalled there in the appendix?}
 
@@
 domain, a horizontal 1-cell $\Fr(\Phi)$ simply amounts to a cospan in $\A$.
-{\chris Perhaps a bit more spelling out here --using specific names of objects and arrows--could help the reader go through that important statement more easily.
-Optional.
-} In this case $\Fr(\Phi)$ is the double category of cospans in $\A$.
+In this case $\Fr(\Phi)$ is the double category of cospans in $\A$.
 We shall use variations on this idea to construct double categories of decorated and structured cospans, and to prove that under certain conditions these double categories are equivalent.
@@
 We recall these ideas in \cref{subsec:fibrations}; here we simply state the result we need.
-{\chris Well we don't recall the monoidal Grothendieck construction in the appendix, just the ordinary one, and the definition of a monoidal fibration.
-Slightly rephrase?
-And also add the definition of a monoidal indexed category in the appendix?}
 
@@
 \begin{proof}[Proof of \cref{thm:decorated_cospans_1}] 
-Let $U \maps \inta F \to \A$ be the monoidal opfibration associated to the lax monoidal pseudofunctor $F \maps (\A,+) \to (\Cat, \times)$ {\chris via \cref{lem:MonGroth}}.
-To obtain the desired double category we apply Shulman's {\chris it's OK to skip ``Shulman's'' here?} \cref{lem:shulman} to the functor $\Phi \maps \A/U \to \A$, which we now describe in more detail.
+Let $U \maps \inta F \to \A$ be the monoidal opfibration associated to the lax monoidal pseudofunctor $F \maps (\A,+) \to (\Cat, \times)$.
+To obtain the desired double category we apply Shulman's \cref{lem:shulman} to the functor $\Phi \maps \A/U \to \A$, which we now describe in more detail.
 In the comma category $\A/U$:
@@
 \end{itemize}
-As in any comma category we have a functor $\Phi \maps \A/U \to \A$ given on objects by $\Phi(a \xrightarrow{i} b, x)=a$ and on morphisms by $\Phi(f,g,h)=f$.
+As in any comma category we have a functor $\Phi \maps \A/U \to \A$; this is given on objects by $\Phi(a \xrightarrow{i} b, x)=a$ and on morphisms by $\Phi(f,g,h)=f$.
 
@@
 where $\phi$ is the laxator for $F$.  The monoidal unit is $(0_\A \xrightarrow{!} 0_\A, 0)$
-where $0 \in F(0_\A)$ is the object given by $\phi_0 \maps \one \to F(0_\A)$.   With this monoidal structure on $\A/U$, it is easy to see that $\Phi$ is a strict monoidal functor.
+where $0 \in F(0_\A)$ is the object given by $\phi_0 \maps \one \to F(0_\A)$.   With this monoidal structure it is easy to see that $\Phi$ is strict monoidal.
 
@@
 Denoting the cartesian lifting of $f$ to an object $z \in \A/U$ by $\mathrm{Cart}(f,z)$, the tensor product of $\A/U$ strictly preserves such cartesian liftings in the sense that $\mathrm{Cart}(f_1,z_1) \otimes \mathrm{Cart}(f_2,z_2)=\mathrm{Cart}(f_1 + f_2, z_1 \otimes z_2)$.
-{\chris We could put ``strictly'' in a parenthesis since even if it is true, it is not required for the definition of a monoidal fibration.
-In fact it is for the definition of monoidal split fibration but this is not relevant here.}
 
@@
 \node (D) at (1.5,-1) {$(\A/U)_d$};
-\node (E) at (0.75,-0.5) {$\scriptstyle\Downarrow \theta$};
+\node (E) at (0.75,-0.5) {$\Searrow \theta$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-defined in \eqref{theta}. {\chris I changed the two cell inside the square to match others in the paper.}  We need to prove that when the square in $\A$ is 
+defined in \eqref{theta}.   We need to prove that when the square in $\A$ is 
 a pushout, $\theta$ is a natural isomorphism.
@@
 
-This shows that $\Phi$ obeys the Beck--Chevalley condition.
-Having checked all the hypotheses of \cref{lem:shulman}, we can define $F\lCsp$ to be $\Fr(\Phi)$ and conclude the proof of \cref{thm:decorated_cospans_1}.
+This shows that $\Phi$ obeys the Beck--Chevalley condition.  Having checked all the hypotheses of \cref{lem:shulman}, we can define $F\lCsp$ to be $\Fr(\Phi)$.
 \end{proof}
@@
 
-Our construction {\chris it might not be a completely clear what we mean by ``our construction'' here.} gives not only decorated cospan double categories, but  also maps between these.
+Our construction gives not only decorated cospan double categories, but  also maps between these.
 For simplicity we only consider the monoidal case.
-{\chris we mean ``non-symmetric''?
-Although it seems we also talk about the symmetric case below!} Suppose we have two categories $\A,\A'$ with finite colimits and two lax monoidal pseudofunctors $F \maps \A \to \Cat$ and $F' \maps \A' \to \Cat$.
+Suppose we have two categories $\A,\A'$ with finite colimits and two lax monoidal pseudofunctors $F \maps \A \to \Cat$ and $F' \maps \A' \to \Cat$.
 Then we can obtain a map between their decorated cospan double categories, namely a double functor $\lH \maps F\lCsp \to F' \lCsp$, from:
@@
 \node (D) at (1,-1) {$\Cat$.};
-\node (E) at (0.5,-0.5) {$\scriptstyle\Downarrow\theta$};
+\node (E) at (0.5,-0.5) {$\Swarrow\theta$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \node (D) at (1,-1) {$\Cat$};
-\node (E) at (0.5,-0.5) {$\scriptstyle\Downarrow\theta$};
+\node (E) at (0.5,-0.5) {$\Swarrow \theta$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 
-{\chris Since a fibration and an opfibration were not in a definition environment, I think bifibration does not need to be in one as well.}
-
 \begin{defn}
@@
 
-{\chris Since we still use monoidal opfibrations in the main text, it could be better to say what a monoidal opfibration and fibration is first, and then the monoidal bifibration. Suggestion:
-
-If $\X$ and $\A$ are (symmetric) monoidal categories, a \define{(symmetric) monoidal fibration} $\Phi \maps \X \to \A$ is a fibration that is also a (symmetric) strict monoidal functor, such that the tensor product of $\X$ preserves cartesian liftings.
-Similarly, a \define{(symmetric) monoidal opfibration} is an opfibration that is also a (symmetric) strict monoidal functor, such that the tensor product of the total category preserves cocartesian liftings, whereas for a \define{(symmetric) monoidal bifibration} the tensor product preserves both cartesian and cocartesian liftings.
-}
-
 In a bifibration we have both covariant and contravariant reindexing functors, and in 
-fact $f_!$ is left adjoint to $f^*$ \cite[Proposition 3.9]{Shulman2008}.   Using this, one can easily show that for any commutative square in $\A$
+fact $f_!$ is left adjoint to $f^*$ \cite[Proposition 3.9]{Shulman2008}.   Using this one can easily show that for any commutative square in $\A$
 \[
@@
 \node (D) at (1.5,-1) {$\C_d$};
-\node (E) at (0.75,-0.5) {$\scriptstyle\Downarrow \theta$};
+\node (E) at (0.75,-0.5) {$\Searrow \theta$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \label{theta}
-   k_! h^\ast \To k_! h^\ast g^\ast g_! = k_! k^\ast f^\ast g_! \To f^\ast g_! . 
+   k_! h^\ast \To k_! h^\ast g^\ast g_! = k_! k^\ast f^\ast g^! \To f^\ast g_! . 
 \end{equation}
-{\chris Shouldn't the middle equality be an isomorphism?}
 If $\theta$ is a natural isomorphism whenever the original square in $\A$ is
-a pushout, we say that the bifibration $\Phi$ is \define{Beck--Chevalley}.  (Shulman  uses the term `strongly co-BC' \cite[Definition 13.21] {Shulman2008}.)
+a pushout, we say $\Phi$ is \define{Beck--Chevalley}.  (Shulman  uses the term `strongly co-BC' \cite[Definition 13.21] {Shulman2008}.)
 

### 2021-06-22 cospans_new.tex
dealt with all but one of Christina's comments in purple

@@
 First, given a functor $L \maps \A \to \X$, a `structured cospan' is a diagram in $\X$ of the form $L(a) \rightarrow x \leftarrow L(b)$.
-If $\A$ and $\X$ have finite colimits and $L$ preserves them, it is known that there is a symmetric monoidal double category whose objects are those of $\A$ and whose horizontal 1-cells are structured cospans.
+We give a new proof that if $\A$ and $\X$ have finite colimits and $L$ preserves them, there is a symmetric monoidal double category whose objects are those of $\A$ and whose horizontal 1-cells are structured cospans.
 Second, given a pseudofunctor $F \maps \A \to \Cat$, a `decorated cospan' is a diagram in $\A$ of the form $a \rightarrow m \leftarrow b$ together with an object of $F(m)$.
@@
 However, when we say a functor `preserves finite colimits', it need only do this up to canonical isomorphism, unless otherwise specified.
+We recall the concept of lax monoidal pseudofunctor in \cref{subsec:bicats}.
 
@@
 Note that when $\C$ is the arrow category of $\A$ and $\Phi$ maps any arrow in $\C$ to its
-domain, a horizontal 1-cell $\Fr(\Phi)$ simply amounts to a cospan in $\A$.
+domain, a horizontal 1-cell in $\Fr(\Phi)$ simply amounts to a cospan in $\A$.
 In this case $\Fr(\Phi)$ is the double category of cospans in $\A$.
@@
 We need two refinements of this construction: one that gives monoidal opfibrations, and one that gives symmetric monoidal opfibrations.
-We recall these ideas in \cref{subsec:fibrations}; here we simply state the result we need.
+We recall pseudofunctors in \cref{subsec:bicats}, and opfibrations in \cref{subsec:fibrations}; here we simply state the result we need.
+{\chris Should we add the definition of a monoidal opindexed category in the appendix?}
 
@@
 Then an $F$-decorated cospan from $a$ to $b$ amounts to an object $c \in \A/U$ such that $\Phi(c) = a + b$.
-With this choice of $\Phi$, Shulman's result gives the double category of $F$-decorated cospans.
+With this choice of $\Phi$, Shulman's \ref{lem:shulman} gives the double category of $F$-decorated cospans.
 
 \begin{proof}[Proof of \cref{thm:decorated_cospans_1}] 
-Let $U \maps \inta F \to \A$ be the monoidal opfibration associated to the lax monoidal pseudofunctor $F \maps (\A,+) \to (\Cat, \times)$.
-To obtain the desired double category we apply Shulman's \cref{lem:shulman} to the functor $\Phi \maps \A/U \to \A$, which we now describe in more detail.
+Let $U \maps \inta F \to \A$ be the monoidal opfibration associated to the lax monoidal pseudofunctor $F \maps (\A,+) \to (\Cat, \times)$ via \cref{lem:MonGroth}.
+To obtain the desired double category we apply \cref{lem:shulman} to the functor $\Phi \maps \A/U \to \A$, which we now describe in more detail.
 In the comma category $\A/U$:
@@
 \[ (f,1,1) \maps (a \xrightarrow{i' f} b' , s')\; \to \; (a' \xrightarrow{i'} b', s'). \]
-Denoting the cartesian lifting of $f$ to an object $z \in \A/U$ by $\mathrm{Cart}(f,z)$, the tensor product of $\A/U$ strictly preserves such cartesian liftings in the sense that $\mathrm{Cart}(f_1,z_1) \otimes \mathrm{Cart}(f_2,z_2)=\mathrm{Cart}(f_1 + f_2, z_1 \otimes z_2)$.
+Denoting the cartesian lifting of $f$ to an object $z \in \A/U$ by $\mathrm{Cart}(f,z)$, the tensor product of $\A/U$ preserves such cartesian liftings, in fact strictly, in the sense that $\mathrm{Cart}(f_1,z_1) \otimes \mathrm{Cart}(f_2,z_2)=\mathrm{Cart}(f_1 + f_2, z_1 \otimes z_2)$.
 
@@
 
-Our construction gives not only decorated cospan double categories, but  also maps between these.
-For simplicity we only consider the monoidal case.
+The decorated cospan formalism gives not only double categories, but also maps between these.
 Suppose we have two categories $\A,\A'$ with finite colimits and two lax monoidal pseudofunctors $F \maps \A \to \Cat$ and $F' \maps \A' \to \Cat$.
@@
 The bifibrations $\Phi$ and $\Psi$ are also isomorphic.
-By the functoriality of Shulman's construction in \cref{lem:shulman}, it follows that the double category of decorated cospans is isomorphic to the double category of structured cospans.
+Because  Shulman's construction in \cref{lem:shulman} is actually functorial, it follows that the double category of decorated cospans is isomorphic to the double category of structured cospans.
 
@@
 For this, let $\Rex$ be the 2-category of categories with finite colimits, functors preserving finite colimits, and natural transformations.
-Also let $\SMC$ be the 2-category of symmetric monoidal categories, strong symmetric monoidal functors and natural transformations.
+Also let $\SMC$ be the 2-category of symmetric monoidal categories, symmetric strong monoidal functors and natural transformations.
 Recall that for us a category $\C \in \Rex$ comes with a choice of finite colimits, so it gives a specific cocartesian monoidal category $(\C,+)$, and this induces a 2-functor $\Rex \to \SMC$.
 
-Our main resut is this:
+Our main result is this:
 
@@
 
-As a left adjoint, $L$ preserves all colimits that exist between the categories $\A$ and $\inta F$, which have finite colimits, so we can construct the double category of structured cospans $_L\lCsp(\inta F)$ of \cref{thm:structured_cospans}.
-
-To show that the symmetric monoidal double categories $F\lCsp$ and $_L \lCsp(\inta F)$ of Theorems \ref{thm:decorated_cospans_2} and \ref{thm:structured_cospans} are isomorphic, we make use of a result of Shulman \cite[Theorem~14.11]{Shulman2010}.
-Namely, he showed that the $\mathbb{F}\mathbf{r}$ construction of \cref{lem:shulman} extends to a 2-functor
+As a left adjoint, $L$ preserves all colimits that exist between the categories $\A$ and $\inta F$, which have finite colimits.
+Thus, we can construct the symmetric monoidal double category of structured cospans $_L\lCsp(\inta F)$ as in \cref{thm:structured_cospans}.
+To show that this is isomorphic to the symmetric monoidal double category of decorated cospans $F\lCsp$ given by  \cref{thm:decorated_cospans_2}, we use a result of Shulman \cite[Theorem~14.11]{Shulman2010}.
+Namely, the $\mathbb{F}\mathbf{r}$ construction of \cref{lem:shulman} extends to a 2-functor
 \[ \mathbb{F}\mathbf{r} \maps \mathbf{FMF} \to \mathbf{FDbl} \]
@@
 \end{itemize}
-Given two monoidal bifibrations $\Phi \maps \A \to \mathsf{B}$ and $\Phi' \maps \A' \to \mathsf{B}'$, a \define{strong monoidal morphism of bifibrations} from $\Phi$ to $\Phi'$ consists of a pair of strong monoidal functors $F_1$ and $F_2$ making the following square commute:
+Given two monoidal bifibrations $\Phi \maps \A \to \mathsf{B}$ and $\Phi' \maps \A' \to \mathsf{B}'$, a `strong monoidal morphism of bifibrations' from $\Phi$ to $\Phi'$ consists of a pair of strong monoidal functors $F_1$ and $F_2$ making the following square commutes
 \[
@@
 (B) edge node[right]{$\Phi'$} (D)
-(C) edge node[above]{$F_2$} (D);
-\end{tikzpicture}
-\]
-and such that the identity $\Phi' F_1 = F_2 \Phi$ is a monoidal transformation.
-The two monoidal bifibrations in question are the functors $\Phi$ and $\Psi$ of Theorems \ref{thm:decorated_cospans_2} and \ref{thm:structured_cospans}, respectively, which share $\A$ as a common base, and thus we only need a single strong monoidal functor $F \maps \A/U \to L/\X$ making this diagram commute:
+(C) edge node[below]{$F_2$} (D);
+\end{tikzpicture}
+\]
+not just as functors but as strong monoidal functors.
+In our case the two monoidal bifibrations are the functors $\Phi$ and $\Psi$ of Theorems \ref{thm:decorated_cospans_2} and \ref{thm:structured_cospans}, respectively.
+These share $\A$ as a common base, so we only need a single strong monoidal functor $F \maps \A/U \to L/\X$ making this diagram of strong monoidal functors commute:
 \[
@@
 \node (B) at (2,0) {$L/ \X$};
-\node (C) at (1,-1.5) {$\A$};
+\node (C) at (1,-1.5) {$\A$.};
 %\node (D) at (2,-1) {$\A$};
@@
 \]
-{\john with $\Psi F=\Phi$ a monoidal transformation.}  There is an isomorphism $F \maps \A/U \to L/\X$ arising from the fact that $U$ is right adjoint to $L$.
-It is clear that $F$ is strong monoidal via componentwise binary coproducts which are preserved by both $L$ and $U$, {\john and that the identity $\Psi F=\Phi$ is a monoidal transformation.} As $F$ is an isomorphism, we obtain an isomorphism
+There is an isomorphism $F \maps \A/U \to L/\X$ arising from the fact that $U$ is right adjoint to $L$.
+It is clear that $F$ is strong monoidal via componentwise binary coproducts which are preserved by both $L$ and $U$, and that $\Psi F=\Phi$ as strong monoidal functors.
+As $F$ is an isomorphism, we obtain an isomorphism
 \[  \mathbb{F}\mathbf{r}(F) \maps \mathbb{F}\mathbf{r}(\Phi) \to \mathbb{F}\mathbf{r}(\Psi)\] between the two monoidal double categories $\mathbb{F}\mathbf{r}(\Phi)=F\lCsp$ and $\mathbb{F}\mathbf{r}(\Psi)= {}_L \lCsp(\inta F)$ of Theorems \ref{thm:decorated_cospans_2} and \ref{thm:structured_cospans}, respectively.
-{\john One can check by hand that this isomorphism
-is symmetric monoidal.}
+One can check by hand that this isomorphism
+is symmetric monoidal.
 \end{proof}
+
+Given the hypothesis of \cref{thm:equiv}, the isomorphism from $F\lCsp$ to ${}_L\lCsp(\inta F)$ works as follows.   It is the identity on objects and vertical morphisms, 
+which are just objects and morphisms of $\A$.   It maps the decorated cospan
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$a$};
+\node (B) at (1,0) {$m$};
+\node (C) at (2,0) {$b$,};
+\node (D) at (3,0) {$s \in F(m)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i$} (B)
+(C) edge node[above]{$o$} (B);
+\end{tikzpicture}
+\]
+to the structured cospan
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$L(a)$};
+\node (B) at (1,0) {$(m,s)$};
+\node (C) at (2,0) {$L(a).$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i$} (B)
+(C) edge node[above]{$o$} (B);
+\end{tikzpicture}
+\]
+Here $L(a)$ is the initial object in the fiber of $\X = \inta F$ over $a \in A$, namely $(a,t_a)$ 
+where $t_a \in F(a)$ is the trivial decoration
+\[    \one \xrightarrow{\phi_0} F(0_\A) \xrightarrow{F(!_a)} F(a). \]
+Finally, this isomorphism maps the map of decorated cospans
+\[
+\begin{tikzpicture}[scale=1.5,baseline=(current bounding box.center)]
+\node (A) at (0,0.5) {$a$};
+\node (A') at (0,-0.5) {$a'$};
+\node (B) at (1,0.5) {$m$};
+\node (C) at (2,0.5) {$b$};
+\node (C') at (2,-0.5) {$b'$};
+\node (D) at (1,-0.5) {$m'$};
+\node (E) at (3,0.5) {$s \in F(m)$};
+\node (F) at (3,-0.5) {$s' \in F(m')$};
+\node (G) at (1,-1) {$\tau \maps F(h)(s) \to s'$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i$} (B)
+(C) edge node[above]{$o$} (B)
+(A) edge node[left]{$f$} (A')
+(C) edge node[right]{$g$} (C')
+(A') edge node[below] {$i'$} (D)
+(C') edge node[below] {$o'$} (D)
+(B) edge node [left] {$h$} (D);
+\end{tikzpicture}
+\]
 
@@
 \begin{proof}
+{\john Here we are using $\bot_b$ to mean trivial decoration.  Sometimes we do this, and
+sometimes we use it to mean initial object in the fiber of $b$.  This leads to the strange
+result $\bot_b = (b,\bot_b)$.}  
 We show that any vertical 1-morphism $f \maps a \to b$ in $F\lCsp$ has a companion and a conjoint.  First, we can make this horizontal 1-cell $\hat{f}$:
@@
 
-\begin{defn}
-A functor $\Phi \maps \X \to \A$ is a \define{bifibration} if it is both a fibration and an opfibration.     
-\end{defn}
-
-\begin{defn}
- If $\X$ and $\A$ are monoidal categories, a \define{monoidal} bifibration $\Phi \maps \X \to \A$ is a bifibration that is also a strict monoidal functor, such that the tensor product preserves cartesian and cocartesian liftings.
-Similarly, if $\C$ and $\A$ are symmetric monoidal, a \define{symmetric monoidal} bifibration is a bifibration $\Phi \maps \C \to \A$ that is a symmetric strict monoidal functor.
-\end{defn}
+If $\X$ and $\A$ are (symmetric) monoidal categories, a \define{(symmetric) monoidal fibration} $\Phi \maps \X \to \A$ is a fibration that is also a (symmetric) strict monoidal functor, such that the tensor product preserves cartesian liftings.
+Similarly, a \define{(symmetric) monoidal opfibration} is an opfibration that is also a (symmetric) strict monoidal functor, such that the tensor product preserves cocartesian liftings.
+Finally, a \define{(symmetric) monoidal bifibration} is a bifibration that is also a (symmetric) strict monoidal functor such that the tensor product preserves both cartesian and cocartesian liftings.
 
 In a bifibration we have both covariant and contravariant reindexing functors, and in 
-fact $f_!$ is left adjoint to $f^*$ \cite[Proposition 3.9]{Shulman2008}.   Using this one can easily show that for any commutative square in $\A$
+fact $f_!$ is left adjoint to $f^*$ \cite[Proposition 3.9]{Shulman2008}.   Using this, one can easily show that for any commutative square in $\A$
 \[

### 2021-06-23 cospans_new.tex
a few comments

@@
 We recall pseudofunctors in \cref{subsec:bicats}, and opfibrations in \cref{subsec:fibrations}; here we simply state the result we need.
-{\chris Should we add the definition of a monoidal opindexed category in the appendix?}
 
@@
 \label{lem:MonGroth}
-There is a 2-equivalence between the 2-categories of monoidal opfibrations and monoidal opindexed categories with a given base, and if the base is cocartesian monoidal, there is a 2-equivalence between these and pseudofunctors into $\MonCat$.
-Similarly there is a 2-equivalence between symmetric monoidal opfibrations and symmetric monoidal opindexed categories, and if the base is cocartesian monoidal, also a 2-equivalence between these and pseudofunctors into $\SMC$.
+There is a 2-equivalence between the 2-categories of monoidal opfibrations $U: (\mathsf{X}, \otimes) \to (\mathsf{A}, \otimes)$ and monoidal pseudofunctors $F: (\mathsf{A},\otimes) \to (\mathsf{Cat}, \times)$ , and if $\mathsf{A}$ cocartesian monoidal, there is a 2-equivalence between these and pseudofunctors from $\A$ into $\MonCat$.
+Similarly there is a 2-equivalence between the 2-categories of symmetric monoidal opfibrations $U: (\mathsf{X}, \otimes) \to (\mathsf{A}, \otimes)$ and symmetric monoidal pseudofunctors $F: (\mathsf{A},\otimes) \to (\mathsf{Cat}, \times)$ , and if $\mathsf{A}$ cocartesian monoidal, there is a 2-equivalence between these and pseudofunctors from $\A$ into $\SMC$.
 \end{lem}
@@
 where $\iota_a \maps a\to a+b$ and $\iota_b \maps b \to a+b$ are the coproduct inclusions in $\A$ and the coproduct in the second component is in the fiber $F(a+b)$.
+{\chris Which parts of this section are actually used in the current proof of 4.1?
+Keep only those!}
 
@@
 \[    \one \xrightarrow{\phi_0} F(0_\A) \xrightarrow{F(!_a)} F(a). \]
+{\chris Right, but $i$ and $o$ are also specific pairs of maps in the Grothendieck category, see equation 26 in earlier version.}
 Finally, this isomorphism maps the map of decorated cospans
@@
 \]
+{\chris ... to that and that map of structured cospans!}
 

### 2021-06-23 cospans_new.tex
fixed a bunch of \bot problems

--- 2021-06-22 cospans_new.tex
@@
 % in LaTeX
-% 2021/6/22 - Finishing up
+% 2021/6/23 - Finishing up
 
@@
 
-\usepackage{amssymb,amsmath,stmaryrd,txfonts,mathrsfs,amsthm}
+\usepackage{amssymb,amsmath,stmaryrd,txfonts,mathrsfs,amsthm,undertilde}
 \usepackage{comment}
@@
 \label{lem:MonGroth}
-There is a 2-equivalence between the 2-categories of monoidal opfibrations and monoidal opindexed categories with a given base, and if the base is cocartesian monoidal, there is a 2-equivalence between these and pseudofunctors into $\MonCat$.
-Similarly there is a 2-equivalence between symmetric monoidal opfibrations and symmetric monoidal opindexed categories, and if the base is cocartesian monoidal, also a 2-equivalence between these and pseudofunctors into $\SMC$.
+For any monoidal category $(\A,\otimes)$, there is a 2-equivalence between the 2-categories of monoidal opfibrations $U\maps (\X, \otimes) \to (\A, \otimes)$ and monoidal pseudofunctors $F \maps (\A,\otimes) \to (\mathsf{Cat}, \times)$, and if $\A$ cocartesian monoidal, there is a 2-equivalence between these and pseudofunctors from $\A$ into $\MonCat$.
+If $\A$ is symmetric monoidal, there is also a 2-equivalence between the 2-categories of symmetric monoidal opfibrations $U \maps (\X, \otimes) \to (\A, \otimes)$ and symmetric monoidal pseudofunctors $F \maps  (\A,\otimes) \to (\mathsf{Cat}, \times)$ , and if $\A$ cocartesian monoidal, there is a 2-equivalence between these and pseudofunctors from $\A$ into $\SMC$.
 \end{lem}
@@
 Such a commuting square is a morphism in Shulman's 2-category of Beck--Chevalley monoidal bifibrations.
-Appying Shulman's 2-functor $\mathbb{F}\mathbf{r}$ to this morphism \cite[Theorem 14.11]{Shulman2008}, we obtain the desired double functor
+Applying Shulman's 2-functor $\mathbb{F}\mathbf{r}$ to this morphism \cite[Theorem 14.11]{Shulman2008}, we obtain the desired double functor
 \[ \mathbb{H} \maps  F\lCsp \to F'\lCsp .\]
@@
 The second part formulates the existence of colimits \emph{globally} in the total category $\inta F$, and if we let $\J$ range over all finite categories it says that $\X$ has finite colimits and $U$ preserves all finite colimits.
-As an example, suppose that $\A$ has pushouts and a Grothendieck opfibration $U \maps \inta F \to\A$ has fiberwise pushouts preserved by its reindexing functors.
+
+\iffalse As an example, suppose that $\A$ has pushouts and a Grothendieck opfibration $U \maps \inta F \to\A$ has fiberwise pushouts preserved by its reindexing functors.
 We can construct pushouts in $\inta F$ as follows:
@@
 where $\iota_a \maps a\to a+b$ and $\iota_b \maps b \to a+b$ are the coproduct inclusions in $\A$ and the coproduct in the second component is in the fiber $F(a+b)$. 
+\fi
 
@@
 \node (A) at (0,0) {$L(a)$};
-\node (B) at (1,0) {$(m,s)$};
-\node (C) at (2,0) {$L(a).$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$i$} (B)
-(C) edge node[above]{$o$} (B);
-\end{tikzpicture}
-\]
-Here $L(a)$ is the initial object in the fiber of $\X = \inta F$ over $a \in A$, namely $(a,t_a)$ 
-where $t_a \in F(a)$ is the trivial decoration
-\[    \one \xrightarrow{\phi_0} F(0_\A) \xrightarrow{F(!_a)} F(a). \]
+\node (B) at (1.5,0) {$(m,s)$};
+\node (C) at (3,0) {$L(a)$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$\utilde{i}$} (B)
+(C) edge node[above]{$\utilde{o}$} (B);
+\end{tikzpicture}
+\]
+where $L(a)$ is the initial object in the fiber of $\X = \inta F$ over $a \in A$, namely $(a,I_a)$ 
+where $I_a \in F(a)$ is the \define{trivial decoration} given in \cref{eq:explicitstructure1}, and
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (A) at (0,0) {$\one$};
+\node (B) at (1,0) {$F(0)$};
+\node (C) at (2.2,0.5) {$F(a)$};
+\node (C') at (2.2,-0.5) {$F(b)$};
+\node (D) at (1.8,0) {$\cong$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$\phi_0$} (B)
+(B) edge node[above]{$F(!_a)\;$} (C)
+(B) edge node[below]{$F(!_b)\;\;$} (C')
+(C) edge node[right]{$F(f)$} (C');
+\end{tikzpicture}
+\]
+{\john NOT DONE!!!}
+
    Finally, this isomorphism maps the map of decorated cospans
@@
 (B) edge node [left] {$h$} (D);
+\end{tikzpicture}
+\]
+to this map of structured cospans:
+\[
+\begin{tikzpicture}[scale=1.5,baseline=(current bounding box.center)]
+\node (A) at (0,0.5) {$L(a)$};
+\node (A') at (0,-0.5) {$L(a')$};
+\node (B) at (1,0.5) {$(m,s)$};
+\node (C) at (2,0.5) {$L(b)$};
+\node (C') at (2,-0.5) {$b'$.};
+\node (D) at (1,-0.5) {$(m',s')$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$\utilde{i}$} (B)
+(C) edge node[above]{$\utilde{o}$} (B)
+(A) edge node[left]{$L(f)$} (A')
+(C) edge node[right]{$L(g)$} (C')
+(A') edge node[below] {$\utilde{i}'$} (D)
+(C') edge node[below] {$\utilde{o}'$} (D)
+(B) edge node [left] {$(h,\tau)$} (D);
 \end{tikzpicture}
@@
 \begin{proof}
-{\john Here we are using $\bot_b$ to mean trivial decoration.  Sometimes we do this, and
-sometimes we use it to mean initial object in the fiber of $b$.  This leads to the strange
-result $\bot_b = (b,\bot_b)$.}  
 We show that any vertical 1-morphism $f \maps a \to b$ in $F\lCsp$ has a companion and a conjoint.  First, we can make this horizontal 1-cell $\hat{f}$:
@@
 \node (C) at (2,0) {$b$};
-\node (D) at (4,0) {$\bot_b \in F(b),$};
+\node (D) at (4,0) {$I_b \in F(b),$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-where $\bot_b$ is the trivial decoration given by
+where $I_b$ is the trivial decoration given by
 \[    \one \xrightarrow{\phi_0} F(0_\A) \xrightarrow{F(!_b)} F(b), \]
@@
 \node (D) at (1,-0.5) {$b$};
-\node (E) at (3,0.5) {$\bot_{b} \in F(b)$};
-\node (F) at (3,-0.5) {$\bot_{b} \in F(b)$};
+\node (E) at (3,0.5) {$I_b \in F(b)$};
+\node (F) at (3,-0.5) {$I_b \in F(b)$};
 \node (G) at (5,0.5) {$a$};
@@
 \node (I') at (7,-0.5) {$b$};
-\node (J) at (8,0.5) {$\bot_{a} \in F(a)$};
-\node (K) at (8,-0.5) {$\bot_{b} \in F(b)$};
-\node (L) at (1,-1) {$\tau_{1_{b}} = 1_{\bot_{b}}$};
-\node (M) at (6,-1) {$\tau_f \maps F(f)(\bot_a) \to \bot_{b}$};
+\node (J) at (8,0.5) {$I_a \in F(a)$};
+\node (K) at (8,-0.5) {$I_a \in F(b)$};
+\node (L) at (1,-1) {$\tau_{1_b} = 1_{I_b}$};
+\node (M) at (6,-1) {$\tau_f \maps F(f)(I_a) \to I_b$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \node (P) at (2,1.5) {$a$};
-\node (Q) at (-1,1.5) {$\bot_a \in F(a)$};
+\node (Q) at (-1,1.5) {$I_a \in F(a)$};
 \node (A) at (0,0.5) {$a$};
@@
 \node (D) at (1,-0.5) {$b$};
-\node (E) at (-1,0.5) {$\bot_{b} \in F(b)$};
-\node (F) at (-1,-0.5) {$\bot_{b} \in F(b)$};
+\node (E) at (-1,0.5) {$I_b \in F(b)$};
+\node (F) at (-1,-0.5) {$I_b \in F(b)$};
 \node (G) at (4,1) {$a$};
@@
 \node (I') at (6,0) {$b$};
-\node (J) at (7,1) {$\bot_{a} \in F(a)$};
-\node (K) at (7,0) {$\bot_{b} \in F(b)$};
-\node (Q) at (1,-1) {$\tau_f \maps F(f)(\bot_a) \to \bot_{b}$};
-\node (L) at (1,-1.5) {$\tau_{b} = 1_{\bot_{b}}$};
-\node (M) at (5,-0.5) {$\tau_f \maps F(f)(\bot_a) \to \bot_{b}$};
+\node (J) at (7,1) {$I_a \in F(a)$};
+\node (K) at (7,0) {$I_b \in F(b)$};
+\node (Q) at (1,-1) {$\tau_f \maps F(f)(I_a) \to I_b$};
+\node (L) at (1,-1.5) {$\tau_{b} = 1_{I_b}$};
+\node (M) at (5,-0.5) {$\tau_f \maps F(f)(I_a) \to I_b$};
 \node (R) at (3,0.5) {$=$};
@@
 \node (D) at (0.75,-0.5) {$b$};
-\node (E) at (0.75,1) {$\scriptstyle{\bot_{b} \in F(b)}$};
-\node (F) at (2,-0.5) {$\scriptstyle{\bot_{b} \in F(b)}$};
-\node (L) at (2,0) {$\scriptstyle{\tau_{b} = 1_{\bot_{b}}}$};
-\node (E') at (-0.75,1) {$\scriptstyle{\bot_{a} \in F(a)}$};
-\node (F') at (-2.25,-0.5) {$\scriptstyle{\bot_{b} \in F(b)}$};
-\node (L') at (-2.5,0) {$\scriptstyle{\tau_{f} \maps F(f)(\bot_a) \to \bot_{b}}$};
+\node (E) at (0.75,1) {$\scriptstyle{I_b \in F(b)}$};
+\node (F) at (2,-0.5) {$\scriptstyle{I_b \in F(b)}$};
+\node (L) at (2,0) {$\scriptstyle{\tau_{b} = 1_{I_b}}$};
+\node (E') at (-0.75,1) {$\scriptstyle{I_a \in F(a)}$};
+\node (F') at (-2.25,-0.5) {$\scriptstyle{I_b \in F(b)}$};
+\node (L') at (-2.5,0) {$\scriptstyle{\tau_{f} \maps F(f)(I_a) \to I_b}$};
 \node (M) at (2.5,-0.5) {$\scriptstyle{=}$};
@@
 \node (S) at (6,-1) {$b$};
-\node (T) at (5.25,0.5) {$\scriptstyle{\bot_{b} \in F(b)}$};
-\node (T') at (3.75,0.5) {$\scriptstyle{\bot_a \in F(a)}$};
-\node (U) at (4.5,-1.5) {$\scriptstyle{\bot_{b} \in F(b)}$};
-\node (V) at (4.5,-1.75) {$\scriptstyle{\tau_{\rho_{\hat{f}}} \maps (\bot_b \odot \bot_a) \to \bot_b}$};
+\node (T) at (5.25,0.5) {$\scriptstyle{I_b \in F(b)}$};
+\node (T') at (3.75,0.5) {$\scriptstyle{I_a \in F(a)}$};
+\node (U) at (4.5,-1.5) {$\scriptstyle{I_b \in F(b)}$};
+\node (V) at (4.5,-1.75) {$\scriptstyle{\tau_{\rho_{\hat{f}}} \maps (I_b \odot I_a) \to I_b}$};
 \node (K) at (-1.5,-1.5) {$a$};
@@
 \node (M') at (1.5,-1.5) {$b$};
-\node (N') at (0,-2) {$\scriptstyle{\bot_b \in F(b)}$};
-\node (O') at (0,-2.25) {$\scriptstyle{\tau_{\lambda_{\hat{f}}} \maps (\bot_b \odot \bot_b) \to \bot_b}$};
+\node (N') at (0,-2) {$\scriptstyle{I_b \in F(b)}$};
+\node (O') at (0,-2.25) {$\scriptstyle{\tau_{\lambda_{\hat{f}}} \maps (I_b \odot I_b) \to I_b}$};
 \node (W) at (3.75,0) {$a$};
@@
 \node (C) at (2,0) {$a$};
-\node (D) at (4,0) {$\bot_b \in F(b)$.};
+\node (D) at (4,0) {$I_b \in F(b)$.};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \label{theta}
-   k_! h^\ast \To k_! h^\ast g^\ast g_! = k_! k^\ast f^\ast g_! \To f^\ast g_! . 
+   k_! h^\ast \To k_! h^\ast g^\ast g_! \cong k_! k^\ast f^\ast g_! \To f^\ast g_! . 
 \end{equation}
-{\chris Shouldn't the middle equality be an isomorphism?}
 If $\theta$ is a natural isomorphism whenever the original square in $\A$ is
@@
 	\end{equation}
-  A \textbf{conjoint} of $f$, denoted $\fchk \maps B\to A$, is a
+  A \textbf{conjoint} of $f$, denoted $\fchk \maps B \to A$, is a
   companion of $f$ in the double category 

### 2021-06-23 cospans_new.tex
Fixed stuff at end of Section 4 - check it out!

@@
 Moreover, each fiber $\X_a=F(a)$ obtains a monoidal structure via 
-\begin{equation}\label{eq:explicitstructure1}
+\begin{equation} \label{eq:explicitstructure1}
 \otimes_a\maps F(a)\times F(a)\xrightarrow{\phi_{a,a}}F(a+a)\xrightarrow{F(\nabla)}F(a),\quad
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$L(a)$};
+\node (A) at (0,0) {$(a,I_a)$};
 \node (B) at (1.5,0) {$(m,s)$};
-\node (C) at (3,0) {$L(a)$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$\utilde{i}$} (B)
-(C) edge node[above]{$\utilde{o}$} (B);
-\end{tikzpicture}
-\]
-where $L(a)$ is the initial object in the fiber of $\X = \inta F$ over $a \in A$, namely $(a,I_a)$ 
-where $I_a \in F(a)$ is the \define{trivial decoration} given in \cref{eq:explicitstructure1}, and
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$\one$};
-\node (B) at (1,0) {$F(0)$};
-\node (C) at (2.2,0.5) {$F(a)$};
-\node (C') at (2.2,-0.5) {$F(b)$};
-\node (D) at (1.8,0) {$\cong$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$\phi_0$} (B)
-(B) edge node[above]{$F(!_a)\;$} (C)
-(B) edge node[below]{$F(!_b)\;\;$} (C')
-(C) edge node[right]{$F(f)$} (C');
-\end{tikzpicture}
-\]
-{\john NOT DONE!!!}
-
-   Finally, this isomorphism maps the map of decorated cospans
+\node (C) at (3,0) {$(b,I_b)$.};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$(i,!)$} (B)
+(C) edge node[above]{$(o,!)$} (B);
+\end{tikzpicture}
+\]
+Here $I_a \in F(a)$ is the \define{trivial decoration} given by the composite
+\[  \one\xrightarrow{\phi_0}F(0)\xrightarrow{F(!_a)}F(a), \]
+while $! \maps F(i)(I_a) \to s$ is the unique morphism with this domain and
+codomain (recall that $F(i)$ preserves initial objects), and similarly for
+$! \maps F(o)(I_b) \to s$.   Finally, this isomorphism sends the map of decorated cospans
 \[
@@
 \begin{tikzpicture}[scale=1.5,baseline=(current bounding box.center)]
-\node (A) at (0,0.5) {$L(a)$};
-\node (A') at (0,-0.5) {$L(a')$};
-\node (B) at (1,0.5) {$(m,s)$};
-\node (C) at (2,0.5) {$L(b)$};
-\node (C') at (2,-0.5) {$b'$.};
-\node (D) at (1,-0.5) {$(m',s')$};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$\utilde{i}$} (B)
-(C) edge node[above]{$\utilde{o}$} (B)
+\node (A) at (0,0.5) {$(a,I_a)$};
+\node (A') at (0,-0.5) {$(a',I_{a'}$};
+\node (B) at (1.5,0.5) {$(m,s)$};
+\node (C) at (3,0.5) {$(b,I_b)$};
+\node (C') at (3,-0.5) {$(b',I_{b'}$.};
+\node (D) at (1.5,-0.5) {$(m',s')$};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$(i,!)$} (B)
+(C) edge node[above]{$(o,!)$} (B)
 (A) edge node[left]{$L(f)$} (A')
 (C) edge node[right]{$L(g)$} (C')
-(A') edge node[below] {$\utilde{i}'$} (D)
-(C') edge node[below] {$\utilde{o}'$} (D)
+(A') edge node[below] {$(i',!)$} (D)
+(C') edge node[below] {$(o',!)$} (D)
 (B) edge node [left] {$(h,\tau)$} (D);
@@
 \node (Q) at (1,-1) {$\tau_f \maps F(f)(I_a) \to I_b$};
-\node (L) at (1,-1.5) {$\tau_{b} = 1_{I_b}$};
+\node (L) at (1,-1.5) {$\tau_{1_b} = 1_{I_b}$};
 \node (M) at (5,-0.5) {$\tau_f \maps F(f)(I_a) \to I_b$};

### 2021-06-23 cospans_new.tex
Fixed stuff at end of Section 4, after proof of Thm. 4.1.  Check it out!
tried to fix all the mistakes Kenny caught in his email of today, e.g. lots of x's

@@
 
-In \cref{DecCospansDoubleCat}, we construct the symmetric monoidal double category $F\lCsp$ and we define maps between decorated cospan double categories.
-In \cref{EquivDoubleCats}, we briefly review the structured cospans framework and prove that the double categorical versions of decorated cospans and structured cospans are isomorphic under suitable conditions.
-{\chris Section 3 is missing!} In \cref{spinoffs}, we establish the isomorphism between structured and decorated cospans at the level of bicategories and categories (via decategorification).
-Finally, in \cref{Applications}, we describe applications, and show that open dynamical system can be described using decorated cospans but not structured cospans.
+In \cref{DecCospansDoubleCat} we construct the double category of decorated cospans, $F\lCsp$, and show how to construct maps between decorated cospan double categories.
+In \cref{Structured} we give a new construction of the double category of structured cospans, ${}_L \lCsp(\X)$.
+In \cref{EquivDoubleCats} we prove that the double categories of decorated cospans and structured cospans are isomorphic under suitable conditions.
+In \cref{spinoffs} we establish the isomorphism between structured and decorated cospans at the level of bicategories and categories (via decategorification).
+In \cref{Applications} we describe applications, and show that open dynamical system can be described using decorated cospans but not structured cospans.
 
@@
 We thank Daniel Cicala, Brendan Fong and Joe Moeller for helpful conversations.
-We especially thank Michael Shulman for suggesting a better proof strategy.
+We especially thank Michael Shulman for suggesting a better proof strategy that greatly improved this paper.
 The third author would like to thank the General Secretariat for Research  and Technology (GSRT) and the Hellenic Foundation for Research and Innovation (HFRI).
@@
 \]
-together with a \define{decoration morphism} $\tau \maps F(h)(s) \to s'$ in $F(s')$.
+together with a \define{decoration morphism} $\tau \maps F(h)(s) \to s'$ in $F(m')$.
 \end{itemize}
@@
 \end{itemize}
-As in any comma category we have a functor $\Phi \maps \A/U \to \A$ given on objects by $\Phi(a \xrightarrow{i} b, x)=a$ and on morphisms by $\Phi(f,g,h)=f$.
+As in any comma category we have a functor $\Phi \maps \A/U \to \A$ given on objects by $\Phi(a \xrightarrow{i} b, s)=a$ and on morphisms by $\Phi(f,g,h)=f$.
 
@@
 Namely, we have $\theta = (1, \zeta, 1)$.   But when the original square in $\A$ (at upper left 
-above) is a pushout, its pasting with the other pushout gives a pushout, so $\zeta$ and hence $\theta$ is isomorphism.
+above) is a pushout, its pasting with the other pushout gives a pushout, so $\zeta$ and hence $\theta$ is an isomorphism.
 
@@
 \path[->,font=\scriptsize,>=angle 90]
-(G) edge node [above] {$x$} (H)
-(G) edge node [below] {$x'$} (I)
+(G) edge node [above] {$s$} (H)
+(G) edge node [below] {$s'$} (I)
 (H) edge node [right] {$F(h)$} (I);
@@
 (E) edge node [right] {$F'(H(h))$} (F)
-(L) edge node[above]{$E(x)$} (B)
-(L) edge node[below]{$E(x')$} (D)
+(L) edge node[above]{$E(s)$} (B)
+(L) edge node[below]{$E(s')$} (D)
 (B) edge node[right]{$E(F((h))$} (D);
@@
 where to define $\underline{x}$ we treat $s \in F(b)$ as a functor 
-$x \maps 1 \to F(b)$ and let $\underline{s} \in F'(H(b))$ be the composite functor
+$s \maps 1 \to F(b)$ and let $\underline{s} \in F'(H(b))$ be the composite functor
 \[  1 \xrightarrow{\phi_0} E(1) \xrightarrow{E(x)} E(F(b)) \xrightarrow{\;\theta_b\;} F'(H(b)) .\]
@@
 \path[->,font=\scriptsize,>=angle 90]
-(G) edge node [above] {$x$} (H)
-(G) edge node [below] {$x'$} (I)
+(G) edge node [above] {$s$} (H)
+(G) edge node [below] {$s'$} (I)
 (H) edge node [right] {$F(g)$} (I);
@@
 (E) edge node [right] {$F'(H(h))$} (F)
-(L) edge node[above]{$E(x)$} (B)
-(L) edge node[below]{$E(x')$} (D)
+(L) edge node[above]{$E(s)$} (B)
+(L) edge node[below]{$E(s')$} (D)
 (B) edge node[right]{$E(F(h))$} (D);
@@
 One can show that this laxator and unit morphism satisfy the coherence laws of a lax monoidal functor, and they are invertible, so $G$ is strong monoidal functor.
-\john{If furthermore $F, F'$ and $E$ are symmetric, one can check that $G$ is symmetric monoidal, and that $\lH$ is a symmetric monoidal double functor.}
+If furthermore $F, F'$ and $E$ are symmetric, one can check that $G$ is symmetric monoidal, and that $\lH$ is a symmetric monoidal double functor.
 \end{proof}
@@
 Given a morphism $f\maps a\to a'$ in $\A$, define $L(f)$ to be the composite
- \begin{equation}\label{eq:Lonarrows}
+\[
   \bot_a\xrightarrow{\mathrm{Cocart}(f,\bot_a)}f_!(\bot_a)\xrightarrow{\;\chi_a\;}\bot_{a'}
- \end{equation}
+\]
 where $\mathrm{Cocart}(f,\bot_a)$ is the cocartesian lifting of $f$ to $\bot_a$ and $\chi_a$ is the unique isomorphism between two initial objects in the fiber above $a'$.
@@
 codomain (recall that $F(i)$ preserves initial objects), and similarly for
-$! \maps F(o)(I_b) \to s$.   Finally, this isomorphism sends the map of decorated cospans
+$! \maps F(o)(I_b) \to s$.   Finally, this isomorphism sends the map of decorated cospans:
 \[
@@
 \node (A) at (0,0.5) {$(a,I_a)$};
-\node (A') at (0,-0.5) {$(a',I_{a'}$};
+\node (A') at (0,-0.5) {$(a',I_{a'})$};
 \node (B) at (1.5,0.5) {$(m,s)$};
 \node (C) at (3,0.5) {$(b,I_b)$};
-\node (C') at (3,-0.5) {$(b',I_{b'}$.};
+\node (C') at (3,-0.5) {$(b',I_{b'})$.};
 \node (D) at (1.5,-0.5) {$(m',s')$};

### 2021-06-24 cospans_new.tex
edits

@@
 
-\usepackage{amssymb,amsmath,stmaryrd,txfonts,mathrsfs,amsthm,undertilde}
+\usepackage{amssymb,amsmath,stmaryrd,txfonts,mathrsfs,amsthm}%,undertilde}
 \usepackage{comment}
@@
 In \cref{spinoffs} we establish the isomorphism between structured and decorated cospans at the level of bicategories and categories (via decategorification).
-In \cref{Applications} we describe applications, and show that open dynamical system can be described using decorated cospans but not structured cospans.
+In \cref{Applications} we describe applications, and show that open dynamical systems can be described using decorated cospans but not structured cospans.
 
@@
 where $\nabla$ is the fold map, which is symmetric when $F$ is, again via the components of $u_{a,a}$. Also, each reindexing functor $f_!=F(f)$ obtains a strong monoidal structure with
-\begin{equation}\label{eq:strongreindexing}
+\begin{displaymath}%\label{eq:strongreindexing}
 \begin{tikzcd}[row sep=.35in]
@@
 \end{tikzcd}
-\end{equation}
+\end{displaymath}
 \end{proof}
+
+{\chris There was a paragraph here (under (21) in old version) which I think is used in what follows, since that is the version of the theorem we actually use, the cocartesian total category one!}
 
@@
 \]
+{\chris I believe these should now be $\bot_a$ rather than $I_a$ although under these conditions those things are isomorphic I think!
+Since $F$ factors through Rex, each fibre has an initial object $\bot_a$ which can now be used.}
+
 Here $I_a \in F(a)$ is the \define{trivial decoration} given by the composite
@@
 \begin{lem}
-The double category $F\lCsp$ is fibrant.
+{\chris For $(F,\phi,\phi_0)\colon(A,+)\to(\Cat,\times)$ a lax monoidal pseudofunctor, t}he double category $F\lCsp$ is fibrant.
 \end{lem}
@@
 \]
-where the decoration morphism $\tau_f$ is the isomorphism given by the pseudofunctoriality of $F$:
+where the decoration morphism $\tau_f$ is the isomorphism given by pseudofunctoriality of $F$:
 \[
@@
 \end{equation}
-\begin{equation}\label{eq:unitality}
+\begin{displaymath}%\label{eq:unitality}
 \begin{tikzcd}[column sep=.3in,row sep=.3in]
@@
 \end{tikzcd}
-\end{equation}
+\end{displaymath}
 subject to coherence conditions listed in \cite[Definition 2]{DS}.
@@
 The unit is $(1_a\maps a\to a,F(1_a)(x)\cong x)$ and composition of $(f,k)\maps(a,x)\to(b,y)$ and $(g,\ell)\maps(b,y)\to(c,z)$ is
-\begin{equation}\label{eq:compGrothcat}
+\begin{displaymath}%\label{eq:compGrothcat}
 \left(a\xrightarrow{f}b\xrightarrow{g}c, F(g\circ f)x\cong Fg(Ff(x))\xrightarrow{Fg(k)}Fg(y)\xrightarrow{\ell}z\right) 
-\end{equation}
+\end{displaymath}
 This is an opfibered category over $\A$ via the obvious forgetful functor, with fibers $(\inta F)_a=F(a)$ and reindexing functors $f_!=F(f)$.
@@
 		\item The following diagrams commute, expressing that the braiding is a transformation of double categories:
-		\begin{equation}
-		\begin{tikzpicture}\label{eq:braidingaxiom}
+		\begin{displaymath}
+		\begin{tikzpicture}%\label{eq:braidingaxiom}
 			\node (A) at (0,1.5) {\footnotesize{$ (M_2\otimes N_2)\odot (M_1\otimes N_1)$}};
@@
 		\end{tikzpicture}
-		\end{equation}
+		\end{displaymath}
 \end{itemize}
@@
 \item{the following diagrams commute, expressing that $\phi$ is a transformation of double categories:
-		\begin{equation}
+		\begin{displaymath}
 		\begin{tikzpicture}
@@
 		\end{tikzpicture}
-		\end{equation}
+		\end{displaymath}
 }

### 2021-06-25 cospans_new.tex
small changes
small updates

@@
 \begin{lem}
-{\chris For $(F,\phi,\phi_0)\colon(A,+)\to(\Cat,\times)$ a lax monoidal pseudofunctor, t}he double category $F\lCsp$ is fibrant.
+{\chris For $(F,\phi,\phi_0)\colon(\A,+)\to(\Cat,\times)$ a lax monoidal pseudofunctor, t}he double category $F\lCsp$ \textcolor{blue}{Kenny: of \cref{thm:decorated_cospans_1}}  is fibrant.
 \end{lem}

### 2021-06-25 cospans_new.tex
edited material after Theorem 4.1 - check it out!

@@
 
-Given the hypothesis of \cref{thm:equiv}, the isomorphism from $F\lCsp$ to ${}_L\lCsp(\inta F)$ works as follows.   It is the identity on objects and vertical morphisms, 
-which are just objects and morphisms of $\A$.   It maps the decorated cospan
+Given the hypothesis of \cref{thm:equiv}, the isomorphism $\Fr(F)$ between decorated and 
+structured cospans works as follows.
+First recall that $\X = \inta F$, so that an object of $\X$ is a pair $(a,s)$ with $a \in \A$ and $s \in F(a)$.
+The functor $U \maps \X \to \A$ maps $(a,s)$ to $a$.
+Its left adjoint $L \maps \A \to \X$ maps $a \in \A$ to $(a,I_a)$, where $I_a \in F(a)$ is the \define{trivial decoration} given by the composite
+\[  \one\xrightarrow{\phi_0}F(0)\xrightarrow{F(!_a)}F(a). \]
+The object $L(a) = (a,I_a)$ is the initial object in the fiber of $\inta F$ over $a$.
+
+The isomorphism $\Fr(F) \maps F\lCsp \to {}_L\lCsp(\inta F)$  is the identity on objects and vertical morphisms, which are just objects and morphisms of $\A$.   It maps the decorated cospan
 \[
@@
 \]
-{\chris I believe these should now be $\bot_a$ rather than $I_a$ although under these conditions those things are isomorphic I think!
-Since $F$ factors through Rex, each fibre has an initial object $\bot_a$ which can now be used.}
-
-Here $I_a \in F(a)$ is the \define{trivial decoration} given by the composite
-\[  \one\xrightarrow{\phi_0}F(0)\xrightarrow{F(!_a)}F(a), \]
-while $! \maps F(i)(I_a) \to s$ is the unique morphism with this domain and
+where $! \maps F(i)(I_a) \to s$ is the unique morphism with this domain and
 codomain (recall that $F(i)$ preserves initial objects), and similarly for
-$! \maps F(o)(I_b) \to s$.   Finally, this isomorphism sends the map of decorated cospans:
+$! \maps F(o)(I_b) \to s$.   Finally, $\Fr(\Phi)$ sends a map of decorated cospans:
 \[

### 2021-06-25 cospans_new.tex
Changed statement of Lemma 5.1

@@
 \begin{lem}
-{\chris For $(F,\phi,\phi_0)\colon(\A,+)\to(\Cat,\times)$ a lax monoidal pseudofunctor, t}he double category $F\lCsp$ \textcolor{blue}{Kenny: of \cref{thm:decorated_cospans_1}}  is fibrant.
+Given a category $\A$ with finite colimits and a lax monoidal pseudofunctor $(F,\phi,\phi_0) \maps (\A,+)\to(\Cat,\times)$, the double category $F\lCsp$ is fibrant.
 \end{lem}

### 2021-06-28 cospans_new.tex
I put the mistakenly deleted paragraph after Lemma 2.4 back in.

@@
 
-{\chris There was a paragraph here (under (21) in old version) which I think is used in what follows, since that is the version of the theorem we actually use, the cocartesian total category one!}
+These 2-equivalences further restrict to the case when the Grothendieck category $(X,\otimes_\X)$ is specifically cocartesian monoidal itself, with coproducts built up from \cref{eq:explicitstructure2}.
+In that case, opfibrations $(\X,+) \to (\A,+)$ that strictly preserve coproducts and initial object bijectively correspond to pseudofunctors into the 2-category of cocartesian categories.
+For more details, see \cite[Corollary 4.7]{MV} and the related discussion.
 

### 2021-06-28 cospans_new.tex
removed "better" from Acknowledgements
fixed the stuff about I_a in paragraph 2 of proof of Thm. 4.1

@@
 We thank Daniel Cicala, Brendan Fong and Joe Moeller for helpful conversations.
-We especially thank Michael Shulman for suggesting a better proof strategy that greatly improved this paper.
+We especially thank Michael Shulman for suggesting a proof strategy that greatly improved this paper.
 The third author would like to thank the General Secretariat for Research  and Technology (GSRT) and the Hellenic Foundation for Research and Innovation (HFRI).
@@
 describes the construction of the adjunction from the original $F$.
-Explicitly, the left adjoint maps each object $a \in \A$ to the initial object in its fiber $\X_a$, namely $L(a)=(a,\bot_a)$, which is expressed as $F(!_a)\circ\phi_0(*)$ according to \cref{eq:explicitstructure1}, where $(\phi,\phi_0)$ the lax monoidal structure of $F$.
+Explicitly, the left adjoint maps each object $a \in \A$ to the initial object in its fiber $\X_a$, namely $L(a)=(a,I_a)$, where $I_a$ is defined as in \cref{eq:explicitstructure1}.
 
@@
 Given the hypothesis of \cref{thm:equiv}, the isomorphism $\Fr(F)$ between decorated and 
-structured cospans works as follows.
+structured cospans works concretely as follows.
 First recall that $\X = \inta F$, so that an object of $\X$ is a pair $(a,s)$ with $a \in \A$ and $s \in F(a)$.

### 2021-06-29 cospans_new.tex
attempted to deal with all of Kenny's June 28 corrections

@@
 % in LaTeX
-% 2021/6/23 - Finishing up
+% 2021/6/28 - Finishing up
 
@@
 This led Fong to develop a theory of `decorated' cospans \cite{Fong}.
-Given a category $\A$ with finite colimits, a symmetric lax monoidal functor $F \maps (\A,+) \to (\textsf{Set},\times)$ can be used to equip the apex $m$ of a cospan in $\A$ with some extra data: an element $x \in F(m)$, which we call a \textbf{decoration}.
+Given a category $\A$ with finite colimits, a symmetric lax monoidal functor $F \maps (\A,+) \to (\textsf{Set},\times)$ can be used to equip the apex $m$ of a cospan in $\A$ with some extra data: an element $s \in F(m)$, which we call a \textbf{decoration}.
 Thus a \define{decorated cospan} is a pair:
@@
 \node (C) at (2,0) {$b$,};
-\node (E) at (4,0) {$x \in F(m)$.};
+\node (E) at (4,0) {$s \in F(m)$.};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \node (C) at (2,0) {$b,$};
-\node (D) at (3,0) {$x \in F(m)$,};
+\node (D) at (3,0) {$s \in F(m)$,};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-together with a morphism $\tau \maps F(h)(x) \to x'$ in $F(m')$.
+together with a morphism $\tau \maps F(h)(s) \to s'$ in $F(m')$.
 \end{itemize}
@@
 In this section we build symmetric monoidal double categories of decorated cospans, and then study the functoriality of this construction.
-\cref{thm:decorated_cospans_1} explains how to construct a double category of decorated cospans from a lax monoidal pseudofunctor $F \maps (\A,+) \to (\Cat, \times)$ whenever $A$ has finite colimits.
+\cref{thm:decorated_cospans_1} explains how to construct a double category of decorated cospans from a lax monoidal pseudofunctor $F \maps (\A,+) \to (\Cat, \times)$ whenever $\A$ has finite colimits.
 \cref{thm:decorated_cospans_2} gives conditions under which this double category is symmetric monoidal.
@@
 \item a 2-morphism is a pair of morphisms $f \maps a \to a'$, $g \maps b \to b'$ 
-in $\A$ together with a morphism $h \maps c \to c'$ with $\Phi(h) = f + g$.
+in $\A$ together with a morphism $h \maps c \to c'$ in $\C$ with $\Phi(h) = f + g$.
 \end{itemize}
@@
 
-\begin{proof} This is \cite[Theorem 14.9]{Shulman2008}; Shulman proves the dual version in more detail in his Theorem 14.4.  
+\begin{proof} This is \cite[Theorem 14.9]{Shulman2008}; Shulman proves a dual version in more detail in his Theorem 14.4.  
 \end{proof}
@@
 \[  G(a \xrightarrow{i} b, s) \; = \; (H(a) \xrightarrow{H(i)} H(b), \underline{s}), \]
-where to define $\underline{x}$ we treat $s \in F(b)$ as a functor 
+where to define $\underline{s}$ we treat $s \in F(b)$ as a functor 
 $s \maps 1 \to F(b)$ and let $\underline{s} \in F'(H(b))$ be the composite functor
-\[  1 \xrightarrow{\phi_0} E(1) \xrightarrow{E(x)} E(F(b)) \xrightarrow{\;\theta_b\;} F'(H(b)) .\]
+\[  1 \xrightarrow{\phi_0} E(1) \xrightarrow{E(s)} E(F(b)) \xrightarrow{\;\theta_b\;} F'(H(b)) .\]
 On morphisms $(f,g,h) \maps (a \xrightarrow{i} b, s) \; \to \; 
@@
 \node (I) at (-2,-1) {$F(b')$};
-\node (J) at (-2.5,-0.5) {$\scriptstyle\Downarrow\tau$};
+\node (J) at (-2.5,-0.5) {$\scriptstyle\Downarrow h$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \node (D) at (2,-1) {$E(F(b'))$};
-\node (C) at (1.5,-0.5) {$\scriptstyle\Downarrow E(\tau)$};
+\node (C) at (1.5,-0.5) {$\scriptstyle\Downarrow E(h)$};
 \node (E) at (4,0) {$F^\prime(H(b))$};
@@
 (D) edge node [above] {$\theta_{b'}$} (F)
-(E) edge node [right] {$F'(H(h))$} (F)
+(E) edge node [right] {$F'(H(g))$} (F)
 (L) edge node[above]{$E(s)$} (B)
 (L) edge node[below]{$E(s')$} (D)
-(B) edge node[right]{$E(F(h))$} (D);
+(B) edge node[right]{$E(F(g))$} (D);
 \end{tikzpicture}
@@
 
-The comma category $L/\X$ has finite colimits because $A$ and $X$ have finite colimits and $L$ 
+The comma category $L/\X$ has finite colimits because $\A$ and $\X$ have finite colimits and $L$ 
 preserves them.
@@
 \[  (a,L(a) \xrightarrow{i} x) + (a',L(a') \xrightarrow{i'} x')=(a+a',L(a+a')  \xrightarrow{\sim} L(a)+L(a') \xrightarrow{i+i'} x+x'). \]
-The monoidal unit is ${(0_\A,0_\X,{L(0_\A) \xrightarrow{!} 0_\X})}$.  It is clear that $\Psi \maps (L/\X, +) \to (\A,+)$ is a strict monoidal functor.
+The monoidal unit is $(0_\A, L(0_\A) \xrightarrow{!} 0_\X)$.  It is clear that $\Psi \maps (L/\X, +) \to (\A,+)$ is a strict monoidal functor.
 
@@
 Namely, the $\mathbb{F}\mathbf{r}$ construction of \cref{lem:shulman} extends to a 2-functor
-\[ \mathbb{F}\mathbf{r} \maps \mathbf{FMF} \to \mathbf{FDbl} \]
-where $\mathbf{FMF}$ is the 2-category consisting of
+\[ \mathbb{F}\mathbf{r} \maps \mathbf{BCMF} \to \mathbf{FDbl} \]
+where $\mathbf{BCMF}$ is the 2-category consisting of
 \begin{itemize}
@@
 \end{itemize}
-Given two monoidal bifibrations $\Phi \maps \A \to \mathsf{B}$ and $\Phi' \maps \A' \to \mathsf{B}'$, a `strong monoidal morphism of bifibrations' from $\Phi$ to $\Phi'$ consists of a pair of strong monoidal functors $F_1$ and $F_2$ making the following square commutes
+Given two monoidal bifibrations $\Phi \maps \A \to \mathsf{B}$ and $\Phi' \maps \A' \to \mathsf{B}'$, a `strong monoidal morphism of bifibrations' from $\Phi$ to $\Phi'$ consists of a pair of strong monoidal functors $F_1$ and $F_2$ making the following square commute
 \[
@@
 \node (J) at (8,0.5) {$I_a \in F(a)$};
-\node (K) at (8,-0.5) {$I_a \in F(b)$};
+\node (K) at (8,-0.5) {$I_b \in F(b)$};
 \node (L) at (1,-1) {$\tau_{1_b} = 1_{I_b}$};
@@
 Thinking about systems and processes categorically dates back to early works by Lawvere \cite{Lawvere}, Bunge--Fiore \cite{BungeFiore}, Joyal--Nielsen--Winskel \cite{JNW}, Katis--Sabadini--Walters \cite{KSW} and others.
-Spivak and others have used wiring diagrams and sheaves to capture compositional features of dynamical systems, \cite{BFV,SSV,VSL}.
+Spivak and others have used wiring diagrams and sheaves to capture compositional features of dynamical systems \cite{BFV,SSV,VSL}.
 Another approach uses signal flow diagrams and other string diagrams \cite{BE,BSZ,FRS} to understand systems behaviorally, following ideas of Willems \cite{Willems}.
@@
 (A) edge node[above]{$s$} (B)
-(A') edge node[above]{$s'$} (B')
+(A') edge node[below]{$s'$} (B')
 (A) edge node[left]{$f$} (A')
@@
 (C) edge node[above]{$t$} (D)
-(C') edge node[above]{$t'$} (D')
+(C') edge node[below]{$t'$} (D')
 (C) edge node[left]{$f$} (C')
@@
 
-We can easily build a double category with `open graphs' as horizontal 1-cells using the machinery of structured cospans, see \cite[Section 5]{BC}.
+We can easily build a double category with `open graphs' as horizontal 1-cells using the machinery of structured cospans \cite[Section 5]{BC}.
 Let $L \maps \Fin\Set \to \Graph$ be the functor that assigns to a finite set $N$ the \define{discrete graph} on $N$: the graph with no edges and $N$ as its set of vertices.
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$L(X_1)$};
-\node (B) at (1,0) {$G_1$};
-\node (C) at (2,0) {$L(Y_1)$};
-\node (A') at (0,-1) {$L(X_2)$};
-\node (B') at (1,-1) {$G_2$};
-\node (C') at (2,-1) {$L(Y_2)$.};
-\path[->,font=\scriptsize,>=angle 90]
-(A) edge node[above]{$I_1$} (B)
-(C) edge node[above]{$O_1$} (B)
-(A') edge node[above]{$I_2$} (B')
-(C') edge node[above]{$O_2$} (B')
+\node (A) at (0,0) {$L(X)$};
+\node (B) at (1,0) {$G$};
+\node (C) at (2,0) {$L(Y)$};
+\node (A') at (0,-1) {$L(X')$};
+\node (B') at (1,-1) {$G'$};
+\node (C') at (2,-1) {$L(Y')$.};
+\path[->,font=\scriptsize,>=angle 90]
+(A) edge node[above]{$i$} (B)
+(C) edge node[above]{$o$} (B)
+(A') edge node[below]{$i'$} (B')
+(C') edge node[below]{$o'$} (B')
 (A) edge node [left]{$L(f)$} (A')
 (B) edge node [left]{$\alpha$} (B')
-(C) edge node [left]{$L(g)$} (C');
+(C) edge node [right]{$L(g)$} (C');
 \end{tikzpicture}
@@
 \begin{itemize}
-\item objects are sets,
+\item objects are finite sets,
 \item a vertical 1-morphism from $X$ to $X'$ is a function $f \maps X \to X'$,
@@
 (C) edge node[right]{$g$} (C')
-(C') edge node [above] {$o'$} (D)
-(A') edge node [above] {$i'$} (D)
+(C') edge node [below] {$o'$} (D)
+(A') edge node [below] {$i'$} (D)
 (B) edge node [left] {$h$} (D);
@@
 
-A \define{Petri net} is a pair of sets $S$ and $T$ and functions $s,t \maps T \to \N[S]$.
+A \define{Petri net} is a pair of finite sets $S$ and $T$ and functions $s,t \maps T \to \N[S]$.
 Here $S$ is the set of \define{places}, $T$ is the set of \define{transitions}, and $\N[S]$ is the underlying set of the free commutative monoid on $S$.
@@
 		T \ar[d]_f  \ar[r]^-{s} & \N[S] \ar[d]^-{\N[g]} \\	
-		T' \ar[r]^-{s'} & \N[S'] 
+		T' \ar[r]_-{s'} & \N[S'] 
 	}
@@
 		T \ar[d]_f  \ar[r]^-{t} & \N[S] \ar[d]^-{\N[g]} \\	
-		T' \ar[r]^-{t'} & \N[S'] . 
+		T' \ar[r]_-{t'} & \N[S'] . 
 	}
 	\]
-There is a functor $R \maps \Petri \to \Set$ sending any Petri net to its set of places, and this has a left adjoint $L \maps \Set \to \Petri$ sending any set $S$ to the Petri net with $S$ as its set of places and no transitions \cite[Lemma 11]{BM}.
-Since both $\Set$ and $\Petri$ have finite colimits and $L$ preserves them, \cref{thm:structured_cospans} yields a symmetric monoidal double category ${}_L \lCsp(\Petri)$ in which:
+There is a functor $R \maps \Petri \to \Fin\Set$ sending any Petri net to its set of places, and this has a left adjoint $L \maps \Fin\Set \to \Petri$ sending any finite set $S$ to the Petri net with $S$ as its set of places and no transitions \cite[Lemma 11]{BM}.
+Since both $\Fin\Set$ and $\Petri$ have finite colimits and $L$ preserves them, \cref{thm:structured_cospans} yields a symmetric monoidal double category ${}_L \lCsp(\Petri)$ in which:
 \begin{itemize}
@@
 \begin{tikzpicture}[scale=1.5]
-\node (E) at (3,0) {$L(X_1)$};
-\node (F) at (5,0) {$L(Y_1)$};
-\node (G) at (4,0) {$P_1$};
-\node (E') at (3,-1) {$L(X_2)$};
-\node (F') at (5,-1) {$L(Y_2)$.};
-\node (G') at (4,-1) {$P_2$};
-\path[->,font=\scriptsize,>=angle 90]
-(F) edge node[above]{$O_1$} (G)
+\node (E) at (3,0) {$L(X)$};
+\node (F) at (5,0) {$L(Y)$};
+\node (G) at (4,0) {$P$};
+\node (E') at (3,-1) {$L(X')$};
+\node (F') at (5,-1) {$L(Y')$.};
+\node (G') at (4,-1) {$P'$};
+\path[->,font=\scriptsize,>=angle 90]
+(F) edge node[above]{$o$} (G)
 (E) edge node[left]{$L(f)$} (E')
@@
 (G) edge node[left]{$\alpha$} (G')
-(E) edge node[above]{$I_1$} (G)
-(E') edge node[above]{$I_2$} (G')
-(F') edge node[above]{$O_2$} (G');
+(E) edge node[above]{$i$} (G)
+(E') edge node[below]{$i'$} (G')
+(F') edge node[below]{$o'$} (G');
 \end{tikzpicture}
@@
 \begin{tikzpicture}[scale=1.5]
-\node (E) at (3,0) {$L(X_1)$};
-\node (F) at (5,0) {$L(Y_1)$};
-\node (G) at (4,0) {$P_1$};
-\node (E') at (3,-1) {$L(X_2)$};
-\node (F') at (5,-1) {$L(Y_2)$.};
-\node (G') at (4,-1) {$P_2$};
-\path[->,font=\scriptsize,>=angle 90]
-(F) edge node[above]{$O_1$} (G)
+\node (E) at (3,0) {$L(X)$};
+\node (F) at (5,0) {$L(Y)$};
+\node (G) at (4,0) {$P$};
+\node (E') at (3,-1) {$L(X')$};
+\node (F') at (5,-1) {$L(Y')$.};
+\node (G') at (4,-1) {$P'$};
+\path[->,font=\scriptsize,>=angle 90]
+(F) edge node[above]{$i$} (G)
 (E) edge node[left]{$L(f)$} (E')
@@
 (G) edge node[left]{$\alpha$} (G')
-(E) edge node[above]{$I_1$} (G)
-(E') edge node[above]{$I_2$} (G')
-(F') edge node[above]{$O_2$} (G');
+(E) edge node[above]{$o$} (G)
+(E') edge node[below]{$i'$} (G')
+(F') edge node[below]{$o'$} (G');
 \end{tikzpicture}
@@
 (E) edge node[above]{$i$} (G)
-(E') edge node[above]{$i'$} (G')
-(F') edge node[above]{$o'$} (G');
+(E') edge node[below]{$i'$} (G')
+(F') edge node[below]{$o'$} (G');
 \end{tikzpicture}
@@
 \node (A) at (0,0) {$\Fin\Set$};
-\node (B) at (1,0) {$\Cat$};
+\node (B) at (1.5,0) {$\Cat$};
 \node (C) at (0,-1) {$\Fin\Set$};
-\node (D) at (1,-1) {$\Cat$.};
-\node (E) at (0.5,-0.5) {$\Downarrow \theta$};
+\node (D) at (1.5,-1) {$\Cat$.};
+\node (E) at (0.75,-0.5) {$\Downarrow \theta$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 (B) edge node[right]{$1$} (D)
-(C) edge node[above]{$D$} (D);
+(C) edge node[below]{$D$} (D);
 \end{tikzpicture}
@@
 \[     \frac{d}{dt} c(t) = v(c(t))  + i_*(I(t)) - o_*(O(t)) \]
-where $I \maps \R \to \R^X$ and $O \maps \R \to \R^X$ are arbitrary smooth functions describing \define{inflows} and \define{outflows}, respectively.
+where $I \maps \R \to \R^X$ and $O \maps \R \to \R^Y$ are arbitrary smooth functions describing \define{inflows} and \define{outflows}, respectively.
 Applying this prescription to the open Petri net with rates shown at the start of this section one gets the differential equations \cref{eq:openPetrir}.
@@
 \item an object is a pair $(S,v)$ where $S$ is a finite set and $v$ is an algebraic vector field $v \maps \R^S \to \R^S$,
-\item a morphism from $(S,v)$ to $(S',v')$ is a function $f \maps S \to S'$ such that $v' = f_* \circ v \circ f^*$.
+\item a morphism from $(S,v)$ to $(S',v')$ is a function $f \maps S \to S'$ such that $v' = f_* \circ v \circ f^*$
 \end{itemize}

### 2021-06-29 cospans_new.tex
moved a bunch of arrow labels in proof of Lemma 5.1

@@
 (A) edge node[left]{$f$} (A')
-(C) edge node[left]{$1$} (C')
-(A') edge node[above] {$1$} (D)
-(C') edge node[above] {$1$} (D)
+(C) edge node[right]{$1$} (C')
+(A') edge node[below] {$1$} (D)
+(C') edge node[below] {$1$} (D)
 (B) edge node [left] {$1$} (D)
@@
 (H) edge node [left] {$f$} (H')
-(G') edge node [above] {$f$} (H')
+(G') edge node [below] {$f$} (H')
 (I) edge node [above] {$1$} (H)
-(I) edge node [left] {$f$} (I')
-(I') edge node [above] {$1$} (H');
+(I) edge node [right] {$f$} (I')
+(I') edge node [below] {$1$} (H');
 \end{tikzpicture}
@@
 (O) edge node[left]{$f$} (B)
-(P) edge node[left]{$f$} (C)
+(P) edge node[right]{$f$} (C)
 (A) edge node[above]{$f$} (B)
@@
 (H) edge node [left] {$f$} (H')
-(G') edge node [above] {$1$} (H')
+(G') edge node [below] {$1$} (H')
 (I) edge node [above] {$1$} (H)
-(I) edge node [left] {$f$} (I')
-(I') edge node [above] {$1$} (H');
-\end{tikzpicture}
-\]
+(I) edge node [right] {$f$} (I')
+(I') edge node [below] {$1$} (H');
+\end{tikzpicture}
+\]
+
 \[
@@
 (Y) edge node [above] {$1$} (W)
-(Z) edge node [above] {$f$} (O)
+(Z) edge node [below] {$f$} (O)
 (N) edge node [above] {$1$} (W)
@@
 (A') edge node [left] {$1$} (L')
-(C') edge node [left] {$1$} (M')
-(K) edge node[above] {$f$} (L')
-(M') edge node [above] {$1$} (L')
+(C') edge node [right] {$1$} (M')
+(K) edge node[below] {$f$} (L')
+(M') edge node [below] {$1$} (L')
 (N) edge node[left]{$f$} (O)
-(R) edge node[left]{$1$} (S)
+(R) edge node[right]{$1$} (S)
 (N) edge node[above]{$f$} (P)
 (R) edge node[above]{$1$} (P)
-(S) edge node[above]{$1$} (O)
+(S) edge node[below]{$1$} (O)
 (A) edge node[above]{$f$} (B)
@@
 (A) edge node[left]{$f$} (A')
-(C) edge node[left]{$1$} (C')
+(C) edge node[right]{$1$} (C')
 (A') edge node[above] {$1$} (D)

### 2021-06-29 cospans_arxiv_2.tex
made Kenny's corrections 23-31 as of June 29, and also fixed more mistakes in the bibliography

--- 2021-06-29 cospans_new.tex
@@
 % in LaTeX
-% 2021/6/28 - Finishing up
+% 2021/6/29 - second arxiv version
 
@@
 \node (C) at (0,-1) {$b$};
-\node (D) at (1.5,-1) {$b+_a a'$.};
+\node (D) at (1.5,-1) {$b+_a a'$};
 \node at (1.2,-0.8) {\Large{$\ulcorner$}};
@@
 \node[below left=2 and 1 of A,draw] (E)  {Special laris};
-\node[below=3 of A,align=center,draw] (B)  {Finite colimit preserving \\ functors $A\to\X$};
+\node[below=3 of A,align=center,draw] (B)  {Finite colimit preserving \\ functors $\A\to\X$};
 \node[below=0 of D] {\rotatebox{90}{$\simeq$}};
@@
 Basic material regarding the theory of fibrations can be found, for example, in \cite{Borc,Gray}.
-Recall that a functor $U \maps \X \to \A$ is an \textbf{opfibration} if for every $x\in\X$ with $U(x)=a$ and $f \maps a \to b$ in $\A$, there exists a \textbf{cocartesian lifting} of $f$ to $x$, namely a morphism $\beta$ in $\X$ with domain $x$ with $U(\beta) = f$ and the following universal property: for any $g\maps b\to b'$ in $\A$ and $\gamma\maps x\to y'$ in $\X$ above the composite $g\circ f$, there exists a unique $\delta\maps y\to y'$ such that $U(\delta)=g$ and $\gamma=\delta\circ\beta$ as shown below
+Recall that a functor $U \maps \X \to \A$ is an \textbf{opfibration} if for every $x\in\X$ with $U(x)=a$ and $f \maps a \to b$ in $\A$, there exists a \textbf{cocartesian lifting} of $f$ to $x$, namely a morphism $\beta$ in $\X$ with domain $x$ with $U(\beta) = f$ and the following universal property: for any $g\maps b\to b'$ in $\A$ and $\gamma\maps x\to y'$ in $\X$ above the composite $g\circ f$, there exists a unique $\delta\maps y\to y'$ such that $U(\delta)=g$ and $\gamma=\delta\circ\beta$ as shown below.
 \begin{displaymath}
 \xymatrix @R=.1in @C=.6in
-{&& y'\ar @{.>}@/_/[dd] &&\\
+{&& y'\ar @{.>}@/_/[dd] & \textrm{in }\X\\
 x\ar[r]_-{\beta} \ar @{.>}@/_/[dd]
@@
 y \ar @{.>}@/_/[dd] \ar @{-->}[ur]_-{\exists! \delta}
-&& \textrm{in }\X\\
+  \\
 && b' &&\\
@@
 \begin{itemize}
-\item objects pairs $(a, x \in F(a))$ and
-\item a morphism from $(a, x \in F(a))$ to $(b, y\in F(b))$ is a pair $(f \maps a \to b,k \maps F(f)(x) \to y)\in\A\times F(b)$.
+\item objects pairs $(a, s \in F(a))$ and
+\item a morphism from $(a, s \in F(a))$ to $(b, t\in F(b))$ is a pair $(f \maps a \to b,k \maps F(f)(s) \to t)$.
 \end{itemize}
-The unit is $(1_a\maps a\to a,F(1_a)(x)\cong x)$ and composition of $(f,k)\maps(a,x)\to(b,y)$ and $(g,\ell)\maps(b,y)\to(c,z)$ is
-\begin{displaymath}%\label{eq:compGrothcat}
-\left(a\xrightarrow{f}b\xrightarrow{g}c, F(g\circ f)x\cong Fg(Ff(x))\xrightarrow{Fg(k)}Fg(y)\xrightarrow{\ell}z\right) 
-\end{displaymath}
+The identity morphism of $(a, s\in F(a))$ is $(1_a\maps a\to a,F(1_a)(s)\xrightarrow{\sim} s)$ and the composite of $(f,k) \maps (a,s) \to (b,t)$ and $(g,\ell) \maps (b,t) \to (c,u)$ is
+\[
+\left(a\xrightarrow{f}b\xrightarrow{g}c, \; F(g\circ f)(x)\xrightarrow{\sim} (Fg)((Ff)(s))\xrightarrow{(Fg)(k)}(Fg)(t)\xrightarrow{\ell}u\right) 
+\]
 This is an opfibered category over $\A$ via the obvious forgetful functor, with fibers $(\inta F)_a=F(a)$ and reindexing functors $f_!=F(f)$.
@@
 A functor $\Phi \maps \X \to \A$ a \define{fibration} if and only if $\Phi\op \maps \X\op \to \A\op$ is an opfibration.
-Equivalently, $\Phi$ is a fibration if and only if for every $y \in \X$ with $U(y) = a$ and $f \maps a \to b$ in $\A$ there exists a cartesian lifting of $f$ to $x$, where this concept is defined dually to cocartesian lifting.
+Equivalently, $\Phi$ is a fibration if and only if for every $y \in \X$ with $U(y) = b$ and $f \maps a \to b$ in $\A$ there exists a cartesian lifting of $f$ to $y$, where this concept is defined dually to cocartesian lifting.
 Furthermore, if $\Phi$ is a fibration there is a contravariant reindexing functor
@@
 \begin{defn}\label{def:isomorphism}
-An \define{isomorphism} of symmetric monoidal categories is a symmetric monoidal 
+An \define{isomorphism} of symmetric monoidal double categories is a symmetric monoidal 
 double functor $\lF \maps \lD \to \lE$ that has an inverse.
@@
 
-\bibitem{BSZ} Filippo Bonchi, Pawe\l~Soboci\'nski and Fabio Zanasi, A categorical semantics of signal flow graphs, in \textsl{CONCUR 2014--Concurrency Theory}, eds.\ P.\ Baldan and D.\ Gorla, Lecture Notes in Computer Science \textbf{8704}, Springer, Berlin, 2014, pp.\ 435--450.
-Also available at \href{http://users.ecs.soton.ac.uk/ps/papers/sfg.pdf}{http://users.ecs.soton.ac.uk/ps/papers/sfg.pdf}.
+\bibitem{BSZ} F.\ Bonchi, P.\ Soboci\'nski and F.\ Zanasi, A categorical semantics of signal flow graphs, in \textsl{CONCUR 2014--Concurrency Theory}, eds.\ P.\ Baldan and D.\ Gorla, Lecture Notes in Computer Science \textbf{8704}, Springer, Berlin, 2014, pp.\ 435--450.
+Available at \href{http://users.ecs.soton.ac.uk/ps/papers/sfg.pdf}{http://users.ecs.soton.ac.uk/ps/papers/sfg.pdf}.
 
@@
 
-\bibitem{CTF} Gheorghe Craciun, Yangzhong Tang and Martin Feinberg, Understanding bistability in complex enzyme-driven reaction networks, \textsl{PNAS} \textbf{103} (2006), 8697--8702.
+\bibitem{CTF} G.\ Craciun, Y.\ Tang and M.\ Feinberg, Understanding bistability in complex enzyme-driven reaction networks, \textsl{PNAS} \textbf{103} (2006), 8697--8702.
 
@@
 
-\bibitem{LP} S.\ Lack and S.\ Paoli, 2-nerves for bicategories, \textsl{$K$-Theory} \textbf{38} (2008), 153--175.
+% \bibitem{LP} S.\ Lack and S.\ Paoli, 2-nerves for bicategories, \textsl{$K$-Theory} \textbf{38} (2008), 153--175.
 
@@
 \bibitem{PollardThesis} B.\ S.\ Pollard, \textsl{Open Markov Processes and Reaction Networks}, Ph.D.
-thesis, U.
+thesis, Department of Physics, U.
 C.
@@
 
-\bibitem{Willems} J.\ C.\ Willems, The behavioral approach to open and interconnected systems, \textsl{IEEE Control Systems Magazine} (2007)
+\bibitem{Willems} J.\ C.\ Willems, The behavioral approach to open and interconnected systems, \textsl{IEEE Control Systems Magazine} \textbf{27} (2007), 46--99.
+Available as \href{https://citeseerx.ist.psu.edu/viewdoc/summary?doi=10.1.1.163.8131}{https://citeseerx.ist.psu.edu/viewdoc/summary?doi=10.1.1.163.8131}.
 

### 2022-02-15 ResponseToReviews.tex
started response file

\documentclass[reqno]{amsart}

\usepackage{amssymb,amsmath,stmaryrd,txfonts,mathrsfs,amsthm}%,undertilde}
\usepackage{comment}
\usepackage[neveradjust]{paralist}
\usepackage{mathtools}
\usepackage{multirow}
\usepackage[outline]{contour}
\contourlength{1.2pt}
\usepackage{tikz}
\usetikzlibrary{intersections,arrows.meta,calc,quotes,math,decorations.pathreplacing,decorations.markings,cd,arrows,positioning,fit,matrix,
shapes.geometric,external,decorations.pathmorphing,backgrounds,circuits,circuits.ee.IEC,shapes}
\usepackage[a4paper,top=3cm,bottom=3cm,inner=3cm,outer=3cm]{geometry}
\usepackage[foot]{amsaddr}
\usepackage{graphicx}
\usepackage{stackrel}

% colors
\usepackage{xcolor}
\usepackage{framed,color}

\definecolor{shadecolor}{rgb}{1,0.8,0.3}
\definecolor{myurlcolor}{rgb}{0.5,0,0}
\definecolor{mycitecolor}{rgb}{0,0,0.7}
\definecolor{myrefcolor}{rgb}{0,0,0.7}
\definecolor{hyperrefcolor}{rgb}{0.5,0,0}

\usepackage{hyperref}
\hypersetup{
	colorlinks,
	linkcolor={hyperrefcolor},
	citecolor={hyperrefcolor},
	urlcolor={hyperrefcolor}
}

\newcommand{\backref}[1]{(Referred to on page #1.)}

\usepackage[draft]{fixme}
\usepackage[capitalize]{cleveref}

\title{Response to reviews for ``Structured versus decorated cospans''}

\author{John\ C.\ Baez, Kenny Courser, and Christina Vasilakopoulou}

\begin{document}

\maketitle

\setcounter{tocdepth}{2}
\tableofcontents

\section{Reviews - to be removed}

\subsection{First Review}

Decorated and structured cospans have been used to model open systems in the work of Fong, Baez, Courser, Master and others.

Previous work by Shulman constructed symmetric monoidal double categories functorially from bifibrations. The present manuscript recovers structured 
and decorated cospan categories as instances of this construction and then compares both using the functoriality of that same construction. The crux 
of many of the proofs is in showing the Beck-Chevalley condition required to apply Shulman’s result. All of this could feel technical but the results 
are detailed and clear. Some of the technology used here is very interesting by itself: monoidal fibrations or the construction of (symmetric 
monoidal) double categories, bicategories and categories.

From the applied point of view, they summarize many other papers in structured and decorated cospans and discuss in which cases both approaches 
coincide. It feels that this should not be this difficult to study for the 1-categorical structure (and indeed it seems to have appeared previously on 
the literature), but here it is done for the symmetric monoidal double category structure.

As the only point against, I feel there is a growing number of “cospan” articles. The present work seems like it could serve as a comparison of all of 
these, but perhaps that comparison could be more explicit and detailed: what is it done in each one of these “cospan” articles? is there anything that 
is not already explained in this one? If some of the articles about decorated cospans were found to contain errors, is this the only construction of 
decorated cospans that solves these errors?

Section 1 motivates decorated cospans in terms of systems and interfaces.

Section 2 recovers a generalization of decorated cospans from Shulman’s construction. The most important part is to show the Beck-Chevalley property 
of the fibration at hand. In Section 3, the construction of structured cospans is recovered from Shulman’s double category using a fibration from the 
comma category of a finite colimit preserving functor L : A -> X. Again, the most important part is to show that the fibration is Beck-Chevalley. Both 
constructions (decorated and structured) are treated in a uniform way, which I see as a very positive contribution. This is used in Section 4 to give 
the comparison.

Section 5 maps double categories to bicategories and categories. For this, they use a result by Hansen and Shulman that constructs them functorially 
from fibrant double categories.

Section 6 explains the problems with Set-decoration for open graphs and justifies the need for Cat-decoration. The best argument for switching Set to 
Cat in the definition of decorated cospan is actually detailed in “Structured Cospans” by Baez and Courser (§5), where they show that the notion of 
isomorphism in graph decorated cospans is too restrictive. Section 6.1 explains how, with theorem contibuted by the paper, decorated and structured 
cospans coincide on the right notion of graph isomorphism.

Section 6.2 seems to simply repeat the same procedure after labelling edges, and Section 6.3 repeats again with Petri nets. Finally, Section 6.4 shows 
something different: a category of open dynamical systems that can be described as a decorated cospan category but that cannot be equivalently 
described as a structured cospan category.

The Conclusions section explains how, if we restrict to a suitable class of opfibrations or one-side inverse adjunctions, we would get the same 
construction from decorated and structured cospans.

In my understanding, the value of this work resides in how it systematically compares the approach of decorated and structured cospans. I would 
highlight the care put in each construction, and how it builds upon previous work for most of the heavy lifting.

Suggested changes, corrections, and general comments.

Lemma 2.4: when talking about the functors $F : (A,\otimes)\to(Cat,\times)$, I think sometimes it is specified that they are lax and sometimes it is 
not. Perhaps it would be clearer to always use “lax monoidal” or to just use “monoidal” to mean lax monoidal.

Theorem 4.1: perhaps it would be clearer to say it “factors through R : Rex -> SymMonCat”.

Proof of Lemma 4.4: there is a typo where “L then becomes left adjoint to R” should probably be “L then becomes left adjoint to U”.

After Theorem A.2: In order to be consistent, it would be practical to state explicitly what is a bifibration.

Beck-Chevalley condition, after Theorem A.2: Using $X_a$ instead of $C_a$ for the fibers on the diagram would be more consistent with previous 
notation.

COVID paragraph: I appreciate the effort into explaining the applied aspect. However, claims about the software (it is “easy”, we “easily” modify, we 
“better understand”) sound too vague (is it computationally better? do we assume that the final user understands structured cospans? are we comparing 
it to other Petri net editors?). Perhaps this paragraph could be fused as a comment to the previous one, which is already a very good justification 
for the use of Petri nets with rates.

Section 6: as a reader, I really appreciate the examples: are there more in the literature? I do not think it is necessary to go in detail over each 
one of them, but perhaps it would be useful to point to other places where they are described.

\subsection{Second review}

Overview

This is an important topic and brings clarity to an open question in the ACT field. The fact that structured and decorated cospans are equivalent in 
many cases is a good thing, and the fact that the authors develop a sufficient condition for proving this equivalence is highly relevant to this 
journal. Having the description of decorated and structured cospans in the same place with a consistent presentation is very useful for the community. 
My review focuses on how I think this work fits into the broader context of ACT research in this area. I recommend publication after addressing the 
following concerns.

Suggested changes, corrections, and general comments.

General Thoughts

Given the title and abstract of this paper “Structured vs Decorated Cospans” I would expect this paper to provide a judgment that structured cospans 
are strictly better than decorated cospans in all circumstances and a justification for that claim, or a detailed analysis of the pros and cons of 
structured vs decorated cospans, some case studies in applications that show how the difference between these double categories is felt in the 
application domain, and a some description of the tradeoffs. This paper should come with some practical advice for the applied category theorist on 
how to choose whether to model their application with structured vs decorated cospans. Section 6 does a good job of detailing the various 
constructions of combinatorial structures that get double categories of structured cospans. The graph and Petri net examples are implemented in 
AlgebraicJulia, specifically the Catlab.Graphs module and the AlgebraicPetri.jl package. Given that Petri nets with structured cospans works, and 
Reaction Networks work, but open dynamical systems do not, I would like some more explanation of the differences here. The examples of graph, labeled 
graph, Petri net, reaction net are all examples of attributed C-Sets [1], the structured cospan construction in provided for arbitrary attributed 
C-Sets in Catlab.CategoricalAlgebra [2]. The open dynamical systems are not attributed C-Sets. All the examples where decorated and structured cospans 
agree are combinatorial, and the only example where they are different is not combinatorial. This gives me the impression that for categories of 
presheaves over a finitely presented category, structured cospans and decorated cospans are always equivalent. The introduction of numerical 
attributes (as in the case of reaction networks) does not appear to interfere with that pattern.

The examples in section 6 would be much stronger if the others included a theorem that all (or finitary) categories of presheaves satisfy the 
conditions of theorem 4.1 or a counter example illustrating that the situation is more complex than algebraic vs analytic distinction between open 
presheaves and the category of open dynamical systems. Without this analysis, I am left with the intuition that for discrete structures like finitary 
presheaves over a finitely presented schema, the decorated and structured cospans are going to be equivalent and for continuous mathematical 
structures like dynamical systems they will be different. If that intuition is correct, the paper should say something about it. If the intuition is 
incorrect, then additional explanation should be provided. I think that the implementation in [2] uses the left and right adjoints L and U in Theorem 
4.1, which is why I think that every category of presheaves should satisfy the main theorem. Hopefully it is easy to check and provide some commentary 
on it in this paper.

The interaction of compositional system behavior and the main theorem is also interesting and worth exploring or commenting on in this paper. If we 
take the categorical systems theory perspective advanced by section 6, and the body of the authors’ recent work on functorial semantics for complex 
systems, then we should ask why the decorated and structured cospan double categories are isomorphic for reaction networks, but their semantics as 
dynamical systems are a decorated cospan category that is not equivalent to any structured cospan category. Is there a different construction of 
semantics for reaction networks that uses structured cospans? The current work does not address the possibility of alternative semantics for 
structured cospans of systems. We can only say that DCsp is not equivalent to any structured cospan category, but is there a different decorated 
cospan category that would provide meaningful functorial semantics that is equivalent to some category of structured cospans. The structured cospan 
view is better for implementing the composition of the system specifications (reaction networks) but the current literature only uses decorated 
cospans for providing the systems with behaviors. If the authors can discuss this issue it would greatly enhance the utility of this paper for shaping 
the research discussion around compositional complex systems.

The conclusions refer to a forthcoming paper. The only conclusion that refers to the work presented in this paper is that theorem 4.1 gives conditions 
under which a category of decorated cospans is isomorphic to a category of structured cospans. Given that the audience for this paper is intended to 
be applied category theorists, this is a place where I would expect some guidance on when an ACT practitioner should choose either structured or 
decorated cospans depending on what mathematical structures they are formalizing within ACT.

Specific Concerns

The development of the AlgebraicPetri software system is credited to Halter and Patterson based on a blog post. The correct citation is to the 
software itself and should be credited to the entire AlgebraicPetri team based on a citation to the repository [3]. The additional authors would be 
Andrew Baas and James Fairbanks.

Several points in the text are written in a way style that can be interpreted as the dismissive style common to many discussions of Category Theory. I 
would recommend rewriting at least the following points that should be made in a more collegial tone.

pg. 2: “But this hope is doomed for reasons painstakingly explained in [1, Section 5] … despite all the tricks one might try.” This paragraph provides 
no insight into the reasons that those tricks fail. Referring them to tricks is dismissive. The citation is to a paper in TAC by the current authors.

pg. 3: “Many of the flawed applications of decorated cospans have been fixed using structured cospans.” This dismisses the work of other scholars 
using the decorated cospan approach as flawed. The alleged flaw should be made more precise. What about the decorated cospan approach is inferior to 
the structured cospan approach? The goal of this paper should be to illustrate to an applied category theory audience the differences between 
decorated and structured cospans. Referring back to previous work of the authors to make that point does not provide value.

pg. 27: To show that U does not have a left adjoint, we use the following well-known result. For readers of the TAC paper previously cited, that might 
be a well known result that does not require a citation, but my understanding of the Compositionality audience assumed that the ACT work was targeted 
readers that are more familiar with the applications and thus cannot be assumed to know such results.

\begin{verbatim}
[1] https://arxiv.org/abs/2106.04703
[2] https://github.com/AlgebraicJulia/Catlab.jl/blob/f06417de29421441c4133c1cfb75b39ae8aa7142/src/categorical_algebra/StructuredCospans.jl
[3] https://github.com/AlgebraicJulia/AlgebraicPetri.jl
\end{verbatim}

\section{Our Answer}

\begin{enumerate}

\item As the only point against, I feel there is a growing number of “cospan” articles. The present work seems like it could serve as a comparison of 
all of 
these, but perhaps that comparison could be more explicit and detailed: what is it done in each one of these “cospan” articles? is there anything 
that 
is not already explained in this one? If some of the articles about decorated cospans were found to contain errors, is this the only construction of 
decorated cospans that solves these errors?

 \item Lemma 2.4: when talking about the functors $F : (A,\otimes)\to(Cat,\times)$, I think sometimes it is specified that they are lax and sometimes 
it is 
not. Perhaps it would be clearer to always use “lax monoidal” or to just use “monoidal” to mean lax monoidal.

\item Theorem 4.1: perhaps it would be clearer to say it “factors through R : Rex -> SymMonCat”.

\item Proof of Lemma 4.4: there is a typo where “L then becomes left adjoint to R” should probably be “L then becomes left adjoint to U”.

\item After Theorem A.2: In order to be consistent, it would be practical to state explicitly what is a bifibration.

\item Beck-Chevalley condition, after Theorem A.2: Using $X_a$ instead of $C_a$ for the fibers on the diagram would be more consistent with previous 
notation.

\item COVID paragraph: I appreciate the effort into explaining the applied aspect. However, claims about the software (it is “easy”, we “easily” 
modify, we 
“better understand”) sound too vague (is it computationally better? do we assume that the final user understands structured cospans? are we comparing 
it to other Petri net editors?). Perhaps this paragraph could be fused as a comment to the previous one, which is already a very good justification 
for the use of Petri nets with rates.

\item Section 6: as a reader, I really appreciate the examples: are there more in the literature? I do not think it is necessary to go in detail over 
each 
one of them, but perhaps it would be useful to point to other places where they are described.

\item Given the title and abstract of this paper “Structured vs Decorated Cospans” I would expect this paper to provide a judgment that structured 
cospans 
are strictly better than decorated cospans in all circumstances and a justification for that claim, or a detailed analysis of the pros and cons of 
structured vs decorated cospans, some case studies in applications that show how the difference between these double categories is felt in the 
application domain, and a some description of the tradeoffs. This paper should come with some practical advice for the applied category theorist on 
how to choose whether to model their application with structured vs decorated cospans

\item ...if the others included a theorem that all (or finitary) categories of presheaves satisfy the 
conditions of theorem 4.1 or a counter example

(Possibly copy John's comments here and finish this list)
\end{enumerate}

\end{document}

### 2022-02-16 ResponseToReviews.tex
finished the list I think

@@
 shapes.geometric,external,decorations.pathmorphing,backgrounds,circuits,circuits.ee.IEC,shapes}
-\usepackage[a4paper,top=3cm,bottom=3cm,inner=3cm,outer=3cm]{geometry}
+\usepackage[a4paper,top=2cm,bottom=2cm,inner=3cm,outer=3cm]{geometry}
 \usepackage[foot]{amsaddr}
@@
 \usepackage{framed,color}
+
+\def\chris{\color{purple} Christina: }
+\def\john{\color{red} John: }
+\def\kenny{\color{blue} Kenny: }
 
@@
 \subsection{First Review}
+
+{\footnotesize
 
@@
 Section 6: as a reader, I really appreciate the examples: are there more in the literature? I do not think it is necessary to go in detail over each 
-one of them, but perhaps it would be useful to point to other places where they are described.
+one of them, but perhaps it would be useful to point to other places where they are described.}
 
 \subsection{Second review}
+
+{\footnotesize
 
@@
 be a well known result that does not require a citation, but my understanding of the Compositionality audience assumed that the ACT work was targeted 
-readers that are more familiar with the applications and thus cannot be assumed to know such results.
+readers that are more familiar with the applications and thus cannot be assumed to know such results.}
 
@@
 application domain, and a some description of the tradeoffs. This paper should come with some practical advice for the applied category theorist on 
-how to choose whether to model their application with structured vs decorated cospans
+how to choose whether to model their application with structured vs decorated cospans (...) [Conclusions section] this is a place where I would expect 
+some guidance on when an ACT practitioner should choose either structured or 
+decorated cospans depending on what mathematical structures they are formalizing within ACT.
 
-\item ...if the others included a theorem that all (or finitary) categories of presheaves satisfy the 
-conditions of theorem 4.1 or a counter example
+{\john That is their guess about what the paper should be about. I guess they were hoping for something like this:
+Theorem. Structured cospans are strictly better than decorated cospans in all circumstances.
+Does our abstract actually suggest that we're talking about which formalism is "better", or the "pros and cons"?
+I just checked: no, it does not.}
 
-(Possibly copy John's comments here and finish this list)
+\item Given that Petri nets with structured cospans works, and Reaction Networks work, but open dynamical systems do not, I would like some more 
+explanation of the differences here. The examples of graph, labeled 
+graph, Petri net, reaction net are all examples of attributed C-Sets [1], the structured cospan construction in provided for arbitrary attributed 
+C-Sets in Catlab.CategoricalAlgebra [2]. The open dynamical systems are not attributed C-Sets.(...)The examples in section 6 would be much stronger 
+if the others included a theorem that all (or finitary) categories of presheaves satisfy the 
+conditions of theorem 4.1 or a counter example (...) Hopefully it is easy to check and provide some 
+commentary 
+on it in this paper.
+
+{\john I agree that a general result like this would be nice, but I don't have the energy to dream one up and prove it. The most we can do here is say 
+that this is worth studying.... maybe after we give the example of a decorated cospan category that's not a structured cospan category.}
+
+\item If we take the categorical systems theory perspective advanced by section 6, and the body of the authors’ recent work on functorial semantics 
+for complex 
+systems, then we should ask why the decorated and structured cospan double categories are isomorphic for reaction networks, but their semantics as 
+dynamical systems are a decorated cospan category that is not equivalent to any structured cospan category. Is there a different construction of 
+semantics for reaction networks that uses structured cospans?
+
+\item The development of the AlgebraicPetri software system is credited to Halter and Patterson based on a blog post. The correct citation is to the 
+software itself and should be credited to the entire AlgebraicPetri team based on a citation to the repository [3]. The additional authors would be 
+Andrew Baas and James Fairbanks.
+
+{\john I wasn't trying to talk about AlgebraicPetri, just the application to epidemiology, and unfortunately that was (and still is???) only explained 
+in a blog article. But it'd be good to add a reference to the repository.}
+
+[Several points in the text are written in a way style that can be interpreted as the dismissive style common to many discussions of Category 
+Theory. I 
+would recommend rewriting at least the following points that should be made in a more collegial tone.]
+
+\item pg. 2: “But this hope is doomed for reasons painstakingly explained in [1, Section 5] … despite all the tricks one might try.” This paragraph 
+provides 
+no insight into the reasons that those tricks fail. Referring them to tricks is dismissive. The citation is to a paper in TAC by the current authors.
+
+\item pg. 3: “Many of the flawed applications of decorated cospans have been fixed using structured cospans.” This dismisses the work of other 
+scholars 
+using the decorated cospan approach as flawed. The alleged flaw should be made more precise. What about the decorated cospan approach is inferior to 
+the structured cospan approach? The goal of this paper should be to illustrate to an applied category theory audience the differences between 
+decorated and structured cospans. Referring back to previous work of the authors to make that point does not provide value.
+
+{\john The "other scholars" are mainly me and Brendan, and the flaws are that some claims are false! I think we describe the flaws in Section 6; if so 
+we should point to that.}
+{\john I don't like referees who say what the goal of my paper "should be". The goal of this paper is clearly to set up a clear relation between 
+structured and decorated cospans, and I hope we make that clear already in the abstract!}
+
+\item pg. 27: To show that U does not have a left adjoint, we use the following well-known result. For readers of the TAC paper previously cited, 
+that might 
+be a well known result that does not require a citation, but my understanding of the Compositionality audience assumed that the ACT work was targeted 
+readers that are more familiar with the applications and thus cannot be assumed to know such results.
+
+{\john We can just leave out "well-known".}
+{\kenny Emily Riehl's Category Theory In Context (Lemma 4.6.1 on pdf page 162):
+
+was where I found that theorem when I was working on how to show that counterexample. I doubt she was the first, but she states it exactly as we have 
+it and she gives a proof.}
+
 \end{enumerate}

### 2022-02-16 cospans_new.tex
made 2 corrections suggested by Kenny on 6/29
Added a reference for Lemma 6.1

@@
 
-To show that $U$ does not have a left adjoint, we use the following well-known result:
+To show that $U$ does not have a left adjoint, we use the following well-known result \cite[Lemma 4.6.1]{Riehl}:
 \begin{lem} \label{lem:initial}
@@
 
+\bibitem{Riehl} E.\ Riehl, \textsl{Category Theory In Context}, Dover Publications, New York, 2016. Available at \href{https://math.jhu.edu/~eriehl/context/}{https://math.jhu.edu/~eriehl/context/}.
+
 \bibitem{SSV} P.\ Schultz, D.\ Spivak and C.\ Vasilakopoulou, Dynamical systems and sheaves, \textsl{Appl.\ Cat.\ Struct.\ }\textbf{28} (2020), 1--57.

### 2022-02-18 ResponseToReviews.tex
added two new reviews

@@
 
+\subsection{Third review}
+
+{\footnotesize
+Decorated and structured cospans have emerged as a mainstay of the current wave of ACT, the latter correcting certain technical problems with the 
+former. This paper poses two questions:
+
+    How can the technical problems with decorated cospans be fixed?
+
+    How does the corrected version of decorated cospans compare with structured cospans?
+
+The paper offers the following answers:
+
+The symmetric lax monoidal functor (A,+) -> (Set, $\times$) defining a category of isomorphism classes of decorated cospans is replaced by a 
+symmetric lax monoidal pseudofunctor (A,+) -> (Cat, $\times$) defining a symmetric monoidal double category of decorated cospans.
+
+A sufficient condition, the main Theorem 4.1, is provided for a double category of decorated cospans to be equivalent, indeed isomorphic, to a double 
+category of structured cospans. Several examples, as well as a nonexample, of applying the theorem are given.
+
+The paper is a technical one, giving slick but abstract constructions and proofs using machinery developed by Shulman for turning monoidal 
+bifibrations into double categories, and it serves more to clarify and compare existing ACT methods than to introduce new ones. The mathematical 
+exposition is, however, very strong, and a fairly wide range of readers should be able to take something away from the paper. Given the central status 
+of decorated/structured cospans within ACT, it was important that the above questions be addressed, and the authors have done so admirably. Also, the 
+constructions and results are “black-boxed” in such a manner that practioners will be able to use them without understanding in detail the proofs that 
+support them. I therefore consider this paper to be a strong contribution to the scholarship of ACT and recommend that it be published.
+
+Suggested changes, corrections, and general comments.
+
+Following are some questions and minor suggested changes.
+
+p. 2. “Unfortunately, many applications of decorated cospans were flawed… for reasons painstaking explained in [1]”
+
+Since fixing these problems is a major motivation for the whole paper, it would be good to explain what they are in slightly more detail, rather than 
+just giving a reference. This could be done in a one paragraph or less. The gist of it, as I recall, is that in the original approach to decorated 
+cospans, the isomorphism classes of open graphs depend on the identities of the edge elements, which is clearly wrong.
+
+p. 4, following statement of Thm 2.1.
+
+The diagram depicting the decoration morphism $\tau$ as a natural transformation, first shown explictly on p. 10, should be moved here since it is 
+implicitly used at the beginning of p. 5 to define the decoration of horizontal composites.
+
+p. 9, ingredients for constructing a double functor of decorated cospan double categories.
+
+Does the natural transformation $\theta$: EF => F’ H have to be a natural isomorphism? Quite possibly I missed something, but I don’t see where in 
+the following proofs that assumption is used.
+
+p. 21, definition of F: Set -> Cat
+
+The use f, g for vertex/edge maps is opposite of the convention used on the previous page. I suggest that the same convention be used for both the 
+decorated and structured approach to constructing open graphs.
+
+p. 27, end of Section 6.
+
+It seems that the left adjoint needed for structured cospans fails to exist because the chosen category of dynamical systems does not have enough 
+morphisms. Relatedly, this is the only example where the pseudofunctor D: (FinSet,+) -> (Cat, $\times$) comes from a simple functor D: (FinSet,+) -> 
+(Set, $\times$) by viewing sets as discrete categories. In the other examples, this would count as using decorated cospans in the old, flawed way. 
+All of this suggests the question: is there a way of constructing a category of dynamical systems that has more morphisms, so that a connection with 
+structured cospans can be established?
+
+p. 30, following Thm A.2
+
+If I am not mistaken, “fibration”, “opfibration,” “monoidal (op/bi)fibration” are all defined, but the definition of “bifibration” is omitted. For 
+completeness, it should be included.
+
+A last general comment is that the paper unfortunately adopts the strategy, all too common in math papers, of putting all the examples in a section at 
+the end of the paper. I think the readability of the paper would be improved, without much change to the organization, if the motivating example of 
+open graphs were added to the relevant places in Sections 2 and 3. The remaining examples could be left in Section 6.
+}
+
+\subsection{Fourth review}
+
+{\footnotesize
+What are the main questions posed by the manuscript, and how does it answer them? Why or why not is this work a significant technical or conceptual 
+contribution to scholarship?
+
+Decorated cospans and structured cospans are two different tools for building categories of open systems, both of which have been applied in several 
+existing papers (and this reviewer believes they will continue to grow in importance over time). This paper explains the relationship between them, in 
+a very elegant way using the equivalence between fibered and indexed categories, to the extent that the two constructions now appear as different 
+perspectives on the same fundamental idea. To me this relationship appears obvious in retrospect, and I mean this as a compliment to the paper. I 
+think this paper is an important contribution to categorical systems theory, and I recommend acceptance.
+
+Suggested changes, corrections, and general comments.
+
+Composition of morphisms f, g in this paper is usually denoted gf, and occasionally gof. I’d suggest mentioning this in the “conventions” section.
+
+p3: “Using the Grothendieck construction” - maybe worth mentioning this is the “covariant” version which is different to the most common convention 
+(at least I think so, but the literature seems to be very split over this)
+
+Theorem 2.1: Maybe worth saying explicitly that s is an object of the category F(m) rather than using $\in$, since this is exactly the distinction to 
+Fong’s original definition
+
+Proof of theorem 2.1: You should probably at least handwave that the cartesian liftings really are cartesian liftings. (No doubt it’s easy, but this 
+is a classic sort of spot where errors can hide)
+
+On page 9 during the construction of H, I would appreciate a sentence giving some intuition for the functor E, at this point I’m confused about its 
+role.
+
+Theorem 2.5: F should be defined on A, not A’
+
+I think it would be worth saying in words a bit more prominently what the hypothesis of theorem 4.1 roughly means, namely that the fibers of the total 
+category have finite colimits, reindexing preserves them, and the monoidal product on the fibers is cocartesian.
+
+I wonder if the “problem” where DCsp is not a structured cospan category could be “fixed” by upgrading the functor from Set to Cat in a non-discrete 
+way, for example with an ordering with the zero vector field as the bottom element. I suppose this would give you different 2-cells in the resulting 
+double category or bicategory, but perhaps it would yield the same 1-category}
+
 \section{Our Answer}
@@
 
+{\chris Second starts here}
 \item Given the title and abstract of this paper “Structured vs Decorated Cospans” I would expect this paper to provide a judgment that structured 
@@
 
+{\chris Third starts here}
+\item p. 2. “Unfortunately, many applications of decorated cospans were flawed… for reasons painstaking explained in [1]”
+
+Since fixing these problems is a major motivation for the whole paper, it would be good to explain what they are in slightly more detail, rather than 
+just giving a reference. This could be done in a one paragraph or less. The gist of it, as I recall, is that in the original approach to decorated 
+cospans, the isomorphism classes of open graphs depend on the identities of the edge elements, which is clearly wrong.
+
+\item p. 4, following statement of Thm 2.1.
+
+The diagram depicting the decoration morphism $\tau$ as a natural transformation, first shown explictly on p. 10, should be moved here since it is 
+implicitly used at the beginning of p. 5 to define the decoration of horizontal composites.
+
+\item p. 9, ingredients for constructing a double functor of decorated cospan double categories.
+
+Does the natural transformation $\theta$: EF => F’ H have to be a natural isomorphism? Quite possibly I missed something, but I don’t see where in 
+the following proofs that assumption is used.
+
+\item p. 21, definition of F: Set -> Cat
+
+The use f, g for vertex/edge maps is opposite of the convention used on the previous page. I suggest that the same convention be used for both the 
+decorated and structured approach to constructing open graphs.
+
+\item p. 27, end of Section 6.
+
+It seems that the left adjoint needed for structured cospans fails to exist because the chosen category of dynamical systems does not have enough 
+morphisms. Relatedly, this is the only example where the pseudofunctor D: (FinSet,+) -> (Cat, $\times$) comes from a simple functor D: (FinSet,+) -> 
+(Set, $\times$) by viewing sets as discrete categories. In the other examples, this would count as using decorated cospans in the old, flawed way. 
+All of this suggests the question: is there a way of constructing a category of dynamical systems that has more morphisms, so that a connection with 
+structured cospans can be established?
+
+\item p. 30, following Thm A.2
+
+If I am not mistaken, “fibration”, “opfibration,” “monoidal (op/bi)fibration” are all defined, but the definition of “bifibration” is omitted. For 
+completeness, it should be included.
+
+{\john If we don't define bifibration, we definitely should!}
+
+\item A last general comment is that the paper unfortunately adopts the strategy, all too common in math papers, of putting all the examples in a 
+section at 
+the end of the paper. I think the readability of the paper would be improved, without much change to the organization, if the motivating example of 
+open graphs were added to the relevant places in Sections 2 and 3. The remaining examples could be left in Section 6.
+
+{\john
+I don't want to bust up the examples and put some in sections 2 and 3. Anyone who wants examples can easily find them all in Section 6, we mention 
+this section in the introduction (and perhaps should advertise it more there), and it's hard to analyze the examples without having all the theory in 
+hand.}
+
+{\chris Fourth starts here}
+\item Composition of morphisms f, g in this paper is usually denoted gf, and occasionally gof. I’d suggest mentioning this in the “conventions” 
+section.
+
+\item p3: “Using the Grothendieck construction” - maybe worth mentioning this is the “covariant” version which is different to the most common 
+convention 
+(at least I think so, but the literature seems to be very split over this)
+
+\item Theorem 2.1: Maybe worth saying explicitly that s is an object of the category F(m) rather than using $\in$, since this is exactly the 
+distinction to 
+Fong’s original definition
+
+\item Proof of theorem 2.1: You should probably at least handwave that the cartesian liftings really are cartesian liftings. (No doubt it’s easy, but 
+this 
+is a classic sort of spot where errors can hide)
+
+\item On page 9 during the construction of H, I would appreciate a sentence giving some intuition for the functor E, at this point I’m confused about 
+its 
+role.
+
+\item Theorem 2.5: F should be defined on A, not A’
+
+\item I think it would be worth saying in words a bit more prominently what the hypothesis of theorem 4.1 roughly means, namely that the fibers of 
+the total 
+category have finite colimits, reindexing preserves them, and the monoidal product on the fibers is cocartesian.
+
+\item I wonder if the “problem” where DCsp is not a structured cospan category could be “fixed” by upgrading the functor from Set to Cat in a 
+non-discrete 
+way, for example with an ordering with the zero vector field as the bottom element. I suppose this would give you different 2-cells in the resulting 
+double category or bicategory, but perhaps it would yield the same 1-category
 \end{enumerate}

### 2022-03-04 ResponseToReviews.tex
first round of easy edits

@@
 
-\item Theorem 4.1: perhaps it would be clearer to say it “factors through R : Rex -> SymMonCat”.
+{\bf We have added ``lax'' at Lemma 2.4 in two occurences, and have checked the rest of the document to verify that this does not happen 
+elsewhere.}
+
+\item Theorem 4.1: perhaps it would be clearer to say it “factors through R : Rex $\to$ SymMonCat”.
+
+{\bf Done, also in Corollary 4.3.}
 
@@
 
+{\bf Done.}
+
 \item After Theorem A.2: In order to be consistent, it would be practical to state explicitly what is a bifibration.
+
+{\bf Done.}
 
@@
 notation.
+
+{\bf Done.}
 
@@
 
-{\chris Second starts here}
+{\chris Second review starts here}
 \item Given the title and abstract of this paper “Structured vs Decorated Cospans” I would expect this paper to provide a judgment that structured 
@@
 
+{\chris Perhaps merge this with point 16 and possibly others, and after we do something, write a common response!}
+
 \item pg. 3: “Many of the flawed applications of decorated cospans have been fixed using structured cospans.” This dismisses the work of other 
@@
 
-{\john We can just leave out "well-known".}
-{\kenny Emily Riehl's Category Theory In Context (Lemma 4.6.1 on pdf page 162):
+{\bf We have added a citation to Emily Riehl's book ``Category Theory in Context'' which includes said result, above Lemma 6.1.}
 
-was where I found that theorem when I was working on how to show that counterexample. I doubt she was the first, but she states it exactly as we have 
-it and she gives a proof.}
-
-{\chris Third starts here}
+{\chris Third review starts here}
 \item p. 2. “Unfortunately, many applications of decorated cospans were flawed… for reasons painstaking explained in [1]”
@@
 
+{\chris Merge with at least 13.}
+
 \item p. 4, following statement of Thm 2.1.
@@
 
+{\bf We have moved the natural isomorphism triangle as equation (1) in the statement of Theorem 2.1, and we have referred to it at page 10.}
+
 \item p. 9, ingredients for constructing a double functor of decorated cospan double categories.
 
-Does the natural transformation $\theta$: EF => F’ H have to be a natural isomorphism? Quite possibly I missed something, but I don’t see where in 
+Does the natural transformation $\theta$: EF $\Rightarrow$ F’ H have to be a natural isomorphism? Quite possibly I missed something, but I don’t see 
+where in 
 the following proofs that assumption is used.
 
-\item p. 21, definition of F: Set -> Cat
+\item p. 21, definition of F: Set $\to$ Cat
 
@@
 
+{\chris I don't think I understand this, anyone else?}
+
 \item p. 27, end of Section 6.
@@
 It seems that the left adjoint needed for structured cospans fails to exist because the chosen category of dynamical systems does not have enough 
-morphisms. Relatedly, this is the only example where the pseudofunctor D: (FinSet,+) -> (Cat, $\times$) comes from a simple functor D: (FinSet,+) -> 
-(Set, $\times$) by viewing sets as discrete categories. In the other examples, this would count as using decorated cospans in the old, flawed way. 
+morphisms. Relatedly, this is the only example where the pseudofunctor D: (FinSet,+) $\to$ (Cat, $\times$) comes from a simple functor D: (FinSet,+) 
+$\to$ (Set, $\times$) by viewing sets as discrete categories. In the other examples, this would count as using decorated cospans in the old, flawed 
+way. 
 All of this suggests the question: is there a way of constructing a category of dynamical systems that has more morphisms, so that a connection with 
@@
 
-{\john If we don't define bifibration, we definitely should!}
+{\bf Done.}
 
@@
 
-{\chris Fourth starts here}
+{\chris Fourth review starts here}
 \item Composition of morphisms f, g in this paper is usually denoted gf, and occasionally gof. I’d suggest mentioning this in the “conventions” 
 section.
+
+{\chris I would be happy to add this to conventions, but I cannot seem to find gf anywhere in the paper. Anyone else?}
 
@@
 
+{\chris Not sure that `covariant' would make this clearer...both are very well the Grothendieck construction I would think, but I don't mind that 
+much.}
+
 \item Theorem 2.1: Maybe worth saying explicitly that s is an object of the category F(m) rather than using $\in$, since this is exactly the 
@@
 Fong’s original definition
+
+{\chris Maybe just specify in the statement of 2.1, definitely keep $\in$ sign in all diagrams below!}
 
@@
 
+{\bf Done.}
+
 \item I think it would be worth saying in words a bit more prominently what the hypothesis of theorem 4.1 roughly means, namely that the fibers of 
@@
 category have finite colimits, reindexing preserves them, and the monoidal product on the fibers is cocartesian.
+
+{\bf We have added a paragraph right below the statement of Theorem 4.1, clarifying its assumptions as suggested, which also incorporates an 
+explanatory paragraph previously located under Corollary 4.3.}
 

### 2022-03-04 cospans_new.tex
first round of easy edits

@@
 \]
-together with a \define{decoration morphism} $\tau \maps F(h)(s) \to s'$ in $F(m')$.
+together with a \define{decoration morphism} $\tau \maps F(h)(s) \to s'$ in $F(m')$, which can be thought of as a natural transformation
+\begin{equation}\label{eq:taunattransf}
+\begin{tikzpicture}[baseline=(current  bounding  box.center),scale=1.5]
+\node (G) at (-3.5,-0.5) {$1$};
+\node (H) at (-2,0) {$F(m)$};
+\node (I) at (-2,-1) {$F(n)$};
+\node (J) at (-2.5,-0.5) {$\scriptstyle\Downarrow\tau$};
+\path[->,font=\scriptsize,>=angle 90]
+(G) edge node [above] {$s$} (H)
+(G) edge node [below] {$s'$} (I)
+(H) edge node [right] {$F(h)$} (I);
+\end{tikzpicture}
+\end{equation}
 \end{itemize}
@@
 \label{lem:MonGroth}
-For any monoidal category $(\A,\otimes)$, there is a 2-equivalence between the 2-categories of monoidal opfibrations $U\maps (\X, \otimes) \to (\A, \otimes)$ and monoidal pseudofunctors $F \maps (\A,\otimes) \to (\mathsf{Cat}, \times)$, and if $\A$ cocartesian monoidal, there is a 2-equivalence between these and pseudofunctors from $\A$ into $\MonCat$.
-If $\A$ is symmetric monoidal, there is also a 2-equivalence between the 2-categories of symmetric monoidal opfibrations $U \maps (\X, \otimes) \to (\A, \otimes)$ and symmetric monoidal pseudofunctors $F \maps  (\A,\otimes) \to (\mathsf{Cat}, \times)$ , and if $\A$ cocartesian monoidal, there is a 2-equivalence between these and pseudofunctors from $\A$ into $\SMC$.
+For any monoidal category $(\A,\otimes)$, there is a 2-equivalence between the 2-categories of monoidal opfibrations $U\maps (\X, \otimes) \to (\A, 
+\otimes)$ and lax monoidal pseudofunctors $F \maps (\A,\otimes) \to (\mathsf{Cat}, \times)$, and if $\A$ cocartesian monoidal, there is a 
+2-equivalence between these and pseudofunctors from $\A$ into $\MonCat$.  If $\A$ is symmetric monoidal, there is also a 2-equivalence between the 
+2-categories of symmetric monoidal opfibrations $U \maps (\X, \otimes) \to (\A, \otimes)$ and symmetric lax monoidal pseudofunctors $F \maps  
+(\A,\otimes) \to (\mathsf{Cat}, \times)$ , and if $\A$ cocartesian monoidal, there is a 2-equivalence between these and pseudofunctors from $\A$ into 
+$\SMC$.
 \end{lem}
@@
 \]
-where the decoration morphism $\lH(\tau)$ is defined as follows.  We can think of $\tau$ as a natural transformation
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (G) at (-3.5,-0.5) {$1$};
-\node (H) at (-2,0) {$F(m)$};
-\node (I) at (-2,-1) {$F(n)$};
-\node (J) at (-2.5,-0.5) {$\scriptstyle\Downarrow\tau$};
-\path[->,font=\scriptsize,>=angle 90]
-(G) edge node [above] {$s$} (H)
-(G) edge node [below] {$s'$} (I)
-(H) edge node [right] {$F(h)$} (I);
-\end{tikzpicture}
-\]
-and in the same style of notation $\lH(\tau)$ is given by
+where the decoration morphism $\lH(\tau)$ is defined as follows.  Thinking of $\tau$ as a natural transformation \cref{eq:taunattransf},
+in the same style of notation $\lH(\tau)$ is given by
 \[
@@
 \label{thm:functoriality}
-Given categories $\A$ and $\A'$ with finite colimits, lax monoidal pseudofunctors $F, F' \maps (\A',+) \to (\Cat,\times)$, a finite colimit preserving functor $H \maps \A \to \A'$, a lax monoidal pseudofunctor $E \maps (\Cat,\times) \to (\Cat,\times)$ and a monoidal natural isomorphism $\theta$ as in the following diagram:
+Given categories $\A$ and $\A'$ with finite colimits, lax monoidal pseudofunctors $F, \maps (\A,+) \to (\Cat,\times)$ and $F' \maps (\A',+) \to 
+(\Cat,\times)$, a finite colimit preserving functor $H \maps \A \to \A'$, a lax monoidal pseudofunctor $E \maps (\Cat,\times) \to (\Cat,\times)$ and 
+a monoidal natural isomorphism $\theta$ as in the following diagram:
 \[
@@
 Suppose $\A$ has finite colimits and $F \maps (\A,+) \to (\Cat,\times)$ is a symmetric lax monoidal pseudofunctor. If the corresponding pseudofunctor $F \maps \A \to \SMC$ from \cref{lem:MonGroth}
- factors through $\Rex$, then the symmetric monoidal double categories $F\lCsp$ of decorated cospans and ${}_L\lCsp(\inta F)$ of structured cospans are isomorphic, where $L \maps \A \to \inta F$ is a left adjoint of the induced Grothendieck opfibration $U \maps \inta F \to \A$.
+ factors through $\Rex\to\SMC$, then the symmetric monoidal double categories $F\lCsp$ of decorated cospans and ${}_L\lCsp(\inta F)$ of structured 
+cospans are isomorphic, where $L \maps \A \to \inta F$ is a left adjoint of the induced Grothendieck opfibration $U \maps \inta F \to \A$.
 \end{thm}
@@
 
-It will be important to know that under the hypotheses of \cref{thm:equiv} the opfibration $U$ preserves all finite colimits.   For this we need the following lemma.
+Essentially, the above assumptions state that the fibers of the induced opfibration $U$ have finite colimits which are preserved by the reindexing 
+functors, and the induced fiberwise monoidal structure is cocartesian. Explicitly, regarding the last point, the lax monoidal 
+pseudofunctor structure $(F,\phi,\phi_0)$ gives rise to a specific symmetric monoidal structure on the fibers $F(a)$ in terms of $\phi,\phi_0$ given 
+by \cref{eq:explicitstructure1}, since $\A$ is cocartesian monoidal. We here ask that the induced pseudofunctor $F\maps \A\to\SMC$ factors through 
+$\Rex$, namely that \cref{eq:explicitstructure1} gives coproducts and an initial object in each $F(a)$.
+
+It will be important to know that under the hypotheses of 
+\cref{thm:equiv} the opfibration $U$ preserves all finite colimits.   For this we need the following lemma.
 
@@
 \begin{cor} \label{cor:fcocMonGroth}
- Suppose $\A$ has finite colimits and $F \maps (\A,+) \to (\Cat,\times)$ is a symmetric lax monoidal pseudofunctor for which the corresponding pseudofunctor $F  \maps \A \to \SMC$ from \cref{lem:MonGroth} factors through $\Rex$.
-Then $\inta F$ has all finite colimits and  the induced opfibration $U\maps \inta F \to \A$ preserves them.
-Moreover we can choose finite colimits in $\inta F$ so that $U$ preserves them strictly.
+ Suppose $\A$ has finite colimits and $F \maps (\A,+) \to (\Cat,\times)$ is a symmetric lax monoidal pseudofunctor for which the corresponding 
+pseudofunctor $F  \maps \A \to \SMC$ from \cref{lem:MonGroth} factors through $\Rex\to\SMC$.  Then $\inta F$ has all finite colimits and  the induced 
+opfibration $U\maps \inta F \to \A$ preserves them.  Moreover we can choose finite colimits in $\inta F$ so that $U$ preserves them strictly.
 \end{cor}
-
-Regarding the assumptions of the above corollary, notice that since $\A$ is cocartesian monoidal, the lax monoidal pseudofunc\-tor structure $(F,\phi,\phi_0)$ gives rise to a specific symmetric monoidal structure on the fibers $F(a)$ in terms of $\phi,\phi_0$, given explicitly by \cref{eq:explicitstructure1}.
-Since we now ask that the pseudofunctor $F\maps \A\to\SMC$ factors through $\Rex$, this fiberwise monoidal structure is required to be cocartesian, namely that \cref{eq:explicitstructure1} gives coproducts and an initial object in each $F(a)$.
 
@@
 \]
-where $\mathrm{Cocart}(f,\bot_a)$ is the cocartesian lifting of $f$ to $\bot_a$ and $\chi_a$ is the unique isomorphism between two initial objects in the fiber above $a'$.
-The functor $L$ then becomes left adjoint to $R$ with unit $\iota_a \maps a \to U(L(a))$ being the identity, using the fact that $U(L(a)) = U(\bot_a) = a$.
+where $\mathrm{Cocart}(f,\bot_a)$ is the cocartesian lifting of $f$ to $\bot_a$ and $\chi_a$ is the unique isomorphism between two initial objects in 
+the fiber above $a'$.    The functor $L$ then becomes left adjoint to $L$ with unit $\iota_a \maps a \to U(L(a))$ being the identity, using the fact 
+that $U(L(a)) = U(\bot_a) = a$.
 \end{proof}
@@
 \[    f^\ast \maps \X_b \to \X_a \]
-for each morphism $f \maps a \to b$.
+for each morphism $f \maps a \to b$.  Moreover, $\Phi\colon\X\to\A$ is a \define{bifibration} if it is both a fibration and opfibration.
 
@@
 \begin{tikzpicture}[scale=1.5]
-\node (A) at (0,0) {$\C_a$};
-\node (B) at (1.5,0) {$\C_b$};
-\node (C) at (0,-1) {$\C_c$};
-\node (D) at (1.5,-1) {$\C_d$};
+\node (A) at (0,0) {$\X_a$};
+\node (B) at (1.5,0) {$\X_b$};
+\node (C) at (0,-1) {$\X_c$};
+\node (D) at (1.5,-1) {$\X_d$};
 \node (E) at (0.75,-0.5) {$\scriptstyle\Downarrow \theta$};

### 2022-03-04 cospans_new.tex
teeny tiny change

@@
 where $\mathrm{Cocart}(f,\bot_a)$ is the cocartesian lifting of $f$ to $\bot_a$ and $\chi_a$ is the unique isomorphism between two initial objects in 
-the fiber above $a'$.    The functor $L$ then becomes left adjoint to $L$ with unit $\iota_a \maps a \to U(L(a))$ being the identity, using the fact 
+the fiber above $a'$.    The functor $L$ then becomes left adjoint to $U$ with unit $\iota_a \maps a \to U(L(a))$ being the identity, using the fact 
 that $U(L(a)) = U(\bot_a) = a$.

### 2022-03-05 ResponseToReviews.tex
Couple comments in the response file

@@
 
+{\color{blue}{Kenny: I think they are correct in that we don't use this extra assumption.}}
+
 \item p. 21, definition of F: Set $\to$ Cat
@@
 {\chris I don't think I understand this, anyone else?}
+
+{\color{blue}{Kenny: I \emph{think} they are complaining that we use $f$ as a map of vertices and $g$ as a map of edges when we're talking about the functor $F \colon \mathsf{Set} \to \mathsf{Cat}$ on page 21, but we use $g$ as a map of vertices and $f$ as a map of edges in the two squares at the start of Section 6.1 on the previous page?}}
 
@@
 
+{\color{blue}{Kenny: They might not mean $gf$ specifically, but there are many instances where we don't use a $\circ$ for functional composition, e.g.
+when we're pushing forward a graph structure over a map $f$ of vertices towards the top of page 21.
+Do we want to use a $\circ$ or not?}}
+
 \item p3: “Using the Grothendieck construction” - maybe worth mentioning this is the “covariant” version which is different to the most common 
@@
 
+{\color{blue}{Kenny: We don't have any examples where $E$ is not an identity, but in my mind it's a functor that possibly modifies decorations, e.g.
+$F(a)$ is a category of graph structures on $a$, and $E(F(a))$ could be something like a category of possibly labeled graph structures on $a$, if that makes sense.
+Something potentially different than \emph{just} a graph structure on $a$.}}
+
 \item Theorem 2.5: F should be defined on A, not A’

### 2022-03-07 ResponseToReviews.tex
added a comment to "Response", made some changes in cospans_new.tex

@@
 
-{\color{blue}{Kenny: I think they are correct in that we don't use this extra assumption.}}
+{\kenny I think they are correct in that we don't use this extra assumption.}
 
@@
 
-{\color{blue}{Kenny: I \emph{think} they are complaining that we use $f$ as a map of vertices and $g$ as a map of edges when we're talking about the functor $F \colon \mathsf{Set} \to \mathsf{Cat}$ on page 21, but we use $g$ as a map of vertices and $f$ as a map of edges in the two squares at the start of Section 6.1 on the previous page?}}
+{\kenny I \emph{think} they are complaining that we use $f$ as a map of vertices and $g$ as a map of edges when we're talking about the functor $F \colon \mathsf{Set} \to \mathsf{Cat}$ on page 21, but we use $g$ as a map of vertices and $f$ as a map of edges in the two squares at the start of Section 6.1 on the previous page?}
+
+{\john That sounds plausible.
+Unless there's a damn good reason let's use $f$ as a map for vertices and $g$ as a map for edges, since ``vertices come before edges'' - morally the first are 0-cells, the second are 1-cells.}
 

### 2022-03-07 cospans_new.tex
added a comment to "Response", made some changes in cospans_new.tex

@@
 % in LaTeX
-% 2021/6/29 - second arxiv version
+% 2021/03/07 - dealing with referee's comments
 
@@
 \]
-where the decoration morphism $\lH(\tau)$ is defined as follows.  Thinking of $\tau$ as a natural transformation \cref{eq:taunattransf},
-in the same style of notation $\lH(\tau)$ is given by
+where the decoration morphism $\lH(\tau)$ is defined as follows.  Treating $\tau$ as a natural transformation as in \cref{eq:taunattransf}, $\lH(\tau)$ is given by
 \[
@@
 \]
+The square at right commutes strictly because $\theta$ is a natural isomorphism.
 \end{itemize}
-The square at right commutes strictly because $\theta$ is a natural isomorphism.
    \iffalse Perhaps we could generalize our construction to handle the case where $\theta$ is a pseudonatural equivalence, making this square commute up to a natural isomorphism.
@@
 
-Essentially, the above assumptions state that the fibers of the induced opfibration $U$ have finite colimits which are preserved by the reindexing 
-functors, and the induced fiberwise monoidal structure is cocartesian. Explicitly, regarding the last point, the lax monoidal 
-pseudofunctor structure $(F,\phi,\phi_0)$ gives rise to a specific symmetric monoidal structure on the fibers $F(a)$ in terms of $\phi,\phi_0$ given 
-by \cref{eq:explicitstructure1}, since $\A$ is cocartesian monoidal. We here ask that the induced pseudofunctor $F\maps \A\to\SMC$ factors through 
-$\Rex$, namely that \cref{eq:explicitstructure1} gives coproducts and an initial object in each $F(a)$.
+Essentially, the above assumptions state that the fibers of the induced opfibration $U$ have finite colimits which are preserved by the reindexing functors, and the induced fiberwise monoidal structure is cocartesian.
+Regarding the last point: the lax monoidal pseudofunctor structure $(F,\phi,\phi_0)$ gives rise to a specific symmetric monoidal structure on the fibers $F(a)$ given by \cref{eq:explicitstructure1}, since $\A$ is cocartesian monoidal, and we ask that the resulting pseudofunctor $F\maps \A \to \SMC$ factors through $\Rex$, so that \cref{eq:explicitstructure1} gives coproducts and an initial object in each $F(a)$.
 

### 2022-03-07 cospans_new.tex
changed "lax symmetric monoidal" to "symmetric monoidal" on line 2716

@@
 \end{itemize}
-The functorality of $D$ is proved in \cite[Lemma 15]{BP} while the lax symmetric monoidal stucture is given in Lemma 16 of that paper.
+The functorality of $D$ is proved in \cite[Lemma 15]{BP} while the symmetric lax monoidal stucture is given in Lemma 16 of that paper.
 
@@
 Consequently, $U$ corresponds to a pseudofunctor $F \maps \A \to \Cat$ by the inverse Grothendieck construction, as in the first part of \cref{thm:Grothendieck}.
-Furthermore, if $U$ preserves finite coproducts, $F$ acquires the structure of a lax monoidal pseudofunctor $F \maps (\A,+) \to (\Cat,\times)$ by the special case of the cocartesian monoidal Grothendieck construction discussed under \cref{lem:MonGroth}.
+Furthermore, if $U$ preserves finite coproducts, $F$ acquires the structure of a symmetric lax monoidal pseudofunctor $F \maps (\A,+) \to (\Cat,\times)$ by the special case of the cocartesian monoidal Grothendieck construction discussed under \cref{lem:MonGroth}.
 As a result, $F$ now has enough structure to induce a double category of decorated cospans $F\lCsp$ as in \cref{thm:decorated_cospans_2}.
@@
 
-A \define{lax monoidal} pseudofunctor (called \emph{weak monoidal} homomorphism in some earlier references) between monoidal bicategories $F\maps\bA\to\bB$ is a pseudofunctor equipped with pseudonatural transformations with components $\phi_{a,b}\maps Fa\otimes Fb\to F(a\otimes b)$ and $\phi_0\maps I\to FI$ along with invertible modifications for associativity and unitality with components
+A \define{lax monoidal} pseudofunctor (called \emph{weak monoidal homomorphism} in some earlier references) between monoidal bicategories $F\maps\bA\to\bB$ is a pseudofunctor equipped with pseudonatural transformations with components $\phi_{a,b}\maps Fa\otimes Fb\to F(a\otimes b)$ and $\phi_0\maps I\to FI$ along with invertible modifications for associativity and unitality with components
 \begin{equation}\label{eq:omega}

### 2022-03-08 ResponseToReviews.tex
all comments of first referee discussed, but see the one with lots of red ink.

@@
  \item Lemma 2.4: when talking about the functors $F : (A,\otimes)\to(Cat,\times)$, I think sometimes it is specified that they are lax and sometimes 
-it is 
-not. Perhaps it would be clearer to always use “lax monoidal” or to just use “monoidal” to mean lax monoidal.
+it is not. Perhaps it would be clearer to always use “lax monoidal” or to just use “monoidal” to mean lax monoidal.
 
 {\bf We have added ``lax'' at Lemma 2.4 in two occurences, and have checked the rest of the document to verify that this does not happen 
-elsewhere.}
+elsewhere.}  {\john $\checkmark$}
 
@@
 
+{\john  I find that this added text confuses me more than it helps me:
+\begin{quote}
+Essentially, the above assumptions state that the fibers of the induced opfibration $U$ have finite colimits which are preserved by the reindexing functors, and the induced fiberwise monoidal structure is cocartesian.
+Explicitly, regarding the last point: the lax monoidal pseudofunctor structure $(F,\phi,\phi_0)$ gives rise to a specific symmetric monoidal structure on the fibers $F(a)$ given by (3), since $\mathsf{A}$ is cocartesian monoidal, and we ask that the resulting pseudofunctor $F\colon \mathsf{A} \to \mathsf{SMC}$ factors through $\mathsf{Rex}$, so that (3) gives coproducts and an initial object in each $F(a)$.
+\end{quote}
+I think the referee just wanted us to change, in the statement of Theorem 4.1, the phrase
+``factors through $\mathsf{Rex}$'' to ``“factors through R : Rex $\to$ SymMonCat”, where $R$ was his name for this 2-functor, not ours!   It's not a good name for it since we have another $R$ in our
+paper.   So, I've commented out the added text and said ``factors through the above 2-functor $\mathsf{SMC} \to \mathsf{Rex}$'' --- we defined right above the theorem.}
+
 \item Proof of Lemma 4.4: there is a typo where “L then becomes left adjoint to R” should probably be “L then becomes left adjoint to U”.
 
-{\bf Done.}
+{\bf Done.}  {\john $\checkmark$}
 
@@
 
-{\bf Done.}
+{\bf Done.} {\john $\checkmark$}
 
@@
 
-{\bf Done.}
+{\bf Done.} {\john $\checkmark$}
 
-\item COVID paragraph: I appreciate the effort into explaining the applied aspect. However, claims about the software (it is “easy”, we “easily” 
-modify, we 
-“better understand”) sound too vague (is it computationally better? do we assume that the final user understands structured cospans? are we comparing 
-it to other Petri net editors?). Perhaps this paragraph could be fused as a comment to the previous one, which is already a very good justification 
-for the use of Petri nets with rates.
+\item COVID paragraph: I appreciate the effort into explaining the applied aspect.
+However, claims about the software (it is “easy”, we “easily”  modify, we “better understand”) sound too vague (is it computationally better?
+do we assume that the final user understands structured cospans?
+are we comparing  it to other Petri net editors?).
+Perhaps this paragraph could be fused as a comment to the previous one, which is already a very good justification  for the use of Petri nets with rates.
 
-\item Section 6: as a reader, I really appreciate the examples: are there more in the literature? I do not think it is necessary to go in detail over 
-each 
-one of them, but perhaps it would be useful to point to other places where they are described.
+{\bf There is now a paper detailing how this software works, so we have changed our paper
+so it simply refers to that.}   {\john $\checkmark$}
+
+\item Section 6: as a reader, I really appreciate the examples: are there more in the literature?
+I do not think it is necessary to go in detail over each one of them, but perhaps it would be useful to point to other places where they are described.
+
+{\bf We have added a word about Markov processes in Section 6.2, and with this, all the applications of structured or decorated cospans that we know of are discussed here.} {\john $\checkmark$}
 
 {\chris Second review starts here}
-\item Given the title and abstract of this paper “Structured vs Decorated Cospans” I would expect this paper to provide a judgment that structured 
-cospans 
-are strictly better than decorated cospans in all circumstances and a justification for that claim, or a detailed analysis of the pros and cons of 
-structured vs decorated cospans, some case studies in applications that show how the difference between these double categories is felt in the 
-application domain, and a some description of the tradeoffs. This paper should come with some practical advice for the applied category theorist on 
-how to choose whether to model their application with structured vs decorated cospans (...) [Conclusions section] this is a place where I would expect 
-some guidance on when an ACT practitioner should choose either structured or 
-decorated cospans depending on what mathematical structures they are formalizing within ACT.
+\item Given the title and abstract of this paper “Structured vs Decorated Cospans” I would expect this paper to provide a judgment that structured  cospans are strictly better than decorated cospans in all circumstances and a justification for that claim, or a detailed analysis of the pros and cons of
+structured vs decorated cospans, some case studies in applications that show how the difference between these double categories is felt in the application domain, and a some description of the tradeoffs.
 
-{\john That is their guess about what the paper should be about. I guess they were hoping for something like this:
-Theorem. Structured cospans are strictly better than decorated cospans in all circumstances.
-Does our abstract actually suggest that we're talking about which formalism is "better", or the "pros and cons"?
-I just checked: no, it does not.}
+{\john In fact our goal, as explained in the abstract and introduction, is to prove that the structured and decorated cospan approaches are equivalent under certain conditions, and to illustrate this result with a wide variety of examples.}
 

### 2022-03-08 cospans_new.tex
all comments of first referee discussed, but see the one with lots of red ink.

@@
 Suppose $\A$ has finite colimits and $F \maps (\A,+) \to (\Cat,\times)$ is a symmetric lax monoidal pseudofunctor. If the corresponding pseudofunctor $F \maps \A \to \SMC$ from \cref{lem:MonGroth}
- factors through $\Rex\to\SMC$, then the symmetric monoidal double categories $F\lCsp$ of decorated cospans and ${}_L\lCsp(\inta F)$ of structured 
+ factors through the above 2-functor $\Rex\to\SMC$, then the symmetric monoidal double categories $F\lCsp$ of decorated cospans and ${}_L\lCsp(\inta F)$ of structured 
 cospans are isomorphic, where $L \maps \A \to \inta F$ is a left adjoint of the induced Grothendieck opfibration $U \maps \inta F \to \A$.
@@
 For more details, see \cite[Corollary 4.7]{MV} and the related discussion.
-\fi
 
@@
 Regarding the last point: the lax monoidal pseudofunctor structure $(F,\phi,\phi_0)$ gives rise to a specific symmetric monoidal structure on the fibers $F(a)$ given by \cref{eq:explicitstructure1}, since $\A$ is cocartesian monoidal, and we ask that the resulting pseudofunctor $F\maps \A \to \SMC$ factors through $\Rex$, so that \cref{eq:explicitstructure1} gives coproducts and an initial object in each $F(a)$.
+\fi
 
@@
 Since the abstract formalism works the same way, we can be brief.
-Concrete applications of this formalism are discussed in the references.
+Concrete applications of this formalism are discussed in the above references, and in \cite{BFP} a class of Markov processes were
+also handled using this formalism, by reducing them to circuits of resistors.
 
@@
 This in turn lets us couple the SIR model to other models, and build larger models from smaller pieces.
-
-Recently Halter and Patterson \cite{HP} implemented this idea in a software tool that makes it easy to build epidemiological models using structured cospans.
-They used this to rebuild part of the COVID-19 model that the UK has been using to make policy decisions.
-The advantage of using structured or decorated cospans is that one can build complex models from smaller pieces, so one can easily add or change parts, and better understand the effects of doing this.
+Indeed, open Petri nets and the mathematics of structured cospan categories have recently been used to develop a software tool for building and manipulating epidemiological models \cite{BFMLP}.
 
@@
 
+\bibitem{BFMLP}  A.\ Baas, J.\ Fairbanks, M.\ Halter, S.\ Libkind and E.\ Patterson, An
+algebraic framework for structured epidemic modeling.   Available as \href{???}{???}
+
 \bibitem{BC} J.\ C.\ Baez and K.\ Courser, Structured cospans,  \textsl{Theory Appl.\ Categ.\ }\textbf{35} (2020), 1771--1822.   Available as \href{http://arxiv.org/abs/1911.04630}{arXiv:1911.04630}.
@@
 Springer, Berlin, 2002.
-
-\bibitem{HP} M.\ Halter and E.\ Patterson, Compositional epidemiological modeling using structured cospans, 2020.
-Available at \href{https://www.algebraicjulia.org/blog/post/2020/10/structured-cospans}{https://www.algebraicjulia.org/blog/post/2020/10/structured-cospans}.
 

### 2022-03-08 ResponseToReviews.tex
more comments added

@@
 
+{\bf The present work reviews all previous work on decorated and structured cospans in Section 6.
+As we mention, our previous paper ``Structured cospans'' fixed the errors in previous work using decorated cospans by using structured cospans instead.
+Here we describe how the new improved decorated cospans can also fix those errors.
+There may be even more ways to correct these errors, but we do not know them.}    {\john $\checkmark$}
+
  \item Lemma 2.4: when talking about the functors $F : (A,\otimes)\to(Cat,\times)$, I think sometimes it is specified that they are lax and sometimes 
@@
 {\bf There is now a paper detailing how this software works, so we have changed our paper
-so it simply refers to that.}   {\john $\checkmark$}
+so it simply refers to that.}   {\john But we still need to add an arXiv link in reference 1!  It should be on the arXiv soon.}
 

### 2022-03-08 ResponseToReviews.tex
fixed a typo

@@
 {\john  I find that this added text confuses me more than it helps me:
+\vskip 1em
 \begin{quote}
@@
 \end{quote}
+\vskip 1em
 I think the referee just wanted us to change, in the statement of Theorem 4.1, the phrase
-``factors through $\mathsf{Rex}$'' to ``“factors through R : Rex $\to$ SymMonCat”, where $R$ was his name for this 2-functor, not ours!   It's not a good name for it since we have another $R$ in our
+``factors through $\mathsf{Rex}$'' to ``“factors through $R \colon \mathsf{Rex} \to \mathsf{SMC}$, where $R$ was his name for this 2-functor, not ours!
+It's not a good name for it since we have another $R$ in our
 paper.   So, I've commented out the added text and said ``factors through the above 2-functor $\mathsf{SMC} \to \mathsf{Rex}$'' --- we defined right above the theorem.}

### 2022-03-08 ResponseToReviews.tex
some small edits

@@
 
-{\bf The present work reviews all previous work on decorated and structured cospans in Section 6.
-As we mention, our previous paper ``Structured cospans'' fixed the errors in previous work using decorated cospans by using structured cospans instead.
-Here we describe how the new improved decorated cospans can also fix those errors.
-There may be even more ways to correct these errors, but we do not know them.}    {\john $\checkmark$}
+{\bf The present work reviews all previous work on decorated and structured cospans in Section 6.  As we mention, our previous paper ``Structured 
+cospans'' fixed the errors in previous work using decorated cospans by using structured cospans instead.   Here we describe how the new improved 
+decorated cospans can also fix those errors.     There may be even more ways to correct these errors, but we do not know them.}    {\john 
+$\checkmark$}
+{\chris As was suggested by John at some point, would we perhaps want to add a sentence or two in the introduction, saying that indeed there are a 
+number of cospan articles etc. and that in the beginning of section 6 we elaborate on those?}
 
@@
 {\bf We have added ``lax'' at Lemma 2.4 in two occurences, and have checked the rest of the document to verify that this does not happen 
-elsewhere.}  {\john $\checkmark$}
+elsewhere.}  {\john $\checkmark$} {\chris $\checkmark$}
 
@@
 
+{\chris Indeed this comment refers to the functor $\mathsf{Rex} \to \mathsf{SMC}$, I also chose to disregard R for the same reasons. The paragraph 
+below existed in part later in text, and was in part expanded it according to comment 29, not this one! I think I agree with that comment in that the 
+assumptions of the theorem deserve a bit of explanation, and tried my best there but possibly did not succeed if you say it is confusing. Could we 
+revive the paragraph and explain better? I can give it another try!}
+
 \item Proof of Lemma 4.4: there is a typo where “L then becomes left adjoint to R” should probably be “L then becomes left adjoint to U”.
 
-{\bf Done.}  {\john $\checkmark$}
+{\bf Done.}  {\john $\checkmark$} {\chris $\checkmark$}
 
@@
 
-{\bf Done.} {\john $\checkmark$}
+{\bf Done.} {\john $\checkmark$} {\chris $\checkmark$}
 
@@
 
-{\bf There is now a paper detailing how this software works, so we have changed our paper
+{\bf There is now a paper detailing how this software works, so we have changed our paper (according to this suggestion)
 so it simply refers to that.}   {\john But we still need to add an arXiv link in reference 1!  It should be on the arXiv soon.}
+
+{\chris Great! The 
+hyperref link ??? opens up notes by Kenny for me, I don't know how or why. I added ``according to this suggestion'' above to reflect that we indeed 
+fused the paragraph as they suggested.}
 
@@
 
-{\bf We have added a word about Markov processes in Section 6.2, and with this, all the applications of structured or decorated cospans that we know of are discussed here.} {\john $\checkmark$}
+{\bf We have added a word about Markov processes in Section 6.2, and with this, all the applications of structured or decorated cospans that we know 
+of are discussed here.} {\john $\checkmark$} {\chris $\checkmark$}
 
@@
 
-{\bf We have added a citation to Emily Riehl's book ``Category Theory in Context'' which includes said result, above Lemma 6.1.}
+{\bf We have added a citation to Emily Riehl's book ``Category Theory in Context'' which includes said result, above Lemma 6.1.} {\chris $\checkmark$}
 
@@
 
-{\chris I don't think I understand this, anyone else?}
+{\bf At the beginning of Section 6.1, we now use $f$ as a map between vertices and $g$ as a map between edges.} {\chris $\checkmark$}
 
@@
 
-{\john That sounds plausible.
-Unless there's a damn good reason let's use $f$ as a map for vertices and $g$ as a map for edges, since ``vertices come before edges'' - morally the first are 0-cells, the second are 1-cells.}
+{\john That sounds plausible.  Unless there's a damn good reason let's use $f$ as a map for vertices and $g$ as a map for edges, since ``vertices come 
+before edges'' - morally the first are 0-cells, the second are 1-cells.}
+
+{\chris I see. Fixed, and see above.}
 
@@
 
-{\bf Done.}
+{\bf Done.} {\chris $\checkmark$}
 
@@
 {\color{blue}{Kenny: They might not mean $gf$ specifically, but there are many instances where we don't use a $\circ$ for functional composition, e.g. 
-when we're pushing forward a graph structure over a map $f$ of vertices towards the top of page 21.
-Do we want to use a $\circ$ or not?}}
+when we're pushing forward a graph structure over a map $f$ of vertices towards the top of page 21. Do we want to use a $\circ$ or not?}}
+
+{\chris Ah you are right. I don't mind, we could specify that for function composition we sometimes use concatenation!}
 

### 2022-03-08 cospans_new.tex
some small edits

@@
 
-One of the simplest kinds of network is a graph.
-For us a \define{graph} will be a pair of functions $s,t\maps E \to N$ where $E$ and $N$ are finite sets.
-We call elements of $E$ \define{edges} and elements of $N$ \define{nodes}.
-There is a category $\Graph$ where the objects are graphs and a morphism from the graph $s,t\maps E \to N$ to the graph $s',t' \maps E' \to N'$ is a pair of functions $f \maps E \to E', g \maps N \to N'$ such that these diagrams commute:
+One of the simplest kinds of network is a graph.  For us a \define{graph} will be a pair of functions $s,t\maps E \to N$ where $E$ and $N$ are finite 
+sets.   We call elements of $E$ \define{edges} and elements of $N$ \define{nodes}.  There is a category $\Graph$ where the objects are graphs and a 
+morphism from the graph $s,t\maps E \to N$ to the graph $s',t' \maps E' \to N'$ is a pair of functions $f \maps N \to N', g \maps E \to E'$ such that 
+these diagrams commute:
 \[
@@
 (A') edge node[below]{$s'$} (B')
-(A) edge node[left]{$f$} (A')
-(B) edge node[right]{$g$} (B');
+(A) edge node[left]{$g$} (A')
+(B) edge node[right]{$f$} (B');
 
@@
 (C') edge node[below]{$t'$} (D')
-(C) edge node[left]{$f$} (C')
-(D) edge node[right]{$g$} (D');
+(C) edge node[left]{$g$} (C')
+(D) edge node[right]{$f$} (D');
 \end{tikzpicture}

### 2022-03-08 ResponseToReviews.tex
few more tiny map label changes

@@
 
+{\kenny I think the reader should come to their own conclusion about which framework they should use if they are trying to decide between the two, assuming both are applicable.
+I wouldn't say that one is better than the other.
+Personally, I would rather try structured cospans first, because I would rather think about a left adjoint than a symmetric lax monoidal pseudofunctor, but other people might feel differently.}
+
 \item Given that Petri nets with structured cospans works, and Reaction Networks work, but open dynamical systems do not, I would like some more 

### 2022-03-08 cospans_new.tex
few more tiny map label changes

@@
 \[ \xymatrix{\La & E' \ar@<2.5pt>[r]^{s'} \ar@<-2.5pt>[r]_{t'} \ar[l]_{\ell'} & N'} \]
-is a pair of functions $f \maps E \to E', g \maps N \to N'$ such that these diagrams commute:
+is a pair of functions $f \maps N \to N', g \maps E \to E'$ such that these diagrams commute:
 \[
@@
 (C') edge node[below]{$t'$} (D')
-(C) edge node[left]{$f$} (C')
-(D) edge node[right]{$g$} (D');
+(C) edge node[left]{$g$} (C')
+(D) edge node[right]{$f$} (D');
 
@@
 (G) edge node[above]{$\ell$} (E)
-(G) edge node[right]{$f$} (G')
+(G) edge node[right]{$g$} (G')
 (G') edge node[below]{$\ell'$} (E);
@@
 There is a category $\Petri$ with Petri nets as objects, where a morphism from the Petri net 
-$s, t \maps T \to \N[S]$ to the Petri net $s', t' \maps T' \to \N[S']$ is a pair of functions $f \maps T \to T', g \maps S \to S'$ such that the following diagrams commute:
+$s, t \maps T \to \N[S]$ to the Petri net $s', t' \maps T' \to \N[S']$ is a pair of functions $f \maps S \to S', g \maps T \to T'$ such that the following diagrams commute:
 	\[
 	\xymatrix{ 
-		T \ar[d]_f  \ar[r]^-{s} & \N[S] \ar[d]^-{\N[g]} \\	
+		T \ar[d]_g  \ar[r]^-{s} & \N[S] \ar[d]^-{\N[f]} \\	
 		T' \ar[r]_-{s'} & \N[S'] 
@@
 	\xymatrix{ 
-		T \ar[d]_f  \ar[r]^-{t} & \N[S] \ar[d]^-{\N[g]} \\	
+		T \ar[d]_g  \ar[r]^-{t} & \N[S] \ar[d]^-{\N[f]} \\	
 		T' \ar[r]_-{t'} & \N[S'] . 
@@
 \path[->,font=\scriptsize,>=angle 90]
-(G) edge node[right]{$f$} (G')
+(G) edge node[right]{$g$} (G')
 (G) edge node[above]{$r$} (E)

### 2022-03-09 ResponseToReviews.tex
improved remarks under theorem 4.1

@@
 
+\iffalse
 {\john  I find that this added text confuses me more than it helps me:
@@
 paper.   So, I've commented out the added text and said ``factors through the above 2-functor $\mathsf{SMC} \to \mathsf{Rex}$'' --- we defined right above the theorem.}
+\fi
 
 {\chris Indeed this comment refers to the functor $\mathsf{Rex} \to \mathsf{SMC}$, I also chose to disregard R for the same reasons. The paragraph 
-below existed in part later in text, and was in part expanded it according to comment 29, not this one! I think I agree with that comment in that the 
+below existed in part later in text, and was in part expanded according to comment 29, not this one! I think I agree with that comment in that the 
 assumptions of the theorem deserve a bit of explanation, and tried my best there but possibly did not succeed if you say it is confusing. Could we 
 revive the paragraph and explain better? I can give it another try!}
+
+{\john  Okay, that makes sense.
+I put the paragraph back in and changed it a bunch: basically, I added some more steps so people who don't know what we're doing will have an easier time figuring it out.
+Does it look okay to you?}
 

### 2022-03-09 cospans_new.tex
improved remarks under theorem 4.1

@@
 \end{thm}
+
+The hypothesis of this theorem is essentially a way of asking that the fibers of the induced opfibration $U \maps \inta F \to \A$ have finite colimits which are preserved by the reindexing functors, and that the induced fiberwise monoidal structure is cocartesian.
+Expanding on this a bit:
+the fibers of $U$ are the same as the categories $F(a)$ for all $a \in \A$.
+The lax monoidal pseudofunctor structure of $F$ gives rise to a specific symmetric monoidal structure on the categories $F(a)$ given by \cref{eq:explicitstructure1}, and the hypothesis of the theorem asks that the resulting pseudofunctor $F \maps \A \to \SMC$ factors through $\Rex$.
+This implies
+that each category $F(a)$ has coproducts and an initial object, and that the resulting cocartesian structure is what makes $F(a)$ a symmetric monoidal category.
 

### 2022-03-09 ResponseToReviews.tex
changes to cospans_new and ResponsetoReviewers

@@
 
-{\bf There is now a paper detailing how this software works, so we have changed our paper (according to this suggestion)
-so it simply refers to that.}   {\john But we still need to add an arXiv link in reference 1!  It should be on the arXiv soon.}
+{\bf There is now a paper detailing how this software works, so according to this suggestion we have changed our paper so it simply refers to that other paper.}   {\john But we still need to add an arXiv link in reference 1!
+It should be on the arXiv soon.}
 
@@
 fused the paragraph as they suggested.}
+
+{\john It's weird that the line ??? opens up anything for you.  It'll go away when we get the arXiv number.}
 
@@
 
+\vskip 1em
+
 {\chris Second review starts here}
@@
 
-{\john In fact our goal, as explained in the abstract and introduction, is to prove that the structured and decorated cospan approaches are equivalent under certain conditions, and to illustrate this result with a wide variety of examples.}
+{\bf In fact our goal, as explained in the abstract and introduction, was to prove that the structured and decorated cospan approaches are equivalent under certain conditions, and to illustrate this result with a wide variety of examples.}
 
@@
 Personally, I would rather try structured cospans first, because I would rather think about a left adjoint than a symmetric lax monoidal pseudofunctor, but other people might feel differently.}
+
+{\john I agree with you, Kenny.
+I think this reviewer saw the word ``vs'' and thought we were going to let structured and decorated cospans fight it out and announce who won, like at a boxing match.
+Instead of arguing that this is not a good idea for a paper, I decided to just point out that our abstract says what our paper does, and it's something else.
+(I also agree with you that structured cospans are simpler when you can use them: that's why we invented them!)}
+
+{\john If you like the response in boldface above, please add a checkmark here.  Otherwise try to
+improve it, or something.}
+
+{\john $\checkmark$}
 
@@
 
-{\john I agree that a general result like this would be nice, but I don't have the energy to dream one up and prove it. The most we can do here is say 
-that this is worth studying.... maybe after we give the example of a decorated cospan category that's not a structured cospan category.}
+{\john Actually it's really easy to prove that presheaf categories obey the conditions of Theorem 4.1:
+given any functor $f : \mathsf{C} \to \mathsf{D}$ the left adjoint functor between presheaf categories $f_!
+: \widehat{\mathsf{C}} \to \widehat{\mathsf{D}}$ obeys the conditions of Theorems 4.1 and 4.2.
+So I think we can easily add this as a corollary, maybe right after Theorem 4.2, to get a pile of examples.
+Obvious to us, but not to everyone.
+Should I do it?}
 
@@
 semantics for reaction networks that uses structured cospans?
+
+{\bf We do not know a semantics for dynamical systems that uses structured cospans; to find one would
+require getting around the result at the end of Section 6.}
 
@@
 
+{\john He thought we were being dismissive because he didn't know that the ``tricks'' were all things I'd done myself!
+If he looked at [1, Section 5] he'd see it was me coming up with a bunch of tricks to try to save the decorated cospan category of open graphs, and then Kenny and me explaining why this tricks don't work.
+So maybe I should just delete ``despite all the tricks one might try''.
+Sound good?}
+
 \item pg. 3: “Many of the flawed applications of decorated cospans have been fixed using structured cospans.” This dismisses the work of other 
@@
 we should point to that.}
-{\john I don't like referees who say what the goal of my paper "should be". The goal of this paper is clearly to set up a clear relation between 
-structured and decorated cospans, and I hope we make that clear already in the abstract!}
+
+{\john I feel like just leaving out this part in our reply: ``The goal of this paper should be to illustrate to an applied category theory audience the differences between 
+decorated and structured cospans. Referring back to previous work of the authors to make that point does not provide value.''}
 
@@
 {\bf We have added a citation to Emily Riehl's book ``Category Theory in Context'' which includes said result, above Lemma 6.1.} {\chris $\checkmark$}
+
+{\john I have also changed ``well-known'' to ``known'', which is more polite to people who don't know it.} {\john $\checkmark$}
 
@@
 
-{\bf At the beginning of Section 6.1, we now use $f$ as a map between vertices and $g$ as a map between edges.} {\chris $\checkmark$}
+{\bf At the beginning of Section 6.1, we now use $f$ as a map between vertices and $g$ as a map between edges.}
 
+{\chris $\checkmark$} {\john $\checkmark$}
+
+\iffalse
 {\kenny I \emph{think} they are complaining that we use $f$ as a map of vertices and $g$ as a map of edges when we're talking about the functor $F \colon \mathsf{Set} \to \mathsf{Cat}$ on page 21, but we use $g$ as a map of vertices and $f$ as a map of edges in the two squares at the start of Section 6.1 on the previous page?}
@@
 {\chris I see. Fixed, and see above.}
+\fi
 
@@
 
-{\bf Done.} {\chris $\checkmark$}
+{\bf We have done this}
+
+{\chris $\checkmark$} {\john $\checkmark$}
 
@@
 
+{\john There were a couple places where I put in $\circ$ --- that's what the referee is really complaining
+about here.
+Almost always we don't.
+I could remove the $\circ$s.
+There was a reason I put them in: there are some places where writing a composite using plain old concatenation looks weird to me.
+But I don't think it's that big a deal.}
+
 \item p3: “Using the Grothendieck construction” - maybe worth mentioning this is the “covariant” version which is different to the most common 
@@
 distinction to 
-Fong’s original definition
+Fong's original definition.
+
+{\bf  We have added a remark about this in the definition.}   \john{$\checkmark$}
 
 {\chris Maybe just specify in the statement of 2.1, definitely keep $\in$ sign in all diagrams below!}
+
+{\john It's hard to tweak the statement, since we're really trying to introduce the notation of decorations in maps of structured cospans here!
+So I've added something about this \emph{after} the statement of Theorem 2.1.
+See if you like it:
+
+\begin{quote} 
+Note that the decoration $s \in F(m)$ is now an object in the category $F(m)$, not an element of a set as in Fong's original approach. 
+\end{quote}
+
+}
 

### 2022-03-09 cospans_new.tex
changes to cospans_new and ResponsetoReviewers

@@
 
-Vertical composition in $F\lCsp$ is done using composition in $\A$.  The horizontal composite of $F$-decorated cospans
+Note that the decoration $s \in F(m)$ is now an object in the category $F(m)$, not an element of a set as in Fong's original approach.
+Vertical composition in $F\lCsp$ is done using composition in $\A$.
+The horizontal composite of $F$-decorated cospans
 \[ \left(a\to m\leftarrow b,s\in F(m)\right), \qquad \left(b\to n\leftarrow c,t\in F(n)\right)\] 
@@
 This in turn lets us couple the SIR model to other models, and build larger models from smaller pieces.
-Indeed, open Petri nets and the mathematics of structured cospan categories have recently been used to develop a software tool for building and manipulating epidemiological models \cite{BFMLP}.
+Indeed, a group of researchers has recently used open Petri nets and the mathematics of structured cospans in their software tool for building and manipulating epidemiological models \cite{BFMLP}.
 
@@
 We then obtain an isomorphism between decorated and structured cospan double categories, $F \lCsp \cong {}_L \lCsp(\X)$.
-We now show that in the case at hand, where $F = D$, the opfibration $U$ does \emph{not} have a left adjoint.
-Thus, the conditions of \cref{thm:equiv} do not hold in this case: $F$ does not factor through $\Rex$.
+We now show that in the case at hand, where $F = D$ is the functor sending each finite set $S$ to the set of dynamical systems on $\R^S$, the opfibration $U$ does \emph{not} have a left adjoint.
+Thus, the conditions of \cref{thm:equiv} cannot hold in this case: $F$ does not factor through $\Rex$.
 
@@
 
-To show that $U$ does not have a left adjoint, we use the following well-known result \cite[Lemma 4.6.1]{Riehl}:
+To show that $U$ does not have a left adjoint, we use a known result \cite[Lemma 4.6.1]{Riehl}:
 \begin{lem} \label{lem:initial}

### 2022-03-09 ResponseToReviews.tex
some comments

@@
 
-{\john  Okay, that makes sense.
-I put the paragraph back in and changed it a bunch: basically, I added some more steps so people who don't know what we're doing will have an easier time figuring it out.
-Does it look okay to you?}
+{\john  Okay, that makes sense.   I put the paragraph back in and changed it a bunch: basically, I added some more steps so people who don't know what 
+we're doing will have an easier time figuring it out.   Does it look okay to you?}
+
+{\chris Yes it does, thanks! Although in my mind, it kinda goes the opposite way: e.g. the already induced monoidal product on the fibers ends up 
+having the universal property of a coproduct for example. Possibly just overthinking and getting mixed up with words.}
 
@@
 
-{\chris Great! The 
-hyperref link ??? opens up notes by Kenny for me, I don't know how or why. I added ``according to this suggestion'' above to reflect that we indeed 
-fused the paragraph as they suggested.}
+%{\chris Great! The 
+%hyperref link ??? opens up notes by Kenny for me, I don't know how or why.}
 
-{\john It's weird that the line ??? opens up anything for you.  It'll go away when we get the arXiv number.}
+%{\john It's weird that the line ??? opens up anything for you.  It'll go away when we get the arXiv number.} Indeed!
 
@@
 \item Given the title and abstract of this paper “Structured vs Decorated Cospans” I would expect this paper to provide a judgment that structured  cospans are strictly better than decorated cospans in all circumstances and a justification for that claim, or a detailed analysis of the pros and cons of
-structured vs decorated cospans, some case studies in applications that show how the difference between these double categories is felt in the application domain, and a some description of the tradeoffs.
+structured vs decorated cospans, some case studies in applications that show how the difference between these double categories is felt in the 
+application domain, and a some description of the tradeoffs. This paper should come with some practical advice for the applied category theorist on 
+how to choose whether to model their application with structured vs decorated cospans. {THE LAST SENTENCE IS NEWLY COPIED FROM REVIEW, WE CAN ERASE 
+IF NOT CONVENIENT}
 
@@
 
+{\chris I agree with both, and also I like the boldface above. I could add ``Those examples should serve as a guide for other similar applications, 
+whereas new applications would require exploring which approach works best, for example if a left adjoint (to start off with structured cospans) or a 
+lax monoidal pseudofunctor (to start off with decorated cospans) is available. We do not make a stand that either is strictly better.'' In fact, we 
+could add something soft along those lines somewhere in the introduction to satisfy the reviewer, if we like.}
+
 \item Given that Petri nets with structured cospans works, and Reaction Networks work, but open dynamical systems do not, I would like some more 
@@
 Should I do it?}
+
+{\chris Sounds like a great idea to me!! I was also a bit scared to go into this when I first saw it, but I kinda thought morally we should, and now 
+it looks like it won't be a disaster, and in fact a very fruitful result!! So yes please, do it and let me know what I can do to help except 
+proofread it.}
+
+{\chris Also perhaps we should add those references they provide somewhere.}
 
@@
 
-{\bf We have added a citation to Emily Riehl's book ``Category Theory in Context'' which includes said result, above Lemma 6.1.} {\chris $\checkmark$}
+{\bf We have added a citation to Emily Riehl's book ``Category Theory in Context'' which includes said result, above Lemma 6.1.}
 
-{\john I have also changed ``well-known'' to ``known'', which is more polite to people who don't know it.} {\john $\checkmark$}
+%{\john I have also changed ``well-known'' to ``known'', which is more polite to people who don't know it.} {\chris Good!}
+
+{\john $\checkmark$} {\chris $\checkmark$}
 
@@
 
-{\bf At the beginning of Section 6.1, we now use $f$ as a map between vertices and $g$ as a map between edges.}
+{\bf At the beginning of Section 6.1, as well as in Sections 6.2 and 6.3, we now use $f$ as a map between vertices and $g$ as a map 
+between edges.}
 
 {\chris $\checkmark$} {\john $\checkmark$}
+
+{\chris Added a few more places where Kenny spotted these mistakes.}
 
@@
 
-{\bf We have done this}
+{\bf Done.}
 
@@
 
-{\bf  We have added a remark about this in the definition.}   \john{$\checkmark$}
+{\bf  We have added a remark about this in the definition.}   {\john $\checkmark$} {\chris $\checkmark$}
 
@@
 
-{\john It's hard to tweak the statement, since we're really trying to introduce the notation of decorations in maps of structured cospans here!
-So I've added something about this \emph{after} the statement of Theorem 2.1.
-See if you like it:
-
+{\john It's hard to tweak the statement, since we're really trying to introduce the notation of decorations in maps of structured cospans here!    So 
+I've added something about this \emph{after} the statement of Theorem 2.1.  See if you like it:
 \begin{quote} 
 Note that the decoration $s \in F(m)$ is now an object in the category $F(m)$, not an element of a set as in Fong's original approach. 
-\end{quote}
+\end{quote}}
 
-}
+{\chris Looks good!}
 

### 2022-03-09 ResponseToReviews.tex
a bit more

@@
 
+{\chris By the way, there is this sentence ''However, it should be clear by now that so
+far, in cases where either structured or decorated cospans can be used, structured cospans are simpler. '' in section 6. Perhaps we could even imply 
+that somewhere in the intro as well?}
+
 \item Given that Petri nets with structured cospans works, and Reaction Networks work, but open dynamical systems do not, I would like some more 
@@
 
+{\chris Should we refer to which result we are talking about? Also, I am a bit confused about the question and answer. I thought reaction networks 
+can be described in both ways?}
+
 \item The development of the AlgebraicPetri software system is credited to Halter and Patterson based on a blog post. The correct citation is to the 
@@
 in a blog article. But it'd be good to add a reference to the repository.}
+
+{\chris I added the reference but looks a bit funny, edit at will. Did not add any text.}
 
@@
 
-{\chris Perhaps merge this with point 16 and possibly others, and after we do something, write a common response!}
+{\bf We removed the part of the sentence ``despite all the tricks one might try'' according to this suggestion. In [3, Section 5], these attempts are 
+explained in detail, and we find them of value because the diligent reader may in fact come up with some of these for fixing the problem.}
 
-{\john He thought we were being dismissive because he didn't know that the ``tricks'' were all things I'd done myself!
-If he looked at [1, Section 5] he'd see it was me coming up with a bunch of tricks to try to save the decorated cospan category of open graphs, and then Kenny and me explaining why this tricks don't work.
-So maybe I should just delete ``despite all the tricks one might try''.
-Sound good?}
+{\john He thought we were being dismissive because he didn't know that the ``tricks'' were all things I'd done myself!  If he looked at [1, Section 5] 
+he'd see it was me coming up with a bunch of tricks to try to save the decorated cospan category of open graphs, and then Kenny and me explaining why 
+this tricks don't work.  So maybe I should just delete ``despite all the tricks one might try''.  Sound good?}
+
+{\chris Sounds good to me! See above, amend at will.}
 
@@
 using the decorated cospan approach as flawed. The alleged flaw should be made more precise. What about the decorated cospan approach is inferior to 
-the structured cospan approach? The goal of this paper should be to illustrate to an applied category theory audience the differences between 
-decorated and structured cospans. Referring back to previous work of the authors to make that point does not provide value.
+the structured cospan approach? 
+%The goal of this paper should be to illustrate to an applied category theory audience the differences between 
+%decorated and structured cospans. Referring back to previous work of the authors to make that point does not provide value.
 
@@
 decorated and structured cospans. Referring back to previous work of the authors to make that point does not provide value.''}
+
+{\chris Right, done. About our answer here, we could politely tell them that the problem is simply that they are wrong! And perhaps, in 
+text amend that sentence to ``Many of the flawed applications of decorated cospans, \emph{like the open graph one described above},...'' because we 
+do actually say what the flaw is there, correct? I don't see where we describe flaws in Section 6.}
 
@@
 
-{\chris Merge with at least 13.}
+{\chris If I am not wrong, the paragraph cited here IS the explanation of the problem, perhaps in application terms rather than in theory terms. 
+Consider perhaps adding one sentence along the lines suggested?}
 
@@
 
-{\bf We have moved the natural isomorphism triangle as equation (1) in the statement of Theorem 2.1, and we have referred to it at page 10.}
+{\bf We have moved the natural isomorphism triangle as equation (1) in the statement of Theorem 2.1, and we have referred to it at page 10.} {\chris 
+$\checkmark$}
 
@@
 {\kenny I think they are correct in that we don't use this extra assumption.}
+
+{\chris I have a vague feeling that we discussed something similar a long time ago, but I do not remember the context at all. Perhaps it was an 
+identity then? In any case, if we don't actually use it then we should make it into a transformation.}
 
@@
 
+{\bf We believe that it is hard to analyze the examples (even the motivating one of open graphs) without having laid all relevant theory. Also, 
+the comparison between the two descriptions -- prominent in Section 6.1 -- would then not be possible to illustrate. In order to 
+better direct the reader to the applications, we added one sentence at each introductory paragraph of Sections 2 and 3 that point to Section 6 for 
+concrete examples.}
+
 {\john
@@
 hand.}
+
+{\chris I agree. How does the above boldface sound?}
 
@@
 {\john There were a couple places where I put in $\circ$ --- that's what the referee is really complaining
-about here.
-Almost always we don't.
-I could remove the $\circ$s.
-There was a reason I put them in: there are some places where writing a composite using plain old concatenation looks weird to me.
-But I don't think it's that big a deal.}
+about here.  Almost always we don't.  I could remove the $\circ$s.  There was a reason I put them in: there are some places where writing a composite 
+using plain old concatenation looks weird to me.   But I don't think it's that big a deal.}
+
+{\chris By searching our paper, I find $\circ$ in many places that should stay in my opinion, for composition of things that are not functions 
+necessarily, and maybe only a couple for functions namely towards the end of 6.4. I also don't think it's a big deal.}
 
@@
 {\color{blue}{Kenny: We don't have any examples where $E$ is not an identity, but in my mind it's a functor that possibly modifies decorations, e.g. 
-$F(a)$ is a category of graph structures on $a$, and $E(F(a))$ could be something like a category of possibly labeled graph structures on $a$, if that makes sense.
-Something potentially different than \emph{just} a graph structure on $a$.}}
+$F(a)$ is a category of graph structures on $a$, and $E(F(a))$ could be something like a category of possibly labeled graph structures on $a$, if that 
+makes sense. Something potentially different than \emph{just} a graph structure on $a$.}}
+
+{\chris Right! We can perhaps add a sentence to this end, saying that although we only use E as an identity, someone could need to change decorations 
+for some application?}
 
@@
 {\bf We have added a paragraph right below the statement of Theorem 4.1, clarifying its assumptions as suggested, which also incorporates an 
-explanatory paragraph previously located under Corollary 4.3.}
+explanatory paragraph previously located under Corollary 4.3.} {\chris $\checkmark$}
 

### 2022-03-09 cospans_new.tex
a bit more

@@
 But this hope is doomed, for reasons painstakingly explained in \cite[Section 5]{BC}.
-There is really a \emph{category} of graphs with $m$ as their set of nodes---and surprisingly, trying to treat this category as a mere set does not work, despite all the tricks one might try.
+There is really a \emph{category} of graphs with $m$ as their set of nodes---and surprisingly, trying to treat this category as a mere set does not 
+work.
 
@@
 In this section we build symmetric monoidal double categories of decorated cospans, and then study the functoriality of this construction.   
-\cref{thm:decorated_cospans_1} explains how to construct a double category of decorated cospans from a lax monoidal pseudofunctor $F \maps (\A,+) \to (\Cat, \times)$ whenever $\A$ has finite colimits.
-\cref{thm:decorated_cospans_2} gives conditions under which this double category is symmetric monoidal.
-These results build on earlier work of Fong \cite{Fong}, and we recommend his thesis for intuitive explanations of the fundamental ideas \cite{FongThesis}.
-
-In all that follows, when we say a category `has finite colimits' we mean it is equipped with a choice of colimit for every finite diagram.
-Thus, if $\A$ has finite colimits it gives a cocartesian monoidal category $(\A,+)$: that is, a symmetric monoidal category where the monoidal structure is given by the chosen binary coproducts and initial object.
-However, when we say a functor `preserves finite colimits', it need only do this up to canonical isomorphism, unless otherwise specified.
-We recall the concept of lax monoidal pseudofunctor in \cref{subsec:bicats}.
+\cref{thm:decorated_cospans_1} explains how to construct a double category of decorated cospans from a lax monoidal pseudofunctor $F \maps (\A,+) \to 
+(\Cat, \times)$ whenever $\A$ has finite colimits.  \cref{thm:decorated_cospans_2} gives conditions under which this double category is symmetric 
+monoidal.   These results build on earlier work of Fong \cite{Fong}, and we recommend his thesis for intuitive explanations of the fundamental ideas 
+\cite{FongThesis}. For concrete examples of the structures that follow, we refer the reader to \cref{Applications}.
+
+In all that follows, when we say a category `has finite colimits' we mean it is equipped with a choice of colimit for every finite diagram.   Thus, if 
+$\A$ has finite colimits it gives a cocartesian monoidal category $(\A,+)$: that is, a symmetric monoidal category where the monoidal structure is 
+given by the chosen binary coproducts and initial object.   However, when we say a functor `preserves finite colimits', it need only do this up to 
+canonical isomorphism, unless otherwise specified.   We recall the concept of lax monoidal pseudofunctor in \cref{subsec:bicats}.
 
@@
 Structured cospans are an alternative approach to equipping the apex of a cospan with 
-extra data \cite{BC}.
-Here we recall this formalism and give a new construction of the double category of structured cospans that clarifies their relation to decorated cospans.
-This new construction again uses Shulman's \cref{lem:shulman}.
+extra data \cite{BC}.    Here we recall this formalism and give a new construction of the double category of structured cospans that clarifies their 
+relation to decorated cospans.   This new construction again uses Shulman's \cref{lem:shulman}. For concrete examples of this formalism, see 
+\cref{Applications}.
 
@@
 
+\bibitem{AP} AlgebraicPetri team, Github repository. Available as 
+\href{https://github.com/AlgebraicJulia/AlgebraicPetri.jl}{AlgebraicPetri.jl}.
+
 \bibitem{BFMLP}  A.\ Baas, J.\ Fairbanks, M.\ Halter, S.\ Libkind and E.\ Patterson, An

### 2022-03-09 ResponseToReviews.tex
Only checks and comments in response file

@@
 {\bf We have added ``lax'' at Lemma 2.4 in two occurences, and have checked the rest of the document to verify that this does not happen 
-elsewhere.}  {\john $\checkmark$} {\chris $\checkmark$}
+elsewhere.}  {\john $\checkmark$} {\chris $\checkmark$} {\kenny $\checkmark$}
 
@@
 
-{\bf Done.}  {\john $\checkmark$} {\chris $\checkmark$}
+{\bf Done.}  {\john $\checkmark$} {\chris $\checkmark$} {\kenny $\checkmark$}
 
@@
 
-{\bf Done.} {\john $\checkmark$} {\chris $\checkmark$}
+{\bf Done.} {\john $\checkmark$} {\chris $\checkmark$} {\kenny $\checkmark$}
 
@@
 {\bf We have added a word about Markov processes in Section 6.2, and with this, all the applications of structured or decorated cospans that we know 
-of are discussed here.} {\john $\checkmark$} {\chris $\checkmark$}
+of are discussed here.} {\john $\checkmark$} {\chris $\checkmark$} {\kenny $\checkmark$}
 
@@
 that somewhere in the intro as well?}
+
+{\kenny The boldface looks good to me, but I also like Christina's suggestions above if we really want to make an effort to appease this referee. I'm fine either way on this.}
+
+{\kenny $\checkmark$}
 
@@
 
+{\kenny Sounds good.}
+
 \item pg. 3: “Many of the flawed applications of decorated cospans have been fixed using structured cospans.” This dismisses the work of other 
@@
 
-{\john $\checkmark$} {\chris $\checkmark$}
+{\john $\checkmark$} {\chris $\checkmark$} {\kenny $\checkmark$}
 
@@
 
+{\kenny Yes, originally it was an identity.
+Structured cospans has similar squares for its maps, but those ones are required to be invertible.
+In my thesis, I was going to try to come up with a recipe for turning those squares into these ones, so I made these ones invertible, too, but never actually got around to this.}
+
 \item p. 21, definition of F: Set $\to$ Cat
@@
 
-{\chris $\checkmark$} {\john $\checkmark$}
+{\chris $\checkmark$} {\john $\checkmark$} {\kenny  $\checkmark$}
 
 {\chris Added a few more places where Kenny spotted these mistakes.}
+
+{\kenny Species and transitions are analogous to vertices and edges, so those maps were also changed to $f$s and $g$s, respectively.}
 
@@
 
-{\chris $\checkmark$} {\john $\checkmark$}
+{\chris $\checkmark$} {\john $\checkmark$}  {\kenny $\checkmark$}
 
@@
 {\chris I agree. How does the above boldface sound?}
+
+{\kenny Agreed about keeping the examples together. The boldface looks good to me.}
 
@@
 
-{\bf  We have added a remark about this in the definition.}   {\john $\checkmark$} {\chris $\checkmark$}
+{\bf  We have added a remark about this in the definition.}   {\john $\checkmark$} {\chris $\checkmark$} {\kenny $\checkmark$}
 
@@
 
+{\kenny Sure, maybe sometime before the official statement of the Theorem when we're describing how the double functor $\mathbb{H}$ is defined?}
+
 \item Theorem 2.5: F should be defined on A, not A’
 
-{\bf Done.} {\chris $\checkmark$}
+{\bf Done.} {\chris $\checkmark$} {\kenny $\checkmark$}
 
@@
 {\bf We have added a paragraph right below the statement of Theorem 4.1, clarifying its assumptions as suggested, which also incorporates an 
-explanatory paragraph previously located under Corollary 4.3.} {\chris $\checkmark$}
+explanatory paragraph previously located under Corollary 4.3.} {\chris $\checkmark$} {\kenny $\checkmark$}
 

### 2022-03-10 ResponseToReviews.tex
a few comments

@@
 
-{\kenny Yes, originally it was an identity.
-Structured cospans has similar squares for its maps, but those ones are required to be invertible.
-In my thesis, I was going to try to come up with a recipe for turning those squares into these ones, so I made these ones invertible, too, but never actually got around to this.}
+{\kenny Yes, originally it was an identity. Structured cospans has similar squares for its maps, but those ones are required to be invertible. In my 
+thesis, I was going to try to come up with a recipe for turning those squares into these ones, so I made these ones invertible, too, but never 
+actually got around to this.}
+
+{\chris I see! So for maps of structured cospans, invertibility is actually essential?}
 
@@
 {\kenny Species and transitions are analogous to vertices and edges, so those maps were also changed to $f$s and $g$s, respectively.}
+
+{\chris Sure, are those in 6.4? As in, are there sections missing from the response sentence above?}
 
@@
 
-{\chris Maybe just specify in the statement of 2.1, definitely keep $\in$ sign in all diagrams below!}
+%{\chris Maybe just specify in the statement of 2.1, definitely keep $\in$ sign in all diagrams below!}
 
-{\john It's hard to tweak the statement, since we're really trying to introduce the notation of decorations in maps of structured cospans here!    So 
-I've added something about this \emph{after} the statement of Theorem 2.1.  See if you like it:
-\begin{quote} 
-Note that the decoration $s \in F(m)$ is now an object in the category $F(m)$, not an element of a set as in Fong's original approach. 
-\end{quote}}
+%{\john It's hard to tweak the statement, since we're really trying to introduce the notation of decorations in maps of structured cospans here!    
+%So 
+%I've added something about this \emph{after} the statement of Theorem 2.1.  See if you like it:
+%\begin{quote} 
+%Note that the decoration $s \in F(m)$ is now an object in the category $F(m)$, not an element of a set as in Fong's original approach. 
+%\end{quote}}
 
-{\chris Looks good!}
+%{\chris Looks good!}
 
@@
 {\kenny Sure, maybe sometime before the official statement of the Theorem when we're describing how the double functor $\mathbb{H}$ is defined?}
+
+{\chris Sounds good to me!}
 

### 2022-03-10 ResponseToReviews.tex
tiny
Few more comments in response file

@@
 
+{\kenny I'm kinda' confused by the question, too, due to its wording.
+Based on what Dr.
+Baez said in response, I think they might have meant dynamical systems instead of reaction networks in their last sentence.
+They even say earlier in their comment that the frameworks are isomorphic for reaction networks.}
+
 \item The development of the AlgebraicPetri software system is credited to Halter and Patterson based on a blog post. The correct citation is to the 
@@
 
+{\kenny It looks like we loosely mention what the problem is on page 2, but we already explained (in detail) what the problems are in \emph{Structured cospans}.
+I don't see why we can't just point the reader that wants to see what those problems are to that paper.
+I don't think we explain any flaws in Section 6; only use both frameworks and compare them.}
+
 \item pg. 27: To show that U does not have a left adjoint, we use the following well-known result. For readers of the TAC paper previously cited, 
@@
 
+{\kenny This seems similar to comment 14 above. So that's two people that want to know more about what the flaws are with the original decorated cospans but don't feel like opening our other paper...}
+
 \item p. 4, following statement of Thm 2.1.
@@
 {\bf We have moved the natural isomorphism triangle as equation (1) in the statement of Theorem 2.1, and we have referred to it at page 10.} {\chris 
-$\checkmark$}
+$\checkmark$} {\kenny $\checkmark$}
 
@@
 
+{\kenny Yep, we needed certain maps $L' F \Rightarrow F' L$ (using structured cospan letters) to be invertible.
+We also built those maps by hand, though, and here, we're using Shulman's mystical machine to build these ones.
+I'm not sure what happens or is required when building maps of structured cospans using Shulman's machine...}
+
 \item p. 21, definition of F: Set $\to$ Cat
@@
 
-{\bf At the beginning of Section 6.1, as well as in Sections 6.2 and 6.3, we now use $f$ as a map between vertices and $g$ as a map 
+{\bf At the beginning of Section 6.1, as well as in Sections 6.2, 6.3 and 6.4, we now use $f$ as a map between vertices and $g$ as a map 
 between edges.}
@@
 {\chris Sure, are those in 6.4? As in, are there sections missing from the response sentence above?}
+
+{\kenny Yes, one map did get changed in Section 6.4. Good catch.}
 
@@
 structured cospans can be established?
+
+{\chris This looks similar to comment 30.}
 
@@
 
+{\kenny Agree with Christina.}
+
 \item Theorem 2.1: Maybe worth saying explicitly that s is an object of the category F(m) rather than using $\in$, since this is exactly the 
@@
 double category or bicategory, but perhaps it would yield the same 1-category
+
+{\chris This looks similar to comment 20.}
 \end{enumerate}

### 2022-03-10 cospans_new.tex
changed "natural iso" to "natural transformation" in 3 places on page 26

--- 2022-03-09 cospans_new.tex
@@
 \] 
-Here $\theta$ is a monoidal natural isomorphism given as follows.  For any finite set $S$, $\theta_S \maps F(S) \to D(S)$ maps any Petri nets with rates 
+Here $\theta$ is a monoidal natural transformation given as follows.  For any finite set $S$, $\theta_S \maps F(S) \to D(S)$ maps any Petri nets with rates 
 \[   \xymatrix{ (0,\infty) & T \ar[l]_-r \ar@<-.5ex>[r]_-t \ar@<.5ex>[r]^-s & \N[S] }\]
@@
 and we think of $t(\tau), s(\tau) \in \N[S]$ as vectors in $\R^S$.
-This formula is explained in the paper with Pollard, where it is also shown that $\theta$ defines a monoidal natural isomorphism between functors to $(\Set,\times)$ \cite[Theorem 18]{BP}.
-As such, it automatically becomes a monoidal natural isomorphism between the functors $F, D \maps (\Fin\Set,+) \to (\Cat,\times)$.
+This formula is explained in the paper with Pollard, where it is also shown that $\theta$ defines a monoidal natural transformation between functors to $(\Set,\times)$ \cite[Theorem 18]{BP}.
+As such, it automatically becomes a monoidal natural transformation between the functors $F, D \maps (\Fin\Set,+) \to (\Cat,\times)$.
 Thus, it defines a symmetric monoidal double functor $\graysquare \maps F \lCsp \to D \lCsp$.

### 2022-03-10 ResponseToReviews.tex
changed theta to natural TRANSFORMATION in 2 places

@@
 \usepackage{stackrel}
+
+% math symbols
+
+\newcommand*{\graysquare}{\textcolor{lightgray}{\blacksquare}}
+
+\newcommand{\double}[1]{\mathbf{\mathbb #1}}
+\newcommand{\lCsp}{\double{Csp}}
+\newcommand{\lCospan}{\double{Cospan}}
+\newcommand{\lOpen}{\double{Open}}
+\newcommand{\Fr}{\double{Fr}}
+\newcommand{\lA}{\double{A}}
+\newcommand{\lB}{\double{B}}
+\newcommand{\lC}{\double{C}}
+\newcommand{\lD}{\double{D}}
+\newcommand{\lE}{\double{E}}
+\newcommand{\lF}{\double{F}}
+\newcommand{\lG}{\double{G}}
+\newcommand{\lH}{\double{H}}
+\newcommand{\lR}{\double{R}}
+\newcommand{\lX}{\double{X}}
+\newcommand{\lY}{\double{Y}}
 
@@
 cospans'' fixed the errors in previous work using decorated cospans by using structured cospans instead.   Here we describe how the new improved 
-decorated cospans can also fix those errors.     There may be even more ways to correct these errors, but we do not know them.}    {\john 
-$\checkmark$}
+decorated cospans can also fix those errors.     There may be even more ways to correct these errors, but we do not know them.}
+
 {\chris As was suggested by John at some point, would we perhaps want to add a sentence or two in the introduction, saying that indeed there are a 
@@
 
- \item Lemma 2.4: when talking about the functors $F : (A,\otimes)\to(Cat,\times)$, I think sometimes it is specified that they are lax and sometimes 
+ \item Lemma 2.4: when talking about the functors $F : (\mathsf{A},\otimes)\to(\mathsf{Cat},\times)$, I think sometimes it is specified that they are lax and sometimes 
 it is not. Perhaps it would be clearer to always use “lax monoidal” or to just use “monoidal” to mean lax monoidal.
@@
 
-Does the natural transformation $\theta$: EF $\Rightarrow$ F’ H have to be a natural isomorphism? Quite possibly I missed something, but I don’t see 
-where in 
+Does the natural transformation $\theta \colon EF \Rightarrow F’ H$ have to be a natural isomorphism? Quite possibly I missed something, but I don’t see where in 
 the following proofs that assumption is used.
+
+{\bf We thank the referee for catching this important mistake!   It does not need to be an isomorphism.
+In fact, in Section 6 we construct a double functor
+\[      \graysquare \colon F \lCsp \to D \lCsp \]
+sending any open Petri net with rates to its corresponding open dynamical system, and we do this
+using a monoidal natural transformation $\theta$ that is \emph{not} an isomorphism.  We had mistakenly
+written that it was; we've fixed this now.}
 
@@
 I'm not sure what happens or is required when building maps of structured cospans using Shulman's machine...}
+
+{\john  As Christina pointed out on Zulip, the $\theta : EF \Rightarrow F'H$ on page 26, where we are
+constructing a map from open Petri nets with rates to open dynamical systems, is \emph{not} an
+isomorphism.  I changed ``natural isomorphism'' to ``natural transformation'' at three points on page 26 --- 
+{\bf please help make sure we catch them all!}
+
+Also, I'd better change the remark about  $\theta: EF \Rightarrow F'H$  on page 9, and
+ in the statement of Theorem 2.5 --- these are two cases where we called it a ``natural 
+isomorphism''.    I'll do this now: I'll change it to a ``natural transformation''.
+
+I've thanked the referee profusely for catching this problem --- check out my response in boldface
+above, and if you're happy, we can check this one off!}
 

### 2022-03-10 cospans_new.tex
updated date
changed theta to natural TRANSFORMATION in 2 places

@@
 % in LaTeX
-% 2021/03/07 - dealing with referee's comments
+% 2021/03/10 - dealing with referee's comments
 
@@
 \item a lax monoidal pseudofunctor $(E,\phi,\phi_0) \maps \Cat \to \Cat$, 
-\item a natural isomorphism $\theta \maps EF \Rightarrow F'H$: 
+\item a natural transformation $\theta \maps EF \Rightarrow F'H$: 
 \[
@@
 (\Cat,\times)$, a finite colimit preserving functor $H \maps \A \to \A'$, a lax monoidal pseudofunctor $E \maps (\Cat,\times) \to (\Cat,\times)$ and 
-a monoidal natural isomorphism $\theta$ as in the following diagram:
+a monoidal natural transformation $\theta$ as in the following diagram:
 \[

### 2022-03-10 ResponseToReviews.tex
more changes

@@
 sending any open Petri net with rates to its corresponding open dynamical system, and we do this
-using a monoidal natural transformation $\theta$ that is \emph{not} an isomorphism.  We had mistakenly
-written that it was; we've fixed this now.}
+using a monoidal natural transformation $\theta$ that is \emph{not} an isomorphism.  We had mistakenly written that it was; we have fixed this now.}   {\john: $\checkmark$}
 
@@
 
+{\bf That's a great question.   We do not know how to construct such a category, but the referee
+is correct in suggesting that doing it might give a structured cospan category of open dynamical
+systems.
+
+As the referee noticed, the ``old, flawed'' construction of 
+decorated cospans from a lax monoidal functor $D \colon (\mathsf{FinSet},+) \to 
+\mathsf{Set}, \times) $ agrees with the new one using a lax monoidal pseudofunctor  $D \colon (\mathsf{FinSet},+) \to \mathsf{Cat}, \times) $ when the categories $D(S)$ are discrete,
+and thus essentially sets.   Thus, our use of this construction amounts to working with a
+set $D(S)$, rather than a full-fledged category, of dynamical systems on the finite set $S$.
+
+In the example near the end of Section 6, the category $\int \! D$ can be seen as a category
+of dynamical systems.   It is not discrete, but it does not have an initial object, as we'd
+need to get a structured cospan
+category that matches our decorated cospan category.
+
+So, giving the category of dynamical systems more morphisms sounds like a good idea. We will continue thinking about it.}  { \john \checkmark}
+
 {\chris This looks similar to comment 30.}
+
+{\john Yes, but it's worth a separate answer.   I wrote an answer above.  See if you like it.  }
 
@@
 
-\item Theorem 2.5: F should be defined on A, not A’
+\item Theorem 2.5: $F$ should be defined on $\mathsf{A}$, not $\mathsf{A}'$.
 
-{\bf Done.} {\chris $\checkmark$} {\kenny $\checkmark$}
+{\bf Done.} {\chris $\checkmark$} {\kenny $\checkmark$} {\john $\checkmark$}
 
@@
 {\bf We have added a paragraph right below the statement of Theorem 4.1, clarifying its assumptions as suggested, which also incorporates an 
-explanatory paragraph previously located under Corollary 4.3.} {\chris $\checkmark$} {\kenny $\checkmark$}
+explanatory paragraph previously located under Corollary 4.3.} {\chris $\checkmark$} {\kenny $\checkmark$} {\john $\checkmark$}
 

### 2022-03-10 cospans_new.tex
more changes

@@
 \label{thm:functoriality}
-Given categories $\A$ and $\A'$ with finite colimits, lax monoidal pseudofunctors $F, \maps (\A,+) \to (\Cat,\times)$ and $F' \maps (\A',+) \to 
+Given categories $\A$ and $\A'$ with finite colimits, lax monoidal pseudofunctors $F \maps (\A,+) \to (\Cat,\times)$ and $F' \maps (\A',+) \to 
 (\Cat,\times)$, a finite colimit preserving functor $H \maps \A \to \A'$, a lax monoidal pseudofunctor $E \maps (\Cat,\times) \to (\Cat,\times)$ and 

### 2022-03-11 ResponseToReviews.tex
some work

@@
 
-{\bf We thank the referee for catching this important mistake!   It does not need to be an isomorphism.
+{\bf We thank the referee for catching this important mistake!   It does not need to be an isomorphism, {\chris so we changed the construction in p. 
+9 accordingly} (right?).
 In fact, in Section 6 we construct a double functor
@@
 sending any open Petri net with rates to its corresponding open dynamical system, and we do this
-using a monoidal natural transformation $\theta$ that is \emph{not} an isomorphism.  We had mistakenly written that it was; we have fixed this now.}   {\john: $\checkmark$}
+using a monoidal natural transformation $\theta$ that is \emph{not} an isomorphism.  We had mistakenly written that it was; we have fixed this now.}
+{\john $\checkmark$}
 
@@
 
-{\kenny Yep, we needed certain maps $L' F \Rightarrow F' L$ (using structured cospan letters) to be invertible.
-We also built those maps by hand, though, and here, we're using Shulman's mystical machine to build these ones.
-I'm not sure what happens or is required when building maps of structured cospans using Shulman's machine...}
+{\kenny Yep, we needed certain maps $L' F \Rightarrow F' L$ (using structured cospan letters) to be invertible. We also built those maps by hand, 
+though, and here, we're using Shulman's mystical machine to build these ones. I'm not sure what happens or is required when building maps of 
+structured cospans using Shulman's machine...} {\chris Interesting!}
 
@@
 
+{\chris The response looks great, see my small addition above. I seached ``isomorphism'' the whole document and I think we are fine (but perhaps 
+Kenny can double check). Except this one place where I changed it to transformation above Theorem 2.5, check that it doesn't break anything? It looks 
+OK to me.}
+
 \item p. 21, definition of F: Set $\to$ Cat
@@
 
-{\chris Added a few more places where Kenny spotted these mistakes.}
+%{\chris Added a few more places where Kenny spotted these mistakes.}
 
-{\kenny Species and transitions are analogous to vertices and edges, so those maps were also changed to $f$s and $g$s, respectively.}
+%{\kenny Species and transitions are analogous to vertices and edges, so those maps were also changed to $f$s and $g$s, respectively.}
 
-{\chris Sure, are those in 6.4? As in, are there sections missing from the response sentence above?}
+%{\chris Sure, are those in 6.4? As in, are there sections missing from the response sentence above?}
 
-{\kenny Yes, one map did get changed in Section 6.4. Good catch.}
+%{\kenny Yes, one map did get changed in Section 6.4. Good catch.} :)
 
@@
 decorated cospans from a lax monoidal functor $D \colon (\mathsf{FinSet},+) \to 
-\mathsf{Set}, \times) $ agrees with the new one using a lax monoidal pseudofunctor  $D \colon (\mathsf{FinSet},+) \to \mathsf{Cat}, \times) $ when the categories $D(S)$ are discrete,
+(\mathsf{Set}, \times) $ agrees with the new one using a lax monoidal pseudofunctor  $D \colon (\mathsf{FinSet},+) \to (\mathsf{Cat}, \times) $ when 
+the categories $D(S)$ are discrete,
 and thus essentially sets.   Thus, our use of this construction amounts to working with a
@@
 
-So, giving the category of dynamical systems more morphisms sounds like a good idea. We will continue thinking about it.}  { \john \checkmark}
+So, giving the category of dynamical systems more morphisms sounds like a good idea. We will continue thinking about it.}  { \john $\checkmark$}
 
@@
 {\john Yes, but it's worth a separate answer.   I wrote an answer above.  See if you like it.  }
+
+{\chris Sounds good! However I am a bit stuck on the following. Remember also in 
+\href{https://thalis.math.upatras.gr/~cvasilak/documents/MonGroth.pdf}{MonoidalGrothendieck}, we had this issue of a lax monoidal pseudofunctor not 
+really being a lax monoidal functor in the split case, whatever I mean here. This also arised for Brendan's graph if I am not wrong. Really what is 
+going on is that for a (strictly) lax monoidal functor into Cat, the laxator is strictly natural and associativity is an equality, whereas a (weakly) 
+lax monoidal functor into Cat may be strict as a functor, but the laxator is still pseudonatural and associativity still an isomorphism, as per our 
+diagram (5). So I am not 100\% sure the starting statement in the second paragraph above is true. Let us think about that for a moment, it may end up 
+being true in this case.}
 
@@
 better direct the reader to the applications, we added one sentence at each introductory paragraph of Sections 2 and 3 that point to Section 6 for 
-concrete examples.}
+concrete examples.} {\chris $\checkmark$}
 
@@
 
-{\chris I would be happy to add this to conventions, but I cannot seem to find gf anywhere in the paper. Anyone else?}
+{\bf We added the sentence ``For composition of maps we use $\circ$ or occasionally concatenation.'' in the convention section.} {\chris $\checkmark$}
 
-{\color{blue}{Kenny: They might not mean $gf$ specifically, but there are many instances where we don't use a $\circ$ for functional composition, e.g. 
-when we're pushing forward a graph structure over a map $f$ of vertices towards the top of page 21. Do we want to use a $\circ$ or not?}}
+%{\chris I would be happy to add this to conventions, but I cannot seem to find gf anywhere in the paper. Anyone else?}
 
-{\chris Ah you are right. I don't mind, we could specify that for function composition we sometimes use concatenation!}
+%{\color{blue}{Kenny: They might not mean $gf$ specifically, but there are many instances where we don't use a $\circ$ for functional composition, 
+%e.g. 
+%when we're pushing forward a graph structure over a map $f$ of vertices towards the top of page 21. Do we want to use a $\circ$ or not?}}
 
-{\john There were a couple places where I put in $\circ$ --- that's what the referee is really complaining
-about here.  Almost always we don't.  I could remove the $\circ$s.  There was a reason I put them in: there are some places where writing a composite 
-using plain old concatenation looks weird to me.   But I don't think it's that big a deal.}
+%{\chris Ah you are right. I don't mind, we could specify that for function composition we sometimes use concatenation!}
 
-{\chris By searching our paper, I find $\circ$ in many places that should stay in my opinion, for composition of things that are not functions 
-necessarily, and maybe only a couple for functions namely towards the end of 6.4. I also don't think it's a big deal.}
+%{\john There were a couple places where I put in $\circ$ --- that's what the referee is really complaining
+%about here.  Almost always we don't.  I could remove the $\circ$s.  There was a reason I put them in: there are some places where writing a 
+%composite 
+%using plain old concatenation looks weird to me.   But I don't think it's that big a deal.}
+
+%{\chris By searching our paper, I find $\circ$ in many places that should stay in my opinion, for composition of things that are not functions 
+%necessarily, and maybe only a couple for functions namely towards the end of 6.4. I also don't think it's a big deal.}
+
+{\chris I made the above edit, see if you agree or change at will.}
 
@@
 
+{\bf It is indeed the case that we use what some people call ``covariant'' version of the Grothendieck construction in this paper, however we believe 
+that mentioning this in the introduction could put people off if they haven't heard of it. We added a footnote about this in the 
+appendix.} {\chris $\checkmark$}
+
 {\chris Not sure that `covariant' would make this clearer...both are very well the Grothendieck construction I would think, but I don't mind that 
@@
 {\kenny Agree with Christina.}
+
+{\chris See if you like the answer.}
 

### 2022-03-11 cospans_new.tex
some work

@@
 
-In this paper, we use a sans-serif font like $\C$ for categories, boldface like $\mathbf{B}$ for bicategories or 2-categories, and blackboard bold like $\lD$ for double categories.
-For double categories with names having more than one letter, like $\lCsp(\X)$, only the first letter is in blackboard bold.
-In this paper, `double category' means `pseudo double category', as in \cref{defn:double_category}.
-A double category $\lD$ has a category of objects and a category of arrows, and we call these $\lD_0$ and $\lD_1$ despite the fact that they are categories.
-Vertical composition in our double categories is strictly associative, while horizontal composition need not be.
-We use $(\C,\otimes)$ to stand for a monoidal or perhaps symmetric monoidal category with $\otimes$ as its tensor product.
+In this paper, we use a sans-serif font like $\C$ for categories, boldface like $\mathbf{B}$ for bicategories or 2-categories, and blackboard bold 
+like $\lD$ for double categories. For double categories with names having more than one letter, like $\lCsp(\X)$, only the first letter is in 
+blackboard bold. In this paper, `double category' means `pseudo double category', as in \cref{defn:double_category}. A double category $\lD$ has a 
+category of objects and a category of arrows, and we call these $\lD_0$ and $\lD_1$ despite the fact that they are categories. Vertical composition in 
+our double categories is strictly associative, while horizontal composition need not be.  We use $(\C,\otimes)$ to stand for a monoidal or perhaps 
+symmetric monoidal category with $\otimes$ as its tensor product. For composition of maps we use $\circ$ or occasionally concatenation.
 
@@
 \]
-The square at right commutes strictly because $\theta$ is a natural isomorphism.
+The square at right commutes strictly because $\theta$ is a natural transformation.
 \end{itemize}
@@
 
-In fact, there is a 2-equivalence between opfibrations and pseudofunctors induced by the so-called `Grothendieck construction'.
-Let $\OpFib(\A)$ denote the 2-subcategory of the slice 2-category $\Cat/ \A$ of opfibrations over $\A$, functors that preserve cocartesian liftings, and natural transformations with vertical components.
+In fact, there is a 2-equivalence between opfibrations and pseudofunctors induced by the so-called `Grothendieck construction'\footnote{This 
+version for opfibrations rather than fibrations is sometimes referred to as the `covariant' 
+Grothendieck construction.}.  Let $\OpFib(\A)$ denote the 2-subcategory of the slice 2-category $\Cat/ \A$ of opfibrations over $\A$, functors that 
+preserve cocartesian liftings, and natural transformations with vertical components.  
 \begin{defn}\label{def:GrothCat}

### 2022-03-11 ResponseToReviews.tex
Few tiny paper changes and handful of response comments

@@
 
+{\kenny Actually, we do talk about the flaws a bit more in the middle of page 21 when we're setting up the example of open graphs for Theorem 2.2.}
+
 \item pg. 27: To show that U does not have a left adjoint, we use the following well-known result. For readers of the TAC paper previously cited, 
@@
 {\bf We thank the referee for catching this important mistake!   It does not need to be an isomorphism, {\chris so we changed the construction in p. 
-9 accordingly} (right?).
+9 accordingly} (right?) {\kenny right}.
 In fact, in Section 6 we construct a double functor
@@
 using a monoidal natural transformation $\theta$ that is \emph{not} an isomorphism.  We had mistakenly written that it was; we have fixed this now.}
-{\john $\checkmark$}
+{\john $\checkmark$} {\kenny $\checkmark$}
 
@@
 OK to me.}
+
+{\kenny I also checked the entire document for `isomorphism' and didn't see any left over from this situation. Christina's catch on Zulip was a great one, and the response looks good to me.}
 
@@
 
-{\bf We added the sentence ``For composition of maps we use $\circ$ or occasionally concatenation.'' in the convention section.} {\chris $\checkmark$}
+{\bf We added the sentence ``For composition of maps we use concatenation or occasionally $\circ$.'' in the convention section.} {\chris $\checkmark$} {\kenny $\checkmark$}
 
@@
 
+{\kenny I think we use concatenation far more than $\circ$, right?
+I'm gonna' slightly change it to ``concatenation or occasionally $\circ$'' both in the response comment above and the paper.
+Otherwise, looks good.}
+
 \item p3: “Using the Grothendieck construction” - maybe worth mentioning this is the “covariant” version which is different to the most common 
@@
 that mentioning this in the introduction could put people off if they haven't heard of it. We added a footnote about this in the 
-appendix.} {\chris $\checkmark$}
+appendix.} {\chris $\checkmark$} {\kenny $\checkmark$}
 
@@
 {\chris See if you like the answer.}
+
+{\kenny Looks good.}
 
@@
 
+{\kenny I think we originally had these details in our proof (of both Theorem 2.1 and Theorem 3.1) but removed them.}
+
 \item On page 9 during the construction of H, I would appreciate a sentence giving some intuition for the functor E, at this point I’m confused about 
@@
 {\chris Sounds good to me!}
+
+{\kenny I've added a long run-on sentence beneath the square on page 9 trying to say more about the functors $H$ and $E$ from an intuitive standpoint. Edit at will.}
 

### 2022-03-11 cospans_new.tex
Few tiny paper changes and handful of response comments

@@
 our double categories is strictly associative, while horizontal composition need not be.  We use $(\C,\otimes)$ to stand for a monoidal or perhaps 
-symmetric monoidal category with $\otimes$ as its tensor product. For composition of maps we use $\circ$ or occasionally concatenation.
+symmetric monoidal category with $\otimes$ as its tensor product. For composition of maps we use concatenation or occasionally $\circ$.
 
@@
 \end{itemize}
+The intuition behind this square acting as a map between the two decorated cospan double categories is that while the pseudofunctors $F$ and $F'$ serve to assign categories of possible decorations to the objects of $\A$ and $\A'$, respectively, the functor $H$ allows us to change the objects being decorated from those of $\A$ to those of $\A'$, and the pseudofunctor $E$ allows us to change decorations as prescribed by $F$ into those as prescribed by $F'$, up to the transformation $\theta \colon EF \Rightarrow F'H$.
+
 The double functor $\lH \maps F\lCsp \to F'\lCsp$ is defined as follows:

### 2022-03-11 ResponseToReviews.tex
dealt with comments (23), (24), (26), (27)

@@
 
-{\bf We added the sentence ``For composition of maps we use concatenation or occasionally $\circ$.'' in the convention section.} {\chris $\checkmark$} {\kenny $\checkmark$}
+{\bf We added the sentence ``For composition of morphisms we use concatenation or occasionally $\circ$.'' in the convention section.} {\chris $\checkmark$} {\kenny $\checkmark$} {\john $\checkmark$}
 
@@
 
+{\john I changed ``composition of maps'' to ``composition of morphisms'' above because people often use ``map'' to mean a morphism in a category of sets with extra structure, and here we just mean composition of morphisms, or sometimes horizontal 1-cells, which I hope is close enough.
+I hope that's okay!}
+
 \item p3: “Using the Grothendieck construction” - maybe worth mentioning this is the “covariant” version which is different to the most common 
@@
 {\bf It is indeed the case that we use what some people call ``covariant'' version of the Grothendieck construction in this paper, however we believe 
-that mentioning this in the introduction could put people off if they haven't heard of it. We added a footnote about this in the 
-appendix.} {\chris $\checkmark$} {\kenny $\checkmark$}
+that mentioning this in the introduction could put people off if they haven't heard of it. We added a comment about this in the 
+appendix.} {\chris $\checkmark$} {\kenny $\checkmark$} {\john $\checkmark$}
 
+\iffalse
 {\chris Not sure that `covariant' would make this clearer...both are very well the Grothendieck construction I would think, but I don't mind that 
@@
 {\chris See if you like the answer.}
+\fi
 
@@
 
-\item Theorem 2.1: Maybe worth saying explicitly that s is an object of the category F(m) rather than using $\in$, since this is exactly the 
-distinction to 
-Fong's original definition.
+{\john Great.
+Except for one thing: I hate footnotes.
+If something is worth saying, just say it, don't stick a little number in the text and make the reader decide if it's worth looking down at the bottom of the page to see what this mysterious number means.
+That's more distracting than just saying it!
+So I moved the comment into the text and merged it into the previous sentence.}
 
-{\bf  We have added a remark about this in the definition.}   {\john $\checkmark$} {\chris $\checkmark$} {\kenny $\checkmark$}
+\item Theorem 2.1: Maybe worth saying explicitly that $s$ is an object of the category $F(m)$ rather than using $\in$, since this is exactly the  distinction to  Fong's original definition.
+
+{\bf  We have added a remark emphasizing this right after Theorem 2.1.}   {\john $\checkmark$} {\chris $\checkmark$} {\kenny $\checkmark$}
 
@@
 this 
-is a classic sort of spot where errors can hide)
+is a classic sort of spot where errors can hide.)
+
+\textbf{Kenny Courser carefully checked that these really are co/cartesian liftings, but the argument is straightforward uninteresting so we will just add remarks saying that this can be shown.}   {\john $\checkmark$}
 
@@
 
-\item On page 9 during the construction of H, I would appreciate a sentence giving some intuition for the functor E, at this point I’m confused about 
-its 
-role.
+{\john It's your evil advisor who removed those details.   I'll ``handwave it''---see above.}
+
+\item On page 9 during the construction of $\mathbb{H}$, I would appreciate a sentence giving some intuition for the functor $E$, at this point I’m confused about  its  role.
+
+{\bf  We have added a remark on page 9 discussing this.}  {\john $\checkmark$}
 
@@
 {\kenny I've added a long run-on sentence beneath the square on page 9 trying to say more about the functors $H$ and $E$ from an intuitive standpoint. Edit at will.}
+
+{\john I edited it --- take a looks, folks and see if you're happy.
+I'm gonna give this one my check mark.
+I actually think the referee's implicit point is right: it'd be more natural in some ways to require $E$ to be the identity, so we'd be working in the 2-category of categories over $\mathsf{Cat}$ and lax maps between these.
+But I think we can stick with what we've got,
+which is more general.}
 

### 2022-03-11 cospans_new.tex
dealt with comments (23), (24), (26), (27)

@@
 % in LaTeX
-% 2021/03/10 - dealing with referee's comments
+% 2021/03/11 - dealing with referee's comments
 
@@
 
-In this paper, we use a sans-serif font like $\C$ for categories, boldface like $\mathbf{B}$ for bicategories or 2-categories, and blackboard bold 
-like $\lD$ for double categories. For double categories with names having more than one letter, like $\lCsp(\X)$, only the first letter is in 
-blackboard bold. In this paper, `double category' means `pseudo double category', as in \cref{defn:double_category}. A double category $\lD$ has a 
-category of objects and a category of arrows, and we call these $\lD_0$ and $\lD_1$ despite the fact that they are categories. Vertical composition in 
-our double categories is strictly associative, while horizontal composition need not be.  We use $(\C,\otimes)$ to stand for a monoidal or perhaps 
-symmetric monoidal category with $\otimes$ as its tensor product. For composition of maps we use concatenation or occasionally $\circ$.
+In this paper, we use a sans-serif font like $\C$ for categories, boldface like $\mathbf{B}$ for bicategories or 2-categories, and blackboard bold like $\lD$ for double categories.
+For double categories with names having more than one letter, like $\lCsp(\X)$, only the first letter is in
+blackboard bold.
+In this paper, `double category' means `pseudo double category', as in \cref{defn:double_category}.
+A double category $\lD$ has a category of objects and a category of arrows, and we call these $\lD_0$ and $\lD_1$ despite the fact that they are categories.
+Vertical composition in our double categories is strictly associative, while horizontal composition need not be.
+We use $(\C,\otimes)$ to stand for a monoidal or perhaps symmetric monoidal category with $\otimes$ as its tensor product.
+For composition or morphisms we use concatenation or occasionally $\circ$.
 
@@
 Next, one can check that $\Phi$ is a fibration.
-Given a morphism $f \maps a \to a'$ in $\A$ and an object $(a' \xrightarrow{i'} b', s') \in \A/U$ over $a'$, a cartesian lifting of $f$ to this object is given by
+Given a morphism $f \maps a \to a'$ in $\A$ and an object $(a' \xrightarrow{i'} b', s') \in \A/U$ over $a'$, one can show that a cartesian lifting of $f$ to this object is given by
 \[ (f,1,1) \maps (a \xrightarrow{i' f} b' , s')\; \to \; (a' \xrightarrow{i'} b', s'). \]
@@
 One can also check that $\Phi$ is an opfibration.
-Given a morphism $f \maps a \to a'$ in $\A$ and an object $(a \xrightarrow{i}b, s) \in \A/U$ over $a$, we claim that a cocartesian lifting of $f$ is given by
+Given a morphism $f \maps a \to a'$ in $\A$ and an object $(a \xrightarrow{i}b, s) \in \A/U$ over $a$, one can show that a cocartesian lifting of $f$ is given by
 \[ (f,g,1) \maps (a \xrightarrow{i} b, s) \, \to \, (a' \xrightarrow{i'} b+_a a', F(g)(s)). \]
@@
 \end{itemize}
-The intuition behind this square acting as a map between the two decorated cospan double categories is that while the pseudofunctors $F$ and $F'$ serve to assign categories of possible decorations to the objects of $\A$ and $\A'$, respectively, the functor $H$ allows us to change the objects being decorated from those of $\A$ to those of $\A'$, and the pseudofunctor $E$ allows us to change decorations as prescribed by $F$ into those as prescribed by $F'$, up to the transformation $\theta \colon EF \Rightarrow F'H$.
+The intuition behind this square is that while the pseudofunctors $F$ and $F'$ serve to assign categories of possible decorations to the objects of $\A$ and $\A'$, respectively, the functor $H$ lets us turn objects of $\A$ into objects of $\A'$, and the pseudofunctor $E$ lets us change decorations as prescribed by $F$ into those as prescribed by $F'$, up to the transformation $\theta$.
+In applications $E$ and $H$ are often identities.
 
@@
 
-In fact, there is a 2-equivalence between opfibrations and pseudofunctors induced by the so-called `Grothendieck construction'\footnote{This 
-version for opfibrations rather than fibrations is sometimes referred to as the `covariant' 
-Grothendieck construction.}.  Let $\OpFib(\A)$ denote the 2-subcategory of the slice 2-category $\Cat/ \A$ of opfibrations over $\A$, functors that 
+In fact, there is a 2-equivalence between opfibrations and pseudofunctors induced by the so-called `Grothendieck construction', or more specifically the `covariant'  Grothendieck construction, since there is also a version of this construction for fibrations.
+Let $\OpFib(\A)$ denote the 2-subcategory of the slice 2-category $\Cat/ \A$ of opfibrations over $\A$, functors that
 preserve cocartesian liftings, and natural transformations with vertical components.  

### 2022-03-12 ResponseToReviews.tex
a few responses

@@
 
-{\bf We thank the referee for catching this important mistake!   It does not need to be an isomorphism, {\chris so we changed the construction in p. 
-9 accordingly} (right?) {\kenny right}.
-In fact, in Section 6 we construct a double functor
+{\bf We thank the referee for catching this important mistake!   It does not need to be an isomorphism, so we changed the construction in p. 
+9 accordingly. In fact, in Section 6 we construct a double functor
 \[      \graysquare \colon F \lCsp \to D \lCsp \]
@@
 using a monoidal natural transformation $\theta$ that is \emph{not} an isomorphism.  We had mistakenly written that it was; we have fixed this now.}
-{\john $\checkmark$} {\kenny $\checkmark$}
+{\john $\checkmark$} {\kenny $\checkmark$} {\chris $\checkmark$}
 
-{\kenny I think they are correct in that we don't use this extra assumption.}
+%{\kenny I think they are correct in that we don't use this extra assumption.}
 
-{\chris I have a vague feeling that we discussed something similar a long time ago, but I do not remember the context at all. Perhaps it was an 
-identity then? In any case, if we don't actually use it then we should make it into a transformation.}
+%{\chris I have a vague feeling that we discussed something similar a long time ago, but I do not remember the context at all. Perhaps it was an 
+%identity then? In any case, if we don't actually use it then we should make it into a transformation.}
 
-{\kenny Yes, originally it was an identity. Structured cospans has similar squares for its maps, but those ones are required to be invertible. In my 
-thesis, I was going to try to come up with a recipe for turning those squares into these ones, so I made these ones invertible, too, but never 
-actually got around to this.}
+%{\kenny Yes, originally it was an identity. Structured cospans has similar squares for its maps, but those ones are required to be invertible. In my 
+%thesis, I was going to try to come up with a recipe for turning those squares into these ones, so I made these ones invertible, too, but never 
+%actually got around to this.}
 
-{\chris I see! So for maps of structured cospans, invertibility is actually essential?}
+%{\chris I see! So for maps of structured cospans, invertibility is actually essential?}
 
-{\kenny Yep, we needed certain maps $L' F \Rightarrow F' L$ (using structured cospan letters) to be invertible. We also built those maps by hand, 
-though, and here, we're using Shulman's mystical machine to build these ones. I'm not sure what happens or is required when building maps of 
-structured cospans using Shulman's machine...} {\chris Interesting!}
+%{\kenny Yep, we needed certain maps $L' F \Rightarrow F' L$ (using structured cospan letters) to be invertible. We also built those maps by hand, 
+%though, and here, we're using Shulman's mystical machine to build these ones. I'm not sure what happens or is required when building maps of 
+%structured cospans using Shulman's machine...} {\chris Interesting!}
 
@@
 
-{\chris The response looks great, see my small addition above. I seached ``isomorphism'' the whole document and I think we are fine (but perhaps 
+{\chris The response looks great, see my small addition above `` so we changed the construction in p. 
+9 accordingly''. I seached ``isomorphism'' the whole document and I think we are fine (but perhaps 
 Kenny can double check). Except this one place where I changed it to transformation above Theorem 2.5, check that it doesn't break anything? It looks 
@@
 
-{\chris I made the above edit, see if you agree or change at will.}
+%{\chris I made the above edit, see if you agree or change at will.}
 
-{\kenny I think we use concatenation far more than $\circ$, right?
-I'm gonna' slightly change it to ``concatenation or occasionally $\circ$'' both in the response comment above and the paper.
-Otherwise, looks good.}
+%{\kenny I think we use concatenation far more than $\circ$, right? I'm gonna' slightly change it to ``concatenation or occasionally $\circ$'' both in 
+%the response comment above and the paper. Otherwise, looks good.}
 
-{\john I changed ``composition of maps'' to ``composition of morphisms'' above because people often use ``map'' to mean a morphism in a category of sets with extra structure, and here we just mean composition of morphisms, or sometimes horizontal 1-cells, which I hope is close enough.
-I hope that's okay!}
+%{\john I changed ``composition of maps'' to ``composition of morphisms'' above because people often use ``map'' to mean a morphism in a category of 
+%sets with extra structure, and here we just mean composition of morphisms, or sometimes horizontal 1-cells, which I hope is close enough.  I hope 
+%that's okay!}
+
+%{\chris Sure, thanks to both!}
 
@@
 
-{\bf It is indeed the case that we use what some people call ``covariant'' version of the Grothendieck construction in this paper, however we believe 
+{\bf It is indeed the case that we use what some people call ``covariant'' version of the Grothen\-dieck construction in this paper, however we 
+believe 
 that mentioning this in the introduction could put people off if they haven't heard of it. We added a comment about this in the 
@@
 
-{\kenny Looks good.}
+%{\kenny Looks good.}
 
-{\john Great.
-Except for one thing: I hate footnotes.
-If something is worth saying, just say it, don't stick a little number in the text and make the reader decide if it's worth looking down at the bottom of the page to see what this mysterious number means.
-That's more distracting than just saying it!
-So I moved the comment into the text and merged it into the previous sentence.}
+%{\john Great.  Except for one thing: I hate footnotes.   If something is worth saying, just say it, don't stick a little number in the text and make 
+%the reader decide if it's worth looking down at the bottom of the page to see what this mysterious number means.  That's more distracting than just 
+%saying it!   So I moved the comment into the text and merged it into the previous sentence.}
+
+%{\chris OK!}
 
@@
 
-\textbf{Kenny Courser carefully checked that these really are co/cartesian liftings, but the argument is straightforward uninteresting so we will just add remarks saying that this can be shown.}   {\john $\checkmark$}
+\textbf{Kenny Courser carefully checked that these really are co/cartesian liftings, but the argument is straightforward uninteresting so we will just 
+add remarks saying that this can be shown.}   {\john $\checkmark$} {\chris $\checkmark$}
 
@@
 
-{\bf  We have added a remark on page 9 discussing this.}  {\john $\checkmark$}
+{\bf  We have added a remark on page 9 discussing this.}  {\john $\checkmark$} {\chris $\checkmark$}
 
-{\color{blue}{Kenny: We don't have any examples where $E$ is not an identity, but in my mind it's a functor that possibly modifies decorations, e.g. 
-$F(a)$ is a category of graph structures on $a$, and $E(F(a))$ could be something like a category of possibly labeled graph structures on $a$, if that 
-makes sense. Something potentially different than \emph{just} a graph structure on $a$.}}
+%{\color{blue}{Kenny: We don't have any examples where $E$ is not an identity, but in my mind it's a functor that possibly modifies decorations, e.g. 
+%$F(a)$ is a category of graph structures on $a$, and $E(F(a))$ could be something like a category of possibly labeled graph structures on $a$, if 
+%that 
+%makes sense. Something potentially different than \emph{just} a graph structure on $a$.}}
 
-{\chris Right! We can perhaps add a sentence to this end, saying that although we only use E as an identity, someone could need to change decorations 
-for some application?}
+%{\chris Right! We can perhaps add a sentence to this end, saying that although we only use E as an identity, someone could need to change 
+%decorations 
+%for some application?}
 
-{\kenny Sure, maybe sometime before the official statement of the Theorem when we're describing how the double functor $\mathbb{H}$ is defined?}
+%{\kenny Sure, maybe sometime before the official statement of the Theorem when we're describing how the double functor $\mathbb{H}$ is defined?}
 
-{\chris Sounds good to me!}
+%{\chris Sounds good to me!}
 

### 2022-03-12 ResponseToReviews.tex
Just a few checkmarks in response file

@@
 cospans'' fixed the errors in previous work using decorated cospans by using structured cospans instead.   Here we describe how the new improved 
-decorated cospans can also fix those errors.     There may be even more ways to correct these errors, but we do not know them.}
+decorated cospans can also fix those errors.     There may be even more ways to correct these errors, but we do not know them.}  {\kenny $\checkmark$}
 
@@
 number of cospan articles etc. and that in the beginning of section 6 we elaborate on those?}
+
+{\kenny I'm fine either way on this.}
 
@@
 better direct the reader to the applications, we added one sentence at each introductory paragraph of Sections 2 and 3 that point to Section 6 for 
-concrete examples.} {\chris $\checkmark$}
+concrete examples.} {\chris $\checkmark$} {\kenny $\checkmark$}
 
@@
 \textbf{Kenny Courser carefully checked that these really are co/cartesian liftings, but the argument is straightforward uninteresting so we will just 
-add remarks saying that this can be shown.}   {\john $\checkmark$} {\chris $\checkmark$}
+add remarks saying that this can be shown.}   {\john $\checkmark$} {\chris $\checkmark$} {\kenny $\checkmark$}
 
@@
 
-{\bf  We have added a remark on page 9 discussing this.}  {\john $\checkmark$} {\chris $\checkmark$}
+{\bf  We have added a remark on page 9 discussing this.}  {\john $\checkmark$} {\chris $\checkmark$} {\kenny $\checkmark$}
 
@@
 
+{\kenny Looks good to me.}
+
 \item Theorem 2.5: $F$ should be defined on $\mathsf{A}$, not $\mathsf{A}'$.

### 2022-03-15 ResponseToReviews.tex
dealt with comment 9

@@
 application domain, and a some description of the tradeoffs. This paper should come with some practical advice for the applied category theorist on 
-how to choose whether to model their application with structured vs decorated cospans. {THE LAST SENTENCE IS NEWLY COPIED FROM REVIEW, WE CAN ERASE 
-IF NOT CONVENIENT}
+how to choose whether to model their application with structured vs decorated cospans.
 
-{\bf In fact our goal, as explained in the abstract and introduction, was to prove that the structured and decorated cospan approaches are equivalent under certain conditions, and to illustrate this result with a wide variety of examples.}
+{\bf In fact our goal, as explained in the abstract and introduction, was to prove that the structured and decorated cospan approaches are equivalent under certain conditions, and to illustrate this result with a wide variety of examples.
+These examples can serve as a guide for other similar applications, while new applications may require exploring which approach works best.
+We do not make a stand that either is strictly better.
+However, we have changed the end of the Introduction to read as follows:
 
+\begin{quote}
+This result shows that under certain conditions, structured and decorated cospans provide equivalent ways of describing open systems.
+We illustrate this in Section 6 with applications to graphs, electrical circuits, Markov processes, Petri nets, Petri nets with rates, and dynamical systems.
+This is meant to be a fairly thorough review of the existing literature.
+It becomes clear that when either structured or decorated cospans can be used, structured cospans are simpler.
+However, for open dynamical systems we apparently need decorated cospans, for reasons we explain.
+Thus, to describe a map from open Petri nets with rates to open dynamical systems, we use \emph{both} structured and decorated cospans.
+\end{quote}
+}
+
+{\john $\checkmark$} 
+\iffalse
 {\kenny I think the reader should come to their own conclusion about which framework they should use if they are trying to decide between the two, assuming both are applicable.
@@
 improve it, or something.}  
-
-{\john $\checkmark$}
+\fi
 
@@
 
-{\kenny $\checkmark$}
+{\john See if you like my new remarks in boldface, and give me a check mark if you do!  Kenny had checked this one off already, but I've changed it a lot.}
 

### 2022-03-15 cospans_new.tex
dealt with comment 9

@@
 % in LaTeX
-% 2021/03/11 - dealing with referee's comments
+% 2021/03/15 - dealing with referee's comments
 
@@
 This result shows that under certain conditions, structured and decorated cospans provide equivalent ways of describing open systems.
-We illustrate this with applications to electrical circuits, Petri nets, dynamical systems, and epidemiological modeling.
-In particular, we describe a map from open Petri nets with rates to open dynamical systems that takes advantage of \emph{both} structured and decorated cospans.
+We illustrate this in Section \ref{Applications} with applications to electrical circuits, Markov processes, Petri nets, Petri nets with rates, and dynamical systems.
+This is meant to be a fairly thorough review of the existing literature.
+It becomes clear that when either structured or decorated cospans can be used, structured cospans are simpler.
+However, for open dynamical systems we apparently need decorated cospans, for reasons we explain.
+Thus, to describe a map from open Petri nets with rates to open dynamical systems, we use \emph{both} structured and decorated cospans.
 

### 2022-03-15 ResponseToReviews.tex
dealt with comment 11.

@@
 
+{\john I changed the paragraph, trying to solve the problem Christina just mentioned.}
+
 \item Proof of Lemma 4.4: there is a typo where “L then becomes left adjoint to R” should probably be “L then becomes left adjoint to U”.
@@
 
+\vskip 1em
 \begin{quote}
@@
 
-{\chris I agree with both, and also I like the boldface above. I could add ``Those examples should serve as a guide for other similar applications, 
+{\chris I could add ``Those examples should serve as a guide for other similar applications, 
 whereas new applications would require exploring which approach works best, for example if a left adjoint (to start off with structured cospans) or a 
@@
 
-{\bf We do not know a semantics for dynamical systems that uses structured cospans; to find one would
-require getting around the result at the end of Section 6.}
+{\bf We do not know a way to construct a (double) category of open dynamical systems that uses structured cospans; to find one would require getting around the result at the end of Section 6.
+This is an interesting challenge.}
+
+{\john $\checkmark$}
 
@@
 They even say earlier in their comment that the frameworks are isomorphic for reaction networks.}
+
+{\john The referee was asking about the \emph{semantics} for reaction networks --- that is, dynamical systems!
+Reaction networks are the ``syntax'' and dynamical systems are our chosen ``semantics'' for these.
+But my reply in boldface was confused --- you're right.
+So I've fixed it.
+Give me a check mark if you're happy now.}
 

### 2022-03-15 cospans_new.tex
dealt with comment 11.

@@
 This result shows that under certain conditions, structured and decorated cospans provide equivalent ways of describing open systems.
-We illustrate this in Section \ref{Applications} with applications to electrical circuits, Markov processes, Petri nets, Petri nets with rates, and dynamical systems.
+We illustrate this in Section \ref{Applications} with applications to graphs, electrical circuits, Markov processes, Petri nets, Petri nets with rates, and dynamical systems.
 This is meant to be a fairly thorough review of the existing literature.
@@
 the fibers of $U$ are the same as the categories $F(a)$ for all $a \in \A$.
-The lax monoidal pseudofunctor structure of $F$ gives rise to a specific symmetric monoidal structure on the categories $F(a)$ given by \cref{eq:explicitstructure1}, and the hypothesis of the theorem asks that the resulting pseudofunctor $F \maps \A \to \SMC$ factors through $\Rex$.
+The lax monoidal pseudofunctor structure of $F$ gives rise to a specific symmetric monoidal structure on each category $F(a)$ given by \cref{eq:explicitstructure1}.
+The hypothesis of the theorem asks that the resulting pseudofunctor $F \maps \A \to \SMC$ factors through $\Rex$.
 This implies
-that each category $F(a)$ has coproducts and an initial object, and that the resulting cocartesian structure is what makes $F(a)$ a symmetric monoidal category.
+that the symmetric monoidal structure on $F(a)$ is cocartesian.
 

### 2022-03-15 ResponseToReviews.tex
dealt with comment 12

@@
 So I've fixed it.
-Give me a check mark if you're happy now.}
+The ``result at the end of Section 6'' is the one where we show the functor from dynamical systems to finite sets doesn't have a left adjoint.
+For some reason we didn't make this into a theorem.
+Give me a check mark if you're happy now.
+}
 
@@
 
-{\john I wasn't trying to talk about AlgebraicPetri, just the application to epidemiology, and unfortunately that was (and still is???) only explained 
-in a blog article. But it'd be good to add a reference to the repository.}
+{\bf We have added a reference to the new paper ``An
+algebraic framework for structured epidemic modeling'' by A.\ Baas, J.\ Fairbanks, M.\ Halter, S.\ Libkind and E.\ Patterson.  We have also added a reference to the AlgebraicPetri GitHub repository.}
+
+{\john \checkmark}
+
+{\john It'd be good to add a reference to the repository.}
 
 {\chris I added the reference but looks a bit funny, edit at will. Did not add any text.}
+
+{\john I've improved the reference and added a citation to it.  Is this okay now?}
 

### 2022-03-15 cospans_new.tex
dealt with comment 12

@@
 This in turn lets us couple the SIR model to other models, and build larger models from smaller pieces.
-Indeed, a group of researchers has recently used open Petri nets and the mathematics of structured cospans in their software tool for building and manipulating epidemiological models \cite{BFMLP}.
+Indeed, a group of researchers has recently used open Petri nets and the mathematics of structured cospans in their software tool for building and manipulating epidemiological models \cite{AP,BFMLP}.
 
@@
 
-\bibitem{AP} AlgebraicPetri team, Github repository. Available as 
-\href{https://github.com/AlgebraicJulia/AlgebraicPetri.jl}{AlgebraicPetri.jl}.
+\bibitem{AP} AlgebraicPetri team, GitHub repository. Available at
+\href{https://github.com/AlgebraicJulia/AlgebraicPetri.jl}{https://github.com/AlgebraicJulia/AlgebraicPetri.jl}.
 

### 2022-03-16 ResponseToReviews.tex
I dealt with comment 10 - maybe.

@@
 
+{\bf Unfortunately not all cases of C-sets meet the conditions of Theorem 4.1.
+For example, the usual forgetful functor from $\mathsf{Graph}$ to $\mathsf{Set}$ sending any graph to its set of vertices is an opfibration, but not the forgetful functor sending any graph to its set of vertices.
+So, this gives a structured cospan category to which Theorem 4.1 does not apply.
+Finding extra conditions such that it \emph{does} apply is an interesting question, but it would take more thought.}
+
+{\john $\checkmark$}
+
 {\john Actually it's really easy to prove that presheaf categories obey the conditions of Theorem 4.1:
@@
 {\chris Also perhaps we should add those references they provide somewhere.}
+
+{\john Now I think this is a bit harder than I thought.  I started writing stuff:
+
+\vskip 1em
+\begin{quote}
+Presheaf categories provide many examples of  Theorem 4.1.
+Suppose $f \colon C \to D$ is any functor between small categories.
+Then precomposition with $f$ gives a functor $f^\ast \colon \widehat{D} \to \widehat{C}$ between their presheaf categories, and this has a left adjoint $f_!
+\colon \widehat{C} \to \widehat{D}$.
+\end{quote}
+
+\vskip 1em
+
+This is a good enough situation to build a structured cospan category, but the right adjoint $f^\ast$ may not be an opfibration, in which case we can't apply Theorem 4.1 --- right?
+
+With a lot of help from Todd Trimble's I once figured out when $f^\ast$ \emph{is} an opfibration, but remembering that argument and writing this up would take some work.
+And I don't really feel like expanding the paper in such a way --- we've got more than enough already.
+So how about if just tell the referee this is a great idea but it would take more thought?
+See if you like my boldface comment above.
+}
 

### 2022-03-16 cospans_new.tex
I dealt with comment 10 - maybe.

@@
 the fibers of $U$ are the same as the categories $F(a)$ for all $a \in \A$.
-The lax monoidal pseudofunctor structure of $F$ gives rise to a specific symmetric monoidal structure on each category $F(a)$ given by \cref{eq:explicitstructure1}.
+The lax monoidal pseudofunctor structure of $F$ gives rise to a specific symmetric monoidal structure on each category $F(a)$, as in \cref{eq:explicitstructure1}.
 The hypothesis of the theorem asks that the resulting pseudofunctor $F \maps \A \to \SMC$ factors through $\Rex$.
 This implies
-that the symmetric monoidal structure on $F(a)$ is cocartesian.
+that the symmetric monoidal structure on each category $F(a)$ is cocartesian.
 
@@
 \]
+
+\iffalse
+Presheaf categories provide many examples of \cref{thm:equiv}.
+Suppose $\phi \maps \C \to \D$ is any functor between small categories.
+Then precomposition with $\phi$ gives a functor $\phi^\ast \maps \widehat{\D} \to \widehat{\C}$ between their presheaf categories, and this has a left adjoint $\phi_!
+\maps \widehat{\C} \to \widehat{\D}$.
+\fi
 

### 2022-03-16 ResponseToReviews.tex
dealt with comment 20

@@
 
-\textbf{Kenny Courser carefully checked that these really are co/cartesian liftings, but the argument is straightforward uninteresting so we will just 
+\textbf{Kenny Courser carefully checked that these really are co/cartesian liftings, but the argument is straightforward and uninteresting so we will just 
 add remarks saying that this can be shown.}   {\john $\checkmark$} {\chris $\checkmark$} {\kenny $\checkmark$}
 
+\iffalse
 {\kenny I think we originally had these details in our proof (of both Theorem 2.1 and Theorem 3.1) but removed them.}
@@
 {\john It's your evil advisor who removed those details.   I'll ``handwave it''---see above.}
+\fi
 
@@
 
-%{\color{blue}{Kenny: We don't have any examples where $E$ is not an identity, but in my mind it's a functor that possibly modifies decorations, e.g. 
-%$F(a)$ is a category of graph structures on $a$, and $E(F(a))$ could be something like a category of possibly labeled graph structures on $a$, if 
-%that 
-%makes sense. Something potentially different than \emph{just} a graph structure on $a$.}}
+\iffalse
+{\color{blue}{Kenny: We don't have any examples where $E$ is not an identity, but in my mind it's a functor that possibly modifies decorations, e.g. 
+$F(a)$ is a category of graph structures on $a$, and $E(F(a))$ could be something like a category of possibly labeled graph structures on $a$, if 
+that 
+makes sense. Something potentially different than \emph{just} a graph structure on $a$.}}
 
-%{\chris Right! We can perhaps add a sentence to this end, saying that although we only use E as an identity, someone could need to change 
-%decorations 
-%for some application?}
+{\chris Right! We can perhaps add a sentence to this end, saying that although we only use E as an identity, someone could need to change 
+decorations 
+for some application?}
 
-%{\kenny Sure, maybe sometime before the official statement of the Theorem when we're describing how the double functor $\mathbb{H}$ is defined?}
+{\kenny Sure, maybe sometime before the official statement of the Theorem when we're describing how the double functor $\mathbb{H}$ is defined?}
 
-%{\chris Sounds good to me!}
+{\chris Sounds good to me!}
 
@@
 {\kenny Looks good to me.}
+\fi
 
@@
 way, for example with an ordering with the zero vector field as the bottom element. I suppose this would give you different 2-cells in the resulting 
-double category or bicategory, but perhaps it would yield the same 1-category
+double category or bicategory, but perhaps it would yield the same 1-category.
 
-{\chris This looks similar to comment 20.}
+{\bf This is an interesting idea but we haven't been able to get it to work yet.  See also comment 20.}
+
+{\john $\checkmark$}
 \end{enumerate}

### 2022-03-16 ResponseToReviews.tex
dealt with comment 16

@@
 {\chris Third review starts here}
-\item p. 2. “Unfortunately, many applications of decorated cospans were flawed… for reasons painstaking explained in [1]”
+\item p. 2. ``Unfortunately, many applications of decorated cospans were flawed… for reasons painstakingly explained in [1].''
 
@@
 
+{\bf We have rewritten this paragraph to explain those flaws.}
+
+{\john $\checkmark$}
+
 {\chris If I am not wrong, the paragraph cited here IS the explanation of the problem, perhaps in application terms rather than in theory terms. 
@@
 {\kenny This seems similar to comment 14 above. So that's two people that want to know more about what the flaws are with the original decorated cospans but don't feel like opening our other paper...}
+
+{\john You're right, Christina, I already explained why ``many applications of decorated cospans were flawed'' in this paragraph!
+See if you like my boldface response.
+I sneakily pretend that we rewrote this paragraph to explain the flaws.
+We actually have rewritten this paragraph...
+but the explanation was already there!
+
+And yeah, Kenny, it's annoying: people complain if you repeat already known stuff, but they also complain if you don't.}
 
@@
 {\bf We believe that it is hard to analyze the examples (even the motivating one of open graphs) without having laid all relevant theory. Also, 
-the comparison between the two descriptions -- prominent in Section 6.1 -- would then not be possible to illustrate. In order to 
-better direct the reader to the applications, we added one sentence at each introductory paragraph of Sections 2 and 3 that point to Section 6 for 
-concrete examples.} {\chris $\checkmark$} {\kenny $\checkmark$}
+the comparison between the two formalisms---a major feature of Section 6---would then not be possible. In order to 
+better direct the reader to the applications, we added one sentence in each introductory paragraph of Sections 2 and 3 that point to Section 6 for 
+concrete examples, and also added a paragraph and the end of the Introduction (see comment 9). }
+
+{\chris $\checkmark$} {\kenny $\checkmark$} {\john $\checkmark$}
 
@@
 {\kenny Agreed about keeping the examples together. The boldface looks good to me.}
+
+{\john I tweaked the boldface a tiny bit, so you can revoke your checkmarks if you want; 
+otherwise just comment out our little conversation here.}
 

### 2022-03-16 ResponseToReviews.tex
dealt with comment 14

@@
 
-\item pg. 3: “Many of the flawed applications of decorated cospans have been fixed using structured cospans.” This dismisses the work of other 
+\item pg. 3: ``Many of the flawed applications of decorated cospans have been fixed using structured cospans.” This dismisses the work of other 
 scholars 
 using the decorated cospan approach as flawed. The alleged flaw should be made more precise. What about the decorated cospan approach is inferior to 
-the structured cospan approach? 
+the structured cospan approach?''
 %The goal of this paper should be to illustrate to an applied category theory audience the differences between 
 %decorated and structured cospans. Referring back to previous work of the authors to make that point does not provide value.
+
+{\bf The ``other scholars'' are John Baez, one of the authors here, and his coauthors.
+The flaws---mathematical errors that render a number of claimed theorems incorrect---are now explained in  in the Introduction, in the paragraph beginning ``Unfortunately, many applications of decorated cospans were flawed.''  In the paper ``Structured cospans'', Kenny Courser and John Baez fixed all these mistakes using structured cospans.
+See also comment (9).}
+
+{\john $\checkmark$}
 
@@
 {\kenny Actually, we do talk about the flaws a bit more in the middle of page 21 when we're setting up the example of open graphs for Theorem 2.2.}
+
+{\john See if you like my boldface response.  I'm acting like we added an explanation of the flaws to our introduction, so we don't have to say ``Hey, buster --- we already explained this.''}
 
@@
 {\bf We have moved the natural isomorphism triangle as equation (1) in the statement of Theorem 2.1, and we have referred to it at page 10.} {\chris 
-$\checkmark$} {\kenny $\checkmark$}
+$\checkmark$} {\kenny $\checkmark$} {\john $\checkmark$}
 
@@
 
-%{\kenny I think they are correct in that we don't use this extra assumption.}
+\iffalse
+{\kenny I think they are correct in that we don't use this extra assumption.}
 
-%{\chris I have a vague feeling that we discussed something similar a long time ago, but I do not remember the context at all. Perhaps it was an 
+{\chris I have a vague feeling that we discussed something similar a long time ago, but I do not remember the context at all. Perhaps it was an 
 %identity then? In any case, if we don't actually use it then we should make it into a transformation.}
 
-%{\kenny Yes, originally it was an identity. Structured cospans has similar squares for its maps, but those ones are required to be invertible. In my 
-%thesis, I was going to try to come up with a recipe for turning those squares into these ones, so I made these ones invertible, too, but never 
-%actually got around to this.}
+{\kenny Yes, originally it was an identity. Structured cospans has similar squares for its maps, but those ones are required to be invertible. In my 
+thesis, I was going to try to come up with a recipe for turning those squares into these ones, so I made these ones invertible, too, but never 
+actually got around to this.}
 
-%{\chris I see! So for maps of structured cospans, invertibility is actually essential?}
+{\chris I see! So for maps of structured cospans, invertibility is actually essential?}
 
-%{\kenny Yep, we needed certain maps $L' F \Rightarrow F' L$ (using structured cospan letters) to be invertible. We also built those maps by hand, 
-%though, and here, we're using Shulman's mystical machine to build these ones. I'm not sure what happens or is required when building maps of 
-%structured cospans using Shulman's machine...} {\chris Interesting!}
+{\kenny Yep, we needed certain maps $L' F \Rightarrow F' L$ (using structured cospan letters) to be invertible. We also built those maps by hand, 
+though, and here, we're using Shulman's mystical machine to build these ones. I'm not sure what happens or is required when building maps of 
+structured cospans using Shulman's machine...} {\chris Interesting!}
 
@@
 {\kenny I also checked the entire document for `isomorphism' and didn't see any left over from this situation. Christina's catch on Zulip was a great one, and the response looks good to me.}
+\fi
 
@@
 decorated cospans from a lax monoidal functor $D \colon (\mathsf{FinSet},+) \to 
-(\mathsf{Set}, \times) $ agrees with the new one using a lax monoidal pseudofunctor  $D \colon (\mathsf{FinSet},+) \to (\mathsf{Cat}, \times) $ when 
-the categories $D(S)$ are discrete,
-and thus essentially sets.   Thus, our use of this construction amounts to working with a
+(\mathsf{Set}, \times) $ amounts to working with a discrete categories $D(S)$, treated
+as sets.  Thus, our use of this construction amounts to working with a
 set $D(S)$, rather than a full-fledged category, of dynamical systems on the finite set $S$.
@@
 of dynamical systems.   It is not discrete, but it does not have an initial object, as we'd
-need to get a structured cospan
+need to obtain a structured cospan
 category that matches our decorated cospan category.
@@
 being true in this case.}
+
+{\john  Oh-ho!
+In this response I don't want to get pulled into any subtle math questions that aren't  actually necessary.
+I was just trying to give the referee a pat on the back.
+See if you like my new simplified reply, and bless it with a check mark if you do.}
 
@@
 {\john I tweaked the boldface a tiny bit, so you can revoke your checkmarks if you want; 
-otherwise just comment out our little conversation here.}
+otherwise just comment out our little conversation here. By the way, you can comment out
+a big chunk of text just by putting $\backslash$iffalse in front of it and $\backslash$fi at the end.  This is a special case of a trick for making some text appear only if some condition is true!}
 

### 2022-03-16 ResponseToReviews.tex
dealt with comment 1

@@
 
-{\bf The present work reviews all previous work on decorated and structured cospans in Section 6.  As we mention, our previous paper ``Structured 
+{\bf The present work reviews all known previous work on decorated and structured cospans in Section 6, and we now point this out in the Introduction.   As we mention, our previous paper ``Structured 
 cospans'' fixed the errors in previous work using decorated cospans by using structured cospans instead.   Here we describe how the new improved 
-decorated cospans can also fix those errors.     There may be even more ways to correct these errors, but we do not know them.}  {\kenny $\checkmark$}
+decorated cospans can also fix those errors.     There may be even more ways to correct these errors, but we do not know them.}  {\kenny $\checkmark$} {\john $\checkmark$}
 
@@
 {\kenny I'm fine either way on this.}
+
+{\john I have added a remark in the Introduction, ``This result [Theorem 4.1] shows that under certain conditions, structured and decorated cospans provide equivalent ways of describing open systems.
+We illustrate this in Section 6 with applications to graphs, electrical circuits, Markov processes, Petri nets, Petri nets with rates, and dynamical systems.
+This is meant to be a fairly thorough review of the existing literature.''
+
+If you're happy with my response above give me a check mark, Christina!}
 
@@
 {\bf The ``other scholars'' are John Baez, one of the authors here, and his coauthors.
-The flaws---mathematical errors that render a number of claimed theorems incorrect---are now explained in  in the Introduction, in the paragraph beginning ``Unfortunately, many applications of decorated cospans were flawed.''  In the paper ``Structured cospans'', Kenny Courser and John Baez fixed all these mistakes using structured cospans.
+The flaws---mathematical errors that render a number of claimed theorems incorrect---are now explained in  in the Introduction, in the paragraph beginning ``Unfortunately, many applications of decorated cospans were flawed.''  In the paper ``Structured cospans'', Kenny Courser and John Baez analyzed these mistakes in detail and fixed them using structured cospans.
 See also comment (9).}
@@
 
-{\bf We have added a citation to Emily Riehl's book ``Category Theory in Context'' which includes said result, above Lemma 6.1.}
+{\bf We have eliminated the term ``well-known'' and added a citation to Emily Riehl's book ``Category Theory in Context'' which includes said result, above Lemma 6.1.}
 

### 2022-03-16 ResponseToReviews.tex
little bit of work

@@
 \usepackage{stackrel}
+\usepackage{soul}
 
@@
 
-\item As the only point against, I feel there is a growing number of “cospan” articles. The present work seems like it could serve as a comparison of 
+\item As the only point against, I feel there is a growing number of “cospan” articles. The present work seems like it could serve as a 
+comparison of 
 all of 
@@
 
-{\bf The present work reviews all known previous work on decorated and structured cospans in Section 6, and we now point this out in the Introduction.   As we mention, our previous paper ``Structured 
+{\bf The present work reviews all known previous work on decorated and structured cospans in Section 6, and we now point this out in the end of 
+the Introduction.   As we mention, our previous paper ``Structured 
 cospans'' fixed the errors in previous work using decorated cospans by using structured cospans instead.   Here we describe how the new improved 
-decorated cospans can also fix those errors.     There may be even more ways to correct these errors, but we do not know them.}  {\kenny $\checkmark$} {\john $\checkmark$}
+decorated cospans can also fix those errors.     There may be even more ways to correct these errors, but we do not know them.}  {\kenny $\checkmark$} 
+{\john $\checkmark$} {\chris $\checkmark$}
 
-{\chris As was suggested by John at some point, would we perhaps want to add a sentence or two in the introduction, saying that indeed there are a 
-number of cospan articles etc. and that in the beginning of section 6 we elaborate on those?}
+%{\chris As was suggested by John at some point, would we perhaps want to add a sentence or two in the introduction, saying that indeed there are a 
+%number of cospan articles etc. and that in the beginning of section 6 we elaborate on those?}
 
-{\kenny I'm fine either way on this.}
+%{\kenny I'm fine either way on this.}
 
-{\john I have added a remark in the Introduction, ``This result [Theorem 4.1] shows that under certain conditions, structured and decorated cospans provide equivalent ways of describing open systems.
-We illustrate this in Section 6 with applications to graphs, electrical circuits, Markov processes, Petri nets, Petri nets with rates, and dynamical systems.
-This is meant to be a fairly thorough review of the existing literature.''
+%{\john I have added a remark in the Introduction, ``This result [Theorem 4.1] shows that under certain conditions, structured and decorated cospans 
+%provide equivalent ways of describing open systems.  We illustrate this in Section 6 with applications to graphs, electrical circuits, Markov 
+%processes, Petri nets, Petri nets with rates, and dynamical systems.   This is meant to be a fairly thorough review of the existing literature.''
 
-If you're happy with my response above give me a check mark, Christina!}
+%If you're happy with my response above give me a check mark, Christina!}
+
+{\chris Looks good, I only added ``in the end of'' the introduction, if it is OK, John, erase current comment.}
 
@@
 
-{\bf Done, also in Corollary 4.3.}
+{\bf Done, also in Corollary 4.3.} {\chris $\checkmark$}
 
@@
 paper.   So, I've commented out the added text and said ``factors through the above 2-functor $\mathsf{SMC} \to \mathsf{Rex}$'' --- we defined right above the theorem.}
-\fi
 
@@
 {\john I changed the paragraph, trying to solve the problem Christina just mentioned.}
+
+{\chris Looks good!}
+\fi
 

### 2022-03-16 ResponseToReviews.tex
Mostly checkmarks in reponse file

@@
 
-{\bf Done, also in Corollary 4.3.} {\chris $\checkmark$}
+{\bf Done, also in Corollary 4.3.} {\chris $\checkmark$} {\kenny $\checkmark$}
 
@@
 
+{\kenny Can we put ``In preparation." if they don't have this on the arXiv in a timely manner?}
+
 %{\chris Great! The 
@@
 
-{\john $\checkmark$} 
+{\john $\checkmark$} {\kenny $\checkmark$}
 \iffalse
@@
 {\bf Unfortunately not all cases of C-sets meet the conditions of Theorem 4.1.
-For example, the usual forgetful functor from $\mathsf{Graph}$ to $\mathsf{Set}$ sending any graph to its set of vertices is an opfibration, but not the forgetful functor sending any graph to its set of vertices.
+For example, the usual forgetful functor from $\mathsf{Graph}$ to $\mathsf{Set}$ sending any graph to its set of vertices is an opfibration, but not the forgetful functor sending any graph to its set of vertices {\kenny edges?}.
 So, this gives a structured cospan category to which Theorem 4.1 does not apply.
@@
 
-{\john $\checkmark$}
+{\john $\checkmark$} {\kenny $\checkmark$}
 
@@
 
+{\kenny I think I recall you trying to explain this to me once: I believe the condition for $f^*$ to be an opfibration was that each hom-set $\hom(d,d)$ was a singleton, and that it was an if and only if.
+I remember trying to prove it, but getting lost in some of the details.
+Regardless, I agree that we have enough.
+The bold looks good to me.}
+
 \item If we take the categorical systems theory perspective advanced by section 6, and the body of the authors’ recent work on functorial semantics 
@@
 {\john $\checkmark$}
+
+{\kenny $\checkmark$}
 
@@
 
-{\john \checkmark}
+{\john \checkmark} {\kenny \checkmark}
 
@@
 {\bf The ``other scholars'' are John Baez, one of the authors here, and his coauthors.
-The flaws---mathematical errors that render a number of claimed theorems incorrect---are now explained in  in the Introduction, in the paragraph beginning ``Unfortunately, many applications of decorated cospans were flawed.''  In the paper ``Structured cospans'', Kenny Courser and John Baez analyzed these mistakes in detail and fixed them using structured cospans.
+The flaws---mathematical errors that render a number of claimed theorems incorrect---are now explained in  in the Introduction, in the paragraph beginning ``Unfortunately, many applications of decorated cospans were flawed.''.
+In the paper ``Structured cospans'', Kenny Courser and John Baez analyzed these mistakes in detail and fixed them using structured cospans.
 See also comment (9).}
 
-{\john $\checkmark$}
+{\john $\checkmark$} {\kenny $\checkmark$}
 

### 2022-03-16 ResponseToReviews.tex
a bit more

@@
 
+{\chris Sounds good to me...}
+
 %{\chris Great! The 
@@
 
-{\john $\checkmark$} {\kenny $\checkmark$}
+{\john $\checkmark$} {\kenny $\checkmark$} {\chris $\checkmark$}
 \iffalse
@@
 improve it, or something.}
-\fi
 
@@
 
-{\john See if you like my new remarks in boldface, and give me a check mark if you do!  Kenny had checked this one off already, but I've changed it a lot.}
+\fi
+
+{\john See if you like my new remarks in boldface, and give me a check mark if you do!  Kenny had checked this one off already, but I've changed it a 
+lot.}
+
+{\chris Looks great to me. Final two minor points, feel free to ignore or not and delete this comment. (1) Is ``apparently'' supposed to sound a bit 
+sceptical? If not, would ``actually'' be better or not? (2) If we were being really accurate, don't we 
+actually ONLY use decorated cospans to describe the map from open Petri nets with rates to open dynamical systems? Namely since dynamical systems only 
+work as decorated cospans, we are required to use decorated cospans also for Petri nets to then get the map between them. Unless I am mixing something 
+there.}
 
@@
 
-{\john $\checkmark$}
+{\john $\checkmark$} {\kenny $\checkmark$} {\chris $\checkmark$}
 
-{\kenny $\checkmark$}
-
+\iffalse
 {\chris Should we refer to which result we are talking about? Also, I am a bit confused about the question and answer. I thought reaction networks 
@@
 So I've fixed it.
-The ``result at the end of Section 6'' is the one where we show the functor from dynamical systems to finite sets doesn't have a left adjoint.
-For some reason we didn't make this into a theorem.
-Give me a check mark if you're happy now.
-}
+The ``result at the end of Section 6'' is the one where we show the functor from dynamical systems to finite sets doesn't have a left adjoint.  For 
+some reason we didn't make this into a theorem.   Give me a check mark if you're happy now.   }
+
+{\chris I see, thanks!}
+\fi
 

### 2022-03-16 ResponseToReviews.tex
a little bit more

@@
 if the others included a theorem that all (or finitary) categories of presheaves satisfy the 
-conditions of theorem 4.1 or a counter example (...) Hopefully it is easy to check and provide some 
-commentary 
-on it in this paper.
+conditions of theorem 4.1 or a counter example (...) {\chris Without this analysis, I am left with the intuition
+that for discrete structures like finitary presheaves over a finitely presented schema, the decorated and structured cospans are going
+to be equivalent (...) If that intuition is correct, the paper should say something about it. If the intuition is incorrect, then additional 
+explanation should be provided.} Hopefully it is easy to check and provide some commentary on it in this paper.
 

### 2022-03-16 ResponseToReviews.tex
a few more checkmarks

@@
 
-{\john \checkmark} {\kenny \checkmark}
+{\john \checkmark} {\kenny \checkmark} {\chris \checkmark}
 
+\iffalse
 {\john It'd be good to add a reference to the repository.}
@@
 
-[Several points in the text are written in a way style that can be interpreted as the dismissive style common to many discussions of Category 
-Theory. I 
-would recommend rewriting at least the following points that should be made in a more collegial tone.]
+{\chris Yes!}
+\fi
+
+%[Several points in the text are written in a way style that can be interpreted as the dismissive style common to many discussions of Category 
+%Theory. I would recommend rewriting at least the following points that should be made in a more collegial tone.]
 
@@
 {\bf We removed the part of the sentence ``despite all the tricks one might try'' according to this suggestion. In [3, Section 5], these attempts are 
-explained in detail, and we find them of value because the diligent reader may in fact come up with some of these for fixing the problem.}
+explained in detail, and we find them of value because the diligent reader may in fact come up with some of these for fixing the problem.} {\chris 
+\checkmark}
 
@@
 
-{\john $\checkmark$} {\kenny $\checkmark$}
+{\john $\checkmark$} {\kenny $\checkmark$} {\chris \checkmark}
 
+\iffalse
 {\john The "other scholars" are mainly me and Brendan, and the flaws are that some claims are false! I think we describe the flaws in Section 6; if so 
@@
 
-{\john See if you like my boldface response.  I'm acting like we added an explanation of the flaws to our introduction, so we don't have to say ``Hey, buster --- we already explained this.''}
+{\john See if you like my boldface response.  I'm acting like we added an explanation of the flaws to our introduction, so we don't have to say ``Hey, 
+buster --- we already explained this.''}
+
+\fi
+{\chris I would potentially skip the first sentence of our response above. Does it sound a bit hostile? And perhaps he also means other people that 
+may have used this approach, or perhaps Brendan himself (not a coauthor at the time?) that invented them. Not too important in any case.}
 
@@
 
-{\john $\checkmark$} {\kenny $\checkmark$}
+{\john $\checkmark$} {\kenny $\checkmark$} {\chris $\checkmark$}
 
+\iffalse
 {\chris If I am not wrong, the paragraph cited here IS the explanation of the problem, perhaps in application terms rather than in theory terms. 
@@
 And yeah, Kenny, it's annoying: people complain if you repeat already known stuff, but they also complain if you don't.}
+
+\fi
 

### 2022-03-17 ResponseToReviews.tex
did a lot of work, almost done now

@@
 the Introduction.   As we mention, our previous paper ``Structured 
-cospans'' fixed the errors in previous work using decorated cospans by using structured cospans instead.   Here we describe how the new improved 
-decorated cospans can also fix those errors.     There may be even more ways to correct these errors, but we do not know them.}  {\kenny $\checkmark$} 
-{\john $\checkmark$} {\chris $\checkmark$}
-
-%{\chris As was suggested by John at some point, would we perhaps want to add a sentence or two in the introduction, saying that indeed there are a 
-%number of cospan articles etc. and that in the beginning of section 6 we elaborate on those?}
-
-%{\kenny I'm fine either way on this.}
-
-%{\john I have added a remark in the Introduction, ``This result [Theorem 4.1] shows that under certain conditions, structured and decorated cospans 
-%provide equivalent ways of describing open systems.  We illustrate this in Section 6 with applications to graphs, electrical circuits, Markov 
-%processes, Petri nets, Petri nets with rates, and dynamical systems.   This is meant to be a fairly thorough review of the existing literature.''
-
-%If you're happy with my response above give me a check mark, Christina!}
+cospans'' fixed the errors in previous work on decorated cospans by using structured cospans instead.   Here we describe how the new improved 
+decorated cospans can also fix those errors.     There may be even more ways to correct these errors, but we do not know them.}
+
+{\kenny $\checkmark$}  {\john $\checkmark$} {\chris $\checkmark$}
+
+\iffalse
+{\chris As was suggested by John at some point, would we perhaps want to add a sentence or two in the introduction, saying that indeed there are a 
+number of cospan articles etc. and that in the beginning of section 6 we elaborate on those?}
+
+{\kenny I'm fine either way on this.}
+
+{\john I have added a remark in the Introduction, ``This result [Theorem 4.1] shows that under certain conditions, structured and decorated cospans 
+provide equivalent ways of describing open systems.  We illustrate this in Section 6 with applications to graphs, electrical circuits, Markov 
+processes, Petri nets, Petri nets with rates, and dynamical systems.   This is meant to be a fairly thorough review of the existing literature.''
+
+If you're happy with my response above give me a check mark, Christina!}
 
 {\chris Looks good, I only added ``in the end of'' the introduction, if it is OK, John, erase current comment.}
+\fi
 
@@
 {\bf We have added ``lax'' at Lemma 2.4 in two occurences, and have checked the rest of the document to verify that this does not happen 
-elsewhere.}  {\john $\checkmark$} {\chris $\checkmark$} {\kenny $\checkmark$}
+elsewhere.}
+
+{\john $\checkmark$} {\chris $\checkmark$} {\kenny $\checkmark$}
 
@@
 
-{\bf Done, also in Corollary 4.3.} {\chris $\checkmark$} {\kenny $\checkmark$}
+{\bf Done, also in Corollary 4.3.}
+
+{\chris $\checkmark$} {\kenny $\checkmark$} {\john $\checkmark$}
 
@@
 
-{\bf Done.}  {\john $\checkmark$} {\chris $\checkmark$} {\kenny $\checkmark$}
+{\bf Done.}
+
+{\john $\checkmark$} {\chris $\checkmark$} {\kenny $\checkmark$}
 
@@
 
-{\bf Done.} {\john $\checkmark$} {\chris $\checkmark$} {\kenny $\checkmark$}
+{\bf Done.}
+
+{\john $\checkmark$} {\chris $\checkmark$} {\kenny $\checkmark$}
 
@@
 
+{\john Yes, we can do that.
+Their paper is written, but they are struggling to get it onto the arXiv...
+and having trouble for stupid technical reasons.
+I'll see if they succeed by the time we submit this.}
+
 %{\chris Great! The 
@@
 {\bf We have added a word about Markov processes in Section 6.2, and with this, all the applications of structured or decorated cospans that we know 
-of are discussed here.} {\john $\checkmark$} {\chris $\checkmark$} {\kenny $\checkmark$}
+of are discussed here.}
+
+{\john $\checkmark$} {\chris $\checkmark$} {\kenny $\checkmark$}
 
@@
 It becomes clear that when either structured or decorated cospans can be used, structured cospans are simpler.
-However, for open dynamical systems we apparently need decorated cospans, for reasons we explain.
-Thus, to describe a map from open Petri nets with rates to open dynamical systems, we use \emph{both} structured and decorated cospans.
+However, for open dynamical systems we need decorated cospans, for reasons we explain.
+Thus, to describe a map from open Petri nets with rates to open dynamical systems, we use decorated cospans.
 \end{quote}
@@
 {\chris Looks great to me. Final two minor points, feel free to ignore or not and delete this comment. (1) Is ``apparently'' supposed to sound a bit 
-sceptical? If not, would ``actually'' be better or not? (2) If we were being really accurate, don't we 
+sceptical? If not, would ``actually'' be better or not?}
+
+{\john I said ``apparently'' because two referees suggested that we might be able to create a structured cospan category of open dynamical systems if we could find more morphisms between dynamical systems.
+But since the readers of our paper aren't being told about this hope, I guess it will confuse \emph{them} if we say ``apparently''.
+So I've deleted ``apparently'' in this sentence:
+
+\begin{quote}
+However, for open dynamical systems we apparently need decorated cospans, for reasons we explain. 
+\end{quote}
+\noindent
+both here and in the actual paper.  The referees may complain, but the readers will be less puzzled.}
+
+{\chris (2) If we were being really accurate, don't we 
 actually ONLY use decorated cospans to describe the map from open Petri nets with rates to open dynamical systems? Namely since dynamical systems only 
@@
 there.}
+
+{\john You're right.  So I've also changed this sentence above and in the paper:
+
+\begin{quote}
+Thus, to describe a map from open Petri nets with rates to open dynamical systems, we use \emph{both} structured and decorated cospans.
+\end{quote}}
 
@@
 if the others included a theorem that all (or finitary) categories of presheaves satisfy the 
-conditions of theorem 4.1 or a counter example (...) {\chris Without this analysis, I am left with the intuition
+conditions of theorem 4.1 or a counter example (...) Without this analysis, I am left with the intuition
 that for discrete structures like finitary presheaves over a finitely presented schema, the decorated and structured cospans are going
 to be equivalent (...) If that intuition is correct, the paper should say something about it. If the intuition is incorrect, then additional 
-explanation should be provided.} Hopefully it is easy to check and provide some commentary on it in this paper.
+explanation should be provided. Hopefully it is easy to check and provide some commentary on it in this paper.
 
 {\bf Unfortunately not all cases of C-sets meet the conditions of Theorem 4.1.
-For example, the usual forgetful functor from $\mathsf{Graph}$ to $\mathsf{Set}$ sending any graph to its set of vertices is an opfibration, but not the forgetful functor sending any graph to its set of vertices {\kenny edges?}.
+For example, the usual forgetful functor from $\mathsf{Graph}$ to $\mathsf{Set}$ sending any graph to its set of vertices is an opfibration, but not the forgetful functor sending any graph to its set of edges.
 So, this gives a structured cospan category to which Theorem 4.1 does not apply.
@@
 
-\item pg. 2: “But this hope is doomed for reasons painstakingly explained in [1, Section 5] … despite all the tricks one might try.” This paragraph 
+\item pg. 2: ``But this hope is doomed for reasons painstakingly explained in [3, Section 5] … despite all the tricks one might try.'' This paragraph 
 provides 
@@
 
-{\bf We removed the part of the sentence ``despite all the tricks one might try'' according to this suggestion. In [3, Section 5], these attempts are 
-explained in detail, and we find them of value because the diligent reader may in fact come up with some of these for fixing the problem.} {\chris 
-\checkmark}
-
+{\bf We removed the part of the sentence ``despite all the tricks one might try'' according to this suggestion.
+In [3, Section 5] we spent five pages discussing these attempts and why they fail.
+The diligent reader may wish to read this discussion and see if there is some other way out.}
+
+ {\chris \checkmark} {\john \checkmark}
+
+\iffalse
 {\john He thought we were being dismissive because he didn't know that the ``tricks'' were all things I'd done myself!  If he looked at [1, Section 5] 
@@
 {\kenny Sounds good.}
+\fi
 
@@
 
-{\bf The ``other scholars'' are John Baez, one of the authors here, and his coauthors.
-The flaws---mathematical errors that render a number of claimed theorems incorrect---are now explained in  in the Introduction, in the paragraph beginning ``Unfortunately, many applications of decorated cospans were flawed.''.
-In the paper ``Structured cospans'', Kenny Courser and John Baez analyzed these mistakes in detail and fixed them using structured cospans.
+{\bf  The flaws---mathematical errors that render a number of claimed theorems incorrect---are now briefly explained in  in the Introduction, in the paragraph beginning ``Unfortunately, many applications of decorated cospans were flawed.''.
+In reference [3], Kenny Courser and John Baez analyzed these mistakes in detail and fixed them using structured cospans.
 See also comment (9).}
@@
 buster --- we already explained this.''}
-
-\fi
+\fi
+
 {\chris I would potentially skip the first sentence of our response above. Does it sound a bit hostile? And perhaps he also means other people that 
 may have used this approach, or perhaps Brendan himself (not a coauthor at the time?) that invented them. Not too important in any case.}
+
+{\john Okay, I deleted it.  Indeed, it \emph{was} a bit hostile.}
 
@@
 
-{\bf We have eliminated the term ``well-known'' and added a citation to Emily Riehl's book ``Category Theory in Context'' which includes said result, above Lemma 6.1.}
+{\bf We have eliminated the term ``well-known'' and added a citation to Emily Riehl's book \textsl{ Category Theory in Context} which includes said result, above Lemma 6.1.}
 
@@
 
-{\bf We added the sentence ``For composition of morphisms we use concatenation or occasionally $\circ$.'' in the convention section.} {\chris $\checkmark$} {\kenny $\checkmark$} {\john $\checkmark$}
+{\bf We added the sentence ``For composition of morphisms we use concatenation or occasionally $\circ$.'' in the convention section.}
+
+{\chris $\checkmark$} {\kenny $\checkmark$} {\john $\checkmark$}
 
@@
 that mentioning this in the introduction could put people off if they haven't heard of it. We added a comment about this in the 
-appendix.} {\chris $\checkmark$} {\kenny $\checkmark$} {\john $\checkmark$}
+appendix.}
+
+{\chris $\checkmark$} {\kenny $\checkmark$} {\john $\checkmark$}
 
@@
 
-{\bf  We have added a remark emphasizing this right after Theorem 2.1.}   {\john $\checkmark$} {\chris $\checkmark$} {\kenny $\checkmark$}
+{\bf  We have added a remark emphasizing this right after Theorem 2.1.}
+
+{\john $\checkmark$} {\chris $\checkmark$} {\kenny $\checkmark$}
 
@@
 \textbf{Kenny Courser carefully checked that these really are co/cartesian liftings, but the argument is straightforward and uninteresting so we will just 
-add remarks saying that this can be shown.}   {\john $\checkmark$} {\chris $\checkmark$} {\kenny $\checkmark$}
+add remarks saying that this can be shown.}
+
+{\john $\checkmark$} {\chris $\checkmark$} {\kenny $\checkmark$}
 
@@
 
-{\bf  We have added a remark on page 9 discussing this.}  {\john $\checkmark$} {\chris $\checkmark$} {\kenny $\checkmark$}
+{\bf  We have added a remark on page 9 discussing this.}
+
+{\john $\checkmark$} {\chris $\checkmark$} {\kenny $\checkmark$}
 
@@
 
-{\bf Done.} {\chris $\checkmark$} {\kenny $\checkmark$} {\john $\checkmark$}
+{\bf Done.}
+
+ {\chris $\checkmark$} {\kenny $\checkmark$} {\john $\checkmark$}
 
@@
 {\bf We have added a paragraph right below the statement of Theorem 4.1, clarifying its assumptions as suggested, which also incorporates an 
-explanatory paragraph previously located under Corollary 4.3.} {\chris $\checkmark$} {\kenny $\checkmark$} {\john $\checkmark$}
+explanatory paragraph previously located under Corollary 4.3.}
+
+{\chris $\checkmark$} {\kenny $\checkmark$} {\john $\checkmark$}
 

### 2022-03-17 cospans_new.tex
did a lot of work, almost done now

@@
 % in LaTeX
-% 2021/03/15 - dealing with referee's comments
+% 2021/03/16 - dealing with referee's comments
 
@@
 It becomes clear that when either structured or decorated cospans can be used, structured cospans are simpler.
-However, for open dynamical systems we apparently need decorated cospans, for reasons we explain.
-Thus, to describe a map from open Petri nets with rates to open dynamical systems, we use \emph{both} structured and decorated cospans.
+However, for open dynamical systems we need decorated cospans, for reasons we explain.
+Thus, to describe a map from open Petri nets with rates to open dynamical systems, we use decorated cospans.
 

### 2022-03-17 ResponseToReviews.tex
all but 10

@@
 
-{\chris Second review starts here}
 \item Given the title and abstract of this paper “Structured vs Decorated Cospans” I would expect this paper to provide a judgment that structured  cospans are strictly better than decorated cospans in all circumstances and a justification for that claim, or a detailed analysis of the pros and cons of
@@
 
-\fi
-
 {\john See if you like my new remarks in boldface, and give me a check mark if you do!  Kenny had checked this one off already, but I've changed it a 
@@
 \end{quote}}
+
+{\chris Cool thanks!}
+
+\fi
 
@@
 buster --- we already explained this.''}
-\fi
 
@@
 {\john Okay, I deleted it.  Indeed, it \emph{was} a bit hostile.}
+
+{\chris Thanks!}
+
+\fi
 
@@
 
-{\chris Third review starts here}
+\vskip 1em
+
 \item p. 2. ``Unfortunately, many applications of decorated cospans were flawed… for reasons painstakingly explained in [1].''
@@
 
-{\bf We have moved the natural isomorphism triangle as equation (1) in the statement of Theorem 2.1, and we have referred to it at page 10.} {\chris 
-$\checkmark$} {\kenny $\checkmark$} {\john $\checkmark$}
+{\bf We have moved the natural isomorphism triangle as equation (1) in the statement of Theorem 2.1, and we have referred to it at page 10.}
+
+{\chris $\checkmark$} {\kenny $\checkmark$} {\john $\checkmark$}
 
@@
 using a monoidal natural transformation $\theta$ that is \emph{not} an isomorphism.  We had mistakenly written that it was; we have fixed this now.}
+
 {\john $\checkmark$} {\kenny $\checkmark$} {\chris $\checkmark$}
@@
 
-So, giving the category of dynamical systems more morphisms sounds like a good idea. We will continue thinking about it.}  { \john $\checkmark$}
-
+So, giving the category of dynamical systems more morphisms sounds like a good idea. We will continue thinking about it.}
+
+{ \john $\checkmark$} {\chris $\checkmark$}
+
+\iffalse
 {\chris This looks similar to comment 30.}
@@
 
-{\john  Oh-ho!
-In this response I don't want to get pulled into any subtle math questions that aren't  actually necessary.
-I was just trying to give the referee a pat on the back.
-See if you like my new simplified reply, and bless it with a check mark if you do.}
+{\john  Oh-ho!  In this response I don't want to get pulled into any subtle math questions that aren't  actually necessary.  I was just trying to give 
+the referee a pat on the back.  See if you like my new simplified reply, and bless it with a check mark if you do.}
+\fi
 
@@
 
+\iffalse
 {\john
@@
 otherwise just comment out our little conversation here. By the way, you can comment out
-a big chunk of text just by putting $\backslash$iffalse in front of it and $\backslash$fi at the end.  This is a special case of a trick for making some text appear only if some condition is true!}
-
-{\chris Fourth review starts here}
+a big chunk of text just by putting $\backslash$iffalse in front of it and $\backslash$fi at the end.  This is a special case of a trick for making 
+some text appear only if some condition is true!}
+
+{\chris Haha had already started doing it before seeing this!}
+\fi
+
+\vskip 1em
+
 \item Composition of morphisms f, g in this paper is usually denoted gf, and occasionally gof. I’d suggest mentioning this in the “conventions” 
@@
 
-{\john $\checkmark$}
+{\john $\checkmark$} {\chris $\checkmark$}
 \end{enumerate}

### 2022-03-17 ResponseToReviews.tex
Couple checkmarks

@@
 
-{\chris \checkmark} {\john \checkmark}
+{\chris \checkmark} {\john \checkmark} {\kenny \checkmark}
 
@@
 decorated cospans from a lax monoidal functor $D \colon (\mathsf{FinSet},+) \to 
-(\mathsf{Set}, \times) $ amounts to working with a discrete categories $D(S)$, treated
+(\mathsf{Set}, \times) $ amounts to working with discrete categories $D(S)$, treated
 as sets.  Thus, our use of this construction amounts to working with a
@@
 
-{ \john $\checkmark$} {\chris $\checkmark$}
+{ \john $\checkmark$} {\chris $\checkmark$} {\kenny $\checkmark$}
 
@@
 
-{\john $\checkmark$} {\chris $\checkmark$}
+{\john $\checkmark$} {\chris $\checkmark$} {\kenny $\checkmark$}
 \end{enumerate}

### 2022-03-17 cospans_new.tex
acknowledged referees
completely solved problem in comment (16)

@@
 But this hope is doomed, for reasons painstakingly explained in \cite[Section 5]{BC}.
-There is really a \emph{category} of graphs with $m$ as their set of nodes---and surprisingly, trying to treat this category as a mere set does not 
-work.
-
-Here we present a solution to this problem.
+The key problem is that two graphs with $m$ as their set of nodes but different sets of edges give distinct elements of $F(m)$, and this prevents $F$ from being symmetric lax monoidal.
+To solve this problem, we need to bring isomorphisms of graphs into the framework---so we need $F(m)$ to be a \emph{category} of graphs with $m$ as their set of nodes.
+
+Here we implement this solution.
 Instead of basing the theory of decorated cospans on a symmetric lax monoidal functor $F \maps (\A, +) \to (\Set, \times)$, we use a symmetric lax monoidal pseudofunctor $F \maps (\A, +) \to (\Cat, \times)$.
@@
 
-We thank Daniel Cicala, Brendan Fong and Joe Moeller for helpful conversations.
+We thank Daniel Cicala, Brendan Fong and Joe Moeller for helpful conversations, and the referees for their many useful suggestions.
 We especially thank Michael Shulman for suggesting a proof strategy that greatly improved this paper.

### 2022-03-17 ResponseToReviews.tex
beginning to format ResponseToReviews

@@
 \setcounter{tocdepth}{2}
-\tableofcontents
-
+%\tableofcontents
+
+\iffalse
 \section{Reviews - to be removed}
@@
 \section{Our Answer}
+\fi
+
+We have changed the paper in response to the four referee's comments.  We list those comments below, along with our
+responses (in boldface).
 
@@
 \item COVID paragraph: I appreciate the effort into explaining the applied aspect.
-However, claims about the software (it is “easy”, we “easily”  modify, we “better understand”) sound too vague (is it computationally better?
+However, claims about the software (it is ``easy'', we ``easily'' modify, we ``better understand'') sound too vague (is it computationally better?
 do we assume that the final user understands structured cospans?
@@
 
-{\bf There is now a paper detailing how this software works, so according to this suggestion we have changed our paper so it simply refers to that other paper.}   {\john But we still need to add an arXiv link in reference 1!
-It should be on the arXiv soon.}
+{\bf There is now a paper by detailing how this software works, so according to this suggestion we have changed our paper so that it  refers to that other paper, along with the AlgebraicPetri GitHub repository which contains the code.}
+
+  {\john But we still need to add an arXiv link in reference 1!  It should be on the arXiv soon.}
 
@@
 
+{\john I think I considered the case where $f$ is an inclusion of $C$ in $D$, and the condition to get $f^\ast$ to be an opfibration is that there's only one morphism out of $d$ for each object $D$ that's in the image of $f$.
+But I could be wrong.
+The example of graphs should clarify things.}
+
 \item If we take the categorical systems theory perspective advanced by section 6, and the body of the authors’ recent work on functorial semantics 
@@
 
-\item pg. 27: To show that U does not have a left adjoint, we use the following well-known result. For readers of the TAC paper previously cited, 
+\item pg. 27: ``To show that $U$ does not have a left adjoint, we use the following well-known result.'' For readers of the TAC paper previously cited, 
 that might 

### 2022-03-21 ResponseToReviews.tex
dealt with comments (7) and (10)

@@
 
-{\bf Unfortunately not all cases of C-sets meet the conditions of Theorem 4.1.
-For example, the usual forgetful functor from $\mathsf{Graph}$ to $\mathsf{Set}$ sending any graph to its set of vertices is an opfibration, but not the forgetful functor sending any graph to its set of edges.
-So, this gives a structured cospan category to which Theorem 4.1 does not apply.
-Finding extra conditions such that it \emph{does} apply is an interesting question, but it would take more thought.}
+{\bf  Indeed, presheaf categories provide a very good environment for the structured cospan construction, and we now mention this at the very end of the Conclusions.
+However, not all right adjoints between presheaf categories $\widehat{\mathsf{D}} \to \widehat{\mathsf{C}}$ induced by functors $\mathsf{C} \to \mathsf{D}$ are opfibrations, so the Grothendieck construction cannot always be used to obtain a pseudofunctor $F \colon \mathsf{C} \to \mathbf{Cat}$ and build a decorated cospan category.
+We give a counterexample.
+There is probably more to be said about this, and we expect that Daniel Cicala and Christina Vasilakopoulou's forthcoming paper will give
+conditions under which this sort of structured cospan category \emph{is} also a decorated cospan
+category.}
 
@@
 
+\iffalse
 {\john Actually it's really easy to prove that presheaf categories obey the conditions of Theorem 4.1:
@@
 The example of graphs should clarify things.}
+\fi
 
@@
 {\bf  The flaws---mathematical errors that render a number of claimed theorems incorrect---are now briefly explained in  in the Introduction, in the paragraph beginning ``Unfortunately, many applications of decorated cospans were flawed.''.
-In reference [3], Kenny Courser and John Baez analyzed these mistakes in detail and fixed them using structured cospans.
+In reference [3], Kenny Courser and John Baez analyzed these errors in detail and fixed them using structured cospans.
 See also comment (9).}

### 2022-03-21 cospans_new.tex
dealt with comments (7) and (10)

@@
 % in LaTeX
-% 2021/03/16 - dealing with referee's comments
+% 2021/03/20 - dealing with referee's comments
 
@@
 \begin{thm}\label{thm:structured_cospans}
-Given categories $\A$ and $\X$ with finite colimits and $L \maps \A \to \X$ a functor preserving finite colimits, there is a symmetric monoidal double category $_L\lCsp(\X)$ in which
+Given categories $\A$ and $\X$ with finite colimits and $L \maps \A \to \X$ a functor preserving finite colimits, there is a symmetric monoidal double category ${}_L\lCsp(\X)$ in which
 \begin{itemize}
@@
 We leave such considerations for future work.
+
+Finally, it is worth mentioning a structured cospan double category to which the argument sketched above does \emph{not} apply.
+For any functor $\phi \maps \C \to D$ between small categories, precomposition with $\phi$ gives a functor $R \maps \widehat{D} \to \widehat{C}$ between presheaf categories which has a left adjoint $L \maps \widehat{C} \to \widehat{D}$.
+Since presheaf categories have all small colimits and $L$ preserves them, the conditions of \cref{thm:structured_cospans} apply and we obtain a symmetric monoidal double category of structured cospans, ${}_L\lCsp(\widehat{D})$.
+However, the right adjoint $R$ is not always an opfibration---and when it is not, we know ${}_L\lCsp(\widehat{D})$ cannot be a decorated cospan double category.
+A simple example where $R$ is not an opfibration was provided to us by Morgan Rogers.
+Take $\phi \maps \mathsf{1} + \mathsf{1} \to \mathsf{1}$ to be the unique functor where $\mathsf{1}$ is the terminal category.
+Then $R \maps \Set \to \Set^2$ is the diagonal, and the morphism
+$(0,0) \to (0,1)$ in $\Set^2$ admits no lift at all to $0 \in \Set$.
 
@@
 \bibitem{BFMLP}  A.\ Baas, J.\ Fairbanks, M.\ Halter, S.\ Libkind and E.\ Patterson, An
-algebraic framework for structured epidemic modeling.   Available as \href{???}{???}
+algebraic framework for structured epidemic modeling.   To appear.
 

### 2022-03-21 ResponseToReviews.tex
polished formatting of ResponseToReviews

@@
 
-We have changed the paper in response to the four referee's comments.  We list those comments below, along with our
-responses (in boldface).
+We have changed the paper in response to the four referees' comments.  We list those comments below, along with our responses which are in boldface.
+
+\section*{First Review}
 
@@
 
-{\kenny $\checkmark$}  {\john $\checkmark$} {\chris $\checkmark$}
-
 \iffalse
@@
 
-{\john $\checkmark$} {\chris $\checkmark$} {\kenny $\checkmark$}
-
 \item Theorem 4.1: perhaps it would be clearer to say it “factors through R : Rex $\to$ SymMonCat”.
@@
 {\bf Done, also in Corollary 4.3.}
-
-{\chris $\checkmark$} {\kenny $\checkmark$} {\john $\checkmark$}
 
@@
 
-{\john $\checkmark$} {\chris $\checkmark$} {\kenny $\checkmark$}
-
 \item After Theorem A.2: In order to be consistent, it would be practical to state explicitly what is a bifibration.
@@
 {\bf Done.}
-
-{\john $\checkmark$} {\chris $\checkmark$} {\kenny $\checkmark$}
 
@@
 
+\iffalse
   {\john But we still need to add an arXiv link in reference 1!  It should be on the arXiv soon.}
@@
 
-%{\chris Great! The 
+{\chris Great! The 
 %hyperref link ??? opens up notes by Kenny for me, I don't know how or why.}
 
-%{\john It's weird that the line ??? opens up anything for you.  It'll go away when we get the arXiv number.} Indeed!
+{\john It's weird that the line ??? opens up anything for you.  It'll go away when we get the arXiv number.} Indeed!
+\fi
 
@@
 
-{\john $\checkmark$} {\chris $\checkmark$} {\kenny $\checkmark$}
-
-\vskip 1em
+\end{enumerate}
+
+\section*{Second Review}
+
+\begin{enumerate}
 
@@
 
-{\john $\checkmark$} {\kenny $\checkmark$} {\chris $\checkmark$}
 \iffalse
@@
 
-{\john $\checkmark$} {\kenny $\checkmark$}
-
 \iffalse
@@
 
-{\john $\checkmark$} {\kenny $\checkmark$} {\chris $\checkmark$}
-
 \iffalse
@@
 
-{\john \checkmark} {\kenny \checkmark} {\chris \checkmark}
-
 \iffalse
@@
 The diligent reader may wish to read this discussion and see if there is some other way out.}
-
-{\chris \checkmark} {\john \checkmark} {\kenny \checkmark}
 
@@
 In reference [3], Kenny Courser and John Baez analyzed these errors in detail and fixed them using structured cospans.
-See also comment (9).}
-
-{\john $\checkmark$} {\kenny $\checkmark$} {\chris \checkmark}
+See also comment (6) in the second review.}
 
@@
 
-{\john $\checkmark$} {\chris $\checkmark$} {\kenny $\checkmark$}
-
-\vskip 1em
+\end{enumerate}
+
+\section*{Third Review}
+
+\begin{enumerate}
 
@@
 {\bf We have rewritten this paragraph to explain those flaws.}
-
-{\john $\checkmark$} {\kenny $\checkmark$} {\chris $\checkmark$}
 
@@
 
-{\chris $\checkmark$} {\kenny $\checkmark$} {\john $\checkmark$}
-
 \item p. 9, ingredients for constructing a double functor of decorated cospan double categories.
@@
 between edges.}
-
-{\chris $\checkmark$} {\john $\checkmark$} {\kenny  $\checkmark$}
 
@@
 So, giving the category of dynamical systems more morphisms sounds like a good idea. We will continue thinking about it.}
-
-{ \john $\checkmark$} {\chris $\checkmark$} {\kenny $\checkmark$}
 
@@
 
-{\chris $\checkmark$} {\john $\checkmark$}  {\kenny $\checkmark$}
-
 \item A last general comment is that the paper unfortunately adopts the strategy, all too common in math papers, of putting all the examples in a 
@@
 
-{\chris $\checkmark$} {\kenny $\checkmark$} {\john $\checkmark$}
-
 \iffalse
@@
 
+\end{enumerate}
+
+\section*{Fourth Review}
+
+\begin{enumerate}
+
 \item Composition of morphisms f, g in this paper is usually denoted gf, and occasionally gof. I’d suggest mentioning this in the “conventions” 
@@
 {\bf We added the sentence ``For composition of morphisms we use concatenation or occasionally $\circ$.'' in the convention section.}
-
-{\chris $\checkmark$} {\kenny $\checkmark$} {\john $\checkmark$}
 
@@
 {\bf  We have added a remark emphasizing this right after Theorem 2.1.}
-
-{\john $\checkmark$} {\chris $\checkmark$} {\kenny $\checkmark$}
 
@@
 
-{\john $\checkmark$} {\chris $\checkmark$} {\kenny $\checkmark$}
-
 \iffalse
@@
 {\bf  We have added a remark on page 9 discussing this.}
-
-{\john $\checkmark$} {\chris $\checkmark$} {\kenny $\checkmark$}
 
@@
 
- {\chris $\checkmark$} {\kenny $\checkmark$} {\john $\checkmark$}
-
 \item I think it would be worth saying in words a bit more prominently what the hypothesis of theorem 4.1 roughly means, namely that the fibers of 
@@
 explanatory paragraph previously located under Corollary 4.3.}
-
-{\chris $\checkmark$} {\kenny $\checkmark$} {\john $\checkmark$}
 
@@
 
-{\bf This is an interesting idea but we haven't been able to get it to work yet.  See also comment 20.}
-
-{\john $\checkmark$} {\chris $\checkmark$} {\kenny $\checkmark$}
+{\bf This is an interesting idea but we haven't been able to get it to work yet.  See also comment (5) in the third review.}
+
 \end{enumerate}

### 2022-03-21 cospans_new.tex
added sentence to end of conclusion
a couple of small things

@@
 
-Finally, it is worth mentioning a structured cospan double category to which the argument sketched above does \emph{not} apply.
-For any functor $\phi \maps \C \to D$ between small categories, precomposition with $\phi$ gives a functor $R \maps \widehat{D} \to \widehat{C}$ between presheaf categories which has a left adjoint $L \maps \widehat{C} \to \widehat{D}$.
-Since presheaf categories have all small colimits and $L$ preserves them, the conditions of \cref{thm:structured_cospans} apply and we obtain a symmetric monoidal double category of structured cospans, ${}_L\lCsp(\widehat{D})$.
-However, the right adjoint $R$ is not always an opfibration---and when it is not, we know ${}_L\lCsp(\widehat{D})$ cannot be a decorated cospan double category.
-A simple example where $R$ is not an opfibration was provided to us by Morgan Rogers.
-Take $\phi \maps \mathsf{1} + \mathsf{1} \to \mathsf{1}$ to be the unique functor where $\mathsf{1}$ is the terminal category.
-Then $R \maps \Set \to \Set^2$ is the diagonal, and the morphism
-$(0,0) \to (0,1)$ in $\Set^2$ admits no lift at all to $0 \in \Set$.
+Finally, it is worth mentioning a structured cospan double category to which the argument sketched above does \emph{not} apply.   For any functor 
+$\phi \maps \C \to D$ between small categories, precomposition with $\phi$ gives a functor $R \maps \widehat{D} \to \widehat{C}$ between presheaf 
+categories which has a left adjoint $L \maps \widehat{C} \to \widehat{D}$.   Since presheaf categories have all small colimits and $L$ preserves them, 
+the conditions of \cref{thm:structured_cospans} apply and we obtain a symmetric monoidal double category of structured cospans, 
+${}_L\lCsp(\widehat{D})$.  However, the right adjoint $R$ is not always an opfibration---and when it is not, the above arguments cannot be used to 
+show that ${}_L\lCsp(\widehat{D})$ is a decorated cospan double category.  A simple example where $R$ is not an opfibration was 
+provided to us by Morgan Rogers.  Take $\phi \maps \mathsf{1} + \mathsf{1} \to \mathsf{1}$ to be the unique functor where $\mathsf{1}$ is the 
+terminal category.  Then $R \maps \Set \to \Set^2$ is the diagonal, and the morphism
+$(0,0) \to (0,1)$ in $\Set^2$ admits no lift at all to $0 \in \Set$.   It will be interesting to find conditions on $\phi \maps \C \to \D$ that 
+guarantee ${}_L\lCsp(\widehat{D})$ is isomorphic to a decorated cospan category, using the above machinery.
 

### 2022-03-21 cospans_new.tex
Fixing some notation in added conclusions paragraph

--- 2022-03-21 cospans_new.tex
@@
 
-Finally, it is worth mentioning a structured cospan double category to which the argument sketched above does \emph{not} apply.
-For any functor $\phi \maps \C \to D$ between small categories, precomposition with $\phi$ gives a functor $R \maps \widehat{D} \to \widehat{C}$ between presheaf categories which has a left adjoint $L \maps \widehat{C} \to \widehat{D}$.
-Since presheaf categories have all small colimits and $L$ preserves them, the conditions of \cref{thm:structured_cospans} apply and we obtain a symmetric monoidal double category of structured cospans, ${}_L\lCsp(\widehat{D})$.
-However, the right adjoint $R$ is not always an opfibration---and when it is not, we know ${}_L\lCsp(\widehat{D})$ cannot be a decorated cospan double category.
-A simple example where $R$ is not an opfibration was provided to us by Morgan Rogers.
-Take $\phi \maps \mathsf{1} + \mathsf{1} \to \mathsf{1}$ to be the unique functor where $\mathsf{1}$ is the terminal category.
-Then $R \maps \Set \to \Set^2$ is the diagonal, and the morphism
-$(0,0) \to (0,1)$ in $\Set^2$ admits no lift at all to $0 \in \Set$.
+Finally, it is worth mentioning a structured cospan double category to which the argument sketched above does \emph{not} apply.   For any functor 
+$\phi \maps \C \to \D$ between small categories, precomposition with $\phi$ gives a functor $R \maps \widehat{\D} \to \widehat{\C}$ between presheaf 
+categories which has a left adjoint $L \maps \widehat{\C} \to \widehat{\D}$.   Since presheaf categories have all small colimits and $L$ preserves them, 
+the conditions of \cref{thm:structured_cospans} apply and we obtain a symmetric monoidal double category of structured cospans, 
+${}_L\lCsp(\widehat{\D})$.  However, the right adjoint $R$ is not always an opfibration---and when it is not, the above arguments cannot be used to 
+show that ${}_L\lCsp(\widehat{\D})$ is a decorated cospan double category.  A simple example where $R$ is not an opfibration was 
+provided to us by Morgan Rogers.  Take $\phi \maps \mathsf{1} + \mathsf{1} \to \mathsf{1}$ to be the unique functor where $\mathsf{1}$ is the 
+terminal category.  Then $R \maps \Set \to \Set^2$ is the diagonal, and the morphism
+$(0,0) \to (0,1)$ in $\Set^2$ admits no lift at all to $0 \in \Set$.   It will be interesting to find conditions on $\phi \maps \C \to \D$ that 
+guarantee ${}_L\lCsp(\widehat{\D})$ is isomorphic to a decorated cospan category, using the above machinery.
 

### 2022-03-21 ResponseToReviews.tex
a couple of small things
small fixes - perhaps we're done

@@
 of are discussed here.}
-
 \end{enumerate}
@@
 
-\vskip 1em
 \begin{quote}
@@
 
-\item pg. 2: ``But this hope is doomed for reasons painstakingly explained in [3, Section 5] … despite all the tricks one might try.'' This paragraph 
+\item p. 2: ``But this hope is doomed for reasons painstakingly explained in [3, Section 5] … despite all the tricks one might try.'' This paragraph 
 provides 
@@
 
-\item pg. 3: ``Many of the flawed applications of decorated cospans have been fixed using structured cospans.” This dismisses the work of other 
+\item p. 3: ``Many of the flawed applications of decorated cospans have been fixed using structured cospans.” This dismisses the work of other 
 scholars 
@@
 
-{\bf  The flaws---mathematical errors that render a number of claimed theorems incorrect---are now briefly explained in  in the Introduction, in the paragraph beginning ``Unfortunately, many applications of decorated cospans were flawed.''.
-In reference [3], Kenny Courser and John Baez analyzed these errors in detail and fixed them using structured cospans.
-See also comment (6) in the second review.}
+{\bf  The flaws---mathematical errors that render a number of claimed theorems incorrect---are now briefly explained in  in the Introduction, in the 
+paragraph beginning ``Unfortunately, many applications of decorated cospans were flawed.''  In reference [3], Kenny Courser and John Baez analyzed 
+these errors in detail and fixed them using structured cospans.  }
 
@@
 
-\item pg. 27: ``To show that $U$ does not have a left adjoint, we use the following well-known result.'' For readers of the TAC paper previously cited, 
+\item p. 27: ``To show that $U$ does not have a left adjoint, we use the following well-known result.'' For readers of the TAC paper previously cited, 
 that might 
@@
 
-{\bf We have rewritten this paragraph to explain those flaws.}
+{\bf We have rewritten this paragraph to explain those flaws.  See also comment (6) in the second review.}
 

### 2022-03-21 cospans_new.tex
small fixes - perhaps we're done

@@
 % in LaTeX
-% 2021/03/20 - dealing with referee's comments
+% 2021/03/21 - dealing with referee's comments
 
@@
 
-Finally, it is worth mentioning a structured cospan double category to which the argument sketched above does \emph{not} apply.   For any functor 
-$\phi \maps \C \to \D$ between small categories, precomposition with $\phi$ gives a functor $R \maps \widehat{\D} \to \widehat{\C}$ between presheaf 
-categories which has a left adjoint $L \maps \widehat{\C} \to \widehat{\D}$.   Since presheaf categories have all small colimits and $L$ preserves them, 
-the conditions of \cref{thm:structured_cospans} apply and we obtain a symmetric monoidal double category of structured cospans, 
-${}_L\lCsp(\widehat{\D})$.  However, the right adjoint $R$ is not always an opfibration---and when it is not, the above arguments cannot be used to 
-show that ${}_L\lCsp(\widehat{\D})$ is a decorated cospan double category.  A simple example where $R$ is not an opfibration was 
-provided to us by Morgan Rogers.  Take $\phi \maps \mathsf{1} + \mathsf{1} \to \mathsf{1}$ to be the unique functor where $\mathsf{1}$ is the 
-terminal category.  Then $R \maps \Set \to \Set^2$ is the diagonal, and the morphism
-$(0,0) \to (0,1)$ in $\Set^2$ admits no lift at all to $0 \in \Set$.   It will be interesting to find conditions on $\phi \maps \C \to \D$ that 
-guarantee ${}_L\lCsp(\widehat{\D})$ is isomorphic to a decorated cospan category, using the above machinery.
+Finally, it is worth mentioning a structured cospan double category to which the argument sketched above does \emph{not} apply.
+For any functor $\phi \maps \C \to \D$ between small categories, precomposition with $\phi$ gives a functor $R \maps \widehat{\D} \to \widehat{\C}$ between presheaf categories which has a left adjoint $L \maps \widehat{\C} \to \widehat{\D}$.
+Since presheaf categories have all small colimits and $L$ preserves them, the conditions of \cref{thm:structured_cospans} apply and we obtain a symmetric monoidal double category of structured cospans, ${}_L\lCsp(\widehat{\D})$.
+However, the right adjoint $R$ is not always an opfibration---and when it is not, the above arguments cannot be used to show that ${}_L\lCsp(\widehat{\D})$ is a decorated cospan double category.
+A simple example where $R$ is not an opfibration was  provided to us by Morgan Rogers.
+Take $\phi \maps \mathsf{1} + \mathsf{1} \to \mathsf{1}$ to be the unique functor where $\mathsf{1}$ is the terminal category.
+Then $R \maps \Set \to \Set^2$ is the diagonal, and the morphism $(0,0) \to (0,1)$ in $\Set^2$ admits no lift at all to $0 \in \Set$.
+It will be interesting to find conditions on $\phi \maps \C \to \D$ that
+guarantee ${}_L\lCsp(\widehat{\D})$ is isomorphic to a decorated double cospan category.
 

### 2022-03-23 cospans_new.tex
added Morgan Rogers to acknowledgements
gave online link to the paper on epidemic modeling

@@
 % in LaTeX
-% 2021/03/21 - dealing with referee's comments
+% 2021/03/23 - dealing with referee's comments
 
@@
 
-We thank Daniel Cicala, Brendan Fong and Joe Moeller for helpful conversations, and the referees for their many useful suggestions.
+We thank Daniel Cicala, Brendan Fong, Joe Moeller and Morgan Rogers for helpful conversations, and the referees for their many useful suggestions.
 We especially thank Michael Shulman for suggesting a proof strategy that greatly improved this paper.
@@
 \bibitem{BFMLP}  A.\ Baas, J.\ Fairbanks, M.\ Halter, S.\ Libkind and E.\ Patterson, An
-algebraic framework for structured epidemic modeling.   To appear.
+algebraic framework for structured epidemic modeling.
+Available at \href{https://github.com/AlgebraicJulia/Structured-Epidemic-Modeling}{https://github.com/AlgebraicJulia/Structured-Epidemic-Modeling}.
 

### 2022-04-03 cospans_compositionality_3.tex
working version of cospans_compositionality_3.tex - for publication

--- 2022-03-23 cospans_new.tex
@@
 % in LaTeX
-% 2021/03/23 - dealing with referee's comments
-
-\documentclass[reqno]{amsart}
-
-\usepackage{amssymb,amsmath,stmaryrd,txfonts,mathrsfs,amsthm}%,undertilde}
+% 2021/04/03 - third version sent to Compositionality
+
+\documentclass[a4paper,onecolumn, superscriptaddress,10pt, accepted=2022-03-25, issue=SS, volume=VV, shorttitle=papers/compositionality-VV-SS]{compositionalityarticle}
+\pdfoutput=1
+
+\usepackage{amssymb,amsmath,stmaryrd,txfonts,mathrsfs}%,amsthm,undertilde}
 \usepackage{comment}
@@
 \usepackage[a4paper,top=3cm,bottom=3cm,inner=3cm,outer=3cm]{geometry}
-\usepackage[foot]{amsaddr}
+%\usepackage[foot]{amsaddr}
 \usepackage{graphicx}
 \usepackage{stackrel}
+
+\makeatletter
+\DeclareRobustCommand{\qed}{%
+  \ifmmode % if math mode, assume display: omit penalty etc.
+  \else \leavevmode\unskip\penalty9999 \hbox{}\nobreak\hfill
+  \fi
+  \quad\hbox{\qedsymbol}}
+\newcommand{\oopenbox}{\leavevmode
+  \hbox to.77778em{%
+  \hfil\vrule
+  \vbox to.675em{\hrule width.6em\vfil\hrule}%
+  \vrule\hfil}}
+\newcommand{\qedsymbol}{\oopenbox}
+\newenvironment{proof}[1][\proofname]{\par
+  \normalfont
+  \topsep6\p@\@plus6\p@ \trivlist
+  \item[\hskip\labelsep\itshape
+    #1.]\ignorespaces
+}{%
+  \qed\endtrivlist
+}
+\newcommand{\proofname}{Proof}
+\makeatother
 
@@
 \defthm{fact}{Fact}
-\theoremstyle{definition}
+%\theoremstyle{definition}
 \defthm{defn}{Definition}
 \defthm{notn}{Notation}
-\theoremstyle{remark}
+%\theoremstyle{remark}
 \defthm{rmk}{Remark}
@@
 
-% Also number formulas with the theorem counter
-%\let\c@equation\c@thm
-%\numberwithin{equation}{section}
-
-% Only show numbers for equations that are actually referenced (or
-% whose tags are specified manually) - uses mathtools. %Christina: for some reason, the command below made it impossible to label any equation!
-%\mathtoolsset{showonlyrefs,showmanualtags}
-
 \def\tobar{\mathrel{\mkern3mu  \vcenter{\hbox{$\scriptscriptstyle+$}}%
@@
 
-\definecolor{purple(x11)}{rgb}{0.5, 0.0, 0.5}
-\def\purple{\color{purple(x11)}}
-\def\chris{\purple Christina: }
-\def\john{\color{red}}
 \newcommand{\upback}{\mathbin{\rotatebox[origin=c]{135}{$\ulcorner$}}}
@@
 
-\author{John\ C.\ Baez$^{1,2}$, Kenny Courser$^1$, and Christina Vasilakopoulou$^3$}
-\address{$^1$Department of Mathematics, University of California, Riverside CA, USA 92521}
-\address{$^2$Centre for Quantum Technologies, National University of Singapore, Singapore 117543}
-\address{$^3$Department of Mathematics, University of Patras, Greece 265 04}
-\email{baez@math.ucr.edu, kcour001@ucr.edu, cvasilak@math.upatras.gr}
+\author[1]{John C. Baez}
+\author[2]{Kenny Courser}
+\affil[1,2]{Department of Mathematics, University of California, Riverside CA, USA 92521}
+\affil[1]{Centre for Quantum Technologies, National University of Singapore, Singapore 117543}
+\author[3]{Christina Vasilakopoulou}
+\affil[3]{Department of Mathematics, University of Patras, Greece 265 04}
+%\email{baez@math.ucr.edu, kcour001@ucr.edu, cvasilak@math.upatras.gr}
 

### 2022-04-05 cospans_compositionality_3.tex
added author addresses
added DOI to reference [7] as an example.
dois

@@
 \usepackage{stackrel}
+
+% to get \begin{thm} and \end{thm} to work
 
@@
 \author[1]{John C. Baez}
+\email{baez@math.ucr.edu}
 \author[2]{Kenny Courser}
+\email{kcour001@ucr.edu}
 \affil[1,2]{Department of Mathematics, University of California, Riverside CA, USA 92521}
@@
 \author[3]{Christina Vasilakopoulou}
+\email{cvasilak@math.upatras.gr}
 \affil[3]{Department of Mathematics, University of Patras, Greece 265 04}
@@
 
-\bibitem{BFP} J.\ C.\ Baez, B.\ Fong and B.\ S.\ Pollard, A compositional framework for Markov processes, \textsl{Jour.
-Math.
-Phys.} \textbf{57} (2016), 033301.
-Available as \href{http://arxiv.org/abs/1508.06448}{arXiv:1508.06448}.
-
-\bibitem{BM}  J.\ C.\ Baez and J.\ Master, Open Petri nets, \textsl{Math.\ Struct.\ Comput.\ Sci.\ }\textbf{30} (2020), 314--341. Available as 
+\bibitem{BFP} J.\ C.\ Baez, B.\ Fong and B.\ S.\ Pollard, A compositional framework for Markov processes, 
+\textsl{Jour. Math. Phys.} \textbf{57} (2016), 033301. 
+\href{https://doi.org/10.1063/1.4941578}{https://doi.org/10.1063/1.4941578}. Available as 
+\href{http://arxiv.org/abs/1508.06448}{arXiv:1508.06448}.
+
+\bibitem{BM}  J.\ C.\ Baez and J.\ Master, Open Petri nets, \textsl{Math.\ Struct.\ Comput.\ Sci.\ }\textbf{30} (2020), 314--341. 
+\href{https://doi.org/10.1017/s0960129520000043}{https://doi.org/10.1017/s0960129520000043}.
+Available as 
 \href{https://arxiv.org/abs/1808.05415}{arXiv:1808.05415}.
 
-\bibitem{BP} J.\ C.\ Baez and B.\ S.\ Pollard, A compositional framework for chemical reaction networks, \textsl{Rev.\ Math.\ Phys.\ }\textbf{29} (2017), 1750028.
+\bibitem{BP} J.\ C.\ Baez and B.\ S.\ Pollard, A compositional framework for chemical reaction networks, \textsl{Rev.\ Math.\ Phys.\ }\textbf{29} 
+(2017), 1750028. \href{https://doi.org/10.1142/S0129055X17500283}{https://doi.org/10.1142/S0129055X17500283}.
 Available as \href{http://arxiv.org/abs/1704.02051}{arXiv:1704.02051}.
 
-\bibitem{BFV} G.\ Bakirtzis, C.\ H.\ Fleming and C.\ Vasilakopoulou, Categorical semantics of cyber-physical systems theory. Available as 
+\bibitem{BFV} G.\ Bakirtzis, C.\ H.\ Fleming and C.\ Vasilakopoulou, Categorical semantics of cyber-physical systems theory, \textsl{ACM Trans.\ 
+Cyber-Phys.\ Syst.\ } \textbf{5} (2021). \href{https://doi.org/10.1145/3461669}{https://doi.org/10.1145/3461669}. Available as 
 \href{https://arxiv.org/abs/2010.08003}{arXiv:2010.08003}.
 
-\bibitem{BSZ} F.\ Bonchi, P.\ Soboci\'nski and F.\ Zanasi, A categorical semantics of signal flow graphs, in \textsl{CONCUR 2014--Concurrency Theory}, eds.\ P.\ Baldan and D.\ Gorla, Lecture Notes in Computer Science \textbf{8704}, Springer, Berlin, 2014, pp.\ 435--450.
-Available at \href{http://users.ecs.soton.ac.uk/ps/papers/sfg.pdf}{http://users.ecs.soton.ac.uk/ps/papers/sfg.pdf}.
+\bibitem{BSZ} F.\ Bonchi, P.\ Soboci\'nski and F.\ Zanasi, A categorical semantics of signal flow graphs, in \textsl{CONCUR 2014--Concurrency Theory}, 
+eds.\ P.\ Baldan and D.\ Gorla, Lecture Notes in Computer Science \textbf{8704}, Springer, Berlin, 2014, pp.\ 435--450. 
+\href{https://doi.org/10.1007/978-3-662-44584-6\_30}{https://doi.org/10.1007/978-3-662-44584-6\_30}.  Available at 
+\href{http://users.ecs.soton.ac.uk/ps/papers/sfg.pdf}{http://users.ecs.soton.ac.uk/ps/papers/sfg.pdf}.
 
 \bibitem{Borc} F. \ Borceux, \textsl{Handbook of Categorical Algebra}, vol.\ 2, 
-Cambridge University Press, Cambridge, 1994.
-
-%\bibitem{Brown1} R.\ Brown and C.\ B.\ Spencer, Double groupoids and crossed modules, 
-%\textsl{Cah.\ Top.\ G\'eom.\ Diff.} \textbf{17} (1976), 343--362.
-
-%\bibitem{Brown2} R.\ Brown, K.\ Hardie, H.\ Kamps and T.\ Porter, The homotopy double groupoid of a Hausdorff space, \textsl{Theory Appl.\ Categ.} \textbf{10} (2002), 71--93.
-
-%\bibitem{Be} J.\ B\'enabou, Introduction to bicategories, in {\sl Reports
-%of the Midwest Category Seminar}, Lecture Notes in Mathematics \textbf{47}, Springer, Berlin, 1967, pp.\ 1--77.
-
-\bibitem{BungeFiore} M.\ Bunge and M.\ Fiore, Unique factorisation lifting functors and categories of linearly-controlled processes, \textsl{Math.\ Struct.\ Comput.\ Sci.\ } \textbf{10} (2000), 137--163.
-
-%\bibitem{CC} D.\ Cicala and K.\ Courser, Spans of cospans in a topos. Available as \href{https://arxiv.org/abs/1707.02098}{arXiv:1707.02098}.
+Cambridge University Press, Cambridge, 1994. \href{https://doi.org/10.1017/CBO9780511525865}{https://doi.org/10.1017/CBO9780511525865}.
+
+\bibitem{BungeFiore} M.\ Bunge and M.\ Fiore, Unique factorisation lifting functors and categories of linearly-controlled processes, \textsl{Math.\ 
+Struct.\ Comput.\ Sci.\ } \textbf{10} (2000), 137--163. \href{https://doi.org/10.1017/S0960129599003023}{https://doi.org/10.1017/S0960129599003023}.
 
@@
 
-\bibitem{CTF} G.\ Craciun, Y.\ Tang and M.\ Feinberg, Understanding bistability in complex enzyme-driven reaction networks, \textsl{PNAS} \textbf{103} (2006), 8697--8702.
+\bibitem{CTF} G.\ Craciun, Y.\ Tang and M.\ Feinberg, Understanding bistability in complex enzyme-driven reaction networks, \textsl{PNAS} \textbf{103} 
+(2006), 8697--8702. \href{https://doi.org/10.1073/pnas.0602767103}{https://doi.org/10.1073/pnas.0602767103}.
 
 \bibitem{DS} B.\ Day and R.\ Street, Monoidal bicategories and Hopf algebroids, \textsl{Adv.\ Math.} \textbf{129} (1997), 99--157. 
-
-%\bibitem{Ehresmann63} C.\ Ehresmann, Cat\'egories structur\'ees III: Quintettes et applications covariantes,  \textsl{Cah.\ Top.\ G\'eom.\ Diff.} \textbf{5} (1963), 1--22.
-
-%\bibitem{Ehresmann65} C.\ Ehresmann, {\sl Cat\'egories et Structures,} Dunod, Paris, 1965.
-
-\bibitem{Fong} B.\ Fong, Decorated cospans, \emph{Theory Appl.\ Categ.} \textbf{30} (2015), 1096--1120.  Available as \href{http://arxiv.org/abs/1502.00872}{arXiv:1502.00872}.
+\href{https://doi.org/10.1006/aima.1997.1649}{https://doi.org/10.1006/aima.1997.1649}.
+
+\bibitem{Fong} B.\ Fong, Decorated cospans, \emph{Theory Appl.\ Categ.} \textbf{30} (2015), 1096--1120.  Available as 
+\href{http://arxiv.org/abs/1502.00872}{arXiv:1502.00872}.
 
@@
 
-\bibitem{FRS} B.\ Fong, P.\ Rapisarda and P.\ Sobocinski, A categorical approach to open and interconnected dynamical systems, in \textsl{Proceedings of the 31st Annual ACM/IEEE Symposium on Logic in Computer Science (LICS)}, IEEE, New York, 2016, pp.\ 1--10.
-Available as \href{http://arxiv.org/abs/510.05076}{arXiv:1510.05076}.
-
-\bibitem{GiraultValk} C.\ Girault and R.\ Valk, \textsl{Petri Nets for Systems Engineering: a Guide to Modeling, Verification, and Applications}, Springer, Berlin, 2013.
+\bibitem{FRS} B.\ Fong, P.\ Rapisarda and P.\ Sobocinski, A categorical approach to open and interconnected dynamical systems, in \textsl{Proceedings 
+of the 31st Annual ACM/IEEE Symposium on Logic in Computer Science (LICS)}, IEEE, New York, 2016, pp.\ 1--10. 
+\href{https://doi.org/10.1145/2933575.2934556}{https://doi.org/10.1145/2933575.2934556}. Available as 
+\href{http://arxiv.org/abs/510.05076}{arXiv:1510.05076}.
+
+\bibitem{GiraultValk} C.\ Girault and R.\ Valk, \textsl{Petri Nets for Systems Engineering: a Guide to Modeling, Verification, and Applications}, 
+Springer, Berlin, 2013. \href{https://doi.org/10.1007/978-3-662-05324-9}{https://doi.org/10.1007/978-3-662-05324-9}.
 
 \bibitem{GPS} R.\ Gordon, A.\ J.\ Power and R.\ Street, Coherence for tricategories, \textsl{Mem.\ Amer.\ Math.\ Soc.\ }\textbf{558}, 1995. 
+\href{https://doi.org/10.1090/memo/0558}{https://doi.org/10.1090/memo/0558}.
 
@@
 
-\bibitem{Gray} J.
-\ Gray, Fibred and cofibred categories, in \textsl{Proceedings of the Conference on Categorical Algebra: La Jolla 1965}, eds.\ S.\ Eilenberg \textit{et al}, Springer, Berlin, 1966, pp.\ 21--83.
+\bibitem{Gray} J. \ Gray, Fibred and cofibred categories, in \textsl{Proceedings of the Conference on Categorical Algebra: La Jolla 1965}, eds.\ S.\ 
+Eilenberg \textit{et al}, Springer, Berlin, 1966, pp.\ 21--83. 
+\href{https://doi.org/10.1007/978-3-642-99902-4\_2}{https://doi.org/10.1007/978-3-642-99902-4\_2}.
 
 \bibitem{Haas} P.\ J.\ Haas, \textsl{Stochastic Petri Nets: Modelling, Stability, Simulation},
-Springer, Berlin, 2002.
+Springer, Berlin, 2002. \href{https://doi.org/10.1007/b97265}{https://doi.org/10.1007/b97265}.
 
@@
 \bibitem{Hermida1999} C. \ Hermida, Some properties of Fib as a fibred 2-category, \textsl{J.\ Pure Appl.\ Alg.\ } \textbf{134} (1999), 83--109. 
+\href{https://doi.org/10.1016/S0022-4049(97)00129-1}{https://doi.org/10.1016/S0022-4049(97)00129-1}.
 
 \bibitem{Jacobs} B. \ Jacobs, \textsl{Categorical Logic and Type Theory}, Elsevier, Amsterdam, 1999. 
+\href{https://doi.org/10.2307/421214}{https://doi.org/10.2307/4212146}.
 
 \bibitem{JNW} A.\ Joyal, M.\ Nielsen and G.\ Winskel, Bisimulation from open maps, \textsl{Inf.\ Comput.\ }\textbf{127} (1996), 164--185. 
+\href{https://doi.org/10.1006/inco.1996.0057}{https://doi.org/10.1006/inco.1996.0057}.
 
@@
 
-\bibitem{KS} G.\ M.\ Kelly and R.\ Street, Review of the elements of 2-categories, in \textsl{Category Seminar}, ed.\ G.\ M.\ Kelly, Lecture Notes in Mathematics \textbf{40}, Springer, Berlin, 1974, pp.\ 75--103.
+\bibitem{KS} G.\ M.\ Kelly and R.\ Street, Review of the elements of 2-categories, in \textsl{Category Seminar}, ed.\ G.\ M.\ Kelly, Lecture Notes in 
+Mathematics \textbf{40}, Springer, Berlin, 1974, pp.\ 75--103. \href{https://doi.org/10.1007/BFb0063101}{https://doi.org/10.1007/BFb0063101}.
 
@@
 networks, \textsl{Mol.\ Inform.\  }\textbf{29} (2010), 838--843. 
-
-% \bibitem{LP} S.\ Lack and S.\ Paoli, 2-nerves for bicategories, \textsl{$K$-Theory} \textbf{38} (2008), 153--175.
+\href{https://doi.org/10.1002/minf.201000086}{https://doi.org/10.1002/minf.201000086}.
 
@@
 
-%\bibitem{LS} E.\ Lerman and D.\ Spivak, An algebra of open continuous time dynamical systems and networks. Available as \href{http://arxiv.org/abs/1602.01017}{arXiv:1602.01017}.
-
-%\bibitem{Lack} S.\ Lack, Limits for lax morphisms, \textsl{Applied Categorical Structures} $\mathbf{30}$ (2005), 189--203.
-Available %at \href{http://maths.mq.edu.au/~slack/papers/talgl.pdf}{http://maths.mq.edu.au/$\sim$slack/papers/talgl.pdf}.
-
-%\bibitem{Lerm} E.\ Lerman and D.\ Spivak, An algebra of open continuous time dynamical systems and networks. Available as %%\href{http://arxiv.org/abs/1602.01017}{arXiv:1602.01017}.
-
-%   \bibitem{ML} S.\ Mac Lane, {\sl Categories for the Working Mathematician},
-%     Springer, Berlin, 1998.
-
 \bibitem{McCrudden} P.\ McCrudden, Balanced coalgebroids, \textsl{Theory Appl.\ Categ.\ }\textbf{7} (2000), 71--147.
@@
 Available as \href{https://arxiv.org/abs/1201.3789}{arXiv:1201.3789}.
-
-%\bibitem{Panan} F.\ Clerc, H.\ Humphrey and P.\ Panangaden, Bicategories of Markov processes,  to appear.
 
@@
 \bibitem{SSV} P.\ Schultz, D.\ Spivak and C.\ Vasilakopoulou, Dynamical systems and sheaves, \textsl{Appl.\ Cat.\ Struct.\ }\textbf{28} (2020), 1--57. 
+\href{https://doi.org/10.1007/s10485-019-09565-x}{https://doi.org/10.1007/s10485-019-09565-x}.
 Available as \href{https://arxiv.org/abs/1609.08086}{arXiv:1609.08086}.
@@
 \bibitem{Wilkinson} D.\ J.\ Wilkinson, \textsl{Stochastic Modelling for Systems Biology},
-Taylor and Francis, New York, 2006.
-
-\bibitem{Willems} J.\ C.\ Willems, The behavioral approach to open and interconnected systems, \textsl{IEEE Control Systems Magazine} \textbf{27} (2007), 46--99.
-Available as \href{https://citeseerx.ist.psu.edu/viewdoc/summary?doi=10.1.1.163.8131}{https://citeseerx.ist.psu.edu/viewdoc/summary?doi=10.1.1.163.8131}.
+Taylor and Francis, New York, 2006. \href{https://doi.org/10.1201/b11812}{https://doi.org/10.1201/b11812}.
+
+\bibitem{Willems} J.\ C.\ Willems, The behavioral approach to open and interconnected systems, \textsl{IEEE Control Systems Magazine} \textbf{27} 
+(2007), 46--99. \href{https://doi.org/10.1109/MCS.2007.906923}{https://doi.org/10.1109/MCS.2007.906923}.
 

### 2022-04-05 cospans_compositionality_3.tex
Added links for bib refs [32] and [39]

@@
 \bibitem{KSW} P.\ Katis, N.\ Sabadini and R.\ F.\ C.\ Walters, On the algebra of systems with feedback and boundary, \textsl{Rendiconti del Circolo Matematico di Palermo Serie II} \textbf{63} (2000), 123--156.
+Available at \href{https://citeseerx.ist.psu.edu/viewdoc/download?doi=10.1.1.51.5758&rep=rep1&type=pdf}{https://citeseerx.ist.psu.edu/viewdoc/download?doi=10.1.1.51.5758\&rep=rep1\&type=pdf}.
 
@@
 \bibitem{Peterson} J.\ L.\ Peterson, \textit{Petri Net Theory and the Modeling of Systems}, Prentice-Hall, New Jersey, 1981.
+Available at \href{http://dl.icdst.org/pdfs/files3/2bf95f7fde49a09814231bbcbe592526.pdf}{http://dl.icdst.org/pdfs/files3/2bf95f7fde49a09814231bbcbe592526.pdf}.
 

### 2022-04-07 cospans_compositionality_3.tex
fixed bibliography

--- 2022-04-05 cospans_compositionality_3.tex
@@
 
-\bibitem{AP} AlgebraicPetri team, GitHub repository. Available at
+\bibitem{AP} AlgebraicPetri team, GitHub repository. 
 \href{https://github.com/AlgebraicJulia/AlgebraicPetri.jl}{https://github.com/AlgebraicJulia/AlgebraicPetri.jl}.
@@
 \bibitem{BFMLP}  A.\ Baas, J.\ Fairbanks, M.\ Halter, S.\ Libkind and E.\ Patterson, An
-algebraic framework for structured epidemic modeling.
-Available at \href{https://github.com/AlgebraicJulia/Structured-Epidemic-Modeling}{https://github.com/AlgebraicJulia/Structured-Epidemic-Modeling}.
-
-\bibitem{BC} J.\ C.\ Baez and K.\ Courser, Structured cospans,  \textsl{Theory Appl.\ Categ.\ }\textbf{35} (2020), 1771--1822.   Available as \href{http://arxiv.org/abs/1911.04630}{arXiv:1911.04630}.
-
-\bibitem{BCR} J.\ C.\ Baez, B.\ Coya and F.\ Rebro, Props in circuit theory, \textsl{Theory Appl.\ Categ.\ }\textbf{33} (2018), 727--783.
-Available as \href{https://arxiv.org/abs/1707.08321}{arXiv:1707.08321}.
-
-\bibitem{BE} J.\ C.\ Baez and J.\ Erbele, Categories in control, \textsl{Theory Appl.\ Categ.} {\bf 30} (2015), 836--881. Available as \href{http://arxiv.org/abs/1405.6881}{arXiv:1405.6881}.
+algebraic framework for structured epidemic modeling.  \href{https://doi.org/10.48550/arxiv.2203.16345}{https://doi.org/10.48550/arxiv.2203.16345}.
+
+\bibitem{BC} J.\ C.\ Baez and K.\ Courser, Structured cospans,  \textsl{Theory Appl.\ Categ.\ }\textbf{35} (2020), 1771--1822.
+	\href{https://doi.org/10.48550/arXiv.1911.04630}{https://doi.org/10.48550/arXiv.1911.04630}.
+
+\bibitem{BCR} J.\ C.\ Baez, B.\ Coya and F.\ Rebro, Props in network theory, \textsl{Theory Appl.\ Categ.\ }\textbf{33} (2018), 727--783.
+	\href{https://doi.org/10.48550/arXiv.1707.08321}{https://doi.org/10.48550/arXiv.1707.08321}.
+
+\bibitem{BE} J.\ C.\ Baez and J.\ Erbele, Categories in control, \textsl{Theory Appl.\ Categ.} {\bf 30} (2015), 836--881.
+\href{https://doi.org/10.48550/arXiv.1405.6881}{https://doi.org/10.48550/arXiv.1405.6881}.
 
 \bibitem{BF}  J.\ C.\ Baez and B.\ Fong, A compositional framework for passive linear networks, \textsl{Theory Appl.\ Categ.\ }\textbf{33} (2018), 1158--1222.
-Available as \href{http://arxiv.org/abs/1504.05625}{arXiv:1504.05625}.
-
-\bibitem{BFP} J.\ C.\ Baez, B.\ Fong and B.\ S.\ Pollard, A compositional framework for Markov processes, 
-\textsl{Jour. Math. Phys.} \textbf{57} (2016), 033301. 
-\href{https://doi.org/10.1063/1.4941578}{https://doi.org/10.1063/1.4941578}. Available as 
-\href{http://arxiv.org/abs/1508.06448}{arXiv:1508.06448}.
+\href{https://doi.org/10.48550/arXiv.1504.05625}{https://doi.org/10.48550/arXiv.1504.05625}.
+
+\bibitem{BFP} J.\ C.\ Baez, B.\ Fong and B.\ S.\ Pollard, A compositional framework for Markov processes, \textsl{Jour. Math. Phys.} \textbf{57} (2016), 033301. 
+\href{https://doi.org/10.1063/1.4941578}{https://doi.org/10.1063/1.4941578}.
 
@@
 \href{https://doi.org/10.1017/s0960129520000043}{https://doi.org/10.1017/s0960129520000043}.
-Available as 
-\href{https://arxiv.org/abs/1808.05415}{arXiv:1808.05415}.
-
-\bibitem{BP} J.\ C.\ Baez and B.\ S.\ Pollard, A compositional framework for chemical reaction networks, \textsl{Rev.\ Math.\ Phys.\ }\textbf{29} 
-(2017), 1750028. \href{https://doi.org/10.1142/S0129055X17500283}{https://doi.org/10.1142/S0129055X17500283}.
-Available as \href{http://arxiv.org/abs/1704.02051}{arXiv:1704.02051}.
+Also available at
+\href{https://doi.org/10.1017/S0960129520000043}{https://doi.org/10.1017/S0960129520000043}.
+
+\bibitem{BP} J.\ C.\ Baez and B.\ S.\ Pollard, A compositional framework for reaction networks, \textsl{Rev.\ Math.\ Phys.\ }\textbf{29} 
+(2017), 1750028. \href{https://doi.org/10.1142/S0129055X17500283}{https://doi.org/10.1142/S0129055X17500283}.   Also available at 
+\href{https://doi.org/10.48550/arXiv.1508.06448}{https://doi.org/10.48550/arXiv.1508.06448}.
 
 \bibitem{BFV} G.\ Bakirtzis, C.\ H.\ Fleming and C.\ Vasilakopoulou, Categorical semantics of cyber-physical systems theory, \textsl{ACM Trans.\ 
-Cyber-Phys.\ Syst.\ } \textbf{5} (2021). \href{https://doi.org/10.1145/3461669}{https://doi.org/10.1145/3461669}. Available as 
-\href{https://arxiv.org/abs/2010.08003}{arXiv:2010.08003}.
+Cyber-Phys.\ Syst.\ } \textbf{5} (2021).
+\href{https://doi.org/10.1145/3461669}{https://doi.org/10.1145/3461669}.
+Also available at \href{https://doi.org/10.48550/arXiv.2010.08003}{https://doi.org/10.48550/arXiv.2010.08003}.
 
@@
 eds.\ P.\ Baldan and D.\ Gorla, Lecture Notes in Computer Science \textbf{8704}, Springer, Berlin, 2014, pp.\ 435--450. 
-\href{https://doi.org/10.1007/978-3-662-44584-6\_30}{https://doi.org/10.1007/978-3-662-44584-6\_30}.  Available at 
+\href{https://doi.org/10.1007/978-3-662-44584-6\_30}{https://doi.org/10.1007/978-3-662-44584-6\_30}.  Also available at 
 \href{http://users.ecs.soton.ac.uk/ps/papers/sfg.pdf}{http://users.ecs.soton.ac.uk/ps/papers/sfg.pdf}.
@@
 
-\bibitem{Courser} K.\ Courser, A bicategory of decorated cospans, \textsl{Theory Appl.\ Categ.} \textbf{32} (2017), 995--1027. Available as \href{https://arxiv.org/abs/1605.08100}{arXiv:1605.08100}.
+\bibitem{Courser} K.\ Courser, A bicategory of decorated cospans, \textsl{Theory Appl.\ Categ.} \textbf{32} (2017), 995--1027.
+\href{https://doi.org/10.48550/arXiv.1605.08100}{https://doi.org/10.48550/arXiv.1605.08100}
 
 \bibitem{CourserThesis} K.\ Courser, \textsl{Open Systems: a Double Categorical Perspective}, Ph.D.\ thesis, Department of Mathematics, U.\ C.\ Riverside, 2020.  
-Available as \href{https://arxiv.org/abs/2008.02394}{arXiv:2008.02394}.
+\href{https://doi.org/10.48550/arXiv.2008.02394}{https://doi.org/10.48550/arXiv.2008.02394}.
 
@@
 
-\bibitem{Fong} B.\ Fong, Decorated cospans, \emph{Theory Appl.\ Categ.} \textbf{30} (2015), 1096--1120.  Available as 
-\href{http://arxiv.org/abs/1502.00872}{arXiv:1502.00872}.
+\bibitem{Fong} B.\ Fong, Decorated cospans, \emph{Theory Appl.\ Categ.} \textbf{30} (2015), 1096--1120.  \href{https://doi.org/10.48550/arXiv.1502.00872}{https://doi.org/10.48550/arXiv.1502.00872}.
 
 \bibitem{FongThesis} B.\ Fong, \textsl{The Algebra of Open and Interconnected Systems},
-Ph.D.\ thesis, Computer Science Department, University of Oxford, 2016.
-Available as \href{https://arxiv.org/abs/1609.05382}{arXiv:1609.05382}.
+Ph.D.\ thesis, Computer Science Department, University of Oxford, 2016.  \href{https://doi.org/10.48550/arXiv.1609.05382}{https://doi.org/10.48550/arXiv.1609.05382}
 
@@
 of the 31st Annual ACM/IEEE Symposium on Logic in Computer Science (LICS)}, IEEE, New York, 2016, pp.\ 1--10. 
-\href{https://doi.org/10.1145/2933575.2934556}{https://doi.org/10.1145/2933575.2934556}. Available as 
-\href{http://arxiv.org/abs/510.05076}{arXiv:1510.05076}.
+\href{https://doi.org/10.1145/2933575.2934556}{https://doi.org/10.1145/2933575.2934556}. Also available at
+\href{https://doi.org/10.48550/arXiv.1510.05076}{https://doi.org/10.48550/arXiv.1510.05076}.
 
@@
 
-\bibitem{HS}  L.\ W.\ Hansen and M.\ Shulman, Constructing symmetric monoidal bicategories functorially.  Available as \href{https://arxiv.org/abs/1910.09240}{arXiv:1910.09240}.
+\bibitem{HS}  L.\ W.\ Hansen and M.\ Shulman, Constructing symmetric monoidal bicategories functorially.
+Available as \href{https://doi.org/10.48550/arXiv.1910.09240}{https://doi.org/10.48550/arXiv.1910.09240}.
 
@@
 \bibitem{KSW} P.\ Katis, N.\ Sabadini and R.\ F.\ C.\ Walters, On the algebra of systems with feedback and boundary, \textsl{Rendiconti del Circolo Matematico di Palermo Serie II} \textbf{63} (2000), 123--156.
+\href{https://citeseerx.ist.psu.edu/viewdoc/download?doi=10.1.1.51.5758&rep=rep1&type=pdf}{https://citeseerx.ist.psu.edu/viewdoc/download?doi=10.1.1.51.5758\&rep=rep1\&type=pdf}.
 
@@
 \bibitem{Lawvere} F.\ W.\ Lawvere, State categories and response functors, unpublished manuscript, 1986.
-Available at \href{https://tinyurl.com/state}{https://tinyurl.com/state-}  \href{https://tinyurl.com/state-categories}{categories}.
+\href{https://github.com/mattearnshaw/lawvere/blob/master/pdfs/1986-state-categories-and-response-functors.pdf}{https://github.com/mattearnshaw/lawvere/blob/master/pdfs/1986-state-categories-and-response-functors.pdf}
 
@@
 \bibitem{MV} J.\ Moeller and C.\ Vasilakopoulou, Monoidal Grothendieck construction, \textsl{Theory Appl.\ Categ.\ }\textbf{35} (2020), 1159--1207.
-Available as \href{https://arxiv.org/abs/1809.00727}{arXiv:1809.00727}.
+\href{https://doi.org/10.48550/arXiv.1809.00727}{https://doi.org/10.48550/arXiv.1809.00727}.
 
 \bibitem{Niefield} S.~Niefield, Span, cospan, and other double categories, \textsl{Theory Appl.\ Categ.} \textbf{26} (2012), 729--742.
-Available as \href{https://arxiv.org/abs/1201.3789}{arXiv:1201.3789}.
+\href{https://doi.org/10.48550/arXiv.1201.3789}{https://doi.org/10.48550/arXiv.1201.3789}.
 
 \bibitem{Peterson} J.\ L.\ Peterson, \textit{Petri Net Theory and the Modeling of Systems}, Prentice-Hall, New Jersey, 1981.
+\href{http://dl.icdst.org/pdfs/files3/2bf95f7fde49a09814231bbcbe592526.pdf}{http://dl.icdst.org/pdfs/files3/2bf95f7fde49a09814231bbcbe592526.pdf}.
 
@@
 Riverside, 2017.
-Available as \href{https://arxiv.org/abs/1709.09743}{arXiv:1709.09743}.
+\href{https://doi.org/10.48550/arXiv.1709.09743}{https://doi.org/10.48550/arXiv.1709.09743}.
 
@@
 
-\bibitem{Riehl} E.\ Riehl, \textsl{Category Theory In Context}, Dover Publications, New York, 2016. Available at \href{https://math.jhu.edu/~eriehl/context/}{https://math.jhu.edu/~eriehl/context/}.
+\bibitem{Riehl} E.\ Riehl, \textsl{Category Theory In Context}, Dover Publications, New York, 2016.  \href{https://math.jhu.edu/~eriehl/context/}{https://math.jhu.edu/~eriehl/context/}.
 
@@
 \href{https://doi.org/10.1007/s10485-019-09565-x}{https://doi.org/10.1007/s10485-019-09565-x}.
-Available as \href{https://arxiv.org/abs/1609.08086}{arXiv:1609.08086}.
+Also available at \href{https://doi.org/10.48550/arXiv.1609.08086}{https://doi.org/10.48550/arXiv.1609.08086}.
 
 \bibitem{Shulman2008} M.\ Shulman, Framed bicategories and monoidal fibrations, \textsl{Theory Appl.\ Categ.\ }\textbf{20} (2008), 650--738.
-Available as \href{https://arxiv.org/abs/0706.1286}{arXiv:0706.1286}.
+\href{https://doi.org/10.48550/arXiv.0706.1286}{https://doi.org/10.48550/arXiv.0706.1286}.
 
@@
 
-\bibitem{Stay} M.\ Stay, Compact closed bicategories, \textsl{Theory Appl.\ Categ.\ }\textbf{31} (2016), 755--798.   Available as \href{http://arxiv.org/abs/1301.1053}{arXiv:1301.1053}.
+\bibitem{Stay} M.\ Stay, Compact closed bicategories, \textsl{Theory Appl.\ Categ.\ }\textbf{31} (2016), 755--798.
+\href{https://doi.org/10.48550/arXiv.1301.1053}{https://doi.org/10.48550/arXiv.1301.1053}.
 
 \bibitem{VSL} D.\ Vagner, D.\ Spivak and E.\ Lerman, Algebras of open dynamical systems on the operad of wiring diagrams, \textsl{Theory Appl.\ Categ.\ } \textbf{30} (2015), 1793--1822.
-Available as \href{https://arxiv.org/abs/1408.1598}{arXiv:1408.1598}.
+\href{https://doi.org/10.48550/arXiv.1408.1598}{https://doi.org/10.48550/arXiv.1408.1598}.
 

### 2022-04-07 cospans_compositionality_3.tex
a few edits

@@
 \bibitem{BFP} J.\ C.\ Baez, B.\ Fong and B.\ S.\ Pollard, A compositional framework for Markov processes, \textsl{Jour. Math. Phys.} \textbf{57} (2016), 033301. 
-\href{https://doi.org/10.1063/1.4941578}{https://doi.org/10.1063/1.4941578}.
+\href{https://doi.org/10.1063/1.4941578}{https://doi.org/10.1063/1.4941578}. Also available at 
+\href{https://doi.org/10.48550/arXiv.1508.06448}{https://doi.org/10.48550/arXiv.1508.06448}.
 
@@
 Also available at
-\href{https://doi.org/10.1017/S0960129520000043}{https://doi.org/10.1017/S0960129520000043}.
+\href{https://doi.org/10.48550/arXiv.1808.05415}{https://doi.org/10.48550/arXiv.1808.05415}.
 
@@
 (2017), 1750028. \href{https://doi.org/10.1142/S0129055X17500283}{https://doi.org/10.1142/S0129055X17500283}.   Also available at 
-\href{https://doi.org/10.48550/arXiv.1508.06448}{https://doi.org/10.48550/arXiv.1508.06448}.
+\href{https://doi.org/10.48550/arXiv.1704.02051}{https://doi.org/10.48550/arXiv.1704.02051}.
 
@@
 eds.\ P.\ Baldan and D.\ Gorla, Lecture Notes in Computer Science \textbf{8704}, Springer, Berlin, 2014, pp.\ 435--450. 
-\href{https://doi.org/10.1007/978-3-662-44584-6\_30}{https://doi.org/10.1007/978-3-662-44584-6\_30}.  Also available at 
-\href{http://users.ecs.soton.ac.uk/ps/papers/sfg.pdf}{http://users.ecs.soton.ac.uk/ps/papers/sfg.pdf}.
+\href{https://doi.org/10.1007/978-3-662-44584-6\_30}{https://doi.org/10.1007/978-3-662-44584-6\_30}.  
+%Also available at 
+%\href{http://users.ecs.soton.ac.uk/ps/papers/sfg.pdf}{http://users.ecs.soton.ac.uk/ps/papers/sfg.pdf}.
 
@@
 
-\bibitem{HS}  L.\ W.\ Hansen and M.\ Shulman, Constructing symmetric monoidal bicategories functorially.
-Available as \href{https://doi.org/10.48550/arXiv.1910.09240}{https://doi.org/10.48550/arXiv.1910.09240}.
+\bibitem{HS}  L.\ W.\ Hansen and M.\ Shulman, Constructing symmetric monoidal bicategories 
+functorially. \href{https://doi.org/10.48550/arXiv.1910.09240}{https://doi.org/10.48550/arXiv.1910.09240}.
 
@@
 
-\bibitem{KSW} P.\ Katis, N.\ Sabadini and R.\ F.\ C.\ Walters, On the algebra of systems with feedback and boundary, \textsl{Rendiconti del Circolo Matematico di Palermo Serie II} \textbf{63} (2000), 123--156.
-\href{https://citeseerx.ist.psu.edu/viewdoc/download?doi=10.1.1.51.5758&rep=rep1&type=pdf}{https://citeseerx.ist.psu.edu/viewdoc/download?doi=10.1.1.51.5758\&rep=rep1\&type=pdf}.
+\bibitem{KSW} P.\ Katis, N.\ Sabadini and R.\ F.\ C.\ Walters, On the algebra of systems with feedback and boundary, \textsl{Rendiconti del Circolo 
+Matematico di Palermo Serie II} \textbf{63} (2000), 123--156. 
+\href{https://citeseerx.ist.psu.edu/viewdoc/download?doi=10.1.1.51.5758&rep=rep1&type=pdf}{ 
+https://citeseerx.ist.psu.edu/viewdoc/download?doi=10.1.1.51.5758\&rep=rep1\&type=pdf}.
 
@@
 \bibitem{Lawvere} F.\ W.\ Lawvere, State categories and response functors, unpublished manuscript, 1986. 
-\href{https://github.com/mattearnshaw/lawvere/blob/master/pdfs/1986-state-categories-and-response-functors.pdf}{https://github.com/mattearnshaw/lawvere/blob/master/pdfs/1986-state-categories-and-response-functors.pdf}
+\href{https://github.com/mattearnshaw/lawvere/blob/master/pdfs/1986-state-categories-and-response-functors.pdf}{
+https://github.com/mattearnshaw/lawvere/blob/master/pdfs/1986-state-categories-and-response-functors.pdf}
 
@@
 
-%\bibitem{RSW} R.\ Rosebrugh, N.\ Sabadini and R.\ F.\ C.\ Walters, Generic commutative separable algebras and cospans of graphs, \textsl{Theory Appl.\ Categ.\ }\textbf{15} (2005), 164--177.
-
-%\bibitem{Reb} F.\ Rebro, Constructing the bicategory Span$_{2}(\mathrm{A})$. Available as \href{https://arxiv.org/abs/1501.00792}{arXiv:1501.00792}.
-
 \bibitem{Riehl} E.\ Riehl, \textsl{Category Theory In Context}, Dover Publications, New York, 2016.  \href{https://math.jhu.edu/~eriehl/context/}{https://math.jhu.edu/~eriehl/context/}.
@@
 
-\bibitem{Shulman2010} M.\ Shulman, Constructing symmetric monoidal bicategories. Available as \href{http://arxiv.org/abs/1004.0993}{arXiv:1004.0993}.
+\bibitem{Shulman2010} M.\ Shulman, Constructing symmetric monoidal bicategories. 
+\href{https://doi.org/10.48550/arXiv.1004.0993}{https://doi.org/10.48550/arXiv.1004.0993}.
 

### 2022-04-07 cospans_compositionality_3.tex
fixed more refs

@@
 % in LaTeX
-% 2021/04/03 - third version sent to Compositionality
+% 2021/04/07 - preparing third version sent to Compositionality
 
@@
 \bibitem{BungeFiore} M.\ Bunge and M.\ Fiore, Unique factorisation lifting functors and categories of linearly-controlled processes, \textsl{Math.\ 
-Struct.\ Comput.\ Sci.\ } \textbf{10} (2000), 137--163. \href{https://doi.org/10.1017/S0960129599003023}{https://doi.org/10.1017/S0960129599003023}.
+Struct.\ Comput.\ Sci.\ } \textbf{10} (2000), 137--163. \hfill \break
+\href{https://doi.org/10.1017/S0960129599003023}{https://doi.org/10.1017/S0960129599003023}.
 
@@
 
-\bibitem{Fong} B.\ Fong, Decorated cospans, \emph{Theory Appl.\ Categ.} \textbf{30} (2015), 1096--1120.  \href{https://doi.org/10.48550/arXiv.1502.00872}{https://doi.org/10.48550/arXiv.1502.00872}.
+\bibitem{Fong} B.\ Fong, Decorated cospans, \emph{Theory Appl.\ Categ.} \textbf{30} (2015), 1096--1120.  \hfill \break 
+\href{https://doi.org/10.48550/arXiv.1502.00872}{https://doi.org/10.48550/arXiv.1502.00872}.
 
@@
 \bibitem{GP1} M.\ Grandis and R.\ Par\'e, Limits in double categories, \textsl{Cah.\ Top.\ G\'eom.\ Diff.} \textbf{40} (1999), 162--220.
+\href{http://www.numdam.org/item/CTGDC_1999__40_3_162_0/}{http://www.numdam.org/item/CTGDC$\underline{\;}$1999$\underline{\;\;}$40$\underline{\;}$3$\underline{\;}$162$\underline{\;}$0/}
 
@@
  \textsl{Cah.\ Top.\ G\'eom.\ Diff.} \textbf{45} (2004), 193--240.
+ \href{http://www.numdam.org/item/CTGDC_2004__45_3_193_0/}{http://www.numdam.org/item/CTGDC$\underline{\;}$2004$\underline{\;\;}$45$\underline{\;}$3$\underline{\;}$193$\underline{\;}$0/}
 
@@
 
-\bibitem{McCrudden} P.\ McCrudden, Balanced coalgebroids, \textsl{Theory Appl.\ Categ.\ }\textbf{7} (2000), 71--147.
+\bibitem{McCrudden} P.\ McCrudden, Balanced coalgebroids, \textsl{Theory Appl.\ Categ.\ }\textbf{7} (2000), 71--147.  \hfill  \break
+ \href{https://www.emis.de/journals/TAC/volumes/7/n6/7-06abs.html}{https://www.emis.de/journals/TAC/volumes/7/n6/7-06abs.html}
 
@@
 
-\bibitem{Shulman2010} M.\ Shulman, Constructing symmetric monoidal bicategories. 
+\bibitem{Shulman2010} M.\ Shulman, Constructing symmetric monoidal bicategories. \hfill \break
 \href{https://doi.org/10.48550/arXiv.1004.0993}{https://doi.org/10.48550/arXiv.1004.0993}.
@@
 \bibitem{Stay} M.\ Stay, Compact closed bicategories, \textsl{Theory Appl.\ Categ.\ }\textbf{31} (2016), 755--798.
-\href{https://doi.org/10.48550/arXiv.1301.1053}{https://doi.org/10.48550/arXiv.1301.1053}.
+\hfill \break \href{https://doi.org/10.48550/arXiv.1301.1053}{https://doi.org/10.48550/arXiv.1301.1053}.
 

### 2022-04-17 cospans_compositionality_4.tex
I will try to fix the Petri net problems in this version
I tried to fix section 6.3.  Check it out!

--- 2022-04-07 cospans_compositionality_3.tex
@@
 % in LaTeX
-% 2021/04/07 - preparing third version sent to Compositionality
+% 2021/04/16 - 4th version sent to Compositionality: version for publication - fixing mistakes
 
@@
 
-We thank Daniel Cicala, Brendan Fong, Joe Moeller and Morgan Rogers for helpful conversations, and the referees for their many useful suggestions.
+We thank Daniel Cicala, Brendan Fong, Sophie Libkind, Joe Moeller and Morgan Rogers for helpful conversations, and the referees for their many useful suggestions.
 We especially thank Michael Shulman for suggesting a proof strategy that greatly improved this paper.
@@
 They used Fong's original decorated cospans to do this.
-Later, structured cospans were used to promote the first of these categories to a double category \cite[Section 6.16]{BC}.
-Here we show that the second of these categories, with open dynamical systems as morphisms, \emph{cannot} be made into a double category using structured cospans.
-However, we \emph{can} do it using decorated cospans.
+Here we show we show how to promote these categories to double categories using our new approach to decorated cospans.
 
@@
 Now we turn to the details.
-A \define{Petri net with rates} is a Petri net $s,t \maps T \to \N[S]$ together with a function $r \maps T \to (0,\infty)$ assigning to each transition $\tau \in T$ a positive real number called its \define{rate constant}.
+A \define{Petri net with rates} is a Petri net $s,t \maps T \to \N[S]$ together with a function $r \maps T \to [0,\infty)$ assigning to each transition $\tau \in T$ a nonnegative real number called its \define{rate constant}.
 There is a category $\Petri_r$ whose objects are Petri nets with rates, where a morphism from
@@
  \[   \xymatrix{ (0,\infty) & T' \ar[l]_-{r'} \ar@<-.5ex>[r]_-{t'} \ar@<.5ex>[r]^-{s'} & \N[S'] }\]
-is a morphism of the underlying Petri nets such that the following diagram also commutes:
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (E) at (3,-0.5) {$(0,\infty)$};
-\node (G) at (4,0) {$T$};
-\node (G') at (4,-1) {$T'$};
-\path[->,font=\scriptsize,>=angle 90]
-(G) edge node[right]{$g$} (G')
-(G) edge node[above]{$r$} (E)
-(G') edge node[below]{$r'$} (E);
-\end{tikzpicture}
-\]
-There is a functor $R \maps \Petri_r \to \Set$ sending any Petri net with rates to its set of places, and this has a left adjoint $L \maps \Set \to \Petri_r$ sending any set $S$ to the Petri net with $S$ as its set of places and no transitions \cite[Lemma 6.18]{BC}.
-Since $\Petri_r$ has finite colimits \cite[Lemma 6.19]{BC}, it follows that there is a symmetric monoidal double category ${}_L \lCsp(\Petri_r)$ where:
-\begin{itemize}
-\item objects are finite sets,
-\item vertical 1-morphisms are functions,
-\item horizontal 1-cells are \define{open Petri nets with rates}, namely diagrams in $\Petri_r$ of the form
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (D) at (-3,0) {$L(X)$};
-\node (E) at (-2,0) {$P$};
-\node (F) at (-1,0) {$L(Y)$,};
-\path[->,font=\scriptsize,>=angle 90]
-(D) edge node [above] {$i$} (E)
-(F) edge node [above] {$o$} (E);
-\end{tikzpicture}
-\]
-\item 2-morphisms are diagrams in $\Petri_r$ of the form
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (E) at (3,0) {$L(X)$};
-\node (F) at (5,0) {$L(Y)$};
-\node (G) at (4,0) {$P$};
-\node (E') at (3,-1) {$L(X')$};
-\node (F') at (5,-1) {$L(Y')$.};
-\node (G') at (4,-1) {$P'$};
-\path[->,font=\scriptsize,>=angle 90]
-(F) edge node[above]{$i$} (G)
-(E) edge node[left]{$L(f)$} (E')
-(F) edge node[right]{$L(g)$} (F')
-(G) edge node[left]{$\alpha$} (G')
-(E) edge node[above]{$o$} (G)
-(E') edge node[below]{$i'$} (G')
-(F') edge node[below]{$o'$} (G');
-\end{tikzpicture}
-\]
-\end{itemize}
-
-We can equivalently describe open Petri nets with rates using decorated cospans.
+is a morphism of the underlying Petri nets whose map $g \maps T \to T'$ obeys
+\[    r'(\tau') = \sum_{\{\tau \in T: g(\tau) = \tau'\}} r(\tau) \]
+for all $\tau' \in T'$.
+This definition was suggested by Sophie Libkind; it agrees with the earlier definition \cite{BP} in the case of isomorphisms, but not in general, and the difference is important here.
+
+We can describe open Petri nets with rates using decorated cospans.
 There is a symmetric lax monoidal pseudofunctor $F \maps (\Fin\Set, +) \to (\Cat, \times)$ such that for any finite set $S$, the category $F(S)$ has:
@@
 \end{itemize}
-This gives a symmetric monoidal double category $F \lCsp$, and using \cref{thm:equiv} we can show that this is isomorphic, as a symmetric monoidal double category, to ${}_L \lCsp(\Petri_r)$.
-
-All this so far is very similar to the previous examples.
-More interesting is the symmetric monoidal double category of open dynamical systems.
-A dynamical system is a vector field from the perspective of a system of first-order ordinary differential equations.
-A Petri net with rates gives a special sort of dynamical system: an \define{algebraic} vector field on $\R^n$, meaning one where the components of the vector field are polynomials in the coordinates.
-We shall think of such a vector field as a special sort of function $v \maps \R^n \to \R^n$.
+This gives a symmetric monoidal double category $F \lCsp$ where the horizontal 1-cells are called \define{open Petri nets with rates}.
+
+There is also a symmetric monoidal double category of open dynamical systems.
+A dynamical system is a vector field as seen from the perspective of a system of first-order ordinary differential equations.
+A Petri net with rates gives a special sort of dynamical system: an \define{algebraic} vector field on $\R^S$ for some finite set $S$, meaning a vector field whose components are polynomials in the coordinates.
+We shall think of such a vector field as a special sort of function $v \maps \R^S \to \R^S$.
 
@@
 \] 
-Here $\theta$ is a monoidal natural transformation given as follows.  For any finite set $S$, $\theta_S \maps F(S) \to D(S)$ maps any Petri nets with rates 
+Here $\theta$ is given as follows.  For any finite set $S$, $\theta_S \maps F(S) \to D(S)$ maps any Petri net with rates 
 \[   \xymatrix{ (0,\infty) & T \ar[l]_-r \ar@<-.5ex>[r]_-t \ar@<.5ex>[r]^-s & \N[S] }\]
@@
 and we think of $t(\tau), s(\tau) \in \N[S]$ as vectors in $\R^S$.
-This formula is explained in the paper with Pollard, where it is also shown that $\theta$ defines a monoidal natural transformation between functors to $(\Set,\times)$ \cite[Theorem 18]{BP}.
-As such, it automatically becomes a monoidal natural transformation between the functors $F, D \maps (\Fin\Set,+) \to (\Cat,\times)$.
+This formula is explained in the paper with Pollard \cite{BP}.
+One can check that $\theta$ extends to a monoidal natural transformation between the functors $F, D \maps (\Fin\Set,+) \to (\Cat,\times)$.
 Thus, it defines a symmetric monoidal double functor $\graysquare \maps F \lCsp \to D \lCsp$.

### 2022-04-17 cospans_compositionality_4.tex
Tried to fix section 6.3 - check it out!

@@
 This formula is explained in the paper with Pollard \cite{BP}.
-One can check that $\theta$ extends to a monoidal natural transformation between the functors $F, D \maps (\Fin\Set,+) \to (\Cat,\times)$.
+Using the new definition of morphisms in $F(S)$, one can check that $\theta$ extends to a monoidal natural transformation between the functors $F, D \maps (\Fin\Set,+) \to (\Cat,\times)$.
 Thus, it defines a symmetric monoidal double functor $\graysquare \maps F \lCsp \to D \lCsp$.

### 2022-04-17 cospans_compositionality_4.tex
fixed paragraph starting on p. 29 with "In applications"

@@
 
-In applications, this double functor lets us turn an open Petri net with rates into an open dynamical system as follows.  Given a Petri net with rates $P$ and defining $v$ as above, we
-obtain a system of first-order ordinary differential equations for a function $c \maps \R \to \R^S$ 
+In applications, this double functor lets us turn an open Petri net with rates into an open dynamical system as follows.
+Given a Petri net with rates and defining $v$ as above, we obtain a system of first-order ordinary differential equations for a time-dependent function $c \maps \R \to \R^S$
 called the \define{rate equation}:
 \[    \frac{d}{dt} c(t) = v(c(t)) .  \]
-More generally, when $P$ is part of an open Petri net with rates
-\[
-\begin{tikzpicture}[scale=1.5]
-\node (D) at (-3,0) {$L(X)$};
-\node (E) at (-2,0) {$P$};
-\node (F) at (-1,0) {$L(Y)$,};
+More generally, given an open Petri net with rates
+\[
+\begin{tikzpicture}[scale=1.5]
+\node (D) at (-3,0) {$X$};
+\node (E) at (-2,0) {$S$};
+\node (F) at (-1,0) {$Y,$};
+\node (G) at (0,0) {$P \in F(S)$};
 \path[->,font=\scriptsize,>=angle 90]
@@
 \]
-we get an open dynamical system called the \define{open rate equation}:
+we get an equation called the \define{open rate equation}:
 \[     \frac{d}{dt} c(t) = v(c(t))  + i_*(I(t)) - o_*(O(t)) \]
-where $I \maps \R \to \R^X$ and $O \maps \R \to \R^Y$ are arbitrary smooth functions describing \define{inflows} and \define{outflows}, respectively.
+where $v$ is defined as above and $I \maps \R \to \R^X$ and $O \maps \R \to \R^Y$ are arbitrary smooth functions describing \define{inflows} and \define{outflows}, respectively.
 Applying this prescription to the open Petri net with rates shown at the start of this section one gets the differential equations \cref{eq:openPetrir}.

### 2022-04-17 cospans_compositionality_4.tex
fixed paragraph starting on p. 29 with "In applications"

@@
 In applications, this double functor lets us turn an open Petri net with rates into an open dynamical system as follows.
-Given a Petri net with rates and defining $v$ as above, we obtain a system of first-order ordinary differential equations for a time-dependent function $c \maps \R \to \R^S$
+Given a Petri net with rates and defining $v$ as above, we obtain a system of first-order ordinary differential equations for a function $c \maps \R \to \R^S$
 called the \define{rate equation}:

### 2022-04-18 cospans_compositionality_4.tex
another change on p. 29
minor fixes

@@
 
-In chemistry, population biology, epidemiology and other fields, modelers use `Petri nets with rates', where the transitions are labeled with positive real numbers called `rate constants' \cite{Haas,Koch,Wilkinson}.
+In chemistry, population biology, epidemiology and other fields, modelers use `Petri nets with rates', where the transitions are labeled with nonnegative real numbers called `rate constants' \cite{Haas,Koch,Wilkinson}.
 From any Petri net with rates one can systematically construct a dynamical system.
@@
 \]
-It is an open Petri net where the transitions are labeled with rate constants $r_1, r_2 > 0$.
+It is an open Petri net where the transitions are labeled with rate constants $r_1, r_2 \geq 0$.
 Here is the corresponding open dynamical system:
@@
 There is a category $\Petri_r$ whose objects are Petri nets with rates, where a morphism from
-\[   \xymatrix{ (0,\infty) & T \ar[l]_-r \ar@<-.5ex>[r]_-t \ar@<.5ex>[r]^-s & \N[S] }\]
+\[   \xymatrix{ [0,\infty) & T \ar[l]_-r \ar@<-.5ex>[r]_-t \ar@<.5ex>[r]^-s & \N[S] }\]
  to 
- \[   \xymatrix{ (0,\infty) & T' \ar[l]_-{r'} \ar@<-.5ex>[r]_-{t'} \ar@<.5ex>[r]^-{s'} & \N[S'] }\]
+ \[   \xymatrix{ [0,\infty) & T' \ar[l]_-{r'} \ar@<-.5ex>[r]_-{t'} \ar@<.5ex>[r]^-{s'} & \N[S'] }\]
 is a morphism of the underlying Petri nets whose map $g \maps T \to T'$ obeys
@@
 There is also a symmetric monoidal double category of open dynamical systems.
-A dynamical system is a vector field as seen from the perspective of a system of first-order ordinary differential equations.
+A dynamical system is a vector field, thought of as giving a system of first-order ordinary differential equations.
 A Petri net with rates gives a special sort of dynamical system: an \define{algebraic} vector field on $\R^S$ for some finite set $S$, meaning a vector field whose components are polynomials in the coordinates.
@@
 Here $\theta$ is given as follows.  For any finite set $S$, $\theta_S \maps F(S) \to D(S)$ maps any Petri net with rates 
-\[   \xymatrix{ (0,\infty) & T \ar[l]_-r \ar@<-.5ex>[r]_-t \ar@<.5ex>[r]^-s & \N[S] }\]
+\[   \xymatrix{ [0,\infty) & T \ar[l]_-r \ar@<-.5ex>[r]_-t \ar@<.5ex>[r]^-s & \N[S] }\]
 to an algebraic vector field on $\R^S$, say $v$.

### 2022-04-18 cospans_compositionality_4.tex
perhaps all errors are fixed... there's one sentence Christina found confusing.

@@
 % in LaTeX
-% 2021/04/16 - 4th version sent to Compositionality: version for publication - fixing mistakes
+% 2021/04/18 - 4th version sent to Compositionality: version for publication - fixing mistakes
 
@@
 In \cref{spinoffs} we establish the isomorphism between structured and decorated cospans at the level of bicategories and categories (via decategorification).
-In \cref{Applications} we describe applications, and show that open dynamical systems can be described using decorated cospans but not structured cospans.
+In \cref{Applications} we describe applications.
 
@@
 
-In many cases, \cref{thm:equiv} shows that the structured and decorated cospan approaches are equivalent: \cref{subsec:graphs,subsec:circuits,subsec:petri} illustrate this.
-However, in \cref{subsec:petrirates} we describe a map from open Petri nets with rates to open dynamical systems.
-The former are conveniently described using structured cospans, while the latter can only be treated using decorated cospans.
-Here \cref{thm:equiv} serves as a bridge that lets us connect the two formalisms.
+In some cases, \cref{thm:equiv} shows that the structured and decorated cospan approaches are equivalent: \cref{subsec:graphs,subsec:circuits,subsec:petri} illustrate this.
+However, in some cases decorated cospans appear to be necessary, and in \cref{subsec:petrirates} we explain why \cref{thm:equiv} does not apply to open dynamical systems.
 

### 2022-04-18 cospans_compositionality_4.tex
I think I fixed all the problems, but there's a sentence Christina doesn't like yet.
One more tiny change - just making a sentence prettier.

@@
 It becomes clear that when either structured or decorated cospans can be used, structured cospans are simpler.
-However, for open dynamical systems we need decorated cospans, for reasons we explain.
-Thus, to describe a map from open Petri nets with rates to open dynamical systems, we use decorated cospans.
+However, in some cases we need decorated cospans, for reasons we explain.
 
@@
 We now show that the decorated cospan double category $D \lCsp$ of open dynamical systems is not isomorphic to a structured cospan double category via \cref{thm:equiv}.
-Recall that in that theorem we start with the data required to build a decorated cospan category, namely a symmetric lax monoidal pseudofunctor $F \maps (\A,+) \to (\Cat,\times)$, and show that if the resulting pseudofunctor $F \maps \A \to \SMC$ factors through $\Rex$, then the opfibration $U \maps \X = \inta F \to \A$ has a left adjoint $L \maps \A \to \X$.
+Recall that in this theorem we start with the data required to build a decorated cospan category, namely a symmetric lax monoidal pseudofunctor $F \maps (\A,+) \to (\Cat,\times)$, and show that if the resulting pseudofunctor $F \maps \A \to \SMC$ factors through $\Rex$, then the opfibration $U \maps \X = \inta F \to \A$ has a left adjoint $L \maps \A \to \X$.
 We then obtain an isomorphism between decorated and structured cospan double categories, $F \lCsp \cong {}_L \lCsp(\X)$.

### 2022-04-20 cospans_compositionality_5.tex
version 5 for compositionality - corrected by Fosco

--- 2022-04-18 cospans_compositionality_4.tex
@@
 % in LaTeX
-% 2021/04/18 - 4th version sent to Compositionality: version for publication - fixing mistakes
-
-\documentclass[a4paper,onecolumn, superscriptaddress,10pt, accepted=2022-03-25, issue=SS, volume=VV, shorttitle=papers/compositionality-VV-SS]{compositionalityarticle}
+% 2021/04/20 - fifth version sent to Compositionality: version for publication
+
+\documentclass[ a4paper, onecolumn, superscriptaddress,10pt, accepted=2022-03-25, issue=3, volume=4, shorttitle=papers/compositionality-4-3 ]{compositionalityarticle}
 \pdfoutput=1
 
-\usepackage{amssymb,amsmath,stmaryrd,txfonts,mathrsfs}%,amsthm,undertilde}
+% journal reference: Compositionality 4, 3 (2022)
+% DOI: 10.32408/compositionality-4-3
+
+\usepackage{amssymb,amsmath,stmaryrd,mathrsfs,amsthm}%,undertilde}
 \usepackage{comment}
@@
 \usepackage[outline]{contour}
+
+\hyphenation{mo-no-i-dal}
 \contourlength{1.2pt}
@@
 
-\makeatletter
-\DeclareRobustCommand{\qed}{%
-  \ifmmode % if math mode, assume display: omit penalty etc.
-  \else \leavevmode\unskip\penalty9999 \hbox{}\nobreak\hfill
-  \fi
-  \quad\hbox{\qedsymbol}}
-\newcommand{\oopenbox}{\leavevmode
-  \hbox to.77778em{%
-  \hfil\vrule
-  \vbox to.675em{\hrule width.6em\vfil\hrule}%
-  \vrule\hfil}}
-\newcommand{\qedsymbol}{\oopenbox}
-\newenvironment{proof}[1][\proofname]{\par
-  \normalfont
-  \topsep6\p@\@plus6\p@ \trivlist
-  \item[\hskip\labelsep\itshape
-    #1.]\ignorespaces
-}{%
-  \qed\endtrivlist
-}
-\newcommand{\proofname}{Proof}
-\makeatother
+% \makeatletter
+% \DeclareRobustCommand{\qed}{%
+%   \ifmmode % if math mode, assume display: omit penalty etc.
+%   \else \leavevmode\unskip\penalty9999 \hbox{}\nobreak\hfill
+%   \fi
+%   \quad\hbox{\qedsymbol}}
+% \newcommand{\oopenbox}{\leavevmode
+%   \hbox to.77778em{%
+%   \hfil\vrule
+%   \vbox to.675em{\hrule width.6em\vfil\hrule}%
+%   \vrule\hfil}}
+% \newcommand{\qedsymbol}{\oopenbox}
+% \newenvironment{proof}[1][\proofname]{\par
+%   \normalfont
+%   \topsep6\p@\@plus6\p@ \trivlist
+%   \item[\hskip\labelsep\itshape
+%     #1.]\ignorespaces
+% }{%
+%   \qed\endtrivlist
+% }
+% \newcommand{\proofname}{Proof}
+% \makeatother
 
@@
 
-\newcommand{\define}[1]{{\bf \boldmath{#1}}}
-
+% \newcommand{\define}[1]{{\bf \boldmath{#1}}}
+ \let\define\textbf
 % other gunk
@@
 \newcommand{\ot}{\otimes}
+
+%=== to fix the overfull diagram
+\usepackage{adjustbox}
+\newenvironment{adju}[1][0.925]{%
+\begin{center}\begin{adjustbox}{max height=0.5\textheight, max width=#1\textwidth}}{\end{adjustbox}\end{center}}
+%=== compatible text and math fonts
+% \usepackage{newtxtext,newtxmath}
+%===
 
@@
 \item of two 2-morphisms $\alpha$ and $\beta$ is:
-\[
+\begin{adju}
 \begin{tikzpicture}[scale=1.2]
@@
 \end{tikzpicture}
-\]
+\end{adju}
 with decoration morphism $\tau_{\alpha\otimes\beta}$ given by the following diagram:

### 2022-04-21 cospans_compositionality_5.tex
final version for Compositionality (?)

@@
 % in LaTeX
-% 2021/04/20 - fifth version sent to Compositionality: version for publication
+% 2021/04/08 - third version sent to Compositionality: version for publication
 
@@
 
-% \newcommand{\define}[1]{{\bf \boldmath{#1}}}
- \let\define\textbf
+% \newcommand{\define}[1]{{{\bf \boldmath{#1}}}
+% \let\define\textbf
+\newcommand{\define}[1]{{\rm \textbf{#1}}}
+
 % other gunk
@@
   Let $\lD$ be a double category and $f\maps A\to B$ a vertical
-  1-morphism.  A \textbf{companion} of $f$ is a horizontal 1-cell
+  1-morphism.  A \define{companion} of $f$ is a horizontal 1-cell
   $\fhat\maps A\to B$ together with 2-morphisms
@@
 	\end{equation}
-  A \textbf{conjoint} of $f$, denoted $\fchk \maps B \to A$, is a
+  A \define{conjoint} of $f$, denoted $\fchk \maps B \to A$, is a
   companion of $f$ in the double category
@@
 \label{defn:fibrant}
-We say that a double category is \textbf{fibrant} if every vertical
+We say that a double category is \define{fibrant} if every vertical
 1-morphism has both a companion and a conjoint.

### 2022-04-22 cospans_arxiv_3.tex
third arXiv version = version that will appear in the journal

--- 2022-04-21 cospans_compositionality_5.tex
@@
 
-\documentclass[ a4paper, onecolumn, superscriptaddress,10pt, accepted=2022-03-25, issue=3, volume=4, shorttitle=papers/compositionality-4-3 ]{compositionalityarticle}
+\documentclass[ a4paper, onecolumn, superscriptaddress,10pt, accepted=2022-02-14, issue=3, volume=4, shorttitle=papers/compositionality-4-3 ]{compositionalityarticle}
 \pdfoutput=1
